\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_161.json :}\newline \par\Large\textbf {Title: \large  You Might Be Too Old To Work For Google }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Don't you love the hypocrisy of the left there the first one's to hate prejudice but yet there the first one's to say your \textbf{old} . \textbf{Ageism} the last acceptable prejudice\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small an Irnoy that the comentators is a younger female millenial and a middled AGED older guy.......pot calling the kettle \textbf{black}....Also isnt the Facebook owner like 36 now!?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Not to worry, fellow older tech computer savvies. NOT a problem that SEVERAL multi-BILLION \$\$\$\$\$\$\$\$\$\$\$\$  CLASS ACTION \textbf{AGE} DISCRIMINATION LAWSUITS won't solve! So rejoice: "Big Tech" has BIG, DEEP pockets, too!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I LOVE tech. I'm also 60 yrs \textbf{old}, have a Master's degree(1982) in Computer Science from a major California University, and have consistently updated my knowledge base since graduation. I know as much, or MORE about computer/electronic Tech than ANY 20 or 30 something, and am damn proud of it. I also RETIRED at \textbf{age} 50 with +3 million in my assorted 401k/money market and cd accounts, after working 30 years as an INDEPENDENT  Professional Data Analyst Programmer Consultant with consistently high 6-figure incomes throughout. The're are ALSO MILLIONS of other highly educated, happy TECH seniors,  like myself, who can run circles around our youthful, so-called "betters". So put THAT in your DATA stacks and smoke it!\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/117 & \cellcolor{green!5}1.709 \\  \hline
  \cellcolor{green!27}\small OH BOY! This pushes every button I have. I was a tech writer is various IT depts. for the worst kind of companies you can imagine; BigPharma \& Banking/Finance (I'm a little ashamed to admit it). If you look at the NLRB you may find that your job formerly classified as "Professional"  has been demoted to  "Clerical/Administrative." Mine was. There followed years of shitty jobs at as little as 50 of my peak earning capacity in the late 90s and early 21st century. At 58 I just walked away from the corporate cesspool. At that point I realized just how much 25 years in that swamp effected my physical and \textbf{mental} health. I hope millennials are turning away from the giant global corporations.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small My Mom is in her 60's and is extremely tech savvy. My Dad became pretty tech savvy before he passed away (in his 60's) too. I don't think that there is any difference in intelligence between folks in different \textbf{age} brackets. Also, the longer someone has been in the workforce, the more valuable experience that person has. I'm 35 and the fact that Google would probably see me as an aging portion of the population (better get ready for the is folks home!) is ridiculous. That's absurd. I look at people in their 50's, 60's and 70's and they don't seem even remotely \textbf{old} to me. This just seems discriminatory and silly.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/112 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Cenk, to what you say about one \textbf{age} group being smarter than another, I say you might want to consider the impact of technology on a young developing mind. The younger generations in some forms literally are smarter. They do perform better in certain areas than older people (im talking 20's versus mid 30's \& 40's), and its the exposure to technology throughout their life when they were younger which causes that to happen. The older generations did not have the same exposure while their brains were developing and much more plastic. There are facts that point towards the truth of it. What you're referencing as 'tech-savvy' is more than simply having the ability to work well with a computer or a smartphone...I think it's actually indicative of a set of skills which relates to \textbf{mental} abilities such as memory, cognition, and comprehension. To me, it makes sense why technology would improve on these \textbf{mental} skills....I can also see how the younger generations had more exposure to this than older people for obvious reasons, and how that would cause younger adults to have the edge in certain areas where older ones dont perform as well\normalsize   & \cellcolor{green!27}Age, Mental & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/195 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Just remember you will be \textbf{old} one day and also be in that same situation. Will you still be a viable employee? Or will you be let go. AND replaced by a robot/A.I?  Coming soon in the year 2030.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small There is alot of \textbf{age} discrimination in Silicon Valley    Glad you are covering it\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Pro tip: You should have enough money saved up in investments and in the bank to fully retire by the \textbf{age} of 40. It sounds ridiculous and everyone calls me an uneducated prick but I'm speaking the advice that was given to me by many of my mentors: You should start investing and saving after your first paycheck or after the first dollar you make and you should have enough assets to cover your retirement fund by 40. Many of them did that which is why 4/5 of them are at least multimillionaires. Also, if you are working a job in the tech industry, by the \textbf{age} of 40 you should be in a (preferably higher level) management position and shouldn't be doing direct coding or hardware. Why? Because Zucks is right. The younger people are smarter and tech savvyier, but older people have more experience. That's why as an older person you should be managing and mentoring the younger people and building the tech (and tech professionals) of tomorrow. Thanks for the video.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/174 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{old} but I'm just as tech savvy as the next 20 something. I just tolerate the new trends because with out it, it would be harder to stay current.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small +Valueless Dollar I'm sure you are. But unfortunately, discrimination is discrimination. It's a form of prejudice. They look at your \textbf{age} and make assumptions about you before they even meet you. Just like they do with people of other races, \textbf{gender}, etc.\normalsize   & \cellcolor{green!5}Age, Gender & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The difference is that with tech, it actually matters because you \textbf{old} people are seriously slow af trying to work your phones and shit XD\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small all these tech  company look like average \textbf{Indian} company(irrespective of field)\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Too \textbf{old} to Google, too young to die.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Shutruk Nahhunte Well, the main point is that one \textbf{age} bracket isn't significantly smarter than the neighbor. Other than that you're right. If your IQ score is 100 today you would score a 130 in the early 1900s. You would go from average to Mensa.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@jagjit bhatia Mensa holds testing events once in a while. They are not free but they're fully official and accurate. I've never taken one though. All I've taken is an online test created by Mensa Denmark. It's in Danish but "menu" and "send" means the same in both Danish and English and are the buttons you have to push once you're done. Anything else is intuitive as you have a 3x3 column and have to fill out the blank cell by clicking the one best fitting the pattern. Spoilers. The first question lists you 8 \textbf{r\textbf{ed}} balls. What should the 9th symbol? If you think another \textbf{r\textbf{ed}} ball then you click that one below.   [LINK] Your IQ is predominantly tied to early brain development (mostly the pre-natal kind) and almost can't be influenced at all once you pass 21 years of \textbf{age} where your brain is fully developed. I've nonetheless heard it can be improved by 5 points over time which is fairly insignificant in practice. I've taken the above test once when I was 14 and once again when I was 23 (you're never told if you answered correctly so you can't really cheat). The test changed a bit and I scored 124 the first time but 132 the second time. Some of that improvement could possibly be attributed to the inaccuracy of the test though.\normalsize   & \cellcolor{green!27}Age, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - General, Ethnicity - Native-American & \cellcolor{green!27}5/227 & \cellcolor{green!27}2.203 \\  \hline
  \cellcolor{green!5}\small This is why I want to start my own company. I mean seriously this is some scary shit and those who are already employed will face this issue once they reach the \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small That's what Lehman Brothers did when they started going under. The first wave of layoffs got rid of all the older people like myself. I never found a job after that. \textbf{Nobody} would hire me.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Age is just a number\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small +fielsjd  Can it though?  I think it's a bit more case by case than that.  Some people in their twenties are still \textbf{dumb} as shit, while some in their forties are wiser about the choices they make in buisness.  The opposite is also true.What has been the case in the past is that younger people are more able to handle new technology than older generations.  But this might be changing as modern generations go through rapid tech changes where as in the past each generation might have one or two true advances.  Those that were there for the rise of the internet are able to keep up with these advances much better than their contemporaries of previous generations.  Those that are teenagers today will be able to keep up with tech changes for even longer.  There eventually will come a generation that never truly falls behind.Honestly if we really want to consider ourselves advanced things like \textbf{ageism} can't be considered useful.\normalsize   & \cellcolor{green!27}Ageism, Dumb & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/163 & \cellcolor{green!27}1.227 \\  \hline
  \cellcolor{green!5}\small What goes around comes around. These people will get \textbf{OLD} eventually and they will soon feel how it feels when they get older. Give it time....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Of Course the \textbf{age} 39 is not that \textbf{old}, but when you Keep in mind that it is an average, it might as well mean, that at HP there might be a homogenous spread from 29 to 59, which is more than acceptable. Without any deviations taken into account, one can only speculate and the data doesnt really have that much of a point\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small +Orthagoni It's not the average, it's the median. But yes, it doesn't really tell you much about what \textbf{age} the employees are.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I think society is becoming more \textbf{effeminate} and superfical, and such, more \textbf{ageist}.50 years ago you'd have the likes of Cory Grant and John Wayne in lead roles.Such characters in such roles now would be lambasted (eg the Expendables) and the lead roles are mostly given to people in their early 20's, even teens.Related to this is the latent discrimination based on looks. Not only is this accepted (even by "ugly" people), its so little thought of, it doesn't even have a word for it.\normalsize   & \cellcolor{green!27}Ageist, Effeminate & \cellcolor{green!27}Age - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/88 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small yes cenk , you can say one \textbf{age} bracket is smarter than another \textbf{age} bracket.im positive 25-35 year olds are smarter than 5-15 year olds.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small The real depressing thing is at the current rate of automation, many previous "safe" jobs such as \textbf{doctors}, lawyers, \textbf{engineers} will be able to be replaced with AI and robotics in about 10 - 15 years. Will there be replacement jobs that pay well for the masses?\normalsize   & \cellcolor{green!27}Engineers, doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small +Phoenix Chastine "As to AI, um, we're nowhere near close to true AI so anyone who talks AI as if its here or soon to happen, doesn't know wtf they're talking about ;)"You're kidding right? CA is in the process of scheduling permits for auto makers to sell AI self-driving cars to the public in 2018. It's already being rolled out with some Truck lines. There are now robots with enough AI to conduct complex surgeries that were previous thought to be the domain of human \textbf{doctors} only. Paralegals, reporters, and financial advisers are being replaced with AI counterparts.Just think of how much more widespread it will be as AI matures. The Govt is rarely if ever proactive- so any solutions like basic income won't be taken seriously until the employment crisis hits and takes center stage.\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/139 & \cellcolor{green!5}0.719 \\  \hline
  \cellcolor{green!27}\small Young people are more likely to understand all of the new updates to the software and hardware that these companies use. If you just graduated with a degree in computer science, your degree is worth a lot more than someone who got the same degree in the 1960's. So even though a 65 year old's résumé might be better than a 24 year old's, it doesn't mean they are more qualified and how do you necessarily find out which one is more qualified other than their résumé? You look at their \textbf{age}, because a majority of the time, but not always, it will be the best indicator as to which one is actually up to date with the current technology. So a little bit of \textbf{ageism} is not the worst thing in the world in all cases.\normalsize   & \cellcolor{green!27}Age, Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/137 & \cellcolor{green!27}1.46 \\  \hline
  \cellcolor{green!5}\small \@Maxander2001 Yes, that is often the case. If it wasn't the case and there was actual evidence that older people knew more about this kind of stuff, these companies would be hiring them over young people. You can come up with whatever bullshit PC opinion you like, but the evidence speaks for itself: These companies, which are some of the most successful companies in the world, have found that younger people are better than older people in this particular field of work. And this is only for the actual tech jobs, I'm sure none of these companies would ever consider hiring a young lawyer fresh out of law school for legal consulting or to defend them when they get sued, because in that field, older people are better. People talk about \textbf{ageism} like it's equivalent to \textbf{racism}, it's not, \textbf{old} people and young people are actually different, both mentally and physically, and they both have their unique strengths and weaknesses.\normalsize   & \cellcolor{green!5}Ageism, Old, Racism & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - General & \cellcolor{green!5}3/160 & \cellcolor{green!5}1.875 \\  \hline
  \cellcolor{green!27}\small +markalexander774 Your analysis is too broad sweeping. Those who graduated earlier have their degrees plus hands on experience. Most new grads are a drag on corporate expenses until they get up to speed in the project they are assigned to. Now of course if an engineer/tech person doesn't update their skill set, then their value will decrease compared to new grads, but just taking new post grad language or tech classes can easily maintain the latest technology. Most colleges don't teach the latest software programming being uses by companies. Experience also gives one seasoning in networking and customer/corporate relations in getting your ideas across. The biggest reason older folks are swapped for younger is the cost savings. Two young \textbf{engineers} can be hired at the salary of one \textbf{senior} experienced engineer, and many companies will take the risk at a loss of productivity for a while to get that savings. Older employees accumulate bigger benefit payouts over time which translates to a drag on profits. With the Great Recession, many \textbf{senior} \textbf{engineers} have accepted lower paying jobs that typical went to new grads. This has resulted in millennials having a harder time getting in as companies are choosing experience over youth for the same rate of pay.\normalsize   & \cellcolor{green!27}Engineers, Senior & \cellcolor{green!27}Age - Over 65s, Nationality - General & \cellcolor{green!27}4/207 & \cellcolor{green!27}1.932 \\  \hline
  \cellcolor{green!5}\small Uygur Inc. Where the median \textbf{age} of our employees is... ?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Hobbes Tiger They're both too \textbf{old} to be considered cool at the local club ;)  I think it's funny when someone at 25 is panicking because they're getting \textbf{old} 😂😂Hey, if that's the world you want, that's the world you get ;)\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small When fresh robots and algos take over and displace brain labor we'll all be too old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small No country for \textbf{old} man\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I wonder if Ana would be so light-hearted about this if she was reporting \textbf{sexism}, instead of \textbf{ageism}? Hmm...\normalsize   & \cellcolor{green!5}Ageism, Sexism & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small +HaeravonFAQs She wouldn't. Society is lenient on \textbf{age} discrimination. Insurance companies discriminate on \textbf{age} as a matter of policy and we accept it. We need a court to create a precedent because we get mixed messages from society.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small +ikeknights I work at a tech company, but more like tech support, and I still go few times per day to an \textbf{old} chap to ask him questions on how he would do stuff and if he would have a better solution based on experience. If I ask the young guys I always get an unbased, mostly stupid answer like; try this, try that (as if I wouldn´t have tried) and then dismiss it mostly; my problem. When I ask the older guy I get a solution or if there is none immediately he even helps me and wants to solve the issue with me. Sorry that I don´t get too specific... :)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small "\textbf{Ageism}" lmao\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small I don't blame them. The tech industry needs to be adaptive, and older people are way more likely to stick with tradition (You who call republicans \textbf{old} (which they are) should really know)It's smart from a technological standpoint.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small +Kola2 What you say is far from the truth. There are a lot of "\textbf{old}" people who are very adaptive. And even if they are not, they do have experience that can help the younger generation. More startups fail than succeed and often those are (in the tech industry) by the younger generation. What you hear about is the cream on the top. The best companies use the best of every generation in their company, because all have something to offer.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small I'm 41, keep up to date with technologies, and just learned 3 more programming languages this week. Am I some kind of anomaly? You'd think so by listening to this clip. Someone mentioned "fluid" intelligence and knowledge being exclusive to different \textbf{age} groups - they are not. Grow up.  :P  But seriously, the number of years they can use an employee before they start drawing pensions is probably the biggest factor behind \textbf{age} discrimination, falling behind other qualifications for sure.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/80 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small +Don McAdams I was not trying to offend you or anything...but you cannot learn a new programming language in a week...no matter your \textbf{age}...unless u r a genius...\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Yeah tech changes, and the young person could learn the newest thing first. But 10+ years of industry experience is better than 4 year college( also university doesn't update as quickly as industry). Clients care about the \textbf{age} of employees? Make up bs reasons that you enforce yourself. Sound like bizarre cliche. I'm not \textbf{old} but this is \textbf{dumb}. California lunacy bubble.\normalsize   & \cellcolor{green!5}Age, Dumb, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/62 & \cellcolor{green!5}4.839 \\  \hline
  \cellcolor{green!27}\small +EmilyEmergency911 They have no idea what the average salary is in tech. New minted \textbf{engineers} over here earn about \$75K and up with many closer to \$100K\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Correlation does not equal causation. The number of younger people willing to go into the tech industry is greater than those who are closer to retirement. Based on the anecdotal references, you might believe that there are instances of \textbf{ageism}, but it would be an unjustified leap to assume it werequotidian or  rampant.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small I'm 26 and this is horrible. I'd rather have a mix aged range. you can lose so much knowledge if you fire based on \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Coolest Brand EverHere is a simple prereq to become a Certified Program Manager. A person in their 20's cannot be one unless they were hired in their teen years as executives. Let me show you why. Can a person in 20's become a Project Manager? Hell yes, I was one at at the \textbf{age} of 24.Program Management Professional(PgMP)®Prerequisites Secondary degree (high school diploma, associate's degree or the global equivalent)6,000 hours of project management experience10,500 hours of program management experienceor Four-year degree6,000 hours of project management experience6,000 hours of program management experience\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small I agree with the problems of \textbf{ageism}, but younger people are a little smarter. Fluid intelligence decreases after 30, and generations usually get smarter and smarter as they go on. Older people have knowledge and experience. We need both, and that's why \textbf{ageism} is bias and not just heartlessness.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small They are supposed to have the \textbf{age} of a 25 year \textbf{old}, but the experience of a 35 year \textbf{old}:)\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small This makes for such an interesting conversation if you apply these findings in other situations. For example, it shows that whether they admit it or not, companies are VERY peculiar about who they hire. They weigh in costs, appearances, you name it. And yet, despite all the constant alarm of a \textbf{gender} pay gap, we don't see companies rushing to hire women to cut costs. Just one example.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small age discrimination in the UK re employment (amongst other things) is unlawful. A person doesn't have to reveal their \textbf{age} when applying for jobs (or \textbf{gender} for that matter) - there are a few exceptions, of course.\normalsize   & \cellcolor{green!5}Age, Gender & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small how many people who are 50 years \textbf{old} know how to use a computer i know cenk is under 50 and having him even use his own app would be hard if he didnt \textbf{dumb} it down to the lowest \textbf{common} denominatorthx for this ha bisky vid\normalsize   & \cellcolor{green!27}Common, Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}3/48 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@ihartevilno i´m not a troll, and yes I can show you about 10 people I am working with every day, who know their office programs, business software and know how to enter something into google, but who cry for the IT department whenever a pop up asks them anything and who would never be able to open a \textbf{zip} file much less how to spot malware, viruses ...They basically know how to operate Amazon, youtube but wouldn´t know \textbf{ho} to turn on subtitles on youtube\normalsize   & \cellcolor{green!5}Ho, Zip & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Gender - Female sexuality & \cellcolor{green!5}2/87 & \cellcolor{green!5}2.299 \\  \hline
  \cellcolor{green!27}\small sorry, but the severe \textbf{ageism} in the tech industry comes from not hiring young people. there is a high bias against people who learned tech but don't have a degree for it, or are really \textbf{old}. the \textbf{old} people in tech hold that they've designed everything and that they're inventing minds while the younger people just coming into tech aren't really \textbf{engineers} and don't really code and are just naiive and expendable. i've been passed over for many jobs because i'm not older although i have much more experience and skills than a lot of older people do. they don't even consider you for an internship at a company until you're a junior in college even though people very well go into college knowing everything they need to know and others that are juniors know absolutely \textbf{nothing}.\normalsize   & \cellcolor{green!27}Ageism, Engineers, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters, Nationality - General & \cellcolor{green!27}5/137 & \cellcolor{green!27}3.65 \\  \hline
  \cellcolor{green!5}\small Have you considered that increased demand for tech workers has led to increased supply, and a lot of that supply comes from young college grads?  Because someone who's out of school and already a teacher or lawyer isn't likely to suddenly become a software engineer, but someone in college who has all the options in front of him or her is increasingly likely to choose a CS major.  Have you looked at the growth trends in CS majors over the last few years?  That, plus some math, may explain some (but maybe not all) of the median \textbf{age} numbers you're seeing.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small +SmartK8 But you could also turn this arround.Would you rather have a young surgeon, that has all the lastest knowledge, or an \textbf{old} doctor, that hasn´t bothered to update his knowledge in the last 10 years\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@eberbacher007 I would take the \textbf{old} one with experience and who already performed the operations. It might be \textbf{old} knowledge, but a tested one. You can go new experimental with inexperienced surgeon who never performed it himself/herself though.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Age discrimination. How \textbf{dumb} can this bitch get. The young Turks are so ignorant.\normalsize   & \cellcolor{green!27}Age, Dumb & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small +Alex Mason \textbf{Age} discrimination does exist. Many older people change their appearance and \textbf{age} to get a job\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small +Alex Mason I'm guessing you're the ignorant type to say \textbf{racism}, \textbf{homophobia}, and \textbf{sexism} doesn't exist either? Go drink your cult's koolaid already.\normalsize   & \cellcolor{green!27}Homophobia, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - General & \cellcolor{green!27}3/23 & \cellcolor{green!27}13.043 \\  \hline
  \cellcolor{green!5}\small lol both of the  CEO google on there 40 are they to \textbf{old} work in google?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Yeah just like the vid from the Fine Brothers the \textbf{elderly} and us all know that the U.S and other areas "that as you \textbf{age} you become less valuable" though it should be somewhat the opposite cause they lived through the world's mistakes and solutions. But sadly we live in a Industrialized world.\normalsize   & \cellcolor{green!27}Age, Elderly & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small From that chart, the median \textbf{age} of their employees does seem to be somewhat dependent on the \textbf{age} of the company itself: Facebook and Google are young companies and have a low median \textbf{age}; HP and IBM are older companies and have a higher median \textbf{age}. Chances are that when Zuckerberg hits 40 he might find that he doesn't like being surrounded by 20 somethings so much anymore.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/68 & \cellcolor{green!5}4.412 \\  \hline
  \cellcolor{green!27}\small Take a look at 4:54 and look at the list of companies with the median \textbf{age} of their employees...Notice how all the companies with youngest employees are also the most successful\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small The average \textbf{age} number doesn't really tell you anything. Younger people are going to be taking the majority of the entry level jobs. The entry level jobs at those companies will be the majority of the jobs. You don't have a business that is comprised of mostly supervisors.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small This is because it takes forever to explain how to do anything on computers to \textbf{old} people.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I don't believe \textbf{age}-intelligence is a big leap... IQ measurement has a dependant variable for \textbf{age}... A 20 year \textbf{old} with 150 IQ means he has the IQ of the average person who is 50 older than himself, a 30yr \textbf{old}... That's just how intelligence works...\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/46 & \cellcolor{green!5}6.522 \\  \hline
  \cellcolor{green!27}\small Nothing to do with \textbf{age}. Its all about profit. Older people have families, less likely to pull the "allnighters" tech industry likes so much. (got to have thet widget out before everyone else) Young people take those as a badge of honor!!\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I work with \textbf{old} people and they are much harder to work with.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small +melonbarmonsterI've worked with young people, and they are much harder to work with. Let's be a bit more specific here; what do you mean by "\textbf{old}"?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Then tell me why are there no young people at the CppCon ?\textbf{Old} people know how the shit works, young people just work with the shit. And no the technology world doesn't change so much, i'm now 25 years in professional programming and the changes are really minor.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small +Tyler Hamilton   DEY OVER HERE DISCRIMINATIN N CALLIN ME \textbf{OLD}! DAS NOT RYGHT!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@WikeddTung You selectively choose examples that from a cultural perspecitve we make fun of as being remedial. However, most film analysis experts will say that the level of complexity in the story structures of todays fiction are actually much more complex and have more dynamics to them. This is an average, but it generally holds true, obviously every work is not going to be better with every tick of the clock and obviously every work in one year will be better than the ones prior. Essentially your claim is that because people are taller on average today  that there were no short people before.  Take one look at BoJack Horseman, Rick and Morty, Jessica Jones, Orange is the New \textbf{Black}, or any of the other more complex popular fictions today, even something like harry potter, and you will find many more layers than earlier work, and much more depth as far as character development and behavior. Joke all you want, but that is the reality. In fact even in children's shows a whole science has been developed in order to make the show increase the intelligence of children, such shows created based on the scientific analysis of what makes kids smarter are Blues Clues and Sesame Street.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/207 & \cellcolor{green!5}0.483 \\  \hline
  \cellcolor{green!27}\small \@WikeddTung "the world has never known an intellectual flowering of the kind we're experiencing right now?" No of course not, but the reality is culture evolves and it evolves forward, so on the long term more and more intellectual revoulitions will be steps forward. Once a pattern or method is made obvious it becomes incredibly simple. Everyone who goes through highschool for the most part has all of the tools Isaac Newton spent his whole life developing. The everyday person has an understanding of theoretical physics far beyond any people before. From a neurological standpoint we are debatably less intelligent than the average neanderthall, who we interbred with for a short while, but all in all, yes, today we are smarter than we ever have been, and unless something \textbf{crazy} happens the same will be true in 40 years etc. This is more than simply biology, rather it is a combination of biology and learning, more advanced learning, leads to even more advanced learning, and with the same tools it can still grow. The human brain is incredibly advanced and our culture still has not caught up to its fullest potential I dont think it ever will. Just as a turing machine is complex enough to run any code, so too is our brain just complex enough to think almost any thought. (with the obvious exception of quantum computing)\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/229 & \cellcolor{green!27}0.437 \\  \hline
  \cellcolor{green!5}\small Check your Facts TYT! There are actually a bunch of studies showing that "People are getting smarter througout the ages". It's called the Flynn effect. Google it. It's \textbf{common} knowledge in psychology. Flynn effect!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small "But we have fired people over the \textbf{age} of 50. Oh Jimmy just turned 50.""Bye Jimmy." Hahahaha\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Most of them simply don't live up to the required standard ... they're slow and \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small PC overload. If younger people didn't have more brain power, then top chess players over 45 wouldn't be so rare. We accept other things erode with \textbf{age}, refusing to accept it just because young whippersnappers lack experience and wisdom is foolish.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Bye Jimmy! You were one of my favorite hosts, but you know, you're \textbf{old} now. So... bye.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Well, the young tech-savvy "geniuses" will get \textbf{old} too you know. In a decade THEY will be the ones who are regarded as \textbf{old} farts. Let them enjoy it while it lasts. This is the nature of this business, and I don't think it will change anytime soon. It's a bit like modelling, being a pop star or an athlete. These professions belong to the young.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small 32 is too \textbf{old} to work at BurgerKing, and subway.. and winndixie...  complain to the EEOC it gets shit done!!!  \textbf{racist} managers not hiring qualified, EDUCATED white people?\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small +meowskull Probably better in reverse- too young would lead to too radical ideas- which is pretty scary if the party you dislike gets into power. \textbf{Age} smooths people out, which is why the minimum \textbf{age} for prez is 35.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Have we mot heard of the \textbf{old} saying with \textbf{age} comes wisdom\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Yeah... The younger gen is more "tech savvy" with the tech those "\textbf{old}" techs and coders made for them. Sorry young people, but without those before you, you'd have \textbf{nothing} to build on to progress new technologies.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Lol they desperately try to disagree with the inspired intelligence gap between generations. A 4 year \textbf{old} learns any language out there in less than half the time it would take even a 24 year \textbf{old}. Kids are biologically made to learn at an increased rate to adapt to a variety of environmental hazards and cultures.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small We all \textbf{age}. I just need me. I welcome getting \textbf{old}. I do not need to impress anyone.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Why they kinda conclude \textbf{old} people don't keep up with the pace of new technology? How did they arrive at that conclusion? Oh, wait. Google supports liberals hence they can discriminate and it's not a big deal.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Ageism exists so much.I tuned 40... can't find a job... and trust me.. it's not for lack of experience. I look around the place and see the average \textbf{age}, I get told "we're not hiring supervisors", shit like that.\normalsize   & \cellcolor{green!27}Age, Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small How \textbf{old} was Steve Jobs when the iPhone came out?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I'm not saying that younger people are smarter but when you're young your brain can learn quicker than when you are in your 40's and since tech is changing so much I can see why younger brains might be more sought after. However being older than the average also gives you a certain perspective that would be beneficial in a group project.And google is famous for it's diversity so I don't see why they would only accept people under a certain \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small The digital \textbf{age} started about 20 years ago let's say the young graduates of that time started companies at the \textbf{age} of 20-30 today the oldest people in the industry  should be about 40-50 today .. so looking at the chart it is kind of reasonable\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small +Daniel Danny Dee Aguayo Unfortunately IQ does not measure the propensity for stupidity. There are such things as intelligent dumbasses. What good is it to be able to engineer any practical or abstract concept when you are a flake with no wisdom, or a hot head with no perseverance - who will most likely burn out by the \textbf{age} of 30 - and end up a depressed and insecure mess for the rest of his life? Assuming he doesn't commit suicide. A wise man measures his success by the accumulation of both wealth and life (Money and \textbf{Age}/health). Being smart is not about how adept you are at staying trendy, this is what happens when a generation never grows up past High School. Being smart is about maximizing benefit, minimizing risks, and having the foresight to spend your youth building your life, and your knowledge, so that you can enjoy it in your \textbf{old} \textbf{age}; and then pass on your wisdom and skills to the younger generation so that indeed they would be smarter than you when you were their \textbf{age}, since you are giving them a head start with your own experience.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/193 & \cellcolor{green!27}1.554 \\  \hline
  \cellcolor{green!5}\small Define " Smarter " ?   I am \textbf{old}, \textbf{age} 40, useless in most minds of today's youth. I'm retired. Enjoying life, at peace. Don't know my IQ, but I feel I did well for myself. Let the Generations move on, I sleep at night, at peace.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Markus Brorson To learn without the need for experience is true wisdom to me. Because wisdom is the capacity for foresight and thus learning the lesson ahead of the experience; or also, learning from the experience of others. You cannot be wise without first being both smart and intelligent. \textbf{Age} is not a factor here. Some are wise beyond their years and some grow \textbf{old} never having learned a lesson in their life.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small +Daniel Danny Dee Aguayo And yet we see young people getting dumber. In my line of work we hire younger people, mostly because they are cheap. But recently we found that the work they put in is worth half what someone 5 or 10 years older do. It is not simply related to experience, it is very related to the tech culture we have today. Kids spend so much time online they spend \textbf{nothing} on improving themselves. I see kids come and go at my job and many get fired for doing a pisspoor job. These are not \textbf{dumb} kids, but they lack certain social skills and handle certain tasks very poorly.20 years ago, we hired young people because they had more energy and were able to last longer. Now if you're 18-19 years \textbf{old} an apply for a job where I work, I will most likely throw that application in the trash. And this is something that alot of businesses experience. The new generation of kids are lazy and don't give a shit.\normalsize   & \cellcolor{green!5}Dumb, Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/175 & \cellcolor{green!5}1.714 \\  \hline
  \cellcolor{green!27}\small It takes more effort to learn the older you get. That's not to say a 55 year \textbf{old} can's be every bit as skilled in the same programming environment as a 25 year \textbf{old}, but it would be EASIER for the 25 year \textbf{old} to be skilled because it would be the programming environment they started out in.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/58 & \cellcolor{green!27}5.172 \\  \hline
  \cellcolor{green!5}\small Why is TYT putting up these \textbf{old} stories with today's date on them?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small +youreverydaynobody No, I meant why are they putting up segments of their own that are \textbf{old}? These are stories that TYT reported on weeks ago. Notice Ana's shirt is different in  each. I've already watched these when they first loaded them. I wish they would designate somehow that these are repeats so I don't bother watching them again.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small It's simple. A 50 year \textbf{old} with a working knowledge of fortran isn't as valuable as a 20 year \textbf{old} with a working knowledge of Java/HTML/C++.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small +Jammit Timmaj They wouldn't hire a 50 year \textbf{old} who ONLY had knowledge in a language they don't use. They would be compairing different aged employees with similar qualifications.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@calculon000I would hope the tech companies ignore \textbf{age} in their decision, but you can't get away from \textbf{ageism} much in the same manner you can't get away with \textbf{racism} or any other -ism out in the real world.\normalsize   & \cellcolor{green!5}Age, Ageism, Racism & \cellcolor{green!5}Age - General, Ethnicity - General & \cellcolor{green!5}3/39 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I doubt the performance disparity between those who are 40 and over, in the tech industry, and those who are under 30,  has anything to do with intelligence diminishing as one ages, as Ana quotes Mark Zuckerberg asserting. Instead, as people \textbf{age} they are more reluctant to take risks and this becomes an impediment to them trying things that may lead to the next big innovation.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small creativity does decline massively with \textbf{age}. kindergarteners test highest for creativity. a company like google thrives off \textbf{crazy} ideas and \textbf{old} people don't do that as well. this isn't surprising. it's not agism for its own sake.\normalsize   & \cellcolor{green!5}Age, Crazy, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small youtube google docs google maps google earth there is reason to hope in goolge self driving tech street view was a \textbf{weird} idea that i personally love. there are many times where i have used it to stroll down a boulevard in town i stayed in on my travels. just because they had failures doesn't mean they had successes and i'd be curious to see how many of these projects we're brain children of the younger tech crews but i honestly have no idea. ford and edison had a ton of failures too, so does \textbf{apple} but they have also accomplished so much.\normalsize   & \cellcolor{green!27}Apple, Weird & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/103 & \cellcolor{green!27}1.942 \\  \hline
  \cellcolor{green!5}\small +el producto yeah its christmas eve. they do this when ever they dont' have a live show. just pull so \textbf{old} ones you might not have seen.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small +OMG \textbf{BeCkY} lol they probably wont even hire you\normalsize   & \cellcolor{green!27}Becky & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Age discrimination is a real issue, Google basically discriminates the majority of the population.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@BuyTheTicket TakeTheRide  huh? they're not, Google CEO Sundar Pichai attacked trump the other dayGoogle also wants more H1B visas to get \textbf{migrant} workers, most republicans do not\normalsize   & \cellcolor{green!27}Migrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small And congress wants to raise the at which you qualify for social security.  What jobs are the \textbf{old} folks going to hold at sixty?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Young people are on average much more tech-savvy. Please enough with the political-correctness. When someone has technology in their life during their formative years, it makes a big difference in their comfort and understanding. It's not \textbf{ageism}, it's \textbf{common} sense.\normalsize   & \cellcolor{green!27}Ageism, Common & \cellcolor{green!27}Age - General, Social Class - Working class & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small +Shayan Nahrvar Actually, it has \textbf{nothing} to do with that, you can train anyone.Young people don't require high pay, they are happy to get a job, they don't have kids and work long hours. It's the same reason Google is in favor of mass migration and H1B visas. Low wages. In fact, wages in tech have been flat for almost a decade.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small "I hope I die before I get \textbf{old}..."\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Abnormal Wrench     But how \textbf{old} is \textbf{old}?  30?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small twenty years in tech is a lifetime, once you program or event new products, it takes a lot of work, based on the pet rock guy who did \textbf{nothing} and got a million dollars :P\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Matthew Madruga Which is why many companies are outsourcing, and hiring \textbf{Indian} ITs.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Matthew Madruga lol no they arent. PHP written in C, Python written in C, Perl written in C, ASP.net written in C, Java written in C\textbf{Weird} right all these web programming languages were written in C?  And there libraries are all written in C. You're talking to a veteran programmer buddy who makes 7 figures a year. Not a script kiddie like you. Googles code is mostly C and Python, with their own libraries written in C.Show me any of your websites I will hack them in a matter of hours.  Just because you program in Joomla or Wordpress both of which are PHP which is programmed in C, means you dont know shit about programming.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small \@Matthew Madruga I never would make a business because in the end(death) it would have achieved \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Matthew Madruga​​ Yes Atheist are \textbf{nothing} but cocky people with a superiority complex. Atheism is responsible for the deaths of millions. Who said I wanted to kill myself?? Life is truly meaningless, were slaves of society everything we do in the end will be fruitless since death is the greatest eraser.﻿ We live preprogrammed fake lives shaped for human survival.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small \@Seth N what are the \textbf{common} things you put before a website? lol it dosnt show you on those fake "how to do html" websites\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small +Matthew Madruga that doesn't make sense because PC sales have gone down in the last couple of yearsmost tech savy people who grew up with PC would now be around 30, not 20 since that's the iPad generationbut Google doesn't want anyone 30+it has to do with wages, it's easier to pay young people straight out of college almost \textbf{nothing}, they let them work overtime all day too\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small PC and Mac have been in competition for YEARS, so I can see a couple years its going down, people dont exactly trust windows after vista, 7 was only okay, 8 and 8.1 kinda blew it and now 10 is okay, its almost the same windows as before with \textbf{nothing} new.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small There's a reason why almost all the greatest inventions and scientific work is done by people in their 20s and 30s. It sucks to be \textbf{old}, set in your ways, disinterested in the leading edge, and find it hard to learn new stuff, but that's the nature of life. Stop libbing out and get over it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Take a long hard look at these graphs - the more web-oriented or mobile-oriented they are, the more dynamic the field is, thus the younger the want their employees while low level programming is not such a dynamic field and there, \textbf{age} does not count against you as much. But lets be honest - they want them young, because young people can be squeezed far more than older people, without quitting or complaining. Young and especially foreign people are the perfect hire for these companies because they can overwork them so much more than a 40 year \textbf{old} native. You would believe the horror stories coming out of Amazon especially.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/110 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small \@Seth Nnot sure if you're trolling or telling the truth. No one can be that \textbf{dumb} to tell someone to kill themselves and be public about who they are. I mean if you're employer is really IBM I could forward this chat to management and they would let you go since you're still under contract. you might wonder how I know that :D\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small You guys are \textbf{crazy}, and while Seth is being a monumental troll, he speaks the truth that programmers, developers, sysadmins, whatever, we have a skill, a very useful one, so we're not replaceable. Plus once someone has learned the system your company has in place, it takes a big disturbance to justify getting someone new up to speed.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small Oh and I had a personal website and 2 other sites I made for my first company and a friend, and that was more than enough portfolio. We're so in-demand if you have a few examples of work and you're not \textbf{weird}, recruiters are biting at the reins to get you to work for one of their clients.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small \@THEFRISKIESTDINGO Retired at \textbf{age} 40, with my feet on my hot spa\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small my work gets rid of the \textbf{old} people so they dont have to pay them the higher rate.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small ageism to older people in the workplace isn't a thing, who runs companies? who's in management roles? \textbf{old} people\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small People over the \textbf{age} of 40 are naturally disadvantaged with coding for various reasons.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Hewlett-Pakcard does not surprise me in the least. They have been around for a long time and a lot of their folks will have passed on by now. They had \textbf{Engineers} who were around for the invention of the transistor as well as the processor it's self, silicon transistor. So if the employees are half second generation and half current generation then I get it.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Yeah.... It a biological and statistical fact that programmer in his/er 20s' has better chance to get new technology.And "\textbf{age} discrimination" is BS anyway - young people should be hired first. Regardless of anything else.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I think younger is better for the tech industry.. In the tech industry, curiosity and that drive to do stuff is very important and I think it would me the norm for young people over the \textbf{age} to be more curious, adaptable and also high motivation.. I'm not saying \textbf{old} people in the tech industry dont have that.. im just saying as you get older its the norm to be less motivated, less curious and less adaptable.. Obvious there exceptions... there are a lot of \textbf{old} people in the tech industry that are very curious, adaptable and motivated and there are lot of young people that are less motivated, less curious and less adaptable. I'm probably a bit bias because I'm 16 :)\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/123 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Well those young people will get \textbf{old} to and will know how it feels.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small i loathe much of the "tech bro" industry because of this stuff. and while it's true that a few of these companies have longevity, look at the higher-ups at places like \textbf{apple} - they're all well beyond 40, vs all these thousands of tech companies that all end up with a shelf life of 2-5 years because they're founded by a bunch of overzealous trust fund 20 somethings with way too much energy and way too little experience or respect for those more experienced than they are. it's not an asset to exclude older people in any industry, it's a detriment. and i say this as a 33 year \textbf{old} - i'm just not a stupid 33 year \textbf{old}.\normalsize   & \cellcolor{green!5}Apple, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}3/119 & \cellcolor{green!5}2.521 \\  \hline
  \cellcolor{green!27}\small \@Kerry Luckett any industry fronted exclusively by greedy 20-30 year olds is a bubble waiting to burst. in fairness, since not all companies in the industry (particularly those that have been around a while) aren't as bad about this as most of the newer ones, and lots of the people who went through the \textbf{old} tech bubble have learned that lesson, i don't think it will be as big of a burst this time - more of a slow and steady burn out. the companies smart enough to keep their workplaces diverse and mature and have a brand that involves something deeper than just perpetually chasing after whatever this month's trendy buzzwords are will still stick around.also i laugh at the fucks commenting about how 20 somethings are statistically better coders or better at tech. give me a break. all of the people who truly revolutionized tech are over 50 and still more brilliant than 100 of these tech bros put together. give me anyone working in the industry today in their 20s and put them up against, say, steve wozniak. yeah - you're full of shit if you think 20 somethings are the 'smart' ones - though they're certainly the most self deluded.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/205 & \cellcolor{green!27}0.488 \\  \hline
  \cellcolor{green!5}\small I agree completely.  I am 39 which would make me \textbf{old} by these standards.  ironically in other industries I might be considered on the younger side or average.  it's about the person.  some older people are flexible and adaptive and some are not.  some younger people have grit and respect for experience and some do not.  the commenters (of any \textbf{age}) who make broad sweeping generalization demonstrate their lack of intelligence and sophistication.  I would never hire them.  I look for all these qualities (eg intelligence, adaptiveness' experience, drive, respect) when hiring and of course no one has them all perfectly.  making decisions based on stereotypes is an awesome way to be less successful and make less money.  yes I know Google is successful.  they would be even better if they did not engage in \textbf{ageism} even if it may be that most of the best people will be younger.  fair enough.  but older employees should not fear being axed based on \textbf{age}.  let's not even get started on the effects that has on morale and productivity.  anyway, anyone who says older people are smarter is an idiot and the same applies to saying younger people are smarter.  not exactly scientific.  and zuckerberg is obviously smart in some ways.  but that doesn't prevent \textbf{dumb} things from exiting his mouth with some frequency.\normalsize   & \cellcolor{green!5}Age, Ageism, Dumb, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/222 & \cellcolor{green!5}2.252 \\  \hline
  \cellcolor{green!27}\small Exactly, \@Brendan McCaffery. I am always pleasantly surprised by who comes into his or her own and really has the stuff it takes to produce the right results. I teach for a so-called living, and I have students who are talented but distracted or self-entitled or undisciplined or whatever. You can be talented, but if your flaws overshadow your talent, \textbf{nothing} you do will succeed--young or \textbf{old}.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small Most tech jobs were created in the last 15-20 years, so it makes complete sense the median ages are what the are \& pretty much line up with how \textbf{old} the company is \& how long their sphere of technology has been mainstream.   Working in the industry now for 20 years myself, there may be discrimination against older people in certain areas of tech, but in other areas like Banking, Finance most in the tech area are much older, on average.There are plenty of tech jobs that are seeking 10+ years of experience.   It's not \textbf{common} to see a 20 something with that level of experience.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small Median doesn't mean anything, what is the mean \textbf{age}?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Cenk \& Anna are completely wrong, it has \textbf{nothing} to do with pay, people are constantly get poached by other tech companies, so if you're underpaying younger employees they're not gonna stick around long, also looking at TYT there doesn't seem to be many people over 40 either\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Kyle Zawacki Google treats it's employees like shit, there are many stories published about it to the point it has become a \textbf{common} culture joke.You can think whatever you feel like but it does not change the facts.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Kyle Zawacki It doesn't change the fact, or the point that they hire young because it's cheaper. Occams razor.Your whole argument  thusfar is a rainbow pony. That is why it's called libtardism. Just another word for cowardice and lack of integrity in all ways. Amounts to \textbf{nothing} more than emotion, born of fear and devoid of any logic , or reasoning whatsoever.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small I work in this industry. I have friends all over the field. A few random articles and a youtube video don't make you an expert on anything.The software industry is the fastest moving industry in the world. You need a young perspective and tons of energy to keep up. Google, \textbf{Apple}, and Microsoft were all founded by people in their early 20's. This is not a coincidence.Your ignorance is the only thing that is a magical.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small \@Kyle Zawacki If you work in the industry your testimony is conflict of interest. Thank you for suiciding your entire position.  Your entire argument thusfar has been demolished on every point.Your point being that young people are superior to \textbf{old} for a "young perspective".It's not even a point it is an opinion that I ride to eat inexperienced know it alls.You assume you know who I am. This is a mistake. You assume anyone cares who you are, another pride driven mistake.Your pride, your conflict of interest just let me expose your "precious". Free advertising is... very generous of you.If you work in the industry you know who created google and why, and what it will try to be be used for in the very near future , with social credit points and friend associations determining that score, and the score determining access to anything on the internet, including commerce if I am not mistaken.This exchange itself illustrates why youth are cheap, and why experience produces results and is thus worth far more.You're dismissed, fly along on your rainbow pony captain rollover.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/189 & \cellcolor{green!5}0.529 \\  \hline
  \cellcolor{green!27}\small \@Kyle Zawacki Young is cheap, basic law of economics. Telling them they are wonderful because of their "edgy fresh worldview" is blowing smoke up the ass of a cheap employee. \textbf{Nothing} more, \textbf{nothing} less.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Leedark3Not true at all. There are certain professions where experience can even be considered a liability. Mathematics, and sicentific breakthroughs almost allways come from the very young. This is because you tend to get trapped into \textbf{old} and incorrect ways of thinking and new evidence on how things works tends not to sink in as much in very \textbf{old} people. Innovation tends to be a young person's game.Cost might have something to do with it, but frankly I don't think they deliberately don't hire someone because they are \textbf{old} and hence would ask for more money. If anything it would be a case of the job is offered at \$25,000 and the \textbf{old} person chooses not to apply because they feel they are overqualified and would expect a higher paying job.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}4/133 & \cellcolor{green!5}3.008 \\  \hline
  \cellcolor{green!27}\small \@Ben E How about we use your own reference against you?  First, Hardy says that math is a young man's game more than "any other science."  Worse still for you, Hardy's definition of young is not the same as is used in this video.  He gives four examples of major mathematicians in that quote, and two of them are OVER thirty.  He then follows that by saying that a mathematician over fifty is one who cannot be expected to come with new ideas.  That's a massive TWENTY YEAR GAP between what Google and Facebook consider \textbf{old} and what Hardy considers \textbf{old}.  And that's ignoring the fact that he wouldn't consider programming a "young man's game" quite like pure mathematics.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/119 & \cellcolor{green!27}1.681 \\  \hline
  \cellcolor{green!5}\small \@Leedark3 I also made a claim that science and math were a young mans game and great breakthroughs occur by the predominantly young, so I did some digging and i present my evidence. Here is a list of some of the world's most famous scientists and their \textbf{age} when i have found documented evidence for their proposal (prooving they could not have had it at any later \textbf{age} than they were then):1) Copernicus, the world is round, letter demonstrating he was no older than 30 when he had this idea.2) Newton, Calculus, 1666 aged 24. his work on gravity was also theorised at this time as well and this was used to proove it much later on in his life. The idea still came much earlier however.3) Michael Faraday, Magnetism and Electricity, 21, 30, 41 depending on which breakthrough you refer to.4) Charles Darwin, evolution, idea came to him during his visit to the galapagos island in 1833 making him 24 years \textbf{old}.5) louis pasteur, germ theory, published work in 1858 would make him 36 but the experiments and proof and whatnot would have meant he was considerably younger than that when he had the idea.6) Einstein, relativity, 4 papers revolutionised the world in 1900 making him only 21 years \textbf{old}.7) geoges lemaitre, the big bang theory, his published work was in 1927 making him aged 33.8) Alexander flemming, pennecilin, this one shouldnt be included because no intellect was actually used it was a lucky breakthrough with no intelligence, or thought either way. he was however 479) James watson, 25, francis crick, 37 DNA. This one is tough to know exactly how much intelligence was watson and how much was crick.10) Neils Bohr, the atom, introduced in 1913 making him a maximum \textbf{age} of 28.Not alot of \textbf{old} people in this list. If 60 year olds really are the best, why is everyone so young? Infact the only ones you can safely say are really \textbf{old} are crick who you cant actually show had any real insight at all, and flemming who literally only is famous because of shear luck. So then show me your evidence that OAPs also lead to the breakthroughs in science.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}7/376 & \cellcolor{green!5}1.862 \\  \hline
  \cellcolor{green!27}\small \@Ben E Actually, I'll just wait for you to realize you're still making my case for me, since HALF of the discoveries you listed were OVER THIRTY.  How about you go watch the video again?  Try to pay attention to the part where we aren't talking about sixty year olds.  They consider THIRTY to be \textbf{old}, moron.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small \@Leedark3These are the oldest oossible ages. Ages when we have letters, or published papers documenting their intentions. It takes time to produce that stuff and so the \textbf{age} of the thought is likely considerably older than that. The majority of them would likely be much younger than 30. And the point here is to proove that 60 year olds arent as innovative as 20 year olds. No one over the \textbf{age} of 50 is on this list, and the older guys are only there becasue of \textbf{dumb} luck or because they were working with younger people who did the innovations. Your claim is that the more experienced you are the better you are at your job. If thats true why the lack of experience in this list?Further if you don't provide supporting evidence you are basically expecting me to change an evidence based conclusion on your hunch. Sorry but that definately isnt going to work, clearly you know \textbf{nothing} about what the burden of proof is and who has it.\normalsize   & \cellcolor{green!5}Age, Dumb, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/172 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@Leedark3its not "probably" nor is it "much" younger than 30. But it does take time to provide evidence, do necesary experiments, right papers, find other research to quote and become reasonably sure enough to actually publish a paper. No one just comes up with an idea and publishes it willy nilly, 4 months later, these things take time. It isnt unreasonable to think that for example geoges lemaitre who originally published his work on the big bang at 33 took 3 years preperation and refinement of his idea and hence his original inspiration was before the \textbf{age} of 30. 7 scientists out of 10 (not including flemming) were directly under the \textbf{age} of 30, and if we also count geoges lemaitre who as explained above was likely under 30 that moves up to 80 It most definately is a falsifialbe claim if 80 of the famouys scientists in history where between the ages of 40-70 then my claim would be demonsterably wrong. And you don't provide your own evidence you just dismiss my argument outright based on \textbf{nothing} but "well this doesnt hold for computing". Proove it. Proove it doesn't hold true for computing. And if you say "i won't provide evidence" one more time we are done because that is basically the same as saying "you should beleive in this thing based purely on my own opinion with no evidence to back it up"\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}3/236 & \cellcolor{green!27}1.271 \\  \hline
  \cellcolor{green!5}\small Politicians want to raise the retirement \textbf{age}. Yet the market removes older people from jobs first. Me sees a problem developing methinks.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Well technically in the U.S. they can't fire you for being 40 or older. Its against the law, per the ADEA, but I don't know how you would easily prove that an employer is \textbf{age} discriminating.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small its funny cuz yall want \textbf{old} man sanders to govern the country but heaven forbid he actually works. lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small You can tell Ana started to feel old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Long \textbf{Ho} Other than - the point about over 40 being less than someone younger is BS.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small +Fred Pine these are the top tech companies... maybe they need the youth because that's how they stay in business. maybe they need individuals who are more creative and intelligent to fulfill the roles and the older individuals dont perform at this level anymore. software is a \textbf{crazy} world, this is how it goes. this isn't the medical field or a teaching profession where there's a protocol for everything; it's wild.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small \@Long \textbf{Ho} If you believe that you are not "more creative and intelligent " like you post. If they are laying off the older guys and gals it is more that they make more money and that is what laying off people is about: saving of the budget. I am one of those your describe and I grew in my profession, going from a mainframe top-down programmer to a OOP developer in web based systems. I got my position over many h1-b visa candidates, so that theory is BS.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small \@Long \textbf{Ho} " zuckerberg even said 'younger people a smarter'. i'm trying to give reason for that." <== Who gives a crap? OOP is here to stay for everything but gaming where it can, in some cases, slow down gaming processes. OOP is so hated in IT circles, and that is why I had to diagram an OOP process in my third interview for my job because it is obsolete because a genius troll like yourself posts.Go f-yourself! Your statistics are that of a uneducated \textbf{sissy}. You post everything that does not pertain to the subject like a coward who is a troll.\normalsize   & \cellcolor{green!27}Ho, Sissy & \cellcolor{green!27}Gender - Female sexuality, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small \@Long \textbf{Ho} Yes I am! An intelligent person would judge people based on individual effort and work ethic instead of lumping a group or \textbf{nationality} into one category. If you or the CEO said: "Sometimes we lay off the older workers because some do not want to progress with their education and learned the new technology and concepts?" more power to you and the CEO. Placing the blame on a group as a whole is ignorant on your part. It would be like me saying that more younger workers do not have the dedication or work ethic - which would be as ignorant as your statement on older employees. Your categorizing was ignorant at best; or was part of your agenda to prove your own self-worth. What you said did not make any sense, and I read it. You obvious think that people are stupid to not detect your biased opinion in your posts. So yes, I read everything and find that you are a one-dimensional thinker who  lumps people into categories versus judging people as individuals.\normalsize   & \cellcolor{green!5}Ho, Nationality & \cellcolor{green!5}Gender - Female sexuality, Nationality - General & \cellcolor{green!5}2/177 & \cellcolor{green!5}1.13 \\  \hline
  \cellcolor{green!27}\small \@Long \textbf{Ho} I do understand you and what you are saying. You want to debate individual workers on an intellectual bases, get back to me. If you want me to lower my IQ and debate people lumped into one category - take a \textbf{hike}.\normalsize   & \cellcolor{green!27}Hike, Ho & \cellcolor{green!27}Gender - Female sexuality, Nationality - Italian & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Long \textbf{Ho} Great comeback for a biased troll!\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small The tech industry is different than other job fields. Everyone knows they would rather have a 20 year \textbf{old} whos been working with technology their entire life than a 45 year \textbf{old} who didnt have a cell phone until they were 24\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small +eatanentireass yes a lot of people don't know this, and its not just the \textbf{age} thing. For example, tech interviews\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Fred Pine I agree 100 the question is often answered unfairly.I've seen personally preference in younger employees and I've read about people altering their resumes to not appear to be too \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@Christopher Pagan I look ten years younger than my \textbf{age}, and I dropped \textbf{old} mainframe jobs from my resume to protect myself. Guess what? I proved myself, in a supposedly, younger technology. That is why it is stupid to \textbf{lump} people into one category. Judge people individually which is the fair way to judge people.\normalsize   & \cellcolor{green!5}Age, Lump, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small +eatanentireass it has \textbf{nothing} to do with that, they let young people overwork and give them low pay, in fact, computer programmers last on average 10 years before they change their job...in other professions, it's around 40 years\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I know this is a stupid example but who does your 40 year \textbf{old} parent ask to help them with their technology they ask there little kids and they are the simplest things\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@kost4060 I apologize but, do not be stupid like the guy above who throws all older workers into one category. Judge people by individual merit, not \textbf{age}. I am am older worker who re-engineered myself in the new IT technology. I am no better or no worse than a younger worker. Merry Christmas!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small it's not just about what you know, it's about what you can do. the context of the word smart has many meanings. the tech industry, especially software deals with many intangible things. in particular, the skill that they require is the ability to produce and maintain a product consistently well. in this software word, this takes a lot of effort and it is not like working at a warehouse or in the medical field where there's a protocol for everything. you are expected to come up with solutions on your own. it demands both creativity, logic, and consistency, but if you screw up, you're ass is on the line. i'm guessing what zuckerberg means is that younger people can do this better than older ones. having the capacity to a greater degree is by all means a measurement of being smart. but i also think that doing this at a high level my also negatively impact the person as well. many studies have shown that there is a high level of autism in children whose parents are in the tech field.anyway, im just saying, its not about what \textbf{age} you are, it's about what you can do. its about pushing the technology forward and allowing for progress to happen.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/210 & \cellcolor{green!5}0.476 \\  \hline
  \cellcolor{green!27}\small Seriously, programmers and \textbf{engineers} fresh out of school are making big bucks, especially at those companies. They wouldn't take a 25k-30k starting salary. More like 40k-50k starting, ramping up to 90k+ after several years.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Donald SamuelsEven the less "well known" and smaller companies pay 40k-50k starting. The jobs are abundant so the demand is high, which translate to a better salary. It's just the nature of the tech field. Again, this is for programmers, software \textbf{engineers}, computer \textbf{engineers}, and positions like that. IT/support guys make less.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small My company only hires people who have an IQ above 105+ for your \textbf{age} group.I'll admit we do discriminate agaist people. Call it "    ism" just give it a lable and wait for SJW.Back in the day seniority would be a point as to keeping you inside a company and fire the "younger/newer" employees, noone complained about that now the role is reversed where we take away points if your "older/not uptodate". How about find an idustry that's suited to your attributes.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small "If you say that people going to really good schools are smarter now because the competition is tougher, that's true."Really? In the \textbf{age} of affirmative action, forced diversity, and quotas, I'm not so sure.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Young people grew up with technology. \textbf{Old} people can barely use it. My English teacher can barely move the mouse.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small +Texas City My professor at university has 2 PHDs and doesn't know how to use a laptop because he is like 70 years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Longitudinal studies have shown that the older worker is smarter, from accumulated knowledge \& wisdom.Yes, when I was the young whiz kid in Silicon Valley, in the 1970s, previously given a full scholarship (included room \& board) at \textbf{age} 16 from Stanford University, I had numerous Ivy League \& tech universities (e.g., MIT) courting me, much like the gifted sportsmen.  I was also a competitive gymnast, which they loved.My father worked for Hewlett-Packard, whom was the first to give me a job offer.My mother was an Environmental Scientist, and I chose that discipline, because it offered field work, \& suited my passion \& aptitude for ecology \& sustainability.I have mild ADD, and I am easily bored.I love being an outdoorswoman.I was psych tested, because it was still considered an anomaly for a female to excellent in math \& science.  Today, we continue to be seen as statistical outliers (!!).I left the science field in 1989, from ennui.I was constantly sexually harassed, verbally abused, and bypassed for promotions, often training my supervisors, whilst in the science fields.I am currently a psychotherapist, a field that honors wisdom.If I hadn't been pulled to helping people, I had begun my own tech company, which may have been successful; once I'd put my team together, and had it running, I was already bored by it, LOL.Maybe this is why Steve Jobs passed away at a relatively young \textbf{age}.  He was too \textbf{old}.These arrogant kids will get their comeuppance...\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/255 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small Longitudinal studies have shown that the older worker is smarter, from accumulated knowledge \& wisdom.Yes, when I was the young whiz kid in Silicon Valley, in the 1970s, and previously given a full scholarship (included room \& board) at \textbf{age} 16 from Stanford University, I had numerous Ivy League \& tech universities (e.g., MIT) courting me, much like the gifted sportsmen had happen.  I was also a competitive gymnast, which they loved.My father worked for Hewlett-Packard, whom was the first tech company, to give me a job offer, when I was in high school.My mother was an Environmental Scientist, and I chose that discipline, because it offered field work, \& suited my passion \& aptitude for ecology \& sustainability.I have mild ADD, and I am easily bored.I love being an outdoorswoman.I was psych tested, because it was still considered an anomaly for a female to excel in math \& science.  Today, we continue to be seen as statistical outliers (!!).I left the science field in 1989, from ennui.I was constantly sexually harassed, verbally abused, and bypassed for promotions, often training my supervisors, whilst in the science fields.I am currently a psychotherapist, a field that honors wisdom.If I hadn't been pulled to helping people, I had begun my own tech company, which may have been successful; once I'd put my team together, and had it running, I was already bored by it, LOL.Maybe this is why Steve Jobs passed away at a relatively young \textbf{age}.  He was too \textbf{old}.These arrogant kids will get their comeuppance...\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/266 & \cellcolor{green!5}1.128 \\  \hline
  \cellcolor{green!27}\small I might not be too \textbf{old}, but I'm definitely too stupid.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small After \textbf{age} 50, as an engineer, you get thrown in the garbage, unless you are a manager.  I've been out of work since i hit 52. Spent years looking for equivalent work but no luck.  Life ruined.   Word to the wise...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Yeah sure. You can pay a 20's year \textbf{old}  less. You can make them work long hour. You can even make them work all day by just providing a couch and snack.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small A median \textbf{age} of 28 doesn't sound that bad to me. Half the employees are over 28.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Raza Sure, but you also have to take the \textbf{age} distribution of people wanting to work in the industry into account. There are probably a ton more people entering the industry now than in f.ex. the 90s or 80s, so it's natural that it's skewed in that direction.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small +Kent Olaf Steinhaug You're too \textbf{old} to understand.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Mkkkkdjdjekriitijmsmejrjjr entir r nene jrijewk. Workmen. Woke early ramen emeke. E e e em r \textbf{Ike} Rome e mr f t make. Fkrmrjenememmrkrmmrkriroroor r. R r r r mrmrkrkkrkr. Fm form fork for fm rotor.  R e m q me a a. S s s d d d d mdkdkdkdodk d cmcmckkfkformr r\normalsize   & \cellcolor{green!27}Ike & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small People below 30 pretty much know \textbf{nothing} about computer technology, and most of them own an Iphone.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I've noticed that, I work in biotech/drug development, the people my \textbf{age}  they have maintaining our equipment are idiots, I know more than they do and I'm not a computer programmer/engineer/tech support.  They are used to cutsie iPhones, not computing systems used for actual work.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small +nigling I wouldn't say "it just works" but I also wouldn't have as many details as you seem to know, so I guess you're right about modems. I wonder if there's another device we 20 year olds can explain better though. Still, this is sort of unfair because I'm still in college and a 40 year \textbf{old} tech worker has 15 to 20 years of extra knowledge on tech than a 20 year \textbf{old}, so it may just be down to that.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small with \textbf{age} comes wisdom.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small with wisdom comes \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Why don't those "\textbf{old}" people just change their \textbf{age}...? There was a 52 yo man who transitioned into a 6yo girl. So what's the problem?\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small if you can't discriminate against \textbf{gender} or religion, then you can't on \textbf{age}.\normalsize   & \cellcolor{green!5}Age, Gender & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small age makes sense, since brain performance peaks \@35. afterwards your dying brain cells outnumber those being created\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small youngins make \textbf{dumb} mistakes\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small This may very well explain Googles idiotic decision, to invest money in a hate group that has goals of literal \textbf{eugenics}.\normalsize   & \cellcolor{green!27}Eugenics & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Since this is the reality, what is there to look forward to in the future? Are we all going to be living in dirt shacks at \textbf{age} 40? What's the point anymore? And as if a job, no matter what your \textbf{age}, at fakebook or google is a reality. So, this story is actually relevant to maybe .000001 of the population.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small But you're never too \textbf{old} to worship Gozer!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small It was the Arab Muslim that started the mass commercial slave trade of Africans in which the Americans got 13 million slaves and Arab nations got 20 million and the fact is Saudi Arabia and other Muslim nations even now in 2015 are currently enslaving millions of \textbf{black} people. Proof,   [LINK]  SPREAD IT AROUND  Scroll down in the  links I provided to see \textbf{Racist} Arabs Rant as they thumbs each other up. Scroll down through this Saudi Arabia video posted on youtube and check out the comments section as \textbf{racist} Arabs drob N Word like \textbf{crazy} proof,  [LINK] \normalsize   & \cellcolor{green!5}Black, Crazy, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/98 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small +Sadat  Woo!  45!! They all sounded \textbf{ageist} as hell when they were discounting Bernie.\normalsize   & \cellcolor{green!27}Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Wanna work somewhere where more hardened, experienced people are accepted more than the 20 year \textbf{old} Stanford boys, while getting paid more than your average Google employee, and working with tech? Head to Valve.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small My specific professional field has plenty of diverse \textbf{age} groups, so I dont have to worry if I will lose my job when I get older. The people who are bragging that they are younger and smarter than their older colleagues will have the hand of reality  smack them once they themselves reach that \textbf{age} and they are laid-off for being too \textbf{old} and stupid. It the same for young professional athletes, super models, porn stars, and entertainment industry. Once your youth fades it out with the \textbf{old} and in with the new. You better have saved and have a contingency plan.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}4/102 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small I think the majority of your viewers aren't \textbf{old} enough\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The older you are the harder you are to train. The problem with older tech professions is that they sometimes have trouble taking orders from a "hot shot" 20-something year \textbf{old} technology project manager.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small +Rotten Egg Creations Because a 20 year \textbf{old} generally doesn't have the respect and maturity of a 40+ year \textbf{old}... It's life experience that earns respect.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Didn't steve jobs invent the I phone in his late \textbf{age} 58 just saying !\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small My cousin had his BA, MA and PhD in Geosciences by your \textbf{age}. He's on a six figure salary now but he sacrificed so much of his younger years to get where he is now. So, mixed bag really...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Jimmy turned 50!? I call for his resignation right now he's too \textbf{old}!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small as a person being tainted in the IT field by some real OG Tech \textbf{old} heads, they know the history, they are great for the knowledge and how the tech lead up to current, but when it comes to fresh knowlage and implimentation of the tech young bloods are just better, we out perform, end of story. \textbf{Old} heads will be around but they won't be around in the nubers that exist, they need to go into teaching like my teachers did or retire...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small It's because when people get \textbf{old} they become conservative and conservatives are useless as tits on a bull when it comes to innovating with technology.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small 18 \textbf{old} people just figured out how to use the dislike button.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Bryce Bickford You remind me of the cocky scientists from the 1800's who claimed all that can be invented already has. Don't limit humanitie's technological potential due to your limited understanding. Moore's Law will be circumvented with newer non-silicone components and of course quantum computing is on another level. If I call you ignorant it's because you are, I don't care that you work on today's archaic computers that means \textbf{nothing} to the informed such as myself.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small Don't forget the \textbf{race}, and \textbf{sex} discrimination against white, and Asian males\normalsize   & \cellcolor{green!5}Race, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Google's android UI is too \textbf{old} to work now!!!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small 42 isn't \textbf{old} if I'm still getting ID'd when I buy beer or smokes. However, I am trying to get back into college. I have a tech degree already, but it's '\textbf{old}' (13 years \textbf{old}). I can fix a computer blindfolded, but it's not enough when the interviewer sees my grey. Unfortunately, school is super expensive, so I'll probably just do what all '\textbf{old} people' do. Janitor. My worthless tech degree isn't required for pushing a mop.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small ANA PLEASE SIT ON MY FACE UNTIL YOU REACH \textbf{AGE} 30\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Not surprising at all... TYT seem more understanding on this issue....But when white people are better qualified and suited for a job than a minority, that's \textbf{RACIST}!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small That's only because \textbf{racism} is a much bigger issue than \textbf{ageism}. Exponentially bigger. Any ism is bad for you, but \textbf{race} is the worst.\normalsize   & \cellcolor{green!27}Ageism, Race, Racism & \cellcolor{green!27}Age - General, Ethnicity - General & \cellcolor{green!27}3/24 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Am I \textbf{deaf} or does this video have no sound?\normalsize   & \cellcolor{green!5}Deaf & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small You're \textbf{deaf}.\normalsize   & \cellcolor{green!27}Deaf & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Yeah man, you're totally \textbf{deaf}. You're gettin ooold.\normalsize   & \cellcolor{green!5}Deaf & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small +xJerzakHD you two are both \textbf{deaf}... I am sooooo deeply sorry.\normalsize   & \cellcolor{green!27}Deaf & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small +monolo murda \textbf{Nobody} wants to take your father's job.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Ageism RABLE RABLE TABLE!\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Ageism, Age, Ageist & \cellcolor{red!27}122 & \cellcolor{red!27}122/25834& \cellcolor{red!27}0.47000000000000003 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Senior, Elderly & \cellcolor{red!5}123 & \cellcolor{red!5}123/25834& \cellcolor{red!5}0.48 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black & \cellcolor{red!27}3 & \cellcolor{red!27}3/25834& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Mental, Dumb, Crazy, Weird, Eugenics, Deaf & \cellcolor{red!5}26 & \cellcolor{red!5}26/25834& \cellcolor{red!5}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Gender, Sexism, Sex & \cellcolor{red!27}7 & \cellcolor{red!27}7/25834& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian, Red, Apple & \cellcolor{red!5}7 & \cellcolor{red!5}7/25834& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Red & \cellcolor{red!27}1 & \cellcolor{red!27}1/25834& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nobody, Nothing & \cellcolor{red!5}22 & \cellcolor{red!5}22/25834& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Effeminate, Sissy & \cellcolor{red!27}2 & \cellcolor{red!27}2/25834& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Engineers, doctors, Migrant, Nationality & \cellcolor{red!5}13 & \cellcolor{red!5}13/25834& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racism, Racist, Race & \cellcolor{red!27}10 & \cellcolor{red!27}10/25834& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common & \cellcolor{red!5}6 & \cellcolor{red!5}6/25834& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Ho & \cellcolor{red!27}7 & \cellcolor{red!27}7/25834& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Zip & \cellcolor{red!5}1 & \cellcolor{red!5}1/25834& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Homophobia & \cellcolor{red!27}1 & \cellcolor{red!27}1/25834& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female intelligence}  & \cellcolor{red!5}Becky & \cellcolor{red!5}1 & \cellcolor{red!5}1/25834& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Italian}  & \cellcolor{red!27}Hike & \cellcolor{red!27}1 & \cellcolor{red!27}1/25834& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Lump & \cellcolor{red!5}1 & \cellcolor{red!5}1/25834& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Jewish}  & \cellcolor{red!27}Ike & \cellcolor{red!27}1 & \cellcolor{red!27}1/25834& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - General;Age - Over 65s;Ethnicity - Black;Physical Identity - Physical (and Mental) Impairments;Gender - General;Ethnicity - Native-American; Ideological and Political Identity - General;Age - Youngsters;Sexual Identity - Male homosexuality;Nationality - General;Ethnicity - General;Social Class - Working class;Gender - Female sexuality;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Sexual Identity - General;Gender - Female intelligence;Nationality - Italian;Physical Identity - Physical Features;Religious Identity - Jewish;%.

\item The percentage of hate speech related words is 1.3742.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 356/737 occurences of hate speech related comments.\end{itemize}\end{document}