\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_173.json :}\newline \par\Large\textbf {Title: \large  Generations X, Y, and Z: Which One Are You? }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small TIMESTAMPSThe five generations 0:57The Traditionalist generation 1:49The Baby Boomers 2:30The Gen Y 3:24The Millenials 4:30The Gen Z 5:31What Millennials and Centennials have in \textbf{common} 6:35\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small I was born in 1962. But the only thing I have in \textbf{common} with baby boomers is that my best friend is one. She's six years older than I am. My entire life is characterised by Gen X instead. Lock \& key. Minimal adult supervision. Peer oriented.  We had the easiest access to tertiary education, when compared with previous generations. The computing industry took off. And everyone I know who was born in the 60's says the same thing. The Boomers lit the way for us. But we're not of the same cloth. We can't relate to Woodstock or the hippy culture either. Instead, our entertainment was defined by discos, Michael Jackson videos \& Atari games. Whilst at work, we wore power suits with giant shoulder pads. And giant hair do's. None of which the boomers liked, let alone participated in. I think they need to re-define Gen X \& baby boomers. They're totally different animals.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/156 & \cellcolor{green!5}0.641 \\  \hline
  \cellcolor{green!27}\small I'd start generation A at/around 2008/2009. Barack Obama, housing market collapse, Facebook, Netflix, Google,  Amazon, \textbf{Apple} dominated industries, leading into Trump era, is a generation unto itself.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Multiple facts wrong including \textbf{age} ranges. Bright Side you are misinforming people.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I was born in 93 and remember 911 a little bit I Kno that I was my grade 3 class as a 8 year \textbf{old} and confused what was going on cause the teachers got are parents too take us home , when I was home I remember watching the news with my parents . But any younger I probably wouldn't of rememberd it .\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Where the 95-2000 kids stuck in the \textbf{weird} middle. Don't consider myself in either cause it is hard to connect with both. Lol\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I'm generation middle \textbf{age}, cause we need a new plague to clean the slate\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small my 97 year \textbf{old} gran is the least boomer person i know. she gets how the world is now. unlike my dad (50)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Ouch! The words towards the Millennials. It also depends on how you are discipline as a child. growing up I was taught to respect my elders and hard work pays off. Make a good use of your stuff. To get respect you need to show respect. It all depends. Rest you could do whatever just to make a person happy and you still get called ' you darn millennial.' 😂 I'm like seriously 😳😂  man some \textbf{old} folks don't really like the younger people. And I am always left with but I didn't do anything wrong. 😒😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small Yes, because you would have come of \textbf{age} in 2000.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I was born in 1986 and I don't really feel like a millennial. If you remember using the dewy decimal system to find a library book, no internet, then dial up internet and Aol, Oregon Trail, real MTV, pagers actually playing outside until the street lights came on because we didn't wear watches, your entire family sharing a cellphone around middle school \textbf{age}, and etc, then I think we should be defined as a different generation. Don't really feel like Gen X or Millennial. Anyone else feel the same?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Anyone born before 1997 is Gen Y anyone born after 2004 is Gen Z \& anyone born between 1998-2003 is a Lifetime Honorary Member of The \textbf{Black} Eyed Peas (I was born on December 26, 1999)\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Youtube recommended this after \textbf{Indian}  Finanace Minister N Sitharaman absurd theory about millenials preferrence of mode of transport.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small And this is the confusion of us 94 and 95 kidsWe don't really know where to fall, We have both expieriences, We were just \textbf{old} enoughto remember 9/11 but also grew up with the internet. Everything started to advance the same way.Some of us aren't SJW's or liberals (probably few) lol but still, I feel as if i'm both millenial and Gen Z.. Maybe a Zillenial lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small It's really \textbf{weird} bc we are in the \textbf{old} generations because people in the next 300 years people will say we are a \textbf{old} generation\normalsize   & \cellcolor{green!27}Old, Weird & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/25 & \cellcolor{green!27}12.0 \\  \hline
  \cellcolor{green!5}\small I was born in January 2001 and was 8 months \textbf{old} when the 9/11 attacks took place. I consider myself a strong cusper (inbetween) millennials and Gen Z but more on the millennial side for a few reasons. One, while I didn't have memories of 9/11, it was not ancient history for me because I was alive when it happened. Two, I definitely remember a time before iPhones and modern technology that really took hold around 2010. Three, I have never been able to relate to those younger than me, only people older. Between me and my sister (born in 2004, almost 2005) there's a stark difference between how connected we are to our friends and to the world, even though we shared many experiences growing up. Despite not having social media, my sister is deeply in touch with modern trends and stuff, while I seem to be behind on everything. So I consider myself and others born late 1990s to early 2000s (probably 2001 at latest) cuspers if they share my thoughts.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/173 & \cellcolor{green!5}0.578 \\  \hline
  \cellcolor{green!27}\small I'm 22 years \textbf{old}. I was raised in the \textbf{old} school way\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Millenials was a word originally coined to refer to the babies born in the 1980s(1981-1982) who were estimated to be the FIRST GROUP/CLASS to graduate high school starting at the new MILLENNIUM.  The year 2000.   So you could be born in 1982 but if you graduated high school in 1999 you aren't a millennial.  It had \textbf{nothing} to do with the year you were born.  Unless you graduated high school in the year 2000 you aren't truly a millennial.  But nowadays the definition of "millennial" has been expanded and so twisted even my dog can be a millennial.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small The new Millennium actually began 1/1/01. Those that became of \textbf{age} (18) in the beginning of the Millennium are the first Millennials. 1983 should be the first year and Gen Y/Millennial generation IMO should be the shortest of all existing ones and end in 1992.Millennials/Gen Y-1983-19921993-2011-Generation Z1981 and 1982 babies belong to Gen X as they became of \textbf{age} before 1/1/01.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small You are a brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I literally grew up using technology 2 years \textbf{old} - now\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I didn't know I can choose my \textbf{age} lol\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small This is inaccurate , I was born in 1996 but I am definitely \textbf{nothing} like my little sister or kids her \textbf{age} lol... Our mindsets are completely different and the cut off point in general for millennials and Generation Z is completely wrong, it's always been cut at 1996, very few say 1997 but never 1995? Many others that have grown up with me and that are also born in the year of 1996 could relate. Our maturity level is not similar to those born in 1997 or younger.\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small 5:35 I grew up in a \textbf{Old} Town type of neighborhood where majority of the parents are Gen X, and I have Millennial parents because of my mother's health issues, because of that she couldn't have children when she really wanted to, so I'm more patience then the other students at my school, and there's a big difference of motivation, kids at my school make there slideshows messy looking while I make mine much more neat, like they'll just write the project down and add some color to it, while I'll make the slides look more presentable like.I'm grateful for finding this video,  I was very confused because how different I was from other kids at my school, this video helped me understand why.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/125 & \cellcolor{green!5}0.8 \\  \hline
  \cellcolor{green!27}\small 6:39 as a millennial I highly disagree with this statement. We more so share similarities with generation x than the current. Most of our (older) siblings were generation x or millennial. We looked up to gen x in so many ways from music (90s hip hop/grunge r\&b etc) to fashion ans slang. We experienced life pre Wi-Fi technology prior to its boom which came at us while we were getting older in \textbf{age}. Please... retract that statement lol. 😉😁😁\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Everyone seems to want to belong to the generation older than them. We get it, you're not like the rest of the people your \textbf{age}. You are special.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small The irony is that generations are typified by 30 year increments. The Gen x cut off 10 years ago was 1987 then 1985... They've also hybridized Gen x and Millennials, making them Xtenials the 1980-1987 bracket🤦🤷Growing up a latch key kid, and staying home after school alone, one dial up computer during \textbf{senior} year of high school, using a corded phone to talk to friends, listening to grunge music and wearing flannels before "hipsters" was a word. Reality Bites being a favorite movie, when the Rachel hair cut was in and Sunflower perfume was popular as well as Claire's for the teens. That was my reality✊\normalsize   & \cellcolor{green!27}Senior & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}\small 1981(millennial) I got some \textbf{old} school and new school in me. You're still classified as a young adult if you are 40 and under. But they recently moved that under 45 because of life advances in health..etc. I'm still on the younger side. \textbf{Old}, young man is the way to put it\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Jessica Emile it was 4 weeks straight the only thing on tv. If you dont remember every little thing about 9.11. , you wasnt \textbf{old} enough, so you're a Zer.I remember how i came back from school, sparked up a joint, sad back and watched my favorite court Show. (Started smoking around 14) Suddenly tv programm was cut off for special News and from that point the only thing in the World for 4 weeks was WTC, Al Quaida, Bin Laden etc.Saw the first tower collapse and i knew this will be the beginning of the end. Since that day the World ist going straight down the hill.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small Meowlody I agree, we have \textbf{nothing} in \textbf{common} with what they call millennials\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Gen z = insufferable snowflake\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small The Cold War needs to have a space in it and it's bugging me.Also idk where I am...  was born in 93 but still dk as funny as the generational lines are. Could I have been born during a generational cutoff? I feel like I have much in \textbf{common} with genY as well as genZ... but idk. All I know is that I think too much, lol.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small I never heard of defining generations by their memory or emotional connections to events. I really like this form of catagorization though. I was born in 1996 and feel closer related to millenials then gen z. I was living in DC during 9/11 so I do have a more vivid memory of the event than most people my \textbf{age}. I also went to boarding school and I had a land line in my dorm so I didn't get my first cell phone until \textbf{senior} year of high school before going off to college.\normalsize   & \cellcolor{green!27}Age, Senior & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small I wouldn't consider those to be born in 1996 born in the same generation to the present day. Like how could they be in the same category as the kids born from 2010 and onwards??? I'd cut the gen y \textbf{age} range as early as 2000.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small I would think that we baby boomers and gen x have the most in \textbf{common}.  I'm from the last of the baby boom generation being born in 64. I don't know how any of us survived growing up: no seat belts, riding in the back of pick up trucks, drinking from a water hose that had been laying on the ground all day waiting for the hot water to run out so we could drink the cold water, playing from sun up to sun down, riding our bikes with no helmets or knee/elbow pads, playing on \textbf{monkey} bars, sometimes falling and getting hurt. I don't ever remember anyone getting sued over it. Losing at something at school and having to deal with it. Failing a test at school and having to live with the fact that it was an F. But let me tell you we had sooooo much fun growing up. I wish times were the same. RIP good ole days!!!\normalsize   & \cellcolor{green!27}Common, Monkey & \cellcolor{green!27}Ethnicity - Black, Social Class - Working class & \cellcolor{green!27}2/162 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small For me the difference between millennials and gen z is technology. Millenials was the last one using \textbf{old} tech like cassetes, vinil, vhs recording, first mobile phones and trought they live, they see techology evolve exponencially, and saw the first steps of the internet, and at same time they saw older techologies desapearing in favor of computer boom. Gen Z already born with techology of modern \textbf{age}. Allways had smartphoones (or at least pdas) and Internet was widly avalible almost everywere. For them Internet is allways available like having water and electricity.Millennials are the gen of techology revolution era. Gen Z are the gen of techology available everywere era.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/110 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Proud Gen Xer. Link between the \textbf{old} and new. Analog and digital. We run circles around Boomers and Millennials period.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I am from Louisiana...so we can all pretty much relate to Hurricane Katrina, where we evacuated to or if we stayed, how \textbf{old} we were, the reaction when the levees broke, and how much water we got into our houses. A lot of Centenials were very young when that happened so doesn't hold as much value/they remember less. Where as milliniels and above were definitely \textbf{old} enough to remember. Whatever our generation, it definitely changed our lives forever and showed the power of Mother Nature and the affect of Hurricane destruction on a population.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/94 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small And Gen X has \textbf{nothing} of all this\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Dogmo Satchmo   Add and Autism are about as legit \textbf{mental} health classifications as the tooth fairy is real.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Born in 1970, in late elementary school then in jr hi and high school when Reagan was president.  \textbf{Senior} in HS when Bush 1 elected.\normalsize   & \cellcolor{green!27}Senior & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Im born in 1980, so many consider me to be a millennial or somewhere lost between gen x and millennial. Computers came into our classrooms when I was in 4th grade, we only had 2 or 3 i think. I had never used a type writer until I was asked to use one at work, I said, "I dont know how to use a typewriter", my \textbf{old} manager joked about that for years. Technology was really on the rise during my childhood. Cell phones became more \textbf{common} during my teen years.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/91 & \cellcolor{green!5}2.198 \\  \hline
  \cellcolor{green!27}\small Epic Corn exactly; i know for a fact many in the us didnt have a tv maybe such as those who lived in a farm or a ranch at that time; also, why should a \textbf{terrorist} attack determine the generation of someone?\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Sorry, but I'm a millennial and have 4 kids under the \textbf{age} of 10. They own a cell phone or tablet and the only technology they use is the computers at school. My nephew, younger cousins and half brother who were born after 2000, have all the gadgets and yet I see a lack of respect; can't look at you in the eye while having a conversation; always on their phone and can't hold a conversation. I would hate for my kids to end up like that.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small Millenials today don't have \textbf{common} sense and lacks resourcefulness\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I'm gen z but 9 year \textbf{old} was born at 2009\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I was born in 1995 and remember where I was at on the \textbf{terrorist} attack. I was at my grandmas. I remember all the wars going on . Does that make me a millenial?\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Shadders2010 Generations aren't defined by a set amount of time passing, they're based on a unique culture general trends shared predominantly by a single \textbf{age} range. The perceived acceleration in tech advancements between 2000 and 2010, in which smart phones and devices caught on and became main stream, and the sudden shift in global politics caused by 9/11 created a short and bizarre period which was influential enough to shape an entire generation.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small \@Shadders2010 By what metric? I gave two revolutionary changes (the rise of smart devises and 9/11) which had a sudden and dramatic impact on the world, yes the world changed between the 1930s and 40s, and that created the Silent Generation. There are periods where events cause change to be more dramatic than in other periods, this is undeniable, the industrial revolution, WW1 and WW2 and the Technological revolution, which we're still undergoing are all examples. 2000 - 2010 bridged the gap between the pre-Internet and the hyper-connected \textbf{age}. (I know the Internet existed before 2000, but it was slow, hard to access and most people didn't have or use it commonly, now you can stream 4k video to your phone in the middle of no-where).You've also got to remember generations aren't just about what happened during the years people were born, but what the world was like as they grew up. I (born in 2001) had a \textbf{black} and white game boy as my first tech device when I was about 6, kids born in 2011 are likely to be playing on an ipad by the \textbf{age} of 3; while someone born in 1940 and 1970 would have been playing with basically the same toys and getting basically the same up-bringing.\normalsize   & \cellcolor{green!27}Age, Black & \cellcolor{green!27}Age - General, Ethnicity - Black & \cellcolor{green!27}3/213 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small I was born in 1996, I grew up with crt tv sets, VHS tapes, and desktop computers. I got my first cell phone at \textbf{age} 15 and my first smartphone at \textbf{age} 19. (Kinda lagged behind the crowd). Still not very tech even now, so I can't really relate to gen z. Especially since all I listen to is 90s and 00s rock lol\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/64 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small fourthgrace yeah, well I didnt have my first cell until 12, my first smartphone until 14, and first laptop until 15. Didnt have social media until 14. Also, no one in my family had a cell until I was like 8, same for laptop and internet, and no one had a social media account until my brother opened a Facebook when I turned 9, and first family smart phone when I was 12. We didnt have a computer until I was 5. I remember tv with antenna on top. No cable. \textbf{Black} box tv and white box computer monitor. First internet browser I used was sbc yahoo browser. I see two year olds swiping youtube videos themselves. Didnt watch internet videos until I was 9. No surpise as 2-year olds are cognizant enough to do many things themselves.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/138 & \cellcolor{green!27}0.725 \\  \hline
  \cellcolor{green!5}\small TGpoppins from many sources, internet wasnt \textbf{common} in households and in elementary schools until like the mid 2000s; even internet use wasnt that high\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Karen Vayssie now you just edited your first comment to make it sound like I am \textbf{crazy} when I said that you said your brother cant recall anything before the 2000s. I should have known you are the kind to start a fight considering you think 1996 is millennial but 1997 is gen z. Thats like saying 2006 is gen z and 2007 is gen alpha\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Early 2006 and same I didnt have my own tablet or anything until I was 9 and I got my first phone when I was 12 it was a very \textbf{old} samsung\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@MegaAirplanelover you guys think you have it bad? I didn't get my own smartphone until I was 17, well into high school when other kids my \textbf{age} already had smartphones for years. I'm in Gen Z(born in 2000).\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Same but I'm an 04 baby. I remember playing with \textbf{old} flip phones and getting super excited over blackberries(type of phone). I remember silly bands and riding bikes and chasing the ice cream truck. But nowadays as teen my life heavily tech influenced. Everything from schoolwork, to family, entertainment, shopping.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small \@TGpoppins You could def use some more historical insight for your metric.I agree that the 2000s bridge some kind of gap but it's not nearly enough to be its own generation. The most revolutionary decade BY FAR was the 1960s and even they wouldn't be considered their own generation. Ironically, streaming 4k videos to  your phone in the middle of nowhere is not \textbf{common} yet at all today. Whereas 50 of American households did already have the internet by 1998. It was DEFINITELY \textbf{common} by 2000, and not hard to access at all. Google and Ebay were exploding in 1999 and in 2001 Wikipedia got thrown into the mix.Your first device may have been a black-and-white Gameboy in 2007 but the first black-and-white Gameboy came out in 1989 and was an instant hit. And by 2004 the Nintendo DS had already come out which is the second best selling system of all time behind the PS2. And to someone who's older like me honestly there's not that much of a difference at all between a Nintendo DS and an Ipad. Both have touchscreens and both have kiddie games with 6th-gen-ish graphics. Add Tamagotchis to that and childhoods changed way more during the 90's than during the 2000's.Again, ironically, the difference between someone born in 1940 and 1970 is HUGE dude, not at all "the same toys and upbringing" as  you said. Kids in the 40's were playing with wooden toys and maybe some board games, and if they lived through WW2 in Europe they probably didn't even have that. Meanwhile kids in the 70's had freaking video game consoles like the Atari 2600, legos, audio books, plastic Star Wars toys, action figures, easy bake ovens, doll houses, play phones, widespread access to arcades, and let's not forget the impact of Disneyland.As someone who lived through it all, the rise of HD, easy-to-access online gaming, and smarphones cut the 2000's in half for me. 2004 feels a lot like 1997 and 2008 feels a lot like today. Trump's Election and \textbf{Brexit} are also bigger events than 9/11, reversing cultural trends that have been going on since the 1960's. The collapse of the Eastern block from 1989-1991 was also a bigger deal than 9/11. Overall, it just doesn't make much sense to define 2000-2010 as its own generation like you did.\normalsize   & \cellcolor{green!27}Brexit, Common & \cellcolor{green!27}Nationality - European or anti-Europeans, Social Class - Working class & \cellcolor{green!27}3/393 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}\small Yes but only because of the recession. Am 16 now but never really had the internet until around 11 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Jessica Cookie do you think that having a phone at 8 is late? 😨 I didn't have one until I was 15. I'm glad I didn't, because I could avoid cyberbullying and all this stuff. I had enough at high school to give them more chances to annoy me. I could enjoy doing other kind of things and hobbies. In my opinion, teens shouldn't have a phone until they're mature enough to understand all risks which technology can bring. It has advantages and disadvantages and we have to take into account both sides. I'm writing as if I was an \textbf{old} adult, but I'm not. I belong to "Generation Z" too. I'm just worried for the premature use of technology without enough knowledge.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small Born 1983 and I would say that people born in the early 80's can go either way (Gen X or millennial) or maybe even a sub category somewhere between the two. I relate more Gen x than millennials. Didn't have MySpace account etc. I have Facebook and YouTube but don't use Twitter or snapchat or instagram. I have several childhood friends (same \textbf{age}) that aren't on any social media at all and we communicate via calls and meeting in person, occasional texts but they're not as keen on texting. On the other hand I have other friends the same \textbf{age} who fully are in the millennial category - in so many ways and as I get older I notice the differences more and more between the two types of people. It's odd because we are the same \textbf{age} and went to school together but it's like one group has fully embraced it and the other group not so much. We were pretty late getting (dial up) internet in our house, I'm sure I was 20/21 by that time and getting ready to leave home anyway. I did have a mobile phone at 18 though - basic calls and could store 10 text messages max type of thing. I still have my original email account I set up when I was 18 - it's on yahoo. I still have a vhs player to watch all my \textbf{old} tapes but also have an extensive DVD collection. I don't download movies as I like to keep a hard copy when I've spent my money on something. Same goes for music. I still use and buy CDs. I've only downloaded about 3 albums in my life and have recently be repurchasing some of my worn out CDs. I also have an \textbf{old} cassette player that I use to play some \textbf{old} concerts and stuff I taped off the radio when I was a teen. My phone is over 3 years \textbf{old} but still runs fine so I feel no need to replace it yet (it's an iPhone SE from when they first came out - I'm sure they are a good 5 newer models out by this point). I don't feel like I always need the latest tech and things which I do think is a millennial trait in general.All that said I do think I'm pretty Internet and computer savvy. I know how to do stuff, I am aware of memes and what they are but don't really find it all that funny. I get the references and jokes made most of the time but I just don't find it all that funny. I do watch YouTube a lot, and a lot of the YouTube channels I watch are by millennials so I must relate to them in parts or I wouldn't follow them. I am attached to my phone a bit more than I would like to be and would be upset if the internet dies tomorrow.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}7/496 & \cellcolor{green!5}1.411 \\  \hline
  \cellcolor{green!27}\small I think that 96-04 should be like considered like a \textbf{transition} generation, because they're widely different than most Gen Ys and Gen Zs\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Meh, my millennial experience as a 30 year \textbf{old} is different that an older millennial that's about 36 years \textbf{old}. Theres slight differences but we grew up with a lot of the same stuff\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Red \textbf{Dot} ayyyy\normalsize   & \cellcolor{green!27}Dot, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (South- India, Pakistan, Bangladesh), Ethnicity - Native-American & \cellcolor{green!27}3/3 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small I am British not \textbf{yank}.\normalsize   & \cellcolor{green!5}Yank & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small why be a \textbf{yank} all the time?\normalsize   & \cellcolor{green!27}Yank & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small born in 92 and my younger brother in 98, I was 5 when he was born, we watched exactly the same TV shows, Disney Chanel, toy ads, PS2,I got a phone 3 years before he did, we started watching youtube like 10 years ago etc etc.  As soon as he got into High school he was in the same bubble I was in - although I was getting ready for college. For the past 5 years with the rise of Social media and everybody using the same apps, new terms, it kind of  creates a sense of sameness and \textbf{age} gets a bit lost on the internet...10 years older than me or 10 years younger than me honestly it just doesn't make much difference  if we both shared similar upbringings during childhood. I feel you will always feel in the middle, for me a completely different generation would be anyone who was in their teens in the 80's and anyone born after 2010, most likely my future children's generation.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/169 & \cellcolor{green!5}0.592 \\  \hline
  \cellcolor{green!27}\small As a centennial, I can assure you our generation is \textbf{nothing} like that of the Millennial's. We have PewDiePie vs. T-Series, YouTube, and rising conservatism as shared experiences.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Im 37 please do not \textbf{lump} me in with whine-enials\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small 30 \textbf{old}. working 14 hr per day.Not marriedNo own housePay bills and loansLife is meaningless\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small There is a big divide between labels and \textbf{age} from country to country. In this video, based on the US population and culture, Gen Y has certain \textbf{age} ranges and fratutes attributed to it. But in Italy, where I am from, people my \textbf{age} (I am 33) have a mindset that is very very generation x, due to the culture not changing fast. I live abroad since 2010 so I think quite as a gen y in anglosaxon countries, and when I get together with my childhood friends, I sometimes feel like I am talking to my parents.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/98 & \cellcolor{green!5}3.061 \\  \hline
  \cellcolor{green!27}\small The video bleeds a lot of dates together. Gen X is actually largely considered to end in 1984 and Millenials after that - but I think in reality X stretches a couple more years than that, because there's a world of difference between people who grew up with mobile phones and computers in the house and those who didn't, and that shift didn't actually start until the late 80s. Anyone born before 1990 has little to \textbf{nothing} in \textbf{common} with the experience of the iPhone generation.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/86 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small But someone born in 1990 has \textbf{nothing} in \textbf{common} with someone born in 2005 though...1990 - 90s kid, no iPhones during childhood2005 - 10s kid, iPhones peaked in their childhood\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Ok  I was born in 2000 but i had my first phone at the \textbf{age} off 11 and that was just an Nokia and my parents where against all those screens but now all the kids at the \textbf{age} of four you see walking around with an iPhone or tablet .\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small \@Millenials who keep getting mocked by Baby BoomersWhen the Baby Boomers were your \textbf{age} I bet all the traditionalists mocked themAnd soon the millenials will take on the role of the baby boomers and mock the next generationThan that generation will mock the nextAnd so on(I'm a Gen-Zer)\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Re Gen X: so, \textbf{nothing} happened in the 70s? I remember disco, the oil crisis, the Iran hostage crisis (which spawned "Nightline"), Sesame Street, Wonderama and Zoom; I was a latch-key kid; I remember life with rotary phones that did NOT have call-waiting, caller ID nor answering machines (the old-timey term for voicemai). A basic calculator cost hundreds of dollars, and the premier  computer company was IBM. DOS. Dot-matrix printers. Ditto machines and carbon paper. Ah, nostalgia.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small Charles Rogers and emojis; they use social media at a single digit \textbf{age} too\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I like the generation thing and generational 'identity' or grouping/classification system although people vary MASSIVELY one from another no matter what However I would like to see one modification. Millennials split into at least two. Millennial 1 or A or Millennial 2 or B. For the older split and younger split. Because there's quite a difference between \textbf{age} 24 and 38 for example\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Dear millenialsUr fine... lazy bums (hippies as i call it) snowflakes, treehuggers, vegans, entitled brats and sjws existed waaaay before you guys in fact my mother is kind of a \textbf{snowflake} herself and shes a baby boomer-a gen x dude\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Just Peachy millennial, but the generation of your parents has \textbf{nothing} to do with what generation you are; millennials can have boomer or gen x parents, some even with members of the silent generation; gen z could have gen x, millennial, and boomer parents\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Tommy TwoGun i wouldn't be so sure of that. most people my \textbf{age} that have it don't use it anymore, and nowaday's teens never even start.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Tommy TwoGun the company itself is doing fine, i'm talking about facebook \textbf{dot} com as a social media plattform\normalsize   & \cellcolor{green!27}Dot & \cellcolor{green!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Tommy TwoGun FB is not slowing down beacause of 40 year \textbf{old} moms.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Im gen Z, millenials are lame\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I'm late to this video but my dad is born ‘78 mom born ‘81 \& I was born in ‘99 . I had a nokia phone as a child lol I was maybe 6 yrs \textbf{old} \& I remember playing outside a lot more than kids now \& those polaroid type of cameras . I had one lol I relate to ppl who are 25 yr olds - maybe 27 yr olds at most.. maybe bc my parents were young parents 🤷🏾‍♀️\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small That moment when you have grown up as \textbf{immigrant} and literally have grown up with gen x values and the parents are millienals  but born in 1999 literally not a 21th but still am?Well, YEEEET!\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I'm a 15 year \textbf{old}. My Gen Z blood has made me a Chad nationalist. DEUTSCHLAND IST BESSER!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Gen Xer here, born in 75.. The product of a broken home through divorce. Had a father but like many boys in my generation only saw him every other weekend. Learned what a man is from Harrison Ford, Stallone, Arnold and Mel Gibson. My eyes and ears were exposed to Duran Duran, Van Halen, Prince, \textbf{old} school rap and Heavy Metal later grunge. Came home from school as a latch key kid and saw Freddie Kruger, Michael Myers, Jason Vorhees over and over again. Now I have two teens in Gen Z.. Proud to be an Xer because we overcame a lot growing up with little or no supervision lots of times.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/112 & \cellcolor{green!27}0.893 \\  \hline
  \cellcolor{green!5}\small I hate being a millennial. But I love \textbf{old} stuff from the 80's and 90's don't get me wrong.   Birth year: 2004\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Just about all of this is total B.S.! I asked my aunt in late elementary/middle school (around 1995-1997) what generation I belonged to. There WAS NO millennial generation yet to claim to belong to and that term was unheard of at that point. I was born in '84. My aunt laid it out like this...The Greatest Generation, The Baby Boomers and then me, Generation X. My aunt also worked in retail. There was a clothing brand that she sold in the store she worked in, exclusive to that store called "Gen X", sold in the Juniors department and geared toward my \textbf{age} group, which I also owned some of their pieces as gifts from her. If I was not Gen X or classified as such, then why would this even exist?? This "Millennial" term and demographic did not become a thing until my generation started having kids. Millennials are products of Generation X. I refuse to be called a Millennial when I remember the Gulf War, can work a rotary and payphone, tape players, record and 8-track players, can drive a manual vehicle, grew up on NKOTB, Debbie Gibson and The Bangles and 80s/90s hard rock. I grew up rolling windows up and down and locking car doors with NO power. I also grew up using one of the first \textbf{Apple} computers available to the public (hello \textbf{black} and green screen, prompts, code and hard disks!) And I'd also write this all in cursive, but Millennials wouldn't be able to read it. Ugh. I AM NOT A MILLENNIAL!! Millennials would be MY children!! Children born anytime AFTER Y2K are Millennials because it was the start of the new "MILLENNIUM". All these made up terms are starting to get on my nerves.\normalsize   & \cellcolor{green!27}Age, Apple, Black & \cellcolor{green!27}Age - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/291 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small Danielle S I was born earlier that decade and I also have some millennial traits. I think it comes from technology, forward and contemporary thinking - moving with the times we used to say, and being around millennials more, now that there are more of them. I've yet to work with 1999+ but the earlier millennials I've found so far to be \textbf{nothing} but a breath of fresh air among older workers. I am predicting there could be more of a disparity though with the Alpha Generation when they hit the workplace..\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small you pretty much are depending how \textbf{old} your parents are\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Gen z is also diffrent more conservative more then the bayby boomers and most of them hate millenials well at least the ones that are retarted like the ones that think its okay for an 8 year \textbf{old} two be trans\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I'm 9 years \textbf{old}, what?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Too much \textbf{ageism} and discrimination from San Francisco Millennial crowd! They tend to isolate themselves if one should be not their EXACT \textbf{age} group! ln fact I have found them quite RUDE to both perceived older folk as well as younger people  (uh ah hem... like mois)!! Such a shame! Too \textbf{old}, too young, how about JUST BEING YOURSELF and RESPECTING ALL \textbf{age} groups!\normalsize   & \cellcolor{green!5}Age, Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/64 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small u guys are much younger than me bcuz im was generation A😂😂 im borned in 1700😂😂😂 now my \textbf{age} is 319😂😂😂\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Genz ish 1999 baby. But speaking for myself I don't like kids having devices at a young \textbf{age}. My sister got my nephew a table at the \textbf{age} of 5. Which I find ridiculous.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small why the need for Wi-Fi....there is \textbf{nothing} wrong with pissing on a wall or a tree if no restrooms are around.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small One blast from an EMP Russian warhead and these millennials and generation Z and centennials will go stark raving drangely \textbf{crazy} when all of their gizmos went KAPUT!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small The \textbf{snowflake} gen vs the addict gen.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Im 36 years \textbf{old} and born in 1983. I just have to say that i really dont relate to millennials at all.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Born in 2000...never gonna forget my \textbf{age} 😂\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I always wanted to be born at that \textbf{age} for that reason.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small If this is about someone sharing a similar collective experience, what is the difference between someone that was born in 1979 that's a few months older than me or even a year perhaps because I was born in 1980, are you suggesting their so cold collective experience differs from mine, like what remembering a baby bottle in their mouth? Seriously you're calling me a millennial and them a Gen X because of a few months difference? Or even weirder you're saying somebody that's a few months older or a year at most has a different "collective experience"?I'm 38 years of \textbf{age} and I've had some people call me a Gen X and other people call me a millennial. This all just seems like a big load of pseudoscience.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/129 & \cellcolor{green!27}0.775 \\  \hline
  \cellcolor{green!5}\small Millennials= \textbf{Snowflake} libtards\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Nobody remembers Y2K\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I'm a Gen X'r I'm all about the technology.  I got my first \textbf{Apple} computer in 1984, at \textbf{age} 9... I started young.   Now I'm watching this channel on my iPhone and playing candy crush on my iPad, while I take my train home.   Gen X - very independent, latch key kid. I had no problem taking the 'EL' to Chicago for the day and come home right before sunset.  This was at \textbf{age} 12.  Now there are so many restrictions with your kids.\normalsize   & \cellcolor{green!5}Age, Apple & \cellcolor{green!5}Age - General, Ethnicity - Native-American & \cellcolor{green!5}3/84 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I'm an older millennial I was born in 1989. Personally I love my phone and my memes haha I am not in anyway narcissistic or lazy. I do remember my space haha sometimes I miss my space. The good \textbf{old} days.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small My 6 year \textbf{old} was born in 2012 she already knows how to operate a computer and type she does not and refuses to play with toys she is all into computers and technology and building I think the up coming generations are going to make flying cars and stuff\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small \@3:48 do they really need lab coats to stereotype someone by their \textbf{age}?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small When I was young I wanted the world to change so badly, now I'm \textbf{old} and wish the world didn't change so much.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I'm born in 2009And I'm lucky I grew up with technologyBut when I'm a baby i don't know cause I don't know when was the first technology inventedi live in \textbf{old} years to now\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I'm a Xennial (1976), that micro generation that's a little bit Gen X and a little bit Millennial, but on our own just the same.  Anyhoo, there are people my \textbf{age} who went all digital while Gen Z, who grew up all digital, are opting to read real books (instead of ebooks), and it's they who have brought back vinyl and cassette tapes in addition to videotapes!!!  That's going to be the generation to turn everything upside down.  I say it's about time.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small As me born in 1995 (24 years \textbf{old}) im not gen z in any shape of form its 1996 and later\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Wrong 1979nis gen y i grew up in the 80s and 90s and had internet at 14 and had video games \textbf{nothing} in \textbf{common} with my uncle and aunt whos a gen x\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Gen Y is definitely much more resilient. They've seen an economic crisis/recession. They've seen industry transformation. They've seen political division and digital \textbf{age} transitions. Then gen x and traditional genGen z isn't too bad either. Some good apples. And a lot of bad. Similar to every generation tbh.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Generation \textbf{snowflake} is worse than x or z ever was\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I dont believe any Gen-Z is of legal drinking \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@MAC VENA millenials are anyone up to the \textbf{age} of 37. The next generation is gen z.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@MAC VENA I am aware of the great depression. My grandma was a child through the war. Like my grandma, we have a get on with it attitude and some of us have a make do and mend one too. Like i said there are different types of people in diffetent generations. Some people were too afraid to fight, they were killed for refusing to fight. Thats no life and doesn't make them any better than the next generation. There are good and bad in each. The trouble is that people who are not \textbf{old} enough to have gone through it personally claim they have and have the attitude that they are better than us. I am anti war, because \textbf{nothing} good ever comes of it. So I am glad we haven't had a war since and I hope we don't. Do you not want peace?\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/146 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small I feel like you could have done more with the differences between gen y and z. I feel as if gen z is more cynical and politically incorrect. While millennials were introduced to Technology at an \textbf{age} they can remember, it is literally part of Gen Z's everyday life. Gen Z sees the global strife for many things as irrelevant, as it is something that will go on forever. Gen Z is less for government or commercials telling us what to do and believe, and are more realistic and individualistic.Millennials see travesties going on around the world as a means to take action, as they feel the world is getting worse, while gen z sees travesties as something that happens everyday, and they either want to release the burden of caring or they become depressed. That doesn't necessarily mean that we are more or less apt to try to do our part, but it is usually used more as a learning experience than an act of sheer good will.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/170 & \cellcolor{green!5}0.588 \\  \hline
  \cellcolor{green!27}\small So as the movie industry goes backwards with \textbf{crazy} prequels and re makes , we must be going down too ? What were the generations called in America (in order please) in the last 200 years or b4 1945 ?.?.? 🇺🇸 and Generation order or labels ? I mean if we are gonna profile our kids let's at least practice correctly then 🤔\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Gen X here (43). My house is paid for. And I own 2 rentals. I go to Hawaii every year and other big vacations. I drive New BMW cars. So when I get my daily Starbucks. I smirk at the Y or M barista who rents a house and drives a \textbf{old} car and also they work 2 jobs and are trying to pay off their college loans. It's called hard work. I worked almost full time at 15. Gen y and M did not have to work a job in high school and many in college. You start life late and live at home in your 20s. You guys do not work overtime and do not understand your first 7 years in a job you are suppose to own your job and prove yourself. Then you can relax and enjoy the money...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/143 & \cellcolor{green!5}0.699 \\  \hline
  \cellcolor{green!27}\small It sucks that modern society is reliant on a computer, (or anything an EMP can damage in this case) because if there is a huge emp attack on just about any first world country, its essentially the end. Very few can drive since just about every vehicle now rely on a computer in some way, aircraft, well, too bad, manufacturing any goods, well, no more! Almost everything gets shut down. Thanks to the EPA, there will be no \textbf{common} way of transportation and farming on large scale.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small I was born in 1995 and by your definition I'm gen x? Growing up we had a 1 color and 1 \textbf{black} and white tv. To this day my dad only has a landline and no cell phone. And we got a computer when I was 10.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small I was born in 1997. We had only one corded telephone in the house so we had to stay in the kitchen whenever making phone calls. My parents didnt have a mobile phone until I was like 8, and before that, it was uncommon for many to have one. We had antenna tv during my early childhood with limited channels, and we had to adjust the antenna everytime to get the tv to work. We used those \textbf{black} casette tapes. We didnt have a computer until I was like 5, and got home internet when I was in third grade, and before that, never saw internet before. None of the computers in my school had it. My dad got his first laptop when I was in third grade. Before that, he always had to take a suitcase with him to work.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/141 & \cellcolor{green!27}0.709 \\  \hline
  \cellcolor{green!5}\small \@isaiah2810 I'm pretty sure the list reads, if you are this, if you are this, if you are this. I realized that too as I read it.  they had internet when I was a \textbf{senior} in high school so I guess I'm not generation x according to this guy either.\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Peter Dods internet existed since 1969, so before the oldest millennials were born; the oldest millennials used the web before college since the schools made them do so. However, millennials remember life before the web was a \textbf{common} thing to use at home and in elementary schools.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small MegaAirplanelover   90s dial up Internet doesn't count. \textbf{Nobody} used it and it was slow. The internet and computers went mainstream in 2003 and by then I was already in high school. So most of my childhood was spent playing outside.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@Channel I was born in 2005. There was landline in my home and also the keypad phone. But we were used to use landline than that \textbf{crazy} type of phone that just had started to have access to internet.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small The comment that the original poster put completely flew over most of you people's heads. With some exceptions, hes making a GENERAL statement and he is correct. For example...I'm sure those born in the 90s have seen an \textbf{old} rotary phone but GENERALLY SPEAKING, people born during that time doesnt even know what a rotary phone is. The ones that know what a rotary phone is probably saw one from their grandparents.Example 2..I've met people born in 2000 and watch \textbf{old} tv shows such as Three's Company or The Jeffersons.  But again, GENERALLY SPEAKING, people born during that time wouldnt have a clue what those shows areI was born in the 60s so I've used rotary phones, had a \textbf{black} and white tv and in my opinion, life was better in the olden days since we interacted face to face and played outside all the time. Not like  young people today that cant go 5 seconds without looking into their phones like retards\normalsize   & \cellcolor{green!5}Black, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}3/165 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small \@Sandwich Breath Ummmmm those \textbf{old} Boomers had those too.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Knoxx \textbf{Black} you could be right there is some crossover\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Remember when creed dyed his hair \textbf{black} and drank \textbf{R\textbf{ed}} Bull\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/11 & \cellcolor{green!27}27.273 \\  \hline
  \cellcolor{green!5}\small I was born in 2000 so Im not going to remember 9/11 but I don't claim any of the jake paul, tide pod eating teenagers now. I feel like their should be a subgroup within millennial because I do classify myself as one more so than a centennial. Hannah Montana, Dora, Spongebob are all part of the late 90s- early 00s era and there should be a group just for them. We were too young too really know about 9/11 but too \textbf{old} to have anything to do with tide pods.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Actually gen x can officially only be 18-19 years \textbf{old} max\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I don't belong in a box. I'm me \textbf{nobody} else. Unique in every way\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I'm 17 years \textbf{old}, born in October 5 2001 so I'm admit myself as half of gen z and half millennial. Btw watch in 2019 Anyone?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Millennials are the losers mainly here.Gen Z had the opportunity to see how idiotic and easily offended the M was.This is why they lean more conservative at an early \textbf{age} than M, they still think leftism is th go.notall of course...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small I am definitely an older X'er, just past the half-century mark.  It is easy to relate to younger boomers-early-mid 50somethings (who are often lumped with \textbf{old} X'ers).  Some of my coworkers, older Millennials born early 1980s, say they relate to my generation more than their own.  And having been immersed around the World War II/Great Depression generation, I was raised around the sense of not wasting, as for my folks that was not good for survival in their era.  Tennyson, from Ulysses:  "I am a part of all that I have met."\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/92 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small Born '94 here. I think years between '91 - '95 is very complicated. I can't even relate to these 15 year \textbf{old} kids nowadays nor with 30's of \textbf{age} people.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small You \textbf{bald} head bubaclouts over 21 can't claim gen z\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Geez 37-38 is an awkward \textbf{age}, right on the line of going from gen x to gen y. Am i combination of both, generation XY lol I mean I turned 18 in 1999 before the new millenium started in 2000 before all tech took off like fast internet, mobile phones etc so I was legal \textbf{age} 18+ could vote etc.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Man I don't wanna be a millennial, I'm too \textbf{old} school\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I guess 40 years \textbf{old} makes me the tail end of Gen X. No ancient computers at school until about 2 grade 2 or 3. I remember watching the Challenger disaster on TV in  first grade.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I was born in 1977 and am gen X i guess. Grew up without inet/cell, only 8088/286/386/486 comps that could only connect to BBS's/CompuServe/Prodigy.. Grew up listening to metal, and still do. I do find that I have many things in \textbf{common} with so called "millennials". It's all just a label.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small The limit between gen Y and gen Z isn't clear at all. Some people say gen Z begins at the XXI century. So 1996 to 1999 are Y.  Honestly I don't inderstand how people does the gen groups but I'm not agree with.  I don't feel like a gen Z, with the people born in 2006 and more. : I like some people younger than me, this is not the problem, but my experience is very different.  My father is a traditionalist and my mother an X.  And I like \textbf{old} and new things.    ' Somebody like me ? I feel alone.  X)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small Charles Branch someone got butthurt and cried RACIST\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small what about zellennials I think they are called a micro generation between gen x and millennials? The experienced the world pre internet \textbf{age} as kids and grew up with the technological advances in the 90s and 2000s, because I tell ya I cannot relate to millennials at all although this video classes me as one.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small I was born in 1984 , but I don't feel like I'm a millennial . I'm very \textbf{old} fashioned , I work 60 hours a week , I'm not on social media , I don't feel entitled , I respect my elders , I believe In God and marriage and Alot of ppl make fun of me because of it , they think I'm \textbf{weird} , and all the older folks love me .. lol\normalsize   & \cellcolor{green!27}Old, Weird & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/75 & \cellcolor{green!27}2.667 \\  \hline
  \cellcolor{green!5}\small I think those on the ends of each generation are not fully like those in the middle. Like a younger gen x person can have most of their life very much like an older millennial and a young millennial may have more in \textbf{common} with a late gen z person than with an older millennial.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Prob bc even a 36 yr \textbf{old} was still in school in the earliest millennium. When ppl used to think the world would end bc of y2k. I think that's what they called it\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small We (Gen Xs) have a lot more in \textbf{common} with our parents then the video claims. Yes we did grow up with the benefits of out parents, however we grew up during the height of the Cold War, we saw the Berlin War fall, we don't remember the moon landing. We grew up during the emergence of IT, so we are not collectively familiar with technology as our children. Yes we grew up with music videos, but when we were growing up we tended to listen to the music of our generation, not our parents. No one in his right mind who grew up in the 1980s would dare admit that they listen to the Beatles. Unlike, later generations who are happy to listen to the music of their parents generation. It is different now we are grown up, things changed in the 1990s. Hence in many ways we are a lot more like boomers\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/155 & \cellcolor{green!5}0.645 \\  \hline
  \cellcolor{green!27}\small Who here didn't get a family desktop until \textbf{age} 16 and their first flip phone in college?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I got my first phone at \textbf{age} 18I was born in 1997 as well.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I am 26 now. My family got me a Windows XP PC when I was 12 years \textbf{old}. I got my first email ID after that. But before that, I was already an expert in using the basic functions in Windows 95, 98 and 2000 from other places. Probably before the year 2002. I started using high speed internet in my PC when I was 17. I had a Nokia 1203 feature phone without internet then.I got my first phone with 2G internet when I was 19.I started using 4G internet when I was 23.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small Alvin Toffler  said first we will divide into tribes.....then it will be young against \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Why dont this \textbf{old} people leave us alone and live the life and find someone they're own age\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Judging people because of their \textbf{age} is not wise.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I was a 90's kid raised by a baby boomer mom. I really don't think of myself as a millennial at all, and I have more in \textbf{common} with generation x than I do with Generation Y by a long shot. I'm also very conservative and strict with my kids on how much time they get to spend with technology. No video games, no phones, no iPads. They do have kindles, but only use them for reading and 30 minutes a day of games. That's it.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small You mean BORDERS, not boarders. You must be a person of HATE then. You must be in support of what I call the Logan's Run syndrome (That was a novel and film of a dystopic society in the 23 century where it was REQUIRED to end one's life upon reaching their respective 30th birthday! Is this the sort of thing you profess? I am a centennial but I do NOT believe in condemning older people -- just because they had too many free annual trips about the sun! This \textbf{age} catagorising into little 'boxes' of isolationism is SHAMEFUL!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small I'm just learning that I am considered a millennial and all the sh*t talking includes me. I am 33 years \textbf{old} and find myself between both worlds of the millennial and Gen Xer. Yes, I related to much of what the video described of millennials, however I am less tied to media and technology than the typical millennial younger than myself. I remember the \textbf{age} of no internet and having to sit near the wall to have a phone conversation. I remember getting excited for the super long phone cord my mom purchased for our phone that allowed me to stretch it to my room. I remember playing outside until the street lights came on, writing essays by hand or on my mom's typewriter when I got into my preteen years. I remember using huge floppy disks and popping records onto my moms record player. I, also, remember winding tapes with a pen, waiting as I rewinded back to my favorite songs, or pressing the record and play button simultaneously to record myself or songs on the radio. I remember cartoons and shows from the 80's as much as I remember shows from the 90's. I was filled with imagination and my childhood was less electronic and filled with make believe play, reading, writing and drawing. Yes, when the internet became a thing in my preteens, I was there for it exploring Yahoo, spending my free time on aol message boards and chat groups. Writing my stories by hand became typing them on our computer. I remember walking into Sam Goody's and the front half of the store slowly getting smaller for tapes, and the back half of the store being dedicated to CD's. Or walking into Blockbuster and them having the VHS and DVD versions on opposite sides of the store or next to each other on the shelf. I, honestly, feel like I am a part of the \textbf{transition} years between millennial and Gen X, and am neither wholly one or the other. I think that the \textbf{black} and white classification of generations is erroneous and the \textbf{transition} is, more so, a blending of cultural shifts and values. Hence why the video states that the last 4 to 5 years of those classified as baby boomers find themselves not entirely relating to baby boomers and feeling an orientation towards Gen X. Same for the early classified millennial.\normalsize   & \cellcolor{green!27}Age, Black, Old, Transition & \cellcolor{green!27}Age - General, Age - Over 65s, Ethnicity - Black, Sexual Identity - Transexuality & \cellcolor{green!27}5/399 & \cellcolor{green!27}1.253 \\  \hline
  \cellcolor{green!5}\small difference between gen z and gen alpha:gen z: bring back the home button!gen alpha: what's a home button?(gen z = \textbf{age} 8-20)(gen alpha = \textbf{age} 0-7)\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I agree the home button should be back on both the \textbf{apple} and Samsung devices! I am 18 lol\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I was 21 last year. Millennials are now teachers of gen z. Its \textbf{weird} cause at my workplace: 2 early gen z girls (2001 born and 2002 born) are teaching younger gen z boys ages 7-8.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small A couple of things. First, I'm not sure if it's different for different countries, but I've always known the 'Traditionalist' as  the Greatest generation. They lived through war and depression, they've earned the right to be called 'the greatest'. They certainly weren't silent.If going by my \textbf{age}, I'm a millennial, but I relate to gen x. I grew up listening to Nirvana and watching MTV (I remember when MTV and The Simpsons were awesome). I don't really 'get' millennials and yes, I think a lot of them are a bit entitled, sorry. But I love memes. The millennials and centennials single best contribution to society. Also they seem to care a lot about social justice and equality. The kids are alright, I just relate more to gen x.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/129 & \cellcolor{green!27}0.775 \\  \hline
  \cellcolor{green!5}\small Lol 1996 is part of Gen Y, who ever remembers about pagers, grunge music on Mtv, floppy discs and \textbf{weird} dial up internet connection.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Rd Castillo22 i am a millennial with an older brother who is also a millennial, and he acts like a gen z now always on his phone texting and using social media; he depends on the internet to get all the answers and he believes them thinking they are all correct; he will rely on yelp to decide on a restaurant or movie based on other people's reviews whether or not they are real or fake reviews; he keeps calling me a gen z even though he knows I am a millennial; he calls my mom a baby boomer even though she is a gen x cause he thinks my mom is too \textbf{old} school; yeah, only time i use my phone is if I am alone\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small For the people not understanding why the years are the way they are it is about the \textbf{age} you came(or will come) into adulthood, where you will have an impact based on what you buy, what events happen, what becomes popular, ect.  Also like this video said it is just a way people try to understand not at all something set in stone or definite.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small s 9 yeah \textbf{snowflake} reflex\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small We thirty year \textbf{old} boomers must stop the zoomers and their lazy parents before it is too late\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'm born in 1991, I can remember many things from the late 90s and early 2000s but I still consider at 27 years of \textbf{age} public WiFi more important than public bathrooms. I have no problem if my future children are on their phones as long as they understand that they don't need to spend \$1000 on the latest iPhone and create a virtual life on Instagram and Facebook. And yes I got my first phone when I was 16 and it was a Nokia 8210. Technology is not bad I'm a techie myself but drowning yourself and getting depressed in the virtual and fictional world is a huge problem with teens nowadays. That is what concerns me. I'm not from the US btw but from Greece.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small Loony Linn 1960 too. I see 1960-1964 as more gen x than baby boomers.\normalsize   & \cellcolor{green!5}Loony & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Joe DiMaggio maybe that is why we are outnumbered by millennials but there are other factors lower birth rate as in less children like two only for example ODs and suiciding are factors also a lot of the adult suicides are my \textbf{age} just thought I'd mention it\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small When I was 13 years \textbf{old}, I enjoyed bloody Marys on beaches by myself.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Gen Y grew up on MTV as well as adult swim. Gen Z ruined MTV though with their worthless reality shows about absolutely \textbf{nothing} but drama and ignorance\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@Joshua Channing I.. Uh.. what? Do you know how \textbf{old} Gen Z's are? They are definitely not making or on TV shows on MTV. Most likely just graduating high school or thinking about college. Don't talk about ignorance, you clearly don't understand the definition.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Defining a generation in relation to remembering 9/11 is interesting and makes sense a bit. I was born in 94, i just turned 7 when it happened and I have no idea where I was when it happened or the immeadiate after affects. I hated when every history class growing up asked us to write about how we experienced 9/11 because I didn't remember I always made something up. I think growing up during the technology boom of the early 2000s is wild. I got my first phone in 5th grade, it had snake, a text was a nickel a letter and my grandma got me minutes for it every month. It was only for emergencies and to check in when id go to a friends house. Technology grew faster and faster, through jr high and high school I got a new phone almost every year. (Thinking about \textbf{old} phones I'm gonna say that sliding keyboards need to make a comeback). I really don't remember butterfly hair clips, but I was obsessed with Britney Spears, Barbies and then Bratz when they were a thing. I was in high school when rage comic memes were huge and I joined MySpace just in time for everyone to leave to facebook about a year later. Personally I dont think generations should have such a broad range. I read somewhere that my moms birth year was at the beginning of the 'millennial' generation and I was born at the end (she was a teen mom). If I told her that she was a millennial shed probably argue and get mad.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/266 & \cellcolor{green!27}0.376 \\  \hline
  \cellcolor{green!5}\small Gen Z isn't bad at all, Baby boomers are \textbf{nothing} but a bunch of reefed out hippies, the generation before them hated them as well\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small My body is confused I look 20 but I have joint pain like a 50 year \textbf{old} and go to bed at 8:30 pm and still listen to Dean Martin.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small For my \textbf{age} (30 ish...) I suppose to be a millennial, however In the way my parents raise me and how I act in general, I'm more like the generation X.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Fany Sweeney 30ish? Just say your \textbf{age}. lol\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I'm almost 34, and Millennial, the thing is the older you get in that generation racket the more conservative you might think about all aspects of life, even if you are a liberal..But you still love the modern conveniences of today..GenZ, is about to kick off in just 5 years before they will make bigger influences in the media..The Boomer Media will likely bash them as hard as us..It is wise for us Millennials to help them GenZ's, and not bash them for their generational leap of \textbf{age}.The baby boomers and their media bashing campaign has taken its shape that most baby boomers themselves are very insecure about their differences compared to ours..\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/118 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}\small Same here.  I'm almost 35 and part of the millennial generation, but I feel more like a mix of Baby Boomer, Gen X \& Millennial because of my family upbringing (people often tell me that I have an \textbf{old} spirit).\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Im 29 and i in no way feel linked to millenialls i feel more x tbh i remember exactly where i was at 9/11 and i remember my first fone  also all these \textbf{crazy} younger ppl with blue or green or \textbf{r\textbf{ed}} hair ps:did u notice how it seems to be hyper colours that the use in everything from makeup hair clothes its not just \textbf{r\textbf{ed}} its highlighted neon red\normalsize   & \cellcolor{green!5}Crazy, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}7/70 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small That's because you're old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Kinda makes me mad when older people say it's rude to ask people's ages. So what if you're \textbf{old}? 44 years on this planet is pretty amazing, you survived for decades now. Just say ur \textbf{age} lol don't be shy\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Morph Verse I‘m a Gen Zer. I‘m currently 19 years \textbf{old}, and what my Generation is doing already isn't benefiting anyone. Our belief in a better world through i. eg. anti-racism, ecological achievement and femenism led us to being naive and believe the institutional frauds which now make up big problems in society. The Jesse Smollet incident, transathletes dominating over female athletes, the whole SJW escapades, rise of communism etc is linked to my Generation. This naivety has been paved by generations before us, starting from the 68‘ers, since then the spiral of naivety amongst young people went upwards. And because of it people lost the sense of realism, everything has to be achieved asap, and the results have to be flawless, even threats like global warming is not talked about enough, because people just believe everything immediately and start overreacting. With global warming i mean, that scientists decades ago preached that a new Ice \textbf{Age} is coming. No the opposite gets preached on News Channels which also spreads hoaxes about i. eg. Jussie Smollet incident and political conflicts like Donbas.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/181 & \cellcolor{green!27}1.105 \\  \hline
  \cellcolor{green!5}\small The years bracket for the term millennial doesn't make any sense. Millennials were not born in the 80s and 90s which is still the 20th century which is the \textbf{old} millennium. Millennials were people who were born in the first 20 years of the 21st century  (2000s-2010s)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small \@Alec T Or the term Millennial speaks for the people who mark the last newborns of the \textbf{old} millenia. It's misleading to a lot of peope, but scientists don't care about practicality of terms it seems.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@Lenny Cash You know better. Women don't tell their \textbf{age}. Somehow they don't think men can guess.ROTFLMAO\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@hoodmistress reloaded Actually you are Xeniall, not milleanial. Xenialls are those between gen X and milleanials, or \textbf{old} milleanials but not pure pure milleanials unless you were born after 1986.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@Morph Verse well \textbf{old} millenial you might mean, or we the Young milleanials have more in \textbf{common} with the Gen Z lol\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I was born in 1980 and growing up was referred to as being as generation x. It wasn't until recently that the debate about whether or not my gen is X or Y a.k.a millenial. But I fail to see how someone a year or two apart from me can bein a different generation. There has to be a few years in which people are part of a combined generation. There are some differences between my little sisters \textbf{age} group. She's 7 years younger than me. I think she is in that combined generation. I'd say combined generation is 3 to 5 years long.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/104 & \cellcolor{green!27}0.962 \\  \hline
  \cellcolor{green!5}\small \@Yah Gurl KaeKae but that would mean that Gen Z is even less than 12 years range which is way too little for a generational span. Generations usually run across aprox 16-20 years. You don't connect with under 13 because those are literally children right now whereas you're a teen or young adult, but it's still the same generational span. Like, When older millenials were your \textbf{age}, the younger millenials were children, and totally unrelateble to them, but still millenials. Get it? This is more of an \textbf{age} (childhood vs teenage/adulthood) than generation.  But in like ten years you'll see it very clearly how much it is the same generation, and also there just  isn't enough GENERATIONALLY  different between someone who's currently 18 and who's currently 10\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/127 & \cellcolor{green!5}1.575 \\  \hline
  \cellcolor{green!27}\small Wait, so I don't understand. If Gen Z kids are only from \textbf{age} 13, and if you're younger than 13 are you a Gen Z or a Gen Alpha?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small AJ - \textbf{Abbie} Jones cause they ain't doin the same stuff as the \textbf{old} ones did. Our millennial formed our economy  future we are living in today. They put in work\normalsize   & \cellcolor{green!5}Abbie, Old & \cellcolor{green!5}Age - Over 65s, Religious Identity - Jewish & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Born in 74 and raised by my grandparents, so i have alot more in \textbf{common} with the ww2 generation.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Which Generation built the Hoover Dam, Golden Gate Bridge, California Aqueduct, Brooklyn Bridge, Lincoln Tunnel, Manhattan Island, Panama and  Suez Canal and California INFRASTRUCTURE? Who designed, built and tested jets, airplanes and rockets WITHOUT COMPUTERS? Who built and captained submarines without computers? Who had the COURAGE to get into a space capsule and blast off into space and go to the moon? Who wrote, recorded and release entire albums (sometimes 3 in one year [The Beatles] etc) without computers or software to fake their 'talent'. Who directed and produced EPIC movies with THOUSAND AND THOUSANDS of extras, REAL explosions, and sometimes ACTUAL TRAIN WRECKS, in movies WITHOUT CGI??? Everyone should understand that we, today, stand on the shoulders of Giants to pat ourselves on the back....when others BEFORE us....(mostly white men, some of them....yes, even where NOT 'straight white men', but still were men) actually in, fact CREATED THE WORLD WE NOW ENJOY AND TAKE FOR GRANTED. FACT. Liberalism is a \textbf{MENTAL} DISEASE.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/163 & \cellcolor{green!5}0.613 \\  \hline
  \cellcolor{green!27}\small Born in January 95 and feeling very torn... i had a myspace....that i was addicted to... like i know jeffree star from this, not from Youtube. I went through emo and scene kid phases.... but i'm a gen z-er? aren't they people who grew up with snapchat??? Something I didn't have until I was 18 - an adult! something feels \textbf{weird}. I'm a hybrid!\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small Personally... there are older generations "technically" but i really don't distinguish any gap or seperation. Have More in \textbf{common} and have more friends there in general.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I always thought of myself as a War baby, born during WW2, when most fathers were overseas fighting. And except for becoming more consecutive, I have more in \textbf{common} with Boomers than my own generation. I for sure was not "Silent" I was involved with most of the "movements" the Boomers were involved in until they left me behind when they became more conservative.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small Im in the latest gen but my soul is like from the medieval age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Generation X is killing themselves at record rates.  In 20 years you will occasionally see an \textbf{old} person.  Look there is a Gen X! they are almost extinct!  lol, so what.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Same🤣How \textbf{old}?😎\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small If you are a Millennial born in the 90s, than you guys are all around the same \textbf{age}. You probably have more in \textbf{common}  with them than you have with older people in your generation.\normalsize   & \cellcolor{green!27}Age, Common & \cellcolor{green!27}Age - General, Social Class - Working class & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small I was born in '95. And I have \textbf{nothing} in \textbf{common} with 2000s babies. So I'd say I'm definitely Gen Y.\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small 96 and I have a little more in \textbf{common} with them but not much, but then again I don't have much in \textbf{common} with Gen Y\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Good, I have both daughters are generation Z too. Both are straight A's students since grammar school to present, all in advanced classes, do lots of sports, After school activities \& join the gym with me twice a week, do volunteer once a week on Sunday morning at the temple for 2 years But stop last year which was 2018. My younger daughter is a sophmore \& the older one is \textbf{senior} and getting scholarship to Northeastern University \& Umass of Boston. I'm hoping my younger daughter will get scholarships as well. You just need to be straight A's student \& take lots of advances classes, get really high SAT score (almost perfect), do volunteer works, do lots of productive activities, write really good essays \& be really active in school -- those are some of the qualities to get scholarships.  I raises them up well, great manners, helpful, loving, kind, friendly, giving \& positive.  I'm very hopeful that generation Z will do much better than Millennium \& other generations.  My daughters also learning programming \& coding at home besides all these school works \& activities.  As a mom I put all my heart \& mind into my kids, all my investments, earnings to my kids unlike the selfish baby boomer generation parents expected their children to give them all their pay checks \& or allowances while they know their children still owe college tuitions\& credit cards debt.  I'm a generation X.  Thank God/Buddha that I had my life plan out well even with all the obstacles I overcome everything years ago \& could be able to give my kids a great life since they were little kids.  I hope generation Y \& generation Z don't give up.  You guys have better technologies \& you're really smarts \& can do anything if you put your heart into it.  Good luck\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/310 & \cellcolor{green!5}0.323 \\  \hline
  \cellcolor{green!27}\small I've watched videos of older people in the 60's and 70's calling baby boomers lazy, dope smokers and so on. It has been disappointing to see many baby boomers fall in the trap and become the grumpy \textbf{old} people that bit\@\@ about the young people today. Generation Y depending on what years you go by could be anywhere from early 20's to late 30's. A 36 year \textbf{old} for example didn't grow up with Internet, probably didn't own a cell phone until their 20's and doesn't fit that negative stereotype of a millennial.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small GEN X was never talked about at all...boomers n millenials are somehow talked about like \textbf{crazy} i noticed they both glorify the hippy movement ...now i see boomers tryna act like \textbf{old} timers like they didnt act that way ..lol\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Michael Anderson You'll get your chance to be the grumpy \textbf{old} person. When it becomes cool to have the friar haircut, you can lecture your grandson about how we wore manbuns in my day.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small No gen Z and Millennials are \textbf{nothing} alike\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small TIMESTAMP DEFINITIONSThe five living generations 0:57The Traditionalist generation 1:49The Baby Boomers 2:30The "end" of the Boomers 3:24The Gen X 3:40The Gen Y 4:30The Gen Z 5:31What Millennials and Centennials have in \textbf{common} 6:35Critical definition of a Generation 6:46\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Buffalo Bry the latest born that i can say that you definitely have at least 1 thing in \textbf{common} is those born 1998...because of 9/11...1981 birthdays were the last to be turning/turned 20 in 2001...1998 birthdays are the earliest that you have vague memories of 9/11...memories ' COULD ' start as early as around \textbf{age} 3\normalsize   & \cellcolor{green!5}Age, Common & \cellcolor{green!5}Age - General, Social Class - Working class & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I actually think that the generation ends at 2007 because only afterwards did universal internet become \textbf{common} for young children. Before that, most Gen Z seem to share the same similarities as those born in late 1980s.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@Ann V. Actually if you look it up, depending on the source Millenials can be born until the year 2000 (since it's still part of the 20th century). Also, tapes and \textbf{old} technology weren't my interests, they were just the most modern technology that was popular in my country at that time.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small On the flip side, despite being born in 97, my parents were born in the mid-70s and I grew up in a decently liberal (labour if we use my native political parties of the uk), low-income, but more importantly very tech savvy household.And I too, despite being 4 and potentially being able to remember, don't have any memory of 9/11. However, I was on game consoles as early as 2 years \textbf{old} before I could even properly speak. However I was using the internet to look up game guides and/or cheats probably as early 7 yo in around 2004.It's interesting because my lil bro didn't take to tech anywhere near as much as I did, despite being born in 2001, however, my little sister born in 2016 has essentially been watching youtube since birth.Could well mean that my lil sis may fall lean into a Gen Omega if you were as a child who grew up with youtube since they were a baby, and touchwood me mum's expecting a 4th in July so it'll be interesting to see if they too go into this next generation.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/189 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small This comment makes me feel \textbf{old}. It weirds me out that people born in 2000 are 'adults' now.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Shabam TV cusp, since sources label those years as either millennial or gen z. I find it \textbf{weird} to say 2000 is millennial. To me, its not even cusp. I would say 1993-1999 is the cusp even though they are millennial years, since those years would have trouble remembering the 90s vividly. 1998 and 1999 would have trouble having even snippets of the 90s.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small The internet became really big for millennials in their teen years, which is like the absolute WORST time for something so life changing and complex to get big. We didn't know how to handle it, that's why we're considered such a messed up, \textbf{crazy} generation. Hopefully Gen Z can handle this stuff better than we did, but looking at the state of the internet right now I'm not so sure...\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small This must be an American thing because I'm 34 and no one i know has anything in \textbf{common} with millenials\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small If I had to choose when I'd be born I'd choose around 2036 or after 2050. lots of interesting things would be happening, and now If I'm still alive by this time (2050) I'll have +50 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small This video was made by a millenial who has been paid by the left leaning newspeak corporate media.  It has \textbf{zero} facts and posits that 'there is a lot of debate' with regards to every statement, thus ensuring it doesn't 'offend' anyone.  It conveniently espousing that technological advancement is synonym with 'social advancement' which is codified as 'left leaning' it carefully weaves positive terms like 'progress' 'sharing more' with and 'collaboration' of the recent generations while dismissing any criticism of the millenials as totally unfounded because the same criticisms can be applied to all generations.  Those criticisms, which are almost always related to work ethic and entitlement characterised by lack of appreciation are in fact self refuted in this video which qualifies hard work as a notable value in older generations due to tougher socio economic situations, war, banking collapses, austerity measures due to geo political tensions etc.Nice bit of propaganda. Try watching Daysofnoah channel or Jonathan Haidt videos, Simon Simek for a non politicised newspeak liberal agenda supporting version of generations.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/173 & \cellcolor{green!27}0.578 \\  \hline
  \cellcolor{green!5}\small I was born in 97 and consider myself a a Millennial but also completely understand why I'd be considered generation Z since I resonate with their experiences too!! I don't remember 9/11 but I feel like there's a cut off between late 90's kids and 2000's. Its little things like I remember having to go to the bookshelf and look up a word in the dictionary if I didn't know it. I remember blockbuster and DVRs/DVD's, I didn't get my first flip phone until middle school, I remember a life without technology where as Generation Z doesn't. My 13 year cousin had a completely different childhood than my 21 year \textbf{old} self.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small ItsSoAli born 1994, different experience as well, such as that remember when vhs was popular as well as MySpace and a time before Facebook and a time before YouTube and 9/11 and some memories before 9/11 and some memories before 2000, didn't enter school until the 00s...also...about 9/11, you don't remember it?...completely possible, however,  if you 1993-1998 that means that it is completely possible for you to remember 9/11 but also completely possible for you to not remember 9/11, (permanent memories ' MAY ' start as early as \textbf{age} 3)(mine start in 1997)\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small "some Traditionalists remember one or more World Wars" (photo of WW1 tank)...Erm. That war ended 100 years ago. Maybe there is a 110 year \textbf{old} somewhere who remembers the church bells ringing when the war ended as a 10 year \textbf{old}. But that would be it...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small i was born in 1995, so i guess im a millennial. but i dont think anywhere near them since i grew up watching adult stuff, \textbf{old} school south park and family guy and all that stuff in the early 2000s. thats what i like.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small The U.S. dollar has lost 97 percent of it's purchasing power because of the fed borrowing fiat(fake) money that is printed out of \textbf{thin} air. But lets all argue about who's lazy and point fingers at each other and label each other.. Seems like a good use of our time on this earth. Forget the IMF and the banks.. I'm sure they actually serve a real purpose.. Maybe no-one has figured it out yet\normalsize   & \cellcolor{green!5}Thin & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small I am 1987 and the babies of generation end at 1989. Gen x babies are 83-89. We can relate to those born in the late sixties. And those born in the early 90's because we are the \textbf{transition}.\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I was born in mid yr 76 . Im a gen Xer . But I do feel more in \textbf{common} with people 7 years younger than me than those who are 7 years older than me.  First president I remember was Reagan.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small It is about the \textbf{age} you come into adulthood not about when you are an infant.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small After Generation "Z", perhaps it can be called Generation "Now I know my \textbf{ABC}, why won't you come and sing with me"\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small No such as these "generations" everyone is different....some \textbf{old} \textbf{old} people act like 20 year olds...vice versa..\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Okoih Ooo i vividly remember being 4 years \textbf{old}, when i got my first dog. I wanted a dog so bad, definitely is my favorite childhood memory. Im not sure if I remember details before then..I have a lot of memories but don't remember how \textbf{old} I was during them.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small memories that will last the rest of ones life can start in that \textbf{age} range*\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Killer Pineaple even then in the 90s baby boomers participated in the gulf war. History repeats itself my friend soon in the future maybe when millenials are the next boomers (not litterally but the same \textbf{age} as boomers as present date) they might even be poking fun at someone\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small you sound \textbf{old} and wise....remember BEN 10? kids nowadays will never know smh\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Yeah I remember Ben 10, I used to watch it when I was 6 or 7 years \textbf{old}, it used to be my favorite cartoon, I liked the Humongasaur the best,  but back to the topic, it's very mind blowing as to how quick things have changed.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Of course you are millennial you were born in late 80s. Common\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Am I the only 11 year \textbf{old} who is part of the gen x community?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I was born in November 79, I guess im a millennial... i don't identify as a millennial. My oldest son is generation Z. Not sure what my 6 yr \textbf{old} is...🤔\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small i was born in 1998, and here is my perspective on gen z, with which i identify (even though i can remember life before the ipod was invented haha). gen z is faster at adapting to new technology bc they've never known life without it, including being extremely attuned to internet-specific humor. gen z also has concentration problems due to this technology and the diagnoses of disorders such as ADHD are higher than ever. additionally, gen z is very adaptable to change bc of how fast the \textbf{age} of information is progressing. they are extremely cynical due to the ever-increasing crises in the world (e.g., conflict in the Middle East, global warming, U.S. mass shootings), and they tend to view things through a lens of irony, casual pessimism, and dark humor. these are just a few things that i've noticed being part of this generation.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/145 & \cellcolor{green!5}0.69 \\  \hline
  \cellcolor{green!27}\small I was born in 2000. I really don't identify with the older mellenials or the younger generation Z's. It's a very \textbf{weird} \textbf{transition} time between the two\normalsize   & \cellcolor{green!27}Transition, Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Gen Z is not 1996 to 2010. It started at the turn of the generation. Generations are 20 years unless something happens that will either prolong the next generation or shorten that generation time span. Gen Z starts at the year 2000, the turn of the century, not in the middle of the 90's. So it's from 2000-2020. Your a Gen Z because the year is 2019 and your \textbf{age} is less than that. But you know what, no one cares what generation you are except for \textbf{old} baggy people or desperate people who want to blame the declining economy and recession on Millenials and Gen Z.If someone says you're a bad person or lazy just because you're a part of a certain generation, just tell them that at least your generation didn't cause a social/political civil war among the parties o the USA, or something else that they cause wherever you may live. I'm just assuming you're American due to the \textbf{age} you stated and the fact you're on YouTube with supposedly fluent English (minus a few spelling and grammatical errors).\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/183 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small What a trash video. \textbf{Age} is a number. If you have ever worked closely with your coworkers, you all share the same experiance. Generational divides are meaningless. I look at individual merit and their strengths above all else.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I was born in 1995 so hypothetically I should be a millenial, but I actually don't understand the "fast fashion" and similar ideas of wasting the energy to \textbf{nothing}. So all of these theories aren't so universal as seams to be, because everyone's different and the idea to put all humanity in "marked boxes" is unlogical and kind of destructive for the identity of flexible society. But it's only my opinion.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Born in 89, I remember the day Kurt Cobain died, I remember the article "Generation X: the Lost Generation," I remember when you called your friend it was on a land-line \& if they didn't answer you were fine with that unknown (unless it was a girl you liked), and the impulsivity \& instant gratification \& phone addiction of my gf born in 97 makes me a crotchety curmudgeon. I fear for my 13 week unborn child's Future. I am Gen X. Convince me I'm not,  the cutoff should be "where where you when   died." Cobain is Gen X. Then Lenon, JFK, MLK, and so on. 2001 is the new >millenium< \& millennials should remember but maybe not have as deep of an impact as older Gens. And centurions should be those born after 2000. But my opinion doesn't matter. Cuz after Gen X you get the trolling for sport. In my day it was "flaming." So bring on the N-word \& calling me a \textbf{fag}. Oh wait,  that was OK in my day bc it meant an inconsiderate jackass. Who knows what I'll be called instead.  Anti-trill? No,  Cuz I'm from Texas so trill by default....  I'll find out soon enuf ig\normalsize   & \cellcolor{green!27}Fag & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/204 & \cellcolor{green!27}0.49 \\  \hline
  \cellcolor{green!5}\small I was born in 1985 I have more in \textbf{common} with Gen x\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Ray - \textbf{Nobody} Important that's why you just get unlimited DUH\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Ray - \textbf{Nobody} Important na I hear ya bro haha thats why I got unlimited data haha gotta pay bills haha can't afford worrying about going over my data\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I would say a bathroom is Way more important than WiFi. Biological need is more important than WiFi. Of course, millenials are more prone to ask Siri or Google.  I was born in 1980. Apparently,  my generation is millennial b/c I don't know anything of the 60's \& 70's but remember watching Disney \& \textbf{old} shows like Nick at nite. Nickelodeon. I remember shows of late 80's - early 90's\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Riding the NEW \textbf{AGE} wave with you, bro!!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small im 22 year \textbf{old} baby boomer because i was raised right.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small My grandparents are the Silent Generation, my parents Baby Boomers, me a Millennial (of the older variety), and my nephews are Gen Z/Alpha. The end of the video is interesting - my generation and that of my nephews do have a lot in \textbf{common}. We both played video games, had computers, and had the internet. Granted, I didn't have social media, YouTube, and iPads as a kid...but both generations are tech savvy.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small I actually think that the boundary is for those born after 2007 when the internet became almost universally everywhere - these people will grow up with the internet from birth. For people before that \textbf{age}, the internet was a luxury until their teen years.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I know exactly what you mean. This is how it goes from my experience. I'm born in 1987. Boomers = 1945-1965Gen x = 66-89After that I don't know. But my point is that each generation has oldest, middle, and baby. I find my situation funny because I can relate to those 10-15 years older and 10-15 years younger because I grew up watching what the older x's watched but also shared the same entertainment as those younger because I was the \textbf{transition} period.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small And I also really think it just depends on the person. I relate completely relate to memes. That's like the best part of my day is just being on twitter and everyone posting and sharing memes. It's so funny. So I'd say that I am more Gen Z (born 1996). I don't have the same "defining moments " that they usually classify Millennials as having. My first phone was an Iphone, we had Internet and \textbf{Apple} computers in my Kindergarten classrooms, my first election was Trump/Clinton etc. So we're like a \textbf{weird} time. I think for those in the 95-00 years we should just chose ourselves which we want to be in\normalsize   & \cellcolor{green!27}Apple, Weird & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small I'm gen X (born 1976) and find myself relating best to the oldest generation, people in their 70's and 80's, but also quite well with the young people who are around college \textbf{age} now.  Everyone plus or minus about 20-25 years of myself pretty much sucks, lol.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Yay we that same \textbf{age} may 96 :)\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small 93 here so I'm 2 years from being gen Z. I have more in \textbf{common} with Z than I do with \textbf{old} millennials, like those born in the 70s \& 80s. Imo millennials are a split generation, as the latter half of it experienced much more digitalization and therefore grew up in a very different world than the first half.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@Karen Hajj 😂😂😂 really bruh? Just that name is an insult because people use it to degrade people for being young. Plus I'm Litterally closer in \textbf{age} to most core Gen Z members 2001-2008, than core Millienials 1985-1992 and relate more with Gen Z than they stereotypical Millienials. Tho both have good and bad Triats\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Im that way with older gen. Im a millenial 90' and kix it with gen x. Call me \textbf{old} school. We grew up outside fighting  👊 too see who was toughest not online. But I do have the know how too handle up on the.interweb lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Born 95 I have more in \textbf{common} with my 2 younger sisters 98 and 02 than my older brother 91\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@Xristos N. here are my citations: Yarvin, Jessica (15 February 2019). "The game for 2020 Democrats: wooing millennials". PBS. Retrieved 13 March 2019.Picchi, Aimee (1 February 2019). "How marriage became a status symbol for millennials". CBS. Retrieved 13 March 2019."Would you take a pay cut to work at an environmentally responsible company?". \textbf{ABC} Australia. 15 February 2019. Retrieved 13 March 2019.Van Dam, Andrew (16 March 2019). "Millennials really are special, data show". The Washington Post. Archived from the original on 17 March 2019. Retrieved 17 March 2019.Boylan, Dan (14 March 2019). "Census Bureau's first-ever online headcount designed to reach millennials likely to miss mark". The Washington Times. Retrieved 17 March 2019.Jarvie, Jenny (3 April 2018). "Parkland highlights political potential of millennials. The question now is if they'll vote". The Los Angeles Times. Retrieved 13 March 2019\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}\small 19(99) I feel like I'm definitely different from others my \textbf{age} I like technology but I'm not necessarily attached to it I can go a month without a phone and not care my only use for a phone is contact when neccessary other than that I'm to busy for social media.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small \@Cutie Cabello I have a niece your \textbf{age} from my oldest suster, your gen is cool bro\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Cutie Cabello its normal, \textbf{Old} people say shis about young people, boomers disliked gen X too, they were hippies and stuff\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Leon sky I just don't get the \textbf{common} theme of making fun of young generations I don't get it\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small 1997 and my childhood related more to people born in the late 80s than to people born in the early 2000s. \textbf{Weird}. So i am gen y both from my year of birth and from my childhood experiences\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small NoodleEdd TV i consider myself as a young millennial, not an \textbf{old} Gen Z, since I was born in 1997, and i can only relate myself to people born from 1991-1999. 1990 and before i can only relate a little, 2000-present, I cannot relate in anyway. So Yz cusp.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small sabrina berriez   I agree with you I'm a older gen z born in 1995 and I relate mostly with other 90s babies. Got little in \textbf{common} with anyone born in 80s or late 70s.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Michael Filla Y/Z border is 95 to 98, they can have traits of both generations, or have \textbf{nothing} in \textbf{common} with either\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I would say that those born in those years could more closely resemble millenials or gen x based on rural/urban lines. Those in urban areas would have gotten internet, cell phones, and other technology earlier, therefore having more in \textbf{common} with millenials. On the other hand, those in more rural areas may not have had internet or even cell towers for up to 10 years later, and thus have more in \textbf{common} with older members of Gen X.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Traits have \textbf{nothing} to do with your generation. It only matters what year you were born. If you were born before 2000, you aren't generation Z*\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I was born in 1982 and it's an awkward time because I feel more X than Millennial.  Some literature says the Millennials began in 1986, but others say 1983, 1981. All I know is that I grew up with Grunge music, little to no internet, and by the time I was 19 years \textbf{old} I sent my first text to someone else's  phone and thought it was amazing.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small I was born in 78: I can relate better with people who are 10 or 15 years younger (commonality of interests and actual - not past - experiences) than with ones who are even only 4-5 years older: the same is true for many people of my \textbf{age}. I think it's all a matter of lifestyle, habits, experiences and personal attitude rather than a simple time barrier. Also, my true formation and the very first life-changing experiences came in the 90s, not in the 80s.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small \@mm 12 actually the birth control pill first came out in 1960. No sources refer to someone born in 1965 as a baby boomer. Baby boomers came of \textbf{age} in the 60s and 70s. Someone born in 1965 came of \textbf{age} in the early-mid 80s.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small I guess I fit within that time range as I was born in 1984, but I have some \textbf{old} school ways about me (I was raised around multiple generations of my family when I was a kid).  I definitely remember the \textbf{Apple} IIe computers and floppy disks from back in the day (every Thursday in the computer lab during elementary school).  And yes, I loved The Oregon Trail.  The closest thing we had to a mobile device back then was either a Game Boy or those Tiger handheld games.  I didn't have my first computer until I was 14 going on 15 as I was still using a typewriter/word processor to write papers, and I didn't start using the internet until my \textbf{senior} year in high school.  I was 18 when I got my first cellphone, though I still prefer a landline even now.  I ditched cassette tapes for CDs and mp3s because there's a chance the tape may mess up and I lose some good music, but I still rock with my VCR and my classic video games.\normalsize   & \cellcolor{green!5}Apple, Old, Senior & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}3/179 & \cellcolor{green!5}1.676 \\  \hline
  \cellcolor{green!27}\small Boomers are often just as  narcissistic, lazy, entitled and impulsive if not more. Their parents lived through the Great Depression and war and spoiled them as kids. Then, they benefited from a great economy. It has \textbf{nothing} to do with do with technologies.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small PC master \textbf{race}?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small you remember 9/11 when you 4 yrs \textbf{old}? ...your cute by the way\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Clarissa Garcia yea \textbf{hun} which boro are you from ?\normalsize   & \cellcolor{green!5}Hun & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{old} grandpa mos thats like saying every computer in the 90s is the same as a computer in the 2000s...every cell phone in the 90s is the same as the 2000s...times are different...10 yrs difference is a big time...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Yeah but you weren't \textbf{old} enough to care.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I agree. I think of millennials as being the first generation to grow up with a computer in the home. I was born in 77 and didn't have my own computer until I was like 20, although we had ONE in the career lab at my elementary school that we played Oregon Trail on (DOS), and my friend's parents had one at their house around that time but didn't exactly invite me to use it. I didn't play Atari until I was like 7, and that was at someone else's house lol Carried a beeper from about \textbf{age} 16-19 and probably didn't get a cell phone until I was like 22 and it was NOT a smart phone.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small The term Millennials are used for coming of \textbf{age} in the new Millennial.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Look at the comments of people being proud of something as coincidental as the time period they were born in like it's something worthy enough to define them. This type of group think creates the toxic striations between people, much like distinguishing each other by \textbf{race}, despite things like that being arbitrary and fundamentally meaningless in the end\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small 1987 here 😎  I grew up in the 90s. Good \textbf{old} times!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I'm also turning 23 next month, and it's \textbf{weird} that I'd be classed as a different generation to my boyfriend, born in 1994, when we grew up with the exact same experiences. Strange.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small A \textbf{freak} of nature indeed.\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Hello \textbf{old} millenial, i'm a young millenial 94 😃\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I'm 1987. The babies of gen x and the \textbf{transition} into the next generation. You are the middle child of the generation.I see it in my family. I have relatives born all over generation and there are nuances between the oldest middle and youngest in the generation.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Laurelindo I'm 5 years older than you and I didn't even have that. I never had internet until I was an adult and it wasn't really usable until much later. The \textbf{old} dialup modems took awhile to load up a single webpage. It was 2004 before I had internet as we think of it now.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Millineal here, completely right leaning. This vid is a bit off on facts. I get the narrator wants to float people based on views to accommodate their belief, but generations are fixed. Otherwise statistics would be based on belief, not \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I don't even care to watch this video, 'cause 38 years \textbf{old} are NOT millennials. That's Gen X. Get your facts straight first.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Nothing wrong by being millenial...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small The oldest current millennials are about 39 years \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small stryderzer0 the fuck,I'm not a god \textbf{dame} generation z\normalsize   & \cellcolor{green!5}Dame & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I was born in 2005, but I don't relate to a lot of ppl my \textbf{age}, most of all the music they listen to, and I grew up using  a Gameboy and a Walkman and when u see the videos now of ppl my \textbf{age} trying to figure out how to use tapes, it's just sad tbh, and I kinda relate to older gen z's tv shows and stuff but not much of them either so I'm a bit of a mix 😂Edit: and a lot of ppl my \textbf{age} are literally addicted to their phones even when we're outside socialising, and they literally have a heart attack when there's no available WiFi 🙄\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/115 & \cellcolor{green!27}2.609 \\  \hline
  \cellcolor{green!5}\small I think people who were born between 2000 - 2005 are in between the Gen Z and the millenials. Tbh, I was never really involved with Technology when I was a kid. I'm an '03 kid. I had my first phone at 7th grade, so no, I'm not one of those kids that has phones and gadgets since they were literal babies 😂. It really affects their personality. They become dependant of technology. Heck, my brother('07 kid) doesn't even know how to spend a day without his phone/play station/TV. I remember playing outside with my neighbors, but not my brother.Also, I think the kids born between 2010 - 2018 should belong in a new category. They're the ones that were literally born with touch-screen phones and VR headsets. They're born in the world of social medias, tech, influencers, etc. I keep seeing 2nd graders posing for pics, and the poses weren't really appropriate for a 7 yr \textbf{old}. Tik Tok really made a difference.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/165 & \cellcolor{green!5}0.606 \\  \hline
  \cellcolor{green!27}\small Only \textbf{old} \textbf{racist} ppl like trump\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small 1950s? Segregation, rampant \textbf{racism}, etc? Definitely a magical time.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I personally think that Generation Z starts with 1995, but I know a lot of people born in 1999 who still think they are Millennials, which, in my opinion, is not the case. Like all generations, there are certain events that will take a toll on a generation and influence their personalities and how they act. I think the main ones for Gen Z (ignoring the technology aspect because that's all everyone talks about) are growing up in the aftermath of 9/11 and the 2008 recession. I think a lot of people tend to think of Gen Z as current elementary and middle school aged children, but this is not the case. Most Gen Z'ers are actually graduated from college and high school or still in high school currently (I also believe Gen Z stops at 2010).Those born in the late 90s and early 2000s, often referred to as those born on the "cusp" of generations, have a lot of similarities to each other, so I think they deserve to be grouped in the same generation. With regards to the US, I don't think most people born in 1995 have an accurate memory of exactly what they were doing on September 11 because, quite frankly, they were only 5-6 years \textbf{old} and likely weren't told the news when it happened because they were children. Of course, this all depends on physical proximity to the attacks. A 6 year \textbf{old} who lived in NYC and possibly lost their parents, family friends, or many classmates lost parents in the attack is much more likely to remember the day itself. Also, none of Generation Z was in the workforce when the 2008 recession hit. Most can't even remember it (myself included). The oldest in the generation would have been 13, and while they may have had some money to spend, they certainly weren't faced with a personal economic crisis and worry about their jobs and futures. Of course, their families likely went through this, so I believe this has shaped Generation Z to be a more realistic generation, especially with their money. We saw the aftermath of the recession, so I think most Gen Z'ers today are more practical with their future career choices, opting for a job that will pay well and will always be in high demand over a job in entertainment. I also think Gen Z is currently seeing Millennials with piles of student debt, so many of us want to find alternatives to college that will be the best for our future careers. Gen Z will "settle" for a college that maybe isn't as good as another simply to save money. I also think that, if you're talking about technology, Gen Z'ers born from the late 90s to the early 2000s have MUCH more in \textbf{common} than those who are born in the late 2000s, and would possibly even call for a reclassification of Gen Z to just span from 1995-2005. This may seem short for a generation (since they are usually around 20 years long), but I think with technology changing so rapidly, the spans of generations are getting shorter. Information is being accessed much quicker now, and things change much faster.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/535 & \cellcolor{green!27}0.561 \\  \hline
  \cellcolor{green!5}\small Generation \textbf{Alien}. ....1978\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small +Kelsea CooperMillennials are pretty much people who were \textbf{old} enough to be vividly aware of the turn of the millennium, but also young enough to not be out of their teens.A usual time span for millennials tends to be 1980-1995.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small I was 3 and watching Barney when 9/11 happened, I was upset they changed the channel to the news. I made a MySpace when I was 11 but never really used it. I made a Facebook next year when I was twelve. The only show of those I remember watching is rugrats. I got a cell phone at the \textbf{age} of 13, it was a slider. My father is a baby boomer and my mom gen x. I was born in sept. 1997, am I a millennial?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small Ali-Marie Ingram ha ha 90s babies have \textbf{nothing} in \textbf{common} with Xers\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small My parents are baby bomers and I was born in 2004 so my experience is much different that of a kid my \textbf{age} with parents 20 years younger.    What generation would you categorize me in?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small I'm glad we created an awesome type of humor... too bad not everyone gets it, but it is so much better than the \textbf{old} overused themes...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I was born in 1999... but sometimes I have the feeling I was born in the 80s and its the same with my girlfriend... we think that because we dont use  facebook twitter and instagram or other social media (we also speak a lot in real life rather then chats)  and we hang a lot outside and we like to listen to older music with an \textbf{old} walkman or \textbf{old} ipod😂\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small Sarah Hobbes here \textbf{age} 13\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Vote Republican otherwise they'll \textbf{lump} you in the same category as millennials\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Born in 1979 , I feel  too \textbf{old} to be a millennial,  yet  too young to be gen xer. Where is my generation  ?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small 77-83 babies have gotten the Xennials nickname because we're pretty much the last \textbf{age} group that grew up without Internet, kids or teens owning cell phones and so on.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small So there are no other races of people in the world? I liked this video but I dislike the lack of diversity and the fact that it appears that white people are the only \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I'm 1996 but I'm more of a traditionalist, not the Gen but a traditionalist in general, I'm very conservative for someone my age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small (To be honest) I am 21 years \textbf{old}... I have always felt older like 24 - 32....I even like talking to people older then me.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small 96 and 97 should not be included in Gen Z . We are millennials. We watched Degrassi, Zenon, Lizzie McGuire and we saw the \textbf{colored} ketchup and 9/11.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I disagree, I'm very conservative born in 96, and I never heard of Zenon or the \textbf{colored} ketchup b4\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small many older parts of generations feel like that but that doesn't mean they are not part of that generation, because if we keep on changing the \textbf{age} bracket of generations because the older ones relate more to the older generation then the new oldest of the generation, for example from what your saying the new oldest would be 1998 and part of those born in 98 will feel like they are part of GenY because they relate to them more and so it will change again\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small The real reason Gen X is more likely to be restrictive with their kids devices is because we grew up during the Wild West of the internet. There was literally \textbf{nothing} you wouldn't see on the internet during that time, before sites were shut down and the internet became more regulated. We were the cynical kids with no supervision during the time when culture was much more hardcore. That's the real reason Gen X is more restrictive with their kids devices, because they've seen just how messed up people can be.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small well what \textbf{age} considered adulthood? at 19 your still a teen, you said 18 becuase thats the legal adult \textbf{age} in your country, but not in all countries 18 is the legal adult \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small Gen z iPhone z Car z \textbf{Gender} Z Toilet Z Family Z And most important dragon Ball Z Lol\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small There are people saying that 2000 is not from the 20st century but from the 21st century \textbf{witch} one is right btw I was born in 2000\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@Zeke the \textbf{freak} how??\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Dedas Almeida the year 2000 is the end of the 20th century. 2001 starts the 21st. Remember guys, there was no year zero\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small We count from 1 to 10, not from 0 (\textbf{zero}) to 9. The final year of the 20th century was the year 2000. Your 20s decade starts on your 21st birthday.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I'd rather judge people on their morals and how they act, instead of what year they were born in. I'm a centennial, and I could be a spoiled \textbf{brat}, but I'm not. I know some people from generations Y and Z, they could be selfless, grateful people, but they're not. I think every person could stand to look at themselves closely and improve everyday.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small I was born in 2000 so I'm too young to be a millennial and too \textbf{old} to be a gen z\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small A positive comment about millennials? Wow this is crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small what is so \textbf{crazy} about feeling positive about Millenials? I know that you probably have had some type of positive experience with them! We need not lock ourselves into thinking what other people tell us to think. Expect the BEST and you will see it!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small I sincerely appreciate your positive words and wise advice. While I do believe in self-sacrifice, the importance of choice and responsibility, and serving the \textbf{common} good, I fear many of my peers do not. From my observations, many of them seek a life of hedonistic pleasure rather than true purpose and meaning. Perhaps there is always that group in every generation, or perhaps this is a new consequence of modern society. Either way, only time will tell if my generation will rise to face the challenges that represent themselves or cower to a place of comfort and security. I will certainly play my part in making a better future. I cannot speak for the rest, however. On another note, while positive thinking is a very useful tool, it must be balanced by skepticism and critical analysis, less one desires to be a target of deception and manipulation. "Speak of the good, notice the bad" is a personal motto I feel works well for most day-to-day situations.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/166 & \cellcolor{green!5}0.602 \\  \hline
  \cellcolor{green!27}\small riffle queen I think the person was just saying that it's rare to see nice comments about millennials. I feel like millennials and generation z should hold the same values as baby boomers if their parents taught those values to them. I know I have them as a millennial and I know a lot of my friends do too. However based on the video it seems like trying to do right for your family caused a mess. We see this starting with Gen X from the video, it seems like with each generation we rely more on technology. There's \textbf{nothing} wrong with technology, but there needs to be a limit.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small Yh cos \textbf{nothing} says intelligence than 70+ genders\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Technology use has to be limited more, it's making society autistic, now people look at you in a \textbf{weird} way if you say hello to them, there needs to be an authoritarian solution to it, the social world is becoming too messed up because of it\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@Yoy Toy typical millennial response, you and the baby boomers are both America's biggest disappointment, \textbf{nothing} but a generation of left wing trash\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@General Leopold Horchigli come to think of it though I don't care about your opinion either. What is it you said again. Oh yeah we can all be tributes in the Hunger Games..... Yeah your comment was full of class dude. \textbf{Nothing} but discriminatory ignorance.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Welcome to the internet \textbf{old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small RIGHT ON! TOO MANY LABELS! This is \textbf{ageism} against trans generationism and ESPECIALLY geared against older folk by younger people. I am sometimes ASHAMED of being a Centennial myself, by the conduct of many of my peers!\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Well growing up with technology its easy for.anyone sooo thats doesnt make them useful. Well us I should say... Idk many guys around my \textbf{age} that are men..(28 byw) not in the middle class...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Depends what study you look at. For generation x some say it ended in 80, others 81 or 82. Others say 79 and ive even seen 84. I was taught in school that gen x ended with ppl born in 80 like me. Ive always had more in \textbf{common} with n got along with gen x ppl more than gen y.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small whens ur birthday, u are almost 30 nowi just turned 30i wonder about the median \textbf{age} of milenials,\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small No you're the baby of generation x. I'm 1987. We are the babies and \textbf{transition} into the next generation. Like don't you find how you can relate to those born in the late 1960's and those born in 1995 lol\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@tipsy09 um, are you trolling? to me 60's are almost parents generation, I do relate to them.. in the same way I can relate to any person regardless \textbf{age} but it's \textbf{weird} and kinda silly to think i would relate to them more on a generational level than someone from 90'sMost of my friends are in the 1985-1994 bracket\normalsize   & \cellcolor{green!5}Age, Weird & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@tipsy09 but you're factually wrong, Gen Y officially begins in the early 80s, usually they say 80-8389 is definitely considered Gen Y , it's right at the middle of it, since Gen Y is considered to end around 199565 and 89 are a world apart, the latter have more in \textbf{common} with early 90's kids, it's simple math, dude\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small People born in the early 80's. Are closer to 65-79 than millennials. Mid to late eighties is like a \textbf{transition} generation.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Fermented Sourdough That's a pretty big gap though. I mean I don't really have much connection with the 80s or even the 90s for that matter. The late 90s is a \textbf{weird} grey area.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Round the \textbf{age} ranges to the decade it makes life easier. About every twenty years starts a new generation according to the video. Also the labels of generations is a guess. For instance, people born to the same parents but at different times are still considered the same generation according to a scientific perspective. Siblings born 10 to 15 years apart from the same parents are still the same generation. Much of their life experiences would be similar but a little different. One, say a person raised in the late 90s, would remember the turn of the century, 9-11 and the end of the hip-hop rap era. Mean while a person raised in the early 2000s would remember Harry Potter, Lord of the Rings, Justin Beiber and the Obama election.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/130 & \cellcolor{green!5}0.769 \\  \hline
  \cellcolor{green!27}\small A lot of Gen X and Baby Boomers insult the millennial generation when actually we had more in \textbf{common} than they give us credit for. They say we grew up attached to screens, but we really didn't. Only the super spoiled or super rich millennials maybe. I played outside and rode bikes when I was a kid, none of my friends had computers or cell phones, tablets didn't exist yet, Netflix didn't exist yet. iPods were brand new and technology like that wasn't considered suitable for kids by our parents. I listened to cassette tapes and CDs on my walkman. Watched VHS and later on DVD. Used a landline phone that was attached to the wall with a twisty cord. That was technology in my childhood. Things started to change when I was in middle school. I got my first video game system, we got our first family computer which I had very limited access to, it ran on our phone line so we couldn't be online very long bc my parents didn't want to miss important phone calls. 😂 A few of the lucky kids got a cell phone, but I didn't. Flash forward to my 10th and 11th grade high school years and this is when things start to change rapidly again. I get my first cell phone which was a flip phone that only does calls and text lol, we get wifi, I get my first iPod the iPod Nano, we get cordless house phones which were so cool and new to me, then we suddenly have video game systems with cordless controllers, and then Netflix. When I'm in 12th grade I get my first laptop. I don't get my first smartphone until I was in college and bought it myself and again I didn't have a tablet until a few years later when I bought it myself. But all this new technology came around when Millenials were in their late teens or early adulthood. I am towards the very end of the millennial generation. Now we have all these smart devices and bluetooth too which I've only jumped on within the past year or so. But this stuff didn't exist when I was a child or my family just didn't have it. I remember my parent's first DVD player they ever bought and remember thinking that was such cool technology at the time, no more rewinding tapes 😂 We had a huge collection of DVDs and CDs even when I was in high school. Now we just stream everything. My high school years were probably very different from past generations, but my actual first 14 years of childhood were not really that different compared to generations before me.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/452 & \cellcolor{green!27}0.221 \\  \hline
  \cellcolor{green!5}\small Eric B, wow. I've never heard anyone claim Clerks is a millennial movie. Totally disagree since it has \textbf{nothing} in \textbf{common} with millennial woes, but interesting opinion nonetheless.\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@daimon7 I'm all 3. I'm 1973 is why, so I saw Breakfast Club first time at \textbf{age} 14 with my older peers and Clerks \textbf{age} 27 first time. I'm both how amazing. Just saw Clerks on DVD again last week and I love Molly Ringwald!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small In this video they focus on Americans... is there any such thing as a video in English with statistics where the people surveyed aren't American?! It's always Americans. Try find a video with stats not about Americans without specifying \textbf{nationality}!\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small hackman669 oh yeah. she has seen everything.  Her mother in law was born in 1886 so she knew someone personally who lived before electricity existed and has seen robots and heard about cloning. unreal I can't imagine what I'll see if I live to be that \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Only the men were considered the greatest generation, she's part of the housewife generation, Sigh women were so much better back then, they didn't call men \textbf{pigs} and didn't \textbf{freak} out if you said hello or miss, like feminist do, feminism has ruined everything\normalsize   & \cellcolor{green!5}Freak, PIGS & \cellcolor{green!5}Nationality - Southern European, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I would say anybody from 1960 and behind live by tech. But those before 1960 are \textbf{old} fastion6 just my opinion.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Z don't exist millenials would rather be called 86eans \textbf{old} people try to make the rules with half knowledge again\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Sitting here lieing to your face again gen X \textbf{SLANT} about the computers Truth makes things run smoothly Fool\normalsize   & \cellcolor{green!27}Slant & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Born in 87 but lived through the 90's, \textbf{dot} com, and housing crisis. So 3 stock market crisis's. My advice for future generations is don't take out a college loan and invest in quality mutual funds and stay debt free and always keep studying through books and other sources.\normalsize   & \cellcolor{green!5}Dot & \cellcolor{green!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Lap TV on the news I'd heard they use this \textbf{age} range for millennials so that's why I thought I was one\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small So am I the only millennial who didn't own or have a cellphone or computer until the \textbf{age} of 21\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small What about kids that they are 5 years \textbf{old}???? What generation??\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small 1984, so I can be called millennial, despite having \textbf{nothing} at all in \textbf{common} with typical stereotype. nice. before Family Guy episode I've never even heard this word 'millennial'\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Being born in a third world country, I share a lot of my experiences with the previous generation.  Kinda cool and sucks, because it's a lot harder to relate to my peers of the same \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small what defines your generation is what you have in \textbf{common} for example someone born in 1994 or 1995 may have more in \textbf{common} with Gen Z than Millennials whereas someone born in 1984 or 1989 may have more in \textbf{common} with Millennials like them, they said Late Baby Boomers tend to have more in \textbf{common} with Gen X,  I believe the Generation that is born closer to the next Generation will have more in \textbf{common} with the next one, than the one it already is\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}5/85 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Babyboomers are the worst thing that ever happened to America, and the only thing causing moral collapse of it is the surge of right wing \textbf{nationalism} in the newest generation. Being a normal human being is today's version of 'counter culture'. You can't change my mind.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small The generational lines are about collective experiences. I am a Millennial born to a Boomer, raised practically by a Traditionalist. I guess, I am a bit of an \textbf{old} soul. I do think Millennials do get unfairly labeled and other groups more so than others, out of fear, ignorance, and arrogance. I also believe Generation X to Centinals or Z. Need to teach Y and Z, to have back ups. Just in case, something did happen. So they are not on technology as much. Just being sensible and reasonable.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small mzzcece don't be silly. You are an older millennial. Older millennials are \textbf{nothing} like the younger millennials. Older millennials are as good as young gen x and the highly  capable ones are even better than any group out of any generation that had existed. Older millennials are the perfect hybrid of the \textbf{old} world and the new world.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Ms H !  Even by culture you are a millennial a 90s kids/teen. You have \textbf{nothing} in \textbf{common} with the older gen xers and therefore you can't ever be considered a true gen  x. Also younger Gen xers are hybrids that have more in \textbf{common} with \textbf{elder} millennials because we both shared the same culture growing up. We both love the mid 80s and the 90s more than any Era.\normalsize   & \cellcolor{green!5}Common, Elder, Nothing & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Social Class - Working class & \cellcolor{green!5}4/70 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small \@lnyc2057You say this as if  I don't know MY own \textbf{age} and MY generation 😑.  You're obviously one of those people that know everything about \textbf{nothing}. I'm a proud Gen Xer.. and always have been since the term was first introduced lol. Thx for your opinion though 😎\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small mzzcece you need to learn to read and comprehend. You can't change reality. You are a \textbf{elder} millennial like me. I was born in 1980 and that is what we are. You are a fool if you think you are something else\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Ms H ! I was latchkey since \textbf{age} 9 and job since \textbf{age} 14. I am 1973.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small \@Alex Wilson I saw the same source, I agreed with it as well but after doing some research on that matter,  the time bracket of 1981-1996 being Millienials with 81-82 have Gen X Traits, 81-84 beimg the Early members, 85-92 being the core Members, 93-96 being the Late Members and 95-96 being in the cusp having Gen Z Triats makes more sense since those born in 95 and 96 would of been  3-4 in 1999 making them the youngest to remember 20th century, would of been 5-6 and most of them in Kindergarten and 1st grade when 9/11 happened which was a very important event for Gen Y would of been too young experience Core Millenial culture 2003-2008 but will be too \textbf{old} to experience Core Gen Z culture 2021-202795 and 96 would of been out school way before the 2016 Election and could of or did Vote for Trump who is seen as the First Gen Z President while all Core  members of Gen Z couldn't vote and were all still in Grade-High School.Gen Z being 1997-2012 with 97 and 98 being on tge same cusp as 95 amd 96 having Millenial traits with 97-00 being Early Gen Z members, 01-08 being the Core Members of Gen Z and 09-12 being the Late Members of Gen Z with and 2011 and 12 having Gen Alpha Traits seems to make more sense than just starting it at 2010. since they would of been born on the Edge of both the 20th and 21st Century, half of them born post Web 2.0, would grow up in a very paranoid divide world where everyone is on Edge of each other and most of them would only remember Obama as President and they all would of been \textbf{old} enough to see Trump in office. By the 2020's who knows they might change it since the Core members if Gen Z/Edge will be older but the 1995-2009 is also a very good timespan aswell\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/332 & \cellcolor{green!5}0.602 \\  \hline
  \cellcolor{green!27}\small If you grew up with a \textbf{black} and white TV u are not a millennial I was born in the early 80s I'm gen x 4 sure\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I understand \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I am a Gen X person born in 1975 and I always felt like our time as media darlings was extremely SHORT LIVED.  It was ridiculous how we got shoved out the door before we hit 25.  When I was still in my early 20s and under 25 back around 1999 and 2000, I was already hearing the media talking about the kids behind us that were Gen Y/Millennials and how much bigger they were then Gen Xers.  Honestly it felt like Xers had like 5 years in the media spot light during the 90s that's it.  I was under 25, young and in college, in the late 90s/early 2000s and it was suddenly all about the Millennials.  I'm 43 today, and the media is STILL talking about Gen Y/Millennials like they are teenagers, some of whom are already like 35, 36 years \textbf{old}, way older then I was when I first heard about them.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/155 & \cellcolor{green!27}0.645 \\  \hline
  \cellcolor{green!5}\small I was born in 83, I wish the media would leave my \textbf{age} group out of the millennial label which has become a name for the media to pretty much s\@it on everyone under 40. We didn't have cell phones, Internet, \textbf{nobody} cared about being PC and I never heard anyone in college talk about safe spaces or any of that other BS.\normalsize   & \cellcolor{green!5}Age, Nobody & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small Gen Xer here (1979).. this is so true. I remember them writing us off as the \textbf{nothing} generation. In all actuality we're the most accepting,  loving, free-spirited, entrepreneurial generation ever!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Lol really? Well take it back. I'm sick of everyone talking about millennials and looking at like 10 year \textbf{old} kids and being like "pffft millennials and their fidget spinners!" Millennials are adults, aged like 24 - 35 now.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@Michael Anderson You're doing the same thing. Mislabeling. Unless they started college really late, the millennial \textbf{age} group is not in college. We are late 20's and early 30's with careers and families. Stop blaming us for everything you don't like or for whatever your 10 year \textbf{old} kid is doing.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small aww poor you!  I remember being a kid in the 90's and looking up to your generation, longing to be that \textbf{age} in your prime, all the people born in the 70's were the amazing cool and beautiful young people I wanted to be....now you're all in your 40's and it's bittersweet lol\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small \@Dina Mule But Radiohead, The White Stripes, Beck, Foo Fighters, and The \textbf{R\textbf{ed}} Hot Chili Peppers were popular throughout the 20-aughts.  So was hip hop, which flourished in the early 90s.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small \@Fermented Sourdough I don't think people more than 15 years apart are of the same generation.  With 15 year spans, Boomers would have been born between 1946 and 1960.  Even then, you have people who came of \textbf{age} in the 60s in the same generation as people who were in diapers during that period, people who were hippies and vividly recall the Kennedy assassination alongside those who watched Sesame Street and barely remember LBJ.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small u-said-what? : It's NOT about WHAT or WHOM one remembers. You remain confused because you erroneously believe that a generation is a period of media (movies, music, news, etc.) influence; it is not. A generation is a Reproductive period of At Least 20 years, lest teenage pregnancy be encouraged. Some background information:  Westerners a century ago married after 25 years \textbf{old} because it took many years of apprenticeship \& journeyman status before one could start one's own business. During this time the bride acquired items for the household; the bottom drawer or the trousseau.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small Shhhh... we are called gen X for a reason... If you identify with this generation you would know that being the wizard behind the curtain is much better then being the sweetheart on the screen...Who do you think makes these films, videos and birthed the punk rock, anti-everything generation... If you care, maybe you identify with a gen Y perspective...your \textbf{age} only groups you, but that need for attention through approval is a gen Y perspective, us GEN X'ERS are fine with being the creaters in a costume over a puppet on stage, and I think that is part of the difference between X and Y.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/107 & \cellcolor{green!5}0.935 \\  \hline
  \cellcolor{green!27}\small \@Dina Mule yeah I felt \textbf{weird} by 97. It's like they flushed out gen xers and brought on the next. No wonder we are always working hard to prove we belong. Yes that makes us cynical. But we are the fun loving flannel wearing hippie crowd too.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Nobody ever talked about your generation. You will be remembered as the generation after the boomers and before the millennials.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I'm a Gen Y person from 1989 and agree with you. It's like the media is obsessed with millenials and boomers and even gen Z now,  but they rarely ever talk about Gen X,  they get so much overlooked. It's \textbf{weird} because people in 40's - 50's are a relevant  \textbf{age} group,  they are or will be  in charge of much of the world, especially now that boomers are retiring or dying off but the media still won't pay them much mind and I rarely ever see stuff marketed for them.This combined with the fact that lots of people just use millenials as a a generic world for 'young ' people that a lot of times is just incorrect since they think any teen is a 'pffft millenial' when they clearly are not. Millenials are over college \textbf{age} now and  Most  are pushing 30, or over it. Those kids doing fortnite dances and eating tide pods ARE NOT milleniialls, but people call them so regardless.That other poster who said that its probably simply because Gen X were a less numerous generation is probably right, it's all down to marketing and numbers. Plus Gen Xs supposed cinism probably made them into a more 'lay low' generation naturally. I don't think grunge type people were trying to hog attention and would be  take selfies to put it on social media, quite the oppossite. Kurt Cobain would be vomiting at that thought... but that attention grabbing narcissitic nature is idiosincratic to both millenials and Gen Z, probably thanks to social media\normalsize   & \cellcolor{green!27}Age, Weird & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/260 & \cellcolor{green!27}1.154 \\  \hline
  \cellcolor{green!5}\small I feel like the \textbf{senior} citizen of the millennial generation. 85'\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small 15 years \textbf{old} CENTENIAL BABY\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Every grumpy \textbf{old} man says that.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small We kinda had to "Man or \textbf{Woman} up" because our Boomer parents couldn't handle, and we got partly raised by the G.I.s.   Being a broke kid, Grandpa's workshop was my playground.  Got all my fingers, and did not get to use power tools until I bought my own.   Grandpa never taught me to weld, and now they don't do it with a gas torch anymore.  Now I hire out jobs to shops in Waipahu or someplace.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small \@freethinker B social media and communication devices definitely have made society more socially autistic,  I once said Hi to someone and they looked at me as if I was \textbf{crazy}, it's ridiculous\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Gen-Z will say the same 20-40 years after, when we are \textbf{old} like you\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Baby boomers and after is \textbf{nothing} great\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@JennieKate and \textbf{nobody} cares what you think\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I'm confused on how most of my generation suddenly became cringy and \textbf{weird} was it cause of the thought that they're cool and too mature for their \textbf{age} or was it those "kid channels"\normalsize   & \cellcolor{green!5}Age, Weird & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small This is beyond ridiculous. 73 years \textbf{old} remembering 2 world wars???? Ha ha ha...you must be generations BS\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small ​\@Fermented Sourdough I was born in 2002, and I prefer to say I'm generation Z. (Moreover, I watched a documentary about that, it said we were generation Z).It depends on the person, some people of my \textbf{age} would say they're Millennials and they're right. In my case, I've seen Millennial  and Generation Z series, but I grown up with more technology than my older brother (he's 5 years older than me). And I've more younger friends (13,14,15years).It's just... I don't see myself as a 1985's person XD. They're 33 years \textbf{old} and I'm a childish teenager. As we're a mixture, some people fit in Generation Z and another people fit in Millennials.Sorry for my English :)\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/119 & \cellcolor{green!5}1.681 \\  \hline
  \cellcolor{green!27}\small These wafting warping clip art people \textbf{freak} me out.\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small How is it the Millennials keep going up in \textbf{age}??? I'm 36 years \textbf{old}, I have \textbf{nothing} in \textbf{common} with Millennials.i grew up watching Lavern and Sherly, and He-Man I've never had social media unless you count YouTube I didn't get a cell phone until I was 25, I drive a 74 ford truck, and shoot guns on the farm I live on, I was in BCT (Basic Training) with the US Army on 9/11/2001. Does this sound millennial at all?\normalsize   & \cellcolor{green!5}Age, Common, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters, Social Class - Working class & \cellcolor{green!5}4/81 & \cellcolor{green!5}4.938 \\  \hline
  \cellcolor{green!27}\small Steven Michael,wow you mentioned Laverne \& Shirley.I was a little girl in the 1970s and they were in my time I am a Generation X \textbf{woman}. You have an older Soul to yourself and that is great to have.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small All this is grouping people by \textbf{age} and what as a whole they identify with.  What you are exposed to and accomplish is an individual experience, (a fabulous one at that) but your personal habits don't change the grouping of the average, which in this example is grouped by experiences collectively shared.  Like a rainbow we all make a collective group, some falling outside the average.Congradulations, you are NOT average in the group of which you are defined as...\textbf{nothing} wrong with that!\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/83 & \cellcolor{green!5}2.41 \\  \hline
  \cellcolor{green!27}\small \@Fermented Sourdough how you going to cut off 85 baby's? I have \textbf{nothing} in \textbf{common} with  Millennials. I remember a time before the internet and smartphones laptops computers.I remember playing outside riding  Bicycles playing basketball and most importantly working to make my own money to go to the movies or whatever activity there was at the time.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small If your only 36 and watching Lavern and Shirley you must be a very \textbf{old} soul.....very old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small These generation labels are not 100 accurate. A tech savvy young gen x'er would have a lot in \textbf{common} with older millennials while an older millennial may have  a lot in \textbf{common} with gen x'ers if they didn't grew up around technology and weren't that into it as it became more mainstream.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small ​\@Fermented Sourdough You're /way off. The generations we are talking about, not the dictionary definition, are not perfectly set at 20 years, they use a series of important national trends or events to help define them. Also, different sources have defined the start and end of each generation differently. Some have gen x ending at 77 and there being a micro-generation between X and millennials. The growing consensus on gen z is the oldest are in their late teens or early 20s right now, I have not seen any say the upper \textbf{age} for gen z is 13 as you are claiming.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small Same here , I'm 35 and I have \textbf{nothing} I'm \textbf{common} with millennials , I grew up watching  all in the Family , Sanford and son , chips , Tom and \textbf{Jerry} , Gumby ect .. I work 60 hours a week , respect my elders and I have no social media accts ..\normalsize   & \cellcolor{green!27}Common, Jerry, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - German, Social Class - Working class & \cellcolor{green!27}3/54 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@mojo I think you mean Xennial. Basically, people born in the late 70s to early 80s that overlap with both generations. The edges of generations are always blurry as I mentioned in my other comments. If you grew up around technology and embraced social media, you likely have more in \textbf{common} with Millennials than Gen X as that is a significant defining trait. Likewise, if you avoided technology and social media, you may have more in \textbf{common} with Gen X, especially if you're someone who grew up watching a lot of Gen X/Baby Boomer show reruns like some of the people in these comments. But I think outside of Xennials, this no longer applies. The fact someone watched a lot of \textbf{old} TV show reruns doesn't make them another generation.  [LINK] \normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}3/131 & \cellcolor{green!5}2.29 \\  \hline
  \cellcolor{green!27}\small F M 85 is 100 millennial no matter how many times you say the tired \textbf{old} reasons why you're not. 85 babies are the 100 millennials\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small E B : The new millennium began in 2001, because we count from 1 to 10, not from 0 (\textbf{zero}) to 9. Generation Y is called The Millennials, NOT the Millennia or Millennium. Semantics, semantics, ...\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@Cyndi Sherry that's pretty cool to hear of "read in this case" 😂. I'm about the same \textbf{age} as you're first child so that's pretty interesting. Do u notice any differences between your kids who were born in 96 and 00?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small YoQuiero LosTacos yes way idk but my gen we atcually went outside and iphones werent popping it was flip phones so little kids weren't playing on phones at a \textbf{age} where kids dont have bussiness ona smart phone these kids are a diffrent breed im sorry my opinion sticks with me atleast when we was little kids gen z btw the  technology isnt what it is now finger prints,face unlock whatver,etc and u barely saw a little kid im taking bout 5-10 on social media but times change it was about 2007-2014 before we have little kids acting grown its sad but these kids cant be gen z sorry\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small \@General Leopold Horchigli , lol. We sure are. I'm a 26 year \textbf{old} Millennial and I'm always called 'cute' by my lady companions. Our only problem with that though is - Many of us struggle with dating for whatever reasons.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small I'm glad I'm in generation Y. And not in generation X. I feel \textbf{old} if they put my birth year in generation X. I was born in 1983.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@guess 66 I lean more towards Gen Z, but I usually have more in \textbf{common} with those born in 1995 to 1999\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@guess 66 but I'm a conservative Republicans, millennials are liberals, and I was only 4 years \textbf{old} during 9/11 it was 3 days before my 5th birthday, so that kind of puts me in both Gen Y and Gen Z, though I would say I have more Gen Z traits, I don't demand a safe space, and I'm pragmatic, collaborative, and not entitled, my late boomer parents raised me well, which is why I don't go on a rampage when I don't get what I want, unlike millennials\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small \@General Leopold Horchigli I understand that and I'm the exact same way, I'm only 1 month and 4 days older than u we're both on the cusp of Gen Y and Z like I said but not all Millenials are like that. It's impossible for an entire Generation of at least over a million people to have those Triats. U don't determine Generations by if they're Conservative or Librals cause any one doesn't matter what you're \textbf{age} can be either one. We really have \textbf{nothing} to do with Core Millienials those born from 1985-1992 but pretty much r whole youth culture up til 2012/13 was under Millienial culture and it wasn't until Mid 2016 when Gen Z Culture began which by that time we've both been done with school for a while and r no longer kids like the core Members of Gen Z were Those born from 2001-2008. We're on the cusp and can choice either one but let's not base it just because of our political preference. I'm a Conservative but know that their r members of Gen Z who Liberals\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/183 & \cellcolor{green!27}1.093 \\  \hline
  \cellcolor{green!5}\small Thought my generation were pretty much just called Yuppies, and not Gen X. I thought Gen X were the kids between my \textbf{age} and the Millennials. Didn't really think there was a Gen Y and Gen Z thing going on. But OK. Dang kids, get off my lawn! LOL. (What lawn? I can't afford a house anymore. I've got no problems with Millennials.)\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Mikey C23   No, gen X kids were school \textbf{age} in the 80s. MTV was good then and cordless phones only existed in the movies or the super rich.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I am a Generation X \textbf{Woman} and proud of it. I grew up as a little girl in the 1970s and a Teenager Lady in the 1980s. I missed the music, Group Bands, Variety Shows,Soul Train, America Bandstand, Cartoons on Saturdays,fashion,hairstyles, sitcoms shows,board games and family togetherness in the 70s. I missed the Arcades,Malls,Game Shows,more sitcom shows,movies,Drive Ins,MTV \& Video Soul on BET music videos of the 80s. We had problems like all Generations,but we did not have any School Shootings that I can recall. Also I still have a home phone long cord that I talked on daily,my answering machine,VCR,Cassette Player and a Record Player to play my Albums that I still have from the 70s,80s and early 90s. If only we had a Time Machine.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/127 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small I liked it changing from landlines to cell phones. Mother and brother couldn't listen to my calls and with living over an hour away from the family now having VoIP and  smartphones so we aren't paying the \textbf{old} long distance rates to talk to each other.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small You could be what is considered an \textbf{old} soul, not to be confused with the stereotype. As in my case, I was born in the early 80s, so am considered a millennial. However I was heavily influenced by 80s music, movies and Micheal Jackson era. I could also be considered a younger gen x. Depends of perspective and point of view. Also many people were influence by their older siblings and grandparents. I too have a fascination with the music and culture of the early to mid twentieth century.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small OMG! You guys are the same \textbf{age} as my mom! Hi guys! Lol!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Barb DeSouza --Yes. Been a while since I heard Lycia. Also, \textbf{Black} Tape For A Blue Girl.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@vic ferg agreed man! I was born in 83 and I consider my Generation X because i don't relate with millennials at all! I'm \textbf{old} school and grew up on cd players and mtv when it played music videos and without technology til i turned 18 and had my first AOL account and 56K dial up to go with it lol. I grew up on Nirvana, Alice in chains and and the whole grunge movement and post grunge ordeal. This video is so far off its not even funny. The first demographic i read awhile ago said Generation X is from 1965-1985 then Millennials 1986-1996 then Generation Z is 1997 til present day or Centennials whatever they call it. My point is you're totally correct though we definitely are Generation X or from now a new study says we're Xennials.. it's a micro generation that goes from 1977-1985. We're caught between gen X and Millennials. But again I do not relate with millennials as i'm sure you do not either.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/170 & \cellcolor{green!27}0.588 \\  \hline
  \cellcolor{green!5}\small \@EmperorNite Byte hey--Our generation didn't ask the later generations to listen to our music. Your generatulion naturally gravitated to it. Most of the later generations state online they don't like their generation's music. They prefer ours. \textbf{Nothing} more to say. Also, you are the one trolling others on the thread. One has to ask : why the trolling?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small Gen x bro that's \textbf{old} that's like 80s or sum\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Gen z...was born in 95, i remember rugrats and all that, i think i was in 1st grade on 9/11... But I'm 22 years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small So you have VCRS, CDs, boom boxes, floppy disks and usbs as a kid? My parents home is a mix of \textbf{old} and new tech as well.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Generation Y. Squeezed between a well off generation and a spoilt generation. Few jobs, little or no training opportunities, apprenticeships nope. House prices too expensive, though the few if got in early and had some help played the market well. In the UK, we can ‘thank' the EU for taking our jobs and careers, why invest in your workforce when you can employ numpties for peanuts? Business too expensive? Relocate abroad instead. Got a mortgage to then purchase multiple properties even though you have no money? Sure don't worry about the long list of people who can't buy a house because a few have bought them all... Computers at school were \textbf{black} screens with green text, (Amstrads I think) and internet just beginning so forget any formal knowledge of modern tech lol\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/132 & \cellcolor{green!5}0.758 \\  \hline
  \cellcolor{green!27}\small There is a reason we are at "Z" right now. We are in exciting times!!! Next up will be the Golden \textbf{Race} and not a generation.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I was born in 1997 so technically I'm Gen Z, but I connect more to Gen Y because I saw technology build and expand. Back in the early 2000s we had flip phones, whereas most in Gen Z grew up already knowing about \textbf{Apple} products like IPhones and tablets. I also grew up with some pretty rad cartoons that most of Gen Z doesn't know about. The \textbf{old} Teen Titans and original Power Puff Girls, Ed Edd N Eddy, Tom and \textbf{Jerry}, lots of shows that Gen Z wouldn't have a clue about if you asked them now. I don't remember where I was during 9/11, I was too young, but I remember a lot of other things from back then that connect me more with Gen Y than Gen Z.Plus I'm 21 and most of Gen Z is in Middle or high school so like. Awkward.\normalsize   & \cellcolor{green!5}Apple, Jerry, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American, Nationality - German & \cellcolor{green!5}3/148 & \cellcolor{green!5}2.027 \\  \hline
  \cellcolor{green!27}\small A Garcia Tom and \textbf{Jerry} cartoons? I think those date back to the Traditionalist generation (1940's)\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small A Garcia If you think growing up with a flip phone vs an iPhone puts you in a different generation, think about how early Gen Y people feel. Most of us had NO CELL PHONE until high school or college. If you didn't go through grade school with the option to turn papers in either printed OR handwritten because most families didn't have printers at home, then you don't have more in \textbf{common} with Gen Y than Gen Z. You watched technology grow (every generation has and will) but not in the same ways.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small Uhhh not. If you only remember cell phones, you're too \textbf{old}. Gen Y remembers beepers. Phones weren't \textbf{common} until 99-2001.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I'm the same \textbf{age} as you and my early gen X parents were always very strict with me on getting a phone. I didn't get one till 7th grade and by then smartphones were already out. But I do remember kids having the sliding keyboard phones.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@guess 66 I don't think I have any Gen Y traits, and I'm very conservative for someone my \textbf{age}, almost like someone from the 1900s\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Millennials call us Gen \textbf{zero}, heck we'll have more potential than those millennials\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Sanyo5580 : Yes, indeed because we count something from one to ten, not from \textbf{zero} to nine. So every decade starts in the year with a 1: 1981, 1991, etc.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Zeke the \textbf{freak} I know. which is why I commented that in the first place. too new for 90s but too \textbf{old} for what 2000s babies are typically seen as\normalsize   & \cellcolor{green!5}Freak, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small What's being born in 2005? I remember having all the 90's and 80's experiences along with the 2000's like \textbf{old} desktop computers and no to very little smartphones\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small MCatwar,You don't determine that you are a 90's kid because you were born in the 90's... you are a 90's kid if you were \textbf{old} enough to experience it and have memories in the 90's... so arguably in order to really be a 90's kid you'd have to be born around the mid to early 80's... you are nowhere near that.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small \@Virtu if u were born in 2002 the earliest memories u can remember would be 2005 when u were 3. U started primary school in 2007 and depends on where u live left in 2013, so from 2008-2012 u were in your core Childhood \textbf{age} 6-10 with the 2009-2010 school year being your peak. You're a 00's Kid but one of the last ones so ce you're a Late 00's-Early 10's Hybrid [With Majority in the Early 10's]\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small \@guess 66 Nice I don't wanna be considered a 2000/2001 kid they're a bit too \textbf{old} for me lol. Even though I was born in February.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I was born in 2000 I'm a early prototype of the gen z batch. I mean I remember rugrats and many other 90s  shows. I didn't have a phone till I was 11. And my gaming experience as a child was my brother letting me play sonic on his \textbf{old} game boy. I would say I got  at least get a after taste of the 90s.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Tf is meme culture how \textbf{old} are you 60 smh you sound 60 too\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Wrong, well mislabeled...most sources break up what is lumped together into the Silent Generation even more than that. A 103 yr \textbf{old} has a different experience than an 80 year \textbf{old}...just saying\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Why you sound \textbf{weird}? Or is it just me?\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small 1983 not \textbf{old} but also not young 😐\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hasn't happened yet. Back in the 70s and early 80s, before my time, there were science fiction films about the topic. We are still in the early \textbf{age} of genetics. Remember Dolly the sheep was cloned in 1999 and the Human Genome project was in the early 2000s. We started growing GM food last decade. Now as of, perhaps post 2012, we are still trying to cure genetic diseases in humans and crops.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small I am Canadian and a gen X, but was born in 1967 so I am considered a Centennial Baby, because Canada was 100 years \textbf{old} in 1967.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{nobody}, I'm to wierd to be allowed to fit in with anybody\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small What happened in 2001? This is a 1961 POST baby boomer/neither millennial. just a forgetful left leaning (all along) who does remember older siblings Vietnam war /civil rights protest experiences and where I was in 9-11.  So what happened in 2001 besides Argentina fiscal crisis. One more things those of us who went to HS in the seventies call ourselves ' the lost children or the forgotten ones' since \textbf{nobody} paid attention to what we did or didn't do.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small I'm just laughing at the Fact of some \textbf{old} person saying Back in my Day I Witnessed the Creation of Sliced Bread Lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Sean Noble you are a older millennial. Older millennials are \textbf{nothing} like their younger counter part. Also older millennials in general are considered better out of all the generations that have ever existed and the younger generation x is considered to be good but not the older one.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small It's not really a "label" it's more of an identification of what time period you grew up in. It has \textbf{nothing} to do with being a follower or leader.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@Jalen Powell drake and josh was ny fav show when i was 7! Im 12 years \textbf{old} now\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Yeah, they seem pretty millennial to me. They're not gen x by the time those shows came out I was too \textbf{old} for cartoons. Let the kids have their shows.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small And ben ten and Scooby Doo, flinstones, Tom and \textbf{Jerry}, and many more.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small The people on friends and living single were x generation... I watched but i wasn't \textbf{old} enough to be out of the house yet. Lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Im on the cusp..I was born around the same time most cable channels came out... im \textbf{old} enough remember video arcades but not \textbf{old} enough to have gone alone.  Im \textbf{old} enough to remember the \textbf{transition} from boxy cars to curves, but wasn't driving...August 1979... so I was in the middle of the carter administration,  but grew up under Reagan..  I don't for neatly in x or y...\normalsize   & \cellcolor{green!27}Old, Transition & \cellcolor{green!27}Age - Over 65s, Sexual Identity - Transexuality & \cellcolor{green!27}4/69 & \cellcolor{green!27}5.797 \\  \hline
  \cellcolor{green!5}\small At the end of the day we're all humans trying to live and survive so these labeling of \textbf{age} doesn't really matter :)\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I'm a Gen Z person/Centennial! I was born December 28, 2000. My parents are from Gen Y, and most of my half-siblings are Millennials. Despite the fact that the younger people are from Gen Z, I've noticed a lot of differences between people born in my year and people born a few years after. Although I can't remember 9/11 despite being alive, me and my peers have grown up with 90's and early 2000's cartoons, and relate more with late 1990's people as a result. The majority of people my friends and I have met that are a few years younger than us seem to have a different attitude and approach to social situations like school. While most high schoolers aren't very respectful to begin with, each new class of students gets worse in the behavioral sense. I'm not saying this is the case of everyone, but based on the majority of the freshman during my \textbf{Senior} year of high school, they seem to think they're entitled to acting \textbf{crazy}, that they don't have to have manners, and thinking they're better than everyone. I don't know if it's because of the influence of the louder and more disrespectful individuals that are in my class, but it's sad either way.Sorry for rambling, I wanted to notice the differences I've seen despite the closeness in \textbf{age}. I can't believe that my class in going into college already. As this new generation grows up, a new one will eventually be born. Only time can tell how they'll be, huh?\normalsize   & \cellcolor{green!27}Age, Crazy, Senior & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/257 & \cellcolor{green!27}1.167 \\  \hline
  \cellcolor{green!5}\small As a millennial I do not feel closest to Gen Z but rather the most closest to our own generation and probably Gen X ... Generation Z is really hard to communicate with and find \textbf{common} interest what so ever!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small kitttcat kissy may be that's just your sister and her friends....doesn't apply to everyone. Just like I know \textbf{crazy} Gen Zs,but I don't think the whole generation is messed up.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I hear you but just because that is true for you I must say most people that I see in our \textbf{age} range are disrespectful and low when it comes to hard work. But that is just my experience.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Jenny Rodriguez  no sweetheart \textbf{nobody} has really ever been "given" a job, nepotism aside...most people have had to earn their place if we are talking a good job...  there have always been entitled prats btw...I think they are much more visible now and almost daring people to challenge them....And I said that child labor laws have been in place even before you were 14....I was asking what NEW ones you were referring to, as most everyone would have had to deal with then unless they're like 100 or something....\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small Oh shush you snowflake\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Jenny Rodriguez that sat back and called us \textbf{crazy} instead of asking questions and trying to help some of us\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Gareth Sheals I don't know why anybody has any hope for my generation (Z). I don't see anybody my \textbf{age} aside from a few friends of mine that use any logic or reason in any scenario, whatsoever.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Victoria Janelle \textbf{nothing} in my comment depicts that I'm offended in any way,shape,form,or fashion. Only stating facts that weren't stated in the video\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small The economy  is good put what has Trump  done \textbf{nothing}!!!!!!!! The economy  is just rebounded from the the great recession and Trump knows this you trumptards!!!!!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small For all those commenting, every generation has flaws. There are lazy, entitled and nasty people and there are respectful, humble, hardworking people in every generation. One thing I will say is that you would think millennials would have been taught to have the same core values as their parents. I know I was and a lot of my friends were. We were taught to work for what we want, to be respectful and to remain humble.  If your child can't even be respectful then you failed them. I know plenty of people who had parents that gave them everything they wanted and are now entitled, as parents you need to set boundaries with your children and set them up to be successful at a young \textbf{age}. Teach your kids what you know instead of complaining about them. With the new \textbf{age} of technology, we need each other. I have to ask people a few years younger than me how to do stuff because it's so hard to keep up with the times. My parents taught me how to balance checkbooks, write checks, etc. I taught myself how to invest, I set myself up with an IRA and learned to spread my wealth on my own. I try to teach what I know to others so that they can set themselves up for success as well. I knew that I didn't want to struggle in life so I did what I could to set myself up for success at a young \textbf{age}. However, I am still like most millennials, I have debt, but I work hard for everything that I have and work to pay it off. There is research to backup Jenny's claims, I'm not sure about the economy part. It's easy to discredit the struggles a generation is going through because you went through times that you believe were harder. Things were hard for each generation in different aspects.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/320 & \cellcolor{green!27}0.938 \\  \hline
  \cellcolor{green!5}\small deesje dee so how could we have made things right before we were born,so we were supposed to be born knowing right from wrong,and you can just sit here and tell me you wouldn't walk into a store and hear a kid screaming because he didn't get a toy or see a teen being rude to an \textbf{elder} you wouldn't blame it on their upbringing. Come on you're digging yourself a deeper hole. As for the rest,we've already had past generations admit to faults so it's really no secret now.\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small deesje dee I'm sorry for taking your comment the wrong way,you're right we'd solve a lot more problems if we worked together and made the USA better,heck the world (I know America is the worst right now),but as you know it takes 2 to tango. I would be willing to with all generations to make more peace in the world,yet I'm a millennial and considered to be a spoiled,lazy,entitled, \textbf{snowflake} regardless of how hard I work,how polite I am,how much I respect others no matter their generation. I apologize again for the misunderstanding.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small \@So Core ¯\ (ツ) /¯ \textbf{nobody} cares\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Yeah, I'm gonna have to agree with ya, Jenny; We are a generation that is about respect, more so than we get credit for. The difference between us and the generations around us is this: the generation before us thinks respect is forced through domination, power, and control. The generation after us thinks respect is a given and is super offended if you don't behave the way they feel you should. Our generation, however, is more about obeying obvious social protocol and otherwise just letting each other be their selves. Big difference. But because we don't make a stink about it like the two surrounding generations and don't try to impose our own personal view of how we want respect given and aren't as controlling and demanding about getting respect bc we are more comfortable just letting everyone be their self, people think we aren't about being respectful as much as other generations. \textbf{Common} misconception. 😘✨\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/156 & \cellcolor{green!27}0.641 \\  \hline
  \cellcolor{green!5}\small I think one needs to understand how grouping for the sake of averages are done.  Your personal identification, work ethics and habits have \textbf{nothing} to do with the average of a group.  These classifications were done by \textbf{age} groups as mentioned in the begining of the video based on identifying collective experiences.  Your personal experience or acceptance of where you fall under the average is irrelevant.  An average isn't a fact, it's a way to classify groups, just because you fall into a group doesn't mean you are the average of that group, nor does it classify you as an individual.Ironically, this comment  is  humorous to me because your need to identify to a group is itself typical for your \textbf{age} group average.Relax, if you don't identify with the average of the group your a part of then your not the norm for your group, and that can be a great thing if you wish it to be.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}3/160 & \cellcolor{green!5}1.875 \\  \hline
  \cellcolor{green!27}\small No. It's \textbf{nothing} to do with decades...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I am completely in love with this video! It is so accurate when it comes to generations. The birth years or definitely different than I thought. I was born in 1974. I'm off to making the comment to my girls that are 23 and 14 years \textbf{old} but I am so glad that I did not grow up with all of this technology. I get a lot of questions about what did you do before Google. I just laugh and tell him how easy it is for you to find out things now as it was not so easy back then. There's definitely pros and cons to each generation. But I will say that I am so glad I was the baby of the 80s! No better decade and definitely no better music than back then!  Good job bright side!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/140 & \cellcolor{green!5}0.714 \\  \hline
  \cellcolor{green!27}\small Oh yeah, \textbf{snowflake} \textbf{communist} millennials are the best. NOT! They're the result of being raised by television with aholes like you eating their souls.\normalsize   & \cellcolor{green!27}Communist, Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Being a Millennial born in 1990 I spent my childhood without the internet and grew up much like Gen x, playing outside pretending to be a Power Ranger. My teenage years, though, were the emergence of the tech boom. I got my first cellphone at \textbf{age} 13 and it wasn't even a flip phone! It was a brick with everything on the front. My family got our 1st computer when I was 8 [because my bro is gen x and was into electronics]  and I remember It had a total hard drive space of around 2-3GB. For 1998 that wasn't actually too bad. A "good" computer could have as much as 6 to 8! A supercomputer top of the line MIGHT have 16. Check out this article written in 1999 about computer harddrive space, it's hilarious. "by year 2000 we expect to have 25-30GB drives for around \$200!!!"  [LINK] \normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/149 & \cellcolor{green!5}0.671 \\  \hline
  \cellcolor{green!27}\small Cal Leary  my daughter was born in 1990 also.  She begged me for a computer at the \textbf{age} of 10 cause everyone in her class had one and she needed to do her work on it.  we got a gateway computer lol. She set it up no lie. I'm a gen x born 1971. I didn't know about computers at all\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Angel Teague My early generation had very strange young lives. One minute your're outside playing, the next your playing a computer game called "walking outside adventure" No wonder the early years of Gen Y are so messed up as adults lol. OH and that reference to Gateway made me realize even I'm getting "\textbf{Old}" lol. My gen will forever be known as the test run faze for Gen Y and it's many humanity crushing editions that ultimately destroy earth on accident.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Cal Leary   I'm Gen X but find it odd that it took your parents so long to get a computer. When I was a kid in 1984, we got our first computer (an \textbf{Apple} IIc) and I started learning computer programming.  We had computers in school also and experienced boomers trying to teach computers when the kids knew 1000 times more about them. Yes it wasn't as advanced as computers now but we used to be able to access the base programming, alter it, and write our own programs. It was more fun than being locked out and having software control everything. We had internet access at home and school in 1991.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/112 & \cellcolor{green!27}0.893 \\  \hline
  \cellcolor{green!5}\small The good \textbf{old} analog world\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small It gets even more interesting if u live in a post \textbf{communist} country since that \textbf{transition} is way more defining than anything else.  Another important date for me  is 1994 and the death of Kurt Cobain, music drastically changed forever after that year.\normalsize   & \cellcolor{green!27}Communist, Transition & \cellcolor{green!27} Ideological and Political Identity - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small You click the \textbf{black} button is eror Youtube <⚫> 👈🏻 ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏ ‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏‎‏⁧‮ereh-hcuot-t\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small if you were entering the labor market around 2008, no matter how \textbf{old} you are, you are millenial. And if you were not an adult before around 2014 you are genz.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small That's weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I was born in 83, I think my upbringing and mindset has more in \textbf{common} with a 45 year \textbf{old} Generation Xer compared to a 25 year \textbf{old} millennial.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/29 & \cellcolor{green!27}10.345 \\  \hline
  \cellcolor{green!5}\small i listen to 40s music and classical music even im 10 years \textbf{old}edit: i also listen to some lofi hip hop but i listen to 40s more\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Zach Lipinski But the majority of Gen Z children have Gen X parents. It's just the way it is. If you were to define generations your way, then actual generations wouldn't even be close to keeping up with the dates of the actual generations. A generation is a group of people a similar \textbf{age} who have similar experiences and living conditions. It has \textbf{nothing} to do with your parents. Besides, literally every source or whatever suggests or outright says that Millenials' children are going to be Generation Alpha while children of Gen X parents are from Gen Z.\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Argue if you want, but \textbf{nothing} you say will ever convince me I'm a Millenial, seeing as I haven't shared their experiences and wasn't born around the same time.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@Michael Anderson oh look we got a \textbf{snowflake} ;3\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I'm 29 I don't consider myself a millennial, I'm \textbf{old} fashioned, values,I don't follow trends\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Sabina xxD I remember it too, but I'm also good bit older than you and I was 13 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small 9/11 is a major event that helps define the toggle point between Gen Y ans Gen Z (used their short names) - The generations have more to do with how the social, economic, political, environmental, etc. events help to form the general outlook of a cohort of the population. You can see from the comments below that just a slight difference in \textbf{age}, can make the difference between remembering a major event and not having it be part of your active memory. This is what helps to define your outlook. That is why those that just barely remember 9/11 are the end of Gen Y.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small \@Vivz McCrea I'm 1996 and I consider myself 90 Gen Z and 40 millennial, don't \textbf{lump} us all in with that failed generation\normalsize   & \cellcolor{green!27}Lump & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I'm a millennial and I have baby boomer parents. A lot of kids my \textbf{age} had cell phones by middle school but my parents wouldn't get me one. They said phones are not for kids. Now I'm an adult and I see toddlers with cell phones.*Edit: I think the only things a cell phone did back then was call and text\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Ive always considered myself as belonging to gen x. In school they said gen x ended in 81 or 80. I have more in \textbf{common} n get along with gen x more than gen y.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I think a lot of this comes from advertisements in the late 80's to mid 90's. That were targeted towards kids. So you're seven years \textbf{old} watching cartoons when a ad comes on featuring other seven year olds on skateboards selling jeans or whatever, and it said things like 'We're generation X...' Turns out, TV just lied to us. It seems the terminology was defined before then, marketers in that time period just didn't use it correctly.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small Melanie Schneiter  The youngest Millennial is 22-23 years \textbf{old} (as of 2018). Teens are Gen Z\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Nope. I was born in 1980 and have very little in \textbf{common} with Gex X. Most of my memorable experiences as a kid happened in the 90s. I grew up with computers and video games, Nickelodeon, the internet, ‘NSync and Backstreet Boys...definitely not Gen X, but maybe Gen Y is the better term. We're the older (and forgotten) Millennials.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Sarah Kenney huh, I was born in 80 as well n the girls I knew were too \textbf{old} for Backstreet Boys. I remember them liking new kids on the block. I was into ac dc, nirvana, Tupac, slipknot when they first came out. Yeah, Cartoon Network and nick, johnny bravo and powerpuff girls, e.t. And Rambo, dukes of hazard...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Common. 80s babies are definition of millennials.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I consider myself Gen X, but I have a lot in \textbf{common} with Millennials. Unfortunately.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Born in 83, We didn't grow up so different. My guess is my childhood would probably have more in \textbf{common} with a 45 year \textbf{old} Gen Xer compared to a 25 year \textbf{old} millennial.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small Im a Millennial raised by Boomers. I am more \textbf{old} fashioned in many ways but have the knowledge for the now. I choose to do things the hard way and back to basics. This is one brave video. The generation labelling could cause a giant trolling war 😂😂😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small I was born in the early 80's raised by parents born in the late 40's. Labeling generations is pointless because a 25 year \textbf{old} millennial raised by younger baby boomer parents or older Generation Xers born in the 60's probably came up a different way.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Somewhere discovering a new gender\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I think what you meant was in such a short period of time we have seen more advancements, which is true. Most likely by the time we reach an \textbf{old} \textbf{age} we would have seen more technological advancements then ever. I'm only 25 now so in 50 years when I'm 75 we would most likely have a world where we are hyper intelligent digital creatures. We will most likely be ageless and \textbf{gender} fluid thanks to new digital social media tech we will see and we most likely will see the creation of humanoid robots that are almost indistinguishable from mankind itself.\normalsize   & \cellcolor{green!5}Age, Gender, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Gender - General & \cellcolor{green!5}3/102 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small taking note that the earliest generation documented was born before WW1 past generations really dont get the love but i do understand but if i were to pick what the generation born between 1760 and 1790 would be called i would say it would be called gen rev why the late 1700`s were defined by revolution and change and when the reign of kings starts to become obscure like today it is a miracle they are still here so fellow commenters tell me in the comments what the generation born between the civil war or if you have your own name for the revolutionary or just pick any generation born before the 20th century and tell me why it can be from the dawn of time to the victorian \textbf{age} i would love to know you can do multiple ones please post the comment like this:-name of generationreasons why they should be called thati would love to hear what you have to say in the comments God bless everyone and have a wonderful day\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/178 & \cellcolor{green!27}0.562 \\  \hline
  \cellcolor{green!5}\small I don't buy the whole concept. For instance, the youngest Generation X person would have much more in \textbf{common} with the oldest Generation Y person than he/she would with older Generation X people. You have more in \textbf{common} with people at or around your \textbf{age} than you do with much older or much younger people that happen to share your arbitrary generation's label. It's just \textbf{common} sense.\normalsize   & \cellcolor{green!5}Age, Common & \cellcolor{green!5}Age - General, Social Class - Working class & \cellcolor{green!5}4/67 & \cellcolor{green!5}5.97 \\  \hline
  \cellcolor{green!27}\small John Gold This is true and accounted for, it's referred to as the cusp of the generation where you can exhibit numerous shares experience and behavior with a different generation, but we look on a mass scale of kids and conclude on that. For example, a kid born in 94 and a kid born in 95 are friends growing up, they share similar values and concepts, similar experience in life. They grow up, are still in touch, but find themselves having more in \textbf{common} with peers a year older/younger than their cusp friend. 94 kid finds his new friend born in 95 shares more of his views etc. While the same is true for 94 kid finding more things in \textbf{common} with his 93 friend. Of course, this is all on averages for mass scale, and there will always be outliers, and more of them regarding cusps. This is just how the cookie crumbles for modern generations, where behavior and observable change is increasing each year thus resulting in much more frequent and more dramatic generation transitions.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/177 & \cellcolor{green!27}1.13 \\  \hline
  \cellcolor{green!5}\small John Gold the average 24 vs 23 year \textbf{old} has a different thought process which is observable in society today, with the 23 year \textbf{old} being more conservative with money, being more practical and business minded where the average 24 year \textbf{old} is less so.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I agree, My \textbf{age} group born in the early 80's is considered Y by some but X by others. My \textbf{age} groups childhood/teen years would be closer to a 45 year \textbf{old} Gen Xer compared to a 25 year \textbf{old} millennial that got their  first cell phone at 10 years \textbf{old} and doesn't know a time without Internet.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}5/58 & \cellcolor{green!27}8.621 \\  \hline
  \cellcolor{green!5}\small PREPFORIT I thought millineals were lazy. Btw. \textbf{Age} 38, we ain't them\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I see it like this. LAZY has Y Z A in it already so if the next generation is to start over alphabetically it already has all the LAZY generations in its spelling. Just add the L and you get their most \textbf{common}  description.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small So you were born in the late 90s? My little cousin, Annie was born in 2002 and is now 16 and in high school. And I was born in the early 80s. We have a lot in \textbf{common}. Mostly goofy antics, over thinking, and \textbf{crazy} siblings.\normalsize   & \cellcolor{green!5}Common, Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Lucy M.D awww.  You are probably the sweetest person that I have encountered here.  I do apologise as it was never my intention to offend or look down upon any generation.  In fact, it was the opposite.  You must have not learned about Socrates yet.  He was one of the most famous philosophers ever.  I was attempting to use his quote to underscore the fact that every generation is guilty of looking down on the ones that follow.  However, apparently you are an exception.  As am I.  You appear to be close in \textbf{age} with my grandchildren.  It is my belief that every generation has great strength...as well as weakness.  As we all do.  I should have been clear that they were not my words.  You express yourself very well and I am impressed.  Keep it up and you will go far in life.  Have a great day/night guys and gals.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/151 & \cellcolor{green!27}0.662 \\  \hline
  \cellcolor{green!5}\small Teri Lefevers I'm technically millennial and pass judgement to younger kids as I've gotten older.'Get off my lawn!''Quit playing that loud hippity hop music.'Not really, I'm a nightclub DJ and drink heavy with the young kids but then I'm the creepy \textbf{old} guy trying to 're-live his younger days.':-(\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Or we could respect people who deserve respect, regardless of \textbf{age}.... just a thought\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small dang now you guys are old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Age is just a number :) Sometimes I feel like 18, sometimes like 80.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small ho!\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Ray M blame goes to technology and how those generations were raised by there parents. You can't blame the generations that have no control over nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small tobagotb10 Wait, you can't be 90 years \textbf{old} and be a kid. .  .\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small POVHFR Videos I don't really agree with that. That may be because I might be biased, because I am part of gen Z, but I think you can't judge all people by their generation. My parents (who are gen X) are on their phone just as much as anyone else. Plus, people seem to think that we are the worst generation purely because we go on our phones. That isn't that bad. Gen Z is a meh generation so far, not anything cool, and \textbf{nothing} too bad. Thanks for reading.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small My name is my name Nah, you just loathe being millennial bashed. Embrace it, and appreciate witnessing the technology \textbf{transition}. The world will be ours soon enough.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Django Marine...Sorry, but that's your opinion of yourself, not mine..I can recall a time before the internet, cell phones that are like mini computers, and PC culture  "safe space" bullshit...I don't relate to millenials at all ...Just my opinion...Anybody \textbf{old} enough to really remember most of the 80s and the 90s is Gen X imho-\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small LOL, Early 80's babies do seem to get left out. The last \textbf{age} group to grow up as kids/teens without Internet or cell phones.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Michael Anderson no they are not gen x even despite some duspute among experts all experts ageee millennials start early than 83 I was born in 83 have \textbf{nothing} in \textbf{common} with gen x I didn't turn 18 untill 2001 didn't graduate college untill 2004\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Michael Anderson also gen x was invented for those who became young adults in 80s and 90s they were called ' MTV generation ' influence on pop culture on 80s and 90s even those born in 19980 had no influence in 80s and most of 90s I still remember when I was in college we were called gen Y which is another name for millennials now millennial is much popular to say than gen y but both are same I mean anyone born in 1980 didn't turn 30 untill 2010 and word millennial start to emerge In 2005  I feel better here early 80s born need to accept the fact they are millennials I mean refusing to call themselves millennial and creating 'new special generation ' is the most millennial thing to do  also not many experts consider ' xennial ' legit generation in order to be generation they should atleast last 15 years  also ' micro generation ' them should be applied to every generation. What about early boomers and late boomers what about early gen z who are in college in their early 20s and late gen z who are still younger than 10 what does 21 year \textbf{old} have in \textbf{common} with 10 year \textbf{old} ?\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}3/209 & \cellcolor{green!5}1.435 \\  \hline
  \cellcolor{green!27}\small That's your opinion but early 80's babies not really being part of the 80's means \textbf{nothing}. By your logic, what does a 1981 and a 1995 baby have in \textbf{common}? Most early 80's babies didn't use internet until they were  high school but it wasn't an every day thing in the late 90's and didn't get a phone until after high  school. 1995 babies had phones before middle school and don't know life before the Internet.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/76 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Michael Anderson i bet in 10 year current early 20 gen z gonna say stop comparing us to younger gen z we \textbf{nothing} like them.  Beside creating this special group 'xennial ' just to run away from being called millennial is the most millennial thing to do and come of as crybabies\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Michael Anderson I didn't become teen untill 1996 technology wasn't different from 2000 as I said technology always evolving.  Let me ask u this what does gen z who born in 1997 have in \textbf{common} with gen z who born after 2010 ?\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Michael Anderson that's what I said what first 62 born have in \textbf{common} with 46 born  same with 1997 gen z born have in \textbf{common} with gen z born 2010  just because. They have \textbf{nothing} in \textbf{common} doesn't mean they are not in sane generation. The older we get less we have in \textbf{common} with younger but ' generations ' defined by year of birth not who had \textbf{common} with who\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}6/71 & \cellcolor{green!5}8.451 \\  \hline
  \cellcolor{green!27}\small All 80s born didn't turn 20 untill start of centusry. Term ' millennials ' goes way back it was defined as ' last cohort ' who will graduate high school or come of \textbf{age} at start of Centauri\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Michael Anderson even those born in 1992 graduated high school 2009 or 2010 still early part of centuary. Just like boomers we can divide millennial into older and younger but they are in same generation beside none of 80s born are ' \textbf{old} ' the oldest is only 38 so they are still ' young generation '\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Dr. Honey Trap Bih • Astro  my daughter is 28 also and she's a mixture of traditional and Gen X.  I'm Gen X 47 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I think that's \textbf{common}. I was born right on the crux between Gen Y and Millenials. But I was brought up by a very strict Irish catholic family, wasn't allowed to listen to music, never could watch MTV, wasn't allowed out on my own until I was much older than my peers. So I think there are a lot of people with these cross generational experiences.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Dr. Honey Trap Bih • Astro isn't that \textbf{weird} ! I was born 1990 and I feel like I'm 17 still\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small We are the same \textbf{age} and I don't fit the sterotype ether. Tech changed so rapidly in our early teens that anyone born a few yes after us would have a much different experience coming into adulthood. 86-93 would probably fit better for us.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small I mean if you wanna be proud of being \textbf{old} fashioned/refusing to change with the times go for it\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I'm Z help it's to bright and a 5 yr \textbf{old} just cursed\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Michael Rhone when I say forgotten I mean that they are lumped in to a generation that they have very little in \textbf{common} with... sorry if I didn't explicitly state that...\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small So old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Millenials stop at 1984 a 37 yr \textbf{old} is not a millennial\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Does it matter both are worthless lazy entitled do nothings that live in Parents basements. They are less then men no matter what \textbf{age}. They grow beards and long hair to look manley instead of being men while being ultra sensitve to every thing but not saying anything to anyone's face just going online and acting tough.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small I feel like I am an \textbf{elder} millennial lol. Born in the mid 80's (84).\normalsize   & \cellcolor{green!27}Elder & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Me too be a use I was born before the Millennial and remember the memories as a very Early \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Josh Morl that's not the point you don't call people by their names but instead you call him on millennial and then you categorize everyone as snowflakes or whatever your new \textbf{age} term is\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I think that's when Douglas Coupland, the author of "Generation X", starts it. A lot of older Generation X members are more into Depeche Mode and U2 than Deep Purple and the Who. ;-) They came of \textbf{age} in the early to mid '80s when music changed. They definitely have more affinity for Live Aid than Woodstock, even if they're lumped in with Baby Boomers who are \textbf{old} enough to be their parents.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small +Yvonce' It's like "Goldilocks And The Three Bears". Generation X was just right. We came of \textbf{age} in the '80s and the '90s, decades that weren't too cold and weren't too hot. It's a shame that we went off course after 9/11.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small I'm the same. The only thing I have in \textbf{common} with boomers is that my best friend is one. She's six years older than I am. I totally identify as Gen X.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I get it, I was born in the early 80's, Some put us as the youngest of X and others the oldest of Y. I will never consider myself a millennial because I never heard that name until more recent years and it seems like people use it to bash anyone under 40. Also my \textbf{age} group didn't have internet or cell phones growing up.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Michael Anderson I was born in ‘80 and had internet on our home computer at 12 years \textbf{old}. It was primitive, but I was playing computer games with kids on the other side of the world. It wasn't long before we had AOL, and in high school I was browsing websites and interacting with people on AIM, message boards, chats, etc. We didn't have internet in the first half of childhood, but we did the second half...at least I did. Cell phones didn't come along until I was a \textbf{senior} in high school, so you're right about that. Still, I don't remember much about the 80s and consider myself a 90s kid/older Millennial. I think Gen Y probably is the better term.\normalsize   & \cellcolor{green!5}Old, Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/122 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small I don't think my generation has been named yetEdit:Nevermind, I'm Generation ZMy generation is pretty much defined by technology. I'm pretty sure the \textbf{age} range is 12-24\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small KyleeWasBored . . We grew up playing outside and we remember how to have fun without tech and the same time with tech we had a balance when we was kids the idk gen is \textbf{weird} 2006-2012 they never go outside without phones and all them had phones in 4th or 3rd grade not all but mojerity them do me being in 9th grade i didnt get my phone till middle school like alot of my peers 6th or 7th grade even 8th its a shame tho atleast we grew up with going outside with friends anf same time with tech but mojerity kids didnt have phones we used game consoles and computers\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small KyleeWasBored . . There are quite a lot of differences between millenials(my gen) and gen z.  I think us millenials are the last generation that knew to run around outdoors without some gadget...then again, obviously as we didn't have gadgets in the 80s and very early 90s!!! Gen z folk don't know what life was prior to \textbf{common} uaage of the internet. It is sad.  It has made them grow up so frivolous and idiotic for the most part.  Technology is not all good. There is so much bad.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small Bright side im going to say this again,can you make a video about a creepy human from whatsapp called "Momo"it's about a girl who responds with disturbing images for those who messages her. I want you to solve this mystery because you are very inspiring and smart. Please find evidence from google and make it like a story...i'm helpful enough to tell you some evidence about momo.She has \textbf{black} long hair,a wide smile,big ears,and a bigg head.Im warning you bright side,if you text her you don't feel like sleeping.Another great evidence is that she is a professional at stealing personal information(Also why you shouldn't call her or message)Im also warning subscribers..i want you safe...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/114 & \cellcolor{green!5}0.877 \\  \hline
  \cellcolor{green!27}\small Generations are \textbf{weird}, guys. People born from the mid-90s to the early 2000s (2000-01) are on the cusp of 2 generations. So whichever one u identify with more is the one u belong to. Case closed\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@watergod 83 My thought exactly. I believe kids born ~1995-2000 are the \textbf{transition} between the two generations, just like the Xennials (those born between gen X and millenials)... So let's make the Zennials (gen z and millenials) a thing !!!\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I am 23 years \textbf{old} and i turn 24 in 1 month so what am I ?!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Based on \textbf{age} grouping you'll considered the younger part of gen Z. Only way to be considered gen I if you turn 24 before Jan 1, 2018. But then again. Since your right in the (mostly) middle. You can choose Y or Z\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small CeddieCed yes. My daughter was born in 1990 and she's not a spoiled \textbf{brat}. She's self sufficient and works hard every day ✌🏽\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Donghoon 2 you are younger than my youngest sister, she is 14, she was born in December of 2003.  y'all making me feel \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small We r all human no matter \textbf{race} \textbf{nationality} \textbf{ethnicity} religion \textbf{gender} and generation\normalsize   & \cellcolor{green!27}Ethnicity, Gender, Nationality, Race & \cellcolor{green!27}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!27}4/13 & \cellcolor{green!27}30.769 \\  \hline
  \cellcolor{green!5}\small But its true that people act different depending on when there born. Were all human that is true but we have different personalities. which is why you might get along with someone younger or older. I personally cant get along with my own \textbf{age} cause most act like children (does not mean they are all like that)but my preference is with older people.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Thuan Doan Haha indeed, that's important but im homeschooled and hardly get out much and most of the time if i do meet people my \textbf{age} they end up to be pretty rude and judgmental. I have a big family and they are older then i am so i get along with that kind of group..somewhat XD (also the people my \textbf{age} have different attitudes. I did not grow up in a school life format.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/75 & \cellcolor{green!27}2.667 \\  \hline
  \cellcolor{green!5}\small Hero of Time true. I get along with a few my \textbf{age}, the rest I get along with people several years older than myself.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small evie shamrooney Plus i love hearing the older people's points of view, their experiences and their life advice. That's something i won't be able to get when talking to someone my \textbf{age} cause they are still growing up themselves.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I hope Gen Z doesn't become like millennials when it comes to politics. Those entitled, lazy, angry hippies almost elected \textbf{crazy} Bernie and his policies!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Beep Beep Imma Dragon Also more degrees doesn't mean more jobs, some degrees aren't created equal. Some are useless and do \textbf{nothing} to help the growing demand of the job market. Jobs in the STEM field will always be in demand due to innovation and technology.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small I'm born in 1996. I identify as part of the millennials for sure, but I am reeeeally close to the boundary. Frankly, I don't see too many differences between the generations, but that might be because those that belong to the next generation are almost the same \textbf{age} as me.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small According to the Internet, there's \textbf{nothing} good about being a Millennial. So there's no way you could have adopted anything beneficial from being a Millennial.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Kitten Doe Kitten Doe I lean more right wing in politics (more capitalist) and definitely don't feel entitled to anything.. i'm living on little right now to better my financial situation down the road; avoiding the rat \textbf{race}.. the trait I hold that can be said to be more millennial is doing well group oriented.. but only as long as they're like minded.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small 1995/96 are awkward years to be born cause people like us can feel too young to be part of the 'og' technology crowd who had the tiny cream-colored \textbf{apple} computer boxes and played Atari, but are too \textbf{old} to have had technology fully immerse us in our formative years (aka, ages 5-10). I like to say that we grew up during technology's awkward 'teenage' phase XD\normalsize   & \cellcolor{green!27}Apple, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small The1nvisibleJeevas No VCR players in cars.. but I did have cassette tapes I'd play in my parents \textbf{old} vehicle as a kid\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Well that's because a generations qualities are always decided by their early years. I was born 1994 which technically makes me a generation Y but to be honest I'm more of a part way \textbf{transition} between Y \& Z.\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Ryan And that's OK these \textbf{age} groups are so arbitrary. Seems you take labeling too seriously\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Me too, not telling you my age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I'm 25782589072598725987 year \textbf{old} kid.Choose a number.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Air Elegant - \textbf{Nothing}. End of the world.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Techno- space explorers.. Gen A for Generation \textbf{Alien} life.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Air Elegant generation alpha the ones below the \textbf{age} of 13 right now\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Gen Zero\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Generation now I know my abc\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Nothing. Blank Space.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Jacob Harper I thought it began after gen z ended because my sister is only 7 months \textbf{old} but I'm 13 so we aren't in the same generation\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@WhoKnowsWho that's a great \textbf{transition}....what are the parameters?\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Probably more space exploration. Or absolutely \textbf{nothing}, and probably turn out like baby boomers just with phones.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Air Elegant \textbf{nothing}. It's over.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Fuckboy \textbf{thot} generation\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Nothing hence "z"...the last letter..\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Nothing - End of the World !\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@AIチャンネル Do you think Gen Z can go through this changes. I mean can we find a cure for aging and other diseases in our lifetime. I dont want to die from cancer or \textbf{old} age\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small my generation is generation MI which stands for \textbf{Mental} Illness where we are born with incredible curiosity to explore and ended up being shunned by the world to the point of \textbf{mental} breaking .... our most famous trend we tend to commit suicide very often specially after we realize how  worthless living is\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small UNLEASHING POTENTIAL - PSYCHOLOGY VIDEOS i am gen z but act like a millennial 😂(edit actually there is no specific date but millennials can also be born into the early 2000s me I think (1981-2002 ) can still somewhat be millennials  since all the \textbf{old} generations have 3 and a half decades like gen x 1965-1980 it has 3 decades in it 60s 70s and 80s I think gen z might be people born from 2003-2021 but there is no specific date )\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small Bart Simpson Pew Research and most credible sources are starting to solidify the start date/cusp of Gen Z as 1995 and forward. There is \textbf{ZERO} agreement for a start at the 2000s, that is your own input because you are probably born 00-02 and want to be a millennial? Either way, you're wrong. It is essentially fact Gen Z starts in 95 based on observable changes, regardless of your feelings.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Ekaspreet Singh literally \textbf{nobody} cares\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Most sources I've visited say 1981-1995 . With 1995 being the cutoff, so I guess since I was born in 1996 I am a very \textbf{old} Generation Z lol XD.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I am an \textbf{old} generation z. You lots better show some respect to your elders SMH\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}95 & \cellcolor{red!27}95/118538& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Apple, Indian, Red & \cellcolor{red!5}16 & \cellcolor{red!5}16/118538& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age, Ageism & \cellcolor{red!27}194 & \cellcolor{red!27}194/118538& \cellcolor{red!27}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Senior, Elder & \cellcolor{red!5}240 & \cellcolor{red!5}240/118538& \cellcolor{red!5}0.2 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Weird, Mental, Crazy, Lame, Loony, Freak & \cellcolor{red!27}48 & \cellcolor{red!27}48/118538& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black, Monkey, Colored & \cellcolor{red!5}18 & \cellcolor{red!5}18/118538& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Brat, Nobody, Zero & \cellcolor{red!27}88 & \cellcolor{red!27}88/118538& \cellcolor{red!27}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Snowflake, Red, Communist & \cellcolor{red!5}18 & \cellcolor{red!5}18/118538& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}2 & \cellcolor{red!27}2/118538& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - European or anti-Europeans}  & \cellcolor{red!5}Brexit & \cellcolor{red!5}1 & \cellcolor{red!5}1/118538& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}Transition & \cellcolor{red!27}15 & \cellcolor{red!27}15/118538& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!5}Dot & \cellcolor{red!5}3 & \cellcolor{red!5}3/118538& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - American}  & \cellcolor{red!27}Yank & \cellcolor{red!27}2 & \cellcolor{red!27}2/118538& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Lump, Bald, Thin & \cellcolor{red!5}5 & \cellcolor{red!5}5/118538& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Immigrant, Alien, Nationality, Nationalism & \cellcolor{red!27}6 & \cellcolor{red!27}6/118538& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Racist, Race, Racism, Ethnicity & \cellcolor{red!5}10 & \cellcolor{red!5}10/118538& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Jewish}  & \cellcolor{red!27}Abbie & \cellcolor{red!27}1 & \cellcolor{red!27}1/118538& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}ABC, Slant & \cellcolor{red!5}4 & \cellcolor{red!5}4/118538& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Fag & \cellcolor{red!27}1 & \cellcolor{red!27}1/118538& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Hun, Jerry & \cellcolor{red!5}5 & \cellcolor{red!5}5/118538& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Dame, Gender, Woman & \cellcolor{red!27}8 & \cellcolor{red!27}8/118538& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female age and physical appearance}  & \cellcolor{red!5}Witch & \cellcolor{red!5}1 & \cellcolor{red!5}1/118538& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Southern European}  & \cellcolor{red!27}PIGS & \cellcolor{red!27}1 & \cellcolor{red!27}1/118538& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho, THOT & \cellcolor{red!5}2 & \cellcolor{red!5}2/118538& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Social Class - Working class;Ethnicity - Native-American;Age - General;Age - Over 65s;Physical Identity - Physical (and Mental) Impairments;Ethnicity - Black;Age - Youngsters; Ideological and Political Identity - General;Religious Identity - Muslim;Nationality - European or anti-Europeans;Sexual Identity - Transexuality;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Nationality - American;Physical Identity - Physical Features;Nationality - General;Ethnicity - General;Religious Identity - Jewish;Nationality - Chinese;Sexual Identity - Male homosexuality;Nationality - German;Gender - General;Gender - Female age and physical appearance;Nationality - Southern European;Gender - Female sexuality;%.

\item The percentage of hate speech related words is 0.6614.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 784/5469 occurences of hate speech related comments.\end{itemize}\end{document}