\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_295.json :}\newline \par\Large\textbf {Title: \large  Gypsy Travellers: A Life On The Run }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Most sensible comment from that stinking \textbf{gypo} cunts mouth was about the \textbf{r\textbf{ed}} button and bombing them to death\normalsize   & \cellcolor{green!27}Gypo, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small \@Farzana Haq A tinker is generally a tin smith who makes pots and pans, generally associated with \textbf{gypsy} gangs, sometimes also called Knackers, chavs or pikeys.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@x y my favourite \textbf{p\textbf{ikey}}, just back from robbing a \textbf{pensioner}.\normalsize   & \cellcolor{green!27}Pensioner, Pikey & \cellcolor{green!27}Age - Over 65s, Nationality - Irish, Social Class - Working class & \cellcolor{green!27}3/11 & \cellcolor{green!27}27.273 \\  \hline
  \cellcolor{green!5}\small Just because you were raise different don't mean you have to discriminate. Gypsys are people as are gorgers so just show some respect will ye, not every \textbf{gypsy} is bad\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I see so many offensive comments towards travelers. You ever heard the saying don't stroke every folk with the same brush. I come from a travelling family myself, to understand the culture, the real culture. You never will. Non of you are open minded which is why true travelers stay private and away from house people ‘gorgers'. It's trying to keep up \textbf{old} traditions. Which stems from respecting the life style your grandparents lived. I, myself and my siblings have been brought up in a house for many years now and have gone to school, college. And work. The \textbf{old} traditions won't stay alive much longer because everything's moving up in life. However have you ever sat and thought to yourself that if we move into a house and live the life you will, you still won't accept us. It's taken many years for us to be accepted in our neighbor hoods. We had so many hate crimes happen, me a young 12 year \textbf{old} having drunk women try and attack me because I'm a ‘smelly \textbf{gypsy} girl'. And you wonder why we want to fuck off and live our own peaceful lives. Because we don't get judged. We had to put up with so much. Just so my 11 year \textbf{old} sister and young cousins can live a peaceful life and go to school. I have to withhold the abuse so eventually you all give up and give the younger generations a chance. I'm 19 now. I smile and say hello to my now neighbours who used to hurl abuse to me, a young child at the ages of 15. Have you ever thought about the effects this had on me, wondering why I didn't want to go to school. I was riddled with anxiety and didn't want to leave my home. The bullying never stopped until I left high school and went to a college. I will say this, my family never once started trouble but we finished it and defended ourselves. My great grandad was a well respected  man, who didn't believe in thieving or lying. Strong catholics at that. And because you all seen something on tv you presumed we was like what you seen on tv. Now, imagine if this was any religion or other culture put through this. You'd stand up and defend them. But us gypsys get no one defending us all our lives we will have to defend ourselves.\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}5/407 & \cellcolor{green!27}1.229 \\  \hline
  \cellcolor{green!5}\small flip inheck \textbf{nothing} better to do again aye\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I am a \textbf{traveller} and we love stealing\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small When the \textbf{traveller} said he could not live a "settled" lifestyle it is no different to a burglar saying he could not stop stealing and get a proper job. Criminality is not a "traditional way of life". Not an acceptable one.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small What a crock of shit, the same thing happens here in America in Democrat run cities, the leftist loons encourage it, enable it, and love the havoc it creates, it gives them more victims as they attempt to change the populous of a \textbf{nation} into needy beggars.No thanks liberal moon bats, lol!\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small That poor girl is a hard 19! This is sad. And I get where the locals are coming from. I can imagine campers rolling up at the local park where my children play. That would \textbf{tacky} n disrespectful. I don't pop a tent on my neighbors yard!\normalsize   & \cellcolor{green!5}Tacky & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small They're rather strange folk. Commonly referred to as gypsies but don't confuse them for Roma gypsies. Irish travellers/Pikeys are a menace to communities, they expect the country to accommodate them but give \textbf{nothing} back. They came over from Ireland a several hundred years ago and have been here ever since. I'm still holding out hope that we can send them back.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Pikeys are known to perform cash in hand and scrap metal jobs, although they're also well known to steal. Theft is a massive problem when dealing with Pikeys. Because they pay no rent, they often have quite abit of money despite their destitute circumstances. Irish Travellers tried to rob my grandfathers house, a couple days after he had sadly passed. They're opportunistic and I would discourage getting friendly with them, they'd rob you \textbf{blind} and skip town.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small Lauren Cooper Why do they live like this?  What do they do in general?  Do they work?  What is their goal in life?  This \textbf{Yank} (US citizen born there, White female who can't say American anymore.)  wants to know.\normalsize   & \cellcolor{green!27}Yank & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small then benagcz Would you please tell this \textbf{Yank} what it is that they do to survive?  How do they earn money?  Why do they travel?  Where are they from?\normalsize   & \cellcolor{green!5}Yank & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Will everyone please be kind to the gypsies? They were the number one \textbf{ethnic} group on Hitler's death list. Give them a break. Hehehe.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small All \textbf{Ethnic} Groups Are Equal. All Cultures Are Equal... Except The Ones We Don't Like. That Hitler had some right good ideas. Just burn the caravans. It's like burning hornets' nests. Rathkeale would be a great testing site for biological weapons.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small A 'proper' British man would never marry a \textbf{P\textbf{ikey}}. Shag? Yeah. Marry? No chance.That's always going to be hanging over your own family's head, whispering and gossiping about the \textbf{gypsy} family ties. It's not something you'd want to wish on your children.\normalsize   & \cellcolor{green!27}Gypsy, Pikey & \cellcolor{green!27}Ethnicity - Roma, Nationality - Irish, Social Class - Working class & \cellcolor{green!27}3/43 & \cellcolor{green!27}6.977 \\  \hline
  \cellcolor{green!5}\small There are mutiple sites where i live all owned by travellers themselves. They dont do \textbf{nothing} wrong apart from the odd drag \textbf{race}... but i like the cars\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small 19yrs \textbf{old}. Looks like 49yrs \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Who's here purely to \textbf{slag} off gypsies in the comfort of the comments section.\normalsize   & \cellcolor{green!5}Slag & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I'm a nine year \textbf{old} \textbf{gypsy} girl and reading these comments makes me feeling like I'm fading from life\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Here ✋Granted, I \textbf{slag} off everyone. Gypsies aren't necessarily special.\normalsize   & \cellcolor{green!5}Slag & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Nobody would have an issue with them its just the condition in which they leave the place they parked on, trash all over the place dirty nappies, food everything under the sun its disrespectful and thats why people have an issue with them, its not hard clean tf up\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small We r not called \textbf{Gypsy} travellers u slow handicaps we are Irish travellers and very proud to be 🇮🇪\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small There is no lower human life form that a filthy gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small She's a filthy \textbf{p\textbf{ikey}} she's in no way fit\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small I'm an Irish \textbf{traveller} live in a house very clean not like them\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small We don't like you as you steal and leave mess behind. You are \textbf{nothing} but crooks. You make me sick.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small You lot need to stfu we can do what we want we ain't \textbf{nothing} none off yous\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small They're technically English but their accents are \textbf{gypsy} Irish cause obviously they're living around other gypsies with \textbf{gypsy} accents\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Bit late, but I am a \textbf{traveller}. My family have lived in the same place for 60 years, all of my family are very well educated and own their own businesses. I myself am going to study at university next year. I beg you, don't let videos like this and tv programmes define what you thing about us, because it only shows the worst of us. Some of us have the best intentions, clearly these people don't. They DO NOT represent us all.\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small I'm kinda retarded when I heard \textbf{gypsy} I pictured like they whisper something and it happens\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Dirty gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Pity there is no \textbf{gypsy} virus to wipe them all out,  That jimmy is a good looking man about town ... 😂 OMG i cant understand a fecking word the twat said\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I don't know how I've lived all these years and know \textbf{nothing} about "Travellers".  I've been watching shows about Gypsies and Travellers in America and I've felt very sympathetic toward them.  I guess my thinking is just "live and let live". But I've never had any kind contact with them and when I read all the comments about what happens when groups of Travellers come to town and I don't know what to think.  It seems to be a very interesting subject.  Can anyone recommend any accurate and balanced documentaries that I could watch to learn more?  I don't mean the "reality TV" kind.  I really would like to know more about these people, their history and lifestyle etc.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/119 & \cellcolor{green!27}0.84 \\  \hline
  \cellcolor{green!5}\small I work at a bar in Germany and one night an Irish \textbf{traveller} family arrived when my coworker was working. She told me the kids started running throughout the bar like it was a playground and the one kid set some tabs on fire with a candle. The mothers excuse was that the kid has ADHD and can't focus properly or some bullshit like that. Then my coworker kicked them out as it was 10pm and kids shouldn't be in the bar at that time anyways.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small Why don't all you haters go and fuck your self they are gypsys it's there way off living with it and so what if they go to a public park they get destroyed almost every year to make new house so why don't you all fuck off and mind ur own business you cheeky twats they should be aloud to be free and do what they want you wouldn't treat a dog the way you treat these telling them to fuck off \textbf{nobody} stands on your garden shouting fuck off to you so what gives them the right to say it to them !!!! They should just leave them alone 🤬😡\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small Nobody tells me to fuck off in my garden because I own it. If I decided to plonk myself on somebody else's.. that would be a definite outcome!\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small SLACKSLANGS BUSTY GIRL,, TRY BE A REAL \textbf{WOMAN} LITTLE GIRL,. WE NO YA MAMMA LOVES CORRI LOL\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small aaand let the \textbf{racism} begin - there is a difference between cussing people out and offering solutions\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Read Mikey Walsh's autobiography "\textbf{Gypsy} Boy" - interesting comments on how the Irish Travellers have taken over the original Romani gypsies and ruined the \textbf{gypsy} image.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small i got my drive block paved by some gypsjes and i said when they came i wanted a good job and not some \textbf{traveller} to do it. I had no idea they were as of how polite they were at then end of the week it had finished and the boss said before the job you told us you did not want travellers to do your drive but we just did. I was so surprised especially after all the hatrid you hear about them just goes to show it is the person not what is attached to them!!\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small One of my best friends at school was a \textbf{gypsy}, (kinda). Her mother fled her abusive husband and got fully kicked out of the whole thing. She took her 2 year \textbf{old} and just bolted.She ended up working as a waiter in London in the 1990's, where she meet her second husband. He's Australian and he made an absolute fuckton in the early 2000's tech boom. This was after my friends mum had married him and moved with her daughter to Australia. So anyway my friend grew up here and never knew her mums family or anything, but eventually her family found out about them. And let me tell you, travellers might talk a big game kicking people out and only marrying within their group, but the minute they found out what my friends step-father was worth (like I dunno defiantly tens of millions) they disregarded the whole thing. They where obsessed with moving here and becoming "Part of the family".\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}2/161 & \cellcolor{green!27}1.242 \\  \hline
  \cellcolor{green!5}\small Heres a radical idea ! How about give them their \textbf{traveller} sites they are entitled too? just an idea local council people!!\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Criminal councillors broke the law by not providing proper sites for travellers, should have been punished.  Most romanies are decent people, most of the so-called law-abiding majority are repeat dangerous criminal offenders, yet are such deluded and/or pompous fools they don't even recognise it. Most romanies value cleanliness, are often shocked by the filthy habits of the settled community. Many non-travellers do fly-tipping, including on sites just vacated by travellers. Most non-romanies are stereotyping racists.  Massive numbers of romanies, including little children, were killed in concentration camps by the vicious non-romany butchers supported by millions of their \textbf{racist} ilk; the Porajmos-holocaust that is rarely mentioned. No doubt millions of racists would want the same extermination today; that shows the character of huge numbers of non-romanies; fascist thugs like those the world war 2 "finest hour" heroes fought against. Romanies and travellers are persecuted and treated disgracefully, as ever- kind, responsible and decent ones attacked, spat on, insulted.  The land should belong to us all, instead of millions of acres belonging to the criminal rich, the rest with nowhere to stay.  The \textbf{racism} of the settled community has caused the problems they now complain about- it could all have been very different, but hatred breeds contempt in return. Shame on all racists and hourray for all those decent people who simply want to live a peaceful nomadic lifestyle but are subjected to so much disgusting harassment and vitriol from hateful and narrow-minded hypocrites\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/242 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small I'm a gypsie and I would not call them the same they probably do steal and break the law and leave mess we're ever they go and trust me we don't all have big \textbf{fat} gypsie weddings were not all rich or snobby some of us are actually very well educated and fun fact all u country people way back years ago we're actually handing ur kids to gypsies because u could not feed them or look after them so don't go saying they don't look after there kids we don't all scam people out of money and steal ur cars and stuff out ur shed so please respect us and u might get some back.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/116 & \cellcolor{green!5}0.862 \\  \hline
  \cellcolor{green!27}\small Bring me ur \textbf{gypsy} tears\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I look in the comments in this and I'm disgusted with how you people can portray an entire community of people with the effects of only a handful most travelers u will most likely meat u will never even know they were travelers and the people u think are travelers are those those who try to copy us and it's disgusting to see in the modern \textbf{age} generalisation to the decree of what I see out side my community and I'm batheld at the idea that those who say these are actually adults and to those who do not do what the idiots in the comments do I applaud you\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/110 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small I am attracted to Bohemian \textbf{Gypsy} \textbf{Woman}. They are the best.\normalsize   & \cellcolor{green!27}Gypsy, Woman & \cellcolor{green!27}Ethnicity - Roma, Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Pikey scum deserve to be round up and shot\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Pikey scum\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/2 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Put'em in camps! And I don't mean holiday camps! One of them attacked my mate (Whose a Full-blooded French/Spanish Romany) In Cornwall a few years ago! My mate gave him a proper pasting, fists, no weapons........He comes back team-handed, all carrying weapons.....Nearly killed my mate. But they were caught by the Local Police almost right away! Loads of local Cornish people appeared as witnesses! With fucking \textbf{p\textbf{ikey}} scum trying to intimidate them during the trial! The local Fishermen followed them back to their vehicles and beat the shit out of the men and older boys.......They didn't hang around! The defendants all had warrants for theft, ABH and twocking....All were held on remand and all received custodial sentences........The two main cunts got 11yrs and 6yrs for Attempted murder!!! Cunts!!!\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/128 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small I once went out with a \textbf{traveller} girl it was amazing she let me play on the waltzes the Dodgers and the next morning she give me a gold fish to take home\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Why are they all fat\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Some nasty people -  they dont want to pay taxes -but happy to go to our hospitals and \textbf{doctors} -  - feel sorry for the kids who don"t know any different - most are thieves - -\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small I'm a full blooded \textbf{gypsy} my whole family are too they don't  steal or litter that much and they all went to school so go fuck yer self ya wee skeety slags Scotland 🏴󠁧󠁢󠁳󠁣󠁴󠁿\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Look at this clip where they try and 'normalise' them and their culture. The fact is that the vast majority of them are thieves. They care \textbf{nothing} but for themselves and will rob, steal and damage other people's property. As that inbred reprobate said "I can't see myself living the 'countryman' life". No interest in integrating. A genuine burden on our society. I only long for the day where there is a crack down on a National scale of these vile criminals.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small money \textbf{race} U Hate Niggaz Cause I'm A Nigga\normalsize   & \cellcolor{green!5}Nigga, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small How do a bunch of homeless people stay so \textbf{fat}?\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small If you built a \textbf{p\textbf{ikey}} from the ground up, he'd look like Jimmy.\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Thieving , disrespectful , \textbf{dumb} CUNTS !!!!!Now I thought ya average \textbf{p\textbf{ikey}} could have a fight , I've had it with 4 different lots and if they punched as fast as they spoke they'd do well , in short there fuckin useless cant really fight for fuck ......If you should happen to see one of these wankers pull a gun and use it , lets clean the country up of these CUNTS !!!!!!Fuckin scum !!!!\normalsize   & \cellcolor{green!27}Dumb, Pikey & \cellcolor{green!27}Nationality - Irish, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}3/78 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small You're fighting on their terms, they don't follow the law and neither should you. Pikeys don't ring the police on you, leave \textbf{nothing} to incriminate yourself.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Pikey wars pmsl🤣theiving inbred scum🤢🤢🤮😷☠☠☠☠\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small I've always tought my sons to treat people how they want to be treated. Last night I was walking with two of my sons to fetch a 3rd from cubs, on the way two 'travellers' tried to humiliate me by calling into question whether or not I was the owner of two functioning testicles. To be honest, I was confused at first, as I presummed by their voices that they were suffering some speech, and or, \textbf{mental} malady. They took my apparent confusion as a win, and sauntered off to intimidate the staff at the local shop.My kids were full of questions! Suffice to say I simply told them that travellers are a proud and noble \textbf{race} who felt so threatened by our walking past them, that they had to strike first. I then reiterated that diversity is our strength, and that our ancestors probably enslaved their ancestors, so really, it's all we deserve.My kids asked why I didn't stick up for myself, a difficult one that, I just went with the truth, and said, "The noble travellers love to fight people, any people, as its part of their rich and diverse culture. However, if I defended myself verbally, then they would see that as a green light from me that I wanted to partake in a fight. Then, if the one I started to fight with looked to be in any way losing, his companion would then feel compelled to join in, to guarantee my defeat. He may also call his nearby relatives, and they would also feel that it would be in everyone's best interest for them to ensure that I spent the next few days in hospital".So suffice to say, I'm sure there are some travellers who are great, unfortunately I've yet to meet one, or indeed, anyone who has had a positive experience with one. This programme virtually celebrates their existence, each syllable dripping with patronising admiration.\normalsize   & \cellcolor{green!5}Mental, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/324 & \cellcolor{green!5}0.617 \\  \hline
  \cellcolor{green!27}\small I'm a \textbf{gypsy} but I live in a house my parents work and pay taxes and seeing this is just such a bad representation of out culture I swear I've never stole anything in my life I was taught to be an honest Romani, I understand what you all mean and as a \textbf{gypsy} I apologise for the bad things the minority do xx\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small If they didn't leave there shit everywhere I wouldn't give a fuck but there so fucking annoying they once destroyed a fence to get on fucking grass you ass hole and then they never got in trouble wtf I am sorry but they piss me off. The kids are the worst to once we where in the carpark with my mom they asked for the trolley while my are food was still in it my mom said no but they tugged it out her hands twisting her wrist and running away with are food police fucking did \textbf{nothing} sorry  but \textbf{gypsy} are assholes\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small American and I have never seen gypsies here. Thank God. I know we have them, as there was a story about some Travellers in the Fort Worth area who were scamming \textbf{old} ladies by "fixing" their roofs. Most of them would get shot if stealing on private property. Maybe that's why they stay in Euroland.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Send the f..kers back to Ireland thieving twats don't belong here they was robbing the \textbf{old} man across the road from me £4000 quid for a  small back yard now it's full of weeds now I was constantly ringing the police to stop them going round and wanting more money of the \textbf{old} man any wonder no one wants them here.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small I bet my Mitsubishi L200 is on this siteThey stolen my car and police found it via tracker on a \textbf{gypsy} site, 14 days later I got it back with £1200 repairs and had the car 2 days before they stolen it again they found the tracker in a lay-by without the car and I never seen it again\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small well the title of the video is wrong for one and most of the comments are wrong too real gypsies dont leave tons of crap where they go like mikey driver insists without actually seeing any evidence of this in the video there is a great difference between a true \textbf{gypsy} and the so called travellers we have today that live out vans and do leave crap wherever thay go\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Whoa! \textbf{Gypsy} girls are so hot and stinky at the same time. Borat, was known to slutting \textbf{gypsy} women. He has a sluttery for any airy dairy area'd girls. The \textbf{gypsy} men also know of slutry, their took-isz protrude for fun and laughed as jokey times. The \textbf{gypsy} men when no longer laughable, look witch-like. Borat and his poops, hunt \textbf{gypsy} widtches and mustard bread sandwhiches to keep the hunt on. The slutry is safe, by the protection of the \textbf{gypsy}-witch poop walkers.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}5/83 & \cellcolor{green!27}6.024 \\  \hline
  \cellcolor{green!5}\small I once made the mistake of befriending a \textbf{traveller}, \textbf{fat} bitch turned on me for no reason.\normalsize   & \cellcolor{green!5}Fat, Traveller & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small I am a \textbf{gypsy} and we live in a house my mum used to live in a caravan but she said she rather be in a house\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Dirty \textbf{p\textbf{ikey}} breeders go and get a proper job.!\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small 19 year \textbf{old} Helen ..... bonnie girl !   Pity she will turn into a \textbf{fat} ugly cow like the rest of them 😟 ..... meanwhile good to practice on 😂\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Why do they not make a document  were \textbf{gypsy} come from then make one were Irish travellers come from because no one knows the difference but us and many people are not \textbf{gypsy} on this project tv not from romani culture\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small I'm a \textbf{Gypsy} but I live in a House\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I am not a \textbf{Gypsy}.But the way people look down on them is horrible.Most of them are hard working people.It makes me feel ashamed of being English the way they treat these people.Instead of councils spending tax payers money constantly moving them on,would it not be better to build more sites for these people to live on.I'm sure the Travellers would not object to paying rent council tax and water rates.The children would be in regular schools and gain a proper education.Our corrupt UK Government spend billions of pounds a year on immigrants who enter the Uk every day without passports or paperwork.But they don't look after our own people.And then have the cheek to ask us not to be \textbf{racist}.But the corrupt Government and councils are \textbf{racist} themselves to our British travellers.This country is on it's knees with the immigrants they are allowing in.The UK is the only country i know of that let people in without passports.Its a joke when they treat our own people this way.The travellers are not invading our country.They are simply wanting somewhere to live in their own country.England Scotland Ireland and Wales all form the UK....I am sure it will not be long before the corrupt UK Government and councils will start building new estates to house our illegal immigrants,which will no doubt be in rural country side.And give them state handouts and new schools.There are thousands on our streets already..HOMELESS ..Yet they are still allowing them in in their droves...But they won't build new sites for our own travellers or our own homeless people..The damage the corrupt Government has done to this country is terminal..This country is fucked big time.Give the British homeless new homes and give our travellers the sites they so desperately need.As for the illegal immigrants send them back to wherever they came from...We want our country back and to make it Great again....\normalsize   & \cellcolor{green!27}Gypsy, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}3/315 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small idiot this isnt about \textbf{ethnic}  origins you dimwitted fuck\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dirty \textbf{p\textbf{ikey}} \textbf{gyppo} cunts. Filthy animals I have no sympathy for any of them, I feel they're from the same clan who robbed my friend of his bike and bag with all his money and new things he just bought at knife point around the same place in Croydon!! Trampy shitting in field caravan living dipshit \textbf{P\textbf{IKEY}} CUNTS!!!!!!!!\normalsize   & \cellcolor{green!27}Gyppo, Pikey & \cellcolor{green!27}Ethnicity - Roma, Nationality - Irish, Social Class - Working class & \cellcolor{green!27}5/58 & \cellcolor{green!27}8.621 \\  \hline
  \cellcolor{green!5}\small I'd fuck the nineteen year old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small im a \textbf{gypsy} and proud bitchs\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small All the comments section filled with hate and saying they cause crime and create mess, you clowns need to look at your own 1st and adress your own issues. The travelers have balls something you lot dont, and they have family life and loyalties something you folks no \textbf{nothing} about. Stop the hate and jealousy because they dont live the same shit lives as yous\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Reading all the top comments from British people is \textbf{crazy}. 😂😂 I'm even pronouncing everything with an accent in my head. 💀\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small i'm a rumney \textbf{gypsy} and i can reassure you, not all of us are like this. i'm a american rumney, these english travellers are refs. not even real rumney.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Romani!!! .. you illiterate yank\normalsize   & \cellcolor{green!27}Yank & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Dirty \textbf{p\textbf{ikey}} bastards\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small Not being funny but whenever I see a \textbf{gypsy} site there's so much shit and rubbish all outside as you can see in this video, it's also annoying for the public they don't want a bunch of caravans in a nice park. Just go buy some land\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Their dirty tramps they don't look like gusty travlers they all look like tramps the way they dresss and their fake tans and make up needs sorting out proper \textbf{gypsy} travelers don't dress like that and plus they don't leave the kids naked and what the hell hair cut was that on that poor baby child,\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small irish accents, definitely not \textbf{gypsy} then. irish traveler yes. but not \textbf{gypsy}. don't be fooled by these tv shows people.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I love  Irish \textbf{gypsy} women. So raw, yet beautiful\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I imagine incest is \textbf{common} in these communities\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Nothing worse than gypsies, horrible people\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small A \textbf{gypsy} stole my dog once thankfully I got him back\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Let me correct you some scumbags stole your dog ,it would have been \textbf{racist} if you said some \textbf{black} man stole your dog\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Mysterious Or not? How's it \textbf{racist} to say a \textbf{black} man stole something? Would it be \textbf{racist} to say some \textbf{Indian} stole it? Some Hispanic man? A white man? It's just providing details. Dickhead. We can't describe people anymore without you easily offended pussies claiming everything as \textbf{racist}? Fuck off\normalsize   & \cellcolor{green!27}Black, Indian, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}5/50 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Zohana \textbf{Banana} you fecking muppet ... 🙈\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Zohana \textbf{Banana} i think you're cool\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small There's no \textbf{gypsy} anymore\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I am \textbf{Gypsy}, never committed a crime. Even If I did, I wouldn't care, as it's the System that steals from us.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Send them to \textbf{gypsy} island in the pacific where they can all live happily ever after\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Absolute vermin. Bet that 19 year \textbf{old} has had a 3some with her mum and dad the bunch of smelly dirty cunts. Burn em all make the world a better place.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Gippo little bastards go round robbing people\normalsize   & \cellcolor{green!5}Gippo & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small i am a \textbf{gypsy}. I always regret watching videos like this and allowing myself to read the comments. In all cultures there are variations, these here are irish travellers.. and yes, most are tyrants to even us romany gypsys people. But true blood gypsies are truly not disrespectful, dirty, tax avoiding people.   We won't steal your things, we'd rather go without than have had to steel it. If our family and friends new we stole from people, \textbf{nobody} would want to live around us or would he embarrassed to say they know us. We are proud, clean, moral people, are culture is not of this \textbf{age}, but we love it and like to embrace it. It seems nowadays, you can be what you want, girls can be boys, boys can be girls, but you can't be a \textbf{gypsy}. i will always understand why we are thought of like we are, when i look at irish travellers in the corner shop, i know it's them tarnishing our reputation and various other bad eggs of the \textbf{gypsy} community. but some are not "all" please keep an open mind when you meet a \textbf{gypsy}, we are just people.\normalsize   & \cellcolor{green!27}Age, Gypsy, Nobody & \cellcolor{green!27}Age - General, Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}6/195 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small as a \textbf{traveller} these comments are very hurtful. lol not all travellers are the same\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small she's not a real \textbf{p\textbf{ikey}}, she pronounced the word 'dog' correctly, she woulda said 'dag' if she was real.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small It's \textbf{crazy} that they have kid's with there family members it's gross.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Those are some fake \textbf{gypsy} them some white bitches\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small deport the vermin post \textbf{Brexit}.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small My first encounter with gypsies was when I worked in my first hotel job as a part-time night auditor. I didnt have to deal with them until it was time to kick them out.....OH MAN. There was shit and trash on the floor everywhere. Literal shit. Found out when I came in one day, that my manager was going to call the cops and kick them out because of the headaches they were giving the rest of the staff and the fact that they were behind on paying their bill. How in the FUCK could you be in a hotel room and have feces on the floor?!?!? The bathroom is right there! The public bathroom was literally 15-20 steps away from the room too. They ended up getting kicked out a few days later. Ever since, I have heard \textbf{nothing} but bad things about these folks which is sad. I hate to judge a whole based on the parts, no matter how many shit parts there are, but damn man.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/170 & \cellcolor{green!27}0.588 \\  \hline
  \cellcolor{green!5}\small The last day's of  ISIS IN SYRIA  LOOKED  LIKE A \textbf{TRAVELLER} SITE  WHEN THEY HAVE  GONE. ITS  A JOKE IN THIS DAY  \& \textbf{AGE} PUT A  STOP TO IT.\normalsize   & \cellcolor{green!5}Age, Traveller & \cellcolor{green!5}Age - General, Ethnicity - Roma & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small That's a hard 19 yr \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small so much \textbf{racism} in the comments smh\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small yk 47 yeah such balls to be stealing off \textbf{old} \textbf{age} pensioners\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small disgusting vicious cycle of \textbf{racism} against travellers and romanies; kindness breeds kindness, hatred and persecution breed contempt\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Gypsy scum\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Paddy o briens family\normalsize   & \cellcolor{green!5}Paddy & \cellcolor{green!5}Nationality - Irish & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small If everyone lived like this the country would be pure mayhem, if everywhere was just a free for all.. people have to earn money to buy land or property.. and its all well and good to want to live for free and just set up home wherever you feel or just claim land but that's not how the world works and the reason a lot of people can't stand gypsies is because not only do they not conform with society so already that would be frowned upon they ruin the land where they stay damaging the grass etc leaving rubbish, crap and even bags of human waste (most recently around a war memorial site) so yeah gypsies don't really help themselves, well they do! But not with other non \textbf{gypsy} communities.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/131 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}\small Helen's a good-looking \textbf{woman}. Her fiancé/brother is a lucky fella.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Not really she's a pikey\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small There's lots of  Gypos near me .... I have a \textbf{gypo} Friend 😂 but she's not as. Bad 🤣\normalsize   & \cellcolor{green!5}Gypo & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small There is a \textbf{gypsy} park near my are and they r there permanently and a bunch of them are being let into my school but they get vexed and offended if u call em gyspys and the teachers av a rught go at yers if u call em gypsys not travellers and my mom is so pissed abt it 😂😂\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small tax is theft, if someone does not take from the state then they owe nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@nunchaku101 yes.. taxation is theft.. but so is using resources others had to pay for under threat of violence by government, when you contrubuted \textbf{nothing}. Laughed at people saying in " Grid Down" travellers and homeless will survive.. nope.. look up the history of pigeons..\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small \@Robert RossI agree with you so go fuck yourself you \textbf{commie} fuck, I take \textbf{nothing} from government, no dole, no free medicines.............Should I pay for everyone else then?\normalsize   & \cellcolor{green!5}Commie, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small My friends holiday caravan was stolen by these \textbf{fat} \textbf{pigs} they need to be shot\normalsize   & \cellcolor{green!27}Fat, PIGS & \cellcolor{green!27}Nationality - Southern European, Physical Identity - Physical Features & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small I don't mind gypsies setting up camp in an unused area and that they pick up their rubbish and don't cause a nuisance. It's a shame that some people taint the name of \textbf{gypsy} culture as they aren't all thieves and bad people but there are that few that give them a bad name\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Group of settled travelers live close to me,about 8 houses,went to school with some of them. Grand ppl. However they're a serious drain on us nearby residents. They live by a park and on a main road in a mini cul de sac,I've seen first hand they're dogs being run over while chasing someone across the road who was simply walking on the wrong side of the path and the dog trying to bite them. Kids get barred from shops and harrass ppl shopping and working all the time. One day I saw one jump up on the counter of a pizza place for a laugh screaming racial remarks. Another time the retail shop I worked in had to be evacuated and staff sent home after there was (with no exaggeration) an all out brawl between two families because someone was wearing the wrong colour,too many of them not enough security and they just had to be left at it . Then at any given time of year at least one of the 8 houses are totally burnt down, constantly being repaired by the council and tax payers and another burns down in a \textbf{weird} cycle. Most are lovely in my experience,but everyone just avoids them with well founded reasons. Respect and manners cost nothing\normalsize   & \cellcolor{green!27}Nothing, Weird & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/215 & \cellcolor{green!27}0.93 \\  \hline
  \cellcolor{green!5}\small As a \textbf{traveller} myself I get disgusted when other members of the travelling community litter my family live a rich life\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small As a \textbf{gypsy} myself this is not good because then we get tarred with the same brush.. we always made sure we cleaned up after ourselves when we was stopping or moving\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@Shane s Yeah some travellers are wealthy, I knew \textbf{traveller} that owned a gated community for 65s and over and even owned his own helicopter some a wealthy as fuck.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@kiera holland I'm a \textbf{traveller} and I can tell you that some travellers are bad people but that's just like other people some bad some good. some good \textbf{black} people some bad \textbf{black} people some good white people some bad white people were all human and you only live once so if some travellers enjoy owning horses or living in a caravan travelling around then fair play that's what makes them happy alot of regular people just live a boring life alot of travellers want to enjoy there life doing things they love\normalsize   & \cellcolor{green!27}Black, Traveller & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Roma & \cellcolor{green!27}3/93 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small \@the jester I sense a butt hurt \textbf{gypsy}. Let me ask you, do you enjoy living off peoples misery?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I just want the \textbf{racism} towards \textbf{traveller} to be abolished  its not fair and its not right and thank you for reply it means a lot.\normalsize   & \cellcolor{green!27}Racism, Traveller & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Praise The Sun bet you wouldn't say that to a gypsies face you \textbf{pussy} your just sitting home doing \textbf{nothing} with your like and jealous that gypsies have nicer stuff than you ...You keyboard warrior\normalsize   & \cellcolor{green!5}Nothing, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small \@Shane s  \@Shane s  "The reason they have nice stuff" Let me guess why? Because most of it was stolen from \textbf{elderly} and innocent people? If I EVER see you skanky fucks in my house or trying to steal my belongings you'll never see sunlight ever again. Also i was put into psychiatric hospital 4 years ago, so I wouldn't mess with my family either since they know alot of tough people around. Do you know what you call a thieve? A skank and you peeps are well known for it.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small I'm Negan You know that people with chronic depression or bipolar disorder can go into a psychiatric hospital, don't you? So I have no idea why you're using that as if it makes someone \textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Why do \textbf{gypsy} women always have enormous fun bags ?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Proud to be a \textbf{gypsy} 😌\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Pikey\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/1 & \cellcolor{green!27}200.0 \\  \hline
  \cellcolor{green!5}\small Okay \textbf{gypsy} they do what they do everyone breaks the law if you don't got \textbf{nothing} nice to say about \textbf{gypsy} don't say anything at all\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}3/26 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small You just racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@Angie Petro explain the \textbf{racism} part please?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Angie Petro stfu, it's all you clowns ever shout ' you're a \textbf{racist} ' Fck off\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Angie Petro \textbf{gypo} scum\normalsize   & \cellcolor{green!5}Gypo & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Angie Petro How are they \textbf{racist} I-\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Angie Petro How is he FUCKING \textbf{RACIST}?! It's the FUCKING truth so screw your FUCKING head on!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Angie Petro that isn't racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small They are a festering boil on the arse of society. Wouldn't piss on a \textbf{p\textbf{ikey}} if they were on fire.\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@had better days Being a \textbf{gypsy} is much much more than breaking laws. Not all gypsies do. In fact many do not. You don't know them all. Most blend into society very well and live in houses.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Tax is theft \textbf{faggot}, but they do rip people off.\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small not everyone is like that, i'm \textbf{gypsy} and i'm not lie that.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Im here cuz i slapped a \textbf{gypsy} and he rang my mum saying hes gonna kill us all and petrol bomb my house\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small The real question is, Why has a \textbf{gypsy} got your mums number?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Dyed black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Woohoo you can feel the hate in here. There's no shame in what happened in new zealand. Your all a bunch of racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Racist British people.  No surprise. It's starting to become clear. Its British who spread their rasict views.  All over the world. Not America.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Some of the \textbf{gypsy} girls are babes but the men are all fuckin monsters so i don't know where they're getting it from.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Grew up in the Midlands where there's a thriving \textbf{traveller} population. As with any demographic there's a few troublesome folks but most of them are just trying to live like everyone else. Many travellers even want to buy land and settle permanently, however local councils refuse to sell them land and grant planning permission simply because they don't want travellers living in their district. This was the case for several families I knew growing up, they were forced to continue moving around because \textbf{nobody} would let them buy somewhere to live. Institutionalised \textbf{racism} only makes this situation worse, it's unreal how many people are prejudiced against gypsies in the UK despite never actually meeting them. They have a noble bloodline that goes back thousands of years and their culture is as welcome here as anyone else's; it's called Great Britain not because it's full of angry white people, but because throughout history we have been invaded and settled by bloodlines from all over Europe and even further afar, making us the most mixed and unique Europeans. Everything about British culture celebrates centuries of immigrants building this great \textbf{nation}, we wouldn't exist without them.\normalsize   & \cellcolor{green!5}Nation, Nobody, Racism, Traveller & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Ethnicity - Roma, Nationality - General & \cellcolor{green!5}4/193 & \cellcolor{green!5}2.073 \\  \hline
  \cellcolor{green!27}\small Their are litterly gypsys living in a trench down near the trees eating squirrels it's really weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small All this \textbf{brexit} shit about Keeping immigrants out yet we can't even keep this lot under control.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I'd give the \textbf{gypo} girls a good hiding I'll tell ya that much boh.\normalsize   & \cellcolor{green!27}Gypo & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small And you would be hunted down and killed. \textbf{Dumb} fuck moron. FYI this vid has no Gypsies in it. They are pikies.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I remember there was a shit legal case recently.Some peaceful \textbf{old} man was sleeping in his house, when a burglar broke in and tried to steal all his shit, the man got attacked, but managaed to fatally wound the burglar.The burglar died, the \textbf{old} man rightfully used self-defense, but then it turned out that the burglar was a gypsie scumbag and all of his friends harrased the \textbf{old} mand and tried to intimidate him for self-defense. Luckily the police got involved before the gypsies got too cocky.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/89 & \cellcolor{green!27}3.371 \\  \hline
  \cellcolor{green!5}\small \@Darryl Moore Your point is not only wrong, mate, it's completely irrelevant. You act like they're a group of fucking Bear Grylls enthusiasts.They're not. They're a community of violent, disrespectful, parasites. They survive off the rest of society. Without that they're \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@Darryl Moore And the funny thing is in our regular society they contribute \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small When you charge a vulnerable \textbf{pensioner} ten grand to repoint their chimney, repeat the process, you find that you can live quite well, like the previous chap said, they are not self sufficient, they don't declare their "earnings" so they can live quite lavishly off what they have, those days of using a horse drawn wagon and selling pegs are long gone, they found a way to exploit the system and did just that.\normalsize   & \cellcolor{green!5}Pensioner & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small \@Murray Jones ,I know the stereotypes aren't entirely unfounded,a lot of them steal. I grew up in eastern Europe till I was 12,when the gypsies have ripped my family members off a few tkmes,but I was also best friends with a \textbf{gypsy} boy and he was awesome.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Criminal scum. They contribute \textbf{nothing}, they just take.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Get the f*ck out of my country you filthy inbred freak\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small leave them alone there gypsys there doing there thing it is there life and there decisions no leave them alone they aint doing \textbf{nothing} wrong there just basically camping and finding a place to stay now leave them alone\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small they prey on the weak and the \textbf{elderly}, make a mess of everywhere they are, steal anything they can get their hands on, have no respect for no one or anything, teach their kids from the get go to steal things and treat regular people like shit and they basically live off going to the government cap in hand begging for money instead of actually doing something and making their way in life like everyone else...........basically an altogether bad breed of people with a toxic culture\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Cross eyed, slack jawed yokels... Simple and \textbf{dim} witted, dirty feckers who don't give a shit about whose town or village they pillage and ruin. Feck right off.\normalsize   & \cellcolor{green!5}Dim & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small This people is not Gypsies Gypsies is litle \textbf{black}Im a Gypsies and im speak Gypsies legaueAKAVA NANE ROMA O ROMA KALE AKAVA DISAVE TARZANJA AKO ISI TUMEN ROMALEN DEN VILO KO AKAVA COM\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small A \textbf{p\textbf{ikey}} tried to fight me in school and it didn't end up well\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Good don't call us a \textbf{p\textbf{ikey}} again\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small Bet her arss stinks the ole \textbf{p\textbf{ikey}}..puts. make up on but can't wash cause they have no water\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small fyoukim12 not going to work me and my 3 mates were jumped by 1 \textbf{gypsy} and we are only 12 and 13 where he was like 17-19 years old\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small Nobody wants these tramps, they disrespect everything. The kids are little shits, who would want to live like that anyhow??\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small They don't live under the same rules as us , they like to think they have there own and it's hard trying to get a \textbf{gypsy} kid into school no one wants them\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small so what are we gonna do about it, lets all protest for a day lets live like \textbf{gypsy}'s,. lets all take a day off school and camp on a roundabout, tell the school your ancestors are \textbf{gypsy}. no disrespect for \textbf{gypsy}'s butt one rule for all, i bet know one has the bottle,\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small as a \textbf{gypsy} would say your a fool\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Romany and \textbf{traveller} children are subjected, as ever, to \textbf{racism} and shameful treatment in schools, deprived of a decent education as a result\normalsize   & \cellcolor{green!5}Racism, Traveller & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Mackenzie Stanton A child doesn't choose to be born into a \textbf{gypsy} family and can't help their way of life. That's all they know and for the rest of their life will stick with tradition and religion. Not all gypsies are the scummy cunts everyone makes them out to be. But I have met and seen gypsies that are definitely a handful.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small banks or an idiot it means that they shouldn't have access to the nhs or anything makes them essential an illegal immigrant\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@Nevaeh Meakin Carl is a funny name for a \textbf{gypsy} woman\normalsize   & \cellcolor{green!27}Gypsy, Woman & \cellcolor{green!27}Ethnicity - Roma, Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Helen the 19 year \textbf{old} is very very juicy,  come to America, we will love you  every night.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I am a French \textbf{gypsy} and I salute my brothers and sisters Traveler!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small rode her round the back ee the pub gud \textbf{old} blowjob queen\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Pikey scum get a job\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small My friends parents got their car stolen by gypsies and they could litteraly see it in the caravan park thingy they were staying in and it was like the police didnt even want to mess with them they litteraly did \textbf{nothing}. So many people are scared of them because if you mess with 1 you have to face every single one...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small And when England \textbf{gypsy} travellers have a holiday in New Zealand, [LINK] The family was served Deportation Liability Notices\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I hurt for the Roma. I am currently sponsoring 2 \textbf{gypsy} children who live in shacks built in dumps outside of Sibiu, Romania. Childhelp for Transylvania, e.V. provides food, clothing, school and social activities for these people. And they help build them small houses, complete with heat, furniture and generators. They need assistance and education how to stay put in one place. Seriously.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Nothing here a can of petrol and a match wouldn't fix\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Racist scum. 🖕\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Ben P being \textbf{racist} is natural? Lol find help and fast\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I am a \textbf{traveller} to\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I shaged a travler \textbf{woman} once, was walking back home drunk one Saturday night walks across a field through a travler camp and a \textbf{woman} offered me a bj, I smashed her on the floor next to her caravan . True story .\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small They get money by charging people for work who dont know the true cost of things.I witnessed a \textbf{traveller} doing a large blockwork driveway, which a local company would have charged about £3k for, and saw my neighbour hand over £8k in cash! Its no wonderthey come here!(I missed out on project managing it for him for £6k!)\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Should have know better Billy mate, i wouldn't piss on a \textbf{gypsy} if he was on fire.   Scum balls\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@sammy smith we wouldn't piss on you either sammy you \textbf{fat} \textbf{slag} 😂\normalsize   & \cellcolor{green!5}Fat, Slag & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical Features & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Your fucking fault for hiring a gyppo\normalsize   & \cellcolor{green!27}Gyppo & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small We've got a Bigfoot problem in KY, lots of poor ppl,like these gypsy's, could go live near them(,they'd leave,)no one would find you,in \textbf{r\textbf{ed}} river gorge,you could grow your own,distil your own,clean up your own!,as long as you vote republican,although,the cleaning part,or money,is an ideology, you may not understand.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small \@SUCK MY ERECT BALLS just been reading "\textbf{Gypsy} Boy", a \textbf{gypsy} autobiography - apparently Irish Travellers were originally native Irish who eventually imitated Romani gypsies. The Romani gypsies and Irish Travellers are totally unrelated and hate each other.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small No one is gonna read this but I am a \textbf{traveller} and I admit there is many bad people in my culture . Tbh the things they do are sickening to me . But there Is bad people in every culture and belief , if you actually go out and become friends with a traveler they will be there for the rest of your life becuse all we have been learned is ride or die. Most of us has all grown up with people being prejudice most are still mad. But the ones who aren't are the travellers you see feeding the homeless, going to holy countrys, trying to educate children is a way there not dissing there culture but still leaning ( I'm 15 I get home schooled 1 a week) most girls in my area do aswell. I dont live in a trailer my dad owns a travler sight it's so safe people walk there dogs and bring them here so the kids who are playing outside can play with them. One thing about my culture is my family dont think getting married at 16 is right my full family dont . My dad bought me a car and said ino your not \textbf{old} enough to drive it but live your life like your sister who got married at 19 . 19 seems young to non travlers but to us that's a bonus . We don't arrange marriages becuse love is love. One thing country people need to experience is bieng on a green field in the summer all the dogs a loose and you and all your friends theres 15 of us walking to the shop. All I have to say is theres more to my culture:)God bless all of you prejudice people I wrote this fast so If its messy sorry\normalsize   & \cellcolor{green!5}Old, Traveller & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!5}2/306 & \cellcolor{green!5}0.654 \\  \hline
  \cellcolor{green!27}\small \@Audi e-tron yes there are very bad people in my community but theres bad in every culture . I bet you haven't even met a travlers the real ones . Please take the time to educate yourself properly about travellers by watching BBC a very British history ep 1 it  uncover all the prejudice travellers faced back in 1950 and how it still happen today but people are two \textbf{blind} by seeing . And another thing I hope you seek them \textbf{mental} health you need, also its funny how a human bieng can have such a big brain but little knowledge like you . Typed this fast so bare with me and spelling mistakes\normalsize   & \cellcolor{green!27}Blind, Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/114 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small \@Audi e-tron fuck of ya chav\normalsize   & \cellcolor{green!5}Chav & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Lol pikey\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/2 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small A couple \textbf{gypsy} travellers set up near me dad's shop stole money accused his good friend of rape and then had the audacity yo say she and her brother (who'd threatened to fight another shop owner) to say they were victims\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Pikey cunts all bullshit artists.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small I would rather live next door to ISIS than a gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Now I wanna be a \textbf{gypsy} looks fun\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small now before i read about everyone dissing us i just want to say there is bad gypsys and good just like you gorgey breads and btw just a side note there is a load of kinds of gypsys i'm a romany but my family have lived here hundreds of years before me therefore if you say me u would not think of me as a \textbf{gypsy} until u got to know me\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small They even have \textbf{traveller} problems in New Zealand now, I hear...\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Jimmy u wouldn't fit in to the lifestyle because of the size of your ears u pikey\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small The kids seem to be trained from a young \textbf{age} to steal and fight\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Alright mate if you marry your sister and your a \textbf{traveller} no other travller will talk to you\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small som big ol' \textbf{gypsy} titties\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small If \textbf{Gypsy} would behave themselves, not everybody would hate them . But where I live they came and the theft rate went up about 100 and when they left again it mysteriously dropped again .\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small I think the one in the \textbf{r\textbf{ed}} top is sexy\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Load of \textbf{p\textbf{ikey}} cunts. They travel around with shotguns and horses and act like they're above the law. Pick up your trash, get your life together and buy a house\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small A little bit of comprising on all sides would go a long way. Travellers staying a few weeks and leaving the place the way they found it, and the council providing waste bins and a bit of \textbf{common} sense if offering services. Where its abused, throw the book at them.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Gypsy  Travelers    are  \textbf{nothing}   but   Con   Artist.    History  has   Recorded   Proof  of   their   so  called   Traditions.      Not  only  that  MANY  of  them   Practice    Voodoo   and   Witchcraft.    Those   Families     should  be   Tracked   Down   and   the  Kids  need  to  be  taken  away  from    them.    The  Kids  are   NOT     Living  in  a   Health   Environment  and   NOT  getting  a  Proper   Education  because   everything  they    get  is  Stolen.\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small I'm a \textbf{gypo} at heart\normalsize   & \cellcolor{green!27}Gypo & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small As a \textbf{traveller} I don't ever admire a country man's life a boring life shop school runs and home every day  NO u only live once\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Shane s wtf u talking about? the home is part of a community and where you have a safe stable place to raise your family- you dont have to be home 24/7. having a home is not boring, it is relaxing and offers security as well as allowing you to do whatever you want, since it's your property. the life of a \textbf{gypsy} looks tragic as fuck... rather not be born at all.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Listen I am a \textbf{traveller} were not here to take part were here to take over so fuck off\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Yeah! All the anti \textbf{Traveller} \textbf{racism} in society, kind of adds more stress to thier lives. Unnecessary really.  🇮🇪☘️\normalsize   & \cellcolor{green!27}Racism, Traveller & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small \@Tudor Miller \textbf{racism}? Are you serious? Travellers aren't a separate group. They are just a bunch of knackers.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I wonder what country this video is filmed in...\textbf{r\textbf{ed}} double decker bus rolls by.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Never trust a \textbf{gypsy}.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Helen looks a bit \textbf{old} for 19...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Pikey bastards\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Thieves and con artists, Florida would get the caravan every winter, they would spread out with thier schemes and fleece the \textbf{old} folks out of whatever they could.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small These are clearly Irish travellers. \textbf{Gypsy} is the wrong term, and refers more to the Roma people roaming all over Europe, who are dark skinned and of \textbf{Indian} origin.\normalsize   & \cellcolor{green!5}Gypsy, Indian & \cellcolor{green!5}Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small so once you could travel, see the world, live on the roads, work when you needed money, and follow the seasons, the herds, you name it. its a very \textbf{old} tradition, originally tribes also moved to match the seasons and herds, world wide. if you have never travelled, then you really have no idea. but bit by bit, its been made harder and harder. Originally these "greens" were deliberately left for people to live on. but its easier to steal from those who stay put, hit them with the endless land taxes, than it is to target people who wont stay still. You can always "take away their home" but its a lot harder when the home ups and drives away. I think this persecution of travellers, not just in the U.K, but world wide, is very wrong.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/138 & \cellcolor{green!27}0.725 \\  \hline
  \cellcolor{green!5}\small I've always got on with Travelers but now the pyky bastards can all fucking die as far as I care. In my hometown of ///::::: they have got single mums who have \textbf{mental} health issues and after befriending them they TURN they then GET THESE SINGLE MOMS TO GROW CANNABIS even though my personal thoughts on cannabis would differ from most THESE JIPO LEAVE THESE SINGLE MUMS IN FINANCIAL RUIN BY GROWING ON AVERAGE 2 FULL BATCHES THEN LEAVE making the mums down here foot the electric bills in the thousands so after what I've seen been done to my hometown they can drown have a car crash or just fall off the nearest cliff \textbf{NOTHING} WILL EVER CHANGE MY MIND ABOUT THESE STINKY PIKES.\normalsize   & \cellcolor{green!5}Mental, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/125 & \cellcolor{green!5}1.6 \\  \hline
  \cellcolor{green!27}\small That little \textbf{r\textbf{ed}} headed lindsey Lohan girl was in another traveler doc when she was smaller.. Shes quite the spit fire \textbf{brat} lol, n is why i imagine they found her again for a video doc.\normalsize   & \cellcolor{green!27}Brat, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small They're tinkers. They're Irish. No \textbf{gypsy} blood in them at all.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small its sad that they are called \textbf{gypsy}.they are not \textbf{gypsy}, they are white. Gypsies are brown ppl from india\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The first thing you need to understand about travelers is that they are essentially stupid! They know f*ck all about anything other than the basics of life, they are like a backwards tribe of \textbf{African} pygmies that are impressed with shiny bits of metal, talk to these thick fu*kers slowly and don't use any big complicated words or you will completely confuse the sh*t out of a traveler, a game of chess or scrabble is totally out of the question but they just may be able to grasp naughts and crosses if you come across an oddly bright traveler.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small Why not buy a skip wagon and take ya rubbish, job done . \textbf{Gypsy} travellers pulled me out of a ditch when I ran off the road so I can't \textbf{slag} them off as that's my only encounter.\normalsize   & \cellcolor{green!27}Gypsy, Slag & \cellcolor{green!27}Ethnicity - Roma, Gender - Female sexuality & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Why don't all leave rubbish we aren't all disrespectful. Give me one person who hasn't  littered in there life . This is stereotypical \textbf{racist} rubbish.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Prejudice, \textbf{Racism},harrasement !Free open Public spaces.The legal right to lead a life.All these things and more for some reason does not apply to Gypsies !??The council's would prefer to keep harrasement these people rather than leave them stay for a couple of weeks and then say move.A skip for waste is cheaper than providing permanent\textbf{Traveller} villages and makes more sense since they are travellers !\normalsize   & \cellcolor{green!27}Racism, Traveller & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small I'm a \textbf{traveller} so shut it mouths\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I remember my uncle had there van stolen by a \textbf{gypo} family. We were in the town over from where we live and he saw his van and he had a bottle of water and the poor bastards had the window down. Long story short he fucked that bottle so hard it was like a bullet\normalsize   & \cellcolor{green!27}Gypo & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small The \textbf{traveller} women are so incredibly beautiful\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small One of my brothers is actually married to a Irish \textbf{traveller} \textbf{woman} they've been together over 20 years have 2 daughters \& a baby granddaughter they married just a month after meeting.\normalsize   & \cellcolor{green!27}Traveller, Woman & \cellcolor{green!27}Ethnicity - Roma, Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Bet that \textbf{gypsy} bird has a fanny like a kicked over trifle.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Can someone tell me , why these gypsy‘s in UK are white ?!! In the Balkans , they are have really deep dark skin and \textbf{black} teeth gums ?!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small 1:48 Meaning, you're a \textbf{fat} lazy fuck who doesn't want to have a real job and pay taxes like everyone else. Just keep making them move to make it impossible for them to sleep.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Should ship the \textbf{p\textbf{ikey}} scum back to Ireland.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Never ever!! do business with a \textbf{gypsy}, I got robbed as a young man by them.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small My farriers a \textbf{gypsy} he's one of the finest men I know very polite, well educated ect\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Thief, lazzy, liar, dirty , criminals, \textbf{nothing} less....... thats all you Shine off \textbf{Gypsy}...sadly you don't want to prove us wrong\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Helen is a very attractive \textbf{woman}, but sounds so sad about her way of life.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small In Australia we have a phenomenon that is called the "Grey Nomads". These people are retirees who travel the country in their motor homes and caravans. They camp wherever they like with impunity, in fact in places they are encouraged by councils to  set up camp. They are all over the place and if you are unfortunate enough to get caught in conversation they will regale you with stories of their free camping experience and bore you to death.Why are these \textbf{old} farts allowed to do the same as the gypsies yet gypsies are hounded wherever they go?My mother would never pass by a \textbf{gypsy} without crossing their palm with silver\normalsize   & \cellcolor{green!5}Gypsy, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!5}2/113 & \cellcolor{green!5}1.77 \\  \hline
  \cellcolor{green!27}\small Wow Australia sounds \textbf{ageist} against younger people. Fuck bloody Australia and fuck their \textbf{elderly} gypsies! they should all be hung!\normalsize   & \cellcolor{green!27}Ageist, Elderly & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Gypsy losers who like moving complaining about being moved? what the fuck?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Big \textbf{Gypsy} clans in Australia. Unless you knew who they were you would have no idea. They drive around in Winnebago mobile homes. They tow cherry pickers onto fields and pick \textbf{fruit} by contract. You wouldn't even realise they're \textbf{Gypsy}. Mostly Irish decendent and some Romanian. Both have European relatives stay who tend to be not as "polished" at clan living. They have relatives in the towns who live there. Their kids are compulsory educated by internet  radio school and very well too. They are certainly not carnys and thieves here. Hard workers. Good earners.\normalsize   & \cellcolor{green!27}Fruit, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/96 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small one of my first girlfriends was a \textbf{traveller} when I was 13.Her family treated me really well even though I wasnt a \textbf{traveller}.Good times and good people....\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Yeah, I feel in love with a \textbf{Traveller} female from Sligo, she wasn't anything like the stereotypes that people on here are ranting about. Just pure \textbf{racism}, completely unnecessary. ♥️👩🇮🇪☘️\normalsize   & \cellcolor{green!27}Racism, Traveller & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small mind you you dont hear about the people with new and \textbf{old} nd home made campers being told to move\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small my 2 sisters were new \textbf{age} travelers in the 80s living in busses or made shift campers,they often got told to move they were always dirty and smelly stinking of patchuli  i remember hearing about driving no licence no tax no insurance some of them never learned to drive leagaly most of them made themselves be moved by stealing and loud music\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small So what if they leave rubbish behind its got \textbf{nothing} to do wit anyone else let them do want they want\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small These arent gypsys,they are Irish Travellers better known as knackers.98 of these people are \textbf{nothing} but criminal scum.Should take their kids off them to try and give them at least some chance in life.After \textbf{brexit} britain should take away their \textbf{ethnic} minority status.Theyre no different to any other Irish bar being a fucking violent nasty nuisance\normalsize   & \cellcolor{green!27}Brexit, Ethnic, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Nationality - European or anti-Europeans & \cellcolor{green!27}3/56 & \cellcolor{green!27}5.357 \\  \hline
  \cellcolor{green!5}\small That 19 year \textbf{old} sounds like a 50 year \textbf{old} smoker.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small These people need to come to America that \textbf{woman} at the beginning would feel at home here and she can follow what ever she wants no one would go after her for it\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Oxide Flamez it's not that hard fo get a house and not all travellers and \textbf{gypsy} are the same I a \textbf{gypsy} and my family's not like that you can label us all the same\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Fiizay wow a \textbf{racist} \textbf{black} man you used to be are sleeves so Shut up\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small \@Rg boxing Uk slaves? because we're stronger smarter and aren't lazy. how many irish travelers have invented anything instrumental in history? ok then? stop lights? \textbf{black} man. caller id? \textbf{black} man. automatic gear shift in your car? \textbf{Black} man. thermostats, pacemakers, etc etc the list goes on. please tell me again what travellers have invented besides making other peoples stuff "disappear"\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/61 & \cellcolor{green!5}4.918 \\  \hline
  \cellcolor{green!27}\small \@Kalle Sven No we don't ,not all of us are like that. Who do you think you are stereotyping us and being \textbf{racist} towards a whole \textbf{ethnicity} group who you've probably never met before  ,also don't tell someone what you think they do and don't do that just bad manners .\normalsize   & \cellcolor{green!27}Ethnicity, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small \@kiera holland And i am far from \textbf{racist} trust me.... i love \textbf{gypsy} ppl they are about familiy and i love that but holy fuck do they all steal or do some shit on the side... i dont know a single 100 legit \textbf{gypsy} family\normalsize   & \cellcolor{green!5}Gypsy, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small As an 'out and proud' Irish \textbf{g\textbf{ay}} man and a member of the settled community currently living in Manchester, UK, I have much respect for Members of the Travelling Community, thier customs, culture and identity, whom I meet on the Ferry from Holyhead when I visit my family back home in my home County of Meath in Rural Ireland - when I used to live in Ireland and worked in Dublin, I had far more daily contact with Travellers and I found them to be very nice, polite and friendly people and this was also true in my home area in Co. Meath - I am also familiar with the great work being done for Travellers by groups such as Pavee Point and on my nights out in \textbf{L\textbf{G\textbf{BT}}} venues, I have even met some Travellers who are also mostly \textbf{g\textbf{ay}} men, but for obvious reasons, are not always out as \textbf{g\textbf{ay}} to thier families\normalsize   & \cellcolor{green!27}Gay, LGBT & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}9/155 & \cellcolor{green!27}5.806 \\  \hline
  \cellcolor{green!5}\small the only good \textbf{gypsy} is tyson fury, every other is poor scum\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Pikey scum they rollup park up illegally trash the place then move on to fuck up another bit of land.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small My ibf is gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small CHECK OUT THE \textbf{GYPSY} SONG ON MY PAGE MOTHER DIE\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small are you sure you've got those statistics its really \textbf{racist} to go around saying that\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small To be fair, it's not always been like that. Because travellers don't want to integrate into mainstream society they have always been demonised and disrespected. It's no wonder communities turn militant when no matter where they go they are discriminated against and judged to be all the same. Any minority throughout history has had to endure untold amounts of suffering until society finally accepted them. It's easy to pretend like certain people don't belong and are \textbf{alien} to society because it makes you feel better about yourself but your identity and your way of life is just as subjective and fragile as anyone else's, including travelers. You could lose your home tomorrow, you could be thrown on the streets, lose your job, be patronised by your peers and excluded from your community. Who says you should be treated like that? If that's true why should anyone else? You get the bad people wherever you go and whoever those people are. Doesn't mean everybody is the same. My ex girlfriend was a settled Irish \textbf{traveller} and she was the nicest \textbf{woman} I had met. She's married now. Her dad has worked all his life. Her mum too. Her family are very well connected. But if you think they've had that life given to them on a plate think again. She used to tell me how people would throw them out of pubs for belonging to the Irish \textbf{traveller} community, without doing anything wrong! She would get dirty looks walking down the street and got bullied at school for being different. She chose to stick with education and came out with a degree despite most women in the community feeling pressured to follow the traditional path. She never said boo to a goose and her family never caused any trouble. Not to say an extended members didn't but you find me an extended family that is squeaky clean and model citizens. It's all relative and your stats are bullshit. Provide evidence or fuck off.\normalsize   & \cellcolor{green!27}Alien, Traveller, Woman & \cellcolor{green!27}Ethnicity - Roma, Gender - General, Nationality - General & \cellcolor{green!27}4/332 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small They are not gypsys they are your people  houses and took to the road years ago. \textbf{Gypsy} people have their own couture and language . These is just like all the other councilHouse estate people in Uk and Europe . Not an \textbf{ethnic} group at all .\normalsize   & \cellcolor{green!5}Ethnic, Gypsy & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small NO INSURANCE!...NO ROAD TAX!...NO M.O.T.'S....NO LICENSES...Yet \textbf{old} Bill let them drive away  every-time...So where doe's this leave the rest of us 'Georgies'...UH!.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small let these people live the way they want the \textbf{gypsy} are people and a way of life . they have been doing this longer than we have been living in homes .. let them be\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Say anything and you are a \textbf{racist} cunt ! Who said crime don't pay Not the poor pensioners they rob\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small There aren't enough \textbf{Traveller} sites for \textbf{Traveller} families across the country.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small That 19 yr \textbf{old} tho lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small In the good \textbf{old} times it was required by the law to kill them on sight.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I'm a traveller\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small That jimmy doesn't look inbred whatsoever Said \textbf{nobody}, ever\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Do not try and shrink me gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small They camp where convenient, poop all over it, and then move on. That's the "\textbf{traveller}" lifestyle. They prefer to stay wherever the richest pickings are.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Living up to the \textbf{traveller} stereotype of wearing the brightest pink lipstick she could possibly find\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Time to regulate these people. Time to have them pay taxes and NI contributions on any income they make.... They have access to the NHS don't they? Why should they if only a small percentage pay NIC? Time to look into what percentage pay NIC. Time for them to pay council tax when they aren't on an officially allotted site where I'm told that they do (?). Time to check if this is true. Time for the authorities to look into the income these people have and where it comes from. Time to have them prosecuted for shoplifting when it occurs instead of police turning a \textbf{blind} eye as I've just witnessed in a TV documentary! ..  and time for the police to stop pussyfooting around. Time for them to be forced to pay for cleaning up the rubbish they leave behind when they vacate a site. Time for them to realise that they can't simply set up camp wherever they want to. Time for them to research where the official sites for them are located ... Time for them to travel ...  and time for them to keep travelling!Why should the taxpayers pay for their rubbish to be cleaned up and why should we continue to pay taxes when many of these 'travellers' don't pay taxes?  Time we woke up!\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/222 & \cellcolor{green!5}0.45 \\  \hline
  \cellcolor{green!27}\small I agree with you. They seem to slip through the net every time. I don't know how in this day and \textbf{age} it still continues.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small I disagree with your grandad, but they should never be allowed near civilized society. They are all part of a criminal fraternity; even the children are indoctrinated from the day they can walk into learning to thieve and parasite and intimidate people. Half their kids are drinking lager in public by the \textbf{age} of 10.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small I don't know why they only travel in the same town. I would follow the weather pattern be a comfortable \textbf{Gypsy},they have the life I reckon. you could park your caravan in some beautiful spots don't like your neighbour pack up move on, you can't do that in a house.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Some don't travel at all they stay where they are if their roots get in. \textbf{Crazy} people trying to sell me heather \& cursing me for not buying it... like I said to them, I'm married, kids etc etc do your worst \textbf{crazy} fuckers.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Irish \textbf{traveller} are originally of Northern \textbf{Indian} descent\normalsize   & \cellcolor{green!27}Indian, Traveller & \cellcolor{green!27}Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Nothing but scum. Hope tf the cunts leave the country.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small saif Malik .. of course you like travellers and their way of life ... you are one. \textbf{Nobody} dislikes them for being a \textbf{traveller} ...  what we dislike is their lack of respect for the country they are living in even if they were born here of course.  You seem to know a lot about travellers. Do you happen to know if the travellers occupying an area which is not an official site, pay council tax and if they pay for the clear up which is almost always required when they finally leave?\normalsize   & \cellcolor{green!27}Nobody, Traveller & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small \@aharvey its all around you. Visit any \textbf{c\textbf{hav}} area\normalsize   & \cellcolor{green!5}Chav & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small \@saif Malik OK so you have no source apart from mentioning "\textbf{c\textbf{hav}} areas" .... are you defending the gypsies  travellers who dump their rubbish at the site when they leave it? Chavs, as you put it, pay rent, council tax and income tax  NIC otherwise they wouldn't occupy the social housing in that "\textbf{c\textbf{hav}} area". Are you telling me that gypsies pay council tax when they aren't occupying an official site? I'm not against travellers  gypsies .... I just want them to respect the laws, pay their way and to clean up after themselves.\normalsize   & \cellcolor{green!27}Chav & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}4/97 & \cellcolor{green!27}4.124 \\  \hline
  \cellcolor{green!5}\small They are dirty dangerous little bastards. The only reason their parents send them to learn boxing is to beat seven bells out of normal kids in the street. Back in the \textbf{old} days before PC culture, pubs used to have signs outside that read "NO DOGS, NO TRAVELLERS". And that was the right attitude.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Only yesterday I was in a local park and asked why this small dog was so timid. She had come from a \textbf{Gypsy} Site and when they moved on she and a sibling were tied to a lamp post and left out in the Winter's cold. She was nervous and had clearly been abused, the new owner said, and he said it took 3 years to get her over the trauma of being simply used for breeding and left outside.She did not have a clue about domestic life.This comes 2 weeks after I heard about 7 dogs being saved from a burning caravan on another site and were left inside.....lovely :(\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small A few social workers in my family, all spend substantial amounts of time a \textbf{Traveller} sites dealing with domestic abuse\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Undisciplined, Uneducated and Unlawful, and they wonder why \textbf{nobody} wants them anywhere near them if they just want to be treated the same as everybody else they should act the same as everybody else, so until they do, Fuck em.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small 11 seconds in might just be the funniest thing on YouTube "a small number of \textbf{traveller} families still spend their lives illegally stealing onto public places ". No shit !!! It's at about 96 😂😂😂😂😂😂\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small That bitch is 19 years \textbf{old}??? Ya right,,, her face is already looking like an \textbf{old} cunt!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small I am personally a \textbf{gypsy} and ive never lived in a trailer i am educated and im good in school and DONT litter.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small The thing that pisses me off the most about travellers aside from the huge amount of cash it costs for councils to deal with them and the high amount of crime committed by the \textbf{traveller} community, is that they go on about how they want to keep their traditions and don't wish to live like the rest of us but when one of them breaks a leg or gets a serious illness they don't start cracking out the lucky heather or magic pegs then do they!? no they go straight to the nearest hospital after a lifetime of paying fuck all N.I or tax and create another  burden on the system!\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small You're judging ALL of them though. It's not every \textbf{traveller} trust me. I was on the street for a year, never really talked to travellers much before, but I met one while I was in a hostel, I was shit poor, there was a notorious family after me and he sorted it out like that, he handed me everything, money, weed, food, clothes. And he made my life ALOT easier, just because I spoke to him and was his friend. He was also a mad bastard. I never judge any \textbf{traveller} again after that because he saved my life.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small \@Billy But Whole \textbf{Brexit} lol.Dont soak up everything you read,itl mean very little to joe public in the long run.I dont like gypsies,they do \textbf{nothing} for society,they dont give a fuck about anybody but themselves,they turn any area of land they come across into a shit hole  and i have no need,want or desire to buy lucky heather or pegs so instead of going round in a caravan pretending to be irish and leaching off the system hows about they rent or buy a proper house,send their kids to school and do a nine to five like every other fucker.\normalsize   & \cellcolor{green!27}Brexit, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - European or anti-Europeans & \cellcolor{green!27}2/100 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small \@Billy But Whole ummm think you got it a bit wrong mate cos they don't pay shit towards much how would you know about English \textbf{gypsy} when Ur names got Reich init u German Jew killing fuck\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small \@john smith haha you actaully told that kiddy made me burst out laughing when that fool reich kiddy said that the Muppet I hate \textbf{gypsy} they cause mayhem\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small dorothy buttlicker  CockLicker i wish i can tell you that you are not right.And , because i wish i'll say it. xDAbout 20or 30 of people are really as you said it , unfortunately.However ,i believe you are not that stupid as you look , right? To say that all of them are the same would mean that you ve seen all of them.Which means around 200-300 millions at least.So yeah , you are not the brightest one.I dont like those bastards as well, even tho im \textbf{Gypsy}.Because of that minority of people , our reputation got destroyed.So , government shouldnt be so easy on them,its their fault.And yeah , to all of you who hate us and generalize all Gypsies (faggots usually) you can easly just suck dicks and fuck yourselves in the ass as usual.Because you can never have a heart and a courage of a \textbf{Gypsy}. You need a balls for that.So, yeah.. You can cry now and bitching on YT all day long.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/177 & \cellcolor{green!5}1.13 \\  \hline
  \cellcolor{green!27}\small \@Elarb CH haha u you need a balls clearly you are as stupid as u look cos u can't spell and u saying that I was speaking about all gypsie you are wrong I was speaking about just British \textbf{gypsy} as they are the only \textbf{gypsy}'s I know so yeah u go fuck yourself in your own arse and stick your nose where it needs to be stuck 😂😂😂\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Rose wtf are you on about you want to be careful of  what you say. I'm a traveler and tbh you know \textbf{nothing} about us\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Billy But Whole But here in the UK we don't pay medical insurance so for gypsies here they can go to any hospital or dr and receive free care.  It is different in the USA i believe.  But most \textbf{traveller} women here now claim all the government benefits going.  They pay fck all to rent a plot on a camp site and the men do all the roofing and tarmac work but pay no tax or n.i insurance and so there is no proof they work and so the women claim benefits for themselves as they cannot work due to being full time mum of up to 5 or more kids.\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small why the fuck you idiots even care whether or not they pay or dont pay taxes or get free healthcare? there are far worse things being funded by government than fixing some \textbf{gypsy} girls broken leg, goverment is pissing on your tax money, they laugh at your face! They are fucking pissing on your face while you give them money and use it to blow up some children in Iraq, or to bribe some government officials in africa so their corporate friends in BP can get access to sweet oil a pay 0 taxes and even charge you 1.30 pounds for litre of gas, most of which is taxes while you fuckers whine about somebody getting "too much health" fuck off will ya? lets cut the bullshit and get to the real reason you hate them, BECAUSE THEY ARE DIFFERENT, they dont live your boring 9-5 bullshit jobs, they dont suck it up to bankers so they can mortgage a house they will never pay off, they dont give a shit about fitting in your inbred culture designed to suck out every penny out of you, get you in debt and be corporate slave to the very same companies i mentioned before while you get fuck all to show for it.  And thats a crime you just wont forgive.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/219 & \cellcolor{green!5}0.457 \\  \hline
  \cellcolor{green!27}\small john smith that is EXTREMELY \textbf{racist} to say, in the  beginning of the 19th century people started to believe we we were witches and wizards and made potions and since no one would hire us because we're 'gypsy scums' we resorted to saying we actually were witches and people would believe it. It's not our  fault that people are \textbf{racist}. Let me remind you we were put in concentration camps too. And before you say something about a different \textbf{race} at least know some background information.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/86 & \cellcolor{green!27}3.488 \\  \hline
  \cellcolor{green!5}\small Billy But Whole the \textbf{gypsy} is a racial slur we prefer ' traveling people.'\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small john smith \textbf{gypsy} is a racial slur it's as bad as saying the N word please use traveling people or travelers.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Terry Pin yes we do and that is beyond \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Elarb CH I'm \textbf{gypsy} too where r u from. But to say you don't like your own kind is a bit unloyal.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Elizabeth Watson i dont give a shit what you prefer how do you like that? there aint \textbf{nothing} wrong with gypsys, i dont need to bullshit myself with some PC jargain, if you think \textbf{gypsy} is bad maybe you are the fucking \textbf{racist}. i hang out with folks and travel around with them on occasion and if they cool with it you cool with it.\normalsize   & \cellcolor{green!5}Gypsy, Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}3/65 & \cellcolor{green!5}4.615 \\  \hline
  \cellcolor{green!27}\small s.o.s As a \textbf{gypsy} i really respect your comment, you're right. irish travellers cause havoc and chaos as they simply don't care what others think, they have to fend for themselves. thanks for not using the word \textbf{p\textbf{ikey}}, it seeks comments like that get all the likes.\normalsize   & \cellcolor{green!27}Gypsy, Pikey & \cellcolor{green!27}Ethnicity - Roma, Nationality - Irish, Social Class - Working class & \cellcolor{green!27}3/47 & \cellcolor{green!27}6.383 \\  \hline
  \cellcolor{green!5}\small \@Ellie May youse r pikeys tho I've been told wat u do by some \textbf{gypsy} bird who I used to fuck 😂😂 wat the lads do robbing the battery's out the cars and taking shit out of laptops use r funny and ino u r all not like that but how else do u always have doe\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small The problem is. Society thinks it's ok to tarnish all Travellers as trouble, when they'd never do that to other minorities. It's seen as acceptable to be openly prejudiced towards the whole \textbf{Traveller} community. Would you do that to the Jewish community ?\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small \@Tudor Miller I disagree that it's considered acceptable to "tarnish all travellers". It was but then the \textbf{Race} Relations Industry got involved so now it's apparently considered \textbf{racist}. Watching this video I'm wondering if they're all UK citizens and if we couldn't just deport them.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small I wouldn't go as far as shooting them but I'd say this to them; completely assimilate or you're going back to Ireland. Either way, \textbf{P\textbf{ikey}} problem solved.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Olivia last year the \textbf{p\textbf{ikey}} scum descended on local school playing field broke into the gated play area and used the infants sand box to shit in . When the council finally evicted the scum the fire brigade came and hosed down all the play ground.The school was shut for nearly 2 weeks If I had my way their caravans and vehicles would all be destroyed with them inside.p.s True Gypsys are totally different and respect the enviroment.\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/78 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Why do you wanna bring your kids up in a shoe box in the middle of a field can't put down any roots it crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Recently \textbf{gypsy} kids threatened my friend with a knife and pepperspray u wonder why everyone hates ur guts 😓\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Anybody else notice that \textbf{p\textbf{ikey}} women all have cracking tits?\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small you not know \textbf{nothing},there are different gypsy's from different country's and when you are in a store you know that gypsy's are in the next aisle over because they have a odour that comes off them because they live right behind a factory that uses carbon in it's manufacturing and they smell of it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Wow, the level of disgusting \textbf{racism} in the comments towards these people says more about you lot than them. You are horrible people and should be ashamed of the ignorant generalizations coming out of your mouths.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small me having \textbf{gypsy} family and reading these comment is pure digustin  all u lot gowan bout how gypsys are 'disgustin' and calling them names like gypos n pikeys. get a bloody grip of urselves!!!! so what they travel its in their fucking culture . stop being disrespectful. all ur comments show how little of people you are being sterotypical and saying all these nasty things online. ur mams should all wash ur mouths out with soap its absolutely bloody disgusting n vile. chattin shit online when ur probably too scared to even go up to \textbf{gypsy} in real life. now thats just the truth n u don't like Gypsies don't watch these type of videos u hypocritical gorgers !!!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/119 & \cellcolor{green!5}1.681 \\  \hline
  \cellcolor{green!27}\small This \textbf{gypsy} girl is beautiful ❤️😊\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small check Youtube for \textbf{p\textbf{ikey}} stealing/fighting or \textbf{p\textbf{ikey}} leaving rubbish then you will understand WHY people do not want them in their town/parks\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}4/22 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small im a gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small these filthy pikeys" .... what are you talking about? they are PEOPLE just like you and I.So they don't choose to abide by the laws of a bunch of elitist snobs in westminster....wow..So you don't like to look at their houses, here's some advice: don't bloody look at them then, just stick your face back in the Sun or the Daily Express or whatever rag it is that has you so full of \textbf{blind} hatred and ignorance...\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/79 & \cellcolor{green!5}2.532 \\  \hline
  \cellcolor{green!27}\small Got to laugh with despair at this blazingly hypocritical comments. I bet half of those commenting about rubbish and calling them "scum", live in council houses which they've not painted for 15 years, with an \textbf{oven} that's falling apart, someone's "forgotten" to clean up all the dog poo in the front garden, and "forgotten" to take the 7 year \textbf{old}, rotting sofa that lays abadoned in the front garden, to the rubbish dump. I bet you chavvy \textbf{c\textbf{hav}} chavlings venture out on a Friday night with your \textbf{c\textbf{hav}}-level "best suit" and prop the bar up at the local, before becoming intoxicated by 4 lemonade shandie, before staggering home in your crappy Primark clothes and beating up your girlfriend. See "Shameless" for an accurate portrayal of how the aptly named ✌️"great unwashed"✌️ squander their simpleton lives, stuck in shitty jobs because they're dragged up by their delinquent parents... and they've got the nerve to call others, whom they've VERY LIKELY NEVER SOCIALISED WITH? Wow. Travellers are people too. They're amazing. Man up, walk down to your local travellers site, knock on the door and spout this crap TO THEIR FACES... then let's talk. Plebs.\normalsize   & \cellcolor{green!27}Chav, Old, Oven & \cellcolor{green!27}Age - Over 65s, Nationality - Irish, Religious Identity - Jewish, Social Class - Working class & \cellcolor{green!27}4/193 & \cellcolor{green!27}2.073 \\  \hline
  \cellcolor{green!5}\small "\textbf{Gypsy} Travellers" ?They're called TRAVELLERS, \textbf{nothing} else.\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Wiz Gee ok I don't think she would go down well if she wore a police \textbf{woman} outfit she would definitely get lynched 🙀😀 her boobs I give them 10 out 10 🥇\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@Elizabeth Sawatzky \textbf{Racist} twat\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Totally off topic but I used to take bathes in that exact same pink tub when I was a baby! Not a \textbf{gypsy} btw\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Damn Gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Gypsies should honestly be arrested for doing this. They contribute \textbf{nothing} and do \textbf{nothing} but take\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Gypsy lasses are fit best around 😍\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small we all started of being travellers ive lived like that me self an its good ur free whats wrong with that.as-far as there rubbish wat do you expect the way hypocritical ppl treat them good n bad everywhere . they would use tips but they get turned away. they dont claim jack shit they work hard they look after each other not like half you cxxts ye \textbf{slag} an rip the person next to ye some ur posts why should they go to Australia how would they make money to live. what do you mean earn there keep they work hard they ask for \textbf{nothing} .ppl have lived that way since the beginning ov time . if half the homeless ppl had a chance of a caravans to live in then would you mind that because i think the counsels should put land with caravans for all the homeless short term while there on emergency housing\normalsize   & \cellcolor{green!27}Nothing, Slag & \cellcolor{green!27}Age - Youngsters, Gender - Female sexuality & \cellcolor{green!27}2/157 & \cellcolor{green!27}1.274 \\  \hline
  \cellcolor{green!5}\small Id love to \textbf{gypsy} grab Helen and make her my wife!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Hate these damn ads telling me you \textbf{sexual} abused complete turn off can't even enjoy the video now\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small well i know you talking shite here cos i seen them in the store with skirts that barely cover they \textbf{bum} cheeks and they have stomach flab hanging out at the front ,how the fk they think they are attractive is beyond me.\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small +stephen john gray hahaha i belive you mate but trust me there are diffrent gipsys and these are more like \textbf{Jerry} springers humans😂 then Theres alot of normal gipsys in Sweden spain France god bless mate\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Gypsys are good in bed I used to explore some beautiful naked \textbf{gypsy} women go body and dirty fantasies came true\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The only difference between Gypsies and \textbf{elderly} caravaners is caravaners clean up after themselves and don't steal shit!They only time anyone cares about caravaners is when they are stuck behind them on the road.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Ben Sims I'm reporting really vile comments. The government really needs to crack down on this. You can't insult Muslims, members of LQBTQ+ or \textbf{black} people (and \textbf{nobody} should!) and yet we have people saying that us travellers should all die.. and so should the children. It sickens and upsets me. Society should fucking grow up! I don't want to live in a world where people wish children dead!! Children!! 😢\normalsize   & \cellcolor{green!5}Black, Nobody & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small Don't give romantic terms like "\textbf{gypsy}" to fucking trash creating free loaders that just keep squirting out and raising more free loading babies. It's a game that their playing at the expense of others and their children. These are the pretty one's with nicer cars  and campers. Still free loaders that feel entitled to impose on everyone else and then play the victim.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small 02:13Sounds like a 40 year \textbf{old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I love how everyone is calling us names.what about the people living in houses selling drugs to anybody who'll buy no matter the \textbf{age} and ye call us names.half of ye have don't know what your on about.oh hang on maybe it's jealousy because we don't have to stay in one backwards town and get into 25yr debt to to own our own home\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small Most right thinking people do not hate others for what they are, just their actions and deeds, and the things they do And much of what gets done by many of yourselves when you land somewhere, is proof positive if ever it where needed. And if you think 25yrs will clear most mortgages off in today's day and \textbf{age}, God bless you.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small I'll talk to anyone anywhere, a lot of people are the same. Your lifestyle fascinates many, me included. What upsets many is the trouble and problems-particularly the rubbish tips and other issues some travellers create, where they rock up. I don't hate anyone for being either \textbf{Traveller} or Romany, but I have seen the huge mess that many create, and been involved in clean ups where lorries and a JCB has been required for days on end, fence repairs etc to put things right again after departure. It costs big bucks, and it's just not right. You see this surely??\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small \@JCBAirmaster73 council wouldn't do that for fear of us all pulling up because it's more of a vote winner to move us on at the end of the day I'll tell how \textbf{racist} the council and government is towards us you can call us a \textbf{p\textbf{ikey}} and \textbf{nothing} will bee done yet use a similar word to discribe a Asian person arrested so we'll always be second class citizens\normalsize   & \cellcolor{green!5}Nothing, Pikey, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Nationality - Irish, Social Class - Working class & \cellcolor{green!5}4/69 & \cellcolor{green!5}5.797 \\  \hline
  \cellcolor{green!27}\small That's crap I agree, no one should be vilified for what they are, \textbf{nobody}. If councils don't respond though to the requests of their local council tax and rate payers over issues, and one will be the illegal occupation or trespass and despoilment of public land, they get slated for it. The problem lies in the fact that if where a good many of your number pulled in, they where not seen as such a threat, and all the mess was not part of it, you cannot help but feel it would be a different story.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Why does that girl who looks about 13 sound like a 50yr \textbf{old} bloke !? These lot are very fishy they treat their kids like adults something's not right there\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small It's the kids who are the worst. They do what they want and have \textbf{zero} fear, I remember having to kick one out of the shop I was working in because he was trying to grab money out the till. After work he's there in McDonald's backed up by six of his older cousins who were closer to my \textbf{age} tried to beat the shit out of me for throwing him out, but I got out of there quick. The only thing these kids learn is fighting, they run around like they own the place and it's plain mad, and the fact the older ones are backing them up is even madder.\normalsize   & \cellcolor{green!27}Age, Zero & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Had a \textbf{p\textbf{ikey}} try to steal my bike one night when I was round a friend's house for a party years ago, friend let his dog out the backgarden and got a cricket bat and whacked that fucking \textbf{p\textbf{ikey}} till he crawled back to his shit den.He's lucky the rest of us were inside drinking, else he'd be fucking dog food\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}4/62 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small When I was younger I went on a fair ride and I stupidly gave a thieving \textbf{Piky} a tenna he gave me change for for a fiver and I was threatened to be beaten up when I asked for my change after the ride.I was an apprentice mechanic at the time and so went back the next evening with small bolt cutters I and cut through diesel pipes to 2 generators that were powering the rides and ran like fuck away not stopping for fear of being caught I will never forget the Adrenalin pumping through me at the time.I'm now in my thirty's now but thinking back and I will admit I was really shitting myself at the time but I can still get great satisfaction even now when I take my children to the fair I always brings a smile to my face thinking about my dirty deed all this years ago 👍👍👍\normalsize   & \cellcolor{green!27}Piky & \cellcolor{green!27}Nationality - Irish & \cellcolor{green!27}1/157 & \cellcolor{green!27}0.637 \\  \hline
  \cellcolor{green!5}\small West Side is da best aww tanks your lovely to \textbf{gypsy} kids we are ppl too\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small West Side is da best thats 10 reason why i HATE the western side,\textbf{Racism}!\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Don't tar all "travellers" with the same brush.Van dwellers are fine and don't bother anyone.Travellers don't bother anyone, unless you hate giant carved mushrooms.Gypsies are normally fine too.Then we have Pikies :(Easily identified by the brand new caravans and transit vans.You can normally find then ripping off \textbf{old} ladies and shoddily tarmacing driveways.They break in to wherever they are staying, wreck the place, then quite literally leave all their shit behind when they go.But they can't understand why everyone hates them........?.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small They're are thieves not millionaires they have around 10-100k saved up from welfare if they do not do drugs/smoking because they do not buy anything they just steal but they're not saving up a million from welfare even though they buy \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small As an Irish man who has mostly (19 years) lived in Dublin and the past year lived in the country! I (AND MY PARENTS) and my partner has made it work! I wish I couldn't pay tax it's expensive enough. I wish I could have the glamours lifestyle these people have. My \textbf{elderly} parents house (who came from \textbf{nothing}) was burgled from people like this Gardai knew who they were but sadly couldn't prosecute because they were children! I never knew I'd be writing this about 'people' but these are not people they take what they want and get away with it! I wish I had a proper voice to denounce these waste of oxygen. So we could focus on what matters\normalsize   & \cellcolor{green!5}Elderly, Nothing & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/122 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Mate there's things called \textbf{gypsy} sites ffs\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small they have no respect can't trust any \textbf{traveller} think only of them selves waste of air\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Average life expectancy for a male \textbf{traveller} in the UK is 53.\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Was cycling passed gypsies just recently and a four year \textbf{old} boy called me a smelly hoe! And there's a park close to my house which gypsies come to quite a lot, and one morning after they left and my family went to the park, they'd literally left poop... yes SHIT on the slide. Absolutely disgusting!!! The amount you get verbally abused when just trying to walk passed them is disgusting enough, but the poop thing is the top nastiest thing I've experienced gypsies do to my home town, on top of all the rubbish they leave when they go.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small I would definitely love to ride her on the sneak as long as \textbf{nobody} found out.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Some rack on that \textbf{p\textbf{ikey}} bird\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small He was there, I think I saw him taking a \textbf{dumb} behind a car\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Muslims aren't an \textbf{ethnicity}, a Malaysian is very different from a Bosniak Muslim and a Saudi is very different from a Turkish Muslim etc,  just because they all follow Islam doesn't mean they all like each other necessarily in the same sense that many Europeans are Christian but that didn't stop Protestants and Catholics trying to kill each other. The Western Europeans love to coddle Muslims from backward nations for some reason, their choice really if they enjoy importing low quality humans.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Get away from my beautiful countryside with you rubbish fires and caravans.I have \textbf{nothing} against your practice...unless you leave your stain on the beauty of the highlands!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Why do all \textbf{p\textbf{ikey}} women look fucking orange\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Did you see that child's eyes, one was pointing east and the other was pointing north, that is a real sign of a \textbf{p\textbf{ikey}}, and that is why cousins should not be aloud to have sex\normalsize   & \cellcolor{green!27}Pikey, Sex & \cellcolor{green!27}Gender - General, Nationality - Irish, Social Class - Working class & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Dirty bastards have just been near me on a kids park and shit in the kids sand pit dirty bastards keep on traveling \textbf{nobody} wants you\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small So, you can have people from any other \textbf{nation} come to Britain and keep their culture but not Gypsies, I'd call that discrimination.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Yea ...General population: 95 good, 5 bad\textbf{Traveller} population: 95 bad, 5 good\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small 19? Shes 19 years \textbf{old}? Try 34\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Nothing beats the smell of burning knackers caravan sites in the morning.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Mr Devawheels \textbf{racist} mother fucker\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Mr Devawheels shut the fuck up, you \textbf{racist} piece of shit\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Winston Churchill y'all \textbf{r\textbf{edneck}}, \textbf{racist}, pieces of white supremacist shits.\normalsize   & \cellcolor{green!27}Racist, Redneck & \cellcolor{green!27}Ethnicity - General, Ethnicity - White, Social Class - Working class & \cellcolor{green!27}3/10 & \cellcolor{green!27}30.0 \\  \hline
  \cellcolor{green!5}\small \@Farhan Rahman hahaha j fucking retarded twat Winston Churchill \textbf{r\textbf{edneck}} u \textbf{dumb} asf bro 😂😂\normalsize   & \cellcolor{green!5}Dumb, Redneck & \cellcolor{green!5}Ethnicity - White, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Farhan Rahman I got \textbf{black} \textbf{African} American mates I have \textbf{African} and South \textbf{African} mates I even know a \textbf{Indian} but thing is they all have put in work towards this country pay their taxes they don't just come here for a easy fucking life and live off our fucking taxpayers money u scumbag fuck show some fucking respect and stick your nose out what ain't yours to stick in bitch\normalsize   & \cellcolor{green!27}African, Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}5/71 & \cellcolor{green!27}7.042 \\  \hline
  \cellcolor{green!5}\small \@dorothy buttlicker White Power u left  tard \textbf{commie}....\normalsize   & \cellcolor{green!5}Commie & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small They were no \textbf{traveller} family tha if it were me travellers they woulda fucked up all yur rugby players nd done it again nd again nd sed we ain't never leavin\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small \@Maryam Malik I'm \textbf{racist} am I? Says fucking Islam lmao\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Farhan Rahman islam isn't a \textbf{race} so shows how much you know. Pretty sure Islam is the backwards thinking savage religion.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Brandon Hughes thats very racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small ho0k html   Wow how \textbf{racist} against my culture\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Niamh Tia XO tour right I am a \textbf{traveller} we've been evicted robbed ,arrested , raided we're disrespectful because yee won't let us live anywhere we don't even use electricity we have horses and wagons tents fires to cook food so that's why were disrespectful\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Ben P Wow lol... I can't wait for more sandies and blacks to move into your neighborhood and fuck all the women you know. Just picture your wife (or husband you little \textbf{faggot}), getting BLACKED by a Mandingo you \textbf{racist} pussy\normalsize   & \cellcolor{green!27}Faggot, Racist, pussy & \cellcolor{green!27}Ethnicity - General, Nationality - Chinese, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small \@Maryam Malik These Gypsies migrated from \textbf{old} North West India. Which is now Pakistan. You will feel for them because they are of your kind.These are the ones who does rape in India. Successful Indians in Europe and US are of Dravidian origin.CEOs of Google and Microsoft are Dravidians\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Ireland's embarrassment. \textbf{Nothing} uplifting or beneficial about them or majority criminal lifestyles. Don't pay taxes but expect all the benefits of standard society. Wherever they are? \textbf{Nothing} but theiving, violence and basic scumbag behaviour.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small BOLLOX YOU ARE ALL IGNORANT GORJER BRED FOOLS. If the council made more sites for the traveling community to park on they wouldn't be forced to park illegally. But no ,you are all so busy pointing the finger and speaking insulting language, \textbf{gyppo},\textbf{p\textbf{ikey}},thief etc etc. None of you have taken one second to look at it from the other way. Their way of life has been as it is for hundreds of years who the hell are you to say that it should change.\normalsize   & \cellcolor{green!5}Gyppo, Pikey & \cellcolor{green!5}Ethnicity - Roma, Nationality - Irish, Social Class - Working class & \cellcolor{green!5}3/84 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@\textbf{gypsy} \textbf{freak} yeah I agree times change but some things don't, did you know that a horse has more right to be on the road than a car, A pregnant \textbf{woman} can take a piece of \textbf{fruit} from a shop and not be prosecuted ! You should never forget where you come from !!\normalsize   & \cellcolor{green!27}Freak, Fruit, Gypsy, Woman & \cellcolor{green!27}Ethnicity - Roma, Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/54 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Pikey shit\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small WOW! the amount of \textbf{racism} in the comment section. It is so vile + toxic. \textbf{Gypsy} is a derogatory term FFS. These people have been persecuted for centuries in europe, you'd think we'd treat them good in 2018!\normalsize   & \cellcolor{green!27}Gypsy, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small That's not \textbf{racism} you \textbf{dumb} fuck!\normalsize   & \cellcolor{green!5}Dumb, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small ~~~~~  Is  there  not  one  person  to  say  anything   good  about  this  video  or  kind  about  these   \textbf{Gypsy}  .\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Nothing wrong with \textbf{gypsy} any ive met have always been nice\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small leave them alone not doing fuck all wrong. im not a \textbf{traveller} but they still human\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Acting like they're badly done to when in reality people hate them because they have absolutely no respect for anyone or anything. We have quite a few open bits of green land here and every now and again some pikeys will pass through and just absolutely destroy the land. Leaving their shit everywhere, starting fires, letting their horses shit all over the place and destroy all the grass. Not to mention the effect they have on the local communities.There are some pikeys in a legal camp that live near me. They have been there for years, pay to be there and respect other people and \textbf{nobody} bats an eye towards them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small Why do they all have Irish accents and probably never seen the place, \textbf{weird}.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small why dont they travel around their home country of ireland . Its a big country with less than 5 million people  and tons of open space .Instead they come to England ,one of the most densely populated countries in the world and wonder why we get upset about it. Us english are a tolerant and welcoming \textbf{nation} but there is a limit to our generosity when it  is taken advantage of\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small fizzbuck1 not all \textbf{gypsy} or \textbf{traveller} come from Ireland I'm a \textbf{gypsy} and I don't I don't know why all u Gorger people are so ignorant\normalsize   & \cellcolor{green!27}Gypsy, Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small \@Amy Bridges Ignorant? You dont pay any fucking taxes and sponge off the rest of us you \textbf{p\textbf{ikey}} thieves. And no you may of been born here but your blood is Irish. You wanna know why you are hated? Go to any town centre and watch the thieving pikeys trying to sell their stolen shit.Or better yet, ask some people about pikeys ripping of \textbf{old} people for driveways etc.\normalsize   & \cellcolor{green!5}Old, Pikey & \cellcolor{green!5}Age - Over 65s, Nationality - Irish, Social Class - Working class & \cellcolor{green!5}3/70 & \cellcolor{green!5}4.286 \\  \hline
  \cellcolor{green!27}\small \@Amy Bridges inbred \textbf{freak}.\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I cant see myself living a country mans lifestyle ? No shit your a \textbf{dumb} fuck looser it takes money \& education and you have neither if those dummy !!!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small They're a people out of time. They used to provide a service of being tinkers and doing other odd jobs, and to some extent some still do but the vast majority have turned to behaviors that have them hated by settled people. Such as, leaving their haulting sites destroyed, feuding between their own families like bronze \textbf{age} savages, stealing and swindling, mistreating their "pets", generally being disrespectful of others and not teaching their children how to be respectful. It's sad that all travelers have to deal with being tarnished with the same brush by settled people but when such a large proportion of travelers are bad human beings it's only wise to act in such a way towards them. What travelers need to do is settle on their own get a stable job, buy or build their own home, not among their extended family and slowly built a good reputation among their settled neighbors and in only a generation or two would be seen as trusted individuals. It might be hard leaving a tradition that's been around for hundreds of years but all that remains of that tradition in the future is misery and poverty.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/195 & \cellcolor{green!27}0.513 \\  \hline
  \cellcolor{green!5}\small It is a free country to a point! Take your litter to a local council recycling centre every town has at least one? And it's free to get rid of your waste! Abide by the law! And don't harass people in the local areas where you decided to put up camp! But non of the above are ever done this is why the \textbf{nation} is so against travellers! I feel sorry for them to a point! but they reap what they sew.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small +Bilbo BagginsYa not going anywhere ya tick \textbf{lump} ya stay til the jobs done!\normalsize   & \cellcolor{green!27}Lump & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Housed people are snakey fuckers with no principles. How many \textbf{gypsy} pedofiles or rapists do you hear off.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Why are all \textbf{Gypsy} girls so good looking I'd bang them all but never get to meet one.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small At the end of the day these are Human Beings and they are following their culture. Those making vile comments are Racists. You cannot name call these people for anything because society across every level does everything that you accuse these folks for. I've seen people living in houses that are disgusting inside and out, in fact they are far far worse than folks from these Cultures. Racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Yeah it's \textbf{weird}. I guess the residents of the local areas object\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@james james shut up, what do they do, steal, vandalise, break countless laws and trespass, there was a news story a few weeks ago a gypsie family broke into a brewery over night, did £10 million in damage stole barrells of booze and drove off like any other day. That family owned company over 100 years \textbf{old} went into administration and shut down because of that. A campsite i legally went to the other weekend the gates were broken down and the camp was invaded by a huge group of gypsies over night none of them paid anything then got into a fight and vandalised the toilet block.So before you go around calling people excplicit namesLook your self in the mirror you "self absorbed rotten cunt"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/128 & \cellcolor{green!5}0.781 \\  \hline
  \cellcolor{green!27}\small \@4wd some yes I agree with you that's all that gypsies do destroy damage Steel and Rec people's lives and we have to spend money cleaning up their mess what the \textbf{nation} should do is vandalise there caravans steel wheels from the caravans stick there caravans on house bricks graffiti there caravans then you would see they would not return again\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small 4wd some like I keep saying, these people are giving us a bad name because not all of us are like that, these are Irish gipsys but if u guys did some research you'd know that there are more types of gipsy for example I get mistaken for \textbf{Indian} because of my brown skin and hungarian background but I'm a musical gipsy which means we have a long background of musicians who make some of the most tear jerking music. Don't put all of us into one stereotype\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small \@Gary Jeffrey You sound like a fucking \textbf{gypsy} yourself with your uneducated spelling.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small i respect the \textbf{gypsy} they are still living freely !! its just the ones fenced in that moan a little\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Ha,they go on about \textbf{racism} yet travellers are some of the most \textbf{racist} xenophobic people on the planet.all they have got to do is  leave people alone and respect others but they can't can they.times are changing boyos and you can't be ass holes like you used to be.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small If they didn't break in to places, steal everything that's not nailed down and wreck the place, \textbf{nobody} would have a problem with them.Other groups live on the road, and \textbf{nobody} even notices they are even there.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Yup only gypsies steal and litter known fact in the world 🌎 oh in case you \textbf{dumb} assed people didn't realise that was sarcasm\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small We're not all \textbf{racist} tbh as not all non travellers are racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Lottie Mcpheei didnt say all travellers are \textbf{racist} but from personal experience most travellers are and are way more \textbf{racist} and xenophobic than people from other backgrounds for sure.like some minorities people have hidden under the \textbf{race} card yet refuse to except that \textbf{racism} is a two way street and they think theres one rule for them and another rule for everybody else.\normalsize   & \cellcolor{green!27}Race, Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}4/64 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Da guardare silenzio it's people like ye that get our young ons expelled or takin out of school due to bullying how would u like it if your mammy car was burned in front of u or my mammy was giving birth to my sister and the bailiffs took our caravan and my daddy could do \textbf{nothing} bc he had to make sure ye didn't take him to jail so he went to the hospital while me my auntie my uncles and cuzzins had to look for a place for my mammy to go after my sister was born and my little cuzzin died last yr bc of ye he hadid diabetes and everywhere his family went  the electricity was cut off \textbf{witch} ment his needles weren't cold enough and he died\normalsize   & \cellcolor{green!5}Nothing, Witch & \cellcolor{green!5}Age - Youngsters, Gender - Female age and physical appearance & \cellcolor{green!5}2/132 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small \@Jamez but there genetically linked to \textbf{Indian} find it out\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Travellers arent \textbf{racist} at all. its more like you british that are racists\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small You people whinge about these guys but your real problem are your new \textbf{migrant} friends. Besides if this is any indication their women look great.\normalsize   & \cellcolor{green!27}Migrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small keep moving.  not one place in the entire world has a good word for you and does not want you . vile filth who have no intention of living by the law the same as anyone else . leave filth everywhere,  steal from \textbf{old} folks . never pay tax insurance stamp etc yet demand its benefits . crawl under a stone till the slugs evict you !!!!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small So no one likes these gypsie type--so just like in AMERICA r they compared to the blax that no one  wants to b around  those \textbf{black} people  either cuz they loud \& thieves \& always fighting...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@George Britten id love you to say that to a \textbf{gypsy} but you're a key board warrior...\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Anon Xo what am saying there \textbf{ethnic} background\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@saeedur rahman it's not the same at all brother, these people are Irish Travelers, probably can trace there ancestor's from northern Spain . They might have a little Romany blood... the word \textbf{Gypsy} comes into English vernacular from the word Egypt....when the first Roma arrived in England they was referred too as Egyptians, "and lots of them played on it! Bringing scrying and Tarot cards, saying they was the priests of Egypt lol ...the Roma come from northern Kashmir,.....I just had me DNA done online...I was born in England too Irish traveler Parents but my DNA came back 68 percent Irish, the rest was Peshawar...and I'm as white as can be lol\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small \@saeedur rahman I like too think I'm probably the first white tattooed \textbf{Gypsy} too complete my Hajj....but probably not Subha'Allah 😉❤\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small The young \textbf{woman} has a nice set of tits 😉\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Loraine Hardy your mum's a slag\normalsize   & \cellcolor{green!27}Slag & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small With a trail of thefts left at every stop!! Poor \textbf{old} violent, intimidating criminals\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Pikey chicks are hot. Proper tramps. Dirty sex\normalsize   & \cellcolor{green!27}Pikey, Sex & \cellcolor{green!27}Gender - General, Nationality - Irish, Social Class - Working class & \cellcolor{green!27}3/8 & \cellcolor{green!27}37.5 \\  \hline
  \cellcolor{green!5}\small Do gypos like \textbf{bum} \textbf{sex} like they like thevin ?\normalsize   & \cellcolor{green!5}Bum, Sex & \cellcolor{green!5}Gender - General, Social Class - Destitute & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I meant pikey\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small \@Judgement Day and you're a fuckboy \textbf{racist}..\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small First of all I'm white, and just because your y dont "see" something as \textbf{racist}, it doesn't mean it isn't, you're just an entitled dumbass who thinks the colour of someone's skin makes them a worse person, or in your case not even fucking human, you should be ashamed if anything, people like you are lost causes.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Bunch of \textbf{p\textbf{ikey}} scumbags\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Micky Driver No, they wouldn't. I've always been respectful of my surroundings, and those around me.. but as soon as they know i'm a \textbf{gypsy}, they think differently of me\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Micky Driver and one more thing if they didn't fucking threaten people because yesterday me and my friends got jumped by a gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@JR P gypsies in my local park man they so fucking \textbf{fat} and lazy\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small If the fucking Councils and corrupt Government gave them sites they could rent and live on they wouldn't shit on fields or leave rubbish anywhere.And if you and other people who think like you showed the travellers some respect then they might think differently about you...And if you think Travellers are bad wait while your fields are full of illegal fucking immigrants.Have a look around your council estates you will find shit and rubbish all over the place.And no i am not a \textbf{traveller} i am fucking English and proud of it.But people like you make me sick to the stomach.You and your 876 thumbs up should be ashamed of yourselves.I wonder how many of your thumbs up live on council estates....No doubt most of them....\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/127 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small Exactly.  When they come round here the area they used to park on (before the farmers barricaded it) was always left in a complete state.  That and the sudden spate of thefts of trailers and farm and other equipment is the reason why most people think gypsies are scum of the earth.  \textbf{Racist}? Maybe but not untrue.  If they acted respectfully they'd be treated likewise but mostly they don't.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Ellie May the thing is some \textbf{gypsy}'s shit on farmers land and stuff one near me went on a public rugby pitch if your going to be a \textbf{gypsy} go somewhere private\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Why does everyone have these stereotypes of the \textbf{Traveller} community ? Ridiculous!!! I feel in love with a \textbf{Traveller} female once, and she wasn't like any of these stereotypes. ♥️👩🇮🇪☘️\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small We don't shit in the fields u spastic\normalsize   & \cellcolor{green!5}Spastic & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I fought s \textbf{p\textbf{ikey}} for a caravan once.. I'm sure he cheated.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small How did you know it was a \textbf{gypsy} did u ask him you cheeky prick\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small dont call someone a \textbf{p\textbf{ikey}} its vile\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small \@The Pine \textbf{Witch} they should use service stations like everyone else.\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@kiera holland What? Call them "vile" instead of "\textbf{p\textbf{ikey}}"?\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small Your \textbf{racist} shit\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@kiera holland Give over Pikey\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Do you fancy picking up their bags of feces they leave everywhere and paying back the deposits to the \textbf{old} ladies that never got any work done on their houses?Cheers, mate. If only everyone was as respectable as you, aye?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@King Brilliant land publicly owned and unused, these Travellers owned their own land which they were building acommodation for the \textbf{elderly}, Essex County Council evicted them from that land, you want to bitch then bitch to them. Other than that your acting like a wankstain that your mother should have swallowed\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small i love \textbf{traveller} women haha\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small they fight over \textbf{nothing} and the kids always act as if they trying to distract you to pick your pocket, apart from that travellers are fine.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Not travellers just a bunch of \textbf{fat} cunt pikies.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@\textbf{gypsy} \textbf{freak} Good dude!\normalsize   & \cellcolor{green!27}Freak, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Moonshine \textbf{Buck} more than these wastes of skin and air. For starters I pay tax and national insurance.\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Moonshine \textbf{Buck} cool story hippy. I've done both. You're just assuming. Assumption is the mother of all fuck ups. I've travelled the world, living in most of the continents other than Antarctica. That's pretty 'off the grid'. Come up with something better, or fuck off. Melt\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Moonshine \textbf{Buck} what I'm saying, is pikeys are cunts. Full stop. You're getting off subject because you can't come up with a reason to back up your defence for gypos and the way they live there disgusting lives.\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Moonshine \textbf{Buck} paying tax is a start. Already that's more than they do.\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Sam C Go conceive another \textbf{gypsy} mutant with your sister-wife, inbred freak\normalsize   & \cellcolor{green!5}Freak, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Judgement Day what type of mammal am I? I'm a human you fucking imbecile. The human \textbf{race} are mammals. I really hope you are just baiting me here.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Everytime they are moved on, it breaks up the community. Community is a real strength within \textbf{Traveller} families. 🇮🇪☘️\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Well the fundamental problem with what they're doing is that if the entire population did it, society as we know it would break down and collapse e.g. the healthcare system/social and public services etc. If everyone decided they were going to live in a caravan and not pay taxes, the country wouldn't function. If you allow some to come over then just as with economic migration, it only encourages more. Then there's the reality that space is extremely limited o this small island as it is. Then there's the fact that they create a mess everywhere they go. Then there's the fact that they intimidate the locals. Another issue that arises is similar to the problem many Western countries have with their Muslim populations and it's integration. The travelling community refuse to integrate into mainstream society. They basically want to live in their own parallel society and at the cost of the tax payer. This isn't good for society as a whole.I could go on and on but these are side points really. Ultimately, a \textbf{nation} can only support a small number of  them.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/185 & \cellcolor{green!27}0.541 \\  \hline
  \cellcolor{green!5}\small Only Gillian I can't even read whatever it is you just said. All I got was you can't read properly, well by looks of it you can't write properly either. How about typing that out again in English so I can understand it you scummy \textbf{p\textbf{ikey}}.\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Sam C Right and we'll just forget about all the empires that came before the colonial era shall we? I guess all these empires stole \textbf{nothing}? Akkadian Empire (2300 BC–2200 BC)Achaemenid Empire (550 BC–330 BC)Roman Empire ( 27 BC–AD 476/1453)Umayyad Caliphate (661–750)Qing Dynasty (1890–1912) Not European!!Russian Empire (1721–1917)Not European!!Mongol Empire (1206–1368) Not European!!Mughal Empire (1526–1858)Not European!!Ottoman Empire (1299–1923)Not European!!And that's only some of them, the list goes on.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small \@Cxnel  They are white, I am white. you can't be \textbf{racist} to your own \textbf{race}! \textbf{P\textbf{ikey}} is not a \textbf{race}, \textbf{Black}, white and asian are races. Snowflakes these days don't seem to get what \textbf{racist} actually means. The word "\textbf{p\textbf{ikey}}" is a slang word not a \textbf{racist} word.\normalsize   & \cellcolor{green!5}Black, Pikey, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Nationality - Irish, Social Class - Working class & \cellcolor{green!5}10/48 & \cellcolor{green!5}20.833 \\  \hline
  \cellcolor{green!27}\small \@Derek Delboy Trotter they are an \textbf{ethnic} minority...\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Derek Delboy Trotter Lmao you bodied all of the illiterate retarded \textbf{gypsy} mutants. It's not even that hard; they all have an average IQ of 60 but still lollll\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I'm a \textbf{gypsy} and have a fine education. Not all gypsies are uneducated. Sure, most are, but not all. My whole family is full of gypsies and most of us are well educated. I have manners and I'm polite. Admittedly, a lot of \textbf{gypsy} children are rude brats, but once again, not all are.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Irish pikies, depot them come Brexit\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Moonshine \textbf{Buck} it has never been about that man... but I 100 get your point. These bastards are all criminal. They're a huge problem here in Ireland.\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Ryan Tandy there is no lie. The cops are terrified. They're afraid of them. The real topic is why are they such out of control scumbags? It's not a \textbf{race} thing it's a culture thing.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small It is gammons like you who think you are being persecuted, crying because some gypsies moved near to you, or a new mosque is being built,or crying because a \textbf{woman} got the job you wanted\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small It is the gammons that think they are being persecuted, they cry because a mosque is being built in their town, or cry claiming that they are being persecuted by have their freedom of speech taken from them,or they are not free to make \textbf{Nazi} salutes in public places. Go and cry silly little gammon\normalsize   & \cellcolor{green!5}Gammon, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - White & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small \@jeflynnenut So stupid so every \textbf{gypsy} ever lived is a criminal if you believe that there is no hope. Yes obviously a small few steal but alot of non gypsies steal stop talking about politics 'dude' hahaahhah up the gypsies\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Nothing wrong with travlers let them be and in peace\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{old} man who stopped you was right. You are doing something wrong you are parking on private land. The guy who said he could not do a country mans life. He meant being honest and not stealing and ripping people off. I should not be harsh I know they have to go somewhere.Could that somewhere be 6 feet under.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small I know how they feel i get called a \textbf{p\textbf{ikey}} or \textbf{paddy} on xbox live all the time by you brit bastards.I fucking hate the english now and mute them every time i hear the accent.\normalsize   & \cellcolor{green!5}Paddy, Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small The travelers leave heaps of garbage behind . They also have bare minimum education .. you want to live a life on the road .. duh! work for it , like the rest of us . \textbf{Nobody} gets a free ride in life 👎🏽👎🏽👎🏽\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Exactly these people make me sick. There is absolutely \textbf{nothing} wrong with travelers. Some of the soundest people you will met. Yes there are some bad travelers but none worse that the loons of settled people. And lets not forget the politicians and bankers who seem to screw everyone and you have fuck all to say about them.. Get off your high horse. I would stand alongside travelers and fight for their rights rather than the likes of you\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small topcatdog you talk like non gypsies are clean. Have you not been in to any city in the UK?. Let's not also forgot how much shit we \textbf{dumb} in the oceans. I suppose that's travellers aswel.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Oisin O Lochlainn Er, I am a \textbf{traveller}. Only I go all over the world. Y'know, as in experiencing a different culture? That's real travel.And why don't people say anything to their faces? Oh they do!! And I have \textbf{zero} qualms going G to their sites to walk the dogs and have a chat. Yeah, I agree, most actually come across as very friendly. But their actions day otherwise. I don't care of people want to travel. I do care when I have to constantly dodge pulled of poo on pathways I walk down everyday. And yes, right outside people's houses.\normalsize   & \cellcolor{green!5}Traveller, Zero & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/101 & \cellcolor{green!5}1.98 \\  \hline
  \cellcolor{green!27}\small Cparker lol pikey\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small Oisin O Lochlainn wasn't talking bout politicians ..pay attention . if a traveler family staying overnight for free . Called civility to pick up ur own garbage .since it's a tight knit community , shouldn't be hard to pass along the message .then \textbf{nobody} have to see it then .\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small t5 Heath there is \textbf{nothing} wrong with not conforming to society as long as you work , pay taxes ,don't break the law \& \textbf{common} civility . If not then go to  3 rd world countries ,where you don't have to conform to \textbf{nothing}.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}3/44 & \cellcolor{green!27}6.818 \\  \hline
  \cellcolor{green!5}\small Moonshine \textbf{Buck}  nope 👎🏽, if this were true , the whole world would be 💩countries\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Also, they have a habit of disruption the personal security of houses and shops around where they park up.As a cab driver,  I have personally been on the receiving end of their habits. In one weekend, I  had five incidents of groups of them exiting the cab with no intention of paying, and four did notes being handed over as payment. Virtually every single cab of a fleet of 250 cabs \& over 200 private hire vehicles in our town had at least one experience of their anti-social behaviour. The shops and houses around where they parked up were subject to break-Is \& theft. The Police were overloaded with reports of crimes committed by the travellers, so the cab trade had to accept being well down the list of priorities. The pubs \& clubs endured a whole weekend of vandalism, theft \& counterfeit  Tenners and twenties being passed. Any establishment where the doorstaff refused them enry were met with violence \& vandalism, or threats of both.. It's  no wonder these reprobate are not welcome wherever they go. The also drove expensive vehicles all over the sports pitches, completely ruining newly laid grass, and trashed the facilities for the pitches. It cost thousands to repair the damage and clean up the  revolting stuff they left behind, once they decided to leave for pastures new. This is all documented fact, not rumour, so, snowflakes \& PC do-gooders, don't bother pulling out the \textbf{racism} card, get off your lazy arses \& follow some of these groups to witness the reality of their rail of destruction and criminal behaviour before you start calling the local population "bigots" and "racists", and sympathise with the travellers/gypsies or whatever they call themselves. That one weekend  cost me virtually a whole week's earnings. Yes, I actually worked for an honest living, but I still had all my expenses like insurance, licence fees etc to cover and repairs to the vehicle after one group tore the rear door off in their attempt to make their trip free of charge!\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/340 & \cellcolor{green!27}0.294 \\  \hline
  \cellcolor{green!5}\small Marylee Macpherson you say Traveler's leave rubbish behind.you are Talking about most of the country.almost all work.\& pay Taxes.you have your opinion you are ignorant as you don't know what the hell you are Talking about.look what's happening to our country who have been invited in and are raping \textbf{woman} \& children.murder our people.but you and idiots like you only have the balls to speak against the Travellers?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small If the whole world was full of pikeys we'd still be in the stone \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Marylee Macpherson Yeah like anywhere I suppose. You have your different levels in society, some more willing to respect and live 'harmoniously' with others. Here in California we have our problems with the homeless. There are really four types who choose this lifestyle, those down on their luck, those with an addiction, those with \textbf{mental} problems and those who just want to be on their own.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small i bet you justify your lies , if they gave them any way of removing the trash they would , if you see inside the vans , they are spotless, way cleaner than most houses , yes i am part roma , i was not raised that way , i was adopted , one thing i do know though is this , i did not know i had roma blood and yet they always treated me as a roma , they took me in to their families every time they came back to my adopted fathers land , i think he knew i was roma descent , for sure he was , he never encouraged my adopted siblings to spend time with them though , only me , i think it was because he wanted me to know the lies the settlers tell to justify their abuse , Roma were in uk from 1500, many way way before some of the now abusers , stop lying to yourself , saying its not \textbf{racism} , it is , just get to know the people you hate for no more reason than they hate being tied down and have the courage to live on the road , i envy them wish i could , or a barge , that takes money though, i do not have any sooo.... stuck , trapped , yes i feel trapped\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/234 & \cellcolor{green!27}0.427 \\  \hline
  \cellcolor{green!5}\small \@Tom Mcdonagh im a Swedish traveller\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Unfortunately you're living in the past. The \textbf{elderly}, the \textbf{disabled}, the darker skinned and the Muslims now get a free ride in life thanks to fucking socialism and the fucking EU! Allot of fuckers get a free ride in life now a days, especially here in SJW Europe!\normalsize   & \cellcolor{green!27}Disabled, Elderly & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Marylee MacphersonYour spot on, a stupider group of people is hard to find, like a newly discovered \textbf{African} tribe of Pygmes with caravans, thick as f*ck!\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Don't forget they rob houses, do sub standard work for people that they've knocked on there doors and rip off vulnerable people like pensioners. Go on call me a liar and a hater....they've done it 3 times in my local area in as many weeks. My next door neighbor is very \textbf{old} and vulnerable and they offered to jet wash the drive for 150 quid. The drives only big enough for one car and their sons car was on it so they were just jet washing around the car. Further up the road they managed to get a job on someone's roof, they knocked on the next door neighbors door and told the \textbf{old} vulnerable lady they'd done some work on her roof as well and wanted £1000 pound for it. She didn't have the money so they took her to the bank to get it. They have slaves as has been reported many times so fuck off with your shite that their nice people. Oh yes don't forget the piles of rubbish they leave behind. Nice caravans though which I suppose the money fell from the sky or the tax man gave them a huge rebate for the 0 amount of tax they paid before.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/206 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small One thing I will say in their defence is that some of these \textbf{gyppo} girls are hot as fuck. I basically had this 18 year \textbf{old} fresh girl who wanted some free board and food without paying rent. I said OK but we must sleep in the same bed as I need the rest of the space for other things. I ushered her into the bedroom and within two weeks we were having the raunchiest \textbf{sex} ever. I mean literally I was blobbing gobs of hot semen into her a large number of times per day [I work from home so can get a lot of spare time]. You know when your balls are literally just empty and you cock is simply shooting out air? That's what it was like. She was quite \textbf{racist} to me [I'm a brown guy], but after about 7 months I kicked her out [she literally used to steal/take anything that wasn't nailed down. No shit but I actually ran chain through hooks that were bolted to the floor, attached to my electronic gear]. Horrible people, but for a while they are great to have \textbf{sex} with. Also, they \textbf{age} really badly [I saw some of her \textbf{elder} cousins... fuck me they were a ghastly vision].\normalsize   & \cellcolor{green!5}Age, Elder, Gyppo, Old, Racist, Sex & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - General, Ethnicity - Roma, Gender - General & \cellcolor{green!5}7/211 & \cellcolor{green!5}3.318 \\  \hline
  \cellcolor{green!27}\small Fuck you im a \textbf{traveller} yous are such doccors\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small U obviously know \textbf{nothing} about us travelers... We are very much hard workers!!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Marylee macpherson people like you are idiots it makes me smile how you can ramble aloud of shit like this when your probably a dosser who doesn't and don't wanna work listen if I had money I'd bye a caravan and travel from town too town making 100 grand plus a year plus being a land scape gardener its a brilliant way of life. Travelers are all \textbf{old} school they don't waste tax payers money by phoning the police every 5 mins they just have a 1 on 1 and that's the end of it unlike toffee knows bints like ya self silly  🐮 😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/105 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small Ur just a fool that don't have a clue about \textbf{traveller} couture and they are the cleverest people going hunny not all are the same u get quiet ones u get bold ones the same as y do with English society but ovios we all have r opinions about minimum education!\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small And when England \textbf{gypsy} travellers have a holiday in New Zealand, [LINK] The family was served Deportation Liability Notices\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small I'm Irish \textbf{traveller} how rude\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Constant K filthy inbred freak\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Yes lets just join the rat \textbf{race}! Society has become the zombie apocalypse dude!\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Moonshine \textbf{Buck} those enslaved, wish for none to be free!!\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small 1st world, 2nd world and 3rd world terminology is a description of political affiliation, From the perspective of the west."The First World consisted of the U.S., Western Europe and their allies. The Second World was the so-called \textbf{Communist} Bloc: the Soviet Union,China, Cuba and friends. The remaining nations, which aligned with neither group, were assigned to the Third World" All are equal.All are not treated equally. Equality is a hope of those mistreated. Mistreatment has a knock on effect. Knock on effects are circular. What goes around come around.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Moonshine \textbf{Buck} what?? The planet has a waste problem so your solution is you may as well let people make it worse? Backwards ass dipshit\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Where i live they took over a park, anyone coming into the play area of that park were then shut in and forced to pay little \textbf{gypsy} kids £2 to go on the swings. Left trash everywhere and theft went up alot in the houses that lived close by. Absolute cunts\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Moonshine \textbf{Buck} your name is moonshine \textbf{buck} with a confederate flag. Stop drinking white wash.\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small \@Moonshine \textbf{Buck} you are a \textbf{yank} mate, fuck off no one on this planet likes the yanks.\normalsize   & \cellcolor{green!5}Buck, Yank & \cellcolor{green!5}Ethnicity - Black, Nationality - American & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Fair play to them.What man has the right to tell another man he cant stop on a patch of grass.These travellers might play \textbf{dumb}.But they are one intelligent breed.And they live a happy life for it.One day soon we will ALL living like this.Except the elite.Dont help the elite bring in stronger laws, it might just go against you one day.Treat them like nighbours,accept that they will stay for  about 2 weeks.If they are noisy and troublesome...then you complain.Youd be surprised at how many will be good people.Jesus it aint rocket science.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/92 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small I did read it, maybe actually read my comment? The police don't do anything even though these people are trespassing for days before they get moved on. if I went and parked my car on my local park I would be asked to move on by the police, yet they wouldn't do the same for travellers. Why should they have special rules? I can't trespass and neither can they, that's the simple bit that isn't hard to understand. I would never rule out a whole group of people saying there is no good in them at all, I'm sure there are people  in the \textbf{traveller} community with good hearts. You have to understand though this is a real problem where I live. The clear up operations can cost £30-£50k depending on how long they stay (funded by mine and your council tax). I mean even if they cleared up after them then that would be a start, but the ones that have moved in to parks and football clubs by me never do. In the case of the football club they had to foot the bill and struggled to stay open, not sure how you can really defend that?  I really don't think it's a simple as you make out 'treat them like neighbours' not sure if you're experienced with travellers but that doesn't work. They are breaking the law from the offset which is what often causes the confrontation, whether that's with the police or the locals. Good look with your approach though, maybe it will work for you.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/260 & \cellcolor{green!5}0.385 \\  \hline
  \cellcolor{green!27}\small ​\@Harry Jagwar For whatever its merits or lack of, 'the system' was imposed by violence in every case; in no case did the people choose it. Every \textbf{nation} state in history was founded by people who took control by force and ruled by force. The infrastructure you mention, while being a convenience to the people, also benefits the elites by allowing for higher population, higher production, more taxes. It's not nearly as simple as you cast it. Whether the people now have democratic control, or whether political choice is a total sham is the debate.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small if they cleaned up after themselves and didn't bother locals, \textbf{nobody} would give a fuck if they camp in park or not.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small ryan roberts it's not just rubbish they don't work but they all drive posh cars...new vans...there the biggest thieves ever they do \textbf{nothing} for anyone just take take take they don't want to contribute they like the freedom but to get by that means living off others \& Fighting stealing \& dumping rubbish they have no respect they come to a town everyone gets cars broken into houses robbed fights in the bar \& then the local park left like a toilet...then they go to the next town \& repeat...it's a lifestyle for them \& \textbf{nobody} wants them near because of what there like..Try to see the good in people...but if you gave one a job \& a house he would steal the light bulbs \& run away with the cash register...I'm a realist..\normalsize   & \cellcolor{green!27}Nobody, Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/135 & \cellcolor{green!27}1.481 \\  \hline
  \cellcolor{green!5}\small That's racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small \@Michael ward I'm sure they don't but unfortunately \textbf{nobody} has left my area decent.. yet. If a bit of trash was left we would go and pick it up ourselves and forget about it. Unfortunately rubbish has been left on a such a massive scale that the council has had to deal with it repeatedly. So now on first glimpse of any travellers arriving the locals are in uproar. I now understand the hostility towards them as now we don't want any because of this. Hopefully one day a family may come and prove us wrong but my nearby neighbours would rather not take that risk with them now.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small \@Jita'ame suluma yes \textbf{racist} people around da place \textbf{racist} to us \textbf{gypsy} and Irish gypsies\normalsize   & \cellcolor{green!5}Gypsy, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Go pick your dirty needles up from the parks u take ur children to . Go clean ur counsel house gardens . Go look after ur children instead of loosing them to social services . Over a 100 thus and people in  UK prisons alone guess what there ur people . Judges n vicars in for nonsing  children .  Drug dealers  .  Your kind of people even have ur own nonses prisons cos there's so many of ur kind abusing \textbf{woman} n children .  Politicians in for tax invasion the list goes on so let's get it right think it's your kind of people who need to pick there shit up dnt you .   That's what you call fact  .  Peter suckliff  . Myra Hindley . Jamie bulger killers . Ian Huntly  . Dennis Nelson.  Lord brocket . Gary glitter . .YES THERE ALL YOUR KIND OF PEOPLE.. Don't think u got room to talk about rubbish do you . You fool\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/162 & \cellcolor{green!27}0.617 \\  \hline
  \cellcolor{green!5}\small manpreet singh why are You defending them you fucktard?? They'd hate you on sure cause you're not a white person, they're  very \textbf{racist} people and you defending them you look like a fucking idiot\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small "the public", as a whole, are dirty criminal deluded \textbf{racist} hypocrites\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Maybe if they stop robbing, leaving shit (usually literally) behind in public/council areas,  incest, underage \textbf{sex}, dumping, animal cruelty, illegal camping, homeland tax fraud, car tax, insurance and/or MOT evasion, public menace citations, cold doorstop calling ..... Maybe we can forgive them? :P\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small racist, tramps and no life dealt with gypsys in past not nice people don't understand law should me more tough on them ?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small My Mercedes sprinter was taken and was clocked by Anpr with a fucking caravan on tow later that day, never seen again presumably on fake plates now like most of the \textbf{p\textbf{ikey}} vehicles\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small \@Constant Kexactly you \textbf{p\textbf{ikey}} fuckers think it's completely acceptable to steal and you wonder why everybody hates you.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@interceptor1986 again not every \textbf{gypsy} steals when will people learn. Many not travellers steal etc just because they have something linked to them doesent mean you should discriminate\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I am half Bulgarian and half Ukrainian and I went to kiev to visit some of my relatives and I had to use the subway, I saw a \textbf{gypsy} family in one and the dad and two of his 5 kids were pissing just out in the open with their genitals out for everyone to see, the point is that they turn every country they stay in into a shithole. In Bulgaria we have a \textbf{gypsy} village in which the girls are prostitutes.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small You sound bitter, you must be an english \textbf{traveller}.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small 4.20 Helen said "if they could \textbf{Bum} us out they would, ""Some truth in that I suppose!!\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Martin Ward we would all have money if we did shitty tarmacked driveways and sold TVs with \textbf{nothing} inside!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Martin Ward \textbf{nothing} like pissing in a \textbf{gypsy} girls ass eah\normalsize   & \cellcolor{green!27}Gypsy, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Always got \textbf{fat} titties\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Mike Murphy i got paid yes and now all other caravan owners are having to pay in increased insurance, do you think thats fair, and of course a good insurance company pays out quick because they know after a \textbf{P\textbf{ikey}} has slept in it who would want it back, why do you think so many people dislike you and you kind\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small \@rich You \textbf{racist}!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small They would be alright if they weren't so f***ing stupid! Talking to an adult traveler is honestly like talking to a three year \textbf{old} child, there is no excuse for this anymore, you can pass a university degree these days from home. I reckon if there was some way to get these daft w\@nkers up to speed with education that would be the end of the travelers, they would disappear for good, it's their stupidity that keeps their culture alive.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small Im a irish traverller and i find the \textbf{racism} disgusting to be honest . All we wanna do is what we want and we get you saying all this shit . When i was 16 i was given 1.7 million and i invested it well . I rarely steal and i dont think you should put everyone in the same bracket\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small John Jibuly oh ya i rarely do  Obviously you dont get to own several sports cars outright by flying straight with little education . But i dont go around hurting people often and like i said i only steal to improve my situation financialy but i dont do it all the time and i dont be writing on the walls or breaking up bus stops.  Im not a \textbf{woman} beater inless pushed but even then i stop at a few slaps the odd punch no kicking . I helped many non traverllers over the years so dont put everyone i  the same bracket\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small anton S actually the out back is a great place to catch indagered animals and send them back for coats and handbags or to be fighted . I dont like animal fights but i have made money from it because when i pull up in new cars people respect that.  And i dont want to sound bad so i explaine about the stealing . Example i want a 100inch tv . I cab either buy it for a few k or i can buy a stolen one for cheap or take it off the person who stole it . Few punches usually does it . Then i have the tv and the money . Sister wanted a watch so i could buy one or take one off someone for free and i get a new watch for \textbf{nothing} . Sister happy and person who i took ot from gets insurance and has a story to tell the other slaves at work . Maybe she will.go.do karate and meet new friends . I want some fuel . I can buy it or slice someones pipe open and take it . I get free fuel they get a day off work and insurance and a story to tell his slave friends from the office . I get excited i can buy a \textbf{woman} for 60 for one hour and do what i want . Go home and kiss my wife . But i dont just steal cheap things for no reason . I see scum bags stealing food and hugcaps and things and i wonder were society is heading . I have over 700 horses . What am i supposed to do ? Do you have any idea how much they cost to shelter.  But they have to eat no . So i out them in outher peoples fields . I keep the best new ones and sell the worse ones for meat in France.  I dont like doing it but it buys me big houses and i have a huge family . Each wedding costs me over 50k . Then they need things and i provide very well . You likely think i am wrong but i was born in a field in a storm and never had a house . I have a army behind me but i dont go hurting people . Iv built what i got from \textbf{nothing} . I never went to lean i taught myself to read and write the 3rd time i was in prison and i know i dont do it very well but its helped make me millions with property in over 18 countries.  I oay tax in petrol and diesel and between us we do over 10 million miles a year so when fuel s 85 tax they do very well indeed . I have paid for the roads english people drive on . A small thank you now and again wouldnt go a miss\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/493 & \cellcolor{green!5}0.609 \\  \hline
  \cellcolor{green!27}\small steerpike50 \textbf{nothing} to steal  there.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small there is \textbf{nothing} to nick in the desert\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small steerpike50 you obviously don't get \textbf{traveller} life.\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small You are describing the social security fraud that is enriching travellers. This is made possible by travellers being allowed to claim social security under a variety of alias and then make multiple claims often buying land in the process to gain addresses for more claims. Hopefully one day a national identity card scheme will stop this theft. It's not clever, its \textbf{common} thievery  made possible by incompetent governing bodies and idiots scared of a police state.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small \@ana lalot, As much as I hope you're joking that you're a \textbf{traveller}. You have to understand that those people do not do anything for society aside from mess it up more. They're like the cancer to modern society, and they must all be removed.\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small \@TheAnalv why not interview some of the millionaires of travellers haha all you idiots working your balls off to have half as much as most travellers these travellers are like the council estate version of buffers except they have more respect for them selves and dont take heroin or have \textbf{sex} with anything or have un married mothers and every breed and every culture has thieves and law breakers but ye waste of oxigen have to be mad at someone for the miserable lives you live!!!!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small \@Chris Big how about the pedos who england is full of and how are the \textbf{black} men who are paluting the streets with drugs how about the other 90 percent of crime what should u do with them u stupid man u should be put down your a waste of place i bet ur a \textbf{drug addict} and u proberly dont know who your dad is or maybe your just angry because your mother has been bringin different men into ur home since your a child or maybe your just angry because you cant provide for ur family so thats why ur angry with travellers for being able to laugh at the likes of you for all those things but there is atleast 1 discusting thing\normalsize   & \cellcolor{green!27}Black, Drug addict & \cellcolor{green!27}Behavioural Addiction - Drugs, Ethnicity - Black & \cellcolor{green!27}2/126 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small \@Mike Murphy and that's why y'all are fucking disgusting 😂😂 you get mad when people talk shit and then admit that it's exactly what y'all do. Pathetic. What a piece of shit. Y'all deserve to constantly be evicted. \textbf{Nothing} but criminals\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small No benefits.... \textbf{P\textbf{ikey}} scum... Fuck off back to ireland\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small \@ramanathan bendylegs your not a \textbf{race}... Your a bunch of thieving bastards\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Because there is \textbf{nothing} to steal in the out back  I guess  only kangaroos 🦘 and a few bushmen\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small johnzo70 i only do it if i want something i either dont want to buy or cant afford . I wouldn't steal for fun usualy . For example if i wanted a speed boat then of course i will take one . Buying a speed boat costs lots but if i take one then its better . Horses are another example . I can take a \textbf{race} horse and it will go faster than one you can buy . But i wouldnt steal a chocolate bar and throw it away for fun . Are you telling me you never stole anything? What if you want a big television for example . What are you going to go and buy one . Or a new fancy car.  I have luxury cars that cost over 50k plus . Lol are you telling me you would buy them . What about fuel dont try and tell me you pay for that\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/158 & \cellcolor{green!5}0.633 \\  \hline
  \cellcolor{green!27}\small Australia isnt exactly closest destination for little road trip now is it you \textbf{dumb} fuck?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Judgement Day the Jews are actually me and your bosses. They control the world, you live with a lot more freedoms than \textbf{common} people but the Jews own everything including you and me\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Pikeys v Alice Springs locals...  That's a fight I'd pay to see.    Seriously though. Not to interrupt the festival of Autism going on here, but people live in the middle of Australia lol. They own the land and know how to survive there. I'd give those soft \textbf{fat} fucks in the video 2 days with a \textbf{jerry} can full of water and a shade hut lol.\normalsize   & \cellcolor{green!27}Fat, Jerry & \cellcolor{green!27}Nationality - German, Physical Identity - Physical Features & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small How would they afford to live if they did this. There would be no one to rob in the middle of the outback apart from the occasional abbo\normalsize   & \cellcolor{green!5}Abbo & \cellcolor{green!5}Ethnicity - Aboriginal & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small sometimes not always Yeah bro cause every \textbf{Gypsy} is gonna be given 1.6mill and become entrepreneurs you silver spoon prick\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Matthew Gallagher i started with \textbf{nothing} and built it up . No o e gave me a pound i took some\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small sometimes not always You literally said when you were 16 you were given 1.6 mill, your words not mine. You either started with \textbf{nothing} or you were given 1.6mill.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Matthew Gallagher i borrowed 1.6 from somone its fair to say no point in telling lies but i still had to take it . You seem polite enough . How \textbf{old} are u and what buisness would you do if somone like me helped you with some money ?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small sometimes not always I'm 20 and I'd probably invest in a business or two instead of building one. You seriously need to get real and humble yourself, you were given 1.6mill which makes you very privileged and a silver spoon, \textbf{nothing} wrong with that as everyone would want to be given 1.6 mill. But what is wrong and what everyone despises is some guy pretending like he came from \textbf{nothing} and is a self made millionaire when in fact he was give 1.6mill.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small steerpike50 There's \textbf{nobody} to steal from out there.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Come to Russia, and you will see real Gypsys, caus true Gypsys have dark skin and \textbf{black} hairs, and dark eyes. They look more like \textbf{Indian} people , not European,white, at all;On this video, there are not true Gypsys, cause they are "too white" to be Gypsys.\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Some Gypos got ‘Evicted' near my town and the \textbf{old} people in the village acted like we'd won the Premier League\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Callum Jordan As an 11 year \textbf{old} \textbf{gypsy} them \textbf{old} people should be thinking a bout how their actions make people feel\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}3/22 & \cellcolor{green!27}13.636 \\  \hline
  \cellcolor{green!5}\small Nocturn Vaka not all gypsies are like that. I am a  young \textbf{gypsy} my self. Get your facts right\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small as a person who lives on a farm iv never had a problem with them, there are two medium sided \textbf{traveller} camps by mine and there has always been gypos about, for me they fuck with townies and most of them probably deserver it tbh\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Alice 224 you are a sub \textbf{race} and should not exist. Stfu and have the decency of never reproducing\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Edward Woodward I 100 would. They would never tarmac it anyways. They would dig up my \textbf{old} driveway, take my money, then never return. Because like I said, they're thieving bastards.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small john boss your an idiot for tolerating this filth . one day they will rob you \textbf{blind} . they always do sooner or later .\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Suckmyballz Gameplays thats a bit mean, do you normally like bullying 11 year \textbf{old} girls? I used to work for a drain maintenance company and my boss got a contract to clean out the drains in 22 of my counties \textbf{traveller} sites. You know what? All the sites we worked on except 3 were kind people who offered us a cuppa and actually helped us find our way around the sites and had a laugh with us. The other 3 sites we had kids trying to steal shit from the lorries and tools we were using and wanting to fight us (im 6'2", weigh 115kg and have been doing karate, muay thai, jui jitsu, wing chun and taekwondo for the past 20 years lol) and a 11 year \textbf{old} 5' \textbf{nothing} 100lb when wet little shit kept trying to spar with me! In the end we couldnt complete those 3 jobs coz they were too annoying so we left before things got ugly. The moral of the story? Yes some of them are cunts, but the majority were actually alright, which as is the way with any group of people, is usually the case. Obviously i wouldnt trust any of them, but then again i dont trust anybody anyway until its proven to me that they can be. If you think they're a problem thats fine man, you're entitled to your opinion, but venting your frustrations on an 11 year \textbf{old} girl is a bit out of order, \textbf{traveller} or not. In your defence though, if they wanted less hate, they really should clear up all their shit when they move on and less people would be pissed off at them and might not even mind them stopping temporarily in a field near them, as long as the burglary rate didnt go up too.\normalsize   & \cellcolor{green!27}Nothing, Old, Traveller & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}6/304 & \cellcolor{green!27}1.974 \\  \hline
  \cellcolor{green!5}\small gypsy \textbf{freak} im a fucking \textbf{racist} and fucking what\normalsize   & \cellcolor{green!5}Freak, Gypsy, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/9 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I alwsys wanted to fuck a \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@video star presets  Alice 224  good for you for saying that at you're \textbf{age} (11) you grow up fast as I did you already know prejudice an it is nice to see younger kids like yourself taking an interest and speaking out, I won't go to deep because of you're \textbf{age} but people love to go against and blame anyone they can so the blame isn't on them as well as seem to enjoy the drama that comes with, they seem to forget all the litter on our streets in general, did all that come from gypsies smh I say this as someone raised around gypsies (true gypsies, my late grandad and uncles have all allowed them to live on land they own/owned) not all people who claim to be true gypsies are hence where the \textbf{p\textbf{ikey}} term comes from Smh derogatory and used for all gypsies today, so now people paint you all with the same brush/name. I could mention the names of my late grandad or uncles that if you repeated them to you're parents they would know the names because my family has always been a friend of and associated with gypsies, but this is to public for that and I'm not a name dropper, trust me not everyone thinks like that, enjoy you're freedom culture and continue not to be a sheep to this bs government an ideology of society baby girl x.\normalsize   & \cellcolor{green!5}Age, Pikey & \cellcolor{green!5}Age - General, Nationality - Irish, Social Class - Working class & \cellcolor{green!5}4/237 & \cellcolor{green!5}1.688 \\  \hline
  \cellcolor{green!27}\small As for everyone else here who replied to Alice the 11yr \textbf{old} \textbf{gypsy} who more than anyone else in the comments has a right to talk on her own people, what is wrong with you smfh basically telling an 11yr \textbf{old} she and all her family should die etc 👏👏👏 wow model of humane society you lot aren't you.\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}3/59 & \cellcolor{green!27}5.085 \\  \hline
  \cellcolor{green!5}\small Gypo is actually quite afensive as my friend is a gypsy\normalsize   & \cellcolor{green!5}Gypo, Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small \@Suckmyballz Gameplays 1 You're an asshat. 2 She's eleven years \textbf{old} - would you care to invite your 11 year \textbf{old} child on here, so strangers can talk to her in such a vile manner? I bet your Mother and Grandmother don't know you go online and talk to 11 year \textbf{old} girls like that - shame on you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/59 & \cellcolor{green!27}5.085 \\  \hline
  \cellcolor{green!5}\small Lazy spitefull amd evil \textbf{old} farts who barely ever leave their hometown. Overly attached to their stinking shithole. Shitty people.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small They're not \textbf{gypsy} gypsies are Romani they aren't Romani they made themselves an \textbf{ethnic} minority back in the 1600's. Gypsies came from India and then migrated to east Europe then into the western world later where alot settle now. Travellers are Celts through and throughout in their DNA.\normalsize   & \cellcolor{green!27}Ethnic, Gypsy & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Callum Jordan because they're miserable \textbf{old} cunts that like making people miserable because they're boring an almost dead and no before you say I'm not a gypo\normalsize   & \cellcolor{green!5}Gypo, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Suckmyballz Gameplays that's racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Keeping it Real typical gypsys can't spell don't act like gypsys r all good I was shagging some \textbf{gypo} only there cus she has a bit of doe she told me how u make ye money the boys go out and do wat they do I mean and am bad cus am a dealer at 15 😂😂 least I'm not scum I sell to people who have broken dreams fiends middle \textbf{age} with no hope not rob cars and laptops and houses\normalsize   & \cellcolor{green!5}Age, Gypo & \cellcolor{green!5}Age - General, Ethnicity - Roma & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Darkcenturex 247 didn't ask for your life story but thanks for that very touching thought I'm not saying the new \textbf{age} gypsies are good I'm saying that they don't deserve to be classed and stereotyped I rest my case\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Keeping it Real your obviously about 11 with that username 😂😂 and I'm telling u wat happens with gypsys ino the whole \textbf{p\textbf{ikey}} heritage\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Ben P There is the lowest level of incompetence then there is you. That's like saying everyone from Sudan is exactly the same,or everyone from Texas. Your like a 40 year \textbf{old} man and you need to go back to school.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Callum Jordan dude that's \textbf{racist} its travellers or gypsies not gypos that's offensive\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Its an absolute disgrace the way travellers are demonized and hounded from place to place, if it were any other \textbf{ethnic} group  people would be jumping up and down screaming human rights abuse.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Real Views,I'm guessing from your irrational rant that you didn't get too much schooling buddy, and it seems you also suffer from Tourette syndrome?  Poor you 😥 But to answer your question, yes my Grandmother on my fathers side  was Romany and my mother was Irish so there's a fair chance of some \textbf{traveller} in that side too..Now crawl back under that rock you call home and try not to tax that teeny tiny brain of yours worrying about all of those big bad travellers, theres a good chap.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Alan Legg hahahaha u picked up \textbf{p\textbf{ikey}} shitt hahahaha whats that make you haha a shitty man hahahhaha\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I am from bulgaria and we have some of the Romani here and we don't hate them because of their \textbf{ethnicity}, we hate them because of their backwards traditions, for example women are seen as \textbf{sexual} objects, and they're thieves too.\normalsize   & \cellcolor{green!5}Ethnicity, Sexual & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Black} Reaper you sounded half way intelligent until you finished your stament with calling me an idiot, I'm a little disspointed really I was hoping for something worthy of debating, oh well maybe when your brain cells multipy eh?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@kenny chamnan another word for "\textbf{gypsy}"\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@The Blazing Dead   I've not heard that one before?Anyway getting back to your original comment, I dont believe I've said that I'd not debate anyone because they were stupid although I have openly mocked a few idiots whos comments the have been little more than idiotic \textbf{racist} and abusive rants, some were even deleted out of embarrassment after I'd shown them just how idiototic they actually were. Now about how travellers benifit the communities that they visit. Why should they benefit them in any way whatsoever who is their to benifit travellers in any way, all they ever get is harassment from police and councils moving them on as soon as they've pitched site and complaints from local residents, but maybe thats the problem, its become a perpetual conflict between travellers and everyone else so much so that battle lines are drawn on both sides long before they even arrive, maybe both sides need to take a step back and reassess how they interact with one another because they way things are going \textbf{nothing} will change.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/177 & \cellcolor{green!27}1.13 \\  \hline
  \cellcolor{green!5}\small Mate look can I explain. I'm a traveler myself and I won't lie we do have some bad apples buts it's the same as any culture , the reason you see us that way is because you or the media only decide to focus on travelers when something bad happens now that's not an insult to you it's just they way you've been thought to think of us but believe it or not saying all travelers ruin where they live is racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Don't you think about how that makes kids feel? I am a \textbf{gypsy} kid and that will hurt my feelings I am 11. And you have made me cry. Think before you do.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Bernard joyce no its not \textbf{racism} as pikeys aint a \textbf{race} there a community ! Of thieving dirty smelly \textbf{p\textbf{ikey}} cunts need drowning at birth\normalsize   & \cellcolor{green!5}Pikey, Race, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - Irish, Social Class - Working class & \cellcolor{green!5}4/25 & \cellcolor{green!5}16.0 \\  \hline
  \cellcolor{green!27}\small seen a \textbf{traveller} not long ago parked up with his wagon and horse, tbh with the way the government is going it would be quite a nice relaxing time, if you have steady work of some kind. anyway drove past steady as to not \textbf{spook}  the horse and guess what the guy put his hand up.... bit of respect goes along way\normalsize   & \cellcolor{green!27}Spook, Traveller & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Roma & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small \@Lange WernerSame everywhere. I work part time security at a shop and irish travellers are always the trouble around the area. They try to come off as innocent, but they are \textbf{nothing} but trouble. Just two weeks ago we caught them on CCTV stealing a JCB digger from a site next door to us.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small youre right bernard, its the same in every culture,,theres good and bad. i know a lot of travellers gypsys  through boxing,, some have become good friends, but i know some who are lowlife scum  who seem to think its their duty to con or rob \textbf{elderly} people.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small I see your point , but not all travellers are the same , I would never do any of those things but at the end of the day I still have to be called a \textbf{p\textbf{ikey}} and other horrible names and there invading my life\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small bernard joyce  Excuse me I've seen first hand some sites travellers have moved into and the complete dump they leave it in when they go. I've also seen the violent side of them as well and all over \textbf{nothing}. It's an arrogance they have\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Gypsy girl "I love to travel" GO ON HOLIDAY THEN!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Which do most hippie or \textbf{gypsy}.?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I'm pretty sure their aren't Any original English travelers they are either Irish or Roma and the Roma gypsies are actualy \textbf{indian} to begin with \textbf{nothing} to do with Romania\normalsize   & \cellcolor{green!5}Indian, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small An English person would just become a \textbf{tramp}, the dream of being a \textbf{gypsy} is too much for some\normalsize   & \cellcolor{green!27}Gypsy, Tramp & \cellcolor{green!27}Ethnicity - Roma, Gender - Female sexuality & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Time For change but they're isn't enough sites. for every mosque and tempel there should be a \textbf{traveller} site.\normalsize   & \cellcolor{green!5}Traveller & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I used to travell the \textbf{traveller} sites are full with long waiting lists.up and down the country.this is why plainng laws need to be relaxed for travellers to build  there own in the right locations.but most of the time thats green belt.just a thought\normalsize   & \cellcolor{green!27}Traveller & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small \@Mike Murphy near enough every \textbf{p\textbf{ikey}} i have mwt smokes weed and drinks alchol you fool stfu\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small ash wood yep thats a true \textbf{p\textbf{ikey}} sentence.\normalsize   & \cellcolor{green!27}Pikey & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Mike Murphy i never drink alchol you dosser and i commented that because a \textbf{p\textbf{ikey}} probarly you said something about clean people smokijg weed and drinking\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Mike Murphy we've had pikeys near a childrens play ground in the town where I live and they've absolutely destroyed it. Rubbish everywhere, patches of burnt grass where they've been burning copper cable, no local kids dared go to the park so it was exclusively the gypsies park. And when they fucked of they took all the metal poles and fixings. They always cry that \textbf{nobody} gives them a chance, only prove what ppl think of them by thieving and destroying everything around them\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small \@Patrick Doherty- Mosques, temples etc are paid for by the followers. They collect money (sometimes over years) and finally build them when everything falls in to place as they also need planning permission etc. I'm amazed the travellers haven't done the same. The amount of \textbf{Gypsy} builders and the money they have, I'm surprised they don't have a network of multi-story sites with all mod cons dotted around the country.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small its not always as easy as that, you wpuld have known if you didnt spend your whole life sitting on your \textbf{fat} arse.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Patrick Doherty \textbf{gypsy}'s just leave a mess wherever they go, no council or resident is going to have them anywhere near, people that use mosques or temples are decent and they're used for religion, being a \textbf{gypsy} isn't a religion\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Travelling wemon \textbf{age} horrible\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She is a \textbf{fat} pig that at best looks like a bloke with tits.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I bet her \textbf{pussy} tastes like piss and hasn't been washed like ever. she's probably got crabs and genital warts from her boyfriends unwashed \textbf{cheesy} bellend.\normalsize   & \cellcolor{green!27}Cheesy, pussy & \cellcolor{green!27}Nationality - Chinese, Social Class - Working class & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small She's \textbf{fat} and ugly lol\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She is \textbf{fat} and inbred.You have poor taste\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Inbred \textbf{p\textbf{ikey}} scum\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small Her home with wheels attached and her car is'... they pay for nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Nah she's just another dirty pikey\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small This is from the big \textbf{fat} \textbf{gypsy} wedding series which was brilliant!!  But can you show full episodes not just clips??😍\normalsize   & \cellcolor{green!27}Fat, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small They were probably a \textbf{gypsy}, in which case you should attack on sight. Or park a caravan on top of their caravans to see how they like it. Filthy cretins\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Red, Indian & \cellcolor{red!27}13 & \cellcolor{red!27}13/71588& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Roma}  & \cellcolor{red!5}Gypo, Gypsy, Traveller, Gyppo, Gippo & \cellcolor{red!5}278 & \cellcolor{red!5}278/71588& \cellcolor{red!5}0.38999999999999996 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Red, Commie, Nazi, Communist & \cellcolor{red!27}9 & \cellcolor{red!27}9/71588& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Pensioner, Old, Elderly, Elder & \cellcolor{red!5}81 & \cellcolor{red!5}81/71588& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Irish}  & \cellcolor{red!27}Pikey, Paddy, Chav, Piky & \cellcolor{red!27}77 & \cellcolor{red!27}77/71588& \cellcolor{red!27}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Pikey, Tacky, Common, Chav, Redneck, Cheesy & \cellcolor{red!5}83 & \cellcolor{red!5}83/71588& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Nobody, Brat, Zero & \cellcolor{red!27}99 & \cellcolor{red!27}99/71588& \cellcolor{red!27}0.13999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Nation, doctors, Immigrant, Alien, Migrant & \cellcolor{red!5}12 & \cellcolor{red!5}12/71588& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Blind, Dumb, Mental, Crazy, Weird, Freak, Dim, Spastic, Disabled & \cellcolor{red!27}40 & \cellcolor{red!27}40/71588& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - American}  & \cellcolor{red!5}Yank & \cellcolor{red!5}4 & \cellcolor{red!5}4/71588& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Ethnic, Race, Racism, Racist, Ethnicity & \cellcolor{red!27}113 & \cellcolor{red!27}113/71588& \cellcolor{red!27}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Slag, Tramp & \cellcolor{red!5}7 & \cellcolor{red!5}7/71588& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman, Sexual, Sex & \cellcolor{red!27}27 & \cellcolor{red!27}27/71588& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Fat, Lump & \cellcolor{red!5}18 & \cellcolor{red!5}18/71588& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age, Ageist & \cellcolor{red!27}20 & \cellcolor{red!27}20/71588& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Nigga, Black, African, Buck, Spook & \cellcolor{red!5}36 & \cellcolor{red!5}36/71588& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!27}Banana & \cellcolor{red!27}2 & \cellcolor{red!27}2/71588& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - European or anti-Europeans}  & \cellcolor{red!5}Brexit & \cellcolor{red!5}5 & \cellcolor{red!5}5/71588& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Southern European}  & \cellcolor{red!27}PIGS & \cellcolor{red!27}1 & \cellcolor{red!27}1/71588& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}pussy & \cellcolor{red!5}3 & \cellcolor{red!5}3/71588& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Faggot, Fruit, Gay, LGBT & \cellcolor{red!27}8 & \cellcolor{red!27}8/71588& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}Gay, LGBT & \cellcolor{red!5}2 & \cellcolor{red!5}2/71588& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}LGBT & \cellcolor{red!27}1 & \cellcolor{red!27}1/71588& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Jewish}  & \cellcolor{red!5}Oven & \cellcolor{red!5}1 & \cellcolor{red!5}1/71588& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Destitute}  & \cellcolor{red!27}Bum & \cellcolor{red!27}3 & \cellcolor{red!27}3/71588& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry & \cellcolor{red!5}2 & \cellcolor{red!5}2/71588& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - White}  & \cellcolor{red!27}Redneck, Gammon & \cellcolor{red!27}3 & \cellcolor{red!27}3/71588& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female age and physical appearance}  & \cellcolor{red!5}Witch & \cellcolor{red!5}2 & \cellcolor{red!5}2/71588& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Drugs}  & \cellcolor{red!27}Drug addict & \cellcolor{red!27}1 & \cellcolor{red!27}1/71588& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Aboriginal}  & \cellcolor{red!5}Abbo & \cellcolor{red!5}1 & \cellcolor{red!5}1/71588& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - Native-American;Ethnicity - Roma; Ideological and Political Identity - General;Age - Over 65s;Nationality - Irish;Social Class - Working class;Age - Youngsters;Nationality - General;Physical Identity - Physical (and Mental) Impairments;Nationality - American;Ethnicity - General;Gender - Female sexuality;Gender - General;Physical Identity - Physical Features;Age - General;Ethnicity - Black;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - European or anti-Europeans;Nationality - Southern European;Nationality - Chinese;Sexual Identity - Male homosexuality;Sexual Identity - General;Sexual Identity - Transexuality;Religious Identity - Jewish;Social Class - Destitute;Nationality - German;Ethnicity - White;Gender - Female age and physical appearance;Behavioural Addiction - Drugs;Ethnicity - Aboriginal;%.

\item The percentage of hate speech related words is 1.3298.

\item Considering that the variable \textbf{Ethnicity - Roma} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 954/2969 occurences of hate speech related comments.\end{itemize}\end{document}