\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_84.json :}\newline \par\Large\textbf {Title: \large  I signed up for a SUGAR DADDY site to see what they would ask for *ILLEGAL* }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small I also, am not interested in being a part of this lifestyle, but fun fact: At least where I live, it is actually not illegal to have \textbf{sex} with someone for money(the act of being a prostitute), it is only illegal to pay for \textbf{sex}, or \textbf{sexual} favours, with money(the act of buying a prostitute). There are actually like, a lot of laws in place to protect prostitutes and people working in the \textbf{sex} trade industry, because it's not regulated at all and can be very dangerous for them. And as much as you said that you have no disrespect or shame for the people who do live this life-style, I feel like there was a lot of it there... Also not sure what exactly you were expecting this site/app to be? Some sugar Daddy/baby arrangements are \textbf{sex} free, dinner meet ups, social/work functions e.t.c., and the older professionals are just paying for exclusive(closed relationship) which they don't have the time to foster-because of their work schedule and requirements-but a lot of the arrangements on these sites DO have \textbf{sex} in them, and I mean I feel like everyone kind of knew that? Idk, I'm just not really sure how you could come onto the site not knowing anything, and immediately disregard it as a job, because you personally had \textbf{nothing} but contempt for it from the start? It's not a job that I personally believe in, or would ever chose to commit myself to, but I also wouldn't just disrespect others like that, especially on a very public platform.\normalsize   & \cellcolor{green!27}Nothing, Sex, Sexual & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}7/260 & \cellcolor{green!27}2.692 \\  \hline
  \cellcolor{green!5}\small Your not really mixed \textbf{race} if you mention germany and the welsh whom are like neighbours in europe Ahahaha... u got any spanish? Any arabic? Any asian? That would be mixed... do a DNA test because almost EVERYBODY is mixed.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small To all of the \textbf{sex} workers out there: do not take advice from someone who doesnt know what "mixed \textbf{race}" is. To people who shame \textbf{sex} workers: if someone who is 18+ years \textbf{old}, voluntarily "sells their own body for \textbf{sex}", there is absolutely \textbf{nothing} wrong with that, you cant change my mind. If you have a job, you are selling your body. You literally need your body to do anything. The only reason why you think it's bad is because you think \textbf{sex} is taboo, which it isn't.To everyone out there: literally no one cares if you have a lot of \textbf{sex}, just make sure that you're getting tested and going to your doctor regularly.\normalsize   & \cellcolor{green!27}Nothing, Old, Race, Sex & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}8/117 & \cellcolor{green!27}6.838 \\  \hline
  \cellcolor{green!5}\small Is it \textbf{weird} to say that I would actually enjoy this because of my kinky side? Not just for money...\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small why does your bf look like a 50 year \textbf{old} dad already\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small You say that you aren't shaming these women who sign up for this platform, but you are. Imagine something that you've done that someone else wouldn't agree to, or that the mass majority of people wouldn't agree to/understand, and listen to what you've said in that light. You're shaming people for a choice that you admit that you don't understand.I've never been a sugar baby, so I don't have a truly complete understanding of it, but I've talked to a lot of people who have been sugar babies or daddies and most men aren't creepy. In fact, overwhelmingly most men just want someone to do regular things with. A good amount of these men also need a date for a function. Intimacy isn't just \textbf{sex}. I need everyone to stop thinking that intimacy is only \textbf{sex}. Intimate relationships look like a lot of different things: parents/guardians, friendships, coaches, mentors, \textbf{old} college/uni friends.... these are all intimate relationships and they all look different. The intimacy that you build with someone you're dating isn't just \textbf{sexual}, and if it is the likelihood of that relationship being long-term is low. Intimacy is not just \textbf{sex}. Intimacy is not just \textbf{sex}. If two consenting adults have \textbf{sex} -- then they have \textbf{sex} but that doesn't mean that that was what the money/allowance was for. You equating everything that these two consenting adults might do in an encounter or a week to a \textbf{sexual} relationship is unfair. Additionally, you said these men creeped you out for asking to meet up but in every instance that you showed all the men said a public place or left it up to you on the details. So again that's really unfair of you to decide that all of these guys are just \textbf{weird} \textbf{old} men looking for a quick fuck. You've written them off without actually knowing anything other than the assumptions that you have -- which at the end of the day means you know \textbf{nothing} at all. And no I'm not disregarding that there are creeps out there on these platforms, but there are creeps everywhere including in the medical field and schools, but we all still understand that that's a small minority within the overall community.As a YouTuber you put in the time and effort to make videos, you're frustrated even in this video about the fact that you've been demonetized many times. Why? Because you put in time and effort, and your time is something that is valuable to you; your time and effort is a commodity. Do not shame women for realizing that there is a market out there where their time, efforts, and whatever else non-\textbf{sexual} is a commodity that they can use to earn major money. 6k a week, or even a month, is a lot of money that can change a person's life. You may not know this but a lot of the women on these platforms or in these arrangements are putting themselves through school, are using the money to build a savings so that their future is stabilized, are just looking for someone to do the activities with that they love but for whatever reason can't afford, are single moms already working a bunch of jobs that aren't making ends meet, are using this as an avenue to network which is just as valid as any other form. You may not also realize that women get just as lonely as men. It's not easy for everyone to be outgoing and meet someone regardless of the kind of relationship. And as far as the \textbf{sex} thing goes, as I mentioned before just because \textbf{sex} is involved doesn't mean that that's what is being paid for. Additionally, many of these sugar couples agree to not exchange money if they enter a sexually intimate relationship. Also many of these couples are couples for years, naturally when you care about someone on a deeper level that you're also attracted to the possibility of \textbf{sexual} intimacy happening is there. Idk Alana, you said you have a friend who does or has done this and I just feel bad for her. Whether or not she takes offense to this video it's quite obvious what you think of sugar relationships. I tried not to be harsh-toned in this comment, and if I didn't achieve that I am sorry for that. Maybe you should reply to some of these men just so you can see and maybe get a better understanding of these sorts of relationships, but only if you go into it without judgment. TL;DR: This video was very unfair and very judgmental on the second half, but I believe that that's due to a lack of knowledge and understanding steeped in popular bias on these kinds of relationships.\normalsize   & \cellcolor{green!5}Nothing, Old, Sex, Sexual, Weird & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}15/796 & \cellcolor{green!5}1.884 \\  \hline
  \cellcolor{green!27}\small the comments here are \textbf{crazy}. i feel like she was so careful not to get her intentions misread and people still did it anyway\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small You're \textbf{crazy},  your boyfriend isn't so excited about "your experience " . Wasn't a good idea,  for my opinion,  his face tells me that.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small This is really \textbf{weird} , your going on the site to see what it's like for girls that do it just so you can drag girls who use this site? 👀\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Cheesy Stick this is soooo wrong 😭😂\normalsize   & \cellcolor{green!5}Cheesy & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Sometimes I kinda felt uncomfortable listening to you speak...First of all, you are not mixed ; you are a Caucasian \textbf{woman} who has ancestors from different Caucasian countriesSecond of all, you say that you're not shaming women who do this but you really areThird of all, you looked at all the body types and you said you didn't want to pick average because that's 'average' so you chose slim?? Who cares what it's calledFourth of all, I can sense you're character... and it isn't good. You know who you remind me of? Summer Mckeen.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small I think the guys who had horrible grammar who offered allowance are scammers. They would probably ask for your bank account number and other identifying info with the reason of "wanting to deposit allowance into your account," except for in reality they would rob you \textbf{blind}.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Hey! This is the first video of yours I've seen and I'm definitely going to subscribe love your personality aha Although you said to let you know what you think so I just wanted to politely mention that not all \textbf{sex} workers or sugar baby's do that work because it's what they feel is their only option. Let's support all women and their choices yay 😊\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Online is dangerous, these sites lure \textbf{woman} for trafficking so it's best to not give your information, once a number is shared they will be able to get information.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Fun fact: it's not illegal to charge for \textbf{sex}, but it is illegal to pay for \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Downvoted. I particularly take issue with the fact that this video it monetised, claims fssw is illegal (everywhere huh?) and paints \textbf{sex} work as a dirty, dangerous last resort. Educate yourself, and maybe you would see the problem with exploiting swers while profiting from stereotypes that contribute to unsafe working conditions.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Hey y'all! I have a \textbf{black} owned luxury hair business, I want my \textbf{black} people to support me. Like my hair page SylaraBeauty, shop : www.sylarabeauty.com Use code ( Everyday) at checkout to get 15 off your purchase\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small youre dating steven......for free....having \textbf{sex} with him...for free, how is getting paid for doing the same thing so wrong?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small how \textbf{old} are u?? also ur boyfriend looks so much older than you...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small You look like Lindsey Logan before she went crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small OMG WE HAVE THE \textbf{DAME} BIRTHDAY 🎁 AHHHHH WE SHARE IT WITH GORGE WASHINGTON AHHHHHHH\normalsize   & \cellcolor{green!27}Dame & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small i dont see how this would be a last resort kind of thing... youd be getting paid for literally going out to dinner with a man.... thats it... thats genius in my opinion?? and even if, \textbf{sex} work is a real job and theres literally \textbf{nothing} wrong w it.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small No offense, but you kind of ARE being a baby about this shit.I am a proud sugar baby, and we get exactly what we want. \textbf{Nothing} less.I have no shame seeing HANDSOME men who want to PAY me for the time and effort I put in? Fuck YAS. I'm not dating anyone, so what's the harmA sugar baby isn't an escort. A sugar baby isn't a prostitute.  We get nice things when we ask, taken out to fancy dinners, nice holidays, and all in the name of our dealings.  On top of being paid for being a loyal SB.There's \textbf{nothing} wrong with it. At all.You do you, and I'll do me, and maybe try not to shame people who do different from you?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/128 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small This entire video did feel like she was shaming people who are sugar babies and daddy's. I also don't necessarily think it's illegal to be paid if the agreement looks and is a relationship. Every single relationship has an agreement of sorts where both people get what they want out of the relationship. So what if it's money? A person should be allowed to do anything, safely,  if it doesn't harm someone else. But that's what I got from this video. Do what makes you happy and keeps you afloat. If it's trading intimacy for money, then more power to you. Intimacy is a feeling of close familiarity or closeness. Where intimacy could be more than just \textbf{sex} or for some people, just \textbf{sex}.Okay rant over.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/127 & \cellcolor{green!5}1.575 \\  \hline
  \cellcolor{green!27}\small Listen, I don't judge any \textbf{woman}... it may make you feel bad but other people need to pay their bills. It's not my life so I cant judge. Your boyfriend looks like Hey Arnolds Grandpa :o)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Speaking as someone who is \textbf{sex} worker adjacent herself, as well as someone with a lot of \textbf{sex} worker friends, please don't respond. The profile for shits and giggles is fine, but there's enough men out there who waste others' time, and the repercussion is that leading them on with responses will make it more difficult for people who actually do this for a living to get worthwhile responses.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small this is so \textbf{weird}>>>>>>>>>>>>;;....\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small The reason this is considered legal is because they found a loophole.  They're paying you for a companionship but you're also having consensual \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small no surprise they all want \textbf{sexual} favors what did you think this was lol\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small R Gonzales of what, her whiteness?? 😂😂 there's \textbf{nothing} to be jealous of\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small white people wanna be \textbf{ethnic} so bad but don't want the struggles of being a minority or adversity\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Y'all better hush on this app, that is not mixed😭😭 I'm \textbf{black} and white.. MIXEDT. white and white don't mix💀\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The allowance is actually for acting as in a relationship with the sugar daddy it can't be just fun travels and free money they expect \textbf{sexual} intimacy in return obviously\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Xoxo, Kierstyn I get why he was uncomfortable bc these creepy \textbf{old} guys are hitting on his girl!! of course he should be upset! i want to believe he  trusts that she wouldn't do anything, but he doesn't know who those creepy guys are!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small \@24601 coffee beans have I said that? I said women often don't get to choose who they marry, especially as marriage in the west comes at a later \textbf{age} (and Western women have little to offer besides their looks).\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Walla Williams why must her boyfriend tell her what is moral? She is an adult, she "should" know better.I agree that some other chump will probably marry her. That doesn't mean much though, since she looks a bit above the average \textbf{woman} (and the average \textbf{woman} consigns herself to her own misery by not creating a moral personality).\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small xerke and u also said women have little to offer besides like? That's extremely sexist. And why would women not be able to choose who to marry? Lol you make no sense and sorry but men don't have anything else to offer than women would and women are the more attractive \textbf{gender} of the species it's just facts most men aren't even attractive to begin w\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small This was kinda fun. My boyfriend would go \textbf{crazy} though 😂😂\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Autumn Poladian uh not sexist if it's true. Take a sample of the average western \textbf{woman}, does she willingly cook, take care of kids, clean the house and be submissive to the husband? No? Well too bad, the quality guys WILL find someone else.You can flail your arms about and say that it's not fair, but truth is truth.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small xerke and where did I say I base a persons worth solely on looks? That was you saying women have \textbf{nothing} to offer except for looks which is also extremely exist lol so you were the one basing worth on looks it wasn't me it's the opposite it's you. Women are way more skillful then men if it was one \textbf{gender} over the other, sorry but we would stay and men would die out and that's cold hard facts. yoU coUld FlaiL Ur arMS and WhIne AbOuT IT aLl u WANt BuT U KnOw ItS tRue. What I'm saying is true what u are isn't there's a difference\normalsize   & \cellcolor{green!5}Gender, Nothing & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/108 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small \@Autumn Poladian uhm if what I'm saying isn't true then why are you so upset? The dating market is very open now, there's no arranged marriages of any kind in the West and women generally don't have to hold certain qualities anymore to be eligible for marriage. That, however, doesn't mean the best of all men won't choose a more traditional \textbf{woman}. Why would a succesful man want to marry someone who has never tried?Sounds like you just don't want to accept reality!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small xerke you know that successful men don't go for traditional women right? They get someone equally successful you act as if women aren't successful. Matter of fact, 61 of people in the \textbf{doctors} field are women. That's more than men if you want to talk about success the roles will soon be reversed.\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small xerke I love when people act like they're winning when they're clearly not because the other person is basing unbiased facts about men and women societies while the other unintelligent one is trying to base a society off \textbf{sexism} and limitations because they are weirdly obsessed with oppressing women and thinks that is what will make a society last meanwhile all societies had that and it clearly didn't last and was outdated so everyone switched.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small xerke lol no sweetie you haven't been giving me facts this whole time that's why there are only three societies and natural selection will take place and get rid of you and them because it doesn't work. I wish your brain could comprehend this view of life instead of bused \textbf{sexism} you clearly can't keep up\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small xerke Judaism isn't a traditional society LMAOOOOOOOOOOOO omg I cant. Judaism is a fucking religion dumbass it isn't even a society it's group of people all over the world with \textbf{common} beliefs similar to Christianity and they can live in western areas they don't agree w that.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@Autumn Poladian "but le natural selection will remove you"Uhhh no? Those cultures are thousands of years \textbf{old}, surely they are doing something right! 🤗\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small xerke Judaism is the backbone of the Jewish society meaning it's the religion you \textbf{dumb} fuck that's exactly what I said 🤣 practice my reading comprehension implies I read something incorrectly but you didn't even state a definition that I could comprehend incorrectly, stop using insults to try to validate your points it isn't working\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small xerke so is Christianity every religion that arised is thousands of years \textbf{old} lmao and they aren't sexist and they're still here, sorry to burst ur bubble\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small First time on your channel and I loved the video idea. There's \textbf{nothing} wrong with showing how these type of sites and apps operate and how people interact there. I'd love to see what happens when you text them back.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small You know good and well you're going to meet some guy on here then you're going to start talking to him a little bit a time playing it off like OK this is \textbf{nothing} I love my boyfriend OK then you're going to go to write back to talking even more to him and then he may start giving you gifts and you going on trips and this and that and you'll be another prostitute basically same thing baby\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small I don't see how this is any worse than tinder...even might be better? Random \textbf{blind} hookup? Or a vacay and 600 dollars? If you're initially attracted to someone for consentual \textbf{sex}? Do you're thang girl!\normalsize   & \cellcolor{green!27}Blind, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small I don't think young girls should be doin this shit but if you decide to, PLEASE be smart and safe about it. Don't meet a stranger alone somewhere, especially late at night. Sounds like \textbf{common} sense but sometimes you think you know someone or you don't think it's a big deal. A girl in my city was MURDERED a few months ago because she met a stranger in the middle of the night at the park right across from me. Like I could walk there in 15 seconds. You don't know these men. Your life and self worth isn't worth a quick \textbf{buck}.\normalsize   & \cellcolor{green!5}Buck, Common & \cellcolor{green!5}Ethnicity - Black, Social Class - Working class & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small I am a Russian \textbf{woman} I am 22 I have been a sugarbaby since I was 19 and yes some want \textbf{sex} and not all of them are ugly and \textbf{old} sum are quite attractive and are nice and kind and sweet to you they won't do things that you don't want to do but there are also men that don't want \textbf{sex} they just want a companion your friend I've literally gotten paid just to eat pizza and watch TV and talk about life not all the men are \textbf{weird} I have gotten paid by playing chess 😂❤️There are some great men out there willing to help beautiful young women because they careEdit) now I am getting towards the end of the video and I'm not going to lie I feel a little bit offended she's shaming all the guys making them look bad they're not all bad really they're not the very few get a bad reputation for the majority of these men are basically just lonely decent looking guys that just happened to be rich or wealthy and can provide for someone that's younger I can provide for myself now but I honestly don't want to when someone else Can provide for me easilyEdit) also prostitution is more like you hook up you get paid sugar babies is more like a intimate experience a euphoric one that goes both ways it's not just for one night you're with this man for a week or two maybe extending on two years you grow feelings and they grow feelings for you too not really Like in love but still a kind of love they care for you\normalsize   & \cellcolor{green!27}Old, Sex, Weird, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/280 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small апокрифическая любовь I love this comment it's so true and relatable I am a sugarbaby I am 21 I started about a year ago and the very first guy I met I am still with Most girls don't have \textbf{sex} with their companion but I have had \textbf{sex} with mine he's a really good looking guy he's 24 he's not super rich but he can still provide for me he's a construction manager so he makes pretty good money he's super sweet and such a nice guy has never told me to do something I didn't want to do I had \textbf{sex} with him because I wanted to (we were both sober)\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/112 & \cellcolor{green!5}2.679 \\  \hline
  \cellcolor{green!27}\small Miguel Perez thank you for your opinion it was interesting to read I know you didn't say I was wasting his money but I just want to put this out there that I'm not wasting time I'm putting effort into something he's paying for my college tuition and I'm studying social science and working hard to get my bachelors degree physiology I want to be a \textbf{mental} health counselor and help people that's why I like being a sugarbaby I feel like I help him in a way.😊 Ethically speaking I have the right set of mind we better each other my intentions are pure.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/105 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small \@Yo baddest Bitch Some maybe waste the money on trips, some put the money to better use, some just live of other people and never work a day on their life. What I criticized is how people are trying to make it seem like you are not taking advantage of his loneliness. Like how lonely you gotta be to pay to spent time with somebody and receive female attention that you don't receive on a daily basis. You are smart because you saw the market and saw an opportunity. But it's still unethical. Why it's so hard to accept you are doing something unethical? Honest question, with all the respect you deserve. People shame \textbf{sex} workers, even women do it. But the term sugar baby that is basically prostitution under an umbrella it's seen as something alright.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/137 & \cellcolor{green!5}0.73 \\  \hline
  \cellcolor{green!27}\small What she says is so thoughtless. Sugar babies DEFINITELY earn their money even when they don't get physical for it, they pretend to be affectionate and intrested in someone they are definitely not into, it's acting. Please think for yourself, don't let society build your brain for you. "I don't want money to just be handed to me" okay, be a slave for capitalism then 🤷 let it boss you around all your life, let it not take care of you in \textbf{old} \textbf{age} and bad health. Don't take your life into your own hands or anything 👎\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Slut shaming. You think it's easy and anybody could do this? Right... Continue on YouTube and stop shaming \textbf{sex} workers...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I watched this video a couple of weeks ago and thought that it would be fun to try this to actually see what its like...........and when I tell yall this is a terrible thing to do this site needs to be taken down I met with a 51 year \textbf{old} man named luther at a local mcdonalds and the whole conversation was just uncomfortable and he was touching my leg the whole time. Just a very uncomfortable so I decided to leave luther gets up and yanks my arm leading me towards his car. I thought this man was going to kill me so I hit him with my phone got in my car and sped down the road. If anyone is thinking of doing this I beg you not to this is just another site that gets girls kidnapped.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/140 & \cellcolor{green!27}0.714 \\  \hline
  \cellcolor{green!5}\small I don't do this but I see \textbf{nothing} wrong with it as long it's with the girl's full consent. I don't know much about this but it's clear to me that the men can vary a little but most insist on \textbf{sex} but you have to meet and go out with the men for the sugar baby to get the money. The older guys with the lower testosterone are the ones more likely to be content with just a sugar baby's company. I heard women often sugar babies get gifts rather than cash. And even if they get paid for having \textbf{sex} with the men, I don't care, to each their own. My only issue is that both parties are fully consenting. Being a sugar baby is not for the \textbf{woman} who thinks they can get money and gifts without giving what the men want in return. Any girl who thinks they can be in and maintain such a one-sided relationship of any sort is painfully naïve and gonna get burned. Think of it this way (exclude family, close friends and charity work): would you give someone money or a gift for simply talking or being in your company and \textbf{nothing} more?   The answer is NO. I certainly wouldn't. And men definitely won't give something without something in return and most likely go on Seeking Arrangements thinking it's a place to meet women for \textbf{sex}. I'd suggest being careful on the sugar daddy for several reasons, some obvious but another reason don't consider is that the man may be fake and not have nearly as much money as they claim. I've no idea why a man that isn't rich would go on Seeking Arrangements since it's for wealthy men to find young women (or vice versa) - maybe to make a video like this or something more harmful. If it's just the hookup aspect there are plenty of apps that men can use instead and it won't matter to anyone if the people on them are rich or not. Anyone I don't care if someone chooses to do Seeking Arrangements or anything like it. Just be aware, safe and 100 consenting. If anything is telling you to back out at any point, listen.\normalsize   & \cellcolor{green!5}Nothing, Sex, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}6/373 & \cellcolor{green!5}1.609 \\  \hline
  \cellcolor{green!27}\small Mariah What makes sugar babies 'even worse'? How do you earn a living? Have you ever had a job? Have you worked as a cashier or in retail or literally anything? It's the same thing. \textbf{Sex} work is still work. Society has scrutinised it because of 'morality' \& deemed it unjust. They are still human beings and deserve respect as much as anyone else. It's not a \textbf{sex} issue, it's a human rights issue.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/74 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@regnilondon i think you took my comment the wrong way. maybe re read it and not get stuck on one thing i said. don't allow me to get you angry. we all have different opinions. \textbf{sex} work is all good until it's exploitative\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@regnilondon you obviously got upset over what i said. and it's exploitative because a lot of those men are lonely. a lot of them just want \textbf{sex}, but theres more that just want someone to go out to eat with. I knew of a girl who was a sugar baby and the \textbf{old} guy who was her sugar daddy literally paid her just to hang out. he was lonely ):\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small what did u espect signing there . another \textbf{dumb} video on youtube🤦‍♀️\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Hey I also have a number tatoo. It's 23. But, \textbf{tramp} stamp location. For one tree hill\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Mikky Bullshit she didn‘t text no one. She made a profile and received these messages -and she asked if he was ok with her making this video. He knew what this app was about so of course the messages you get there will be \textbf{sexual}. If he couldn‘t handle it, he should have told her before. But in my personal opinion it wouldn‘t be a good sign if your partner can‘t deal with that. You can disagree of course but I think jealousy over something like that shows little self esteem and that you don‘t trust your partner at all. I mean it was so obvious that her heart wasn‘t in it at all and at the end of the day YT is her job. If he had found this app on her phone, it would be a completely different story but it was \textbf{nothing} like that.\normalsize   & \cellcolor{green!5}Nothing, Sexual & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/147 & \cellcolor{green!5}1.361 \\  \hline
  \cellcolor{green!27}\small When a guy says he wants to be "FRIENDS" it means friends with benefits, and if he says he wants to have "FUN" that means \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small This \textbf{chick} is so naive but it's cute, it's a prostitution site honey.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small They EXPECT \textbf{sex} for any kind of money.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Canadian i was in a sugar relationship before and i was literally paid to just go on dates. not everyone expects \textbf{sex}. most of them do though.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small bf looks like hes gonna \textbf{age} badly and sounds hella controlling tf\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small You have plastic surgeries, in young \textbf{age}, but it's your body and your choice, some girls just like this lifestyle and that's what they want to do soooo\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@Breakfast AT Tiffanee Yeah because I'm responsible for the \textbf{dumb} system that men created decades ago. \textbf{Dumb} logic. Not everyone thinks the same and people change with time. Or you have the same mentality as your parents or grandparents?I know that shit won't change because like you said  most attractive women think like you. I just wish people would be better.You see a lot of movements about women empowerment and equality. But they never speak about stuff like this. Some women don't have to work a day in their life and just worry about someone taking care of them and to do what makes them happy for Society that's okay. But for men they tell you since you are a Little boy that you have to provide for your loved ones and if you can't you are a loser and aren't worth it🤷🏻‍♂️\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/145 & \cellcolor{green!27}1.379 \\  \hline
  \cellcolor{green!5}\small Raven \textbf{Black} Lol, their point was bad tho😂\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Raven \textbf{Black} Did you even read my explanation for what I said?😂\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I live in an area where people prefer to leech off of others rather than do anything for themselves using government aid. I honestly know people who have never worked a day in their lives who can fully support themselves because they lie to the government about their situation and receive obscene amounts of money in EBT (food stamps) or claim a disability when there is none. I absolutely agree that laziness is disgusting and breaking up a relationship is disgusting. However, that doesn't mean that someone who enjoys the lifestyle of being with a man, a \textbf{woman}, or anyone else to get money or vacations or dinner is wrong. Some people are willing to do things for money, and some will lie and cheat. Sugar babies should never be shamed for their lifestyle even if you don't agree with it. Personally, I don't have a dream career or anything like that. I just want to be married and have a happy life with my husband. Is that shameful? To some people, yes, but it shouldn't be. We can only see our very very limited perspective, and it isn't fair to judge anyone. I have a hard time with it myself, so don't feel like I'm calling anyone out or being hypocritical. Just try to love and understand others and have compassion for those you don't agree with <3\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/229 & \cellcolor{green!5}0.437 \\  \hline
  \cellcolor{green!27}\small \@Kendal Olguin Both are wrong ethically in this transaction. Women are taking advantage of lonely low value men. Like how lonely you have to be to pay someone to spent time with you.Women are smart for taking advantage of this market and getting money to get whatever they want. But let's not act like it's not wrong.  Low value men because money doesn't determine your value and high value men would never pay to spent time with some women who just want his money. Acting \textbf{blind} whenever we see something wrong it's what it's getting to this time we are living into. Both men and women gotta do better. We are better than this.And tell me I'm wrong. Now you can't call out someone when they are doing something unethical because you are supposed to "mind your own business". This why the "\textbf{gender} equality" the media always talk about it's never going to happen. There is double standard for everything. I try to be a better human being by calling both men and women when they are wrong.\normalsize   & \cellcolor{green!27}Blind, Gender & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/180 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small yeah she kind of is \textbf{dumb} and hypocritical... her poor bf\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small WHAT \textbf{RACE} IST THIS DOG OMGOSH\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small If I had money, I would be happy to use such an application because I need a relationship with a beautiful girl for health reasons. As a matter a fact, I need an affective shelter and to belong to someone in order to release the very painful muscular contractures in my back that make an every-second hell of my life, due to a very severe ptsd that makes me a \textbf{handicapped} person and a nightmare of my days and nights, and whereas I would never ask for a \textbf{sexual} relationship bc it is not what I need, and a girl like these sugar babies, if they look like you, could never possibly have desire for a man like me, but I suppose that at a moment, I would be very frustrated not to kiss. I have never kissed a beautiful \textbf{woman} in my whole life and tbh, I've been missing to know how it feels for my whole life - should I feel guilty, aren't all men the same ? I believe it's a basic need, only not vital - , although I had some adventures, but with girls who would not turn my head, though they were adorable friends. But I don't even have any money so I will never use this. However, I respect the girls who can accept this job, whatever their limits are, bc, I don't know if it is any part of their motivation, but they bring some happiness and maybe some kind of unforgettable experience, and thus, they also put some kind of an end to the \textbf{sexual} competition war that is such a cost for the world, except that the customers still have to be rich, unfortunately. Sorry for my english, for the seriousness of the comment, and for looking like a beggar, I think my reflexion is worth it anyway, bc it opens a lot of interesting and fundamental debates.\normalsize   & \cellcolor{green!5}Handicapped, Sexual, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/318 & \cellcolor{green!5}1.258 \\  \hline
  \cellcolor{green!27}\small \@stan loona "it SOUNDS creepy" ; again please, if you wanna discuss with me, please talk of the bottom, don't speak about how things look, thank you. My personal situation is basically totally creepy in itself btw. You have no consideration for what I write here. At all. 1- I don't need ( "want" amof though I hadn't said that yet ) a \textbf{sexual} relationship 2- my social situation and my handicap attract no \textbf{woman} 3- the women I could seduce even if I was not \textbf{handicapped} and if I had a correct situation would never be beautiful girls, even if I could care for them, that would never resolve the problem I'm talking about in my comment. Again, if you want to discuss with me about my comment, consider what I say in my comment, obviously, at my stage, you ought to understand I don't give a dam about how I look or sound.\normalsize   & \cellcolor{green!27}Handicapped, Sexual, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/155 & \cellcolor{green!27}1.935 \\  \hline
  \cellcolor{green!5}\small wonder girl yes it should because you're selling yourself for \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Nick The Great no it shouldnt. Just because you think its morally wrong doesn't mean everyone thinks that and it doesn't mean other people shouldnt be allowed to do it. Especially considering that people who prostitute themselves are often forced into it by \textbf{sex} trafficking or extreme poverty\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small \@Karolina Kobierska I agree with you that they know well on what kind of arrangement they are getting to. But if you think about it...the fact that somebody has to pay to spent time with somebody else. They have to be lonely af. And the fact that some women( in this case because \textbf{g\textbf{ay}} men also does stuff like this often) are okay with taking money for their bodies or for spending time with somebody they don't like or find disgust in them it's \textbf{crazy}. In my opinion both are wrong. But that's just my opinion 🤷🏻‍♂️And about the shaming, we are living on a Society that it's all about "body empowerment" "female empowerment". Because women were looked as less decades ago. Now I feel like men or even other women are afraid to call out other women when they are doing something unethical or simply taking the easy way out. It's all about "You do you gurl".\normalsize   & \cellcolor{green!5}Crazy, Gay & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/159 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small \@Miguel Perez well yes, maybe they are lonely but maybe they want easy \textbf{sex} or they are \textbf{old} and want a relationship with a young, pretty girl who wouldnt be interested without monetary compensation. Also "you do you (as long as youre not hurting anyone)" is a pretty good rule to live by. Life gets much easier when you dont concern yourself with what other people do 🤷🏻‍♀️ also i dont think its unethical - its a consensual agreement that does not hurt anybody so i see no reason to call people out. Thats just my personal perspective\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small \@Karolina Kobierska One perspective I've been thinking about is What are we teaching the younger generations? Would you want your daughter to do this kind of stuff? Younger generations has all this access to all kind of platforms or information. Which is good in certain aspects but I wouldn't wish my future daughter to be a \textbf{sex} worker or a sugar baby. I would do everything in my power so she could study the career that she wants, so that she doesn't have to rely on this kind of practices to pay for her college tuition.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small Brandalyn Williams in this day and \textbf{age} women don't have to sell themselves sexually. that's not all we're made for.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Karolina Kobierska okay but \textbf{sex} trafficking is different from being to lazy to get a proper job or finding an alternative.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Miguel Perez the basic concept of female body empowerment is for women to be able to decide what they want to do with their body. So YES women being forced into \textbf{sex} traffiking and/or prostitution is unethical, because these women are not deciding for themselves what is happening to their bodies. HOWEVER women are deciding to participate in these arrangements, and u are shaming them for it, so it seems to be like you actually dont understand what female body empowerment is about.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small Don't put ideas in young womens minds especially those who have financial gains on their minds and think this is all fun and games..There are \textbf{weird} people out there and theres no guarantee about who you are really conversing with when it comes to these apps or sites.Just looking at all the other youtube videos promoting sugar daddies also known as another form of prostitution..\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Okay let's be real clear we do not shame \textbf{sex} workers! Also sugar babying isn't prostitution\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small We don't shame \textbf{sex} workers but sugar babying is very much so usually prostitution\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Jassy If you read all the messages she received all were about having a "friendship" and meeting to "get coffee or something else" that's like basically a financial transaction to have \textbf{sex} lol\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small My bfs friends gf did this and she would meet these \textbf{old} guys at like restaurants and would just talk, so she said, and they would give her \$. Her bf would go before she met a guy and would sit a table or two away just to make sure she was safe. I was seriously contemplating doing it\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small He sounds controlling as fuck and annoying. plus he looks like hes gonna \textbf{age} so bad and go \textbf{bald} or sumn\normalsize   & \cellcolor{green!27}Age, Bald & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small You're going to spend this much time and effort to find out what middle-aged men want from younger women? REALLY?!?Young \textbf{woman} exchanges \textbf{sex} for money from older men who want to get their rocks off. There. Boom.*watches the rest of the video*I am so glad you addressed this in the video and believe me I'd never want to delve into the hellhole that is prostitution. It doesn't matter how you dress it, how you wrap it in a bow and use flowery language to describe it. A \textbf{spade}'s a \textbf{spade}. Not for me. SUPER GLAD you're not actually going through with it.\normalsize   & \cellcolor{green!5}Sex, Spade, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/105 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Poor bf 😂 scared to lose you to an \textbf{old} guy....\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I know some people that do this. You don't have to do anything \textbf{sexual} or sendnudes etc. Like my friend just says that sometimes they just want company or someone to just talk to. She says that she gets to set the boundaries etc etc\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small You're so gorgeous, I fr think you could make bank on one of these apps, but really respect you speaking up about \textbf{mental} health and taking a stand against earning money this way, and doing it in a non hateful way.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small CRYINGGGGGG Did she just say "mixed" and say different white. LMAO she dosnt know the difference between \textbf{race} and countries\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small White Americans love listing every \textbf{ethnicity} they are mixed with even when they haven't stepped on European soil in a century\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small -signs up on an app whose purpose is to help \textbf{old} men fulfill their \textbf{sexual} fantasies while helping young women fulfill their financial needs-receives a vaguely suggestive messageThis girl: surprised pikachu face\normalsize   & \cellcolor{green!5}Old, Sexual & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small So this is what a girl with fetal \textbf{alcohol} syndrome looks like up close...its annudah Greta.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I go out to eat with my grandpa a lot and I don't even wanna know how many times people have thought it was a sugar daddy thing. That's so \textbf{weird} to even think about, ewww\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I think I'm \textbf{g\textbf{ay}} now\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small 'Guys I'm so proud of myselffff'Ad: \textbf{Nothing} says confidence like an armpit packed with powerful chemicals like aluminum\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Nah, not in real life and not on these sites. People who have money don't just give it away for \textbf{nothing}, that‘s why they have money in the first place. They‘d rather donate it to a charity, buy gifts for their friends and family or collect expensive items. And you won't find filthy rich men of that caliber on those sites anyway, simply because they have better things to do with their time and meet insanely attractive and interesting people anyway.The only way those people will give you money „just because you‘re talking to them', is when they actually get to know and like you and for that you have to meet them and cultivate a relationship with them. Rich men aren't \textbf{dumb}, they are very aware of scammers and rinsers. That also goes for regulars who give very high tips to their favourite strippers, escorts and camgirls just to spend time with them and talk to them — they do this because they genuinely like them and have known them for some time.Of course you could meet a unicorn, that sweet older gentleman who isn't horny and just wants to makes you happy because he‘s smitten with you, but even he will want to meet you and be sure that you are who you are and that he isn't giving his precious money to a catfish.Stay realistic, stay safe and don't believe everything people tell to get attention.\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/242 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small I'm gonna laugh when this slut's boyfriend has a \textbf{mental} breakdown and murders her. It'd serve you right.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I thought the \textbf{thot} in the video was about as bad as they get. Clearly I was mistaken.\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Yes, you are mistaken. She was doing an 'American Uncovers' video to expose the site so viewers could be aware and educated.  He was acting like she was going to sign up, even though she told him numerous times 'this is for an informational video' and included him all along the way.  He gave off the illusion of being insecure, which was completely unnecessary as she clearly loves him.  She's no \textbf{thot}....how rude.\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small She is stressing him out giving him no clarification at all what the fuck she is on about. She's reading those messages and clearly enjoying or not caring about the fact that her boyfriend who is driving by the way is stressed out. Can you not read faces? Just look at the fellow, he is frustrated, annoyed, distressed, anxious and angry throughout the video. She is filming this all the while and putting it on the internet for all to see. And then in your view it is this very guy being in the wrong, the one who is being emotionally  harassed and denigrated for it by her and countless of thots in this  comment section. No one who watches this and reflects a bit gives a flying fuck about her \textbf{dumb} little attempt at an experiment for sugarsluts. The real experiment here is seeing how far you can push the buttons of your supposed loved one and see how popular it gets on the internet and how much it gets endorsed by similar simple-minded degenerates.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/176 & \cellcolor{green!27}0.568 \\  \hline
  \cellcolor{green!5}\small I do facetune now because of my acne. But i only get rid of that. No reshaping. (I sometimes make my arms look thick er because in some photos i have reaaalllyyy \textbf{thin} arms and i hate it.)\normalsize   & \cellcolor{green!5}Thin & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small men use these apps now to pay cheaper fees than they would for a prostitute/escorting service. So they are doing it to try and get \textbf{sex} cheaper which to me is quite sad and disrespectful to women happy as \textbf{sex} workers etc.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small don't want to sound \textbf{weird} but she is so pretty (:\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Let's be clear. \textbf{Sex} work IS work. Just because it's not for you doesn't mean you should judge others for doing it. If it's not for you, that's totally cool.For some women it's what they do \& they actually enjoy it. And it's a mutual exchange between two consenting adults..it's not always because they feel they have to- there is \textbf{nothing} wrong with \textbf{sex} work or enjoying \textbf{sex} work. So to anyone who is a \textbf{sex} worker or has done \textbf{sex} work in the past- there's no need to justify yourself whatsoever or feel ashamed. \textbf{Sex} work is work. <3 xx\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}7/102 & \cellcolor{green!27}6.863 \\  \hline
  \cellcolor{green!5}\small Also..if you did ANY or do ANY research..it's actually not illegal to exchange \textbf{sex} for money. Like working in a brothel as a \textbf{sex} worker is legal but actually running one is illegal. Maybe this is an opportunity to educate yourself on \textbf{sex} work \& that world. I say that in a completely positive way- hard to tell intonation with text. It's better to be educated \& informed about things we don't understand than to spread misinformation.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/77 & \cellcolor{green!5}3.896 \\  \hline
  \cellcolor{green!27}\small Sorry, I keep adding into these comments but you say you aren't and actually you ARE judging people who are \textbf{sex} workers. You're turning it into a joke when it isn't- you're right, it took a turn because you realised that it isn't a joke. You put 'intimate relations' in quotes and are telling girls that there are other jobs they can do other than this..that's what judgment is, thats looking down on someone who is a \textbf{sex} worker because you deem it wrong on some level. I'm not being hard on you..I am just saying what I see or my opinion because you put out a public video with this content making a joke out of a job \&/or lifestyle that millions have died for \& fought so hard for. Just perhaps is something to think about before you make a sequel to this.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/145 & \cellcolor{green!27}1.379 \\  \hline
  \cellcolor{green!5}\small \@regnilondon Let's be clear.  \textbf{Sex} work ISN'T work.  It takes literally \textbf{zero} effort or intellectual power to get on your back and do exactly the same thing a fleshlight could do for a dude looking for a quick cum dump.  You are good for absolutely \textbf{nothing} other than the wet hole between your legs, and you somehow think you deserve respect and validation for that lifestyle?  You're fucking high if you think prostitutes or porn workers for that matter, female or male, deserve anything more than to be relegated to the amoral fringes of society where they've always been.  Once your looks are gone you're just another used-up worn-out \textbf{slag} with no tread left on her tires and completely unwanted by anyone for anything more than a quick fuck, except maybe a few desperate beta males who literally can't get anyone else.  Good job making yourself completely undesirable.\normalsize   & \cellcolor{green!5}Nothing, Sex, Slag, Zero & \cellcolor{green!5}Age - Youngsters, Gender - Female sexuality, Gender - General & \cellcolor{green!5}4/148 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small J E WOW, okay. There is a lot to unpack in that but I will just say..I don't work in the \textbf{sex} industry but know lots of women who do- they are human \& deserve as much respect as anyone else. \textbf{Sex} work IS work, regardless of whatever moral ground you claim to stand on. I think you are incredibly ignorant \& that's all I'll say in reply.Have a nice weekend. :)\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small Keep deleting my comment roastie. Your bf is a gigantic \textbf{cuck} and you literally should've been kicked out of that car.\normalsize   & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Poor guy, he needs to find someone that's not a disrespectful \textbf{thot}. People in genuine relationships don't pull shit like this.\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Prostitution is legal now? Poor \textbf{cuck}.\normalsize   & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small If the boyfreind is reading this. Dont allow yourself to be exploited for youtube views. This is cruel and i can see it was uncomfortable for you. its obvious shes trying to assert that she has other options. Please remember that your better than that and you have other options too. Dont let yourself be degraded by toxic people because \textbf{nobody} deserves that\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Can you recommend a way to get rid of \textbf{double chin}. I noticed you got rid of yours. Have u tried kybella?\normalsize   & \cellcolor{green!5}Double chin & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Your honestly a really terrible person. I weep for society if this is the calibre of women coming of \textbf{age} right now.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Language Lover Being in a relationship requires commitment and faithfulness from both parts and towards each other.The moment she started this sugar daddy farse she broke those two,as if that wasn't already enough,she recorded herself taking advantage of her boyfriend for the solely purpose of money.SelfishGreedyUnfaithfulCruelThe only thing she has going is beauty,but it won't last forever.She doesn't know how to cook,clean,take care of children and her soul is rotten to the core.This \textbf{woman} is useless\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small I really hope your boyfriend left you soon after this video.  If he didn't, he's as much of a beta as you are a whore.  Would be nice if women like you were still shunned and left to grow \textbf{old} alone and unloved in society, instead of having your slutty tendencies validated by the slack-jawed masses.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Would have dumped you out of the car for that \textbf{thot} behavior.\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small its quite disgusting how little this \textbf{woman} respects her BF. BF is a \textbf{cuck} for staying so they are meant for eachother I guess.\normalsize   & \cellcolor{green!27}Cuck, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Gender - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small God, this was so fucking cringe! This \textbf{woman} is out of control. I would've stopped the car and told her to get the hell out! That shit would not fly with me! Shame needs to be a thing again! Too many double standards and no responsibilities. Christ.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Based 30-year \textbf{old} boomer.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Her boyfriend is such a \textbf{cuck} he should have slapped your ass\normalsize   & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Dus M. K. I agree with you on that every one is quick to judge and \textbf{nobody} takes the time to find out about someone\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small simple really, shes a millenial thot\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Language Lover youre wrong and the dude is basically already full blown cuck\normalsize   & \cellcolor{green!27}Cuck & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Stop deleting comments you \textbf{dumb} bitch. The disrespect you have for you boyfriend shows you don't deserve him.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small i think you took the wrong approach to this video and your privilege is jumping out. not everyone has the luxury of being able to make it on their own and as sad as it is to use something like this app, it's given a lot to people who've had \textbf{nothing}. your reactions are very judgmental and show how uneducated you are on this very subject. not everyone has the resources as you or someone who will support them, they're using this as a tool to get by and it's unfair of you to assume that people are using this just because.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small "Mup da doo didda po mo gub dat tum muhfugen PRIVILEGE bix nood cof bin dub \textbf{ho} muhfugga EDJUCAIT YOSELF"\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small 21:08 "let's go on vacation".. Tempting huh? This \textbf{thot} is gonna \textbf{cuck} him on the low someday if he doesn't dump her ass now. Begooooone THOT\normalsize   & \cellcolor{green!27}Cuck, THOT & \cellcolor{green!27} Ideological and Political Identity - General, Gender - Female sexuality & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small Looks like he's uncomfortable with his girlfriend being a (potential) whore. \textbf{Nothing} to do with insecurity actually...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Not leaving a \textbf{woman} when he gets a bad feeling about the \textbf{woman} is the biggest mistake men make in their lives....\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small He should have dropped her in the middle of the street and never speak to that bitch again.Imagine if a man did this type of  video,every cunt would be complaining about \textbf{sexism}.Fucking cunts I swear,thank God not all females have been pozzed\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small \@S. S. Cuck\normalsize   & \cellcolor{green!27}Cuck & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@jaree voldemort Cuck\normalsize   & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Yoitsu "\textbf{Cuck}"? That's all you have in your glossary you little sack of shit?\normalsize   & \cellcolor{green!27}Cuck & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Remember ladies, we're living in a \textbf{patriarchy} where a \textbf{woman} gets to browse for a sugar daddy right in front of her boyfriend, with no consequences. So opressed!Absolutely no respect for the lad there. I'd dump you right on the spot and make you walk miles to get your stuff out of my apartment."B-but im doing it for a videooo", that might be your excuse, but make no mistake, if you'd find some offer that actually interested you, you'd go through with it and abandon your S.O.Screw you and screw this video.\normalsize   & \cellcolor{green!5}Patriarchy, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/95 & \cellcolor{green!5}2.105 \\  \hline
  \cellcolor{green!27}\small Poor guy. I hope he finds a wholesome girl instead of that thot\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Cyonotic wtf is wrong with you? It's clearly for a fucking video, she's sweet well behaved educated plus beautiful if you call a combination of these 4 a \textbf{thot} then i agree\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I also signed up for a sugarbaby site (as a joke) and my profile pic was an empty wallet and my name was Eva. Some guy named Adam wrote me and i responded with: "Would you like an \textbf{apple}?" .....an he did nout lough and i deleted my account :))\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small If this isn't a sign that you were sexually abused at a young \textbf{age}, I don't know what is. You need help. Promiscuity doesn't make you happy deep inside dear.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small there's a bigger \textbf{pussy} at the wheels than on his rightDUMP THIS BTCH\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@Ella Sparkles That's your business, and yours alone.There should be  Mutual respect and loyalty forRelationship to survive in this \textbf{age}. It is evident from the video that she lacks any respect for him, it's all just an act.Since you overtly and vehemently supporting these very  behaviours..... You too are flawed.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small You really should shut up sometimes about things you know \textbf{nothing} about haha. Imagine being an actual \textbf{sex} worker. The risk of assault and murder is REAL. Not funny or a joke. Yes Seeking Arrangement is a real thing and yep lots of people are on there not to be a stupid lil girl like you. I know it wasn't mean in a mean way but making jokes about this stuff is what contributes to our risks. Bye lol\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small Sex work is one of the world's oldest professions and comments like yours literally kill us fuck you\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@oprah did 9/11 Wow I've not used it to support a drug habit nor have the other 50+ workers I have ever met. It's usually to support a student, family, or literally none of your fucking business. \textbf{Sex} workers have been PROVEN to have lower rates of STDs because we actually use protection even for oral \textbf{sex} (something most of you don't bother with lol). And increase crime how? It's not a crime to be a \textbf{sex} worker where I live. Imagine talking about something you know \textbf{nothing} about.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}4/87 & \cellcolor{green!27}4.598 \\  \hline
  \cellcolor{green!5}\small \@Katy Smith You are good for literally \textbf{nothing} more than the wet hole between your legs, and once you hit the wall and your looks disappear you'll be just another used-up worn-out \textbf{slag} and drain on society, whom \textbf{nobody} except the weakest of beta males will ever even touch.  Good job making yourself completely undesirable for anything beyond a quick cum dump.\normalsize   & \cellcolor{green!5}Nobody, Nothing, Slag & \cellcolor{green!5}Age - Youngsters, Gender - Female sexuality & \cellcolor{green!5}3/62 & \cellcolor{green!5}4.839 \\  \hline
  \cellcolor{green!27}\small Yeah, bc he's a little \textbf{crazy} jealous\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Oh yikes I was down with the video until she started shading \textbf{sex} workers...even though she's profiting off of using \textbf{sex} work as clickbait for her videos...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Please respond to some messages and create a second video.. I want to know how much these guys will explain about what they're looking for! This is so \textbf{crazy}, and an insight into a secretive/hidden world.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small FullMoonFullHeart not really. you always have a choice in life. this is just the easy way out. it's not a necessity to do this if you're in desperate times. hard work pays off. it's too easy and self destructive to go around having \textbf{sex} with men just because you're desperate for money. you have to realise there's so much in this world that you can do.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small He kind of looks \textbf{old} or maybe it's the angry face face from the side lmao\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Julianna Gatlin wait, what? once I \textbf{age} like not many years Imma make some coin off my gayness\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Never said I would leave my bf said if I was single and I was much younger and not the same person I am now. Now I wouldn't do it for any amount of money because I have my own business and have grown. Stop degrading women. Sounds like you got hurt by a \textbf{woman}, and your having a pitty party.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small I wouldn't want to ever meet anyone in person in fear of being murdered or imprisoned. Fuck that. I would want everything like the main comment says minus meeting in person...and no \textbf{sexual} pics either lmao just pics of my feet 😂\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Yeah, you have to be pretty for that. Sorry hun\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Jessica Daydreamer OMG LMFAOO I have some \textbf{weird} ass feet haha😂😂\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@INESSA no need to be pretty, to each their own. I even saw a website where men pays to have \textbf{sex} with very overweight women.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small what if your bf bought you a happy meal, and then you liked it so much, you had \textbf{sex} with him in the car at the parking lot. Does that make you a working girl? lol\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small People are UNEDUCATED about sugar babies-sugar daddies this is PROSTITUTION y'all are \textbf{dumb}, NO ONE is going to pay you that much to talk!!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@Yoitsu I think it's time for you to return to your elementary school playground so you can play kooty wars with your mgtow and \textbf{feminazi} friends over there. Leave the adults alone, please. Don't forget your baby aspirin in case the mere sight of a \textbf{woman} causes you to cry.\normalsize   & \cellcolor{green!5}Feminazi, Woman & \cellcolor{green!5}Gender - Female intelligence, Gender - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Ppm means 'pay per meeting.' Like for \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Oh wow girls that look like her flourish on those sites yawn \textbf{black} sugar babies are the REAL TEA. Much better content\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Check out popped by cherry 🍒 and her sugar baby story while \textbf{BLACK} thats tea sis. This....cliche\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@asha is right tho. Mixed and when you can't classify as \textbf{African} American or White; or White and Asian. Her \textbf{nationality} is entirely European but she was born in the US aka white.\normalsize   & \cellcolor{green!5}African, Nationality & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Ian Kin mixed means you can't be classified under one \textbf{race} but a lot of times when you're mixed you can tell what you're mixed with and ambiguous is when you can't tell but it doesn't really matter it's just one word😂\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small \@Kenna Tupper okay so if I'm \textbf{black} and indigenous (native) and a bunch of other things and i turned out lighter than a "fully \textbf{black}" person does that mean if you looked at me and said oh she's this.... Would that make me any less of what I am? Absolutely not 🤦🏾‍♀️the girl in the video is white. That's why I said what I said. There was an option for white and she still put mixed.... 🙄\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small \@Kenna Tupper sorry I didn't mean to attack you like that just yeah \textbf{race} is a touchy thing for a lot of people. As you can see from the comment section.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Girl you not mixed💀💀everybody has different nationalities, your \textbf{race} is WHITE\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small sica starr I think maybe they're just so lonely and blame it on the money. Ya know? That \textbf{old} saying 'mad at your money' or 'burning a hole in your pocket' It's super unhealthy but I think they know the reason they can't get real companionship is because they have so much wealth (and probably flaunt it a lot) and it attracts the wrong people. I feel for my fellow broke ladies who feel the need to sell their souls to a man for 6k a month. It's not entirely their fault that life is unaffordable but they're responsible for themselves, maybe even happy doing it. Idk how tho it's like they put a dollar amount on their self worth.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}\small I'm the only one who thinks all women need a sugar daddy... And not wasting their time with a dustie boy who has literally \textbf{nothing} to offer but a dick! We need to own our femininity and let the men provide... I see pickmesha''s commenting here like ow your boyfriend was so uncomfortable you have to  make it right and bla bla.. omg so BS!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Dj \textbf{Crazy} you figure it out over time lmfao\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Your boyfriend is clearly insecure and beneath you...A loving partner would not question your intentions.  You are beautiful and he is ugly but more important is his negative attitude.  He knows you are better than him and insecure.....Dont waste your time with him. I am 51 years \textbf{old} and met many nice men on seeking arrangement much nicer than your boyfriend and better looking and I am much older than you......\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small You must be trolling right?Otherwise you're just some dried up wine aunt in which case you just have to shut up and go to the nursing home already like a good \textbf{old} lady.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small 🤣🤣🤣🤣🤣🤣🤣🤣 deffo  he's a \textbf{fruit} loop by the look of it he's punching above  his weight going we her to xx lol pmsl  his face though 😂😂😂😂\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Well I genuinely hate \textbf{old} or grown creepy ass men who just wanna fuck around and degrade girls young enough to be their daughters. It disgusts me.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Sugar daddy sites are 99 middle class or lower class divorced idiots having a midlife crisis. They have no \$ and they expect \textbf{sex} from 18 year olds lol.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small That's \textbf{weird} as fuck if a guy finds this normal, his girl putting sexy pictures on an escort site. 🤮 imagine your man going on a site and looking at half naked women, and telling them he wants to fuck them, for a 'joke'.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small funny how only men complaining. Its a joke or at least if not a joke a reaserch for \textbf{woman}. If she with him she with him he dont have to be so protective. Its for a video and for reasearch. If my man is doing that honestly im fine with it. Besides she aint looking at no half naked pics of anyone.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small very random but i literally have all the same backgrounds as you (\textbf{ethnicity}).\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small PPM is pay per meet. This video is really overdramatic, and not very informative since you're completely inexperienced and just made a profile. There are plenty of videos of people who've done this, but basically girls are attracted to it for the money but it's very rare to find a guy who's just gonna throw money at you, pay your rent, etc. These are guys who want traveling companions (someone to fuck while they go on work trips) and the most you'll get is probably free dinners, in exchange for \textbf{sex}, obvi. Or a free dress or something. And yeah, the guys are usually \textbf{old} and ugly, and probably married. It's really not that big of a mystery\normalsize   & \cellcolor{green!5}Old, Sex & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/118 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Why is everyone up in arms about her saying she's a mix of different things. Stop taking \textbf{nothing} and trying to turn it into something.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small and I will say, the ones asking you to immediately text you and a weekly allowance they ARE trying to scam you. They'll immediately send you the \$, and ask you to buy gift cards, and send them the codes... so DONT text those ones. Lmao. As soon as you text them they'll delete their account.Platonic relationships on that site are rare. Some just want escorts. Most want a \textbf{sexual} relationship on the side.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small sugar daddy's want \textbf{sex}. why she playing \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I've always heard of various stories of 'sugar babies'. They definitely target broke university college students and it has become a new way to prostitute. It is scary to think of \textbf{old} men finding another way to take advantage of young women. I agree with you that it makes me feel very uncomfortable too just thinking that girls out there do this.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Who cares if it's prostitution? There is \textbf{nothing} wrong with prostitution and it should be legal.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Perry O'Parsonnes eating juicyfruit gum If you're physically \textbf{disabled} and mentally ill fresh out of escaping imprisonment by an alcoholic psychopath with a machete and have just lost your life savings to a scammer with no family, friends or anywhere to stay you're kind of in a vulnerable position. Like last night when I physically could not change my clothes by myself and was a complete mess crying over the results of my CT scan at the hospital and a guy twice my size took his opportunity to fuck me when I couldn't get up without my walking stick. But yeah, at least I have a couch to sleep on now.\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/111 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small Little Wolf Taima I didn't specify that this applied to mentally/physically \textbf{disabled} people. Obviously their situation/mentalities will differ from a regular, 20 something, fully competent, mentally stable female who just isn't in the best of financial situations. Yes, if that 20 something \textbf{woman} wasn't in the best of financial situations AND she was in some way \textbf{disabled}, that would be a different story. Regardless of your \textbf{age}, if you have a mentality that doesn't allow you to comprehend the repercussions or feelings of \textbf{sex}, then you are being taken advantage of. If you have a stable, healthy mindset and have made the decision at your own free will, you are not. Like I said, young \textbf{woman} ≠ child.But, that is a shame you had that experience and I feel for you. Obviously the man in that situation was at fault, though he wouldn't not have been under different circumstances, i.e. if you were not physically \textbf{handicapped} and in a bad \textbf{mental} state.\normalsize   & \cellcolor{green!27}Age, Disabled, Handicapped, Mental, Sex, Woman & \cellcolor{green!27}Age - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}8/163 & \cellcolor{green!27}4.908 \\  \hline
  \cellcolor{green!5}\small this app isn't technically meant to allow money for \textbf{sex}, a lot of my university friends used it to pay for education - they ended up literally just providing company (no physical contact) for lonely rich men 🤷‍♀️\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@Alana Arbucci i'm not using such sites, but as an entrepreneur and investor, who owns multiple companies, i ... got such offers sometimes from women. it is called catfishing. i'm a bit surprised how cheap those messages are, aren't they? in my experience, you are way out the league of your bf. so it eventually will come to your mind, right? if you meet somebody wealthier, this can get complicated after a while, having different life backgrounds. so, better check how he is. is he in good health? is he jogging? what did he study? so at least there's more to the relationship than money, \textbf{sex} and being a trophee. because for \textbf{sex} only the more decent weahtly friends of mine have escort girls and tinder. in my experience... chemistry is everything. maybe it is because i'm still in my 30's, better looking, so i never had trouble to meet women. but... i have troubles to imagine such "paid relationships" that extend more than 1 night myself, that is true. but the issue is, if you are at a party or in a club with friends, you can see instantly which girl is paid. the more serious, better educated or wealthier gf and wives will simply ignore you if you are sugar babe, which can be painful and insulting. a waste of time for me, but i know that it is quite popular, for instance inviting beautiful young women for a yacht trip etc. i suppose such things will never change.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/251 & \cellcolor{green!27}0.797 \\  \hline
  \cellcolor{green!5}\small sam Ragab Calm down. Not everything is \textbf{racist}. She literally didn't say anything rude, shut up.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small sam Ragab that's literally nit \textbf{racist}..?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small sam Ragab if anyone here sounds \textbf{racist} it's you\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small sam Ragab wait what are you talking about? Who is ashamed of being \textbf{black}, and wdym when you're mixed u are \textbf{black}? I'm also mixed with Italian and Filipino, and viet... how does being mixed makes you be counted as \textbf{black}??\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small sam Ragab you seem unstable no one is offended by this... OP is white... and you called her a '\textbf{black} bitxh' you're the \textbf{racist}. Why you saw the word white and decided to be \textbf{racist} to \textbf{black} people. Clown\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/39 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@sam Ragab you don't even make sense. no one was being \textbf{racist} lmao chill tf out\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Samantha Derrick does she look Asian to you, \textbf{African} or Middle Eastern, umm no. she's white. Ok.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Samantha Derrick did I say it was a \textbf{race} I just announced her \textbf{ethnicity} and its Caucasian. She called out all of Europe.\normalsize   & \cellcolor{green!27}Ethnicity, Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Jessi0 o Jessi0 o yeah she is Caucasian but that's a \textbf{race} and the next title heading on her phone looked like \textbf{ethnicity} which is more localised. '\textbf{Ethnicity}, however, refers to cultural factors, including \textbf{nationality}, regional culture, ancestry, and language. An example of \textbf{race} is brown, white, or \textbf{black} skin (all from various parts of the world), while an example of \textbf{ethnicity} is German or Spanish ancestry (regardless of \textbf{race}) or Han Chinese.' I think she was just saying a mix of things, not mixed \textbf{race}.\normalsize   & \cellcolor{green!5}Black, Ethnicity, Nationality, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!5}8/84 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Sarah alfakih she meant caucasian,not white. (Americans call whites caucasian which is \textbf{weird} and incorrect). Both arab and white are caucasian, that doesnt make arabs white or whites arab\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Giorgia M this isn't 23 and me or ancestry.com we get that she's fully white but she's not mixed \textbf{race} she's just white, like the queen of England isn't fully English she's also German but she doesn't call herself 'mixed'\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Crystal Malik \textbf{racism} doesn't exist. It was made up by a Russian Jew by the name of Trotsky. GetYour facts straight and dump that junk history you learned in public school.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Michael Castillo I'm not \textbf{dumb}, she literally called out white countries, stating the fact that she's 100 white\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@mbg140897 they didn't say it was \textbf{racist} she just described herself the wrong way\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small The world isn't \textbf{black} and white you fucking idiot.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Crystal Malik mixed doesn't mean your \textbf{black} and white🤦🏻‍♀️\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small mbg140897 lol when did someone say it was \textbf{racist}??\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The definition of being mixed isn't just the one you guys give it to it. You can be mixed \textbf{race} or of mixed nationalities. Not everything is about you. And the concept of being mixed \textbf{race} isn't even a concept that people know about everywhere. You probably won't see a lot of people use that kind of concepts or vocabularies outside of the usa even if they apply to it.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I didnt hear her say she was mixed \textbf{race} just mixed as she meant didnt ethnicities.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Yeah mixed doesnt mean \textbf{black} and white. My dad is mixed; he's Italian and Cherokee\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small There is not a 'white' \textbf{race}... you can be a mix of german welsh etc.. these are different races\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small zorp 12 Caucasian is the name for a white \textbf{race}. A mix of euro centric races is Caucasian, aka white\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Oh. And just to add something being "Arab" isn't a \textbf{race}. Just like how being "Latina/o" isn't. These places have very diverse racial backgrounds.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small akoisha mixed doesn't automatically mean \textbf{black} and white. We are all mixed you can't tell me that your 100 from a country. (Sorry for my english)\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Uhhh mixed doesnt just mean \textbf{black} and white.. anyone that is more than one thing is mixed\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Samantha Derrick africas \textbf{african} (mostly), europes european, asias asian (mostly), south americas south american(mostly) australias european (mostly), and north america is everything. suck it.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small zorp 12 those are nationalities.. white, \textbf{black}, australoid or asian with the rest just being mixes like latino and natives.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Mika Kokomi Being caucasian means you're from caucasus or have roots from there so you are incorrect, swedes brits etc have \textbf{nothing} to do with caucasus\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@Mika Kokomi No, english people have \textbf{nothing} to do with caucasus, they don't get to call yourselves caucasian, unless you're chechen, georgian, armenian or any other \textbf{ethnic} group of caucasus you are NOT caucasian, coming from someone with some actual roots from caucasus\normalsize   & \cellcolor{green!5}Ethnic, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small \@Mika Kokomi I don't have to read articles for your \textbf{dumb} outdated flawed caucasian \textbf{race}, not from caucasus? not caucasian.\normalsize   & \cellcolor{green!27}Dumb, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The fact that she said so many times she was just trying to see how it was and he asked 'u like this' 'so now your contemplating' reminds me of my toxic controlling \textbf{crazy} ex boyfriend\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@Artliker1234 I know a lot of guys that wouldn't. Just because guys like \textbf{sex} doesn't me they would sell themselves willingly. Especially if it was an \textbf{old} lady\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@thunderdrake13 it's about their boundaries, that's true. But the fact that he would even think that she is not joking about HAVING \textbf{SEX} FOR MONEY when she says so many times how \textbf{weird} it is for this kind of an app to even exist... kinda shows there is a lot more issues to how he feels about her. You can see how worried he is every second of this video, like he's gonna lose her any second now. That's not how a confident person in a healthy relationship acts... she is joking around but she should also see how uncomfortable he is, i agree with that. However, she should see that as a \textbf{r\textbf{ed}} flag more than anything else.\normalsize   & \cellcolor{green!5}Red, Sex, Weird & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/119 & \cellcolor{green!5}3.361 \\  \hline
  \cellcolor{green!27}\small \@thunderdrake13 i wouldn't. If it were the other way around i still would feel that the girl is overreacting. People joke about stuff all the time, and yeah, there are bad jokes that don't have their place in a relationship, but when you're saying time and time again how wrong something is only to then make a few small jokes about doing it, when that person shows no sign or reason actually going through with it, it's really \textbf{weird} to feel so insecure about it. This isn't about double standard, it's about a relationship clearly having some \textbf{r\textbf{ed}} flags.\normalsize   & \cellcolor{green!27}Red, Weird & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/99 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@Victonica \textbf{Black} there is a difference between a very realistic "prank" when you feel like everything is ruined and your partner cheated on you, and a few jokes about becoming a prostitute, c'mon.  If my man were to joke about that i would have a real good laugh. She says so many times that this is not something people should do, and even she feels a bit \textbf{weird} about it, but she was just curious about how far this whole thing is going and did it on behalf of all the people who are also curious. Since we clicked on this video, we obviously knew it wasn't supposed to be taken that serious and we were all just as curious. I get it if he really wasn't into this kind of a video, but acting like your girl is gonna leave you throughout the whole time and being so obviously scared about it is not ok. If he simply weren't that into the idea but still wanted to support her he would've told her in private then just let her be, knowing that in the end it is still just a youtube video and \textbf{nothing} is really serious. This just looks like he's scared of losing her but also scared of speaking up.\normalsize   & \cellcolor{green!5}Black, Nothing, Weird & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/213 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small \@Victonica \textbf{Black} yeah i know what you meanIt's just that him being uncomfortable makes everyone uncomfortableIf his reaction was something, like, you know, laughing along and stuff, the whole vibe of this video would be different\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Victonica \textbf{Black} you see this is what I hate about humans. They assume things and then they leave it as fact. WHEN IS NOT. Not because some people in your life know it all means the rest of the world does —it's kind of pathetic really. Believe it or not one of my friends were talking about this app \& look it up on this video to see what's up. You should travel more, get to know more people than your small circle. Maybe that way you get wiser.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small I used to be on this site and did not last because every guy just wanted \textbf{sex} in exchange for the gifts \& money....shocking...should of known 😂🙃\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small LOL as you say it 2:22 i look at the clock and its 8:22. alllllso \textbf{WEIRD} but funny- my friends and I have an ongoing joke about 22 because we always see it. whether its the time, or on a bus or graffiti. So weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small yes write them...and yes you get paid to call! ! he might ask you to prove its you but not in a nasty way! then they talk on the phone for 5 years...but you get a wad of cash..some guys will go to dinner...whatever..its up to you to kind of make the vibe clear..Just remeber things like coffe and meeting can just be that...especially at first! make ity clear thats all..its not scary..but id never meet anyone without\$\$\$\$\$ everything is money on this! everything..a call \$ messages\$ everything.. A sugar baby in 2019 doesnt have to be about \textbf{sex}..men need attention and friendship..the ones that have \textbf{sex}..probably make no money\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/110 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Everyone just wants \textbf{sex} 🙄\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small The allowance is to pay for \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Your bf's reactions are hilarious! So is this video in general. BUT.... I'm kinda surprised that you don't seem to really understand what they're asking for. These are rich and busy guys who are wanting to date and have \textbf{sex} with hot women, and they are willing to pay the women an allowance, buy them lots of gifts, and take them to nice restaurants in order to so. It's pretty straightforward. Young hot lady gets money, guy gets to be seen and have \textbf{sex} with young hot lady.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/88 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Did your friend do \textbf{sexual} things? Or just pictures? Just friendships?\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I'm always surprised when girls are offended these guys want \textbf{sex}. They're paying for a girlfriend that they can create conditions for (how many times they see you, if you guys are discrete, sometimes what you wear, etc). That's just as bad as you wanting a stranger to give you money you didn't earn through hard work. You're both in the wrong, but the element of being attracted to each other is still very much a thing.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small as  a \textbf{sex} worker watching this it's so funny haha\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The way you put down the \textbf{sex} industry and these jobs makes me feel really uncomfortable. Your not just being handed money, a lot of people just need company or a companion and by paying for someone's time it's mutually beneficial. Those who are exchanging \textbf{sex} services for money have the right to make that decision for themselves... it's a service in exchange for cash... therefore a job. Just like any other job. Just because you wouldn't do it doesn't make it a bad thing. I wouldn't work at McDonalds however it's not because ‘I'm too good for that kind of work'. It's just not my cup of tea, however if times were desperate and that's all I could do it's something I'd consider. However there's loads of people that would happily work at mcdonalds.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/135 & \cellcolor{green!5}1.481 \\  \hline
  \cellcolor{green!27}\small She totally wants to do this she's just trying to find out how to do it without having \textbf{sex} with someone\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small This is so dangerous! \textbf{Sex} trafficking is a real danger and this is the perfect platform for it. I'm glad you made this video and talked about the dangers.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small bahumbug 🙄 Why does everything like this need to be turned into 'racism' that's not \textbf{racist} to say you are a different mix of things. If we are getting technical, EVERYONE is, not just white people. Stop taking \textbf{nothing} and trying to turn it into something.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small mbg140897 ahahahahahaha 'why does everything need to be turned into \textbf{racism}' 😗sheesh sounds like YOU just did. I stumbled across this video and wanted to clarify, with my opinion solicited or not I can voice it but let's be honest here first generation Americans with parents descendent from a European country would still fit into the same box as a white American. It's truly not that deep. Anyone saying she's mixed is really reaching. Maybe their census or categories are different in European countries idk but here to me it seems pretty clear where she lies. So no boo you're using the word \textbf{racism} very loosely and sorry sis I'm not jealous\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small mbg140897 the way op liked this tweet just shows how much of a clown she is, white ppl don't face \textbf{racism} bc you don't !! suffer from oppression, get it thru ur thick skulls\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Samantha Derrick THANK YOU. as a mixed european, we definitely are different from each other and it's important to remember that because it can even affect medical things. like i'm in the uk, my dad is half italian, i'm quarter, but not being in the sun so much hits me (and him) much harder than 100 british people with my vitamin d levels for example. this also means those with darker skin in a place with less sun are much more at risk. tiny things like that can impact an individuals life so much!i'm sick of people treating \textbf{race} like it's the only thing. maybe i'm just used to the uk being so diverse depending on location, but it's baffling to me that people don't realise this\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/128 & \cellcolor{green!5}0.781 \\  \hline
  \cellcolor{green!27}\small Samantha Derrick Algeria is a country and every white American calls a \textbf{black} person \textbf{African} American why cant you just say American full stop.\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Aryaxna Mostly because we're not that \textbf{old} of a country,  and we're still proud of what our ancestors did to get here. I'm third generation  Italian American,  which is my closest tie to Europe... But I've also got Irish, German, Scottish, and Native American \textbf{Indian} as my genetic background. In the melting pot of the world, I guess it's kinda cool to still know where you came from. 🤷🏻‍♀️❤\normalsize   & \cellcolor{green!5}Indian, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small You mean white and Asian. 'Mexican' isn't a race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@lcveless as a non white what world are you living noone oppressed and white people get just as much \textbf{racism} as everyone else what part of that dont you get\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Obviously being a sugar baby is not "being friends", more like escorting with an \textbf{age} imbalance. They're not paying thousands a month to hold hands.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small What a sweetheart. God bless you. And so smart at a young \textbf{age}. Alana, you give good advice. No wonder your YouTube channel is doing well. Keep it up. I need to start a new channel/s. Activism is difficult and dark. I should start a business, art or entertainment channel to make extra money and show my talents. I am over 50 now. Photo is from 10 years ago. Anyways. I even though about getting a rich guy (just 1) to take care of me. Being an activist is difficult when no salary and only volunteer while fighting powerful special interests, including mass media. AlternativeMedia \& AlternativeHealing by MayaBell\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small I tried doing that and they all wanted \textbf{sex} lol i was like NOPE! 😂I'm a bartender so i make good money without sleeping with anyone.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@Sarah Marie3 Some men just want company. All the ones I talked to wanted \textbf{sex}.But at my job they give extra tips for more attention from a beautiful girl 💁🏻‍♀️Which is why I decided to keep bartending and not meet creeps from the internet 😏😏😁\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small What do you think? Obviously \textbf{sex} dummies lol\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small ethereal angel someone's \textbf{g\textbf{ay}}  😋\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small arii e mari games if you think I would honestly ever be a \textbf{lesbian} you're out of your mind 😂😭\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small ethereal angel  lol I wasn't talking abt you it was a \textbf{g\textbf{ay}} who commented\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Lol this website can actually be really good! A lot of times it's just straight up prostitution (which honestly I have no problem with as long as it's safe and consensual) but most of the time it's either REALLY busy guys who dont have time for a relationship, a really lonely guy who can't find a relationship, or a really "unattractive" man who feels like he has to pay for companionship. A lot of the men on there have a lot of money and want to go on vacations and to nice restaurants or to watch a movie but they have \textbf{nobody} to do that with so a sugar baby kind of works out because they're someone to share your experiences with and to provide fun and companionship to your time away from work or to their lonely lives. It's pretty cool! If you put in your profile that any physical intimacy is off the table you'll get less messages. Also, they usually want to meet you right away because they want to see if they like you and can talk to you because if you don't vibe you're not going to have fun together going out to do fun things or going on vacation. My friend had like 3 sugar daddies from SA in college to help her out and she never had \textbf{sex} or kissed any of them. They hung out in public, did fun activities, they would take her shopping, help her out with bills, etc. She loved it! The only reason she stopped was because she got into a serious relationship and he didn't like it, lol.\normalsize   & \cellcolor{green!27}Nobody, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/271 & \cellcolor{green!27}0.738 \\  \hline
  \cellcolor{green!5}\small Wrong. No honey, he does \textbf{nothing} for two reasons: 1) he doesn't really gives a sh\$t or 2) he is fuc\$ed up on the head. No men will be ok his girl does this sort of experiment 😂 it's same as pimping his girl....just for experiment lol\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small alena s First off you were stupid enough to stay with a guy, have \textbf{sex} with a guy and control how you used your Instagram for a guy who had no intention of investing in you or marrying you. Sounds like free prostitution to me. Secondarily, her boyfriend GETS IT. They're mature enough to do something like this for a YouTube video. There was complete transparency. Your man didn't give a fuck about you and still controlled your pictures sooooo... I guess your logic is wrong, babe.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small \@alena s lmao girl you dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@alena s you're \textbf{weird} for thinking he should be more controlling and not let his girlfriend do little things like this just as an experiment.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small This is \textbf{crazy} haha so many ppl with these dates\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She sounded like this one \textbf{woman} from American horror story xD\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small he seems angry and uncomfortable. can anne hathaway look alike stop pretending to be \textbf{dumb}. we all know sugar daddy sites is meet ups for \textbf{sex}.\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Hannah Mares-Montoya lmfao!! Triggered much \textbf{thot}? Hannah can't seem to take criticism... hmmm imagine that. Again, Hannah you have to use filters because you have unironically hit the proverbial wall at 24. You will never find a good man...ever.\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small GURL. Chill out!! It's one video and it's for fun. She has a boyfriend who loves her and she loves him. Dang \textbf{old} ladies like you shouldn't be on here if u get offended or hate every single YouTube video. Like chill outtttt. You're the only one making a big deal out of stuff\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small 'They don't ask me for \textbf{sex}, they just want a companion on vacations, ect'. Says every sugar baby 😂😂\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small so the thing is, women are always gonna be objectified and oversexualized by men so there's \textbf{nothing} wrong with women wanting to take that power and make money off of it. especially because \textbf{fatty} rich corporation CEOs who are males, financially benefit off of  women everyday (VS) lmfao. get your bag ladies!!! be one of 'those girls.' \textbf{sex} work can stop being villainized now and people can stop referring to it as a last resort, as if having a desk job at a business is super dope lol.\normalsize   & \cellcolor{green!5}Fatty, Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}3/88 & \cellcolor{green!5}3.409 \\  \hline
  \cellcolor{green!27}\small plus lolllll, women didn't enforce oversexualization of tits ass and \textbf{pussy}, originally men did so like how are we to be slut shamed for it because we embracing it? damned if u do, damned if u don't\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small I agree 100 however it does become is an issue (legally) when women perform physical \textbf{sexual} acts in exchange for money, at least in this country.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Alana Arbucci that is also true, but i'm more so talking about the stigma and mistreatment of women and \textbf{sex} workers in general. i can get where you're coming from at a legal standpoint tho 🤷‍♀️ and i don't condemn you for promoting following laws either\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small I am so glad you did this video because there is a entire youth that could consider that type of site and it is absolutely scary. No ones body should be able to attach a price to it. Any girls thinking of this I really hope you really consider any other option to make money you are worthy of respect and you matter. You can do it on your own you don't need a \textbf{old} man daddy who wants to live out his creepy role plays with you. Girl get to work and take yourself to spas and vacations without the violations. I am not meaning to rhyme lol apparently when I am passionate about something I turn into Eminem ahhaha\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/121 & \cellcolor{green!5}0.826 \\  \hline
  \cellcolor{green!27}\small Obviously they want \textbf{sex}, but I knew someone who said if you tell them upfront you're not doing anything you can weed out all the dudes who will make the moves and find someone who just wants to be friends and is lonely as hell. Depends on the person, some guys just are so lonely they want company and will literally pay for it.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small Tinder and POF can be the same thing as that. People hide who they truly are. I've had girl ask if I was down for \textbf{sex} and it would cost this much...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I totally understand that. I had a friend who is \textbf{transgender} and would catfish men and sugar daddies on tinder/sites for money, trips and hookups. She passes as a female VERY well and doesn't tell the guys she sleeps with. We used to work together (she paid the rest of her rent that way alot). This one dude would fly her all over the place. She'd show me pics.. And I was like damn! I feel like in another life I would do this to get out of rough spots. But only if needed and with no \textbf{sexual} favors. I heard that's a thing.\normalsize   & \cellcolor{green!27}Sexual, Transgender & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small hey-- I'm so sorry you went through a tough time, but I couldn't help but notice how apologetic and almost ashamed you were writing this. Don't ever apologize or put yourself down for your decisions (especially ones that do not hurt anyone!)-- you don't owe anyone anything. There's \textbf{nothing} wrong with being a sugar baby, a companion, an escort, a \textbf{sex} worker, etc. Society just deems it that way, but you do you sis and it's all good.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/78 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small D1G1TALSYNAPS3 lol she wont be saying that when her future spouse cheated on her with a \textbf{sex} worker\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Have you ever heard of punctuation marks? Your entire stupid story about these \textbf{old} morons was hard to read.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@A M Hopefully you will learn to be less judgemental about women's lives you know \textbf{nothing} about, nor are entitled how she should live it. Wish you the best <3\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small You've been through so much! Wow! That sounds like it was a really overwhelming \& stressful time for you. Just want to reach out \& let you know you shouldn't feel ashamed at all, you have no reason to. \textbf{Sex} work is work. 'Society'..humans..are \textbf{weird} \& are slow to change. It should be decriminalised \& it would make it a lot easier- but you don't need to justify yourself in any way, shape or form. Other people's hang ups \& judgements on it is their own thing \& tied to moral things usually from their upbringing. <3\normalsize   & \cellcolor{green!5}Sex, Weird & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/97 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small i can understand stand that. i've never done that and I'm definitely not planning on ever doing that though. it would be too scary and \textbf{weird} for me\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@Jacqualyn Horbury Funnily I also got into it after being in a long term relationship where he lost all \textbf{sexual} interest in me and it destroyed my self esteem.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Honestly, I feel as a dude, I'd never have that option for a way out like that. It feels as though you're trapped with no way out. \textbf{Nothing} of that sort is ever on the table. God forbid, a loved one has a health issue, I will die with their debt basically.The world telling you you're useless is a way of life. The only way you're useful is if you have money. Mom has cancer? Work your 9-5 and hope to God that you win the lotto, get a promotion, or just let her go :/.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small chun li yea that app is full of cheap \textbf{old} creepy guys\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small We all know what you mean filthy \textbf{fatso}.\normalsize   & \cellcolor{green!27}Fatso & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Doesn't happen. I live with him and he gets what he wants when he wants it on top of me doing all the cooking and housework. I'm doing it because I'm \textbf{disabled}, fleeing domestic violence, was homeless and I'm saving up money from him and my part time job to get out and start a new life. It's not glamorous and you will feel under pressure.\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small So you would rather give them \textbf{sex} than the money LMAO OK\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small BreakFerFun stupid? Says the one that can't even spell \textbf{woman}. Ffs u clown\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small BreakFerFun you sound like a 27 year \textbf{old} man that blames the way he acts because he's apparently a ‘sociopath'\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Why should you get something for nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@BreakFerFun don't come for me I did \textbf{nothing} wrong smh\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Lol! The fellow is turning \textbf{r\textbf{ed}}   really interesting vid. Have an awesome week.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Lovely Krissy nice filter \textbf{fatty}.\normalsize   & \cellcolor{green!27}Fatty & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small BreakFerFun It's her life, you don't have to be a douchebag and insult a person's profile pic.  If your self confidence is so low that you mock girls to feel better, I hope you get a healthier mindset.  If you don't like the filter, okay cool.  Everyone has different tastes, but that doesn't justify making fun of a random young girl on the internet.  \textbf{Nothing} productive comes out of you calling a person \textbf{fat}, I don't understand what your goal was.  As for Lovely Krissy, I think you rock the filter.  Don't listen to what others say, you look greatest when you feel like a damn queen.\normalsize   & \cellcolor{green!5}Fat, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small \@BreakFerFun yo wtf man? Literally for you to comment something completely different that has \textbf{nothing} to do with the comment is a waste of time. Especially under an Alana video when she stands for positivity and anti bullying. Literally  ridiculous!! I know you just commenting this to get attention but goddamn learn how to be nice tf\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small K so I signed up with SA and met a couple guys. I signed up like last spring or summer until I met my now boyfriend. It really is a crapshoot haha some guys wanted like a non commitment travel girlfriend or in town main squeeze, the offers usually consisted of obvi \textbf{sex} but always with an allowance of \$1000+. Some would be in my area and some would be in other states offering to fly you out to their city or two like LA or NY for a nice 'no expectations' dinner or to spend the day together. And yeah the dudes on there are pretty quick to give you their onfo or some app where you can videochat so they can see you and know you aren't catfishing.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/130 & \cellcolor{green!5}0.769 \\  \hline
  \cellcolor{green!27}\small cal Yes and I don't regret it necessarily because I was incredibly fortunate to have met and gotten to know some pretty decent men. However, seeing as its a specifically labeled for those greater \textbf{age} gaps and straight to the point reasons kind of relationship, it's not something that I can admit to and feel all too great about.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small jaime thaisamsen be smart and meet in public so they don't have a way of locking you in their basement.. just use \textbf{common} sense and be aware of your surroundings. Same thing if you're meeting someone from tinder or anyone you've met on the internet\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Ajay Thakur No, she's disgusting and should never be a role model for any young \textbf{woman}. Imagine being this dense and retarded.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Ajay Thakur go to sleep weirdo\normalsize   & \cellcolor{green!5}Weirdo & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@sam Ragab If you have \textbf{nothing} nice to say, why are you saying anything at all?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@sam Ragab FFS . DID SHE HAVE \textbf{SEX} WITH THOSE MEN? WDYM SHE LIKED IT? cuz the only thing i see is her trying it out for A VIDEO . Ur fucking \textbf{dumb} literally  fuck off\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Alana Arbucci he is \textbf{nobody} \& talking BS I like how you deal with haters/mean people in general\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small sam Ragab LMAOO what planet are you on? No one be spitting on me, not everyone is so negative like you yknow. And i aint defending anyone it's just your comments r just ugly and if you carry on the way that you do irl or anywhere else then you could seriously harm someone and for what? What do you get out of it? \textbf{Nothing}. So again, learn how to deal with your problems in a different way please for the 10,000th time i will say this. Just trying to help\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small sam Ragab you are so upset over this random \textbf{woman}'s actions that we can't help but wonder if all of this hit a nerve. People don't usually get so upset, unless the issue is personal to them. The question is, why are you so upset over this \textbf{woman} that you will never meet?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small \@Alana Arbucci You are just using his weakness,because is a weak man,and try to rationalise your whorish behaviour.In the future you'll regret it,besides beauty you have \textbf{nothing} to offer,once you hit the wall and lose your beauty you'll become bitter and start complaining about the lack of real men.This generation is ruined\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Sex, Sexual, Woman, Dame, Gender, Sexism, Chick, Patriarchy & \cellcolor{red!27}174 & \cellcolor{red!27}174/51955& \cellcolor{red!27}0.33 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Zero, Nobody & \cellcolor{red!5}47 & \cellcolor{red!5}47/51955& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Race, Ethnic, Ethnicity, Racist, Racism & \cellcolor{red!27}42 & \cellcolor{red!27}42/51955& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}32 & \cellcolor{red!5}32/51955& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Weird, Crazy, Blind, Dumb, Mental, Handicapped, Disabled, Weirdo & \cellcolor{red!27}59 & \cellcolor{red!27}59/51955& \cellcolor{red!27}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Cheesy, Common & \cellcolor{red!5}4 & \cellcolor{red!5}4/51955& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, Buck, Spade, African & \cellcolor{red!27}29 & \cellcolor{red!27}29/51955& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}14 & \cellcolor{red!5}14/51955& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}doctors, Nationality & \cellcolor{red!27}3 & \cellcolor{red!27}3/51955& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Tramp, THOT, Slag, Ho & \cellcolor{red!5}14 & \cellcolor{red!5}14/51955& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay & \cellcolor{red!27}4 & \cellcolor{red!27}4/51955& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, Fruit & \cellcolor{red!5}5 & \cellcolor{red!5}5/51955& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Bald, Thin, Double chin, Fatty, Fatso, Fat & \cellcolor{red!27}7 & \cellcolor{red!27}7/51955& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Behavioural Addiction - Alcohol}  & \cellcolor{red!5}alcohol & \cellcolor{red!5}1 & \cellcolor{red!5}1/51955& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Cuck, Red & \cellcolor{red!27}12 & \cellcolor{red!27}12/51955& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Apple, Red, Indian & \cellcolor{red!5}5 & \cellcolor{red!5}5/51955& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}pussy & \cellcolor{red!27}2 & \cellcolor{red!27}2/51955& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Hun & \cellcolor{red!5}1 & \cellcolor{red!5}1/51955& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female intelligence}  & \cellcolor{red!27}Feminazi & \cellcolor{red!27}1 & \cellcolor{red!27}1/51955& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Female homosexuality}  & \cellcolor{red!5}Lesbian & \cellcolor{red!5}1 & \cellcolor{red!5}1/51955& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}Transgender & \cellcolor{red!27}1 & \cellcolor{red!27}1/51955& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Age - Youngsters;Ethnicity - General;Age - Over 65s;Physical Identity - Physical (and Mental) Impairments;Social Class - Working class;Ethnicity - Black;Age - General;Nationality - General;Gender - Female sexuality;Sexual Identity - General;Sexual Identity - Male homosexuality;Physical Identity - Physical Features;Behavioural Addiction - Alcohol; Ideological and Political Identity - General;Ethnicity - Native-American;Nationality - Chinese;Nationality - German;Gender - Female intelligence;Sexual Identity - Female homosexuality;Sexual Identity - Transexuality;%.

\item The percentage of hate speech related words is 0.8815.

\item Considering that the variable \textbf{Gender - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 463/2418 occurences of hate speech related comments.\end{itemize}\end{document}