\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_67.json :}\newline \par\Large\textbf {Title: \large  Serena Williams: Victim of Sexism or Sore Loser? }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small None of the above ITS CALLED FEMALE ENTITLEMENT..   They are never wrong and its always someone else's fault and they reevaluate the victim!! And then her natural female pettiness comes out because she did this out of spite.,   she's the kind of \textbf{woman} who  would lie about rape of violence ..  I have a daughter haha haha yeah that's such a good point NOT!!!  GROW UP SERENA , you just lost a fan!! WE SEE YOU NOW SERENA  AND WE ARE NOT IMPRESSED\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small Have you heard "she" is a dude? Just seeing her body and face with a dress and female name is confusing. I guessing the \textbf{tranny} story is true. Does any one else see it?\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small I salute America Uncovered for providing a reasonably straightforward brief of the 2018 Open controversy.  Admittedly, Serena's heated emotions were on full display, but let's examine a small measure of her 20 year career that could shed some light, but not necessarily excuse such passion.  The 2001 \textbf{Indian} Wells incident where a then 20-year \textbf{old} rising star endured behavior so unkind she boycotted the event for over a decade.  Or perhaps the 2004 U.S. Open tournament quarterfinal loss against J. Capriati which gathered more attention for erroneous calls against her which existing technology easily confirmed were wrong, not to mention the unfounded accusations of match fixing given voice by names within the game such as John McEnroe or fellow player Elena Dementieva.  Suffice to say, Serena is no stranger to unjust treatment by officials, competitors, or fans on random occasion.  Regarding double standards, she raised a valid point.  During the 2019 U.S. Open, Russian player D. Medvedev covertly offered a vulgar gesture to the crowd, rudely snatched a towel from a ballperson, openly insulted an umpire, and contemptuously tossed his racket toward center court.  He was fined a whopping total of \$9,000.00, versus Serena's \$17,000.00 in 2018.  The outburst served as no more than a temporary distraction and to state it ruined Osaka's moment is completely arbitrary.  Two unequivocal points to bear in mind: (1) Osaka raised the 2019 U.S.Open Championship trophy over her head, not her opponent.  (2) A winner's check of \$3.8M bore her name and no other.  As added rationale, during post-match activities Serena supported Naomi during her moment of triumph in front of a largely pro-Serena crowd, imploring the crowd to cease booing the young champion.\normalsize   & \cellcolor{green!27}Indian, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}2/280 & \cellcolor{green!27}0.714 \\  \hline
  \cellcolor{green!5}\small Woman says men are sexist. We must believe her.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Sore loser. How can she cry \textbf{sexism} when her opponents are all female?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Talk all the shit you want about Serena! She still has won moe medals/plates than any female in tennis... still the greatest ever,  sorry \textbf{racist} people!🖕\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{black} and most of the comments I'm seeing on Serena are gross and disgusting and you guys should be ashamed of yourselves. Second, Serena shouldn't of played the \textbf{sexism} card. If you want to empower women you win the game!\normalsize   & \cellcolor{green!27}Black, Sexism & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small all SW has to do is play tennis to the best of her ability to win.  Getting caught in judgement calls is when SW pulled the \textbf{race} and \textbf{gender} card.  SW LOST her game and shot at breaking the record.  All SW has to do is remember her manners and not break racquets on the open court during her playing frustration.\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small This is Serena Williams we're talking about ? She's a \textbf{Racist} Sore Loser\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small all these 'hate comments' bc like she said she doesn't care 🤣✌🏾 are made by white men and women - 🤣✋🏾 you are mad bc a \textbf{black} women is doing great you get out on that court and do what she does and get all the 'hate' she does it isn't easy so bye - 🤣\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small "That \textbf{woman} is a man, man!" ~ Austin Powers\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Crazy lady moment\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small A sense of entitlement that is beyond belief. \textbf{Nothing} else to add. A champion at tennis, a child at behaving.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small She's not only a good loser but Serena I no longer consider her the best tennis player in the world. She lost that title when she fit in the category of a an angry \textbf{black} female who acted worse than a spoiled 2-year \textbf{old}I couldn't believe her attitude and actions. She was a disgrace and acted so disrespectful...smdh\normalsize   & \cellcolor{green!5}Black, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small Sorrlooser she whent full \textbf{black} lady on da referee poor man just doing his job\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Bunch of people attacking on one \textbf{woman} (Serena)?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small No way that is a \textbf{woman}. Cheating is an understatement for that player.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Bad loser, no, just an exceptionally ugly \textbf{woman} (and not just physically). She is no sportswoman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Shes such a sore loser. Soo funny to watch the people on top complain about it not being fair. Soo pathetic. She should be boycotted. The only reason the gets away with it is by being a \textbf{black} \textbf{woman}. If you say anything shell say your \textbf{racist} or sexist. She just wants attention.\normalsize   & \cellcolor{green!27}Black, Racist, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}3/53 & \cellcolor{green!27}5.66 \\  \hline
  \cellcolor{green!5}\small It's sad to see powerful women needlessly falling back on their \textbf{gender} to back them up. It really hurts the whole 'equality' issue because people can point to these instances and say "see, that's what it's 'really' about, somebody throwing a hissy fit".\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Serena get over yourself! Your coach and you were cheating and you're a sore loser and this is coming from a \textbf{woman}! How dare you ruin that young girl's win.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small She's just a loser in general. I'm surprised she didn't play the \textbf{race} card. I bet you she was about to.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small What a humble \textbf{woman} and a great role model.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Isn't \textbf{sexism} when it's unfairness when it's men against women or women against men? She was playing against another women right? How is that \textbf{sexism}? That's like complaining it was \textbf{racism}... Oh wait, her opponent happens to be "\textbf{black}". The real sore loser was the crowd that supported Serena Williams and made Naomi Osaka cry.\normalsize   & \cellcolor{green!5}Black, Racism, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/55 & \cellcolor{green!5}7.273 \\  \hline
  \cellcolor{green!27}\small Wait til some dude identify as a \textbf{woman}, her record wont be unprecendented anymore.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small POOR sERENA TRYING TO USE \textbf{sEXISM} AS A EXCUSE.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small She is such a class act. Instead of screaming and shouting she keeps her cool as she moves her slender super feminine figure on the court. Maybe because she is \textbf{black}, and a \textbf{woman}, and also a mom and humble and honest. Amazing role model!\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small BT-1000 and wicked \textbf{witch} of the south\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Sore loser. Period. Is always the \textbf{race} card, the \textbf{sex} card, but never a deep and profound exercise of introspection. \textbf{Nobody} can deny the rough and tough road she and Venus had to travel, but that doesn't entitle her to behave as a complete ass whenever she is losing. It's a recurring pattern.\normalsize   & \cellcolor{green!27}Nobody, Race, Sex & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}3/53 & \cellcolor{green!27}5.66 \\  \hline
  \cellcolor{green!5}\small 'You're going to take this from me because I'm a \textbf{woman}? And you're going to give it to a \textbf{woman}?! Sexist!'\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small At 3:40 she says "...I've seen other men call other umpires several things..." OTHER MEN !!! is than an oblique admission of actually being a man herself? she's certainly not what i would call feminine.In any case, it seems to me that IF there was any \textbf{sexism} in this incident, it was on the part of Ms. Williams by calling the umpire sexist. smh\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small she left her \textbf{race} card at home\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small The empire was not \textbf{sexism} It was favoring a girl from Japan.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Sexism for taking a match from one \textbf{woman} and giving to another?🤔\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Hehe. Naomi's younger, when you get \textbf{old}, you become slower. Your reaction time also diminishes.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small You're making me anxious about growing \textbf{old}..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Because she's a \textbf{woman}...So, her argument is because the tournament officials sided with the male judge, they are inherently sexist?  I don't blame her for being upset over taking a coaching penalty. Maybe she should be upset with her coach?  Not a tennis fan, but I'm guessing she could still have won the match had she not received the additional two penalties?  Then, she could have pursued satisfaction for the coaching penalty through other avenues.  Instead, let's have a tantrum.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small Women today have the tendency to blame \textbf{sexism} for their own stupidity and failures.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Was her opponent a man? Williams' \textbf{sexism} is really SORE LOSER! She's the real hater. She is the one that should apologize.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I would say sore loser when she lost against the Japanese \textbf{Black} \textbf{woman}.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small black \textbf{woman}, ammaryt?\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small "penalised" and "penis" has the same root, so yes -  \textbf{sexism}! :)\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Any one else Just waiting for the \textbf{race} card?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Holy shit, I thought you were an \textbf{alien} until I remembered that you used to not have a beard.\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Serena Williams has shown a pattern of behavior of verbally abusing referees this incident is not surprising it's only surprising she had the gall to use feminism and \textbf{sexism} as an excuse for her terrible Behavior.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Serena is man disguised as a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small What about inequality. How about no bias in sport, every competition based on merit and not \textbf{gender}.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small You have to keep in mind that the \textbf{sexism} part relates to her being peanilised for arguing. Other male tennis player argue and insult the officials yet they never get called out for it.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small That is a huge man!! Sir-ena is a man! If yall can't see That, there is no hope for humanity! We are too \textbf{dumb} to town if people can't see what's in front of their face!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Woman wins 1.85 million runner up prize Still complains\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Of course it's \textbf{sexism}. The other female she was playing against was obviously a guy smh\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Not \textbf{sexism} because the judge is known to call out men and women equally\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small She's also \textbf{black} so trying to explain something rationally to them is a waste of time.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small WowCheated and just taking \textbf{sexism} as a tool of getting awayWhen did 'women's right' became so cheap, so devaluated and utterly speaking, disgusting. Where is the honor in that? Where is the integrity that supports the spirit of fighting for rightful rights and status?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small The blatant bias in the comments is scary. There's a discussion to be had here but 'people' would rather tear down the successful \textbf{black} \textbf{woman}. Serena is not the only petulant athlete, are you people consistently spiteful across the board?\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small she through a tantrum and there was a high chance she cheated.Also it's not because she's  \textbf{black} just look at who she is playing against no one is discrediting her.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Serena's the one,  though,  who refused to accept accountability for her actions and instead pulled the \textbf{sexism} card to justify herself.  Also,  it's indeed not as if other players haven't duked it out with umpires but she handled it in a bizarrely un-smart way. I say bizarre because she's experienced enough to know about tennis' step wise escalation of code violation. She got a code violation each for receiving coaching, then smashing the racquet and finally the last argument where she called the umpire a thief.  Third code violation earns a game penalty.  This was a bit like the Hingis Graf FO 99 final where Hingis just completely lost her mind and it was \textbf{nobody} else's fault that she did.\normalsize   & \cellcolor{green!5}Nobody, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/120 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small All points by the way that the video covered.  It was a rare good and informed video on the subject where mainstream media simply ran with the \textbf{sexism} narrative without bothering to understand tennis rules or that other players did in fact receive code violations.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Slag\normalsize   & \cellcolor{green!5}Slag & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small The only innocent \textbf{woman} hurt was her opponent. Thats a fact. That she doesn't have the courage to admit she fucked up, even after the match shows her opinions are trash. And that umpire is a bit of a rule \textbf{nazi}, and she embarrassed and belittled him in front of all those people because he followed the rules. She is a horrible person.\normalsize   & \cellcolor{green!27}Nazi, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Gender - General & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small Sexism accusation is a valid point when it comes to Serena Williams.  After all, Naomi Osaka is visibly a female.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small If Yui Susaki doesn't win the Olympic Gold next year, I'm gonna claim \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small You said "Liar" don't water it down with "thief" which actually holds the same water in the regulations handbook because it's abusive/derogatory.  And do NOT say that you are fighting for women's rights to be vulgar and \textbf{sex} shaming.  You make a living playing a game.  It's a game.  It's a modern day coliseum.  You have to control yourself these days. But to say it's a woman's right to be as vulgar as a man?  I thought women hated the way men acted.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small Her opponent IS A WOMAN\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Feminists: he is mansplaining of course it was \textbf{sexism} because a the ref was a male\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Definitely \textbf{sexism}. They dont accept her because shes a man.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Guys it's \textbf{sexism} because we don't know what her opponent identifies as, she could very well be an oppressive apachi attack helicopter\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Female vs female. Female loses. \textbf{Sexism}. Everything is sexist, always, it didn't go my way therefore oppression\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small How is it \textbf{sexism} when the opponent was a women to????????   Please explain\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Serena is not a \textbf{woman}, she's something else\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Haha..blame it on \textbf{sexism}. When ur the one called him names and ur the one or atleast ur coach trying to cheat in the gameShe is a sore loser definitely in the match\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small is \textbf{nobody} gonna talk about that forehead? Anyways, it's a great video.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Stop taking \textbf{black} American women seriously they think like 12 year's \textbf{old} and toddler's\normalsize   & \cellcolor{green!5}Black, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Yeah she is just mad cause she lost lol she played too many cards \textbf{sexism} card \textbf{black} \textbf{race} card lol\normalsize   & \cellcolor{green!27}Black, Race, Sexism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}3/20 & \cellcolor{green!27}15.0 \\  \hline
  \cellcolor{green!5}\small Im so glad Naomi beat that \textbf{brat} with the tutu, who wears that crap to a tournament, she is racist\normalsize   & \cellcolor{green!5}Brat, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I think false accusations of \textbf{sexism}, \textbf{racism}, rape etc.. should be severely punished as well.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Haha! She is fighting for women's equality ?! What a bollocks is that ?She is like the loser feministst and leftists who don't know how to lose or argue their own point. They are calling these big slogans which mean \textbf{nothing}! Sore LOSER !!!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Not \textbf{sexism}. I'm so disappointed in  Serena. Win or Lose, you need to be graceful in attitude. Poor Osaka, 20 years \textbf{old}, win against your idol and yet her 'fellow' fans booed her Win, which should have been a huge cause of celebration.\normalsize   & \cellcolor{green!27}Old, Sexism & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small A \textbf{black} \textbf{woman} whining when they don't get what they want. What a shock.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Sexism or sore loser? Simply put she makes like she's so important that she's running the tournament and umpires are beneath her. It's arrogance really. Venus has much better composure. Serena has done this more than once. Even threatened linesmen. She's also dull of hearing it seems. The ref told her it was a coaching violation...what? The self-delusion really showed when she talked to the ref and said she would never cheat...problem fixed...no code violation right? Well, in her self-important mind it was solved. Then the racquet smash...now she's really ticked. Yes, the violation stood...no your argument didn't make any difference. What? My self-convincing speech didn't work. Point deducted. Then after ranting she says "don't talk to me"...he doesn't...but no she's got to win this argument...with a ref...of course you're more important than the ref...right? Wrong. So after much verbal abuse...he get's pissed off...game deduction...you can't be serious...it's not fair...it's not fair. The whole thing reeks of a self-absorbed, self-important attitude. Lesson taught...lesson learned. Osaka would have won anyway.Yes, she's been the greatest female tennis player in history...and no...you don't run the tournament or tell refs what to do.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/190 & \cellcolor{green!27}0.526 \\  \hline
  \cellcolor{green!5}\small Wow! Cant believe Serena didnt say \textbf{racism} instead of \textbf{sexism}. Such a sore loser.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small You guys are not understanding why the \textbf{sexism} argument is being made. It's being made because umpires get treated much worse by men than they are by women and the men arent penalized. This has \textbf{nothing} to do with Serena's opponent. Serena horribly overreacts but she shouldn't have been penalized, especially in such a large scale match.\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small WTF transwoman against woman: that's \textbf{sexism} right there!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I doubt she's even a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Oh, how dare that man act so sexist. It's just like a man to take the win from a \textbf{woman} and give it to a \textbf{WOMAN}.....of all the people he could have given it to, he chose a \textbf{WOMAN}...How is a hard working \textbf{woman} supposed to get ahead in life when men keep taking stuff from them and giving it to women?....\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/62 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small This kinda reminds me of Rocky 3 where the champ is a big asshoIe to everyone but the \textbf{underdog} wins in the end and the former champ is going on a huge tantrum. Real 80's like you know?\normalsize   & \cellcolor{green!27}Underdog & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small She stole the Osaka's spotlight by bitching about "\textbf{sexism} \textbf{racism} \textbf{patriarchy} feminism " as she destroys another womans lifetime achievement. This is why feminism is bad, this is why PC culture and identity politics are bad, they are toxic and need to be stopped\normalsize   & \cellcolor{green!5}Patriarchy, Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/44 & \cellcolor{green!5}6.818 \\  \hline
  \cellcolor{green!27}\small It's \textbf{sexism}. Serena called it "Other men have said worse to umpires and have not been penalised" It wouldn't of been a fair game for Osaka to win anyways.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Not only was she a sore loser... she tried blaming men for her actions! \textbf{Sexism} from her not the judge! 'The men get away with worse' boo hoo! Cry baby.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small It wasnt \textbf{Sexism} or being a sore loser. Sirach 26:25 A shameless \textbf{woman} shall be counted as a dog; but she that is shamefaced will fear the Lord.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small The first thing she accused him of was being sexist. Then she suddenly remembered she was playing with another \textbf{WOMAN}, so obviously she comes up with the \textbf{racism} card... Childish... She lost and stole Naomi's moment. How "feminist" of her... Shame on you Serena.\normalsize   & \cellcolor{green!5}Racism, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small That coach was \textbf{dumb}.  He should just let her do her thing.  Williams should fire his sore ass.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Sexism is the fact that Williams felt she could speak that way to Ramos. If Federer screamed at a female umpire for 15 minutes, including a barrage of strong insults he would be torn apart by the media and branded sexist. Serena never even apologised to Ramos.She is unattractive inside and classless.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Steven Williams is not a \textbf{woman} Stevarina is a man .Typical manbitch talking shit into a hole deeper and deeper They do it to cops too, talk and flap until they get TASED beat up or shot.It's in the DNA\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small mmmh Chris the reaction of the Japanese \textbf{woman} she is really classy\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Because other player is not a \textbf{woman}? wow what pathetic person she is\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small definitely a sore loser who using \textbf{sexism} and \textbf{racism} to get what she wants\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small serena has a serious problem in her head and not with sexism\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Oh, I'm losing a match and getting penalties because I actually cheated? \textbf{SEXISM} GUYS, \textbf{SEXISM}!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Just a sore loser. No \textbf{sexism}, not even one bit...\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Serena did not loose in the grand slam final cause she was a victim of \textbf{sexism},nor did she loose for being a sore looser:she lose because she was being too busy arguing with the official,than playing the game.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Nothing to do with a \textbf{woman} you were abusive and just don't know when to quit. You got your behind kicked period. But you are still the female GOAT.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small No she deserves to win, how would you like it if you lose when you lose you're weak and pathetic and your a \textbf{nobody}.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Woman's right and equality? I don't see her complaining about the fact that males have to play 5 sets and the \textbf{woman} only 3 in grand slam tournaments?.. so \textbf{woman} get paid the same for doing less? Where's the equality?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small That is a \textbf{black} guy pretending to be a \textbf{woman}.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Bruh trying to say hes never lost anything in his life 😂 hes loosing that hair line real quick though. My two year \textbf{old} acts more controlled than this hoe.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small woul'd  he be charged of \textbf{sexism} if he didn't penalise her? thus not going by the book and doing damage to osaka?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I think amid the whole Serena Scandal and her using the \textbf{sexism} card, I find her statement "you will never be an umpire on any field again" to the umpire so terrible and basically a threat...how did that one elope???\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Sexism because so many boys in my class say you can't run fast or you can't play basketball and the most worst you can't play video games like we are all people and we should all be treated the same so when you see some one be treated like that stand up for them because that might be you some day who ever reads this have a great day 😊😎 girl power 💪🏾👩🏽👩🏾 boy power (even though I'm a girl) 💪🏾👦🏽👦🏾 love your self ❤️😊\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small Women can't win pull the \textbf{sexism} card\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small No, there's no \textbf{sexism}.There's just umpires not doing their job right when male players violate the code.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Sexism\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/1 & \cellcolor{green!27}400.0 \\  \hline
  \cellcolor{green!5}\small You guys nuked Japan and now you feel sorry for this \textbf{woman}. LOL\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Carlos Ramos don't care what is your \textbf{Gender}. Serena Williams is a Sore Loser.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Serenas a yucky steroid beast. Barely can call herself a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small But wasn't Osaka a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Serena got angry because she is actually a man and she lost against a real woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The thing that I just don't get is what happens at 1:25. She's pissed yes but she's still in control. That she lost it so spectacularly later on is \textbf{weird}. And yes all three warnings were valid.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small I wonder how she didn't pull the \textbf{black} card as well...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small First they come up with the \textbf{race} game, then \textbf{gender} game, what's next? If the rulebook says can't abuse, coaches can't signal then the official was right to penalize her.She should stop being an attention seeking * and focus on the games and rules. And stop this Gen-Z game... What a waste of oxygen... just retire already!\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small HOW IS SHE A SORE LOSER WHEN SHE HADNT LOST WHEN SHE WAS UPSET?!?! You're all mad no one is going to ever be as good as Serena so call her a sore loser all you want racists. After the match was over she was very gracious to Osaka. I think we have a BUNCH of \textbf{racist} haters in the comment section. You \textbf{racist} can't beat her any other way but through this one incident and after years of being a champion you all relish the opportunity to treat this strong \textbf{black} \textbf{Woman} like dirt.\normalsize   & \cellcolor{green!5}Black, Racist, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/95 & \cellcolor{green!5}4.211 \\  \hline
  \cellcolor{green!27}\small It's sexist because he's never done that to a man before! Not because both players are female!!! He didn't like how that \textbf{black} women talked to him and took the match from her! He's been talked to MUCH WORSE by white men and has NEVER done anything like that? In the FINALS?? Yeah she lost because as a \textbf{black} women you can't do what white men can do.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small It's not Serena most Americans are rude, \textbf{racist}, cheap, selfish and ignorant. Feeling sorry for Japan.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small She's a sore loser, a spoiled \textbf{brat} that wants her title but couldn't get it because she got her ass handed to her by another player. The one at fault here, is her, and her alone. The rules apply to everyone, even to the best players.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Women already get positive discrimination in Tennis. In Wimbledon at least. The men play best out of five matches, the women play best out of three, but now the winners of either \textbf{sex} get the same reward. Same money, less matches. Sexist.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I really love my tennis but I found it so offensive to see the poor loser \& ugly behaviour by Serena Williams.   Serena was clearly at fault on all three code violation counts.  I know it, Serena knows it, you know it \& the tennis world knows it.  (sadly, the USA crowd \& USA tennis officials disagree by supporting Serena)  Serena already has a track record for throwing her tantrums when she is losing \& still \textbf{nothing} has been done to stop her.    The umpire's job is to enforce the rules.   That is his job.   Serena seems to think that she is bigger than tennis itself when she behaves like that.    I give credit to the umpire Carlos Ramos for remaining calm after a barrage of insults \& accusations.   Serena certainly owes him an apology.   I admire the young Naomi Osaka for remaining composed throughout this ordeal.   She was the true champion on the day.    Serena can learn a lot from Naomi.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/162 & \cellcolor{green!27}0.617 \\  \hline
  \cellcolor{green!5}\small how is it \textbf{sexism} if her opponent was also female?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Serena Williams has \textbf{nothing} to be sore about people are just making a big deal cause she fight for the females in the sport. The problem is with America they just don't have equal rights for females in their country, sore loser why would Serena Williams be lets look at her records23 grand slams single titles 5 time tour finals Champion14 grand slams doubles titles2 grand slam mixed titlesFed cup champHopman cup champ4 Olympic GoldsFormer no.1 for consecutive yearsHighest paid female athleteLegend of the game and respectedlook on youtubeNick Kyrgios they dont do anything about his tantrums Roger Federer has sworn at a ref \textbf{nothing} happened there 2019 Australian Open Pablo Carreno Busta through the biggest tantrum \textbf{nothing} happened he apologised ooooohhhh Victor Troicki massive tantrums It just shows Serena makes a statement and you fuckers cant help but focus on her and the men get covered up. Thats alright she's still a legend of the game and makes her millions and your words wil mean \textbf{nothing} but being jealous of her success. Sore loser hahahahahahaha not even close just unfair robbery learn a think or two about tennis being a unfair sport with language barriers and corruption.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}4/209 & \cellcolor{green!27}1.914 \\  \hline
  \cellcolor{green!5}\small How is it \textbf{sexism} both of the player were female\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small after all them wins over the years. she just not \textbf{woman} enough when she dont win. the other player was just better that day.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Strong independent \textbf{woman} trying to hold her tears so baldly😒\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small she's a sore loser and total piece of female trash for once again being a \textbf{woman} who brings her kid into the discussion to try to create favoritism to herself.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I got a ticket for double parking. I was furious, there were other people who double parked before, they didn't get any tickets, why should I?!! Clearly \textbf{sexism} and \textbf{racism}!!!\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Stop it she says"l have a daughter"She is female, even though at times she looks \textbf{tranny}.\normalsize   & \cellcolor{green!27}Tranny & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Serena tried to argue that it is okay for female to call male umpire a thief or else it is \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small yeah. thats a consequense of the way too left US   nowadays you can call \textbf{sexism} on the most ridiculous cases and still its gonna be discussed  \normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small This \textbf{transgender} thing has gone too far. Why do they let this dude play against women?\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small She is an idiot by saying that men want to take away her win because she is a \textbf{woman}. What she doesn't think is that, that point goes to another WOMAN\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Claims \textbf{sexism} for taking a point and giving it to another women sounds like good logic to me\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Wouldn't it be \textbf{racism} not \textbf{sexism}? Oh shit nevermind she thinks all men get away with everything, she just acting spoilt\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Tennis \textbf{brat}.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Neither \textbf{black} privilege\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I'm confused... Serna Williams was born female, right? I've not seen nor heard any confirmation that she was born a male. She may just be a muscular \textbf{woman}, and I'm the type to refer to people as their biological \textbf{gender} and legal name no matter the fantasized \textbf{gender} you claim to be. From the searches I've done, she is female, and her being male are just conspiracy theories. Unless I'm wrong, because right now... my explanation is that she just got really lucky when it came to her genes.\normalsize   & \cellcolor{green!5}Gender, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/89 & \cellcolor{green!5}3.371 \\  \hline
  \cellcolor{green!27}\small Osaka too is a women.  How tf did serena creep \textbf{sexism} into this?! 🤒😑\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small losing gets caught cheatinggets punishedplays victim cardpitches fitbreaks racketplays i have kids cardplays \textbf{sexism} cardmakes threats at a guy doing his jobgets punished againruins match for opponentwalks  away satisfied  knowing that by pitching a fit she avoided a one sided loss and can now blame the situation on \textbf{sexism} instead of her cheating you can tell she never thought in a million years that an umpire would actually enforce the rules vs her she probably thought she was special and that they didnt apply to her\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/96 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small I do think that men are allowed to get away with far more on the courts than women do.  That's where the \textbf{sexism} comes in.  A male player would not have been penalized like Serena was for doing the exact same thing.  However,  she was not at her best and It's probably time for her to retire.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Psycho.\normalsize   & \cellcolor{green!5}Psycho & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small It's just sad that this all overshadowed Naomis win. Naomi completely thrashed Serena in the first set and in my opinion would have won the match even if Serena hadn't lost a game. I believe that Serena truly believed she didn't deserve the coaching penalty as she didn't see the hand gestures, but after that needed to let it go instead of continuing to bring it up several times after. She absolutely deserved the point penalty for breaking her racket. However, calling the umpire a thief doesn't merrit a warning and definitely doesn't merrit a game penalty. If a man can't handle getting called a thief by a \textbf{woman} he needs to grow a pair lol. if  he really was insulted by being called a thief and a liar he should have overuled and just given another point penalty rather than a game penalty as it was a final and to close to the end of the match. I completely agree with Serena that men say much ruder things with worse infliction and don't even receive warnings let alone penalties. have you seen The things Nick Kyrgios comes out with?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/190 & \cellcolor{green!27}0.526 \\  \hline
  \cellcolor{green!5}\small One name... John McEnroe.... I rest my case. Im not into the whole \textbf{sexism} and blah blah blah. rape culture etc. thats all bullshit. but my mom forced me to watch tennis match's as a kid. and i dont want to say its \textbf{sexism} but holy fuck that bitch did \textbf{nothing} other than be angry.... compare that to the 70's-90's men that would fight the ref and smash shit.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/69 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Bo ho\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small It's pretty easy to throw the words \textbf{Racist} and \textbf{Sexism} when you don't get your own way these days.\normalsize   & \cellcolor{green!5}Racist, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small I gotta 2 yeat \textbf{old} that acts like that in toy stores\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She is the worst.Her sister Venus is one of the best spirits out there though.  \textbf{Weird} how that works.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Lol I feel bad for that dude 😂 probably has some \textbf{homosexual} tendencies and being with a \textbf{woman} who looks like a man is easier\normalsize   & \cellcolor{green!27}Homosexual, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - General & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Is Serena Williams a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small The only reason why she only accused him of \textbf{sexism} and no \textbf{racism} as well is coz, N. Osaka is no white.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Liberals and feminist politics are \textbf{racist}. period. It will ruin every sport, entertainment and social venue world wide.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small color is no excuse for breaking the rules of the game. Case example roger federer, he broke the rules and got punished too, so what does being \textbf{black} or a \textbf{woman} have to do with breaking the rules? Maybe she didn't see her coach trying to signal her, but that does not change the rules regarding the game. The coach cost serina's title shot so why would serina keep this \textbf{dumb} ass as a coach. If it's your responsibility to keep your help in line then don't bitch to the umpire about your help when they get out of line, own it and fire his \textbf{dumb} ass for getting you your code violation!\normalsize   & \cellcolor{green!27}Black, Dumb, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/113 & \cellcolor{green!27}3.54 \\  \hline
  \cellcolor{green!5}\small I would not say it was guilt for Serena because there was \textbf{nothing} to be guilty about. I would say her winning occasion was destroyed and she was emotional.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small romonabruno I don't think it's about that it's more like she ruined a woman's achievement by lashing out, she insulted and berated a referee(I know that many people do it but with this specific ref he follows the rules closely and fiercely so know the boundaries of who you insult), slamming your racket which she's done a few times so she knows what could happen if she did it again, and ultimately she made it about \textbf{gender}. Naomi may have some the same but this is someone who's been called the goat been a champion and should know how to act by now because she knows people look up to her like the Osaka the very person she faced\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/119 & \cellcolor{green!27}0.84 \\  \hline
  \cellcolor{green!5}\small romonabruno oh no how could I not have seen it coming......it seems I've activated your \textbf{race} card\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small romonabruno I agree with you for the most part in fact I hold her passion about the sport in high esteem and your right I can't live up to the standards, but that's fucking okay cause I'm a human and she's a human too; however, I still believe in striving for those standards so when I stumble and fall I try my damned best to admit to myself and the people around me that I slipped up. And I guess the one thing I feel is missing not just from Serena here, but plenty of people who have achieved greatness, is there is no shred of humility to admit that maybe there was an over reaction and that maybe jumping straight to \textbf{sexism} was a bit much, but as far as I know there has never been anything of that sort to come from this. Being able to accept and admit your mistakes is a key to continuing progress as an athlete but even more so as a human. I'm sure at some point in her career she had that and I guess I could probably cut her some slack because I have no idea what it is like to be rich and famous and even more than that to be the absolute best. So I can see how that might be a big factor in the ego and outburst, but I still really hate to see when a prominent and inspiring figure misses a great chance to set an example for the people that admire them by showing some incredibly reputable human traits like humility and redemption. Admitting mistakes has fallen out of fashion and that leads to stagnation and I think it plays a big role in society as a whole. Sorry it's a rant I have a bit of ADHD so when I get rambling it keeps coming doesn't really help I study psychology with a bit of philosophy on top...\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/324 & \cellcolor{green!27}0.309 \\  \hline
  \cellcolor{green!5}\small \@Mona Hard work shit Serena at this stage has Multi Millions Physios Psychologists. private jets Even the big tournaments have all the help a player needs Try Margaret Court 500 miles from the nearest big city, played for Umbrellas Eskies, went overseas with \textbf{nothing} and won 65 Grand Slams Singles Doubles and Mixed Doubles. Bloody hell the women players back then played all the  games just to get a few bob/This over pampered excuse for a professional has had it too good for too long And needed to be reminded of the rules\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small Is against another female minority calls \textbf{racism} and \textbf{sexism}. Ok\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Sore Loser she uses \textbf{sexism} as an excuse for getting destroyed by a young girl\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Transgender \textbf{woman} Vs Japanese \textbf{Woman}.\normalsize   & \cellcolor{green!27}Transgender, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}3/5 & \cellcolor{green!27}60.0 \\  \hline
  \cellcolor{green!5}\small The \textbf{african} ogre vs the beautiful asian woman\normalsize   & \cellcolor{green!5}African, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Where was the \textbf{sexism}?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Sore loser, played victim card, played \textbf{sexism} card, mentioned her daughter for no reason. Surprised she didnt throw the \textbf{black} card in there as well.\normalsize   & \cellcolor{green!5}Black, Sexism & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@Crack Both of them are women yet she still used the \textbf{sexism} card.(Tbh Serena isn't even a \textbf{woman})\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Osaka's father is \textbf{black}. He's Haitian\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small The \textbf{sexism} in tennis is so huge lol. How can women get the same money for doing merely 2/3 job at Grandslams… so unfair.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small My apologies to Osaka and the \textbf{nation} of Japan for all the decent Americans for that display\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small yeah 70 years ago.....it is really \textbf{nothing} compared to what USA does each year in the last 70 years\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small romonabruno Serena was acting this way and made the umpire out to be sexist and racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small A other \textbf{black} person complaining\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small alright...Serena did bad, she realized that, judging her for outburst is wrong, she got penalty that she deserved by book of rules...but those fucking feminists backing her up, editing another article about how there is \textbf{sexism} around...? Makes my blood boil....also...it was not cool for Serena to state afterwards she was fighting for womens rights. Classic example of victim pretending to be rescuer.  She had the argument out of self interest, no question about it. There should be new rule in a book...complaints about \textbf{racism}, \textbf{sexism} or homofobia....end of match for you, period.I feel sorry for the other player...she seemed innocent. Another example how victimhood is toxic thing and tends to destroy its surroundings...\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/115 & \cellcolor{green!5}2.609 \\  \hline
  \cellcolor{green!27}\small Well she's \textbf{black} I'm not surprised\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Omega \textbf{libtard} is what she is\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small They let men play in the women's tennis now?  Someone feed him a \textbf{banana} already.  GRRRRR I R LOSE, MUST BE SEXIST.\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small She is absolutely a sore loser. She took away an amazing moment from Osaka, was attacking an umpire for following the rules, and used \textbf{sexism} and \textbf{racism} as an excuse for her losing\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small She broke the rules and these are the consequences. HOWEVER there are many men in tennis that fits that would put hers to shame and they rarely get punished ever. Yes she got what was going to happen to her but the fact remains there are men who completely destroy their rackets/equipment \textbf{nothing} or/but a warning is given to them. We expect men to get angry but we can not allow that for a female since we expect them to behave better then them. I think there is a point everyone is missing here since we like to hate then think about things logically.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/104 & \cellcolor{green!27}0.962 \\  \hline
  \cellcolor{green!5}\small me*= it made *me feel as if it was sexist.Then don't fucking try manipulate your own daughter, women, white men and many others.Notice how she could have /easily played the \textbf{race} card. But she didn't and why not? Because all these people aren't white Americans. That won't work on your gullible women, men of any \textbf{race}. You are right that the most tragic part is her opponents win. People should be talking about how great she is to have beaten the ‘great' serena Williams and how much potential she has but no. I lost, threw my racket at the ground, verbally abused and cheated in a final but feminism rocks. The umpire has a history of being tough with the rules and not easy going.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/127 & \cellcolor{green!5}1.575 \\  \hline
  \cellcolor{green!27}\small As a powerful and highly influential \textbf{woman}, she made a victim of Carlos Ramos by potentially and unfairly turning millions of people on him. She owes him an apology.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Imagine being Osaka. Imagine managing to beat Sirena Williams. But then to get booed by the crowd. People to tell her "You only won because of \textbf{sexism}." IS it worth it? Sirena you ruined her game and ruined your own game. Don't just flash your feminism card when you get salty.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Oh my god he let a \textbf{woman} that isn't sirena williams win the gameSEXISM\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Lol I seen this match, Serena was gettin her ass handed to her for a lil bit, but to say it's sexist is dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small No but she had basically 2 warnings before loaing the game. We can all agree she looked like an idiot, denied \textbf{r\textbf{ed}} handed use of coaching. A guy can give banter back and forward, women just call it \textbf{sexism} or misogynistic. Shr got what she deserved. Serena would have lost either way, fucking show pony serena taking all the enjoyment out of the sport. Verdict, A Sore Loser.\normalsize   & \cellcolor{green!27}Red, Sexism & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!27}3/68 & \cellcolor{green!27}4.412 \\  \hline
  \cellcolor{green!5}\small I thought she was playing against another woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Serena let her emotions get the best of her. So she was being a sore loser. No \textbf{sexism} here.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small She's a triggered brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small She learned all that shit from \textbf{honkie} boy extraordinaire john mcenroe. Just admit your outrage is because shes \textbf{black} cause you didnt say a fuckn word about \textbf{honkie} boy who acted like this every tournament\normalsize   & \cellcolor{green!27}Black, Honkie & \cellcolor{green!27}Ethnicity - Black, Ethnicity - White & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small While an extraordinary athlete, she is at times an appalling human being.  The garbage about \textbf{sexism} is simply to excuse to herself her own putrid behavior.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small black \textbf{woman} vs \textbf{black} \textbf{woman} how can be \textbf{sexism} or \textbf{racist}?\normalsize   & \cellcolor{green!27}Black, Racist, Sexism, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}6/11 & \cellcolor{green!27}54.545 \\  \hline
  \cellcolor{green!5}\small Lol wtf she looks like a man so no \textbf{sexism} card plz\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "because i m a \textbf{woman}" !!!! loooooll\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Shes a sore loser, was acting like a baby on the court and tried to pull her \textbf{woman} card/mother card/and \textbf{race} card all in the same match\normalsize   & \cellcolor{green!5}Race, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Hell of a sore loser. Or was just having an awful day or something idk but that was all out of place. Also definitely not sexism\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Going \textbf{bald} in your 20's in not winning\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small It is so damn embarrassing to be a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Sexism ???? Her opponent was also a women wtf is she talking about ???\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small It's really stupid because her opponent was also a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Serena can't even say \textbf{racism} to add to her \textbf{sexism} claim because she's \textbf{African} American and Naomi is Asian. If the umpire was \textbf{racist} they'd both get code violations.\normalsize   & \cellcolor{green!5}African, Racism, Racist, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/29 & \cellcolor{green!5}13.793 \\  \hline
  \cellcolor{green!27}\small Black \textbf{woman} vs asian \textbf{woman}.One of them wins.Umpire still accused of \textbf{sexism} and \textbf{racism}.Welcome to the leftist brain.\normalsize   & \cellcolor{green!27}Black, Racism, Sexism, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}5/21 & \cellcolor{green!27}23.81 \\  \hline
  \cellcolor{green!5}\small \@Kerly Lapaine She has claimed Japanese \textbf{nationality} herself, thus making her Japanese\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Gray JediI consider myself left but this isn't left or right this is reversed (elite)  \textbf{black} privelege.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Black v Brown. \textbf{Black} is a colour. White is a colour. Brown is a colour. Olive is a colour. \textbf{R\textbf{ed}} is a colour. 'Asian' is not a colour I've ever heard of. The problem with the word is that it doesn't describe a person very well. In Great Britain, if you say "the guy over there is Asian" most people would  take that to mean he was of \textbf{Indian} or Pakistani origin. Not \textbf{o\textbf{r\textbf{iental}}}. And there's a huge difference In colour between \textbf{Indian} people and \textbf{o\textbf{r\textbf{iental}}} people - one darker, the other paler. What's in a word? A lot.\normalsize   & \cellcolor{green!5}Black, Indian, Oriental, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}12/99 & \cellcolor{green!5}12.121 \\  \hline
  \cellcolor{green!27}\small You're generalising, confused and misleading- I'm a leftist and support the umpire. The main claim in this match- taken up by deluded feminists- was of \textbf{sexism}. It was unfounded. In this instance Serena was in the wrong. However USA is a deeply \textbf{racist} country and she has had \textbf{racism} to contend with.\normalsize   & \cellcolor{green!27}Racism, Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small \@\textbf{R\textbf{ed}} Cirkus no one wants her to be european anyways, she will be an asian\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small \@Gandalf606 To be honest the difference between northern and southern \textbf{indian} color is noticeable too.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Kerly Lapaine dude, the point is that she is a \textbf{woman} and that it is not sexist\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@\textbf{R\textbf{ed}} Cirkus Exactly, it's not that hard to understand.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small \@\textbf{R\textbf{ed}} Cirkus cmon, you literally dont want her to be an european in the last comment and now you say its completely different? stop twisting shit that is not coming your way...\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small You have much still to learn, young Skywalker!  \textbf{Racism} and \textbf{sexism} are complex and deftly deployed social ills that are used with cunning deception and sharp precision.  It's been ManvsWoman (\textbf{sexism}) since Eve asked Adam to take a bite of the forbidden \textbf{fruit} from the Garden of Eden.\normalsize   & \cellcolor{green!27}Fruit, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/48 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small That's a \textbf{black} woman\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small The Umpire isn't a \textbf{woman}, \textbf{Black} or Asian, and, even if he was, prejudice can still exist.  You have a lot to learn about what it means to offend people of different stations in American society.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small how can you accuse of \textbf{sexism} if you are playing vs another \textbf{woman} ?\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Foolish mortals, I am a \textbf{woman} and have a daughter! Your accusations have no effect on me!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small i never understand why some mothers like to use their kid as an excuse. Like that \textbf{woman} who made the rounds on social media for wanting a special mothers line in places like starbucks, so mothers could cut to the front of the line. Being a mother is a good thing but doesnt make you exempt from the rules.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small You are crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Not sexism\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small It's not \textbf{sexism} its \textbf{racism}.... white male,  European especially dont usually get dont remarks from \textbf{black} women. But serena williams is just \textbf{crazy} tho....she tries to scare everyone. Lol\normalsize   & \cellcolor{green!27}Black, Crazy, Racism, Sexism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/29 & \cellcolor{green!27}13.793 \\  \hline
  \cellcolor{green!5}\small I don't think it was a sexist decision. And some times people just don't want to deal with crap from anyone on certain days. Maybe he was being \textbf{racist}, I don't really know. I think he was being reasonable, but I couldn't say for sure.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small But the other player is a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Try seeing this from Naomi Osaka's point of view:Your opponent is cheating and the referee is not doing anything because he is afraid of being called a sexist. Your opponent now has an unfair advantage and you have to accept it, because you are a \textbf{woman}!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Did I miss something? Did a man win in lieu of a \textbf{woman}? How can this be remotely sexist?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small But... she was playing against another \textbf{woman}, so it's not sexist...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I want a \textbf{sex} test done on that man woman\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Serena needs to shut up and just retire. She acted like the only thing she did was say thief. \textbf{Nothing} else. SORE LOSER!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Wtf woman's right? I mean her opponent is also a female how tf can it be \textbf{sexism} by any means?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small This \textbf{transgender} is going crazy\normalsize   & \cellcolor{green!5}Crazy, Transgender & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Because she's a \textbf{woman}? Interesting how her opponent was a \textbf{woman} as well\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Sore lower using \textbf{sexism} as an excuse\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Wow, what a hero fighting for women, her daughter, marginalised people.....blah blah blah. For some people it doesn't matter which card they use: \textbf{race}, \textbf{sex}, etc.\normalsize   & \cellcolor{green!27}Race, Sex & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Stop this hate, \textbf{racist} and sexist speach against Serena - it is not possible for her to cheat as...  she has a daughter.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Standard fare for \textbf{black} women\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small when people play the \textbf{racism} or \textbf{sexism} card without it being justifiable i always go like: UGHHHHHHHHHH\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Serena is a big sore loser, it definately was not \textbf{sexism}, it was just a bad call, and she handled it terribly\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small HOW IS THIS \textbf{SEXISM} IF HER OPPONENT IS A FEMALE?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small 'Because I'm a \textbf{woman} and got a game penalty so it's sexist' I mean Osaka is a \textbf{woman} and played the game fair and won..... hmmmmmmmmmmmmmmm\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small >accused of \textbf{sexism}>is woman's 1 on 1 tennis match\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I think it's both \textbf{Sexism} and Sore Loser\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I don't understand not to be \textbf{racist} or whatever, but why asian countries start getting \textbf{black} people to represent them it's just false\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small How is a dude vs dude situation sexist? This so called \textbf{chick} is a dude. There is no \textbf{sexism} here. Get a life people.\normalsize   & \cellcolor{green!27}Chick, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She is just \textbf{dumb} lmao\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She is definitely a sore loser! She should be ashamed of herself for falsely accusing that referee for \textbf{sexism} and taking away from the winner and then  major accomplishment she had, who wiped the floor with her!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Sore-losing feminazi\normalsize   & \cellcolor{green!5}Feminazi & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Reverse racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small As a typical spoilt child..First line of defense is to blame others!.. Second line of defense is to claim \textbf{racism}!...Third line of defense is to blame the socially hated \textbf{ethnic} group...white males!!!...well done Serena!!\normalsize   & \cellcolor{green!5}Ethnic, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Serena Williams , the way she looks she cannot claim \textbf{sexism} , shes more masculine than the guy giving her penalty\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small The other opponent was a \textbf{woman}, how in the world could it have been \textbf{sexism}? That is the worst excuse imaginable.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Sore loser... she wasn't disqualified because of verbal abuse towards the umpire because she was a \textbf{woman}, she was correctly disqualified because she was penalised two times before... And her argument of men not being disqualified for verbal abuse... John Mcenroe, anyone? And all male tennis players defending her saying they said worse things and not be disqualified and penalised: well, did you get two penalties before it?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Total sore loser. \textbf{Sexism}? how can it be when the person that won WAS A WOMEN. A women that deserved to win unlike Serena Williams who tried to cheat to win. Poor Naomi Osaka shouldn't have appologised for winning because she won by having the skill \& integrity to play by the rules \& by being profesional. Serena Williams should be ashamed of herself \& her unsportsmen-like conduct \& for crying \textbf{sexism} when it wasn't \textbf{sexism} at all, she is a loser inside \& out.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/85 & \cellcolor{green!5}3.529 \\  \hline
  \cellcolor{green!27}\small Had I been that umpire, when she said "Don't talk to me!" - I would have docked her a game for every single word she said for verbal abuse.As for fighting for women's equality - how about taking on the men then? Let's draw a line under it all - no \textbf{gender} separation, and see how many matches she wins, how many Grand Slam's she wins.I think the difference is that she was like a dog with a bone - she just couldn't keep her mouth shut and it came back to bite her.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small She says it's \textbf{sexism} even though Osaka is also female so there can't be bias\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Such an entitled women. She thinks just because she has kids it means that she could never have an fault. Also the double standard is amazing because if an men did this to an women it would had been harassment. I also hated how she could called him sexist and \textbf{racist}. I hate how she and other women stan feminism yet  think they can attack and harass men without no consequences. Feminism was made for women to have equal rights to men.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small When events happen it's never one thing. It's usually multiple things coming together to flip the switch. I think it was a little of both plus Patrick not keeping his hand motions to himself.I speculate that Serena was feeling the pressure and she cracked. She was being beaten by Naomi playing her own game. It was close and Serena wasn't sealing the deal as handily as she would have liked. Naomi was matching her. It was too hot in the kitchen for too long lol.If Serena didn't win this tournament she would have to start alllllllll oovvvveerrrr again at the Australian and time is not her friend.  She got \textbf{age}, motivation, motherhood, an off season to manage and all these new fearless, strong, big ball hitting whippersnappers who are not intimidated and have far less to lose and let's not forget the regular cast of spoilers too.She needs two more to pass Margaret. She was feeling it and maybe all of the above mentioned and all it took was that call by the umpire to light the whole thing on fire 🔥. Btw I don't think she was cheating with her coach. Don't know why he said what he said. It's odd and irresponsible right!?Sleeping with one eye open here in case she's coming for me. Lol just kidding.Honestly, when you think of the immensity of the pressure she's under and how she has to play it out in front of the whole world..the money, the people, the organizations, the family, the sponsors, the coaches, the media, the popularity of the game, equal rights, women's rights, representin', the legacy, setting a record that we will probably not see broken in our lifetime or the one after ours plus all the other things we don't know about and probably never will etc etc etc! you/we will never experience at that level. We can only imagine what it's like. We can't judge what happened as if we know everything.  In the long run everything will be ok.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/340 & \cellcolor{green!5}0.294 \\  \hline
  \cellcolor{green!27}\small Sexism. Serena only yelled at the official because he was male.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I would find it funny to see a man tennisser say this is sexist you just gave me a penelty because I am a man and not a women. Later at press conferenceI am fighting for the weak man that are alone againt the \textbf{crazy} women\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small "I never lost anything in my life"\textbf{nigga} never lost his virginity oof.\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small LOL it was because she's a \textbf{woman}, that's hilarious XDDD C'mon!!!! - -\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small KKKrusher I bet she beats on her husband. The poor guy. She probably comes home after losing a match and demands rough \textbf{sex}. And if he doesn't get it up he's a dead man.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small And you're a victim of ignorance, jealousy and envy you klansman😊Speaking of "Klan"... You MFers stole your uniform design from the Blackamoors(Negros😊) that reigned in Europe for more than 1,000 yrs. DO YOUR RESEARCH! On a grand scale, your physicalities aren't, never was, and never will be even COHESIVE with ours💯 Let alone supercede us.  Lol!!! You are a mutated \textbf{race}... Here in America you have scientists working around the clock with food corporations on how to destroy SPECIFICALLY the \textbf{NEGRO} HUMAN BODY! Not realizing that you can't live without us. YOU are destructive by nature💯We are loving by and respective toward/by nature... Do you want long longevity on this planet? Well if you do,  then you need us to complain, scream \& cry about you destroying it. That way we can at least TRY and make of some balance you PARASITE🦠\normalsize   & \cellcolor{green!5}Negro, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/142 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small \@atque scientia europa universalis lol that is great humor you cracker😂😂😂But that is simply JOKES💯 No facts... but you know what else is a Joke, but "not" funny...? Is that you crackers' forebearers has built a system to cater to your privilege to such a magnitude. That they've made you so wittingly ignorant and \textbf{dumb}, by being taught that we are \textbf{dumb}... You are soon to be fucked💯Your time/existence on this planet is nearing is end... If the ancient scrolls predict correctly, for us planet's sake. Help is on the way... And maybe you won't be able to destroy this planet and dip off outerspace to colonize anywhere else. SO YOU CAN REPEAT THE SAME PROCESS😊\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/116 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small Magnum Opus whoah there \textbf{crazy} person. You think that \textbf{crazy} \textbf{racist} rants is acceptable behaviour? \textbf{Nothing} you've said even makes sense. You're making a fool of yourself.\normalsize   & \cellcolor{green!5}Crazy, Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/27 & \cellcolor{green!5}14.815 \\  \hline
  \cellcolor{green!27}\small Magnum Opus you're \textbf{dumb} because you as an individual are of low intelligence. That's got \textbf{nothing} to do with your \textbf{race}. Why do idiots like you bring \textbf{race} and ridiculous religious beliefs into everything? It just makes you look stupid.\normalsize   & \cellcolor{green!27}Dumb, Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/40 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small "All  KINDS OF STUFF" pretty \textbf{lame}excuse, tried to give a reason for horrible attitude, doubled downas an activist social justice warrior.If she honestly said, "wow, people I went kinda \textbf{crazy}, I should have handled it differently, but I just couldn't let it go. I apologise. Sorry for the way I acted so entitled.That is the way you teach your daughter that you are only humaneven though in your own head you sometimes think you are a queen and goddess.\normalsize   & \cellcolor{green!5}Crazy, Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I think Williams forgot that her opponent was also a \textbf{WOMAN}!Duh!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small SexismI hated that umpire anyways.But take \textbf{nothing} away from Osaka who played a great match.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small She shot off her mouth to the wrong umpire. She continued. She shouldn't have. She needs to do anger management. And her coach shouldn't have been cheating. As a \textbf{woman} I'm not happy that she declared \textbf{sexism} and took the spotlight\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Always white people reviewing \textbf{African} greats. Who sent u? Stop dragging this. Everyone done it\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Now imagine being Serena's opponent. A \textbf{black} Japanese girl who idolizes her.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small why even have womens tennis? why not just simply tennis? womens tennis itself is sexism\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Wtf she was against another female so how could that even be \textbf{sexism} lol\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small She meant that since the umpire is a man and she's a \textbf{woman}, he was treating her differently. Pretty ridiculous statement to make, after all the crap she did, throwing trantrums and rackets like a little baby.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small She lost simple ...... so called \textbf{woman} Got more male hormones than me.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Trevor King umpire apparently made a decision based on \textbf{sexual} bias.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Wow!  Your ignorance on what constitutes \textbf{sexism} is pitifully glaring!  This is why women get little to no respect in politics, business, and sports.  Together and separately, women and men can be sexist towards women and their plights against discrimination, \textbf{misogyny} and all sorts of society ills that are way outdated in 2019.\normalsize   & \cellcolor{green!27}Misogyny, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small Bruh she ...my bad he was playing against a \textbf{woman}...sooooo yep it was \textbf{sexism}...\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small The ref just hated Williams more? To be fair, the Japanese \textbf{chick} probably deserved it more based on the way Williams acted.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small She's a literal \textbf{Racist}. Which the left proclaims to most extents\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small This comment is sexist.... You need to apologize to *"well you know"*...A man judging a \textbf{woman}? That's the ultimate \textbf{sexism} in our time\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I thought her testicles would rule \textbf{sexism} out\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Maybe she should have went with \textbf{racism}. ROFL.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Her opponent is a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Another \textbf{black} \textbf{woman} with victim complex why I'm not surprised\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Serena is a trash just like Michelle Obama and what they both have in \textbf{common} they are mens and they don't recognize\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small This Ladies is Gents is why when your kids play sports, you SHOULD keep score, because learning how to deal with failure is as important as learning how to be a gracious winner. Sernina Williams should admit that she let her temper get the better of her and appologize rather than screaming \textbf{sexism}. It was her own lack of sportsman like behavior that cost here all those points in a match she was already losing.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Roses are \textbf{r\textbf{ed}}Serena is \textbf{black}If she losesShe gets mad\normalsize   & \cellcolor{green!5}Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/12 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@Ravage PS hedge's comment was funny but your reply is quite offensive and \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small 🤣🤣🤣 at least you dont hide the real reason underlining your opinion. Your a \textbf{racist} \textbf{honkie} 🤣🤣\normalsize   & \cellcolor{green!5}Honkie, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - White & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small \@Cecil Gordon \textbf{racism} or just facts\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Serena Williams get over it u lost you angry \textbf{black} \textbf{woman}! 0 o\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Sexism, did you not read what happened?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I would love to see what would Serena have done in an alternate reality where the match was exactly the same, but the umpire was a \textbf{black} \textbf{woman}.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Sexism? Is she serious? She does realize that her OPPONENT was a \textbf{woman}?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Honestly this behavior is terrible. I'd love to see her banned from the sport for crap like this, and I'm surprised that she still has a \textbf{black}  \textbf{woman} card to play after this.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small so you a women and playing against another women you are getting penalized while the other women is not, how in any way is that related to \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Sore \textbf{transgender} who is ugly on inside and outside!! I don't see how this could ever remotely be \textbf{sexism}!?!?\normalsize   & \cellcolor{green!5}Sexism, Transgender & \cellcolor{green!5}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Getting caught cheating is neither \textbf{racism} nor \textbf{sexism}. And playing the "you are racist/sexist" card for justifying cheating is just disrespectful for the people who are victims of \textbf{racism}/\textbf{sexism}.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small Didn't she lose to a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small The ones who were booing should be ashamed of themselves. They destroyed the probably most important moment of a hardworking athlete who worked her ass off to be there and achieve her dream. \textbf{Pigs}.Poor Naomi. She didn‘t deserve that.\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Sore loser lmao. Lose is lose, \textbf{nobody} cares if she lost, ain't no one gonna remember this in 10 years\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Loves her Reasoning....because Im a \textbf{Woman}! (Played in a female league)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Naw man no \textbf{sexism}, just a man not with taking bullshit no mather how famous you are...\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small aww, come on! she's just a sore loser. you just showed us two other occasions where she thrown the SAME ball of excuses when she was losing, but "\textbf{sexism}" bullshit wasn't trending back then and the umpire wasn't male so she couldn't and didn't use that bullshit, magic excuse. "Well, I am sorry but there's a lot of people who said way worse!"That's a huge sign of unaccountability and sore loser. She ruined Osaka's play and victory, giving her an "easy" victory and making people boo instead of cheer her in her [already unearned] victory. I can only say Osaka did good.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small "The umpire is sexist for taking her win and giving it to another \textbf{woman}", how is that logical?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'm gonna say sore loser on this one. The whole \textbf{gender} thing was only brought up by her to convince everyone that she didn't deserve a penalty.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Sexism? Really? Her opponent was also a female.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Ok lemme get dis straight:1: Your coach cheatsPenalty2: You slam the stick on the groundPenalty3: You are verbally insulting and yelling at referee for doing his job and following rules, for that you are punished with a game penaltyYour anwser to that: \textbf{Sexism}! Cuz men don't get punished.My anwser to that: Becuase men above 20 playing tennis don't usually argue like teen bitches the way you do. And they certainly get punished if they cheat. In every sport they do and the referees from football and hockey aren't different from those in tennis.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small The umpire was obviously sexist because he wanted the other \textbf{woman} to win.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Sexism should have never existed.She's literally a Sore Loser, that's not sportmanship, she's the most immature and selfish player i have ever seen.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small You know who else was a \textbf{woman}, Osaka.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I thought Osaka was the only \textbf{woman} in that match.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small "I have a daughter and I never cheat."\textbf{Weird} flex but okay\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Yes its because you are a \textbf{woman} even though there was another \textbf{woman} going against you\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hold on a secHow the freaking hell this is a sexism\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Serena William a great winner but more sore than a four year \textbf{old} at monopoly\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small wait how is it \textbf{sexism} if its just her? Naomi osaka is a girl too\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small How can it be \textbf{sexism} if it is between 2 wamen 1 wamen loses but it benifits the other 1 wamen\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I can definitely say it wasn't \textbf{sexism}. I mean come on like all umpires are different and can be more lenient depending on their moods. She's just mad she got in trouble in my opinion.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small She is perpetuating \textbf{sexism} against men by believing she is in the right when she is a sore loser.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small It's quite easy to people who know \textbf{nothing} about tennis matches to criticise Serena! It's not about this match! Like she said: a lot of men break a lot of rules and are not penalised...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Sexism in a match against two women 🤐\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Why do people still fight for women's rights? Women in first worlds have all the rights that men have, sometimes even more. What they should be fighting for is \textbf{sexism} down in the middle east and other religious countries.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small There's no way that it was because of \textbf{sexism}. She was way out of line to say that. That umpire is probably not gonna be in another match and it's because Serena Williams is a sore loser and can't lose a game without blaming it on \textbf{sexism}. Great tennis player, but because of this, myself and many other people have lost respect for her\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small She's a sore loser she wants people to feel bad for her because she's a \textbf{woman} 🤦‍♂️\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small As an American myself, Serena is a disgrace the way she acted. She is supposed to be a character of class and grace and a role model to young girls. However the way she acted was absolutely disgusting and she set a very poor example to the world and poorly represented us. It's not \textbf{racism}, it's not \textbf{sexism}, these excuses are what contributes to her negative characteristics. She needs to hold herself accountable. As an American, she totally embarrassed us and I would apologize to the world for her disgraceful and classless behavior.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small So she Claims \textbf{sexism} against an umpire in a \textbf{woman} vs \textbf{woman} match?\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/13 & \cellcolor{green!5}23.077 \\  \hline
  \cellcolor{green!27}\small in this case she did something wrong but look at the bigger picture for women in sports if this case may not be a direct ecample of \textbf{sexism} look at what is since it now has your attention\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Bernard Elmargi I thought Serena Williams was transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Bernard Elmargi She looks like the male version of every other \textbf{woman} lol\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Rolex bolox You know how I know you're a \textbf{bum}? You have a playlist about money but you were too lazy to add more than two\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Monica Wells miles ahead of th \textbf{feminazi} gorrila\normalsize   & \cellcolor{green!27}Feminazi & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small So sad she couldn't play the \textbf{race} card against Naomi.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small U guys remember when debates over \textbf{sexism} had substance and meaning and were over valuable and blatant cases of actual \textbf{sexism}?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small I don't think the umpire knows how lucky he was that this exchange occurred in the open and was recorded!She would have destroyed or damaged him with these \textbf{crazy} accusations.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Isnt naomi also a \textbf{woman}?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small "Also" implies Serena is a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Zatderpscout 25 she's also \textbf{black} tho\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small transgender according to serena\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I mean come on it can't be \textbf{racism} either since naomi is asian and not white either\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Just \textbf{black} women\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Cant believe the title is even a question. \textbf{Dumb} people\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I don't think he was sexist because she was playing against a \textbf{woman}!!!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Benny top of the tops  I beg to differ. The stories would of been about an \textbf{underdog} claiming the first Grand Slam ever for her country, instead it's all about Serena and \textbf{nothing} about the game\normalsize   & \cellcolor{green!27}Nothing, Underdog & \cellcolor{green!27}Age - Youngsters, Social Class - Destitute & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Why she didn't accuse the umpire of \textbf{racism} too? What a stupid snowflake\normalsize   & \cellcolor{green!5}Racism, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small The umpire is sexist? Does she not realise she's playing against another \textbf{woman}? Is she high?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Thats embarrassing for america......if you can't act professional in a game regardless of whats happening...you shouldn't be playing period.Your on the International stage and represent not just yourself but your country.Don't look at Carlos Ramos,regardless of what people think he has pretty much umpired all the games he has been in the same,so you can't say this is new or he was picking on her.And how can it be \textbf{sexism} if the other player is also a \textbf{woman}.......and fuck the crowd of liberal crybabies who booed Miss Osaka,they should also be ashamed of their behavior as well.I guess sportsmanship only applies when you win now when it comes to american so called pro athletes.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/117 & \cellcolor{green!5}1.709 \\  \hline
  \cellcolor{green!27}\small Why did the chicken cross the road ? Serena : Because I'm a \textbf{woman} and I have a daughter....\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Serena thought that she was superwoman after coming out of a birthing a daughter and trying to win a grand slam game but then she saw her dream of superwoman being destroyed and she couldn't phantom that it was happening. And the other alternative was to draw the \textbf{sexism} card which by the way doesn't hold water because the women are getting equal pay even though they only play 3 sets in comparison to men which play 5 sets and they do not called that sexist. So go figure and put that in your pipe smoke.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small It cant be \textbf{sexism}, they are both males!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Surprised she didn't cry \textbf{racism} too\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Lost all respect for her. She's emotional and wrong so it's \textbf{sexism} cause she cheated and got caught. And second place pays over a million dollars cause \textbf{sexism} and women have it so hard\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small If he was sexist why would he help the other \textbf{woman} win?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Accused of \textbf{sexism}...both players were women...how...i dont even...\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She is absolutely pathetic and the kind of \textbf{woman} who ruins everything. As soon as princess doesnt get her way she pulls the \textbf{gender} card. Disgrace to the sport\normalsize   & \cellcolor{green!5}Gender, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small He owes her nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small So he gave a penalty to a \textbf{woman}, but her opponent is also a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Of course it wasn't \textbf{sexism}!It was \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small typical \textbf{woman}, can't handle the truth\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small she is built like a tank.  it is not fair that \textbf{woman} like her compete against feminine women.  There should be a 3rd league in sports... butch chicks.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Black genes.  All strength, no brains.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small manictiger And where did your 'brains' get you? A decade of living out a dead music career? This \textbf{bum} is living out the ultimate irony\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Has \textbf{nothing} to do with her \textbf{sex} lmao. The reason she got a penalty and some men haven't is because not all referees are the same. I guarantee there are also women who've been disruptive and never received penalties as well. Seems like the only way for leftists to get what they want nowadays is by playing the victim card, sad.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small I don't think it was actually what she said, but how nagging she was and how relentless she was in her complaining. The umpire would have been waiting for anything that could be defined as verbal abuse to get her to stop, and thief happened to qualify. I don't think it Was \textbf{sexism} and think it was a justified penalty. I even think they could change the definition of verbal abuse to include repeated defiance or arguing for a certain length of time, as that was probably why he gave a penalty for such a minor thing.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small 'Im a woooman' 'I have a child' sad to see such a great female tennis player being just a average \textbf{woman}. No respect for her.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Because the other person was a \textbf{woman} and  Asian, she cannot claim white supremacy. So, she claimed \textbf{sexism}. Lol 😂 😂 😂 😂  I cannot stop laughing 😁 😂 😂 😂\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small The \textbf{sexism} accusation is just desperate.  It's women's tennis!  That doesn't even make sense.  Are they penalizing more women than men?  Maybe it's Serena-ism.  Ref doesn't like people named Serena Williams.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small That is the UGLIEST \textbf{TRANSVESTITE} I've ever seen in my life...ooooooofffffff\normalsize   & \cellcolor{green!27}Transvestite & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small This is \textbf{old} news!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Both players were \textbf{black} \textbf{woman}. How can she play the sexist card?\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small She said she's a mother. To mean that she's a role model she doesn't condone cheating. Its \textbf{crazy} how alot of u \textbf{dumb} idiots don't understand the context of her words. If she said that she's a mother during a press conference you all would take it to mind now because she said to an umpire u all acting smart. Plz shut the fuck up u idiots\normalsize   & \cellcolor{green!5}Crazy, Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small C'mon people. She screamed at Ramos: 1. You owe me an apology (an accusation that he deliberately wronged her). Ramos did \textbf{nothing}. 2. I've never cheated. You owe me an apology ( a second accusation). Ramos did \textbf{nothing}. 3. You owe me an apology. You'll never ever ever be on another court of mine as long as you live. (A threat to Ramos's career \& livelihood and a claim that she has more power with officials in the game, than he does.) Ramos did \textbf{nothing}. 4. You are a liar. (A direct libel towards Ramos and in clear breach of the player's code). Ramos did \textbf{nothing}.  5. You stole a point from me. (A direct accusation of the umpire's dishonesty.) Ramos hesitated. 6. You're a thief too. (A direct libel towards Ramos). He STILL hesitated. And then awarded the penalty.How much abuse is an umpire supposed to take without being speciously accused of \textbf{sexism}? Ramos showed amazing restraint probably BECAUSE Serena is a \textbf{woman}. If a male player had behaved like this, Ramos surely would have called a code violation long before.Another telling moment is when she breaks her racquet. She flinches in case the racquet bounces back and hits her. This shows (a) she is not out of control, she is aware of the consequences of what she is doing, even in the minutia, and (b) she has done this many times before and instinctively knows what happens. This is a clear giveaway of her intentions and her state of mind. It appears every bit as if she is deliberately stalling, trying to interrupt her opponent's concentration and to intimidate the umpire or at least challenge the umpire's authority by "double-daring" him to award a code violation.She's losing. She knows it. Like all great champions she has a healthy dislike of losing. But that's no excuse for behaving in an appalling fashion towards the official and to rob her opponent of her moment in the sun. The New York crowd should also hang their collective heads in shame. Serena was not behaving like a local hero that day.\normalsize   & \cellcolor{green!27}Nothing, Sexism, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}6/352 & \cellcolor{green!27}1.705 \\  \hline
  \cellcolor{green!5}\small It's completely unprofessional of Serena to jump to \textbf{blind} assumptions to Ramos' rationale for penalizing her. It's the job of whatever committee that evaluates judges to conclude whether he's consistent and objective in his rulings.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Can you imagine if her opponent was white instead of Japanese...it would be a double win for these far left loons, CNN, and TYT...sexist and \textbf{racist}!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Because she is a he. And it's typical \textbf{black} behaviour\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I lost because of feminism, even though my opponent was a \textbf{woman} too\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small How can I be \textbf{sexism}...IF HER OPPONENT IS A FUCKING WOMAN\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small She's a world class drama queen.\textbf{Nothing} more.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Wasn't her opponent, who was helped, a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I watched this live and Osaka did a really good job, but she had such a shit attitude that she made Osaka feel BAD for winning. She deserved all of those losses. I lost any respect I had for her. And it's not \textbf{sexism} in anyway???\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Sexism \textbf{sexism}? She was the one who was disrespectfull towards the umpire! And he just followed the rules!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Serena is GOAT; anybody that is hating on the Queen for getting pissed was a hatter anyway; this \textbf{Black} queen will win several more slams; save your hate up.  You are going to need it for a few more Serena GOAT years.  Love you Serena..and the new Asian/\textbf{Black} Queen Osaka.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Match is being played by two women. The umpire gets called sexist because he ruled in favor of the other \textbf{woman}? Or does she not count because Serana is the only true \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small \@SparksFly This is \textbf{old} news now but Serena Williams went on a tirade about an umpire in a match. She told her fans to go after the guy and said he was sexist. The only backing she had for this was that he ruled against her in the game in favor of the other \textbf{woman}. When people reviewed the footage it basically showed that she had been let off multiple times for unsportsmanlike behavior and had just finally been reprimanded. She has built a reputation of blaming umpires when she gets penalized for breaking rules or procedures and doesn't shy away from personal attacks.\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small \@Corrupted Archangel she is legitimately a trans gender\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I killed someone but please i am a  \textbf{woman} i have kids,, i have robed a bank but please m a \textbf{woman} n I have kids\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I gotta give you guys credit though,at least you didn't super-impose a halo over her head in that \textbf{cheesy} thumbnail. I know how much restraint that took on you guys' part, so well done for THAT, America Uncovered. America Uncovered -that name isn't a BIT over-dramatic at all, either, so don't ever let anyone tell you otherwise, okay? Okay. (lol) B-bye!\normalsize   & \cellcolor{green!5}Cheesy & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Serena has been complaining about the empire's cheating in her but the media has been telling a wrong story  \textbf{racism} is big on tennis sport and I have been watching many Serena Williams matches the official used to cheat on her and she never complain about it  and just because Serena is about to brake a very important record that is why the officials is against her which is wrong .she has been fighting against \textbf{racist} crowd and \textbf{racist} officials and the opposer\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small You saw her antecedents, the Us Open semifinals in 2009 against Kim Clijsters when she threatened to kill a chair umpire. If a male tennis a player whoever is he decides to spit at an umpire, that doesn't not mean Serena is able to falsy accuse an umpire of \textbf{sexism} just because "she's a mother and men do worse". That for me is sexist, Serena is sexist and she believes because she's the strongest FEMALE tennis player that I have seen, she can do whatever she wants to do.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small Q. Did serena broke a rule?A. Yes she did.Q. Was she penalised for that? A. Yes she was.\textbf{Sexism} or \textbf{racism} has \textbf{nothing} to do with this matter, these were just a card pulled by a looser to justify her behaviorI saw the match and serena was playing bad she was out of touch she committed many unforced errors in 1st set \& osaka played really well to capitalise on those errors and won the 1st set.I think serena knew that osaka was playing well and she cant beat her \& that's where her focus shifted from the match \& then all this drama happens\normalsize   & \cellcolor{green!27}Nothing, Racism, Sexism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}3/109 & \cellcolor{green!27}2.752 \\  \hline
  \cellcolor{green!5}\small BEGONE \textbf{THOT}!\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small sore loser, If you cant accept a loss then don't play the game. Cant be a good loser but can only be a good winner.  sounds like SEXISM\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I would like to ask anyone whether you have seen an angry \textbf{woman} from all background and all ages anytime, anyplace, where? Work, public transport, school, etc? I must have seen them plenty of times but society is just as bad. Rights and responsibilities should be a universal issue for every individual and if he/she does not live up to a standard or criteria, you face the consequences.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small OsakaWell, if it is \textbf{sexism} than why isn't Osaka getting "\textbf{sexism}"? She is also a \textbf{woman}.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/17 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small She's a cry baby b** there was no Sexes no \textbf{sexism} or \textbf{nothing} like that she got caught then she tried to play the I'm a \textbf{woman} you're being sexist and then I wouldn't be surprised since you brought up the \textbf{race} card she's a cry baby b** she lost she got caught cheating and a story she's a cry baby b**\normalsize   & \cellcolor{green!5}Nothing, Race, Sexism, Woman & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!5}4/62 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Couldn't pull the \textbf{race} card so she pulled the sexist card.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small If it was a cartoon about any other \textbf{race} it was okay but whenever there's something with a \textbf{black} person all this shit comes out...... Even if there's \textbf{nothing} to do with \textbf{race} they'll make that way and then the flavor of \textbf{sexism}...... Then some people are even saying that she's one of the greatest tennis players is all time n ol n ol.....Does it mean there's a special preference ?? Lemme give you an example.....Michael Schumacher overtook his team mate on the finish line in Austria and he was already the most successful racing driver of all time..... Still his team got penalised.....in 1997 he closed on the last \textbf{race} with this rival Jack Villeneuve..... He was disqualified from the championship....... In Monaco he did similar thing in qualifying...... He was sent  to the back of the grid..... Same goes for Valentino Rossi..... In 2015 he crashed into Marc Marquez which made the other guy go on the ground....... What Happened ?? Rossi was sent to the back of the grid in the next \textbf{race} knowing that it was the final \textbf{race} and if he was sent to the back there was no chance of him winning his tenth title but still he was penalized.So keeping all this, the bigger personality you are the harder is and should be the punishment...... Comparing all of the Serena Williams fans and she are accusing the coach of \textbf{sexism} and the cartoonist of \textbf{racism}......... They've gone \textbf{crazy} 🙄\normalsize   & \cellcolor{green!5}Black, Crazy, Nothing, Race, Racism, Sexism & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}11/247 & \cellcolor{green!5}4.453 \\  \hline
  \cellcolor{green!27}\small She's not a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Chris is still a virgin. He said he never lost anything his entire life...As to Serena she started off LYING. She said "No coaching!" "I would rather lose than cheat". Or was it lose than get caught cheating. Her coach admitted cheating. She SAW the gesture as she said "Thumb"s up!" If she was not looking then how does she know what he did? She LIED and got caught lying and CHEATING. She described the signal...therefore BOTH are guilty. The first penalty did \textbf{ZERO} as far as score is concerned. Just a warning. Then a point for racket abuse. But the whiney bitch just did not let up. Game penalty. Then the whiner accused him of \textbf{sexism}. She she be tossed for a year. The game has long been listed as a gentleman's game. Then we get this loud mouthed bitch.\normalsize   & \cellcolor{green!5}Sexism, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/142 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small What about playing the \textbf{race} card!! He is clearly \textbf{racist} too!! Probably misogynistic, islamophobic, and deplorable!! And, I think he was mansplaining too!!! Lmfao\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small So it was sexist when Serena's opponent was a \textbf{woman}? Her tirade only took away from her female opponent's victory. Then Serena had to make it about herself (I say 'her' very loosely here) again at that post match interview by telling the crowd to stop booing and directing them how she wanted.Nike needs to teach their asset how to behave better.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small S-Sexism?!S e X i S m ? ! ? ! ?She was playing against a \textbf{woman}, why would a sexist coach favor the opponent?!W-Who was sexist?!THE BALL?!?!?!?!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Loud ,obnoxious, mean like 90+ of \textbf{black} females !! "Stand Down", don't you know your place ? !!Learn to lose,learn some civility !\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Sure she just laughed at the \textbf{dumb} pratt when the media was gone.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small "SHE" is actually a "HE".   TRANSSEXUALS SHOULD NOT BE ALLOWED TO USE THE TERM \textbf{SEXISM} FOR SHIT!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small He's a man, so when he looses, he's aggressive and a bully. He sickens me. Let's have a \textbf{transgender} league. This lying dude has no right to use ' \textbf{sexism} '.\normalsize   & \cellcolor{green!27}Sexism, Transgender & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small BIG SORE LOSER, taking all the attention from the winner who worked just as hard if not harder than you just because you think the umpire doesn't like you or he is sexist, that's just wrong on so many levels, poor \textbf{woman} even apologized for winning, where do you see that?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small She's a Sore loser ! That's it ! when anyone at her level and winning so many games seems to want it their way and as her it seems that athletes who are use to winnig don't want to Amit defeat but they have no problems in defeating their rivals , she's just being a Big baby about it , now she's claiming \textbf{racism} and discrimination cause she can't face the facts that she lost the game stop crying and get over Bitch my bad ( DUDE )\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small Some of the men kick and hit the umpires which starts a few to bleed. JMO the men are doing much more out of control behavior than \textbf{woman}. But we should keep in mine that male or female , they are all only human . For them to play at this level , the pressure is high. I'm a fan of tennis and love to see great players play . This sport should sometimes let the players show some emotions because they are not robots.  JMO if you hate a player , you will never see anything positive in them. If you pay attention to Naomi Osaka , she apologizes to ever player that she beats.  After all this Naomi said she still respects and loves Serena Williams , I think everyone should let this go. When Serena per Naomi own words told her she was proud of her , Naomi said it meant a lot to her . So Naomi and Serena do not hate each other . This is not the first nor last time a player will show emotions. I'm not  looking for them to be machines . Most of them are proven winners and should be respected for their hard work.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/205 & \cellcolor{green!5}0.488 \\  \hline
  \cellcolor{green!27}\small This commentator is an idiot, it is not "impossible to say" if \textbf{sexism} was involved here.The same umpire has penalized men for the exact same level of aggression, and behavior before, and has done so consistently.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Dam that umpire for cheating \& giving that white male opponent the game.. Oh wait it was another \textbf{black} female opponent.. Shes for women's rights that's why women only play 3 sets in majors \& men play 5 sets..\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small That other \textbf{chick} may be ugly on the inside, but Serena is ugly inside and out.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Sexism applies if she had played a man what a moron! XD\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I don't get how Serena Williams says this was sexist when her opponent is also a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Lol looks like a bad drag queen\normalsize   & \cellcolor{green!5}Drag queen & \cellcolor{green!5}Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small How many white players have had such treatment in the past? I think I will plead innocent for pointing a finger at you the loud mouthed presenter for magnifying the issue out of proportion. Lastly I feel and think you are not only a \textbf{racist} but a very cheap white presenter. I hope my opinion will be respected.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small Didn't a white male tennis player have a tantrum like this? Didn't they whoop his ass too? Doesn't that mean she can't claim \textbf{sexism} or \textbf{racism}?\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Yeah.. she's a \textbf{woman}, so she should be in a kitchen somewhere taking car of her man, the master...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small IF I WAS SERENA, YA, I WOULD BE PISSED THAT A YOUNGER GAL BEAT ME.  I THINK HE HAS EVERY RIGHT TO BE UPSET.  REMEMBER SERENA IS A \textbf{CHICK} WITH A DICK.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Such a selfish and entitled spoiled \textbf{brat}. I feel that tennis breeds narcissism and superiority complexes because it's such an individual sport. Just look at the number of absolute fuckwit tennis players like Kyrigios, Serena, Tomic, etc.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small "I'm a  \textbf{black} \textbf{woman} so I should win."\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@Ai Kun You a \textbf{racist} too. She was outplayed by Osaka yet WAAAH SERENA WAS VICTIM OF \textbf{SEXISM}.  Please, she sounds like Steve Smith, busted for ball tampering in South Africa.\normalsize   & \cellcolor{green!27}Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Osaka is also part \textbf{black}....so she couldn't cry \textbf{racism}.\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Everyone gets angry at times about perceived unfairness and injustice.  The problem is that it's not as big a deal when a man blows his top as when a \textbf{woman} does.  There is an expectation that still exists, especially upon very powerful women, to always maintain control and never show any emotion AT ALL.  Whether it's a tear (oh, she won't be able to handle the responsibility) or a shout (she's out of control and a poor loser).  Think back for a moment about how Hillary Clinton over modulated her emotions, almost appearing to be too stoic and impersonal at times (was she trying too hard?) and compare her demeanor to Donald Trump during the 2016 Presidential campaign...it just shows you that a \textbf{woman} will always be judged more severely than a man when it comes to portraying herself as powerful and in control.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/144 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small Sexism?, no she is just a bad loser\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Serena has no business crying "\textbf{sexism}" in her loss to Naomi . She is a \textbf{transgender} . She's the one at "fault" in my book . The "sexist" is her as I see it . She is on a very slippery \textbf{slope} however she see's the future of tennis in Naomi and knows her days as a leader are  numbered in my opinion .\normalsize   & \cellcolor{green!27}Sexism, Slope, Transgender & \cellcolor{green!27}Gender - General, Nationality - Chinese, Sexual Identity - Transexuality & \cellcolor{green!27}3/64 & \cellcolor{green!27}4.688 \\  \hline
  \cellcolor{green!5}\small If the opponent is male and the umpire favors the male then that is \textbf{sexism}. Im just imagin8ng if having a child makes you deserve to win, then federer has 3.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small The LATIN AMERICAN guy/coach was clearly depicting \textbf{RACISM} and \textbf{SEXISM}.  This was very clear !!!\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small yes there was \textbf{sexism} a**** remember John Mcenroe play some tapes you stupid f***\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small You're full of S\@\@\@ !..slightly different yea right 🤦‍♀️ He acknowledge he was wrong dum a\@\@..what are you going to fine wrong with her..she's \textbf{black} too ...lol\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small This has \textbf{nothing} to do with Osaka.. She played very well congratulations to her 👏🏼👏🏼🎉🎉🎉👏🏼👏🏼 Serena Williams was right to stand up for what is right ..Don't allow no one to threaten your integrity or your character, I would be offended as well 🗯G.O.A.T HATER WILL BE HATER BECAUSE SHE'S a very strong And professional \textbf{woman} tennis pro 👑🗯 She has a child that looks up to her... and this is \textbf{nation} wide 🗯I would've done the very same thing to defend my rep.👏🏼👏🏼👏🏼👏🏼👏🏼 their both are \textbf{Black} now what you going to say ...hold on Osaka they will come after you too... 👑👸 so proud of Osaka winning for her family name 👏🏼 Two soul sisters Queen 👑 and Princess 👸 bravo 👏🏼👏🏼...Serena Williams is a comeback 👑 Just In case you didn't know 🗯 she was so hurt 🗯\normalsize   & \cellcolor{green!5}Black, Nation, Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Gender - General, Nationality - General & \cellcolor{green!5}4/141 & \cellcolor{green!5}2.837 \\  \hline
  \cellcolor{green!27}\small Self entitled angry \textbf{black} \textbf{woman}. They all are. ALL.  Nuff said.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small DUMB LOSER . She used almost all the cards available to get people on her side and still failed.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small would you expect any other type of behavior from a \textbf{negro}?\normalsize   & \cellcolor{green!27}Negro & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Shame that record is \textbf{nothing} to being a sore loser! Shame\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small America should honor Miss Osaka ! She won because she is good but those people who went to this tennis match are and should be ashamed of themselves for making what could have been sa beautiful moment ' horrible for Miss Osaka' shame on you Grand Slam spectators .And you Miss Williams you behaved like a little spoiled \textbf{brat} ,unacceptable and unprofessional you are a sore looser trying to distract the world from the fact that there's someone equal or better than you,besides sport people don't die of \textbf{old},\textbf{old} \textbf{age} with the trophy on their hands if not now someday you have to step down.What you are going to brake rackets every time you loose Shane on you! .You made matters worst by saying no more booing did you realized that?? I'm sure you knew! If I was Japan I will never send another player ever again to the Grand Slam or whatever😞😟😡\normalsize   & \cellcolor{green!27}Age, Brat, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/153 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Its not \textbf{racism} or \textbf{sexism}, its Steroidism\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small If her opponent was white she should have surely used \textbf{Racism} Card........ Her soul suits up with her looks...\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small She is taking attention away from her ridiculous behavior by putting the focus on \textbf{sexism}. She should first explain her foolish behavior. You dont get out of a punishment by pointing to someone else who got away with it and wanting to also get away with it. Thats how little kids argue. 'My brother does that all the time and you never punish him'. She knows she made a huge mistake. She should have kept her mouth shut during the match and brought up her complaints afterwards. And she knows it. But she is still trying to win the arguement the wrong way. The more she blabbers on, the more she is losing respect. She should be asked the right questions like what she thinks of her behavior and if it merited punishment and not let her compare it to other players who got away with anything. If other similar situations had different outcomes is besides the point of whether or not she deserved what she got, according to the rules, THE RULES! And serena is great at coming back from being behind in a match. She could have won, had she just controlled herself. Then she would have looked like a champion instead of a big baby. Sorry to say that because she is such a great player. I hope her behavior is not provoked by drugs. I dont mean recreational drugs. I mean performance enhancing ones. She should have bern tested after that long long outburst. I understand outburstts but not like that where she knew she should have stopped long before, but couldnt, maybe due to having consumed something. The communucation with her coach was obvious and blatant. Take the pount penalty and move on. Dont act like a baby and carry the behavior into interviews after the thing is long over.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/305 & \cellcolor{green!5}0.328 \\  \hline
  \cellcolor{green!27}\small No, he is the greatest  \textbf{tranny} tennis  player.\normalsize   & \cellcolor{green!27}Tranny & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Racism and I fire that coach\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small No she's not! Shes a not a looser and it is not \textbf{sexism} either. She's bipolar...period!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small you are a winner? In which Biotope..she is \textbf{old}.. AT the end of kariere..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small serena is \textbf{nothing} but a bully,always setting a very bad example to young people!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small This girl is just trying to blame \textbf{sexism} for her downfalls.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small SERENA WILLIAMS ACTED LIKE THAT BECAUSE SHE IS A MANHATER AND SHE IS A \textbf{RACIST}   (and maybe a man)\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I don't get how it's \textbf{sexism}. Her opponent is a \textbf{woman}. Even if he was favouring the other player, it still isn't \textbf{sexism}. It would be wrong,  but not sexist.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/30 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Time to hang it up \textbf{old} girl...CRIP WALK OUT THE DOOR...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I have a daughter, I am a \textbf{woman}, therefore I should be allowed to insult and abuse whoever I want.What the hell is wrong with you guys ?Jokes aside I watched the match on TV, after that coatching signal Serena goes forward and gets the point as her coach's signal.That moment after what she said to umpire and then does that was quite annoying to watch tbh.Rest of the violations however is hard to explain and you will ask why...Because this individual is a professional, she knows the game, she knows how to handle stuff so how the hell in a world or why a professional player would keep acting that way if it's not McEnroe ? That's the question, I saw Serena play many matches before and she was all fine, not as emotional or careless like this except we came across to same scenario before against Kim Clijsters which was a new mother back then and the \textbf{woman} casually won US Open.Gotta love her. :DThere is no excuse for what Serena did or what she said about all \textbf{sexism}, \textbf{racism}, etc. She just ruined Naomi's first grand slam celebration which meant a lot to her and her country as well.Never cared much about Serena before, her gameplay doesn't give me any joy but never had any type of emotion against her till now since I didn't care about her games but now I just don't like her at all.Hope never gets to any other finals so I won't have to watch her, hope no one has to watch her.\normalsize   & \cellcolor{green!5}Racism, Sexism, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}4/265 & \cellcolor{green!5}1.509 \\  \hline
  \cellcolor{green!27}\small Sore Loser. \textbf{Nothing} more, \textbf{nothing} less. She should feel ashamed for ruining a new champion's victory.If I were the umpire, after the first minute of whining I would have disqualified her.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Is that a \textbf{transgender} tennis player.???\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Sore loser and liberal \textbf{snowflake} with a victim complex\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Sore loser? There is only one person who has won more grand slams. Too...ramos has been verbally abused by kyrios...he was sending f-bombs at Ramos and he did \textbf{nothing}. Same with Djokovic....ramos did \textbf{nothing}... that is why she complained. Also..i don't how many of you actually follow the sport or just want to comment...but tennis more than any other sport is really about the players. Yes they are bigger than the game that is why the stars get appearance fees to play at tournaments. Also...if a tournament is sponsored by a sports management company ..players who are not managed by that company will not get invited.  Too...if Serena is in a final the ratings for the final are very high versus her not being in a final. Which means more money in advertising dollars.... however...her point is that he ignored the men but instantly penalized her... that is why she complained and no he probably won't work another match of hers. Too..Only one Serena...chair umpires are everywhere. \textbf{Nothing} special about him. The don t pay to see chair umpires...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}3/180 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small How is she the victim of \textbf{sexism} when the other player was also a girl,also the same ethnicity\normalsize   & \cellcolor{green!27}Ethnicity, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Serena is a SORE LOSSSERRR absolutely disgusting that she made it about \textbf{gender} and using her mother hood as in excuse for her bad play. She is a disgrace to the sport and she should just retire. Absolutely disgusting\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Well, i would attribute Serena \textbf{mental} breakdown to prolonged chronic steroid usages,medical warning do cites such \textbf{mental} breakdown as side effects of prolonged steroid consumptions.However the Contents of said \textbf{mental} breakdown would be attributed to Serena's leftists ideology.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/40 & \cellcolor{green!27}7.5 \\  \hline
  \cellcolor{green!5}\small It's not \textbf{sexism}, it just depends about who the ump is and what you do\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Was the person she was playing against a \textbf{woman}? If yes the it can't be \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I'm sorry sir you're wrong about that most \textbf{black} women have a bad attitude because they've been oppressed rate and they sell out they \textbf{black} man for the white man\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Not \textbf{sexism}, Ramos is a VERY strict umpire, men may have said worse things to other umpires but that's what it is, other umpires you can't compare other people saying other things to other umpires isn't a fair case\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Woman rights hahaha 🤦🏻‍♂️🤦🏻‍♂️🤦🏻‍♂️\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Funny thing is that they were saying all she said was "thief" but she was also pointing and threatening him with his job, she was abusing him ever since the first code violation and was lucky not to get disqualified. Because I have seen men get disqualified for acting in the exact way she was. \textbf{Nothing} but a thug and a bully and she doesn't deserve to play on another court ever again.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Are they sure its a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small A \textbf{black} \textbf{woman} being overly dramatic and wicked sassy. I don't think that's the stereotype everyone knows all to well. \textbf{Black} women are not known to act like this.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/29 & \cellcolor{green!27}10.345 \\  \hline
  \cellcolor{green!5}\small she deserves to be suspended for playing \textbf{sex} card...what a nightmare of a human being?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I have a motto for society: Punish the man, help the \textbf{woman}. Even when the \textbf{woman} does wrong, she gets praised by society. If I think that the \textbf{woman} is fifty percent a sore loser, then society is also fifty percent sore loser. A mismatch.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/45 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@JACKOCHAN21 The other day on a topic whether sixteen year olds got the vote, one female caller said that young voters are stupid. Well, if she thinks that then she is stupid. It goes both ways. If this was at a workplace and her employees heard it, she would have been suspended from her position, same with the male equivalent or any individual regardless of \textbf{nationality}, \textbf{age}, able, less able, etc.\normalsize   & \cellcolor{green!5}Age, Nationality & \cellcolor{green!5}Age - General, Nationality - General & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small Dante pillonHer " I have s daughter' argument doesn't hold was as with same breath she screaming and , abusing an official and calling him a thief- what if he had said that.Sorry, that daughter should be shown this tape on her 12th birthday and told not to behave like this spoilt, entitled \textbf{brat}!! Shame in you Serena- you rmbaras womankind.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small It's simple, if Serena didn't want those penalities, she should've acted like Naomi. There was no \textbf{sexism} in that game because \textbf{nothing} happened to Naomi.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Embarrassing woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small How is it \textbf{sexism} or even \textbf{racism} when her opponent is also a female and half black\normalsize   & \cellcolor{green!5}Black, Racism, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small Serena is a \textbf{transgender}, She calling \textbf{sexism}?\normalsize   & \cellcolor{green!27}Sexism, Transgender & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small a \textbf{black} japanese girl, thats something i thought id never see\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Boken ka gaming Japanese were originally \textbf{black}, go check ur history, white men killed them out and raped they \textbf{woman}, that's where u came from,\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small She was completely out of line showed \textbf{zero} class\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small All I know is that it isn't \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small In the wake of Serena Williams' temper, tantrum and allegations of "\textbf{sexism}" of Carlos Ramos's penalties levied at Williams, it turns out studies have found that male tennis players are penalized more often than female tennis players. Ramos has received an apology from USTA president Katrina Adams, who joined in on the fray to claim that men get away with more than women in tennis. The facts, however, show that women get away with more than men in tennis.   [LINK] \normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small Since when is trashy unsportsman like behavior something to be proud of? You can't just cry \textbf{racist} and sexist at everything. It completely waters down the term and delegitimizes actual instances of \textbf{racism} and \textbf{sexism}.\normalsize   & \cellcolor{green!27}Racism, Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small If her opponent was white im sure she would have cried \textbf{race}... ugh....\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small ........serena williams accused of \textbf{sexism}?....bruh she looks more of a man than me\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I feel like this is less about her being a \textbf{woman}, and more about her being one of the most famous players. With all eyes on them, no ref is going to let the world think that a top player is above the rules, or they can just do whatever they want.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small She's not fighting for women's rights. She's doing it all for herself, she is selfish and greedy. I absolutely cannot believe the pettiness she has displayed by breaking the rules and then calling \textbf{sexism} in order to empower herself with a legion of man haters, that's why she said it. She knew she would get support. She is the thief, she stole that match and all the pride and glory from the true winner. Serena would have lost anyway, utterly pathetic.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small When she threatened him that he would not officiate any of her future matches is what I think broke the camel's back...jeez who makes that kind of threat when she has \textbf{ZERO} control over who officiates the matches...\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small The answer is no, it wasn't \textbf{sexism}. Over the past 3 years, that same umpire has done the exact same thing to men along with \textbf{woman}. The problem wasn't \textbf{sexism}, it was the umpire who has his own way of judging.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small wtff..  In what way does she think she's fighting for women's equality by making herself an embarrassment to her \textbf{gender}? Her loss of temper and her bad behavior do not equate to sexist behavior. These officials calls are all logged, you can find the logs of his calls against every player that he's ever officiated for. It's pretty consistent. She's an asshole..and a terrible example for "equality for women".\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Lmao that ain't no woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small You must have seen an angry \textbf{woman} plenty of times, let alone tennis. This does not comes as a surprise. You lash out, you face the consequences.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small I dont even care about that claim but she complained about her being a women as a reason dir \textbf{sexism} while playing against a.... women...\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Norbert Chong I think there is \textbf{sexism} for both sides. I see what you're talking about though.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Actually this us open's \textbf{woman} final was watched by more people than man's final\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small The analysis ist mostly fair, but it fails to point out clearly why Serena was docked a game after continuing to hassle the umpire: he docked a game solely because calling him a liar and a thief was her THIRD code violation during the match after the illegal coaching and her subsequent raquet breaking. If it would've been her first or second violation, he wouldn't have docked a whole game. Serena is right: men have indeed called umpires far worse many times and haven't been docked a whole game - but this was simply because they hadn't accumulated three code violations,  after they had insulted the umpire. They knew when to shut up. Serena didn't. That's all. No \textbf{sexism} at all triggered this unfortunate escalation. When Andy Roddick said on Twitter that he has called umpires far worse without getting a game penalty, he hadn't thoroughly analyzed Serena's specific situation. Andy simply hadn't accumulated three code violations after  he had insulted an umpire with foul language. The umpire acted totally within the existing rules in Serena's case. It's deplorable that the WTA and the USTA failed to acknowledge this clearly.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/190 & \cellcolor{green!5}0.526 \\  \hline
  \cellcolor{green!27}\small Even if this were down to \textbf{sexism} vs. the idea that male tennis players have said worse and got off scot free so what. One umpire is not the entire association of umpire and a couple of male players is not all of the male players. I thought an umpire was a judge and discretion and case by case judgement are applicable to the day and situation. In a court room a judge can hold you in contempt (with probable cause) if you give them a reason OR guess what...they DON'T have to. The idea is why tempt it. Why bash and shit on the individual who can JUDGE rather or not you're being out of line in that very moment and invoke a penalty against you. And even then --- PERSONALLY ---- I'd rather be called a chicken shit or a wanker or a fucking idiot than to be called a sexist. The former statements are made out of just anger. The latter statement isn't just made out of anger. Its an assault on my character. \textbf{Nothing} is more insulting than having your very nature attacked --- especially when you're just doing your job. The only way you could systematically prove this MAY have been sexist is to gather up all of code violations based on abusive or derogatory nature and tally how much of it is female player to male umpire and male player to male umpire. I'm willing to bet my fucking left butt cheek that in the last 10 years more infractions were against men nearly 3:1\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/261 & \cellcolor{green!27}0.766 \\  \hline
  \cellcolor{green!5}\small Not so... she didn't want the line ref (a \textbf{woman} by the way) removed... she threatened to shove the ball down her throat for calling a foot fault, to which the (female) umpire docked her 2 points... 1 for the foot fault and 1 for threatening an official.   The second point she got docked was the match point    She's just a sore loser, as noone can call \textbf{sexism} in that case as both the line ref and the umpire were female.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small 3:47 "I'm fighting for women." No, you literally were fighting against a \textbf{woman} in a game of tennis and you ruined what was going to be her first huge victory by bitching at the ref for penalizing your childish behavior.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Naomi is a girl, and Serena says \textbf{sexism} is the reason she lost.🤦‍♀️😅Sore loser and cry baby\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Built like a man. Dominated the courts because of being built like a man. Pissed off when she loses to a \textbf{woman} shaped like a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small African americans were originally slaves, bred for work in the fields.  \textbf{Eugenics} made them stronger than other people, the line carries 150 years later, and that's why they excel in sports so often.  Apparently not swimming or gymnastics though.\normalsize   & \cellcolor{green!5}African, Eugenics & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@A Jim Fan. I like how you carefully crafted your response and spoke of slavery. But no there's a difference between a man from a cotton picking slavery plant 7 decades ago looking like a brick shit house and having a reason for looking so big. Serena isn't from any of decades past , hasn't been slavery cotton picking or anything. This man \textbf{woman} is light years bigger built than most twig tennis players. Its like bringing a tank to a knife fight. Kinda obvious who's gonna dominate. So no the \textbf{chick} has had tons of success from her enormous build. Amazon \textbf{woman} vs the chicklets. I'm sure she'd say its been hard work only but hard work is easier with so much testosterone running through you. Your comment made me chuckle \textbf{black} people aren't bigger built because they were slaves. There just bigger built. You have a great imagination though.\normalsize   & \cellcolor{green!27}Black, Chick, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}4/151 & \cellcolor{green!27}2.649 \\  \hline
  \cellcolor{green!5}\small \@Reliable Drywall It's a meme I heard, tbh.  It could be that the benefits of \textbf{eugenics} take hundreds of years to wear off.  Not all blacks are like that - sometimes it doesn't show up, but other times it does.  Uncomfortable truths.\normalsize   & \cellcolor{green!5}Eugenics & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Crestfire come to africa you will that it is not always the case it is actually like here very rare to see a huge \textbf{black} guy.... most of them are very \textbf{thin} and \textbf{skinny}.. still strong... but even SA rugby you will see our bigger guys are white and not black\normalsize   & \cellcolor{green!27}Black, Skinny, Thin & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!27}4/51 & \cellcolor{green!27}7.843 \\  \hline
  \cellcolor{green!5}\small Serena Williams is a Dude so there can't be \textbf{sexism}. I mean come on look at Him, never seen someone more masculine\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small She is \textbf{old}....should retired...she's \textbf{crazy} too..\normalsize   & \cellcolor{green!27}Crazy, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small even if she defines as a \textbf{woman}, she looks a lot like hormone cures, or like a genetic anomally by birth (wouldnt call it trans, it doesnt have much to do with sexuality, more with the \textbf{sex}, or \textbf{gender} itself). some very succesful women in sports have balls behind their vagina. testostorone destroys womens sports (its doping) and could even be a reason for her temper. rich martzenis comment was meant more like a "daddy joke" i think, mine is not. just google the name "caster semenya" for example, she has to take estrogen to still get licensed in sports because she is a hermaphrodite.\normalsize   & \cellcolor{green!5}Gender, Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/105 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Hmmmmm. Sounds like you guys don't know that Osaka still admires Serena and would appreciate the non \textbf{racist} comments considering she is also \textbf{Black} They are in good terms. You guys just want this 'Serena vs Osaka' mindset\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Serena you are the biggest sexiest and \textbf{racist} person there is not to mention a winer\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small She claims it's \textbf{sexism} but wouldn't it be \textbf{sexism} if the ref didn't indiscriminately enforce the rules which caused her to lose because she's a \textbf{woman}?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small Saying he was \textbf{racist} and sexist is stupid when the other player was literally also a \textbf{woman} and \textbf{black}... so why then was one penalized but not the other? Both are women so it can't be \textbf{sexism}, both are at least part \textbf{black} so it's not \textbf{racism}, the only key difference was one broke the rules and the other didn't.\normalsize   & \cellcolor{green!5}Black, Racism, Racist, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}6/60 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Serena lives a dream life that most will never experience. She's a rock star and is given rock star treatment and it's gone to her head in moments not going her way. I think she was finding an excuse for having her tantrum and reached for what was available, so the chair umpire was a man so why not say that \textbf{colored} his officiating for her excuse. Her 2009 US Open final blowup had a \textbf{woman} chair but still Serena went as far as to threaten the lines person with shoving a fucking tennis ball down her fucking throat for calling foot fault on her, so you see we have Serena getting out of hand because things were not going her way. The match was over when the female chair umpire gave a point deduction on match point, well \textbf{race} came into play because the chair umpire was white and the lines person was Asian. You see where I'm going with this, unless there's some glaring proof where do you stop blaming \textbf{race}, religion or \textbf{sex} for the outcome of umpiring? And if a male player was to say the same thing Serena said to a diminutive female lines person about shoving a ball down her throat, he would have effectively ended his career and never heard the end of criticism, so yes I can see \textbf{sexism} in that instance because Serena has gotten a free pass for that one.\normalsize   & \cellcolor{green!27}Colored, Race, Sex, Sexism, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}6/240 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small can everyone say: secret \textbf{transgender}?? Even the voice sounds \textbf{g\textbf{ay}} in this video. If this isn´t an example of 'hidden in plain sight' I don´t know what is.\normalsize   & \cellcolor{green!5}Gay, Transgender & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small How can it be \textbf{sexism} if the other player was A \textbf{WOMAN} TOO?? AND CHINESE??!?!?!?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small I'm sorry but he is a sore loser. He acted like a spoiled \textbf{brat}. He called him a a thief and was very abusive towards him,but he kept his cool and was being the bigger man.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Of course she blames it on \textbf{sexism} instead of taking responsibility for her actions.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small If you went against the rules and got a penalty, you have friggin \textbf{nothing} to say. "People have done way worse?" Well some people are serial killers. Does that mean its ok to kill just one person? It doesn't justify your wrong doings. So illogical lol\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Trigger Warning what if that daughter is a \textbf{thot}?\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small As posted elsewhere.Basically, Serena is full of her own self importance and deserved everything she got. She is an insult to everything she claims to stand for and has set so many things backwards because of her petulance and infantile hissy fits.I have been complaining quite a lot recently about tennis stars acting like they owned the world, instead of them owing the world everything. A prime example was Djokovic, who I suspect has been put firmly in his place by all around him because he is now acting more like an adult and not a spoilt 6 year \textbf{old}.Did you see the match when a kid couldn't understand when he was called out and penalised for hitting a ball into a  chair umpire's eye and injuring him "because everyone does it". And that is what Williams and her ilk are responsible for. She should be ashamed of herself and apologise to the world.fyi I have read and watched reactions and reports from around the world and the telling thing is that the only country where Williams gets support is the USA, which is also an indictment of the sorry state the USA has sunk into.I remember JFK with his 'My fellow Americans, ask not what your country can do for you, ask what you can do for your country.Trump, Williams et al : "My fellow Americans, ask not what you can do for your country, ask how much your country can subsidise and support you, whilst you avoid doing anything remotely meaningful in life.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/261 & \cellcolor{green!5}0.383 \\  \hline
  \cellcolor{green!27}\small Every \textbf{black} person i ever met has this personality if they do something wrong or fail it somehow is racist/sexist or what ever reason so long as it is not your own fault.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small How egoistic of her to claim that's sexist. \textbf{Sexism} is a real problem and she's just bringing it up for her own profit. She deserved the penalty and when she got it she couldn't take it.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I wonder if Serena knew that osaka was also a Woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Ugly animal ! This is not a \textbf{woman} !\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Sore loser entitled \textbf{brat} always the victim ramos calls it fair\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Isn't Osaka a \textbf{woman} too???\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Anyone else notice that she looks to make sure the camera is filming after yelling \textbf{sexism} at the judge. 3:32\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Common Man, especially agree with disappointment of Billy Jean King's statements. However, over the recent years she has been revealing more and more of her feminist-sexist attitude. Wish Bobby Riggs or someone else had beaten her then. Anyway she is an embarrassment to having the USTA Tennis Center with her name on it. Especially compared with Rod Laver in Melbourne is a true representative of tennis and would not attempt to use his credentials to further political agenda or false social agenda; Though Martina Navratilova's social media statements support Carlos Ramos and state the conduct and behavior of Serena was incorrect, still she stated about inequality of judgments across tennis, which is not correct though there are some variances, but so do every sport-game. It is normal, because of humans vary. Am actually more disappointed with Chris Evert, especially she was commenting on the match, and during the broadcast states the issues of Serena's conduct and behavior. Then on social media states that Carlos Ramos went overboard. That is clearly two-faced. Secondly, would expect she would actually know the Regulations, but her social media statements show her ignorance; Martina's statements confirm her knowledge of the Regulations. Billy Jean King seems to ignore the Regulations and states her opinions based upon her pre-supposed, premise of Feminist-SJW, PC type mindset. And Patrick McEnroe, former head of USTA is another embarrassment, also showing his ignorance of the Regulations. So is Katrina Adams a similar embarrassment. Seem time for a replacement to get balance in their. Katrina at the award ceremony clearly showed bias toward Serena. It was disgusting, appalling, disgraceful. See how different she was last year with Sloane Stephens. Indications she is a racist-SJW type, though not absolutely clear. Nonetheless, under Katrina's direction there has been degradation and there needs to be a turn-around. They could have supported Naomi Osaka. They also have not much going in the Men's area so far either. There are so many foreigners who specifically move to the USA for tennis development and training, and maintain their country affiliations. That is fine, just shows, there is among the best training, development available but not very many USA citizens. The women do have many rising often, not many stars from the bunches yet. Some more promising currently, we will see. Of course, which other sport other than professional tennis can a \textbf{woman} excel and achieve large amounts of money. Do not have to even be 1 nor GS winner to get high levels, though the bigger amounts come with either or both. For men, there are numerous other sport-games for athletes to choose. This is world-wide, though elsewhere limited more to football/soccer and tennis.\normalsize   & \cellcolor{green!5}Common, Woman & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/446 & \cellcolor{green!5}0.448 \\  \hline
  \cellcolor{green!27}\small I don't agree what she did but media were really blowing this issue out of portion. Athletes being frustrated are very \textbf{common}, but many people attacked and mocked her appearance as well which is very uncalled for.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Zero to do with the coach. At that level, if he is throwing out hand symbols...she is certainly in know and they have had conversations about these exact situations.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Neither, victim of \textbf{racism}.Get it togetherYou see it, you just don't want to say it.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Serena need to control her attitude and to accept if ather are beter then her.I ges is hard on Serena to accept to loose from some one who never  got so far beafor.Bravo Naomi and good luck in the feauture.Serena start to blaime the umpire for \textbf{sexism} so she wont be judge so bad,and many will be on her side.It is a big shame what she did to Naomi's wining.Shame on you Serena.:(\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small Wow......No body wants to say it....Be \textbf{black} for a day and you might begin to understand. Beyond understanding. We can't be good we have to be great all the time. The minute we stand up for ourselves we become violent a bully  ect.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I say ban her for life, absolutely disgusting attitude, \textbf{nothing} to do with sexism\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Other players have said worse and gotten away with it, true. Most of those matches weren't officiated by Carlos Ramos, who's picture is joked to be next to the term "\textbf{Zero} Tolerance Policy" in most law books.It's a well known fact that he doesn't play around, he sticks to the rules and if he sees you breaking one he will waste no time hitting you with a penalty. He's done it to men, he's done it to women, he is the equivalent of an \textbf{old} catholic nun in a catholic school. She knew this going in, and yet here we are anyway.\normalsize   & \cellcolor{green!27}Old, Zero & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/103 & \cellcolor{green!27}1.942 \\  \hline
  \cellcolor{green!5}\small Nah I would rather call her a over privileged and overrated tennis player that really needs to cut the shit and stop blaming \textbf{sexism} and just realize she's a bit \textbf{old} now and may just wanna retire before she destroys her reputation like JK Rowling\normalsize   & \cellcolor{green!5}Old, Sexism & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small \@tenedria Yes, being defensive over being accused of cheating is normal, but it is not normal to play the \textbf{sexism} card. She is taking advantage of it which makes it hard for women who are actually having sexist acts against them to make things right.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small \@Qwerty Keyboard over rated? She was out of line and cant stand her. But to call her over rated is crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small lol how did a call for a thief from Williams use the \textbf{sex} card? Like how does that even connect to the argument? XD She should probably think before she speaks. Cuz she WAS cheating haha, and she was trying to cover it up, and then have no other argument then called the chair umpire a thief, then use the \textbf{sexism} card? LOL.\normalsize   & \cellcolor{green!27}Sex, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small ...the other player was a \textbf{woman} too. Moving on...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I don't know the probability of a \textbf{woman} having male index fingers or belly button positioning but Serena's got so many masculine physical proportions/characteristics. As a kid she was the most boyish girl I've ever seen.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small totally both she is a \textbf{racist} sore loser who didnt like getting beat by a Asian first-time grand slam player\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Money and glory make most of times people arrogant. Tennis is a gentle sport. Vitriolic criticism isn't tolerated. I don't see any \textbf{sexism}. I just see a frighten umpire who is attacked verbally. The umpire at the beginning wasn't willing to punish her immediately but Serena was becoming more vicious and he couldn't let her continue. Soon afterwards Serena was transformed to a crying innocent victim of \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Sexism? Naaahh!  Bratt Brat\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Sad for Osaka. Her moment was taken from her. Stupid \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small To address Serena Williams game  with Naomi Osaka in the US open final in 2018 I did not watch the game but I have this to say to Serena Williams let your tennis do the talking and not your mouth, on some occasion your opponent is going to out play you do not let that be a problem and a distraction to you, the most important thing is you are still playing the game of tennis right now, and there will be lots more opportunity so stop wasting your golden opportunity to be the best player ever in the \textbf{woman} game of tennis 🎾,Your main gold and focus right now is to beat Margaret Court title, and that will definitely shut up 🤐 all the bad minded critics in the media that have a lot to do with how people will perceive you, the bad minded critics in the media will never make you forget that Margaret Court is still the best number one \textbf{woman} player ever, It will be very bad to see the statistician use statistic to beat you with if you do not brake Margaret Court title, you really do not want any one to hold that against you it is in your hands all you have to do is put more effort and planning in your tennis final, your opponent do a lot of study 📖 on you they watch video tape of you day and night to find your weakness and your main weakness is your service game falling apart by you some time rushing the game when you need to stay calm and  focus, get your service game right and it is impossible for any one to beat you, and do what your opponent do to let them serve first your opponent always want you to serve first so that you can drop your service game so that they can have a very easy game, by not holding on to your service game that will only put pressure on you to stay in the game, it is full time now that you turn the table and let them serve first to put them under pressure by attacking there game if you do not really know what they are trying to do is use psychology on you, when you serve first you're at a disadvantage simply because your body is not fully tune up or insync as yet, for you to get a positive rhythm going the motivation may be there but your have to be in tune to get a feel of how the tennis court is playing, It is to be expected that the people that run and control tennis will tell the chair umpire like Carlos Ramos to issues a violation on Serena Williams by any means necessary the people that run the game of tennis will tell the chair umpires that they have to be very strict with Serena Williams simply because they do not want to see Serena brake a white person record and that is  Margaret Court record, people still have \textbf{racist} bioses so do not be fool all that glitter ✨ is not always gold, you should know by now that white people have not change from being bias and \textbf{racist} toward \textbf{black} people, and it was said in the US open tennis 🎾 game that your manager Patrick Mouratoglou was coaching you in the stands, if that is true he should know better by now, he should knows that is not allowed or permitted in the game, And I really miss seeing your father Mr Williams at your tennis games, Mr Williams was your coach and your mentor and your inspiration. So big up to your father Mr Williams, and I do hope that everything is ok 👌 with him. And I cannot understand why have Serena take on a white person mentality Serena you are \textbf{black} and white people will always see you as \textbf{black}, even though you are married to a white man it make no difference what so ever, now you adopt the white people dirty nasty mentality of being very arrogant and you have move far away from your own culture and roots to embrace and adopt another person culture before and one say anything I am a very realistic person, yes I know that we have choices but it is what we do with the choices that we are given that is what define a person of been who they are. It is said that we are living in a white man world, but I begged to differ we are living in Jehovah god world 🌍.so did not the white man came and saw that the earth was here long before he came and imposed his will with physical brute force and the white man did not pay any attention to what Jehovah our righteous majestic father had said in the bible he said thou shall  not kill the white man shed lot of innocent 😇 blood on this earth to get where they are now.\normalsize   & \cellcolor{green!5}Black, Racist, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}7/845 & \cellcolor{green!5}0.828 \\  \hline
  \cellcolor{green!27}\small 100 entitled \textbf{brat}.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I don't think it was \textbf{sexism} but I do think they've had enough of Serena as she's \textbf{black} she wasn't meant to get that far the fact she won all of them medals should take her lost as a win because they never liked you or your sister from the start you was a stepping stone for later on in the years they can say that they will never \textbf{racist} they never expected you to win I thought you would be a loser I'm sure there's other \textbf{black} women that can play tennis but they seem to only keep you there because you're entertaining if you look at it you are winning and the white people are interested as they will win in their bets I wish you didn't play tennis when you started to get too much spotlight seeing you every year winning medals that is when the media started to get nasty paint you as a sore loser it's because you're \textbf{black} tennis is for those white prestige people they don't want to see \textbf{black} women in tennis running around the court it's the truth because you were winning they had to put up with it and just make the most profit out of you spreading rumours in the media to mess with your head to start throwing you off your game that's why you lost that last match against that white \textbf{woman} you wasn't a sore loser then as the Media problems never got to you that much now when it came to the cup final you have the energy of the people that fill against you you don't need the support of those in the crowd but if you're getting social media getting into your head into your personal life then it can affect the way you play they got tired of you winning medals they just wanted you to play tennis because of your \textbf{race} it attracts more people to watch and to join in to what they don't understand that's the truth🤔😊🖒\normalsize   & \cellcolor{green!5}Black, Race, Racist, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}8/338 & \cellcolor{green!5}2.367 \\  \hline
  \cellcolor{green!27}\small She is so damn agressive and she gets away with it because she is a \textbf{woman}. If you don't agree with her you are sexist and \textbf{racist} wtf?\normalsize   & \cellcolor{green!27}Racist, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I respect \textbf{woman} but in this case keeping things short .. it's Serena who is to be blamed for her actions and absolutely there is point of \textbf{sexism} at all .. Carlos Ramos did well 👏\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small She would have lost the match anyways , she is \textbf{old} .\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Victim of \textbf{sexism} is carlos ramos\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Way to ruin a young fans dream!!!  Naomi always wanted to play against Serena and Serena ruined the young womans moment with her own selfish ranting and cheating. Serena not a \textbf{woman} anyways, she a freaken man!!! Even her shitty eyebrows and facial bone structure shows us that. Men have big eyebrow ridges and sloping skulls. Which as you can see Serena has along with a male body. You can see the difference in the skull structure as the two players stand side by side. Hell her forehead slopes back just like the guy's narrating in this video and her eyebrows are as thick as his too. Only a man can put so much force into the way she threw her racket down and bent it up like that. The older she gets the more manly she becomes. The harmone she has been taking only works best when young. You can't fight nature. Wake up people Serena and her sister are men!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/162 & \cellcolor{green!27}0.617 \\  \hline
  \cellcolor{green!5}\small Williams claims \textbf{sexism}, but she gets a higher salary than Men.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Really people...some of you melting butterflies, actually truly believe that this tennis player was hard done by.This \textbf{gender} b.s...is becoming very devisive  and toxic!!!The tennis player was out of line...and a Prima Donna!!!Learn something women...accept the decision and more importantly...keep your angry mouth closed!!!Also just to fuel the fire some more with you liberal idealists...the tennis player mentioned was born a MALE!!!\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Serena \textbf{feminazi} sore loser\normalsize   & \cellcolor{green!5}Feminazi & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Serena, you are unattractive both outside and inside. Do you inject testosterone steroids like female bodybuilders\textbf{Sexism}, but what \textbf{sex}??? Is he/she, just like Michael (The Frontal Bulge) Obama...\normalsize   & \cellcolor{green!27}Sex, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small If Serena wants equality with men in tennis she should give back two-fifths of all her prize money. After all, women only play over 3 sets, men play over 5. Therefore, men should earn 2/3 more than women. It's not a \textbf{gender} pay gap- it's simple maths.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small How it's a \textbf{sexism} that is a man\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Sexism,what a loud a crap,she just carried on abusing the umpire,look what happened to John mcenroe when carried on back in the 80's at Australian Open he was kicked out of the open.the talk about womens rights,well she was using that to dig herself out of a hole,if it was a regular round she should have been kicked out but being American at in the us open final they were very lenient\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small Serena lost the match because of \textbf{sexism}!  As Americans we all need to stand behind this \textbf{woman} and support her!!\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small A better question is, why is this question even being asked? \textbf{Sexism} is not even possible because her opponent is female...\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She is \textbf{old}. The young will always have their turn. \textbf{Nothing} is forever-it is a cycle. Ask B. J. King.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Sore loser. She's done this before and needs anger management counseling. If her opponent had been white she would have called \textbf{racism} too.PS: Good exposition of the situation. Perhaps missing was the fact that breaking a racket is a code violation that the umpire HAS to call, per the rules. It's not a discretionary call, and Serena knows it.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Just a cry baby, \textbf{nothing} else...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Not American... snobbish assholes that love Serena... has \textbf{nothing} to do with americans… Plus most of the Fruitcakes at these tournaments are Europeans and Foreigners... Most American do not even watch tennis...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small As an American, someone is purposely f!\$king us up. Their tools, i believe, are PC culture, SJW, (fake) \textbf{racism}, feminism and other things. We may be doomed\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I assure you well over 75 of them animals in the crowd were democrat voters..... Go to the next finals and make them show their social media or voter registration and you will have your proof... This behavior is \textbf{nothing} new from democrats in america and across europe and Australia....... democrats in america are unhinged and have these types of videos all across youtube, but 99.999999999999999 of all these triggered unstable democrat videos are hid by MSM... the moment conservative republicans act like animals, MSM puts it all over tv for a month straightYoutube- triggeredthats months of footage of democrat votersYou dont have republicans going to colleges and acting like animalsDemocrats stalked down a \textbf{black} female republican eating lunch and acted like the kkk towards her, they even called \textbf{black} cops every single thing you could think of, MSM buried it, had that been white conservative republicans stalking down a \textbf{black} democrat girl and acting like the kkk to her at lunch, democrats would still be crying \textbf{racist} today and MSM would still be covering it.... Democrats just did the same thing with tucker as well, they went to his house at midnight and acted like the kkk..... Had conservative republicans did that, it would still be all over main stream "news"...... but democrats are animals, losers and the most backwards creatures on earth, "double standard" was 5-10 years ago, now democrats and MSM are far worse than that...Bottom lineserena is a full blown \textbf{snowflake} democrat and her fans showed their colors......\normalsize   & \cellcolor{green!5}Black, Nothing, Racist, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/258 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small As an american i thought that was beyond shameful to see Miss Osaka get Booed like that,she had done \textbf{nothing} wrong to begin with.America could learn a lot about being respectful from Japan.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small "Serena Williams: Victim of \textbf{Sexism} or Sore Loser?"How about just 'obnoxious entitled brat'?I think that should cover it.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{fat} cow was spotted getting COACHED....simple....the rest was her grasping at straw....patheticly blaming anyone and anything she could....her poor "daughter" now has to live this down.....shame!!.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small *\textbf{woman}WOMEN means MORE THAN ONE \textbf{WOMAN}Courtesy of your friendly neighbourhood grammar Nazi\normalsize   & \cellcolor{green!5}Nazi, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Just a giant pile of \textbf{tranny} sht . with lib tears rolling down the sides.\normalsize   & \cellcolor{green!27}Tranny & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small That Tennis Champ has turned Most of Us into Chumps................That "Champ" is a MAN and by claiming \textbf{Sexism} has Proven the Fact.TRUTH is NOT FAKE!The Williams Brothers are a Modern Day Scam, Based on the Professional Tennis Rules. Ever Since the \textbf{Tranny} Renee Richards Escapades, professional women in tennis have been robbed.....................Stolen!The Williams Brothers NEED TO BE EXPOSED by TRUTH and HONESTY!\normalsize   & \cellcolor{green!5}Sexism, Tranny & \cellcolor{green!5}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small repost1. She ended her shift \& returned to the CORRECT police department 2. She clocked out using the CORRECT time clock 3. She retrieved her CORRECT belongings from the CORRECT locker4. She went to the CORRECT parking lot \& retrieved her CORRECT car using the CORRECT set of keys 5. She then drove .2 miles on the CORRECT side of the street using CORRECT hand \& eye coordination \& observing all CORRECT traffic laws 6. She turns her car into the CORRECT apt building............ Wait For It....NEXT IS WHERE THEY WANT US TO BELIEVE AN ACUTE ONSET OF BLINDNESS \& AMMESIA TOOK PLACE 7. She is now CONFUSED \& parks on the WRONG garage floor on the WRONG side of the building 8.She gets out of the CORRECT car \& locks the doors with the CORRECT keys \& takes her CORRECT personal belongings. 9. She takes the stairs \&/or elevator to the WRONG FLOOR 10. With her eyes open (The same ones used in the preceeding events \& she used all day) She walks to the WRONG apt door 11. At this door is a \textbf{R\textbf{ED}} DOORMAT that she has never seen before \& located on the side of the door is where the apt number can be visualized( Sorry I forgot she went \textbf{blind}) 12. According to different reports she either A. Bangs \& yells on the WRONG door because her CORRECT keys won't open the WRONG door \& Mr. Botham answers the door \& is shot.   B. Stated WRONG door was UNLOCKED \& she enters the WRONG dark apt and SUDDENLY REGAINS HER SIGHT \& sees an unknown male \& fires her police issued weapon at suspect striking him in the chest 13. At this point she turns on the light \& realizes she is in the WRONG APT \& shot the WRONG PERSON 14. She regains her vision \& calls 911 (It has not been reported that she began CPR on Mr. Bonham) 15. EMS \& police arrive in 4 minutes and per a video taken by a tenant \& posted on social media said officer can be seen pacing hallways \& talking on phone (family? lawyer?) 16. EMS is seen providing CPR to Mr. Bonham who is subsequently taken to \& pronounced dead at a local Dallas Hospital 17. Officer sleeps in a comfortable bed \& remains free without charges for 3 days because this has been described to the public as " A VERY SPECIAL CASE" 18. Mr. Bontham is placed on a cold slab in the coroner's morgue as his family flys thousands of miles from St. Lucia to identify their beloved son \& brother's body 19. 72 hrs later officer is charged with manslaughter in the death of Mr. Bonham \& posts 10 of the \$300K bail is back home with her family 20. Mr. Bonham's family prepares to bury him on Thursday. * Now Let That All Sink In*\normalsize   & \cellcolor{green!27}Blind, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/489 & \cellcolor{green!27}0.613 \\  \hline
  \cellcolor{green!5}\small I think it was a lil of both. Sore loser and \textbf{sexism}. She's dominated and won for so long....I'm sure it's difficult to except losing. Show me a great athlete who is cool with losing.😳 And as for \textbf{sexism}.... she definitely has a point. Men and women are definitely treated differently in sports.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small It was both \textbf{sexism} and her being a bad loser. She was sexist towards officials because she is a bad loser.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small She was talking about \textbf{sexism} while her opponent was a girl that doesn't make any sense she was being delusional....\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Sexism she was playing a \textbf{black} women\normalsize   & \cellcolor{green!27}Black, Sexism & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small He's not a \textbf{Woman} though...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small So if your \textbf{transgender} like Serina Williams, pretending your a \textbf{woman} in a real \textbf{woman}'s league with real \textbf{woman} and you claim \textbf{sexism}.... typical Neo Liberal \textbf{mental} WACKJOB. Mike Tyson in a bad weave.\normalsize   & \cellcolor{green!27}Mental, Sexism, Transgender, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!27}5/34 & \cellcolor{green!27}14.706 \\  \hline
  \cellcolor{green!5}\small This brings Feminism in such a bad light happy haha :-). That im happy \& content Serena Williams went \textbf{crazy}... phantastic \& delicious hahaha!! thumbs upIt was about time that Feminism gets a blow because its cancer for the world worldwide how it is practiced now (3rd wave Feminism).Horrible for Osaka. What a gd \textbf{black} female narcissist filled with hatred her opponent was...\normalsize   & \cellcolor{green!5}Black, Crazy & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small sexism or sore loser?..... neither. just another self-entitled whining twat of a person from what i see.osaka wiped the court with her. congrats to naomi. great job carlos!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small After \textbf{racism}.. \textbf{sexism}.. osaka was a man?\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small The smashing your racket rules is so \textbf{dumb}. I play tennis and it's so hard not to get angry.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Ericka Hayden I agree.if the player brakes their racket and \textbf{nobody} got hurt why give a violation?\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Aaron Sun But as the rule said, both parties had to be communicating. It was wrong to judge this instance as coaching. Therefore she was justified to criticize the umpire.Im neutral on whether this is a case of \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@HeyIt'sMe XoXo Serena had her points taken away because she acted like a salty 10 year old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Chunky \textbf{Monkey} yeah naomi got 6-2 in the first set. naomi is definitely a great player\normalsize   & \cellcolor{green!27}Monkey & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Serena is an absolute top tennis player BUT why the attitude? 4:52 The people in the rows behind the poor \textbf{woman} all heard clearly what she had said.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small She lost all my respect after this match. She showed her true colors n all I can conclude is that she's an offensive, disrespectful, aggressive , irresponsible ,big sore loser with \textbf{zero} sportsmanship who considers herself a self-righteous queen and knows how to play the victim taking the spotlight away from the people who truly deserve it. In all, she's a bitch\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small You had respect for her before this? She has had the typical \textbf{black} attitude from the start. Guess what, I don't care if you call me \textbf{racist}. It is the truth. She can't control herself to begin with and the she uses her \textbf{race} to get out of trouble. It didn't work this time, so she played the other card. Sexist!  12 of the US is responsible for 50 of all murder and violent crime(one city alone they kill over 1k people a year. To make clear just how bad that is, every mass shooter in the history of our country has killed about that many people.  12 in once city in one year match every mass shooter EVER. Zimbabwe started killing pasty farmers in 2000. Well, they were tortured to death and their wives and children were raped to death.  Now the people of Zimbabwe are starving and want the people they tortured and killed back. The same thing has just started in South Africa, Female genital mutilation, gang rape of babies, genocide, fistula epidemic, albino children are hunted killed and eaten for their magical powers. There is no such thing as an 12 first world country. It does not exist. What is worse my words stating facts or the things I just typed.\normalsize   & \cellcolor{green!5}Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/215 & \cellcolor{green!5}1.395 \\  \hline
  \cellcolor{green!27}\small Theo Dunsmuir John Tate last statement is the truth,however what does Serena actions have to do with the entire \textbf{race}.Serena represents herself not AA or BW.White guilt libtards who agree with SW and support her,they don't speak for you\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small John Tate actually it's more like  6 of AA that commit more than  50 of the violent crime . Because women commit very little violent crime. I know majority of WA are sick and tried of the \textbf{race} baiting AA and now the \textbf{gender} card,however it not just the \textbf{Black} supremacist.the culprit is also The White guilt \textbf{libtard} When white people stuck together before the Obama era the country was Great ,Now diversity and among other things will destroy it\normalsize   & \cellcolor{green!5}Black, Gender, Libtard, Race & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/80 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Theo Dunsmuir shut it you \textbf{racist}.♎️figure it out\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Blast Animation \textbf{Nation} - The same reason why you responded.  Because it is good to tell people the truth.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small J M and she is a he. \textbf{gender} testing is jot required in pro tennis. look at his navel versus waist indention. he has a male pelvis. this is not a result of muscularture. his navel is above the waist indent - only found in men. if \textbf{sexism} and cheating are involved, the navel knows where fault really lies.\normalsize   & \cellcolor{green!27}Gender, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small He's a tranny\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Ted its not the right place. The best marker for political radicalism is if people start talking about THEIR topic in every situation, regardless how little it fits to the topic. At least here its a bit about \textbf{black}, but all those things after the first two or three sentences are useless\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small \@John Tate typical \textbf{black} attitude typical \textbf{black} attitude TYPICAL \textbf{BLACK} ATTITUDE\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small You using serenas moment as an excuse to show yo \textbf{racism}. What a hypocrite\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small John Tate what is a typical \textbf{black} attitude\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Kevin number 3 sounds \textbf{racist} but it's true I've had \textbf{black} freinds who play the \textbf{race} card all the time I mean not all pull out the \textbf{race} card however the news makes it sound like all \textbf{black} pull the \textbf{race} card.\normalsize   & \cellcolor{green!27}Black, Race, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}6/42 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@tuned colours  the news hides never ending \textbf{black} on white crime, the news hides 100000000 cases of \textbf{black} crying \textbf{racist} for every 1 case they report.....\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/26 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small \@John Tate Well I do agree that the \textbf{black} do have their own problems however you can't judge all members of that \textbf{race} based on that\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Hmmm... In a match where both people are \textbf{black} and female, how could the umpire be \textbf{racist} or sexist? Wouldn't he be helping a \textbf{black} female by targeting the other one? Thankfully Naomi was a \textbf{black} female otherwise many would think Serena's argument stands ground. Even now some people believe this nonsense, unfathomable! Imagine if she played against a white man, the umpire would have been fired by now. This shows the hypocrisy of people who see world through their own lenses and isolate themselves from reality. Want to tell me Fabio Fognini was discriminated against because he was secretly a \textbf{black} female? Mouratoglou himself, Serena's coach admitted he was coaching her. She is a disgrace, Serena should be punished and Naomi compensated from being robbed of her victory.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}5/129 & \cellcolor{green!5}3.876 \\  \hline
  \cellcolor{green!27}\small No \textbf{sexism} whatsoever. Take your social justice where it's necessary (nowhere really) and take responsibility over your own acts.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Not everybody falls for this liberal, bullshit, crybaby, \textbf{snowflake} behavior. Good job referee for following rules\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small yes u  winning the ugly award, um \textbf{weird} dude\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small This is despicable that is not a \textbf{woman} that is a man both Serena and Venus are men DNA check it out  Look at that Deceiving piece of garbage 23 grand slams in the female category when she's a man this is despicable I'm sick of it the lives\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small So, weren't the players both women? How then, can it be \textbf{sexism}? Serena should know how to accept good AND bad calls. I think she needs to take a breath.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small SW defending arguments make no sense and are basically pathetic - Ramos followed the rule book correctly.  Until the WTA starts to check the physiology of their players I remain convinced there are many transexuals playing in the women's game.  As for \textbf{sexism} in sport - of course it exists and it exists everywhere and in every sport that men and women play; until men and women line up on the same start line or take part in the same tournament there will be \textbf{sexism} - obviously in about 99.00 of all sports it would mean women would win \textbf{nothing} or even get close to winning anything (actually in terms of Tennis Grand Slams - there would be no women players taking part as no \textbf{woman} would ever get into the top 128).  So please SW bought this topic up.\normalsize   & \cellcolor{green!5}Nothing, Sexism, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}4/140 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small She couldn't pull the \textbf{black} card because her opponent was half \textbf{black} so she pulled the \textbf{woman} card. But then again, their both women so I don't know how that works.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small How is is sexiest if her opponent was another \textbf{woman}?????\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small It was obviously \textbf{sexism}!! Not only to Serena, but all the player that Ramos penalize!! So basically, Ramos is playerism!! Abuse to player!! Owh wait, only to the rude player right? Ramos is rudism!! He abusive to rude players!! Yeah to Serena. Hoorahh!! Owh, and Ramos is also a cheatism!! Hoorahh\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small "I´m A \textbf{Woman}"..........Barely\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small We always had kid in gang thrown a tantrum when that kid start to loose.First she was clearly in lossing side of match, still had to take it back. 2nd her coach himself admitted of signals, which is clear violation of rules.And 3rd she accuse to umpire to to giving penalty for those rule violation. Top of all this, she made matter to worst by making this case \textbf{sexual} accuse. I really feel sorry both Niomi where she didn't get what she deserves and Umpire got booed by croude for doing his job. For all this, she was and is great player. But sore looser, with this and \textbf{old} time example it's proved.\normalsize   & \cellcolor{green!27}Old, Sexual & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/115 & \cellcolor{green!27}1.739 \\  \hline
  \cellcolor{green!5}\small As a singles player myself, Serena playing this 'sexist' card is completely incorrect. It's hard for people who do not play tennis to understand the rhetoric used, but umpires frequently do call coaching penalties, regardless of the \textbf{sex}. Either way, Serena would still lose. I'm not a Serena hater for everyone who thinks first about hating on this comment, I'm just trying to debunk this bullshit rhetoric that is flying around from people who don't even play the sport.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small She makes remarks like a crazed \textbf{drug addict}. THEN, erases all dignity by trying to dial it back using every "Card" in the book she can (Gee I wonder who coached her this time...)\normalsize   & \cellcolor{green!27}Drug addict & \cellcolor{green!27}Behavioural Addiction - Drugs & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Victim of \textbf{racism} not \textbf{sexism}.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Serena has sadly messed up in a big way, whatever respect i had for her is now gone!  Who does she think she is? Disrespecting and making false statements, Ohhhh NOOooo its because of \textbf{sexism}!!! She should of played the \textbf{race} card while she  was at it to. She made herself look like An entitled \textbf{brat} to all the world.\normalsize   & \cellcolor{green!27}Brat, Race, Sexism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}3/60 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small SORE LOSER \& a poor example for women, mothers and \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Serena has had a pattern of yelling,cursing and getting mad at lines people,umpires,the chair umpire in this latest fiasco and this goes back a long ways, I looked up all the times she DIDN'T get fined for outbursts and its a lot.The one \textbf{common} denominator in all this is that she has done this type of thing when she was losing. She feels entitled to it because she is Serena Williams. Just look at the ads before and during the entirety of the U.S.Open...it went something like this...Don't call it a comeback because I've been here before and no matter how much she wanted it and how much the sponsors thought that she was a shoe-in to win, she lost plain and simple. How does one make a big fuss hoping to change the outcome of the match and go so far as to slander and ridicule a very good chair umpire.The fine should have been much,much bigger.Let's see how much she is booed at the Australian Open in January.People pay huge money for these seats and don't need such childish outbursts. No \textbf{sexism} here,she was just plain wrong here.\normalsize   & \cellcolor{green!27}Common, Sexism & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/190 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small If a footballer spoke to a referee like that.....\textbf{r\textbf{ed}}. card...off!!!!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I understand you tried your best in keeping this video as unbiased as possible, and you did really well, but you missed a trick! When you mentioned the other male players that have "clashed" with Carlos Ramos, you said they didn't get penalised, but they did. If you read the articles you showed us, they clearly state "The serb got a time warning violation" ; "I say towel out loud and I get a code?" ; " [...] before deciding to dock Nadal a first serve".The point here is that Serena accumulated code violations for multiple infractions. And just like in soccer,  where you can get sent off for a not so severe foul by accumulating \textbf{y\textbf{e\textbf{llow}}} cards after a series of fouls, in tennis you can get bigger consequences like game penalties after accumulating code violations (Serena lost a game after her third code violation). A fourth code violation would see her lose the match by default, just like it happened to John McEnroe at the Australian Open. So it's not a matter of \textbf{sexism}, or \textbf{racism}, or anything. It's a matter of Carlos being very strict with the rules and enforcing them regardless of the player's \textbf{race}, \textbf{sex}, or even status. He's not afraid of penalizing the biggest players like Serena, Rafa or Novak. Great umpire\normalsize   & \cellcolor{green!27}Race, Racism, Sex, Sexism, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - General, Gender - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}7/219 & \cellcolor{green!27}3.196 \\  \hline
  \cellcolor{green!5}\small Did anybody check the weight of the tennis balls? Some people shave some of the \textbf{fuzzy} shit off for an unfair advantage.\normalsize   & \cellcolor{green!5}Fuzzy & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small How can it be \textbf{sexism}? I'm pretty sure Naomi is a \textbf{woman} as well... I'm a fan of her, but this has been somewhat embarrassing to watch.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Sore Loser,  acted like a 5yr \textbf{old} child. May be greatest tennis player in world at present, but is not a Champion!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Patronising fkn \textbf{b*tch}.\normalsize   & \cellcolor{green!27}B*tch & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small You're taking some drug that makes you \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small People often have a soft spot for \textbf{Sexism}, \textbf{racism} cry. And those who cry often gets the initial support of people. But it is a time when people also have to understand that if potential people used these tricks in a well knitted matter just to gain mass support and help themselves then at the same time they can be doing it to create war!!Clearly, Women are ruining their own image as none will support an athlete fighting for \textbf{racism} and \textbf{sexism} as they would have before this incident.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}4/90 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Nothing short of a regime change can solve the problem.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small High tech lynching of a uppity \textbf{black} \textbf{woman}.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small A majority of people here in the US don't not play the victim card, It's a somewhat small- but loud group (Hence all the media attention). The way most young people learn this is through bad parenting, which is becoming more and more \textbf{common}. The other culprit that I can think of is collage minor classes, where young girls learn about regressive feminism- which doesn't even resemble feminism any more.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small but sir reena is not a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I hate to break it to you, Hayosiko, but we've been going backwards for a decent amount of time now. It's no wonder we haven't found any \textbf{alien} life (supposedly) or been visted by another intelligent \textbf{race}, they'd take one look at us and think "yeah, fuck that, not getting involved in this bullshit." or "yeah I checked, no intelligent \textbf{race} found here."\normalsize   & \cellcolor{green!5}Alien, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/63 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small sexist \textbf{racist} Democrat voting KKK loving Back wood herms.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Sexism when both players are female. You lost, get over it.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Hate to say it but Serena was wrong..then she brings up motherhood which had \textbf{nothing} to do with the situation..but she's still the GOAT\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I wonder how long she has been getting hand signals from her coach while playing.. probably her whole career. She seemed very defensive when called out for it and instantly said that she was not a cheater. Yet according to her coach, he admitted to doing it, which means she is a cheater. Then she brings her kid into it, playing that card was low. Her kid has \textbf{nothing} to do with the match, there is no reason to bring it up. Then the \textbf{sexism} accusation and saying that he'll never ref her court again? Now she is just being mean because she doesn't have any basis for that claim, (do you think she knows his history of calls enough to make that claim? Personally I do not.) and to threaten the man's job because of her entitlement that the sport has given her? I don't follow tennis much and this turned me off from following women's tennis, at least while Serena is still playing. The possibility of the 'greatest women's player of all time' being a cheater and sore loser is not a great look.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/186 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small From which perspective u luk like a \textbf{woman} u luk like an untamed beast, \textbf{Woman} tht horrible I havent seen in my dreams.lol\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Sport is no longer a sport when politics get in the way during play. That is where Serena was out of hand. Politics before play is like state doping their players as happened in the \textbf{commie} world in Olympics.\normalsize   & \cellcolor{green!5}Commie & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small every champions have to lose one day, and naomi is the best person serena can lose to. she is half \textbf{black}, non white, \textbf{woman}, and yet she had to act like that. it is such a shameful closure to your long great career serena, your poor self control and class\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Sore looser she will say its becouse she is \textbf{black} .just normal \textbf{black} playing the victim again\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Because \textbf{sexism}? I'm confused, didn't a  \textbf{woman},nonwhite no less, win?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Oh Yeah she's a Victim...a perpetual Victim. That's her mentality. Pull the \textbf{Race} card 1, then the women card, if all else fails throw a tantrum.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I think she forgot her opponent was also a \textbf{woman} ...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Why are all \textbf{black} people victims in this \textbf{snowflake} world that's just sprung up over night. From what I can see on the real news it's completely the other way around.\normalsize   & \cellcolor{green!5}Black, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small She is victim of racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Oh yeah thats it \textbf{racism}, unfortunately that's not it. She has been playing tennis for years now. I don't think that her career longevity backs up \textbf{racism} at this point. Entitlement, victim mentality, poor sportsmanship. Plus people of color cant be \textbf{racist} right? I believe the umpire Carlos Ramos just might be considered a person of color, but not sure. So I disagree that she's a victim of \textbf{racism}.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/69 & \cellcolor{green!5}5.797 \\  \hline
  \cellcolor{green!27}\small What an easy thing to say. Claiming everything is against them and is \textbf{racism} is back privilege.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I can't stand this loser put \textbf{sexism} on the plate. Shame on her. She did that because she didn't have any good excuse for her awful behavior.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Of course it wasn't \textbf{sexism} :D Anyone that thinks that didn't watch the entire thing. She's just a bully, and I'm surprised she didn't get her third penalty when she threatened the Umpire that he would never be at another one of her games. She didn't fight for women, she fought for herself... The game wasn't taken from WOMEN, it was taken from HER, because of HER actions... It's not like another man got the win, if anything she took the victory from her FEMALE opponent, who probably would have gotten it anyway.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small Lol I accidentally replyed to the wrong comment, I meant to reply to one that said "crybaby, sore loser, \textbf{brat}, anything I'm forgetting?"\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small It kind of was \textbf{sexism} though...but it was against that referee.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small k01dsv in her mind, it's \textbf{sexism} because men exist\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Sore Loser 100. Anyone who thinks \textbf{sexism} was at play is an absolute imbecile.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Well, if 1 player in the world got beaten by 20 yrs \textbf{old}, it's hard to swallow.  A good player should shut up and play the best game.    The women final should have 5 sets just like men because the players will conserve their energy for playing not standing around arguing with the umpire.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Hes a man. I'm a \textbf{woman}! Therefore \textbf{Sexism}. 3:25\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small Sore loser, because she is \textbf{black} and a \textbf{woman} so obviously she can blame it on \textbf{sexism}.\normalsize   & \cellcolor{green!5}Black, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small you.lost Serena you.were not fighting for.women you got caught cheating and u.were losing anyway. if as a society we let the \textbf{sexism} bs slide it will be prejudice against POC next, because.this.is all self serving BS\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small The most disgusting Female tennis player I've ever seen. No respect for the game and its laws. If you've got and issue about the umpire take it up with the Confederation after the game, respect your support \textbf{woman} your a \textbf{Racist} and a Sexist.\normalsize   & \cellcolor{green!5}Racist, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small She's a sexist bully, that had roid rage and abused this male victim on Tv. If a male tennis player screamed and became violent towards a \textbf{woman} umpire the \textbf{Libtard},Feminazis of Hollywood  would be accusing him of rape and prison sentence.\normalsize   & \cellcolor{green!27}Libtard, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Gender - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Sore loser absolutely \textbf{nothing} more realisation shes no longer the dominant force in female tennis\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small How can they claim \textbf{sexism}? Women's tennis is equal pay for not equal work! Let's see them play the same as the men! This is stupid!What's the longest women's game ever compared to the men's game?How many women's matches are hard fought in the first set and 6-0 or 6-1 in the second? How often does the loser of the first set actually win the match?So many times they work less are still get paid absurd equal amounts. Just a few thoughts!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small TRANSVESTITE\normalsize   & \cellcolor{green!5}Transvestite & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small THERE ARE VERY FEW PRO ATHLETES THAT ARE REAL 100. OH I WORKED HARD TO BECOME WHAT I AM AND I THINK THAT GIVES ME THE RIGHT TO BE ARROGANT AND DEMANDING.  WE ARE NOT ALL CHOSEN TO BE ON TOP OF THE WORLD. SOME OF US ARE NOT MADE GREAT. WE LIVE LIFE AS IT IS DEALT TO US AND THEY LIVE THEIRS IN THEIR WAY. THE \textbf{OLD} STATEMENT. THERE IS A PURPOSE FOR EVERYTHING UNDER THE SUN.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small CNN: Hope the umpire gets fired!Me: \textbf{Sexism}... Right... Sarcarm\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Playing the \textbf{sexism} card is a mark of a sore loser: If you can't win legit, discredit the opponent (or the umpire, in this case). It's a last ditch low blow, simple as that.But the Twitter fringies comming to the "victim's aid" won't have any influence on the outcome of this one.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small serena: "I'm a \textbf{woman}"hmmm what about your opponent?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small She is getting \textbf{old} and losing her touch of play.....now she will blame her bad play on \textbf{sexism}   RETIRE and be a mom!!!\normalsize   & \cellcolor{green!27}Old, Sexism & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small I felt incredibly sorry for Osaka. Her win was sullied by all the controversy and the audience should be ashamed of themselves for treating a young \textbf{woman} that way. It's a high-pressure environment and it is no wonder that players lose their cool on occasion. Serena would be better off owning it and apologising profusely to Osaka for not being the idol the young \textbf{woman} had dreamed of playing. It was uncomfortable to watch and a very disappointing display of a star losing her cool and making matters much worse than they should have been. It seems to me rules were clearly broken and penalties were correctly applied but it needs to be the same across the board. Being strict with everyone, men and women alike would hopefully improve court conduct all round but at the end of the day, we are all just human beings and when emotions become involved in such a high-pressure situation, it must be so very hard to keep your cool 100 of the time. Rather them than me. :)\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/175 & \cellcolor{green!5}1.143 \\  \hline
  \cellcolor{green!27}\small Only biased WS agreeing to this atrocity against \textbf{BLack} people.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small America is a shithole country. they don't even have a pure American today. pure american are the \textbf{r\textbf{ed}} \textbf{indian} people who are seen in cowboy movies. this is what happen when impure American wants to represent America. look at her. she isn't American.\normalsize   & \cellcolor{green!5}Indian, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small Sore loser !! She's taken the true winners enjoyment away by doing this bullshit !! I was  waiting for her to say your only doing this because I'm a \textbf{black} women !!  Dont jump on ya high horses ,not being a \textbf{racist} at all ,just being real !!\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "i ve seen men call them worse, so im here to fight for eaquality, i fight so i can call him worse", thats basicaly it, she was fighting againt another \textbf{woman}, if he didnt punish serena's code violations, it would be discriminatory againt her opponent\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small If it was anyone else they wouldn't have the media side with her, she has more privilege than any other \textbf{woman}... like ever. Then she plays the victim card in a \textbf{woman}'s match about him being sexist?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small She was losing and going lose. She had to blame someone or something. Being a mother doesn't make you a saint. \textbf{SEXISM}??? Gimme a break. You lost accept it. Maybe it had something to do with the ADS she was doing. She expected to win to boost the coverage.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small It is interesting to me how mad "she" got when accused of cheating, given that I believe "she" is a \textbf{transgender}.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small And another thing, hasn't everyone noticed how \textbf{FAT} her arse has got lately?\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small easy she is victim of \textbf{sexism} the coach is a real ******** she is not a sore loser she loves to play this game and play BY THE RULES two mins later 5 year olds gonna attack me\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small The real question is the double standard. \textbf{Nobody} is perfect, I was against Serena but I changed my mind when I learned that some others players were involved in similar abusive languages and that some were worse with the very Ramos and they were never penalized. This is the issue when it comes to \textbf{sexism} or \textbf{racism}. They capitalize  when you make a small mistake and  and they escalate the issue while others would do the same thing and they would say they didn't see anything. The issue here is the double standard and you need to be a victim to understand that trap.\normalsize   & \cellcolor{green!5}Nobody, Racism, Sexism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!5}3/104 & \cellcolor{green!5}2.885 \\  \hline
  \cellcolor{green!27}\small But it was not born a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I would never support you , Serena did \textbf{nothing} wrong bt. defend her rights\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I am an 81-year \textbf{old} granny and trust me, I have seen my share of tantrums!  However, I have NEVER seen anything comparable to the display that Williams put on at the U. S. Open!  I wonder if she has looked at the film of her yet!  If so,  she should be humiliated!  Somehow I do not see this display for what it is worth!  Because she so arrogant, she will, no doubt, think she lost the matches because off \textbf{sexism}.  It truly is time for Williams to hang up the racket!\normalsize   & \cellcolor{green!27}Old, Sexism & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/92 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Agreed, as an \textbf{African} American, I find this appalling\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small you r not an 81 year \textbf{old} granny.....im sure ure a punk grinning behind that comment now hahahahahaa. i agree about williams though.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Keyon J  It's cool that you agree and all, but why does it matter that you're \textbf{African} American? The whole issue wasn't even about \textbf{race}, it was about "\textbf{sexism}" which isn't even true according to the way she handled the situation. Even if this was about \textbf{race}, it shouldn't matter, saying you're \textbf{African} American doesn't give your opinion any more validity than someone saying they are caucasian or even left-handed for that matter.\normalsize   & \cellcolor{green!5}African, Race, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}5/73 & \cellcolor{green!5}6.849 \\  \hline
  \cellcolor{green!27}\small Mike Shark well I know that, but in this case he is already disagreeing with her so there is no need to include grouping/siding in this. I feel only if someone was commenting strictly about her \textbf{race} and how they agree with her based on that fact, then it would be necessary.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Andy roddick is gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small It's about her \textbf{Race} the attitude is Typical of it.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small sore loser, are we forgetting Serena did this before and cried racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Sore looser!!! And angry \textbf{black} womman\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Sexism? He's a man.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Its not \textbf{sexism}. She is not sore looser. She cheated and was caught. She is stupid. As simple as that.If she was smart, no one would know she cheated....\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Well America babies the \textbf{negro} to keep them under control but the \textbf{negro} will always come out\normalsize   & \cellcolor{green!5}Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small conclusion  ? it was no country for \textbf{old} men ,now its no country for \textbf{old} women lmfao\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small She fight for rights for \textbf{black} men but married to a white man. Claims \textbf{sexism} but playing against female player. Lol\normalsize   & \cellcolor{green!5}Black, Sexism & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small She didn't claim \textbf{sexism} for playing a female player\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She's definitely a sore loser. From what I could tell she played the mother card, the \textbf{race} card, the victim card, I'm popular \& likeable more than you card, and the \textbf{gender} card. She was completely insane and guilty obviously.\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Wow full respect to this guy as the news reporter. I was thinking as soon as he mentioned the \textbf{sexism} "oh here we go, another man denying there is ever \textbf{sexism} in the world, in sports, ever!!!" But no!!! He really gave a fantastic, fair dissection of the whole thing breaking down every part with a lot of respect and precision. I agree wholeheartedly when everything he was saying. Yes there IS \textbf{sexism} - and men have to stop getting defensive as a whole and deny there ever is - and yes serena did push just too many buttons. It was a fantastic analasys with a cool level head with logic and humanity in it. Rather than some who have an agenda, hating and spredding propaganda through this issue. A million thumbs up!!!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/133 & \cellcolor{green!27}2.256 \\  \hline
  \cellcolor{green!5}\small she's getting picked on because she's \textbf{black} and \textbf{woman}.  That's it.  All you white mofos should just STFU, because you'll never be anything close to her.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small These creatures who are the banners of \textbf{gender} equality and feminazism does certainly have an audience in USofA.Shameful behavior of Audience!\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Sore Loser...\textbf{Sexism}...lol\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small She's had a history with that particular umpire to begin with, so she should have known better. Pulling the \textbf{sexism} card is embarrassing for her.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Sexism in a woman's match?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Sexism? Sore loser? Why not both?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small her opponent was a \textbf{woman}. but lets be honest, Serena isnt that far off being either...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I was most disappointed by her post game conference. During the game I can understand emotions run high and u say stupid stuff in the moment. But after when it is over and you had a bit of time to calm down and process you say stuff like I am out here fighting for women's rights? I'm sorry, weren't you playing a tennis match against another \textbf{woman}? Exactly what rights are you fighting for? Women's rights to break the rules?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small Calling Serena a \textbf{woman} seems pretty misgendering to me. \textbf{Common}, she has probably the same amount of testosterone in her body as Arnold Schwarzenegger\normalsize   & \cellcolor{green!5}Common, Woman & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Let's compromise \& say the umpire was sexist \& \textbf{racist} since he's not the same \textbf{sex} or \textbf{race} as her. Similarly, Serena was sexist for using abusive language against an umpire who's not the same \textbf{sex} as her \& \textbf{racist} for sort of stealing the joy of winning from Osaka Naomi as the first Japanese citizen to win that she had to apologies for beating her.\normalsize   & \cellcolor{green!27}Race, Racist, Sex & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}5/66 & \cellcolor{green!27}7.576 \\  \hline
  \cellcolor{green!5}\small That's one ugly dude. Men should not be allowed to play a \textbf{woman}'s sport, even if they do wear a dress and call themself a man. There are 2 sexes. Man and \textbf{woman}. You are what you are born, FOREVER!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small She isn't there fighting for \textbf{woman} rights and equality.She there to play tennis for money.She"s a sore loser\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small It's not faaaiiirr.... Because i'm huge \textbf{black} man (i mean \textbf{woman}).\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Sore loser, spoiled \textbf{brat}, selfish...they all apply to the way Serena behaved.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Jason T she needs to stop taking steroids may be her giant head will shrink back down a bit. Look at her \textbf{old} pictures  her current has doubled in size.you know she always gets out of drug test somehow\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Thank you for being normal in this time and age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Serena is like the Wicked \textbf{Witch}.  She doesn't have the power to pick who the umpire will be.  If anything, I think they should give her the same guy on purpose.  You don't just abuse the umpire and rub their face in it.\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@scribe712 you just proved your own point wrong that she isn't the game though. There are plenty of other players in tennis, she is just a female \textbf{colored} player is what you are saying. She has no control over her emotions and acted like an impulsive animal. And like every other person that acts this way, she then victimizes herself when appropriate actions are taken against her. Every umpire csn make a call they see fit so if one takes less shit than another, it's probably not wise to start screeching at him. She is just another failed sports career in the making brought down by her own victimization and inability to act like a decent human being.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small Her mouth, ego and ass are ALL bigger than the game. But do not forget, \textbf{black} lies matter!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small How can she be a victim of \textbf{sexism}? she was playing Osaka (a women)... If the umpire was sexist they'd still be on a level playing field.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I can't believe this person is even a roll model to anyone after witnessing her behavior it was obvious she's a silly spoiled brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Why does \textbf{sexism} still exist?and \textbf{racism}?....And don't use \textbf{sexism} as an excuse Lady and Gent.,,But I never see a Guy use \textbf{sexism} as an excuse or defense..I wonder what will happen...For the record I never see I don't know if other's see the male use it...(damn this is why I hate society someone will judge this,Im pretty sure,someone will find an excuse to Trash this comment..)\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}4/66 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Sexism or sore loser ??  BOTH\textbf{Sexism} because she acted like John McEnroe who was never penalized.Sore Loser because she acted like John McEnroe\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small I think your title is misleading, it isn't either or - I think it is sexist but I also think she acted like a sore loser! No worse than the men folk having a fit on the court tho and that's where the \textbf{sexism} comes in....It's BOTH, not either or!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small " because I'm a \textbf{woman}" are you kidding me. The person she's playing is also a \textbf{woman}. Maybe it's the testosterone she takes talking.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "because I am a \textbf{woman}!" - plays against another \textbf{woman}. This world...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Two points. First, it's far from certain Serena is even female (since there's compelling evidence which suggests she was born a male -- and has therefore been "cheating" her entire professional career). Second, assuming for the sake of argument that this extremely masculine-looking "\textbf{woman}" was not born a male, the fact remains she deserved to be penalized for the ridiculous tantrum "she" thew, because it was not a brief, one-time, heat-of-the-moment outburst, but rather something she kept on doing.  When a spoiled rotten \textbf{brat} doesn't get her precious little way, what does that \textbf{brat} do? Throw a hissy fit until she does get her way. That infantile tactic might work in your private bubble life, Serena, but not in the outside world. Welcome to reality.\normalsize   & \cellcolor{green!5}Brat, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/125 & \cellcolor{green!5}2.4 \\  \hline
  \cellcolor{green!27}\small come on, that is ridiculous, she just had a baby. YOu cannot create a \textbf{woman} out of a man. Why not just stick to the obvious facts. She should apologise, and the pseudoliberals should apologise, but they won't. Don't taint this obvious argument by insulting her body etc. It detracts from the truth and just gives more ammunition to the pseudoliberal PC twits\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Manipulative cry baby, sore loser, \textbf{brat}.... am I forgetting anything else lol?\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Hurricane Hipster the world would be better if serena hadnt acted like a salty 5 year \textbf{old} who acts like she lost a game of fortnite. Plus ffs, she even made osaka apologise to the crowd for having this way. Then serena trying to justify her penalizers as if they werent anything, breaking her racquet, and then straight complaining to the umpire for over 10 minutes, verbally harrassing opponents and umpires just because she didnt have it her way... ya superstar for sure (not), she cries more than a person mourning over death...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small \@Hyper Hurricane the issue is, yes those things are all nice and good hearted but it's literally expected of millionaires to do this. Sports players, musicians, actors, hell even youtubers do it now. All of these careers are inflated with money and make way more than they ever deserve for what they do. Yes they can all be stressful jobs but do they make the world go round? No. If each of those careers died off the world would keep going. They get paid shit tons to do what is known as a hobby. So it kind of dims down these "amazing things they do" when they can literally wipe their ass with money because "I hit ball good" or "I catch ball good". Not saying what they do isn't amazing at times. It's just a cash cow product and they really serve no importance. So yeah it's kinda expected of them to do these things since the normal people with normal jobs can't throw that much money around. It is funny you throw \textbf{race} into it though as slowly but surely all through the "white male privilege" you all like to screech about, being a white male is becoming shitier to be as literally anything you don't agree with or do can be labeled as \textbf{sexism}/\textbf{racism}/any kind of ism the victimized can come up with. Their opinions are thought of as null and void on any topics even if it is to further the ending of such issues. And while there are many forms of \textbf{racism} and \textbf{sexism}, women and \textbf{colored} people are becoming just as if not more guilty of it now. They just like to create their own rule called the "I'm not white or male so i can't be it" rule. Hate to break it to you but through all this commotion about \textbf{racism} and \textbf{sexism}, there's been a lot more \textbf{racism} and \textbf{sexism} coming from the females and \textbf{colored} lately which is sad since they should be helping to end it.\normalsize   & \cellcolor{green!5}Colored, Race, Racism, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}9/336 & \cellcolor{green!5}2.679 \\  \hline
  \cellcolor{green!27}\small \@Hyper Hurricane tbh that was meant to say "\textbf{colored} people" so that's my bad for not revising well enough auto correct probably fucked it up a little on me. Honestly while I do agree I'm starting to believe slowly but surely it's going to creep to the 50-50 mark of what is truthful and what is exploiting in my opinion. It's becoming way too convenient and commonly used to call \textbf{racism} \textbf{sexism} to the point it is hurting the cause for the people it actually matters to because more and more people are starting to have the whole "boy who cried wolf mentality" about it now because the amount of people that abuse these terms are increasing which isn't good.\normalsize   & \cellcolor{green!27}Colored, Racism, Sexism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}3/120 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small I think everyone can agree then that serena abuses the terms \textbf{racism} and \textbf{sexism} to get her way. And yes. She donates money to charity. So i guess in the mind of people who worship her like she's God that makes her entitled.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small \@Hyper Hurricane true and I had a feeling you would say that though it is what it is. I'm not horribly pc like most people are and considering the normal for everyone else is calling us whites or white people I have no issue with the term \textbf{colored} people when referring to people of any color, didn't mean to just say \textbf{colored} earlier though as I feel that sounds like I'm being an ass. But yeah unfortunately that's how people are nowadays. Everyone is a victim and everyone is offended so \textbf{nothing} can be taken seriously now. And that's exactly how the government likes it's people. Emotional and divided\normalsize   & \cellcolor{green!27}Colored, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/109 & \cellcolor{green!27}2.752 \\  \hline
  \cellcolor{green!5}\small \@Hyper Hurricane really? Trying to seem like your just being positive, can't fool me sjw, saying that all americans think she should be sent to hell, talking about how good the world would be without right wings and people. Why are you fighting for this spoilt little \textbf{brat} who can't take a loss.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small you left out liberal \textbf{snowflake} with a victim complex\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Entitled \textbf{brat} whose victim card was declined.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I have no idea why \textbf{sexism} or \textbf{racism} is EVEN BROUGHT UP. Completely irrelevant in the situation. Any knowledgeable tennis fan that knows the rules, providing they aren't a \textbf{blind} deluded Serena fanatic knows the victim is Osaka and Ramos.\normalsize   & \cellcolor{green!27}Blind, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/40 & \cellcolor{green!27}7.5 \\  \hline
  \cellcolor{green!5}\small Chris Chapel, this is the most unbiased, complete,  intelligent, mature and accurate compilation of what happened.  Your report was such a refreshing departure from other reviews of what happened (of which I have read most, if not all)  which have been sketchy, biased (pro Williams)and irresponsible because of their lack of thoroughness of enforcement of the rules vs. \textbf{sexism} question.  I don't understand what mass mesmerization has caused millions of people to adore Serena Williams despite her history of an unconrollable temper, simmering rage and abuse of officials.  I feel so much better knowing that there is someone (you) smart enough and competent enough who has presented both sides of the story and has come out with the truth.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/119 & \cellcolor{green!5}0.84 \\  \hline
  \cellcolor{green!27}\small Her opponent was another \textbf{woman}, therefore it stands to reason that it was not sexist. She's just an entitled \textbf{brat} who got caught cheating and decided that her best course of action was to throw a temper tantrum on the court, in front of millions. She even went so far as to use her child as a weapon. Fukkin shameful.\normalsize   & \cellcolor{green!27}Brat, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I hate when people like Serena play the \textbf{sexism} card... is she forgetting that she's competing against another female athlete?... did the umpire penalise that other female? No... \textbf{nobody} no matter how great or famous is above the rules of tennis.. if you break the rules then you will get punished\normalsize   & \cellcolor{green!5}Nobody, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small She knew the rules inside out, she was losing badly and as usual in that situation, had a tantrum, abused the umpire, then tried every trick in the book for sympathy. No way \textbf{sexism}, it was a bad loser having a tantrum and out of order, woman's rights no way, she should be banned. The umpire was spot on. The fine was a joke, ban her\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Sore loser she should admit she lost to a young player. surprising the did not claim \textbf{racism} too\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Nobody is getting it she knew she was going to lose she wanted to disrupt the game so that she can blame losing on \textbf{sexism} like leftist libtards do like they did when they lost to trump\normalsize   & \cellcolor{green!27}Nobody, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Screw diversity and everything else.  Serena didn't come close to what I grew up watching.  John Mcenroe, Jimmy Connors, Ilie Nastase.  I thought she was within the bounds of normal  superstar meltdown tantrums.  No doubt she had a bad day.  I assume she regrets her loss of control but from my \textbf{old} white man 62 year \textbf{old} perspective, I thought it was rather subdued and respectful compared to what I watched in the 70's and 80's.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Let's make sure there's a \textbf{black}, female umpire anytime Serena plays. That way we'll avoid all this drama next time.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Rich, entitled \textbf{BRAT}!!!!!!\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small That \textbf{black} man getting beat at tennis by a \textbf{woman} is a really angry man...-boohoo, you accused me of cheating...-boohoo, I broke my tennis stick...(yes I know it's a racquet, not a protection racket though)-boohoo I'm not really a man...\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small Well Mr. Smith I say the audience was terrible they all should be ashamed. To rethink it again I say somewhere Serena is a victim too though not of of \textbf{sexism} but this terrible far leftwing-victim culture.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Totally agree, \textbf{sexism} was not clear, but her bad attitude was .Sch a shame when it comes from such a legend.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Serena is right \& as a \textbf{woman}...she accepts no physical abuse.  It's  better to stand against injustice right on your face. So many abuses goes quietly ...Injustices\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small *\textbf{woman}WOMEN means more than one WOMAN\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small SJW Logic: The umpire is \textbf{racist} and sexist because he gave me a warning for cheating in a multimillion dollar match only because I'm a \textbf{black} \textbf{woman}, he never gave any warnings to my opponent though who is a balck \textbf{woman} so thats why he's \textbf{racist} and sexist\normalsize   & \cellcolor{green!5}Black, Racist, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}5/48 & \cellcolor{green!5}10.417 \\  \hline
  \cellcolor{green!27}\small Dispicable woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Unless it is the very same umpire letting men get away with abusing them who punished Serena here then she doesn't have a point and neither does Roddick. That's a bit like a schoolgirl getting away with a particular type of behaviour from one teacher and then being punished for the same thing by a different teacher (who happens to be male) and then claiming \textbf{sexism}.Apart from anything else, there could have been any number of reasons why Roddick got away with it anyway, such as were those umpires more tolerant than this one? Were his tantrums generic and/or about the situation only and not personally abusive to umpires?  Did Roddick make his point at the time and then move on and accepted the situation (even if reluctantly) as opposed to dragging it out over a prolonged confrontation?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/139 & \cellcolor{green!5}0.719 \\  \hline
  \cellcolor{green!27}\small The worse part of this are the N.Y fans that  were booing the chair ump Ramos. And when the trophy presentation some fans were still booing the result as the fans really wanted Serena to win. Then to top it all at the podium Serena pulled out the \textbf{Sexism} card and  the media folks applauded her. ????  Sickening...\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small Tennis is probably the only sport where \textbf{woman} are taken more seriously than men\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small But the other one is a \textbf{woman} too\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small too \textbf{old}.... too slow.... time to go\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small For anyone that thinks that Serena (and hundreds of other athletes from ALL pro sports) isn't a "cheat", read on... Most top athletes are "cheats", it's just that they manage to do it "within the rules". The biggest culprits in tennis would seem to be Serena, Venus and Nadal, though it happens in ALL professional sports. There is a system in pro sport known as TUE (Therapeutic Use Exemption), which allows pro sportsmen/women to have otherwise illegal performance enhancing drugs prescribed to them. What they do is tell their personal doctor that they are ill, the doctor then fills out a TUE form stating the illness and the drugs required to treat it and hands the form to the sporting governing body. The sporting governing body then ok's the use of the drug requested for the time period requested. This is a system that has been abused by most top sports people in almost every pro and Olympic sport for many years. The higher profile athlete you are (and all high profile athletes have their own personal \textbf{doctors} making it even easier because the doctor will back up their claim of being ill) the more likely the governing body will say yes to the use of otherwise illegal performance enhancing drugs. This system has remained secret to the public until a couple of years ago when the WADA database was hacked and hundreds if not thousands of previously confidential TUEs were downloaded and made available for all to see. Journalists got hold of the forms and both Serena and Nadal were interviewed about their prolific and in Serena's case almost constant use of illegal performance enhancing drugs and all both could say was "I have done \textbf{nothing} wrong, everything I've done is within the rules". In Serena's case I personally looked through all her TUEs and cross referenced the drugs she took and the times that she took them and I was astonished to find that they almost always coincided with the major slams. In fact on quite a few occasions she was taking hard-core performance enhancing drugs (officially for a particular ailment) from between 6 and 2 weeks before some of the grand slams dating back to 2009 and when I researched the particular drugs she was using, they didn't have an effect on the athlete until 2 weeks AFTER adminstering ended. In other words, she was reaping the performance enhancing benefits just as the tournament started and throughout it's 2 week duration. This I found to be a recurring feature in her TUE strategy way above any other athlete from any other sport. I'm sorry to burst your bubble (I was devastated and very upset for days when I realised the truth behind ALL pro sport) but these are the hard facts. Let's not forget that we live in a capitalist society where profit comes above all else and the bottom line is that top athletes bring a HUGE amount of money into their given sport and thus the governing bodies constantly allow these TUEs to be granted, especially to the biggest names because they bring in the most money - also the use of drugs (particularly in athletics) means that at various times world records will be broken, which HAS to happen because that generates greater public interest which in turn generates even more revenue. If world records were never broken interest would eventually wane, meaning less profit. As we saw in the Lance Armstrong case, a governing body will protect a top athlete because they bring so much attention (money) into their sport. In Armstrong's case he was protected for years by the UCI until the evidence became so overwhelming that the UCI eventually had to distance themselves from him to protect themselves. As a lifelong sports fan, it breaks my heart knowing this ugly truth but I'm afraid to say that the whole pro sporting arena is a sham and a charade and just another HUGE, GIANT corrupt industry.\normalsize   & \cellcolor{green!27}Nothing, doctors & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/664 & \cellcolor{green!27}0.301 \\  \hline
  \cellcolor{green!5}\small Mr. Serena Williams is so ugly inside and now the world see her real colors.  Mr. Serena, this is the consequence of taking too much hormones shots to change your identify!   We will wait for the day when it will be revealed of your true \textbf{gender} and then we will know.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small How can it be \textbf{sexism}... It's not like she was playing a male opponent\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small he should be her own \textbf{gender} lol...\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Serena Williams behaviour was very poor indeed....\textbf{sexism}?  well?  had the umpire been a \textbf{woman}, I believe the cry would have been \textbf{RACIST}.   SHE HAS TAKEN THE SPORT OF TENNIS TO A NEW LOW.\normalsize   & \cellcolor{green!27}Racist, Sexism, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small There is \textbf{zero} chance she's not on steroids. If you look at how her body has changed is similar to Barry bonds. She is getting older and is now double the size in muscle. Her neck is twice the size it was. Not to mention her outbursts.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small If you bothered to do your homework, you'd know Serena is actually drug tested more than the other female tennis players. You'd also know she has never once tested positive for drugs. You're also obviously White and therefore, used to women who look like \textbf{skinny} flat-assed Barbie dolls. \textbf{Black} women have thicker body types. Something White people never cease to be both fascinated and confused about. Google Sarah Baartman and you'll understand what I mean.\normalsize   & \cellcolor{green!27}Black, Skinny & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!27}2/75 & \cellcolor{green!27}2.667 \\  \hline
  \cellcolor{green!5}\small scribe712 I'm \textbf{black} I play tennis and I don't look like that I have leg muscle but I don't have a wife neck large hands etc it's not about \textbf{racism} bc right now you assumed this person is white and bc of it your are saying this person only likes this or that that's a \textbf{racist} stereotype let a white man say that to a \textbf{black} person grow up dude\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/70 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small jesus the umpire was just doing his job, plus she call \textbf{racism} and \textbf{sexism} EVEN THO the other opponent who was female and part asian.. so she can't really call both those things\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small excellent analysis, victimization, victimization, victimization. victimism, \textbf{sexism}, \textbf{racism} nowadays are words used to justify all the ills of the human being. and put on the other the reasons of their own failures\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Sooooooore loserrrrrr. Ban her. Naomi is such a greater role model, not so that Williams \textbf{woman}. New York crowd is utterly despicable. Thank God the majority of Americans are very different.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Osaka won fair and square no \textbf{sexism} at all\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Other commenters have pointed this out already, but there really is no reason to think this is \textbf{sexism}. Her opponent was female, and part of a minority group to boot. She got a penalty for illegal coaching. The ref did his job.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small John MacEnroe had a match penalty called against him in Australia for less than what Serena did. I'm just glad she didn't play the \textbf{race} card. If the umpire hadn't been Latino (which would have made that accusation luddicrous), she probably would have.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small When did everyone start wearing \textbf{black} in n tennis? It looks like a bad dream\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small What do I think? Americans are \textbf{dumb} as a rock! Booing Osaka was the proof.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small HOW CAN THIS BE \textbf{SEXISM}? SHE IS COMPETING AGAINST A \textbf{WOMAN}. SHE REMINDED ME OF MIKE TYSON. SO ABUSIVE COMING FROM A \textbf{WOMAN}. A SORE LOSER.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small Impossible to say if there was \textbf{sexism}?  IT WAS SERENA WHO WAS SEXIST!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small What's that \textbf{old} saying, you can take a person out of the ghetto, but you can't take the ghetto out of the person. !\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small That's gotta be Mike Tyson in drag.I LOVED the Australian cartoon. Not only is her skin \textbf{black} ,but obviously very \textbf{thin}.\normalsize   & \cellcolor{green!5}Black, Thin & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Lol i m fighting so that \textbf{woman} can abuse the match official\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small It was a \textbf{racist} judge. Good for her not playing that card. Lol no such thing of abuse of white men.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Playing the victim card is \textbf{common} thereby trying to gain sympathy and moving away from the truth\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Serena abused the referee n stole Osakas big day..."\textbf{SEXISM} " is her cover up bcoz she has \textbf{nothing} else to lean on bcoz she wrong ..\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Sore loser...I've seen her lose it before and on a female umpire at that. Where's the \textbf{sexism} there? Nice try Serena but there's a pattern here: when you don't get your way you throw a tantrum.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Not rocket science, yelling \textbf{sexism} is the hottest shit atm, and what else she had to lose?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Obviously what people don't like is the way <BAD> she claimed \textbf{sexism}, as opposed to the claim itself. ( I don't think the ump was out of line )\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small She didnt say she would kill her but im pretty sure if you shove a tennis racquet down someones throat they would die..she claims \textbf{sexism} but her opponent is a \textbf{woman} who's skin is about as \textbf{black} as hers...\normalsize   & \cellcolor{green!5}Black, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/39 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small This crowd sucks,The crowd are biased yanks, Serena acted like a spoilt little \textbf{brat}, she should be taught a lesson in how to act like a proper loser.  Hahaha Serena!!\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small This is the Tiger Woods of women's tennis, she's dealt with a lot over the past years as a \textbf{woman} and as a person of color. Should have kept her from this one\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small What a load of crap trying to defend her reaction by using the \textbf{sexism} card. Serena you are just a bully.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Serena you were wrong, grow up and it wasn't \textbf{sexism}. 🙄\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Don't make excuses for them by bringing up things from 50-60 years ago. It's irrelevant to today, today women unfortunately as they scream equality are treated better than men. They get to ruin lives with lies \& deceitful behaviors. There is no \textbf{sexism} when it's two freaking women because for it to be sexist he'd be doing it for the same \textbf{gender} he's supposedly going against \& frankly \textbf{race} as well. She was a grade A piece of shit.\normalsize   & \cellcolor{green!27}Gender, Race, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/79 & \cellcolor{green!27}3.797 \\  \hline
  \cellcolor{green!5}\small Is not \textbf{sexism} is animal abuse 😂😂😂😂😂😂\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small You know it funny how the Japan acceptance of miss America half \textbf{black} and Japanese was indecisive ! But this tennis victory is a first for Japan so this again, half \textbf{black} and Japanese tennis star victory must also be indecisive as will. Just stating facts\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I don't see this crap in any other sport.  Spoiled \textbf{brat}!  Where is the taken over the knee and spanked punishment?\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Its clearly a coaching and not a thumbs up unless im \textbf{blind}.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Men copped almost 100 violations in grand slams this year. Women less than 30, obviously it's \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small How's it \textbf{sexism} when her opponent was also a \textbf{woman} lol\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Very sore loser. And how can she moan about \textbf{sexism}. She a man for crying out load. When she wins she's acts decent but when she loses she becomes what she really deep down is. Ghetto \textbf{woman} with money\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Serena williams = sore loser. Got caught 'couching', racket abuse and verbal abuse. All against the rules. PLUS, playing the \textbf{sexism} card!? WTF!? Yep, definitely a sore loser. This video says it all, she and some of the women players were not the only ones getting penalties. In fact there were MORE MEN players that had been penalized than women.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small What Serena did, was certainly not great. However, people seem to miss the context. She is competing at a very high athletic standard and when people get argumentative in those circumstances, the body chemistry is not very helpful. When competing, the confrontational behavior seems natural. A veteran of her experience must have handled this better, no doubt, but still, she isn't the worst I have seen when it comes to vulgarity. The length of her argument is by no means a factor. However, her accusation of Carlos was. Hence she had a point taken in a crucial way. Has Carlos did the same in every instance with men, history suggests, no. Hence there is some grey area in the \textbf{sexism} context. However, all credit to Osaka and Serena could have been much more graceful in supporting a young girl.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/139 & \cellcolor{green!5}0.719 \\  \hline
  \cellcolor{green!27}\small Most times Carlos has even with men... known to be a stickler to the rules so the \textbf{sexism} is completely wiped out... there was no \textbf{sexism} at all otherwise Osaka would be affected by it too and she wasnt\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Jesus dude....a ten minute video?  Really?  Anyone with a brain in their skull could see that she was being a sore loser and a spoiled \textbf{brat} because things were not going her way.  \textbf{Sexism}?  Really?  A \textbf{blind} man could see from miles away that was not \textbf{sexism}.  Get out with this garbage.  lol\normalsize   & \cellcolor{green!5}Blind, Brat, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/53 & \cellcolor{green!5}7.547 \\  \hline
  \cellcolor{green!27}\small It was \textbf{sexism}.... against men.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small There's no debate here. It's been proven multiple times that she is a sore loser, and this is a perfect example. Even her coach admitted that she was wrong and that he did cheat. And her nonsense about \textbf{sexism} has also been proven wrong if you look at the umpires track record\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small I still think Serena is a \textbf{weird} name for a man...\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small They talk about \textbf{sexism} in sport as if its a detriment that only exists for women. The way I see it, females have the privilege, and not just in sport. The privilege of playing the \textbf{sexism} card in any situation they want and having the world believe it because ...poor \textbf{woman}, bad man. Were it a man claiming \textbf{sexism} no-one would care and that in itself is sexist.Take Carlos Ramos for example, look at the situation he is in; he was abused, a victim of \textbf{sexism} at the mouth of Serena Williams and no-one gives a damn, I doubt anyone even noticed. The type of \textbf{sexism} that sets out to demonize a man because its a convenient way of getting what you want when things arent going your way.I haven't seen many people as "ugly inside" as Serena Williams proved herself to be. That should have been the best moment of Osakas life, a moment she confessed to have dreamed of for all of it. Serena took that dream away from her and I hope Serenas kids realize who they absolutely should not aspire to be.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}6/188 & \cellcolor{green!5}3.191 \\  \hline
  \cellcolor{green!27}\small How lucky we are that Naomi is \textbf{Black}. Otherwise we would also hear about judge discriminating her because she is \textbf{Black}. Unbelievable!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It is learned behavior she is \textbf{black} also so for example if she got stop by a cop the first thing she would think is not that she did something illegal but rather that \textbf{racist} cop again at work.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Good point - I did not think about it. See oppression in anything that happens to you. Luckily Osaka was \textbf{Black}, otherwise we would hear about \textbf{racism} against Serena because she is black\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small She literally said she saw him giving a thumbs up! How could she have not seen him?! But yeah, \textbf{sexism}...\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small But wait...what does her daughter have to do with her cheating?? And where does the \textbf{sexism} come in a women's match? Her reaction showed excess emotion and showed that she was a sore loser but \textbf{nobody} is perfect. Suck it up snowflakes.\normalsize   & \cellcolor{green!27}Nobody, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Dumbass, she said it was \textbf{sexism}. She bought in the \textbf{sexism} shit\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Sore loser specially when she uses her first baby in her explanation its got \textbf{nothing} to do with \textbf{Sexism} it ain't the first time she has been this way pathetic\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small So now women can get away with murder because it's sexist if the judge condemns them?  Whew, I'm glad I'm a \textbf{woman}!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Yelling "I have a daughter" sounds more like "I'm not a man, I'm a \textbf{woman}"... Strange creature... Is it really a \textbf{woman}?!In any case it played against another \textbf{woman}, not against a man and there is no game going on between it and the referee... So who was the one to get any gain out of this 'sexist discrimination" - actually that is the question... Next stupid thing it says: "I never cheat"... Really??? How about taking the same drugs Sharapova got banned for, for years in a row with the discrete knowledge of the WTA; should Wikileaks not showed us the documents, who would have ever known? This creature actually never won fair and square... Once a cheater, always a cheater!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/123 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Serena's behaviour revealed her emotional immaturity, narcissism, and sense of entitlement. She became a liar when she claimed there was no coaching violation, and she became a thief when she stole the spotlight from Osaka with her childish temper tantrum. She is guilty of the very things she accused Carlos Ramos of, which is typical of narcissists. Allegations of "\textbf{sexism}" are an attempt to cloak a dismally poor character behind a veil of virtue. The veil is \textbf{thin} and full of holes. Serena's behaviour was disgraceful, and young women who want to grow up empowered in pursuit of their dreams would do better by looking up to Osaka than to her. \textbf{Nothing} further needs to be said about this shameful incident.\normalsize   & \cellcolor{green!5}Nothing, Sexism, Thin & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}3/121 & \cellcolor{green!5}2.479 \\  \hline
  \cellcolor{green!27}\small Bad for:1.The sport2.Your \textbf{Gender}3. Your \textbf{Race}4. Your Country5. Your Opponent 6. Your Racquet 7. Your Coach8. Your Bank AccountPeople you Owe an apology1. Naomi2. The Umpire4.Your Coach5. Your fansGet some counseling and own up to losing to someone who was just better on that day.\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small Suppose hypothetically it was sexist and tenis really holds women to other standards than men,  it's still a match between 2 women so it would be fair in the context of that match because she is competing against another \textbf{woman} who is also subjected to this \textbf{sexism}, if the other player would have also talked back to the guy and not get penalized that would be unfair.Anyway many sports have slightly different rules for men and women and they are mainly there because women and men are different... is this sexist, idk ... maybe... but since you compete against people of the same \textbf{gender} it is still fair in that context.\normalsize   & \cellcolor{green!5}Gender, Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/112 & \cellcolor{green!5}2.679 \\  \hline
  \cellcolor{green!27}\small I felt very sorry for Osaka. This was the highlight of her career so far and it was ruined by this spoilt precocious \textbf{brat}. I do think Williams was using gamesmanship too - overreacting causing a massive scene and trying to unnerve and unsettle Osaka. And playing the \textbf{sexism} card is pathetic. You're playing the sport for yourself and your country not for women's lib, get over yourself.\normalsize   & \cellcolor{green!27}Brat, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small if the umpire was a \textbf{woman} it would be a story about someone who's job is to enforce the rules and he mets someone rich famous entitled and perceiving themselves in a position of power. And rules enforcer does not flinch, does not resign from treating everyone equal, even if it may them cost a lot of trouble. And all the liberal comedy show hosts would make comparisons with Trump and Comey.But because Williams is american and played the sexist card, all discussion went to \textbf{sexism} issue.Williams and even more her defenders sabotaged the \textbf{gender} equality issue. They just equipped every sexist asshole with a simple excuse "you libtards see \textbf{sexism} everywhere". She should be called out by honest liberal media, not defended\normalsize   & \cellcolor{green!5}Gender, Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/125 & \cellcolor{green!5}3.2 \\  \hline
  \cellcolor{green!27}\small The US Tennis Association should be mortified by the example their standard bearer has given to young athletes.  Serena acted like an entitled middle school \textbf{brat} getting caught red-handed doing something wrong but is incapable of accepting responsibility for ANYTHING.  She owes the tennis world an apology.  Instead, the USTA board president gave a press release praising Williams' SPORTSMANSHIP?!?!?  WTF!!!!  Because she could chill out long enough to say something nice about her opponent at the award ceremony?!?!  That's not sportsmanship, it's self-preservation and self-aggrandizement by "humbly" putting the crowd in its place for following Willams' earlier porr sportsmanship lead??!?!?  \textbf{CRAZY} TOWN!!! If the USTA cared about the future of the sport instead of not pissing off their favorite athlete, they would have strongly denounced Williams' behavior and suspended her from upcoming tournaments. It's not \textbf{sexism}, it's eliteism, and Williams was a huge beneficiary in this case. Serena, ESAD.\normalsize   & \cellcolor{green!27}Brat, Crazy, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/149 & \cellcolor{green!27}2.013 \\  \hline
  \cellcolor{green!5}\small How lucky we are that Naomi is \textbf{Black}, otherwise we would hear that Serena was discriminated because she is \textbf{Black}. And yes, she went ballistic because she was loosing despite coaching provided to her during the match by her coach.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small +Joe Ninety - Serena certainly did play the feminism card.  She called the ref, sexist and said that she was a \textbf{woman} (Serena ain't no \textbf{woman} from this planet.) and she's playing for her daughter.  And Serena said if "any other man" had said what Serena said it would have been ignored.  That's clearly pushing feminist views.  Unless you are kidding and I'm too tired to realize your humor?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/69 & \cellcolor{green!27}2.899 \\  \hline
  \cellcolor{green!5}\small GunzoModern feminism is no more about \textbf{gender} equality than \textbf{racism} is about racial equalityIf it was truly about \textbf{gender} eqality, why does the national organization for women (the largest feminist group in America) fight to TAKE AWAY the rights of fathers? Taking rights from one group and giving them to another group is SUPREMACY, not equality.TRUE equality is called EGALITARIANISM\normalsize   & \cellcolor{green!5}Gender, Racism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/63 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I do not care what Serena does, because she is such a beautiful person inside and out.  I think she is being singled out for being a combination of being not just a \textbf{woman}, but also a \textbf{woman} who happens to also be \textbf{black}!\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/44 & \cellcolor{green!27}6.818 \\  \hline
  \cellcolor{green!5}\small The umpire is Portuguese. What if she was being \textbf{racist} towards him? \textbf{Black} people are very \textbf{racist} toward me DAILY. I don't see white women raising hell over that, ever. It's because you're selective in your equal ideologies. Which is hypocritical. So screw your opinion, because you aren't truly for equal rights, only for what is popular at the moment. Facts!\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/61 & \cellcolor{green!5}4.918 \\  \hline
  \cellcolor{green!27}\small Hahahahaha! Beautiful outside??? Hahaha!!!!!!! I've never seten a \textbf{woman} like that, EVER! Nastiest, manliest "\textbf{woman}" I've ever seen. Tyson with a weave. I pray for those who fell for the lie that that thing is a "beautiful \textbf{woman}". Total cringe, no one would fuck or could inpregnate that man. BAAAAARRRF!!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/50 & \cellcolor{green!27}6.0 \\  \hline
  \cellcolor{green!5}\small Obvious Liberal mentality, You're not fair to me sniff sniff...(oh wait let me make this about something completely irrelevant)….ok, yea \textbf{sex} that's it. You don't do this to a man, it's because I'm a \textbf{woman}....(Now I have to have a cause for my actions)....OK yea, I'm doing this for women\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Wannabe commentators still talking about Serena? Jesus, there is a lot going on in sports, I'm damn sure if this was Chris Evert or Martina Navratilova, the sports world would have move on. \textbf{Race} people, she's \textbf{black}, I guess entitled white Americans need to be reminded for the next six months what Serena did wrong!\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small Black privilege the only one that exists!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Mark Barton  You have to be kidding, her biggest thing was that she was a \textbf{woman} overall idiot.  Now let's not get started on privileges.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Gender based double standard!  Really, Serena!  Men must win 3 sets to win the same prize money as women, who need only win 2 sets.  What happened to equal pay for equal work?  The men were dropping like flies due to the heat and humidity in conjunction with the three set minimum victory rule for men.  There's the real \textbf{gender}-based double standard but its politically incorrect to discuss that fact.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Ho can Ramos be sexist if the other player was a \textbf{woman} too :D ?\normalsize   & \cellcolor{green!27}Ho, Woman & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small What a disgrace, and even worse was the support she received from the media, celebrities and the crowd, absolutely disgusting and to claim this was a fight for feminism and \textbf{racism} is highly offensive.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Spoiled sore looser... in a game that contributes absolutely \textbf{nothing} to the world.. Next !!!!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Serena is not a "victim" of \textbf{sexism}, as he is not a she. Isn't it "\textbf{sexism}" and good \textbf{old} fashioned bullying for this huge, brutish, powerfully built man to play against women that don't have a chance against his massive strength?\normalsize   & \cellcolor{green!5}Old, Sexism & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}3/41 & \cellcolor{green!5}7.317 \\  \hline
  \cellcolor{green!27}\small She wants equality in tennis?? Isn't there a \textbf{gender} pay-gap - ie: women get paid the same as men but play fewer sets or something?\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Come on! Serena kept on bashing Carlos Ramos, and plays the victim afterwards!, absolutely pathetic!!! she berates the idea of \textbf{sexism}, and reduces it to a mere means to win an argument or get female spectators on her side after a clear bad behavior\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Poor sport along with big \textbf{fat} liar!!!Playing the Sexist  card. seriously!!!! Tuck your balls up and take your punishment like the man you are!\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Naomi Osaka is a dignified and mature young \textbf{woman} who beat the overgrown infant Williams.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Serena Williams is a fake \textbf{woman} she's got the body and strength of a male. She is also infantile and emotionally immature. she should play men.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Sore Loser all the way... get over yourself Serena...using \textbf{Sexism} as a justification for your idiotic behaviour.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small One wonders the reaction if it were a white male player behaving exactly the same towards a \textbf{coloured} female umpire ?\normalsize   & \cellcolor{green!27}coloured & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small How can she have lost because of \textbf{sexism} when her opponent was also female? America uncovered? Stupidity uncoverd. A 9 minute-video about \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Williams could not play the \textbf{race} card because she was playing an Asian \textbf{woman}, so she played the sexist im a mother, she always wants to be the centre of attention even when she is losing, this should have been about that young Japanese lady who is the first tennis player ever to do it for her country, I'm sure that women didn't want to win like this, she kept her composure while haven't to listen to Williams gibberish, once a sore loser always a sore loser shame on you Williams, and if this is the face for women well shame on you's\normalsize   & \cellcolor{green!27}Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/103 & \cellcolor{green!27}1.942 \\  \hline
  \cellcolor{green!5}\small marko Builder  The \textbf{woman} was Haitian and Asian. Not just Asian.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small +Alcia Luv - True but Naomi Osaka is also "\textbf{black}" so Serena couldn't play the \textbf{race} card.  Naomi was a double \textbf{race} so no matter what, Serena could not bitch.  I frankly think that was actually part of why Naomi was winning.  She was young, beautiful and just being her career where Serena is at the end of her/his career.  The green eyed evil monster of jealousy crept under Serena's skin and she/he could not keep her/his composure.  Boo hoo!\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/80 & \cellcolor{green!27}3.75 \\  \hline
  \cellcolor{green!5}\small If thats the case ....i'm sure u can call all \textbf{black} people in America white cuz their all mixed too\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Yall loved her up until she had a human moment.  As a \textbf{black} person Ive seen this so many times to count, if she screwed up forgive her and move on, you did it to Hulk Hogan.  Yea go kill yourselves who pays money to watch good character anyway?  That's why I don't watch sports.  Lastly what I think is you are trying to racially mascot others against blacks, like you do in college over Affirmative Action. Asians are being used to make the case against affirmative action. Again. [LINK]  Osaka didn't have to apologize but she wasn't forced to, it was a Japanese thing to do.  She's not running for office, so if you all here like good character so much why is Trump in the White House?   She did wrong but you all forgave worst.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/137 & \cellcolor{green!27}0.73 \\  \hline
  \cellcolor{green!5}\small race card mother card Obama card\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small She's only human.  We have all had our Mcenroe moments, but if your \textbf{black} and you do it just once it will stigmatize you for life here in the United States.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small It was really sad ..Serena is great great athlete but the worst loser I've seen so makes her a horrible sports \textbf{woman} and this episode had \textbf{nothing} to do with genders or \textbf{race} or she being a  mother.She kept attacking Ramos's character and accused him of doing so. Not sure if Naomi would think high of her once role model ..really sad\normalsize   & \cellcolor{green!5}Nothing, Race, Woman & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!5}3/62 & \cellcolor{green!5}4.839 \\  \hline
  \cellcolor{green!27}\small NO it's not \textbf{sexism}  It's \textbf{racism} in this \textbf{racist} society\normalsize   & \cellcolor{green!27}Racism, Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/10 & \cellcolor{green!27}30.0 \\  \hline
  \cellcolor{green!5}\small how is it \textbf{racism}? both players were \textbf{black}?\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Your not a \textbf{woman} your a man\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small She is talking about un attractiveness.. I swear by \textbf{old} nad new gods.. Even gorrilas look. Better than this fucking whoMAN\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She does not look like a \textbf{woman}. Testosterone on board ? she looks like a \textbf{d\textbf{rag queen}} to me......\normalsize   & \cellcolor{green!27}Drag queen, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small The saddest thing here is that a girl of 20 years was devastated by her own player favorite here, on wich she has dreamed about this day, for her own favorite player, does this...Classless, yes, stupid, yes, \textbf{lame}, and sadly she is a \textbf{woman}, you would expect from a \textbf{woman} a little bit more of some behaviour... especialy for her \textbf{race}, it certanly adds an bonus to her own cry baby moves, for her to be a sore loserAnd let's not forget that she changes the story every single time she can... bringing her daughter in this, is just... all time low for you Serena, instead of learning your kid how to be an awesome sportsman, you teach your own kid how to be arogant, and spoiled\normalsize   & \cellcolor{green!5}Lame, Race, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/129 & \cellcolor{green!5}3.101 \\  \hline
  \cellcolor{green!27}\small Serena Williams was \textbf{racist}, attacking a Portuguese umpire. And to accuse him of \textbf{sexism}? Disgusting behaviour. Can't believe Naomi Osaka admired her. Williams lost my admiration that day. God help her daughter if she has to put up with rants like that at home. Everyone should boycott J.K. Rowling's books in protest after she supported Williams. After all, the Harry Potter books are just a rip off of The Lord of the Rings.\normalsize   & \cellcolor{green!27}Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small Yep she couldn't handle losing to a 20 year \textbf{old}!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She's a bully. She did this to a lines \textbf{woman} in her match against Kim Clijsters. Got tossed for it. In this exchange she sounds insane. There ya go young aspiring women, if it doesn't go your way, throw a tantrum and blame everyone, especially men. Only thief here is Serena, for taking the spotlight from her gracious opponent that wiped the floor with her. Hopefully she'll drop and fess up, and disclose what was really driving the anger. This doesn't require her to surrender her belief, but it does mean that she doesn't get to attack others...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small He has been playing Tennis As A \textbf{Woman} For Years....Against OTHER "REAL" \textbf{WOMAN}...NOT FAIR TO HAVE MAN POWER BEHIND THE RACKET...and WON all those time ALL "" FRAUDULENT ""SHOULD BE STRIPPED OF TITLES AND RETURN ALL THE WINNINGS 💰\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small see her attitude , omg \textbf{black} American  people never changes.always fights. she thinks she is great and see an small japanese girl defeated her\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small SerHEna, no doubt about it. 110 certified \textbf{tranny}.\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Woman? REALLY?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small If the Umpire had no hateful intentions for Serena, there would have been no distraction from the game.  Osaka won the game only because of the \textbf{Racist} and hateful umpires call and penalties he pressed upon Serena.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small She cracked under pressure I would have understood if she didn't play the \textbf{sexism}, mother, threat and victim cards.She actually got a warning, then a penalty for the racquet slam and then another penalty for a threat.Her whole \textbf{sexism} arguement is ridiculous\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Serene is a real  woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I dont care about any of this but I just can't get over what she is wearing, its some kind of \textbf{weird} satin tutu.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Don't forget that she didn't say only that the umpire was thief. She said that she will arrange to loose his job as umpire. So this is a theat whatever the \textbf{sex} is\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Serena is a bully, she has used bully tactics before.She was losing and was looking for an excuse.Notice that she was breathless when abusing the umpire.Ramos did exactly what the rules state, remember this is HUGE money...Also you could see in her eyes at the ceremony that she was enjoying the crowd booing.All in all a bad sport.As to \textbf{sexism}...Same prize money for best of 3 versus best of 5 for men???? Now that IS \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small Serena Williams is gone \textbf{bonkers}! Her behavior was unexpectable!\normalsize   & \cellcolor{green!5}Bonkers & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Spoiled little Cheating Brat\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small cmon! is a sport, at international level, tv cameras whatch everything... the players just have to do their job... not have histeric explosions and go to a tv program talking about \textbf{sexism}... are she serious? is she bipolar?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small The first warning was a bit severe (and the no-coaching rule makes no sense)... but then she surely lost it and was totally wrong. The \textbf{sexism} rant is ridiculous.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Serena's own fault for looking too much like a \textbf{woman} and for being too \textbf{black}, and for being a terrible spoilt \textbf{brat}.\normalsize   & \cellcolor{green!5}Black, Brat, Woman & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Gender - General & \cellcolor{green!5}3/22 & \cellcolor{green!5}13.636 \\  \hline
  \cellcolor{green!27}\small She was unprofessional, brought \textbf{sexism} into it when there was none, her coach was caught cheating, argued with the umpire when she had no argument, and she was punished for it all. Seems feminazis have a real problem with facts and reality.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small We all know tennis is rife with \textbf{sexism}. For example, women get the same prize money in Grand Slams despite having only to play to the best of three sets, not five like the men.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Had \textbf{nothing} to do with her being a \textbf{woman}. Had everything to do with her being a spoiled entitled \textbf{brat}.  This isn't the first time this has happened.  Her and Mcenroe should get married and pump out more entitled whiny ass brats that play all the cards they can to get out of personal responsibility. Time to retire "lady'.  You got your ass handed to you.\normalsize   & \cellcolor{green!27}Brat, Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/66 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Epic embarrassment of accusing of \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small "SerHEna" is a \textbf{transgender} posing as a real \textbf{woman}. PATHETIC. Fake, fake, fake. Do you really think that's a female??? You really can't tell the difference??? I feel sorry for you.\normalsize   & \cellcolor{green!27}Transgender, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Racism.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small first, show me a dna test to prove that serena is a \textbf{woman}.it appears  to me that a man, posing as a \textbf{woman}, is beating women at tennis.  this is why there is men's tennis and  then women's  tennis. so, this serena man, is making claims, that he lost because the judge doesn't  like his femaleness?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small The whole way she acted was just wrong. Her throwing a temper tantrum led to the audience booing and acting out of place themself. Serena Williams should be a rolemodel, in this case it led to the entire audience being, sorry If I have to say it like that, a**holes. All of this could've been talked about after the game, no referee or umpire would ever take back their decision, no matter how much you feel it was unjustified, so discussing it on the cord should obviously not be your go to action. This is not a case of what other people do and did, but what you are not allowed to. Just cause some tennis players haven't been penalized for something which seemingly is the same situation you're in, doesn't justify you not being penalized for breaking the rules. This lack of patience, and inability to adress problems after the game, led to the audience being major douchebags.The saddest thing is, because of that Osaka, a 20 year \textbf{old} \textbf{woman} who just won the US-Open for the first time, felt like she had to apologize for something she had worked on her entire life. This should've been a happy occasion. And Serene even praises the audience in the same moment. That's some major bollocks. The audience started to act like that because you clearly couldn't control your temper, and now you praise them for being a great audience? Yeah well they did what you wanted them to do I guess..\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/252 & \cellcolor{green!5}0.794 \\  \hline
  \cellcolor{green!27}\small I mean Osaka didn't get any violations so how is it sexism\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She's an absolute bellend. Nuff said. \textbf{Zero} class. Shame she has talent, she is a vile human being.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Fair? A man playing a \textbf{woman}?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small First of all Serena Williams is a very gracious when she loses. You just said the rules are "a player shall not receive coaching" if you watched the match you would know that she did not receive  coaching she was on the opposite side of the court and he was seated several rows behind rather tall people so let's be honest did she receive the coaching? No is the answer it doesn't  matter  because what this remarkable \textbf{woman} has achieved and will only get better remember 1 year ago she was fighting for her life during childbirth. And she made it to the final  of 2 grand slams. If that is not remarkable idk what is. And gracious is the way Serena treated her opponent  by telling the crowd to STOP booing. It could have went a whole other  direction. Cudos to Serena Williams  the G.O.A.T THE EMPRESS OF SPORTS. I LOVE YOU SERENA YOU SAY IT BEST " You have \textbf{nothing} to lose. Love always, Michael Page\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/168 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small \@Pedro Jorge Barbosa everyone is entitled to their own opinion. I guess you haven't seen the you tube remixes of a male tennis player throwing his racket at Carlos' chair and not getting a warning. Also Nalbandian kicking a wooden sign and broke threw and hit the linesman in the shin and Carlos' did \textbf{nothing} again. But your about as attentive as Carlos. I get it that your sticking up for him because he's from Portugal. But get a grip \textbf{Sexism} does exists very much in Tennis and there is no denying it. I'm a male and I even have to be honest with the subject. The truth shall set you free.SerenaGOAT\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small There's absolutely no situation in which her behavior could be deemed gracious let alone appropriate. Your suggesting so shows a total lack of maturity which is something you have in \textbf{common} with your idol.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small 1. Serena admitted to seeing the signal2.The reason the crowd booed was because of her immaturity and the japanese \textbf{chick} had to apologize for winning3.she verbally abused the umpire and also broke the bat which are both code violation and can result in a penalty for 1 point\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small i wish i was a \textbf{woman} so i could yell \textbf{sexism} at everything so i would get what i want\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Because she's a \textbf{woman} ? Then wtf is is Osaka Naomi ? A supreme \textbf{alien} being from Krypton that was sent down to Earth just to beat her there and then ? Erm , not ! She's a \textbf{woman} too , and I don't see she fucking about calling \textbf{sexism} . God , I literally lost ALL respect for her after this shit show . Acted like a little self entitled little \textbf{brat} .\normalsize   & \cellcolor{green!27}Alien, Brat, Sexism, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General, Nationality - General & \cellcolor{green!27}5/74 & \cellcolor{green!27}6.757 \\  \hline
  \cellcolor{green!5}\small Ramos was amazing. Hope he umpires every game that stupid \textbf{woman} plays.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small AEROSMITH SAID IT BEST... THE DUDE LOOKS LIKE A LADY!  SHE IS \textbf{TRANSGENDER}.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Also let's not forget Naomi. She's not only a \textbf{woman}, she is also \textbf{black} and a product of diversity, very talented and she was treated unfairly by Serena and all those people SHAMEFUL\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Black ??? Can you explain how a 50 Japanese and 50 Haitian = \textbf{black} .....?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Why does it matter if she's a \textbf{woman}, \textbf{black} or a product of diversity? Isn't it the whole point of equality to abstract away from people's physical attributes?\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Tomiwa is obviously slightly racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@GRIZZLY FLAME45 am not \textbf{racist}, I was just pointing out the hypocrisy of those who supported Serena and booed Naomi calling \textbf{sexism} and am also \textbf{black}, so how can I be \textbf{racist} to blacks?\normalsize   & \cellcolor{green!5}Black, Racist, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/34 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small GRIZZLY FLAME45 He didn't mean it in a \textbf{racist} way.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small If we tolerate tantrums like these, it will be the end of sports. Everybody will just play a \textbf{race}, \textbf{gender} ... card. Sports Social Justice\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small +Dane Cotar - It's the American way.  But she couldn't play it because Naomi Osaka is \textbf{black} also.  But I'm sure Serena thought he/she was blacker than Naomi.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small The Umpire sits gentle,\& was monitoring,sometimes the cloud of success make us \textbf{blind} and we wanted everything to happens in our way,Another way she could have focused her attention on the game,won and sued the empire later,Either as a job holder or a player ,you will be encountering hard times,but maintain peace \& get won the assignment,\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small I hope this wont end Naomi career  she far better person than that \textbf{fat} cow  i wish her only the best and never to play against Serena again.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Divided the tennis world? A lot of the people that are defending her are not fans. They have no idea what and how it happened. They only hear \textbf{gender} discrimination and rush to her side. Which wasn't even part of this. No, she is just a sore loser. Not a fan. Although I am a fan of Venus. She's the classy one.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small How lucky we are that Naomi is \textbf{Black}, otherwise we would hear that Serena is discriminated against because she is \textbf{Black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small I wonder was she playing the game, or counting the 90 or number of times others were not penalized. BTW this  business of equality is dividing the world into grossly unequal parts. Like men being pushed to relatively underdeveloped less land mass  containing southern hemisphere. I would prefer that as well, if women don't come there to claim equality there also after they finish ruining the civilization in northern hemisphere. I want peace between the \textbf{gender}, but that peace cannot be claimed by demonizing men for any chaos that plagues women's mind.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small Just when the Anchor says i have lost \textbf{nothing} in my life i was noticing his hair and couldn't stop laughing :D\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small The heading for this "video" is Serena Williams: Victim of \textbf{Sexism} or Sore Loser?.. How about DICKHEAD or perhaps FUCKWIT??\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Why she used the \textbf{woman} empowerment? Its all about rules.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small "you owe me an apology">ref is apologizing>you can see him mouthing and saying "I'm sorry">Serena Williams still considered a wohman instead of an actual ape\normalsize   & \cellcolor{green!5}Ape & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small she being a mother had \textbf{nothing} to do with the match and the codes she violated in the match.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small sexism?? don't make me laugh\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small What does being a mother or being a \textbf{woman} has to do with anything??\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small When I watched the video, I didn't take the boos as being for the umpire but for Serena. They didn't seem to boo until Serena start throwing a tantrum. This is a disgrace when athletes do this. One of the most important things in sports, in my opinion, is sportsmanship. Personally I don't like when players celebrate too much. There shouldn't be more than a few high fives or slaps on the back after a big play. These players are role models. The kids coming up are having enough trouble with being coddled by parents and teachers. It's even worse when their sports heroes throw fits and act like children. Serena made it even worse by playing the \textbf{gender} card. I saw the penalty stats for the past few years and men were penalized more in every category except one. Sometimes they were even penalized double what women were. I would think feminists would be pissed because Serena trivialized their cause by blaming \textbf{sexism} instead of taking responsibility. Then again when did feminists ever want women to take responsibility. They want women to have all the perks of being a man except with all the responsibilities that come with them. They want to be firemen and police but don't want to be held up to the same standards. They want all the high paying and cushy jobs but want the dirty and dangerous jobs to stay majority male. They want equality in marriage but then still want alimony, full custody, and child support. They want to the same as men but then still expect men to pay for dinner and open doors. They want the right to vote but scream when someone brings up the idea that they pay for that vote with the draft like men. They want all this on top of all the perks they get for being women, for example control of conception. They fight against releasing a male birth control pill and absolutely hate the idea of a financial abortion for men. They want to be able to get pregnant even if the man doesn't and then control what happens to the pregnancy. If they decide to keep it even if the man didn't want it, he's required to pay for it. They want to have \textbf{sex} all they want and if the man doesn't meet their expectations afterward, they want the ability to take back consent after the fact. They want to lock a man who sleeps with a minor up and throw away the key but if they do it they should get a slap on the wrist, keep their teachers license, or not penalized at all. I went off an a rant but basically they want to have their cake and eat it too. Now that they got everything they've wanted, studies show they've gotten progressively more unhappy over the years. Also, more men are staying away from women because of all of the pitfalls of dating in a feminist culture. This cause all the good men to abandon ship leaving only the weasel male feminist types who will do whatever to get laid and the women cry about 'where have all the good men gone?'. Well you drove them away. Because of all this men are relying on porn, prostitution, or \textbf{sex} robots and women are trying to shut that down. Some countries are even trying to institute a bachelors tax to force men to go back to women. Basically they'll do whatever it takes to coerce men into being their slaves. The real victims in all of this are the good women who can't find a good man because of the actions of a few or the real rape victims who aren't believed because of the tons of BS false rape accusations. Or the children who end up being raised without fathers because of these rules or they see their father get ruined and have to hear their mothers constantly tell them their father is a piece of shit. Many of these fathers have killed themselves because they can't take it. This creates young men who don't know how to act like a man. They either find father figures in gangs or they lash out because they didn't have a father to show them how to control their emotions. This is why 85 of inmates came from single mothers. It also creates women who don't have self confidence and don't find good relationships because they didn't have a father to show them what a good man is, Thus creating a vicious cycle of that will ultimately destroy the nuclear family thereby destroying the building block of western civilization which is ultimately their goal. It's one of the main stated goals of all Marxists. The Frankfort school said it, 2nd and 3rd wave feminists said it, and modern day SJWs say it. Jesus H Christ, tell us how you really feel! I'll end my \textbf{crazy} ranting tangent here.\normalsize   & \cellcolor{green!5}Crazy, Gender, Sex, Sexism & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/827 & \cellcolor{green!5}0.605 \\  \hline
  \cellcolor{green!27}\small why is this even an argument? Serena acted like a spoiled \textbf{brat} and is a sore loser because of it. I feel bad for the umpire, Naomi, the ballboys, and the crowd for having to watch that.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small I don't follow with tennis at all, so I don't know why this video was in my recommendation tab. However, the moment I clicked on the video and saw that it was about a \textbf{black}, American, female, all these stereotypes about them flooded my mind, including: loud, obnoxious, entitled, and rude. I'm sad and glad to know those stereotypes proved true.Also, only 17 grand out of 1.85 million for that violation? Wow, talk about privilege...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small Just addressing the title.  Serena's actions had \textbf{nothing} to do with being a sore loser.  This all occurred long before it was clear she was going to lose.  This is called "entitlement" and "self victimization" and not being accountable to her own actions.  Personally I think the \$17K fine is a joke.  This amounts to a mere parking violation in Ms. William's world.  She should be bared from future tournaments until she had made full public apologies to the Umpire, USTA, US Open, Fans and her opponent to whom she already apologized, but for all the wrong reasons.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small sorry but, did you watch the match? she was completely outplayed by Naomi Osaka and had just recently seen Naomi break her game, it was obvious to anyone impartial who was watching the match that it would be extremely hard for Serena to comeback from how well Osaka was playing and how not so well Williams was playingSerena Williams is a smart and experienced player, she probably already knew she would lose the match halfway through the second set, her breaking the racket is most likely due to the frustration of knowing she had to up her game but felt it simply was not one of those days where she could do itelite athletes can feel these things, in tennis is even more \textbf{common} and we see it many times when players throw a set away just to try and get back in shape for the rest of the matchso, what do we call someone who knows she's on a clear path to lose the match and suddenly throws a fit trying to find excuses and blame others for it? isn't that what a sore loser is? I mean, it's not even a issue to be a sore loser since it's normal for elite athletes to always want to win BUT the real problem is not only insulting others, the umpire in this case, but also question the character of someone who's history speaks for itself on how he treats everyone with the same rigorous interpretation of the rules BUT still being fair, that's the problem\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/259 & \cellcolor{green!5}0.386 \\  \hline
  \cellcolor{green!27}\small Willie - I fully agree with you. Serena went ballistic because she was loosing to Naomi. Luckily Naomi was \textbf{Black} because otherwise we would hear that Serena was discriminated because she is \textbf{Black}. Can you imagine if Serena would loose to any white tennis player? ("I fight for women equality and other things").\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small Agreed.....i think until she makes a formal apology to the umpire...she should be banned...Shes a fake ass grying every angle to get one over the umpire....\textbf{sexism}, \textbf{racism}, womens rights, im a mother etc...pathetic\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small WillieRants says:"This all occurred long before it was clear she was going to lose..."==Way I see it, it came out of her frustration.It could have been any reason, she blew up.Her glorious days are over and she knows it.You can't argue with aging.She's 36 yr \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Agree with every word! Serena went too far and it backfired! She definitely tarnished her reputation. \textbf{Sexism} was just an excuse and a space goat strategy to get out of this mess. Bravo for Naomi. She is like a breath of fresh air for this sport ...\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small There is a youtube video analyzing if Serena and Venus are \textbf{transgender}.  Very interesting facts presented. (Sorry I don't have the link but you should find it in the search )Perhaps Serena has changed women's tennis more than most know.  Congratulations Naomi Osaka,  You won against all odds!!\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Undoubtedly a transvestite\normalsize   & \cellcolor{green!5}Transvestite & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} is just awful\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small You have been doing it to us for 400 years, and now God is casting his judgement upon you.  Low birthrate, \textbf{mental} problems drug use. If I want to end white supremacy all I need to do is buy a bunch of heroin and drop baggies in all of your towns and you all are done.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small The past doesn't justify any kind of bad acts that proceed on today... \textbf{black} people claim to be the ones who have suffered the most in history playing victim card here and there but what about Jews? If anything they have suffered the most in history. What about when the moors invaded and occupied Portugal and Spain for 800 years? Did Portuguese and Spaniards sit around and cry and play victim? no they moved on did what they could. What about all the slaves the arabs and jews once had? Jews and Arabs rarely ever get slandered for slavery and do you see the people that descend from their slaves crying about and making excuses? no you don't. Things are changing for the better and we need to move on.P.S If you put a bag of heroin in front of me or my friends, trust me we wont do anything and none of our towns will be "done"\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/158 & \cellcolor{green!27}0.633 \\  \hline
  \cellcolor{green!5}\small at least he isnt \textbf{black}.  the spanish were relatively constructive people.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Lion Of Judah are you \textbf{crazy}?? He's Portuguese and FYI Spaniards and Portuguese are white people... perhaps not fully due to being kinda mixed(specially in the south) but they still classify as white\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Obake Tora belive it ore not \textbf{black} people are more in debt to white then white people to \textbf{black} people. Because before europians go to afrika, Afrikan population was 30 milion in total then europians give them agriculture, medicine, infrastrutture, tecnology, potable water, food etc etc then \textbf{black} people started growin in peopolation and to day are Close to 1 billion because before they died from viruses, no potable water, lack of food, no medicine, from waild animals , war tribes etc etc so look the other part of the medal not only " my slavery cry cry cry give me free things because my slavery cry cry cry you lacist you lacist cry cry cry my slavery etc etc "\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/121 & \cellcolor{green!5}2.479 \\  \hline
  \cellcolor{green!27}\small \@Lion Of Judah he is white..he's European...🤣🤣🤣🤣Go to Spain and call them \textbf{black}. See what reaction you get.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Serena is a strong \textbf{black} \textbf{woman}. She's going to be outspoken. That's why, many say, \textbf{black} men go for white women. She's still a champion and this is getting blown out of proportion\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/33 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She's a sore loser. And a bully that think cos she's a \textbf{woman} and \textbf{black} the rules do not apply to her. Guess again, princess!!\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small She's a Sore Looser who opportunistically latched onto \textbf{Sexism}. Typical of people who fail to accept personal responsibility - it's always someone else's fault.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small why would a \textbf{woman} be penalized only because she's female if its a match between two women? its like accusing the ref of being super stupid cuz you'd have to be super stupid to be "sexist." i cant imagine anyone treating someone different just because of their \textbf{gender} or \textbf{race}. people may have bad prejudice about races, \textbf{gender} and sexuality but that doesn't usually lead to different treating, especially not if no one else (like the \textbf{gender} or \textbf{race} you prefer) could benefit from it.\normalsize   & \cellcolor{green!27}Gender, Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}6/85 & \cellcolor{green!27}7.059 \\  \hline
  \cellcolor{green!5}\small How lucky we are that it was \textbf{Black} tennis player Serena played against. Can you imagine what would happen if she would loose to a white tennis player? We would hear that Serena was discriminated against because is is \textbf{Black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small She looked like an \textbf{obese} hippopotamus in a tutu.\normalsize   & \cellcolor{green!27}Obese & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She 's the only \textbf{woman} to have a daughter you know.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small When you´re net worth \$170 MILLION for playing with little \textbf{y\textbf{e\textbf{llow}}} balls and complain about \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Gender - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}4/16 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small The thing is: she didn't have to throw her racket or yell at the umpire after the 1st warning. She is just \textbf{dumb} and a bad loser on top of it. hope she disappears from tennis stadiums asap\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small It is clear S. Williams lied and cheated, she admitted seeing the thumb position with the coach coaching. The WTA look biased, what would be the reaction if the abusive player was white \& the umpire a \textbf{black} \textbf{woman} I wonder. Williams \& Katrina Adams need to publicly apologise. Billie-Jean King appears ignorant.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small Oh, gawd, she is \textbf{nothing} more than a selfish, poor sport. Osaka outplayed her from start to finish. Now,  to be fair, IMO, there was an element of \textbf{sexism} involved. A lot of male players DO get away with receiving hand signals from their coaches, but still, a lot DON'T. And those that have been caught have been fined. McEnroe was famous for his meltdowns. He got caught, he got fined. Then there's Williams playing the mom card. Really? What does that have to do with anything? And then she threatens the umpire about never working her matches again. Hey, I'm going to take your livelihood away. How's that for good sportsmanship? Not. Williams IS a great athlete. She's won a lot of titles and deserved them, but her attitude has always stunk and always will.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/136 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small How is it sexist. She's not a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You know it's crystal clear to me that both of the Williams sisters are both transactions. They clearly have the male body physique. After doing a little research I found that in 1977 the courts ruled the tennis could not ask for a \textbf{gender} test which open the doors for all mediocre male tennis to turn into women and be great tennis players which a few did. As a society whyDo we allow this nonsense to take place?\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Only because millions of people were watching the game she did not slap Ramos on the face. I believe her aggressivity is a lot more than what we have witnessed. Besides that, she looked in that outfit like an \textbf{old}, \textbf{fat} and ugly ostrich.\normalsize   & \cellcolor{green!27}Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small What do you expect from a "successful" \textbf{black} \textbf{woman}??\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small I am more appalled at the lack of tennis sense ( or knowledge) of the USO audience. They kept booing  the umpire and cheering for Serena when she played her cards one by one, \textbf{sexism}, mother, victim, daughter. No one shows the proper guts to stand up to her except the umpire ( in this match) and the lineswoman ( in the Clijsters match) and then she flipped when that happened.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Right..Serina is a big time bully with a track record. NYC crowd supporting her is retarted as it's dying to be politically correct in the worst liberal tradition. And being politically correct means finding \textbf{racism}, \textbf{sexism}, antisemitism etc as soon as one opens his mouth. However, in all fairness, Ramos did bring out the worst out of Serena instead of controling her anger. They were both out of control. Conclusion: it is time for Serena to retire while she still has some dignity and it's time for Ramos to be re-trained.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/91 & \cellcolor{green!5}2.198 \\  \hline
  \cellcolor{green!27}\small +Lisa Tuvalo I'm a liberal, as well, and I think Serena is an entitled, narcissistic and often out-of-control asshole, which has \textbf{nothing} to do with politics. Being a good sport is not a political affiliation, it's a character trait.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small No question Mordy Slmn. I'm surprised she didn't play the \textbf{black} card with that crowd  while she was at it. She is a typical spoiled, selfish celebrity and the morons in the crowd went right along with it. She brought all of that on herself and the crowd proved their lack of character as well.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small he said he doesn't cheat to win well I think cutting your penis off and putting a slit there is cheating because you're still a man with a man's physique and a mans endurance and a man's muscle structure yeah just because you removed your penis does not make you a \textbf{woman}. looks like that idiot Bruce Jenner he doesn't look like a \textbf{woman} and just looks like some guy in Drag.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small +78tag - she couldn't play the \textbf{race} card because the other girl was half \textbf{black}.  I mean should could have gone into the "you ain't \textbf{black} enough" rant but that really was a stretch too far.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Everyone went to emotional. An American vs a Japanese I'm even surprised that we didn't hear those "USA, USA, USA" chants. That would have been funny considering the fact that Osaka grew up in the USA. Anyway, public wanted Serena to win so badly and lost all sense of objectivity. Futhermore what they didn't know is that the referee had to punish Serena BECAUSE of his coach. He was the one breaking the rule, but \textbf{nobody} knew that at that moment even Serena (based on her saying). The referee should have said "I'm sorry u didn't do anything wrong but your coach did therefore following the rule I have to give you a sanction". But it's hard to keep calm in ur mind and speak while an Amazon is yelling on you having lost all self control. The public didn't see anything and just emotionaly followed Serena because their hearts told them to do so.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/155 & \cellcolor{green!27}0.645 \\  \hline
  \cellcolor{green!5}\small T NGUYEN,  Your idea is interesting and reasonable for an average umpire, perhaps. However, look at the videos more closely. Clearly Carlos IS responding to Serena's claim in her first retort to his Code Violation-Coaching - Warning. Again after the Code Violation-Racquet/Racket Abuse-Point Penalty Mrs. Williams, when Serena counters with "Warning", Carlos explains again to Serena, which Serena counters, disagrees, begins her onslaught and barrage, during which Carlos responds to Serena several times explaining. We do not hear his words. Also note, Serena after her statement and claim to Carlos about the 'thumbs up' not as coaching but as encouragement 'Come On', she turned away, headed back toward the baseline, after a few steps away turns back toward Carlos shouts something in a strong tone, points her finger at him; Her words are not pickup by the microphones, but her non-verbal indicate something strong, perhaps intimidating-threatening. Her motion is not as strong nor anger was at the \textbf{woman} line judge in 2009, less, but along that line of similarity. Carlos ignores it.Many are quick to say about Carols Ramos known as a 'stickler' or 'strict' umpire. However, Carlos Ramos endures at least three separate onslaughts of verbal abuse. One after each code violation statement and penalty status. Each one is increasingly more abusive, with multiple abuses in each. After the third onslaught and barrage of verbal abuse finished, which contained intimidation, threat, demand of apology, questioning-refuting judgement and correctness, defamation of character ['liar' and 'thief'], did Carlos Ramos rule Code Violation-Verbal Abuse-Game Penalty. The discussion with Tournament Director Brian Earley is not audible [intentionally], but as it completes a few words of Brian saying " ... okay then it's Verbal Abuse for 'thief'. Seems there was much more and maybe agreed to minimize it, else a greater penalty could be assessed as a Major Offence of 'Aggravated Behavior' and disqualification. Perhaps agreeing that with this game penalty, Serena will stop her tirade, the match will be ending soon, and minimize any worse detriment to the tournament, at least the match will complete in a closer to normal proceeding, not by default.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/352 & \cellcolor{green!5}0.284 \\  \hline
  \cellcolor{green!27}\small Serena the halfwit gobshite played the victim to \textbf{sexism} \textbf{racism} and cheating blah blah blah she's sore\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Why are people supporting this \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Don Orion she's half \textbf{black}....so according to your \textbf{racism} they are both males\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small \@Plat what made that \textbf{racist}? Because she happens to be \textbf{black}? Who is the \textbf{racist} here...YOU. And damn...are you \textbf{blind} too. Look at her skeletal structure and figure. It's a biological man.\normalsize   & \cellcolor{green!5}Black, Blind, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/32 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Or the male testosterone and female injected hormones  trying to fight over control of "her" body. That is not a \textbf{woman}. Plain as day.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small 3:39 "I've seen other men call other umpires other things and..."Huh..? Other than whom, darling? Aren't you supposed to be a \textbf{woman}..? I'm done.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Williams threw away a successful tennis career with an infantile tantrum.This wasn't the first, however,  she has spouted immature, spoiled \textbf{brat}, outbursts before and now she will reap boos and ridicule when she next appears.She needs anger management bur her pride will never allow her to accept responsibility and the remainder of her career andcfragile ego will forever be tarnished by outbursts unacceptable in multi-millionaire sports figures.It is also unlikely, because of her immaturity, her marriage can survive longer than 3 years and she will end up hugely overweight, drowning in self pity.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small She is a nasty and ugly individual! Thinks she's bigger than the sport! Wouldve used the \textbf{race} card had she not been playing Osaka! Hideous and odious individual and dont forget, she has a hell of a lot of previous!!\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I'm sick of all you thinking that this is a "\textbf{woman}" it's a " MAN" stop saying it's a real \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small I think it should be mentioned that her anger wasn't what caused him to penalize her, but her accusing Ramos of something that could end his career, like \textbf{sexism}, bias, being a liar etc. It was a more "credible/real" threat then other players short schpeels filled with a bunch of F bombs.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small ...as in all aspects of the world these days. If you don't like something - cry, scream and kick the air - get a sympathetic group behind you and declare "VICTIM". THE HUMAN \textbf{RACE} IS NOT MATURING PAST 5 YRS \textbf{OLD} ANYMORE.\normalsize   & \cellcolor{green!27}Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Thats a man how can people think its a \textbf{woman} \textbf{blind} fools\normalsize   & \cellcolor{green!5}Blind, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Serena is a victim of her DNA - she's a \textbf{black} \textbf{woman}. nuff said.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small both. its both \textbf{sexism} with the dog piling and williams was being a sore loser. Its both.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I think her stats are fake, it says 5 foot 9 and 155. Thats my stats as well but im \textbf{skinny} and shes huge?\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small More divide and conquer. \textbf{Black} vs white. Men against women. These psychopaths run the world.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small anyway \textbf{black} girl from japan? i dont get it?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She lost to a \textbf{woman}. How could it be \textbf{sexism}?\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Cipta Pradja wtf? What does \textbf{nationality} has to do with it?\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Cipta Pradja what has \textbf{nationality} got to do with superiority...that's just illogical\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small They should nerf the \textbf{woman} card in the next patch.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small buff \textbf{common} sense pls\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small It wasn't \textbf{sexism}. It was \textbf{racism}!\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small the only victims I see here are Osaka and Ramos. victims of a stupid women/\textbf{black} movement in U.S. it's become a serious crime to even slightly verbally abusing a \textbf{black} person while other races are openly harassed in the world. double standards at its finest.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Why call her a lady? She didn't act like one. Well she acted like entitled whiny \textbf{woman}, and she ironically fights for women's rights (her claims, not Mine) but proving the stereotypes about to be right.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small The only \textbf{sexism} and \textbf{racism} was on display was from Serena Williams... Well not really... Crowd booing the umpire was also sexist and \textbf{racist} act...Oh! Another thing.... I guess Serena thought that, as her abusing women umpires didn't get her penalty, she could get away with abusing men umpires.... May be that made her think that he was being sexist by punishing her. But that only means she has got hubris \& entitlement filling up space inside her skull. Also she justified the stereotype of how women behave when they don't get what they want...\normalsize   & \cellcolor{green!5}Racism, Racist, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/96 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small A victim of botched \textbf{gender} realignment surgery\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Serena got mad because Naomi Osaka out played her when shes literally half her \textbf{age}.  Carlos Ramos is a true hero of the sportSerena Williams should be banned from tennis due to her bad sportsmanship and misconduct.The coach even admitted he was coaching her\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small it's not even a \textbf{woman}, where does \textbf{sexism} come onto this? Research "adonis' belt" people. Bones don't lie, but people sure do\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small There's \textbf{nothing} has to do with \textbf{sexism} or WHAT so ever, she ruined Osaka grandslam, I think she was emotionally disturbed\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Yep, thats \textbf{black} women for ya. Its everyone elses fault except themselves.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Sore Loser and brings bullshit \textbf{sexism} into it . Playing her cards as they  always do .\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small She played three cards to support her \textbf{thin} argument:1) Mother card2) \textbf{Woman} card3) Victim card( babbling about never cheating)I think this rant is just out of place and unprofessional of her.\normalsize   & \cellcolor{green!27}Thin, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small This could be the most shameful act of a professional tennis (\textbf{woman}) player I've ever seen.  I myself feeling upset to view this.  What a f'<k.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Is it just me or is Serena starting to look \textbf{weird}.  \textbf{Age} maybe idk but its a pick with her and her opponent that day where she looks like a demonic humanoid.\normalsize   & \cellcolor{green!27}Age, Weird & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Good thing the other player wasn't white otherwise she would of pulled the \textbf{racism} card as well lol\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small She's a \textbf{transgender} ya know.  Her sister too.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Serena' \textbf{sexism} claim is false. MacEnroe, for example, was penalized and fined many times for similar behavior.  So have countless other men. He was even thrown out of the Australian Open entirely once. 35 players at this particular Open were penalized for various reasons. Being The Great Serena and possessing a vagina does not exempt her from following the rules. Neither does being a mother -- that was her most pathetic attempt to get special treatment.  I have a baby!  How dare you expect me not to throw tantrums when I'm losing!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small It could be the \textbf{race} card. This time was the \textbf{gender} card, the victim card and the mother card too.\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small How's he sexist if the win is being given to osaka....a \textbf{woman} - -\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small She is \textbf{old} stupid women with their menopause.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Why is a man allowed to play tennis against a \textbf{woman} I don't get it?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Nope, she's not the greatest female tennis player. She played during a time when there was no competition. When she had competition she was meh. And she was much younger than Clijsters in that match, for example.Roddick?? You are giving as an example an american player in the US Open? Come on, it's like you guys don't know how the US Openc crowd behaves every year.Look at Federer, 37 years \textbf{old} and still kicking ass against 21 year olds. Look at Nadal, he was destroying his opponents when he was 20 years \textbf{old}. Soooo nope.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/97 & \cellcolor{green!27}2.062 \\  \hline
  \cellcolor{green!5}\small How can it be \textbf{sexism} if she and her coach cheated and on top of all that there was another \textbf{woman} fighting her for the title???\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small It's HE not she. Give me a break. This is not a \textbf{woman}. Total \textbf{tranny}. My god just look at his face, arms, shoulders, Man hips, etc. Serena is a \textbf{tranny}. Total MAN. She's cheated...wait. He's cheated his entire life. Cheating REAL women out of victories and championships. If you can't just look at him and see he's a man you're not looking with both eyes. \textbf{TRANNY}!!!\normalsize   & \cellcolor{green!27}Tranny, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}4/67 & \cellcolor{green!27}5.97 \\  \hline
  \cellcolor{green!5}\small I love the \textbf{sexism} argument. Tell me, if he is sexist, and both of the players are female wouldnt he be sexist towards both? You cant play the \textbf{race} card either, Naomi Osaka is half Japanese half Haitian, she is almost as dark skinned as Serena is. She is a sore looser, and was given 3 warnings. This is not the first time she has done this before.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Oh my god... how is it \textbf{sexism}... if her opponent is a \textbf{woman} too!?!!?!! :D xD ... can she even think straight anymore ?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Liberal is short for \textbf{racist}. She is a flat out \textbf{racist} and deserves to be permanently banned from tennis.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small amazed66  - Democrats wanted to keep slavery around, started the kkk, and are the ones that killed \textbf{Abe} Lincoln the President that freed the slaves.\normalsize   & \cellcolor{green!27}Abe & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small amazed66  - I agree, we shouldn't have to take the blame for things that happened before we were born, but you chose to be a democrat after learning history and seeing how they are still trying to divide us with \textbf{gender}, \textbf{race}, and sexuality. Know why \textbf{black} people like myself who voted for Trump calls it "Getting of the plantation"? It's because now you democrats only see us as votes and use us to feel better about yourselves as if we are lesser beings that need your help 24/7. The world democrats want to create with the sjw and censoring shit is very close to what the Nazi's used to do which is another reason I find it so funny you guys like to call people Nazi's. Funnily enough you guys also are the first ones to call someone a \textbf{racist}, sexist, or homophobe just because you didn't like what they said while at the same time secretly being the things you call people. Democrats are the worse kind of people.\normalsize   & \cellcolor{green!5}Black, Gender, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/171 & \cellcolor{green!5}2.339 \\  \hline
  \cellcolor{green!27}\small +Deku Heroic - Just so as you know, prejudice means to pre-judge and I'm afraid that's exactly what you have done here with me because not only am I not a Democrat but I'm not even an America either. I might also add too that naturally assuming that I could only be American is quite an insular attitude and in some ways a form of "\textbf{racism}" in itself.The trouble with those on the political right is that they think they have a monopoly on things like condemning crime and upholding law and order, a dislike for overly politically correct attitudes and showing patriotism, probably because they collectively place "the left" in one all encompassing bag. Yet if anyone tries to do that to those on the right and tags them by the most extreme and insane brigade from the right, then they will be the first to protest. Yes there are plenty of liberals and those on the left who like to unjustifiably play the victim via the \textbf{race} or \textbf{sexism} card, yet equally there are plenty of liberals or those on the left who will condemn that because it devalues it when it actually happens. Just as there are plenty on the right who at times will try to unjustifiably explain away any genuinely discrimination of any form, as if none ever exists.Also as a \textbf{black} person, unless you are worth millions and don't really care about others but yourself then voting Republican is like turkeys voting for Christmas if you really think Trump and Republicans value you and have your best interests at heart.Amway, my original point was that it's is total nonsense to say "Liberal is short for \textbf{racist}" as if there is only one kind of liberal, especially when as I alluded to above, the KKK are hardly colourblind and definitely are neither liberal nor of the left of the political spectrum.\normalsize   & \cellcolor{green!27}Black, Race, Racism, Racist, Sexism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}5/319 & \cellcolor{green!27}1.567 \\  \hline
  \cellcolor{green!5}\small amazed66  Not a democrat but you sure are defending them as best you can. Not an American but you are commenting on an American Tennis player and talking about the kkk that happened in America while also weighing in on US politics like it affects you in some way. It's not \textbf{crazy} to assume these two things. If you are not an American democrat then I am sorry for assuming you are the worse thing in our country right now. I actually live here so  my opinions on the matter I think hold a bit more weight than someone that doesn't.  You don't know what it's been like here in the last 10  years. It's gotten really bad. Not Merkel bad yet, but it's not far from that. Democrats are slowly ruining our country.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/134 & \cellcolor{green!5}0.746 \\  \hline
  \cellcolor{green!27}\small serena was the sexist and \textbf{racist} on the court....it was disgusting to watch her behavior....js\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small What is most annoying about Serena is that she is very good at using the strategy she used in this match to break down her opponents. She has done it many times. The anger and injustice that I am sure she actually felt she long ago realised she could use to either get a crowd on her side, fire up her own game and take the rhythm out of the opponent or both. It's called gamesmanship and she, like other superstars who should know better (Neymar, Ronaldo, McEnroe etc..), has tried to cover up her own failings with whataboutism. It's a politicians game. When things are going against you, find a distraction, put your opponent off, take them outside the game and maybe, just maybe you can come out victorious. So \textbf{sexism}? Really. The points were taken from Serena and given to.... a man? Actually, I can't be bothered to get into that side of the debate because that is exactly what someone like Serena wants. Talk about the controversy that she, alone, created and forget about the fact that she was outplayed by a superior player. Well Done Osaka - you overcame the toughest hurdle out there, both athletically and mentally.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/202 & \cellcolor{green!5}0.495 \\  \hline
  \cellcolor{green!27}\small who \textbf{woman} was mad\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I think she knew she was gonna lose already when he gave second penalty, so she came up with a brilliant idea to overshadow the success of Naomi , and create a controversy that could have Serena's name in all media. Then she purposefully called Ramos a liar and a thief , resulting in her losing a game point which she knew would happen, and then she played the \textbf{Sexism} card to make her look as a victim. So I think she orchestrated all this drama just to maintain her popularity and to be saved from criticism from her fans and media. What a loser!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small Why are they even asking, is it sexist or racial, it's obviously not, that bitch was having a massive 'do you no who I am, how dare you' tantrum ! I don't like anything about that \textbf{woman} now, disgusting person !!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small The greatest \textbf{TRANSGENDER} tennis player in history.  Not even professional female body builders can achieve the physique that Williams (either of them) have.  Look at the musculature....the body proportions....IT is a man. So...it really WAS \textbf{sexism}....just the opposite  kind....against a man instead of a \textbf{woman}.\normalsize   & \cellcolor{green!5}Sexism, Transgender, Woman & \cellcolor{green!5}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Retire yourself, you're classless, you're a bad example to your daughter, you're a privileged no class trash adult \textbf{brat}(: go back to boxing! Oh, wait that's mike tyson!! Just couldn't tell the difference (:\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Naomi Osaka please don't idealize Serena. She is an entitled \textbf{black} American. Please stay the respectful, humble \textbf{nationality} that the Japanese culture is.\normalsize   & \cellcolor{green!5}Black, Nationality & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Serena is the \textbf{common} denominator in her tirades. No, \textbf{sexism}, \textbf{racism}, motherism just really bad sport and sore loser...ism\normalsize   & \cellcolor{green!27}Common, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Social Class - Working class & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Know the sport before you flap your lips. Williams lost a game because she pushed it to strike three! Williams was in the wrong times three. The rules are well known by the players. Admonishment, point, game, and finally you risk being defaulted. Ask Nick Kyrgios about his meltdown experiences on today's tour when he gets out of line. Ask Nadal about his experience in this year's U.S. Open when he got out of line. Unlike Kyrgios and Williams, Nadal knows when to shut up, be a professional, and get back to competing. is the rule against coaching outdated, probably. But the rule is in place now and Williams knows she is responsible for her team's behavior. Instead of returning to a model of veteran professionalism, she chose to personalize the admonishment and martyr herself to hide the fact she felt she was going to lose. Williams could have pointed at her coach wagged her finger NO! and apologized for his actions. That would have ended it with the referee. But Serena being Serena, she has to blow it out of portion. When she smashed her racquet I knew, from having watched her for decades, that more was coming. She berated the umpire numerous times on a worldwide broadcast. How could he rule anything different? The attempt to demonstrate bias by dragging out decades \textbf{old} tolerated bad boy behavior is silly. How about we use the standards of the 1930s \& 40s? Say Bill Tilden with the world celebrating his tennis excellence while turning a \textbf{blind} eye to his open pedophila. If Nastase, Connors, or McEnroe were to try their antics on today's tour they would be sanctioned just a quickly as Serena Williams. Williams threw the second set away with her actions and paid token pennies in fines when compared to her 2nd place prize money for a very poor performance while robbing a very fine young \textbf{woman} of her golden moment. So will Serena Williams close out her career allowing us all to remember her substantial accomplishments or will she leave us with the image of outrageous adult tantrums?\normalsize   & \cellcolor{green!5}Blind, Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/351 & \cellcolor{green!5}0.855 \\  \hline
  \cellcolor{green!27}\small Lets just stop \textbf{sexism} and merge female and male tennis matches, thats only fair after all.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small you're not a \textbf{woman}, king kong!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I am a big fan of Serena, but I can definitely see both sides.  Her behavior is not the greatest and \textbf{nothing} to be proud of, but not exactly over the top.  And so sorry for Naomi.  When you are competing at that level there is a lot adrenal flowing, and that makes  for great competition and sometimes less than great behavior  But it is true, that when men exhibit this behavior, sometimes it is not only excused, it is heralded.  A very difficult call now.  In the past it would be an easy call--any \textbf{woman} that did this was an animal  A man that did this, well it is just boys being boys.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/114 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small I saw some screenshots in the clip and for former tennis players to say that they have never had a game docked for abusing the umpire is half truth. What most commentators missed was that Serena was not docked a point because she broke her racket or a game because she abused the umpire. Those are all code violations. She got docked the point because it was her second code violation and a game because it was her third code violation. To say other men players are not similarly penalised is false. If those code violations are their first. the players will only get a warning. How is it no one is speaking on this? To claim \textbf{sexism} and \textbf{racism} is ludicrous as her opponent was also a \textbf{woman} of mixed parentage. Let's call a \textbf{spade} a \textbf{spade}. She was beaten fairly by a better player on that day.\normalsize   & \cellcolor{green!5}Racism, Sexism, Spade, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}5/149 & \cellcolor{green!5}3.356 \\  \hline
  \cellcolor{green!27}\small Sexism?? The OPPOSING PLAYER was also a female.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I always thought her as competetive but now I think serena is \textbf{racist} towards Asians. She had previously abused an asian official.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I dunno it its a cultural thing. But I, like Carlos, wouldn't take that sort of shit from anyone. Much less from a man, if it a question of \textbf{sexism}. I dunno or care if its normal no cuss umpires like that in the United States, but in Portugal where Carlos and I are from, you will get sent off which ever sport we are speaking of, for speaking to an umpire/referee like that. She can go fuck herself. \textbf{Sexism}... she's a sore loser that wants to get the attention off of her loss, that's what she is.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Osaka was majesticSerena had realised that she can't win against her , and got hand gestures from her coach which Ramos (a dignified refree) clearly saw. Then came the raquet abuse , it was all fine till then,but she started her bullshit about the Refree. And sorry to say this but she is an outright LIAR and PATHETIC BULLY. She should look at stats to know that it was'nt \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small What a horrible \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Maybe if she would control her temper and kept her mouth shut it would be better, but then she will say I'm \textbf{black} your doing me wrong imagine that\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small She broke the rules and became a drama queen against the umpire Because he was a guy yelling \textbf{sexism}, but at least she didn't threaten to ram the ball down his throat, like she did when confronted by a female umpire at a different match ! Fine her and expel her for several matches until she understands that she doesn't get special treatment for being a award winning athlete When she's on the court!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small Lol..a \textbf{woman} playing another \textbf{woman} and you're crying \textbf{sexism} By the official?..Serena absolutely lost the match for herself, it's not hard to figure out what happened first of all, even if she didnt see her coach giving hand signals it was still illegal, if she didnt break her racket she wouldn't of lost the point and if she would have just shut up she wouldn't have gotten a game penalty..truth is she knew she was goin to lose and used the official as a scapegoat\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/85 & \cellcolor{green!5}3.529 \\  \hline
  \cellcolor{green!27}\small Spoiled \textbf{brat}, sore loser. The fine was far too small.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small SHE IS \textbf{NOTHING} BUT A SORE LOOSER AND IF IT DOES NOT GO HER WAY SHE WILL HAVE A MELTDOWN AFTER MELTDOWN - SHE WAS ALREADY A VERY NASTY PLAYER SINCE AROUND 2009 !!!!!!! WE WILL NOT WATCH HER ANYMORE !!!!!!!!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Well done Naomi Osaka; congratulations!This is not \textbf{racism}, \textbf{gender}, whatever. This is bad behaviour case. By someone who should be a role model, which she is not. Serena has always acted like trash when things don't go her way . Her huge EGO needs to be gone from tennis. Serena is a sore loser. The Umpire Ramos has did what he's suppose to do. Serena is making excuses for what she knows is wrong, calling it fighting for "women's rights!" This is not your first time bullying people. Shame!Serena, if I may add, wasn't on the court to "fight for women's rights and equality." She was on the court fighting for a 3.8 million dollar check and her 24th gland-slam title. Naomi was playing at a much higher level than she was and that frustrated her more than the umpire did. Had Serena been playing well, her coach wouldn't have had a need to use hand signals, and she wouldn't have smashed her racquet. It was Naomi's incredible performance that brought out Serena's despicable behavior.she was pulling another stunt today, got called out and then played the victim card and cried....she's a vile person. she's awful! arrogant, rude, no manner, no rule, no respect.\normalsize   & \cellcolor{green!27}Gender, Racism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/207 & \cellcolor{green!27}0.966 \\  \hline
  \cellcolor{green!5}\small that crowd on the court is just pathetic, booing at osaka. be ashamed, 20 yrs \textbf{old} girl kicked ass of that tantrum diva and you booed at her. i hope she stays extra player and never again attend your grand slam in protest. better yet, i hope you will lose grand slam tournament at whole. to be erased from calendar and that one to be given to crowd who will appreciate to see winners especially young ones who beat leaders...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small Amazing video Mr . I am all against \textbf{Sexism} but this wasn't not the case of \textbf{Sexism} she just lost\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Hahahaha, A real \textbf{woman} beats a big lying man, pretending to be a \textbf{woman}.  I am for the real \textbf{woman} no matter what country she is from. Serena man just can't believe she has been beat by a genuine \textbf{woman}. Serena isn't bouncing back from pregnancy because she is a man. Serena is a cheat, pretending to be a \textbf{woman} in a female competition. Already had the upper hand in strength being a man. That is what HE gets. Sore loser for sure.  Male anger shining through. It's discrimination letting Serena play against a \textbf{woman}, now that's true discrimination.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}6/99 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Since Renee Richards, I strongly believe that both genetic and testosterone levels  testing and testosterone levels must be part of the biomedical screening for all women's sports.  Big \textbf{buck} sporting franchises make trans-gender cheating very attractive to those at the lower levels of the socio-economic spectrum.  As a retired umpire  I hope that the best possible outcome of this tirade could be just what we  need to address the weakness that trans-sexualism exploits.I look forward to their next match-up.\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small As a \textbf{woman} myself, I dont need her to stand for \textbf{woman} rights in this manner.  I dont want to be seen as a sore loser as a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small Wait. Serena is a \textbf{woman}?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Time for her to go out in dignity than a wicked \textbf{witch}!!\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I have met the williams sisters father and known him since 1991.Calling both \textbf{race} traitors based on her fathers strong beliefs should be a part of this.He Gave them Tennis not her coach .Serena compares her situation to mens so why not have her play men in the future. I do not view someone her size as female or feminine. Bwsides, her presence in tennis is too long and very boring.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small This trans \textbf{gender} \textbf{woman} was an extremely sore loser. Then she tried to make it into, that she was looking out for \textbf{woman}'s rights. lol I was just waiting for \textbf{racism} to be next.\normalsize   & \cellcolor{green!5}Gender, Racism, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small Serena's fans are so \textbf{dumb} and stupid!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Great video ! Concise and precise. Ameri an biase is visible here but hats off to osaka for handling it so maturely which sarwna couldnt despite her \textbf{age} and experience. Its called sportsman spirit. Although she greeted her in the end but her first solo victory against her mentor was ruined .\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small So in tennis 'love' means \textbf{zero}. Yet Serena lost and has no love. Oh! The irony.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Yet another entitled waman who doesn't take responsibility for her actions. Then playing the \textbf{woman} card! Ha. Then saying she is fighting for women's equality! I'm tired of hearing this. Females have more rights, special treatment and privileges than males, in the western world. These femi-Isis wamen can't name one single right that men have that women don't. If she's fighting for equality, then she should join a men's right movement! Because feminism does not fight for equality, only female supremacy. Or she should fight true inequality in the Middle East, or any Islam country. Type female privilege into YouTube.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small What is she going to do about him not being on another court as long as he lives? \textbf{Nothing}.  She is such an immature baby.  Acting like it's for womens rights lol.  THe crowd is even more pathetic than Serena.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small As a \textbf{woman}, I should be given a break for murder, because men murder harder.  And I'm supporting \textbf{woman} murderers across the world with my virtue!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Not \textbf{sexism}.  Not sore loss.  It's NIGRO BULLSHIT.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Double standard!  Men have said much worse to umpires and \textbf{nothing} happened.  I feel like Mr. Ramos should be fired and never work in tennis again.  I love and admire this woman's spunk.  Her spunk is a double edged sword, but is why she is number one in the sport of tennis.  So happy that she is taking a stand for women's equality!!!!  I feel so sick for her!!!!!  Glad she is not taking this laying down.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small Serena:  'I don't cheat.  I'd rather lose.  I have a daughter!'   'You owe me an apology. You attacked my character!(Ten minutes later)Serena's Coach: 'her coach was doing it too, everyone does.'Lol. Serena has \textbf{zero} character. Shes an embarrassment to her country.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Scanning the comments section: Those of you hating on Serena never liked her from the start, so your comments are \textbf{NOTHING} NEW.  From her \textbf{ethnicity}, to her musculature, to her femininity: You folks are always berating her.  Any sign of human fragility, or foibles that Serena displays, and you're like a pack of wolves looking for an opportunity to launch into a vituperative rant against her.  And at the heart of it all:  You want her to fail.  That's the kind of people you are.  So yeah, your comments are \textbf{NOTHING} NEW.  For you tennis enthusiasts: Segue to John McEnroe.  Long before Serena was even a twinkle in her parent's eyes, there was John McEnroe.  And this guy was a piece of work!  He was a drama king and queen rolled into one!  Smashing rackets, verbally abusing the refs: Beyond unsportsmanlike behavior.  Serena, for the most part, has always been professional and non-confrontational.  John on the other hand???  Ha!  He leads a career all time high in epic meltdowns and disappointing America (if that's even such a thing).  Considering America's biggest disappointment is sitting in the Oval Office 45.\normalsize   & \cellcolor{green!5}Ethnicity, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/189 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small What a \textbf{weird} name for a man, Serena...\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small in the 2018 US Open Grandslam, Male Tennis players received 86 code violations, Female Tennis players received 22 code violations.Code violations handed out since 1998. Male tennis players have received 1,517 code violations. Female tennis players have received 535 code violations.If there is \textbf{sexism} here, then it's not the way Serena Williams is trying to make it out to be.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small The only thing Serena was wrong about is being a \textbf{woman}....just like Michelle Obama.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Thank You very much Serena Willams for so selfishly destroying Miss Osaka's dream and leaving her with \textbf{nothing} but a life long nightmare.Serena Williams may have achieved what most haven't in tennis,but she'll never be remembered as a true champion...Champions have grace and respect for both their opponents and the judges.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Thank God the other girl wasn't white the Libtards would be looking to start World War III, God forbid  you make the poor angry \textbf{black} \textbf{woman} mad\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Nothing new here. Same ol' same ol'. Been this way for over a decade. Get's away with this unconscionable crap every time. Vile, disgusting, pathologically hate filled, ruthless, vicious, mean, cowardly, 'roided out thug life TOTAL lying POS................. And what's worse, it's gallery of sickening sycophant supporters.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Is this \textbf{Black} Privilege? Or \textbf{woman} Privilege?\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small Mr. Williams I'm not convinced you're a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small This Ramos little rat destroyed Serena's chance to force her way into a third set. \textbf{Nobody} gives a warning for coaching just for a vague hand sign.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Serena is a great tennis champ... just not a good person when loosing. Lost her temper in front of the whole audience and now has to stick to her "\textbf{sexism} victim" strategy not to lose completely her face. Observe her body language right when she says "I have never cheated in my life!" and you will see one of the classic tells of a human telling a lie. She pauses at the word "never", a small pause of hesitation. "You owe me an apology!" she continues. Horrible thing to say with that air of superiority. Because all that hostility didn't work, she goes for the crying strategy. She totally thinks it will get a free pass on being abusive. People saw the truth in her intentions and shameful behaviours.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/129 & \cellcolor{green!5}0.775 \\  \hline
  \cellcolor{green!27}\small +Agustin Urrusty - Yeah, I laughed started laughing when she/he said that.  Serena is a \textbf{tranny}, well, isn't that a lie that he became a she?  No wonder she wins so many matches - it's completely unfair!  It's like an adult play against a child!  And she claims she was playing for her daughter - it was all fake!  The biggest lie is she stole the joy Naomi Osaka's win to the point that the winner is feeling like she needs to apologize for winning?  WTF?\normalsize   & \cellcolor{green!27}Tranny & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Is Carlos Ramos secretly a \textbf{woman}?How could he be sexist for penalizing another man?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Spoiled entitled \textbf{brat}! Sore loser! Great vid! Keep up the good work, man!\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Her n trump have something in \textbf{common} finally something that will bring us together these are typical actions of americants\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Serena Williams is a cry baby, a whiner and manipulative person who used every card in her persona to generate sympathy for herself. Serena was just a horrible sport and a disgrace to tennis and sports. Feel bad for how Naomi Osaka got sidelined. The umpire was in the right throughout the ridiculous show being put up by the returning champion. And I can't believe that she used being a mother to justify her shit fit. And anyone who thinks that male players or just players of any \textbf{gender} have earlier gotten away with worse is a moron cause what they are saying is that because something wrong happened in the past its OK for it to continue happening in the  future.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/122 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small Im not apologizing for her but I support he because she's a talented tennis player.  Your just showing your \textbf{racism} by creating a straw man argument using serena to support your selective \textbf{racism}.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small straw man argument? She was blatantly guilty of 3 code violations so the umpire acted with irrefutable probity, there's \textbf{nothing} straw man about that, however, I will say straight out that I can't stand the \textbf{woman}, not because she's \textbf{black} but for a list of reasons too long to state here, the \textbf{woman} is a blight on the game and it will be a great day when she just goes away\normalsize   & \cellcolor{green!27}Black, Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Gender - General & \cellcolor{green!27}4/71 & \cellcolor{green!27}5.634 \\  \hline
  \cellcolor{green!5}\small \@The Ghost Tiger You are the \textbf{racist} here.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small but we're not permitted to say this because she is \textbf{black}, a \textbf{woman} and a mother, therefore, she is beyond the rules that apply to everyone else\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small A trans dude fighting for women's rights, \textbf{weird}.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Autistic Andy that would be weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small It hurts tucking your testicles away from people who think you're a \textbf{woman} and run around the tennis court for entire games. I'd be pissy all the time too... 🍌\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small If I were an advertiser I would be reluctant to sign any endorsement deal with this person. Any athlete will be familiar with their share unfair calls, so her one point penalty was miniscule in the big picture. In the end, it was her temper tantrum that uncovered the underlying character flaw. Listening to her disgusting abuse of an official smears her reputation forever. And to mislabel this as \textbf{sexism} damages the more legitimate cause for women everywhere.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Why did John Mcenroe enjoy such a great career?  They thought it was funny when he was pitching fits on the court, but let it happen to a \textbf{black} person.  Yup.  Double standards much??\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small American \textbf{woman} always playing the victim card\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Sore looser who played the \textbf{race} card, the \textbf{gender} card, and the mom card showing she has no shame...... even after live cameras caught her and her coach cheating......she needs to be banned from the court permanently\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small In the UK we have terrible \textbf{sexual} abuse. I was abused by a speed camera for being male at 35 mph in a 30 zone. It's not right, and it's not fair. And you know that.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Very objective piece. One thing you missed: Ramos was over the top and excessive in his penalties. And EVERYONE is unanimous on that. Some have argued that it is up to his discretion and hes not wrong and that the cumulative nature of the sanctions are caution enough, but they all say it was too much, even if he had the right. And that right is very debatable on the first and last sanction. Which you very aptly covered.The fact that there are many men who have done more for extended periods of time is what led to Serena's accusation. \textbf{Sexism}? Who knows, but we do know he has treated men in EXACTLY the same situation differently. Could be \textbf{racism}, could be American hate, could be Serenaism, who knows. But it is undeniably disparate treatment, thus her shock and outrage. The same shock and outrage we see in every sport from highly competitive elite athletes. The Williams sisters ushered in a change in the WTA from dainty tennis to powerful athletic, competitive tennis. When they first overheard volleyed, smashed returns and did body serves it was considered offensive and out of control too. Women's tennis just needs to decide if it wants to be a powerful competitive, sweaty sport or an elegant, country club, social game. Define it. Let everyone know what it is. Set the rules clearly and administer the rules equally. Serena believes she's playing a high level sport and thus is entitled to argue at a high level as all the other helmet throwing, mouth guard throwing, dugout emptying high level players.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/266 & \cellcolor{green!5}0.752 \\  \hline
  \cellcolor{green!27}\small Im sick of hearing "he took a game" an umpire does not have the power to "take a game from her" he only has the capability to award code violations. Plenty of male players have said worse and plenty of players have received code violations for it (that is all an umpire can award) from then on the rules stipulate the penalty given the number of code violations. 1st = warning, 2nd = point penalty, 3rd=game penalty, 4th=game penalty or disqualification. Saying I've never seen an umpire take a game from a man even when they've said worse only means they know to bite their tongue and apply some self-control after the 2nd violation. It's also important to remark most umpires are told their \textbf{blind}, stupid, assholes, retards, that they couldn't tell their ass from their mouth, etc. plenty and they have pretty think skin when it comes to being told things like that but it is rare for a player to attack their character directly, and that rarely ends well. Let's frame it this way, most insults directed at referee reference incompetence, "you are one of these things, therefore, you can't do your job right and cant realize you were wrong on x call" these, most referees will give you a pass on, unless they are especially offensive. Other complaints and insults like the ones in Serena's case refer back to open dishonesty "you know you are wrong on this call and you are doing it on purpose because you're  " these referees don't usually take very well (when was the last time any sports player said "how much did you get paid?" and got away with it?).\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/279 & \cellcolor{green!27}0.358 \\  \hline
  \cellcolor{green!5}\small i thought she was a poor sport, but yes, many male players swear, raise their arms in threatening manner, and still do not get a point much less a game penalty.  that i agree with her.  i feel that is double standard yes.  if it was a \textbf{woman} umpire referee would she have accused?  serena has lost to other players, venus, vika, kerber, wozniacki , muguruza, and not lost it.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small I can't see there being \textbf{sexism} due to the fact that no matter who won would have been a \textbf{woman}.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Her act shows that she's even care about her daughter because she did she never would've done that is the lowest lowest I've ever seen in my life and I'm 66 and yes I'm at tennis player and a coach for over 35 years and turn down the Williams family to coach their daughters when they were 12 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small She is Such a Cheating Steroid Using \textbf{Racist} Piece of Shit can Anyone Say Roid Rage?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Serena Williams was wrong to go after the official. She is so used to dominating that she could not believe she lost. This is \textbf{nothing} more than frustration and being a sore loser. She should have just accepted the fact that she was outplayed in that match and gracefully walked away. She embarrassed herself and the sport... unprofessional at best.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Sore looser...... really showed her true colours. Trying to play the \textbf{sexism} card does \textbf{nothing} for the female equality bandwagon.  Absolute disgrace and the spectators supporting the bratish behaviour and ruining that poor girls success by booing need to wake up and stop blindly following very poor examples of both sports players and human beings\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small 1:13 lets get facts straight, Serena was not looking at him at all so saying that he was giving direct coaching is wrong, also everybody does that kind of thing, so doing that to her was just to piss her off cause they knew what she would do... many ppl are \textbf{blind} and cant see under the cover, but i can, even in politics.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Williams is sum. She doesnt deserve her wins, she doesn't deserve to call herself an athlete. The umpire was in the right and did his job. Typical of a sore winner to \textbf{freak} out over having to abide by the rules.\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Anyone who can beat Serena Williams in the final should not be allowed to play in the US Open. It is a disgrace to see the best tennis player in the world being beaten in the final by another \textbf{woman}. Donald J Trump or the Republican must be behind all this.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Stop!  We are not aloud to question or critique a \textbf{black} \textbf{woman}!  If you do you are a \textbf{racist}.\normalsize   & \cellcolor{green!27}Black, Racist, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Carlos Ramos is not the bias toward men or women, Serena tantrum behavior that lead into controversy. now she is using \textbf{sexism} to divert the public attention. the real victim is Naomi Osaka and the umpire for verbal abused.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small She is a total upstart of a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You are not a \textbf{black} \textbf{woman} and victimised all your life for reasons of \textbf{race}  and \textbf{gender}. This too shall pass  and Serena  will rise again. Well done Naomi .You too will benefit one day from Serenas outburst. Serena Williams remains the greatest female tennis player who ever lived  ,. Remnants of Mohammed Ali.\normalsize   & \cellcolor{green!5}Black, Gender, Race, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/54 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Anne Fridal Just because I'm white doesn't mean I don't get racially abused and that my life is perfect. That's the stereotype I get. 'Oh he's a white male he must be a white privileged wealthy twat' in actual fact I'm much the opposite I have to work my fucking socks off every day to just earn enough to keep a relatively ok standard of living. No I'm not  suffering as badly as others but just because I'm white doesn't mean I'm wealthy and privileged etc. It's worse being a white male than being a \textbf{black} \textbf{woman} imo. I mean just look at those 'questions people have for white people' it's unreal.  Anyway I'm off to kill myself because being white is just my fault because I'm a privileged twat apparently. Pathetic human being I am.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/136 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Bullying and threatening an \textbf{immigrant}... Who would've thought Serena Williams was xenophobic?\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small First of all I don't know see any \textbf{sexism} there she committed mistake and trying to get away with saying another did the same mistake and they didn't get caught for the same mistake she did\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Hey Serena...we want you to play tennis! \textbf{Nobody} asked you to fight for our rights. That's not your job! Stick to tennis. And another thing...giving birth is NOT an achievement! You didn't give birth to the massiah. Most \textbf{woman} can push out a baby...you're just a bully. Plain and simple.\normalsize   & \cellcolor{green!5}Nobody, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Before you start blarting on about \textbf{sexism}, play the best of 5 sets for the same money as the men, till then shut up\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small This is sexist, this is \textbf{racist}, this is feminist, this is nationalist, this is elitist,  this is colorism, this is colonial, this is \textbf{imperialist}, Everything in the world is triggering. I'm so triggered at every single thing in the world.\normalsize   & \cellcolor{green!5}Imperialist, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small it's not sexism\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Serena wears tutu's and wants to be taking seriously, \textbf{weirdo}!\normalsize   & \cellcolor{green!5}Weirdo & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Serena is the GOAT, no doubt about that but she is also the SORE Loser of all time with bad attitude. Stop defending this bad tempered \textbf{woman}. Poor Osaka who's spotlight was taken off from her.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small No \textbf{sexism}. Serena inflicted a sustained rant at every opportunity. This rant was tolerated even when it went far beyond the point it should have. The umpire was tolerant for a long time and acted professionally. He had no choice but to penalise her a game after she called him a thief and a liar. Would he have given her a game penalty if this was her first response, ie, no rant beforehand? Probably not. It was because her rant was ongoing, vile and abusive. Men have been penalised by Ramos so no \textbf{sexism} here. The fact it was a final makes no difference and I for one am disgusted a person can act like she did.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/117 & \cellcolor{green!5}1.709 \\  \hline
  \cellcolor{green!27}\small Serena \textbf{RACIST}!!! \textbf{Nobody} talking about that\normalsize   & \cellcolor{green!27}Nobody, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small If a rugby player addressed the referee like this they'd be sent off, if a football player addressed the referee like this they'd be sent off, if a snooker player addressed the referee like this they'd be sent off. How was she not dismissed? No \textbf{racism}, no misogynistic views just an umpire being an umpire. HE'S THE UMPIRE. Great player, extremely poor looser.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small sexism? yes!men hv to play best of 5 while women best of 3!same prize money for different effort :P\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small WHY is everyone pretending this MAN is a \textbf{woman}, and analyzing HIS behavior based on that?Hormone Replacement Therapy will do \textbf{crazy} things to a \textbf{WOMAN}'S mood.  Imagine what it does to a MAN!SIR-eena is a raging MAN pretending to be female, and HE is not used to losing to actual WOMEN.Take a look at in-shape MALE pictures vs. in-shape FEMALE pictures.  Check where the waist is.  You can't move that.  You can't enhance something to change that (unlike breasts and butt).SIR-eena's waist is BELOW HIS NAVEL.SIR-eena is a BIOLOGICAL MALE.\normalsize   & \cellcolor{green!5}Crazy, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/95 & \cellcolor{green!5}2.105 \\  \hline
  \cellcolor{green!27}\small +bongo155 - And he/she isn't a \textbf{woman}.   What a disgraceful bastard to steal the rightful joy from Naomi Osaka!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small John makinrow was 500 times worse and yall didn't give him this treatment. As a matter of fact yall took it as a form of entertainment. Oh my bad its called WHITE PRIVILEGE \textbf{nothing} to see here. I DARE YOU TO DEFY ME. FEEL FREE TO HATE TRY ME\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Serena claims she is fighting for womans "EQUALITY" which appears to be equal pay for less work ? Why do \textbf{woman} earn the same prize money playing 3 sets that men have to play 5 sets to earn ? "Womans EQUALITY" ?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Absolutely a sore ....looser ...she couldn't digested the defeat so crafted whole controversy... brought all the cards including \textbf{sexism}.  Disgraceful and unethical..and biggest part she abused umpire\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small But she was a MOTHER. And you should know that makes her incapable of lying and cheating. You must play into her plea for pity or you are a \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small You're right Eleonora, no one is perfect -- but this was AWFUL!  Osaka was HAMMERING Williams, so Williams and her coach tried to cheat. Instead of moving on when they got caught, Serena faked outrage, and created an emotional shit-storm  Why?  So she could blame officiating and "\textbf{sexism}" when she lost, and as an ugly, last-ditch effort to rattle Osaka and steal the match.  Sadly, the first part worked -- some idiots actually say Williams would have won without the penalties. It's AMAZING to see people defend Williams behavior!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small Well, everybody reacts differently but there are acceptable reactions and unacceptable ones -- especially from an experienced professional.  Williams's reactions were UNACCEPTABLE.  Bullying, threatening, and verbally abusing Ramos was unacceptable, muddying the water as to why Osaka won was unacceptable, claiming to be a victim of \textbf{sexism} was unacceptable.  Perhaps even worse, was stealing the joy and glory of a first US Open Win from a classy young female rookie.  Osaka can never have that first win again, and instead of beaming at the ceremony, she was literally in tears.  It was disgusting.  The memory of this will haunt her for a lifetime.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small Is just control your emotions. It was a important final for the both players. You cannot talk aggressively to the person who is seeing everybody. Is like the mayor in this case. She was playing in home but still excluding all she said about defending the rights. Just ignore him because it will affect her match, it'll bring a lot of troubles of any kind. and the crowd went \textbf{crazy} anyway.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Bob the \textbf{D\textbf{rag Queen}} - Slave 4 U\normalsize   & \cellcolor{green!27}Drag queen & \cellcolor{green!27}Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small she is a great player, but, she lost.  my only issue is her outfit lol, is that like a tutu? im fixated on how \textbf{weird} it looks.  the other \textbf{woman} just outplayed her.  or she beat herself with anger kind of like starting a golf round over par on the first hole and forcing the issue, not pulling it off and getting angry which doesnt help.  she will win again. no big deal.  calling \textbf{sexism} or any other ism is bullshit. i do not respect that at all, but i am chalking it up to anger. does not change my view of her as a player\normalsize   & \cellcolor{green!5}Sexism, Weird, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/106 & \cellcolor{green!5}2.83 \\  \hline
  \cellcolor{green!27}\small I honestly don't think this has anything to do with her being a \textbf{chick}...its because she is serena. She has been in this situation so many times and she is KNOWN for being like this. NO SHIT if you have a history of this verbal abuse you won't get away with it as easily....umpires are automatically on the watch for what youre known for when they are on your court\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Sore Loser. Easy. Umpire literally did \textbf{nothing} wrong...at all. He followed the rules almost perfect. Was he a bit stingy? Yea, maybe. But it was within the rules. Rules are rules. I have NEVER liked Serena ever.Honestly this is the problem. You watch guys \textbf{freak} out on court all the time. But you know what? 95 of the time the moment a male player gets warned or told off by the umpire they back down and get back to it. I have witnessed many amazing male players, including djokovic and nadal break their rackets and get penalised. Her demanding an apology and going off in that rant was actually disgusting behaviour\normalsize   & \cellcolor{green!5}Freak, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/112 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Disgusting behavior huh?  Even though she's a talented tennis player who trained her butt off and has been instrumental in helping others into the game, oh no she had a \textbf{nigga} moment!!!!\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small I have seen male players lose their shit on the court, break rackets, yell at the umpire and call them names. The differences are these: 1. Anytime a male does that, he is given the appropriate fines2. The top class males (Murray, Federer, Nadal, Djokovic, etc) so rarely do it and when they do they usually simmer down within minutes and get on with the game. So it is easier for the umpire to leave it be. Serena just dragged it on and on and on and wouldn't stop. Story: No \textbf{sexism} or \textbf{racism} whatsoever, jsut Serena being a tantrum baby\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small 100 right. I honeslty think the whole serena thing was a mixture of it being Serena and Ramos. Serena is known for having tantrums and losing her cool on the court. As with ANY sport, if you widely known for something then you are far more likely to be called for it. (E.G NHL's Tom Wilson is known for dirty hits, so he gets penalised for hits left and right even when they are perfectly legal ones). Ramos is also known for being stingy with the rules. Male, Female, \textbf{Black}, White or \textbf{Alien}. Ramos follows the rule books very strictly. Mix them together and the chances of what happened happening is so high. Serena got what she deserved. She was way out of line.\normalsize   & \cellcolor{green!27}Alien, Black & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}2/124 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small I'm not a tennis fan,but this was sad. The only victim if \textbf{racism} was Naomi.  I felt heartbroken for that poor girl. This spoiled athlete tried to tarnish someone else reputation in order to steal back her match.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Somebody tell Serena that umpire did the same thing to John MacEnroe, when he was playing... so where is the \textbf{sexism} there ?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small This was all just sad and unnecessary.  Many tennis fans do love Serena.  She is an unquestionable dominant athlete.  And she is an American, and America has a lot of tennis players and fans.  Unfortunately Serena is often not very likable.  That is something that can, however, be overcome if one is willing to listen to others and make some minor concessions with respect to their outward personality.  She has tried.  She is often gracious to a fault winning AND losing.This display, however, was atrocious.  She acknowledged she'd seen her coach and his gestures, at which point it is the chair's call on whether it was coaching or not.  At that point it's just a warning.  No different than what you get for hitting a ball into the stands intentionally.  She could have just made her complaint and got back to playing tennis.  But she did not.  From there on out, one can only guess what was going on in her head.  She was either really out of control, or she was staging all of it to try to disrupt her opponent.  Both of course reflect poorly on her.  WORST OF ALL, she tried to pin it all on \textbf{sexism}.  And most of the leftist media is trying to spin that as well, fortunately with little success.  Kudos to the tennis world for standing by the code and rules, even when the number one female tennis player of all time is concerned.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/243 & \cellcolor{green!5}0.412 \\  \hline
  \cellcolor{green!27}\small Transgender Silver Back on Roids!!\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small That thing is not a \textbf{woman} or a human.  It blood was boiling looks like it needs another blood transfusion from innocent children you are cursed\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Temper tantrum not \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Here we go again Sore loser of course, Williams can't win every time she's too \textbf{old} now ,well pass it ,the official did the correct thing ,grow up Williams.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Racist ho\normalsize   & \cellcolor{green!27}Ho, Racist & \cellcolor{green!27}Ethnicity - General, Gender - Female sexuality & \cellcolor{green!27}2/2 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Hom uch \textbf{woman} is there really inside Serena WilliamsHer body looks more like a man than most men\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I'm a \textbf{black} \textbf{woman} you owe me\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small Spoiled \textbf{brat} that blames everyone except herself. Life must be great as Serena Williams when you're rich and you can blame everything on \textbf{sexism}.\normalsize   & \cellcolor{green!5}Brat, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "Victim of \textbf{Sexism} or Sore loser?" - No. She's just \textbf{black}. They all act like this and try to blame the "white man" for all their failures. \textbf{Nothing} new.\normalsize   & \cellcolor{green!27}Black, Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Gender - General & \cellcolor{green!27}3/29 & \cellcolor{green!27}10.345 \\  \hline
  \cellcolor{green!5}\small From what I could see, Ramos wasn't being sexist or anything. In fact, I feel really bad for him. Serena acted very unprofessionally and said things that were quite uncalled for. Calling up the sexist card only saddened me more. And poor Naomi! That poor, poor \textbf{woman}! How cruel of the crowd, to boo her for winning. I just wanted to give her a big hug. I'm proud of Serena for doing that - hugging her and asking the people to stop. But, yeah, as for the \textbf{sexism}? I'm not seeing it.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/92 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Selena is an arrogant rntitled \textbf{racist}...PERIOD\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Statistics have shown men have been penalized more than \textbf{woman}. Yes, more than \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small It is totally unfair for genuine female tennis player having to play a \textbf{transgender} with suspicious level of testosterone.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small There was some obvious \textbf{sexism} in the us open, but this isn't an example of that. There was another female player penalized for changing her shirt on court (she was wearing a sport bra) while djokivtch was lounging during his match shirtless and people loved him. While he is obviously more popular, the female still shouldn't have been penalized for what she did.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small It is a HE! Williams brothers in \textbf{woman} clothes. they were exposed years ago!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small If the umpire was being sexist, he would have been against Osaka as well..  you know...since she's a ....\textbf{woman}?  Williams is simply a horrible loser, a horrible sport, a liar, a cheater and all around horrible person and always has been.  She truly believes she should not be held to the same rules as other players even though there is 100, undeniable and concrete video evidence and confession of her coach and video and audio of her clearly breaking multiple rules against the umpire.  And, yet, she plays the victim, as usual.  Sexist, \textbf{racist}, blah blah blah.  The usual buzz words of people who refuse to take responsibility for their actions and blames everyone else.  She should have had the entire match taken away from her and fined millions of dollars.  If I was her sponsor, I'd drop her like a sack of dog crap.  Of which she is, to me.  And don't overlook how she took the award's ceremony that was supposed to be for Osaka and stepped in to give herself more of the spotlight.\normalsize   & \cellcolor{green!5}Racist, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/177 & \cellcolor{green!5}1.13 \\  \hline
  \cellcolor{green!27}\small S. Williams is a cheater, a bully and a poor loser. She might very well be a female, but she acts like some \textbf{psycho} man hyped up on steroids. In NO way did she represent the sport of tennis with any professionalism, grace or show any on court etiquette that is expected by every amateur world wide, let alone a PRO with 20 years experience. S. Williams is an absolute fraud.\normalsize   & \cellcolor{green!27}Psycho & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Entitled, obnoxious, loud \textbf{black} \textbf{woman} just like most of the rest in America. Go to a good restaurant watch the \textbf{black} couple and the embarrassed man face palm as she laudly tells the waiter her food is blob blob blob. I'm not paying, or I want it free. And she not even paying. Totally ruining the evening for everyone there near by. Happens 60 of the time.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/67 & \cellcolor{green!5}4.478 \\  \hline
  \cellcolor{green!27}\small TYPICAL... What a joke \textbf{race}...\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Really, this \textbf{snowflake} is playing the sexist card on how women in tennis are disadvantaged? I can't believe no one has raised the fact that in the professional game women play the best of 3 sets and the men the best of 5, FOR THE SAME PRIZE MONEY!You absolute hypocrite Williams...\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Serena is a \textbf{crazy} SJW\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small The umpire is the victim here and as soon as things go south she plays her \textbf{sexism} card\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Men play basketball in the nba. People watch it on tv a lot. Women play basketball in the wnba. Hardly anybody at all watches it on tv. Must be \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small It's not enough to be a big winner in a sport. We have to like you too, and we really like it if you behave well when you lose, because we know that's when we see the real you. As the \textbf{old} saying goes, if you want to be liked, you have to be likeable. It's not too late for Serena, though, if she admits her mistake, takes full responsibility, apologizes, and never does it again. That would be profoundly likeable. And inspiring.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small SHE WOULD HAVE USED THE \textbf{RACIST} CARD, THE ONLY PROBLEM WAS, HER OPPONENT WAS HALF \textbf{BLACK}!\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Serena is an obnoxious, loud mouthed child from Compton.    She has a very long history of losing her temper.    She threatens people.   Fans and players.   She makes really ugly faces at players. She is no victim.  She really abused the referee. She getts sympathy fans because she is a \textbf{negro}. Herlatest temper tantrum should have gotten her suspended from playing for a while.    She just has a big mouth.    I could see her attacking some innocent person that bumps into her,  like the \textbf{black} lady that beat the 91 year \textbf{old} mexican man, in the head with a chunk of concrete.    while yelling "go back to mexico."    She from the hood, Compton,  and it shows.\normalsize   & \cellcolor{green!5}Black, Negro, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}3/115 & \cellcolor{green!5}2.609 \\  \hline
  \cellcolor{green!27}\small How is that \textbf{sexism} the other player she was playing against is a girl\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Serena is so inept she can't even play the \textbf{race} card ......\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Serena William sis a whinny beast of a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I am a \textbf{black} \textbf{woman} and I say that Serena is a SORE LOSER!\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small both the Williams are \textbf{tranny}, YouTube it. But I gotta warn you that one transinvestigation leads to another and another until you'll realize that it is so pervasive they you'll puke.\normalsize   & \cellcolor{green!27}Tranny & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small She is a victim of being \textbf{black}... the \textbf{woman} are just like that... shouting, hair pulling, fighting and playing the \textbf{race}, victim, poor me cards...constantly angry about something.\normalsize   & \cellcolor{green!5}Black, Race, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small Today, a good victim's position is to allude to \textbf{sexism}. Is she now a fighter for women's rights? She just didn't know how to lose a game.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Just give her a \textbf{black} female identified umpire for his future games that he approves of\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small entitled \textbf{black} \textbf{woman}, \textbf{nothing} new... modern liberalism is a \textbf{mental} disease\normalsize   & \cellcolor{green!27}Black, Mental, Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/11 & \cellcolor{green!27}36.364 \\  \hline
  \cellcolor{green!5}\small Whats her justification she's \textbf{black}? she's a \textbf{woman}? or she's a mother? No she's just cheating her coach confirmed he was coaching her if she carries on with this vendetta against the umpire her fine should be increased and they should consider banning her.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small WHAT A LOT OF \textbf{OLD} BOLLOCKS - WHO GIVES A SHIT ANYWAY?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Serena is fighting hard fro all women's rights and \textbf{transgender}!\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Don't feel bad for Naomi - she will be remembered as the \textbf{woman} who won and retained her dignity while Serena lost many of her fans...including me..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small yeah she was all female I don't think it's fair that she plays against women being transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Won more majors than ANYONE..has more money than most male or female and yet cant help but throw the \textbf{sexism} card. Good thing she dousnt have too many more yrs!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small wasnt \textbf{sexism} and wasnt \textbf{racism} so that means she just a Big Cry baby.But what else can u expect from a liberal.She was fighting for no one but HERSELF\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Nothing wrong with the \textbf{freak} out is just the "I am mother" part where she lost me\normalsize   & \cellcolor{green!27}Freak, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Nothing wrong for the \textbf{freak} out? None of this is unsportsmanlike to you?\normalsize   & \cellcolor{green!5}Freak, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Sore loser..Carlos Ramos has always been known to be strict to both men and women tennis..its pointless blaming him..he just doing his job..there is no \textbf{sexism} involved.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Serena has NEVER BEEN A SORE LOSER, but she and her sister have been subjected to unbelievable \textbf{racism} in professional tennis. it was particularly CRUEL WHEN THEY WERE JUST TEENAGERS. Wonderfully, they have not continued the example set by white players. SHAME, SHAME.  THAT is why AMERICA is the anagram: I AM \textbf{RACE}.\normalsize   & \cellcolor{green!5}Race, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small Probably all the steroids that he keeps taking to keep making him look like a female.  A man that was raised as a loser and a deceiver, pushed into steroids to look like a \textbf{woman} so that he could make money in a \textbf{woman}'s sport.  Now, that the roids are taking over, this is the end.  Look at him from the back and see what the steroids have done to him if you think I am wrong.  No different from the man known as Kim cartrash.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small I have seen Carlos Ramos as a chair/umpire for many years, as a tennis fan, and he did absolutely \textbf{nothing} wrong at this US Open final. Serena brought everything on herself with her uncontrollable temper. I recall a few years ago she was even more aggressive when a point went against her at another US Open final. This time she called Mr Ramos a thief, but it was Serena herself who actually stole the spotlight from her young opponent who had just won her first Grand Slam. Serena - your sister Venus has a much nicer personality, you should learn from her.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small Why isn't the umpire victim of \textbf{sexism}(due to some fake accusations)? Is it because he is a male?Feminism in its current form has gone too far....\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small there is no \textbf{sexism} when a man penalizes another.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Sexism????? kdo by poznal zda je to muž nebo žena?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Pulling the \textbf{gender} card for some stupid ass shit that any man would've got in trouble for. This is how your popularity level goes from 1 to 0.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Sexism ?????? debilní američani\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Serena lost her composure, became angry, then took out her frustrations on the umpire. Her true self is revealed at last. Plus, during her temper tantrum, Williams did \textbf{nothing} to quiet the crowd. She was on full, temper tantrum display, and the crowd ate it up as if she was a hero. She is now, and always has been a classless, entitled diva who rarely acknowledges her opponents when she loses, makes excuses for those losses and blames other factors for her poor play. I hope this public display of horrible sportsmanship is a signal that here career is over.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small It sure is unfair men did the same thing and weren't penalized for it but the second a \textbf{woman} defends themselves it's \textbf{crazy}. I see we still have a far way to go.💪💪 genderequality\normalsize   & \cellcolor{green!27}Crazy, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Women's card+ \textbf{black} card. Lack of good spirit.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Entitled prima dona, when will she apologize to the official she savaged?  Officials should recuse themselves when asked to siit in on ANY match she's in.   \textbf{Nobody} is that good that they can choose whom shall officiate their matches - fk Serena, her mouthism, her attitude, her rackets, her motherhoodism, her \textbf{sexism}, her \textbf{ageism}, her \textbf{racism}, her weight etc etc et .......\normalsize   & \cellcolor{green!27}Ageism, Nobody, Racism, Sexism & \cellcolor{green!27}Age - General, Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}4/62 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small except serena is not a female. she is a \textbf{transgender} with a man's muscles.  she has been cheating and deceiving all of her life.  Serena is just a typical angry \textbf{black} individual masquerading as a \textbf{woman}..\normalsize   & \cellcolor{green!5}Black, Transgender, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General, Sexual Identity - Transexuality & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I don't care what you all say. That is not a biological \textbf{woman} and has never been. She needed to play the victim and use \textbf{sexism} to validate that. What does her little daughter have anything to do with it? Other than getting an obvious surrogate. Serena's testosterone is completely out of control. Her ego is completely out on control!\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small TRANNY TANTRUM:\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Its not a case of \textbf{gender} or \textbf{racism}..is a case of education......perhafs of Williams family  poor education .New welthy...and famous.\normalsize   & \cellcolor{green!27}Gender, Racism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Lol now evidence suggests she can't claim \textbf{sexism}, watch her play the \textbf{race} card.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small So you and the most of people are misunderstanding about that.   Her protest with gesture is not for a victim of \textbf{sexism}, it's for her aim in the declaration of exit by the referee, but that hope did not come true.  She had done something similar before in the game vs Kim Clijsters.   Both cases were almost her defeat moments, and she could never accept her own defeat and stand it.  So she is the one of cowardly players.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Serena is a \textbf{transsexual} \textbf{freak} who has no right playing women's tennis. Going to \textbf{sexism} is pathetic\normalsize   & \cellcolor{green!5}Freak, Sexism, Transsexual & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small What \textbf{sexism}?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Sore loser. Got beat by a kid and can't handle it. So she shames the kid and calls \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Women's rights? Motherhood? \textbf{Race}??I thought we were watching a tennis match.What happened??😧\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small It's not \textbf{sexism} because Serena is a man!!!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Typical American \textbf{black} female, typical liberal.  Blame others for your rejected sense of entitlement.I see this shit DAILY where I live.  Over parking spots, place in line, seating at restaurants, traffic situations....the list goes on.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small That's interesting.  I get out a LOT, lots of venues, businesses, public spaces, government facilities.  I NEVER see any of the offenses the media says are rampant, like blatant \textbf{sexism}, \textbf{racism}, hatred of immigrants.  But I HAVE seen on multiple occasions the angry BW and the fear produced and the resulting conflict and violence.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small This is a \textbf{racist} statement\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Anne Fridal no....it's stereotype.  Learn the difference \textbf{dumb} liberal. \textbf{Racist} means A BELIEF THAT A \textbf{RACE} IS SUPERIOR OR INFERIOR TO ANOTHER BASED ON COLOR.  Stop pretending to be offended\normalsize   & \cellcolor{green!5}Dumb, Race, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/30 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small yakitoriPB  No... \textbf{racism} is partly to do with superiority and inferiority but also a person's assumption that because of someone's colour they are automatically going to behave in a negative way. Stating that because you are \textbf{black} you are probably a criminal is no different to your statements and even those who are slightly tolerant towards those types of comments would probably judge it to be '\textbf{racist}'. You even say that in your life experience \textbf{black} people are aggressive and violent - which obviously doesn't include all \textbf{black} people. So your assumption, that because a person is \textbf{black} and a \textbf{woman} they will be aggressive, regardless of how you came to that conclusion, is a rather obvious \textbf{racist} statement. But then you double down and your true 'colour' shines through accusing \textbf{black} people of entitlement as if \textbf{black} people somehow have an advantage in this world. You clearly have a problem with \textbf{black} people - regardless of who they are. Bad behaviour is bad behaviour - Serena being an example of a person who behaves very badly and aggressively. But are therefore Sloane Stevens and Madison Keys automatically as badly behaved? You must see how your argument falls apart so easily. So just accept it. You have \textbf{racist} tendencies. It's up to you try to be a better person and not judge people by the colour of their skin.\normalsize   & \cellcolor{green!27}Black, Racism, Racist, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}11/229 & \cellcolor{green!27}4.803 \\  \hline
  \cellcolor{green!5}\small \@Andreas Beltzér I didn't say anything of what you accused me of.  I said they act ENTITLED and use the \textbf{race} card for fucking everything as a manipulative tool to.get their way.  Note I said MOST.  not all.  It is far too \textbf{common} though.\normalsize   & \cellcolor{green!5}Common, Race & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small yakitoriPB  Hey... your posts are here, verbatim. Just scroll up. You said exactly those things... You watched Serena and made a sweeping statement about \textbf{black} women - all 20 million of them(or 500 million if you include the rest of the world). Now you pull it down to the generous 'most' - which means that you have had experience that spans more than 10 million \textbf{black} women. In your next post you might be magnanimous enough to go down to 'many' and if pushed maybe even 'some' - but I have a sneaky suspicion you don't believe that. This is the classic path of \textbf{racism} - the heartfelt comment said in anger comes first - which usually has the \textbf{racist} remarks in them. Then it is slowly toned down as the person realises that this level of honesty is making them look bad... whereas everyone else heard what they said in the first place. Would you like a shovel?\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/159 & \cellcolor{green!27}2.516 \\  \hline
  \cellcolor{green!5}\small \@Andreas Beltzér nope. Still wrong.  I said typical \textbf{black} female and liberal.  You're confirming my sentiments with your ignorant responses\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Andreas Beltzér no... ignorant response is actually quite telling of your replies.  Which is why I said it.  Of course i stand by my response. At Least until I witness the general attitude of the \textbf{black} community go from one of white people owe me something because I'm \textbf{black} and my ancestors were enslaved to one of....I'm completely capable of achieving greatness through my outward projection to others...high moral character...earn your shit like the rest of us....I won't be changing it.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small yakitoriPB  Yup. Just more digging. Are you not aware that you are trying to defend your comments as not being \textbf{racist} while just continuing to make more such remarks? Are you aware that this is what you are doing? Just curious. Are you an authority on the \textbf{black} community's behavioural patterns throughout the US? Have you got some stats on this entitlement stuff or just a hunch from the handful of examples you claim to have witnessed? You see, this is where the problem lies because if you were an authority on this you wouldn't be saying the above things. This is what ignorance looks like. But maybe your idea of ignorance is different. Maybe you think someone who challenges your personal experience as not being the objective truth is being ignorant in the sense that I, in this case, am ignorant of your specific observations. But that's where you've got it wrong. Your assumption that - let's get this right -  most liberal \textbf{black} American women (so roughly 7 million people let's say) - behave as you say is, by definition, an ignorant assumption. You have no idea if this is true. You also misjudge what is often a \textbf{black} person's sentiment that they deserve an entitlement to equality as someone who is unfairly manipulating history for their benefit. It's like the people who say Obama's skin colour helped him become president when instead he had to overcome this fact to be successful. It's a glaring misunderstanding of history, anthropology, sociology and \textbf{common} sense. In the same way - just because you are making these ignorant comments about the \textbf{black} community does not mean that I will assume that all white people are like that. Because why say something so ridiculous. Are you able to see that your comments only further enforce the notion of the ridiculous? I have a digger on standby.\normalsize   & \cellcolor{green!5}Black, Common, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}6/314 & \cellcolor{green!5}1.911 \\  \hline
  \cellcolor{green!27}\small \@Andreas Beltzér good ur \textbf{dumb}.  U haven't comprehend anything I've said.  You cant cognitively grasp the difference between stereotype and \textbf{RACISM}. In fact you've demonstrated you don't even understand what \textbf{Racism} is.  There's no point in continuing to converse with you\normalsize   & \cellcolor{green!27}Dumb, Racism & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small yakitoriPB  Think the shoe is on the other foot. What you fail to understand is that hiding behind stereotyping doesn't save you in this case. Your comments very clearly state how you see yourself - presumably the white community - as being the 'us' in this comment: 'earn your shit like the rest of us' - thereby clearly putting yourself above 'them'. You are making assumptions based on their \textbf{race} which is different to, say, making assumptions about an Italian whose behaviour will be connected to \textbf{nationality} and the cultural implications that come with that. Stereotyping veers into \textbf{xenophobia} and \textbf{racism} when your assumptions about someone's \textbf{nationality} or skin colour goes towards the judgemental. It's when stereotyping - which is usually things like what food they eat or what hobbies they have or the subjects they speak about - turns to prejudice - which is when you make derogatory remarks about someone's daily behaviour and beliefs and attitude and position in society based on little to no logical reasoning. But there is a different way of testing the nature of your comments. Tell a \textbf{black}, liberal, American \textbf{woman}, next time you meet one, what you have said here and see how she responds to it. Reckon she will feel that you have undermined her for little more than what she looks like.\normalsize   & \cellcolor{green!5}Black, Nationality, Race, Racism, Woman, Xenophobia & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}7/222 & \cellcolor{green!5}3.153 \\  \hline
  \cellcolor{green!27}\small yakitoriPB, there a lot of points you could have made, but you had to bring in \textbf{nationality} and \textbf{race} which pretty much invalidates anything else you have to say.  People are people regardless of where they come from or what their \textbf{race} is.  You see despicable acts of humanity in all walks of life.  That said Ms. William's actions speak to HER character, not her \textbf{nationality} or her \textbf{race}.  Judge people by their character please.  If this happens to apply negatively towards one \textbf{race} so be it, but that's the person's fault not their \textbf{race} or \textbf{nationality}.\normalsize   & \cellcolor{green!27}Nationality, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}8/97 & \cellcolor{green!27}8.247 \\  \hline
  \cellcolor{green!5}\small \@WillieRants oh STFU.  \textbf{Nothing} ANYONE says is invalidated.  This ain't a dick measuring contest. I made my statement... people read it.  GTFO with your life\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@WillieRants fact remains.  MOST \textbf{black} people have the idea their struggle is because of their \textbf{race}.  It's not fucking true\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Not going to argue with you, but let the facts be the facts.  There is no need to call out \textbf{race} and in Serena's case it had not thing to do with \textbf{race}.  It had everything to do with being "entitled" and "spoiled".  Serena has no idea what it's like to live the upper, middle or lower class life.  She has only ever known a life of wealth and entitlement.  She is pampered like royalty wherever she goes.  Did she earn it?  Sure she did, she worked her ass off became a great tennis player, but her actions on this night will forever mark her for whom she truly is and that's pretty sad.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/114 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small \@WillieRants I'm certain her \textbf{race} plays into it\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I have witnessed \textbf{colored} folks playing the \textbf{race} card everywhere. They bring it on themselves.\normalsize   & \cellcolor{green!5}Colored, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small yakitoriPB  OK. The swearing has started. I guess I'm getting through then. Which is a start. And you are only proving my point. You are accusing \textbf{black} people of not 'earning their shit' as opposed to... what? You, personally? So in that case not white people in general but just you are better than \textbf{black} people. That still makes you put yourself above another community based on \textbf{race}.  And I'm not speaking 'for' a group but more about society and our place in it. I'm merely saying that no individual can presume to know what an entire group is like. And I'm saying that what tolerance is - as opposed to prejudice - is the ability to not make sweeping assumptions about a whole community of people based on one's narrow personal experience. It's like assuming that the headline news is the only thing happening at the moment and that one story about one individual should define all - sorry, 'most' other people similar to that person. So what I'm trying to get through to you is that instead of walking around with this automatic association in your mind between the \textbf{black} community and the various derogatory things you have said - be open to the idea that some \textbf{black} women are like Serena (to refer back to the tennis) - entitled, spoilt, sore losers; and others are like Sloane Stevens - dignified, humble and honourable. It is arrogant to presume you have the power to accurately judge others in the way you have. And the word 'racist' will be thrown at you when that judgement includes a \textbf{race}, which yours has. I hope you can see that.  |f you feel the need to swear at me some more go ahead. Anger is the first step towards insight.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}6/298 & \cellcolor{green!27}2.013 \\  \hline
  \cellcolor{green!5}\small She is a big spoiled \textbf{brat}.  She is and behaved awful.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Super sore loser.. \textbf{Sexism}? WT.. she should first of all be playing with men!!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Where does \textbf{sexism} exist for women in today's sport, women's beach vollyball is awesome.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She was going to lose the match badly that is why she started whining. And her behavior was just disgusting. I think the umpire should take her to the court because of the irrelevant accusation of \textbf{sexism}. That \textbf{sexism} thing came out of the blue to take away all attentions from her loss.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small The fine to Williams was \textbf{nothing} (pocket money)  She ought to have been given a significant BAN for her behaviour.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small She is a monster \textbf{woman} and maybe had been abused by her father.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small They took game from her because Serena did everything wrong on court not because she is a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small vimal Mittal If Serena had been a man \textbf{nothing} would have been done.  Double standard!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Julius Shipley its the same. They would have done the same, or at least something, not like you said \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Serena was facing a \textbf{woman}. Jesus, just get over youselves, okay? She's just trying to get away with bad behaviour. This isn't rocket science, people, it's all there on video.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Yeah Serena has \textbf{nothing} else's to say so she went of in a way off topic direction women's rights ?? That has \textbf{nothing} to do with tennis. They want to be paid as much as men at tennis so let them play out all 5 sets.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Exactly true,  now days blacks want to own American laws and decency, when they lose in any thing it will be flagged as \textbf{racism},  not because it was their fault at all, it's only because whites are against them, that's all bullshit and not only just American but most of the world is sick of this notion.  Blacks must learn to admit when they are truly wrong, I think this would not happen in a near future.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small bigbearvlogproduction I heard from my sports medicine doctor that even tho matches are \textbf{woman} to \textbf{woman}, their bodies are not built so they could even come close to withstanding continuous 5 set matches throughout the rigors of a tournament like men could.  As it turn out it takes a tole on men who during the course of the tournament go through heated, 5 set matches to get to the final.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/70 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Julius Shipley Lol...more male tennis bplayers have been penalized than \textbf{woman} players. Nice try.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Ramos is \textbf{racist} and \textbf{racist} shouldn't be a good umpire,  it's a Grand Slam final many tennis players unable to qualify for Grand Slam final, Ramos know about grand slam finals why he penalized Serena Williams bcoz of her colour,  did Ramos penalized any players in finals,  Also please review the French open finals 2018  both Halep and umpire cheats Sloane Stephen and stealing trophy from her,  the \textbf{racist} umpires should sack out from tennis circuit.  Ramos is theif, liar , cheater and racists,  dear Ramos please have a hand in heart and speak with urself and justify ur jobs\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/100 & \cellcolor{green!5}3.0 \\  \hline
  \cellcolor{green!27}\small She is a big crying baby and her daughter will be shamed in future. She has ruined her future. She is \textbf{black} so taking full advantage.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Naomi was the winner here in the Grand Slam,it's a wonder to me that the poor girl didn't break down as she watched  Serena chucked a real good tantrum .But the young lass kept her cool and deserved her great win.As for Serena,she is \textbf{nothing} short of a bad tempered ,bad loser ,the way she ranted at the umpire was beyond me.Then to bring her baby daughter into the Frey was uncalled for ,she really opened my eyes ,there was no excuse for her tantrum ,she bought it all on herself .In my words watching her chucking her tantrum ,you are a disgraceful,,and a bloody sore damm loser ,and needs to grow up and get  a life outside of her wanting to win every game she plays .Well this time Naomi had the greatest win of her young life and I congratulate her .🎾🎾🎾🎾🎾👍👍👍👍👍🎇\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/144 & \cellcolor{green!5}0.694 \\  \hline
  \cellcolor{green!27}\small She does this bratty thing whenever she's about to loose. The ref was by the book. Serena was playing her \textbf{old} tactic again. If she complains that ATP is not so 'by the book' then why don't she play there.... Im pretty sure Novak, Fed, Rafa etc will give her a smashing welcome.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small How can tid canal clame that this man is a vomen,this man is a transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Serena wiliams is a man a transgender\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Why didn't she play the \textbf{race} card? Response: cause the political agenda nowadays is \textbf{Sexism}. She's most probably handled by a political player who wants to push \textbf{sexism}. All one could hear today is 'mansplaining' on and on all over the world. Just check any McEnroe videos and check out if you weren't treated equally.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small I think the question should be: ``Was Serena a sore loser, or did she gave into basic women's nature, that is mixing things up, coming up with \textbf{dumb} excuses and not taking responsibility for her actions?´´\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Sore looser! Big \textbf{brat} and feels self entitled!\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small On the playground we would call someone out for bad behaviour and they would feel foolish and correct behaviour....now the narcacist turns it around and we are sexist, \textbf{racist} etc...no correction for poor behaviour just another victim....like Serena Williams.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Claiming \textbf{sexism} but if a man behaved exactly the same, everyone would be talking only about his horrible behavior, not about the perceived unfair umpiring. And she only claims \textbf{sexism} when she's losing. She's a disgrace.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Bitch be crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Can't wait to see this \textbf{woman} lose to Osaka again. Serena is a legit loser 🖕🏿🖕🏿🖕🏿🖕🏿\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I never had any respect for her after I saw her \textbf{racist} ass with Crapperdick.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Sorry but you are wrong!! Yes we all have bad days BUT ITS HOW YOU DEAL with said bad day that makes you who you are. So the so called excuse " She had a bad day" is NO excuse to act like a 5yr \textbf{old} on court period. Your comment has \textbf{ZERO} merit.\normalsize   & \cellcolor{green!5}Old, Zero & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small A SORE LOSER...AND A \textbf{TRANSGENDER}!!!\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Sexism my arse ! ..sHE is one of, THE "Most Privileged" persons on the planet ...And, ..all due to the Massive Fraud perpetrated by HEr father ..and his co-conspiriters,  "from" the time they were toddlers.This has to be one of the Biggest Scams of our time. And, ..HEr "initially" being "a pawn" in this scam, is the "ONLY" thing sHE can claim to be a victim of.So far, sHE has personally been "Gifted" around \$90 million in prize money ...plus, all the many millions in endorsements etc ..and then, there's all the millions gained from this scam, by the father AND all the co-conspiriters.   And what of, ..All the "ACTUAL" women, who over the duration have been defrauded of "their" rightfull successes \& monetary gains, Due to this behemouth.Regarding the \textbf{Freak} Show \& HEr behaviour in this match, ..sHE has a track record of abhorent disgusting behaviour and, ..of being the "Actual" sexist \textbf{racist} bigoted pig.  How ironic that this cunts initials, are SJW.Everyone ought be sick to the stomach about HEr repugnant behaviour \& attitude, ..as well as the fraud. Certainly, ..No-one should be defending HEr, or any of it.As for HEr (supposed) daughter, ...well, ..it sure as hell did "Not" come from HEr "manufactured vagina" ..and, it would not surprise me in the least, if it is also a Male child being masqueraded as Female, ....With Purpose.\normalsize   & \cellcolor{green!5}Freak, Racist, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/234 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small What a disgusting \textbf{woman}. Thank god she was playing against a half \textbf{black} \textbf{woman} or she would have screamed racism\normalsize   & \cellcolor{green!27}Black, Racism, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}4/20 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Black people.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small When Feminism Tries to infiltrate sports using the Loud UN-So-Strong dependent \textbf{woman}. looked like a baby throwing a tantrum. Bad attitude issues. I could play better than her.No, of course that last part is a lie, I woulnt be able to go against that Man, I mean \textbf{woman}, how is being penalized for braking the sport rules a \textbf{sexism} act, And thank you for ruining the celbration of that little girl and try to make everything about you. Even \textbf{ho} you had ennough titles in the past, this was her first grand slam as you said yourself SMH\normalsize   & \cellcolor{green!27}Ho, Sexism, Woman & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}4/99 & \cellcolor{green!27}4.04 \\  \hline
  \cellcolor{green!5}\small in womens tennis, She lost ,IN her  temper  she smashes her racquet and attacks the umpire, then  screams sexist???? WTFCongratulations to the TRUE WINNER NAOMI!!!!!!!!!!!!!!! Liberal \textbf{nazi} feminism BAN IT!\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Serena Williams, sexist, \textbf{racist}, fowl mouth, slander, false accusations, liar, and disgraceful lack of sportsmanship must warrant withdrawing all medals; awards bestowed on her over the history of tennis. At this point, Serena Williams is a criminal loose in the USA. Williams' unpardonable display of threatening rage looks like a person on steroids or opioids. Serena's looks have transformed into the face of evil as has her behavior. I'm sorry that she had a baby as she appears unfit  to care for a child. God watch over this little   girl.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small black attidude  like all wahys\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She threw EVERYTHING..  Im a WUM MAN!   Im a MOTHER! She claimed she was fighting for EQUALITY.... so I guess its because she is \textbf{BLACK}?  I hate manipulative people-\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Sexism.  What about a spoiled, whiney, self-indulgent, rich \textbf{black} female who like most \textbf{black} females just can't keep her mouth shut\normalsize   & \cellcolor{green!5}Black, Sexism & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small She is a typical \textbf{black} women. \textbf{Black} women know what that means and white women know what that means and to each group it means different things.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Sexism or Sore Loser,,,,she is BOTH...\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small How do trainies claim \textbf{sexism} !!!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small To be honest! SORE LOSER: I think she was pissed because she was getting beat by a 20 year \textbf{old}!! who hasn't got a big name in tennis! she probably went into the game thinking she was the big player! and got too frustrated when she knew her ass was getting kicked\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small She'll play the \textbf{race} card, make the rounds on late night tv and be hailed a \textbf{black} hero.She'll never apologize.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small 19xfan 1 \textbf{black} lives matter properly have her framed in gold in their cave.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small every penalty given to Serena was justified - if she wants the umpire to ignore justifiable penalties because of her \textbf{sex} then that would be \textbf{sexism} as well. She has no logical argument against the umpire. I can only imagine that she wants someone besides herself to blame for her loss. So she illogically blames the umpire. She should pick her battles against \textbf{sexism} better \& cases where it actually exists.\normalsize   & \cellcolor{green!27}Sex, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/71 & \cellcolor{green!27}4.225 \\  \hline
  \cellcolor{green!5}\small Serena Williams Let Naomi Osaka Win...Serena Is Passing The Throne To The Osaka Sisters...Serena Played Y'all Racists...Now Ya'll Have Two New \textbf{Black} Sisters To Win Money \& Trophies.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small That was sad... really ... \textbf{woman}'s right??? Really??? Gee! This \textbf{woman} acted like spoiled \textbf{brat} and that who she is\normalsize   & \cellcolor{green!27}Brat, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small This is what gets me:1. If a guy had broken his racket in a match, the punishment would have been lesser and the comments would be in the lines of 'the passion of the game...'2. If a guy would have argued with the umpire, the conversation would be different, but because she's a \textbf{woman} she gets criticized as 'unable to control her temper.'3.Since when are umpires so touchy-feely. Other players have done worse or said worse comments and the umpires just let it go.4.I love the fact that she is the one penalized and chastised for standing up for herself, but no one seems to understand that the one really at fault here is her coach. The big head decided it was ok to coach her, knowing it was against the rules, and she gets the short end of the stick for his actions.5. Sure,  Serena could have handled it better, but then again, it would have not been necessary had the coach sat on his little hands and let her play.I honestly think she would have been ok with losing the match to her great opponent Osaka, but the issue is not the loss of the match, but the fact that because of a man, she gets punished by a man and then gets criticized by all other men as a \textbf{woman} unable to 'control her temper.' That's right, because unfortunately, some men are threatened by a strong \textbf{woman}.Serena, we love you, and know it was complete BS.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/256 & \cellcolor{green!5}1.172 \\  \hline
  \cellcolor{green!27}\small Sore loser.Definitely a sore looser.Bringing up the \textbf{racist} card for no reason, doesn't that make you the \textbf{racist}?Ditto for the female discrimination card?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Sexism... Well let's see. Shes a \textbf{woman} playing against another \textbf{woman}. So while one \textbf{woman}'s cause was harmed by the ruling, another \textbf{woman} gained from it. Soooooooo....no \textbf{sexism} there.  Unless..... she is saying that it's unfair for a man to enforce the rules of the game if a \textbf{woman} breaks the rule.  Of course these days it's sexist to be male and simply exist... I wonder if she will ever admit that she is wrong.  I've noticed through the years that sometimes both men AND women have trouble in this area. Aggressive and competitive members of both sexes tend to avoid the admission of mistakes. I'm guessing that eventually her PR people will get through to her.  I wonder what her daughter will think when she watches this one day...\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}6/130 & \cellcolor{green!5}4.615 \\  \hline
  \cellcolor{green!27}\small I find it odd that two \textbf{transgender} siblings  h ave gotten away with it for this long, they're allowed to play women's tennis it's in the rules that \textbf{transgender} men can play female tennis I don't know why they just come clean and admit that they're \textbf{transgender} all you got to do is look at how their hips are placed where men's hips are compared to a woman's hips everything about their skeletal structure is male\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}3/76 & \cellcolor{green!27}3.947 \\  \hline
  \cellcolor{green!5}\small A sore loser and wholly unprofessional and the \textbf{sexism} angle is deplorable. She's bought the sport and herself into disrepute and owes the umpire, her fans and tennis in general an apology. Not to mention she tremendously degraded the occasion for Osaka.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Anthony Kist continue to be \textbf{blind}, you'll go far in life, I see.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Anthony Kist It's not a \textbf{woman}, neither is Venus.  Go study pictures of them when younger, two little boys dressed as girls.  There is plenty on YT to show this, you just have to pay close attention and discern.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Should've been the greatest moment of Naomie's life and what happens? She pulls her hat down over her face because she feels guilty that she beat Serena. Wow I bet your daughter must be really proud of you Serena!! And even after your half ass congratulations to Naomi you go to the press conference and start whining again about \textbf{sexism}. There's being passionate and being a spoiled \textbf{brat}!!! Learn the difference!!!\normalsize   & \cellcolor{green!27}Brat, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small She is an mother now.... You don't know the size of her trauma!!!! When you become a mother you become traumatic.... She wasn't an \textbf{fat} \textbf{woman}.... Now what?\normalsize   & \cellcolor{green!5}Fat, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small It has \textbf{nothing} to do with being a sore loser. She had her character questioned and that's what set her off. Not the fact that she was losing. Although her coach was coaching her, whether she noticed it or not, that's the fact.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Serena William should shut the hell up.Her pathetic remarks and attempts to play the \textbf{gender} card is absolutely pathetic.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small reverend al \& jesse will be at the next tournament protesting the "lying \textbf{racist} sexist " umpire\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small THIS IS SO CLEAR!!  1) The men had an overwhelming majority of code violations overall in the tournament.  2) The 2nd, 3rd, etc code violation for any player DURING THE SAME MATCH will result in a more significant penalty (e.g. warning, point penalty, game penalty...a fact Serena knows "in her sleep!").  3) Her behavior that "she doesnt cheat" is a thinly veiled lie as it implies she NEVER saw the NUMEROUS coaching signals from her box (Now, we all know how often players look to their box --- pretty much after every point? Yeah, I'm gonna stand by that estimate).  So, are we to believe that with her knowledge of the rules,  her unavoidable awareness that her coach was signalling (which he immediately admitted post-match), her decision to NEVER GESTURE TO HER COACH TO STOP (Nadal has done this, for example, MANY, times), that her reactions to the 2nd and 3rd code violations were authentic, sincere, and surprising?  Give me a break: this,  IMO, would constitute an equal insult to Serena's knowledge of Grand Slam rules.  4) Finally, a logical overview of this situation is not a contrast of what men and women get code violations for.   The data is clear:  \textbf{sexism} cannot be supported by the statistical records of Serena 's generation including the ten years previous.   THIS SITUATION IS SIMPLY AND ABSOLUTELY ABOUT A PLAYER "EARNING" MULTIPLE CODE VIOLATIONS IN A SINGLE MATCH --- THUS THE PROGRESSIVE IMPACT OF THE PENALTIES.   SHE KNEW THIS; SHE LOST CONTROL; SHE CHOSE A VERBAL ABUSE THAT HITS SQUARELY ON A SPECIFIED VIOLATION (LIAR, THIEF ----》  RULE: "DISPARAGEMENT.....HONESTY").   SERENA IS A TERRIBLE LOSER!!  LOOK AT CLIPS FROM HISTORICAL FOOTAGE OF LOSING ON COURT AND POST - GAME PRESS CONFERENCES.   DO YOU SEE A "GOOD LOSER---SPORTSMANSHIP UNDER DEFEAT?"  I CLEARLY DO NOT.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/299 & \cellcolor{green!5}0.334 \\  \hline
  \cellcolor{green!27}\small Can you imagine if Naomi Osaka was white- it wouldn't be \textbf{sexism} it would be \textbf{racism}... Serena is a sore loser and highly disrespectful to the sport. Her outfits are at times outrageous- respect the Sport that made you. Still feel Graf is one of the greatest of all time- professional and humble. Serena robbed Naomi of a well deserved celebration. She urged the crowd to support her then tells them not to boo. Let's face it, Naomi has class.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/80 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Sore loser. She's pulled this act out before. She's crying \textbf{sexism}, thisism, thatism, the simple truth is she broke the rules. She feels that she can because. Men in today's tennis have been penalized for this type of behavior over 3 times as much: 26 to 12. As far as the McEnroe and Connor behavior of yesteryear? They didn't have the type of rules regarding the behavior. The current rules are BECAUSE of their behavior back then. It's all strawman arguments to excuse her egregious behavior. She's a spoiled rotten bully who was called out for her behavior. Simple as that. The sooner that she goes away  the better.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small Entitled? Do you even know what the word means or is it just a general slander against \textbf{black} people you picked up at the KK-Mart? You do understand that Ms. Williams is an athlete who since 20 years beat the best in the world in women's tennis on a regular basis and is the only tennis player in the world who holds a golden slam in singles and doubles, do you? So you may not like her, but she is one of the very few persons who really did earn all her titles through her own, incredible hard and incredible talented, work. And what did you do in your life?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small \@Franz-Dominik Imhof what the person was talking about was the fact that williams thought that she was losing due to the penalties and that she would have won if not for that (this is proven by the fact serena agreed to osaka when she apologised for winning). I think what he meant to say was egotistical but you cant just devoid the point of the comment because he said entitled, and plus maybe she is entitled on things outside of her game since she pulls out the \textbf{sexism} and \textbf{racism} card. Sure she won a lot but that is due to her physical ability whereas the comment was talking about her personality and social aspects.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/115 & \cellcolor{green!5}1.739 \\  \hline
  \cellcolor{green!27}\small that devilish giggle right after she said no more booing.. what an uncivilized woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small While the umpire wasn't displaying \textbf{sexism} against Williams the culture sure  is. You have NEVER  seen a male player pilloried this much for misconduct on the court.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Thank God Osaka wasn't a white girl , CNN would be have wet dreams hyping that one , white player , white umpire , ganging up on the poor \textbf{black} girl\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Neil Macleod Her being female, and \textbf{black} also played a role in his extra attacks against her!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Why do \textbf{black} people always play the victim ... always. The only thing she taught her daughter is how to be a complete ass.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small she is so much more, she ruined the moment for Naomi. she behaved like a \textbf{racist} entitled hypocrite. I would ban her for 5 years.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small She needed to have better dna in her body ..when a \textbf{woman} allows weaker dna sperm in her it weakens her body ...She acerbated  weak dna sperm and for 9 months ...Its a wrap ..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small White genetics  are weaker than \textbf{black} .....if u say that incorrect i understand ur type ....\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Sore loser is minor!! Violent lying bully....and its not the first time is it.Her coaches eyes and eye brows nod and raise (zoom it!! and see)..that means she saw!! Their eyes met. Then SHE admits she saw thumbs up to the umpire!! The coach didnt have thumbs up he was gesturing to move closer to the line.SHE ADMITS SHE SAW THE THUMBS...SHE THEREFORE ADMITS LOOKING...SHE THEREFORE ADMITS SHE WAS RECEIVING COACHING!!Your a liar williams.26 men penalised is way  more than women penalised.When it rains matches arent stopped in the infinitesimal same place Every time Its a matter of judgement. So is handing out a warning. you weigh the pros and cons...each situation is different. To then say you have a case that within that bracket of fine judgement on such things that you can build a case of \textbf{gender} bias and \textbf{sexism} is preposterous and stupid.Its getting dark lets stop play.....your stoppin coz im a wimun.my meter says its dark...your meter was designed by a man..its cuz im a wimun.my calibrated meter says its dark...it was a man calibrated it..to bias cuz im a wimun.my female calibrated light meter says its too dark..its parts were made by bias men..cuz im a wimun.my female calibrated female made female operated meter says its too dark...yes but your a thief cuz u stole 0.78 secs off the length of time it took u to say that compared wiv a mans game...thats sexist coz im a wimun!!!\normalsize   & \cellcolor{green!27}Gender, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/253 & \cellcolor{green!27}0.791 \\  \hline
  \cellcolor{green!5}\small sexism? isnt transgenderism a word already?!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Ramos was absolutely not sexist, nor was he \textbf{racist}What other judges allow is irrelevent In this situation its down ti what ramos allows and hea a strict rules enforcerSorry serena but this is not a case for \textbf{sexism} nor is it a case for racist\normalsize   & \cellcolor{green!27}Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/47 & \cellcolor{green!27}6.383 \\  \hline
  \cellcolor{green!5}\small The judge noted a clear secret hand code sign by the coach to Serena.  So yeah that is \textbf{racist},  and abusive \textbf{sexism} as well, by the judge.\normalsize   & \cellcolor{green!5}Racist, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small We get it, Non. Anytime a person of color doesn't get something he or she wants, there can only be one reason: \textbf{RACISM}!  Lol...\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Ramos was a pro, he's been doing this for a LONG LONG time.  He didn't need a spoiled \textbf{brat} like William's to tell him how to do his job.  It was her fault she didn't know how to do her's.  The mere notion that her coach would imply that Serena might not have known the implications of throwing her racket down in an Open match is absolutely laughable.  How long has Serena been playing tennis?  And you are going to imply she may not know basic rules of the game?  STFU and go home... losers.  Losers.  [edit] <--- Referring to the coach and Serena, not people in this thread.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small UndertaleSkeleBros THANK GOD FOR SOMEBODY THINKING RATIONALLY. Serena's go to excuse is that 'people do way worse.' It's the same excuse she used in 2009. And her comment about male players doing the same thing or worse and getting away with it and not getting a game taken away is completely off kilter. First off, most males have short outbursts but they stop pretty quickly, she kept going on and on. Secondly, most male players yell about the call and they try to argue why they thought the call should have been different, Serena went straight to attacking the character of the umpire, most male players do not do that. And third, yeah make players do this and they DO get a warning, except usually it's not their third warning and the only reasons Serena got a game taken away is because it was her THIRD warning. Most men know when to stop so they don't have that happen and Serena has been pro for 20 years, she knows the rules. And last like you said, it doesn't matter what other umpires have done. She brings it up like men do things worse than her and don't get penalized and that because she got penalized it must be because of \textbf{sexism} but that does not being into account WHO is doing the penalizing. Ramos is known for being a stickler for the rules and he has always upheld them very strictly. There may be other umpires who are more relaxed and who would have let Serena's thing go, but that doesn't matter. What matters is consistency with each INDIVIDUAL umpire to tell if it's \textbf{sexism}. Ramos is extremely consistent. Serena has completely lost any respect I've ever had for her\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/290 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}\small Taken lessons from Hillery , \textbf{nothing} is her fault , the umpire only followed the rules , she wants the rules bent for her because a, she has a daughter , b, other men get away with worse ( her words not mine ) . You can't threaten an umpire . "You'll never work in another one of my touraments as long as you live , " you're a liar , " you're a thief .   Prima donna is \textbf{ageing} and can't keep up , she has to come to grips with the facts .   Oh wait , it's all about womans rights , what a load of crap from a sore loser .\normalsize   & \cellcolor{green!5}Ageing, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/114 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Sore \textbf{racist} loser. McEnroe was banned for three months, and kicked of the American Davis Cup team, and lost the Australian open for his bad mouthing referees. But because she is a privileged \textbf{black} tennis player this won't happen to Serena.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Serena Williams IS a champion woman's player, hands down.  Her level of competitive drive,  perseverance, and single -handedly changing the style of woman's tennis is \textbf{nothing} short of generational.  Having said that, she was blatantly wrong in this case, and further tried to change the narrative so that the radical left media (and virtue signalling activisits) would jump on board with the accusation of \textbf{sexism}.  I am very disappointed in this blatant example of poor sportsmanship.  Not only is she not owed an apology, she needs to apologize to Naomi Osaka \& Japan for ruining this special moment.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/98 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Sexism Period!!! Serena has lost many titles before.Get Real People!!!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Couldn't claim \textbf{racism} so went for \textbf{sexism}, well done to the other lady.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Wow because she's \textbf{black} she's not supposed to stand up for herself. She is supposed to take whatever they dish out!!!! Stand you ground!!!!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Serena Williams, your daughter if she will be an honest person when she will arrive at the \textbf{age} of reason and will see the video of you at US OPEN 2018 WILL BE ASHAME TO BE YOUR DAUGHTER .POOR MOTHER WHO WILL LOST RESPECT BY HER OWN DAUGHTER.....\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small wow you uncovered an american story. i wonder why \textbf{nobody} else talked about this.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Actually. When Serena lost and accused him of \textbf{sexism}. Another girl won the match.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She lost a game to a \textbf{black} \textbf{woman}, and still cried \textbf{sexism} and \textbf{racism}, because those words don't actually mean anything to leftists like Serena Williams, they use them to shirk off their personal responsibility for their failures and mistakes.\normalsize   & \cellcolor{green!27}Black, Racism, Sexism, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}4/40 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Oh look another \textbf{black} athlete acting like a jerk - play by the rules or quitSerena = Killery SORE LOSERS - HEY HONEY THE COURTS ARE NOT YOURS\textbf{SEXISM} - 2 \textbf{BLACK} WOMEN WERE PLAYING - IS SHE \textbf{COLORED} BLIND\normalsize   & \cellcolor{green!5}Black, Blind, Colored, Sexism & \cellcolor{green!5}Ethnicity - Black, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/41 & \cellcolor{green!5}12.195 \\  \hline
  \cellcolor{green!27}\small People are saying "she can't go for the racial card because the other \textbf{woman} is bi-racial" but surely she can't go for the \textbf{sexism} card either? Why didn't he punish the other \textbf{woman} for "no reason"? What a pathetic display. Just take the penalty and play on.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/47 & \cellcolor{green!27}6.383 \\  \hline
  \cellcolor{green!5}\small He's ...oops I meant she's.... a spoiled \textbf{brat} and a sore loser!\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small So coaches can't coach, kinda a \textbf{weird} rule to be honest.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Can't be \textbf{sexism} there were two women playing the game and they were both women of color sore loser\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She has ingrained \textbf{racism} brought on by decades of illusory social mollycoddling.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small randy osborne If she is a \textbf{racist} like you say, then why did she marry a white guy??  Personally I would love to be married to someone as pretty as Serena!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small "Was there \textbf{sexism} at this year's us open? It's impossible to say." Ridiculous! Ramos has been completely consistent in how he has treated men and women. The fact that some other umpire may not have penalized some man is irrelevant. Also I have trouble with my temper playing games like tennis, but it would never cross my mind to say the sorts of things Serena said. Having a temper tantrum is bad enough, but verbal abuse is unconscionable. It doesn't matter if others have done worse. That's an absurd defense, as is the statement that "I'm fighting for women's rights." I'm still a Serena fan though - I love her as a tennis player.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/114 & \cellcolor{green!27}0.877 \\  \hline
  \cellcolor{green!5}\small Why would being a \textbf{woman} be the reason to receive a penalty if she's playing against another \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Serena had a point behind her accusations, but took it too far. However, I think the umpire could've of devoid from penalising Serena, since it was the final of a GS. Furthermore, Serena had a point behind the men and \textbf{woman} comparison when it comes to penalisation of verbal disputes. But, nevertheless, adding her child to defend her argument was completely uncalled for. I think Serena and the Umpire could learn from this mistake, and tie loose ends at both ends. But Naomi Osaka was the flower on the AAS unwilling to blossom, under the shade of Serena. We should forget the argument and focus on Naomi as she deserves the victory and the title, despite the major impact the stipulations around the on court has created....congrats Ms.Osaka.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small Narcissistic \textbf{woman} .. the worst. Period.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small It's not called \textbf{sexism}. It's called playing by the rules.You break your racket in frustration, got illegal hand signals from the coach in the crowd and demands an apology from the umpire. When he doesn't give you what you want you proceed to call him a thief as well as accuse him of being a sexist among many other things.So, if you look up bad sportsmanship in the book, Serena Williams face is going to be on there now.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small albert fish"Her" face should also be in the dictionary for transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Now i find out she is a \textbf{woman}?   Can't be, women don't  act like that.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Serena Williams is a \textbf{transgender} person I did not realize that SRS has come so far that they can actually have babies please somebody signed me up LOL\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Just an angry \textbf{black} man. That's all. She wins because she's built like a \textbf{black} man.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Or \textbf{Transgender}! She's undeniable a MAN!  That SHOULD be the REAL story! Wake-up people. It's REDICULOUS..HE IS a terrible spoiled selfish person! that's entertainment?! wake up!\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Women's rights in a game where no men play? Interesting! A ....no men empires in women sports. Good idea Serena....I never thought of that.If it were only a \textbf{woman} that was an empire. You have an excuse now to be more rich than you are.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Considering the fact that the chair umpire literally coached Nick Kyrgios to comeback and win, I would say there is a fair amount of \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Sexism for sure even though people will ignore the facts\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small "I have never cheated in my life"... Maybe: but you've always been a spoiled \textbf{brat}.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Just another spoiled rich , entitled athlete who thinks everybody should bow down to her.. I'm surprised she didn't call him \textbf{racist} along with sexist. POOR SPORTSMANSHIP and a huge disgrace . Not a fan . 👎✌💖🇺🇸🇺🇸🇺🇸\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Women when they kick off don't have an off button. Hence why the Greeks called it Hysteria thinking the Womb was wondering causing \textbf{mental} imbalance. Wrong science but correct psychology.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small CNN = "\textbf{Sambo} Williams is robbed of another game by sexist umpire. \textbf{Racist} opponent shamed into submission by crowd booing her for cheating".\normalsize   & \cellcolor{green!27}Racist, Sambo & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small John McEnroe 1990 Australian Open.  Almost exactly the same scenario as Serena with the result that he was disqualified.   Case closed, umpires just dislike jerks regardless of \textbf{gender}.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Sexist? not at all, but we can thank feminism for her entitled, rude, childish, victim card behavior. Anyone that behaves with that little honor or class, man or \textbf{woman}, deserves whatever they get.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small No class! Typical reaction of a sore loser. Play the \textbf{race} card or \textbf{gender} card. Sick and tired of these egotistical narcissistic athletes.\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Being a 'hater' basically means ever holding a \textbf{black} person to account for anything.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Sore looser...and sexist. Serena didn't even noticed that in the whole she was loosing against...another \textbf{woman} and playing better than her. By misplacing the sexist accusation Serena revealed that she's the sexist and bully not looking at means to reach her "end" (as she had done so many times before). Not to mention the time where to avoid the dope control knocking at her door she called 911 she hided with her baby in the bathroom pretending that she was being "threatened"...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small a man rob a bank and escape.  a \textbf{woman} rob a bank and got caught. maybe it is \textbf{sexism} but that doesn't prove robbing a bank is a right thing.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small The Hulk of tennis courts. A \textbf{gender} baiting Hulk.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I hate her tantrums but if they keep on being tolerated then she is going to stay in the habit of throwing them.   She isn't the only \textbf{woman}, from what I've seen the game is flooded with on court hysterics and hissy fits and verbal attacks against the ref.  It is sexist in the sense that men get away with worse and more often.  It is true that aggression and anger are more expected and accepted from men.  If the rules are expected to be respected then the game needs to address this inconsistency.  A rule needs to be upheld 100 of the time and currently its a farce because sometimes it is and sometimes it isn't.  If Osaka was being coached throughout the match, then how on earth can only Serena be penalised?  It isn't good enough to say that the ref didn't see it.  Didn't he?  Or has the Serena bias built up to such an extent that people just want to see her lose no matter what?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/170 & \cellcolor{green!27}0.588 \\  \hline
  \cellcolor{green!5}\small 3:45 but a \textbf{woman} won that game. So basically she is just mad because she didn't win.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small She is an angry, ignorant low life even after getting the best life she could imagine..  She does not just have a "temper", she is an overpowering \textbf{racist} bully.  Her injustice is her uncontrolled diarrhea mouth.   She realizes she can say anything because she is \textbf{Black}, and for some reason the crowd cheers for her regardless of what she does...  She destroyed the joy of Osaka in her life's greatest moment.  Osaka was the one really abused here for outplaying that stuck-up biatch and having the moment destroyed...  She needs to retire and join \textbf{Black} Lives Matter...\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/97 & \cellcolor{green!27}3.093 \\  \hline
  \cellcolor{green!5}\small He is getting \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Serena made a big show.playing diva. It's a shame to tennis and sports. How convenient to violate rules and abuse others when caught out. "Am I not the superstar?I can do no wrong! Got it? And I am setting an example to my infant daughter! If call me out you are sexist \textbf{racist} and a liar! Got it? " Dear Sir there's an \textbf{old} saying :"right is right when nobody's right, wrong is wrong when everybody's wrong".\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small How come \textbf{nobody} talks about strange and funny speech defect that Naomi has??? She is so funny how she talks :))\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small totally agree with your view.I think Serena was wrongUmpire was too harshCrowd was too insensitive Bringing in \textbf{Sexism} into the argument is Uncalled for!So many things spoiled this perfect final match\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small She's a man how can it be \textbf{sexism} ? ,Get rid of now\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Drug test the \textbf{d\textbf{rag queen}} (and i really doubt she is a \textbf{woman}, (s)he has more testosterone than me...)\normalsize   & \cellcolor{green!27}Drag queen, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Sexsim?? WTF is that about. BOTH of the tennis players were women!!  She should have had him thrown out after the first warning. Plus, she was clearly UNWILLING to be held to the same standards as MEN during competition. All tennis players get into arguments with umpires, \textbf{nothing} new at all about that; however, claiming 'sexism' ? That's bull shit.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Because I'm a \textbf{woman}, I should be allowed to break the law like a man.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small The umpire is a \textbf{old} fart\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Reminds me of how \textbf{black} people interact with the police.Or any authority.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small well then how come men play to the best of 5 and and women to the best of 3? \textbf{sexism} lol\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small if she called him a poo poo \textbf{bum} \textbf{bum} and she lost a game it could be the first \textbf{woman} to lose game for that too\normalsize   & \cellcolor{green!27}Bum, Woman & \cellcolor{green!27}Gender - General, Social Class - Destitute & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Again the \textbf{racism} of a privileged \textbf{black} millionaire stole and ruined that beautiful young lady's victory.\textbf{Black} supremacists must be treated like the trash they are.\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/26 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small IT'S A SHOW FOR THE MASSES! Serena is a boy in drag - \textbf{Transvestite}. There's no if, but's or how's about it.\normalsize   & \cellcolor{green!27}Transvestite & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small She is the typical \textbf{black} privileged millionaire that cheats then claims someone white is \textbf{racist}, or sexist  or....Basically blaming white people because of their cheating, lying, and often criminal behavior.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI NAOMI ...Naomi Osaka is truly gracious and great behavior at a very young \textbf{age}. US should apologize to Japan and Naomi family for this act.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small If you are replying to me Mr.Thong, it looks like you do not understand \textbf{common} English!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small All respect to you but as far as the US as whole goes, there was never more unfair and indecent country/people, starting with the genocide of the natives, slavery and the continuous war waging and aggressions  that's been going on for last 100 years. The brain washing is so deep that despite the  most despicable crimes  average Americans think highly of themselves and their country. Again, \textbf{nothing} against you, your comment was sincere and somewhat critical of the todays situation as a whole. Cheers!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small Serena lost it because she was losing. That's all there is to it. Enough with this \textbf{sexism} bullshit. If she really wants to do something to right the wrongs of humanity. let her use her money and energy to really help!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small How is it \textbf{sexism}?  She was playing another \textbf{woman}. Ref couldn't really be favoring the male player over the female in this case\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Serena Williams, when she calls out for \textbf{sexism} victim, just perfectly reminds me of the raped victim in the 'To Kill a Mockingbird'\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Serena is a spoilt \textbf{brat}.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Hi Mr. Chapel, you call it just about right in calling SW out for her outrageously unsporting conduct. Regardless of the how the Drama Queen spins it -- ridiculously trying to hang the \textbf{sexism} peg on the umpire for doing his job -- her history of unsportsmanlike antics is coming back to haunt her. Flip, flip, she and her diehard, uncritical hierophants are tarnishing the reputation of this sport once known for the grace and beauty associated with its female pros.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Pre-middle \textbf{age} , sore loser🖕😭\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Dont do me any favors with the womans right shit!!!!  And i am a \textbf{woman}!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small both - a bit \textbf{sexism} and she is a sore loser\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small this guy is a queer\normalsize   & \cellcolor{green!5}Queer & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Serena was counting on winning that 3.8 MILLION dollars. She and her coach would have done anything to win that money, including, taking the chance that they wouldn't get called out for coaching. With that much money on the line, they should have known that they were going to be scrutinized....both sides scrutinized. \textbf{Nobody} likes a sore loser, and it wasn't the judge that made you destroy your racquet honey, you did THAT out of frustration at losing the point. Serena has been the best. The greatest. But time always catches up with everyone, and the younger generation comes along and you hand the torch over to them. Gracefully is better than throwing fits and claiming to be the victim, but alas, your kind knows \textbf{nothing} else but to claim to be the eternal victim if you lose, even after two decades of being the winner.\normalsize   & \cellcolor{green!27}Nobody, Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/146 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small The \textbf{black} lady. Handing 2nd place trophy to serena. Said. This is not the outcome I wanted.  .  You got robbed ....  during ceremony.  Disgraceful. Behavior.   All these \textbf{woman}. Are out of line.  Boisterous   Poor sports   no class  No etiquette  New York is rudeI believe that's because most of the audienceI low class I'm never watching women's tennis again disgraceful and disgusting\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small cuz im a \textbf{woman}.........could have fooled me ....i see no \textbf{woman} ........i still looking for the broomstick for that \textbf{witch} to fly off up and away over the crowd............\normalsize   & \cellcolor{green!27}Witch, Woman & \cellcolor{green!27}Gender - Female age and physical appearance, Gender - General & \cellcolor{green!27}3/29 & \cellcolor{green!27}10.345 \\  \hline
  \cellcolor{green!5}\small Serena is the Lance Armstrong of tennis. He used the greater cause of cancer research as a saintly front, while going after anyone who tried to discredit him will full, bully-type force. Her behavior is the same, she's just using a different front, in this case \textbf{sexism} and \textbf{race} to justify her actions.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small in addition to playing the \textbf{sexism} and \textbf{racism} card, she could have played the \textbf{transgender} card.  the previous two won't work against osaka, but this third one can.\normalsize   & \cellcolor{green!27}Racism, Sexism, Transgender & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small marshall wright its a \textbf{gender} bender\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small THERE IS \textbf{NOTHING} WORSE THEN AN ANGRY \textbf{BLACK} \textbf{WOMAN}. SHE SHOULD HAVE BEAT UP HER COACH INSTEAD OF MOUTHING OFF TO THE REFF\normalsize   & \cellcolor{green!27}Black, Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Gender - General & \cellcolor{green!27}3/23 & \cellcolor{green!27}13.043 \\  \hline
  \cellcolor{green!5}\small Look at her face when she's claiming \textbf{sexism} on the court. It's like 'you know you can't challenge that or else you are a sexist/racist.' She's a disgrace. Such a shame.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Ok youve got a man pretending to be a \textbf{woman} claiming \textbf{sexism} cause another man is picking on her cause shes a \textbf{woman} but its obviously not a \textbf{woman} ,how can a man claim \textbf{sexism} against a man .............\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}5/39 & \cellcolor{green!27}12.821 \\  \hline
  \cellcolor{green!5}\small The ref did \textbf{nothing} wrong there at all. She's just a sore loser\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Sexism or sore loser?  Good headline, but as usual things are not that cut and dried.  She's at the top of her game, pretty much something she did because she herself is awesome.  I'm not able to connect that with her doing this for women's rights though.  Its like the football players at the tops of their games.  They give lip service to \textbf{black} agenda; really they are there to win and make big bucks.  So they kneel during the national anthem for all the \textbf{black} folks who couldn't be there?  I don't think these causes are getting as grand a gesture as the participants seem to think they are giving.\normalsize   & \cellcolor{green!27}Black, Sexism & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/111 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Neither. Serena is just the most obnoxious, sexist, \textbf{racist} , dishonest person in sports. She should've been permanently banned after threatening to kill a lines-woman back in 2009. But of course, PC culture in the US and the media will ensure this insufferable boorish buffoon will continue to disgrace Tennis.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Her fear of losing overcame her so she elected to bail rather than risk a defeat. To convince herself this was a righteous cause she created this \textbf{sexism} senario. She sprinkled in a little women's rights rhetoric and a dash of mother's tears. And viola! Chef Williams has baked the perfect bullshit pie. Bravo! Bon appetit. What a racquet.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Couldn't have been \textbf{racism}, since they are both \textbf{black}. So, yeah... \textbf{sexism}.\normalsize   & \cellcolor{green!5}Black, Racism, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}3/12 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small wasn't she supposed to be playing this sport for years now? dear, you've had 2 violation calls already, you should have known what will come next if you don't (and she didn't) back down. sure, some players have said way worse things to umps before, and some don't get penalized. But what people fail to realize is that perhaps 1. the verbal abuse was their first offense (so they just get off with a warning as per rule), or 2. the verbal abuse, as mentioned in this video, were short outbursts that the ump was able to let go. On the other hand, Serena ran with her mouth for a good few minutes there before Ramos has had enough and called her 3rd violation. i'm all for fighting for equality, but please, let's not call something for what it isn't. As a world-class athlete, Serena should be the first to hold herself in high standards, because crying foul and saying, "why are there other [men] who can get away with worse but i can't?" for me is just \textbf{lame}. why even would you be committing the same violation as what those [men] did in the first place?\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/197 & \cellcolor{green!27}0.508 \\  \hline
  \cellcolor{green!5}\small Her being the greatest female tennis player of all time is just a matter of opinion. Her competition has been the weakest in the last 5 years in women's tennis history. It's a different opponent in the finals every time. And Serena is still behind Margaret Court in all time majors. And Steffi Graf won 22 majors one behind Serena. But she is the only \textbf{woman} to ever win the golden slam against the toughest competition in female tennis history.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small It's a \textbf{mental} illness folks!!\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small "cause i'm a \textbf{woman}...?!"Chris, Martina, Margaret and Althea are all lessened by your antics.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Serena and BJK, and the WTA have set us female tennis players back.  If you want to be respected, you need to respect others, and the rules. Women tennis players do draw in the money that the men do....and they have to play 5 games in the majors.  Yet, they do not complain of \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Manners, manners! One of the best players in the world, but she lost to herself:) \textbf{Sexism}! Yes, by her! Grow up!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Serena is a disgusting \textbf{transgender}.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small " She" reminds me of Bo Jackson when he broke a bat over his knee. Cheaters never win goes the \textbf{old} saying. I think she was pissed that they got caught cheating. She was struggling and needed the help. Wonder how many times they got away with it before?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small 1:15 She said he was giving her \textbf{dumb} up... hahahahaha so she did saw him!1:22 That was not a great atitude.. because she was lying! He DID NOT give her dumbs up!3:40 I have seen OTHER men call empires several things! OTHER MEN! Hahahaha LOL\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Well, she really is in love with herself. She has millions and yet shows such contempt for the system. The very system that gave her the millions. Her mood and personality is a reproach. But, she will go on playing the \textbf{sex} card and any other card she can play when things do not go her way. She is a real loser and a reproach to the profession. It is because, in her mind, it is all about her. But the clincher was when she started invoking he motherhood, this is feminism at its zenith. She lost and she had to escape that fact. You know, when will there come a time when such frauds will no longer be tolerated. I just feel sad for her opponent who could not enjoy her achievement because of a spoiled, winey and arrogant prima donna . Thanks Serena, for taking the US open to the gutter.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/153 & \cellcolor{green!5}0.654 \\  \hline
  \cellcolor{green!27}\small sore loser... there was no \textbf{sexism}. it was a all female match. just cause a man was the ref doesn't mean that it's sexist. this story is a joke\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Serena , CK, and Mayweather are all trash Nike lmao.. if you want a \textbf{black} hero ..look at Joe Louis\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small When penalties do not hit someone properly financially they are laughable for the very rich.Penalties should always be  based on percentage of income not some fixed numers.If  one wants to have fairness one have to apply logic and \textbf{common} sense.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small After all these years she turns out a stupid feminist... \textbf{nothing} her slams and titles and as a sportswo..er..\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She is a \textbf{freak} of nature\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small He is a giant woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small He is a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small You are such a sexist🐺 because you picked another \textbf{woman} over me she's not even as \textbf{black} as I am, how dare you😭 you owe me an apology🐑 where's my apology🐍\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Racism yeah right you got to blame white people for her behaviour\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small lol, careful - she'll accuse you of \textbf{sexism}.  She has a daughter don't you know?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Sexist? She's playing against another \textbf{woman}. This is undoubtably her just being a sore looser.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small My favorite was the \textbf{racism} complaint, Naomi Osaka is half black/half asian.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She was playing with a womaaaaaaaaan!!!! How can that be \textbf{sexism}?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small remember 9 years ago when she told the line judge(a \textbf{woman}) "i will kill you" how does she stand for women's rights when she lost to a better \textbf{woman}???\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small I'm surprised he did not scream racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small she couldn't scream \textbf{racist} since Osaka is also of \textbf{black} \textbf{ethnicity}.\normalsize   & \cellcolor{green!5}Black, Ethnicity, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small In terms of \textbf{sex} equality in sports tennis must surely be the most equal. In what other sport are women competing at the same level of fame, pay and at the same major events as men? I find it sad that a sport that has given such a fantastic lifestyle and wealth of adulation to one of its greats is abused and accused with this pity me attitude. How does this help the rights or goals of women in other sports or other walks of life?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small A young girl beat an \textbf{old} \textbf{woman}. Period.\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Serena's Big \textbf{Fat} Mouth i'm glad the World saw all this maybe She had Vodka in Her Water\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I hate her.  Screaming \textbf{sexism} makes me hate her even more.  I wish she would just go away.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Women already have rights. Don't need Serena fighting for something I laready have.  What  a \textbf{dumb} statement.  Whiney, and poor loser.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Sexism in tennis? Sure women get pa8d the same for 33 less work\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small What no one seems to be picking up on is that Serena probably intentionaly misbehavedat first to throw off Osaka and to rev her own motor up. She also overplayed the situationmaybe to deflect the attention from how an unknown 20 year \textbf{old} was kicking her \textbf{fat} ass!From a talent perspective she is the best all time Womens Tennis Player! Not Classiest!!\normalsize   & \cellcolor{green!27}Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small An excellent news review and I now understand why USA is most developed and a super power people like you who say \textbf{spade} a \textbf{spade} make this country.\normalsize   & \cellcolor{green!5}Spade & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small make a special about the Silk Road guy, that was crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Regardless she should not try to overshadow the win for the other player. Just trying to make it about her. She could have filed a complaint without blasting it to the media.  So weather it is sexist or not is besides the point . She showed \textbf{zero} respect to her opponent.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small If Naomi was a white \textbf{woman} , well you know this would be a whole different conversation and not about feminism. Got to play some card.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small We all witnessed the righteous, self-entitled tantrum of a narcissist blinded by rage. No one likes losing, some people feel they let themselves and others down, they feel deep disappointment and sadness. But when someone identifies one way or another with losing the way Serena did, there's a problem... That's when you HATE losing and you have to do something about it... I don't think it's any exaggeration to point out the potential for violence here... In fact this is something I read other females players talk about as being the reason they feel intimidated by her. As in "scared" and/or "guilty" for beating her. This is one of the classic dynamics created within the narcissist field/environment.I'll leave it there.. I'm just tired of seeing her vicious manipulations and people calling it something else...(afraid and intimidated they will be accused of being \textbf{race} motivated) Please, enough of "you wronged me and you owe me an apology" BS. Nope.. you cheated (amazing she used her daughter as a reason for never cheating and having impeccable character...) I mean, just priceless, and it couldn't have happened to a more manipulative FRAUD of a person; who wasted no time to accuse the umpire of being a "thief" (who was right to make the call in the first place) and threatened with taking his job away in future matches... There, the great Serena defined. I don't give a flying F---- how many grand slams she won... She's a s----t human being, who has repeatedly displayed her ghetto intimidation tactics and the "How dare you wrong me !!!!!" BS judgments and accusations.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/268 & \cellcolor{green!5}0.373 \\  \hline
  \cellcolor{green!27}\small Music\&FXMaster, Perfect summation of this \textbf{Freak} Show Creature. ..thank you 👍\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Lisa Walker. That's sad. Things like this just make you wonder about our morals as a collective whole in society. For the most part we're all different but there should always be some things that we collectively agree won't be tolerated and an umpire needing security because he officiated a game correctly is one of them. This is just \textbf{crazy}. Poor guy.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small She was getting destroyed by Naomi. And she was frustrated even before the first warning. She know the media and SJW's will line up behind her if she called \textbf{sexism}. So even though she lost the match, it was like she won.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Lisa Walker Vast majority of people are against Serena's attitude. But it doesn't matter that much in today's society. The Mainstream media and the SJW's are projecting her a hero who fight against \textbf{sexism}. Even people who didn't know \textbf{nothing} about tennis are backing Serena. Look at Twitter post against Carlos Ramos and the likes those shitty tweets get.   The one person who was really impacted by all this is Carlos Ramos. Media is constantly attacking him and the media will continue to call him a sexist.\normalsize   & \cellcolor{green!5}Nothing, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/87 & \cellcolor{green!5}2.299 \\  \hline
  \cellcolor{green!27}\small The "live!" crowd actually at the match were overwhelmingly on Serena's side so that's probably the consensus across the U.S. The crowd was likely too \textbf{dumb} to even understand what good sportsmanship is anyway....sooo. Ain't that America?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small She must have some pretty \textbf{dumb} PR people .\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Loser, just because you're a \textbf{woman} doesn't give you privileges\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Anybody thinks the umpire looks like the \textbf{old} Djokovic?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small If she's a 19 year \textbf{old} who hasn't won a Grand Slam, and she is showing that attitude, probably I can overlook that. But for a 23 time champion who sort of the face of women tennis... I am sorry, but that attitude wasn't acceptable. She has brought shame and done damage to women tennis. Being a tennis pro she couldn't even respect the sport or her opponent. Standing up to women's equality? Best leave it to others.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small whats so \textbf{dumb} is that she thinks what she called the umpire is not as bad as what other men have called umpires. it doesnt matter what it is, she verbally abused him and didnt stop. she is in the wrong here\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small why is this sh*t even being discussed. She is a spoilt Amercan \textbf{brat} , and her \textbf{black} culture provides the lack of hunility at taking a whupping !\normalsize   & \cellcolor{green!27}Black, Brat & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Serena you have no authority to talk on behalf of women. First behave like a \textbf{woman}. More than the disgrace from Serena is the disgusting crowd. Cannot believe this is the USA\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Sore loser. Drama queen. Desrespectful deceiving biaaaatch!!!! Don't misuse and abuse being \textbf{black} being women being mother matter. Seriously.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small That thing is definitely not a \textbf{woman}. It has more muscles than a grown bull.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Serena is trying to justify one incorrect attitude referencing other incorrect attitudes!And then bringing up the \textbf{sexism} sh*t.... C'mon! Shame on Serena!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Rob Bleeker apparently serena williams is \textbf{blind} and didnt her coaches signals but she noticed osaka coach coaching from the stands but only today decided to mention that, shes \textbf{nothing} but a sore loser who has lost alot of respect and alot of fans!!!\normalsize   & \cellcolor{green!5}Blind, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Becky Bewley its the internet \textbf{nobody} cares about spelling, and its my second language so not bothered one bit about it.\normalsize   & \cellcolor{green!27}Becky, Nobody & \cellcolor{green!27}Age - Youngsters, Gender - Female intelligence & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Becky Bewley your entitled to your opinion as i am entitled to mine. You think what you think its a opinion at the end of the day, it wont bother me and im sure it wont bother serena either\normalsize   & \cellcolor{green!5}Becky & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Becky Bewley spew poison? She was cheating you idiot is that not wrong in your book or are you that native that you think that is right.\normalsize   & \cellcolor{green!27}Becky & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small It was racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small "Because I'm a \textbf{woman} you're gonna take this way from me?" Wait...was her opponent a man?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I never care much about tennis until this meltdown by this no class Serena. Typica  \textbf{black} excuses.. Everyone is out to keeps them down.. SMH\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small I've lost all respect for Serena. She threw a \textbf{paddy} because she lost. She was beaten by a quicker opponent and couldn't handle it.\normalsize   & \cellcolor{green!27}Paddy & \cellcolor{green!27}Nationality - Irish & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small The worst thing is she irreversibly spoiled Osaka's big moment, her first grand slam victory. \textbf{Nothing} can bring that moment back. For that she needs to apologize publicly not just to Osaka but to the audience she used her foul behaviour to mislead into disrespectable booing. She seemed to grasp her error in the ceremony but no, in the press conference the tantrum continued. Only a deep and humble public apology can revive her tarnished image.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small Arthur Rush...I cant see what that has to do with her behavior!! She acted shamefully, whether \textbf{black}, white, green or purple!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Osaka the big winner....! Cool temper, gracefully handled, great athlete, but over look by every body. What a sad tragedy we are living..... the unprofessional Serena Williams created more applauses to her favor because she pulled the \textbf{race} and \textbf{sexism} bait.👎🏾\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small samboggetti , \textbf{witch} was trying to distract Naoimi. Shes a filthy cheat...\normalsize   & \cellcolor{green!27}Witch & \cellcolor{green!27}Gender - Female age and physical appearance & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Women dont want you fighting for their rights. Osaka is who they want. A \textbf{woman} who handled herself with such grace.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small This is feminism. This is the insanity that the modern feminist movement produces. For anyone to defend her and her delusions of \textbf{sexism} is also deluded. Utterly shameful behavior. Shes become an ugly, angry, delusional, man hating feminist.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small i really DON'T understand his commentary.Male tennis players did say worse with no penalty and at the same time there is no \textbf{sexism}....Dude u better get together\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small The \textbf{Sexism} argument is invalid. She was playing against a \textbf{woman} so the Umpire couldn't have possibly showed biased based on \textbf{sex}. I used to have respect for Serena\normalsize   & \cellcolor{green!27}Sex, Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/29 & \cellcolor{green!27}10.345 \\  \hline
  \cellcolor{green!5}\small So many bad things. Serena's behaviour was deplorable. Then the crowd booing, was disgraceful. Then Serena doubles down in the press conference, and the media heads interviewing her were too frightened to call her out on her behaviour, tippy tapping around the subject. Finally, idiots like Billie Jean King seem to think Serena can do no wrong and this really was all about \textbf{sexism} - no calling her out about her behaviour. Thankfully Navratilova at least managed to be more balanced. And people looking in on this, like the people in the comments section here, think - what the f*** is going on in this world that Serena can act like a bully and an entitled \textbf{brat} and get praised for it?\normalsize   & \cellcolor{green!5}Brat, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/122 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Its never this races fault its deny,deny, deny then when confronted with evidence its allege targeting and \textbf{racism} to become the victim its \textbf{old} and tired but works.\normalsize   & \cellcolor{green!27}Old, Racism & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Americans are good at openly cheering for their teams and/or players regardless of whether or not are supposed to be neutral. I tried to follow a sports news commentator commenting about highlights from a Giants NFL game. It took me a second to figure what was going on. The Giants are so wonderful to the American people that when they do well, the entire league makes money.  They are the largest market.  But what this commentator was doing was calling all the Giants players by their initials.  They showed the back sides ( G ) of the players enough to where I could see the names on the players. No other players on the opposing team got the \textbf{r\textbf{ed}} carpet treatment from the TV presentor, just the Giants.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/128 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Serena is certainly not fighting for my rights as a \textbf{woman}. And she certainly doesn't represent me as a \textbf{black} \textbf{woman}.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/21 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The Japanese player Naomi wasn't a ... \textbf{woman}?!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small women right lol---women has no.rightsduring war and invasion they become \textbf{sex} slaves or c ommodities, exchangeable for food or toilet paper does slaves have rights?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small that \textbf{black} faced ogre is a sore looser, that's all.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Surely it should be the shameful way ozaka got her trophy they should be the headline. If this was a French crowd booing Serena after ozaka had lost her temper then the yanks would be going nuts. The lack of respect for the champion was utterly disgraceful and for neither Billie Jean King or the wta to denounce this says it all for me. Blaming the umpire for Serena behaviour is ridiculous. At least mcenroe admits he was a \textbf{brat}.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small +dislike 'freeloaders L. - You left out that Serena is a \textbf{tranny} and therefore could not have given birth - so it's not "her" daughter in the sense that he/she gave birth.  Serena said he/she was playing for his/her daughter.  Serena said he/she had never cheated or lied - he/she is \textbf{nothing} but a lie!Poor Naomi Osaka felt like she had to apologize for winning.  Serena stole that girl's rightful joy.\normalsize   & \cellcolor{green!5}Nothing, Tranny & \cellcolor{green!5}Age - Youngsters, Sexual Identity - Transexuality & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I totally agree, aside from her very unusual physics which makes any male GORILA jealous, she is very \textbf{racist} towards all other races specially whites and very very rude. Look at her support of the ex-football player Coil karedickhead,  she supports him not to respect the flag of this country even though Kaperdickhead grew up with ton of welfare money from hard working American taxpayers.  That is absolute shame.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Transgender ‘female' MMA fighter gives female opponent concussion, broken eye socket.  the boxing-commission doctor hands her a small plastic cup: the pregnancy test, required of female fighters\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}3/27 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small You owe me an apology, you will never umpire in my court as long as you live, you are a thief. Lowiqness from a champion of champions accrdng to that american \textbf{woman} commentator.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Serena was a poor sportsperson.Not \textbf{racist} or a poor loser.What she did is NOT about who''s right....her or the umpire, but about ruining the sporting spectacle for the audience and for her opponent.Tennis fans didn't pay to see this, or wanted to. Serena should be ashamed.  She has to write a public apology to Naomi Osaka and give her the second placed prize money because she (Serena) doesn't deserve it.Serena also needs to sack her coach.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small Why would they boo the Umpire? Mr Ramos did absolutely \textbf{nothing} wrong?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm surprised the \textbf{race} card wasn't played.  Instead of blaming the official she should blame her coach\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small So let me get this straight! Ramos hasn't fined men in the past for their foul mouths, but you state that Serena deserved her because she didn't back down! That in and of itself is a double standard! You're are judging an athletes interactions on nitpick points! Serena didn't tell the umpire to go fuck himself, which several male players have admitted to and not gotten fined. Second, the umpire can decide to give a person a warning, a fine, give set or points or all three. In this case, he decided to give the tripple whammy. Meanwhile, when men play, it is business as usual and the male players can do what they want. I don't mind Ramos having a reputation for being a hardliner! What I take issue with is that he does it more to females than to males! That a player got away with the f bomb or worse is inconsequential in this argument if a person is watching the video. Second, Naomi may play for Japan, but she is also Haitian. She is the victim in this  because she got fallout for Venus's poor sportsmanship and Ramos's sexists calls. That said, I watched the after match interviews with Naomi. I want to call Naomi's BS right here and now! Before I continue, I am not trying to make Naomi responsible for Serena's actions. Let's get this straight. However, what I saw at Naomi's press conference disturbed me. Naomi denied hearing or understanding what the debate was about! Nor did she make any comment about the situation or defend Serena for trying to help her out! WOW! You see Naomi is playing her Japanese kawaii card (kawaii means cuteness) while scheming over the fact that her father is Haitian. You see it's easier for her to do that because the majority make it so hard for people of color! When Naomi performed kawaii, she insulted Serena! Everything Serena is fighting for or has fought for, Naomi along with other players will benefit from. Case in point: Naomi is considered the victim, which should be. Yet, if the umpire association does indeed find Ramos has  been unfair in his handling of matches, he along with others will get a clear message to clean up their acts. Speaking of umpire associations, I don't mind that the UA took supported Remos. That said, the UA should also make it a point to monitor their umpires to insure there is no misconduct on their part. Returning to kawaii, because Naomi plays her kawaii card, her voice is taken from her and she is made into a puppet of what the establishment wants: a person who simply plays tennis and does not demand anything from professional tennis associations who may or may not have her best interest in mind. By staying silent, Naomi may want to appear gracious, polite and sportsmanlike, but the truth is that she hurt women, especially Asian women by living the stereotype of what the public expects out of them: quiet, polite, obedient! Because of these things, the public is more accepting of her and empathizes with her despite the personal slight against Serena, who has been made public enemy number one in all this. I'd love to see what would happen if Naomi was playing for her father's country of Haiti or if Naomi had a bad day and openly argued with an umpire. Would the public be so understanding of Naomi whose homeland is the poorest country and has the highest poverty, AIDS and illiteracy rates? When I see Naomi walking around the ghettos of Haiti, giving tennis lessons, I'll be the first to apologize for under estimating her! Until then, you need to give Serena props for standing up to unfair treatment. That said. I don't like any athlete having tantrums on the court including Serena. It makes them look immature. However, that \textbf{old} game where  Naomi is an angel and Serena the devil needs to end here and now! When Naomi opens her mouth to talk about being treated unfairly is the minute the establish will say she is spoilt and entitled--just like Serena. And this is what Serena and many people want to end so women will be treated equally, because we are not.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/712 & \cellcolor{green!27}0.14 \\  \hline
  \cellcolor{green!5}\small Serena was getting her ass beaten. Osaka had beaten her before. People forget that. So in her frustration Serena lashed out at everything. She played the female card, then victim card, then \textbf{race} card any card she could come up with. But bottom line she was out played. A sore loser is a sore loser. She knows the rules. She doesn't like the rules in tennis then go play golf. As for Trevor Noah stirring up the \textbf{race} card is just sad.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Serena should apologize to NaomiNo doubt and take a few lessons on manners and graciousness from her Please Serena don't make \textbf{race}, \textbf{gender} motherhood your reasons for losingThank God Naomi is half Japanese and Haitian, otherwise \textbf{race} would been the main reason for SerenaSerena is the thief who stole Naomi's best moment\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/55 & \cellcolor{green!27}5.455 \\  \hline
  \cellcolor{green!5}\small Sore loser!  I think she has become so arrogant, what? teaching her kids what, what?  Stop whining then.  It's never about \textbf{sexism}.  Its about how good or bad you played.  Stop blaming your shortcomings at other people...example like the umpire...your racket..etcI hope Osaka won't ever pick up any arrogance from you after few years.  Geeez\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Spoilt \textbf{brat} deluxe - down there in the dregs along with John macenroes antics. It set a really  poor example on how to behave in front of the younger generation  and was completely  out of order and unladyl like . For good examples look to the likes of roger Federer and Rafael Nadal\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Curios, she only air about \textbf{sexism} if she's about to lost a match. If i am using the same method as she is, i would accuse her as a professional victim, but hey what do i know about feminism method  of producing a proof.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small The only way the accusation of \textbf{sexism} makes any sense is if Serena's opponent on the court was of the opposite \textbf{sex}, otherwise the question remains why Naomi was not also "victimized".Unfortunately for Serena, her opponent is clearly a \textbf{woman}, so the accusation becomes ridiculous.\normalsize   & \cellcolor{green!27}Sex, Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/46 & \cellcolor{green!27}6.522 \\  \hline
  \cellcolor{green!5}\small Why not throw \textbf{racism} into it as well,the umpire was white hes racist😂😂😂😂😂😂😂😂😂😂...\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Now its hard to win against an sjw athlete they will always blame their lost to \textbf{sexism} lol\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small How can it be \textbf{sexism} when she looks like a man\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She is misleading the situation. She deliberately brought \textbf{sexism} into argument for making bigger issue . She is just a terrible \textbf{woman}. I don't care if she is the greatest \textbf{woman} player. I hate her attitude and  her manipulative behaviour .\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small How is it \textbf{SEXISM} when her OPPONENT is a \textbf{WOMAN} too?\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small The whole fiasco is absurd. I really don't see any \textbf{sexism} evident. I wonder if the umpire was a \textbf{woman} Serena would have behaved the same way? She doesn't consider her verbal abuse towards a male umpire sexist. She made herself a loser in more ways than one \& her opponent the winner in more ways than one. Even if Serena had been wronged, she completely mishandled the situation, or rather not at all. She has let herself down \& set a poor example to her fans. If you disagree, find a member of the opposite \textbf{sex} to abuse \& start throwing things in temper 😉\normalsize   & \cellcolor{green!27}Sex, Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/106 & \cellcolor{green!27}2.83 \\  \hline
  \cellcolor{green!5}\small As a \textbf{senior} citizen of the tour, she should give advice and set the example to the younger ones. Raise the roof - not lower it.🤔🤔🤔\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Blatant \textbf{Sexism}.  When Williams threatened a female lines person in the Clijster's match she was tossed immediately. Ramos had to endure minutes of William's abuse after which the \textbf{senior} officials let her continue to play. What gives?\normalsize   & \cellcolor{green!27}Senior, Sexism & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Why can't people do both? Watch sports and not be duped by the elite?  Why hasn't anyone figured out a formula to solve this ole \textbf{age} problem??\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small WOW this video clearly explains all sides, was in-depth, showed the entirety of the situation, and addressed the incorrect sexist angle Serena decided to take, accurately. (Stephen A Smith made a good response video to this incident as well) I've done my own digging and reached the same conclusions this video made, when considering the strict umpire, the code violations, diminishing Osaka's historic victory, etc. I think if Serena was able to discern that the warning for cheating was inevitable, when the ump called it, she could've stayed more focused. I think in her situation I would've reacted the same, b/c I would feel mischaracterized and clearly deny something I'm not doing. But from this strict ump's view the coach made clear coaching signals and she even admitted to seeing a thumbs up. I don't believe Serena the tennis goat would rely on coaching, but the ump operated within the rules. The ump has that luxury to make that call, if she could've taken that as just a warning and moved on I think she would've maintained her composure. Also with that initial warning i think there's a clip where Serena and the ump came to an "Understanding", they both said they understood each other but I think Serena mistook that for the ump retracting the first warning. Which would explain why she got confused about the point awarded after racket abuse. She would've thought that her racket abuse, would be her first warning.This ump is a veteran, well known for being by-the-book, and because she did call him a thief, his third violation was correct. However, since every ump is different, one could argue that this ump could've let go of that 'thief comment' because that third violation would result in a game being awarded, in a Grand Slam final. Not only is that devastating but it rarely happens in Grand Slams, and I think for good reason. Stephen Smith also made a good point that an athlete prepares for the opponent and the ump. There have also been studies that talk about this 'uncontrollable rage' athletes can experience while in the game that may affect their behavior and performance. I think it is wrong/unprofessional for a professional athlete to succumb into this intense emotion, but it can also be very difficult to control this rage. Examples: losing in a video game and breaking your property or when Tyson bit off an ear. It think it starts when someone doesn't internalize their frustration, it can consume them. Its clear she was upset and retained her upset mentality. It made me think of times when I should've let go, instead of holding on to that state of being upset. But I think it's very difficult to realize that.It reminded me of when a teammate of mine in high school football messed up a play and fumbled the ball on a punt return. I've never seen him rage this way, he threw his helmet on the floor before getting off the field and yelled like a maniac. The coach immediately scolded him and benched him for that entire game.I think whether it's a verbal or physical meltdown it's still unprofessional, unsportsmanlike, and a lack of control over emotions from both men or women. Each sport deals with unsportsmanlike conduct their own way, so dont be comparing tennis to hockey.I think in this incident, it was a meltdown. With a physical aspect coming from racket abuse. And the due to the length of her arguing and saying "because she's a \textbf{woman}" (essentially pulling the \textbf{sexism} card) was part of her verbal meltdown.Since Serena mentioned the \textbf{sexism} it became the main point of this incident, along with the perception of men and women meltdowns.Im not denying the existence of \textbf{sexism} in the present or past, but this video mentioned that men received more violations than women and the degree of their arguing was different. Also consider the female vs female match and Osaka not experiencing the \textbf{sexism} Serena felt. This doesn't appear to be a sexist ump tennis issue.I also disagree with people stating that "when it comes to women it's called a meltdown, but with men it's passionate". On one hand, no one said Tyson ripping off an ear was passionate. Most people if not all agreed, that was a disgrace and disgusting. I think people can find examples of both scenarios. Although I would consider both meltdowns, I understand that Tyson bitting an ear off is on the extreme end of the spectrum. Regardless it was still wrong on Serena and she had a meltdown and the aftermath resulted in Osaka apologizing for her victory. I still must credit Serena acknowledging Osaka's win and not saying that the "bad reffing" caused her loss or Osaka's win. Osaka had a momentus victory and as Serena said deserved to win.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}5/814 & \cellcolor{green!27}0.614 \\  \hline
  \cellcolor{green!5}\small She is victim of \textbf{sexism} as always.Keeo fight Serena.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Sore loser without a doubt.. Lost all respect for her as soon she turned to the \textbf{sexism} card😴😅..so pathetic... She's literally all over media as one of sport's top \textbf{woman} and she's making millions doing the sport she loves! Yet has the audacity to play victim jus because she was gonna lose😅....totally ruined Osaka's moment. And the pple tht were cheering for her in the back are idiotic.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Once again \textbf{black} people show what they do best.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dear serena you are there fighting womens rights, thats ok. But  on the other hand you destroyed the celebration ceremony for a \textbf{woman}, Osaka.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "I am a whaaaaaaaaman!!!! This is \textbf{sexism}" Oh letting win other \textbf{woman} is \textbf{sexism} Xddddd\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Maybe she should take it easy with the testosterone. She barely looks like a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Just the same sort of typical self-entitlement that you see from a lot of \textbf{black} women these days.The fact she's complaining of \textbf{sexism} while her opponent is also a women just proves it.\normalsize   & \cellcolor{green!5}Black, Sexism & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Serena has at least 50lbs of muscle advantage.  How can it be \textbf{sexism} when it was a match between 2 females?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small You're all incredible, one wonders if paid by this president just to divide the "nice people" angle... So quickly, ready to deject the Best Tennis Player you've ever had, because she reacted just dominantly? You seems to have forgotten all the men who've done the same...or maybe, you just hate \textbf{Black} People who wins.... Even if just jumping on a band-wagan, You are unaware of the Power of your Wife's.....! Grow up.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small Yes, we were all paid by the President to offer our opinions. I'll get my check by next Monday. That would be odd, since he doesn't give a rat's ass about tennis and neither do I. The only reason I'm here is because the media backed her, wasted my time watching news with this frivolous \textbf{racist} and sexist crap. They are the ones pressing \textbf{racism} and \textbf{sexism}. Take those things out of the equation and she's just a bad sport. \textbf{Nobody} would pay attention. They do exactly what you are doing now - "Maybe you just hate \textbf{Black} people who wins"? \textbf{Nobody} minded her winning the previous 20 times. She didn't mind, either. Only when she was already down by a set and got a warning did she decide to throw a fit. Then she broke the rules repeatedly. That ref could have penalized her for a game stoppage the first time she appealed. Or the second. Or the third. He didn't. He only did it when she started insulting him.  Maybe she knew she was going to lose and just put up a public struggle to win some support. Did that ever occur to you? As it was, she was losing even without the penalties. So what's your point? You don't have one even with a generous amount of leniency concerning your English.\normalsize   & \cellcolor{green!27}Black, Nobody, Racism, Racist, Sexism & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}6/224 & \cellcolor{green!27}2.679 \\  \hline
  \cellcolor{green!5}\small Theres no \textbf{sexism} at all.Just a mere loser.Serena was the one being rude not only once but many times in her matches.Her foul words are more than \textbf{sexism} and discriminating but humiliating to people.No respect,unprofessional and proud.You maybe at the pedestal of your career but be careful,your fall might be too high and that will hurt you.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small Serena is a baby, a big one \& here is way: She is 36 something years \textbf{old}. She is suppose to be a veteran now in this sport. A veteran, yet on the field it was like Serena was the 20 year \textbf{old} \& Osaka was the veteran. Her attitude was appaling. Having this kind of behaviour at this point in her career is just low. Heard Osaka looks up to Serena to. Is she still a fan after Serena did this? I would not be. Made the crowd turn on her \& booing her when she got the award? Serena says "She stands for women"? yeah right. She did not do much, to support a half japanese-black young tennis player, who looks up to her. Just stands there in the backround with a smirk on her face when Osaka gets booed. She is a very disgusting person. On the inside she is really nasty.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/155 & \cellcolor{green!27}1.29 \\  \hline
  \cellcolor{green!5}\small I've never seen anyone give a thumbs up without folding their fingers. Considering Serena saw that he was giving her a "thumbs up," clearly she saw the signs.Serena's \textbf{sexism} argument is so irrelevant. The rules are clear, and she was penalized according to the rules. "But the boys do it too" is so weak. It's unfortunate that Serena's childish behavior, and the fans that went along with her, marred Naomi's achievement.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small Ill make it easy to say in this case type. There was NO \textbf{SEXISM}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Sore Loser. This is Serenas 2nd time losing to Osaka. Wasnt \textbf{sexism} at all. Osaka has Serenas number.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Serena can learn a lot from Osaka: emotional and \textbf{mental} focus. Learn Serena...learn!\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small It was racism; not \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small 'Vows to fight for women?'She fought against a fellow \textbf{woman} and lost.  You have a daughter and stand by her?Serena lost to a kid(20 vs 36).Children learn from us.  When Naomi turns 36, is she going to learn from Serena and repeat her behavior?  Bitch, please.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Yes, Serena is an unprecedented shame for all women, mothers, \textbf{black} people, tennis players and Americans.Additionally, if you read more carefully, Ramos was strict to Djokovic, Nadal \& Kyrgios, they all received penalties too but were clever enough to shut up \& stop making code violations. They did not rant, threaten, abuse. And they certainly would not go to extreme lengths to justify their misbehaviour afterwards. We also need to bear in mind that top athletes have plenty of psychological preparations \& they are well in control of their emotions, that is why they can perform on that level, which implies that it is not just Serena's bad temper what we've seen, but her deliberate display of power.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/119 & \cellcolor{green!5}0.84 \\  \hline
  \cellcolor{green!27}\small Disgrace.. Unsports"\textbf{woman}"like..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small What an absolutely deplorable role model S.Williams truly is.  A contemptible self entitled \textbf{brat} with a piss poor attitude to anybody that dares to challenger her.  Tragic really!\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small So her answer is the men are abusive so you must let us? I'm sure I've seen lots of \textbf{woman} abusing the umpire for decades\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Violation number 1. Racket abuseViolation number 2.Cheating Violation number 3.Using child as a shield.Violation number 4.\textbf{Sexism} Violation number 5.Cartoon caricature 😂😂😂😂😂😂😂😂😂\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small No one should be allowed to verbally abuse the referee like that without some penalty; not a man or \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small serena was up 3-1 in the second set then she lost the next game now is 3-2 at that particular moment serena realized that she was NOT going to win the final so she broke the racquet and also realized that she was getting whipped by a 20yr \textbf{old}..this deflated and pierced her ego..and she took out on the umpire..there was absolutely no \textbf{sexism} here and i'm all in for woman's equality but this fiasco was an embarrassment..a champion should lose like a champion.\normalsize   & \cellcolor{green!5}Old, Sexism & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small So a \textbf{woman} beating another \textbf{woman} in a tennis match is sexist !Tell ya what Mrs Williams why don't you mix it with the men and lets see how you get on !\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small No \textbf{sexism}, the winner was another \textbf{woman}. If both women were to loose and the winner was a man; that's \textbf{sexism}. How can you call it \textbf{sexism} when the winner is another \textbf{woman}? She's fighting for women's rights!? What about Osaka's victory? She won and she's a \textbf{woman} with rights. We don't need Serena to fight for the rights for women.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}6/61 & \cellcolor{green!5}9.836 \\  \hline
  \cellcolor{green!27}\small Stop throwing all the cards ... it's not \textbf{sexism} it's poor sportsmanship . Also, Ramos penalized other male athletes like Novack and fined so nice try!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Serena has had an outstanding career and accomplished many things.  But she is also getting on in years.  You can't win against the 20 year olds forever.  The fact that she is still so competitive at her \textbf{age} is a testament to her outstanding athleticism.But I don't see how a penalty could have been sexist.  That was out of bounds.  It was a \textbf{woman}'s game and Osaka is a \textbf{woman}.  The call perhaps could be construed as \textbf{racist} perhaps, but with Osaka also being a person of color that would also have been quite a stretch.Calling someone \textbf{racist} or sexist in today's world is one of the deepest insults you can level at them, especially if it isn't true.  It's worse than liar or thief for sure, both of which also seem to be unfounded accusations she leveled at the ref.The original call of coaching might not have been necessary but what was the penalty?  1 "point"?  I'm not sure exactly what that means but I think it would be equivalent to losing one serve.  It should not have been a big deal.  Then she smashed her racket, which is unprofessional and cost her another point.  But calling the ref a thief, a liar, sexist, and threatening his livelihood was simply over the top.And anyway even without the penalties Osaka probably would have won.  You can't win them all, not even if your name is Serena.Serena was gracious towards Osaka afterwards though, and that goes a long ways towards me being able to forgive the whole thing as just an outburst due to stress.  She should probably publicly apologize for calling the ref sexist though.\normalsize   & \cellcolor{green!5}Age, Racist, Woman & \cellcolor{green!5}Age - General, Ethnicity - General, Gender - General & \cellcolor{green!5}4/280 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Its not a \textbf{woman}!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Serena is much like a Muslim. Extremely vocal in her own victimhood and desperately clinging to the dream that someone cares despite her own complete lack of empathy for anyone else. All in all a pretty horrible person. What a shame that while she was standing up for women's rights that she didn't notice the \textbf{black} \textbf{woman} standing right next to her who had just won the match. Ofcourse most people advocating equality eventually get to the point where they believe that the only sure fire way to achieve equality is to eliminate everyone else. I guess we should just be glad that she is a tennis player and not a world leader\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/113 & \cellcolor{green!5}1.77 \\  \hline
  \cellcolor{green!27}\small All those wins mean \textbf{nothing} now\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Serena succesfully got our attention off the fact that she was defeated by a very young \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small She knew her coach was coaching - he even admitted it.Yet she denied it.She was losing.She then proceeded to bust her racket (lack of respect for property - and there is a kid to there that is going to be a great tennis player and could have used that racket, but I digress) and gets a penalty for it. Oh, and she is still losing.  Badly.Then she has the nerve to threaten the referee?Yea, I have no sympathy.  He got beaten by a girl.  And he has the nerve to cry \textbf{sexism}.  LO-fucking-L!!!!!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small ABW Syndrome !!!!  She doesn't have a temper She Has ABW Syndrome!  Watch some Tommy Sotomajor he'll explain it perfectly.  It's gross!!! But, \textbf{common} in the culture.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small She lost to a 20 year \textbf{old} sore loser\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small What do you expect from a spoiled \textbf{black} \textbf{woman}. I'm surprised she's not calling him \textbf{racist}.\normalsize   & \cellcolor{green!5}Black, Racist, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}3/16 & \cellcolor{green!5}18.75 \\  \hline
  \cellcolor{green!27}\small tbh, I don't even think Sxxxxa Wxxxxxxs is really a female, probably a \textbf{transgender}.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small the umpire is known to be very strict to men before women..... she quickly tried into \textbf{sexism} 😂\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small She received coaching, argued with the umpire, had harsh words etc etc. Par for the course for Serena Williams. No big deal. But the accusation of \textbf{sexism} is cheap shot, cunningly calculated to turn a simple issue of a tennis violation into a sociopolitical one of \textbf{gender} discrimination and get the feminists on her side. Yup, the victim card. An fight between a \textbf{black} motorist and white motorist does not automatically mean it's a racial attack. A punishment by a male teacher on a female student does not mean the teacher is a \textbf{misogynist}.\normalsize   & \cellcolor{green!27}Black, Gender, Misogynist, Sexism & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}4/94 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small There was no \textbf{sexism}, since the beneficiary of Serena's punishment was a \textbf{woman}. Even if Ramos had acted unlawfully, how could helping Naomi Osaka be considered \textbf{sexism} against women? It makes no sense.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/33 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small if you can read this Serena...know that you are a cheat, a liar, a card player....a disgrace....that poor girl Osaka, humiliated and insulted on the world stage because of your spoilt \textbf{brat} antics......there fighting for 'women's rights'? you must be joking\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small That's a genetic \textbf{freak} , if she has a vagina . I'd need to see it to believe she's not a man . Which would make her one ugly women\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Yes, the winner has to apologize to a tantrum throwing \textbf{sexism} blaming cry baby.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small You Lost \textbf{snowflake}, get over it. It wasn't \textbf{sexism}, it was your bad playing and delusional sense of entitlement.\normalsize   & \cellcolor{green!5}Sexism, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Gender - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Apart from her being beaten fair and square, the other great thing to come out of all this is that it set the far left feminists cause back about 20 years, as we all got to see   (even her supporters)   her  play the ridiculous feminist \textbf{gender} card and bomb out badly. At that moment even a child could see through all the bull shit theyve been spinning. This one in incident totally exposed all other ridiculous \textbf{gender} claims.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I have never cheated in my life! I have a daughter and I have never cheated in my life! I am a \textbf{woman} and I have never cheated in my life! I am a \textbf{black} \textbf{woman} and I have never cheated in my life! You know, not so long ago, this is the sort of a diatribe you would have heard coming from an insane person being dragged off to an institution.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/72 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Serena is a great man player, not a great \textbf{woman} player. Will people stop calling Serena a She already.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Every intelligent person MUST and ACCEPT that there is no pure \textbf{race} on earth and every \textbf{gender} is unique ! Get a life, all of you, people who have negative and jaded souls! We must concentrate instead of global warming and other negative things that are and will give us problem to live the life that God gives us to live !!!\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Guess the Big \textbf{Apple} is very rotten that they couldn't hide it.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Il faut éviter toute polémique et propos racistes sur les deux joueuses qui ont très bien joué ! Cessons de venir avec des caricatures disgracieuses non pas pour les personnes ciblées mais pour celui ou celle qui produit ces dessins.  Tout le monde qui parle d'elle ou de sa famille devrait se concentrer surtout sur ce qui se passe dans le monde comme le ''global warming  le changement de climats à travers le monde'', les virus et autres problèmes pouvant éviter les hommes de profiter de cette belle terre que Dieu nous a donné ! À tous ceux qui parlent de sa famille, laissez-moi vous aider à voir la différence entre elle et vous, entre sa famille et la votre : Voici la différence : Si vous étiez son père,  ne pratiqueriez-vous pas la vantardise ?  Alors que lui n'en fait pas ! Ils sont fiers de leur origine et vous, en êtes-vous fiers?  Il n'y a pas de \textbf{race} pure, toute personne intelligente devrait le savoir !\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/169 & \cellcolor{green!5}0.592 \\  \hline
  \cellcolor{green!27}\small America has become a feminist nightmare and it shows clearly in this situation.  Women are never responsible, it is always (((\textbf{sexism}))).  Wumenz Feelingz.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small serena williams is a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small It is NOT a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Getting coaching.... breaking racket.... threatening umpire/line referees.... acting like a \textbf{snowflake}.... thinking she is better than everyone around her.... really embarrassing display... Great playing OSAKA!!!!\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small The poor girl was sad that she won her first US open wow women's sports when are overseers did not want her to win liberalism is a \textbf{mental} disorder sepal people. That means the brainwashed young people and the liberal teachers who hate everything mostly us and our country. Sucks to be young as they are taught to hate the world I came from thanks liberals your hate is growing if you don't believe me watch how people start fighting man what's going to happen to us is because of liberals. Just saying. ..................!!\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small Sore loser, cheat, spectacularly committed liar and bully. We know she was cheating because she said "he was just giving me a thumbs up". She couldn't have known that without looking but then also claimed she never looked. Furthermore the signal itself while obvious was not obvious in its meaning. The coach was doing it in the knowledge that his player would see it and understand the meaning. So there's no doubt she's a cheat and, because she then denied having done so in the most strident possible terms, also a liar. That no-coaching rule btw is absurd. Eating a \textbf{banana} could mean "go to the net", removing a cap could mean "attack the forehand" etc etc.\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/117 & \cellcolor{green!5}0.855 \\  \hline
  \cellcolor{green!27}\small Serena was in a battle to win in anyway she could but the distraction did not deter Niomi Osaka's focus. The judge definitely did not exhibit \textbf{sexism} in anyway. Serena lost, get over it girl.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small She's a dirty apple\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Sorry,, loser Osaka only 20 years \textbf{old} and SERENA she is getting older and 37 years \textbf{old} THAT LIKE A mother playing with DOUGTHER   ,sorry SERENA  you are getting ,,RUSTY,, \textbf{OLD} LADYIT IS TIME TO RETIRE  😔😕🤔😟😔😕🤔\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/38 & \cellcolor{green!27}7.895 \\  \hline
  \cellcolor{green!5}\small 1.8 million dollars says there's not much \textbf{sexism}, \textbf{racism} or discrimination.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small So she also threatens him and his job. Not just calling him a Lier as she and the media is trying to make out. This only happens when she is losing, it's happened before. She likes to threaten umpire. It is not \textbf{sexism}, in fact more male players were penalized than female. So how is that \textbf{sexism}. She broke the rules, with a umpire who is known for being a stickler.... sounds not only unprofessional but stupid.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small There's this trick. Don't threaten the man who controls the game with you taking away his job. There is rampant \textbf{sexism} here. The sexist person  is Serena Williams.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Angry \textbf{black} \textbf{woman}, troupe. Fine.I predict Serena will shoving alot of balls up peoples asses on the court in the future.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small This was not a man vs \textbf{woman} issue nor was it a \textbf{race} issue. Simply put this was about violations of rules and poor misconduct. Shame on Serena, breaking rules and poor misconduct have consequences\normalsize   & \cellcolor{green!5}Race, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Serena, when you are on the court play Tennis and fight for your victory. Don't fight for \textbf{woman} or for their equality.  What a loser!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Women rights and women equality? What about man rights and man equality? The White man did not do anything to \textbf{Black} women. She proved on Live TV that she is a \textbf{Black} \textbf{Racist} and Hates the White people. She did not blamed herself for losing, she did not point the finger on the Japanese \textbf{woman} that was winning, she blamed the White man next to her. Everything is Racists to the Blacks and they blame some White person next to them, when they themselves are the losers.\normalsize   & \cellcolor{green!5}Black, Racist, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/87 & \cellcolor{green!5}4.598 \\  \hline
  \cellcolor{green!27}\small Pathetic entitled sore loser \textbf{brat} ... It has \textbf{nothing} to do with \textbf{sexism} (both women) .. Nor \textbf{racism}, Naomi is blasian ... Congratulations Naomi !!! .. Naomi is a humble sweet great girl... Serena is an entitled ugly drama queen\normalsize   & \cellcolor{green!27}Brat, Nothing, Racism, Sexism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}4/40 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Serena is a shameless sore looser! Congratulations to Naomi Osaka! As for Sir Carlos Ramos unfortunatly he is a victim (like many other Men) of this craziness some \textbf{crazy} people call \textbf{sexism}. If my wife hits me with a pan or a broom I will not go to the police because they will laugh at me! Thank god that does not happen in my reallity, because if my wife tries to hit me with a broom I will order her to ride it to hell!\normalsize   & \cellcolor{green!5}Crazy, Sexism & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small 'Because i am a \textbf{woman}'.. since when is a \textbf{transgender} man a \textbf{woman}?? He is the real thief. Playing against real natural born women and stealing their possible victories and money..\normalsize   & \cellcolor{green!27}Transgender, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small She is a piece of work, says no coaching, he says he did, dear God help us, she cheated period.   She is just tarnishing her legacy.  I have a daughter, I'm a \textbf{woman}, womens rights, men do it worse, blah blah blah, and it's this b.s., \textbf{sexism}, all that sets any legitimacy of today's feminism into a laughing stock we all know it is.  I'm sure the female umpire was sexist too.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Why did Serena accused the umpire of \textbf{sexism}?, they were both women that were playing wern't they?, or perhaps she is a man pretending to be a \textbf{woman} and that's why. Personally, I'm a white middle aged western man and all this is rather beneath me, let the kids play.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small you know whats \textbf{sexism}?  When women only play 3 sets because they are SO weak.  Had it been a 5 set GS LIKE IT SHOULD BE.  Serena stops, composes herself, and maybe wins the match in 4 or 5 sets.  But wamen are not equal.  FACT\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Guillermo Vega I agree she took her spotlight away Because she feels victimized for being \textbf{transgender}? Hoops did I say that out loud SRS has come along way\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small +kevin gallagher We're not, we are blaming every United Statian. That's proof 1 and also of your stupidity, there is no such country called America, it's a continent and here's where the ugly or arrogant "American" part come in, you believe you own the continent or should own it, and tried to, at least the north half in the war of 1812, when we kicked your ass and burnt down your capitol (Canadian if you haven't guessed). Speaking of war, here's a little joke that also explains why the world thinks of you as Ugly "Americans". The rest of the world gave shit to the US for joining WW II late and that pissed them of so much that to ever avoid that kind of criticism again, they've started every war since...lol. And finally the latest in a long list of things your country does to make the rest of the world hate you, you elected a \textbf{racist}, sexist, \textbf{homophobic} bully, who according to John Kerry on Real Time last night (Sept/14/2018) and I along with the rest of the world agree with, has the maturity of an 8 year \textbf{old} boy with the insecurity of a teenage girl. I could also go on about both your Dem. and Rep. leaders attacking your own troops and people. LBJ (Dem.) and the USS Liberty  [LINK]  and Bush with 9/11 and and Trumptard and the Republicunts with Syria.  [LINK] \normalsize   & \cellcolor{green!5}Homophobic, Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General, Sexual Identity - General & \cellcolor{green!5}3/237 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small \@Dennis Robertson I agree with your point. It's just funny the way you said United Statian when we're called American when spoken of in a collective. I see why you see things the way you do, but Canada and Mexico are not part of the United States. We're still American. We're called the United States or the AMERICAS. United States was the original "America". So we're American. If spoken of in a collective sense continentally, Canada, Mexico and United States make up NORTH America. So they are called NORTH Americans. Just as Brazilian and Venezuelan people are Venezuelan and Brazilian separately, but when spoken of collectively combined, they're SOUTH Americans because of the continent.  Just as South Africa is its own seperate country in  Africa, but still part of the \textbf{African} continent. Make sense?\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small Sexism? She knew her opponent was a \textbf{woman}, didn't she?\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small How can she be a victim of \textbf{sexism} when her opponent was also a woman\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small If Ramos would have been a \textbf{black} \textbf{woman} and Serena a white \textbf{woman}....Come on, you know what would happen to Serena....\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Serena owes the umpire an apology. She was a disgrace with her whining and carrying on. What an absolute embarrassment of a \textbf{freak} show Serena was. Tried playing the \textbf{gender} card saying that this is only happening bc she's a \textbf{woman}. It was her job to keep track of her penalties. She said that her coach just did a thumbs up and went on a ridiculous clueless rant berating the ump. Then the coach admits he was coaching and the replay showed that the coach was doing a lot more than a thumbs up. Strike 1 and a warning. Then she smashes her racket. 2nd offense and a point is awarded to her opponent. Then she gets all uppity and again starts berating and mouthing off to the ump culminating in calling the ump a thief. The ump had had enough of princess serena's mouthing off and rightly gave her strike 3 for verbal abuse. Game penalty awarded to Naomi. It was serena's job to know that she had 2 strikes and that the 3rd would mean a game penalty but no... she's still all uppity and makin' a jagoff outta herself. She starts blathering about how she's a champion on the court and a champion of issues away from the court. Translation: When she's done with tennis she wants to be some kinda ridiculous left wing mouthpiece, yawnnnnn.... Go fuck yourself you disgrace. You stole the moment from Naomi with your childish tirades where you were WRONG on every aspect and point. Naomi crushed Serena and woulda beat her anyway but jesus christ what an embarrassment. She made a complete spectacle of herself and the ny crowd was terrible and rude. Fuck you Serena, you've tarnished your image for life. No class.\normalsize   & \cellcolor{green!27}Freak, Gender, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/293 & \cellcolor{green!27}1.024 \\  \hline
  \cellcolor{green!5}\small Fabio Fognini was kicked out of the US open in 2017 for yelling at the (female) umpire.  She was not kicked out, merely penalized.  Now, THAT is \textbf{sexism}.  She only played the \textbf{sexism} card when she saw that she was only making things worse for herself and had no other justification.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small Who cares what you think this is really getting \textbf{old}.   Men do it all the time.  I have watched tennis for years and men use profanity and everything else.  She should fire the Coach.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Glad others noticed as well and for those \textbf{old} enough to rememberJohn McEnroe used to do the same thing and always when things weregoing against him...never when the match was going for him.Perhaps they are great champions but they suck as human beings.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Flawless reporting. However one important detail which you missed and should have included is that Osaka was the first \textbf{woman} from Japan AND Haiti to win a grand slam tournament. Yes she represents Japan but she is also of Haitian background (from her father's side). This is also significant. Aside from that, you really did present the arguments well.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small "I'm a \textbf{woman}"... Has a thicker neck than the referee.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Is it just me or what but it seems like all of Serena's game that she played up till now...many if not nearly all of her opponents looks more feminine? I don't think I'm \textbf{racist} since it's been proven that blacks or rather people of \textbf{African} decent tend to possess more athletic prowess than other \textbf{race} in general when it comes to activities being physical in nature. Yes...evolution does play a part as Africa is a harsh place therefore the people must evolved to adapt. She's blessed to have such prowess and wasn't expecting much to her current opponent when she started realizing she was starting to lose and that's when she basically used the "sexist" card against the empire. Osaka is half Haitian which is of \textbf{African} decent therefore she also possess some prowess in the field, add that to her \textbf{age} and she really is in her prime. Serena you are a sore loser simple as that!\normalsize   & \cellcolor{green!27}African, Age, Race, Racist & \cellcolor{green!27}Age - General, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}5/159 & \cellcolor{green!27}3.145 \\  \hline
  \cellcolor{green!5}\small We saw someone have a \textbf{mental} breakdown and a show of true colors.Like all blk wemon she's a victim of mean sexist white men damn our masculinity!!¥\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Serena acted unprofessionally at this US Open, no doubt! And her negative conduct on the court, is what ultimately spoiled Naomi's special moment during the trophy presentation. And that was really sad and disgraceful. Because, Naomi certainly deserved better. She played great. And she is such a humble and sweet young \textbf{woman}. But, I wish that people would stop acting as though this is something Serena does all the time.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small 1. It was \textbf{sexism} on SERENAS part.2. How can it be sexist if she is playing against another \textbf{woman}?3. Her coach admitted that she was indeed cheating and therefore the penalties were more then justified.4. Such childish behaviour should get her ass banned for a couple months. It was beyond pathetic.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small SERENA IS A MAN, HIS FEATURES ARE SHOWING MORE NOW THAT HE IS \textbf{AGEING}.VERY UGLY.\normalsize   & \cellcolor{green!27}Ageing & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Sore loser, a spoilt privileged \textbf{brat} that completely took away the limelight from Osaka's magnificent victory.Spitting your dummy when you are losing is pathetic.Osaka called her her ‘idol'.Well, there's an \textbf{old} saying...'Never meet your idols' And this is exactly why.\normalsize   & \cellcolor{green!5}Brat, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Is this a neurological disorder or what? I don't think a sane person can act like that. If we did not have tapes, probably a lot of women, especially \textbf{black} women would have believed her and witch-hunted the umpire. He was a Caucasian, so it would have been doubly bad for him. This kind of behaviour is bad for women, because now real \textbf{sexual} discriminations would be considered like this case.\normalsize   & \cellcolor{green!27}Black, Sexual & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small Arguing with the ref generally doesnt give you a penalty but arguing after every single geme would give you one, most players dont do this, and even less go as further as to actually threat and insult the ref. I dont know what andy roddick said that was worst but if it was and the umpire didnt penalize then it was a bad call, and djokovic was penalized by ramos multiple times so i dont know what he is even arguing about. Is it that \textbf{weird} that insulting a ref is a code violation? in football is a \textbf{y\textbf{e\textbf{llow}}} card in basketball is a technicall, this is litterally a rule in every sport.\normalsize   & \cellcolor{green!5}Weird, Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/113 & \cellcolor{green!5}3.54 \\  \hline
  \cellcolor{green!27}\small If you're asking if she's a victim of \textbf{sexism} you are an imbecile. Serena has a history of foul behaviour. It's easy to find the videos of her being abusive and aggressive towards officials.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Good job. Fair and straight to the point. Any unbiased person can see whose behavior is in question here. Out of control behavior has no \textbf{gender}, \textbf{race} or \textbf{nationality}. It happens all the time, but more frequently from some who thinks he or she can get away with it. She was at home, so she felt she was in charge. She played a victim so she could get her supporters to back her up. The lauder them became the more she increased her barrage against a man who was just doing his job. A very good job we must say! Give this real man the \$17,000.00 they collected from the abuser. She went home with more than a million. The penalty to be effective it needs to cause a pain in the pocket of the offender. The penalty amount should be a substantial percentage of what they are taking home. That will stop or decrease this abusive manipulation of the game (which is a form of cheating). This behavior is being used by some dishonest players not only in tennis but other sports as well. Humans will push the limits as long as they are allowed to. With all the attention they are getting for doing what is wrong, they won't be motivated to change. Can we honestly blame them for pushing the rules, if they are being allowed to? The decline in our society's morals is creating more opportunities for this barrage to be tolerated, encouraged, excused, and insanely justified. As one general famously said once, 'NUTS'.\normalsize   & \cellcolor{green!5}Gender, Nationality, Race & \cellcolor{green!5}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}3/258 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small Drama queen...covering up her pathetic performance against osaka under her \textbf{sexism} drama\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Serena was upset for two reasons. One: She was getting her butt kicked and was on the verge of losing anyway. Two: She was upset because her and her coach was caught cheating. She claimed she didn't see the coaching yet when she approached the umpire she told him just because her coach has two thumbs up that doesn't mean he is coaching. So that should tell you right there she was lying. The fact of the matter is she is a poor loser. She becomes emotionally unstable like a three year \textbf{old} \textbf{brat}, when she is losing. I hope they play again and Naomi destroys her.\normalsize   & \cellcolor{green!5}Brat, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small No. Her coach later admitted he was in fact coaching her with his hand gestures. So she knew exactly what he was doing. And guess what...so did the umpire.  But to cover herself and her coach from embarrassment, she had to deny the accusations by attacking the umpire's judgement.  In other words..."How dare you catch us cheating. I won't allow you to embarrass me in front of the world, so I have to protect my image and integrity by attacking  yours. I have to accuse you of being ignorant and bias. I can't say you are a \textbf{racist} because Naomi is a \textbf{woman} of color also. But since you are a man...I can accuse you of \textbf{sexism}. "\normalsize   & \cellcolor{green!27}Racist, Sexism, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/118 & \cellcolor{green!27}2.542 \\  \hline
  \cellcolor{green!5}\small The Umpire was going by the rule book (no \textbf{sexism} was involved).\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small What the hell is wrong with people. Booing at a 20-year \textbf{old} girl who won absolutely fair and square, and who has shown remarkable talent, achieved through iron discipline and big sacrifices. I want to give her a hug and a huge high five. I hope she can forget about the spiteful people that wouldn't give her the roaring praise she truly deserved. Williams should be ashamed. She has played a long and succesful carreer and yet hasn't learned to deal with her temper. Even IF she was judged unfairly, she should know better than to resort such childish behaviour. What should have been one of the highlights of Osaka's carreer was deflated by Serena's drama (and with help of ignorant members of the audience). Luckily she is still young, and with her grace and humble attitude, I hope to see Osaka rise to the top and staying there.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/149 & \cellcolor{green!27}0.671 \\  \hline
  \cellcolor{green!5}\small \@Thor L that's the Japanese culture. Shyness. She probably a lot more awareWhat's going on than you think. ExtremelyIntelligent \textbf{woman} if she didn't no it thenShe's figured it out by now. Osaka is myFavorite\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Definitely a sore loser without any class nor any regard for the winner! Trying to use this platform for her feminist agenda was very inappropriate. She brought the sport in disrepute by behaving like a spoilt and entitled \textbf{brat}!✨✨\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Serena Williams is not only a sore loser but a bully and a primitive character. She is a disgrace to the sport. No question. But then she plays the \textbf{sexism} card and hey....all of a sudden \textbf{nobody} cares about rules and decency anymore....just \textbf{crazy}!\normalsize   & \cellcolor{green!5}Crazy, Nobody, Sexism & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/44 & \cellcolor{green!5}6.818 \\  \hline
  \cellcolor{green!27}\small The fact of the matter is, he has his hands moving from side to side in parallel encouraging her to move forwards and attack. His thumbs are sticking in the air at the same time but I agree , it is not a thumbs up it is just the way he has positioned his thumbs. However, stupid \textbf{fat} bints like Marion Bartoli have said there is no way he could have seen him which is obviously a load of bollocks as Williams interpreted his signal (according to her) as a thumbs up of encouragement. If she wanted to claim she had no coaching then she should have simply said "I didn't see anything" - it was her saying "when he holds his thumbs up, it's not coaching" that gave the game away that she had clearly seen him.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/138 & \cellcolor{green!27}0.725 \\  \hline
  \cellcolor{green!5}\small \@Nozomi Yu-chan bruh, the coach ADMITTED TO COACHING, AFTER THE MATCH. Claimed that everyone else does it, I'll use that excuse next time I get pulled over for speeding. Let's see how that works. (I'll pull the \textbf{racist} card as a back up, me being Mexican and all). 👌🤣🤣🤣\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small He was signalling for her to run toward the Net..She saw Him,so did her Sister..She was sitting next to him..!!Crap Speech from \textbf{Woman} Official and Crap Crowd👎\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Because she's a mother.. And a \textbf{woman}..\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small She is a victim of of \textbf{SEXISM} in the sports world. Why are you all so against Serena and her talent as a tennis player? Is it because she is a \textbf{black}? I'm just curious. Did any of you think it was classless the racial cartoon they depicted of her? I did. I'm honestly disgusted... sick to my stomach 🤢\normalsize   & \cellcolor{green!27}Black, Sexism & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small dj Blackwing, Even spoiled babies, have absolutely \textbf{nothing} on this \textbf{freak} show, ...and they certainly don't pull the sexism/racism cards\normalsize   & \cellcolor{green!5}Freak, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small How can it be sexist when the only person who benefited from "discrimination" was another minority \textbf{woman}?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small If Naomi Osaka was White, Serena would probably use the \textbf{Black} card. But she used the alternative — sexism\normalsize   & \cellcolor{green!5}Black, Sexism & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Actually, she also failed at using the alternative, since her opponent was also a \textbf{woman}. She should have used the "I have a daughter" option more, would've probably gained her more sympathy.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Why are you selling a \textbf{race} card to other commenters?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small damn671, Did you miss the part where sHE pulled the \textbf{racist} card ? Just like HEr 'left leg', ....sHE claimed:  ...It's not Right \& not "Fair" 🙄😉\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small This mashine is soooo horrificly disgusting that I want to vomit. This used to be \textbf{woman} is a pumped up mashine full with steroides and doping. Disgusting! Disgusting! Playing the victim! What a joke this mashine is.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Although \textbf{sexism} wasn't clear, there are many sexists in this comment section. They just get sucked in by the title. Such lack of grey thinking from them. Sad!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Rules are \textbf{gender} neutral.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small She was about to lose the match. So she needed to make this drama to make herself look as a victim. She completely ruined Naomi ‘s moment. What upsets me is the Serena then started to act like a good person asking the audience to stop booing while it was her fault that the audience was booing and Naomi had to apologize. Shame on her and shame on the audience who made this 20 year \textbf{old} young innocent humble girl cry.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small At this point, I've seen A LOT of evidence, including here in this video, that male athletes can and do get away with similar behavior. Why are so many people so hell-bent on denying the existence of \textbf{sexism}? This video even admits that "like many great athletes, Serena Williams has a temper." The match went the way it went, Serena lost, and that part's not up for debate. She's calling it out in the hope that future female athletes won't be penalized for having passion (which is what we usually call it when a man gets upset, as opposed to "hysterical" or "sore loser" and "out of control"). Why is it so upsetting for someone to address double standards? Oh, yeah, I suppose a lot of men appreciate the uneven playing field, whether they recognize it as such or not...\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/140 & \cellcolor{green!5}0.714 \\  \hline
  \cellcolor{green!27}\small Sexism or \textbf{racism}?!?!? You be the judge!!!!!\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small the victim card is so easy to play..weak people love it.You broke the rules and got caught, when I played hockey and I broke the rules to retaliate to someone who also did it; i still got a penalty...BECAUSE I BROKE THE RULES.Also how are you standing up for women's rights, when you were playing a \textbf{WOMAN}.She in the past has threatened female umpires.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Williams was wrong. I did not see \textbf{sexism} in the game. She was a sore loser and took it out on the umpire period.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Woman?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small yes on the \textbf{sexism} but doesn't excuse her for her outburst\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It's not \textbf{sexism}, rather bold umpiring\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Remember that \textbf{transgender} men are allowed to play in women's tennis without revealing their true \textbf{gender}. Look it up.\normalsize   & \cellcolor{green!27}Gender, Transgender & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small If the chair umpire was a \textbf{woman}, Serena would of probably found some other excuse.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I followed Serena from a very long time... If u think she did all this becoz she is losing, i think you should have watched the match, game penalty came when the score was serena 3-4 osaka and serena was the one to serve and the penalty gave osaka a game lead that means serena lost the opportunity to equal the score on her serve, if penalty is not there, osaka needs to break serena serve to get the match. I am saying all these, because i have seen serena coming back even at the last moments to claim the matches. I am saying all these because i have seen djokovic, murray saying things to umpire but never got any penalty. So i think her point is very clear. BTW i am not american, i am an \textbf{indian} and i support serena not because what she won, because of her oncourt grace. If you don't support serena that's absolutely fine but don't say bullshit things to her, because serena lost the match. Even if she won the match you guys would have told that she distracted osaka with her tantrums and won. Anyhow you guys will not say good things to serena, because you don't like her. You can watch the wimbledon final 2018, australian open final 2016,  \textbf{indian} wells final 2016 when she lost to kerber  and azarenka she acted like a champions by encouraging them. I know there would be lots of negative comments to my comment because you guys are so sick that you want to spread negativity about serena. Also i would not respond to any comments now because all i need to say i said.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/280 & \cellcolor{green!27}0.714 \\  \hline
  \cellcolor{green!5}\small anyone defending that \textbf{mental} behavior is an idiot..\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small "But they do it too" doesn't absolve you of your own mistakes. This is a logical falacy I wish would die How other people act has \textbf{NOTHING} to do with how you act\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small victim of \textbf{sexism}? did umpire break the rules or did she?? more discusion is pointless..\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Victim of \textbf{sexism} or sore loser?  Can it be both?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The video shows Serena's coach looking at some place within the tennis court and doing coaching gestures. Unless he is \textbf{crazy}, he was certainly looking at Serena. He would not have done coaching gestures if Serena wasn't looking back at him! Therefore, this "I wasn't looking" excuse is totally \textbf{lame}.\normalsize   & \cellcolor{green!5}Crazy, Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small She's a sore loser! Blame it all on \textbf{sexism}?! EXACTLY!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Its the wirld we live in. She was trying to make a reason y she loet. Not because she was out beat, but because the judge is sexiest and racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Leave it to \textbf{woman} to make everything looks sexist.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She's a man/transgender just like her BROTHER Venus. What do you expect with all that testosterone. They've been scamming the entire \textbf{blind} ass tennis world since they showed up. The USTA and ITF are all in on it. They know these are the Williams brothers not sisters. Damn people are \textbf{blind} as hell!!!!!!!!! HOW CAN YOU NOT SEE THIS?!??!?! IS EVERYBODY \textbf{G\textbf{AY}} NOW OR SOMETHING EXCEPT FOR ME?!?!?!?!?!\normalsize   & \cellcolor{green!5}Blind, Gay & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}4/68 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small How can she be the victim of \textbf{sexism}? Her opponent was female. Didn't notice the umpire being sexist toward Osaka.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Imagine what she would have said if she was playing against a white \textbf{woman}. Her opponent is a \textbf{black} and Asian mixed \textbf{immigrant}, there was no other card for her left to draw\normalsize   & \cellcolor{green!5}Black, Immigrant, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General, Nationality - General & \cellcolor{green!5}3/33 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Chris Chris Chris. I did not expect you to have joined the "\textbf{sexism} in sport" cult. Because that's what you did when you showed gave the Boston Marathon example. Things have changed since then. There is no \textbf{sexism} in sport. There are sexIST individuals, but there is no \textbf{sexISM}. I have never been so disappointed before. I quite like your videos, but this, this \textbf{sexism} line of yours, well, I will still watch your videos, but I like you a lot less.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/82 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small She says the Ref took the game from her, stole the game from her. What he did had \textbf{nothing} to do with her playing a bad game.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Ignore the booing Naomi. Like you said 'this is New York', you are not the first to be booed at the Arthur Asshe Stadium in 'New Yourk'. They did this to Pete Sampras too. Kind of difficult to be different \textbf{nationality} and different shade (of skin) to be playing Tennis in New York. That is just the fact. (WTF - What the Fact). Sports is meant to bring people together whether you are Japanese, \textbf{Indian} or whatever political boundary you are from.\normalsize   & \cellcolor{green!27}Indian, Nationality & \cellcolor{green!27}Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}2/82 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small she played child card, \textbf{sexism} card, if osaka is white, SW would play the \textbf{race} card too\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small No \textbf{sexism} at alleven if just women are penalized and men not (statistics say is not the case), this is not \textbf{sexism} because women don't compete with men, so this mean just that men tornaments are degrading and women tournaments are more correct, that is not \textbf{sexism}But a young player lose her unique chance to enjoy her first GS win as she deserved SHAMEPS her coach shake is had after coaching gesture something like "you get it, ok !", that means they had visual contact\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/88 & \cellcolor{green!27}3.409 \\  \hline
  \cellcolor{green!5}\small Despicable behavior from Serena and the crowd. Have watched and played tennis for decades. Arguing a ruling (even passionately) is allowed in both the ATP and WTA, however umpire name calling crosses the line and is not tolerated in either, nor am I aware of any sport that tolerates it. Yes you have seen top players, Djokovic , Nadal,..., as well as female players, argue a call without penalty, but  derogatory name calling is an instant \textbf{r\textbf{ed}} card  (violation) for both.  Carlos Ramos actually let it go on longer than I have seen some umpires tolerate it. Likely the greatest female player of all time. A good sport and honest? No! Shame of Serena, shame on the booing crowd. It is also interesting to me that \textbf{nobody} called out the USTA (who run the event) for breaking the rules and seating Serena 17th when see was actually 26th  in order to protect her from losing in the early rounds to the top seeds. Wow Katrina Adams (president), you pulled a fast one and got off free. I can't find anyone discussing that!\normalsize   & \cellcolor{green!5}Nobody, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}3/182 & \cellcolor{green!5}1.648 \\  \hline
  \cellcolor{green!27}\small Katrina Adams lost a lot of credibility when she announced, after Serena's horrible behavior,  that Serena was a good role model.   I'm guessing Katrina is a bit \textbf{racist} and has her own private agenda.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Serena.....\textbf{NOTHING} you did helps women in ANY way ,shape or form. (I'm a \textbf{woman}) You play a GAME.......period.\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Naomi Osaka gracious winner, so proud and happy for her.. Serena Williams,  a disgrace to America and a disgrace to \textbf{black} people everywhere.What a loser.... she is a hater and unattractive inside.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Why is it being reported that serena may not have seen the signal! She clearly said to Ramos, When he gives me a thumbs up bla bla bla... So how did she know the call was for thumbs etc., if she didn't see it? I believe that proves she saw, but \textbf{nobody} is mentioning that.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small I watched a video comparing Serena to a man and suggesting she could be \textbf{transsexual}. That never occurred to me before but now s/he totals looks male to me in general and the racket smash was totally ‘lady boy-esque'. Could this be possible?\normalsize   & \cellcolor{green!27}Transsexual & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small But she's correct in the new court of popular opinion because White men are always \textbf{racist} and/or sexist, and the umpire was a White man.  So she can say whatever she wants, however she wants, with impunity.  She's justified because he's a White man.  Sort of a twisted quid pro quo.  EndWhitePeople.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Sexism im tennis but they get the same pay for playing half the time. Only sport wjere it happens. Men should also play 3 sets in slams.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Her illogical \textbf{woman} brain\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I don't think you realise this all happened BEFORE she lost the match. So I don't understand where you are getting sore loser from. And how many times has Serena made a comeback in such difficult situations? The lying and thieving umpire also stole Serena's chance for a comeback in that match. \textbf{Nobody} knows what would have happened. It seems everyone was desperate for Serena Williams to lose to Osaka, so you got what you wanted and now shut the fuck up! 😏🙄😳🤷‍♀️🤷‍♀️\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small Serena Williams is definitely a sore  looser,  She was  ashamed by that  20 year \textbf{old} Naomi Osaka both on and off the tennis court\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small SERENA WILLIAMS demonstrated poor sportsmanship, in a bad example for all of our children, including her daughter.  But I do think the cartoon drawing of her was \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Serena brought our Sport into Disrepute. No ifs. No buts. To outsiders, we must look so incredibly dysfunctional if our Grand-Slam tournament can look as shambolic as it did by the hands of one single player. The essence of this sport, "Sportsmanship" died a miserable death on American soil by the hands of an American. Didn't anybody tell Serena "not to shit on your own door step"? Pity Mouratoglu didn't learn how to hand signal that message. He would have saved us and poor Naomi much anguish. It has taken Serena decades of hard work, tenacity and professionalism to build her reputation. Is it worth losing it all in \textbf{Crazy} moments like this? She will reflect upon this episode with regret I'm sure for years to come but will need to look long and hard at elements in her team and their destructive nature. No 24th GS is worth winning at this kind of cost.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/155 & \cellcolor{green!5}0.645 \\  \hline
  \cellcolor{green!27}\small I don't believe that Serena is calling \textbf{sexism} because she doesn't want to admit she was losing... I believe that she thinks she is SO GREAT that she couldn't possibly be losing without there being some form of discrimination. Obviously, there is some sexims involved by male players not being punished, but you can't use that excuse to clear yoir own wrong doings. That's like killing 3 people but saying 'Jeffrey Dalmer killed WAY more so you should be let off'.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Yes she is above the sports because she is The Serena Williams. No rules could be applied to her because she is The Serena Williams. She was fighting for women's rights because she is the chosen one. She wasn't bullying him, neither did she threaten him because she is a classy women with character. She didn't pulled out \textbf{race} card, women card, mother card, because she pulled out the truth card symbolising feminsm. She wasn't upset or frustrated because someone is going to beat her twice in a row. She is a mother and that's why she could never cheat and couldn't be wrong ever. She is not a liar but her coach is. She didn't stole Naomi's moment because she was fighting for her. PS:  Indeed Serena Williams is a great role model and great example for women in particular and sports in general. It wouldn't be wrong if I call her the Goddess of Tennis. My Respect for her got increased 10 folds. 🙏\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/166 & \cellcolor{green!5}0.602 \\  \hline
  \cellcolor{green!27}\small Terrible behaviour by her. \textbf{Sexism}. Pfft.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small why are americans so attracted to \textbf{racism} \textbf{sexism} and all that bullshit......such sensitive SJWs\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small First of all Serena is the greatest tennis player of all time and I've been a Serena Williams fan forever however in this particular case she was just being a sore loser. You just cannot keep talking trash to the umpire and then act surprise when you get penalized. She knows the rules and should have acted accordingly. This had \textbf{nothing} to do with \textbf{sexism}, Osaka just outplayed her and fully deserve credit.\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small Blind blacks like you hurt my brain. Greatest of all time? Lolololololol. Wake up man.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small She's a spoilt, entitled \textbf{brat}.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Neither,it was clearly \textbf{racism}.But she to DAMN STUPID to say it.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Re. \textbf{racism} and sexism: Williams got politicized, but does not have the inellectual level to understand for what she's used for! BUT her character??!! Both Williams sisters get practically in every match illegal coached; this is a FACT! Everybody in the circus knows this! How ever, she started this episode or theater first to break her opponent's rhythm = very unsportive and unfair. Then she lost temper and went against the chairman because he did NOT let himself intimidate, what is the general purpose of the "Williams show";  to intimidate people incl. the opponent on the other side of the net! I hope in future in every Williams match there are people enough who have a eye on her coaching staff around the court! (it is NOT just 1 person!).\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/130 & \cellcolor{green!27}0.769 \\  \hline
  \cellcolor{green!5}\small Sore loser and bringing \textbf{sexism} and everything else into her arguments is disgraceful.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Kathy Fisher   I don't think you get it.  You obviously aren't \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Her opponent was \textbf{o\textbf{r\textbf{iental}}} so your \textbf{race} card is invalid\normalsize   & \cellcolor{green!5}Oriental, Race & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}4/10 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Oh-I forgot, there are special rules for \textbf{black} tennis players...? And now I guess women with little girls too.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Dean-where else can you cheat, lie, break your toys, yell at the adults making sure the rules are followed, and throw temper tantrums, accuse the officials of \textbf{sexism}, and throw a fit with the very people who allowed her to play in their tournament and then take almost 2 million dollars from them.  Only in America...the US Open.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small Now that's more like a \textbf{woman} i would give all my respect to. Bravo Ma'am, lots of respect and  power to you !\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small firetheho, I don't think it has anything to do with color. The drama started because of illegal coaching from her team, and the rules are clear. Others including herself might bring in color, \textbf{sexism} etc whether deliberate or otherwise... they are irrelevant. The violations committed by her team and herself are as clear as day light. No ambiguity.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small \@Katy O'Neil I agree overall with your comments. The remarks made by Williams don't stand up to scrutiny. The \textbf{sexism} charge is bogus. Look at female tennis players getting the same prize money as men for working fewer hours. Last year a male Italian player got a far worse fine than Williams for his own misconduct with a suspended grand slam ban hanging over him after it. In 1990 john McEnroe was disqualified from the Australian open for his own misconduct. At the us open far more code violations were given against men than women. Williams was not fighting for all women everywhere when she threatened a female line judge before her disqualification against Kim clijsters there in 2009. She should have got her focus back after the first code violation and used her own experience to get back in the match against an inexperienced opponent. Instead she lost her discipline destroying any chance of a comeback. You cannot do that in any sport. Naomi Osaka deserved her victory and the way the presenters and the crowd treated her was a disgrace. In mitigation Williams did not take any of her anger out on Osaka but the poor atmosphere she stoked led to this.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/204 & \cellcolor{green!27}0.49 \\  \hline
  \cellcolor{green!5}\small Randy   The \textbf{race} card works with any \textbf{race}, as long as you are \textbf{black}.  Don't you know how to pretend?\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/20 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small Katana Aerobatic    It does if you are Serena Williams.  She is just like her father, the big \textbf{black} turkey.   Just ask him.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small trying to think of a right that a man has that a \textbf{woman} doesn't\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Sexism or sore loser? Yes to both.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I believe this is \textbf{sexism} personally.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Typical behaviour of  a narcicssist! Bullies, looses temper, and makes the opponent feel guilty for winning! Poor Osaka! She could not handle a narcissist and covered her face in shame for winning? This terrible \textbf{woman} Serena knows how to manipulate people and rob them of their victories and self esteem! Shame on Serena Williams!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small I feel for Osaka who had to put up with this immaturity .   " Cause I'm a \textbf{woman} " hhmmm , doubtful.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small How can it be \textbf{sexism} when the player she's up against is also a \textbf{woman}?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Definitely a sore looser!  But as usual women use the excuse of \textbf{sexism} against them.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small How can there be \textbf{sexism} when both are females?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Oh yeah she uses the 'i am a \textbf{woman} card' . She is a narcissist! Pull her down from her high chair....Oh man what I dislike those who think they are entitled...Time to go Serena! Make space for some new winners!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Even the SJW's are finding it hard to call it \textbf{sexism}.ps. Yes she saw the coaching- otherwise how did she know it was a " thumbs up"?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Fighting for women equality ? Fuhhh.. Lady you were playing for the title for the money , stop playing that \textbf{sexism} card everywhere!!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small She is just a sore loser, has a super small temper, there is no reason for any tennis association to back up Serena and yes, waaay more men tennis players get penalized then \textbf{woman} players, start watching the sport and dont just stand on Serens side because she fights for "Womans rights" 😂. That is the dumbest thing i have ever heard her say ...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small No \textbf{sexism}. Ramos applied the rules and the protocol of professional tennis as they exists. Serena is a great champion. Respect to her for getting back to such a high level after having a child. But Serena can also become arrogant, insulting, a bad sport and a bully when she doesn't get her way. That's what happened.🤔🇨🇺🇺🇸\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small If a \textbf{woman} say you are sexist, then you are sexist. Gotta respect women's opinion\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small The color of her skin or \textbf{gender} is not in question but the content of her character...Her past performance on Court confirm her shortcomings. Instead of selecting who she want to have as an umpire, she may be lucky that anyone in future will want to officiate in her matches. The 20 year \textbf{old}, Naomi Osaka put the spectators to shame by apologizing for winning.\normalsize   & \cellcolor{green!5}Gender, Old & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small The sorest loser from this match was the \textbf{black} community. They couldn't boast about Serena Williams winning so instead they try to start drama about Naomi Osaka being biracial, trying to claim that she should be considered \textbf{black} because of her dad just to then their community can steal her victory. Pretty pathetic how much they seem to care what her \textbf{race} is or what her \textbf{nationality} is when just a week ago, they didn't even know who she was.\normalsize   & \cellcolor{green!27}Black, Nationality, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!27}4/80 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small If she is against \textbf{sexism}, why does she not battle to get women to play 5 sets like the men do, or lobby for the lowering of the man's game to that of the ladies (3sets)? Look at average match times men and women and then compare pay. I do not hear her doing anything about that.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Just another entitled racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Looked more like Washed up to me. Naomi had the \textbf{age} and health on her. She couldn't deal with that properly\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The umpire was obviously a misogynistic Pig and should apologise to Serena Williams. This was without a doubt a \textbf{racist} move by the umpire to eliminate Serena Williams from the tournament. I want to see him fired and also forced to pay a fine and go on public television to apologise.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small It is all based on stating that SHE was responsible for her coach's hand movements on the sideline, which insiders say is \textbf{common}. I feel Serena was pretty controlled of herself. Opponent getting a point for her loss of cool is itself barbaric imo. All things considered, I feel something is rigged against Serena here.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Looks like a muscled bound dude with a \textbf{black} tutu on.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Why do people put this \textbf{woman} on a pedestal? She's a diva. Pulling the \textbf{sexism} card is a childish response to what is  unprofessional behaviour on her part.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She was both. She was a sore looser,  that one is obvious and of course she was sexist, if the umpire was a \textbf{woman} she wouldn't behave like that. Oh... Wait, she also argued with a female umpire....Ok, she would not use "I am a \textbf{woman}"  on a female umpire.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small Two wrong doesn't make it right. Just because men and others violate the rules doesn't mean you can do the same and try to get away with it and used \textbf{sexism} as an excuse? Sore Loser!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Serena was warned about the coaching, she obviously broke the racquet and she definitely called the umpire a liar and a thief, she was punished according to the rules. Throwing a tantrum and crying \textbf{sexism} doesn't change what she did, and those who defend her are helping to push her excuses into the headlines and spoiling the victory of an up and coming player, shame.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small She's just lump\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Serena Williams has always treated the ballgirls at matches totally disrespectfully at many matches. Plus she seems to hate men. I'd say Serena is a sexist herself. \textbf{Sexism} goes both way. I believe she's going to lose a large sum of her fan base.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small She is a disgusting example of what is wrong in sports today. No sportsmanship...or sportswomanship ...or sportspersonship...whatever you like. Over entitled selfish, juvenile and completely unacceptable. She should have been thrown of the court if she could not behave in a sporting manner. Too much money in sports makes the players think they have a special right to behave like an arsehole and get away with it. Big, big scary looking , childish \textbf{woman} whose behaviour on that day, and also on a lot more days judging by some of the clips I've seen, was \textbf{nothing} more than a petulant bitch. Bitch might be too strong a word for some, lol, but I think it fits here.\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/117 & \cellcolor{green!5}1.709 \\  \hline
  \cellcolor{green!27}\small "\textbf{Sexism} or Sore Loser"How about both....\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Well it could have been a case of \textbf{sexism} if she were playing against a male opponent,..\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Are you kidding me a "Victim of \textbf{Sexism}" really.?!, she was playing another female not a man, can't really even use the \textbf{race} card in this situation, that obviously leaves "Sore Loser", this was a prime example of unsportsmanlike conduct and she should be banned, I agree fully with the umpires all not wanting to be up on the stand when she plays, she did this to herself, oh' but the point was the umpire was a man and thats where the issues begin, so I'm guessing things would be completely different if it was a \textbf{woman} on the stand, is this what we are supposed to believe, I think Serena Williams is a entitled feeling player, someone get her a participation trophy and maybe she'll calm down a bit.\normalsize   & \cellcolor{green!27}Race, Sexism, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/130 & \cellcolor{green!27}2.308 \\  \hline
  \cellcolor{green!5}\small She lost sorely \& blamed it on \textbf{sexism}, she did a nice job playing the "\textbf{Black} \textbf{Woman} Victim."\normalsize   & \cellcolor{green!5}Black, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/18 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Not sure if he is a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The chair umpire is victim of \textbf{sexism} bc he was abused bc of his gender\normalsize   & \cellcolor{green!5}Gender, Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Making this about '\textbf{sexism}' was a big mistake on Williams' part. Although it seems more likely from the evidence that she was being coached, there is still a large grey area with regard to that. It's entirely possible that the coach did it on his own, and she didn't use it, instead, realizing how it could be misconstrued, she openly admitted what the coach was doing. On the other hand, she may have been lying to cover it up. Who knows. What is justified is the second penalty. If implying 'dishonesty' about an 'official' is classified as verbal abuse, then she certainly did violate that one. Perhaps she was being treated unfairly at first, but not because of \textbf{sexism}. She just had a disagreement with the official on a judgement call, which happens all the time in sports, but instead of quietly and begrudgingly accepting the decision, she made a big scene and retaliated verbally. That is on her, not the official. Making this about \textbf{sexism} after the fact removes any sympathy I may have had for her. If instead she owed up to the facts and tried to be as accepting of the possibility of how she may be wrong, and then defended her actions, that would look a lot better on her part. Instead, she's being childish and just accusing the person she disagrees with of being a bad person (sexist). That's how a child responds to speech they don't like. Rather than respectfully disagreeing, they call each other names.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/252 & \cellcolor{green!27}0.794 \\  \hline
  \cellcolor{green!5}\small Used to like Serena. But now  I see she is not only ugly on the outside but also on the inside. Fade away and get \textbf{old} gracefully so that we dont have to be embarrassed by you any more.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Sexism? Well let women play men if she really wants equality\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small How can it be \textbf{sexism} when Serena was facing another women.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small At last \textbf{common} sense about this Sore(ena) Loser!\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She been a professional and a running champion for to long and she's full of it, she thought she won't get penalized because shes \textbf{black} shes a women or she's a running champion, regardless if your a professional you know what's better.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I can relate with my ex girlfriend.First she cheated, then claimed she was not a cheater.Then i showed her proof, she accused me of stalking.Then i broke up with her, she started to whine to everyone, i used her as she is a \textbf{woman} and only \textbf{woman} can be used (by logic of feminists).\& then when everyone understood she was a characterless slut, she went to her parents and cried, everyone was defaming her, \textbf{nothing} of the rumor is true.A PERFECT REPRESENTATION OF MODERN DAY'S WOMEN\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/91 & \cellcolor{green!27}3.297 \\  \hline
  \cellcolor{green!5}\small she's a rotten \textbf{brat} ... always has been\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Sore loser. Typical women. And yes am \textbf{black} got \textbf{nothing} to do with \textbf{racism} nor \textbf{sexism}, but I also love tennis and have respect for her. But this time Osaka was brilliant and precise. And she won fair and square. Serena was just was a sore whine loser. End of story. Yes I've sat the whole 2 hr game.\normalsize   & \cellcolor{green!27}Black, Nothing, Racism, Sexism & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}4/59 & \cellcolor{green!27}6.78 \\  \hline
  \cellcolor{green!5}\small Should have waited until after the match to make a formal complaint but took it upon herself to accuse Ramos of something she has no proof of.Even Serena's coach later admitted to coaching which drew the first code violation and is essentially just a warning.Serena berating the male umpire is instigating and pestering. Demanding an apology from Ramos is \textbf{nothing} short of bullying. Ramos did a fine job and Serena should be suspended for next years USO.It is Serena that owes Ramos the apology.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small Woman lost to another \textbf{woman}. \textbf{Sexism}!!!\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/6 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Well, a \textbf{woman} was playing a \textbf{woman}, so the 'sexism' card won't fly. So, I'm going with 'the spoiled rotten princess who didn't get her way' card.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Do women get get penalized at a higher rate than men? If people want to investigate whether there is \textbf{sexism} in tennis, that might be a good place to start.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Refs in every sport need to crack down on all unsportsmanlike conduct. Osaka is a \textbf{woman}, it's not \textbf{sexism}. The ref had not opportunity to commit \textbf{sexism} because Serena wasn't playing against a man. She might imply \textbf{racism}, you know that some kind of latin American is \textbf{racist} against \textbf{black} people, and for some reason, just wants Japanese people to win at everything... but damn that'd be digging up an even more vile cultural maggots. But female vs female is as even as the playing field is going to get, and as more men become "Women" and demand entry into women athletic leagues because of trans rights how much longer is someone like Serena really going to dominate the show... LOL you know what, I'm just going to shut-up because the entire western world is just a hot mess right now.\normalsize   & \cellcolor{green!5}Black, Racism, Racist, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}6/141 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small I think he gave a very fair analysis. I don't know if calling the umpire a thief was what tipped it over the edge for him, but after she started threatening the umpire with "you will never work on the same court as me again", I really wasn't surprised she got the code violation.The point penalty for racket abuse was correct. If you totally break your racket it pretty much always gets you a code violation, for both men and women. If you slam your racket and don't "break" it, they'll usually let those slide. So that's why sometimes players slam their racket and then keep playing with it for another couple of points.And breaking your racket isn't very unusual. But normally players never break their racket after already having 1 code violation because \textbf{nobody} wants a point penalty.When Serena slammed her racket, she 100 knew that she was going to get a point penalty (being the 2nd code violation). Then she wanted the umpire to go back and remove the 1st code violation so she wouldn't get the point penalty. That literally never happens in tennis. She knew this. It's not really fair of her to \textbf{freak} out about that.So her getting that point penalty had \textbf{nothing} to do with \textbf{sexism}. She got that penalty because just lost a game that made it look like she would lose the match and she was pissed.Also, I don't think she should come out looking positive because she tried to salvage the ceremony that she ruined by creating a huge drama right before she was about to lose.\normalsize   & \cellcolor{green!27}Freak, Nobody, Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/271 & \cellcolor{green!27}1.476 \\  \hline
  \cellcolor{green!5}\small I don't care who they are or what sport they play, tantrums are completely unprofessional, childish and unacceptable. I loathe when Kyrgios has a 'dummy spit' and I loathed it when Serena Williams did likewise. But what I really despised is Serena Williams fans booing Osaka's victory, now THAT smacked of \textbf{racism} and bad sportsmanship.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Oh, and she's definitely a sore loser. She's trying to use her \textbf{race} and \textbf{gender} to deflect from criticism, but it isn't fooling anyone outside of the left.\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small She is full of shit. Take the penalty like a \textbf{woman}, not a baby.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small jerry caughron Or worse: they show the same rude behaviour\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Let's see...1) Williams actually did commit those violations. Her coach admitted to the illegal coaching. She broke her racket against the ground. She called the umpire a liar and a thief.2) The umpire acted within the rules of tennis.3) Her opponent was a \textbf{woman}.4) This umpire has given other male tennis players the same penalties for similar violations.5) Williams has a history of verbally abusing and threatening umpires... female umpires.I'm gonna say the problem here is Serena Williams.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Grow up \textbf{woman}. Just follow the rules\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Raz Khan Rules r rules. Her coach took a chance and got caught, whether she saw it or not is irrelevant. She should have lashed out at the coach, not the ump. Or r u suggesting that the ump should have turned a \textbf{blind} eye, ignored it and gave her preferential treatment?  Isn't preferential treatment one form of cheating? What happened to you athlete rather lose than cheat?\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Nelson Luis Freire , WOW Nelson Luis I loved your comments and you Nailed it and Serena that Shameless \textbf{woman} you see her talking with her mouth wide open she was just putting an act by praising Naomi were she didn't even meant one percent also very very Selfish lady wondering how people like her for what a big fan following Bullshit and by the way God Bless Naomi Osaka 👍\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small \@Raz Khan Shoot the messenger? The umpire should be credited for standing up to \textbf{racism} and bullying on the world stage. Ms Osaka and the umpire still have their credibility and integrity.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small wendef ung. There is no evidence that she saw and understood her coach's signals as coaching. I believe in 'innocent until proven guilty.' For example. You could be \textbf{racist}. You could be sexist. I wouldn't make any assumptions about it based on your comments that seem to be against Serena. Thus I asked you. If you tell me you are not, and I don't have any evidence to the contrary, I will believe you. As I believe Serena. The difference between Serena and you is \textbf{nothing}. \textbf{Black}, white, men, women...I would believe everyone equally...unless there is undeniable or irrefutable evidence against them.\normalsize   & \cellcolor{green!27}Black, Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/102 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Raz Khan I never said she saw and understood the coachs signal. I said it's IRELEVANT she saw it or not. Are u trying to play \textbf{dumb} now?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small wendef ung. 'Are you trying to play \textbf{dumb} now.' If I am, it is only to try and get through to you, Sir/Madam.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Raz Khan, Congrats! You finally got it. Yes, it's entirely up to the ump to make the call. Temporarily blindness (didn't see), cognitive dissonance (didnt understand) or memory lapse (don't remember), none of those are valid defenses. Otherwise, no violation calls would ever stick if all a player has to do is play \textbf{dumb}. Once again, they r not even disputing the coaching violation despite Serena maintaining her innocence which is totally irrelevant. Remember, ignorance is not a defense.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small wendef ung. Yes it is up to the umpire, and in this case, it is clear to me that he made he wrong one. What an insignificant YouTube viewer like you or I think about it does not matter. Which is why I would like to see an investigation by competent authorities to see if Ramos overstepped his authority, or was motivated by a racial or sexist bias. And your problem with that is? I'm here because I believe an athlete was wronged because either she is a \textbf{woman} or she is \textbf{black}. Because I believe women should be treated equally, and color means squat. \textbf{Black}, white, \textbf{y\textbf{e\textbf{llow}}}, brown...we all bleed \textbf{r\textbf{ed}}. Why are you here?\normalsize   & \cellcolor{green!27}Black, Red, Woman, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Gender - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}8/116 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small THE CHAIR UMPIRE IS A DAM DISGRACE TO TENNIS HE GAVE THAT SECOND SET TO OSAKA PERIOD KERBER.BEAT SERENA AT WIMBLEDON IT WAS FAIR BUT OSAKA DIDN'T WIN THAT SECOND SET IT WAS GIVEN TO HER BUT AM HAPPY FOR OSAKA BUT THAT CHAIR UMPIRE IS A \textbf{RACIST} BASTARD\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Sore loser and a many of \textbf{black} men have told me a \textbf{black} \textbf{woman} don't know when to shut the hell up. That's why quite a few lose their husbands and boyfriends and why the guys cheat on 'em. They can't handle it any more. If she would have shut that mouth.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small I think it is unfortunately accurate to the event, and it is also a \textbf{black} eye to her religious beliefs. Siding with Colin Kaepernick was bad enough, but this outburst shows her to not be a Jehovah's Witness by any definition. She should retire in embarrassment.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Sore loser. I am a man. But I emphasize with women who really are victims of \textbf{sexism}. In my opinion, in no way is this \textbf{sexism}. Serena Williams hates to lose. \textbf{Nothing} wrong with that. However, if she was a real champion of society, she would have a). Said her piece about not being coached (as she did) and then leave it alone until after the match, and/or b). Never had a temper tantrum in the first place\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/78 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small This is the same \textbf{woman} who did the Crip walk after her sister was murdered by Crip Gang Members and had an affair with her married coach....the same coach who gave her those illegal hand signals.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small It was not about Osaka and congratulations to this young lady 👏🏼job well done 🗯Serena Williams always stand up and stay strong and stand firm to what you believe and don't allow no one to knock you off your game...G.O.A.T  Worlds greatest female tennis 🎾 player in history 👑💕💕💕nor to attack your character and your integrity , and I agree with you ☝️you are a gift from God and a daughter, sister, wife, and a mother  and  daughter who will be looking up to you and you were right 👍🏼unfortunately it was in the mist of the game🗯. Thank you keep up the great work 👏🏼👏🏼👏🏼❤️👏🏼👏🏼👏🏼👑👏🏼👏🏼👏🏼❤️👏🏼👏🏼Bravo....who cares about you \textbf{racist} people out there....lol... congratulations Japanese and \textbf{black} Osaka..another \textbf{black} female tennis awesome player...key word \textbf{black} lol....hats off the the queen 👑 and princess 👸...you haters will find something wrong with her too 🤦‍♀️\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/144 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Three infractions...that's what \textbf{nobody} is admitting\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I'm a \textbf{woman}, I have a daughter, I'm a mom!!! Then go be a mom.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Great athlete, small "\textbf{woman}"\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small She is a sore loser.Her opponent was also a \textbf{woman}, so there is no way the ref could have been behaving in a sexist way, as you can't be sexist against a \textbf{woman} by showing favor to one.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Serena received a game penalty for verbal abuse on her 3rd violation.  The rules are as follows: 1st violation = warning, 2nd violation = point penalty, 3rd violation = game penalty.  Most players (men or women) do not reach a 3rd violation; they control their temper after the 1st or 2nd while Serena did not.  For her to blame \textbf{sexism} is disingenuous and childish.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small You forgot \textbf{RACISM} moron, Serena deals with \textbf{RACISM} because she didn't deal with in the beginning of her career.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small It is not \textbf{sexism} it is \textbf{racism}. How is it \textbf{racism} you may ask as both are \textbf{colored} players? I would argue that in the \textbf{racism} hierarchy blacks are at the bottom...I am an \textbf{Indian} and I know how an \textbf{Indian} (brown) is \textbf{racist} towards blacks....My argument is simple...IF BOTH THE COACHES WERE COACHING WHY WARN SERENA ALONE? WHY NOT BOTH? THE ANSWER IS SIMPLE: THE UMPIRE EITHER DOES NOT LIKE SERENA ( \textbf{BLACK}) OR JUST WANT ATTENTION....\normalsize   & \cellcolor{green!5}Black, Colored, Indian, Racism, Racist, Sexism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}9/78 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small she's just a little \textbf{crazy} biach who can't take too loose and a cheater\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small It is unfortunate to see such behavior from Serena. This behavior only makes her look as a very bad loser, very weak person, with this episode the respect of her fans and people in general had for her is jeopardized and it will change. The rules apply to everyone, including Serena Williams. The fact that she can't accept that these rules are to be respected is something that she totally disregarded, I though she knew better. It is clear that coaching is not allowed in Gran Slams, period!!! Even Chris Evert while broadcasting this match, said that Serena was watching her coach when he was sending signals to Serena to move to the net. Besides that it doesn't matter if Serena saw the coach coaching her, if the coach is coaching even if the player doesn't see him/her, this is going to get the player a penalty.Who does she think she is? I think Serena is the one with double standard rather than the empire. If she portraits herself as a super champion, an advocate for equality, etc. etc. why can she not back all this up with fairness and intelligence? Why does she expect to be treated differently than any other player, male or female and hide herself in all kind of ridiculous causes that some of them don't merit to even be mentioned because they simply don't make any sense. She is simply an arrogant and weak person trying to convince the world differently. I am a mother of a daughter and son and it was pathetic and embarrassing to see her behavior. Not a role model at all or someone to admire regardless of of her victories, Serena is simply someone too hungry for another Grand Slam and she couldn't bear the possibility that she was going to lose and she took it up on the umpire. Who is the unfair person here, Serena or the Umpire? The rules are there to be applied. I feel sorry for the umpire who is told to apply the rules, but specially the WTA and ATP are backing up Serena, tennis fans are also very disappointed at these organizations for not keeping the sport with high moral standards and double standards like in this situation, they need to put it this together ASAP before they lose more credibility. In a nutshell, it is all about Serena. She didn't think for a minute that she was ruining the entire match, this includes, the real Champion Naomi Osaka, all the spectators, all the fans in the entire world, the tennis world, the young tennis players to name some,I find this absolutely irresponsible and acceptable. Then she tried to console Naomi during the ceremony which is a joke. Serena has received so much credit for this in circumstances that Serena created this horrific situation, but so many \textbf{blind} people are out there that can't see this clear because a lot of them don't know anything about the rules in Grand Slams or they just can't think objectively and without emotions.Serena, this is for you, it is time to retire, there are new gracious champions coming, i.e. Naomi Osaka!!! Jelena Ostapenko.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/528 & \cellcolor{green!5}0.189 \\  \hline
  \cellcolor{green!27}\small Want me to create double standards out of \textbf{thin} air? Watch me.Imagine that, instead of Serena, you had Djokovic at the US Open final. He receives the same punishment from, say Louise Engzell (Swedish female umpire in case you don't know). He proceeds to react the same exact way than Serena. Smashes his racket, shouts at her that he deserves an apology, calls her a thief and so and so. Then he calls the tournament director and cries that what she's done is unfair. Now please tell me who in their right mind is going to defend him?It's easy to yammer about \textbf{sexism} as soon as a man punishes a \textbf{woman} for violating the rules. It's even easier to create double standards that have no basis in reality.\normalsize   & \cellcolor{green!27}Sexism, Thin, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}3/130 & \cellcolor{green!27}2.308 \\  \hline
  \cellcolor{green!5}\small Damn. Imagine that \textbf{crazy} umpire trying to follow the rules.  Every single one of those people that booed that you \textbf{woman} for playing a great game and winning to live out her dream should feel so ashamed.\normalsize   & \cellcolor{green!5}Crazy, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Sigh, williams took the moment from Osaka. But tennis is still sexist and \textbf{racist} af. I mean y'all need to search "tennis tantrums" here and you'll see that men players are more \textbf{common} showing discontent and anger.\normalsize   & \cellcolor{green!27}Common, Racist & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small I would NEVER be proud of anyone who acted like she did.  This is \textbf{nothing} to do with her skin colour or how much she earns - its about her breaking the rules and getting penalised for it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small There is no debate. No parent could be proud of a child that behaves like that let alone a person approaching 40 years of \textbf{age} behaving like that.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I'm confused by the "\textbf{sexism}" accusations. Isn't Serena Williams actually Mike Tyson in a wig?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small it's not \textbf{sexism} if it'll favour another woman\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Serena could never get over the fact that she is \textbf{fat} and ugly, so she always tried to mask that with her play ability. Great tennis player but bad sportsman and person. After retirement she should spend some serious time for therapy. She can afford it, I guess...\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Stacey Mobley  Naomi is a Japanese professional tennis player and Serena is a American professional tennis player. These are reference toward there \textbf{nationality}, not there race/ethnicity.\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small How this \textbf{sexism} if her opponent was a women as well. If Niomi lost could she have said she lost because of \textbf{sexism} as well?\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Lord Justiceor more like feminism isn't mature yet. Men have been taught to face the consequence for bad behaviours and attitudes for centuries while feminism just grows last century after all.I would say that today's feminism is the dark \textbf{age} of feminism.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small surprised she did not cry racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Well  done Umpire.  Who  the hell does  this arrogant  \textbf{woman}  think  she is?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I see it as sore loser, she couldn't play the \textbf{race} card because the ref, isnt american, and its not \textbf{sexism} because the other girl didn't get any warnings. end.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small 3:30 manliest \textbf{woman} on earth. And the terrible sexists gave the points to another \textbf{woman}. Find another excuse for your rage. Not a man's fault that you cant follow the rules\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small "I don't know what to say or do because I'm a sore loser so I'm gonna use the \textbf{sexism} card" Stop acting like a child, you threw a fit and looked stupid so you had to try and make it about "women's equality". Give me a break..Everyone is trying to take her side because she's \textbf{black} and probably gonna use the \textbf{race} card next...I mean, it's what everyone does when they have \textbf{nothing} else to say.\normalsize   & \cellcolor{green!5}Black, Nothing, Race, Sexism & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/76 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small He's being sexist to a \textbf{woman}, playing a \textbf{woman}. How does that work? She's just a sore loser. Being called a thief and liar are pretty big insults. It's not like she called him a poopy-faced booger-eater.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Being a \textbf{woman} is like being a dog. Its really REALLY impressive if they can do something a man can do. My dog can open doors, so can my sister like wtf how smart are they?!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Cheat, get caught, then deny, then insult, then destroy stuff and then blame the punishment on \textbf{sexism}. She truely knows no shame.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Serena Williams talks about being a mother and setting an example for her child, and in the next breath she acts like a two year \textbf{old} and throws a tantrum.  Maybe instead of letting women get away with more because men do it, we should make men live up to a higher standard.  Your getting paid millions to play a game. Grow up.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Serena bit off more than she could chew Naomi is near half her \textbf{age} and out played her .she should of let Naomi enjoy her victory but instead she destroyed it\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small SHE HAS A DAUGHTER. SHE WOULD NEVER CHEAT!!!!!! We all know the judge is a sexist, \textbf{racist}, and a \textbf{nazi}.\normalsize   & \cellcolor{green!5}Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She's \textbf{nothing} but a sore loser throwing a temper tantrum because she didn't get her way. Face it she cheated and got called out for it. Seriously,  she needs to grow the hell up and deal with her loss.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small She is an appalling human being! And as a \textbf{woman}, I'll just say it- what a \textbf{fatso}!\normalsize   & \cellcolor{green!5}Fatso, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small The coaching ruling should be reexamined if Everybody Does it. \textbf{Nobody} Does it or Everybody Does it. It can become a gamechanger in tennis.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Angry \textbf{black} \textbf{woman} LOL\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small It's a shame that \textbf{sexism} is just casually thrown about as an excuse nowadays despite it still being prevalent and carrying serious consequences when a man is accused.I think  that if false allegations are made in sports whomever made them should be banned regardless of whomever they are.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Apple withholds \$250billion from flowing freely in the marketplace. How many other Multinational corps are withholding money from the American people?\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Hot tempered John McEnroe argued that Serena is not better in mans tennis world and Serena proofed to john that \textbf{woman} is much better in hot tempered action field and we got Sirena Williams :)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small that thing is not a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small HANDICAPPED SERENA WILLIAMS THE MOST TALENTED \textbf{HANDICAPPED} TENIS PLAYER EVER\normalsize   & \cellcolor{green!27}Handicapped & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small How can any of this be \textbf{sexism}? The judge was directly benefiting another \textbf{woman}.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small It was \textbf{Black} Pride straight out of Compton.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Its getting harder for "her" to hide that adams \textbf{apple}.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small SW is a sore loser. Her attitude proved it and no \textbf{sexism} or \textbf{racism} involved. Period.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small No one shamed Serena more than Osaka herself by saying sorry for winning the US Open. Unfortunately, Serena still went ahead and uttered more crap in the press conference suggesting that she learned \textbf{nothing} from this humble lady Osaka.Serena should accept that she cheated and apologize to Osaka and to the tennis fans all over the world. While this is obviously a dream that's never gonna come true, I hope at least the crowd who booed and clapped for Serena will apologize to Osaka and Ramos.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small Its time you tetire. Your sweet baby and husband needs you at home. There is \textbf{nothing} more out there waiting to fulfill. Girl you did your best. Put this behind then go on a long vacation while putting your retirement into the mail. Your family is much more important that people who quickly forget you.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small White American has no clue how it feels to defend your character as a \textbf{Black} Women... This is not the first problem Serena has had with the US Open. You say it's not sexist or \textbf{racist} but you are leaving hateful comments that attack her \textbf{gender} and color. Stop being a hypocrite and wake up to the fact that this is part of our culture.\normalsize   & \cellcolor{green!5}Black, Gender, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}3/65 & \cellcolor{green!5}4.615 \\  \hline
  \cellcolor{green!27}\small ithink serena wanted that penalty to cover her embarasing lost (which to me not that embarasing) so she bring up the sexist thing.. Serena has been the GOAT of \textbf{woman} tennis for very long time.. i think she never prepared to actualy accept losing in a big margin. The world should also focusing a new champ from japan rather than keep discussing the ref's desicion and the match controversy\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small I think that she has a right to explode. Let's not forget, the \textbf{woman} has lost before. She knows what it is like to lose. She can handle that. I think that what she couldn't handle was her character being questioned. After all the flack she gets in her league and from other aspects of her life, questioning her character was a step over the line for her. Was it \textbf{sexism}? I don't know. Did she go over the line? In my opinion, yes. Do I understand why she did what she did? Yes. I think calling her a sore loser is preposterous, though. Sidenote: After reading through some of these comments, I am curious about the type of following this channel, and China Uncensored, has.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/126 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Michael Tapia As I stated, she has lost before. This was not her first loss. Also, with as much flack as she gets in all aspects of her life, I'd understand why she would go off, but she was out of line and penalized for it. However, I'm not sure if \textbf{sexism} had a play in this or not. Also, if she's such a sore loser, why would she give so much props and love to Naomi?\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small Michael Tapia I see that you're nor getting it. I'll try to explain one more time, but that's it. Her temper is not what causes the flack she get in various aspects of her life. She gets it because of who she is and where she comes from. I can understand why she exploded the way she did; her character was questioned. It had \textbf{nothing} to do with her losing. She has lost before. That is \textbf{nothing} new to her. Also, she showed Naomi love because, for some reason, the crowd wasn't. She repeatedly stated how well of a player Naomi is. It's not about being a sore loser. It's about someone's character being questioned.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/115 & \cellcolor{green!5}1.739 \\  \hline
  \cellcolor{green!27}\small \@ME She gets all the "flack" that she gets because she brings it upon herself with her petty \textbf{feminazi} ways of depending on double standards to justify her shortcomings and blaming it on society. In this instance alone she lied about not being coached because even her coach admitted to it, she tried using \textbf{sexism} as a smokescreen to blame her lost on the judge, consequently creating a spectacle all by herself that stole Naomi's hard earned moment of glory and she has tried using the \textbf{race} card in the past when it wasnt warranted like she tried using the \textbf{gender} card this time. So no your technicalities to justify her behavior are pure bs and that's what you dont want to understand.\normalsize   & \cellcolor{green!27}Feminazi, Gender, Race, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - Female intelligence, Gender - General & \cellcolor{green!27}4/123 & \cellcolor{green!27}3.252 \\  \hline
  \cellcolor{green!5}\small Nope. All I said was that I can understand why she did what she did. I also stated that she was in the wrong, though. As for the flack she has received and still is receiving, that has \textbf{nothing} to do with her "petty \textbf{feminazi} ways..." and more with the fact that if you would read through this comment section, you'd probably see what I am referring to. I said what I said and I stand by what I said. I can see that you don't comprehend what I am saying, but I'm tired of this back and forth. Is there anything else you would like to say?\normalsize   & \cellcolor{green!5}Feminazi, Nothing & \cellcolor{green!5}Age - Youngsters, Gender - Female intelligence & \cellcolor{green!5}2/108 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small \@ME It has everything to do with her \textbf{Feminazi} ways and the fact that they can depend on technicalities and blame all of their shortcomings on men and \textbf{sexism} instead of admiting to their mistake like the fact that her coach was indeed coaching her.\normalsize   & \cellcolor{green!27}Feminazi, Sexism & \cellcolor{green!27}Gender - Female intelligence, Gender - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Can you draw a map of that \textbf{mental} leap you just made? Comparing this situation to \textbf{terrorist} attacks and pedophilia/molestation is a huge reach. I can agree that there are so-called feminists who use the term to hide behind in order to oppress others, but I don't feel like this is one of those cases. We are going to have to agree to disagree, but coming up with hypotheticals that will never happen, me understanding terrorism and pedophilia/molestation, to try to justify your stance is absurd and derails the discussion.\normalsize   & \cellcolor{green!5}Mental, Terrorist & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@ME It is an example of people trying to justify actions that clearly wrong. What is Wrong is WRONG no matter the seriousness of the matter. Also, gotta love how easy it is to get technical when it comes to defending the wrongdoings of a \textbf{woman} for instance it is so easy to get technical to defend Killary, Serena or Argento but yet so hard to get technical to defend Trump, Weinstein or any other man in the wrong.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small \@ME Prime example can be Andy Murray when he called the very same judge stupid and got penalized and still didnt go half as far into his rant and berating the judge and \textbf{nobody} ever dare get technical or try to justify his actions when it happen. The rules were simply the rules, Andy Murray deserved what he got and \textbf{nobody} try to sympathize with Andy Murray or question the judges decision. Why? Because Andy Murray is a man and he has to learn how to live and die by his decisions and learn how to be responsible for his mistakes. So if Andy Murray has to be responsible for his mistakes so does Serena because EQUALITY said so. The bottomline is that what is wrong is simply wrong no matter if it's a man or a \textbf{woman} no ifs or buts.\normalsize   & \cellcolor{green!5}Nobody, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/142 & \cellcolor{green!5}2.113 \\  \hline
  \cellcolor{green!27}\small Again, I said that I understood where she was coming from, but I do think she went over the line. What part of that do you not understand?  Also, there is a difference between the reactions and consequences of wrong actions bad on their seriousness. A person who sped through a \textbf{r\textbf{ed}} light wouldn't/shouldn't be treated the same or receive the same punishment as someone who killed someone. Point. Blank. Period. Stop pretending as if it's the same because it's not. Neither Hillary, Argento, Trump, nor Weinstein has anything to do with this situation. Please, stick to the topic at hand.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/101 & \cellcolor{green!27}1.98 \\  \hline
  \cellcolor{green!5}\small \@ME My point is that she doesnt deserve the empathy that you are trying to have for her. Serena created this hot mess all on her own, she could had easily controlled herself the same way Murray did when he was upset with the same judge. Also, Serena didnt have to lie about the coaching business so no she doesnt deserved a bit of empathy especially after she created her own monster all on her own. Is not like the judge escalated the situation berated her back while she berated him. She also double down and on the fake/pseudo notion/smokescreen that she was victim of \textbf{sexism} so no she doesnt deserve any empathy.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small Easy.If you're black: victimIf you're white: sore loserJust like everything else in America these days, the media is trying their best to start a \textbf{race} war that will be swift and one sided if it ever did happen.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small STEROIDS,  SPLIT PERSONALITY, ANGER MANAGEMENT,  \textbf{BLACK} is the new white.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Serena Williams Behavior was absolutely unacceptable. especially for professional athlete.It's absolutely disgusting williams tried to say " I'm standing up for women" or I have a daughter or this is \textbf{sexism}.   trying to play the \textbf{sexism} card etc .  that alone should give williams a 3 game suspension minimum.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Go and research NARCISSISM and there you will ring they can never , ever blame themselves ,this MAN paint as a \textbf{WOMAN} for one thing should be sacked ,kicked out of the game because it is cheating and it said (sir Rena) that hes never lied in his life ,well that's strange because he is only living a lie ,which is worse ! it's those who own all sports the evil Zionist criminal enterprise Rothschild  freemasons , ! just follow the money !?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Black people always talking about what "White People owe Them"\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Yes you have a daughter, daughter of a cheater.What Alexis Ohanian see from this \textbf{woman}? Not just ugly outside, but inside more ugly, absolutely \textbf{mental} disorder.\normalsize   & \cellcolor{green!5}Mental, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small But how can it be \textbf{sexism} if her opponent was also a \textbf{woman}?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small She is \textbf{black} and a \textbf{woman}...the entitalment trifecta\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small – In 2017 at the French Open, Novak Djokovic was given a fault on his serve by Carlos Ramos for time violations. He then received a code violation for unsportsmanlike conduct after yelling.– In 2018 at Wimbledon, Ramos gave Djokovic a code violation for slamming his racquet into the ground. Djokovic later complained about a double standard from Ramos, who did not penalize Kei Nishikori for something similar.– In 2017 at the French Open, Ramos called a time violation on Rafael Nadal. Nadal thought the call was selectively enforced and said he was not satisfied with it.– In 2016 at the French Open, Ramos called Nick Kyrgios for a code violation for yelling at a towel boy. Kyrgios accused Ramos of having a double standard and was described as 'mystified' by the penalty.– In August 2016 at the Olympics, Ramos called Andy Murray for a code violation for saying 'stupid umpiring.'– In July 2017, Ramos called Andy Murray for a time violation for playing too slowly. Murray acknowledged he had been warned before receiving the violation but was still bothered by it.\textbf{Sexism} intensifies.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/189 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small Sexism caRd,  always works\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Williams suffered \textbf{sexism}... \textbf{misandry} is a terrible thing\normalsize   & \cellcolor{green!27}Misandry, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Does she play \textbf{dumb} or is she really that \textbf{dumb}. Geez...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small This was \textbf{black} privlidge on display she is starting to believe the BS nike is telling her TRUMP 2020 and the way she threw that racket down but flinched when she thought it might bounce back screamed fake outrage\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small It's things like this that make me criticize the left. How is this fair or right? It seams every time we victimize someone it ends up hurting someone else yet people always double down on who the victim is and attack the other person. It's especially true when we hear of \textbf{sexism}, \textbf{racism} or rape violations. These are extremely serious issues and we should tread lightly when accusing people of these things. Here in Australia, you can go to jail for discrimination and can get up to 3 years in prison for insulting someone based on \textbf{race} and of course you can get years and years in prison where you'll be beaten daily if you have a rape conviction. What I am saying is, no we obviously shouldn't blame the apparent victim but we should be listening to both sides of the story and sympathizing and empathizing with both parties. If we don't, it'll end up like White Australia or \textbf{Jim C\textbf{row}} america where one \textbf{woman} has the power to have a man lynched for looking at her wrong.\normalsize   & \cellcolor{green!5}Crow, Jim Crow, Race, Racism, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}6/179 & \cellcolor{green!5}3.352 \\  \hline
  \cellcolor{green!27}\small So Serena Williams has a bad temper and not so good attitude when losing, but that are \textbf{common} traits in sports ( yes she shouldn't be that way, I know,  but that's not my point ), How about her coach , as it was his cheating that started all of this bs. Is he so scared for being sacked if she lost the match or was he the real sore loser?\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small It's not just about what she said, it's about the coaching violation, the racket abuse, and the refusal to let it go. It just kept escalating. She is the worst kind of trash. Behave terribly. Blame \textbf{sexism}, \textbf{racism}, whateverophobia. Pathetic.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Sore Loser ... playing the victim all over...the \textbf{Race} card.. the \textbf{woman} card... OMG\normalsize   & \cellcolor{green!27}Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Serena is a "pro" and needs to act like it. She did several un-sportsman like things and the final straw was the verbal abuse. Calling \textbf{sexism} when she clearly broke the rules is not right at all. For someone that has been doing tennis for as long as she has, she should have better control her emotions.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small How is this \textbf{racism} or sexist?😂😂😂\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small It's a \textbf{black} thang...………….\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I'm standing up for women's rightsYeah. NOW you are but on the court you weren't you were just being a \textbf{brat}At least that female umpire is only ugly on the INSIDE\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Arguing with the ref never gets them to reverse themselves - ever. It's as \textbf{dumb} as arguing with a police officer who is writing you a ticket. All you do is make things worse. Williams should know this by now. Choices have consequences and she got what she deserved.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small What a \textbf{misogynist} ref, Serena instead of the man she was playing against....... oh, wait. It was \textbf{woman} vs \textbf{woman}. How long until Serena changes it to \textbf{racism}?\normalsize   & \cellcolor{green!27}Misogynist, Racism, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}4/28 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small None! It's actually \textbf{racism}.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I was very sad to watch Naomi apologize for winning...her culture is \textbf{nothing} like ours,the are so humble,and she should have been celebrating instead of feeling small.....I don't like how it all went down....\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Naomi lived in America for most of her life. She was in Japan from birth to \textbf{age} 3.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small John Smith oh, poor Umpire, should he call his mummy because Serena called him a thief. He was a wuss and ridiculous. Serena has also \textbf{mental} disorder who always plays the victim and is quite entitled. Shame on both. The Umpire was pathetic and Serena a scumbag.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small We love it when a \textbf{woman} abuses us over and over again.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small No-he doesn't need to scream out for Mommy like Serena screamed out \textbf{sexism}.  It is simple.  Ramos followed the rules (he was hired to do so he was doing his job).  Serena didn't follow the rules (cheating, gamesmanship, smashing racquet, being disrespectful to her opponent, and lastly, verbally abusing the officials which she has a LONG history of doing.  One this she was doing was her job-to hit the ball-play tennis.  Yeah-she was losing and she let her ego eat her alive - which we didn't hire her to do.  She is fired....oh wait, fined after the review board deemed Ramos correct and Serena, well, WRONG.  \$17k WRONG.  When is this abuse going to stop?  When is she going to stop taking the glory of the win from her opponents?  Come on Mauricio-Take the rose \textbf{colored} glasses off and get into reality with the rest of the world.\normalsize   & \cellcolor{green!27}Colored, Sexism & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/148 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small mauricio virmond  The Umpire made \$500,00 for doing his job. Five hundred lousy bucks for shovelling Serena's crap. I can't recall an official in any sport taking so much abuse without throwing the athlete out. It was up to the same \textbf{senior} officials  who through her out against Clisters for threatening to kill a female linesman. \textbf{Sexism}?\normalsize   & \cellcolor{green!5}Senior, Sexism & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small John Smith: Good! Any unbiased person can see whose behavior is in question here. Out of control behavior has no \textbf{gender}, \textbf{race}, \textbf{nationality} or excuses. It happens all the time, but more frequently from some who thinks he or she can get away with it. She was at home, so she felt she was in charge. She played a victim so she could get her supporters to back her up. The lauder them became the more she increased her barrage against a man who was just doing his job. A very good job we must say! Give this real man the \$17,000.00 they collected from the abuser. She went home with more than a million. The penalty to be effective it needs to cause a pain in the pocket of the offender. The penalty amount should be a substantial percentage of what they are taking home. That will stop or decrease this abusive manipulation of the game (which as a form of cheating). This behavior is being used by some dishonest players not only in tennis but other sports as well. Humans will push the limits as long as they are allowed to. With all the attention they are getting for doing what is wrong, they won't be motivated to change. Can we honestly blame them for pushing the rules, if they are being allowed to? The decline in our society's morals is creating more opportunities for this barrage to be tolerated, encouraged, excused, and insanely justified. As one general famously said once, 'NUTS'.\normalsize   & \cellcolor{green!27}Gender, Nationality, Race & \cellcolor{green!27}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!27}3/254 & \cellcolor{green!27}1.181 \\  \hline
  \cellcolor{green!5}\small No a \textbf{black} female or me too or LGBTQURF so Carlos don't matter\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Koala Bare No, no you won't, because the men that it's happened with from this umpire were different scenarios. The thing is that they had out bursts, yet they were warned once, and then they STOPPED!!! She was warned repeatedly and was given a chance to cool down, however she doubled down and continued, so that's the reason. She was DEFINITELY CHEATING, her coach even admitted to it so that's why she was docked. Yes, there was 100 \textbf{sexism} taken place, yet again it was on Serena's behalf. Basically she was acting like a child, cheating, being reckless by breaking her racket, lied, and continued to break the rules by abusing the umpire! She's the one who owes Carlos an  apology, along with Miss Osaka. She ruined Miss Osaka's first Grand Slam.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small John Smith she verbally abused Mr Ramos because he was white and she behaved like a \textbf{racist} because she would not have given him lip if he was \textbf{African} American, for sure!\normalsize   & \cellcolor{green!5}African, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small If Serena was the man and Ramos was the \textbf{woman}, this situation would be treated very differently.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small The only \textbf{sexism} and \textbf{racism} was on display was from Serena Williams... Well not really... Crowd booing the umpire was also sexist and \textbf{racist} act...\normalsize   & \cellcolor{green!5}Racism, Racist, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/25 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small rules are rules this as \textbf{nothing} to do about \textbf{gender}, jack!!!!!!!!!!!!\normalsize   & \cellcolor{green!27}Gender, Nothing & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small What a horrible  final event. I'm so glad I didn't spend my money on this Open. I would have felt robbed.The \textbf{sexism}, \textbf{racism}, and abuse that this Portuguese \textbf{immigrant} had to endure! I've never liked or rooted for Serena, because she is an entitled, manipulating \textbf{brat}, and a very much dislike brats.\normalsize   & \cellcolor{green!5}Brat, Immigrant, Racism, Sexism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}4/53 & \cellcolor{green!5}7.547 \\  \hline
  \cellcolor{green!27}\small Craig Chez are you assuming the \textbf{gender} of that racket? SEXIST!\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Carlos Ramos was victim of \textbf{racism} because he is Portuguese!\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@K J N oh! You mean to say that, when self declared women's rights activist (read: feminist) tries to find \textbf{sexism} where none exists and blames a person of \textbf{sexism} who was threatened by her because he is a non-victim class man and consequently  that person is booed by the crowd -- is not a sexist and \textbf{racist} act of the crowd ??\normalsize   & \cellcolor{green!27}Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/63 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Susaant Menon No, it isn't. Clearly these people supported Serena and this is not necessarily \textbf{sexism} or \textbf{racism}, simply strong support no matter what happens.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@K J N I understand what you wrote, but I guess u contradicted yourself. Because if they were supporting her no matter what happened, then his actions cannot be blamed for he receiving the boos...I now know you labeled crowd's actions as not sexist and not \textbf{racist}, because they were merely supporting her no matter what. But I precisely labeled that act as sexist and racists, because she acted sexist and \textbf{racist} in the first place ans the crowd supported her.BTW if you ask me personally I would be inclined to call any act of any person not \textbf{racist} and not sexist, because everyone reacts to situation they are in. But as the leftist in almost all of us makes political issue out of everything happening by blaming everyone else, especially those whom they think cannot be labeled as victim, I also pitch in with my counter narrative.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/150 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small +K J N Again, that's your personal preference. Regardless, \textbf{nobody} else has received this much attention for calling someone a thief.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Мила Јовановић Wait Carlos Ramos is white? Well maybe in \textbf{Communist} Russia.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Wandering Oryx  she knows she was loosing   so she created a scene  she took away the young talented  player who was her idol  she took away this young girl first glory with her emotional outburst ... she is  38 years \textbf{old}  she should  retired before her \textbf{age} caught with her and  focus on being a mother  now\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small mauricio virmond  The umpire did \textbf{nothing} wrong. He just followed the rules, that rage has to be penalized. That you try to make him ridiculous, only makes you look ridiculous.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Yes - Serena should apologize to both Naomi and to Ramos. But Serena knew that the win belongs to her so when she was loosing to Naomi, she went ballistic.  Luckily Naomi is \textbf{Black}, so Serena could not complain that she was discriminated against because she was \textbf{Black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small John Smith I didn't seemed to me he felt like a victim; no he was firm, didn't left himself intimidated. If the umpire would have been a \textbf{woman} probably she would have reacted in a different way, but Mr Ramos it's a man and that's why he wasn't to impressed. Remember the moment 2009 when she threatened that line umpire (that was a \textbf{woman}). She decided that Serena broke the rule and warned her (by the book), but when Serena threatened her she got scared. In opposition, I repeat, Mr Ramos wasn't scared or intimidated in that moments. This is not about \textbf{race} and \textbf{gender} and bed time stories like that. Think is that Serena it is like a bull that base herself on brute force. So it was from the beginning...\textbf{nobody} can change her.\normalsize   & \cellcolor{green!27}Gender, Nobody, Race, Woman & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}5/135 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Serena is a sore loser.  She needs to apologize to Mr. Ramos. She is a jerk. She's not bigger than the game. She is not fighting for women's equality like she says. She is playing tennis and collecting a \textbf{fat} paycheck for herself. You sore loser!!!\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small He had no choice. Would you recommend that he yell back at her like little kids or like gang bangers. He is a mature person doing his job. Hevdid exactly the right thing. It was easy fornhim to control himself because he is a professional. Mature professionals get \textbf{nothing} from playing childish games.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small crventura, No, Ramos is a \textbf{racist}!!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Anna Warner, is. Ramos \textbf{black}???\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Absolutely.  Solid proof of all womens' completely hypocritical, untrue, denigrating, bigotted, sexist bitching-assualts at and about men.  In general this unmitigated practice of obvious and pernicious predation is condoned and applauded today.  It shows me, big time, mankind is under (covert?) assault by amoral opportunistic women, virtually, now \textbf{gender} nazis, 90 years updated, in particular and in general.  What reaks me out the most is womens bizarre, relatively singular orientation/concern to their genetalia, et. al.  This cannot be true.  Is it biologically inherent?\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small \@mabatommy Are you implying sado-masochism is a mature attitude or practice?  Its as unnatural, bad and unattractive to me as it's always been, regardless of \textbf{age}.  No one told me how to feel about it, but its always been goofy bad/or wrong; something to avoid and discourage for good reasons.  It cannot be mentally healthy nor normal.  It appears quite selfcentered, selfconcerned and psychologically-twisted aggression and /or self-hate.  Whats good or normal about that? What is sport but good-natured, mostly physical competition with preestablished rules, practices, courtesies, etc.?   Theyre ALL designed, maintained and developed to keep hurricane issues, tantrums/tirades/rages DO NOT HAPPEN in all the excitement and something else, better, does happen - what they paid and came to watch happen - championship women's tennis.  Its a game.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small \@Pedro Moura regarding portugals history: how is regime survival a measure of national excellence?  regarding portugese maritime superiority, what did they do that somebody else couldnt?  what happened after vasco de gama?  \textbf{Nothing} good or noteworthy other than to avoid.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@mabatommy isnt not caring at all about others' feelings what's the problem in the \textbf{gender} war?  If no one cares about my feelings, as you emphasize so emphatically, then, why the double standard?  I care about your feelings, of course.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Alien} 0330 Yup. Just like you is probably because he is \textbf{racist}.\normalsize   & \cellcolor{green!5}Alien, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Oral Powell I'm pretty sure I'm not \textbf{racist} nor abusive , and I don't assume unlike you , I respect you defending her , but I'm not calling YOU a crybaby for doing so .Plus I'm not defending him for being "\textbf{racist}" or "sexist" I am defending him for doing his job eficiently . And please if you're just going to continue assuming my personality and assuming it wrongly , just stop , you got your opinion and I respect it , I got mine hope you respect it as well , my opinion has \textbf{nothing} to do with my way of living my life . Thank you and good day/afternoon /night to you .Sorry if this is over the top and long , but i've had a long day and I'm not here for nonsense , wanna talk about memes ? Sure , just borderline assuming my ways , not here for it . For clearing up I do not hate you , and I would love to see you around and agree with something , again foregive me if I myself assumed or misunderstood something .\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/190 & \cellcolor{green!27}1.579 \\  \hline
  \cellcolor{green!5}\small Serena should be banned from playing tennis professionally. And playing against the opoosite \textbf{gender}. As he has an unfair advantage.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small spoiled \textbf{brat}, that can't take the fact she is over the hill\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She threw a tantrum, tried to bully an Umpire, failed so played the \textbf{gender} card. Unsurprisingly, the liberal media are behind her puerility. Her total lack of dignity took the gloss of her opponent's outstanding achievement. One \textbf{woman} Williams wasn't concerned about.\normalsize   & \cellcolor{green!5}Gender, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Ok ppl \textbf{nothing} to see here, It's a Man's fault.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small ah yes what victim of \textbf{sexism} he was\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Williams deserved everything she got. She is a selfish \textbf{woman} and a disgrace to the sport.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Male players may indeed have said worse things to their umpires, but how many of them did so after already receiving 2 previous code violations in the same match?This is not a case of \textbf{sexism} or \textbf{gender} inequality. It is a story of a sore loser and someone that clearly doesn't know when to STFU.All professional athletes know that a referee/umpire decision is never rescinded during a game, as it would undermine the authority of the referee/umpire. The correct way to deal with what you may feel is an unjust penalty is to follow the official appeals procedure laid out in the rules of your game.Take your first penalty on the chin, brush it off and carry on like a professional. Then appeal after the match if it means that much to you.It is extremely offensive and disrespectful of Serena Williams to claim \textbf{sexism} for this case, due to the fact that she truly did break the rules and received fair and just penalties according to the rules she agreed to play by.By claiming \textbf{sexism}, she is trivialising real \textbf{sexism} and \textbf{gender} inequality in the world and playing down all the experiences of women who have to deal with REAL \textbf{sexism} on a daily basis.No \textbf{woman} should be standing up for Serena's behaviour, it was unacceptable and playing the \textbf{gender} card simply took her petulance to the next level.You broke the rules, now "\textbf{woman}" up and take your medicine.\normalsize   & \cellcolor{green!5}Gender, Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}10/246 & \cellcolor{green!5}4.065 \\  \hline
  \cellcolor{green!27}\small Some morons go as far to saying that the entirety of Portugal is \textbf{racist} and sexist. I'm not kidding.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small first time i see a \textbf{woman} beat a man in tennis\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I would love to see Serena Williams plays against a Goat because Goats don't give a damn about her PMS mood swings and Immaturity.What made me very Angry is the fact that Serena Williams has just robbed her fan, Naomi Osaka of her chance of a lifetime to compete with her in a grand event by throwing EMO tantrums like a Spoilt Child, threatening the Umpire and demanding for special treatments and privileges to Cheat, all because she is a GOAT.Therefore she is the Thief, not the tennis umpire Carlos Ramos.And what is even more Disgraceful about Serena Williams is that now she has become a Coward by trying to hide behind Political Correctness and \textbf{Gender} Cards instead of taking full responsibility for her own Failures and "Deranged Tennis Syndrome".By going SJW and turning her own Farce into issues of "\textbf{Sexism}", Serena Williams has not only prove herself to be disrespecting the sports, but also Insulting other Sportswomen like Naomi Osaka who worked very Hard, never complain and Sacrifice Everything for the sports they love.But the most Stupid thing is that Billie Jean King even came out to support her Orwellian Nonsenses and Hypocrisy.In conclusion, Serena Williams' Immature EMO outbursts were clearly Not "Fight for Equality", but "Fight for Irrationality".Just like Colin Kaepernick's kneel protests aren't for fighting discriminations, but to support Slavery.And I can see why the Left PCs and SJWs are going to destroy the Western Civilizations and the Whole World too.\normalsize   & \cellcolor{green!27}Gender, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/252 & \cellcolor{green!27}0.794 \\  \hline
  \cellcolor{green!5}\small Rather a sad precocious looser that is a spoilt brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small WOW SERENA...Fighting for Women's Rights ?? Did You forget yer \textbf{Feminazi} banners and to pass out those freebie hat pins at the starting introductions ??\normalsize   & \cellcolor{green!27}Feminazi & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Excellent analysis, the 26 penalized men vs 9 penalized women is quite telling. Good luck trying to glean \textbf{sexism} from that! Spoilt petulance of a former champion unable to handle the fact that she was outclassed that day durind play and otherwise! Whose to blame for her losing? Of course it's mean mad white man!\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small And \textbf{nothing} will ever get that back for her... And people say caucasians have no empathy... I hope she can put this behind her and go on winning matches!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Made in England ---i guess when i think of spanish people...i think of the ones from south of the border....mexico and south......and it is kind of difficult at times...to figure out what color they out....or shade maybe.......seriously....some are almost as white as i am....some, caramel.....some  \textbf{black}...and some...i am just not sure.....what color they are......i am not saying anything bad here...i just saying the truth.......\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Remember girls if it doesn't go your way, accuse him of \textbf{sexism} 😘\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small start taking points away for verbal abuse from any \textbf{gender} even more firmly I mean it's a sport it has rules you have to behave with good Sportsman\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Sore loser. Entitled \textbf{brat} who thinks they can get away with breaking the rules while others can't and because she's a \textbf{black} \textbf{woman} she can always play either the \textbf{racism} or \textbf{sexism} card.\normalsize   & \cellcolor{green!27}Black, Brat, Racism, Sexism, Woman & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}5/33 & \cellcolor{green!27}15.152 \\  \hline
  \cellcolor{green!5}\small Serena had already lost to Naomi before, and was losing this time again. This was a desperation play to try and shift blame on her loss from her \textbf{old} ass to the system. Serena is too \textbf{old} to compete. She's going the same route Venus did and is slipping down the rankings, and can't take that.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Serena's likely upset that she's getting \textbf{old} and can't handle it. Venus had the same arc, but accepted slipping from 2 to 16 with grace. Serena will likely place fairly low in her rankings, and it'll only fuel her bad personality.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small My heart beats for Osaka. Williams has played the \textbf{racism} and \textbf{sexism} card both. I used to respect her a lot. She's a player of a sport. And nobody's above a sport, just like nobody's above the law. Great job Osaka. And all the very best for all the future grand slams.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Sexism? Women at the Open were paid 2.11 times more per minute than their male counterparts. How little did we know that John Mcenroe was fighting for equality all those years ago...\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small This is a non-story.  Serena Williams is a champion that fights for everything.  If she doesn't fight for her point penalty, she's a failure.  However, Nick Kyrgios is a complete jerk.  Why the ATP calls him NextGen is a complete disgrace.  Serena has done some over-the-top \textbf{crazy} things, but, she has always stood tall.  Australia is only 4 months away.  BTW: TwitterisStandardOil pass it on!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small The only reason why \textbf{racism} isn't included, because the opponent was \textbf{black} Asian mix\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The only thing that mattered (in Serena's mind) was that the referee was a male (and also white, so the \textbf{racism} card could have been applied)\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small 3:34 But... the other person also is a \textbf{woman}...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small t is ridiculous this ware of people trying to defend something the is not possible to defend. 1) coaching - they have been spotted and , once it is so, the refereee MUST apply the rule violation - The excuse " everybody does it" is really low - There is a speed limit of 50 and we all know that many travel at 55 but that time that the police catches you and fine you try to tell them that many do so let's see what they'll reply to you. - 2) how many offences a referee has to take before acting? You are a Thief - You owe me an apology - you'll never chair when I am on court, never again till I am alive - year - All with the index finger pointed straight at the face of the referee which for me is the worse of all - after all breaking the racket on the ground. . . and when she have seen that all this did't work tried with tears, with "I am a mother " and more and more down in level - \textbf{sexism} - - -Pathetic excuse. - Still defending Serena? Of course you are free and you can but, honestly you do not have much ground. Maybe the Business system will try to bail her out somehow but, to me, Serena is a great player but a very poor loserShow lessREPLY\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/241 & \cellcolor{green!5}0.415 \\  \hline
  \cellcolor{green!27}\small Hey Serena - you do not own motherhood. Stop. Please. It is disrespectful to mothers everywhere.And also Serena.. if you want to be treated like a \textbf{WOMAN} - stop acting like a petulant child.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Crazyhot, \textbf{crazy} and hot\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Naomi Osaka is not really Japanese.  She has lived in the USA since she was 3 years \textbf{old},  and she doesn't speak Japanese.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Exactly it's \textbf{crazy} how people keep pushing this. Especially considering a lot of Japanese people wouldn't accept her because she's half Haitian.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small first of all, the japanese player deserved to win. congrats to her. she should be celebrating.this isn't a clear cut black-and-white case. yes serena did violate the rules, BUT the umpire isn't consistent in his calls. it's not fair to portray serena like she's \textbf{nothing} but a sore loser.put yourself in her shoes. it's really not fair that other athletes basically get free passes or minor taps on the wrist, or even just warnings while she gets called out in a major way. even if she wasn't dealing with the umpire with decorum, i think it's still understandable that top athletes would get all fired up when they feel that the rules apply only to them and not everyone else.to everyone saying she is a sore loser, i don't see it that way. she even said that naomi osaka was good at the match and that she deserved to win.also, why do they refer to the umpire as a "stickler for rules" when he literally isn't consistent with other athletes who have openly said they don't get punished?what she's being ungracious about is with the umpire, not her opponent. nuance matters. this isn't black-and-white.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/199 & \cellcolor{green!27}0.503 \\  \hline
  \cellcolor{green!5}\small So the umpire is sexist for penalizing one \textbf{woman}, and handing the game over to the other woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Well that explains why she was angry. Out with the \textbf{old} in with the new\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small What I observed was Serena is frustrated she's losing, interpreted the umpire's coaching violation as her cheating, and not handling the moment well at all. \textbf{Sexism}, some believe. Sore loser, some believe. Not controlling her emotions under pressure, absolutely. Who hasn't? She'll either pull herself together or retire, either way doesn't matter to me but I hope she pulls it together for at least one more grand slam win. Naomi was robbed of her moment and I felt sorry for her. Would Serena have turned the match around if she had not been penalized, we'll never know but Naomi did outplay her.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small Just sore loser, \textbf{nothing} more\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small That Umpire Call Serena A Liar,I Got The Video To Prove It.And She Responded By Saying,No You Are A Liar And a Thief Too.Those Were The Exact Words.Verbal Abuse Comeon! I Did'nt Hear Not One Swear Word At This Umpire.He Was Out Of His Depth.The Umpire Has No Balls.He Needs To Grow A Pair.He Just Could Not Handle The Angry \textbf{Black} \textbf{Woman}.He Felt Intimidate.So What Does He Do,He Stole A Whole Game.Serena Was Right.He Is A Thief.Men Should Not Umpire Womens Matches.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/83 & \cellcolor{green!5}2.41 \\  \hline
  \cellcolor{green!27}\small How is it sexist if her competition is a \textbf{woman}?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small How can we be sure if it was \textbf{sexism} or \textbf{racism}?  It has to be one or the other, right?\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I think part of her problem is she is under a lot of pressure to break records but, at 36 yrs \textbf{old}, time is definitely not on her side. It ABSOLUTELY does not excuse her behavior though. She completely robbed Naomi of the spotlight that she's rightfully earned for her historic achievement.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small If there was a female umpire, she would of pulled the "\textbf{Race} card"\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small and if it was a \textbf{black} female Umpire?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Feminists have that one covered. If you are a \textbf{woman} and judge women by any objective standards, you suffer from "internalized \textbf{misogyny}". It's a neat concept. 😁\normalsize   & \cellcolor{green!5}Misogyny, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small That Japanese girl? Her name is Naomi Osaka. She is a young \textbf{woman} and is Japanese and Haitian.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small She's actually \textbf{black} and Japanese. Her father is from Haiti 🇭🇹 And I believe her Mom is from Japan. She was raised in a \textbf{black} Haitian household and also in the Japanese culture. She represents two cultures 🇯🇵🇭🇹\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She's asian and \textbf{black}...she's BLASIAN\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Americans throw this champion of a \textbf{woman} under the bus, this is pure \textbf{sexism} because of the amount of coverage it gets, men who do this and do even worse stuff don't get this kind of coverage.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small women love to be the one in power until they fuck up then they just act like a child and blame the \textbf{patriarchy} instead of just fucking taking responsibility\normalsize   & \cellcolor{green!27}Patriarchy & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small This Insane SJW Feminist rhetoric is now spread into sports where it's encouraging them to not take responsibility and project there BS on to others etc. Or it could be Steroids, explains her manly build and outbursts. Also she was playing against another \textbf{woman}, so how is it sexist.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small I didn't know much about this controversy and I still really don't care. Tennis is the only sport to rival golf in terms of 'clawing-at-my-eyes-I'm-so-bored-please-Jesus-God-almighty-make-is-stop-please-God-please' boringness. But what she said at 2:36 was waaay out of line. She threatened his career because she didn't agree with his, uh, referee-ing(?). That's grounds for ejection from the tournament imo. Was the referee sexist, though? Fuck if I know.One thing that irks me about the whole controversy is this cartoon of her drawn in this antiquated style of \textbf{racist} caricature drawing where it looks like the artist tried really hard to make her look aboriginal/tribal. Seeing a lot of apologetics surrounding it. I'm usually pretty quick to defend those being called \textbf{racist}, but not this time. I've seen that style enough to know what it represents. My favorite comment around it is (paraphrased) 'once I saw this cartoon, I knew the leftists would call it \textbf{racist}.' This person recognizes the signs and is still in denial smh. Some people literally require somebody to say 'I'm a \textbf{racist}, no joke' before admitting the person is \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}5/183 & \cellcolor{green!27}2.732 \\  \hline
  \cellcolor{green!5}\small Haven't watched the video, but because I now realize that Chris is just another white nationalist, I'll guarantee you that he's going to paint Serena Williams as a sore loser and I'm positive that everyone in the comments is going to echo him and agree with his analysis. I lived in Asia for years and found 'China Uncensored ' so refreshing, but after leaving and moving to Europe I ran across this channel and it has become painfully clear that Chris and his supporters are less seekers of truth, but more bent on painting white america as superior and ANY people (be they \textbf{Black}, Latino or Asian) who threatens this image of themselves will be attacked and mocked on his channels. Predictable and pathetic. Haha—just scrolled down to see a few comments, and boy was I right!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/137 & \cellcolor{green!5}0.73 \\  \hline
  \cellcolor{green!27}\small shes just a sore loser or he? idk it looks like a man , prolly a tranny\normalsize   & \cellcolor{green!27}Tranny & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Serena just mad because she lost to another \textbf{black} lady\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Remember, everything is sexist, everything is \textbf{racist} and you have to point it all out.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small People are abusing the fight against \textbf{sexism} and \textbf{racism}.I'm not a white guy, but when I commented about the girl who cast as Starfire on the new Titan serie that she's \textbf{old} (she's over 40 while Starfire is a teenager) and ugly, people stormed me that i'm \textbf{racist}.\normalsize   & \cellcolor{green!5}Old, Racism, Racist, Sexism & \cellcolor{green!5}Age - Over 65s, Ethnicity - General, Gender - General & \cellcolor{green!5}4/49 & \cellcolor{green!5}8.163 \\  \hline
  \cellcolor{green!27}\small Usually you would call someone like that a manchild... or would it be \textbf{WoMaN} cHiLd???  Don't want to be sexist\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Wow would you believe it a wamens organisation believes its \textbf{sexism} well i never, of course you can run around claiming \textbf{sexism} but only if your a wamen, wait whats that chris more men by over double penalised and on average double the number of men to women penalized over all tournaments well by god it must \textbf{sexism} how dare we say otherwise....Probably not the sort if \textbf{sexism} she ment tho...if you get my meaning....\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/76 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She had already lost and she knew it. Naomi owned her in Miami, and she owned her Saturday too. She was plain and simply outclassed by Osaka in every possible way. This was a drama queen, intent on painting herself a victim in an attempt to save face. Any defense of this on court bully with an extensive history as such, is pathetic. Serena knows the rules, and the rules were applied fairly. In no other sport would the application of penalties be brought into question, you break those rules, you're penalized accordingly. Fact is, it had no effect on the outcome of the match, she was already dead in the water. The chair actually showed far more patience than he was obligated to by the rules of the game. Serena was to be the loser, and by her own actions, she's just a bigger one now. She was a disgrace! For that matter, so are all of the people defending the indefensible. This is the same Serena who once told a FEMALE line judge, "If I could, I would cram this f-ing ball down your f-ing throat!" Way to fight for women's rights!!! If a man said that to a female line judge, it would most probably end his career, or at least put a dark cloud over him forever. She's an egocentric, spoiled \textbf{brat}, with a total lack of accountability. In my opinion, this day defines, not only her career, but shows us all what the real Serena is like. She may be a tennis great, but she's a detestable human being.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/264 & \cellcolor{green!27}0.379 \\  \hline
  \cellcolor{green!5}\small still doesn't make sense, punishing serena would only benefit osaka, and osaka is a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@chupei cycling No, it does make sense. Forget about the game itself, it's irrelevant. The point of \textbf{sexism} can be made and entertained when the context of the accusation is about a \textbf{woman} talking back and verbally abusing a man and the man not having thick skin with the \textbf{woman} when the man has, in recent incidents prior, ignored harsher verbal abuses from other men... Serena has noted this ref has taken worse words from men and done \textbf{nothing} but she calls him a thief at worst and loses the game. For obvious reasons however, her claims are not entirely sound and entertaining the accusation is \textbf{nothing} but a political agenda move. So yeah, it's not entirely irrational and has \textbf{nothing} to do with Osakas existence at all. If it was \textbf{sexism}, he still wouldnt mind awarding Osaka when, in that context, it would be all about focused spite.\normalsize   & \cellcolor{green!27}Nothing, Sexism, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}7/149 & \cellcolor{green!27}4.698 \\  \hline
  \cellcolor{green!5}\small Seriously? What an idiotic question. Serena claimed that men who have behaved similarly in previous matches have gone unpunished. This has \textbf{nothing} to do with the opponent.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Because! If you don't know then you are sexist too! Serena is a \textbf{woman} and he is a man! He wanted her to lose because she is a \textbf{woman}! Not only that but she is a person of color and he wanted her to lose for that reason too! Serena is a mother!! Serena breaths air and eats food and uses her arms and legs! How dare you insult her for being a mother and for being an organic bipedal lifeform! Serena has never don't one thing wrong in her entire life, she is a perfect being, even more so than Jesus!! You and Carlos both wanted her to lose because she is so perfect!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/115 & \cellcolor{green!27}1.739 \\  \hline
  \cellcolor{green!5}\small Hahah ok. Next time it has to be a female. Oh and a \textbf{black} female. This avoids \textbf{sexism} and \textbf{racism} arguments, oh and the ref needs to have a history of giving penalties for every type of penalty on the book, and not just to males but also women and \textbf{black} women in particular, also of ref that... well you get the picture. Horrible that Naomi saw her as an idol. This \textbf{woman} is horrible. Does she have skills, yes. But as a role model, no way.\normalsize   & \cellcolor{green!5}Black, Racism, Sexism, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}5/87 & \cellcolor{green!5}5.747 \\  \hline
  \cellcolor{green!27}\small Claim \textbf{sexism} or \textbf{racism} in everything, that the new America, also like Hilary when she lost, say your playing/fighting for womens rights.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small She trampled the right of her rival, a young talented \textbf{woman}. So whats this talk about fightng for women's rights. Charity begins at home.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small You can't blame Serena Williams for her raging while losing - steroids can have menacing emotional side effects. Yes, "'roid rage" is real. Researchers have documented several cases of violent, aggressive behavior associated with anabolic-androgenic steroid use, even athletes with no prior history of violence (according to a paper published in 2010 in the journal Hormones and Behavior). Check out Serena's workout schedule - Jazzercise and running won't produce that body. Serena Williams is often called not just the greatest female athlete but also the greatest athlete period (what a joke). They said the very same thing about Marion Jones who finally admitted to doping. When Serena's coach admitted to cheating because "everyone does it," it sounded a lot like drug use - when you consider the people most likely to have an ADD diagnosis are Olympic athletes (so they can take uppers). Sharapova was caught. \textbf{Nobody} questioned whether Joyner was roided - just too much muscle in too short a time. Cox and White were caught. Thomas's facial hair was too obvious. It's not just the Russians. The other issue is once you start lying, becoming pathological is the natural end result. The claim men have done the same is not accurate. They're rages were short - they were all able to get control of themselves. It was so sad that beating her had to come with an apology from her opponent - not fair. Repeatedly, Trevor claims we should allow athletes whatever is \textbf{common} but then he chokes down almost saying "drugs." Google NFL "excessive rage." Trevor lies. The issue for many is their only source of news is comedians pandering to their biases. Serena did not get the penalty for her childishly slamming her racket but for her non-stop verbal abuse. Sounds like every person to get a speeding ticket like ever - why didn't everyone get one? It was not "amazing," only disgusting and juvenile. Serena has illegally threatened refs before. [LINK]  => Trevor's take on it.\normalsize   & \cellcolor{green!27}Common, Nobody & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/331 & \cellcolor{green!27}0.604 \\  \hline
  \cellcolor{green!5}\small Fighting for Feminists, that is, \textbf{communist} useful idiots.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Richard Stead said "Tucson Jim you are dead right . STEROIDS."There have been all kind of rumors circulating around men in many sports over the years and even on rare occasions a few women (like Joyner)... why never Queen Serena? Doesn't her completely closed workouts further raise suspicion? We readily accept that men behave poorly but we refuse to suggest that women might ever be held accountable. Serena admits to seeing her coach but pretends she didn't understand the obvious sign to play closer to the net saying it was a "thumbs up" BUT then later lied saying she never saw him. People are saying the ref was incompetent (he wasn't) for going overboard when she called him a "thief" - it was for failing to ever stop her silly tantrum. Trevor's suggesting the problem was destroying her racket is a bold faced lie. He was there - he knows. At no time was she able to control herself like an adult. She uses the victim troupe women have been using forever. I'm a \textbf{woman}, I have a child, won't you rescue me? One might suggest it's unfair to blame Serena since girls are raised to be drama queens. There is \textbf{nothing} more pathetic than when Naomi Osaka was forced to apologize for beating Queen Serena. Shame on the mob for not allowing her to have her moment of glory. :-(And again, just look at real \textbf{woman} Naomi Osaka's body. My mother got a physics degree from Duke with my dad (and got better grades) and was easily able to get a better paying job than he even in the late 1940s. However, they couldn't afford to buy a home so my 5'2 mom volunteered to build it herself (eventually winning the Delco Home award in 1965). She could easily carry four cinder blocks at a time while my 6'4" Navy Commander dad gave himself a hernia trying to carry one. Mom ended working in construction for the next decade. I once saw two larger youths attempt to rob her - she had them both on the ground in seconds. Her body didn't look anything like Serena's. Get real. You are the first person to affirm such an opinion makes sense - I don't get why. I honestly believe women could compete with men in sports. There's no doubt mom could have taken my dad. Bruce Lee proved size doesn't matter. Women just aren't willing to make the same effort. Listen to the other female tennis players talking about how lifting weights would be too much effort... like the male tennis players do. It's the same with surgeons - there's no \textbf{sexism} just women raised with a more "healthy" life  work balance. And oh, studies confirm that just like the guy who claims to do "it" the most usually doesn't at all (and doesn't even like it), those who scream "I never cheat" the loudest are cheating the most often. The Freakonomics statisticians showed the most corrupt people are those never held accountable, and by profession K-12 teachers are most likely to lie, cheat, and steal.\normalsize   & \cellcolor{green!27}Nothing, Sexism, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}4/519 & \cellcolor{green!27}0.771 \\  \hline
  \cellcolor{green!5}\small That's what a \textbf{woman} isA man without accountability and respect\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Black females.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Stevia Sugar: Well said! Any unbiased person can see whose behavior is in question here. Out of control behavior has no \textbf{gender}, \textbf{race} or \textbf{nationality}. It happens all the time, but more frequently from some who thinks he or she can get away with it. She was at home, so she felt she was in charge. She played a victim so she could get her supporters to back her up. The lauder them became the more she increased her barrage against a man who was just doing his job. A very good job we must say! Give this real man the \$17,000.00 they collected from the abuser. She went home with more than a million. The penalty to be effective it needs to cause a pain in the pocket of the offender. The penalty amount should be a substantial percentage of what they are taking home. That will stop or decrease this abusive manipulation of the game (which as a form of cheating). This behavior is being used by some dishonest players not only in tennis but other sports as well. Humans will push the limits as long as they are allowed to. With all the attention they are getting for doing what is wrong, they won't be motivated to change. Can we honestly blame them for pushing the rules, if they are being allowed to? The decline in our society's morals is creating more opportunities for this barrage to be tolerated, encouraged, excused, and insanely justified. As one general famously said once, 'NUTS'.\normalsize   & \cellcolor{green!5}Gender, Nationality, Race & \cellcolor{green!5}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}3/254 & \cellcolor{green!5}1.181 \\  \hline
  \cellcolor{green!27}\small She's the number one \textbf{woman} tennis player, but about the top 300th when you count men. Just your daily reminder that men are physically superior. :)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small LuvCali28 find the white male chauvinists and quit assuming/implying/stating that all whites are \textbf{racist} and all males are chauvinists. That would be a great place to start.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small She's a spoiled \textbf{brat} who couldn't take a loss.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small The second out rage is the cartoon in a Australian newspaper like how else would you draw the cartoon which has \textbf{nothing} to do with \textbf{race} or anything else just player behavior on the court.\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small coralinealgae She has lived in America since she was 3 and only allow a dual citizenship until the \textbf{age} of 22\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Lol... If Serena Williams was any other white \textbf{woman} or MAN😱 this wouldn't even be in issues. She has more Grand Slam then any other American MAN and \textbf{woman}, past and present and she still get no respect. She has no glass😱 really? Why? she's tested more? She just had a child a year ago😱 and made 2 finals. Had a very tough pregnancy and almost died. All the Mary Jo and her team our jealous of all her achievements... Haters. She stood for own right's. Let this go... Your President needs the attention😟\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/94 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Rayshon Pittman stop playing \textbf{gender} card,\textbf{race} card ,mom card... It doesn't help.... If she was dying then shouldn't have played.... That hippo should learn how to behave first.....\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Ref is sexist in favor of the other \textbf{woman}.....??? What?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The luxury of winning is not having to make excuses or \textbf{lame} explanations. Osaka shouldn't have apologized for winning. Women's tennis sucks anyway.\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small When I consider that at the majors,  to win a match, men have to win 3 sets \& women only have to win 2 sets but both receive equal prize money, that sounds like \textbf{sexism} to me---institionalized reversed \textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small so..he took the game away from her and he gave it to another....\textbf{woman}, so....\textbf{sexism}?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small No...your comprehension is off. She is obviously referring to the male players before her that have acted similarly and gone entirely without punishment. This is a comparison to previous rulings. It has \textbf{nothing} to do with her opponent..and it has \textbf{nothing} to do with the umpire's future call.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Sore loser. Period. Her behavior is unacceptable, especially considering that she's is a champion. Everyone must be held to the same standards and follow the same rules, or the standards and the rule are completely worthless. You see how social justice is always being exploited for a person's personal benefit? Notice how it's being exploited by corporations to turn a profit? Social justice has become cheap and superficial, and that's why society is doing the exact opposite of becoming a better place for everyone. Guess who's greatly enjoying the social instability and cultural degeneracy of the West? China and Russia. We make it way too easy for them to manipulate us. I've a friend who experimented with it, and it's really not hard to get an internet mob of hundreds to attack an individual or group for absolutely no reason at all. Their greatest achievement in the game of social engineering was to persuade a \textbf{black} rights Facebook group that the Jews were really behind the Atlantic Slave Trade and everything that followed. By now a few of them have probably adopted extremist ideologies and have become fervent anti-Semites. Ez Pz. Social justice has become a kind of market, and it's also become a kind of social credit. The more zealously a person promotes it, the better their personal image. Authenticity and sincerity not required.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/225 & \cellcolor{green!27}0.444 \\  \hline
  \cellcolor{green!5}\small Hogwash Serena.....you claiming "\textbf{sexism}" is just you hoping to end any further discussion about this\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small So they lost because of \textbf{sexism} even though her opponent was a female.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Honestly I find the whole story despicable, and frankly there are so many people who have cried \textbf{racist} or sexist that I automatically thought she cried sexist like the boy who cried wolf.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small If that dude didnt make hand gestures \textbf{nothing} wouldve happened. That coach shouldve been the one she shouldve raged at. She didnt, she instead went for everything and everyone else. Its her fault and her coaches fault.I always respected Williams but this is just screams bullshit to me...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small huh...the call of coaching implies the coach was coaching. The player looking up and seeing the coach just sitting there doing \textbf{nothing} isn't against the rules Obviously he wasn't questioning her character. And if he was? evidently according to the tennis community that's vocal about this, all coaches coach in the box, and even Billy Jean King said it should be allowed. That's a pretty shallow attack on someones character. It's more a by the books technicality.  plus you've just made an excuse for athletes. Plenty of people have stressful jobs, that doesn't mean you can blow up on people. If anything, that's less stress for Serena, she doesn't need to win to make rent, or keep her job, or provide for herself. She's filthy rich in her own right, married to someone even more filthy rich, and she's already broken almost every tennis record male or female.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/148 & \cellcolor{green!5}0.676 \\  \hline
  \cellcolor{green!27}\small The coach can send a signal.  Who is to say if the player saw it?   Every player can say, I never saw a signal.  So, if a coach is spotted sending signals it has to be asserted the player saw it.  This prevents the I Did Not See Any Signals.  Everyone does it is not excuse.  The fact the U.S. Open does not allow it is another battle for some other day.  Persoally I'd love to see the players get real time coaching.  It could make for some great tennis.Serena Williams kept stating she is not a cheater.  The chair umpire could have told her that's not the issue.  The issue is what her coach did.  The rules require the player to bear the discipline.  That may sorted it.Next up.  We are all human and far from perfect.  People will lose their temper.  To believe they won't is \textbf{crazy}.  Even someone as successful as Serena Wiliams is allowed to lose her cool.Finally, yes Serena is successful and wealthy.  She is also 36 and trying to set a record.  Time is not on her side.  She knows that.   Setting records is stressful too.  In the end, sports refs and umpires should never be the big story in a match.  This chair umpire blew it too.  The fans potentiallhy were screwed out of a great match too.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/228 & \cellcolor{green!27}0.439 \\  \hline
  \cellcolor{green!5}\small THANK YOU SERENA! Thank you so much for highlighting such an important issue that goes unreported all the time! Thank you so much for highlighting how a large amount of women use the notion of \textbf{sexism} as a scape goat to hide their own poor behavior, poor performance, poor attitude, sense of entitlement, and overall shortcomings. Using \textbf{sexism} as a means of escaping responsibiliy for your piss poor actions, attitude, and judgment is a shinning example for all women of what a strong and independent \textbf{woman} is. Your a proud and strong role model for any looking to escape personal responsibility. I'm glad you lost, in your head and in your heart Serena you know you behaved like a spoiled obnoxious child. I know you know, and I know you know that most people know. I hope you feel that deep shame when people look at you.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/147 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Oh no, she didn't just pull the \textbf{sexism} card... somebody is a little spoiled.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Serena is a spoiled \textbf{brat} and a sore loser..\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small the \textbf{sexism} argument for "serena" is a bit iffy because he is really a man\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@⦓Za Warudo⦔ Serena is \textbf{tranny}, ( born as a man ).\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small To Sifon Medua : Have you heard of surrogate mother?Serena is a \textbf{transgender} pretending to be a female. The skeleton and muscle show that sHe is a male. He needed to shut down rumors that said he was a male playing against women. The best way to shut down rumors was to staged motherhood. The whole pregnancy was staged  publicly, not the birth itself. The baby is now used to promote the image of Serena as a mother. BS\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small \@Li Yong shit for brains, they don't actually \textbf{transition}.  They play pretend.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small ⦓Za Warudo⦔ I know right lol! How can she accuse the man of being sexist when she's playing against another \textbf{woman}.  She played herself with that BS.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Right! Those male arms and legs...no real \textbf{woman} compete. They are killing women's sports. Can we start an un-altered league?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small you accuse M. Obama of the same thing?  You are \textbf{racist} as all hell.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Yes she's of the female \textbf{gender},  but I'm sure her testosterone levels are right up there with a man's.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Richard Owens You're just stupid. I'd rather be \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Duncan Siror how? I'd love to hear a genuine explanation from a \textbf{black} person, in their own words. Go for it. I'm waiting. This should take some time.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@Rich Martzeni Why did you have to bring \textbf{race} into it? I thought this was about \textbf{sexism}? 🤔\normalsize   & \cellcolor{green!27}Race, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She also pulled the \textbf{race} card....Last time I checked a half \textbf{black} half Japanese \textbf{woman} isn't WHITEAnd neither was the PORTUGUESE referee\normalsize   & \cellcolor{green!5}Black, Race, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}3/24 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Oh Lawd haha that's a pretty \textbf{lame} excuse lol\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I am not so sure it is as simple as sore loser versus \textbf{sexism}. First, it wasn't \textbf{sexism} to me. Could it have been... Sure... But it was not remotely clearly so and she did push it regardless so even if it was, we can never really know. On the sore loser side however I do not think it was losing in and of itself that pissed her off, but when Umpires interfere with her winning or competing. She seems to have an issue with authority more than her opponent. At least that is what it looks like to me.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/100 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small I'm no tennis expert, but this definitely seems more like a case of sore losing and a stickler ref. If anything Serena should be idolizing Osaka for how well she handled her victory. Also, it's kinda hard to validate claims of \textbf{racism} and/or \textbf{sexism} when your opponent is an interracial \textbf{woman}.\normalsize   & \cellcolor{green!27}Racism, Sexism, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/51 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Joseph McHugh Where would she be without Serena. She has been watching Serena since the \textbf{age} of three.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Notsoscared There are layers to this. Her father was inspired by The Williams family and took it upon himself to train his daughter in tennis just like Serena's father. She has followed Serena since she was three and even used some of the same coaches. If you look at the sport, it is predominantly white sport and Richard and his daughters endured a lot of \textbf{racism} that just being \textbf{Black} and dominant.\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small After all these years....I had no idea that John McEnroe was such a staunch fighter for feminism and \textbf{gender} equality when he was screaming at judges.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small The \textbf{race} card, and the \textbf{gender} card, using either of these makes you look like a tool.\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small The "\textbf{race} card"? No. \textbf{Racism} is not over. You've just made an absolutely idiotic statement. To blindly discount every claim of \textbf{racism} would be absolutely foolish.\normalsize   & \cellcolor{green!5}Race, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/26 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small serana williams did it all by herself, she should of stopped after the first warning and never broke her racket, she knows the rules and have been playing pro since she saw 14 or 16 and won her first USOPEN when she was 19 years \textbf{old} back in 1999 give or take a year or two\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Wow. She lost, so it must be \textbf{sexism}. She also cheated.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Everytime somebody uses the "\textbf{racist}" or "sexist" card when losing he/she loses all my respect.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Here in Europe the vast majority of \textbf{black} people don't act like that, the ones that do are the kind that believe in Sharia Law. \textbf{Black} Americans however (not all of them) are a disgrace to the \textbf{black} \textbf{race}. In fact most \textbf{black} people in Europe call \textbf{black} Americans "FAKE Africans"\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/51 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Is there \textbf{sexism} and tennis? Of course there is. Against men. Women only have to play three sets men have to play five cents. Man get five minute break between sets women get 10. The top ranked \textbf{woman} Serena Williams can't beat a middle level college men's player.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small and then some idiots will tell us that blacks are not \textbf{racist}... lol\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Well we all know Serena knew she was caught getting coached, otherwise it's impossible for her to know if her coach was giving her 'just a thumbs up'. So let's put it this way; When Serena gets paid a million bucks for being the runner up, will she cry \textbf{sexism}? Women play much less than the men and yet they're paid the same in tennis. Will Serena give back a part of her money and say it's sexist towards men? I think we know the answer.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small not only that but women sell way less tickits and have why less viewer ship than the men, the men reached a bilion while women was 390 milion. so if it was \textbf{sexism} it is towards men.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small +415City - just a shame that Serena is even allowed to play in the womens league considering he/she is a \textbf{tranny}.  How unfair to the other players.  It's time to do \textbf{gender} testing for these games.\normalsize   & \cellcolor{green!27}Gender, Tranny & \cellcolor{green!27}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small +Taylor by that logic no man with a wife can hate women, obviously false, some of the most sexist men ever have wives or girlfriends. Liking or tolerating a single member of the opposite \textbf{gender}(who also helps pay your bills and such) does not mean you do not harbor intense hate and resentment towards the \textbf{gender} as a whole.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small KappaW a feminist is different to a sjw . Feminism is based on the notion that everyone is equal. I don't quite understand how Serena is depicted as a sjw just because of this one incident and the fact that she didn't understand that the umpire is strict to every tennis player. Making assumptions that Serena is a 'man-hating sexist' is ridiculous. I understand that she might appear that way because she called Carlos a thief, but that is totally unrelated to \textbf{gender} if you recall the 2009 us open incident ( she threatened the lineswoman and called her way worse).\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/101 & \cellcolor{green!27}0.99 \\  \hline
  \cellcolor{green!5}\small +Taylor - Serena isn't a SJW.  Serena is a MTF.  Serena wasn't out there playing for women's rights or her/his daughter.  Serena was out there for the money.  Serena didn't just have a baby because MTFs cannot have children you have to have a uterus and ovaries to have a baby.  The baby was either adopted or is a surrogate courtesy of her husband's sperm.  MTFs (and WTM) do not \textbf{age} well.  Serena is 36 and the estrogen isn't working any longer.  So each year Serena (and Venus) are reverting back into the males that they were when they were born.  Unfortunately, they've had so much plastic surgery done with breast and buttocks and who knows what else, that this will not end very pretty.  Can't you tell by looking at Serena's huge skull?  Her skull didn't look like that when she was a teenager.  Look at the eyebrow ridge, the slanted forehead and jaw line. Women do not have the kind of arm and leg massive skeletal muscle structure that Serena has.  Can you think of any other \textbf{woman} tennis player that was that huge?  Hell, she's bigger than most of the men! Serena is really pissed that the gig is up.  I'd be pissed too.  Serena and Venus never had a choice in the matter.  Their father into the worship of the baphomet and he sacrificed both his two sons for wealth.  He said as much in a magazine.  He wanted out of Compton but was poor.  So he sacrificed Serena and Venus to the baphomet. They were given estrogen from a very young \textbf{age} (Just like Shiloh Pitt is being sacrificed.)  Serena and Venus were castrated before puberty and their penis was made into a "vagina."  Their father is a bastard and should be put in prison.  I'm sure Serena was very jealous of the beautiful young \textbf{woman}, Naomi Osaka she/he played against and that might actually be the reason Serena played so poorly.  Naomi is at the beginning of her career and Serena is at the twilight of hers/his.  Hell, even the referee got to live a more authentic life than Serena and Venus.  How sad is that?\normalsize   & \cellcolor{green!5}Age, Woman & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}4/362 & \cellcolor{green!5}1.105 \\  \hline
  \cellcolor{green!27}\small +Taylor - As serious as a heart attack.  If you cannot see it, there are plenty of anatomy charts on youtube specifically addressing this issue.  Look at the shape of her head since she was in her early 20's (not hair, just eyebrow ridge, forehead \textbf{slant} and jawline).  She is more muscular than most men.  Frankly, I don't care how she/he chooses to live but it is not an honest competition for a MTF to play against a female.  And since this is our new reality, it needs to be addressed.\normalsize   & \cellcolor{green!27}Slant & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small And now for my real comment...  Chris basically nailed it.  Serena broke the rules, was rude and abusive to the umpire and ultimately got what she deserved.  Her argument is like a speeder asking the cop why he didn't pull over all the other speeders.  There was no "\textbf{sexism}" here.  Just another entitled millionaire athlete thinking she was above it all.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Sore loser. If it was \textbf{sexism}, how did a \textbf{woman} won?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small She's a terrible person. Not because she's \textbf{black}. Not because shes a \textbf{woman}. She's just a terrible person.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small You're \textbf{crazy}, there's no way being a terrible person can be a separate thing in and of itself, it has to be tied to race/gender/politics/religion/etc!  /s/\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Lies cause she played Serena her 1st tournament back after the baby and Naomi won and Serena was \textbf{nothing} but gracious so come again boo😒😏💁\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@America UncoveredEven members of the Chinese \textbf{Communist} Party?\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Rico Shaye  The \textbf{Black} Swan whaaaaman🤣🤣🤣🤣🤣\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small mr grey+  the heroes will turn out to be big disappointments.  possibly in this case, also a \textbf{transgender}.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Politically Unreliable my mom said that \textbf{woman} have veganas.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Both competitors are \textbf{black}, and Im sure she was playing for a championship, not for women's rights. I mean if she did they lost.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "\textbf{Racist}" "You owe me an apology "\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small KappaW       Im \textbf{old} enough to remember McEnroe's 'You guys are the pits of the Earth' outburst at Wimbledon. They made a pop record out of his antics.   Advertisers ensure he's been eating off that line to this day. Cos he's a MAAAAAAAAN right?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Said the \textbf{Chick} with the Ironman arms...no real \textbf{woman} can compete with that. 😡\normalsize   & \cellcolor{green!5}Chick, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Beau Lijah losi \textbf{mong} supot ka.Ang lobot \textbf{mong} mabata.Na para-iwang san papel.dusta.Pwe.matigbak ka ki kakaisip na supot ka.\normalsize   & \cellcolor{green!27}Mong & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Just a baby popped out between the legs does not a "\textbf{woman}" make...  Ask Caitlyn Jenner.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Good God. She is a \textbf{black} monster! Like those from fairy tales.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small oldi184 you are making a \textbf{racist} comment here ! Also why does she trigger a memory of a monster in you ? Cd you check your social conditioning in your Brian where you are told to believe that women should fit a certain body and COLOR and behaviour ? Huh so sorry for you and your environment.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small KappaW - She's a \textbf{woman} is debatable.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Turns out Naomi Osaka isn't a \textbf{woman} according to Serena.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small dave erwin \textbf{woman} do it far more than men in every day life nowadays...called feminism...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small A "\textbf{woman}"\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small How is it \textbf{sexism}, she was playing against another female and the umpire had \textbf{nothing} to gain from the call.\normalsize   & \cellcolor{green!27}Nothing, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Nobody wants to see women play 5 sets. It's boring enough as it is. 😁\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small lol. Wow. 2:35 that was never mentioned in the other reports on this 'incident'. She basically said "You won't work in this industry every again."And wow. Look at all these allegations of \textbf{sexism}, which has in recent times been used to castrate men out of their jobs. For a FUCKING GAME!\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Using \textbf{sexism} as a excuse of your failures without hard proof makes you  a sore loser. I hear it too many times the excuses of \textbf{sexism} being thrown a lot that I am afraid it will blur the line real \textbf{sexism} and non-\textbf{sexism}.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small It's not sexist....because her challenger was a women, a mixed \textbf{race} women....so she is a bad looser....she is playing the victim....\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Actually they might be. But whichever ones you are talking about (as well as other \textbf{woman} athletes) have always had the sense to be professional and guard their emotions until AFTER the match.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Oh they are, and they are punished the same most of the time. They are punished MORE than women, if you look at how many code violations are dished out to men as opposed to women at any grand slam in history.Just look at John Macenroe back in the 80's, and in 1990. He was disqualified for being just as bad as Serena.But you're right in how the violations are dished out. Warning, point, game. She kept pushing it, and as soon as you start insulting the umpire, calling him a thief and a liar, demanding an apology, she was guilty of another infraction. The umpire had no alternative.Her pulling the mother card and the \textbf{woman} card is just telling of how angry she was at losing to a virtual unknown, especially one that was a minority, so she couldn't pull the \textbf{race} card.\normalsize   & \cellcolor{green!27}Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/147 & \cellcolor{green!27}1.361 \\  \hline
  \cellcolor{green!5}\small These rules are made by the fucking lawn tennis association, and the international tennis association. These associations are made up of ex-players, founders, and owners of the clubs where tennis is taught and played. If they aren't the appropriate people to come up with rules, then I don't know who is.And of COURSE they aren't allowed to go breaking property, their own or otherwise. Act appropriately.And it's not that coaches can't coach. In a grand slam, they aren't allowed to coach during the game. In other championships they can, but not in grand slams, they are the pinnacle of the sport and rely on certain sets of rules. These rules have been in place since day one for the most part, and every player who plays knows the rules and agree's to abide by them.They don't have to agree, they can refuse to take part in grand slams if they don't like it. But Serena has been at the very top of this sport for over 15 years, she knows the rules.As you say, you don't like the sport anyway. Good for you. You're obviously just a SJW \textbf{feminazi} demanding everyone change the rules of a sport you know fuck all about. That is fascistic, don't you think?And regardless of whether she agreed with the umpire decision, claiming feminism and claiming "I'm a MOTHER" is just fucking ridiculous, and this is why people hate her. She had absolutely no right to claim it was because she was a \textbf{woman}, and claiming this \textbf{old} "I have a daughter" line is really fucking \textbf{old} now. We know you have a daughter Serena, you have been banging that drum for over a year now, since you're the only \textbf{woman} to ever give birth in the history of mankind (Sorry, PERSONkind. twat)\normalsize   & \cellcolor{green!5}Feminazi, Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - Female intelligence, Gender - General & \cellcolor{green!5}5/303 & \cellcolor{green!5}1.65 \\  \hline
  \cellcolor{green!27}\small "You're obviously just a SJW \textbf{feminazi}" - yep, obviously. 'Ex-players' - like who? Can you provide me a list of these people? Or are you making shit up again? I've played tennis for fun too. Am I now an Ex player? I'm reading a few things about Tennis \& it seems as though, various rules have changed over time. So what makes the 2 rules, the most important? Don't show emotion, be a robot? How can anyone actually tell if a coach is coaching? What if a coach \& player make up secret hand-signs? Kind of renders the rule useless. Not to mention the accusation by Serena's coach, who said that the Japanese coach was coaching more. So, now does the Japanese player get disqualified \& the trophy gets handed over to Serena? Nah. I guess not. \& where does the line of 'breaking stuff' stop? Can anyone rip a towel in half? Or does the rule only apply to the racket? These rules do not exist in - any other sport. So why is Tennis pretending to be better then any other sport?\normalsize   & \cellcolor{green!27}Feminazi & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/184 & \cellcolor{green!27}0.543 \\  \hline
  \cellcolor{green!5}\small ..Yeh \& Carlos Ramos has such a \textbf{thin} skin that being called a thief = verbal abuse. But fine, whatever. Serena still got a shiny silver thing and money anyway.\normalsize   & \cellcolor{green!5}Thin & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Honestly, all this seemed to do was lower her reputation and that of other women in the sport. And how would men have benefited from penalizing a \textbf{black} \textbf{woman} playing against an Asian \textbf{woman}, when all the records that those women could break were already set by other women?\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/49 & \cellcolor{green!27}6.122 \\  \hline
  \cellcolor{green!5}\small Yes and she is 36 and trying to break a record.  Time is not on her side and she knows it.  I think \textbf{age}, trying to set a record and playing bad on Saturday got to her.  When she played where I live a few weeks ago she got her ass kicked in the first round.  She did not make a big deal out of it.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small I agree.  Compete with grace, win with grace, lose with grace.  Don't be a whiny cryababy victime thug.  \textbf{Nobody} respects that even when you win.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small thelongslowgoodbye She's A \textbf{Black} \textbf{Woman}. \textbf{Black} Women are a stone in any mans shoe.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/14 & \cellcolor{green!5}21.429 \\  \hline
  \cellcolor{green!27}\small I feel really bad for the girl who one. That was very uncool of us.   This current naritive of the media and it's affect on the US population has just now embarrassed the whole country and made us look like jack asses to the whole world.   My days off being compassionate twords \textbf{race} and \textbf{gender} is now officially over\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small Kay Em no, it wasn't, it was about a \textbf{dumb} rule. They should have just removed the coach since he isn't allowed to do or say anything. He can sit there and do all types of hand gestures and she doesn't have to know about them to get into trouble.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small crying \textbf{sexism} while playing in a womens tennis match, against a \textbf{woman}, as a \textbf{woman}......am i missing something?\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/18 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Racism/\textbf{sexism} or sore loser? I think it's a champion who got a bit too caught up with herself and had a moment of bad sportsmanship, but because she's too big, so if she falls she's falling hard, so she's using the \textbf{sexism} card. If she could, the \textbf{race} card, but her opponent was the same color, so can't use that.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small oh she is using the \textbf{race} card now.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@TheNodrokov her opponent is japanese with a Haitian father. You could also say her opponent is Haitian with a japanese mother. Regardless, it's still 2 opponents of \textbf{colored} complexion going against one another, what's your point anyways?\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small If by "\textbf{colored} complexion" you mean "not ethnically european," then yes, they're both of a "\textbf{colored} complexion". But Asians and \textbf{Black} people are not the "same color." They're literally on opposite ends of the skin color spectrum. No, I don't see what you're saying. \textbf{Race} and \textbf{nationality} are different things. You can be white and be from Ghana, but if you're white, you don't have the same skin color as Serena Williams, it doesn't matter where you were born.\normalsize   & \cellcolor{green!27}Black, Colored, Nationality, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!27}5/79 & \cellcolor{green!27}6.329 \\  \hline
  \cellcolor{green!5}\small Maybe Serena was \textbf{racist} because she saw the straight white male and prejudged him.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Stepnort of course he's white. He's a Portuguese white man. But what's with Americans having to put \textbf{race} and \textbf{sex} in every discussion? Most sexist and \textbf{racist} people I've ever encountered.\normalsize   & \cellcolor{green!27}Race, Racist, Sex & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small Guess im white now, because im not \textbf{black}.But i should be because im way more light skinned than that guy. And did you just assumed his \textbf{sexual} orientation??\normalsize   & \cellcolor{green!5}Black, Sexual & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Right out of the \textbf{black} victimology handbook.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The Brazilian butt-lift looks very unnatural on the male frame of that mandigo Sereno. What a \textbf{freak}!\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Standard operating procedure in this day and \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She played the "I'm a \textbf{woman}!" "I am a mother!" "This is \textbf{racist}!" Cards.\normalsize   & \cellcolor{green!5}Racist, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@ls7orBust \textbf{weird} good information thanks friend\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Besides just look at her. She is taking male hormones thats why she is strong and have more muscles. This not a normal female body but male body. Her ass, her legs and face. Its male hormones all over the place. So comparing her to other normal female players like Sharapova is pointless. Watching her playing vs other \textbf{woman} is like watching a guy vs female.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Another \textbf{lunatic} leftist displaying why we have a Trump in the White House today. She tried to play all the 'political correctness' victimization cards that applied to her for all the world to see...the poor pitiful thing. This will end up being a huge endorsement for the right...thank you Serena!\normalsize   & \cellcolor{green!27}Lunatic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Elias Frahat.she couldn't play the \textbf{race} card as I so often hear in my country,her opponent was not exactly white,so she took the easy way out \textbf{sexism}.Serena is the worst loser the game has ever seen.I actually can't stand to watch her play,she has no class,the opposite of Venus.what in heavens name did her husband see in her.This marriage may last 2 yrs tops.As for Oracine she definitely is Serena's Mama only difference is the color of her hair.\normalsize   & \cellcolor{green!5}Race, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/79 & \cellcolor{green!5}2.532 \\  \hline
  \cellcolor{green!27}\small \@Folk Aart Exactly. \textbf{Black} people, especially \textbf{black} Americans all have a major chip on their shoulder.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Elias Frahat Actually,  a man playing tennis as a \textbf{woman}.  Look at pics of Serena when she was a little boy wearing beads.  Look at her waistline below her belly button as all men have. Baphomet transgenders.  Clue yourself in already.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Revolver As if white \textbf{t\textbf{railer trash}} meth freaks don't.\normalsize   & \cellcolor{green!27}Trailer trash & \cellcolor{green!27}Ethnicity - White, Social Class - Working class & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small I think Serena "tried" to apologize in her own way but it was too late...for Serena. :-) Nike stock price hitting a 52 week high though. I bet Nike will even pay any fines levied for "poor behavior" on Serena's fault. A suggestion to the entire \textbf{black} community. It is better to just take the traffic citation instead of accelerating the madness, because sometimes that doesn't work out in your favor. Unless you own a shitload of Nike stock of course.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small That's "being \textbf{black}" 101Colleges teach this.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Mind Freshener lol no kidding. I've seen tons of irrefutable evidence proving he/she's body is more parallel to that of the male biology. In every comparison between male or female in the photos regarding different parts of the body, Serena and Venus 100 of the time matched up to the body of a man even when compared to REAL \textbf{woman} with plenty of muscle.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small \@Phil Douglas Someone else with a good eye for detail. Saw information about it years ago but it's irrefutable that only men have a waistline below their naval as opposed to women having it located above due to difference in the shape of their pelvis. Comparing the "sisters" to openly \textbf{transgender} people is too harsh for sheeple to process and accept due to cognitive dissonance but unfortunately facts don't care about their feelings.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small I loved it when she said of  her disgusting \textbf{black} catsuit: "I feel like a warrior wearing it, a queen from Wakanda maybe," but then when it was banned said "I was wearing a special suit that prevents blood clots." Right. Surprised she didn't say it was for the "Children of Africa",or a "dying child" she knew asked her to or some other defense she made up that you're trained to be sacred to say anything against. Classic argumentum ad misericordiam, an appeal for pity. Sorry Serena, Some of us are educated enough to see right through that.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small Like a normal \textbf{black} person does ...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small BakkedBakkon What about abnormal \textbf{black} persons.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Mom Live Yeah huh.  What can account for people being so \textbf{blind} and stupid? I mean,  it's so obvious!\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Phil Douglas You don't see them organising violent protests and destroying public property because a criminal of the same \textbf{race} got shot by police.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small ruptured duck ...kanye is also a sore loser and always demands attention like a spoiled \textbf{brat}! 😡\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small You stole a point from me, you owe me a point too! Since when does the umpire 'owe' points to any player? So... if you have a son, that wouldn't be sexist, but since she has a daughter, the umpire is sexist? What if the umpire were a \textbf{woman}, or if he were \textbf{g\textbf{ay}}? Hmm... thank goodness Serena is not unattractive inside. Just outside. Just her mind. Just her mouth. Just saying...\normalsize   & \cellcolor{green!5}Gay, Woman & \cellcolor{green!5}Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/72 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Gay men might be the most sexist group of people by stereotype there is..... Lol they'll cut a bitch down with sass; quick.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Once again a \textbf{woman} of colour is pulling the \textbf{sexism} and \textbf{racism} card, for being punished for her own actions. The world we live in today.\normalsize   & \cellcolor{green!5}Racism, Sexism, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/26 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small \@anarchore You guys claim \textbf{racism} and \textbf{sexism} don't exist when \textbf{black} people and women complain about it yet here you are, the exact examples of \textbf{racism} and \textbf{sexism} that you claim doesn't exist\normalsize   & \cellcolor{green!27}Black, Racism, Sexism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}5/33 & \cellcolor{green!27}15.152 \\  \hline
  \cellcolor{green!5}\small I heard her play the mother card, I heard her play the \textbf{woman} card. Can I get a timestamp of the \textbf{race} card?\normalsize   & \cellcolor{green!5}Race, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small honestly, although I know what she did was wrong, thats just plain \textbf{racist}, and is the root of scientific racism\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small well, she is \textbf{black}, I am \textbf{y\textbf{e\textbf{llow}}} and you guys are PINK not white.... white is the color of clouds and you guys don't look white to my eyes. you guys are pink in normal days and sometime \textbf{r\textbf{ed}} and pink mixed. stop saying I am white and they are \textbf{coloured}. PINKTARDS\normalsize   & \cellcolor{green!5}Black, Red, Yellow, coloured & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}7/52 & \cellcolor{green!5}13.462 \\  \hline
  \cellcolor{green!27}\small \@Lucas Ferreira you can say just by analogy but behind that very sick analogy there is subliminal message which says white is pure, nice and clean and \textbf{black} is dirty, dark and unclean. I don't buy this shit. This analogy should be changed. No more \textbf{black} or white. You are not white and I am not \textbf{black} or \textbf{y\textbf{e\textbf{llow}}}. Why can't the analogy be pink or brown. Don't twist the subject. :)\normalsize   & \cellcolor{green!27}Black, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}6/72 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Sarge Sacker25. Please go listen to the rant again. I have a few times due to shock that it happened. Your comment is 1/2 right. Serena Williams played two cards. 1. \textbf{Sexism}2. (As another poster posted) the 'I AM A MOTHER!' cardHowever, unless I totally missed it all 3 times I listened, Serena Williams never played the \textbf{racism} card.\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small \@Lamarr WillifordPlenty of \textbf{race} card pulling in the YT comments sections but none by Serena herself AFAIK.People just seem to assume she did.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small What \textbf{race} card did she play??A guilty mind needs no accuser.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Sarge Sacker25 her Japanese opponent not white not doing so. So nice try. I don't support Serena but happy to see the rent a \textbf{racist} mob out again. Her husband looks white.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small You assumed that she played the \textbf{race} card coz she's a \textbf{woman} of colour??You played it for her.\normalsize   & \cellcolor{green!5}Race, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small I do have to give her some credit for NOT playing the \textbf{race} card. It was everyone else who started throwing \textbf{race} into it.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Did she accuse anybody of \textbf{racism}...?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small nomad 59 what? I'm white but skin tone has a \textbf{y\textbf{e\textbf{llow}}} tinge... not pink\normalsize   & \cellcolor{green!27}Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}3/14 & \cellcolor{green!27}21.429 \\  \hline
  \cellcolor{green!5}\small Black isn't even a color. It's when all the colors of the color spectrum have been removed\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Here ass must be glowing red\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@TentaclePentacleExactly. Some men have been DQ'd for not letting go.It's about knowing when to quit arguing much more than about how heated the argument or how \textbf{coarse} the language.Roddick got away with calling an umpire an idiot once. The operative word is "once". He had a point, spoke badly but ultimately let it go. It's a judgment call by the umpire each and every time so it's never going to be "consistent".\normalsize   & \cellcolor{green!5}Coarse & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Actually sore player on her way to losing.  That Osaka \textbf{woman} got in Serena's head.  She must have been laughing on the inside knowing she had Serena on the ropes.  Osaka did not need any singals from her coach.  She knew it was time to move in for the kill and she did.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small If you have another citizenship which automatically you loses the Japanese citizenship by Japanese \textbf{Nationality} law. Dual Citizenship is really not recognise in Japan.\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@ミーム王 I totally understand your logic there that if an athletic has a US Citizenship and he or she represents the US in the World Cup or the Olympics which athletic born in the respective \textbf{nation} should represent in that respective \textbf{nation} but it is probably her individual choice for some reason (US National Tennis Teams has full of young talents, the US National tennis team does not really need anymore young talents and there is really no spot for her in it so she is forced to represent the Japanese National Team instead or represent Japan) and same goes for Chinese Nationals who happened to be athletics which they could not find a spot in their national team because they had full of young talents in it so they are forced to represent other nations who doe not speak their language like the Mainland Chinese Table Tennis players like Li Jia Wei or Swimmers like Tao Li in here in Singapore \& the US who happened not speak their language \& of course they have to give up their Chinese citizenship automatically because of the Chinese \textbf{Nationality} law .\normalsize   & \cellcolor{green!27}Nation, Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}3/190 & \cellcolor{green!27}1.579 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman, Sexism, Gender, Sex, Patriarchy, Chick, Sexual, Misogyny, Misogynist, Misandry & \cellcolor{red!27}1535 & \cellcolor{red!27}1535/212017& \cellcolor{red!27}0.72 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Transexuality}  & \cellcolor{red!5}Tranny, Transgender, Transvestite, Drag queen, Transsexual, Transition & \cellcolor{red!5}73 & \cellcolor{red!5}73/212017& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old, Senior & \cellcolor{red!27}99 & \cellcolor{red!27}99/212017& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian, Red, Apple & \cellcolor{red!5}29 & \cellcolor{red!5}29/212017& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racist, Race, Racism, Ethnic, Ethnicity & \cellcolor{red!27}487 & \cellcolor{red!27}487/212017& \cellcolor{red!27}0.22999999999999998 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black, African, Nigga, Negro, Colored, Monkey, Fuzzy, coloured, Ape, Spade, Buck, Sambo, Crow, Jim Crow & \cellcolor{red!5}416 & \cellcolor{red!5}416/212017& \cellcolor{red!5}0.2 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Crazy, Dumb, Weird, Psycho, Lame, Blind, Mental, Eugenics, Bonkers, Freak, Weirdo, Handicapped, Mong, Lunatic & \cellcolor{red!27}148 & \cellcolor{red!27}148/212017& \cellcolor{red!27}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Brat, Zero & \cellcolor{red!5}267 & \cellcolor{red!5}267/212017& \cellcolor{red!5}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Witch & \cellcolor{red!27}5 & \cellcolor{red!27}5/212017& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Alien, Nation, Nationality, doctors, Immigrant, Xenophobia & \cellcolor{red!5}34 & \cellcolor{red!5}34/212017& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Slag, Ho, THOT, B*tch & \cellcolor{red!27}8 & \cellcolor{red!27}8/212017& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Nazi, Libtard, Red, Snowflake, Commie, Imperialist, Communist & \cellcolor{red!5}36 & \cellcolor{red!5}36/212017& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Destitute}  & \cellcolor{red!27}Underdog, Bum & \cellcolor{red!27}5 & \cellcolor{red!27}5/212017& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}Homosexual, Gay, Queer, Homophobic & \cellcolor{red!5}8 & \cellcolor{red!5}8/212017& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!27}Banana, Oriental, Yellow & \cellcolor{red!27}12 & \cellcolor{red!27}12/212017& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - White}  & \cellcolor{red!5}Honkie, Trailer trash & \cellcolor{red!5}3 & \cellcolor{red!5}3/212017& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Bald, Thin, Skinny, Fat, Obese, Lump, Fatso & \cellcolor{red!27}24 & \cellcolor{red!27}24/212017& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}Oriental, Slope, Yellow, Slant & \cellcolor{red!5}11 & \cellcolor{red!5}11/212017& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Japanese}  & \cellcolor{red!27}Oriental, Yellow & \cellcolor{red!27}9 & \cellcolor{red!27}9/212017& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Fruit, Drag queen, Gay, Queer & \cellcolor{red!5}11 & \cellcolor{red!5}11/212017& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female intelligence}  & \cellcolor{red!27}Feminazi, Becky & \cellcolor{red!27}12 & \cellcolor{red!27}12/212017& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age, Ageism, Ageing & \cellcolor{red!5}29 & \cellcolor{red!5}29/212017& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common, Cheesy, Trailer trash, Coarse & \cellcolor{red!27}25 & \cellcolor{red!27}25/212017& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Southern European}  & \cellcolor{red!5}PIGS & \cellcolor{red!5}1 & \cellcolor{red!5}1/212017& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Drugs}  & \cellcolor{red!27}Drug addict & \cellcolor{red!27}1 & \cellcolor{red!27}1/212017& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Jewish}  & \cellcolor{red!5}Abe & \cellcolor{red!5}1 & \cellcolor{red!5}1/212017& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Irish}  & \cellcolor{red!27}Paddy & \cellcolor{red!27}1 & \cellcolor{red!27}1/212017& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry & \cellcolor{red!5}1 & \cellcolor{red!5}1/212017& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}1 & \cellcolor{red!27}1/212017& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Sexual Identity - Transexuality;Age - Over 65s;Ethnicity - Native-American;Ethnicity - General;Ethnicity - Black;Physical Identity - Physical (and Mental) Impairments;Age - Youngsters;Gender - Female age and physical appearance;Nationality - General;Gender - Female sexuality; Ideological and Political Identity - General;Social Class - Destitute;Sexual Identity - General;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Ethnicity - White;Physical Identity - Physical Features;Nationality - Chinese;Nationality - Japanese;Sexual Identity - Male homosexuality;Gender - Female intelligence;Age - General;Social Class - Working class;Nationality - Southern European;Behavioural Addiction - Drugs;Religious Identity - Jewish;Nationality - Irish;Nationality - German;Religious Identity - Muslim;%.

\item The percentage of hate speech related words is 1.5527.

\item Considering that the variable \textbf{Gender - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 3295/8451 occurences of hate speech related comments.\end{itemize}\end{document}