\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_297.json :}\newline \par\Large\textbf {Title: \large  Partying In Europe's Biggest Slum | Lunik IX }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Giving the camera to that kid and letting him go film was a seriously fresh idea.You dont get that on any type of travel documentary. To see the young ones and how they act naturally was brilliant.Changing the game \textbf{Bald}!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small \@Vegan4life not just4fashion It's like that in many rich areas of the world aswell though. Its quite normal for young teenagers to act that way in this day and \textbf{age} unfortunately, since the rise of TV and the internet, it's so easy for kids to observe what should be kept exclusive to adults.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small \@Vegan4life not just4fashion i too feel sorry for the children. near impossible to get out of that. drugs, \textbf{alcohol}, tobacco, etc. i wonder why they live like that? i suppose each generation teaches the next the same that they learned.  perhaps the cycles somehow needs to be broken somehow.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small I have to agree. What I saw was raunchy, but real... And the fact that \textbf{bald} was like, "what the hell, here you go," risking never seeing his camera. I found it endearing.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@Ealdy  not true. \textbf{nobody} wants rapists and idiots, maybe.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Tom Walsh It was quite normal for adolescents and young teenagers to act that way 15 years ago.And it wasn't much more restrained 25 years ago when I was their \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Tom Walsh Are you sure about that?Because I've seen footage of \textbf{promiscuous} teenaged dancing from the 50's, 30's, 20's and even photos from the Edwardian era.\normalsize   & \cellcolor{green!27}Promiscuous & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Siblings are among themselves.  Girls are 12, 13 year \textbf{old} girls and live on social benefits.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Yeah, \textbf{Bald} builds the trust by acting like a brother.  Having a drink, respecting the elders and above all, being on their level.  Not better, not worse....  Being real..  Full credit..\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small This humanistic psychosis will get a lot of people in dangerous situations, see people for what they are, sense the danger, (but do not show it)..There are countless people that will take advantage of this do-gooder mentality. People have been living around gypsies all their lives, so it's kind of arrogant to think that all these Slovaks/host nations have never thought of being nice to them or talking to them, it's the worst mistake to try change people. Never trust people who are in groups like these, regardless of their \textbf{ethnicity}, since in a group you don't have to take responsibility for your actions. If you have lived a sheltered life knowing danger is very important.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/116 & \cellcolor{green!5}0.862 \\  \hline
  \cellcolor{green!27}\small \@Vegan4life not just4fashion women have many features that do not serve any useful purpose than attracting \textbf{sexual} partners.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Oula  what \textbf{nationality} are you?and how can i contact you ?\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Tom Walsh \textbf{Bald} knew where the kid lived and his parents.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Vegan4life not just4fashion a long time since you were that \textbf{age} it seems\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Vegan4life not just4fashion what does school help, as soon as you are a romani - \textbf{nobody} will hire you, because you are a \textbf{gypsy}.. thats where the vicious circle starts\normalsize   & \cellcolor{green!27}Gypsy, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@James Douglas someone should stab you 44 times in the face with a rusty rail road \textbf{spike}, no warning.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small ⲈⲘⲒⳐ ϝᚱⲀ ⱌεᚣⳚϟⲯssέᛇ  Stop throwing your garbage out of your windows. Typical \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small that shit was crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Bald gave the kid something more than just the device. He gave him confidence and hope.! Such kind of kindness can change a life.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small My kinda place \textbf{alcohol} and ho's.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small That forest part of lunik ix not only had iron walls, a tv, and a roof, but also somewhere to cook their food\textbf{bald}, if you go to Bulgaria, gulabovo, on the road to Mityo stanev you will see a 2 square km \textbf{gypsy} village where their houses are made from falling bricks,without roofs, no money, and especially do not go with a car there otherwise rocks will be thrown at it. They ride horse wagons so you will easily tell where to go if you see one.\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/88 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Song on 1:44 is serbian song not gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Yh is kind of Pakistani or \textbf{Indian} like the genes\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Better help this children than grow up \textbf{Refugee} Men That coming to EU\normalsize   & \cellcolor{green!5}Refugee & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small What \textbf{ethnicity} are gypsies?\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Europe will be better place....India of  today is paying for being good to  other world for many thousand years....not.more than 200 years ago, all voyages from Europe was to steal loot and plunder from India, our ancestors didn't doubted European people intentions and hence we are suffering...anyway we \textbf{Indian} are 5000 years \textbf{old} civilization, we know better how to beat odds....\normalsize   & \cellcolor{green!5}Indian, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small I m Pakistani and we hate \textbf{Indian} bocoz of some reasons... and many wars between us! But personally I don't hate much as like European' hate these \textbf{gypsy} \textbf{ethnic} people. European is full fill of hate averagely' not at all...'\normalsize   & \cellcolor{green!27}Ethnic, Gypsy, Indian & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!27}3/40 & \cellcolor{green!27}7.5 \\  \hline
  \cellcolor{green!5}\small As a Slovak, I admire the courage of \textbf{Bald}, because even some of us are afraid of that place.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small The flies don't necessarily mean the aparment itself is that dirty. It can be pretty hard to keep the flies out when there's a garbage dump outside your window. You saw it yourself and it was pretty clean, at least relatively to every other place there. It's in the \textbf{gypsy} culture to keep their own house very clean, even absurdly clean, but everything else can be dirty as hell and they don't give a shit.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Gypsy: "He is not smoking!"\textbf{Bald} guy: "Oh so he just finished them?"\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small lol I love it little \textbf{Gypsy} kids in Slovakia talking like a young \textbf{nigga} from the hood lol 😂\normalsize   & \cellcolor{green!27}Gypsy, Nigga & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small And people tell me not to be \textbf{racist}. Fuck off. Gypsies are nasty\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small All the romani hate in the comments is disgusting. People are born into circumstances which are difficult; this is the life of any group with a history of nomadism. With the urbanization of the industrial revolution, nomadic life was made impossible, and those nomads who settled down had no material history of privilege in that society. Where are you going to put your trash, the trash which was forced upon you through modernization, if there is no designated dump? This video made me happy, to see the thriving life in what are less than favourable conditions. Instead of scapegoating the problems of your \textbf{nation} upon an underprivileged class, why don't you call into question the Powers which stochastically regimented them into slums, and prevented them from higher education, basic living necessities such as a garbage dump, standardized plumbing, and so on. People are not driven to "live in squalor" out of choice or out of cultural nature, this is a \textbf{racist} lie meant to justify continuing the injustices and the peoples' ignorance of said injustices.If you want to actually change these peoples' lives and bring them out of this situation, don't continue the hate which justifies their oppression. How must it feel as a mother knowing that your children will never grow past what you have given them, to have "no chance" to leave Lunik 9? So much of the prejudice I see pointed towards the romani people is echoed within the prejudice against \textbf{black} people in my own country, and they both have similar material conditions which have lead for the need to justify that prejudice. Given no other choice, many \textbf{black} people in America live in redlined houses infested with lead, and neighborhoods with no public support or urbanized systems.I reiterate this once more: \textbf{Nobody} chooses to live in oppression. \textbf{Nobody} willfully throws their trash out their window knowing that a garbage truck will come next thursday. \textbf{Nobody} commits a crime for money not out of desperation. You people who reduce the struggles of the Romani down to their \textbf{race}, or their culture, are fundamentally ignorant of how societies form and how upper classes make their profits.\normalsize   & \cellcolor{green!27}Black, Nation, Nobody, Race, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!27}8/361 & \cellcolor{green!27}2.216 \\  \hline
  \cellcolor{green!5}\small the modern day india have majority aryans who are descendants from Caucasus mountains(russia),who almost ruled india for centuries and neglected \textbf{black} Indians(native indians) the \textbf{black} Indians are taken far away from india to islands like fiji ,Mauritius,guyana,suriname and even parts of Europe ...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small The problem is in the government a few little facts u get 60 something euros a MONTH a month, child benefit was cut from 25 to 5 euro a month on one child, if u want a job i would say more than 50 of them will have a statement that will be pointed out that they wont accept gypsys!  So tell ne if u are a mother or a father of lets say 2 kids u are getting just over 100 euro a month what will u do pay for your bins or feed your kids? They cant pay for water or electricity the ones that emigrate come back and buy houses in which they pay for everything a normal citizen would. Even if a person really wanted to be successful it is impossible in this country as we are not treated the same as we have no rights as we are blamed and are treated because of how we will but no one will ever say well hold on why are these people doing all this well because they are not treated fair and yes there are gypsys that will never change and thats because they will never forget and forgive even if they move to a different country. A lot of it also goes back to where they are not very educated as it goes back to the government as they have not provided the same for  gypsys as the normal slovakians. This is the same thing as you would have someone in Nigeria or other poor countries but in today's world if u are \textbf{racist} against a \textbf{black} person u are in deep trouble so everyone has to treat eachother right and as the years go by the new generations take this one as a normal thing and \textbf{racism} slowly but surely disappears because no one is born \textbf{racist}!\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/313 & \cellcolor{green!27}1.278 \\  \hline
  \cellcolor{green!5}\small How is she? The lady with the \textbf{bald}?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small How the heck do these idoits drop bro as much as my 20 year \textbf{old} co workers.   The bro virus spread\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small 99 percent of romanian gypsys are tramps they leave rubbish everywhere they live. Alot of them scam/rob innocent people, like \textbf{old} women. Never trust them with anything.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small This place looks \textbf{mental}. Would've never have guessed it was in Europe. Reminds me of parts of Dublin from the 80's.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Europe is \textbf{racist}, thats why these people have no help. Cool place, cool people.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Eli Jackson yes super true, everyone in Europe is super \textbf{racist} and \textbf{nobody} gets any help over here. Lol boy! could you name any place on earth were people are better off than in Europe? With in many places free heath care for all, affordable education and social benefits if without work.\normalsize   & \cellcolor{green!27}Nobody, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Ironically it's because the Romani people are \textbf{Indian} migrants.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small You know \textbf{nothing} about gypsies... Trash people. I live in the Czech republic (Country west of Slovakia) and here we have also some gypsies. You dont live with them, you are just English person to make fun of poverity of countries of Eastern Europe (I mean Russia, Ukraine, Belarus) and some part of eastern Slovakia... They are simply rubbish people. They dont work, they are stealing stuff, mugging. Shame on you.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Watch out for that snake 🐍 🐍 🐍 Harold \textbf{Bald}.... you guys are beautiful and GOD bless you both in Jesus name ✝️❤️✝️\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small you was walking there with the \textbf{bald} head and bomber jacket like a man :D :D :D\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Bald you visit interesting places and viewers like me get to know these places, you are doing great job!!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Wow some of the kids that were drinking at 3.45 looked 100  indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small These romanis are mostly \textbf{indian} migrated to europe in 1000 yrs ago\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Damn. I live in Bratislava, the capital, and watching this video feels like I live in completely different, distant and foreign country. That's \textbf{crazy}.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small My big \textbf{fat} Slovakian wedding.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small How do you want integrate these people hm? Not possible at all they are like 600 years in europe still they acting like this. And its not about \textbf{racism}. When i see gypsies work  im really glad but unfortunately its not very often. For most of them the only job is making children thats the way how to get more money from the state. Of course they children acting in the same way when they grow up... How i said never ending story. I hope so its gonna change one day\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small So \textbf{bald} is about to be the president. Interesting.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Now this is the proof that people are predisposed to their nature and culture , these gypsies truly are \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small "They came from South Asia" is a little bit too easy. They are exilants from untouchable caste in India. A system that has prevailed until today and bears \textbf{crazy} fruits - like these massrapes, heavy discrimination in schools and lynchmobs. It's basically like Apartheid or Slavery-System back then in USA. And just like the jews who have other reasons to live in Diaspora they are being discriminated heavily ever since in the western sphere. Check out your english wikipedia for "AntiziganismIn the Middle Ages"\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small \@El Nada You are spot on about the caste system however you really have no idea about them \textbf{Gypsy} origins. They were not ostracised from society  but moved on for greener pastures and migrated to EU. Their kind would go on and sing and dance and entertain the peoples. It was their profession .\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Only few \textbf{old} people in the \textbf{gypsy} settlement in Slovakia. So its same like in my country , roma people die young before the \textbf{age} 60 +\normalsize   & \cellcolor{green!5}Age, Gypsy, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - Roma & \cellcolor{green!5}6/27 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small This is my favorite video from \textbf{bald} so far!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small What is \textbf{gypsy} means did they migrate from india long time ago ?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Looks like a nice life. No work, party, dance, do drugs, socialize all day, big family, lots of friends. Why wasn't I born a \textbf{gypsy} in Lunik IX :D\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Goes off to lucik 9 proceeds to get robbed and beaten, some \textbf{bald} dude said it was ok lol\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small You and Alinchik would make a great couple. I wonder if the both of you are a thing yet. Also I like your videos man keep it up. It makes me want to visit the Chernobyl Zone as well. I especially like the videos with good \textbf{old} Koyla and Alinchik\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small They got nice free brand new houses. Who gets that? But they don't appreciate all the help they get they ruin everything, make mess, rob do drugs kids don't go to school they don't want to work. What would u do with them? U put kids in the care home once they leave they go back to lunik. People always help them . And when \textbf{nobody} want help them anymore they use the \textbf{racist} card and poor us. Does single parent get free houses? Or \textbf{elderly}? No \textbf{nobody} just \textbf{gypsy}. Even the people who been in England they had many opportunities to stay in uk work but all they did was using kids for money and house and when that stop they go back. They could save money but house but they will never. Don't feel sorry they like to live the way they do\normalsize   & \cellcolor{green!5}Elderly, Gypsy, Nobody, Racist & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}5/145 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small that's your privilege, \textbf{bald}. you're able to go and fit in everywhere without facing such threats\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Putting this one in my list of favorites. Well done Mr \textbf{Bald}.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Friendly because you're a foreigner, you know how to approach them and have a camera with you. They won't do anything because they fear the consequences. Stay safe \textbf{Bald}! Keep Alina close to you.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I like he says he is slovak in heart but doesnt act like one at all :) classic gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small As  an  \textbf{African} who has been stereotyped, I have mad respect for the  Romani/gypsies of Europe. They  do not have  anything but  smile and ensure their houses are spotless. Of  course  there are bad people everywhere and in every group but  you'd think europeans  have  passed the \textbf{age} of  tribalism and marginalizing people  for their  \textbf{ethnicity}...\normalsize   & \cellcolor{green!27}African, Age, Ethnicity & \cellcolor{green!27}Age - General, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/56 & \cellcolor{green!27}5.357 \\  \hline
  \cellcolor{green!5}\small Damn that \textbf{chick} is hot\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Ryan Bandler those kids aren't innocent, they'd rob you \textbf{blind} before stabbing you\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I would be jolly like them too if I lived of government. They get more money than people who work every day. Every \textbf{gypsy} is popping kids since she is 15 years \textbf{old}. They don't go to school and rarely make it out of the ghetto. They turn every building they move them to into another one. I give \textbf{zero} f***s what color are they but they have been living in Europe for centuries and did not assimilate until this day.\normalsize   & \cellcolor{green!5}Gypsy, Old, Zero & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}3/81 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small I love you \textbf{bald}, way to go.. This brought tears to my eyes.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Europe should be ashamed of themselves.....the discrimination of gypsys is awful....has been happening since they left india...its \textbf{crazy} it's still happening....shame on u Europe....\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Are you \textbf{crazy}? These people ar the worst criminals who get everything from state for free, but they just destroying all. For them is not a problem to disassemble wooden floor of the flat they got for free and make a fire in centre of the room.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small my grandmother was a \textbf{gypsy} from Prague God rest her soul...came to America back in day...im polish irish lithuanian and \textbf{gypsy}...100 american....\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I promise u she gets raped if she is alone w/o \textbf{bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{bald} why dn't you show us Elina house n hw she stay n her family waiting for dat volg\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small It was given to them and destroyed by no one else... just them . "poverty" most of them live in is just outcome of doing \textbf{nothing} ... Government is donating their living... without help... I can't imagine what it would be like there. Helping to most of them is so difficult ...there is so many nice \textbf{gypsy} people who can live normally. They certainly not. Big problem of our beloved Slovakia ❤🇸🇰\normalsize   & \cellcolor{green!27}Gypsy, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Dirty outside nice inside house. Very Indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small what a wash.Try to live with them for long period not a day visit you \textbf{bald}  fool\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I think the people \textbf{ho} are poor in india nowadays are more humans than the european gypsies.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Hats off \textbf{bald} just shows you shouldn't always believe what ur told looked like you had a hell of as experience\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small some people cant hear brit accents (like maybe every English? who I chatted to  persumabley they thought iw as arab or \textbf{gypsy} or greek or something)  Czech Nazis messed with me in prraha.  \textbf{gypsy} wman are hot maybe... but maybe dangerous??\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small This is a \textbf{gypsy} ghetto. In the \textbf{old} \textbf{communist} era they got nice clean new block of flats for free. And this is what they made of it. They don't pay anything. They are living on the state support. So why should not be happy and why to care about anything, right?\normalsize   & \cellcolor{green!27}Communist, Gypsy, Old & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small Best documentaries so far on youtube /thank you Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Hi \textbf{Bald}, You took my  advice as I told you about Slovakia in May. Was in Kosice last month. I've been going to Slovakia since 1998 and the problem is the government and local council in Kosice are tyring to educate the people in Lunik 9 by sending them to school. It's a problem that needs to be address.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small 2:10 stench is a typical \textbf{indian} trait lol 12:00 also typical \textbf{indian} trait lmfaoo have u smelt southall??\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Seems like they have a lot in \textbf{common} with people from India after all. They make any place they live in a dirty rat hole.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald} your over confidence is going to get you into a sticky situation someday\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I fucking hate Gypsies and this video proofs once more that those people are mostly uneducated, lazy, filthy and naughty. There is \textbf{nothing} good about them. Here in Germany we offer them a new house and give them money for free. But after a year the whole building got destroyed by them and everything around them is in a great mess with rats and cockroaches. They rob, they steal and lie, beg, there is \textbf{nothing} good about them.  They were originally settled in India, but even the Indians hated them, so thats why they had to leave and came to Europe.  During the period of the "Third Reich" those Gypsies were called as anti-social people and being brought to labour camps. Maybe thats what they deserve. Kick their lazy asses.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/130 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Commies becoming the greatest capitalists, liberals pushing for censorship, \textbf{gender} becoming a spectrum, Luník IX becoming the Slovak's top tourist destination... What is this world coming to?!\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small As an \textbf{Indian}...i should say we should take them back. Romas should come back to rajasthan...were they naturally belong to . Atleast their children should be given a free pass to study and work in India.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small It's fascinating to see how the gypsies are the same from Turkey all the way pass Romania, and into Slovakia. I also ran into them in London, telling me they're Bosnians, and by calling me Sheikh or saying the traditional greeting of Islam. But I immediately knew they were just walking around pretending to be Bosnian, assuming that we would feel sorry for fellow Muslims, and that it would be \textbf{crazy} for them to say that they're Syrians because we would immediately converse with them in Arabic, and assuming that no Arab would speak a word or two of Serbo-Croatian. Nonetheless, they don't look anything like neither Bosnians or Syrians, and whenever I uttered zdravo kako si! They were lost. I later found out from the local Londoners that most of them are gypsies from Romania, who own villas back in Romania from all the money they gather here.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/149 & \cellcolor{green!5}0.671 \\  \hline
  \cellcolor{green!27}\small BALD AND BANKRUPT, you are a torturer. All take off beauty, but you take off the most ugly, dirty, disgusting ....At least combine, but no, you are shooting all the ugliest in the country, the very bottom ...Are u ok? Brrrrrrrr\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small It's the  \textbf{nation} I squeamis (no wonder the Indians and Pakistanis are their ancestors). They are dirty people in their daily lives and also in their minds.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small his \textbf{woman} ran away with those gypsies?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small im your biggest fan \textbf{bald}..but you are wrong about calcutta. come and visit calcutta i will show you why your english chose the city as their capital.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Wow! I'm shocked by the conditions that the children are born into. It's not fair to the kids because they have no choice. Poverty sucks!!I will never complain about my life again after that.  I bet that what they survive on a year is less than what I spend on Chinese food. WTF?? Sir, you are a brave guy bringing that stunning girl of yours to such a place. She is a nice girl, don't lose her okay!!Love your content!! Best documentary real life stuff I've ever seen. I'm an \textbf{old} man now and will never get the chance to go to these amazing places. Thank you for your dedication to your journeys. Simply the best!!Peace my friends ✌🏻🇺🇸\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/122 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small I've never actually seen gypsies who look \textbf{Indian}.. They all  usually  look irish..white irish with a hint of Scottish.. .. Here some  of them actually  look  asian..And their English accent.. Bless,  the kids  speak better English then some english people. Lol\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald}. Your girlfriend is so nice and very pretty.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small This is in Slovakia? In the EU? This is something \textbf{remoaners} don't tell us all about their glorious EU!\normalsize   & \cellcolor{green!5}Remoaners & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Wow. \textbf{Bald} may be bankrupt but he goes on adventures with a beautiful \textbf{woman}! Jesus she's amazing\normalsize   & \cellcolor{green!27}Bald, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Is this country in EU? Thanks god for \textbf{BREXIT}!!!\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small AcePilot HD Simulation Thanks for \textbf{BREXIT}, when you even do not know, which countries are in EU. Do we need UK? No.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Go to \textbf{gypsy} slums in skinhead jacket from 90s. Awesome :D\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small They never did anything bad to you because you were with a \textbf{woman} and not alone, they could see you were a tourist filming for youtube. If a local Slovak went there he would get robbed and beaten up.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Gypsy disease = dick stands - I don't want to work -\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small pathetic people.  parents out there selling drugs, robbing people and ripping off peoplekids running around , don't see any of them in school.little girls looking like hoes at \textbf{age} 12,  little boys , future thugs and losers.Of course they look happy.  they have no morals, no education, and simply don't givea fuck about their surroundings.   they will just move on and destroy and pollute another country.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Which language does Alina speak here with the \textbf{gypsy}?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@LeeSmokeyday yea also.....they are the same \textbf{age} probably... so how is it creepy?that he is attracted to her lol....wtf\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Allô français canadien I think what's messed up is the fact that those children may be engaging in \textbf{sexual} affairs at a young \textbf{age}. The one kid also seemed very hostile.\normalsize   & \cellcolor{green!5}Age, Sexual & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small It's not uncommon for \textbf{black} kids to have \textbf{sexual} encounters at a young \textbf{age} that's why they catch STD's lol.\normalsize   & \cellcolor{green!27}Age, Black, Sexual & \cellcolor{green!27}Age - General, Ethnicity - Black, Gender - General & \cellcolor{green!27}3/20 & \cellcolor{green!27}15.0 \\  \hline
  \cellcolor{green!5}\small God Lunik IX is \textbf{crazy}..... something i didn't expect from Slovakia...\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I'd like to see you at Zakarpattia region (Ukraine) to look up for our gypsies .U visited most of iconic \textbf{gypsy} places , so it's a nice destination to go for it .)\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Jb Jaguar Are sure they never know such horrible slums exist on their own backyard and continent? Yet they know about it in Africa, blinding on their own locality. What an irony ! They know but actually cover it. Look at even how horrible Moldova is. My country Ghana in Africa is even better than that place yet they disregard us because we are \textbf{black} in skin. I once advised a friend never to attend any school in Romania and Ukraine else he'd regret it later and it's true.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small \@Elijah Tetteh Kudjordji Europe is a big place my friend, you can't expect people to know what goes on in every corner of the continent. Many \textbf{African} countries used to be owned by European countries and speak our languages, that is why they are reported on so much more. "My country Ghana in Africa is even better than that place"This place is one of the worst in Europe. I guess if you went to the worst areas of Ghana they would be WAY worse than this.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small \@Jb Jaguar Is Europe bigger than Africa, no. Anyway, let's not argue much about this. We speak your language , it has now become mother tongue for some of us but we still keep our indigenous languages, especially those of us who speak English. As for the French \textbf{African} colonies, the least said about them, the better. France had fooled them to the point of not being able to speak their own \textbf{African} languages again except French and they still keep on paying annual post-colonial royalties to France. So sad.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small may be can you please put some thoughts why these people don't want to integrate, as I can see they want to improve thier life, may be they don't have means to do it, as I have heard from so many that \textbf{gypsy} neighborhood is always a pain. In India too there are \textbf{gypsy} people, although most have integrated now with mainstream, what I have seen is they are not bad people, they do steal etc. because they don't have jobs, money etc. which has changed now as thier children are educated now.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small \@IndiaTV They dont want to integrate, trust me. Gypsies are the least favourite \textbf{ethnic} group in whole Europe - Bulgaria, Slovakia, Britain, Sweden, you name it - wherever they are, they cause troubles. Canada? France? UK? Never heard about that?Tho, there are thousands of gypsies who integrate without issues - they have work, often even decent education, same with their kids.Dont worry, state have many programmes for integration, finantial supports, donations, study programmes. Efficiency? Minimal.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small 8 years \textbf{old} Gypsie slut looking to get pregnant at the party lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small mr \textbf{bald} can you answer this ???having seen poverty around the world do you think poor people are happy with their lives than the rich or do they have no option but to be content with what they have and contentment brings happinessplease answer\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Adults know there is no fucking way children can escape this pathetic life and still they keep making babies non stop like rabbits. And no, biggest \textbf{gypsy} slums are in Bulgaria\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Some have made it . 12:54 Watch the fine houses on the hill . When \textbf{Bald} became Borrat lol\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small They regularly travel to all the countries in the EU on special \textbf{Gypsy}, er, "projects", and stay until they are somehow deported from those countries, for no reason whatsoever.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@xlukas this entire section tries to completely ignore an absolute ostracization of  gypsies all over the EU. It's very easy to just say that they are all at fault, they ruin everything and only to crime, but this is so absolutely ignorant and people don't know the context. You can see documentaries about it (about gypsies in Eastern Europe) and the thing is even the ones that "make it" have jobs, kids go to school, have apartments are usually still treated like shit in Eastern Europe. Sure, they might go through their life 80 of the time not having any problems, but then that 20 something happens, for example, the story one documentary followed was of a \textbf{gypsy} man being assaulted almost to death by locals, and the police, hospital, everyone just tried to get rid of him while the people who assaulted him mocked the family. There are 100000's of instances like that. Sure, there are all sort of programs to try to help and integrate to society, but most of it is just a show. Now think of it, if you can't even feel safe to not be assaulted just for existing, what do you do? You go back to "ghetto". It might not be the safest place, the hygiene is shit, education is forbidden, but at least there is commmunity that will not stab you for just existing. And so the cycle continues.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/236 & \cellcolor{green!5}0.424 \\  \hline
  \cellcolor{green!27}\small WebbyS he said he lived in derby . Most had English accents . The uk I'd had any Slovakian \textbf{gypsy} people my town has a community of them . Many have been arrested for pick pocketing\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small If you ever wonder why \textbf{Brexit} is a thing..\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small slovakia its understanding why the romanian are so \textbf{racist} on \textbf{gypsy} ;)\normalsize   & \cellcolor{green!27}Gypsy, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@MT its not just that .... they have a  similar culture with india but the \textbf{gypsy} are not going to school and they are stupid and the girls its have a boyfrend of 50 years and that girl its have  16 year  .... they are stupid ,  they steal   , they lies and they are ugly like syrian people or afghanistan people .. you look this people are from asia  immigrants    but now we have the same problem with syria and afghanistan , iran ....  on this time we need to stop them ... we need to do their country better but not to come to us and to destroy all what we have .....\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}\small Actually, biggest \textbf{gypsy} slum is in Plovdiv, Bulgaria called Stolipinovo.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Matthew SdZ Color of your skin means \textbf{nothing}, it's our actions that matter the most.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small why do they beahave like animals wiht all that trash out of the window? \textbf{nobody} will treat them better than they treat themselves.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Thanks \textbf{Bald} and Bankrupt, you opened my eyes in Europe, i always thought Europe is all beauty and rich but their is always side of every continent/country that ain't good.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small They were from india did they speak any \textbf{indian} language ??\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Edd Grs I don't think i ever saw gypsies living in apartments here in Serbia. My shit apartment costs 50 000 euros, i don't think that they could afford it, and even in \textbf{communist} era you had to pay some money to buy apartment, not possible for gypsies...\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small They should be deported to India where they belong, not to Slovakia, Romania or Bulgaria. Europe is the wrong continent for them, incompatible with their criminal \textbf{Indian} culture.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small less footage of \textbf{gypsy} kids more of alina plz\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small also they dont even respect the place THEY LIVE they fucked up everything and of course they will ask the government to help them to clean the mess they did and guess who will pay to clean this mess people whos paying taxes and working hard, but yeah in the end if you point the obvious you are the bad guy, the \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small yeah yeah ok, well for me they are still worthless cunts cause they are not working living on government subvention they are not even pay taxes, they steal, selling drugs, guns, and they dont care about laws or rules they dont want to educate and they actually taking advantage of everything and everyone, yeah you can call me \textbf{racist} or whatever you want but deep down you know i am right about it and if they want respect and talking about human rights maybe they must first learn what human rights are because they only know how to ask and demand things but they never try to earn them.And now people like that will never chance and yeah they are worthless cunts\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/122 & \cellcolor{green!5}0.82 \\  \hline
  \cellcolor{green!27}\small Yes, their culture is rural nomadic \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small My wife is a romany \textbf{gypsy}, she took a dna test and shes like quater eastern european slovak urkraine belarus etc and the rest asian and 2 Pakistani but mostly soviet genes. Seeing this vid i can see my misses looking like a native akin to the people in the vid apart from shes a clean \textbf{freak}. Its sad to see relatable people living badly. You shed so much light on foregotten people mr blad you could do with a nobel peace prize mate.\normalsize   & \cellcolor{green!5}Freak, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Tom ServoYou have to be kidding me right?She would blow me every single day and swallow my cum as a good \textbf{sex} servent!!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small It's not about \textbf{race}But i live in an area where there are a lot of gypsies and its always the same around them:Trash,crime,bad smell.Never understood it.Their piorities don't seem right.After all it's really similar to their brothers in India.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I live in Slovakia, but in the main city Bratislava. Gypsies attacked my parents when they were 20 years \textbf{old} and during the day. They tried to call for help, but \textbf{nobody} came to help, because everyone is scared of gypsies. My dad defended my mom, but the gypsies beat him up so badly he went to the hospital and had a concussion. He stayed in hospital for a long time. I don't wanna judge gypsies or I don't automatically think all of them are bad, but I don't wanna end up like my dad. And since I'm a girl i could end up even worse.\normalsize   & \cellcolor{green!27}Nobody, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/106 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Everything you showed here proves gypsies are lazy. And everybody knows that. they want to do \textbf{nothing} and just get benefits and free stuff.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Gypsies are Gypsies they are the same for centuries. This is the lowest cast among them: beggars and thief. They didn't rob you because the \textbf{elderly} told them not to, because of that other incident. They respect the \textbf{elderly}. Also you didn't show them that you are scared.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small How \textbf{gypsy} start a car ????Cigi cigi cigi Rom rom rom\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small All hats down for \textbf{Bald},  he went into that slum wearing typical jacked used by skinheads(neonacis) and all pretty resemble like one given his \textbf{bald} head. Im surprised  he  didn't vanish there lol\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Spend a month there, \textbf{Bald} with your girlfriend, like you spend a month in other places.  Let us know how it goes!!  Would be so interesting!!!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Hello there I am from this city of Kosice and I have never been in lunik 9. Everyone who lives here is afraid from this place. They were nice to you because you were foreigners. I dont wanna imagine what will happen if there was 18yrs \textbf{old} casual girl from Kosice.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Exactly..Hes a white foreigner recording them for YouTube... they're not gonna do anything \textbf{crazy} knowing that and knowing that he possibly has money to donate to people if they give him a tour and protect him\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small \@Alex Conde Only people such as \textbf{bald} and bankrupt have enough guts to go there\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Alex Conde It's neverending story- everything they got for free, they turn to pile of rumblings. Those buildings were built in eighties, they are actually ones of the  newest housing project of  socialism era.  Housing projects from seventies and sixties, where the \textbf{ethnic} Slovaks live are in good condition. You know, we didn't sell the pipes for scretch metal and we didn't burnt timbers for firewood.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Náhodou, to dievča z \textbf{L\textbf{G\textbf{BT}}} pride-u by som tam s radosťou poslal a pozeral sa na to.\normalsize   & \cellcolor{green!27}LGBT & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}3/17 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small \@Joe yeah i mean 50 of them suddenly beating you and stabbing you is \textbf{nothing} to be afraid of, apart from bleeding to death, being robbed and being given the pleasure of aids...all peachy\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small That's true mate. I'm from Plzeň, Czechia. My freinds were there just to see it in a real life, they went by the cars. As soon as they we're arriving near to the Lunik IX the gypsies were running at them like in some zombie horror movie, they gear the reverse as fast as they could and drove back. I grew up in gypsies quater here in Plzeň, and I am the biggest \textbf{racist} you could ever possibly met on the planet Earth. I wasn't born as a \textbf{racist}, I've grown to it due to the gypsies and my lifes experiences with those animals... This is the worst video I've seen from you \textbf{Bald}... Kratký Proces 4ever.\normalsize   & \cellcolor{green!27}Bald, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}3/117 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Lukáš Soki I once took a bus from Dresden to Prague, as we entered Czech Republic from Germany we went through a long tunnel and after we came out it seemed as though we'd somehow arrived in India as we drove through a \textbf{gypsy} town, everyone dark skinned and a complete mess everywhere. Would you know what town that was ?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small \@Lukáš Soki I'm from London. I looked at Dubi and Teplice on google earth and they both look too nice compared to the shithole I went through, although it was about 8 years ago. It was a total shock after being in Germany with everything clean and people typically northern European to then go through this town where it almost looked like an \textbf{Indian} slum with Indians included. Thankfully the next town we drove through was genuine Czech and back to civilisation. I love your Czech beers, would like to visit Pilsen one day.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small Hey whats up  i am from Kosice and Lunik 9 was built for police and military. Government built it for soldiers and police men to have flats there. but Shit happened and it is a \textbf{gypsy} slum. So Lunik 9 never served its purpuse.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small i cant look on this video .........thats my city and that shit is worst part in slovakia and europe.. shouldt happen that appartments was build for police officers,firefighters,and \textbf{doctors},pilots,goverment officials. it was really modern and luxury zone to live in but look who over take it and fucked it up not us ,we build it and other destroid it .......this is always like that just dont show your camera and just go there and you will see what happen ..fighting random people .stealing from oldery people ..i know that is the reallity about this and that people...i growe up in this city kosice and you try to tell me and show other people that these people and that area is normal and no dangerious shit happend ..........\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small 9:50 if that thing behind you is a montage, well played bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small My wish is that anytime any video documenting something bad (situation, living, crime, whatever) comes out, I would love filmmakers/youtubers to mention or even better to show the city, living situation and people nearby, because for example from this video it could seem that whole Slovakia lives this poorly and in bad condition and this is completely \textbf{common}, eventhrough that this is shocking even for other Slovaks to see this and close to this place people are living completely different lifes, have cars, jobs, nice houses, there are shopping malls, historical places, clean surrondings, parks, everything,... It´s not because I´m defending Slovakia or Europe there, but it gives me sense to mention this on travel channel, because next time other video can be about other countries and I don´t want to feel like ´´Oh that´s disgusting! I would be so affraid and I don´t ever want to travel to this country.´´ even when in reality the bad looking place (or whatever) was just an exception and I would be absolutely missing other beautiful and enjoyable places to visit in that country. For example close to Lunik IX there is Košice city and it´s worth the visit. I don´t want to feel like this about other countries and I would appreciate to see things I can´t see from youtube in some context and be explained to me to have an idea what the overall situation really is and how much whats showed to me is different from the rest of the country maybe, because even 5km from place like this you can find completely different life :)\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/266 & \cellcolor{green!27}0.376 \\  \hline
  \cellcolor{green!5}\small Every country has problems with homelessness, addiction, petty criminality and so on. \textbf{Ethnicity} really makes no difference because these are socioeconomic problems. Countries with less corruption, less inequality, better government services and more liberal policies are consistently the best performing countries in the world when it comes to tackling social issues. In successful countries we view everyone equally, we don't leave our neighbours to rot and act as if it's not our problem.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small Look, a \textbf{gypsy} plague\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I love how you always capture the goodness in people's hearts, now my favourte yt channel, Bless you Mr Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small dont worry every \textbf{nation} has its own problem. us here in eastern part of asia has a more dangerous problem than that. Example is north korea shooting missile at the sea and china creating many base near our \textbf{nation} and start some kind of land grabbing. tell me whats worst than having a \textbf{crazy} neighbor that is willing to throw their military might if you try to meddle on their plans.\normalsize   & \cellcolor{green!27}Crazy, Nation & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/71 & \cellcolor{green!27}4.225 \\  \hline
  \cellcolor{green!5}\small The logic of the Slovac \textbf{gypsy} was stupid (as expected). Slovaks are people with Slovak background not Northern \textbf{Indian}. The story is that even Indians didn't like their brothers the gypsies so they banished them from India. Also they are called ''\textbf{gypsy}'' cuz the Europeans thought they came from Egypt. That's how the world works. Being born in that country doesn't give you the \textbf{ethnicity} of the people who founded it, but it makes you part of its future history.\normalsize   & \cellcolor{green!5}Ethnicity, Gypsy, Indian & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small the boy that you gave the camera to and when he recorded the party and the boy that was swearing i know him iv been to lunic9 im a \textbf{gypsy} like all of them i understood what they were saying i live in england im in a hotel here im on summer holiday and the boy that was swearing he went to my school in england\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Even \textbf{gypsy} hates living in Derby.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Sexual Chocolate Robbie 😂😂😂😂😂😂\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small There's some races/ethnicities who appear to have a natural way of living that would make them poorer if measured by normal modern standards..........could be that they have a work/life balance that leans more toward the life than the work side, just as part of their culture.........we probably shouldn't expect that every \textbf{race} will always earn the exact same average income, and that if they don't, that means the system is unjust. Cuz it probly doesn't.  People are different, both individually and on average across different races.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small This little \textbf{brat} speaks good english for an slovakian/gypsy/whatever\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small These people are so damn filthy. No wonder why \textbf{NOBODY} likes them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Don't worry, \textbf{bald} man got enough charisma not to.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I don't think these kid's parents are teaching them to respect the females a lot and to not let them swear at a young age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{sex} trade of children might be another reason.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Prune Squallor apparently u don't have any knowledge of whats going on in the world...gypsies are hated among the whole world....they are not in the system ...as far as most European countries they literally don't exist in the system...do not....no government or place wants anything to do with them...they have no where else to put the garbage ....n \textbf{nobody} gives a shit about them...let that sink in for a while....u piece of shit...\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small \@Yim Yam they don't exist in a system for a reason. Because they don't work honest jobs and when they are they are beggars and \textbf{sex} workers. they trash the surroundings and bring the value of neighbourhood down. You fucking piece of shit, talking about christianity while calling others by the names. Stop using back yard as a trashbin you fucking christian. That's why paganism is Europe's only hope, so degenerates like you can be thrown off the cliff or get Buried in the bog.Gypsies are worthless for the society and system, because you have low IQ and loose morals. You can't even make your community better, only asking a handouts and complaining what you should deserve. You don't deserve even a toilet paper because you would just leave it on the grass. These gypsies in the videos have grassland, right next to the housing, grow a potato or something... No why would they do work for their own food. let's use it as a trashbin instead. Epitomy of lazyness.Fuck gypsies\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/173 & \cellcolor{green!27}0.578 \\  \hline
  \cellcolor{green!5}\small \@Apex Gemini im not a "\textbf{gyppo}" you Fcking mongaloid🤣🤣 you  cant handle the truth. You are probably  a greasy Israëli\normalsize   & \cellcolor{green!5}Gyppo & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Ever thought that it might not be as easy as just toss it in the garbage bin? Many times areas like these are avoided by locals and even worse, ignored by the government solely based on the fact that they are Roma. Issues like these often times aren't as \textbf{black} and white as you think they are.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small \@Allô français canadien well i live in Israel, and there is no trash here\textbf{weird} huh?don't start saying things unless you have proofREAL PROOF not media or from the news\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@Yim Yam Maybe you should have a look at Duisburg-Marxloh, it is a neighborhood in a german city. A \textbf{gypsy} clan hotspot. There is waste collection, but those people just throw their trash out of the 3rd or 4th floor on the street. Also almost every month there are some family clan fights. I don't wanna say that every \textbf{gypsy} is the same, but if you see the same pictures all over the world, it makes you think.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Did that 14 year \textbf{old} boy really just drink \textbf{alcohol} and say these are bad bitches? Huh.\normalsize   & \cellcolor{green!5}Old, alcohol & \cellcolor{green!5}Age - Over 65s, Behavioural Addiction - Alcohol & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Indian slums are far better than this.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small This is Roma village, and. They still have \textbf{Indian} traits. Clean house but ....\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small 1:46 \textbf{g\textbf{ay}} gypsis\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small Been around lots of \textbf{gypsy} communities in Romania, I learned I need to establish position fast to come off as if I'm familiar with them so they'd not try to sell me coke or rub me.  lots of them carry guns and knifes too so its really dangerous place.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{bald} regards where is original Alina  i have joined another Alina channel she is also making good video\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Those \textbf{gypsy} girls are fine asf\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Aaakkaashh I see u are much into this topic of recognizing \textbf{Racism} and helping marginilized people. Would you like to do some community work?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@Aaakkaashh spotted the she. Europe owes \textbf{nothing} to anyone. Sod off.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Aaakkaashh ive seen you under every comment, and so far you have gotten \textbf{zero} support, \textbf{ZERO}! Why dont you just fuck off gypsy\normalsize   & \cellcolor{green!27}Gypsy, Zero & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}3/23 & \cellcolor{green!27}13.043 \\  \hline
  \cellcolor{green!5}\small There's  a lot of untapped  talent amongst  them......the cleanliness  of the inside of their  homes speak volumes  about  what  they actually  desire. Lose the vulgarity in action speech and manner and they will leave everyone  else in the wake of their success . The same is true of our \textbf{black} population  here in the US....less so with the Hispanic  and very little amongst  working class asians.....honor is still important with the Asian  community. As a truck driver I see this every day\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small \@Oricand I am from the Czech Republic and I have never seen a blonde \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Luke Bruce , that's \textbf{weird}. Maybe it's because gypsies in Romania were forced to assimilate, hence they also mixed with the native population.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald} please come to the same place in England.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I'm from Kosice and I've never gone there. A \textbf{bald} guy in a bomber jacket going to Lunik IX. You're the best hahaha\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Fickers brought Mumbai slums with them\textbf{Dot} head fuckers\normalsize   & \cellcolor{green!27}Dot & \cellcolor{green!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small 5:42 look at that ass bro 😶😭These kids need to learn respect and to respect women, they're not \textbf{sexual} objects and this young fella has such an awful mouth, swearing here and there and saying 'you're going to get fucked up' yep this is the new generation of gangsters and wannabe's. We need to change them\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small gypsy women are hot\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small debunked: there are no problems in the world.\textbf{bald} and senile better name perhaps :D\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Bald and baldr Wish you guys were vlogging together like you used to. Dead boring with Russian women and harry bring the lonesome cow boy lol cmon fellas enough crap give us the \textbf{old} \textbf{bald} and baldr we knew and love go travel srilanka together - enough of that Russian stuff and the Russian chic haha you've had yo fun me \textbf{bald} now back to business\normalsize   & \cellcolor{green!27}Bald, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}4/66 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small I was having doubts about a hard \textbf{brexit}...errr not anymore.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Krzysztof Kapliński are you sure? Sounds a liitle bit different. \textbf{Bald} speaks russian, then why she translates for him?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Krzysztof Kapliński people say she was speaking czech, you \textbf{dumb} polak.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Gyere le a Hős utcába kopaszkám, ha elég tökös vagy! Ott nem lesz ilyen kedves a fogadtatatás. Hello \textbf{Bald}! Come to the Hős street( Kőbánya district in Budapest). That's more scarier and catasrophic place, than Lunk IX.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small So it's a \textbf{gypsy} safe haven - nice , I respect that\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Only the \textbf{blind} would see those kids as living in poverty. Those kids are not living in poverty, real poverty is social poverty. Those kids are way happier there, together with all the kids. Compare that to kids in America on drugs, depressed, on social media, and killing themselves, thats real poverty right there, open your eyes and see, don't be \textbf{blind}.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Wann be negro\normalsize   & \cellcolor{green!5}Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small careful taking that beautiful young \textbf{woman} to places like this! omg\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Isn't that Czech language what "Bald's lady" used to communicate with \textbf{Gypsy} guy? How she learnt Czech, where? :)\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small No we don't judge by the colour of your, but your BEHAVIOR. Look what do you do with your environment. \textbf{Nobody} else, even people from Africa and Middle East don't destroy it so much.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Bike DXer Hey man, I cannot agree. I speak czech and slovak as well cos those languages are so close, almost like US and UK english. Almost... Not saying exactly same. I can understand Polish, I would say most of conversation - roughly 70, but I understand almost \textbf{nothing} russian/ukrainia/belarus or bulgarian which is also slavic language. Once I listen that I am almost lost and cannot get anything.I do understand more swedish maybe more since I handle german and english, than russian  :-D Strange word, isn't it ? :)\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Why are these buildings not being repaired?They look like they are being neglected since \textbf{Communist} government stopped workingAnd what about the slums?I can definitely expect them in my country but being in Europe's rapidly developing country,they are a stark contrast.What do they do for living?\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small unemployment is nearly at a 100 there. why should tax payers fund the renovation for people that contribute absolutely \textbf{nothing}?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small These are new immigrants for liberal England, we will be glad when democratic and tolerant English people will teach us patience and tolerance. Because we are \textbf{racist}, what a terrible word, but good to hear. We start by moving them to England and there we watch the English integrate with the gypsies and culturally enrich. We like to learn and watch. But first we close the borders and armed passage with machine guns if the English want to return the gentlmeans.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small Meanwhile at \textbf{Gypsy} Headquarters......\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small No respect for Gypsies and i can careless about  \textbf{Gypsy} slum party. Dirty people in so many ways. Thumbs down.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Perhaps another word Anlishik was looking for was "congenial". No disrespect \textbf{Bald} but it would be great to hear more of Alina's opinions considering the fact that in the cultures you spend the most time in women's opinions are silenced and to quote a certain boss I once worked for (along with the rest of the staff, delivery people, etc. I learned the phrase in Albanian) "Women are less than dogs".Fantastic video, I haven't seen one yet that hasn't delighted me. Thank you!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small And the child \textbf{sex} trafficking.....\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Aa Lot I  pray to God that you transform into \textbf{Gypsy} living in Lunic 9.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@IndiaTV I'm \textbf{Indian} myself. They look like Indians, how did that hurt your butt?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@Andrew Vitiuk I absolutely agree that a poor economy and lack of development force people into these situations. We don't know why they throw their rubbish out their windows. \textbf{Common} sense would tell u that it's because of a lack of services not because they choose to live in filth. You can see that inside their homes are very clean. I'm sure it's a not of choice to have the smell outside their windows. In fact they seemed embarrassed by it.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Thanks \textbf{Bald}.  Fascinating.  Your social experiment giving the kid your camera produced some pure gold with the video of the impromptu rave.  I think Margaret Atwood noted a major obstacle in anthropology is that observing human activity changes the activity.  But you caught real, raw scenes with your leap of faith.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Alina is such a sweet \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Damn that house is better looking than mine!. I got small shitty apartment to compared to that. And there is many \textbf{gypsy} cultures, im scandinavia \textbf{gypsy} and we live totally different to these people.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Those are \textbf{gypsy} slums, not made by the natives.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I used to live next door to a Roma \textbf{Gypsy} family, nice people. Sure there are problems with \textbf{Gypsy} culture and \textbf{Gypsy} people, but there are problems with every culture and every people.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small 8:11 - Melania Trump getting palm reading from Slovakian \textbf{Gypsy} - 2004 Colorized\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small What about \textbf{Indian} homes in Mumbai\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small The \textbf{Bald} and sexy girl should make love and create good healthy white babies.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Fact... The dont want to work just uses all goverment benefits stealing robing didnt pay \textbf{nothing} throwing trash out the window\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Shut up you \textbf{racist} prick\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small It's \textbf{common} knowledge for us European who have to deal with gypsies. They have a really bad reputation across the whole continent.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small nishant rb Only a small percentage, has North \textbf{Indian} ancestors\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small And Hollywood always show \textbf{Indian} slum area only\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This should silence people who accuse \textbf{Bald} of not taking risks when he's with Alinchik\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Still can't figure out if that's the same \textbf{chick} he took to the \textbf{Indian} restaurant in Belarus?\normalsize   & \cellcolor{green!27}Chick, Indian & \cellcolor{green!27}Ethnicity - Native-American, Gender - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small because you're \textbf{fat} \textbf{murican} murderer ?\normalsize   & \cellcolor{green!5}Fat, Murican & \cellcolor{green!5}Nationality - American, Physical Identity - Physical Features & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Bald and bankrupt isn't a youtube channel, it's a state of mind.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald} is now one of the hottest guys on the planet. Beyond COOOOOOOL. XX MR B.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small The ''Myth'' about Gypsys is true.... They are in avarage not good people. If they move in next to you, i would recommend you move far away as fast as possible. We had a \textbf{Gypsy} family here making life a Real Hell for the people around them...The Government recommended that the White scared neighbors moved from the area to solve the problem!!!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small It doesn't matter if you're living in poor conditions or good conditions in Slovakia i was dirty \textbf{gypsy} all my life because the people are \textbf{racist}. I adore all those who are stereotyping my people. Kindly f \@\@\@ off ;)\normalsize   & \cellcolor{green!5}Gypsy, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small You can take a \textbf{gypsy} out of the slum.. but you can't take the slum out of a \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Countries have been working with finding solutions for decades. I hear in some parts of Spain they've managed to do some improvements. Key is education, getting the girls out there at a young \textbf{age}, before pregnancy. Easier said than down.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I've been to Bangladesh ... it's bad but there but nowhere near \textbf{gypsy} slums like this one. I didn't see 3 m mountains of trash near the buildings in Bangladesh\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Did you ever see gypsies paying for anything? Who will pick up their trash for \textbf{nothing}?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Krzysztof Kapliński Yea well, their 2 little brain cells aren't worth much, so I guess the trash is a direct result of \textbf{pigs} being inbred for generations...\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small There´s a translation mistake. At 3:34 that \textbf{woman} says "oni majú šancu" what in slovakian means "they has a chance" but you heard "nulovú šancu" what means "\textbf{zero}" or "no" chance. It is very important statement I think.\normalsize   & \cellcolor{green!5}Woman, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald} - why Calcutta ? Like any other city in India there are contrasting regions in the city. There are regions that are filthy shitholes and some ends that are beautiful and modern. I love your content but this negative image that Calcutta has been bearing is severely denigrating. I mean it has accepted vast influx of refugees from neighboring countries and states - yet it has accepted everyone as its own. I am sorry if I am getting to personal with Calcutta - it's my home, my city and I love everything about it\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Bald you should visit Bulgaria for sure\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Imagine what happens at night. thanks \textbf{bald} and bankrupt.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small alien invasion there parent took them to uk 2 get money for going school\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small 1:36 Ok I don't need to watch the rest of the vid that boy said they are bad 😂Mr \textbf{bald} should have left immediately 😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald}, if by any chance you have the entire unedited footage of this trip available then I would be happy to watch hours of it. Thank you.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small This video was beyond incredible. It goes to show that if you have the right attitude life can be wonderful no matter the circumstances maybe. The grass always looks greener on the other side. But once you reach that grass, you find out that the grass is actually laced with fire. So enjoy what you have and enjoy your health and your family. Congratulations to Mr \textbf{Bald} and his wonderful friend for making this video.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Tell it to every European \textbf{woman} defending gypsies and migrants.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@AetherAkasha if Japanese women are getting abused by Japanese men then that's their problem. If they're getting abused by uninvited foreigners then maybe they should reconsider who they allow to walk their streets - and so should every other \textbf{nation} with roaming bands of rapists.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small \@Silver Legion By japanese men lol!!! especially during rush our on the metro.. Go look into it. Its also happens to underage girls! Its quite \textbf{common} in japan they even have name for it. the japanese arnt even orignaly from japan they are the "forigners" they killed all the original people of japan called the ainus . Japanese are just a mix of chinese and something else. If you are  a citizen of that country then i dont give a fuck where u came  from , countries already sold thier people to globalization\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small \@AetherAkasha Japanese people have been in Japan since the stone \textbf{age}, yes there were wars between different local Asiatic tribes and the Japanese people are a conglomeration of those early tribes. We're talking 40,000 years ago. Yes, \textbf{sexual} harassment is bad in every form but would you like to see it reduced as much as possible?\normalsize   & \cellcolor{green!27}Age, Sexual & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small RosieJonesRules It's super risky for any \textbf{woman} to travel in an American city alone at night also.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I bet half of those \textbf{gypsy} kids aren't even virgines.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I dont understand these people, why not make something of the place clean out the garbage and plant some tree,s and make gardens with \textbf{fruit} en vegetable,s , you dont need to wait for the goverment to make it a better place lots of people there...\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small It's just not part of their traditions, genes. They have always been nomads, not stayed for any longer time in one location. One make it nice enough within one's living space, but what's on the outside is some place they will leave soon anyway. girls married and pregnant at 13-15 years, no education, generation after generation, a bad circle. If one only could take the girls out of the families before that \textbf{age}, and got them to school and college, given them some other options in life than 20 years and 4 children, it could have helped the group to a better life. but naturally, it's a inhumane thing to take children out of the families.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/116 & \cellcolor{green!27}0.862 \\  \hline
  \cellcolor{green!5}\small With all due respect Mr. \textbf{Bald}, stop calling gypsies roma, romani or romi since people, out of ignorance or ill intent, will immediately associate them with Romanians. In Romania, we have our own share of gypsies living here, yes. Unfortunately, our government is responsible for the confusions between the Romanian and Roma, romanes, romi, rom etc. words. They thought it would be a great fucking idea to call them Romi instead of tigani so they won't be discriminated, and now, us Romanians ended up being discriminated all over Europe instead, because when a \textbf{gypsy} goes from Romania to UK for example and they call themselves Roma, Romi or whatever, people from UK will say "all right, so they are Romanians", well no, they are not. They don't look like us, they don't behave like us, they think the laws exist only for fun, they refuse to get integrated in society, they avoid taxes, they refuse to send their kids to schools, they refuse to work honest jobs, they prefer making tons of kids and living off their allowance, and then we are the ones who end up being discriminated and judged by other Europeans for the shit the gypsies do in their countries.I suggest you take a trip to Romania and see for yourself, we're also a former \textbf{communist} country and there's stuff around for you to be interested in. Cheers.\normalsize   & \cellcolor{green!5}Bald, Communist, Gypsy & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}3/232 & \cellcolor{green!5}1.293 \\  \hline
  \cellcolor{green!27}\small That would require initiative and effort. That community employs neither, even for their own sake.They let it pile up until it gets really gross, then call in some bleeding heart 22 year \textbf{old} "activist journalist", parade their cutest children in front of it, get news stories done in the German media about how poorly the Slovak government treats "minorities". Then, the German government hassles the Slovak government to clean up the mess the gypsies made all on their own.It has been this way for decades, in every country in Europe. The gypsies have this whole system gamed perfectly.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small \@Movin On It seems like you are from Slovakia as you are so ashamed of answering me where you are from. If Slovaka was a such a great \textbf{nation} then why many Slovakian women work in Germany, UK and the Czech Republic? Is it the \textbf{Gypsy} fault when your economy is doing bad?before the Gypsies it was the Jews who got the blame. Since the Jewish people have a country and are powerful you dont dare to say anthing but beneth you there is a big Antisemetic way of thinking. As Gypsies are easy to blame then you blame them. How very ironic.\normalsize   & \cellcolor{green!5}Gypsy, Nation & \cellcolor{green!5}Ethnicity - Roma, Nationality - General & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small Mr.\textbf{Bald} you're a crowd puller and May be you will become a good leader in one day\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Bald... ur a lucky guy! U have a great \textbf{woman} by ur side, all ur videos are top notch. And you travel and let us see the places no tv show would ever talk about let alone film there. ***will you ever go to South America? Like Brazil or Cuba? Maybe Any Asian countries???~~~ u should come to the United States, we have some great slums here. And the ppl are super friendly. 🤭🤫🤤🤤🤤😂😂😂😂😆😆😆\normalsize   & \cellcolor{green!5}Bald, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small Holy fuck this is crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I use to live in kosice teaching English back in 2003-2004,  Lunik 9 looks Identical \textbf{nothing} has changed.  Yeah slovaks will warn you not to go there but most non slovaks I know who went in the day didn't have any problems. I have seen worst Roma encampments just outside the city that make lunik 9 look very modern.  Love the videos keep fighting the good fight.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small nice video good to know hey are from \textbf{indian} descent\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Too many English accents in that \textbf{Gypsy} slum. That's a little bit suspicious.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Bald, come to Romania, i can show you some places where the communism is still alive :D\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small only reason why they speak english so good is because their parents travel to UK for benefits and most of them dont work for years...i see some gypsies from slovakia and czechia start work because they are worried about \textbf{brexit}...\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Bald, please come visit the white squatter camps of South Africa 🇿🇦\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Not wanting to adapt \textbf{old} traditions to a changing Europe -> suffer.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I agree. We should organize an "help a \textbf{gypsy}" working holiday. Get 1000 SJWs together and tell them to go free.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small No more shows or movies for me, I just watch Tim K, Baldr and \textbf{Bald} videos now.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Ok so those people living in the slums of Brazil and India are simply poor, but in Slovakia they live in those conditions cause they are gypsies?! how about poor and neglected for being gypsies? Slovakia is one of the most \textbf{racist} countries in europe and this  sums it up\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Bald is best buds of Jeffrey Epstein.  We know they are the same blood. \textbf{Bald} is doing reconicense for kids to be kidnapped by the Jews and sold for body parts.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small British well known film director Danny Boyle needs to see this place. His "Slum Dog Millionaire - 2" will come from this place. I am sure there are people live in these places make living by sale drugs and they have gangs. Mr \textbf{Bald} is brave to go into such notorious places and show them in positive light. Thank you for posting this. Mumbai big slum people will feel better after seeing this.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small \@IndiaTV i wish we could...But in Slovakia is very strong \textbf{racism} again gypsies and politicians dont want to do anything about it...\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@IndiaTV What is "do something" with gypsies, special \textbf{indian} people, who just get things for free, destroy them and ask for other, don't like education and pass this disinterest to their kids? The only solution is to separate kids from the dull parents and educate them in special college, separated from their parents for long period. Is this "right" solution from your point of view?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small bard icus person kill animal end of word Person kill person it's \textbf{nothing} I hate ppl like u autistic logic pussy\normalsize   & \cellcolor{green!5}Nothing, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small SERIOUSLY this guy \textbf{bald} is super handsome\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Aaakkaashh Noone cares if you are brown, golden or violet here. But if you had \textbf{gypsy} neighbor, you wouldn't write such bullshit.  Their way of life is something totally different to any other \textbf{ethnic} group and has \textbf{nothing} to do with skin color.\normalsize   & \cellcolor{green!5}Ethnic, Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small \@Aaakkaashh you are complete right slovakia is a big \textbf{racist} skinheads  country i know becouse i from kosice but i moved to brussels the People are very evil dare they dont like brown People in slovakia\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@Royce people are just \textbf{racist} for no reason, lol. Maybe people don't like immigrants who coming to change their ancestors land. 300tribes in Nigeria, they don't keep themself as the same. Should we call it as a \textbf{racist}.... But ohno just a whiteman is \textbf{racist} because they don't want completely different people with different traditio s to live as their neighbours.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/61 & \cellcolor{green!5}4.918 \\  \hline
  \cellcolor{green!27}\small \@PeelingFlame You know, Romas live in a "clan" system....they have their leaders. A \textbf{gypsy} leader is called "vajda" and he is usually rich AF. :)\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small No..it's \textbf{old} news, they have been there for like 1000 years) So the skin color thing is no big deal anymore)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small In this episode, a \textbf{gypsy} fortune teller reveals that Alina is going to marry a female president!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small This is not slum go and look \textbf{Indian} slum ..\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{chick} is super cute. Lunik 9? Total shithole. Those people are disgusting.But again... the bird is a cutie.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Bald please Visit in Philippines and Documentary\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small After looking at the trash I'm pretty sure these guys are \textbf{Indian} in origin.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Bald you are the man. New to your channel and 2nd video I've seen. Love the content. Subbed!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small my most favorite youtuber in my homeland with my most favorite \textbf{ethnicity} <3\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Mostly \textbf{Gypsy} from Haryana, Punjab and Rajasthan\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Amazing video \textbf{bald}!! This one really got to me! Just fantastic\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Fucking \textbf{Indian} desi \textbf{race} every where..😂😂\normalsize   & \cellcolor{green!5}Indian, Race & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small The amount of \textbf{racist} ignorant males commenting on this video is alarming.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I am a \textbf{gypsy} but these people ruin our reputation\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small human nature is that when you own something, you want to take care of it and not the \textbf{common} areas. first \textbf{nation} reserves in canada are often shit because they don't own their houses or yards. if individuals can not afford to pay the fee for garbage pickup and see others dumping, then they will dump too. it has to go somewhere and if there are no community bins then it will get messy fast. people who are poor do not care about keeping things clean, they have more important day to day matters.this video was also amazing to see how quickly those children grow up and become \textbf{promiscuous}. birth control needs to be provided for free or subsidized for the poor with mobile clinics for the teenagers who can not get to town on their own.\normalsize   & \cellcolor{green!27}Common, Nation, Promiscuous & \cellcolor{green!27}Gender - Female sexuality, Nationality - General, Social Class - Working class & \cellcolor{green!27}3/138 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small These lot prob moved back when they heard about \textbf{brexit}.. Or deported lol\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small 8:03 - Mr. \textbf{Bald} for president then! xD\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Señor \textbf{Bald} You have completely outdone yourself this is Incredible. What an unbelievable place this is, and you have taken us there. Riveting from start to finish.  Blessings.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Is it \textbf{weird} I want to go there\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This was one of my my favorite videos of yours keep up the work \textbf{bald} you're really doing big things\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small hey \textbf{bald} if you at slovakia come to my house in piestany spa city,let me know i gave you my adress\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Copy, I've never heard anyone besides an incel refer to women as ‘females'. But the 'males are the creators and females are the passengers..' line really makes me have \textbf{zero} doubt:)\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small \@Whatevenhappenshere it always seemed \textbf{weird} to me, even being a non native english. What the fuck is a female? Isnt that what they use to describe animals in the wild? "The female is hunting for the cubs"\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@Little Ears Does the word male seem \textbf{weird} to you too or is it just your political indoctrinations speaking to you. When the subject being discussed is already known to be humans, male and female correctly describes the whole of the \textbf{gender}, whereas men and women describe only adult humans. You people are too retarded.\normalsize   & \cellcolor{green!5}Gender, Weird & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small \@Little Ears that's the stupidest shit I've ever seen on a YouTube comment. Why do u not question the word male but only question the word female? Obviously equality in Ur eyes is men deserve \textbf{nothing} and women deserve everything and need to be empowered by being treated better than men.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small PowerTuber 3.0 unless you are super \textbf{fat} lady noone would want to tap.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small It's funny to see a feminist calling people who she disagrees with an "incel". Feminism makes you an incel, who would like to have any kind of relationship with a \textbf{chubby} unshaven femnazi Alf? You're just a lazy creature, feminism is just an excuse to keep acting this way.\normalsize   & \cellcolor{green!27}Chubby & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small I totally disagree.  \textbf{Woman} as a right of passage,  upon puberty should have to go to these places and those who make it out,  well they are the ones which all men should desire to marry.  It shoild definitely be a right of passage IMO..\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Then what's stopping you from converting to Islam. Your views seem to have a lot in \textbf{common} with said religion.But to be honest, in my opinion. i would shank you or shoot you on sight and sit quarter of my life in prison with a grin knowing that there's 1 less one of you "naturalists"  out in this world. Even the Romans didn't had such extremist and ~incelic- views as yours against women. Whatever floats your boat, Best of luck to your future relationship my manly man.painting all of women because of a few rotten apples that unironically share the same views as yours but of the opposite \textbf{gender}, makes you really seem like aloof to what's actually happening in that field(which none cares)\normalsize   & \cellcolor{green!27}Common, Gender & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/126 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small \@ZaxWaffles I am more inline the what the Christian western world knew to be true about genders prior to 1965, before the leftist neo-Marxist psychological transformation of the west. I go strictly by hard statistical voting data by \textbf{gender} and by the differences in brain structure by \textbf{gender} proven by science and obvious to anyone with a brain living in the real world.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small \@Pepe Baller my aunt for her BS research trekked all over Middle East and rest of Asia. White \textbf{woman}, alone, in her 20's and she did it numerous times (her all treks combined added up to years now). Guess what, absolutely \textbf{nothing} happened and she had a great experience and met many friendly people. You probably have higher chance to get raped in US college.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small In Slovakia we have free schools. They have opportunity live better life. These horrible apartments was in perfect condition and \textbf{gypsy} people ruined them. And they didn't pay anything.Goverment pay them something like support every month and that money use for alkohol, drugs. Usually when I meet them in city they are making problems.Maybe month ago I was on trip in the nature. When group of young boys from Luník saw me (i am a girl) thes start sreaming at me and showing their penis...I know many \textbf{gypsy} people and they well educated, having normal  jobs. \textbf{Gypsy} from Luník 9 living poor life because they want to.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}3/110 & \cellcolor{green!5}2.727 \\  \hline
  \cellcolor{green!27}\small \@\textbf{bald} and bankrupt the \textbf{woman} said "Oni mají šanci" meaning "They have a chance" actually, but her men is not so optimistic haha\normalsize   & \cellcolor{green!27}Bald, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small India is a diverse country. To understand and imagine the \textbf{Indian} Union, you need to comare it with the European Union by area and culture diversity in every 500km. Every state have different language \& culture. We have more than 100s of communities living here. Gypsies are one of them. Some of them migrated to Europe centuries ago. Some are still here in India. They live in the same condition just like they live in Europe. Even if you give them 1 million \$, they would stay in slum. Only few have merged into mainstream. They belong to Rajasthan and Sindh of Pakistan. That's why Gypsies are called Sinti (Derived from Sindhi)\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small Bubbles I agree with you bubbles but I hope \textbf{bald} doesn't get too big because fame might change him or 'Netflix' would change his natural way of documenting life. I prefer him the way he is, honest and humble\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small East European people \& we \textbf{Indian} have    alot of similarities in looks.Respect to all of them living there\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Shutka is the biggest \textbf{Gypsy} slum in Europe.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hi \textbf{Bald}. Just a FYI… Your concept is being heavily plagiarised on Danish national TV. I just tried to link to the show but it doesn't work – something to do with Youtube comment policies, perhaps? I've never commented on anything on Youtube before, so I don't know. But this would be a prime case of imitation being sincerest form of flattery. Your channel really is one of the very best on Youtube, and I'm delighted to see that you're approaching a million subscribers. I have been travelling to many obscure parts of Europe myself in the past few years, and I have also somewhere at the back of my mind considered ripping off your concept, but being painfully aware that I could never make it anywhere near as good as yours, that will never happen. Keep up the good work, mate. Inspirational stuff.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/144 & \cellcolor{green!5}0.694 \\  \hline
  \cellcolor{green!27}\small Congratulations on your first comment. So they're not using his footage but imitating his style. As you say mimicking \textbf{Bald} can only do him good.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small So now this a love bird video of \textbf{bald} and that girl , never expected such a rapid decline ... total waste now\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Bruh you need to get back to your true love HAROLD BLDR! Miss your guys colabs ive been just watching only your \textbf{old} colab vids traveling together! Brunettes a hottie though i do understand but BACK TO BIZNESS MR \textbf{BALD}!!!! LOL. Meet Harold some where cool and dangerous! Live the movie "Beaches" or something!!\normalsize   & \cellcolor{green!27}Bald, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Slavic + Indo-Aryan = Gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Gypsies are not slavic they are indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The \textbf{communist} Czechoslovakian government built Lunik 9 but as communism collapsed and Slovakia broke off from the Czech Republic and the economic problems of that those 2 big changes would have impacted the Roma people in Slovakia.Question is what was this place like in the 70's and 80's before the \textbf{communist} collapse?\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small the \textbf{woman} said they have a chance, but the man said their chance is 0 and that they have no chance\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small what is going on with the hardcore \textbf{racism} here in the comments?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small 2:39  no ur not slav ur fuckin gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Oh Fuc* you feel sorry for them??? So now imagine they got the houses new and nice!!! THEY DESTROY THE HOUSES and they make the mess so it looks like after war there... \textbf{Nobody} come there and ruin their nice life, they ruin their life by themself!!!  YOU FEEL SORRY FOR THE KIDS????? THEIR PARRENTS LET THEM LIVE LIKE THIS!! Im your big fan but this is too much i was think you not gone eat everything what they throw you for story...\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small They survive just because they got money for the kids did you see anyone work there??????? WORK? They don't even know what it means.... and you think people from normal city lied to you about them???? Yea make GOOD PEOPLE FROM CITY WHO WORK EVERYDAY LOOK LIKE LIARS??!!! "OH THOSE \textbf{GYPSY} ARE SO NICE"...\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small You don't need to go to Lunik 9 to see people in slums. Just go to Portslade or parts of Brighton. Poor people are generally nice. Only rich ones are greedy and possesive, and are miserable. Great vid, and enjoyed the interactions with the \textbf{gypsy} community. Thanks\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small dude you \textbf{crazy} and so lucky they not robed you :D or worst...\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Does this \textbf{chick} who is from Belarus speak Slovak? because it is not russian that she is speaking to that gypsy\normalsize   & \cellcolor{green!5}Chick, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small why \textbf{zero} chance to for kids to escape lunik 9? I mean big percentage of them invade foreign countries like England, so I would say at very least 10 chance\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{bald} darling you've made it big King of youtube pewdpie says youre his fav\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Honestly I'd Nuke the area. Fucking \textbf{gypsy} cause more havoc than any other people\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small pewdiepie watches \textbf{bald} and bankrupt he said it in one of the podcasts he was on\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small those kids by 12 are no longer virgins, unbeliavable, awesome job there mr \textbf{bald}, and btw, this community looks so vibrant!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small There are all kind (races) of gypsies there. Gypsies are freeloaders, and they can be of any \textbf{race} (brown, white or mixed as seen in video)\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small this what happens when \textbf{gypsy} move in turn things into a shithole fucking hate \textbf{gypsy}'s\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small How does it work when everyone is a \textbf{gypsy}?  Who do they prey on?  Each other?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small If \textbf{Bald} has taught me anything, it is that I live in an expensive place(Bay Area) for a reason😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I'm a Finnish \textbf{gypsy} and most of us dont do illegal stuff or stealing\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Hi, Great to see you in Slovakia! I think you found a most controversial and interesting point in Slovakia. Good job with this video. There are dozens of gypsies slums around Slovakia which looks much worse that this.The biggest problem with the gypsies is that they like this way of life, they like to get social aid for free and they rather live in such condition than working hard and have something better. It is their mentality, which is hard to change. And the worst is when the \textbf{gypsy} people are living together in bigger  settlements.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald} I think you show us about \textbf{old} Soviet building and telling us about the history is so amazing. I find the \textbf{old} Soviet crown molding and the decoration is mind blowing, oh and I'm in love with Alincik, can you tell her to add me on Facebook: Mario Alvz\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/51 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Gypsies aren't treated badly TBH. It's the other way around. You see, they're given a social welfare based on how many children they have (so, naturally, they make a lot of children just to have more money), they're also given fresh houses (Slovaks are really outraged about this) and they turn them into shitholes. They have really poor manners, yelling, stealing, giving smokes and \textbf{alcohol} to the minors... No wonder normal polite Slovaks don't like them. The worst part is when you say something bad about them, their lifestyle or anything, you're automatically branded a \textbf{racist} (even when you're pointing out something which has \textbf{nothing} to do with skin color). Not too long ago we had a situation when one \textbf{gypsy} (he was incarcerated not too long prior to the incident) killed a man in front of a pub... just like that out of nowhere. He killed a normal, hardworking man without any reason. That's why gypsies have a bad reputation. I also have an all around bad experience with gypsies and I don't like them in general but that doesn't mean I mind a polite, hardworking \textbf{gypsy} who's trying to prove that not all of them are like this.\normalsize   & \cellcolor{green!27}Gypsy, Nothing, Racist, alcohol & \cellcolor{green!27}Age - Youngsters, Behavioural Addiction - Alcohol, Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}5/200 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Crazy but cool\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Who's the smoking hot babe with you? Killer green eyes, lovely \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Aaakkaashh Give me ANY evidence of slaughter AFTER WW2  and im gonna change my mind to so called 'facts' (blatant lies)It is true that sometimes they are marginalized , but \textbf{nobody} is killing them\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Aaakkaashh Also Greeks in India were assimilated a long time ago. There's no distinctive Greek identity in \textbf{Indian} Subcontinent.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Good Sir, or M'me. Been to Mexico, seen the Romani community in Jalisco, and it's true they get along with the Mexicans much better, and they' re accepted much more while still largely keeping to themselves in their communities (historical reasons.) The issue between Romani communities and the majority in post Eastern Bloc countries stems mainly in how the governments dealt with them in general. It is a very complex issue, which points at faults on both sides. However, the greatest deal of trouble was, and still is, caused by the people in power. Thanks to the people in power the antagonism between the two prevails, it even grows stronger, sadly. Most Romani see the gadzhos almost as an impersonification of all evil, someone not to trust, not to respect. Then, some, or many, depends on the place, too, they feel entitled to show that distrust and disrespect in all-out way. Among 'gadzhos', there's belief, often taken as an ultimate truth, that Gypsies only want to be 'parasites' on the system, steal, avoid work, take any benefits their home country can offer, without any chance for a change. And they treat them accordingly.  Many of the Romani \textbf{ethnicity} in these countries are engaged in all kinds of criminal activities, which can be also highly organized - targeted against those gadzhos.. most often, they do not commit these crimes against each other.. Oh, the hate. Also, more often than not, Romani kids ignore the school, as their parents seem to not care at all. Other side of the coin then shows that these kids are outsiders the moment they begin attending a school. There is a stigma coming along with their origins. Are you a Romani kid who so much wants to show that you're not who they think you are? You want to get along with the rest, have friends, etc.? Tough luck. I remember a tiny Romani kid crying when on a walk with his kindergarten group, as only a teacher was willing to hold his hand, and even she seemed somewhat uncomfortable doing so. Heard kids talking about dirty Gypsies. (Yes, you have these families that do not care much about hygiene, and it's the part of the \textbf{Gypsy} stigma, as if simply all of them were filthy.) Another thing - a public belief that Gypsies, in general, are \textbf{dumb}, uneducated, and if they can land a job, there's a risk they'd steal there, or make trouble. And that they actually do not want to work, they' re lazy, and they enjoy social benefits offered by the state. As a result, it can be extremely hard for an adult Romani to find a job. There's a plenty of Romani people who are skilled, skillful, even really educated, but they are unlikely to land a job where there is non-Romani competition. And guess what, it hints about where that goes. Reliance to social support, if possible. If not, they can opt to leave for other countries,(which, however is not always an option to them), or join some others who are crime-positive. I managed to know these Romani people in Slovakia, and abroad. I quickly earned their respect as they got to know me, and gave me the chance to see they are people like all of us.I had a chance to travell, visit some countries around the world, and get to know the people there. We're all the people, are the same after all. The cultural differences are always a painting on the top after all; underneath, we're all the same. But, I also acknowledge that I learned to understand that only thanks to getting to know these people. To open myself to knowledge, embrace it. It is not that everyone achieve this. Anyways, there are people with power to influence us, who could unite the people if they only had the will to do it. Instead, they keep dividing us, as it serves their own agendas.\normalsize   & \cellcolor{green!5}Dumb, Ethnicity, Gypsy & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/659 & \cellcolor{green!5}0.455 \\  \hline
  \cellcolor{green!27}\small Why you film \textbf{gypsy}? Those people don t work , they don t do anything all day .. it s a shame for me as a romanian to be compared with a \textbf{gypsy} . The same the slovakians think ... a shame for their country as it is a shame for my country ..\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Bald, I discovered your channel a week ago and have just finished watching all of your videos, wow man what an amazing adventure and some amazing people, that I've definitely felt a part of. Thank you for the videos, look forward to many more 👊\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small I Created An Account For This Putin doesn't ask to upload more videos, Putin invades UK, makes queen his bitch and tells her to order \textbf{bald} to upload more\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small tons of gypsies came to latin america during the colonial times, since gypsies were always a large minority group in spain. many of those "latinos" are \textbf{ethnic} gypsies.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Well mr \textbf{Bald}, finally i see someone calling them by their name. Idk from where they came with "romani" but it's spelled wrong info. It's Rromi the more polite way to call them.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Has there been a fire in every apartment or what? All the balconies are charred black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Wow i didn't realise places like this existed in europe, thanks for enlightening me Mr \textbf{bald} man.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I think you are doing some really top documentary making \textbf{Bald} - giving us the reality of what is out there without filters - better than anything on TV.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Communism DOES work! \@Mr \textbf{Bald}..... You still use the Sony fdr x3000 to film these videos eh?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Bald, you made me wanna buy a flat in Lunik 9 now.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Bald gets on with everyone. Literally everyone\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Evgenia Stankevich Good to see a Strong and Independent \textbf{woman} like you in this chat. Can recommend you visit this place too:)\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@Evgenia Stankevich found the \textbf{old} ugly \textbf{hag}.\normalsize   & \cellcolor{green!27}Hag, Old & \cellcolor{green!27}Age - Over 65s, Gender - Female age and physical appearance & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small \@John This is exactly true, especially since \textbf{Bald} has used that exact term on camera on numerous occasions and been greeted with \textbf{nothing} but a smile from Alina. Many ex USSR countries are like this, a woman's worth is only in her sexiness, after she isn't sexually attractive anymore she's almost worthless. That's why it's a compliment to her. The same goes for many other countries, like the USA for example, where being called 'hot' is often regarded as a compliment. In civilized countries you'd never get a positive response if saying that to a stranger.\normalsize   & \cellcolor{green!5}Bald, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}2/96 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Nick GurrI'll let you figure out that on your own through life experience.As for Sweden, while they certainly have plenty of problems with their muddies, the reason the figure is so high is that Swedish women actually report the crime. Do you understand the sociological reasons why in Sweden a \textbf{woman} reports such a crime and in many other countries, women simply don't generally do it?You are smarter now than you were six hours ago, you're welcome.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small NutLover360You are just a \textbf{dumb} kid.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Pepe Baller baby I leave in \textbf{gypsy} area in Belarus guess I know more than you\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Evgenia Stankevich what it proves is how fragile the female ego is and how we've come so far that we've actually began regressing. You're so obsessed with the quest to be treated "equally" that you've forgotten about the natural differences between the sexes and how to embrace them. \textbf{Nobody} here was harassing or using defamatory language. You're just easily triggered and pointlessly defending a lady who obviously doesn't want or need your defense. She seems comfortable with the image she projects. I guess the question really is, why are you so unconfident that you need to be a keyboard warrior?\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small John why are you sure about her feelings? Whether she is comfortable or not? The whole point of my message was about how primitive and narrow minded was you. Not about the girl in the video. And why when men have \textbf{nothing} to say they bring up natural differences?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Young Coffee he is a \textbf{gypsy} he is not slovakian\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Thomas Bramley \textbf{Immigrant} groups like theirs who have no respect for the local culture or values and show no gratitude for their accommodation in a foreign country are responsible for the conditions in the worst neighbourhoods in British cities. Though really it's our reckless government's immigration policy that is to blame.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small I grow up surrounded by Gypsies,  I  can spot them from distance. Doesn't matter where they are from.  Mentality is same everywhere. Ofcourse there is always exceptions. It's amazing how people who are not connected neither language or countries,  but they have same mentality ,same mysterious history, you can't find such a thing as \textbf{Gypsy} language in translator but they all speak their own Language. They are different but  similar same time.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small I love Mr. \textbf{Bald} GF.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Gypsies everywhere they are make a good building to the worst slum thats why i dont l like em! Nd all you politic correct motherfuckers let em live next to you i swear to good u became in less than 3 months a Rassist they dont care about hygiene the only thing owned and support by Gypsies are \textbf{R\textbf{ed}} Star Belgrade fans even tho i dont like em but pfc fans grobari a 1000× better then them\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small oh, fuck off. literally every person in this video is worth more than you are, and they can wash the filth off the skin but you can't scrub it from the inside of your \textbf{black}, shriveled, malnourished fucking heart\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Been hooked on your videos for the last couple of days and I feel the need to thank you like many others have. Its incredibly rewarding watching through your experiences. Also very relaxing and informative. Its really beautiful! I will myself most likely never visit India or any eastern europe country as I'm to afraid to travel alone and I don't make many friends to travel with anymore, so this is so very rewarding for me. Thank you \textbf{bald} \& bankrupt for letting me experience some of the beauty :) Hope you known how good you are for your viewers.Really wanted to ask for subtitles for some of the times during the \textbf{indian} trips but I just realised that you've started to add some. so I can't really complain about anything :'(  Keep it like it is!\normalsize   & \cellcolor{green!5}Bald, Indian & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!5}2/138 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Some Won \textbf{Immigrant} groups like theirs are responsible for the shit conditions in certain neighbourhoods.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Derby you mong\normalsize   & \cellcolor{green!5}Mong & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald}, your kinda hot;)\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I live in Slovakia and I am really surprised (not really) of GB natives comments about gypsies. Leftist PC propaganda in our media says that all our gypsies in GB live as normal citizens  and locals love them.  All it took for them was to leave bad bad \textbf{racist} Slovakia (Romania,Bulgaria,Czechia,...). They were not able to accomplish that here for hundreds of years under different regimes and with different approaches.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Jan Filo Haha what a joke. They replicate shitty conditions here in the the U.K. It is their natural way of living. Only the violence and conflict is even worse when you have multiple \textbf{immigrant} groups with regressive mindsets like Somalis all mingling with them.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small You see inside their Home all stolen items.....and this Goofball Balder \& his 16 year \textbf{old} girlfriend idolize them.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small so those were the slums? I'm not playing down their situation, maybe i can't find the right words, but they seem to be doing quite alright with what they have compared to other places in the world, electricity in the middle of the bush away from the apartment blocks, a nice wedding where everyone is still able to dress nice, and both adults and children seem to be fed well. I'm quite surprised. The one guy that seems to speak honestly and seems to want to have a better life is the one that was asking to be judged based on his heart.Thanks \textbf{bald} for sharing videos like this, it really is an eye opener to the different cultures and view points from places that many of us don't get to see, your videos are the very definition of a window to the outside world\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/146 & \cellcolor{green!27}0.685 \\  \hline
  \cellcolor{green!5}\small They are basically \textbf{Indian} brownies\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small 30 Years ago there was an idea to mixed whites and gypsies together on this area. Buildings were built specially for this reason. It was half to halt as about ethnics... Expectances were so big, but... Whites started to leave this area from time to time. They could not to hold out mentality of gypsies. They lost all price money, had to overhand their own flats to gypsies. \textbf{Nobody} but gypsies wanted to move there. Gypsies from Lunik IX do not pay for \textbf{nothing} - water, electricity, garbage, suburban traffic ... 5 Years ago, Kosice town cleaned area from waste material. Around 30 trucks had to be loaded and transported material on dumping site. Area shown in video, cowered by garbage, was completely clean 5 years ago. Gypsies cannot take care about themselves. Pity...\normalsize   & \cellcolor{green!27}Nobody, Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/136 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Idk, they really don't look \textbf{Indian} to me, rather South American\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small XD idk if i have to laugh cause im \textbf{gypsy} too but thats funny\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small kahan bund mara rahe \textbf{ho} desi daru shodke\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Not the biggest at all! You have to come to Bulgaria, in Plovdiv there is the biggest \textbf{gypsy} slum in Europe,  there are 50 000 people compared to those 10 000 in Slovakia. Check Stolipinovo in google - its epic!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Been following the \textbf{bald} for awhile.  This is some deep insight that no one is sharing.Thank you.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Ah \textbf{Indian} culture really is like a leech taking in everything around them destroying it.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small No slovak will ever live there, you would get robbed, bullied, raped, beaten just because you are the odd one out, very sad. I hope they do something about the littering that shit is very unhealthy, and i hope these kids would go to school insted of drinking \textbf{alcohol} and doing \textbf{nothing} all day, in the this time you need an education if you want to be someone or something.\normalsize   & \cellcolor{green!5}Nothing, alcohol & \cellcolor{green!5}Age - Youngsters, Behavioural Addiction - Alcohol & \cellcolor{green!5}2/70 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small I'm glad i came across this video. It show me that the world is much bigger than \textbf{black} and white when it comes to racial discrimination. And these individuals are being discriminated by the governments they are under. And it is sad.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small I DUNNO...one thing if BB travels to dodgy areas solo/with mate where locals WARNED not to go but with ALINA?...NO.It's puttin her into potential bad situation they may not be able to talk themselves out of. Look....I'm not puttin down ANY specific culture/country, i went to Slovakia \& Hungry (someday  Romania too) and loved it. I also live in U.S. and there are parts of MY city I wouldn't walk around solo at ANY time of the day ..let alone WITH an attractive \textbf{woman} and obvious expensive electronic equipment. IF I were SOLO a would be aggressor would be less likely to approach ...ESPECIALLY if I had \textbf{nothing} of interest...but a pretty Russian gal? ...that draws attention like White On Rice! ....RECENTLY these 2 female vloggers dissapeared  beneath the mountains in Morocco (I think it was)...the men who murdered them were found 2 weeks later. I KNOW Slovakia and Belarus are NOT Morocco but "Tragedy is more \textbf{common} in places of  Disparity".Hate to sound "Debbie Downerish" but I KNOW how situations  can turn bad rapidly... more so when vodka is the \textbf{common} beverage :/\normalsize   & \cellcolor{green!5}Common, Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General, Social Class - Working class & \cellcolor{green!5}4/188 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small bald and bankrupt m it's not much but it is a start towards a better life just saying, these people chose to live like this not because there is lack of opportunities.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small OMFG . Another bitish vlogger Pro-\textbf{Brexit} , went to europe to specifically look for the poorest places and present that like - This is the country and this is why we voted for \textbf{brexit} - kind of shit . I'm romanian from Transylvania and a british reporter propagandist came to my country a couple of years ago and he went in some village on the south of the country and it was not actuall in the village cause it was outside of the village where a \textbf{gypsy} familly were living on the streets and he presented that familly like - '' Omg dear british brothers , look this is romania and they will come into our precios kingdom - and everybody knows that romanians are different than gypsies and gypsyes stays outside on the streets and some of them who choose to go to work and go to school they stay in the city .. So to my slovakian brother , please dont get upset because of this british propaganda , its just how they do everything .\normalsize   & \cellcolor{green!5}Brexit, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Nationality - European or anti-Europeans & \cellcolor{green!5}2/178 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small President \textbf{Bald} lol\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Sad, the face of a low IQ population but it needs to be seen. I doubt those are real Gypsies \textbf{Bald}, they might be Migrants from the lower USSR. Too dark of complexion. Real Gypsies look whiter. They might even be Palastinian migrants.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small No lol. They are Gypsies. Not one Soviet \textbf{ethnicity} is darker than the Gypsies.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Crazy, im from south east medway, A lot of Slovakian migrated from there to here when i was about 7 years \textbf{old} about 11 years ago, amazing to finally see where they r from\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Lucky you \textbf{Bald}, You didn't get raped.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Man how could you judge a whole country just by visiting its slums.! Why would you name Bangladesh or even India? You're a super judgemental delusional guy. Go visit Bangladesh, yes it does have some slums, but go to urban areas and talk to locals and see how educated they are and how hospitable they are. Yah do go to villages as well and see how naturally beautiful they are. Yes I am judging you now, you \textbf{bald} thick head dumbass!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small apparenty she took of with another guy and left bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Shit man you are goodly wasted halfway there. Keep it up \textbf{bald} <3\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Thanks for the insightful video! I myself am half British and half Slovak. I'm saddened by the level of \textbf{racism} in Slovakia, but I understand that gypsies are seen polluting land as well as partying and doing drugs/alcohol which fits into the stereotype.There's no easy solution, as gypsies are discriminated against (which is wrong) but many don't seem to have a will to change. I hope the \textbf{gypsy} majority will start living sustainably and sensibly so the minority who DO want equality can defy stereotypes and earn trust! :))\normalsize   & \cellcolor{green!27}Gypsy, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/90 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small this was one of your best videos, \textbf{Bald}.  Loved when you gave the kid the camera for a bit... great!  I really look forward to your next adventure!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Maybe i'm wrong but i heard that there was a plan to move gypsies from the city center to such districts and put them between high-ranked army officials, police and their families to lower the crime rate. It was very \textbf{common} in Soviet era in countries that were members of Warsaw Pact. There are severel disctricts in Polish major cities (such as Cracow and Warsaw) when they plan to re-settle criminals and put them between police officers and they families. In all cases - these "experiments" failed. Only criminals and poor families were moved and flats planned for officials were sold or were for rent. This resulted in almost no-go zones and such places are dangerous till today. Lunix X is definitely the worst case.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/125 & \cellcolor{green!27}0.8 \\  \hline
  \cellcolor{green!5}\small So hear me out. Pewdiepie said \textbf{Bald} is his favourite Youtuber currently, and as I have been watching \textbf{bald} for quite some time now I have had the pleasure of being in the top comments a few times. So it means Pewds saw my comments and it is a good chance he thinks I am funny cause you guys did. So yeah, Pewdiepie thinks I'm funny. Thank you.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Politicians want these scum to come to Britain 🇬🇧 make \textbf{brexit} happen fast.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Vanman1965 \textbf{Brexit} won't slow non-EU migration which is generally even worse for this country.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald}, you are one of a brave man :) great to see such a video about Lunik IX.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small MORE \textbf{Gypsy} videos!!!! Please!!!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small They are mixed, not a single \textbf{ethnicity}.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Please go to kosovo also to the gypsy\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Bald i love u, but u need to let the girl go if u want this channel to be succesfull\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small 🍎🍎🍎🍷🍷🍷👹👹👹   ΙY, UNANSWERED📯📯📯🥛🥛🥛🐷🐷🐷The 'Devĕt Brand' is a very \textbf{old} mark:And if Jiří Langer's no longer in the dark, The struggle of those who are buried with forkIs announced — alas, so far — in the mereSquealing of pork.Find his book of interest — or better, walk on by?You'll not hear Lady WindimereFanning ancient superstitions!Easy come now, the causes and concisionsSighing in 'the y'⌚️⌚️⌚️🍴🍴🍴💣💣💣⛩⛩⛩⛩⛩⛩⛩⛩⛩\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Poor \textbf{gypsy} people are harassed extremely since centuries because of their look, language, life style were different. They weren't Christians or Muslims and they didn't convert or change their life style. They couldn't live even city. I noticed they are forced to live outside of town or city. They don't get basic things like electricity, water, cleaning , schools etc... People says they're involved in crimes. What you expect than if you behave like that? They have to survive. They had no choice other than crimes to earn some money. Hates of to them even after hundreds of years of harrassment they survived and living lively. Hope Europ and middle East will be nice to them and would do to end suffering of gypsies. Best of luck to \textbf{gypsy} people. Love from India.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/133 & \cellcolor{green!27}1.504 \\  \hline
  \cellcolor{green!5}\small Wtf dont go to this people \textbf{Crazy} idiot\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Still better than \textbf{Indian} slum\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Hey \textbf{bald} mate please go to romania it is a beautiful contry but it has been robed by the gouvernment a lot in the last 29 years...thanx\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Slum made by brown motherfuckers from india they a truly a shit eating \textbf{nation}. And yes brown gipsies are related to curry chaps\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Gypsy s live filthy..They are nasty..\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Aaakkaashh didn't they say the government build their housing FOR FREE? Are you assuming they're not on government assistance? Did I say anything about them being brown? The reason they are "turning white" is because some prostitute their wives, daughters, sisters (no all - NOT ALL . . .  NOT ALL!!!) They are a public menace and a burden on tax payers who owe them \textbf{NOTHING}. You did make a great point tho, they've been in Europe for hundreds of years and they refuse to assimilate and there's no reason to think that's going to change any time soon. That's something we should keep in mind when it comes to the current batch of migrants, are they still gonna be demanding free housing and assistance in hundreds of years? Will people like you still be defending them in 2319?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/139 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}\small \@Aaakkaashh someone's gonna turn my country to ashes? Sorry, you're speaking gibberish like some kind of \textbf{gypsy}.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small The guys an idiot. There's not an ounce of Slovak in him, he's \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Italian \textbf{gypsy} are the worst\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Balkan \textbf{gypsy} are the worst\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small italian \textbf{gypsy} dont exist they are either from romania\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald} for President! :'D\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Parents and elders need to put this community in check. They are all bums. This is what you get without enlightenment living in ignorance. All fun in games in edits, but stay a month it will be different. The ghettos I been in in USA are more violent than this and I can't wait to leave them when I stop by to see people. They also have no \textbf{elder} groups taking a role with responsibility. They all reach the base level of living and stop growing.\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small they have just different culture then white slovakian people but also is not fair to generalize. There is a stigma about these people, that they are lazy, don´t work, abuse social system and they children don´t care about school. And for some of them it is true but you can see here that not all of them are like that. If you grow up in certain enviroment it is not easy to break away from that. And also, I feel like lot of slovakian people have prejudices against just \textbf{gypsy} people in general, because  they just belive all that bad stuff and they don´t really bother to find out more by themselves, that´s probably why they told you not to go there.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/122 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald}, you'll never be in danger of being mugged when you  look like Tyson Fury.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small noble jose \textbf{gypsy} slum\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small hey Mr \textbf{Bald}, did you know that Pewds watches your channel?  he mentioned you on Cold Ones Clips channel PewDiePie on his Favourite Youtubers un Jul 15. Did you experience growth? 1Mil is around the corner! whoop whoop!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Hi, Lunik 9 is not the most controversial place in Slovakia, there are worst places where people live like in 2 ww. But when kids dont learn eng, they are not to clever I guess. But in \textbf{racist} Slovakia, they were never allowed to do so whether they were supplying European money  money for the issue . Thank you for your video and for being in Slovakia\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small yes \textbf{Indian} lowest cast moved to Slovakia and we can't get rid of them since then..\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small As an \textbf{Indian} i can say that, yes Romas are ancient \textbf{Indian} who migrated to Europe.Secret fact:: Mary magdale and Bathsaheba were also roma \textbf{indian} women......\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/27 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small They look like Indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small GYPSY DISTRICT NINE\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small There's \textbf{nothing} positive about having Gypsies in your area. They're  the epitome of incompatible cultures that don't blend in , even after  many generations of being present. Possibility the oldest non white minority in Europe......yet they are STILL different!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Non-white? Who else in Europe is non-white according to you in Europe? Spanish? Italian? Like, you know the \textbf{old} \textbf{racist} definition of "caucasian"?\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small \@5000Kone Siggghhhh......I'll spell it out for you guys. They originate in India. They are thieves who transform every area they touch into a rubbish tip. They leech off the welfare system.  They have \textbf{nothing} positive to offer. All this after how many generations in Europe?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@John Gibson Well, many people in India are white, related to Aryans. Basically, all people who have a mutation that makes skin other than \textbf{black} are basically white. Most people from Europe do not originate from Europe, that's why example most European languages are from the Indo-European language tree, etc. So what if the "gypsies" originate from Europe, they have lived in Europe for a long time, about 1500 years.  They moved to central  Europe about the same time as the Germanic tribes (Slavs.etc) and have mixed a lot with other Europeans, so genetically they are as Europeans as most nations in Europe.  Finland, where I´m also from, have Romanian people and they do not "transform" areas to a rubbish tip, same thing in all Nordic countries. Some people leech of the welfare system, most don´t. All ethnicities have something positive to offer, but not all people. I have been to Romani festivals etc. and they have lots of good things to offer, you are just a bigot. Who are you asking your loaded questions? From your self? Where all your hate, stupidity and \textbf{racism} come from? Do you have some kind of self-esteem problem when you must hate people as a group? Don't you know that only idiots do so? Even you sound like a moron, I do not expect that all people that come from the same \textbf{ethnicity} as you are morons ;)\normalsize   & \cellcolor{green!27}Black, Ethnicity, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/235 & \cellcolor{green!27}1.277 \\  \hline
  \cellcolor{green!5}\small \@5000Kone You've effectively written be an entire book on how we're all the same!Your arguments are confused and complex , and your side do this on purpose to confuse the public. '\textbf{Black} is white. White is \textbf{black}......and there's a lot of grey in the middle'Most people don't care if Europeans may have come from Africa two million years ago. Todays Europeans are white , have higher IQ's and superior culture.  I am a \textbf{racist} yes. I want my grandkids to look like me , and to have a future in a culture where they will be safe and can prosper. If that makes me \textbf{racist}......then i guess I'm a \textbf{racist}.We've all met lovely individual Chinese and Indians. They have some lovely food and attractive women.  I get all that. But it doesn't mean they should make up 55 of our population mix.  European culture will not survive.....with a majority consisting of Pakistanis or Indians. And we never asked to be replaced.  If Africans and Europeans are the same , then why the huge difference in IQ and living standards between both continents? Import the third world ,  you become the third world.  As for the Italians and Spanish, well they're about as white as the Welsh and Irish, whome they share some DNA with.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/217 & \cellcolor{green!5}1.843 \\  \hline
  \cellcolor{green!27}\small That girl with you speaks Russian so maybe she could tell you about situation in Ukraine and Russia where houses are burn and \textbf{racist} attacks happen on daily basis.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small There was a couple of allegedly \textbf{racist} attacks in Ukraine last year, but what you write is an exaggeration.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Is that your actual girlfriend, \textbf{Bald}? Jeezus, I'm glad I don't have a girlfriend like that, I'd be ill with love every day. I'd never get anything done. My life would fall into ruin. LOL.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Aaakkaashh Height of \textbf{racism}? Did you watch the video? Gypsyes created their reputation. All of the sudden people who speak the truth are \textbf{racist}? WELL I AM RACIST\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small Yeah we came from India but not every \textbf{gypsy} is poor im medium and every adult in my family got a job\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small You know even i (\textbf{gypsy})would not go there .even on morning\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@The Aryan Iranian damn you people are filled with so much hate and \textbf{racism} it must suck to be you who cares what color they are long as you're having fun life is short you guys are idiots get off your high horse\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Azuran 66 The thing I have always observed is that anywhere there are freebies, people become lazy, whether it is charity or social welfare or rich parents. It has more to do with leftist bullshit for these groups than \textbf{ethnicity}. I can bet you 9/10 times that if you see a hardworking poor Hispanic person in USA, that person would an illegal \textbf{immigrant} getting no food stamps or health benefits. Why? Because they were not given the fish but instead taught how to fish by the companies hiring them.\normalsize   & \cellcolor{green!5}Ethnicity, Immigrant & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/89 & \cellcolor{green!5}2.247 \\  \hline
  \cellcolor{green!27}\small you're bunch of \textbf{racist} shits here who are coming from somewhere Europe was fucked by Ottoman Turks for 500 years so yes all of you are pure white 🤣🤣🤣🤣🤦🏽‍♀️🤦🏽‍♀️🤦🏽‍♀️🤦🏽‍♀️\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@ky malone \textbf{Race} is not the color of the skin dumbfuck, get the fuck out of here.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@The Aryan Iranian ironically gypsies are almost as West Asian/Iranian mixed (as well as Balkan) as they are \textbf{Indian}. Just look at \textbf{gypsy} genetic results\normalsize   & \cellcolor{green!27}Gypsy, Indian & \cellcolor{green!27}Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Very British. Self promotion. It's their life. They live there life's. \textbf{Nothing} strange. Just different. It's everywhere,around us.....Broke post komunist society. With Gipsy-Romenians....\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small It would make sense if there ancestors was indians. Based on how many if not most neighborhoods in india have trash casually thrown outside it might be apart of the culture. Not that surprising  for a people to live with their trash when you have so many people who believe certain or all objects are spiritually connected to humans. If they had better more popular platforms than many \textbf{gypsy} women could be models.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Haha best thing to see after watching videos on mumbai slum. You are the best Mr bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{bald} Alina Bhabhi   Har jagah sath rahti  ajkal..😃😃 bhabhi achhi h na ...\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Interesting isn't. Makes me think that a multi \textbf{ethnic} Europe won't work ever... If after 500 years they are a separate community.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@Jdlc They are an itinerant group without any homneland. It's true that their ancestors came from India but their ethnogenesis took place outside of it, so to speak. Although you could just kick them out, since they have no connection to the land at all. As for the other immigrants that have come furing the \textbf{immigrant} crisis, I agree. Send them back. But don't just stop there, how about the UK gets rid of all those pesky Poles and other Eastern Europeans?\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small \@First Name Last Name The colonization of America and its consequences have been a disaster for the human \textbf{race}. It's too late to bring them back now, though.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@Jdlc They are very mixed, they arent pure \textbf{Indian}. They are almost as European as they are \textbf{Indian} now so it makes no sense to tell them to 'return' to Indija\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small In my country, we have sea \textbf{gypsy} which sometimes behave like \textbf{gypsy} in the video except that they build house in middle of sea or near the coastal areas instead of in land but since they don't want to live in land, most of them don't even have citizenship. Just incase u interested to make a content from that.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} are those girls dancing like thots damn\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Wait, since when did Slovak poor people become \textbf{Indian}? One day they tell us Aryans migrated from Europe and now they say Slovaks are Indians ??\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small What are you on about? The Gypsies come from Northern \textbf{Indian} and Pakistan and it's not a secret.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small So i saw the video where he meets Alina and Tanya, has a couple videos with Tanya, then the rest are with Alina. I guess she's travelling with him now ?? Very curious. I figure Tanya lives in Minsk and doesnt have the luxury to join \textbf{Bald} and Alina?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small I just want to ask when exactly are you planning to leave? Because It's pretty embarrassing at this point. Idk how many prime ministers do you need to change, whatever... Maybe the least competent will sort it out. You think you can run away from world problems? That's adorable and surely correct thing to do :) \textbf{Brexit} is going to make more damage to your country than all the slovakian gypsies would. For me UK has always been country of 50 heroes and 50 cowards.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small Slovalia heart of europe? Heart of EU? Wtf did you drink. The heart of europe is paris/Berlin. The heart of EU is brussels, berlin,paris. Letting eastern countries into the EU was a Political decision of good will. These countries contribute \textbf{zero} yet receive a lot\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small 9:13 I knew it. \textbf{Bald} says 'their homes so clean!'Yes, of course, because they throw everything out the window!I'm sorry, \textbf{Bald}, my opinion is this is a terrible place.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small \@onehappynegro young \textbf{age} players\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@Crowtein it has \textbf{nothing} to do with cultures... its the social economic conditions and the particularities of the spatiality that sets it in motion. Under the right circumstances any community will decend into this state of being.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@ⲈⲘⲒⳐ ϝᚱⲀ ⱌεᚣⳚϟⲯssέᛇ No, its \textbf{common} decency that they are lacking\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@onehappynegro Otherwise there is \textbf{nothing} to touch.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@ⲈⲘⲒⳐ ϝᚱⲀ ⱌεᚣⳚϟⲯssέᛇ You are an idiot.Their culture is the core of the problem. Have you ever seen a \textbf{gypsy} that works and earns an honest living? There is no such thing, it's just scamming and thievery.They take pride in getting by without working, go find a \textbf{gypsy} and ask them.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small So according to this palm reading \textbf{bald} will be the first transexual president\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small 菩薩Bodhicitta They sound like \textbf{black} street thugs who live in Britain.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Hello, I recently subscribed to your channel and think the videos are great.  I like the history of the U.S.S.R and you are giving us an inside look at the lives of \textbf{common} people living in areas for the former Soviet Union that we would not normally be exposed to.  I recently read a story about the subway system in Tashkent, Uzbekistan which features architecture started while the city was under Soviet control.  No pictures were allowed to be taken of the stations or trains until 2018 because the subway was used as a nuclear bomb shelter and the government didn't want it exposed to the outside world.  The few pictures I have seen are wonderful.  If your travels take you into Uzbekistan I think this would make a very interesting to see and maybe hear from locals about the city and its history.  Thanks and keep up the travels and videos.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/152 & \cellcolor{green!27}0.658 \\  \hline
  \cellcolor{green!5}\small Can someone pls explain how that \textbf{woman} could use Czech words easily? How many languages she speak? She can use Russian, english, Czech. Its awesome for me. And im really suprised. And im sending greetings from czech.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small so sad..... These people deserve to live like any other European.....  another example of eu doing \textbf{nothing} but letting  thief  greeks stealing billions of euros....\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small its \textbf{crazy} how all the people in Lunik 9 that speak english have such english accents\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small No,you were not from india,u and us hav \textbf{nothing} in \textbf{common},we a civilized ppl, even nomads in high up mountains are more  civilized\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small WTF was that? calling a 13 year \textbf{old} child a bad bitch?  that place is fuck'dup.. where is govermant? children probably getting raped there, i bet they've hidden pregnant one.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Indian people are better then these people\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Thanks for having the courage and sharing this experience. I see people just like me or anyone else, being marginalized due their \textbf{ethnicity} and culture, young children with not much hope, a sheer lack of support, schooling and the like. Obviously they opt for \textbf{alcohol} as an easy escape. Should we not be more fraternal with these? спосиво\normalsize   & \cellcolor{green!5}Ethnicity, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - General & \cellcolor{green!5}2/58 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small In slum i live in house and i got no \textbf{weird} accent\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Christian Collins Actually the notion that Czechoslovakia should split and the eventual dissolution was almost entirely orchestrated and popularized by the politicians, namely Václav Klaus and Vladimír Mečiar and their posse who eventually made it reality and became heads of state of each respective \textbf{nation} along with extremely corrupt and nepotistic aministration. At the time the average person in either region preferred the union and there still is a signifcant minority today who are of the opinion that the dissolution was a mistake.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small \@Mathew Van Ostin Gypsies are descended from low caste \textbf{Indian} Hindus who migrated out of India during foreign invasions\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@wozzup08 No...\textbf{Dumb} Western libtards giving them benefits.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Cristi Magda I had romanian coworker and he flipped out one day when I explained to him that gypsies in Spain lost their language, romaní. And he explained to me about that, romanians refers to themselves as romani... and gypsies is almost guarantied that they don't want to be integrated and they just want to keep being gypsies, which is 99 true here in Spain. He told me that gypsies gave a very bad reputation to honest romanians, and to be honest he was angry, upset, and I felt that he didn't liked them AT ALL. I met few more people from Romania and they shared the same opinion. Women or men they always wanted to clarify that they were romanians and were much more closer to Spain than Hungary that it's just right there. A \textbf{woman} just told me "we all came from the Roman Empire so we share a big root, our languages are romance and our cultures are not so different between ourselves if we compare it to Germany or nordics". She was clever and right... also a very smart bartender.Spanish gypsies totally lost their language and they only use now a few words of a variant called "caló".\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/203 & \cellcolor{green!27}0.493 \\  \hline
  \cellcolor{green!5}\small what do you whant to say with romani ? mybe roma not romani ...  and they are not from romania they are from india and the gypsies from this video they are slovakia \textbf{gypsy} bro .... you are stupid.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@Papaya Tasty and btw this gipsys live în Slovacia. .they have \textbf{nothing} do do with România\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Papaya Tasty just to correct a little, India is approximately 5300 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Great work agent \textbf{bald} ...\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Im from Slovakia and Im \textbf{gypsy} as well but in all communities are nice and clean and messi, rude people... its everywhere in world... In UK are lots of british people  who live similar like in Lunik 9....In Slovakia is big \textbf{racism} and discrimination thats why we are in UK...We comes here because in EU states like Slovakia,Czech republic or Poland is 2£ per hour for work? [if u have luck and get work ] ...20£ per month for childs benefit and rents similar like in UK ...\normalsize   & \cellcolor{green!5}Gypsy, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}2/88 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small I am English \textbf{gypsy} and I would be scared to go there you guys are so brave   And thank you for true reporting  ♥️  I think education is the only way out\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Give this\textbf{bald} guya Pulitzerffs!!!!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small It has to be said that as much as I abhor the Romany (\textbf{Gypsy}) way of life, imagine the British garbage collectors (dustmen) in the UK going on strike for two or three continuous years ... tourism would also disappear.  Taxation is usually a good thing.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Looks intriguing or something when shown by the highly entertaining Mr. \textbf{Bald} and his beautiful sidekick, yet I can't help but think that some truly awful shit must go down there especially with the poverty and \textbf{alcohol}.\normalsize   & \cellcolor{green!5}Bald, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Physical Identity - Physical Features & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Bald gonna get married I see it in the future ❤️❤️❤️❤️❤️❤️❤️❤️❤️❤️\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small THIS PEOPLES DESTROYED ALLL FLATS AND THIS FLATS WAS BEFORE NEW!!!!IN LUNIK 9 MAKE PEOPLE ONLY KIDS, \textbf{NOTHING} ELSE....\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Marry her she wil Serve u likeA king them kind of \textbf{woman} they wil die for u. Or even give their kidney heart any body organs them type of \textbf{woman} wil Giv. But English \textbf{woman} they want to Giv u drink 🍸 n get u alcoholic and take money and not even cook u anything 😂 English \textbf{woman} 👩 they need to come here for REHABILITATION ON HOW TO TREAT UR HUSBAND. Hey 👋 MR \textbf{BALD} MARRY HER ONCE SHE COMES TO UK AND POLISHED UP SHE WIL LOOK LIKE A MODEL\normalsize   & \cellcolor{green!27}Bald, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}5/93 & \cellcolor{green!27}5.376 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bakrupt - The humble guy said he is \textbf{Indian} decent LOL - throw some light plz! Intersting\normalsize   & \cellcolor{green!5}Bald, Indian & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small These people are just pure dirt, how can you happy live in your own waste? I don't care how poor you are , it's about pride. I have travelled all over Bulgaria and have seen places like this. This is not the true  representation of Slovakia. This is the dregs of the world. All they want to do is steal,  cause crime then play the victim. \textbf{Bald} I love you mate, but this is just pure propaganda for them. I have had first hand dealings with these people and they have no interest on bettering themselves. They steal, cause crime then  look so innocent for the camera. Please don't give these people anymore time in front of the camera, leave them too their own filth which is of their own making.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/131 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}\small Welcome to dodgy parts of my home town, Baldy!I love your capability to understand people you are dealing with, I very much agree with your conclusion at the end of the video.It's true, that we, Slovaks, look down to gipsies. Sometimes it bothers me to see how people consider them not equal, they don't show them politeness required for a formal meeting with strangers.On the other hand, the vast majority of them is burden to society- they steal, they take advantage of benefits as much as it gets (they pretend to \textbf{disabled}, they let their grandparents to formally adopt their child to get money...). I think some of them understand the benefits legislation better then lawyers do 😀 People call them lazy, but they can be hardworking when they see immediate profit of their work.I hope you felt welcome in Slovakia.\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/145 & \cellcolor{green!5}0.69 \\  \hline
  \cellcolor{green!27}\small The rubbish: normal thing for the gypsies. They can't live without that.Same for the sorry plight of everything around, they can't help destroying everything.It's like that."A brighter future" . Yeah! Invent something to steal more money somewhere.When it was \textbf{communist}, the kids went to school and the parents had jobs.What you saw inside is everything they stole in France or Germany!Now, it's free wheel, pure \textbf{gypsy} style.\normalsize   & \cellcolor{green!27}Communist, Gypsy & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Roma & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small You have my respect, that you've visited Lunik IX. I wasn't there, even I am from Slovakia. I truly like your content, as you capture living in nasty places, which have the greatest glory behind. On the top of it, your provide to the subscribers pretty enriching commentary. Next time you gonna be in Slovakia, take Alincik to our charming mountains "Vysoké Tatry (High Tatras)" or romantic \textbf{old} mining town "Banská Štiavnica" to make up a bit reputation about Slovakia. Greetings from the capital on other side of Slovakia :)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small First of all, Slovakia is central Europe, not eastern. Also, fuck you for saying we're "one big slum". That is not true st all. Lunik IX is getting torn down for a good reason - it's an eyesore, thanks to the \textbf{gypsy} problem. There's \textbf{nothing} the authorities can do about it. It's gonna take decades for gypsies, that live VOLUNTARILY in these slums to adapt to the rest of Slovakia. Most of them refuse to work, however and are uneducated (even though our school system is basically free, healthcare as well). Educate yourself.\normalsize   & \cellcolor{green!27}Gypsy, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small And this is why we (White Europeans) need to change first. we need to be more kind and accepting of them, and allowing them into schools. In some parts they are not allowed into school. How are they going to integrate or access a better life if they don't go to school? In Romania, a Roma girl was not allowed to go to school anymore (by her parents this time) because they were scared she would sleep with some guy before getting married... Older generations also need to understand that if they give their children some education, could prevent this from happening -if the child really wants to study. That girl wanted to study. instead she was forced to get married to a guy she didnt even like, and then they separated (his mother's doing for a \textbf{weird} reason)...\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/139 & \cellcolor{green!5}0.719 \\  \hline
  \cellcolor{green!27}\small I am from Slovakia and these \textbf{gypsy} people pretend to be nice but they're not. Why wouldn't they be happy when they don't have to go to work they don't have to pay bills. They have built their 'houses' on land they don't even own. And government? Instead of banishing them they get new houses for free. People like us have to work for them. So why didn't you take thousands of them home? I would be very grateful if you did. That's all I wanted to say.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small These kind of social parasites are the reason we voted Brexit\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small All \textbf{gypsy} places look this messy. It is a mentality thing. Most of the kids have been somewhere in England. But probably in a period they should have been in school. A large number of gypsies drop out of school. Instead they go pickpocketing somewhere in Europe. But on the other hand I am not surprised that they are great hosts when you show some positive interest in them. That is in their culture too.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small lets film normal slovakian apartments, you will see them clean nono desolate and good \textbf{colored}. even in czech republic.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Go to Stolipinovo in Plovdiv, Bulgaria. The biggest \textbf{Gypsy} suburb in Europe. Very similar to this one.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small The blog reporter is a citizen of UK or New Zealand, He is an \textbf{ethnic} Russian or \textbf{ethnic} Ukrainian or something. His finance is, I believe, a Slovak who speaks the local languages of east Europe and Russian too. . Countries where Russian is spoken: These countries which do not get a piece of the pie , in terms of aid , and free food and lodging, of America's trillion dollar loan every other year. Plus, these Gypsies and some Slovaks do not get any govt aid from govt of Slovakia or America.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/93 & \cellcolor{green!5}2.151 \\  \hline
  \cellcolor{green!27}\small This one is the best from \textbf{Bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Your videos will \textbf{age} well and cary a beautiful message that humanity is forgetting and desperately needs to wake back up to!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Keep Em coming Mr \textbf{Bald} You're a Rockstar. and Leena too!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small There is no \textbf{traveller} more fearless than \textbf{bald}.\normalsize   & \cellcolor{green!5}Bald, Traveller & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Quality content as usual, even PewDiePie watches Mr \textbf{Bald} and Bankrupt ha ha.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Wow most interesting vlog Mr \textbf{Bald} and Elena (I hope I spelt your name correctly). This is what we often dont see.What a \textbf{crazy} world we live in.Russian oligarchs have hundreds of billions of dollars and one just bought a yacht for 1.5 billion which is what 1500 average people in 🇦🇺 earn in a lifetime. Friggin insane disparity between the rich and the poorest of people.\normalsize   & \cellcolor{green!5}Bald, Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small Prečo neboli deti v škole a dospelý v práci ???  Normálny slušný ľudia posielajú deti do školy a sami pracujú, aby uživili svoju rodinu. Títo cigáni nepracujú, deti do škôl neposielajú, kradnú, lúpia, fetujú a my ich živíme. Ten Luník má pradové číslo IX ne zo srandy, ale pre to, že ich je postavených skutočne 9. Bol si sa pozrieť na ostatných Luníkoch ako vyzerajú ? Či aj tie sú takéto zničené ? A to Luník  IX bol postavený ako posledný ! Milý "\textbf{bald} and bankrupt" prečo si ich nezoberieš k sebe domov a nezačneš sa o nich starať ty ? Je ľahko kritizovať ako nezúčastnená strana ! Títo ľudia sa naučili využívať na maximum sociálny systém. Choď sa u vás doma pozrieť do Sheffieldu a potom začni kritizovať !!!!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/130 & \cellcolor{green!27}0.769 \\  \hline
  \cellcolor{green!5}\small This guy must host a new show... It would be very popular... SLUM VS \textbf{BALD} 😂\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small A SHITHOLE location with SHITHOLE people with a SHITHOLE culture....and everyone has to bow to their plight because of PC and \textbf{Libtard} power....Rubbish....Excellent video\normalsize   & \cellcolor{green!27}Libtard & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Those \textbf{old} buildings! Looks similar to Mahim in Mumbai\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Amazing video \textbf{Bald} - really really interesting. Did you find out how those kids got to Derby and London? The one saying wagwan sounded like he'd lived in London all his life.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small "dont judge me by the colour of my skin but by whats in my heart" ... what? no ... you get judged by how you behave. period. everybody gets judged by his/her own behaviour. to exclude sinti and roma (gypsies, but youre not allowed to call them that even if they call themselves \textbf{gypsy}, but the government at least in germany buttfucks you pretty hard for violating hate speech laws when using that term) from that is simply \textbf{racist} as fuck.\normalsize   & \cellcolor{green!5}Gypsy, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small The last \textbf{Gypsy} camp you went to, reminded me of a Syrian \textbf{refugee} camp I visited in Tripoli, Lebanon.\normalsize   & \cellcolor{green!27}Gypsy, Refugee & \cellcolor{green!27}Ethnicity - Roma, Nationality - General & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Hi Mr \textbf{Bald}. You are doing great things for people like us, showing how much poverty is in the world, except that these people live good lives. If i could, you should have a look at Electroneum, a cryptocurrency for the people, which is based in England. You could be an amazing ambassador for ETN to spread the word. They have just partnered with Ubuntu Pathways in South Africa to help kids from disadvantaged areas. If you need more info just go to Electroneum website!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small It's worth mentioning that whenever \textbf{bald} goes somewhere dangerous, just like the video where he was in the most dangerous place in Russia, there are two reasons he is safer than a lot of people would be. The first is that he's fucking huge, mugging someone big, loud and confident, is far more daunting than mugging someone scared, small and easy to target. The second is that his social intelligence is ridiculous, he goes to these places, is very charming, very flexible, very accommodating, and learns to read people quickly, meaning within five minutes he has usually made multiple friends, you're far more likely to get shit if you're an isolated outsider, than if you quickly integrate yourself and make friends.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small Gypsies are \textbf{crazy} people. Sad but true they cannot be trusted. They will smile at you while they steal from you.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I think this is insulting to all the good people that have been on this channel to try see good in people who throw their trash out of the window and destroy their own environment, who are a problem in any \textbf{nation} they live in. It's like a complete denial, refusing to see whats right in front of you.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small It makes me really sad and annoyed that one video trying to show the goodness in some people has comments like this.Every \textbf{race}, country or person has good and bad things\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small So \textbf{weird} to hear roma gypsies in Slovakia talking like roadmen from London?\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small paul Asian Way These are not even European people, and some of the \textbf{African} immigrants are creating poverty and crime in Europe,\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Also, is Alinchik speaking Slovak/Czech, Belarus or Russian with them? I would guess not Russian since mr \textbf{Bald} surely would had join in if that was the case.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Bald tell them kaisaho  or kia hal hee...to know if they are indians..reporting from kenya\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Bold is the bravest man in the whole fucking universe. He went to the worst \textbf{gypsy} spot at Slovakia dressed up in a green/orange Bomber jacket, which was worn by Slovak \textbf{Nazi} skinheads to beat the shitout of gypsies around whole Slovakia...And obviously... he is \textbf{bald} :D\normalsize   & \cellcolor{green!27}Bald, Gypsy, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}3/47 & \cellcolor{green!27}6.383 \\  \hline
  \cellcolor{green!5}\small Its amazing that in just a few videos I see Alina grow into a strong confident \textbf{woman}.  At 3:46 look at Alina squeeze Balds arm that looks like love to me.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small dude its always like this :] .. but show me one czech or slovak who was never robbed or beaten by a \textbf{gypsy} group .. thats also speciality from them how \textbf{old} are you??? 25 oh there is 25 of us aswell... always screaming for whole fuckin street ... every \textbf{woman} atleast 10 kids for more money from state.. But dont get me wrong i have a lot of \textbf{gypsy} friends .. Its just that the majority doesnt give a shit about anything\normalsize   & \cellcolor{green!27}Gypsy, Old, Woman & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma, Gender - General & \cellcolor{green!27}4/83 & \cellcolor{green!27}4.819 \\  \hline
  \cellcolor{green!5}\small I hope that you will visit also beautiful places in Slovakia so the world doesn't image Slovakia as a dirty, sh***y country. I have to correct you :) that not SOME Slovakians, but MOST Slovakians don't like gypsies, as they are lazy, cheeky, fake, they have a very low IQ, which means they end their education at the \textbf{age} of 15 and when you give them a nice for living they turn it to this dirty place in a couple of days. They have a lot of privileges, they do \textbf{nothing} and the rest of the country has to work on them. Of course, there also some good exceptions, but unfortunately very little exceptions.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/114 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small They do get assistance though. I don't know about Slovakia but here in Romania and many places in Eastern Europe they have special reserved seats in colleges. They can join any university and get up to Phd level for free, without ever having to pay a cent. They are encouraged to go to school and kids that go to school receive a monetary allowance from the state. There are numerous financial and social benefits they receive. But most decide it's better to live off welfare and do petty crimes on the side. The generous welfare state in Europe sends you more and more money the more children you make. If you have 4-5 children in your care and no official income, you can receive the equivalent of a full time paycheck in welfare without doing anything. Help is plentiful, what they need to do is help themselves. I know because my mother comes from a \textbf{gypsy} family and grew up in such a ghetto. In my experience, people are quite accepting here in Eastern Europe and as long as you follow an education, act like a civilized and decent person, dress cleanly and take care of yourself, \textbf{nobody} will attack you or disrespect you, or even treat you as an outsider just because your skin is a little browner than normal.\normalsize   & \cellcolor{green!27}Gypsy, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/221 & \cellcolor{green!27}0.905 \\  \hline
  \cellcolor{green!5}\small The antiziganism movement in Eastern and Central Europe was repelled in the early 1930s for being inhuman and oftenly being associated with anti-semitism, then communists came, they were offered housing, jobs and were integrated into the society, after the fall of communism, they blamed Eastern Europe for the \textbf{gypsy} problem — Lunik 9's situation can easily be compared to the \textbf{gypsy} neighborhood Ferentari in the Romania's capital Bucharest. It's not that the authorities are not trying their best, it's just that this is their way of living. They throw waste out of windows, the sanitary teams come and clean the place, just to confront the same issue few days after. They're uneducated, not because the government is not offering them free education (education is free in Romania), but because they prefer to commit theft at an early \textbf{age} and if caught in a western country (ie Italy) they're incarcerated in hotel-like conditions and just forced to go to school. Don't let the environment they live in fool you, they're not poor — beggers make more than €100 a day, not to mention the shoplifting from the high-end shopping outlets or the pick-pocketing. Stop blaming governments for your people's way of living and more importantly stop describing yourself as Romanian, Slovakian, Hungarian or Bulgarian, describe yourself as being \textbf{gypsy} and stop denigrating the Eastern and Central Europe countries.\normalsize   & \cellcolor{green!5}Age, Gypsy & \cellcolor{green!5}Age - General, Ethnicity - Roma & \cellcolor{green!5}4/227 & \cellcolor{green!5}1.762 \\  \hline
  \cellcolor{green!27}\small It's really foolish to encourage a bunch bumbling, naive tourists to go stumbling around drunk in \textbf{gypsy} slums with their fancy cameras and smartphones.In Ukraine I met this older British guy who went to photograph a \textbf{gypsy} slum in Besarabia, near the the border of Ukraine and Romania and was beaten half to death and robbed by \textbf{gypsy} guys. It took him like a year to recover from his injuries, he still had problems breathing because of how badly his nose had been broken - this is the sort of thing that can happen when you don't heed the advice of the locals, if locals tell you that a neighborhood is dangerous don't be the idiot that goes there asking for trouble.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}6/123 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bankrupt Well Mr \textbf{Bald}, it would be nice if you tell us how much you payed the gypsies to film them or how things would have been if you let Alina go there all by herself.But you are not not going to answer that,  I'm sure.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small poverty, bad situation, .... cˇmon these are central european gypsies, these appartments looked like anywhere else in the country some yrs ago, gypsies just damage everything, they dont work, they live on social support and have many children. this has \textbf{nothing} toi do with real poverty, this is just gypsies way of life.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small They didn't get deported.  They live in England and mainly claim benefits, but spend a lot of time in beloved \textbf{gypsy} camps. Mind you, some areas in London are turning into the same state due to the infestation of Romanian gypsies\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Bojan Nišević I wish they were deported. The sad thing is that the media and politicians would call that \textbf{racist}.. and the government has such a destructive immigration policy.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small my country, aaaah...you're \textbf{crazy} man\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Do they have any hopes from India or \textbf{Indian} government?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small What \textbf{Indian} government has to do with them?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small i am from slovakia and i have to tell you someting , we build them brain new flats \textbf{witch} can stand 100 years , we gave it to them for free , some of those flats din t last for 20 years becouse they sold windows and steel from walls :Daslo , gypies are not bad people  well , not everyone , but believie me you dont want to go there at night :D drugs fights and stuf... police is there at least every day\normalsize   & \cellcolor{green!27}Witch & \cellcolor{green!27}Gender - Female age and physical appearance & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Yea this is the point, you are slovak a they are them . I am from czech rep and its same here - if you grow up as a \textbf{gypsy} you are branded as a \textbf{gypsy} and for example you are not allowed in normal schools mostly - so all the choices are taken away from them from the begining ... and you feel like giving these poor people something is any way of retribution for generations of discrimination .... ha.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small \@GSH RDY Sorry to say but you guys are completely wrong and just making excuses for them...Maybe what you said is true for \textbf{black} people in America or other minorities, but the gypsies around the world are another story. This is their way, it's what they do, what they've done, and what they will do, always and forever. They will never change, it's a part of their culture for centuries. How come every \textbf{gypsy} in the world is the same, in every country? They are born in completely different parts of the world, in different times, in a different environment and they are still the same. It's a mystery really...Even the best \textbf{gypsy} in the world is still a \textbf{gypsy} and you can see it in their character. \textbf{Nobody} treats them badly anymore, they are very spoiled and they get all the help they can but it's no use. People who do treat them badly are doing it because they are acting badly. But no matter how they are treated, it runs in their blood and they can't hide it. If you grew up knowing gypsies, you can always sense them from miles away. They don't even need the dark skin color, it's their mentality. For example, \textbf{black} people from UK are different from \textbf{black} people in Belgium (both in Europe). Also there's a big difference between American \textbf{black} people and others. Not to mention the biggest difference between \textbf{African} \textbf{black} people and others. But a \textbf{gypsy} is always the same wherever he is. If you send one single \textbf{gypsy} alone to Mars, firstly he would demand a very low price for him. Then he would find a way to produce 6 children, 2 mothers and one half sister-half wife. You would be able to see the trash on Martian ground from Earth, he would trade all the equipment for golden necklaces, chains and bracelets. He would destroy the space shuttle and take everything made of copper.\normalsize   & \cellcolor{green!27}African, Black, Gypsy, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - Roma & \cellcolor{green!27}12/327 & \cellcolor{green!27}3.67 \\  \hline
  \cellcolor{green!5}\small \@This is the best name I could come up with It sounds like you are talking about blacks. But it is clear to me that you don't think much of them. They are Europeans "\textbf{negro}" problem. So instead of really helping these people, they let them languish in ignorance. The same thing could happen to any people (white or \textbf{black}) if the foot of power is on their necks. We must recognized that people are not accepting of poverty and ignorance. They want the same things like anyone else. But the system has to stop discriminating against people, so they also have a chance to the same things.\normalsize   & \cellcolor{green!5}Black, Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/108 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small It is interesting that the richest \textbf{ethnic} group in the US are of \textbf{Indian}(From India) descent. Google it. :)\normalsize   & \cellcolor{green!27}Ethnic, Indian & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small \@yan These Gipsys are slovak as much as other slavs are slovak. It's just a \textbf{nation} not a etnicity. Slovaks are predominantly Slav but other etnicities can be Slovak as well...\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Hitler so-called Aryan master \textbf{race} originally came from India according to his bullshit racial theories.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@The Aryan Iranian haha, they are the same so-called 'Aryan' \textbf{race} as you, the ancient Aryans were Indians according to Herodotus\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@d ch What ?? The Roma have \textbf{nothing} to do with the Slovaks Slovaks are slavic german etnic btw I am a Slovak and I will be born in Pakistan i been Pakistan guy omg i don't understand it liberal mind ...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small In Hungary the goverment gave them brand new huses also, socialworkers gave them advices how to clean, how to dress, how to cook, how to treat the chidlren, how to get a job, how to handle money etc. Didn't work out. They sold the materials of the buldings. I was born in Hungary, studied hard, worked hard, I didn't have anything. \textbf{Nobody} gave me a house or financial help. They had and they throw it away. They didn't study, didn't work but had all the support. Others are working for a home a life time and they... We try to integrate them and it just doesn't work out. And this is not our fault I think. Average ppl when have a chance to live a better life, are thankful and try to prove they deserved it.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/136 & \cellcolor{green!5}0.735 \\  \hline
  \cellcolor{green!27}\small \@Júlia Juhász same in slovakia , our liberal politics just talk about tolerance , they do \textbf{nothing} else , just talk about it . Our people had to work hard for everyting ... its shame\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Protector of the Republic They're NOT given even a chance. Change doesn't over night, just like a baby doesn't turn into an adult over a night.  Universities here have maybe 1 or 2 spots open for Roma people. this is discrimination. Trust me, that you wouldn't care how your child acted either if he or she wasn't allowed by the system to study. Many Eastern european countries still think and behave like under the \textbf{communist} regime. This mentality won't disappear until those over 50 years \textbf{old}, die. Sadly, many of those who are 35+ have a very similar thinking and they continue to pass it down to their children.\normalsize   & \cellcolor{green!5}Communist, Old & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small \@Sapphire Camui My mother is a \textbf{gypsy} and I spent all my teenage years in a slum like this. Don't tell me what they can't or cannot do, I know too well, I was one of them. They live like this by choice. It is an active and conscious choice.  The only thing required of you is to behave like a clean, decent, civilized human being and everyone will respect you if you carry yourself the right way. They choose instead to act like thugs. I've been in a slum gang, I've been in their shoes. Changing is easy, you just have to move away and start living like a normal human being. The only catch is that you must want that.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/122 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small \@GSH RDY easy to say from your comfortable western home in a safe area, fucking retarded \textbf{faggot}.\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Hello my fellow 9 years \textbf{old}!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Bald will become President of Lunik 9!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Woooop wooop blatant \textbf{racist} and cultural supremist train makes a stop in this comment section\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Showdown lol it would take 12?lol those faggots don't know hand to hand combat stop it...now what about u mr.\textbf{faggot},what are u about?Tell them to come to USA,come conquer an area here lol...they'd be dead by the morning\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@DeAngelo Claytor you cleraly have some kind of \textbf{mental} disorder m8. I wish I knew what caused that to you. I suggest you to find some therapist if u don't have one already, or u might just have forgot to take your medications ffs I don't know. If that's the case then I'm truly sorry and please forgive me. But if u r sane!? I can arrange for u full midnight experience and it"s all on me. All costs included, such as Hotel for the first night, also further medical bills and of course plane ticket from and wherever to shithole u coming from. Lemme know\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small Dali F. Be lucky we are not there,we'd make u bums pack up and leave.Gypsys are the trash of Europe! wouldn't u say Mr faggot\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@DeAngelo Claytor first of all you complete \textbf{pussy} its really pretty easy to act hard when you've got a gun and on home turf. Come to Europe and try the shit you do in America you'll be eating through a straw for months you gimp.Btw you telling the guy to speak English is fucking ironic since you clearly barely speak it yourself you charity store, sub 90 IQ, \textbf{fat} ass \textbf{pussy}.\normalsize   & \cellcolor{green!27}Fat, pussy & \cellcolor{green!27}Nationality - Chinese, Physical Identity - Physical Features & \cellcolor{green!27}3/72 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@SongBillong i wasnt saying you were mocking them and im \textbf{gypsy} too\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small SongBillong It's a street accent. It's basically \textbf{black} gang slang. Not an authentic Derby accent.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Iam from Slovakia and I am too \textbf{Gypsy} I hate that place because is just shame of good \textbf{gypsy} people\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Petra Hamster stop being jugdemental, we are all created by God, and we all have faults. In fact we are all sinners, sometimes its hard to look in the mirror. You are no better than them. We all need Jesus Christ, anyone that comes to him, he will save. Sadly most people do not want God, but I can tell you from my heart, God has blessed me with many good things, changed my life for the better and freed me from \textbf{mental} slavery and darkness.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Indian government should pressure the Eu to improve the life of these people.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I'm embarrassed to say that as a tourist from New Zealand last year I never saw any of this. Yes, Kosice on the outskirts looked poor but \textbf{nothing} like what \textbf{Bald} says although I can well imagine how it could actually be. Travel to the central of Kosciche and you have traditional tourist experience insulated from any prospect of poverty\normalsize   & \cellcolor{green!27}Bald, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Hi pervert, still dreaming about Himachal police \textbf{woman}?😅\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Gypsy wedding ah?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Gypsy people are good the only bad people on this earth are Greeks who think they are Macedonians \textbf{nothing} but thieves who need to return the stolen land to the Macedonians\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}6/31 & \cellcolor{green!5}19.355 \\  \hline
  \cellcolor{green!27}\small Clean inside, filthy outside. They definitely took their \textbf{Indian} ancestry seriously!\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small You'd probably adapt. I have an empty house to myself most of the time and I see this kind of place as stressful and annoying, but if I was there from an early \textbf{age} it'd probably be tolerable.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@TheOriginal GGHarasser If you were there from an early \textbf{age} you probably wouldn't be an introvert to begin with.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I think being social and friendly is a matter of learning and survival at least when you're traveling like \textbf{Bald} is- why I don't think I'd travel well alone then.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small In places like those you can't really be introverted because theres \textbf{nothing} keeping you inside, all you have for entertainment are other people. Introverts in senarios like these are just the guys who talk a little less than the rest.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small So far I could probably handle the situations that \textbf{Bald} goes into, but this one, no way xD.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Are they \textbf{indian}? As if they then welcome to 🇮🇳 india.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I bet those \textbf{gypsy} slums are richer than most middle class Indians....\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small come to Serbia \textbf{Bald} ! so much material here :)))\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bankrupt  yes, didn't think about that. Serbian language  and russian are 27 same :)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Did you score that mix feeling \textbf{chick}?\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Gypsy are also famous in Rajasthan,india...\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I'm impressed by that boy who speaks English fluently. I was born in Presov and I remember my \textbf{gypsy} classmates... They were barely able to read in Slovak.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Edina  Maybe \textbf{Brexit} will help keep them out.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Larry Bones They are \textbf{nothing} more than human parasites.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@2:47 :  "judge me by colour of my heart.."  Alinchik, your heart is huge beware of big \textbf{fat} baldy.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small huge respect to \textbf{bald} I mean like you are an exceptional youtuber i never enjoyed videos more than yours\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small hey \textbf{Bald}, are you still in Slovakia? we could. meet. up and I can show you some places here\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Respect to \textbf{Bald} and Alina for this video.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You are brave my friend. You look like skinhead. Jacket, hairstyle... And like this you go to \textbf{gypsy} ghetto...\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Modern \textbf{gypsy} swimming pool/watch?v=megTg0Alm c\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small gypsy aquapark/watch?v=W7hTpBopCsU\textbf{gypsy} aquapark 2/watch?v=rUZ1VxXZfzs\&t=5s\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small I lived in \textbf{old} USSR countries as an expat and loved it so much. The garbage mountain can be explained with an \textbf{old} USSR mentality, although this place is an extreme example of it. They don't care the public spaces in the building, because government used to do it for them. But these beautiful people decorate their home, keep them tide and clean. It is just lack of communal living sense...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small Thank you for comming to Slovakia, hope you will enjoy much more than lunik 9 :) there ale plenty of places with \textbf{old} soviet stuff as well, when you know where to find yhem ;) in case you will visit Orava, we can enjoy some trip and beer together ;)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Wow. I went to Kosice one month ago in June with some friends from my Erasmus year, and we decided to go to Lunik IX. Craziest place I've been to, it's unbelievable how isolated it is. But I really wasn't expecting that \textbf{Bald} would upload a video about it one month later, what the fuck. I'm from Spain btw.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small I've watched a lot of \textbf{gypsy} films and this  was great.  Of course its viewed with mixed feelings.  But beyond a doubt this is the strongest argument against multiculturalism and open borders in Europe, as you said they have been there for centuries yet they fail to assimilate and thrive by choice.  Such beautiful children they need love and good roll models, not drunks and thieves.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Fucking shit bag gypos. All of that area was very nice and was given to them for free. They trashed it. They are welfare leeches, thieves and drug dealers who contribute \textbf{nothing} good to society. Fuck the lot of them. Greetings from Czech Republic.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small They look like \textbf{Indian} people\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I see none of these people that commented knows anything about \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Kids drinking at 12 years of \textbf{age}....ummmm sounds like Chris Hansen is going to walk in\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small One thing I like about \textbf{Bald}, he never pushes you to tap that Like Button, and because of that, I tend to forget to Like the Best Videos on YouTube.  So, hey, hit that like button if you liked this video..\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small seem to be they cook barbecu at their balconies that turned almost every balcony covered with \textbf{black} soot ? Inside the flats actually better than many Belarussian Apartments some how .Large specious very well furnished and clean .\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Bald is such a cool genuine dude just wanting to experience living\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Fantastic video \textbf{Bald} - loved the stark reality of humanity that you take us to.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Do a Finland tour, and you will see a "real" \textbf{gypsy} party.. immigrants I guess, I have no problem....but haha, you could not show the footage in youtube :D\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small If you wanna visit the biggest \textbf{gypsy} ghetto/slum, you should check Bulgaria/Romania. Lunik 9 is consider quite small in size compared to our \textbf{gypsy} slums.In my City which is Plovdiv, we have a \textbf{gypsy} slum consisting of over 80,000 people and they are IN the city, not the outskirts. Not a thing to brag about, but just letting you know :) This slum is pretty close to ours in terms of how it looks like.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}3/76 & \cellcolor{green!5}3.947 \\  \hline
  \cellcolor{green!27}\small I don't think it's fair that you blame these people more for their living situation than you blamed the abkhasian refugees in the sanatorium. in fact, it is almost certainly harder for the roma to get out, because everybody hates or distrusts them. they can hardly get a job or rent a place. they live in segregated ghettos for the same reason why any \textbf{ethnic} minority lives in segregated ghettos: because the people in power and society at large keep them there.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small From Pattaya Yacht ⛵ Club  Love you \textbf{Bald} n Harald you guys are so good at what you do. \textbf{Bald} your chic seems sweet as Cola. Slavic chics are sweet. Her mom seems very nice.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small You're a real traveler!Keep them coming mr \textbf{bald}.Love from London\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small From Playboy in Thailand 🇹🇭 Wonderful \textbf{Bald} n Lovely Young lady n Harold your all WONDERFUL. Marcus 81 n Lovely Jian Chan 23 my one n only honey 🍯 hehehehehe Pattaya n Baguio n Taipei\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald} ! These apartments were made for officers of the Czechslovakian Airforce !Jei Boleki\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Hello again Mr \textbf{Bald}. Can you please tell me the name of the folk band who covered prodigy at the start? Cheers and safe travels.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Amen. Nice job, \textbf{Bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Anna M ok thats good!I just experienced that younger Czechs when speaking in Slovakian to them had a harder time understanding than the older ones.Whereas Slovakians have no problem at all, because of a lot of movies/series for children are in czech dubbing, so they are in contact with it even from young age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Bald president?Anyone have the same idea?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small When the \textbf{gypsy} kid started filming his \textbf{gypsy} whores, I lost it, CHEERS YOU BLOODY GYPS!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Change the channel's name to "\textbf{Bald} and Balls" -- as we say in the U.S., it took brass balls to visit that area!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{bald} you heard the lady you're going to be a president one day . 😏\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small This is part of the reason people voted \textbf{Brexit}. There enough Brits that are sponging wasters without having the league of nations here as well. They can come over and fleece the benefit system. Gtfo here. \textbf{Brexit} cannot come soon enough\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Was in Birmingham UK - Kings Heath i think it was called, 1995 and there were 12-13-14-15-16 year olds in a prefab type of pub on a council estate drinking spirits and smoking their heads off(they were lying down over the seats and floor in middle of the day) normal school day and \textbf{nobody} cared......barman said they were safer there - made me feel ill. This video reminds me. There's shit holes in every country......No go pros that time....\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small Exact same as the pikeys here kids robbing you look smell like shit. Disgusting place you here me you \textbf{gypsy} benefit cheats here in the uk.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Bald is defo smashing that bird all over the gaff\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Pewdiepie states on a recent podcast from ‘anythingforviews' that \textbf{Bald} is his current favourite vlogger. Great endorsement! Hope you get a surge in subs.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small The child is now well known for his \textbf{bald} head  in Lunix IX\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small First time I saw an Englishman shocked by a \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Košice is actually quite nice. This camp was very evidently a \textbf{gypsy} area. Saw it when was driving to Banska Bystrica\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Never in my life did I think I'd see a Slovakian \textbf{gypsy} say 'wagwan'. Amazing content as per.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Omg, I was worried you will show up there :D But you described it the way it is. Only \textbf{gypsy} slums looks like this in Slovakia. Looking forward for more videos from here.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Thanks for showing us the Roma!The 'original' brown people of Europe!These share \textbf{common} ancestors with the manicure people you met at the beach in Goa!\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small the best ever by \textbf{Bald} keep em on coming ma manz.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small "Historians estimate that between 220,000 and 500,000 Romani were killed by the Germans and their collaborators—25 to over 50 of the slightly fewer than 1 million Roma in Europe at the time.[1] More thorough research by Ian Hancock revealed the death toll to be at about 1.5 million.[3]" A lot of hate being directed towards the Romani community from people who perhaps if they were around 75 plus years ago would have collaborated with the Nazis. Do the people of Lunik 9 need to take responsibility? Yes, they do.  However, the rest of society needs to start seeing them as human beings.I am pleasantly surprised at how well-spoken the young are (in English), though disappointed that they picked up the 'Roadman' dialect.  If \@\textbf{Bald} and Bankrupt does read this, maybe he can leave them with one of Akalas tracks. His first appearance on BBC Radio's,  Fire In The Booth, extolled the virtues of education. That's the one I would pick.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/161 & \cellcolor{green!27}0.621 \\  \hline
  \cellcolor{green!5}\small It's like they're feral. \textbf{Bald} for President!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Aidan \textbf{Immigrant} groups like theirs are responsible for the shitty conditions in certain neighbourhoods in our towns and cities. I don't really blame them though, rather I blame our careless government and Parliament who have allowed this to happen.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Bald, you know PewDiePie watches your videos? You deserve it as your videos are very informative and well done. Hi Pewds. We love you fam, you too \textbf{Bald}. No homo\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small No need to be scared \textbf{Bald}, we all saw Alina's right fist punch in the last video ;-).\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small If you come to Serbia \textbf{bald} let us know!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Disgusting manners, doesn't matter if a \textbf{gypsy} is dirt poor or a millionaire, he will always live in dump. How the fuck can you walk in your own shit and smell it all day? I know that it is hard to understand for people from USA, UK, northern Europe etc, and that you are feeling guilty when you are seeing them on the streets and begging for money - but oh boy how they are collecting your money with joy. Ask them if they would collect some firewood or cut your grass for some money haha... They would rather sit there in dirt and beg than to lift their ass and work. There are thousand of f*cked up stories about these people...\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/122 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small Trash everywhere and \textbf{old} fucking apartment complexes that looks like they are about to collapse - but the kids run around in suits. Such a contrast man...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Why are all these "lovely" people being pushed away from England, Mr. \textbf{Bald}? Keep them all if you like them, would you.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small 6:26 The kid calls \textbf{bald} and bankrupt Ben\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small A lot of them have pretty British accents and use British slang which would seem \textbf{crazy} without context\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small The Blethering Maw There is no 'London type of accent', there are, for example, Estuary, Cockney and RP. But those are not all and you could even go on to divvy them up further. And all of them, like Scottish and Welsh and West Country and you name it are all dialects from Britain. So inherently, these boys have some sort of a British accent. The point is, it's English not as taught in school outside of Britain, but they obviously had to have lived in Britain, hence the 'which would seem \textbf{crazy} without context' remark from the original comment.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small \@Michael Pencio here we go, waiting for the \textbf{racist} rant...\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@it'sMe TheHerpes no peace between those two nations. even here in czech republic, no piece between our \textbf{nation}. even one story of goup of gypsies knife attack on swordsman. that attack wasnt succesfull. In hospital they have told, they fell from stairs.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Josef Malár You do know liberal just means an open mind right? As opposed to \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small With this video you have gathered some pretty \textbf{dumb} people in the comment section. The video was nice, thanks. Ps. You were wasted when you gave the camera away and a bigger boy could've snatched it quickly from the smaller lad - lucky you! haha :D\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Alina and \textbf{Bald}. I think that you didn't have trouble here because the two of you treated these people with sensitivity and respect. While you did ask some hard questions you did it without judging them for their answers. You two are the true definition of "travelers". Thank you for your videos recording your journeys.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small \@Indy Jones No it does not automatically of course. They are free to go everywhere it is not reservation or anything. There are lot of Roma people with nice living conditions and stable jobs. But sadly quite large percentage of them are rather just recieving the welfare and expecting to get everything for free. And that is the majority of them in Lunik IX. That housing estate was build not only for them there were also living Slovak majority ( mostly cops and military people- idea was for them to re-educate them) but they soon left it. In 1996 city council decided to put there almost all Roma people from city there and this is the result. They destroyed many of the blocks (few years ago some of them had to be tear down because of bad static). Schools are free in Slovakia they can get education also they can get work if they are willing to but these people rather just roam up the city  garbage cans all day and do \textbf{nothing}. And it is quite dangerous part of city. They did \textbf{nothing} to \textbf{Bald} luckily but few months earlier they attacked Ambulance personell that came there for pregnant \textbf{woman}.\normalsize   & \cellcolor{green!5}Bald, Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}4/201 & \cellcolor{green!5}1.99 \\  \hline
  \cellcolor{green!27}\small \@David Szabó You fail to mention the bigotry and \textbf{racism} that they encounter. Most Slovaks will not hire Roma for jobs and consider them subhuman. It is no wonder that they stay in Lunik IX.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Come on, they don't have a chance. Most schools don't allow them in, and many \textbf{doctors} refuse to see them. If you have no education, you'll never find a job. And even if they do have some education, most employers won't hire them.Yes, they don't make it easy for themselves either, but they are stuck in a vicious cycle.\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small \@38snubby My grandma hired \textbf{Gypsy} constructors for reconstruction of her house. Contrary to prejudices people say about them, they could be really hardworking, but only if they see imminent profit of their actions. And they are unreliable, in sense, they have problem to commute to workplace regularly.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@TheTurboLazi They are experts of how to milk welfare system. Frauds with  fake pensions for \textbf{disabled} people and etc. Sometimes they even threat medical \textbf{doctors}, to make them confirm them their lies\normalsize   & \cellcolor{green!5}Disabled, doctors & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I am living in this city from 6 years. I would like to add more few things. This kind of people just happy when they  get everything for free ,so they getting all kind of requried needs . They like vodka from morning till midnight. When they waked after drunk then they thinking why i dont have \textbf{nothing} like outside living people have. Outside people working from morning till evening in a week.Kosice city is full of cultures , food and history .kindly make video about real cultures and really beauty. People very friendly .\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small 38snubby you fail to mention gipsies encounter just as much prestige, how much they created themselves by their own previous actions. Its not because of color. Its not \textbf{racism}. And btw the gipsies are racists. They call all white people 'gádžo'. What you mean by bigotry? That the majority doesn't believe their undisciplined laziness and parasitism is acceptable? They don't work but still cost money. Who do you belive is pressed to support their survival?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Titina de Cassovia You might save on your renovation if you hire some \textbf{gypsy} workers, but it's not worth the trouble.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@38snubby You would hire them and they would DEFINITELY take advantage of you, you haven't lived among them so of course you will never understand. But yes, "\textbf{racism}".\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I didn't see any \textbf{gypsy} in central kosice. Guess they stay in their own yard\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Im \textbf{gypsy} and i would never live in Luník ix\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I wouldnt be afraid to get rob by an \textbf{Indian} guy😂😂\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@it'sMe TheHerpes what is 8 grade? meaning 14 yaers \textbf{old} kid?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small In start of video you should show how Kosice looks. Its a normal modern city with 200k people and then you should go to slums. Its pitty you don`t show normal Slovakia firtst and then these slums. I`m from Presov, 30km from Kosice and I`ve never been in Lunix IX but we have gipsies here too, a lot of them living in smaller slums in smaller towns everywhere here in eastern Slovakia. Gipsies are problem here and a lot of politicians were trying to solve this problem but it could not be solved that easy. If you live here you would know that 80 of gipsies from slums here live just from social money. They dont care about their kids, they dont pay taxes, rent etc. Goverment build them houses to live. They destroyed them because they hate government.  Normal family here must take loans for 20years!  to build a house or to have a flat.   They are looking into garbages everywhere around the city. A lot of them are in jail or are trying to steal something. Few of them are trying to get socialized, get jobs and live normal life.  But the problem is their mentality. Even if you hire them, they will not do their jobs for 100. They will not be happy to have a job. I havent seen gipsy that was happy to have a job here and to be thaknful for that.  They want quick money. Most of them are working as construction workers or in waste companies but they really don`t do their jobs very well. This is problem that normal companies are hiring them only as last option... By the way I hope you will not get Hepatitis B. You and the \textbf{chick} should check yourself at a doctor after visit to these slums.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/302 & \cellcolor{green!27}0.331 \\  \hline
  \cellcolor{green!5}\small Crazy to think that some parts of Europe are so run down like this.  Tho the people still seem really happy. I'm from West Europe U.K🇬🇧\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Man, this is awesome! :)) But what I find extra funny, is that you are dressed like 90s neonazi and you are in a \textbf{gypsy} ghetto :D balsy move! :D\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small If Trump refers to \textbf{African} countries as shit hole, I don't know what he gon call this one.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'd take that \textbf{gypsy} palm reader back home with me\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small High poly people live in there own screwed up world they never set foot in a place like that, this is why you are a special person you can fit in anywhere \textbf{Bald}, you can be successful in anything you set your mind on, a very special quality.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small don't you always shit on the former \textbf{Communist} regimes? Well who do you expect to take out the trash and maintain this place now that the dreaded commies are gone? Capitalists certainly don't give a shit about the Romani. I'd say it actually looks pretty good for not being maintained since the end of communism\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small As per wiki: "Health standards are low and diseases such as hepatitis, head lice, diarrhea, scabies, and meningitis are \textbf{common}."  Umm....hope you guys had your shots and stuff....\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Looks like every \textbf{gypsy} campsite ever\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Come to Tecuci street in Galați. You can look it up on google maps. Now it is refurbished, the lanes are sleek, there have been bike lanes added, to boot, the telecommunication cables have been buried yet all the houses are ramshackle hovels.I dare you. At the end of the street there are two shabby bars where they generally smoke, listen to manele (turbo folk) and self harm. After 18 the central market is the gloomiest place in town, \textbf{nobody} sets foot there besides dwarfish gypsies.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small "Turned out not to be that dangerous" After you heard that a German guy got mugged and seeing all the toxic waste outside of the apartments? I'm sorry \textbf{Bald} but you're being a bit too generous this time.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small If they were from India they would speak some \textbf{Indian} language, wouldn't they?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Niamh Butler What is that supposed to mean? Slovakia is a Central European country and a member of the EU. It's a normal developed \textbf{nation} which isn't that different from other EU countries. Plenty of other developed nations have problems with ghettos and gypsies or other marginalized groups of people. There are areas on the outskirts of Paris for example where you wouldn't want to walk around either.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small krispy kreme it's \textbf{nothing} to do with richness of the \textbf{nation} or lack of opportunities. Some people just chose this life and benefit from complaining about it.\normalsize   & \cellcolor{green!5}Nation, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small xDDDDD My friend had a \textbf{gypsy} who used to go in school with him. He was on court because of stealing from a shop. He also liked to roll cigarets in school (like when is math or any othet subject). There was also the story that his brother fucked somebody in a bush\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small His channel started in India. West Bengal and Kolkata needs a capitalist concept like Telangana and Hyderabad. The intellectuals of Kolkata are book worms which makes them ulnerable for \textbf{Communist} and Socialist nonsense... Also, the influx of Bangladeshis and villagers as beggars has to be limited. Maids and cheap labours are good and handy, but not useful if majority end up begging and homeless on the streets - and shitting on it. Case study: I own a house near Quest Mall! It is a \textbf{old} hospital with \textbf{doctors} having practices in it without contracts. Because of Socialist laws I can't kick them out and build a new one. Imagine, Mamata Banerjee was elected to stop Tata building a factory there ... Bengalis need to make their place better instead of denying how much can be improved\normalsize   & \cellcolor{green!5}Communist, Old, doctors & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Nationality - General & \cellcolor{green!5}3/136 & \cellcolor{green!5}2.206 \\  \hline
  \cellcolor{green!27}\small I paused at 8:30 to comment. This video is "strait fire" as the kids say, Mr. \textbf{Bald}. You and ol' girl have hit a stride which equally rivals the videos that made you famous. I have been missing the videos of \textbf{old}, but this is a supreme example of excellence. The kiddie party was questionable but understandable considering who shot it (the older \textbf{woman} breaking it up was hysterical). You and Ms. Video have definitely hit a stride which I once considered unattainable. Y'all freaking rock. Thanks again.\normalsize   & \cellcolor{green!27}Bald, Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}3/88 & \cellcolor{green!27}3.409 \\  \hline
  \cellcolor{green!5}\small Damn that was sad to watch , first the poor puppy in the corner in your first scene, you can see clearly the dog's getting beated a lot. And then a +/- 14 yr \textbf{old} boy talking about girls like that : they arent raised the right way obviously.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Best content on the internet, keep up the great work \textbf{bald} 🙏\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Great video. Its a bit like the aboriginal town camps of Alice springs here in Australia. White People will live in the town of Alice Springs all their lives and will never set foot in these all indigenous communities for rumour and fear of the camps being dangerous and unsafe places. Its the opposite if you ever do. A little hit of natural suspicion but you get left alone if you do. Great summarization at the end \textbf{bald} and Alinchik. Especially the part that the kids don't deserve to grow up in such abject poverty. Even if they seem happy on the outside.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small It's \textbf{crazy} hearing them all speak with accents from my area\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small that's czech they're speaking? weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small No offence \textbf{bald}, that kid's camera work is better than yours LOL he should have his own YouTube. Ps I love your channel keep on doing what you're doing ️:-)\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small 8:05 \textbf{Bald} for president of Lunik 9!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small 1:40 - you haven't even started drinking Mr \textbf{Bald}, yet you look already hammered. 1:56 - you recorded first video that smells, great success\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Wow, that's brave. This is probably the most danger he's put himself in. Next \textbf{bald} will be travelling to Venezuela.  :o\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small That kid said Ben is waiting on me... never knew Mr \textbf{Bald} was actually Mr Ben :o\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small they dont look \textbf{indian}, time to accept them in europe, and give them som,e chances\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Europe's largest \textbf{gypsy} slum is Stolipinovo in Bulgaria\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small 5:04 This kid who got a camera to film from a British guy visiting \textbf{gypsy} slums, with an \textbf{old} T-pain song playing is such a \textbf{weird} culmination of culturs and I love it\normalsize   & \cellcolor{green!5}Gypsy, Old, Weird & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/33 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I am also from Košice and i see Lunik IX. as a kinda taboo topic. There is a lot of prejudice among Slovak people about gypsies because it's not pleasant to see them doing drugs literally everywhere they are. But as this video showed there are some which are nice and know how to behave. Thanks Mr.\textbf{Bald} for another great video. Much love from Slovakia\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Great video showing the real world of abject poverty. It probably would be unsafe to stay too long until night, but you can safely go almost anywhere to have a short look if you're confident as bold and bankrupt to embrace poverty with everyone's attention on the rich English man. Asia and \textbf{African} countries will surprise those who risk personal safety to embrace poverty 3rd world self touring. As long as we have this corrupt global debt based economic system marginalizing the majority of people just trying to live their lives here on Earth, there's no remedy though they need to tidy up a bit for it's a rat infested disease and fire risk to let happen.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/117 & \cellcolor{green!5}0.855 \\  \hline
  \cellcolor{green!27}\small I just realized that you're Pewdiepie's favourite YouTuber Mr.Bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small as much as I like your videos, these people need to be removed from the earth... These people are \textbf{nothing} but a huge cancer to the earth.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Awesome work breaking Paradigms \textbf{Bald}. Thanks. One Humanity, One Earth, One Human Family.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I can see how it was possible to prohibit them from entering the Russian Empire. A lot of them look like they just left India last year, and it's been more than a thousand I believe. And they still have  \textbf{Indian} values when it comes to keeping public spaces clean.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small You're videos started being too short Mr. \textbf{Bald}. They used to be much longer. Great video though....\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small the \textbf{gypsy} are bad  and that is true . why do you think they have been run out of most places in europe .ask the Croats they will tell you\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Gypsys are not good people... everywhere they occupy they destroy. England has a massive problem with gypsys. Here in America they are very isolated as well and don't have a very good reputation. I know some families that have a bunch of kids and they go to a decent restaurant to eat and after they are done eating almost everything they call for the waitress and tell them that the food was not good and that they are not going to pay for it. They eat almost everything and then lie about the food not tasting good in order not to have to pay. The whole family is full and they just leave the restaurant. I know a few huge \textbf{gypsy} families that do that. Also, watch put for your belongings in your pockets when being around \textbf{gypsy} people, they are masters are pick-pocketing and will take your wallet out of your pocket or jewelry without you even knowing. Not all are bad but a good amount of the \textbf{gypsy} people are just not good people. I think it's a cultural thing.... look at how they live even in their own town and neighborhoods. They made a shithole out of it. All that rubbish and shit all over the place. They throw all that rubbish all over the streets and then live in it. That's disgusting....\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}3/226 & \cellcolor{green!27}1.327 \\  \hline
  \cellcolor{green!5}\small "\textbf{Gypsy}" are from India !!! I've heard this topic many times and read about it in Wikipedia !!!! Love and best wish to them from India ..... <3 <3 <3\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Great stuff as always Mr. \textbf{Bald} 👌\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small There a \textbf{gypsy} slums all over slovakia, it's not something you'd expect from an EU country it's quite sad to see this day and age\normalsize   & \cellcolor{green!5}Age, Gypsy & \cellcolor{green!5}Age - General, Ethnicity - Roma & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@Roosk1 While there are \textbf{Gypsy} slums in Central and Eastern Europe, there are \textbf{Gypsy} trailer camps in Western Europe (especially in Italy, Spain, Sweden and France)\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{bald}, you are a legend, sir. This is some amazing footage.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Big up Mrs \textbf{bald} she did a very good job in this video\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small That "Camera Trust" thing made me cry... Give these kids a chance...They are like you only! 😭\textbf{Bald} and Beautiful... Thanks Man..Love from India\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Fuck me \textbf{bald}, no bullshit at the end. You just tell it like it is.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Congrats \textbf{bald} super vid yet again the truth comes out and Europe shits on the young ,you can not blame them for being poor but one guy came from derby so why leave at least he would have social security housing and school......god bless you both\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Adults do the right thing..clean up all those rubbish...be a good example for the young generation... stop waiting for the authorities to help you...am sure most men in those complex can find \textbf{old} trucks to remove those garbage ...."where there is a will there is a way"\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Hi \textbf{bald}, how's your girl friends nose infection, i saw the \textbf{witch} \textbf{doctors} remedy, but had to leave real suddenly. Enjoy learning about Russia \& other places you visit.\normalsize   & \cellcolor{green!5}Bald, Witch, doctors & \cellcolor{green!5}Gender - Female age and physical appearance, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small Senior \textbf{Bald}, I hope you'll visit more places in Slovakia.\normalsize   & \cellcolor{green!27}Bald, Senior & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald} isn't that \textbf{old}! Next, Mr \textbf{Bald} would probably visit Petrzalka in Bratislava, because that place is known to be dangerous and full of gypsies. But when I was walking around Petrzalka myself, it wasn't so dangerous so Mr \textbf{Bald} might decide to give it a miss.\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}4/48 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small TheTruthIsFiction Petržalka isn't dangerous at all, however I suggest Mr. \textbf{Bald} to visit Pentagon in Bratislava - a place full of junkies\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Lmao Mr \textbf{Bald} is called senior\normalsize   & \cellcolor{green!5}Bald, Senior & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small hook ne up with a gypsie chick\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small After seeing so much unfairness in the world I wouldn't even be surprised if \textbf{Bald} leads the next great socialist revolution.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Heyya \textbf{Bald}! I‘m i love with the music! :-D got some  names for me?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small You're lucky you had that \textbf{chick} with you, without her, they would definitely have drilled your backside.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small bald England win the cricket world cup how u feeling now?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Bald, please visit every country in the world, if you can. You do a really great job at showcasing the various sides of every country you go to; great production value, great interaction towards locals, and lots of historical information as well. More power.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Amazing command of English by some of these people ,I have some stories ( personal experience ) with these \textbf{Gypsy} people in the USA but I'll not spoil the good vibes presented in this video.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small There are even shittier \textbf{gypsy} slums than Lunik 9 and they eat dogs frequently there. They will steal the dog from you and cook him. Or you can pay them like 100 euros and you are free to go with your furry friend. And after month it will happen again :)\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Bald with out boundries\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small and now some parts of the vid where the 14 year \textbf{old} kid was recording everybody ignored 'look at that ass''shut the fuck up im recording''look at her''come here bitch'lmao\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small today I learned even poor female \textbf{gypsy} children dress slutty.. must be a worldwide phenomenon\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Harald, Mr. \textbf{Bald} and Tim K are the three best travelers. hands down!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small but lets bring in tons of Africans and Islamist when a sizeable percentage of Europe has no problem maintaing the birth rates just let \textbf{woman} be \textbf{woman} again.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Slippery \textbf{gypsy}.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Kid on the left at 3:14 with glasses looks full indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Yes I feel most em are \textbf{Indian} DNA or \textbf{Indian} ancestors cuz of the look n facial structure and skin color ..  I think we need to help them to clean up their area and put some garbage bins.   And also educate them about cleanliness and about social status and bring them to front line of society...  It's duty of Slovakian's, Slovakian governments, local administrations and also duty of us the viewers..  , we should give them hope we should give them equal status..  They are humans too..   Peace..  ✌\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small BALD and Alina, going to these places is very brave of you guys. However, just please still be careful.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small So many people with \textbf{nothing}. Another camp, another country. How does it get solved. Maybe \textbf{Bald} since your exposing this horrific life for these \textbf{migrant} people, you can attempt to approach the leader of these countries, or at least the politicians. Follow the followers and likes. Thank you.\normalsize   & \cellcolor{green!5}Bald, Migrant, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}3/48 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small How many are searching Mr. \textbf{Bald} in the thumbnail??\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small So no one seriously noticed a guy in a \textbf{black} tee with a big ass white F * C K? Only me? Okay..\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small That's not true they get the chance in western Europe but they fall back into their \textbf{old} habits stealing\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small The world is an amazing place, thanks Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Slovakia look so poor and abandoned the buildings are deteriorated and the city look dirty, and those kids drinking \textbf{alcohol} wtf  is wrong with that people\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Middle of Slovakia and they all speak perfect English.  No doubt from having been here grabbin all the benefits they could. This is why \textbf{Brexit} is happening. Not to stop educated smart Europeans coming to the UK, but because working class people are sick of having to put up with Europes dross moving in and sucking the life (and money) out of town and cities around the UK, and turning entire areas into shitholes like that.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small One day Mr. \textbf{Bald} you might push your luck too far .Not everyone has the same mindset and honour think of the Scandinavian chicks who were murdered recently they thought all peoples were of the same mindset just be very careful .\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small what do you mean by pushing your luck ? those girls who were killed did not do anything to have it happen. as for being killed by islamic \textbf{terrorist} that could happen while living in the UK also. and in the US people can get killed while in their classroom or at a movie theater or just any other everyday thing like waiting for the bus.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald} did you 💩 outside?!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small 8:03 as a closeted \textbf{lesbian} in Russia if I went to a fortune teller and she made that mistake I'd shit myself on the spot\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small From Wikipedia:Lunik IX houses the largest community of Romani people in Slovakia. Although originally built for 2,500 inhabitants, it is estimated that the population is now three times larger. Living standards are low, with services such as gas, water, and electricity cut off, as the majority of inhabitants are not paying rent or utilities fees.Health standards are low and diseases such as hepatitis, head lice, diarrhea, scabies, and meningitis are \textbf{common}. Unemployment in the borough reaches almost 100 percent. The borough has one elementary school and a kindergarten.Luník IX is serviced by a bus line, which stops only on selected bus stops. Boarding the bus is only allowed through the front door. Due to frequent attacks of aggressive residents, bus drivers deployed on the line receive a hazard pay.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small Perfect work, \textbf{Bald} ;) I'm very impressed by Alina because she can speak czech language very well. Would you like to visit some Czech town or city? For example Ostrava. I like your videos so keep it up ;)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small No way, I'm from Derby we had some gypsy's on a patch of grass just down our street the other week this is such \textbf{weird} timing 😂😂\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small These kids are fucking smarter than some well schooled people I know!Thanks \textbf{bald} for the trip 🤙\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I was eagerly waiting for this episode! I shot a documentary about \textbf{gypsy} settlements in Slovakia a couple months ago and it was quite an experience. However bad it may look, the situation is getting better. Their mayor is a smart guy with a university degree and does everything he can to improve things. The crime rate decreased substantially, many people are getting new flats and they are working on taking away the garbage.By the way, if you want a really horrific experience, you should go to \textbf{gypsy} settlements at Svinia, Secovce, Trebisov or Chminianske Jakubovany. I've never seen things as terrible as there. You're basically crawling through human feces, 6 year olds are doing drugs in front of you, there are dead dogs rotting on piles of garbage etc. It's a very sad side of Slovakia and it's extremely difficult to find a solution to the \textbf{gypsy} problem.Great video as always by the way;)\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}3/157 & \cellcolor{green!27}1.911 \\  \hline
  \cellcolor{green!5}\small It would be cool if you Peter would show some \textbf{gypsy} settlements yourself. Big compliments to both channels of course :)\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Pppeter and \textbf{bald} and bankrupt u need to meet up guys and make video together about Slovakia. You both got great sense of humour and travelling experiences.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small It's so \textbf{weird} hearing a British accents from these kids. Very unexpected!\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small That boy is a small \textbf{bald} and not balder... Wish you could get back there and film for more. Gypsies are one of the most lovely people... Wish i can visit that place one of these days. Wish Alina can start her own channel as well, i'll be subbing it :)\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Mr.\textbf{Bald},if ever we contact an \textbf{alien} \textbf{race} you should be appointed ambassador from  Earth.\normalsize   & \cellcolor{green!5}Alien, Bald, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}3/14 & \cellcolor{green!5}21.429 \\  \hline
  \cellcolor{green!27}\small Has Alina visited England yet Mr \textbf{bald}. Show her around.  That be good video\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I like your channel. The best channel on you tube! Such adventures! You are so lucky. Traveling , adventures, new places, new people and you havd with you such a beautiful and smart \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Your government name has been exposed Mr. B. \textbf{Bald} ❤️\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Also Mr \textbf{bald}. What happened to Meeting Alina grandad part 2\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Me \textbf{bald} best YouTuber by far. Content is amazing.  Better than BBC could make. Please visit Poland Germany etc. \textbf{Old} Ww2 sites\normalsize   & \cellcolor{green!27}Bald, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Hope you'll check out some other places too.. Slovakia has much more to offer than a \textbf{gypsy} slum.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I once knew a one leg one eye gypsy…what a fun chap..accoding to the fortune teller aleanchick is \textbf{lesbian}...\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Ditto Chicago/Detroit/ETC  Slums ...each one features an MLK Blvd Shit Hole main Street....all Created, Run, and  Governed by Idoit \textbf{Racist} Democrats (\textbf{Black} and White) who have wasted Billions of \$\$\$ since 1965 telling us all the while they were going to "Fix" it...but it's all Donald Trump's fault now....Trump 2020. The only thing Democrats can "Fix" is an Election.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small Bald, love your videos.  I watch  Harold B and Tim K as well, Of the three, I would have to say that you are more  of the ladies man.  Love the strange and interesting places that you visit and the foods you eat make me hungry and jealous.  I  would love to see you and Harold do Cuba.  Oh  yes, take Tim K with you as well that man needs a \textbf{woman}. Keep up the good work! Just wondering if the ghandi topi would be a hit in the slums of Europe!\normalsize   & \cellcolor{green!27}Bald, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/92 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small A total inspiration Mr \textbf{Bald}.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Could have come to my estate I grew up on and never have to of left the UK; wouldn't have got the camera back though, nor free \textbf{alcohol}. Your wallet would have been used to pay for theirs though! Haha\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald} for president!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Fucking eh \textbf{Bald}. Gripping, and hard hitting content once again. You're probably the YouTube creator I look forward to the most.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small You can't get raped with the \textbf{bald} stud nearby \textbf{hun}. Boom! and i'm done commenting.\normalsize   & \cellcolor{green!5}Bald, Hun & \cellcolor{green!5}Nationality - German, Physical Identity - Physical Features & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Dam and i thought I live like bum\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small When is Mr. Bald's wedding?? He plowed that 23 or 24 year \textbf{old} girl and he fell in love. He hasn't left her side since he hit it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small people in the comments acting like gypsies r new to europe or eastern europe...are u \textbf{dumb} this isnt a new problem theyve been arounds for hundreds of yrs lolll\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Wooooo this was a great video, real aye opener , seem nice people and happy, your got balls mr \textbf{bald} , best video I've seem in a long time ❤️👌👍\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Bald my question did you fellt scarry in this district and how much did you had in your wallet\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Chutiye \textbf{ho} kya bhai! Phli civilization jahan toilet construct ki gayi, systematic system bane sab India main hai.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Rahnee K This is bullshit, this "real people" a very small minority in the slovakian society, and all other parts of this society are full with "real people": The main philosophy of this channel, to showing people on the edge of the society, and abandoned, halfly destroyed \textbf{old} \textbf{communist} buildings, or ghettos in third world places, like India. This didn't mean, only the poor people are "real people"!\normalsize   & \cellcolor{green!27}Communist, Old & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small president Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small It's all IQ and it's a tough fact Europeans have yet to face despite hundreds of years of issues with this single group. Some data from Metapedia's Gypsies article..:Several studies of the IQ of Gypsies have found average IQs ranging from 70 to 83.[9]The average IQs of Gypsies in different countries have been stated to be 85 in Slovenia, 83 in Slovakia, 70 in Serbia, and 60 in Romania.[7]A 2015 meta-analysis stated an average IQ of 74.[10]During a Slovak study in the 90s, 23 510 children in the \textbf{age} of 6 – 14 years in the district of Banská Bystrica, Slovakia, were given a Wechsler Scale test. A total of 510 children (2,16 ) were diagnosed as mentally retarded (with an IQ 70 or less). 0,9  of the non-Gypsies were diagnosed as mentally retarded, as opposed to 21,5  Gypsies. Although the \textbf{Gypsy} children constituted only 6  of the testing sample, they counted for 60,7  of the mentally retarded. [11]Many attempts to improve the living conditions and/or integrate the Gypsies into the larger society has been tried. Sometimes these attempts have involved the use of force in order to settle down, educate, and assimilate the Gypsies. All such attempt have been stated to have been without success.[7]In Central and South-Eastern Europe, an average of 46.8 percent of Roma families receive social assistance; 56.8 percent receive child support payments. In Bulgaria, 90 live on state benefits. In Britain, their "skillful manipulation of [the] benefits system has brought an outcry from the media, police, and charities for the homeless."[7]One reason for migration to Western Europe has been stated to be much more beneficial welfare systems.[17][18]The \textbf{Gypsy} population continues to grow rapidly. \textbf{Gypsy} girls traditionally marry between the ages of 14 and 17. Fertility is high: 3.0 children per \textbf{woman} in Bulgaria, 3.03 in Serbia, 3.12 in Hungary, 3.2 in Bratislava, 3.3 to 3.7 for 'some' groups in Romania, 3.9 in Croatia, and 4.3 in Eastern Slovakia. This can be compared with 1.1 and 1.4 children per \textbf{woman} by 2000 in former \textbf{Communist} countries.[7]\normalsize   & \cellcolor{green!27}Age, Communist, Gypsy, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Age - General, Ethnicity - Roma, Gender - General & \cellcolor{green!27}7/352 & \cellcolor{green!27}1.989 \\  \hline
  \cellcolor{green!5}\small i think demonizing the community isn't the solution.  i would have liked to have seen you (mr \textbf{bald}) ask them what are their aspirations and dreams and goals.  try to understand why they are taking drugs, \textbf{alcohol}, smoking, possibly sexually active.the one's that do manage to get out of that society should be supported by people everywhere and not persecuted as they are.  everyone has to work together to make changes.\normalsize   & \cellcolor{green!5}Bald, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Physical Identity - Physical Features & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Been a big fan of Mr \textbf{Bald} for a while now and he's inspired me to get out and see some of the more ‘off the grid' areas of European culture and history. Ended up booking a cheap spontaneous flight to Košice and went there last week, not knowing much about Slovakia at all. We got a tour ‘authentic Košice' which was a fascinating insight into the area's raw past and struggle with Soviet occupation, as well as showing us an abandoned factory and bunker. On our tour in a 1985 Skoda (which we were allowed to drive) we passed through Lunik 9. It was like a warzone, and t left a huge impression upon us. Hot water and electricity was turned off by the council, people were throwing sewage off their balconies with children running around. As we turn the corner a gang of men were out in the street and stuck their fingers up at our car as it went by, basically saying a big ‘fuck you' to tourists. It was quite dangerous - if our car stopped we would've been battered alive! I actually filmed a video of this myself to get my own blogging/documentary making going which I need to edit. Then I get back home and load up YouTube and what do I see a week later - mr \textbf{bald} has done a video here! Unbelievable, I cannot believe how much balls this guy has to come here. Despite what he says it was dangerous as hell, and we blended in with our really shit car. Legitimately this man is risking his life to show us how people live around the world in places which escape western media attention. A massive hats off to this video and I'm also low-key gutted I didn't see Mr \textbf{Bald} out there!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}3/303 & \cellcolor{green!27}0.99 \\  \hline
  \cellcolor{green!5}\small Damn right he's off the grid. I was in Kosice. Mr \textbf{Bald} is trying his best to make it look like Russia and the other dirty places he's been to. The fact is, Kosice is a nice looking quiet town where most people speak English. Stay in the centre of town and you're fine. There are some American tourists walking around too. I walked around the streets through several areas of Kosice and not once did I feel any danger. Slovakia is in the EU so it isn't so bad. I didn't meet any gypsies when I was there.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small you probably paid the dad of the kid which you gave the camera no chance he did that without payment or a bottle of vodka try the same shit in uk germany anywere in europe and dont have to be \textbf{gypsy} whatever 90 will take ur cmera\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small It's \textbf{crazy} to think that \textbf{Indian} nomads ended up in Slovakia 😂\normalsize   & \cellcolor{green!5}Crazy, Indian & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I wonder if the gypsies who were educated in the uk were evicted back to slovakia? It was \textbf{crazy} to see them speak UK slang English in Slovakia😂😂\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Another inspiring look into the way others live makes you appreciate what you have ✌ 1 million subscribers soon well done mr \textbf{bald} ❤\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Bald, did you fuck that cutie?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Well, nice video as always but please, do not get final thought from these seeing that all \textbf{gypsy} slums are non-harmless as this one. If you'll ever travel through country Slovenia in Europe, try to visit our country biggest and most dangerous \textbf{gypsy} slum called Zabjak in Novo mesto area. Immediately when they will see you're coming towards them with a camera, they will start throwing rocks and come on you with axes and bats. Everyday criminal there, drug dealing and similar activities are just their culture and beside that no body in country does not take care of this, everything is presented to public that is under control. But is not. Far from control. New challenge given. :)\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/119 & \cellcolor{green!5}1.681 \\  \hline
  \cellcolor{green!27}\small \@\textbf{bald} and bankrupt it's a greeting like hello but it means what's going on\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small This place look exactly like the one in Chula Vista California whatever I used to lived there  in an apartment complex and there were a lot of motherfukers  Mexicans and \textbf{black} ghetto children they were all on Welfare and fighting with each other everyday and smoking Marijuana so three months later we moved from there to La Mesa which is  very beautiful place now we own a beautiful house  a\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Welcome to Slovakia, \textbf{Bald}!!! Here is a greeting for you \& Alinchik from a fan in Bratislava! I didn't expect you to come here so I am really happy to see this! You already left an amazing trace and did what only a very few people here would dare to do. To show Lunik 9 without prejudices and with human touch. My hat off to you. And Alinchik's Czech is great!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small yup. If he went alone it would have been a very different story. This video is quite dangerous: gives you the idea \textbf{nothing} can happen to you. Think agan.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Bald and bankrupt love Goran Bregovic for sure\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald} I love what you do please don't ever stop all right live life vicariously through your eyes and camera because I only wish I could do what you do I literally can't wait to see your next episode I wish you posted every single day and I love your knowledge of the areas\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Fantastic footage once again! More content like this- interacting with people and not just abandoned \textbf{old} buildings haha peace\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I love your series and love your vlogs, \textbf{Bald}....but!  I'm getting dizzy trying to keep track of your travels such as Georgia to Slovakia..that's my problem, though.  Don't ever stop!  Alina seems to be gradually becoming an accomplished vlogger and more and more active as a part of this whole adventure experience.  That is a very good thing, by the way.  (Alina is also much, much easier to look at than you, \textbf{Bald}....no offense, mate.)  smiles\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small This is next level vlogging. Handing your camera over to the kid was both reckless and awesome. Aline the interviewer brings another angle. Earlier I watched the one back in Minsk where you take her and her sister (?) to the only \textbf{Indian} restaurant in Belarus. You definitely came out well from meeting Alina, my friend.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Big balls mate really interesting video.I get myself in some \textbf{crazy} situations when I travel at times by myself but would be worried with a \textbf{woman} as got to keep her safe how do you feel about that?\normalsize   & \cellcolor{green!5}Crazy, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Racism is ingrained into the veins of Europeans\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald}, Hungary is short drive from Kosice, in fact it's right on the border, Kosice used to be a Hungarian city.They have slums too, drugs, crimes and prostitutes infested, They got them ALL!!!! Also have \textbf{gypsy} slums in the IX. district (Ferencváros). Or just walk around the Eastern Railway station (Keleti PU) and meet wonderful druggies zombied and homeless using the streets as their personal toilets.\normalsize   & \cellcolor{green!5}Bald, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Bald deserves to be YouTuber of the year!! He's going to all theses \textbf{crazy} places just for our amusement!\normalsize   & \cellcolor{green!27}Bald, Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small \@Scifi FantasyGirl I love learning.......I question the established media, even if it is National Geographic etc., they all have an agenda.  \textbf{Bald} and Alina's videos keep you returning for more.   I hope they always remain safe.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I hope you visit Hungary next, Mr. \textbf{Bald}. Am 22, born and raised here and Budapest is an awe-some place to visit. Would love to show you around. :DNot to talk about how everyone says Budapest is the most affordable place for tourists.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small The "BEST VIDEO SO FAR" Top Man \textbf{Bald}......  I bet you used to go to "Sterns in Worthing" HAA\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small mr \textbf{bald} has the same jacket as me\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Infornografista Nah, just don't go to \textbf{gypsy} slums\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Jinky Yeah, I don't necessarily agree with that. Once someone born into a slum there is a good chance they can never get out. Nearly impossible. But the few gypsies who do get out have to deal with \textbf{racism}, embarrassment and discrimination on a daily basis.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Good on you \textbf{Bald} for what you did - !!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Alina is so cool man (and very pretty too). Wouldn't mind seeing her in every video for those 2 reasons. Anyways \textbf{Bald} thanks so much for providing me consistently with great content to get high to. 🙃\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Can't believe that you visited my hometown \textbf{Bald}! Wish I would have been able to meet you guys. Too bad you didn't show the rest of the city, so that people could see it's not only slums like Lunik 9, but sadly that is one of the most interesting parts of Košice 🇸🇰\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Great to see you back near me. I went to Slovakia near Hungarian border east of Kosice, called Chlmec. They have a lot of \textbf{gypsy} as we do in Romania.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small The Slovakian government needs to just level the damn thing. Those people aren't doing anything productive like getting jobs and all there's like 100 unemployment.  They need to find work and the Slovakian government need to build regular housing for them. Not some damn Soviet style apartment. What hideous conditions. Worse than Dharavi slums! Everything I read about this place is bad. These people should do better and make themselves into productive members of society. Clearly the social welfare the state gives them is squandered on drugs and \textbf{alcohol}. I hear disease is rampant too. Never catch me there...  "They make the most of terrible situation"...a situation they created.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small U need to buy that kid his own camera o we can see more of his footage lol great content \textbf{Bald}!!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I thought mr \textbf{bald} was recording 13 and 14 year olds shaking their ass thank god it wasn't it was another kid filming them makes it more understanding lol\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small alinchiks gonna marry a \textbf{woman} president. hahahaha\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Just like every \textbf{old} Hungarian city.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Em JHu Why would I care what you think?Why did you even mention Hungary to begin with? Oh I know; you're pulling some bullshit that Kosice is somehow a Hungarian city (and \textbf{nothing} great).So you're probably some Orban-voting Hungarian nationalist piece of shit idiot who has a big boohoo every "Trianon day".\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small \@Daniel Eyre Congratulations, you"ve got to be a pleasant person! :)1. I did not mention Hungary.2. Kosice (ie: Kassa) IS an \textbf{old} Hungarian city.3. You have no idea about my vote.4. You would probably feel comfortable if your city was attached to a non-existent country by the decision of some lousy politicians.5. You DO seem to care about what I thought. ;)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small \@Daniel Eyre Well, it was non-existent until 1993, and Czechoslovakia even more certainly was at the time when this decision was made.You know \textbf{nothing} about history, \textbf{chauvinist} arsehole.\normalsize   & \cellcolor{green!27}Chauvinist, Nothing & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small The base of their culture is nomadism. Being romani or ciganos (other type of gipsies living in south europe) they all share nomadism. The discussion should be if europe wants to respect their culture or to impose certain values (example for young \textbf{woman} marriage) and living in society. If they acept them living in those buildings they should at least teach them. That is called integration. Great video. (*reading some comments I must assume that many europeans really don't understand the gipsies)\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small I am addicted to your travel vlog... question mr bald: are you visiting the baltic \textbf{nation} and, or plan on visiting the Baltics?\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Those kids sound like they are from London it's crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I'm sorry to say that the Lunik 9 situation in Slovakia, is very similar to the Aboriginal situation in Australia. Although the billions of dollars in welfare money, free healthcare, housing, and education thrown at the problem in Australia, would be much greater. Yet the slums, rape, general crime, violence and \textbf{alcohol} problems remain.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small \@Mr.Magnussen The trash is equally part their problem, they generated it. Even if the government didn't place bins  dumpsters for pick-up, the people should at least        make and effort to clean-up their own filth. For what the community spends on booze, cigarettes, and drugs they could pitch-in for an \textbf{old} dumpster        and burn the mess or dig a pit and burn it for that matter. Lazyness is no excuse but you can blame the government all you want it's all good.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small WOW. Amazing footage, \textbf{Bald}. This reminds me a LOT of the favelas we have in Brazil. I had no idea this kind of places existed here in Europe.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Wow, this footage is so interesting.  But you have one mistake in your translate: when you asked if their kids have any chance to live outside of Lunik IX, the man said "\textbf{zero}", but \textbf{woman} said "they could have". So there is not as much pessimism.I was there too when i ived in Košice town. Just to observe and see that legendary place with my own eyes, i was little scared but having \textbf{nothing} valuable i had \textbf{nothing} to lose. They were a bit aggresive but it was just verbal which is no big deal. However i can imagine being beaten up or robbed because as there are many such cases.  I know about few settlements that are poorer than this one, but they are located on countryside in eastern part of Slovakia far away from big cities. Anyway Lunik IX looks to be really the biggest "slum" in our country.\normalsize   & \cellcolor{green!5}Nothing, Woman, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}4/152 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small hey \textbf{bald}, what is your current location?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small ahahahhahah in Bulgaria we have \textbf{gypsy} (roma) "slums" with more than 50000 people. Prob in Romania as well. This place is clean and orderly!!!!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I actually found Luniks IX, Slovakia on Google maps!  That was a surprise! Good \textbf{old} Google maps to keep us going!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small So many of these children spoke english with a native accent but I bet an equal amount speak french, italian, spanish.  Why? Because they are taken to these countries to beg, steal and register for benefits then return to their family home.  Their homes are all pristine inside as they live off their illicit earnings (child support from several EU countries) but they have \textbf{zero} civic pride so throw literal shit out of their windows. Their whole culture is built on taking what they can get and giving \textbf{nothing} back.\normalsize   & \cellcolor{green!5}Nothing, Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Wow they actually look \textbf{Indian}...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Just dirty people, no wonder why \textbf{nobody} wants them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Wow \textbf{Bald} \& Alinchik, i always wondered what gypsies that ran out from India some 1100 years back to different parts of Europe, looked like. I am surprised that they more or less look Caucasians at this stage. Though there were few distinctive \textbf{Indian} features in some but most looked white. Also this roma tribe is world famous for creating garbage and then moving on to the new place, concept of permanent settlements, working hard for better future, do not fall in their dictionary. You can't help a tribe if they don't want to help themselves.\normalsize   & \cellcolor{green!27}Bald, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small They would do \textbf{nothing}. They are waiting for someone else to clean up their mess.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Impressive video Mr. \textbf{Bald}. This was had a lot of production value especially with the kid going to the party with your camera. Many people will see this video and hopefully NGO or governmental organizations will do the right thing at least for the kids.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Guess being drunk and Lucky counts for something. Mainly your camera returned and your girl unmolested. Be careful \textbf{Bald} or play the damned lottery dude!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Great clip! I lived and in Hungary and Romania in the late 90s and visited similar places (shock tourism) and most of the time people were super friendly. BUT you gotta be careful in some places. Cheers \textbf{bald} and alinchik :)\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small lots of gipsy s lived  live in UK and London.. fake "refugees".They had a free apartments in 2 -3d zone paid by government, food stamps, pocket money, gipsy women steal money on streets. At the same time white  \textbf{black} British guys work 10-12 hours per day and live outside of London as they can't afford to live in downtown\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small A place of total Anarchy. And I believe what you were told...it IS a dangerous place. They were all just friendly and nice for the camera. The Adults cut the 'party' short because of the camera!  Otherwise they just allow that chaos with those kids! Try living there a week or so, you'll lose all you have. Maybe even your life! I know the mind of the \textbf{Gypsy}, it's sly and deceptive!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small LoL this is how you invite mr.\textbf{bald} 🤣\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small vijay mn really you dare him and he is there. \textbf{Nothing} can be more dangerous than Mr. \textbf{Bald} 👨‍🦲\normalsize   & \cellcolor{green!27}Bald, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bankrupt Uruguayan Twitter's  1 trending topic last week was USSR (URSS) you should definietly come.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I let all the ads playthrough. Support mr \textbf{bald}....wheres balder?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Na, the biggest \textbf{gypsy} slum is in Skopje, Macedonia.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Those kids or youngster they speak fantastic English and they seem happy and welcoming shame this goes on in today \textbf{age} a fantastic video Ben 👍\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small It's sad to see these kids have \textbf{nothing} to do but... get involved with each other.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Gypsies are the lost tribe of judah. And if you wonder why they are not called jews anymore read the bibel jeremia 42 forward. The onley forever opressed people in the world without no own \textbf{nation} backing them exept God himself. They have never submited to no kings or goverment becuse Jesus is their king amen, thats why most nations hate and fear them. Hats of to you \textbf{bald} and russian girl for going there and having a good time.\normalsize   & \cellcolor{green!27}Bald, Nation & \cellcolor{green!27}Nationality - General, Physical Identity - Physical Features & \cellcolor{green!27}2/80 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Bald Im watching you for a quite a while now, having fun of these under developed countries of eastern block you visit,... I would have never imagine you would visit my own country.,....\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small So after getting through half of the video i felt the need to start a presidential campaign for mr \textbf{bald}. Progressive lance could be your vice?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I think it's time you renamed your channel \textbf{bald} and beautiful ;)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small They never robbed you, They were scared of you, Bad ass \textbf{bald} man \& no money\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small If i kick a \textbf{gypsy} how many points do i get?  (Side note...remember to change shoes before kicking my dog. Dont want to get the dog sick)\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Come to Holland I'm half Indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small BALD! come to Hungary, I can show many places like this unfortunately. Same situation with gypsys as well.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small No 1 u tuber mr \textbf{bald}...take not harold the market man\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Cool! But you should proceed to the Czech Republic and visit Chanov, which is a much more interesting \textbf{gypsy} slum than Luník. It's on the outskirts of the city of Most and last year there was even a hugely popular TV series about it called Most! 😀\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Whrn i see a \textbf{gypsy} i judge the \textbf{gypsy} by his ability to dodge my fists and kicks 👊\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small \@Андрей Нико no. Where im from it is best to yell at gypy before striking a \textbf{gypo} by yelling you are lilly to scare away other starving \textbf{gypsy} offspring\normalsize   & \cellcolor{green!5}Gypo, Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small It's hard for me to wrap my head around \textbf{gypsy} culture.  Everywhere the live is dirty, poor, and very few are educated.  It truly can't be the government, whom they are always blaming. So what is the deal?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small It isnt the goverment. Here in Slovakia, lots of them are given brand new houses for free and literally destroy them by month. But I know a lot of polite and good gypsies who work and live like normal people. The people showed in this video are sadly the 90 of slovak \textbf{gypsy} population which just live off goverment money. The problem is probably in their mentality.. But I hope that when These kids grow up, they will become a part of "normal" society and live normal life in Kosice and not in this shithole their parents created. Becouse even when the guy in video said they will clean the place in 2 months, i dont really trust him.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/119 & \cellcolor{green!5}0.84 \\  \hline
  \cellcolor{green!27}\small MASSIVE inbreeding problem, \textbf{gypsy} people can only marry other gypsies lol.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Mutual Altruism the inbreeding explains the lowered \textbf{mental} state/IQ. Fact remains that \textbf{gypsy} communities in EVERY country act the same even when presented the opportunity to leave their \textbf{old} ways behind and adapt to modern life. As you can see they start drinking at the \textbf{age} of 10 which further shrinks the brain, combine this with marrying your niece/sister and the problems at hand are not ''omg so complex its uhhh socio-economic factors''. You have obviously never met a \textbf{gypsy} community have you?\normalsize   & \cellcolor{green!5}Age, Gypsy, Mental, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/83 & \cellcolor{green!5}6.024 \\  \hline
  \cellcolor{green!27}\small \@Alis opportunity to leave their \textbf{old} ways behind? There's millions of slavic people all across eastern europe who are just as desperately poor  as a result of the economic situation and find themselves struggling with unemployment, etc. These are issues which occur predominantly as a result of the type of society they are within,  not because of some IQ reasoning. You know who else thought slavics and gypsies were inferior and had low iq?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small Mutual Altruism Yes and even the poor Slavic people hate the gypsies, that should tell you something. At the very least Slavic people work hard and the hooked nosed tribe people are very sneaky and crafty when stealing your money. Gypsies just steal your shit where u stand. They will never change and adapt civilization, hope you meet a \textbf{gypsy} community one day and you will experience it first hand. Its a sad thing honestly. My intentions arent \textbf{racist}, I hate all people equally.\normalsize   & \cellcolor{green!5}Gypsy, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Mutual Altruism but still poor slavic people will not shit inside their apartment building to the floor, throw garbage outside of window and give pack of cigaretters to 4 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small A.P.B ! Just like \textbf{black} people.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@John Jordan well when you fuck your sisters and brothers there are bound to be \textbf{mental} challenges. Fact.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Not even close to the biggest \textbf{gypsy} slum. The biggest \textbf{gypsy} slum is where I live, in Plovdiv, Bulgaria and it's called Stolipinovo. You can google it\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small It's \textbf{crazy} how many people still live in Khrushchyovkas today.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small needs to be upvoted so that mr \textbf{bald} will see it in time :/\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I disagree. I've been to Kosice and parts of it look very good. There are parts which are bad of course with \textbf{black} buildings and poor people hanging around but the centre of Kosice is good and I enjoyed my time there. It's a perfectly safe place. I wish I could live there! The people speak English so there is no language barrier.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Where are these people from ? Are they \textbf{ethnic} slovakians ? Don't look like Indians\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small LauraTheOwl Yes that would be good to have a few drinks with \textbf{Bald} \& Alina. Can I ask you one question please? Do you think the \textbf{gypsy} children go to school?\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small All \textbf{gypsy} settlements around the world are the same, and they will never listen, care and learn. Disgusting.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Go check the famous rapper foukme gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Stalin tried to fix the \textbf{gypsy} problem, even he failed. They separated some hardcore \textbf{gypsy} clans, gave the children a lot of education, gave them good jobs....after 4 years when the Stalin investigators returned to Moscow they reported that everything was gone, gypsies have robbed and stole everything and disappeared. They are born believing that the world owes them something\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small these are almost \textbf{african} slum level, \textbf{weird} that one apartment was all nice and clean, it's probably the \textbf{gypsy} boss house lol\normalsize   & \cellcolor{green!27}African, Gypsy, Weird & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/22 & \cellcolor{green!27}13.636 \\  \hline
  \cellcolor{green!5}\small Bald will be president!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Congratulations, another British guy or a "westerner" coming to Slovakia to experience the \textbf{Gypsy} problem for himself and to tell us Slovaks how \textbf{racist} we are for not wanting to have these people around us anymore, ( because we tried many times before, it never worked out). Spending 2-3 hours in Lunik IX surely is enough to understand how innocent the gypsies are and how all us Slovaks are filthy Nazis for giving up on gypsies. I wonder if you're going to stick around Slovakia for longer so maybe some Slovaks could tell you how it really is living 24/7 in a Slovak town terrorised by gangs of \textbf{gypsy} kids, teens, women and men all and any of them, the robberies, the killings of grannies for 10 euros, the torturing of pets by \textbf{gypsy} kids, the beating of rail conductors and passengers on trains, the slicing of young men's head with an axe for telling drunk gypsies off, and much more terror every day throughout central and eastern Slovakia. But surely a lifetime experience of Slovak people with gypsies is \textbf{nothing} compare to the 2 hours of a British guy seeing smiling kids in a city block with brand new cctv installed and police station just stones throw away. This image you made in your head during the short visit is definitely the accurate picture of the situation, come on give your head a shake.\normalsize   & \cellcolor{green!27}Gypsy, Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}5/235 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Baldy, you didn't need to go all the way to Slovakia to film this. They're already in England. Hence \textbf{Brexit} !!\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small This is why this channel is awesome, always something unique. The history of the gypsies is an ancient and mysterious one. Great Job Mr. \textbf{Bald}!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Alina has gotten good on camera, she is fearless, and she also provides another angle for the people they meet to like them than \textbf{Bald} alone would.   \normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Nice one \textbf{Bald}  that was eye opening\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Some hardcore footage alright! Here in Bulgaria the \textbf{Gypsy} slums/houses everywhere look similar. Some small villages are exclusively inhabited by Zigani, as they are called in Bulgarian, all other people left. Why do these people not give a flying fuck about their surroundings? In a BBC documentary 6 or 7 out of 10 \textbf{Gypsy} young boys said their goal in life was to become a pimp! WTF!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small The goverment actualy does clean it up regularly. They send in buldozers and containers to pick up tons of trash. But the locals dont want to pay for trash colletion and they just throw trash out of the window. Typical \textbf{gypsy} behavior. Also it wasnt always a slum. They lived in huts before and goverment built these apartment buildings and relocated them. But gypsies destroyed the buildings, ripped out windows and anything that they could sell. To a point when the goverment had to demolish a building because its statics were compromised because they were removing and selling rebar from the walls.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small You see happiness is not the circumstance at all. This community of people is still a community that communes. Gathering together as a family, a loud \textbf{crazy} vodka fueled family, but they make the best of it.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small How do they know such good \textbf{c\textbf{hav}} English when they live in Slovakia?\normalsize   & \cellcolor{green!27}Chav & \cellcolor{green!27}Nationality - Irish, Social Class - Working class & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small GOOD one \textbf{Bald} and Alina\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small when you gave your cam to the little gipsy kid it definitely started to get \textbf{weird}...\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Bald \& Alina have a lot of charisma and personality that allows them to be accepted wherever they go.  They make friends very easily.  Just because \textbf{Bald} \& Alina had no issues, I would not consider going to these places as safe and don't worry about it.  That would be very naive in my opinion.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small Bald getting really \textbf{bald}!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Trutst me it isnt ,european \textbf{ethnic} are way worse\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Two months to clean up their own filth? With all the people milling about doing \textbf{nothing} in that video they could get it done in two weeks. But it appears they don't mind living  in the stench of rat infested squalor. What ever floats your boat.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Hi you said something about Kolkata ....nowhere in Kolkata is like this \textbf{Bald} ...btw did you visit Kolkata ..never seen any videos on the city ...or is it just a perception.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small When I visited Bulgaria for the first time about 10 years ago I went to a similar place outside Sofia. Speaking to locals the story they told was that the \textbf{communist} authorities built flats for the Roma but the Roma then turned the area into a rubbish dump. So everyone left the Roma to it.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small your future husband will be the president of \textbf{bald} people\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small 🍁This vid is some \textbf{crazy} dope man! Well done \textbf{bald}!\normalsize   & \cellcolor{green!27}Bald, Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Me and my girlfriend are watching this on my mobile in a hostel in Kerry, Ireland. Love you \textbf{bald} x\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Great content Mr \textbf{Bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I'm amazed by the fact that all the kids have been in England for most of there life, what made them go back? Don't tell me its \textbf{brexit} because if you're in England for 5 years you are eligible to stay.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Alinchick can't do interview, \textbf{Bald} Please takeove hahaha.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hey Mr. \textbf{Bald}, I'm glad you came to Slovakia and I can see your perspective on our country.I really hope you're going to visit some other places in Slovakia aswell... kinda sorry for this "place" ... If you'd like to have some places to visit reccomended just say so and ,I deffinitely can help you up with that.Also you got few words not correctly translated. For example  3:33: The man said they got "\textbf{Zero} chances" ,but the \textbf{woman} said "They got a chance".\normalsize   & \cellcolor{green!5}Bald, Woman, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}3/85 & \cellcolor{green!5}3.529 \\  \hline
  \cellcolor{green!27}\small Don't go to Most. Mr \textbf{Bald} would probably make Bohemia look like Russia. Decin and Liberec are better, if you want to go to that part of the country.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Wondering where \textbf{Bald} will be next ? Turn out he is in my city, OMG. To clarify your visit, there used to be more Apartment Blocks, but because of safety violation, they were torn down, turn out stealing iron from your own building is not such a great idea. Garbage pile outside, was cleared multiple times by City Government, but they keep throwing garbage outside via windows. Building in the end of your video is school for children, multiple charities are working with people, and as a citizen of Kosice, i can tell you, we are trying our best, to give them jobs, but it is difficult to hire them without education. If you are still in Kosice, reach out, beer is on me.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/124 & \cellcolor{green!5}0.806 \\  \hline
  \cellcolor{green!27}\small HAHAHA hell yea \textbf{Bald}!!!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Please stop going around with that girl! I want the \textbf{old} Blad videos!! She is annoying\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Wow amazing Mr \textbf{bald} 😀 you can't judge a book bye it's cover,  I feel overwhelmed bye how friendly the gipsy's where , hopefully the future will bring some hope for all the kids ,I've been to Slovenia myself you should try the pestonya caves in Slovenia caves Mr \textbf{bald} 😀 great and interested place to visit, you will see the stalagmites and stalactites and you see on the comes together named a Piller well worth a visit mr \textbf{bald} ✔️👍\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}3/81 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Holy hell \textbf{bald} 👨‍🦲🤣🤣🤣\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Oh man, I just figured something. Imagine a collaboration between mr. \textbf{Bald} and Ross Kemp! That would make the entire Internet collapse! Two \textbf{bald} badasses touring the shittiest places in the world! After that, there would be no more Youtube, it would be impossible to top that and everything else would just seem meaningless. Maybe it's better if it didn't happen.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small I don't think Mr \textbf{Bald} is a real badass the way Ross is, but who knows.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small It's going to be after we clap them \textbf{alien} cheeks in Area 51\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Nobody is going to fuck with you, you have La Femme Nikita as your side kick!\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small It's really \textbf{weird} how good English they speak. What do they do for cash?\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Bald, seriously, if you dont marry that girl i'm going to go whenever the fuck you are and im gonna punch you in the gut and slap your \textbf{bald} head\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Wow, a \textbf{gypsy} ghetto!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Aaron Turner India is more dirty than Africa . this place \textbf{bald} visited was more dirty than many parts of africa.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small bald u should come to austria\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I don't know why They look like \textbf{Indian} and Pakistani..... May be they are migrants\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I clicked this video so fast. I remember learnng all about Lunik IX a few years ago \& being fascinated by it to this day! Thank you for this Mr \textbf{Bald} :)\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small After going to the Exclusion Zone, \textbf{Bald} fears no one anymore\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small 9:06 As much as I want it to happen, I can guarantee \textbf{nothing} will be done\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small It's a difficult situation, because  \textbf{nobody} is talking about the ten thousands of Sinti and Roma people living in normal houses and having normal jobs. But those East European gipsy are a different culture. When Bulgaria and Romania became Schengen-states, many came to Western Europe. Here in the neighbouring town of Duisburg they rented whole houses. In no time they looked like Lunik IX. I remember a live reporter on TV, when during he was speaking a window opened and the shell of a water melon flew out of the window just on the street. That does not work, and that makes it very difficult for us to accept them as they are. But again: They are not all like this! Most have normal jobs and normal homes, and  only sometimes you can hear it from the family-name that their ancestors were gipsy.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/143 & \cellcolor{green!5}0.699 \\  \hline
  \cellcolor{green!27}\small They look more like \textbf{L\textbf{G\textbf{BT}}} community rather than bad guys.\normalsize   & \cellcolor{green!27}LGBT & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}3/10 & \cellcolor{green!27}30.0 \\  \hline
  \cellcolor{green!5}\small B\&B, when is the Elena \textbf{Bum} Shots Compilation video being released? There'll be over a million views in no time!\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small taco cat Their family in western europe probably send money back for stuff like that, but its still \textbf{weird} how some of them have suits while living in a slum\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald} Kolkata is not as bad as what you think when u compared it with lunik 9 . Please visit Kolkata again and change ur comments please.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small There is an award-winning documentary called "Paradise Hotel" (available here on YT) where they follow a group of gypsies in Bulgaria. The government wanted to help them so they built a block of flats for them to live in but now that block looks pretty much identical to this place. In the documentary they even admit that their living conditions are their own doing. It's not \textbf{racism} or \textbf{xenophobia} that have them living there, it's their own laziness.There have been a ton of programs, both government, NGOs and EU to "help" these people but \textbf{nothing} has worked. These people know that if they just stay put some bleeding heart leftist will come running with a fist full of cash to hand them.These people don't need another program, they need a kick up the ass\normalsize   & \cellcolor{green!27}Nothing, Racism, Xenophobia & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Nationality - General & \cellcolor{green!27}3/136 & \cellcolor{green!27}2.206 \\  \hline
  \cellcolor{green!5}\small Get the kids cleaning no. 1 - Pay them.Get them education no. 2 -  All those \textbf{old} books we have, start a library Get them farming no. 3 - I wanna see home grown veg, allotments, bee hives, cheese etcStart micro businesses no.4 - I wanna see them selling, sell, sell, sellI wanna see there self esteem up, how can you motivate them? Any ideas?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Even \textbf{black} poor areas in the US are not like that. Nor poor white areas.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small When I read "biggest slum", I went. Right, must be \textbf{gypsy}.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I hope Alinachick is coming to Russia with \textbf{Bald} when his visa gets issued.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Very interesting for an \textbf{Indian} like me who hasn't visited Europe. No wonder the EU is justified in their urgent concerns for restoration of democracy in Afghanistan. Then of course they will clean up their backyard and bring social justice...\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Oh sweet Jesus , out of all that poverty they stand together as a community , and above all that they are all happy I didn't see one sad face . God bless them and thankyou \textbf{bald} for this video in a sad way it was wonderful xxxx. Peta from the UK\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Damn \textbf{Bald}. Didn't think you would turn on Kolkata and Bangladesh like that 😔\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Hey \textbf{bald} what's that music called in the beginning of the video ?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small The people of the USA that listen to AOC should watch your videos and see what Socialist  \textbf{Communist} countries live like.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small The conditions are self-imposed. They've been given hundreds of chances to move on to a better life, but the fact that the offers come from outsiders and their parents and peers pressure them to stay turns it into a continuous self-perpetrating cycle. They have been repressed and persecuted thorough history, but that's because of what you've seen here and the fact that previous regimes and people were far less compassionate and expected them to uphold their part of the societal contract. The government does \textbf{nothing} in fear of being perceived as \textbf{racist} (as well as the issue seemingly being unsolvable without radical solutions) but keeps being their ATM to further enable this. State gives parents plenty of money to ensure their kids can go to school, but when they pocket the money instead of buying school supplies, meals and clothes, attack the buses which would take the kids to school and then decry the school/state for being tyrannical and genocidial when they try to enforce regular school attendance and taxes/bill payments and basic security then you lose any sympathy you'd have for them pretty damn quick.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/186 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small You're probably not far off. A sad situation. I would guess there are more and more of the young ones that manage to break out of the \textbf{old} traditions and adapt to the society around, but possible not a large group. It's mindblowing that after hundreds of years in Europe the Romani people have not managed to change and adapt more over time, and we see people living in ghettos like his in 2019. The problem seems overwhelming. Is it a possibility to try avoid such large ghettos like this, but more relocate people to smaller settlements, well apart from each other, where it might be easier to 'pull' more of the young generation out of the 'bad circle'? Glad I'm not a politician those places\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/126 & \cellcolor{green!5}0.794 \\  \hline
  \cellcolor{green!27}\small \@S As long as said community  culture isnt willing to chance, \textbf{nothing} will work. We have these people in the netherlands aswel and they are given every opportunity to improve, free housing, free education, free money and still they feel entitled to it all and wont lift a finger themselfes. I have to work for every cent but those people get everything for free and are laughing their asses of. They are a bunch of parasites living of other people's money.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small You can throw as much money as you like at low IQ people but \textbf{nothing} will change.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small You and people with mentality like yours are a big part of that "self-perpetrating cycle". State gives gypsies plenty of money? That's an urban legend (currently used by populist politicians to earn easy votes). Gypsies do get some money. Not plenty. And same as any other citizen, so what's your problem? Also moving from there to a city is not so easy...actually just being \textbf{gypsy} in Slovakia is not easy, no matter if you/re educated or employed. People with mentality like yours will do what they can to make it hard. Renting an apartment while being polite, clean and having money, but being an \textbf{gypsy}? In Slovakia (and Czech rep. is the same) you have to work 10x harder and longer (compared to a white person) to find something and you will also have to bribe the landlord, so it will also cost you more than a white person would pay...otherwise the aparment rather goes to some white person. And exactly the same thing with getting employed. That's why gypsies rather go woring to UK, where people are not that \textbf{racist}.\normalsize   & \cellcolor{green!27}Gypsy, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}3/181 & \cellcolor{green!27}1.657 \\  \hline
  \cellcolor{green!5}\small ​\@S The sad thing is, they have been given homes of the middle class, and this is what's become of it. They have been given resources. Many families broke the cycle, many families happen to live there in a clean environment, but there are much more of them that just enjoy the life they are leading. They enjoy the benefits, the apparent immunity given by the local police that see no reason to enforce law, for example by giving fines, because many of them have no means to pay them. Like Harambe said, there is no will to enforce it for the fears of being called \textbf{racist}, which just further deepens the problem.That's why Teach for Slovakia does what it does, focusing on children from poor conditions, most of them gypsies, which have a chance of breaking the cycle in the future, other than wasting the resources on the generation of parents, resources that have been proven does not just work.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/162 & \cellcolor{green!5}0.617 \\  \hline
  \cellcolor{green!27}\small Spot on. \textbf{Nothing} happens without a reason\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I'm from Romania and the city centres of many towns used to be inhabited by the bourgeoisie. Needless to say, the communists kicked them out and brought the nomadic or rural gypsies in, and they have also brought their lowlife culture along. They taint any place they come across, even now when they get a free tenement in some \textbf{old} building, they blast kitschy Balkan music, make a mess of everything and frighten the law abiding neighbours. Their culture cannot be tackled with, it's too deeply lodged on both sides of the society. The white Romanians despise them, and once they are met with \textbf{racism}, they fall back onto the lowlife safety net, alongside their own anti-white Romanian \textbf{racism} (they have a word "gadjo" in their tongue, but also other demeaning ones such as "whitewashed" or "albino"). They aren't helped by the Romanian majority, and if they are, it's really hard for this kind of aid to strike home. Usually it's in vain.\normalsize   & \cellcolor{green!5}Old, Racism & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}3/163 & \cellcolor{green!5}1.84 \\  \hline
  \cellcolor{green!27}\small \@cfgvd \textbf{Nothing} to do with what I just wrote. But if you talk about people looking worse, slavery in the 1800 was beautiful and really high iq.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@Angakok ThothState absolutely does give them enough money for them to be able to take care of their children and ensure they are ready to attend school with supplies, clean and fed. If the parents would rather pocket the money for drugs and \textbf{alcohol} rather than ensure their childrens future and any kind of government control of the state-given money is considered too tyrannical then perhaps the benefits should be cut altogether. I will absolutely grant you that they for aren't exactly living high-life with the money, but they sure as hell don't spend it on the intendded purpose. And I can also appreciate that the well-adjusted Roma who are contributing members of society have it harder then other people due to discrimination but those people are unfortunately a minority. The stereotypes and distrust of the people as whole are well-earned over at least a millennium.The average Roma is a wastrel. Pretending it is not so and to obscure the truth by outrage over \textbf{racism} does not alter the reality, if you wish the improve the situation you must first acknowledge it. Giving them benefits for existing and fucking does not work, government programs to non-forcefully integrate them do not work, the situation remains the same as it was 10, 20, 30, 40, 50, 100, 200, 1000 years ago, the Roma are culturally-incompatible tribalistic people separate from the rest of society who are not net contributors, outside of the few who succesfully entered the society the better ones are vagabonds who earn a living by odd-jobs and as travelling performers the worse ones steal, mug, swindle and scam.\normalsize   & \cellcolor{green!5}Racism, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - General & \cellcolor{green!5}2/270 & \cellcolor{green!5}0.741 \\  \hline
  \cellcolor{green!27}\small \@StrawMan While the socialist regime did try to integrate them (and failed spectacularly), the Roma have very similar history to Jews. They've generally lived in isolated enclaves apart from the community and were semi-regularly target of people and rulers thorough history, whether it be priests and merchants instigating pogroms or dukes and kings trying to banish and erase them. The difference is that while Jews managed to integrate quite well and even slip into upper echelons of modern society by embracing familial encouragement of education and dedication leading to many of them becoming lawyers, \textbf{doctors} bankers etc. despite suffering one of the worst atrocities in history, the Roma haven't changed one bit, as a whole they're the same swindlers and vagabonds they've always been.\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small Az 3:36 the \textbf{woman} said: "Oni maju sanca"  "they have a chance". Im just saying because the caption is missing\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Kyril J the guy have said "0 chance" but you can hear the \textbf{woman} say the opposite in the backgrpund. But the caption is only for the guy. Someone, who doesn't speak slovak can miss that part\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small There's a big diference betwen normal people and \textbf{gypsy}... Normal people have to go to work to live a good life... \textbf{gypsy} they just dont understand why they have 2 work... they do everything else but working\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small I see similarities between Lunik 9 and certain areas in India; the people seem happy for the most part, yet they throw their trash all over the ground ( on the way to the houses in the forest I saw 2 huge dumpsters, so they do have a place to put garbage ).  I don't see why they don't clean it up, maybe plant some gardens so they can have their own vegetables and maybe some nice flowers to make the place look nice and also to have something to be proud of.   I just don't understand what the issue is; is it simply drug and \textbf{alcohol} addiction keeping them in such a state?\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/114 & \cellcolor{green!27}0.877 \\  \hline
  \cellcolor{green!5}\small I am a Polish Roma. I've been watching your videos for months now and there wasn't a time when I didn't like it.  You have great content, keep up the good work!! However, watching this video really saddened me knowing how Romani people still lives up this this day. The sad truth is that; in majority countries we are excluded from the society. The government does not invest in the Romani peoples wellbeing, living standards, etc... For example in Albenia a 7 year \textbf{old} child was burned by hot oil when playing with his mates. The child was in desperate  need of medical assistance but because of the families skin colour and their ethical background, they were thrown out of the hospital. We are the oldest and the biggest ethical group in Europe and we face great hostility from non Romas. \textbf{Racism} is an massive issue.The reason why Romani people got a "bad" reputation is because they have been neglected by the non Romani people. ITS AN ISSUE CAUSED BY NON ROMANI PEOPLE.\normalsize   & \cellcolor{green!5}Old, Racism & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/174 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small this is the most dangerous part of lunik where noone should go.. Moments later \textbf{bald} visits , its not at all dangerous\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Thank you for your work. Roms are the scapegoat of Europe. Some of them are no angels but I would be worse than they are if I had to go through what they do. For instance, not many people know that the last prisoner to leave a French concentration camp was a Rom. He left it almost a year after the end of the war, in 1946...Indeed, the idea of Lunik IX was an excellent one: to house a mix population of Slovaks (Roms, military and police staffs) but the military and police staffs refused to move in, they didn't want to live with the Roms. If they had move in, you can imagine how the situation would have been different. The present residents aren't fully responsible for the bad condition of the area. The owner of the building is responsible for the maintenance and it looks like \textbf{nothing} has been done for decades.When I was a kid, in the Parisian suburbs, the building where I lived was in bad condition too (not as Lunik IX). The paint, door-frames, electric system, \textbf{old} elevators, etc. gave a slum-like feeling because they were simply unmaintained by the government who didn't want to spend money for immigrants. Among other consequences, the resident didn't take care of anything. During the nineties, after twenty-five years of neglected state, the government financed a global and huge renovation plan. The building became clean and practical, with reliable elevators, entry phones, new bathrooms, etc. Since the renovation, the residents respect the shared areas and they keep the place clean.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/263 & \cellcolor{green!5}0.76 \\  \hline
  \cellcolor{green!27}\small \@lamebubblesflysohigh The police and military staffs never moved in. For what I know, the city of Košice first decided to house any type of non-Romani population (we now know they didn't come from Egypt so we could stop calling them "Gypsies"; and "White" doesn't mean anything either) but since \textbf{nobody} wanted to live near the Roms, they then started to house only problematic non-Romani populations (dodgers, maladjusted and squatters from other parts of the city). Which means they sent people with problems to live with people who already had their own problems. As you may know, by mixing social groups you can sometimes reduce problematic attitudes. A few countries excel in doing this, many don't or give up because it involves a complicated management.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small These people may be nice but there is ALWAYS a way out of poverty, saying there is no chance shows how lazy these people are. They don't care about their future or their kids. If they spent less time partying and doing something productive their future would be brighter. They just pump out more kids and care about \textbf{nothing} else in life. There is a reason they are sent to live in these places, because they are not a benefit to society.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Hey \textbf{Bald} , you show the real truth !!! You're videos are beyond good Man !!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small No wonder these people kept coming to the UK.. thank god for brexit\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Jaswinder Bansal Lol aren't you \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Jesus how many languages does Alina speak another great video it's like a breath of fresh air you be great doing \textbf{R\textbf{ed}} Nose Day you give use the real views not the shit the bbc want us to see\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small It is quite a shocking to see poverty even exist in Europe and yet people are happy in their lives. Thank you \textbf{Bald} for sharing this video.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Well I guess Mr \textbf{Bald} is going to be a president then (according to the girl making a palm reading). Never mind the fact that England is a monarchy. He'll be the president of England. :-)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Damn. The utter scum of human \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small So \textbf{Bald} name is Ben?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald} finally met the kids from the Hostel 1 movie : )\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Was in my local "B \& M" store in UK the other day and spotted they sold "Baltika" russian beer....thought i'll get a bottle of that for next time i watch \textbf{Bald} and Bankrupt's latest soviet adventure video. :-)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Fun fact: Lunik 9 was projected as APG borough ("block") A = army, P = police, G = gypsies during socialism. The idea was to integrate (yet another of countless attempts to do so) \textbf{gypsy} minority into majority society by making them live in a fairly high class neighborhood settled by people who would serve as an example of someone living by rules. Basically mostly police officers, army officers and their families and gypsies lived there. It failed spectacularly. Everyone who could (including already integrated gypsies) moved out after the fall of socialism when the state stopped dictating who lives where. It took gypsies less than a decade since fall of the iron curtain to transform wealthy neighborhood with brand new residential building to this. Barely anyone pays rent and buildings are beyond repair which means when they finally reach the threshold of being dangerous to live in, the city have to demolish them because gypsies would settle them illegally with no thought about safety.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/165 & \cellcolor{green!27}0.606 \\  \hline
  \cellcolor{green!5}\small What a nice couple, and it really improves your videos having her around. I hope you \textbf{crazy} kids make it!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Bald isn't bankrupt, working for Mi6 pays really well. More propaganda.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Yeah I'm sure MI6 is really interested in what's going on in \textbf{gypsy} slums and eastern bloc countrysides\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Bald only goes where people tell him not to go. So if you want him to come to your country you need to try to convince him to never go there\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Jay bhole ki , \textbf{Indian} fan\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small 8:08 Yep thats a \textbf{gypsy} for sure\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small "i gave my camera to a \textbf{gypsy}"\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Just want to remind people that this is rare that they were welcomed like that, gypsies will rob you \textbf{blind} and hurt you, its them vs the world, good video tho\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Did they \textbf{blind} you? Oh no, wait.. They damaged your brain, right? Now I see. Poor you. :)\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Men seem to enjoy dancing with A Lean Chick\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small That \textbf{gypsy} kid trying to be British gangster was the highlight\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small It's so \textbf{alien} to me to see these guys in an environment like this for it to get even weirder to hear them say that they stayed in Derby and to hear them use the same colloquialisms that we use in the West Midlands.\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Bald, cool that you popped up on my YouTube. Cheerio!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald} how many times you bang that \textbf{chick}???\normalsize   & \cellcolor{green!27}Bald, Chick & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small \@x y I dont force them to integrate, I try to avoid contact with them as much as posible in my country and in other country I visit. And for your information, what you have said is exactly what is happening in Romania - \textbf{nobody} want or force them to integrate and leave them be. Thats why they do a lot of bad things and are uncivilised and they dont have any respect for the law or anything. Not to mention that in any country they are, they make a bad reputation for Romania and that really piss me off, because I am not a \textbf{gypsy} and I dont want to be treated like a thief , like a paria in other country from the EU or anywhere in the world where they do bad things. France, Germany, Great Britain and other civilised countries from Europe keep telling Romania "Oh, you dont support them, they need to be respected, integrated, etc..." but when this gypsies are in their countries they want them out as soon is possible :)) Hypocrisy at its finest!\normalsize   & \cellcolor{green!5}Gypsy, Nobody & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/182 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Slovakia..so next stop Czech republic? I think we can offer some \textbf{old} soviet buidling to explore.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Bald , go back and help that poor , injured dog that was cowering in the corner. They have beaten it by the looks of things and looks like its back legs are gone. These gypsies are well know for abusing animals and dog and cock fighting. They even do it here in Ireland.  Do a really good deed man and do something.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Good man \textbf{bald} and Harold good for you . You do a service for humanity.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small This video is really interesting. It shows that Roma problem in Slovakia is not just "\textbf{black} and white". As you can see even at Lunik IX, you can find people who live decently, like that family with beautiful flat even in Lunik IX. BUT Europeans did not marginalize them. They marginalized themselves. Whatever they did get from state, they destroyed - the flats at Lunik IX is clear example. They even admitted that all that rubbish was made by themselves, there are dustbins, they just do not use them. And in whatever conditions you live, how is it possible that you let your kids drink \textbf{alcohol} in such young \textbf{age}? and then the parents just say that there is \textbf{zero} chance for better life of their children ?!?! Just to be clear, your video is interesting and I agree with many comments below that you were able to show people something that even journalists were not able to do. I am from Slovakia and I live in a village who has a problem with Roma population, so I know something about it. But for those who never really had this experience I just wanna say that those news in media like "Slovakia/EU marginalize Roma population" drives me mad, because most of their problems are caused by themselves. And of course you do not think they are dangerous, but you should ask postmen or social workers how agressively these people can behave when they are visited.\normalsize   & \cellcolor{green!5}Age, Black, Zero, alcohol & \cellcolor{green!5}Age - General, Age - Youngsters, Behavioural Addiction - Alcohol, Ethnicity - Black & \cellcolor{green!5}4/245 & \cellcolor{green!5}1.633 \\  \hline
  \cellcolor{green!27}\small I really doubt the \textbf{Gypsy} created that rubbish pile. That to me looks like municipal services failing in their responsibility to keep the city clean.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small The video gets a little \textbf{weird} in the middle. Almost like the parents are not doing their jobs. Obviously , they're not very moral people.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small easy enough to smile When life flows along like a sweet song; But the man worth while is the one who will smile even when all around everything goes dead wrong. by Kent Remember.Great stuff Mr. \textbf{Bald} :).\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Stay alert because \textbf{black} shirt guy can fuck your girlfriend 😂😂😂😂😁😁😂😂\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small bald! is there any chance that you visit philippines?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Im a roma \textbf{gypsy} from poland and i think im really lucky to grow up in a wealthy  family living in a million pound house in london.Thanks United Kingdom.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Alina is so sweet!❤️  Absolutely loved this video...Thank you Mr, \textbf{Bald}!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Bald, the shithole explorer\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small 12:22 she said she had mixed feelings about this place, that they did not get robbed or raped ......I can't see anyone trying to rape Mr \textbf{Bald} 😐...that would be a surprise....😂😁\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Guy just turned the music down a bit, but \textbf{woman} shut that \$hit down.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small If i ever end up visiting a though neighbourhood, i will say mr. \textbf{Bald} sent me, and no one will touch me😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small In what language does Alina speak with the \textbf{gypsy} local?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I LOVE this show. I hope to travel with Mr. \textbf{Bald} sometime soon\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I've been to this place and many other \textbf{gypsy} slums. I had almost the same experience as you recorded here each time. This place is like sk govt created a trash bin for unwanted people.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small The kid filmed a party which Mr \textbf{Bald} was not invited to ......mate it was a kids party.....😂😁\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Mr.\textbf{Bald} : Boy came back with the camera, why not try the wallet?Alinchick : Don't make me decide sides\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small U made me laugh as again \textbf{bald} u Funny man . Good new videos\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small And people in the USA complain about their lives.... great job \textbf{Bald}!!!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Love their \textbf{OLD} TIME CARTS OR WHATEVER THEY CALL THEM. WOULD LOVE TO BUILD ON... GET ME A ASS AND I'M OFF... LOVE THE VIDEOS... YOU HAVE A GREAT FRIEND NOW.. ❤👊🇺🇸\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Also may I say... how my heart GRIEVES for all the CHILDREN... NO CHILD NOT ANYONE SHOULD HAVE TO LIVE IN THAT... GOD HAVE MERCY ON US ALL... AND YESSS THEIR JOYFUL... LOVE THE \textbf{OLD} PICTURE OF CHRIST ON WALL ALSO.. J.S.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small while youre here you should try our beloved national alcoholic drink called borovicka. every 14 year \textbf{old} loves it\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@6:25 Mr. \textbf{Bald} found out a new Talent future YouTuber\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Its about beinging an ambassador to the many countries and approaching people where they are and \textbf{Bald} is wonderful at feeling his surroundings. He melts in to the local culture and they trust him. Smiles and openness and the fact that he is from England is a novelty for this community. What a great video!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Hey \textbf{Bald}, if you're still in Košice, I'd be happy to show you some \textbf{old} \textbf{Communist} era sites in this region: insane asylum, battlefield from WW2, chata (dacha), etc..\normalsize   & \cellcolor{green!5}Bald, Communist, Old & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small Bald you live in a huge city in England you have no idea how bad people gypsies are. They didn't harm you and Alina cause you told them you where there so you can show people that they are good and staff. If they didn't consider you their guest you would have been in some serious shit. Also you lived with them one day so stop judging by the cover. They are favoured in any Europe country with free homes and they pay back by ruining them and making illegal activities (something that's against the society thats trying to help them).\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/101 & \cellcolor{green!27}0.99 \\  \hline
  \cellcolor{green!5}\small Sam S 'A little untidy'? Understatement of the year there pal. Not surprising \textbf{nobody} wants them anywhere near their country.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small briliant .... this channel is one of my favorites,,,,,\textbf{nothing} staged.. i tell everyone about this channel.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small wait what gypsies ancestor is from india,wow I didnt know that,I thought they are from europe,this what I didnt found in scholl thank \textbf{bald}you are not only \textbf{bald} but also bold\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small "They were just telling me that the last vlogger grabbed this exposed wire and was electrocuted.  Let's see what happens when we grab it."', said Mr. \textbf{Bald}.  Hahaha\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Bald they didn't rob you because you looked like a \textbf{old} skool skinhead. You just needed your 14 hole doctor martins. Untouchable.\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small This slum is far better than \textbf{Indian} slums\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small 95 of them are just bad people wanting to live for free off government money and not work for a single time. In the small city that I live in they just cause chaos, steal, beat you up when you are walking alone etc. Funny how this state gives them more privilege and money then Slovakians who work hard for all their life. Gypsies were even given a whole street close my town that is now called "Čierne Mesto - \textbf{Black} City", it was originally built for \textbf{doctors} but gypsies somehow ended up there and fucked that place up.\normalsize   & \cellcolor{green!5}Black, doctors & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small Bald is a journalist now, doing a great job.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Once again \textbf{bald}, you made an amazing video (with help of course), amazing stuff and way more inspiring than one of those voice over ads "one in five children in Africa are starving".... Anybody know of any orgnizations that help out area 9?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small I like your new thread's mr \textbf{bald}. Nice jacket, your looking well Thanks for the video Cheers Laura 🇮🇪\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Ahhh the wonders of multiculturalism. It is lovely to see Native Slovakian \textbf{Gypsy} youth drunkenly demonstrate the aggressive body posturing of \textbf{African} American tribesmen to the sounds of some hybrid hip hop melody!The generosity of Europeans is really helping families like these, and they seem so appreciative.Thank you for sharing this lovely adventure in diversity!\normalsize   & \cellcolor{green!5}African, Gypsy & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Roma & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small The idea that gypsies living in Europe or elsewhere are from India is wrong.Then the \textbf{R\textbf{ed}} Indians in US are from india ?.This originated from British rule.For example they categorised a tribe  in India as criminal one when the tribals refused to move to tea gardens to work there leaving their habitat .\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Czech here so glad to see you visiting my Slovakian brothers, come here when you have the chance comrade bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small See the contrast between outside and inside, these people dont have \textbf{common} sense about public stuff...\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small The US Government wants to import millions of those \textbf{engineers} and \textbf{doctors}! 👍\normalsize   & \cellcolor{green!5}Engineers, doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small How many languages that \textbf{chick} can speak?\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small waau \textbf{bald} and bankrupt in eastern Slovakia!!!  I would like to meet you here and drink together!! :DD\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small A Košice native here. Seeing what has been going on in Lunik IX is indeed very sad. Unfortunately, it's not going to get any better (no simple solutions here). There are several reasons for this and both the Roma and the whites (the local Slovaks and Hungarians) are responsible (to various extents). Children growing up there see their parents being trapped in a vicious circle of poverty (unemployment in the borough reaches 100) and drug addiction, and the kids themselves often struggle with drugs from a very young \textbf{age} (it is not uncommon to see Roma kids as young as 8 years inhaling solvents). The kids often don't go to schools (even though it's mandatory and free) and thus grow up illiterate. They consider this lifestyle acceptable because they simply don't know any better.The way the whites are responsible for this is the prejudice against the Roma and turning a \textbf{blind} eye on what's been going on there. If you're that extraordinary 1 in 1,000 who is capable of "escaping" but are treated like shit by the majority, then good luck.30 years ago, after the fall of the previous regime, everybody had more-or-less the same starting position (or was equally poor as I like to put it). The same endowment, education, dwellings, healthcare... everything. How did we get where we are right now? My only explanation is a different temperament of the Roma. While you cannot generalise, they've always struck me as a slipshod and happy-go-lucky bunch. They've been in Europe for more than 3 centuries and still haven't integrated. Currently, the far-right is polling at around 10 and the majority of what they talk about revolves around the Roma. The fertility rates vary greatly between the whites (at around 1.4) and the Roma (my conservative estimate would be 5.0+), which only further exacerbates the tensions. In my opinion, the best solution would be a very strict child welfare service in Slovakia, not unlike the "Barnevernet" in Norway. But I'm not convinced even this would help.\normalsize   & \cellcolor{green!27}Age, Blind & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/339 & \cellcolor{green!27}0.59 \\  \hline
  \cellcolor{green!5}\small Here in Vilnius, Lithuania we call it Taboras. Gypsies usualy sell many kinds of drugs there, young people dying every year. This is great curse with this \textbf{nation} and they need to repent of tbem sins and come to God. There is no other way for them. Our church run 4 rehab centers and saving a lives of many drug-alco addicted people.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Bald for president! Since the \textbf{gypsy} told her she would marry the president! Lol\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small such great travel companions, didn't think it would get better than just \textbf{bald} but alina is such a great addition!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small that isnt neccesarily true, there are many examples of high ferrility and low poverty, in fact, what i just mentioned is more \textbf{common} than overcrowded high fertility slums.  another case of something you dont expect is south korea, 48 of south korean \textbf{senior} citizens are in poverty, and south korea has the lowest birth rate in the world\normalsize   & \cellcolor{green!27}Common, Senior & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Absolutely \textbf{crazy}! I heard about this place. I went to some rough places before but a lot of respect for you for going there and showing all this.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Big Respect Mr.\textbf{Bald} !!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small go \textbf{bald} marry your babushka and put it in her butt hol'!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Zaz babushka is also a scarf that \textbf{old} Polish women used to wear tied around their head.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Hammered 'Round the World with Mr. Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small That place looks like good fun, then again a morgue would look like great fun with \textbf{bald} !\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Glad \textbf{Bald} went to this place so I don't ever end up there while travelling\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I can't believe no one put a spell on you or you were turned into a \textbf{toad}.\normalsize   & \cellcolor{green!27}Toad & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Hey mr \textbf{bald} when are you doing a reunion video with harald ??\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Well \textbf{Bald} you are a little bit late to visit Hős Street in Budapest(got demolished some time ago) but I bet you would have enjoyed it😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small you hit the internet content lottery with Alinachek \textbf{bald}...not only easy on the eyes but a perfect "partner in crime"\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Wow, leaves me speechless. Thanks \textbf{bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Unfortunately the majority of the people in this comment section have had a bad experience with the \textbf{gypsy} community myself being one of those people! I also don't really have \textbf{nothing} nice to say about them either as the majority of them are just the scum of the earth only a small minority are still decent human beings!.\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}2/58 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Weird how you have your username in spanish! 👀🇲🇽\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small 'The people united will never be defeated' it's a very famous quote used in \textbf{communist} rallies\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small i live in a \textbf{Gypsy} neighborhood but im not \textbf{gypsy} and  bro at night is scery end dangerous\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Great video. It's \textbf{weird} hearing the Derby accents on the ones that lived in England.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Bald and blyat\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Looks like the Hoods of New Orleans in the 90s and early 2000s, 100s of kids everywhere in the streets and \textbf{old} people out drinking and playing cards and dominos, hip-hop music blaring out only minus the high crime, drugs and murder.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I don't care how nice they are. The apartments were built new and nice for them and they threw garbage out their windows to make a trash dump outside their windows?kids drinking? No wonder the Slovaks don't care for them. Someone said in a year they destroyed the place? Then they say they are hopeless? \textbf{Crazy}! That's their lifestyle wow !\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Please \textbf{bald} never relax around gipsys never They will steal even if they are 3 year olds\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small gren spitfire jacket , \textbf{bald} ... you look loke skinhed, and you are in gipsy slum...\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I lived with a slovakian \textbf{gypsy} family in Bratislava for 50 days,they were super cool and they learn punjabi very quickly.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small some of them do look like \textbf{Indian} ....\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small To all those saying they are dirty because of there culture and watch how dirty modern India is let me tell u something:1. Indus valley civilization (2000bc): 2000 year before christ born when whole Europe was in stone \textbf{age}. There were cities in India(specifically in places frm where gypsies are) with brick walls, multistory houses, covered drainage system. So, it shows that culture is not here to blame.2. There r many Indians migrated to Malaysia, Singapore etc and they r among the most educated, financially secure there.3. Now come to modern migration. There r many \textbf{Indian} migrated to US, EU in Modern time. They r also educated, modern.So, india is dirty not because of culture but because of poverty. It takes a lot money to build and maintain sewage plants, garbage collection. Even rich countries like UK, Canada find it tough to manage garbage. That's why either theydump it in ocean or export it to Asian countries like China, Philippines.\normalsize   & \cellcolor{green!5}Age, Indian & \cellcolor{green!5}Age - General, Ethnicity - Native-American & \cellcolor{green!5}2/164 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{bald}. Marry her in the slums. 😍\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small U should go to north eastern Bulgaria near varna I drove through once it is similar to this but instead it is a whole town full of \textbf{gypsy} some of them still speak true Romani dialect which is similar to North Indian\normalsize   & \cellcolor{green!5}Gypsy, Indian & \cellcolor{green!5}Ethnicity - Native-American, Ethnicity - Roma & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small There's a whole bunch of North \textbf{Indian} languages so which one?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Zero} 01 it's no way like punjabi don't be chatting if you don't speak punjabi and Hindi was created in the 16th century by the mughals ain't the gypsies an ancient type of people from India\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small toocharged bro I don't know which North \textbf{Indian} language all I know is that many of the gypsies their don't speak Bulgarian but grow up learning Romani only\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Bald didnt get raped? Huh? 😂😉\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Thats why I like this man.....Who shows the true reality ....So many problems....but still have hope of elevation.We miss you Mr. \textbf{Bald} , love from india\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Wow. Those little girls shaking their ass and dressing slutty around boys are going to be raped at a very young \textbf{age} by either some boys or pedos. Wtf..\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small 10:39 -  this is a stew they're cooking....   Shows a empty pot Coming up next week - How to lose weight on a \textbf{gypsy} diet.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small I grew up in ibrany Hungary near the Ukrainian and Romanian border and we have many \textbf{gypsy} slums as well some of the biggest slums are not even official apartment buildings just abandoned areas and landfills\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small First of all they choose the way they live. All those apartments was  new and now u can see what they did and how it look like after years. All they can do is wait for social welfare money ..waste them all for \textbf{alcohol} and drugs and then robbing and stealing. Crying how all white people are \textbf{racist} etc.. they want everything for free. Move your arses gypsies and get a job!!!\normalsize   & \cellcolor{green!27}Racist, alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol, Ethnicity - General & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Your future husband will be a President))President \textbf{Bald} of the Brighton and Hove  bowling club.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Too bad for \textbf{Bald}, she said wife.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Anastasia Petrova \textbf{Nothing} really, as long as it doesn't involve butches.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small This looks like Kolkata? 🤐Are you kidding me??? Mr.\textbf{bald} ..I am from Kolkata India ..and it's far far better than what it's shown in Ur shit video .Do visit Kolkata and then comment .Stop disrespectful of places u least visited ...have u ever seen Bangladesh????? U mostly  got all Ur subscribers from India ...and u are showing disrespect to the culture of an \textbf{Indian} state??? Man stop Ur nonsense video ..Look at harld ...and learn something about making video .Taking a girl ,and inducing your followers to watch them ..and eventually hurting them .It's quite disappointing .😥\normalsize   & \cellcolor{green!27}Bald, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!27}2/102 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small This is not Europe's biggest \textbf{gypsy} town, it's either Ferentari in bucharest or Craiova city\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Bald, you should come to Bosnia and Herzegovina. The entire country is a fucking slum.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Looking at the appearance of some of these precious souls, I soundly believe they have Anglo DNA.   There's just something about them that differentiates them from the nomadic Asian descendants.  For one thing, there attitude and character traits sets them as probable brethren to the Anglo-saxon \textbf{race} as the Anglo-saxon's were sojourning from the Caucasian mountain regions making their way to northern France, Denmark, Belgium,  Netherlands, Norway, Switzerland, Sweden, Finland and Britain.   The so-called 'white' Anglo-saxon's were called and are still called "Caucasians" due to inhabiting areas around the Caucasian mountains for so many generations in the past.  These are probably some who were not able to stay in the sojourn.  There were more than three million that completed the migration to the West.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/124 & \cellcolor{green!5}0.806 \\  \hline
  \cellcolor{green!27}\small Bald, you always take me to places I would never visit myself.  Well done!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Allways interesting video by \textbf{bald} and bankrupt.....allways watch him\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Maybe she studied in CZ.  So many girls I have met here in Poland from Belarus and UA speak 4-5 languages.  Pretty \textbf{crazy}.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small bald just goes out into the \textbf{gypsy} hood like an absolute king, damn bro wtf\normalsize   & \cellcolor{green!5}Bald, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small It's so inmtresting and cool that we live in a world where a large portion (I would even say majority) of kids in the EU know English at least at some level before the \textbf{age} of, I dunno, 10. Even in a remote slum in slovakia the kids can talk to a british guy and a belarussian girl visiting them.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small \@Peter VlčkoVlčko you should read up on your dictionary to expand your vocabulary also try to pick up some English grammar book to better your use of the past tense and your syntax of the sentence. He can help people on the street without spewing \textbf{homophobic} and \textbf{racist} bullshit.\normalsize   & \cellcolor{green!5}Homophobic, Racist & \cellcolor{green!5}Ethnicity - General, Sexual Identity - General & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Lena' makes my willie go Boing Boing Boing and i would like to marry her that is if \textbf{Bald} would approve! I would bring her to america if she wanted to and treat her like the princess that she is!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Health standards are low and diseases such as hepatitis, head lice, diarrhea, scabies, and meningitis are \textbf{common}. Unemployment in the borough reaches almost 100 percent. The borough has one elementary school and a kindergarten.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Brexit needs to hurry the fuck up\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small I don't think you can call yourself bankrupt Mr \textbf{Bald}. Richest man in the world now with that lovely lady.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small How does \textbf{bald} go to the most dangerous places and become friends with the local people almost instantly? 😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small How  much did Mr. \textbf{Bald} pay them in advance to put out this little show for him, including the \textbf{gypsy} wedding? Mr. \textbf{Bald} makes an impromptu visit to a \textbf{gypsy} slum in Slovakia, which happens to celebrate a wedding at the same time.\normalsize   & \cellcolor{green!5}Bald, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}4/43 & \cellcolor{green!5}9.302 \\  \hline
  \cellcolor{green!27}\small I got near mugged in Huelva from a Gitanos (Spanish \textbf{Gypsy})\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small bald come to romania please you'll love it here!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Yes there is. I believe in the Balkans that there is this town in Macedonia that's known as the \textbf{gypsy} capital of the Balkans, forgot what it's called though\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Next video \textbf{bald} goes into \textbf{Migrant} Detention centers.\normalsize   & \cellcolor{green!5}Bald, Migrant & \cellcolor{green!5}Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small DavidDavidDavid no he needs to go see foukme \textbf{gypsy} rapper\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Gypsy life matters!Too many....😏😏😏\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small No matter how shady shit gets in the video, I know if we are watching it, our man \textbf{Bald} made it out.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small What wonderful people with good \textbf{common} sense 👍, who live with adversity of all kinds in a world that's, for the most part, wealthy and without W A N T but don't know how to appreciate what they have.  These are the immigrants needed in the USA and Britain.  I feel that they would quickly become as one with the people.  Sadly, Africans and Muslims are being promoted in these two countries by traitors in high places.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small Bald and Bankrupt Soviet Adventures are the best\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Man Slovakia's gypsies are way more integrated into modern society than i ever thought , they can speak english so well and not only that .. If you ever come to a Bulgarian gyspsy ghetto do NOT expect the same result mr. \textbf{Bald} !\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Alina has a smile of a \textbf{promiscuous} goddess 🌹🌹🌹(we love her for that) and you Bean, most charismatic person on the YouTube, please more videos  PLEASE  MORE  VIDEOS !!! May Allah smile upon your face's ! 🤙👍👍 P.S. When are you going to come to Los Angeles California ?\normalsize   & \cellcolor{green!27}Promiscuous & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald} , that is \textbf{crazy}! I must take you to task for to task for taking Alina to that place 😊\normalsize   & \cellcolor{green!5}Bald, Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Will \textbf{bald} go to Bulgaria?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small 2:17 :Alin \textbf{chick} 'my daughter '😂😂🤣😂🤣😂\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Alina is a fucking treasure. What a smart, beautiful, well-spoken \textbf{woman}. Love from Japan!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Alta Fedelta he would be \textbf{crazy} not to. She is a real catch\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small True.  I'd dump a massive load inside her \textbf{pussy}.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@twoluckyone You are one \textbf{dumb}, naive \textbf{snowflake}. After the one video where her and that other girl went with him to eat at a \textbf{Indian} restaurant she's travelled with him and is in every video. Anyone that doesn't know he's smashing her is a dumbass. I hope you don't have kids or have a daughter.  She would probably get away with giving a dude head in the backseat while you're driving.\normalsize   & \cellcolor{green!5}Dumb, Indian, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/71 & \cellcolor{green!5}4.225 \\  \hline
  \cellcolor{green!27}\small \@Володя Балодя I sound mad for stating facts? How can you hear me type? You have some issues \textbf{weirdo}. But I can assure you that I'm happy.\normalsize   & \cellcolor{green!27}Weirdo & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Bald is boss. THis is why we watch. Top man mate\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small My late father came from \textbf{gypsy} blood. He NEVER spoke of his family.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small This channel is getting better with each new episode, brit TV at it's best.I don't think this is a typical slum, this is more like government organized and EU sponsored geto, build to keep certain stigmatized minorities away from modern, present civilization. There's no good reason why they let those people live like zoo animals, people are told it was always this way and \textbf{nothing} can change that, they must suffer because they were born to the wrong parents. Eugenic BS is still very alive in Europe. And they are definitely not happy, this have \textbf{nothing} to do with spirituality or a good hearth, they simply don't understand and can't even describe what is going on because they were raised by not thinking, just accept existence as is by itself and give in to the basic biological instincts. Not all are Pakistanis and Indians, many third class European citizens are exiled into similar \textbf{gypsy} communities, many are also government and military agents, EU should be ashamed of itself for allowing this to go on.\normalsize   & \cellcolor{green!5}Gypsy, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}3/175 & \cellcolor{green!5}1.714 \\  \hline
  \cellcolor{green!27}\small She is getting bigger and bigger becoz of mr. Bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small We love Mr. \textbf{Bald}... The world as we know is different from what it is..........\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Hey \textbf{Bald}, are you planning on coming to Hungary? There are many small villages in the northern part of the country flooded with gypsys.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Another great video \textbf{Bald}! It reminds me of when I was in Kiev in the mid 90's and saw a 4 yr \textbf{old} \textbf{Gypsy} boy standing on the corner smoking a cigarette.\normalsize   & \cellcolor{green!5}Bald, Gypsy, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}3/32 & \cellcolor{green!5}9.375 \\  \hline
  \cellcolor{green!27}\small Speaking as a bin man ...  I know what \textbf{old} rotting stinking garbage smells like, and can you imagine the maggots \& flies too in the summer months !    And  do they all have jobs or are they claiming some sort of state benefit ??\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small bro \textbf{bald} hope you enjoy at lot with that beautiful young lady😅😅😑rite*peace👍\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small By Mr. \textbf{Bald}?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Bald, why do you keep changing titles of your videos?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Bald you are such a nice guy showing stuff we wouldnt see anywhere else.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small BALDcollect some of their tearsit can cure AIDS\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Yeah that's their hideaway where they hoard all of the shit they stole throughout the year that's sad it's \textbf{nothing} to do there all they do is have babies. Great life to bring kids up in.You gonna take your young beautiful girlfriend away from that life in Eastern Europe and show her the big city lights.Definitely inspire those kids to go away to find better life n educate themselves.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Bald please come to Pakistan you will find what all the Indians and the media say is absolutely wrong. Watch Eva Zu beck videos or Mark Wien's videos or Food ranger Pakistan Vlog to see what Pakistan is.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small A fourteen year \textbf{old} is drinking Vodka it cant get worst than that!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Ohh \textbf{snowflake} 😂😂😂\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Never knew such a place existed in Slovakia. Mixed feelings i think best describes it. Nice 1 \textbf{Bald} and Alina! Bruvs!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Great video, \textbf{Bald}! As for those who moan about their beloved UK being ruined by these people, keep in mind that there are gypsies everywhere in Europe. I doubt it that Irish Travelers leave everything tidy before they move their caravans. Some council estates in England look very similar with Lunik 5. The only thing that makes them different that council still comes to pick up the trash they leave behind. But if you notice in the Video, despite all that mess from outside, houses inside (as \textbf{Bald} says it himself) look a lot cleaner than any average British full time proud mummy of 6 with 6 different dads house given for free by the council. Every \textbf{nation} has their own bad eggs. Let's not blame it on gypsies only. UKs benefits system is fucked up already. And most of those on benefits are smack heads and whores, not foreigners.\normalsize   & \cellcolor{green!5}Bald, Nation & \cellcolor{green!5}Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}3/150 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small bald has more hairs on his head than videos of which he didn't change the title\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Awesome \textbf{bald} bro......👌👌\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I really love these places! More \textbf{gypsy} please!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Gypsy District 9\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small 1. This was recorded by a boy he gave the camera to. 2. What difference does it make how \textbf{old} the person is? If someone doesn't approve of this kind of dancing then it could be a 20 year \textbf{old} and it will still trigger them. And not everyone has the same beliefs on "appropriate" dancing. Heck, if this portion of the video upset you, then you really shouldn't study \textbf{gypsy} culture. They have a much different mindset than most. (I happen to appreciate a small amount of their culture)\normalsize   & \cellcolor{green!27}Gypsy, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!27}3/90 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I only watch for 1 thing and it's that pretty little \textbf{bald} man🤘\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small It's amazing that 1400 years after their ancestors were forced to flee the \textbf{Indian} subcontinent by muslim invaders, that they still remember where they come from.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small you are either brave or very stupid... never give anything valuable to a \textbf{gypsy} especially not to slovak gypsies.... PS: Alina your slovak is pretty good, im impressed !\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I really appreciate the comments from people that live in the country that \textbf{bald} visit. They give a  good insight most of the time.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Why should anyone be surprised seeing how the Roma people live. This is normal for them. Anywhere in Europe. They are a wandering people that countries want them to settle down in one place. \textbf{Bald} should not feel sorry for them since they do this to themselves.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{Bald}, Thanks for yet another interesting video. Really appreciate your courage for visiting a so-called dangerous place. However, I'm deeply offended by your reference of Calcutta which you used as a benchmark. Calcutta is the cultural capital of India and one of the fastest growing cities of India. Tall skyscrapers, shopping malls, new metro lines are being built in the city and yet westerners still associate this city with poverty just because Mother Teresa started her operations in the city. Even today, western media tries to highlight poverty in India without showing the economic progress. Unfortunately, you have also fallen victim to this western stereotype.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small M R The colds ones podcast it was just the pewdiepie episode. They just had a short clip of \textbf{bald} in there.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small England after Brexit\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Bald come to Bosnia \&Herzegovina we have some things youwould like many abandoned buildings from time of comunism you can be my guest ;)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Bald, if you want to see the other side of the coin - filthy rich gypsies - you are more than welcome to Romania, where there are entire towns full of \textbf{gypsy} pagodas (Strehaia, for example)!\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Slovakia is such a nice place , and you choose to go in the \textbf{gypsy} ghetto ? \textbf{Gypsy} ghettos is same as in england or Germany,Russia so why filming it in Slovakia?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small They actually do look like \textbf{Indian} nomads. Especially ones you can find around North India.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small If you like \textbf{gypsy} ghettos you should definitely come to Bulgaria - every city has several of them - our gypsies are more dirty, more uneducated, more lazy and more dangerous.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Come back to india... \textbf{Indian} people loves your videos...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small 7-40 loved the fly paper. So \textbf{chick}.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small they r all over in east Europe (\textbf{gypsy} ) most of them do not work,having lot's of kids,no education ,cheating,beating ,stealing other people  ,i worked with some ,they r lazy as f..uk, collecting welfare 4 ever ,  cancer of Europe for sure!  (should deport all of  them somewhere a  far away island ),u got not robbed or beaten because your are with you camera, things   r working,happening way different what you experienced over there with Alina ! trust me i got some bad (very bad ) experience with them !!!!\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small I often remember her saying "stranger danger" to Mr \textbf{bald} on first encounter\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Those buildings were built for upper middle-level class, for families of policemen or soldiers. \textbf{Communist} regime had the idea to mix white folks with gypsies to "educate them" somehow. All left except for the Roma. I think these "blocks of flats - činžiaky" as we call them were destroyed within three years. You can't say its safe just because you paid a visit; they treat you nicely of course, as a guest. It would be different if you stayed longer. From time to time I can see kids doing drugs, which is inhaling thinners here.The small kids know some English because some of their relatives left for UK.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small \@Jan Bodnar We have a large Romanian \textbf{gypsy} culture in Birmingham UK. This videos says a lot about them and how little the value anything. I have worked with Romanian people and they hate the \textbf{gypsy} people. Not even their own government want them.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@R T Rap is big with gypsies in Slovakia. Most famous rapper in Slovakia is half \textbf{gypsy} and has some brutal youtube views for a 5 million country. He is like king to gypsies. Type "Rytmus"\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I mean it sounds \textbf{racist}, but whereever a band of gypsies goes you're better off checking if tools, building materials and wiring are still in place.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@R T "multiculturalism is a fail". How can you mongoloids say this given the US is the world's most powerful \textbf{nation}?\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Steve Rozi USA was already the world's most powerful \textbf{nation} when it was around 90 white.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Never trust an elf "white" didn't mean anything for a long time. Reducing europeans to just our skin colour is astoundingly stupid, especially back in the day. The US still was able to group people all around the \textbf{old} world to contribute to the country and that made it the behemoth it is.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small \@Steve Rozi That term was and still is often used to describe European people and their descendants. Other groups of people contributed too, but their contribution in building and developing USA was negligible in comparison to that of the European people by the time USA became the world's most powerful \textbf{nation}.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small The shittiest places in the USA are the most \textbf{Colored} areas.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Kyril J Yes, it is like that. And they do it because it is cheap and they can't afford the more expensive drugs such as cannabis. In general, paint thinners, cigarettes, and slot machines are destroying \textbf{gypsy} families here.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Liam McIntosh I wish they go deported, but likely not. Our government has an immigration policy that equates to ‘let them all in'.  Not to mention that the media and people on social media would call it \textbf{racist} if they were deported.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small El Catto Excluding the shit cultures or even determining them as shit when they quite obviously are is considered \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Harambe And how many Roma people   gypsies do you know personally ?The way you see the world or gypsies is very simplistic it is much more complex and what is on this video is a reality in specific location Lunik 9 that dos not mean all Roma people in Slovakia living like this .  Our actions define who we are not our \textbf{ethnicity}. And your comment defines you very well !\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small \@besne prasiatko i saw that in the video... Just wanted to reiterate, cuz I'm an \textbf{Indian} and found it it a bit \textbf{weird}..🙂\normalsize   & \cellcolor{green!5}Indian, Weird & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Great and original content. Keep going Mr. \textbf{Bald}! I enjoy these videos way too much haha\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Ontyyyy ....Thanks for the words of intelligence and good sense! I see through these people as you do! They don't fool me one bit! Mr. \textbf{Bald} and Alina were duped into believing these were wonderful people!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small They are "victims" exactly as they are in Serbia. They make their cardboard slum settlement on some non developed piece of land in some town, and when the town or the government wants to build something, we have to give them FREE apartments. so, basically, if you are a Gipsy, you just make a tent of a cabin anywhere you want, and wait for the owners of the land to evict you, and then ask for the government to give you a permanent living for free in some new building, because you are "a victim of prejudice and injustice". And the government obliges, of course, because they are \textbf{nothing} but EU puppets. EU is always more than ready to pour money for their accommodation.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small Actually, Mr \textbf{Bald} does speak of a German filmmaker, who was robbed of everything  - and he got that info off of their \textbf{Gypsy} hosts... So it's not like he and Alina were naive. They just wanted to show another side of the local people, a real side as well. And I'm sure they were aware that that trash heap is never getting removed. But then again, both sides, show both sides, and leave the conclusions to you. Greetings from Poland.\normalsize   & \cellcolor{green!5}Bald, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small I can see some typical  \textbf{indian} faces out there.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Grant Toranzo I don't remember kids being THAT \textbf{sexual} at such a young \textbf{age}. Sure we'd joke about nasty words and say stuff adults wouldn't expect, but I never remember hitting on girls like that or any of my peers being like that besides maybe the trashiest of them lol. Not until late middle/early high school did that behavior become normal. These kids look like they're in late elementary/early middle school and haven't even hit puberty yet... (It's all dependent upon how and where you are raised in my opinion)\normalsize   & \cellcolor{green!5}Age, Sexual & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@Pink \textbf{Alien} can easily hire an editor\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Gay \textbf{G\textbf{ay}}  He can easily hire an editor. Ok.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small \@Pink \textbf{Alien} Where there's a will there's a way\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Had to laugh at that kid wearing an England top.Wonder if there's a \textbf{p\textbf{ikey}} knocking about in England in a Slovakia shirt?\normalsize   & \cellcolor{green!5}Pikey & \cellcolor{green!5}Nationality - Irish, Social Class - Working class & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small i have been curious about lunik 9 for a number of years since first reading about it online... the best i was able to do as far as self-exploration was taking a google street view tour. i was able to "walk" amongst the buildings there, and i could see faces staring down from the windows of the tenements - but there was no way of learning anything about the demeanor of the people living there... this video has now provided that facet. thank you for your efforts, \textbf{bald} (and elena)!!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small "This is what I'd expect Banglaldesh or Calcutta to look like"Yeah, well they bring it with them where ever they go. This is the problem, and it's like you said at the end of the video: they're the ones who turned the place into a shithole. They're incapable of living in a civilized manner and there is no amount of taxpayer funded handouts that will change their culture. It's not PC, but some cultures are inherently inferior to others. This is why \textbf{nobody} wants them in their countries and why I don't blame anyone for not wanting them in their countries.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small \@Impeach the orange Clown well, you can only write in the internet "through the chimney". Cause pretty sure you are a \textbf{pussy} to openly call for concentration camps in Germany. But pussies still have internet, right? You look rather pathetic. Like a teenager jerking off while parents do not see. :--)\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Fred \textbf{R\textbf{ed}} bingo\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small \@jacob f I don't know if a person with a flag like yours should be saying this publicly, lol, jk, that's what \textbf{pussy} sjw's be thinking.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small You better be careful, especially for partner.    Its one thing to go by yourself, but quite another to be responsible for a young lady....  I would never have gone their, you are \textbf{crazy}.  LOL.  Well it is very informative and entertaining.    Just be careful.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small If they were only \textbf{communist} it would all get better lol.  I guess comrade Stalin and Brezhnev did not make much of a difference.  They did get a 1968 USSR apartment building out of the deal though.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Crazy video, mr \textbf{bald} a true legend\normalsize   & \cellcolor{green!5}Bald, Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small BALD, PLEASE GO BACK IN TWO MONTHS. IF IT IS STILL DIRTY, FIND THE GUY YOU WERE SPEAKING TO. WE CAN MAKE A MONEY COLLECTION THROUGH YOUR CHANNEL TO EMPLOY SOME OF THE LOCAL GYPSIES TO CLEAN UP THE PLACE … I'M READY TO HELP WITH MY TIME AND MONEY .. WE NEED YOU \textbf{BALD}!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small Jerry Springers final thoughts. 😂\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small surprised there are so many likes. what \textbf{bald} said at the end of the video is such bull shit. how can gypsies being marginalized by all of europe and them making lunik 9 a slum/shit hole go hand in hand? if people are marginalized by society, how can they not make a place a shit hole  dump. \textbf{dumb} assertions by \textbf{bald} and alina in this video. kind of disgusting. look at india and the people there, is it the people's fault that they live in slums and throw trash on the ground? comon, its more than that.\normalsize   & \cellcolor{green!27}Bald, Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}3/98 & \cellcolor{green!27}3.061 \\  \hline
  \cellcolor{green!5}\small well, looking at the number of kids running around all over the place, it doesnt look  like poverty has kept them from jamming a dick in a \textbf{pussy} every spare minute of the day and night\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Bald for President 2020!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small C'mon man....call a \textbf{spade} a \textbf{spade}. That place is shit. They made their own bed now they have to sleep in it. I'd be outraged too if I were a Slovak.\normalsize   & \cellcolor{green!5}Spade & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small bravo mr \textbf{Bald},great video\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small This is why we watch \textbf{Bald}, you just don't get content like this anywhere else! Keep up the great work \textbf{Bald}!!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Sharper Shooter we have loads of these \textbf{gypsy} in Glasgow too\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small The traditional Romanies place a high value on the extended family. Virginity is essential in unmarried women. Both men and women often marry young; there has been controversy in several countries over the Romani practice of child marriage. Romani law establishes that the man's family must pay a bride price to the bride's parents, but only traditional families still follow this rule.Once married, the \textbf{woman} joins the husband's family, where her main job is to tend to her husband's and her children's needs, as well as to take care of her in-laws. The power structure in the traditional Romani household has at its top the oldest man or grandfather, and men in general have more authority than women. Women gain respect and authority as they get older. Young wives begin gaining authority once they have children.Romani social behavior is strictly regulated by Hindu purity laws[187] ("marime" or "marhime"), still respected by most Roma (and by most older generations of Sinti). This regulation affects many aspects of life, and is applied to actions, people and things: parts of the human body are considered impure: the genital organs (because they produce emissions), as well as the rest of the lower body. Clothes for the lower body, as well as the clothes of menstruating women, are washed separately. Items used for eating are also washed in a different place. Childbirth is considered impure, and must occur outside the dwelling place. The mother is considered impure for forty days after giving birth.Death is considered impure, and affects the whole family of the dead, who remain impure for a period of time. In contrast to the practice of cremating the dead, Romani dead must be buried.[188] Cremation and burial are both known from the time of the Rigveda, and both are widely practiced in Hinduism today (although the tendency is for Hindus to practice cremation, while some communities in South India tend to bury their dead).[189]Some animals are also considered impure, for instance cats because they lick their hindquarters. Horses, in contrast, are not considered impure because they cannot do so.[190]Belonging and exclusionEditMain articles: Romanipen and Gadjo (non-Romani)In Romani philosophy, Romanipen (also romanypen, romanipe, romanype, romanimos, romaimos, romaniya) is the totality of the Romani spirit, Romani culture, Romani Law, being a Romani, a set of Romani strains.An \textbf{ethnic} Romani is considered a gadjo in the Romani society if he has no Romanipen. Sometimes a non-Romani may be considered a Romani if he has Romanipen. Usually this is an adopted child. It has been hypothesized that it owes more to a framework of culturerather than simply a\normalsize   & \cellcolor{green!5}Ethnic, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/438 & \cellcolor{green!5}0.457 \\  \hline
  \cellcolor{green!27}\small Most have open fires in their flats, as can be seen from the blackened facades. Most dislike to care for proper rubbish disposal, they throw the rubbish out of the window. Most do not feel any need to pay for electricity and water. They live there just as they lived in caves.I'm not saying that all of them are bad people. But if things are like that, is it a wonder \textbf{nobody} wants to be near them?\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small So ready for this \textbf{gypsy} bonanza... My romani family came to England in 1500s, these people are similar but foreign. It is \textbf{crazy} to see this. Thank you, Mr \textbf{Bald}. You are an excellent presenter. Better watch it, though, because Alina is surpassing her role as your lovely assistant!\normalsize   & \cellcolor{green!5}Bald, Crazy, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Rimrock300  :))) \textbf{dumb} question yeah , i thought they speek russian.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Wow again Alina the best fit bird and best flat stomach. \textbf{Bald} guy is  just a dickhead.........\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Anyone able to go there and acquire some \textbf{Gypsy} tears for me?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Xxpwnage223x First you put tooth of a \textbf{r\textbf{ed}} hair \textbf{woman} in your head\normalsize   & \cellcolor{green!5}Red, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}3/13 & \cellcolor{green!5}23.077 \\  \hline
  \cellcolor{green!27}\small \@VladdyTheBear I can carry a \textbf{woman} against her will for up to one mile\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bankrupt you should totally visit romania!!! especially the northen part like Bucovina or Maramures. you shoul google: happy cemetary in romania, not that hardcore but very beautiful.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald} you ever going to do a live video?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Greetings from Oklahoma City, \textbf{Bald}. I love seeing the sights and places you take us. We can see tens of thousands of videos of all the wonderful monuments and places in Europe but it is rare to get a glimpse into the lives of the indigent people you feel comfortable with.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small In the UK we have people from slovakia  Romania and we hate them because they are all \textbf{gypsy} and live on benefits. They are lazy. I aint \textbf{racist} because i have a few slovakian friends that are hard workers and he knows slovakian are lazy\normalsize   & \cellcolor{green!27}Gypsy, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small You've got no idea what you're talking about...the Slovak government is at fault 100. Those buildings never got maintained since the end of the 80s. There is barely any electricity and no communal services such as rubbish collection occur at stable intervals. Now, maybe a little better, but for decades \textbf{nothing} has been happening in this area. The Slovak government even sterilized the \textbf{gypsy} population in the late 90s and early 2000s. This is a fascist apartheid regime in the middle of Europe that is incapable of providing for its citizens in general. All they are able to do well is be  corrupt and run the country to the ground with loans by using what was built in Czechoslovakia under \textbf{communist} rule as collateral. These east European governments aren't even capable of painting over what was built under communism. \textbf{Nobody} is saying that was a good system, but it was a million times better for the people than this neo-liberal crony fascism they have today.\normalsize   & \cellcolor{green!5}Communist, Gypsy, Nobody, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Roma & \cellcolor{green!5}4/165 & \cellcolor{green!5}2.424 \\  \hline
  \cellcolor{green!27}\small To be fair to \textbf{Bald}, I though he balanced things very well, but many of the \textbf{racist} comments below are moronic.  Gypsies have been persecuted for centuries, something that escapes most of these idiots.  Thanks for the background info.\normalsize   & \cellcolor{green!27}Bald, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Shut the fuck up \textbf{Commie}.\normalsize   & \cellcolor{green!5}Commie & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small You have no idea what you're talking about (not surprising since you're a \textbf{commie}). The gypsies refuse to change/integrate (not all). In middle school there was a \textbf{gypsy} girl in my class who dropped out to marry and be a housewife (I was like wtf?). So what are we supposed to do? Giving them money doesn't work. They receive welfare, housing, healthcare, schooling and they just keep pumping out kids. And you blaming the "fascist" government isn't helping. Maybe next time try coming up with actual solutions. And this is coming from a minority (Hungarian) living in Slovakia. I also had to integrate/learn the language.\normalsize   & \cellcolor{green!27}Commie, Gypsy & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Roma & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small Hungarian here, with a probably worse \textbf{gypsy} problem than our northern neighbors. The truth is : while gypsies are a huge problem, I don't think they could ever be fully integrated and I don't think there's a solution, but they are very friendly, trusting, helpful, fun if you know one.They still have the tribe mentality that we Europeans lost. They stick together, keep their traditions - good and bad ones too - , and are resistant to change that's coming from the outside. For example, they don't say "cousin", but they consider them sisters/brothers too, even very distant family members. Even if somebody moves out from the family home, they still live 5-10 minutes apart and they still spend most of the day together. They consider their friends family members. So if you're friends with one, you're friends with every one of them. If you don't know one, well, they won't be aggressive if you don't show fear, this is the reason why Ben was welcomed there. And yeah, the truth is they are not really poor, but they spend their money on drugs most of the time, be it \textbf{alcohol}, meth, weed, or on just pointless stuff like expensive clothing, cars, etc. When they steal, they do it because they need money for drugs, like 90 of the time.\normalsize   & \cellcolor{green!5}Gypsy, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - Roma & \cellcolor{green!5}2/221 & \cellcolor{green!5}0.905 \\  \hline
  \cellcolor{green!27}\small Dee Raz He did(but much less then he could do), the situation is better then it was before he became the president.The most significant thing he did was probably, that if anyone denies to work(in Hungary the towns are offering public work for those who are unemployed) they won't receive social benefits(but many still dont want to work for the towns because the money they earn is like 200euros, which is even below the hungarian minimum wage (around 400euros) ), but even though this program motivated many of them to get jobs, i wouldn't consider it successful. Another thing what Orban is messing up is the public education(not only for the romani people, but good teachers go to schools where the students are mostly hungarian so they don't have to deal with the problems which are made by the mentality of the parents of those kids) But gypsies who are well integrated, are facing less discrimination today then they did like 15yrs ago(probably has \textbf{nothing} to do with Orban, hungarians probably just regonised ,that well integrated romas can't do anything about many romas being antisocial)\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/186 & \cellcolor{green!27}0.538 \\  \hline
  \cellcolor{green!5}\small Benedek Cseh didn't Orban declare that families who have large numbers of children would get extra money ? The Romanis or Gypsies seem to have more children than the average \textbf{ethnic} Hungarian?\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Dee Raz lol Orbán pretty sure he is gypsy\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small ​\@Dee Raz He is a \textbf{gypsy} too. All he did he gave them fake jobs, and if they breed, they can make more money than a nurse with the fake jobs combined with tax return. :DD Some people say this is better than the past social security system, but this only motivate them to breed more, and also gives more power to the local government to abuse these people, for example who is not voting for Orbán is not going to get these jobs, and without these fake jobs and without social security system, they are totally fucked. So now we have a second baby boom in the slums and they deliver the votes(often with 80-90 voting for the current gov in the high \textbf{gypsy} populated places).\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/127 & \cellcolor{green!5}1.575 \\  \hline
  \cellcolor{green!27}\small Yes the Video was informative and I am also a Mr \textbf{Bald} follower .  Incidentally Slovakia is part of the Eurozone because they have adopted their currency to be EURO..\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small That's such a shame that children are forced to live in such poverty. I cannot believe that children were drinking and shaking their asses in a sexually explicit way at such a young \textbf{age}. It's even more frustrating that many of them will never be able to escape such trash.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Number one reporter. \textbf{Bald} has invented a new form of journalism.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Fred \textbf{R\textbf{ed}} White phosphorus 👌\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small The point about the \textbf{Indian} documentary filmmaker being jumped and Baldy not I mean thats because of \textbf{race} stuff. The white guy card goes far. And no shade about it either it is what it is. Would work against him in Zimbabwe and south Africa but its a boon in Europe Asia and South America\normalsize   & \cellcolor{green!27}Indian, Race & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small He was German not \textbf{Indian} so there goes your r tire \textbf{race} card theory\normalsize   & \cellcolor{green!5}Indian, Race & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Hi \textbf{Bald}!!  Great video.. Keep them coming!🤭\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Our long lost brothers and sisters ....u guys like like my \textbf{Indian} people.......\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That's right.  Anti \textbf{gypsy} \textbf{racism} means they have no future.\normalsize   & \cellcolor{green!27}Gypsy, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small And yet modern \textbf{Indian} immigrants to the West have integrated well, I'd be interested in knowing why the Romani haven't.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Ashish Shembekar Some modern \textbf{indian} immigrants have integrated well...SOME...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{bald} it is the children of pro.....  who robs,  and do all illegal activities. The child to whom u gave the camera returned u back bcoz he didn't belong to that category. This is the universal truth.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Well I think this is the most disgusting video I've ever seen. Every \textbf{Indian} slum is nice compared to this\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small bald just please don....... \textbf{BALD} PLEASE GO TO SYRIA ITS VERY SAFE AN UNEVENTFULL\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small william warjri The fuck kind of logic is this, you are a real \textbf{dumb} fuck.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@6:50 did that guy Mug that \textbf{Old} lady just sitting there for her necklace ?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Also you might be wondering why there are so many gypie kids that learned English in England. Well the truth is that they come to England to claims all kind of benefits. After few years they get deported back to Slovakia. Most \textbf{common} scam they run is that 2 brothers with same surname claim child benefits on kids and as well as each other kids.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Come to Zilina (300km from Kosice) and you can have a ride to Montenegro for free tommorrow (Serbia, Montenegro, Albania, North Macedonia, etc.). Gotcha some \textbf{crazy} places there you would like :P I am serious, contact me if you are interested. We are leaving 22.7. around 17:00, can pick you up anywhere from Zilina to Bratislava. Every year me and friends go thru balkan countries exploring them same way as you do, except we dont use hotels, only car and car tent. Would be honor for me to drink with you :))\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small \@g2 it's actual Slovak national joke, after PM of Slovakia said in TV report " there's \textbf{nothing} ! (In Eastern Slovakia Area)\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small good \textbf{old} brown immigrants\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small One of the most sketchy things I've ever seen \textbf{bald} do, take a pretty girl into the woods where people get mugged. She's got guts lol.😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Gosh \textbf{bald} and bankrupt in my hometown yaaay😂\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Hi Mr.\textbf{Bald}, I'm Slovakian. Most gypsies aren't bad people. Lunik 9 is something else. They will attack other Slovaks soon as they see media or any foreigner they will act completely different. Lunik 9 has been rebuild by the government multiple times. Gypsies destroyed the buildings ripped out the cables and water pipers to sell to scrappers for extra cash to buy dope.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Full Throttle  And do \textbf{NOTHING} to earn money. Unless you count begging and burglary.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small When will you go to Chelyabinsk with Roman Mr. \textbf{Bald}?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Bald, I said this to you once before, and this video is even more stark in how close it is to the movie Import/Export. Truly the last cul de sac in Europe.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Yes I remember your comment mate. \textbf{Crazy} place.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hello Mr. \textbf{Bald} and Alina, great to see you in central Europe!  We are watching your channel for a long time and we are very happy to see you in Slovakia. There is a lot of \textbf{communist} architecture still in use in SK (as opposite to many abandoned and ruined you've showed in your videos from Belarus and Georgia...). Don't you want „a guided tour' in Bratislava (the capital of Slovakia)? We would invite you for a lunch too. 😊 (Anyway, I will write you an email with details.) Good luck, we are looking forward to your future content. 😊\normalsize   & \cellcolor{green!5}Bald, Communist & \cellcolor{green!5} Ideological and Political Identity - General, Physical Identity - Physical Features & \cellcolor{green!5}2/100 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small \@Praise the sun Exactly so, the \textbf{gypsy} \textbf{woman} has in average 4-5 children.\normalsize   & \cellcolor{green!27}Gypsy, Woman & \cellcolor{green!27}Ethnicity - Roma, Gender - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small \@Piotr The people are friendly and say "Dobre" a lot, and the food is super cheap and good quality . THere's not a lot there, it looks like the \textbf{old} soviet union. I never saw areas like this though. The airport was also tiny as hell. Idk it wasn't awful, wasn't great. I just like seeing places.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Dey dont look indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small They looked \textbf{Indian}...\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small At 3:35, when the man said there's no chance, the \textbf{woman} said the opposite: ,,Oni majú šancu,, whats mean, They have chance :D\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Bald this is exactly why I love your content. You go to places no one else will go to and you make the most incredible and fascinating videos there.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small That was a really great and informative video, plus funny especially when the kid denied it was vodka that he was drinking, but instead said it was beer !! That made me laugh !! Also I didn't realise Alina spoke Slovak. I wonder how many languages she speaks, apart from English, Russian and Belorussian? Another interesting fact, which the kid with the camera revealed, was that \textbf{Bald} \& Bankrupt's (the latter name not anymore!!) real name is Ben !!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Yo \textbf{Bald} what is it with the houses ugly on the outside and better than mine on the inside?😂\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Bulk Sales Uk Ltd  Yep. That's what they do. They burgle \textbf{old} folks and pickpocket anyone else. They are vermin.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small There's been cases in Ireland and Greece of blonde children being taken off \textbf{Gypsy} people only for it to turn out they were their natural parents. So don't worry.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small this is why mr \textbf{bald} is my favourite youtuber scuffed ross kemp!!!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small When \textbf{Bald} goes full Borat!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small After thausand year still no integration. Question, how much time will take that fresh \textbf{migrant} from middle east integrate in european society?\normalsize   & \cellcolor{green!27}Migrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small You should add to your name mate - \textbf{Bald}, big balls and bankrupt✌️\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Thank you for this video . We got to see good, bad , and worse . Sad about the children being raised to think this is normal .Basically they created their own slums. \textbf{Bald} and Alaina are a good team when interacting with the people , for sure !Enjoying this from SE Georgia USA ❤️🇺🇸❤️\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Them kids at 5:30 are \textbf{crazy} lol. The kid with the camera is on next level cool.😂 I noticed you like to meet new people and see new slums and poor areas... My question is when are you going to come to America? There are many slums here that are filled with many different races. The building at 8:26 reminded me of Belle Glade in Florida.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small You had some balls my friend glad you got out safe, majority of \textbf{gypsy} people in Slovakia aren't very pleasing.. Greetings from Slovakia enjoy it here! A lot more beautiful places to see than Lunik IX\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@Big Man depends what you're looking for, nature' definitely the Tatras and Slovensky Raj, Pieniny National Park is also beautiful.. castles are a big hit, my personal favs are Bojnice, Spis and Orava castles. Most of Slovakia's beauties are outside of Bratislava contrary to what a lot of Western tourists believe. Cities with more of an \textbf{old} town feel but stunning architecture includes Komarno (altough the majority of people there speak Hungarian) Banska Bystrica in the heart of Slovakia has a very beautiful city center. Just have to look outside of the capital city sometimes' tourists get really drawn into Bratislava, but personally, there is a lot more to Slovakia, and I lived in Bratislava for some time.  Slovakia is a hidden treasure.  Cheers!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/124 & \cellcolor{green!5}0.806 \\  \hline
  \cellcolor{green!27}\small Lol, I'm studying in Košice, but i never been in Luník 9 xD You are so \textbf{crazy} xD If i knew, that you were there, i would you show the best underground bars and pubs :D\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Glad you are visiting India again , Mr \textbf{Bald}.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small 3:33 guy says \textbf{zero} chance, \textbf{woman} says they have a chance.\normalsize   & \cellcolor{green!27}Woman, Zero & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small I always thought you should go to Slovakia but I wouldn't imagine you would go straight to the Lunik IX. When you are in the east you should check out zemplinska sirava. Many abandoned \textbf{communist} buildings. Used to be nice place.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small There's a way to win the respect of ppl quickly.And you are doing it \textbf{Bald}.:)Great\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small 01:00 Marvels of \textbf{communist} architecture: Only the best for the people, very cozy. (In East Germany some  used to call apartments in those buildings "shagging cells with district heating")\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small MR \textbf{BALD} "this is a real sh*thole" 9:57\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Bald I hope you will not become a chronic alcoholic during your Eastern Europe tourne. I couldn't imagine that Slovakia has such a places. Show us more beautiful shitholes from Bulgaria, Romania and Serbia!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small This is the result of when people have \textbf{nothing} better to do than drink and fuck\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small OMG I thought Slovakia 🇸🇰 Rich and clean country but after watching this there are so many poor people 😱 osm documentary \textbf{Bald} 👏🏻👍\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small "We didn't get raped " \& smiled at \textbf{bald} \& \textbf{bald} was like 🤔😅😵 whattttt did she just said . 🤣🤣🤣🤣\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small I think you should buy some land next to Lunik 9, build a mansion then become President \textbf{Bald}, king of the gypsies.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@savvageorge so will i (\textbf{gypsy})move from my house to Luník for president \textbf{bald}?\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald}  it is dangerous I don't care how much you want to simpatize, you went under control condition just like a nuclear reactor test, the uranium however is stil, there.By the way, wtf, this is the center of Europe in the 21 century  how can there be a slum like this worst than venezuela or Rio.. maybe you can organize a gofundme to build all this kids a community and recreation center they can be proud of. Take care\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Wow this is hardcore \textbf{gypsy} area.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small They have jobs every \textbf{gypsy} is not poor im \textbf{gypsy} and i got maybe more money than you\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Best content ANYWHERE.  These adventures are TRULY enthralling. Don't stop \textbf{Bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Bald here is some history which you missed: the \textbf{Communist} had the Idea of the "Perfect" District they called it \textbf{ABC} Sidlisko (Panel housing) - A - Armada (Army) B - Bezpecnost (Police) C - Cigani (Gypsies) the Idea was that if the Gypsies would have the military and Police personnel as they neighbors then they would behave...well it did not work and now on the 1 square KM that is LIX 7000 Gypsies live...\normalsize   & \cellcolor{green!5}ABC, Bald, Communist & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - Chinese, Physical Identity - Physical Features & \cellcolor{green!5}3/75 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Bald upgrading from the Ray-Ban's to Prada sunglasses.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small To be honest even when you say, it is not that bad. You are still pretty lucky to not be robbed. These places are known for that and that is also the reason why \textbf{nobody} come there.  They dont like strangers. I can imagine even police beying so pissed of to go there. I would say you again found some decent guy who gave you tour around and because they know him, he kept you save. Still i am impressed how alina speaked to that slovak. I could understand almost everything :D\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small Indian colonization of europe. Here we go\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small You have to visit Ferentari Bucharest please \textbf{Bald}!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Mr. \textbf{bald} always make a bold move. 😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small They don't use bins because they are gippos \textbf{bald} man\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small 8:08 Be careful \textbf{bald}, Lukoshenko is going to steal you girlfriend\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small So you are now in Slovakia? No goodbye Georgia? By the way I am not sure how they ended up in Europe but those gypsies are actually \textbf{Indian} in origin like he said. So Alina speaks Slovakian? By the way you touched a very sensitive spot dragging Kolkata into the slums- especially that you have not been there.....Kolkata is NO different to big cities in the United States- just that the US cities hide their stuff well and there is some order with regards to traffic, health and sanitation.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small Tenet P.S. 25 is still a kid as far as I'm concerned. Looking back now I still had a juvenile mentality into my early 20's. I'm not proud of it but it's the truth. It's just sad when I see people resort to that at such a young \textbf{age}. But I get it, what else is there for him there. It's a catch 22.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small \@NSA 000 I think it depends on the person, but by the time you're 20 you should have yourself well put together and not acting like an 16 year \textbf{old} kid, but that's just me.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small You don't have to worry they take anything from you because you are \textbf{Bald} and bankrupt..😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small i went to the philippineshorrible experiencefirst this young \textbf{woman} stole 20 dollars from mebut that was not the worst part20 minutes later....SHE RAPED ME !!OMG HORRIBLE PLACE\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Well I think big part of this is the way they approached the settlement. Like lil guy who had camera said: Englishmen gave me camera don't do this. As if : hey be careful how you act here ; this will be shown to the world. They care when they feel they are observed by world...but when you're just total random without a camera or many fans who would miss you... I don't know: I would be worried. I'm sure a lot of them are nice but I wouldn't come into their settlements like that : p \textbf{Bald} knows how to approach them ; he has charm; I don't : >\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small \@HQMix Did you ever encounter \textbf{gypsy} societies in your life?\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small They didn't just show up there unannounced and started walking around the place filming. If they did things might have turned out diffrently.  For sure they had been in touch with somebody from there. This video was heavily scripted. What with the oh so casual \textbf{gypsy} wedding party and Alina's interview?  They were the guests of the gypsies. It's disingenous to believe that everything in this video is as impromptu as the twerking bit.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small ​\@Jim B What makes you think that I didnt? Cause I understood what she was trying to say? I live in this very city maybe 4km away from Lunik IX my friend. We had couple of gypsies in classroom in elementary school. I meet \textbf{gypsy} people almost every day in my hometown Kosice. All kinds of them. There are asocial gypsies who failed to integrate, they live in slums in many Eastern Slovak villages, they dont work and dont know any better. Then there are gypsies who live like normal people. Go to work, kids go to school... They might have more temperament in general, but they are valuable part of society. PRoblem with gypsies is largely historical issue which I believe can be fixed. Because we have some positive examples where integration worked pretty well. Take village Spissky Hrhov as one example. Google it, I believe you will find about it something in english too.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/156 & \cellcolor{green!5}0.641 \\  \hline
  \cellcolor{green!27}\small \@curioso you must be able to understand that all good for audience are scripted before its shown. Mr \textbf{bald} is no immature in this regard.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Empor ! Writing Makedonia talking about some kind of \textbf{nation} that has \textbf{nothing} to do with Makedonia is at least stupid.\normalsize   & \cellcolor{green!5}Nation, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small \@beckys2222 Ofc they say that. Sounds better than "I'm a \textbf{gypsy}."\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small karapuzo1 yes she can actually speak a little and understand also it's Slovakian not average Czech that's why \textbf{bald} referred to her a lot\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small FrozenFrost it's pretty much a Eastern European staple you'll find slums in Slovakia, Ukraine, Hungary etc there all just Romani people mostly though as you can imagine after world war 2 they weren't treated the best kind of like \textbf{African} Americans there's a lot of civilized and well thought Romani but the majority for some reason like living in a cesspool\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small beckys2222 uhm? No not at all do you even know what a slum is? Has \textbf{nothing} to do with mass immigration also Romani people have \textbf{nothing} to do with Romanians you uneducated fuck and I'm not defending either people group the Romanians are just as bad\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small They are the sort of peoples who wear their hearts on their sleeves...You can draw an analogy with \textbf{black} slaves who were brought over to the Americas over the centuries, they were quite similar and indeed were persecuted for a long time by the ruling classes. These were believed to be notions termed as \textbf{racism} but it's not. It's actually more a question of ego.\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@Thr1ll B0real Every slum ive witnessed is full of brown/black immigrants. You must be one of them so please go home and rebuild. You people are destroying Europa and we're done with it. I voted \textbf{Brexit} for this very reason and no other.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@Alex Werner Its \textbf{crazy} , when i was i Germany last year i was forever being asked for directions as the Asia tourists thought me and my friends were German. In reality , we were the only white people around. Smh\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Yess! I've been eagerly awaiting this epic next chapter. But the people of glod may implement another lawsuit siting improper compensation for appearing in the video if \textbf{bald} isn't careful!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Such a great video \textbf{Bald} and Alina!   Harrold would approve!!  😂😂😂\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Holey shut \textbf{Bald} I've never believed you would come here! :o\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Dustin Q Lol...\textbf{nothing} to do with centuries of mainly Caucasian countries pillaging their minerals, resources and people.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Linckel When you take everything from a generation, how are the coming generations supposed to recover from that? Especially when there are \textbf{racist} people that will look down on another human being because of their skin color and where they're from. That is why \textbf{alcohol} and drug abuse is \textbf{common} in poverty stricken areas. I'm not trying to "excuse their behavior" but you really need to look at the psychological aspects of why things are the way they are.  Not everything is as easy as "well why don't they just stop doing that?"\normalsize   & \cellcolor{green!5}Common, Racist, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}3/93 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Barbados, Bahamas, Qatar, UAE and others have seceded and prospered. Sometimes a \textbf{nation} has a negative mindset and that coupled with their corruption makes them more likely to fail. Fuck them I say, they were given a hand up but couldn't use it.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Shit,this is europe? \textbf{Bald} was right,It looks like the slums of Dhaka (minus people drinking and doing drugs),even my grandmas \textbf{old} crappy village house is better then the one at 10:25\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Looks like a proper \textbf{indian} shithole. Must be in the genes to live in such conditions.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small just abandon that wemon and go back to the good \textbf{old} days\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Do you think Alina has fukked the \textbf{bald} \textbf{old} a\$\$ guy yet?\normalsize   & \cellcolor{green!27}Bald, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small G'day mate from Australia... I enjoy your videos a lot.. I think you are a mad bugger though for some of the dangerous places you go.. I hope you will always be safe... I notice with your vids it is the people with \textbf{nothing} that are the most generous... Look forward to the next video...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Looking at those dirty \textbf{Gypsy} fuckers, you fully understand why the \textbf{Nazi} party rounded them up.\normalsize   & \cellcolor{green!27}Gypsy, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Roma & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Bald it helps you walk around with hotties . Keep up the good work\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Video was amazing, I have a cousin working is a \textbf{gypsy},  actually has good life. My family is from Slovakia. I'm always amazed that when wedding and special moments they dress amazing. Love the music and festivities. ⭐️⭐️⭐️⭐️⭐️\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Every video ever posted by \textbf{bald} and bankrupt:possible danger ahead"Let's see what happens to us."\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Like how \textbf{xenophobia} isn't tolerated against most minorities except gypsies. People should get out and meet real people you might realise they're just as human as you and me. Perhaps the real sub humans are the 1 elite that create these slums and steal the worlds wealth. Food for thought 😊\normalsize   & \cellcolor{green!27}Xenophobia & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small So basically those people live like like \textbf{pigs} just because they are \textbf{pigs}. Just litter, drink, fuck - that's all they want. Well, ok. It's theirs choice. P.S. Wow Alina also speaks Slovak(if that was it was). That was unexpected.\normalsize   & \cellcolor{green!5}PIGS & \cellcolor{green!5}Nationality - Southern European & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small ive lived in slovakai for a while and i had so much fun. !! i hope you have fun \textbf{bald} and bankrupt. you are going to enjoy it!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small You're \textbf{dumb} as fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald}... Most YouTube couples travelling the world are rather boring, with their jazzy background music, Instagrams and cappucinos, but you guys are something else entirely. You make us laugh, and sometimes cry, and sometimes we worry about you.  Please keep Alina safe. She's pretty special. And you are too!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Bald you should come to Hungary pls!!!👀\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small You did not mention one thing. For a long time, the city was putting all people who weren't paying their rent to Luník 9. That's why it became so f...ed up. The city itself created this mess and it was pushing the problem away. Deeper reasons lay within our own \textbf{racist} society. After the collapse of socialism, the private and public sectors were not willing to employ Romas and if something like this goes on for decades, you're in deep trouble.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small I almost break Mr \textbf{Bald} teeth when he was in Jaipur India for teasing  girl.  But fortunately I'm his big fan now\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Anyone else misses the type of video's \textbf{Bald} would give us when he was in India? I honestly can't be bothered with these anymore.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Bald you are getting Closer to my Town Ostrava, come and i will show you some \textbf{crazy} Sh*t :P\normalsize   & \cellcolor{green!5}Bald, Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small in poland gypsies also got free flats. Gov build a whole new apartment building for \textbf{gypsy} families. It last not even one year and those ungrateful people turned it into Lunik style stuff. They even cut out power wires, water pipes and toilets from walls and to sell it. BUt hey its part of their culture right\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Your summary, \textbf{Bald} (13 min), was fair, and spot on.And the lovely Alina, really adds to your video,don`t lose her...compassionate ,intelligent,and easy on the eyes..\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small I carry \textbf{gypsy} tears, always\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Damn didnt knew Slovakia has so many Gypsyes .But i dont think is fair what \textbf{Bald} does on his channel . Every new Country he visit he find the worst shitiest place possible . I know he doing this to get more viewers only but people may do a terrible impression about a Country just by seeing this video only. And dont think this is fair. This channel is like exploring the shitiest places on this planet lol.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Bald, I am from Bulgaria and there are gypsies here too. In the second biggest city in BG, Plovdiv, there's a slum called Stolipinovo, which is something like Lunik 9. Many gypsy-defenders from the West went there and said "\textbf{nobody} robbed me, they are good people, Bulgaria is \textbf{racist}", but when you live here you see their real side. I know there are some, that are intelligent, but mostly they walk on gangs and then it's dangerous. Most of the cases of robbery are from gypsies.Gypsies also influence our culture very badly, which brings negative points against them too.  Most gypsies have very bad character, they are very likely to lie. They have a really big problem integrating their culture into European.P.S: When are you going to come here? If there isn't anybody who offered you, I can tell you where to go? :Д\normalsize   & \cellcolor{green!27}Bald, Nobody, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}3/146 & \cellcolor{green!27}2.055 \\  \hline
  \cellcolor{green!5}\small Bald is hitting 10+ on reactsThe next Jenna Marbles?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Not everyone's charisma and street smarts are at you're level \textbf{Bald}. People going to a place like that without those tools are going to find themselves in trouble!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Bald is from Brighton and you have to be double hard to live there. I'd say \textbf{bald} would be used to the punch ups and you can tell he can fight by looking at him\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small MR \textbf{BALD} AND MS ALYNA GREAT JOB. THE HONESTY AND TRUE CARING WITH NO BULL IS WHY THEY GET ACCESS ALLOVER. GOD BLESS YOU BOTH 😇👌📷🎥👋🗽\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bankrupt \textbf{Bald}, go to Bratislava - it's a lot of fun and you'll get plenty of material to shoot there. if you want some tips, hit me up, I'll advise you.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small bald and bankrupt if you fancy hiking i recommend visiting high tatras, overall Slovakia has beautiful nature and terrible government. Cities are basic boring Eastern European-ish cities. P.S. The saddest thing about these \textbf{gypsy} slums are that working people payed for those buildings and they destroyed them.\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small \@\textbf{bald} and bankrupt too boring for everyone looking just for idiosyncrasy and strangeness\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small it'a messed up how they are perverts from a young \textbf{age} to their girls\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Channel name needs changed from \textbf{bald} and bankrupt to \textbf{bald} and alena\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small This channel should be renamed \textbf{Bald} and Alina\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Third World or \textbf{Alien} World 👽\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small what a shit hole mr bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small OUTSTANDING!  Bringing the world, the real world, closer for all of us!  The power of your work/youtube has, someday,  offers the potential to begin to solve the problems of poverty.  That's powerful brother \textbf{Bald} and sister Alina.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Gypsy logic i was born in Slovakia therefore I'm slovak... yeah that's not how it works\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald} and Alinchik should go on the H3 podcast!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small From 5:17 to 6:49 some of those kids are speaking pretty decent English to the point where they know British-Patois slang like "wagwan". Their accent also sounds pretty close to what you'd expect from some working class \textbf{ethnic} minorities in Britain. What's the story behind that? They must've spent a good amount of time in Britain mingling with natives to pick up on that accent.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small \@Cuckasaurus Rex Right, which is why I said British-Patois slang. Could've been more specific but that's generally understood as the speech patterns of British born, ethnically Jamaican, or more generally Caribbean people. It has obviously spread over to other ethnicities as well. You can now hear anything from whites to South Asian Brits in certain ares of East, or South London (and many others all over Britain) speaking similarly. My point wasn't about knit-picking definitions though. I was just wondering how some kids from a segregated \textbf{gypsy} neighbourhood in Slovakia picked it up, to the point where both the accent and jargon are on point?  Surely, it must come from significant exposure to people with those accents, rather than just watching a few grime videos on youtube. Surprised \textbf{bald} and bankrupt didn't investigate...\normalsize   & \cellcolor{green!5}Bald, Gypsy & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}2/133 & \cellcolor{green!5}1.504 \\  \hline
  \cellcolor{green!27}\small \@Cuckasaurus Rex Which generally requires very close contact with those who have it in the first place. Just wondering what the story was. The odds of a kid in the biggest \textbf{gypsy} slum in Europe speaking hoodlum East London slang and barely missing a bit on the accent are quite slim. If you've got \textbf{nothing} to say and you're just trying to be cute and make small talk, keep it shut and keep walking buddy.\normalsize   & \cellcolor{green!27}Gypsy, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/75 & \cellcolor{green!27}2.667 \\  \hline
  \cellcolor{green!5}\small By the way the jacket was a symbol of skinheads in the 90s. Mr \textbf{Bald} can wear  anything  with his personality 🔥🔥👌😂\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Im Mr Balds \textbf{Age} and I had one .... in like 1988\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Bro visit some \textbf{old} \textbf{communist} parts of Slovakia some villages are pretty out there\normalsize   & \cellcolor{green!5}Communist, Old & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Andy Mc L  the hotel in Folkestone seems similar to the \textbf{gypo} block of flats in the video lol\normalsize   & \cellcolor{green!27}Gypo & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I like the balanced assessment at the end.  At some point - you need to take responsibility for yourself.  But kids aren't \textbf{old} enough to be responsible.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small ✨💖✨ \textbf{bald} \& the beautiful ✨💖✨\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small There's a high chance you won't get robbed in this place (or any other \textbf{gypsy} slum) if you bring the camera. They like to be recorded for some reason. Government has completely gave up on them, cleaning of the place is so expensive and useless. These blocks are slowly being torn down but it's almost impossible to intergrate the gypsies into the society... Anyway, thanks for the video, greetings from Slovakia.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald} you've got enormously big balls going there, the gypsies look a friendly bunch.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small bald and bankrupt: Let's have some fun in Lunik 9Karl Rock: Let's get scammed in Lunik 9\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small This is \textbf{crazy} shit literally never seen footage of this\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Slavo Danko How \textbf{old} is she? Do you know?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I hope you show other sides of slovakia too Mr \textbf{bald} 🙆\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{black} and I keep wondering if that'll put me at some disadvantage in places like this if I went.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Viktor B I hate the word and was debating using it in my head, but decided on it as it was meant for Bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@Viktor B \textbf{Immigrant} is the correct word, not "\textbf{migrant}".\normalsize   & \cellcolor{green!5}Immigrant, Migrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small There is \textbf{nothing} for the children! A playground will be such a diffrance for them😯\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Don't think its possible to make really positive content about the situation but you gave it the good ole college try bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Great video, I really appreciate you showing places that the general public in Europe turns a \textbf{blind} eye to\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I've changed my aim in life. I want to be mr. Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small The ten years \textbf{old} boy said .."look at that ass"\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Hi \textbf{Bald}. you come in everywhere with no attitude. kindness and love..You truly want to know the people..that is why you can go anywhere..Keep up the peace and love..\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small We Indians feel the same when foreigners visit \textbf{crazy} \textbf{old} Delhi and slum in Mumbai.. most of India videos r about those two places..lol..\normalsize   & \cellcolor{green!27}Crazy, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{Bald} was just being diplomatic, we all know how gypsies are, blaming everything on "but they're being discriminated for centuries" well why would that be?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Coffee Pjesht It's not so bad - \textbf{Bald} has just picked the most notorious example. In Romania, Bulgaria or (maybe) Hungary it's definitely more relevant issue.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@A Miller exactly who should be ashamed and why? They are masters of their own luck and fortune. \textbf{Nobody} is forcing them to live that way. Even if slovakia was the richest country in the world, gypsies would still be living like they are now. Just because country is rich does not mean it is obliged to give away free money to  people that are just a waste of space. You sound like a \textbf{cuck}.\normalsize   & \cellcolor{green!5}Cuck, Nobody & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small sounds a lot like arabs and \textbf{black} people in sweden\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small ricky coker \textbf{Bald} should have asked why they were in Derby, unfortunately I bet it was a massive benefits scam or pick pocketing. I feel for the kids and the animals.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Kind of like where I am. Not trying to sound \textbf{racist} but when blacks move into our cities they turn neighborhoods into disasters which is their way of living. I don't feel \textbf{racist} when I'm saying it because it is obvious and the evidence is in front of everyone's eyes the behavior and thug trend but \textbf{nobody} steps in because of the laws that protect. When the businesses collapse the economy goes which means welfare is overthrown by irresponsible thugs.\normalsize   & \cellcolor{green!27}Nobody, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/80 & \cellcolor{green!27}3.75 \\  \hline
  \cellcolor{green!5}\small It also doesn't help that when they're given brand spanking new apartments the bills don't get paid, copper wiring disappears and insulation is looted and sold and trash starts piling up etc. The government trying to make sure the children come to school after the parents receive child support from state as well as a stipend for school supplies is decried by them as tyranny and other nonsense that generally makes people believe the stereotypes about them. Them forming begging/scam rings is also not uncommon despite them not generally being violent, although it only is a minority who does it it still sucks when they're the prominent ones.I appreciate  that for hundreds of years they were repressed and marginalized, but that was mainly because of their stubborn refusal to integrate, which you can still see to this day, even in this video, they keep claiming to be slovak, but how many Slovaks do you see living in ghettos, polluting everywhere and leeching water, electricity and internet/tv? Even the poor \textbf{elderly} in forgotten villages who struggle to live and have every reason to not give a shit about a country that abandoned them don't behave this way.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/197 & \cellcolor{green!5}0.508 \\  \hline
  \cellcolor{green!27}\small Harhar, comment sector full of Slovakians blaming on the situation on just \textbf{gypsy} population but why there are no \textbf{gypsy} slums in Nordic countries even they have \textbf{gypsy} population? Hmm. could it be that we have had better integration and we have not kicked gypsies on the head so much as Slovakians and now you have the hurry to explain what is happening in your country?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}3/66 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Your friend Harold invading world heritage site in Sri Lanka and you are invading \textbf{gypsy} slum in Slovakia. I wish I could invade both your house in England and Norway now...\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Part of \textbf{Indian} likely cities\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I'm scrolling through the feed and see Mr \textbf{bald} visited my city and ... Lunik 9 :D I've never ever went close to the place and I've been living here for 17 years. Most people avoid gypsies in this town including me but if you treat them normally they won't rob you or hurt you as many people think. The place is getting better partly thanks to the local church and social workers. I hope you visit better parts of Košice or Slovakia, have fun here!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small I didn't expect \textbf{bald} to visit countries outside of the former USSR but \textbf{gypsy} ghettoes are his style I guess\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small yeah it's like .. I as a Czech person can understand a little from f.e.  Polish, Croatian, Slovenian people but not that much from Russians, Bulgarians etc. Only a few words that sounds like they have a very \textbf{old} Slavic language roots so it's a little bit similar.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Jon Snow oh believe they are \textbf{indian} originated..kids literally looked like Indians\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Wow Some children hete are exactly same as \textbf{indian} children sp. Boy with glases i m from india\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Its not about \textbf{race}, its about behaviour\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Hearing \textbf{gypsy} kids In the slums of slovakia speaking english with a West mids accent saying "wah gwarn" 😂😂😂😂 never did I imagine that\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small The \textbf{crazy} Tories want to end freedom of movement.  Why would you do that? I love diversity. ❤️❤️❤️\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@catscats50 if anything it's not the Tories, it's the far right parties. Also as a foreigner, from my understanding I could move to the UK once \textbf{Brexit} happens there will just be stricter policies. I despite \textbf{Brexit} want to attend Cambridge University when I grow up.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Yuri Petukhov If you are a Russian you will have equal rights with the people of Czechia to study in the UK after \textbf{brexit}. At the moment you are discriminated against.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small \@Yuri Petukhov if you're educated enough to come to Cambridge, you'll be let in \textbf{Brexit} or not :)\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Yuri Petukhov Learn to spell. It's the Far left retards who love "diversity". Freedom of movement is a BAD thing for a country. \textbf{Brexit} is a good thing, it will make the UK safer from illegal immigrants and pikeys etc. Legal immigration = ok. illegal immigration + bad.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small \@Adam Potter Ya in for a shock mate when it does happen. Ya know those thousands of \textbf{fruit} and veg pickers etc who come here from Europe every year... after \textbf{Brexit} they will still be needed... but now Mr Abubhakar from Abbottabad will be on equal footing as Mr Wozniak from Warsaw to apply for the same job. And he might work for even less too.\normalsize   & \cellcolor{green!5}Brexit, Fruit & \cellcolor{green!5}Nationality - European or anti-Europeans, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Mário Podolan No... very few people get deported sadly. Our immigration policy is effectively equivalent to ‘let them all in'. What likely happened is that various \textbf{immigrant} groups with regressive and primitive mindsets congregated to particular neighbourhoods in Derby, this means that the worst aspect of all those cultures are combined and there is conflict and tension and violence between those groups. They probably ended up creating more depravity than they left behind in Lunik, thus they returned.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Adam Potter It's not going to change much, sadly. We will likely see even more \textbf{African} migrants. Our government has no interest in reducing migration.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Jon Seymour After \textbf{brexit} the nature of immigration will not improve.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Um... is this what is called "poverty porn?" We get to see poor people living in the worst possible conditions and then pat ourselves on the back, saying, "At least we're not THAT bad off!" and then do \textbf{nothing} to change the situation we privileged people or the poor are living in? Maybe it is good that we see how the poor live, but it should motivate us to improve their condition, not to get all smug about our superiority. I think Ben is walking a tight rope here between providing a genuine service by showing us people and places we might never dare try to experience on our own, on the one hand, and profiting from the misery of those people on the other hand. I will keep watching and, in the meantime, giving money to a home for \textbf{old} people in Moldova through GlobalGiving.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/146 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small mr \textbf{bald} and pewdiepie in brighton hookup\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I hope it's an \textbf{old} video,still waiting for the next video from Georgia\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small No, \textbf{bald} and alcoholic is more acurate\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Dawid Lyczko Nah, more like \textbf{bald} and bankrupt countries.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Or Beauty and the Bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Bald and beautiful... where did I hear that before? .... DAMN! This show is STILL running? That's almost as \textbf{old} as I am.\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small bald and jolly coz Alina is always jolly xD\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small You think that \textbf{bald} is beautiful?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small bald and alenchik\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I would hazard a guess that they have garbage everywhere  because they don't pay any utility bills so the local county doesn't send any garbage collectors. I bet they would cut their electricity and water as well, but then they would riot. And no, they might be born in Slovakia but they clearly are from India even after all those generations. The level of squalor they are willing to generate and willing to live in is not what a standard European would be OK with. This is some \textbf{Indian} level stuff.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Is it just me or does \textbf{bald} always try to put Europe down\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small come to Dunamocs in Southern Slovakia \textbf{Bald}! happy to host u!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small bald and bankrupt is now a certified journalist, no doubt\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Vitaj na Slovensku \textbf{bald} (i ked vtej najhorsej casti). Alina, ale hovori takou CeskoSlovencinou :)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I don't want to be \textbf{racist}, but I have to say that \textbf{gypsy} people are the 'trash' of Portugal.\normalsize   & \cellcolor{green!27}Gypsy, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small When people come there with camera, they r kinda nice to you, but try to come here as normal slovak person and u'll see what's really happening here. City government gave them public transport line for free because they r not paying for tickets, they broke couple of windows on buses and the driver is covered by window from the rest of the bus because they attacked drivers quite often, kids from this ghetto are jumping in front of cars on nearby road causing multiple accidents throughout the year, nearby suburbs have walls against those people cuz they tend to sneak up in night and steal from people, Luník 9 was built cuz of gipsies living in \textbf{old} town small streets and in abandoned houses\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/125 & \cellcolor{green!5}0.8 \\  \hline
  \cellcolor{green!27}\small I'd just like to say that this place is a disgrace to the city and to the country even. I live in the city of Kosice and there's a lot more to it than just this. You were really lucky not to get mugged during filming your experience. The guy who was saying they're about the clean the rubbish around their flats.... I guarantee they're not going to clean anything, because that's just who they are. There are some decent \textbf{gypsy} people ofcourse but that's just one in a million. Almost all of them are animals. Everyone in the city despises them.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small Wow. Journalism as we once knew it is dead. If you want to see what's really going on in the world just subscribe to \textbf{bald} and bankrupt, Indigo \textbf{Traveller}, Empire Files,etc. Any other suggestions out there? Mr. \textbf{Bald}, thanks for keeping me informed and entertained. Greetings from Texas.\normalsize   & \cellcolor{green!5}Bald, Traveller & \cellcolor{green!5}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!5}3/48 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Alif48 true,mr Harald and mr \textbf{Bald} are very good tem\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small try Harald Baldr  chanel,very good,and he is a friend of mr.Bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@TheTruthIsFiction Harald is trying to make himself look better... If you watch a video from Harald where him and \textbf{Bald} are in India he seems chill. If you watch \textbf{Bald}'s video from the same place all you see is Harald being pissed off and having no chill. In both videos \textbf{Bald} is chill.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small Welcome to Kosice Mr.\textbf{Bald}.Waiting for more videos from Kosice.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small This is in no way to be \textbf{racist}, but the littering ect. is also evident in northern europe in the \textbf{gypsy} camps you see in parks and forests. It honestly makes me think its a culture thing.\normalsize   & \cellcolor{green!27}Gypsy, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Roma & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small What worries me is that these people keep on having babies although they are poor and they have absolutely \textbf{nothing} to offer except poverty.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small listen up \textbf{indian} slovaki, i cant see whats in your heart, but i can see the colour of your skin and i can look up statistics based on where you live.that is what ill judge you by - what i can confirm\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Holy shit I'm so privileged to live in America. Wow! This really woke me up. Great video \textbf{Bald}!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small It turned into a \textbf{gypsy} slum, because thats what gypsies do. The government actually tried to get rid of all the garbage and fix the buildings, but gypsies doing \textbf{gypsy} stuff.....\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small \@BEEN BRACKIN See my reply above \textbf{libtard}...\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Bald moving up to 1mln subs. Blowing up in the overseas.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Good one Baldy, tough situation. Identity is a complex thing, it seems like a part of the way peoples act is through the way they are treated. Socially marginalized groups act 'marginal' in so many ways. It's easy to say from the outside 'fix yourself' but when put in an environment where so many of the cards are stacked against you I could imagine how some would just say f it. Very interesting look at things,  other \textbf{gypsy} communities would be awesome!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Bald is a visibly kind-hearted person and acceptable to everyone.... rarely available personality indeed....\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Bald and alenchic you both have big balls. Its pays off.  Love your work and videos are one of the best on youtube.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small That kid filmed a cool little party. Music was banging. And full of loose \textbf{gypsy} women. Looked like a good time.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Those kids need a serious ass whooping if u ask me 😎 not the one with the camera but the one he filmed. Lol. \textbf{Crazy} shit\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I wonder if the group \textbf{Gypsy} King lived like this before they became famous?\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Well, they live In Europe, with all the European opportunity. And they still make it look like Pakistan. People make nations, \textbf{nothing} else, some people are more prone to be... Well let's just say they won't create an empire where the sun never sets\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Bald, I like your videos but you are absolutely nuts taking your girl in that place. She must really like you to stick around for some of these insane trips, especially this one. Gypsies are not all fun and games, they rob, rape and even stab people.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small At 3:50 is that girl rocking a R2D2 dress or am I \textbf{crazy}?\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That one apartment was nice because, it belonged to the main \textbf{gypsy} man of the Lunik 9. xD Taxing those other fools\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Looks like Hackney lol😝 you know they are 100 \textbf{gypsy} by the girls dancing\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small 👍Stunning \textbf{Bald}! You and Elana deserve an award for that.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small BBC we know why you've resorted to mugging the over 75's  \textbf{Bald} certainly spent less on booze than John Sweeney in PANDORAMA ......Time for a ((Waaaaah)) Tommy\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@James Douglas Yeah, I've seen documentaries about their camps in Spain and Italy, and they literally sell their children who are better thieves. They use a trick to scam people for money, where a \textbf{woman} takes a baby, give's it a little bit of whiskey or some hard \textbf{alcohol}, and she sits in the streets saying she need money for her child. In some cases I read of, the baby died. It's disgusting\normalsize   & \cellcolor{green!27}Woman, alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol, Gender - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small He's definitely banging this \textbf{chick} he's always with lol\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Bald had to shell out a few cases of vodka dosh protection\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small So THIS is the \textbf{gypsy} part of town!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Bald} where is the next step- Asia, Africa?  Take care, your biggest fan!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small You are a legend \textbf{Bald}. The world would be a better place if there were more people like you!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small wut? i am india i have no idea what this \textbf{gypsy} guy is speaking haha, maybe pakistan.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Two friends of mine were attacked by at least 10 Romanof \textbf{Gypsy} kids in the 12 yr \textbf{old} range, they most everything, glasses ,watch, money ,I said did you fight back ,he said I kicked one so hard I lifted him off of ground , he's gonna remember that for a long time. They still got everything ,these two Guys were not wusses ,this happened in Paris in one of Squares. I would gladly contribute towards liquid refreshments if and only if they get their property cleaned up.This actually surprises me , The Nomadic Life I understand,  the litter   NO !\normalsize   & \cellcolor{green!5}Gypsy, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!5}2/101 & \cellcolor{green!5}1.98 \\  \hline
  \cellcolor{green!27}\small Hi Mr \textbf{Bald}  How r u\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I was thinking of leaving a comment on one of your videos asking you to take a look at eastern Slovakia, but I thought to myself that it's not going to happen since you speak Russian and the Gypsies there barely speak Slovak. So I was quite surprised when I saw this video in my recommended, and it made me smile seeing the inter-Slavic communication between Alinchik and the \textbf{Gypsy}. Keep up the good work and maybe take a look at the Balkan some day, particularly Bosnia or Bulgaria\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small Alina \textbf{Chick} the Boss! She does not want to hear how the Trash got there - Just tell her how long it will take to Clean - Period! Nice\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@Karedog Maybe so - But you never know if \textbf{Bald} promised them Cash or Vodka or both if it is clean when they return! Never Know!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small The \textbf{bald} and the beautiful :) Living in a slum, the people seems to look healthy and happy. Amazing! Google map: 48.695833 21.223611\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Little Ears why are you \textbf{racist} lmao they will eat him or what?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@F. B. I \textbf{nothing} to do with \textbf{race}, just facts. Go live near an area like this for 6 months, you'll become pretty "\textbf{racist}" :)\normalsize   & \cellcolor{green!27}Nothing, Race, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/25 & \cellcolor{green!27}12.0 \\  \hline
  \cellcolor{green!5}\small This is why we watch \textbf{bald}.Everyone: Dont go there!\textbf{Bald}: Im there!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small OG SHITHOLE people \textbf{nobody} wants them to be there neighbor\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Arab Trappers Our government can't do shit about them. They constantly keep building a new houses for them but you can see how they treat it. Money the recieve monthly is spent on \textbf{alcohol}, cigarettes etc. They don't send their kids to school and when they do the kids threaten others and they usually drop it so it doesn't even matter\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Mathilde Wesendonck It happens a lot in Germany. And the authorities can‘t do shit because they can‘t tell from who it was and \textbf{nobody} will talk to them.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@Matej Šuhajda same in Toronto .  \textbf{Pigs}.\normalsize   & \cellcolor{green!5}PIGS & \cellcolor{green!5}Nationality - Southern European & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small such a b.s. you \textbf{dumb} fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@razbijenhr you are \textbf{racist} thats not true some are good like me and my family we have clean in my home and never been dirty\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Michael Cozza im \textbf{gypsy} and i am normal how is that possible\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@F. B. I he's not \textbf{racist} for telling the facts. Although the reasons for them to be like that "generally" speaking is also our fault for treating them as subhumans\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Wrong. Local government does organize a big clean up from time to time. Months after the place is full of rubbish again. They've been given rubbish bins but those ended in scrap yard. Same with radiators. Windows provided, got torn out and burnt. Inside the flats. Because bashavel - party must go on. Three to five days of nonstop parties and then they have \textbf{nothing} to eat until next month's social security pay check. Gypsies can live a good life but only if they leave their community. Bad examples are strong, when those kids see such way of life everyday, this is what is going to be of them.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small Crazy hearing those English accents, I wonder how long they spent in Derby.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Fid Fyodor Don't generalise and don't be stupid \textbf{racist} either, please. There are many decent hardworking Gypsies in Slovakia (and in other countries, too). Even among Gypsies you have more tribes and communities, which differ in social situation, etc.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small S S lol I'm from Derby. We had some gypsies settle in a nearby park and they did \textbf{nothing} but cause trouble and litter. After they left, the community planted trees in the area to stop them from doing it again.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Are people really \textbf{dumb} to think white majority countries have a problem with different skin colour and not the obvious trashy culture that will cause any society to regress back into the Stone \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Dumb & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small A big thank you for showing us places that I would most probably never visit in my life. You're better than any travel channel. Keep up the good work Mr. \textbf{Bald}. You're my favourite vlogger.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small the trust \textbf{Bald} has in humanity, it's adorable. you are the saint of youtube my man\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I'm from Slovakia Košice and these people make a bad name for us make sure you check out the \textbf{old} town part of our city too mr.\textbf{bald}!\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small I bet they robbed some shit from bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@daVe Clima I´m not \textbf{gypsy} so i cant´t be from romania so stfu lol.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small You should go to the \textbf{gypsy} encampment near vilnius.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small one of your best video \textbf{bald}.. most happiest men and sexy gypsie girls from india migrate all over. human \textbf{race}.\normalsize   & \cellcolor{green!5}Bald, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I thought some parts of the uk are bad , your a brave man mr \textbf{Bald} , Getting stuck into that vodka must  help 🤪\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small go to hell with these words. Goverment spent milions in the past to educate them, their kids, they give them new flat when they demolist theirs. White people go to work every day to pay taxes and goverment gives this money to gipsies for \textbf{NOTHING}! They dont want to get educated, they are satisfied with their lifes. They dont go to eork, their kids dont go to school. Yes, we tried to helped them in the past several times giving them uor money. But they are satisfied with this style of life!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small in 3:35 she said they have chance, not \textbf{zero} chance lol\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small What does a 14 year \textbf{old} \textbf{gypsy} girl need to be in order not to get pregnant.She needs to be faster than her younger brother.She needs to be stronger than her \textbf{elder} brother.And she needs to be smarter than her father.\normalsize   & \cellcolor{green!5}Elder, Gypsy, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Roma & \cellcolor{green!5}3/44 & \cellcolor{green!5}6.818 \\  \hline
  \cellcolor{green!27}\small No waay Mr. \textbf{Bald} is i my hometown of Košice. How long will you be staying?\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small It is true that gypsies are a pretty big problem here in Slovakia but I have to say that it is much worse on the east of Slovakia. The more you go west the less problematic gypsies there are. I live for instance in Nitra (West) and I have a lot of \textbf{gypsy} friends.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Bald \& Bankrupt \& Beautiful \& Belarusian = 4B² posse.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Most Romani survived the Bubonic plague because they actually have extremely strict cleanliness rules, they were washing their hands and their bodies well before most Europeans were hence the high survival rate during the plagues. It's odd to see that they have littered so much in their own area, I suppose the cleanliness laws are only applicable inside lol. Good on you Mr. \textbf{Bald}, Alinchick is proving to be a really cool sidekick too, thanks for the content :)\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small Hahhaha \textbf{bald}, you are really in Slovakia!! I am czech, wish you all the best\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small This is rather GROSS!  Kids drinking \textbf{Alcohol} and living like rats and roaches... Its low life behavior... The Parents....Omg!  Smdh\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Sydney Austin well like this most of the \textbf{gypsy} are they don't give 2 shits about they'r children\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small skoda ze som \textbf{ho} nestretol, dali by sme borku v zemplinke alebo daco 😁\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Bald will marry Alina and become the 1st minister of England\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Brasileiro Patriota  The \textbf{gypsy} fortune teller has forecast it.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small So much in this great video...1:15 Why leave when you get all the free TV with those satellite dishes8:04 Devlish looks despite being told that you are a happy \textbf{woman}.Only \textbf{Bald} and Bankrupt can bring further joy to the slums.... but that kid at 5:27 is not to be messed with lol\normalsize   & \cellcolor{green!27}Bald, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small Gypsy District 9!\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@jonte M \textbf{Bald} and Bankrupt to Rinkeby 2020\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Here we go, \textbf{Bald} in my country! Lunik 9 is a notorious place for Slovaks we are not proud lets say very softly. But i hope you visit other places in our country because nature is really beautifull and people are mostly generous and kind.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Went to England , found it to rough .🇬🇧🏴󠁧󠁢󠁥󠁮󠁧󠁿 and for all you \textbf{remainers} ,this is your beloved E.U , where's the money going?\normalsize   & \cellcolor{green!27}Remainers & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Indian blood \textbf{Indian} origin can handle all difficulties in Life and smiling\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small 2:20 she want one one mr bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Looks like the young girls they get pregnant at very young \textbf{age} and have lots of kids. Because of no education, no protection. They have to feed those kids, so they turned themselves into prostitution in Europe and also in drug business. Lots of kids for sure does not know who their father is. It's a complete mess. I met a gypsi girl in Italy. I told her you marry me and get the fuck outta there, I will take care of you. She never came back. She went with the herds.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small this isn't gonna \textbf{age} well, especially with the cp and nonces on yt nowadays\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@One Hunnit Tech at least he's honest, unlike "you're \textbf{racist}" ideologues.statistically, Aaron is precisely correct, factually accurate, and there \textbf{nothing} bigoted about that. stop denying \textbf{black} culture, bigot..\normalsize   & \cellcolor{green!5}Black, Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small Haha girls being hoes in a very young \textbf{age}. And inbreeding is a big problem. xD shit...\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Grease quala if you think \textbf{brexit} will stop them coming you're a naive fool\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Ghryst VanGhod Yikes.. There's not 1 \textbf{black} person shown in the area yet you idiots have to find reasons to put blame on them from your own personal victimizations. What is he Angel right about anyways??  He's complaining about the music "All that Brap brap bollocks"...  While most of them don't even understand or speak english.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small \@keatonf3 it's called you being a \textbf{snowflake}.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Grease quala, Similar landscapes in England as well in council estates overpopulated with smack heads and "Full Time mummies" having 6 children with 6 dads. The only difference is that UK local authorities still come to collect the shit they left behind, unlike in this video. So stick the \textbf{brexit} up your ignorant ass for now. Peace out.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small \@Grease quala London is a shithole and not because of immigrants. England has really \textbf{nothing} to offer to the planet at the moment. Neither in natural resources nor in skills (not much anyways), we got America,Japan,China and India for that, so its fall without the slave economy was bound to happen and they kinda had it coming so eh.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small \@Ghryst VanGhod So you are saying all you know of \textbf{black} culture is what you see in rap videos.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small One Hunnit Tech 22 likes for a current year comment, this just shows how bad your arguments against \textbf{common} sense are.It will be 2020 next year bruv! Trump will be re elected again bruv, seems \textbf{weird} considering whites were being told it was 2016 in 2016 bruv.It's almost like saying what year it is doesn't change the fact that right wing, anti immigration parties are surging across the western world. How strange, considering it's such a great argument.\normalsize   & \cellcolor{green!5}Common, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/80 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small the Ying Yang Twins lol \textbf{crazy} how American Southern Crunk rap made its way to Slovakia slums\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@One Hunnit Tech"muh \textbf{racism}!" Fuck outta here mate. Don't bring your cancerous hypersensitive victim complex onto this channel.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Italian Fascist You don't like being called out on your idiocy? YOU "fuck outta here." Calling you a dumbfuck \textbf{racist} isn't being hypersensitive, it just stating a fact. Get over it, you dumbfuck \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small They have \textbf{INDIAN} Blood thats reason always happy and smiling... its our \textbf{Indian} Blood and Nature.  after many difficulties we always enjoying our life...\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I guess being super dirty and uneducated is also in the \textbf{indian} blood.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Vladimír Novak yes... but we are not Murderer like Stalin..like ISI.. like \textbf{Communist} party.. like china..  we are Human massanger.. ❤❤ we share Love and humanity\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Typically \textbf{gypsy}:))). All nice clean and decorated in the inside but rubish outside. No sanitation or plumbing. Go visit the south of Serbia gypsies. Nice, decorated houses, but hella lot of rubish:))). But those guys can work a trumpet and a trombone:). Check out Guca, \textbf{gypsy} music festival.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Slovakia is basically the west...their capital Bratislava is a beautiful city where you can live a life with all the comforts you're used to. However the \textbf{gypsy} people are somewhat different\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small President Mr. \textbf{Bald} confirmed. You all heard it from that fortune teller girl.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small They must fear \textbf{bald} is a MI6 agent or something.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small In the beginning of the video I want  \textbf{Bald} to ask them to clean that garbage luckily Alina did that I am so happy....\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Yes i think democracy is outdated...we need a systrm like in china. No RIGHT TO VOTE. POOR PEOPLE MUST BE EXECUTED INLY RICH PEOPLE SHOULD VOTE. look at the west eith the rising of populism ehote \textbf{nationalism} and communism. We need an authoritarian capitalist system.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@GIHAN lol? Those rich people in china or former eastern block were fucking lowest scum and had \textbf{nothing} before communism\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I suppose that racial segregation and discrimination, and unfair distribution of services (including education) has \textbf{nothing} to do with it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Looks like it's kind of a social \textbf{mental} disease. I found the same people behaviour in some regions of post soviet countries. The poorer people the less they care about everything around them, even if it is a garbage. It is something in their mindset. Maximum they take care about their own flats, but if you make a step out of the door you will find a shit around.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small \@Gamer Bhai you do realize the Indus valley civilization has about as much to do with present day Indians as ancient Egypt with modern Egyptians? key word is admixture, various people came to the area and mixed with the local population, which is why (no offence), most Indians don't look very European, and certainly aren't white, despite actually being the same \textbf{race} still. This also resulted in the dumbing down of the once great civilization, which is probably why your country is simply unable to clean up all the trash and make it look at least halfway developed. Ffs people are swimming in what is essentially sewage water and call it "the holy river". If it's so holy, then why can't you take proper care of it? You have over a billion people, surely organizing a nation-wide cleanup wouldn't be that hard.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}\small \@Peeping Tom Definitely not. Czech/Slovak are very different to the Russian languages. She can say the Ř, so she has possibly lived in the Czech Rep. There is virtually \textbf{zero} reason or benefit for a Belarusian to learn Czech.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small tvl cigani z Luniku, nejvetsi ostuda Kosic a celyho Slovenska. You can try to live there several weeks with them, you will see what are they really like and \textbf{nobody} wants to live next to them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Holy shit, \textbf{Bald}! Even the purest of Slavs are afraid of Lunik 9 and you're over there having a blast? This is the content I subbed for!! I hope next video I will see you travelling through Ostrava, Czech Republic. Some parts of Ostrava resemble Lunik, you might like it over here, in this post-communist concrete jungle. Love your videos, cheers!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Mr \textbf{bald}, please explore northern siberia as well\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small This lost generation in the middle of Europe is sad. Never heard of it in our press. Thanks to you \textbf{bald}.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Unknown Assassin nope, I work manual labor that pays high wages and we struggle to find any other \textbf{race} other than Mexicans to work. When 4pm comes around whites blacks Asians all beg to go home while the Mexicans literally will and do work to 7 or 8\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Joe \textbf{Black} I'm sure, but that doesn't mean I wouldn't work as hard as them with a good wage.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Joe \textbf{Black} Please, if that were the case, the homeless population would be close to 0. Mexicans tend to work long hours when their usual wage isn't enough.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Nah , Mexicans are \textbf{nothing} like Roma , Roma \textbf{gypsy} are jst a bad bunch of people ( exeptions of course ) , they will steal from the poorest people with out remorse , don't do honest work , leave there mess for everyone else to clear up , jst bad people\normalsize   & \cellcolor{green!27}Gypsy, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small In Seoul you see the \textbf{old} and \textbf{disabled} hauling and sorting trash. It is off-putting to those  of us from countries with guaranteed pensions but it kind of works. Keeps the city clean and reduces the carbon footprint since anything bigger than your fingernail is recycled. I think the program is run by a nonprofit.\normalsize   & \cellcolor{green!5}Disabled, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small \@Silverfox Lol at you autistic "ppl" thinking you are "good and moral" by protecting these shitty "ppl" Hope someone in your family gets robbed and almost beaten to death like this 80 year \textbf{old} lady in my town, who got 5 of these monsters breaking into her house, raping and beating her so hard that she spend over 3 months in the hospital.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small \@Gotopost tt You want to murder several \textbf{old} women.....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@Gotopost tt i'm literally a \textbf{faggot}, i don't support ISIS in any way shape or from lol there is no correlation\normalsize   & \cellcolor{green!27}Faggot & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Gotopost tt Thats sed I fel bed for the \textbf{old} lady fuck those gypsies they should get out of Europ\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@dsmythy Way to try to put words in my mouth lols Typical "honest" "anti" "\textbf{racist}" lols\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Gotopost tt 😂 And I suppose \textbf{old} women would be spared the humanitarian that you are.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Anssi Ilari You're obviously just some jew from america who tries to say that "\textbf{race} doesn't exist unless you're a jew or muslim from outside Europe" lols\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@dsmythy What is your hangup on \textbf{old} women? lols\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@Gotopost tt You're pissed off how a local \textbf{old} \textbf{woman} was beaten. But you're no better than them?\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Gotopost tt did i say they are finnic? I believe I said Finnish, and \textbf{gypsy}, believe it or not it's possible. But hey then again your country doesn't have as good school system as mine so I don't know if you can comprehend ;)\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Being poor is not an excuse to be dirty, behave bad and live in shit.Gypsies haven't heard the proverb "Don't shit where you eat" i guess : - ) Everyone keep telling people how "\textbf{racist}" they are if they point out how gypsies are,act and behave.. any country they are in.. they are same everywhere...\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Stereotype about \textbf{gypsy} is always true.There is no way to help them\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small meeds Brad - Not the \textbf{old} fashion ones with Swimming pools from yesteryear though\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small so many \textbf{racist} people in the comments\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small You're the best \textbf{Bald}! Showin that many places labeled as dangerous are very welcoming if you respect the people there :)\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Bald} you waiting for visa for how long, its not for you I'm presuming of course? Been waiting for you to get back for months man.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I went to ploiesri in Romania as I was invited to a \textbf{gypsy} wedding last year I was told by many people don't go that I would be robbed and beaten even none \textbf{gypsy} Romanian people told me this . I still went and I was treated with the most respect ever in fact I was treated like royalty the wedding lasted for 3 days and I have never had such a good time and I will definitely be returning at some point. They would not let me spend any money either even my hairdresser wouldn't take money from me .imagine that in England lol never xx\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}2/107 & \cellcolor{green!27}1.869 \\  \hline
  \cellcolor{green!5}\small That thumbnail, For a second I thought \textbf{Bald} getting married. Soviet Style\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Bald you need to come and see the Balkan gypsy's they will do what these didn't. Rob you and stuff :D. Love your videos!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@\textbf{abc}He? He personally? Dude, the guy in the video even admitted that no one made them live this way and it's their own fault. How did a random dude on YouTube create that shithole? They throw the garbage directly out of the window. Yes, always blame other people, you filthy little cockroach.\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Rather a shit hole full of lazy People who drink cheap \textbf{alcohol} and breed like rabbits 🤣\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I'd rather risk it in the Chernobyl exclusion zone than go to that \textbf{gypsy} slum.\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small LMFAO...\textbf{Bald} will make a beautiful first lady. So says the tarot \textbf{gypsy}.\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Her wife will be the president. That's some \textbf{weird} future.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Bald to be bride will be \textbf{bald} soon\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Just another \textbf{gypsy} practicing her 'fortune-telling' lol\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Hearing a 14 year \textbf{old} say "look at that ass she a bad bitch" really made me die inside a little. I hope some of  those poor kids make it out of the slums into a better life\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Jay bhole ki missing your \textbf{Indian} trip..\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small In Bulgaria every abandoned village is a \textbf{gypsy} slum.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Flying Mushroom what ones? All the rest is just not that interesting, whole Europe is too sad and normal to mr bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small No. \textbf{Bald} only does the worse, there are your usual journey bloggers who visit tourists destinations.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Nothing better to kill time whilst internationally travelling and Mr. \textbf{Bald} puts out new content! Cheers mate!!\normalsize   & \cellcolor{green!5}Bald, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small \@Acharya Utsab they're \textbf{indian} by their roots. Religion does not define your \textbf{race}. There are catholics and muslims in india too.\normalsize   & \cellcolor{green!27}Indian, Race & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small \@Smackrecker Those are recently converted people. \textbf{Gypsy} been in europe since thousand years\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Mr.\textbf{Bald}. your last 3 to 4 videos sucks,  I thought Mr.\textbf{Bald} is loosing his momentum.  Now back with bang.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small 2:40 - yeah, you are \textbf{indian}, and i dont judge that by your skin color but by the way you handle your trash...\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Of course I'm trying to go to sleep and I get a notification of Mr. Balds upload. Come on \textbf{Bald} it's 4:30am here in Las Vegas. Lol. I guess one video won't hurt.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@Trevor Atassi Same thing, \textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Iskalder It is a fucked up place. Do not go there. also a breeding ground of \textbf{terrorist}. Girls will be raped for sure.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Trevor Atassi it was hindu once, then the muslims came and well u know, same shit is gonna happen to europe but we cant say shit or we RaCiSt\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small How about Rapistan where \textbf{Indian} Niggaz rape \textbf{fat} whores for fun?\normalsize   & \cellcolor{green!27}Fat, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Lundian dogs eating cow beef off their mums \textbf{pussy} roadshitters bastard\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@x x Today all of you Europeans are dying to just connect yourself somehow to that word or \textbf{Indian} community. You are bringing theories like Indo-European family and what not. You all are just trying to be part of early era great civilization which India was.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@Just another geek You are very mistaken. India has a bad reputation for being unclean in my european country at least. We are not taught about the \textbf{indian} civilization at all in school. \textbf{Nothing} pre Gandhi.\normalsize   & \cellcolor{green!5}Indian, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Yeah Mumbai and Delhi in India posh are worse than those. You filthy \textbf{Indian} bring Pakistan in every situation.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Just another geek You are just a \textbf{racist} that makes shit up as you speak\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@kautschuk I don't recall any 9 million population country to have a Anti Satellite Capability(India, China, Russia, USA). I don't recall any 9 million population country to first discover water on moon(\textbf{Indian} orbiter Chandrayaan around in 2008 discovered water).\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@kautschuk The problem is you all don't know about India. Who owns Jaguar, one of the most luxury car? \textbf{Indian} businessman. Ratan Tata through Tata Sons was biggest private employer britain few years back. I don't know of about right now. There are tons of thing you will never hear in your media.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small \@Silverfox Yeah for sure... But for what i saw in the video. The girls at that children party were not shy. Already full blown hoes at such young \textbf{age}.... XD\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small leandoer india was bhuddist one then the dirty hindus came and look at ur hindu ancestors wat the have done in Europe...bloody gypsies fuckers \textbf{indian} cints\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small As an \textbf{Indian} it's so much to see Indians and Pakistani abuse each other😂😂Why can't you just live with harmony for once\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Just another geek What great civilization? Most achievements of India is due do Aryan invasion. Sorry native (brown) \textbf{Indian} culture is of little interest.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@U'll float too Hinduism is 4000 years \textbf{old}. Buddhism and Jainism are 2500 years \textbf{old}. Sikhism is 700 years \textbf{old}. These are 4 major world religion which originated in India.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/30 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Just another geek I can assure you no European wants to be \textbf{Indian}. I'd rather live in Chernobyl than a shitter like Mumbai.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Anyone with a brain who has  access to internet can search .. Islamabad (Pakistan Capital) or Lahore or Karachi two biggest cities and see how media brainwashed these 12 years \textbf{old} Indians are. I know many Indians who never say things like these because they know the realities but these children when they have access to internet they spread hate. That's our next generation. Ok .. just search India Capital New Delhi and Pak Capital Islamabad and see the difference. You will be amazed to see the difference and will know how these \textbf{Indian} lies ..\normalsize   & \cellcolor{green!27}Indian, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small abhishek Singh No I really wont. Could never get a decent bird there most look worse than the \textbf{midget} men.\normalsize   & \cellcolor{green!5}Midget & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small marty james And those places have \textbf{immigrant} groups with regressive mentalities like the gypsies.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small ok, time to say to Mr. \textbf{Bald} something about Chanov, dear brother\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Come to Romania Mr.\textbf{Bald} !\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Wow Mr \textbf{bald} you are amazing\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I ain't sure if you can call them Indians now.Like the nomadic tribes left India during 11th century.I mean in that case all humans are just Africans and \textbf{nothing} like Americans exist.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Prasann Kshatriya actually if you go on the wiki page about Roma you will find that genetic research has concluded that they are indeed genetically \textbf{Indian}.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Bald \& Alina forever! ❤️\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Come to Denmark you \textbf{old} \textbf{bald} twat. We're very hospitable and shit.Edit: Also, \@1:56 is about where I stopped feeling sympathetic towards these people..\normalsize   & \cellcolor{green!5}Bald, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small It's so funny \textbf{Bald}, every time you two pop-up on my computer I feel like a kid sitting down to watch his favorite cartoon on Saturday morning. Ha ha ha 👋😁👍Love you guys!  Florida Bob\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Watching in 360p for the authentic \textbf{gypsy} experience\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Which is also why his \textbf{old} phone didn't get stolen. LMAO\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Pankaja kathaita your country is a shithole and most of your \textbf{race} are dirty\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Pankaja kathaita quality of life in Slovakia is so much better than in India. Look at your wealth divide and percent of people in poverty and your attitude to \textbf{woman}. there's a reason everyone hates Indians like yourself\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Same in the uk there dirty cunts but when an \textbf{Indian} starts pipin up when there whole country is a dump\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Mjl bruh, did you just generalize 30 india as a whole \textbf{nation}? Have you ever been to India? LolGo look up Uttrakhand, Himachal Pradesh. The areas near the Himalayas. You'll see what the other half of india looks like. Some places are literal shitholes no doubt, but don't generalize the whole country. Oh, ofcourse that's what you have seen on YouTube. Anyway i agree with you on some points, some indians would potray like india is the best country of all, but it isn't. No doubt. But you aint completely right either\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small \@Mjl atleast i have a profile pic, not like a keyboard warrior sitting behind his computer with a huge fuckass gut and \textbf{fat} on his ugly face. Keep on hating mate. You gotta whole life ahead of you to hate 😂\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Darpan Goswami more like 80 of your country is a dump shoulda said - and your sayin these areas are nice which they probably are but like there is \textbf{zero} economy in these areas and they probably still message women online about Bob and vagana pics\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Mackenzie Lawton When a person fears from anything it doesnt really exist is called hallucination , how much time u spent in India ?  I guess u never landed on \textbf{Indian} soil , but still so much negativity and hatred inside ur heart , dont know why 🤔\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Mjl u hv clean hands with dirty mind .At least we hv good behavior , look at these  Slovakian  gyspies they behave rudely with this \textbf{bald} man .we respect everyone who visits our country .u dont know  India is a  6" th largest economy in the world n will supress Uk n germany in next 2 - 3 years . we can buy most part of europe  . Slovakia is just a small town for us\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small Darpan Goswami funny that I'm a keyboard warrior but with my 8 years of this YouTube account I haven't ever been in an argument online - and I'm \textbf{fat} am I yet I go the gym regularly and have a balanced diet which about 90 of Indians can't afford to do\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@Mjl no there is no \textbf{zero} economy, those are heavily involved with tourists, treks/hikes, organic weed/hash etc. So you're wrong. And no not 80 is a shithole, the places you see on YouTube are what every youtuber visit. But there is no point arguing. Anyway, india is not the best country, it will never be, because the people here are shit in some parts, they are far behind the technology or even the mindset. But the people in the area i mentioned are far ahead, far educated and ready to progress. But it can't happen unless all are aboard. India = best are the people who asks for bobs. Not everyone.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small Mjl U need to study about history and geography and economics and some good books and stuffs  , if u get some time from smoking weeds ... dont know which country u belong but i wish other people from ur country are not \textbf{racist} and haters like u 🤔\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Mjl Forget what 90 Indians can afford , only 1 \textbf{Indian} billionaire is enough to buy ur Country in a second , and there are many such billionaires here ... if they stop investment and giving jobs to peoples in other countries and if India stop trade from other countries whole world will go in economic crisis\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Loving Mr \textbf{Bald} and his Banter,   When are you going to Vlog your home town ?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Fantastic work \textbf{Bald}, I was just recently in Moldova did some street interviews. I asked people if they watched any YouTube videos on Moldova ...and guess who kept coming up ?..Your a legend, I will put up the video soon.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Bald, harald and Tim all upload on a Sunday, my afternoon sorted 😀\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Gypsies 🥰 I have \textbf{gypsy} blood also ❤️\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small nothing to brag about in these countries tbh\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Every community/race have bad/uncultured people. Don't let the people on the internet get to you. I believe not every \textbf{gypsy} are like them. Be proud to be one. There's \textbf{nothing} better than being proud of who you are while everyone hates you for being you. Goodluck! :)\normalsize   & \cellcolor{green!27}Gypsy, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Roma & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Why are \textbf{black} people so angry, violent and \textbf{dumb}???????\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small The reason why \textbf{Bald} stays safe in all these dangerous places is because they think he's Ross Kemp.\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Mr. \textbf{Bald} follows the tradition of great English explorers to bring to us tales of lesser known parts of the modern day world. He has stayed and travelled extensively in India. I thought he has become a indophile. Now I know, after seeing many of his recent videos, although he is a true friend of India, USSR, that great country which is now no more, is his love and he portrays the people now living there, with great human touch. I am from Calcutta and he has an unkind comment for my city in the present video, which is however true. He has an infectious smile and very honest with his comments. I only wish he keeps on doing what he is doing and he keeps on loving what is he is doing.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/133 & \cellcolor{green!5}0.752 \\  \hline
  \cellcolor{green!27}\small Alina has his back.  She's the reason he stays safe.   But \textbf{Bald} is a helluva guy!   They work in tandem!\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Bald would make a great cousin to Phil Mitchell!\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Ross Kemp is \textbf{g\textbf{ay}}.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Bald is actually accompanied everywhere by a 20-member close protection squad made up of ex-marines. We don't see them because of the clever editing.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Slovak government needs to sort that slum out, \textbf{bald} and alinchik can tell us they are salt of the earth type people but look at the state of the place, the environment reflects the nature of the people imo, absolutely amazing hearing those gypsies speaking English with regional English and Irish accents though! Open borders great thing if your a \textbf{gypsy}!\normalsize   & \cellcolor{green!27}Bald, Gypsy & \cellcolor{green!27}Ethnicity - Roma, Physical Identity - Physical Features & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small Lunik 9 is normal \textbf{gypsy} town he should look to Letanovce Slovak \textbf{gypsy} village its HARDCORE Local Police is looking like American Rangers and villagers are equiped with guns against gypsyes\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Jai bole ki \textbf{Bald} 😄 love from India\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I love u bald\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Hi \textbf{bald} you da man !!! 😁✌👍\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Hai \textbf{bald} iam ur huge fan from india...can i get reply???\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small yo bald\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small it's because it's free to hate them. \textbf{nobody} cares. they certainly don't. you know, an average muslim would feel bad about being called a \textbf{terrorist}, whether s/he acknowledges there is some truth about islam being a violent religion or not. Romani just don't give two shits what other people think of them. it is somehow worse and better at the same time.\normalsize   & \cellcolor{green!5}Nobody, Terrorist & \cellcolor{green!5}Age - Youngsters, Religious Identity - Muslim & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small \@Laylla's Locker Gypsys are immigrants from India and some \textbf{gypsy} girls are actually pretty.\normalsize   & \cellcolor{green!27}Gypsy & \cellcolor{green!27}Ethnicity - Roma & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I guess I shouldn't be shocked to hear such hatred and \textbf{racist} comments coming from white European people.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Loving your vids \textbf{bald}, keep up the good work. Also, Number 1 😎\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Bald, Fat, Chubby & \cellcolor{red!27}623 & \cellcolor{red!27}623/176937& \cellcolor{red!27}0.35000000000000003 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}41 & \cellcolor{red!5}41/176937& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}22 & \cellcolor{red!27}22/176937& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nobody, Nothing, Zero, Brat & \cellcolor{red!5}164 & \cellcolor{red!5}164/176937& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Promiscuous, Ho & \cellcolor{red!27}7 & \cellcolor{red!27}7/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Elderly, Elder, Senior & \cellcolor{red!5}125 & \cellcolor{red!5}125/176937& \cellcolor{red!5}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Ethnicity, Ethnic, Racist, Race, Racism & \cellcolor{red!27}148 & \cellcolor{red!27}148/176937& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Sexual, Chick, Gender, Woman, Sex, Chauvinist & \cellcolor{red!5}86 & \cellcolor{red!5}86/176937& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationality, Refugee, Nation, doctors, Alien, Immigrant, Migrant, Xenophobia, Engineers, Nationalism & \cellcolor{red!27}59 & \cellcolor{red!27}59/176937& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Roma}  & \cellcolor{red!5}Gypsy, Gyppo, Traveller, Gypo & \cellcolor{red!5}381 & \cellcolor{red!5}381/176937& \cellcolor{red!5}0.22 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Protestant}  & \cellcolor{red!27}Spike & \cellcolor{red!27}1 & \cellcolor{red!27}1/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Crazy, Mental, Blind, Freak, Weird, Dumb, Mong, Disabled, Weirdo, Midget & \cellcolor{red!5}109 & \cellcolor{red!5}109/176937& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Indian, Red & \cellcolor{red!27}133 & \cellcolor{red!27}133/176937& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Nigga, Black, African, Negro, Colored, Toad, Spade & \cellcolor{red!5}62 & \cellcolor{red!5}62/176937& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Communist, Red, Libtard, Nazi, Snowflake, Commie, Cuck & \cellcolor{red!27}41 & \cellcolor{red!27}41/176937& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, Chav, Pikey & \cellcolor{red!5}25 & \cellcolor{red!5}25/176937& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - European or anti-Europeans}  & \cellcolor{red!27}Remoaners, Brexit, Remainers & \cellcolor{red!27}33 & \cellcolor{red!27}33/176937& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}LGBT, Gay, Homophobic & \cellcolor{red!5}6 & \cellcolor{red!5}6/176937& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}LGBT, Gay, Fruit, Faggot & \cellcolor{red!27}11 & \cellcolor{red!27}11/176937& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Transexuality}  & \cellcolor{red!5}LGBT & \cellcolor{red!5}2 & \cellcolor{red!5}2/176937& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!27}Dot & \cellcolor{red!27}1 & \cellcolor{red!27}1/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - American}  & \cellcolor{red!5}Murican & \cellcolor{red!5}1 & \cellcolor{red!5}1/176937& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Southern European}  & \cellcolor{red!27}PIGS & \cellcolor{red!27}4 & \cellcolor{red!27}4/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}pussy, ABC & \cellcolor{red!5}10 & \cellcolor{red!5}10/176937& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Hag, Witch & \cellcolor{red!27}3 & \cellcolor{red!27}3/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Terrorist & \cellcolor{red!5}3 & \cellcolor{red!5}3/176937& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Female homosexuality}  & \cellcolor{red!27}Lesbian & \cellcolor{red!27}2 & \cellcolor{red!27}2/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Hun, Jerry & \cellcolor{red!5}2 & \cellcolor{red!5}2/176937& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Destitute}  & \cellcolor{red!27}Bum & \cellcolor{red!27}2 & \cellcolor{red!27}2/176937& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Irish}  & \cellcolor{red!5}Chav, Pikey & \cellcolor{red!5}2 & \cellcolor{red!5}2/176937& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Physical Identity - Physical Features;Age - General;Behavioural Addiction - Alcohol;Age - Youngsters;Gender - Female sexuality;Age - Over 65s;Ethnicity - General;Gender - General;Nationality - General;Ethnicity - Roma;Religious Identity - Protestant;Physical Identity - Physical (and Mental) Impairments;Ethnicity - Native-American;Ethnicity - Black; Ideological and Political Identity - General;Social Class - Working class;Nationality - European or anti-Europeans;Sexual Identity - General;Sexual Identity - Male homosexuality;Sexual Identity - Transexuality;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Nationality - American;Nationality - Southern European;Nationality - Chinese;Gender - Female age and physical appearance;Religious Identity - Muslim;Sexual Identity - Female homosexuality;Nationality - German;Social Class - Destitute;Nationality - Irish;%.

\item The percentage of hate speech related words is 1.1919.

\item Considering that the variable \textbf{Physical Identity - Physical Features} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 2109/8339 occurences of hate speech related comments.\end{itemize}\end{document}