\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_276.json :}\newline \par\Large\textbf {Title: \large  Tackling antisemitism in Manchester: 'We are feeling more and more unsafe' }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small I have no problem with any \textbf{race}. But I do have a problem with all governments that use us for their benefit!\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Luke M israel will be sent back to stone \textbf{age} - nasrallah\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small If you feel unsafe, emigrate to the \textbf{Shylock} State.\normalsize   & \cellcolor{green!27}Shylock & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Where in for a \textbf{crazy} time in the coming decades\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Herman} Browndog If the shoe FITS\normalsize   & \cellcolor{green!27}Herman & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Well there's at least one thing that i can find in \textbf{common} with muslims.A strong  dislike for the chosen ones and the special treatment they seem to get from the entire world.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small thinking israel should have not been created is not been antijew, is a historicopolitical opinion. besides  that i think antisemitism is in the rise in occident, as it is the rise of the extreme right, and hate for other minority, luky im \textbf{old} and soon all this conflict will  mean shxx to me. How i miss \textbf{old} 80's when we thought the world was going to be a peacefull social wellfare utopia xD and extreme right wingers were hidden under rocks.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small This as become a recent topic in the UK to try and overturn \textbf{Brexit}, we have over 200 UK MPs who have claimed loyalty to the state of Israel and they will put israeli interests before that of the U.K people, Just because Corbyn is against the instability in the middle East. Many other countries detest the war crimes being carried out like  watching IDF snipers laughing and jeering as a bullet takes a unarmed man's head off, this is not a single incident but just one of many, Israel has been interfering in UK politics for to long, this has to be stopped, those 200 MPs should be made to state which country do they represent or they can leave. This is a distasteful low dirty tactic those \textbf{remainers} are playing, with direct threats to British people.We will have our \textbf{Brexit} it's what we voted for but I see so much MSM news talking about loss of jobs and doom and gloom if we leave but that is all just talk by people who don't have a UK passport and they should stay out off what was supposedly a people's vote but now people are being threatened in all kinds of ways, these are sad times for U.K democracy.Ford threatening jobs, Ford built trucks for the Nazis before and during WW2, after our brave pilots bombed those factories with horrendous losses, Ford claimed and won compensation for being \textbf{Nazi} collaborators, we fought bravely then and we will now. "NO TO THE U.K Being in the E.U."\normalsize   & \cellcolor{green!5}Brexit, Nazi, Remainers & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - European or anti-Europeans & \cellcolor{green!5}4/259 & \cellcolor{green!5}1.544 \\  \hline
  \cellcolor{green!27}\small Antisemitism is a \textbf{mental} disorder.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I find many of the comments bellow damn right scary in their sheer misguidedness. No, anti-Semitism is far from the preserve of muslim communities. A dear family friend of ours had bars fitted to his home windows to stop the bricks coming through from known BNP members, he was in his nineties when this happened.Speaking of Leon, he had survived Auschwitz. His child and wife didn't. My grandfather never met his brother again. The historical evidence of the holocaust shouldn't need defending, how did this denial come to be? These comments alone show the serious problem of holocaust denial, the denial of six million deaths because people were judged purely on their \textbf{ethnicity}.  Furthermore, these jewish mancunians don't represent Israel and the very valid criticisms that many of them will also have. It is a shame this documentary didn't show the various views. The term zionist is also thrown around as if it is well defined. For many zionism means the eventual return to the homeland, there is \textbf{nothing} of the theft of land from those who also live there. In other words there are many interpretations of this longing which is why self describing yourself as 'anti-zionist' plays into the hands of extremists on both sides whilst insulting a very many other people who are peaceful in their lives.If you find yourself judging people on their \textbf{ethnicity}, religion, or some other broad definition you have a serious problem. People among every community in Britain are far more diverse than the differences between the communities themselves. I really wish there was a little more self reflection, and reflection upon where people are getting their information.\normalsize   & \cellcolor{green!5}Ethnicity, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/277 & \cellcolor{green!5}1.083 \\  \hline
  \cellcolor{green!27}\small If you go around telling idiots that you are special in the eyes of a non-existent supernatural being then you are asking for it. After all, if you believe it, why shouldn't they?Isn't Judaism an elitist cult? What is the difference between  the 'Chosen People' and the 'Master \textbf{race}?'Is it any wonder that people who say that god prefers them, get picked on?I despise Judaism in the same way as I despise Islam and Christ inanty. People who are too lazy to think for themselves and eat the excreta spoon-fed to them from the pulpit, bima or minbar are too scared to think for themselves. The shyte they've been digesting for generations is easier to handle.Religion is poison and the pious are highly tolerant.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small The Jewish Kalergi plan bought Muslims into Europe to weaken it,break it up,divide it and destroy it.They are also being gringing in \textbf{Black} people from Nth Africa to try and subvert by racial blending creation a people of mixed \textbf{race} like Egyptians as per this said plan\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small 10:32 washington d.c is a tiny \textbf{dot} but look at the mass murder it caused.\normalsize   & \cellcolor{green!27}Dot & \cellcolor{green!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Racist.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small israel will be sent back to stone \textbf{age} - nasrallah\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Aidan Tisch you slavic mongolians have \textbf{nothing} to do with middle east , you are all races in one but not from middle east dna doesnt lie\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small no one dislike you because you are jewish rather because you are zionist terrorist\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Zionists are \textbf{TERRORIST}. Do you history  (  ;\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I wonder whether people like you are just plain \textbf{crazy} or simply jvueniles.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Ishaan Rahman that is what exactly you are....indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Ishaan Rahman i know how citizenship and \textbf{nationality} works....by law you are british but in reality,you are still \textbf{indian}...that is how it is..and always have been...now matter how much i have citizenship of france.. I will never be french because i am english..that is in my blood....if a chinese guy obtain  citizenship of british, he would still be a chinese because that is what he is.....by law you are...but in reality,you are not\normalsize   & \cellcolor{green!27}Indian, Nationality & \cellcolor{green!27}Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small \@Ishaan Rahman yea those people have something in \textbf{common}..europeans have \textbf{common} ancestors....slavs...greek..roman..anglo..celts..germanic.. etc..they are all of the same origin...its not foul even if they have dual nationalities...\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small \@Ishaan Rahman it isn't just pigmentation and melanine...i can differentiate who are chinese \textbf{black} \textbf{african}..indians..arabs and european even if they change their skin colour...\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Ishaan Rahman so do you every considered your self chinese or sub saharan  \textbf{african}?\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Ishaan Rahman on paper you are a britisher....but in reality,you are still an \textbf{indian}.....a german guy obtaining \textbf{indian} citizenship is an \textbf{indian} on paper...but in reality he is still a german...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small \@Ishaan Rahman read the comments carefully...i said you can called yourself either \textbf{indian} or Pakistani, bangladeshi, nepali because these nations are of south asian origins...where your kin belong.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small My guess is your attackers are muslims. You cannot ride roughshod over Palestine and expect palestinians to accept it because you claim to be 'gods chosen people'. Look in the mirror. Do you have a reflection or not? Your claim to Palestine, no matter how heartfelt is a deceit. Based on a 2000 year \textbf{old} folk memory. Go back 5 generations of 'Israelis' and you probably end up in Poland.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Look around the world. Who is invading who, who is raping and killing  your daughters,  who is breaking all your laws , who is shutting down free speech. When did this massive amount of violence get out of control. There is one \textbf{common} denominator and it is being allowed to happen.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Please tell me these Jewish people sitting around the table voted for \textbf{Brexit}, in order to get control of immigration.  Cuz if you're some open borders clown, and hundreds of thousands of more Muslims pour in, anti-Jewish incidents will rise, without a doubt.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Criticise any other country and it's \textbf{nothing}, criticise israel and your an anti-semite lol what a joke\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small self serving \textbf{race} . waiting for there master . its only a story . globalist money lenders and mosairs\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small To all the \textbf{dumb} fucks spouting their pseudo wisdoms about not being able to question, it's all you idiots talk about and you're fine. No one is stopping you from being a jewhater and no one even wants to. Most people actually agree with you. Yes, you're an anti-semite but no, you're not being ostracized or censured. You're fine. But don't let logic get in the way of a good hatred.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Pro Palestinians Muslim and leftist are the new \textbf{nazi} . That's sad to see this hatred in Europe again ( I'm a rangers fan stand with the Jewish and the state Israel )\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Israel is doing \textbf{nothing} wrong.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Confused and defeated English \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small There will always be \textbf{racism} but I think most modern governments have the ability to control it if it gets out of hand. I think there will also be new laws introduced and more safeguards. However, you should't be called a \textbf{racist} if you criticize Israel for killing unarmed Palestinians.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small 14 anti Semitic racists thumbed up this \textbf{terrorist} lover SICK!\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@P C israel will be sent back to stone \textbf{age} - nasrallah\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Good, leave, it's not your \textbf{nation}.  Wherever these people go, the nations/society become debased and crumble.  They're toxic.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small White people being \textbf{racist} to each other......it completely blows my mind.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small what?  that's \textbf{nothing} Palestinians are been killed  and removed from their houses by yor people and they complaining  about antisemitism?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Hale Hortler that's a \textbf{dumb} comment.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small "We're being picked on"Continues to rule the Western world through bankers and enjoyed protection from ALL governments AND gets \textbf{racism} against them rebranded as anti-Semitism as if they're special\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Judaism is not a race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small This anti semitic card is being flung around for every problem  and is now getting \textbf{old} ...... !\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I guess Enoch was bang on when the natives of a \textbf{nation} are taken over by other races and people . And the   natives are poor TROUBLE AHEAD\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Its funny because Islam was basically Mohammed trying to be Jewish so maybe one party shouldn't have maintained that they were a superior \textbf{race} of people in the first place and there wouldn't be copycats.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small You go to prison for criticizing islam in those countries. People who deny the holocaust are \textbf{racist} so its illegal across the board. You should have respected american values now you will suffer.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small the special people its not \textbf{racism} or hate crime they get there very wn special wording ANTI SEMITIC oh look the chosen special people get there own special phrase BUT NO ONE ELSE DOES PATHETIC CONTROLLING LEACH ON NASTY PEOPLE\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small No ones was being \textbf{racist} or antisemetic. They were standing up for war crimes and land theft blatantly carried out by Israel on a daily basis. One day Palestine will be free. Mark my words\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small The \textbf{Quran} is toilet paper for pedophiles and anti seminstm\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small It makes me angry knowing that people are being persecuted in any form due to their religion, \textbf{ethnicity}.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Oh the outrage if a tax payer funded school had any other nations flags in pride of place (i did not see any british flags nor any vocal support for british armed forces ,what a pity they dont raise their voice for the actual soldiers who have died for them to live such happy lives )and so connected to a foreign \textbf{nation} whos founders killed british servicemen and their families(see king david hotel bombings ) . It is just as outrageous as having an islamic state school in 70 years time  could you just imagine a muslim school with say afghan flags with sports teams named after herat ,helmand , nuristan, and kabul sickening hypocrisy Ps the more i watch the more anstinishing the hypocrisy is could you just imagine somebody walking down the street in a turkish ,iranian afghan or  pakistani army t shirt he would be arrested\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/149 & \cellcolor{green!27}0.671 \\  \hline
  \cellcolor{green!5}\small דוד גולדשטיין you are \textbf{dumb} muslims in the UK don't cause any trouble to the Jewish community because we don't have hatred for them\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small What about Muslim misbehaviour? or indeed Christian and Catholic misbehaviour? Every religion and \textbf{race} has a history of some misbehaviour but it shouldn't be used as a reason to kick a kid in the head...\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small 1rst English are a \textbf{racist} Mongrel \textbf{nation}!\normalsize   & \cellcolor{green!5}Nation, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small Loyalty to the state of Israel?????? Get on out there! 100 years ago you'd never have dared say that in our country. You can't serve 2 masters.If anything it's a recipe for subversive interests. This is why Duke Wellington didn't want them living here.  [LINK]  We can respect them as human beings and wish them well but they should live in there own state. It's a disgrace! This country is falling apart from Organised Jewrys ideas of multiculturalism.They wonder why there not safe, because their crack skull  leaders like Rothshild and other organisations him and his ilk set up like the Fabian Labour Government promoting jewish interests from gradualist Zio Marxism as Sir Ernst Cassel put it another Jewish financier who set them up have promoted multi culturalism, which demographicly eans we are to be bred out in our own homeland in 50 years and we turn into the third world then after their leaders and organisations work in tandem co-ordination to destroy our culture, patriotism, values and promote \textbf{alien} values as we've seen for 60 years, it literally destroys the country, and  as the lady said the great grandchildren pack up their tents! Yet we are left! This is our home We know whats going on between the Coudenhove Kalergi plan and the Oded Yinon Plan. See through! We can read the Practical Idealism book from 1925 where Rothschilds Warburgs and Baruchs Zio man Count Richard Coudenhove Kalergi tells of the plan. If only the Great British reformer William Cobbett in nobodies pocket was around to speak truth to corruption and power and expose their madness in Parliament and defend the natives as he did in 1832 making the powerful tremble. We have \textbf{nobody} now they broke us.\normalsize   & \cellcolor{green!27}Alien, Nobody & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/289 & \cellcolor{green!27}0.692 \\  \hline
  \cellcolor{green!5}\small Yet again they refuse to ignore the cause of the problem. Just the same \textbf{old} rhetoric "anti-semitism, we're being picked on."\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small HITLER was pro-palestinian during WW2.The Palestinian founder Amin Al Husseini was a member of the \textbf{Nazi} party. Repacking a genocidal movement into a civil rights movement is how the Palestinians fool people!\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small great video. i would also like to see the tackling anti islamism video. i am against attacks on jewish or muslims, or any \textbf{race} or religion. i am also against conflating criticism of israel, for what they are doing to the palestinians, to anti semitism to shut the critics up. boycotting israel for its apartheid policies is NOT anti semitism. attacking jewish people and other semite people like muslims is anti semitism. but pro israeli gangs have hijacked the term anti semitism to mean something completely different to suit their political agenda which is abhorrent and evil. thank you\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small I was a Christian Zionist until 2013 when the UK government put me on a "target list" beginning with a laser beam attached to a satellite at my home. It took a  magical "spell" and the JEWISH KABBALAH  to find out it was a Jesuit who put me on the list. Of course the media lies to us and covers up for the damnable sons of Loyola. And you wonder why there is such anti Semitism in the \textbf{nation}.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small 'We are feeling more and more unsafe'      Then stop pumping the country full of Muslims you \textbf{dumb} asses!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I don't care if you are the hardest of hardline Zionist, as long as you find yourself within the confines of borders on the far side of another continent, \textbf{racist} abuse, threats, and violence is totally unacceptable. It's disgusting that there are schools, museums across Europe being protected at gunpoint. I'm not sure how much lower we can get as a society.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small But with mass jet travel and the electronic communication, especially INTERNET, the global Diasporas  can now field  paramilitaries in the host countries much better than the Irish could against the English during the \textbf{Fenian} era or even during  Provo times.\normalsize   & \cellcolor{green!5}Fenian & \cellcolor{green!5}Nationality - Irish & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Heinz Hertz,  I agree with you about Christianity but not about Judaism and Islam. Islam is only criticised freely away from the mainstream media or mainstream society. To criticise it opens you up to being called a \textbf{racist}. Judaism is probably a bit more protected from criticism than Christianity among normal people but definitely not in the mainstream media. The media trashes Judaism all the time.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small It's all a Jewish conspiracy you \textbf{R\textbf{ed}} \textbf{Nazi}..\normalsize   & \cellcolor{green!5}Nazi, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/8 & \cellcolor{green!5}37.5 \\  \hline
  \cellcolor{green!27}\small Eric Watchtower ....if you said any term at all that doesn't gloat all over Zionism ... you're automatically an anti-semitic... but you as being superior can get away with calling someone a \textbf{Nazi} without knowing one thing about them! Let's not forget who the allies were that fought against them...\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Questioning has \textbf{nothing} to do with hate.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Anna Bella  is that why an 89 year \textbf{old} German \textbf{woman} is sitting in jail to this day for questioning, not denying mind you, the Holocaust?\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Eric Watchtower  funny how those that accuse people of a "Jewish conspiracy" are obsessed with "everyone is a \textbf{Nazi} conspiracy"!\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I love when neo nazis quote Voltaire.  Here's some more Voltaire:It is difficult to free fools from the chains they revere.\textbf{Common} sense is not so \textbf{common}.and most apt:Those who can make you believe absurdities can make you commit atrocities.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small One can criticse Israel as long as they have evidence. Israel commits atrocities and war crimes;  it bombs hospitals,  schools and civilian homes. Israel shells kids playing on the beach. At the same time, they have the audacity to label critics as 'antisemitic'. Israel kills and arrests innocent Palestinian children.  They really do- don't take my word for it, search it up yourself. To sum it all up, Israel is a \textbf{terrorist} state. There's not a shred of doubt about it, consider its notorious history and it's penchant towards massacring the native Palestinian population.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small It's the English who should feel unsafe, there is more prejudice towards white English people at the current time  than Jews.. The Jews live in closed off communites and go to all Jewish schools. They do not have to take part in the multicultural experiment and experience what then English have to in a daily basis. It is English kids who are bullied just for being white, it is English girls who are groomed and raped by blacks and Muslims, it is the English who are victims of \textbf{witch} hunts for pointing out problems with multiculturalism . Stop with the poor \textbf{Ethnic} minority's act guardian you traitorous scumbags\normalsize   & \cellcolor{green!27}Ethnic, Witch & \cellcolor{green!27}Ethnicity - General, Gender - Female age and physical appearance & \cellcolor{green!27}2/108 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small There is more peace on the planet than ever in history.  You used to just tar and feather people for being \textbf{weird}.  Or cut people in half AT CHURCH for being pagans.  Hell humans used to cut out hearts of little girls and eat them.  The UK used to love pulling people apart with 4 horses.  And omg water boarding?  Humans used to stuff people in boxes filled with nails and pour boiling water on them to clean their sin.  Maybe you just need to move to a modern country where churches of other beliefs are built right next to each other.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small Jesse Davis like the \textbf{Nazi} lifestyle?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I cant get over how I was genuinely upset about the \textbf{racism} yet in the end the man was wearing and IDF shirt. \textbf{Racism} as seen in the rest of the video is NOT the same as being against the most evil army who commits crime after crime in extremely disturbing ways. What a tricky video, these should be CLEARLY distinguished!\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small Assuming a Jew supports Israel is just as wrong as assuming Muslims are extremists or Blacks are thugs. There are plenty of Jews against Israel and also who coexisted with Muslims and Christians before Zionists ruined that beautiful country. Also, any Arab cant be antisemetic because arabs are also semits! And these hate crimes are unexcusable and discusting on any level. However being against Jews is NOT the same as hating people who commit genocide, are \textbf{racist}, kicked people out of their own country because they think they should live there, and continue to commit atrocities everyday. These people are disgusting, and any clear minded Jew, Muslim, or Christians throat will swell with disgust at their crimes. I wish people would understand that all religion is pure, it is people who are impure. And let us stand up against injustice together hand in hand!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/144 & \cellcolor{green!27}0.694 \\  \hline
  \cellcolor{green!5}\small Also, the words antisemetic and \textbf{terrorist} are never used in a correct manner. These words are used to envoke emotions to get certain peoples agenda done. I suggest avoiding these two words as you the emotion behind them blinds peoples ability to understand reality.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Religion is a virus that has kept man in the dirt.  You are all one.  You are the cosmos.  God is in you, not a book.  One day Religion will be gone and all that will remain will be faith in your fellow man.  Then \textbf{nothing} in this verse will be out of our reach.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Why are people soo fickle to believe that hurting an unrelated segment of the group which acted poorly is in any way making things better or a solution to these political grievances?. They had \textbf{zero} to do with it. This happens all the time, whether it's Jews being attacked for the actions of Israel, Arabs after a \textbf{terrorist} attack. Etc. This is the exact same mindset which leads terrorists to blame the entirety of the west, \textbf{black} radicals see all whites as being 'the devil' or white supremacists blaming entire races for perceived slights against them.\normalsize   & \cellcolor{green!5}Black, Terrorist, Zero & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Religious Identity - Muslim & \cellcolor{green!5}3/96 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Palestinian movement was founded by a member of the \textbf{Nazi} Party (Amin Al Husseini).Once the media starts revealing this more: it will make all sense!\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Tnn Dll  There's aleady a documentary about him:  \textbf{Nazi} collaborators, the Grand mufti of jerusalem.  They still have Swastika's on Palestinian flags, saw them in footage of the the so-clalled peaceful protest.They even stores called Hitler in Gaza.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small They dont those evil scumbag terrorist\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Palestine doesn't exist because it destroyed its own \textbf{nation} by attacking Israel\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small HITLER was PRO-Palestinian during WW2.The founder of the Palestinian movement was a member of the \textbf{Nazi} Party (Amin Al Husseini).Something the media wants to keep a hush on.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Then go to Israel and fight the IDF and die like the \textbf{insect} you're !!!\normalsize   & \cellcolor{green!5}Insect & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Tnn Dll  You're right. Watch \textbf{Nazi} collaborators The grand Mufti of Jerusalem. Btw Palestian still support the \textbf{Nazi}'s, they even have stores called Hitler in Gaza. Look at the Swastika on their flags in the video by Pierre Rehov; Behind the Smoke Screen part 1 \& 2 or full movie, about the so-called peaceful protests in Gaza.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Jamie Grieve They are posers. They aren't Semitic. They are Eastern European converts. Since you mentioned Solomon, here's some scripture:Song of Solomon 1:5-6 King James Version (KJV)5 I am \textbf{black}, but comely, O ye daughters of Jerusalem, as the tents of Kedar, as the curtains of Solomon. Yes, B L A C K\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Is it primarily Muslim bigots acting out against the English Jewish community or Caucasians? The one man said he felt it wasn't Neo \textbf{Nazi} types, but I didn't catch what was said afterwards. Having grown up with Jewish friends, I have a special place in my heart for the Jewish religion, culture, and amazing food! I wish every Jewish person in this video could come live in Northern California! 😀However, California is having its own issues with immigrants, but that's another story...\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small and I am going to spit at every last Brit that I will encounter on the street due to their hatred of Israeli people who have \textbf{nothing} to do with their government!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Richard England why? The idf is not a \textbf{terrorist} organisation and is there to protect Israels borders and it's citizens. They don't fly planes into buildings, the don't bomb underground train stations and busses, they don't run people over with trucks and vans, they don't send suicide bombers into the public, they don't capture yazidi women and sell them as \textbf{sex} slaves, they don't go around destroying artifacts and raping children before putting a gun in their hands and forcing them to kill others. You are an ignorant child.\normalsize   & \cellcolor{green!27}Sex, Terrorist & \cellcolor{green!27}Gender - General, Religious Identity - Muslim & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small Not that I support the violence but what did he expect wearing an IDF t shirt to a protest? The IDF even admit themselves they target children and the disabled\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small "The IDF even admit themselves they target children and the \textbf{disabled}"Moron. The Palestinians teach their children to target civilians. and use their children as human shields.\normalsize   & \cellcolor{green!27}Disabled & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Yvette Moore it's highly documented that the idf have deliberately targeted children and the \textbf{disabled}. Deliberately killed unarmed civilians.This is in the documentary record.However, acknowledging crimes of one particular part of the Israeli government does not mean you have to withdraw support to Israel.I support Israel while at the same time can recognise criticism of the government.The amount of anti-semitism still rife is disgusting. The protests at the Kadem were awful.\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small +kc3vv the same reason people mix up ISIS with normal muslim \textbf{doctors}, nurses, shopkeepers, community leaders etc etc.\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I don't care if you are Jewish or you are a Heavens Gate Member.  All that matters is you are civilized enough to have your church next to a church of different beliefs.  And anyone who is \textbf{racist} towards Jews is a piece of shit.  When was the last time Jews even hurt people????  What you don't like Baklava?  Damn those Jewish neighbors and their tasty plate of treats!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small \@Jesse Davis​ Baklava is \textbf{common} pretty much everywhere in former Ottoman countries.Pizza is \textbf{common} in America, and Americans have their variations on it, doesn't make pizza American.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small She put the evidence right there , as she enters the Jewish school and pow symbols  of  ! ZIONISM !  The anti sematic thing is totally a farce a meme that gets them no were because it just doesn't exists not as a \textbf{race} not as a people. All that just remains is ZIONISM and its Zionists. Like the lady said true Jewish faith has totally utterly \textbf{nothing} to do with Zionism as it is infect forbidden by GOD and a sin.\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small +\textbf{Kraut} and Tea Fuck Israel, free Palestine! Greetings from the US.\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small +\textbf{Kraut} and TeaSettlements are colonialism and illegal.\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Kraut} and Tea The Israel apologist is imitating Nazis, how cute.\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Kraut} and Tea Irony deficiency seems a \textbf{common} problem with Israel apologists\normalsize   & \cellcolor{green!5}Common, Kraut & \cellcolor{green!5}Nationality - German, Social Class - Working class & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small +\textbf{Kraut} and Tea Nazis were in support of Israel, they just wanted Jews out of Europe.\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Kraut} and Tea How is this b8 m8?\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Kraut} and Tea Israel apologist advocates genocide of religious group, still calls others Nazis without sense of irony.\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Kraut} and Tea Read about Haavara Agreement and Madagascar Plan.\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small +Crystal Method If you don't want a Muslim \textbf{woman} in London to be spat on because of what ISIS is doing in Syria, then don't justify shitting on ordinary Jewish people thousands of miles away from Israel.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Kraut} and Tea Delusional man calls himself "civilised" while advocating largest genocide in history, still misses the irony.\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Kraut} and Tea There is pedophilia in Judaism too.\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Kraut} and Tea Delusional man calls himself "civilised", advocates mass genocide. Still missing the irony.\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@CJTaylor 87 Exactly. Palestinians suffer tremendously and their struggle against the occupation is a just cause. But that has absolutely \textbf{nothing} to do with ordinary British Jews who have every moral and legal right to feel safe in their home country.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small +\textbf{Kraut} and Tea you are the best example for the way people must think in order to create a country on top of another.every thing you said is a good representation of the country of israhell and every zionist should be proud of you.and i love it when you call others "\textbf{Nazi}"  :)\normalsize   & \cellcolor{green!5}Kraut, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - German & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small \@ndogg20 I call out bigotry whenever I see it. I don't give a shit whether it's a Muslim, a Jew or a Christian. As far as the attacks on Jews are concerned, it is ridiculous to blame 'Palestinians' for let's say the Aleppo or Alexandria pogrom on Jews. The overwhelming majority of Palestinians have never even set foot in those cities. Or even the Hebron pogrom for that matter. Much like my nickname indicates, I am an 'Afghan'. I however am not responsible for whatever sick shit \textbf{crazy} Afghans did, are doing or will do in the future. If a Palestinian attacks a Jew, he should be punished. If a Jew attacks a Palestinian he should be punished. Other people who happen to be either Jewish or Palestinian have \textbf{nothing} to do with that. Personal responsibility is the only thing that matters.\normalsize   & \cellcolor{green!27}Crazy, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/142 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Oh....and I'm not a Muslim. I'm related to \textbf{Abe} Lincoln and a direct descendant of Roger Williams, Founder of Rhode Island and Founder of The First Baptist Church in America through a once famous Reverend Valentine Wightman and Susannah Holmes.\normalsize   & \cellcolor{green!5}Abe & \cellcolor{green!5}Religious Identity - Jewish & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Kraut and Tea Don't listen to theses Putz.\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +\textbf{Kraut} may g-d the creator bless you for blessing his people Israel.\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Race, Ethnicity, Racist, Racism, Ethnic & \cellcolor{red!27}28 & \cellcolor{red!27}28/15120& \cellcolor{red!27}0.19 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}3 & \cellcolor{red!5}3/15120& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Jewish}  & \cellcolor{red!27}Shylock, Abe & \cellcolor{red!27}2 & \cellcolor{red!27}2/15120& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Crazy, Mental, Dumb, Weird, Disabled & \cellcolor{red!5}12 & \cellcolor{red!5}12/15120& \cellcolor{red!5}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Herman, Kraut & \cellcolor{red!27}15 & \cellcolor{red!27}15/15120& \cellcolor{red!27}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common & \cellcolor{red!5}9 & \cellcolor{red!5}9/15120& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}5 & \cellcolor{red!27}5/15120& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - European or anti-Europeans}  & \cellcolor{red!5}Brexit, Remainers & \cellcolor{red!5}3 & \cellcolor{red!5}3/15120& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Nazi, Red & \cellcolor{red!27}14 & \cellcolor{red!27}14/15120& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Zero, Insect & \cellcolor{red!5}14 & \cellcolor{red!5}14/15120& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, African & \cellcolor{red!27}6 & \cellcolor{red!27}6/15120& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!5}Dot & \cellcolor{red!5}1 & \cellcolor{red!5}1/15120& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist, Quran & \cellcolor{red!27}9 & \cellcolor{red!27}9/15120& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian, Red & \cellcolor{red!5}7 & \cellcolor{red!5}7/15120& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationality, Nation, Alien, doctors & \cellcolor{red!27}9 & \cellcolor{red!27}9/15120& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Woman, Sex & \cellcolor{red!5}4 & \cellcolor{red!5}4/15120& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Irish}  & \cellcolor{red!27}Fenian & \cellcolor{red!27}1 & \cellcolor{red!27}1/15120& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female age and physical appearance}  & \cellcolor{red!5}Witch & \cellcolor{red!5}1 & \cellcolor{red!5}1/15120& \cellcolor{red!5}0.01 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - General;Age - General;Religious Identity - Jewish;Physical Identity - Physical (and Mental) Impairments;Nationality - German;Social Class - Working class;Age - Over 65s;Nationality - European or anti-Europeans; Ideological and Political Identity - General;Age - Youngsters;Ethnicity - Black;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Religious Identity - Muslim;Ethnicity - Native-American;Nationality - General;Gender - General;Nationality - Irish;Gender - Female age and physical appearance;%.

\item The percentage of hate speech related words is 0.9458.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 145/754 occurences of hate speech related comments.\end{itemize}\end{document}