\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_120.json :}\newline \par\Large\textbf {Title: \large  Ageism Towards Older People - Motion Graphics }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small This is backwards in some areas. Obviously people who can't hear well in \textbf{old} \textbf{age} need to be spoken to louder. And people who are weak in \textbf{old} \textbf{age} obviously need someone to help them.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}4/35 & \cellcolor{green!27}11.429 \\  \hline
  \cellcolor{green!5}\small Its so sad. 30-50 year olds think they are really intelligent and hate on other ages. As a kid so many people thought I would be horrid and noisy but really I wasn't and they were so suprised when I was polite. Many \textbf{old} people are thought to be stupid although they are so much more intelligent than adults. They are not \textbf{racist} or bigoted unlike adults and are equal to everyone.  They treat \textbf{racism} equally against everyone not just so called minorites\normalsize   & \cellcolor{green!5}Old, Racism, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}3/83 & \cellcolor{green!5}3.614 \\  \hline
  \cellcolor{green!27}\small Is this why some people don't like to say their \textbf{age}? Because they think the other person will be condescending towards them just in case they're older?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Umm.. honest question: I helped an older lady who seems to have her hand full and walks slow with  getting a shopping basket at a supermarket, am I an \textbf{ageist} now?\normalsize   & \cellcolor{green!5}Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small It's so unfair. I'm 12 and even I think \textbf{age} laws are \textbf{dumb}. I mean, I understand the "Can't drive till 16" law, but you can't get a job until your 14? That's just pure dip shi. I mean, girls are way more mature than boys, and at \textbf{age} 12? IMAGINE HOW MATURE THEY'D BE, AND THEY'RE NOT MATURE ENOGUH TO GET A JOB? BOYS ARE VERY MATURE AT \textbf{AGE} 12 AS WELL. AND NO PERSON UNDER THE \textbf{AGE} 14 CAN GET A JOB? PURE DIP SHI. AND DONT COMPLAIN ABOUT MY GRAMMAR JUST CAUSE IM A KID OR ELSE YOUR JUST ANOTHER ONE OF THOSE STUPID \textbf{AGEIST} GOVERMENT SHIS.\normalsize   & \cellcolor{green!27}Age, Ageist, Dumb & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/110 & \cellcolor{green!27}5.455 \\  \hline
  \cellcolor{green!5}\small EVERYONE UNDER THE \textbf{AGE} OF 12 IS ACCEPTABLE AT NOT HAVING ONE\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small iphone is fucking up. better ask my grandpa. after all i don't want to be \textbf{ageist} and \textbf{old} people have more experience so i'm sure he'll be able to help me out.\normalsize   & \cellcolor{green!27}Ageist, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I am daily criticized for my \textbf{age}, and constantly suffering derogatory comments. And I'm not even \textbf{old} yet!\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small There's a difference between \textbf{elderly} people and geezers.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small i call bull on this because \textbf{old} people don't go through \textbf{ageism},in fact people respect \textbf{old} people that even cops won't ticket them for doing wrong,now young people on the other hand gets the short end of the stick just look at how society is treating young people compare to \textbf{old} people\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/52 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small a comment that tears at humans society - \textbf{ageism} works both ways\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Affects just \textbf{old} people ?? NO I am afraid it affects even younger people, for example in my case young people who are 5 or more years younger than me avoid having anything to do with me.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Being \textbf{old} is not a disease, but many \textbf{elderly} folks think of themselves that way. And most young people look at them that way. Rise up \textbf{old} folks! Shake off your generations of decline, defeat, surrender and despair. Hit the eject button on your recliner, grab your cane and whack a man bun wearin' \textbf{snowflake} upside the head! When he looks up from his smart phone...whack him again!\normalsize   & \cellcolor{green!27}Elderly, Old, Snowflake & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!27}4/68 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Your video is wonderful. It's very well done and informative. If you fix the typos it will be perfect. First, fix "assistance" in the slide citing the \textbf{Age} Discrimination Act. Then fix the word "gereatric." It is spelled "geriatric."\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Being 50+ and a top segment programmer or coder doesn't mean anything if you see yourself losing out to young coders who not even possess one quarter of your experience, just because your prospective boss thinks you couldn't possibly know about the latest languages or are not able to learn the new ones. This \textbf{ageism} is especially rampant in Silicon Valley.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Okay, seriously? What is wrong with helping \textbf{old} people move heavy things? It is not an "assumption" that they are weak, it is true! Yes, of course, some \textbf{old} people have kept up with fitness, so they are unusually strong. However, from personal experience in seeing my grandparents \textbf{age}, they are, in fact, getting weaker. It happens. Atrophy increases as people \textbf{age}; it's science. So, it is not assumption if it is true. There is \textbf{nothing} wrong or "\textbf{ageist}" about supporting and helping \textbf{old} people, especially the ones you love.\normalsize   & \cellcolor{green!5}Age, Ageist, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!5}6/90 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I work in the supermarket and I have to put up with these \textbf{old} crones\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small How the hell does \textbf{ageism} affect young people? I didn't even know you could be \textbf{ageist} towards anyone but \textbf{old} people.\normalsize   & \cellcolor{green!5}Ageism, Ageist, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Exactly, I'm young and every time I've been discriminated based on my experience it's because I don't have any, being just 20 years \textbf{old}. Honestly, I think that as young people we shouldn't be whining about \textbf{age} discrimination because we're still far from reaching the top of the income ladder which is during our 50s. What I usually see is people that could continue working and become even more productive being set aside because they're seen as too \textbf{old} and unfit for the job. Society has to realize that not every person's income has to peak at around the ages of 50 some people are extraordinarily healthy and would fare better as employees if they had the possibility to at least prove they could extend their income gains up until around they reach 70. Top executives are able to prove to society that they are better workers in their 60s than in their 50s and 40s but most people don't even have that possibility, that is ruled out for most people who don't belong to the elites. Donald Trump is 70 and I don't see \textbf{age} as being the reason that would make him unfit to be president of the USA, maybe other reasons may exist, but not \textbf{age} because he walks well for someone his \textbf{age} and he reasons the same way he reasoned about issues when he was in his 30s so he doesn't have any form of dementia. But still, the media promotes the belief that politicians should be young and energetic, and people prefer to be represented by the younger and less experienced politicians. But why? Do people want to do physical exercise with their young and also the sexiest prime minister ever (media), Justin Trudeau? I generally think it's risky to put very young people who haven't proven themselves in very high positions, particularly in investment banking, for instance, which is what's happening nowadays. For for-profit corporations, investment advisories and the like being young, energetic, and educated at an Ivy League shouldn't even be seen as an asset, rather they should be seen as a risk factors. It used to be that way, just look at what happened to Stroh Brewery after a Harvard brain with no experience and "notebook" notions of risk and management took over his family company. As a young person I've always been weary of taking a job which I know it will be very difficult to significantly start climbing up the income ladder when I'm 30 because I know I wasn't educated at an Ivy League institution, thus I I'll never have the possibility of landing a 100k job even with relatively little marketable technical skills like it happens with Ivy alumni nowadays, but still I want to continually learn and become more productive. Also, I know that when I reach an older \textbf{age} I'll probably be healthier than most people my \textbf{age} so I'd want an employer who knows how to calculate employee productivity so I could extend my income ladder gains to match my productivity gains. Ideally, we could live in a world in which everyone retired when they wanted or when they were really unfit, but we don't live in a world like that and the main fault is people. My paternal grandfather is 80 and semi-retired though he only really retired at around 75, when he reached the peak of his career, being very competitive I've always wanted to be like him when growing up, but that's next to impossible if you're not self-employed or already in the top of the income chain. I can bet with anyone that as more and more people in their 30s and early 40s are given more control of operational activities in investment banking and the like, whereas employees still in their 50s enter retirement mainly as a result of crowd thinking and too much academization of business, it will harder and harder to find large companies which can handle important and informed decisions for their clients in a professional manner. They say the world is data driven and we need people who have knowledge in acquiring it, and the best to bother learning new systems and processes on a weekly basis are the young. But how are they the most productive if they're also generally too \textbf{dumb} to understand the signicance and insignifance of the researched data? Every older investor realized instantly that high-frequency trading was doomed towards abismal failure through easy deductive logical reasoning but the young careless silver spooners didn't. "The best CEO is an 80 year \textbf{old} male inside his office during the day, thinking and reading", Charlie Munger.\normalsize   & \cellcolor{green!27}Age, Dumb, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}10/773 & \cellcolor{green!27}1.294 \\  \hline
  \cellcolor{green!5}\small I cant fucking stand white \textbf{old} ladies. They bitch and complain bout anything, hold up the lines with there coupons to save 25 cents, and god forbid there cupons arent valid and they have to pay 25 cent extra thats a whole process. Rude ass ppl, im at the point i get angry just seeing an \textbf{old} ass bitch even walk into my store because i knows shes gonna trouble my life. I my friend am an agiest i cant stand them. U walk .05mph well step to the side and let ppl through you \textbf{old} fuck.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/97 & \cellcolor{green!5}3.093 \\  \hline
  \cellcolor{green!27}\small Lmao. I hate \textbf{old} white women with money and have that shifty Bucharest face.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I'm white but cool lol. I refuse to be a frumpy \textbf{old} white bitch no one likes. My mom was cool, everyone loved her and hse had a great sense of humor and was an amazing artist.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small \@cameleon Girl Yeah some \textbf{elderly} are just super sweet cant say there all bad lol Chances are if your mom was cool you most likely took after her :)\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Old men are the ones who make the decision to go to war, and the young men are the one's who die at war. get real!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Some of those \textbf{old} men ALREADY have been to war themselves.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Ageism to older people? Seriously? In a society where its completely legal to pay someone under 18 a lesser wage... omg... You can't be serious. Even on welfare older people get paid more LEGALLY!!! That is \textbf{Age} discrimination toward younger people is written into LAW. If one of these young people were to speak out against this no one would bat an eye simply because no one respects the opinion of a "kid".... \textbf{Age} is \textbf{nothing} but a number? Most of the people complaining about \textbf{ageism} are older people and people listen because they are \textbf{old} and people take their opinions seriously. Young people complain and no one cares smh... And im 33\normalsize   & \cellcolor{green!5}Age, Ageism, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!5}6/113 & \cellcolor{green!5}5.31 \\  \hline
  \cellcolor{green!27}\small +Michael Gibson I am absolutely serious. And I agree that it goes both ways, against the young and older alike as I already stated if you read what I said. I experienced the same bullshit 20 years ago with the lower pay when you are younger. But my point really is that this society does that to youth and then turns right around and displays the same sorts of attitudes toward you once you get older as well. I'm not talking 80 years \textbf{old} here or even 60 but 40s-50s primarily. This isn't an ;older vs younger issue with me. This warped society does not look at merit and ability as much as it does \textbf{age} whether that be younger or older. Think about it, you get it hit with it when you are younger and then hit your 40s-50s and people as well as employers etc begin hitting you with it again. Not always in the same categories but it is an attempt to marginalize and limit you just the same.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/172 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small +Michael Gibson If you would like to hear more about \textbf{ageism} towards younger children rather than \textbf{elderly} citizens, i suggest you look up and research adultism. I think it will provide you with what you seem to be looking for. \textbf{Ageism} CAN mean discrimination against young people, but it is generally regarded as discrimination against older people, as to seperate them into categories. \textbf{Ageism} against the eldery is very much a problem, and it is your opinion if you believe that adultism is more of a problem. In MY opinion I would agree with you if that were the case. I DO believe that adultism is a bigger issue, but \textbf{ageism} is very much a problem that needs to be dealt with. AS a thirteen year \textbf{old} boy who deals with adultism on a daily basis, it is not a surprise that I would have a bias towards abolishing all forms of adultism over \textbf{ageism}. I hope you have a great day man, and I hope i helped you in any small way that i can. Much love, bro <3\normalsize   & \cellcolor{green!5}Ageism, Elderly, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}7/180 & \cellcolor{green!5}3.889 \\  \hline
  \cellcolor{green!27}\small ageism is so bad it happens even if your 26, there a lot of cases where a yunger person with just a few years looks down on me, where is the world going ?\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Well can't say I didn't see this term coming feminists are going to have to use this in a different way to combat the men that do not want to marry women that either put \textbf{sex}, have children or jobs and waited until they were 30/40 to marry. At the end of the day with our gov in work men only need \textbf{sex} and comfort in a relationship. Both can be obtained through other ways.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small This is very well made. Do you mind if I show it in my presentation on \textbf{ageism}?\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small People do not necessarily naturally create these stereotypes but rather iyt is the culture that chiefly government and media have foissted upon us and beat into our minds on a daily basis, multiplee timees a day. Radio, internet and TV. I believe thiss has been and continuess to be hardest on those in their 40ss and 50s. Often people at this \textbf{age} can sstill do things much the same as they have always done because unless they have abusedd themselves, they are often not \textbf{age}/health limited in theeirr functions in life. But we do not accept them doing so, thuss they have to artifficially give in to what society says it will limit them to. You might, for example, even feel too \textbf{old} at 85 to do certain things and that is okay, but whaat off the man or \textbf{woman} at 40 or 50 who is still physically healthful? Are they to stop living as they see fit simply because society says they are too \textbf{old} ffor this or that? Yes, really these are the group who I believe are quietly the mmosst negatively affected by \textbf{ageism}. At that \textbf{age} range you can accomplish or bee healthy enough to ddo thee ssame ass any otherss but are literally harrassed by merely doing so. I am 38 this year and can already see theese attitudes approaching in people around me in this country. Very strange world we live in.\normalsize   & \cellcolor{green!5}Age, Ageism, Old, Woman & \cellcolor{green!5}Age - General, Age - Over 65s, Gender - General & \cellcolor{green!5}6/238 & \cellcolor{green!5}2.521 \\  \hline
  \cellcolor{green!27}\small When you are young they tell you that you cannot do this and that and once you get older they tell you the same thing. Youth and the \textbf{elderly} are the focus of the \textbf{ageism} issue when in truth, it is those within the 40-60 \textbf{age} ran ge that are in the middle and are the real crux of the problem. Would we live in a more merit based society, it would not be an issue. If you could so something, then it is acccepteed that you can no matter your \textbf{age}. However, we live in a system based society and we have been inculcated that whether you can actually do a particular thing or not, the focus is not on you ability but rather your \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Ageism, Elderly & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}5/127 & \cellcolor{green!27}3.937 \\  \hline
  \cellcolor{green!5}\small There's also \textbf{ageism} towards teenage individuals. Me and a group of friends decided to go shopping at a local grocery store a few months ago, we were all teenagers. An older-aged adult lady stomps up to us with her loud high-heels as we walked through the door and rudely asked us if we were going to shoplift or rob the store, and threatened to call the police if we didn't exit the building. We weren't planning to commit a crime, either...This is the same thing as a \textbf{racist} thinking a \textbf{black} man walking into a store is a thief.\normalsize   & \cellcolor{green!5}Ageism, Black, Racist & \cellcolor{green!5}Age - General, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/99 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@TheBarracudaDriver13 I believe you because I have experienced that sort of attitude as well. However, think of the times you yourself have probably acted similarly toward someone older. I don't even mean \textbf{elderly}. Just wheneever you yourself have expressssed the attitude that someone older than you should not be in a certain place or be doing a certain thing, simply based on their \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Elderly & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@ScemptorDraghie I respect people regardless of their \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I'm 59, \& I recall crabby people of all different ages assuming incorrect things about me when I was a teen \& in my early 20s.  I think \textbf{ageism} is an equal opportunity employer...against both ends of the \textbf{age} spectrum.\normalsize   & \cellcolor{green!27}Age, Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small no one makes videos of \textbf{ageism} against KIDS?!?!?!?!?!? IM A KID, BUT GUESS WHAT? I CHALLENGE ANY ADULT HERE TO GIVE ME REASONING QUESTIONS THAT I CAN'T GOOGLE, REPLY! caps are for attention.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small sorry but kind of angry, because you adults think of us as inferior pieces of walking meat with no ability to use their brain. I have plenty ability to use my brain, and my dream is to stop \textbf{ageism} and give equal rights to people of all ages. Abraham Lincoln, Martin L. King, Cezar Chaves, John F. Kennedy- all people who helped in a civil rights protest. I wish to be next on that list someday.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small Is it possible that you send me the text that you talk in that video, I would need some parts for a presentation about \textbf{ageism}. It would be awesome\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Would you mind if I used this video in a class presentation about \textbf{ageism}, if I gave you credit/cited you?  And if so, would you like your full name to be used or your screen name?\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small They should have talked about both. How \textbf{ageism} effects youth so much. Kids aren't allowed to drink, drive, get no education, vote, go in tanning places, or get a job.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I didn't talk about the youth because the main video was directed to showing how \textbf{ageism} affects older people specifically.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small ageist make a video about youth \textbf{ageism} NOW \textbf{AGEIST}!\normalsize   & \cellcolor{green!5}Ageism, Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/9 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Title says "\textbf{Ageism} Towards Older People"\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small What does \textbf{ageism} have to do with \textbf{old} people\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small No. I used the man with a cane for the viewer to better differentiate between the different ages. Since I only had simple graphics to work with I had to include objects to better describe the \textbf{age} group I was talking about.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Almost made me cry. Almost, Can you hook me up with a sponsor to move me to Japan? People are so \textbf{lame} as to think they will not get older. GET A CLUE WAZOO! Good report! Well done...sad. But...true. Very sad. Very true.\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age, Ageist, Ageism & \cellcolor{red!27}61 & \cellcolor{red!27}61/3788& \cellcolor{red!27}1.6099999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Elderly & \cellcolor{red!5}37 & \cellcolor{red!5}37/3788& \cellcolor{red!5}0.98 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racism, Racist & \cellcolor{red!27}3 & \cellcolor{red!27}3/3788& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Dumb, Lame & \cellcolor{red!5}3 & \cellcolor{red!5}3/3788& \cellcolor{red!5}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Snowflake & \cellcolor{red!27}1 & \cellcolor{red!27}1/3788& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing & \cellcolor{red!5}2 & \cellcolor{red!5}2/3788& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Sex, Woman & \cellcolor{red!27}2 & \cellcolor{red!27}2/3788& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black & \cellcolor{red!5}1 & \cellcolor{red!5}1/3788& \cellcolor{red!5}0.03 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - General;Age - Over 65s;Ethnicity - General;Physical Identity - Physical (and Mental) Impairments; Ideological and Political Identity - General;Age - Youngsters;Gender - General;Ethnicity - Black;%.

\item The percentage of hate speech related words is 2.9039.

\item Considering that the variable \textbf{Age - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 113/81 occurences of hate speech related comments.\end{itemize}\end{document}