\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_153.json :}\newline \par\Large\textbf {Title: \large  Ageism and misogyny could become hate crimes in UK, but police are wary }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small What about \textbf{misandry}?\normalsize   & \cellcolor{green!27}Misandry & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Misogyny only? Do \textbf{woman} not objectify men? Of course not. Feminazis are an interesting bunch.\normalsize   & \cellcolor{green!5}Misogyny, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Effectively what are the police going to do? Issue an ASBO? On the spot fine? If there's an issue they can already deal with it.If you are the victim of discrimination there is legal redress available to you. For example if you are fired due to your \textbf{gender} or \textbf{age} and you can prove it you will receive appropriate compensation. Discrimination is illegal.The question is do we need additional laws to address what is already dealt with under the law? If some guy is being a vile cretin and harassing every \textbf{woman} in sight the police can already deal with him. Ask the police, do they need these laws to do their job?\normalsize   & \cellcolor{green!27}Age, Gender, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}3/115 & \cellcolor{green!27}2.609 \\  \hline
  \cellcolor{green!5}\small Are they going to arrest a child who upon seeing a \textbf{bald} headed man, naturally describe what he or she see, put in jail?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small For some reasons, the government wants to control social behaviour. Freedom vs social control has become something normal. Probably the government just wants to control the people, particularly males. But what if a \textbf{woman} doesn't like another \textbf{woman} or fight  each other? Maybe British culture is kind of extreme and the government wants to change that. How about religions or cultures that are generally against women? Do they get a pass?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small Misogyny?How many years in jail will we get for telling feminists to make us a sandwich,while rapists rape up a storm while the Plod are busy arresting us for sandwich requests?ENGLAND IS FUCKED.\normalsize   & \cellcolor{green!5}Misogyny & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small So now adults can have \textbf{sex} with underage, and if you are against, then you are an \textbf{ageist}. Also, being against \textbf{misogyny} is islamophobic.\normalsize   & \cellcolor{green!27}Ageist, Misogyny, Sex & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}3/24 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small WTF is \textbf{Ageism} ?\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small ageism and \textbf{misogyny} do not belong in the category of hatecrime  they belong in the discrimination category that's all. also so if u don't give more funding to police to go with all that extra work than this becomes a hollow gesture. but let's be frank the British govt are using this as a desperate distraction technique because \textbf{nothing} else is going right at the moment.\normalsize   & \cellcolor{green!27}Ageism, Misogyny, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters, Gender - General & \cellcolor{green!27}3/66 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I think they rather should patrol London making sure normal People dont get stabbed all 5 minutes by some \textbf{migrant} Gangs\normalsize   & \cellcolor{green!5}Migrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small a few years ago.i got almost murdered because i refused to join in illegal activities... but i managed to get away from it (by running)... but the judge said i was likely a \textbf{racist}... my mouth fell open and then i knew "they are incompetent, next time i will do anything i can to keep the police out of it"... best to let the criminals and murderers go their way.. just run thats it\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small Lipidism should also become a state crime. \textbf{Fat} women and men are routinely discriminated by employers.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Maybe stop making new laws, till police can keep up with there \textbf{old} laws, like rape of children all over UK.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small If being called a Coconut Head is a hate crime, you need to get a thicker skin, being \textbf{black}, I was called all sorts at school and outside in the the 80s and it didn't bother me one bit...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Hate crimes need to be eradicated from our planet. I've been writing my congressman to write new legislation about this problem. I'm proposing the death penalty to anyone who discriminate against another human being. It's the only way we're going to eliminate \textbf{racism}, bullying.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small First get real crime under control. People are sick of hearing the entitled victims screaming about \textbf{gender}, diversity and trans rights. Get rid of the polically motivated police commissioners, that would be a good start.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small How about \textbf{Misandry}? There is more than plenty of that going around now a days.\normalsize   & \cellcolor{green!27}Misandry & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Â©â„¢ TMALX Transnational ðŸŒ MilitantðŸ’¥ ArmedðŸ”«Liberationâ›“ XecutiveðŸ•¶ Observation âœ âœSo a dirty \textbf{old} man ( mysogonistic) is being discriminated against by picking on his proclivities when he's \textbf{old}?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small It should include Misandry\normalsize   & \cellcolor{green!27}Misandry & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small What the \@ is \textbf{ageism}?  I thought it was a pagan god.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Qualifying \textbf{ageism} as a "hate crime" is a good thing". That way, next time an 20-year-\textbf{old} girl says that I'm too \textbf{old} for her (I'm 49), I will go to the police and denounce her for "hate crime". That'll teach her.\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small It should be hate crime when chinese \textbf{woman} release garlic fart in elevator.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small The Queen is an unelected \textbf{nazi} \textbf{old} fart, but it's a crime to say it because is a \textbf{common} secret.Puritanism is a neurosis, wake up people and face the truth.\normalsize   & \cellcolor{green!27}Common, Nazi, Old & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small So if you get called a coconut that means a bad thing?? I'd imagine one would be flattered to be called an exotic \textbf{fruit}. Hard brown and hairy on the outside and sweet and juicy on the inside. I don't see the \textbf{racism}. Don't come to America if being called a coconut ruins your day.\normalsize   & \cellcolor{green!5}Fruit, Racism & \cellcolor{green!5}Ethnicity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small UK is already a dystopian \textbf{crazy} house with their "hate crime" nonsense, let's see how this helps them out. Fools...\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Anti-Ageism implies equal \textbf{age} of consent?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small British values seem not to include the idea of upholding their \textbf{ethnic} makeup... The uk has become a fucking zoo!!!\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small no-thing Whaaaaaat??Let's fact check shall we?When Europeans came to India (17th century) India had 27 GDP.When Europeans left india (20th century) India's GDP stood 1You people exploited and crippled a once great \textbf{nation} for centuries. Same with Africa, (Google 'Scramble for africa')\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small What about still having a fucking Queen!? The world speaks english because of a psychotic royal family who still holds power and collects taxes from the poor. You want me to beleive the royal aryan bloodline needs to step down , its the definition of \textbf{racism} and hate\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small too \textbf{old} to go to any toilet  .... ahhhhhhhh\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Melodramatic snowflake\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Tony blair is a \textbf{terrorist} who bombed people over and over\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@drop the dead donkey doesn't make him any less of a terrorist\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@drop the dead donkey the killing part howevrer is only true in western nations that still function like good \textbf{old} vikings...britian,france and america  the worst at the moment.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@drop the dead donkey yes the food blockage by trillions of dollars of weapons sold openly to saudis by americans clearly has \textbf{nothing} to do with the west.... the same west that claims to fight radical islam are the strongest ally with the most radical \textbf{nation} there is next to israhell.\normalsize   & \cellcolor{green!27}Nation, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small The UK is so mind fucked but I'm still hoping \textbf{Brexit} succeeds. As long as it's out of the god damn EU is a start.Don't forget the EU wants Europeans replaced by "diversity" and this tracks back to "Mr." Richard Kalergi.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Hey that's \textbf{racist}!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small And the madness continues, liberalism really is a \textbf{mental} disorder\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Liberalism is NOT a \textbf{mental} disorder. But Leftism and Socialism ARE.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Maybe not liberalism, but certainly a \textbf{mental} disorder. Gone soft in the brain. I am 64, so anyone who calls me an \textbf{old} fart gets picked up by the local constable???? ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚Political correctness you say? That concept has already lost its true meaning. What a sobbing sad little world this has become that we soon won't be allowed to shout a few curse words at each other to vent our anger and be done with it.\normalsize   & \cellcolor{green!5}Mental, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Misandry, Misogyny, Woman, Gender, Sex & \cellcolor{red!27}15 & \cellcolor{red!27}15/3892& \cellcolor{red!27}0.38999999999999996 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age, Ageist, Ageism & \cellcolor{red!5}7 & \cellcolor{red!5}7/3892& \cellcolor{red!5}0.18 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Bald, Fat & \cellcolor{red!27}2 & \cellcolor{red!27}2/3892& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing & \cellcolor{red!5}2 & \cellcolor{red!5}2/3892& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Migrant, Nation & \cellcolor{red!27}3 & \cellcolor{red!27}3/3892& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Racist, Racism, Ethnic & \cellcolor{red!5}6 & \cellcolor{red!5}6/3892& \cellcolor{red!5}0.15 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}8 & \cellcolor{red!27}8/3892& \cellcolor{red!27}0.21 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black & \cellcolor{red!5}1 & \cellcolor{red!5}1/3892& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}1 & \cellcolor{red!27}1/3892& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Nazi, Snowflake & \cellcolor{red!5}2 & \cellcolor{red!5}2/3892& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Fruit & \cellcolor{red!27}1 & \cellcolor{red!27}1/3892& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Crazy, Mental & \cellcolor{red!5}4 & \cellcolor{red!5}4/3892& \cellcolor{red!5}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}2 & \cellcolor{red!27}2/3892& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - European or anti-Europeans}  & \cellcolor{red!5}Brexit & \cellcolor{red!5}1 & \cellcolor{red!5}1/3892& \cellcolor{red!5}0.03 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Age - General;Physical Identity - Physical Features;Age - Youngsters;Nationality - General;Ethnicity - General;Age - Over 65s;Ethnicity - Black;Social Class - Working class; Ideological and Political Identity - General;Sexual Identity - Male homosexuality;Physical Identity - Physical (and Mental) Impairments;Religious Identity - Muslim;Nationality - European or anti-Europeans;%.

\item The percentage of hate speech related words is 1.4132.

\item Considering that the variable \textbf{Gender - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 55/224 occurences of hate speech related comments.\end{itemize}\end{document}