\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_278.json :}\newline \par\Large\textbf {Title: \large  Lord Jonathan Sacks: 'Anti-Zionism is the new anti-Semitism' - BBC Newsnight }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small You must be \textbf{crazy}. A vast majority are very pro Israel. Me included.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Antizionism as I understand it, is opposition of the Political and Military actions of the Israeli Government and their THEFT of Palestine and ever-growing land grabbing.  THAT is what i oppose and that is why I refuse to be labelled as antisemitic. I have \textbf{nothing} against Jewish people or their religion. And because I am an Atheist, I do not believe in any religion. I see all religions as ways for governments to force regimes onto lands of people for control through blackmail and fear of persecution. So, take away religion in Israel and you're left with a Banking Gangster Cartrl who stole a country to use as a military base in order to force commercial, economical and governmental control into other local countries, especially for their oil and other minerals.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/131 & \cellcolor{green!5}0.763 \\  \hline
  \cellcolor{green!27}\small Am I drunk or did he equate being British to being Jewish and therefore being anti Jewish is \textbf{racism} consequently making being anti British also \textbf{racist}... Even though neither are a \textbf{race}... Seriously I'm drunk, help me out\normalsize   & \cellcolor{green!27}Race, Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/38 & \cellcolor{green!27}7.895 \\  \hline
  \cellcolor{green!5}\small Zionism is the problem here .... \textbf{nothing} to do with Judaism\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Nothing is wrong with Zionism. It's purely the belief Jews deserve there own Home land and that Israel is it.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Beside the fact that Judaism as a religion have \textbf{nothing} to do with \textbf{ethnicity}, while Zionism as a political ideology is separate from Judaism, if being against Torah, or Talmud also means to be against the Semites as an \textbf{ethnic} group, then being against Quran/Islam is even more anti-Semitic, because the wast majority of (pure) Semites are currently Muslims, not to mention that it's hard to find a Semitic-Jew, or a Zionist of Semitic background, because most of those, who occupies Palestine are actually of European origin.\normalsize   & \cellcolor{green!5}Ethnic, Ethnicity, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/87 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small This man led the march of the flags through east Jerusalem.  I've seen who the real racists are the last two years. Loxism is the elephant in the room. Loxism is the oldest form of \textbf{racism}. Sacks, sugar, lipman, overman and hodge are loxists.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Antizionism is \textbf{racism}, all nazis are antizionists\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Israel probably funds this guy \textbf{nothing} he says can be taken seriously\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Anti-Nazism, Anti-KKK and Anti-White-Nationalism is anti-white and \textbf{racist}.  Now Mr Sacks I have a request: let me bulldoze your house and build a castle for white people on top of it.  If you disagree you're saying you don't believe white people should have a home.  So you're saying you don't think white people should exist.  I eagerly await your reply so I can know when the demolition/construction can begin.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Oh come on, If I criticise the Israeli government I'm seen to be criticising Zionism, so lets debunk this myth that Zionism is the new anti-Semitism. It is not anti-Semitic to say that the state of Israel should exist within a framework of equality, and not in the framework of preference and superiority, but by god, if I was an MP in the Labour Party that said this, I would be outed from the party and hounded by the press as an anti-Semite! Anti-Semitism can exist without anti-Zionims and anti-Zionism can exist without ant-Semitism. Anti-Zionism is on the rise because young progressives are suspicious of any form of \textbf{nationalism} that appears exclusive and Zionism is \textbf{ethnic} \textbf{nationalism} because it excludes many of the people under its control. It denies millions of Palestinians their basic rights. Anti \textbf{nationalism} is a growing trend and that's why anti-Zionism is on the rise. Its not a disease that's causing this, its easy access to knowledge.\normalsize   & \cellcolor{green!27}Ethnic, Nationalism & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}4/161 & \cellcolor{green!27}2.484 \\  \hline
  \cellcolor{green!5}\small Antizionism is nazism + \textbf{racism}. All nazis are antizionists.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small TRUTH IS THE NEW RACISM\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I am very much a believer that language is mutated in much the same way as Jonathan Sachs descirbes \textbf{racism} as a virus. I came to watch this because I have noticed that throughout the "anti-semitic Labour Party " alegations two of the most direct victims of the attacks are two old-guard traditional socialist leaning politicians with incredibly positive records regarding combatting \textbf{racism}. My earlist political memories are associated with the Anti-Nazi movement and the free festivals arranged by Ken Livingston, in the late 1970's with the "Rock against \textbf{Racism}" events. And Jeremy Corbyn, who has protested throughout his adult life in many anti-racist events.Neither of these individuals have made statements that involved any attacks, but their words were intentionally taken out of context. I am almost bemused by the fact that no-one at all in the mainstream media addresses the question of "political zionism", and apart from george galloway in a very biased episode of QT, I have not seen an episode of Questiontime where an audience member has asked a question about the "Zionism" issue. Continually I watch the media use the entirely weaponised "anti-semitic" but never in mainstream media do we hear the word "Zionist" or "political zionist", these are not fictional beings, and these expressions are not used as insults to describe these people. I also researched a little history on the initial beginnings of the accusations and very quickly found the generally identified starting point of the accusations. In fact, the initial accusations begun under Ed Milliband's leadership, and seemed to result from Milliband's statement that he, if made the next prime-minister believed in a two state solution, this is not something that the political zionists agree with, and through their network of pressure groups and action groups began the momentum of accusations. I also did this with Ken Livingston, and found that his the trigger was a quote in the JC stating that Livingston had said "most jews are tories...", What livingston had actually said was "during the 1980's under Thatcher many Jewish people did very well, and they started to vote Tory". I would really appreciate seeing a question on QT which asks the panel about Zionism and Anti-Semitism, there is a  very important distinction and it needs to be explained and seperated instead of avoided. Anyone who spends any time studying it can see that the political zionist unit has far too much global power and is using language to hide behind\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/411 & \cellcolor{green!5}0.73 \\  \hline
  \cellcolor{green!27}\small If the British Jewish community spoke up against the \textbf{racism} in the right wing government in Israel they could change public opinion and embrace the injustice that most of the uk believe is happening to the Palestinians. It's not anti Semitic to speak the truth of what's happening but that seems the trend now and the BBC is completely wrong and completely one sided on this issue.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small The \textbf{jig} is almost up. There's no way for Zionists to repay all the crimes they've committed against humanity. Time's almost up.\normalsize   & \cellcolor{green!5}Jig & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Nationalism is haraam\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small If I criticise German politics, does that mean I hate Germans? No!! When I attack the \textbf{racist} genocidal policies of the Zionist regime, I know there are millions of Jews who also criticise Israel\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Zionists are a \textbf{terrorist} criminal enterprise.  Anyone who who aligns themselves with this should get their moral compass serviced.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Nationalism isn't the same as wanting an ethno-state\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Says the \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Cole Blackman Jews believe themselves to be the descendants of the assembled multitude, at the foot of Mt Sinai, when Moses came down with the Ten Commandments. What you believe about Jewish descent, \textbf{race} = who cares? Christian/Muslim animus does not spare Ashkenazim, on grounds that Ashkenazim are not " racial Jews." Israel came too late to save European Jews from Christians. The Jews of Arab countries, of Ethiopia, of Russia have been saved . A wonderful achievement.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Who made this dip a lord?  The German queen of Britain?  Jews weren't hated for their \textbf{race}...it was their actions and usury to squeeze all wealth into their own pockets from the nations they were in.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Zionist "Jews" descended by far from the defunct Khazar Empire. Khazars are ruthless psychopaths who were nearly wiped out by the Mongols. They only converted to Judaism to escape persecution. They spoke Yiddish- which is not Hebrew- but is phonetic Khazarian that is made to sound like Hebrew, so they can claim ancient tie to Semite Jew! They started Zionism- a military movement- in the late 19th century. This movement- headed by Rothschild Jews- force England to grant them Palestine officially in 1948 via the Balfour Declaration. Ever since then, these Zionist cunts have embarked on the mission of \textbf{ethnic} cleansing (a crime against humanity) against Palestinians- the true Semites (or should I say, Canaanites) of Palestine- a place where Jesus was born. Jesus was not Caucasian. Being a Palestinian, he would have olive skin, brown eyes and dark \textbf{black} hair. Judaism is a dead religion:Jews lost their kinship. The \textbf{Old} Testament says; king David's line would stop once the Prophet Jesus Christ arrives on earth and he did, but the hatful Jews killed him.Jews lost their priesthood once the second temple was Destroyed in 70 AD and with it the genealogy. Therefore, no Jew can prove he is from the trouble of Levi. And with no Priesthood; there cannot be a temple. Jews have no prophet; there has been no Jewish prophet after Jesus Christ. Therefore, These fake politically driven Jews are mere thieves, \textbf{nothing} more.\normalsize   & \cellcolor{green!5}Black, Ethnic, Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/239 & \cellcolor{green!5}1.674 \\  \hline
  \cellcolor{green!27}\small zionism is a \textbf{racist} ideology\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I've personal never met an anti-zionist who isn't anti-semitic. It's just code for it. Anyone I know who is against israeli policies who isn't an anti-semtie doesn't use or in many cases know the term anti-zionist. They just state they don't agree with this or that. To use the phase anti-zionism u need to be in the know somewhat. Also if u use the phrase anti-zionist on any jew outside of israel that is also anit-semtism. Since a jew in London, or Panama, or anywhere in the world has \textbf{nothing} to do with israel. It's like blaming a catholic on Boston for something the vatican says or does.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small Zionism is an ideology that promotes a globally-spread ethnostate.  It's not about a \textbf{nation}.  It's about the threat Zionism presents to all nations.  Imagine believing this 'Lord.'\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Religion is the cause of all suffering through the \textbf{mental} disorders caused by trying to live up to ideals that take us further and further away from a truly natural state.Freedom of speech is just that. When we lose that we are doomed to be slaves to ideology and the oppression born of it.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Ashkenazi Jews are \textbf{racist} white supremacists and are extremely \textbf{racist} towards non white Britons and even non-white jews....He's wrong as The British isles is not a country but an extremely diverse land with many languages and cultures, the white britshitsh majority tyrannizes non white Britons even the \textbf{black} Britons are older to the isles than the Germanic \textbf{nazi} saxonian tribals\normalsize   & \cellcolor{green!27}Black, Nazi, Racist & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/60 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Antizionism is the last remaining extreme Antijewish \textbf{nationalism}. And just like all the extreme nationalisms of the 20th century, this one is also based on Antijewish racial superisority. All neo-nazis are an Antizionists, Neonazi David Duke is antizionist, KKK are Antizionists, etc... Because antizionism is \textbf{racist} genocide and neo-colonialism\normalsize   & \cellcolor{green!5}Nationalism, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Yes and \textbf{race} is irrelevant.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Yawn, same \textbf{old} same \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Where's the full unedited discussion? I'm disappointed in you BBC. Mr. Sacks example of some criticizing the British government vs. others saying Britain shouldn't exist clearly shows he has a nuanced view of the situation and a good interviewer would have asked questions like "What do you think of those who support the existence of Israel as a Jewish ethnostate but also support the right of Palestinians to have their own ethnostate and not be forced out of Gaza where their ancestors have lived for at least a 1,000 years?"Or another good question: "Do you support the State of Israel's policies to ensure that \textbf{ethnic} Jews are the dominant majority? If so, would you also support the British people (i.e. English, Welsh, Scots, \& Irish) if they were to implement policies that ensure their ethnicities remain the dominant  majority in Britain?"\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/142 & \cellcolor{green!27}0.704 \\  \hline
  \cellcolor{green!5}\small Jews (who love their shared values and Culture, which isn't \textbf{racist}) are the Nazis? ...jews.....are the......Nazis?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small God u people are dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Jonathan Sacks is a vile \textbf{racist} rabbi giving credence and justification to hate jews\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Right, so at least we now know where he stands.  Fucking \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small The Jews are despised not for their \textbf{race}, they are despised for their actions. Lord William Shaw.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small You are obviously an intelligent man who is deliberately trying to muddy the water with your interpretation of anti-Zionism. The State of Israel was built on terrorism and \textbf{ethnic} cleansing and no amount of fine words will change that.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Meanwhile, the Zionist-state is carrying out \textbf{ethnic} cleansing of innocent, Palestinian civilians in Gaza and the West Bank.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small every time someone charges that the state of Israel's treatment of the Palestinians is, say, in violation of international law, the issue of the validity of this charge is replaced by 'straw man,' which in this case is alleged anti-Semitism of the critic. It is to be noted that in most of these confrontations only one side has any real evidence. The critic might point to evidence of \textbf{ethnic} cleansing, property destruction and land theft, and various policies that have, according to David Harel, the vice-president of the Israel Academy of Science and Humanities, turned Israel into an 'apartheid' state. On the other side, however, those using the straw man fallacy often have no objective evidence at all. Their claim of anti-Semitism is based on their own idiosyncratic definition of this prejudice. Making a case in this way also involves 'begging the question' or 'circular reasoning,' which are also erroneous ways of arguing. This occurs when a person 'assumes as evidence for their argument the very conclusion they are attempting to prove.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/172 & \cellcolor{green!27}0.581 \\  \hline
  \cellcolor{green!5}\small Rubbish !  This man doesn't have an idea.  You come on \textbf{common} terms.Zionist B****The land is no more left for Palestinians.Idiot, talks about 2 state solution. Fraudsters \& Tricksters living among us. Zionist just grabbed all the land.Zionist snakes in the midst of our Democracy\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small From the day when the Lord brought our ancestors out of Egypt until today we have been disobedient to the Lord our God, we have been disloyal, refusing to listen to his voice.And we are not free even today of the disasters and the curse which the Lord pronounced through his servant Moses the day he brought our ancestors out of Egypt to give us a land flowing with milk and honey. We have not listened to the voice of the Lord our God in all the words of those prophets he sent us; but, each following the dictates of our evil heart, we have taken to serving \textbf{alien} gods, and doing what is displeasing to the Lord our God.\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small Zionism is a natural duty, it's a moral stand against palestinian terrorism , surviving of the Jewish \textbf{ethnic} minority ..Antizionist is nazism is cancer\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small The \textbf{Old} Testament is the most "anti-semitic" text ever written. In it, God promises to punish the Jews again and again for their transgressions!No wonder Zionists hate the religion and despise ultra orthodox Jews.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small How can criticising the zionists who slaughter palestineans which are also semite can be antisemitism ? arabs are a semitic \textbf{race} too so tecnically the most anti semitic country on the world is israel.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Israel will not survive without diversity we are all equal in g-ds eye israel needs to help the poor \textbf{refugee} no place for Hatred Racism\normalsize   & \cellcolor{green!27}Racism, Refugee & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small What a bunch of crap. Could it be that some Jews don't support Zionism? That it has \textbf{nothing} to do with religion in the first place? \textbf{Nobody} is entitled to anything if you break laws.\normalsize   & \cellcolor{green!5}Nobody, Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small What a  load of Gelfilte fish: figures. To equate anti-Semitism with anti-Zionism is to call many many secular Jews (and Israelis) anti-Semitic - and most of the enlightened world as well. No true humanist or secularist can support the present \textbf{nation} State of Israel because it is not a democracy - Zionism ensures it never will be - and it engages in apartheid. The same holds for most, if not all, of the Arab states - there's no democracy and the entire Middle East is flooded with \textbf{nothing} but warring misogynistic theocracies. And no one with half a brain supports a Christian America or any Christian \textbf{nation} state. Further, no one that accepts the scientific method and natural selection can truly support any state founded on religion/mythology. By "Lord Load of Gefilte Fish's" definition millions, perhaps billions, are anti-Semitic.  Even the most obnoxious zealot anti-Israel loudmouths mean the State of Israel shouldn't exist - in its present form. But no wonder. As long as corporate media continues to give religious leaders a seat at the table - these myopic folk who make stuff up to further their own religious agenda - \textbf{nothing} will ever change. That goes for Christians, Muslims, Buddhists, and Wiccans as well. Lastly, it's too bad to see religious leader's willful but ignorant erudition on display when they cannot distinguish social stereotyping and tribalism and implicit bias - from \textbf{racism} and anti-Semitism. Clearly "Lord Gefilte Fish" never took a psych 101 class. A little less emphasis on being the chosen little Gefilte fish in an anti-Semetic pond - and a little more emphasis on being a primate - then let's here what 'Lord Gefilte Fish' has to say.\normalsize   & \cellcolor{green!27}Nation, Nothing, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Nationality - General & \cellcolor{green!27}5/281 & \cellcolor{green!27}1.779 \\  \hline
  \cellcolor{green!5}\small Shut up you dirty indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small heres to hoping this land thief gets hit by a truck...You cant compare israel to the UK, the UK has been here for thousands of years and still is here, Israel was established out of jewish religious extremism, thousands of people all throughout history have experienced diaspora by \textbf{race} and genetics, Israels claim of diaspora pretty much purely comes out of religious identity, false, evil.Israel should not exist because it was stolen from innocent people, the Jews faced a historical choice, convert from Judaism or be expelled from parts of the middle east, there are arabs Muslims in palestine today who are direct descendants of people who converted from Judaism to Islam, Palestinians have more of a claim to Israel than the "Jews" of Europe.A better example to those school children, and please don't corrupt my childs mind to think Israel deserves to exist based on modern day colonialism and theft, would be somewhere along the lines of, the gypsys,gays and \textbf{disabled} suffered harshly during world war 2, and through their suffering they were given the land of scotland, they took scotland from the scottish and massacred them reducing the scottish population and slowly stealing more and more of the scots land illegally.Do all peoples who experience diaspora have an entitlement to there land of origin dating back hundreds or thousands of years? Do the Navajo get to reclaim the USA from the European Americans who live there, I'm assuming the disgusting \textbf{old} man in the video would think not, even though the Navajo and natives had their land stolen from them more recently than what the Jews claimed happened to them? Israel and its zionist followers are hypocrites and evil, Israel should not exist, it was stolen from innocent people and innocent people have died for the Zionist extremist claims of entitlement to that land.FUCK ISRAEL Fuck zionism, and fuck antisemitism.\normalsize   & \cellcolor{green!27}Disabled, Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/317 & \cellcolor{green!27}0.946 \\  \hline
  \cellcolor{green!5}\small It is so disgustingly disingenuous to claim that anti-zionism is the new anti-semitism. Zionism is by its very nature a \textbf{racist} ideology, which is the basis for the \textbf{ethnic} cleansing and theft of Palestine. Being anti-zionist is \textbf{nothing} to be ashamed of! in fact be proud like those who were anti-apartheid can reflect and be proud of their efforts to end Apartheid in South Africa!\normalsize   & \cellcolor{green!5}Ethnic, Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/65 & \cellcolor{green!5}4.615 \\  \hline
  \cellcolor{green!27}\small 1:19 the belly rumbles.. 😬 Even your body know of your deception. Much like your belly, the tide has turned and they are 💩 themselves. How long can you shout and claim "Anti Semitic!" Before people stop listening? They only gave you that curtesy of listening because they were only hopping you could be reasoned with. But anti Zionism is now anti semetic? Oh dear. This one is wearing \textbf{thin}. So Jews were hated for their religion? And what was practiced in this religion that has had them kicked out of over 100 countries in the past that we know of?Like I said the tide is turning. Is calling you the "Tares" Anti-semitism? Matthew 13:24-30 24 Another parable put he forth unto them, saying, The kingdom of heaven is likened unto a man which sowed good seed in his field: 25 but while men slept, his enemy came and sowed tares among the wheat, and went his way. 26 But when the blade was sprung up, and brought forth \textbf{fruit}, then appeared the tares also. 27 So the servants of the householder came and said unto him, Sir, didst not thou sow good seed in thy field? from whence then hath it tares? 28 He said unto them, An enemy hath done this. The servants said unto him, Wilt thou then that we go and gather them up? 29 But he said, Nay; lest while ye gather up the tares, ye root up also the wheat with them. 30 Let both grow together until the harvest: and in the time of harvest I will say to the reapers, Gather ye together first the tares, and bind them in bundles to burn them: but gather the wheat into my barn.They look physically like us but that "White Devil" the world hates are the very ones who run the media, banks, all corners of entertainment industry and government. Then they claim to be victims?  They hate whites, they masquerade as whites except when they want to claim or get recognition. Then it's "I'm not white. I'm Jewish." And that is what they are brought up to believe and do believe.These Tares (as Jesus told us) are the same ones who are infesting white Europe and only white Europe under the guise of multiculturalism.Jesus was not a Jew. He was an Israelite. Jacobs name was changed to Israel. Israel is not a place, it's a memory, it's who you are. Hence "The lost tribes of Israel" Where is Jacobs pillow? "The Throne of David"?Why is it that their Israel has never matched up to the bible but it matches up to Britain perfectly?How can anyone honestly believe that that middle eastern robbery is the work of God. Why is it these Jews do not have the throne?It was emperor Constantine who established the Jerusalem in the Middle East 200 years after Hadrian had torn down the \textbf{old} and disassociated it with Edinburgh. Constantine established it for political reasons that are still being practiced today. there is a plethora of sites in Edinburgh that still carry its past. There have even been gold and silver coins with King Solomon been found in the city and as far as Cornwall England. Do you know that Edinburgh has a "Jacobs ladder"? Names have a way of sticking even "The Jacobites" were no mere conscience. How can people claim to be of God when most of them know the lies and diciest Israel was established on. This is not the work of God.The bible makes it quite clear that Israel is a covenant, a promise, a memory, it's Jacob. Not a place. And when that memory gets blotted out of the history books (for the most part) they control. People forget who they are and that's why they are called the lost tribes of Israel.Hosea 4:6 6 My people are destroyed for lack of knowledge: because thou hast rejected knowledge, I will also reject thee, that thou shalt be no priest to me: seeing thou hast forgotten the law of thy God, I will also forget thy children.Robert the Bruce of Scotland was the last king to sit on the throne of David. Before it was taken into hiding in Scotland when Edward Longshanks invaded Scotland. It still remains hidden in Scotland today. Edward Longshanks (King Edward I of England) claimed to have stolen it when he invaded scotland, he did not. All Edward Longshanks did was create a counterfeit throne (much like the Jews counterfeit "Israel") and paid a few traitor lords of Scotland in land and gold if they would pay homage to him as King. And acknowledge his counterfeit throne as the real throne of David. That \textbf{hag} that claims to be sitting on the throne knows it's counterfeit. She and all her kin are illegitimate. Understanding the oath that is given to God by those who can sit on the throne of Israel. Is to understand that the monarchy now ruling the uk are illegitimate and not gods chosen to rule Gods people. Brits were all celts so to speak before Rome invaded. Jacobs pillow (the Thorne of David) was carried for hundreds of years by the  people's of ancient Britain after the fall of Judea. The throne of David was transplanted in Ireland. Then it was taken to Scotland where the Kings of Scotland were crowned. The reason for the term "God save the King!" Is because only a king who is of the blood line of David and of God can sit on that throne and rightfully rule over gods people (The tribes of Israel the Israelites).  Ezekiel 21:27I will overturn, (Judea)overturn, (Ireland) overturn, it: (Scotland) and it shall be no more, until he come whose right it is; and I will give it him. ("Him" being the King of kings, Jesus Christ)Where is the these Jews answer to Ezekiel?Genesis 12:2And I will make of thee a great \textbf{nation}, and I will bless thee, and make thy name great; and thou shalt be a blessing: (Great Britain) !These are both from the \textbf{Old} Testament. They may be oldies but they are goodies, and these Tares fufill none of them.Here is a new one. Revelation 2:9 I know thy works, and tribulation, and poverty, (but thou art rich) and I know the blasphemy of them which say they are Jews, and are not, but are the synagogue of Satan.The BBC are the PR firm of these Tares and all other MSM outlets.Beannachd Dia Dhuit.\normalsize   & \cellcolor{green!27}Fruit, Hag, Nation, Old, Thin & \cellcolor{green!27}Age - Over 65s, Gender - Female age and physical appearance, Nationality - General, Physical Identity - Physical Features, Sexual Identity - Male homosexuality & \cellcolor{green!27}6/1101 & \cellcolor{green!27}0.545 \\  \hline
  \cellcolor{green!5}\small Amazing how this video got 156 dislikes? JEW HATE is sadly strong in Britain, reaping the "fruits" of "multiculturalism" after having imported millions of JEW HATERS from countries where this sentiment is cultivated since young \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Over 300 dislikes now. Many people are uncomfortable with extreme \textbf{racism}. Jonathan Sacks incites racial hatred. people can see that. It is not him being Jewish or a rabbi, it is his extreme \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small The Rabbi's description of anti-Zionism is a straw-man... many anti-Zionists have no objection to the existence of Israel, nor do they question Israel's right to exist.'Eretz Yishrael' on the other hand, - ie. Zionist expansionism/imperialism - is another matter entirely... and the Rabbi, in failing even to admit there is such a thing as a 'Greater Israel Project', is using a typically Jewish kind of verbal 'sleight of hand' with this straw-man and hoping no-one will notice.If Israel were to cease her continual genocidal behavior against her neighbors, stop her \textbf{ethnic} cleansing of Arab countries, and and pull back out of all occupied territory, to the borders established for her by the international community in 1967, perhaps the anti-Zionist movement would dwindle considerably... (and if she were to hand over her Zionist banksters to international legal authorities for their international monetary scams, the 'Federal Reserve' banks, it could possibly disappear altogether!)Instead, however, all we see is Israel (and her Zionist banksters) behaving abominably, and in true Jewish style, scapegoating her victims/neighbors. If Jews do not like 'anti-Semitism', perhaps they might ask themselves, where does it come from? How could anyone possibly NOT love 'God's Chosen People'? Or what said 'Chosen Ones' have planned for the 'Goyim'...? What's not to love, already...?\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/214 & \cellcolor{green!5}0.467 \\  \hline
  \cellcolor{green!27}\small Theseustoo AstyagesWow what one man says you believe all Jews or Zionist believe. Amazing. The wako from wako (David Koresh) was a devote Christian speaks for all of Christianity. Maybe Jim Jones speaks for Christianity. Why don't you read more sites on Zionism and Judaism. True and real Zionist is just the believe that Jews deserve there own homeland.  \textbf{Nothing} else. Jews don't own all the  money and banks. Just use \textbf{common} sense. Do you think any of the 600 billion promised to Iran would of gone to them if so. Just think so much goes to enemies of Israel. Just think. You can go to any Jewish bookstore and buy a Talmud. Non Jews are not forbidden to go. You can find translations on line. Go and try. As for your quotes this is what your sources do. Lets say that the Talmud says in Tractate X page y.   "Rabbi X says that the world thinks it's permissible to lie, cheat, steal and even kill non Jews with no punishment. I'm here to tell you it's wrong and here is the proof. "Your sources will do this. Here is a quote from Rabbi X in Tractate X page y it's permissible to lie, cheat, steal and even kill non Jews with no punishment. See how evil the Talmud is.  If you bother to read before and after the quote you'll see how they lie and manipulate the verses to produce anti Semitism. Challenge me on anyone of your quotes and I'll show you. Would you like the religious reason or the non religious reason why Jews were kicked out of all countries? Or both?My Site is the actual Arab leaders telling you this. It's not lie. It gives you all sources what TV shows, what papers so you can yourself go to the archives of those stations or papers and see for yourself. Just like me this site doesn't ask you to take my (or its) word for it. Check it out yourselfI am more than willing to get into a Gaza discussion with you but let us try to separate. I don't want post to get to long. But believe me I have what to say and prove to you who the real \textbf{terrorist} are. Who is the liars are. Look at there media and ours. That alone should tell you something. Israel is not perfect but it's much more human than they are. They lie to you much more.  You are justifying the wrong way. Israel defends itself from suicide bombers. They don't force them. As for the chosen ones. You misunderstand that too. It doesn't me G-d love big over small, white over \textbf{black} and so on. What it means is simple. G-d was first looking for someone to choose him. No one did.  \textbf{Nothing} but idolatry.That was until Abraham came along. He past on his teaching to Issac and Jacob. It was then that G-d made a covenant. Since you chose me (to the fathers) i will choose you and your descendants as my people. Our post are getting long. Please keep them short. One subject at a time. But do me a favor. Please read the Israel side of things. Have a good day\normalsize   & \cellcolor{green!27}Black, Common, Nothing, Terrorist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Religious Identity - Muslim, Social Class - Working class & \cellcolor{green!27}5/544 & \cellcolor{green!27}0.919 \\  \hline
  \cellcolor{green!5}\small As I've said, it's not so much what Israel 'says' that makes me believe that Zionism is a \textbf{racist}, \textbf{imperialist} doctrine, but what Israel actually DOES in Gaza and the WB... I watched her actions for a long time before I became an anti-Zionist and it is her actions that I judged her on, not just her ideology... and it seems like ISrael is quite full of 'wakos'... (Btw, it's spelled 'Waco'...)And believe it or not, I was brought up as a Christian, and was taught that Israel was the 'Holy Land' and that the Jews were 'God's Chosen People' as per the bible (Torah), along with Christians, of course, as believers in the same sky-fairy. I did not become an atheist, nor an anti-Zionist until much later in life... (only during the last few years) until after I'd learned that 'God's Chosen People' were not all 'nice guys', or 'the good guys' as per the myth.What you call 'True Zionism' is really the complete inversion of Judaism... and it belies current and on-going Israeli expansionism. And here's a curious question for you: How is it that prior to WWII the Ashkenazim were in a minority of 'World Jewry', but today they comprise 90 of it... How did this come about?Listen up: The ownership of the banks by ISrael's banksters does mean that they quite literally own virtually all the money in the world, which is only LOANED to the rest of us; no money at all comes into existence without being BORROWED into existence... and who owns it? Those who print it, who create it (out of \textbf{thin} air!) and loan it out to we 'Goyim' at interest. This is 'usury'... surely you've heard that word before? And it is the source of all inflation, which exists as a secret form of taxation imposed, willy-nilly, upon the rest of the world.And I've NEVER judged ALL Jews, nor even all Israelis, as if they were ALL Zionists; I'm aware that many of them aren't... but you are using the 'No True Scotsman' myth for Israel and saying 'No True Zionist' would do anything devious or underhanded... Do I really need to explain why this is a fallacy? In any case it is usually a mistake to believe one's own propaganda... (as you are doing, I might add).If what you say about 'True Zionists' 'just wanting a homeland' were true, then how do you account for Israeli expansionism/imperialism? Why is ISrael not content to stay behind the more than generous allocation of borders which was given to it by the international community in '67? And why does Israel continue to attack her neighbors (when she's not getting them to attack each other using false flag operations... The Gulf of Tonkin, the Lavon Affair, the attack on the USS Liberty and 9/11 were all Israeli false flags used to drag her golem, the USA, into wars from which ONLY ISrael and her banksters benefit). Of course, you will deny the veracity of these facts too... but they ARE true.I don't know which '600 billion' you're talking about but if Israel is 'giving' this money to anyone, it is a LOAN which will be repaid with interest, like all loans from the banksters. Debt is their weapon... so any 'loan' is no act of friendship or kindness; quite the contrary.And yes, I'm aware that there ARE actual 'rabbis' who, like your 'rabbi X' in your example, contradict other rabbis who say it is permissible to rob, rape and murder non-Jews... but this does not change the facts that, a) such rabbis DO exist and DO believe those things in the first place, and b) that such rabbis are actually in the majority now, and your 'kind' rabbi, who objects to such an evil double standard is very much in the minority... Like Norman Finkelstein, perhaps... Now there is a believable Jew... an admirable fellow.I've already given you quotes, and challenged you to give me a context which could make any of them sound less evil, but you just say are not in the Talmud and so do not even attempt to place them 'in context'. I don't know any Jewish bookshops but I'd be happy to read a Talmud if I can get hold of one... Is there no online version I could read? Rumor online has it non-Jews are forbidden, on pain of death, from reading it. And what about the Zohar? From what I've heard it's even worse than I've said the Talmud is supposed to be... (and then, of course, there's the Kabbalah, but that's quite another story, isn't it? But much used by your banksters, for a start... you DO know that 'Freemasonry' is a Jewish invention? This is a fine example of the use of mystery cults as tools of imperialism, about which I've already spoken briefly).I'd actually like to know the REAL reason they were kicked out of so many countries... truly, 'anti-Semitism' really just doesn't explain this at all... but some of those cabbalistic and imperialistic practices I've mentioned just might.Now you personally may not think Zionism is about imperialism or expansionism, but this doesn't make it so, does it? Did you google the 'Oded Yinon Plan' for 'Eretz Yishrael' yet? You see, in spite of your denial, such imperialism not only exists, it is central to Israeli policy, so your denial comes across as just another lie... You already have a 'homeland'... why bother that the borders are not quite what your fairy-tale character says they 'should' be? Why the expansionism? "Today Eretz Yishrael... tomorrow the WORLD!" perhaps? (Sound familiar?).Tell me also, why is it that Jews have a 'right' to a homeland (which was someone else's before they took it!) but Palestinians don't? The same reason, no doubt, that Jews have the 'right' to 'self-defense' but Palestinians don't...You still don't get it, do you? Israel's treatment of Palestine and Palestinians is what creates suicide bombers... or do you think you can treat people worse than you'd treat any animal and it would have no effect on them? That you can steal people's land and homes and NOT have them fight to get it back? This does not make sense. Or do you think that, as "God's Chosen People" you Jews can do no wrong? That any evil you do is 'God's evil' and thus 'good'? (as per the Talmud's 'Law of Inversion'? Or do you deny that this law even exists?)I suppose you don't remember how the Zionists thanked the British for their help in obtaining Palestine for the Jews' 'homeland'... by bombing the then British headquarters in the King David Hotel in Jerusalem... After such treachery, who can fail to believe in Jewish duplicity?I really don't care how you attempt to justify the 'Chosen Ones' phenomenon... I really don't care how they say they were 'chosen'... (So a Jewish fairy-tale says Jews are their own god's 'Chosen Ones'... Big deal! Why should ANY non-Jew even take such a notion seriously?) As I've said before, there are NO 'Chosen Ones'... only self-chosen R-souls.And how come the majority of Ashkenazim are actually atheists, but this still doesn't stop them from using these fairy-tales as the basis of their claim to the land that Israel currently occupies, as well as the rest of 'Eretz Yishrael' as it is described in Jewish fairy-tales? Seems a little 'odd' don't you think? Not to mention 'hypocritical'...I'm sorry our posts are getting long... but it is necessary for me to address each point you make and I like to do so as completely as I can.Oh, one point I've missed... you say there are Arab 'leaders' who now 'toe the Jewish line' and say that Arabs are the 'real terrorists'. So what? What about all those Jewish soldiers, ex-members of the (ironically-named) IDF, who have told the truth about what they were expected to do in Gaza and the West Bank? I think you know as well as I do that it is not so difficult to brainwash people into saying just what you want them to say, so such examples (of 'Arab leaders') are questionable at best... Though in the case of the IDF soldiers, who gave their testimony willingly and without any form of brainwashing,  prompted by their consciences alone, these ARE believable.Have a nice day.\normalsize   & \cellcolor{green!5}Imperialist, Racist, Thin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!5}3/1406 & \cellcolor{green!5}0.213 \\  \hline
  \cellcolor{green!27}\small You have no idea what is truly going on in Gaza that is my point.  All you believe is from the supposed Jewish own media that you learn.  You are \textbf{blind} as a bat to the truth. Jews do not own the banks period. Jews own some but plenty are owned and operated by non Jews or a board of directors that aren't Jewish. Zionism and Judaism aren't the same but a vast majority of Jews support  Zionism. Zionism is \textbf{nothing} like you think it is. Anti Zionist are that for one of two reasons. They had bad experiences with some so they take it out on all. That or you were befriended by an anti semit and or  Zionist who talked to you and conceived you of the lie you believe. Which one for you?Tell me if Zionism is so much about expansion then why has Israel  been willing and actually gave away so much land for peach? Amazing all they want to do is expand expand but all they seem to do is give ups land. Remember the Gaza, Golan Heights. They offered 5 times to give up almost all that the Palestinians want but  were rejected each time. And each time we give up land it's used against Israel. The Gaza is used to launch rockets and for tunnels. One gives up for peace one rejects peace and users there new land for war. Look at the history the actions alone should tell you Israel is not about expansion. You seem to want to mention the supposed bombing of Israel but forgot the non stop bombings of the Arabs in Israel and all over the world. Why concentrate on Israel and ignore the rest of the bombings. Anyway we can go one by one with your anti Israel bombings if you wat. The majority of the world is not Ashkenazim. The're plenty of sfardim. In my area t he majority of Jews are not Ashkenazim.  Most Jews aren't atheist they believe in G-d but just don't feel they have to be religious. oThe Chosen people idea is in the bible read it. The IDF is not perfect but believe me they are a zillion times better and more moral than the Arabs. What other country would throw it's own out of a land to give it to there enemies who swear to kill them. What other army warns there  enemies to move because an area will be bombed.?   What other country stops planned bombings to save lives. You say all they want to do is kill look into the news the go out of there way to protect there enemies civilians.  Read what is really going on. I live in Israel I talk to many people in the Army or who was in the Army all you believe is  BS. Have a good day.\normalsize   & \cellcolor{green!27}Blind, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/479 & \cellcolor{green!27}0.418 \\  \hline
  \cellcolor{green!5}\small All you seem to be able to do is to keep repeating your denial... this proves \textbf{nothing} and I simply don't believe you. I do not believe the Israeli narrative with regard to Gaza and the West Bank either.I never said "Jews" own ALL the banks... but Zionists most certainly DO. You DO realize that the majority of Zionists are actually Christians? (And some Muslims, too... believe it or not!) And, as the current saying has it, "all wars are bankers' wars!"Funny how the 'vast majority' of Jews are now Ashkenazi, too, isn't it? You never did answer my question about how this came about since they were in a minority before WWII...What land has Israel given away? That it was not FORCED to by the International Community...? Do you deny that the settlements and the encroachment of the 'security' wall (Ie. the 'land grab' wall...) continue to go on, in direct contravention of International Law? And in total provocation of the Palestinians... who you claim have no right to defend themselves from this on-going real-estate theft, even if they had the means to do so, which they DON'T.Do you deny that ISIS were supported by Israeli air-strikes during ISIS' invasion of Syria? Or the desire of Israel to get its golems, the USA and NATO to go to war YET AGAIN on ISISrael's behalf against both Syria and then Iran so ISISrael can install a pro-Zionist puppet government? Sorry mate, but your denials are fooling no-one.If someone invaded your property, and killed off many of your family members, then after a lengthy battle a stalemate was reached, in which you were given permission to live in the attic and basement, while the invaders occupied the rest of the property, how long would it take you before you would stop fighting to get back ALL your property? Or would you be content to live in the attic and basement, like a rat?You seem to think I don't criticize Islamic terrorism but I do... on sites where it is relevant; this site it is Israeli terrorism which is relevant. And even if it was relevant here, Islamic terrorism does NOT excuse Israeli terrorism (or Israeli 'false flags' or 'perpetual war for perpetual profit'; the motto of the Zionist banksters!), though I realize you apparently think otherwise.So... now you are equivocating about most Ashkenazis being atheists... I suppose you really have to do this, don't you, so you can go on maintaining the claim that your sky-fairy 'gave' you that land... "A land without people for a people without land" was how it was originally sold to the rest of the world (and, I'm quite sure, still how it is taught in Israeli schools), rather than the truth that 800,000 people were either slaughtered or evicted from their homes in order to make way for your 'Jewish homeland'...So... you DO believe in the 'Chosen Ones' concept, then? I don't... I'm an adult and far too \textbf{old} to believe in fairy-tales! There are NO 'Chosen Ones'; ONLY self-chosen R-souls who think they're above everyone else. Such arrogance usually comes a cropper in the end."What other country would throw it's own out of a land to give it to there enemies who swear to kill them." Well now... it's funny you should mention this; now I have a chance to tell you how the Ashkenazim got to be such a vast majority of world Jewry... but I won't go into great detail here; suffice it to say that in the diary of Theodore Hertzl, prior to the start of WWII, it says, "The suffering of the Jews must be made to increase"... and "The anti-Semites will be our best friends; the anti-Semitic countries, our allies..." You see, they had a problem: How did the Zionists get Jews who had been living in Europe quite comfortably for centuries, to 'up stakes' and start all over again in the middle of a middle-eastern desert? Not only was WWII the Jews' idea... so was the Holocaust; what better way to get them to move?Isn't it true that it was mostly the Sephardim who were 'exterminated' in the concentration camps? And now the Ashkenazim are the 'majority'? You deny this, but I've seen statistics which said that the Ashkenazim represented 90 of the Jews in New York, and more like 95 of the Jews in Israel, which are the two largest Jewish communities in the world.I understand too, that Germany was one of few countries that would accept Jews after they were kicked out of Russia... but this didn't stop 'Judea' (ie. the Jews in diaspora) from declaring war on Germany in 1936, did it? They introduced sanctions which led to the deaths of millions of Germans... and this was also the REAL beginning of WWII.And don't forget Israel's 'Thank You' to the British for all their help in getting a homeland for the 'Jews' only three years after the war ended... Not real strong on 'gratitude' the 'Jews', eh?But you think you're a 'Chosen One' and as such, you can do no wrong, so I realize there's little point arguing with you any further. Your position is more religious (and propagandist) than rational, therefore you prefer mythology to history and doing whatever you like to anyone you like, to having to behave like a civilized human being towards everyone, even those you dislike, and negotiate with them in good faith, as equals.I'm not surprised. But I thought you 'Jews' were supposed to be smarter than that.Have a nice day...\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/937 & \cellcolor{green!5}0.213 \\  \hline
  \cellcolor{green!27}\small You don't believe me and I don't believe you so I guess we are even. I live in Israel so I know your beliefs are BS. Israel doesn't encourage there citizens to blow themselves up.  Israel readily agrees to peace talks and offered so much so many times for peace. It's the Arabs that rejected every offer of Israel. It's Israel that does  what it can to protect enemy civilians not the Arabs.  Arab media says over and over kill kill kill. You'll never find this on Israel media. Far more Arabs are killed by Arabs in far more cruel ways then Israel ever killed but somehow you think Israel is the bad ones.  ARabs live far better with far ore rights in Israel than they do in Arab lands.  You believe lies. So with this let us just call it even. You won't change my mind and I won't change yours. Let the readers decide for themselves. Zionist don't own banks. So much money goes to so many things against Zionist interest. Why are you so \textbf{blind} not to see this?I answered you.  A vast majority of Jews today are not Ashkenazim. There are many Sfard and Sfardi ones. The  Bible is clear this land is the Jews read it.  You say that Palestinians were evicted from there homes. Yet you forget that in Gaza Jews were evicted. Palestinians have plenty of places to go. Many live in Israel. All Arabs can live in Israel. You also forget that there was a Jewish presence here long before there was a Palestinian one. I see you ignored my 12 questions to you. There never was a Palestine before Israel came along. That was invented after Israel became a state.Israel had to give up the land BS. Israel freely offered the land. More than 5 times. When Ehud Barak was prime minister he freely offered 95 of what they wanted and each time every offer it's the Arabs that rejected the offer. Not  Israel. This people that want to expand offer to give up there land over and over. Offer not forced offer. No country for any reason does what it can to protect it's enemies citizens the reasons you gave are made up.  Amazing anything pro Israel you have a logical reason why it's BS but with anything anti Israel so true. The Jews are the chosen ones. Read the bible. Just read it. It's clear the land was given to us. It's clear that G-d chose us. If you don't believe in the bible how can I argue with you on this. Jews started WW2 that is funny. I see you clearly read anti Zionist sites and believe any BS they give you. Germany tried to kill all Jews. Yet Jews started this. I suppose you believe crap like Jews did 911, there was no holocaust and that the Arabs are really peace loving people.   I agree there is no point in arguing with you. Your a \textbf{blind} fool. I suggest to all readers look up Prague University. They support all I say with facts. How Israel is the most moral army.  How Israel always offers land for peace and so on. We are done here. I can't deal with someone so \textbf{blind} to the real truth. That hates Israel for no reason and refuses to see both sides. Anything pro Israel is jus propaganda BS but anti Israel is absolute truth. You'll say this even if the sources where from the same paper and source. If you dare read and see the Zionist sites what they have to say. You clearly only read one side. Good bye. You go on being right. Till then we are done. Any reader can contact me separately to ask any questions.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/631 & \cellcolor{green!27}0.475 \\  \hline
  \cellcolor{green!5}\small Of course Israel 'regularly agrees to peace talks'... this is how they keep the International community off their backs while they continue the settlement program which steals more and more Palestinian land. But there will never be peace until ISISrael has ALL the land between the Nile and the Euphrates... and probably not even then. Any 'peace offerings' by Israel have been disingenuous... they offer only what they know damn well will be refused... Would you agree to live in your attic while those who raped and killed your family and stole your property live in the rest of your house?Whether or not there was actually a \textbf{nation} called 'Palestine' is irrelevant; the land belonged to them and the Zionist STOLE IT, UNDER FORCE OF ARMS.Zionists DO own banks! And I don't understand why you refuse to admit this... except, of course, that it suits your narrative; the Zionist propaganda narrative you prefer to believe. I've read the bible and I really don't care what your sky-fairy says; I'm far too \textbf{old} to believe in fairy-tales. And even if I did, you are NOT the same people whom the fairy-tale says your sky-fairy gave the land to, anyway, as I've already explained.There are NO 'Chosen Ones'; only self-chosen R-souls...'Facts'??? LOL! That's a good one! You wouldn't recognize a 'fact' if it jumped up and bit you on the nose!And I don't hate Israel... only her imperialistic ideology and much of what this means for the rest of the world. But I've read many Zionist sites and do not find them the least bit credible. The TRUTH is that the anti-Zionist sites really ARE far more credible; that's why I believe them.Have a nice life; try not to kill too many innocent Palestinian women and children, eh? 'Bye now...\normalsize   & \cellcolor{green!5}Nation, Old & \cellcolor{green!5}Age - Over 65s, Nationality - General & \cellcolor{green!5}2/304 & \cellcolor{green!5}0.658 \\  \hline
  \cellcolor{green!27}\small You are clearly the \textbf{blind} one. All over Arab media it says kill kill kill. You're promised 72 virgins in heaven if you kill Israelis and Jews. Kindergarten graduations always have plays of them killing Israelis and taken over the land. The media has kids programs about killing Israelis and Jews. Arabs brutally kill each other. There are beheading in public. There are public executions on a regular basis all over the Arab world.  None of this you find in Israel. None. Yet somehow you insists it's the Israelis that are the cruel brutal killers and don't want peace.  Tell me again if you are so sure that Zionist or Israelis are so cruel then please go in the middle of the Palestinian control areas.  Yell I love Israel. say anything against the goverment there. Dress like a religious Jew and see it will take around 10 seconds for you to be tortured and kill. This is no joke.  You can dress and live like a religious Arab in Israel. You can vote and receive all the rights in Israel as an Arab that any Jew can.  But again somehow it's Israel that is the brutal people. Just don't get you. With your peace talks. Israel not only agrees they make real offers. They gave away land. Each and every time this peace offer of Israel was meet with war from the Arabs.  Each and every time it was Israel that makes the offer and the Arabs that refuse. But again somehow Israel is the one that doesn't want peace. Jews were in this land long before Arabs. We were kicked out first but again somehow  Israel is the cruel one. Arabs have plenty of places to go. Where do the Jews have to go in the middle east?  Israel is a tiny ant like country surrounded by enormously huge Arab countries but it's Israel that has to give up it's land.  The Palestinian land never existed before Israel was born. But you act like it did forever. You are \textbf{blind} as a bat.  Zionist sites are far more credible for they tell you the truth and have real facts from real neutral experts. Zionist do not own the banks.  [LINK] Sorry you are \textbf{blind}. You hate Israel so much you just look at it with Tunnel vision. All you can see is anti Israel stuff. Why don't you try to live here and see how Arabs are treated. I do. They are treated the same as Israelis. You don't believe in the bible so there is no point in discussion the chosen people ideology. We are finished please say goodbye and end it here. I don't want to waste so much time with you.  Go on hating Israel and being right. When the Messiah finally comes you'll know the truth. Till then let us go on believing as we do.  You'll never change my mind. I live in Israel and I see the truth. Have fun.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/497 & \cellcolor{green!27}0.604 \\  \hline
  \cellcolor{green!5}\small I don't know... you slaughter and evict 800,000 people, steal their land and deny them any 'right of return' and you wonder why they hate you? It doesn't surprise me in the least the extent they will go to, but it seems to surprise you; why? I'd probably do the same in their shoes... and so would you too, probably. You will probably say "I would never do such things..." but you really don't know what evil you're capable of until you're pushed to extremes... the way the Palestinians have been.You FORCE them to live in conditions which make civilization impossible, and then wonder why they become barbaric? This makes their barbarism, however bad it gets, less than yours, because you Israelis are responsible for it... you drive them to it. So many straw-men... and so many lies... so little time...It's not the Arabs in Israel itself who I'm worried about: Because Israel at least likes to call itself a democracy, it is obliged to at least put up some kind of show to that effect... even if it means granting a small minority of people the right to vote and a few members of parliament.Tell me just one thing before I go, however: What difference, in terms of their practical application, is there between the Zionist ideology of the 'Chosen Ones' and the 'Ubermenschen' ideology of the Nazis? So far as I can see, absolutely none whatsoever... You see, I really don't hate Israel... what I hate are 'Chosen Ones' in any form... whether \textbf{Nazi} 'ubermenschen' (whom both of my grandfathers fought against, btw) or Zionist 'Chosen Ones'... SO a fairy-tale written by Jews says that Jews are the 'Chosen Ones'? Do you REALLY expect anyone, other than a Jew, perhaps, to take such nonsense seriously?You may live in Israel, but you see anything BUT the truth!Messiah? Lol... I hope you don't expect me to hold my breath while I wait... but I'm glad that at least you don't claim Sabbattai Tsvi as your 'messiah'.I said goodbye already... but you came back... and I had to answer you... 'Bye now...\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/357 & \cellcolor{green!5}0.28 \\  \hline
  \cellcolor{green!27}\small Theseustoo AstyagesYou have to be the blindest man I ever met. First chosen one idea and Messiah is not up for discussion. You dont' believe in the bible so it's useless to mention it. You claim that Israel makes the Palestinians live in barbaric conditions. Why don't you bother to find out what is going on. Israel allows tons and tons of aid into the area. They allow so much food and cement to rebuild houses. What did the Hamas authority do? They kept the food for themselves and took the cement to build tunnels to get into Israel and do \textbf{terrorist} attacks. All the medical supplies, and medicines and ambulances in the territories are from Israel. So many Palestians go to Israeli hospitals to be treated. I believe it was the Hamas leader (or one leader) that requested he be treated in America or Israel. Don't give me this BS that Israel makes things unlivable for the Palestians. It's there own that does. They deny there own the very basics.  You should see areas in the territories. They certainly aren't lacking. This is what you are saying Israel wants to expand expand. Reality. Israel has to give up give up (and does) and the Palestinians want want want and get. Israel are the evil \textbf{terrorist}. Reality They send there own to kill themselves by killing Israelis. Arab are responsible for almost every \textbf{terrorist} attacks in the world. Yet Israel are the ones that are the \textbf{terrorist}. Israel is evil and teaches there own to be evil.  Reality. there media is full of kill kill kill. You're a maryter who gets 72 virgins if you kill Israelis and Jews. You get streets named after you if you kill. You never find this on Israel media. This is never taught to Israel. Yet again Israel is the \textbf{terrorist}. You say the PLO are forced to act so barbaric since Israel treats them so bad. Reality is the opposite. Israel was forced to build the wall because of the \textbf{terrorist} attacks. Those attacks dropped dramatically since that wall was build. But it's wrong for Israel to build there own. All the security measures are wrong even though they protect Israelis. One of my favorite that I only noticed on Shabbat. Israel only gives land because the UN says so. Or the world must listen to the UN. Yet it was the UN that gave Israel to the Jews. Not all of it. The Palestinians got more land than Israel. Israel was willing to live in  peace. The Arabs attacked  So in short. If the UN does something that makes Israel looks good well Israel does it because they have to. Opposite if it makes the Arab look bad O ignore the stupid UN. You Israel is so bad that they don't care about there enemies citizens. Reality Israel does everything to make sure they have a chance to leave before an attack. The response of Hamas is to force there own to stay in the line of fire. They take there own into the battle fiels. There wives children and babies. They put there weapons in hospitals, schools and residential areas. But somehow  Israel is the evil ones. My above should answer your questions.  Israel in reality treats the Palestinians good. makes sure they are taken care of Nazis did the opposite to Jews. It's there leaders that make life miserably for the Palestinian. Now you come back and back and I have to answer you. If  you want to stop then stop but do me a favor. Research the Zionist side. If you want to stop stop. If you answer just like you I feel I have to answer. So it's your choice stop or continue. I prefer you stop. Your just to \textbf{blind} to see what is really going on. I hope you wake up one day.\normalsize   & \cellcolor{green!27}Blind, Terrorist & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!27}7/648 & \cellcolor{green!27}1.08 \\  \hline
  \cellcolor{green!5}\small You are the one full of BSIsrael always allows aid into the territories. Israel always gives there enemies medical supplies. Israel went to many countries Arab and non Arab and helped them in need. Israel is almost always one of the first countries to  respond when disaster strikes any country.  They would do it with or without any UN or any international pressure.  So many Arabs even \textbf{terrorist} are treated for injuries in Israel. And again we give them no matter what the reason and instead of using it what is was given for the authorities steal it and use it to attack Israel and deny there own. As for your settlement issue that we have no right or it's a barrier to peach here is a good answer [LINK] Israel doesn't steal any land. Israel is the Jewish land. It was long before any Arab got there. It's the Jewish homeland. Here you claim that Israel only does what the international community says is right. They only follow orders of the UN and you forget it was the UN and international communities that gave the Jews to Israel. Funny how when it's for Israel they only do what they have to. But the same facts against Israel it's because they are so barbaric. You forget that the Jews would of stopped in 1948 but the Arabs attacked us.  There never was a Palestinian land. I proved this to you. More than 77 of what you say was Palestinian then is still under Palestinian control (Jordan). THey have plenty of places to go. Jews don't THIS ADDRESSES YOUR QUESTIONYou say I'm lying I say your just an ignorant fool so again lets see what is really happening. Is it the Palestinians or Israel that has it plastered all over there media kill kill kill. Even on programs targeting 3 year olds? Is it the Palestinians or Israel that clearly uses there own citizens to protect there weapons? Putting everyone in direct danger. Is it  the Palestinians or Israel that is willing to give up thousands of prisoners for one of there own?Is it the Palestinians or Israel that offered and even gave up land for peace? Which always only demands more more more. Is it the Palestinians or Israel that refused every single peace offer made?Who does everything to protect there enemies civilians during war with SMS, Pamphlets and phone calls warning to leave? Palestinians or Israel? Then who goes out of there way to attack there enemy civilians?Is it in Arab countries or Israel you see regular beheading, killings of there own.  Is it in Arab countries or Israel that a \textbf{woman} can be arrested for not covering her hair? Were do you find religious police? Arab countries or Israel?Is it Judaism or Islam that the ultimate goal is death? Don't even think of saying Judaism. You say that that the Palestinians are forced to use such \textbf{terrorist} acts which means it's not in there nature to do so.  Tell me who is responsible for a vast majority of \textbf{terrorist} acts in the world? Against the USA, France Belgium and the like? Israel or the Arabs? Why were they forced to do 9/11, bombings of all US embassies and all \textbf{terrorist} acts in countries other than Israel?. O let me guess all those \textbf{terrorist} acts are really Zionist plots. I bet you believe that BS.Tell me who outright celebrates the attacks outside of Israel (even all in the USA) by cheering and passing out candies? Palestinians or Israel?All the above should make it clear that it's the Palestinians that keep the violence going not Israel. It should be clear that human life means \textbf{nothing} to them but means a lot to Israel. If you are so sure that Israel is the monster here then take me up on my challenge.  You conveniently never mention that. Will you go deep in there territory dressed as a Jew? I'm more than willing to do the opposite in Israel.As for your claim Jews kill so many Palestinians. Again if there authority would just let there citizens listen to the warnings.  Leave dangerous areas. If there authority would not use there own citizens as shields then around 90-95 of the Palestinian deaths would not occur. Jews do not think non Jews are subhuman., I proved it to you and you just ignore that.  You have no clue of the idea of chosen ones. It's not that we think we are so much greater so we can mistreat others. I explained it to you but in one ear and out the other. I"m no liar and I am not paid to do this. Israel doesn't need to pay anyone. There are plenty of Israel supporters that freely and willing post pro Israel stuff like me. Now I will say goodbye. Just like you if you bash Israel I feel I have to respond. If you think you can be the better man then don't reply.  Don't  tell me I"m wrong for replying and should say good bye when you reply and do the same.  Just like so many anti Israel people. Israel is wrong for doing x but when non Jews or non Israelis do the same it's ok they are forced to.Can we agree to disagree? Just say yes. Your pro Israel and always will be and I'm anti Israel and always will be. I'll say good bye and that will be that.  Can you be a big man? Can you do this?Have a good day.\normalsize   & \cellcolor{green!5}Nothing, Terrorist, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General, Religious Identity - Muslim & \cellcolor{green!5}7/934 & \cellcolor{green!5}0.749 \\  \hline
  \cellcolor{green!27}\small I see you can't be the bigger man and I'm just tired of your \textbf{blind} foolish ignorance and taking all I say out of context and not even understanding what I say so I'll say good bye. Please say good bye. If you say BS like I"m afraid of your proof then I'll be force to continue and I don't want to continue. My challenge was for you to go to Palestinian or ISIS areas dressed like a Jew or just wearing an I love Israel T-shirt. And for both of us to do the opposite in Israel just to see who really is the more peaceful people. One thing you say there is no Talmud online first go to any Jewish bookstore and you can by one. Artscroll one is one of the best. You can get any Hebrew speaking expert to see if what the site I gave you is true or if the translation is accurate.  Dress up as a Jew and go to any Yeshiva and see the ones they got there. But here are a few on line Talmuds that you say don't exist.  [LINK]  [LINK]  [LINK]  (Hebrew) [LINK]    This is a very good one. Goodbye now if you can't be a man be nice at least and stop. No more back and forth such a waste of time for both of us. Readers read and they can make up there own mind.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/238 & \cellcolor{green!27}0.42 \\  \hline
  \cellcolor{green!5}\small And I'm tired of your bloody-minded constant propagandist's repetition of Zionist bullshit, but you won't stop, will you?I understand what you say... I just don't believe it. Its self-serving Zionist propaganda which does \textbf{nothing} but demonize Arabs whilst lionizing Jews... and about as far from 'truth' as such ideologically-originated positions usually are.I never once denied that the Palestinians hate the Jews... or that they were brutal. I merely gave you a better explanation for their hatred than mere 'anti-Semitism' (as YOU define that word... it's meaningless to me!) as well as their brutality... (which Zionist Jews have driven them to, of course).  So of course I'll refuse your 'challenge'... which amounts to \textbf{nothing} but a challenge to suicide. But you STILL seem to think it's okay for Jews (no doubt because they are 'God's Chosen People') to steal land from people and deny those same people any right to either defend themselves or to protest against the theft... but hey, they're NOT 'chosen ones' are they? So whatever they feel doesn't count, does it? It's not like they're actually HUMAN or anything is it...  Okay, so I was wrong about there being no online Talmud... on this issue I'll stand corrected... and, as it was a far more reasonable challenge (though still a tall order, mind you!) I shall read it and get back to you when I find the quotes I have previously mentioned... or other quotes of similarly \textbf{racist} content. It may take me some time, however, but I'm sure you won't mind waiting, will you?But I notice you still haven't addressed the Oded Yinon Plan for Greater Israel ("Eretz Yishrael"). I suppose, as you have provided me with a link to the Babylonian Talmud (I hope it is in English, or there will be little point in your referring it to me...) perhaps I should return the favor by providing you with links to explanations of the Oded Yinon Plan for Eretz Yishrael... Here you are: [LINK]  [LINK]  [LINK] I suppose three links should be sufficient to establish its existence... which is absolute proof that much of what you've said is just Zionist bullshit, simply because there IS such a plan, and this in and of itself PROVES Israel's imperialistic, expansionist nature and goals.Okay, I won't say 'goodbye' because I still have to come back to you with the quotes from the Talmud, if and when I find them.Just in case you think I'm totally making them up, however, I'll also give you the sources I have them from... This video clearly shows them in The 'Treatise Sanhedrin' of the Babylonian Talmud: [LINK] You may not hear from me for a while (for which I'm sure you'll be as grateful as the Jews were to the British for 'giving' them Palestine...) but I will be back, after I've read the Talmud, so I won't say 'goodbye'... just 'au revoir'...PS: Oh, btw, exactly what is your position on these quotes? That they exist and are disputed? Or that they don't exist at all? I merely ask because I'd like to know exactly what it is I'm trying to refute... You know all I asked for in the first instance was an explanation of what context could possibly make these quotes any less evil than they obviously are... (assuming, for the moment, that they do exist... though tbf, the links I've given you should be plenty of proof that they DO come from the Babylonian Talmud... perhaps you might like to save me the trouble of reading the whole thing and accept that, yes, they do at least exist... and maybe confine any rebuttal to trying to make them sound less 'evil'...)Then maybe our discussion might move to more fruitful areas... such as philosophy, perhaps...\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/633 & \cellcolor{green!5}0.474 \\  \hline
  \cellcolor{green!27}\small Just dropped by with a very brief note on my reading so far: From the definitions of what constitutes a 'Jew' given in the Babylonian Talmud, taken from the site you gave me to explain the 'context' of the quotes we were discussing, I would have to conclude that Zionists, by their behavior towards Palestinians (among others, eg. the USA and UK...), as much as by their evident disregard for the Torah in their establishment of a Jewish state, cannot possibly be considered 'Jews' at all. Yet even the most Israeli-nationalistic of Zionists still call themselves Jews.Bit odd that, isn't it? So how do I know if you are really a 'Torah-observant' (ie. 'true') Jew if you disobey the commandment of God that you should not have any \textbf{nation} of your own until the messiah comes? (And if you're not a true Jew, but call yourself one, how can I - or anyone else - trust you?)Or will you say that the messiah has already been and gone? Are you secretly accepting Sabbattai Tsvi as your messiah? Or perhaps it was his 'reincarnation', Jacob Frank? (The author of the Zohar, I understand...)Okay... I've done enough reading for tonight; I'll get back to it tomorrow. Goodnight... See you later. :)\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/212 & \cellcolor{green!27}0.472 \\  \hline
  \cellcolor{green!5}\small Just for you to knowMy Messiah is one who has not come yet. He's not here. There are jobs the Messiah must do and qualifications he must  have before anyone can call him the Messiah. No one to this day ever did those Jobs.   The author of the Zohar is Shimon Bar Yochai not Jacob Frank. Learn Judaism please. Show me your definition, from my site if you must, of what a Jew is.  A Jew simply is a Jew if your mother is Jewish. Or you convert properly. He is a descendant of Abraham Issac and Jacob and is a member of one of the 12 tribes through the father.  He is one obligated in doing the Mitzovt. There is no law that the Jews can not have a \textbf{nation} for themselves. If you read the bible correctly. it says they can not live in Israel the sages agreeing. Many sages agree today we can have a \textbf{nation}. Many even say it's a mitzvah  to live in Israel. The many sages that disagreed and said we should not have a established Israel today still live here. Showing they clearly accepted the fact that Israel is a \textbf{nation}. Funny thing to tell me it's a law we can't have a \textbf{nation} but so many great sages of today live in Israel. I still prefer one point at a time or to just stop. The latter is honestly my preferred choice.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}4/241 & \cellcolor{green!5}1.66 \\  \hline
  \cellcolor{green!27}\small I AM in the process of reading that site you linked me to... but it IS a very big site and will take some time... also it is not the easiest of sites to read as it is full of either Yiddish or Hebrew terms I've never met before, so I may need to ask a question or two every now and then. I'm not being deliberately obtuse; I have agreed to read that site (and the Talmud), and I'll do so in good faith, but this is obviously going to take some time.You know that I don't think of 'all ISrael' as being 'cruel'... just the Zionists... although you can't deny that they are in the majority. (What percentage of Israel would you say are Zionists?)You were talking about 'True Zionism' and saying that 'True Zionism' was neither expansionist nor \textbf{racist}, nor cruel... I send you a link to a video which disproves this from the mouths of Israeli prime ministers throughout Israel's history which totally proves that your statement is untrue, in their own words. You have yet to comment on that video. But my latest question is taken straight from your linked site and I think it's a fair enough question... According to the definition of what constitutes a true Jew in your (Babylonian) Talmud, Zionists cannot truly consider themselves 'Jews' because Jews MUST observe the Torah and obey God... these two things are essential to being a Jew, even according to the Talmud... and God commanded that Jews should never have a state until after the return of their messiah. So how can any Zionist truly consider himself a Jew? It seems to me that either you are a "True Jew" or you are a Zionist, but it is impossible to be both simultaneously, even according to your Talmud...I must point out too, that there are some Jews (or 'ex'-Jews, such as \textbf{Shlomo} Sand, and perhaps Norman Finkelstein, for example) who might agree with my reasoning... Now, for me to stop would be to give up on your challenge... which would be an easy thing for me to do... but then neither of us would learn anything, would we? However, I shall try to keep my posts short and down to one point at a time... You may notice that my last couple of posts were both brief and had only one question each in them, though I have reiterated them both here as I would like them both answered because they are both directly relevant to claims you have made yourself.Btw, I'm very glad that you consider your 'messiah' has not come yet... but you can't deny the Sabbattaean element of (modern, so-called 'reformed') Judaism... or Zionism. My question with regard to what you call 'True Zionism' (but by which I think you really mean 'True Judaism') is an attempt to discover to what extent 'True Judaism' has been 'infected' and subverted by Sabbattaeanism and Frankism... ie. to what extent is 'reformed' Judaism STILL 'True' Judaism? Or, put another way, to what extent is Zionism REALLY Judaism? Does it not rather stand traditional, Torah-observing Judaism on its head? That's how it seems to me, anyway...\normalsize   & \cellcolor{green!27}Racist, Shlomo & \cellcolor{green!27}Ethnicity - General, Religious Identity - Jewish & \cellcolor{green!27}2/534 & \cellcolor{green!27}0.375 \\  \hline
  \cellcolor{green!5}\small I'm not interested in you reading the whole Talmud. I'm only interested in you reading the site (Angel fire one) that responded to all of the accusations. You can't just read the whole Talmud and just expect ot understand it. That is like saying you can read the whole Encyclopedia and understand everything in it. Sabbattaen is a small group and it doesn't speak for mainstream Judaism. No more than any one branch of Christianity speaks for all of Christianity. Zionism and Judaism are not the same. You don't have to be religious to be a Zionist nor do you have to be Jewish that should be obvious.  But a vast majority of religious Jews are Zionist. This should tell you something.  You tell me there are some Rabbis that agree with you that Zionist is evil. Unfortunately you are correct. But I can show you a huge list of Arab leaders that are pro Zionist. Your response to that is my response to you. Being observant does not mean to observe perfectly. And again I told you there is no law that Jews can not have there own homeland even when it's not under Torah law. That is a minority opinion. I gave you the answer to that and I see you ignored it. This is what I"m seeing with you. I respond to your points but they are ignored or you just repeat your points as if I never responded forcing me to repeat mine.  Do you remember my answer to this?You say there are Jews like Norman that agree with you. Funny how you ignore the tons of Jews that don't. You seem to want me to say his opinion is much more important that all the Jews in Israel that love Israel.  I can give you an Arab that to me has much more weight than  Norman. She is not Jewish and grew up in Lebanon. She's very pro Israel. She'll tell you over and over that Israel is a great country and the radical  Muslims that run Palestine and many other countries are the real monsters. Her name is Brigitte Gabriel.  Take a look at here stuff. But I bet you'll find a reason why your Norman is real and speaks for all of Israel and Brigitte shouldn't be taken serious.  [LINK] My challenge to you (about going into the territories) was to only show you who the real monsters are. You are totally safe looking and acting like an Arab in Israel but you put your life in danger just looking like a Jew there.  I see you just making excuses for there brutality. Even if you feel they have an excuse it still gives them no reason to teach 3 year \textbf{old} kids to kill. To have three year \textbf{old} girl on public TV give a demonstration on how to kill Jews. It gives them no reason to have kindergarten graduations put on plays were they pretend to kill soldiers and take over Israel.  If they truly wanted peace they should only teach the adults to kill and say I wish we didn't have to but we must. This they don't say but Israel does. Now again only one question or point at a time. Please. Ask me directly then I'll answer. I think I addressed all your points. I just you see you ignoring many of them and act as if I never said it.  But to be honest the kindness thing you can do is to just stop. I really with my heart and soul prefer this. It's a true waist of time for both of us. Readers can decide fore themselves and contact me or you for questions. Have a good day.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/623 & \cellcolor{green!5}0.321 \\  \hline
  \cellcolor{green!27}\small I responded to all your points one by one. Pick just one now. Orthodox Judaism today and Sabbattaenism are not the same. Tzev Tvi converted to Islam. That alone should tell you something.  His points of view are not accepted as valid in Orthodox today. His form of Judaism is not an acknowledged form of Judaism in the Jewish world. Just like Messianic Judaism. Zionism didn't start with them either. Get realI think Israel has every right to exist.  I don't think there is any legitimate reason for Israel not to exist. If you want to say there is then every country has been brutal past. Look at America and how it was to the Indians. Maybe America should be given over to the Indians for Americans were brutal to Indians. Britain has a history. The church has a history of violence. Not one country or religion can you not find reasons for it not to exist.  But as always Israel is the one that gets all the attention.  I say a vast majority of the claims against Israel are lies and I am willing to prove one by one. I understood your points but just like you I see you being advasive of my points to you. The following mail seems to ignore so many of them.Being a Jew and acting like one are two different things. By Jewish law your a Jew if your mom is or you convert properly.  But that doesn't mean your acting like one. Messianic Jews act like Christians not Jews. Jews that ignore Torah and the commandments aren't acting like Jews.  It would be the same as an American. If he has citizenship he's an American. If he lies on his taxes, joins a \textbf{communist} party or anti American stuff then he's not acting like an American.  But again do me a favor just call it quits. Such a waste of time. That again would be the kindest thing you can do for me.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/333 & \cellcolor{green!27}0.3 \\  \hline
  \cellcolor{green!5}\small To me it's the same for the anti Zionist lies the are outright lies and semi truths. Why do they not have a right to there own land. I gave you the answers I guess I have to again. 1. There never was a Palestinian land before or a Palestinian people. I gave you those 12 questions to prove it.  Just look at who is called the Palestinian people all the time.  People of Lebanon, People in the Gaza. People all over the world. 2. Jews were there fare longer and long before Islam was even heard of it's really the land of the Jews. 3. They were given the land in 1948 and they could of had it and kept it for Israel had no interest in war. But they went to war and lost it. Is it not the UN rule that what a country wins in war they get to keep? I think you fail to realize that the UN is one of the most anti semetic organization there is. They pick on Israel far more than any other country even when the accusations against Israel exist far more in other countries. 4. Jordan is what was the Palestinian land.  They have plenty of places to go. That is were  they live. Tell me were do the Jews have to go? Why don't they deserve a land of there own? Why is it that this tiny ant of a \textbf{nation} has to give up land when the Arabs own the rest of the middle east? Take a look at a map. Always Israel that has to give up. None of the  Arab nations have to do anything. 4. Every time they are given weapons (and believe it or not Israel has given them weapons in the past) or land they turn around and use it to kill Israeli and Jews and you honestly can't understand why Israel wont let them have an army? Tell me why won't the US allow Iran to have nuclear weapons? Same reasoning here.  But I guess it's right not to give Iran Nuclear weapons but wrong for Israel not to let the Palestinians have weapons. 5. Read the charter of Hamas it's clearly says they only want the destruction of Israel \textbf{nothing} else. This is why they reject every peace deal even the one were they could of had 95 of what that asked for. I can go on but I think you got the idea. Have a nice life and may you only find blessings and happiness. So have a nice life.\normalsize   & \cellcolor{green!5}Nation, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/431 & \cellcolor{green!5}0.464 \\  \hline
  \cellcolor{green!27}\small (Sighs gently...) I can see you're not learning anything... You see, this response is really unsatisfactory and only demands further comment and/or questions:1: It does not matter that neither a \textbf{nation} nor a state of Palestine existed prior to '48; the region has been called Palestine since Roman times, and it is hardly surprising that its occupants, both Jewish and Arabic (as the Jews were never really 'expelled' from Palestine by the Romans either), identified themselves as Palestinians; it was called Palestine even under the Ottomans and British... Besides, if you're saying that a people without a state have no right to establish one (even in the region in which they have lived for centuries) then you're also saying that the Jews, prior to '48, had no right to establish one either. Remember it was the RIGHT to a state I asked about... not the 'reality' - or otherwise - of one... And as I've already said, whether or not there was an actual state or \textbf{nation} of Palestine prior to '48, the 800,000 people who lived there and who were either killed or forcibly evicted during the Nakbah actually owned the land; they had LEGITIMATE title to it and were evicted under force of arms. Illegally. 2: Now I think you finally reveal your real objection; it is not to the presence of Arabs as such, which Israel objects to but Arabs as Muslims... it is the presence of their religion in what you regard to as YOUR 'holy land'. (Does the phrase 'religious intolerance' mean anything to you?) Ironic that their fairy-tale and yours are so similar, especially in their belief in their own status as 'Chosen Ones', and the fact that the region is THEIR 'holy land too'... and, even more ironically, their fairy-tale is based on YOUR Jewish fairy-tale, too. If you would only think for a few moments about what I've said about religions being the tools of, not imperialists, but the (money-)power behind the imperialists, you might realize that it is, and always has been, through religion that imperialists control the people... and the Jews been controlling both Muslims and Christians for centuries, through those ancient Jewish fairy-tales. There is some hope for the world, perhaps, in the fact that most of the Ashkenazim are atheists... if only they can eventually learn to let go of their 'self-chosen' 'Chosen One' status!3: Now this is just a lie... they were NOT 'given land' in '48 at all, but rather had the large majority of their land taken away from them; only a Jew could squint enough to see it any other way. IF Israel had 'no interest in war' where did this 'Nakbah' (Catastrophe) come from? Who was it that killed or evicted all those 800,000 Palestinians? (Which fact also well explains why there are so many people all around the world who now identify as Palestinians). They did NOT 'went to war and lost it'; they were invaded, tried unsuccessfully to defend themselves from their invaders, who then promptly grabbed as much of their land as they possibly could... in direct contravention of International Law. Oh, look... there's that word again: "anti-Semitic"... wonder what it means? So far as I can tell it's just a kind of tic; a nervous response to any kind of criticism of anything remotely to do with Israel, Judaism or Zionism.4: Jordan was not part of the territory agreed to by the UN as 'Palestine' under the 1949 Armistice Lines; and instead became the kingdom of Jordan (or rather, TransJordan)... But in any case we're talking about those Palestinians who were living in what is more commonly recognized as 'Palestine', the borders of which, strangely enough, prior to '48 were identical to those Israel currently claims... (to the extent that Israel recognizes ANY borders at all...) Besides which, to transfer Palestinians away from their home land to Jordan would involve their mass deportation and this would be against International Law. (Not, I realize, that Israel gives two hoots about that... 'Goyim' Law, eh...?)4 (b): You should have given them freedom and maybe even their land back; or at least the right of return, so they could live as Israelis in the new Israel... (as per the 'one-state solution', perhaps?) then they would have had cause to thank you, rather than hurt you... but if you rob them, force them to live in intolerable and uncivilized conditions, and then YOU give them weapons, who is to blame for your stupidity?If you wish to discuss nuclear weapons, I could point out that Israel is already a nuclear armed rogue, \textbf{terrorist} \textbf{nation}, with at least 300 illegal nukes and an existing plan, very eloquently entitled, the 'Samson Option' in case she should fail to get her way through more conventional means. (Need I say more?) Need I say that the threat of force is also illegal under International Law?Tbh, from where I sit, were it not for your Samson Option, it might actually give me a strange sense of relief, if anything, if Iran were to get nuclear weapons, because then at least there might be some possibility of a 'balance of power'... and if this means Israel and Iran get locked into some kind of 'cold war', arms \textbf{race} stalemate, then so be it! Apart from anything else, however, it must also be pointed out that, unlike Israel, who has not stopped attacking her neighbors (when she's not getting them to attack each other...) ever since her inception, Iran has not actually attacked ANY OTHER \textbf{NATION} in several hundred years. ISISrael was born in blood and can only continue to exist in blood... apparently!Hamas is an extremist, \textbf{terrorist} organisation who bullies the Palestinian people into doing whatever it wants... left alone, the Palestinian people might even be persuaded to accept a one-state solution. But Hamas is also Israel's creation, and it was infiltrated by the Mossad very early in the piece and has in all probability been largely controlled by them ever since. Besides... judging all Palestinian people, or what they want, by the Hamas charter would be like judging all Israelis and what they want by the standards and actions of the Stern Gang, or the Ergun... Oh, dear! Unfortunate choice of words... I forgot how many of your previous prime monsters have been members of those particular \textbf{terrorist} organizations. Anyway, I seem to remember that Hamas have also 'come on board' for what is referred to as the Palestinian 'Peace Offensive' (though one can only imagine why ISISrael finds peace so offensive...) I could go on, but I think you get the idea... Sorry, but I couldn't let your lies and half-truths pass without comment. It's just not in me.'Bye now... have a nice life.\normalsize   & \cellcolor{green!27}Nation, Race, Terrorist & \cellcolor{green!27}Ethnicity - General, Nationality - General, Religious Identity - Muslim & \cellcolor{green!27}8/1134 & \cellcolor{green!27}0.705 \\  \hline
  \cellcolor{green!5}\small You're lying again, because some of the points raised in my last post are quite new to this discussion... but as you have neither reiterated the \textbf{old} points, nor raised any new ones in your last post, I can respect your wishes, I suppose... I"ll just have to settle for the knowledge that there are some questions that you simply will not answer. Fair enough; I think I can see why. "But goodbye is too good a word, babe... So I'll just say 'Fare thee well!' (Bob Dylan). Have a nice life.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small ThesustooThis is your pattern also. Before I answered your questions you replied to you said this .But as I doubt you can answer this anyway,  Always here are the points. I bet you can't answer. I answer you reply and say again like you just did you will not answer them.  So if I continue and answer you'll  reply and say something like. Oye can't address certain points. You know very well Zionist has answer for all your points. If you honestly think that all Zionist will just go DUHHHHH to any point you make then you really have no sense of reality. You know very well that a vast majority of your points I have answer and you know very well I can answer any point you give me. But you also know very well that we are wasting our time. So be a man and stop completely. Don't try to make me look bad. Just reply to this and say goodbye. \textbf{Nothing} else. Good bye until we meet on any other video and post.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/178 & \cellcolor{green!27}0.562 \\  \hline
  \cellcolor{green!5}\small Faisal Ali. Absolutely agree.... Even Ben Jehuda who re-created the language did not want any \textbf{nation}, he wanted to live in peace on the land of Israel in little colonies, but his son turned Zionist. Then from suddenly from Europe ( where millions of Jews were killed in the II.WW)  millions of Jews started emigrating to Israel. Those, 90  fake Askenazi Jews who have almost \textbf{nothing} \textbf{common} in Biblical times Israelites. Look at the Yemenite Jews. Lives in dirt, simple, poor, still speaking a " different"  Hebrew. They are once of those small groups leftover who might be real Jews. Peace with everyone.\normalsize   & \cellcolor{green!5}Common, Nation, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General, Social Class - Working class & \cellcolor{green!5}3/103 & \cellcolor{green!5}2.913 \\  \hline
  \cellcolor{green!27}\small That's impossible. Zionists aren't semites. Sharing features with their fellow \textbf{ethnic} Europeans of a sharp nose and fair skin, they ought to return to their European homeland. Genuine Arab and Jewish semites of the region who share features of a soft nose and olive/tan skin, deserve to remain in the region. As for the comparison against Britains right to exist vs Israels, this is a flawed comparison for the simple reason that Israelis lay false claim to that land. They falsely claimed they were semites and that their forefathers lived here. That may have been true for SOME of them, but the vast majority of Israeli Zionists are not true semites. They are Europeans who used the European White Guilt  as a way to usurp Palestinian (Muslim, Christian or Jewish) land! It's not just about Israels policy or bad decisions. It's about their fundamental claim to that land which is an ABSOLUTE LIE.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/153 & \cellcolor{green!27}0.654 \\  \hline
  \cellcolor{green!5}\small What is it, 95 of Jews that support Zionism, or even more? Zionism is simply an \textbf{ethnic} Jew's right to live in peace in his indigenous sovereign homeland. Anti-Zionism is 100 rooted in Antisemitic values. People who try to obscure the truth are just racists who are afraid to accept that label. Why don't they just admit what they are, instead of trying to glorify it and make it into some righteous cause to openly hate all Jews who support Israel (most Jews). It's because they are cowards. An anti-Zionist Jew is like a \textbf{black} person who is \textbf{racist} towards blacks, or a Non-Jewish white person who wishes he was \textbf{black}, and hates all white people. There are always a few people in any \textbf{ethnicity} who are self-hating.\normalsize   & \cellcolor{green!5}Black, Ethnic, Ethnicity, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}5/128 & \cellcolor{green!5}3.906 \\  \hline
  \cellcolor{green!27}\small Ngata \textbf{Tan} and you're anti Arab\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Quote Gilad Atzmon (musician, fellow human, and ex-jew) "The only people who can defeat anti-Semitism are the Jews themselves. All they have to do is to drop their choseness and become ordinary people – in effect, stop being so special and join the human \textbf{race}."\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small by "others" do you mean the millions of none Jews living in Israel with full rights? fucking spastic\normalsize   & \cellcolor{green!27}Spastic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Enjoy killing each other over the same God and equivocating on the murder and torture of children in Palestine for the same God they believe in. Yahweh, God of child rape, genocide, and \textbf{racism}.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Terrorism is the use of violence in order to make an ideological point, therefore the \textbf{terrorist} is anyone who attack Israel trying to destroy it, it's not terrorism the act of Israel to defend its people from those \textbf{terrorist}. Worrying that an adult person is able to twist even the simple and clear meaning of terrorism. If you're looking for terrorism just look at the palestinian CV:  [LINK] \normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small There are two sides to the story.  Gaza comes under the Palestinian Authority control, not Israel.  If Gaza is a shithole, blame them.  Billion of dollars have been poured into Gaza and the West Bank to no effect.  Where has the money gone?  Most of land used for Jewish \textbf{immigrant} settlements was fairly purchased.  Granted there has been unfair confiscation of some Palestinian settlements.  Every time Israel made 'land for peace' deals with the Palestinians, it ended badly for Israel.  Palestinians and Arabs living in Israel enjoy unpresidented freedoms, even election to the Knesset. Name me one Middle East country that has a Israeli cabinet member!  In fact, where are the Jewish populations of those countries?  Where are the Christian and other religious populations?  Palestine is a convienient excuse to criticise Israel by the other Arab nations.  Why don't they open their doors to Palestinian refugees? Why don't they cerate a Palestinian \textbf{nation} somewhere else that is safe for them?\normalsize   & \cellcolor{green!5}Immigrant, Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/160 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small And, where is Judaism comes from?  Talmudism!   A  Satanic sect, where the "Jewish" religious leaders ( Rabbis) forced an entire \textbf{nation} to take up that religion. Moses the mass murderer who bowed down in front of the Satanic Jahve. Thousands were even following Jesus even Israelites, as they did not like the Selfish Talmudist Judaism. Thus, around 100 ad, Rabbi Shaoul a Jewish high priest started "reforming" it all, creating the "Judeo-Christianity". mixing Judaism with Christianity. Similar grouping created the Evil ISlam.  I know the Thora is different and Talmud is not the base to worship nowadays ( except some Jewish communities who call non Jews "goj".) And anyone can be  Jew, peaceful man, \textbf{woman}, with NO ZIONIST thoughts in their heart. Zionism in its way as it is must be stopped! Israeli mass murderers, Politicians must be imprisoned!\normalsize   & \cellcolor{green!27}Nation, Woman & \cellcolor{green!27}Gender - General, Nationality - General & \cellcolor{green!27}2/139 & \cellcolor{green!27}1.439 \\  \hline
  \cellcolor{green!5}\small National Zionism- \textbf{NAZI} political party\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Of course we shouldn't attack people for their religion or for their \textbf{race}. But should we allow evil, corrupt politicians \& bankers to hide behind religion while they fund (\& in some cases participate in) illegal wars \& apartheid, in effect, going against what they preach? It's bad enough that some who claim to worship God really worship money above all else. It's even worse when they sponsor illegal wars, apartheid, terrorism \& the forcing of much of humanity down into poverty, even famine. Lust for money, lust for the suffering of others. This insane GREED is so great they can't even see their own hypocrisy when they try to blame other races or religions for crimes THEY are committing!Just follow the money trail \& see WHO is getting rich from it all.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/134 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small Nothing to do so with zionism. But those notorious 4 letter words should be non-typable. Otherwise, i  shouldn't be here (youtube chat), and neither should my children, if i have any.I sort of get used to it, but i certainly deplore it, and i must be very careful not to ever get used to it and say it myself, when I'm in better company. It's a big hazard. I never spoke with such people before. I think it should be made untypable.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small +violin614 AHHH, another Zionist advocating death, seems to be a \textbf{common} trait amongst you lot.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small hytyt985875t0fh really? you are either wilfully \textbf{blind} or simply a Jew hater.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Ngata \textbf{Tan} You should see a psychiatrist for your paranoia.  It is a genetic disorder and not your fault, but treatment is available.\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small +Ngata \textbf{Tan} you are the one who is \textbf{blind}, Israel is a \textbf{terrorist} state.\normalsize   & \cellcolor{green!5}Blind, Tan, Terrorist & \cellcolor{green!5}Nationality - British, Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}3/14 & \cellcolor{green!5}21.429 \\  \hline
  \cellcolor{green!27}\small Anti-zionism is not anti-semitism don't let this \textbf{racist} make you believe any different\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Kevin WalshI say they are one in the same if the concentration is always and only on Israel. For example. Many people falsely believe Israel is an apartheid state. So they go and post how terrible Israel is for it's apartheid and so on. Yet they totally ignore   South Africa which is a far worse Apartheid state. IF they want to boycott Israel and ignore all countries that deserve boycotts also.  If they go on line and yell how terrible Israel is for it's treatment of the Palestinians yet ignore the \textbf{terrorist} attack they give to Israel. Or they ignore the countless countries that are far  worse to there own then that person is anti semetic.  If there is a person that speaks against all countries and peoples for the behavior they believe Israel does then that person I would say is not ant semetic.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/146 & \cellcolor{green!5}0.685 \\  \hline
  \cellcolor{green!27}\small South Africa.  The situation there is the same as it was under apartheid. The only difference is there are \textbf{black} faces behind the guns instead of white faces, and the country is mismanaged.  Most \textbf{black} South Africans still live in shanty towns.  I had hoped for better for the poor and downtrodden people.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small LMAO says the \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@peter kelly makes em blind\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Zionism is the last remaining extreme \textbf{nationalism}. And just like all the extreme nationalisms of the 20th century, this one is also based on racial superisority. Make no mistake, Israel is has become a de factor \textbf{racist} state.But allow me to use the some of the same arguments used to fend off accusations of islamophobia; Israel is not a \textbf{race}, judaism is. And the people who oppose Israel are not against Jews per se, they are against Israel because it is OCCUPYING with brutal force an indigenous people against their basic human rights.BBC, have you no shame?\normalsize   & \cellcolor{green!5}Nationalism, Race, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/99 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small what utter nonsense. Zionism, by definition, means that there should be ONE homeland for the Jewish people. after all, there are approximately 60 Muslim countries and more Christian nations.  Zionism, by its definition, is vehemently against \textbf{racism},  religious and \textbf{ethnic}  bigotry.  when Ben-Gurion declared the new state of MEDINAT YISRAEL , he asked ALL arabs, Christians, and druze to stay in there homes to be full citizens of the new democracy. here not ask them to leave and he did not force them from their homes. you are demonstrating the anti-Semitic double stand. one standard for Jews and one for everyone else.  how pitiful\normalsize   & \cellcolor{green!27}Ethnic, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Judaism is a religion never a race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Hold on, Hebrews as an \textbf{ethnicity} are native to Israel much in the same way that the gypsies and travellers are native to India.....The problem is the partition and divide and rule anti solidarity \textbf{racism} shown by the ashkeneonazi Jews and the baghdadi colonialist jews\normalsize   & \cellcolor{green!27}Ethnicity, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small What? What a ridiculous argument, and Evan Davis doesn't even have the integrity to dispute it. Did the UK govt come up and seize the land from another settled group in England? So Bishop Desmond Tutu is a \textbf{racist} according to Sacks? Incredible!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small HO waterbrd : You should go and learn some history and what really happened in the Middle East. You are a fool because you have believed all the lies that people are saying about Israel. Israel did not "seize the land from another settled group" as you seem to think. There was a United Nations vote to partition what was then Palestine into a Jewish state and an Arab state....the Jews agreed but the Arabs did not. Then the armies of FIVE surrounding countries all attacked the new state of Israel with the intention of destroying Israel and killing all the Jews. Unfortunately the Arabs lost and they have been lying about it ever since.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/115 & \cellcolor{green!27}0.87 \\  \hline
  \cellcolor{green!5}\small Exactly- The difference between criticising Israel- and believing it has No right to exist...This is \textbf{nothing} but vicious murderous anti semitism.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Good for them, I know plenty of jews with morals that deplore the occupation of the West-bank and the prison camp that is Gaza. Opnion polls are quite often useless and fraudulent. I can make an opinion poll express whatever end result I desire.  The gvt does it as a matter of day to day governance of the plebs. When the state of Israel has to employ Hasbara en mass with Orwellian internet propaganda you don';t have to be a genius to see that this is the act of a state desperate to hide it's true face. Its a pretty narrative Israel the defenseless little Jewish state, what about Israel the nuclear state with some of the most powerful weapons technology in the world, brutally and systemically oppressing the \textbf{ethnic} people that's land they were given by callous colonial powers, stealing more and more everyday, blatantly and arrogantly indifferent to the world's outrage beacuse successive American governments and Bilderberg types see the value in a strong Western colony on the Levant.See I can construct a narrative too and I don't even get paid a few quid an hour by state propagandists to do it :)\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/196 & \cellcolor{green!27}0.51 \\  \hline
  \cellcolor{green!5}\small It's a \textbf{racist} philosophy. Jews live all over the world. They are welcome to live in the UK, but Zionists cannot both live in the UK and have a homeland they can scamper off to whenever they feel like it. It's really greedy. You can live wherever you like in the free world, but Zionists also want an ethnostate. Greedy ethnonationalism won't survive the 21st century\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small \@LMFK \textbf{weird} I am jewish I never heard this story. Would you be ok wity any size of Israel in the world like the one the UN voted on creating ?\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small ohad bracha btw are you retarded or something? You don't know what Zionism is? I thought you lot are supposed to be really clever. I guess not all the stereotypes are true about Jews. The only true ones are that you are cheap, greedy, and filthy scumbags. You are either \textbf{dumb} as a rock or you are trying to come across like you have no idea what your people are all about (stealing land, starting wars, leeching off the USA, and being complete cun7s)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Dual loyalty in my homeland and their \textbf{racist} tendencies is my beef with the Jew, the Jews that matter anyhow.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Blind\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small \@Kindred Spirit Comparing Israel to \textbf{Nazi} germany of all countries... you're an anti semite without even knowing it...\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Leah Oliver If you're comparing A \textbf{nation} of people and the people who purposely murdered 5 millions of them within a few years, you're clearly being sarcastic and clearly are being anti semitic as you certainly aren't comparing the US to \textbf{nazi} germany even though they killed way more innocent people then Israel and used WAY less regard to innocent lives via methods of airstriker.Comparing Israel to \textbf{Nazi} germany is a sadistic evil analogy.\normalsize   & \cellcolor{green!5}Nation, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - General & \cellcolor{green!5}3/75 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@TheIsraeli G Oh btw it's BRITISH Christians and non-religious Jews from the early 20th century who never read or abided by the Talmud that we have to thank for so-called Israel to begin with. "Lord" Sacks is a liar and not even a Talmud Jew as the Talmud SPECIFICALLY states that Jews are NOT to ever form as a \textbf{nation} again until Judgement Day. God's own Word. Who will argue against that and still call themselves a practicing Christian or Hebrew?\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small \@TheIsraeli G "Comparing Israel to \textbf{Nazi} germany is a sadistic evil analogy."Tell it to the hundreds of thousands you've helped to murder in cold blood, creep. Many of those Iraqis you helped butcher were Semites as well, creepy.Murder Christians in Syria. Who cares, right? You are such a tool.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small He's absurd on both points. For one thing, the evidence suggest that segregation is decreasing among most \textbf{ethnic} groups, with the only exception being the White British population, who are becoming more segregated from everyone else.Secondly, believing that Israel should not exist isn't an illegitimate position. The entire premise of the country is that it used to be a colonial land that was then gifted to European Jews, and has since colonised more land around it. If someone invaded Britain, took our land and formed a new \textbf{nation} state on top then no one would say it's \textbf{racist} to criticise such a system, yet somehow Israel gets away with it.\normalsize   & \cellcolor{green!27}Ethnic, Nation, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}3/111 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small it's totally ok to criticise the politics of a country-Israel included. What it's NOT ok to do is to spread lies about what is going on, to assume that all Jews are Israelis and so are legitimate targets for attack or to start denying a people's right to exist or holding one nations to standards that others aren't.  America,Australia,New Zealand and South Africa are all countries created by invasion and genocide. If Israel has no right to exist based on its supposed "occupation" then neither do these countries. BUT when you start to say things like Israel should exist while living in a country formed by  occupation yourself and if you deny the right of a people to exist under the guise of political opinipn then THAT is anti semtic.. The Jewish people have a right to our homeland that we have occupied continously for over 3000 years. Disagree with the ISRAELI government if you want- deny our right to exist as a \textbf{nation} and you are an anti semitism whether you like it or not! !\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/177 & \cellcolor{green!5}1.13 \\  \hline
  \cellcolor{green!27}\small Israelis were not guilty of any war crimes in those wars. The Hamas \textbf{terrorist} organization which rules Gaza ARE. There isn't even any criticism of Israel. It is simply that Israel is not being given the right to exist. Any criticisms needs to be backed up by facts, and they must be verified. Hamas is using the world to get israel destroyed with all its jewish inhabitants together. And that is why Hamas made the recent wars. You may criticize Israel as much as you want, but one thing I will NEVER hear anyone say, is that Israel committed war crimes in recent wars. There was never a more moral and humane army in the whole history of warfare than the IDF. And this is the absolute TRUTH. Check the facts, from the right places.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/135 & \cellcolor{green!27}0.741 \\  \hline
  \cellcolor{green!5}\small \@krag3rAttack the perpetrators, not the innocents. Then again, to Israeli extremists/terrorists, I guess every Palestinian (whether man, \textbf{woman}, or child) is a target.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@krag3rHospitals, civilians homes, even cemeteries were target by Israel, resulting in hundreds of civilian deaths.\textbf{Doctors} killed and injured; the latter absolutely and categorically denied there were militants in the area. There's been many accounts of IDF soldiers saying they were told to shoot and kill anyone they came in contact with, be they men, women, or children.And it's funny you call the deaths of innocents as collateral damage. Would someone saying the same thing when Israeli civilians are killed, be ok in your book?\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small Yes, as it says so. Basically no freedom of Speech here. Israel, the \textbf{nation} that was built and founded on Political ideology, and for serving certain concerns and fulfill political aims and \textbf{nothing}, and \textbf{nothing} to do with Jews and Judaism. That Cionist Elite is leading the US and other countries too. Owning banks, media, politics.\normalsize   & \cellcolor{green!5}Nation, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}3/56 & \cellcolor{green!5}5.357 \\  \hline
  \cellcolor{green!27}\small Roman Newland, and you are a stupid \textbf{Nazi}. The Jews have a right to ha W their own home. They have been there for thousands of years you stupid anti-Semite.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Roman Newland, maybe you should know this. The Romans called the Jews in the area Palestinians. Also, they are taking \textbf{nothing} yet. They will liberate the whole region of Palestine, then Jordan, and Sinai will be encompassed into Israel.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Will Scarlett, you idiot, the population of the Arabs is rising like \textbf{crazy}.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Will Scarlett itvus not a war crime to retaliate against people who continue to attack you -every \textbf{nation} has a right to send defence and the Palestinians have been attacking Israel for 70 years  And as these attackers are not part of a regular army in uniform then international law they are not entitled to the protections og tgr Geneva Conventions. Until the Palestinians desist they will continue to pay a heavy price in blood -their choice .\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Ronnie Ince I didn't know that. It's a pity the \textbf{papist} stooges are turning against them now - I think there is still a lot of support for Israel from ordinary people because we also suffer under those criminals!!\normalsize   & \cellcolor{green!27}Papist & \cellcolor{green!27}Religious Identity - Roman Catholic & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Ronnie Ince+ The PA in the Occupied West Bank recognises Israel as a \textbf{nation}. Why is it still being illegally occupied by Tel Aviv? And you haven't answered the question of illegal settlements. And what did you make of Netanyahu's recent statement re. Israel being a country where Jewish rights come first, overriding minority rights? Is this how a democracy acts?\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small \@Will Scarlett All citizens if Israel have the same civil rights including voting rights .The Palestinians do not officially recognise the State of Israel and it's right to exist and their continued attacks mean that the Israelis occupy territory that the Palestinians lost in war .Whether you like it or not unless and until the Palestinians cease all attacks on Israel they are going to suffer military responses that will cost them loss of life .In the end they will have to do a deal just as Japan and Germany has to unconditionally surrender or the war continue -the Palestinians cannot possibly win so \textbf{common} sense days that in those circumstances you surrender unconditionally and accept the best terms you can get .The alternative is to fight to the last man and die for a lost cause - the Palestinians have not the military means to defeat Israel and have no military support from elsewhere so defeat is inevitable -it is just that they don't care about their losses do choose to fight to the last man \textbf{woman} and child  So they either give up , do a deal or die -their choice .have no friends\normalsize   & \cellcolor{green!27}Common, Woman & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/197 & \cellcolor{green!27}1.015 \\  \hline
  \cellcolor{green!5}\small Francesco Cecco you hypocrite.  A Jew isn't a \textbf{race}!   And if it's by genealogy they need to prove it!  They can't.   Also, here is a simple thing:  Jacob and Esau were TWINS, so the \textbf{race} argument is stupid.   Right to exist is \textbf{dumb}.   He means the right to be \textbf{racist} and play the victim while hiding behind \textbf{race} identity that was invented.   How can you be a 'secular' Jew?  That is \textbf{dumb} and nonsensical.   It was and always be a belief and you have the wrong belief you are not JEW.   Logic 101.  Plus the point of the CIRCUMCISION was to let them know it wasn't based on their physical 'seed' but by and for ALL WHO ACCEPTED THE spiritual seed ('the word') of God.   And the fact, that the \textbf{racist} are appealing and getting help from 'goyim' nations is just proof this is a fraud because God doesn't work through lobbying, voting, military alliances with other nations which Zionist claim serve a false 'god'.  It's called stupidity and not knowing the Bible, and being a HYPOCRITE.  That is why the so-called 'Jew' has become strangely a \textbf{race}, they do no conversion and don't even tell others to convert which was the WHOLE PURPOSE of the 'Jew'—to bring other nations to the truth by making converts!   Why don't they do this!?   Because these Pharisees are fake...they use '\textbf{race}' as a shield but a Jew isn't a \textbf{race} at all.  Only a \textbf{racist} would make it a \textbf{race}.  Try not to be gullible. Think circumcision and why God had them do it.  If you are a child of God based on the flesh, then MAN IS GOD from Adam onwards.  Seem like a bunch of self Idolatry pretending to worship God but just a form of \textbf{racist} colonialism repacked and blaming God to sucker the ignorant\normalsize   & \cellcolor{green!5}Dumb, Race, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}12/305 & \cellcolor{green!5}3.934 \\  \hline
  \cellcolor{green!27}\small Odd how the "Jewish (master \textbf{race}) State" of Israel never promotes that "Diversity" in their own country. How many of those Syrian refugees has Israel taken in?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@Ngata \textbf{Tan}  No I'm anti-bullshit...and its easy to confuse that with just about everything most Israel supporters say. LOL  Speaking of which...so Israelis believe these people are dangerous but still want to dump them on neighboring countries and Europe?  No wonder Israel isn't well liked !\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@TheIsraeli G   Most racially diverse in the Middle East??!  Are you kidding?  Over 75 of Israel's population comes from one racial/ethnic group.  Iran, by comparison, has a Persian majority of only 61...meaning that the remaining  39 are split between the 12 million Azeris, the 8 million Kurds, the 2 million Baluchis,  the 4.8 million Lors...and other smaller minority groups.  The point here is that there is at least some semblance of power sharing, such as the Kurds holding 18 seats of Iran's 290 seat parliament (as of the 2013 figures).   I challenge you to find Israel's Knesset doing anything similar to engage in diversity.  Israel doesn't WANT diversity.  Israel wants what Hitler wanted...a state controlled by a pure \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/119 & \cellcolor{green!27}0.84 \\  \hline
  \cellcolor{green!5}\small \@Jake Ryan theres around 10 percent mostly none Jewish Russians in Israel around 20 percent north \textbf{african} JewsAnother 10 percent of Etheopian Jews maybe 10 percent western european Jews another 15 percent east european Jews around 20 percent of middle eastern Jews and around 15 percent of Muslim arabs.If that's not diverse idk what is.Also if you claim that our religion is not diverse idk why you didn't use religion as a factor in Iran which is like 99 Muslim.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small \@Jake Ryan which Jewish only roads? HAHAHA Jesus man you belong in a \textbf{mental} assylum.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Jake Ryan seems to be the only one that knows the truth here. Arabs live freely side by side with Jews here. They are \textbf{doctors}, lawyers just like Jews here. They have there own party and even a Judge on the supreme court. Israel treats Arabs in hospitals just like Jews. If anyone things that Israel is diverse and hates Arabs then you are \textbf{blind} as a bat. Please come to Israel and see for yourself.\normalsize   & \cellcolor{green!5}Blind, doctors & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small therobbieunited\@No it ain't. Most of you BDS \textbf{terrorist} symapthizers simply like to utilize the palestinian cause as a vehicle to justify your internalized anti semtism. You people are almost always synonymous with those who believe retarded conspiriacy theories such as their being some secretive, all encompasing, jewish cabal that somehow secretly controls hollywood and the entire world from behind the scenes. I was once one of you, and I know all too well how your lot thinks.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small 7/11 Truther.If criticising Isreal is anti-Semitic and defending palestinians is \textbf{terrorist} sympathizing, then call me an anti semitic terrorism sympathizer, feels good to be I'm quite proud actually\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Storm RiderAlso Israel counts the calories that enter Gaza there's restrictions imposed by Isreal on Gaza \textbf{nothing} enters Gaza without the knowledge of Israel because no one can enter Gaza by sea or air only by land through Israel, and let's not pretend that Israel didn't help creat and put hamas in power [LINK]  [LINK]  [LINK]  [LINK] \normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small Storm RiderYour created the problem, your analogy is idiotic it would be like England creating a \textbf{terrorist} organisation in Wales to have an excuse to fire missiles on the civilians, god damn your own officials said that "when a greater power rules over a smaller \textbf{nation} a violent response is to be expected" Mattityahu Peled\normalsize   & \cellcolor{green!5}Nation, Terrorist & \cellcolor{green!5}Nationality - General, Religious Identity - Muslim & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Francesco  "  Gekko"  LOL. Antisemitism is a tool for keeping people shut up, and stop them from free speech. The main problem is, how the Early Zionist Jewish politics took Palestinian lands, and killed thousands just get lands. Now, of course Arabs are angry. Israel started that, now deserves mocking.  Instead of creating a \textbf{Nation} and taking lands illegally they should have lived in peace in little communities in Israel or in the area. Even Ben Jehuda who revived the Hebrew language did not want it and was against all bad intentioned Zionism. His son turned Zionist and He denied him later.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small \@Francesco Cecco  Have you any idea how insane it is to make anti-Zionism = antisemitism? Herzl the founder of Zionism was born in Budapest in 1860. His parents were secular, assimilated, German-speaking Jews and he himself admired German culture, philosophy, art, literature as the acme of Western civilisation. As a student at Vienna University, he joined the German nationalist fraternity, Albia, whose motto was Honour, Freedom, Fatherland, though he did later resign in protest at the antisemitism that he encountered. Like many educated, German-speaking Jews, he had \textbf{nothing} but contempt for the mass of religious, Torah-abiding, Yiddish-speaking, shtetl-dwelling Eastern European Jews. There is \textbf{nothing} in his writings to suggest that he had any great attachment to Judaism or much interest in or knowledge of Judaic teaching.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/126 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small MagicKirin1 Do you have any evidence of human shields being used or is this just things you relay from the mainstream propaganda you're fed? I can provide evidence of UN reports highlighting the fact that Israeli troops were sniping and shooting from point blank range against unarmed protesters, children, \textbf{disabled}, journalists and even medics who were helping Palestinians. There is irrefutable evidence to suggest that Israel has violated countless human rights and war crime acts many many times, yet everyone turns a \textbf{blind} eye against it all. Why is this the case?\normalsize   & \cellcolor{green!27}Blind, Disabled & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/92 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@7/11 Truther. Damn, you must be \textbf{dumb} as fuck. to get woke then to go back to sleep. lmao.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Cockoff Gewgle There is no air prisons just prisons. I suppose it's wrong to arrest Arabs that do \textbf{terrorist} attacks against us. The ones that  blow themselves up in theaters, restaurants. Kill people sleeping or watching TV in there homes I supposes that is wrong in your eyes. You do realize that before any major bombs (I suppose that it's wrong to defend against the Missles they shoot at us) Israel warns all Arab citizens to leave. They send pamphlets, give SMS and even call everyone encouraging them to leave. Citizens are given warnings. What is the reaction of Hamas. They force there own to stay right in the line of fire. They are not allowed to leave.  I think you really need to learn what really is going on here. You have no clue.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/135 & \cellcolor{green!27}0.741 \\  \hline
  \cellcolor{green!5}\small \@Michele Doveri You think I'm lying then please come to Israel. Arabs have there own party in the Knesset. There is an Arab judge on the Supreme court. There are Arab \textbf{doctors} and lawyers. One of the major bus companies is owned by Arabs. It's called Native Express check it out. Every factory you find Jews working and owning you can find Arabs. If you are so sure it's dangerous to be an Arab in Israel I'll do an experiment with you. I'll do only half only you can do the rest. Let us both dress up as an Arab and go all over Israel. In restaurants, theaters all over and let's see how we are at the end of the day. We'll be alive and well and treated as equals. Then you and only you can go too the territories dressed as a Jew or holding an Israeli flag, dressed as an Israeli supporter. Then let's see what happens. If you are \textbf{crazy} enough to do this then make sure your family makes your funeral arrangements. I'm seriously not kidding on this one. If you still insist the hate is on the Israeli side then take a look at there media which they plaster all over if for all ages 3 and up to kill kill kill as many Jews and Israelis as you can. Please show me the equivalent on Israeli media.  [LINK] You are extremely ignorant of what is really going on here.\normalsize   & \cellcolor{green!5}Crazy, doctors & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/246 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}\small The manufacture of the \textbf{nation} of Israel in  1948 was a crime, this was no different from the Europeans going enmase to North America and determining that this land, lived on already by native Indians, was now theirs, or like the British going to Australia and making that land theirs, even though the land was already inhabited and owned by the native Aborigines or South Africa or Rhodesia/Zimbabwe or the many other land grabs.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small The manufacture of a \textbf{nation} is what's going on with the palestinian propaganda. Israel has already existed twice in History to it was just re-born. Jerusalem is a HEBREW NAME of the city that's been their capital.  [LINK] \normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Absolute crap. How does opposing the policy of a \textbf{nation} state somehow equate to being hateful of an entire religion?! This is how Israel can brush off its expansionist critics with cries of antisemitism\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Jews returned to Israel because Europeans like you forced us back!  We needed a homeland to keep us safe from centuries of your aggression.  My Jewish ancestors were kicked out of Israel and sent to Spain.  Kicked out of Spain and fled to South America.  When the Inquisition caught up with us in Peru, fled to America and finally onto another country in the Southern Hemisphere.  As far away from Europe as possible. It was Edward Long Shank who made us wear the \textbf{y\textbf{e\textbf{llow}}} star and expelled most of England's Jewish population to mainly Scotland.  It was the British who invented the Concentration Camp during the Boer war.  It was the bankers, industrialists and profiteers who profited from Jewish labour in European death camps. You have the gall to make such statements.  Just before a crusade,  Christian psychopaths murdered the nearest Jewish population for the fun of it.  Don't you dare try to take the moral high ground on the matter of the so-called Palestinians! If we don't defend ourselves, who will defend us?\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/174 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small \@Kathy Jeanmarie No, you're incorrect on what \textbf{Nazi} means. \textbf{Nazi} actually means National Socialist German Workers' Party\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small + \textbf{Kraut} and Tea   When Zionists habitually lie eventually people stop listening...so down-voting becomes automatic with all Zionist propaganda.  This is how it should be.\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Kraut and Tea Go back to your hole\normalsize   & \cellcolor{green!27}Kraut & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Kraut and Tea funny how Europe cant be ethnostate but Israel can. God damn you zionist are a weak people\normalsize   & \cellcolor{green!5}Kraut & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Point 1: Everything you stated is an overly generalization and false. It is clear you are not a Torah scholar, a historian let alone what Zionism, anti-Semitism truly is and means. You simply ignored the points the great rabbi Sacks was making. Why, simple because your an anti-Semite and a STUPID one at that.Point 2: People of good-will, unbiased individuals want \textbf{nothing} to do with you.Therefore, What you just said is one of the most insanely idiotic things I have ever heard but typical coming from anti-Semites. At no point to your rambling and incoherent comment were your ever close to anything that could be considered rational thought. Everyone in this forum is now dumber for having to listen to it. Anti-Semites have no facts and are not concerned with truths but resort to falsification of history, fabrications and CANARDS in order to support their evil claims and agendas which their objectives is demonize Israel the Jewish people. This is done through willful lies by miseducating and misleading the public with their perverted one-sided, anti-Israel, anti-Semitic views and propaganda. We has seen your filthy kind throughout history and your STUPID arguments have been bandied about so much that everyone is sick and tired of them. We people of good-will and a pure-heart will not accept such evils and we shall haunt you and will inflict greater damage by spitting you out and sending you to that place called the abyss of insignificance.Anti-Semites have no case whatsoever and may your bones be ground to dust.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/257 & \cellcolor{green!27}0.389 \\  \hline
  \cellcolor{green!5}\small unfortunately for you prominent jews are also anti-zionists (Chomsky, Zinn, Finkelstein...) because zionism is a \textbf{racist} ideology, thus being anti-zionist is NOT equal to anti-semitism\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Patrick Van Gelder Your comment is one the most insanely idiotic things I have ever read.  It is clear you are not a Torah scholar, a historian let alone what Zionism, anti-Semitism truly is and means.  Thus, you simply ignored the points of the great rabbi sacks was making.Zionism in its political form is the national liberation movement of the Jewish people which holds that the Jewish people like any other \textbf{nation} are entitled to a homeland. This is based on the fact that the Jewish \textbf{nation} are the indigenous people to the land and maintained a continuous presence for 4,000 years as recorded in the Bible and has been proven to be true based on archaeology and history. Therefore Zionism recognizes that the Yiddishkeit (Jewishness) is defined by shared origin in terms of religion, culture and history, hence the Balfour Declaration. The Balfour Declaration holds categorically that Palestine (the idiom of that time, yet a misnomer) is the national home for the Jewish people. The Mandate for Palestine includes the Balfour Declaration and it specifically referred to the "the historical connection of the Jewish people. . . " This means the moral validity of "reconstituting the Jewish homeland as a National Home in Israel as the country of the Jewish people. Therefore the term "reconstituting" demonstrates the fact that Palestine (Israel) had been the Jews' home. Furthermore Zionism is composed and consists of Western values of individuality, equality and freedom. For example the values of freedom of speech, press, dissent, association and religion just to mention a few.Moreover, Zionism does not discriminate against anyone. Israel is a pluralistic and democratic society and its open character qualities allows everyone to be the best person they can be. It also protects religious and political rights for all its citizens including Christians, Muslims, atheists an all others. Anyone who believes in these values that I mentioned above regardless if they are Jewish or not is a Zionist. One more point and that is many who are against Zionism do not really understand the concept because their information is willfully distorted by propaganda which comes from the anti-Semites (the Jew haters). Moral leaders of various faiths have repeatedly warned that anti-Zionism is antisemitism in practice. The late Dr. Martin Luther King, Jr., said upon hearing a \textbf{Black} student at Harvard launch a tirade against Zionist: "When people criticize Zionist they mean Jews. You're talking antisemitism."In conclusion anti-Semites have no facts and others alike are not concerned with truths but resort to falsification of history and fabrications in order to support their evil claims and agendas which their objectives is demonize Israel the Jewish people. This is done through willful lies by miseducating and misleading the public with their perverted one-sided, anti-Israel, anti-Semitic views and propagandaAnti-Semites have no case whatsoever.\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}3/470 & \cellcolor{green!27}0.638 \\  \hline
  \cellcolor{green!5}\small you are truly the most insanely idiotic moron on the entire internet (you see I can also behave like a third grader). Everyone knows when you are talking about zionists that we mean the \textbf{racist} ideology that is now ruling Israel, all your "history " is pointless we don't live 100 years ago we have to confront this sick ideology at this moment. You still have not refuted why all these renowed jews are anti-zionist, you are just a piece of intellectual cowardness\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Herman} Browndog Islam swept across a large swathe of the known world - by force. It's all well documented. They even got as far as Spain and parts of Europe. Islam isn't interested in compromise. The harsh truth is - that Islam is going to need to be dislodged by force. There Will Be Blood.\normalsize   & \cellcolor{green!27}Herman & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small adjc88 I suppose the words "\textbf{zero} tolerance" would mean that if someone starts speaking like that, the one representing the hated side (the jews/israelis) should walk right out, or consider the dialogue closed, at any rate, and leave that person to contemplate in shame, and to speak better next time.ie not to tolerate such a person as a person in dialogue..If he wants to say one fact at a time and then listen to your answer OK, but when he starts building fact after fact, it's quite obvious he's not going to listen to you for te next 20 hours when you undo his "facts" one by one. So better to leave the room already.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/117 & \cellcolor{green!5}0.855 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Herman} Browndog Get real. The whole population of Israel were a bunch of freeloaders shipped-in from outside. Re-drawing borders is one thing. Shipping in a totally \textbf{ALIEN} population is a totally different thing. My father fought the Germans to help save the Jews. When he was in Palestine after the end of the war - he had Arabs AND Jews trying to kill him (Look-up the 'Stern Gang'.). The SAME Jews he's been fighting next to. There's thanks for you. Not surprisingly - he preferred the Arabs, well, it was the Palestinians own land after all...! After the war, the U.S. kept butting-in to affairs in the Middle East. Then - as now, they kept making matters WORSE. Why...? Huge Jewish business interests in the USA. Simples.\normalsize   & \cellcolor{green!27}Alien, Herman & \cellcolor{green!27}Nationality - General, Nationality - German & \cellcolor{green!27}2/127 & \cellcolor{green!27}1.575 \\  \hline
  \cellcolor{green!5}\small \@HeavensGremlin Gosh, I didn't realize that. There was always a strong Jewish presence in Israel, even when the region was part of the Ottoman Empire. Also, the major Jewish population of Israel (almost 55) has been Sephardic for decades, largely as a result of the Arab countries expelling their Jewish population after the 1967. I also didn't realize that World War 2  was fought "to help save the Jews." I thought it was because Germany had invaded Poland, France, Belgium, Holland, Norway, Denmark, Greece, Czechoslovakia, Yugoslavia, the and  the Soviet Union and had declared war on the US. Anyway, this all seems to be a kind of \textbf{mental} masturbation. The people who don't think that Israel should exist should stop chattering and do something about it. They've already tried four times. The next time will, I believe, be the last.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/140 & \cellcolor{green!5}0.714 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Herman} Browndog The truth is - a) Without US support the US wouldn't even have EXISTED in the first place, \& b) Would rapidly vanish without it. \& c) No one would miss it when it was gone - except maybe the Arabs, would have one less other body of people to blame for their incessant in-fighting.\normalsize   & \cellcolor{green!27}Herman & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small \@violin614 ALL of the people running around the Middle-East 2,000 years ago were basically desert tribes - except for the Romans that were not auxiliaries. Sadly, you are living in a time-warp come alternative reality. The Romans ruled all of Europe 2,000 years ago. Should we all move-out so that the Italians can take over...LOL..? Going by your logic, you should all get out and allow the Palestinians to take-over anyway. It's all BS in reality. What is this 'returned' BS too...? Do you even have the slightest comprehension of how utterly stupid this is....? What happened 2,000 years ago is now totally and completely  IRRELEVANT. No one gives a flying toss. The REAL displaced people died 2,000 years ago. You are not then. They are long dead and gone. You are fantasist trying to justify theft. That said - I have no liking, or even respect for Islam. If there is a God - he doesn't need ANY of these \textbf{crazy}, murdering religions. Mankind is far better without ANY of them.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/172 & \cellcolor{green!5}0.581 \\  \hline
  \cellcolor{green!27}\small "Calling for the destruction of Israel ("Free Palestine") is a call for \textbf{ethnic} cleansing and genocide."Typical Jewish bullshit and hyperbole... Why can calling for a 'Free Palestine' not simply mean just a change of name to what it was prior to '48? And possibly more equal representation for the Arabic section of the population? Why the need for any animosity at all? (Except, of course, that it is Israel who wants conflict; and it is lsrael who has always generated it, ever since the Nakbah... Israel has not stopped attacking its neighbors; indeed it seems Israel can ONLY continue to exist by continually attacking her neighbors. Can ANY country which can ONLY continue to exist by attacking its neighbors ever really be said to have a 'right' to exist? Or 'legitimacy'?)That's what really scares ISISrael, isn't it? Because if Israel were truly a democracy, sooner or later, the Arabs WILL overtake Israel's percentage of the population, and then it would naturally take over (most of - we're assuming 'democracy', right...) its government; and when it does, such a name-change IS 'on the cards', I'd say...Such a 'Palestine' may be 'free' from Zionism, eventually... but one can only hope that they will also free themselves from the slave-religion Islam too, otherwise they will have gained very little.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/219 & \cellcolor{green!27}0.457 \\  \hline
  \cellcolor{green!5}\small I would love to hear Sacks' definition of the term "Zionism". Does his definition include stealing land which doesn't belong to you to establish your own homeland? Does it include evicting indigenous residents from their homes and turning the land over to settlers of a different \textbf{race}? Does it include attacking unarmed fishing boats when the Palestinian people are trying to feed themselves? If his definition DOES include those things, then I would like him to justify those actions. If his definition does NOT include those things, then his position puts him at odds with the state of Israel and the Israeli government, and I would like him to comment on Israel's actions. Does he support the way that the Israeli government behaves, or not?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/125 & \cellcolor{green!5}0.8 \\  \hline
  \cellcolor{green!27}\small very sadly he seems to be defining "zionism" as jews entitlement to act just like every other kind of raging ass hole patriot..one would hope that a rabbi of his \textbf{age} would be rather wiser and more grown up.. wish he could recognise that all mindless \textbf{nationalism} is idolatry..\normalsize   & \cellcolor{green!27}Age, Nationalism & \cellcolor{green!27}Age - General, Nationality - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small When a politician says that, and I am paraphrasing 'we have a duty to ensure that Israel is kept Jewish and white 'then any person with an ounce of human dignity should have a problem with that.  When a state uses the law to deny a section of its people equal right before the law then I have a problem with that.  Israeli Arabs and Bedoiun Arabs are denied ownership of land and property through rigged laws and \textbf{racist} courts.  When a state forces birth control onto a \textbf{black} \textbf{ethnic} group then I have a problem with that.  It was discovered that under the guise of State provided medical aid the Ethiopian Jews, and especially the women subjected to both sterilisation and birth control.  The recent inclusion of the hard right wing extremists into the Israeli government is worrying.  If these right wing extremists were in a state other than Israel they could be called neo-nazis.  When politicians who call for the expulsion of Arabs and even talking of gassing them are then included within the Israeli government then you can talk of the similarities with the Nazis.A foundation legend of Israel is that it was founded on the deaths of millions in the Holocaust.  By following policies of apartheid from South Africa and legalised discrimination against non white and non Jewish citizens it is urinating the memory of the dead.  \textbf{Nazi} Germany did not start with gas chambers they started with legalised discrimination and exclusion of Jewish Germans from society.  The rhetoric of the Israeli right wing and settler movement is following the path of the Nazis.  Never forget the nazis went from the Nuremburg laws to Treblinka.Anti-semitism is evil.  It has no place in our world.  We have a duty to combat and stand up to evil where ever we see and find it.  Currently the politicians of Israel's hard right are embarking on a dark, dangerous and evil path that echoes Germany of the 1930's.\normalsize   & \cellcolor{green!5}Black, Ethnic, Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/330 & \cellcolor{green!5}1.212 \\  \hline
  \cellcolor{green!27}\small Nice bit of bigotry there. In Palestine Jews, Muslims and Christians live side by side for hundreds of years.  You are the sort of of bigot who makes things so much easier for anti semites around the world.  There is no difference between you and a \textbf{Nazi} from the SS.  In fact,, I think that in the 1940's you would have been happy working as an administrator in Aktion Rheinart.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small \@Greg ari there is no cosmic law that says that the members of any \textbf{ethnic} group are immune to becoming ass holes.. so once things have turned as ugly as they have in palestine - it is not surprising that many from both sides have added to the misery...\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small The way I look at it is if he supports Israel and defends Zionism the. He is equally complicit in their crimes. This man is the acceptable face of Jewish radicalisation, if he was a Muslim he would be called a \textbf{terrorist}.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Greg Ari!  Learn some real history where the Jews came from, to that land, if ever!  And how owned that land before the Jews, before the Arabs, before all times?  Moses the mass murderer who led its people ( \textbf{nation}) because "  God"  told him so...  ?  Wow, was that God?  murdering innocent?  Evil Talmudist Jewish sect.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small I'm sorry but there's a massive difference between discriminating against a race/religion, which you are born into and don't have much choice in (i know that's theoretically the case for religion but in practicality it effectively is, certainly in the middle ages), and being being against a state which imposes \textbf{racist} systematic oppression. Now i know the Isreal-Palestine/Arab conflict is complicated, I personally find my sympathy leaning towards the Palestinians but they and their backers are by no means perfect and I do understand why Israel does some of what it does. But trying to compare anti-Zionism to anti-Semitism just makes you sound like either a liar or a fool, and errodes what respect I have for the Israeli perspective.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}\small \@suziecreamcheaseAnd Muslims... and tbh all major religions, I think they feel assaulted both by other religions and modern secularism. Hence they all play the victim card while getting increasingly aggressive in their stance, as they don't want to fall without a fight :/I am convinced we are heading towards a more enlightened secular world, but to quote that wise \textbf{old} head Harvey Dent: "The night is darkest just before the dawn. And I promise you, the dawn is coming".\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small \@suziecreamcheasefor sure religion is not the entire problem, people have always fought and always will fight, whether there is religion or not. But it is still a part of the problem, and it currently divides people more than it unites us (not that division is always bad... I'm all for diversity, but not when it turns violent).Even if it is only a vehicle for stupidity (which is debatable: suppression of contraceptives is the first example that comes to mind when i think of badness to have come purely from religion. That alone has contributed to mass suffering in the form of the spread of STDs/STIs, overpopulation and all the misery that comes with that) does that make it ok? even as just a vehicle, it can still amplify our problems (womens rights, \textbf{homophobia}, suppressing freedom of thought and speech, acceptance of other cultures are all problems not unique to religion but certainly aggravated by it). and even aside from that, the vehicle for a problem is still a part of that problem, and one way to solve a problem is to eliminate all the vehicles through which it spreads itself.(sorry for the long comment)(no i'm not Canadian but i am British, so i still have to apologize for everything ;))\normalsize   & \cellcolor{green!27}Homophobia & \cellcolor{green!27}Sexual Identity - General & \cellcolor{green!27}1/214 & \cellcolor{green!27}0.467 \\  \hline
  \cellcolor{green!5}\small \@suziecreamcheaseyes i do get your point a bit better now. I guess the thing is, religions are such massive institutions that you are bound to have many good and many bad people within any major religion. And yes, there are examples of good, understanding people overcoming the barriers placed in front of them by religion to collaborate (i think the SESAME project is a nice example of this), but even here they are having to overcome barriers that are at least partially there because of religion, and it is rationality that is helping them to overcome these barriers (i know that was a specific example but you can use it as a general formula for intelligent, sensitive religious people who are having to overcome the barriers set in place by their own religion).My point was more that, while it certainly has the power to conjure some good out of \textbf{nothing}, religion also very definitely has the power to create much evil out of \textbf{nothing}. I guess our difference in view lies on how these two factors balance out?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/180 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small \@suziecreamchease(sorry for the long comment, but you have interesting points so i'd like to return as good as i can... and there's a treat for you if you make it to the end!) but then we get to the problem that, as an atheist, i see religion as \textbf{nothing} but a power structure constructed to let those at the top abuse the masses... As I sincerely believe none of the major prophets ever actually spoke to God or any angels (as they don't exist) that gives a few options:a) Jesus, Muhammed, Moses (if he existed, i'm fairly sure the others did at least) were plain barking mad, to the point of hallucinations and talking to things that didn't exist. I doubt this is the truth, as they were all coherent enough to create a major religion.b) They were benign and wished to tell white lies to help the world, but incredibly naive with little understanding of human nature and how their prophecies could be abused. Even if this is the truth, this is not a particularly desireable foundation for the moral guiding of the majority of people in the world todayc) They were malicious, cyncial and power hungry, and created the religions precisely because of the power structures and subordination that could lead on from this. I honestly wish it were not this way, but a few things lead me towards this. Firstly, all these religions were created back in the mists of distant past, where scientific knowledge was at a low and ease of deception was at a high. But there are a few younger "religions", which have grown since the ages of enlightenment. Namely Scientology and Mormonism. Now i know this is not a massive sample, but given that these are the only two religions that we've really been able to study the rise of, and they both clearly call into category c, that is already a hint at the true nature of what religion is.Then we go searching in the books for clues. Take the most popular book in the world (the Bible) and go right to the very beginning, the opening Genesis, one of the most famous stories to man, and a foundation of Christianity. Even if many Christians no longer believe it as literal truth, many love it for it's moral message. and that message? That we should live in blissful ignorance underneath an untouchable dictatorship, and that the original sin was to gain knowledge and leave the state of blissful ignorant submission under said dictator.Does that, one of the very founding moral stories of Judeo-Christian philosophy (I don't know Islam's genesis story but i suspect it is similar) not scream "Population control" to you?Hence I feel there actually is something wrong with the philosophy of religion, as it seems clear to me that, at their core (for the major monotheistic religions at least), they were created cynically and specifically to allow for oppression and dictatorship, whilst tricking people into being content with their "spirituality" and feeling good about themselves as subordinates so they dont rebel.P.S. If you read this far, go get yourself a cookie as you fucking deserve it ;) again, sorry for the long comment\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/541 & \cellcolor{green!27}0.185 \\  \hline
  \cellcolor{green!5}\small genius..fuck \textbf{racism}.of course but true\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small When were Jews deemed a \textbf{race}?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Well Jews are an \textbf{ethnic} group, and \textbf{race} and \textbf{ethnicity} often go hand-in-hand\normalsize   & \cellcolor{green!5}Ethnic, Ethnicity, Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/13 & \cellcolor{green!5}23.077 \\  \hline
  \cellcolor{green!27}\small No they don't. Greeks and German are ethnically different but are of the same race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small What I mean is, people often consider them the same thing, e.g. a person that's half British half American, despite being white will sometimes be called Mixed \textbf{race}, even if it's not entirely accurate, \textbf{Race} is about more than just skin colour you know.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@Bar Mayerovitcz What have those people back then got to do with the people who follow Judaism today? Basically \textbf{nothing}. Whatever happened 2,000 - plus years ago is irrelevant today.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Is Judaeism a \textbf{race} or a religion...? I always thought it was a religion. That's the only real link. I just fervently hope the current mess can be sorted out and the bloodshed stopped. There are idiots on both sides. I frankly cannot see the sense in Lord Sacks linking prejudice against Jews with the opprobrium that is more specifically aimed at the more extreme elements in Israel. He's clearly making a crude and transparent attempt to shut-down discussion. Counter-productive I would say.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small \@HeavensGremlin Judaism is a religion, but Jews are an ethnoreligious group, meaning an \textbf{ethnic} group that shares a \textbf{common} religion. It's entirely possible to be both Jewish and Atheist. Though Jews aren't a "\textbf{race}" factually speaking, but many people consider them to be. It's highly problematic because many people don't see a clear distinction between \textbf{race} (appearance) and \textbf{ethnicity} (ancestry) and will often confuse them.\normalsize   & \cellcolor{green!27}Common, Ethnic, Ethnicity, Race & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}5/65 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small When were they deemed a \textbf{race}? Why? Isn't a "people" a \textbf{race}?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@frank zappa's \textbf{pussy}Jews have made a big contribution to western society it's a shame the Muslims haven't made a similar contribution rather than trying to drag us back to the middle ages.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@frank zappa's \textbf{pussy}Yes without the number \textbf{zero} much of modern Physics would not be possible. They had to grasp the concept of 0 before science could advance.\normalsize   & \cellcolor{green!5}Zero, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Crazy, Mental, Dumb, Disabled, Blind, Spastic, Weird & \cellcolor{red!27}31 & \cellcolor{red!27}31/42604& \cellcolor{red!27}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Zero & \cellcolor{red!5}37 & \cellcolor{red!5}37/42604& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Race, Racism, Racist, Ethnic, Ethnicity & \cellcolor{red!27}105 & \cellcolor{red!27}105/42604& \cellcolor{red!27}0.25 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Nationalism, Nation, Alien, Refugee, Immigrant, doctors & \cellcolor{red!5}47 & \cellcolor{red!5}47/42604& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Jig, Black, African & \cellcolor{red!27}11 & \cellcolor{red!27}11/42604& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Terrorist & \cellcolor{red!5}26 & \cellcolor{red!5}26/42604& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}13 & \cellcolor{red!27}13/42604& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Nazi, Imperialist, Communist & \cellcolor{red!5}14 & \cellcolor{red!5}14/42604& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}6 & \cellcolor{red!27}6/42604& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Hag & \cellcolor{red!27}1 & \cellcolor{red!27}1/42604& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Fruit & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Thin & \cellcolor{red!27}2 & \cellcolor{red!27}2/42604& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}2 & \cellcolor{red!5}2/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman & \cellcolor{red!27}4 & \cellcolor{red!27}4/42604& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Jewish}  & \cellcolor{red!5}Shlomo & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - British}  & \cellcolor{red!27}Tan & \cellcolor{red!27}4 & \cellcolor{red!27}4/42604& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Roman Catholic}  & \cellcolor{red!27}Papist & \cellcolor{red!27}1 & \cellcolor{red!27}1/42604& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}Yellow, pussy & \cellcolor{red!27}3 & \cellcolor{red!27}3/42604& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Japanese}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Kraut, Herman & \cellcolor{red!27}6 & \cellcolor{red!27}6/42604& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}Homophobia & \cellcolor{red!5}1 & \cellcolor{red!5}1/42604& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Physical Identity - Physical (and Mental) Impairments;Age - Youngsters;Ethnicity - General;Nationality - General;Ethnicity - Black;Religious Identity - Muslim;Age - Over 65s; Ideological and Political Identity - General;Social Class - Working class;Ethnicity - Native-American;Gender - Female age and physical appearance;Sexual Identity - Male homosexuality;Physical Identity - Physical Features;Age - General;Gender - General;Religious Identity - Jewish;Nationality - British;Gender - Female sexuality;Religious Identity - Roman Catholic;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Chinese;Nationality - Japanese;Nationality - German;Sexual Identity - General;%.

\item The percentage of hate speech related words is 0.7511.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 322/718 occurences of hate speech related comments.\end{itemize}\end{document}