\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_234.json :}\newline \par\Large\textbf {Title: \large  Arab Superiority...Needs to Go }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small On the airport of Bahrain. On my way to somewhere. I was eating at the cafeteria then there was an Indian/brown boy moping the floor. And that random Arab guy with his thobe started screaming him and called Miskeen or something because he was on his way. That's all I could remember when I was 11 years \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small I've gotta admit that my parents are so \textbf{racist} too! And I can't really blame them cause it's integrated in the culture like you said.. They are 100 convinced that all other human beings aren't as loved by Allah as they are, for example they say Asians are dirty and disgusting cause they eat dogs and Indians are disgusting cause they worship cows... etc and each time I start arguing with them about such things they bash me off and start treating me as if I was a Kafira that I'm trying to be open-minded and it's against Allah's rules. I'm sick of trying to the point where I don't even want to argue anymore, I'll let them think the way they think and I feel blessed to not be ignorant about this.The bigger problem is the fact that the majority of Arabs are like this that's why we aren't developed and we still have wars and conflicts, I'm not optimistic about this cause the society is so messed up they don't teach love but rather hatred and division.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/180 & \cellcolor{green!5}0.556 \\  \hline
  \cellcolor{green!27}\small Thank god my grandfather is \textbf{African} if I was full Arab I would kms I'm probably like 80 and I would die to get rid of this 80 dirty Arab dna\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Good video to remind ourselves again that never treat people based on they re job or \textbf{nationality},we are all same,im as malaysian also see people that local here treat people in diffrent way just because thay do lower job and they come from other countries.\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small What's worse is that some arab cultures are \textbf{racist} on other arabs. For example, as a half Lebanese, half European, I had many Lebanese friends that had \textbf{racist} comments on other arab countries, let alone countries like India, china, \textbf{Paki}, \textbf{african} etc... and I know that most of them  don't even realize it is. I am not going to talk about into the \textbf{racism} from my other half because I guess everyone knows how \textbf{racism} fares in Europe.\normalsize   & \cellcolor{green!27}African, Paki, Racism, Racist & \cellcolor{green!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh), Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}6/78 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small LOL this is why I don't fuck with Arabs. They're \textbf{weird} af and have issues with themselves. Literally all non Arab Muslims, be it Turks, Somalis, Indonesians and or Indians are chill and down to earth. But the Arabs, can't stand them. It's not even like they have much going for them, only people that rate them are themselves 😭\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small You seem like a homosexual\normalsize   & \cellcolor{green!27}Homosexual & \cellcolor{green!27}Sexual Identity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small What about the unbearable Arab \textbf{racism}, terrorism, hatred towards indigenous people where these Arabs immigrated to. Like North \textbf{African} Berbers, Kurdish, Kubts..etc. They exploit Islam to forbid others from speaking their own languages and bring that Arab dirty culture of hatred and racism\normalsize   & \cellcolor{green!5}African, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small Ofcourse arabs will be \textbf{racist} when Islam is so arab centric. The majority of muslim are non arabs who pray and do everything in a foreign language\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Afghanistan, Pakistan(Northwest Indians) and Iran people's biggest mistake was Islam. If you are talking about superiority; Physical, beauty, intellectual. They leave the gulf arabs behind in everyway. I hope more non arab muslims would speak about this and don't hesitate to punch a \textbf{racist} arab right in his face. A \textbf{racist} arab needs to be humbled\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small What's a "\textbf{racist}"?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Arabs need to get over their superiority. So full of arrogance as if they are God's given gift to the world. Well guess what you Arabs, Islam came for whole of humanity not just for your \textbf{nation}.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Arabs and Muslims are big racists but it is just more subtle cause they think \textbf{racism} is only between 'Whites' and 'Blacks'\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small There's only one noble \textbf{race} and it's the white \textbf{race} 💪🏻\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Iridescent Eyez You guys are fkn \textbf{racist} and take Islam out of Afghanistan, Pakistan and Iran and you guys will have the biggest enemies\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Is notv it so funny that arabs are crying when they deal with \textbf{racism} and they are even \textbf{racist} to theirselves LMAO\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small In our Noble Qur'an, Allah [s.w.t] had already addressed the issue of 'racial superiority' in which THE CONTEXT is in the following verse:'Say, O you who are Jews [ applicable to any \textbf{race} ], if you [ verily ] claim that you are favoured  chosen by Allah with the exclusion of the rest of mankind, then [ why don't you ] desire death if you are indeed truthful.' [ Qur'an Surah Al-Jumu'ah: 62:6 ]For anyone who needs further explanation on why Allah [s.w.t] explicitly said '.... then [ why don't you ] desire death if you are indeed truthful' is because, in the minds of the 'Chosen People of Superiority,' they believe that just for being 'Chosen and Superior,' Allah [s.w.t] have already reserved Jannah [ i.e. paradise  heaven ] for them. Well, if they are indeed truthful, shouldn't they have the sincere desire to go straight to Jannah [ rather than stay in this world ] ?? They are the 'Chosen People of Superiority' after all. But nope! Never will they admit to this because they know they are arrogantly living in their own delusion of superiority which they themselves claimed. Even Allah [s.w.t] NEVER claimed anybody to be superior.LASTLY, FOR THE DELUDED 'CHOSEN PEOPLE OF SUPERIORITY,' ALL OF THE THINGS I'VE SAID ABOVE, ALL OF THE INFORMATION IS THERE IN THE NOBLE QUR'AN, HENCE ALL OF THIS ARE FROM ALLAH'S [ S.W.T ] WORD. SO DON'T BE ANGRY WITH ME. BE ANGRY TOWARDS ALLAH\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/251 & \cellcolor{green!27}0.797 \\  \hline
  \cellcolor{green!5}\small I don't like \textbf{nothing} about y'all because you guys are disrespectful the ones I met are... foreign arabs too the women geez die single asf maybe it's just humanity and how disgusting humanity is. Can't wait for the moshiak to come down already\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Islam is a \textbf{racist} religion\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small but those bad people is in All part's of the world not just Arabs,  your making the Arab evil and all others are Angel,  I'm Arab and I'm not like what you said nor my family and I'm full Arab Iraqi live in Arab country Jordan and we don't do All of that,  yes there is people like that but those people is in every single place on earth,  every \textbf{race} things their better than some others and all \textbf{ethnicity} have good and bad people.\normalsize   & \cellcolor{green!5}Ethnicity, Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}8/85 & \cellcolor{green!5}9.412 \\  \hline
  \cellcolor{green!27}\small Okay i relate to this soooooo much Subhi !!! i'm a tunisian girl living in France, i'm exposed to other cultures and other arabic friends aaaand that other day i was debating with my mom on the fact that possibly later, if i wanna marry a man coming from a village that is not my tunisian village, will they accept and she firmly said "NO"actually i understand her because her brother married a \textbf{woman} from another village and she's just a problem in our family but it's not a generality !! like not every person from other villages are badthen i told her "can i marry a man that is not from my village, or from tunisia but who is muslim, like a moroccan, a filippino or a malaysian man ?"she literally said "NO !" She told me "you won't eat the same food, you won't speak the same dialect or language, you won't have the same perspective of the world, your kids will be lost with their identity..."but i think if the man is a very devout man, who loves Allah, who is a good muslim, has a good family and has a good heart and above everything who loves me, then why should my parents reject him because he's not a tunisian man coming from my village ?????\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/224 & \cellcolor{green!27}0.446 \\  \hline
  \cellcolor{green!5}\small Subhi Taha am glad you talk about this but I feel like you only talk about this because your half Palestinians and you have faced \textbf{racism} yourself maybe but God knows best\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small No wonder Arab countries are the most intolerant and \textbf{racist} countries in the world.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Im not arab but grew up around them they r great people y is everyone in the comments being \textbf{racist} SMH!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Here in Saudi Arabia we're not \textbf{racist}. Just xenophobic to everyone who's not Saudi, including people from Arab countries.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@bflf jfldhsm They're \textbf{ethnicity} not that much, most are Arabised.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small What a condition, we Turks are \textbf{racist} to Arabs in Turkey.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small You are \textbf{racist} to poor Syrians who are turks.. we Saudis treat Turkish like shits.... we own half of your country\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small How about the prophet known hadeeth "there is no difference between an arab and ajami "non arab" except with takwa,  "how much you consider God, the one, and how much you are determent to stay a good human", that what takwa means.  It is in \textbf{quran} too when God said ( we have created you in nations and different tribes for you to meet and learn,  the most dignified among you are the ones who consider Allah more)  meaning who truly knew Allah, God,  and respect God teaching,  to be peacefull and wise in  dealing with other cultures.  And one must ask,  why God ask us to travel and learn about people from different \textbf{race} and culture.  Through knowing others we learn new tings about the creator, the universe rules through god's well, and the mysterious beuty in his creation. This also expanding peoples thinking.\normalsize   & \cellcolor{green!27}Quran, Race & \cellcolor{green!27}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!27}2/145 & \cellcolor{green!27}1.379 \\  \hline
  \cellcolor{green!5}\small I'm Nigerian. Before coming to the UAE, I thought the world of  Arabs. I've being here now for more than ten years. Its horrible guys. The \textbf{racism} and decrimination is so much. Being \textbf{black}, I'm looked down upon by everyone of every \textbf{race} including my own for being dark skinned. It amazes me how much Arabs here especially those from sham(Syria,Palestine,Lebanon, and Jordan) always ask people in the masjid to pray for their country as we are all Muslims but would not want to stand next to me for salah. Its very hypocritical of them. Many of them are raised this way and its so sad. Thanks for talking about this😭😭\normalsize   & \cellcolor{green!5}Black, Race, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/111 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small they aren't being \textbf{racist} only to other races even to other Arab people I'm from sudan and i can  tell that  Arab people from Asia think that they are better than Arab people from Africa.. sooo annoying + excuse my English\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small I agree with this! Thank you for promoting this mentality. Cultural superiority and this kind of "tribal identity" thing has been the cause of so much conflict. There's \textbf{nothing} wrong with being proud of your culture but you shouldn't let it make you look at others as below you. Also, not to offend anyone, but at the time before Islam, the ignorance was rampant among Arab tribes. The \textbf{Quran} literally calls it Jahiliyyah, or the Period of Ignorance/Paganism. Worshiping idols, burying their daughters alive, etc. The Prophet (s.a.w.) and the \textbf{Quran} were sent to correct them and "perfect their character (akhlaq)". So I think it's inaccurate for Arabs to feel superior for having Islam revealed to their people. It's a beautiful language and a beautiful culture, but again, not inherently better than everyone else.\normalsize   & \cellcolor{green!5}Nothing, Quran & \cellcolor{green!5}Age - Youngsters, Religious Identity - Muslim & \cellcolor{green!5}3/134 & \cellcolor{green!5}2.239 \\  \hline
  \cellcolor{green!27}\small Pride turned lucifer into satan it's the first sin commited in heaven. It's major trouble, it blinds us and offends others. All races struggle with it. Among blacks I grew up with for a time, they would attack the darker skinned among them. I had some trouble for being fair skinned. Among hispanics they idolize fair skin and talk among themselves about who's white in the family. It's everywhere. But I always thought it's might just be a preference most people have of what they admire. Not so much a \textbf{race} thing.I say that because men like Tom Cruise sell at the box office and all races come to see him or men and women like him.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/117 & \cellcolor{green!27}0.855 \\  \hline
  \cellcolor{green!5}\small whats up with people from Egypt, Morroco, Algeria and Palestine in the comment section who are claiming that they're not Arabs Lol !!! your first language is Arabic and your culture is influenced by the Arabic Culture for more than a thousand years. you don't have to be from the "ARABIAN PENINSULA" to be Arab Lol.  if you guys hiding your identity or trying to get rid of it because you want people to look at you different, or to get rid of all the stereo types that people have about us.... well guess what, they'll keep labeling you as the "ARAB MUSLIM VIOLENT" even tho you're not even Arab or you've \textbf{nothing} to do with all the shit that is going on in the middle east.i'm not trynna sound religious and shit, but instead of satisfying others, just be proud of your identity and your religion, and satisfy your God instead, and practice your religion. and keep in mind that other cultures will keep label and categorize you the same way, whether we are successful or not, violent or nonviolent, even smart or stupid, we're going to be looked at the same. so in this case SCREW OTHER PEOPLE AND SCREW THEIR VIEWS ABOUT US.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/207 & \cellcolor{green!5}0.483 \\  \hline
  \cellcolor{green!27}\small It all depend on money, ironically the lands of \textbf{Black} is the most richest\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small You should travel to ksa Kuwait uae and Qatar and see the real \textbf{racism} fascism and hatred for other human beings and discrimination for non Arab  Muslims and Allah is taking revenge they are already suffering and being destroyed for that please travel to gulf countries see that .\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small \@Bryan Cowo make your own search IGNORANT.the FIRST men WERE \textbf{black}.The \textbf{BLACK} skin doesn't become \textbf{BLACK} in hot weather.That it it called leucodermia the change of \textbf{BLACK} to white.Depigmentation occured during the ice \textbf{age} ,many WHITES migrated from THE STEPPES of Pakistan india like the ayran of iraq and IRAN.The majority of yours ancestors arrived 3000 years ago FROM the STEPPES.Let me remind you that in the Sahara the amazight or so called berbers migrated from THE STEPPES and had to dig galleries to protect themselves from the xrays of the sun.Moreover Nasser recognized that the Israelites were \textbf{BLACK} and ALSO that the ACTUAL EGYPTIANS are not the first Egyptians.The Egyptians are descendants of ham the dark people.The prophet Muhammad recognized himself the \textbf{BLACK} skin of moses.The real SEMITES ARE \textbf{BLACK} for most of them.The so called arabs today's are a mix of afrosians and 80 of Eurasians.Do u think that would have put first leycoderm or white in the dryest place in the world.Know your history after we will if yours lol is appropriated.The so slaves were there BEFORE because the Arabia was not TOUCHED by THE ice \textbf{age}.The ice \textbf{age} changed the color skin of all THE ANCIENT humans.Moreover the WHITES don t become \textbf{BLACK} tanned yes but not \textbf{BLACK} unless mixed with BLACKS or brown.You better of to get interested to nasser and the HEBREWS,and also origins of the WHITES skin\normalsize   & \cellcolor{green!27}Age, Black & \cellcolor{green!27}Age - General, Ethnicity - Black & \cellcolor{green!27}12/250 & \cellcolor{green!27}4.8 \\  \hline
  \cellcolor{green!5}\small Arabs are always \textbf{racist} especially to a \textbf{black} pple. i hate that mentality when i see muslim person that thinks that he/she is superior then \textbf{black} pple.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/27 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I hope you stand up for \textbf{black} people and \textbf{black} Muslims as well. As a Somali person, I've been Muslim my whole life but Arab people still act like they have more of a right to Islam than I do and I just think...my country is 99 percent Muslim lol\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small as a somali muslim, i've had more \textbf{racism} from arabs than white people lmao\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Ibrahim yeah that's exactly what I'm saying which is \textbf{dumb} bc we should as a community not be like that\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small You are 100 arab ,palestinians are not a different \textbf{nation} and definitely not a separate \textbf{race} from arabs, also does not matter where your people live it is never enough for you ,and you always need to whine about how much you oppressed.but I do agree about the \textbf{racism} problem in the arab world.\normalsize   & \cellcolor{green!5}Nation, Race, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small Well I have an \textbf{Indian} friend in uni, in the U.K, who lived in Saudi for most of her life before doing 2 years medical boarding school in India after and moving here. She said Saudi is the best and when she lived in India she loved it too but she didn't feel fully equal to her \textbf{Indian} friends because they view Islam and Arab culture as backwards, ugly and non-progressive or non-beneficial to the world compared to \textbf{Indian} culture. She had no Muslim friends, she truly didn't fit in anywhere, her own \textbf{ethnic} place or her own religions place. Her dad was a doctor and some of his lazy untalented colleagues (yes Arab) would ask them to do some of their shifts time to time with no pay, he would be depressed but can't say anything because human rights and equality exists less there. She said the people there seem to lack intelligence, more lazy, apparently their king or something doesn't even have his personal doctor as Saudi/Arab, he is south asian, which is \textbf{crazy}, as it shows he doesn't really believe in his people's capabilities. At least we work hard for our successes and stay humble, and not rely on natural resources or faking our way through. It's embarrassing. Like without it, I feel like everyone knows the country would still be the squalid undeveloped, medieval-minded place it was before. It saved them man it really did and those arabs (I know not all of them are like that) are undeserving of it in my honest opinion, it's a waste. Imagine all the good other countries that need help would've done with it. I hope they realise that and get off their high horse and come back down to reality, because outside the UAE etc they are \textbf{nothing}. It's pathetic and cringey. I've only met like two in my life, both good people and not fit the horrible descriptions people give them. I won't treat Arabs any different to anyone else if I ever meet any since my parents taught us some class and values. I know not to generalise. Thank Allah.\normalsize   & \cellcolor{green!27}Crazy, Ethnic, Indian, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/354 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small im arabian and not \textbf{racist} and i dont distinguish arab over non arab don't generalize all arab are \textbf{racist}!!!!!!!!!!!!!!!!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small It's wrong yes. But we Arabs have history and we proud I'm talking about Yemen Iraq Syria jordan Palestin sudan North africa we gone through hardship the rest are Jack shit like 100years \textbf{old} \textbf{racist} badion and the rest they be sitting there watching us go through shit etc like where were you yesterday\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small no matter if you an \textbf{african}, arab, europian, asian, american, etc.. we are all just HUMAN being. Love from Southeast Asian (Indonesia). Palestinewillbefree\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Ethnic Arabs look down on anybody who is Non Arab in \textbf{ethnicity} especially Jews\normalsize   & \cellcolor{green!27}Ethnic, Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small One of the ugliest thing ive heard arabs say is calling deeper skin people (\textbf{black}) SLAVES or a3bedoon. It shook my heart and my brain. I felt sad and angry at same time. And the worst part is they r not white either, but who cares?! Its just a skin color! 😶Saudia, kuwait, qatar, bahrein, uae are special kind of arabs who think they r even better than other arabs. Haha! Just few yeas ago, u were poor.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small as an \textbf{indian}, FRICKIN THANK YOU SO MUCH SUBHI\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Here's a place you might start in defeating your "arab superiority", realizing you're probably not "arab". Arabia is a place. If you weren't born there, which you weren't, then you're not an Arab. In your case, your ancestors weren't even Arab's. Palestinians are largely SEMITES, descended from biblical SHEM. They were invaded by Arabs and so there is some Arabic heritage there in Palestine. But just because you were born in Palestine doesn't mean you're descended from arabs. It's a big mix now of Arab offspring plus Semitic offspring that people's Palestine and I wouldn't doubt even that there's bunches of more people types in Palestine than just semites and arabs. If you want to do some research on it you might google this term: "Haplo-types of Palestine", then take each haplogroup you find listed and do additional research on each of those haplotypes and figure out what their migratory route was and what cultures each of those haplotypes were part and then you'll have a real good idea of where the people of Palestine are from.It's \textbf{weird} that Palestine is largely peopled by Semitic Muslims, ay? But it's true.Provisionally, I did the search and came up with these people types as all being part of the population of Palestine: Persians, Turkish, Macedonians (Hitites), Egyptians, Italians, East Africans, South Africans, Greeks, Spaniards, Portugese, French, Moroccans, Berbers... None of which are from The Arabian Peninsula. So the odds are greatest that you're no part Arab, even if you're born in Palestine, where for years the \textbf{lame} media has been pushing the narrative that there's a split between Arabs and Jews. It's just hokey nonsense being sold by the billionaires who like to create division to use in conquering people for the purpose of THIEVERY, stealing their property and the minerals that are buried in it.If you want to REALLY KNOW your heritage, get a DNA test, I recommend Family Tree DNA as they'll test for your genetic haplotype. Other "genetic testing facilities" make claims to know where you're from, which they can not possibly. So avoid any genetic test that is making claims about the region or place of your ancestry. You can know it if you know where your family is from, but they can't know it by testing your genes. So don't believe the fraud. But get your genes tested by a genetic testing facility that reports your HAPLOTYPE and then do the research on your own as to what MIGRATIONS your GENETIC HAPLOTYPE has endured. You should recognize in those \textbf{common} migrations someplace where you've been told your family is from.\normalsize   & \cellcolor{green!5}Common, Lame, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}3/436 & \cellcolor{green!5}0.688 \\  \hline
  \cellcolor{green!27}\small It's a huge problem not only treating others with superiority, but even with Islam there are subgroups who think they are better than others, even within families male and female,rich and poor, white and \textbf{black}!!  they just want to categorize everyone and yes we are as Muslims and Arabic speakers are more accountable, because we understand the language of Qura'an more effectively. It's actually a shameful attitude that we have to get over.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Lol, Why did you distinguished at the start between being arab and palestinian? there's no such thing as "palestinian \textbf{ethnicity}", you're an arab.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small True Muslim cannot be \textbf{racist} whether he/she is Arab or non Arab Prophet Mohamed صلى الله علية وسلم saysYou have one God (Allah) and one of you are descended from Adam and Adam was created from dust.And also said there is no difference between Arabic and not Arabic People and between white or \textbf{black} person, but except in piety.( believing in god and doing good deeds and to move away from evil deeds , Obedience to Allah ....)I'm from Saudi Arabia And I'm Arabic but when I see some uneducated \textbf{racist} Arabs, I feel so bad for them because they are committing big sin which is superiority of others If Allah gives you anything in this dunya, you must be thankful otherwise Allah may takes from you وَإِذْ تَأَذَّنَ رَبُّكُمْ لَئِنْ شَكَرْتُمْ لَأَزِيدَنَّكُمْ ۖ وَلَئِنْ كَفَرْتُمْ إِنَّ عَذَابِي لَشَدِيدٌ\textbf{QURAN} SURAH IBRAHIM 7 IN ENGLISH TRANSLATIONSAHIH INTERNATIONAL(14:7) And [remember] when your Lord proclaimed, ‘If you are grateful, I will surely increase you [in favor]; but if you deny, indeed, My punishment is severe.'\normalsize   & \cellcolor{green!27}Black, Quran, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!27}4/178 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small Some Arabs are \textbf{racist} among each other After the colonization of Europe and divided us to different countries, some Arabs see themselves are superior to other Arabs\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Problem is when they know they're doing it, \& you call them out on it \& they're all like oh yea whatever who cares kinda thing .. Unfortunately this issue (double thumbs up for addressing it) is beyond repair, but we gotta try I guess, it is what it is 🤷‍♀️ Also, I know I'm a year late with this post but hey ho\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small This is so misrepresenting to be honest. I've lived in several Arab countries and haven't seen that kind of superiority you're describing except in some gulf countries. Arabs are generally down to earth and easy going people and we don't think of ourselves as a \textbf{race} because we're not. The majority admires westerners/Asians as people of experience, knowledge, and science.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small This is so relatable. Some arabs but not all are \textbf{racist} to other Arabs. For example I'm Moroccan and I still get the \textbf{racism} just for being "Moroccan" It's unbelievable and \textbf{crazy}. This Superiority needs to end.\normalsize   & \cellcolor{green!27}Crazy, Racism, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/37 & \cellcolor{green!27}8.108 \\  \hline
  \cellcolor{green!5}\small Mesopotamian Kurd I don't know why they would do that, obviously some \textbf{racist} fools thinking they are superior but I know that some Lebanese don't even identify as Arab. But Abd doesn't mean \textbf{black} it means slave (Abdullah, Abd - Allah, slave of god)\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small You are quite obviously a fool, I don't care whether or not you share my belief, that doesn't mean you should go out and bash about it although. The West are becoming humane? When is disregarding the lives of fellow human for some political influence and oil considered humane? Who were the one's whom lied to us during the Arab revolt, dividing us into a dozen states, left the Hashemites when the Sauds invaded, is allowing Saudi Arabia to commit their crimes in Yemen, bombing Syria, invaded Iraq without any thought of what the fall of a government would mean; same thing with Libya! We are inhumane? But you are glad that Arabs are dying, and for what? When did we force the Indonesians or Malaysians to follow this belief? You think expanse comes without conflict, without violence? Any wrong we've did is \textbf{nothing} compared to that of the Europeans, for we weren't the one's that brewed two world wars. After oil, the Khalijees will not suffer, you are ignorant to the economic precautions they've taken to combat when the oil rates begins falling. By the way, a Jihadist is one that struggles, Jihad means to struggle or rise up against struggle. Your definition of Jihad is incorrect. Turks are Muslims just as us, you are ignorant and oblivious to what they  have done in Europe for the past 800 years.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/231 & \cellcolor{green!27}0.433 \\  \hline
  \cellcolor{green!5}\small Syrians, Iraqis, Sudanese and Afghans are not a people group. Syria and Iraq are created by the French and British, Syrians and Iraqi are Arab. Arabs roamed Al-Sham even before the \textbf{age} of the Khalifa. Assyrians are not Arab, they also live in these areas and are still around. Sudan is an Arabic word for land of the blacks, you are calling Arabs the bad guys by referring to people of an Arabic name? Hmmm... that doesn't make sense. Afghani is a \textbf{nationality} that in fact could refer to an Arab inhabiting the country (listen to the anthem) According to the anthem, Afgans include: Balochs, Uzbeks, Pashtuns, Hazaras, Turkmen, Tajik, Arabs, Gujjars, Nuristani, Brahuis, Qizilbash, Aimaqs, Pashais. North Africans include Amazigh and Copts. Amazigh are around, their culture is still vibrant, and they've adopted Islam. Copts are Christian Egyptians, they are around, and we live in harmony with them. Anyone who disturbs that peace is an extremist. East Africans are Sub-Saharan, we haven't engulfed any of their cultures, they are around, and in vast numbers. Somali do not call themselves Arabs, they practice Somali culture, they are proud Somali. Iranians are Iranians, Albanians are Albanians, Malays are Malay, Bosnians are Bosnians, Turkics are Turkics, and Indians are Indians. The fact that these countries and people speak their own language, wear their own clothes, have their own cuisines and even arts prove these people have their own culture. Death cult? Suicide is haram, hope you know that. Saudi Arabians are \textbf{fat}? That stereotype is reserved for another people. Slaves were around before we came into power, we did not create any of these disgusting things. Arabs never had any harem, this is the Turks, not us. The Atlantic Slave trade was the largest in history, not any Arab one.\normalsize   & \cellcolor{green!5}Age, Fat, Nationality & \cellcolor{green!5}Age - General, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}3/298 & \cellcolor{green!5}1.007 \\  \hline
  \cellcolor{green!27}\small Was Christianity spread without war? No, you can't have an expanding empire without war, that's not logical. ISIS actually does many haram things, suicide is haram, they don't follow the ten rules of war, rape is haram. Islam affects peoples cultures, even the Arabs cultures. Look at Arab culture before and after Islam, very different. It doesn't destroy them though, that's wrong. Europeans trying to solve problems in the Middle East? Many Europeans are angry at the \textbf{refugee} crisis, not because children are suffering or people are dying, but because it's flooding their countries. It's what happens when you lie to a people group, divide them into unnecessary nations, ignore other ethnicities (Kurds), implement weak puppet monarchs, and all for some oil. Look at what the French, British and Italy did in their colonies! Now they complain because those same people are coming back to bite them. Look at how the west messed up Afghanistan, you supported the Mujahadeen, and they then become Al-Qaeda. You know what happened from there. Yes... and according to you, only Khalijee are Arab, but all Khalijee are rich and can thank their oil for that. I completely agree with you when you say they depend on the west. Sauds are US puppets, and look at what they do to poor people in Yemen. Also, Jordan, Lebanon, Algeria, Tunisia and Morocco are all succeeding and good countries. Arabs actually weren't strict before Islam, they were barbaric tribal people who would steal from each other. But that was over a thousand years ago, we can't compare the people then to the people now. Yet look at what Sauds are doing in Yemen. Also, there is a difference between Salafism and Islam. Salafism is a strict interpretation of Islam, amd not Islam itself. Don't mistaken it for Islam. There are Arabs who still call blacks by this name, just as there are whites whom my refer to them as things that are even worse. I'm not sure where you get anything that Egyptians were slaves of the Arabs. Please go look at why Arabs were so easily able to take Egypt.\normalsize   & \cellcolor{green!27}Refugee & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/354 & \cellcolor{green!27}0.282 \\  \hline
  \cellcolor{green!5}\small No brother, you are wrong. Europeans have always been looking to us, there is a reason Britain left us with monarchs in Egypt and Iraq. They wanted to implement a government that leans in their favor, so while they don't directly administer these countries, we are still under their heavy influence. You are right, some of this stuff is self-imposed. It wasn't a Brit who poisoned Gamel Abdel Nasser, it was an Egyptian, our own people, betraying our beloved Gamel Abdel Nasser, just like that. But in fact, it is somewhat to blame of our colonizers, they were the one's who left us with these weak forms of government. Look what it cost us in the long run, if Britian would just mind their own business, none of this would have probably happened. ISIL had \textbf{nothing} to do with Europeans? Weren't European countries (UK and Poland) the ones whom aided in the Iraq invasion of 2003, the same invasion that took down it's government, and put ISIL in power. There are many prosperous Muslim nations. Tunisia, Algeria, Morocco, Saudi Arabia, the Emirates, Oman, Bahrain, Malaysia, Kuwait, Brunei, Qatar, Jordan, Lebanon, Turkey, Turkmenistan, Kazakhstan, Kyrgyzstan, Uzbekistan, Albania, Bosnia and Tajikistan. These countries are doing pretty well. Even countries like Iran are well developed, they just aren't doing too well politically and diplomatically. The Lebanese along with any other Arabs are well liked, whether we are Muslim or not. Syria is not in this state because of Islam. ISIL and Al-Qaeda are groups don't aren't part of the original reason for the war. It began because of conflict between the people and the government, initiated by the Arab spring. An utter failure in Egypt. The Assad regime is secular, not a theocracy.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/290 & \cellcolor{green!5}0.345 \\  \hline
  \cellcolor{green!27}\small Also, when you speak of Muhammad peace and blessings be upon him, you it seem as if he is of pedophile nature or was one to be which is completely incorrect. I don't know where you get this from, but it's wrong. Also, Muhammad peace and blessings be upon him was indeed a war leader, there's \textbf{nothing} wrong with that. He was simply a general, there is \textbf{nothing} wrong with any general. Under him, they conquered almost all of Arabia, not even Al-Sham, Anatolia, Persia, Maghreb, Egypt, Indus River, Central Asia, Caucasus or Spain. These expeditions were made after his by the Khalifa that came after him. There were supremacist leaders like the oppressive Umayyad's, but that doesn't mean all of Islam is bad, simply because some Muslim leaders were bad. It should be noted that the Muslim community themselves were very angry at Umayyad's, hence the Abbasid revolution and why they killed any Umayyad leader that they could find or get a hold of. It was the medival ages, of course things like this happened. Things like this happen even in the modern \textbf{age}. I would also like to say, that even before the Khalifa, there were Arabs in Al-Sham and the lands of Iraq (which is considered Al-Sham sometimes?)\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}3/211 & \cellcolor{green!27}1.422 \\  \hline
  \cellcolor{green!5}\small Sorry if reply in two comments, I'm using my phone and I can't see the entire comment at once. Being secular and Islamic doesn't mean anything, these countries are Muslim nonetheless and they embrace that. Brother, wjat you say about Khalijee is true, I don't disagree with you on this. Indeed they do depend on the west, but they are also diversifying their economies to brace for the price fall when oil begins becoming rare. Women are oppressed, although if your taking about Hijab I think you should know that majority Saudi men wear Kufiya a lot. I didn't know that they stopped cutting people's hands off, it's disgusting that they ever thought of doing so, something so barbaric, so uncivilized. I didn't beg anyone for help, no one is helping out the Egyptians, no one has helped out the Egyptians. I'm not putting the entire blame on the Brits, French or Italians, even the Spanish took some of the Arab world (*ahem ahem* western Sahara) but it wasn't us who implemented these weak monarchs. We were also lied to and left alone when the Sauds invaded Hejaz, allowing them to spread their strict interpretation of Islam. We couldn't stop them, what could we do? We can't fix our countries when they are run by foolish and horrible leader's. Name one good thing that Hosni Mubarak has ever done. Eastern Europe is better than us because they were able to successfully able to implement a good government system. We can't do that because we are confused and divided, we just keep starting conflicts, when will they stop? How do we even stop them? I mean, look at Iraq. In a couple years, probably a decade or so, it'll probably be better than it's ever been. Why? A good and stable government. But what do you expect us to do in Egypt? We've lost our chance to do anything, protesting won't help. I'm sure what really we could do here. Communism and dictatorship in both South and North Yemen have have severely damaged the two countries, the dictatorship still went on even into the newly unified Yemeni state. But then the Arab spring came along and just triggered a civil war, now what do they do? Europe is doing great because even before the two wars they were great major powers, those conflicts and wars have passed on. But we are still dealing with conflict, war, and bad government. Arab countries like Tunisia, Algeria and Morocco are okay because they managed to go on without conflict, but look at Libya, they are in a civil war, how do you expect them to develop in this situation. Syria, Libya, and Yemen are in civil war. Iraq and Lebanon just recently came out of a civil war. Lebanon and Jordan are dealing with a \textbf{refugee} crisis, they are not rich countries like Britian or Germany, they cannot as easily combat this.Egypt is dealing with a horrible military dictatorship. On top of this, Khalijee aren't even bothering even try to host any refugees.\normalsize   & \cellcolor{green!5}Refugee & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/510 & \cellcolor{green!5}0.196 \\  \hline
  \cellcolor{green!27}\small with the reason of ISIL requirements. There are many reasons why people join ISIL, instead of guessing as to why, you should instead do some actual research. Islam is not a male-dominated belief, it just seems like this because we are much more apparent. Enslave women? In what way? I don't know anyone who has married their cousins, but while it may be seen as taboo in the west, it's not in other places. I'm really not sure about here, because I don't know anyone who's married their cousin. Although a lot of what your saying is not factual information but simply assumptions, trying to make out of this and for some reason not bothering to do any proper research. Islam says \textbf{nothing} of joining ISIL, almost everything ISIL is doing is haram. Suicide is haram, rape is also haram. Slavery I don't believe is specifically haram, but Muhammad peace and blessings be upon him tried hard to abolish slavery. In fact, he married women to release them of their bonds. Please also do look up the 10 rules of warfare in Islam.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/183 & \cellcolor{green!27}0.546 \\  \hline
  \cellcolor{green!5}\small Turkey is not European, by shifting towards European values they are denying the traditions they have held for many years. And Arabs are the one's engulfing other's cultures? That's not why their prospering, astughfirallah they should completely remove of any form of prostitution, it's extremely disgusting. Whether you are Muslim or not, this should be \textbf{common} sense. Good on Tajikistan, there is no where saying women have to cover their heads, wear burqa's or hijabs. But they've done more then simply ban burqa's for cultural preservation, the president has done some things to restrict Muslim belief, and for a country that is over 90 muslim. Iran is still a Islamic theocracy where 99.99 of the population is Muslim, some Iranians teens becoming lax or atheists doesn't mean anything.  Actually, incest is very haram, tons of hadith (sunnah) is highly incorrect, and the prophet Muhammad peace and blessings be upon him never married his cousin, actually, it was his cousin which married his daughter. That's not incest, and his cousin was much younger then him. ISIL should know what their doing is haram, just because some hooligans running around in guns, spreading violence, claiming their doing good in the Islam, does not automatically mean that these people are following the rules and teachings of Islam. Like I said, tons of things their doing is haram. And do some research if you'd like to know as to why ISIL is a thing. ISIL was founded by a salafist in 1999, I'm pretty sure it had no actual significance or relevance at this point, but what put them in power was the fall of Saddam Hussein which basically collapsed the entire government making it easy for them to come to power. Like the Taliban and Al-Qaeda, they want to get rid of foreigners like the west but they are also trying to conquer as much as they can and impose their strict salafist beliefs. And no, it doesn't sexually repress anyone, its just says to keep from doing disgusting haram things.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/338 & \cellcolor{green!5}0.296 \\  \hline
  \cellcolor{green!27}\small Why should Turks stick to what? Ever since Turks have converted to Islam, they have kept their own traditions! Speak their own language! Did they not wave that one of those Turkic pole things during Ottoman times? Those stuff are not Arab! Prositution is a disgusting thing... can't believe you would even think of ever legalizing anywhere. Tajikistan government, not the people. Tajiks mostly got Islam from Persians not Arabs, same thing with Turks, actually, same thing with a lot of people. Albanians and Bosnians never got Islam from Arabs, but from Turks. Islam is not Arab culture, it's an Abrahamic religion like Judaism or Christianity. In Ramadan, Bangladesh does not feast on Arab food, they do so on Bengali food, same thing with Indonesia, Kazkhstan, Somalia, and literally every other non-Arab muslim country. No... Zaynab was no his cousin, never was. Also, where do you get that we marry later? I understand that we might marry in our mid-20s, but this isn't late not for us. Even so, this is mostly likely a modern thing. I do think I've been told that at the time of my great grandparents that people would marry around the \textbf{age} of 16 or 18. We do not care about \textbf{sex}, we are not \textbf{sex}-hungry, it is only necessary to have kids, \textbf{nothing} more, \textbf{nothing} less. They way you lay out this information, really really does sound like your assuming at least half of wjat your saying.\normalsize   & \cellcolor{green!27}Age, Nothing, Sex & \cellcolor{green!27}Age - General, Age - Youngsters, Gender - General & \cellcolor{green!27}4/243 & \cellcolor{green!27}1.646 \\  \hline
  \cellcolor{green!5}\small Islam is not going to force anyone to cover their head, that's an option. And by thinking that the Islamic influence is simply Arabic culture, your not making any sense. Stop assuming stuff, look at history! Even Arabs were changed by Islam, yes, their vocabulary may have some Arabic words or they may use the Arabic alphabet, but the English, Spanish, Dutch, French and Portuguese have forced many people to follow their religions, speak their languages and follow their traditions. Many natives were assimilated into the language of the Spaniards, and many Africans, American Natives and even some places in Asia were forced to convert to Christianity! French and English are highly spoken in Africa, much more then Arabic! Same thing with the Americas, but with Spanish instead of French. Vietnamese uses Latin alphabet, not Arabic, not their own, same thing with many \textbf{African} languages, and other East Asian countries. Lots of Central Asia was highly influenced by the Secularist \textbf{Communist} Rooskies, its not a surprise that the government in Tajikistan is how it is right now. Even today, they are heavily influenced by Rooskies. They use the Cyrillic alphabet, not Arabic. It's not Islam that plays fear, it's the Muslims. You are mistaking Salafist terriosts for Islam. So what if it's in Arabic? Most of our prophets are not Arabic, in fact, only two of our prophets were even Arab. Majority of them are Jews. It's in Arabic for fear of lost of meaning through translation or mistranslation, why are some Christian studies in Hebrew or Latin? Why are some Jewish studies in Hebrew? Arabic norms? I already said, it has \textbf{nothing} to do with Arabs, you think it does because Arabs instead follow these norms, and you mistaken that for Arabs following their own norms instead. How is prostitution disgusting? You don't find that a women is making a show of herself simply for money at all even somewhat disgusting? Or that someone would pay a women for her to show herself at all disgusting? Yes, to a degree it is disgusting. Were not afraid of it, you just shouldn't do it before your married, that's all. If you want to view it as a disease go ahead. But to add a few things:1. If your going to speak of the actions of the Muslims themselves or even "Muslims" blaming their doings on Islam, refer to the Ummah, not the Deen. 2. ISIL does not fulfil anything to do with Islam, they instead are attempting to grew an empire with themselves at its head. They are using Islam as a cover, and they are also trying to us force people into it, using it. It's not Islam, it's just hooligan terriosts. How can these people be considered Muslims if they don't even truly follow Islam? Think about it.3. Salafism or Wahabism is a extreme interpretation of Islam. Not Islam itself. Even Muslims themselves think sharia is a flawed system, laws made by people from centuries ago.\normalsize   & \cellcolor{green!5}African, Communist, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/500 & \cellcolor{green!5}0.6 \\  \hline
  \cellcolor{green!27}\small Also, please show proof, no where does it say that he was married to his cousin. Apparently it's now being a pervert to marry women who are a different \textbf{race}, religion and \textbf{age} to you. There are tons of women who marry men around even 20 years older than them, to this day. Same thing with \textbf{race}, and especially \textbf{race}, what's wrong with marrying someone that of a \textbf{race} different to you? Same thing with religion, although I don't remember him ever marrying someone of a different belief. Probably another fake hadith or something of such, and where does Islam allow \textbf{sex} war captives? Perhaps war captives, from a warrior fighting against you or something, but where does it ever say that \textbf{sex} slave war captives are okay?\normalsize   & \cellcolor{green!27}Age, Race, Sex & \cellcolor{green!27}Age - General, Ethnicity - General, Gender - General & \cellcolor{green!27}7/128 & \cellcolor{green!27}5.469 \\  \hline
  \cellcolor{green!5}\small No matter wt we say or do this \textbf{racism} wil continue..Bcoz it's something dt can't b fixed\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I am so glad that you have the same feeling as me.. That I wasn't \textbf{crazy}.. And it's harder because I am half Arab too .. And I really can't stand the fact that they think they are superior over everyone just because they are not Arabs or even not full Arabs!!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small If Arab \textbf{racist} to white that's ok because white abuse them. But they shouldn't be \textbf{racist} to \textbf{black}. Because \textbf{black} is only real human who is kind and not hurt you. But too bad , ones I see , like white who abuse them and not beautiful superior \textbf{black}.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}5/49 & \cellcolor{green!5}10.204 \\  \hline
  \cellcolor{green!27}\small All non \textbf{black} looking peoples cultures are \textbf{racist}. Weather it be in Asia, Europe, South America etc they all are mentally enslaved and wish to be as white as Anglo Saxon white and they see \textbf{black} color and anything close to it as bad.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/44 & \cellcolor{green!27}6.818 \\  \hline
  \cellcolor{green!5}\small Love this video.I also find this type of behaviour frm Arab people in social media. My Ammu did Hajj few years ago.She said that Arab people were nice with us because probably we r well off.but they behave very badly towards poor people. Which is surprising because Islam specifically teach us not to do this.and in the Last Sermon Hazrat Muhammad SWT told us Arabs r not better than Non Arabs,White is not better than Blacks.\textbf{Racism} doesnot make any sense specially frm Muslim background.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small man u spoke so right i had to login and like subscribe,,,,u shd visit saudi arabia  these guys are on another level of \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Arabs are \textbf{racist} and crap..superiority?..LOL..what did those ugly Arabs invent anyway?..\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small +Subhi Tahabro its thanks to Sykes-Picot Agreement, Arab Superiority is principle form of \textbf{Nationalism} or at least what Arabs took from European \textbf{Nationalism} and imitated it......We can only give Dua and change our conditions at heart to be better people.P.S. Im Bengali from NJ just to make sure noone misunderstands me, lol\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Every \textbf{race} have pride being that \textbf{race} , to pinpoint this as an only Arab phenomena is pretty unjustly inaccurate. Every human on the face of this earth have prideness circle that starts from within himself and gets bigger with time reaching to his family , \textbf{race} , beleifs , country untill the cirlce reach to the point that you cannot have pride of something and then you start to hate. The thing you're describing is more of being patriotic in my opinion and this is coming from a guy  who's 100 Arab. The prophet Muhammed pbuh told us : "There is no superiority for an Arab over a non-Arab, nor for a non-Arab over an Arab. Neither is the white superior over the \textbf{black}, noris the \textbf{black} superior over the white -- except by piety."So we follow.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}5/139 & \cellcolor{green!5}3.597 \\  \hline
  \cellcolor{green!27}\small LOL they feel superior because the \textbf{Quran} is in Arabic and Islam was first revealed to them? Do they know why the prophet pbuh was sent to them in the first place? I mean they were rapping goats and burying their daughters alive ffs how is that something to be proud of? 🙄\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small No I'm totally right in the middle with you. I'm half white ( mix of Spanish/east Europe) and half Palestinian, and I grew up right in the middle. I was too white to be on my arab family's side, and They couldn't connect; and I was too ' exotic' for the blond white kids, those nazis lol. And it is AN ABSOLUTE FACT about the superiority complex of Arabs. Especially over \textbf{black} people. It's disgusting. Which is why I'm pan-racist. I don't like anyone. Not even myself 😂😂😂😂 المسيح يحبك 😊\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Ok the only time I've seen \textbf{racism} between the Arabs is in saudi Arabia (not everyone but majority) because they think that if ur not Saudi ur basically trash... Personally I'm Egyptian and I think all the Arabs should set aside there differences and become one loving community again\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Arabs are \textbf{racist}! I'm arab, I know what I'm talking about. Well first I also said \textbf{racist} stuff but I didn't know that I'm being \textbf{racist} it was ok to say those stuff! And now I'm more grown up I opened my eyes and saw alot of \textbf{racism} specially the fact that I love Kpop and watch \textbf{Indian} movies sometimes( they are is alot of Kpopper and people who watch \textbf{Indian} movies but there is some people that are so funny to make up those jokes ), Let me tell you what people tell me in a joking way : " Oh you like those Chinese that can't see with their eyes! ""Their eyes are small!""How do you know the difference between them? " " They all look like girls! Don't they have beard? " "There names are all Chang Chang choo. drop a coin on the floor and the sound it makes is a new Chinese name " " There is no difference between Korean Chinese Japanese! They are all the same! " " Can I have their number so they can clean my house? You know all Filipinos are maids! Hahaha get the joke? "  No I Don't get the joke😑" Do they work for MacDonald? I have seen them cleaning the tables once! "Let's get to \textbf{Indian} : " I hate \textbf{Indian} the way they talk is so annoying! " " Do you think I'm \textbf{Indian} to not understand? " " Put lipstick on your forehead and walk with you hands together, You're \textbf{Indian} now! " " Just like \textbf{Indian}! So stupid! " " Look at him he doesn't understand anything hahaha just like our \textbf{indian} maid! " That's only 1 of what arabs say, And they don't think it's ok to say that! I wanna punch every stupid arab in the face!!! Ugh!!! How!!!! We have to educate about \textbf{Racism} in the arab world. Not all of Asian look the same and No \textbf{Indian} aren't stupid they are 100 smarter then your ass!!\normalsize   & \cellcolor{green!5}Indian, Racism, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}14/341 & \cellcolor{green!5}4.106 \\  \hline
  \cellcolor{green!27}\small I am Qatari (Arab) and i hate \textbf{racist} people... i treat all people the same way regardless of their \textbf{race} or status... if you are good person ill be good to you.... but i believe we can't do much to change the mind of \textbf{racist} people.. there will always be racists people around us... also if any other \textbf{race} got the privileges of the Arabs today... they probably gonna act the same way and maybe worse.... all human are prone to be arrogant and racisit when they get to have what makes them feel powerful over others... but when they are not as powerful they would act humble and shit (most of them)..  i am just being honest... it's a fucked up world and you can't do anything about it... just deal with it!\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}4/134 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small Thank you for talking about this! I'm North \textbf{African} (Algerian) and I can relate to this.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small My relatives and family say \textbf{racist} remarks and it just pisses me off Ive always told them to actually just stop because we're all human! I honestly love this video\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Uhh have you even read the \textbf{Quran}?...الْأَعْرَابُ أَشَدُّ كُفْرًا وَنِفَاقًا وَأَجْدَرُ أَلَّا يَعْلَمُوا حُدُودَ مَا أَنزَلَ اللهُ عَلَىٰ رَسُولِهِ... - التوبة The Arabs are the worst in disbelief and hypocrisy, and are most likely to not know the limits that God revealed to His Messenger... - Surah Tawbah \textbf{Nothing} to be proud of I'm afraid!\normalsize   & \cellcolor{green!5}Nothing, Quran & \cellcolor{green!5}Age - Youngsters, Religious Identity - Muslim & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small MashAllah beautifully said! As a revert, I find challenging to learn \textbf{Quran} since most of the explanations are in English and my  first language is Spanish. May Allah make it easy the path to knowledge, understanding and respect.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small we feel superior cause other ,muslims see us as superior we feel superior cause our men are men and our women are women we have \textbf{nothing} called \textbf{g\textbf{ay}} in the arabian desert we are feel superior cause we teached the EU peopol how to clean them self cause it was forbbiden for them to take shower we feel suprior for our history we are awsome that is all\normalsize   & \cellcolor{green!5}Gay, Nothing & \cellcolor{green!5}Age - Youngsters, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/68 & \cellcolor{green!5}4.412 \\  \hline
  \cellcolor{green!27}\small we are good looking as well not to white and not to \textbf{black} in between\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small أحمد الحويطي Shame \textbf{nobody} else believes it lol.The rest of the Muslim world laughs at you, we only value your language and the good Muslims among you. The rest of you are disposable.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small أحمد الحويطي 😂😂😂Only arabs LIKE YOU thought that arabs are superior. Yes I agree. SUPERIOR IN STUPIDITY.This dude doesn't even realized that he has just ACCUSED GOD ALMIGHTY OF BEING UNFAIR. Hence his superiority in his stupidity, right there. Sorry to break your delusion but GOD ALMIGHTY DOES NOT create this \textbf{race} to be superior than that \textbf{race}.Let me just say this to those arabs who are supposedly "SUPERIOR" that it's PERFECTLY O.K. to say "I'm Arab and proud" just like anybody and everybody else should be proud of whatever their racial background is. But it's totally a massive difference to say "my \textbf{race} is superior than other races."\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/112 & \cellcolor{green!27}2.679 \\  \hline
  \cellcolor{green!5}\small M A but i don't agree with people who lighten their skin, because it's their features and face structure which defines your \textbf{ethnicity}. Most of Arabs to me look more natural in their own skin shade, when they lighten it up, they don't look natural and it's a fake look. Facial features are very important in that, not only colors. I've see fair Arabs on the internet and they have Arabic features despite their fair complexion. I just don't think anyone should change their skin tone, they look good in their natural way.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small Being \textbf{black} will not prevent hazrat Bilal(r.a) from going to heaven and being an Arab will not prevent  Abu Jahl from going to HELL!THEREFORE,BE HUMBLE! Because if u r not humble then u r clearly going against the teachings of our beloved Prophet (s.a.w)!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Please admit next to white-ish looking people, latinas, Europeans and many many more that little delusional  mentality of yours goes down the drain 😂 oh how you bumlick whites, oh how you don't see that we all see it among you 😂. You think arabs are superior? Keep dreaming, I'm not \textbf{black} but even next to a \textbf{black} man you won't say shit.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small So If a \textbf{black} person said (White people are ugly and evil) this is not \textbf{racist}, and if \textbf{Indian} said (I'm \textbf{Indian} and I'm proud, and the Indians are the best) this is not \textbf{racist},But if the Arab said (I am an Arab and I am proud) .. these become \textbf{racist} ??The funny thing is that most of these hypocrites who claim that Arabs are \textbf{racist}, when you read his comments you will find that he is writing \textbf{racist} comments against the Arabs, I do not say that there are no \textbf{racist} Arabs, but Arabs compared to other peoples are less \textbf{racist}, ... See how the white police in America shoot at \textbf{black} people, see how rich Indians are treat poor Indians like a shit, Pakistanis think themselves better than Indians, and Indians themselves better than blacks,..when the \textbf{Black} people got weapons and power They killed and exterminated all Arab Citizens in Zanzibar, they did not  even mercy the women and children,... the Arabs are allowed to blacks and Indians to live in the Arabian Peninsula, and give them citizenship in the era of King Faisal.\normalsize   & \cellcolor{green!27}Black, Indian, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}12/188 & \cellcolor{green!27}6.383 \\  \hline
  \cellcolor{green!5}\small You are using the same language the Islamophobic propaganda is using but this time with Arabs. I'm not saying all muslims are bad some of them are really nice bla bla .. it's obvious and need not to be pointed out for some cultures without the others. The disaster that the muslim communities face today is \textbf{nationalism} which is found each and everywhere, nationalists in Pakistan believe in Pakistani superiority and so do the arab nationalists. Therefore \textbf{Nationalism} in Islam is among the worst haram things to follow. Cut your nonsense ..\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/93 & \cellcolor{green!5}2.151 \\  \hline
  \cellcolor{green!27}\small racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Prophet Muhammad  sallallaahu  `alayhi  wa  sallam ( may  Allah exalt his mention ) said: "O mankind, your Lord is One and your father is one. You all descended from Aadam, and Aadam was created from earth. He is most honored among you in the sight of God who is most upright. No Arab is superior to a non-Arab, no \textbf{colored} person to a white person, or a white person to a \textbf{colored} person except by Taqwa (piety)."\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small To all the people in the comments who are bashing Saudis or Iraqis or Egyptians PLEASE STOP!! This video is for awareness not for bashing. We are an Ummah, if we have a problem we will solve it TOGETHER, but we need to remain united as MUSLIMS. All races have \textbf{racism} and inequality issues, no surprise there. So instead of bashing one \textbf{race}, and quite frankly being just as \textbf{racist}.. Just watch the video and agree. We all have suffered \textbf{racism} at one point or another so we get that everyone has had bad experiences but people don't make other Arab brothers and sisters feel unwelcome or harassed. South-Asians, Asians, Arabs and all the other nations do have problems involving \textbf{racism}. Don't take one horrible person as an example and paint an entire \textbf{race}, religion or \textbf{nation} with hatred.\normalsize   & \cellcolor{green!27}Nation, Race, Racism, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}7/139 & \cellcolor{green!27}5.036 \\  \hline
  \cellcolor{green!5}\small My family  grew up in the \textbf{racist} environment where \textbf{racist} comments are normalized in the house hold. When I try to teach them, I litearly  ge attacked for having \textbf{common} sense, and get called disrespectful lmfao. Thank you sm for this\normalsize   & \cellcolor{green!5}Common, Racist & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}3/41 & \cellcolor{green!5}7.317 \\  \hline
  \cellcolor{green!27}\small ShaguftaF2000 true. I'm American Moroccan and I've been living on KSA for the last 10 years of my life.. (i came here when I was 8yrs) and even tho I'm supposedly Arab , Saudis seem to think that they're better than everyone else. Whether Arab or not. A little too \textbf{racist}. Hell, the first thing they ask is "are you Saudi?" . God help us all. ... We're all humans and \textbf{nothing} makes no one better than anyone except for what they do. Whether they do good or bad. \textbf{Racism} and discrimination needs to stop. It is the main problem of our world today. It needs to stop\normalsize   & \cellcolor{green!27}Nothing, Racism, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/108 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I love when Arabs try to use \textbf{Quran} as a means of being "like I'm superior because arabic is the language of the \textbf{Quran}" but they only  have Surah Fatiha and Surah Nas memorized. 😭\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small This is so true, Arabs are so \textbf{racist}, they literally think they're better than everyone else, it's crazy\normalsize   & \cellcolor{green!27}Crazy, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I'm arab and i'm not \textbf{racist}. I don't think i'm better than people of other races.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The only solution to this disgusting Arab \textbf{racism} is putting Indians and others who speak fluent Arabic on television as hosts  newsreaders. Pretty much like in UK or US.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small No, the \textbf{Quran} itself is the result of this just like in Jews. I find that the Jews and Muslim Arabs hate each other for the same reason. Because they think they deserve everything since they are the chosen one. The \textbf{Quran} gives these verses where it's seen as it's not \textbf{racist} or anything but it gives that idea deep down in the head as an example in a verse where it's said that god wrote made \textbf{Quran} Arabic so we can understand and be smart. I find this is very disrespectful as a non Arab who learned Arabic and the verse does exist you can search (thankfully learning Arabic  allowed me to see the truth behind all of the good glazed things that Arabs and their religion claim) so it's pretty normal why a lot of the Arabs think they are superior.\normalsize   & \cellcolor{green!5}Quran, Racist & \cellcolor{green!5}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}4/143 & \cellcolor{green!5}2.797 \\  \hline
  \cellcolor{green!27}\small May Allah make us stop be \textbf{racist} ...i had Many \textbf{racist} redmark on me in Sweden by Swedish people but i proud to have another \textbf{race} but i still Will respect Swedish people ,as our prophet Muhammed pbh teach us to be kind\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/43 & \cellcolor{green!27}6.977 \\  \hline
  \cellcolor{green!5}\small I'm not really arab but one of my native languages is arabic... although its kinda fake arabic xD I'm moroccan berber so we speak a mixture of tamazight, spanish, french and arabic. My arabic is \textbf{weird} though xD not at all like the qu'ran but it does help to read xD\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small This is actually very \textbf{common} in South Asian culture too. Even Indians consider other Indians to be inferior if they are dark skinned (Not all, but many). Desi people have a problem when white people or even arabs be \textbf{racist} to them but they don't realise how hypocritical they are because ...Indians are pretty \textbf{racist} to their own people. Lmaooo\normalsize   & \cellcolor{green!27}Common, Racist & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}3/60 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Every \textbf{race} think they are most Superior.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small hey subhi!  I know you are passionate about Islam but have you read the Bible and compared it to the \textbf{Quran}? I think you should read the Bible and study it. Islam was created by the Vatican Catholic Church\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Anyone has this issue of \textbf{racism} in should repent. Pride destroys a person just how Allah cursed Iblis and took away his status as the leader of the angles. Iblis thought he was better so he didn't prostrate to Adam. At the end he harmed himself and turned into a shaitan. I think these people are really turning many people away from Islam  because of how they treat others. Please try to correct yourselves and follow the prophet (s) accordingly. 'There is no difference between an Arab and a non Arabs except piety' لا فرق بين عربي ولا أعجمي الا بالتقوى Why Arabs in particular are imitating the Jewish. In order to be Jewish you need to have Jewish blood. Because God ‘chose' them. Unfortunately, they understood the meaning wrong. God chose them at the time because of their faith. I feel bad when for the muslims when they keep on complaining about the \textbf{racism} in the West. I would recommend to resolve the issue of \textbf{racism} in Middle East then we can have the privilege to talk and correct other nations.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/182 & \cellcolor{green!5}1.648 \\  \hline
  \cellcolor{green!27}\small As one who became a Muslim in 1999 at \textbf{age} 39, I didn't run into that problem in my community. However, I have seen it. In a few cases, I saw converts/reverts leave as a result. But, I really love the Arab brothers and sisters in my community.  InshaAllah, keep making good videos like this one!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Totally subscribed, love the video, You are absolutely right and very wise! I'm American but my ex husband is Saudi, And my children are half Saudi. Not all saudis are bad or horrible but from my personal experience I've had more of the bad hand. At first things were lovely and picture perfect, and I've had a lot of Saudi friends and no offense but I've noticed the ones from the eastern providence such as Safwa and especially Al qatif come off as if they are better, richer, and more important, arrogant. They flash their expensive items and belongings, money, designer wear, and act as if you are beneath them. It's disgusting and wrong! And the way men treat \textbf{woman} is as if they are meat. A lot of saudis I've witnessed have wives back home or fiancés and they come here have \textbf{sex} with multiple girls and have babies leaving them behind after promising their mothers the world, false hope, and partying, drinking, drugs, and it goes on and on. It breaks my heart that the mothers and women wives back in Saudi have no clue. Again I'm not \textbf{racist}, I mean come on my children are Saudi, and I love the Arab  Saudi culture and everything about it, but I can't stand others who are arrogant, liars, and come off as if you are \textbf{nothing} but trash beneath them. There is good and bad people all over. Just be wise and take care of yourself, And of course trust your instincts. I love arabs and the cultures. And I will always defend arabs and Muslims. Inshallah the world will wake up one day and become a better uniting place. Much love.\normalsize   & \cellcolor{green!5}Nothing, Racist, Sex, Woman & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!5}4/284 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Stephanie Almulla thanks for sharing, I had a feeling many had wives back home and only wanted non-Arab women for \textbf{sex} most times.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small im half arab but \textbf{black} and I hear what arabs say about me when they think i dont understand so I can understand thats why i never claim being half I just say im \textbf{black} and proud\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Asali Balali your mother is \textbf{black} or your father?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Good, don't claim to be Arab because you are NOT an Arab but a \textbf{Black} \textbf{African}. You will never be Arab..\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small \@nina a who wants to be a arab get the sand out of your ass eyes  bitch qaxaba.you waba be white so mutch weak ass arab bitch I am a muslim fuck a rasict arab a grew up in Europe I have more respect for the Europeans than the jahiil badouin from the desert.you wher \textbf{nothing} g till allah brought prophet mohamed and\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Thank you! I am half Jordanian half Danish and I grew up in a Somali  Arabic community. I remember that there was this huge Eid party and me and my siblings were playing on the bouncy castles when other children (Much older than us, they were like 14) would threaten us. They'd say things like ''You're not real Muslims, you're Danes! You can't be here! I bet you brought your pig meat as well!'' (This was in the Arabic Eid party, our mosques were based on \textbf{ethnicity} which is just horrible) This made me very sad, and soon enough i began throwing away aspects of my Danish culture. I didn't grow up with Arabic as my second language like all of the other kids, so i started to say things wrong, Grammarly incorrect, just so they'd see me as one of their own. My friend also talked very bad about Somalis and Danes, and she'd very often talk down to me.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/162 & \cellcolor{green!5}0.617 \\  \hline
  \cellcolor{green!27}\small This is AMAZING!! I have tried for years to get my parents to understand that even though they aren't openly \textbf{racist} they are subconsciously \textbf{racist} and they need to acknowledge it! Thank you I will show them this!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I agree, i'm Yemeni and my family is quite \textbf{racist} especially towards the \textbf{black} \textbf{race}. Thank god I was born into this generation so I can tell them that what they're saying is wrong and make sure my mentality isn't like my family's.\normalsize   & \cellcolor{green!5}Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small \@Shalj cuz they are not pure yemeni thats why.... but we live together .. there are alot of yemeni somalian \textbf{african} and ethiopians in yemen\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Shalj Yemenis are not blacks!  the true Yemenis who represent most are white or tanned skin, we have \textbf{nothing} to do with \textbf{African} blacks\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Borame hargeisa laascanood burco berbera cergabo um no😂😂😂most Yemenis are \textbf{tan} although they're r some dark ones. At the same time there's some Yemenis who can easlit pass as European\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small On point, but let's be real it's the way they are taught Islam and they are the better chosen \textbf{race} by god. Shame\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I have been to Iraq twice, and to think at all that those people are "superior" to any other culture (not \textbf{race}) since anthropologically we humans are the same genetically, is absolutely laughable after seeing asses wiped with bare hand (left) and flung to the ground, and a shoddy attempt to use toilet paper (the whole unraveled roll used to wipe shit from ass all at once and left for everyone to see). Two Iraqi dudes constantly getting caught having \textbf{sex} in PORTA-POTTYs, (always different people). Oh and lest I forget the Iraqi guy who kept having diarrhea in the shower!) AHHHHHHHHHHHH!!!!!!! Yea true story folks! Oh, sooooo superior...\normalsize   & \cellcolor{green!27}Race, Sex & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/109 & \cellcolor{green!27}1.835 \\  \hline
  \cellcolor{green!5}\small Calling someone \textbf{racist} is \textbf{old}, calling your own people \textbf{racist} is just cringe, pushing \textbf{ethnicity} of \textbf{old} occupiers upon your people is worst than all of the above.\normalsize   & \cellcolor{green!5}Ethnicity, Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}5/28 & \cellcolor{green!5}17.857 \\  \hline
  \cellcolor{green!27}\small THANK YOU for this video! You make me wanna continue going against all the \textbf{racist} comments arabs can make. Sometimes arabs are even racists towards other arabic countries, that IS SO MESSED UP\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Most Arabs are racists in my original country. They forget that Islam didn't start with a pure \textbf{race}. I am fed up with all the muslim community because of how insanely ignorant they are. If they don't act civil and see Allah, I don't have place for them in my life. I am tired of speaking about humanity and respect. My mother used to swear and be nasty just because she think she can. V.V you can't fix people who are fixated to be this. I can only apologize for her actions and that's it. You can't spend your life trying to change a stone! A lot of people are stone heads and they have blocked ears .. speaking to them is a waste of energy. Also it's not about \textbf{racism} for color or country but also religion and beliefs .. it's the full package\normalsize   & \cellcolor{green!5}Race, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/145 & \cellcolor{green!5}1.379 \\  \hline
  \cellcolor{green!27}\small TARoOoK100 Flag is not a \textbf{race} and my folk is older than this flag, you failed\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Lmao, sorry but the Palestinian flag is a pan-Arab color flag.. \textbf{black} , white, green, and \textbf{r\textbf{ed}}. Which is why your case is fucking hilarious to me. I'll let you live your fantasy now... bye 😂\normalsize   & \cellcolor{green!5}Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small TARoOoK100 Your fantasy tells you that you can claim other nations for you. Color is not a \textbf{race}, Egyptians had different flag and they spak arabic, so did other nations, where is your crappy argument now?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@An Naeem Bin An Nahari…Mixing isn't wrong. I'm ONLY talking about the fact that 99 of Lebanese Arabs and Syrian Arabs are NOT mixed even the ones with white skin and light \textbf{colored} eyes are real Middle Eastern Northern Arabs. Real Arabs have always had white skin and olive skin color NOT brown skin as people are brainwashed to think. Saudis and Yemenis are mixed people NOT real Arabs. And real Arabs come from Prophet Abraham's DNA like most Semitic Caucasians and prophet Abraham came from the Arab Levant from Syria and Iraq NOT Yemen or Saudi Arabia...People can mix but DO NOT spread false lies about Levantine Arabs and Syrian Arabs. Syrian Arabs and Lebanese Arabs is how real Arabs from thousands of years ago looked like. Arabs never looked like Gulf people such as Saudis and Yemenis or Kuwaitis who are all mixed with Indians and Pakistanis from South Asia.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/152 & \cellcolor{green!5}0.658 \\  \hline
  \cellcolor{green!27}\small Perfectly said. We need another one about \textbf{racism} between Arabs. It is worse\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small A lot of times we think peoples are \textbf{racist} or arrogant etc,  but most often its our own inferiority complex and not another's superiority complex.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small I️ don't get what's superior about Arabs, you have no ancient history, your language is ugly, and let's be honest you aren't very attractive people either (I️ know that's subjective but still).. lastly \textbf{nothing} pleasant about your culture.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Thank you so much for talking about this brother Subhi. A lot of us "muslims"  are infested with \textbf{racist},nationalist superiority complexes.Muslim I suppose don't read the \textbf{Quran} anymore. Read and COMPREHEND guys.  May the most Merciful bestow wisdom,understanding peace and love in the Muslim community and every other community in the world. Ameen.\normalsize   & \cellcolor{green!5}Quran, Racist & \cellcolor{green!5}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small Majority of Arabs are at higher level of \textbf{racism}.  They believe that it's only them whom can understand Islam well then non-arabs\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small superiority complex is a \textbf{mental} disorder that needs to be treated with medication or Ruqyah. As a muslim i know its the work of satan, remember when he refused to bow down to Adam (AS) because according to iblis he was better than Adam (AS). Look where his pride brought him... We should all take notes and be careful not to follow his footsteps.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Lool he says Arab weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Slightly superior??? No offense but I really tried to be friendly and open with arabs but they are soooo concieted, \textbf{racist} and think theyre shit don't stink... they are even \textbf{racist} within themselves.. its amazing.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Sakineh Anikeh it's true. They are \textbf{racist} against the Arabs from North Africa and Levantines saying that we are "less" Arab like it doesn't really benefit me to be Arab. My country is known for its ancient culture not for being Arab\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Nadine Zacki never heard anything like that... some say north Africans are arabized with some Arabs living there, but not the Levant, they probably say that about the Lebanese because there annoying af with al that "we wuz Phoenicians an shiiiet".most of the time it's the Christian Levantines that say we are not Arabs, and were not dying for them to be one of us... we honestly don't care :/but Syria, Jordan, southern Palestine have been territories where the most prominent pre Islamic arab kingdoms rose up.(Qedar, Tanukh, Nabatea, Iturea, Emesa, Araba, Osroene, Palmyra, Ghassan, Lakhm)Not to even mention the 4th largest empire and the 1st largest arab/Muslims empire in history, the Umayyads, \textbf{witch} were mostly made up of levantine Arabs, also the largest pre Islamic arab empire, the Palmyran empire.we have a history in the Levant and every arab knows that.\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/148 & \cellcolor{green!5}0.676 \\  \hline
  \cellcolor{green!27}\small ehsan iq it's not "some" people who say north Africans are Arabized. We actually are Arabized it's true like Egypt for example. Egyptians are a different \textbf{race} of people than Arabs. About the Levantines no they have actually been Arabized, too because the Phonecian culture took place before the Islamic culture and Arabs at that time were only tribes with no specific location.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Nadine Zackuhm... i meant "some" Arabs believe that north Africans are arabized and not Arabs.but most of us don't care.and i agree that most north Africans are arabized, i never said i didn't, but it's not the same case in the Levant.the majority of the Levant are of arab origins and the Arabs of the Levant belong to tribes.there are non Arabs living in the Levant like some Maronites (as there are also \textbf{ethnic} arab tribes like Shemor who are part of the Maronite community and many other), arameans, Assyrians, Armenians, kurds, Turks etc.but they are a minority :).and Phoenicians inhabited coastal cities in western Lebanon, and the Tartus Governorate region in Syria.and that's it!, they are Lebanese and Lebanese only.and they weren't any "Phoenicians" when the Arabs conquered the Levant, they only saw Arabs, Greeks, Romans, and latinized Semites like the arameans and a minority of Assyrians.and both Palestinians and  Jordanians are of Nabatean arab origins :).\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/168 & \cellcolor{green!5}0.595 \\  \hline
  \cellcolor{green!27}\small I think he was joking when he said "slightly"! 😂 I'm an Arab and I can say that \textbf{racism} is now even worse! ☺ It is just now people are even more detached from Allah. But, there is always good and bad.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Not all Arabs are \textbf{racist} 🤦🏻‍♀️\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Couple of years ago, I met this \textbf{chick} who was "dating" a Jordanian guy.  She was Colombian and Puerto Rican. They were together for about 3 years.  As soon as it came time for him to find a wife, his parents openly told him to "dump the Spanish girl." And he did! He just got married to an Arab girl and dropped my friend without warning! He just stopped talking to her and months later, she ran into him at a fucking diner eating with his wife. When she confronted him, he casually told his wife "oh, she's just some Spanish \textbf{chick} I used to hang out with."  That's fucked up.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/111 & \cellcolor{green!27}1.802 \\  \hline
  \cellcolor{green!5}\small I'm Palestinian and I'm not Arab and I'm not proud if it even I don't look Arab even I don't sound like Arab even I removed Islam of my religion because it was by forcing and beating up to become moslim and this talking about him self he is Arab he doesn't know what he saying only some \textbf{racism} it's true but about he being Arab he is confusing him self between Arab and moslem he thinks because he speak Arabic with his own accent by the way and he is moslem and maybe live in Arab countries think he is Arab ,, u know don't mention he maybe having his education and money from Arab Bs egyptions and morrcoans and Sudanese and somalies saying they are Arabs please people see them in GCC or other countries ,, it just they are heavily Arabs to us so we don't ban them to go to GCC countries and make money\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/159 & \cellcolor{green!5}0.629 \\  \hline
  \cellcolor{green!27}\small Most "Arabs" aren't even "Arabs" anyway. Unless you're from the Arabian Peninsula, you aren't Arab. People speak Arabic now and have parts of the culture, because they too were conquered by Arabs centuries ago, yet they seem to forget that fact. Palestinians are a mixture of the original Semitic peoples of the Levant who were living there long before Arab conquest, and non-Mideast ancestry from Europe, Asia, and sometimes Africa. Most of the people in my family look like \textbf{nothing} like Arabs anyway, and the ones that do, well it's because they simply look Semitic like their Semitic ancestors of the Levant did thousands of years ago. It's not like Saudis or Gulf Arabs would be very accepting of us anyway, so why kiss their asses and wish to be one of them?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/133 & \cellcolor{green!27}0.752 \\  \hline
  \cellcolor{green!5}\small Common sense\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Assalamu Allaykum,Not a person likely to comment much but I wanted to let you know that I really appreciate this video. This is absolutely true but I completely agree that it is a subconscious thing or unfortunately openly \textbf{racist}. I am a Pakistani \textbf{woman}, born in Hong Kong and raised in England. I am so open to different races and cultures as I have been around different people from different backgrounds. Unfortunately, its sad to know people can be cruel because of your heritage and background. Mashallah, thank you for creating a video that is respectful and worded perfectly. May Allah reward you for your good intentions and forgive you for your sins. In Sha Allah, I hope for the best for you.Wallakum Assalam.\normalsize   & \cellcolor{green!27}Racist, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/126 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small its good to see tht u thought so.. thru out my life ive meet certain people who have arab blood in their generations and they r so proud of it..bragging it.. and making me thought so too.. cuz in my perspective i see they've nice face features, pretty eyes,pretty nose,light skin colour.. their culture and all tht.. when i saw this im kinda owh u r right..thts \textbf{racist} actually..sigh..\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small I am Arab and kind of \textbf{racist}, but not against everybody. Also \textbf{racist} against other kinds of Arabs (Like Egyptians and Khalijis). My superiority complex has \textbf{nothing} to do with religion as I'm an atheist. But the fact that all these people have their asses up praying to our god means we cucked the shit out of them. So, its mostly about the fact that we have an \textbf{old} history (Mesopotamia, Egypt...) and some of the greatest empires (Umayyad, Abbasid).... As an Arab male I find great role models for masculinity as well. Now look at you combining islamic farts and western \textbf{libtard} bullshit to cope with your asian \textbf{beta male} complex.\normalsize   & \cellcolor{green!27}Beta male, Libtard, Nothing, Old, Racist & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Age - Youngsters, Ethnicity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}6/112 & \cellcolor{green!27}5.357 \\  \hline
  \cellcolor{green!5}\small I have many things i want to say but got no energy to type everything out BUT I'll say one thing an that is we should fight against the evil thoughts that comes to our mind concerning other people's culture,\textbf{race}, and beliefs. I wont lie, at times i wanna say what is on my mind (not a nice thing) to those \textbf{racist} people who minimize the struggles my people went through and still are but in a different form but than i hold myself back and say no no no, no matter who they are and what they say let them be safe from your hands and mouth. the worst thing you can do as a Muslim is by you treating your fellow human beings that Allah created UNJUSTLY. It sucks you good deed out. Ain't worth it.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/138 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Arabs and North Africans are by far the most \textbf{racist} Muslim \textbf{ethnic} group out there, especially ok especially ok I am going to emphasize this again, especially "Saudis", they cheat on their math and english exams in college, and most of them that I've meet in the USA are massively over weight and "below average bad looking", bad fashion, bad breath, stinky smell, and they will still look down on a beautiful fit \textbf{black} or brown lady, what do you call that? ignorant mixed with ugliness and bit of \textbf{racism}.\normalsize   & \cellcolor{green!27}Black, Ethnic, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/90 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small I'm an Arab and I am not a \textbf{racist} in anyway however when people of non Arabic background try to blend in by wearing Arab clothes and kaffyih I get mad because that is our culture and some try too hard to be Arab stop! It's pathetic especially true for some Pakistanis, Persians, Afghans.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small AGREED A 100.👍All Arab countries are \textbf{Racist} af esp SAUDI😑😑 and others except lebanon,palestine and Syria.Out of All Muslim countries ,the only loyal ones (whu donnot surrender to Evil zionist israeli )are IRAN,,Lebanon(Hizbollah LOVE THEM),Palestine,Syria,Pakistan and Turkey.The rest all muslim countries are sell outs esp Evil Wahabi SAUDI,thr 2nd puppet of israhell apart from USA\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Palestinians are not arabs !!!Strange that you talk about arab superiority while arabs mainly fight with their own \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Slight sense my ass!!! Some Arabs are more \textbf{racist} that White Supremacists.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I gess it's more like nationalistic spirit than \textbf{racism}, just like in Japan. But it's always good to address these taboos.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small being from Moroccan origins i see the exact opposite thing, Moroccans preach every \textbf{race} but themselves i dont get it\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small the thing about being sub-consciously \textbf{racist} is \textbf{common} in Asian culture from my experience\normalsize   & \cellcolor{green!5}Common, Racist & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small It even mentions this in the Quran\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I think Arabs are on the same level of \textbf{racism} as whites.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small nahhh asorry but white people are the worst when it comes to \textbf{racism}, supremacy etc. a very vile history even the arabs don't reach their level tbh\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small notorious namrod how do you know that arabs enslaved that many people? were you there? did you count about how many people were that enslaved? no, your claims are just built on exaggerations. so don't talk because you are ignorant. and if you really want to talk about which group of people that are the most \textbf{racist} and supremacist on earth, it would be white people. arabs are the least \textbf{racist} on earth. so next time talk with real facts instead of ignorance.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/83 & \cellcolor{green!5}2.41 \\  \hline
  \cellcolor{green!27}\small \@Bryan Cowo "Arabs are the least \textbf{racist}." What a load of BS\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm half Arab too and I hate how high and mighty they act especially towards the \textbf{black} \textbf{race}! How can u be a Muslim and be so disgustingly \textbf{racist}??\normalsize   & \cellcolor{green!5}Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small Yes!!!!!!!!!!!!!!!!!!!! Somehow there are those who actually obsessed and revered the Arabs as a superior \textbf{race}, almost like if u are embracing less Arab culture, then u are less of a muslim.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small you are wrong arabian features are so clear \textbf{black} hair \textbf{black} eyes between white and bronze skin these are arabs and most of saudi arabia are arabs and the \textbf{black} peopol in saudi arabia came from africa to visit makkah for hajj and they stayed there but most of the desert of arabia is arabs\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small Liked this before even watching purely from the title. Its 2017. Get over yourselves you \textbf{racist} Arabs.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small as an arab from iraq i agree. so many arabs look down on \textbf{black} people and indians etc\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Unfortunately, people not only find themselves superior because of their \textbf{race} but also because of their career or financial status. If you're not a doctor, lawyer, engineer, or some high paying career, then you're \textbf{nothing}. Subhanna'Allah, to see this happen in the Muslim community is a real shame! We are created from dirt \& will go back to being dirt, so how dare we act like we are better than everyone?! It disgusts me! It's like we have taken on some sort of caste system within our community. Ugh! May Allah help us all. It's good that we acknowledge this \textbf{racism} \& this superiority-complex- may Allah help us to extinguish this to the best of our abilities.\normalsize   & \cellcolor{green!27}Nothing, Race, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/117 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small The \textbf{race} that u see right now in America is \textbf{nothing} compared to the one in Middle East. They still use slave to this day to call others specially \textbf{black} ones and it saddens me and disturbs me deeply!!!\normalsize   & \cellcolor{green!5}Black, Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/39 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small It's not that Arabs have "\textbf{racism}" in the Western sense (I.e segregation, lack of opportunity for those of colour), it's that many parts of the Arab World are ethnically homogenous, so they have the "We're used to what we see complex". Also, there is \textbf{zero} Political Correctness in the Arab World. So many times there'll be remarks that would be considered \textbf{racist} in the West. Because I have a much darker skin tone than my whole extended family, my Grandma once joked about me being "Abed al Aswad" which literally means the \textbf{Black} Slave. My Grandma isn't a \textbf{racist} (hell, she's of mixed \textbf{race} herself) but when you're raised with statements like this being normal, it grows on you and eventually passes on generation to generation. As the new generation, we, the youth of the Arab World must put an end to this. However, it's not like people of colour are mistreated and not given a role to play in society, it's just that we grow up with these shitty thoughts that are very wrong.\normalsize   & \cellcolor{green!27}Black, Race, Racism, Racist, Zero & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}6/175 & \cellcolor{green!27}3.429 \\  \hline
  \cellcolor{green!5}\small Shafali Begum true but british asians look down on \textbf{black} muslims aswell. How can you complain about something that is engraned into your culture just as deeply?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small You should talk about \textbf{racism} for other ‘Muslims' towards Arabs... who they always say ‘oh you Arab' you're this and that and they try to show that Arabs are bad peoples!!\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small In London, I notice the Arabs think they are superior to EVERYBODY. Even white people which is \textbf{crazy} because in every case where I have noticed this superiority complex, they are visiting Arabs. Arabs that were not born nor grew up in the UK. They come to an English speaking country and have no respect towards the people who's country they are in. A lot of this I believe comes from their wealth.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small coo koo the fact you won't ever compare to whites, and won't say shit infront of a \textbf{black} man in person, makes me really laugh and confused at the fact how did they actually do that 😂 pathetic\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Sheikh-ul-Islam, Ibn Taymiyyah (ra) was of the opinion that Arabs ARE SUPERIOR (Afdal) than Non-Arabs and he claimed that this was the view that was held by the MAJORITY of the scholars – ‘Al-Jamhoor'- .He wrote: 'And the MAJORITY of scholars are of the opinion that the Arab species is better (Afdal) than the Non-Arab (species) just as the \textbf{nation} of Quraish is better (Afdal) than the Non-Quraishite nations and (just as) the \textbf{nation} of Bani Haashim is better (Afdal) than the Non-Bani Haashim (nations).' Majm'u Al-Fataawa 19/29He also wrote: '…This was the position of Imam Ahmed (ra) and the MAJORITY of Ahlul ‘Ilm.' Iqtidaa As-Siraatil-Mustaqeem 2/421Also, refer to what he said in Majmu' Fataawa 27/472.Unfortunately, when discussing the issue of the ‘Afdaliyyah' or superiority of the Arabs over the ‘Ajamees' (Non-Arabs), many people fail to do justice to this hotly debated topic.Sheikh-ul-Islam, Ibn Taymiyyah (ra) wrote:'Verily, what Ahlul Sunnah is upon: Is the BELIEF (I'tiqaad) that the Arab \textbf{race} is better (Afdal) then the Non-Arab \textbf{race}. Whether (the Non-Arabs) are Hebrews, Aramaic, Romans, Persians and other than them…'. Iqtidaa As-Siraatil-Mustaqeem 2/419Abu Muhammad, Harb ibn Ismail ibn Khalaf Al-Kirmaany (died 280 – ra) who was one of the students and companions of Imaam Ahmed (ra) also mentioned this point when he wrote about the descriptions and BELIEFS of the PEOPLE OF THE SUNNAH.He began his treatise by saying:'This is the Madhab of the Imams of ‘Ilm and the ‘Ashaab-ul-Athar' and (the people of) Ahlus Sunnah – who are the ones who are followed – (and they) are well known by these (issues).And I met those who I met from the Ulemah of Iraqand the Hijaz and As-Sham and other than them and they were upon these (issues).And this was the madhab of AHMED, ISHAQ IBN IBRAHIM IBN MAKHLAD (RAAHUWIYAH), and ABDULLAH IBN AZ-ZUBAIR AL-HUMAYDEE and SA'EED IBN MANSUR and other than them from those who I sat with and took knowledge from.They used to say Emaan (faith) consists of (making) statements, (doing) actions and (having) the Niyyah…'Imam Harb ibn Ismail (ra) then proceeded to mention many of the well known issues of the Aqeedah of Ahlul-Hadith and then he said:'…And we know the rights of the Arabs and (we know) their VIRTUE and their PRECEDENCE (in the Deen) and we love them because of the Hadith of the Messenger of Allah (peace be upon him): 'Loving the Arabs is from Emaan and hating them is hypocrisy'.And we do not say as the ‘Shu'oobiyah' (those who hate the Arabs) and (as) the lowly ones from the ex-slaves (say) who do not love the Arabs and they don't recognize their virtues, for verily their statement is a BIDAH' and (it's) in contradiction'.It should be noted that the Hadith that was used by Imam Harb ibn Ismail ibn Khalaf Al-Kirmaany (ra): 'Loving the Arabs is from Emaan and hating them is hypocrisy' is not an authentic Hadith! Even though it's a famous and widely used Hadith, it should not be used to prove a point in Aqeedah!\normalsize   & \cellcolor{green!5}Nation, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}4/520 & \cellcolor{green!5}0.769 \\  \hline
  \cellcolor{green!27}\small I have conversations with my Pakistani family members, and friends of all ethnicities about colourism and how the ideology that a lighter skin tone is better than others is so flawed and makes no sense- biologically those with darker skin are more resilient to things like sun damage so its very ironic to think light skin or certain physical features makes a person more worthy, just because of one persons' idea of 'beauty' which is subjective. Yet, its so deep rooted into all cultures that explaining makes no difference to some people- but I will never give up. We need to remember that our \textbf{African}, Afro-Caribbean, \textbf{African} American and dark skin brothers and sisters are treated most unjustly by other Muslims. We have to be conscious of their struggles in order to make a change.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/135 & \cellcolor{green!27}1.481 \\  \hline
  \cellcolor{green!5}\small Lol the Arabs you are referring to get so big headed because the \textbf{Quran} was revealed to the Arabic people. Forgetting that the Arab pagans were some really fucked up people and it was an act of mercy that Allah revealed the \textbf{Quran} to them because they needed it the most.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small i really struggled w this when i went to an islamic school. my family is from Sudan, and although i do speak arabic, i always felt like i never belonged. I had it better than most of the kids there though. Some of the arabic and \textbf{quran} teachers would be so rude and degrading towards the kids who had trouble reading or just weren't the best students. unfortunately, its been happening since forever, but i just wish it would stop and people could just be nice.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small preach!!! \& Also the treatment of east \textbf{african} muslims in arab counties is horrible. fix up.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Wallahi sometimes I cry because of how hard it is for me to memorise the \textbf{Quran}. I've been learning it for more then 10 years constantly and haven't even finished it yet. I feel bad when my fellow mates talk about how easy it was for them to memorise it at ages 10,11,12 while I'm still here barely passing half way. I've always wished I was Arab so I can learn quickly but unfortunately I'm Somali and don't know any Arabic. Please brother and sisters make dua for me.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small "Unfortunately I'm Somali"...wow what a sad statement to make. You should be proud of being Somali. It's a blessing. And learning \textbf{Quran} isn't that hard, I know so many Somalis that memorized it. It's actually very easy for Somalis to memorize the \textbf{Quran}...but understanding it, is another story.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Arabs are even \textbf{racist} against other Arabs such as Saudis vs. Emiraties Tunesian vs. Algerian, Morrocan, Egyptian etc. ... Sadly nowadays one will always ask you where you from then subconsciously categorise you... I sometimes feel like just saying i'm Muslim alhumdolillah...\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small It is so unfortunate that it gets passed down generations and the younger generations dont even realize it...I'll never forget the time a friend used the word عبيد to describe some \textbf{black} people while she was telling a story\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small 'An Arab is not better than a non-Arab, and a non-Arab is not better than an Arab; a white man is not better than a \textbf{black} man and a \textbf{black} man is no better than a white man – except if it is in terms of taqwa (piety).'Prophet Muhammad ﷺ We are one ummah 🕋🕌 Allahu Akbar☝️☝🏻☝🏼☝🏽☝🏾☝🏿\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small 1. Arrogant will not enter in Jannah.2. If we behave in \textbf{racist} way/arrogant way/superior way then Allah will put Zalim, tyrant ruler over us.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small So me as a moroccan Islamic berber can relate to this. Arabic moroccans actually always act like they're better then us just because they speak Arabic. People speak Arabic in public thinking we don't understand what they say, but most of us understand everything but it's just  so so hard to speak. Inshallah when I graduate I'm going to study arabic so I can understand the \textbf{Quran}. Bc now I just know how to write and read it alhamdullah. Peace💕\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small Bro as a \textbf{black} Muslim. They always try to correct me or recommend me skin bleach\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Imagine what it's like in the Gulf 😅 I'm Omani and it's so \textbf{common} for people here to see non Arabs as inferior\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small And \textbf{racism} is the action  of satan. When he refused to bow down to Adam (AS) and said that he is basically made of clay and I am made of fire. He set the bar for \textbf{racism} in humanity. \textbf{Racist} people are just following shaytans way, end of discussion.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Wow this is the first video I've watched of yours and i really like how you get straight to the point. Yh it's a sad thing that most arabs are \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I once had an Arab person absolutely gobsmacked that I knew how to read the \textbf{Quran} and could recite some verses by heart and even knew what they meant. I found it very judgemental and degrading of them to think that I was an illiterate Muslim. Just because I'm not Arab does not mean I'm a brainless robot following a cult for fashion or whatever the heck he thought 🙄\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small totally agree. but sadly when you let other Arab people know that they're being \textbf{racist} (even in the most polite way), their pride is too big to accept the fact that they're actually \textbf{racist} and they just get mad at you\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small So when would it be the right time to talk about such pressing issues? We wait until the hate dies down?? Erm the hate hasn't died down since the gulf wars. This is the very reason why so many people don't talk about problems like this because they're too concerned about what other people will think or say. I mean if you really truly acknowledge how dangerous and detrimental \textbf{racism} is within the Muslim communities you'll want to bring a change this instance and not wait until the 'hate dies down'. There will always be people hating from within the religion and outside of it. It's quite worrying to me that you think this way.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}\small its \textbf{weird} bc i think other cultures think arabs are worst than anyone else. as a turkish person i can say that we call \textbf{black} stray dogs "arap" and pretty sure most of the population despise them. idk.\normalsize   & \cellcolor{green!27}Black, Weird & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Racism is also between Arabs themselves where some Saudis think they're better than the rest of Arabs or consider themselves "the real Arabs"!! I once was called "Palestinian" by a Saudi AS AN INSULT!!!It's really really messed up and thank you for bringing it up 🙏.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Yussuf Daher hehehehe a fucking lazy \textbf{fat} fucking Saudi called "palestinian" as an insult.. Palestinians are the best educated beautiful "arab \textbf{nation}" actually Palestinians look down on all the arabs,,, No one give a shit to them here in Palestine , we see them " the Saudis " just a lazy ugly nation\normalsize   & \cellcolor{green!27}Fat, Nation & \cellcolor{green!27}Nationality - General, Physical Identity - Physical Features & \cellcolor{green!27}3/53 & \cellcolor{green!27}5.66 \\  \hline
  \cellcolor{green!5}\small Preeacchh Subhi!! Finally you're talking about this issue. So many people believe that arabs are superior to the rest of the world. To the extent where saying "you look Arab" is the biggest compliment to people, and people are ashamed to look the same as their own \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small It's exhausting, we have millions of religions/moral guides in the world but people still can't figure out how to treat others right such ashame. I was talking to someone specifically talking about the U.S. and immigrants who come here from Latin/Central America, Africa, Asia etc.. "How can you come to a country and not relate to the people of "color" there and their struggle?" Basically, do not pretend you are better than people with darker skin (\textbf{black} americans, africans etc). In the Western world white beauty is still the standard representation of beauty (although there've been some changes in advertisment/social media) so it does \textbf{nothing} more but create more tension when Indians, Egyptians, Chinese etcc,, think they are better than "\textbf{black}" americans or those of darker skin.\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/127 & \cellcolor{green!27}2.362 \\  \hline
  \cellcolor{green!5}\small Peace be to those in each of the worlds who struggle with these social situations.  My folks have a proverb that says "trouble don't last always."  And they said that when the struggle was thick and deep. There is a \textbf{Quran}, a deep \textbf{Quran}, written in creation that tells your soul what to say when you're in between a rock, a hardplace and there are many people looking down on you.  Trouble don't last always means "With every difficulty comes relief." Listen, this \textbf{racism} thing is all time based and has no covenant of perpetuity.  Whether you hide the truth or publish it, the truth is that it is a sin and those who practice it among any \textbf{race} will be held to account.  Allah knows best.  When it is done and it will not last always, make plans to turn attention towards the Eternal.  It will not last always.  It will done.\normalsize   & \cellcolor{green!5}Quran, Race, Racism & \cellcolor{green!5}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}4/153 & \cellcolor{green!5}2.614 \\  \hline
  \cellcolor{green!27}\small Anti-black \textbf{racism} is a worldwide phenomenon unfortunately. Some of the most vitriolic \textbf{racism} i've witnessed has come from the mouths of Non-black POC, oftentimes muslims. Arabs and Desis. It's pervasive and goes against Islam. It needs to go.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Dad: manar don't trust desi, \textbf{black} or anyone unless they are arab.Me: dad thats \textbf{racist}. Not everyone's bad.Dad: astkafurallah you do as I say I know more than you. Bad child.Me:😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑😑Also me:😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕😕\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small DUDE okay my sister always says stupid \textbf{racist} stuff like "ew shes so dark" and shit like that!! i always tell her that this is \textbf{racist} but guess what she doesnt even care! as a muslim egyptian gal i asure u that this problem is gonna take a long time to fix. theres so many \textbf{racist} people in our community and they simply dont even care and they know it\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/70 & \cellcolor{green!27}4.286 \\  \hline
  \cellcolor{green!5}\small This is so, so important. I've been talking to people about it for so long, especially since I come from a country or region where people, for some reason, think they're superior? I'm a Bahraini who lives in Emirates and despite how diverse Emirates is with people from every part of the world, if you're not Arab or sometimes even from the gulf, then you're looked down upon. I like having friends from all parts of the world and somehow I found myself getting along with Pakistanis and Indians really well, and the other day we had a group project in my biology class where my \textbf{Indian} friend and I were put into a group with two other local girls. They were literally talking to us in such a mean way until they asked me if I were Arab and when I told them where I'm from, their tone with me changed COMPLETELY, but they were still treating my friend like shit. I got so pissed. I'm still so pissed. I don't understand why they think they're so superior. We're all equal. We all come from the same God; where we're from does not make us superior nor inferior.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/199 & \cellcolor{green!5}0.503 \\  \hline
  \cellcolor{green!27}\small And what makes it even worse is that we can't marry people from Asian countries without being looked down upon? Like I've witnessed some relatives in front of me going like "oh my god, she married an \textbf{Indian}?" and it's so disgusting. My own mother always talks about how I'm only supposed to marry someone from my own blood and by that, she means someone that's from the gulf region and if it isn't, then he "doesn't love me" and only wants me for my passport and it's just.. wow. A big disappointed wow.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small You look like jake gyllenhaal like \textbf{crazy} 😍😂\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small That's true but here in Algeria I don't think we have this kind of problems , I mean as we all know Algerians are Arabs + amazighe . and we have all kind of skin colors we're 100 mixed ... There's always some differences in culture ect .. And there are some \textbf{racist} ppl .. But in general we don't have that issue hmdlh   يا سكان المملكة العاشورية اذا راكم هناا قولولي واش رايكم في هذا الموضوع !!!!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Thank u for this! As a Arab, I too do my best to correct the subconscious \textbf{racism} engrained within our culture. My parents are not bad alhamdulillah, but when it comes to older generations, they definitely need a little work! JZK for speaking on this!! Needed to be said!\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Yeah you're right they're not just \textbf{racist} for not arab they're \textbf{racist} to each other and not just that they're \textbf{racist} in families names they're just so sick people I'm arab and i hate how they act especially between palestinian and jordanian 🤦🏻‍♀️🤦🏻‍♀️🤦🏻‍♀️\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/43 & \cellcolor{green!27}6.977 \\  \hline
  \cellcolor{green!5}\small AHH THANK YOU!!  Thank you so much for putting this out there subhi! As a non arab who has lived her whole life in Saudi Arabia I have felt this more than i can explain. And its true that some arabs welcome us with open hearts. But often i do not get the respect as equal to arabs here even though i do \textbf{nothing} wrong. And i am studying ARABIC FUSHA. Its a struggle. But its arabs who are teaching me. So thank you. To all those arabs who care. 💕 and you as well.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small I just start my first year of university in an Arab Country, and im so upset seeing arabs cant even read \textbf{Quran} , so bad even my 8 years nephew could read better, and we are not even Arab, we used to struggle learning Tajwid when we was kids\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Completely and utterly agree! Especially when arabs use the word "abd" towards \textbf{black} people\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small adnar bullak Yup, that's how disgustingly \textbf{racist} you guys are.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I swear the more diverse the community is the less \textbf{racist} it becomes.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small This is obvious even in the holy cities I kid you not. There are nice people but some people make it obvious, that they look down on you. Disgusting behaviour for a Muslim. And because I speak Arabic I've even read tweets from Arabs making fun of the Arabic pronunciation of south Asians, southeast Asians when they read \textbf{Quran}. How low can you go? May Allah guide them\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small In Singapore, the Arabs who have settled in our country are the same way. Although they've adopted and assimilated themselves into our culture and language, they still perceive themselves as better than some races. No marrying outside their \textbf{race} unless of course it's a Caucasian. (Go figure).\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small that's a preference, it ain't mandatory nor it makes you \textbf{racist} and as seeing oneself superior lol , its the most basic of the mankind trait.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I think if "they" as in "the majority" act upon this [i don't know, rule??] regarding "no marrying outside their own \textbf{race}" then that is no longer a "preference"\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small PAH-REACH!!! On the day of qiyamah everyone will be standing in the same empty plane. Under the blazing sun. In front of allah swt. No arab will be above an ajami because he's "Arab". \textbf{Black}, white, \textbf{r\textbf{ed}}, green, or whatever you are you will be standing there next to the person you think you're above today. Actually he might be under Allah's shade while you're being drowned by your sweat. So HUMBLE yourselves people.\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/74 & \cellcolor{green!27}4.054 \\  \hline
  \cellcolor{green!5}\small dude im egyptian and the country is in deep deep poop and there are still egyptians that think that we are the smartest the greatest of them all \textbf{racism} inside racsim I feel sad that we still consider racsim is normal  and not addressing it as an issuewhenever I hear something like "indans are this " or "asians are that" from friends or family member i try to tell them it's  LOGICALLY impossible for a \textbf{race} or a \textbf{nationality} to have the same atitude\normalsize   & \cellcolor{green!5}Nationality, Race, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/85 & \cellcolor{green!5}3.529 \\  \hline
  \cellcolor{green!27}\small yasmeen nour wow that is kinda \textbf{weird} to hear, because in my country, we mash all the Arabs, Indians, Iranians, Asians in a one bowl, like for us they're all the same. I didn't even know if Arabs felt any superiority until seeing this video, to be honest.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small As an \textbf{Indian} living in Kuwait, I just want to say THANK YOU!!!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small thats my parents and when i tell them to stop being \textbf{racist} they tell me to  shut up. Well mostly my dad, sometimes mom sides with me and corrects herself\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small People read 49:11 and 49:13 from the \textbf{quran}. Also \textbf{Black} has no superiority over white nor has white superiority over \textbf{black} except in piety and good action. This superiority thing and \textbf{racism} has to stop. We are an umma.\normalsize   & \cellcolor{green!5}Black, Quran, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}4/39 & \cellcolor{green!5}10.256 \\  \hline
  \cellcolor{green!27}\small That is actually true and whenever I try to mention it to my Arabic friends, they get offended or they don't even know most of the time that what they just did was \textbf{racist}!Love from Pakistan <3\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small anti-blackness is the biggest problem in the muslim community. Just because I have \textbf{black} skin doesn't mean I'm less of a human being. That's why I don't hang out with Arab ppl they r \textbf{racist} asswipes.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small So with Arabs here we mean the Arabs who live in Saudi and gulf , not the other \textbf{African} Arabs like Egypt Sudan >.>\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small please the so-called "arabs" in sudan (who are mostly arabized in language) are some of the worst in terms of how they relate to other non-arab or non-arabized \textbf{African} groups in the country precisely because they've internalized the anti-\textbf{Black} \textbf{racism} of arab socieities and cultures and actively distanced themselves from the rest of the continent and threw their lot with MENA in the hopes of being accepted by the whiter arab center, and dragged the country into one of the longest and most brutal civil wars fuelled as much by racial/cultural chauvenism as it is by power and control of resources. And when these arabized sudanese started migrating to other arab countries they would often get the shock of their lives when they realize that all along they've been a \textbf{Black} ppl wearing white masks and that other arabs from the Levant and Gulf actually looked down at them and viewed them as 3abeed, resulting in an acute crisis of identity. A similar thing happened when self-identifying arab sudanese immigrated to north america and much to their disappointment, realized that here too they were just another group of \textbf{Black} ppl. It's a surrea tragicomedy largely of their own making.\normalsize   & \cellcolor{green!5}African, Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/199 & \cellcolor{green!5}2.01 \\  \hline
  \cellcolor{green!27}\small kuntbrigade I'm living in Egypt (arabized \textbf{African} country) Sudanese are known for their kindness here, I have mates who are Sudanese in my college who seem to blend in and doesn't treat us like other Arabs >.> (Calling us ta3mia and fala7en).\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small I'm not speaking about your friends specifically but I'm speaking about the mainstream society and culture as a whole, especially the one based in Khartoum. Go speak to a southern Sudanese  or someone from Darfur or Kordofan and ask THEM about their experiences. Or better yet, look at how southern sudanese and darfur refugees were treated by the egyptian state and police and the daily \textbf{racism} and violence they encounter from egyptians. Step out of your bubble and learn to listen to the experiences of others and accept that they will not always confirm your own biases. It's your individual responsbility to educate yourself if so you choose.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small There is literally no moral equivalence between the \textbf{racism} encountered by someone and their completely understandable reaction to that \textbf{racist} behaviour and calling it as such. Reverse racim doesn't exist and especially in the absence of any institutional power to back it up.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small You speak Arabic? specifically Egyptian Arabic Cause I'm not good at English >.>, I want to know more about Egypt in this particular subject cause it's a shocker to me hehehe, I thought we were the least \textbf{racist} country compared to what I've read about the others.Apparently, all of us deserves El 7ar2 after reading the comments on this video*.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Like I said, its your personal, individual responsibility. The information and resources (books, articles, documentaries, movies, personal accounts etc) are all available out there, and google is your best friend. Mafi zol gal leykum tit7argu, just hold yourselves, families and socieities accountable for their rampant , unchecked and unchallenged \textbf{racism} towards non-arabs. I can assure you that for many of us who have been on the receiving end, it's not a shocker but just the usual we have come to expect. We inhabit completely different realities.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small kuntbrigade bs masr mafehash 3onsorya MN El no3 El bytklm 3leha Fe El video, we don't see Arabs as superiors or anything...As much as I know, about shami guys only Lebanon has a little problem with \textbf{racism} but it's not Arab superiority ,then going to rest of North Africans where some think they are not Arabs but Berbers.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small And you are the perfect example of why I don't engage with you ppl. Like a comment ago you said you were interested in learn more about this issue then without even trying to do the bare minimum to challenge your lazy blinkered worldview that was handed to you by your society, you go off into "but egypt is not \textbf{racist} like that" I'm not gonna spoonfeed you education your parents should have imparted to you. That's not how it works.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small kuntbrigade that's not what I meant 😂 \textbf{racism} exists but not in that form ,"Arab superiority".People don't look down at non Arabs here, yet \textbf{racism} exists in other forms.We don't say "look he isn't Arab he isn't like us ko5a ya baba" like some comments claim here but in the same time , people might throw \textbf{racist} jokes like " eh da shekabala 3antra ibn shdad El wad da shokalata ( hya msh shtaym bs msh lama tshof wa7ed bashreto soda t2olo keda)".But it has never been far than jokes as much as I know, we believe that people with \textbf{black} skin color carry good hearts and that El Samar nos El Gamal 😃.\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/117 & \cellcolor{green!5}3.419 \\  \hline
  \cellcolor{green!27}\small Omer Gamal talking to you is like talking to a white person about white \textbf{racism}.  We're done here.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Maaaaaaan half philipino 😍😍😍😍😍 we arabs are of painful double standads. We say: no difference between an arab and a non arab (لا فرق بين عربي واعجمي) but then we say: the prophet is arab, \textbf{quran} is in arabic. And the issue is that we are completely oblivious to it. I say we to not exclude myself from the group 😂😂😂 plus the political issues take part in deepening that more. Not to mention how many arab countries, mostly gcc (my region), have a high percentage of expactriates who work in lower positions which makes us look down on those nationalities overlooking that in the end of the day we are all HUMAN BEINGS. But sometimes specific races are not perceived as humans 😊💔\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/124 & \cellcolor{green!5}0.806 \\  \hline
  \cellcolor{green!27}\small i can relate to this most of the time. as a half arabic person, it is easier for me to see the flaws. some of them are \textbf{racist} to me because im not 100 arab and it upset me alot. i hope with this video people would rethink themselves and change for the better\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Zoya Salim same goes for pakistanis treatment of dark or \textbf{black} people x\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@nader nyc how can arabs treat \textbf{black} people badly when bilal bin rabah (a \textbf{black} man) is one of the most popular and loved companions of the prophet pbuh\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small \@bflf jfldhsm Arabs enslaved \textbf{black} people. South Asian Pakistani DID NOT DO THAT. Arabs look down on blacks and South asians. So fuck out of here anyone that is trying to put the \textbf{racism} label on us.\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small \@bflf jfldhsm what is that to supposed to mean, lol syrian refugees even refused share the same travelling boat to europe with \textbf{african} cuz they are \textbf{black}. Lol another arab who denies that the culture is \textbf{racist} lol.\normalsize   & \cellcolor{green!27}African, Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/38 & \cellcolor{green!27}7.895 \\  \hline
  \cellcolor{green!5}\small I really appreciate your video, I'm from sudan and my parents sometimes they don't release that they are saying \textbf{racist} comments in my family we have people who are not \textbf{black} as the sudanese people because we are mixed.I always hear them saying " i don't want my kids to marry someone who is darker then them" and they don't even understand that this very racist\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/67 & \cellcolor{green!5}4.478 \\  \hline
  \cellcolor{green!27}\small Afnan Yagoub its not \textbf{racist} sis, everyone has his own choice of what he wants his children to look like..\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small The \textbf{Quran} was revealed to the Arabs because they needed it the most. That's not necessarily something to be proud of.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small MzKyu who are u to say that? Arabs who the god chose the prophet and sahaba from them and especially sahaba are the best,,, the god knows very well who to chose so even if u have faced \textbf{racism} that don't give to say this ,and only a few group who are \textbf{racist} from them\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small MzKyu who said the \textbf{Quran} is right anyway. Arabs have really succeeded in brainwashing the rest if the world. But there's a huge rise in ex Muslims all around the world now and people are waking up to the disgrace of Islam.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small MzKyu will, this is a stupid comment from arab hatters that i heard a couple of times..and tbh with you .. I understand why some ppl (and you among them) make this claim , that allah send Mohammed peace be upon him to the arabs because "they were the worse" .. I understand when someone faces \textbf{racism} that he trys to make a counter \textbf{racism}, but in this subject particularly u make fun of ur self really.because there are several hadiths that says that arabs were "chosen people" in a sense that they had a good manners and honor so allah send his loved prophet to be among the right people to spread the last and final message (Islam) ..and you can just google it to see how much hadith that says that allah had chose the arabs\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/141 & \cellcolor{green!27}1.418 \\  \hline
  \cellcolor{green!5}\small A lot of the replies under this comment are pretty \textbf{dumb}. OP is not saying Arabs NOW are the worst/bad people. But BEFORE Islam they were. And there is \textbf{nothing} wrong with that. OP is only saying that's the reason the \textbf{Quran} is in Arabic and that's pretty much a fact. No need to be butt hurt over it.\normalsize   & \cellcolor{green!5}Dumb, Nothing, Quran & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}3/59 & \cellcolor{green!5}5.085 \\  \hline
  \cellcolor{green!27}\small - Aileuna - read the (Muslim solider) is comment you filthy disgusting woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small MzKyu god revealed \textbf{Quran} to the Arabs cuz he knows they are the only ones who can successfully pass the Islamic religion on to other races and Arabs are the ones and first who would fully believe in it. Do u think god would count on just anyone to take care of his holy book and teach the rest about it? No dear, we are teachers and you are our students. Good day.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small \@ford07 ford07 Nah, other nations were living peacefully because they were already naturally guided, however the arabs of the past were stuck in the dark ages with tribalism and barbaric customs, so they needed God's guidance the most in the form of the \textbf{Quran}.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small MzKyu .....🤣 Islam was invented by \textbf{racist} Arabs for Arabs. Muhammed was a Arab supremacist that called blacks "raisin heads", conquered and slaughtered many tribes, and owned many slaves and \textbf{sex} slaves.\normalsize   & \cellcolor{green!5}Racist, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small ford07 ford07 You are teachers? The rest are students. Ok... Just so you know, all the hadiths that all Muslims regard as authentic collected by Imam Al-Bukhari, yes that guy was Persian, not an Arab. Imam Muslim? This guy also a Persian, not an Arab. The Muslim scholar, who placed values of Sufi into Fardhu 'ain and Sharia Law/Jurisprudence, Shaykh Al-Ghazali. This guy also Persian, not an Arab. O.k. how about today, the Muslim scholar who is learned regarding matters of the End-Times/Eschatology, Sheikh Imran Nazar Hosein. This guy from Islands of Trinidad \& Tobago, also not Arab. What about his teacher Sheikh Fazlur Rahman Ansari? \textbf{Indian}!Oh so those not Arabs are students of Arabs. So O.K. when the Arabs could BARELY even scratch the surface meaning of the Noble Qur'an and others have gone far in giving the INTERPRETATION of the Qur'an. Yes, just like when Sheikh Imran Hosein kept on asking, "WHERE ARE THE ARAB 'ULAMA ??"We are the students?? Oh.. O.K.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/166 & \cellcolor{green!27}0.602 \\  \hline
  \cellcolor{green!5}\small \@ford07 ford07 Allah said in the Holy Qu'ran in Surat at Tauba "The Arabs are the worst in disbelief and hypocrisy, and more likely to be in ignorance of the limits (Allah's Commandments and His Legal Laws, etc.) which Allah has revealed to His Messenger. And Allah is All-Knower, All-Wise." Allah also mentions that amongst these Arabs, there are those who believe in Allah (good Arabs). The poster is right. There is a reason why Allah sent the Qu'ran to the Arabs, at that time they were the worst of people and amongst other things like the beauty in the Arabic language. Now to correct your arrogance, brother. Arabs are not the teachers of Islam. Every Muslim is a teacher of Islam. We teach others literally or by our actions. What you're saying as is against the teachings of Muhammad (SAW). You are propagating superiority, do not do that brother. Arabs, Indians, Somalis, Europeans, and what have you are all equal except in good deeds. I repeat Arabs are not the teachers of Islam as Islam belongs to Allah only. Don't forget that Islam existed before Muhammad (SAW). It existed through Abraham, Musa (who was \textbf{black}), and Isa ibn Maryam. Islam was perfected in Arabia, but it started with Abraham. Don't forget your place brother, we are all on equal footing in learning the deen. If you were born Arab say Alhamdullilah that Allah has given you an easier time in learning his words. But do not think you are superior to those who weren't born Arab as they will earn rewards when reading the Qu'ran. Read more brother, the great scholars came in all shapes, colors, regions, etc. Persian, Ethiopian, Roman, Arab, Egyptian, etc. Allah is our teacher and we are ALL students of Islam. Salam.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/297 & \cellcolor{green!5}0.337 \\  \hline
  \cellcolor{green!27}\small so you claim that arabs are the worseyou are a racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Nouf Abdulrhman Actually, the \textbf{Quran} clearly states in Chapter As-Shura, Allah states that the \textbf{Quran} was revealed to the Arabs because they were the center of paganism and the belief of many gods (worst than India). The  best way to spread His word was through them. The prophet Muhammad PBUH was sent there for the same reason and that's why many small Jewish tribes moved there.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@Tranquil Lee Oh boii ya such a fucking brainwashed moron i cant belive how \textbf{dumb} some one can be. Ex Muslims were never Muslims this a Fact. They do this only for Money.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@nxx pluto Actually it is in Arab because the arabic language is kinda special and cant be compared with others. Thats why \textbf{quran} is in Arabic noz because Arabs were chosen\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small ford07 ford07 you sound \textbf{dumb} asf😂😂\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Iam Egyptian....and yes alot of people here consider them selves better than asian or \textbf{African} .. and every time i talk to them about it they make fun of what i'm saying ✋😏\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small I live in an Arabic community, the reason why they feel superior isn't because of the \textbf{Quran} or Islam as there are a lot of non Muslim arabs that still feel superior... I believe it's the history that our countries hold and just traits they pick up from their parents.. for example parents that feel superior over other nationalities will show it in front of their kids because they were raised not knowing it's bad so their children pick up from it as well.. that and the lack of education without being up any examples because I do not wish to insult any \textbf{race}. In the end I believe that \textbf{Quran} and Islam play a minor role in this. If anything Islam teaches us to be more humble and we all know that some Arabs (not all) neglect most of the good traits Islam teach us\normalsize   & \cellcolor{green!27}Quran, Race & \cellcolor{green!27}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!27}3/146 & \cellcolor{green!27}2.055 \\  \hline
  \cellcolor{green!5}\small Omg  I wana like this 300 times 😭💙yes , Im Frm south America n i've been living in saudi  a while now , gosh it's nice that an arab explained this so nicely , the \textbf{racism} is kind of the only flaw I c here ,but I've learnt to shut up ,n take it . (Everything I wana do , ..miss, r u arab?)😰...   .... well hello!, I'm here teaching your growing generation to speak English n that's how u treat me ?😭... but then again like u said ,they were born with that  mentality frm their forefathers so I can't blame them today,  so I shut up n be kind. May Allah guide us all.  (We r all flawed ).\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/121 & \cellcolor{green!5}0.826 \\  \hline
  \cellcolor{green!27}\small I'm so guilty of this. And I realize at moments I need so step back and tell myself- shut up that was \textbf{racist}... I'd also like to point out discrimination occurs within arab countries as well . Ex like in the gulf, they look down upon say Egyptians as a subordinate .. etc\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Too true! They reap greater rewards when memorizing and reading the \textbf{Quran} because it's harder for them! May Allah subhana wa ta'ala reward them for their efforts!\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small This time we all got Ramadan on same day...Arabs and we \textbf{Indian}..it's the nature of Allah..❤️❤️❤️💕💕💕💞💞💞💞\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small The only man who killed \textbf{racism} in this worldRasuulullaah saw\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I'm Algerian and since I mostly grew up in Canada I never really studied Arabic (fos'ha). Besides the Saturday Arabic school I used to go to when I was younger, I never really got to learn how to read and write and speak (proper) Arabic. I'm fluent in the Algerian dialect though. But I was once told that since I didn't know how to speak "real" Arabic, I wasn't Arab. According to the person who told me that, being Arab is defined by your ability to speak Arabic and I was excluded from being one because Algerian Arabic is far from its classical roots. That encounter sort of made me self conscious about my identity. So I started identifying myself as Algerian period. See how us Arabs even discriminate within our own "\textbf{race}".\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/133 & \cellcolor{green!27}0.752 \\  \hline
  \cellcolor{green!5}\small Well, to be fair, Algerians are ethnically amazigh mixed with either south european, sub-saharan or middle-eastern dna. \textbf{Ethnic} Arabs are found in the Golf, but you may be an arab speaker though. Algerian dialect (derja) is arab heavily mixed with tamazight, french, spanish and turkish, it may be a language on it's own at this point just like Maltese is. To be understood by other arabs, Algerians have to speak the Lebanese and Egyptian dialects...why change who we are, why make all these efforts if they don't even make an effort to learn our dialect? For them, Algerians will never be arab enough, so why bother? We have two amazing languages and an amazing culture, let's celebrate us as Algerians and North Africans.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/123 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}\small I stopped bothering a long time ago and to be honest even before I still considered myself Algerian first because of how different we are from the Middle Eastern Arabs. And I completely agree with you, we do have an amazing culture and languages. I'm an Arab (derja) speaker in the sense that I do not speak Amazigh. Ethnically I do have some Berber blood (like all Algerians whether they acknowledge it or not) and some Turkish ancestry as well. But it's hard to pin point my \textbf{ethnicity}. Us Algerians have known centuries of colonialism and migration that I can't really trace back my ancestry (believe me I tried and it's frustrating not knowing). As far as I know I'm just Algerian and on a broader scale North \textbf{African}.\normalsize   & \cellcolor{green!27}African, Ethnicity & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/129 & \cellcolor{green!27}1.55 \\  \hline
  \cellcolor{green!5}\small Their problem not yours.. \textbf{Nothing} wrong with ur accent.. I am from KSA and I still struggle to understand some accents inside my own country like "لهجة بني مالك، اللهجة المهرية"..etc.. So, don't buy it when we "easterners" say "We don't understand ur accent".. cuz we also don't understand each other's accent. :)\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Sarah  kt my mother is Polish too, my father has \textbf{black} hair and brown eyes and me too, my mother has different colours but I don't think that I'm similar to them, I always prefer other people to tell me instead of me.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small I don't blame arabs entirely for their superiority, growing up in the Bengali community we also held Arabs on a pedestal. Growing up I used to think they were the better muslims, we asians were some how lower class. Its only now years on do I see the problem with that. I mean it still exists in both communities. I went to a Muslim majority high school and I was looked down upon for brown skinned. \textbf{Racist} rhetoric was just seen as the norm.The worst was when I went hajj though. To go into the area with the  prophet's grave they split everyone by country, my mum and my sister was with me and we're all brown girls so despite being Australian they pushed us in with all the Pakistani/Bengali/Indian people. I have no issue with being put with that group but my issue was that the people in charge decide that it was appropriate to split everyone by country, then to have all the people of Arab decent go through first because some how their prayers are much more important than mine. In the end we waited for hours and we didn't even get to go in, we ended up having to go back another day and had to have the Arab members of the hajj group we went with help us get in.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/225 & \cellcolor{green!5}0.444 \\  \hline
  \cellcolor{green!27}\small Your a honest kind soul! May god bless you. Very helpful for a lot, Arab or another \textbf{race}! :)\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Being an Arab in the Muslim world is a privilege. Yes, in western society muslims are now being frowned upon, but WITHIN the Muslim society we do have that privilege. Also, I am really disappointed in the Arabs calling our \textbf{Black} Muslims 'Abd' instead of 'Sowd', and using religion to justify that. You cannot call someone 'Abd' and justify it using religion without adding 'Allah' (Like, we are all Abed Allah but when you remove the God part you're literally just calling someone a slave- and that's \textbf{racist}).\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/88 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Here's part of the prophet pbuh last sermon "All mankind is from Adam and Eve, an Arab has no superiority over a non-Arab nor a non-Arab has any superiority over an Arab; also a white has no superiority over \textbf{black} nor does a \textbf{black} have any superiority over a white except by piety and good action. Learn that every Muslim is a brother to every Muslim and that the Muslims constitute one brotherhood. \textbf{Nothing} shall be legitimate to a Muslim which belongs to a fellow Muslim unless it was given freely and willingly. Do not, therefore, do injustice to yourselves."\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/100 & \cellcolor{green!27}3.0 \\  \hline
  \cellcolor{green!5}\small MY mom keep saying \textbf{racist} insensitive things .. and every time I call her out privately, she get so offended and upset ...\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small What do I do if it's my so called friends making \textbf{racist} comments towards me? Calling me a "\textbf{terrorist}" and saying things like "are u gonna bomb up the school?"\normalsize   & \cellcolor{green!27}Racist, Terrorist & \cellcolor{green!27}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small The same issue applies in South Africa but with \textbf{Indian} Muslims being the "Arabs" in this scenario. Majority, unfortunately look down upon \textbf{black} Muslims and will only engage with \textbf{black} Muslims if they are mixed, Somali, or an imam or sheikh. It gets becomes such an issue that some will not eat with \textbf{black} people from the same dish. As well as they think that one cannot be a South \textbf{African} Zulu Muslim and not be 'beautiful' or have a 'nice sharp nose' but rather immediately think that you are Somali, or Sudanese or whatever. This is such a sad thing to see and experience especially considering the fact that the Prophet Muhammad (saw) and Allah (SWT) clearly said that it is wrong to think that you are above anyone. May all \textbf{racism}, prejudice, pride and any sign of evil attributes, attitudes and behaviour be removed from us and may we be an understanding and tolerating ummah. Ameen.\normalsize   & \cellcolor{green!5}African, Black, Indian, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}6/158 & \cellcolor{green!5}3.797 \\  \hline
  \cellcolor{green!27}\small I see that A LOT in our community especially as an Arab kpop (Korean Pop) fan who gets a lot of \textbf{racist} comments from like SO MANY people I always call them out (in a mannered way) that hey look they're humans just like us I say that while I'm actually angry and boiling inside but trying to stay as polite as I can to not give a bad impression to that person but to give them a good advice\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small abdirahman ali Somalis are one \textbf{ethnic} group, share one religion, one language, one country, and one \textbf{common} father. I'm Hawiye Somali I don't understand people's motivation for wanting to make sure Somalis are mixed with other races.Allah created us differently for a reason.\normalsize   & \cellcolor{green!5}Common, Ethnic & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Being \textbf{racist} is not just a Somali thing, many other \textbf{African} countries are extremely \textbf{racist}, look at South Africa, look at the treatment of congo refugees in Angola. It just pisses me off, that when it comes to \textbf{racism}, Africans always point the finger at Somalis only\normalsize   & \cellcolor{green!27}African, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/47 & \cellcolor{green!27}8.511 \\  \hline
  \cellcolor{green!5}\small I am Arab, living in an Arab country and obviously, I spend most of my time with other Arabs. I often witness the indirect \textbf{racist} remarks us Arabs make unintentionally, especially of the desi community. The desi community in the Middle East are riducled and bashed, Arabs make their beliefs a mockery, and some Arab Muslims feel superior because they speak and read Arabic, so they don't have to invest so much time in trying to read Qur'an because it's their native language. But majority of Arabs own internalised hate for their own selves, you can kind of see it when they immediately want to befriend someone of Cacausian descent or someone with an "ajnabi" passport. I apologise to anyone who had to deal with us, and some of our \textbf{racist} remarks, and the unwanted cultural situations we put you in, just because we're Arab. I hope that made sense.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/150 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Amen! I was just talking about this to my students today. I am a teacher at Muslim Academy in New Orleans, La. 99 of my students are Arab Muslims. As a Cuban \textbf{woman} who converted to Islam, I have faced and dealt with this a lot over the years. You are very correct when you say that many are unaware and they simply repeat words and expressions they have heard all their lives but it doesn't make it okay. As a teacher I always work to open the minds of my students to all cultures, religions, and walks of life and remind them that we are all Allah's creation and should be treated equally, respectfully, and with compassion. I'm going to play this video in class for them. Very well said, Subhi. Thank you.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small The biggest shame of all is that most Muslims have not actually read the \textbf{Quran} cover to cover, or even bother to really learn about Sunnah, the \textbf{Quran}, and the Hadith or to implement real islamic teachings in their lives. If they actually did this, the problem you mentioned as well as many other problems in Muslim countries would not exist! Being just, fair, not \textbf{racist} and treating others equally and with respect and dignity are the underpinnings of our religion. There is a reason we are mandated to complete Hajj. At Hajj every color, \textbf{race}, and social class stands in the same clothes next to each other, because no one is better then anyone else and we are all servants of Allah (swt). We always get mad at American's for conflating culture with religion, yet sometimes I think so many Muslims in Muslim countries don't know the difference between culture and religion either! Half of the things that happen in Muslim countries are completely antithetical to Islam.\normalsize   & \cellcolor{green!5}Quran, Race, Racist & \cellcolor{green!5}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}4/168 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small ladyessi No, she has talked about \textbf{racism} before it affected her life deeply. So she appreciates Subhi speaking the truth because it might change some people's minds she doesn't want to look down on arabs, her best friend is arab.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Tazzy never makes fun of arabs. That's mostly when she invites her friends in her videos to spoof certain stereotypes for instance her arab friends spoofs arab men, and tazzy herself spoof south asians. Anyways sometimes as a muslim it can get hard to not get angry at the \textbf{racism} in the community, but I think in the end you can't really change what people say or if they think you'll never be a good muslim just because you aren't arab. As much as it hurts in the end you just move on, and you do things you love, and leave the rest to Allah. And for me being the control \textbf{freak} I am, that is hard to do because my first (not best) reaction is to immediately trash talk people who are \textbf{racist} or be \textbf{racist} back, to take control of the situation and make them feel equally as hurt. But that's probably not even going to change their minds tbh. And my time is worth so much more than trying to prove to people who don't like me for something I can't help that I'm good enough. I don't do it for white racists or arab racists or any type of racists. I think putting your \textbf{mental} health over what the haters say is very important, and just block if you have too. Hopefully if we makes small changes as a whole the Ummah gets better, InshaAllah the \textbf{racism} towards each other ends\normalsize   & \cellcolor{green!5}Freak, Mental, Racism, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/245 & \cellcolor{green!5}2.449 \\  \hline
  \cellcolor{green!27}\small I knoww right ! I'm algerian, considered a fake arab by middle eastern arabs, and I know that I'm technically not arab, but God i'm happy arabic is all I know as a mother tongue, because when I see how my revert latina friend struggle with learning \textbf{Quran} and duas, in my heart I'm saying hamdellah north africa hasn't just been reverted to islam but reverted to arabism aswell ! Proud amazighia either way, but lets face it, arabic is a must when you're a muslim\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Sometimes when I'm amongst white people and they make a \textbf{racist} joke about muslims I tend to just let it slide to make it look like it doesnt affect me but it does. I just wish we could all be sensitive equally to \textbf{racist} connotations.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small To every \textbf{racist} Muslim, this is for you. قالَ رسولُ اللهِ "صـلى اللهُ عليهِ و سلـم " : ( لا فرق بين عربي و لا أعجمي و لا أبيض ولا أسود إلا بالتقوى )"There is no virtue of an Arab over a foreigner nor a foreigner over an Arab, and neither white skin over \textbf{black} skin nor \textbf{black} skin over white skin, except by righteousness"\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/66 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I'm Pakistani and I loooooove my olivey \textbf{y\textbf{e\textbf{llow}}} skin tone. I love all cultures and respect everyone. Beauty is in the eye of the beholder\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/25 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small I was so shocked the other day, i was in a mosque and an \textbf{old} man looked at me from his chair as i sat next to him, and i put my hand out to shake, and he held his hand up to sort of say 'no thanks'... idk i was just so surprised because i've always succeeded in shaking another brothers hand, so i felt weird\normalsize   & \cellcolor{green!27}Old, Weird & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small 'O people, your Lord is one and your father Adam is one. There is no virtue of an Arab over a foreigner nor a foreigner over an Arab, and neither white skin over \textbf{black} skin nor \textbf{black} skin over white skin, except by righteousness. Have I not delivered the message?' -Muhammad pbuh\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Omg I'm Egyptian and this is sooo true you have no idea how many times I'd be sitting with friends or family and they'd comment on someone's color in a \textbf{racist} way sometimes when that person sitting right in front of them!!! And you're so right they don't even think it's \textbf{racist} when I say something about it to them they'd be like chill it's just a joke and they look at me like I'm \textbf{crazy} and can't take a joke. The sad part is most of them are pretty educated and some even claim they're religious\normalsize   & \cellcolor{green!27}Crazy, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/97 & \cellcolor{green!27}3.093 \\  \hline
  \cellcolor{green!5}\small imo it's more colorism than racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small As a desi who was brought up in an Arab country, I can't stress how important it is to bring awareness to this. Of course this doesn't apply to everyone, most of the 3arabs I knew were lovely and some of my closest friends are arabs but there was always that group of people that referred to you as a "bengali" or "hindi" in a derogatory tone like it was an insult or something. Little did they know there's a difference between Pakistan, Bangladesh and India and Hindi is actually a language, not an \textbf{ethnicity} lmao. Also some ignorant people used to just assume all desis are hindus unless you wear hijab? Like they were legitimately surprised if you told them you could read Qur'an or something loool. Disrespecting other religions was another thing but that's really \textbf{common} in a lot of Muslim majorities (like Pakistan), not just arabs.But like a said, I only encountered a couple of people who did this most of the arabs I knew were very loving and accepting and actually really liked desi culture, as I did theirs\normalsize   & \cellcolor{green!27}Common, Ethnicity & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}2/184 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small jxvf i think the same goes to discrimination in the desi community to dark skinned people and \textbf{black} people x\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small That's so true.. Arab people claim to be "better Muslims" then others just because their language is the same as \textbf{Quran} language but the truth is a religion has no language or \textbf{race}. Actually the only reason why \textbf{Quran} is in Arabic is because it's Quraych's first language Allah swt said in surat Fussilat : "And if We had sent this as a Qur'an in a foreign language other than Arabic, they would have said: "Why are not its Verses explained in detail (in our language)?".\normalsize   & \cellcolor{green!27}Quran, Race & \cellcolor{green!27}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!27}3/86 & \cellcolor{green!27}3.488 \\  \hline
  \cellcolor{green!5}\small Pakistani here! \textbf{Racism} exists here too but \textbf{nobody} ever talks about it so people go about making \textbf{racist} remarks without paying much attention to it. I hope we all change our mentality too Thanks for thissss ✌✌\normalsize   & \cellcolor{green!5}Nobody, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small Elitism is \textbf{common} in every racial group, even among tribes of the same land.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Subhi bro ur awesome. I'm Palestinian too. I'm from Ramallah. My family speaks the falahi dialect. We don't say "Keef halak" we say "cheef halak". But bro \textbf{common} Arabs were the chosen people and the \textbf{Quran} says so. And also the third most holiest sight in Islam is masjid al aqsa which is in Palestine which means Palestinians run this bitch. Wallah bro Palestinians are the best\normalsize   & \cellcolor{green!5}Common, Quran & \cellcolor{green!5}Religious Identity - Muslim, Social Class - Working class & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small Jalil Foty ignorant so called Arab here lmao. Where does it say arabs are chosen ppl in the \textbf{Quran}? lol the \textbf{Quran} actually says otherwise '"The Arabs are the worst in disbelief and hypocrisy, and more likely not to know the limits of what God has sent upon His messenger' 9:97\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small Star dust 90In my email it says the person who made your exact comments was Somali Shia 4eva. Now the name is different. Just want to know if your Muslim or not. While after looking into it you are correct. The \textbf{Quran} does not specifically say that Arabs are the chosen people. And truth be told the prophet did say Arabs are no better than non Arabs. Those who remain steadfast in prayer and fasting and truly believe in allah and the last day are the ones who are superior in the eyes of allah compared to disbelievers. However masjid al aqsa is in fact in Jerusalem which is in palestine and or Israeli occupied stolen territory. But I thinks facts point to where the location of the masjid really is.\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/132 & \cellcolor{green!5}0.758 \\  \hline
  \cellcolor{green!27}\small Aywaa Ba'aa Ma tigii roh bel ahwaa waa seeer asaaab 3ala geninaah (Egyption Accent) By indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I come from a Persian background and this rings just as true. I think a lot of it does have to do with our cultures existing and progressing in the context of war, political strife, whatever it may be that makes us part of the "developing world" as opposed to the "developed" or western world that has been able to have the convenience of opening up large, nation-wide discourses about \textbf{race} or other progressive topics instead of having to worry about living under occupation or where their next meal is coming from\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small "An Arab has no superiority over a non-Arab nor a non-Arab has superiority over an Arab; also a white has no superiority over \textbf{black} nor a \textbf{black} has superiority over white except by piety and good action" - prophet (saw). It's sad how much we as an ummah have deviated. You also don't know whether to laugh or cry when people think that it is the colour of their skin or their \textbf{ethnicity} that will do them merit. This type of thinking is also ingrained within the Asian community where being fair is considered being beautiful. Seen it within my own family. We can only educate and try to follow the teachings of Rasool (saw), with the hope that the noor from that will also affect those around us as well as ourselves.\normalsize   & \cellcolor{green!27}Black, Ethnicity & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/133 & \cellcolor{green!27}2.256 \\  \hline
  \cellcolor{green!5}\small I'm white and I think gorgeous arab muslim women like you are lovely and I would love to start a family and have children with someone like you. If you have brown skin I love it even more because I'm very light skinned and think the contrast looks great. Does that make a \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small If you're someone who feels they are better than anyone on ANY basis, be it your \textbf{race}, your skin color, even your language, please remember that arrogance and pride are diseases of the heart. The Prophet (saw) said "None shall enter the Fire (of Hell) who has in his heart the weight of a mustard seed of Iman and none shall enter Paradise who has in his heart the weight of a mustard seed of pride"\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small Lol, this applies to Turkish people as well. Some genuinely think they're the shit because of their \textbf{nationality}. So much \textbf{racism} against Arabs (Syrians) and Kurdish people; it makes me ashamed of my heritage.\normalsize   & \cellcolor{green!5}Nationality, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Kay Bell i am an arab and turks are very \textbf{racist} (not all) and consider themselves better and think they are superior to us arabs. just because turks are whiter than arabs does not mean that they are better. i love my turkish brothers and sister. please stop looking down on us. we are the same...HUMANS!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small we are not \textbf{racist} but that's true we are prejudiced against syrians, because they're fucked up our country\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small nina a you can sure for this; we are so different you. i'm not saying this badly, but so many different tips in turkey, example east turkey kurdish look arap, \textbf{black} sea look europian people, west regions in turkey looks greeks.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small So what if those people happen to be like what 100 of your family??Ehh no grandma thats against our religion. El Rum 22...explains it all.And you know what21 is about Allah creating our partners and RIGHT after that comes 22 which is about \textbf{race} and language.Oh and another thing. No one is 100 anything. No one. Have you forgotten about the first prophet and the start of our existence?? We are ONE with every single human being.But if you think like darwin did.. well..you are one with every bacteria, virus, animal, tree walrus dolphin etc ever existed...what about that??\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/104 & \cellcolor{green!5}0.962 \\  \hline
  \cellcolor{green!27}\small And this is what aggrivates me about arabs they look down on people but then when everything goes wrong in their country and they need to flea they look to the same people they looked down on and expect the world of help when they have just been \textbf{racist} and ignorant to those people. I just don't understand 😩\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small I am a Somali in my culture Somali's do think they are superior than all Africans .This is surprisingly \textbf{common} in every part of the community even the young and especially the fobs\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Dahir Fatma I have come across many Africans who try to make me feel bad about being Somali, saying disparaging comments about my culture or country. Sorry but many Africans are also extremely hateful towards Somalis too, it's not just us being \textbf{racist}. BUT people like to put the entire blame on Somalis only\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small \@Bahjo Mohamed u are \textbf{african} lol where is somali\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small It's a vicious cycle and i feel that south-east asians don't have the right to complain about this injustice because they also treat \textbf{black} people just as bad if not worse.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small ahahah exactly!!!! I think every \textbf{race} has \textbf{racism} in it to make them feel better about themselves!!!\normalsize   & \cellcolor{green!5}Race, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small tbh yes! Most of arabs think they are better than others. They dont know how they hurt others while talking.  hope they can understand Islam doesnt talk about ur \textbf{race}, color, \textbf{nationality}.\normalsize   & \cellcolor{green!27}Nationality, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Superiority complex is in every \textbf{race}. Talk about Malay in Malaysia. Japanese in Japan. White in USA. Just name it.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Thanks for making this video! It's really so shameful how stuck up our cultures are. And it's such bigotry when everyone's always going on about how Islam is a merciful religion, and that the prophet taught us to be loving and kind and treat everyone equal, but then you always hear someone refer to a \textbf{black} person as  "abd" and make low and high key \textbf{racist} remarks about everyone from India to China. Not to mention the sense of superiority arabs hold against each other, between countries and even in their own countries (the more someone resembles a white person, the more they're shown kindness and respect and vice versa). This really needs to stop. We really need to start being more aware and not let things slip by unnoticed.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/130 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Salaam. Hats off to you Subhi for addressing something which hasn't been before! Daaaymn it! I've visited many Arab countries and it infuriated me each and every time!!! I'm a British, \textbf{Indian} but when I'm the uk you don't get recognised as being British and on the other hand, whilst travelling you get idiots at the airport (arabs) who stop you at the airport and hold you back just to have a laugh at your expense.i can't even count on my hands how many times they stop us and ask if I'm really Muslim. Hello I have a Muslim name! Urgh. I'm just ranting now Saudi Arabia are notorious for this...\textbf{nothing} against Arabs but this is disgusting behaviour and these people need to be told. It is in the hands of the younger generation to iron this problem out and point this out to individuals they know when witnessed.\normalsize   & \cellcolor{green!5}Indian, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}2/149 & \cellcolor{green!5}1.342 \\  \hline
  \cellcolor{green!27}\small i experienced that once. when i was went to makkah and i got light wifi connection, arabian guys like hitted me tru some apps. i ignored their messages but cuz one of them like droped me text and like forced me and told me somethin like this "hey lets meet, our location is not really far, i work in a hotel near masjidil haram, and if you dont wanna meet me you loose your chance to meet a great arabian guy who born aand rised in makkah and we are special cuz we are the decent of prophet Muhammad SAW (PBUH)." i was just like stood stupidly read that message and start to think " am i not the decent of prophet Muhammad SAW?" :D .... masha allah, that made me throw my phone and like trauma to open my phone when i was in makkah. and some of them address my mother as "MELAYU" cuz my mother has fully south east asian face and put my mom in LONG LONG LINE to reach a place, while i can passed the line cuz my height and \textbf{black} abaya i wore. they maybe think i was arabian and let me passed first. yallah i hold my mother hands and told them "UMMI" ..... wallah your video reminds me to that bad experienced subhi, HAHAHHAHAHA  Allah blessyou inshaalah :)\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/227 & \cellcolor{green!27}0.441 \\  \hline
  \cellcolor{green!5}\small Appreciate this video but let's not baby these people. A lot of them do know what they're saying is in fact \textbf{racist} and bigoted. And the younger generation can't be excused for \textbf{racism} because it was "brought down". Everyone knows what's right and wrong\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Spot on Subhi. I was born and raised in Saudi Arabia, and I am of Bangladeshi descent. Astonishing how most of the Arabs there think everyone else is beneath them. I personally haven't seen much of it as I can speak Arabic AND am 'light skinned'. But those that aren't suffer massively. As you say, not just with Arabs. \textbf{Racism} is rife within the Bangladeshi community too. Anyone with 'light skin' is considered beautiful, just because it's bloody closer to white. This shit needs to end. Totally against the teachings of the Prophet SAW.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small May Allah bless you brother for speaking the truth. Be proud of your \textbf{ethnicity} brother, don't let anyone drag you down because of it. Respect it, and respect every other ethnicities. :)\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small We took this ideas - that white are superior more beautiful - from the europeans. After decades they have  changed (or are trying to) but we still have the same wrong belief. Why do we always take the bad ideas from the western countries ...? It's so sad.Every time I go to Egypt I feel like people are much more \textbf{racist} than European. At least the europeans don't disparage the people that are from their own country...\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Spot on. I have conversations with my Pakistani family members about colourism and how the ideology that a lighter skin tone is better than others is so flawed and makes no sense- biologically those with darker skin are more resilient to things like sun damage so how could light skin be more worthy just because of one persons' idea of 'beauty'? Yet, its so deep rooted into all cultures that explaining makes no difference to some people. We need to remember that our \textbf{African}, Afro-Caribbean and \textbf{African} American brothers and sisters are treated most unjustly by other Muslims. We have to be conscious of this in order to make a change.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/111 & \cellcolor{green!5}1.802 \\  \hline
  \cellcolor{green!27}\small Absolutely. This is exactly what white privilege is. The whiter or 'closer to white' you are, the more normal you seem and the more 'easy' it is for one to integrate and be accepted in society. I have plenty of \textbf{black} friends who go through rubbish like this on a daily basis. And it has to end right from the core. From within. From the house. Probably end up marrying a \textbf{black} \textbf{woman} at this rate lol\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/77 & \cellcolor{green!27}3.896 \\  \hline
  \cellcolor{green!5}\small Omg I'm from Bangladesh I was born in England and I recently moved to Dubai I have come across lot of \textbf{racist} people they call us 'miskin' which means poor people I'm very light skinned as well it's really hard to tackle racism\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small IslamPath Those who arabized Levant had no respect for our \textbf{ethnicity} and they still think that we owe them.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small TheBlooRayChannel ShaguftaF2000 true. I'm American Moroccan and I've been living on KSA for the last 10 years of my life.. (i came here when I was 8yrs) and even tho I'm supposedly Arab , Saudis seem to think that they're better than everyone else. Whether Arab or not. A little too \textbf{racist}. Hell, the first thing they ask is "are you Saudi?" . God help us all.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small The notion of Arab superiority predates oil and is deeply rooted in ancient history. Surprisingly, color was not the main driver as Arabs came in different shades. It was the fact that they followed a strict code of "ethics" that valued genealogy and the ability to trace ancestors back to hundreds of years which they believed reflected back on one's personal conduct. It didn't only target non-Arabs as this superiority complex manifested itself in inner-Arab tribal rivalries. Islam came and introduced laws that improved \textbf{race} relations, especially among the first generation of Muslims in Arabia .. it strongly encouraged the freeing of slaves generally and as an atonement for certain crimes. Sadly, it didn't ban it altogether. Muslim Arabs went from having the first \textbf{black} secretary of treasury (Bilal bin Rabah) in Medina in the early days of the Muslim state to enslaving people of all colors in later generations, including white Europeans (Saqalibah). That is not to say it was only practiced by Arabs .. most cultures did it. The only difference is that as Muslims, Arabs struggled to reconcile their pre-Islamic traditions with a new religion that emphasized the equality of all races. This feeling of superiority is a remanent of days past and is mainly discussed behind closed doors since it is frowned upon religiously and morally.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/220 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small Good so why dont u go back to where u came from?   I was attacked like a million times from banagali people IN MY OWN COUNTRY  just because i look like a Pakistani! IM NOT EVEN AN ASIAN!  u asians keep crying \textbf{racism} yet u r the most racists in any country!\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Yasmine Nour people are "much" more \textbf{racist} in Egypt than in Europe. What kind of a \textbf{dumb} logic is that. They created \textbf{racism} itself. KKK didn't happen in Egypt after all\normalsize   & \cellcolor{green!27}Dumb, Racism, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small M SS Egyptians aren't \textbf{racist} against anyone from the West or any other country. We don't have this \textbf{weird} Arab ego and we don't feel like we're the blessed \textbf{race} because we're originally not even Arabs amd she can't say we are or any Arab is more \textbf{racist} than Europeans. \textbf{Racism} was created in European countries and still is one of their biggest issues.\normalsize   & \cellcolor{green!5}Race, Racism, Racist, Weird & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/64 & \cellcolor{green!5}7.812 \\  \hline
  \cellcolor{green!27}\small M SS I'm not sure about the "\textbf{racist} against other Arabs" part but \textbf{racist} against blacks? I don't think so. Our judgement based on skin color is not as high as in Saudi Arabia European countries but that doesn't mean that we are all angels there might be some judgemental people and yes our origin is not Arab. Arabs didn't build the Pyramids you know\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small TheBlooRayChannel  ...same brother I'm \textbf{Indian} but was born in Bahrain and speak Arabic.. some people just assume I'm from Bahrain because I know their language.. But alhamdulilah I haven't found much rasicm.. but mostly when I say I'm \textbf{indian} they get shocked sometimes excited since they watch \textbf{indian} movies and all. But one thing bothers me is that they say "you dont look \textbf{Indian}!" .. what are Indians supposed to look like?😂.. don't get me wrong I don't hate them in fact they're so much kind and loving than I can ever be. And it's true there's also rasicm betweens Indians as well which I witness myself. NRI and all..\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}4/110 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small very light skinned for a bangladeshi means \textbf{nothing} and you're still  brown so just accept it and be proud of it rather than need justification of your self worth from those disgusting people\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Just the fact that mohammad alledgedly has said that muslims should follow a ruler, even if he is balck....says you are wrong about his teaching. lol. So being \textbf{black} was something that he used to show how important it is to obey the ruler...EVEN if he is \textbf{BLACK}  show that this was the worst thing he could imagine that a ruler would be hahahahaha\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/64 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Howl Pendragon Arabs look exactly like Indians many of them do! But oh my didn't most of them miss out on that beautiful \textbf{Indian} hair?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small lets also not forget that so many arab still call \textbf{black} people '3abeed'. GUYS, don't be afraid to call out friends and relatives if you hear them say that word. it's so messed up\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small once  this lady was saying how beautiful this girl was and my best friend was sitting next to the \textbf{woman} in her own world of thoughts and she so happens to be half \textbf{black} half Moroccan so her skin is a little darker and guess what that lady saidshe said even though you \textbf{black} you are still beautiful cause she thought my best friend was feeling down for not being light skin which i found disgusting tbh even my best friend was like why would she say that.\normalsize   & \cellcolor{green!27}Black, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/89 & \cellcolor{green!27}3.371 \\  \hline
  \cellcolor{green!5}\small wiji nhdnd If you're taught (directly or indirectly) from a young \textbf{age} that certent ethnicities are beautiful and others are ugly, it'll be hard to see how ignorant/uneducated you seem. Children believe whatever the people they look up to say, so I feel sorry for that lady for being raised that way. May Allah soften their hearts\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Rose A She severely lacks \textbf{common} sense dear. I, too have dark Pakistani family members but  they are embraced. Coming from a multi \textbf{ethnic} background, we have both light and dark skin tone within my family and \textbf{nobody} is made to feel different or less beautiful which is how I believe it should be. You are beautiful girl. Keep shining.\normalsize   & \cellcolor{green!27}Common, Ethnic, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Social Class - Working class & \cellcolor{green!27}3/60 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small +Rose A smooth dark skin can be VERY attractive to men,including light skinned ones. I had three girlfriends so far and all them had darker skin than mine,I don't care about religion,\textbf{race} and all that stuff,I just love when a girl has brown skin,\textbf{black} long hair and matching eyes,and many white men love that too.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small All Muslim countries have problems some more then others but Arabs have sold there soul to the devil \& sold out the Muslim world, Arab leaders \& countries are so useless that its unbelievable, they have money but \textbf{nothing} else\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small they have money and everything and u HAVE \textbf{nothing} but jealousy and envy\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Yes I'm 100 with bro , but like what you just said in every \textbf{ethnic} groups there is such a thing. So we (people ) no matter Arab or not must change that. Thanks for this great video\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I don't know about others,  but at least the Pakistanis that I know...especially my very own family. ..they constantly put Pakistanis down and say oh look arab Muslims,  turks,  Indonesians etc are so good and better Muslims and look at us. ..and then my family forces my brother to wear a thobe and instead of his regular shalwar kameez (traditional outfit)..i mean be proud of your culture and don't do the wrong things practiced! It's not our fault that just because we have similar heritage as of Hindus,  that we have to adopt evrything of theirs. If pakistani culture is influenced by Hindus,  Bollywood,  India etc  then let it be as long as it is islamic (respecting elders, getting a good education,  working hard etc) just because (others).... they're arab doesn't mean they're better Muslims!! That's a huge generalization! So I think it goes both ways, arab superiority and arab praise from non arab culture. Like stay muslim and stick to your culture! And if there's anything unislamic in your culture,  don't follow it or simply just try your best to fix it or find a solution to it. ....NO need to make your own children feel bad about the culture they were born in. I think a lot of pakistani ppl don't like how pakistanis get major influence from Bollywood whereas Arabs get major influence from their being arab and their history and how they come from the land/race (?)  The prophet came fromI'm not saying that the ethnicities I mentioned  (turks,  Arabs, Indonesians) can't be good or better Muslims than pakistanis. .all I'm saying is that saying evry single one of them is good and flawless is plain \textbf{dumb} and stupid. Although I do agree that in some areas,  other Muslims are better compared to pakistani Muslims.Idk ..I maybe wrong\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/304 & \cellcolor{green!5}0.329 \\  \hline
  \cellcolor{green!27}\small maham meher hello I'm Indonesian and I just want to correct you that Indonesia is not based on only one \textbf{ethnicity}. Indonesian is a group of ethnicities and races like javanese, bugis, balinese, malay, papuans, arab, chinese or \textbf{indian} descents. Indonesia is not the same like Turkey or most of middle eastern countries that is homogeneous. We are heterogeneous and multicultural society but we have identity and our own uniqueness. I know it's not really important but just FYIAnd about the video, I think what he said is not to underestimate his own \textbf{ethnicity}(arab) but just to emphasize that everyone is same just like what Allah says in \textbf{Quran}. Of course I'm sure he's proud of his culture but he aimed it to racists that are still exist in arab society who look down people who are not arab. I've heard it many times from Indonesians who live in Middle East like in SA. At least we need more people who think like Subhi in this way\normalsize   & \cellcolor{green!27}Ethnicity, Indian, Quran & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American, Religious Identity - Muslim & \cellcolor{green!27}4/168 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Ana Sawitri id like to inform you that The republic of Turkey is a mix of all ethnicities. People tend to either cluster Turkey in the middle east or say Turkey is very Western. Turkey is the remnants of a very indigeneous empire. It consisted of all kinds of people. for eg in the \textbf{black} sea region of Turkey there are the Laz people they have the laz language. There are the spanish jews, italians, kavkaz, chepni, turkmen, Rum. In Turkey they would ask which part you are from and ask your ancestry because we are not all Turks. Turkic people are spread out across asia and Eurasia. Turkey is different. People dont realise that.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}\small Us Muslims in Western countries hopefully can eradicate and breed out the \textbf{racism} from our children...... I find that people who stick to their own country and own \textbf{race} are the most closed minded, regardless of where they're from, what's their culture or beliefs. Atleast in Western countries there's a lot more exposure to many cultures and religious tolerance\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small I believe the issue of superiority or colorism is due to western colonialism and the spread of \textbf{nationalism} into the east by the west if you look at Islamic history you would find that this issue did not really exist, Muslim empires often embraced other cultures and intermarried. The issue of colorism is not limited to the east neither but also exist in Africa and Asia. It's sad Islam was suppose to remove this disease of superiority. The prophet warned us against this in his final speech. And It's definitely created division in the Muslim ummah, i see it as one of the diseases that holding us back from succeeding as an ummah. Thanks for addressing this topic much needed.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/120 & \cellcolor{green!5}0.833 \\  \hline
  \cellcolor{green!27}\small A.a I think the Arabs already had this feeling of superiority and practiced \textbf{racism} before Islam (they were known for that), but Islam has successfully eliminated it and then western colonization sadly brought it back, as you said.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Amina Jay \textbf{Nationalism} is older and it works perfectly.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small No. Arab \textbf{racism} existed long before colonialism and long after Islam. Ibn Taymiyyah is a good example of this mentality, a well respected scholar who believed Arabs are superior. Arab superiority is found in many aspects of Islamic jurisprudence, despite many Hadith that run counter to those ideas.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Oh you're very ignorant about history. It changed a little bit in the late abbasi times almost when the Turks started taking over. In the Emevi empire there was a strong movement along non Arabs called shuubiyya and they were all non Arabs who are against the \textbf{racism} and slavery that is done. Search it. It's sad and even till now Arabs say that the movement was wrong when it wasn't. Also a lot of the non Arab Muslim scientists and authors in abbasi times were arabnised and even shamed and discriminated and called infidels for having different knowledge or religion (that is not told to anyone who doesn't dig in the history those people we know now as big were people who were wanted for their heads) and for having a mixed blood or for being completely from another \textbf{race} or writing about things that is not \textbf{common} to Arabs knowledge which Persians and Turks mastered. And even now they still make all the non Arab authors back in the "Islamic history" as Arabs with really smart way like adding "al" in the beginning of surnames as an example instead of well known khavarizmi they add alkavarzimi. Those people suffered a lot sadly the pressure was real. Islamic history isn't something to be proud of just like the times of dark ages Europe. And if people kept believing in what they do \textbf{nothing} will change which doesn't\normalsize   & \cellcolor{green!5}Common, Nothing, Race, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}4/238 & \cellcolor{green!5}1.681 \\  \hline
  \cellcolor{green!27}\small Arabs are even \textbf{racist} to other arabs!! I mean I'm Egyptian and I still get \textbf{racism} for just being "Egyptian". It's unbelievable and I'm glad taha made this vlog, honestly and truly.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Menna Ahmed Hahaha why did you got triggered  ? It's the Truth,  do you really think that speaking Arabic makes you an Arab ? Hahah I'm the one who's gonna educate you here,  There are White people who are able to speak Arabic does that make them Arab ? No, That would be ridiculous. You're speaking English, Does that mean you're English ? See how silly you sound ? No, speaking a language doesn't make you an Arab, and the language you speak is a corrupt language, It's not the original Arabic, but that's another topic....Being  Arab means having Arab genes,  Do a DNA test and compare your DNA with the DNA of a Saudi or a Yemeni, You will see that their DNA is completely different from yours.  Arabs conquered Egypt , That's the reason you speak the language you speak, Your people were already in Egypt and they didn't speak Arabic. Egypt was a Christian Country and the Current Egyptian language was influenced by the Coptic language, The language of the Egyptian people. + There is not 22 Arab countries.  Hahaha Sad to see that so many Egyptians are brainwashed.  You could say Arabic speaking country , Not Arab, even saying Arabic speaking country would sound kind of \textbf{weird} because The language spoken in Algeria is not the same Language spoken In Iraq.  Arabs don't come from Africa nor  did they manage to get rid of the native Egyptians.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/241 & \cellcolor{green!5}0.415 \\  \hline
  \cellcolor{green!27}\small Menna Ahmed Hahaha No I didn't ignored it, speaking a dialect of Arabic natively doesn't make you an Arab, I know white people who grew up speaking Arabic, meaning that Their Native language is Arabic and Guess What, they're not Arab. I'm not sure why you're acting like an immature  13 year \textbf{old} child,  I'm trying to have a constructive discussion but i suspect that you might 13 or 15 years \textbf{old} judging by your immaturity and defensive mode. And I got news for you:  Your DNA does show which region of the globe your ancestors are from, the region you're from.  You seem to be very uneducated, The problem is not even the fact that you're ignorant about your own identity but the fact that your mind is not open to enlightenment.  Why be arrogant and defensive  ? There's \textbf{nothing} wrong about being wrong. Really sad that So Many Egyptians are still trying to be something they're not.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/159 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Pek Mek listen pek mek get off your high horse. You arabs are so prideful. Egyptians are arab do a google search. Or do you need assistance? Since you are so ignorant and clearly uneducated. Why was that comment necessary. The thing is with you arabs is that you are so full of it. When things go wrong in arab countries you want to run to the same peoplw you shun and then you are so self entitled you think you deserve the world of stuff. Please stop with this arab supremacy stuff. It's getting \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small Kay Bell Hahahah You say:  "You Arabs are so prideful" and "Please stop with this Arab supremacy stuff"    You just showed how ignorant you are by making the assumption that I'm Arab and on the top of that an Arab supremacist,   I'm not even Arab hahahaha What Arab supremacy ? Hahaha Assuming that I'm Arab and I believe in Arab supremacy just because I said something that goes against your ignorant world view  just  shows how uneducated you are.  No, Egyptians are Not Arabs. A simple DNA test will show you that, Todays Egyptians are natives to Egypt , just like their North \textbf{African} neighbors are native to their respective countries  (Morocco,  Algeria,Libya, Tunisia). Even Middle Easterns like Palestinians are not Arabs.    Really sad to see so many Wannabe Arabs out there. It just shows that the educational system has failed.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/141 & \cellcolor{green!27}0.709 \\  \hline
  \cellcolor{green!5}\small Menna Ahmed Hahahah I called you what you are: ignorant.  There's \textbf{nothing} immature about it. Read your first comment sweet heart and  by the type of language you use I think I know what kind of person you are.  And no, what I said is not m opinion,  It's a fact, Your DNA is not my opinion nor anyone's opinion. I can identify myself as \textbf{black} as much as I want, That won't make me \textbf{black}. Simple as that.\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/79 & \cellcolor{green!5}3.797 \\  \hline
  \cellcolor{green!27}\small Menna Ahmed  Start by reading about the history of your country and your culture ,   I will  leave the information about the DNA here:  [LINK]     and an article from this year about a DNA analysis which showed  that the majority of Egyptians don't even have Arab ancestors  :  [LINK]      Your people is not Arab, They're \textbf{African}, They're Egyptian.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small unfortunately there is \textbf{racism} even among the Arabs themselves, just like that sad ignorant person over there 👆\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Nehal Shallal Are you \textbf{crazy} ? You're taking about Arabs and at the same phrase implying that I'm Arab when I clearly stated that I'm not Arab. Nor am I \textbf{racist}, Egyptians are not Arabs and there's \textbf{nothing} \textbf{racist}  about saying that.  It's a simple fact\normalsize   & \cellcolor{green!27}Crazy, Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/46 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Pek Mek what I believe and think is entirely none of your business. Please do stop replying to my comment because my beliefs have \textbf{nothing} to harm you.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Menna Ahmed Hahaha Arabs enslaved your people and brainwashed them with this Wannabe Arab ideology and now you guys are excuse of a Once great civilization.   Not  only Egyptians but  Maghrebis are also brainwashed with  this ideology,  I long for the day that this cancerous collective shame of the pre-Arab civilization will end. Egyptians should embrace their roots. \textbf{African}, Coptic, Egyptian , Pharaonic.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small yes she can be bothered you think it's your duty to define who she is and what her culture is when you're not arab or Egyptian have you got \textbf{nothing} better to do?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small blue No you ignorant fool. I don't think it's my duty to define anyone's identity.  What I'm doing is simply waking up Egyptians and other colonized people of their delusion,  their \textbf{mental} slavery. I  have a Palestinian friend who fell in love with a Saudi \textbf{woman} and her family was totally against and \textbf{racist}, he told me how they saw him as inferior. Why would a \textbf{black} person claim to be white ? Wouldn't you think that that person has been brainwashed or has some internalized opression or shame of who they are ?   Egyptians should embrace who they are. I can tell you one thing:  As long as Wannabe Arabs like Egyptians keep bowing down to Arabs they will never be enlightened, Egypt will keep being a shithole and a backwards country. The culture of Egypt is not Arab and will never be. The current Egyptian culture has been infested by a cancer which is destroying Egypt and dividing it's people. Look at the Coptic Christians being  hunt down and killed,  to the ignorant fools in this comment section who are saying that I'm trying to define her identity :  what are you doing to the minorities in your country ? Which people are trying to impose their identity on others ?  Christians are being hunt down for being Christians so don't even start with that BS.   Why are people of color   so quick to march against European colonialism but when it comes to Arab colonialism \textbf{nobody} says a damn thing about it ?  You get what you deserve, The leader reflects the image of it's people,  You got Dictators like Sisi and Assad because you are not enlightened and not prepared to progress and development.  You worship Tyrants, you get tyrants. You live in total ignorance,  look at any middle eastern or north \textbf{African} country and ask yourself,  what went wrong  ? You know the answer.  Keep rejecting reality, worshipping Tyrants  and EMBRACING ARAB COLONIALISM , all you Wil achieve by doing that is your total destruction. By the way:  Tiran and Sanafir are Egyptian !!! Look how weak and pathetic the Egyptian gov't looked like giving it to Saudi Arabia, And the people have the audacity to complain about it when they themselves are Wannabe Arabs, That's what you get for being a Slave of Arabs. TIRAN AND SANAFIR - Egyptian-Coptic-\textbf{African}.\normalsize   & \cellcolor{green!27}African, Black, Mental, Nobody, Racist, Woman & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/394 & \cellcolor{green!27}1.523 \\  \hline
  \cellcolor{green!5}\small Omer Gamal I'm a citizen of the world who stands against Colonialism,  Emprialism, Fascism and Advocates for Freedom, Independence, Justice and Rights for all mankind.   I'm also from the  Gabari school of thought ;)  but I lean more towards the Hitcheni school of though t ;)    My people is the Egyptian people, My people is the Maghrebi people,  My people is Middle Eastern/\textbf{African} people. I'm half \textbf{African},  My identity was also erased by Colonialism and Supremacy,   But Not the Arab one, The European one. I love Mohamed Hamaki and I love Egyptian culture in general. Egyptians are my brothers and sisters, just like the rest of Africans. Peace my \textbf{African} brother. Spread reason and knowledge, the only way to save   humankind from ignorance and slavery\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/125 & \cellcolor{green!5}1.6 \\  \hline
  \cellcolor{green!27}\small Pek Mek Don't waste your time dude, Arab supremacy is an inherent part of Islam and has brainwashed everyone in the Middle East. In addition to politics  and Abdelnasser's "pan-arab" pipe dream.  You're literally talking to people who think speaking a language = \textbf{ethnic}, genetic identity. There are many valid genetic tests and studies done on Egyptians that show they're significantly more genetically related to copts and their ancient Pharoa ancestors than to their neighboring Arab countries like the Gulf Arabs.  But unfortunately they're too far gone to even look at scientific studies. Are you half Amazigh BTW?\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small Pek Mek actually it is true. Egyptians are not Arabs and we know it and we're damn proud of that. I'm an Egyptian myself mixed with other 2 Arab countries that are not originally Arab as well. Well let me tell you that when we speak about Arabs we don't include ourselves and when you state this fact it doesn't trigger us. I'm a person who is really proud to not have even 1 Arab origins and if you consider us Arabs this doesn't flatter us because you're putting a 7 thousand + culture under the Arabian category. We surely all know that the pyramids were built by Egyptians not Arabs. This Arab superiority thing doesn't work on us we're the ones who don't want to be called Arabs not you who don't want us to be one of you. Oh and btw one of the reasons why "you" put us under this category is because of our military forces and we all know that if Egypt becomes independent again your countries will be \textbf{nothing} without us and our protection. The world knows Egypt for its culture not for being Arab. Have a nice day\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/195 & \cellcolor{green!5}0.513 \\  \hline
  \cellcolor{green!27}\small Omer Gamal oh seriously? Don't we say "Arabs visit Egypt in Winter" for example? We call them Arabs like they are not one of us and no more of us don't consider themselves Arabs because we really aren't. Being Arabized does \textbf{nothing} other than bring us down. They only want us to be Arabs so we can protect them because they literally have no military forces\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Omer Gamal Oh yea the whole "gomhoreyat masr al arabeya" started a couple of years ago. This isn't an \textbf{old} thing. President El Sadat was the first one to do this and the first one to convince us about the whole Arab thing. Why are we Arabs tho? Have you asked yourself this question? We don't share the same culture or the same traditions or even the same costume. We're not the same people we're not from the same \textbf{race}. Is it just because we speak Arabic that we are considered Arabs? Australia speaks English but is it a British country? America speaks English but is it a British country? No. Seriously we have been Arabized just to back them up. A freaking 7 thousand year \textbf{old} culture country has lost its identity. We're neither Arabs nor Africans. Egypt is just Egypt\normalsize   & \cellcolor{green!5}Old, Race & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}3/142 & \cellcolor{green!5}2.113 \\  \hline
  \cellcolor{green!27}\small Omer Gamal well one thing that is \textbf{common} between Egyptians is how they think with their heart not their mind which is a cute thing but it makes them believe anything. So I'm different than you guys in this point. I think with my mind\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Menna Ahmed Egyptians are not arabs, different \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Menna Ahmed Arab is a \textbf{race} and speaking arabic doesn't magically make you an arab, definition was created by globalists who want to destroy Levantine identity and it means \textbf{nothing} in reality.\normalsize   & \cellcolor{green!27}Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Pek Mek Pan arabists and zionists force this \textbf{ethnicity} opon us, they would like to keep us in chains.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small +Nadine, You are ignorant, the world and especially the Islamic world knows Egypt as the center of Arab world. Egyptians are very Arab.Egypt protects \textbf{nobody} and is still an ally of the US.  Not very independent.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small exposed yt  okay they're arab now no one has a problem with that.. but if u study the whole thing historically, the language spread from saudi and yemen to north africa and like lebanon and other places.. \textbf{race} wise beduins in saudi and GCC have a different \textbf{race} than egyptians .. egypt was a huge civilization before arabic was even spoken there .. u get me?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small M7mdic Wahaibi i am sorry but .... are you saying that you are from the arabian penensula and you say \textbf{dumb} shit like that ? Arabic appeared in the 9th century by the adnanites but there were people who are called qahtanites smart ass.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Elyahu Akbar So I take it you have studied this person's personal DNA results? \textbf{Ethnic} and national identities are not as simple as you seem to wish they were.  Yes, Egypt has an ancient non Arab cultural heritage, no-one denied that. However, Arab culture has been a huge influence on Egypt for well over a thousand years, in addition to the many people that migrated to Egypt from the Levant and the Arab peninsula. In the modern political sense most Egyptians consider themselves Arab and are considered Arab in a broad sense on the world stage due to their close linguistic, geographical and cultural ties with the rest of the Arab world. This in no way means that Egyptians have given up, or were asked to give up their unique cultural identity as Egyptians. I get that you think you have made a very clear open and close argument, but in trying to substantiate a group's \textbf{ethnic}/cultural identity  by citing "DNA tests" you've only succeeded in sounding anachronistic.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/168 & \cellcolor{green!5}0.595 \\  \hline
  \cellcolor{green!27}\small \@Elyahu Akbar honey majority of arabs are arabized stupid. The levants and north \textbf{african} arabs are arabized the only arabs by DNA are those from the gulf but arab is more than an \textbf{ethnic} background. Its the countries that has progressed their semitic language into arabic and adapted cultural/traditional arabic values. We are all arabs, get ur facts straight!!\normalsize   & \cellcolor{green!27}African, Ethnic & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small baby girl  you are \textbf{African}  Egyptian is \textbf{AFRICAN} IT is in AFRICA\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Mah-Bintou Traore africa is a continent, \textbf{African} is an \textbf{ethnicity} arab is political/lingual and \textbf{ethnic} termWe are Arabized Africans\normalsize   & \cellcolor{green!27}African, Ethnic, Ethnicity & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/20 & \cellcolor{green!27}15.0 \\  \hline
  \cellcolor{green!5}\small \@Elyahu Akbar Arabs are backwards cunts who have \textbf{nothing} to offer to the modern world. what exactly are they so proud about.? lol\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small well we can't paint us all with one brush.. look at all the muslim people here in the comments who are agreeing with Subhi and being against \textbf{racism}. I think we as Muslims have many issues of our own to think about and fix .. but we are no different from any other human being or community in the world (muslim or not)... but yeah Islam is perfect but humans are not..\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small You're right and the only reason the \textbf{Quran} was revealed to the Arabs is that they needed it most lol. Also I have the same bed IKEA REPRESENT\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Aside from the language \& feeling superior because it's the same language of the Qur'an aspect, most cultures are like this and it's sad. Because I am also mixed and literally witness my two nationalities (mostly, but not limited to family) literally bashing each other like "so-\&-so does this-\&-this because they are   (insert \textbf{nationality})  "But it is said in such a condescending way that it makes me want to scream. Cause, first of all, it literally pisses me off so greatly  because.. how.. how are you this ignorant? In a world where there is so much more diversity \& exposure to different cultures.. like how have you not been able to see that we are literally all the SAME?Y'know.. aside from the fact that we have different skin tones \& speak different languages, which, for the record, is epic. What difference is there?I can't -- I can't keep talking about this. I'm getting a headache.Conclusion: don't be a \textbf{racist} pig\normalsize   & \cellcolor{green!27}Nationality, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/163 & \cellcolor{green!27}1.227 \\  \hline
  \cellcolor{green!5}\small The problem is even when you point out that they are being \textbf{racist} they say "so what?" Aaaaaa god help me\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I am Arab, but I study abroad in the US..  And a lot of people from my own country think that I am \textbf{weird} because I have a lot of Chinese friends..  Because I work on campus..  And because I am always smiling around\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Everything you said in the video is true. I haven't realized this about myself untill you said an example of you meant. I do say " oh he is Hindi " or " she is Filipino". It's so built into my mind. Everyone around me says the same thing. And it's not like we ignore the word, it's just okay to say it amongst the culture and \textbf{nobody} minds it. Thank you so much for using your social media to educate us in a very good way. Also, It would be much nicer if you included Arabic caption tho.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{indian} and I always go to Dubai so I experience this a lot. I was soooo scared to speak out about it so thankyouuuuu for saying something\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Fuck Indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Sometimes arabs are \textbf{racist} to other Arabs because of  pride!!!!! 😫 wth\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small RACISM IN THE ARAB WORLD NEEDS TO BE ADDRESSED\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I am hoping that millennials and future generations of Muslims living in the West will be able to eradicate this fitnah in sha' Allah. This problem doesn't seem like it is repairable in Muslim countries in the near future.... As a Pakistani I can read the \textbf{quran} due to same alphabets as Arabi but... how I wish to learn the language of \textbf{Quran} is beyond explainable, and that my children may speak it as their mother tongue in sha' Allah.And the Prophet (peace and blessings of Allah be upon him) said:'The likeness of the believers in their mutual love, mercy and compassion is that of the body; when one part of it is in pain, the rest of the body joins it in restlessness and fever.' Narrated by al-Bukhari (6011) and Muslim (2586).wAllaho a'alam.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}2/136 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Wow I cannot express how relatable and how much I felt every word said in this video.I work as a medical intern here in Riyadh, KSA and as the only half \textbf{Indian}, half Filipino intern amongst Arabs, it feels like I am probably the only one who notices these things. Every Arab patient is referred to by their name but if it was a non-Arab then they are known as "that Hindi guy" or "hada filibeeni", etc and I can go so far as to say that they do not receive the same attention and care as the other Arab patients do. I could actually go on forever about this haha but I truly appreciate the fact that you shed some light on this, and there is actually someone out there other than me who wants to change this 😅You go Subhi!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/142 & \cellcolor{green!5}0.704 \\  \hline
  \cellcolor{green!27}\small Oh I can totally relate to this. I'm an \textbf{Indian} and I've been living in Saudi Arabia for almost 10 years now. For the most part, saudis are actually really nice and friendly. But then there are some who just never think of us Indians as equals. Like you said, people come up to me to ask something and then they realize that I'm not Saudi and go "ohh anta hindi" and then just walk away. Not everyone is like that but there are some who just think we are not one of them (as in we're Muslims too). I also face something similar in India because of my religion (a religion I'm grateful to be able to follow). But it's basically like we belong no where 😓 Wait, I think I know where we belong! Jannah is where we belong, in sha allah 🌸\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/145 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}\small 100 this but as a Muslim brother of Gujarati \textbf{ethnicity}. My family and I left KSA over a decade ago to Canada for my career and it's a little embarrassing to admit that I've been treated better by the hostile non-Muslims here than by some of the Saudi natives back home. To be fair though, I've hardly acquainted myself with European Canadians in my time here since I live in Toronto, but on the off-chance that I have it's almost always a negative experience because I'm outwardly Muslim. Despite all this, I do miss life in Jeddah, the friends I made, the vibrant masjids, the overall friendly people, and the feeling of truly living under Islam. I cannot stress the final point enough, since living in the west inevitably corrupts your imaan. As evidence for this, the general Muslim population where I live are deep into riba and their brains have been hardwired to accept secular liberalism. If it were up to me, I would have never left KSA, even if it meant working a menial job. And if any of you are thinking of leaving your Islamic environment just because of a few bad encounters with non-practicing Muslims, by Allah, it's not worth it. Islam comes first.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/208 & \cellcolor{green!5}0.481 \\  \hline
  \cellcolor{green!27}\small Now you ready for tax lol  madam indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small ShaguftaF2000 true. I'm American Moroccan and I've been living on KSA for the last 10 years of my life.. (i came here when I was 8yrs) and even tho I'm supposedly Arab , Saudis seem to think that they're better than everyone else. Whether Arab or not. A little too \textbf{racist}. Hell, the first thing they ask is "are you Saudi?" . God help us all.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Sadly this is true. I apologize for the \textbf{racist} actions and words you have received from my 'people'. I pray that they wake up one day and realize that we're all humans who deserve to be treated equally.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small everyone is \textbf{racist}, indians also are racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small "O people, your Lord is one and your father Adam is one. There is no virtue of an Arab over a foreigner nor a foreigner over an Arab, and neither white skin over \textbf{black} skin nor \textbf{black} skin over white skin, except by righteousness. Have I not delivered the message?' They said, 'The Messenger of Allah has delivered the message.'يَا أَيُّهَا النَّاسُ أَلَا إِنَّ رَبَّكُمْ وَاحِدٌ وَإِنَّ أَبَاكُمْ وَاحِدٌ أَلَا لَا فَضْلَ لِعَرَبِيٍّ عَلَى أَعْجَمِيٍّ وَلَا لِعَجَمِيٍّ عَلَى عَرَبِيٍّ وَلَا لِأَحْمَرَ عَلَى أَسْوَدَ وَلَا أَسْوَدَ عَلَى أَحْمَرَ إِلَّا بِالتَّقْوَى أَبَلَّغْتُThat's what the prophet peace and blessing upon him said in his last sermon.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small You're so right My grandfather is like that Sometimes he just says "wa7d hendi, wa7d chenwi" And ma grandmother keeps on telling him that Its \textbf{racist} And it is ""funny"" because Hes tunisian And his father was \textbf{black} And now he lives in France And his daughter (my mom) just moves travelling in Asian countries and loves Asian culture and people We keep on telling him that what hes saying is \textbf{racist} but he doesnt see it that way Its so annoying But yeah i find it great that you just talk about it because people tend to think Arab are not \textbf{racist} (they put them in this box with \textbf{black} people and have this idea that only white people are \textbf{racist} NO) And i was just thinking about that yesterday so Very niiiice 7elwaa el video ✌🏻👌🏻😁\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/138 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Omg yes, thank you. As a south Asian Muslim, I can relate 100 to this kind of \textbf{racism}. And it sucks.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I am an \textbf{african} living in an arab country and I'm TIRED of arabs! I mean i grew up with you i speak your language i believe in your religion.. WHY DO YOU LOOK DOWN UPON ME!!I'm sick of \textbf{racism} and feeling that I'm less in there eyes it really hurts !I hate the fact that i have to listen to \textbf{racist} comments about me being \textbf{African} from MY OWN FRIENDS and just laugh because talking is of no use !! These ppl never think they even could be \textbf{racist}! They get offended that you got offended!! They have that Islamic arabic moto that just comes out when they sense someone got offended. Man i wish sometimes if i was just another arab to fit in or if there weren't any \textbf{racism} in the world !But then .. i tell my slef let go you live in a 3rd world country what would you expect there are bigger problems to address.\normalsize   & \cellcolor{green!5}African, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/164 & \cellcolor{green!5}3.659 \\  \hline
  \cellcolor{green!27}\small Names are overrated !! \textbf{Racism} is every where and within every culture so unfortunately moving to another country would not address the issue. You need to call your so-called friends out on it.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Names are overrated !!  I can relate, I used to live in Iran and although we had the same religion and spoke the same language. They would always make fun of non- Persians ( arabs, Turkmens, Afghans, Africans etc..). Especially since I don't look Persian, people tend to be even more outwardly \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Kay Bell no where have you seen that? In America, they sexually exploit women all the time. Look up the rates of \textbf{sexual} harassment and rape in America vs in the Middle East.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small leee baps i'm not speaking about \textbf{sexual} harassment. Abd you know aswell as i do \textbf{sexual} harassment is not well documented in the middle east\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Kay Bell what are you speaking about then? And what does it have to do with \textbf{racism} and superiority the orginal commentor is talking about?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Kay Bell I've seen your other comments. What is your comment about a Pakistani maid being beaten in the street in the middle east and not in America do you think is insinuating? Do Pakistani maids not get beaten in Pakistan? You don't speak for everyone. If you want to address your own personal experience then that's fine but don't make blanket statements. What about the \textbf{racism} and prejudice in south Asian communities towards others? That's more appropriate for you to talk about. Subhi is arab and is talking about what he has witnessed in the Arab community. It's not to open a discussion for a south Asian to attack Arabs. It can't be that bad if south Asians still flock to the middle east right? Also, the examples you give are not so much to do with \textbf{race} but rather with class. Maids are mistreated everywhere. How are south Asian \textbf{doctors} and \textbf{engineers} treated in the Middle East?\normalsize   & \cellcolor{green!5}Engineers, Race, Racism, doctors & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}4/159 & \cellcolor{green!5}2.516 \\  \hline
  \cellcolor{green!27}\small Names are overrated !! Im really sorry u had to face this, but not all arabs are like this. ONLY ignorant people, doesn't matter what their \textbf{race} is, but yes some of arabs have this mentality because they didn't learn enough or so.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Kay Bell yes it is, I'm sure if they were educated they wouldn't be saying a bunch of \textbf{racist} words or so\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I'm arab and i have alot of \textbf{African} friends we can be friends don't be sad 😔\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Don't be disheartened by ignorance. Muslim has no \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I'm sorry you're going through such \textbf{racism}. :( You don't need to change your country you should change your "friends". Being alone is better than being with people who don't love you. Stay strong\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small My sister of Islam please don't lose hope for a whole group of people for the ignorance of a few. And don't ever settle for less when looking for good friendships. A good friendship should never be degrading. I am truly ashamed of how those ignorant "good Muslims" have treated you. May Allah reward your hardship and patients with the highest of heavens and may He clean the hateful and \textbf{racist} hearts of our brothers in Islam and in humanity. Ameen.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Names are overrated !! Hey so I'm Arab and I hear \textbf{racist} remarks from time to time. Honestly, I hate it. I think everyone and every culture is beautiful and unique in their own way. Genuinely. Hope these remarks abt \textbf{race} stop because thats what needs to happen. X\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small The worst thing is not being validated or making it seem like you're hallucinating. I am not gonna lie to you growing up \textbf{black} in the Arab world damaged my self-esteem as a child and it took time for me to recover being in the U.S now, not saying that the U.S is perfect but at least \textbf{racism} is discussed and not denied as much the Arabs do. Confront them and if they keep on hurting you then they are not real friends. Good luck to you and always remember that you matter and your blackness is beautiful!\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/98 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Names are overrated !! 10 from Arabs like that not all of them at all it's the same in Europe countries you will see some of them also hate the \textbf{black} and the Asian and other\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Thank you for this, my mum is half Arab and half East \textbf{African}, so she's been through it all\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small How is it like growing up as half arab half phillipino? My nephew is in the same boat, he's only 5 months \textbf{old} but I'm worried for his future. I'm full arab and get discriminated against just because I haven't lived with Arabs for 18 years, so I can't imagine the treatment for someone who's half.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Oguz K. I live in turkey .. and they are less \textbf{racist} .. I'm \textbf{African} and they've only treeted me with respect! I know turks that are married to Africans and it's totally normal for them they don't give any negative comments or \textbf{racist} remarks. They act like muslims tbh .But then i think turks FOR SURE look down upon arabs .. i talked with an Egyptian friend in arabic on the buss and everyone was uncomfortable and like 'offff' ing to us 😂😂 the funny thing is that other turkish teens where speaking loudly and laughing yet no one was bothered 😂😂 but arabic talk bothers them??Also they treet some arab \textbf{nationality} in a condescending way.\normalsize   & \cellcolor{green!5}African, Nationality, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!5}4/119 & \cellcolor{green!5}3.361 \\  \hline
  \cellcolor{green!27}\small Turks look down upon Arabs for one of the other reasons. Which is around WW1, where the Arab tribes were set up against the Turks, by the English. We actually fought some Arabs, and to this day, a lot of Turks have not forgotten that. My father for example always brings that up. Funny things is, my whole friend group is Arab (like 95 Moroccan) haha. They love Turks and the Ottoman Empire, they stand by it. So yeah it is kind of a \textbf{weird} relationship. Then some Arabs do hate Turks too. But now it sounds like all Turks hate Arabs (which is not the case btw) there are lots of us who love them back.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/117 & \cellcolor{green!27}0.855 \\  \hline
  \cellcolor{green!5}\small Oguz K. yh but Morrocons are north \textbf{african}. i mean i agree the grudge should go and in Turkey there has been brianwashing since the republic. but they also eradicated the essence of islam. Arabs can be another level. There culture can be viewed as rude. And they seem not to care if they are disturbing people. I dislike \textbf{racism} its ridiculous.\normalsize   & \cellcolor{green!5}African, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Happens in Somali culture aswell. My parents are so \textbf{racist} and they don't even realize it\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Idïl Somalis are not \textbf{racist} at all. They are just fearful of the unknown. Once they get to know you all their prejudices will fall way, of course we have minority who are \textbf{crazy}(I mean they hate on follow Somali tribes) but majority of us Somalis are dope people\normalsize   & \cellcolor{green!5}Crazy, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Thanks for highlighting this issue. We definitely don't have a lot of public influencers that talk about racial supremacy or even anti-blackness (from non \textbf{black} poc anyway) because everyone gets so defensive. I remember one beauty blogger who talked about \textbf{racism} within Pakistani community towards Bengalis/Africans and she received a lot of backlash from people crying "but not all Pakistanis!!" - I wish people stopped focusing on 'not all people' defense but rather on the issue that YES there ARE people in our communities that (even unintentionally) hold \textbf{racist} views. And discuss HOW we are going to rectify this problem. I'm Bengali and we have a lot of colourism and anit-blackness issues even though we are dark ourselves - and I am always being vocal to my family about it because change happens at home first!\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/136 & \cellcolor{green!27}2.206 \\  \hline
  \cellcolor{green!5}\small Thank you Subhi for putting this out there! Much respect that it came from you addressing this type of \textbf{racism} which exists all over the world, As Muslims, as the youth we must unite and not let allow our differences in language,culture or colour divide us...yet it should be a blessing that we learn from each other and be better muslims! 🇬🇧\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small \@Xtylish B go get a life and learn how to answer the comments with a proper answer not talk about irrelevant subjects. \textbf{Nobody} asked about your opinion on gays unless you're an undercover one who feels the urge to bring up this topic all the time Lol\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@Rasha Zedd you are \textbf{g\textbf{ay}} hahahahs\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Xtylish B I'm not \textbf{g\textbf{ay}} I'm a girl you idiot! I won't be arguing with a kid who's addicted to PUBG go get treated Lmaoo\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Everything you said r true!sad and funny but true!Arab ppl also should check with skin color issue.they kinda obsessed with white.Most of them think all subcontinental ppl r \textbf{black} and less Muslim then them.which is not true.😦😦\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small i want to share this, me and my cousin have the same last name which is related to arab. So basically we are pure indonesian and the name is from our great grandfather who was yemeni. we raise in an "arab" culture but the difference is she takes this arab culture too far. she's bluntly \textbf{racist}, always saying "why is chinese everywhere?" "indonesians will never be in the same level as arabs" "i hate indonesian, they won't understand the greatness of arab" "why would you go to indonesian schools? you're wasting your time." she sounds even more stupid and ignorant when she said "whoever has the arab last name should know that assegaf (her last name) is one of the best and we need to realize what's in our blood".   😂😂\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/131 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}\small kinekine96 in kuwait we dont have colorism instead we have shea vs senah Kuwaitis vs others My friend is syrian her mom is kuwaiti she was born in kuwait i can't tell you how hard to her to live in kuwait because of the \textbf{racist} comments she gets even from her own family Wallah god bless us and our culture I hope that we get better\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small As an Arab I agree with what you said 100 !! growing up with an all Arab friends and family members, I can testify  that there is a huge problem with our culture concerning \textbf{racism} and it disgusts me. I am an Egyptian that grew up in the UAE, and there I've met and befriended people from all cultures whether Arab and non-Arab. Just looking back at it, makes me feel ashamed of how this sickening mentality has seeped through our minds without realising it. Arabs also are unfortunately \textbf{racist} not to the non-Arab only but to other Arabs as well. Of course I am not generalising but there is a problem.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Racism can be seen at many levels... there is an Arab/non Arab things but what strikes me the most if the one about descent/nationality and skin color.Most of the issues can be solved by using \textbf{common} sense and abiding to basic principles of Islam (no discrimination whatsoever). Beautiful to see you encouraging your viewers to speak up and "be" the change through their own behaviour.\normalsize   & \cellcolor{green!5}Common, Racism & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small OH MY GOD , YOU DONT KNOW HOW MUCH IVE BEEN ARGUING WITH PEOPLE THIS YEAR , 20 17 . ABOUT IT . ITS SO ANNOYING . Like ,  Ik this is going to sound \textbf{racist} , but The arabs , i mean the arabs from saudi arabia , most of them have this feeling , Yall i love saudi arabia , country of the prophet . BUT FFS , THEYRE SO \textbf{RACIST} TOWARDS , THE LESS ARABS.  ITS LIKE THERE ARE DEGREES OF ARAB . LEVEL 1 , 2 , 3 AND THEN COME THE NON ARABS . LIKE OMG HELP ME YA ALLAH\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small As a Saudi, I would say this isn't true. I was born and raised in Saudi Arabia. I'm a Saudi myself and have so many Arabian friends and classmates from other nationalities. I've never witnessed \textbf{racism} nor heard a friend complain about it. You saying "Most of them" is Fasle. There is \textbf{racism} in all countries, I myself have experienced \textbf{racism} when I was at a summer school in Lebanon. Does that mean "most" Lebanese people are \textbf{racist}? Hell no.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/80 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small soso117  Whenever they would discuss about deen ,i would come witj ahadeeths and daleels , but they just shrugged me off , and sakd that they know more about it , becausw they were saudis . They had this mentality that i didnt understand? , they respected me  , but were lowkey \textbf{racist} toward me , they had their own clique , and would start talking in their dialect whenever others were near , they had this feeling of superiority , and u see , i was respected less than the khalijis and southasians because i am moroccan (north \textbf{african}) , but i was respected more and taken into consideration compared to my european and \textbf{indian} muslim classmates . It was really hateful  to think that we were one body (muslims) but it was true.\normalsize   & \cellcolor{green!27}African, Indian, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/135 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small this is so true!! when i learned to learn the \textbf{quran} as a turkish girl some arabs would make fun of us? for saying it in a different way and i still get that we say words like vallah wrong but its literally that our pronounciation is just !! different!!\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Hmm I'm not Saudi but I'm living here and just like soso117 said, they have been so nice to me. I know a lot of terrible Saudis (mostly they've been boys ahaha) but really they aren't that much, honestly. And Saudis especially are very nice to Sudanese people (I'm Sudanese), honestly they're one of the few Arab countries that have respect for us. I can happily say that I have never been wronged by them and my father also says in Sudanese, "ma gasaru leyna"! Yeah there are some \textbf{racist} ones but these ones are \textbf{racist} to Saudis that are dark-skinned as well, so I don't really care what they say. :)I have been mistaked for being Saudi and \textbf{Indian} though, and I can assure you the difference! This happened TWICE before, I'm looking outside the bus in the morning, this random Saudi guy rolls down the window and makes fun of me for being "\textbf{Indian}" by attempting to sing an \textbf{Indian} song. Some of the boys in my neighborhood tease and make fun of me whenever I hang out with my \textbf{Indian} friends 'cause they think I'm \textbf{Indian} as well, and when I talk Arabic back to them calling me names in Arabic they get all shocked.  but tbh even some of my \textbf{Indian} friends have said \textbf{racist} things about Saudis because of how much they hate him.. both are at fault. :(\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}9/235 & \cellcolor{green!27}3.83 \\  \hline
  \cellcolor{green!5}\small Som Ebody yeah true , i know alot who arent \textbf{racist} . But ive been through shit .And i know f sure that most of the pure blood arabs despise us\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small I've been living in Saudi since I was 5 and now I'm 27 almost 20+ years and I can assure you Saudis are one of the \textbf{racist} people out there, they may not be as \textbf{racist} to the other Arabs who aren't Saudi like Lebanese Jordanian etc but to an \textbf{Indian} they sure are \textbf{racist} as hell. Sorry but this is the truth.\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/63 & \cellcolor{green!27}6.349 \\  \hline
  \cellcolor{green!5}\small soso117 as a Saudi, I would say what OP said was true. A LOT of Saudis are racists and like Subhi said they're not aware of their \textbf{racism}. Your friends probably didn't say anything to you because you're Saudi and this is how you responded to someone calling out \textbf{racist} Saudis. So please, try to listen to non-Saudis instead of trying to invalidate their experiences.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small I did not "invalidate" anyone's experience! don't put words into my mouth. In every country there are \textbf{racist} people. People will feel superior in their own country and this is valid ALL over the world. OP saying "most" Saudi's are \textbf{racist} is what i found offensive. My "friends" are non-Saudi and I do listen to them. You saying they do not tell me about their experience because I'm Saudi is none sense. I've lived in Canada for a couple of years and have experienced \textbf{racism} and I have told my "Canadian" friends about it.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/94 & \cellcolor{green!27}3.191 \\  \hline
  \cellcolor{green!5}\small soso117 I think it actually depends on in which part of that country you are living. Cuz I live in Germany and I was born here and there where I am living there are alot of people with a migration background so there isnt much \textbf{racism} but when you go to east germany ohhj boyyy they will kill you if you look like a arab cuz they would think that you are a \textbf{terrorist}. There where actually arent rly foreogn people are the \textbf{racist} people thats what I have witnessed.\normalsize   & \cellcolor{green!5}Racism, Racist, Terrorist & \cellcolor{green!5}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}3/90 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small soso117 most doesnt include you . Ive had experiences . My parents had experiences in hajj . \textbf{Racist} saudis arent aware of their \textbf{racism} towards us lesser arabs\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small i think some gulf Arabs "khaleejis " are \textbf{racist} in general and not only saudis, if you're an arab from north africa or levantine arab they would view you less than them and think that you want their money. I even heard some gulf arabs  referring to other arabs as poor in a sarcastic way.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Im saudi myself. Arab are \textbf{racist} among them selves too. This tribe cannot marry from that tribe and this region cannot marry from this. It is less \textbf{common} than before but its still happening among them selves too you shouldnt be surprised. Im Saudi but originally Kurd since my great grandfather moved here long ago. Im still not considered saudi by some saudi people. So wat? just dont give a s**t and move on with your life. Don't let them put you down, just walk with your head up you done \textbf{nothing} wrong. Things are changing and new generations are more aware of \textbf{racism} and changing inshallah. I study in private university and I have friends from pakistan and india and other saudis are their friends too... things are changing so just live your life dear.\normalsize   & \cellcolor{green!27}Common, Nothing, Racism, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Social Class - Working class & \cellcolor{green!27}4/136 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small soso117 you haven't experienced it bc your Arab and not \textbf{black} so please don't speak on what you don't know\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Thank you for sharing this! Just wanted to share my experience too. In my country, Singapore, we're (alhamdulillah) quuuite united in terms of \textbf{race}, culture, religion etc. However, that doesn't mean \textbf{racism} doesn't exist. It is VERY MUCH alive, just that majority of the people here normalise this, which is so so sad because they think that \textbf{racism} is only exclusive to the US. SEE FOLKS THIS IS THE PROBLEM RIGHT HERE. I've personally received remarks from random strangers eg. "wow you're in a university? You're smart for a Malay girl" and "you speak well for a Malay". I've even heard things on the street (and whoa, the things people say are so upsetting). I try my best to politely call people out on this, but they take it as a joke like "man, don't be so serious", "it's true right?" and "he/she also said this". LMAO just because other people say this doesn't make it ok!!!! And you're right about the family/relatives thing - it's even harder to call them out on this because of our family tie and my respect for them. s i g h.\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/188 & \cellcolor{green!27}1.596 \\  \hline
  \cellcolor{green!5}\small I literally live \textbf{racism} within people of my own country, i try to clean it up each and every day but people are so close-minded it's \textbf{crazy} !\normalsize   & \cellcolor{green!5}Crazy, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Im so inpired by ur vids dat i cant xplain,ur genuine ur generous ur humble n ur polite too...i wish all da arab ppls think dat way da way u think..bcoz evn i hv worked in gulf fr couple of yrs n i did felt da same \textbf{racism} big tym..so thanks Subhi 😊\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small The 2 persons who disliked this video are openly racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I disagree with you wearing an abayah isn't imitation of Arabs it's called the dress code for Islam 😩and wearing a thobe is part of sunnah as the prophet muhammed used to wear it . Arabic isn't only for Arabs it's the language of the \textbf{Quran} so anyone can speak it . Get off your high horse and educate yourself . You clearly cannot differentiate the difference between culture \& islam.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Sabz Ismail I also see wearing an abaya as an Islamic dress code and the dress of the Prophet Muhammad (saw). That's why I'm proud to wear it as a separation of the other religion of my \textbf{race}, to show I represent Islam. Sorry to go against your view \@Kay Bell 🙈🙈 But see it as more Islamic than Arab. Islam does not belong to the Arabs any more than it belongs to the Turks, Africans, Malaysians, Tartars, Pakistanis, Indonesians, Iranians etc.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Ayesha Sheik exactly but they have this superiority complex because the prophet pbuh was an Arab and that the \textbf{Quran} is in Arabic . They seriously need to humble themselves because the religion of Islam doesn't belong to them.\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Kay Bell Christians do, they also have a \textbf{race} problem. The non white Christians blindly look up to white Christians for who knows what possible reason. Jesus gets depicted as a white man, not an Arab. In some \textbf{African} churches, the head priest is a white man and below him are the \textbf{black} priests. We should be glad Hazrath Bilal and Sayyidah Hajra were given such high status in Islam, both being \textbf{African}. No matter what any Arab says, the first Muazzin was and always will be an \textbf{African} man.\normalsize   & \cellcolor{green!5}African, Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}5/90 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Kay Bell people only learn arabic so they can learn the language of the \textbf{quran} and maybe one day be able to understand what the message is and its mostly not trying to be arab\normalsize   & \cellcolor{green!27}Quran & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small you are probably the most stupid person i've ever met. other races (non-arab)  know how to appreciate other cultures, and not translate the appreciation as a signal of inferiority. If an \textbf{indian} likes italian foods or language, italians dont translate this as 'we are superior.'  it seems that you arabs have a problem understanding that.stop translating the unfortunate minority who like your cultureless stuff, as them 'worshipping you.' appreciating other peoples customs and cultures is a global trend.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small no one is misunderstanding what you wrote - so stop talking shit. you clearly said that arabs and non-arabs play a part in feeding the arab superiority complex. i love how other cultures (who are civilised), can appreciate other cultures, and not translate this into 'being superior.' as a south asian, i can eat chinese food or go to a caribbean carnival - but these races wont think that i am 'worshipping them/trying to imitate them + be them.' but me wearing an abaya or thobe is trying to 'be arab.'  - non arabs learn arabic and wear thobes/abayas? guess the \textbf{quran} should be in a different language then, and what other loose /unfitted piece of \textbf{black} cloth should we wear when we pray?you guys really need to get over yourselves. if it wasnt for your oil you discovered a few years ago, y'all would all be more trash and stuck in civil wars.\normalsize   & \cellcolor{green!27}Black, Quran & \cellcolor{green!27}Ethnicity - Black, Religious Identity - Muslim & \cellcolor{green!27}2/155 & \cellcolor{green!27}1.29 \\  \hline
  \cellcolor{green!5}\small People really need to differentiate between Arab culture and Islamic teaching. Wearing abaya is sometimes not because other \textbf{nation} want to imitate arabs, but to follow islamic teaching.. Learning arabic is to understand \textbf{quran}, but not because we want to be an arab.\normalsize   & \cellcolor{green!5}Nation, Quran & \cellcolor{green!5}Nationality - General, Religious Identity - Muslim & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small At Mas okay. Listen to me at mas. You don't need to swear or act ignorant althought ik its well engraved into ur \textbf{race}. Don't \@ me pls. Why don't you try to fix the huge colourism problem and the huge amount of \textbf{racism} in pakistan and ur problem w fair n lovely yh? Instead of coming after me. I didn't word it correctly. My bad. But you need to get off your high horse as if your corrupt \textbf{racist} country is any better w your widespread drug problem and all the other stuff that goes on there. You built pakistan so muslim could be treated equally and for a thriving economy. Worry about how that's working out and how awfully you mistreat other races and religion etc. You are no better get off your high horse and use better language. There is a way to come to someone to talk about something there is no need for you to be so rude just because we have different opinions. I was trying to show a different perspective and how this kind of behaviour can be misinterpeted for trying to be like them rather than cultural appropriation so stop being ignorant.\normalsize   & \cellcolor{green!27}Race, Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/200 & \cellcolor{green!27}1.5 \\  \hline
  \cellcolor{green!5}\small At Mas you need to get over yourself. Idk why pakistanis think they are so much better than everyone else or deserve so much attention or gratitude when they have \textbf{nothing} to show for themselves and constantly push people away from islam because of their ignorance and ill nature and mistreatment of non-muslims and people of different races.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small At Mas your whole culture comes from india the movies you watch are \textbf{indian} the music you listen to is \textbf{indian}. So please worry about the fact pakistan has \textbf{nothing} to show for itself before you worry about arabs thank you.\normalsize   & \cellcolor{green!27}Indian, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small LOOOOOOOOOOL YOU WANT TO CALL MY \textbf{RACE} IGNORANT ?!? - When yours calls \textbf{black} people 'Abeed' and still practises modern slavery?!Theres colourism in every society, even \textbf{black} societies, but y'all and your crusty fake asses take it to a whole new level. we dont call in millions of  foreign workers,  steal their passports of , refuse to pay them, beat them sometimes kill them etc.You clearly are an idiot because Afghanistan is the country with the heroin/opium problem - not Pakistan. Yes - Pakistan was a leading modern muslim country. It resembles and represents Mughal culture and the mughal empire. We had a female president twice. it is secular, and women actually have the freedom to do what they want. But extremism which comes from your countries, and is funded by your corrupt billionaires like Bin Laden have spread their arab cancer to our countries. the only person who is ignorant here - is you for thinking that a muslim wearing a thobe is them trying to beg being arab LOOOOOOOOOOOOOOOOL\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/173 & \cellcolor{green!5}1.734 \\  \hline
  \cellcolor{green!27}\small i am not trolling? i just cant believe that some people have the audacity to blame arab-racism + superiority on non-arab muslims who exercise muslim traditions. the reason why arabs are \textbf{racist} is not because of south asians/africans wearing thobes. this is a extremely pathetic excuse.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Tbh at the mosque I always wonder why most of non arabs not wear abaya when they attend the mosque(not that I'm trying to force it on them) but as in it's a \textbf{black} outfit and can be worn with anything and easy. And I would think that they're trying to hold onto their culture outfits which is nice of them and there is \textbf{nothing} wrong with it.\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Cannot agree more to the first line of your comment. Not saying non Arabs made Arabs \textbf{racist}. But we sure did help them become worse by thinking they are superior. Bt its something they tried enforcing on us.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Kay Bell Ma'am you're extremely rude and did you say Pakistanis think of themselves as superior? How many years have you lived in Pakistan and for how long? My father went to Dubai a few years back and the first thing he told me was how rude and inconsiderate most native arabs were not just to him but to all foreigners even on the damn airport. He said he never experienced that in any of travels to the US because no matter what they treat you politely. My sister lived in Saudi Arabia and she narrated the arrogance with which Saudis treat South Asian workers and it's beyond anything you can imagine. Pakistanis don't have a superiority complex that does not mean that every Pakistani will be inclusive of everyone but they don't treat you like shit the way some Arabs do. Your own comment proves that you lack basic manners on how to deal with criticism. There is colorism prevalent in most societies including Pakistan but people don't treat foreigners living in their communities as lesser humans as a norm. It actually was an \textbf{Indian} incident in which \textbf{black} Nigerians were attacked and beaten horribly in a mall this year not in Pakistan. We struggled for our own country so please don't pass those holier than thou snide remarks in our direction informing us how our country is less Islamic and it's inhabitants lesser humans.\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/236 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}\small You shouldn't be replying to a \textbf{racist} comment with another \textbf{racist} comment. You just stooped to this person's level. Insulting an entire \textbf{nation} that in fact was built for Islam and for which millions of people died is quiet insulting and tragic. A Muslim wouldn't do that, Arab or non-Arab! And unfortunately, you just proved the point of this video. As soon as you were insulted you broke and put the rage of one person on an entire group of people. Every country has problems and Pakistan does too. The fact that you said it is "well engraved into your \textbf{race}" just reaffirmed the fact that your comment was not a misunderstanding it was the \textbf{racism} in you that you are unwilling to admit. Not all Arabs are horrible or have a superiority complex but unfortunately you do.\normalsize   & \cellcolor{green!27}Nation, Race, Racism, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}5/138 & \cellcolor{green!27}3.623 \\  \hline
  \cellcolor{green!5}\small This video made me feel so much better. I realised while watching the video that i always subconsciously envied arabs for knowing the language of the \textbf{quran} and i have to work so hard to understand it. I guess now i understand that the more mujahidah i do the more sawaab i ll get (inshallah)\normalsize   & \cellcolor{green!5}Quran & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Issssaaa bout time someone talks about this. It bugs me while being East \textbf{African} because some east Africans even look up to Arabs. It's really sad.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small IKR. We need to get rid of this in the east \textbf{african} community\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Niko Bogatko Egyptians are not Arab also Lebanese people are not Arab Egyptians are actually native to Africa and Lebanese are completely different to Arabs DNA wise so your half \textbf{African} most likely Coptic origin and half native Lebanese\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I completely agree. It's such a deeprooted type of \textbf{racism} that it will be difficult to remove I 100agree that it is a subconcious kind of \textbf{racism} aswell. Sometimes i feel that they are so \textbf{racist} to the point they don't even realise they are \textbf{racist}. Actually I think it is a superiority complex i don't think they are \textbf{racist} tbh\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}5/61 & \cellcolor{green!5}8.197 \\  \hline
  \cellcolor{green!27}\small Im with you, but you should really stop using the Term \textbf{RACE} in America.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Kay Bell yh it's true they grope women. But I've heard not from Arab men but mostly from \textbf{Indian} men.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Islam and the Arabic language does not belong to a \textbf{race} or an \textbf{ethnicity}.The way you react to the wrongful behaviour of some Arabs is completely counterproductive and illogical.Moreover no matter where you go there is a possibility of facing disgusting behaviour and/or discrimination so fear should not dictate your life.Just make sure to avoid places where bad things could happen, be cautious and stay close to friends/relatives.\normalsize   & \cellcolor{green!27}Ethnicity, Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small You do realise you've just generalised all Arabs and are just as bad as the \textbf{racist} Arabs.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small leee baps I AM NOT GENERALISING ALL ARABS I AM JUST NOT SPECIFICALLY SAYING THE \textbf{RACIST} ARABS I THOUGHT IT WOULD BE \textbf{COMMON} SENSE THAT IM REFERRING TO THE \textbf{RACIST} ARABS...\normalsize   & \cellcolor{green!27}Common, Racist & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small Maha not really the just laugh at us for trying to learn 'their' language and it make me uncomfortable thinking about saudi knowing that there are people there that really don't want me there and the ill treatment i may receive. Nevertheless i would still go there but i am just nervous about it. There is \textbf{racism} everywhere but let's be real there are different levels of \textbf{racism} everywhere you go. Some people are more openly \textbf{racist} and some are less.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/81 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small leee baps and let's not lie here it is a very wide spread issue. It's not just one or two arabs it's lots of arabs that have this \textbf{racist} mentality engraved into them\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small The silliness and narrow-mindedness of some individuals should not dictate the way you live your life. Arabic is not "their language" it's commonly spoken (with some differences/dialects) even by non arabs and it's most importantly the Quran's language.Moreover what you highlight is pretty \textbf{common} no matter the language: native speakers tend to laugh at others accents/makes fun of them which is childish. Let them "laugh" and believe that the world revolves around their little self while you keep educating yourself, moving forward.I understand, I am not claiming that there is no \textbf{racism} and that you should not to be careful just to avoid over-thinking and overly fearing.\normalsize   & \cellcolor{green!5}Common, Racism & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small If u want to learn arabic then dont go to saudi arabia. Go to morocco or egypt cuz saudis are soo rude and \textbf{racist} even to other arabs. Moroccans and egyptians are so humble and cool\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Arabs also have a massive colorism problem, they value fair and light skin above all!!! I've called out my mom several time for saying things like "Mashallah she's has very light skin, she's so beautiful" and after asking her is said person was beautiful only because of her skin she didn't know what to say and I told her that it was very insensitive and borderline \textbf{racist} even if she didn't mean it. Its very difficult for them to see outside that mentality they grew up with where light=beautiful and dark=ugly. Like my cousin actually said to me that she'd never marry a \textbf{black} man because her father would kill her and also "what would my children be ?? Arabs, blacks? can't be both" so that's SUPER MESSED UP UGH\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/130 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small I RELATE TO THIS SO MUCH also i was in my home country, Iraq this year and honestly there r lots of \textbf{BLACK} ARABS. Like not africans but arabs who hapöened to have the same skin color and they were honestly beautiful\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small This is soooo true I hear sayings like this all the time and it's exhausting how many times I have to call people out on this. I really hate when they say 'oh shes pretty but tan' when describing somebody pretty with darker skin. During school I always get darker skin and everyone keeps telling me to use fair and lovely!! My classmates were so shocked the other day when I said I would marry a \textbf{black} man if one asked for my hand.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Malak Abuzaid if that's what you heart desires do so sister. At the end of the day as long as he is a good muslim man it doesn't matter what \textbf{race} he is or where he is from. I'm sure your children will be beautiful anyway. Ignore your ignorant friends if they would turn down a good muslim man just because of the colour of their skin sin is on them wish you the best. Inshallah you will find the right man for you\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small And not just that. If there was a family member who's slighlty darker than the rest of the family he or she are automatically called ugly and a "slave" and other \textbf{racist} remarks. I've actually witnessed this kind of discrimination first hand and what baffles me is that this backwards mentality is normalized in a "deal with it" sort of way.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small kinekine96 she can be butt ugly but if she has fair skin and light hair/eyes shes called beautiful by the older arab ladies 😂 my aunt used to not let my cousins daughter play outside bc she didnt want her to get dark and when i asked her why she said we like white skin 😳 mind you i have a \textbf{tan} complexion.i see them using samra in a negative way and its like hmmmm. Growing up too my little brother had blonde hair and he was the only one complimented by arabs how cute he was lol. Luckily younger generation arabs in the west where i live dont have that issue its the boaters or usually the older generation. I do see younger desis with that issue tho. If anything my arab cousins who live up north get jealous of my  california \textbf{tan} and say i wish i had ur skin color.\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}2/153 & \cellcolor{green!27}1.307 \\  \hline
  \cellcolor{green!5}\small soo true! people with light skin and \textbf{colored} eyes are considered more beautiful.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small So truuuue my mom would say the cute and beautiful babies are the white and blue eyed one, and she wants to possibly have grandchildren with lighter eyes because that's more beautiful. It even had gotten to me as well as I grew up and I'm ashamed at myself for unconsciously thinking green and blue eyed people are prettier. I'm not like that anymore alhumdullilah (cuz Asian eyes are attractive, and dark eyes against chocolate skin of \textbf{African} people are gorgeous and I love them)\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small kinekine96 it's also to like arab-african country's like Sudan in Sudan there r from light brown to \textbf{black} but all r Muslim and Arab\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small So so so true, my mom tries her best to not be \textbf{racist} and she has \textbf{nothing} against people of certain races, but she's let it slip once or twice that she feels bad with people with dark skin \& saying that it's mean to call \textbf{black} people "\textbf{black}" as though it's an insult. It's extremely infuriating but that's legitimately the Arab thought process, it's so sad\normalsize   & \cellcolor{green!27}Black, Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/67 & \cellcolor{green!27}5.97 \\  \hline
  \cellcolor{green!5}\small kinekine96 not all arabs, if u go khalij (emarat, qatar, Saudi Arabia etc) there aren't \textbf{racist} to \textbf{black} because there are many \textbf{black} Emiratis, Qataris etc....\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/26 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small I heard that Sudanese-Americans walk around and hear white-Arabs talking trash about them because they think they are \textbf{African} American.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Dark doesn't mean ugly! I'm a white girl and I'm interested in Arabs and \textbf{African} guys!\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Though it's expressed implicitly or explicitly depending on the culture, the skin colour issue in particular is a problem with every \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small LOOOOOOOOOL im both arab anf \textbf{black} and i think im pretty chill ngl\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small kinekine96 man I'm sudanese I can relate to this so much, my dad is Egyptian sudanese and my mom also sudanese but has Turkish in her, when i go to sudan, to my dads family they're all really really fait skinned to almost white, and I'm \textbf{black} but fair skinned I basically look like a \textbf{black} arab/middle eastern hybrid probably because i am. I'm \textbf{black} but when i tell people im sudanese they say ah so that's why you look like that or when to arabs they immediately connect. But you cannot escape \textbf{racism}, even people on my dad side where guilty from it, subconsciously thought they aren't \textbf{racist}.\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}5/109 & \cellcolor{green!27}4.587 \\  \hline
  \cellcolor{green!5}\small Queen of The Darkness  no I'm not even saying they're \textbf{racist} or we to say the least, of course not that's stupid i meant like, it's ingrained in them some of them they don't know better it's the mentality.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Lol "can't be both?"- tell your cousin about \textbf{Black} Arabs cos they exist too lol\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Man, say you're Egyptian and throw em off lmao. But yeah, most will know that South Egypt has many \textbf{black} people like Nubians, etc.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Or when they say things like " ow she's beautiful although she's \textbf{tan} or \textbf{black} " as if it's the weirdest thing they have ever seen\normalsize   & \cellcolor{green!27}Black, Tan & \cellcolor{green!27}Ethnicity - Black, Nationality - British & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Most Arabs are dark and yeah theres a small percentage with light features and tell other people from outside their culture that its very \textbf{common} for Arabs to have light complexion and features. Which is false its not that \textbf{common}.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Alhassan Its usually lighter skinned people who deny colorism  lol. You never heard the word abeed?  U never heard it uttered by ur fam and friends? BTW there is \textbf{racism} in Iraq. Iraq is notorious for \textbf{black} slavery and there was a massive slave rebellion there. Maybe u were blessed with a great educated family. But to deny colorism isnt a overall problem among middle easterners and south Asians come on. Its a huge problem. Maybe education plays a part too.\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small NZ A I never denied colorism nor \textbf{racism} from existing. I simply said that not everyone is admiring white skin left and right..\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Alhassan there r exceptions to every rule but there is a reason why this got 800 likes dear 💅And the colorism doesnt have to be open. Usually its more covert and coded in other ways. As a fair skinned person you are less likely to pick up on it. Blonde girls being called shalabiya even though they are not pretty at all and overweight or grandmothers favoring the more european looking or blonde hair blue eyed kids over the kids who look more arab. Or denying of a marriage prospect for their son and there is \textbf{nothing} wrong with the girl shes just tanned and its blatant why it was rejected. And this is from my experience but my other arab friends and by others as well as evidenced by this thread.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/133 & \cellcolor{green!27}0.752 \\  \hline
  \cellcolor{green!5}\small all people do that including \textbf{black} africans, you're brainwashed by hollywood\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small kinekine96 Your mother did \textbf{nothing} wrong :)\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small ummm the Gulf States literally employ debt "slaves" from poorer countries to build their rich infrastructure.  Also Abeer Kuwiat has a population of 4million and out of that 4million on 1.9 of your population is \textbf{african} soooooooo you really cant talk\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Same with filipinos. I blame partly the casta system that the conquistadors indoctrinated into the society centuries ago. If your status in society and quality of life depends on your \textbf{ethnic} background for 700 years, then of course people will carry on the idea of "the whiter the better." Basically the more creole blood one had, the more of a chance to have a better life, while the native "aetas", who had dark complexions, lived in designated areas away from towns. They could only paricipate in the "developing" society as basically slaves.The casta system in the Philippines can be paralleled almost in the exact way as what Mexico experienced\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small Am I the only that gets took joke of due my pale skin? Daily people are like '' ew you looks like a zombie '', ''omg you never been at the beach? You looks dead! You need more color'', '' are you some \textbf{freak} vampire? '' ecc... My parents are typical Mediterranean (sun kissed should be what you call them) and only one I'd my bros is pale like me\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small kinekine96 I'm a Sudanese person so I'm both \textbf{black} and an Arab. So definitely there are millions of \textbf{black} Arabs. As I grow up I'm learning more and more on the colorist in this world even in my country. My mom is light while my dad is dark however both are Sudanese. Even my mom says and believes that lighter skin is prettier. When my younger sister grew darker, my mom was upset and same for me. She always says how we were sooooo white when we were babies like it's a compliment. It's so sad it needs to stop. Why do we view blackness with such negativity. I remember watching a video where a girl said in her culture it would be much better if the baby was \textbf{fat} rather than dark and fatness is unhealthy. It's really upsetting to see prejudices to things people are born with and can't even control. May God bless this world.\normalsize   & \cellcolor{green!27}Black, Fat & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!27}3/158 & \cellcolor{green!27}1.899 \\  \hline
  \cellcolor{green!5}\small Hassan Ali that's honestly so untrue. I live in khalij and they're actually quite \textbf{racist}. They also take tooo much pride in their country that they always feel superior and treat others as lower.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Well no need for manyake and laff wa dawaranJust fucking realize that people with fair skin look more beautiful than people with natural dark skin.Darker skinned people usually have larger nostrils, unruly hair, and are limited to small number of eye colors limited to the brown/greenish spectrum. You can take your "progressive" and sorry ideals, crumble them up, and shove them deep up 6izak.It's not in the Arab world fair skinned people are preferred. Even blacks themselves really favor white people, pretty sure you can find a few articles about \textbf{black} youth always orbiting around whites in schools.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/101 & \cellcolor{green!27}0.99 \\  \hline
  \cellcolor{green!5}\small Do you know why Arabs favor light skin?? Because real Arabs had white skin and olive skin. Real Arabs never had \textbf{black} skin or dark brown like South Asians(Indians, Pakistanis, Bangladeshi)..So what's wrong with real Arabs like light skin when they are originally light skin? The only people that suffer from self hate are the \textbf{black} Africans, South Asians, and mixed \textbf{black} Africans living in the Middle East who use skin bleach and say "Mashallah" when someone has light skin.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small I'm a pure blooded Arab \textbf{woman} and even my DNA is 100 Middle Eastern like ancient Arabs and I was born with white skin like most of my family and my parents never say anything about skin color...Only the mixed people who call themselves "Arabs" who are not real Arabs would say things about skin color.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small \@Shushu El.. I'm sorry but there is No such thing as "\textbf{Black} Arabs". There is \textbf{Black} Africans and mixed \textbf{black} Africans living in Iraq, Syria, Saudi Arabia, and other parts of the Middle East. There is also \textbf{Black} Africans living in Israel, Iran, and Turkey...And Iraq does NOT have lots of \textbf{Black} Africans. The only \textbf{Black} Africans found in Iraq is in the south city near the Kuwait border called "Basra". And \textbf{Black} people in Iraq are around 1..If there was so many \textbf{Black} people in Iraq I would have met and seen many of them. All Iraqi Arabs I know and meet have white pale skin and naturally olive skin with many hair colors and eye colors...Never met an Iraqi who looked \textbf{black} because they are NOT \textbf{black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}10/129 & \cellcolor{green!5}7.752 \\  \hline
  \cellcolor{green!27}\small \@Selma Ismail. No such thing as "Arab \textbf{African}" country. Sudan is a \textbf{black} \textbf{African} country. East Africans are \textbf{black} Africans and look like \textbf{Black} Africans. You people are NOT Arabs. And real Arabs are from Western Asia(Middle East) NOT Africa. Just because ancient Middle Eastern Arabs conquered East Africa does NOT mean East Africans are Arab. Real Arabs have white skin and olive skin NOT brown skin or \textbf{black} skin. And no, being a Muslim does NOT mean you are Arab. Muslim is a religion. Anyone can be a Muslim. Being an Arab means bloodlines and Arab is by DNA NOT language or culture. Arabs come from Middle Eastern Caucasian DNA NOT \textbf{African} DNA.\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}7/114 & \cellcolor{green!27}6.14 \\  \hline
  \cellcolor{green!5}\small \@Hassan Ali...LOL, Saudis and those gulf Arabs are \textbf{racist} towards \textbf{Black} Africans...And funny thing is many Saudis, Kuwaitis, Yemenis, UAE..etc. are NOT even real Arabs but mixed with South Asians LOL..They don't even look like real Arabs.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small \@Ban Naes..Don't speak about Arabs or Middle Eastern countries when you don't know shit about us...99 of real pure blooded Arabs don't use "Fair and Lovely"...Because real Arabs do NOT have dark skin but white pale skin and olive skin color. Those who sell "Fair and Lovely" Are South Asians(Indians, Pakistanis, and Bangladeshi) people who live in the Middle East. Its the South Asians and \textbf{Black} Africans and mixed \textbf{black} Africans living in the Middle East who use skin bleach and "fair and lovely" \textbf{Indian} bleach creams. I never seen a real Arab who used skin bleach because real Arabs do Not use any skin bleach.\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/106 & \cellcolor{green!27}2.83 \\  \hline
  \cellcolor{green!5}\small \@I like Burritos...Arabs are NOT \textbf{black}. You are NOT an Arab but a \textbf{Black} \textbf{African} or mixed \textbf{Black} \textbf{African}..Stop calling yourself something you are not. Arabs are Middle Eastern Caucasians from ancient Western Asia NOT \textbf{Black} Africans from Africa.\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}6/39 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small \@Ali Muhammed...Sudanese do NOT look Arab even if your family has Middle Eastern Turkish bloodlines. What don't you people understand? \textbf{Black} people don't look Arab and Arabs don't look \textbf{black} and never looked \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small \@SandCastles...No, \textbf{Black} Arabs do NOT exist. Because real Arabs are NOT \textbf{black}. Real Arabs are from Western Asia. Real Arabs are Middle Eastern Caucasians and come from Middle Eastern Caucasian DNA haplogroups..Real Arabs in ancient times had white skin color and olive skin color. Arabs never had very dark skin. Arabs also never had \textbf{black} skin. Anyone who does is NOT a real Arab but a mixed person.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/68 & \cellcolor{green!5}4.412 \\  \hline
  \cellcolor{green!27}\small \@Alhassan.Are you Iraqi Arab or any native Iraqi??..Because most Iraqis have white pale skin and olive skin color which is why they don't complement you since Iraqi people see other Iraqi people with white pale skin. White pale skin is not rare in Iraq its very \textbf{common}.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@Dasha Doll...Are you stupid? You clearly never seen real Arabs. You probably seen mixed South Asians or other people who are NOT even real Arabs but call themselves "Arabs" in Arab countries because they been brainwashed to think anyone who speaks Arabic is an :"Arab" which is a LIE. Most Arabs don't have very dark skin. Most Arabs have olive skin color and white pale skin especially in Northern Middle East where pure blooded Arabs are still found. Real Arabs never had dark skin like Indians, Pakistanis, or \textbf{Black} Africans. Go read history on ancient Arabs and you will see ancient Arabs had ONLY white pale skin and olive skin NOT dark skin. Don't spread lies about real Arabs and stop confusing those mixed \textbf{race} people as 'Arabs".\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/128 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small \@NZ A...."European looking blonde over kids who look more Arab". Are you stupid? What does an Arab even look like?...REAL Arabs have white skin and olive skin. A real Arab can have dark brown hair, \textbf{black} hair, blonde hair, light eyes, dark eyes, exotic light eye colors and so on. That's how Arabs look not those South Asian looking mixed people in the gulf Arab countries who look \textbf{nothing} like ancient Arabs. Arabs are Caucasians by DNA so of course they will have white skin, \textbf{black} hair, blonde hair, \textbf{r\textbf{ed}} hair, brown hair, blue eyes, big brown eyes, green eyes, and so on. That's in our DNA..I know Arab tribes where real Arabs never mixed with any South Asians and they all have white skin with \textbf{black} hair or blonde hair with big dark eyes or big Arab green eyes or big Arab blue eyes. Those who are having skin color problems in the Middle East are NOT even real Arabs..\normalsize   & \cellcolor{green!27}Black, Nothing, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}6/161 & \cellcolor{green!27}3.727 \\  \hline
  \cellcolor{green!5}\small \@Ya Ra...You are \textbf{Black} NOT Arab. Arabs are not \textbf{Black}. And Sudanese are \textbf{Black}. Be proud of who you are and Stop claiming the Arab identity..Arabs are Caucasians from Western Asia while Sudanese come from \textbf{Black} \textbf{African} DNA like Ethiopians and other East Africans who are all \textbf{Black} Africans.\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}6/49 & \cellcolor{green!5}12.245 \\  \hline
  \cellcolor{green!27}\small in morocco I never saw signs of \textbf{racism} but as you said, light skin is considered beautuful, so much that if a girl is light skinned they say that she's "white and beautiful"\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small I am arab and my  mother do the same she is see a \textbf{black} man with a very dark skin and tell me this poor man has very dark skin\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small there are many cultural, historical and also social factors which drive the opinion that fairer \textbf{coloured} skin = higher quality human\normalsize   & \cellcolor{green!27}coloured & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small EE KK  I understand u don't want Arabs to be targeted but am pretty sure u seen Arab \textbf{racism} against another Arab it happens and is true\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Lost Soul in Arab culture you can't be Arab and \textbf{Black} u either \textbf{black} cause u have a browner skin\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Actually, Arabs prefer skin tones that are within a certain range. Too dark or too pale indicates that the person is not actually pure Arab. Not sure where this idea that we prefer pale skin and blue eyes is coming from. It is often questionable and referred to as mixed blood. The root of it comes from the fact that during the glory days of Arabs, slaves and concubines were brought in from Africa, Eastern Europe and Caucasian mountains. It is associated with most Arab's minds that way. That's why very dark and very light complexions are not favoured. Some Arab tribes are known to have gingers and in the greater Syria region ( Syria, Lebanon, Palestinian, Jordan and north western Iraq) we know what towns and villages have \textbf{r\textbf{ed}} hair and pale skin gene mutations. The obsession with pale skin and blue eyes comes from the same mentality of idolizing your colonizer. For Arabs that refers toThe ottomans. True Arabs genuinely dislike very pale skin and blue eyes because it is either associated with slavery and concubines or colonization. Dark skin is just like the rest of the world association with slavery. Avoiding the sun is mainly because when an Arab tans, most often it gets blotchy and uneven after few weeks. I personally grew up hearing ' too pale .. has no colour.. looks skinned.. has Asian features.. kinky haired.. big lips' as characters to dislike. All back to the same point, just like everyone, Arabs prefer what resembles them. Supreme? Not really.. it is simply not same values or look of who we are. Arabs are the kindest and most genuinely accepting of others. Just because we appreciate who and what we are does not mean we have supremacy complex. I believe that as Arabs we have always been defending who we are because other Muslims and neighboring nations resent us for a few hundred glory years that are long gone now.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/326 & \cellcolor{green!5}0.613 \\  \hline
  \cellcolor{green!27}\small The last thing is also \textbf{common} where i come from (chechnya)\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small IS NOT İT SO FUNNY WHEN THEY ARE NOT FAİR?Are they  just being racist to theirselves LMAO!!!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small If we prefer clear skin to \textbf{black} skin,it is our right... Why u want force us to like something? tastes vary from one population to another\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small everyone is \textbf{racist}, blacks are \textbf{racist} they hate Arabs and whites, in all peoples there is racism\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small I'm half arab and \textbf{african}, im egptian and sudani and I have skin and a lot of people mistake me for being \textbf{Indian}. I hate how Arabs think light skin= beauty and dark skin is ugly because its just not fair and right. My mom is light skin but I always hear her talking bad about people with dark skin and she completely forgets about me her son. My dad is also light skin even though he is sudani, but he doesn't talk bad about people with dark skin because he was born in an \textbf{African} country. I just wish people in general could stop judging beauty by skin color.Edit:  You know actually Sudan is an Arab country because we speak Arabic as our first langue and we practice the Arab culture, of course we have our differences like every Arab country. Not all Arab countries are the same, but I still consider my self \textbf{African} mainly because people won't acknowledge the fact that im Arabic even though I speak the langue!\normalsize   & \cellcolor{green!27}African, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}4/173 & \cellcolor{green!27}2.312 \\  \hline
  \cellcolor{green!5}\small nina a you want to be European so bad 😂😂😂😂. You are pitiful and sad. Clearly you're brainwashed. Real Arabs as you say from the jet herb Middle East as you are those mixed \textbf{race} people you are bashing. Like the Syrians and the levant people. Those people are mixed with European from the days the ottomans enslaved Europeans and raped and mixed with the European women slaves. That's why they look like that. Also 'real' arabs as you say look \textbf{nothing} like what you describe them as. Imam Ahmed Hanbal had dark skin so they say and he was an Arab. It seems that you're deluded and want to apply a fixed narrow perspective on what real Arabs look like. It's probably only your tribe and a few other Arab tribes with fair skin, but many other Arabs tribes have dark skin. And yes, their DNA test is 100 percent arab!\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/152 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small nina a that's a lie. How can Yemeni Saudi not be real arabs when arabs ORIGINATED from Yemen and spread to Saudi? Are you ok? Are you high on ignorance? You're taking mixed Arabs aka levant Arabs who are extremely mixed just like the North \textbf{African} Arabs and calling the Levantine Arabs, real Arabs. Even though they are not. Those people are mixed with the indigenous Phoenicians, southern and Eastern Europeans and north East \textbf{African}. You need to do your research. When Yemenis saudis Emiratis get DNA they have one of the highest amounts of arab blood. And they are brown skin.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/102 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Well when the oil runs out you Arabs who think you're so great will be the laughing stock of the whole world! No one will feel sorry for your lazy ass! India is on its way in becoming a super power we will see who gets the last laugh! All the \textbf{black} people and dark people you have hurt will be thanking Allah that he finally humbled you!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small I always call people out (in a mannered way) for being \textbf{racist} but they always don't take it seriously and start laughing. Those people are the spawns of the devil. they think that me saying you shouldn't talk badly about other races is absurd and doesn't fit their brainwashed \textbf{racist} minds. some of them even think I'm مفلسفة. يا عفو الله\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small very true.... they lit look at you as if youre speaking the most bizaar ignorant thing ever for telling them theyre being \textbf{racist}. spawns of the devil it is. LOL\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Sarah Dirbas Usually People who accuse other people of \textbf{racism}  are lacking arguments, that's why we laugh at them.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Fadi when I hear someone saying \textbf{racist} slurs I adress it politely to them just like our prophet peace be upon him used to do, do you think I have the energy to argue with someone whose mindset is so brainwashed that they can't accept the fact that they're \textbf{racist}? no.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small Sarah Dirbas It's better to be \textbf{racist} than traitor.Author made a vid about alleged arab superiority complex then he calls us arabs even though arabs invaded Palestine, this crap is twisted from the top down.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Sarah Dirbas \textbf{Racism} is a word made by bolshevik jew, back to the topic, arabs are not "\textbf{racist}" towards all non arabs but they fight with other arabs.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Sarah Dirbas He calls Palestinian culture an arab culture, it's more pissing that alleged "\textbf{racism}" because arabs were the ones who messed up there.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Sarah Dirbas Btw If you really want to stop \textbf{race} war you can make some friends or encourage others to improve so they might be respected, it's better than calling someone a \textbf{racist} because they don't care.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Sarah Dirbas They laugh at people who see \textbf{racism} in people that don't agree with them.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Yousef Ghanimeh Palestinians aren't arabs like you, your people invaded our people and switched language, was ancient Egypt related to arabs? - no. Get your shit togeather and stop making clams like x people were \textbf{black} or x people were arab it's fucking \textbf{dumb} and pathetic.\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Fadi Fadi so you believe they should continue being \textbf{racist}? You think the people they say \textbf{racist} things about should 'improve'? How? Because you ain't all that, where's the confidence from?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Unfortunatley,even if I don't live in a diverse country as the U.S,this is something I noticed too....just by watching egyptian tv...Personally I don't think it has anything to do with islam and the fact that we speak arabic  because we don't have the same degrading attitude towards other non-speaking arabic cultures like the western one (europeans and americans) bel3aks, we respect them and lately we're even trying to be more and more like them...so I think this is more about "the victim syndrome" (--> when victims of bullying become bullies themselves)we've experienced \textbf{racism} and been looked upon bu the west "men fo2 le ta7t" so we try to feel better/feel superior again by treating other ethnicites (especially asians and blacks) in a really horrible way...Either way this is a disgusting behavior that really needs to stop :( Thanks for addressing the issue 😊\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/144 & \cellcolor{green!5}0.694 \\  \hline
  \cellcolor{green!27}\small For someone who's brought up in an Arab country as an \textbf{Indian}, I can totally relate to it. It's so overwhelming to see that they express their superiority even in the masjids. Even if you try speaking in Arabic to them, you're laughed at. It's really sad to see this happening in the land where once our Prophet (saws) spoke of equality among all races. But nevertheless, there are Arabs who are generous and kind. May Allah swt bless us all with hidayah and hikmah.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small I know what you're saying sister, it's very sad we have to face such kind of \textbf{racism} in a mosque let alone the airports etc\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Majeedah KhanI have seen the Prophet PBH 17 times in my life ,most Arabs I have seen do not look like the Prophet PBH. Yes I know that there are many Arabs who have  this type of behavior but I have also seen this with some of the Pakistanis so \textbf{racism} and arrogance exists in all races .  Can you imagine the Prophet PBH he was majestic and people would tremble in front him yet there was 100  no  pride and arrogance in him so people should feel ashamed of themselves if they say "I am"I have seen Prophet Abraham ,Isa,Musa,and Nabi Khidr PBT one time  how I saw Nabi Ibrahim PBH was the following: I saw Sayyidina Ibrahim PBH with a face that was not completely round but slightly oval, upside v eye brows, v hairline and hair was a raven \textbf{black} and wavy and he had a aquiline nose bridge which was one flowing curve not a bump then a curve and not hooked neither jagged neither too big or too small . The curve started at root of nose  and was straight across at the nasal base  and he was  fair in color  and i saw him without a mustache just like how you see some muslim grow their beard everything about him was not too much and not too little.   The Prophet PBH said he resembled his forefather the most and he is truthful in his speech\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/244 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small everyone is \textbf{racist}, indians are Also racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small I kept thinking about the Ahadith and happy you put it in end. I'm not Arab but even if noticed it sometimes, \textbf{racism} exists in my culture too and I'm always telling everyone off because that's not the Islamic wayGreat video Subhi, will deffo share it\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small On that note, some of y'alls \textbf{nationalism} needs to be put in check. It's dangerous  and in every sense of the word arrogant.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small People are mixing up things badly now days.. They believe to be by the right side of the road when all they do is being purely \textbf{racist}. Some don't get the difference between loving your country and being a pure racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Aiman Salman   It's all about labels,idenitity and cliques,it's making me sick. It's so damn obnoxious. Arabs are like whites. They obviously think they're the superior \textbf{race} and is above every other races.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Fadi LOL, you guys are 100 arabs dumbass, there's no such thing as "palestinian \textbf{ethnicity}", mostly jordanians and egyptians, the "palestinians narrative" was adopted in '64 with the foundation of the PLO in Cairo by Nasser.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Subhi! Thank you for this video! I've been always trying to fix or fight this mentality but I'm usually told that I'm just too sensitive or it's not that big of a deal or I should just shut up about it. The superiority thing has always made me very angry and I was never afraid or shy to tell the people or my family and relatives that what they're saying is indeed very \textbf{racist} and is very wrong. We are equal to other races and cultures as humans but Arabs are very arrogant, it's just \textbf{dumb} and annoying. I hope it changes one day.\normalsize   & \cellcolor{green!5}Dumb, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/104 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small As an Asian at \textbf{age} 11 that hadn't been exposed to Arabs before umrah, I was to say the least shocked how they treated us. \textbf{Nobody} really looked at us like equals and i wasn't sure why. I heard my parents discussing how they judged us through our colour and inability to speak Arabic. The way even shopkeepers treated us was appalling. I've never understood it since we have been taught that we are all equal but coming from a part Arab I'm glad to know that I wasn't just hallucinating about the discrimination we faced.\normalsize   & \cellcolor{green!27}Age, Nobody & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small It's probably your features not your colour because some arabs are quiet dark and that's a shame. Especially in saudi when it's supposed to be the holiest and one of the most religious lands. I suppose \textbf{racism} exists in every culture though south-east asians are usually very \textbf{racist} towards \textbf{black} people but they look up to arabs a lot. I just think \textbf{racism} is a display of ignorance and miseducation or no education. I can definitely tell this is how the muslim community feels as a whole though\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/88 & \cellcolor{green!5}4.545 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}12 & \cellcolor{red!27}12/69643& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Racist, Racism, Race, Ethnicity, Ethnic & \cellcolor{red!5}497 & \cellcolor{red!5}497/69643& \cellcolor{red!5}0.7100000000000001 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}African, Black, Colored, coloured & \cellcolor{red!27}252 & \cellcolor{red!27}252/69643& \cellcolor{red!27}0.36 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Nationality, Nation, Refugee, Nationalism, Engineers, doctors & \cellcolor{red!5}27 & \cellcolor{red!5}27/69643& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!27}Paki & \cellcolor{red!27}1 & \cellcolor{red!27}1/69643& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Weird, Dumb, Crazy, Lame, Mental, Freak & \cellcolor{red!5}36 & \cellcolor{red!5}36/69643& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Homosexual, Gay & \cellcolor{red!27}4 & \cellcolor{red!27}4/69643& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Zero & \cellcolor{red!5}60 & \cellcolor{red!5}60/69643& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman, Sex, Chick, Sexual & \cellcolor{red!27}21 & \cellcolor{red!27}21/69643& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Quran, Terrorist & \cellcolor{red!5}62 & \cellcolor{red!5}62/69643& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age & \cellcolor{red!27}8 & \cellcolor{red!27}8/69643& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian, Red & \cellcolor{red!5}52 & \cellcolor{red!5}52/69643& \cellcolor{red!5}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}23 & \cellcolor{red!27}23/69643& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho & \cellcolor{red!5}1 & \cellcolor{red!5}1/69643& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Fat & \cellcolor{red!27}3 & \cellcolor{red!27}3/69643& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Communist, Red, Libtard & \cellcolor{red!5}6 & \cellcolor{red!5}6/69643& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Gay, Beta male & \cellcolor{red!27}4 & \cellcolor{red!27}4/69643& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - British}  & \cellcolor{red!5}Tan & \cellcolor{red!5}4 & \cellcolor{red!5}4/69643& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Witch & \cellcolor{red!27}1 & \cellcolor{red!27}1/69643& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}1 & \cellcolor{red!5}1/69643& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}1 & \cellcolor{red!27}1/69643& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Japanese}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}1 & \cellcolor{red!5}1/69643& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - Over 65s;Ethnicity - General;Ethnicity - Black;Nationality - General;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Physical Identity - Physical (and Mental) Impairments;Sexual Identity - General;Age - Youngsters;Gender - General;Religious Identity - Muslim;Age - General;Ethnicity - Native-American;Social Class - Working class;Gender - Female sexuality;Physical Identity - Physical Features; Ideological and Political Identity - General;Sexual Identity - Male homosexuality;Nationality - British;Gender - Female age and physical appearance;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Chinese;Nationality - Japanese;%.

\item The percentage of hate speech related words is 1.5465.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 1081/1816 occurences of hate speech related comments.\end{itemize}\end{document}