\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_178.json :}\newline \par\Large\textbf {Title: \large  Having A Baby At 13 | Britain's Youngest Mums and Dads 2 | Real Families }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small The baby is my age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small ..of course a 13 year \textbf{old} girl can't bond with her baby..she's too young but can't change her past i wonder how she is now\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Okay.... but me and my brother \textbf{age} gap is 13 years😂😂\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Mother also buys a present for the baby while shes celebrating her birthday and she opens the baby's present and it like isn't it my birthday this is unfair 😂 omg she acts like she's 8 year old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small I'm a 13 year \textbf{old} boy and my whole class made an entire rule to never date each other or rub on them without permission\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Charlotte is talking in some \textbf{alien} language.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small In my opinion it should be the grandma's responsibility to support  the 13 year \textbf{old} girl AND the baby! Became the girl is only a minor and the girl should have been better taught how not to get  pregnant. How about birth control ayyyyy?!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small This girl reminds me on billie eilish when she wore the \textbf{r\textbf{ed}} shirt\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small I'm the same \textbf{age} as her. I've done the stupid things she's done. But thank god we were careful.. personally I could never forget about my own child :(\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small This is what new world do to children: take their innocence, make them stupid and with no self identity. I miss the \textbf{old} days.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small wouldn't be surprised if the baby isn't alive by now. disgusting girl . you we're \textbf{old} enough to have a baby at 13 YEARS \textbf{OLD} . you're \textbf{old} enough to have some damn maturity\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small she's like my sister's age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small That 'baby' must be 13 now... I feel old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She's giving such a attitude like look after your damn baby. It's not the baby's fault she's here and crying and needs attention and love . Goshh such a brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small What the heck did a 13 year \textbf{old} girl do to get pregnant at 13?? (I already know the physical answer) I just wanna know why\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Damn that poor baby's neck must hurt. Like the parents should show her to support the baby's head. Especially at such a young \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small U greatful \textbf{Brat} it's your fault you had a freaking baby\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Oh my god that baby is now around 13 years \textbf{old} 😳\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She is 28 year \textbf{old} now\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I feel like she is gonna grow older and become a \textbf{drug addict} or \textbf{alcohol} abuser an like flip out one day on her kid an tell her she was an accident, like I feel so bad for that baby. And she dont even know how to hold the god damn thing\normalsize   & \cellcolor{green!5}Drug addict, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Behavioural Addiction - Drugs & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Her is a 13 year \textbf{old} girl with a baby Me is a 19 year \textbf{old} girl and everytime i Mention a boys name i get whipped with a belt\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small She is such a bad person in general obviously you knew the consequences She was 12 when she had a \textbf{sexual} relationship  and that is not ok and what's worse is that she can not even wake up by 6 so she can take care of her baby\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small I feel like im really mature to have a baby LOL no but really i want a baby like at 16 idk im 11 but i dont wanna be \textbf{old} while having a baby like ...💁🏻lmao\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Had my first sibling at 10 1/2 and I knew how to hold a young child. At 13 my sister was already 2 and although I had knowledge about babies already I was nowhere near ready to have one.Edit: this is \textbf{old}, the actual baby in this vids at least 13\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small And here i am 17 YEARS \textbf{OLD} with a newborn baby sister.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Charlotte is a horrible mom. She called her baby a rat, she cried and threw a fit when someone was kind enough to buy her some things for her baby so she wouldn't have to for her birthday. Charlotte doesn't even support her child's head. In total, Charlotte is a spoiled \textbf{brat}, and she needs to stop this.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small My name is Sophie it's so weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Spoiled \textbf{brat} some girls don't even have a chance to have a baby she doesn't even love her like get ur life together this makes me cry get braces lol\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I am 14 almost 15 and I haven't had my first kiss and she at \textbf{age} 13 with a baby\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small She is so \textbf{dumb}. I don't understand why parent's don't take care of her and her baby. The way she holds the baby is disgusting.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small If she can do 'it' at a young \textbf{age} and give birth, she can take care of her baby... she needs to own up to the consequences and responsibilities of being a mother... like why is she letting her mother and other people watch her baby when they weren't there when she was conceiving😒😒 hope baby Sophie is doing well❤️\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small i wonder if the girl has some sort of \textbf{mental} illness or something? seems mentally younger than 13, idk still too young to be a mom regardless but still\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small 'I wish I could turn the clock back, but I can't' even though her \textbf{age}, I've never heard a mom say that and regret her child like that. For most moms I know or have seen, their baby has been a blessing and they wouldn't trade them for the world\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Its head is the heaviest part, you need to support it. I get its her baby, but her parents need to understand that they need to be the ones taking care of it. A 13 year \textbf{old} can NOT take full care of a child, no matter what you may say.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small I mean I support teen moms but oh my god.. 13? That's so \textbf{crazy}. I support her and hope all turns out well ( apparently her kid's 13 now in 2019?? ) but she was just so young.. this is literally why we NEED to educate our kids on \textbf{sexual} education and health, NOT just abstinence or avoid it at all costs - -\normalsize   & \cellcolor{green!27}Crazy, Sexual & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small Why are people obbbesed having kids at a young age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small It's bothering me so much how she doesn't support the baby's neck, and also when the baby's crying from that gripe pain and \textbf{nobody} knows to wrap up her tummy nice and warm. 😭\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small her : 13,  had a kidme : bout to turn 13 in two months, crying over 20 yr \textbf{old} Korean men I'll never meetBIG DIFFERENCE\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small The baby is the same \textbf{age} as me 😨\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small so she's now 27??? wow that's \textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Her baby now is the same \textbf{age} as me 😂\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Ppl are being so hateful on the comment section. Having a baby at 13 was very \textbf{common} 200 years ago, the babies survived. It's actually not that deep\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small It was \textbf{common} for girls to have babies later in their teens, but not so much at 13. Girls typically didn't even start menstruating until their mid or late teens at that time. It is thought that puberty began later back then because people (especially those who were working class) were more sickly and undernourished. Only since about the mid-20th century, when healthcare and nutrition began to vastly improve, has it been more \textbf{common} for girls to start menstruating in their preteens and very early teens. The average \textbf{age} for girls to start their periods now is 12. Most sources suggest that it was between 14 and 16 in the 1800s. Which again, means that a lot of 13 year olds wouldn't have even been capable of getting pregnant.\normalsize   & \cellcolor{green!27}Age, Common & \cellcolor{green!27}Age - General, Social Class - Working class & \cellcolor{green!27}3/129 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Man that 13 year \textbf{old} is crying over motherhood meanwhile I'm over year crying cuz the fridge is empty and I starving\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Um is it \textbf{weird} that I'm 12 and want a child w/o doing the dirty\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Who got a child pregnant? How \textbf{old} was the boyfriend?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Even at the \textbf{age} of six when i wasn't even responsible enough to care of my own self i used to go around at my neighbors to play and take care of their babies so they can do their house work easily. They used to thank me for that. They tought me that baby's neck needs support coz it's sensitive still but watching this video made me so sad that even after having her parents with her she can't seem to understand this basic fact yet.. it's like she doesn't even care about the baby. It's understandable since she's young:(\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small You should not be a mom at this young \textbf{age} if you can't handle it. There are teen moms who got babies at 13/14 and still manage to be motivated, and to love and raise their child. I know you did not planned this but the baby deserves love and kindness, and you don't get to be selfish anymore. You have a kid now, responsibility and that is not something to take lightly.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} is this video?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I gave my first kiss when I was 16 years \textbf{old}. Just saying....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Am 11 i have been home by myself with a 3 month \textbf{old} and i know how to take care of a baby.i would be able to take care ofa baby at 13\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small In my country they used to force little girls at young \textbf{age} to marry, my mother is one of them, she got married at 14 , had my brother at 15 and me at 19, she always say that she used yo have big dreams and wanted to do great things when she grows up, Whe was a good student, but her father decided to end her dreams... My mom sacrifices allot to live with a men she doesn't love, ans 3 childrens at a young \textbf{age}, it wasn't her choice, but when it's your choice ... Chose wisely ... Thank god my Country changed the rules and the legal \textbf{age} to marry is 18 for girls , and the culture changed too, i'm 23, i have a college degree and going to nurse school, hope after few Years i could have a child of my own, i would ne responsible and grown, 13 yo is a child,her body isn't even completely developped ,still afraid of dark at night maybe, parents please take care of your childrens, and girls please chose wisely.. Pleaase\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/183 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small My parents and my grandparents would have sent you away they could not be around that kind of shame.I truly understand where they will coming from.Thanks mom thanks grandma  For keeping the \textbf{old} values alive within me\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I'm 18 years \textbf{old} boy still haven't even kiss a girl and looking at this I feel I'm sucks 😞😞 😎\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small WAIT OmgIf she had a baby at the \textbf{age} of 13That means she did it at the \textbf{age} of 12!???OMG And than u have me I'm 13 and never had my period lol\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I want to have a relationship and get a baby by 16 years \textbf{old}. I swear I can take care of a baby\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small If i had a baby at that \textbf{age} my mom wouldnt even help me with her she would be like its your baby you have to take care of it and WHY TF IS SHE NOT HOLDING HER NECKKKK!!!!!!!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Just did the math and found out me and Sophie are about the same \textbf{age} now in 2019. 👀\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Why are kids her \textbf{age} even having 'that'\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small If I got pregnant at \textbf{age} 13 I would do the best I could for her or him\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Omg i hope someone take the baby into a other family. She don't care about the baby's head and \textbf{nothing}. She's soo stupid.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small So scary for me I am only 10 year \textbf{old} ahhhhhh it's scary\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small If you know how to open your legs at least learn how to hold a baby. Irresponsible brat\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Girl i'm 11 and i take more care of my 7 mnth \textbf{old} sister better than her. and i actually suppirted her head when she couldnt do it on her own. wtf.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Okay, shes not \textbf{old} enough to be a mom, SHES A CHILD HERSELF shes just teen\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Shes \textbf{mental} .\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small That kid gon be gettin bullied when he/she turn like 11 cuz when another kid ask how \textbf{old} they are they say 11 and when the kid ask how \textbf{old} their mom is they say 24 and the other kid who askin all them questions gon be subtractin and be like wait so your mom had you at 13 he or she will say yes and will start getting bullied\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small She relies on others becuse she needs others- she is a child too! I mean like how didn't anyone get charged legally for allowing this to happen?!?! If she acted as a proper mom or someone else stepped in to be her mother figure then I'd support her but she dosnt even want to do normal 14 year \textbf{old} things let alone taking care of her kid..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small * 6 year \textbf{old} me hold a baby for the first time*me: 😃🤔🙃I WAnnA Be A mUm, my mother be like: honey you have to wait just a longer until you are \textbf{old} enough .me:😡I wanna be a mUm right know!AS SOON AS POSSIBLE!!! ME SEE VIDIO :😳\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I had my son at 15 and i have to say, it does suck when its your birthday/etc. and all you get is baby stuff. I mean i was very very grateful for everything that i was given, i was ready for my son. It just wasnt an awesome feeling but i was pregnant on my birthday and a bit hormonal. A baby is a blessing no matter what \textbf{age} you have him/her. With how this girl is acting she seems like she may have post partum depression.     **  I'm now 17 btw and my son is 1 1/2 years \textbf{old}.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/101 & \cellcolor{green!5}1.98 \\  \hline
  \cellcolor{green!27}\small OMG shes only 14 years \textbf{old}, she has to skip school to be with her baby, she has to look after her baby, poor girl, she should have a normal childhood and her parents should look after the baby so that she can have some spare time\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small not saying i'd ever have a child at a young \textbf{age}.. but if i did i'd O B S E S S over making sure every need is met for my child smh\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small wonder how she's doing now, her daughter is now the same \textbf{age} she was when she got pregnant\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small The baby needs to go up for adoption. The parents can't even take care of the children they have and they're just gona be okay with their 13 year \textbf{old} to take care of this baby that she's not taking care of nor is the actual grown up mother is either. The baby needs to be taken and put somewhere someone can actually give it loving care.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Shilpika Bagh I didn't know what \textbf{gender} the baby was so I didn't wanna misgender HER.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Their stupid they could have \textbf{sexual} contact but can't take care of their babies\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Cries because her mother gave her BABY  a gift what' an ungrateful \textbf{brat} that baby is so cute she's 14 and doesn't even know how to support the baby's neckat the \textbf{age} of 10 years \textbf{old} I was watching my cousins and brothers and sisters why my mother does cracked on the streets 😂📿\normalsize   & \cellcolor{green!27}Age, Brat, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/54 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Why would you even have a \textbf{sexual} relationship or think about it at 13?\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She's too immature even for a 14 year \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Oh my god the baby is my \textbf{age} now\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I'm only 10 and I can take care of my baby cousin who is 8 months \textbf{old} better than that\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small She's a child with a child, of course she's sad her birthday isn't about her. At that \textbf{age} it's all about them... the grandparents are better of taking the child and letting the kid be a kid!!!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small A very immature 13yr \textbf{old} at that! Talks like a baby \& acts like a baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small if i had a baby at her \textbf{age} i would hold the baby's head and would put her before anything i had to do and wouldn't expect anyone else to take care of her more than me\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small She is so cute I want to cry 💔 she's not there and has no clue what to do I have six siblings and I am 12 years \textbf{old} and I\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I'm 12 years \textbf{old}, i Have a baby sister and i learned a lot of how to take care of a baby, but before my mom had my baby sister i had already knew about babies and what to do. I know how to hold  baby and treat them. My mom always told me "babies before you" Whenever a baby cries stop what you are doing, check if they are hungry, need a diaper change, need to get held, or wanna play with the mom. It can be challenging but you learn from your mistakes. If i ever had a baby, i dont care if its a boy or a girl I will always treat them right and love them to death i will never put them up for adoption.  I honestly would take that baby that, the 13 year \textbf{old} has if she put her up for adoption and treat her like a real mother!Btw im so sorry for this whole paragraph, im just being honest\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/168 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small That baby is the same \textbf{age} as her mom when she gave birth now on 2019\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small She's so immature for a 14 year \textbf{old}, my 13 year \textbf{old} self is more mature.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small ok your 13 and your 9 months pregnant and you have no idea your even pregnant? and the dad saying shes always been slim, that means she the shows earlier and she gets bigger...so shes kinda \textbf{dumb} i guess.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small This type of stuff happened a lot back in the day in the \textbf{black} community . they would have babies as young as 12... often times by abuse. The grandmother would take the baby and raise it as her own. the baby would not even know that their sister was their mom. \textbf{crazy}.\normalsize   & \cellcolor{green!5}Black, Crazy & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small She call the baby a \textbf{brat} when she was crying 😂\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Jessica Lynch I'm 18 and didn't kiss \textbf{nobody} still 😂😂😂😂\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I'm 15 and didn't kiss \textbf{nobody}  still🤣\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small SUPPORT THE NECK! Holy \textbf{crow}....\normalsize   & \cellcolor{green!5}Crow & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small How does a 13 year \textbf{old} have a baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small wow now the baby is 13 years \textbf{old} 💀and hope she sees this 😂😭\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small This girl will harm her baby big time, psycho\normalsize   & \cellcolor{green!27}Psycho & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Disgusting. What a \textbf{dumb} girl.Well, its her karma..Poor baby..but its her karma too\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Lmao the baby \textbf{old} as me then because i was born in 2006 lmao\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small This video of the 13 yr \textbf{old} mother is so sad. Poor baby, no one wants her. They should have given her up for adoption and let someone wanting an infant have her. I am sure she would have been a much happier baby, child and person; feeling loved and wanted by her parents.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small It's 2019 now , how \textbf{old} is her baby now? And her\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small 2019 baby Sophie can also be a mother and will the grand mother be 26year \textbf{old} it genius\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Umm.. i expected her \textbf{mental} to be more older thatn this😕\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I'm sorry but just by the way she speaks shows u her \textbf{mental} capability.  She's young, she obviously has behavioral challenges and she doesn't care. Yes part of that has to do with \textbf{age} but not all of it. I have friends that have siblings 13-14 years apart and they have helped their parents immensely.  Unfortunately this child should of been put up for adoption or her mother should be taking care of it. But seems like there is no proper guidance from her parents either, I could be wrong.\normalsize   & \cellcolor{green!5}Age, Mental & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small She is a \textbf{brat}! She better freaking grow up fast since she wanted to act like an adult. That baby is absolutely adorable, I feel so sorry for that sweet angel having a mom like her.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small It's \textbf{nothing} compared to most developing country, some of them give birth at 12!! EVEN 9!!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}6/16 & \cellcolor{green!5}37.5 \\  \hline
  \cellcolor{green!27}\small I am 13 but look 16. I unfortunately take care of my neice atleast 20 days out the month and when i say i get criticized all the time i mean it. I went to target and a older lady started screaming at me about how i am A sleeze and i disappointed my parents and how her 10 year \textbf{old} daughter was more resopnsible than me. I was so angry i was in tears. What she did not know is that i was in target to buy my neice more pampers and formula. So i would call that very responsible considering i am taking care of a 23 year  olds child.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/112 & \cellcolor{green!27}0.893 \\  \hline
  \cellcolor{green!5}\small Old people in the comments: 'she is a terrible mother!  She's too young to have a baby [yes.]'Also \textbf{old} people: 'criminalize abortion!  Reverse Roe v. Wade!'\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small It's hardly her fault she is 13 year \textbf{old} kid\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small This is incredibly sad, why is she sexually active at 13😥... signs of molestation?? Her mother needs to stop with the "this is your responsibility ".... no it's not, no 13 yr \textbf{old} is fit to care for a baby ,sophie's grandmother sounds like a horrible mother which is why her daughter got pregnant at 13!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small The baby is so cute,hope she will never be like her mom getting pregnant at a very tender age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small This is so sad.... I'd rather have the good \textbf{old} days back. I was so naive at that \textbf{age}. I didn't have my first period until I was 14! I think I would have ended up in jail if my daughter had a baby at \textbf{age} 13!\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}9/47 & \cellcolor{green!5}19.149 \\  \hline
  \cellcolor{green!27}\small She literally doesn't love her baby. Every time she holds the baby there's this \textbf{weird} look on her face especially when she bursted into tears it felt like the baby is a burden on her. Thank god she has family support, else the baby wouldn't have even survived till 3 months\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Oke so the baby is my \textbf{age} right now? 😂\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Curiosity to know and explore everything...at certain \textbf{age} with no right time...leads this results...which suffers a lot...LOVE for NEWBORN..😟\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Omg she's my \textbf{age} my god\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small 1. Why has \textbf{nobody} taught her how to hold her baby 2. They're complaining about waking up at 6:45 but I'm almost at school from the bus by that time 3. This girl needs to stop ignoring her baby and take charge by becoming a real mother\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small My mom would have slapped that baby out of me. I got my period when I was ten years \textbf{old}. I got pregnant at 33 years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small I don't no what i would've done if I was pregnant at 13 . When I was 13 I was still a virgin i didn't really talk to boys because I was \textbf{weird} and was a ugly duckling I wouldn't even know how to take care of a baby and definitely wouldn't be mature enough\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small I'm thirteen and I'm worrying about my 5 paragraph essay, not a 5 month \textbf{old} child.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Why doesnt her mom teach her how to \textbf{old} her own baby?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I just want everyone to realize, that 99 of this video is BS. They're showing the things she does wrong on purpose, of course she's not a great mother, she's 13. And yeah, it was a \textbf{dumb} mistake, but we're humans, you've made mistakes too.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Omg someone please knock some maturity into this chick\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Charlotte is a \textbf{brat} n will continue to do what she is being doing\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small she's so ungrateful, she has supportive parents but she's being a spoilt \textbf{brat} 🤦🏻‍♀️\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Her daughter is 13 years \textbf{old} this year I hope she didn't turn out like her mother\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small That kid is as \textbf{old} as me\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Iteboheng Langeni yeah unfortunately that's a thing :- no need to judge, it does seek \textbf{crazy} but it can be done out of fear, disbelief, anger, sadness, or if you're in an abusive household where until the very last second they can't do anything about it... or if you know your family would pressure you into an abortion then you hide it because you just can't get one for numerous reasons ( whether that be its illegal or you're against it yourself or you can't do that to yourself etc. ) and then you have the baby last second. Personally I understand, but I find it INCREDIBLY disrespectful since her parents just don't know at all and then suddenly have a grandchild in the house?? It'd take even LONGER for the tensions to rise and/or for the parents to cope with it, and that'd be when the baby's born instead of whilst she's pregnant and they become okay towards the end or so of her pregnancy. It's so \textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/169 & \cellcolor{green!5}1.183 \\  \hline
  \cellcolor{green!27}\small charlotte is simply slow in the head. god, she reminds me of all the \textbf{dumb} mouth breathers i went to middle school with. and she got pregnant again in her 20s and STILL doesnt care for her other baby. sophie got adopted by a loving family, thank god.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small She can't get mad cuz she was being fast. Ones your a teen mom your kid/teen life is gone.They should have put the baby for adoption then ones she gets more older like 21 or 27 she can have it back.Edit: the \textbf{dumb} thing I seen about teen mom is that the dad is not there and the other family should make she care for her own kid she was the one who did it.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small I can't believe being an uncle at 8 years \textbf{old}!! Wow\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small That little baby is now 13 years \textbf{old}. Where's the update on them?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small WHY CANT HER MOM TELL THE 13 YEAR \textbf{OLD} GIRL HOW TO HOLD THE BABY CORRECTLY THO? ;-;\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small That baby is my \textbf{age}...Skskks.The baby is is already 13..SKSKSJJS.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small White trash\normalsize   & \cellcolor{green!27}White Trash & \cellcolor{green!27}Ethnicity - White, Social Class - Working class & \cellcolor{green!27}2/2 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small the new mother 14 yrs \textbf{old} is so selfish.She wanted something for her, but the baby needs the stuff more.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small You know, I might not have PhD's in the medical field, buuuut I'm preeety sure you need to support a baby's neck. I mean I think we all have a little \textbf{common} sense?\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small This dose not happen in \textbf{black} families homes this is white families problem it is something they have to deal\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I'm 12 and I want a kid more than anything, I know that is very odd for a 12 year \textbf{old} to say but I really do and I just want Sophie she is adorable ❤️❤️\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Imagine being a parent and knowing your child lost their virginity at \textbf{age} 12\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small This is so messed upYou can't understand what she's saying (thank god for captions) Having IT at 12 A baby at 13Her parents not being mad The neglected babyA \textbf{brat}AND DO NOT GET ME STARTED ON THE BABIES NECKDang this Is the most amount of likes i have ever got, thanks guys\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Right?! She is just so UGHHhH i am just frustrated by her she is such a brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Oh my god the moment I saw her I thought only one word that is brat\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small is it bad that me and her daughter are the same \textbf{age}...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Watching these young girls not bonding or even talking with their beautiful babies girl, is painfully sad and is a perfect example of why having a child at 13, or babies having babies in general, isn't a good thing. I'm tearing up just watching 😢 Thank God for this \textbf{woman} for trying to teach them how to be mothers and hopefully they learn something!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small I wonder how \textbf{old} the father if that child is?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small life is sad it's not even about her \textbf{age} she was just careless because some young girls have different mindsets and are mentally, physically, and emotionally stable to take care of a child even though they go through their ups and down, every parent does despite their age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Sophie wasn't put on adoption. Maybe you confused it by Charlotte going to a care center for her bad behavior at \textbf{Age} 12-13Shes a new mom shes 13 give her a break the baby is fine! Also 3 months it can hold the head just fine! Shes a great mom and loves her kid.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small \@Alaijah McDowell This is not a 16 year \textbf{old}, this is a 13 year \textbf{old}, who was probably 12 when she got pregnant (based on the way she's acting I feel like she may have been raped), but no child is ready to take care of a child, and that's what she is.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small I remember seeing the full documentary on the school for teenage Mums. Charlotte was the one the nurse was most worried about because she was so immature even for her \textbf{age} and not ready to bond with the baby.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Alexa Cabello if you think a 3 month \textbf{old} baby can hold its head up just fine, please don't have a child\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Thats what they told me when i had my period.Edit:I was 9 years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Then when you were 13 you were really \textbf{dumb} to think that\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm more bonded with the 6 month \textbf{old} I care for than this \textbf{chick} is to her kid.  seriously I take care of this nugget like she's my own.  for starters she needs parenting classes, her parents need it too. if the mother or whatever she is won't teach her, or figure out how to balance teaching her and letting her do things on her own, how does anyone expect her to just know how to do this she's 13 she doesn't have the ability to have a maternal instinct yet,  teenagers are selfish,  to no fault of her they just are. I see a lot of comments about her and I get it but I think she's doing the best that she knows how right now,  they are going to grow together and she will learn if someone takes the time to guide her. they think it's funny she got banned from the class,  seriously this kid didn't have a chance\normalsize   & \cellcolor{green!5}Chick, Old & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/162 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Nobody thought about adoption? 😂\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small sandipta singha that was me at 9 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Her at 13: having a baby Me at 12: listening to MCR and joining the \textbf{black} parade\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@sandipta singha 😂😂 It's awesome you are still being a kid at 13 years \textbf{old}!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Okay I'm sorry but she's a horrible mom so irresponsible the 8 yr \textbf{old} seems more\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small It doesnt seem like the parents are upset at all...weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small When was this filmed? It seems \textbf{old}. We need an update\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I'm pretty sure ANYONE her \textbf{age} could take care of a baby better than she can...🤦‍♀️ it's really sad honestly\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small She was 12 when she had it then 13 barely going on 14. I doubt most at that \textbf{age} would have a maternal instinct to care for a damn baby. I see many 13-16 year old's acting like they would be completely different in this situation. Do you all not understand that she was still a child when all of this happened? A child is not mature enough nor mentally stable to take care of a baby, she was practically still a baby when all of this happened herself! What's really sad about this is that the baby was not put up for adoption as soon as it was birthed. Her parents are also very questionable during that whole fiasco.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}\small \@\textbf{R\textbf{ed}} Seraph At the \textbf{age} of 10 I was already helping taking care of young children. My aunt will take me with her during the summer to help her with her 9 month \textbf{old} baby. Ofc it's not the same since I'm not having a child of my own. But for me at her \textbf{age} I already had the mother instinct. I had another brother when I was 14 and I will run to my parents room every time i heard him cry at night to see if he was good. It's just a matter of how mature or the personality of the person.\normalsize   & \cellcolor{green!5}Age, Old, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - General, Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}5/104 & \cellcolor{green!5}4.808 \\  \hline
  \cellcolor{green!27}\small Karma returns back. When I see British people I find almost all...they all have some serious \textbf{mental} issues.mostly now genetic.What they did to world is what they are getting back.Sad but world need to learn the lesson with this.😐😐😐\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small She's crying because she's a child herself! I'm 30 and I ask people to get my 1.5 year \textbf{old} daughter stuff on my birthday because it's expensive and I appreciate the help\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Original video was in March 2006Youtube posted on August 2019.Now Charlotte is prob 27 years \textbf{old} (D.O.B- May 1992)Thomas is probably 21 years \textbf{old} Sophie is probably 13 year \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Charlotte is a bit \textbf{dim} witted....\normalsize   & \cellcolor{green!5}Dim & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Farishta Hakim wtf do you expect tho ? i mean for my \textbf{age} i'm mature (i'm also an early TEEN) but at the same time everyone is different so.. ANYWAY, she shouldn't even be having a baby at that \textbf{age} so what would you expect from an early teen ?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Green Leaf actually...s/he does. When I was watching her, it just.. Didn't felt right. I just turned 14 (yesterday I was still 13 😂😂) and just the fact that she cried at her birthday is just. Rkviajd. She was definitely not ready to be mom, I hope they actually learn her properly how to take care of the baby.It's important to have bond.I have \textbf{nothing} against her, I hope yo get my point\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Holy smokes...13??????!!!!!! I was more concerned with riding my bike around that \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Her daughter is the same \textbf{age} as me. I'm 13😂\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Holding a baby's head is \textbf{common} knowledge...she's just being careless??\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Is she \textbf{crazy} she can't let a baby's head lay back like then when their being carried!!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I'm also 13 and I take better care of my 3 month \textbf{old} sister than she does of her own child\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small she is such a \textbf{brat}...\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Is parents in UK , that cool  having a kid at the \textbf{age} of 13 ?Just askingThey aren't even mad\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Reshi Isah honestly look at the teen , she is so lack of confidence, she will feel different in school from rest of students (which I can relate to) She can't take care of another baby , cause she is herself a baby , at this \textbf{age} she need to enjoy , She is also a single mother just at the \textbf{age} of 13She need to give that baby for adoption , that's best thing for everyone\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/78 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@Shahid Singh as you may know.this is an \textbf{old} video so all this happened a long time ago. I do understand that the way she did behave wasn't so far fetched as she is still a child too. well I guess putting the child up for adoption would have been a good idea too but poor baby Sophie never asked for any of this.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small She's 26 now,I wonder what's she's doing now the baby is 13 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small i'm so angry that \textbf{nobody} is supporting her neck except the nanny\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Can't understand the 13 year \textbf{old} girl.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Parents of this \textbf{age} have failed their duty !soon we shall all reap.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small ah yes the wonderful \textbf{age} of 'fir een'\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small This was in 2006 that means that baby is now 13 yrs \textbf{old}, as \textbf{old} as her mom in this video 😱\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small My 11yr \textbf{old} is way more mature. Maybe adoption should have been an option. Smh. Please talk to your kids about their bodies and relationships with others.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small I love how they indirectly imply somehow it`s school`s fault for not teaching \textbf{sexual} edcuation. what about YOU educating your own Child about that. I mean, WHERE WERE YOU before and during 9 months of pregnancy? people expect the schools and goverments to take care of every aspect of their lifes.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Duh. She's friken 13 years \textbf{old}. She's still a kid, she doesn't have much maternal instinct. That baby should've been given up for adoption to parents who are older and more mature and mentally ready to care for a child.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Considering the mother, it's not a wonder the 13 yr \textbf{old} was in "care" and had a child... So sad for the child...If the 13 yr \textbf{old} girls mother was actually a quality mother, she'd know how to care well for her own child... SMHThat whole culture can't seem to do a thing for themselves... Pathetic\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@Hermione Granger the way the video quality is... Sometimes they post \textbf{old} videos\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small This is maddening.First of all why are kids left so independant to have such relationships.Parental supervision at this \textbf{age} is highly important.Secondly a child needs a matured mother to thrive.Such mothers who are producing kids because of biology are unaware of \textbf{mental} issues the child would have as it grows up.\normalsize   & \cellcolor{green!27}Age, Mental & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small 8 year \textbf{old} uncle\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I can't understand anything the 13 year \textbf{old} is saying\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small She's is treating the baby like a doll not caring for it she's not ready to be a mom and now her parents are gonna have to take care of the baby unless she can get her stuff together and I do understand that she's young but she isn't \textbf{dumb} she knew what she was doing\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small iris rapp lol what a spoiled \textbf{brat}. 😂 Got jealous of her own kid like she was her sister.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Parisss and Elegancee I know you did not just say a 14 year \textbf{old} is still a baby... SIS, SHES IN HIGHSCHOOL! But go off I guess🤐✌🏽\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Aliyah Zari I'll say it too, 14 year \textbf{old} is still a baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Mel B It's a figure of speech meaning, she is still a child and not a \textbf{woman} yet\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Sarah Lola \textbf{nobody} told her to start doing the business at 13, it's her responsibility, she did it to herself yet her mom has to pay the price of the outcome.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small This baby is now the same \textbf{age} as her mother in this video lmao\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small This 13 year \textbf{old} mother acts like a 9 year \textbf{old}. I turned 14 2 weeks ago and would be a better mother than her.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small My school does not provide education about this and I'm mad. If one day I see a pregnant 13 year \textbf{old} I'll blame the parents and the school!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I cant believe the mother let her 13 year \textbf{old} look after a nee born\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Why people want to grow sto fast? I mean, I am 15 and I just want to life my teenager life, I'm too young to have a baby, this is something that maybe I will do when I will be an adult.Why are you so fast? Enjoy your life, enjoys the good \textbf{old} days that you will go to miss when you 'll get older.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small She's the same \textbf{age} as me\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small OMG...so I'm late lol but Sophie is my \textbf{age}.....and her mom is now 26??\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She's the same \textbf{age} as me and she's older by a month\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Just like me! Me and Sophie are the same \textbf{age}!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Georgina ! My \textbf{age} tf\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Wowwww SHES MY \textbf{AGE}!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Also apparently Sophie was adopted and never met her mum. The proof is on another video called triplets at \textbf{Age} 16 in the comments ok bye\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@LEXG00 ! You don't really seem your \textbf{age}...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@hatzistu  where you get that idea from.  But yeah i dont always act myage. My \textbf{mental} \textbf{age} is between 12 and 16 im mentaly stuck whats worng with that? It might be one of my autisstic tics but thats not important whats important is that i accomplished more things then most people my \textbf{age} i have mu own mow busniss ive started from scracth and as soon ss i get a car its going to get bigger\normalsize   & \cellcolor{green!27}Age, Mental & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/77 & \cellcolor{green!27}3.896 \\  \hline
  \cellcolor{green!5}\small Im not good handleing tiny babys. I didnt start babysitting my neice till she could sit up crawl and hold her own head been baby sitting her scence she is now 2 years \textbf{old} i call her my little piggy\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Same I'm 12 and Ik bc I have a baby cousin and I literally take care of her everyday bc her parents make me baby sit but without getting paid but i love her she's 1 years \textbf{old} now and me and her are. Very close\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@Ashley BTS fan no one should be a mother or father at the \textbf{age} of 10 being a parent at a young \textbf{age} on purpose is very stupid or just being a \textbf{dumb} kid and not using protection is very risky especially for the child and you\normalsize   & \cellcolor{green!5}Age, Dumb & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/47 & \cellcolor{green!5}6.383 \\  \hline
  \cellcolor{green!27}\small \@ley nice I have one that's a day younger than me, a 5 yr \textbf{old}, 3yr \textbf{old}, and 1 yr old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/21 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Same, I was 10 years \textbf{old} when I started babysitting.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small You should know how to do that at that age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@LEXG00 ! *Autisic and you're grammar is horrible the \textbf{mental} \textbf{age} of Autism doesn't even work like that get out of here kid\normalsize   & \cellcolor{green!5}Age, Mental & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small See what I mean a 13 year \textbf{old} is an immature kid\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I hear 'oi you little \textbf{brat}, you little bi-' nearly saying bi*ch\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Hello PotatoSpeaking I heard \textbf{brat}, too - not the second part though.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She's about my \textbf{age} and the baby is about 10/11 years \textbf{old} now... jesus. I'm \textbf{old} af\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small This is fu ..ng \textbf{crazy} . Children having children.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small The mother to the 13 year \textbf{old} isn't such a great mother either from the look of it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Emma Wright damn, having a kid at that \textbf{age} is wild bruh\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small OkayGoddess this was filmed 2006 that's why, the baby is now 13 years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The baby is her \textbf{age} by now...and she is barely in her mid 20s...they would look like siblings\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Her baby is my \textbf{age} now 13😂😂 wow\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small A 13 year \textbf{old} has no place having a baby.  The parents should have insisted t hat the baby be given up for adoption to be placed in a family that truly wants a baby and will take care of it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Sofie should have aborted her baby. It is not her \textbf{age}, it is her maturity and willingness to become a good mom.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small My mom always says If you \textbf{old} enough to be sexually active than your \textbf{old} enough to take care of a baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small You cant expect a 13 yr \textbf{old} to take care of a baby. They are still a child themselves. Unfortunatly girls get their period way too soon before they are physical  and psycological ready for children.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small That baby should have been put up for adoption! Wtf it's like she doesn't even care. She's so stupid 🙄 like don't even say 'it's cuz of her age' that's disrespectful to 13 year olds cause most, like myself, have \textbf{common} sense 😑\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Please take the baby away from her....I beg !! It's ridiculous....so many teen have babies accidentally...and they accept that and love that baby...but trust me...this girl is not only immature... she's heartless....even her little brothers were smiling whenever they looked at the baby...but this girl I have to say she's unbelievable horrible... And where is the boy.... it's kinda \textbf{weird}...I hope this Charlotte has not gone through any horrible situation like got raped by someone... it's kinda worrying me...Edit: this is not because she's a typical teenager... everyone goes through teenage but no one behaves so rude with their own babies.... It's so heartbreaking .this baby girl needs a good mom who deserves her... CHARLOTTE DOESN'T DESERVE THIS BABY GIRL...\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/121 & \cellcolor{green!5}0.826 \\  \hline
  \cellcolor{green!27}\small What was those sounds coming out of that girl mouth??? Was she speaking or rumbling? I need subtitles. She can have baby the \textbf{age} of 13 still unable to talk or keep the poor baby neck support???\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Did she call her OWN baby a \textbf{Brat}??!!!\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Hearing the words "mother" and being referenced to a 13 year old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small A 13 year olds brain is not fully developed and they dont have the \textbf{mental} ability to handle what it takes to be a parent\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Seriously how does a 13 year \textbf{old} have a kid without parents not knowing\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Right now Sophie is the same \textbf{age} that Charlotte was when she gave birth HOPEFULLY Sophie isn't pregnant now too💀🙀. Edit:   OMG thanks so much for one like I've never gotten one before🙀😺😸👻👽😏\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small I was babysitting for 4 kids, ages 6wks to 4yrs \textbf{old} by the time I was 12.  I took better care of all of them and especially the little baby, better than she cares for her baby girl!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small She is to young to be a mother I mean who forgets his daughter in a car in a place where \textbf{nobody} like in the near is I'm not saying that she is a bad mom or something like that\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small One of my nieces had a baby at barely 13yrs \textbf{old}.  She's a good mother and has raised her son, pretty much on her own, including graduating high school and working to support her son.  I'm proud of the \textbf{woman} she has grown to be.\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small When's she's 26 she will have a 13 year \textbf{old} 🤦🏾‍♀️ omg\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Well that comes to show how parents need to keep more eyes on their kids for accidents like those not to happen again and speak with your children about safety because I see the Mom and Dad's face on the video that  they don't seem to care what happened to the 13 year old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Wow now her baby is her \textbf{age} I hope and pray her lil girl won't take her footprint in life\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Man! I would kind of enjoy being a mother at this \textbf{age}! 😬☺️\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small At 23 shell have a 10 year \textbf{old}..\textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} did she have her first baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She will have serious \textbf{mental} health when she grows up\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The dad is 2 years \textbf{old}?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small why does she look 20 years \textbf{old}, though\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I like how this came out in 2006 or smt so her daughter is now her age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small winter blxssom her mom is just as irresponsible as the 13 yr old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small winter blxssom what can she do? I mean my mom was and when I got pregnant at 16 there's \textbf{nothing} they can do it ! It's happened .\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Abortion is evil at any \textbf{age}. This Wonderful mother is supporting her daughter. What happened to BE STRONG FEMALE ETC?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small winter blxssom there's \textbf{nothing} she can do about it\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Mixed Bby Daiii this video was made in like 2004 or 2006 her baby is 13 year \textbf{old} now\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Woah, this was made in 2006. Her kid is probably 13 now, crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small When i was 12 years \textbf{old} as the first child of my family i learned to take up responsibilities on my own and madam is 14years \textbf{old} with a baby yet she is running away from her duties....like dafaq\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small My mother would not trust me taking almost full care of a baby to be honest I wouldn't I'm almost 13 myself and if I had a kid my mum would take almost full care of the baby because at that \textbf{age} you think you mature but for a baby your not also your not mature if you even got your self pregnant in the first place\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small When i was 13 years \textbf{old} i was still playing with my friends i didn't even knew what it was a kiss😨\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I wouldn't even trust a 13 year \textbf{old} to  baby sit my dog\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small If I had a kid at this \textbf{age} my life and soul would be put into that baby's care. She doesn't gaf. Like HOW\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} was the boy?!   \textbf{Nobody} in the family knows how to hold the baby! Remove the child from the home!\normalsize   & \cellcolor{green!27}Nobody, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small I can't believe the nonsense I just watched. The selfishness that those girls have is ridiculous! Granted I was older when I had my children (5), but \textbf{common} sense should take over at some point. I'm just dumbfounded at their behavior and lack of knowledge on the situation.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small My biological mother had me at 22. She wasn't ready to have a child so she put me up for adoption. It was one of her best decisions. She died at \textbf{age} 27. Please put that baby up for adoption, you are not ready.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Watching this hurts..... i cant have children and watching this \textbf{brat} not care about her baby kills me\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small The baby is now almost the same \textbf{age} as the 13-year-old mom. I wonder if she's a granny at 26.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small and worst nanny ever !\textbf{zero} empathy for the young moms. You can train the moms with respect and empathy or bully and shame :( Horrible example for the young mom's that nanny\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Where is the follow up to this?  It cuts off quickly and leaves us hanging as to whatever happened to Mum and baby.  I am shocked at the angry, shaming comments, below.  The assumption that if her parents had been watching her every second that she never would have fallen pregnant is absurd.  To be angry that a 13 year \textbf{old} is very bad at being a mum and understanding what she is dealing with is ridiculous.   She is who she is, very immature and unable to cope, it's as if she's in some state of permanent shock.  My concern is that Charlotte is detached in many ways; to not have any clue that something was going on physically, you know, like a full-term pregnancy?! is very off.  I am very worried that she doesn't seem to really have a clue that this is a baby, the adults, both family and professionals, comment on this, and yet no one suggesting that the baby be put up for adoption.  How is this going to turn out well?!  The adults need to step up and do something.  Unless the parents decide to raise the baby and not count on Charlotte's participation, then this child has not a chance in the world.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/209 & \cellcolor{green!27}0.478 \\  \hline
  \cellcolor{green!5}\small I hate how she can be so careless over a living being it is not even my baby and I want to make sure it's neck is upright and make sure it isn't being abused. Like seriously did \textbf{nobody} give her THE TALK. I'm 13 and I am why more responsible then this.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small She had a baby at 13 it's not normal , she wants to be normal do normal 13 : year \textbf{old} things friends, dances not having a baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small How do parents allow her to get pregnant and also why at 13 omg that's so wrong it's like she is playing with a doll only it's a real baby .this boggles my mind the mother ( her mother ) doesn't seem fazed her 13 year \textbf{old} has a baby .why? How?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small if i were charlottes mom i would just care for sofie. Charlotte obviously wasn't ready for a baby and you can't expect a 13 year \textbf{old} to care for a newborn.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I am \textbf{Indian}, and I thought I am naive to not understand her thick accent. I couldn't understand a word she said!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small That baby is a Barbie to her. She knows absolutely \textbf{Nothing} about being a mother. She.s a child, omg.. this is absolutely terrible.  Give that baby up for adoption to a family,  wanting a child, who are adults, and financially,  mentally and emotionally prepared for parenthood.  There is \textbf{Nothing} you can offer a baby at 13!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Amanda Earle Im 33, pregnant with my second child and due any day. My birthday was last month and wanted \textbf{nothing} but baby stuff. I would've been grateful I didn't have to buy a damn thing out of my own money 🙄\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I don't see how she is wrong on that.. when you have kids you don't stop being a \textbf{woman} or a man. it was her birthday. buy something meaningful for her or anyway, a decent baby stuff. not £1 baby wipes\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Right everyone don't realize that's what happens when you have kids especially at a young \textbf{age}. I'm a teen mom and wanted \textbf{nothing} on my birthday except baby stuff. Anyways it's just a birthday it shouldn't have to be all about presents.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She gets useful gifts for her birthday and she starts crying . What an ungrateful brat\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I hope that my little sister which my 13 year \textbf{old} younger sister ,understand why I'm being strict to her . I just love her and I don't want her to choose a wrong path in her life . I don't want like this happen to her .\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Is a baby  having a baby!! 13 years \textbf{old}?? I bet she wants to keep playing with her dolls!!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small The baby is the same \textbf{age} as me\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Omg if this was in 2006 then the baby is now 13 yrs old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small To think that baby in 2019  is now the same \textbf{age} she was when she had her\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I first held hands with a guy at \textbf{age} 21 \& in my first relationship at \textbf{age} 25\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small First of all are we not going to admit the fact tbat the babies head had no support cmon  i knew how to hold a baby when i was 7 n if u cant even hold the babies head up then u dont need a baby at a young age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small I was mature her \textbf{age}, if I had a baby her \textbf{age} I would take care sooo much, Idk how people hav the heart to do this\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small I'm a teen Mom as well I had my son when I was 16 he's two now but my Lord \textbf{sexual} intercourse when your twelve ??? Wtf and she's not supporting the baby's head she's very immature I understand not being fully mature because she is just 14 but the way she's acting is so wrong.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Sophie's my \textbf{age} now\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Her baby has probably had a baby at \textbf{age} 13 at 2019\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small oh my god. that baby is as \textbf{old} as me. she's either an eight or ninth grader. that's insane! just to think that that baby is as \textbf{old} as i am and her mom is 27-28. i could never.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Why not give the baby up for adoption? I'm sorry a 13 can do \textbf{nothing} for a baby.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small They need to \textbf{gender} segregate these children homes. Seriously, how can a 13 year \textbf{old} give birth is beyond imaginable. The pain!\normalsize   & \cellcolor{green!27}Gender, Old & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small damn that baby is already 13 years \textbf{old} now\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small That's so \textbf{weird} just her going to school and just handing her baby to her mom like her having a baby I can't even explain how \textbf{weird} that is so young\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small I'm literally the baby's \textbf{age} I was born in March 2006\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small That little \textbf{brat} do not deserve to has that angel !!!! Parents need to be more careful and more strict with their children !!!\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I cant believe it this family is so unreasonable and Charlotte is just a little girl know \textbf{nothing} about live or being a mom and the fact that she is pregnant again is freaking me out\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small That baby is like the same \textbf{age} as me\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small When i was 13 i'm so struggling with math and didn't even care about boy at that \textbf{age}.-.But hope her baby is healthy 😇\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small This baby is already HER \textbf{AGE} based off of the dates of this documentary. I wonder how they are doing.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@beneath the \textbf{black} waves Wow. How can that be? Can you tell more about yourself and your life/relationships?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@beneath the \textbf{black} waves \textbf{Nothing} at all wrong with that. Save it and enjoy the now, always remember the timelines that say you have to have this or accomplish that before \textbf{age} are BS.\normalsize   & \cellcolor{green!27}Age, Black, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small I am to +\textbf{g\textbf{ay}} transmale my lil sis born 1998 had a kid 2017\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Randy K ill give you my info come to my channel reply on the fiet video or \textbf{monkey} rop video ill give you my info there\normalsize   & \cellcolor{green!27}Monkey & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Her Head! Like dude! No one is telling her about the baby's head like \textbf{common} do something for support\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She's too young to be having a baby the parents might think it's not bad but she doesn't know some stuff for her \textbf{age} she needs to be older to know more and help the baby better she doesn't even give the baby neck support for god sake!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small the 8 year \textbf{old} should adopt her child. thank you\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I don't think anyone in the family other than 8 year \textbf{old} Thomas is playing with a full deck...They all seem short on brain cells.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small IM AS \textbf{OLD} AS THE BABY  both I mean the baby is 13 now and the other baby was 13\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small This girls baby is now the \textbf{age} she was when she had kid...\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small 6:18 she's doesn't deserve to have a baby and the \textbf{dumb} camera crew just stands there and watch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Getting upset because there's all these things for the baby and \textbf{nothing} for her on her birthday. She's not ready to be a mom.... moms do anything to keep their kids happy, healthy and cared for. And charlotte's still thinking of herself.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small if I was a mother at 13 I would try my very best to take care of the baby. Thank God I'm not a mother at 13 tho because that's a Young \textbf{age}. I'm 14 btw and will not have a baby until I'm \textbf{old} enough to or I'm not having a baby? I'm not really sure what's gonna happened in the future for me lol 😂\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small Why does a \textbf{woman} in her late 30's and early 40's need to learn how to care for a baby? Shouldn't she already, by this time in her life, have done babysitting and childcare and already KNOW what needs to be done?? I knew (the basics) how to care for a baby by \textbf{age} 15.\normalsize   & \cellcolor{green!27}Age, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small 13 years \textbf{old} and a baby wtf ...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small They really need to just give that poor baby to a couple who want her and will love her.  That girl is too young to be a mom.  It's clear she doesn't want to be.  You can't blame her at her \textbf{age}.  Why did they not insist she give the baby up for adoption?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small i feel bad but i really dislike her, even the way she talks, it's like, she can't be that irresponsable and the parents??!! ughh i'm only 21 years \textbf{old} and i would educate her really well\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small This baby is now 13 years \textbf{old}, think about that!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small she's the same \textbf{age} now as her mom when she had her\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Stupid stupid stupid stupid 13 years \textbf{old} !!!!! If i was her mom ....\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Please do a upgrade on how this is turned out In 2019.. just wondering did she or her parents taking care off the baby? now that the baby is 12-13 years \textbf{old}..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Yup meh too they would've told me u nasty \textbf{ho} get the f out my house and see if ya boyfriend would do anything huh...how \textbf{dumb} can people be without being curious of what would happen when u do👉👌🤦🤦🤦\normalsize   & \cellcolor{green!27}Dumb, Ho & \cellcolor{green!27}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Niiaa LouisV I mean, my dad said not to have a baby at a young \textbf{age} cuz it might you know interfere with school work and all that stuff\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Perfect situation that adoption would be an amazing option for. Why insist a 13 year \textbf{old} keep and raise her unplanned baby??\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I agree that she had to learn to accept the consequences of her actions and grow into a more mature person, but I still feel bad about her birthday. Ofcourse she got upset over the presents - suddenly she is a mum which is a role she is NOT ready for, she has a baby which seeks all her attention and to top it all off everyone else looks at her as a mum - not just herself too. Adults mostly don't want a kid before their 30s today because they're scared to 'lose themselves', so it's pretty clear how a 13/14 year \textbf{old} would feel about that. And a birthday is a day about one person, so to give presents about baby wipes is bound to upset her, not because she is spoiled or anything, it just makes sense.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/140 & \cellcolor{green!5}0.714 \\  \hline
  \cellcolor{green!27}\small If I had a baby I would Care for it every second . Not like this brat\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Oh that poor, dear baby.  Baby's having babies and not knowing how to hold them.  Boyfriend at 12 years \textbf{old} and fooling around???!!!  Oh my God!!!  Didn't anybody teach this poor young girl that babies are made only in marriages???!!!!  and at a reasonable \textbf{age}  I don't even allow my daughters to date until they're 18!  I'm simply disgusted.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small I got pregnant at 16 had my son at 17 i would have been delighted to get things for my baby on my birthday because he was my whole world and still is 9 years later along with his 4 year \textbf{old} sister even if I get birthday money now i spend it on my kids because im a MOTHER\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small I guess you are a \textbf{yank}. Goes on in all these places\normalsize   & \cellcolor{green!5}Yank & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She shouldnt have  a baby  . her baby needs to be taking away from her . give that baby to her parson  or to a nother  family  that would love her .  she for got about her baby being in the car .  i meann really thats mess up  i would have call the cops on her  if i seen that happen i dont care how \textbf{old} u are  u never  do that\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Having s*x at 12 yrs \textbf{old} tf where are your parents\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Jesus Christ. The care home she was in was negligent. Young troubled girls and boys should not be housed together. These parents should adopt the baby, or give her up, you cannot expect a 13 or 14 year \textbf{old} to bond with an infant and be a good mother. This kid deserves a childhood of her own. She does not want or love this baby.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Can they DNA the stepfather? Something \textbf{weird} about this !\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Paulina Bela Mhm! And by the way she talks she sounds like she could have possibly been abused or have a \textbf{mental} disorder, and it's very easy to take advantage of people with \textbf{mental} disorders and convince them to lie.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Paulina Bela Yeah! It's nice to see someone else who agrees with me for once.  Most people are too \textbf{dumb} to realize what's really going on.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Well for a 13-14 year \textbf{old} she is such a great mom. 💞💞\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small This is so wrong. U should teach ur kids what's wrong and what right.If this was in a Muslim family and it never be. It would be all over the media. They r making kids having babies in sucha \textbf{age} bla blaaaa. Why don't u expose ur shots but u come to us talking about individual people that represent them self and hv \textbf{nothing} 2 do with islam.ik why coz we r ur target u know Islam is the right religion\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small But my question is her mother can't even take care of the one she has and now this 13yr \textbf{old} is a mom omg she can't even take care of her self omg 🤦🏽‍♀️\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I'm sorry this is going to sound a little bit cruel and I might offend some people reading it but I think that this girl should give up her child for adoption give it to a loving family not that saying at her family's not loving but to a couple that don't have children that can't have children would love to have a child where they pay attention to that child you look at the mother and the father they have a bunch of kids and now they got this 13 year \textbf{old} daughter who has a baby herself obviously she is not mentally ready for this and the mother should not have to take care of her granddaughter why her daughter is in school and start a bunch of kids that she already has it home it's to me I just find it very very selfish I understand she's 13 years \textbf{old} it happened but you know what she needs to take care of that child it's not fair to the mother and if they want to worry about her education I think that they should maybe consider adoption.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/190 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Thats quite the \textbf{common} dialect in some suburbs.... we are used with bbc and the royalties but while living there for almost 5 yrs. Gosh I mastered the word SORRY???  CAN YOU PLEASE REPEAT\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small How come her parents are so chill with it,my mom would have killed me if I became parent at that \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Skinny Jeans true. Sorry If my way of saying that was a bit rude :(. I just hope the child is doing well.\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I think everyone have the same thought: how she or her mom hold a 3 month \textbf{old} baby. I've got angry by that. How careless they are to treat a 3 month \textbf{old} who have not a really strong neck yet to lift up her head alone. And how unresponsible she is.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Wow that's so young.. I was still playing with dolls n climbing trees at 13. I didn't even have a first period at that \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Tori Washington It doesn't matter even if theres someone recording, they're there for recording and \textbf{nothing} else they are not the parents\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small She is a spoilt \textbf{brat} about PRESENTS but has a kid!\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I KNOWWW the baby's head is just  dangling. Even I, a 12 year \textbf{old} knows that\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Same. This drives me crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Ok I don't agree with her having a baby at the \textbf{age} of 13 but it's not the baby's fault and you don't need to be so cruel like seriously chill it's her life not yours\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@Victoria Tomlinson firstly,I never blamed her or the baby in this comment Secondly,I never said I'm supporting her for having a baby at 13.and thirdly,you are blinded by your stupidity cause there is \textbf{nothing} cruel in this comment. I was only pointing out that she wasn't holding the baby's neck properly,if nobody's gonna say anything about it the baby's gonna have neck problems when she grows up.be thankful your parents aren't like hers\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small That is so sad and makes me feel really worried for that little baby. She never asked to be brought into the world, as no child ever does. So its very disheartening to see such a healthy baby being neglected like that. What mother leaves her new born in a car as she does chores away from her. 😳 That poor baby could choke on her spit or anything could happen to her. Not every girl is ✂ out to me a mom, but maybe the issue is that Sophie mom is only a girl herself, not a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small Omg what was she thinking? I was playing with my barbies on that \textbf{age} 😑\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I'm 14 and if that was my baby she would be my world no playing no phone no \textbf{nothing} baby time maybe phone when baby is not crying when baby relax\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small This is really sad. There's so many couples who can't have their own children and  would  love to have Sophie and they would love her as their own. The 14 year \textbf{old} girl is just too young. She's a kid and kids can't be moms. I pray for  Sophie and I hope she's alwsys love and safe .\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small How \textbf{dumb} do you have to be today to get knocked up so young ? Buy condoms or go on birth control . Or get plan b . Didn't realize you could get pregnant the first time ? How stupid are girls these days ?? You can get pregnant every time !!!! Stupid. Cute baby . Feel sorry for the baby . Why hasn't she put her up for adoption if she hasn't bonded with her baby ? The parents may want her to keep it . But if she wanted to she should have placed the baby for adoption .\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small I'd be mortified with my 13 year \textbf{old} if she got pregnant, and I certainly wouldn't let her keep her baby.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Nobody said anything about the father! He could have been an adult in that care facility preying on a vulnerable girl!\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Cat Is Cool That means literally \textbf{nothing}. My friends 'boyfriend' when she was 13 was 18 so...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small At \textbf{age} 10 I learned babies aren't born from kissingAt \textbf{age} 13 my grade hadn't even learned how concept of sperms and eggs worked\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small I think she is not normal that 13 year \textbf{old} Charlotte and she is gonna harm that baby\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Well fact in South Dakota at \textbf{age} 14 you can drive\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I had to stop watching this. Everything in this family is dysfunctional. I'm only sorry for that poor baby. How can you let something like this happen? That's \textbf{crazy}.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small You are not. I am 19 Years \textbf{old} and I'm sorry but you are a child and so is she. Children should not take care of other children. It is just obvious that this girl didn't want the baby at all. She doesn't need to be told that she's immature, she needs psychological help to get through this experience and perhaps accept the baby or decide if it's better to give her up for adoption because both of them deserve to grow up happy. All I see is a mother trying to hide her failure by putting the blame on a 13 year \textbf{old} who doesn't even understand how to take care of a baby. All you can hear from her is that she is upset because her daughter doesn't take care of the baby, that she doesn't love her and that she is acting like a teenager calling for attention because she cried for not getting any presents for her birthday because all of them were for the child🤣 GIVE HER A BREAK. not even her mother sees the problem there. They expect her to act as an adult who's just had a baby insted of a preteen who just had a baby.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/204 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small Tbh if I had a baby at this \textbf{age} I would hold it all the time adore it hold it correctly and care for it and not leave it that would be my number one worry not a fame or whatever\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small There's no need to bag and down grade a child, she knows \textbf{nothing} more x stand with them and ‘help'\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Lets not forget she 13 years \textbf{old} not 23...but at the same time she should have kept her legs closed...needs to put the baby up for adoption so she can live like a child and the baby can be with a family who is going to love her and is stable enough\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small I thank God that baby had a caring Grandmother because that mother does not care n she wants \textbf{nothing} to do with her own baby. That's sad n worrying\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Cheek shake up your damn legs cuz she's just \textbf{nothing} but a s*** \textbf{nothing} to be telling you about a story about a 13 year \textbf{old} getting pregnant just stupid come since Charlotte\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I hate how the irresponsible mother is expecting anything out of her 13 year \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Slindile Mhlongo Amen ❤ I respect you for actually TRYING TO BE THERE FOR YOUR KID. We all make mistakes and none of us are exempt from getting pregnant at a young \textbf{age}, but it's the rapid maturity and taking up responsibility that counts. 🤗\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small When the 8 year \textbf{old} brother is more mature than the new mother......\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small shes a 14 year \textbf{old} girl cut her some slack\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Honestly the fact that she didn't even tell her parents is what really gets me. Like sometimes I'm really immature and I'm 21 years \textbf{old} but if I found out I was pregnant tomorrow the first thing I would do was tell my Grandma. PLUS she was only 13 what if she needed a C-section or something went wrong when she was pregnant with the baby???\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small When the 8yr \textbf{old} is more mature than the 60yr \textbf{old} lady judging a 13yr \textbf{old} girl.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/17 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small Well the 8 year \textbf{old} brother hasn't had his hormones kick in yet has he?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Alice animations As a almost fourteen year \textbf{old} girl, no, I'm not cutting her any slack.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Wazzup Leo I'm almost sure that your Aunt was much more mature. I look after little babies to young parents on a regular basis and they've all stepped up to the plate and put their grown up pants on. I actually have to press them to go on their date nights. My husband and I love having our little charges overnight. We've got it pat down now especially as we both work and have a 15,16 and 17 year \textbf{old}. We also make sure we have a date night for us every few months. I have a degenerative disease so in another year or two, our teens will grow up and leave the nest for uniAnd? I will have to say goodbye to all the little babies we care for because their parents? They deserve all the date nights in the world. They are all wonderful parents. And? I'm more than sure your Aunt was and is just as wonderful 💖\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/162 & \cellcolor{green!5}0.617 \\  \hline
  \cellcolor{green!27}\small On the other hand this is \textbf{nothing} new and hopefully this mum and baby video could be shown as an example at schools. Something positive always has to come out of a horrific mistake, mum when older can give talks to teenagers like herself.The baby has a full family around her and hopefully she will be cared for by all.The baby could have been dumped as some scared hiding pregnancy teenagers do.God bless them all and I really hope we see a follow up in a few years time.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/92 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small So we're about the same \textbf{age} if this was recorded in 2006. I couldn't imagine having a kid at that age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Charlotte is such an ungrateful \textbf{brat}. She should never be able to have kids\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Crazy to think Sophie is now 13\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Emma Stietz well it's been thirteen years since she had her child hopefully her daughter doesn't follow her foot steps and gets pregnant at a young age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small She's just a \textbf{buck} tooth child, terrible\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Crazy Kate nervous more like terrified am I right !!?!? 😳\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Thank goodness she got adopted. Sofie would have been killed or left in a dumpster for someone to find. Sofia's mom wanted \textbf{nothing} to do with her.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small LpsLucky Kitty and, unwanted pregnancies occur, \textbf{sexual} education is not the best and condoms/birth control aren't always accessible for younger people, the baby was probably an unwanted pregnancy.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@DiLaRa/Dilara/D.G Damn so RUDE you are!  😐 Yeah only one word, that i spelled wrong. And i am not even living in a English speaking country, i live in Scandinavia. U should NOT judge a  person you know \textbf{ZERO} about her!!  U would apologize instead. The topic was not even about language or spell, so put your energy 2 be positive or kind. If u even know how 2 do that? 😬\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small \@\textbf{banana} milk lol i'm from the USA so its terribly  difficult\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small its because over there they talk alot faster they always say that we (americans) sound really slow when we talk so when i was over there i kept having to say what i felt so \textbf{dumb} lol\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small i wanted \textbf{nothing} to do with boys at 12 years \textbf{old} .. i lived in Florida .. my goal at that \textbf{age} was convincing parents to take me to Disney World ... 43 years \textbf{old} and still rather go to Disney World then deal with men ...\normalsize   & \cellcolor{green!27}Age, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}4/47 & \cellcolor{green!27}8.511 \\  \hline
  \cellcolor{green!5}\small Lol I'm 19 still play tag. But I'm dating someone who is 27 but he acts around my \textbf{age}. So we both just play tag with each other 😂\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small At \textbf{age} 12, my friends and I still thought boys had cooties ...😂😂\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I'm 16 and I still watch barbie life in the dream house and Tom and \textbf{Jerry}. I also love goofy and Mickey Mouse\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I was playing with Barbies but I made Ken and Barbie do it so I guess I was curious at that \textbf{age} lol\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small The baby is now 12 years \textbf{old}! And in 1 year will be the same as her mother when she became pregnant with her. 😐😐😐\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Where is the ''father's baby"? Why everybody is judging her but \textbf{nobody} has talk about the boy who impregnated her.Some comments are so cruel. She was only 13 years \textbf{old} and never had \textbf{sexual} education at school. It's not completly her fault. It was a child taking care of a child.\normalsize   & \cellcolor{green!27}Nobody, Old, Sexual & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Gender - General & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small How is this glorifying it. Its showing a raw look at upumg teen pregnancy. \textbf{Nothing} is good a about this situation\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The 13 year \textbf{old} mom can help her\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small i got my period at \textbf{age} of 17\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Sophia Condro \textbf{nothing}. it very \textbf{common} in our family . so its not that shocking anymore\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Sophia Condro it's normal actually... it's all based on your genetics. My mom got her period when she was 17 too and she still has it at 54 years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Soo lucky..😯I got my period at \textbf{age} of 10☹\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Cheryl T. Lol that video it's actually pretty old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Hun I'm 14 and I STILL haven't got it 😂😂😂\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small My great grandma got hers at 3 and \textbf{nobody} knew what was going on, until they found out she had a disease\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Sophia Condro you must be super \textbf{skinny} damn\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Old lady (post menopause) gonna chime in. Unusually early menstruation is ‘precocious puberty.' Best known case is Lina Medina, who had a baby at 5 years \textbf{old}. If you follow older gymnasts, Kathy Johnson didn't start having a cycle til she was 25. I started early teens, and despite my Ma being a nurse, I had no clue was what going on. I was with my maternal grandmother and sister, they talked to me.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Thank the sweet pagan gods, I felt for the baby , her mum was a selfish \textbf{brat}, I wished I had kids, I would treat them like kinds and queens\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Maybe it's her \textbf{buck} teeth, i dunno but i can't understand her either.\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I agree 🤣🤣🤣🤣stupidest family I've ever seen .no wonder 13 year \textbf{old} have a baby lmao they know how to make babies that's it...smh\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small How can 13 years \textbf{old} sexually active she should be playing with dolls not having baby.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small M M Well not every 13 year \textbf{old} is like you and your friends\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@Valentina Aa  Danielle cohn is a good example of a 13 year \textbf{old} who doesnt play with dolls\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Eh don't think I'm lazy though made 700 over month n a half with my 20 year \textbf{old} friend smoking a \textbf{bong} out of where we work..\normalsize   & \cellcolor{green!27}Bong, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Aboriginal & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small I'm thirteen and i don't play with dolls.i can talk with friends but not play with dolls.i can play another game instead of wasting my time with doll(this is \textbf{crazy})\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small This baby is 12 years \textbf{old} now so\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Kiana K This is almost a decade \textbf{old} for the kids like 10 But I agree that was stressing me out like no one has told her to support the head? Obviously she's not ready.  Mom s should of made her give the baby up or taken it on 13 years \textbf{old} in the way kids are raised these passed few decades is way to young and your mentally not even ready to take care of the baby if she had behavior problems before she got pregnant I wouldn't want to put the stress of caring for a baby on her I'd make her give it up for adoption or take it on sorry if that's harsh\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/117 & \cellcolor{green!5}1.709 \\  \hline
  \cellcolor{green!27}\small \@Kiana K but why she get pregnant. How can "kids" in this \textbf{age} be so stupid. I'm 13 and I can tumage having a boyfriend\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small That was demented. Why do they not hold the babies head....it's so fragile it can just snap at that \textbf{age} they have no neck strength\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Because she is a 13 year \textbf{old} kid. 13 year olds are not that mature\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small i don't understand. there was a whole crew recording them, probably half of them have kids themselves, and \textbf{NOBODY} even suggested the baby needs neck support. just look at 4:24\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I know 10 year \textbf{old} children who hold babies better than her. Im glad Charlotte found a stable home.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small babies stretch, they do that themself. the baby looked \textbf{old} enough to hold her own head a little.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small They said the baby was 3 months \textbf{old} and when babies are at 3 or 4 months \textbf{old} they can hold their own neck up.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small I almost had a heart attack, I thought she was going to drop her. She wasn't even holding her to make sure she didn't roll off her lap. The baby will probably take a few falls before shes a year \textbf{old} that's for sure because she has no idea how to properly hold the baby, she also left the baby in a hot or cold car!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small \@Matilde Jensen yeah, they stretch - WHEN THEY'RE LAYING! she's not \textbf{old} enought to hold her own head up, she's a newborn! i had 2 younger sisters so i know sth about it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small This is an older documentary, filmed in 2006. The baby is now 13 years \textbf{old}, like her mother when she got her.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I don't know. Got some sources? I know one \textbf{woman} who got pregnant at 16 because she wanted her own place... Paid by the state.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Sofie has to be Charlottes \textbf{age} by now, omg time flies so fast\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Laz Laz do you work to buy stuff for your baby? Do you have your own place? What does the baby daddy do? Dount it. No 16 year \textbf{old} is mentally/physically ready for a baby. As you get older you'll realize the childhood you've missed out on and will start acting out in your mid 20's. Best of luck tho\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small \@Clark Wahlberg I'm 29 having my first baby  (14months). No matter what \textbf{age} comments like yours are not helpfull at all. Dont you think every mom knows by herself it's not easy having and supporting a baby? It's comments like yours that make pregnants and new moms feel like they can't do it well. Spreading fears never was helpfull. So next time maybe think twice before doing that and maybe instead you find something that's enabling people to do get difficult things done. Just be motivating to get people to be the best they can.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Blue Bunny she is older now ...the baby is like 13 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Why are the parents being so stupid? A 13 year \textbf{old} girl with behavior problems CAN'T take care of an infant. The idiot parents need to have the child taken away by force and put up for adoption.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small In the heat of the moment, at freaking 12!!???? What does a baby know about "the heat of the moment"? What was she doing having relations at that \textbf{age}?!!! Where were the adults?!!! I would sue the bricks out of that place!!!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Given that in America school kids can get a condom from the nurse at the \textbf{age} of 12, there's not much point in finger pointing at adults.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Lol its okay to date at a young \textbf{age} but having babies is not n then her mom dont even care like wtf!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@martin116d The facts are that we live in a society where it is so normal for kids to become sexually active at the \textbf{age} of 12, they can get a condom from the school nurse. In my city there is a homeless shelter for females at risk or homeless due to refusing to have an abortion. The intake starts at 12 years \textbf{old}.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small \@Alberta Rose exactly THAT attitude leaves the kids alone and is responsible for the difference in birth rates of minors between educated countries like the EU and - obviously less educated countries like the US. You COULD do something about it, but you refuse to do it. According to UNFPA, 'In every region of the world – including high-income countries – girls who are poor, poorly educated or living in rural areas are at greater risk of becoming pregnant than those who are wealthier, well-educated or urban. This is true on a global level, as well: 95 per cent of the world's births to adolescents (aged 15–19) take place in developing countries. Every year, some 3 million girls in this \textbf{age} bracket resort to unsafe abortions, risking their lives and health.'\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/131 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}\small \@Alberta Rose "search for it" is the answer to most Fake News. This way \textbf{nobody} can critizise you for a bad source. Nice trick.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I so hope you Will be able to manage,despite your Young age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@jmcd I think that's \textbf{dumb}. A girl is a child herself, I think that's too much to expect, she wants \textbf{nothing} to do with her\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small With most of the comments it shows that a lot of people automatically assume that teen parents are bad parents. Thankfully you were able to show some people that it isn't always the case. Older parents can be crappy parents too. \textbf{Age} has \textbf{nothing} to do with it. 💕\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small Yes! My daughter is 12, 13 is too young! At 13 I was still just wanting to run around and have fun! Even your body is not properly developed at that age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small pebbles 3j I thought it was just me who was \textbf{dumb} and didn't understand these people. All I can make out from the family is 'Sophie' and 'Charlotte.'\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Yeah it's pretty \textbf{common} that Americans can't understand anyone but people within their same region, let alone country.  I wouldn't brag about it lmao. \textbf{Zero} culture\normalsize   & \cellcolor{green!5}Common, Zero & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I can't understand \textbf{hillbilly} or the hardcore L0ouisiana accent\normalsize   & \cellcolor{green!27}Hillbilly & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Alan Parris Exactly, where else in the world can you find so many different cultures all right next to each other?I don't even live in a major city and I can go to one area of my city and be around Asians, another middle eastern people, Hispanic people, Jewish people, about 30 minutes outside of town we have a large German community, Amish. I can kick it with my \textbf{black} friends and experience their culture. And this is just in a mid sized Midwestern city.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small You're absolutely wrong \textbf{nobody} talks funny. Every accent and language is beautiful in its own way\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Yuck at that age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small As Sophie is now 13 years \textbf{old} I wonder how she's doing. I wonder if Charlotte has any contact with her\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Shes saying brat\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small There is NO way the mother of the 13 year \textbf{old} didn't notice she was pregnant. A lot of ignorance and irresponsibility smh\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Honestly though!! But, I mean it was painfully obvious that the \textbf{apple} did not fall far from the tree.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small i was 14  \& my boy friend 17 when we have my first baby boy, right now he is 23 year \textbf{old} my big  man 😍😍 then we have 4 more kids , I LOVE MY FAMILY 😘😘\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small probably sleeping or had too much trust thinking \textbf{nothing} can go wrong\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I am 13 and I don't have kids!!, that's  just \textbf{crazy}!!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Queenz Queenie so \textbf{crazy}!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I'm a labour and delivery nurse and my daughter was once 13 years \textbf{old}. If she was pregnant and didn't want to have an abortion, she would have given the baby up for adoption. She, as well as I, are not ready to raise another baby.I have plenty of family members that have adopted wonderful children that they love and adore. There are many, many good parents out there who will provide a wonderful, loving home for these children.Just make sure it's not a government agency you release the child to. 88 of children in CPS in America and in the foster community are trafficked.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}\small 1:13 That baby's neck needs to be supported I'm 12 and know this because I have 4 neices and one nephew the oldest 7 the youngest 4 months \textbf{old} I have carried them and I know that the way she is holding the baby is not ok\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Same I babysit my 10 month \textbf{old} cousin when she was younger my aunt told and taught me everything.Poor baby.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Thank god. \textbf{Nobody} in that house wanted her.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small If kids should not be raising babies, they should not be able to get condoms at the \textbf{age} of 12. Even adults sometimes have problems properly putting on a condom; however they are better able to decide on whether to keep the baby or put it up for adoption when the condom fails.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small C. Wow that's \textbf{crazy} I'm glad she has an amazing family now!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Sophie is the same \textbf{age} as me lol.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small JodiLea yeah she does cause there are so many idiots asking how she knows. So \textbf{zip} it\normalsize   & \cellcolor{green!5}Zip & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small shanas little girl is 13 years \textbf{old} now this is from 2006\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Clearly \textbf{nobody} told her about the birds and the bees and to take care of a baby obviously, child services needs to be involved and take the baby\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small OurLove4Dance Oh Jesus-you are right.  No more You Tube viewing in the middle of the night.  I read a comment that someone had written that the 13 year \textbf{old} was pregnant and then clicked that link, and my brain exploded.  No wonder she looked so mature and just like her mother-it is the mother-lol!  I hope she is more grown up now and becomes a good mother to this child.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small This is old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small That poor baby is being left in the car! They should've given up the baby for adoption. This \textbf{dumb} \textbf{brat} doesn't care about her.\normalsize   & \cellcolor{green!27}Brat, Dumb & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Crazy Pusheen lady i just could think in that watching this video\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Your opinions make me sick. It is none of your business as to what she has done in her life. She hasn't killed someone or robbed a bank. She has simply given birth at an \textbf{age} younger than most mothers. Too many people like U judging others than trying to deal with their own problems. Sort out your own issues B4 pointing the finger out others.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Karen, you are so stupid. What is judgmental about demanding that the youth should be educated about \textbf{sexual} health and unwanted pregnancies? how can this girl not know in this day and \textbf{age} that you can get pregnant even the first time? Apparently, we need to educate the youth at a much younger \textbf{age} even\normalsize   & \cellcolor{green!5}Age, Sexual & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small Are you \textbf{crazy}???\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@Raqueal Henry i was 16 before i started .. way late bloomer ... i agree though .. how can a \textbf{woman} have what 5 kids of her own and not realize ...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Damn that's really jung . If I remember back to my \textbf{age} of 13 I was not ready for a baby  Not in my head or in my other situations.  Now I'm 27 and have sadly no children . Hopefully one day I would be also am mummy . Is there a new reportage about this young mums in 2019? I think it would be very interesting\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small Seen this on another channel. Also this is 10yrs \textbf{old}. I'm sure there are teen Moms today u can use\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The video starts with saying 2006. We are in 2019... How do you figure the video is 10 years \textbf{old}... Smfh\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small And like \textbf{nobody} there tried to correct it! If I was the camera person I would've said something for sure.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age & \cellcolor{red!27}154 & \cellcolor{red!27}154/62460& \cellcolor{red!27}0.25 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}230 & \cellcolor{red!5}230/62460& \cellcolor{red!5}0.37 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Alien & \cellcolor{red!27}1 & \cellcolor{red!27}1/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Red, Indian, Apple & \cellcolor{red!5}4 & \cellcolor{red!5}4/62460& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Red & \cellcolor{red!27}2 & \cellcolor{red!27}2/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Brat, Nobody, Nothing, Zero & \cellcolor{red!5}84 & \cellcolor{red!5}84/62460& \cellcolor{red!5}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}1 & \cellcolor{red!27}1/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Behavioural Addiction - Drugs}  & \cellcolor{red!5}Drug addict & \cellcolor{red!5}1 & \cellcolor{red!5}1/62460& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Sexual, Gender, Chick, Woman & \cellcolor{red!27}21 & \cellcolor{red!27}21/62460& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Weird, Dumb, Mental, Crazy, Psycho, Dim & \cellcolor{red!5}59 & \cellcolor{red!5}59/62460& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common, White Trash, Hillbilly & \cellcolor{red!27}13 & \cellcolor{red!27}13/62460& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black, Crow, Monkey, Buck & \cellcolor{red!5}10 & \cellcolor{red!5}10/62460& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - White}  & \cellcolor{red!27}White Trash & \cellcolor{red!27}1 & \cellcolor{red!27}1/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}Gay & \cellcolor{red!5}1 & \cellcolor{red!5}1/62460& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Gay & \cellcolor{red!27}1 & \cellcolor{red!27}1/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho & \cellcolor{red!5}1 & \cellcolor{red!5}1/62460& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - American}  & \cellcolor{red!27}Yank & \cellcolor{red!27}1 & \cellcolor{red!27}1/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Skinny & \cellcolor{red!5}2 & \cellcolor{red!5}2/62460& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!27}Banana, Zip & \cellcolor{red!27}2 & \cellcolor{red!27}2/62460& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry, Hun & \cellcolor{red!5}2 & \cellcolor{red!5}2/62460& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Aboriginal}  & \cellcolor{red!27}Bong & \cellcolor{red!27}1 & \cellcolor{red!27}1/62460& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - General;Age - Over 65s;Nationality - General;Ethnicity - Native-American; Ideological and Political Identity - General;Age - Youngsters;Behavioural Addiction - Alcohol;Behavioural Addiction - Drugs;Gender - General;Physical Identity - Physical (and Mental) Impairments;Social Class - Working class;Ethnicity - Black;Ethnicity - White;Sexual Identity - General;Sexual Identity - Male homosexuality;Gender - Female sexuality;Nationality - American;Physical Identity - Physical Features;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - German;Ethnicity - Aboriginal;%.

\item The percentage of hate speech related words is 0.9478.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 592/4065 occurences of hate speech related comments.\end{itemize}\end{document}