\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_175.json :}\newline \par\Large\textbf {Title: \large  How Generation Z Will Change The World According To Experts | TIME }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small We won't. Expect nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Most of the comments are self proclaimed depressed teens who think they know everythingThis is just a phase in life no matter how much you dont wanna hear it. By the \textbf{age} of 21 your hormons cool off and your mindset growsYou realizie that shit you gave shit about is stupid\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small The truth is no other generation is better than the other one, one comes and goes, it does not make it smarter. the fact is that they all need the help of the savor Jesus Christ and without it they are \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small As a gen X'er,  I feel for the gen z's. My niece and nephew (my sister's kids) and my daughter are gen z. My son is born after them in 2008 so I don't know what he'd be. I'm reading some comments on how social media may not be causing anxiety or depression, but rather it's the state of the world that is, and I totally agree. The kids are REALLY scared for the future but feel powerless so they escape thru electronics, they feel super timid about social rules being and not being offensive and are insecure and super sensitive in a crippling way. It makes me shake my head that people want to blame something else rather than look at the world they're leaving to them as a major cause. Especially the boomers. My mom is a boomer. She divorced three times. My brothers are millennials and never married and one still lives in my moms basement. They're scared of relationships. They're screwed up. She does not fully understand how hard it is for the other generations. My daughter just started high school and last year she had to pick her courses. What do you tell a kid who may not even see half the jobs existing by the time she graduates? When my son graduates, will university even exist? Already it's becoming obsolete and too expensive. It's a dinosaur and behind the times. Many companies will train directly because many degrees will mean \textbf{nothing}. Education is still stuck in rural farming culture. The biggest fears are the economy, and climate change. It's not encouraging to see boomers so selfish and critical of younger generations even denying  climate change altogether because they don't want to change their lifestyle or give up comfort.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/294 & \cellcolor{green!5}0.34 \\  \hline
  \cellcolor{green!27}\small It's so \textbf{weird} how the vast majority of Gen Z kids (10 - 13) have depression or anxiety...Like damn who hurt you? I'm also 13 but I have never felt depressed or felt anxiety from what iv'e seen is that we are actually pretty optimistic but somehow we have a STRANGE obsession with sexuality? TBH from what I heard before the 90s like I guess kids had more freedom like they could literally stay outside until the light flickers or go to the movies by themselves. I want that experience while I am still young cause I'm practically a teen now and tbh I want more time.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}\small bruh huge difference betwee younger genz and older genz ..... younger genz \textbf{age} 7-12 are closer to gen alpha and older genz 13-18 are closer to the actual definiton of Genz and 19-24 closer to millennials as genz: i can sure tell you that we never had a smart phone growing up nor did we spend our time watching youtube like the younger kids gen alpha is a joke because of millennials look at the most subscribes YouTubersrn theres isn't much to group us all together as Genz and most of the time people get Genz mix up with alpha and gen y ( millennials....) like hello we are gen z...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small Do NOT call is igen, Gen Z, post-millenials,  Homeland Generation (I prefer this one), The Sisu Generation, or Gen Delta. It hurts knowing that the other generations take us for living on our smartphones. But your the ones who created it. We are just the result of the creation. We dont get depressed because of our smartphones, iPads, tablets, or computers. We get depressed because we are the only generation that accepts \textbf{nothing} matters and that the world is practically a shattered vase. We are depressed because we know the pain.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small Gen ALPHA is the smartest gen bc they know how tobuse a phone just as a 2 year \textbf{old} or some time one. They are getting smarter and i think they should notice that.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Old homies:Let's create social media Reality: people are getting addicted to this stuff\textbf{Old} homies: Oh shit let's just blame the babies\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small They are idiots i was born in 1989 i will be 30 years \textbf{old} next Thurs and man when i look at the world i see some strait goofy ass shit.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small A) The internet was commercialized in around the 1985 era when Britain and the U.S. saw the growth of early email services,B)  Generation Zs where Not Born-5years \textbf{old} when 911 happened and thus would not be able to remember the event\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small i was born in 2002 and i only really got into the internet when i entered year 7 in high school (which i was about 12-13 years \textbf{old})\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I have Replied on this Post for a while now, But this is my final one. Generation Z is a Young but not the Youngest generation out there. There is Gen Alpha, Whom literally always finds ways to Play with the Tech available to them. Gen Z is a Multi-Personality Generation, So you obviously can't speak for all of us. I'm currently in 7th Grade, but tbh, Me and MILLIONS of Gen Z feel as though they are Cheated or Ignored by the School System, and put as a Puppet. When most of us go to explain it to our Parents or Family, Many of them above the \textbf{Age} of 20 say "your generation is just lazy" or "we did much more work than you ever did". In a way, They are right, But mostly no. Millennials are the Generation just above us, and who still believe we are apart of them or a Puppet. Back in 2009, I used to see that the Millennials in my Family treated me and my Fellow Gen Z Family members like utter Dirt, While the Millennials were treated (not like angels but similar). 10 years later, In 2019, Me and my Gen Z family members are Grown as they were 10 years Earlier, But we are treated like Children, Even though we qualify as Teenagers. Moving on, Gen Y is VERY Similar to Millennials, So similar in fact, They are often being Joined into the Generation. Gen X, The Generation above Gen Y/Millennials is a very different Generation. They are very Organic and Nature going and often believe the 1950's/1940's are some of the Best decades in American History. Like almost all Generations before and after, You cannot Speak for all. Most of Gen X is the way the Stereotype is, The Nature going/Natural Organic/Angered at literally Everything wrong kind. Baby Boomers, Baby Boomers are one of the most "different" Generations out there, Simply because they were Hippies while most of their Children became Hipsters and their Parents being the Average 1950's Kind. Baby Boomers are the ones who do blame us for being messed up due to "social media" and Iphone use, But in reality, They were the ones who made it after all, \textbf{Apple}, Microsoft.. Etc.. Going deeper, The Silent Generation is one of the few, Very "antique" Generations. They are in fact (Different but not Different). They are the Reason Factories were able to bring up Economic Growth for Gen X, But ultimately failing to Help other Generations due to their motto for Kids/Teens: "To be Seen, But not to Speak" Or something like that. I would continue this, But time matters, so I will end this with one, Very simple Signing to my Fellow Gen Z, and also Gen Alpha: Pls fricken make this world greater and end the corrupt school system pls ;-;, the school system is a failure, and we should all learn via online (from tuesday to thursday), if this happens for workplaces as well, depression and stress make go down a bit, so pls do it :)\normalsize   & \cellcolor{green!27}Age, Apple & \cellcolor{green!27}Age - General, Ethnicity - Native-American & \cellcolor{green!27}2/512 & \cellcolor{green!27}0.391 \\  \hline
  \cellcolor{green!5}\small 'Values \textbf{transgender} and \textbf{sexual} orientation issues the most' if you consider bullying the hell out of them with memes 'valuing them' then yeah....sure I guess. Lmfao.\normalsize   & \cellcolor{green!5}Sexual, Transgender & \cellcolor{green!5}Gender - General, Sexual Identity - Transexuality & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small WHO TOLD U THAT WE HAVE ANXIETY BC OF SOCIAL MEDIA!?! DO YOU KNOW HOW HARD IS SCHOOL NOW?! IF U THINK THAT WHEN U WERE GOING TO SCHOOL THINGS WERE DIFFICULT U ARE WRONG! WE HAVE MORE ACTIVITIES AND EVERYTHING IS WAY MORE DIFFICULT NOW!!! THE TEACHERS DON'T CARE MOST OF THE TIME! TEACHERS NOWADAYS ARE MOST LIKE "u are bulling a kid everything is fine*! " U are chewing gum OUT OF MY CLASS!" ALSO IF U COMPARE US SAYING "oh your partner is smarter than u" and other shits like that *YOU ARE MAKING US INSECURE!!!! "But when I was at your \textbf{age} everything was different blah blah" OFC IT WAS DIFFERENT THE WORLD IS CHANGING U KNOW!!!!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small Why can't there be a single video on youtube about genertion z given by generation z. It's always \textbf{old} people thinking they know who we are and who we will become. It's ridiculous.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Previous generations, if you do not understand our Intellect then do not study us, technology completely changed us to smarter people, we search all kinds of things on google and we become more curious we learn and use the knowledge, you cant just say that were laziest generation looking at our phone screens on 24/7 doing \textbf{nothing}, while "\textbf{nothing}" is actually learning something new, if computer didn't exist I would have been a casual guy, now I stand out from most of the people and my personality definetly changed after the internet, I'm proud of myself and us, there are many Gen Z kids who wanna change the world to positive place and do not care about money at all, alot of Gen Z are smart and willing to change world, education system will be terminated completely after few decades because the way of it treat us is just horrible, they're forcing us to do something that we don't want to and that is a crime, however we might want to find alternative resources for further knowledge investments of the society.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/181 & \cellcolor{green!27}1.105 \\  \hline
  \cellcolor{green!5}\small Anna Mireault no we didn't. We had absolutely no millennial experiences at the \textbf{age} of 3 or 5 wtfðŸ˜‚ aside from the fact that although technology was present none of us got to use it, we're still pretty gen z. Definitely better than 2005 and beyond but accept you're a gen z.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small This makes me more depressed knowing that us gen zs are looked down upon. \textbf{Nobody} think that one day we will be the future, \textbf{nobody} knows past generations have given us so much problems to solve.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Honestly the Gen z generation is so much more realistic. \textbf{Nothing} is really sugar coated.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I'd say genZ should be described as 'planners' I have been exploring potential career paths from \textbf{age} seven, now at thirteen I'm using the sjwness of millennials to my advantage, toget in to an early college program called peg by sayin pg that my \textbf{gender} dysphoria is me being non-binary rather than actually trans(ftm). I'm going in to biology, and going on to a good graduate school to get my doctorate in biomedical engineering to design devices that actually make a difference for people who were injured or lost limbs fighting for our country. I plan to double major in art and design so that I can design appealing advertisement by myself, independently. Maybe the I in igen stands for independent, because most of my classmates are also planning to make it on the world on their own. If you want something done you have to do it yourself, but leave room for passion. I'm passionate about art and biology, and I want to help people who serve in the armed forces, to be a support to lean on. GenZ will be successful, using the shortcomings of previous generations to their advantage, helping each other because no one else will, seeking out facts for them selves because every other source has an agenda, this is genZ, and we're here to stay, until we inevitably fail and die.\normalsize   & \cellcolor{green!27}Age, Gender & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/227 & \cellcolor{green!27}0.881 \\  \hline
  \cellcolor{green!5}\small Where the hell did they get that we aren't spending time with our friends? Also why are they acting like our generation sucks because we have technology. We have more quality than our screens, and it's honestly disrespectful to act like we do \textbf{nothing} but stare at a screen all day. WE didn't make technology. And it shouldn't be the concern about how WE will change the world.Ifwe're sick? oH iTs thE phOnEsDepressed? SoCiAl MedIA, SCrEeN tImETired? NoT eNoUgH sLeEP (Also because of screen time)Generation Z? tEchnOloGy AddIct\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small Having readily available knowledge helps us, the Gen Z, to be realistic, to improve and change. Like sure, \textbf{mental} illness is on the rise (has been for a while), but heck that's why we bring it out because we want to be honest with ourselves and help each other out. We all have our struggles, and it's those struggles and relating to others that might actually leave a better world for the generation after us.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Lol humans are \textbf{weird}.ðŸ˜‚\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Why does no one mention the fact that the vast majority of gen z aren't sexist, \textbf{homophobic}, or \textbf{racist} we accept so many different types of people without being obnoxious about it like the millenials. We take time to get to know people before smacking labels on them like all the older generations and refusing to give them a chance. No one talkes about the fact that we have reached the point where we consider \textbf{homophobia}, \textbf{racism}, and \textbf{sexism} to be idiotic and illogical.\normalsize   & \cellcolor{green!27}Homophobia, Homophobic, Racism, Racist, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - General & \cellcolor{green!27}5/84 & \cellcolor{green!27}5.952 \\  \hline
  \cellcolor{green!5}\small This video is liberal media prapaganda. Gen Z and even more as you get older continuing into what the most accurate polls can predict, the next years of voters will be more and more and more conservative than the last years of voters with exceptions for typical party intervals. They are expected when they are all of voting \textbf{age} to be solidly conservative politically and extremely entreprenerial similar to gen Xer's but the degree to how socially liberal+conservative will be surprising. The ONLY thing confusing those media talking about Gen Z/iGen that aren't making propaganda pieces is that they seem socially "liberal" and conservative on punishment as well as economically conservative/liberal, except liberal in this sense refers to the laws while conservative refers to society's responsibility to people while liberal also refers to it's traditional political meaning and not it's reversed leftist meaning of "authoritarian progressive social laws that criminalizes all traditions and things older generations value," into meaning they are very liberal with the law with regards to social issues but very traditional with regards to expectations and the expression of those expectations (that fall under liberal social laws that allow expression for and against mainstream), economically traditionally american and conservative, both in their spending and the government's.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/209 & \cellcolor{green!5}0.478 \\  \hline
  \cellcolor{green!27}\small Can we stop hating on generations that are mainly comprised of children? Every generation has had serious issues, whether you like to address it or not, for example, ( \textbf{racism}, slavery, \textbf{sexism}, normalised abuse, \textbf{homophobia}, freaking WW1 and 2..)And yet, with all the other far more major problems that have occured, what will be the most tolerant and advanced people that will likely accomplish so many wonderous things, are being criticized for spending too much time on their phones.. A very minor issue compared to the rest of human history if you ask me..May I add that criticising children and calling them stupid for technology overuse has a sort of sick and twisted feeling to it? It's almost as if saying that they're already predestined to be moronic druggies that can't do anything useful for anyone.Mocking the younger generations has always existed and different generations just have different cultures than you do,criticising it doesn't make you better than anyone.Anyway, those are just my views, have a nice day to whoever is reading.\normalsize   & \cellcolor{green!27}Homophobia, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - General & \cellcolor{green!27}3/176 & \cellcolor{green!27}1.705 \\  \hline
  \cellcolor{green!5}\small Millennialist: 80s-90s Gen Z: late 90s-Late 00sGen Alpha: 2010-2020s The generation being surrounded with technology and phones is gen alpha. My cousin is only 8 and has never been seen without a tablet in her hand. As a gen Z member, I remember how everyone was amazed by the iPhone. It was kind of unfathomable to have a phone like that. Our house had only one computer which everyone in the house used. Eventually everyone got a laptop or desktop but that's because they became easier to purchase. Also, there was an increase for them in childhood education. Sure, I learned how to work a computer at school, and I've learned the proper way you should be surfing the web; it wasn't a big of a thing to use technology until I was in middle school. Advances in phones, tablets, and computers made it easy for anyone to communicate, research, and veg out however they wanted.What I think that is forgotten is that now, the teenagers who are constantly on their phones, are seen more as introverted losers. When in fact, this is the opposite. We go through the same social experiences as the older generations. We aren't unable to relate to others. We go through break ups, fall outs, drama, gain friends, build international relationships, learn about various cultures, keep up with family all using our phones. Sure it's not pen and paper, or face to face, but at it's core it is still considered communicating. It's the same as sending a letter and waiting for a response, but only quicker. Most people have \textbf{mental} disorders because there is no barrier from the real world, the thousands of ads we receive in one hour, and the pressure that we have to be better than our predecessors simply because we can type things fast. We process so much that it's hard to put it down when almost every thing you see is designed to prey on the weakest parts of your mind.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/334 & \cellcolor{green!5}0.299 \\  \hline
  \cellcolor{green!27}\small We all know that when we're older the human \textbf{race} will come to an end\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I was born in 2003 and this video is frustrating. My \textbf{age} group and those older than me as some may be on social media too much are also the ones addressing issues like climate change. When baby boomers are too scared to recognize it as a problem. Social media isn't only dividing us as \textbf{age} groups it's uniting us. Although, the kids I babysit rather go on there iPad than the park or do some crafts. I'm not going to tear them down, I want to see when their tech savvy minds can do for us as a whole in the future.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small What makes me depressed is me in the future being stuck in a 9-5 office job, working everyday in a tiny cubicle until I get \textbf{old} enough to retire.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small The lady has a adam's \textbf{apple}.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small this whole ass video is annoying and it smells like \textbf{old} people thinking that they did it best.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I hate that everyone keeps saying the reason we are depressed us because of technology. First of all most people are self diagnosing themselves and don't even know what depression actually is and!! \textbf{Mental} health is almost never fucking talked especially stuff other than depression. I root from a very toxic family and life and I think things like these are never talked about. Children who have dealt with trama at a young \textbf{age} are just treated like it never happened. There's alot of shit going on in families that everyone likes to pretend doesn't exist. I have issues that root from a very bad past. Lots of gen z are realizing the stuff they went through might have been toxic emotional abuse or manipulation. THESE STUFF NEED TO BE TALKED ABOUT. the reasoning isn't like being there's more tech it's because alot more people are speaking up about what they have been going through.\normalsize   & \cellcolor{green!5}Age, Mental & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/155 & \cellcolor{green!5}1.29 \\  \hline
  \cellcolor{green!27}\small It's interesting that this video didn't talk at all about how much this generation cares about the environment. There is a movement to reduce consumerism, go vegetarian/vegan, compost, recycle, buy less, have a smaller carbon footprint, stop fast fashion, etc. This generation also values travel quite a bit. The self-help and body positivity movement is thriving, as is minimalism, zero-waste, and nomadic lifestyles. This generation will not be known as "iGen" in fifty years..... my dad uses his iPhone and Facebook way more than I do, and I'm 20 years \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small It's because the boomers don't want to give up their jobs and just retire, most places I apply for is run by older people who refuse to give up their job even if they are \textbf{old} farts...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Why's everyone bursting at this? This video is actually quite hopeful and positive compared to the usual yet everyone is focusing on the little tidbit of social media. It always comes back to â€˜oh woe me, the bitter \textbf{old} people think we are losers because of what THEY did smh' but we fail to realize that we shouldn't take what we don't agree with to heart and instead use it to better ourselves. Social Media makes us connected but ofc it has its own cons, so what we can do is to emphasise the pros.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small Uhm gen z is ruining everything. Far too sensitive. Offended by a God damn apple\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I was born in 1997 (22) and I absolutely HATE when older talk about our generation, grouping all of us in a box, and talking about us like were some odd species. I honestly have so much hope for the future. What I see in my peers and the change that is happening right now because of young people is inspiring. I think the internet forces you to become more open minded. Now don't get my wrong, the internet can be a dark place and there are negatives to it, but at the end of the day would you choose living in the \textbf{age} where there were radios and no TV or just simply appreciate how far we've come?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/119 & \cellcolor{green!27}0.84 \\  \hline
  \cellcolor{green!5}\small Ok \textbf{old} people keep talking about what's wrong with our generation when yall are the ones that ruined the planet and the economy but ok whatever blame it on the phones which were created by the past generations might I add...mhmm\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small You want gen z to fix the world?? Then fix the fuckin education system and maybe we'll have the time! \textbf{Old} people\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Personally as a 16 year \textbf{old} female, I struggled so much with depression and the anxieties from social media. So for my 2019, I decided to remove social media from my life. For the two months I've been doing it thus far, I have had so much more perspective. It's good to take a break, and now I get to study my imbecile peers up close and personal.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Born 1996. I definitely knew a world without smart phones and the internet. Granted, the internet existed when I was a kid but it was nowhere near as commonly used in households. I grew up with a Nintendo, PlayStation 1, and CD players. When we did actually get the internet we had aol dial up. Smart phones were not a \textbf{common} thing until late into my teen years, and I didn't even actually have one until college. I have never considered myself Gen Z. I definitely have more in \textbf{common} with my older millenial sisters (80s) than Gen Z.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/99 & \cellcolor{green!27}2.02 \\  \hline
  \cellcolor{green!5}\small What is key to keep in mind is that \textbf{age} we were when the digitalisation happened heavily depends on where we live. For myself, growing up in central-eastern Europe, the Internet didn't really happen until around 2007, so it is far from true that everybody born in the "western world" after 1995 grew up with Internet at home from birth.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Honestly, I wouldn't say I'm born in the wrong generation but I feel as if there is a lot of pressure growing up in these times. And as accepting as a lot of us are of things that weren't accepted years ago, if you wanna set your phone down and not text back for awhile, people act like you die or don't care about them at all. Over a simple conversation. It's like everyone feels entitled to attention 24/7 and they blame you in some way of being a problem. Start something out of \textbf{nothing}. Of course someone of this generation can go outside and get away from technology but it gets lonely sometimes. Almost like it's \textbf{weird} behavior for an average kid/teenager. Inviting a friend is a hit or miss. They could either be on the same page as you or most likely, bring their phone to snap a selfie. But at the same time, I understand bringing your phone for safety reasons. That was the intention of phones in the beginning. Contact. Emergency. But I almost feel as if that leads to someone eventually going on their phone out of habit. If you have little self control... of course you'll check every 10 minutes. Now it seems the amount of followers and appreciation you get, determines self worth. Technology is amazing, I just wish that people could embrace both life and technology and important and not. This is just my thoughts on this. I just turned 19 this year and I feel as if it's hard to keep contact with people who have (so far) lived the majority of their lives online. No one can really say how this will turn out as kids will get older but I just hope my kids get a choice or can get balance between the real world and the online world. I just want them to be able to have a choice and be happy.\normalsize   & \cellcolor{green!27}Nothing, Weird & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/324 & \cellcolor{green!27}0.617 \\  \hline
  \cellcolor{green!5}\small I was born in 1996, and I feel like I can relate to both early gen z's and late millennials. Like, my childhood was playing outside with friends and family. I watched cartoons on a box tv with an antenna. I grew up with more VHS than DVD movies, and even when I got DVD's, they were normal ones cause Blu-ray wasn't really a thing yet. I didn't get an actual working phone until 8th grade, and that was only because I had after school clubs. If I wanted to use a real cellphone, I could... but there'd be no battery or no SIM card in it. And I was fine with that. My family didn't alway have cable. For half of my life, we'd have cable for Maybe a couple of years before it got shut off because we couldn't afford to pay it. I remember dial-up somewhat because we had a super \textbf{old} computer, and I clearly remember using a landline until I was about 14 or 15. But, what I don't get is why my parents, the same ones who wouldn't buy me my own phone until I was almost in high school, have gotten my 11 year \textbf{old} sister an iPhone, 2 ipads, and a kindle. She's 11. She only needs the iPad cause it's for school, and that's it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/224 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small Lol I didn't have a phone till I was 14 ðŸ™„ meanwhile nine olds are getting phones. Like 200 kids have \textbf{nothing} in \textbf{common} with 2012 kids so just stop.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I think that generations should be grouped up into short time frames. I was born in '98 and I have very little in \textbf{common} with the kids born post 2005. I didn't grow up with the internet on tap, and I was in secondary school by the time I actually saw and used an iphone in real life.  The decades of generations works for older gens as they had slower advancements in technology and society.  If we keep the generations as is, I'm put in the same box as someone whos baby pictures were taken with a smartphone, while mine were shot on kodak film.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small It's so \textbf{weird} how people born in the late 90s are this gray area between generation y and generation z, depending on what definition you look at\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Gen Z is the saddest generation, most everyone I know at school are depressed, have anxiety or some other \textbf{mental} disorder. I myself am struggling with some and may I just say, it fucking sucks. But we are also the generation with a great sense of humour, we use jokes to cope with bad situations.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small what i'm worried the most is that our parents and the \textbf{old} generation is gonna leave the society facing new problems such as the dependability with social media to get through any occassion. Seriously we really dont need the internet and social media because it. is. ruining. us. And it's for generation z and the next generation's problem to face in the future as well as with global warming and unsustainability with pollution -ehem--plastic pollution.  But we must realize that as early as now we need to solve it. The \textbf{old} generation would leave the future with something they started that they didnt know could create a problem and the generation z are left to solve it which is very inconsiderate. But then again, so was the generation before them to them haha.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/133 & \cellcolor{green!27}1.504 \\  \hline
  \cellcolor{green!5}\small I was born in 2003 but i can clearly remember a time where we didn't have internet in my house - i probably didn't have internet until the \textbf{age} of 7?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small 1995 Internet commercialised world wide Gen Z startGen Z: it should be way after 9/11 (Tragic American event)Let's ignore a major events that changed every country for the better, of 1 tragic event in one country. By that logic Japan, certain parts of Africa, UK, Germany, Poland and more should change. Some countries went through huge changes while others didn't.The idea of basing a generation on tragic events mainly from the US is ridiculous.If we go by a tragedy that messed up every country all Generations would have to change and some unchanged.You can correct me on this opinion.To those using personal experience, everyone is different with some similarities due to riches (poor, middle class or rich), \textbf{ethnic} background, religious or no beliefs, and how you were brought up.You can be 30, 20 and 8 but be brought up by the same generation with similar things within the household and values but only differ due to changes in neighbourhood and background.Some of the newest gens alpha Z and oldest Gen Y were raised by Gen X, thanks to egg freezing, surrogates and....single mothers doing their thing.If we add changes to education, gaming systems and apps (some are using as change of generation) that would make generations ridiculously small. People in the 80's had games and cartoons that still being made so I wouldn't use that as a generational difference since those things started earlier.Just a cusp opinion generation 5years before 2000.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/251 & \cellcolor{green!27}0.398 \\  \hline
  \cellcolor{green!5}\small I'm sorry...but we are the children of Gen X and I think we will be a great generation...its too early to see some of the affects etc. Almost 18 years \textbf{old} and I never got my real first piece of tech until 9th grade\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Maybe because it's harder to get a license, job, a partner, and get \textbf{alcohol} than previous generations not because we can't do them ever thought of that?\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I understand that social media has pros and cons. But people seem to focus on the cons way more. I also understand that social media can bring unhappiness to people but social media isn't he only reason that people have depression or anxiety. Lots of people act like 'social media is the devil and it's the only thing that causes \textbf{mental} health problems' but that's not right. Personally, I have depression but I don't use social media Social media at all. Sorry I wasted your time reading this, but a lot of people don't like the internet and I just needed to vent.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small I am a millenial-Gen Z cryptid. I identify more with millenials than Gen Z.I don't completely relate with the kids who said "We've only known phones that are smart". I definitely remember having a landline, then flip phones, keyboard phones, THEN smart phones.Technology has changed so much from my childhood to now in just a few short years. Thinking about it makes me sick with nostalgia. Just a few examples:Music: Tapes to CDs to iPods to Limewire to \textbf{Apple} Music to Spotify streaming. Movies: VHS to DVDs to Netflix Nintendo: Gameboy to DS to Wii to Switch The Internet: Only html pages that were extremely basic and slow to load versus what we have now that is lightning quick and cluttered with ads everywhere.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small This shit gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small They are weak. Born of sensitivities to everything on earth from climate and environment to food allergies. They have 0 survival skills in natural world, and know even less of what it means to be a human on earth. Youve created delusional beings that require some type of constant adult to always be around because they have no individuality and lack self actualization. They are nice beings, most of the time though. Politics and tech is a complete waste. \textbf{Nothing} of the new world is sustainable or will last.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small transgender issues - but of coiurse you had to put it\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small As a gen Z born 2000 I have somethings to say. diversity is \textbf{g\textbf{ay}}, stormtroopers are better then rebels, /pol is never wrong, and if your \textbf{fat} you need to lose weight \textbf{fatty}.\normalsize   & \cellcolor{green!27}Fat, Fatty, Gay & \cellcolor{green!27}Physical Identity - Physical Features, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/33 & \cellcolor{green!27}12.121 \\  \hline
  \cellcolor{green!5}\small Born in 1999 and i am a college grad in holland and am teaching gen Z that are like 10 years olf to be honest i relate more to millenials than gen Z and i consider myself millenial because in holland everything you guys grew up with in the 90's was here later as in programs on tv.. i grew up with \textbf{old} school toys and mentally also am older than my peers so yeah to be honest that's how i see it\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small Millennials begin in 1982 which means they came of \textbf{age} on or after the year 2000, Gen Z are born from 1998 since they would be too young to remember 9/11. That is the true \textbf{age} difference between the two\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@Shade Scientists demarcate the \textbf{age} of 3 when children are too young to remember. I was born in 1988 and I am a native Miamian. I was 4 and half years \textbf{old}  when Hurricane Andrew hit Miami.  I remember the winds, the destruction, I wasnt even in preschool yet.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small \@Shade exactly that's why I'm proving my point if u were \textbf{old} enough to remember at 4 or 5 9/11 then you are born after 95 into 1997.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I was born in 1980 and i own a business that employs a lot of teenagers. I love this new generation of kids. They blow the so called millennial generation out the water in terms of \textbf{common} sense and resilience. I think this generation will do great things.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Hey, at least we can wear pants now. Or not, since there are some religious groups that still against \textbf{woman} wear pants.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small M.L. Soll in generation Z too (born 2003) but I'm not depressed nor I loathe myself, I'm curious tho, why do you hate yourself, why is depression so \textbf{common} in today's world?\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@PugAssassin Another \textbf{common} claim I see is global warming and other world issues that we have access to through social media and such. You don't have to be depressed over that, instead you can go out and be productive, work in self growth, exercise, read, practice a new language, go help out in a charity, volunteer hours, etc.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small I hate how people assume I use the internet and social media to compare myself and to play around all the time. Yeah, I'm Gen-Z by technicality, I use technology to write and communicate because I have anxiety and depression, but that depression came later on in life when people started telling me I was going to fail because of my career ideas. I didn't grow up using computers. I grew up running around in the backyard and wanting to be a cowgirl with a big truck. Then I learned about writing and dance and I have to use the internet for some of the connections with that and help because people hear "I want to be a dancer" or "I want to be a writer" and then bam! "You're going to be a failure". But I go online to research how I can make it possible  and bam! "You rely on the internet too much, why don't you ask people around you for help" like... bitch. \textbf{Nobody} around me knew how to dance or thought I should be a dancer. Did you want me to run away to the city, possibly end up on the streets alone hating myself everyday or killed? Or in the same safe enviorment, hating myself because of how much you tell me I'll never be worth anything and progressing in my career digitally?\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/229 & \cellcolor{green!5}0.437 \\  \hline
  \cellcolor{green!27}\small Idk bout u guys but for me (or in my place) Gen z is mostly stressed rather than depressed because they already have to think about the future the time when they are already adults and they Must have decent job and all, so you need to get higher grades. My classmates would rather think about wanting to get decent jobs and all at a young \textbf{age} not being able to enjoy being young and just stress about those stuffs when they are already adults they want to be "mature" because they are expected to be, expected not to make the same mistakes again seriously if you talk about any kind of game and they see you like it you'll be bashed (for ex. Minecraft, Roblox, sorry I only knew the popular ones and Fortnite ain't a thing in my country ) I mean when will we enjoy these? When we grew up?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/153 & \cellcolor{green!27}0.654 \\  \hline
  \cellcolor{green!5}\small Im gen z but these dudes won't do anything, we are so \textbf{dumb} girls only care about being better than men and focus on pure internet and try to play the rule of a man and not a mother, men are getting softer and focus are Jordan's and shit like come on we are losers\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small As someone from the stone \textbf{age} I say gneurzch\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small As a \textbf{alien} u pple are fycking stupid  I'm pass on killing ur planet u do just fine on ur own\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I was born in 2005 and I don't have a phone until I was around 12 so basically all my life have grew up without internet which I'm so grateful for because were last generation probably ever that didn't have internet, I mean look at my 4 year \textbf{old} cousin who got a fricken iPad for Christmas! I went out with my friends before I had a phone (and after?ðŸ˜‚) but I rode my bike, went camping with my friends, had the best  sleepovers, played in my back yard all day, went to my friends houses in the summer and I feel like the kid kids today won't be able to do as much because of the dangerous internet and it's sad but I'm grateful my mom and dad didn't get me a phone until a year ago so I could enjoy my life without one while I can, but even now I don't go on it a lot mainly due to the fact I have no friends lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/169 & \cellcolor{green!27}0.592 \\  \hline
  \cellcolor{green!5}\small Please stop using the term "iGen". We're not an \textbf{Apple} product. fuckin hell.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Gen this gen that whatever we're all humans living in the same day and \textbf{age} . \textbf{Old} people get addicted to, this is just a lecture on technology.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small This is such a myth I was born in 2005 and I'm \textbf{nothing} like people born in 1995 experiencing 9/11 and the economic crash in 2008 the technological difference between our childhoods was the original iPhone to iPhone 6's which is not similar at all I do not feel a connection with people of 1995 at all and feel like the can not claim a title if gen Z because it's just not true not to mention they are potentially 24 where i am 13 there is just little connection and this is not who I want to be represented by\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small Gen Z, please find way connect science with God. Since we can see global news and recognize that global warming is real and our planet can live perfectly fine without humans. So you should certainly know Noah's flood is also absolutely real, 70 of earth is water. And our bees may be extinct by 2050, losing 80 of our vegetation and fruits. You all know colonizing Mars, gives 1 of world in slightly better place, 99.99 of us civilians on a dying planet. Know that the 1 don't care about the environment as long as they can make money off you and your future children. And while they have us fighting each other politically, socially, racially, economically, they are each other...they keep producing Hollywood films advertising their junk and making us pay to view their ads in theaters and on Netflix shows. Let's remember we're all brothers and sisters, fathers and mothers, uncles and aunts, granddads and grandmothers, sons and daughters, builders and lovers, we're all Human.Jesus 11 Christ. Ecclesiastes 3:11 Eternity in every heart. John 3:16 God â¤ï¸ the WORLD, death to LIFE. Daniel 5 God writes with Human Finger. Genesis 3 Forbidden \textbf{fruit}(\textbf{Apple} iPhone) Do NOT give to children under 12. Jeremiah 29:11 God wants to prosper you, think about the FUTURE.\normalsize   & \cellcolor{green!27}Apple, Fruit & \cellcolor{green!27}Ethnicity - Native-American, Sexual Identity - Male homosexuality & \cellcolor{green!27}6/215 & \cellcolor{green!27}2.791 \\  \hline
  \cellcolor{green!5}\small Or a combination of the two. Or the two things have a \textbf{common} cause.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I think technology and social media just amplify and show you how alone you really are. If you're jealous of other people making friends, being famous/succesful, etc... There is \textbf{nothing} stopping you. You just dont want to get up and do something. Its kinda your fault, but social media really shoves it in your face about how youre a loser. Also most people aren't succesful BECAUSE of them being addicted and constantly stuck to their phones\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small \@Daddy Deutschland Boomers didnt cause the 2008 crashes gen X and millennial's took loans they couldn't pay making banks go bust. And no idiot they did fight for ay rights You just hate them fr being \textbf{old} and successful.  [LINK] \normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I love it cause they show childs, and some of us are 23 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small They blame social media and comparing themselves to others for gen z being higher in depression and anxiety rates, it's true but in the way that this generation is wildly more aware of what's going on in the world at a younger \textbf{age}, they don't get the filter of the local news station or paper to see what's going on in the world, they have easy access to every angle of everything going on. Living in the moment isn't as easy of a choice anymore with having to deal with the fact that things like global warming aren't jokes anymore like they were 20 years ago and that fossil fuels are running out because some rich people wanted more money, they're left to deal with real life consequences of the generations before us and well if that doesn't give you anxiety I'm not sure what would\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/146 & \cellcolor{green!5}0.685 \\  \hline
  \cellcolor{green!27}\small Older gen Z's aren't as obsessed with technology as young ones. Kids born in like 2008 were using IPads as soon as they were like 12. Yeah I always had the internet and computer games, but smart phones weren't \textbf{common} until I was in 6th or 7th grade. We'll really see how gen Z is in 10 years. I can honestly say that there are very prominent differences between people born when I was born (1998) and people born in like 1990, but the differences between us and those born in like 2012 are more profound in my opinion.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small I'm currently in 8th grade, so I would like to inform some adults what goes on in a Gen Z's day to day life. I would like to inform you that we are not what we think. In my school, I can't speak for others, the kids are pessimistic, tired, sad, and opinionated. "See Something, Say Something"(an initiative based on preventing violent acts and improving student \textbf{mental} health through student awareness of problems and learning to see signs of depression in and outside of school, mostly based on social media) is shoved down our throats, teaching us do something most of us refuse to do, not for our sake, but for others. Almost all of us know what it is like to be in a dark place, and we know that adults knowing that you don't want help from does \textbf{nothing} but hurt you. We are too sympathetic to do something before they try to handle it themselves, but no adult understands that, and rather sees \textbf{mental} illness as something that they could prevent by forcing the child to talk. In my school, we talk about what a wreck the school system is. State testing gives us anxiety that we can't afford. We retain very little of what we learn, a result of being taught to learn for a test, and not to learn for ourselves. We find our interests outside of school and have intelligent disscussions about these interests with our friends. We pressure ourselves to succeed in school, even though we find most of it pointless, because if we don't do well our failure will be on the news, mocking us for being the "worst generation yet." In my favorite class, English, we have class political discussions and have Socratic Circles, a learning form borrowed from Socrates, in which we teach each other based on what we already in an organized and polite disscussion. That is the only class I have ever taken in which the teacher encouraged us to be free thinkers, further our learning by ourselves, and to pursue our interests. In fact, we once had a debate on whether Fantastic Beasts was \textbf{racist} or sexist because of an article that a student read. Our teacher assigned homework that night was to research the issue, form an educated response, and be ready to discuss it with the class the following day. Our generation believes that learning like that furthers us, and learning based on a test hinders us. In my school kids consistently get an unheathly 4 to 8 hours of sleep. Studies show that this effects our ability to learn immensely, as well as our \textbf{mental} heath, and physical growth. Not only are we physically tired, we are mentally tired. Tired of having to break down walls adults have thrown up, tired of putting up walls around adults because we are scared of our beliefs getting out. We just want it to stop.In my school, although we are depressed and sleep deprived and annoyed, we want to change the world. We have lofty goals and would do so much to accomplish them. I don't know what career I want, but I want to change the world. I want to make someone's life better, to put a smile on their face. I don't know what that is yet, but it might end up having something to do with the psychology field. I find it incredibly interesting. I know other kids do too, but none of us say anything, because when we do, people are concerned that we are depressed or need a therapist our self. Every kid I know has a passion for something. Every kid I know wants to change the world, to fix what the adults messed up. So yeah, we're a wreck. But we also have our heads on straight. Social media is not just an escape, but a learning system. We don't know if there's hope, but we want to make our own. So maybe we're better than you thought, or maybe we're worse. My friend gave me an interesting fact the other day: they used to put people on insane asylums based on stress levels. Based on tested fact and observation, almost all of our generation should be locked up by those standards. As a generation, we intend to change this, even if we lose everything in the process. That is what Gen Z is like. Depressed, but determined. Thanks for reading.\normalsize   & \cellcolor{green!5}Mental, Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/742 & \cellcolor{green!5}0.674 \\  \hline
  \cellcolor{green!27}\small 16 year \textbf{old}, so also Gen Z. This is the most accurate thing I've read about us. So accurate I'm at the point of tears. Even if other generations don't understand us, we pride ourselves on understanding each other.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small As a 16 year \textbf{old}, I think generations before were much worse, in some places in the world there were racial segregation and remarks from some groups of people, disease and illnesses which are easily curable now and world wars and poverty.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Millenial here. Dont you think the sleep deprivation thing is a \textbf{common} teenager thing? In my highschool and university years everyone was sleep deprived (and some at work even). My generation also suffers from general anxiety, i dont get how it became such an epidemic. Just yesterday we were almost 10 people between 25-30 and suddenly we realized almost all of us had major anxiety.And about depression for the future, i actually think things in some countries are going to shit but on the bright side i see people becoming more tolerant, more accepting, more united. So just give it time. Right now my generation is (or is becoming) the main work force and we are changing how we work, what is expected. Older people in businesses are being forced to change cause they need to retain young talent and we dont care about the corner office or that \textbf{dumb} stuff, we care about life quality. So yeah, basically, we still have hope :)I think we are going on the right direction. I just hope that when my generation gets into politics and become the presidents of our countries they will do things better. I still worry about how in some countries (mine included) people praise such \textbf{dumb} political figures. But idk, maybe the educated group of my generation will be the future presidents and your generation, that is more concerned about the world in general, will vote for them and we will see a brighter future :)Hope this helped somehow!\normalsize   & \cellcolor{green!27}Common, Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}3/254 & \cellcolor{green!27}1.181 \\  \hline
  \cellcolor{green!5}\small When you're \textbf{old} enough, run for office. The world needs people like you. You made my day bro, rock on\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Omfg someone though fantastic beasts and where to find them was \textbf{racist}!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm a 17 year \textbf{old} and I really liked a paragraph from this fantastic speech, if it's okay with you, can I use it for my assignment? it's this speech that I have to give that's about our generation. again, if it's cool with you.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small 22 years \textbf{old}. We were a bit more optimistic than you guys were, but you guys are going through a darker period in 2019 than I went through in 2011.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Becca, I'm going to 8th grade in about two weeks and I hope that I can be as clever as you. This is the truest and most thoughtful thing I've read on Gen Z. I recently got into it and I'm terrified about the world that is given to us. So many adults in my life and on the news (of which I've seen) talk about the bad and the only thing I think of is 'Ok, how the hell can I change this?!' I have had many conversations about college, my main problem is not 'What do I want to do with my life?' rather, 'What can I do that will help?'  I am willing to learn and do whatever I possibly can to help the future of the world. I hope you become some sort of leader when you become of \textbf{age}. You should be going to 9th grade, right? You have a great way with words! Best of luck in high school, Kayla. ðŸ˜\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/167 & \cellcolor{green!5}0.599 \\  \hline
  \cellcolor{green!27}\small As a 16 year \textbf{old}, I must say that this is so true\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small As a 18 year \textbf{old} Gen Z I completely agree with you 100 many adults put their problems on us and thinking that we gonna save the world and bs but we are the generation that social media and pressure from adults have been shoved into our throats and we had enough of it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Right now all the conflicts happen between genZ and millennians mostly about equality and \textbf{mental} health but in 30-40 years when they die then a Massive change in the world is gonna happen for the better. And millennians always say we are on our phones a lot, yeah we are that's the future - technology, it's a true prediction. (just my opinion) ðŸ˜‰ðŸŒ\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small WE'RE ALL DEPRESSED \textbf{G\textbf{AY}} MEMERS AND WE'RE GONNA CHANGE THE WORLD\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small I think the cut off point for gen z (as a gen zer) should be between 2006 to 08 because those born after that didn't experience the economic depression of 2008/9 and therefore will act quite differently from those born 1995 to 2006. Right now for a lot of the world, the economy is looking up and those kids who are between 10 and 6 rn will only know a childhood where their parents could afford to, say, buy the more expensive options in the store. Plus, as a sixteen year \textbf{old}, I would find it a little hard to believe that that a child born the same year that the iPhone 5 released will have a similar childhood to me (b.2002).\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/122 & \cellcolor{green!27}0.82 \\  \hline
  \cellcolor{green!5}\small I have an iPhone 5, and it's \textbf{crazy} to think that my phone is older than some children in my generation\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Just gonna shout out that the speed at which technology developed between 1995-2012 was astronomical and there are very, very few similarities between the children born at each end of that spectrum. 1995-2003, and then 2004-2012+, would be much more appropriate. I was born in 2000, and am currently in university, and every encounter I've had with someone born after 2005 has shown how different our childhoods were. Obviously, those born closer to 2010 are still in their childhood, but there are some very fundamental differences in upbringing that make it impossible to compare our \textbf{age} groups. I distinctly remember a time when iPhones didn't exist. When the iPod nano was the greatest technology. When blackberries were the backbone of our \textbf{nation}, and how much the iPod Touch changed everything for kids. I burned CD's, my main "technological" form of entertainment was CD computer games, my family did weekly Friday trips to blockbuster for movie night, and I memorized the days and times my favorite shows would come on TV. Yes, using Word and Powerpoint and being able to do online research was integral to my schooling, but that was something we had to teach ourselves because adults were still learning too. Social media didn't exist; those without strict parents had MySpace, and then in late childhood had FaceBook (not me), but "Youtubers" didn't exist, "Instagram personalities" didn't exist. Technology was not integral to our social environment. Kids born in 2010 have phones at the \textbf{age} of 8, because that's what's normal. I see 10 year olds on Instagram, completely exposed to current celebrity culture and fashion and \textbf{crazy} representation of the ideal body/lifestyle, born in 2008; Instagram didn't even exist when I was 10, and the idealization of celebrities was not nearly as big, with the only way to keep updated being TigerBeat and Seventeen (magazines). Kids born in 2012 were given iPads to entertain them as babies. It bothers me to have my year get grouped in with 2004+ because we really don't have anything in \textbf{common}, yet experts who study generations have never recognized this.\normalsize   & \cellcolor{green!27}Age, Common, Crazy, Nation & \cellcolor{green!27}Age - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}5/348 & \cellcolor{green!27}1.437 \\  \hline
  \cellcolor{green!5}\small What gets me mad is the fact that most adults think they know so much about technology, that "it's bad and will negatively affect our future generations". In some ways, yes it will. We can become more self-centered and their are bad uses to tech. But if you choose to use it properly, you can help create a better world for yourself and others. We now have access to things they didn't teach in school, we can work on any skill, anytime, and have a lot of opinions and things to see. We can change our views, and not just believe the things the people around us do. Before technology, we never really knew the consequences of our actions and people who haven't been traveling in the sea might not have noticed the trash that's washing up all over it. With our technology we can create positive change and influence others around us to do the same. We can communicate with people we might never would've been able to without tech. It has many bad sides such as cyberbullying, hate, and can be used for doing the opposite as mentioned in the good side.You can also share much media and this tremendously helps develop small companies (which also helps the economy). I think the world has been made into better place with technology, and we're finally starting to care more about solving world issues and fixing the environment. We've helped clean up what the last generation has left and are helping people and ecosystems worldwide through the use of technology. And hopefully our future generations will continue to do the same. Sorry for the very long comment, I just had to rant about this \textbf{common} misconception.EDIT: And yes, I do consider it unhealthy if you're on your phone too often. It can lead to depression and anxiety, and we need to balance it. I'm just saying that technology is a very useful tool if you use it properly and responsibly.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/331 & \cellcolor{green!5}0.302 \\  \hline
  \cellcolor{green!27}\small What a joke!! Theoretically this sounds great but reality is much different!They're lazy, want everything on a platter, generally pretty \textbf{dumb}, has little ability to interact with any \textbf{age} outside their own and the list goes on and on!!We'll see the 'true identity' of gen-z only in a few years from now. However, if you look at the gen-z's reaction to \textbf{brexit} e.g. their general knowledge and opinions about politics and the leaning toward socialism (of which they clearly know \textbf{nothing} about), I believe, the world is in for a rough ride!!\normalsize   & \cellcolor{green!27}Age, Brexit, Dumb, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters, Nationality - European or anti-Europeans, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/94 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Or maybe we just see the world differently. Gen Z is set to be the least religious generation ever,  we're more inclined to believe in science and research things on our own, we are the most pro vaccine generation, for our \textbf{age} we are the least sexually active generation. We don't drink or smoke. We lean to the left as social democrats, but we understand why socialism didn't work - authoritarianism. We aren't stupid. We think critically, we're realistic to a detriment, we are determined to clean up the mess people like you have made of our Earth.  Do you want to know why birth rates are projected to fall once we reach our childrearing years? We don't want to raise a child in a world as toxic and disgraceful as this one. We see the dark side of our achievements as a species. We are determined to help begin the effort to fix the world. Just remember -Young â‰  stupid\textbf{Old} â‰  smart\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/165 & \cellcolor{green!5}1.212 \\  \hline
  \cellcolor{green!27}\small Stats say 1 of every 2 marriages currently end in Divorce (thanks to 3rd wave feminism)... 1 of ever 3 or so children are abused. One of every 3rd kid has "\textbf{mental} health issues".When I see kids at the Mall, I just remember these stats, because it's Just A Mirage.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small I like being part of Gen Z because I have things to do (my parents are busy a lot). At the same time though, most of my generation makes really offensive jokes but than will say well it's not \textbf{homophobic}, \textbf{racist}...ect... because I don't have anything against those people I just think the joke was funny...and that's a dangerous way of thinking. To be fair my generation is still pretty young and they are a lot more accepting than previous generations. (But we all have \textbf{mental} health problem and joke about our pain - -(My sister spelt something wrong and the teacher marked it right 'cause "It sounded right, and she'll have auto correct anyways.") SO HOPEFULLY THE YOUNGER HALF AREN'T ALL ILLITERATE!!!\normalsize   & \cellcolor{green!5}Homophobic, Mental, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General & \cellcolor{green!5}3/123 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Same I also have \textbf{zero} social media.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small true...sounds like we're an \textbf{Apple} product, lol.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small iamindianbutidont pooponthestreet Exactly, it just lets \textbf{Apple} have more control over the market\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I'm 15 years \textbf{old}, so I know \textbf{nothing} but a world with technology. But it's all about how you were raised, because I just learned that kids having their phone out at dinner is a problem. I didn't even know that was a thing, because I wasn't even raised with the thought of that possibility. So yes technology, but its also about how you were raised.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small We won't change anything cause the \textbf{old} generation are the one that have the power and are in the high places and control the government you won't see the effect of the us until we are \textbf{old} enough to be an elected official.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small Same, I was born 96 which from multiple sources tells me I'm gen z. But then people will say "no you're millennial". It really doesn't matter, especially when you're born so close to the cut off point. You can go one way or the other. Like I have more in \textbf{common} with gen z then I do millennials. So I just go with gen z personally\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small The world is a really shitty place. I've learned that already at a young \textbf{age}. We have to watch what to say, be careful to not insult anyone. Parents teach us that if you don't study well, \textbf{nothing} will happen in your life. We see bodies of water filled with trash, landfills that extend for miles, plastic everywhere. One day, when we're an adult, we will have to clean up the mess you made. We are the ones who have to suck it up and listen to you going off on how we are always glued with our phones, obsessed with social media. I'm not trying to be rude here, but can older people just stop it with those? We experience the most suicide rates and yet you still like to rub it on us that were useless and pathetic, more you're wondering why this is happening. People may call me pessimistic but I'm honestly trying to be realistic. Anyway sorry for this long ass rant, I just wanted to get it is my mind. Also I don't mean if your older you're already like what I was talking about. I just see most of the adults are like this.\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/200 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small Oh and generation z there are only two genders and no women are not equal to us real men nor as strong as us real men and note i said real men they are equally strong to little \textbf{pansy} generation z soy bigs who wear \textbf{skinny} jeans\normalsize   & \cellcolor{green!5}Pansy, Skinny & \cellcolor{green!5}Physical Identity - Physical Features, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small This is what they should of done a very long time ago took the younger millienials out of my generation and gave them their own generation so they could ruin it because I was never coddled niether was my beautiful wife we believe in working hard for everything we have and own I'm only 31 years \textbf{old} and I'm already a retired firefighter I retired from the fire service because I injured my middle back and a month ago my nurse practitioner diagnosed me with osteoarthritis in my thoracic spine and I have chronic pain all over my body and my wife works 70 plus hours and when we go out on dates we have our cell phones in our pockets and we socialize and we confront people face to face the younger millienials is the ones who ruined my generation\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/141 & \cellcolor{green!27}0.709 \\  \hline
  \cellcolor{green!5}\small i pressed on this thinking it would be about how gen z have accepted that most of them will be unemployed, they're all  more accepting than the generations before them and are not the type to stay silent and let capitalism rule because they already have \textbf{nothing} to lose. But nope, it's about cell phones.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small I mean I don't think equality is one of our top priorities I just think we're more libertarian about social issues. Like the mentality where if you want to identify as a \textbf{woman}, a man, both, neither, or something else, I don't care as long as you don't make it my problem.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small As long as they are not \textbf{dumb} liberal's I fucking hate my generation..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small As a part of gen-z I see that kids end up on our phones and social media a lot just because it's really the only option we have to connect. I and plenty of others I know prefer to meet and talk in person but with the increased paranoia of millenial and late gen-x parents we end up being stuck at home and away from other people making us have to turn to the internet for social interactions. Besides communication we also end up getting into the world at a later time with the average \textbf{age} of being allowed outside without an adult raised from 5 to 13.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small Mouth Eater i was allowed to go out at the \textbf{age} of 8 without an adult on my block but other places by myself is 12\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I am a 95 baby, so the beginning of the gen it's. But I have spent most of my life hanging out with the baby boomers and was homeschooled. So here is my view.My generation is to much into the phones. They can't live without them. They don't have a good work ethic. The eant to do \textbf{nothing} and get paid for it. They are to quick to yell "I'm offended". We are to accepting. Anything goes.No morals. Marriage doesn't matter, just move in, etc.I thing the baby boomers were they best also the greatest generation.I do not have high expectations for the future.Remember, I am one so I can say this without "offending" anyone.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}\small Maybe we don't like marriage because we don't want the government involved in our relationships. Maybe before you comment on someone's living situation, get off your high horse. You were deprived of a proper education, free of religious bias. You were robbed of your right to learn how to think freely. You had to hang around a generation that has persecuted people based on who they love and what they believe. A generation that has polluted this earth near its breaking point. A generation that is incapable of taking responsibility. Lack of morality? That doesn't affect you. Since when does the \textbf{sex} life of others affect you?Best generation? Honey, they didn't do shit. They coasted off the fact that they were the children of the Greatest Generation (look them up), and then when it was their turn to lead, they messed almost everything up.Bad work ethic? Most of us throw away our youth and focus almost all our time and energy on school and employment, to the point where we don't have many friends, if any. Phones are useless? Do you know what we do on them? We read the news, make our planners, do our homework, research, get what social interaction we can, etc. Stop believing that you're better than us - because you've clearly had your view tinted by ideologies that have worn themselves \textbf{thin}, and have become what holds us back as a society. We don't live in an Archie comic. Get over it.\normalsize   & \cellcolor{green!5}Sex, Thin & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/249 & \cellcolor{green!5}0.803 \\  \hline
  \cellcolor{green!27}\small We are Generation Z, We are a generation of Conquers. So you have this generation, a generation of easily offended crybaby snowflakes known as Millennials who kind of made it to college who had been told that they're amazing and they're perfect every way that they were,when in reality none of them actually are. They went to college, accumulated thousands in student loans and then there was a reality check in the real world, and we have seen all kinds of problems with Millennials in the real world. They bitch, whine, and cry about getting paid low wages and not being able to get a job with their \textbf{gender} studies degree, after that they blame the system and vote Democrat in an attempt to create an impossible utopia. Where as Generation Z has been told the most horrendous things that you could possibly imagine due to the internet, a uncensored and unfiltered flow of information. Generation Z was the first generation to be born into the internet \textbf{age}, socially our parents or guardians were not able to protect us from the harsh reality of getting offended as so many parents of Millenials did. And as a result we have the outrage culture perpetuated by Millennial snowflakes, while Generation Z learned to be self reliant, and resilient. And this has many positive results on our generation, while Millennials tend to be optimists, Generation Z tends to be realist, Millennials want to be discovered while Generation Z want to work hard for success, In the realm of maturity Millennials tend to have a prolonged adolescence while Generation Z is "up-ageing".\normalsize   & \cellcolor{green!27}Age, Gender & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/268 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small Gen z kids are majorily young kids and they're as young as 8-9 years \textbf{old} I myself am 16 and my brother is 9 so I happen to think that is not the older generation of gen z that's going to change the world ,but the younger generation because they were born in the middle of the new technologically advanced time.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Gen Z has been really screwed over. I love branding 'no work life balance' as a 'work life blend'. Way to brand the degradation of employment benefits as a positive. Gen Z and Millennials don't work 7 days a week because of their 'better work ethic'. They/we work 7 days a week because we hold more debt at a younger \textbf{age} than any other generation in American history and have been brought up in an economy with stagnant wages that can't pay for city rent prices without working more than one job. It's called hustling because we're all getting hustled.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small As someone from Gen Z i feel like it's not the phones or new technology that's making us  depressed or have \textbf{mental} health problems. A phone or Internet is just a device which makes our lives easier. When older generations say that we spend too much time on our phones i wonder if they realize all the things we actually do with a phone. Talking to friends, reading a book, doing reserch, making our planners, reading articles, watching videos and learning new things everyday. We are not just  doing useless things or simply wasting our time. Lots of us do use our phones for a lot of good. I don't see why phones can make people depressed. If anything it can help a lot of people having \textbf{mental} health issues as there are many things online which help you go through some of the things you go through. You can talk to someone who had gone through similar things that you are dealing with. And trust me i know that it's helpful. However, i think that many of us have mwntal health problems is because we are more open about it. I bet other generations also had lots of people with \textbf{mental} health issues but due to circumstances they didn't really believe it could happen or they weren't so open about it. So basically just stop blaming everything bad that happens to Gen Z on phones.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/236 & \cellcolor{green!5}1.271 \\  \hline
  \cellcolor{green!27}\small Baby Boomers are the reason why environmentalism became a thing and why equality exists. You're just butthurt your \textbf{Gender} Studies degree didn't get you the job\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Maybe one of the reasons why we're seeing more young people talking about their \textbf{mental} health issues is because the stigma against \textbf{mental} health issues is going away\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@pink pink  I don't know what it was for you, but that's not really the reason. Most parents do allow their kids to go outside. Of course parents don't allow their kids to stay too late. Who knows what kids could be doing at the time? Drugs, \textbf{alcohol}, or \textbf{sex}?\normalsize   & \cellcolor{green!27}Sex, alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol, Gender - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Speed Gonzalez the \textbf{old} people on comment sections of political videos\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I'm a 15 year \textbf{old} who is just below the middle class.   Minninum wage was never made to pay for college. Its meant to maybe get your first car in highschool or just help rent a small apartment. The only people who say the world is gonna end in 12 years is AOC and other idiots lmao. We are in a rather good state I would say when you were preparing to get nuked any second. Maybe stop getting useless degrees too? People with degrees in the arts have a 11.1 percent unemployment! Like half the girls in my school want to get deggrees in the arts or psychology or other degrees which wont get you far. My grandpa and his 19 siblings all lived in a 2 bedroom house which they wernt able to pay off decades later. People are like o0ooO I cant buy a 4 bedroom 2 bathroom 2 story house out of new york o0oh my god damn baby boomers wreeck economy!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/166 & \cellcolor{green!27}0.602 \\  \hline
  \cellcolor{green!5}\small \@Showery Yeah sure, I want to become an animator but I'll go to med school so that I won't be drowning in debt, because like, what's working a job you hate for the sake of the \textbf{patriarchy} any way?\normalsize   & \cellcolor{green!5}Patriarchy & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Hana Foudah no one destroyed equality you \textbf{dumb} duck. Equality has always been bad, it's just gotten better now.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Thanos Elmo Thanos Elmo Are there really that many places in the US to study \textbf{gender} studies? only one university in my country offers it.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small baby boomers were the beginning but I can still get along with many of them, millenials are the ones who think that destroying the planet would cause depression, even though their isn't enough destruction to warrant those views.  It's not like I can't go to Miami or anywhere.  There's still snow.  It's liberal generations I hate for ruining job opportunities and enforcing child labour acts.  make the employment \textbf{age} 14!  I can't just focus on my own life because everytime I turn around I see liberals trying to use my money to experiment for their moral consciences and namesake on a bill of some type.  I don't need other peoples money, I need you to quit being a \textbf{q\textbf{ueer}} and let me worry about myself, I need you to stop making sure I'm not offended, I need you to find me some tru frens, not PC fairweather frens from well to do spoiled baby-boomer and millenial hipster families.\normalsize   & \cellcolor{green!27}Age, Queer & \cellcolor{green!27}Age - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/158 & \cellcolor{green!27}1.899 \\  \hline
  \cellcolor{green!5}\small \@Mr. Bean eww priuses, Chevy Silverado, or you're a \textbf{commie}, only marxists drive priuses and teslas\normalsize   & \cellcolor{green!5}Commie & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small 9 Year \textbf{Old} Watch CBN, world news, Japan news, Canadian, Australian News, floods, earthquakes, death happens everyday, 150,000 people die each day, babies die, children die in their sleep...God has you alive for a reason. He loves you and is giving you an opportunity to join Him in heaven. Only through Jesus can happen. Don't make the mistakes of genZ's and end life meaninglessly. Ecclesiastes 3:11. Beautiful time. Eternity in human heart. Beginning to End.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Nothing in this video made me think drastic change, tbh. I personally believe that humanity should always advance, and we used to advance quite rapidly with technology and new creations back then but now I feel that growth has been going down. I wonder where all the geniuses and the inventors and creative minds have gone...all I really wish for is to grow and advance even more. I want to be able to see our world change drastically in a good way. But...I'll admit most of us genz people are kinda lazy, but at least for me I've been getting much more energetic and ready to learn as I get older...so maybe it's possible that we can get off our asses and advanceðŸ˜„\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/123 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}\small Kyle Pickus speak for yourself I agree with \textbf{NOTHING} you said and a lot of people my \textbf{age} don't either\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Kyle Pickus I agree with it, and I know other my \textbf{age} would too\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The igen..O shoot, not inclusive enough, I mean the weGen.No, I just assumed we as a \textbf{gender}.O well, stick to boring ol gen Z. ðŸ‘ŒðŸ‘ŒðŸ‘Œ\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small generation Z is gonna be rampant with \textbf{mental} illness\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I'm GenX. Still kind of a slacker, but my son is GenZ. The things I really respect about his generation is how open they are about \textbf{mental} health issues. They've taken the shame out of a lot of it.  Also,  I've seen GenZ totally chew someone out and still respect the pronouns they identity with. I still kind of marvel at how they do those things.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small I am part of generation z and i dont feel like we are going to do very good. I feel that we have a ton of deppression and anxiety and sucicide. We have drugs and \textbf{alcohol} at our disposal. Many kids are having kids in highschool, no hate but it does make us grow up faster. All of this pressure is on us to do better things and look and be better, i feel like we will crash and just give up. This might just be me but look at us we go on social media to get away. We are "petty" because we carry things close to us and dont know how to get through them other then forget for a while and deal with it later. Wtf. At least thats how generation z is looking at life.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/139 & \cellcolor{green!5}0.719 \\  \hline
  \cellcolor{green!27}\small Actually - GenZ is less likely to have kids at a young \textbf{age}, and more likely to remain virgins into adulthood. And those of us who are sexually active are vastly more likely to use protection. Which is good.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small That's just pessimism. We still have a ton of nature, we get a very diverse weather all around the globe. We have amazing people and thinkers. We have the ability to be the first people to colonize Mars with a robotic AI or to be successful self employed entertainers. If you think the world is horrible then that limits your hope of what you can do with it. Even being a homeless person is an option, maybe not a healthy one but you get to explore with \textbf{nothing} holding you back not even taxes. I'm glad to be living right now with everyone I know\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small Ella Hughes what about things to be positive about like the civil rights movement, woman's movements, \textbf{g\textbf{ay}} rights movements, etc? As a gen z, the world would be much different if those movements never happened. So why not just enjoy the fact that we now have those opportunities?\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small The world owes you absolutely \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Crazando anonymous They weren't scared of WW2 yet they were scared of the cold war. They had drills where they'd hide under a desk at school to keep cover from an atomic blast, after realising that you basically can't defend that without a bunker, they stopped. And no, if you're poor you don't just automatically have the greatest opportunity to be rich. Calling us wealkings is the equivalent of calling a 3 yo unintelligent because they're unable to speak properly or even at all. This is because a majority of iGen are teens. Also, calling us wealkings is still quite \textbf{dumb} because we can't do much at our ages. And America is also a place where you have to be afraid of shootings anywhere you go. During the first 21 weeks of 2018 there were 23 school shootings. Winston Salem Shooting, Italy Texas shooting, Benton Kentucky, Philadelphia, Los Angeles, Oxon Hill, Maryland shooting, Nashville Shooting, Parkland shooting, Savannah Georgia, Itta Bena, Norfolk Virginia, Mount Pleasant, Jackson shooting, Birmingham shooting, Mobile shooting, Seaside shooting, Lexington Park, Gloversville, Raytown, Ocala, Palmdale, Santa Fe, Noblesville, Thousand Oaks, Watertown, must I keep going? Yes? OkayLong Beach, Tallahassee, Springfield, Minneapolis, Detroit, Vallejo, LA, Riverside 2x, El Dorado, and many more. Being pessimistic is more reasonable than thinking everything is a-okay in the United States. Being the smartest or most popular brings competitiveness. Oh, you want us to be philosophical? Sorry, that's not how the world works. Not everyone has experienced what you have. You're merely speaking off of how you see the world rather than looking at your own generation's panic. You want us to all be philosophical as if it's the answer to everything. Not everyone was born in the same conditioning as you. Empathy is basically the most you could give someone as most of us are too scared to speak to others about our true intentions and/or feelings. Let's take someone who was abused as a child and currently is still abused, tell them to not be pessimistic and tell them to be philosophical, how would that play out?Oh, you're afraid of your father beating you? I'm sure you're just being pessimistic. Someone just threaten your school with a picture of a gun on Snapchat saying, "Don't go to school tomorrow" and no one arrives and you think what pessimistic idiots. You just got done hearing of the Syria bombings and watching a couple of children dying, oh, just pessimism. You hear gunshots whilst in school and hide under your desk, oh, why am I being so pessimistic? See how \textbf{dumb} it is? Oh, your two cousins were killed in a school shooting? I'm sure you just need to see the world positively.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/453 & \cellcolor{green!27}0.442 \\  \hline
  \cellcolor{green!5}\small Real ARMYkid I agree with your statement. However, other generations tend to belittle our own for these types of issues. They act as if our lives are perfect and we have \textbf{nothing} to complain about while they have that privilege. We are seen as inferior to them cause we are advanced and â€˜have it easy.' It's just not correct for others to treat us that way when we are only being human. Of course, it's not everyone who says that type of stuff but I have seen a fair share of it and it angers me that some will never understand.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small \@Inno Noctis Under trump the economy is booming and your more likely to die going to school than in school. Your just lazy and want to blame other things for you doing \textbf{nothing} and thus being unhappy.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@billy osullivan Notice how you know \textbf{nothing} about me, yet you still attempt to call me lazy lmao.The economy wasn't booming before 2016, in which we were born into.Just because the economical status is increasing greatly because of one president doesn't mean it will continue to do so.Also, there's \textbf{nothing} wrong with being sad, if you haven't noticed.Just because you have something doesn't mean you can't be sad. Having money, toys, technology doesn't make everyone happy.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/80 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@billy osullivan Also, that makes no sense, doing \textbf{nothing} and being depressed?Most people are depressed because of the homes they were born into in which may have abusive parents, an abusive family, or they move homes a lot due to them being into foster homes.Doing \textbf{nothing} could make someone depressed, but you attempted to assume I'm depressed by doing \textbf{nothing} lmao.Assuming things on the internet is the most clown thing I've ever seen.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}3/76 & \cellcolor{green!27}3.947 \\  \hline
  \cellcolor{green!5}\small \@Inno Noctis I said under trump so after 2016. I never sad there is anything wrong with being sad and you missed my point doing \textbf{nothing} makes you sad and i ever said anything about material making you happy which is a lie one of the happiest places is a slum in india. Citation for most depressed people having abusive parents.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small There is Definitely a \textbf{Transition} group, those born in 1994-1999. I was born in 1996. We basically just copied off of what teenagers did (born in 88-93). And the Biggest thing was, technology was almost the Same for All of us (88-99).It's not the same comparison as someone born in 1996, and someone born in 2006. Everything changed in 2008 -- and those born in the mid-2000s were just babies. So we can't relate lol\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small Instagram is 10 years too old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Marmite Are u kidding me. We're getting more ignorant.Go back 50 years and u will find all of those kinds of people but doubled. I guarantee u could find somebody preaching how \textbf{black} or \textbf{g\textbf{ay}} people should die. People are just starting to realize the amazing medicine we have.\normalsize   & \cellcolor{green!27}Black, Gay & \cellcolor{green!27}Ethnicity - Black, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/49 & \cellcolor{green!27}6.122 \\  \hline
  \cellcolor{green!5}\small \@Marmite We're not getting dumber, you're just \textbf{dumb}. The world has always had these kind of people. Yes, we have SJWs, flat-earthers, extreme global warming preachers and non-global warming preachers. But we're advancing in technology really quickly therefore we're getting smarter.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small My little sister is a 'Gen Alpha ' can't wait to see what changes they will make. Also, how are you going to put a 23 year \textbf{old} and a six year \textbf{old} in the same generation??\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small How \textbf{old} people can blame younger generations for everything part 1\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small That lady is wrongWe really don't care about \textbf{gender} identification because there are only two genders\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small While Gen Z doesn't seem like the best generation to many, I (being apart of GenZ) believe we will surprise many. We grew up in a world that's more connected than ever before, which means it's easier for people to be hurtful, but it also means many kids and teens are more aware what the world is like. We grew up in a world where being different is normal and is often celebrated and discrimination is seen as something awful. We grew up in a world where \textbf{mental} health messages are spread better so more people are aware of it and know they are not struggling alone. Sure there's a lot of violence happening but lots of that is caused by people from generations before us, and sure not everyone will grow up to be good, but I know many people my \textbf{age} and younger who want to make a difference in the future and hopefully change this sometimes scary, ugly world into something beautiful and loving. I hope you have a good day. ðŸ˜€ðŸ˜€\normalsize   & \cellcolor{green!5}Age, Mental & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/175 & \cellcolor{green!5}1.143 \\  \hline
  \cellcolor{green!27}\small I was born in 2002 and yet it's such a stark contrast compared to kids born now or even in lets say 2006. I still remember coming home and sitting down to watch tv or play with toys. And now kids know \textbf{nothing} else other than technology at their fingertips. Something I wasn't used to.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Am I the only one who thinks that's a transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I am right on the cusp of either millennials or gen z... And honestly I don't want to be apart of either group. I am \textbf{nothing} like my peers. I don't really fit in either group.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I like my generation bc we're so open to a lot of things. Like for example, a few years ago it might've been \textbf{weird} to see a \textbf{g\textbf{ay}} couple openly kissing in school but now it's just like eh ... who really cares? I think because we grew up with things like that a lot of us are open minded and we're learning to think for ourselves instead of listening to society and older generations.\normalsize   & \cellcolor{green!5}Gay, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/75 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small im tired of seeing \textbf{old} ass ppl talk about young ppl..\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I'm 18, and I'm telling you 100 America will not last another 100-150Years. No way. Western kids are so consumed by social media. Our society has rebuilt a peer system thru phones. The Importance of most kids lives is to be accepted and that starts with socializing online constantly. It's all fucking \textbf{dumb}. It's honestly just sickening to me to know how normal it is for people to sit on their phones all day. Kids today would of gotten bullied and Harassed in the 80s and 90s. Kids today are either soft or extremely bummy and brag ab doing shady shit. \textbf{Nobody} has a work ethic anymore because times have changed so much. It used to be respected if you were hardworking and had accomplishable goals. Everything is jus different now. Gen Z will be the start on the downfall. I promise you. Nothin lasts forever. Hard times create strong people Strong People create Good Times Good times create lazy peopleLazy people create hard times. This is fact.\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/170 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small NO NO NO NO NO NO NO NO NO! Two Gen Zers and one clearly not Gen Zer do NOT get to speak on behalf of the entire generation WHEN most of us ARE STILL IN SCHOOL (elementary through High school!) Our identity has not yet been formed! Our experiences molding our minds are not yet done!! NOT ONCE did these 'experts' mention the things that have effected us on the daily. Our memes, and the internet culture that has grown BECAUSE OF US! The daily fear we experience because 'safe' locations (schools, concerts, bars, etc) are target by people who are not being barred from weapons of deadly destruction! And people are are able to receive those weapons and need help are failed but the system sloppily put in place to 'help' them. THESE THREE PEOPLE do not speak for an entire generation! Not once has a person spoken on behalf of a large group of people, who most of  WERENT EVEN \textbf{OLD} ENOUGH TO VOTE IN THE LAST USA ELECTION! Not okay! Not okay!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/176 & \cellcolor{green!27}0.568 \\  \hline
  \cellcolor{green!5}\small Another case of \textbf{old} people being hating lik bruh b honest lik what generation doesn't complain about the next\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Expected \textbf{nothing} from this video and was still disappointed\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Majority minority don't matter as we are Americans...  as long as ur not \textbf{black} or Mexican or Muslim then u r welcomed\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Wtf, I don't have anxiety and depression because I have a cell phone and social media. I have anxiety and depression because the generations before me are screwing my future up the ass all the while telling me "you are too young to understand; you are too young to have a say". I have anxiety and depression because the people who do get a say are doing things at my expense; at OUR expense. I have anxiety and depression because the people who YOU have put in charge say things like "THOSE people don't exist" and "Journalists disappear all the time" and are derogatory toward women, PoC, \textbf{L\textbf{G\textbf{BT}}}+ people, people with \textbf{mental} illness and disabilities. I have anxiety and depression because you are killing our planet. I have anxiety and depression because governments are kidnapping people and attacking people and killing people. I have anxiety and depression because scientists are being silenced. I have anxiety and depression because NO ONE is being held accountable. You can't have the nice kids, the "respect your elders" kids, the "do as your told" kids back, it's too late for that. You've drowned them all in debt and anger. All that's left is us. And we're sick of being spoon fed your garbage.\normalsize   & \cellcolor{green!27}LGBT, Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}4/209 & \cellcolor{green!27}1.914 \\  \hline
  \cellcolor{green!5}\small The older \textbf{woman} is talking more shit about gen z, and the younger dude is justifying our actions. I see through your shit Time.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Hey not my fault that there's \textbf{nothing} to do at my house and the fact that there are shooters and criminals in the outside world that is called reality but on the bright side I got memes on my phone soooooo....That's a safe plus ain't  it\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small I don't care what the official starting and stopping points of generations are, as far as I'm concerned, if you're \textbf{old} enough to remember 9/11 and the immediate aftermath (so at least 4 or 5 years \textbf{old}), you're a millennial. If not, you're Gen Z.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small I wish people would stop saying technology is the reason we are depressedâ€¦ because it more like we have access to news and current events. 12yr olds 30-40 years ago would normally be like a 5 or 6 year \textbf{old} today. Kids today know that the world they are going to have to work and raise that families in is a crappy dirty place. So it's not technology that's making us depressed it having access to knowing what we are going to have to live in.Edit: thanks for the likes I am also a gen z\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small iGen sounds like a \textbf{Apple} product...\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Of course,  who else to narrate a story about Gen z  , two \textbf{elderly} people and one millennial.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small this is really dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I don't think GenZ should be 1995-2012. So much has happened, and so much is different in the way kids born at each end of the range grew up. When I was kindergarten \textbf{age}, (2007-2008) it was rare to see things like smartphones everywhere, sure, there was a lot of technology, but it wasn't used to the degree that it is used today. My cousin, however, was born in 2011. She's already using iPads for everything in school. She doesn't know a world where everybody doesn't have the latest iPhone or tablet. There are children in first and second grade that have smartphones. A child born in 1995 has a way different experience growing up than one in 2010 or 2012.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small Everybody in this video keeps saying all this stuff about how my generation is too addicted to phones, but that's not really the case in my experience. We are all able to disconnect from our phones, and even when on our phones we are able to socialize. For example, I was at a gift exchange a few days ago, and \textbf{nobody} was on their phone, except to look something up, to share a video, or to listen to music.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small I was born in 2004 but didnt remember having internet until this year. And i got my first phone on April 3rd 2018. So I was kinda late to the game of the whole internet thing. I used internet at school for educational purposes but \textbf{nothing} else. And I think this video just talked about use and the technology not really our future/fate on society as a whole when we grow up. Im 14 so I still got a few years left and we will see what happens next...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Its a huge shame that we have started to label our generations with letters as if humans are models off a factory chain.Humanity sure has gone \textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small This is so out of touch with reality it's depressing. There is \textbf{nothing} good about this generation, they are horrible. They may have been growing up with the technology but they got no idea how anything works or how it even got to that point.  They are just consumer zombies that are  already responsible for the regression of most mediums/franchises we loved. Of course their parents are to blame too.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small I value equality and change for the better. I have my career figured out for the most part and I'm 17. I work and I'm already starting on my career before college. We are the generation that grew up in a tough world. We know we have to work hard to get where we want to be and that life is very complicated. Generation Z are complainers but we're also do-ers. We fight for what we want. We are the first to endure school shooter lockdowns. We know what's been going on politically, we know our world is dying and by the time our children are grown, they will live in a hotter, much less environmental friendly world than we have. That's why we push for changes because the generations before us screwed us over. We were exposed to a lot at an early \textbf{age} and you can bet that when we become adults, change will happen.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/157 & \cellcolor{green!5}0.637 \\  \hline
  \cellcolor{green!27}\small Damn I hate when they say we don't interact w other ppl our \textbf{age} and that we just sit on our phones because in my experience that's really not it at all people my \textbf{age} are very social and we do interact in real life more than we're on our phones when we're around each other. maybe our parents just see us come home after a long day and forget about everything we do and assume that we're always online because the only time they see us is in our downtime\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/91 & \cellcolor{green!27}2.198 \\  \hline
  \cellcolor{green!5}\small This generation crap is all stupid. Way to \textbf{lump} a bunch of diverse people into a category. Like any generation, there will be stupid ones. There will be smart ones.\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I'm a 11 year \textbf{old} Gen Z (as if 13/12/18), and found out that my classes student-teachers are in the same generation as me.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small adults \textbf{freak} out about phones more than gen z does lol\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small It's kind of hard to know how us gen z's will turn out, since we are only 6-23 years \textbf{old} currently. We haven't really had a chance to do things with our lives yet\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Even though I can classified as gen z cause I'm 17 I think that society is advancing at such a rapid rate that kids even a few years younger than me are completely different. I grew up with a leap \textbf{frog} and still had mostly vhs types I played with LEGOs and outside with my brother's a lot. However, kids that are \textbf{age} 6 now have iPhones iPads and almost never go out side I see a big difference. I think a generation should not be classified by just time but by technical advancement. Their for the faster society advances the smaller generations get.\normalsize   & \cellcolor{green!5}Age, Frog & \cellcolor{green!5}Age - General, Nationality - French & \cellcolor{green!5}2/104 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small You should spend less time attacking Gen Z and more time helping them. You don't help them by talking about all their flaws on YouTube. They need help I need help. My parents never told me how to live without technology. We aren't as experienced as you I'm 15yrs \textbf{old} I know I don't have the knowledge to think for myself so help us be the best we can be.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Im 20 years \textbf{old} and eveyday I feel scary, unhappy and feel like my parents are going to die cause theyre becoming \textbf{old} and I scare that I will die alone with no friends and girldfriend. Its fuckin scary and sick feeling, what should I do please help guys? Would anti depressants help?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}8/53 & \cellcolor{green!5}15.094 \\  \hline
  \cellcolor{green!27}\small John Stern thats the problem I tried once and its one of the reasons why Im in a bad \textbf{mental} health nowadays, tried shrooms exactly one year ago..\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small K but what about \textbf{mental} illness tho haha people post "I want to die" and get 50k reposts. love it.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small real gen z 1996-2003 those are the ones who didnt had phones until 11 year \textbf{old} i remember myself playing football with friends outsideand the only thing i saw few times in pc and youtube was \textbf{crazy} \textbf{frog}and we are the ones  who can remember PC VIRUSES lolIGEN is 2004 to 2012 they had smart phone in thier handsthey will never remember the PS2 sound or PLAYING OUT with friends\normalsize   & \cellcolor{green!27}Crazy, Frog, Old & \cellcolor{green!27}Age - Over 65s, Nationality - French, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/74 & \cellcolor{green!27}4.054 \\  \hline
  \cellcolor{green!5}\small Nah more like 96-02. 2003 kids are hella weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I think generation z is gonna change the world . We act and think diffrently to the other generations . I dont wanna say were most ambitious but i think we use our words and we speak up to things more and we wanna make a difference. Like look at march for our lives and how that changed the thoughts of teens and stuff and how we wanna get involved more . I dont wanna say every single teenager out there is like that because there are still some people out there who need to act there \textbf{age} and stuff but if you ask most of the teens questions about society and politics and stuff they always have a saying to it and i know that for a fact because i am a teenager myself and i know how my \textbf{age} groups act in class and in school and there is messing around and stuff but when someone has something to say about the world we live in we all can agree that things needs to change . We all have eachothers backs nomatter what and even tho we dont act like that by teasing eachother or getting in fights or whatever, i know that we all care for eachother deep down and we wanna make a diffrence together.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/219 & \cellcolor{green!27}0.913 \\  \hline
  \cellcolor{green!5}\small I'm a part of Generation Z (born in 2000) and I think that you should not label a whole generation without even knowing about them. I'm not unempathetic, materialistic or narcissist. I'm completely opposite of that. And I've seen many people of my own generation who are kind and caring.   Well I'm not saying that everyone is kind or caring, but to say that everyone from Generation Z is materialistic, unempathetic or narcissist is wrong. On the contrary, I would say that Generation Z is more diverse and accepting regardless of someone's \textbf{race}, \textbf{gender} or \textbf{sexual} orientation than most of the people from previous generations.  In the end I would like to say that there are good people and bad people in every generation.\normalsize   & \cellcolor{green!5}Gender, Race, Sexual & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}3/124 & \cellcolor{green!5}2.419 \\  \hline
  \cellcolor{green!27}\small I agree born 2000, I grew up with my Wii, N64 and DS. In no way do I even associate with my sister born in 2008 who was basically since the \textbf{age} of 7 has used an iPad since. I can rest assure you my future kids will not be getting iPads or iPhones or personal computers until at least 10 maybe 12. Kids just don't get the roaming around they used too. What also builds on this is the helicopter parents decide to help keep their kids inside with iPads. I mean until I was \textbf{age} 12 I was all over but then I was in a small town and didn't roam much because there wasn't anywhere to go. When I was 17 I roamed in my first city and rode the bus. Oh my, if you could hear my thoughts they were flying as if were crashing a plane. I am certain these kids now growing up with technology and being shielded from the outside world will practically come running back.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/173 & \cellcolor{green!27}1.156 \\  \hline
  \cellcolor{green!5}\small That's why everyone hates millennials. Stop trying to fix everything. You do way more harm than good and you go about it in the worst way possible. You lack the true understanding of human behavior and act as if everything can be changed. You guys fix a problem to create ten more problems and people wish you guys would just go away. Your completely sheltered life made you  \textbf{blind} to the true reality of the world we live in. You are the Jim Jones generation. \textbf{Nothing} more \textbf{nothing} less.\normalsize   & \cellcolor{green!5}Blind, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/89 & \cellcolor{green!5}3.371 \\  \hline
  \cellcolor{green!27}\small Gen Z hates Millennials. You guys are so annoying and whine about everything. You accuse everyone who doesn't agree with you as being \textbf{racist}, \textbf{homophobic}, misogynistic blah blah blah whatever you wanna call it and Gen Z is so over it. ðŸ™„\normalsize   & \cellcolor{green!27}Homophobic, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Bruh, by my \textbf{senior} year of high school I not only expect to have a drivers license, But a private pilot license. Or be training to get it.\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Generation Z is feed up with all the bs politics. We are going to change the world more than you know. So narrow minded to be focusing on issues of \textbf{race} and culture. Our generation sees past that. We see each other as equal, but we also have a strong sense of self worth. Together we are going to push technology and science into realms you can't even imagine. We have grown up with these tools. We are going to create the boom in technology that is going to change the world. Don't plaster your issues onto our generation.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small yo i remember when my mom had to leave the house to get pictures printed from some \textbf{old} timey camera thing for our photo album. actually i dont cuz i was what 2 years \textbf{old}???\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small This video pretty much tells you \textbf{nothing} significant.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Nobody wants to be a millennial so i'm okay with being a gen z.....I don't care if being born in 1997 makes me too \textbf{old} for that\normalsize   & \cellcolor{green!5}Nobody, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small "we don't fear failure" that's 'cause we don't have \textbf{nothing} to lose and we all want to die, lmao.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small What they will have to be careful of is superficiality. Skimming across the surface of an overwhelming amount of frivolous information. Without developing any depth of worthwhile  knowledge. To build wisdom to think,reason and make right judgement on decisions made.The days seem long gone where thick books were \textbf{r\textbf{ed}} and comprehended  as a way of life.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small all these people only think that we are phone obsessed creatures.we also are the ones standing up against mass shootings and \textbf{racism}?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small People born between 1994-2000 are pretty much their own generation... They can understand Gen Y and Z but don't really belong to either. They grew up in the \textbf{weird} \textbf{transition} period where everything was changing.\normalsize   & \cellcolor{green!5}Transition, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small We value equality cuz we all gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small \@Cyberrr so am i, I think some kids our \textbf{age} act more like gen Z than others tho\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Yeah Gen Z 1995-2005 is completely different to 2006-2012. Like I was born in 2000 and my sister 2004 and we both didn't get deep into any technology until at least the \textbf{age} of 12 (by that I mean smart phones and computer usage at its highest since), my sister born in 2008 was using a tablet since she was 7-8, and I mean really using it quite a lot. Totally different sides of the same generation.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small I mean I get that ppl say I'm gen z coz I'm an early 97 kid but I genuinely feel like my sister who was born in late 94 had the exact same upbringing as me so?? Why is she a fully fledged millennial but I'm a gen z? What about working class families who didn't have access to the internet until wayyyy after their middle class peers? Idek I think it's \textbf{weird} to not have a grey area between millennial and gen z because so many of us have a unique experience of going from absolutely no internet access to complete immersion in social media etc... I can't relate to people whose first phone was a smart phone. I can't relate to people who don't know what video tapes are etc... but then I know I can't relate to going my entire adolescence without having made an msn turned Facebook account etc..  idk I feel like with these 2  generations in particular there has to be a grey area between millennial and gen z because literally SO much changed in such a short period of time. My sister can relate more to me than she can her millennial counterparts who are 10 years older than her. Generation barriers are \textbf{weird}.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/211 & \cellcolor{green!5}0.948 \\  \hline
  \cellcolor{green!27}\small im 18 .... gen z is a generation with as much untapped pottential as the american internet itself, destracted by likes and streaks lack of SOCIAL EFFICIENTCY (lots of distractions that confuse developing minds) pigeon holds us. if america stops trying to pigeon hold us in your \textbf{old} systems of education, debt, and workplace norms, we will change the world for u. alot of u grew up in a time where face time, drones, selfdriving eletric cars, and finnacial crises, and iris scaners, facial recognition were things of the future to use everything thats here was always here and depending on the intrest growing up we wer not only allowed to group with the innovation we can grasp it as it happens as ar minds grow physicly and intelectualy dont get  our way teach us how to go above and beyond desision making and autonomy is the most valuble expirence u can give us in many ways we r socialy desperate for achievement (stop manipulating us lmao) the with ppls reach expanding with social media realize that all of america is responsible for being the ideal parent, stepping stones, u give the future its tools not the other way around. if u could only grasp that we can, and most of us have, learned how to get access to know how to do everything we see  online ... u would be buckling up. (what does the future look like to the kids of the future?) Millennials where your first born america gen z is kid no. 2 (as a first born hats off to u guys and thank u to all my big blue blood brothers and sisters[ and all of our freinds, colleages and peers whose we not born here) u guys really paving the way snow plow if u will u guys r our bosses and teachers ... got let your fire go out we know u didnt ask for all the shit u had to pull up\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/330 & \cellcolor{green!27}0.303 \\  \hline
  \cellcolor{green!5}\small Is that person in a woman's sweater, \textbf{r\textbf{ed}} lips, long hair, a trasvesti?\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small On a cultural level, I hope Gen Z continues to revitalise the ideas of free speech and individualism. Economics is another issue and more about adaptation to technological changes. But we need young people to stand up for culturally libertarian values. There are signs that this is the case and reassuring. I was born in 1984, so not sure what that makes me, but sometimes I do feel I have more in \textbf{common} with the younger generation than many of my peers.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small My daughter is going thru the exact thing! All homework is electronic. She has a chrome book at school. It stresses her out. Her younger brother tho still has printed pages but less than she had 3 yrs ago at his \textbf{age}. She just started grade 9. Already between them can you see how fast things are changing. He also is getting a chrome book assigned to him this year. Yey, now I'll have 2 stressed out kids.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small goes to my \textbf{old} elementary schoolI leave Generation Z in your hands children.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small In the uk we are known as generation 'sensible' we have the lowest rate of teen pregnancy ever lowest rates of drugs and \textbf{alcohol} in a ridiculous amount of time .\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small 1. Stop demonizing social media, it's done a lot for people. Saying we all get depressed from it is like judging \textbf{alcohol} by alcoholics.2. Maybe we're fucking anxious because y'all made a huge mess of the world.3. We are still really young, middle school and elementary school kids can't tell you all that's gonna happen within a generation.4. We are exposed to violence all the time because not only is there a lot of it, it's being talked about constantly. We hear about global terrorism and people of our own generation dying because we are abusing what we have.5. We are growing into a world that's already been destroyed for us and we don't know how to fix that!!!! We don't know safety anymore and considering the fact that older generations created what they're complaining about, they won't be much help.Thanks bye\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/147 & \cellcolor{green!27}0.68 \\  \hline
  \cellcolor{green!5}\small Noe Ruiz just because you dealt with it doesn't mean it should exist. I know a lot of kids my \textbf{age} who would stand up for themselves individually if they got into a fight without crying about it online.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small That one guy looks like a \textbf{g\textbf{ay}} Trent Rezner\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small As a 17 yr \textbf{old} I think a lot of this'we aren't fearful ' is bs, I know so many kids who just do things to do things, yes not being fearful but causing so many stupid and unwarranted consequences\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small tbh i wish \textbf{Apple} was never invented, people spend way to much time on there phones. Im 14 btw\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small There are no generations, you can't define an entire \textbf{age} group, everyone is different. Of course smartphone usage has risen a lot for children and young adults, but adults between 30 and 50 have also started using their phones so much more. So let's just stop putting people in generations.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Anxiety and depression, not to mention other \textbf{mental} illnesses (from what I've heard) were not talked about 20 or so years ago. People turned a \textbf{blind} eye and/or looked down upon those with these \textbf{mental} illnesses. It's easier to get help now, so I think this counterbalances the effects of social media. Also I find it's easier to open up your feelings for the first time behind a screen, because you feel you still have a guard up. However it's also easier to bully from behind a screen, so I hope that the next generation will be more able to expose cyberbullies, and more places will have real consequences and ways to prove that you or someone else is being cyberbullied.\normalsize   & \cellcolor{green!27}Blind, Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/121 & \cellcolor{green!27}2.479 \\  \hline
  \cellcolor{green!5}\small I'm always called a millennial and I was born in 99. Everywhere I look, it always says I'm Gen Z, or it says I'm a millennial... So I'm no where? I knew a time without internet. I was around 8 years \textbf{old} when we got our first computer with dial up. Even then I never used the computer. So what am I? Because these people make everything so confusing. I've always classified myself as a millennial..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small As someone born in 2000 im just glad \textbf{old} people are realizing now that im not a millennial\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Wigg ED Because it was during technological advances as technologies are still advancing, if you compare Gen Z to Millennials, they have almost \textbf{nothing} in \textbf{common}, of course they grew up as kids, but it's about significances that makes them grow up to who they are today, I was born in 1999 and a Generation Z.\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Wait, so I am born middle 1994....I dont remember anything at six months \textbf{old}....But I am a millennial?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small According to the chart shown at the beginning of the video, most Millenials should've had children by the \textbf{age} of 15 in order for Generation Z  to have been created around 1995. I think they should've extended the cut off date to 2005.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small I'm millenial, 33. We are depressed because we are bombed by shits from when we are born, they ask to us to be responsable for things did by \textbf{old} generations. Help the rain forest! Do that, do that! Look what are you doing!.. Me? Why no one say wars and shits were made by my parents and grandparents... i don't know \textbf{nothing} about a war,  i didn't \textbf{nothing}. And the same generations asks to us to weak up in the morning at the 6 o clock to make stupid jobs to be slaves of angry elders to be paid less than anyone. Why we are depressed? Because for us the society is not a society, is a trap, a prison, and when you have a phone or internet in your hands, or a videogames, everything look better than that. Can you feel any difference between generation x and z?\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/149 & \cellcolor{green!27}2.013 \\  \hline
  \cellcolor{green!5}\small Why do you need a distraction? Sounds like you're running from our worlds problems, it's literally almost our turn to run this planet. My phone and video games made me super depressed, I had to put it down and face myself and my own issues, gen z lacks the basic concept of loving oneself for who they are because theyre always seeing other peoples life highlights online and think that's all their life is supposed to be, \textbf{nothing} but good times. Pain is essential for growth, if you can't run from it, run to it\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small random person I'm very happy with my life actually. But explain to me why most gen z kids are so depressed in this day and \textbf{age}? Meme culture is used as way to cope with depression, why do kids my \textbf{age} online always talk about dying? There's more to life than your phone, if you want to escape reality for a bit find a hobby or meditate, or maybe even go outside. Just like you said, if it happens that way for you doesn't mean it happens for everyone. You're not everyone, I'm specifically talking about people that lack self love. Change the world don't adjust to it\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/108 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small sunshine bear phones and gaming does not make people depressed but depressed people go to technology or games to get away cause they feel depress so the technology is not making them depressed also on 27 of gen z reported their \textbf{mental} health from good to poor it's not most gen z are depressed it's just Loren then it was for gen y or gen x but it's still not majority\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small why do I feel like I'm watching an \textbf{Apple} ad video? this music LOL. Its like Gen Z is new item. explaining the pros and cons of the Gen Z. Now introducing the Gen Z\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Generation z is \textbf{nothing} special every generation changes the world\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small why do they keep lowering the Gen Z \textbf{age}? first it was 2000, then 1998 and now 1995? Keep that shit at 2000\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small GEN names are the WORSTEvery person is different these gen names just stereo type poeple based on there \textbf{age} :/If a person would tell you they know all the facts about 20 year olds.How do they account for the insanely different upbringings.Most of the data there using to make these predictions are based around the influence of techChange is always bad when your \textbf{old} > Books are bad > TV is bad > PC is bad > Rovots are bad\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small Looking back at my middle school, i'm going into HS this year, not many people put the effort into school or going above and beyond, personally I think the next 4 years will have the most school drop outs, personally I hope to get masters in college in computer science which is why i'm taking advanced math classes in addition to any classes that have to do with tech that aren't about designing, I have an idea of a direction to take and working toward it but most people my \textbf{age} don't even make the effort to TRY to pass their classes\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small You are a commie\normalsize   & \cellcolor{green!5}Commie & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Honestly imo people born around 96 are kinda in this \textbf{weird} in between generation of millennials and gen z's\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I'm pretty sure I'm Gen Z (I'm thirteen) and the \textbf{woman} who was going on about negative effects of social media really annoyed me. The way they keep saying â€˜they prefer, they like to' also annoyed me because you can't group millions together no matter what. And trust me Gen Zers fear failure.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Old people talking about the young without giving them a voice, again. \textbf{Nothing} to see here.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Bryce yeah sure back to when \textbf{black} people were getting lynched and everyone was afraid of nuclear war ðŸ¤£ those were the gOoD oL dAyS\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small I think equality is the best thing we're gonna be known for. I mean accepting equal marriage, \textbf{transgender}, you know all those things happened when I was in my prime so :)\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small 1980s born of the kingdom of the 90s try and make up gen Z because their jealous that gen Y is taking over.  Gen Y brings peace to the earth, none of that shit has happend yet, the gen Y spokesman has yet to appear so you know for a fact gen Y hadn't even begun.  Your all gonna be played for fools for even believing in a Gen Z Gen Z theoretically doesn't even have to exist.  You are all a part of a kingdom that Gen Y encapsulates Generations begin when completely new technology is introduced to planet Internet didn't used to exist and when that was created in earth along with social media videogaming and skateboarding Gen Y were the generation that sprang up from that technology.  The whole world is that and \textbf{nothing} new owns the culture and Gen Y pioneered all of that new technology and became the masters of that and this world.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/159 & \cellcolor{green!5}0.629 \\  \hline
  \cellcolor{green!27}\small WHO FUCKING CARES? All these labels just divide us up and it's so stupid. These generation labels mean \textbf{nothing}. I have friends of all ages. You guys are doing a huge disservice to the world if you continue to divide people up with meaningless labels.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small This whole "iGen" thing really gets under my skin. First of all, I was born in 2001 and find that I have \textbf{nothing} in \textbf{common} in my childhood with those born anywhere near 2012, because I was already in middle school. Also, continuing to say that social media and phones wreck our generation is so confusing, because "Gen Z-ers" did not invent all of these things. We were raised with millennials and Gen X giving us technology and social media. If people over the \textbf{age} of 40 want to continue to say we are "ruined", they should consider WHO RUINED US IN THE FIRST PLACE. Children don't have access to advanced technology without being enabled by their parental figures. Every generation is a product by those that came before them. We are raised in a world that has been changed by people who lived prior. It's not like our generation is obsessed with technology because we wanted to be. Parents now give their kids iPads so they don't have to worry about them, as opposed to giving them creative outlets or encouraging them to advance their talents or finding new passions or simply playing outside! I myself was not raised like that - I played outside every single day and didn't have a phone until I started high school. We were not born with smart phones in our hands, we were enabled and encouraged the have the newest technology.\normalsize   & \cellcolor{green!5}Age, Common, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters, Social Class - Working class & \cellcolor{green!5}3/239 & \cellcolor{green!5}1.255 \\  \hline
  \cellcolor{green!27}\small Same. I was born in 2000 and a lot of my friends are my \textbf{age} (and maybe a year younger) and older (by up to 7 years). I find that I relate better to someone in his early 20s than someone in his mid teens. I find it hard to relate to even my younger brother who was born in 2003. That's why even though I'm kind of in the gray area between millennials and Gen z, I identify slightly more as a millennial. Also, I didn't get a phone until I was 16, and I remember my parents using fax machines for their immigration documents. I also remember things like  big bulky white computers, DVD's, VCRs, cassette tapes, and, most importantly, VHS\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small Same here. I was born in 2000 and I used to play outside as a kid. I got my first phone at the \textbf{age} of 17. I use my phone to find some information regarding my interest, hobbies or homework. I only watch You Tube and I use What's App only when I have to ask or tell something necessary. I don't play video games or use social media. I just listen to music from my phone while resting or doing some work.    So it depends on the individual and not the technology. Technology is a blessing if we use it correctly. Today's generation is more diverse, open and accepting, thanks to the internet and technology. We should also not forget that because of the internet we are aware of the things happening around the world.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/136 & \cellcolor{green!5}0.735 \\  \hline
  \cellcolor{green!27}\small The kids born in 2010+ started on technology when they were young, like I see 2 year olds with big ass tablets or Nintendo switches. While me born in 2002 my mom made me do work books, read a book, watch that \textbf{old} ass TV (non flat screen cause they didn't exist yet) or play on those \textbf{old} computers\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small yea. i played outside everyday and ate stuff that was probably poisoned, we didn't tell anyone, so \textbf{nobody} cared. i'm so glad i wasn't growing up with helicopter parents. me and my friends parents let us do whatever. but i see these little kids with phones and i only got a phone simply to communicate with a single parent who couldn't always be there\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Deirdre N  I was born in 2000 and definitely feel I have more in \textbf{common} with the late 90's kids.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small This is less about technology than it is about economics and social laws. Mellenials all were born and mostly raised in a time of plenty early and so feel entitled and also later in life or upon adulthood a time of economic hardship that was heavily blamed on corruption or the capitalist system failing and so either don't trust the current economic system or the politicians and so believe the mostly progressive media that was required to cite sources when they were younger and so along with their \textbf{common} economic beliefs, they believe that social liberty is gone/eroded by older generations moving far too traditional that they believe restrict them -- often missing that currently politics have undergone a massive propaganda campaign for years and starting with mellenials is the first generation of people that mostly believe that part of each parties intent or principles aren't what they actually are, while baby boomers just have the highest amount of these people in a generation before, they confuse the two current parties when put into policy what the outcomes would be and sometimes even their principles, which is:The propaganda has tricked those into thinking only the government can provide services to all people and convinces people they lack rights. And with heavy economic regulation far beyond increasing competition, they stamp out the ability of most average people of having the ability to work on their own and then lower their wages while working for a company by increasing the labor force with third world immigrants that don't benefit americans currently. Creating a situation where even more americans become dependent on them. This is the short version,\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/276 & \cellcolor{green!5}0.362 \\  \hline
  \cellcolor{green!27}\small Kyra Kronberg you do know their is no exact cutoff. You are a millennial roughly around the early 80s -2000. The ones who coined millennials and others put it about 2000. If I had to choose everybody born in the 90s are millennials. Truthfully looking pass it \textbf{nobody} are these garbage lables. These fake bubbles people made up .\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small I agree. I got into technology when I got into 6th grade. I see now kids over 2 years \textbf{old} with technology (phones,tablets,etc)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small While I was born in a later year than most of y'all which was 2006 I didn't grow up with technology really.  My mom made me go outside to play, read, just do anything but technology.  I would say the cutoff for gen z would need to be 1998-2007.  2008 and up has been too involved in the online world since such a young \textbf{age} and do not have a major part in our generation\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Exactly! I'm not saying that I hate tech or social media, but the whole reason we had iPhones at \textbf{age} 5 is because our parents just didn't want to deal with us.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I'm currently 11 years \textbf{old} yet I still remember VHS and DVDS and I do have a phone when I was ten since I walk home and to school and my parents would rather I keep in touch. Yet I'd rather talk to an adult or 20 year \textbf{old} then anybody my \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/53 & \cellcolor{green!27}5.66 \\  \hline
  \cellcolor{green!5}\small For SOME people, social media is linked with \textbf{mental} illness, but I hate that people link the growing rate of anxiety and depression with solely just technology. I believe that a big reason there is much more anxiety and depression within the younger generations is because of how the education system is changing. College used to be a place you could go to FURTHER your education if you wanted to better yourself and to get a better job. Now, college has basically become a necessity: if you don't want to work at fast food forever and live in a shitty apartment and live in poverty, you HAVE to go to college. It's so much harder nowadays to find a steady job without a college education. Plus, on top of that, college puts people into a lot of debt, because it's becoming more expensive and they can't afford it, but they NEED it. I feel like because of this, the schooling systems as a whole have really amped things up, specifically high school, and that's why we are seeing a lot more teenagers who struggle with anxiety and depression: not because they're lazy conceited idiots who are on their phone all the time, but because, I don't know, maybe pressures are growing and growing. I hate when older generations just blame everything on younger generations, instead of looking at how they've changed the culture themselves. EVERY generation has changed things, for better AND for worse.Thanks for coming to my ted talk lol\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/252 & \cellcolor{green!5}0.397 \\  \hline
  \cellcolor{green!27}\small to me, the strange part is how people presume that they can tell an entire generation what they're all about, even tho the oldest are only twenty-three and the youngest are six.   it's a little soon to put Zers into a box.also strange:  why 1995 and 2012?    who gets to determine that boundary and why?the stereotyping of a generation comes more from defining events experienced during their formative years:  great depression in 1930s,  ww2 in 1940s, korean war, large scale prosperity and economic growth, vietnam, energy shortages, mariel boatlift, iraq vs kuwait, arrival of dial up internet + brick phones, later arrival of broadband + social media + smart devices, 9/11, 2008 crash, michelle obama school lunches, and so on.  in the context of being in middle school during 2008 crash: a kid then would remember how their' parents were suddenly out of work or losing their homes.  even if they were a "rich kid", they saw it happen to others.   seeing entire neighborhoods of houses under construction become a no mans land after being suddenly abandoned.  coming home famished after school cos the obama lunches were both tiny and disgusting.shit like that during the formative years is, well, formative.  particularly when it's nationwide or worldwide.  it's entirely too soon to "define generation Z", yet those middle schoolers  i mention?  as adults in 2038, they'll base their actions/decisions on finances/work/voting/schooling/house/their own children partly on that 08 crash + obama lunches.  and someone of the same \textbf{age}, who is an otherwise complete stranger from across the country, will nod in agreement.that nationally formative commonality relating to specific years is how generations get their specific traits that we observe as 'stereotyping'.remember: stereotypes would not come about if they were not at least partly true\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/297 & \cellcolor{green!27}0.337 \\  \hline
  \cellcolor{green!5}\small Almost same situation. I was born in 2000. I first learned about the internet when I was 8. Even then, I only used it like once or twice in a month. I began to use internet little more at the \textbf{age} of 14. I got my first phone at the \textbf{age} of 17 (yes, i.e. in 2017).\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small I feel like saying 1995-2005 for gen z is super \textbf{weird}? Like culture has changed so dramatically and so often during those years I kinda feel like there needs to be fragmented, smaller generations in that decade. The culture between someone born in 95 and 05 is so drastic. I'm 19 and my niece is 10 and we literally have \textbf{nothing} in \textbf{common} and I've caught myself saying 'when I was your age' a few times lol\normalsize   & \cellcolor{green!27}Common, Nothing, Weird & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}3/77 & \cellcolor{green!27}3.896 \\  \hline
  \cellcolor{green!5}\small David Chan I think 97 and 98 should be there own cus it's \textbf{weird} I don't relate to mellinials yet still I don't feel like Igen too I don't remember anything from the 90s but growing up we weren't always on our phones...shit \textbf{weird} I'm 97\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small That's a fair point that I think is often mistaken. I don't think the name of our generation should change cuz that's just \textbf{dumb} but yes, the idea that we are totally technology dependent should be tossed out because it's true we've never lived a life without it but at the same time, growing up in the early 2000s or into 2010, most of us have very VERY few interactions with it because it was new, amateur and not available to us. Technology has always been there in our lifetime, we just didn't always have the opportunity to use it.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small I think Gen Z will be the generation  that legalizes \textbf{g\textbf{ay}} marriage in general and reduce strict travel laws around the world. These kids are more open minded and less \textbf{racist} than the older generation like us as they did not live during the \textbf{age} when globalization was only starting.\normalsize   & \cellcolor{green!5}Age, Gay, Racist & \cellcolor{green!5}Age - General, Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}4/50 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Baby boomers thought the great generation was \textbf{old} and outdated, Generation X thought baby boomers were \textbf{old} and uncool, Millenials think Generation X is \textbf{old} school and outdated and now Gen Z will make fun of everyone! LMAO\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/38 & \cellcolor{green!27}7.895 \\  \hline
  \cellcolor{green!5}\small Smartphones is for \textbf{old} people. I don't understand why people think that is so innovative. AR\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Don't like that they \textbf{lump} people born 2000 and after with the ones born 1995 and after there's a difference in how we grew up when it comes to electronics they weren't as updated so at least for me I didn't care as much\normalsize   & \cellcolor{green!27}Lump & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small They will make it one \textbf{dumb} ass wold\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small not this video specifically but im tired of hearing about everyone talking about how awful this generation is or how its going to save the world... in reality like every generation before us we are just going to try and live our lives with the cards we've been dealt ... we might have been given different cards than past generations but in my own personal opinion I wish the media would just leave us alone .. and while some generational stereotypes may fit me, many aren't the kind of person I am at all but the thousands of videos about my generations make older people think a certain way about me that isn't always true.. every person regardless of generation is raised differently and exposed to the greater culture in various amounts. the internet  in my limited experience on earth seems to make it easy for stereotypes to spread since its easier for opinions to spread... not facts.. opinions... and all these videos about peoples opinions passing as news is driving me \textbf{crazy}... if it were possible to live without the internet I would but today's society has integrated it so tightly into the daily fabric of our lives  - and I know this video had statistics and various things that are more factual, sadly in today's world even facts can't always be trusted, and when I say today's world I mean a world made up of all generations and ages - people from all ages benefiting and negatively affected our world... so in closing please stop trying to fit everyone into nicely sorted boxes, I'm growing tired of all these convenient descriptivetitles \& categories\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/275 & \cellcolor{green!27}0.364 \\  \hline
  \cellcolor{green!5}\small massive perversions and manufactured rape statistics alliances between the DOJ and state and local police forces...are forcing guys to go \textbf{g\textbf{ay}}, or go MGTOW..just to not be harassed by the legal system!!\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Same here. We're in the same situation as 1964-1967 born's (\textbf{transition} from Boomer to X) or 1979-1982 born's (\textbf{transition} from X to Y/millennials). We are in that \textbf{transition} from Y/millennials to Z. We're on the cusp or like hybrids. People don't understand that we're not part of either generation. We don't relate completely to millennials but we don't relate completely to Gen Z either. I would say that our childhoods felt more millennial like but since our teen years up to college when social media came up the culture has felt more Z like. My opinion though. A 1996 born with older cousins or older siblings might feel like they relate more to millennials, but a 1996 born with younger cousins or young siblings might feel like they relate more to Z. It varies from person to person.\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}3/138 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Yea with this social media crap our world is doomed, it's like living in that \textbf{old} Jim Carey film 'The Truman Show' everyday damn day, real fabricated, \textbf{nothing} feels authentic anymore ..and I'm at 1991 baby btw\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Even though smart phones are easily accessible it is up to the parents to take baby steps with their kids. There's 7 yr olds running around with iPhones. They need to start with a \textbf{dumb} phone just like older generations did just to ease the exposure that they have to the internet.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small I think this is a little biased because I've been reading a lot of articles and studies showing Generation Z being pretty right wing and I'm not talking about the same right wing that we see in American politics like the \textbf{cuckservative} but I'm talking about their little bit more third position and nationalistic. This documentary is showing Generation Z more globalist and part of the global Community which to some degree and aspect that might be true but in other aspects that's less true especially in Europe with the \textbf{migrant} crisis.\normalsize   & \cellcolor{green!5}Cuckservative, Migrant & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - General & \cellcolor{green!5}2/92 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small I was born in 96 am I an \textbf{old} gen z or a young millennial??\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Is this just me or does anyone else hate when this happens, when an \textbf{old} person says you millennial to the students in a class, and  youre over here thinking, i am not a millennial, were gen z!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Omgggg more \textbf{old} people hating on the internet\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I swear the numbers always change. I was born in '96 and I've seen multiple sites telling me that Millenials were born from '86 to '96 and then I've had multiple sites telling me that Generation Z is from '95 to 2012. So which is it!? Am I Gen Z or am I a millennial?I'm Twenty Two and unlike most my own \textbf{age} range, I don't have a Driver's License, I'm never drank coffee before and I've never tasted \textbf{alcohol}.\normalsize   & \cellcolor{green!5}Age, alcohol & \cellcolor{green!5}Age - General, Behavioural Addiction - Alcohol & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small If you actually fucking knew anything 1. The media made it look like there were hundreds of thousands of kids doing it (which there weren't) 2. The same \textbf{age} group of kids made a walkout in support of the 2A and Police 3. those kids that actually did do it were either forced or doing iy yo miss 20 mins of class.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Someone's been watching too much rick and morty... kid you know \textbf{nothing} yet\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I honestly thought like gen x owned slaves. Like how \textbf{old} are you?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Ha ! another generation of weakness, generation of people who cannot live without technology, \textbf{nothing} is special about them. Absolutely \textbf{nothing} and they think they are special, and there lies the problem .\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small wtf is this \textbf{g\textbf{ay}} shit look at them\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Overall they have never known a life outside of the internet and wireless internet and IPhones became the norm when the oldest ones were in elementary school. At 18 years of \textbf{age}, boys obsessions are with minecraft, beyblades, and drawing anime pictures. Partying, drinking \textbf{alcohol}, and having \textbf{sex} don't even cross their minds. Anything dirty offends them. If you say anything that offends them, that can be used against you and you could lose your job. Snapchat, Youtube,  and Instagram are their interests on the phone. Facebook is for \textbf{old} people, that is, those over 21.\normalsize   & \cellcolor{green!5}Age, Old, Sex, alcohol & \cellcolor{green!5}Age - General, Age - Over 65s, Behavioural Addiction - Alcohol, Gender - General & \cellcolor{green!5}4/96 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small 'How Gen Z will change the world'..... brings \textbf{old} people talking about social media and depression.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I think all the gen Z'ers who say they are fed up with PC culture (see comments) view Millennials as what I would call "Neo-Victorians" for lack of a better term. Ever uptight adults who \textbf{freak} out over what can seem like petty things. Different morals stemming from a different worldview than the Victorians, perhaps, but enforced just as sternly in an authoritarian manner. Kids love to rebel against adults like that, so it's not surprising if they're rejecting them in a way (mostly by poking fun at them), though thankfully they seem to still be embracing the good things our society has made progress in like tolerance and equality, just with a more positive, hopeful, grounded outlook."Table legs are offensive and must be covered up""Milk is \textbf{racist}"Yeah, objects are not the same as the things they remind you of. We have the actual, more serious things to worry about here, and that seems like a petty distraction from them.\normalsize   & \cellcolor{green!5}Freak, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/163 & \cellcolor{green!5}1.227 \\  \hline
  \cellcolor{green!27}\small chris c What's a \textbf{snowflake}, we don't say that in Ireland\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I am a millennial (1985). Grew up on bmx, music, nature, adventure. Leaving school during 9/11 disaster, followed closely by recession/housing market crash.The generations above myself never gave ANY chances to the creative millennials when seeking work/careers. I fought hard but lost, I was a pioneer trying to incorporate the use of Xanaga \& MySpace to reach a good audience by free advertising and creative speech. ...Not a single generation above me realised the awesome use of these platforms before the word Facebook had even been mentioned. I could talk for weeks but I'll leave you with this; I am 32 now and still have the creative open mind I grew up with, so any gen z'ers out there thinking \textbf{nobody} is listening to your dreams, if our paths ever cross then you can guarantee I'll see that potential in you. Unfortunately there are not a large amount of â€˜me' out there.âœŒðŸ¼\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/154 & \cellcolor{green!5}0.649 \\  \hline
  \cellcolor{green!27}\small Nobody uses hashtags, tf??\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small The purpose of the generational system is to identify major shifts in consumer and worker behavior. You'll find that people born in '95 have more in \textbf{common} with people born in 2005 than those born in 1980.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small You don't understand generations. They aren't saying that 23 year olds are the same as 6 year olds but there are similarities. Of course there are differences. I was born in 2002 and I think my childhood was different to someone born in 2008 but we can't split generations up into tiny groups of years. The general similarity is that you all had access to the internet from a young \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small \@JC 11 Lol Gtfoh I was born in 1996, and the people born around the same time have more in \textbf{common} with 80s people than ones born in 05. If you were born in 95', that would mean you were 10 by 2005 - cellphones weren't even close to being a thing yet (2011). And our style of dressing growing up were practically the same as people born in 89', baggy clothes and spikey hair. And the internet still wasn't fully A Thing yet in 2005, unless you were a rich kid. Also we still used CDs.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small \@B P Lol I'm 22 (born in 96'), people around my \textbf{age} group have WAY MORE in \textbf{common} with people born in 1988. We grew up with the same style of clothes, listened to the same eras of music, played almost the same game consoles (Dreamcast, Gamecube, PS1, Super Nintendo, and even Arcade games like Street fighter/Mortal Kombat), we regularly watched the same movies - and the same way (no Netflix), we remember when the Twin Towers fell, and the Internet wasn't as \textbf{common} and advanced as you think it was. We were from the \textbf{Transition} period (94-98).\normalsize   & \cellcolor{green!27}Age, Common, Transition & \cellcolor{green!27}Age - General, Sexual Identity - Transexuality, Social Class - Working class & \cellcolor{green!27}4/98 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small \@Jay Luis For a start we didn't have Netflix growing up either lol that's a really new thing. We also didn't have internet as it is today. What people don't understand is that you can't just draw lines between generations because every birth year will have slightly different experiences. You were born in 96 meaning most of your childhood and adolescence was in the 00s whereas I was born in 2002 meaning my early childhood was in the 00s. Therefore we will have similar experiences during that time period, not the same because we were different ages. It's important to clarify that I didn't have a smartphone growing up, we had internet but I hardly used it. Many people think our \textbf{age} group grew up with smartphones but that is not the case. Anyway, my point is that there will be differences between each \textbf{age} group but I have more in \textbf{common} with your childhood than other childhoods, they aren't the same but they aren't that different.\normalsize   & \cellcolor{green!5}Age, Common & \cellcolor{green!5}Age - General, Social Class - Working class & \cellcolor{green!5}3/167 & \cellcolor{green!5}1.796 \\  \hline
  \cellcolor{green!27}\small \@JC 11 depends on the situation.  Of course we use the same social media, like similar memes, etc...but no way can a 13 year \textbf{old} and a 23 year \textbf{old} have anything in \textbf{common} other than that. Sometimes i feel i am not an adult until i speak to actual kids. Then im like "yeah definitely older than them! Definitely not as young and lacking adult responsibilities...." ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/68 & \cellcolor{green!27}4.412 \\  \hline
  \cellcolor{green!5}\small I love how you got \textbf{old} people telling us what our generation is and what defines us...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small You can learn about people through their behavior and mindsets and apparently these cats do that for a living so it's \textbf{nothing} new. Might be new to you? Ever heard of psychology or is that something unknown for you Rugrats?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small I HATE THAT \textbf{OLD} PEOPLE THINK they can do that! Why assume you can do that? The \textbf{old} are not the new!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I was born in 1997 and I knew a time without internet. Only at about 8-9 years \textbf{old} did I start using the internet. Am I the only one?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I'm a baby boomer 65 years \textbf{old} an I'm glad we have millennials an gen z or whatever because I need them to show me how to deal with all this technology . Computers an the like.where not part of my generation. Lol!!!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small I would like to start a course for the \textbf{elderly} to teach them a crash course in computers, but I don't know if anyone would be interested. I'm no teacher, I'm just a IT-student.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Hey, John! You piqued my attention. I'm 5 years younger than you. I learned computing on a mainframe. I wanted a Mac. As an art student as well as a chemistry student, I really wanted to make computer graphics. Using the mainframe, my \textbf{senior} computing project was a graphics program to plot a titration  (acid/base) curve. I always hated drawing graphs that would go straight off the end of the page! The the internet and the world wide web came about when I was in grad school. Very helpful stuff! Anyway, I'm savvy because I fooled around with all this stuff back then and I never stopped playing with my toys. Devices, sure I can do that. But the culture surrounding the gens and their toys is something else again. That's what I need to learn from them and I am starting to pay more attention. Now as far as dealing with devices, how do people walk and text? That is a skill developing now for the future!\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/168 & \cellcolor{green!5}0.595 \\  \hline
  \cellcolor{green!27}\small The best way to learn about technology is to teach it yourself. There is no magic switch and then you understand everything. It's all trial and error. If you have a problem, any problem with your technology just look it up. If you don't know how to look things up, i don't know how you got here. Anyways I belong to generation Z and this was really made clear by my 63 year \textbf{old} teacher who is really good with tech. She said she just had to learn it by her self like this whole generation does. There are tons of tutorials to literally do anything you can think of. Hope this helps.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/113 & \cellcolor{green!27}0.885 \\  \hline
  \cellcolor{green!5}\small Eiji Fujimura that's good  to hear.yea I gusse \textbf{nothing} is written in stone.but simple advice is always the best thanks\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Paintball enthusiast really, I see you guys as the most accepting and carefree generation, I think our generation, gen z is going to be a failure, sure we're probably going to invent amazing things, but most of us have \textbf{mental} health problems.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Both my parents are Baby Boomers and they are very tech savvy. Stop using your \textbf{age} as an excuse. Time to tech up!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I think you are lucky to be of the generation of no technology. \textbf{Nobody} communicates in person anymore.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Real Hip-Hop Head - Rhyme Asylum The generations before the baby boomers were the same generations who were fine or even promoting \textbf{racism} and they were also the same generation that were probably doing other by today's standards barbaric shit. Every generation can be seen in a bad light.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Props to you! A fair bunch of baby boomers tend to look down on the younger generations. It's refreshing to see someone who can appreciate other people regardless of \textbf{age} ðŸ˜Š\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Puro Durango emojis are gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Ketsugi you deadass have a anime for your profile but I I'm the \textbf{g\textbf{ay}} one ðŸ˜‘\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Sorry our generations left you a mess to clean up...but remember how resilient you are and you're not given some of the most advanced tools in the world to bring people together. You teenagers got 1million teens worldwide to stand up for something you believed in for the March for our lives. Consider a MARCH FOR HUMANITY, on 7/7/2019. Need us to stop driving, polluting the planet, actually DO something about GLOBAL WARMING because it's your future children's homes that will be eliminated. Imagine a world with brown water, \textbf{black} mountains, gray sky's everyday. You've seen the international news, you're not forced to see only CNN like we did. Do your research and make a STAND for your children and your FUTURE! ðŸ‘ðŸ•ºðŸ»âœï¸\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/123 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}\small Gen Z is said to be the most conservative generation ever since the early 1900s. And I must say, I 100 agree with that statement. There is so many right wing people who are my \textbf{age} (early teens) even though I live in Ireland. Even though the current society in Ireland is quite liberal, it won't last. I'm actually glad about this. Also, I disagree with the multiculturalism. I only know 2 Protestants and 1 \textbf{black} person. All are white, catholic and straight\normalsize   & \cellcolor{green!27}Age, Black & \cellcolor{green!27}Age - General, Ethnicity - Black & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small Gen z goes up to \textbf{age} 24 lolz\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@The PO From Hell No... gen z starts in 1995 to 1996, and doesn't end until the late 2000s. The oldest a gen z is right now is 23 to 24 years \textbf{old}. - Coming from an 18 year \textbf{old} gen z (I was born in 2000, I'm roughly in the middle of the gen z years)\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small Oh wait that's actually \textbf{weird} to think about\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small If you were all about technology than you were truly not living your life. I was born in 1983 never in the house is a kid ever my parents never worried about me always they said you have to be home before it's dark. Play video games hang out with friends actually did things if you are constantly on your phone and online all the time you were truly missing out on life because there's more to life then technology and being online. I would really hate to see what would happen if the Internet was to die, kids today would not know what to do they really would and I would like to see what would happen if the Internet was literally cut off to the public sector for one month just to see how people would react young and old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/142 & \cellcolor{green!27}0.704 \\  \hline
  \cellcolor{green!5}\small Cryptic Wintermoon those memes died a long time ago \textbf{old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small lol that one \textbf{chick} was holding that thigh a little too kindly :D\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I didn't hate this video, but they framed a lot of things as if Gen Z was doing it by choice, instead of by necessity.This video acts like work-life blend is by choice, and not forced upon us by gig economies that necessitate it for many.  (Raise your hand if you'd rather not have a job with full benefits and a livable salary that's 9-5, and instead work two part-time jobs and drive for Uber, without benefits, job security, or a predictable schedule that you can fit hobbies and friends into?  Anyone?  No?)I also disagree with the "developmental trajectory" being slowed down for recent generations.  We're not hitting the traditional milestones at the same pace of previous generations, but that doesn't mean we're more immature or inexperienced as a whole.  I actually think that kids today are exposed to important and mature issues earlier than in the past.  Younger generations are just prioritizing those traditional milestones at different times, due to preference or necessity.  High schoolers not having part-time jobs probably has less to do with immaturity and more to do with the \textbf{crazy} high demands of college admissions.  If you're doing 3 AP classes and 4 extra-curriculars, where would you even find time for a job?\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/209 & \cellcolor{green!5}0.478 \\  \hline
  \cellcolor{green!27}\small \@Boi singhn how \textbf{old} are you?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Connor yeah i graduate in 2024 and honestly it's very \textbf{crazy} to think that\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Hol M people shot up schools before us too. It's sadly just more \textbf{common} and talked about now.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I think the definition of Gen Z rather different amongst countries, I was born right at the start of the year according to this video (which means I am technically a Gen Z) and from a different country but didn't reallyown a phone till I was 13 and even then for a few years, it wasn't really a huge part of our lives. I remember hanging out with friends at dinners, playing soccer sports in the early am, visiting families open house, working in warehouses etc. pretty vividly until the last few years of HS and then college. The U.S is pretty digitally driven amongst the youngsters and its pretty unhealthy at the way they consume it. Unnecessary conflicts arise through social media and then brought into real life. Talking about interconnection, yeah, teenagers are pretty connected in the realm of the internet but in real life, definitely not. A lot of teens 'fight/argue' online but in real life do \textbf{nothing} and want pretty much everything. Yes, with the recent news and everything, teens are definitely doing something, but those only represent the small percentages in the news and not the other large percentage of teens existing in the country. But then who knows, I may be wrong.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/208 & \cellcolor{green!5}0.481 \\  \hline
  \cellcolor{green!27}\small \@Shadow Ranger "I think you should apologize for polluting our gene pool with immigrants."We shouldn't have to apologizing for not being \textbf{racist} white supremacists like you older generations are, this is a good thing. The \textbf{racism} was never good to begin with.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small \@ZGaming I'm fucking 16 years \textbf{old}. Yes, I am a white sup*REEEEEEE*macist aren't I\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Í” So the ice \textbf{age} it got supwr cold let a lot of ice be around then it heated up melted and then later formed some more its a over all cycle of melting and freezing. Also did you ever read the bible we are given free will if we do or do not want to follow God but now you follow false prophets making your life very sad this is how the world is becoming the generation of depression. No one believes making people have problems.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small \@Markicore after 1000s of years. Jesus, how \textbf{dumb} are you. Saturated hydrocarbons don't break down in a healthy amount of time.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Ethan Dude are you being serious? you sound like you are but i sincerely hope you're not. because global warming is real whether you like it or not. and tearing down other religions is, well, a dick move to say the least. also you said absolutely \textbf{nothing} that convinced me that global warming isn't real. if you have any actual evidence please share with the class.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small The oldest generation z member is like 24 years \textbf{old} so they took the younger millienials out od mg generation thank God and gave them their own generation so they can ruin it\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@beginger xx And as a Gen Z, I'm disappointed that many of us are siding with right extremism in response to left extremism. I'm seeing a lot of people my \textbf{age} (20) and younger blindly follow the alt-right antics which is counter productive to any bit of progress we've made.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small You've also imported millions of third world migrants with insane medieval religious ideologies and criminal/terrorist intentions because you wanted cheap labor instead of giving us well-paid jobs. Are you going to apologise for that, or are you going to call me a \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small I feel like the thought that GenZ is the most conservative since ww2 is bullshit, especially when it comes to \textbf{race}. To say that "O they're just angry white kids on the internet who can hide behind a screen is stupid. GenZ kids, such as myself (19 now) grew up in diverse groups. For the most of us, our immediate friend group (being where we see on the daily) consist of many ethnicities and sexes/sexualities. The only difference is that we're not \textbf{dumb} enough to believe all the \textbf{race} bait bullshit shoved down our throats on a daily basis by millennials. Like no Karren, the statistical fact that a certain \textbf{ethnic} group commits more crimes is not \textbf{racist} and no Karren, just because I pointed that out doesn't make me think that all those people will commit such crimes\normalsize   & \cellcolor{green!27}Dumb, Ethnic, Race, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/139 & \cellcolor{green!27}3.597 \\  \hline
  \cellcolor{green!5}\small fake and gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small Born in 95 and cringing at this vid. Hate being compared to the kids today considering I know MY childhood was spent at least 90 outdoors camping, catching bugs and animals (i liked catching things as a kid), playing games like tag, â€˜kick the can', manhunt with my brother and neighbors, going on 'adventures', etc, all without even owning a cellphone. Sure we had the tv and \textbf{old} computer that we could occasionally use (after asking permission) for maybe an hr if we did our chores or homework, but you bet your ass if it was a nice day we'd get kicked off the tv or internet to go play outside. Or maybe someone would need to make a phone call and that awful dial-up would kick you off anyway. Not going to deny i'm gen z if that's a fact, but I still don't like being lumped in with the kids born in the 2010s or late 2000s who were literally born into technology, while in 95 the internet was still just getting its footing.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/176 & \cellcolor{green!27}0.568 \\  \hline
  \cellcolor{green!5}\small Generation \textbf{Snowflake}?The Earth is doomed so Mars is an objective\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Ha ha, hold my beer.still awake at 3amwait l, just realised im not \textbf{old} enough for beer...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small It's refreshing to see such insight in someone from my own generation younger than myself. (2001). As a whole our generation is actually more liberal than millennial's but is less inclined to support social justice. You see when you look at the hard facts on paper women have the same rights and privileges as men do and minorities have the same rights as white people do in the developed world (United States, Great Britain, France, Japan, South Korea, etc.). The differences we see between men and women in the roles they play are partly genetic and partly learned and while to some people that may be looked down upon or outright denied I believe in many ways femininity is a good thing. In the case of minorities the differences we see in their behavior are almost exclusively caused by their cultural background. In some cases the tolerance and multiculturalism supported by the developed world has resulted in conflict as the customs and beliefs of one culture are not compatible with the culture that accepts them. Rather than focusing on multiculturalism I believe we should follow the analogy of a melting pot as the United States is often referred to. Rather than dividing people into separate groups the cultures of the people that live there whether born there or having immigrated there should slowly coalesce peacefully combining elements of many cultures with people trying new things while not forgetting \textbf{old} traditions. The true strongest divider in the world is wealth though and the amount of money you possess or your family possesses can determine a lot more. I would like to go on but I need some sleep. It would be interesting to see what your opinions are.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/287 & \cellcolor{green!5}0.348 \\  \hline
  \cellcolor{green!27}\small My generation and the following generations are \textbf{nothing} but entitled morons who are ruining the world.  There is a fight coming, and maybe a second civil war.  But I'll tell you this much, if it comes to that, they won't be winning.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small A \textbf{g\textbf{ay}} drink\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small Generation made by Apple\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small A lot of people make a distinction between iGen and GenZ. With GenZ encompassing both, but iGen not remembering (or having) a time without Touchscreens and iPhones. I think there is clearly a separation between those groups, and not just \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Honestly, I know the lines are blurred, but kids born in 2000 kinda skirt the line. I have a lot in \textbf{common} with Millennials, and we did get told we could be whatever we wanted. We did know life before the smart phones, we remember flip phones and talking on a landline with the chord, meanwhile my little sister (born in 2009) has always known tablets and ipads and has always had access to that kind of technology. So, I'm not really sure where 00 kids would land, but I definitely don't think we all fit into the Gen Z mould, and I've definitely noticed I fit in a lot better with older people than younger (people born 2002 and up), especially when it comes to stuff like social media, politics, etc\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small Same. I was born in 2000 and a lot of my friends are my \textbf{age} (and maybe a year younger) and older (by up to 7 years). I find that I relate better to someone in his early 20s than someone in his mid teens. I find it hard to relate to even my younger brother who was born in 2003. That's why even though I'm kind of in the gray area between millennials and Gen z, I identify slightly more as a millennial.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small There is \textbf{nothing} new under the sun, let's get real, we are all one generation, the human generation\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Me, a 16 year \textbf{old} on his phone watching a video about my generation always being on the phone\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Capricorn Of January 4th Bakugou vs Deku congrats on being a kid, Idgaf if I hurt your feelings. It's not your fault but your generations and the generations that surround it have been ruining our world for years now. Unfortunately the generations effect each other. You kids rely to much on technology and your minds takes in to much information. And you soon come to realize \textbf{nothing} can be done to fix it.and you are but a mear Speke in this world. We are all mindless zombies blinded by money and material possessions.My belief is that if we take down governments and rid ourselves of a ridiculous currency system and rely on small communities to lead themselves with a trade based currency. We need to go back to living like natural humans. Hunting and tracking our food, instead of having to work a job to earn a price of paper that allows you to buy things that would normally come from the earth naturally. But all our natural resources have companies that control and run them now, and they make a killing off of selling what would normally be free. I want Gen Z to realize this and to fix it in the future. Or we will go down a long dark path of relying on the government and big business to keep us alive.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/226 & \cellcolor{green!27}0.442 \\  \hline
  \cellcolor{green!5}\small Money, houses, television, phones. Most people strive to have these things in life. While I choose to dream of a mud cabin in an empty wilderness, and \textbf{nothing} but me and nature going at it. All the things I listed at first have been compromised, taken over. Television is used to distract and entertain and it cost money. Money is earned by working, houses are earned with money and phones are what connects us to other people or places where we can spend more money or waste more time watching television or working.We all strive to have money? Why? Because it's the key to happiness right? Wrong, it's what our society has made to be important. If you all can't see that we live unnaturally then I have no hope for gen Z. Because we will remain lost and slaved for the rest our lives. Break the system, raise an army to over throw government, why couldn't we do these things? Imagine a natural world where your entertainment is walking down to the lake to take in a real view, and not watch it on YouTube. Imagine instead of earning the money to buy the food, you had the ability to track animals and grow your own food on land that you own outright and don't pay taxes on. Some of you would say this is a barbaric way to live.. and to that I say you are lost\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/240 & \cellcolor{green!5}0.417 \\  \hline
  \cellcolor{green!27}\small Cam 123 If that's what you think is best then do it yourself, \textbf{nobody} is stopping you and you have all the freedom to do you. Don't shit on society just because it doesn't fit your own views and opinions, sensitive ass.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Hiram Chill lmao nah I said it cause your \textbf{blind} to it, with your bitch ass. Fix it\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Cam 123 You wrote a whole essay on overthrowing the government. \textbf{Nobody} is \textbf{blind} to anything and there's \textbf{nothing} to fix ðŸ¤·ðŸ¾â€â™‚ï¸ sorry it's not the future you imagined you boomer\normalsize   & \cellcolor{green!27}Blind, Nobody, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small Ikr, ain't our fault you made us, boo! Also, we didnt give ourselves the tablet or phone, you did! Not our problem, \textbf{hun}.\normalsize   & \cellcolor{green!5}Hun & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Roses are \textbf{r\textbf{ed}}, violets are blue. There's always an Asian, better than you.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small I was born in 1993 but I relate more to gen Z maybe because all my close realtionships, \textbf{sexual} and platonic were from gen Z\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small It's \textbf{weird} hearing people from other generations generalising our generation. I've always pitied millennials for this reason. Well, at least they're not blaming us for anything at the moment.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I honestly think 1995 - 2000 should be like a \textbf{transition} generation, because my childhood was part millennial part technology world and well someone born in 2012 or even 2005 or 2008 will never have the full experience? Not even partly. Its \textbf{weird}, but I think since technology moves so fast the generations should become smaller? I hope someone else feels this way too.\normalsize   & \cellcolor{green!5}Transition, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!5}2/64 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Generation Z will be like the human plug with wires  living in a simulation like in the matrix. Capitalism doesn't care about generation. They just want to get their hand on every little thing that you do and like so you could CONSUME more and more bs...  Ask the Baby boomers. They once had  the fate of humanity right in the middle of the palm of their hand and they trade it all for cheap mortgage, low price oil and a big \textbf{fat} home T.V in the living room. Millennials just live in the wake  of their Parents gluttony and three financial bubble after we just the realize we got way more bill to pay than our parents, internet, the phone, the gym yadiyadiya... rolling my eyes....\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small i HATE the name iGen. we're not a fucking \textbf{apple} product, we're not some screen zombies. the older generations like x and baby boomers never care about our drive to change the world, our drive for change, for success, they're just focused on 'how kids these days never get off their phones'. its so idiotic.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small I was born in 1995 and consider myself a millennial. as many will tell you the exact years for generations are not solid. I view gen Z as 2000-2020. even though the internet was commercialized inÂ 1995 does not mean everyone had it. we didn't have internet in my home until 2010.Â we grew up playing with toys, going outside and watching VHS and later DVDs forÂ entertainment. it was not until my teens that I got into computer technology.Â having time to be a kid without needing to be online I think was very helpful in teaching meÂ not to become too attached toÂ technology. I have concerns many other millennials and most of gen ZÂ got into technology too soon in their development. the internet is a useful tool butÂ the things it allows you to access are not always appropriate. it can destroy innocence and there is the danger of being brainwashed by media to think, act and be someone you're not. I know when I have kids teaching them to use the internet in a safe and productive way and at the right \textbf{age} will help them in the future.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/194 & \cellcolor{green!27}0.515 \\  \hline
  \cellcolor{green!5}\small Anjay Watts Which ever publication is talking about them will fill in their bias. That being said, the idea that GenZ are extremely accepting of Transgenderism and \textbf{L\textbf{G\textbf{BT}}} is based on anecdote with no statistic back up.\normalsize   & \cellcolor{green!5}LGBT & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small We also have less \textbf{sex}  :(\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small the drivers license thing is a \textbf{fat} ass stretch like if you live in a city obviously not but everywhere else how are you gonna get anywhere\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small It's because our parents, generation x. They had the highest suicide rates and \textbf{mental} illnesses. So we got it from them?\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I'm sorry but yeah electronics really are the reason. Most of my good experiences come from my phone dying and making me live in the moment. It's a lot easier to think without being on your phone because at least for me, my thoughts become less cluttered. One time I was visiting my fathers \textbf{old} roommate and my phone died so I ended up talking to the guys son and we had a little fling. If my phone didn't die, I wouldn't have even bothered to talk to him. I went to the movies without my phone and became observant of what was around me. As much you might hate it, your \textbf{mental} health does get better when you get off your phone. You learn that the media blows everything up, you meet people, you learn more about the world. I'm not saying get rid of it, but spend less time then maybe you'd realize 'wow the world isn't too bad at all'. Social media influences us on what we should think and how we should act. In all falls into this toxicity of confusion and sadness since we practically have grown up with it.\normalsize   & \cellcolor{green!5}Mental, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/195 & \cellcolor{green!5}1.026 \\  \hline
  \cellcolor{green!27}\small Godd Howard    we're not complaining about our privileges, considering that many people don't have them. We're not complaining about our phones and electronics. Yes, our electronics contribute to our \textbf{mental} illnesses but what are we supposed to do?? We grew up with electronics and we don't know what it's like to live without electronics. Some people think that we're all just ungrateful, but that's not true. It's not our fault. It's not like we're the ones who made this world into, as she said, a â€˜hellhole'. We don't try to mess with the media or people's lives. That's just cruel. We're trying to fix it cause that's what people want us to do and that's what we need to do.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}\small No, I'm a part of Gen Z and the most anti social and depressed people I've met are online. I'm fine, most people I know in real life love being around and I love being in people's presence. There's \textbf{nothing} to be depressed about, human invention can stop anything. If you make enough money then you could literally dig straight through India to North Russia. Quit the pessimism and you can do anything, may sound \textbf{tacky} but it's true from experience\normalsize   & \cellcolor{green!5}Nothing, Tacky & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small Ikr. I hate when older generations say that all my problems are caused by being on the phone or because of internet. Like no. It's just a device which makes our lives easier if anything. Most of us are depressed or have \textbf{mental} health problems is because of our childhood and how shitty of a place the world is rn and we are the next generation so we have to fix all the issues that previous generation had made.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Godd Howard  Are you illiterate? He/she clearly said the world. As in political unrest and \textbf{old} farts in power licking the boots of oil tycoonsâ€”not giving a crap about our planetâ€” because it makes them lots of money. As in drinkable water will become the new gold by 2050 (if not sooner). As in older generations will be making the decisions that affect humanity in the long run for a while and Gen Z will be too young to do anything about it. Also, the idea that there are enough nuclear weapons to wipe out entire countries and render the planet uninhabitable for humans is not very pretty either. So, to rephrase the OP's comment, maybe we'd be happier if we knew that there was a future for us, our children, and humanity in general.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/135 & \cellcolor{green!5}0.741 \\  \hline
  \cellcolor{green!27}\small I actually hate it when I'm with my friends and they're on their phone caus it loses the moment. Also genZ's culture may be defined by the internet but that says \textbf{nothing} about who we are as a generation\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Shan DLR We just need to hit voting \textbf{age}. We just need to hit the \textbf{age} where we can run for government.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I don't think Gen Z thinks it's 'the chosen one'. I think they/we all feel like all of this is pointless and life has few \textbf{fruit} to offer. I think Gen Z is just trying to cope with inevitable mediocrity.\normalsize   & \cellcolor{green!27}Fruit & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Lizzie King well depends on what your definition of phone is. My first phone was 10, I had a 6 year \textbf{old} Samsung flip phone. (Nostalgia hits hard. One of the best phones I had.) That was 2012.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small That one guy in the \textbf{black} shirt looks like Squidward\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small GenZ: insecure shit heads with divorced parents, and \textbf{zero} dignity taking selfies all day, and feel suicidal when their phones are taken away.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Why do we still elect politicians that are 70 years \textbf{old} and have \textbf{old} ass ideas and beliefs\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Elio because Baby Boomers are the single most consistent voters. This year and 2020 will be when Millennials and the eldest iGen can fight back. Look at the election of Alexandria Ocasio-Cortez to Congress. She is a 27 year \textbf{old} Socialist who ran on a platform of abolishing ICE and she beat the Democrat incumbent who was Nancy Pelosi's heir apparent. Millennials really fucking dropped the ball in 2016 not getting Bernie elected, but the youth can still make things right.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Gen Z here, because maybe, just maybe, a person's \textbf{age} does not alter their ability to act as a vehicle for the policies they support, and that their \textbf{age} does not change the legitimacy of their policies?Because \textbf{age}-\textbf{old} ideas are generally the ones that are tried and true, at least if you consider \textbf{age}-\textbf{old} since the Enlightenment.Liberty, justice, meritocracy, democracy, rule of law, God-given inalienable rights, constitutionality, etc. seem to be pretty good ideas, they've been around a lot longer than your 70 year \textbf{old} politicianHave fun with your Ad Hominem fallacy!P.S. "who is not a liberal in youth has no heart, who is not a conservative by \textbf{old} \textbf{age} has no brain."\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}5/117 & \cellcolor{green!27}4.274 \\  \hline
  \cellcolor{green!5}\small How bout, The \textbf{Mental} health problem generation\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small As a millennial, I agree.   This is the \textbf{mental} health generation.  From mine till gen z.  What the hell is wrong with the newer generations?\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@RyanFresh I think we're just more open about \textbf{mental} health tbh.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small More like the gayeration... because we're really \textbf{g\textbf{ay}}?... Imma leave now\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small I think it's because we (?) have more access to information and \textbf{mental} health is getting more awareness. I don't necessarily think more people are mentally unwell, more so that more people are getting help for it! Everybody can benefit from therapy anyways.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small I'd say give us about two or three years. Truth be told, you'll either see too much or \textbf{nothing} at all from us.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I think we'll see plenty of Gen Z in 5-6 years too, but we won't be able to see what Gen Z is really like until we're \textbf{old} enough to be in positions of mass power, such as presidency and shit. That's when literally all of America will be in the hands of Gen Z instead of Baby Boomers and Gen X\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small B0omer96 yet the white \textbf{race} has tried to kill others. I don't want the white \textbf{race} to die off a have friends and family but you are a Hypocrite\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small \@ChikaCherry.  I'm a hypocrite because I don't want my \textbf{race} to end?  I don't want any other \textbf{race} to end either so how am I a hypocrite again?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Boomer96, you do realize the american population is increasing don't you? Wealthier people tend to have fewer children. This also is one of the reasons why places like sweden and Japan are having severe birth crisis. They're very homogeneous countries as well as prosperous. All this is to say is that the white \textbf{race} isn't coming to an end. It's a silly notion, and even hypothetically speaking, if it were coming to an end it's certainly wouldn't be by force or some global conspiracy. The fact that white families have fewer children isn't the fault of any other \textbf{race}. Nor is the fact many choose to marry interracially. Many of the world's most powerful countries are majority white ...i'd say it's one of the last races to worry about extinction. Many tribal races are definitely dying out. Now if your concern was a loss of power... that's a fair argument.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/150 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small +B0omer96 Celebration? Where? It's \textbf{nothing} more than a simple fact. The birth rate of white Americans is the lowest of all races, tied only with Asian Americans. No one is celebrating that fact, just pointing out the obvious. If we are truly equal, like I know so many on the right claim we are, it shouldn't matter, should it?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small well actually genZ based on their \textbf{age} demographics are pushing 23, so i wouldn't label them all as kids, im 19 and I was born in 99.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small You think a 22 year \textbf{old} person born in 1995 don't matter?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small B0omer96 Lol. You have a \textbf{r\textbf{ed}} ice subscription kiddo. Lana only has 1 kid\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Also from personal experience of horde of young cousins n some of their frens . They are also quite physically lazy and weaker even than millennials . They hate going out more than anything and need internet to be there and rather chat than be where they are. Our parents are forcing us to take these dweeb on trips cuz they r tied umbilical cord to their rooms and devices . I am ranting at my 20's like an \textbf{old} man. They are well informed though but...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small Personally, the "Generation Z'ers" that I know could have it easier in life (in general). That's mainly because of the previous generations before them. Mainly because of the foundation that their parents could work on and the huge technological advancements.I also consider myself very lucky to be part of the "Y Generation" as I'm able to witness the "dying" of \textbf{old} fads and tech as well as the "birth" of new fads and tech (cartridge games naruto nokia 3310 samsung s9 yoyo AI tetris Ryzen Windows 95 tamagotch adobe flash... and much much more).\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small The teens of genz z are the face of it. We have seen libtards fail. We have seen donald fuckin trump become president despite all the cordinated efforts used to \textbf{cripple} him. We have seen innovations in SO MANY AREAS. Knowledge is easier than ever to receive. The only reason why I got hope for 2020 and beyond is rooted in the things that can be done and have been along with our road ahead that is clear. We know of the horrors of the past AND the bright light oh so close to us. Gen z will NOT PUT UP WITH TYRANNY.\normalsize   & \cellcolor{green!5}Cripple & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small Are mixed people (European-\textbf{African} mixed people) letting the European \textbf{race} die off or the \textbf{African} \textbf{race} ? (I've heard that the \textbf{African} \textbf{race} is more dominant)\normalsize   & \cellcolor{green!27}African, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}5/26 & \cellcolor{green!27}19.231 \\  \hline
  \cellcolor{green!5}\small Danie F Well i hope they dont get more offended over \textbf{nothing} than the young people of today already are then :vvvWas born in 2002 btw, if you mistake me for an older person.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Crystal K Asians and native Americans have the lowest. And the \textbf{black} birth rate is now the same as whites.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@Dino that's not what I've seen, it said gen z was 1998 but who tf knows, \textbf{nobody} can decide on it\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small the oldest gen z are already of \textbf{age}... wtf u on\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Raccoon how \textbf{dumb} do you think we are\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@David Johnson Mainly because of western countries exploiting them. Libya would've been a first world country and the powerhouse of Africa until the United States invaded, killed Gaddafi and forced democracy. France still steals money from former \textbf{african} colonies including Haiti and only leaves them with 15 to develop their countries (even recently the Italian president accused France of creating poverty in Africa) Hillary Clinton steals money from Haiti also. Not to mention, American influence in the middle east. Why you think those countries hate us so much?\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small \@C. Smith thats actually chaging quickly. the last updates of \textbf{ethnicity} increase in population is expected to tip tables in 2025\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Honestly ,I don't agree with the \textbf{age} range that you're using. I think that people born in the 2000's( 19yo now) that will set the image the the world will have about the GenZ\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Yeah \textbf{race} wars sure are interesting huh\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Wow I learned \textbf{nothing} in this video. Thanks Time.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Please don't call us iGen.... Why would I want to be associated with \textbf{Apple} like that? Gen Z is a great name.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small the enslavement part was a little hyperbolic. You have the ability to make your own choices and think for yourself, especially if you live in the United States. \textbf{Nobody} can control you if you're in control of yourself.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Awww it's official I'm an \textbf{old} millennial.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Is it possible that Depression among Gen Z is prevalent, because Gen Z has for the most part accepted science, and rejected Religion? Religion taught that people were put on Earth for a reason, and science says nope, everything is meaningless. This principle is called Nihilism, and it's the reason I fell into Depression. Just to clarify, it had \textbf{NOTHING} TO DO WITH SOCIAL MEDIA.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small As with every generation, there's a definite disconnect between how Gen Z operates and how other generations perceive it. For instance, I have a Catholic friend who gave up her social media for Lent. And halfway through this, I got a message from her telling me how difficult it was to give it up because she had to receive messages from other people through social media, particularly for school. She wanted to disconnect completely, but without accessing her social media she was missing out on a lot of important things in her life. And that's something I feel like other generations don't necessarily realize. In some ways, the new technology gets to a point where the youngest generation can't operate without it if they want to make and maintain connections in their \textbf{age} group.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/134 & \cellcolor{green!5}0.746 \\  \hline
  \cellcolor{green!27}\small Bruno your theory is badly flawed once economy collapses - \textbf{nobody} has internet or phone/computer to make the connections you are talking about- appears millenials don't know how to communicate one on one only online which they are about to lose\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small I remember "boomers" ridiculed millenials for carrying around "useless" cell phones (we could barely afford) in 1999. And even now they still barely understand the importance of global connectivity...The older generations never needed to actively learn how to manage their attention in the midst of all the 24/7-in-your-face advertisers. Or fake friends trying to rip you off online. :( They were also able to learn at their own pace (if at all) and their habits were already formed when the smartphones and tablets became \textbf{common}.To all you Gen-Z'ers: enjoy the praise. Won't be long before they start complaining about you. Probably after your first years in the workplace. :P\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/111 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small nobody will afford smartphones, tablets or computers soon\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Brandon King sounds like you know \textbf{nothing} about economics - let me guess you are a millenial.  Sorry buttercup but you aren't the voice of reason if you think technology is free.  Predictions are easy when you know the design of the SYSTEMS- you might want to educate yourself on ALL systems like economics, government, justice systems they are all 100 designed to create specific results and they work perfectly so it's not really a prediction as it is a description of the designs of all systems silly.  For someone who knows technology you sure no \textbf{nothing} about technology\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small Another thing to consider is that doubling the processing power does not necessarily double the value or utility of the device... software tends to take advantage of all that processing power and squander it on frivolous inefficiency. Windows 10 has a processing and memory footprint at least several times greater than Window XP... but how much MORE can I actually do with it than I did with XP? I had to upgrade from my 1st gen iPad mini because I couldn't even surf the internet with it anymore. Websites are so bloated with extraneous scripts and advertisements, my browser would frequently run out of memory and freeze or crash just trying to do routine business. Furthermore, many essential apps were barred from me because they did not support the \textbf{old} version of IOS. So all that extra processing power we love to praise isn't really improving our productivity at all - it is simply in an arms \textbf{race} with the software environment it needs to support.And no, technological advancement is NOT independent of the economy nor does technology inevitably improve. It is in fact DEPENDENT on a good economic environment and a a stable, prosperous society. Just ask the people living in political chaos and poverty for a thousand years after the economic and military collapse of Roman civilization if technology always improves.\normalsize   & \cellcolor{green!27}Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/224 & \cellcolor{green!27}0.893 \\  \hline
  \cellcolor{green!5}\small You mean the shit you started, promised to fix before the millennials got too \textbf{old}, didn't do your job, and then shoved onto them like a broken promise? We Gen Z have no issues with Millennials. We saw how you did them dirty. It's you that we're gunning for.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small That one guy is like Trent rezners \textbf{g\textbf{ay}} brother\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small We had Gen X, Gen Y, Now Gen Z. Gen Z will probably not reproduce. What comes after Z? \textbf{Nothing}. Are we predicting the end of civilization, here?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Sese Talitau-Tio I'm Gen z and I love the idea of getting paid hella cash. In AZ, minimum wage is 10.50. really awesome wage for a 17 year \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small iGen??? What about those of us who don't like \textbf{apple} products??\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small my mom \textbf{g\textbf{ay}} the whole concept of generation is a very American creation. The Greatest Generation, the Silent Generation, the GI Generation, the Baby Boomers. The reason why the Baby Boomers are considered the whitest generation is because in America during the 1950s America was majority white. Every generation is increasingly more and more racially diverse, which is why the Boomers struggle to understand how the status quo is changing.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small i was today years \textbf{old} when i found i am a gen z not a millennial... whattttt i was born in 1996\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Gen Z is and will be much smarter than we give them credit. As a millennial, im not too proud to admit they will probably be more intelligent and more progressive than us by our \textbf{age}, but thats okay. Thats better than okay, they are our future and they should lead the way when we have become too \textbf{old} or too arrogant to do it anymore.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small being born in 2001 im kinda in that \textbf{weird} generation. not a millennial but also not a kid who grew up with technology all around me\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I really dislike the name iGen, like yeah we know that we grew up next to \textbf{Apple} and others, but just because that's what adults now think about when Gen Z comes to their mind doesn't mean that it's a name that should represent us.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small People say children are different now. They act differently, play differently, talk differently than previous generations. But remember, children aren't born with a smartphone in their hand. Children need parents to raise them and teach them how to act, so don't hand your kid a phone and complain about how they spend too much time on there phone. There are teenagers, like me, who are living amongst these gen Zs and millennials but have no part in it. I am 16, I have no social media other than YouTube, I read books, I work full time and go to school, I drive a manual car. I'm not boastling in any way, but I am ultimately thankful to the discipline my parents, mainly my dad, installed in me at a young \textbf{age}. I'm glad that at 16 I have the job experience of most 30 year olds, I'm glad that I worked for every cent of my car. Remember that kids will be however you raise them, I'm glad to have had an amazing dad.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/174 & \cellcolor{green!5}0.575 \\  \hline
  \cellcolor{green!27}\small SweetTea742 Thanks for the reply man. You brought me back to the day I commented this, and It's \textbf{crazy} to see how far I've already come since then. Enjoy the rest of your life, peace. âœŒï¸\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Your Majesty This may seem \textbf{dumb}, but what do you think about communism?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Not Politically Correct Well, an ideal economic system for me would involve complete laissez-faire and the abolishment of any and all government intervention when it comes to business practices and things of that nature. Such means no anti-trust laws, no anti-monopolistic laws, \textbf{nothing}, nada. Honestly, I couldn't care less in regards to the loss of blue collar jobs for, if anything, such would further hasten the shift towards a more service based economy which, in turn, will, in theory, make labor cheaper (we'll no longer have to hire Hispanics to do our landscaping).Also, in case you were curious, an ideal governmental system for me would involve immigration quotas and such. Basically the immigration/maybe partially??? domestic policies of the early 1900's.In short, I absolutely despise communism.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small Your Majesty God bless, Better Dead Than \textbf{Commie} \textbf{R\textbf{ed}}!\normalsize   & \cellcolor{green!5}Commie, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/9 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Not Politically Correct for me, I wonder if communism in the ussr would have actually worked if the government wasn't so curropt. But I wouldn't actually want a \textbf{communist} government in the us. I'm center left. Financially right, but socially left. I'm Gen z btw\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Abc \textbf{Abc} How is equality bad? I'm in Gen Z. Equality would be a great thing.On the other hand, it doesn't, and never will exist. With feminism and crap, there's always going to be one side trying to overthrow another.THAT is bad.\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Equality of opportunity is great, equality of outcome is terrible. When you have equality of opportunity, and everybody can freely choose how to live their lives, you will naturally have more male \textbf{engineers}, and more female nurses, based on personality trends between the sexes. When you push equality of outcome and demand there be more female \textbf{engineers}, you will realize there's a shortage, and you're turning down perfectly qualified men because diversity. The vast majority of dangerous/hard labor jobs are held by men and you don't see people demanding that the lumberjack industry hire more women. And that's a good thing because there are differences between the sexes and there's \textbf{nothing} wrong with that.\normalsize   & \cellcolor{green!27}Engineers, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}3/114 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Doesn't mean it's not opposed to equality, I think what the OP missed is that it's equality of opportunity people are for, which makes sense, because that'd mean all people regardless of \textbf{race} would have equal relationship opportunity as far as they're concerned.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Armand Castilla Equal opportunity is not a good goal. People are always going to have to work harder in some things, and get it easier in others things. That's the way it should be. You're right about the thing with more male \textbf{engineers} for example, but if a male is born with an IQ ten points lower than another guy, he will have to study more and work harder than the other guy. Or if the guy was born a bit more gifted in mathematics. That's not an equal chance. You have to work harder for your chance. It's ok though because I think most people who are for equal opportunity really aren't. I think they just mean everybody CAN do it IF you work harder than the guy who was born having to work less for it. But that's obviously not equal at all so I think conservatives' use of the word "equality" is pandering to how far left the political "center" has gone. There are only certain situations where money for example shouldn't matter as much and more equal chance would be nice (like in school or sports), but money will always matter and to say otherwise just means you have to stop valuing capitalism or money and its worth at all. Everyone has the chance to work hard to earn money so it works fine.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/228 & \cellcolor{green!27}0.439 \\  \hline
  \cellcolor{green!5}\small Abc \textbf{Abc} I think we're arguing about semantics here. When I say equality of opportunity I mean there's basically no discriminatory laws says you can't do something. Beyond that it's up to you to earn whatever you can. We already have equality of opportunity. Somebody with 10 less IQ points has no less opportunity than somebody smarter, they just have to work harder but they still have the same opportunity. You're talking about equality of outcome. Jordan Peterson always argues for equality of opportunity and against equality of outcome so you can debate him if you want\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small I'm a \textbf{woman} and please don't fall into feminist lies. Trust me. This is coming from a classical liberal\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Zoomers knows \textbf{nothing}, really.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small How ? Without equality the world would be much more \textbf{racist}, sexist and \textbf{homophobic}.\normalsize   & \cellcolor{green!27}Homophobic, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small BoolNRelaz in today's day and \textbf{age}, yes, it is useless, because most people who go to college end up working for a fucking McDonald's or Star Bucks the rest of their lives. Look up theburgerkrieg's "you're doing fine millennials." And you get to see how the workspace is now saturated with overqualified people. You are replaceable so why bother?And yes. We hate PC and SJW behaviour. Because we don't expect equality of outcome we expect the equality of opportunity. While millennials tend blame others for their own failures, and sometimes themselves. Gen Z likes to own it's mistakes and often times look for solutions on how to fix them, not who to blame for them.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/116 & \cellcolor{green!5}0.862 \\  \hline
  \cellcolor{green!27}\small College isn't obsolete, choosing \textbf{dumb} majors is obsolete. You can't expect to get a job from a bachelor's in psychology, since there are thousands of PhDs more qualified than you. However, you are guaranteed a decent future if you go into STEM or even business (for the most part). And to hate the archetypal SJW with blue hair, 15 piercings, and "no \textbf{gender}" is fine, but the problem arises when you think all liberals/all millennials are SJWs and thus hate all of them. All "atheism" channels of 2012-2015 suddenly converted into "SJW hate" channels, and that \textbf{transition} is very sad. The "SJW hate" phase is something that feeds perfectly into teenage angst/hormones as it feeds a need to put others down. This makes Gen Z currently a prime target for these videos. The dangerous biproduct of this is when some viewers associate the whole left with SJWs. Anyway, the words "SJW" and "PC" shouldn't even have a negative connotation, but the right wing internet successfully brainwashed those words to be insults.  To advocate social justice is to advocate equality, no matter what a few whackjobs have you believe. And to be politically correct is to be polite, although there are extreme exceptions which everyone finds annoying. And for the record, I'm Gen Z although i'm within the awkward half-decade from 1995-2000, so i'm not some "millennial whining"\normalsize   & \cellcolor{green!27}Dumb, Gender, Transition & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality & \cellcolor{green!27}3/227 & \cellcolor{green!27}1.322 \\  \hline
  \cellcolor{green!5}\small Oh same here, I'm from 1998, the thing I have a problem with is the left which goes too far into the sjw mindset. And I think being an SJW and PC is rightly negative. Because Sjw stands for social justice WARRIOR. Warriors being fighters and when it comes to fighters... Leaves little in terms of neuance for discussion. And PC is a stupid idea too, you can't call the MS-13 animals because "Oh that's so \textbf{racist}." no, they act like animals, barbarians at best. Why should I curb my dialogue to fit someone's world view?Libertarians are fine. The people who tend towards SJW and PC crap, really tend to be just middle-classed shits that want to impose their self-righteousness on everyone else. \textbf{Nothing} more.\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/126 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small \@Horny Dolphin Considering I don't tend to watch or even like Alex 'they're turning the frogs gay' Jones or the others within that group. I'd have to say I'm far from brainwashed. I and many within my \textbf{age} bracket, from what I know, don't believe equality of outcome is possible or desirable, and tend to lean on the libertarian side of things. Many uni/college courses are being made redundant either by over saturation or automation.I don't know what you're accusing me of brainwashing for but those are the only things that possibly come to mind.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Abc \textbf{Abc} yeah, but my point is that Generation Z is way more balanced than most people seem to be letting on\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Abc \textbf{Abc} also, being conservative isn't necessarily a good thing.\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I don't think the classification of gen z being born from 1995 to early 2000s is accurate. Reason being is that I was born in 93 and I've always had internet in my house. I started using computers when I was 5 years \textbf{old} and so on. I think gen z should be like early 90s to early 2000s.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Layback Studios nope. most gen Z support gays, \textbf{g\textbf{ay}} marriage etc. Ur just a bigot mate\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Layback Studios I'm not offended \textbf{snowflake}. We are all about equality, acceptance etc. If you don't wanna be part of this, sure, be our guest. But you are the anomaly.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Tobias I'm not a \textbf{snowflake} idiot. Shows you and your judgement is trash. If you can't get something right about one person, shows you can't know anything about an entire generation. Lol. And yes you are based upon your reaction. Also most of us don't care if they do what they believe. We just don't support them. Shows how much you know.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Lol the \textbf{snowflake} is triggered! Shows how much you know, anomaly...\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small As a bisexual gen z, I don't care at all for any pride related bull shit. It's literally like they are bragging about \textbf{sexual} preferences in a way when I feel humans are much more than what makes you aroused.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Tobias Oh I thought I told you I'm mixed. So can't call me a \textbf{snowflake} you \textbf{thot}.\normalsize   & \cellcolor{green!5}Snowflake, THOT & \cellcolor{green!5} Ideological and Political Identity - General, Gender - Female sexuality & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Wow you gen z seem to be more sensible than the millennials(sorry for my bad spelling). I'm a classical liberal and a \textbf{woman} who is not brainwashed by this feminism and sjw bullshit. I am all for \textbf{g\textbf{ay}} rights but i hate how the left tried to shove it in our throats.\normalsize   & \cellcolor{green!27}Gay, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small If it walks like a homophobe/transphobe, and it talks like a homophobe/transphobe.....Next time you're trying to hide your bigotry, try talking about trans people and \textbf{g\textbf{ay}} people l like they are. People. Y'know, instead of like products. Or objects. Dick.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small I was born 1997 and im going to army this world is \textbf{g\textbf{ay}} asf\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I feel like as a gen z, we are stereotyped. We are seen as lazy people who don't care about education or careers. I stress so much about my grades because I want a good career. I am definitely not the stereotypical teen. I'm a huge nerd and an \textbf{old} soul. I love learning and helping people. When I'm older I hope to set an example like those who have influenced me!  Have a great day to those who are reading this!!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Abc \textbf{Abc} a career matters more than having marriage and kids\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Abc \textbf{Abc} 'useless career' BOI if u don't get a good career good luck trying to find stability. How u gonna have a good fam if u don't get stability? We have time unlike last gens they worried about reproducing/staying alive.\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Abbey Murff you just said you are not a typical teen and you are an \textbf{old} soul, therefore you don't represent gen z. So which is it? Are you gen z or not? It sounds like you do not identify as gen z which is fine but your comment makes no sense.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small 00101 111001 I'm saying when people find out my \textbf{age} they make assumptions about me like being lazy and not caring\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Abc} \textbf{Abc} "the problem with gen z" well there are a lot of people in that generation so I don't think it can be generalized like that.\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Since the dawn of civilization, older folks have been calling the younger generation lazy, anti social, etc. \textbf{Nothing} new at all.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Abc} \textbf{Abc} career so that I can fucking survive > relationship I where I have to buy a lawyer to break up and small income leeches\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small chilidili they look like lunatics to me. I was born in 2003. It's the first time I hear of 'iGen'. Moreover it makes me feel like an \textbf{apple} device and less like a human being.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small These are some \textbf{old} people who make those generation things, so they don't really know what they're talking about, especially about the \textbf{age} group...But us, who were we born during that time, we know that there is something wrong with putting someone born in 95 and 2012 in the same generation. This is two completely different experiences omg!!! There is a big difference between growing while the internet is getting bigger and biggerand being born right into it.The \textbf{age} group for gen Z really need to change that's not accurate at all... So yeah, either put ~1995-mid 2000 with millienials or either create a specific generation for us and the problem will be fixed\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/117 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Ahem.  They're called "Isotechnics"  Stop ripping off Generation X's name.  \textbf{Nobody} wants the added rule that new generations now have to have a letter labeling system.  Isotechnics are a generation of "Isolated" people due to "technology"  through spending so much time on their phones, social media vs real life human interaction and online ordering so they never leave the house.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small abc alqadiri I honestly don't know much about American politics, but I don't think the details are that relevant here. Liberalism is bad, because it makes it hard to have an opinion of your own. Liberal thinking has become a necessary thing to be considered a decent person. Don't get me wrong, you can be a classical liberal or at least not a hardcore liberal, but if you look at the movement itself (a. k. a. SJWs) you'll see that it's highly illogical, depends on feelings alone and can actually become so intolerant and straight up aggressive, that the people don't seem liberal at all anymore. That certainly doesn't characterise every liberal, but that is what drives liberalism and every sub-movement it has, like feminism and \textbf{L\textbf{G\textbf{BT}}}+. The thing is, if you don't actually research the political or philosophical movement you identify with, you can end up being simply brainwashed and as a result say a lot of stupid stuff. Because every real movement is interested in adding new members, therefore it's not unbiased, it doesn't give you freedom. That's why calling yourself a feminist and reciting a bunch of repeated phrases doesn't do any real good for the world, only create an illusion that people are fighting for the right thing. But who said changing the world for the good is easy?Basically, modern liberal ideology makes you \textbf{blind}. Because any ideology makes you \textbf{blind}. And I actually never specified that the 'healthy thinking' part is about conservatism or republicanism. Liberalism is the opposite to healthy thinking nowadays because it is currently dominating mainstream media. These days if you want to be seen as progressive you absolutely have to be a liberal. Only, truly progressive thinking can never be dominant in society. You have to risk being offensive by saying new stuff, if you want to actually move society forward. Liberals don't want you to understand that.\normalsize   & \cellcolor{green!27}ABC, Blind, LGBT & \cellcolor{green!27}Nationality - Chinese, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}6/318 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small I'd say what we are is apathetic, especially compared to millennials. Like the millennial teachers I have all really do seem to believe in that social justice warrior politically correct crap. Most of us Gen Z all realize that the political correctness has gone way overboard, and now we treat it like how people treated the social expectations of conservative etiquette a few decades ago. Essentially being politically correct is the new "show some manners" but now it's coming from the left instead of the right, and instead of being anti-rocknroll and anti-sex, its anti-cultural appropriation, and anti-microaggressions. They're all equally bullshit. We definitely are socially liberal, and our stance on gun issue seems to be pretty left (although since we also know \textbf{nothing} about guns that aren't on our xbox, our ideas for gun reform amount to banning the machine gun 1007 which killed about 3.5 people this year, while leaving machine gun 1-1006 as the same) we are more fiscally conservative however, and our attitude on foreign policy is basically1. Let's make friends with everyone through diplomacy and trade, always trying to avoid war.And 2. As long as no part of Mohammed Ahtmu lands on my shirt after the drone strike, the war on terror is just a part life (or death) And we don't seem to care/know too much about the constitution.We also aren't foaming at the mouth like Democrats are about Trump. Most of what Trump does we either laugh at, see as just some far away policy from D.C. that won't effect us, or don't know and don't care. And we don't seem to want Washington to be involved in our daily lives, we don't really trust them and see them as usually ineffective. Generally though you can still feel the inclination towards the left within Gen Z, but maybe that's more just me since I do live in silicon valley where everyone is already liberal. Any Gen Z out there who live in more moderate areas.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/335 & \cellcolor{green!5}0.299 \\  \hline
  \cellcolor{green!27}\small Symphony No. 5 What do you mean by "Conservative" Cause sure as hell no one in this generation is going to dress up formal 24/7, oppose \textbf{g\textbf{ay}} marriage and the \textbf{woman} sure as hell arent going to stay in the kitchen or at least  be more " Traditional" I know my generation well enough.\normalsize   & \cellcolor{green!27}Gay, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/54 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small QUEEN TRISHA ok, I know my generation too. But do you know what are we going to be in the future? Conservative for our generation isn't the same as conservative for our parents or grandparents. The idea remains the same, but the world changes. Right now young conservatives are mostly a reaction to liberalism being overrated among "progressive" people. It only means that we chose to look at things from a more mature, experienced worldview. Of course, we are all trying to be smart, but it only makes sense to become more conservative when you see the world becoming too liberal. We are \textbf{old} enough to be interested in politics and young enough to be dissatisfied with the way our world is ruled. So, if you think about it, conservatives that we need today are not at all the conservatives we all know from childhood. And, the liberals, that we all consider ourselves to be, are not at all that progressive anymore. With that logic, "liberal" is the new conservative, and "conservative" is the new progressive. And, by the way, if you haven't thought about it, the world will always be devided into conservative and liberal. Our biggest priority is not to choose either side, but to seek balance between the two. We have to learn from each other and learn to compromise in order to preserve peace.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/228 & \cellcolor{green!5}0.439 \\  \hline
  \cellcolor{green!27}\small Symphony No. 5 makes it hard to have an opinion of your own? I grew up Conservative. I was the youngest member of my local Tea Party Chapter and was involved with the American Militia Movement in high school. After i became atheist i literally got kicked out of Conservatism. If you dont think exactly as they do your the 'enemy'. As a Liberal i am a Libertarian Socialist/Anarcho-Transhumanist. I have never experienced a greater level of individuality than i have on the Left. I'm high functioning autistic. On the right i was ostracized and bullied for being neurodivergent but in the left my differences are embraced and accepted. What you seem to be bitching about is that \textbf{racism}, bigotry and hatred is less tolerated. Thats the new world we are living in. A diverse world where everyone has the freedom to live their lives how they want as long as they arent hurting anyone else.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/156 & \cellcolor{green!27}0.641 \\  \hline
  \cellcolor{green!5}\small Symphony No. 5 i disagree with that. The fact is what most people seem to be calling '\textbf{racism}' is in truth called Institutional \textbf{Racism}. Its the \textbf{racism} of those in power. Anybody can be \textbf{racist}, but only those in power can project \textbf{racism} onto entire demographics of people.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/48 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small abc alqadiri the Libertarian Party is turning Socialist bruh, we have a LibSoc Caucus and had an Anarch-Communist run for LNC Chair. He lost to the incumbent Nick Sarwark, but Sarwark is LibSoc friendly so its still a victory. We are kicking the Fascists out.\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small I'm assuming this is from an American viewpoint? All I can say on this topic is that as an Australian born in 03, many people want change. A large majority agree that the world has gone to the dumps and we're the ones that have to do something about it. I've been taught from a young \textbf{age} about global warming, etc. and countless classroom debates have ended in the agreement that something has to change. I think we should all collectively agree that the concepts of conservatism and liberalism need to go. With changing times come changing ideas - how are you supposed to go by ideals that are quite \textbf{old}? You can't really say an entire generation is either liberal or conservative when there's Gen Z kids all around the globe who are still quite young.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/137 & \cellcolor{green!5}1.46 \\  \hline
  \cellcolor{green!27}\small Symphony No. 5 Boyyy you are sooo wrong, more people are out here being feminists (good), \textbf{L\textbf{G\textbf{BT}}} members and allies, against \textbf{racism} and having their own opinions.\normalsize   & \cellcolor{green!27}LGBT, Racism & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}4/27 & \cellcolor{green!27}14.815 \\  \hline
  \cellcolor{green!5}\small \@Symphony No.5 As Gen Z, I couldn't agree more. You see, I have very moderate beliefs, if anything I am more of a moderate libertarian than anything. Look, I don't care if you are a Millennial or Genz, Liberal or Conservative, if you have \textbf{common} sense, I can have you as a co-worker or peer/friend.I do support marriage equality, racial equality, \textbf{gender} equality, not because of being raised in a multicultural America, but that is important to me. Think about how Baby Boomers in the Civil Rights movement made it possible to even change the same things we fight for today.\normalsize   & \cellcolor{green!5}Common, Gender & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@TacoMasters 2049 Arrogant for expressing an idea. Right.Listen, I don't mind if you're a liberal Gen Z, whether classical or freshly brainwashed. I can say what I want, just like you do. Gen Z's becoming conservative is a NATURAL progression. If you don't see that, you clearly don't understand the dinamics of societal thinking. The occational sparks of \textbf{racism}, \textbf{homophobia} and \textbf{sexism} amongst younger people are just reactionary. The true colours of neo-conservatism are yet to come out. To you, at least.\normalsize   & \cellcolor{green!27}Homophobia, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - General & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small Gen Z here, and lmao y'all are \textbf{dumb}. You all just fell for the Anti-SJW 'skeptic' trap. Stop relying on stupid 'centrist' YouTubers, Ben Shapiro and Peterson (Conservative Jesus). The left isn't evil.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@\textbf{abc} alqadiri not when thw person has had to deal with the same liberal propaganda for years\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Once a lot of Gen Zers get voting rights things will certainly be a lot better. They won't make the same mistake of voting for crap like Donald Trump and \textbf{Brexit}. Gen Z is a lot more informed thanks to the internet and so are less prone on making ignorant decisions.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small spidey .s Think again. \textbf{Nationalism} is on the rise, and Gen Z is the most conservative generation since WW2\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small You would rather have some bureaucrat in Belgium that dictates what the rules are enforced in your country then have the choice to pick your own, the problem with \textbf{Brexit} are bad leaders. The EU have a lot more to lose without the UK then the EU. Picking between Trump and Hillary isn't much of a choice. Hillary wanted to plant boots on the ground in Syria to put a no fly zone where the Russians are operating. What that would mean is war with a Russia... so picking Trump might have been a better deal and he doesn't give a crap about PC culture which is nice but fucks up the environment which is bad.\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/116 & \cellcolor{green!5}0.862 \\  \hline
  \cellcolor{green!27}\small Nationalism IS rising though, and is a factor in Brexit\normalsize   & \cellcolor{green!27}Brexit, Nationalism & \cellcolor{green!27}Nationality - European or anti-Europeans, Nationality - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Stevie is Generic Yeah most people my \textbf{age}, including me, would agree with what you just said.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I'll also be \textbf{old} enough to vote in 2 years. And I plan to vote for more conservative/libertarian parties (Given that I support their manifestos obviously), come try and stop me buddy.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small spidey .s \textbf{Nationalism} in the youth is rising. Marine Le Pen was the most popular president among the youth in the last election. Most Eastern European youth are for nationalist parties even insane nationalist ones. Youth support for AFD is huge and rising and the Swedish Democrats are more popular among young people than elders. I don't know about America since I do not live there but in Europe the youth are becoming nationalists.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small Gourab Kundu ||| And why are people talking about this like it's a good thing? If history means anything, it's shown that \textbf{nationalism} is always a bad thing. I guess some people are not only stupid, but proud of it and brag about it.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Adrian  Roth History has overwhelmingly shown \textbf{nationalism} is good. \textbf{Nationalism} has gone far with the Armenian genocide and the Holocaust but \textbf{nationalism} ended imperialism. Every single \textbf{African} country, India Pakistan and Bangladesh, Southeast Asia, and many more ended foreign rule thru them embracing \textbf{nationalism}. \textbf{Nationalism} gives identity and purpose.\normalsize   & \cellcolor{green!5}African, Nationalism & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}5/49 & \cellcolor{green!5}10.204 \\  \hline
  \cellcolor{green!27}\small Almost every atrocity in the 20th century was a result of \textbf{nationalism}. I guess history will have to repeat itself before people understand. Also, if the best example you can possibly give for something is fucking Pakistan, you should probably consider it isn't so great.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Adrian  Roth Really? Are gonna forget about Holodomor where the Soviets were trying to suppress Ukrainian \textbf{nationalism} by killing almost 7 million of them? Literally every country ever impacted by imperialism ended it with \textbf{nationalism} like in every \textbf{African} country. \textbf{Nationalism} gives identity and that gives purpose. What about the Native Americans who developed enough \textbf{nationalism} to get at least some land? Filipinos were suppressed there \textbf{nationalism} by the US due to them not wanting US control. Communists and Socialists both against \textbf{nationalism} killed way more people than \textbf{nationalism} ever did. For example, GULAGs killed about 3 million. The cultural revolution killed up to 3 million with about 100 million suffering. Great Leap Forward killed about 45 million.\normalsize   & \cellcolor{green!5}African, Nationalism & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}8/118 & \cellcolor{green!5}6.78 \\  \hline
  \cellcolor{green!27}\small acar1994 your r \textbf{dumb}...please do some research on how generations studies make connections and draw conclusions before you say another nonsensical statement ðŸ˜‚\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small they are different because people born in 95 could have given birth to someone in 2012, had to only be 17 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Yeah because people who are born in 1980 and 1994 have so much in \textbf{common}.....\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small This could be your advertisement! Not really. The most important thing about generations is technological advancement and world events within a certain time period and how your affected. Like i was 7 years \textbf{old} during 9/11 so i am \textbf{old} enough to remember where i was when it happened but i didnt comprehend it until years later. In 2 years the first kids who were born after 9/11, to whom it is only history they learned about, are gonna be turning 18 and becoming productive members of society. For Millennials 9/11 was a big historical event and had i just been a year younger i probably wouldnt have even been \textbf{old} enough to accurately remember where i was during 9/11. My 2nd grade classroom. The teacher had the lights off and the news on. We spent the day watching the twin towers falling on repeat. A couple kids were crying but i didnt really know what was happening. I dont think any of us did. All we knew was it wasnt good.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/172 & \cellcolor{green!5}1.744 \\  \hline
  \cellcolor{green!27}\small Alex Aguilar since technology and world events are what defines generations i believe after iGen every generation will begin getting shorter and shorter, imagine the kids growing up today who have been using tablets since birth. My 5 year \textbf{old} niece has had a tablet for years. Its stocked with educational games and she is at a 7 year \textbf{old} level intellectually. She was part of a study on child development at UC Merced where they measured her \textbf{mental} level.\normalsize   & \cellcolor{green!27}Mental, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/80 & \cellcolor{green!27}3.75 \\  \hline
  \cellcolor{green!5}\small I agree I was almost starting high school in 2012, It's \textbf{crazy} to think that the people who were born in 2012 are in my generation.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Thank you I'm glad I'm not the only one who takes this into serious consideration kids born in even 2010 have started using the internet as soon as the leave the womb. I had my first smartphone at \textbf{age} 14 with parental restrictions put on it. Lack of discipline these younger kids' parents provide is a painful issue too\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Exactly! I was born 1997 and my sister was born 2007 - and we're completely different people. Her digital and tech use is different from mine, and her netizen exposure at her \textbf{age} is different from my younger days online.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small This video is total BS. First of all, historians are the main people who define which group of people is a "generation," and they can't do that until a generation has pretty much lived their lives, e.g. around retirement \textbf{age}. ðŸ¤¦ Second, a new generation needs to be birthed by the preceding generation. For example, the Baby Boomers are children of the Silent Generation. We can't call people born in 1995 and after as generation Z because most Millennials were in elementary school in 1995!!!! ðŸ‘€\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Alright, yeah I was born when the Internet existed but everything changed after 2005 it seems. My childhood is much different from those born after 2005. I can see it with my own eyes. We were not centered around technology as kids, these kids are always on their technological devices. Life was different for us. Even the cartoons we watched, it's like everything has changed. Either 1995-2005 is a short generation of its own, or Generation Z itself has two different stages. In addition, both of my parents are Generation X. There is a flaw in the Generation timeline. I usually put those born before 2005 in the late Millenial stage. Though our experiences are still different from other Millenials, its closer to them than Generation Z. Comparing someone born in 1989 to someone born in 1999, there are noticable differences, but not that much. However, someone born in 1999 and someone born in 2009 have a much bigger gap. Significant differences where you can tell they aren't from the same generation. Therefor I go back to my original statement. Either 1995-2005 is another generation its own, or its some sort of \textbf{transition} stage between Millenials and Generation Z (which basically would make it another short generation).\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/207 & \cellcolor{green!5}0.483 \\  \hline
  \cellcolor{green!27}\small i think 98-08 should be genZ BUT we should subdivide it into 98-04 and 05-08 since during the 2000s there was so much new technology that was created as well as \textbf{old} technology that became mainstream.  I think that the defining characteristic of early genZ would be remembering the world before smartphones and tablets took over.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Di Vepets every generation will be getting shorter after iGen because technological advancement is a key determinant in generations. Its about how a certain \textbf{age} group grew up and live.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Di Vepets but i see 2008 as more the turning point. The next generation will be the Touchscreen Generation or some shit. The ones, like my 5 year \textbf{old} niece, who have been using smart devices since birth.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Definitely! I was born in 2001 but my childhood wasn't centred around technology at all, I got my first phone at \textbf{age} 10 and it was a flip phone\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small oh yeah i'd definitely class 95-04 as a separate generation. i was born in 02 and not be one of those "bAcK iN mY dAy" arseholes but i certainly remember the \textbf{transition} over to a technology based childhood. i remember going out with my friends and playing football in the road, but i also remember being connected through club penguin at first (lol), kik later and soon instagram. it's only natural that generations begin to break down into smaller ones as time goes on, considering the speed of reality these days. society has evolved so much quicker than it has in the past few centuries in the last few decades alone, and every new child is born into a slightly different reality. okay im waffling now lol but i'm sure you get the point.\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small I totally agree! I was born in 2002 and I can not relate to the kids born in 2005/2008 and afterwards. When I grew up I played with toys. All I see now is kids with their own ipads. I call them them the Ipad generation, at the \textbf{age} of two their parents gave them an ipad to keep them shut so that they themself can take photos for their instagram. While kids born before 05 had to use their imagination to keep them entertained and discover the world and people around them. It is sad to see.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small Diversity is code for \textbf{ethnic} cleansing.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Jon Vance like you'd fucking have a problem with \textbf{ethnic} cleansing...\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small abc alqadiri Still true tho\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Jon Vance I'm white and proud of being white but \textbf{ethnic} cleansing is a conspiracy theory\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small jon vance, how \textbf{old} are you? someday, you will realize, it doesnt matter what color you are, everyone is different, and the same person with the same color as you, can be an enemy to you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Blu implying that \textbf{race} is only skin deep\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small abc alqadiri Diversity does not mean anything and if it's so great why are the most diverse places in America the most violent and economically struggling places? Diversity is another word for less white people\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Do you have any sources? Running quick research, the most violent places in America are not diverse and usually have a minority population such as all \textbf{black} or all mexican. And diversity is code for less white people because that's the majority... Diversity is all about downsizing an overwhelming majority; if China campaigned for diversity, it would be code for "less chinese people" too. It doesn't mean any white people will die, it just means the percents will change..\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small BoolNRelaz In America, when people say diversity it is less white people. People were calling \textbf{black} panther so diverse when it was just \textbf{black} people. As for the most diverse places in America being violent here u go  [LINK] \normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small abc alqadiri diversity isn't bad or good, its just a thing that may happen.\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small You people who don't know why \textbf{black} people are struggling should really take a history course, it wasn't that long ago...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Its kinda \textbf{weird} that we are all grouped in gens like in Pokemon ðŸ˜„ðŸ˜(ima a igen/gen Z btw)\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small hello! ! we live in a shitty pc world where i am no longer allowed to make asian jokes \textbf{black} jokes white jokes or mexican jokes call me \textbf{racist} but Issa joke and i don't care about people's feelings im also a part of gen z but i oppose government, \textbf{g\textbf{ay}} marriage, transgenders (it not he or she), and all sjws i believe that gen z should know what's its like to actually live im hard times and besides recession is barely affecting us but you know what will that 23 trillion dollar debt we need to pay ohhhhweeee can't wait for the great collapse i got my Ar-15 and my wather ppk on me also im loaded with enough food and water enough to fund a fallout settlement (fallout 4 sucked btw and its was all prestons fault)\normalsize   & \cellcolor{green!27}Black, Gay, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/139 & \cellcolor{green!27}2.878 \\  \hline
  \cellcolor{green!5}\small \@cristina uh no it's not \textbf{racism} it's stereotype\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@cristina Lol nah, ya are the " find \textbf{racism} in everything " generation.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Skip. \textbf{Nothing} new or interesting\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Millenials are basically the \textbf{transition} generation. Society had a confused direction for a generation, and millenials bore the brunt of that. Once the smoke clears Gen Z and their successors will have a clearer technology/innovation led pathway which will be focused more on constant change, and being used to that constant state of flux.\normalsize   & \cellcolor{green!27}Transition & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Look at your username, how are we even meant to believe you've reached \textbf{age} 12?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small School shootings have been \textbf{common} for a long time and at least we aren't serial killers.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small ARE U \textbf{CRAZY}!?! WE DON'T COMPARE WE ACTUALLY DO IT. Look at me!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small abc alqadiri What you don't understand is that the older you get you tend to lean more conservative (or just more right wing in general). Usually looking at young generations they are always leftists for the overwhelming majority, this is a very special generation where in the very beginning it is very evenly split (compared to the past generations) meaning that when my generation becomes older it will be extremely conservative. This should scare you, I know it scares me.\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small Edgy Cats 69 not really. A kid might develop their personality but it's not going to be the same when they reach their \textbf{senior} year of high school. And are you in middle school right now? how can you possibly think middle schoolers back in 2008 were tolerable than â€˜18 kids.\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Blaming young people for the failures of the \textbf{old} seems almost cyclic in humans. Hopefully I won't also be an asshole to the younger generation when I get older.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Actually i think the opposite. My classmates are lazy and seem like if they didn't know too much, but i think they are like that because they know all the bullshit we are going to go through when we grow up, so it is like if they were spending the few time they have before reaching adulthood (in two years) for making lazy, \textbf{dumb} stuff\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small relateableoldman ðŸ‘´ðŸ» i live in a white majority neighborhood and theyre still \textbf{crazy} here. It doesnt matter what \textbf{race} they are, theyre all \textbf{crazy} lmaoo\normalsize   & \cellcolor{green!27}Crazy, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/25 & \cellcolor{green!27}12.0 \\  \hline
  \cellcolor{green!5}\small I still feel like Millennial's should of ended around 2002. There is a big gap between my \textbf{age} group and the next few down in terms of about everything. The fact that me and my peers are classified as them disgust me, as we are \textbf{nothing} like them. Are we in the digital \textbf{age}? Yes. Are we somewhat similar to the peeps 2 years under us? Absolutely not.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}3/68 & \cellcolor{green!5}4.412 \\  \hline
  \cellcolor{green!27}\small Was born in 95, didn't log onto the internet until the \textbf{age} of 11, meaning I knew of a world without an internet. I've had nokia brick phones and flip phones, not just smart phones. Please bump GenZ to 99.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small i was also born in 2001... my parents had an \textbf{old} computer for a few years, but i didn't use the internet at all until i was 11 or so.  I got my first cellphone a year ago.  I knew what it was like without internet, and i sometimes i wish i could go back to that :)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small I was born in 2000, I remember my childhood that we had that big tv, not a flat one until like 2012. My phone was Nokia 1100 when I was 7-10. Later I got a flip phone and in 2013 I got my first smart phone. I remember being absolutely in shock when I saw a laptop irl in 2007-2008. At home we had \textbf{old} Windows computers (95 and 98). Also touch screen was a completely new to me when my brother got his first smart phone in 2012.   We used VHS tapes and cassettes. Also CDs were a big thing. And MP3 players! Everyone wanted those in middle school. I don't see myself as Gen Z, internet became part of my life in 2009-2010 and my childhood was pretty much the same for my brother who was born in -98\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/141 & \cellcolor{green!27}0.709 \\  \hline
  \cellcolor{green!5}\small Orla Thorburn i dont think as far as 2004 should be a separate generation, i was born in 2004 and grew up with the internett and at \textbf{age} 2 i played computer games sometimes (although i was horrible at it). But this depends on what part of the world you live in too, seeing as i am from Norway, the internett was at that time was already a part of a todlers life at that point (2004)\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small I also has a flip phone at \textbf{age} 6, but that was very young for even a Norwegian child, most people born in 2004 got their first phone around \textbf{age} 9\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Tony Ravioli i was born in 2000, I believe the childhood between the \textbf{age} your talking about and mid to late 90s kids is very minimal, the biggest difference exists more in the teenage years because social media became such a thing. Personally I believe that kids my \textbf{age} and others born early 2000s have more in \textbf{common} with mid and late 90s kids then late 2000s kids and early 2010s kids\normalsize   & \cellcolor{green!5}Age, Common & \cellcolor{green!5}Age - General, Social Class - Working class & \cellcolor{green!5}3/72 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small The actual demarcation line is 1995 because that's the year the internet became commercialized... The first computer my family owned was when my father was in his late teens - early 20's (I obviously didn't get to see this and there was no internet access yet)... I was born when he was 31 years \textbf{old} in 1995, I wasn't allowed to use the family computer until much later but I had internet access at school when I was in 1st grade back in 2002, though there's not much to see... We had Yahoo and Friendster accounts (some of the earlier forms of social media).\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/104 & \cellcolor{green!27}0.962 \\  \hline
  \cellcolor{green!5}\small personally, i define gen z as whoever was too young to remember 9/11... i think that represents more of a before/after, at least in america than Â¨the commercialization of the internetÂ¨ iÂ´m 2002 also, and i remember my early life was wayyyy different than how my 9 and 7 year \textbf{old} siblingÂ´s life is. they are totally reliant on technology, they donÂ´t know how to play/relax otherwise.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small A lot of 11 year \textbf{old} now may not have used a computer yet as well does that mean they're a millennial? your logic doesn't make sense.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small 1994-2000 is like a \textbf{transition} phase between the two generations, those kids can relate to things from both.Just like the Xennials who were  born between 1977-1983... In between gen X and millenials.It's real so let's make the Zennials real !!!!\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I was born 2005 and I always had some type of Internet access from a young \textbf{age}. My first experience with Internet, was when I was 3 ish, and it was flip phones, then when I was 5 or 6 years \textbf{old} I used to use my dad's iPhone, then at 7 I got my first tablet, then lastly at 11 I got my first phone. I think the definition for genz is just a generalization of the majority.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small Well I am 00 and we got our first pc in 07 with very restricted access for me. My first phone was not a smartphone. I remember the day a kid in my group of mates was the first to get a smartphone. It was truly something special and we would play games in that thing and pass the phone arround so everybody could try it. It always reminds me of some stone \textbf{age} savages who just discovered fire the first time lol\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small Thezebraherd probably because we are now \textbf{old} enough to understand and so the millenials get to hate on the next down, to add to this, they care about us now because people are starting to vote now\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Lara Snows ugly comments. Millennial don't want a generation to hate on. All these labels just divide us up and it's so stupid. These generation labels mean \textbf{nothing}. I have friends of all ages. You guys are doing a huge disservice to the world if you continue to divide people up with meaningless labels.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small This little "argument" if you can even call it an argument is \textbf{dumb}..... No Generation is the best, no one perfect, and i honestly Think stuff like this drags the word humanity into the mud....And i'm sick and tired of pointless child like arguments that are happening around the world.......\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Miggerz by doing so you've proven my point that you Fucktards are pro Government wanting more Government Regulations than your Millennial Predecessors. You \textbf{fat} fucking little chunky Gen Z Shits will learn the hard way when you give up basic Freedoms for "protection. Your Parents pampered you so much you think the World is a Disneyland type of Place thinking your Sky Daddy will come back to protect you from the big bad Government. BTW I knew what Memes were since you were in Diapers you stupid little shit so nice try.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small Anthem Uu Where do you live in a \textbf{R\textbf{ed}} State? Because Blue States are more populated than \textbf{R\textbf{ed}} States and I could tell you the majority of Gen Z Kids I've seen here are anything but Conservative in California and Blue States in general. Plus Gen Z will have less Whites (Which will be divided as many Whites are Liberals) and a bigger Minority Population than my Generation (Which generally lean more Left) so Gen Z will be worse.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/79 & \cellcolor{green!27}5.063 \\  \hline
  \cellcolor{green!5}\small I don't eat tide pods or any of that other crap, I'm not smartphone obsessed, and all I want is a change in gun laws. I'd rather some \textbf{crazy} idiot be without a gun than some kid dead in a school.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I call you a troll, because i'm trying to be the "bigger person"(Adult) and not argue with you since how toxic you are.... literally this is why i hate today life, people are divided up into stupid arguments that doesn't help progress the human races..... so if you think your "so" better then me then you should have say \textbf{nothing} and keep this to yourself.... and I do have an argument but you seem to "barbaric" to even have a damn civil conversation...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small Roman Parisian lmao a couple of people ate tidepods here come the \textbf{old} people generalizing everything.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@I TOLD YOU NOT TO TOUCH IT! How are we the most conservative gen when we're the least \textbf{racist} and least \textbf{homophobic} gen ever ?\normalsize   & \cellcolor{green!27}Homophobic, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small +AvokadoKiniGen is just what \textbf{old} farts call us. We're Homelanders. Very few of us would even consider using \textbf{Apple}. Nokia is better than \textbf{Apple}.\normalsize   & \cellcolor{green!5}Apple, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}3/25 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small As a genZer myself I can't say we are the most realistic of any generation. Others were influenced by the media but because of social media we can see the raw events and naturals become more conservative libertarian because it's \textbf{common} sense. We are driven even further to the right because the PC culture is being shoved down our throats in school and everywhere we are.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small a capitalist socialism is the best form of government. not \textbf{communist} or socialist, a lot of the scandinavian countries use it and they have the best quality of life and are very succesful.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small The mistake in applying Scandinavian results to the US is that they are \textbf{nothing} alike. US has a much bigger economy (1 in the world actually) and a much bigger population. Welfare Capitalism (which is what you are referring to when you say "capitalist socialism") doesn't work nearly as well once you get to countries that are superpower-level. Ideologies like Socialism, Communism, and Anarchy work fine within small, tightly knit communities. But once you get to a worldwide scale they become far more detrimental. This is evident by the fact that the US is currently using (and has been using for some time) a Welfare Capitalist foundation, and the consequences of implementing this foundation can be seen everywhere.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small Computers are super beneficial if it's not used in excess, but it's very easy to use them too much. A few days in front of the screen without going outdoors in good weather and I go crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Neon Rose It just mean your Gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small Gen Z BOIS: "There was a shooting in Florida, the officer who was armed did \textbf{nothing} and let those kids die, Nicholas Cruz is the confirmed shooter. Some conspiracies say that it was set up by the government because some teachers and students said that he was dressed in military gear but he was seen during the shooting dazed and confused in normal clothes. The shooting ended 20 minutes ago"Gen Z BOIS getting a tide pod from the fridge later that nightGen Z parents: "OMG did you hear about that shooting in Florida"Gen Z BOIS thoughts: "I hope I get killed in a school shooting. WAIT nvm lmao I can't make money and juul if I get killed lmao maybe when I get \textbf{old} someone will shoot up the nursing home when I've got \textbf{nothing} else to live for."Gen Z BOIS actual response: "Yeah my thoughts and prayers go out to them"Gen Z BOIS thoughts on the way back to their rooms: "Where we landing BOIS" Hits Juul\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/173 & \cellcolor{green!5}1.734 \\  \hline
  \cellcolor{green!27}\small why is that \textbf{old} \textbf{woman} talking about Gen Z's?? She doesn't seem to have a Gen Z daughter or son so really her views on it dont matter.\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small (Entitled Millenial) I love that saying because unlike the generation before us we receive \textbf{nothing}. We have no long term job security and the value of the same degree earned has dropped or become invaluable. We see jobs continuously contracting out to hire 3rd parties. There used to be pensions with jobs to ensure a good 401k plan and products were cheaper.Not to mention as a country we have debt being passed on to us from those who call us these names now of 21 trillion dollars. So when people say these things (entitled millennial) they're not backed up by any facts or logic and never explained so feel free to try. By the way no one cares if generation z has made some products every generation does it's part of growing up.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/134 & \cellcolor{green!5}0.746 \\  \hline
  \cellcolor{green!27}\small Okay, but heres the thing. In this whole reply section, no one has ONCE brought up the millennial job crisis. Why are you bringing it up? You suddenly got defensive, and totally forgot the context of the conversation. Also "By the way no one cares if generation z has made some products every generation does it's part of growing up.". Your english comprehension is HORRIBLE. That is NOT what it means. It means that GenZ has the tools, and currently are using them, to be entrepreneurial in a way no other generation has, and that they are ALREADY proving this prediction. They are selling products, as in an item, themselves, films, or etc, at a very young \textbf{age} in a successful matter that influences the social media landscape or etc. Are you jealous? No one is discounting Millennials here. Gtfo if you cant have a constructive argument.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/148 & \cellcolor{green!27}0.676 \\  \hline
  \cellcolor{green!5}\small Dude please don't mix being smart with learning things off of the internet. I mean think of a farmer in the 1800s you might think hey this guys \textbf{dumb}, I have the internet. But that guy has to learn farming techniques which take math and patience.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Dude, I'm gen z. I have \textbf{nothing} against you being an atheist. But I'm Jewish, and it is part of my life. I don't really believe a lot of the Torah but I love being part of a culture, singing songs. Forgetting religion is forgetting a beauty. I recommend you take time to visit a small church, temple, or mosque and experience that kind of thing first hand.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small GINNVNGAGAP Good points, but as it has had a negative impact on history it has had a positive one as well. Religion is good at least individually, Religion encourages good selfless acts like charity, and it gives people something to believe in and fills them with hope. Science and Religion do not have to disagree and I think they usually don't, the Big Bang theory was created by a catholic priest something many are unaware of. Religion should be allowed to continue for these reasons, but of course you are allowed to believe in whatever you want be it a spaghetti \textbf{alien} or absolutely \textbf{nothing} is fine with me.\normalsize   & \cellcolor{green!5}Alien, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small Roman Parisian You used the past as an example, are we living in medieval times? Where people could use religion to justify their atrocities? Religion through all it's flaws had a concrete basis, atheism never did, no such thing as a true secular country. You're naive, religion gave us more morals and humility than atheism every could, you owe religion quite a lot you know.Society is already established full of free thinkers, who take advantage of religion's progressiveness in society. Religion made you think outside the box, even though people did that long before you did. It's the 21st century and \textbf{nobody} can use religion as the reason why we have conflict. We all know the reasons why, people are capable of vile things..People are responsible for the corruption, religion originally was used to bring order and rightfully so. People need control on their lives...\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/147 & \cellcolor{green!27}0.68 \\  \hline
  \cellcolor{green!5}\small Joey Cash Cotter and Pepin "Trending towards traditionalism: Changes in youth \textbf{gender} ideology" (2017) for example. You might not be familiar with the social science on the issue, but there have been several prominent papers published on this very topic within the last year, year and half.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Religious people are so funny and \textbf{dumb} in trying to defend their ideas...it's like watching a boat that's sinking and the people inside thinking it's notðŸ˜‚, I love being an atheist, and I love the fact that Gen Z will finally cut and maybe even to some extent stop and erradicate all the religious nonsense some random people have been brought up to believe ðŸ˜‚ðŸ˜‚ðŸ™ŒðŸ½ðŸ¤˜ðŸ½\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Isabella Let me tell you what atheism caused. It caused the world's biggest massacre in human history in thr 20th with horrendous campaigns on the likes of Hitler, Stalin with a godless, \textbf{communist} regime, Mao Zong murdering millions under his \textbf{communist} Chinese regime, which still suffers from the effectd today.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small GINNVNGAGAP the crusades were a response to stop invading Muslims, and besides, they are just using religion as an exude, thwy would attack regardless.Religion created the greatest \textbf{nation} in the world with its values and morals\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small My Name Is No!! Never caused anyone any problems? Why dont you ask the millions the Christians persecuted, tortured and killed if religion caused anyone any problems. How about you check on those who died in 9/11 and ask if they feel religion caused them any problems today? Science flies man into space, religion flies man into buildings. Your God is a reflection of yourself projected. We are becoming increasingly self aware as a species and realize that now. Man wasnt made in Gods image. He was made in ours. Thats why the same flaws humans have, God has. God as depicted in the Bible is, in the words of Richard Dawkins, "Jealous and proud of it; a petty, unjust, unforgiving control-freak; a vindictive, bloodthirsty \textbf{ethnic} cleanser; a misogynistic, \textbf{homophobic}, \textbf{racist}, infanticidal, genocidal, filicidal, pestilential, megalomaniacal, sadomasochistic, capriciously malevolent bully."\normalsize   & \cellcolor{green!5}Ethnic, Homophobic, Racist & \cellcolor{green!5}Ethnicity - General, Sexual Identity - General & \cellcolor{green!5}3/140 & \cellcolor{green!5}2.143 \\  \hline
  \cellcolor{green!27}\small Captain America what? America was founded on a combination of Graeco-Roman Democratic Republic ideals, secular Enlightenment Era and \textbf{Age} of Reason ideals and the Iriquois Confederacy.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Captain America the Treaty of Tripoli, signed and ratified by the Unites States Congress in 1797, states that America is not a Christian \textbf{nation}."ARTICLE 11.As the government of the United States of America is not in any sense founded on the Christian Religion,-as it has in itself no character of enmity against the laws, religion or tranquility of Musselmen,-and as the said States never have entered into any war or act of hostility against any Mehomitan \textbf{nation}, it is declared by the parties that no pretext arising from religious opinions shall ever produce an interruption of the harmony existing between the two countries." [LINK] \normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/106 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small EnternalEntropy internet natives sounds lame\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small how about The Dab Nation\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Sean Huesman 1) Not every phone is made by \textbf{Apple}.2) Do you really think that every single person in this generation has one? Remember that this name is supposed to represent the entire generation, not just those individuals in developed countries where everyone can afford a smartphone.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small +0doublezero0Millenials in this case doesn't mean born in the 2000s, but those coming of \textbf{age} around the 2000s. I think the main reason Baby Boomers bully you for it is because you remind them too much of their Hippie past. You tend to act almost as batshit \textbf{crazy} as they did, only for stupider reasons like microagressions. Just like you are all about Peace and Love, as the hippies, the Homelander gen will be more Millitant and Self Reliant. I hope my generation do not fall for the lies of (((Them)) just as easily as you did, you even ridiculed those questioning the governing system as conspiracy theorists. You protest (((Their))) wars, but blame the "white men" who die in the wars, instead of blaming the ones who earn Trillions on them. And you still wonder why you're a laughing stock...\normalsize   & \cellcolor{green!5}Age, Crazy & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/142 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small No its more like they blame us for the crap the Gen Xers did.  Cause I got that stuff since I was in middle school (I was one of the early 80s born).  Meaning that we were blamed for stuff even before we got into the working world.   And the whole hippie generation we were blame for was actually caused by the younger baby boomers themselves (got that from my high school baby boomer born teacher).  Of course, we were a whiny generation, I agree, but I call BS in that we didn't work as hard as other generations before. Your last sentence makes \textbf{zero} sense.  We fell for their lies because those lies were true for them.  Back in the day jobs did value their employees and they retain them.  However, now a days they don't invest in their employees and want to save their dollars by downsizing.  And having an education does mean you will get a job like you did back them.  Yet they don't take the time to update their brains to this knowledge.  All the debt that the country has accumulated was thanks to the baby boomer generation not wanting to boost the future generation up like the silent generation and the generation before that did.  I have been paying for THEIR social security when I was previously working, but of course I will never get that social security when I retire.  Yet Gen Z, assuming its your generation, will most likely be lucky in that you won't be paying into a system that won't be their anymore.  Gen Y hasn't done jack to Gen Z, and Gen Z's university tuition problem isn't our fault its the baby boomers.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/284 & \cellcolor{green!27}0.352 \\  \hline
  \cellcolor{green!5}\small Centennials - this name is great because it sounds like sentinels and it suits the role of this generation perfectly - make sure the 21st century is not the \textbf{age} of fascism and communism even though everything is leading to it.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small madcapromanian all generations are important, sorry for commenting on a few month \textbf{old} comment. The Greatest Generation formed America through wars and hard work. The generations that followed brought ideas that changed views such as political or social. Us Gen Z, or Internet Natives, are currently very young but that doesn't mean we can bring good ideas. Most of us will possibly be entrepreneurs, making ideas.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small abc alqadiri And You can explain why Trump won ? Hey you agree US embassy should be in Jerusalem right ? Israelis have right to Homeland and Muslim countries in Middle East hate gays and don't believe in women's rights\normalsize   & \cellcolor{green!5}ABC & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Millenials are now parents and will be for quite some time. They are going to raise their kids in a ridiculous pc culture-esque \textbf{gender} neutral crap. Worst of all we as a gen z will be wedged in between the two generations. We are going to have to make sure out influence is strong on the next generation just like how the millennials are all over social media. Hopefully from their we can create a strong, sustainable society.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Yes, we are the new defenders of or culture against the army of blue haired beluga whale \textbf{lesbian} feminists\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small milats13 â€¢ People like milats are the pc people. They bring about a boring, \textbf{dumb}, annoying effect on culture, that us delightful gen z memers have been counteracting recently. Our job as gen z is to influence people not to be like them, but like us instead, as I've noticed we're a very realistic, futuristic, entrepreneurial, creative, fiscally conservative generation with potential to change the world and fix what the baby boomers and millennials did. Hopefully the alpha generation will learn from us instead of being like millennials.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small Daniel Gomez   I am Gen Z but I go to a very progressive school. We shouldn't teach Generstion Alpha do become the stupid, intolerant, hateful assholes that people were a hundred yeard ago. We should be teaching them about equality and progress. About going forward and not going back to the thoughts from decades ago. I don't give a shit about 'conservative or liberal'. All that matters is that we don't hate others and that we don't teach others to hate. And Baby Boomers and Millenials didn't ruin anything. Without them and their inventions we would have \textbf{nothing}. Each generation brings good and bad things. You could say that Gen Z are dukb and have the attention span of a \textbf{fruit} fly, or you could say they are resourceful, independent, young multitaskers who will change the world. And that goes for all generations.\normalsize   & \cellcolor{green!5}Fruit, Nothing & \cellcolor{green!5}Age - Youngsters, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/143 & \cellcolor{green!5}1.399 \\  \hline
  \cellcolor{green!27}\small milats13 â€¢ Ur mom gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Enforcer 88 No but ur mom is \textbf{g\textbf{ay}} lol\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Daniel Gomez  I'm sorry, is that supposed to offend me? I go to an extremely liberal school in a really liberal city. My best friend is \textbf{transgender}, my other best friend is bisexual. You're comment bothers me as much as if you said 'Ur mom straight'. Also it's 'You're mom is gay'. At least try with the grammar.\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small milats13 â€¢ No it's just a meme, stupid. Bad grammar is part of the meme. If you were cultured you would know. It's not serious at all lol. Smh people like you are so dull are you sure you're not a millennial?And it's not "You're mom is \textbf{g\textbf{ay}}." You are mom is \textbf{g\textbf{ay}}? It would be "Your mom is \textbf{g\textbf{ay}}", \textbf{dumb} try-hard.  Smh doesn't know memes, can't even correct grammar properly. Do better. This is embarrassing.\normalsize   & \cellcolor{green!5}Dumb, Gay & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}7/77 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Your best friends should be shoved in the nearest \textbf{oven}.\normalsize   & \cellcolor{green!27}Oven & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small milats13 â€¢ You make a smart, thoughtful comment like you did, and then the only thing people can say is 'ur \textbf{g\textbf{ay}}.' Honestly, the people on this thread calling themselves conservatives sound \textbf{dumb} as shit, and I hope you all know that as a Gen Y kid, I'm going to do everything in my power to keep your ideas from being prevalent in the future. Keep your outdated bullshit in the 20th century, because I'll fight you before I let it touch the future.\normalsize   & \cellcolor{green!5}Dumb, Gay & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/84 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small First of all, Left wing Millennials in general tend to promote this unhealthy idea of "whoring" around due to the \textbf{sexual} liberation idea of the 3rd wave feminism. The feminizing of men and "machoing" of females will only deteriorate society since biologically, men tend to seek for young looking women (more fertile) and so, because of the multiplicity of partners and postponed marriage without settling down, the majority of Millennials today will find themselves "lonely" after their peak years pass away without a partner. Females tend to look for men who are confident due to the illusion that confidence correlates with power (better chance for protecting and providing for their children). So females tend to look for partners whom they think will be strong enough to raise their children. The feminization of males will only make men less "attractive" to females, thus reducing the number of successful relationships in the present. In addition, due to the late "waiting" of marriage and the probability of a female having already experienced multiple partners, the bonding effect caused by the release of chemicals after intercourse is severely reduced, making them less susceptible to successfully attract and keep men  more often. In addition, the loss of production of testosterone in males due to the lack of physical activities (excersising increases the production of testosterone) will only make them more unattractive for females and lose pheromones to attract females. In other words, there will be a lack of children in the future which means less revenue in taxes to pay for social programs such as welfare (especially since more people will be retiring without dying, and thus there will be a lack of money to pay for the pensions and social security for these people). Underpopulation will be a severe crisis in the future in 1st world countries. Some people say that overpopulation is a problem... which indeed it is... in 3rd world countries, not in 1st world countries. So by not having children, these people in 1st world countries will eventually bring the demise of the US, Europe, and Asian countries (just look at Japan) while the nations with the most population will govern the world in politics, such as the Middle Eastern countries - Muslim nations - and India as well as other non-feminized men/non-machoed females nations. This defeats the whole purpose of progressive movement since those countries which will take the lead in the world tend to oppress minorities and hated opponents, such as in the Middle East (where rape is legal). Of course, some say China will take the place of US so maybe it will be influenced by it more, unless, of course, China's economy is unable to recuperrate from the financial crisis they are about to experience (a future Real Estate crash in the chinese market due to the dependency on Chinese's real estate government laws).The point is that we need to act now if we want to prevent a catastrophy like this.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/495 & \cellcolor{green!27}0.202 \\  \hline
  \cellcolor{green!5}\small I admit, I over exaggerated the economic downfall of the world etc., but the unhealthy consequences done by today's "progressive" movement (I personally call it regressive) is a real problem. For example, due to them, they have achieved the reduction of time of "recess" in schools since they claim it is benefitial (more time in school) but it has been proven that recess time is actually very healthy for males since it gives them an opportunity to do physical activities and increase their production of testosterone in a healthy manner. Also, this helps "control" the children with ADHD more since it gives them a chance of exhausting that energy in playtime. Making them "sit" down for hours without breaks actually makes their symptoms worse. Females, on the other hand, are encouraged recently by modern way feminists to pursue powerful activities and "demonize" any past female activities since according to them it only "oppresses" them. They discourage them from accepting \textbf{common} courtesy manners and indoctrinate them to fear men (this is an irrational fear). In fact, there was a study made which found that the main reason that females tended to avoid STEM fields even though they liked it was not due to opportunities in the field (they are encouraged actually), instead, they refused to join due to an irrational fear that they would be discriminated even though in actuality, it does not happens. When asked where did they heard these fake news (since STEM is actually very welcoming to females) they answered that they heard it from feminist propaganda. When you continuously repeat a lie, eventually, you will start to believe it, and this is just what happened in STEM. Feminist propaganda is the reason why there is a lack of females in STEM fields. Also, the "machoing" of females only increases the testosterone in females which, by the way, a high level of testosterone in females gives them a higher risk for obesity, heart disease, and diabetes, thus, in the future, my prediction is that females will begin to die off younger than in previous generations. We still do not see this since today's older generation is composed of Baby Boomers which had, at least in the development in hormones, a healthy upbringing (not psychologically of course).\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/378 & \cellcolor{green!5}0.265 \\  \hline
  \cellcolor{green!27}\small Nathaniel \textbf{Tan} the kids will rebel against the strictness, and the Progressiveness will have the opposite of the intended effect, where conservativism+Libertarianism will become more prevelant\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Nathaniel \textbf{Tan} im 26, 2018.\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Nathaniel \textbf{Tan} i think gen y and z can relate\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Nathaniel \textbf{Tan} DO NOT LABEL PEOPLE FOR STUPID REASONS not all millennial are the same, not all genz are the same, STOP FUCKING LABELING PEOPLE FOR \textbf{DUMB} REASONS\normalsize   & \cellcolor{green!5}Dumb, Tan & \cellcolor{green!5}Nationality - British, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Reyhan Ziad Right, because I need another \textbf{old} person with outdated ideas telling me how to think. Thank you for that suggestion, but I think I'll stick to not having my mind poisoned by more ignorant bigots.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small wiseguy240 Winston how? I never seen one post about gen z being against millenials. I've used the word millenial in school to find out that middle/high school gen z don't even know there's name for different generations. \textbf{Nobody} cares about the different generations as much as millenials. I stg\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Stfu, stop using that same excuse,'go outside' if you don't realize we already do go outside, you \textbf{dumb} ass. We are multi task'ers and we do everything you wish you can do. We play our games and we do everything you listed. The only problem is that you can't understand how we could do that with that small ass brain of yours. 'Go outside,' pfft! How idiotic. We would've died of diabetes a long time ago if we didn't.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small At your \textbf{age} group most people would have been digital natives in terms of their teenage years, conversely most of Gen Z haven't grown up with the internet before the iPad was invented.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small not everybody is you. litterly every single person is diffrent. we can't generlize a whole \textbf{age} group\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Sese Talitau-Tio depression doesn't always mean people with it want to kill themselves. Ive had depression since the \textbf{age} of 7 and i thought about ending my life about 3 to 4 times (im 21 now) i cant say this for everyone with depression, but i know that for me, when my depression hits i remind myself of all the good things in my life instead of focusing on the bad. But i do believe in letting myself cry it out and bc of this, i am able to maintain my own mood. When i am at work, my mind will start to randomly remind me of all the bad in my life so when that happens i start cleaning and humming a tune. To others it looks like im a perfectly happy person when in reality, im just dealing with my depression the best way i know how\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/149 & \cellcolor{green!5}0.671 \\  \hline
  \cellcolor{green!27}\small we aren't the real depressed generation. Millenials, Generation X, and the silent generation have more \textbf{mental} illnesses and suicide rates.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small krishna L rich kids depressed, poor kids depressed, we are all depressed. I think it's because of the unreal expectations put on us (my school is impossibly competitive, everyone's self medicating to deal with the stress). We are supposed to be the gen to make everything better, and yet I get told "Y'all teenagers are so self righteous. You don't have to work for anything. Entitled brats." We live in a world of contradictions. Be idealistic. Dream Big. But we see all of those ideas fail and watch our parents and our friends parents lose their jobs and such. That's why we're realistic. We are more intelligent (average SAT scores increase yearly), but are constantly being told that we are \textbf{dumb}. And we inherited a world destroyed by the mistakes of others. \textbf{Racism}, \textbf{sexism}, \textbf{homophobia}, terrorism, global warming, gun violence, political corruption, social upheaval. All of that is why we are more fluid and accepting in our beliefs . If somebody is \textbf{homophobic}, they'd be the one I'd stare at in disbelief. Recycling is a thing at my school, and we are concerned over the environment and the humanitarian crisis. My friend group consists of whites, blacks, latinos, Asians, and Indians, and all I care about are their personalities and interests. Skin color has never been a factor for my gen. My friends are girls and boys. Some girls hang out with just guys and vice versa. \textbf{Gender} isn't a thing (like literally with \textbf{transgender} people on the rise) when picking friends. For me when has terrorism not been something to be scared about? I'm just as likely to get that here in America as I am in other countries. My first concert, I prayed that what happened in Vegas or Manchester would not occur there. My point is we are depressed, but it's not totally our fault. We get bad reps, unrealistic expectations, and no support which is why I believe we are depressed, yes, but are more than anything, independent, strong, and are going to make a difference in the way the world works.\normalsize   & \cellcolor{green!5}Dumb, Gender, Homophobia, Homophobic, Racism, Sexism, Transgender & \cellcolor{green!5}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Transexuality & \cellcolor{green!5}7/346 & \cellcolor{green!5}2.023 \\  \hline
  \cellcolor{green!27}\small Gen Z is the generation that will see reality and work with it. Gen Z is set to be the most conservative generation since boomers. They know that they can make a difference and change the path of a failing \textbf{nation}. They also understand that this will require not only hard work, but a shift in "popular politics." Conservatism will have to take over once again in order for America to stay safe.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Mosin Cieblene we need more deregulation not less. I'm part of generation Z  living in one of the most regulated places in the country, Bay Area (Silicon Valley) California, and it fucking sucks. Everything is way overpriced, and much of the decisions to what risk we want to take or what we want to buy are made by some of the most privelaged arrogant people. I've had multiple moments where my phone is about to die, so I decide to pick up a newspaper while I'm waiting  for something and every fucking time their is a story about how after 10 years of construction, going through every hoop to pass all the regulation, getting the approval from multiple government officials from different agencies, using all the right material that meets the environmental standards, and spendng millions of dollars on its construction, a building which was supposed create dozens of new jobs and make things easier for the consumer or set of desperatly needed new housing complex, gets blocked because some bitchy neighbor decided that he/she doesn't like the cars on the sidewalk or shape of the buiding, so compalins to the city counsel, and just like that, contruction is put to a halt, and another 2 years are added to the time table,  and when it does finally get completed, the business will often end up leaving because prices and taxes make more too expensive  make it less expensive to sell the place than actually trying to run the business. It took one year to build the empire state building, and now it takes 4-6 years just to build a new highway. The only businesses that thrive here are the tech companies, which have almost \textbf{ZERO} REGULATIONS. Meanwhile Housing is unaffordable here, and yet the state has rejected multiple bills to raise the height most our buildings are allowed to be, limiting the housing market even as our population grows and as a result, we some of the worst homelessness problems in the \textbf{nation}. Inefficient Regulation is also the reason drugs in this country are so goddamn expensive, because it takes 10 years for a drug to pass through the FDA, making impossible for anyone except Big Pharma to fund drug testing and studies, and then they reap all of the benefits by claiming ownership and raising the prices so high that most people can't afford them, which they wouldn't be able to do if our laws allowed drugs from other countries to enter. Crony Capitalism is destroying this country!\normalsize   & \cellcolor{green!5}Nation, Zero & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/420 & \cellcolor{green!5}0.476 \\  \hline
  \cellcolor{green!27}\small Yeah but we are different from the millennial style of liberals, I can tell from talking to the older guys (and especially the women) including our very young teachers that the millennials are way more sincere and genuine about their liberal beliefs, always trying not to offend people, really believing that everyone is truly good and innocent, and thinking that all we need to do is be kind and independent and celebrate our diversity in order to make the world perfect for everyone. Generation Z is more apathetic, most of us are part of the politically correct culture only in the formal sense, I.E. we all know that the when your talking to the class, at serious work meeting with the boss, or on camera, you talk very superficially  like a person on CNN, MSNBC, or a white house official from the Obama administration, making sure to note your tolerance and utmost desire to achieve whatever the goals are of the topic they are addressing at the mandatory presentation in the school auditorium - \textbf{sexual} abuse, alchohol, suicide. But once you leave you go back to your real self, swearing and with most students altering 0 of their attitude or beliefs, not even showing any signs that we just came from a presentation on a super depressing and serious topic except for the almost amused impressions at how we had to go to this \textbf{lame} assembly being led by people who actually think that they are going to change anything instead of just being some mandatory bureaucratic event that makes us (them) feel better and cover their asses. And for a noticable amount of people, there is even some resentment that we are basically being forced by our schools into an indoctrination assembly. This goes along with our rather low expectations of our current government (and I mean government in general, not just Trump) We also don't really feel invested in the successful ideal outcome of most movements. And even though most of generation Z naturally tilts left/liberal most of us are actually pretty accepting or at least used to of not very leftward policies and trends, like we don't get shocked or emotional about school shootings unlike our parents, we actually had a false alarm a month ago where the principal said someone with a gun was in our school, and to me at least it didn't seem particularly scary or dangerous, I figured it was most likely a false alarm, and even if it wasn't the chances of my class getting picked would be very small. Or the U.S war on terror and use of drones in Pakistan, most would probably say that we shouldn't be a as jumpy to launch a drone strike, and that it could do more damage than good in the long run;,  but almost all of us seem to accept it as something that is part of life (or an end of life for some Pakistanis) which we rarely have to think about. It's not that we don't have morality, it's just that what goes on in the middle East is so far away and doesn't really effect our daily lives, so whatever happens to the life of Mohammed Ahtmu in Pakistan or one of the other countries we are bombing really isn't one of our priorities. And as for Trump, although most of udissaprove of him like the rest of the younger generations, most of us aren't seething at the mouth like Democrats, we look at his policies or statements and mostly just laugh. Even even though there is definitely a PC culture, there isn't really a feeling of being pulled into the democratic camp or Republican camp, both are pretty \textbf{lame} to most people. We don't really trust the government to be effective, or efficient, or sincere, or to be able to make our lives that much better; our interest is in the tech companies and the idea of being the CEO of a startup company and going to a prestige university. Combine this lack of faith in the government, and this individualistic entrepreneur attitude, and I've actually found that at least in my experience, most of us can agree that although Bernie Sanders is cool and definitely has conviction and good intentions, we kind of agree that his expectations are unrealistic given the trouble we have with just trying to keep the government open. This is Not to say that we don't support the environment or think that it is necessary to do all that we can to save the earth and solve our problems, it's just were not really expecting to make big momentous gains or achievements that we will feel in our daily lives through most of these programs like preventing \textbf{sexual} assault, solving racial inequality, making things cheaper, cleaning the environment. We generally expect and accept mitigation, not revolution, although there are topics where we seem to think we will be able to make radical changes like gun control and immigration, but these are often the ones with the most vague goals and least understanding of the facts,  like knowing what makes a gun an assault rifle, that a pistol kills the most people in America, that the NRA is relatively tiny compared to big pharma, that there are very large parts of the country and public that will make it nearly impossible  for the House and Senate  to pass meaningful gun reform legislation. Or most of generation Z not knowing that being an illegal immigrants  can literally means being a second class citizens similar to the status of freed slaves after the civil war; that our immigration population as a percentage of our total population is at near historic heights; that this cycle of dealing with DACA kids and their parents will continue unless you have tougher immigration security; that if we were to make our immigration system more merit based and designed to include how well the immigrants would adapt and prosper in American society like Canada's system, we would have less people coming from Latin America and less family members and children, instead having more workers from Asia; and that as sad as the average life of \textbf{refugee} is, most of the Syrians aren't very tuned into western values like freedom of speech, women's rights, not being antisemitic, etc. I feel terrible for the Syrians and their situation, but instead of just listening to people who aren't experts talk on MSNBC, CNN, or Fox, I actually looked what the statistics are, what the mainstream beliefs of people in the region like Egypt, Jordan, lebanon and Turkey. What percentage of them say yes to imprisoning \textbf{g\textbf{ay}} people for being \textbf{g\textbf{ay}}, or say yes to killing people who leave their religion, or yes to women having unequal status under the law, etc. It's not just the fringe, and would probably cause even more Trump backlash in America if they were allowed to come in massive numbers, as has been the case elsewhere, so although though I don't agree with Trumps muslim ban, I do understand why some people are saying that we should let Europe handle the \textbf{refugee} crisis. And yet when I say this to my class citing ever statistic and its source, and only suggesting that we should be more cautious about the unamerican beliefs that are being held by the group than we normally would before we let them in, it's like they don't even hear what I'm just saying, and imagine that instead of having cited statistics with credible numbers about people from the region, they imagine that I had said that all Syrians are \textbf{terrorist} and suggest that the people in the surveys were lying about having dispicable beliefs and are actually very good people,  one of the dumbest things I've ever heard.  But overall Generation Z are like millennials in that we generally have the same inclinations and beliefs, however we are more individualistic and don't actually have as much faith in either the government's ir the excessive and annoying liberal social justice warriors. And there is definitely growing resentment over all this mandatory social justice programs and getting pretty tired of these unnecessary expenses like the new law in california that requires solar panels for all new homes.  If a significant portion of our generation were vote conservative, it would have to be after an aggressively overbearing and liberal leader and the emergence of a new conservative that would be libertarian on social issues, promise stability and clarity, points out all political bullshit and the ugly facts, promises to decrease the economic/government restraints, push the entrepreneurial spirit, stands out for his conviction and strong opinions, believes in science, and can appeal to the independents, think of someone with the balls of and style of Trump, the promises of Rand Paul, and the moderate appeal and politics of Bill Clinton.\normalsize   & \cellcolor{green!27}Gay, Lame, Refugee, Sexual, Terrorist & \cellcolor{green!27}Gender - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}11/1480 & \cellcolor{green!27}0.743 \\  \hline
  \cellcolor{green!5}\small with each every generation, the definition of conservatism changes. today's conservatives accepts gays and lesbians now. go back 20 years, conservative will tell you, HELL NO to \textbf{g\textbf{ay}} people.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Adrian  Roth Considering YouTube is dominated by the nationalist right and the youth watch YouTube at much higher rates, they will turn out on the right. This depends on the state u live in. If ur in California, you won't get many right wingers. Go to a swing state like Florida and u will see the difference. By the way, fascism is not civic \textbf{nationalism}.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small \@Gourab Kundu I'm not sure that's an accurate statement. It's not that people get more conservative as they \textbf{age}, it's that people in general were more conservative (even Democrats) a few decades ago, and they are now all older. Modern liberalism is now asking us to accept things like multiple genders and abortion, whereas 40 years ago even Democrats weren't in favor of this. It's not that the people changed politics as they grew older, it's that liberalism itself changed and became more radical.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Or you know just get on with the fact that it doesn't matter? Why would you start a war with someone just because he's slightly older than you? This distinct line being drawn between Millennials and Gen Z will really just create useless conflict that shouldn't exist in the first place. Each generation will have their own failures and winners,and like it's just their \textbf{age}! God damn.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small Nah, The millennials are like our protective big sib. We just got to team up and kick some \textbf{old} people ass.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Ok in 2018 it would be \textbf{age} 6 to 22\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small when i hear that name, i just think"wow \textbf{old} people, really creative"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small me too! its like theyre calling us \textbf{apple} freaks or something\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Keila Ramirez we're basically \textbf{Apple} products\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Makes our generation sound like an \textbf{apple} product.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Keila Ramirez It's \textbf{old} people who think everything with a screen other than a tv is an ipad\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I can't stand it. \textbf{Apple} didn't make me. I don't even own an \textbf{Apple} product. Should we just name all generations after successful businesses?\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Lmao \textbf{apple} is shook. "iGen" I bet there gonna make a product called "iGen"\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I prefer igen to gen z as I think gen z sounds boring and it has \textbf{nothing} special to offer, it's just like gen x and gen y, when you hear those names you don't think about anything of significance.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Keila Ramirez considering the fact I've never owned an \textbf{apple} product, yes.ðŸ˜¡\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small +Keila RamirezWe're not iGen. We're Homelanders. Only the \textbf{old} farts that think \textbf{apple} is any good call us iGen.\normalsize   & \cellcolor{green!27}Apple, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Keila Ramirez I hate it so much like please there's more to me than my phone..... thanks \textbf{old} people\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small AvocadoKin Actually anxiety and depression is becoming more \textbf{common} because of the lack of sleep people get nowadays. Which can be caused by our slightly excessive use of phones and devices. We also spend a lot less time actually communicating with other people, so our social skills have kind of devolved and a lot of us are lonely most of the times.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Samsung \& Windows > \textbf{Apple}, any day of the week\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small same it sounds like a name some 34 year \textbf{old} came up with while tryna be 'cool and hip'\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I bet \textbf{Apple} came up with it - more advertising!\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Jacob Major At what \textbf{age} do you consider \textbf{old}?\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small R Lanterman What do you mean \textbf{old} be more specific? I could easily say 60 or I could say 35\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Me too. \textbf{Apple} sucks\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I only hate the name because it refers to \textbf{Apple} and \textbf{Apple} sucks ass.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I do. I don't like that our entire generation is named after \textbf{Apple} products.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small We sound like a new \textbf{apple} product\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small It makes us seem like a \textbf{apple} brand\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I mean they might have grown up with it...but like anyone who was \textbf{old} enlugh to have an iphone in 2009 or 2010 had them before a child did.  Mostly because they were much more expensive than other phones. Smartphones have become the norm quite recently and even adults had to get involved with them way before their offspring.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small no. \textbf{apple} is bad.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small avinash tripathi logically, socialism does work. Take the Scandinavian countries for example. I definitely agree with you though. I'm really hoping that America pulls out of the capitalist roots, and abandons the soon-to-be relics that we call our elders. Conservatism has no place in a rapidly advancing world. Liberalism and progressivism are the new \textbf{age} of humanity, and Gen Z is the driving force of this new era.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Fajitahmed    Social Democracy is democracy based from socialist ideals. A \textbf{nation} based upon socialist ideals is socialist.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Fajitahmed   I disagree with you. Based upon the structure of the term. Social Democracy is "democracy" (the noun) influenced by the term "social" (the adjective).  Meaning that in any and all cases of social democracy, the \textbf{nation} or organization MUST be democratic. Democratic socialism is the opposite; "democratic" is the adjective and "socialism" is the noun which means that the system is in all aspects socialist, with the additional incorporation of democracy.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small Joey Cash I'm an \textbf{immigrant}, Muslim, a professional engineer (Hence why I love capitalism) and I agree with 100 of what you saidBut just some "provocative" ideas to think about, while I agree with your idea of \textbf{nationalism}, I think the entire north American continent is a land of immigrants, like who are you going to nationalize? Everyone who came to this peace of land of earth is on the same level, why not nationalize hard working professionals who want to seek the north American dream? Make it a place where only hardworking people deserve to live, those who put in the effort to make a good living, contribute to society, be a productive member of society, contribute to the overall betterment of the north American economy, where hard work, and only hard work is what defines the continent, away from religion and other stuff, and without pushing ideals and beliefs on others..... Lets face it, north America has no identity, it's not Europe, remember what Adolf Hitler tried to do, he wanted to nationalize the country and make it exclusive to the Aryan \textbf{race} in, while maybe the ways he took to achieve his goals were horrible, I kind of understand why he wanted to go this path, Europe is originally white, so it's only logical to put white people first...... It's not the same in North america.....I dunno just a thought, maybe people would look at things differently\normalsize   & \cellcolor{green!27}Immigrant, Nationalism, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}3/242 & \cellcolor{green!27}1.24 \\  \hline
  \cellcolor{green!5}\small Osama Al-Humaimidi I agree with you however the sense of \textbf{nationalism} for the U.S. is the love of the country and its history, specifically the values that built this country. When I think of \textbf{nationalism} for the U.S. I think of our rights for everyone, being the most free country, and so on. It's just I minor disappointment but I thought I'd mention it. It's good to have people like you contributing to this great society by the way\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/79 & \cellcolor{green!5}2.532 \\  \hline
  \cellcolor{green!27}\small James Dutile I don't think you fully grasp it. I don't mean this in a rude or condescending way, but I think a lot of people in the western world don't understand it since we've been the freest in the world. Under socialism there is complete control over the economy, something that these "socialist" Scandinavian countries aren't doing. They allow elements of a free market, which isn't socialist. When people think of socialism the tend to think of social services really, and for the Scandinavian countries they do have more services, however they don't pay for a military because we are their protection. When you don't have to pay for your defence you can use a large amount of taxes for health care and etc. But these countries don't have nearly as good as health care as in the U.S.  because of our free market companies must compete to get business, so they need to lower prices, provide the best service, and innovate to stay in business. Socialism doesn't take that into account. When there is 1 force controlling a service they don't have to compete or innovate because they're the only service. Why make something more affordable or better when people will have to go to you by default? In fact \textbf{doctors} are leaving these countries because there's no incentive to be a doctor when you don't get paid much by the government, so these countries are now losing \textbf{doctors}. One of the appeals to that career is the money and without it what's the point of going through med school and going through all that effort. Another problem is that the  Scandinavian countries have a way smaller population. Truly socialist countries look like Venezuela, where the government took full control of their natural resources and made the prices extremely high, so no foreign people invested in it. There was no point in buying Venezuelan oil when you can get it somewhere else far cheaper. Also with a socialist government many people in the government don't understand economics. They spend way too much on social services. It's also harder for them to price things like food, because in a capitalist market the consumer sets the price based on demand, because of this companies try to meet the demand to get the customer. Thats what happened in China under Mao. Part of the 50 to 80 million deaths under his rule had to do with people starving to death for that reason. Another problem with socialism is that the government is pretty much the one making all decisions in your life. This greater good mentioned earlier sounds nice but it isn't. There isn't individuality. You may lose all your money because the government thinks its best going to someone else. That's theft. Taxes are government people coming to your house and taking money at gunpoint. If you refuse you go to jail or might be killed. So even in theory it's wrong because it isn't you deciding to give money for the good of humanity, it's the government stepping in and taking it from you whether you like it or not.  Basically I could argue that me taking your hard earned money is for the greater good because I'm hungry, which wouldn't be moral because it's your money and I have no right to take it. Lastly, socialism is not like democracy. True democracy is mob rule which never works because the ever changing will of the majority take the rights away from the minority. Socialism is government control of the economy. Anyways I know this is a long comment and if you read this far thanks for taking the time to read this. It would be interesting to possibly continue this discussion so maybe we can keep talking unless this is enough.\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/633 & \cellcolor{green!27}0.316 \\  \hline
  \cellcolor{green!5}\small Septic Neuron Not true. I don't know about girls; but guys are constantly insulting each other and no one really gets hurt. As for giving up easier, I'd say that depends on the individual.\normalsize   & \cellcolor{green!5}Septic & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small avinash tripathi judgement and restrictions are people-basedMaybe we should switch the entire human \textbf{race} out for something different ðŸ¤·ðŸ¾â€â™€ï¸\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small not true. born 2005, musically is \textbf{weird}. don't be stereotypical\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Fajitahmed. I think that from 1997 to 1999 we have a mix between both generations Y and Z. I remember playing the Mortal Kombat 2 or 3 in the sega (I'm from 1998), and I had access to internet aroung 7 or 8 years \textbf{old}. I remember playing PS1 and mostly PS2. But I also remember playing outside with my cousins and having tons of fun playing hide and seek, soccer/fÃºtbol, tennis, etc. My beloved childhood ðŸ’•ðŸ’•ðŸ’•\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small Fajitahmed Not all kids born in the 21st century get phones at fucking 5. Most children these days get their phones at the \textbf{age} of 11 and above, like you should.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small F255123 Its an accident of birth, and whatever things you think you hate millenials for, some of thats going to bleed over to younger \textbf{age} groups. The biggest thing people didnt like late millenials for was the overuse of sm. I dont see that suddenly changing. 1995 or 2000 isnt some magic cut off. People exist in a continuity.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Fajitahmed that's how my life was too and I was born in2001 I played outside all of my childhood and I thank god that I played more outside than playing video games. My first game system was a N64 I got my first smartphone when I was in middle school and I'll tell you this I am glad that I enjoyed my childhood with out tech because the new generation of 2012 and in have more tech at a young \textbf{age}. I see 1 year olds with tablets my childhood wasn't like that and kids get there first phone at your ages\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small 1998 is millennial. They keep changing the range for generations this last decade. Millennials are 1981-1998. Gen Z is 2000-2018. The \textbf{age} of each generation is 18 years and then a new generation starts. Do you know why? Legal consent to \textbf{sex}. The generation that is breeding must be 18 or older by law in order to consent to \textbf{sex}. The average \textbf{age} of a new generation being created after the previous become adults is around 5 years (23 years \textbf{old}).Millennials gave birth to generation Z around the years of 2000-2008. Which would line up with the proper \textbf{age} of over 18 and younger than 25.Generation Z will create the next generation starting in 2018 at the earliest since they themselves have become 18 by then. The majority of millennials would have given birth by this point (peak female reproductive \textbf{age} below 30). The last of millennials to give birth before 30 years \textbf{old} were born in 1998, and become 30 by 2028.I just felt like typing all of this word salad for no reason.\normalsize   & \cellcolor{green!27}Age, Old, Sex & \cellcolor{green!27}Age - General, Age - Over 65s, Gender - General & \cellcolor{green!27}8/178 & \cellcolor{green!27}4.494 \\  \hline
  \cellcolor{green!5}\small "Whew"? Get lost then, kid. Is the term Millennial an insult now? Yeah, screw you too then. Way to fall for the Baby Boomers' propaganda. Is being part of Generation Z better? Enjoy your fucking tidepods then, you ignorant \textbf{brat}.\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Suprajira Morakot haven't come of \textbf{age} yet, haven't had work experience/higher education/serious impact on economy. The oldest Gen Z is 23 right now, which mean only 5 years of Gen Z are adults who have experienced life in the fullest. Even at that, only a sliver of life has been experienced. Including children to speak for the generation, how they think and behave is wrong because they are still developing critical thinking skills and growing mentally and physically. You would need every gen Z to pass \textbf{age} 23-26 and average their overall contribution to actually make a good conclusion on who or what they are as a whole.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/108 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Why would you exclude them though, and only include the older end of the generation. Would that not still be limiting the voice of the generation? Something like this would need several \textbf{age} perspectives of the generation. Not just the adults.  Also I wouldn't exclude teenagers on work experience and higher education.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Suprajira Morakot I just explained why you would exclude the younger generation in detail, why would you ask again? A generation can't be solidified based on actively changing variables, thus you ask people who are for the most part set in stone about their way of life (adults). While it is valuable to gather information about how kids behave, they do not represent the final product of the generation because they are constantly changing every aspect of their life until they enter adulthood and even until their mid twenties. Asking young kids questions they don't know how to answer realistically completely defeats the purpose when they don't have a grasp on the real world. That's not an insult it's just a part of growing up. The face of the generation is the workforce currently, 18+ they are making real world impacts and they are how people perceive the generation as a whole because it's well understood that kids develope for a long time before they can offer wisdom and confidence in themselves and their peers. These kids will get asked questions and for input when they reach the stage of their lives with they impact the world, which they don't do as mere children alone. \textbf{Nobody} is limiting their opinion or voice, but we will take it with a grain of salt because kids flip flop on topics all the time, and we need concrete answers when they are more mature. I am Gen Z in my twenties, I actively impact what others perceive of Gen Z because I am in the workforce with 3-4 other generations, THAT is what I am implying. \textbf{Nobody} will take you as you are as a kid because you change every year as you grow, but you remain relatively the same as an adult.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/300 & \cellcolor{green!27}0.667 \\  \hline
  \cellcolor{green!5}\small Veloxica i'm 24, i was born in 1994 so technically i am in that same generational gray area as Xennials but i have always identified closer with iGen than Millennial. I have almost \textbf{nothing} in \textbf{common} with Millennials except greater memory of the 90s as the late 90s and early 2000s was my childhood lmao thats about it. Been jacked into the 'Net for as long as i can remember.\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/70 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small We have a history of \textbf{old} people hating on young people\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Gen z marks - for want of a better term - the regression of the species; they have the worst working memory of any generation, have the shortest attention span, are the likeliest to have a \textbf{mental} disorder, have been indoctrinated but not educated, and have as much creativity as a brick. On a side note, 1995 seems far too early, unless you live in a vacuum and are talking only of a select part of the United States, or some other first world country. Most of the world didn't have the internet at home until the early 2000's - and even then it was from a PC; not mobiles, tablets etc., and the internet wasn't all consuming as it is now.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/122 & \cellcolor{green!5}0.82 \\  \hline
  \cellcolor{green!27}\small Renzen So it's Gen Zs fault for an increase in \textbf{mental} disorders because of bad parenting from people who were either millennials or from other generations? Okay.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Milkycharizard yes cuz I grew up in a bad environment but I have no \textbf{mental} disorders\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I feel like Gen Z is probably the most self-conscious and self-aware generation because of the amount of access to news that we have. We realize how \textbf{dumb} the news is since we are able to compare the news to what is actually happening. For example, some news brodcast may say that LA is the best city ever while you might also recieve information from a homeless person talking about the amount of issues LA has.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small Renzen in all seriousness though, I think gen z is going to be good overall. Studies have shown we tend to have a more conservative view, which the previous few generations haven't. With a new outlook through that we might make changes for the better. Not all of us have \textbf{mental} disorders or act fully stupid. Like someone mentioned before me, the internet just allows you to see us do more stupid stuff because we can post it wherever. Also I've seen studies and even had a psychology teacher explain that older generations use their phones more in a day. Also people born in the 50's had extra carbon in their DNA from all the nuclear bomb tests at the time, so there were problems with them mentally. Doesn't mean they're a terrible generation though. My argument seems more biased as someone born in generation z but I truly believe we aren't going to be much worse if at all  worse than previous generations.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/164 & \cellcolor{green!5}0.61 \\  \hline
  \cellcolor{green!27}\small i wonder what all the war propaganda did to previous generations? and also maybe its not the generations fault that they were indoctrinated, maybe that was the other generations choosing that for them. also, have you even seen deviantart and tumblr? like, if you want some creativity go there, ms. baby boomer. also, maybe we are just more aware of the \textbf{mental} disorders now.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small It's true that Gen Z has it's faults, but so does literally every generation. It's a well known phenomenon that older generations are generally of the opinion that the younger generations are useless, lazy, spoiled, etc. I think it's rather insensitive to blame Gen Z for our \textbf{mental} disorders. Blaming someone for their bad \textbf{mental} health is a lovely way to send them into a downward spiral of self destruction, and generally a shit idea. While obviously I don't want my generation to have these issues, we do, but calling us "the regression of the species" (nice college graduate lingo btw) is helping? how???This is especially ridiculous to me considering that this bad \textbf{mental} health is heavily influenced, in my experience, by the stress of inadequate education, which doesn't prepare us for the real world, and contributes to stress, and the events happening currently- the insane political division and general chaos in our halls of government, the ongoing occurrence of terror attacks and school shootings, the opioid crisis, etc. etc.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/171 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Gen Z as well as Millennials are probably the most tolerant and accepting of all generations, other generations have started all of the worst wars in history as well as \textbf{racism} and \textbf{sexism}.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small +Queen of ManilaThe paradox of tolerance is that if you become too tolerant you doom tolerance in it's entirety. Because if you become tolerant of intolerance, those less tolerant than you will force you to become less tolerant, or abuse your tolerance in it's entirety.So in order to protect our tolerant society, we have to, in the name of tolerance and freedom, become intolerant toward intolerance, so that we may maintain a free society. Because without freedom there is no tolerance, only totalitarian dogma.And for those of you longing for a more "down to earth" explanation. Don't be a spineless wuss, never let anybody shit on you, and be a respectable shitlord. Because \textbf{nobody} likes an sjw.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/120 & \cellcolor{green!5}0.833 \\  \hline
  \cellcolor{green!27}\small Majority of millenials are the most dipshited bunch of kids I've ever seen, error young adults. Generation Z (whatever) kids are a strange bunch. Everything revolves around the internet. Selfies with duck lips or tongues out and social media and \textbf{weird} You tube videos. How many thumbs up and likes can I get.   I have a " millenial" and a "gen z" kid.  The young one can't live without technology or so he thinks and the other without her phone.  Their lives would end. ðŸ˜£ðŸ¤£\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small bigpolitical829 grouping people by generations is stupid. would you proudly say that you are in the same \textbf{age} group as someone who is 6? Get real, you're born in the mid 90s and in your twenties already balding. no way in hell, should you be proud of that. It's a stupid \textbf{age} grouping followed by stupid people who feel the need to belong somewhere and feel special\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small Hannah Jasmin That's not even a good point. The 6 year olds today will be 18 in 2030, when the oldest of gen z have just gotten into their 30s. At that point, we will increasingly have a lot more in \textbf{common} as a generation.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Daniel Gomez You can't compare someone I their 30s to an 18yr \textbf{old}, get real..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small the generational labels arent all the same. you can be born in 95 and be a millenial its all just fluid at the moment because we arent \textbf{old} enough to properly define it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small bigpolitical829 Born in 92 but I prefer being a Millennial were so much more interesting and not afraid to speak our minds. We grew up and remember what times we're like before the digital \textbf{age}. I personally identify more as a millennial and prefer it.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Joey Cash Yeah in 2030 those gen Z who are barely 30 will have more in \textbf{common} with a young millennial in their 30s than with the really \textbf{old} teens who will be more like gen Alpha who are kids and teens. Obviously.But the general generation will be in their 20s, which can easily be grouped together with some young 30 yr olds and older teens. Kind of like millennials a few years ago. Now all the teens are gen Z and those in their mid 30s are millenials.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/90 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Max Ramos I've noticed people born in 1997 relate more to millennials and those born in 1999 relate more to Gen Z. Most people my \textbf{age} would self identify as gen Z while people your \textbf{age} would say they're millennials.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Melanny R. Martinez wym? From what I've seen that's the case. Very few people my \textbf{age} identify as millenials and very few people from '97 and before think they're gen Z. There's a few commenters on here from 95 and 96 who say they have gen Z traits, but irl they're still millennials. 1999 is completely different bc everyone irl just knows they aren't a millennial cuz we're just farther away from them cultural and \textbf{age} wise.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small Yeah, your generation is way to deep in your phone screens, with attention span of 6 seconds (vines? Anyone?) And no social, actual face to face skills, you live in a digital world where everything is fake, everything is made up to be up to ideal standards you had in your head which it not real and almost not feasible, and when real life hits with no filters, no pictures enhancements, you feel depressed because you have no experience outside your phone's. oh and your obsession with instant gratification, And no values whatsoever, everything is blended with everything and \textbf{nothing} makes sense anymore.And don't start on the work place, non of you (even lots of us millenials) have discipline, no responsibility, \textbf{nothing}, you expect everything to happen just because you FEEL it should, you don't even put in the effort to make it happen, or maybe you just rally/riot (UC Berkeley antifa idiots)/yell/shout/defame on twitter/start a hashtag (the stupid metoo)/post a video on Facebook and make it all emotional and all about YOU, it's like you are the center of the universe, you don't even bother to have a civil conversation anymore. Everything is about bullshit equality regardless of merit and qualifications. These are all made to pander to your fragile feelings and emotions, instead of toughening you up to be ready to face real life, because boy..... Real life will crush you, and \textbf{nobody} cares about you little safe space rainbow unicorn bubbleSomething is wrong happend along the way and if we don't start working on it, you gen zer's will be the doom of everyone. I envy generations in the past who had discipline and order, and had goals, rather than fake dreams. And I don't blame you only, I blame US millenials, and I blame the generation before us, who thought making everything available instantly to us will give us a happier life, instead we turned to little bratty entitled shitheads with no respect for anything and anyone, selfish, arrogant, and stupid\normalsize   & \cellcolor{green!5}Nobody, Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}3/337 & \cellcolor{green!5}0.89 \\  \hline
  \cellcolor{green!27}\small another artist entrepreneurship isn't about making a business of something you love, it's about finding a problem people face and try to solve it, that should be your main goal, like people who wanna be better hockey players, there are many hockey wearable tech for them to help them track their progress..... That's entrepreneurshipYour dreams mean \textbf{nothing} if they don't generate MONEY, REVENUE. sure you love art, but is it sustainable as a business plan and a career?Think about that for a second\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small The \textbf{woman} speaking was the one who coined the term 'gen z' and was just presenting the statistics she found through her research of how we are 'more likely' or 'less likely' to act. It's a given that what she is saying won't necessarily apply to everyone individually because they are just general statistics.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Osama Al-Humaimidi most gen zers use Instagram, twitter and Snapchat. barely any of us use Facebook, and the riot and \textbf{snowflake} bullshit is millennials. studies show that gen z will be more conservative than Democratic. also, just because we dont have a lot of face to face interactions doesnt mean we will become dumber. holy shit stop assuming stuff\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Ic0n at most they're 23, as a 22 year \textbf{old} i can say we have no experience\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Totally agree our meme status puts us way above these \textbf{old} normies\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Gavin C. You \textbf{old} guys don't understand that that was a meme where we made fun of the pple that ate them lmao\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Only younger Gen Z do that \textbf{dumb} tide pod  shit\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Teenagers of all generations have done stupid things. For example, in the 1930s, teenagers would swallow goldfish. And I'm sure teens did \textbf{dumb} things in your generation too. However, the difference between us is that \textbf{nobody} was there to record your stunts and post them on social media.\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Liverpool 32 I'm gen z and those people who ate them are \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Gen Z behaves the way it does because the world we live in makes us this way. Im 1998 and I kinda call BS on the work/life blend 7 days a week thing. Precarious work is a very real threat so I would say we are always in the process of advancing our credentials due to capitalistic competition. I also think with the advent of technology human work is becoming fabricated for the sake of the economy. Since the \textbf{transition} to the service industry, it seems technology is allowing us to pursue more intellectual work which naturally lends itself towards the hobby territory. My point is I think that this video  credits too much individuality to Gen Z.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/118 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}\small Im not entirely sure how the 24/7 work life blend goes against the advancing credentials, unless you're offering an explanation for it and say we work 24/7 because we're always in school or teaching ourselves something. Is that it? I 100 agree with the fabricating jobs for the economy, I've thought about that a bunch before. I also find it interesting how we fabricate jobs but outsource many jobs because capitalism has always relied on cheap/free/slave labor in America to function so that the rest can live in better conditions so it's like we're saying 'WE NEED JOBS' but also 'ooo but not those kinds of jobs (because then we'd have to pay a livable wage and increase the cost of \textbf{common} goods)'\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small Whether or not capitalism is "good" or has "worked" says \textbf{nothing} about its sustainability or how it will adapt to major changes in how the economy is driven, such as automation.Whatever you want to call it, I think we will see a move towards a shorter, more flexible working week with more job sharing and overall less consumption. People will become less hostile towards \textbf{zero} hours contracts and skills/labour will be pooled into a more fluid marketplace rather than individual companies. In other words, work will be based less on long term employment contracts and more on freelance or agency hiring.\normalsize   & \cellcolor{green!5}Nothing, Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Reda Zaki \textbf{nobody} notice... dont call atention to that.... zombies is what we need\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Fajitahmed Not too much just like as in everyone being a \textbf{snowflake} I would like to see change in the near future as in technology, how far we can go into space.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small abc alqadiri ExactlyðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Abhishek what positive changes could they possibly offer? they lack problem solving skills while massive problems coming our way? It's a selfish generation which was created by a previous selfish generation it's like selfishness on steroids now - not going to be pretty.  It all started because of 1930's depression- growing up with \textbf{nothing} parents wanted to give their kids everything they never had- a few generations of that and you repeat the economic cycle of depression.  Don't see how they will fair well in an economic collapse bigger and longer then 1930's was\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small Nekouls Fegeti Honestly, I hope races end up dying out or completely changing from the ones we have now in a few thousand years or so. Since keeping a certain \textbf{race} going, like Europeans, will have to involve inbreeding.Yuck.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Nobody, Zero, Brat & \cellcolor{red!27}130 & \cellcolor{red!27}130/141488& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}145 & \cellcolor{red!5}145/141488& \cellcolor{red!5}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Weird, Mental, Dumb, Crazy, Freak, Blind, Cripple, Lame & \cellcolor{red!27}127 & \cellcolor{red!27}127/141488& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Elderly, Senior & \cellcolor{red!5}185 & \cellcolor{red!5}185/141488& \cellcolor{red!5}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Apple, Red & \cellcolor{red!27}46 & \cellcolor{red!27}46/141488& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Sexual, Gender, Sexism, Woman, Sex, Patriarchy, Chick & \cellcolor{red!5}41 & \cellcolor{red!5}41/141488& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}Transgender, Transition, LGBT & \cellcolor{red!27}23 & \cellcolor{red!27}23/141488& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Racism, Racist, Race, Ethnic, Ethnicity & \cellcolor{red!5}60 & \cellcolor{red!5}60/141488& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Homophobia, Homophobic, Gay, Queer, LGBT & \cellcolor{red!27}50 & \cellcolor{red!27}50/141488& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, Tacky & \cellcolor{red!5}39 & \cellcolor{red!5}39/141488& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}7 & \cellcolor{red!27}7/141488& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, Fruit, Pansy, Queer, LGBT & \cellcolor{red!5}45 & \cellcolor{red!5}45/141488& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Fat, Fatty, Skinny, Thin, Lump & \cellcolor{red!27}9 & \cellcolor{red!27}9/141488& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Alien, Nation, Migrant, Engineers, Nationalism, Refugee, Immigrant, doctors & \cellcolor{red!5}40 & \cellcolor{red!5}40/141488& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - European or anti-Europeans}  & \cellcolor{red!27}Brexit & \cellcolor{red!27}4 & \cellcolor{red!27}4/141488& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Commie, Red, Cuckservative, Snowflake, Communist & \cellcolor{red!5}23 & \cellcolor{red!5}23/141488& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, African & \cellcolor{red!27}17 & \cellcolor{red!27}17/141488& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - French}  & \cellcolor{red!5}Frog & \cellcolor{red!5}2 & \cellcolor{red!5}2/141488& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Hun & \cellcolor{red!27}1 & \cellcolor{red!27}1/141488& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}ABC & \cellcolor{red!5}17 & \cellcolor{red!5}17/141488& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}THOT & \cellcolor{red!27}1 & \cellcolor{red!27}1/141488& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Female homosexuality}  & \cellcolor{red!5}Lesbian & \cellcolor{red!5}1 & \cellcolor{red!5}1/141488& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Jewish}  & \cellcolor{red!27}Oven & \cellcolor{red!27}1 & \cellcolor{red!27}1/141488& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - British}  & \cellcolor{red!5}Tan & \cellcolor{red!5}4 & \cellcolor{red!5}4/141488& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}1 & \cellcolor{red!27}1/141488& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - American}  & \cellcolor{red!5}Septic & \cellcolor{red!5}1 & \cellcolor{red!5}1/141488& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - Youngsters;Age - General;Physical Identity - Physical (and Mental) Impairments;Age - Over 65s;Ethnicity - Native-American;Gender - General;Sexual Identity - Transexuality;Ethnicity - General;Sexual Identity - General;Social Class - Working class;Behavioural Addiction - Alcohol;Sexual Identity - Male homosexuality;Physical Identity - Physical Features;Nationality - General;Nationality - European or anti-Europeans; Ideological and Political Identity - General;Ethnicity - Black;Nationality - French;Nationality - German;Nationality - Chinese;Gender - Female sexuality;Sexual Identity - Female homosexuality;Religious Identity - Jewish;Nationality - British;Religious Identity - Muslim;Nationality - American;%.

\item The percentage of hate speech related words is 0.7209.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 1021/4456 occurences of hate speech related comments.\end{itemize}\end{document}