\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_119.json :}\newline \par\Large\textbf {Title: \large  Ageism: The Last Acceptable Prejudice in America | Real Time with Bill Maher (HBO) }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small California is a \textbf{Communist} shit hole. Brown didn't fix anything but he broke a lot of shit.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Praising \textbf{Jerry} brown Eye\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Ageism is wrong. We can agree. Shit, I hate Mahr but he's finally right.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Didn't he make fun of John McCain's \textbf{age}  when he was running ??\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Jerry created the Silicon Valley boom. Lol. at some point to silicon valley people are going to get sick of paying huge taxes.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small No. We need a young, vigorous president more than ever. Get these \textbf{old} fossils out of the White House. Trump is an \textbf{old} timer too.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Two years before Cheetos in Chief - 73 years \textbf{old} now - managed to prove on a daily basis that there's no limit to human stupidity and pettiness.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I've been saying this for years. In the pre-Trump world of pretend equality, \textbf{ageism} in the job market was and still is pervasive. Believe me, older women get it worse.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small when someone says "Asian Driving" everyone gets it! and it is not one bit \textbf{racist} . as a matter of fact Asians are incoherent and not spatially aware in general. Bill Mahr, thanks for being Real!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small MARVELOUS comparisons of older famous people with younger famous people. And marvelous commentary on \textbf{ageism}.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Oh God, do I love you Bill Maher - thanks for giving laughs to this \textbf{elderly} 73 yr. \textbf{old} me....\normalsize   & \cellcolor{green!27}Elderly, Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Ageism is not the last acceptable prejudice. \textbf{Fat} people are the last acceptable prejudice and if you're \textbf{old} and \textbf{fat}, you're really in trouble.\normalsize   & \cellcolor{green!5}Ageism, Fat, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}4/24 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Here we are in 2019 and evey city in california has a huge homeless problem over 165,000 people sleeping, shooting heroin, shitting \& pissing in the streets, illeagle immigrants everywhere and a \textbf{communist} policy on guns and ammo. Ya. bill. Jerry's doing great. People are leaving in droves.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Bill Maher is a \textbf{pussy}.  A stanky \textbf{pussy}.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small As much as I love Bill, he shits in his own mouth quite a lot. You just can't criticise \textbf{ageism} by being \textbf{ageist} against young people. Wisdom is just bullshit, there are brilliant kids and stupid adults.\normalsize   & \cellcolor{green!27}Ageism, Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Who's the bint to your left. Just caught a glimpse but that was enough to make an \textbf{old} man cum. 😜She's gorgeous.😘\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small One of the most important things \textbf{Indian} kids are taught by default since early years is to respect elders..\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Umm the \textbf{old} bastards rule over everything and fuck all the young. So you can stick that up your ass.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Yeah I didn't hear Bill Maher opening his \textbf{fat} mouth when John McCain was running for president and Democrats skewered him about his \textbf{age} but you're willing to put a guy on in the White House who's going to be 80 after his 1st term\normalsize   & \cellcolor{green!27}Age, Fat & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Bill Maher is right except for one statement - that \textbf{ageism} is the only thing people can be judged on.  Gays, \textbf{fat} people, people with disabilities, and many other groups are subject to judgement based on what should not matter in most cases.\normalsize   & \cellcolor{green!5}Ageism, Fat & \cellcolor{green!5}Age - General, Physical Identity - Physical Features & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small That's why abortion is acceptable.  \textbf{Ageism}...\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Asian and European cultures respect the \textbf{elderly} and prefer them to be leaders. \textbf{Jerry} Brown would be an excellent president.  Joe Biden in 2020 is on that horse where all the gates open except his. Gordon\normalsize   & \cellcolor{green!5}Elderly, Jerry & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Cognitive ability declines linearly with \textbf{age} once you reach what we consider middle-aged. 90 year olds should not legally be eligible to be president. Fuck they shouldn't even get to drive, we all agree that 14 is too young.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Jerry Brown.............fixed............. California.............\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Age brings wisdom, however the office of presidency tends to \textbf{age} people. Look at Clinton in 92 and again in 96. The stress that comes with the job ages presidents horribly.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small The optimal \textbf{age} range for a president is 50-60 years \textbf{old}.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small It's not pre judging.   It's science:  As people \textbf{age} in this world, their mind gets more polluted, leading to many brain problems (ie trump).  We should do without this risk.  To run for pres, there is a lower limit of 35, but no upper limit.  This shows a LACK of old-ageism in the US.  The real last prejudice is being able to trash men.PS, I'm not a young biased person.  I'm 51\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Ironically, this segment didn't \textbf{age} well.  tRump is president, in his 70's, and is not wise or competent.  If someone is a good leader, then they shouldn't be judged by \textbf{age} or anything else, period (well, unless they're a murderer or predator).  But, I do agree, \textbf{ageism} is real.  Especially in the work force.  My father got laid off from his job in his early 60's and had a real difficult time finding a new one.  Thank god he did.\normalsize   & \cellcolor{green!5}Age, Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small Prejudice against atheists is rampant, and also acceptable. And if you're an \textbf{old} atheist, you're screwed.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Ironic being that the Dems elected AOC...an idiot 29yr \textbf{old} bartender to Congress. 😂😂🤣\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} was Ronald Reagan when he served as President?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Funny how Maher never knocked \textbf{ageism} until he reached his sixties. It's legitimate to question the \textbf{age} of candidates who are even older than Reagan was when he first ran for president. I don't recall Democrats or liberal comedians complaining about \textbf{ageism} back then.\normalsize   & \cellcolor{green!5}Age, Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/44 & \cellcolor{green!5}6.818 \\  \hline
  \cellcolor{green!27}\small Trump will be \textbf{old} when re=elected, thanks billMaher\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small It's funny cause he is always talking down to younger people who dont want to fuck him cause he is \textbf{old}...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small it's not \textbf{AGEISM} to Want To Get The GRANSPAS OUT OF THE GOVERNMENT.  They've made a HUGE MESS and are not willing to do anything to clean it up. Time For THEM to GO!!!  you have a bunch of Olde White Guys with 19th Century values regarding non-whites and women, IT'S TIME TO GET THE GRANDPAS OUT OF THE GOVERNMENT  VOTE2020\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small People call me about enlisting their job finding service. About six times they ask me questions. When we get to what year I finished high school I say 1971 they respond with they can't help me or I'm uneligible even though I'm looking for online work. \textbf{Ageism} truly does exist.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small We're \textbf{sexual} adolescents because the bible banging ignorant jesus freaks want us all to hide from our sexuality.  Murder is OK to the bible fuckers, but \textbf{sex} is a sin.  Hypochristians all.\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I'm guessing that's because it's one thing every single human being on the planet has in \textbf{common}..we will all \textbf{age} and be aged..not everyone will be white or female or \textbf{gender} fluid or Muslim or etc etc etc.....but we will all be aged one day\normalsize   & \cellcolor{green!5}Age, Common, Gender & \cellcolor{green!5}Age - General, Gender - General, Social Class - Working class & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I wonder how many of the trained seals clapping in his audience did the same when they threw out the "\textbf{age}" fish for McCain in 2008.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Ageism is the last acceptable prejudice in America. Now let me tell you how worthless millennials are!\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small actually I speak this from experience, in many Chinese industries, agism is rampant. Some recruiters brazenly demand candidates to be below the \textbf{age} of 35. Why not? easy to deceive, demand less money and more impressionable.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Jerry Brown chased a multi billion dollar, worthless train; was 'fine' with businesses leaving California for Texas and taking tens of thousands of jobs with them. He wasn't that great of a governor.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Fuck \textbf{Jerry} brown\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Now California has the worst school systems in the country or close to it and the state is insolvent because of your bullshit social welfare programs and free handouts that's why all of the taxpayers and many of the businesses are moving out of the state. Yeah and liberals bashed John McCain saying he was too \textbf{old} to be president when he was way more qualified than Hillary Clinton and he's a decorated veteran. Hillary on the other hand is in her late sixties or early seventies and she can't walk a hundred yards without falling on her face or passing out so your right \textbf{age} is relative and it's a good thing Hillary wasn't elected\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/116 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small Governor English as a second language.... funny unless of course thst aren't white.then ur a big racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Wise when your \textbf{old}? Strongly disagree with him there\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small This video title is bullshit, the last excepted prejudice is \textbf{racism} against white people.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small No, it's not. \textbf{Sexism} and \textbf{racism} are still acceptable by many. Speciesism is still the norm, too. Also, there's a lot of \textbf{ageism} against young people too. Attend university as a 30-year-old and see what I mean: you go from being treated like a competent adult to a  stupid, incompetent, untrustworthy, inexperienced baby and profs and admin talk to you condescendingly in almost every interaction. Not to mention all those entitled parents I see treating their children like property or extensions of their egos instead of autonomous individuals.\normalsize   & \cellcolor{green!5}Ageism, Racism, Sexism & \cellcolor{green!5}Age - General, Ethnicity - General, Gender - General & \cellcolor{green!5}3/88 & \cellcolor{green!5}3.409 \\  \hline
  \cellcolor{green!27}\small LOL Bill talks about young people like they are satan, but he wants to talk about \textbf{ageism}? K.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Double edged sword.  \textbf{Old} people become demented.  You never know past a certain \textbf{age} when the decline will begin.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small No.... Liberals openly hate on farmers and assume they are stupid, \textbf{r\textbf{edneck}} hillbillies. Liberals will do this until the end of time. I say this as a Liberal.\normalsize   & \cellcolor{green!27}Redneck & \cellcolor{green!27}Ethnicity - White, Social Class - Working class & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Ageism? How \textbf{old} is Bernie Sanders? Trump? come on.\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small This speech comes from an \textbf{old} man wo is fucking young girls. And he wanted an \textbf{old} president? He got Trump... what an asshole\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small 2019 , my god is it broken now. More homeless people then entire country combined. \textbf{AGEism} IS BAAAAAAAAAAADDDDDDDDDDD, but when republicans have a \textbf{old} guy running......HAHAHAHA HE \textbf{OLD} HAHAHAHA....maybe it isn't \textbf{ageism} after all\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/34 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Most wise people are \textbf{old}, but not all \textbf{old} people are wise.Also, \textbf{ageism} goes both ways. You can be \textbf{ageist} against young people too.\normalsize   & \cellcolor{green!27}Ageism, Ageist, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}4/25 & \cellcolor{green!27}16.0 \\  \hline
  \cellcolor{green!5}\small Well when you're a hormonal teen \textbf{age} kind of comes to mind easily\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Disagree. I don't want a \textbf{old}, grumpy, foul tempered white man controlling the fate of the free world.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Racism against white people is acceptable in America too, if not praised.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small It's ok to laugh at \textbf{old} people, it's socially acceptable and \textbf{nobody} defend the \textbf{old} people.It's not generation ass, it's generation \textbf{FAT} ASS !\normalsize   & \cellcolor{green!27}Fat, Nobody, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!27}4/25 & \cellcolor{green!27}16.0 \\  \hline
  \cellcolor{green!5}\small I have no idea which planet Maher is living on. \textbf{Ageism}? The last 2 presidential candidates were like 100. Half of the Senate is over 60. All the Democratic and Republican leaders are in their 60s and 70s. What the hell is he talking about?\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small The only problem with Bill's words is that he'd be the first to say \textbf{old} fossils like Chuck Grassley should be forced into retirement.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small TRY BEING \textbf{G\textbf{AY}}IN AMERICA IN2019\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small BULLSHITTO\textbf{AGEISM}AS A PREJUDICE\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small i think rudy ray  moore  said that line young, \textbf{dumb} ,and full of cum. he was a comedian from the 70s. google it.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small how many times did Bill say that Bernie was too \textbf{old}? fuck off Bill.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I don't know.  He just made a prejudice comment about Arnold with English as a second language to lots of laughter.Of course, I doubt that same joke would've been made on a Spanish speaker :pNot that I disagree.  \textbf{Age} shouldn't be a factor in "Can they do it."  It's not like being President is a physical job.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Seems reversed \textbf{ageism} and fat-shaming is okay too.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small If you think California is fixed then you're a dumber \textbf{libtard} then i thought Bill\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Bill, With All Due Respect....I Know A lot of Fucking Stupid \textbf{Old} People!!! \textbf{Age} Does Not = Wisdom!!!\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Ageism is  a great topic for a guy dating someone half his \textbf{age}.\normalsize   & \cellcolor{green!5}Age, Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small I googled 'bill maher best jokes'...... \textbf{Nothing} came up\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Yeah he fixed \textbf{nothing}, fuck he made California worse. Arnold would have done way more for California if it wasn't for the liberal Democrats fucking things up. Yeah \textbf{Jerry} Brown was a genius, high homeless rate, large income inequality, you all understand that,  the fifth largest economy in the world has income inequality and high homelessness, outstanding.\normalsize   & \cellcolor{green!5}Jerry, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - German & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small Isn't it rational to consider \textbf{age}? If Bernie Sanders is elected in 2020 he would be 80+ when taking office. Considering average life expectancy and the stress of the job, there is a good chance he wouldn't survive 8 years. Prejudiced, yes. Irrational, no.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small You can say what you want about Maher.  Is he an asshole?  Sure.  But he also often makes surprisingly profound points as here in this example. Unfortunately the party that is suppose to be against prejudices and \textbf{racism} doesn't want you if you're an "\textbf{old} white guy".  Ironic isn't it.\normalsize   & \cellcolor{green!5}Old, Racism & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Bill I hate to tell ya this man but California is STILL BROKE and UNGOVERNABLE. SORRY CALIFORNIANS but you're state officials have turned a once gorgeous state into a overflowing \textbf{septic} tank with LIBERALISM.RIP CALI.🙊🙉🙈UNFILTERED UNAPOLOGETIC TRUTH 🇺🇸🕇\normalsize   & \cellcolor{green!27}Septic & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small No one should be respected more just because they're \textbf{old}. You know what young idiots turn into? \textbf{Old} idiots. Respect smart people. They're always getting better with \textbf{age}. When you say \textbf{old} people can't or shouldn't drive, guess what, they always sucked at driving, because they've always been stupid.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/49 & \cellcolor{green!5}8.163 \\  \hline
  \cellcolor{green!27}\small This clip did not \textbf{age} well. California is a shit hole now\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Nothing hotter then a \textbf{chubby} ass 😝\normalsize   & \cellcolor{green!5}Chubby, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small the part about not respecting the \textbf{elderly}, it is such a big problem through out the world\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Yeah, Bill. And what was our cry in the 60s? "You can't trust anyone over 30." Or are you so \textbf{old} and decrepit now you've forgotten?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Bill is full of shit.  \textbf{Jerry} Brown is great at 76. That's great but Trump is 72 and although he never should've been President at any \textbf{age}, twenty years ago I doubt he  needed help finding his car when he was standing right in front of it. By the way, I've seen a few of the women he's dated. For a guy not interested in butts, it strikes me as odd most of his girlfriends can't go through a doorway without hitting both sides.\normalsize   & \cellcolor{green!27}Age, Jerry & \cellcolor{green!27}Age - General, Nationality - German & \cellcolor{green!27}2/84 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Yay for job creation if you're a liberal but if you're conservative you're still a bigoted \textbf{racist} devil.. liberal logic\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Trump is \textbf{old}. That does not make him wise.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I usually agree with Bill, but I don't agree with the concept of wisdom=age. Look at the majority of people who voted Trump: by and large fearful \textbf{old} white people. Then there are the unfortunate consequences of Alzheimer's which can almost literally change an individual's personality. And personally, I don't see baby boomers as having the wisdom of seniors of the past, especially when compared to the WW2/Great Depression generation. That generation made the world a generally better place for their children. The baby boomers have done that with technology; leadership I'm not so sure.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small I love how he says the best one for the job is \textbf{Jerry} Brown while he is sitting next to Bernie Sanders.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Regan was 69 when he first took office. By the time he left office he was deep into dementia. My mother got her drivers license renewed at the \textbf{age} of 90. She did not have to have her vision checked again for 8 years. (By that time she was \textbf{blind}, but she still had a drivers license)There is a point where the human body starts to break down. We can't ignore that. Not everybody ages at the same rate, and there is no magic number, but pretending it doesn't happen won't make it go away. I hope I have the awareness to realize when it happens, but sometimes it doesn't happen that way. Yes, we need to respect the \textbf{elderly}. In doing so we must also realize that a 75 year \textbf{old} man is not able to do things the same way he did when he was twenty.\normalsize   & \cellcolor{green!5}Age, Blind, Elderly, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/149 & \cellcolor{green!5}2.685 \\  \hline
  \cellcolor{green!27}\small if a president is 78 at the start of his term, he is 82 by the end. no, grandpa, that is too \textbf{old}. there are reasons why most people retire in their 60s. 80 year olds are ALL past their prime as a matter of biological fact. america has a problem of electing presidents (and other officials) that are TOO \textbf{OLD}, not TOO YOUNG. even donald trump would not have been as bad a president before his dementia.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Define "fix," SF is covered in shit and needles and almost every street in LA is homeless camp.  On top of that everything is taxed out control and overly regulated.  \textbf{Jerry} Brown is a jackass.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small RBG!!! she was truly a beautiful young woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small "Were wise when were \textbf{old}" is proof the 21st century culturalism has mythology. Some \textbf{old} people are stupid and Bill Mahers favorite stupidity prop is an \textbf{old} man.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small Add ism to anything and it is bad. Fatism. I'm a fatist, I have a prejudice against excessively \textbf{fat} people. I don't trust 'em.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Point to be noted: In India, if you're young , you're probably not good enough to govern the country/state,... All our leaders are \textbf{old}, decrepit and corrupt.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Not exactly the last. It's ok to disrespect short people too. The complete and utter disrespect they get on a daily basis would have most people drinking Drano.. If you're short and \textbf{fat}, for Christ's sake, you're openly begging for ridicule. Kevin Hart is a successful young man, but in almost every every single interview, he's ridiculed because of his height. Fair or unfair?\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small Sounds wrong now that the \textbf{old} Trump is in office. Man has dementia.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Actually, I lived in China for several years. A lot of the people DON'T respect the \textbf{elderly}, and it's getting worse as they adopt the Western lifestyle.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Jerry Brown ruined California! Their economy is tanking, crime is through the roof, they have homeless people galore, shit/piss/needles flowing through the streets, and it's no longer a crime to intentionally infect someone with AIDS....... what are you talking about, Bill???\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small There's a very practical reason for not nominating an \textbf{old} person: they are at a high risk of dying before finishing two terms, and if their VP isn't stellar, then that's a big deal. That was a big reason I didn't vote for McCain in 08. I think he would have done great, but his lifespan was questionable, and there was a very real chance that Sarah Palin could have succeeded him.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small I agree but what happens when your \textbf{old} and look young naturally ?Jill walker\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The legitimacy of \textbf{ageism} is that a 76-year-old for president raises the concern of whether he'll live long enough to see a second term.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small drop dead \textbf{jerry} brown. loser\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small In the sixteys we in Germany elected a 92 year \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Funny, but not all \textbf{old} people are worth a shit. Congress is my point. However, that's more of a brain-dead voter problem than anything.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Funny how Bill didn't make a big deal when liberals went after McCain for age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Jerry Brown broke Califórnia even worse, fool\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I agree with Bill to some extent, but here I believe he falls into the same fallacy that many do. America is not ruled by the young. The millennial generation is only just beginning to assert generational dominance, the political, judicial, military, and industrial leadership of this country is still dominated by the Baby Boomer generation. It's why our country refuses to move forward, because so many of those in power think that progress is a bad thing, that things were perfect when they were young and the key to American success rests in recreating the circumstances of that supposed lost golden \textbf{age}. And this is a cross party problem, our leaders are blinded by nostalgia and ideological entrenchment. Experience is important, but more so is the ability to look forward rather than backward.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small He says \textbf{ageism} is a problem but then says young American voters don't know anything. \textbf{Ageism} applies for both the \textbf{old} and the young.\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/24 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small America is a teenager where Europe is the \textbf{old} guy. Europe has burned itself on the ground on more than one occasion and has finally learned the lesson. Only this America's 'coming to age' story is quite frightening. Just don't burn down Europe along with you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Haha...fast forward three years and look what \textbf{Jerry} Brown's leadership has done to California.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Shut your \textbf{old} ass up\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Wisdom: Youth is fleeting. Don't make fun of others \textbf{age} or generalize older people otherwise you will end up being treated badly when you are older and you will not like it. There are wise young people and wise \textbf{old} people just as there are young assholes and \textbf{old} assholes.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/50 & \cellcolor{green!5}6.0 \\  \hline
  \cellcolor{green!27}\small The president is \textbf{old}, everyone in Congress is \textbf{old}, the supreme court is \textbf{old}, the oligarchs are \textbf{old}, how exactly are young people running everything?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}4/25 & \cellcolor{green!27}16.0 \\  \hline
  \cellcolor{green!5}\small Welp.... This didn't \textbf{age} well.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Yes! \textbf{ageism} definitely exists. I swear, a \textbf{woman} is taught that after she turns 40 her life is over. I know men experience \textbf{ageism} as well. I love this video and I love the honesty. And the ass comment.... Everyone should watch milk milk Lemonade by Amy Schumer. Considering the fact that s*** comes out of her ass would make you think that people would not glorify it. It's a butt, who cares.\normalsize   & \cellcolor{green!27}Ageism, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}3/73 & \cellcolor{green!27}4.11 \\  \hline
  \cellcolor{green!5}\small Let's see him make the same argument about Trump. Trumps just 8 years younger than Brown. Is he as intelligent, or wise? I doubt he'd argue that. \textbf{Age} is relative. As in it's not all that important in regards to intelligence and wisdom. David Duke is 68. How intelligent is he? Or wise? How about the countless of \textbf{old} idiots walking around? Let me guess, they're intelligent too, right? As George Carlin said "Kids are like any other group, a few winners, a whoooole lot of losers" And the same concept can be applied to \textbf{old} people. Intelligence and wisdom can be found across a wide spectrum of people regarding \textbf{age}, the characteristics themselves can be found within people few and far in between.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/124 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Asian are following west , thier was time when student respect teacher and elders but now it's become popular in teenager to call  \textbf{elder} by name. Every society have something good and something bad but we choose bad things.\normalsize   & \cellcolor{green!27}Elder & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small You are a \textbf{dumb} bitter \textbf{old} man bill... young people do not run this country. A ton of \textbf{old} corrupt should be dead in the way fucks run it. That's why this world is as fucked as it is. We keep letting \textbf{old} shitty people put their hands on our lifes. Yea people get \textbf{old} and they should learn how to take that with grace.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/65 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small "Elders" are not all the same, for every wise \textbf{elder} out there there are a dozen who spent a lifetime learning fuck all and drooling in front of a TV. These ones are way past their expiration date and are like sand in the gears of civilization. Come to Europe if you don't believe me, see for yourself the crowds of useless half-dead \textbf{old} people clogging everything up.\normalsize   & \cellcolor{green!27}Elder, Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Measuring success by saying California is "leading the \textbf{nation} in job creation" seems to me like saying we've hired the best chef money can buy and achieved the highest level fine dining experience on the Titanic.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Jerry Brown sucks. He's the same dipshit who legally recognized 3 genders, reduced the penalty for purposely infecting people with AIDS, and criminalized misgendering people.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small We live in an \textbf{ageist} society it's just the way it is I don't see it changing anytime soon\normalsize   & \cellcolor{green!5}Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Right on!!! They can be mean too. I stop young'ns who imply I'm \textbf{racist} because I don't like rap with, "Who are your top five favorite classical composers?" Who do you like more? Ella or Sarah? And on and on. Pop culture has been reduced to bad overworked tripe. Better stop here before the wolves arrive....\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Just out of curiosity, does Bill have \textbf{sex} with women his own \textbf{age}?Just asking...Honestly, I prefer much younger women myself.\normalsize   & \cellcolor{green!5}Age, Sex & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small It's  about how likely a person is to die of \textbf{old} \textbf{age} while president....not that they can't do a good job. A wonderful example of SWING AND A MISS! from Bill Maher.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Jane Fonda looks 40...???!!! Errr.....No. No she doesn't.  To me,  she looks around 65.  An incredible looking 65 year \textbf{old}, but 65 nevertheless.  To say she looks anything close to 40 is just ludicrous!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small The problem with \textbf{age} is that senility is also present. Just look at Trump.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Bill, what the hell are you smoking?  It's a pretty safe bet that the 2016 slate of U.S. presidential candidates is the oldest on record.  Donald Trump was 70 years \textbf{old}.  Hillary Clinton was 69.  Jill Stein was 66.  Gary Johnson was 63.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Maher: \textbf{Age} means wisdom and maturity in governing.Trump: Hold mah beer....\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small It is ironic that Bill make fun an overweight politician when he is complaining about \textbf{ageism}.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I voted for \textbf{Jerry} Brown\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Oh, STFU Bill Maher. You're just butt hurt you're an \textbf{old} fart now.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Generation ass,  has the most \textbf{fat} people ever.. and now you can't even tell them their \textbf{fat} so imagine the way that's gonna trend.. So yes, they are obsessed with sexy asses because they're not easy to come by...\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Three and a half years later, he has 17 year olds on his show who think, because a \textbf{crazy} person pointed a gun at them, that they're suddenly policy experts on the second amendment and gun control... hmm...\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small 😒 wth is Bill Maher talking about, the "youngest" president in US history was Teddy Roosevelt at 42...ALL our presidents have been \textbf{old} people. Is it so wrong to ask for a younger president at some point? Is this really what you call discrimination? 😒 sthu Bill Maher\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small love how bill says this about ass when he constantly dates \textbf{black} women who all have it...apparently he is attracted to it too...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small What the fuck is he talking about California is almost bankrupt more people left than came for the first time in history. Why does he lie to push an agenda it bothers me because I liked him when he was a true libertarian. Now he's a socialist the true disparity  one ruling rich class and a bunch of broke people. Unless he's confused on what it really ends up being . Sad he used to make sense sometimes. But \textbf{Jerry} brown? Ouch\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small nah, \textbf{fat} is too\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small This video didn't \textbf{age} well\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small He can joke about Asians, but imagine the trouble he would've been in had he joked about say \textbf{Black} people?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The youngest president ever was 42 years \textbf{old} when he got elected. The oldest, was 70. There has never been a "young" president. There probably never will be. So what exactly is he complaining about?  Dude probably just realized he was in his 60's at this point.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Jerry Brown? Competent? HA!!!\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Oops, I guess \textbf{fat} jokes are ALSO acceptable.  Just sayin.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Well Trump is 71 years \textbf{old} so I don't think it was \textbf{Ageism} at the polls.   More like an Aneurysm .\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Yes. He makes this video about the "discrimination against \textbf{old} people," and how we venerate young people too much, and don't take older people seriously, and how young people can't have our government, yada yada yada.Yyyyyyet, he had no qualms with having a bunch of kids on his show to speak about gun legislation/gun control. 🤔\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small What the fuck happened to Lorde by the way, she's basically my \textbf{age} but she's not looking too hot anymore, in both senses of the word\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small This video is \textbf{OLD}!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small go figure the \textbf{old} capitalist pig wants more privlidge for the boomer \textbf{faggot} generation who ruined america and gave us trump\normalsize   & \cellcolor{green!5}Faggot, Old & \cellcolor{green!5}Age - Over 65s, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small I'm no republican but I can tell you one thing from being an independent \textbf{Jerry} brown is causing California to go bankrupt. Lol. Those high taxes are a butch but they get the job done. The problem is there is to many state programs causing too much spending. Decrease that shit\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small oi \textbf{ageism} goes both ways\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small He's arguing against \textbf{ageism} by using \textbf{ageism} lol tf\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small The Last Acceptable Prejudice in America is against short people and maybe \textbf{R\textbf{ed}} Heads...\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Actually, the "other" accepted prejudice in America is White Males. It's just fine to bash the crap out of White Males, but god forbid you say anything about a Female, Minority or \textbf{Homosexual} \& you are labeled a Sexist, \textbf{Racist} \&/or \textbf{Homophobic}.\normalsize   & \cellcolor{green!27}Homophobic, Homosexual, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}3/42 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small quite frankly, I could care less what anyone says about me personally. If you choose to hate me simply because i'm a White Male, that's YOUR problem, not mine. My original point was that it's still acceptable to attack White Males, so it's not just \textbf{old} people.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Soldado vii would you like some cheese with that whine? Maybe you need your diaper changed, ya baby! Go cry somewhere else about how bad the rest of the world has it. Looks like you are a \textbf{Snowflake} who got butt-hurt by the truth. Please head to your nearest "Safe Space" and proceed to cry all you want about how unfair life is. I am done with you, child.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Ageismsure, give facts a name, but that doesn't mean people that are really young or really \textbf{old} will always be the same as someone in their 20s. This is petty, this is the type of scum that clickbait tabloids use to get clicks.\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Jerry Brown fixed California? Too bad \textbf{nobody} told us.\normalsize   & \cellcolor{green!27}Jerry, Nobody & \cellcolor{green!27}Age - Youngsters, Nationality - German & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small You made \textbf{age} jokes about McCain when he ran for president... hypocrite\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "\textbf{Ageism} is bad, and here's why millenials are all asses."\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small so a white \textbf{woman} can swim from cuba to florida and not get eaten by sharks, but cubans cant? why aren't the white suprematists jumping on this fascinating tid-bit? LMFAO. just kidding -- on a side note, since you dont like letting the young run everything, shut that Hogg kid up already!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small 4:50 if you cant see the appeal of a nice big round ass than you really are old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I too don't understand the obsession with  the human 'ass', today's generation music is all about, ass, drugs, \textbf{sex}  etc........ eehh\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small jerry brown is and \textbf{old} baby boomer who should retire now being in his late 70's like Joe Biden\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Yeah, I get it. But, when all there is, are dumb-asses, smart-asses, and genie-asses, The \textbf{common} denominator is jack-asses. So, does it really matter?\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} is Trump?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small "English as a second language" ?  So it's okay if Maher says \textbf{racist} things?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small ageism is so much worse in Asia... Here in Japan, if you're over 22 and a \textbf{woman}, you can barely get on TV... all girls have to be pretty and act dumb\normalsize   & \cellcolor{green!27}Ageism, Dumb, Woman & \cellcolor{green!27}Age - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/32 & \cellcolor{green!27}9.375 \\  \hline
  \cellcolor{green!5}\small Bullshit - everyone considers \textbf{age} and judges according.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Governor \textbf{Jerry} Brown of my home state of California I was born there I was  raised there in the Southern and the northern is turning the state of California into a shithole repeat a SHITHOLE  in capital letters\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Ageism in the other direction is a problem, too. No one takes young people seriously. Just take this segment for example. Shitting on millennials is easy the same way making oldie jokes is. Look at Congress. I doubt anyone in there is younger than 97 for fuck's sake.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small I thought the problem was \textbf{elderly} people like Jeff Sessions who won't hear any facts that were written after 1960.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small age has no direct correlation to wisdom. experience however does.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Democrats are looking more and more at Biden despite his 75 years, but I think that is fueled partly by desperation to get a Dem, any Dem, back in the White House.  Won't do much good, though if they don't also give him either the Senate or House.  I would vote for \textbf{Jerry} Brown in a heartbeat, but he is now 79, so I would also need to like his choice for VP.  The job is massively stressful, and \textbf{age} could very well matter.  And he, too, would need a Dem Senate and/or House in order to get anything done.\normalsize   & \cellcolor{green!27}Age, Jerry & \cellcolor{green!27}Age - General, Nationality - German & \cellcolor{green!27}2/100 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small With \textbf{age} comes wisdom. Too bad the young innocents are driving the bus today: Over a cliff!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Bill Maher: \textbf{Jerry} Brown 2016!While sitting next to Sanders. lol\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small How did you react when your wife divorced you? What did you feel the first time you got fired from a job? Remember the pain you felt when your son died in a car accident his \textbf{senior} year of high school? What was it like living in a world before computers? Last time we went to war, what were some of the concerns you had as a general? and how did you over come them?   How difficult was it when you were a child with \textbf{nothing} compared to now when you have made something of yourself?  Its cool to memorize a textbook, it doesnt make you intelligent. Living life and learning from past mistakes and experiences is what makes you intelligent. Did you see the story of the student who ran onto the desk at his college board of directors, sat down and demanded everyone listen to him? He thought he was intelligent, but he wasnt, and next time he wants to make a point, he will learn from his experience and try a different approach. Thats why children and 20 year olds arent qualified for office. They dont know what they dont know.\normalsize   & \cellcolor{green!5}Nothing, Senior & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}4/194 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small Funny that your rant about \textbf{ageism} was entirely \textbf{ageist} against younger people. Maybe the most competent people should be praised regardless of \textbf{age}?\normalsize   & \cellcolor{green!27}Age, Ageism, Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/23 & \cellcolor{green!27}13.043 \\  \hline
  \cellcolor{green!5}\small Young people are not denied opportunities like \textbf{old} 80 yo people\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Right, so let's just keep letting the \textbf{old} assholes stay in charge. Because that generation is doing such an amazing job.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Year 2018, you've got an \textbf{old} fart in the White house!  FINALLY HAPPY NOW BILL?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Ironic that Trump is the oldest President ever elected... wisdom doesn't always equal \textbf{age}, Bill. I get the point though.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Add being a ginger to \textbf{ageing} for acceptable prejudices.\normalsize   & \cellcolor{green!5}Ageing & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Bill Maher sounds like a grumpy \textbf{old} man who doesn't like/understand our generation. It is not like millennials are 100 to blame for the way we turned out. And it really isn't true that our generation are the only ones guilty of the many different negative things, that people tend to attribute solely to us. There are plenty of immature "adults", from many different generations, who act just as shitty as the average millennial. Can we stop being so divisive over things like \textbf{age} and start trying to solve real problems? All of these over generalizations and shit talking media personalities, are not helping...\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small i disagree, there should be a too \textbf{old} for president, just like there should be a too young. People who have just started or are about to end life are on the fringes of society and shouldn't can't make knowledgeable decisions for the rest of us\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Yep. Ronald Reagan was 70 when he took office and people thought the "war hawk" would lead us to Nuclear war, but instead his \textbf{age} and experiences helped him understand how to negotiate with Soviet leadership and under his watch the cold war came tumbling down. I also think \textbf{Jerry} Brown is doing a great job as governor of California (not perfect, but pretty damn good).  I'm younger(ish) and I like having someone who isn't angling for their next position as the leader. It frees them from so much stuff where they can just act on what they truly feel is best.\normalsize   & \cellcolor{green!27}Age, Jerry & \cellcolor{green!27}Age - General, Nationality - German & \cellcolor{green!27}2/102 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Talks about \textbf{ageism}, yet constantly craps on millennials\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small '78 shouldn't be too \textbf{old} for president' but what about a 22 year \textbf{old}. The real agism is to assume that REAL young people cannot do the jobs as well as or better than their older peers.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Age is NOT a "social construct". Young people are young. \textbf{Old} people are \textbf{old}. Deal with it.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small Race for presidency there starts 2 years before the actual election, half of the presidential term? OMFG! Do I find that's \textbf{weird} only because I am a foreigner?\normalsize   & \cellcolor{green!27}Race, Weird & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I am a Republican in California.  I have to say, \textbf{Jerry} Brown is pretty good for a Democrat.   He is wrong on a lot of things like High Speed rail and the secret gas tax.  But overall, a good governor.  I voted for Arnold and was disappointed with his global warming policy as well as his backing down on a lot of things like Tribal Gaming revenue sharing. IF \textbf{Jerry} ran for President, he would get my serious consideration (regardless of \textbf{age}).  Still glad Hillary lost, she would have taxed us into the ground and got us involved in war.\normalsize   & \cellcolor{green!5}Age, Jerry & \cellcolor{green!5}Age - General, Nationality - German & \cellcolor{green!5}3/100 & \cellcolor{green!5}3.0 \\  \hline
  \cellcolor{green!27}\small Ageism is every where. I am glad Bill is talking about it.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small He makes some good points but I think he's strawmanning a bit here.  First of all, \textbf{Jerry} Brown never even put his hat in the ring for president and secondly, the most popular candidates in the 2016 election were all in their late 60s or 70s.  When it comes to politics I think there's a more \textbf{ageism} against younger candidates than older ones, but even then I don't think it's that strong.  I also think it's ironic that Bill implies here that Hillary was incompetent but suddenly thought she was the greatest after she "won" the Democratic nomination.  I totally agree with the ass thing though.  I'm a millenial and I think asses are gross (I blame \textbf{black} culture for that whole fetish).  I'm still a boobs guy.\normalsize   & \cellcolor{green!5}Ageism, Black, Jerry & \cellcolor{green!5}Age - General, Ethnicity - Black, Nationality - German & \cellcolor{green!5}3/128 & \cellcolor{green!5}2.344 \\  \hline
  \cellcolor{green!27}\small Making fun of \textbf{fat} people is the last acceptable prejudice - not \textbf{ageism}. Bill exemplifies this right in this same clip.\normalsize   & \cellcolor{green!27}Ageism, Fat & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Only \textbf{old} people would GET the Betamax joke.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Well,we got an \textbf{old} man in office.He damn sure isn't wise.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small not really old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Just cause bill is getting \textbf{old} he is feeling the grasp of funnier and smarter comedians.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I'm with Bill when he says that \textbf{ageism} sucks and is wrong. But how many of you feel that it can go both ways were we cannot only judge are Elders accusing them of being stuck in their ways when many are not. But also the youth were we accuse them of being full of nativity when many are not.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Bill must be eating these words now, \textbf{Jerry} Brown has RUINED California... then again it was already a giant sink hole with Liberals and moronic celebrities\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small also people love hating on millennials but guess what we aren't the generation that has put countries into millions of dollars of debt that guess what the younger generation now has to pay off. you \textbf{old} fucks are the ones destroying the world not us. so fuck off on blaming the younger generations, yes they are \textbf{dumb} but we are not the ones responsible for the problems in this world. we are just the ones that have to clean up after you \textbf{old} fucking retards\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/85 & \cellcolor{green!5}3.529 \\  \hline
  \cellcolor{green!27}\small AGEISM IS PREJUDICE, exc when it comes to john McCain and his candidacy , then it was ok to make jokes\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small The \textbf{elderly} shouldn't be respected because they are \textbf{elderly}. They should be respected if they do something respectful as all people from other ages.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I love ass and I'm not a millennial. Maybe it's because I'm \textbf{Black} then.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small LOL, Bill you are a riot and right on about the \textbf{age} bit.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small ya its too bad we dont respect our \textbf{elder} like we should they know more than us and they can teach us\normalsize   & \cellcolor{green!27}Elder & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small " That's life ... you're beautiful when you're young and you're wise when you're \textbf{old}. Only we don't get this. Our culture is shallow, because we don't respect the \textbf{elderly}. We venerate the young and let them rule everything! " Bill Maher\normalsize   & \cellcolor{green!5}Elderly, Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small stay salty bill, you \textbf{old} timer, LOL\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Age is relative. Hillary goes all over the world, endured 11 hours of Congressional testimony in which she let the Republicans look like hyperpartisan idiots and she smiled through much of it, and, in spite of talk about how she was "dying," she's fine.Trump is just a year older, 70, and after 48 hours of his first foreign trip as Fake President, he's "exhausted."\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Why are you using terms as \textbf{ageism} and millenials? That's crap: you should rather talk about excesses of unwitted edonism and lacks of understanding.Why are you Americans so much damn obsessed with making fashionable neologisms as if you were making fun of Ancient Greek? That's silly as hell!\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small "\textbf{Ageism} is the last acceptable prejudice in America", Bill says, whilst casually fat-shaming Chris Christie to the laughter and approval of his audience.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small How do the young run everything?? 90 of all govt positions are retirement \textbf{age}! And the youth all voted for BERNIE!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Well,  Tump heard Maher !!!    And, here we are with an stupid, moron, \textbf{racist}, etc.,etc.,etc.,........\textbf{old} man !!!\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small "So soon \textbf{old}, so late smart." Supposedly that's an \textbf{old} Chinese adage.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I agree with Bill that butts are overrated, but I'm disappointed that he seems to think younger people have every advantage. I notice that no one ever cries "\textbf{ageism}!" about any \textbf{age} group besides the \textbf{elderly}. Children (and maybe other \textbf{age} groups, too) are treated worse because of their \textbf{age}. Very rarely do you hear about this.\normalsize   & \cellcolor{green!5}Age, Ageism, Elderly & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}5/57 & \cellcolor{green!5}8.772 \\  \hline
  \cellcolor{green!27}\small Well the overwhelming amount of voters who vote for people like trump and Bush are older....so there is something to \textbf{ageism} for certain.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Ha! \textbf{Old} \textbf{age} don't scare me! I've always been ugly\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Right, young people run everything, except the government!  The average \textbf{age} in congress is 58, and \textbf{old} people have the largest voting presence out of all \textbf{age} groups.  I'm honestly not sure what Bill Maher is talking about there, he's complaining about a nonexistent problem, young people aren't taking over the government.  At least not until all the \textbf{old} people die.  I agree that \textbf{ageism} is \textbf{dumb}, but he's being kinda \textbf{ageist} against young people.\normalsize   & \cellcolor{green!27}Age, Ageism, Ageist, Dumb, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/75 & \cellcolor{green!27}9.333 \\  \hline
  \cellcolor{green!5}\small As a Californian who has voted for \textbf{Jerry} Brown every time I've had that opportunity, I agree with Bill Maher that \textbf{age} shouldn't disqualify him from serious consideration as a candidate for President. Having just viewed this video for the first time, 101 days into the Trump presidency, it's sadly ironic that America took  part of Bill Maher's advice and elected its oldest president ever. Bummer.\normalsize   & \cellcolor{green!5}Age, Jerry & \cellcolor{green!5}Age - General, Nationality - German & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Jerry Brown brought CA out of Dept and fixed CA?  It has the highest dept of any state! I hope you live there Bill, it needs your tax money.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small There is that \textbf{age} that is  "too young to retire and too \textbf{old} to hire." < that spells "homeless"\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small EOE on applications is just a formality. You can't prove that an employer won't hire you because you're too \textbf{old}, or for any other reason.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Fat is the last acceptable prejudice!!!!\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Wait... \textbf{Jerry} Brown "took a broken state and fixed it". Really? When? California is in the worst shape right now that it's ever been in!\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small I would say physical appearance is just as acceptable as \textbf{age} when it comes to prejudice.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Yes because the last years of Reagan were such a success.You really should see, that if someone reached a certain \textbf{age} over their seventies, a stressfull job like being the President of the United States, will take their toll with any person over 70. There are serious dangers of having a President who is going to be unfit for office. A President should be able to lead the country at any time and not just between their hip replacement operation and their when they are high on stomach pills.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small This seems very ironic now that \textbf{old} man Trump is president..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small If the young ruled EVERYTHING, they could afford their education. Instead there are these \textbf{old} farts who got their education for A LOT less money who make stupid decisions for them.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small "\textbf{Ageism}, the discrimination against people based on \textbf{age}" Also, "Young people are terrible and the things they like are terrible" ok mango.\normalsize   & \cellcolor{green!5}Age, Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Why does everyone call a problem or prejudice "the last" when it's the one that concern them? Human being have always being disgusting to each other and it's not because lately the labels of \textbf{racism}, \textbf{homophobia} and \textbf{sexism} have become unacceptable socially that it means we fixed every goddamn problems with how people think.Look throughout history, every civilization think themselves as superior by looking at what they accomplished while ignoring the horrible things they still support. Doesn't matter if you think you're a saint, you're doing or at best supporting horrible things like every other human.\normalsize   & \cellcolor{green!27}Homophobia, Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General, Sexual Identity - General & \cellcolor{green!27}3/97 & \cellcolor{green!27}3.093 \\  \hline
  \cellcolor{green!5}\small None of you Lefties give a shit about \textbf{disabled} people either.  Not oppressed enough for ya, even though they're the only group with a legit case to be taken care of by the state if their families can't.  Pathetic.\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small And two years later America elected a man who is \textbf{old}, \textbf{dumb} and full of cum.\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Older \textbf{age} is something we should celebrate. The \textbf{elderly} are wise, far beyond that of youth. We need that in our society desperately.\normalsize   & \cellcolor{green!5}Age, Elderly & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small TIL, people like Mitch McConnell, John McCain, and Donald Trump are millennials.I find this a bit hypocritical though. I don't disagree that being \textbf{old} proves anything, but he's trying to "prove" it by comparing non-senile \textbf{old} people with cherrypicked idiot young people. Don't complain about \textbf{ageism} and then go on to say "young people are stupid and inexperienced and should move aside for the adults".\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/66 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small 2:45 Uses \textbf{fat} shaming, while complaining that \textbf{ageism} is the last acceptable prejudice.\normalsize   & \cellcolor{green!5}Ageism, Fat & \cellcolor{green!5}Age - General, Physical Identity - Physical Features & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small try being older \textbf{woman}, completely dismissed or shunned\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small We dont respect \textbf{elderly}.. never thought i would agree with atheist.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small old fart. set in his ways. will not adapt.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Average \textbf{age} in Congress is 60 - don't think having older people in power is the problem. Having the wrong people in power is the problem.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Is that the \textbf{woman} from friends\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small WTF? US Senate is full of \textbf{old} people. The \textbf{old} rule the country. The president is 70 years \textbf{old}. WTF ARE YOU TALKING ABOUT BILL?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/25 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small I am going to have to disagree with this, \textbf{Age} is not just a number. Your \textbf{age} means a lot and there are certain things you should just stop doing once you reach that \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small A baby-boomer has the nerve to claim that it's time to respect the \textbf{elderly}...\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small As a foreigner, I watched a lot of American cartoons and I was alarmed to see how many times "\textbf{old} senile people doing ordinary things \textbf{old} senile people do" was used as a joke. Not only was it a cheap gag and seldom had any wit put into it, but I was alarmed because you never do that where we come from. It's not even unconditional worship and respect for the \textbf{elderly}. Over here it's considered like fatshaming in America: a social taboo. Actually it's worse than fatshaming, because some mean people still do that. Because unlike \textbf{age}, some people do avoid becoming \textbf{fat} and feel no guilt for pointing others' obesity out. Everyone knows they will grow \textbf{old} someday, and you just don't make fun of it.I know \textbf{age} can be a double-edged sword, but at least it shouldn't be a RESTRICTION to governing.\normalsize   & \cellcolor{green!27}Age, Elderly, Fat, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}7/146 & \cellcolor{green!27}4.795 \\  \hline
  \cellcolor{green!5}\small Ageism is a joke. My grandad is 80+.... Letting him drive is fucking scary! It's like rolling dice at a Casino! Let us hope he doesn't roll against the house!\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Yes the \textbf{old} are wise. Tell that to Trump, tell that to does in Congress whom are Republicans. Who want to live in their 50s and 60s. All this \textbf{old} hags hate progress and technology because they don't understand it. More \textbf{old} hags voted for trump and \textbf{Brexit}. We the young want respect for other we want to travel freely and have a better wage like our father and mothers. But because of their idiotic way of choosing Congress man and getting distracted from the really issues they voted for Bush and Trump. WISE \textbf{OLD} PEOPLE DIE ALREADY.\normalsize   & \cellcolor{green!27}Brexit, Old & \cellcolor{green!27}Age - Over 65s, Nationality - European or anti-Europeans & \cellcolor{green!27}5/98 & \cellcolor{green!27}5.102 \\  \hline
  \cellcolor{green!5}\small just as much \textbf{dumb} \textbf{old} people out there. by the way, when McCain was running, he used the "too \textbf{old} card" too\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/22 & \cellcolor{green!5}13.636 \\  \hline
  \cellcolor{green!27}\small Sorry Bill but 78 is too \textbf{old}. If we get a candidate into office we're hoping for him/her to last 2 terms or 8 years. Average life expetency is 87. Brown would be 90 by then which means, statistically speaking, dead a year into his 2nd term. Balance of probability makes him a poor choice.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small your hot when young and wise when \textbf{old} B-)B-):-P\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Oh boy.. I think the baby boomer generation has amnesia. They were just like us once too with the free love hippy thing back in the 60's. I've seen Woodstock footage. \textbf{Nothing} more than young dirty naked \textbf{sex} crazed young adults and teens on acid and everything else. Just a little fyi, you do realize that those dirty hippies are now teachers and professors teaching this generation. Also a lot of the reason the youth of today are so fucked up is because the pryor generations have dropped the ball and failed at maturing themselves. Stop looking at the symptom of the problem and look at the cause. The \textbf{old} generation has become like their parents who pointed the finger at them when they were young.\normalsize   & \cellcolor{green!27}Nothing, Old, Sex & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Gender - General & \cellcolor{green!27}3/126 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small He says this right next to the best of all possible \textbf{elderly} candidates.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Bernie sanders laughed at the Asian are shit drivers joke.  Is he \textbf{racist}?   No he's just awesome\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small ageism and \textbf{racism} against whites. both are acceptable to most idiots\normalsize   & \cellcolor{green!5}Ageism, Racism & \cellcolor{green!5}Age - General, Ethnicity - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Oh, \textbf{old} people have it so hard. You know, with all the money, property and power.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small atheist are actually more hated in America than \textbf{old} people look at everyone in gov all \textbf{old} but no atheist. Y U NO SEE THIS\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small In Sweden the \textbf{ageism} is the same.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Are you serious? Asian drivers gets a laugh before the audience figures out that they should applaud? What a joke. \textbf{Ageism}? \textbf{Mental} degradation is a fact. I don't trust that someone who's that \textbf{old} wouldn't have \textbf{mental} instability or at least have a hard time reasoning in coming years. We can't all of a sudden say 'shit, he went crazy' and revoke the election results. Donald trump is a prime example of checks and balances really not being enough. Fuck off. Someone who's older has so much more experience than the rest of us and that experience should be greatly valued...with a lens on. Don't give that person power to speak to the impressionable in absolute terms. If we know for a fact that that person has been cleared of all \textbf{mental} instability...I'm for it. This isn't \textbf{ageist}. It's fact. I won't apologize for \textbf{mental} health declining in older people. Serve as an advisor, absolutely! \textbf{Age} is a deterrent for high positions in office that is just makes scientific sense.\normalsize   & \cellcolor{green!5}Age, Ageism, Ageist, Mental, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}8/170 & \cellcolor{green!5}4.706 \\  \hline
  \cellcolor{green!27}\small Poor bill Maher, 70 year tump, the oldest president ever, was elected and proved everything he says here wrong AND tump was elected with the votes of every white guy over the \textbf{age} of 45 and their wives. Doesn't say much for wisdom of the aged does it? We don't worship youth, we worship money and its rejuvenating effects. And women are still seen more as ornaments and less as people. Until millennials are the \textbf{age} of today's baby boomers women will still be viewed through the prism of their looks. Money is our God.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/95 & \cellcolor{green!27}2.105 \\  \hline
  \cellcolor{green!5}\small Moses recognized the pitfalls of \textbf{ageism} when he wrote the fourth commandment, the only commandment with promise.  If we honor our parents, our elders, we will live long on the earth.  Well, that only makes sense.  The more we honor our seniors, the more we learn from them.  We then have more knowledge on which to base our decisions.  We don't die right away because of something that should have been learned in kindergarten.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small Anti-intellectualism is much healthier in the US than \textbf{ageism} could ever be.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small "\textbf{Ageism} is the last acceptable prejudice in America."Actually, no it's not. ... It's ATHEISM.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small He consciously made a \textbf{racist} joke about Asians, then without irony made a \textbf{fat} person joke.There are several acceptable prejudices left in society such as against ugly or \textbf{weird} people, and apparently \textbf{fat} people.\normalsize   & \cellcolor{green!27}Fat, Racist, Weird & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}4/35 & \cellcolor{green!27}11.429 \\  \hline
  \cellcolor{green!5}\small Ageism is real, yes. Not against the \textbf{old}. Not at all. It's actually against the young. You need any evidence? Look above for the first reference\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Then why were so many Presidents in the last decades beyond retirement \textbf{age}? Take Reagan and both Bushes as examples.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Sure, \textbf{ageism} isn't a problem is it? Half the people fucking up the country right now are \textbf{old} ass baby boomers trying to recreate pre world war 2 conditions...you are out of touch!\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small It's not about the human ass, it's about young chicks with huge \textbf{fat} asses. \textbf{Weird} fad.\normalsize   & \cellcolor{green!27}Fat, Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I know why Lorde looks so \textbf{old}. It's a big conspiracy.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small All I know about \textbf{Jerry} Brown is that the Dead Kennedy's don't like him much :0\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small young people run everything, here's a picture of Ruth Bader Ginsburg a 200-year \textbf{old} Supreme Court justice has been serving for a hundred and fifty years just like every cunt. he's funny but I swear to God it's so hard to hear him speak.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Senility is a thing and \textbf{old} people are bad at changing their mind and learning new things. We should be careful with very \textbf{old} people, just like we are with very young people.Maher is kind of a liberal Bill O'Reilly. We don't venerate \textbf{old} people enough?! Bullshit. At the head of every significant movement is some \textbf{old} person. Every political school of thought has some \textbf{old} geezer, they look up to. And if they don't, it's just because he, or she, has died lately.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}5/85 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Ageism can be directed towards younger people too. Young people are often underrated and underrepresented. My generation can be pretty stupid, but there hasn't been a generation that hasn't been seen as stupid by the previous generations. Obviously there are challenges the \textbf{elderly} face in this country, but young people face challenges too. Millennials have gotten a bad rap, but we aren't so bad. Some of us might be more intelligent and level headed than you think. I think we all have things to learn from each other.\normalsize   & \cellcolor{green!5}Ageism, Elderly & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/88 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small While Maher definitely makes good points, this certainly goes both ways. Yes, some people might think that at 78 you become too \textbf{old} to be in government, but the same is true for young people too. Many different people assume that just because a person is young they are immature, inexperienced, and ill-fit to do any job of value. This may be true for some, but we shouldn't generalize it.Instead of worrying about whether or not someone is too young or too \textbf{old}, we should start worrying about how qualified they are. Because no matter how \textbf{old} someone is, they can still be stupid, but they can also still be relevant and experienced, and no matter how young someone is, they can still be intelligent, but they can also still be inexperienced and unprepared. We honestly should stop generalizing in a lot of different aspects...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/146 & \cellcolor{green!27}2.055 \\  \hline
  \cellcolor{green!5}\small Ageism is a real problem in this country. Women who go on rants about older guys that date younger women of legal \textbf{age} are some of the most vocal ageists in this country. How about letting two people that are the legal \textbf{age} of consent love each other without judging and labeling them.\normalsize   & \cellcolor{green!5}Age, Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/53 & \cellcolor{green!5}5.66 \\  \hline
  \cellcolor{green!27}\small old people rule the world, what the fuck are you talking about?and the ass-hype is great, i'd rather have young girls do squats than starving themselves to death because the generation before them somehow turned from Marilyn to \textbf{Twiggy}.\normalsize   & \cellcolor{green!27}Old, Twiggy & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I am getting the wibes that Bill is not much of an ass-manI suppose the biggest irony is that America did get  unusualy \textbf{old} president, only this one came without the wisdom\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Jerry Brown would have made a great president\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Well Bill you know what they say, \textbf{fat} bottom girls make the rocking world go round.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small "young \textbf{dumb} and full of cum' - what a line Bill\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Fat ass, that's all a \textbf{woman} is for this generation, that's the point bill is making! Degradation, women degrading themselves and those type of men that find it attractive!\normalsize   & \cellcolor{green!5}Fat, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small \@Deepa Shrestha a nice ass doesnt have to be \textbf{fat} to be nice, but a nice ass is a nice ass you know\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I don't know...\textbf{old} people also constitute the avg fox news audience\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small let me critize young people for generalizing \textbf{old} people, then generalize young people calling them the "ass generation".\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Shut up Bill Maher, you \textbf{old} fuck.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Fuck \textbf{old} people\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small ah, the good \textbf{old} days.2014\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small and American politics are being run by \textbf{old} white men so I don't know what he is  talking about\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small How did I know since bill is \textbf{old} it would be \textbf{ageism} against the \textbf{old}? The people who remember the police as protectors, have a reasonable retirement \textbf{age}, and still have social security. The \textbf{old} people fucked the current generations opportunities and then want to blame us for not being as successful. Even though we're more educated we have a lower standard of living compared to my grandparents era.  Years ago when YT would publicly show viewer stats I would laugh that I somehow always ended up watching the vids that were popular with the 55-64 group. (significantly older than me)"We venerate the young and let the rule everything" uhhhh what? Evidence? You point to young attractive female asses? If I wanted to claim \textbf{old} people rule everything I would point towards voter turnout, the people's elected/appointed representatives. avg \textbf{age} of management, ect ect ect.\normalsize   & \cellcolor{green!5}Age, Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}7/146 & \cellcolor{green!5}4.795 \\  \hline
  \cellcolor{green!27}\small Meanwhile, how \textbf{old} is Trump?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small nathan van 't hof 71 years of \textbf{age}!😯\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I work in retail and my rudest costumers are the \textbf{elderly}. excuse me if I'm hesitant.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Jerry Brown making California the number one state in job growth bill you need to wake up 😂😂 clown brown is killing this state jobs are fleeing because of our high taxes\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small a 70yr \textbf{old} proud moronic douchebag is now president. I guess \textbf{ageism} is one thing where the right are actually more progressive than the left?\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Ageism exist no matter how many bevery hills' surgeons try to hide it\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Jerry Brown... oh yeah the guy who regulated cow farts because they contribute to global warming. He definitely lives in the real world.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Are you fucking \textbf{dumb}? The methane released from cows is worse than the CO2 from fossil fuels. Have you even seen the UN report on this?  Or are you one of those Alex Jones nuts?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small oh yeah, and storing the methane in special fart boxes is going to help save the planet from evil carbon emissions and cow farts. The UN is bullshit, global warming is bullshit and you're criticizing people who listen to Alex Jones when you listen to a guy like Bill Maher. He's fucking entertainment news buddy, he's no better than SNL or comedy central. The only difference is that Maher is allowed to drop the F bomb and he was fined 1.7 million for smoking pot on live television. who's the \textbf{dumb} one?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/92 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small Not all elders deserve respect.  Older does not always mean wiser.  I have the utmost respect for most of the elders on my street.  Especially the ones that lend friendly advice on life to the younger generation  (myself included).   But there are those others.....  Like the damn near 60 year \textbf{old} man that kicked and dented my car because he was playing loud music in his truck, and I nicely and respectfully asked him to turn it down.  I guess every demographic has it's 1 percent.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small No, this is America being changed by other cultures, in other countries, the ass is the prefered part of \textbf{woman} body, in latin countries being more specific, and, unfortunately, It has become part of american culture now. Because the people that are in evidence in this days in show business.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Said the \textbf{Old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Ass fixation is an \textbf{African} trait, it basically means I'm healthy and I have food, twerking is an \textbf{African} fertility dance.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Oooooh. I see Bill touched a nerve with all the "Generation Assers" responding here with offense. The young hates the \textbf{old} because they fear what they see they will become in a few years.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small eh, I don't take \textbf{age} into consideration when voting.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small If the Democrats had nominated someone like \textbf{Jerry} Brown, they could have annihilated Trump.But because Clinton got the nomination, there's an actual chance that this nut bag could become the Commander in Chief.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small for once bill Maher is wrong.  Come to my country and see what respecting the \textbf{old} got us.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Yes, respecting \textbf{old} people is why Ethiopia is poor...not Mengistu, not corruption from Meles and Desalegn, its respecting \textbf{old} people. Dedeb\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Opposes \textbf{ageism}, proceeds to generalize about millennials. 🤔\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Connor Ferrand much like how \textbf{black} joking about white people seems to be less \textbf{racist}, \textbf{old} people making fun of young people also seems to be less "\textbf{ageist}".\normalsize   & \cellcolor{green!5}Ageist, Black, Old, Racist & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/28 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Yeah, he should have made the case that you should judge a politician based on his or her character, not by their \textbf{age}, \textbf{sex} or the color of their skin. Instead he made the case that the more \textbf{age}=better which isn't in any way shape or form true. Also don't care about these people who use the classic, it's just a joke argument when we know that Bill Maher does't lie to make a joke, he tries to make a good point while being funny just like George Carlin and sometimes, he fails which is fine. We should, however, be able to point out the flaws in his arguments without there being cop out excuses.\normalsize   & \cellcolor{green!27}Age, Sex & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/115 & \cellcolor{green!27}1.739 \\  \hline
  \cellcolor{green!5}\small Isn't the \textbf{ageism} coming from millenials???\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Yep, Millennials invented \textbf{ageism}!  :)\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small And makes \textbf{fat} jokes all the time\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Didn't know we ran everything.. Bill is an idiot at any age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Ah,Yes. Another double edged sword to be added to the arsenal of intolerance. \textbf{Ageism}. Unfortunately when this works against the younger generations it isn't taken very seriously or heard of much.Florida quite likely has the largest population of people who are retired or are at least of retirement \textbf{age}. Because many of them are retired and have no need to work a consistent job. They have more time than most to allocate toward influencing county and state legislature naturally biased in their favor. This consistently includes cuts to school board and foster care funding, amongst other county and state resources particularly geared toward the welfare of children. They also frequent town hall meetings to advocate against allowing certain businesses that would attract young people to establish themselves in their city. They have also saturated the local real-estate economy, not only forcing young adult tax paying citizens and families into unsustainable and unlivable situations, but also working In cahoots with property management to set up communities specifically for themselves, hoarding property and retaining rights to a home that they only live at for 3 to 4 months out of a year.So yeah \textbf{ageism} is a bitch especially when it doesn't go your way.\normalsize   & \cellcolor{green!5}Age, Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/204 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Age is just a number...live life and go for it. As long as you draw breath you can still achieve your dreams....\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Age shouldn't be a barrier to government but bill seems to be implying \textbf{old} people are better at governing and the record says otherwise. \textbf{old} people usually don't understand technology which isn't great... and they tend to carry a lot of social baggage from the last 100 years we could do without.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small Fuck \textbf{Jerry} Brown and his suede denim secret police.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small All these \textbf{old} people are agreeing with him\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Yes, agreed.  But I guess we can agree that our present bias is towards us young people.  It is also no surprise as it is the demographic sector theoretically more productive, creative, emotional and with it more likely to consume, in the sense of buying but also of destroying, which following Schumpeter is the source of growth.  In short, most billionaires are \textbf{old} but their businesses invest and focus in the young because their marketing departments know the larger gains are there.We may also say that we don't pay enough attention to the adolescents and kids.  I am not saying immediate equal vote, but perhaps new forae for participation and feedback.But again, you in the States don't participate much in politics even as young adults.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small So let them get a physical and if they're healthy, drop the \textbf{ageism}. And at the same time, test the young to see if they have a fifth-grade knowledge of history, literature, and how to use their own language beyond 140 characters' worth of truncated words.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small You make a valid point, but only for an argument that doesn't exist.My understanding of Bill's argument is that America is driven by pop culture, and pop culture currently reveres the young and condemns the \textbf{old} in most things, especially in areas where it shouldn't.When it comes to progress, wisdom does not cause stagnation. On the contrary, wisdom prevents the world from revisiting \textbf{old} mistakes.Our mistaken belief that "new things" can only come from "new people" is the very reason why we were always on the brink of another world war.It wasn't the "new things" that prevented another war, but the wisdom of a small group of "\textbf{old} people" that knew societies on Earth will always be too immature to understand the consequences of their actions, because they (the "new people") will always think that their ideas are new, simply because they are ignorant of the past, and/or unable to apply past knowledge in a philosophical way.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/161 & \cellcolor{green!27}1.863 \\  \hline
  \cellcolor{green!5}\small Being older means you've had to actually change things several times. \textbf{Nothing} beats experience - especially when it seems like knowing economics is the things people value most in a leader. The young guns are exactly that - young guns. They come in with a fresh view on things, but they have no sense of perspective. Whether [whatever] is genuinely revolutionary thinking, or if it's just a rehash of something that's been tried before.\textbf{Old} doesn't necessarily mean sedentary and conservative - even people like Sanders (regardless of views) is a perfect example of that. It's not about shutting out young people, there just can't be two presidents, so it's about picking the right one. It's a point on what \textbf{age} actually mean. People seem to be put in boxes as either "\textbf{old}" or "young" - and to young people, that first box comes creeping veeery fast. Is 40 years "\textbf{old}"? Well, compared to what most 20 year-olds do, it's very \textbf{old}. They "no longer know whats cool". But in terms of looking at a lifetime of politics - 40 is barely getting started. It's like "young" is considered like 10-15 of adults. But just because someone at 20 can't tell the difference between a 50 and a 60 year-\textbf{old}, doesn't mean there isn't one.The point made in the video is that we've shifted initiative from middle \textbf{age} to young \textbf{age}. Likely because the middle \textbf{age} live so comfortably, they don't really care to riot that much anymore. Which is how they getcha'. Objectively speaking, everyone has a voice - but why does the 85 have to live by what the 15 feels? There needs to be a vetting system in place - and that's experience. Not google.\normalsize   & \cellcolor{green!5}Age, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!5}9/289 & \cellcolor{green!5}3.114 \\  \hline
  \cellcolor{green!27}\small Its not a politicians \textbf{age}, its whether he is Progressive or Conservative. Bobby Kennedy explained the difference succinctly when he was asked to explain why he supported Progressive Democratic policies in general over Conservative Republican ones. "Some men look at the world the way it is and asks  "Why?" I dream of the way the world COULD be, and ask "Why Not?"   But I get your point, also. There is an \textbf{old} Chinese proverb that goes A man who is 20 and isn't idealistic has no heart, And a man who is still idealistic at 40 has no head."  Young people shouod always be holding the older generations feet to the fire when they see them selling out. But believe me, getting married starting a family and having a mortage and maintaining a career, with 3,4 5 other peoples lives depending on you maintaining a job and being responsible and dependable to your family....trust me,  keeping all that going will wear down the best of us.. An older adults  world, compared to 20/30 year olds, the commitments and responsibilities make a individuals ability to rebel look irresponsible, if not insane.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/190 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small dgrant7291 I like what you say.  My son is now in that \textbf{age} group.  I am \textbf{old} and free again!  One lovely thing about longer life spans is to be free and have experience to utilize it well.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small The president is one man or \textbf{woman}. But the work of the presidency is not a one man's show. You don't have to worry about the possibility of influence from other people.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Society needs to be updated, but the West is in a fucking out of control free-for-all to the bottom of human idiocy, ignorance, and hypocrisy.Yeah us \textbf{old} people do know more than you, "get it", more than you, and only care about you not throwing out the baby with the bathwater so you don't fucking nuke the most advanced, just, and sophisticated society in human history...But, meh it's up to you if you want to live better than we did or revert to whips and chains....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small Chico Bicalho   When I was about twelve years \textbf{old}, I asked my grandmother what it was like to be \textbf{old}.  She said it was like being young, but in an \textbf{old} body. I thought, oh my god.  As it turned out, she was right!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/44 & \cellcolor{green!27}6.818 \\  \hline
  \cellcolor{green!5}\small Not necessarily. I know some baby boomers that are more progressive than some teenagers that I know. Bill is correct: \textbf{age} is relative. Some people have wisdom and some are just stupid. \textbf{Age} has \textbf{nothing} to do with that.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}3/39 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Hold up. He's talking about a single person holding a very powerful position. I do think that someone that is tried and true would be a better choice. Their advisors and cabinet members can be varied, and should be valued for their input and insights. But look at the very nasty \textbf{old} fart we ended up with; \textbf{age} alone is obviously no asset.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small The \textbf{ageism} thing is spot on. Especially now when everybody wants to be fucking 16. I remember 10 years ago when I was 16 everyone wanted to be 25. This ridiculous shift to everyone wanting to be a fucking child has led to grown men playing Pokemon fucking Go.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small not in the computer \textbf{age}.  youth dominate computer wisdom\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I think it's very telling that people are of less relevance after the \textbf{age} of 60 \& that death is something to be feared...our society, as Bill aptly put it, is a teenager who DOESN'T want to grow up. So sad\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I am an older American, soon-to-be 68, and I agree \textbf{Ageism} is real.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Only because u \textbf{old} \textbf{racist} bigots can't stop being prejudice so the rest of us have to deal with y'all not getting that ur the problem\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Well I have to say the main reason young people don't respect the elders is because a lot of them still believe ridiculous shit like the world is 6000 years \textbf{old} and life begins at erection and evolution and climate change are myths hell my father believes all that shit and he's not even fifty but mostly we don't respect our elders because all those idiots think they deserve our respect just because they were born before us I'm sorry but dumbasses don't deserve respect no matter what \textbf{age} they are though that is not to say the guy he was talking about is \textbf{dumb} just a lot of people from that generation are\normalsize   & \cellcolor{green!27}Age, Dumb, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/114 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Dylan Minish every generation has their dumbass, but I hate it when people just \textbf{lump} one generation as that quote on quote "dumbass one" .\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Foalan Is a Lupo I was not lumping anything I was saying generally people who believe all that bullshit on my previous comment most of the \textbf{racist} \textbf{homophobic} sexist religious nuts in this country are Predominantly people 50 years of \textbf{age} an older\normalsize   & \cellcolor{green!27}Age, Homophobic, Racist & \cellcolor{green!27}Age - General, Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}3/43 & \cellcolor{green!27}6.977 \\  \hline
  \cellcolor{green!5}\small Ethan Lucas, Respect must be earned.  I will not respect a \textbf{dumb} shit just because they lived a long time, but I also will not disrespect them.  (Unless they really deserve it.)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Incognito Torpedo. Of course it must be  earned. Only a fool would respect \textbf{dumb} shits. Dogma, good \textbf{old} days, etc can be a severe hindrance to the progress of the human \textbf{race}. People of that ilk can be very persuasive in their sophistry to the ignorant mass, but there are those of \textbf{old} \textbf{age} that do see the corruption around them by having lived and experienced the passage of those years. Something the younger generation can only read about.  There lies the problem.  The information being viewed today is confused by different opinions on history. Sophistry and propaganda rule. I leave my mind open to all opinions, then use my knowledge of my experience to come to some idea on what I believe could be the right idea to ponder on and focus on a way to make it a reality. Regardless of the climate change debacle. I believe this is a limited resource we have and must take care of it. I believe that there are those that are against this for one reason only: Profit. I see a vast confusion where people get confused and talk about Fascist and communism as if they're up to speed on both.  I believe these people are narrow minded, tunnel vision freaks that are jumping on some insane bandwagon that looks like being good for their soul.Socrates was right when he considered democracy the worst form of gov't for the people. The ignorant mass ruling the intelligent few.  Yet  after trying all the other methods, we have ended up with what we have today.  Some \textbf{old} man once explained that the longer he lived the more convinced he was that other planets use earth as a \textbf{lunatic} asylum. Fair comment, me thinks. How about you?\normalsize   & \cellcolor{green!27}Age, Dumb, Lunatic, Old, Race & \cellcolor{green!27}Age - General, Age - Over 65s, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/294 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small When Bill realizes hes getting \textbf{old}...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I'm pretty sure he has done plenty of \textbf{old} person jokes and he has never let up on the \textbf{fat} person jokes (like now).\normalsize   & \cellcolor{green!27}Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Matt w4k He's just making the obvious point that dismissing \textbf{old} people just because they're \textbf{old} is stupid. Specially* in politics. If you can't see that I don't really have anything else to say.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Im from a country where we let all the \textbf{old} people govern and run the country, guess what that gives us? \textbf{sexism} and \textbf{racism} , concepts from 50 - 70 years ago, religious and cultural intolerance, strict laws where the government thinks police and military check points where citizens have to produce ID cards to the the authorities regardless of if they've done anything wrong or not, a vestige from fascist and \textbf{communist} ideology . .\normalsize   & \cellcolor{green!27}Communist, Old, Racism, Sexism & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - General, Gender - General & \cellcolor{green!27}4/76 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small and extreme conservatism, where there is no right or left on things like abortion, \textbf{g\textbf{ay}} rights all political parties with unanimously agree that abortion and things like \textbf{g\textbf{ay}} marriage should be illegal and it isnt even on the agenda for the next few decades to address that and \textbf{sex} out of wedlock is thought of as infidelity and u can go to jail for it . .all because \textbf{old} politicians are more resistant to change\normalsize   & \cellcolor{green!5}Gay, Old, Sex & \cellcolor{green!5}Age - Over 65s, Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}6/75 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small He didn't say all \textbf{old} people should be able to govern. Just that \textbf{age} shouldn't be a restriction. Bernie is rather \textbf{old} but he has many young followers.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small What country?  Because elders are not always right, but there are evil elders as well as the usual lovely people who have much to share!  You can't blame rigid \textbf{old} power mongers on \textbf{age}; it happens at any \textbf{age}!  Do not blame \textbf{age} for your troubles!\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/46 & \cellcolor{green!5}6.522 \\  \hline
  \cellcolor{green!27}\small >a vestige from fascist and \textbf{communist} ideologyFascist AND \textbf{Communist}? how the hell does that work?\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Gosh how people can be \textbf{dumb}. Where else all these things can be ? That's the Middle East he is talking about . I feel you brother, I'm in the same shithole.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Sorry Bill no one should be allowed to run after the \textbf{age} of 57.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Clinton, Trump, Johnson and Stein are all over that \textbf{age}...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small He says this now, but when John McCain was running for president in 2008, Bill Maher joined the bandwagon of making fun of McCain's \textbf{age}.  It's amazing how many "news reporters" from all walks of life have ideas and principles that wax and wane with who they are referring to.  This guy is no better than Sean Hannity.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small That's just middle \textbf{age} almost to the women in my family.!   lol\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I like how he is sitting to Bernie Sanders who is 84 years \textbf{old} when he said this.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Karan Chaphekar \textbf{indian} bitc'hes are born to be enslaved by their chinese and british masters\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Kawhi Mvp sorry but there will be no earth. To fight over. Plus you people fuck too much and are an overpopulated,undereducated,filthy,gang raping cow worshipping. Swine. Never first world when the Olympics can never be held in your shit filled streets. Build toilets,and tampon factories and wait till the \textbf{Indian} ocean covers all but Tibet.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Catalina Simmons if you ever learned history you would know india is naturally overppulsted because of geography, seconds our population grows at 1.2 percent (which is just bouts to the same as world average), defacation isn't an issue anymore, rape and women rights have improved a lot, and what's your problem if we worship a cow, it was the reason civilization was able to form. And by 2050 well be a first world \textbf{nation}(with high middle class income and 2nd largest GDP)\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Sorry to disagree, Bill, but Generation Ass is being manipulated and distracted by \textbf{old} farts like George Sorryass (Soros) and other \textbf{old}-but-not-wise wealthy white sociopaths. And \textbf{Gerry} Brown could never be president, not because of his \textbf{age}, but because he's too busy taking away people's right to self defense, banning this gun and that magazine. People like you and politicians and celebs who have armed bodyguards and live in gated communities don't live in the same world with the rest of us, so you're all for taking our guns. How are you different from the Brits in the 1700s, ruling over colonial America?\normalsize   & \cellcolor{green!27}Age, Gerry, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!27}3/103 & \cellcolor{green!27}2.913 \\  \hline
  \cellcolor{green!5}\small Jerry also fucked over 3 local small businesses in my town by enabling minimum wage hikes\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small People didn't appreciate a \textbf{fat} ass like they do now. The "heroin' \textbf{chick} was in for so long.\normalsize   & \cellcolor{green!27}Chick, Fat & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I feel like if I fucked a heroine \textbf{chick},  she'd break her legs\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That is true about \textbf{ageism}! And it's not just America.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small You know, the argument that \textbf{old} makes wise just got slightly less convincing after the \textbf{Brexit} vote, where most older people voted to leave. And in a number of Western countries, \textbf{racism} is also much stronger in the older generation. And you know what, that's not ageism: that's a statistical fact.\normalsize   & \cellcolor{green!5}Brexit, Old, Racism & \cellcolor{green!5}Age - Over 65s, Ethnicity - General, Nationality - European or anti-Europeans & \cellcolor{green!5}3/51 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Well, \textbf{old} does make wise, but statistically. It doesn't follow that all \textbf{old} people are wise, only that they are more likely to be so -- not even that a majority of them is, again just that a higher proportion is. And even if the young voted well on \textbf{Brexit} when compared to the \textbf{old}, note how many of the young didn't even bother to vote at all -- they might have won if all 18-30's had actually bothered to vote...  So Bill's point still remains valid: people should be judged by their accomplishments and skills, not by their ages.\normalsize   & \cellcolor{green!27}Brexit, Old & \cellcolor{green!27}Age - Over 65s, Nationality - European or anti-Europeans & \cellcolor{green!27}4/100 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Acknowledging \textbf{ageism} is my favorite video. Thanks, Bill Maher. Good for you.One prob: Jane Fonda is not what 80 looks like. That was an \textbf{ageist} example. That's what a trillion\$\$\$\$ of plastic surgery and wigs looks like. If you don't like \textbf{ageism}, show a real 80-year-old! Show Jane's girlfriend, Vanessa Redgrave! She's the beauty of 80.\normalsize   & \cellcolor{green!5}Ageism, Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/57 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I think Bill is full of shit on this one. It's the \textbf{old} people who have fucked this country over. Young people are not in any position of power, and the \textbf{old} people want to keep deciding the future of this country, yet they are the ones on their way out. Nah, that makes \textbf{zero} sense at all. Young people need to have a say too, and there are plenty of wise young people and a lot of stupid \textbf{old} people. Where do you think most of the bigotry and \textbf{racism} in this country comes from? Young people?? No, it's \textbf{old} fuckers who are still living in the 1950s. According to Bill's respect our elders logic here, we should all respect Trump and George W. Bush. No...I am not going to respect them because they're stupid. Look at three of our greatest presidents: Lincoln, Teddy Roosevelt, Kennedy...what did all three have in \textbf{common}? THEY WERE YOUNG when they became president. Sorry Bill, you're wrong on this one. Not saying \textbf{old} people can't do a good job, because Bernie would have, but \textbf{old} people shouldn't be listened to just because they're \textbf{old}, plenty of younger people are wise too and have great ideas. We're not all drooling over Kim Kardashian's ass on our cell phones okay? Maybe if younger people had more say this world wouldn't look the way it does today.\normalsize   & \cellcolor{green!27}Common, Old, Racism, Zero & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - General, Social Class - Working class & \cellcolor{green!27}10/231 & \cellcolor{green!27}4.329 \\  \hline
  \cellcolor{green!5}\small young people do have lots to say, they gave us the Political Correctness  culture that's getting irritating, Social justice Warriors that are as sensitive as dandelion on anything uncomfortable and \textbf{Black} lives mater club that think by rioting and creating havoc  In the name of justice will make things better for their lives or image. yeah I think I'll learn from the people who came before me because that's how you separate the do-ers from the complainers.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small \@Arahat Pena Actually that's not true. The reason BLM exists is because of the faults of the older generations. If they handled segregation and reconstruction better, we wouldn't have BLM today. If it weren't for the backwoods older generation, \textbf{African} Americans would have integrated into society and we wouldn't have needed a Civil Rights movement, a War on Drugs, etc etc, all this crap that has caused more rifts and issues. It's not the young people who are creating those issues, it's the \textbf{old} timers who are prejudiced that have been screwing this country over, along with their poor foreign policy decisions. It's because of them the Taliban/Al Qaeda exists. Because of them that the Middle East is the way it is. These are more important issues than political correctness. Who the fuck cares about PC when there's terrorism running amok in the Middle East? Get your priorities straight jack ass.\normalsize   & \cellcolor{green!27}African, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/151 & \cellcolor{green!27}1.325 \\  \hline
  \cellcolor{green!5}\small \@RyZombie619  first of so many civil rights activists are not affiliated and even against BLM. The BLM are protesting that too many \textbf{African} men are being killed by as in their view as the cops for  being \textbf{racist}. It's not really about \textbf{race} at all but because of the stereotypes that the \textbf{African} American gang culture have produce. Although still morally wrong and some cases the fault of cops, the majority of blacks being reported killed by cops were warranted in defense of their own lives and or in the event that they were  committing a crime of an extreme circumstance. Chicago has the most \textbf{black} on \textbf{black} crime in the country and yet people expect cops not to be as a result a little prejudice. So  civil rights were fought for the color of one's skin not to be a subject for being excluded from ones right by their constitution.  BLM people think they are the same but in reality they are  fighting for the right not to be stereotyped. I'm latino and I know when I'm pulled over and the cops think I have drugs, I know it's not because of me or them to blame but towards the people of my \textbf{race} that is tied to criminals. No one's perfect not even politicians so get over it. Also when your trying to make a point, Be courteous and stick with one subject at a time or else you just person doing a rant.\normalsize   & \cellcolor{green!5}African, Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}7/246 & \cellcolor{green!5}2.846 \\  \hline
  \cellcolor{green!27}\small Hey use us!  Bond with elders who you respect; learn from experience before you screw up we are a team; use our advice and ideas, we need your youth and drive and are aware of the big picture!  I screwed up \textbf{nothing} ; people, especially democrats have not been turning out the vote and evil creeps have taken over!  I did all I could, many of us did; but the need to vote is not making an impression on the country as it should!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small no Bill, you are wrong about Chris Christy, he does immense CORE exercises for hours each day on the toilet.  i bet he has a biday ~he should! ~i know those short arms can't reach that far.  unfortunately there is \textbf{nothing} we can do about the brain constipation.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small I will challenge Bill Maher to a car \textbf{race} around New York City.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small What a \textbf{psycho} smile\normalsize   & \cellcolor{green!5}Psycho & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Jerry Brown fixed California? Man. I must've missed that.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small we have the exact opposite of this problemin iran. for example, 89 years \textbf{old} Ahmad Jannati just got elected as the chairman of assembly of exeprts for the next 8 years :|\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small There's a HUGE GAPING HOLE IN HIS ARGUMENT and it is this: Just because someone is "\textbf{old}" doesn't mean that person is wise. I know MANY \textbf{elderly} people that just don't "get it". Intelligence is multifaceted and cannot be easily assigned to ANY particular group..and it is like respect and trust, intelligence is earned. There is NO "magical" \textbf{age} people can make it to and suddenly be spoken of as wise. Sorry.\normalsize   & \cellcolor{green!27}Age, Elderly, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/72 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small True. It doesn't apply to everyone. But it's still a valid point because of statistics. And as someone else mentioned, a good governing body will benefit best from a mixture of both \textbf{old} and young people - the \textbf{old} for the wisdom and experience, the young for their energy and fresh eyes.Bill's argument wasn't about supporting \textbf{old} people all the time, but essentially this - don't judge someone by their \textbf{age}. Just because someone is 80 doesn't mean they are too \textbf{old} to govern. That's all.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}5/87 & \cellcolor{green!5}5.747 \\  \hline
  \cellcolor{green!27}\small He is right. But it seems a litle bit hypocrite coming from a guy who only dates girls half his \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Who's the real \textbf{ageist} in this video... Seems like juvenoia to me. I hate when it comes from a liberal source.\normalsize   & \cellcolor{green!5}Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small This is great, but wasn't \textbf{age} the reason leftists told moderates not to vote for McCain?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small My grandpa was biking 15 miles a day at \textbf{age} 82!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Trump is a \textbf{senior} and he is an idiot Larry King  is a \textbf{senior} another moron.Just because you were lucky enough to reach \textbf{senior} status doesn't necessarily  make you wise anymore than being young makes you stupid\normalsize   & \cellcolor{green!27}Senior & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/37 & \cellcolor{green!27}8.108 \\  \hline
  \cellcolor{green!5}\small :(  :( i blame \textbf{old} people for his loss.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small A generalisation/stereotype which is used to do absolutely \textbf{nothing} except tell jokes, and therefore is completely harmless.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I never called Trump a \textbf{racist}, but nice way to generalize. Maybe these anti-SJW videos aren't your most reliable news source\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Gordon Freemason no him laughing at a stereotype makes him a clear cut \textbf{racist} [/the worst of SJW]\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Says \textbf{age} is the only acceptable form of prejudice left...goes on to make a \textbf{fat} joke - -\normalsize   & \cellcolor{green!5}Age, Fat & \cellcolor{green!5}Age - General, Physical Identity - Physical Features & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small +MysticalTechno Being \textbf{fat} is unhealthy\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Eduardo Martínez Sáez By that logic, being \textbf{old} is also unhealthy. Oh no wait, not all \textbf{old} people are feeble? Cool. No need to continue generalising and stereotyping then. Especially when there are plenty of \textbf{thin} people who are unhealthy too. Didn't even realise lack of health was a good reason to mock people. Are you sure its not because \textbf{fat} is stereotypically considered ugly?\normalsize   & \cellcolor{green!5}Fat, Old, Thin & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}4/65 & \cellcolor{green!5}6.154 \\  \hline
  \cellcolor{green!27}\small \@MysticalTechno \textbf{Fat} pride is stupid. You can't control aging, but you can fucking stop eating garbage and work out. It doesn't mean you have less dignity. But please... just relax and stop policing JOKES. If a friend of mine was getting too \textbf{fat} I would get worried about him/her, but fatties are funny, deal with it.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Not true. \textbf{Old} people can get off their feeble asses and go get face lifts and stuff so they don't appear so damn \textbf{old}. I'm not policing jokes, I'm pointing out hypocrisy. If he's joking about \textbf{fat} people then HE should stop policing jokes about \textbf{old} people. If a mate of mine was getting too \textbf{old} I would get worried, but oldies are funny, deal with it :)Note how I don't normally show prejudice towards \textbf{old} people, I'm just making fun about how you seriously think everyone who's \textbf{fat} eats garbage and doesn't work out. I know that's how society stereotypes them, hence why I'm giving you society's stereotype for \textbf{old} people.\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}8/113 & \cellcolor{green!5}7.08 \\  \hline
  \cellcolor{green!27}\small \@MysticalTechno Comparing \textbf{old} people and \textbf{fat} people is stupid.  He's just saying you shouldn't be \textbf{old} for being president.\normalsize   & \cellcolor{green!27}Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small +Eduardo Martínez Sáez he's saying you can be \textbf{old} as president. But he constantly takes cheap shots at Chris Christie (there are a lot better ways to insult the guy than pathetic \textbf{fat} jokes).It's not stupid at all. There's a lot of misinformation out there when it comes to both \textbf{old} people and \textbf{fat} people. \textbf{Old} doesn't  necessarily equal weak and useless, and \textbf{fat} doesn't necessarily equal lazy and unhealthy (plus you can be young, weak and useless, just as you can be \textbf{thin}, lazy and unhealthy too). Keep it real, the only reason you find \textbf{fat} shaming appropriate is because society has told you that people are meant to eventually get \textbf{old} but you've never considered the fact that some people are meant to be \textbf{fat} as there is no universal healthy weight. Of course, \textbf{fat} is subjective just as is \textbf{old}.\normalsize   & \cellcolor{green!5}Fat, Old, Thin & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}12/144 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@MysticalTechno he's an asshole, we both agree on that I think. But at least he's one of the few liberals who still remain some \textbf{common} sense.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Entitled baby boomers ruined this country and you wonder why millennials hate \textbf{old} people?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Bill maher logic: \textbf{ageism} is bad, \textbf{fat} shaming is good (as long as it fits my political narrative).\normalsize   & \cellcolor{green!27}Ageism, Fat & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Yeah, we need \textbf{elderly} wisdom in government... Says the guy who endorsed Obama (then 47) over McCain (then 72)\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small THIS is why the Oscars are so white. Once it Kanye and Jay Z and the rest of those schlubs start tricking in the doors, Hollywood, like the music industry will become an industry of \textbf{fat} dumpy stupid looking asses.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Age and wisdom do not necessarily follow. If it did, Ronald Reagan at the end of his turn would have been much wiser than Ronald Reagan at the beginning. If he ever had been wise that is.There are plenty of people who either walk through life with blinders, or who simply live quiet lives and so never get the experiences Bill assumes is necessary for wisdom.Not to mention the effect of personality. Some people, when encountering hardship say "This should not happen to me" others say "This should not happen to anyone". I leave it up to the reader to decide which is wiser.Then again there are those who achieve wisdom at a young \textbf{age} and sticks with it.VOTE BERNIE!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/124 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small While it's not right, \textbf{ageism} is accepted because no matter what, if ppl live long enough, everyone gets \textbf{old}. It's not like being \textbf{black}, \textbf{g\textbf{ay}}, or female, where you're born that way. No one is born \textbf{old} \& therefore not discriminated against until later on in life. And IDK what Bill is talking about , this country is ran by \textbf{old} ppl, namely \textbf{old} white men. And I don't really see the issue with having a cut off \textbf{age} for running for president, when there's a minimal \textbf{age} to run in the 1st place. Clearly these \textbf{age} restrictions were put on for a reason. Probably because younger ppl aren't wise enough to run the country \& older ppl are too stuck in their ways, may have \textbf{age} related physical/mental issues, or might die in office of \textbf{old} \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Ageism, Black, Gay, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Ethnicity - Black, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}14/138 & \cellcolor{green!27}10.145 \\  \hline
  \cellcolor{green!5}\small I think Bill doesn't understand why white guys are now starting to appreciate ass (like \textbf{black} \& Hispanic men have been for decades), when traditionally they apparently only cared about breasts. But he forgets that there was an \textbf{African} \textbf{woman} back in the day, named Saartjie Baartman, who was put on display because of her big ass. And the white slave masters use to rape their \textbf{black} female slaves, because they had curves that white women back then didn't have. So no, this isn't something new for white culture either, the only difference is back then they use to do it in secret. But now that white men are starting to publicly appreciate ass there's suppose to be a problem. GTFOH.\normalsize   & \cellcolor{green!5}African, Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}4/121 & \cellcolor{green!5}3.306 \\  \hline
  \cellcolor{green!27}\small I love it when he brings up bad Asian drivers. It is so true. I have lived in Asia, Borneo to be specific, and it is so true: here, there and looks live everywhere. What is it? Even pulling a shopping cart is dangerous in their hands.    I blame \textbf{age}. To be a good driver, and now it looks like a shopping cart puller or pusher, one has to learn early. More and more non-Asians, home spun people, are bad drivers. Single focused drivers~eyes planted straight ahead, never checking mirrors, (there are three of them in most cars), no awareness of those around them. And sorry, girls, but few of you seem conscious of road share; but don't feel bad, late learners of any persuasion ain't got the 'awareness' of what is not directly in front of 'em.    But I must point out, young Asian drivers, who have their experience and licences in their earlier teens are excellent drivers. Maybe a bit too fast, but that is youth.   If you want to be a concert pianist, star sportsman/woman, automobile driver, you must learn early and have a great trainer.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/189 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small Being President does take a toll on one's body (look at Clinton, Obama, and GW Bush). I'm a little worried that if Sanders becomes President, he may die before his term is up. "\textbf{Ageism}" exists for a reason. It's not because they cant' do it, but because of the implications behind \textbf{old} \textbf{age}. If Sanders becomes President, will he step down because of health issues that are \textbf{age}-related? I think that's a legitimate question.\normalsize   & \cellcolor{green!5}Age, Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/74 & \cellcolor{green!5}4.054 \\  \hline
  \cellcolor{green!27}\small every \textbf{old} person i encounter is just as fucking stupid if not worse than every young person i encounter\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Bill , \textbf{Jerry} Brown said he welcomes all illegal immigrants to our country.? WTF ? And Bill though I admire you as a liberal and standing up to radical islam all you liberals are against building a wall on the Mexican boarder . Pray tell.... do you and your liberal friends have "Walls and Gates"  to keep people off your property?  I'm serious, can I just drive up to Alec Baldwin or Bill Maher or god forbid  Oprah Winfreys house.... I know people who live in Monticeito next to Oprah and no one is getting close. Anyway I'm looking to the right hand side of my you tube screen and i'm seeing I can watch Lisa Lampanelli do a one hour skit on "Take it like a man" If I'm going to get smoke blown up my ass I'll take it from a comedian.  At least I can laugh at myself\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/151 & \cellcolor{green!5}0.662 \\  \hline
  \cellcolor{green!27}\small The young don't run shit in this country! It's the middle aged people who do. The nicest cop you'll ever meet is the one over 60 years \textbf{old}. The second nicest is the 24 year \textbf{old} guy who might just know what it's like to be young. But the 45 year \textbf{old} cop will beat your ass, take a bribe, do your coke and throw you in jail for it. Of course this is all a generalization, but take a look at politics. the good politicians are either \textbf{old} (\textbf{jerry} rice, bernie, fuck even mccain sometimes) or....nope you can't even be president until you're 35.\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}5/105 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Hillary going to get the Hispanic  vote the female vote and the \textbf{black} vote she gonna win just saying\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Martti Suomivuori I'd say you were psychic but Americans are nearly all \textbf{dumb} asshats so.... Not surprised\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Yes except \textbf{old} people are bigoted nut jobs including my family members with the exception of few. I hate when people get \textbf{old} and they cannot stand that young people have ideas they want to push as well. No, we don't worship the ass. But we are becoming more accepting of our bodies and right to occupy space and be celebrated. However check every fucking statistic and young people are leading in everything except the opportunities \textbf{old} white rich governors refuse to give us.Ironically, Maher audience is majorly young people. STFU\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/91 & \cellcolor{green!5}3.297 \\  \hline
  \cellcolor{green!27}\small 91 of the \textbf{African} Americans that are over 65 and voted in the primary voted for Hillary because they "know her" compared to Berine who was fighting for Civil Rights in the 50s, while Hillary was still deciding if she wanted to be a Republican or not. If you know Hillary then you should know about how Bill during his term as president in 94 signed a bill (heh) that made mass incarceration worse, and he admits it.Which makes you wonder, if the \textbf{elderly} are "wiser" than younger people in most respects, then why don't they read up about the different candidates and then make their judgement after. Instead of using name recognition to vote.\normalsize   & \cellcolor{green!27}African, Elderly & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/116 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small \@Liche Christ She was a "Goldwater Girl" who was a supporter of \textbf{Jim C\textbf{row}}.\normalsize   & \cellcolor{green!5}Crow, Jim Crow & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Old people don't use the internet. They're not tech savvy enough to research this stuff on the internet, and the media doesn't discuss Bernie at all.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Does maher make that stupid asian stereotype joke every episode? All I ever see him talk about is what's wrong with millennials. If he wants to sort out of the politics of this great \textbf{nation}, then look no further than your own generation. If you even think about putting that fool \textbf{Jerry} Brown into the white house, just listen to the song "California Uber Alles" by The Dead Kennedys.\normalsize   & \cellcolor{green!5}Jerry, Nation & \cellcolor{green!5}Nationality - General, Nationality - German & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small Problem is though Bill, for every Bernie Saunders there are are one hundred Strom Thurmonds waiting in the wings.......of course \textbf{age} in itself shouldn't be a block to political office, but as a rule once people pass retirement \textbf{age} they are pretty set in their ways and not open to compromise, and generally fairly right-wing.You don't want kids as politicians, and equally you don't want geriatrics either.....\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I like Real Time... I don't always agree with Bill, but I enjoyed this rant. One thing he says that's false is that \textbf{ageism} is the last acceptable prejudice. \textbf{Fat} people are one of the most open targets, as he proved with the Chris Christie joke. Smokers are also a massive target. I get that they shouldn't smoke in an inclosed location, but restricting people from smoking in their own cars, or giving them an outdoor space is unreasonable. I think Trump is proving that even open \textbf{racism} is still pretty accepted in this country. There will always be prejudice, but all we can do is try to inform people without pissing them off in the process. Most prejudice stems from ignorance and can be fixed, but there will always be the stupid prejiduce and that shit sticks.\normalsize   & \cellcolor{green!5}Ageism, Fat, Racism & \cellcolor{green!5}Age - General, Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!5}3/138 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Lisa's laugh gives me a boner. Is that \textbf{weird}?\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small yes \textbf{old} people have wisdom, but the majority is still living in the \textbf{old} times when \textbf{woman} are supposed to be in the kitchen, \textbf{black} people are bad, religion is good and all that backwards shit. yah the young are stupid but our minds are open to equality and change, unlike the \textbf{old} who are set in their ways. any leader should be at least in their 40's to be a good one, they are in the Now, not the past, and they will actually live to see the future.\normalsize   & \cellcolor{green!5}Black, Old, Woman & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black, Gender - General & \cellcolor{green!5}5/90 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small That's Bernie Sanders? (1:28) I had no idea! And I've already watched this vid several times! That's awesome!Watched this again today, and thought Bill was talking about Bernie thought of being too \textbf{old} to run for president - not \textbf{Jerry} Brown.\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I'm certainly no millennial. I'm almost 40. But I seem to remember the human buttocks always being sexualized, even when we were watching MTV back when they actually showed music videos. Checking out people's asses is not something kids today invented. Sir Mix-a-Lot released "Baby Got Back" in 1992, before any "millennial" was even out of diapers.Furthermore, I'm sorry Bill, I love you, but a candidate's \textbf{age} IS an issue. John McCain was 72 on election day in 2008, just six years shy of the life expectancy for Americans. And he chose as his successor SARAH PALIN. I don't care how much you like John McCain, you think the fact that a 72-year-old man chooses... THAT... to succeed him, you would be a damned fool not to take that into account when you vote.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/135 & \cellcolor{green!5}0.741 \\  \hline
  \cellcolor{green!27}\small State-level positions usually have a lower \textbf{age} requirement.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small My generation is way to emotional to be in congress at this \textbf{age}. Maybe when they get older would it be fine.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I cant wait until millennials get to congress. Passing laws against hurting peoples feelings will be fun. Cant wait for the congressional selfies. Senator 2 Chainz will be the voice of the people. Kim Kardashian day will be a national holiday. \textbf{nobody} will have any weapons to protect themselves. We will sign the "I am sorry for toppling your dictator bill". Free health care for everyone! (unless you have a job). no borders at all, elections will be done by caucus only. CNN will be funded by the goverment so everyone can watch. They will pass a law mandating female professional athletes are paid the same as Lebron james. Every statue will be replaced by a statue of whoever is trending on twitter each day. Cant wait for a mix of both lawlessness and complete totalitarian dictatorship!\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/137 & \cellcolor{green!27}0.73 \\  \hline
  \cellcolor{green!5}\small I think when it comes to older people, we just need to be honest: Certainly, many \textbf{old} people have become much wiser over the years \& young people should be willing to hear them out. But also, \textbf{old} people are still people, and some of 'em are just too fucking \textbf{dumb} \& stubborn to know better or act better. So, respect should be given to older people, as should \textbf{old} people respect younger people. \textbf{Age} doesnt matter; what matters is not being a dick.\normalsize   & \cellcolor{green!5}Age, Dumb, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/84 & \cellcolor{green!5}5.952 \\  \hline
  \cellcolor{green!27}\small Jerry Brown hasn't fixed that 'mini Chernobyl' of a gas leak.. he hasn't throttled the fracking industry, poisoning the groundwater while pumping all that precious needed gas into leaking underground storage sites.. \textbf{Jerry}'s sister is big in that industry? We should be glad \textbf{Jerry} runs three miles a day? at his \textbf{age} it must take him two hours.. less time to think up new schemes.\normalsize   & \cellcolor{green!27}Age, Jerry & \cellcolor{green!27}Age - General, Nationality - German & \cellcolor{green!27}3/65 & \cellcolor{green!27}4.615 \\  \hline
  \cellcolor{green!5}\small Agreed, I enjoy most points but not the bashing of republicans, and \textbf{Jerry} Brown is horrendous!\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small shut up \textbf{old} man, it is ALL ABOUT THE MIGHT ASS!!! Love me some Nicki Minaj quality butt right about now  thirstyAF!!!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Actually, the young don't rule anything in America. In fact 80 of them don't even vote. And when that happens, the \textbf{old} people you want us to venerate end up being the main voters, and since they are overwhelmingly right-wing, we get  republican politicians, who are the \textbf{old}, white men who actually rule everything and make terrible decisions. This is exactly what happened during the November 2014 elections. If young people, who are mostly progressive, actually had more of say, then Donald Trump wouldn't even be a fucking option. It would be Bernie's win guaranteed. Look into it. Young people love Bernie and support him far more than any other candidate. So as you can see, there has been a meeting of the minds between Bernie, the oldest presidential candidate, and young voters. This happened based on ideas, and based on young people recognizing good ideas. We currently live in a country ruled by \textbf{old} republicans who are put in power by \textbf{old} people voting. You want a progressive country ? that would be a country where young people have a real say in politics.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}4/185 & \cellcolor{green!5}2.162 \\  \hline
  \cellcolor{green!27}\small Bill Maher must not be an ass man but surely we all can understand why a \textbf{fat} booty is attractive. what he said is like saying oh why are humans attracted to female lumps on a chest? def lost me on the butt diss.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I agree with the ass part, I mean women with big asses is definitely good for \textbf{sex} and butt-fucking but for worshiping, another type of other religion, instead worshiping a cross, you worship an ass-crack, back then, it was about worshiping big tits which was also \textbf{weird} but good for \textbf{sex}, I like to be smothered by them and smother other women with mine, but if our music videos and dancing is gonna be about that, then let's just have nonstop \textbf{sex} marathon then.\normalsize   & \cellcolor{green!5}Sex, Weird & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/84 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small +Liche Christ Ummm....so what's the real difference with breast? They are designed to nurture offspring....not to mention men have the capacity to have breasts as well (\& if they are \textbf{fat} enough they kind of do have breasts). And why do ppl kiss, when mouths, tongues, \& lips are filled with bacteria \& are designed primarily for consuming nourishment? I mean ppl do burp \& sometimes throw up, sneeze, \& cough. Not to mention ppl's breath usually stink unless they brush their teeth, use mouthwash, chew gum, or use breath freshers. And even then it doesn't last all day \& your mouth is always "on display" (unlike your ass, which is covered by clothing).\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/114 & \cellcolor{green!27}0.877 \\  \hline
  \cellcolor{green!5}\small I don't have a "case." In a relationship, \textbf{sex} life good. \textbf{Nothing} you say is going to change reality bud.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Generation Ass..I'm down with that! If those \textbf{old} cooks don't like ass, well good for them. I don't give a fuck! Few things in life makes me happier than admiring a perfectly shaped butt.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I don't like \textbf{FAT} ass !\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Nunya bizness ass, rack, that's all a \textbf{woman} is for this generation, that's the point bill is making! Degradation, women degrading themselves and those type of men that find it attractive!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Deepa Shrestha\@ That is the only thing on these males' minds is the female physiognomy.  \textbf{Nothing} else! And they think they are very macho or big man if they insult a \textbf{woman}.   Just the opposite, they shrink into nothingness.\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Bernie needs to have \textbf{Jerry} Brown as his Vice President in 2016. feelthebern\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small +turtle14 I think \textbf{Jerry} cooked his own goose with the fracking stuff.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small He's a hypocrite. Any straight guy claiming that a woman's ass is not a big deal is \textbf{g\textbf{ay}}. I'm sorry. He loves the ass as much as anyone else does. The funny thing is he was using photos of women most guys don't care about. Kim K, Minaj, Beyonce...so what?\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small i dont like ass, i like \textbf{pussy}, duh\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small what hes saying is hes \textbf{old} so his dick doesnt work as it used to\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Where was Bill's voice when the media was attacking Hillary Clinton for her \textbf{age}? Liberals can be as sexist and hypocritical as conservatives.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Age is greatly overrated as this mechanism for accumulating "wisdom". Anyone of a high intelligence doesn't need reality to rear it's ugly head over and over through the decades to know the right decision to make about most things. The vast majority of \textbf{elderly} people are just like the vast majority of young people, ignorant, stupid, and either in denial or totally content with thatThere's no reason a 20 something couldn't do well as a President or any other important high up position.\normalsize   & \cellcolor{green!27}Age, Elderly & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/84 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Maybe Bill is implicitly sowing the seeds of support for Bernie's eventual run by attempting to disarm the stigma behind \textbf{ageism}.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small This video struck me as very "\textbf{Old} man yells at cloud" from the Simpsons idk\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small old people die, more than young people. Is political correctness now telling us to ignore even more fundemental biological facts?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Great message, although Im British, I am really rooting for Bernie to win - BUT he calls \textbf{Ageism} the last known acceptable stigma and then makes fun of a \textbf{fat} person to try and prove his point...\normalsize   & \cellcolor{green!27}Ageism, Fat & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small the ancient Roman Senate came from the Latin word senex meaning an \textbf{elder},even their statues in the Republic all had men with wrinkles and sagging jowls, they hated the Greek art of celebrated perpetual youth.\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small It's kind of absurd that Bill criticizes \textbf{ageism} by insisting that young people are stupid.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small lots of \textbf{old} people are \textbf{dumb} too. you cant just assume they are smart, just based on \textbf{age}. you need a brain too.and since you dont live forever. the older you get.. the more chance you have for dying. or maybe geting altzheimer.\normalsize   & \cellcolor{green!5}Age, Dumb, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/44 & \cellcolor{green!5}6.818 \\  \hline
  \cellcolor{green!27}\small really nigga\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Unlucky mate. He lost to the \textbf{woman} who was so comically unpopular she lost to a TV celebrity who had a tape released on him sayin he grabs women by the \textbf{pussy}.\normalsize   & \cellcolor{green!5}Woman, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I completely agree with him, but historically, look at William Henry Harrison. He was 69 when he ran for president, and as a result of \textbf{old} \textbf{age} (and pneumonia) he died a month into office. Sure modern medicine is better, but the average life expectancy of an American is only 78.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small Yes, Americans worship the young - and the attempt to remain young by acting like teenage girls, even the males. Watch any day time talk show or night time reality show and you will see the values and behaviors of teenage girls being put on display. Personally, I have always preferred talking to the \textbf{elderly} versus the young. The young have \textbf{nothing} to say because they lack life experience - they are long on confidence, but short on wisdom. They're also boring.\normalsize   & \cellcolor{green!5}Elderly, Nothing & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I love it when he is talking about \textbf{ageism} and it doesnt matter what your \textbf{age} is to run for president, and Bernie is probably sitting there like, 'YES BILL, KEEP TALKING BILL.  WHY AM I SO FOR THIS RANT? UMMMMMM, NO REASON\normalsize   & \cellcolor{green!27}Age, Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small Joshua Gill It does matter what \textbf{age} you are, you have to be over 35\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Isn't this just \textbf{ageism} against the young?\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Wisdom comes from experience and knowledge. If you're young and simply google up things you'll forget in five seconds, you're not accumulating wisdom. The threat is that kids today will never be wise, even when they're \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small i got so excited when i saw bernie! who knew he would run for pres that time last year? away with \textbf{ageist} bullshit!! feelthebernmillennialsforberniewomenforbernielatinosforbernie\normalsize   & \cellcolor{green!27}Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Bitch about \textbf{ageism} whole simultaneously being \textbf{ageist}. Thanks, Bill. I guess I'm just to young (making me too naive, inexperienced, and self centered, right?) to understand. You sound like one of those rude \textbf{old} fogies that think the world owes them something because their a certain \textbf{age}. I understand that we should care for the \textbf{elderly}, and we shouldn't lose respect for them just because of their \textbf{age}. But older does not always mean wiser. Many people don't learn jack in all their years.\normalsize   & \cellcolor{green!5}Age, Ageism, Ageist, Elderly, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}6/84 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The fuck?  Bill, you bitch about McCain in one of your New Rules videos because he's \textbf{OLD}!  Along with numerous other \textbf{old} white guys.Don't be a hypocrite now!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small Nope. \textbf{Ageism} isn't the only accepted prejudice. Fatism is the most accepted prejudice. It's encouraged and rewarded. You should know Bill. You make those cheap \textbf{fat} jokes all the time. I wonder, do you have any close friends or family that struggle with their weight? Do they laugh?\normalsize   & \cellcolor{green!5}Ageism, Fat & \cellcolor{green!5}Age - General, Physical Identity - Physical Features & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I thought exactly the same thing. Bill, like everyone, loves the \textbf{fat} jokes. Often they're not even jokes. They're just insults. But they can be counted on to get the laughs and cheers.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small I'm sorry Bill but I am 50 and see my contemporaries as so \textbf{fat} and out of shape that their bodies are repulsive and I LOVE the open and deserved celebration of female butts, it is after all their second best feature.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small The Rolling Stones are an embarrassment to \textbf{old} people!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I agree to a point. We definitely have a culture that's obsessed with youth. I just turned 33, and I'm even sick the media's attention on tweens, teens, and twenty year olds. I absolutely want to hear advice/feedback from someone who is much older.  However, \textbf{age} doesn't always bring about wisdom. There are people in their later stages of life that carry over prejudices from their pasts. We need someone in office that will treat everyone fairly, and not have their decisions influenced by unfair practices that they find just.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small Larry King is terrible, always was. The guy doesn't know the first thing about some of the most important subjects in the world and you think he's "seen it all"? He might as seen however much you like, but that doesn't mean he got any of the things he saw.Did Bill forget that you can't rationally generalize anyone? Not everyone who is \textbf{old} is also wise. Did he suddenly forget about all the \textbf{racist} \textbf{homophobic} \textbf{old} people?And actually, if Bill has ANY problem with the times we live in it's precisely because it's the \textbf{old} generations that build this era! They made the worst mistakes that the youth has to fix, so gimme a break. The ass obsessed world was made by the oldies.Did Bill not even fact check the junk he says? And he thinks he's a rational guy? Ridiculous. Here's a reminder Bill: \textbf{old} people run the world, \textbf{old} people ran the world when all the worst mistakes were made, \textbf{old} people run all the horrible corporations and banks. It's not like you oldies weren't here and then suddenly now when the consequences of your actions show in the long run you pretend that you've innocently been somewhere else all this time? No this is the world YOU made!\normalsize   & \cellcolor{green!27}Homophobic, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}8/214 & \cellcolor{green!27}3.738 \\  \hline
  \cellcolor{green!5}\small \@BeaglesRuleTheRoost How? How did I misconstrue a single thing he said? He said it quite plainly, there's \textbf{nothing} to misconstrue.But it's great to see your process of reasoning only includes slandering strangers, brilliant, but let's see if you can actually discuss the subject instead :P\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@BeaglesRuleTheRoost Did you not hear what he said and read what I write? In his remarks Maher generalizes the youth and undermines them in the exact manner you just claimed he was claiming that people generalize the \textbf{old}. I did not whatsoever create straw men, I replied to what Bill said for goodness sake, go back and listen properly. I mean that's why I even bothered to write to begin with because he precisely made those statements about the youth and at the same time did not at all explain the \textbf{elder} generation :P and it's mistakes and it's issues. And yes, the older generations made the world we're living in, you were here, we were not.\normalsize   & \cellcolor{green!27}Elder, Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/117 & \cellcolor{green!27}1.709 \\  \hline
  \cellcolor{green!5}\small when mccain was running maher would mention how he was too \textbf{old} almost every week...so not really sure why he's upset about the "\textbf{ageism}" when he's a huge reason it's even a thing.\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small oh come on we all know he was joking,if he's joking at murderers he must be joking at mccain too for being old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Albert EinsteinI don't.  But, as a Republican, his "Anti-Republican Rhetoric" gets a little \textbf{old} after a while.  I don't take him seriously, but other people do.  And those same assholes vote.  And THAT is what scares me.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@Vladpryde Idiots vote all the times,its not something \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small +Vladpryde Which is interesting since people tend to align more and more with the Republican Party as they \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@KigondolI know that's true for me.  When I was in my late teens and early 20s, I was a liberal Democrat, which may surprise a lot of people.But then I grew up (I'm 32 now), had some life experiences, and saw the world for how it REALLY is, and realized that the Liberal Democrat mindset was more fantasy than reality, based on emotion instead of logic and reason.It's okay to have emotion, but it's also practical to have healthy doses of logic and reason.  And that is something the current crop of Lib Dems are seriously lacking.Now I consider myself a Moderate Republican.  I still have some liberal views, such as Marriage Equality, Women's Rights, and Global Warming beliefs (though I believe humans play 1/500th the problem when it comes to Global Warming; not all of it).But I am also a strong supporter of the 2nd Amendment and gun rights, smaller government, less taxes (for EVERYONE), free market, a strong military, and strong Law Enforcement at the State level.  I don't pander to PC bullshit or whiny \textbf{racist} minorities either.Therefore, I consider myself a Moderate Republican.  If anything, I'll probably vote more Libertarian than Republican if given the chance.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/205 & \cellcolor{green!27}0.488 \\  \hline
  \cellcolor{green!5}\small \@VladprydeI see.  Logic, reason and \textbf{common} sense enabled you to conclude that human activity contributes but 1/500th to the development of climate change.  And you accomplished this feat without emotion \& feelings.  Interesting. Tell me, can you share your formula or equation with us? On another note, as a libertarian, what's your opinion about the Secret Service not allowing people to bring firearms to the Republican National Convention?  I was shocked \& surprised that the 3 major republican candidates were so very quiet about this affront to 2nd amendment rights. I would think that they'd want as many people  to be armed as possible.  After all, it would make the delegates \& candidates safer.  Don't you agree?\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/118 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Abe} OttoEasy.  It's \textbf{common} sense: humans are only one out of many different contributors to Global Warming.  One active volcano, for example, puts out more Carbon-monoxide in one day than all the cars of a major city combined in one month.The only people who can't grasp this simple logic are the same idiots who think Sanders would make a good president.\normalsize   & \cellcolor{green!27}Abe, Common & \cellcolor{green!27}Religious Identity - Jewish, Social Class - Working class & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small +Vladpryde Ugh god... please at least try to hide your stupid when  out in public. You basically invalidate yourself by saying Carbon Monoxide... when the actual greenhouse gas that is posing a big threat is Carbon DIOXIDE.... But hey, when the scientists of the world have all come to a consensus that man made global warming due to CO2 emissions is real, and is a huge threat, why listen to them when you can sit at your computer eating \textbf{cheesy} poofs and googling conspiracy theory websites that tell you \textbf{nothing} bad is happening.Like I said, at least TRY to hide your stupid...\normalsize   & \cellcolor{green!5}Cheesy, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Abe} OttoJesus, really?  We're ONE of about 500 different things that give off CO2 on this planet.  Probably more than that.I have a hard time believing that, on this giant planet, there would be less than 500 different sources of CO2.\normalsize   & \cellcolor{green!27}Abe & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small \@Vladpryde I don't have the answers either, so why don't we leave it to the \textbf{engineers} and experts working in clean technology? Oh wait, oil companies are buying patents to stop clean energy solutions from seeing the light of day and the Koch brothers are fighting for taxes on solar energy.... Fossil fuels is hurting our planet tremendously. And to take your stance of "well... it would be too hard to get rid of..." is just stupid... That is how \textbf{nothing} is ever solved. We must work towards real solutions. Of course no one expects it done tomorrow you buffoon. The issue is \textbf{NOTHING} is being done TODAY so SOMEDAY we will have change... That is what people are fighting for. And with more clean energy, more jobs will open in the clean energy sector, and people will just need to migrate from fossil fuels to clean energy. YOU apparently need a clue.\normalsize   & \cellcolor{green!5}Engineers, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}3/153 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@BawnawgwaSnort.  You're conveniently ignoring the fact that, in the past 10 years, there's already been HUGE inroads with cleaner technology.  But like it or not, we have billions and billions of things on this earth that run on coal, oil, natural gas, and electricity produced by one or more of these sources.But nooooooo.....all I hear about is "WWAAAA!  Big Oil be BAAAADDD!  WWAAAAA!  I want my IPad, but the Chinese factory that produces it is POLLUTING!  WWAAAA!"That's all people fucking do nowadays is bitch and moan about Big Oil, "The Rich", and Republicans.  All while conveniently ignoring the fact that the MOST polluting (and corrupt) countries on Earth are countries like Pakistan, China and India.  Not the US.And hold on a minute.  You can't bitch and moan about taxes being pushed through Congress by the Koch Brothers against Solar Energy (and remember: the majority of Solar Energy is produced in FACTORIES overseas, which POLLUTE ENORMOUSLY), while supporting King Bernie and his ridiculous Tax Hikes against "The Rich" and Big Corporations.  You can't have it both ways, sweet pea.  You do realize that, because this is AMERICA, successful Solar Companies based here are run by very rich people, right?  That we allow people the freedom and opportunity to become successful enough to own and run their own companies and corporations that you NEED to produce the shit that you want....in this case, Solar Energy.And I need to get a clue?You are FUCKING delusional.  Deluded morons like you are the reason I stopped being a Liberal Democrat in my 20s.  You better wise up about how the REAL WORLD works here.  You CANNOT have something for \textbf{nothing}.  Not with Clean Energy, and not with "Free Healthcare/Education/etc etc". Everything is a give and take, and EVERYTHING costs something in this world.  There is ALWAYS a price to be paid; whether it's pollution for being able to have commerce (which gives you what you need and want), or enormously high taxes for tuition-free education.  Everything's got a price.  \textbf{NOTHING} is "free".It's not perfect, and you won't hear me say so.  But we get by just fine, and you will either accept that, or continue in your little pipe dream fantasy land of flowers and Kumbaya.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/378 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small \@Vladpryde God you are stupid. Ok... let's address some things.The Koch brothers taxing solar energy. They put a tax on it MAKING IT HARDER FOR INDIVIDUALS TO GET SOLAR PANELS RUNNING ON THEIR HOMES!!! I don't even know what you were trying to rant at there. The point of the Koch tax was to make solar energy not viable, thus making fossil fuels the only real choice, which puts MORE money into the Koch brothers pockets. Good god... good god, that wasn't hard to understand, but apparently for some people it is...And you realize the mega rich and large corporations pay almost \textbf{nothing} in taxes considering what they make right? To ask that they actually pay proportionally fair taxes considering their income brackets is not \textbf{communist}, nor is it out of line. We have tax loop holes and out of country tax havens to thank for that...And people bitch about big oil because THEY BUY OFF POLITICIANS TO STOP CLEAN ENERGY SOLUTIONS SO THEY MAKE MORE GOD DAMN MONEY!!!! Again, what about this is hard to grasp... I don't even know.And you  still are not getting it. Plants that make products run on fossil fuels because their equipment does, because WE DON'T HAVE CLEAN SOLUTIONS YET!!! That is what people are working for... when clean energy solutions to machinery and equipment are produced, they can be swapped out, but most focus is going towards reducing car pollution and pollution from factories. And you ignored my question as to why you are attacking people for wanting clean energy... Why is reducing pollution bad? lol... so ridiculous.And again, you are adopting a "It's too hard to change, so lets not and watch the world die..." attitude. \textbf{Nothing} gets done by people like you. The big reasons clean energy solutions have been so slow going is BECAUSE of fossil fuel industries working hard to stop it, and that is not a conspiracy theory, they really do that by buying politicians. Sorry, some of us don't want the world to warm up, causing mass extinctions in species, flooding coastal areas, causing devastating weather phenomena, causing oceans to become incredibly acidic, leading to mass extinctions of marine life.....\normalsize   & \cellcolor{green!5}Communist, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!5}3/368 & \cellcolor{green!5}0.815 \\  \hline
  \cellcolor{green!27}\small \@BawnawgwaJesus, you lose WAY too much sleep over this shit.  I don't buy conspiracy theories about the rich and not paying taxes.  And that's exactly what it is.  You can't bitch about the Koch Brothers forcing people to pay taxes for Solar Energy (or whatever the fuck it is you're ranting about), and then turn around and support King Sanders....who's entire campaign revolves around taxing ALL citizens unnecessarily for shit that \textbf{nobody} wants.  It doesn't work that way.  You can't complain about taxes and then support Sanders.  I don't think so.  That makes you a hypocrite."And again, you are adopting a "It's too hard to change, so lets not and watch the world die...""No I fucking didn't you stupid cow.  I've repeatedly said that I believe Global Warming exists.  My stance on it is simply "let's work at our own pace, or a pace which is best for humanity in terms of job growth, industry, and environmental status."  And what I mean by that is that we're doing FINE at the pace in which we're phasing out \textbf{old}, outdated means of energy (such as coal and oil).  If you do this shit too quickly, you won't have the technology in place to make it work, and you'll lose jobs because those industries (oil, coal, etc) will lay off jobs and put people out of work.In the next 10 years, if we reduce the number of Coal factories and Oil rigs/companies by, say 20, that will be a huge step towards building a Clean Energy Industry.  That gives time for technology to improve/catch up, as well as knowledge, education, and training for those fields which are required to have sustainable job growth in the Clean Energy Industry.If, for example, we'd shut down 20 of that industry in the next 2 or 3 years, that would put a LOT of people out of work, because this country isn't ready for it.  And what are you going to say to them?  "Sorry you can't put food on the table for your families anymore....we need Clean Energy NOW."You see, the difference between a dumbass like you, and someone like me, is that I don't lose sleep over this.  I acknowledge that there is NO such thing as a free ride in this country, or on this planet.  Every single industry, which gives us the ability to have electricity, gas, or even an IPhone, all adds to Global Warming.  Every single one.  And it's beyond ridiculous to expect these things to just go away in the name of Environmental Change.  Not gonna happen.  We are too tied into these objects.  Take away Oil, and this country would go back to the dark ages; I promise you.  And there's NO other source of energy for cars that we can afford, produce on a mass scale, or sustain at this time.Hydrogen?  WAY too expensive, and incredibly difficult to produce ON A MASS SCALE.So until we find CHEAP, reliable, abundant energy that works ALL the time, then we're stuck with Oil.If we build Nuclear Plants, people like you will still bitch about it.If we build Clean Coal (I know it's an oxymoron) factories, people like you will still bitch about it.If we build Solar plants and install panels over wide areas of a city, people like you will still bitch about the cost of housing (which will inevitably go up with such installations) and the impact to the environment due to cutting down trees or threatening protected wildlife areas.You CANNOT have both in this world.  You cannot bitch about this shit....then demand IPhones from factories that pollute.  You cannot bitch about the price of gas....and then drive your kids to soccer practice in your V8-powered car.  Or Prius (and I trust you know just how much pollution goes into making ONE Prius).The sooner you get on board with this, the happier you'll be.And drop the "Tax" and "The Rich don't pay" conspiracies.  Otherwise, I have to believe that Dick Cheney caused 9/11.  Or something equally stupid.\normalsize   & \cellcolor{green!27}Nobody, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/682 & \cellcolor{green!27}0.293 \\  \hline
  \cellcolor{green!5}\small \@BawnawgwaMore pointless rambling about Conspiracies and nonsense about the wealthy.  Why should I take you seriously about that?  Because BERNIE told me so?  Give me a fucking break."Bernie Sanders is taxing people for thiings they don't want? Yep, no one wants affordable health care with better coverage than most have."I'll remember that when I hear about small businesses and couples losing their healthcare coverage, \textbf{doctors}, and being forced to accept plans that don't cover preexisting conditions, or forcing them into a coverage plan that doesn't work for them and that they don't want.  Yeah, I'll remember this when I read of numerous small businesses losing their healthcare coverage plans because of higher taxes that don't conform to some idiotic liberal nonsense.Tax Havens....you mean, countries with less restrictive tax laws than the US?  OOOHHH BOOO HOOOO!  Oh NOES!  Don't wanna give EARNED MONEY to BIG GOVERNMENT.  OHHH BOO HOO!  CRY CRY!Your stupid ass doesn't even realize that ANYONE can go to one of these countries and put money away.  You don't have to be "Rich", you just have to be SMART.You wouldn't know trickle down economics if it smacked you in the face.  This is a made-up term to play on gullible people's emotions.  You're truly stupid if you think the CEO of a multi-national corporation should be making the same kind of money as a substitute teacher or burger flippers.  It's the same kind of stupidity as saying that there are "Gun Show Loopholes", which there AREN'T.Are you REALLY so stupid that you think business in this country should be FAIR?  That money should be FAIR?  Are you THAT fucking stupid?  Do you have any idea how much in poverty this country would be if we played by the rules of what's "Fair"?Wanna get ahead?  Wanna make more money?  EARN IT.  I know the idea of people having the FREEDOM to make as much money as possible just chaps your Socialist ass, but....well, that's the REAL WORLD.  Deal with it."And... What the hell is your argument? You are talking about changing stuff today, but how all these jobs and money will be lost because we don't have the technology yata yata. Are you this stupid? Are you... this stupid? The answer is clearly yes."So, insults without answering the question or addressing the problem.  Got it."What happens when we move from fossil fuels to clean energy? Oh, they lose money"Bullshit.  They aren't going to lose a dime because, as you pointed out, they're buying the rights to this technology and these patents.  Are you so stupid as to believe that they're buying these rights/patents so that they can keep the country dependent on fossil fuels?  Humanity is constantly evolving (unless you live in a 3rd world shithole); they aren't "sitting on these bills to halt the advancement of clean energy".  What a bunch of crap.  The reason these companies are buying out these patents and rights is to MAKE MONEY when it happens, because THEY are the ones who are going to be making it and, thus, making PROFITS from it.  They're not buying something for \textbf{nothing}!  What a bunch of stupid bullshit, lmao!You don't GET this?  There is no conspiracy here!  It's \textbf{common} sense!  If I'm a corporation who deals in fossil fuels, and I'm watching the markets, politics, and the advancement of the Clean Energy field, then I'm going to buy as much rights/patents as I can NOW, before prices go up on them.  I do it because I CAN.  And it's not illegal to make money in this country by doing so.  Of COURSE I want to buy them out!  I'm a corporation!  My SOLE BUSINESS is to make PROFIT by providing things people want and need; in this case: Energy.You don't like it because corporations have the ability to spend billions on buying bills, patents, and rights, and the average person doesn't?  Tough shit.  Start up your own company and do something about it.  That's Capitalism."like make it unreasonable for people to power their private homes with solar energy instead of relying on the power plants"Again: bullshit.  Anyone can go online, buy a solar panel or two, and hire someone to wire it to their house.  Fuck, HOME DEPOT sells them for decent prices!  People do it all the fucking time in this country, and no power company comes out and harasses them.  Just more paranoia and bullshit from you."And you sound like you don't think the Koch brothers are evil"No no, sweetpea.  I just DON'T CARE.  And I promise you that the majority of Americans don't care either.  You know what they care about?  Their IPhones, IPads, jobs, couches, cable, internet, free time, paid bills, putting food on the table, candy, soda, beer, the big game on Sunday, and spending time with their kids.  We don't wake up every day biting our nails and crying about shit that we have \textbf{ZERO} control over.  And if you think the American people, or even politicians, have control over a billionaire CEO of a company, then you're beyond retarded.  Because as much as you want to bitch about them, they are also PRIVATE CITIZENS.  Just like you, and just like me.Wanna stop them from being "evil"?  The BEST thing that you can do is NOT buy products from "evil corporations".  If you don't buy their product, THAT is what hits their pocket books the MOST.  Not penalties or citations from the government, and sure as fuck not taxes.  The only thing that taxing them does is make them raise the price of their products to counter the additional cost of taxes and regulations.  What, you think that TAXES are going to make products CHEAPER?  Are you THAT fucking stupid?But ooohhhh....can't have that, huh?  Can't boycott companies because you want your cable and internet?  Want your burger and fries?  Want electricity and gas for your car?Well....yeah.Now, I'm done with you.  Your proof that socialists and liberalism is a disease in this country.  Now, if you'll excuse me: my basketball team full of millionaires and owned by a billionaire are in the Playoffs.  And it's being presented to me for free by a multi-billion dollar media corporation on local TV.  And I'm grateful to watch it.  And I'm done with you.  Bye now.\normalsize   & \cellcolor{green!5}Common, Nothing, Zero, doctors & \cellcolor{green!5}Age - Youngsters, Nationality - General, Social Class - Working class & \cellcolor{green!5}4/1064 & \cellcolor{green!5}0.376 \\  \hline
  \cellcolor{green!27}\small \@Vladpryde \textbf{Dumb} ass.... The Koch's are in the oil business. You can't not buy their crap... And no one will lose healthcare coverage you simpleton. Do you understand what single payer is? Apparently not. It is when EVERYONE gets healthcare paid through taxes, and under Bernie's plan, that involves a 2.2 raise in income taxes for the vast majority of Americans. This actually takes away the burden of employers needing to cover their employees healthcare. Honestly, everything you say sounds like a troll. It is sooooooooo stupid that I can't believe you are serious and are trolling... Ah well, your idiocy means \textbf{nothing}, because I hate to break it to you, but Trump or Cruz will never win the presidency. I know... it must be heart breaking for you. And Hillary is on the rapid decline. Then let's not forget that those of us with a brain (this doesn't include you) will be voting the do \textbf{nothing} republicans out of congress the earliest they can be kicked out. We'll have a liberal president and liberal congress. The country will FINALLY begin catching up to the European countries that are vastly ahead of us on almost all fronts except military... and the middle class will boom again.But feel free to leave, because no one wants people like you who do \textbf{nothing} but impeded progress around. Good riddance to you and your filthy ilk.\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/233 & \cellcolor{green!27}1.717 \\  \hline
  \cellcolor{green!5}\small I'd vote for Bernie Sanders in a heartbeat; having said that, I would be a little nervous electing someone over the \textbf{age} of 70.  I don't think it's being "\textbf{ageist}" because I have no doubt that many people 70 and up would do just fine--I just think it's being realistic.  Realistically, that person could die in office.  Realistically, their health is probably waning.  Realistically, they may be sharp as a tack at 75 but then could begin developing dementia at 76.  They could also be just fine for 8 years and do an excellent job, but it just seems like such a gamble with a person north of 70.\normalsize   & \cellcolor{green!5}Age, Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small This is a sad dilemma. Especially since at \textbf{age} 30 I am less in touch with aspects of my own generation back when I was fifteen. No I don't care about assess or the Kardashians. Clearly I am insane.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Right, cause \textbf{old} guys never enjoy looking at a young, hot, ass- whoever heard of that? Jesus Bill, you must be running out of shit to talk about or something. Young ppl run everything?  Take a look around you genius- who is in power? \textbf{Old} fucks that can't bring themselves to let go of \textbf{old}, tired paradigms and norms- that's who. And ppl not wanting to vote in an \textbf{old} president is entirely understandable- considering the last few vice presidents we've had it makes me a bit nervous.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}4/88 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Gerry Brown did a great job turning Cal around.  Now he's trying to blow it  by not doing better with the water issue \& lately trying to forcefeed big pharma poison (vaccines) on everyone .\normalsize   & \cellcolor{green!27}Gerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Doesn't he know that \textbf{black} men has loved asses for generation\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small So...we should all just arbitrarily defer to whatever "wisdom" Pat Robertson spouts simply because he's survived for more years than most of us? Call me \textbf{crazy}, but I think it's entirely possible for someone to be an intellectually vacuous loser during their youth and still be an intellectually vacuous loser by the time they're pushing 80. Doesn't matter how many years you give 'em, those who refuse to learn simply won't learn.Of course, I suppose one could always make the argument that Robertson is actually a genius for manipulating as many weak minds as he does, and that even he doesn't truly believe the bullshit that comes out of his mouth. But even if that were true, it would only be evidence that not all geniuses are worth listening to, not evidence supporting why we should hold arbitrary reverence for our elders.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/143 & \cellcolor{green!27}0.699 \\  \hline
  \cellcolor{green!5}\small +TheThrashyOne Gotta love maher logic. If they're \textbf{old}, they're automatically smarter than everybody else.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Through fire and war, the young did prevail.Through land or by air or by unfurled sail,And when war subsided, the young took ahold,Fiery hearts, passions, the brave and the bold.When brevity aged, grew wisdom and calm.Good leaders are born midst gunning and bombs.But then \textbf{old} leaders were replaced by the new,And dragged down the \textbf{nation}, a decision of rue.No merit, no precedent, no experience,Did define the new leaders, no rightful pretense,And then stagnation threatened the land,But \textbf{nothing} was done till the worst was at hand.And now a great country, a trillion in debt,Stopped in its tracks by the grossly inept,When will it end? When will we be free?When will we come to stop this tyranny!Oh, when will we go back to those glory days...When one made a ruler did change the \textbf{old} ways.Democrat, Republican, Socialist... Labels that prevent anyone from doing anything. Parties, affinities, rivals, conflicts... I just want to see something done. Please. I'm begging you, America.\normalsize   & \cellcolor{green!27}Nation, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Nationality - General & \cellcolor{green!27}4/176 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small +irllcd13 By president I'm assuming you mean sitting in an \textbf{old} folks home and pretending he's in the White House as Alzheimer's eats away at the remainder of his brain.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@LazyClown48 nah rand killed hit own chance ever since he decided to poke the \textbf{fatty} in the first debate, Ted seems a bit fishy to me\normalsize   & \cellcolor{green!27}Fatty & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@simunator that \textbf{fatty} needed to go anyway.\normalsize   & \cellcolor{green!5}Fatty & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small +Blood Moon Funny that you couldn't even retain the message of the clip you watched a second before heading into the comments to show everyone how \textbf{dumb} you are.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Wow, an honest to God civil answer. Good for you, I commend thee. I'm glad you asked because ''better career choices'' in your end means really means ''better paying choices''. Now unlike you I actually grew up rich. Not über rich, but absolutely in the top 20. But I teach school children. This is not a lack of trying nor a poor career choice, this is something I genuinely find exciting and it makes me happy. And because I live in a social democracy, I too am Danish, I can actually make a decent living off of it. I am comfortable with the idea that I will never become a rich man. I will never be a millionaire, but I'm very, very happy. Now I want to make it very clear that \textbf{nobody} is paying for me, because I too pay tax, and I still pay more than any American. Also because so much tax goes into education, the level of education in public universities is no lower than the private universities, so we have no equavelant to your IVY league universities. We do have expensive private universities, but they're worth no more on a resumé than a public education. So most of Denmark's top 1, including our royal family, went to public university, and so they too have used the system. Now if your tax went up and you had to pay more, you would, from a certain perspective, be supporting others. But is the happiness and security of your fellow countrymen not worth it? I mean looking from the outside it seems like you genuinely despise each other. The problem is that not all people are inheirently bright enough to make ambitious choices so you can A. Leave behind or B. Allow them to live a decent life with a profession they can be productive in.I mean for fuck sake, you have people calling universal healthcare the work of satan and communism while coughing up blood!!! The only conclusion I can come to is that \textbf{nobody} in America sees themselves as poor, but rather, because of this ''American dream'' idea , see themselves as temporarily inconvenienced billionaires. Is this true? That was a real question btw, I genuinely want to know.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/374 & \cellcolor{green!5}0.535 \\  \hline
  \cellcolor{green!27}\small \@Kristian Brandt Shit posting never gets anything done, if you want to have a civil conversation then I don't care what your political affiliation is. Let me start off by saying that I'm going into petroleum engineering which will net me around \$100,000-\$150,000 a year. At the current tax rate that means I'm going to have to pay between 20,000-30,000 a year in income taxes alone. So right off the bat you can see why raising taxes would elicit such an angry response from me and others like me. I'm not sure how things are in Denmark but in America the lowest class is looked down upon as leaches and not without reason. The average cost of keeping one person on welfare in the states is \$25,000 a year. That's disgusting. So no I have no desire to help those people in the least. As for healthcare I can afford my own and I don't want to be forced to pay for benefits I'll never use. Why should I, a healthy 22 year \textbf{old} male, pay the same rate as a pregnant 40 year \textbf{old} \textbf{woman}?\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}3/186 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Well you're not paying for the 40 year \textbf{old} pregnant woman's healthcare, you're paying tax and a portion of that is spent on healthcare. The government won't hand you the bill for Donna's labour. I can't see how your tax situation would affect you emotionally, cause like I wrote I, a 27 year \textbf{old} working class, pay much, much more than that. As for the poorest, who we weren't discussing, you'd imagine welfare leeches would be a problem with our system, but we have an effective solution. This is the problem with American politics, the slightest suggestion that you could learn from other nations, and the republicans and southern liberals cut your hand off, politically speaking, for even hinting that the US might not be the best at everything. Well the solution is called ''activation'', and what it does is that if you've been on welfare for more than 3 months, the government will find you a place to work, and your pay will be your welfare check, which is less than what the job would actually make you, thus encouraging you to get a real job. This ensures only those who genuinely need welfare get it, because the alternative to a real pay check takes just as much work, but pays less.Also you're 22 mate, it's a little early for the victory tour. Humility truly is a charm long lost on you Yankees XD\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/236 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}\small \@Kristian Brandt That's certainly a better solution then the American welfare system and I have no problem admitting that there are some things other country do better then us. As for my healthcare what I'm saying is that I shouldn't have to pay for something I'll never use, I used the example of the pregnant \textbf{woman} because I'm never going to get pregnant thus I shouldn't have to pay for a plan that covers labor expenses. I'm not sure what you mean by the victory tour comment.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small Well what of those of your countrymen who oppose nuclear warfare? They're still paying the maintenance of your warheads. What of those 2nd amendment nuts who believe the police is obsolete and that all you need to solve crime is a bible, a semi automatic rifle and a can do attitude? They're still paying the police. If every American, or every Dane for that matter, was allowed to tailor their tax to their needs, society would collapse because every country is, ultimately, nations of I. Someone needs to force our wallets for the betterment of the nations. \textbf{Nobody} likes paying tax, but it's the price we pay for security and high standards of living. And like I wrote, your tax is not paying healthcare, it's paying everything. And the idea that you should pay more the more you make, is not a punishment for ''smart career choices'', it should be so because that way your tax will have the same impact on you, as it will on the ''failures'' working the nightshift in walmart.The sad truth is that some people just aren't that bright, and punishing them by making them pay more than the top(i.e. leaving them behind) is not fair. Especially not in a country like the US where people don't have equal access to social services. The victory tour comment was to underline that you are in fact 22 and still at uni, yet you're talking like you've practically bought the penthouse. Life is cruel mate, and an arrogant attitude like that leaves you open for a knock out. I know you Yanks love your sports references, so let me say this. Don't go southpaw till the last round, or you'll end up punchdrunk.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/287 & \cellcolor{green!5}0.348 \\  \hline
  \cellcolor{green!27}\small Sorry this is a bit long : But like I said with the social services we're provided, services that working class Americans pay a lot of money to have, we're realistically walking away with more disposable income than your average American. We also have a much narrower wealth gap than you, and we have no absolute poverty, and you do. In case you're wondering there are two pillars of lower class poverty. The most \textbf{common} in western nations is relative poverty. Relative poverty means you're poor relative to your \textbf{nation}'s standard of living. You can feed yourself, but you won't spend a romantic summer in Paris. Absolute poverty means you're actually having serious problems taking care of yourself, and you're one payment away from eviction. This is what you sometimes refer to as ''trailer trash''. Sadly this also means you have the highest percentage of child poverty of any western \textbf{nation}. If you still think privatised medicine is a good idea, then consider this. Not only do you have the lowest life expectancy of any western \textbf{nation}, you also have the heighest infant mortality rate. Which is heartbreaking. This is why I say that looking from the outside, it seems that you genuinely despise each other. The top 30 must know this, and yet they're not willing to have their tax raised. Look, if you cut your defense spending, which is way too high, raise working class tax 15, and tax the 1 as much as the working class, those numbers would improve dramatically. You have inner city schools that spend more on metal detectors and security than books which is just mad. And introducing advanced pedagogy to education would also help at risk students. It's hard to say how much people here pay, because  tax is adjusted. People in my field usually pay around 40, although I pay 50 because my master's degree gives me a slight pay raise, as does my Ph.D(wasn't going to mention that because it seems like boasting, but in this instance it's relevant). A slight tax raise would also enable you to look into the enviroment. I know many conservatives don't give two shits about this, but if you've ever been to Los Angeles, you'd know what I'm on about. As for my hypothetical life in America, I'm not sure you're right. My epilepsy didn't ''wake up'' till I was 14, however I was born with eczema. It went away after a few years, but it's still a pre-existing condition. I'm sorry if seem a bit zealous, but I just don't see how you can put a price on being healthy.\normalsize   & \cellcolor{green!27}Common, Nation & \cellcolor{green!27}Nationality - General, Social Class - Working class & \cellcolor{green!27}3/437 & \cellcolor{green!27}0.686 \\  \hline
  \cellcolor{green!5}\small \@Kristian Brandt Don't worry about it, we both have busy lives. I can't agree with your first point. \$100,000 a year with 20 tax and less then \$10,000 for for all of the same benefits is more then \$40,000 with 50 + tax if not more, you don't need to be an engineer to see that. As for the wealth gap that argument is extremely weak when you start to analyze what it really means. Does it really matter that people like Bill Gates makes billions of dollars a year and I'll make maybe \$250,000 annually by the end of my career? No. I want to do well for myself and I couldn't care less if 1 makes an outrageous amount of money. Yes Denmark has a small wealth gap but at the same time the average person is much poorer then the average American for it.Raising the taxes by 75 is completely unacceptable. Yes the infant mortality rate is high in America but the lives if 1.6 of children born is not an adequate reason for such an unreasonable \textbf{hike} in taxes. The defense budget is too expensive, I'll give you that. Personally I don't think we should spend a dime protecting nations that don't want us in the first place.The reasons the inner city's spend so much on security equipment is because the gang culture breeds violence, they really are necessary to keep the schools safe.Boast all you want, a PH.D is something to be proud of.I don't really have an opinion on the environment. I don't live near Los Angeles but all of the other cities I've been to a remarkably clean with the exception of Pittsburgh.I don't put a price on my personal health, but I'm not going to pay someone else's hospital bill.As for your final point let me put it like this: Denmark has a population of smaller then that of New York City. Do you really expect us to take the option of such a if relatively small country seriously?\normalsize   & \cellcolor{green!5}Hike & \cellcolor{green!5}Nationality - Italian & \cellcolor{green!5}1/343 & \cellcolor{green!5}0.292 \\  \hline
  \cellcolor{green!27}\small Yeah I've always found that hilarious, you could fit our entire population in New York and still have room for 3 million more XD I didn't understand that last bit. I'm thinking what you ment to write was ''do you expect to take the opinions of such a small country seriously?''. If this is true, then I have to ask you to slow down, because you can't rule a \textbf{nation} irrelevant because of its size. The Vatican, which is actually a country, has the world's smallest population... Yet they house the richest and most influential corporation in the world, the Catholic church. Also we're actually quite a large country, because Greenland is Danish territory, and we haven't granted them independance yet. Although to be fair their total population is 50.000. I will absolutely agree that Americans have higher income than us, but our standard of living is still higher than yours because our tax is spent on shit which makes our lives better. Feel free to look it up. Apparently we're also happier. And Copenhagen is the cleanest capital in the world, and trust me mate, you can tell. I'm a bit curious, have you ever left the States? Also in which city do you live. I'm thinking Houston, or somewhere in Texas. Your name is a bit southern, very strong, and oil is big business in Texas.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/228 & \cellcolor{green!27}0.439 \\  \hline
  \cellcolor{green!5}\small Eh debatable, I would rather spend my money how I see fit then have a nanny state decide for me but I have a feeling we're never going to agree on that haha.I've left the states quite a few times. I've been to Mexico, Jamaica, and New Zealand to name a few. I'm actually from Maryland which is actually an extremely liberal state. My name is actually a "Americanised" version of Schlagle which is German. I do plan on living in Texas after university because Petroleum \textbf{engineers} make more there then most places in the western world.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small Ah cool, I studied in Auckland. It's a fantastic country. My American geography is awful, but isn't Maryland somewhere near Pennsylvania? Haha my name is unique to Scandinavia. Not sure if you've worked it out yet, but I'm not a \textbf{woman}. Many people read my name too fast, and get Kristen or Kirsten. In both English and Danish Kristian is pronounced exactly like Christian, it's just that Christ is ''Kristus'' in Danish, hence the K. I travel a lot and it's caused a few misunderstandings XD You're right we won't agree, but it's nice to meet a conservative mind that is actually open to argument, this was beautiful mate ;) So round two, GUN CONTROL!! Better not XD\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small he is way ahead of you. what ever your age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small you know it is a question on the immigration papers that asks if you have even been a \textbf{Nazi} or fascist. you seem to have it all.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Shhhhh \textbf{nobody} tell him\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small he is a socialist.............far from a \textbf{communist}....the right is actually closer to facisim than he is to communism.......but corrupt capitalism leads to socialist revolutions\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Health Care DOES NOT completely belong in the private sector anymore than education does....its a human right....which is why we treat you even if you dont have coverage....but now tooo MANY UNINSURED  are breaking our system....and why do you not mind that the private sector has us paying TWICE AS MUCH AS THE NEXT HIGHEST WESTERN COUNTRY???. Insurance and Big Pharma have been raping us dude.You dont have a choice about needing healthcare when you need it...its not like buying a house or going to a fancy school...And no one is saying private expensive heath care would not be there too.......look around you man....no other modern \textbf{nation} has millions excluded from insurance or treatment....wake up pal...and again I AM AN ENTREPRENUER   PAID FOR MY COLLEGE SERVING DURING NAM..incorpotated in 1989.I HARDLY WANT A TOTAL SOCIALISTIC ECONOMIC SYSTEM.....and i not single payer.whats your solution?....the right doesn't have a solution because they dont give two shits about anybody but themselves...well I care about my fellow man and America in General. You just are too young to realize we use to get health care from our employers....hell when I came back from serving and using my GI Bill I worked at 7/11 and even THEY provided health care after 90 days!!. Corps took away the pensions, took away worker's heath care and they just screwed about 108 job categories out of their OT....WAKE THE HELL UP SONNY BOY OR YOU WILL not enjoy the \textbf{nation} you hope to make a higher income in.....there is plenty of profits for decent wages and benefits....ita just pure ugly greed  and \textbf{nobody} getting in there faces like the early labor strikes that established everything YOU take for granted,\normalsize   & \cellcolor{green!5}Nation, Nobody & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}3/281 & \cellcolor{green!5}1.068 \\  \hline
  \cellcolor{green!27}\small +Will Whitman Why? He can't pay for anything he's been campaigning on. The real men with plans would be \textbf{Jerry} Brown or John Kasich!\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small David Mathew nope. he lost because of \textbf{black} people, Latinos, and \textbf{old} people.\normalsize   & \cellcolor{green!5}Black, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small This actually has no basis in fact.  Pop culture has always been juvenile, each generation is overall smarter and better educated than the previous, and if you look at our congress, clearly \textbf{ageism} hasn't had much effect on who we choose to govern.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small So wait. When John McCain at \textbf{age} 72 in 2008 runs for president he's too \textbf{old}, but when \textbf{Jerry} Brown at \textbf{age} 78 is excluded for 2016 because of his \textbf{age} we're \textbf{ageist}? Gotta call you on your unstandardized standards Bill Maher. And I actually like \textbf{Jerry} Brown and didn't vote for McCain. Just saying...\normalsize   & \cellcolor{green!5}Age, Ageist, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}7/55 & \cellcolor{green!5}12.727 \\  \hline
  \cellcolor{green!27}\small Spot on... We are definitely a shallow \textbf{nation}...\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Wasnt Bill Maher one of the people that was dissing McCain for being to \textbf{old} to be president?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Generation I can't deal with change and \textbf{sexual} liberation, hypocrites!\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small But people aren't celebrating the human ass in general—they're celebrating beautiful \textbf{woman} who have voluptuous asses, just as the Greeks did when some unknown artist made the statue of Aphrodite Kallipygos, Aphrodite with the beautiful rump.  The cultural moment is not a moment of celebrating the female ass, since we've been doing that from time immemorial—it is instead the moment when the \textbf{woman}'s ass isn't just a generic indication of her sexuality, but instead a moment when people are willing to talk about anal \textbf{sex} openly.  You show Nikki Minaj spreading the cheeks of her ass apart, a clear invitation.  And you yourself joked about teenage girls who take the Christian abstinence pledge who let their boyfriends fuck them in the ass—you would not have been able to say that on the air forty years ago, even if forty years ago you would have liked to have fucked a  high school girlfriend in the ass.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/155 & \cellcolor{green!5}1.29 \\  \hline
  \cellcolor{green!27}\small ass fixation is not a young thing bro hahah young dudes love tits cause they havnt had \textbf{sex} yet  ass worshipers more like ass calves quads hamstring worshipers have had enough \textbf{sex} to know that the visual stimulus of these bodyparts are important in a \textbf{sexual} partner the egyptians knew it the greeks knew it and the romans knew it it has taken 2000 years to socially reacept the beauty of the female form after 100 of years of white \textbf{pancake} butt\normalsize   & \cellcolor{green!27}Pancake, Sex, Sexual & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Gender - General & \cellcolor{green!27}4/82 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small I had to come back to this vid after Kanye West announced on the VMAs that he's running for president in 2020. He believes in new ideas not just for himself, but for everybody.Backing up on what Bill is saying about wisdom coming with \textbf{age}, Kanye still has a lot to learn. I call Kanye's announcement to run for president as in vain. Sure, he has ideas, but are they the right ideas? Are they the best ideas?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small +Teddyballgame9 Yeah because Mikhal Gorbachev did \textbf{nothing} who wasn't a reformer - -Reagan increased the War on Drugs, increased income  inequality, opposed \textbf{g\textbf{ay}} rights, and hated the idea of universal healthcare Also how may lives Reagan saved when he ok'd mass killings in South America\normalsize   & \cellcolor{green!27}Gay, Nothing & \cellcolor{green!27}Age - Youngsters, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/45 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Clearly Bill and company forgot what they did and what they thought about the world when they were young. They were the rebellious generation that defied their parents, with hippie style and socialist utopic ideas (that they quickly abandon as soon as they had to live on their own salary and not their parent's allowance),  then quickly turned into Yuppies.They were the first generation of spoiled kids who could afford to buy a new car at the \textbf{age} of 19. A house by the \textbf{age} of 25, let alone the money they blew away in coke (the white powder drug not the drink).By the way, the \textbf{old} generation under 70 loves facebook (I know a few \textbf{old} ladies hooked on it)About ass... lets see: who invented playboy? and micro-skirts? the millennials certainly weren't! it was cool when they did that nudity thing, but is not cool now that the not-so-young millenials do it!Basically in their own way, when they were young, they did the same stupid shit some of the millenials are doing now.Does anyone remember how New York was like in the 1980's? it was the world capital of dope and crime, courtesy of the young baby boomers.As we grow up we become wiser, the same thing is happening with the not-so-young millennialsI'm a 'Millennial' and I feel \textbf{old} and tired!!! I will never have the same live prospects that the baby boomer's had, not even a glimpse: education is now expensive and a college degree does not give anyone a certainty of a well-paid job;There are no stable jobs anymore and the paychecks are smaller; Houses are 4000 more expensive now than in the 1970's (and is not just because of the normal inflation);We will have to pay more taxes to support the growing number of retired \textbf{elderly} baby boomers that complaint about the world THEY created; For my generation retirement (if ever) will come at the \textbf{age} of 75, not 62 or 65;We are going to have to deal with global warming and other natural hazards we inhered;There will be a shortage of resources (overused during the last 3 generations);Wars in the middle east, the prospect or a real WWIII and its consequences; My life expectancy is shorter than the baby boomer's.We are not the rebellious ones, we barely protest and mostly accept the establishment (except small groups).Should I go on????Baby boomers: can you really complaint about us or about yourselves?\normalsize   & \cellcolor{green!5}Age, Elderly, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}7/419 & \cellcolor{green!5}1.671 \\  \hline
  \cellcolor{green!27}\small you have a whole lot of "facts"  completely wrong. And you obviously think what our folks generation set up for us was easier...that's total crap my friend  Just for starters   my first house in 91 cost 110,000 in Chicago land   my fathers first 5,000 in the 50.. todays housing has barley tripled from the early nineties  and your talk about work it really naive, as is the world now a vastly more stable situation around the world.  And there certainly ARE stable positions, just far less manufacturing, which WE WERE EDUCATED ABOUT IN 1970 AS INEVITABLE AS OTHER AGRICULTURAL COUNTRIES BECAME INDUSTRIALIZED   BOO FUJCKIN.WE NOW HAVE THE LOWEST FUCKING EMPLOYMENT 3.9 SINCE 1960.And we HAD TO SERVE AND FIGHT  .THE SIMPLE FACT IS, ABSOLUTELY NO GENERATION IN MODERN TIMES CHANGES SO MANY THINGS  THAT HAVE MADE THE FOLLOWING GENERATIONS LIVES FAR IMPROVED. AND YOU CALLING US REBELLIOUS AND YOURS NOT IS YOURS GENERATIONS PROBLEM MORON. And the ridiculous delusion about us selling out, your so ignorant and think the bull shit labels  used for us are even close to accurate. We did major in subjects in college and work in jobs benefiting society, as apposed to the say Gen X  whose main concern  or goal was to get rich. AND .LET ME MAKE ONE THING CLEAR YOU IDIOT MILLENNIAL  LIKE TO SPOUT OUT LIKE ITS REALITY.  \textbf{Nobody} sold out anything and we certainly were  not socials idiot. We were the first generation where BOTH THE WIFE AND HUSBAND WORKED AND TOOK HIGHEDUCATION SERIOUSLY.  The number of laws we passed to radically change how minorities the environment, the work place, access to loans for college, etc etc etc..is us never quitting in trying to achieve those idealistic youthful ;riorities in action \textbf{dumb} fuckl, i\normalsize   & \cellcolor{green!27}Dumb, Nobody & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/296 & \cellcolor{green!27}0.676 \\  \hline
  \cellcolor{green!5}\small at 4:18 I agree with the Maher.  In Catholic Tradition, we find all life valuable no matter how \textbf{old} or how young.  ahem, ahem.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small "If it's (\textbf{Jerry}) brown, flush it"\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small i just checked Wikipedia and i found tha both me (32 years \textbf{old}) and my nephew (10 years \textbf{old}) are both part of the generation ass, since members of this generation are those born between the early 80's and early 2000's. So this world wich is now governed by the great Ass, will continue to be ruled by it for another 70 years, or maybe even 80 or more, since longevity is increasing.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small As much as I agree I also disagree, I agree that there are those of the older generation who are being pushed out because of their \textbf{age} but are still some of the sharpest people about, Larry King being an example of this. I also agree that my generation are has got stupid trends, however I disagree with the fact that all of our youth are too concerned about ass, there are a lot of youth out there, 20 odd years of \textbf{age}, who have spent there 20 years studying and applying their chosen subject to real life and have mastered it to a T and I know wisdom comes with \textbf{age} but there are a lot of the older generation in high power who like to ignore wisdom and can't keep up with world society and can't use their wisdom for the world we leave in.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/147 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small "We venerate the young and let them rule everything."I think that's because the young are the ones with disposable income that they are willing to give you if you can do slight of hand in your advertising. \textbf{Old} people aren't swayed by advertising the way young people are, so advertisers doesn't bother with them.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Wisdom is great but when you get \textbf{old} your cells start to degenerate. That includes your braincells where this "wisdom" comes from.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Basically, the same group of people who always ruled the country are still in charge.  Rich white guys.  The Lords of the Universe are no longer \textbf{old} men however, they're younger, brasher and less seasoned and they're businessmen, not statesmen or people versed in any kind of ethics.  Ethics and the business culture are as oil and water.  Wall Street habitually replaces CEO's when they get into their 50's.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small So what if he's 78 the president of Ireland michael D Higgins is 74 and he's doing ok. The more politically correct \textbf{old} people make excellent leaders.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Bill couldnt be more wrong about millenials in every single wayelders and their \textbf{old} ways are having a bad influence on millenials in general, once their \textbf{old} ways are gone the millenials will re-unite and change the world forever 3000 years of injustice, selfishness and suffering will be ending and with it will come our rise to tyype 1 civilization; the awakening of mankindof this im more than certain\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}why not? best trolling ever, then you put Never Gonna Give You Up by Rick Astley in the back :D\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}your point?im not actually a "member" of the so-alled "information generation", im a person of power, rationality and justice, a "man of the people" as you could sayas such, i dont recognize stupid \textbf{old} and outdated ways of thinking that uses highly inefficient and obselete methods as anything "clever" and "sophisticated" nor do i find any of it worthy of "doing the morale" to younger generationsif you were any educated and informed yourself as you seem to imply, you would know that theres no such thing as information in our current world order, hahahawell thats all :)\normalsize   & \cellcolor{green!5}Banana, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}no big deal, im actually an entrepreneur alreadyno im not talking shit, im dead serious\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}heh, you nervous? im not :)\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}mhmmm im sure it is\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}im sure of it, you done with your ass-stockpile?\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}only if you wanna go all the way LOL\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}good for you then :)\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small And then a newer generation will disrespect yours when you get \textbf{old}. So fuck you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small +Marshall \textbf{Banana} Look up a man named Barry Seal.\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}whoever made that freewebs site sure is a big fan of the misguided concept of "freedom and liberty"\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}so sad to see people actually ready to kill for their delusions of "freedom"guess what, you cant have actual freedom because then it would hurt someone else'sthe only freedom you have is your privilegesmake me ~\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}i think you really misunderstand external concepts hahayou would rather die than live in a peaceful world where justice is dominant and corruption is ruthlessly prosecuted and executed and where people have come together under the banner of science and humanism rather than suffering and war?really?\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}i hope you DO realize theres a difference between authority and tyrannya man that grants outstanding "freedom of life" to the people while making sure order and laws dominates everyone's lives is no tyrant, he becomes the face of justice and thus the idea of authoritarianismif i was talking about totalitarianism THEN i would agree with you but im probably as disgusted by such an idea as you arepeople should be allowed to choose what life they want to live however justice and order should never be neglected otherwise you only end up with a broken unity, war and corruption which, all mixed together, breeds extreme hatredpeople need to be kept in check and they need to be guided and looked after, they only need not to be told how to build their future\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/140 & \cellcolor{green!5}0.714 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}power only corrupts the people who cant hold it which pretty much includes the overwhelming majority of the people on earth (including the so-called "leaders")to hold absolute power you need to dedicate your entire existence to the cause or it will corrupt you and kill you from the insidepowerful leaders are very rare, i estimate only one of such individual awakens every 300 years cycles on averagethese powerful leaders that were recorded in history are legend (many historical figures are what i call "false leaders")this, i came to understand while many still dont\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}fine then, since you seem to see any form of regulation, law and civilization as oppressionhow will you blow my brains out if i outsmart you and blows yours out first?if a man even ascends to such a degree that he becomes the figure of the entire earth's civilization and the driving factor behind human compassion, he will outsmart and outmanoeuver everyone and anyone in everything everywherebrawns cant defeat superior intellect, im just sayingthe man that becomes what i describe can only be the most intelligent human to yet live\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}what, bullets? hahawell for one, i think you watched too much Hunger Gamesi wont go over to someone and attack him over something so stupid, im no murderer and im also no psychopath\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}and thus what separates me from the rest of the likes of me is that i understand provocation and i know it would be foolish and hypocritical of me to take actions against mere words, especially considering the case im makingin other words, my understanding of such a simplistic and narrow-minded situation dictated by shows of cojones (force) is what makes me way above average in terms of intelligenceand i say that with no narssissism and no sarcasm at all :)\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small \@xGoodOldSmurfehx It's the people who are above average intelligence but not quite genius level that make all the trouble in the world. A little bit of intelligence can be more dangerous than a lot of stupidity, believe it or not. You can look at any dictator, they're always smarter than the average bear. Look at Hitler, textbook example. Just smart enough to outsmart himself, in the end, because he made the classic mistake all smart people are prone to: He forgot that other people could disagree with him and still be intelligent. Sounds like your problem too. You know, I'd bet more than half of what you classify as your own intelligence is actually \textbf{nothing} more than intellectual vanity. Big difference between the two.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}as far as im concerned im not one of these people then because im causing absolutely no trouble whatsoever, im actually dedicated to solving problems and helping people out :)you cant really deny someone's intelligence when the person: creates a brand new system on its own (let alone a unique one that surpasses anything previously known), understands how the core of the universe works despite not having qualification in physics, understands the "4 aspects of life" and at last but not least is dedicated to the humanitarian cause and tirelessly fighting for a better tomorrow against overwhelming oddsthat, my friend, is no mere vanity\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small \@xGoodOldSmurfehx Your self-importance is like a choking, blinding fog. I didn't actually read much of what you wrote, it's starting to get a bit thick in here for my tastes. Why talk to you if you're \textbf{nothing} but empty words? LOL, I could defeat you forever by forgetting you exist.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}self-importance? are you sure you arent the selfish and self-righteous one with a narrow-minded view here?the fact i care for other people and that i would consider myself as an empty shell and slave to my own system if i were to give everything i have and everything i could have just to create a world where humans no longer suffer from the terrible and ignorant deeds of others, that alone shows that im anything but selfish do you even care for other humans? didnt think so, no libertarian hardliner (AKA retards) would ever care about other people unless it affects themjust as a reminder, my ideology of unity is winning and your obselete ideology of individualism is dying, better yet i dont even have to do anything to affect that result as its the people's wish to unite and everywhere you go in the world you will see that this wish is their dearest: to live in a peaceful world with no more pathetic wars happening, where starvation is completely annihilated and crippling poverty is no longer a thinginstead they are stuck with governments and elites that spreads fear, hatred and that mistreats them (the people)\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/202 & \cellcolor{green!5}0.495 \\  \hline
  \cellcolor{green!27}\small \@xGoodOldSmurfehx Well the key difference being that I don't impose myself on anybody else, all of my associations and all of my transactions are 100 free, fair, open, and voluntary. Am I rationally self-interested? Do I concern myself with my own affairs and my own domain? Yes. Does that make me an \textbf{imperialist}, stormtrooper, statist piece of shit like you? I really don't think so. I honestly believe there's an important distinction between us.\normalsize   & \cellcolor{green!27}Imperialist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}theres a difference between imposing and inspiringmy point is to inspire people to achieve great things and discover themselves by giving them the environment they need to do so, that is; peace, unity and justice (as to get rid of corruption[crime], discrimination and wars)the fact you compare me to a selfish \textbf{imperialist} prick shows your ignorance and arrogance towards ideologies other than your own, which frankly stinks corruption and selfishness all overquite frankly, any ideology that doesnt aims to rid the world of its hatred is completely obselete\normalsize   & \cellcolor{green!5}Banana, Imperialist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}2/93 & \cellcolor{green!5}2.151 \\  \hline
  \cellcolor{green!27}\small \@Marshall \textbf{Banana}do you really think i would communicate sensitive informations of my own things over a network (internet) thats intercepted by a dozen of intelligence agencies? let alone communicate sensitive data to a person i dont even knowget real a bit, you watched too much Hunger Games\normalsize   & \cellcolor{green!27}Banana & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small \@Marshall \textbf{Banana}riiight, feel free to go onyour keyboard-warrior skills amuse me :)\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@xGoodOldSmurfehxHow is that? Show some examples. I see millennials following the same \textbf{old} paths. As I mentioned, when we were young we, "the hippies", really thought we were gonna change the world. We did a lot, actually, there was no such thing as environmental awareness before us, but the "system" prevails in the end.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Imagine that liberals want another \textbf{old} white guy\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Great show - Churchill was \textbf{old}, didn't look great, and probably wouldn't have been supported/considered electable by today's media standards.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I just happen to think \textbf{Jerry} brown is a cunt of his own volition. mostly conjecture though. has \textbf{nothing} to do with his \textbf{age}.\normalsize   & \cellcolor{green!5}Age, Jerry, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters, Nationality - German & \cellcolor{green!5}3/24 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small In another video he slams all these \textbf{old} people still working in the Government when they should be retired,make your mind Bill which is it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small So if a Democrat is 70+ its wrong to judge his \textbf{age}, but McCain cant run cuz "he will die in office" and add in every other \textbf{old} man joke ever\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small The only thing he's wrong about is that \textbf{age} makes you wiser. I guarantee you, for every one wise 76 year \textbf{old}, there's ten \textbf{crazy} ones. As there would be with any \textbf{age} group.\normalsize   & \cellcolor{green!27}Age, Crazy, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/34 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small All my life i watched as \textbf{skinny} blonde women with flat asses were held up as the model of beauty.It's good to see big asses appreciated. Generation ass RULES!\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Right, people are ageists and an \textbf{old} guy could never run for president... Except for Bernie Sanders of course. Bernie actually has a really good shot at being elected too.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@Jeff Lebowski Ron Paul had a better chance than that \textbf{crazy} \textbf{old} jew\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Except that he's not \textbf{crazy}, no matter what you'd like to believe, and unlike Ron Paul, he actually advocates a ton of political positions that most Americans agree with, i.e. disbanding the NSA, ending the Fed, blocking the TPP, rebuilding national infrastructure, breaking up big banks that caused the financial crisis, reducing taxes on the poor and fixing the broken tax policy that allows billionaires to pay less than 20 in taxes when our country is drowning in debt, etc. Read up on his views, he's one of the few honest politicians in Washington, and he could really change our country for the better if elected.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small \@ossimjew No, no he's not. You don't know what that word means. Does he advocate for social ownership of businesses and the end of wage labor? Meaning the end of welfare, the end of capitalism, and the placement of the means of production in the hands of workers? No? Then he's not a socialist. FYI, he's a left of center social democrat who still believes in capitalism as a system but wants to improve quality of life while leaving the economy privatized (instead of socializing it like a socialist or \textbf{communist}, or nationalizing it like a fascist). He's a big proponent of the Scandinavian model, which is very much a capitalist system. So now you know.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/116 & \cellcolor{green!5}0.862 \\  \hline
  \cellcolor{green!27}\small \@Jeff Lebowski Actually he is a socialist and is very proud of it and says so openly, also the Scandinavians are socialists too. Just because some one or some \textbf{nation} is moderate doesn't mean they are not socialist\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small He's wrong here.  Considering most presidents stay in the oval office for a decade and considering how incredibly draining the job is, 78 is most certainly too \textbf{old}.    Ronald Reagan was 9 years younger than he and during his second term Reagan suffered from Dementia.  Do we really need that again?  The average Life expectancy for men is only 76.  It's just not practical to have a man that \textbf{age} run for POTUS.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small Old people tend to be more conservative. I'd say that's a pretty big mark against them. But hey, overall, I think \textbf{age} is meaningless. For every hate-filled ancient bigot, there's a stupid, drug-obsessed jock kid.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small Is \textbf{Jerry} Brown \textbf{homophobic}? Xenophobic? warmonger? wants  government to spy us? no? well then it's because he is the EXCEPTION to the rule. Your generation left us with many problems like global warming, a police state, a broken political system were only the rich can govern, and a huge fucking war with the middle east. So fuck off with your grandpa rants.\normalsize   & \cellcolor{green!5}Homophobic, Jerry & \cellcolor{green!5}Nationality - German, Sexual Identity - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Old white people are \textbf{racist} they live through civil right's. Yet cop's are shooting unarmed people. That's their kid's grown up with a badge, doing what they were taught from their elder's . They think \textbf{g\textbf{ay}} people choose that life . \textbf{old} people are hypocrite's like you .so make up your mind , because i remember you criticizing mccain for being \textbf{old} . What did you have an epiphany now that you realized your \textbf{old} ?\normalsize   & \cellcolor{green!27}Gay, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}7/76 & \cellcolor{green!27}9.211 \\  \hline
  \cellcolor{green!5}\small Judge Judy put it best "Beauty fades, \textbf{dumb} is forever"\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I don't get it.  In one of his previous "new rules" segments, he was being critical about how there are too many \textbf{old} fucks in government who never seem to lose their jobs.  I agreed with him more back then than I do now.  "\textbf{Age}" doesn't automatically imply "wisdom."  More often than not, \textbf{old} people are not so much wise as they are set in their \textbf{old}, regressive ways, which is why most vote conservative and take the longest to accept new facts and ideas.  For every one \textbf{Jerry} Brown, there are like 20 Strom Thurmonds.  And in an \textbf{age} where climate change is an increasingly serious issue, the last thing we need is men on their deathbeds making and breaking our policies.\normalsize   & \cellcolor{green!27}Age, Jerry, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!27}6/123 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Afraid I can't go along with Bill on this one on the lack of concern over \textbf{old} \textbf{age} when electing a president. A president who is intending to run for a second term has a lot less leeway in their first term, and sadly an American white male at \textbf{age} 78 only has about a 79 chance of surviving their first term and 55 chance of surviving the second, with a substantially lower chance of surviving to that \textbf{age} healthy enough to keep working one of the most stressful jobs on the planet. If they can keep going at that \textbf{age}, that's fantastic, and their experience may be a real asset, but I just can't accept those odds for a position like POTUS.I'm perfectly happy with an \textbf{elderly} supreme court justice, senator, or cabinet member. For president and commander in chief, I'd much prefer someone under 70.\normalsize   & \cellcolor{green!5}Age, Elderly, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}6/148 & \cellcolor{green!5}4.054 \\  \hline
  \cellcolor{green!27}\small Whenever I hear the name \textbf{Jerry} Brown I can't help but hear in my head the DK song, California Uber Alles; "I am Governor \textbf{Jerry} Brown, my aura smiles \& never frowns."\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Age doesn't automatically equal wisdom.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Taught me something about \textbf{ageism}, but I don,t care i proudly belong to generation ass.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Has anyone ever listened to, "California Uber Alles"? It speaks about this \textbf{Jerry} Brown character.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The booty generation is more of a pop culture trend, all started by Miley Cyrus in 2013 with her twerking bullshit. Booty worship has been around forever, particularly in the hip-hop industry, but once a white girl started doing it in the early 2010s, my GOD the world followed suit. Jennifer Lopez was KNOWN for her ass in the late 90s, yet only NOW she's relevant again after doing a song with Iggy Azalea about her 47-year \textbf{old} behind. He's blaming millennials which is typical of an \textbf{old}, out-of-touch man to do. Vince McMahon did the same shit on the Stone Cold Podcast. It's not OUR generation's fault that YOUTH is worshipped in the West. You geriatrics have been pushing 20-somethings for decades, especially in the media. Whether it's James Dean, The Beatles, \textbf{Twiggy}, Elvis Presley, etc....America has been putting over 20-somethings FOREVER and ONCE you hit a certain \textbf{age}, you're \textbf{OLD} news. SMH.\normalsize   & \cellcolor{green!27}Age, Old, Twiggy & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}5/154 & \cellcolor{green!27}3.247 \\  \hline
  \cellcolor{green!5}\small Generation Ass..... that sums it up nicely. I have to disagree with Bill on this one. \textbf{Old} people arent great for governing because they get out of touch. Lindsey Graham doesnt know how to email, but he wants to regulate my internet? They get stuck in their ways and cant adapt to the new world. Its not always true but it frequently is true. No, l think \textbf{old} people are usually clueless and thats because your competence goes on a curve from birth to death.  from moron to competent to moron. The sweet spot is like 55-60.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/97 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small I agree with the stuff he said about \textbf{old} people being wise, but come on, Bill. Having an ass fixation is not a millennial thing. We've been entranced by physical beauty since before we even evolved in to humans.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small People are beautiful at all ages.  If you want to be shallow, I will say this.  I feel that some people are more beautiful as they \textbf{age} and some are more beautiful in their youth.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Very valid points that Bill is making.  Trying to take someone down because of their advancing \textbf{age} is the lowest of low.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small That's about as "grumpy \textbf{old} man" as you've ever been, Bill.That being said, I'd like to see Brown run for president. Unfortunately, the biggest issue the young left has with Brown isn't his age; he's the \textbf{old} white guy they paint the Republican Party as being.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small Ok so here's my thought. \textbf{Age} has a factor especially when it comes to governing. I mean one of the reasons why the Middle East has failed is because a lot of the leaders are in the 60-85 \textbf{age} group. Yes wisdom has a key in this but in my opinion \textbf{elderly} should play roles such as counseling or advisers rather than Presidents. Someone who can be a part of something but from the "Small Council". Having a young leader is not a sign of disrespect but you need someone who can think like the generation that is currently active and who hold the key to the future rather than a leader who is thinking it's still 1950. If a candidate has what it takes and he's \textbf{old} then by all means. But if he's going to bring the "\textbf{old} tricks" which would've worked back in the 70's then I'd rather have another one.Yes Millennials suck big times. We had the spoils of our hard working parents. The 80's and 90's were a lot of fun. We sucked at school and we had boy bands (yes I know The Beatles could be considered as boy bands but I'm talking about...will you know what I'm talking about). So no wonder we stare at asses. But that doesn't mean that's it.Any way. Feel free to agree or disagree.\normalsize   & \cellcolor{green!27}Age, Elderly, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}5/228 & \cellcolor{green!27}2.193 \\  \hline
  \cellcolor{green!5}\small Right Bill but you can't have it both ways. The reason our \textbf{nation} is unable to value wisdom in governing is because in other sectors, like education, entertainment and ideology, they have already been convinced that wisdom=traditional and traditional=oppression and regression. You cited China's respect for the \textbf{elderly}, which is quite right, but look at other things China does not allow. I am quite sure you would not want the amount of control China has over nearly everything and everyone in it's country.\normalsize   & \cellcolor{green!5}Elderly, Nation & \cellcolor{green!5}Age - Over 65s, Nationality - General & \cellcolor{green!5}2/83 & \cellcolor{green!5}2.41 \\  \hline
  \cellcolor{green!27}\small Ageism is a thing because at a point, it's no longer their future. A president at 65 who has another 10 years left in them shouldn't be making policies that will effect America for another 50 years. They don't have to deal with their consiquences. Also, many of their views are primative and their policies based on nastalgia and not on current events, like the men in their 50s who want the Reagan era back. We need the young. We need to condition them."The young rule everything." Pop music? Beauty standards? What, because in the 70s every 80 year \textbf{old} on the block was hitting up the disco and dressing in that \textbf{dumb} ass shit they wear. We like ass. We like new music. Bill, I agree with a lot of your shit, but this is fucking stupid.\normalsize   & \cellcolor{green!27}Ageism, Dumb, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/139 & \cellcolor{green!27}2.158 \\  \hline
  \cellcolor{green!5}\small Truth Preach I feel so \textbf{old} turning away from pop culture but this made me feel better about myself. Maybe it's not that I'm \textbf{old}, maybe it is just trash. Worthless, tired, played-out trash.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Intimations of mortality, Bill? It ain't the \textbf{age}, anyway, its the wisdom alright. In any event, how does that figure with many on the SCOTUS, who are batshit \textbf{crazy} leftists?\normalsize   & \cellcolor{green!27}Age, Crazy & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I seem to remember Bill Maher gleefully joining in the chorus of those mocking John McCain's \textbf{age} in 2008\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Sadly, age-ism isn't the last acceptable prejudice.  There is still a totally open hatred of people suffering from addiction and that spills into the prejudices of \textbf{common} conversation.  And it's scary to see how there's actually a growing prejudice against men... Although admittedly these may not be universal prejudices the way Maher is saying we have against the \textbf{old}, which I'm not sure I agree with, they are still widespread and they needlessly diminish people around us.  I hope \textbf{ageism}, anti-male and anti-addict prejudices die soon at the hands of a robust, well-informed, compassionate public discussion.\normalsize   & \cellcolor{green!27}Ageism, Common, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/96 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Jerry Brown proclaimed in 2014 "Bring all the illegals to southern california!"  That is treason, not a reason to run for president... you fuck\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I looked for clips about on  McCain being bashed about his \textbf{age} by Bill, but I found , that bill Bashed John about is ideology.  and he included his \textbf{age}, but didn't say he that McCain was uncapable because of his \textbf{age}, just that he was uncapable because of his conservative thoughts at being that \textbf{age}.  We liberals or prgressives look to the future, imo,  Conservatives want to keep things the same, even 'tho, they are not. IMO\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}4/78 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Old is Gold\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Poor \textbf{old} "Liberal" white Bill, who doesn't get the beauty of women's behind, ass, butt, culo, it's \textbf{old} good and precious. Fuck you Bill!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Old people are always gonna hate young people cause they know how much power they will have when they get into their diapers. Too bad they put us into so much into debt that we won't even be able to afford diapers for them. I predict Euthanasia will become very popular soon.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Weren't libs like Bill Mahr saying John McCain was too \textbf{old} to president in 2008?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small your beautiful when your young and your wise when \textbf{old}, only we don't get this. finally we agree on something bill\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Too Many Lives Archive That's \textbf{racist}. Typical liberal bringing \textbf{race} into it.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small How is it he's already forgotten the headless beast that the Executive Branch became when an \textbf{old} and dementia-riddled Ronald Reagan (according to testimony) let the DoD engage in Iran Contra without him knowing (or being able to remember) anything about it? At 76 today, he'd be 78 in 2016. That makes him 82 at the end of his first term (if he won, and survived). I think there's just too much likelihood, at that stage of life that he's more like your great-uncle who comes over at Christmas and spends the afternoon slobbering on the couch half conscious and muttering things \textbf{nobody} understands or cares about while being leaned up against whomever it is that has the misfortune to sit next to him at any given moment. As other posters have pointed out, many of the current problems in America can be lain at the feet of \textbf{old} white dudes who are still pulling all the strings, I don't think we need advocate, at this juncture, for more of the same...\normalsize   & \cellcolor{green!5}Nobody, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/172 & \cellcolor{green!5}1.744 \\  \hline
  \cellcolor{green!27}\small Maher is aging and thus sympathetic towards \textbf{old} people surprise, surprise.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small and maher thinks he's still young 4:20 – buddy you ain't young and are getting ready to dodder, so your \textbf{senior} moment is soon coming chump\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small California isn't in debt anymore??  Bill needs to give the \textbf{bong} a rest.\normalsize   & \cellcolor{green!27}Bong & \cellcolor{green!27}Ethnicity - Aboriginal & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I'm sure Bill Maher never had a go at John McCain for being \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small jerry brown also failed to veto a law that eliminates "innocent until proven guilty" in rape cases on college campuses in california. fuck \textbf{jerry} brown, he's more of a threat to the constitution than fucking nationwide illiteracy\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small there's \textbf{nothing} more stupid than raising stupid kids\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Not a big fan of Bill Maher but that was very well done and well-said. As for the argument that \textbf{old} white men are to blame for everything, they would have done a lot more damage when they were young white men if they'd had the power to.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small A dude who spent the better part of his 40's and 50's at the Playboy Mansion is accusing Millennials of being addicted to Ass?....  This guy is all over the place.. McCain was senile ... \textbf{Jerry} Brown is the wise \textbf{old} man...  He's a 60 year \textbf{old} bachelor with a penchant for 20 somethings and is accusing the guys in their 20's of being addicted to getting tail? ....  Come on Bill, your more clever than this...\normalsize   & \cellcolor{green!5}Jerry, Old & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}3/77 & \cellcolor{green!5}3.896 \\  \hline
  \cellcolor{green!27}\small Looks like someone's getting \textbf{old}, Bill I, for one, am stoked that asses are now getting all the attention because they're just great. Way better than the heroin chic of the 90s! Work those buttocks, girls! haha\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Funny how Maher called John McCain too \textbf{old} to be President at 72 when he ran in 2008. I guess it depends on what political party you're in hey Bill.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small The average \textbf{age} of the house of representative's = 57. The average \textbf{age} of the senate = 63, The average \textbf{age} of the last 4 presidents at the time they took office = 51. Are you high Bill?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/38 & \cellcolor{green!27}7.895 \\  \hline
  \cellcolor{green!5}\small you are talking about best democratic leaders not being hyped up because \textbf{age}....and you have bernie sanders sitting right next to you...seriously get that man in office he is pure gold\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small No... I'm pretty sure people still accept \textbf{sexism}.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Bill Maher didn't say that older people are always better.He was stating that there are some people who are older who are better who because of their \textbf{age}  are being rejectedbecause of there \textbf{age}.I agree with him that Brown is the only person I can think of who I  would support  in the next Presidential election and I said this a year ago.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Generation ass? Oh come on! As if Baby Got Back and \textbf{Fat} Bottom Girls weren't songs that were hot before I was even born! \textbf{Ageism} may be one of the last excusable prejudices, but guess what, Bill! So is adultism and you demonstrated that brilliantly throughout you r monologue.You may make some good points, but you can't be a hypocrite and use a prejudice to condemn the prevalence of another.\normalsize   & \cellcolor{green!27}Ageism, Fat & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small Old people aren't respected because there are too many stupid ones around. And it is possible for young people to be wise, wiser than some \textbf{old} folks. That's were most of all the new and ground breaking ideas in science, technology, business and so forth come from. They don't come from \textbf{old} people, usually. And I say this as someone of 50. There are many young idiots around, but there certainly aren't enough \textbf{old} wise people to compensate for them. Lots of those young idiot just grow into \textbf{old} idiots.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}5/90 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Because \textbf{black} people\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Bill this country is RUN by hateful mummified corpses.  We have every right to despise the people that refuse to step aside even after they've greedily absorbed every financial boost this country had to give after WW2.  You got cheap education, cheap houses all the opportunities in between and you STILL won't give anyone an inch!  Everyone complains about the younger generation being entitled and spoiled but when people who are increasingly uninformed and outdated are working in jobs that are trying their best to leave \textbf{old} ideas in the dust during one of the worst recessions in US history it makes it real hard to see the positive aspects of "the older generations".  I usually agree with Bill on things, but this is dead wrong.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/126 & \cellcolor{green!5}0.794 \\  \hline
  \cellcolor{green!27}\small 78 IS too \textbf{old}.  Because the 78 year \textbf{old} genius can turn into the drooling child by 79.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Don't knock \textbf{old} \textbf{age}. It's not a luxury granted to everyone.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Ageism... You can't be \textbf{old} and president. You need stamina and a nimble mind. It's no more \textbf{ageism} than to expect people to have retired from sports before \textbf{age} 50.\normalsize   & \cellcolor{green!27}Age, Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}4/30 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Ha HA \textbf{hO} ho\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Bill, you hypocrite. You incessantly bashed John McCain for being too \textbf{old} in '08.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small That's because McCain is \textbf{crazy} and has horrendous ideas...Brown does things that WORK\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@JJ Thomas​​ He could have bashed him without making his \textbf{age} an issue. However, he chose to constantly imply that John McCain was too \textbf{old} to be President and could keel over at any minute.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small \@kay jay Yes and if \textbf{Jerry} Brown hires a totally incompetent VP candidate, we can worry about his \textbf{age} then. Maher was worried about the fact that if McCain had keeled over, the \textbf{woman} who thinks Jesus is coming back in our lifetime would be in charge of our nuclear weapons. That's the big difference.\normalsize   & \cellcolor{green!5}Age, Jerry, Woman & \cellcolor{green!5}Age - General, Gender - General, Nationality - German & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small \@Evan Macropulos That was not his only concern about McCain's \textbf{age} in '08.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I think it had more to do with McCain's running mate, imo.  That being said.  I know State Troopers that wanted to kill Obama when he was elected, \textbf{age} doesn't matter.  People need to start looking at the PEOPLE RUNNING!!!  And the people who are there to protect and serve.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small \@JJ ThomasMcCain certainly wasn't my choice, he IS a bit nutty, and a bit \textbf{crazy}....  But Brown is essentially worse....  some of his political views and actions are immoral and just plain wrong.  The Nazi's balanced the budget.... but look how bad they were.We would have been better off with a little nutty than the immoral, facist, remaking of America into a \textbf{Communist}/Socialist country Obama.Romney is who should have been President, and Allen West VP, and then after 8 years, Allen West President.Those two men are the most charactered and smartest men we needed at this time for this country.But instead, we get a \textbf{Communist} who 50 years ago was maginalized (Democrats used to be more conservative), a man whom the Founder specifically created the Constitution to stop from being President, a man never-mind if he was born here or not, he wasn't born to CITIZEN parents.... he was born to only ONE.There is a reason the Founders made that law.... and it's because of those like Obama.\normalsize   & \cellcolor{green!27}Communist, Crazy & \cellcolor{green!27} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/174 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small \@kay jay yeah but \textbf{Jerry} Brown didn't choose Sarah Palin as a VP candidate\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small You're wrong and liberals also insult Regan all the time for his \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@kay jay I get your point. McCain's \textbf{age} was primarily scary though for the express reason that if he got a heart-attack then nuclear launch codes would be transferred to Sarah Palin, the craziest and most dangerous person to ever come close to having high office.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@kay jay I think he meant being cynical rather than \textbf{old}, still making him a hypocrite kinda. I still don't really like Bill much because his humor is simple and delivered with no class.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@kay jay Simply because McCain knows \textbf{nothing} but WAR, WAR, WAR, not effective governance that Governor Brown is showing right now. You DON'T GET the POINT. \textbf{Age} is RELATIVE, get it?\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small \@kay jay "\textbf{Age} is relative, and individual." - Bill Maher.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@kay jay That's true, I remember. Bill Maher's getting \textbf{old}, that's why.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@kay jay Well said and isn't amazing how Ronnie Reagan became a saint?And the Pope had \textbf{nothing} to do with it.......\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@kay jay Of course he did because McCain WAS too \textbf{old}. You have to understand some people are \textbf{old} at 60 and some not until 80.  Anyway, his show is equal portions humour and satire.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small He says \textbf{age} is relative you stupid\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Well, John McCain was too \textbf{old}.  They released his health examination report, and it was as thick as a physics textbook.  Obama's was literally one page long.  And when your running mate is Sarah Palin, you had better be immortal.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@kay jay He's a comedian. He seriously wouldn't make that statement. I'd like to hear that in context of his total schtick at the moment and see what it was about. Perhaps he was even pointing out some sort of \textbf{ageist} hypocrisy of the right, by bouncing that on McCain. I'd have to hear it.\normalsize   & \cellcolor{green!27}Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small \@kay jay He didn't bash McCain for being \textbf{old}. He bashed him for being senile.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@kay jay There is a difference between being \textbf{old} and being senile. McCain is senile. Senile in his thinking and policies\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@kay jay Clearly the \textbf{nation} didn't think so. Otherwise he'd be our president. But its just like mine and your opinion man.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@kay jay and he might be cogent but that doesn't mean his ideas arent senile. Senile ideas are outdated ideas...like that \textbf{g\textbf{ay}} marriage somehow destroys the fabric of this country. It doesn't. It only allows people that love each other to be able to have healthy families.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small +kay jay John McCain was 72 years \textbf{old} (lost 2 barack obama) - \textbf{jerry} brown will be 77 years old\normalsize   & \cellcolor{green!5}Jerry, Old & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}3/20 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small +kay jay Some \textbf{old} people are senile or their brains have calcified. McCain was a young asshole and now he's an \textbf{old} asshole.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Fair criticism.  He should had bashed McCain and his party for \textbf{old} IDEAS and \textbf{old} THINKING versus \textbf{old} \textbf{age}.  Ideas if which \textbf{Jerry} Brown is the antithesis.\normalsize   & \cellcolor{green!5}Age, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}5/27 & \cellcolor{green!5}18.519 \\  \hline
  \cellcolor{green!27}\small Funny how these same people kept saying Bob Dole was too \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Young \textbf{dumb} and full of cum hahaha\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Wow!  I haven't heard Bill Maher make so much sense since around Sept. 12, 2001, when he refuted those who said that hi-jacking the planes that hit the WTC and Pentagon committed cowardly acts, and that what was cowardly was the U.S. military dropping bombs on entire populations in foreign countries.  I'm not that big on \textbf{Jerry} Brown, but being \textbf{old} can definitely be an advantage for a leader's ability to lead.\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Hey Bill the folks who run and have always run this country are all \textbf{old}, and they are corrupt greedy pieces of shit. There are \textbf{age} minimums for jobs in politics. Is that not \textbf{ageism} towards the young?\normalsize   & \cellcolor{green!5}Age, Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/38 & \cellcolor{green!5}7.895 \\  \hline
  \cellcolor{green!27}\small What a dick.  Only this asshole can start by saying \textbf{ageism} sucks and then finish by calling stereo typing young people as stupid.  He's as hypocritical and ignorant as Bill O'riley just on the other side of the fence.  Yes we should respect our \textbf{elderly}.  But, young people are not all stupid, horny underachievers, and the ass phenomenon is not new!\normalsize   & \cellcolor{green!27}Ageism, Elderly & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small Jane Fonda does NOT look 40 years \textbf{old}. WTF is Maher smoking?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I have to agree... \textbf{Jerry} Brown for President!\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You'll notice that last time we had a really \textbf{old} guy (Ronald) he fell asleep at the wheel and forgot most of what he was doing at any one time. If we do have a 70+ president we should absolutely make sure we get a VP that is younger as people in their late 70's have a habit of passing away when you least expect it, actually they pass away at that \textbf{age} and it is expected. As for generation ass you nailed it, however we must have some engineering marvels. Who else could make Minaj and Kim's oversize back of their fronts from falling down to their ankles?\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small He is Zionist and idiot; Show off type individual. He has \textbf{zero} intellectual honesty. Let us track his ties to Israel; that he justify all its crimes against humanity.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Hey I got that joke he made with crack. You see: he's not actually talking about the drug, in reality he is talking about the upper part of the behind that for some reason isn't covered by clothing and therefore creates a crack where the two buttocks meet each other above the pants. This point is further emphasized by a picture, and that's how I deducted what he was really talking about. It's what you might call a double entendre, a play on words in \textbf{witch} one phrase or word actually has two meanings \textbf{witch}, if you use your wit a little hahar!, can be executed for comedic effect.\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small \@BearWindAppleyard LOL you using the wrong version of "\textbf{witch}" while talking about homonyms. Isn't it ironic?! :)\normalsize   & \cellcolor{green!27}Witch & \cellcolor{green!27}Gender - Female age and physical appearance & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Seriously.  Fuck \textbf{Jerry} Brown.  You only like him because you are from southern California.  Because you are not in the completely ignored Northern California, whose water gets stolen and whose drought and wildfire problems are brushed under the rug.  Fuck \textbf{Jerry} Brown.From a consummate progressive who usually votes Dem.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small And let's not forget the fact that \textbf{Jerry} Brown has opened the state to Fracking, a process that uses a boat load of water and has the potential to contaminate drinking water downstream all the way to the big cities... DURING A 3+ YEAR DROUGHT.  Fuck \textbf{Jerry} Brown.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Who do you think are the execs in charge of putting out the music videos and movies obsessed with ass? \textbf{Old} white men.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Funny how things change....6 years ago it was funny to make fun of that \textbf{old} man McCain...smdh\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Grand fathers are \textbf{dumb} and their brains are usually coming to an end of their existence that's why they're not relevant to the contemporary culture where fast decision making and heavy \textbf{mental} processing is needed\normalsize   & \cellcolor{green!5}Dumb, Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small I agree with most of this but bill I gotta say, your an \textbf{o\textbf{ld} h\textbf{ag}} with a wide ass crack\normalsize   & \cellcolor{green!27}Hag, Old, Old hag & \cellcolor{green!27}Age - Over 65s, Gender - Female age and physical appearance & \cellcolor{green!27}3/20 & \cellcolor{green!27}15.0 \\  \hline
  \cellcolor{green!5}\small Youth run the CULTURE, the \textbf{old} monied elite run the COUNTRY. There is a big difference between the two.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Did he not once do a new rules about congress being too \textbf{old}?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Yes, \textbf{nothing} comes out of an ass except for a lot of shit! "Generation Shit"!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small You know most people collecting welfare are 30+ right? "This generation" believes strongly in social welfare because we grow up realizing that \textbf{old} white guys have incredible power in this country.And what does a TV show have to do with anything?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small \@Map42892 this generation, no matter what \textbf{race} subscribes to the easiest way to get free stuff.   stop \textbf{race} baiting....as my minister Farrakhan once said.. "how can you expect another man to respect you if you are constantly begging"\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@ros1tony Absolutely not \textbf{race} baiting, it's a generalization admittedly, but there's a streak of truth in it. You preach about "free stuff," but most collectors of welfare are not part of this generation (i.e. born 1985+). That doesn't mean anything.Who is begging? Do you really think you're being "discriminated" against? Are you listening to \textbf{old} guys on cable news tell you how bad you have it? And that those of us in our 20s have it oh-so-good because we get "free stuff"? I think you'd be surprised.\normalsize   & \cellcolor{green!27}Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/88 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small \@ros1tony Also Farrakhan and extremist Islam's bullshit need to disappear. Way to listen to a bigoted \textbf{nutter} who dabbles in Scientology and murders those who speak against him. The \textbf{Nation} is a fucking joke and Mohammed was a child rapist.\normalsize   & \cellcolor{green!5}Nation, Nutter & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Oke as long as you can prove that you are capable \textbf{age} is relative but above 85 most people become less capable.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Why is Gov.Brown not running? I will like to him and Gov Omarley of Maryland in the \textbf{race} against Hillary. I really think Hillary has developed a glass chin this time around and if she goes untested into the elections against pragmatic conservatives like Jeb Bush or a bridge builder like Rand Paul she is going to be floored easily.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Yawn, older generations have complained about "kids these days" for thousands of years and the world is still going fine. In fact, now it is better than ever and improving faster than ever before thanks to science, technology, declining beliefs in fairy tales, and increasingly easy access to greater knowledge. For a Democrat, Maher doesn't sound very smart here, he sounds more like a pissed off \textbf{dumb} Republican.Our youth now love luxury. They have bad manners, contempt for authority; they...gobble up their food \& tyrannize their teachers. - Socrates\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small Yeah well, a 76 year \textbf{old} president is a bad fucking idea.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Funny how he ripped McCain for being too \textbf{old} and it was even scarier because he picked Palin...and no, I am not a Republican.But I do think that Brown should run, he is a politician that knows how to do things.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small What really pisses me off about this latest generation is that people 20-30 (especially \textbf{woman}) think that being 40+ and not being 'family-carreer oriented'; but rather still enjoy having fun at the bar/nightclub or partaking in other 'youthful' activities is considered creepy. Fuck that! People 40+ who still have lots of energy for such activities should be appreciated, not ridiculed and side-lined. I have more energy than most 20 somethings I have met. Plus I am much wiser now, still have my hair-line and am in better shape than ever before! I would like to see how they fair when they reach my age; especially with all their video-game playing and pot-smoking.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small THOSE DERNED VIDEO GAMESWhy do \textbf{old} people think video games rot your brain? And you're probably creepy in the club.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Map42892 No...  i am not creepy... i like electronic music culture because like to let off steam and dance  ...and have you seen the those type of people anyways? ...the whole spectrum of \textbf{weird} ...lets say all the colours of the rainbow ...yes video games rot the brain lets not kid ourselves here.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small And yes, you're creepy. Not to me or you, but to most people. If you're 40 or over in a nightclub with mainly 20-somethings you better have some killer moves.Lol at "their video-game playing and pot-smoking." Marijuana does not affect your hair line. \textbf{Alcohol}, by contrast, does numbers more to your appearance over time.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small \@Map42892 I smoke weed everyday; but i don't drink much. I like movies ...don't watch TV ...TV i would say is worse than video games in my opinion. But how creepy is playing video games all night in your mid/late twenties or thirties or older as some gamers are ...almost on par with playing with advanced children's toys or watching cartoons! ...now how creepy is that? ...and these are the same people who judge me for being able to still party! I will give you that video games strengthen hand-eye coordination for a great career in Drone-flying no doubt.   Actually, I do not care what people think of me in the slightest at the bar; and i do have some serious moves lol ...I practice serious Kung fu on a daily basis for the past twenty years ...before that i boxed; so \textbf{nobody} touches me. Now, I also meditate and practice Qi gong daily. I am in wicked shape ...have all my hair and a nice 6-pack still.  I go to rave parties that last for days at least once a year and am always the last man standing (unless i am getting laid). Even when the twenty somethings are dropping like flies. I don't hang out in top 40 bars... never have, even when i was young; because a straight male dancing in that environment, is still to this day, liable to get in a fight over it. I am a free spirit... no one can touch me. But it is a shame what rolls society places on a person, just because of ones \textbf{age}. Yes... I do know that I am not the typical 40-something divorcee... overweight and balding with responsibilities like children and a family, child maintenance, alimony, a huge mortgage and shit; like 95 of most guys my \textbf{age} ...It will happen to you too if you are not careful8-(...I figured it out though, how I can work as a bouncer in that environment so I can still participate, meet girls and work at the same time :-)\normalsize   & \cellcolor{green!5}Age, Nobody & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}3/344 & \cellcolor{green!5}0.872 \\  \hline
  \cellcolor{green!27}\small Essentially Bill's obligatory "kids these days" rant. He's right, though; \textbf{age} doesn't automatically make you \textbf{dumb} and weak... OR smart and strong. There are plenty of intelligent, compassionate millennials and plenty of bigoted, fearful \textbf{old} people, and he should know. Saying all Asians are super smart is \textbf{racist} too, even if it's a compliment. Maybe he should get the memo that automatically hating millennials is ALSO \textbf{ageism}.PS, for all of his cries of \textbf{ageism} being "the last acceptable prejudice", he sure loves to \textbf{fat} shame Chris Christie to oblivion.\normalsize   & \cellcolor{green!27}Age, Ageism, Dumb, Fat, Old, Racist & \cellcolor{green!27}Age - General, Age - Over 65s, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}7/90 & \cellcolor{green!27}7.778 \\  \hline
  \cellcolor{green!5}\small is Bill suggesting that \textbf{old} people are always smarter than us younger folk?. typical clueless Bill.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small people who easily gets fixated on something every single human(well,maybe not some people with birth defects and accidented people) really makes them look incredibly dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Am I \textbf{crazy} or wasn't Bill saying that John McCain was too \textbf{old} in '08?  I mean, he was right... but... just sayin'\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Brown for president? In what bizarro planet? Brown is the guy who made Calif dead last in new businesses created, let out convicted criminals, imposed a property "fire fee", \& made Calif number one in property \& sales tax in the \textbf{nation}. His record speaks for itself. Now, \textbf{Jerry} wants to spend billions to build a high speed rail.\normalsize   & \cellcolor{green!27}Jerry, Nation & \cellcolor{green!27}Nationality - General, Nationality - German & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small It's not just asses. It is round, jiggly asses that were ignored except by blacks and Latinos.It was about time that nice asses be appreciated instead of being mislabeled as \textbf{fat}."I like big butts and I cannot lie"\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Has he been to Washington lately? Congress practically looks like an \textbf{old} folks home.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small For a man who spent his entire career wining and dining at the Playboy Mansion, I cannot take you serious when you dismiss sexuality in the media. If you had mocked the plastic surgery of modified asses and went with how absurd it is and continues to be I would give you props for stating so.\textbf{Jerry} Brown is a quality Governor. He's fortunate to have a super majority in the State Legislature to do what he's accomplished, and a President who authorized \$30 Billion in relief funds for his term to invest.It's a team effort.It is also true that WASPy/Jewish \textbf{old} men run the spectrum of entertainment conglomerates and have always spent considerable investment in keeping the youth distracted, while simultaneously creating neuroses through moral condemnation, thus neutering them from observing that the \textbf{nation} they live in doesn't want them to oust the \textbf{old} pricks out of Congress that continuously muck it all up.\textbf{Jerry} Brown is the exception, not the rue.\normalsize   & \cellcolor{green!5}Jerry, Nation, Old & \cellcolor{green!5}Age - Over 65s, Nationality - General, Nationality - German & \cellcolor{green!5}5/165 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small on the ass issue, \textbf{black} people have been liking nice asses. this is \textbf{nothing} new, the thing now is everybody is praising women who just happen to not be \textbf{black} and act like they are starting a trend.\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/38 & \cellcolor{green!27}7.895 \\  \hline
  \cellcolor{green!5}\small race doesn't matter. ass is ass.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small im seventeen ave volunteered for the state democratic convention saw \textbf{jerry} brown give his acceptance of the democratic nomination and absolutely fan girled when i got the opportunity to meet nancy pelosi\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small They sell it because it's what we want. There's \textbf{nothing} wrong with consumption. Many of us choose ass with our own free will lol\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I am a 15 year \textbf{old} guy, and I have to say I don't understand my generation at all. I was born in one of the last years of the millennials and most people my \textbf{age} baffle the shit out of me. We as a generation are too self-centered, egotistical, narcissistic and centered on material goods and wealth than anything else. We care little for politics, economics and news and instead are interested in what celebrity is doing what and the newest and best products to buy. I don't hate my generation, but saying I am disappointed with us would be an understatement. We are straying into an individualistic mindset and that is distressing, but I ask older generations and people of my generation to not make assumptions and generalize us because in that 'we' is included many different people. Most of the people that are seen on tv and the internet today that are of our generation doesn't reflect many of us and what we value. The normal everyday Generation Y's are not the ones you see in the media, because today 'news' is not about facts and relevant stories it is about what is 'interesting' and what will get someones attention to make them stay on the channel. Normal people just aren't interesting enough for us anymore.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/219 & \cellcolor{green!27}0.913 \\  \hline
  \cellcolor{green!5}\small Maybe Ronald Reagan scared us off of \textbf{old} fogeys for president, Bill. He was pretty terrible, and not at all wise. The \textbf{old} people at my university are the worst professors: mean, spiteful, \textbf{racist}, sexist, \textbf{dumb}, arrogant, selfish and unhelpful. So speak for yourself Bill. And talk about a straw man. Using those nitwits to represent the young? I could do the same with some truly useless oldies. Let's start with the wise \textbf{old} men of the GOP. And let's not forget who is profiting off of this stupid pop culture stuff Bill references. Yeah, \textbf{old} white guys. Not so long ago Bill was chasing every slutty big-assed chic out there.\normalsize   & \cellcolor{green!5}Dumb, Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/111 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small well,  it is said that in the past we needed to turn to \textbf{old} people to be wise,  but now \textbf{old} people need to turn to young people...  at least in technology, \textbf{old} people don't seem to get it, and young people do,,,,\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/43 & \cellcolor{green!27}6.977 \\  \hline
  \cellcolor{green!5}\small I remember when Mccayn was candidate and Bill was making \textbf{old} jokes about him... and now this. I like consistent people.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Gotta agree with him.  2014 was the year that the unhealthily \textbf{fat} female ass was mass marketed to youngsters.  What baboons we truly are.  High fructose corn syrup has apparently won the battle.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Don't blame me, Bill. I'm 23 and I voted for Ron Paul. He's 79 and I don't really give a shit about his \textbf{age}. If he dies, oh well, that's what the Vice President is for.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Same guy said McCain was too \textbf{old} to run for president\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Just because someone was good in the past does not ensure that he will not turn an idiot when \textbf{old}. There are plenty \textbf{old} people that made great contributions but when they open their mouth now you think "that can not be the same person".\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small The reason people today like ass is that most people today are \textbf{fat} and the ass is the only part of the female body which, thanks to spanks and tight jeans, still look human with all the excess blubber. We may be young but we're not into whales. It's the 50-60 year old's fault for not teaching their kids the importance of exercising.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small He do nit think the same way back then.. Maybe because he is \textbf{old} now. Hahaha..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small IDK Mahr... \textbf{Old} people get dementia.... \textbf{Old} people seems ot get confused easily... and don't like new information, or can't reconcile new information.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Your right \textbf{old} people are the new \textbf{black} and \textbf{old} \textbf{black} people are rare.\normalsize   & \cellcolor{green!5}Black, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}4/14 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small Mccain's \textbf{age} was never a problem until he chose Sarah Palin for his running mate!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Hey everyone, lets play a game. Search through youtube and find Bill Maher videos about John McCain, and take a shot every time he takes a crack at his \textbf{age}. See how long it takes for you to die\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small You do know that so much of what you call "Youth Culture" is manufactured by entertainment companies that use \textbf{Sex} to sell stuff. Justin Bieber is a designed patented product that is no more representative of my generation than Heman was representative of all of Generation X. But yeah you got me on the booty, I love me some booty.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small "\textbf{Ageism} is the last acceptable prejudice. "(Proceeds to \textbf{fat} shame the hell out of Chris Christie)\normalsize   & \cellcolor{green!5}Ageism, Fat & \cellcolor{green!5}Age - General, Physical Identity - Physical Features & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Hey bill it doesn't take a genius to have predicted that the same companies who only gave 38 hrs per week to avoid paying benifits would have slashed those hours to 28 hrs per week to avoid paying benifits so now those people who were just getting by on one job now have to work 2 jobs and not only does the job market suck but both jobs think they own u so won't schedule your work hours around each other so you end up losing both jobs because you want to stay off the welfare systems who want to know every time you take a shit or blow your nose you support obumphuccare because you take it up the \textbf{bum} if you would take your head out of your ass and support America instead of politicians who by the way want the samethings and are just fighting about who will be in power when it happens , then you would be able to see that 1 you are stopped being counted as unemployed when your benifits run out whether or not u have a job2 underemployment is actually worse then unemployed 3 being penalized for being an American who cannot afford the affordable care act healthcare but makes to much for free healthcare and then letting in millions of illegal aliens and giving them the world ie paying for school, and welfare, when they can't even speak English its no wonder the school systems are failing real Americans and yes I said real Americans as in citizens of the USA  not mexico or latin/south america or other countries like cuba or china  (I say let them have their own revolutions to overthrow their corrupt governments instead of corrupting ours more then it already is ) obama is the worst, weakest, and most corrupt president we have ever had in the oval office and I never thought I would be saying that when bush2 was in office because I thought he was and that no one would be worse but I admitt that I was wrong obumphuc is\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/349 & \cellcolor{green!27}0.287 \\  \hline
  \cellcolor{green!5}\small I hardly ever bother with the comments section anymore. But I think the reason most millennials like myself have turned away from so-called "respecting" \textbf{old} people or have become more involved with "\textbf{ageism}" is because the media... and politics... only present us with \textbf{old}, white, rich Conservative nuts with a terrible agenda as the "leaders" of the Rep party. The Republican party COULD be great... but right now its political leaders are giving the more reasonable Reps a bad name.\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small Wait, didn't BIll Maher complain about how Congressmen were too freaking \textbf{old} and need to retire already?\textbf{Jerry} Brown is a good governor because not only has he already been governor before, he also had a lot of time to reflect on his experience. However, \textbf{old} \textbf{age} has its bad side as well; \textbf{old} people can be "\textbf{old} fashion" and not understand or agree with how the your people think. Though with America the way it is, some could argue that that is a good thing. Also, the brain deteriorates with \textbf{old} \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Jerry, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!27}8/93 & \cellcolor{green!27}8.602 \\  \hline
  \cellcolor{green!5}\small It was just an example, there are sader breaking news like what CNN did, breaking news the titanic sank 102 years ago. And a small list what was breaking news:Breaking news my wife left me for a \textbf{woman}!Breaking news video game watchdogs teaches kids how to hack!Breaking news new Bigfoot DNA evidence!And the cherry on top breaking news \textbf{sex} ed is being taught at school!You know when today's news media tries so fucking hard to get the news they resort to using idiots that range from batshit \textbf{crazy} like Alex Jones to superstitious nut cases like Pat Robertson.\normalsize   & \cellcolor{green!5}Crazy, Sex, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/103 & \cellcolor{green!5}2.913 \\  \hline
  \cellcolor{green!27}\small \@crypto457 If cable news was solely about politics and whatever boring shit you passionately care about, \textbf{nobody} would watch it. It's meant to attract viewers like any other channel. People are sick of the constant right vs. left battle, so they stopped giving a shit. I don't blame them.Alex Jones is barely on TV. He has a discrete following of nutters that believe every word he says. But honestly, so does Jon Stewart. If you want to get news, don't watch cable TV (although I do like AJ English) or go on news sites with the word "truth" or "info" in the URL.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/104 & \cellcolor{green!27}0.962 \\  \hline
  \cellcolor{green!5}\small Ah true but idiots are like silverfish all its missing is conservative version of Raid! bug spray to rid ourselves of their insanity. When governments get away with shit that is downright unconstitutional yet \textbf{dumb} media outlets do a terrible job and talk about things conservatives seem to think is a threat such as condoms and haunted houses...I think that channels like Fox, history, discovery and now animal planet should die a quick painless death to stop the stupid from spreading like a disease. And as a basic idea why anyone should care, the golden dawn party. A right wing \textbf{nazi} group that got 48 seats in the senate, and the religious fundamentalists and corporations corrupting the voting system where majority votes have the same impact as using a feather to destroy a tank.\normalsize   & \cellcolor{green!5}Dumb, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/134 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Seriously? Perhaps I should have been more clear. In Greece sorry I did not mention this the golden dawn \textbf{nazi} party took over 48 seats in the senate, in America you got something that is just as backwards as the nazis the republicans and other of their ilk who do not care about the constitiuion and want a theocracy, they want to replace education with creationism and last time I checked you cannot establish and have favouritism for one religion, votes don't matter since the republicans are getting paid by exon mobile. They favour only two amendments free speech if it only effects them and fuck the other poeples opinion, and right to bear arms, they favor torture, and prefer supernatural explanations over science. They got Ted Cruz as head of NASA and science development, it's like having an Amish priest as a dentist.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/144 & \cellcolor{green!27}0.694 \\  \hline
  \cellcolor{green!5}\small Does anyone know if Maher cracked jokes about McCain being \textbf{old} when he ran against Obama?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small You could make an eight-DVD set of Bill Maher \textbf{old} jokes about McCain.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I'm surprised someone who makes fun of power so much protects \textbf{old} people. Pop culture is one thing but when it comes to governing its \textbf{old} people who run the show, poorly at that. competence and corruption know no age\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/40 & \cellcolor{green!5}7.5 \\  \hline
  \cellcolor{green!27}\small "Generation a... ,"Teenager of a country, Young \textbf{dumb} and full of c..." And why he didn't show pictures of Ruth Bader Ginsburg taking a nap during state of the union speech?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Ageism is the last acceptable prejudice in America?  God you KNOW that's a lie.  It's called \textbf{misandry} Bill and you know it.\normalsize   & \cellcolor{green!5}Ageism, Misandry & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small It's whatever one has to do with you. \textbf{Fat} people think it's "\textbf{fat} shaming," misogynists thing it's \textbf{misandry}, misandrics think it's \textbf{misogyny}, etc.\normalsize   & \cellcolor{green!27}Fat, Misandry, Misogyny & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}4/23 & \cellcolor{green!27}17.391 \\  \hline
  \cellcolor{green!5}\small \@Map42892"misogynists thing it's \textbf{misandry}"No it's \textbf{misandry} and realists think that, not just "misogynists".  Ask yourself what other groups can you simply ignore when talking about who your policies will benefit?  Have you ever heard anyone say "My policies will benefit men"?  Even in the rare case where the majority of the benefit goes to men.\normalsize   & \cellcolor{green!5}Misandry & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@Michael Price You're allowed to call out \textbf{sexism} in either direction. Men and women can be sexist. You don't have to be either a radical feminist or a neckbeard MRA. There's such thing as being reasonable and calling out bias.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@Map42892 "You're allowed to call out \textbf{sexism} in either direction."Notice that you use the term "radical" to describe the feminist, and "neckbeard" to describe the MRA.  One is a strict description of their position, the other is a description of their appearance with implications about their personality and habits.  So even when you try to say that calling out either type of \textbf{sexism} is allowable, you're misandrist.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@Michael Price I don't think either group is right. When I say "neckbeard" I'm talking about self-victimizing babies on the internet that got ditched at the prom.  I'm not a feminist or an MRA because both subcultures are awful.When did I demonize or insult men in general? I'm a man who loves men. I can't take seriously those who wrongfully think they're being oppressed. You may not have it as bad as you think you do. Empty cries of \textbf{misandry} are no better than empty cries of \textbf{misogyny}.\normalsize   & \cellcolor{green!27}Misandry, Misogyny & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small I shouldn't be able to tell you're a man with 100 accuracy just because of your leanings on \textbf{sexism}. It shows that you come from an incredible place of bias. Rape-accusing tumblr feminists are prejudiced against men, but most people don't take them seriously. Redpiller basement dwellers are prejudiced against women, but most people don't take them seriously either. The best moral path is to not be a dick to the opposite \textbf{sex}, even if you have internal struggles with it.\normalsize   & \cellcolor{green!5}Sex, Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small Governor "English as a second language"?  Really?  You're slamming him for being an \textbf{immigrant}?  Screw you.  And screw you again for making me defend that Democrat in Republicans clothing who sold out California, which BTW is STILL broke.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small What allowed \textbf{Jerry} Brown to fix California's fiscal situation is that Democrats gained a super-majority in the legislature and the useless, destructive Republicans could no longer gum up the works. Anyone in California that still votes for Republicans is a proven fool.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I am governor \textbf{Gerry} Brown, my aura smiles \& never frowns, soon I will be president. California! Uber Alles!\normalsize   & \cellcolor{green!27}Gerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small What? America is ruled by \textbf{old}, white, rich men.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Most of us democratic minded people didn't feel that way about McCain though. We definitely used his \textbf{age} against him. I think we used it because \textbf{age} effects each person differently.  Not every person is jaded by their negative experiences--that is the difference between a stodgy \textbf{old} person and someone we look up to and concider wise.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/57 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small 78 is too \textbf{old} to run for office. I rmember German president Lübke who got dementia during his second term. Good thing, the German president has no real power but more of a representative function (head of state, not head of gouvernment). Well, having an US president with dementia might not be much worse than one who almost chokes to death on a prezel, but neither is desirable.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small \@SquirrlyburtDon't give me that. I have been the victim of this prejudice too often to give you any credence. And even though there are a minority of atheist trolls, that is no more a reason to judge the group than it is to decide that all evangelicals are closet homosexuals, because a few have been outed like Ted Haggard.I had been promised an equity stake in my company if I achieved certain goals, which I greatly exceeded. The Company was owned by devout Christians. But before the year was done, and the final results were in, I happened to be at a bar one night with the President of the company who kept badgering me to come and join his church. I finally broke down and told him that I was an atheist - something I had carefully hidden for 4 years. After that, I was no longer invited to board meetings unless my expertise was absolutely required, I never got another raise (I had been getting them about every 6 months) and my division of the company was moved to a holding company and out from under the company I had been working with. The result was that at year's end, they were legally able to honor their contract with me by giving me 2 of the nearly worthless holding company. When the company I actually did the work for was sold a couple of years later with a net profit of 5 million dollars I should have gotten \$100,000, but I got almost \textbf{nothing}. At the same time, they liquidated the holding company and I got 2 of it's \$10,000 valuation  - about \$200.I never spoke about religion except one time, when, after a few beers, I wanted to stop my boss from pestering me to come to his church.A group of conservative Christians at my club/marina tried to have me kicked out when they found out through a 3rd party that I am an atheist. I don't even associate with them - i never insulted, badgered or bothered them.These are just two incidents that happened to me personally. There have been more, and several of my friends have had such experiences too. So please don't tell me about how it's our fault, or it's not really a prejudice. I made more money for my bosses in my last 3 years than any other TWO people combined, and they screwed me.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/408 & \cellcolor{green!27}0.245 \\  \hline
  \cellcolor{green!5}\small I wouldn't say that's prejudice. When you're \textbf{old}, people think you can't do certain things and you can prove them wrong. When you're atheist, people think you dont believe in God and that's enough for them to not want you. And you can't prove that wrong.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@Mike WilliamsPrejudice - to prejudge. To judge an individual or group without knowing the facts. So, if I sit through a 3 month trial of a person, and good evidence is presented of their guilt, and I sentence them to prison, that is neither prejudice, nor discrimination. But if a \textbf{black} person is convicted and jailed because they are \textbf{black}, that is. They were prejudged based on skin and not on the facts.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/74 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@Pat Doyle If a \textbf{black} person is convicted just for being \textbf{black}, that's not prejudice, that's a law that needs to change. Like immediately lol. If a person won't vote vote for an atheist, just because they are atheist, that's not prejudice, that's just a \textbf{dumb} way to vote. If you refuse to vote for an atheist because you make the connection atheism=baby killer then THATs prejudice.\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/67 & \cellcolor{green!5}4.478 \\  \hline
  \cellcolor{green!27}\small \@Mike WilliamsNo, it's prejudice, because the law does not allow that person to be convicted for that reason already. But if the jurors JUDGE him BEFORE (thus the "pre" in prejudge) they know the facts because his skin is \textbf{black}, that is the very definition of prejudice.And if you don't vote for an atheist just because they are an atheist, the means that you judged them to be unworthy regardless of the evidence. You had a pre-existing (there's that "pre" again) idea that atheists should not be trusted to hold office, and the facts do not matter. That is prejudice.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small \@Pat Doyle no, if you try to convict someone ONLY for being \textbf{black}, that is not prejudice unless you show that there was a PRE-judgment. See, there's that PRE again. You'd have to show that. They're not assuming the person's \textbf{black}. They can see it. To call it prejudice, they're would have to be a connection made between \textbf{black} and an PRE-assumed quality that the person assumes "goes with" being \textbf{black}. This may not meet the legal definition of prejudice but I'm talking about the general definition.And for the voter who doesn't vote for atheists, they also are not being prejudice unless they are PRE judging. See, there's the PRE again. They would have to make a connection between atheism and some other PRE-assumed quality in order to call this prejudice. And that's why you threw in the quality of "they are not trusted in office" i.e. Bad policy maker. In that case it WOULD be prejudice. In other words if you are making the connection atheism=bad policy maker then yep, that's prejudice. But many people DONT. there are many people who are this type of voter but if asked do you think the atheist will make for bad policy, they will say no, I just don't want to see an atheist in that office. You see, no PRE judgment. Just a dick voter. The only thing they claim to know about the candidate is that they're atheist and that is TRUE. They are atheist. No bad assumptions involved. Just a person who votes very stupidly.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}4/257 & \cellcolor{green!5}1.556 \\  \hline
  \cellcolor{green!27}\small \@Mike WilliamsSeriously Mike? Are you that stupid? They pre-judged that he was guilty based only on the fact that he was \textbf{black}. I have to assume you are a troll - \textbf{nobody} is this stupid. Goodbye.\normalsize   & \cellcolor{green!27}Black, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small \@Pat Doyle no, you don't know that they are assuming the person's guilty just because they want a conviction. They could simply want \textbf{black} people in jail, innocent or guilty. If they assumed guilt, then sure, that's prejudice.Does this surprise you? There are cops that plant evidence in order to get \textbf{black} people in jail for no other reason other than they're \textbf{black}. No guilt assumed, obviously. You don't think jurors can possess that same sentiment, the same evil desire? Many many do.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/84 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Fair enough. I personally consider Islam to me more of a political ideology than a religion. I don't think christianity today is even remotely comparable though. Besides, the biggest issue in the US now from what I can see is \textbf{race}. Anyway, each to their own, later.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Who would dislike this? Your bias has \textbf{nothing} to do with \textbf{age}. the argument is flawless? A man's \textbf{age} need not matter if his track record speaks volumes.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small Bill is not scared to say it as it is. \textbf{Ageism} sucks!\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Bill and anyone on a network TV show is/are just doing what FoX News was smart enough to do from the beginning...pander to the self entitled children of the greatest generation, whose parents' accomplishments helped make up for the mediocrity and lack of interest and respect for the United State's position as world leader shown by their neglectful children. If you have a problem with the generation that comes after you realize you made them, realize that no 15-20 yr \textbf{old} owns their own broadcast station; and lastly realize that we're you to actually engage with members of this generation you would see that just like every other there are members making a huge difference and contributing in real and important ways. Sit at home watch fox and cnn and believe the world is going to hell and keep shelling out money to protect you from roving Ebola infected \textbf{g\textbf{ay}} Latino-African street gangs with ties to atheists and al quaeda while the millennials clean up your mess and get back to the business of maintaining a \textbf{nation}.\normalsize   & \cellcolor{green!5}Gay, Nation, Old & \cellcolor{green!5}Age - Over 65s, Nationality - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}4/177 & \cellcolor{green!5}2.26 \\  \hline
  \cellcolor{green!27}\small i'm 32, from right after the generation X. I've lived through the birth of hip hop, fantastic pop music through the 80's and 90's.. I was little, but even remember the tense cold war near the end of it..  The rich got very rich in my generation. The good music is all gone, there is \textbf{nothing} more technologically that is changing the world.. we're living in a stagnant era. Obama is not the hope or the change we expected, the appearance of our country is packaged to look neat and not so shabby, but in reality is a piece of crap that you can't lend any money to because it has such bad credit. The prison and military have made fortunes for many and because of it, we can't get rid of bombs and bullets fast enough.. nor can we stop the persistent revolving of cell doors to house prisoners. Since the business part of it has us stuck in its wake. The banks are greedily, and even criminally sucking us dry, very often legally, because they count fines within their profit risk.. and \textbf{nobody} specifically is to blame and jail when a company makes group decisions.. papers get lost. Its a big fuckin joke. Corruption is higher than its ever been.. and everything  just fuckin sucks... On top of that, \textbf{racism} is alive and well.. if not thriving.. thanks to the cherry fuckin syrup of all the recent beatings of \textbf{black} citizens by law enforcement. Regard for human life is out the window... we're devolving into shit.. The generation fucking sucks ass... DONT HAVE KIDS! Its a sentence to a fucked up life... wait 10-15 years and determine if you have the time.. cause this time just fuckin sucks.\normalsize   & \cellcolor{green!27}Black, Nobody, Nothing, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/290 & \cellcolor{green!27}1.379 \\  \hline
  \cellcolor{green!5}\small Actually I would vote for \textbf{Jerry} Brown if he ran for president. Looks like such a better option than everyone else in 2016. And 78 nowadays isn't a problem anymore. William Henry Harrison was president at 80 and Ronald Reagan was president at 76/77 and is considered the best president by republicans.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small I remember Bill giving John Mc Cain grief because of his \textbf{age}????\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Hmmm I like the video all \& jokes from you until you mention Asian drivers.. Like you \& jokes much less... Because I've seen terrible driving by some blonde, redheads brunettes white punk kids and single white male/females adults in sports cars or mayb you were afraid to say Mexican drivers as those would've bombed your status more eh? Many Whites drives worst than many responsible "Asian drivers" as you so made fun of. Whatever. Peace out!! Just proving Driving is NOT based on \textbf{race}.. You just come of as a \textbf{racist} here. Whatever Jews blues.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/96 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small So \textbf{ageism} is wrong… except when you stereotype an entire younger generation and call America a "teenager of a country". Way to directly contradict your own point.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small spot on bout disrispecting \textbf{elderly} and worshipping youth.. this thought pattern is paranoia overload\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Millenials are living in the ideals of the previous generations.  You \textbf{old} fucks have yourselves to blame.  Fixing your mess is our problem, but the problem was caused by you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Bill, you were JUST complaining about the Crypt Keeper Congress. John McCain was 72, and he would have been 80 at the end of a second term, Reagan was 77 when he became President. You aren't even allowed to run unless you are over 35.Its official, Bill Maher got \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small When he talked about congress he said, "this is not about \textbf{age}. This is about congressman who suck at their jobs because their jobs are never at stake." That was more about how congressman can get elected at 50 and stay til they die at 90. It's not really an equal comparison.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Wisdom is independent of \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Let the record show that the Baby boomers inherited a post WWII America which held the most debt of any other \textbf{nation} in the history and they turned it into the most indebted \textbf{nation} in history.They outsource America's industrial base. They bankrupted Social Security so even though we millennials are paying into social security we will never see a penny from it.All the baby boomers know is to borrow and spend other people's money. They are the most spoiled and sociopathic generation in America's history. They steal from their own kids, and if that wasn't enough they borrowed trillions from foreigners and put it on the backs of their children and grandchildren to pay.They don't care about America, they don't care about their kids, all they care about is themselves. As long as they have their Viagra and Botox everyone else be damned.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/146 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small America had its chance with \textbf{Jerry} Brown in 1980 and 1992.  We went with Ronnie Reagan and Bill Clinton respectively.  America does not DESERVE \textbf{Jerry} Brown!\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I like Bill, but hold on. Didn't he criticize Mccain for being too \textbf{old}? Wasn't that his whole point? That he's too \textbf{old} to be president?Maybe I'm misremembering.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small From aiming to be Astronauts, \textbf{Doctors} and Entrepreneurs to aspiring Kim KarDashian, Paris Hilton, Nikki Minaj and Snooki. America has come long way!!\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Yeah because \textbf{nobody} wants to be \textbf{doctors} anymore. I know a huge Nicki Minaj fan in her residency. Get off your nostalgic high-horse. What does the existence of pop stars have to do with those careers?\normalsize   & \cellcolor{green!27}Nobody, doctors & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Map42892 You are just helping me to prove my point. You have NO FUCKING IDEA on how much a doctor, an engineer or an Entrepreneur can earn. You are one of the new generation Americans whose only wish is to become famous, get on TV, make a \textbf{sex} video, show oiled and shiney ASS and make as much money as possible. Trust me, I am not upset with current lack of education in USA, FUCK i don't even live in USA. I am an \textbf{Indian} (from India - which is a country FYI). I work and earn money that an American should be doing and earning. And thanks to \textbf{DUMB} ASSES US mellinials, there is a huge migration of intellectual jobs in India, Canada and China from USA.Americans can continue aspiring to be the next star of the \textbf{SEX} TAPE their parents recorded, be the potty mouth bitch with one hit wonder and be a waana-be celeb. I am happy with my nostalgic high horse as all the boob and ass you Americans will need to alter to look like an \textbf{Alien} will be done by an \textbf{Indian}, or a Chinese or an European.\normalsize   & \cellcolor{green!5}Alien, Dumb, Indian, Sex & \cellcolor{green!5}Ethnicity - Native-American, Gender - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/195 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small There is a great difference between being of advanced \textbf{age} and being \textbf{old}. \textbf{Age} is just a number, it has \textbf{nothing} to do with the biological state of your body.\normalsize   & \cellcolor{green!27}Age, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}4/30 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Funny, coming from a man that was on McCain case due to his \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I gotta raise a flag here Bill.Sheldon Adelson, John McCain, the Koch brothers and those are just three examples where \textbf{old} \textbf{age} and treachery have not just fucked the young but everyone else as well.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small This is the same guy who was probably saying that Mccain was too \textbf{old} to be president and that America needs younger people with more fresh, modern ideas like Obama in 2008. All he is doing is picking and choosing his stances to suit his politics at the given time.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small The only real reason to worry about someone being \textbf{old} is they might die in office.I mean if you are a man over the \textbf{age} of 73 you have already gone over the average.(not that younger people don't' die)however the one flaw in Maher's argument is Reagan.He got dumber as he aged.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Somebody's getting \textbf{old}..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small bill maher claims that age-ism is he last acceptable prejudice in this country then makes a \textbf{fat} joke about chris christie to great approval from the audience. not that maher doesn't have a point, because he does, but age-ism isn't the last acceptable prejudice.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Anyone else notice the \textbf{fat} shaming that is also still acceptable? Just sayin'. There are plenty more prejudices out there that are still mainstream.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small The Dimocraps ran screaming away from \textbf{Jerry} Brown when he tried to run 20+ years ago---far too outspoken and common-sensical. And that cowardice is why they are as finished as the GOP, although the latter still has some more catastrophes in store before the end.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Correct me if I am wrong, but I seem to recall Bill blasting war-horny John McCain as being too \textbf{old} to be President.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small McCain's \textbf{age} wasn't the problem, it was who would have become President if he'd died in office. The day he took Palin on board was the day he lost the election.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Although I agree that \textbf{Jerry} Brown has been, on the surface (I'm not from California) a good governor this time around and that the United States has become amazingly shallow just over the course of our lifetime, I find your inconsistency irritating. You, yourself, pointed out a few years ago that Sarah Palin was just one, then seventy one year \textbf{old} John McCain hearbeat from being President, were they to be elected, (by the way, I didn't want McCain, much less Palin to lead our country, not because of \textbf{age}, but because of, in one case fossilized and in the other "disbelief in fossils" ways of thinking). \textbf{Jerry} Brown is only a year and eight months younger than McCain.Talk about a double standard. At least try to be consistent in your criticisms. By the way, I'm about your \textbf{age} and a Progressive, politically.\normalsize   & \cellcolor{green!5}Age, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}5/143 & \cellcolor{green!5}3.497 \\  \hline
  \cellcolor{green!27}\small Hmm ... "and you're wise when you're \textbf{old}" ??Has Bill Maher noticed the high percentage of \textbf{crazy} \textbf{old} "professor emeritus" amongst climate change deniers?Cranky \textbf{old} men who think they  know everything about a research area only vaguely related to their own.\normalsize   & \cellcolor{green!27}Crazy, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/43 & \cellcolor{green!27}9.302 \\  \hline
  \cellcolor{green!5}\small I'm a fan, Bill... but I think one of the reasons you were slamming McCain was because of his \textbf{age}. Of course he only made it worse for himself by terrifying the world with his choice of VP running mate. But at a certain point, term of office does come into play.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small I think all the active hate against short men is more rampant than \textbf{ageism} and just as acceptable.  At work if I made a joke about overweight women I would be fired, but someone makes a short man joke and you'd better laugh along or you have a Napoleon complex.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small And the libs complained and complained 24/7 about Ronald Reagan being so \textbf{old} for the job, and he turned to be one of the best Presidents this country has ever had.  \textbf{Jerry} Brown?  not so much, even at his \textbf{old} \textbf{age}, he is still a lib, with tax-and-spend in his mind.  He runs out of money to run his liberal policies?  No problem, he goes to the taxpayer and asks for more.... what a guy!  but not for President, please!\normalsize   & \cellcolor{green!5}Age, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}4/80 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Esteban, I don't agree about your assessment of Reagen, but you proved Bill Maher's point about the country needing to be governed by the elderly\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Kr Chou Yes, we can agree on this point, \textbf{age} does not matter. But Reagan was one of the best Presidents in my lifetime, if that puts your underwear tight in your crack it means you're a lib, just like Maher is.  And it is certainly good that you have your own opinion.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small No Bill ,  you are 100 wrong on this issue.   The reason we hav a bunch of -- control \textbf{freak} , war mongering , greedy , selfish , soulless , incompetent , senile , dillusional , \textbf{old} , close minded jackasses for politicians ,  iz because we dont hav maximum \textbf{age} restrictions on politicians.   We hav minimum \textbf{age} requirements , because the greedy \textbf{old} plutocrats want to suppress young people and dont want any new ways of thinking into gov.  .    We need maximum \textbf{age} restrictions for politicians , just az bad az we need maximum wage restrictions for CEO's.  Get dillusional , \textbf{old} ,  close minded , control freaks out of gov. ! ! ! ! ! ! !              REBELWARRIOR  NET  and  ORG .\normalsize   & \cellcolor{green!27}Age, Freak, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/125 & \cellcolor{green!27}5.6 \\  \hline
  \cellcolor{green!5}\small Strange coming from the guy who makes fun of \textbf{old} politician all the time.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Bill Maher is a hypocrite, one minute he says the problem with our country is that \textbf{old} white guys run and have control of it, and then the next minute he says that we need an \textbf{old} "wise" white guy (\textbf{Jerry} Brown) to become the next President. \textbf{Jerry} Brown became governor of a collapsing state that is still collapsing, just a little slower. Like going from doing 90 mph heading towards the end of a cliff, to doing 80 mph… LMAO and then crying myself to sleep!\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}4/87 & \cellcolor{green!27}4.598 \\  \hline
  \cellcolor{green!5}\small apparently, it's also an acceptable prejudice to put \textbf{fat} people down. I don't like Chris Cristy, but not because of what he weighs and what he eats. These kind of commentaries are hypocritical and completely discredits Bill, as far as I'm concerned.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small I live in Florida, I am surrounded by the \textbf{elderly} its no picnic, of wisdom either. feeble \textbf{old} bats who can't drive and spend most of their time complaining.. Bill your just getting \textbf{old}...\normalsize   & \cellcolor{green!27}Elderly, Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small Ageism cuts both ways.Young people are often discriminated against with unfounded constructs like maturity and wisdom.Wisdom is a completely unsubstantiated construct.If you're \textbf{elderly} and still very competent, sure you can be of use,but the standard must apply to young people.Lastly who is selling us all this ass?It's Generation X, who's business people have no non-sexual ideology left to contribute.Millennial's intellect and financial independence have been written off by bitter politicians and cynical Freudian tycoons.Where's this revolution Generation X was supposed to bring us.It not state-side I'll tell you that much with confidence.- Sincerely a twenty-something Millennial.\normalsize   & \cellcolor{green!5}Ageism, Elderly & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/106 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Bill, it's ironic that this is your first closing monologue after an election when octogenerians practically decided the election. Young people don't turn out during midterm elections and the establishment in both parties knew that. That's why the candidates spent much of the time talking about perpetuating war in the middle east, denying climate change and dragging their feet on social issues. Hardly any of the candidates made any effort to relate to issues that matter to people in their 20s and 30s. And they were right; young people stayed home, and the older electorate sent more science-denying bigots to the senate and gave the party of "no" control of both houses of congress. This country is already completely run by the \textbf{elderly}, and that needs to change.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small John McCain is 78 but Democrats see his \textbf{age} as "\textbf{Old} and out of touch". Obama even made a campaign ad about his \textbf{old} \textbf{age} showing a young John Mccain sitting in a suit decades \textbf{old} and way out of style, wearing glasses like they wore in the 1950's along with a disco ball from the 1970's, and  claims that in 2008 John McCain "couldn't even" use a modern day computer to send email because he was "\textbf{old} and out of touch" at \textbf{age} 72.Democrats feared that since McCain was 72 , he would die in office and Sarah Palin would've been our President. Sarah Palin was said to be "A heartbeat away from the Presidency". (Suggesting that Mccain was near death at \textbf{age} 72.)BACK THEN, Bill Maher referred to the 72 year \textbf{old} Mccain as "Grandpa" on his show. NOW he refers to the 72 year \textbf{old} \textbf{Jerry} Brown as "\textbf{Jerry} Brown" on his show.\normalsize   & \cellcolor{green!5}Age, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}12/158 & \cellcolor{green!5}7.595 \\  \hline
  \cellcolor{green!27}\small Didn't Bill make constant references to McCain's \textbf{age} in 2008 ?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small But I bet Maher thought McCain was too \textbf{old} to be President\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Gonna have to disagree on this one. Congress is chalk full of \textbf{old} white men. The supreme court isn't getting younger anytime soon. And if Hillary wins in 2016 she's not exactly a spring chicken either...I think the problem with gov't now is that it's being run by \textbf{old} people who behave like immature brats\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Michael Hwang 'chock' full. Some of us \textbf{old} people understand the English language.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small LOL! LOL! LOL! I had to stop at \@3:00 to catch my breath!  No wonder batshit-\textbf{crazy} wingnuts can't stand Maher, he actually makes them look as \textbf{crazy} as they are, and ... he does it so easily!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Old people used to be highly respected for their experience and wisdom. When did people start thinking younger people are smarter?\textbf{Ageism} is a stupid word by the way. Not everything needs to be an "ism".\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small How can he not see the beauty of the female.....uh....."form"Then again america has done some \textbf{weird}.....form....related things lately - -\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small What is beautiful about a \textbf{fat} azz!?!?!?!\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small He does since he likes \textbf{black} chicks. He just doesn't understand how it became popular just now\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small It's not about \textbf{age}, it's really about enlightenment. You can be \textbf{old} and still unwise.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Jerry Brown? Is Maher joking.....California is still broke...\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Actually, the driver group with the highest rate of traffic death in America is American \textbf{Indian}, per 100,000 population (31.17). This is followed by Native Hawaiian or other Pacific Islander (13.90), then by White (12.50). African-American (12.31) and Hispanic (12.27) follow closely. Asian traffic death rate is 4.Considering there are more Asian people (around 13,000,000) than American-\textbf{Indian} people (around 3,000,000) in America, the negative stereotype of 'Asian Drivers' clearly does not apply. Especially not in 2014, on a Bill Maher show... Tut tut, Mr Maher.(p.s. 71 of drivers who died in motorcycle accidents in 2012 were male, 29 female.)\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small I partialy agree, but I have to mention that he made jokes about McCains \textbf{Age} when he ran for President.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small He did a whole routine that was just jokes about \textbf{old} people, so---. I fet it with the wisdom thing, but it is one of life's tragedies that as we aquire more experiance, knnoledge, and wisdom, the odds get higher and higher that we will get some kind of dementia. Reagan had dementia while still in office. And by the way, he was plenty \textbf{old} when elected, but not, IMHO, much wisdom, evan before the dementia.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Bill Maher has dated many thick \textbf{black} women.....He is an ass man !\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small He makes a good point but he totally contradicts himself. He is also the one who also thinks we need to get the \textbf{old} white conservative men out of office and has made some fairly offensive comments to get his point across. But, yes, wisdom does need to count for something in governance.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Young people run everything? Uh did Bill sleep through the last election cycle where \textbf{senior} citizens were 39 of the electorate?\normalsize   & \cellcolor{green!27}Senior & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small This is so true all the young people do run this country and are terrible generation doesnt help like every kid is a \textbf{brat} who sits there and listens to dubstep and say stupid things like 420blazin like wth\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Love Bill but he is absolutely wrong here. Odds say we will hit a wall mentally and physically. The older we get the higher the likelihood that happens. Playing the odds is not only natural it is smart. 80 years \textbf{old} is way too \textbf{old} to be President.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small He's so right. \textbf{Age} discrimination is the last "accepted" discriminated in the United States. There are so many in my \textbf{age} group that were let go at work because of \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/31 & \cellcolor{green!5}9.677 \\  \hline
  \cellcolor{green!27}\small Excuse me Bill, but didnt you critize John McCain for being too \textbf{old} when he ran in 2008? hypocrite!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Yes Mr Maher, it would have been nicer if you opened with a "Mea Kulpa" for all the \textbf{ageist} shit you spoke about McCain in 2009 when he was running aginst Obama.\normalsize   & \cellcolor{green!5}Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Lorde is a 40 year \textbf{old} male geologist from Colorado.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Gotta love \textbf{Jerry} Brown he saved our state\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I have no argument either way to make here but I find it supremely ironic the point Bill Maher is trying to make here.Didn't Bill Maher rail against John McCain for two years as he was running for president specifically because of how \textbf{old} he was?Also the truth people like Bill tend to ignore on this issue is an economic one.Two points here just for thought not academic. 1) The people that make products and media geared for younger audiences and profit off that product are Bill's \textbf{age}.  (I.e. record labels promoting songs about the female posterior are not run by young people. )2)  The people in Bill's generation didnt believe in saving like their depression era parents did.  They believed in spending and having a good time, borrowing money, and living larger than their means which in turn wrecked the economy twice very severely.   As a result of this, Bill's generation doesn't have alot to retire on so instead of stepping aside from the workforce they have to stay in, preventing young people from getting career oriented,  middle class jobs.So blame young people if you want but look at the whole picture first.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/199 & \cellcolor{green!27}1.005 \\  \hline
  \cellcolor{green!5}\small Bill maher is such a hypocrite. He gave McCain so much shit because he is \textbf{old}. Now he is lecturing America on \textbf{ageism}.....\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Jello for President. He's not to young and not to \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Bill should've had a sentence or two in there that coordinated the subject of this monologue with his other one about "crypt keeper" Congressmen who are too \textbf{old}.Here, he did mention that effectiveness despite \textbf{age} is on an individual basis, but it went by quickly. As for Gov Brown, it would be nice to hear from him about how much more of this political shit he has left in him. After he serves this latest term, I think he should go ahead and "start watching ESPN in his underwear".\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small In some sense, Bill Maher just repeated what my Gov. professor had mention in the beginning of this semester. The difference is that Maher takes this approach that since he is OLDER, he should shame the younger generation. Well i bet his sorry ass he wasn't thinking this thought whenever he was 20 or 30. That's where his rant just comes off as petty and a last cry of "back in my day" type of attitude towards the youth. It's not that America is "young, \textbf{dumb}, and full of cum" it's that its always portrayed itself as that. That is what sells, that's what capitalism is all about.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small I mostly agree with Maher on this, but this commentary seems of awfully hypocritical when compared to his \textbf{ageist} statements about McCain.\normalsize   & \cellcolor{green!5}Ageist & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Yeah, I also recall some of that "\textbf{ageism}" being directed at Ron Paul when he was running for president (which was one among many other smear tactics used against him). He too, I believe, was 76 at the time. And when questioned about his \textbf{age}, he challenged all of the other presidential candidates to a bike ride in the sweltering, summer heat of Texas.\normalsize   & \cellcolor{green!27}Age, Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small I would support a \textbf{Jerry} Brown presidency. . . On one condition: You have to tell me, right here, right now, who his Vice Presidential nominee would be.Remember John McCain? Remember who he picked for his running mate? That, Bill, is why so many people worry about \textbf{Jerry} Brown's age: Because when a President's "way of the flesh" comes to its logical conclusion while he is in office, his V.P. becomes the leader of the free world by default. And the last \textbf{old} guy who tried to run for POTUS picked a violent greedy two-faced anti-intellectual as his V.P. nominee.So while I would absolutely love to see \textbf{Jerry} Brown run for POTUS, unless he announces Elizabeth Warren as his V.P. nominee right off the bat, I'm out.\normalsize   & \cellcolor{green!5}Jerry, Old & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}4/129 & \cellcolor{green!5}3.101 \\  \hline
  \cellcolor{green!27}\small Bill spoke the truth. \textbf{Age} and wisdom are no longer applauded. It's mostly ridiculed and shunned.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small This sounds like sour grapes from a man who is getting "\textbf{old}".I agree that American culture is disrespectful toward older generations. Interestingly some sociologists describe the millenial generation as being more concerned with the opinions of their elders than they are with the opinions of their peers. Also, I would imagine that many millenials feel frustrated with the mess that they are inheriting from previous generations - global climate change, global recession, \textbf{imperialist} wars etc.\normalsize   & \cellcolor{green!5}Imperialist, Old & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small How retarded. This same ass clown got on McCain's ass about his \textbf{age}. Fucking hypocrite.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Leadership of the USA involves a lot of travel, speaking, late night worry etc.POTUS' \textbf{age} TREMENDOUSLY in 4 years!Not sure an older guy can demonstrate he can cope with such - convincing the public.There should DEFINITELY be a panel of "oldies" though, to ADVISE these young whippersnappers!It is really depressing to see, as I get older, that a lot of the problem is youthful foolishness and inexperience with L I F E !!!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small Generally, people who were born around the turn of the millennium or came of \textbf{age} during it (born early 1980s to recently)\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Bill, I love you, but didn't you shit all over John McCain again and again because of his \textbf{AGE}?So \textbf{age} is fine if you're a Democrat, but a liability if you're a Republican?I don't get you.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small McCain's \textbf{age} wasn't a problem until Mrs Palin became his running mate - that changed matters significantly! But I would still agree that 70+ is too old; tis a shame because I think Biden would be a fine American PotUS: shoots from the hip, has the drunken uncle persona that is familiar to most, and is generally middle of the road politically (left-of-center rather than center-left). I really hope the world doesn't get stuck with Hillary - that would be a tragedy\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small \@\textbf{R\textbf{ed}} Meth I didn't like McCain either and did not vote for him, but a double standard is a double standard. Running, doing Yoga and not having heart problems doesn't mean you're going to be good in office. Those things are so beside the point I was making that you might as well be talking about how John McMcain had a certain type of dog breed which would have made him a worse president. - -So put your shirt back on and knock it off with the condescending insults.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/89 & \cellcolor{green!5}2.247 \\  \hline
  \cellcolor{green!27}\small \@JAY MURR Why should it be someone else's responsibility? How about you tell me why thousands of dollars of credit card debt can be forgiven but not student loan debt? You don't seem to mind it in that situation you hypocrite. The laws are broken and in favor of predatory loan sharks.I'm curious how \textbf{old} you are because you probably either had your tuition paid for you, didn't go to college, or went to college when it was cheap. If you can't get a job after college then you're screwed out of 100,000 dollars, and I would LOVE to see you try to work minimum wage to pay these student loan bills with increasing interest while also paying other bills.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small I am 25, and my generation is great. We have lived through the greatest technological breakthroughs since the industrial \textbf{age}, most of us have a great work ethic and are smart enough to realize that most post secondary education is a waste of money, if you are worried about getting a job after university perhaps you should change your studies to a more relevant field. There may be idiots in our generation, but what generation doesn't. The only thing i dislike about my generation is the lack of humility displayed behind the safety of a computer screen.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small Don't listen to bill. Even though his personality is magnetic to the zombie viewers and I do watch him along with other late-night news hosts such as Colbert and Jon, I happen to disagree with him the most. Sure, he is hilarious and has a very similar personality to mine, which is why I find him so appealing and entertaining to watch and play around with his (biased) opinions, but that doesn't mean he is a perfect human being. Turn your Maher-Blinders off and actually LISTEN to the ideas he is saying- in this case, he's talking down on our generation, Gen X and Y. Yes, I am disguisted by the things that we happen to worship, such as the human buttocks and Miley Cirus, and I do happen to love Larry King, but the progressive perspective of our generation are THE most relevant ideas for the world and how it is shaped, we are the future and it is now our turn to shine. WE created Facebook, Google and letting technology and letting far-left liberal policies slowly take over the country. \textbf{Old} people like Bill are in our way, but our views are only getting more powerful by day.What I'm saying is, the younger generation right now is the future and we are as relevant as anything, no matter what anyone says.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/224 & \cellcolor{green!27}0.446 \\  \hline
  \cellcolor{green!5}\small \@ann landersIf you're using the interwebz then you're not \textbf{old}. Fact.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Fresh Nips i know people will paint me as a \textbf{racist} but i seriously think it is mostly \textbf{black} people, mexicans, and poor white people who are exerting this influence. as they become a bigger portion of the population, hispanics in particular.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Jackie Vester wtf? did you read the same statement I read? I read "I am 16 and disgusted at my generation." Nowhere in that statement was there any semblance of "class" let alone a debate. So yes, what I said was 100 justified. then you go on to assume i read/watch certain things. You're literally the worst kind of person. Put yourself on a pedestal, condescend, and then presume knowledge about the other person.Seriously, fuck you. Let me guess, 15 year \textbf{old} liberal-thinking atheist? you fags are a dime a dozen, so quit thinking you're special.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small \@Prometheus Spanky I do need to say that I agree with you on some stuff you said. I hate the public radio. I don't understand how certain groups of people (let's not say \textbf{black} or white cuz we know it exists in all races in america), enjoy songs that promote shit. Like shooting people doing drugs fucking blowing being a thug etc. And then they turn around to blame EVERYONE else that they don't have jobs education equality opportunity etc. It's just too funny to watch their parents ignore the type of things they see and read yet tell the government the teachers are not doing their job.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small When I was 16 I failed to comprehend why so many \textbf{black} women in my community were so obsessed with shaking their asses. Now, 10 years later, we have "twerking."\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Gen Y is not the only generation that deserves a harsh reprimand. It could be shared, across the board, except Gen Z because they are too young yet and they are watching our actions, collectively, and learning from us. Generation X and the boomers have a part of blame, in where we are today, as well. After WW2, when industry picked up in America and the activism of the 60's, took off, we were a \textbf{nation} of ideals, fresh ideas and innovation (we still are, of course), but we got careless. Now we have that activism, turned political correctness, dictating what is acceptable and what is not. We all share a part of the blame for that. Millennials we're dealt a bad hand, inherited many pitfalls, like an inflated economy, rampant politically correct enforced thought, that dictates what individuality is and what is cannot be, and a very uncertain future. Ultimately, maybe everyone is in that boat, now. If the millennials are guilty of anything, it is not caring enough about where society, is going. Many of them are working part time jobs (multiple jobs), just to work to attain a future they have no real assurance, even will exist. Carelessness and uncertainty are everywhere. What I see much of the problem, as being, is people who follow this societal trend of political correctness, without questioning where it is leading our collective futures and people who have a "generational" mindset and want to play the blame game, without assuming any themselves. We already have too much of that. Collectively, we are a living society of responsibility shirkers (generally speaking here). Maybe this is going to be our demise, as a society, one can only hope not.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/286 & \cellcolor{green!27}0.35 \\  \hline
  \cellcolor{green!5}\small Yet he became real popular when he took a rap song about butts in the 90s and translated it into \textbf{old} English...then there is Queens song \textbf{Fat} Bottomed Girls from the late 70s.This isn't new, Maher is just getting \textbf{old} and blaming the young now.\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/46 & \cellcolor{green!5}6.522 \\  \hline
  \cellcolor{green!27}\small TY SO MUCH Lily for standing up to YOUR generation with the TRUTH about YOUR generation. I have a 19 year \textbf{old} daughter, four teenaged granddaughters, too many nieces to count and I'm just getting started lol! You are VERY astute for your years, cause my younger family members are having to constantly REMIND members of their own generation to ACKNOWLEDGE my human rights. Good enough for me cause I already KNOW respect and \textbf{common} courtesy are OUT OF THE QUESTION with some so called 'Millennia's'. They DEMAND 'respect' yet they TOTALLY DISRESPECT somebody else's Granny, that's when they get 'touched up' so to speak in the only language some understand VERY well lol! BTW: That rude boy/grrlll crap went out with the \textbf{Sex} Pistols kids. Lily, your words have TRULY inspired me NOT to give up on ALL the youth of today. Peace. :~)\normalsize   & \cellcolor{green!27}Common, Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General, Social Class - Working class & \cellcolor{green!27}3/145 & \cellcolor{green!27}2.069 \\  \hline
  \cellcolor{green!5}\small \@austria giancarlo I got one for you...'I see no hope for the future of our people if they are dependent on the frivolous youth of today, for certainly all youth are reckless beyond words. When I was a boy, we were taught to be discrete and respectful of elders, but the present youth are exceedingly wise and impatient of restraint.' Guess who said that? Hesiod...over 2500 years ago.The only thing that has changed is the year in which \textbf{old} people say the same shit about young people.Signed,A 44 year \textbf{old} that retained a youthful outlook on life.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/101 & \cellcolor{green!5}1.98 \\  \hline
  \cellcolor{green!27}\small \@Azure Hughes Lauding past generations is typical \textbf{ageism}. This notion that younger generations, "owe it" (excuse the pseudo intellectualism, personally I find it more of an emphasis on cynicism), to the last generation to respect everything they did or didn't do, carry on the mantra, without question, and be responsible, regardless of the bullshit they were left with, is just more failure to assume responsibility, by the prior generation.It was the boomers who watched a surplus economy, a booming western GDP industrial economy (not an economy that relied, completely, on consumerism to stay afloat, like we have now), a gold-backed dollar, slip away. While they promoted "free love" (excuse me again) and peace, sitting passively by, watching, as bureaucratic assholes slowly, but surely, undermined everything that gave America real prominence in the world. And they didn't have to rack up 100k in debt, in the false hope that opportunity and prosperity was on the other side of higher education. All the while selling Generation Y and Z's future, down the river, on a ship called Free Trade. And now, we are decrying carbon emissions, telling this generation they need to "Be responsible", while the baby boomers wasted, like there was no tomorrow. And maybe now there really is, "no tomorrow". You can't help that kind of ignorance.Generation X, Y and Z now get to engage a daily struggle to hold onto jobs, they aren't guaranteed to have, in 5 or 10 years. While the baby boomers will get the full circle return of not championing the benefits, they were given, when the pension fund runs out in a few years because more boomers will be retiring, while fewer will be paying back into the fund. That is, unless the global economy goes, belly up, when the dollar (the world reserve currency), finally is declared worthless because it is being over printed.All this bullshit because of a failure to take responsibility. We should stop beating the dead horse, of telling the youth to be more responsible and get their priorities straight, and face the facts for what they are.Fuck it, I haven't even touched on wars and international disasters, but this rant has been long-winded enough.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/369 & \cellcolor{green!27}0.271 \\  \hline
  \cellcolor{green!5}\small Nothing wrong with the word 'cunt' it's 100 normal language in Australia. The current generation though.... \textbf{nazi} germany here we come. Twitter, facebook, privacy what?\normalsize   & \cellcolor{green!5}Nazi, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@sangun123Sure, the current generation with their new phone every 6 months and their constant consumption of \textbf{apple} bullshit bear no responsibility for whatsoever for ruining the environment.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@Bman Chu What are you basing that on? There are many criticisms that can be made of my generation, but I would not say a lacking in a sense of social justice and environmental awareness is one of them.I don't know the statistics, but I'd bet that compared to past generations millenials generally accept the reality of global warming on a wider scale. I know for a fact less of us are \textbf{dumb} enough to believe in a god, so we're already more inclined to be convinced by scientific data, something that often prevents older generations (in my experience) from believing in things like climate change. I ask this of you and everyone so quick to judge my generation; Think your criticisms through at least. I understand some level of disappointment towards people my \textbf{age}, we certainly aren' perfect, but we have greater potential, in my opinion, than any of you do at this point. Also, the more bitter you people sound the less inclined your criticisms are to actually make any change, as we young folk tend to rebel against any form of authority because we're young and think we know everything. ;PFor the most part, all I'm saying is you could give us more credit and express your expectations in a more constructive way considering the advantages we have in terms of both development and information distribution. (After all, if there's one thing we are good at, it's making fun of other people regardless of their intention or the context of their actions.)\normalsize   & \cellcolor{green!5}Age, Dumb & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/257 & \cellcolor{green!5}0.778 \\  \hline
  \cellcolor{green!27}\small \@Lily Feather I can tell you are 16 because you follow what \textbf{old} people tell you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I judge based on first hand interaction with young people i employ. they are incapable of working with older generations because they believe they do not need to pay their dues by working a position they believe is beneath them. Which is a joke because no one gets a job they have \textbf{zero} experience doing.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small If you're 16, you're not a millenial. I could be your father,  but they label me one. Boomers are \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Same here 1940's 16 year olds were lying about their \textbf{age} to serve their country now their \textbf{age} so they can get beers how far the human \textbf{race} has fallen\normalsize   & \cellcolor{green!5}Age, Race & \cellcolor{green!5}Age - General, Ethnicity - General & \cellcolor{green!5}3/30 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small nuance in political thought? Are you joking right now? SJW are taking the left with their fascist agenda and rethoric. This is not nuance, this is not conscience. Calling any adversary a \textbf{nazi} is not a healty way to promote political debate. Segregating people with safe spaces based on \textbf{race} and \textbf{gender} is not a way to create social conscience, equality. Denying the science behind \textbf{gender} and sexuality because it does not 100 fit your socially constructed view of sexuality is not rationality, it is not empiricism and it is not science. Forcing speakers not to talk on a university is not a liberal action, it is fascism in its early stages.This is the reallity on the campus right now. Being a classical liberal, for equality, free speech and individual freedom is almost a conservative position in the brave new world of the regressive left.\normalsize   & \cellcolor{green!27}Gender, Nazi, Race & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Gender - General & \cellcolor{green!27}4/146 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small I'd say you're disgusted by your \textbf{age} group, matey. You think teenagers were much better informed 50 years ago?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small people truly are oversensitive. even with \textbf{age}. Everyone having to tiptoe around everything they do apologetically. Even older people who should know better looking down on young people expecting them to be sorry for being young to strangers because these adults have a bitter perspective. No matter what someone does theyre criticized for every step not because its impossible to please everyone but because people are assholes that you dont need praise from. Every person alive now is living their life for the first time so dont believe they have all their bullshit figured out. There is a point to giving young people their chance. Their minds are expanding for intake of knowledge. And a smart kid shouldnt allow their time taken up by an awkward adult who thinks they have wisdom because theyre judgemental and overly generalizing.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/138 & \cellcolor{green!27}0.725 \\  \hline
  \cellcolor{green!5}\small Age does not always mean wise. There are plenty of \textbf{elderly} people that are just plain ignorant.\normalsize   & \cellcolor{green!5}Age, Elderly & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small As my Grandfather lived to \textbf{age} 91, and was a veteran of Normandy and the Battle of the Bulge (officer and former Shakespearian actor) ...started running over pedestrians with his car at \textbf{age} 81...I feel \textbf{age} 78 may be too \textbf{old} to control the nuclear football...and Bill has made countless Jokes about McCain's \textbf{age}...sigh...must be nice to have a comedians immunity from critical thinking.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}5/64 & \cellcolor{green!27}7.812 \\  \hline
  \cellcolor{green!5}\small California is fixed?? Hilarious. \textbf{Jerry} Brown didn't fix California, and California is still is terrible shape.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The ass was fat\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Jerry Brown is 2 years younger than John McCain, and a lot less senile and obviously in better physical health.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small You know, \textbf{Jerry} Brown did run for president. Three times: 1976, 1980, and 1992. With that kind of track record, I doubt he could win the presidency now. Not that I'm saying he shouldn't, because I actually feel his views compliment my own.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small back in 2008 Bill Maher made fun of McCain for being 69 years \textbf{old} and wanting to become a president.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Love this argument about actuarial fitness for office... so I guess that means you really shouldn't allow any men to run for office, since they have a higher risk of heart attacks, no overweight or diabetic people, and for that matter no Americans, since Europeans and Japanese live about a decade longer... another wise \textbf{old} man (Mark Twain) said it best: There are lies, damned lies, and statistics!Vote for the person who will govern the best, and as was surely the case with the McCain/Palin ticket, if the guy you want as president makes an idiotic choice for vice president... disqualify him or her by voting for the other ticket!!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}\small What america needs is young fresh ideas with a conservative agenda ..Bill is an asshole for even considering a 76 year \textbf{old} left wing loon\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small You can't use "fresh" and "conservative" in the same sentence. Conservative means to stick with \textbf{old} ideas because they work well enough. For others well enough isn't good enough, so they want change. Ergo "fresh" is the opposite of conservative.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small 76 is too \textbf{old} to be prez,get a life \textbf{libtard}.\normalsize   & \cellcolor{green!5}Libtard, Old & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@excelerater Agreed. I'm pretty sure Bill was making \textbf{age} jokes about McCain during that election.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@excelerater how \textbf{old} was Regan?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@excelerater "76 is too \textbf{old} to be prez"Prove it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small 6 years under Obamas rule and this country has less jobs and \textbf{black} un employment is at the highest rate ever,you brainwashed liberals thing he can fix it and that the Right Wing is evil...I got news for you loons,both sides are only looking out for themselves !\@!\@!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small If ideas are fresh and young, they surely will not be conservative. The nature of conservative ideology prohibits this. They could, however, be right wing ideals. Though very few young people embrace the right. (For good reason.) Young people are more keen to grant equality than those of the "if it ain't broke, don't fix it" mindset.76 is too \textbf{old} for the presidency though. It isn't some bullshit "\textbf{ageism}," either. The chance of him dying before finishing his first term is high. He would be 84 at the end of his second term. If he didn't pass before then, chances are he's going to have chronic health problems than will keep him from doing his job to the best of his abilities. If he were president, I would be looking at his VP as much as I'd be looking at him.\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/142 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small \@excelerater And you are unable to think for yourself. Why don't you go finish painting your car camoflauge and attend an NRA meeting while watching NASCAR and Duck Dynasty reruns?Just like at least 90 of "conservatives" you are \textbf{nothing} but a chicken shit.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small \@Lizard Ahaz Funny thing is is half of these "conservatives" make less than \$40,000 a year and think their rich caucasian party is going to save them. They don't even understand why they support who they do, but because it's a white candidate, will support them anyway. \textbf{Blind} leading the \textbf{blind}.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small And Dick Cheney was how \textbf{old}?How \textbf{old} was Reagan?You just refuse to think before speaking don't you?You and Elizabeth Hasslebeck or Sarah Palin would make a great couple. Just think, you alone would be responsible for lowering the standardized testing criteria.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@excelerater Yeah, that's what we need; some young conservative idiot to further run our already reeling country into the ground. Conservatism as a political belief is, in itself, a defeatist way of thinking. The only way a person or \textbf{nation} grows is by learning and applying that knowledge. It's great to learn from history but conservatives want to repeat history and that NEVER works. In the U.S. there is ONLY conservatism. Neither party is interested in learning from our mistakes. The Republicans want to go back to them, (hence the fixation on making the rich richer - even though the late nineteenth and early twentieth centuries told us that making the rich richer only makes the poor poorer and SLOWS DOWN THE ECONOMY), while the Democrats want a law for every part of our daily lives. (How did that work in the U.S.S.R., or the P.R.C. or the P.R.K., to site an ongoing totalitarian regime?) Face it, our present political system; an oligarchy in all but name, is broken badly and quickly destroying the country. Both political parties are really run by a few very wealthy, very self interested business entities. In a few years, unless these entities are curtailed, we the people will be \textbf{nothing} but wage slaves (as many already are) working long hours to benefit those very few at the expense of our own desires and dreams.  One possible answer is true Libertarianism, the way Robert Heinlein described it, before the conservatives latched onto it and made it much like the present oligarchical system. Heinlein described Libertarianism as a system where minimal constraint was put on the individual while the corporate structure was firmly regulated, (oversimplified but basically what he was saying, I think). What that means is: Let the individual be free to think and create and make sure that no one who is rich can stifle that freedom, by statute or by stealing. From the mind of the individual comes the greatest of ideas: The Declaration of Independence, the telephone, the computer, the airplane, the automobile. The list is endless. I believe that if this country is going to remain at the forefront of human freedom, the only way t o do it is to throw off the oncoming tyranny before it clamps down on us all. We do that by finding the independent thinkers and electing them DESPITE the constant bombardment of lies by a media, again, run by those few very rich and very self interested entities... ©Caelroigh Blunt 2014\normalsize   & \cellcolor{green!27}Nation, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/417 & \cellcolor{green!27}0.48 \\  \hline
  \cellcolor{green!5}\small I'm not sure how I feel about a 76 year-old president. We \textbf{age} at a different pace, so I don't think his \textbf{age} should automatically disqualify him. However, I would pay attention to who his VP is. All of that being said, someone who would want to see a conservative agenda pushed and uses a picture of money as his profile picture seems absolutely appropriate. Using words like libtards does not promote intelligence. However, it can cause people to question what's lacking.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@timetravelr28 \@excelerater Reagan was a month short of his seventieth birthday when he was sworn in, in 1981. He was just short of 78 when Bush the \textbf{elder} was sworn in, in 1989.\normalsize   & \cellcolor{green!27}Elder & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small You fucking bigot, the whole point is people like you assume that no one over a certain \textbf{age} is capable of having a "young fresh" idea! Why do you think Ron Paul's biggest supporters in 2012 were young people?!?!? FFS\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I love bill maher, but he himself embraced \textbf{ageism} against John McCain(At the time 72yrs \textbf{old}) in 2008 election...I am sorry but when someone aged 77 runs for office, the \textbf{age} becomes a factor.\normalsize   & \cellcolor{green!27}Age, Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small I fully agree, however, we once had a president who was a tad on the \textbf{old} side, and that one \textbf{old} man pretty much ruined it for every other \textbf{old} person in America. At the same time there was one \textbf{old} prime minister in England and she ruined it for every \textbf{old} person in that country and together they made fools of \textbf{old} people everywhere. I assume all the \textbf{old} people know who I'm talking about.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}7/76 & \cellcolor{green!5}9.211 \\  \hline
  \cellcolor{green!27}\small The fact that California's unemployment rate has so consistently and for so long been higher than the national average should be a clue that there are likely a number of forces at work in making that so. You say "people like \textbf{Jerry} Brown" have been running California into the ground for 50 years - well, that time frame includes some Governors who are \textbf{nothing} like \textbf{Jerry} Brown, such as Ronald Reagan, George Deukmejian, Pete Wilson, and Arnold Schwarzenegger - heck, even fellow Democrat Gray Davis....And when you say "it'd be Detroit if the weather wasn't nice...and not such a big tourist attraction," you realize those are REALLY big "ifs," right? I mean, the Sierra Nevadas would be like Kansas if they were flat. San Francisco would be like New York if it were on the Atlantic Ocean and bigger. The weather is nice and partly because of that, people want to visit here. Those are defining characteristics that aren't going anywhere.\normalsize   & \cellcolor{green!27}Jerry, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - German & \cellcolor{green!27}3/162 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Coming from the same guy whose 90 jokes about McCain were about his \textbf{old} \textbf{age}. It is so easy for people to tilt towards the side of argument that benefits them. funny.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Bill is right, but he has to realize he's wrong at the same time. Yes, maybe a 76 year \textbf{old} has the vigour of someone much younger, but you're also at risk of numerous diseases, and can that "fading" vigour last a whole term? Perhaps two? Also, the government is full of \textbf{old} people living in \textbf{old} times. Society is able to progress with new mindsets--with new blood.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/68 & \cellcolor{green!27}4.412 \\  \hline
  \cellcolor{green!5}\small Bill Maher is not saying all \textbf{elderly} people are wise. Hell, earlier in the show he made a crack about Pat Robertson, who is himself a crotchety \textbf{old} fart that I doubt anyone sane would label as wise. No, what he's saying is that older people like \textbf{Jerry} Brown who are incredibly intelligent and have gained so much insight through experience aren't being given a chance because of their \textbf{age}. He's also pointing out that the millennial generation (which I admit I am a part, I am sorry to say) is incredibly shallow. And it's true. We idolize people like Beyoncé and Miley Cyrus because they throw their ass out there, not to mention that every damn generic rap song is about ass and \textbf{pussy} and chicks twerking or "gettin dirty on the floor." Hell, anyone remember that song where for the first minute, it's just a guy going "ass, ass, ass, ass, ass, ass?" His point is that we idolize the young because they're young and physical and we discard older people who could potentially save this country because we view them as \textbf{old} and practically knocking on death's door. He's not saying elect Brown for being \textbf{old}, he's saying don't write him off for being \textbf{old}.\normalsize   & \cellcolor{green!5}Age, Elderly, Jerry, Old, pussy & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - Chinese, Nationality - German & \cellcolor{green!5}8/208 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small that is the thing the point about \textbf{Jerry} Brown is on point but to say that millennial are shallow because they like Beyonce and Miley Cyrus is wrong. Every generation has pop stars that do not talk about anything that are famous. As much as u want to point out songs about ass the highest selling rap artist in recent time is somebody who talks about alcoholism.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small No I totally agree with you that every generation has had this type of music, which is to say catchy but pretty shallow in that it's really not saying anything. It's just fun to listen to. However, this generation more than ever has seen the rise of Pop stars who don't play instruments, don't write their own music and really have \textbf{nothing} to say or sell other than fame. Look at Rebecca \textbf{Black}, look at Justin Bieber and Miley Cyrus. Their music is so vapid and pointless and just BAD. Even most rap is like that, and the reason why artists like Eminem are so sacred is because they actually do have something to say and that's why they get so much love and attention. I love Eminem precisely because he communicates a point in his music. But Miley Cyrus, her entire point is "look at me, i'm twerking, I have street cred."\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/153 & \cellcolor{green!5}1.307 \\  \hline
  \cellcolor{green!27}\small \@moVwatchr67But once again u are nitpicking to support ur belief. Also during this time u have the rise of artist like Kanye West, Lupe, Wale, and early on u had people like Outcast, Mos Def, and \textbf{Common}. who have plenty to talk about. In this day in \textbf{age} music has changed so much that a lot of music is so personalized that what is seen on MTV and other music station does not accurately represent the wide variety of music that this generation listen to. It does not matter if they are playing instruments or not music has evolved to a place where the sound of technology are incorporated into music.\normalsize   & \cellcolor{green!27}Age, Common & \cellcolor{green!27}Age - General, Social Class - Working class & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Kanye West may have talent but I think his personality is pretty reprehensible. The guy has got an ego like nobody's business, which may be an act for all we know, but that's another point. It seems like anyone will do anything to achieve fame these days or to keep themselves in the spotlight. \textbf{Sex} tapes, skanky outfits, public meltdowns, and most of them get reality shows out of it. Sure, singers creating images for themselves is \textbf{nothing} new, but the purpose for it has changed. Look back at Marilyn Manson in the '90s. Whether you like his music or not, you know who he is because he got everybody's attention, but he was trying to get people to think and his music reflected what he was trying to get across: free speech, individuality, etc. there was a point to it other than attention and tabloid attention.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/147 & \cellcolor{green!5}1.361 \\  \hline
  \cellcolor{green!27}\small Today it's all about selling an image that earns money and fans, it doesn't even matter whether the music is of any quality. The industry runs on whether or not people are buying the music. Rebecca \textbf{Black}, I guarentee, would not have been able to release a studio single after Friday came out of it hadn't sold. Justin Bieber, Miley Cyrus, Kesha, Rihanna, Nicki Minaj, Katy Perry, One Direction, Carly Rae Jepson, those are the people who top record charts these days and their music is as shallow as it gets. Doesn't matter though, because they sell, and they're well known. The music is almost arbitrary at this point.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small Not all modern music is garbage, unfortunately it's usually not what sells. I'd like to see another Kurt Cobain-not literally-but someone who brings back a sense of purpose to music. That's what great music has always done: made a point. Our generation is rype for material, unfortunately the biggest message in music right now is "\textbf{sex}, twerking, dance, fuck and repeat." It's like what the '80s glam rock and hairband era was: loud and flashy but ultimately empty.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small But then you realize that they're the reason your expenses increased right? those Generations -parents of the Baby Boomers and BB themselves are the LaST generation. They were spoiled and lucky for all the largess from the world but what did they do and give back???? Did they produce or give back to the world... Make life better for future generations? Hell No!!! Look at the world! See did They made the world worst?!!! Only a few cared for the future of future generations; What are the cause of our world problems? Who caused it? The deficit-- the joke of their wars  H Games-- who'll stand up for what they've done?!? Can you justify that on one generation a few decades, the system crashed/went down..? When it took Rome 209 years.. I think many Millennials are misled and spoiled and many others are suffering because of the selfish greedy \textbf{elderly} hoarding the funds and sitting on their asses sipping wines, and lobster or whatever they do while youths starve.. For a way to make a difference but forced to work \$9 min wage after paying \$90k for a degree that requires experience and connections and who does have those? fresh out of college except their own already privileged kids. Go figure!! Wake up and walk out ;-) the MatriX. Check out Stuart Wilde videos and see.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/227 & \cellcolor{green!27}0.441 \\  \hline
  \cellcolor{green!5}\small how could bill maher not understand the love for great ass's, this guy only dates \textbf{black} women so how could he not love a nice \textbf{fat} ass.\normalsize   & \cellcolor{green!5}Black, Fat & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Most of us young people have experienced \textbf{old} people with major \textbf{mental} health issues. That is why we won't vote for someone that \textbf{old}, because it is based on our personal experiences.\normalsize   & \cellcolor{green!27}Mental, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/32 & \cellcolor{green!27}9.375 \\  \hline
  \cellcolor{green!5}\small proud member of generation ass. and just because we may not be "wise" that doesn't mean we're ignorant. forgive me though, I don't want to seem agist, I'll just go wander off and pay into social security even though I probably won't be able to draw it until I'm 90 and watch as 72 year \textbf{old} conservative wack jobs deny me the right to marry and vote for people like Ted Cruz. So cry me a river.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small very true in the \textbf{age} part\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small TO ALL YOU \textbf{DUMB} ASS M.F'S YOU WILL ALL GROW \textbf{OLD} AND WHAT THEN?, ANY COUNTRY THAT SHIPS IT'S \textbf{SENIOR} CITIZENS TO \textbf{OLD} \textbf{AGE} INSTITUTIONS IS MORALLY BANKRUPT ALA THE UNITED STATES. BILL MAHER IS VERY CORRECT. IN CHINA THEY RESPECT \textbf{AGE}, KNOWLEDGE, WISDOM AND LOVE FOR \textbf{OLD} FOLKS.YOU YOUNG ASS HOLES SHOULD CHERISH YOUR \textbf{OLD} FOLKS BY PRACTICING RESPECT AND LOVE, THEN MAYBE SOMEONE IN YOUR \textbf{OLD} \textbf{AGE}, WILL WANT TO TO TAKE CARE OF YOU WITH LOVE,,TENDERNESS,AND DIGNITY. I HOPE YOU A. HOLES WILL LIVE LONG ENOUGH TO GET THERE, BILL MAHER IS RIGHT ON POINT. MR BROWN SHOULD BE CONSIDERED. AGESIM SHOULD NOT BE TOLERATED AND MUST BE ELIMINATED IN OUR \textbf{NATION}.\normalsize   & \cellcolor{green!5}Age, Dumb, Nation, Old, Senior & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}11/115 & \cellcolor{green!5}9.565 \\  \hline
  \cellcolor{green!27}\small I didn't dislike Ronald Reagan because of his \textbf{age}. I feared him because he used an astrologer to make decisions. \textbf{Age} is relative, stupidity is not.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Age doesn't always mean wise. You can see a lot in this world over a lifespan but doesn't mean everything you say is golden. While \textbf{ageism} is real, sometimes we need some younger people to bring some new ideas to the table that are more open minded. If more older people like Bernie Sanders existed then it wouldn't be an issue, but there's a lot of bitter \textbf{old} folk out there that do not deserve our respect just because they've been living on earth for 70+ years. It honestly goes both ways, I've met some wise young and \textbf{old} people, it all depends.\normalsize   & \cellcolor{green!5}Age, Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/103 & \cellcolor{green!5}3.883 \\  \hline
  \cellcolor{green!27}\small Is that the same Bill Maher who in 2008 made fun of John McCain's \textbf{age}? What a fucking hypocrite! Now Maher chastises younger generation for allegedly not giving consideration to the 78-year \textbf{old} \textbf{fruitcake} because of his \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Fruitcake, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/38 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Mahers is lying as usual. Here are the factsCalifornia's debt crisisThursday, January 9th, 2014Issue 02, Volume 18.Debt at the national, state and local levels has mushroomed in recent decades. Three California cities have sought bankruptcy protection and there are constant rumors that more may soon follow.Among the problems impacting California cities are the huge debt obligations owed to CalPERS, the state's public employees' retirement system. For example, Stockton, one of the bankrupt cities, is paying CalPERS roughly \$29 million a year, in addition to payments being made to other creditors.Despite passage of a so-called "balanced" budget last June, a report by the California Taxpayers Association placed state and local debt at an astounding \$443 billion, which amounts to \$11,600 for every man, \textbf{woman} and child in the state.Mac Taylor, the legislature's budget analyst, recently reported that California's structural budget deficit has disappeared. While this is good news, the report is based on a shaky economic recovery and temporary taxes. It also ignores California's huge future debt obligations.As we enter 2014, we should remember that all state programs are based on tax revenues generated by private-sector economic activity. Future state and local spending must be reined in so that the debt burden we have accumulated over the last decades can be addressed along with massive unfunded mandates and liabilities that threaten future prosperity. Only then can we truly begin to celebrate California's return from the brink of fiscal insolvency.By Calif. State Assemblymember Marie Waldron (R-75th District\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/254 & \cellcolor{green!5}0.394 \\  \hline
  \cellcolor{green!27}\small Bill, you idiot!  You touted \textbf{Jerry} Brown as the example of agism which would stop a man from being elected President, while Bernie Sanders, an older man who really deserves (and is considering) a run for the Presidency, is sitting at your side.  I was embarrassed to Bernie Sanders.  Did you realize who was at your side?  Am I assuming too much about Bernie being considered to be in the "older" category?\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small If Brown was a Republican he'd be \textbf{old} and out of touch...If Christie changed parties it would be enough with the \textbf{fat} jokes.  Merit doesn't mean a thing if you're on the other side.Perhaps Maher realized he's over 55....\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Generation Ass is 100 the result of \textbf{black} men taking over the music industry. And they STILL wear their pants down around their ankles. For 30 years that trend has been hanging on. Don't expect pop culture to evolve past this anytime soon. or ever. big \textbf{fat} ugly asses in our face. None of us, \textbf{black}, white, brown, male, female have evolved since the 60's. It is over. Hope the big asteroid comes soon.\normalsize   & \cellcolor{green!27}Black, Fat & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!27}3/74 & \cellcolor{green!27}4.054 \\  \hline
  \cellcolor{green!5}\small I like Bill Maher, but his Asian stereotyping was a little \textbf{racist}. Just like all races you have good drivers and bad drivers, but because of \textbf{racism} people only pay attention to bad drivers that happen to be Asian. If you see a White driver driving badly, you don't think about stereotyping that driver, but if you see a bad Asian driver, then all of sudden you start stereotyping him/her. That is called confirmation bias.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small This is not the "last acceptable prejudice in America." \textbf{Fat} prejudice is alive and well in USA!\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Old or young, what matters is competence. In short.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small "My flesh may wither with \textbf{age}, and my memory decline.  But my love for ass will never falter."- Percy Bysshe Shelley\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small How many times did Bill (and liberals in general) picked on John McCain for being too \textbf{old}?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small age is irrelevant, we dont know how healthy he is. a medical or a marathon should prove if hes suitable to hold office?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small didnt bill do a new rule about \textbf{OLD} congressmen who've hoarded congress? just saying..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Unfortunately, with \textbf{age} comes conservatism, and that's why \textbf{old} people are losing respect, they can never accept new shit.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small That's one of the parts why Idol worshipping does not work: Maher would surely not make that Point when the Oldie in question was Ronald Reagan or McCain. I stick with McCain: If you really elect someone that \textbf{old}, you should have a Sound vice president.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small This is the exact reason why a "Smarter - Been there- Know that" person was not elected as President in 2008 and 2012.   The "Generation Ass" Idiots voted Twice for the younger/stupid person, and skipped right over the Best (and older) Wisest person on the ballot.    Im sure you Smart people know who I'm talking about..  Ron Paul Of Course!   But you have to remember, Bill Maher Loved Obama, and bashed Ron Paul during both Elections.   Which just tells me that Bill is \textbf{nothing} but a Hypocrite.   I wonder what this country would look like today if these "Generation Ass's" had elected Ron Paul...   kind of makes you wonder..  But I would bet it would be a lot nicer than it is now.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small McCain and Romney were both \textbf{bonkers}. \textbf{Age} plays no part.\normalsize   & \cellcolor{green!5}Age, Bonkers & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small What's interesting is \textbf{Jerry} Brown has a little bit of a libertarian streak in him - though he still is a corporatist faux-progressive Democrat.I think most people are libertarians but just too stupid to realize it. If Obama had Ron Paul's "bat-shit \textbf{crazy}" political ideas, people would riding his dick way harder.\normalsize   & \cellcolor{green!27}Crazy, Jerry & \cellcolor{green!27}Nationality - German, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small Jerry Brown would make a good president...though I'd have to disagree with the \textbf{old} people being generally wise thing. Considering that Faux news' audience is a retirement home.\normalsize   & \cellcolor{green!5}Jerry, Old & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I mostly agree. But again Bill with the generalizations! Ffs not all millenials are idiots and not all \textbf{old} people are BerniSanders\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I'm sorry Bill, but everything you said is just untrue. Youth do not run this country. This country is run by \textbf{elderly} baby boomers who have refused to retire and give up the reigns of power.All the stuff you claim is somehow youth culture are all entertainment products that \textbf{old} men in the entertainment industry cram down the throats of the youth. The older generation is mostly stuck in the same stupid ideas they had back in the stupid ages when they were youth. \textbf{Sexism}, \textbf{racism}, \textbf{homophobia}, \textbf{xenophobia}, religious stupidity of all kinds, and backward ideas about economics and technology these are the wisdoms that the babyboomers have perpetuated long past where they should have been left behind as the millennial already have left behind. I do agree there are exceptions and I would readily vote Bernie Saunders, just because he is a true believer and I think he could make it another six years, but for the most part the \textbf{old} are still stuck in \textbf{old} bad for the world ways. Look at it in the tribal sense: the elders are respected and listened to but they are not the chiefs or warlords.\normalsize   & \cellcolor{green!5}Elderly, Homophobia, Old, Racism, Sexism, Xenophobia & \cellcolor{green!5}Age - Over 65s, Ethnicity - General, Gender - General, Nationality - General, Sexual Identity - General & \cellcolor{green!5}8/195 & \cellcolor{green!5}4.103 \\  \hline
  \cellcolor{green!27}\small ,,,says the \textbf{age} of enlightenment and enlightened,,,lolno,,, corporations don't make money giving what is wanted,,, they make it cramming what they want, down the public's throat,,,,right,,,lol.....and what 'stupidity,' will you bring to your generation,,,since you've demolished,,lol,,, all the negativity of the previous ones? lol\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@monokhem 3D printing, genetic modification, smaller and smaller high-density storage, smaller and smaller high-density batteries, getting footage from a fucking comet's surface, footage from Mars, electric cars, solar technology getting better and better......and yet, you think this is a stupid \textbf{age} because social media is a thing.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@ann landers And your evidence for this is... absolutely \textbf{nothing}.So it's just a shitty opinion used to handwave any argument a young person might throw your way. You bring this kind of pathetic crap and you think that you're part of the adult's table? Get real bud.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small I'd agree with the "\textbf{old} people are shoving this stuff down young people's throats" accusation if I didn't have the misfortune of reading YouTube comments under the videos of the millennial's stars, or hell, just the interest level as measured by video views of various videos.  You actually can't control what people like and make them like what you want them to like.  Way too simplistic and conspiratorial view of the world (something else that's easy to find on YouTube).\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small \@monokhem nah, the baby boomers ruined this country. The only \textbf{old} people that actually did good for this country were the Greatest Generation who fought WWII, launched us forward in science, brought us the New Deal and government that actually cared for the poor instead of just for corporations, etc. It's a shame their children ruined everything by voting for the likes of Reagan and Bush.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small There's no "true" freaking greatest generation. What the hell are you talking about? What does it matter? For people concerned about being the best adults, everyone seems to be confined to pretty basic and faulty argumentation (the argumentation is faulty and basic, not you dear reader). How can you measure the impact of internet and compare it with the "landing on the moon" or winning WWII? Most of people don't even know anything about that no more. Time gets by and its forgotten and lost. Let's focus and get real. You want facts? 3,035,749,340 people used the internet from the beginning of the year until June. 70  use it daily! The internet use grew 700  since 2000. Even without any scale of measurement its very difficult to disregard the importance of such present "thing" ! Let's use it in a constructive way! Stop having \textbf{dumb} arguments and insulting eachother (I am saying that the arguments are "\textbf{dumb}", not you as a person!)!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/164 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small \@bensomething I didn't say the internet was \textbf{nothing}. Just because it is less significant than the monumental things I mentioned doesn't mean I don't think it's important, but more important than our debate is this Important fact that you should understand: "free education" is not something "the internet does." Just taking information from wherever does not amount to education.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small \@Mexindian01 Babe, you're a little bit confused on your dates. While the civil rights movement certainly started with the previous generation, as we boomers came of \textbf{age} we helped carry it forward. And except for the contribution of a few radical professors the antiwar movement was entirely ours. Ultimately we stopped the forward momentum of the US war machine and changed the direction and policy of the most powerful \textbf{nation} on earth. Which is maybe a little more than playing Angry Bird and amassing a good following on Twitter.  And Reagan was elected largely by our parent's generation in their later years (the \textbf{age} of people watching FOX News today was the \textbf{age} of the people who elected Reagan then), by appealing to their fear of rapid social change and their nostalgia for simpler times. I was there, pal; I saw it play out...\normalsize   & \cellcolor{green!5}Age, Nation & \cellcolor{green!5}Age - General, Nationality - General & \cellcolor{green!5}4/144 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@Mexindian01 ROFLMFAO!!! WWII vets! Right wing sure has blown a lot of smoke up your \textbf{old} stupid asses. It is so cute how they stroke your pathetic little egos with one hand and cut your benefits with the other. No matter....your brains are so shriveled up an useless, you prefer the ego strokes to the benefits. That is all we gotta do! That is the secret to controlling the world! Make the idiots think they are special so they dont care that they are being fucked in the ass.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Be sure and remember to give up and die when you get \textbf{old}. We're all counting on it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Amen! Those \textbf{old} farts keep fucking up the world for our generation. They can keep all the power they want once they acknowledge that global-warming exists!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I disagree with you, the \textbf{old} white people are still trying to hold onto power.  Hillary 67, Warren the 1/32 Native American 65, Reid 75. And most of them are still doing the same thing as they did in their 20's. Politics. Can't seem to do anything else.  And won't leave until they are dead.  Just like government workers never retire, work until they die.  I have seen that.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small I agree with a lot of what you say. I'm almost going on sixty and most people my \textbf{age} are stuck in the past. I try to listen to new ideas, new music (anything with half a brain anyway) and look forward to new technology. Geezers my \textbf{age} bitch about shit you can't change and don't have any better solutions than when they were twenty two years \textbf{old}. I love Bill and take this rant with a grain of salt. But I don't think he's saying \textbf{old} people are synonymous with smart people. Just don't write them off as dull, slow or stupid due to their \textbf{age}. That's the lesson to take away here.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}5/114 & \cellcolor{green!27}4.386 \\  \hline
  \cellcolor{green!5}\small \@nmeunier well he did say(not sure if he did in this video) that the \textbf{dumb} people didnt just appear out of nowhere\textbf{dumb} people were always there,from the very startbut that number might be increasing and basing your culture on the ass(something all humans goddamn have) doesnt make you look pretty intelligent\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small \@Alxmir23 Exactly. The things we Millenials (I was born in 94) have done are the following:-We have played a lot of video games.-We complain about things we don't understand.-Some of the older people in our generation have done some cool things, but you find that they have more in \textbf{common} with Generation X, not the twitter generation.We really may be the worst generation so far. The reason? We have access to infinite knowledge, but we don't have any experience. It makes us think we know what we're talking about, but we don't know anything. We end up being pompous, snooty, know-it-all punk kids. The worst part? So many of us are socialists when we don't understand economics.Also, there was someone in this chain that said that we will be the ones to make solar power, electric cars, etc. Bullshit. These things are already being done by generation X, and people like Elon Musk. The Millenials have literally done \textbf{NOTHING} AT ALL.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/166 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small \@Steven Edelmann PLEASE!!!! Don't buy into this bullshit! You are who you are and when you were born has \textbf{nothing} to do with it. Grouping and labeling people by generation is for morons and manipulators. Be neither! The only way anyone can convince me otherwise is by building a working time machine.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small \@Steven Edelmann Your generation isn't entirely to blame. You had parents who influenced you up to the \textbf{age} of five. Schools changed from what they were and coddled many of you. That's something you had no control over. All this political correctness garbage a lot of kids must deal with now while also posting rude, insensitive things to each other on YouTube. Kids like a certain amount of discipline but to me they're given the run of the house. I've met some young kids who have their heads on straight and others who live totally hedonistically. In the end,  it's up to each individual to fulfill their potential.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small \@Steven Edelmann just because you are lazy and \textbf{dumb} dosnt mean this generation is... this generation is on the verge of sending colonists to mars.. creating true AI, we've gotten closer to creating the higgs boson... were genetically altering diseases to fight cancer...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@monokhem your a fool for disceeditng the internet.. when the fuck has it been possible to access all the information in the world with a tiny \textbf{black} box you carry around with you...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@monokhem the moon is so uselss you fool, it was a publicity stunt to say "we won the space \textbf{race}" even though the russians were first in everything else.. we've stopped going there because it is so useless... WW2 isnt due to america, just because we got dragged in doesnt mean shit... mastering the atom led to the most devestatng bomb ever created and nearly destroyed the planet for the years to come... and the civil rights movement is due to the few brave \textbf{african} americans... way to take credit for something that we really shouldnt be porud of\normalsize   & \cellcolor{green!5}African, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small \@sangun123 The Russians weren't first in everything else. The moon isn't useless. It has countless uses and people not totally ignorant on the subject know this."WW2 isnt due to America" is without meaning.Nukes never nearly destroyed the planet. They ended WWII saving millions of lives.Only the ignorant think the civil rights movement is only due to \textbf{black} people. Americans of countless ethnicities played a roll in it, including white kids who died for the cause. Even If your vacuous ignorant assertion about the \textbf{ethnicity} of the people responsible for the civil rights movement was true it would be no reason for me to not be proud of it. I am proud of my countryman's achievements regardless of \textbf{ethnicity}. I am also proud of the Tuskegee airman.Read more history. Look less ignorant.What do you think I did to the internet?\normalsize   & \cellcolor{green!27}Black, Ethnicity & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/144 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small \@sangun123 Oxford? Ox \textbf{DUMB} more like. "your dying ignorant generation that my generation has to fix"BWAHAHAHAHA you are a generation of IDIOTS!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Tom Evans do you see your own comments? im done speaking so an idiot like you, i have said \textbf{nothing} incorrect dumbass\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@fuchusen666 Agree with everything beside the tribe comparison. Tribes did not have \textbf{elder} chiefs and warlords because back then, strength mattered more than brains. Today strength means \textbf{nothing} and military strength is not directly tied to public office.\normalsize   & \cellcolor{green!5}Elder, Nothing & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Thomas C Thomas, here's the context:fuchusen666: "This country is run by \textbf{elderly} baby boomers who have refused to retire and give up the reigns of power.All the stuff you claim is somehow youth culture are all entertainment products that \textbf{old} men in the entertainment industry cram down the throats of the youth."monokhem: "Those "stupid ages" are when Man went to the moon, won WW II mastered the atom, and had the civil rights movement. Now is the time of Facebook. That makes these the Stupider ages."NightfallGemini "This country is going down the tubes because of young people.  Obsessed with their cell phones.  Have no idea how to communicate.  Terrible work ethic."trysometruth: "I'd agree with the "\textbf{old} people are shoving this stuff down young people's throats" accusation if I didn't have the misfortune of reading YouTube comments under the videos of the millennial's stars, or hell, just the interest level as measured by video views of various videos.  You actually can't control what people like and make them like what you want them to like.  Way too simplistic and conspiratorial view of the world (something else that's easy to find on YouTube)."Mexindian01: "Nah, the baby boomers ruined this country. The only \textbf{old} people that actually did good for this country were the Greatest Generation who fought WWII, launched us forward in science, brought us the New Deal and government that actually cared for the poor instead of just for corporations, etc."trysometruth: "If you hate the Boomers so much, stop listening to our fuckin' music.  It's our music, we wrote it and sang it to one another, about us.  It's our music and you can't have it.  Enjoy Coldplay and Nickelback."Taken out of context, it sounds like I'm just raving mad about \textbf{nothing}.  Beating my chest and trying to take credit for Pet Sounds.In context, the conversation was already over the top and ridiculous.  People making sweeping generalizations about entire generations.  I wasn't even being all that serious in my statement.In other words, relax.  It's just YouTube brother.  : )\normalsize   & \cellcolor{green!27}Elderly, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}5/348 & \cellcolor{green!27}1.437 \\  \hline
  \cellcolor{green!5}\small \@fuchusen666 It seems you weren't really listening to his main point which was that American society venerates youth at the expense of the \textbf{elderly} which btw isn't the case in virtually every other society including all of Asia, the Middle east, Africa and to a lesser extent Europe. This shouldn't be about labeling one generation or another as inferior but recognizing the problem with a 78 year \textbf{old} candidate being thought of as inconceivable candidate solely because of their \textbf{age}.\normalsize   & \cellcolor{green!5}Age, Elderly, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small \@Tom Evans Oh shaddup about "the blacks", \textbf{racist}.  Phfehhhhhh.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Marilyn Newman And destroying an economy is the \textbf{black} saving it... just look at Obama.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Tom Evans  Yes, you are stupid.  The current national debt amounts to \$56,649 for every person living in the U.S.  As a percentage of GDP, we're at 103, far less than the 120 we were at during WWII, and we're still correcting from the 7-years-ago worst recession since the Great Depression. The inflation rate is so low that Social Security beneficiaries probably won't get a cost-of-living raise after this year, the CBO said. But tax revenue is up and spending has stayed pat, which is helping reduce the pool of \textbf{r\textbf{ed}} ink in the federal budget.Combined, those numbers mean the government will run a deficit of \$426 billion in fiscal year 2015, down about \$60 billion from 2014 and marking the smallest deficit since the recession of December 2007 to June 2009 torpedoed the country's numbers\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/137 & \cellcolor{green!27}1.46 \\  \hline
  \cellcolor{green!5}\small \@Enrique Godinez We may be attracted to youth and aspire to retain it but,the youth do not run this country. In fact we are sent to die by the thousands at the whim of \textbf{old}, white, men who stay at home and risk \textbf{nothing}. Religion, Wall street, and government are the three most dominate forces in this country and they are all run by \textbf{old} men- generally \textbf{old}, white,men.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}4/69 & \cellcolor{green!5}5.797 \\  \hline
  \cellcolor{green!27}\small I have to say that millennials are more accepting to the LGBTQ community and minorities, well the baby boomers generation and the WWII generation was severely \textbf{racist}, \textbf{homophobic}, and very white supremacist, for God sake the Kkk ku klux klan, Took over and  ran the police departments and cops and chefs departments then. So much division and hatered...you couldn't even drink from the same fountain has a \textbf{black} person. so meny assassinations and don't get me started with the Vietnam wars, that war should have never happened. this millennial generation is more accepting to differences and more tolerant, being \textbf{g\textbf{ay}} isn't a big deal to them. it's the older generation that throws fire and doesn't let this generation progress. This generation isn't about haterd, \textbf{racism}, and \textbf{homophobia}, the world war II and baby boomers generation are the ones who were Brain washed and indoctrinated.\normalsize   & \cellcolor{green!27}Black, Gay, Homophobia, Homophobic, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}7/144 & \cellcolor{green!27}4.861 \\  \hline
  \cellcolor{green!5}\small \@Emerson Silva In other words there's \textbf{nothing} more pathetic than an aging hipster like Maher.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Something tells me that Maher's ratings are falling, and that he's probably going to blame \textbf{ageism} for it.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small you nailed it. I did not even think about that until you said it. Whites are probably tuning out from Bill altogether, along with the \textbf{racist} Democrat party who has said repeatedly that they want \textbf{old} white men extinct.\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@TrueBag PipeRock \textbf{Nobody} has ever said that, you sound ridiculous, please do not vote.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@Too Many Livescmon,,the guy is already on a jihad,,look at those "death to \textbf{old} men," threatsyeah,, he graduated,,full fledged\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The \textbf{age} makes you better and better inside (if you have something there,of course) and worst and worst outside. I´m 45 and I feel better than ever despite my image on the mirror. One thing the years teach you is that every \textbf{age} has good and bad things. Enjoy everyone because some day life will end. But this time we live don´t teach you how to grow inside, to be a good parent, a good friend, a good lover. You only learn to use... internet and comment the videos on youtube ;-)\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/92 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small This is bullshit, give me a break, rich \textbf{old} people run the fucking country and young people have \textbf{nothing} but student debt. Look at every place with people with political power and it's a plethora of \textbf{old} people. I generally like Bill, but he's wrong on this one.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/48 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small We love ass because we are primates. The ass is the storage for \textbf{fat} and the bigger the ass the more likely the \textbf{woman} can survive food shortages, making her more attractive. It's quite funny how religious people think we are special created even though our animal heritage is so obvious.\normalsize   & \cellcolor{green!27}Fat, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small \@Kim Chem You do realise that having stored \textbf{fat} does mean you'll be more likely to survive a food shortage right? Also it can be a sign of youth and fertility, and possibly draw in \textbf{sexual} attraction from behind like the breasts do from in front.This took a couple seconds of research. Also none of this anything fucking new, people liking ass is a part of human life that is older than dirt.\normalsize   & \cellcolor{green!5}Fat, Sexual & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Nobody is saying that this particular instinct doesn't have an evolutionary explanation. If it stuck with males, then it means it served a purpose at a certain evolutionary stage and spread. But it's still just a basic instinct that serves no real purpose of survival anymore in a civilized modern society, and thusly doesn't warrant making a national meme out of it.But anyway, Bill just used that meme as an example that our culture is becoming led by instinct-driven impetuous youngsters. It's not that serious, I guess, as long the vital areas that keep the country running (government, academia, finances, etc.) are being run by wise people.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small \@Holz Name I'll point out your BS you fuck nut, by your theory the hottest girl in the room to us should be the girl with the fattest ass. So Rosie Donnell over say kim kardashian. And Furthermore your dumbass doesn't realize that your ass is not \textbf{fat} but made up of muscle. The difference is someone who has an actual \textbf{fat} ass it will look like cottage cheese, if someone has a nice ass it's toned and in shape and usually the person is physically fit or has good genetics. It makes more sense that were attracted to phsycially fit women because that's a sign that they would have good genetics to pass on to our offspring and could forage for food be a good mother.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/127 & \cellcolor{green!5}1.575 \\  \hline
  \cellcolor{green!27}\small \@Tim Clarkson "\textbf{Nobody} is saying that this particular instinct doesn't have an evolutionary explanation"  "it's way too early for me to listen to an idiot try to justify BS with his own brand of pseudoscience"Reading  comprehension 101.Also who made you the arbiter of which facets of human sexuality (attraction to certain signs of fertility or \textbf{sexual} displays) are no longer necessary? So the fact that males are attracted to the traits females have is no longer necessary? (Yes I'm baiting you) Because attraction tends to help with reproduction and that is necessary.I also love in the comment's section of a speech about \textbf{ageism}, you're being \textbf{ageist} vs young people calling them impetuous and impulse-driven, because of course all people who are young are stupid and all who are \textbf{old} are wise. That's why it's only young people hell bent on stopping \textbf{g\textbf{ay}} people from getting married, discriminating against people on the grounds of belief, skin, colour and religion and the \textbf{old} folks are just showing them up.\normalsize   & \cellcolor{green!27}Ageism, Ageist, Gay, Nobody, Old, Sexual & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters, Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}8/170 & \cellcolor{green!27}4.706 \\  \hline
  \cellcolor{green!5}\small \@Antoine VelloThe "pseudo-science" comment wasn't from me.The original commenter argued that attraction to a larger butt for males was an evolutionary advantage because "the ass is the storage for \textbf{fat} and the bigger the ass the more likely the \textbf{woman} can survive food shortages". And that doesn't serve its purpose in a modern civilized society, as no one is dying of hunger in America.I didn't call young people stupid. I just said they were more instinct-driven and impetuous, which they are. The current ass-worshipping trend is more typical of the high-testosterone younger mind that is dominating culture than the older one. But as I said, I don't care much because I don't see those memes as a threat to civilization (yet), as long as the sensitive areas are being controlled by more pragmatic and wise people (who could very well be young, for that matter).\normalsize   & \cellcolor{green!5}Fat, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}2/148 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small \@Tim Clarkson Holy sidestepping batman!Yes that reason doesn't hold up now, issue is there are other reasons why people are attracted to a larger butt. You can't throw it out because one facet of it no longer relevant."our culture is becoming led by instinct-driven impetuous youngsters" You said they are instinct-driven and impetuous not that they are more instinct-driven and impetuous, which is an unfair characterisation. \textbf{Ageist}.\normalsize   & \cellcolor{green!27}Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small \@Antoine VelloWell, they are, to varying degrees. And it's not their fault; it's biology's fault. Most of the activities that require high drive and impetus (loud parties, petty crime, hooliganism) are dominated by young males. Testosterone levels only begin to drop at \textbf{age} 30. Incidentally, so do crime rates. [LINK]  [LINK] That said, one should also evaluate young people on an individual level, as some may be more self-possessed than others. Which is what Bill is suggesting here. It would also be hypocritical from me to pretend I wouldn't have taken part or been interested in these trends if I were 20 years younger.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small \@litcguitaristIf you actually read some history and anthropology, then your statement was basically true. The problem is that with today's technology we have plenty of food available, so the big ass is not such a huge factor anymore. Andobesity is now disliked because it shows a weak character, prone to hearth decease, and other medical issues.See  [LINK] if you want an idea what was the "perfect" body of a \textbf{woman} over 10,000 years ego.\@LivingInVancouverBC Yeah. That's why we like big boobs and why breasts implants are so popular.You can't escape your biology. Of course individual beauty standards vary. Some like small, some like big. But on average we like big.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/115 & \cellcolor{green!27}0.87 \\  \hline
  \cellcolor{green!5}\small \@Clifton100It is explained by evolution. What other hypothesis can you offer why man are attracted to big asses and boobs? Why the \textbf{woman} body 100,000 to 10,000 years ego was depicted as the Venus figurines? Why are \textbf{African} and other native tribes still find big \textbf{woman} very attractive?\normalsize   & \cellcolor{green!5}African, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small \@Kim Chem you are \textbf{dumb} as shit, aren't you?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small it has also alot to do with width of \textbf{woman}'s hips, it just that \textbf{woman} with wide hips also have big butts\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@blackraider777\textbf{Woman} with wide hips have good chance to bear a child easily."In humans, unlike other animals, the hip bones are substantially different in the two sexes. The hips of human females widen during puberty"[1][1]  [LINK] \normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@iwasborntobeflyIn the eye of the beholder, yes.  But I'm not so sure about cultural.  If attraction was cultural, \textbf{g\textbf{ay}} people wouldn't exist and clearly they do.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small \@HoOGenghisB it is cultural. \textbf{black} people, no matter where we are, tend to appreciate a high round ass. other people don't get it because they have flat asses. there are things white people salivate over - blues and blond hair - because they view that as beautiful and ideal. asians like \textbf{skinny} women and pale skin. what is considered beautiful is very much part of a culture. and the \textbf{g\textbf{ay}} analogy is totally out of place. even \textbf{g\textbf{ay}} people bring cultural values they were raised with to whatever person they may regard as attractive. it is all cultural. i'm a \textbf{black} \textbf{woman}. you probably aren't \textbf{black} and so you have no idea what is important or interesting to us aesthetically. i know that culturally, darker skin, an ass (even on a small frame) is not considered the height of beauty among asians. please stop.\normalsize   & \cellcolor{green!27}Black, Gay, Skinny, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General, Physical Identity - Physical Features, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}9/144 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Why stop?  My point is that if it is cultural, then \textbf{g\textbf{ay}} people wouldn't find those of same \textbf{sex} attractive because, culturally (at least historically) it wasn't accepted.  All attraction is is a visual stimulus.. why would it be cultural up to the point of it being someone of the same \textbf{sex}?  Its still a human body.Now there can be cultural norms that people conform to, but I just don't see that being the case with attraction.  I've never felt like my cultural upbringing had any effect on who I was attracted to.  I don't see why that is seen as a contentious statement.  There is no malice behind that. I'm not sure how your examples of blacks like this and whites like that makes your point.  If anything it adds to my inherent case.  Whites perhaps are attracted to those of the same \textbf{race}.  Asians, Blacks, etc.  I've always thought attraction was innate.Perhaps I'm being naive, but I don't see what cultural values people are raised with have to do with it.  I wasn't taught this is what "we" like. Basically I don't understand how it can be argued that being \textbf{G\textbf{ay}} is innate, but everything else is cultural. I think its all inate\normalsize   & \cellcolor{green!5}Gay, Race, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}7/207 & \cellcolor{green!5}3.382 \\  \hline
  \cellcolor{green!27}\small \@HoOGenghisB just stop. you are making this more complicated than it has to be, maybe because you think you're being clever?\textbf{black} gays are raised around \textbf{black} people and have those same cultural affinities and values, FOR THE MOST PART, just like asian gays do and white gays. you either just don't comprehend or you want to be provocative. only a moron would not understand the role culture plays in everyone's lives. your preferences are not entirely innate, they are learned. there is no universal beauty or even intelligence.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small \@Timothy Flood and when did i not say \textbf{black} women do not have high round asses? i'm a \textbf{black} \textbf{woman}. i know how we are shaped. damn people.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small \@HoOGenghisB obviously you don't, even when someone from the group that admires ass is telling you it's cultural. you still refute it and run around in a \textbf{mental} maize you've created for yourself instead of just accepting that different people have different values and beliefs.i don't mind a conversation, but a silly one is just \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb, Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small \@iwasborntobeflyAn opinion doesn't count as refuting.  And why would you think that your brief comment would all of a sudden make me change mind?  If I don't accept what you originally said then I'm an idiot?  Is there something special about the fact that your opinion came from you so I should just listen and forego any critical thinking.. because you know I wouldn't want to fall into the trap of a \textbf{mental} maize I've built for myself. Lord knows, I built it, I may never get out!\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small \@Holz Name i didn't read your whole comment. but i find it bizarre that people's fascination with/love of  blue eyes and blond hair isn't scrutinized or regarded as strange or unnatural. yet when a cultural vision of beauty deviates from what has become the norm (meaning whatever white people value/elevate) it's cause for ridicule and questioning. frankly, it's \textbf{racist}. also, to assume that you have to be \textbf{fat} to have a high round ass is totally stupid and ignorant. if you look at naomi campbell and other \textbf{black} models, you will see they still have the high round asses that are typical of women who are \textbf{african} descended. i myself have run marathons and am a size 4. i still have an ass. this has \textbf{nothing} to do with obesity. you don't get it.but i will say that this typical \textbf{black} body - with the high round ass - has so fascinated (and frightened) white people that you have actually put us in glass cases to ridicule our bodies. you've actually tried to study us by dissecting our bodies. yes, this is fact. look it up. you have no idea what you're talking about.\normalsize   & \cellcolor{green!27}African, Black, Fat, Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}6/195 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small \@Timothy Flood i said they do which is why it is valued among many \textbf{african} descended people. just as blue eyes and blond hair are valued among white people. but when i first saw a person like that when i was a girl, i thought blue eyes and blond hair was frightening to look at.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small wow than i must be evolved. my brain  had to realize we dont live in middle ages anymore and i like nice small \textbf{skinny} asses.\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Holz NameI think we have all heard that in school, when we talked about paintings from 400 years ago which all show hefty women.The problem is, these paintings were painted for rich customers, so the "half-starving" argument doesn't make any sense;the people who ordered and bought those paintings were themselves never poor or starving.Your nature vs culture argument is correct, but the other way round: it is natural to be attracted to \textbf{skinny} women, and it is a cultural thing that some people prefer \textbf{fat} asses. It is a harmless form of a fetish.\normalsize   & \cellcolor{green!5}Fat, Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/98 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small \@Holz Name"I want to be \textbf{fat}" (meaning I always want to have enough food) is not the same as "I want to fuck a \textbf{fat} girl". Those figurines do not depict the ideal of beauty; they are depictions of fertility goddesses. You cannot compare those figurines to paintings from Renaissance times.(Ich weiß, dass die manchmal Venus genannt werden, aber das ist doch mehr als Witz gedacht.)\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/68 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small In my opinion, our natural love for ass came with a natural love for \textbf{fat} in general. our fixation on only \textbf{fat} asses is indeed socially constructed, in the sense that all the rest of the body part preferrences were reshaped around it\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small \@Joaking if you're \textbf{black} then you need to not fall into this \textbf{racist} trap of explaining or justifying why \textbf{black} people may or may not find certain things attractive on a \textbf{woman} or anything else. they don't justify what they like. why are you?\normalsize   & \cellcolor{green!27}Black, Racist, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!27}4/44 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small i love ass and im white. the "only \textbf{black} people like asses" is a USA thing really. Where i live in Argentina asses are fucking worshipped too and by everyone.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I'm not sure. I think that a lot of these " I like \textbf{fat} asses better " are cultural. I know more than well the evolutionary reasons for considering someone beautiful, but I'm pretty sure this has no limits and its the cultural.It's just like getting addicted on a porn fetish, it has no obvious explanation.I don't think its natural for people to like such big buts ( even if I like it or not ) and it's a product of our pop culture.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small \@Matthew Trujillo No I mean for the past 150,000 years human evolution has driven men to be attracted to certain physical traits women have that would be a benefit to the man himself and ti his offspring, such as foraging for food. The past 100 years of human evolution where we have grocery stores is irrelevant when we look at our most basic instincts.Let me also point out that most people on this thread are confusing attraction and \textbf{sexual} arousal. When a \textbf{woman} with a nice ass bends over in front of you that instinct is not the same as when she says she has a trust fund. Also for a women it's different power/money is often a \textbf{sexual} desire for them because their instincts are to be with the strong powerful male of the social group in order to pass on those genetics and to ensure her offspring and herself will be protected.\normalsize   & \cellcolor{green!5}Sexual, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/155 & \cellcolor{green!5}1.935 \\  \hline
  \cellcolor{green!27}\small \@litcguitaristAgain - this is not true. We are not attracted to \textbf{skinny} girls nor to \textbf{fat} bottomed girls by nature, because if we had been prefering one type over the last million years, the other type would be extinct by now. It is called natural selection, and it obviously does not apply to asses.Some men like big ass, others don't, and that has always been so. And as I pointed out further up, studies show that your macho type guy usually prefers big boobs, big ass, while the brainy type prefers \textbf{skinny} girls.\normalsize   & \cellcolor{green!27}Fat, Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}3/95 & \cellcolor{green!27}3.158 \\  \hline
  \cellcolor{green!5}\small \@BartJ583 \textbf{Fat}/\textbf{Skinny} can not go extinct idiot. It is not a genetic trait to be \textbf{fat}, although we do have genetic traits that lead to putting on weight faster/slower. Regardless of genetics if you eat a surplus of calories you will put on weight and if you are deficient you will be \textbf{skinny}. This can never go extinct. hahaha\normalsize   & \cellcolor{green!5}Fat, Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small \@BartJ583 Furthermore I just need to point out that all life on the planet has 1 goal and that is to reproduce, now if you're the king of the jungle \textbf{ape} you have your choice, but if you are not you gotta make some concessions that doesn't mean you're not attracted to the hot ass girl it just means you take what you can get!\normalsize   & \cellcolor{green!27}Ape & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small \@televisionninjaYou can look up the anthropological articles yourself.  See  [LINK] "In humans, females generally have more round and voluptuous buttocks, caused by estrogen that encourages the body to store \textbf{fat} in the buttocks, hips, and thighs. Testosterone discourages \textbf{fat} storage in these areas. The buttocks in human females thus contain more adipose tissue than in males, especially after puberty. Evolutionary psychologists suggest that rounded buttocks may have evolved to be desirable trait because they provide a visual indication of the woman's youth and fertility." [LINK] \normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/86 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@BartJ583Did I wrote that? I wrote "We love ass because we are primates. The ass is the storage for \textbf{fat} and the bigger the ass the more likely the \textbf{woman} can survive food shortages, making her more attractive". I did not wrote "we all want pumpkins down there".\normalsize   & \cellcolor{green!27}Fat, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small ...and there are millions of \textbf{fat} asses these days who could already live for a month without eating.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small The huge ass obsession run especially in US. In EU is shameless when girl has huge \textbf{fat} ass and she covers it up with layers. Does it mean we arent from animals in EU, or is it just escalated media trend? Yeap, we all like butts, but healthy butts, not the monstrosity that is adored overseas...And we like it with dignity. Or maybe it is \textbf{black} thing, because I dont see any white \textbf{fat} ass  in magazines. And I wont even aply THIS to your theory, because it just show, how is your theory stupid.\normalsize   & \cellcolor{green!27}Black, Fat & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!27}3/95 & \cellcolor{green!27}3.158 \\  \hline
  \cellcolor{green!5}\small \@Aubrey OleandereieBecause in Europe we recognize that obesity is a real health problem to society. 10,000 years ego people lived maximal to 40 years and to survive the next winter season was more important. Today people live well over 80 years, food shortages are history, and obesity leads to problems like arthritis, hearth attacks, diabetic, and so on.But the impulse still exists, that a good rounded ass and bigger boobs are more attracktive. It's only in today's society that a \textbf{fat} ass means obesity and means health problems.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small :D are you serious? Just learn some anatomy. There is few women whos ass is just from big muscles. But its not Nickis, its not Beyonces. I am definitely not saying they are \textbf{obese}! I am saying that muscle is not main part of their butt. Muscle butt looks absolutely different. And about boobs? VERY LITTLE \textbf{woman} are slim with breasts bigger than C. And even those are lucky ones.\normalsize   & \cellcolor{green!27}Obese, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Aubrey Oleandereie  I don't think the OP meant necessarily guys like a \textbf{fat}, giant, ass.  He just means that men are hardwired to be attracted to a 'healthy' ass, and what exactly that means will vary.  Yes, some guys like a \textbf{fat} ass, but almost all guys like a nicely shaped ass with a little meat.  I know very few guys who like a \textbf{skinny}, flat ass. Sorry if that's what you got.\normalsize   & \cellcolor{green!5}Fat, Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}3/73 & \cellcolor{green!5}4.11 \\  \hline
  \cellcolor{green!27}\small \@pheeel17Sure. And the explanation is that we are primates and \textbf{fat} is stored mostly in the ass and hips of female primates. If someone have a better explanation, please offer so.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small that would be true if we were primitive. We have a fucking brain to use, there is a reason we evolved to become smarter than any other animal. Saying that something is loved because we are in the same category as monkeys and apes is ignorant of our differences.It is not "ass" we love. As Bill said, ass has been there for millennia and \textbf{nobody} cared as much. We created "ass culture" and horny teenagers get hooked on it.I personally don't see how you can like a \textbf{fat} ass. In our time it means the girl eats too much and doesn't do exercises. And if she has an ass of a 35-year-old at the \textbf{age} of 25, imagine her at the \textbf{age} of 35. No, thanks, I prefer women who look after themselves.\normalsize   & \cellcolor{green!5}Age, Fat, Nobody & \cellcolor{green!5}Age - General, Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}4/135 & \cellcolor{green!5}2.963 \\  \hline
  \cellcolor{green!27}\small \@ToughTotoro  People has always been attracted to asses  snice before the greeks. It just been a symbol of beauty . And No it doesn't have to Be "\textbf{Fat}" ass most women have a shapely ass regardless of weight\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small The belly is also a storage depot for \textbf{fat}, perhaps even more so than the ass. So why are large bellies actually seen as unattractive? Your theory falls short.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@Ronnie Gonzalezso is the belly, you \textbf{mongoloid}.\normalsize   & \cellcolor{green!27}Mongoloid & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Antoine Vello This. it has \textbf{nothing} to do with "food storage".\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I think you're an idiot, with that logic everyone would be lusting after \textbf{fat} women but we know men like \textbf{skinny} and toned women more\normalsize   & \cellcolor{green!27}Fat, Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small \@Antoine Vello I wonder how people with no knowledge about science understood big ass means youth and fertility.LOLI found a pebble on the beach, I thought its lovely.Why do I think the pebble is lovely genius?Answering everything on the basis of science is a very depressing thing indeed, because you can't and any attempt you make will sound as \textbf{cheesy} and stupid like some stupid verse in some religious book, embrace the mystery, because you don't know everything, probably never can.\normalsize   & \cellcolor{green!5}Cheesy & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small \@Donald Dangelravis I actually debated if I should respond because you seem to be a \textbf{mental} \textbf{midget}. I never said anything was a fact, I was certain to say probably, can possibly serve as,  and likely, this is not hard and fast, there is however evidence that backs up what I say.How does someone's ability to survive a food shortage make them attractive? Well seeing as our genetic imperative is produce offspring likely to survive and a body with stored \textbf{fat} is more likely to survive in a time period when food was not a given. It is pretty easy to see why such features would be selected for.Why do asses indicate youth and fertility? Well I said they suggest that. Also the fullness of someone's as0s tends to reduce with \textbf{age}. So that's a sign of youth and the young tend to be more fertile. It does not take the scientific method as a young male human to walk through your almost butt-ass-naked tribe and see the women with children and the women of your \textbf{age} having different asses and be compelled by instinct to gravitate towards the younger women.\normalsize   & \cellcolor{green!27}Age, Fat, Mental, Midget & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}5/193 & \cellcolor{green!27}2.591 \\  \hline
  \cellcolor{green!5}\small \@Antoine Vello So we must be attracted to \textbf{fat} girls I guess, by that theory.oh young \textbf{fat} girls.I just think the habit of trying to explain everything in terms of science even when someone is only joking, is disturbing and its not like you have a solid theory of how \textbf{sexual} attraction works in terms of science.\normalsize   & \cellcolor{green!5}Fat, Sexual & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}3/58 & \cellcolor{green!5}5.172 \\  \hline
  \cellcolor{green!27}\small \@Donald Dangelravis Of course you go and deliberately misinterpret what I say. Where did I say that excess amounts of body \textbf{fat} that get to the point of impeding someone's health is a good indicator of survival? Because it isn't.Also younger people tend to be fitter and thinner than their elders, even now when food is in abundance. [LINK] So that suggests a disposition towards fitter people rather than as you so eloquently put it "oh young \textbf{fat} girls."Are you quite done?\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/84 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small \@Ritchiemomitchie   \textbf{sex} abundance, Yet people still want more\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Ape your.....\normalsize   & \cellcolor{green!27}Ape & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small \@bustedprius  you do't eat ass \textbf{nigga}?\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small The stop typing you \textbf{dumb} fuck.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@Ronnie GonzalezNope. Not if the \textbf{fat} ass is laden with sores and massive boils.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Roen Spacy How \textbf{old} are you dear?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Ronnie Gonzalez\textbf{Old} enough to be called your father. Child.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@ChiquitaSpeaksYou mean homosexuals? As far as I understand homosexuals have the same \textbf{sexual} instincts and preferences as hetero but for their own \textbf{sex}. If we would not be primates and the ass would not signal healthy amount of \textbf{fat} storage, then there would be \textbf{zero} interest in any ass. Fish, birds, frogs, squid etc. don't prefer ass. Birds prefer feathers and dancing and singing, but no ass. Don't ask me what those other animals prefer.\normalsize   & \cellcolor{green!27}Fat, Sex, Sexual, Zero & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}4/76 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Kim Chem \textbf{Nigga} just cause you asian dont mean you got ALL the answers shit\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Holz Name man ass is not voluptuous and curvy like a \textbf{woman} which has more attractive \textbf{fat} storage. As well, the curves of a womans body which instigate a healthy body for bearing a child is not present on a man. For what evolutionary reason would a man be attracted to a man. Overpopulation? Doesn't make sense since thats not a feature that sticks and benefits a single creature not to mention this is the first time we've really experienced it in history. Even then, its a matter of resources in the future, no one feels overpopulated and dies. \textbf{G\textbf{ay}} guys eat as much as straight guys.\normalsize   & \cellcolor{green!27}Fat, Gay, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/107 & \cellcolor{green!27}3.738 \\  \hline
  \cellcolor{green!5}\small Yeah that's it, every time I see a \textbf{fat} ass I think to myself, boy I bet that ass would help her make it through a famine!\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@Holz Name LoL Is that what the ass is for? We love a big ass, but do NOT let a \textbf{woman} be \textbf{fat}. God no. No one brings up \textbf{fat} storages when it comes to looking healthy! WTF kindda logic is that?!\normalsize   & \cellcolor{green!27}Fat, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}3/42 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@OoMASEoO What kind of stupid argument is that??? Men also like big tits but not \textbf{fat} women.Same thing. It's proven men are attracted to the ass and breasts on women because the subsoncious instinct of a man is attempting to find the best physical offspring. Women with larger breasts/asses will pass it down to their daughters. As for sons, they will actually have stronger attributes. Height/shoulder width/muscle tone.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small \@HoOGenghisB  so by your logic unless a \textbf{woman}'s breasts are 100 identical and congruent, you would take a flat chested \textbf{woman} over a \textbf{woman} like Hitomi tanaka? You better switch playing fields\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@litcguitarist Rosie has an indented ass. Second, a \textbf{woman} can be \textbf{obese} and have big tits. doesn't mean she's as attractive as the toned/leaner \textbf{woman} with not big tits\normalsize   & \cellcolor{green!5}Obese, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small \@Tim ClarksonThe article goes in many directions. Though it's more likely believed that instinctively men in fact love big breasts/big butts because of the subconscious of men looking for a mate that wold produce an attractive offspring to further their genetics. Really that simple.The "paris runway" models. Well hate to bring this up, but those \textbf{thin} sticks with no bodies were operated mainly by \textbf{g\textbf{ay}} men who lead the fashion industry, who aren't after women for the bodies of women, but women with the bodies of 12 year \textbf{old} boys\normalsize   & \cellcolor{green!27}Gay, Old, Thin & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/92 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Here is another study linking evolution with attractiveness. Maybe it's a combination between the curvature of the spine and the \textbf{fat} in the bottom. That would also explain why we are still find smaller asses attractive. It's always a mix between health, \textbf{fat} storage, and other factors. I really don't get why many people think it is a black/white issue. Attractiveness (and the underlying evolutionary traits) are always in a continuum. Some people find smaller more attractive, some find bigger more attractive. But the question is, why do we find ass attractive?Lumbar curvature: a previously undiscovered standard of attractiveness [LINK] \normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/101 & \cellcolor{green!5}1.98 \\  \hline
  \cellcolor{green!27}\small \@Holz Name The fact that the female gluteal region is an arousal trigger for males has \textbf{nothing} to do with \textbf{fat} storage and food shortages and everything with the ideal waist-to-hip ratio of 3:4 - 3:4.5, which signals \textbf{sexual} maturity as well as fecundity. It doesn't matter one bit how big a woman's buttocks are as long as the w2h ratio is within the desirable range. Women with a lot of body \textbf{fat} are actually considered unattractive, because the \textbf{fat} stored around the waist messes up their w2h ratio.\normalsize   & \cellcolor{green!27}Fat, Nothing, Sexual & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}5/89 & \cellcolor{green!27}5.618 \\  \hline
  \cellcolor{green!5}\small \@Strayed WayfarerYes, interesting. But how do you explain the venus figurines from 28,000–22,000 years ago, and the statues and paintings of \textbf{woman} through the history that certainly don't have the 3:4 waist-to-hip ratio, but are actually more \textbf{chubby}? For answers to my own question, see below.Maybe the waist-to-hip ratio is more important for the \textbf{sexual} attractiveness, and the \textbf{chubby} \textbf{woman} depicted in art are more of a fertility symbol than attractiveness symbols. But there is also an indicator that the optimal waist-to-hip ratio changes through the time. It could be that people 10,000 years ego find more \textbf{chubby} \textbf{woman} more attractive than today."We suggest three possible roles for Venus figurines. Firstly, a minority of images may have been intended to represent young, sexually attractive and nulliparous adult females. These might truly be considered as 'Venuses' in the conventional sense. Secondly, a subset of figurines represented changes in body shape during pregnancy and might be symbols of fertility. Thirdly, the figurines, depicting corpulent and often middle-aged women, may not have been 'Venuses' in any modern or conventional sense. They may, instead, have symbolized the hope for survival and for the attainment of a well-nourished (and thus reproductively successful) maturity, during the harshest period of the major glaciation in Europe." [LINK] "In this study, we demonstrated that the WHR of women considered as symbols of beauty did not vary during the antiquity period (500 BCE—400 CE) and decreased since (at least) the 15th century in western societies. A closer analysis of Playboy models and Miss pageant winners' measurements from 1920 to 2014 revealed a reduction, or even a reversion, of this WHR decrease. The universality of one preferred WHR is thus challenged, and the evolution of men's preferences could be linked to demographic, economic, health or social changes in western societies, which are older than the mass media growth of the 20th century."  [LINK] \normalsize   & \cellcolor{green!5}Chubby, Sexual, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical Features & \cellcolor{green!5}7/315 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@Mushy 808 Yay! Let's \textbf{boogie}!\normalsize   & \cellcolor{green!27}Boogie & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small You are a fool. \textbf{Nothing} more, \textbf{nothing} less.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small more importantly, the ass is the storage center for small adipose cells which are better at releasing energy on cue and doesn't signal as many health risks as subcutaneous \textbf{fat}.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Erwin Müller What's with the \textbf{g\textbf{ay}} obsession with ass?\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small No, the ass is not just for \textbf{fat} storage. It's meant to balance out the body (hence why women have bigger asses - it's cause we have tits).\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Not all \textbf{old} people are wise as he claims if they where fox news wouldn't exist.  yes there are a lot of wise older people(my grandpa was one).  but there are a lot of ignorant \textbf{old} people to.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Obviously. Maher didn't say that all \textbf{old} people are wise. He implied that people get wiser as they \textbf{age}. Do you really think the Fox News viewers were smarter when they were 26?\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small \@Хатима Эсмурзиева That is true. Over here people learn how to pass tests and regurgitate their majors; instead of learning how to think rationally or with \textbf{common} sense, despite all the general education they stuff down their gobs.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Bullshit."The average \textbf{age} of Members of the House at the beginning of the 113th Congress was 57.0 years; of Senators, 62.0 years."\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Old \textbf{age} does not always bring wisdom.From my experience, \textbf{old} \textbf{age} usually brings fascism...or Alzheimer's.I love my Grandmother but damn, she says some awful \textbf{racist} bigoted things!If you're going to stay in the same place your whole life,you will not get much of the experiences required to attain the so-called "wisdom";there are exceptions however.What I find to be true \textbf{Ageism} is assuming that just because that person has a higher number of birthdays than you,she automatically knows a lot more than you about any subject or topic.And yes,that person has had more time to learn about different topics,but that does not necessarily mean they've used that time to do so. And 78 is wayy too \textbf{old} to be President.I'm not being an \textbf{ageist} but a realist.How are you going to determine if the President is in possession of his \textbf{mental} faculties during office,when at that \textbf{age}, most people deteriorate mentally and physically.Everything he does will be evaluated using that prism,and I assume the Veep or the opposition will have a greater incentive to prove that the President is not fit for duty,or put more plainly,senile.Besides,from what I've seen of  the American Congress,I'm not sure \textbf{old} people (or at least \textbf{old} politicians)understand or are equipped to identify or handle the paradigm shifts that we are experiencing,along with the new realities and the new problems and difficulties that arise from all this,and  pose a threat to younger generations.\normalsize   & \cellcolor{green!5}Age, Ageism, Ageist, Mental, Old, Racist & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}12/237 & \cellcolor{green!5}5.063 \\  \hline
  \cellcolor{green!27}\small Due to the minimum \textbf{age} requirements, a millennial couldn't even be on the Presidential Ballot until 2020 and history shows we won't see a millennial president until 2036 at the earliest. Plus, in this last election, 37 of voters were 60 or older, 12 of them were Millennials. If we were "running everything", wouldn't those numbers be flipped?Prop up older, wiser people all you want - but this is still a fight between people in their 50s and people in their 70s.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small If we had a parliamentary system I would agree. The problem with electing 78yr olds is not that they are too \textbf{old} to govern. They may very well stay sharp for another couple of decades. The problem is that at that \textbf{age} (78-86, the \textbf{age} \textbf{Jerry} Brown would be during a two term presidency) a significantly high percentage of people start to decline mentally. In our presidential system it is very difficult to force our chief executive out. Many believe that Ronald Reagan had already begun to show symptoms of Alzheimer's by the time he left office. If he had, luckily it didn't cause any disasters, but what if he had started to decline a couple of years earlier? What if his decline had been more rapid? What mechanisms do we have to determine that the President is unable to execute his office? Maybe if Congress passed some laws governing these things more clearly it might be an entirely different issue. It is not so much \textbf{ageism} as fear of potential senile dementia. If anyone could weigh in with some statistics regarding the actual percentage of people developing Alzheimer's during this \textbf{age} period it would be great. Also, it would be interesting to know how many former Presidents have been afflicted with these types of conditions, how load they were at onset, and how long they had been out of office at the time. If it turns out that very few Presidents ever develop Alzheimer's or that they are diagnosed at a statistically higher \textbf{age} than the general population, I would be less concerned.\normalsize   & \cellcolor{green!5}Age, Ageism, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}7/264 & \cellcolor{green!5}2.652 \\  \hline
  \cellcolor{green!27}\small Age should be relevant, but not automatic grounds for dismissal - e.g. Bill's example vs say John McCain who, let's face it, is pretty much senile at this point. If someone's \textbf{old} but still in good health with a sharp mind, then sure - they should be able to get elected. Keep in mind though that the job is incredibly demanding - just look at what being in office has done to the last 3 Presidents - Bill George \& Barack all look far older than they are, and it's \textbf{nothing} new - it goes all the way back to Washington. That job ages and stresses the hell out of everyone who takes it.Well, until we get that youth serum perfected anyway. It works on mice so far >.>\normalsize   & \cellcolor{green!27}Age, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/130 & \cellcolor{green!27}2.308 \\  \hline
  \cellcolor{green!5}\small I think both houses of congress should have an \textbf{age} of mandatory retirement set at 65, and supreme court justices required to retire at 75. I think that the generation that makes up the majority of the workforce should make up the majority of the legislature. And we need term limits for both houses.I don't get my generations obsession with the ass.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small I love Maher, but come on, man. When McCain was running Maher was the first in line to tell everyone he's too \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small There's a difference between being too \textbf{old}, and being bat shit \textbf{crazy} too \textbf{old}.\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/14 & \cellcolor{green!5}21.429 \\  \hline
  \cellcolor{green!27}\small McCain was too \textbf{old}. Not in the sum of his years, but in the decay of body and mind.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small As Bill said... it's relative to the PERSON and not the \textbf{AGE} of the person.McCain was DONE... He wouldn't have survived 4 years and we'd have a goofy \textbf{dumb} broad at the helm, in a time of deep crisis!\normalsize   & \cellcolor{green!5}Age, Dumb & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Actually, there's a lot of technology and routines your can do to beat \textbf{old} \textbf{age}. Larry King takes HGH. If \textbf{Jerry} Brown or Bernie Sanders become president, they can do things to give them more longevity.\textbf{Old} people need to do shit like Tai Chi.\normalsize   & \cellcolor{green!27}Age, Jerry, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!27}4/45 & \cellcolor{green!27}8.889 \\  \hline
  \cellcolor{green!5}\small Bit rude on Schwarzenegger, his casual \textbf{racism} kind of weakens his argument but I do agree with him for the most part\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small But what about those that hold \textbf{old} outdated beliefs?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small i dont agree with this at all ....\textbf{old} bitter rich white people run this country not the youth................\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@mrohyoudidntknow3 Yeah. They started messing around with that around 1980 with \textbf{black} and white images. It was Magic Eye in 96 tho. I just have to know, have you ever got one to work for you? My daughters are teens, and it blew their minds when they got it to work for them. Me too back in the day. Oh, and did you ever get to see Carson when you were little? (That's another one that blows my mind these days that young adults don't know about.)\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small \@mrohyoudidntknow3 Yep. I stared at one every day for about a week at the mall. (Just like in that movie "Mall Rats") until it finally popped up. Just think of what the next generation will bring us. I have \textbf{nothing} but great expectations form them. I must say that you might not know what the world was like when Gen X was coming up. We got everything all at once. (At least it seemed) We went from 3 TV channels to 200, phones with cords to cell phones, no home computers to 2 in every household all over the world. All over night. The new smart phones, ipads, ipods, Xbox's, that's all us now. What the Mellennnials will do for us when we are \textbf{old} will be amazing. You wait and see. We can be friends, my man. Just don't be so quick to judge. Okay?\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/146 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small \@mrohyoudidntknow3 gen x is one of the hardest working, creative generations there is. we came from single parent homes a lot of the time and became a generation of self reliant people who don't blame everyone but themselves for their problems.Generation X statistically holds the highest education levels when looking at current \textbf{age} groups also.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small \@WisemanTimes It is always like that. You cannot blame a new generation for the shitty state of affairs. All these people trying to force laws on peoples lives (abortion, \textbf{g\textbf{ay}} marriage, etc.) because they are worried about their children. So ridiculous. Maybe they should go back to raising their kids and actually being parents. Being a parent isnt filling your childs head with your ideas. It is filling it with knowledge and truth, and the wisdom to use it appropriately. How the hell do parents expect their kids to make the right choices in life if they continue to lie to them about \textbf{sex} and drugs and politics. Lying to your kids about how the world is doesn't protect them, it sets them to be a pawn in the game of life. And when they find out the truth they will just be offended and shocked and most likely rebel with negative consequences\normalsize   & \cellcolor{green!5}Gay, Sex & \cellcolor{green!5}Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/153 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Careful about lumping us all together there, WisemanTimes. That's how any discrimination gets off the ground, including agism, \textbf{racism}, \textbf{sexism}, you name it.\normalsize   & \cellcolor{green!27}Racism, Sexism & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Consider for a moment the sheer multitude of people within the "How Dare You" Generation and you'll realize that saying, "They're all    " is doomed to fail. Its over-generalizing, and easily proved false by any one individual from that generation who can demonstrate otherwise. "They're all entitled." Wrong. "They're all whiners." Wrong. "They're all over-sensitive." Wrong. "They're all illogical." Wrong. And on and on and on. To say otherwise would be stereotyping, and the same applies to generalizing members of a \textbf{race}, \textbf{gender}, age-group, \textbf{nationality}, etc.\normalsize   & \cellcolor{green!5}Gender, Nationality, Race & \cellcolor{green!5}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}3/86 & \cellcolor{green!5}3.488 \\  \hline
  \cellcolor{green!27}\small plenty of How Dare You‘s are \textbf{old} liberal cat ladies or \textbf{old} conservative bible moms.  I blame feminization of everything mostly.  No \textbf{fat} guy is ever going to use the term \textbf{fat} shaming, thats \textbf{woman} shit.\normalsize   & \cellcolor{green!27}Fat, Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}5/36 & \cellcolor{green!27}13.889 \\  \hline
  \cellcolor{green!5}\small "that's \textbf{woman} shit." When you say "\textbf{Woman} shit," like that, it sounds like you mean all of them. Like if I say, "Its a man thing," it sounds like I mean men in general. And when you try to rationalize it by saying you "blame [the] feminization of everything mostly," it means you don't understand feminism.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@common101sense If you don't understand feminism, then how would you be able to detect when something has truly been "feminized"? You wouldn't be able to. You seem to be confusing feminine for "sensitive," which is rarely the case. As most people can likely attest to, a man can be just as sensitive as a \textbf{woman}, and a \textbf{woman} can be just as uncaring or insensitive as a man. \textbf{Gender} roles are largely illusory categorizations which over-generalize trends but ignore the marginal cases that define the complexity of the matter.But anyway, feminism is a kind of misnomer for equality.It means reverse \textbf{gender} discrimination. So a true feminist wouldn't be any more sensitive than anyone else, unless they saw true discrimination at work. True discrimination doesn't mean, "let's treat the \textbf{woman} and the man the same in deciding who gets the job, despite their differences in qualifications." Discrimination has to be unfair differentiation. So, if their qualifications were identical, and the employer said, "I went with the man because he is a man," that's discrimination. Similarly, if a bus driver is hiring his replacement, and a \textbf{blind} man applies for the job but the employer says, "I'm not going to hire you because you're \textbf{blind}," that's not discrimination, whereas if a \textbf{black} man applies and the employer says, "I'm not going to hire you because you're \textbf{black}," that is. The differentiation has to be unfair.\normalsize   & \cellcolor{green!27}Black, Blind, Gender, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}9/235 & \cellcolor{green!27}3.83 \\  \hline
  \cellcolor{green!5}\small \@common101sense "college liberal BS"...its called reasoned conceptual analysis, and its the basis of logical discourse. You'd think someone named "\textbf{common} sense" would be more in tune with such a notion... though you'd be good friends with "WisemanTimes."I'm telling you that this has \textbf{nothing} to do with being "over emotional," nor does feminism, and I'm guessing the assumptions you bring to the table have gone unanalyzed for too long, otherwise you'd know the difference, because its fairly \textbf{common} knowledge that feminism doesn't mean "make everything emotional and girly." If I parroted everything I heard I'm guessing I would end up approaching argumentation more in your fashion than in a reasoned one...\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}3/112 & \cellcolor{green!5}2.679 \\  \hline
  \cellcolor{green!27}\small \@SystemFreaKk13 You really think you're hot shit.  I didnt bring up feminism, you did.  Im talking about feminization, creating beta-males, removing natural aggression and competition.  People these days think its illegal to hurt someones feelings.  Cant even say basic facts like men and women are different bags of chemicals, each with their own set of biological skills  without pissing off some \textbf{chick}.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small \@JAY MURR I don't know what Generation Z is going to do when they enter adulthood, but they're the first generation completely prepared for the 21st century. They have no memory of the prosperous years after WWII or the Cold War. They know \textbf{nothing} but instability, and what you have to do to stay afloat. I'm no prophet, but I'm expecting less excuses, similar to Gen X\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small You can search "X Y cusp," "late/young Generation X," "Xennials," etc; you can see there's a wide dispute up to '84, an \textbf{age} group too young or too \textbf{old} to really associate with either Gen X or Y (how I've always felt). You can say "sorry, but no" to my rule about having a pre-recession adult life derailed in 2008, since it's not a \textbf{common} opinion afaik.ps. The video game test-- my older Gen X brother and cousins played their Atari when I was really young, but I had a Sega Genesis for myself, when they were getting ready to graduate high school and leave town.  That sounds like a gray area to me\normalsize   & \cellcolor{green!27}Age, Common, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/115 & \cellcolor{green!27}2.609 \\  \hline
  \cellcolor{green!5}\small I tried to explain that the rule isn't widely agreed upon, even among people who closely study the topic. Either way, generational boundaries are almost always arbitrary. The group that's really shaping the image of Millennials, like your Wayne's World example of Gen X, were born in the 90s, in their mid-20s or younger. Unlike the first Millennials and the last Xers, 90s kids were too young to be my peers when I was growing up. And my interactions with that younger group, online and in person... has been absolutely oil and water. I usually get along with anyone from the 80s. I obviously don't know much about Zuckerberg personally, aside from his birthdate, but I'm guessing that "first Millennials" and Gen X influenced him more than people born in the 90s, who were in elementary/middle school when he was in Harvard. For example, you brought up Xers creating Napster-- Zuckerberg was a close friend of one of the Napster co-founders, who was born in the 70s. People my \textbf{age} are definitely caught between two generations and evidently show characteristics of both.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/182 & \cellcolor{green!5}0.549 \\  \hline
  \cellcolor{green!27}\small The generational gap between people born in the 90s, and everyone before them, is so great, it really doesn't matter what middle-aged political catchphrase I belong to. I don't really have anything in \textbf{common} with "my generation" from the 90s, aside from using the Internet a lot.  Call that what you'd like.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small You would think that we should not respect young or \textbf{old} but those that deserve respect.... \textbf{old} idiot republicans or young idiot democrats that don't vote. Both don't deserve respect in this case.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Ok I'm sorry, but while I agree that there are some older people who are wiser than their younger counterparts, lets not forget that stupid people get \textbf{old} too.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small 78 is too \textbf{old} to be elected president.  It's past the average life span (for a male) in the US, and the office of the president demands a certain stability that a person teetering with one foot in the grave can't offer.  Bill, you've jumped the shark on this one.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small You are wrong and right at the same time. 78 is too \textbf{old}, because the job of president is physically demanding. As governor of California, \textbf{Jerry} Brown doesn't have to go on trips around the world; as POTUS, you cannot avoid that.But describing Brown as teetering with one foot in the grave - that's just idiotic.\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small I believe your missing my point, yes I understand the statistical norm. These people who are at the top of the game are far from a statistical norm they are disciplined and dedicated to defying the odds. They have the means (monetary) to take care of themselves physically and mentally which is proven by his routine to run 3 miles a day and yoga. Statistical data are people who are normal and for the most part do not take care of themselves. My bet is he'll live at least till he's 88 years \textbf{old} or older, more than enough for presidential term or terms.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/104 & \cellcolor{green!5}0.962 \\  \hline
  \cellcolor{green!27}\small \@Jonathan Stewart On top of that, the office tends to \textbf{age} men faster. It's so incredibly demanding, that despite the fact that he WOULD make a good president, he'd basically be giving up a healthy life in order to do so. I would say that if he decided to be a 1 term president, that I'd have less of a problem with it though.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small On that same token, electing someone like Chris Christie is even riskier.  His physical \textbf{age} is probably close to 80.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Kochu KamuganYeah, but his \textbf{mental} \textbf{age} is 6, so that's 43 altogether!\normalsize   & \cellcolor{green!27}Age, Mental & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small It's debatable, and while Maher is right about the \textbf{ageism} ignorance in this country, being 76 or 78 years \textbf{old} "should" mean you are some sort of part-time advisor, at best, even though our lifetimes are reaching into the 80's now fairly regularly.  The stress and activity required to be the president ages people faster than any other role.  I can't imagine how effective someone would be at that \textbf{age} for long.  There's \textbf{nothing} wrong with someone that \textbf{age} contributing to society in some meaningful, similar fashion when it comes to government though.\normalsize   & \cellcolor{green!5}Age, Ageism, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!5}5/93 & \cellcolor{green!5}5.376 \\  \hline
  \cellcolor{green!27}\small So because someone is likely to die sooner they shouldn't be president? That theory is kinda...\textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Mounir AlayExactly!!! Thanks, somebody gets it. These individual that reach to the top are a rare breed they've left the statistical norm pack. They are no longer part of the herd they are leading the herd. Just like him leading the herd in staying fit for his \textbf{age} to stay relevant, and taken one of our most prized broken state, fixed it quite a big feat to have accomplished.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small \@ToXiCVaPoRz29 Exactly, a lot of people didn't get that our Constitution had back up plan of a V.P., more than likely he'll have a younger minority V.P. to offset his \textbf{old} \textbf{age} and push the progressive agenda. There are a lot of variables to this conversation and people commenting can only see 1 dimensionally, should he die in office we'll cross that bridge together. What if he serves 1 term? Until then let's just see what kind of President he turns out to be and how long he'll last (see my prediction). Remember FDR was one of our greatest President who was elected and re-elected  a total of 4 terms, who got better at his job as he aged. What's more he had health issues just like JFK. Again these men are rare and exception not the \textbf{common} statistical norm.\normalsize   & \cellcolor{green!27}Age, Common, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/140 & \cellcolor{green!27}2.143 \\  \hline
  \cellcolor{green!5}\small \@mechanoid2kAgreed, such small way of thinking I would rather have a 1 term President like Theodore Roosevelt that got a lot done or JFK who inspired a \textbf{nation}, than a \textbf{lame} 2 term President like "George of the Bungle".\normalsize   & \cellcolor{green!5}Lame, Nation & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@BartJ583 Ford was a unique situation. He was only Vice President because Spiro Agnew resigned 10 months before Nixon did, facing corruption charges that had \textbf{nothing} to do with Watergate. I don't think people are ever really scared off of a Presidential candidate by the VP running mate, with the possible exception of Sarah Palin in 2008. McCain was over 70 at that point, and had already had a cancer scare - not to mention his years as a POW, which certainly added a physical stress that most of us don't have the misfortune to experience. Now he looks like he's going to make it to January 2017, but back in 2008, his \textbf{age} and physical history did make that a more relevant question than it normally is. And he was backed up by somebody who was stumped by the question, "What do you read?" If \textbf{Jerry} Brown ran, chances are that his running mate would be somebody who is both competent and young enough that people expect he or she will still be healthy and strong after two terms. I don't think he's going to run, though. But it will be interesting to see who Hillary picks as a running mate - in 2016, she'll be almost as \textbf{old} as Ronald Reagan was in 1980.\normalsize   & \cellcolor{green!27}Age, Jerry, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters, Nationality - German & \cellcolor{green!27}4/216 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small As I said before - OP is right, and quite obviously so. He just didn't use the right words.There are 75yo people who are so healthy that there is no reason to assume that they will die within the next ten years.But most of them do not have to work anymore. And we are not talking about a 75yo who spends his days with fishing and hiking and visiting museums. We are talking about doing a very stressful 16-hours-a-day job.Chances are that a 75yo \textbf{old} will have much more difficulties doing such a job for 8 years.When McCain chose Palin to be his VP, people were shocked. Not because she is a moron; they didn't know that from the start, but because many thought: 'when (not if) McCain dies, we will be left with a president with little to no experience.'So in my opinion, this is the point: candidates who are 75 or older can run, and Bernie Sanders definitely should run, but only with an experienced middle-aged running mate.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/175 & \cellcolor{green!5}0.571 \\  \hline
  \cellcolor{green!27}\small 3 simple questions1. Would he be a great potential candidate as an option/variety on the Democratic ticket to run for the presidency?2. Given his track record and accomplishment in California if he mimics that as POTUS would he be a good to great President?3. Is it not his choice to work and die serving his country at the highest level if he so chooses, I mean we have a Constitution with fail safe for succession should something happen, am I not correct?Please answer Jonathan Stewart or those on this comment thread who are still on the fence on whether Gov. \textbf{Jerry} Brown and or any mature candidates ie; Senator Bernie Sanders who feel are to \textbf{old} to run for the Presidency.\normalsize   & \cellcolor{green!27}Jerry, Old & \cellcolor{green!27}Age - Over 65s, Nationality - German & \cellcolor{green!27}2/125 & \cellcolor{green!27}1.6 \\  \hline
  \cellcolor{green!5}\small By the way BartJ583  you are and were wrong that Gov. \textbf{Jerry} Brown can't handle the work load due to travel fatigue. He's traveled and met with 2nd most powerful nation's president and discussed term of trade and collaboration. Would you like more examples of his foreign travels and dignitaries he's had that privilege to work with? Would you like to see what he accomplishes on a daily basis and still finds time to run 3 miles a day and occasionally does yoga when he has a chance to? Do you have the same experience, capability, will and drive like his? Just asking questions, an answer would be greatly appreciated.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/110 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small \@Think2 BI am not wrong. He has traveled exactly \textbf{zero} miles at the \textbf{age} of 80. If you can't understand that there is a difference between being 75 and being 80, then you just don't know any \textbf{old} people.Also, no matter how much a governor of California travels - a president travels more. Much more.That being said, I still think that it would be no problem to have an 80yo president, as long as his VP is an experienced politician who is not yet 60.\normalsize   & \cellcolor{green!27}Age, Old, Zero & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/88 & \cellcolor{green!27}3.409 \\  \hline
  \cellcolor{green!5}\small BartJ583 You are wrong I know many 80 year \textbf{old} mature people who happen to travel a lot and take care of themselves so do not presume to know who or what I know. You making an ass of yourself. You quoted " As governor of California, \textbf{Jerry} Brown doesn't have to go on trips around the world; as POTUS, you cannot avoid that". Have you read and done your research of where this man has traveled and at what \textbf{age} he's traveled. He stayed in China for a week as I've stated previously, worked with Mexico President Enrique Peña Nieto  [LINK]  just this June 2014. Do you think he's your typical 70 to 80 year \textbf{old} who's inactive (couch potatoes) who doesn't stimulate his brain. Last I read and heard is he's the darling with The Economist rubing elbows and cutting deals with Presidents of other countries just recently as a matter of fact. I don't think he travels in the luxurious Air Force one but I'm sure if he becomes POTUS he'll get that perk what do you think? Lol...Maybe you don't know the 70 or 80 year olds that we know who go to the gym and are successful in life, I do and they are exceptions in life because they take care of themselves. Just like Gov. \textbf{Jerry} Brown who runs 3miles, does yoga and fixes a whole state he's an exception, successful and good at what he does. You should acquaint yourself with those mature exceptionals. It'll be good for you so you won't be so judgemental and make an ass out of yourself. Do your research on this particular individual Gov \textbf{Jerry} Brown because he's the topic of the discussion. Feel free to make an  ass(umption) and comment again BartJ583, just make sure you have facts not generalization (statistical data).\normalsize   & \cellcolor{green!5}Age, Jerry, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - German & \cellcolor{green!5}6/306 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@Think2 BI am rather angry now.Again - \textbf{Jerry} Brown didn't do any of those things in his 80s. He was in his 70s.And again, we are not talking just about traveling. We are talking about a 14-16-hour workday, every day, with very few vacations and very few weekends.If you cannot see how demanding that job is, then you do not know any 80yo people.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small He just traveled 4 months ago dealing rigorously about NAFTA trade and immigration. I think that's pretty stressful don't you? Do you have a crystal ball that tells you how Gov. \textbf{Jerry} Brown will be in his 80's or are you relying on your ass(umption) or generalization of statistic. I certainly don't know but I'm willing to give the man a shot because of his track record, dedication, and discipline. What are you basing your rationality on? I know an 88 yr \textbf{old} who can dead lift 415lbs and works 14-16 hours actively and is successful. I've seen many more at the gym, they don't settle in life they keep pushing the boundaries. I've seen in YouTube an \textbf{old} boxer show up a young boxer. Do not presume what one can and can not do. Speak for yourself. Don't get angry, get factual knowledge and defend your points. You know the \textbf{old} saying, if you can't handle the heat in the kitchen, then get the........if you don't like the channel change it. As for me I'm moving on, fun to see you get mad over something so minuscule and irrelevant. I mean come on its just a comment thread and we don't even know if he's running. I mean do you really know what's going to happen in the future. If so you would've beaten Warren Buffet and been a TRILLIONARE. Again he's one of the wisest, sharpest, workaholics, and richest who works and travels to China to cut deals and ohhh I forgot to mention he's 84 year \textbf{old}. Really? C'Mon smile and laugh LOL\normalsize   & \cellcolor{green!5}Jerry, Old & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}5/266 & \cellcolor{green!5}1.88 \\  \hline
  \cellcolor{green!27}\small \@Mike McTighe Not Reagan.  He spent most of his time in office on vacation and/or asleep. Reagan was unusual in this respect as most \textbf{elderly} people find it difficult to sleep for long periods. Teens and twenty somethings are the champions at sleeping for long stretches.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Actually, it's gonna be middle \textbf{age} before you know it, and Ron Paul and \textbf{Jerry} Brown can run circles around my 30-something ass. Gee, I guess you really don't know everything, after all. FFS\normalsize   & \cellcolor{green!5}Age, Jerry & \cellcolor{green!5}Age - General, Nationality - German & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small The \textbf{elderly} are not the only "acceptable" group still being discriminated against in America, not at all. \textbf{Handicapped} for one. And sure its fine to elect an \textbf{old} president but usually \textbf{old} means \textbf{old} idea. And many \textbf{old} ideas suck, lets be real. Liberals all want new so I have no idea what Bill is talking about... Of course there are exceptions to the rule..\normalsize   & \cellcolor{green!27}Elderly, Handicapped, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/65 & \cellcolor{green!27}9.231 \\  \hline
  \cellcolor{green!5}\small Wasnt fdr \textbf{handicapped}?\normalsize   & \cellcolor{green!5}Handicapped & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Generally, I love Maher's ability to critically analyse US culture. Yes, it is shallow and youth-obsessed (like any other culture I am familiar with). But having "respect for the \textbf{elderly}" has \textbf{nothing} to do with considering people unfit to govern at a certain \textbf{age}. Furthermore, \textbf{age} isn't necessarily linked to wisdom. I know just as many wise and reflected people in their late-20s as I know ignorant, stupid and by no means "wise" people over 50.Claiming there is a cultural bias against \textbf{old} people in politics is ... well, just look at your government.\normalsize   & \cellcolor{green!27}Age, Elderly, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}5/95 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Agreed, not sure what the fuck Bill is talking about when he claims the U.S. is unfair to \textbf{old} people...our society give too much \textbf{blind} respect to \textbf{old} people.  One of the reasons we are so religious...\normalsize   & \cellcolor{green!5}Blind, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small Well... unfortunately the driving regulation/training system in mainland China isn't very friendly.It's always the \textbf{old} and conservative folk who haven't adapted to the culture who cause the stereotypical accidents.But isn't USA mainly run by older people? And doesn't agism exist against young people as well? i.e. assuming that young people = less educated, less experienced, don't know anything, etc.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Yeah, I completely disagree with Bill on this issue. People give \textbf{blind} respect to the \textbf{old} in this country, while blaming the problems of society on the young.\normalsize   & \cellcolor{green!5}Blind, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Communist, Libtard, Red, Snowflake, Nazi, Imperialist & \cellcolor{red!27}23 & \cellcolor{red!27}23/101845& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry, Gerry & \cellcolor{red!5}120 & \cellcolor{red!5}120/101845& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Ageism, Age, Ageist, Ageing & \cellcolor{red!27}465 & \cellcolor{red!27}465/101845& \cellcolor{red!27}0.45999999999999996 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Elderly, Elder, Senior & \cellcolor{red!5}674 & \cellcolor{red!5}674/101845& \cellcolor{red!5}0.66 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racist, Racism, Race, Ethnicity & \cellcolor{red!27}66 & \cellcolor{red!27}66/101845& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Fat, Chubby, Twiggy, Lump, Thin, Fatty, Skinny, Obese & \cellcolor{red!5}137 & \cellcolor{red!5}137/101845& \cellcolor{red!5}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}pussy & \cellcolor{red!27}4 & \cellcolor{red!27}4/101845& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian, Red, Apple & \cellcolor{red!5}10 & \cellcolor{red!5}10/101845& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Sex, Sexual, Gender, Sexism, Woman, Chick, Misandry, Misogyny & \cellcolor{red!27}113 & \cellcolor{red!27}113/101845& \cellcolor{red!27}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, Redneck, Cheesy & \cellcolor{red!5}21 & \cellcolor{red!5}21/101845& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - White}  & \cellcolor{red!27}Redneck & \cellcolor{red!27}1 & \cellcolor{red!27}1/101845& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nobody, Nothing, Zero, Brat & \cellcolor{red!5}97 & \cellcolor{red!5}97/101845& \cellcolor{red!5}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay, Homophobic, Homosexual, Homophobia & \cellcolor{red!27}29 & \cellcolor{red!27}29/101845& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, Faggot, Fruitcake & \cellcolor{red!5}22 & \cellcolor{red!5}22/101845& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Dumb, Blind, Crazy, Weird, Disabled, Mental, Lunatic, Psycho, Nutter, Freak, Bonkers, Mongoloid, Midget, Lame, Handicapped & \cellcolor{red!27}97 & \cellcolor{red!27}97/101845& \cellcolor{red!27}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - American}  & \cellcolor{red!5}Septic & \cellcolor{red!5}1 & \cellcolor{red!5}1/101845& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nation, Engineers, doctors, Immigrant, Alien, Xenophobia, Nationality & \cellcolor{red!27}33 & \cellcolor{red!27}33/101845& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black, African, Crow, Jim Crow, Nigga, Ape, Boogie & \cellcolor{red!5}84 & \cellcolor{red!5}84/101845& \cellcolor{red!5}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - European or anti-Europeans}  & \cellcolor{red!27}Brexit & \cellcolor{red!27}3 & \cellcolor{red!27}3/101845& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Jewish}  & \cellcolor{red!5}Abe & \cellcolor{red!5}2 & \cellcolor{red!5}2/101845& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Italian}  & \cellcolor{red!27}Hike & \cellcolor{red!27}1 & \cellcolor{red!27}1/101845& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Pancake, Banana & \cellcolor{red!5}23 & \cellcolor{red!5}23/101845& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Aboriginal}  & \cellcolor{red!27}Bong & \cellcolor{red!27}1 & \cellcolor{red!27}1/101845& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho & \cellcolor{red!5}1 & \cellcolor{red!5}1/101845& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Witch, Old hag, Hag & \cellcolor{red!27}4 & \cellcolor{red!27}4/101845& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Behavioural Addiction - Alcohol}  & \cellcolor{red!5}alcohol & \cellcolor{red!5}1 & \cellcolor{red!5}1/101845& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Destitute}  & \cellcolor{red!27}Bum & \cellcolor{red!27}1 & \cellcolor{red!27}1/101845& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : :  Ideological and Political Identity - General;Nationality - German;Age - General;Age - Over 65s;Ethnicity - General;Physical Identity - Physical Features;Nationality - Chinese;Ethnicity - Native-American;Gender - General;Social Class - Working class;Ethnicity - White;Age - Youngsters;Sexual Identity - General;Sexual Identity - Male homosexuality;Physical Identity - Physical (and Mental) Impairments;Nationality - American;Nationality - General;Ethnicity - Black;Nationality - European or anti-Europeans;Religious Identity - Jewish;Nationality - Italian;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Ethnicity - Aboriginal;Gender - Female sexuality;Gender - Female age and physical appearance;Behavioural Addiction - Alcohol;Social Class - Destitute;%.

\item The percentage of hate speech related words is 1.9972.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 2038/2786 occurences of hate speech related comments.\end{itemize}\end{document}