\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_81.json :}\newline \par\Large\textbf {Title: \large  Interview with Porn Star Dani Daniels }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small She will be a very sad \& \textbf{old} \textbf{woman} later possibly with no partner \& very few friends !\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small White girls become whores so easy. Not strange that they get raped a lot. Most guys I know would fuck this girl and piss on her \textbf{pussy}.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Crazy how prostitution became a job\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small She should get tested for having \textbf{sex} with her bodyfriend because its her issue not his.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small 1. You just described my high school. 2. How active is a Pornstar's personal \textbf{sex} life? 3. Wanna go out some time?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small ..i felt sorry for her...but imagine your girlfriend having \textbf{sex} with many guys....that is something i cannot handle\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Real men don't care 🤷‍♂️ about who you have \textbf{sex} with so long as your safe\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Soooo..., once-again, it's, ALLL-about-tha-CHOICES, CHOICES, CHOICES...!!  Also, to all of the 'porn-haters' below..:  like-EVERY-THING-else (in life) there is \textbf{NOTHING} wrong wit 'porn', as-long-as it's used (consumed??) maturely \& in-MODERATION.  The problem iz in  the over-use there-of.Additionally...:   "I don't understand why prostitution is illegal (in the U.S.) but, porn -- is not...??"  Porn continues to exist, PARTLY cawz, (so-called) 'regular' women do NOT know how to treat their men, sooo, he looks else-where for:  release, satisfaction, \&/or, 'entertainment' (etc.)!  The REAL blame here, belongs to the hidden elites \& organizationz who front \& fund porn \& for the destruction of hetero-relationships:  FemiNazi'z, Socialists, \& the 'Divorce-Corp' (U.S. family-law 'profit-system').  THEY, are the ones who hav purposely destroyed the hetero-family, buuuut.., NO-one is talking abt tht TRUTH, cawz, it duzn't fit their political-'NARRATIVEs'!!  It's just sooo much easier to blame 'men' -- in-general (which causes even more divisions) \& that's just TOO MUCH, B.-S. to tolerate!!   Having-said-that..., I, do NOT (NOR, could I EVER) condone treating any-one poorly, or especially -- debasing them.  Sooo, WHERE is the personal-ACCOUNTABILITY of these whining females??  WHYyyy, can't these women have made better 'life-DECISIONS'??  Helllo...??  Make women accountable for THEIR actions (\& decisions) \& this problem WILL -- WILL, resolve itself.  This mantra of:  'always-blame-the-man' is such COMPLETE \& utter B.S.!  The REAL-issue here is:  NONE of these women are willing to be held-ACCOUNTABLE, for THEIR, bad-DECISIONS!   Annnnnd, now...., they wanna whine \& bitch cawz they (effectively \& UN-realistically) DEMAND that, a 'GOOD-MAN' accept them, with ALL of their faults \& (\textbf{sexual}) WARTS to, 'wife-them-up'.  Are you serious...???  W-t-F...???  They do NOT hav the 'right', to make such a demand!!!  As so many of these women have said... (para-phrased \& consolidated):  "NO-one really wants to date, or, have kids with, an (ex) porn-star."  To that I, query:  ...annnnnnnnnd..., WHO's fault, is that??\normalsize   & \cellcolor{green!5}Nothing, Sexual & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/308 & \cellcolor{green!5}0.649 \\  \hline
  \cellcolor{green!27}\small I don't understand...Her "civilian" boyfriend isn't allowed to be jealous of her having \textbf{sex} with other performers as part of her job...but when SHE dates a fellow performer she admits to getting jealous of him doing scenes with other performers and that's a big reason why the relationships don't work?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small I'm sure feminists think she is an empowered and happy \textbf{woman} 😂\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She's weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small this is crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Dani is such a Beautiful \textbf{woman} , what she does is her job her life. I wish I could find someone like her in the Porn or any industry.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Holly Randall she knows how to turn a \textbf{woman} into angel through make up.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I think Dani would like to meet a real man. That loves her for personality, her smile which could be so much bigger being a little more happier. Me personally. I wouldnt have a problem dating a \textbf{woman} in the adults biz. It's a job plain \& simple. I've met a few \textbf{woman} in the biz. Ginger Lynn was the best \textbf{woman} I got to know. Just wish my bike was fixed lol\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/73 & \cellcolor{green!27}4.11 \\  \hline
  \cellcolor{green!5}\small i will list all the actors i bang who have superior d*cks to yours, and then i will crap on you if you feel insecure about yoursdid i mention i'm single and have \textbf{sex} for money?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small "A Human Being is not a Being,he is always in a state of flux.One minute they Feel Godlike the other times they feel brute.\textbf{Nothing} is fixed."(Sadhguru)...For this reason She will not be like this forever.Lets not forget this.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small It took that shallow \textbf{bimbo} 3:55secs..to answer..'dating doesn't  happen'...geeze!\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small fuck her \textbf{pussy} and piss on it lol\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} has to be demon possessed.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small If she is sad. Im sorry. If porn is bad im sorry because i have seen a lot of porn. It taught me how to have \textbf{sex}. And yeah im above  average but what good is that if you dont know how to use it. I dis agree i think you can have a good relationship no matter who you are. Hang in there Dani your man will find you when its the right time.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small what a sad life. this \textbf{woman} has lost her soul. and a boyfriend.?  how can she tell the difference between her partners and the boyfriend? ummm.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I want xxxx vedios acting job porn movies acting job I need Mony l am block men My country india my \textbf{age} 28 My Email address mathivananmathivananmv\@gmail.com\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I can't imagine living a life with the most private part of you, not being private, it has to eat away at you, something must give, she acts so casual about something that will leave her to no joy in this life, and one of the most binding things that a man and \textbf{woman} do is to be married and bear children together. When it become something casual and meaning \textbf{nothing}, then what. She is a little girl, who pretends she is doing a job. She's  a prostitute and can't find a good life with a man, and yet, she has \textbf{nothing} tells her to stop. It never works she just won't say it.\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/114 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Who is smarter the girl that has \textbf{sex} for free for love and probably treated like shit or the girl who selectively has \textbf{sex} for money and treated well by a sugar daddy ?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Must make the \textbf{pussy} numb all those big penis\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small double standards weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} has to be demoned possessed. Stay away from porn. It has ruined the minds of our young to which these scumbags could care less. We need to ban porn and put these producer bastards behind bars. These women are all prostitutes and should also be behind bars. They are contributing to the downfall of America.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small When you become an adult you make choices it's your life and your decision what you want to do for a living. I'm still looking at porn websites to see if porn stars and adult actresses are still making and producing more new pornographic materials you will be surprised that there are more new porn stars filming and producing \textbf{sex} tapes. So why do self righteous people want to judge and act like they are holy or something. \textbf{Nobody} cares about your thoughts and opinions including porn stars. If people enjoy selling their bodies and having \textbf{sex} on camera than so be it. Also I want to mention in western countries \textbf{nobody} is interested in marriages and serious relationships. Women initiate majority of the divorces so who cares if people want to watch porn. Some people want to marry porn stars, strippers, escorts, hookers and prostitutes because they are in love with them. Some people are interested in \textbf{sexual} relationship than serious relationship. But honestly who cares and who gives a flying shit what society thinks your a grown adult go live your life the way you want too.\normalsize   & \cellcolor{green!27}Nobody, Sex, Sexual & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}5/189 & \cellcolor{green!27}2.646 \\  \hline
  \cellcolor{green!5}\small she have \textbf{sex} with dicks all the time  what a dick\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small She is really genuine and I know it is very hard to find love for a pornstar she may get \textbf{sex} easily but really it is very hard to get love i will love to date this lady after all pornstars are counsellors if thought from a bright side. Love you dani daniels\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Why do they call these sluts  "porn stars"?. John Wayne ,Elizabeth Taylor, Russell Crowe they were stars. These adult film trash should be called porn whores and porn sluts .Why is it ok for them to engage in all kinds of \textbf{sexual} acts with all types of people for money that is sene by countless people but a guy pays for oral from a \textbf{hooker} in his car can be arrested ? If a guys buys a \textbf{hooker} he should carry a camera so that he can say he is making an adult film when they try to arrest him.\normalsize   & \cellcolor{green!27}Hooker, Sexual & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}3/100 & \cellcolor{green!27}3.0 \\  \hline
  \cellcolor{green!5}\small what a \textbf{slag}!!!!!!\normalsize   & \cellcolor{green!5}Slag & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Age registration video monutize hute ha\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Sounds like dating a porn star is a lot more complicated than dating a  \textbf{hooker} . There are hookers , but then there are sophisticated hookers. Bottom line, they are all people screwing for the almighty dollar.\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Makes men insecure? Okay, she is clearly \textbf{crazy}. Of course it makes people uncomfortable. No decent human would feel comfortable with their s.o fucking other men and or women. That is what you do and reserve for a partner.Her civilian and performer titles are  laughable. It's like when we call cash register employees, brand embassadors. Lol\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small THOT you picked this profession. You could have picked another career, but no I ride the CC all the time.\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small She is a \textbf{thot} but otherwise not an issue, and yes she chose this. Go and jack off to porn and complain about porn afterwards.\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Flee from \textbf{sexual} immorality. All other sins a person commits are outside the body, but whoever sins sexually, sins against their own body.Ephesians 6:18\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Excluding groups of some wiser people. Society is sad. I hate everything this generation does. Pornography is disgusting. You can see the hurt in her face. She is a beautiful young \textbf{woman}, and she gave it all away to several other Pornstars. People need to stop watching pornography and get their life straight. Pornography is a abomination and blot on mankind's reputation it does \textbf{nothing} but hurt people. I have never watched pornography and I never will. This is disgusting.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/80 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small U may be porn star ,,but ur honest \textbf{woman} as long u keeping honesty with people no matter with ur professional\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small the non-spleenful laughter belies the dissatisfaction with her choice of employment.  \textbf{Sex} is an emotional  communication.  It's value is priceless.  To do it for money is to abandon the self.  Yet it can be done so casually, for no money, that it is the same thing as self abandonment.  Before we conquer Mars we should get a handle on the \textbf{sex} drive.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I think it would be hard to satisfy a \textbf{woman} like her but that doesn't  mean men are insecure is just that she s been practicing all positions and everything so what else a  normal men can do to satisfy  her .? She s very wrong that make me think she s very insecure  and sad inside she try to blame on an normal men... i feel bad for her\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small What are you fuckin \textbf{g\textbf{ay}}?\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small This girl is very stupid she is trying to smile while she is burning inside  a sinner will never have peace whether you do what or what. Anywhere \textbf{nothing} supplised me cause all this thing was prophesied long time ago, and this should also remind us that JESUS CHRIST is about to come cause all these things were prophesied we have seen them all.and remind you that they are only 2 ways there is a way to HEAVEN and Way to hell so it's up to you to choose which way to pass through. REPENT YOUR SINS AND BELIEVE IN GOSPEL RECEIVE JESUS AS YOUR SAVIOUR .\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/107 & \cellcolor{green!5}0.935 \\  \hline
  \cellcolor{green!27}\small Lmfao who in there right mind would marry a pornstar smfh ok honey noproblem you could go suck five cocks tonight iam ok with it get the fuckoutta here gross how to bring a pornstar home to mom id never disrepect my mother like that we live in a sick world were \textbf{woman} actually get paid for \textbf{sex} acts these people need jesus in there life\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small She's probably useless in society...just a shallow \textbf{woman} addicted to big dick\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small This female prostitute is all smiles now in a few years should be a war out \textbf{o\textbf{ld} h\textbf{ag}} drug addictive disease infected creature \textbf{nobody} will care \textbf{nobody} til sorry for her or \textbf{nobody} will like her poor her\normalsize   & \cellcolor{green!27}Hag, Nobody, Old, Old hag & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Gender - Female age and physical appearance & \cellcolor{green!27}6/38 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Is she \textbf{crazy}??? :)))\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@ʕ•́ᴥ•̀ʔっ woah, how \textbf{old} r u now tho ?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small smh obviously relationships most likely won't work lmaooo they're difficult if cheat and have \textbf{sex} w someone else let alone have \textbf{sex} w multiple men in a day :/\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Porn isn't normal at all.If u watch excess porn u start treating women as objects.U think \textbf{sex} all the time ,it  destroys relationships and our dreams in lifeSo don't be foolish listenining to pornstars what they need is only moneyU will never realize that ur addicted to porn untill u try to stop it\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small The odds of things working out if marrying a porn star or a Russian \textbf{woman} who you met on the internet is \textbf{ZERO}.\normalsize   & \cellcolor{green!5}Woman, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small No honey. The truth is \textbf{nobody} wants a filthy cumdumpster. So stop lying and admit that you´re a filthy pig.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Vile woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Yea they'll have something in \textbf{common}. Jesus loved getting nailed too\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small She goes on to say how dating a civillian is hard because they get jealous that she's having \textbf{sex} with other guys yet also ironically says how if she had a pornstar boyfriend she would get jealous if he had \textbf{sex} with others. Hypocrite alert!!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small NOBODY wants to date a cunt slut whore with a giant gaping snatch!!!!\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small BF: "Hello, how was your day? "Hello, how was your day?"" "Hello, how was your day?" "Hello, how was your day?"Dani:  I'm not \textbf{deaf}, I heard you the first time you said "Hello, how was your day?"BF: "I didn't say it several times, that was the echo!"\normalsize   & \cellcolor{green!5}Deaf & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Pussy seller  😂\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small all those people are possesed, it s not a normal thing to seeek for  hundreds of \textbf{sexual} partners\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small "Dating is a nightmare. Dating is so bad. It's so bad."Yeah, no shit. You're literally CHEATING on your boyfriends for a living. Meanwhile, your boyfriend gets to have \textbf{sex} in the missionary position twice a week while you're yawning at the ceiling after you've been double-penetrated by half a dozen douche-bags.Here's a newsflash: There are MANY guys who would love to date a porn star, but, every single one of those guys has serious \textbf{mental} health issues. The kind of guy you WANT as a boyfriend or husband, is NOT going to be okay with you fucking a dozen random guys every week. Period.\normalsize   & \cellcolor{green!27}Mental, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/106 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small This is a most toxic creature among many who is a rabid animal with no sense of existence or respect for herself or others! The craters to her body are infested with cancer. What intelligent man even a drunkard would fuck this "\textbf{woman}" and not take a shower with Lysol immediately thereafter?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Typical Muslim. Stone a \textbf{woman} to death for showing too much ankle. Then watches porn stars on the internet.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Wait, the porn star can have \textbf{sex} with other peeps but the "civilian" can't?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I think love and \textbf{sex} are the same thing, you have \textbf{sex} with thousands of Men these thousands of men actually become your husbands\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small For me pornstar \textbf{woman} or man they are people without ambition. Really without. Lazy people\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small It's not the fact that you are having \textbf{sex} with guys who have huge dicks, it's what those huge dicks are doing to your vag. Could she even feel an average sized man? I've seen enough of her to know that she is gaped just sitting there during the interview.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small I have never once had \textbf{sex}, so that wouldn't apply to me. I hated my school and the people anyway.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Finding a spouse who is a virgin is rare these days, but most people accept it.  However, who's looking for a porn star, or ex porn star?  If you met a "nice" guy or girl and after a few dates they tell you they are, or used to be, a porn would you continue the relationship?  The \textbf{old} adage of "\textbf{nobody} buys used shoes" maybe has run it's course.  But who the hell buys worn out shoes?\normalsize   & \cellcolor{green!27}Nobody, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small She just a \textbf{hooker} who get taxes that's all\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small In the '60s I was "recruited" by a girl I was hanging with.  She \& her group told me about the great money, the constant hot \textbf{sex}, the swingers I'd meet...all BS!  I learned just how grubby the group was and split! Didn't want any STDs!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Is she worried about cuckold boyfriend? I mean that is the only kind of boyfriend she is ever going to get a \textbf{beta male} cuckold. Very pretty talking fuck hole.\normalsize   & \cellcolor{green!5}Beta male & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small she.is.so.\textbf{dumb}.enough.said.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small She has a lot to say. Has clearly thought it through. I could actually date an ex \textbf{sex} worker if I thought they could be monogamous and were drug free. Trust would be a huge issue as she says.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small she has a nice \textbf{pussy} and belly\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Remember the story in the bible   there were going  to  stone the young  \textbf{woman}  to death  and Jesus came told her go sin no  more  we all need to look at are own life.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small It's pretty simple, ladies:  It is completely humiliating to a normal, good man for you to be sleeping with so many guys, even if it is your profession.  It makes the person feel inadequate.  People don't decide what to feel, it happens to them.  An honorable man who would stay with you for the rest of your life, does not wish to have his dignity deprived by being embarrassed about how many other men are screwing you.  It's also not worth the financial risk of getting divorce.. or the health risk of catching a disease.  A real man, and a good man will always prefer monogamy.  Nightclub sociopaths can have the \textbf{promiscuous} women, and they usually deserve them.  The "Alpha" fucks and "Beta" bucks era is over.  If you choose to be \textbf{promiscuous}, it would be best you didn't get married or have children.\normalsize   & \cellcolor{green!27}Promiscuous & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}2/144 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small Kayden Kross and Manuel Ferrara got married and had a family so probably that works for pornstar to pornstar. The issue is when it's pornstar with other people. And I believe they don't care if their dignity get sullied because if they did, they won't be fucking in the internet for the world to see. It's on them. No surprise no man would want to date or marry them unless the person is just extremely thirsty for pornstar \textbf{pussy}.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small \@Unfazed Well, if they can do all that and still find happiness, then I am happy for them!  It definitely takes a different kind of person to be able to pull that off.  However, men are now privy to the fact of female manipulation of men for resources through \textbf{sexual} dimorphism..attempting the pragmatic approach of utilizing resources confiscated from less attractive males to finance their \textbf{sexual} pursuit of high testosterone males, based strictly on warrior traits.. traits that have absolutely no value in a civilized world.  Now we see meathead high testosterone males turned into primal entertainment by getting them to fight each other or play sports.  Meanwhile, they are relentlessly dominated by intellectuals.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/114 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small I can't even fathom why anyone would want to be in a relationship with any \textbf{sex} worker.  That's just gross\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small She wouldn't feel a normal dick inside her from a normal bloke , saggy \textbf{pussy} the size of a fist .\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small This is \textbf{nothing} but sad.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She's like any whore selling her body for few dollars! This selling dignity, and it's a \textbf{R\textbf{ED}} LIGHT that once it's scratched then it's not the same at all. A \textbf{woman}'s pride and virginity is like a match stick o ly burns once whi h is a husband! This \textbf{woman} is like any other pornstar who are at the bottom of dirt unless they repent (I don't mean being a fanatic in religion) but STOP that shit and believe that they are humen and worth respect.\normalsize   & \cellcolor{green!27}Red, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!27}3/86 & \cellcolor{green!27}3.488 \\  \hline
  \cellcolor{green!5}\small There is the..'you're a prostitute factor...' look at it anyway you want if you get paid to have \textbf{sex} your a \textbf{hooker}. How the fuck would she know what it takes to be in a relationship? Lmao!!!\normalsize   & \cellcolor{green!5}Hooker, Sex & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Plz make a video with \textbf{indian} dick\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small biggest Guilt or Sin is the Barefacedness or naked \textbf{woman} for other mans ,,,we are going totally for destruction\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small YEAH WHY DID YOUTUBE RECOMMEND ME THIS VIDEO? (: :) OH BECAUSE I'VE WATCHED PORN INTERVIEWS BEFORE THEY RECOMMENDED FOR ME.. OH HEY IT'S GREAT THEY GET THERE PUSSIES CHECKED EVERY 2 WEEKS FOR STDS \& MORE BUT HERES BUT THAT WON'T HELP PREVENT OR CURE THIS ... WELL 20 YEARS AGO I HEARD SEKA ANY PORN STARS \textbf{PUSSY}, PRIVATES, JUNK IS TOXIC WASTE MATERIAL \& IT'S SAD \& SIC AS A SAD SAC WHY? ANSWER: BECAUSE SO MANY PEOPLES JUNK HAVE BEEN IN THERE \textbf{PUSSY}, ASS, HOLES, WHATEVER \& SPEWED LOADS OF CUM IN THERE TOO OOH BOO BOO!!! HAHAHAHA!!!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}2/101 & \cellcolor{green!27}1.98 \\  \hline
  \cellcolor{green!5}\small All she has shown here is how shallow and hypocritical porn stars are. Seriously? They fuck multiple partners and justify it by saying, 'It's just a job. We are acting." but then say that they get jealous of OTHER porn stars with the same philosophy?? WTF.....Bunch of double standard hypocrites. Be alone all your life. \textbf{Nobody} in the real world wants you as a girlfriend or wife and your shallowness stops you from dating others who WOULD accept you.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small Well love to see chinese businessmen owning her ass let them rain her with more and more dollar notes... so much of chinese dicks up her ass she should so that bareback anal and vaginal penetration would be done what if shes drugged without her not knowin of it and become a victim of  hiv infected dicks and poor dear any of these poor souls been her dear fans here who are defensive of her by their verbal comments can do \textbf{nothing} to stop while shes in deathbed having her last breath not even her mommy or daddy or siblings or her relatives or friends can save and its goodbye forever baby girl...☹️\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/113 & \cellcolor{green!27}0.885 \\  \hline
  \cellcolor{green!5}\small Who is gonna marry this \textbf{woman}.? There are a lot of men have had inside her with different size of Penises . Even without protection . She can create a terrible disease to her future husband and children too.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Men are so full of shit.  They want a slut, but they wont marry one.  Total double standard. I don't know if I could have a lasting relationship with a performing porn star.  Only because I think there would be times of jealousy, on my part. Though I admit I wouldn't have an issue with it if she were very good at reassuring me of the solidity of our relationship, which I am sure would get \textbf{old} and burdensome. Personally, I would marry a retired porn star in a heartbeat. Imagine how willing she would be (hopefully) to doing pretty much anything you want to do. That would be hot!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small Sex can not be a good source of income; it cost your life!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That's what happens when you wanna be a \textbf{thot}, gotta live like this now lmao\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small It's not destructive to the performers or viewers you \textbf{dumb} fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Tech Mania LTD Well I believe Porn takes your innocence away. I was once a child that would have all the confidence in the world and run up to anybody to make a joke, it all changed once I started masturbating to Porn. I couldn't look at girls the same way, I couldn't concentrate in class, and I just felt extremely bored and depressed with my life. In fact everything I mentioned is still happening now. I started at 12 years \textbf{old}, I'm 15 now and just can't seem to stop.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small What do you mean? It's a normal job. Porn videos are just showing something that is natural, \textbf{nobody} should be ashamed of participating in them or watching them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@xBrandon 24 It actually is since they all have mental/emotional/relationship issues which this stupid slut is literally talking about, you \textbf{dumb} piece of shit. White knight harder cuck\normalsize   & \cellcolor{green!27}Cuck, Dumb & \cellcolor{green!27} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small one day she will be \textbf{old} and she ll be very sorry for what she had done in the past\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Shes very beautiful \& look young. Shes the only one so far that quit doing porn \& still look young \& beautiful. Everybody else that did porn looked really \textbf{old} \& you could tell they were hurting on the inside\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Many people has this notion that people working in the adult industry is broken, unhappy with their lives, take drugs, drink \textbf{alcohol}...etc but that is far from the truth. I have a friend who works in the adult industry and she is much happier than I will ever be. I am here with a dead end job, fuck up depressed life and she is out there enjoying every second of her life. I know for a fact that apart from smoking weed she doesn't do drugs and only drink occasionally. She is living while I am existing.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small \@angelo alonzo non of them do. their work is harder than what they earn. you can earn that much working at McDonalds doing \textbf{nothing}! the most famous of them get maybe 2-5000 dollars for each scene. this amount of money for this job is a joke. and they have no right to any scene they worked in. all the profits go to the companies. Yeah, it's the shittiest job with the least income. and if you see stats of it being one of the most profiting things, it all goes to companies, not the performers.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small Porn actors aren't special or \textbf{crazy}.  The ones I met living in Canoga Park drove catering trucks between jobs, or if they were famous they seldom left their houses.  Boring people, overall.  But there's a creep-factor in a guy who wants everyone to see him hard and cumming.  The women?  This girl goes on about massive dick-size, how big she takes them, but she rolls her eyes about a normal guy who's put off about it.  When girls are violated at young ages, they tend to only see themselves as valuable for \textbf{sex}, and experience confirms it.  They over-emphasize their sexuality and it's cliché to point it out, but porn is the 'Island of Broken Toys' for the sexually abused.  There's exceptions, and some \textbf{black} guys can't dance.\normalsize   & \cellcolor{green!5}Black, Crazy, Sex & \cellcolor{green!5}Ethnicity - Black, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/128 & \cellcolor{green!5}2.344 \\  \hline
  \cellcolor{green!27}\small Dating issues? Why? Your twat is like a massive \textbf{black} hole...when a penis crosses your slippy pussy's event horizon, it cannot escape. Why would you have any problems?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small A \textbf{woman} body can handle tons of dick, but it's the \textbf{mental} capacity that suffers, she have a hard time bonding with one man one day ..when she wants to settle down, it sad how she doesn't value  herself as a \textbf{woman}..\normalsize   & \cellcolor{green!5}Mental, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/42 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She needs to have her boyfriend OR girlfriend get tested? Wtf??? And why am I watching this? 😂😂😂😂 what you stumble upon is \textbf{crazy}! She has no self respect at all!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Crazy lady\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small "Dating is so bad...." That's true because most men are insecure about their \textbf{sexual} performance from a psychological perspective. They wouldn't want to date an expert whom they cannot please. Male sexuality is tied to our ego and to some extent our personal success. If we fail in the bedroom, it goes without saying that we will manifest these tendencies in other aspects of our lives unintentionally. My advise - find a fellow pornstar and get married.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small The porn industry sadly reels in young women like this with glitter and quick cash...a seemingly huge dose of "self-esteem" for a little bit of work. However, soon enough when the "next young thing" comes along young ladies like this who \textbf{age} like the rest of us are discarded like used rubbish. Uneducated, ripped of their sense of self-worth, they end up in life's dustbin...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small I dated a porn star once and she was out of the business when we met. She actually moved in with me very gorgeous. I own a funeral home which she never came to my business she wanted \textbf{nothing} to do with it. I was totally taken care of her. I was able to get her a job as cashier at a convenience store part time. Coming home was off the charts. She walked around in daisy dukes , or very skimpy lingerie. We had so much \textbf{sex}. She couldn't get pregnant because she messed herself up down there from all the guys she fucked, she did a lot of gang bangs and her reproductive system got fucked up and she had a hysterectomy at a young \textbf{age}. We stayed together for about 27months, and she started doing drugs , and she became violent at times. I had to let her go. She smashed my brand new SUV Mercedes and the insurance company gave me hell. Great \textbf{sex} probably the best I had in my life. But for my sanity, I got so I couldn't sleep because she would get my car keys while I was sleep go out and get high. Probably fuck and suck other guys. I was paranoid. My mother saw her one day with a bunch of unsavory characters in my car riding around. We were tight for about a year , we even talked about marriage, we on some great vacations. Guys were always starring at her she had a 10 body and 10 face. I haven't heard from her in about 5 yrs now.\normalsize   & \cellcolor{green!27}Age, Nothing, Sex & \cellcolor{green!27}Age - General, Age - Youngsters, Gender - General & \cellcolor{green!27}3/270 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small better than being a hooker\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small What I find amazing is women like her feel that they are entitled to a normal traditional relationship, this mindset for a \textbf{woman} in the biz (in my opinion) is beyond delusional. I would absolutely have fun with a porn actress but I would never date or make one my wife.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small With all that \textbf{sexual} experience but still sounds very young.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Porn stars have \textbf{mental} health problems. Period \textbf{nothing} wrong with that but being a porn star ducks u brain mind up after they stop.\normalsize   & \cellcolor{green!27}Mental, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Ohhh man it is hard to say but no way a \textbf{common} person would have a relationship with a porn star,  it is every man dream to fuck a porn star , but to have a serious relationship is tough... if you mary any girl she might have done the same thing the pornstar did but at least you didnt  see it. Now imagine you watching your wife films ...ashole fucking ,swallowing,  gangbanging, white and \textbf{black} guys with huge cocks entering her both holes,  all  these scenes in your mind  can delete any sing of love and besides you would never be confifent enough about your performance...\normalsize   & \cellcolor{green!5}Black, Common & \cellcolor{green!5}Ethnicity - Black, Social Class - Working class & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small If you like food and you are a chef of a 3 star restaurant. In the evening you make your homecooking. Or you can tail like a gynecologist all day in someone's \textbf{pussy}. I assume that a relationship with someone can suggest something like that. I think.If you sell intimacy, Or deal with cheaply it will become less valuable in the long run. What she is looking for is someone with whom she can maintain an emotional platonic relationship. Let's be realistic. The \textbf{common} orgasm and need for \textbf{sex} will be a lot less at home. Shifting people's lack of self-assurance what does that mean? Just think about that.\normalsize   & \cellcolor{green!27}Common, Sex, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese, Social Class - Working class & \cellcolor{green!27}3/110 & \cellcolor{green!27}2.727 \\  \hline
  \cellcolor{green!5}\small She does allot of \textbf{lesbian} porn and its obvious she prefers women. Fkn mixed up girl but moneys not a problem and I bet you she will never have kids and a steady relationship..\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Speak for yourself. Some of us like a girl with a \textbf{sexual} appetite.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Your insecurity is showing.....a \textbf{woman} has to 'look' a certain way for you to be comfortable, because if she's ugly, she won't cheat on you?  LOL....\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@aboctok Yea, if a \textbf{woman} is going to be having \textbf{sex} with other guys during the relationship, that's something that should be discussed beforehand and agreed upon.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small I bet girls are queueing up to feel "average" in your eyes! Can you imagine knowing your boyfriend respects you and likes you, but is not blown away with desire for you? It should be all of that! Newsflash, women don't get dressed up and make themselves look beautiful for men! They do it for themselves! They look in the mirror and think "damn i look good tonight!" They do it to feel their most attractive self! So they can head out the door feeling good about themselves! Bit of an anti climax when she meets her man and wants to see his desire for her reflected in his eyes, and instead gets "oh I'm so lucky to have such an average looking girl who no one else will want to bang!" Inner beauty, loyalty, faithfulness, kindness, etc etc are \textbf{nothing} to do with how beautiful a \textbf{woman} is on the outside! Being beautiful doesn't turn women into a cheating whore! Keep telling your women they are Miss Average, and it'll be those girls who are desperate for validation in the arms of another man! And we'd all be cheering them on! You got trust issues clearly!\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/197 & \cellcolor{green!5}1.015 \\  \hline
  \cellcolor{green!27}\small I can't take a pornstar serious when they says dating is a problem for them, they say men are insecure because she sucks cock for a living, of course, what guy wouldn't be pissed off knowing his girl is getting railed by other dudes? There's no relationship, \textbf{sex} objectifies women, changes your perspective on a relationship and love/bond.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small take about her calling the pot calling the kettle black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Brandon M The young blonde porn \textbf{chick} Elsa Jean revealed that's a natural progression of the industry for young white girls. First girl-on-girl, then same-race boy-on-girl vaginal, then interracial boy-on-girl vaginal, then anal and everything goes. I think somebody told me it progressed that way to maximize interest and hence views.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small WICKEDLEE LOOPY She's  just a nasty whore , plain and simple....Shes acts like she's so dignified because she trust the people that she has \textbf{sex} with on set\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@realradiant1 R Why don't she just request her boyfriend to wear condoms when they have \textbf{sex} with each other in case he court something from someone else?  \textbf{common} sense, but I guess I forgot women and pornstars don't have \textbf{common} sense.\normalsize   & \cellcolor{green!27}Common, Sex & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small \@Timmy Thistle even kissing could transmit the some of the hpv you know, oral \textbf{sex} , and kind of touching . so you have to wear a full body latex suit and wear a condom plus not kissing then you would be fine.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small "why don't she just use condom?"You do unprotected \textbf{sex} on work, and you tell your bf to use a condom? That'll raise a lot of arguments and lose respect or confidence from bf's side. In work, they do unprotected \textbf{sex} coz they know they are tested and they trust that result. How is it any different from trusting your bf to be honest too? Trust is the issue here, not the irony. You can't tell her in the face about irony when you enter that relationship with full knowledge with what her work is all about.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/97 & \cellcolor{green!27}2.062 \\  \hline
  \cellcolor{green!5}\small \@Michael James \textbf{Nothing} hard to understand here, just hypocrisy\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Why is that ironic? And are you insinuating that because someone does adult films, that makes them a cheater? Please be really \textbf{old} and on the way out.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Just show us your tits and \textbf{pussy}. That's what these type of women are good for anyway.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small So when she's dating a civilian and they get jealous that's annoying but when she's dating someone that's in the business they get jealous of each other and it's that's annoying to so you can f*** whoever you want but can't \textbf{nobody} else f*** \textbf{nobody} else\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Common sense , cheating is having \textbf{sex} with someone else so if your job is to have \textbf{sex} with multiple people your job is to cheat lol no shit a relationship wouldnt work lol\normalsize   & \cellcolor{green!5}Common, Sex & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small If you believe evolution shouldn't be a problem just have \textbf{sex} however it doesn't work cus it wasn't meant to work like that. God made them male and female and \textbf{sex} is for a husband and wife.Were all not perfect that's why we need a savior.To be saved believe on the Lord Jesus Christ and you will be saved he died in your place of your wrongs cus he loved you even when we rebelled and hated him. Read KJV bible to learn more if your just gonna respond hatfully to this comment I would say that's a waste of your spec of time. Hopefully someone will see I text this to reach the lost in love not hate.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/121 & \cellcolor{green!27}1.653 \\  \hline
  \cellcolor{green!5}\small What guy want's to date a whore?And YES, that's the definition of someone who has \textbf{sex} for \$\$\$, "A WHORE"\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Would you call an inexperienced mechanic to fix your car? Same with a \textbf{woman}.  Danni, I love you, please marry me.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I can't believe guys are insecure or maybe they don't want to have \textbf{sex} with her\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Hmm no wonder lot of men lost interest in \textbf{sex}...\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I want to \textbf{sex} Natasha malkova..I like the pron star..Malkova is so beautiful n sexy..Wesome..\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small its a shame and discusted for you tube for interviewing this porno .she.s not a role model for our kids..sad so lovely but so dirty inside. .cause of \textbf{woman} like this. it distroys families. what the hell they were thinking..!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Yeah, Uh huh, dig it.....why don't you take that ugly \textbf{r\textbf{ed}} dress off and show us that beautiful big butt\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small its sad ever she took this career she lost respect. So lovely but so dirty inside. she.s \textbf{nothing} but trash. only an idiot would wanna marry something like this. Well she was raised by a \textbf{lesbian} mother what do you expect. .All porno actors should die of aids. She really gives a bad name to all. i hope she reads this comment. someday. women.\normalsize   & \cellcolor{green!27}Lesbian, Nothing & \cellcolor{green!27}Age - Youngsters, Sexual Identity - Female homosexuality & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Noticed the Adams \textbf{apple} right away! It's a DRAG MAN BAM 🔥 🔥 Some of you are in a world of hurt 🔥 BAM 🔥\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small So that's why u guys joined the \textbf{terrorist} community 😂\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small why would you have to date? you get everything you need from your job,, what a gambling match profession,, i bet everyone i has \textbf{sex} with made responsible \textbf{sex} decisions all there life,, \textbf{sex} tester,, i bet you did not,,,\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/40 & \cellcolor{green!5}7.5 \\  \hline
  \cellcolor{green!27}\small WHAT YOU DO ISN'T OKAY SWEETHEART NO \textbf{WOMAN} WANTS TO BE A RECEPTACLE.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Getting tested. Obviously a lot more important for XXX actors. But really it should be important for "civilians" too. Does this mean it's more risky to have \textbf{sex} if you're not a XXX actor? Maybe. I think NOT. It's maybe MORE risky outside of the XXX biz as no one asks a potential mate to go get tested "...before we...". Relationship ending immediately..some getting offended. In the XXX biz it's "normal"...whether actors really get tested or get the "having been tested" paper faked. Which I bet happens with the smaller companies who don't send actors to a Dr they know.On the other hand, in the XXX biz, there are the larger known companies and the "3 man crew companies". Some are more strict about testing. At the same time they can fake the test results. Unless the test results are sent to the company by the Dr's office. Or unless they have an in-house doctor or nurse. Certified. Or if the company is close to a clinic or Dr's office.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/171 & \cellcolor{green!5}0.585 \\  \hline
  \cellcolor{green!27}\small What  a good   interview  with  more than  8 million  viewers. Most  like  to   know  this  because  it is  very interesting although  it  is  normal  thing  and \textbf{nothing} new.  What  say  you.  about   this.  What  is  absurd  about  \textbf{sex} because  it  is  normal  thing   is  life  and  it  is  essential  to human  being.  What is  so funny about  this.  Thnak  you.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Well, what makes 'Porn a problem' is the fact that Port is a terrific outlet for the Sexually-Frustrated and the lonely, which happens in everyone's life.  What is your solution to remove \textbf{sexual} frustration and loneliness from society?\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small There will come a time when pornography will be re-invented and stripped of all bullshit. Maybe monogamous couples having \textbf{sex} in front of camera or something like that. Until even the scenarios are disgusting: always something with (step)mothers, brothers, cheating husband, white husband whoring his white wife out to 5 \textbf{black} men, etc. etc. jesus christ.\normalsize   & \cellcolor{green!27}Black, Sex & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Get Married When U feel u need a partner. .. Stop This Fucking Pornography Shit...Its Destroying Peoples Lives...\textbf{Sex} is for having kids, Not For Just Fun...Don't Make Fun with what almighty has given us..\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small lol i know right? the comments don't at all mostly contain of 14 year \textbf{old} kids who play video games 12 hours a day \& 50 year \textbf{old} pedophiles who watched child porn after they watched this. totally a serious study\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small \@Michael James a lot of things can get your mind rid of those \textbf{Sexual} thing.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small You can't just stop watching it. Everyone that consumes porn has no right to be critical of it. It's ridiculous.\textbf{Sex} is good, porn is bad. Bc Porn portrays \textbf{sex} not realistically.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Mahidul Islam  You should never have \textbf{sex}.  It would be bad for you, and the camel wouldn't like it, either.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Es3iya when i do watch it, those are the videos that are more satisfying.  Now that normal couples can upload their stuff there's less \textbf{weird} and disgusting shit\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small What else are you supposed to do when no \textbf{woman} will fuck you though?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small No matter how many male \textbf{sex} partners you had you have and you would have I will keep on watching your porn videos because I mostly like your face than rest of your body so no matter how many men fucked you in the ass vagina and mouth I still like to glue to the screen when you're in it because I think I'm in love with you and would like to fuck you in the ears and nostrils because probably these are only holes left in you to penetrate  ecstatic isn't it😋😘😍😁😀like a wild ant I want to penetrate into you😘😍\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small George Lux you shouldn't live a life like this, it's completely self destructive, you must be \textbf{mental} if you enjoy this career to make your money get fucking real\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I feel sorry for you and your miserable life of \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small How could she expect to have a regular relationship with anyone with some sense because she's screwing someone else on a regular bases and getting paid for it. It's sad \textbf{NOBODY} in their right mind would be okay with it. If you want a regular relationship, get out of the freaking industry!!! 🤦🏾‍♀️\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small \@God's Daughter \textbf{Nobody} wants a dirty, nasty whore after they´re done with her. She ´s used up, now throw her away.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@ann l You´re being really, really stupid. She´s already had many stds, on average 4 per year. She´s also a \textbf{hooker} on the side. She´s just a used up \textbf{hooker} to be thrown away.\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Paige White Her eyes look sad because her mother sold her into \textbf{sex} slavery very young and laughs about it to her face today. Now let´s all have a pity party and let her get away with anything. YOU SOUND LIKE A BUNCH OF DIRTY FAGS!!!!!!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@Vania Hollis She´s a dirty, sperm guzzling \textbf{hooker}. Who cares what her mindset is?\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@AMIR NABI This bitch chose porn because she´s a nasty whore. She´s not a victim. You stupid captain save a \textbf{ho}. She´s a nasty \textbf{hooker} who accumulates diseases like it´s nobody´s business.\normalsize   & \cellcolor{green!27}Ho, Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small God you people sound like morons trying to seem like \textbf{doctors} lmao, you don't know her or how she's feeling\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small That was her choice \textbf{dumb} sluts\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@tk tk Stop being such a simp \textbf{pussy}. She´s a manipulative whore with more diseases than you can count.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@2011packattack Stop being such a \textbf{pussy}. She´s a lazy whore and \textbf{nobody} likes lazy whores. I bet she´s one manipulative  \textbf{hooker} too.\normalsize   & \cellcolor{green!27}Hooker, Nobody, pussy & \cellcolor{green!27}Age - Youngsters, Gender - Female sexuality, Nationality - Chinese & \cellcolor{green!27}3/22 & \cellcolor{green!27}13.636 \\  \hline
  \cellcolor{green!5}\small \@tk tk All I´m saying is that she is not an innocent \textbf{snowflake}. She is a predator.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small listen my friend,,is someone else responsible for her doing all this?if we want we can change the whole world then why not just our own lives?????I respect alllllllllll girls of all types but not prostitutes and pornstars.for me,, Every \textbf{woman} is an angel except these 2 categories of women.they DESERVE to be called "bitch"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small \@Lily Flower \textbf{nobody} asked your opinion but you gave it right... In the same way everyone can... That's what comment sections are for... The person in the video doesn't need to send you a fucking personal note to comment\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Most every one of them have at least one male from their immediate family still living - I can't think of a more disrespectful representation of myself, my family \& where we come from if my mom or sister chose that "career" choice. Pornstars are extremely selfish in that aspect \& there is \textbf{nothing} worse than a whore who could care less how her actions negatively affect her own family. Most of them are doing it to support their drug addiction anyways. It's a sad fact.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small I just have to say ... do thay take plain looking \textbf{woman}...im just a plain.. looking borning girl.. looking to see if.. LOL so funny\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@justin Haripersaud im 41 years \textbf{old}.. lol.. you sound young\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small So 2yrs after this clip she got hitched to a dude 30yrs her \textbf{senior}? He's the side piece\normalsize   & \cellcolor{green!5}Senior & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Thank God I have \textbf{nothing} in \textbf{common} with any of you.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Nothing els jirr gents\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small imagine being the child of a famous pornstar. knowing all your friends and their fathers probably saw and jerked off to yo mom naked and \textbf{sex} videos. oh the horror\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Easy come easy go after few years she will be \textbf{old} and no one want to see her\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small she love big \textbf{black} cocks\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small It disgusts me that men see women as products. So you have \textbf{sex} with her that makes her damaged? What about you? If a guy has \textbf{sex} with a ton of women is he a "used product"? People are not objects.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small 0:55 'I'm totally compassionate', yeah right🙄She has no clue about a guys concern that they can't 'measure up'. She's complaining about no dating options?Tough shit- that's the trade off. Lotsa hard core \textbf{sex} vs no love. Bitch👿🖕🏼\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Sex workers are working people just like you who are literally doing their jobs yet you continue to stigmatize them while you are the consumer who fills the demand for it in the first place.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Oh my God stop trying to make it seem like it's 'just another job' imagine telling young girls that where this society would go lmao u might as well promote having \textbf{sex} on the street bc 'it's just another person performing an action mind ur own business' blah blah blah PLZ\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small You have a \textbf{blind} eye. Pornstars do not have jobs like you or me. It is not a job. The demand is gone when she reaches a certain \textbf{age}.\normalsize   & \cellcolor{green!5}Age, Blind & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Dillon Callaway how \textbf{dumb} are your comments.....seems you're the one consuming it. You don't have to admit it, just by you defending it tells all.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small What the fuck is that pedo comment here for? Sicne when should a dad be upset that his daughter is \textbf{sexual}? Ur gross\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Deliberately Loving - Goddess of Heart no he should be upset because she's a cum dumpster. \textbf{Nothing} else. She got More bodies than Hiroshima and Nagasaki\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Nobody use a used condom\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Brady Pentecost ‘When a fool speaks and thinks he's wise, there's \textbf{nothing} left to say.'\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Dark Heart the funny thing is you jump into something that has \textbf{nothing} to do with you and lead off with a insult! But where is your picture  you don't have one? I never said I was attractive but I think the bigger point is maybe you are not attractive and just trying to make yourself feel better. I hope you can find happiness in yourself someday!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Dani Daniels i love ur \textbf{sex} video\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Porn stars are not stars. They are \textbf{nothing} more than prostitutes, \textbf{sex} for money plain and simple.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Imagine a \textbf{woman} feeling some type of way about her "civilian" bf not being okay with her fucking other people but having an issue with her "performer" bf fucking other people. This is how women rationalize things fellas. It's okay when she does it because it's her job. This "logic" doesn't apply when her performer bf does it though\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Beautiful \textbf{woman} I date u doesn't matter me\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small she sounds like a loser stupid f**** b** no wonder why she can't have a decent man in her life look at what she does seriously \textbf{dumb} b**\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Sex outside marriage is a sin.... therefore pornstar is not just a job.... its a job thats destined u to hell.... just saying....\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Mike Newton I have very high standards, I assure you. Most of you don't get that the manner in which you judge this lady, and probably most women, is completely corrupt and full of nonsense. You just don't get that the act of having \textbf{sex}, with a lot of people, or a few, is not by itself an accurate measure of anyone's character. A guy would have to be a fool to pass up knowing a girl like Dani just because she knows her way around the bedroom more than you do. I have a strong feeling all these triggered dudes out there being all holier-thsn-thou are just trying to coverup their fragile egos.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/114 & \cellcolor{green!27}0.877 \\  \hline
  \cellcolor{green!5}\small So literally someone have extend true love these whores(so we call them)  if we could seek to help love people, money will not make them end up in some adult \textbf{sex} industry.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I can marry a pornstar. Everybody have \textbf{sex} with so many people but not in public. Pornstars have guts to do it in public. They are more brave partners. And a lot of benefits I can think of. All u people will keep on commenting for no reason. U all gonna die one day. I treat people like walking deads. Fuck u all. Ty:)\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small Why YouTube recommended this video I don't understand??Porn kills.A lot of \textbf{sexual} demonic spirits are transferred from one body to another.It will kill you spiritually, physically and emotionally.I don't understand the joke? It's destroying innocent lives.Q: Ever wonder what happens after you die or doesn't it really matter?It is not right in God's eyes.He detests it!Ps. Open your eyes I pray.Proverbs 9:10 (KJV)10 The fear of the Lord is the beginning of wisdom: and the knowledge of the holy is understanding.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Tramp\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small with all your respect . .lets end these talking and do some anal \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small That perfectly summarizes the mentality of young women these days.That reminds me of the girl who didn't like her boyfriend pressuring her to have \textbf{sex} because they weren't quite "there" yet. So, just to piss him off, she went and lost her virginity to some random arsehole. This is how LOGIC works in the minds of these women.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Michael Moretti dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small With this very same mindset people become \textbf{terrorist} and criminals. Are you defending this??\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Industry propaganda. They are not happy and bubbly like the act they put on for this interview. No \textbf{woman} with a healthy upbringing would ever do this. It's a coping mechanism for psychological trauma and a dysfunctional childhood. The drug addiction and suicide rate among them speaks for itself. Watching porn is also psychologically damaging to the individual as well as to society. Masturbation is an addiction. It's a waste of time at best. Time that could be spent in the gym or bettering yourself any other way, in order to attract a desirable \textbf{woman}. At worst, it desensitizes you to the point that vanilla \textbf{sex} becomes boring, and you require more degenerate stimuli.Porn exploits performers and viewers alike.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/120 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@echelon2k8 It's not about being religious; it's about having a moral compass. Pornography is extremely negative in many ways, both physically as well as mentally. \textbf{Nothing} to do with religion, it just so happens that religion and having a moral compass agree with each other.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small \@echelon2k8 a moral compass is what a religious and a properly raised nonreligious individual have in \textbf{common}. Neither will defend pornography. They'll actually be in very close agreement; regardless of one believing in a God and the other not\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@echelon2k8 You're ignoring my point. All I'm saying is that you don't need to be a \textbf{Bible Thumper} to have serious issues with what the pornography industry is doing and promoting. I'm not staying anything more, and not anything less\normalsize   & \cellcolor{green!27}Bible thumper & \cellcolor{green!27}Religious Identity - Christian & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@A Hofer  What are they doing and promoting that you have serious issues with? You have a problem with consenting adults being payed to have \textbf{sex} with each other on film to be shown as entertainment for other consenting adults? Do you feel the same about what Hollywood does with its actors?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small \@echelon2k8 Pornography isn't real. Anybody who is married and has kids will know that. Not to mention the negative health issues resulting to the actors. Most, if not all are lured and blackmailed into the industry. \textbf{Nothing} is natural about it. The girls get lured in and can't leave. It's a sad situation.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small \@A Hofer Of course porn isn't real; it's entertainment, just like the movies. There are potential negative health issues for anyone who is having \textbf{sex}. People in the porn industry typically get tested for these much more regularly than those who aren't, so people in porn are actually more likely to get a negative health issue from having \textbf{sex} with people outside of the industry than they are with those inside of it. "Most, if not all are lured and blackmailed into the industry." "The girls get lured in and can't leave." And I'm guessing you have actual evidence for these claims?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@echelon2k8 There's alot of evidence of Blackmail. Why else do you think girls would let themselves get into the situations? The industry is getting more and more degrading towards women..it's drugs that keeps them in it. No sane person would put up with it.STD's are tested for on a regular basis...but guess by who: very few \textbf{doctors} check these actors. They're all part of the industry. They're all paid to keep the business running, it's sickening.\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small \@A Hofer  People (girls) get into porn for a number of reasons. It's a job that can pay them good money, for one. There's a demand for them. If they want that money, they might want to try porn to see what they can get. They don't have to do porn to get money, sure, no one is forcing them, but believe it or not some actually want and like doing porn for money. A lot of people who get into porn actually like what they do, even if people like you might not. "The industry is getting more and more degrading towards women" That's a pretty blanket statement. What are you basing this on exactly? "STD's are tested for on a regular basis...but guess by who: very few \textbf{doctors} check these actors. They're all part of the industry. They're all paid to keep the business running, it's sickening."And yet they have a very good track record of keeping performers safe. Serious incidences these days are rare.\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/168 & \cellcolor{green!5}0.595 \\  \hline
  \cellcolor{green!27}\small \@wzяđ hello and thank you for Your good feelings !!!We muslims believe in jesus christ as a great holy prophet \& we respect him \& love him We believe that his mother holy Mariam is a saint  \& blessed \textbf{woman} ...but they are not gods There is one and only one god He didnt give birth neither he did Borned ..excuse me for my poor English ..with best regards\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small \@Allah Motherfucker teri aukat hi yahi hai bete ki har jagah muh se hugne aa jate ho\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I'd certainly date Dani and would have no problem with what she does for a living or the testing issues  . At first I just  thought she is one very attractive and sexy looking \textbf{woman}  . After this interview I find her very down to earth  , pleasant , intelligent and personable  .\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small I love how people will always judge you if you don't conform to their views and way of thinking. It just f**ks with them. They can't stand to see you doing your thing. It's the people that are most insecure and most bitter about their life choices that feel the need to vocalize distain for the choices made by others. People that are happy with their life don't feel the need to bring others down. Just live your life and don't worry about how others choose to live. \textbf{Nobody} is imposing any views on you why should you on them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small It's a pretty demeaning job.  The kind of job u take when u don't have a choice. When it's time to date, u go get another job. A \textbf{woman} should be conscious of her ticking body time Clock,  as well as being a good example to her future kids\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small The idea that a \textbf{woman} could start working in the p*** industry at 18 and make enough money to retire for life at the \textbf{age} of 30 must be an awesome burden.\normalsize   & \cellcolor{green!5}Age, Woman & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small 😂😂😂😂Omg really what do u expect how is a good guy supposed to feel about being with a gal who automatically still has \textbf{sex} with others u killed ur own dating life for that business have a nice day\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small BEGONE THOT\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Did she just say that her guy can't cheat on her while she takes huge cocks in her ass daily? That \textbf{Ho} is high as fuck.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Dani I 🤔 I think after you had lot of fucking \textbf{sex} your vagina skin might be curly and \textbf{black} shady 🤣🤣🤣🤣\normalsize   & \cellcolor{green!5}Black, Sex & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Nothing gonna happen after death\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small No one wants to date a prostitute. Call it a profession or 'actors' but they're prostitutes. They take money for \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small man hands, \textbf{jerry} seinfeld was right\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small judgmental pricks on this board........a porn star contributes more to society as a whole by providing \textbf{sexual} relief in one year  than any of you doing your socially acceptable and meaningless paper pushing jobs would in your whole life.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small A sad shame to hear this girl talking about her body and \textbf{sex} as though she were a dude, and a really degenerate dude at that.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small She's actually human...I thought she was just a de-humanized \textbf{sex} object\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Has \textbf{nothing} to do with dick sizes. Just \textbf{nobody} wants a relationship with a hoe, and some guys might be down to fuck for a few times but average men would probably be disgusted or scared of catching something. For me personally, I wouldn't pass on this opportunity;) However, I would never be down for a relationship with a pornstar nuh uh.\normalsize   & \cellcolor{green!27}Nobody, Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Honestly speaking I would never date a \textbf{woman} who's nakedness is all of the internet \textbf{nothing} against them but it's ridiculous.\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small BBeBegBegoBegonBegoneBegone TBegone ThBegone ThoBegone \textbf{Thot}Begone ThoBegone ThBegone TBegoneBegon BegoBegBeB\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I watch you having \textbf{sex} on camera but I don't jerk off , I just watch for hours and secretly know what excites you the most is bondage and domination and being treated rough like shit.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Maybe guys are uncomfortable about dating pornstars because pornstars by definition do not find intimacy in \textbf{sex}.  \textbf{Sex} used to be called making love and for some people it still is.  You can't share that intimacy with someone when you know she/he is sharing it with that many strangers.  It loses its value.  Maybe for some men they can do that, but I bet all of her frustration comes from the reality that most men cannot handle that.  And who the fuck should?  We evolved to have \textbf{sex} in a way where emotional personal connections are a by product of the \textbf{sex}; we cannot separate the emotional side of \textbf{sex} in the same way that the incredibly minute percentage of people like pornstars can.  AKA jealousy exists lmao big surprise..\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/130 & \cellcolor{green!27}2.308 \\  \hline
  \cellcolor{green!5}\small Dont you love how people glorify themselves, they call themselves performers or sometimes actors, please give me a break, where i come from which is 'planet earth', people who get paid to have \textbf{sex} are prostitutes.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@Guzzman 65 ...well then, maybe she's waiting on Christ to forgive her!...you stupid f*** you!! Morality doesn't have to do with \textbf{SEX} alone. The set of JAG-OFFS who lied about WEAPONS OF MASS DESTRUCTION just to start a War, are more MORALLY reprehensible than a \textbf{woman} selling her body!!...If YOU don' t understand that, you need help my friend!!\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small I can't image any decent man would be OK with his wife or girlfriend having \textbf{sex} on film with other men.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@PrinceUchie ...another nit-wit. Your brother, half-wit, is 'ass'-erting that "a \textbf{woman} selling her body...i.e. a prostitute is the most immoral thing in the World!... and i have given an example of so called "decent human beings" ...i.e Dick Cheney et al, ...being MUCH MORE immoral than a "coochie seller". Not for once was I in support of stars...or the porn industry. He alluded that porn stars are BEASTS ...not human... and I simply asked if a whore is not human, was it true then to say the Christ "healed a beast?". Maybe YOU can help your "BRO" and answer it for him!!...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small They're porn stalks not stars! Dig a hole in the ground then select any dry cornstalk and ram it in! When you pull it out the hole is the same but deeper. \textbf{Nothing} more, Keith. Would you dare introduce that thing to your mother and your most intimate friends?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small One word: Hasan piker\normalsize   & \cellcolor{green!27}Piker & \cellcolor{green!27}Nationality - Irish & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@kirkland sewell I strongly believe you are the one who needs a \textbf{mental} help. 😊\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Christina Ronaldo ...lol...Chrissy, Did I disturb your "conscience"?... Btw can you answer this question for me?...Is there a difference between a prostitute and a \textbf{woman} having \textbf{sex} with a man for 'BENEFITS'?...\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Paul King They already dehumanize themselves you stupid fuck. She's a whore, she's meant to be fucked and jacked off to, \textbf{nothing} else, and will never be treated with respect because even just the way she talks and the vulgarity she spews verbally is enough to not respect her. Respect is earned and she's done \textbf{nothing} to earn it. She's just a whore\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small porn star ?? she is a whore ...its simple and easy ...there are male whores as well( \textbf{gender} equality right there ) ...and yes dude nornal sanr minded people wont like to date a whore let alone wed and start with a one and those who are doing it are either just plain stupid or are not in love with you they are just there for \textbf{sex}.\normalsize   & \cellcolor{green!27}Gender, Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small You're a glorified \textbf{hooker}, get over yourself.\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Well or people just not interested be in a relationship with someone that having \textbf{sex} with different people all the time. I mean how do you justified cheating then? Love is physical and spiritual and I just don't understand how could anyone open to the other partner having \textbf{sex} with other people. What's the measurement of cheating then? I mean you can fuck someone but not go out and having dinner? Is that how it work?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/76 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Disgusting \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I don't know why some \textbf{pigs} are appreciating her work If I ever found her alone I would put a bullet in her stupid face\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Zip it you \textbf{dumb} perverted pig. No respectable person will ever marry you.\normalsize   & \cellcolor{green!5}Dumb, Zip & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Imagine how lose her  \textbf{pussy} is probably like a paper bag\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Same, I love this woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small picsupmic She doesn't here and I'm guessing she doesn't act a dead steak in her porn clips either (can't check as this is my work computer). For me \textbf{sexual} satisfaction depends a lot on knowing or (at least imagining) that a person full of caution and concern has nevertheless decided to trust me and let me play with their body. Good erotica uses this. Very often, though, the behaviour is unrealistic and that doesn't get me.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small To be fair she does. In her videos men use her any way they want.The fact you see \textbf{nothing} wrong with this shows you have a very low opinion of women.They aren't something just to serve a man\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Better learn to hold onto your mic ... "The fact you see \textbf{nothing} wrong with this" is not a fact. I haven't watched her. I don't like or watch objectifying hardcore porn. I explained my preferences in my last post. When I see a \textbf{woman} performing a blow-job, I still see a sensitive person, not a cum hoover. If she looks unhappy that makes me feel bad for her. To get aroused, I need to believe the \textbf{woman} is enjoying herself. So I generally prefer softcore erotica and have taken up erotic writing to create the stories I can't find online.If Dani Daniels encourages dehumanization of women through her work then I'm not a fan of that. Nor would I follow the encouragement. Still, it's her choice and I respect that choice even if I would choose differently in her place. But consider that she might not be out to objectify herself at all. It's not always easy to tell from a video whether the person wants to be seen as a person.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/174 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small \@\textbf{paddy} Mcgarren: that's true. I don't know her life story but I wonder what made her opt for porn.\normalsize   & \cellcolor{green!5}Paddy & \cellcolor{green!5}Nationality - Irish & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@tempest411 Yeah but she be sucking a guys dick while you at work nigga\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small She not even fuck material anymore..I find it a serious turn off hooking up with someone who has pretty much \textbf{zero} respect for her body that she will fuck anyone for money fucking sad..\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@Molybdaenmornell Look man, i agree that is her choice, but i dont agree with her not objectifying herself because thats not what comes through in the videos she partakes in.Since she has made no effort to take down those videos where she is sexually violated in a dehumanizing way that seems to only serve a man's \textbf{sexual} appetite, then its pretty safe to assume that she does not respect herself enough to NOT be objectified. So yes, this \textbf{woman} has issues and of course she's gunna smile through it. No one hires someone who's going to be depressed or talks ill about their work.\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small \@Molybdaenmornell I am not saying she deserves to be dehumanized. Not at all, but this \textbf{woman} has emotional and \textbf{mental} issues and shouldn't be surprised when people don't respect her when she doesnt respect herself.\normalsize   & \cellcolor{green!5}Mental, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Glasgow Blues You view \textbf{sex} as something women do to please men only...? I get that there are porn where women are used by men, and those women don't enjoy it really. But sometimes it's just two people using each other and having fun.  As long as the \textbf{woman} enjoys it, I don't see a problem wit it. There are genres where men are used by women. Or where women sleep with other women. I guess those genres are fine with you?  A \textbf{woman} giving a man a blowbob is not exactly a „slave being used' since it's a part of \textbf{sex}, just as a man is not a slave for pleasing a \textbf{woman}. As long as both enjoy it, it's \textbf{nothing} like that. I don't watch videos where women are treated like shit and used by men for the pleasure of those men only.\normalsize   & \cellcolor{green!27}Nothing, Sex, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}6/145 & \cellcolor{green!27}4.138 \\  \hline
  \cellcolor{green!5}\small JMalik Lewis What is or with dudes like you who watch porn but get so triggered when they hear women doing porn. It doesn't make sense. You either think \textbf{sex} is evil or you are a hypocrite. So you never watch porn. Great. If you fuck around, I still will view you as an actual person even though I won't agree with it. \textbf{Sex} alone doesn't make someone „less than fuck material' nor does it make women or men less of a human being. You guys are weirdos.I agree that having \textbf{sex} in private isn't the same, and I agree that a lot of porn stars are damaged, the men and women. But it's to much of a pseudo shock to act so anti porn when in fact most of you did watch it. I do view porn stars as people, bc it's pretty stupid to act so damn triggered about someone fucking in front of a camera when you did  or do consume it\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/166 & \cellcolor{green!5}1.807 \\  \hline
  \cellcolor{green!27}\small Having \textbf{sex} isn't bad. And if you can get money from having \textbf{sex} it, why not? It doesn't make you a bad or disgusting person. You guys need to chill.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small "makes guys feel insecure"  No Dani, that has absolutely \textbf{nothing} to do with it, the only reason some people have problems with dating or being together with a pornstar is because they see \textbf{sex} from a different perspective, something you do with someone you love and only share with someone you love to name a few of the many reasons some people don't want to be with a pornstar, and on top of that, a pornstar, generally, I would guess at least, has a completely different view on the matter and both of you end up with different goals in life anyway so personally I could never consider dating a pornstar, maybe if they quit long before we meet, MAYBE, that doesnt mean I consider pornstars to be anything else than a normal human being with a different perspective on life.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/141 & \cellcolor{green!5}1.418 \\  \hline
  \cellcolor{green!27}\small the ammount of contradictions is rediculous... dating a civilian is considered annoying for various reasons according to her on being the jealousy factor and thats not ok for the civilian to be jealous BUT its ok for her to be jealous of a performer fucking other people on set in a professional setting,,,,hmmm,,,,  Worried about cheating on her when her job is to literally cheat on him/her EVERYDAY lol its just obsurd. Dating for her doesnt happen because she doesnt allow it to happen, its one sided and THATS why it doesnt happen has \textbf{nothing} to do with similar goals, its literally only going to happen if the person just bows down to everything she wants and thats the end of that story.,\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small Her \textbf{pussy} ain't ''broken'' like some in the industry ,just watched it. Her eyes are beautifull ,smile , DAT ASS . She is hot, superhot no , but hot. So fk yea, i would date her ,as would you. This is a video 'bout dating and how hard is it for pornstars .  Don't know why this video was on my yt but anyway i found out bout a new pornstar . To bad her videos aint that gr8 ,she worked with aloooot of pornstars , maybe its just me shes not my style , she just dosent have that ''fuck me motherfucker'' face . Meh to each his own\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/110 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small Pornstars Get makeup. Like any other \textbf{woman}, too. What`s the problem?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I don't think it has to do with insecurity, but it has more to do with the fact that you sleep with so many men and think it's not a big deal... That itself is already a \textbf{r\textbf{ed}} flag to a lot of people. Most people prefer monogamy relationship, not their partner having \textbf{sex} with everyone at work. Some people are more traditional and believe that intercourse should be reserved only to your spouse or partner, not something you do casually and think it's like drinking water on a daily basis. There needs to be loyalty and faithfulness to your partner when it comes to relationship, where your body and soul is only reserved to the person you are married or in a relationship with. That's what makes it special. Otherwise, why bother even dating or marrying at all? Just sleep with anyone you like.\normalsize   & \cellcolor{green!5}Red, Sex & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}3/145 & \cellcolor{green!5}2.069 \\  \hline
  \cellcolor{green!27}\small crazy bitch, keep saying things that you did urself, ruin ur life.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She's a whore. Whores are not relationship material. \textbf{Nobody} in their right mind would date one. If you're a whore then it's who and what you are, by choice.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small You're a whore. It doesn't matter if you call yourself "performer". You get paid for \textbf{sex}. No guy wants to date a whore. I mean they want to bang them yeah.... not date them.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small she seems to be the type of person that would be difficult to be in a relationship, porn star or not. She seems high strung and pedantic and given to drama. I would date a porn star, but not this \textbf{chick}. I have had my share of drama queens and control freaks.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small So 'civilians' she dates can get jealous and insecure, and when she dates 'performers' there is STILL jealousy and insecurities on BOTH sides. Just a thought, but maybe it's like, the porn industry that's the problem here? Get a proper job you \textbf{dumb} whore.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I'm not pointing finger at her choice of work. But I do say that it would be extremely difficult, if not impossible, to date her. Simply because when you date someone you'd think that they're only with you intimately, just as you are with them but in that line of job that won't happen. Your date is intimately with many others, it's all open to everyone to see on Internet, you need to test yourself because you can't be 100 sure that one of her "co-workers" didn't get something which now she has too. And of course the jealousy, that's a natural part of life. I don't mean going \textbf{crazy} over it, that's stupid but also can't really go on if you know that your partner is "doing it" with others on a daily basis, job or no job. No matter how you look at it, you still feel bad and cheated on.So yeah, if she likes that job and wants to do it then go ahead, not saying anything about that. But it is true, dating life is pretty much impossible, unless she'd date someone from totally different country where she may not be perhaps known as well (which in the time of Internet may be impossible), and of course would not be in that business anymore. There would still be always the chanced that at some point, someone around her would say "hey, aren't you that person on Internet in that porn movie?" and, as it usually is, go around and sharing the news with everyone, of course. And like she said, even dating someone inside the industry can still cause issues with jealousy and health and so on. So yeah, definitely not an easy thing to do.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/291 & \cellcolor{green!5}0.344 \\  \hline
  \cellcolor{green!27}\small Penis size insecurity is why guys don't date pornstars ?!? Hahahahha Well, keep saying that if that makes you feel better..Pornstars (getting money for \textbf{sex})  = Whores (getting money for \textbf{sex})\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Just get another job if it so damn hard ... \textbf{Nobody} put a gun to your head and forced you to become a porn star ... Either be a porn star or have a happy family, you can't have both ...\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I'm sorry but my cock size has \textbf{nothing} to do with the failure of a relationship. It's the thought of what you do for a living and you wanting me to be okay with it. If other fellas are ok with it then hey more power to you. I just find it hard for me to accept it because it's not a normal thing. Hope she finds someone who will accept her for her though.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small eARN MONEY with \textbf{SEX} omegaLUL\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small i would marry her, if she is a nice person. \textbf{sex} must be amazing :D of course, and besides, she is a millionaire :D what else u want   on second thought, i cannot imagine her having trouble finding a man. but iffffff u still have trouble, Dani, just if..... consider dating me :DDD\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small I couldnt have a pornstar as a gf..dude your licking that \textbf{pussy} which was full of cum from a guy the day before\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Yeah star, simple whore \textbf{nothing} special.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small so it's NOT alright for the guy to be jealous because you suck every dick they push in your face he just needs to accept you being fucked by 365 dicks (at least) in a year but it's alright for you to get jealous ? stupid ass \textbf{dumb} bitches with their double standarts.. gtfoh\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Here's the issue I have...She comes across as well hinged and logical about the whole thing. It kind of seems like she is disappointed a normal relationship doesn't work out. And I totally respect that she treats working in porn as a legitimate and normal line of work. All good.But for your average human being (whether they choose to admit this or not) \textbf{sex} is an emotionally bonding experience. The part of your brain that the feel good chemicals hit (oxytocin) are also the same area that correlate to attachment and feeling of deep connection.When you're screwing lots of guys (one way or another) you are devaluing the uniqueness that most people feel about bonding. Once again whether most people choose to admit this or not, not everyone feels comfortable opening them selves up to anyone for this experience.Its easy to say well "alot of guys go out to bars and sleep with lots of women", yeah sure. But the misconception here is that this is the norm. People who operate in these circles will have you believe this, but its not what most people want (by a landslide majority). Its the same as saying all women want is a big dick. Not the case!In a normal world, if you have a partner who asks you for constant std tests, well.... thats not a relationship. Trust being the key component.This \textbf{woman}'s POV on how she would like her life to be makes her come across as delusional to the point of psychopathic.I get feminism, I fully support it. But sometimes some individuals mistake it for some sort of area where the \textbf{woman} has created this PINNACLE situation where the term "Have your cake and eat it" has never been more relevant.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/298 & \cellcolor{green!27}0.671 \\  \hline
  \cellcolor{green!5}\small She needs to marry a rich man who doesn't care what other people think and is proud to be married to such a hot \textbf{woman}.  Now I just need to win the lottery.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Sounds like I'd be damn near perfect to date a porn star. I wouldn't mind if my partner fucks other people, even outside of work, and cheating just isn't in me. I wouldn't even mind if she loves other people. To me that doesn't reduce what we have. I'd still get to have great \textbf{sex} and make a life with a gorgeous \textbf{woman}. We could always get STD tested together and go out on a date immediately after, y'know. I also get lots of vacation days and do part of my work at home while still earning a full and steady paycheck, so we would get to see each other plenty. She should've spoken more about her goals, perhaps SHE would've gotten lucky :D\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/124 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small I don't give a fuck about my penis being smaller or whatever. No sane man would wanna have a longterm relationship and start a family with a fucking pornstar :S..... Even if she was out of the business it would still be a HUGE \textbf{r\textbf{ed}} flag.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April Congrats on completing Psychology 101.How about you spending more time assessing your own adherent \textbf{mental} health instead of playing shrink on strangers.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Dr O'Boogie Do you also feel the same way about the OP "playing shrink on strangers"? :PI completed a psychology degree with second-upper Honours actually, not just 101.What makes you think I don't pay attention to my own \textbf{mental} health? Do you? :)\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@Daniel Snyder What makes you feel that way about \textbf{sex} workers? What do you think the scientific and public health literature says about what will or will not protect their health and human rights? :)\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Alwyn April Wow... Looks like my comment has been deleted... Yep, Fightthenewdrug may be managed by Mormons, I thought about that, I am not part of this religious group myself and don't agree with some of their practices but I do agree porn kills love and change our fantasies and \textbf{sexual} behaviour. One interesting Tedx talk about this if you feel curious:  [LINK]   Also, you may want to read Raffaella Anderson's autobiography "Hard", it was written in French but it may have been translated. And also listen to some ex-porn stars about why they quit, "Redhead Redemption" talks about it on Youtube for example. Have you watched Rashida Jones' documentary?\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/110 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small \@Daniel Snyder   Even a Prostitute has 1000x more self respect than these Low-lives!   Example: 38 years ago a bunch of us went out and passed by a Slum in Manhattan where Hookers hung out.  One of the guys wanted a Blow. The \textbf{Hooker} refused to give it to him unless ALL the rest of us got out of the car!   These people fuck in front of others!  Many times in front of Audiences!  The whole world watches them!  They're No better than a Dog that shuts in public on the street!  They're totally detached from any decency and morality!!  Just listen to how freely She talks about How many Huge Penis's she's had.  As though it's Candy!!   A pure fucking Shameless Slut!!  Where are her parents?  Who raised these people??\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/130 & \cellcolor{green!27}0.769 \\  \hline
  \cellcolor{green!5}\small \@Alwyn April Well, I can imagine some do "feel" this way. I just seriously question the reason(s) why people "choose" to sell their body for money. I have a hard time to believe it is a childhood dream to have \textbf{sex} with strangers for money without emotional implication and intimacy, so if it is not then it is a conditioning, and I tend to hear from all the \textbf{sex} workers from all places in the world that they either got abused before entering the industry or that they lacked attention, love and affection and developed serious self-esteem issues. At the same time I do understand that some people see \textbf{sex} differently than others and I do believe ALL people deserve respect and care. Which is precisely why I question the well-being and health of the sew workers because it is dangerous not only for the body but for the heart and the spirit, of course if you don't believe in spirit in people you may think I serve you spiritual bullshit and that's ok, that's your belief. I mean really who wants to get sodomized almost everyday for years?!... By huge "things"? In front of a camera? And say it's what they really want? Do you know how they "prepare" and deal with this on sets? I encourage you to research it, it is gross.... Not to mention the anal issues that come with a regular practice on the long term... And what is the percentage of sew workers who have a happy and nourishing LOVE life? You can listent to Bree Olsen's interview who cries because she feels so rejected and judged all the time because people just see her as a whore... Now again, I personally respect her like any other living creature on this planet, no matter what they did. As I believe judging is makig the world the hellhole it has become... Yet, I cannot believe social death NOR glorification is the way to treat \textbf{sex} workers. People with a super high libido can go to private clubs, do orgies, meet \textbf{sex} partners on the internet.... But as soon as money is involved PLUS regarding porn workers, the abandonment of ones image rights for life, I just cannot believe it is making them happy on the long run. And again all the interviews, articles, research I have read or listened to reveal the obvious sadness behind the bright white smiles and make-up, or the incoherence in the speech when they just say it is fun to get gang-banged. How can a human being live its whole life without experiencing deep intimacy with another human being? Care, affection, love, tenderness, laughter, caresses, do you see this often in porn? And by the way, have you checked the other sources I mentioned? I didn't only talked about fightthenewdrug...! Have you?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}5/472 & \cellcolor{green!5}1.059 \\  \hline
  \cellcolor{green!27}\small \@David Topchiev What makes you feel that they have no decency or morality just because they have \textbf{sex} for others to see?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Leihita Danse Do you feel the same way about construction workers, factory workers, etc., "selling their bodies" for money, and all the exploitation, abuse, and violence they may face when they work in conditions that do not protect their health and human rights? Can you imagine having a childhood dream to work long hours for little pay and no workplace benefits or protections, regardless of the job? Just because some people get exploited in the industry or do not like their job, does that mean the industry itself should not exist?If you cannot personally believe or imagine yourself feeling or doing something, does that mean that other people cannot? Or does it rather speak to your own lack of imagination or perhaps relevant knowledge and experience?If you only listen to one side of the story, of course you will develop only a one-sided view of the reality. What do the \textbf{sex} workers who advocate for themselves actually say?I work in public health in my day job and have conducted research into \textbf{sex} work, volunteer with a \textbf{sex} workers rights organisation in my country and regularly interact with many different kinds of \textbf{sex} workers, and have engaged in \textbf{sex} work myself on a few occasions. Would it surprise you if I told you that many \textbf{sex} workers do not fit the negative stereotypes you have described above?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}6/229 & \cellcolor{green!5}2.62 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April I do feel kind of the same way about other industry work yes. The difference though with the porn industry is that having \textbf{sex}, having someone's parts inside of yours, exchanging fluids, etc. involves, according to me, more consequences than other sorts of exchange. I would be curious to know what brought you to engage in \textbf{sex} work, and what you gained from it, how do you feel about it. I need to point out that I never said the porn industry should not exist. I have listened and will probably still listen to different points of view, I do not wish to share about my personal experiences here but my view on \textbf{sex} for money has changed and has evolved, which still allows me to understand why some people do it or consume it. Are you worried or angry by assuming I lack imagination?! Yes, I do see differences in taste and behaviour and preferences in humans and that can be such an enriching thing! Nevertheless, I express my feelings and point of view here. I guess that is what people do on a chat, isn't it? I find it a little frustrating thoug that you question some of my personality traits but don't answer any questions I have asked so far. What's the deal here?! To finish, I would add that I have a problem with body and \textbf{sex} not being sacred, which is also part of the shoratges of the "modern" world which create  a lot of pain on this planet, and it hasn't started just recently.... By saying "sacred" I mean a link with our divine nature, our link to soul, spirit, Gaia, the Goddess, God, or whatever ones wants to call something encompassing all living life. And this doesn't mean to me that \textbf{sex} should only be practised in the "holy estate of matrimony", as matrimony is men's invention and doesn't always fit my view and definition of the sacred. Having \textbf{sex} is to me, and to ancient practices in different parts of the world a union which engages for longer than the duration of the act itself, I believe in energies and I believe that when you have \textbf{sex} you carry the partner's energy inside you for a long time, and that has an impact on your life. Also, I feel sorry that in most of porn content on tha most popular platforms there is a tendency to violence, \textbf{sexism}, domination, and nearly systematic white shower endings which are supposed to please these women so much...: Hum...Not all women like this first of all, plus women are cyclic and this cycle is not always respected when they work in the \textbf{sex} industry which is a violence against their body and their soul. Having \textbf{sex} without consent is to me a tremendous harm for the human and it happens a lot in this world, and it does happen often in the \textbf{sex} industry. I don't feel surprised you say many \textbf{sex} workers you have talked to don't fit the "stereotypes" I have described, I feel sceptical! I am still open to hear more about this!\normalsize   & \cellcolor{green!27}Sex, Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}12/522 & \cellcolor{green!27}2.299 \\  \hline
  \cellcolor{green!5}\small \@Alwyn April "have engaged in \textbf{sex} work myself on a few occasions."And there we have it.uglypeoplefucking.com called and said even they had standards. Sorry, looks like you'll be needing a new part time gig.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April Not being ancient would make me feel better actually. Back in the day when shame existed. Now every little \textbf{brat} gets participation trophies and learns how special they are, no matter if they're below average and destined to be a worthless leech on society.\normalsize   & \cellcolor{green!27}Brat & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@angryoldfatman Well you can't change your \textbf{age}, but I don't think you have to feel bad or ashamed about that at all. :) I don't really know what "average" means in this context, but I wouldn't say that anyone is "destined" to be a worthless leech on society - I think people can all contribute in their own ways.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small ​ Alwyn April  "Well you can't change your \textbf{age}, but I don't think you have to feel bad or ashamed about that at all."It would be foolish to be ashamed of an immutable trait. Unlike \textbf{sexual} deviance and general degeneracy."I don't really know what "average" means in this context"As in not special. Average. Unlike what Mommy tells them. Those that abandon deities have an even worse opinion. They consider all humans to be miniscule little bits of \textbf{nothing} in a vast uncaring universe."but I wouldn't say that anyone is "destined" to be a worthless leech on society - I think people can all contribute in their own ways."Contribution to society is helping to produce a service or good that is useful. So I guess you're correct there if you consider helping to separate degenerates from their income to improve society.BTW there are wangs not being touched because you're here. Get back to work, slacker.\normalsize   & \cellcolor{green!27}Age, Nothing, Sexual & \cellcolor{green!27}Age - General, Age - Youngsters, Gender - General & \cellcolor{green!27}3/160 & \cellcolor{green!27}1.875 \\  \hline
  \cellcolor{green!5}\small \@angryoldfatman Well, I don't know what you mean by "\textbf{sexual} deviance and general degeneracy", exactly. By which standards?Just because some people do not believe the universe cares about them or has given a special purpose to their lives does not mean that they cannot create purpose and meaning for themselves. :) Also, many people in many cultures around the world grow up never believing in deities and yet can live happy and fulfilling lives.What makes you describe people who engage the services of \textbf{sex} workers as "degenerates"? Do you mean any kind of \textbf{sex} work, or just some? How about people who engage in any kind of \textbf{sexual} activity outside of marriage, or for the purpose of procreation?So what else is not being done because you're here? Would you like to get back to that as well?\normalsize   & \cellcolor{green!5}Sex, Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/140 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April "Well, I don't know what you mean by "\textbf{sexual} deviance and general degeneracy", exactly. By which standards?"Not Jesuits, that's for sure, judging from those who were "educated" by them. Try a dictionary. possibly, along with philosophers slightly less obscurant than Kant. "Just because some people do not believe the universe cares about them or has given a special purpose to their lives does not mean that they cannot create purpose and meaning for themselves."Ah, absurdism. Every life and deed and invented purpose will mean absolute dick-o-la in 10,000 years. So you go ahead and read your Camus, invent yourself a purpose and be all happy. Take drugs, indulge in hedonism, do nasty things with your body for money or for free, commit any crime you wish, make the Marquis de Sade scream with outrage. Means \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing, Sexual & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/140 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small \@angryoldfatman How about you tell me what deviance or degeneracy mean to you, and whether and why people ought to feel ashamed about them?Indeed, many of our lives and deeds may very well mean \textbf{nothing} in 10,000 years, including yours and mine. But that does not mean they don't mean anything to us, or the people we care about, or the people who will survive and remember us after we pass on. :)\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April  "Do you think people that do not carry your genes cannot or will not remember you?"I said "easiest way", hence progeny. There are a few other ways to be remembered long after your death, but those are usually not good."What makes you describe me as "very triggered", or my happiness as "suboptimal"? "You keep replying on this thread to counter those with whom you disagree, mainly because you sympathize with the young \textbf{woman} in the video and wish to tell them how wrong they are."How about yours? "I'm having fun just continuing to trigger you. Every time you reply feeds my sadism. Please continue, \textbf{sex} worker.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/113 & \cellcolor{green!27}1.77 \\  \hline
  \cellcolor{green!5}\small Bcz she hadn't \textbf{sex} for a long time\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Shes a very depressed \textbf{woman} , yes weve talked on different occasions\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small dirt woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small TrickyFun \textbf{Nation} it's just her job, it's very different, but it shouldn't stop someone from dating her.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small would marry her and would fuck her every damn day. btw im a 6 foot 6 \textbf{black} guy with a 4 inches\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small imagine marrying a \textbf{woman} who's been fucked that much by different people. gross. then there's the fact that other people will have jerked off to her lol.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Do you think everyone you have ever been with was virgin territory? lol hate to break it to you dude but chance are they all had \textbf{sex} with multiple people before you.  Did it make you like them any less?  the exact number is only relevant to shallow folks and children because how much cock someone has had is not a defining factor in whether you like or are attracted to them or not and THOSE are the things that matter when it comes to marrying or procreating with someone.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small \@Neo Wolfen Are you dating some amateur pornstar ??  It would be so nice when your son get in "JerkingOff" ages, and find a title "Two \textbf{black} dudes filling holes" but holes of his mother = your wife.. Thanks, but NO thanks\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Neo Wolfen if a girl has been with a shit ton of guys, it shows a lack of commitment among other things like promiscuity/character/etc. you could just be another guy on the list. if you just wanna have fun, go for it! if you want to settle down, find another \textbf{woman}. only desperate men would marry a slut.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small It shows no such thing, all it shows is she has a job in the porn industry.  Yet somehow to some of you people you think that makes them less human or tarnished in some way, ironic when most of you would be pants down at the opportunity to be with them.Imagine you discovered your mother had done porn, would it make you love her less? would she suddenly be a bad and imoral person?  of course not.  A job is a job \textbf{nothing} more.  And noone who watches porn is in ANY position to be making moral judgements of someone who stars in them.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small I think its fairly safe to say any child of jerking off \textbf{age} is not going to be jerking off to porn featuring either of their parents.  And again anyone watching porn is in no moral position to be making judgements about people IN porn.  Thats called hippocracy.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small who in a hell a a non-porn guy that has 6inchs dick date a pornstar anyway? At the end of the day, we all look for tight \textbf{pussy}, and 6inches is more than enough to satisfy a non-porn \textbf{chick}.\normalsize   & \cellcolor{green!27}Chick, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Lil \textbf{hooker}...\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small The real concern is STDs of course, the not so real concern but legitimate tho, is that some pornstars dicks are \textbf{crazy} huge\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I mean dating, yeah sure that's a problem. It's one of the smaller problems though. What about when you have kids, and they grow up and their friends find you online and tease them about it. What happens when your 14 year \textbf{old} son finds videos of you being anally dicked by Tyrone on pornhub.Moral of the story, don't be a porn star if you are concerned about anything to do with the way your life is going or will go in future.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small I wouldn't mind dating her? Not even 6 inches, but I'd love to date her. Porn and real \textbf{sex} is different. Sure, I would be insecure at first, but if she was into me, then I would not mind it at all. I mean, she's with me right, she's with me for a reason, and not those guys with a big dick.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Lol she's worth 800K.. that's  \textbf{nothing}.. bruh this bitch ruined her whole damn life\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small This is DJ ICEDITZN43 on I    am not \textbf{g\textbf{ay}}. ICEDADDY ICEWATER GUY.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I'm sorry but my cock size has \textbf{nothing} to do with the failure of a relationship. It's the thought of what you do for a living and you wanting me to be okay with it\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Umm...models have \textbf{sex} every day too. What's being beautiful got to do with anything? Beauty makes you too good for porn but not too good for modelling? How's that work?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Models are fucked by \textbf{old} retards every day\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I don't get why you people are saying it like she hates her job. I mean, she probably doesn't, does she? I thought \textbf{sex} is a fantastic feeling, isn't it? I don't get why people don't just let people like this do what they do. I mean, so many people (especially men!) watch porn every day.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small What if..and I know this is going to sound \textbf{crazy}, but what if they actually enjoy getting paid thousands of dollars to fuck the biggest cocks from the most in shape guys??\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small My big concern would be , what if you pass something to me....as much as porn star's clam  the civilian's they date need to get tested, doesn't mean the people they work with are stand up people either....your in the \textbf{sex} industry! and a number of porn stars tend to escorts on the side also, but if your bold enough to date a porn star, It's not like you don't know the risks either ha ha :)\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small Such a \textbf{weird} life\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small okay whats with the fucken judgement in the comments jesus fuckin christ.  "Her life is meaningless" maybe to you? for all you know she loves her life how it is and who the fuck do you think you are to express an opinion on it? "shes a used whore, a spent product"  Yet in the past 24h you were jacking off to and fantasizing about the same, 'used whores' while your wife girlfriend wasn't looking? life itself is meaningless anyway who gives a fuck, do what you enjoy and thats exactly what shes doing, your life isnt important no matter how amazing you think you are.  you mean \textbf{nothing} unless youre making revolutionary discoveries, which i can guarantee your worthless ass isnt doing.  you make your money your way and she makes hers in her way.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/136 & \cellcolor{green!27}0.735 \\  \hline
  \cellcolor{green!5}\small She's \textbf{common} on pornhub, seeing her here is \textbf{weird}.\normalsize   & \cellcolor{green!5}Common, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Gets a job where she has \textbf{sex} with a lot of people, then complains no one wants to date her. Gee  I wonder why that is?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small How can you be a star when all you do is have \textbf{sex} with different people?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small the people on this board are so judgmental.......if you are a guy, you would pay half your salary to have \textbf{sex} with her and, girls......you would do the same to be half as hot and have as many guys masturbating to you on the internet as she does.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Lowlife \textbf{tramp} !\normalsize   & \cellcolor{green!5}Tramp & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Oh, that's yet to come, like in about 3 or 4 years from now when \textbf{nobody} wants her anymore ...\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small She´s the beautifull \textbf{woman}.She´s delicious.I would love fuck her. I get high!!!!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She didn't break her life. We, rest of the world, being stupid and ignorant people won't ever ignore the thought of watching her having \textbf{sex} and doing dirty things, condemning her for life.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Errrrrmm for one thing I don't fuck women as a job to the point I have to get tested every other week so no she is \textbf{NOTHING} like me stop deluding yourself.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@Jared Clark Im sorry but your opinion is just stupid and ridiculously flawed. Saying that we are all the same is a really \textbf{dumb} thing to say which I can't take seriously.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@Shadman Khan You know how there was \textbf{nothing}, then the Big Bang and then there was everything. Well the thing is the Big Bang never "stopped". The universe is still expanding. So everything in it is all still a part of that Big Bang including us. We're all still a part of that first event, we all come from the same place, so again. We're all the same. I know this sounds stupid to you, but when I stop looking at life from an individual perspective, it's what I believe to be true.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small I'm not judging her per se. I have fapped to her porn countless times. However, calling guys insecure because she is taking huge dick on a daily basis is kinda \textbf{weird}. Like, if somebody is fine with living someone like her, more power to that person. I however, would never want to myself. I'd always see her as used goods\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small Same as me and you JaredDo you get paid for \textbf{sex} on screen Jared?I don't.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small she is diffrent she sells her body to live a life which other people need to work hours and hours. She shows her boobs and let \textbf{old} people fuck her ass so she can live her dream... Fast and easy money for minimum of effort.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Isaac I agree. It's not their fault. But I also think we should all at least strive to be better and do better even if that very choice is itself predetermined. We should at least try. And my main point is that having \textbf{sex} on camera for a living isn't any worse than anything else you could do but judging someone for something like that and therefore saying you're better than said person is not what we should strive for. And if that sounds hypocritical that's cuz I suppose it is. But that's exactly it. I don't think I'm any better than anyone else but other people do. So I am judging those people and that's exactly why I'm no better than them. Well that made sense in my head.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/130 & \cellcolor{green!5}0.769 \\  \hline
  \cellcolor{green!27}\small You deluded stupid twat, don't go on saying this bullshit, shove your words off your ass, she's a cheap piece of meat who can never have a decent warm family, no kid will ever want a mom like this you fuckrardAnd every porn star is a \textbf{drug addict} and can never find peace so fuck off with your nasty moronic logic\normalsize   & \cellcolor{green!27}Drug addict & \cellcolor{green!27}Behavioural Addiction - Drugs & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small She is a porn star...She will always be different you \textbf{dumb} ass\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small A man who really is successful,  not just a little rich,  looks at your attitude,  values,  ethics,  principles,  demeanor,  and yes your smoking hot appearance is a factor but you are inclined to cheat since you already use \textbf{sex} as a bargaining tool.  Not even a moderately successful person would get a state license with someone who has little dignity.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small Did she has any other  job  rather than be  a porn star  like  a whore.  She can talk  freely about  copulation  or  intercourse.  What a  shameful conversation  and  revealation.  Is  this  a way to  get  people  know about  \textbf{sex}.  It  is  abdsurd  and  shameful revealation.  Do you  agree with me.  Thank you.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Just propaganda and fantasy, I don't really think 🤔 any \textbf{woman} in this \textbf{crazy} world will wish to be a pornstar m, it's a life time disgrace, you may quite porn but your videos will stay online.\normalsize   & \cellcolor{green!27}Crazy, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Wow youre an idiot why would you even ask that of course her line of work doesnt deserve any respect. Shes a whore who gets paid to have \textbf{sex}. Thats all\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small ​\@matt g oh but I bet you would envy a male pornstar for all the "nice \textbf{pussy}" they get to try. You would never call him a "prostitute", cause that´s not what they taught you. What you are doing is a slut shaming a \textbf{woman}, something you probably do on a regular basis. Because this girl do porn, you think you can be particulary nasty and harsh judging her.\normalsize   & \cellcolor{green!27}Woman, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}2/69 & \cellcolor{green!27}2.899 \\  \hline
  \cellcolor{green!5}\small \@J.C Rodríguez . Wrong, stupid.  A guy getting paid to perform \textbf{sex} is a prostitute as well.  "Slut shaming" isn't even a thing.  It's made up BS by and for pussies like you.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Are you retarded ? I , a car's change parts salesman , going to get thrown i  the same pit as a \textbf{chick} who gets fucked by dude's left and right ( sometimes both LOL )\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small They consider loving another person is cheating not having \textbf{sex} with other person.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Get a job madam u could aswell have a break and give yo \textbf{pussy} and soul some rest some peace.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Most of the disparaging remarks by men, below, reveal what self-righteous, judgmental \textbf{pigs} they are and next to \textbf{nothing} about the porn star.  But then what else is new?\normalsize   & \cellcolor{green!5}Nothing, PIGS & \cellcolor{green!5}Age - Youngsters, Nationality - Southern European & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Sucking cock, eat sperm, they doing this type of \textbf{crazy} thing for money popularity, when i am doing \textbf{sex} with my partner I never told him suck my cock cumshot because she is my wife \& I respect her, do you understand\normalsize   & \cellcolor{green!27}Crazy, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small THIS IS THE AVERAGE \textbf{WOMAN}...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small This beautiful \textbf{woman} has a huge career ahead of her\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Being a pornstar would be so inconvenient and affect you in ways that you never even imagined like dating, but what happens when you get really \textbf{old}? And you don't want or can't do that anymore. Will you still get paid even after you retire through your social? If you don't that fucking sux\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small this is the classic \textbf{dumb} whore\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Mean commenter ,you hypocrites watch porn and then complain about bow \textbf{dumb} the pornstar is.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small She is a smart and very interesting \textbf{woman}. I like that she is very aware of toxic or successful relationship based on trust and clearly s connection not related to \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small That \textbf{pussy} is so wide\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Sloots gonna \textbf{sloot} , I feel sorry for beta men who date women who are used up 🤣😂\normalsize   & \cellcolor{green!27}Sloot & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small No one can put you down without your approval. \textbf{Sex} and love are two different things what is destructive is jealousy. From most of the comments it's a wonder anybody watched it. Why would they if they weren't into it it's p***\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small She has destroyed her life for the sake of just money ..she will realizing one day in the future that all of this means \textbf{nothing}...this is not what life is about..\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Nothing like a classless dirty w** my favorite\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I'm going to have to play devil's advocate with you there. Sure no one forced them into it. But many of them saw no other choice. Many of these girls came from broken homes and had no real way of earning a living, especially one that pays so well. It's either have \textbf{sex} professionally or on the streets. Maybe stripping would be an option but really porn pays better.Think of it this way too: these girls that enter the industry do it at a young \textbf{age}, like 18 usually. Are you telling me you've never done anything stupid when you were 18? Now imagine that you're 18 and you basically had no education, reliable family, place to live, or source of income. Then you find out that you have a pretty decent body and can make money by doing normal adult things. If the idea doesn't at least cross your mind then bravo to you. Otherwise, I think you'd at least consider it.I disagree with you fellow fapstronot, but I am going to upvote you for visibility of your comment as I believe it should be something that is at least discussed further on this forum. I used to think exactly like you too.\normalsize   & \cellcolor{green!27}Age, Sex & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/206 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small Regular single people have \textbf{sex} with total strangers once a week at least\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@truth success? Vagina and ass ruined. Seen on video for life getting jizzed on. \textbf{Mental} problems. She might have money but I don't measure success by that alone. Look at jenna Jameson. One fucked up millionaire porn slut.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Measure success by money, period.Everyone dies, when we are ALL rotting in the ground...doesn't matter our virtues, our accomplishments.What are virginal/moral-compass/righteous people saving themselves for ? oh right the fear of eternal damnationTHIS IS hell, there is no after-life-bullshit.  Live your life, do as you please.  As for retirement...that isn't my problemSometimes crime does pay.Sometimes things aren't as simple as black/white...and there are far far worse things to be in this life (I listed those above in another comment/post).Fact is...she will die, you will die...I will die, and none of this will matter.Get your nut, get you \$\$\$, success is subjective (from person to person).If I am wealthy, I would consider that successful in any form...she can get her \textbf{pussy} tightened, she can get lipo, she can buy drivers, she can get treatments, and medicine/pharmaceuticals.For every issue, there is a fix.  You retire, then you die...period...not like living wholesome/righteous is going to buy you IMMORTALITY (besides who would want to live forever anyway?)\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/173 & \cellcolor{green!5}0.578 \\  \hline
  \cellcolor{green!27}\small True that. Suffer a hell lot probably they don't even live upto that ripe \textbf{age} of 80 I mean imagine how many times they do in a year forget about year just think about months.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small This whore actually has the nerve to call guys insecure because of her failed relationships? Maybe they want a \textbf{woman} who actually has some dignity and self respect.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small If you date her you're just dating her body. She has \textbf{nothing} else and it's sad 😞\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Nothing else? She sounds pretty intelligent to me.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Fun. And that's actually smarter than sitting 24/7 in a job you hate more than anything, the monotony, the climate, etc. until you gank your boss and  or co-workers. Only if you're a man though. If you're a \textbf{lame} \textbf{pussy} you obviously dont got the balls to go through with what you think and dream about every day and every night. Generally speaking. MAYBE you are among the 0.2 of men who is happy with their job, or rather, pensionated. Well I for one AM pensionated nowadays, 24/7 of my time owned by me and noone else. But I was a man. I was once "away" after not having fun. ....... I'd totally love being paid for having fun with medically clean Sapiens. If I had had looks and \textbf{gender}, back then, I wouldn't have lost years, I am certain of that.\normalsize   & \cellcolor{green!27}Gender, Lame, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/143 & \cellcolor{green!27}2.098 \\  \hline
  \cellcolor{green!5}\small 'Insecure' is not a bad word. She said she understands it and is compassionate towards it. Just fuck off with your pretentious and arbitrary conservative values; somebody can have 'self respect' and like having \textbf{sex} for a living. Who cares?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small if you think self-respect is a conservative value then u cannot have \textbf{sex} for living my frienda self-respect is all about not doing a low act that gonna make you lose people's respect you can't have it and a dick in your mouth at the same time\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Blake Sosebee, oh fuck off, would you? If you had the chance you'd probably bang the shit outta her straight away. Calling women whores because they're in the \textbf{sex} industry is not okay.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small News flash - any \textbf{chick} that's been with more than two dudes is a whore.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small It really sounds like you have an extremely shallow underdtanfing of dignity and self respect. She has \textbf{sex} on camera with men that she isn't involved with, so what? Do you also believe 'professional' wrestling is real?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small \@Marian Sony And I say so fucking what?  This holier than thou bullshit in this day and \textbf{age} is absurd and idiotic.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Blake Sosebee White men will always be jealous and look like a lig , poor snowflake\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small She says his boyfriend fucking someone else is a problem. And that's the same problem for the guys who dates a bitch like u. So no dating until u stitch ur \textbf{pussy} and mouth and then it's death, Then u can Reborn and u can get a date if u r not being a bitch.... All the best....\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small Porn Star????...whats ANYTHINGto look up to a hoe?? Trying to make it a " legitimate " job. What a crock of crap to the mass of \textbf{Blind}...headed for hell.WAKE UP!!\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small look mam! you look upright and good in spirit you don't have to deserve such life. And \textbf{sex} is not a job you do for payment  it is like part of a life between a man and a women being one flash when you do it with the one who U loved each other  and to be one forever that is why God protects it not to be abused. That is why there is a lot of plagues on those people who abuses it. And Mom I beg you to stop it and come to Lord Jesus who is the son of God who can cure any sin make you clean like     -you feel as you did not do it.      -Make you free from condemnation and give you new life.Please mom come to Jesus! when I write this  am feeling gracious to you and also there other too I feel gracious to ward. And don't feel you are \@ dead end and feel desperate. I can say everyone is part of it like those who-watchs a porn-making a porn -thinking it -doing it for personal pleasure etc.. are part of it.Please this is not life it is hell! I beg God in the name of Jesus to forgive us amen.God bless you\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/217 & \cellcolor{green!27}0.461 \\  \hline
  \cellcolor{green!5}\small "Get tasted in a regular basis" while shes having \textbf{sex} with a lot of other people? Same goals??? Hahaha the stupidity its real\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I don't want to date a \textbf{chick} that fucks other people, gets paid to fuck, or whose snatch looks like a punched lasagna\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small She made me feel not so bad about my 6" dick. Now i just gotta find a \textbf{woman} in real life who feels the same way.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Lol your keeping me from being successful at my job nasty weenie washing spermburper what happened to the real Woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small What about the \textbf{mental} illness factor?\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Why some guys should fuck all this beautiful \textbf{woman} and some guys can't find any \textbf{woman} to fuck maybe the months and years?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small This not good. Hey lady your body is the temple of the Holy Spirit stop doing for having \textbf{sex} someone someday you'll realize that God hate those things hey beautiful lady repent before is too late hell is real\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Disgusting how she talks about \textbf{sexual} intercourse so loosely as if its just some sort of sport.  Intimacy is a sacred thing.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small It's \textbf{crazy} how much \textbf{Black} Dick this girl has taken.  That \textbf{pussy} is botched. All of Wakanda has gone through this \textbf{Pussy}. Talk about the true definition of 'Wakanda Forever!'\normalsize   & \cellcolor{green!5}Black, Crazy, pussy & \cellcolor{green!5}Ethnicity - Black, Nationality - Chinese, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/30 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Uneducated brainless \textbf{woman}..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small This is one of beautiful girl I have seen in the same time unfortunate too. She is not thinking it will last soon with her \textbf{age} and then after what will happen she has no idea. For money million of girls chosing this so called professional but they r nt thinking about here after and living a uncontrolled life with proud. 'CONSEQUENCE IS FAR BAD THAN IMAGINATION.'\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Because of the way you think and the way you are you can only have \textbf{sex} or get fucked but never can make love. The feeling of love is above everything and empty head whores like you can never get that feeling.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small That's why...pornstars belong with each other, they should just stay in their own circle, who would want to date or marry a pornstar...just picturing all the men's filling all your girls holes, would make me go \textbf{crazy} lol....its a big NO for me.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@igor šajinović You dumbass degenerate, \textbf{black} people were the first people, and are the oldest people on earth. If anything we should separate your bitch ass.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@random epic videos Thats where the problem lies, society controlling people with its opinions. Society is not perfect at all. Society is not always correct. Not victimizing anyone here and yes, every job has its weaknesses. But peope just can't ridicule and defame the \textbf{woman} just because of that. Its called respect, no matter if you hate him/her. Shes just another human with feelings, not a criminal.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Sex is like Russian roulette, if you love life, don't have \textbf{sex} with a whore\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small \@Hakeem Sd70M bro I'm \textbf{black} too we are native to America but dont take it to the heart just laugh it off\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Hey "ladies"; your just pissed she gets paid for \textbf{sex} but doesnt have to pretend to like the person afterwards like you do.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Like testing would help when you have unprotected \textbf{sex} like this.  Some time it takes 6 months to shit to come out.  whoops too late.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Hard as people riding this \textbf{woman} if you're not dating virgin all time everyone is pretty much dating pornstars it just Dani Daniels performs on camera \& you do it behind closed doors same thing just different venues!!!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Wayne Robinson no wayne, my last two exes haven't fucked literally 1000 dudes, 700 of them being 15 inch \textbf{black} dicks railing them at the same time. Get your head out of your ass\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small but we date for the \textbf{sex} (at least majority for the people) so why do you need to d....a....t....e?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Its Yo Boy V no, the majority of people do not date for \textbf{sex} LMFAO, not sure where you're learning that nonsense but you need to drift away from that bs\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Thot!!!!!!\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Why is the porn industry even allowed to exist when its basically just prostitution?  Everyone gets paid money to film themselves having \textbf{sex}, so how the hell is that not as bad as some random \textbf{woman} accepting money from a random guy who wants to have \textbf{sex} with her without filming anything?\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small She is fine, but i had a \textbf{freak} today. Mine got a lot bigger from the watermelon recipe ;   [LINK]   (youtube link)\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Are you that ugly you can't get girls, or are you just one of those \textbf{weirdo} white guys that girls avoid???\normalsize   & \cellcolor{green!5}Weirdo & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small This poor child she is spiritually dead and needs Jesus Christ in her heart she is on her way to hell with her eyes wide open Satan is Ravishing her her mind and her body and all who participate in her actions and those who are spectators as well I can speak from experience knowing how awful point is on your mind I have had everything in my life \textbf{sexual} relationship after \textbf{sexual} relationship I never appreciated a \textbf{woman} for her beauty it was only what gratification I could get I finally found the love of my life thank you God for your Grace \& Mercy thank you for your love and kindness and forgiveness I pray for all of those who have a Heart of Stone that is callus for the Lord Jesus Christ to come in and soften it\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/141 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Hooker\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small all these people calling pornstars whores but they are literally using what they have to make a shitload of money. this is by far one of the coolest pornstars ever. she deserves someone who will accept her job and accept her for her. yall need to grow up and quit calling them whores. how many people have each of you fucked? \textbf{sex} is a fact of life. get over it.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small AhaHaHa....Goals ? What fucking goals ...Please!Hard to take her seriouslywhen her and the other women take Boatloads of cum in the face ...Have thererear guns and front bunsstrecheted out poked prodedassaulted by every object under the Sun and then have an Ocean of Semen dumped in again on a daily basis....Ahhh yeah I want to date a girl like that kiss her on the mouth ...go down on her and have ordinay \textbf{sex}...I SURE would..Mom Dad I met someone...Tell us dear what is it that you do....please repeat above for answer..Again I say they all suffer from the grand illusions that what they are doing is important.....These people are screwed up in the head.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/123 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}\small Then if you marry this \textbf{woman} and have children and the children is gonna be ashamed poor and victims...when they knew her mom is a fucking pornstar and if they watch porn and they see there mom...just WTF!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Nothing more funnier than these hoes tryna be smart\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Woman u have lost respect..... Everything\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Nasty sickmined whore hooker\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small What a beyond disgusting disgraceful proud bragging hiv aids infested whore \textbf{hooker} savage animal\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small What a disgrace to the human race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small moral of this story, pornstars stay single and have more \textbf{sex} than everyone else...\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I bet she stinks like \textbf{old} smelly fish \textbf{nothing} but a dirty smelly slut she probably got HIV AIDS and every std yuuuuuuukkkkk smelly rat\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small You can \textbf{slag} her off all you want. Bet your not thinking that when your watching her take the cock.. . And playing with your dick\normalsize   & \cellcolor{green!27}Slag & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small to everyone saying that she's "open minded" listen: pornography is just like prostitution they're all paid to have \textbf{sex}, but the difference is, in pornography it's filmed and on the internet don't you understand that ? so when people call them whores it's normal, if you think they are open minded so it's the same for those on the street selling \textbf{sex}. guys come on open your eyes and stop being that dumb\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/73 & \cellcolor{green!5}4.11 \\  \hline
  \cellcolor{green!27}\small what a charming,lovely,warming,attractive,bright,hard working,considerate,compassionate,interlectual......little slut! get the f outa here! dirty infested \textbf{tramp}. although I wouldn't mind a good hr with her lmfao\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small "Imagine going to a school, and having \textbf{sex} with everyone in that school, and then trying to date people that are in that school but they just fucked your friend yesterday." welp, that"s enough internet for today.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Your that \textbf{dumb} you cant get a normal job you have to pimp out yourself out to a mucky seedy porn film company really who want to date someone who works in porn most of them end up alone cant formulate relationships SAD\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Isn't she a \textbf{lesbian}?\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I feel sorry for her. Its obvious she's having a tough time living. The desire to be normal is there, conflicted with her passion of having \textbf{sex} as a job.It is not even that too easy of a job.If she's strong enough she can make a choice, of leaving that porn job forever and try to do other thing she's passionate about.If being normal is really important for her she can do this. She has to.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Age restrictions.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small What's up with all the dweebs in the comments? You pathetic losers come here to talk shit about a \textbf{woman} we all know you want to fuck but claim you wouldn't because she's stupid and she's a whore blah blah blah. Half of you are virgins and the other half had \textbf{sex} once 20 years ago and haven't been able to bring yourself to pay for another pro since the last one laughed at your micro penis. Gtfo\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small who are you to judge this \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Dani Daniels looks like this one \textbf{chick} in my class\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Never fapped to this girl. Now i know why. She's a cabbage. I'd never shoot my bolt over a cabbage, not even if i was in the \textbf{fruit} and veg section of my local supermarket.\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small I dont get this comments, i really don't. i mean, why \textbf{sex} is so important to you all. Ok it s a big part of relationship, but shit, when you like someone you LIKE someone doesn't matter wtf they do for living. Maybe i'm \textbf{crazy}, but i just don't have this property thing on people i like, i dont know\normalsize   & \cellcolor{green!27}Crazy, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Porn is kinda messed up. Guys look at it and think they can't compete,when actualy having \textbf{sex} should be about the connection and the love you have for the lady and vise versa rather than the pure physical transaction you have.I have been watching a lot of porn in my teen years and after the jerk was done i felt so insecure because my penis is not as big as the dude's penis i just saw.And when you see him giving that girl the time of her life(yes i know it's all an act and \textbf{nobody} moans like that irl),you feel like you can't pleasure a girl like that. 100 Years ago we did not have porn on this massive scale we have today and i'm convinced the dating life would have been a lot easier. Heart size has been replaced with dick size.So i think i still have a lot to learn and a lot less porn to watch till i get over my fears of feeling good about myself to actualy go talk to a girl i like.I feel porn has messed that up for me,but i should get all the credit for my problems because i am the one who is watching it.\normalsize   & \cellcolor{green!5}Nobody, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/206 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small Thats not the Dani Daniels i know. I thought she was a \textbf{transsexual} adult star.\normalsize   & \cellcolor{green!27}Transsexual & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/1 & \cellcolor{green!5}200.0 \\  \hline
  \cellcolor{green!27}\small I couldn't imagine a man wanting to be with this disgusting slut. She happily announces proudly how she has penis' 'this huge' and like demonstrating with her arm how huge they are and that she isn't ashamed of what she does. It's unthinkable for someone to sit there, talk about this in such a matter of fact way. She's \textbf{nothing} but a slimy vile mess.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Lol pornstars are \textbf{dumb} asf\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Marcel. Is ok but you call her brainless, like you feel superior to her because you "want kids with a \textbf{woman} you love". And for that I´m calling your bullshit, kid.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Porn stars are a special breed..Wouldn't date one mainly because she'd have more pricks than a second hand dartboard and a \textbf{pussy} like a clowns pocket and oral \textbf{sex} would be like yodelling in the Grand CANYON. Need I continue?\normalsize   & \cellcolor{green!5}Sex, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Wow thats mean u love \textbf{sex}....\& seen a lot of pennis types \& size... dammmn does ur \textbf{pussy} still tight😂😁😄😄😂?\normalsize   & \cellcolor{green!27}Sex, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I wouldn't have an issue. It's a job and it's \textbf{sex}. I guess society hasn't accepted that yet.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Omg all the people calling her stupid cuz she wants to date someone and she is explaining how hard it is to date,let me tell you that she is a human being and yeah you are \textbf{blind} if you think she doesnt want that!and then you are calling her all kinds of names bcuz she is a porn star and if it was a man saying this you wouldnt be calling him whore or a bitch! And i dont care why she chose that as her career that doesnt make her a less of a human being and well lets be honest at ghe end of the day you all will be watching porn and getting turned on by her perfomance\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small It's in her eye she wants LOVE ...OHHH not sex\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small What \textbf{nigga} she cute\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small numair sheikh you are stupid she did not destroy her life we are on a \textbf{age} now that society accepts it now only \textbf{old} heads care\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I'll marry her, come here dani hubby's got you! Just no \textbf{black} dudes cool? Cool. And if you marry me and get a girlfriend can she be my girlfriend too? That would be awesome. PS I'm serious.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small I will  show her a better  side of love  game,  than \textbf{sex} game.  I can make her believe in love than cock game, will power. Yes\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Scorer Scored so my dear friend why are you bringing your personal grudges here on a post which has \textbf{nothing} to do with Islam ... Try this on some videos of Islamic scholars where people could answer your questions  and clearify your griefs ... Ok may I ask my brother where are you from which country .?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small numair, you're so worried about this porn star's life being destroyed buy you have \textbf{nothing} against islam that destroyed lives of millions in last 1400 years, hence I brought up this topic.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April and about your comment I don't like her as a person so what should I do then.... You tube has given me the right to comment so I am doing it ...and if this slut has problems with my or any one else's comments then why didn't she \textbf{disabled} the comments option\normalsize   & \cellcolor{green!27}Disabled & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small \@MULLA ROCKETYY if it's basic human nature, then what about all the humans who don't feel the same way?is it also basic human nature to hate others for having a different skin colour, \textbf{sexual} orientation, language, religion, socioeconomic status, etc.?\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@Alwyn April OK I explain it in detail . this act of pornography is like animals . humans are different as they feel ashamed of while exposing themselves . even animals mate in secret places not openly . this much sense they also have . while the color and \textbf{race} difference are a different topic which I think we can discuss at some other forum with socialist people around\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Alwyn April um, people who were porn stars in the past struggle to find a job because of their past job being in the \textbf{sex} industry and it can affect you negatively in the future. if you listen to past porn stars' stories on why they quit you will see how abusive and terrifying the industry really is and how they always act like they're happy with their decision. when they've made a terrible mistake.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small and I could sum up your point with 1 analogy.  A young female soldier joins the United States  Armed forces, And shot in combat for Nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small She is destroying her soul and helping to corrupt the lives and souls of countless men and women--she is clueless.  The porn industry is ground \textbf{zero} for western paganism come back to life in this world.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I wouldnt be insecure around her, i just wouldnt want to date/fuck her … just because i wouldnt date/fuck a slut! That has \textbf{nothing} to do with being secure or not.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Just lost all respect for \textbf{woman}, die bitch.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Find me a pornstar who actually has good \textbf{mental} health!\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small yam ck its really not the same thing. You're analyzing the \textbf{sex} component and assuming that since it's literally the only thing they have in \textbf{common}, they are equal.\normalsize   & \cellcolor{green!5}Common, Sex & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Yep, pornstar and prostitution has a lot in \textbf{common}. So what ? There is \textbf{nothing} to blame. They are hurting \textbf{nobody}, so there's no reason to disrespect them.\normalsize   & \cellcolor{green!27}Common, Nobody, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small "Porn star and prostitution has a lot in \textbf{common}." So you do admit they are both categorize the same. lol\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Luca Volpini prostitution paid to have \textbf{sex} porn paid to have \textbf{sex} on camera thats the only difference\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small TheBritishBulldog - "prostitution paid to have \textbf{sex} porn paid to have \textbf{sex} on camera thats the only difference" (sic). Yeah, besides being tested for STDs on a regular basis, the chance of being arrested, the chance of being murdered, and the income....Yep, no difference at all.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Vexumy Imagine being over 11 years \textbf{old} and not being able to use your/you're correctly.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small It takes one time not  to get  tested finding  out the person  you just had \textbf{sex} is got HIV.  Etc.. is a risk you take is  it worth it, is up to the individual . People  would  say who wouldn't  get paid to have \textbf{sex} most people  do but the risk vulnerability.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Pierre Dudoret yeah there not hurting anyone but that doesn't mean I have to respect the \textbf{dumb} hoes\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Pierre Dudoret We are not disrespecting them, we enjoy them, and always think if they came in front of us we will ask her for \textbf{sex} ✌️\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@Pierre Dudoret My "evaluation" has more rationality than you think. It is literally not hard to become a pornstar as a \textbf{woman}. There are loads of people with different fetishes so you don't have to constrict yourself to one set of body type. On the other hand, jobs that require loads of hard work to become professional in don't get the recognition they deserve because people don't see them as a way of pleasure. The human mind tends to see sources of pleasure in higher priority. It might not be right, or it might not be wrong, but that's how it is.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small People have no issues wanking off to her, yet they think they are somehow better than her and label her as a whore/prostitute /brainless/thing... Hypocrites! But yes, having a normal relationship with a pornstar would be almost impossible for a guy simply because no guy can be ok with  their girl having \textbf{sex} with anyone else, professionally or otherwise...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Let's pretend my girlfriend is a pornstar. I am a 20 year \textbf{old} college student, hanging out with my friends. I text my girl and say, "hey babe how was work?. She'll say, " it was great babe , I cummed 5 times by this guy who fucked me incredibly, i jerked him off and let him cumm on my face". I'm disturbed as I write this! Ofcource relationships don't work with pornstars!!! Relationships are about trust, respect, loyalty!! I couldn't have any of that if I dated a porn star. To summarize, i would never date a pornstar because I don't want my \textbf{woman} sexually involved with any man besides me.\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Why would anybody share something they love or like with a lots of people they dont know. its not insecure it's \textbf{common} sense.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small So she feels pride so she needs to make her job look cool by referinh to other people as "civilians" as in "unexperienced or untrained" in the (supposed) art of \textbf{sex}. It's like those \textbf{dumb} hoes buying army pants\normalsize   & \cellcolor{green!27}Dumb, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small This is what you see. What you don't see is that all these women have special stealthy drugs in their system to prime them to constantly have \textbf{sex}...and be horny. Ask some of the cunts that try to recruit young girls.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Such confidence talking about something so embarrassing, disgusting and degrading. \textbf{Hun}, don't be proud of what you do, you're \textbf{nothing} more than a prostitute with no self-worth.\normalsize   & \cellcolor{green!27}Hun, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - German & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Yep, \textbf{sex} with tonnes of people and lending yourself to be an object for \textbf{sex} goes hand in hand with loneliness cobber. And it sounds like you've figured it out and you're pretty young so don't get stuck there.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small A liberal snowflake\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small How can I make \textbf{sex} appointment with a pornstar?  .i got \$\$\$\$ 😋\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I actually had a girlfriend that was in the \textbf{sex} industry. Very hot and sexy. I had no clue at first what so ever about her job .Well until she decided to tell me about it... I mean fuck! LolTold her to fuck off and moved on with my life.. The most surprising  part for me is that she did not realise she was a bitch and she kept on telling me that it was no big deal and she could stop and have a normal life lol...WELL NOT WITH ME lol\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small WTF would anyone wanna be with a fkn whore ass porn \textbf{tramp}?!?!? No way could I be with a \textbf{woman} thats had a 1000 dicks in her \textbf{pussy} and her asshole!! Plus the same 1000 thats been in her mouth! Sick cunts!\normalsize   & \cellcolor{green!5}Tramp, Woman, pussy & \cellcolor{green!5}Gender - Female sexuality, Gender - General, Nationality - Chinese & \cellcolor{green!5}3/42 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Everyone is putting a negetive thoughts about this girl...I don't think soo that she is brain less...just because she is telling a truth about her life and what heppend if any \textbf{common} guy love's her and date her but why no one can't love her or date her  because she is an pronstar.) any one can doo this because she is doing his work for money and for her family...because money and family is most important thing and i think that she have any porblems in past that why she became a porn star Please guys just think one time and then judge any girl....and Im sorry for if im wrong in words or any matter but guys I think that type soo i write it...sorry and thanks\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small She's a prostitute. Id est, she has \textbf{sex} for money. Men don't date prostitutes for a million and one good reasons.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Honour ,Dignity, self-respect  components of our humanity .Such a beautiful \textbf{woman} so intelligent ,but is that all???Mat God Almighty guide and protect you my sister.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Imagine how \textbf{weird} that would be knowing that you have a daughter who is fucking for a living and theirs millions watching them naked I don't about you but that would really gross me out\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small I have \textbf{sex} with huuuuuuge penises 8------------->me 8-> ..... hard as a rock!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Cheat on her? Wait she wants her partner to not have \textbf{sex} with anyone else?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Your pathetic attempt at judging another, just another sad sappy weak, tight-jean-wearing-emotions-on-sleeve, angry virginshes a whore, your a virginglass half full kind of guy.  I'd say you are far more pathetic.  You are too much of a loser to have a crush on a whore. You just sit on the side-lines...the one "never asked out"   "never involved" judging others, the back-seat  passenger seat youtube[r]. OH and hey idiot...guess what ? (psst lean in close douche-nugget) ...just b/c someone finds a random young porn star attractive, does not mean he has a "whore crush" this is the first I've ever seen of this girl...and guess what ? you said "how much you wanna bet she went straight to sucking someones dick after the interview"Considering she says halfway through the interview it is her off day from shooting, I'd be willing to wager quite a high bet on that...and you would loose more then likely.But besides the point, even if that was true, and she gave a blow-job only hours after the interview, so ? cool - whoever received it...I'm sure he's blue-balls free, and relaxed.  LOL Jealous much ? loserNot our fault your \textbf{chick} at home is probably a 450 pound sarlacc pit. And that's a big "if" you even have one.  But hey bro...you've always got the option of blow-up dolls, I hear you can fuck the shit out of them a bunch of times before tearing a hole \& deflating.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/247 & \cellcolor{green!27}0.405 \\  \hline
  \cellcolor{green!5}\small revealing...they get jealous too if their bf engages with another \textbf{woman}...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small cuck\normalsize   & \cellcolor{green!27}Cuck & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Nasty pig-resembling \textbf{cuck}.😷🤢\normalsize   & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Gunashekar Reddy shitty \textbf{indian} spotted\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small In India most guys don't get to meet or talk with real girls till marriage which is around 27. Guys like him are a prodcut of that, they would take even a man with a \textbf{pussy} to date.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Is lesbian\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small that \textbf{old} broad just sat there and went "uh huh" for 3 minutes lmao\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Joyson Wildhart - "that \textbf{old} broad"? She was 26 at the time of this interview.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small scarzoo005 - Only if you are 10 years \textbf{old}. Are you on your mommies computer again?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small You're obviously a child so there's no need to respond. Just make sure to get your \textbf{mental} health checked though because you really need it kid. Good luck.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small when i said \textbf{old} broad i meant the \textbf{old} person not the 26 year old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Its all of these religious cucks in this comment section that go hate on a \textbf{woman} that decided to sell their body. Its her choice, theres plenty of people that watch her I bet some of them reading this have. You're all pathetic for hating someone for that. Yes she might have made some \textbf{weird} comments on cheating but its not like shes not just a normal human being.I bet ya'll hating cuz ur insecure virgins.\normalsize   & \cellcolor{green!27}Weird, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small Weird seeing her with clothes on\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I would NEVER date a \textbf{Woman} who's job is to be filmed and photographed while being banged by every Tom, Rick and Harry in the porn business.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small CALL ME \textbf{CRAZY} BUT WHY NOT GET A BETTER CAREER THAT'S DOESN'T INTERFERE WITH YOUR RELATIONSHIP\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Dating a \textbf{Hooker} would be the hardest relationship to keep... Ok Hunny, I'm going to work now, just a quick cream pie and anal scene and I'll be back in a jiffy... Gotta pay them bills' These women are hookers, not performers, hookers... lol Dating a \textbf{Hooker} would be very difficult, she has a point...\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small Well we know why she does porn. She's really \textbf{dumb}! Poor girl, so so sad!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Yeah   it fucks up your \textbf{mental} health and \textbf{sexual} desire\normalsize   & \cellcolor{green!27}Mental, Sexual & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I'm just jealous you have \textbf{sex} with Xander!!! lol\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small No dude  with his full faculties wants to date a porn slut.  Have \textbf{sex} with her without commitment? Maybe.  Her last words in this interview that she followed with laughter (\textbf{nothing} funny there) shows that this \textbf{chick} has lost her way.\normalsize   & \cellcolor{green!27}Chick, Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small hahaha YES your "boyfriend" is the one likely to contract a \textbf{sexual} disease~you see, guys do like whores like you, they just don't want a relationship with them.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small oh booo hoo, being a pornstar must be soooo hard. us civilians have no idea what its like. yeah its not rocket science. you have \textbf{sex} with people for money and have to get tested regularly. big deal.alllll of the stuff she said, normal people have to deal with too. jealousy, infidelity, insecurity. thats not confined to the industry.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small she wont date pornstar because she can get jealous, but wants a man or girl that is OK with her getting fucked every day.... i have \textbf{nothing} nice to say about her, wont even check her videos\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small i want to feel what \textbf{sex} taste like\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I don't even understand how a pornstars brain is with all the dopamine being released. Too much \textbf{sex} leads to being forgetful, it would be hard to learn new things for them apart from \textbf{sex}. I am struggling with porn addiction (and I will surmount it)I  can't even get into a sincere relationship because I begin to see my partner as a \textbf{sex} object, as a tool (wgich is why i wouldnt jump into a relationship unless the girl is willing to help me fight the addiction and support me, female/male  should never be seen as an object just like i would never want my own children to be seen as that am not even acting the porn, can't  imagine how a porn star copes.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/125 & \cellcolor{green!5}2.4 \\  \hline
  \cellcolor{green!27}\small I went from one video about "Randy Spears" ("George" is his real first name, but I don't recall his birth surname currently), who was penitent about having been involved in making pornography, to this video wherein this young \textbf{woman} is so seemingly shameless \& base that it is simply shocking! I was hoping to find here a testimony of her having experienced help from the Lord to desist from \textbf{sexual} sin, but quite the opposite is featured herein. She actually, ironically, admits somewhat that it is not normal to be experiencing \textbf{sexual} activity with different persons \& then expect to have a healthy monogamous relationship not only in the wake of such sexing around but even while still sexing around! This foul-mouthed young \textbf{woman} needs to be redeemed by the Lord Jesus Christ, but she needs to come to that acknowledgement herself first!\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/143 & \cellcolor{green!27}2.797 \\  \hline
  \cellcolor{green!5}\small She is now married to a rich guy . \textbf{bald} man . she loves money for sure\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small PORN IS SLAVERY AND HUMILIATION TO WOMENS, BUT IS AN ATACK TO MAN AND \textbf{WOMAN},THIS IS JUST FOR CORRUPT SHAMELESS. THERE IS \textbf{NOTHING} MORE BEAUTIFUL FOR YOUNG PEOPLE TO BE CAREFUL, RESPECT AND RESPECT OTHERS. WE LIVE IN A WORLD CONTAMINATED BY THE BAD INFLUENCE OF TV, MUSIC AND THE NEGATIVE ENVIRONMENT OF VANITIES AND VICES THAT ALWAYS END DESTROYING LIVES AND FAMILIES. IT SEEMS THAT EVERY TIME IT IS MORE POPULAR TO SEE MOTHERS OF 12 AND 13 YEARS \textbf{OLD}, GIRLS WHO MAKE MOTHERS WITHOUT ANYONE HAVING COMPLETED THEIR PRIMARY STUDIES, THEN THEY HAVE CHILDREN AND DO NOT HAVE THE EDUCATION TO EDUCATE THEIR CHILDREN AND THEY ARE ALSO PREPARED IN THE ECONOMY TO MAINTAIN A FAMILY AND IN MOST OF THE CASES THE PARENTS ARE ONLY AN IRRESPONSIBLE SHAMELESS WHO JUST WANTED TO PASS THE MOMENT, IN THE END MANY GIRLS COMMIT THE HORRIBLE CRIME OF ABORTING AND THEY ARE DAMAGED EMOTIONALLY AND PHYSICALLY, USED, DECEIVED AND TRAPPED, WITHOUT STUDIES OR WORK ... THEREFORE THERE ARE MANY CRIMINALS AND LONGS IN THE STREETS. THE TIME COMES IN WHICH ALL YOUNG PEOPLE AND PARENTS HAVE TO BEGIN A NEW LIFE AGAINST THE HARMFUL CURRENT OF THE WORLD, BORN AGAIN AND LIVE A LIFE OF RESPECT, PEACE AND LOVE !! LOVE AND BE FAITHFUL TO GOD ABOUT ALL THINGS AND LOVE OTHERS AS OURSELVES. GOD BLESS YOU )\normalsize   & \cellcolor{green!27}Nothing, Old, Woman & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Gender - General & \cellcolor{green!27}3/228 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small as a man i think who's gonna have a relationship with a pornstar?, pornstars are basically over rated whores, who get paid for having \textbf{sex}, that's legal prostitution if you ask me, you have to have very poor selfsteem for having some trash cum dumpster person as a girlfriend.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Sad she'll never know what a good real wholesome relationship with a rightous man feels like, listen good ,, for the rest of your life you'll be \textbf{nothing} but a fuck tool for men ,sad😔\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I hope she realize what she is doing is not "normal work". What self respecting man would be with a \textbf{woman} who is fucked regularly by another men ? Even if he continues to be with her what wud he tell to their kids ? I respect prostitutes atleast they have decency to fuck in closed doors. These are horrible women who fucks for money and shows it to the world.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Shut up you daft cheap nobody\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Wow, the comments section here is a fuckin disaster....Got a bunch of jackasses in the comments judging her job choice, as if they do something noble for a living like cure cancer or something.  Pretentious assholes..    I mean utterly disgusting comments.  People writing off her opinion \& words as "she's just a whore," as if whores aren't people too, saying she's empty inside, etc.  Fuckin sick people.  Like damn, what the fuck you do for a living, clean the toilets at McDonalds?  And you're going to judge this \textbf{woman} for her job?  \textbf{Crazy}.\normalsize   & \cellcolor{green!5}Crazy, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/94 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Have \textbf{sex} with my penis baby🍆👅\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small As a true Christian I love you as my sister and don't want you to be a porn addicted anymore. Remember that your are a child of loving God. Your body is a temple of God. I was once addicted to pornography but I decided to stop it and not to Watch it because God does not allow it except legal marriage. Please use your body for the glory of God. Remember that you  can be infected by HIV and other \textbf{sexual} deseases and regretful lately.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small THis video is not good for the Children all over the world. Never seen \textbf{woman} talk happily like this about her shameful actions and verbal behaviors. She will be regret one day when she get \textbf{old} or lose her beauty together with the \textbf{crazy} interviewer.\normalsize   & \cellcolor{green!27}Crazy, Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/45 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I am looking the future. Incest \textbf{sex} will Normalised because human never satisfied . stop Pornography.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Jones your as \textbf{fat} as a Buick and as ugly as a Smart car, both with high mileage.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@n0ti5 I wonder why you must turn your opponent into a \textbf{woman} to feel confident. Afraid to face a real man? Penis insecurity? Hahahaha\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small If you have \textbf{sex} with a shit ton of men, you are devaluing your \textbf{sexual} market value.\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small When she's 50, she won't be able to hold her shit in because of all the ass \textbf{sex}.  Good luck with that, Honey.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small most of you who whines about her not having a ‘real job', whatever the fuck that means, have \textbf{sex} for free while she's out here getting paid for having \textbf{sex} lmao\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Wow...dating her...hmm. \textbf{Sex} would be like throwing a hot dog down a hallway\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small yeeahhhh definitely \textbf{crazy} AF perfect for being a pornstar lol\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small +\textbf{r\textbf{ed}} she looks nice\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small 1:06 "all of my friends have seen me having things inside me" what a \textbf{lame} society we have. She's even proud of that\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Would you 'I have no faults in my life' people cut this \textbf{woman} a break. So what....she's a porn Star. 'OMG she's the devil'  if I was her I wouldn't date a dumbass dude anyway. I'd stay home.....count my money.....and if I still have time after that play Xbox.  She's a person just like you and me. Before you judge others that you don't know look at yourself in the mirror\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small This bitch is fucking bat shit crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Beautiful \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I agree with most of what is being said in terms of not judging his \textbf{woman} of course, and when men judge her they are being total hypocrites because they watch porn themselves, but I do want to point out that there are differences between men and women. Women produce more oxytocin during/after orgasm, which binds them emotionally to the male. Men produce less of this hormone.Also, from an evolutionary perspective, men want to spread their seed and women typically do not desire multiple \textbf{sex} partners. So, in a sense, women who do porn may be ..sort of...going against their nature, at least in the beginning. Not that there is anything wrong with this, but it bares consideration because there may be psychological impact.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/124 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small \@Linda Lowther I'm accepting The fact that oxytocin is love harmone...but its main function as \textbf{sexual} gratification and social behaviour.... muscular contractions... but dopamine as neurotransmitter plays role in \textbf{sexual} arousals... motivation..desire and addiction.....\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small but males bond less during \textbf{sex}....right?? i thought that was proven\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small VKRGFAN  Hmm....good point. WIthout orgasm, I dont think oxytocin is released. The high rates of suicides with female porn stars probably has to do more with the social stigma of being a porn star. In general, I am against it and against prostitution too, because it re-enforces the idea of women being just \textbf{sex} objects; however, I cannot be all that vocal about it because I sometimes watch porn so it would make me a hypocrite.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small "also there is moral aspect to it and that is disarming the \textbf{woman} to take on a role of a \textbf{sex} slave"You do know that there are male pornstars as well? Who is a slave then? Aren't the guys in porn, slaves as well, by that logic? Pornstars do porn out of their own will, either to pay for their college, or because they love having \textbf{sex} a lot, sometimes because they're not satisfied with their personal \textbf{sex} lives, or simply to earn money.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/85 & \cellcolor{green!27}4.706 \\  \hline
  \cellcolor{green!5}\small I wonder the effect on the porn industry when they actually perfect the \textbf{sex} robot over the next say 10-20 years.......... i wonder the effect on relationships as well..... ?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Tan} that is just a convenient explanation for some men so they dont have to feel bad about watching porn. same rationale the ugly \textbf{old} men who go to 3rd world countries and hire 18 yr \textbf{old} (or younger) girls for \textbf{sex}....oh she likes it...she prefers this job....she is having fun....she likes me....etc etc. its all bullshit. there might be the rare anomaly but usually these people are so fked up you wouldnt even believe it\normalsize   & \cellcolor{green!27}Old, Sex, Tan & \cellcolor{green!27}Age - Over 65s, Gender - General, Nationality - British & \cellcolor{green!27}4/76 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small you gotta loves women who make porn when she speaks shes so comfortable and relaxed what would be funny a guy asks her for \textbf{sex} and she knocks him back can you imagine the argument she would carve him up\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Dani Daniels you are a good woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small There's not a guy on planet earth that would feel comfortable with \textbf{woman} that's sucked lots and lots and lots of cocks and who's had lots and lots and lots of big cocks up her ass. Even a guy that's paid to do it in a porn movie would be on edge doing something like that. Would you like some slut that's been gang banged by ten guys at once, What if you saw some gal that's had triple penetration by three guys at once that aimed their cocks at her face and all three shot their huge big mother fuckin' load's all over her face and her tits and then fucked her some more after wards, would you still like her? I mean it's its real hard to feel at ease with some \textbf{chick} that routinely has cum drippin' off her chin while shes gettin' fucked up the ass at the same time. Well think about it fellas' how would you feel around a gal like that!\normalsize   & \cellcolor{green!5}Chick, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/168 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Uh yea im a "porn star" cause im lazy af and \textbf{dumb} and cant even boil water\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Gives her ass and sucks dicks for money and than talks about integrity and respect.......! WTF is this man....! She's \textbf{nothing} but an eaten candy wrapped up in New packing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small OK, you will not date a person, not in the industry, "civilian", but then no fucken way with a \textbf{sex} actor/actress? So who do you date? Ok someone with similar goals? But you do not have any? Jesus, catch 22 much.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small "I have \textbf{sex} with a lot of dick... I mean I fuck huge penises"...geez, you can't get a decent man when you're proud to be a vile, disgusting potty mouth. And btw, I don't fuck \textbf{pussy}, I make love with women.\normalsize   & \cellcolor{green!5}Sex, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small Ten years from now she'll be an \textbf{old} shoe asking God, "What have I done to myself." Perversion is not glorious.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Lol everyone's live is completely meaningless, in a couple million years our star is going to be a \textbf{r\textbf{ed}} giant, explode and kill the earth will know it and end humanity or maybe if we got lucky an asteroid or an apocalypse would end us and then there would be \textbf{nothing} just complete darkness for all of us but might as well use the time we have for something we love instead of using it for something we hate.\normalsize   & \cellcolor{green!5}Nothing, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}3/79 & \cellcolor{green!5}3.797 \\  \hline
  \cellcolor{green!27}\small How is it meaningless? A secretary just files papers but you're not hating on them. Fuck off and let them live their lives. You prob. have to jerk off to a pic of your mom because no \textbf{woman} wants your crusty ass.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small How is her life meaningless? LOL she literally only talked about her work and dating, you don't hear anything about her life outside of that. Pathetic, cant take a \textbf{woman} make her own decisions about her body.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small meaningless? lol, you nutter\normalsize   & \cellcolor{green!27}Nutter & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small There are some hateful comments here and some insightful comments regarding duplicity. I have watched porn, lot's of it but less now. I admire that Danj is intelligent and secure enough to know that "enhancing" her body is a mistake. It is a mistake made too often by very attractive girls with A Cup, B Cup and even larger breasts and enhancements are, ironically, MORE noticeable if the girl is naked.Dani is a sincere, excellent performer and has directed as well. Many will judge her but to them I ask, why did God make us naked and why are some born with such a libido? Finally,  why are so many more interested in watching? When i was 20 I had the same libido and wanted to have \textbf{sex} with my girlfriend all the time. I also wanted to accomplish much.Dani strikes me as someone who makes good money satisfying her libido, is proud of her body (like most exhibitionists) and is ambitious to  accomplish more than just a list of starring roles. I won't speak for God as some have but Dani is not harming me and seems stronger than many "normal" people.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/195 & \cellcolor{green!5}0.513 \\  \hline
  \cellcolor{green!27}\small Schooled in the carnal ArtsShe is a vixen, Emotionally vacant, Decommissioned, Debunked like governmental provision, Her eyes slanted She couldn't give a shit for chivalry, Romance is dead, Affections are as welcomed As cyanide laced air, Read the epitaph drenched in a bloodbath, Deafened to your pleases of reprieve, Numb to your advances, Letters I wrote, Accomotose, Literally denounced, Your whole narrative, Disparaging, As she prances with such Mesmeric motion prowess, Impatiently waiting for the sun to set, To take another befuddled victim to bed, For it is promiscuity not monogamy, Which is her  modus operandi, Rose tinted romanticist and sentimentalists Need not apply, For you are not exclusive, But a mere vessel in her tantric transfusion , She just wants to fuck, Unless your emotionally vacant thug, Bring funds, You will inherent a bounty of illusionary love, Through barber wired and Maya, Even if you sat on celestial clouds, You won't get any higher, Honey , she's not that way inclined, Or wired, If you can see beyond the satire, Your eyes the window to a tortured soul, Begrudgingly I scream, No one can hear, Unnerving silence, My heart you devoured, Like a manical villianess, Now it's my self pity, You encircle incessantly, A sultry snake charmer, With indefinite evil karma, Now I quiver in the realisation, Yet another mistaken millennial, Love fool who got schooled, Elegant egotist, Ascencensed in the upper echelon, Of the dark arts, More concerned with money and Revelon, Only now I realise it's not the \textbf{sex}, But my spirit that was slept on,\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/260 & \cellcolor{green!27}0.385 \\  \hline
  \cellcolor{green!5}\small The perfect interview.. \textbf{Dumb} interviewing the Dumber ...Obviously there intelligence is at the bottom of the shit pile – apart from that well done.. \textbf{dumb} n dumber\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/28 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small MJ Stark black\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@Crossfire Games   ...why you keep saying \textbf{black}, dummy? She married a white guy.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small theres no dick size to make a \textbf{woman} happy they pull babies out of them\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small She needs to stop associating \textbf{sex} with relationship.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small one day she wakes up..... and \textbf{nobody} might be there.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@KING \textbf{BUCK} shes retarded\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@KING \textbf{BUCK} ofc she is smart be a horn is the dream of every intelligent girl I agree with you do you have any sister or I can call your mom for a little fuuck with money is that ok?is not bad right?\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Black Benny Hill holy fucking shit I'm crying 😂😂😂😂😂😂😂😂😂😂😂\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Taking 100 dicks a month would make anyone empty (\textbf{pussy} full of dick but empty in the soul) That's why 99 of porn stars are addicted to drugs and dead by 30\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Black Benny Hill fuck off you bitch\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Black Benny Hill shut up\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small +\textbf{Black} Benny Hill If she's so intelligent, why is she in that business? Oh I know, she probably does \textbf{black} guys on camera, lol.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small +Ceedat ! \textbf{Black} Beeny's little brain is full of white \textbf{pussy} because his \textbf{black} women look repulsive.\normalsize   & \cellcolor{green!27}Black, pussy & \cellcolor{green!27}Ethnicity - Black, Nationality - Chinese & \cellcolor{green!27}3/17 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small if she was smart which she probably isn't to resort to this lifestyle but maybe it is only money for her and not because she is to \textbf{dumb} for other work, anyways if she was smart she would be banking everything she makes for that day when she is not desired anymore and will not be able to attract anybody because she has done \textbf{nothing} but fuck her whole life( which means you won't be getting any other job) she will need that money to live off of and enjoy her cats.\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/92 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small yeah she married a \textbf{old} man\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small After 10 years, she'll move to "\textbf{Old} and Young" category.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small What? In 10 years she's not gonna love see anymore? Pls mate, I will still love having \textbf{sex} even if i'm 80.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Suppose if every pornstar ask some money for every view we see daily, by this time the industry would be so rich than Aramco, \textbf{Apple} Inc.. Still they work for cheap, we enjoy porn rich\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Ankit Bhatia \textbf{indian} guys have great knowledge about these porn queens.Thats why sunny leone taken shelter in indiaProlly every \textbf{indian} is becoming a potential rapist ,which is very bad for india Concentrate on your study ankit and not on these bimbo's ,they will get you to nowhere .\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small she really did get married with some \textbf{old} fugly dude and now she's only doing \textbf{lesbian} porn\normalsize   & \cellcolor{green!5}Lesbian, Old & \cellcolor{green!5}Age - Over 65s, Sexual Identity - Female homosexuality & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small jorge pearl she will love in 10 years unlike your \textbf{old} ass\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small The adult business has finally come mainstream.I think it's a good thing as long as people are not coerced or forced into it. We are in fact all voyeurs and brave people like Ms. Daniels no longer suffer public shame as they did years ago.I think she is beautiful and love her girl on girl stuff. Porno, (wrongly named) is usually a self \textbf{sex} aid and what is wrong with that?Surveys show that both genders access sexually stimulating information on a regular basis.I was reading Cosmopolitan regularly by the time I was 14 or so. Anyway I find hunger, lack of access to education, medical aid, and brutal dictator regimes pornographic.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}\small Empty headed twenty-something who fills her fanny for money. Can't listen to her self-absorbed rubbish.  ('Civilians'.  Just plain \textbf{dumb}! Who is she listening to?) You want her to be the mother of your kids???\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small They are either terribly stupid and maladjusted or have \textbf{mental} issues - who else would be doing porn?\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Stephen Dedalus those who are below the poverty line. Those desperate poor people who got attracted by money. You wouldn't have \textbf{sex} with me for a grand if you are already rich, right?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Stephen Dedalus Some choose to do it as they find it empowering. Look up the \textbf{Sex} Positive movement to gain more insight.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@Stephen Dedalus I would and pretty well put 2gether .... sort of ... Ok I'm \textbf{crazy} fuck it, but I would\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Trust me .....if you want to be happy ..marry pornstar...they got \textbf{nothing} to hide as long as u love them .\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Just think of an alternative job before  you hit 30 or 35 years \textbf{old} .\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Guys don't want to date pornstars because you Guys are like objects but like an \textbf{old} object that have been used for years\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Well, she is getting paid to do that stuff, isn't she? So I guess it is a job. If there was a job where get paid to do \textbf{nothing} but sit on your ass all day and stare at a wall, would you call that a job? Most peoples' definition of "job" includes the word "labor". Are you not working hard and doing heavy physical activity to ride a cock or pound a \textbf{pussy}? A lot of people would also assume that working at McDonald's isn't a "real" job just because you're flipping burgers all day and then claim that sitting at an office desk while typing on a computer is considered a "real" job. It doesn't matter what you do as your job, you're still getting paid to do it. So yes, the porn industry is a "business" who are paying those pornstars to do their "job". Would you much rather have the pornstars be called "actors"? Because about 90 of the time, that's what they're doing. And as far as I know, acting is a "job". Look at all the actors who get paid for acting in all of those big budget films.\normalsize   & \cellcolor{green!27}Nothing, pussy & \cellcolor{green!27}Age - Youngsters, Nationality - Chinese & \cellcolor{green!27}2/195 & \cellcolor{green!27}1.026 \\  \hline
  \cellcolor{green!5}\small Well they are getting paid for \textbf{sex}, which kind of what a whore is.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small thats... her job. thats literally what her job is calledare you legit \textbf{disabled}? what the fuck rofl\normalsize   & \cellcolor{green!27}Disabled & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Whore and pornstar two different things. One fuck anyone for Money and other just other pornstar. Ya but after all this much of \textbf{sex} partners, \textbf{nobody} gonna be with that person. I mean that's the only thing which very much private.\normalsize   & \cellcolor{green!5}Nobody, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small 1.a person, in particular a \textbf{woman}, who engages in \textbf{sexual} activity for payment.synonyms: call girl, whore\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small +alok Mishra not trying to be disrespectful Dude but someone that is being paid  for having \textbf{sex} is technically a whore.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@shut Up yeah open minded...all holes are opened for a \textbf{fat} nut for \$\$\$\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small a job with  the risk of getting  pregnant or get HIV ,and facing \textbf{sex} humiliation is like a dream job.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} are you? So disrespectful, what the fuck? :P\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small These people are \textbf{mental},relationships will never work and who wants to be around someone so vulgar!\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small whore....come on first of all she is a Human being... and thats a job... brazzers paid her for that... and more imp thing she entertain us...so some respect dude... all pornstars are human being not \textbf{sex} dolls... they also have feellings, emotions like u, me \& others...\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small If you think about it and research it whores have saved humanity 3 separate times. 3 different times humanity almost went extinct and whores came threw to save the day by repopulating. So instead of thinking of whore as a bad thing you should look at it as a good thing. Plus no one likes a stuck up bitch who keeps her \textbf{pussy} locked up only for one man.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small People who ridicule people in the \textbf{sex} work industry are so fucking childish and stupid. Grow the fuck up! You sound like a fucking child. Especially since you have probably beat your little pathetic dick to her a 100 times this week.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Fif Jason it is regular job you \textbf{dumb} fuck a job that pays more than you will make in a year\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small eric you are such a dumbass, porn is in a controlled environment, infact its safer to have \textbf{sex} with them than these regular girls you meet in bars that you dont really know. you think if you pick up a girl in a bar who has HIV will outright tell you that she is infected?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Fuu Sama A 'controlled environment'?? LOL!!! Oh, that's a good one!!! You think the fact that porn stars are regularly tested for STDs means they don't get them? That's retarded. That's just like saying that weighing yourself every week will keep you from getting \textbf{fat}. The fact is that STDs are rampant among porn stars and here's one article among many to prove it:  [LINK]  come back here when you've grown yourself a functioning brain with some decent critical thinking skills.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small shadowninja81500 You're at least the second person to put out that \textbf{dumb} idea on this discussion thread. Getting tested for STDs does not stop you from getting them. That's exactly like thinking that weighing yourself will keep you from getting \textbf{fat}. They have \textbf{sex} for a living. There's \textbf{nothing} safe about it.\normalsize   & \cellcolor{green!27}Dumb, Fat, Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}4/52 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small +Dude What? Who gives a shit? Getting tested for STDs only proves that you don't have one right at the moment. It doesn't mean that you won't get one eventually when you're having \textbf{sex} with dozens of people whom you know \textbf{nothing} about. The minute you test positive, all those negative test results in the past mean \textbf{nothing}, and your chances of getting one at some point are very high when you're having so much \textbf{sex} with so many different people all the time.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}4/84 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Eric Liestoh Weighing yourself every two weeks won't prevent you from getting \textbf{fat} but it will let you know when you've become \textbf{fat}.Using analogies and not even understanding them,jesus.If she's positive for something then her career is over and if it weren't so the porn industry would be full of dead or hospitalized people.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small CreedManiac I'm not using it analogy. I'm using a directly relevant parallel. It isn't even really very different from what I'm talking about. The fact that you tested negative for an STD at a particular moment means absolutely \textbf{nothing} when you're continuing to engage in the same behavior that will very possibly lead to your contracting one. And what happens when you do test positive for an STD? That's the real issue here, isn't it? When that happens, all those negative results in the past don't amount to shit. The implications are the same for you and everybody else that you've had \textbf{sex} with. Sure, you don't have an STD...until you do. I understand perfectly well what I'm saying. You're not even making an argument here.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/126 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small \@Eric Liestoh Yeah and the risk is there whether you have \textbf{sex} with a normal person or a pornstar but you're saying that pornstars are more exposed to STDs since they have \textbf{sex} everyday. You would be right if you had proof that even if someone in that field tested positive they would be free to continue working.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small CreedManiac Whether or not they're allowed to continue working after they test positive for an STD has absolutely \textbf{nothing} to do with it. The damage is done whether they continue working or not. And there is plenty of proof out there to be found that people who have \textbf{sex} for a living, be it on film or on the street, are in fact at a far higher risk for contracting an STD. No question about it. Here's just one link to show you what I'm talking about:  [LINK]  do the research for yourself. I've done enough thinking for you.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small the one who examines her definitely make a \textbf{sex} with her...isnt it?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small +Honfy Lam If you honestly believe that, you're a moron. \textbf{Sex} workers are so much more likely to catch a potentially deadly STD than anyone in any other profession, it's not even funny. You're making a completely idiotic claim.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small +sportagus3 Great. Go and have \textbf{sex} with a few and see how that works out for you.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Derek D. Closed system, my ass. They are still free to have \textbf{sex} with anybody they want outside of their job, and just how careful do you think these people really are about who they have \textbf{sex} with, when they have \textbf{sex} for a living with total strangers? Don't be stupid.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/51 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small My god you are a stupid one arent you? If all pornstars get checked for STDs and they are clear to do their job, when they have \textbf{sex} with each other they wont just suddenly contract and STD. Dont be stupid. Your analogy makes no sense hur hur if you constantly check your weight it wont stop you from getting \textbf{fat}, are you stupid? Just think for a second about your retarded analogy. The point of the weight is to not stop be from getting \textbf{fat} its to show that I am NOT \textbf{fat} you fucking idiot. They obviously are still free to have \textbf{sex} with anybody outside of the job but why the fuck would they take the chance to contract and STD that would obviously put them out of a job you fucking idiot? So we assume pornstars want to keep their job and are responsible for everyone's health in the industry. Stop being stupid please it harms people.\normalsize   & \cellcolor{green!27}Fat, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}5/161 & \cellcolor{green!27}3.106 \\  \hline
  \cellcolor{green!5}\small Eric Liestoh I wont deny that pornstars can contract STD's based on the fact that they have \textbf{sex} with different people for a living and partake in orgies and so forth, but I still think engaging in unprotected \textbf{sex} with a pornstar like lisa ann is much safer than protected \textbf{sex} with a random stranger\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small They get checked multiple times a week. Remain fucking retarded if you truly believe otherwise. You say you wouldn't touch her with a pole because you've actually come to terms with only being allowed dirty peasant \textbf{sex} with your local swamp monsters. Stupid \textbf{faggot}, your statement was retarded but you're too ashamed to admit it.\normalsize   & \cellcolor{green!27}Faggot, Sex & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small They have \textbf{sex} with other pornstars which DO NOT have STDs . If they have \textbf{sex} with someone OUTSIDE the industry, that would make them NO DIFFERENT than \textbf{common} women that also do the same. So you can be sure to not catch any STDs if you have \textbf{sex} with one. Besides, they LITERALLY earn money by having \textbf{sex}, so they are even more careful, as one mistake can cost them their career.\normalsize   & \cellcolor{green!5}Common, Sex & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}5/73 & \cellcolor{green!5}6.849 \\  \hline
  \cellcolor{green!27}\small In one way i feel sorry, she is a human being like everyone else and don`t get the chance to date someone. I guess \textbf{nobody} would if they are not in the same business of course.But she should not complain either, she knew this from the first start that she probably never will live a normal life. She claims that she would be jealous if her partner cheat on her.Her other option is to find a boyfriend or future husband that are into Polyamorous Relationships. This is my opinion and Sorry all for my bad English.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small Interesting, but understandable. Finding someone that isnt jealous or not to emotional is tough. It would be best to date people in the swinger community, little to no stress and good \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Nitish Bhardwaj Yahi toaapki soch hai....Woh uska kaam hai....Aur uski identity ko aap uski kaam se judge karte \textbf{ho}....????Woh porn films karti hai to kya woh buri hai..I respect every human being from a PornActor to a ToiletCleaner....GodBlessU..\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Maybe its hard to date because you are a thot\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Syn Cloud Only someone with \textbf{zero} self respect would defend another hoe.😷🤢 And don't come at me with the whole 'you're a repressed prude' crap please.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Is she related to Stormy Daniels? Who cares if she didn't have \textbf{sex} with , at least, 5 Presidents.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Guys have to be real ass hole or hard up for \textbf{pussy} to marry or date a porn star, firstly she is trained to accommodate and have \textbf{sex} with men with only men with large penis every day beating and abuse occur while having rough \textbf{sex} so what ever Dani Daniel says is true she cannot find a date ,secondly u have to get out of prostituting your self for money and call that a job, thirdly u need a therapy and a new make over a new look and a new name and trust in God that foolish man who desperate for a \textbf{woman} will marry u or date u ,word\normalsize   & \cellcolor{green!27}Sex, Woman, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}4/112 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Most viewers are \textbf{Indian}?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Nasty woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Nobody wants the town bike, this bitch is deluded.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small maaaan,  this world is fucked up.   This bitch is totally \textbf{crazy}.  trying to justify her whoredom with "performance" or "Job"   and still demands the other to get tested.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Its a toxic lifestyle period. And despite having \textbf{sex} daily..... it must be a extremely lonely existence.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small She must be on Blacked.com if she's taking all of those huge \textbf{black} cocks!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I suppose it can be difficult for a bloke to think ur actually enjoying \textbf{sex} with him\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small she's \textbf{nothing} but trouble!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small who would've thought that \textbf{sex} tied to emotions\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Makes guys uncomfortable?  You mean guys gag at the thought of touching your diseased mind/body,  You present as a functional illiterate with no  morals.   The main reason guys even watch porn is for the degradation fantasy.  This is why as all genres of porn became available straight \textbf{sex} even huge dicks up small asses is now boring.  Dani is almost at the next career step, caning, whipping, nails, piss, shit, blood.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small All these fake laughs by the \textbf{woman} that interviews her....\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{misogyny} is amazing here. A male pornstar is treated as a STUD and no one comments about how SAD his life is. But a female one is trashed and her life is less WORTHY suddenly, she is leading a SAD existence. You have the sad existence here.\normalsize   & \cellcolor{green!27}Misogyny & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small In one breath this \textbf{hooker} tells "civilian" men to basically get over it.  Then in the other breath she tells us that performers get jealous of each other.  She is a \textbf{lunatic}.  These people forget, they are product...not people.  LOL and when they are no longer good product, they don't get to come back and be people.  You are a subculture.  Deal with it.  Go to your holes and stay there.\normalsize   & \cellcolor{green!5}Hooker, Lunatic & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small Having \textbf{sex} with her is most likely resembles throwing a hotdog down a hallway.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I find this \textbf{woman} very intelligent.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Pornstars have to get tested for HIV every two weeks now. So why is it hypocritical for her to ask the same thing in return?I mean, I dont have \textbf{sex} with anyone unless I see those test papers so does that make me a hypocrite?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small When people lose touch with reality and everything that was  normal. This is the warp reality they live in and their view of life is sad. Hey \textbf{chick} look up all the porn people that have committed suicide. It doesn't end well.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Nobody\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Had Jesus said those words Jewish priests would have gladly stoned the adulteress if for \textbf{nothing} else but to prove their purity. He used the words "let the one who has never sinned" which impossibility is the corner stone of all organized religions.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small At this point it is not really about who is "clean and pure" enough to call out this young \textbf{woman} for her remarkably shameless \& deluded remarks, SS S, though I admit that I find the mercilessness \& judgmental reaction of some on here who most likely regularly \& voraciously view pornography to be quite appalling, pathetic, \& somewhat disgusting, but it is about stating reality in the face of fiction \& for the sakes of the ignorant \& the vulnerable.     To illustrate, can you imagine if -- God forbid -- you had in an accident cut off your dominant hand at the wrist or perhaps even, horrifyingly, in the throes of some \textbf{mental} lapse in judgment like due to intoxication suffered such a debilitating injury \& then you encountered somebody grinning about, laughing about, \& claiming that their own similar injury is a mere joke \& that they intend to, "for fun," amputate their other arm \& also a leg, because losing one's limbs is somehow a plus? Would you remain silent in the face of such insanity or would you openly protest?\normalsize   & \cellcolor{green!27}Mental, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/184 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small so simple business is business ... they need cash and fame so what fuck my ass and \textbf{pussy} cat\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small And shame on the man that actually wants to be with this tramp\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Cmon now once your in the business that's all your good for. Only someone \textbf{crazy} would marry these hoez\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Someone should tell her guys won't date a \textbf{woman} who has \textbf{sex} with other dudes for money. Not because "the guys I film with are bigger than you." SMH\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small dani daniels all u people have no heart and are \textbf{mental}. Ofcourse dating won't work, when heart is involved. You need to find a respectable job\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I was watching fortnite, and somehow here I am listening to some \textbf{chick} say she has taken multiple dicks the size of a forearms.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Pip Santos. You say men are whores yet the oldest job in America is prostitution. These women in porn are not very pretty for the most part, but there is a handful who are a definite gift. I am 53yrs. \textbf{old}. In college at SLO in California, I came across a beautiful girl who was just starting in porn to pay for her books and rent to share an apartment.. She was very shy and helped me out with getting my clothes washed, getting up on time for my classes, only dating the right girls, Siobhan was wonderful. I graduated because of her.. We never made love, nor did I ask questions about her " job".. What we did learn was her and I could sleep together for 2yrs. and hold one another, kiss for hours at a time, and love each other with our " Hearts🗽\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/147 & \cellcolor{green!5}0.68 \\  \hline
  \cellcolor{green!27}\small ha ha , men dont like their partners having \textbf{sex} with other guys regular , no fucking shit they dont .\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small This poor girl doesn't know what she doesn't know.  She has no self esteem and no self care or self value.... She cannot see the self destruction and damage she is doing to herself.Performing in porn is not performing.  It is low down fucking and the lowest form of \textbf{sex} than all beings on earth.  Hopefully she will grow some self worth and stop the wrecklessbehavior before she gets married and has children otherwise her marriage and parenting will be like a family where mom and dad are on a runaway train doing cocaine.....:(\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small she a \textbf{slag} that has 3 way and gangbangs  to pass around her crabs and all that shit hoe dont give um no treatment\normalsize   & \cellcolor{green!27}Slag & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I personally think it's very stupid for a porn star to think or have the belive they can also date and enjoy a normal healthy fun relationship....I mean like how \textbf{dumb} is that😟\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small You know I wouldn't even call them actors honestly though 😂 I mean porn wasn't even a thing back in the day either, but hey you got to make your money somehow, just your family and friends plus the people you date, will all look and see you differently, and it's not about entirely just being insecure no no, but she's not completely wrong, there's more to it than that, I mean there making \textbf{sex} basically an object, like it's \textbf{nothing} special in any way\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/85 & \cellcolor{green!27}2.353 \\  \hline
  \cellcolor{green!5}\small Remembered.....Top Unintentional Kek of all time.  By the time I've gotten to this comment...I've already forgotten what she looks like.  This beast is meaningless.  A thousand years from now...all her images will have been scrubbed from the consciousness of mankind.  All this porn will be \textbf{nothing} but a minor curiosity of what the chimps did back in the day.  Yet Mozart will be more famous and loved then ever before.  This thing is at best an egg donor.  But the future has no place for low IQ people, so she is the last hurrah of her genetic lineage.  I don't see it going much further.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small I'm also confused on the cheating part?  If my boyfriend cheats on me?  Uhhhh why would you care bitch?  You fuck dudes on the daily, aren't you already cheating?  And don't say "It's just work" because this \textbf{dumb} bitch just said, she'd get jealous if she dated a male pornstar, because she would know that those other girls were fucking her boyfriend or husband, lol.  This bitch is \textbf{crazy} as hell man.\normalsize   & \cellcolor{green!27}Crazy, Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small So if this \textbf{dumb} bitch is a porn star and takling about it's hard to date civilian guys because of the work she does, and they would get insecure about her fucking guys with big dicks and fucking lots of guys.  Then why the fuck would she get jealous her dating an male porn star?  Shouldn't she understand it's just work?  What would you be jealous about?  I thought it's a understanding in the "Industry" as she says.  That's it's just work?  Why she get jealous of her pornstar boyfriend fucking some other \textbf{chick} in the ass if it's just work for everybody involved in the industry anyways?  This bitch is \textbf{dumb} af.What dude in their right mind would date one of these low life pornstar sluts? lol.  You gotta be fucked up in the head yourself if you date a \textbf{chick} like this or marry one.\normalsize   & \cellcolor{green!5}Chick, Dumb & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/148 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small awww enjoy ignore the \textbf{dumb} ass comments\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small looks like a \textbf{transgender}.\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small keep being blind\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small She is ruined. She took too many \textbf{black} dicks. Not a very special \textbf{woman}. Just a prostitute. By the way she is married now.\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small There are some very good looking women in porn. But I couldn't see myself making one my wife There is a big difference between a brand new car and a \textbf{old} used beat up one.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small this is soo weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Actually you are religious, Gabi X. Every human being is religious. We are each comprised of body AND spirit. In the spirit we form memories \& store of education \& decide how we are going to relate to phenomena around us; indeed, it is a spiritually based system we operate from \& such is idiosyncratic while also in nature categorically conglomerate, for there are others who, even if not in every particular, believe \& live according to the same form as another person does, according a specific spiritual system.     James simplifies the matter for us greatly in his NT epistle when he notes in James 2:27-28 that there is one "pure religion" \& that is the one that has Christ Jesus as its focus \& submission to Him as its priority while all other religions are deception \& destructive, no matter what pieces of truth they may have in them to make them each seem valid, wholesome, \& worthwhile.     You have rightly reacted negatively to this young woman's lack of self-respect \& shameless dysfunction as well as to the idea that one having one's private body parts \& \textbf{sexual} activities with or without \textbf{sexual} partners photographed \&/or filmed for public viewing is not "a normal everyday respectable job" because we humans are made in "the image and likeness of God" \& in our individual spirit's consciousness we do have an awareness of the phenomenon of wrong \& right \& can in generally determine what is wrong from right. In your consciousness, you are rightfully aware that \textbf{sexual} indiscretion \& promiscuity are not virtues.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/263 & \cellcolor{green!27}1.141 \\  \hline
  \cellcolor{green!5}\small And every single person has \textbf{sex}..\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small These comments!  I couldn't have possibly imagined the quantity and/or severity of judgments being made here in my wildest imagination! Thousands and thousands of people who are either religious zealots, moral crusaders, ethics visionaries, \textbf{misogynist} creeps, and even just plain ole' standard assholes.  Every level of dirt-bag seems to be pretty well represented. Congrats planet Earth...you suck!\normalsize   & \cellcolor{green!27}Misogynist & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Geee....I have no idea why I would have a problem with a \textbf{chick} who has had a thousand more dicks than the average American/Western \textbf{woman}...and that's a lot of dick. No ability to pair bond. I couldnt care less about the bbc you've had. I care more about the potential for me getting VD and your daddy issues impeding my life you psycho-tramp.Yes gentlemen, this is modern-day feminism...empowering western-women by saying it's ok to have 1000 miles of cock and saying it's men's fault because we're 'insecure' about it due to large penis envy.\normalsize   & \cellcolor{green!5}Chick, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/95 & \cellcolor{green!5}2.105 \\  \hline
  \cellcolor{green!27}\small Preach!  Couldn't have said it better myself.  This \textbf{dumb} bitch thinks that a dude should be cool that she's got cock in her mouth daily, lol.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small leodalatinolover black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small You know, though, Christpher R \textbf{Fritz}, in all honesty, how is "dating," with what "dating" means in this day \& \textbf{age} \& in many societies, especially in America, not itself prostitution? If we are to be really honest \& technical, even if literal money is not a part of the transaction of \textbf{sexual} intimacy \& activity, in the absence of a marital commitment to be with that one person for the lifetime of each of the two of the marital union \& yet \textbf{sexual} intimacy \& activity is included in that temporary relationship, that is the currency that is being exchanged -- one's precious private parts.    And then when the "dating relationship" is over \& each moves on to another "dating relationship," what's that? In this day \& \textbf{age} \& in cultures of with no morality governing, virginity before marriage is quite sadly nearly nonexistent. Most who have come to the decision to become married come to the decision to be married only after having interacted with the mouth or genitals of at least one other person before meeting the one with whom marital vows will be exchanged \&, most often, with far more than the one premarital \textbf{sex} partner.     In fact, the Greek word translated "fornication," which is the English word used to denote "\textbf{sexual} intercourse with one to whom one is not married," is porneia. Sounds familiar, doesn't it? Yeah, in fact, pornography is derived from the word porneia.\normalsize   & \cellcolor{green!27}Age, Fritz, Sex, Sexual & \cellcolor{green!27}Age - General, Gender - General, Nationality - German & \cellcolor{green!27}7/241 & \cellcolor{green!27}2.905 \\  \hline
  \cellcolor{green!5}\small I believe their job is not as easy as having ordinary \textbf{sex} which would look too mechanical and below standards. Lights, cameras, positions, repeating scenes, not covering cameras view and exposing exact body parts that director wants, not to mention tests, preparations and inevitable actors incompatibilities...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small This may be a stretch, but... dudes may possibly be a little hesitant to date you, Dani, because...You're a whoreIf you're still confused, consider that maybe just maybe, some people hold that odd opinion that \textbf{sex} is rather private, intimate, and personal. Shocking, I know\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Disgusting shit she is laughing about being a whore she is a stinky looser and anyone who has \textbf{sex} with more than one person is shitly disgusting.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small last 5min of my life listening this bimbo\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small she's not faulting the guy she is saying, when someone has \textbf{sex} for their job, their significant other can get jealous  very easily. This applies to both normal people (1:16) and adult actors (2:35)(3:00). She is not saying the guy is wrong for being jealous because she can feel the same when in the same position. Therefor "dating doesn't really happen".Please don't slander someone who actually thought about what they are saying, there are so few of those kinds of people left.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small Ian RustNo question most guys couldn't deal with it.  But it's not so difficult or complicated, personally I'd give it a go if she was fun, just forget about what she does for a living if it bothers me, I'm not looking for a virgin.  Frankly I prefer a slut.  As long as she is honest and upfront about it, you know what your getting into, pun intended.  Deal with the circumstances or avoid it.  Simple.  Everyone has been with many others it's no big deal to me if it was yr.s ago or yesterday.  I have been involved with \textbf{crazy} chicks and that's a hell of a lot worse than this girl, and I don't even regret those, I just wouldn't knowing repeat them probably, but they were great fun too much of the time.  Life is short, take a chance.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/143 & \cellcolor{green!27}0.699 \\  \hline
  \cellcolor{green!5}\small yeah because she is a selfish bitch that wants a lap dog as a men.she is so full of herself that she thinks she can fuck all she want but when the guy does not like it. he has low self esteem....\textbf{woman} logic.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small She's admitting that no one wants to date a guy who sticks his dick into 100 whores each month and no one wants to date a \textbf{chick} who takes 100 different dicks a month.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@Zaea you're definitely a \textbf{dumb} feminist bitch cuz you sound sexist\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small LOL dude why would you want to date a hoe? It's not confidence it's \textbf{common} sense. YOU KNOW SHES GUNNA BE FUCKING OTHER DUDES AT WORK! get out of porn if you want a serious bf or date another porn star who he in turn he will also fuck a lot at work.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Sex is natural \textbf{sex} is good. Not everybody does it but everybody should.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small What's the difference between a \textbf{hooker} and a female slut like this pornstar \textbf{Nothing}.\normalsize   & \cellcolor{green!27}Hooker, Nothing & \cellcolor{green!27}Age - Youngsters, Gender - Female sexuality & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I am sure, for u, nearly all the women who are not covered from toe to head in \textbf{black} are whores.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I'll date yuu for bout 3 months cuz I get bored fast..I don't mind yuu having \textbf{sex} with other guys I'm not that insecure!!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I don't trust you?  Really this \textbf{chick} has all kinds of dick being pounded into her and she wants trust.  Filthy mouth 🐖pig.  Steight to hell she's going.  Wow.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Whore on camOffcourse \textbf{nobody} will love you\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Perhaps intercourse was meant for child production. Maybe, because it has the power to spawn life, and give meaning to all the trivial and mundane things we do... maybe it is an expression of devotion. Maybe if you express your devotion to everyone then you're not really devoted. Maybe when you are \textbf{old} and you have been replaced by a younger girl, you will realize that you objectified beauty rather than leveraging it to forge a big family. The \textbf{sexual} value of a person is scattered in the wind by your form of sodomy. You will have no offspring to cherish your true worth even in your \textbf{old} \textbf{age}. The grandmother of the traditional family is just as valuable as her sexually mature daughter or the daughters precious toddler.\normalsize   & \cellcolor{green!5}Age, Old, Sexual & \cellcolor{green!5}Age - General, Age - Over 65s, Gender - General & \cellcolor{green!5}4/129 & \cellcolor{green!5}3.101 \\  \hline
  \cellcolor{green!27}\small You know it really broke my heart to see such a smart, beautiful and articulate \textbf{woman} make a life decision to become a porn star but even worse, acting so nonchalant about it all. She makes it seem as if having a big dick inside all of your cavities all at the same time is the most natural most normal thing to do. She has the potential to be so many other more positive professions in life even to marry a decent life partner and have a family then to degrade herself down to the lowest \textbf{common} denominator. What a shame and what a waste...... I really wonder why would a person like her end up in such a degrading job. What was it that ticked in her mind which motivated her to be in the porn business. Was it low self esteem, \textbf{sexual} abuse as a child, demonic possession? This girl  is someone's daughter, niece, cousin and sister what a shame to her family.\normalsize   & \cellcolor{green!27}Common, Sexual, Woman & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}3/165 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small man this girls does the \textbf{crazy} kind of porn tho\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Regardless of what these porn stars call themselves, be it men or women, technically they're actually just high paid whores. And most of the women in porn, without makeup on, they look \textbf{nothing} like what's seen in the videos. In truth, I don't know how they can live with themselves, doing anything and everything when told to by the directors.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small You Do This because The Government has Sent All the Good Jobs Overseas And They Let You Get Abused As A Whore!!  Jesus Lovs You ane Wants To Save You And forgive You but You Need To Repent!!!  swrc.com  endtime.com  theprophecyclub.comjesus is coming soon. matthew 24. isaiah 17. receive him and eternal life righteousness in jesus name. john 3. 2 cor 5:17 to 21. romans 10; 17 to 20. be filled. healed acts 2. 3. swrc.com endtime.com don't take the 666 microchip. revelation 13 to 18Free KJV Bible PDF Download   [LINK] There may be some controversy in mel gibson's movie the passion of christ, but one thing is not a controversy and that is being INChrist.  If you are you would know it. Its like being hit with lightning.In Him was Life: and the Life was the Light of men. John 1:4  Do you know if you are In Christ. It is called being saved beingborn again, receiving Jesus. The only way for you to be "In Christ", is to let Christ be "in you". In other words you need to receiveJesus as your Lord and savior. When you receive Him into your heart and believe in Him, He gives you His Life and you become united toHim.  Just confess that Jesus is your Lord and believe that He rose from the dead to make you righteous and you will be saved (Romans10:9,10).When you do this, this is some of the things God will make and give you In Christ!!!!1. I am a New Creation. 2 Cor. 5:17.2. I am Delivered. Col. 1:13.3. I am Righteous. 2 Cor 5:21.4. I am Sanctified. Heb. 10:14.5. I have Boldness, Access. Eph. 2:18, 3:12.6. I have Eternal Life. John 3:36.7. Always Triumph. 2 Cor. 2:14.8. Can do all things in Christ. Phil 4:13.9. Christ, my wisdom. 1 Cor 1:30.10. Blessed with all Blessings. Eph 1:3.11. Needs met by God. Phil 4:19.12. Have Freedom. Rom. 8:2.With Christ1. Was Crucified. Galat. 2:202. Died. Col. 3:3, Rom 6:3.3. Was Buried. Rom 6:4, Col 3:12.4. Was made Alive. Eph. 2:5, Col 2:13.5. Conquered with Christ. Col 2:15, Heb. 2:14.6. Was Raised. Ephes. 2:5, Col. 3:1.7. Was Seated. Ephes.2:6.  How to Receive Your Heavenly Prayer Language  His Inspirational Gifts:  Manifestation and Church Gift of Divers Kinds ofTongues...1Corinthians 12:4-11  Mark 16:17...Divers kinds of tongues is supernatural utterance by the Holy Spirit in languages never learned by the speaker, notunderstood by the mind of the speaker, nor necessarily always understood by the hearer. Speaking with tongues has \textbf{nothing}whatsoever to do with linguistic ability; it has \textbf{nothing} to do with the mind or the intellect of man. It is a vocal miracle.  Tongues is primarily a devotional gift  Jesus told his disciples, "After the Holy Ghost has come upon you, you shall receive power" (Acts 1:8). The evidence of this baptism isthe gifts of the Spirit, with tongues almost invariably comingfirst. There are various kinds of tongues. One type—the prayer and worship language—is for private use and personal edification. Itdoes not need to be interpreted. In fact, Paul informs us that although he spoke in tongues more often than all the Corinthians,when he did, his understanding was unfruitful. He describes his use of a prayer language as praying "with the spirit" (1 Corinthians14:14-15). This prayer and worship language is indispensable for every Spirit-filled Christian.  Public ministry of tongues  Paul teaches that only a few believers will be used in what we would call the public ministry of tongues, because he said in 1Corinthians 12:30, "do all speak with tongues?" Some take that out of context and say, "Speaking in tongues isn't for everyone. You canbe filled with the Spirit without speaking with tongues." However, we must remember that Paul is talking about the ministry gift oftongues, because he began by saying, "And God hath set some in thechurch...diversities of tongues" (1 Corinthians 12:28). Then Paulasked, "Are all apostles?...do all speak with tongues?" The obvious answer is no. But Paul is talking here about public ministry. Weshould not be too concerned about our ministering in tongues and interpreting. We should be primarily concerned with maintainingtongues in the place where they principally belong—as a devotional gift to assist us in the worship of God.  Why should I speak in tongues?   Speaking in tongues is initial evidence of Holy Spirit baptism...Acts 2:1-4; 10:44-48; 19:1-6.  Speaks unto God...1 Corinthians 14:2.  Speaks in mysteries...1 Corinthians 14:2.  For spiritual edification...1 Corinthians 14:4.  Build up yourself...Jude 20.  Pray for the unknown--don't know what or how to pray in anysituation...Romans 8:26-27.  Produces rest in our Souls...Isaiah 28:11-12.  Out of your belly shall flow the river of Life...John 7:37-38.  People often ask me why tongues is a \textbf{common} manifestation of baptism in the Holy Spirit. I tell them that if God is going to ruleus, He must certainly rule our tongues; it is our most unruly member. Just as we grab a bit to control a horse, God takes hold ofour tongue to assert His control of us.  Another reason He gives the gift of tongues first is to enable us to build our faith for the appropriation of other spiritualgifts...How are we to appropriate these gifts? Martin Luther tellsus, "Faith is the arm that reaches out to take the gift God offers." But our arm of faith is weak and short. So God's first gift is theonly one that edifies the user. With it, we can build up our arm of faith to appropriate other gifts we may need. That's why whensomeone with a great need comes to me, I find myself instinctively praying in tongues.  Because tongues, above the other gifts, is a worship gift, it helps us fulfill our primary reason for being: to glorify God andenjoy Him.  Folks always ask me, "Do I have to speak in tongues to receive the baptism in the Holy Spirit?" I give them evangelist DavidWilkerson's answer: "You don't have to. You get to. It's part of the package."  How do I speak in tongues?  Instead of telling people to ask for the gift of tongues, I urge them, with the words of the apostle Paul, to "stir up the gift ofGod which is in you" (2 Timothy 1:6).  1. You make the sound by furnishing the raw material. God helps you with the utterance. He helps you shape the sound of your voiceinto words. Acts 2:4 says, "And they were all filled with the Holy Spirit, and began to speak with other tongues, as the Spirit gavethem utterance."  2. Don't speak words your mind understands. As long as you do, your mind will remain in control.  3. Don't listen to yourself. Can you imagine a little child learning to talk? Does he say, "Ma-ma-ma-ma," and then stop with: "Ican't say that. That's not a language?" No, he just hugs his daddy's neck and prattles away.  swrc.comRod of God weapon used in New Haven, Taylor Michigan? [LINK] Trump is trying to Push the 666 Microchip.   swrc.com [LINK] Dr Ben Carson pushing 666 RFID Chip [LINK] Trump is pushing 666 Mark of the Beast swrc.com [LINK]  Voice to Skull Technology    [LINK]    swrc.comDid Trump Devastate California? [LINK]  …Fox Reports Govt Laser Weapons before California Fires [LINK] The Islam Catholic Church Connection Islam  [LINK]  …   IF YOU MISS THE RAPTURE Calif Fires [LINK]  …Free KJV Bible PDF Download  [LINK]  …Free KJV Bible PDF Download Read John 3.    [LINK]  …KJV Bible Dramatized  [LINK] Gospel of John KJV Dramatized  [LINK] Free KJV Bible PDF Download  [LINK] The Blood Covenant [LINK] We are King James Bible Users!!!    swrc.comNEW CREATION BOOK OBAMACARE 666 SCANNER [LINK] Obama 666 Scanner at Walmart, Virginia, Don't take the Mark of the Beast Chip! Revelation 13-18.Wal-Mart: "RFID Chip Obamacare Machines" YV3zwqnIfqNbAWonderful Name of Jesus [LINK] Salvaccion En Jesus Cristos! [LINK] Ten Reasons Not To Go Through The End Time Tribulation! [LINK] The Book of Ephesians KJV Dramatized Bible [LINK] Ephesians In Christ   [LINK] Ephesians In Christ 2   [LINK] ARE YOU IN CHRIST  [LINK] Healing In Christ  [LINK] Zoe Eternal Life  [LINK] Jesus The Healer  [LINK] Identification with Jesus  [LINK]  KJV Bible PDF Download Read John  3 Rom 10   [LINK] The Islam Catholic Church Connection Islam  [LINK]  … Gospel of John KJV Dramatized  [LINK] Identification with Jesus [LINK] Identification In Christ   [LINK] Christ The Healer Free PDF Download    [LINK] KJV Bible with Strongs Concordance Greek and Hebrew Dictionary   [LINK] Importance of Paul's Revelation [LINK] Identification with Adam [LINK] \normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}3/1457 & \cellcolor{green!5}0.206 \\  \hline
  \cellcolor{green!27}\small Rozli Yusof Definitely the second but how do you know whether the girl next door was never f*kd before? She might be sleeping with someone else while being in relationship with you.  Not talking about girls in specific but guys as well.  Sometimes I think these girls are better cuz there is \textbf{nothing} to hide and you have a choice for a GO or a NO GO than the ones who behave as totally innocent and you come to realize their true self until its too late.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small Rozli Yusof1 - I'm not 'stupid' for calling out your bullshit. 2 - what you're implying here is that women can be 'used up' after which they have \textbf{zero} value, only due to their \textbf{sexual} history. This has \textbf{zero} rationale and is extremely hypocritical if you also watch = condone porn.\normalsize   & \cellcolor{green!5}Sexual, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small A mans typical argument yet a man is a hero and a legend if he can sleep with as many women as possible but god forbid a \textbf{woman} sleeps with anyone at all or she's disgusting. I personally am a \textbf{woman} who would only want to sleep with someone i'm in a serious relationship with because that is how I work i'm a careful person but I don't judge the women who likes to have many one night stands and it does not affect their value as human beings.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small soda well Miss Daniels opens her legs for a living. But let's disregard that and give her a fair estimate. No! She has to live with the consequences of her actions. Are we not allowed to have values anymore? That's the thing with Feminists! It's always one side versus the other. This is about integrity and self respect. And those who possess such values and morality should at the very least be held in high regard irrespective of \textbf{gender}. Your stock is worth more as a human being. But now that I objectify both genders equally, it doesn't give you the right to spew that \textbf{Feminazi} bullshit! Right?!\normalsize   & \cellcolor{green!5}Feminazi, Gender & \cellcolor{green!5}Gender - Female intelligence, Gender - General & \cellcolor{green!5}2/108 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small kalyanbv1000 there are levels. Miss Daniels has \textbf{sex} for a living. You can't compare her to the girl next door and then claim that the girl next door is a hoe who pretends to be relationship material but fucks around behind everyone's back. So in a way a girl like Miss Daniels is the better option because at least she's real. What kind of logic is that? You don't know that! In life, you get all sorts. And of course, you can't expect your future half to be a virgin. But at the very least she should have certain qualities that you're looking for in a partner. For instance, can you trust her? Is she family oriented? Is she hard working? Just these 3 things will tell you enough that you won't compare a porn star to a girl next door with good morals and values.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/146 & \cellcolor{green!27}0.685 \\  \hline
  \cellcolor{green!5}\small And yes the number does count! Especially if it's double digits. I wouldn't be with anyone who has had \textbf{sex} with more than 3 people. Remember! You're taking all the baggage with you. And I think that's more than enough!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Christian JardinWell, if you wanna hold the view that porn is awesome but the girls deserve \textbf{zero} respect as individuals, then I can't stop you, but know it's an extremely hypocritical view that basically amounts to seeing some women as, and wanting them to be, 2nd class citizens. This is why I asked you 'do you watch yourself'? If you're just against porn, that's a whole other story.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small nick supreme no one ever claimed that porn is awesome and that girls deserve \textbf{zero} respect lmaol maybe you need to learn English comprehension by revisiting the thread again Smh\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Christian JardinYou definitely claim above that the girls (i.e. female pornstars) deserve \textbf{zero} respect. So, I want you to answer me - question: Do you watch porn yourself?\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small nick supreme porn stars deverve \textbf{zero} respect. No one said ever. But what I did say is that I'd rather be with someone that has had less partners. Why? Less baggage train! \textbf{Nothing} to do with porn stars deserving \textbf{zero} respect. Are you a native speaker? Or are you using Google Translate?!\normalsize   & \cellcolor{green!5}Nothing, Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small Christian JardinIn response to a comment that says this: but I don't judge the women who likes to have many one night stands and it does not affect their value as human beings. (emphasis added)You wrote: "well Miss Daniels opens her legs for a living. But let's disregard that and give her a fair estimate. No! She has to live with the consequences of her actions." as well as"This is about integrity and self respect"This will by 99 of people reading it be taken as 1 - you disagree at least partly with her point that a woman's \textbf{sexual} history doesn't affect her value as a human and 2 - female pornstars have in your view \textbf{zero} self respect.You're not getting away from that. This is why I want you to stop dodging my question: Do you watch pornographic material yourself?BTW, when you use grammar like "No one said ever" I don't think you should attempt to attack me for allegedly 'not being a native speaker' or 'using Google Translate'.\normalsize   & \cellcolor{green!27}Sexual, Zero & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/176 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small In terms of dating a pornstar, a better way of looking at it would be that yes a girl may be in this industry and she's slept with lots of people, she knows \textbf{sex} inside and out but also knows what makes people tick, what their characteristics are and knows what appeals to her because this industry could be a window into both the good and bad of people. Then, with all that in mind, she chooses you an average person. Out of all the people she's been with, you are the one who is worth her time, you are the one who has passed the test of quality so surely that must make you feel proud. Also there are far worse types of people doing what many would consider to be "decent" jobs. Just because you work in the porn industry doesnt make you a bad person.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/148 & \cellcolor{green!5}0.676 \\  \hline
  \cellcolor{green!27}\small nick supreme it doesn't affect their value as human beings but it does affect their value as partners. What don't you not get? Of course the mileage affects porn stars when it comes to relationships. Are you two years \textbf{old}? How much more bluntly do I need to put it for you to understand. And who hasn't watched porn? But I avoided because it's not healthy. It's like smoking and drinking. They are bad habits. It's just \textbf{common} sense.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small omg hey there 👌exactly bbg these bozos are \textbf{crazy} smh didn't even think about the candies point of view.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Bruh \textbf{nothing} is untouched anymore...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small You cant compare food with a \textbf{woman}, a fucking human.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Andres Larsson also in Sri Lanka...in Myanmar they have made \textbf{terrorist} organization namely Arakan Liberation Army and bombed places. Typical liberals consider this bigotry secular.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Having \textbf{sex} with someone to whom one -- be the one female or male -- is not married is a devaluing of one's self, soda. You likely would prefer to think this is not the case, but it is.     The Creator doesn't speak meaninglessly; He has instituted rules not for the sake of rule making, but for our protection. Disregard a rule of His \& you can be sure to encounter the dangers lurking in the shadows behind that rule.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small The fact that so many on here refuse to acknowledge the nature of a metaphor aside, Rozli Yusof, what gets to me is that many of these commenting disparagingly on here are the very same ones guilty of making it practically impossible for a virgin looking to get married to find -- sticking with the analogy -- an "unsucked candy," be the "candy" female OR male.  Back in the day, "dating" may have been simply spending time with someone of the opposite \textbf{sex} who one is attracted to \& is trying to find out if the person is compatible for personally marrying, but this all without \textbf{sex} or even kissing, which arouses to the point of wanting to go further; however, nowadays, "dating" is just a euphemism for "fornication."\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/129 & \cellcolor{green!27}1.55 \\  \hline
  \cellcolor{green!5}\small This whore doesn't want her civilian bf to go fuck other people but she wants to fuck half of the world in front of the camera.  Then she says she can't date performers cause she's jealous, what a \textbf{dumb} hypocritical bitch it's incredible...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small How can any man Date a cheap whore like her ? Men will never ever ever be anywhere near comfortable around a whore who has \textbf{sex} with anyone willing to pay or anyone at all. She tries to give all those sorry excuses but the truth is, men only want her body, and that's it.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Yea but now they have Prep so you can prevent HIV and you can even take the meds after \textbf{sex} to prevent it from taking hold in your body. They have vaccines for the harmful HPV strains and also a new Herpes vaccine is going to be out soon to prevent almost all outbreaks. Furthermore, there have been cases where a porn star has married and gone on to have kids and a normal family. Sometimes they change, find God, whatever...but it has happened so you cannot say never.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small Thatbrownguy Damn you've probably never had a girlfriend if you're saying \textbf{dumb} shit like that. This bitch has already stated that dating is nearly impossible as a porn star which proves the original comment CORRECT\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Men are \textbf{weird}. They love porn but then call the actresses sluts and whores. Then want to marry a virgin while they themselves are manwhores. When they do marry, they get bored with the \textbf{woman} and fantasize about the porn star. Then call her a slut and a whore. Then go to hookers. Then call hookers sluts and whores. Then leave their wives for younger women. Then call their ex wives theives and when the younger \textbf{woman} leaves, call her a slut and a whore too. Then hate women, go MTOW, and die alone.\normalsize   & \cellcolor{green!5}Weird, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/94 & \cellcolor{green!5}3.191 \\  \hline
  \cellcolor{green!27}\small 'can cook clean what???' No job in the world should have that criteria. Except that of a maid. The level of \textbf{sexism} here is here. xD\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I'm a young, handsome dude and I have healthy relationships with plenty of whores. I wouldn't marry them or take them to meet my family, but we would enjoy each others company and understand what we mean to each other. Only \textbf{pussy} niggas with feelings wouldn't be able to handle the "relationship".\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small THERE IS \textbf{NOTHING} MORE BEAUTIFUL FOR YOUNG PEOPLE TO BE CAREFUL, RESPECT AND RESPECT OTHERS. WE LIVE IN A WORLD CONTAMINATED BY THE BAD INFLUENCE OF TV, MUSIC AND THE NEGATIVE ENVIRONMENT OF VANITIES AND VICES THAT ALWAYS END DESTROYING LIVES AND FAMILIES. IT SEEMS THAT EVERY TIME IT IS MORE POPULAR TO SEE MOTHERS OF 12 AND 13 YEARS \textbf{OLD}, GIRLS WHO MAKE MOTHERS WITHOUT ANYONE HAVING COMPLETED THEIR PRIMARY STUDIES, THEN THEY HAVE CHILDREN AND DO NOT HAVE THE EDUCATION TO EDUCATE THEIR CHILDREN AND THEY ARE ALSO PREPARED IN THE ECONOMY TO MAINTAIN A FAMILY AND IN MOST OF THE CASES THE PARENTS ARE ONLY AN IRRESPONSIBLE SHAMELESS WHO JUST WANTED TO PASS THE MOMENT, IN THE END MANY GIRLS COMMIT THE HORRIBLE CRIME OF ABORTING AND THEY ARE DAMAGED EMOTIONALLY AND PHYSICALLY, USED, DECEIVED AND TRAPPED, WITHOUT STUDIES OR WORK ... THEREFORE THERE ARE MANY CRIMINALS AND LONGS IN THE STREETS. THE TIME COMES IN WHICH ALL YOUNG PEOPLE AND PARENTS HAVE TO BEGIN A NEW LIFE AGAINST THE HARMFUL CURRENT OF THE WORLD, BORN AGAIN AND LIVE A LIFE OF RESPECT, PEACE AND LOVE !! LOVE AND BE FAITHFUL TO GOD ABOUT ALL THINGS AND LOVE OTHERS AS OURSELVES. GOD BLESS YOU )\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}6/208 & \cellcolor{green!27}2.885 \\  \hline
  \cellcolor{green!5}\small Bunny Bob my man. I have a very good keyboard, i use it almost every day. I like, mu keyboard its ok. The reason why i \textbf{dot} give it tu lot of unknown people every day tu use its because they will ruin it four me.\normalsize   & \cellcolor{green!5}Dot & \cellcolor{green!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Martin M   really? so the HIV testing can be negative if you have a different strain? Can you link me to your source of that information? And I never claimed you can be 100 safe but you can lessen the likelihood to almost \textbf{zero}...you can even take PreP before and after \textbf{sex} AND use a condom too!\normalsize   & \cellcolor{green!27}Sex, Zero & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small Talik which of the 2 genders is programmed to spread their seed? Which of the 2 genders is programmed to seek diversity in their \textbf{sexual} partners?\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Linda Lowther Women are \textbf{weird}. Women think slut walks and riots are "EMPOWERING"\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Sloth I´m against feminazism bs, but she is just pointing the fact that women are very often slut shamed, while men are usually praised for getting \textbf{pussy}. Maybe the underlying point is we should learn to respect people and maybe shut the fuck up when we have \textbf{nothing} nice to say.\normalsize   & \cellcolor{green!5}Nothing, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small \@Antun Šturlić so let me get this straight..the porn star has bad karma but you wont get any bad karma when you have \textbf{sex} with her, is that correct?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@John Q its difficult when you have witnessed men acting abusively, when you turn on the tv and all you see is  robberies shootings murders rapes pedophilia etc etc almost always being committed by men. do you know there are so many men interested in underage \textbf{sex} that the UK can no longer jail men for having child porn on their computers? they have to send them to rehab now because they simply do not have enough room to house millions of people. studies show most men are attracted to girls like 14 to 15 yrs of \textbf{age}. in fact, MGTOW discussions is where i have found a lot of men discussing how they want to lower the \textbf{age} of consent. 80 of the deep web is child porn and its almost all men. so....all i can say is....i hope you are right. i know men evolved differently...that they want to spread their seed to the most fertile partners....and they had to hunt animals so could not always be as empathetic as women, who had to raise children......but in today's society, it all translates into a bad view of men. anyway, obviously i have been \textbf{colored} by my experiences so i do hope you are right. ...but 30 is not a small number\normalsize   & \cellcolor{green!5}Age, Colored, Sex & \cellcolor{green!5}Age - General, Ethnicity - Black, Gender - General & \cellcolor{green!5}4/213 & \cellcolor{green!5}1.878 \\  \hline
  \cellcolor{green!27}\small That may be true but her worth alone isn't based on whether someone would date her. There is no decent \textbf{woman} that would date a male porn star either, sadly. But that alone doesn't make the porn star a bad person or worthless.Women and men do consume porn, but it's something private. ‚Most of them wouldn't date one. That's ok. But hating on one? That's ridiculous considering you view it.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Belly Button Women and men consume porn. I do too, I'm a \textbf{woman}. I don't mind porn stars as people bc it would be hypocritical of me. But would I marry a man that lets say has his dick in 100 videos? Hell no.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small \@Thatbrownguy You are \textbf{blind} chump\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small It's called the normal perfectly natural MANHOOD factor - \textbf{nothing} to do with insecurity. If u want a man then be a lady. Those sorry and depressed people - u can c the sadness in their eyes for the life choice they've made - poisonous filth in society. God Help them\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small Sh is just liek \textbf{dumb} girl in school , she is really got an ego aswell\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I'd rather date some ugly \textbf{fat} women than with her.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small So, she gets paid for \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small 0:33 lol"it makes guys very unconfortable" ok, so a regular \textbf{woman} would be thrilled to have Keiran Lee from brazzers as a boyfriend, right? Dude's got over 1k scenes there.. imagine the number of different girls he's fucked.. nah, they have to date among themselves.. it's the only way\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small I would rather clean toilets for money and still have dignity then having \textbf{sex} for money... can you go any lower?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small IQ  \textbf{zero}!\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small she is \textbf{crazy} as fcuk ....\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Feminists are talking about "inner beauty"... YET, they promote \textbf{fat} love over \textbf{skinny} favoritism.\normalsize   & \cellcolor{green!5}Fat, Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small And this proves exactly \textbf{nothing}. Are you implying that being in a relationship is the same as going to a prostitute? You can't have respect for whores.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Probably, but imagine how bored she must be with regular \textbf{sex} after all the unspeakable things she's done. Also anything you do for money becomes trivial and a drag eventually. I think she might be way too used up  to enjoy it.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small sex is as much about WHO you do it with rather than the act of doing...  Just because she's done it a lot, doesn't mean she doesn't want to do it with the person she loves\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small If she does it with anyone, it's \textbf{nothing} special for her anymore. The intimate and emotional side of \textbf{sex} matters only because you do it with a special person and it's an act of affirmation of your love. It's a ritual. The other side of it is purely instinctual and physical. When you turn \textbf{sex} into an exercise it loses it's deeper meaning and is no different than masturbation.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/69 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Unbelievable. Why would any boyfriend or husband be uncomfortable with this girl having \textbf{sex} with other people on a regular basis?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small So... she's jealous when other performers have \textbf{sex} with HER partner, but she's irritated when "civilians" get upset by the fact that she fucks other people... like... does she NOT see the hypocrisy?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Greg, You are saying as if others who are not pornstars can't? I'm not talking in regards to \textbf{sexual} stuff. I'm just saying that i would love to have a cool person like her around me.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small She have one of the most glorious ass i have ever seen.Beautiful hairy \textbf{pussy} too\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Slut no one cares about your opinion. Your officially a \textbf{sex} object. Don't date.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small notice how all the blame is put on men?maybe it has to do with the fact that no self-respecting man would waste his time trying to build a meaningful relationship with a \textbf{woman} that fucks other men on camera for money\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Hypocrite and selfish is what I'm hearing from her.  Cake and eat it too, is the \textbf{old} saying.  She doesn't want  a 'civilian' to be jealous/insecure, and demand he be tested periodically, while she's the one who is having countless partners doing porn, risking herself and him, and he must burden not only that aspect, but the social stigma and ridicule of her public profession. She has no right to claim she can be jealous if the shoe is on the other foot. Dating another guy doing porn is the same as what a normal joe is faced with dating her! She's experiencing what the repercussions are for choosing to be a whore.  I have no beef with her choice to be in the \textbf{sex} industry, but she can't whine and complain about the consequences that comes with it.\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/139 & \cellcolor{green!27}1.439 \\  \hline
  \cellcolor{green!5}\small Then you're as pathetic as she is.  Wanting to watch a below-average looking girl getting fucked by homely looking guys.  Maybe you feel you're the ugly guy in her videos. I recommend you get yourself a real \textbf{woman} and have some real \textbf{sex}.  Hooking up with a \textbf{woman} today is as easy as picking up groceries at a market.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/59 & \cellcolor{green!5}5.085 \\  \hline
  \cellcolor{green!27}\small W N you're the only hypocrite here. Shaming someone for being a whore, then the next advice you give is "go hook up with someone and have \textbf{sex}". I mean, don't you really see yourself the double standard here? How is fucking a random person who is "as available as a grocerie store" different from doing the same on the set? Oh, I guess as long as we call it "dating" and pretend it's real relationships then it's somehow much better\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Jackie Carla i can treat her like trash if i want to. I dont give a fuck what you say. Im not going to have compassion for whore trash who has no compassion for people shes closest to. This bitch is pond scum and should be treated accordingly in my opinion. You must be trash like her if you feel the way you do. And in my opinion you should be treated like trash too. Being kind isnt always the best thing to do. When you are confronted by an evil entity they must be crushed and destroyed. Because if you smile in the face of evil and welcome them into your home.. That evil will destroy you. So good people must be better at destroying people than evil people are which is very hard to do because evil is obsessed with hurting people and destruction. They cant get enough of it. Evil loves it. Evil lives for those things. But still. Good must not let evil prosper. And must be more ruthless than evil.So my point is. By damning this sick \textbf{woman} i am a good person still. Because i wish and condone the destruction upon an evil distructive being. Which is a righteous cause. The world will be destroyed and enslaved if people dont understand the importance of this pillar.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/223 & \cellcolor{green!5}0.448 \\  \hline
  \cellcolor{green!27}\small You crucified him, exactly my thoughts. I liked his original post, but damn - he had to expose himself like a chump. \textbf{Zero} self awareness I guess.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small i checked her out because I got curious.. and umm..\textbf{nothing} special\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She doesn't see how selfish she is .Poor \textbf{woman}. Wish her well\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small My english is too bad to understand everything she said but good enough to see that she talks and talks but literally says \textbf{nothing}.And posts with: "why is that on my recommended list"? Why did you click on it? PLZ calm down. Ofc no one would ever watch a porn. It was on my list today and I clicked it because she looks georgous.Just watched a scene with her - and have to say - without that cheep "porn-make-up" she looks way better.End of story.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small what a disgusting \textbf{woman} , your parents must be proud\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I feel bad for all of them. It will be very hard for them to have a normal family because not many people can accept that their partner used to have \textbf{sex} with other people and show the videos to the whole universe. This is suck. Maybe, she can find someone with an open-minded in the future. Open-relationship may be worked out, but serious one is getting nowhere. Life is tough.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small She said it \@ 2:52. That's why 'civilians' like us have a hard time accepting the idea of 'you are about to date a porn star.' It's really hard not to get jealous on people having \textbf{sex} with your gf/bf even if they are just 'working'.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Wow!  What an empowered and strong \textbf{woman}!  She truely owns her sexuality.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small she's smart. She's saying that men who don't want a \textbf{woman} who had \textbf{sex} with MANY MANY men are insecure. Implying that a "secure man" will want, or not mind, a \textbf{woman} who had \textbf{sex} with MANY MANY men. Lol\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/40 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Ella, what exactly are you trying to defend?? Please don't tell me that you think porn acting is ok? (And don't say that it's ok if it doesn't hurt anybody because that answer will quickly be shown to be absolutely, unequivocally false. Porn destroys lives! And is the result and or causes \textbf{mental} illness and that's just getting started.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small \@Jon Snow - your comment adds no value to the conversation - and no majority doesn't rule. Classic example of that is slavery of \textbf{black} men/women in the past. It was scene as perfectly normal for a family to have \textbf{black} slaves working for them, and that was the majority. Nowadays when we look back, people clearly see and agree that it was absolutely wrong, even though back then it was how the majority of Americans lived.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small They like \textbf{sex}, yes, a lot, but they're human beings too. You can call them whatever you want but they deserve as much love as you do. Your judgment is based on rules and ethics of society or religion. Human beings are not monogamous, we were naked before we discovered clothes. For all we know, the only reason why the rule of monogamy was set was to control population. And to know that this comment is centered on female pornstars, what do you think about male pornstars? Normal guys who want to have \textbf{sex} like all the other guys?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small Ella Luìz lol i doubt that. Every guy here has probably dated more women than you even if you're a \textbf{lesbian}. But your previous posts have shown what I meant lol\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small why not what is wrong with having \textbf{sex} with lots of people\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small of course, every \textbf{woman} does this!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small all \textbf{woman} are narcisistic natural sociopathic whores!!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@badgoy i respect myself and I am 18 years \textbf{old}, dating a girl (also 18) who has had \textbf{sex} with 6 other people- it doesn't bother me and I have only had \textbf{sex} with 3 others\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Damn exactly what I was thinking!!! Who wants to come home to a vagina that's all used and wore out from the hours of \textbf{sex} at her Job. And she doesn't want her guy to chest on her wtf?..? Hahahahaha\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small OMG you are totally right...women want a man who's desired by others while men want a \textbf{woman} not desired by others..as in \textbf{old},ugly \textbf{woman} oh yeah.stupid idiot,dont even know facts\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}3/30 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small indeed, they even have \textbf{sex} with \textbf{black} guys. i dont think a norma person would ever want to be even close to them\normalsize   & \cellcolor{green!5}Black, Sex & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Zachary Weare it's different if they are currently screwing someone while the two of you are together. Past \textbf{sex} experiences don't really matter\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Luchon20082010 what's wrong with \textbf{black} people? Why can't we just be tame and not hate on other races? Like honestly, I'm clueless as to why you had to say that.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small If she had \textbf{sex} with 200 men with an average penis length of 6 inch thats 200 ft of dick that's been inside her.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@imlaxurian Rapists are human beings. Serial killers are human beings. Child molestors too. Do they deserve love as much love as you do? Female pornstars don't just like \textbf{sex}. They are nymphomaniacs. As for male pornstars, they are anything but normal as most of them suffer from the same addiction, and their activities are equally frowned upon. Back in the day, they were called gigolos.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Mr Morality up there thinks you've all forgotten that he was typing "porn" into the Youtube search bar, or saw the title and somehow couldn't resist coming to the video. Dafuq is the difference between selling \textbf{sex} and selling your skill at painting ceilings? There is none unless you are a backwards \textbf{hillbilly}, soon to be extinct. It's not sacred, it's not magical. It's just \textbf{sex}. Even you will do it one day...eventually.\normalsize   & \cellcolor{green!27}Hillbilly, Sex & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}3/73 & \cellcolor{green!27}4.11 \\  \hline
  \cellcolor{green!5}\small "poisonous filth in society"lol one of those people...\textbf{fruitcake} religious typesgod isn't helping anyone. he left this place along time ago.I don't see sadness, you don't see it either, you are seeing what you want to see, "moral compass" just another schtick to place people in a box. Its insecurityMen are insecure, and people are soft/PC/religious/fruitcakeswhat she does is legal, face it, its normalized, its accepted and your a soft \textbf{sissy} \textbf{fruitcake}.  "life choices they've made"Everyone dies REGARDLESS which life choices you've made.Being good, wholesome, virtuous, cleansed...does \textbf{nothing} for the soul.  It does not buy you an entrance to a fictional sky-valley beyond this world, it does not buy you immortality.What are you saving yourself for ?\normalsize   & \cellcolor{green!5}Fruitcake, Nothing, Sissy & \cellcolor{green!5}Age - Youngsters, Sexual Identity - Male homosexuality & \cellcolor{green!5}4/124 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small \@michael stillwell i can probably be described as a "soft \textbf{sissy} \textbf{fruitcake}", but i fully support her right to do what she wants with her own body\normalsize   & \cellcolor{green!27}Fruitcake, Sissy & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small and rememberyou shall not trust any man cuz they are all are \textbf{sexual} but of course, you should accept female porn stars cuz they are just sexaul\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@Mohammad Ali i don't think that men or women cannot be trusted just because they are \textbf{sexual}... our sexuality is a fundamental part of who we are, after all :)\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small naaaaaaaaaaaaaaaaaah not all men are offended by other penises if you were big enoughare all women offended by a good shaped \textbf{woman} with a nice tits and ass???\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@Mohammad Ali and what makes you feel that \textbf{sex} work is a "low thing"? what if not everybody feels the same way? :)\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Alwyn April not everyone feels the same doesn't mean it's right a \textbf{terrorist} thinks that he is doing a sacret job that doesn't make hik right actually it is the total opposite he is not realizing the stupid shit he is doingJudging acts according to people's opinions is wrongful and \textbf{dumb}, wrong and right is not based on your opinion, feeling, your way of thinking it's definitions beyond humanity's judgment when something is right it is right and when it's wrongfeeling won't matter\normalsize   & \cellcolor{green!5}Dumb, Terrorist & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small Alwyn April and the joke was about pointing the hypocrisy of some feminazis that accuse men for being \textbf{sexual} at the same time justifying a \textbf{woman} being \textbf{sexual} and giving it right the same time\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small \@Mohammad Ali you know a \textbf{terrorist} could also say the exact same thing to defend his actions and judgment towards others, right?so what makes you feel that it's wrong? do you think everybody else should feel the same way? :)\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@Mohammad Ali i don't know about those feminazis, but i don't see her judging or shaming men for being \textbf{sexual} at all :)\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Google UserX \textbf{dumb} btch.... its not that.... women r not the center of the universe.... its a question of whether the man can run the family with his dignity and lead them in safety and respect they deserve...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@Andrew Huynh still slaves today boss. Always been that way. Just used for \textbf{sex} now.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small exactly have more respect for your cucks my dudes iys gross thinking how many penis have gone in there and to kiss those err but then again pretty much every hot \textbf{woman} is \textbf{thot} now dudes beware\normalsize   & \cellcolor{green!5}THOT, Woman & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Obviously why would i date someone whose having \textbf{sex} everyday with different men and i probably womt even be able to have \textbf{sex} with her on a daily note.....\textbf{sex} is an important part of any relationship......and these are just whores calling themselves performes the fact is they are good for \textbf{nothing} thats why they have \textbf{sex} for money and show it on internet\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}5/63 & \cellcolor{green!27}7.937 \\  \hline
  \cellcolor{green!5}\small I think so. Or the idea of catching a \textbf{sexual} transmitted disease from one night of pleasure.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small What about the way life is today where so many women give \textbf{sex} away for free.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Porn industry is a joke nowadays Any male pornstars under 30 basically dont get a look in.. there very few.. No its all 30+ men Just go they are older doesnt mean they cant perform any better than a 18-25yr \textbf{old}... Just wrong.. At least back in 60-lte 80s porn you dont have that\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small why would you date someone if you can cum in her \textbf{pussy} many times?\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Wait, what is she talking about when she says "if he or she cheats on me"? What does cheating mean to her? Cheating is when you are in a relationship or married and fuck someone else but your girlfriend or wife. So when she has \textbf{sex} constantly with other people, isn't that classified as cheating? I mean we're in a relationship and you go and fuck other dudes but it is totally fine?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small Ok so she rips guys for being jealous...and then she says she can't date performers because of her jealousy...that's definitely the logic of a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Porn is supposed to be about having any and all \textbf{sexual} fantasies and desires fulfilled with no consequence. Yet troughout this entire video she indirectly proves that \textbf{sex} can never be casual and using it wrong can ruin your life.\normalsize   & \cellcolor{green!5}Sex, Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small what the fuck is the \textbf{common}  american syndrome of anyone who performs in any number of adult films regards themself and certainly referres to themselves nas na porn STAR? for the multitude of men and women performing in adult films, there a a fuckin precious few who legitamitely qualify as a STAR. a giant piece of shit or whatever physical female attribute one clings to as supreme in importance really dont mean a mutherfuckin thing. scores of people all over every corner of the globe have massively gifted manhood units and women are perfect  and impressive in every way in every toiwn and village. probably the ability to perform in a genuine and appealing manner relatable highly to \textbf{sexual} activities commonplace. of course it all must have a more sensual erotic and so forth overtone to it. constant over the top moans and wails created to express the unbelievable unparalleled extacy happening usually are highly and almost invariably written off as straight up fairy tale nonsense. and almost as often this almost singularly, and loud as fuck, sonic offering to the visual quickly becomes notably irritatating  and in the end this horrific accompanyment to physical get-down serves to do little other than pollute the picture with start-to-finish unaopoealing wailing and shit and the other most likely outcome is the irritating repetition of dischord. whatever the fuck else i could possibly add or subtract bfrom the industry is most certainly personal crap nnobody would likely find enlightening or relatable at all. but the porn STAR shit is so overly applied that the term incredibly rarely applies to the actor at all  in their prolific history, tangible fame, industry awards or formal nods, etc..without some reasonable and extensive acting following and probably a few awards as well as regular inclusion in whatever type of magazine, website, periodical things that the aduklt film industry in 2018 primarily utilizes to showcase or promote actors films events or what the fuck ever is most relevant in that current slice of world lifestyle and cultural shit its all about. cause honestly, there is no vocabulary or writing seductions i can conjure to divert any impressions here away from the fact that i do not know very much at all about any detalied realities of working and personal realities of the relevant performers, absolutely \textbf{nothing} about directing, sound, tech aspects of the productions, and though im aware there certainly are gala events with various appropriate awards that are well respected and proudly recieved comprable to the many motion picture events with \textbf{r\textbf{ed}} carpet nonsense and the obviuous awards for shit involved. i bet the adult awards are likely more applicable anbd deserved by the winners than many of the far out and poorly deserved films actors directors that motion pictures recieve leaving evryone scratching their heads and analyzing and scheming to find a justfification far below the surface shrouded in a thick mist and wearing a cloak of invisibilty.\normalsize   & \cellcolor{green!27}Common, Nothing, Red, Sexual & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American, Gender - General, Social Class - Working class & \cellcolor{green!27}5/493 & \cellcolor{green!27}1.014 \\  \hline
  \cellcolor{green!5}\small a f**** his f**** eating \textbf{pussy} is eating \textbf{pussy} if it's the job is a job all it is is a job you're going to go home with me afterwards anyway I just when I get home I'll do clean it out good and we do what we got to do my saying is I might not bottom out but I sure will beat up the side walls\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small People with low self-esteem and abusive childhood ended up in \textbf{sex} industry\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Old, \textbf{bald} \textbf{fat} man bet u looked her up now lol\normalsize   & \cellcolor{green!5}Bald, Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small Bruh. Best \textbf{lesbian} scenes ever\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Oliver B She's KS is relatively newer as compared to DD. Hell KS made her start Masturbating in a College Library.....\textbf{Crazy} how some porn careers start.....lol\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Old, \textbf{bald} \textbf{fat} man Which rock have you been living under all your life?\normalsize   & \cellcolor{green!27}Bald, Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}3/14 & \cellcolor{green!27}21.429 \\  \hline
  \cellcolor{green!5}\small Old, \textbf{bald} \textbf{fat} man I have heard of and seen of her.\normalsize   & \cellcolor{green!5}Bald, Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/12 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small old \textbf{fat} man-STFU You pathetic Moron-Get a LIFE.Anyone who watches porn or intelligent knows Dani daniels\normalsize   & \cellcolor{green!27}Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You only "like" her because you fantasize about fucking her. \textbf{Nothing} more. \textbf{Nothing} virtuous about that. By the way, I've never heard of her either. Thanks.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Old, \textbf{bald} \textbf{fat} man Swearin' on his grave and lying all the way 'til death on this.\normalsize   & \cellcolor{green!27}Bald, Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}3/17 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small Old, \textbf{bald} \textbf{fat} man How the fuck havent you heard of Dani Daniels??\normalsize   & \cellcolor{green!5}Bald, Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/13 & \cellcolor{green!5}23.077 \\  \hline
  \cellcolor{green!27}\small Old, \textbf{bald} \textbf{fat} man She's not a bad actress.. I have seen her in a few clips!!\normalsize   & \cellcolor{green!27}Bald, Fat, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}3/17 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small yeah me either, and I would never get involved with a \textbf{woman} PORN lady.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Maybe you should get a real job and avoid the \textbf{mental} breakdowns later in life.   Lol\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Eman323  kesay \textbf{ho} ga proud  explain pls\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Eman323 wo to hay but ap to out of subject bat per a gai \textbf{ho} I think we need to talk on WhatsApp if you don't mind pls\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small R E - V A P E ....lol, she is obviously \textbf{dumb} and stupid\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small why is this coming up in my recommended its like 2 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Until many as her comprehend how beautiful their souls are.  The choices they makes are \textbf{nothing} more than the flesh lure their free wills to accept it. They are enslaved to the flesh. Once they master their flesh then the awakening essence of their soul shall connect them back to their twin soul in the higher plane. Until then to each choices are their own to choose from as the prime creator gave us all free wills. No one are righteous on this planet not even one!Ain't Life Grant...Bouyah!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small Joe Martin men does it cuz they actually want \textbf{sex}. Women does it cuz they cant do anything else to make a living.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small woman want \textbf{sex} as much if not more than men\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Smiles infront of the camera's. Leaving lost and lonely in real life. When u get to meet an outwards attractive \textbf{woman} u never know the mystery of her draws.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I just can't help it.  I have to comment....at 1:23 she says "there's the fact of, you (her hypothetical boyfriend) have to get tested all the time.  Because if you cheat on me, as much as I trust you....."(Briefly imagines places himself in the shoes of the imaginary boyfriend.  Immediately goes off) WHAT??????If I cheat on YOU???   are you serious???YOU ARE A EFF-ING PORNSTAR!  You have \textbf{sex} with different dudes several times a week....sometimes with several dudes at the same time, several times a week... AND YOUR CONCERN IS ME CHEATING ON YOU.  "ME cheating on YOU" is actually a thing that exists in your world!  How is that even possible?  So in your head, we DON'T have an open relationship. Really???  You are worried about you catching something from me......Where are from, Narnia?  WherEVER you are from, go back there, but leave me here.  Be sure you take all your stuff with you.  You can keep all the stuff I left at your house. I don't want it.  END RANT.  I'm sorry YouTube community, I just couldn't help it. When I got to that part it all just jumped in my head at one time.  I had to get it out.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/207 & \cellcolor{green!5}0.483 \\  \hline
  \cellcolor{green!27}\small "If you cheat on me" - there's a \textbf{weird} concept after the whole speech about having huge penises inside of her every day. She's broken goods, telling girls anything else just encourage them to make bad decisions. Yeah, easy money, lots of dick, but you'll die alone.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small SEX IS MARRIAGE if the female is a virgin or a faithful widow, it is adultery otherwise.This female cannot commit, the only thing she's committed to is the money.  She is a prostitute in front of a camera. You cannot make a whore into a wife unless Jesus actually change her and that is show by her actions not her words. No such thing as a born again virgin. Tell me she talks about being cheated on, doesn't she cheat every day she goes to prostitute herself for money?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small WHY  WOMEN  ARE  NOT  LIKE PORNSTARS . FUCKING WITH \textbf{BLACK} GUY  WHITE GUY ,EVERY GUY..😂😂😂😂\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Men don't feel insecure because you are a porn actress and have had big dicks in you, men don't want to kiss a women who's had hundreds of dicks in your mouth, ass, and \textbf{pussy} not to mention all the STD's that come with it\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small What a stupid anal \textbf{bimbo}... What kind of man wants a \textbf{woman} who has been fucked with all these guys?Tito ortiz? Rocco?who stupid bitch? None you piece of shit... You will know at the future... Loneliness will be your best friend because you thought that money is everything, you empty goofy...A totally used product....\normalsize   & \cellcolor{green!27}Bimbo, Woman & \cellcolor{green!27}Gender - Female intelligence, Gender - General & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small They are just immoral whores.Lets not get distracted trying to make this "job" look normal.Its disqusting,period end of story.No normal man can tolerate the love of his life,his precious Princess,to screw around with thousands of dudes every fucking day!It simply doesnt work,and it will never work.I know it from personal experience (with a prostitute).Its horrible and \textbf{weird}.Thanx God there are enough girls out there,who dont live fucking for money!Screw these whores-they deserve to be alone and die in their own sin.The same for the male whores.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small I get that people don't like seeing their significant other getting fucked by dudes who have bigger cocks but ya know Porn is literally just a job to them, it's not real \textbf{sex}, it's a bunch of scenes, Stop, Go, Cut, repeat until said video is done. Imagine doing the same scene over and over again and in the same position. I don't know about any of you but I could date a porn star if was option. Porn is a job like anything else, people are just insecure.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small There is no way you can have \textbf{mental} health with a career in being sexualized daily. Things don't mix well.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small "It's very hard to date someone that has \textbf{sex} every single day with other people."RAZOR SHARP INSIGHT DANI!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Well...I'm not. Maybe I'm just too emphatic. It really is situational. We both may find a job incomprehensible for us to do, difference is, you supposedly look down on them, but I'd respect them even more. But perhaps we're both ignoring the individual aspect of it. I wouldn't simply respect a childish CEO who didn't get the job through merits. I wouldn't respect a porn star who is stuck up and has no other skill set or personality. I wouldn't respect religious leaders unless they put truth and reason above faith. I wouldn't respect a genius who is megalomaniacal. Wouldn't respect an honest politician if he was \textbf{dumb}. Now this \textbf{woman} answered questions about a porn star's love life dilemma without insulting any men. I think it was an appropriate answer and she seems like a rational person who understands the trade off of being a porn star. I don't think she deserves to be degraded.\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/156 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small How about fucking lots of men not on film without getting paid? Is that rational? Men who would want to fuck lots of women or wanks to porn, but slut shame women who have \textbf{sex} openly, is not rational. Its hypocritical.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small The Truth ....lmao, you went \textbf{old} school , lmao\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dating is hard because no guy wants to be with a \textbf{chick} who has had 2000 guys drop there loads on your face.  You date quality and fucks sluts.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Hard to be a performer? Hard to be in relationships? Really? No questions on porn stars suicide rates? None on drug forcing or drug use? How about easy access to kids? How about your short career span due to aging and having \textbf{nothing} but HIV to show for it? This isn't acting and it isn't harmless. It is a seductive disease like heroin or crack. Lord save us from hypocrites, liars and idiots like this who have a 4th grade education. I hope the best for this girl....but she might want to take another path. Life is a marathon, not a sprint.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small )ews run our societies, this is )ew sh*t, porn sh*t, it's all about subversion. Trump is a joke, he's a Chabad Mob Construct, just like Obama and the rest. Elections aren't real. )ew mob runs this country, and they're running it into the ground...."We'll turn the United States into a bottle sucking welfare state and collapse it!  That's what we do to countries we don't like!- PM of Israel B Netanyahu Greater Israel Expansion Project, for most important trade route on earth(obviously), sandwiched between Big Oil \&African Hi Tech Resources Bloomberg Corporation and other cultural and breeding alliance members engaging in incestuous \textbf{eugenics} to maintain caste system supremacy based on usury not merit are already entrenched in Africa for major heist. So far Int'l )ewry has killed babies, a 35 Christian population Seculars and some Muslims for Rothschild land grabbers. Displacing millions, dispersing millions to others homelands for depopulation agenda, and their maniacal utopia. Tel Aviv was named in 1910...\normalsize   & \cellcolor{green!27}Eugenics & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/161 & \cellcolor{green!27}0.621 \\  \hline
  \cellcolor{green!5}\small Wow, it's almost like \textbf{sex} can't be separated from relationship without serious consequences, hmmm...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She has a beautiful \textbf{pussy} ✌\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Who the hell would want to be in a relationship with a \textbf{chick} that takes random dick for a job? And she's afraid from contracting a disease from the boyfriend??? Ok...\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Womens dont create drama arround almost \textbf{nothing}. The lightning strike that men experience at some point after making some mistakes like drinking too much or destroying your family life or fighting and picking fights constantly can't be applied to women because they rarely look to the imoraloral aspects of life experiences...in general speaking ofcourse. Men are cheaters...yes they are but they also are the true sons of Jesus Christ they also are passionate about what they do evil or good right or wrong women however despite they also are the daughters of Jesus Christ they have this self defense mechanism that makes them million times much more stronger than men as if they the women did not belong to this ocidental and christian standards and were borned on some other planet or dimension and brought back to Earth. Men = Intense Life Drama When They Reach 40yo +.....Women = Entire Life Robotic Behaviour....in 2018 general speaking ofcourse.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/157 & \cellcolor{green!27}0.637 \\  \hline
  \cellcolor{green!5}\small I consider myself as a rather conservative Person, but being a Pornstar or a prostitute has \textbf{nothing} to do with being immoral at all, especially from the Christian perspective: wasn't it Jesus himself who defended and saved the whore Maria Magdalena while the "morals" tried to punish her for her Actions? Also: if a guy had a wild time as a Young Person and "did" 50 or 60 Girls in his time, why is he better than the \textbf{Hooker} around the Corner? Hypocrits! Something different I guess is if one is Dating a Pornstar/\textbf{Hooker} and the one continues having \textbf{sex} during the Dating days. Even I find that hard to come by. Don't cruzify me, just my Point of view.\normalsize   & \cellcolor{green!5}Hooker, Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - Female sexuality, Gender - General & \cellcolor{green!5}3/120 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small here I am again...in the \textbf{weird} part of youtube, late at night. feel like I need to go shower now.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Man scrolling through these comments was harsh what a bunch of hypocrites, Dani seems like a cool person, and at the end of the day that's what matters, so what that she's a porn star. The way I see it she's performing a service to all the people that go online looking for \textbf{sexual} release. Relationships have little to do with who you have \textbf{sex} with but rather who you're willing to connect with on an emotional level. As for her career choice, all I can say about that is at least she's making it. I'd rather be in the porn industry than what I'm doing now working 6 days a week at a restaurant living paycheck to paycheck.\normalsize   & \cellcolor{green!5}Sex, Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/119 & \cellcolor{green!5}1.681 \\  \hline
  \cellcolor{green!27}\small If I got a different piece of \textbf{pussy} everyday I would never date anyone. Women are only good for their \textbf{pussy} and if you want a kid, you can do everything else yourself. I can cook, clean, drive, wake up, put on my shoes, mow the yard, all that myself. If you look at it that way you'll only go after women who are beautiful and have a great paying job cause the rest are just a waste of your time you could be doing something fun.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}2/87 & \cellcolor{green!27}2.299 \\  \hline
  \cellcolor{green!5}\small This is why people have to stop watching porn- it allows this pathology to continue to corrupt both the viewers and performers. Imagine this \textbf{woman} in 5 or 10 years when she hits the wall. She thinks she's got dating problems now?!?! lol. It'll get way worse!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Adam, you are so right. I hesitated to listen to this \textbf{weird} \textbf{chick} speak. She is absolutely narcissistic and depraved and oblivious to how much of a joke she is. And we only feed into this narcissism by watching her act out her \textbf{mental} illness on camera. What she has to say about "dating," is beyond incomprehensible and wratchety. The horror.\normalsize   & \cellcolor{green!27}Chick, Mental, Weird & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/61 & \cellcolor{green!27}4.918 \\  \hline
  \cellcolor{green!5}\small I'm shocked. Between the prude and the nofap gang, I am tempted to believe that the world is inhabited by little, innocent angels fallen from the sky and this poor girl is the only "\textbf{black} sheep" who's somehow pure evil and should be stricken down by the wrath of God asap so as not to corrupt the innocents around her. Just remember, boys and girls: the snake didn't make Adam and Eve eat that forbidden \textbf{fruit}, just like no one made you watch porn. It's on you, people, no matter how much you blame those who make the movies.\normalsize   & \cellcolor{green!5}Black, Fruit & \cellcolor{green!5}Ethnicity - Black, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/99 & \cellcolor{green!5}2.02 \\  \hline
  \cellcolor{green!27}\small I've met Dani, she's actually the most genuine person you'll ever meet.....she likes to cum, and she's unapologetic about it. She is happily married.....and mostly only does exclusive stuff for her personal site these days...with her husband...She is a talented artist, and has many other successful businesses... coffee, clothing, product boxes, \textbf{sex} toys...so for any of you who judge her....there's \textbf{nothing} wrong with enjoying \textbf{sex}....\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/65 & \cellcolor{green!27}4.615 \\  \hline
  \cellcolor{green!5}\small Jade Reynolds I wish her the best and I wish the best for all the individuals in that scene, but I was commenting more on the nature of porn and porn viewing in general. I'm not a prude or anti-sex or moralistic about it, I just know first hand and thru discussion the awful effects it has on many people. Sure, there are some women who can successfully separate and dissociate from their work and there are men who can watch it without developing neurotic or \textbf{weird} habits or performance/arousal issues, but those are exceptions. I'm all for free choice in what you want to consume, but people(especially younger millenials and now gen z) really should know what this stuff can do to you.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/124 & \cellcolor{green!5}0.806 \\  \hline
  \cellcolor{green!27}\small Or the rest of you seem pretty \textbf{dumb}. Take your pick.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Wht the fuck is "the wall"?  Why do people keep saying this?  Jesus, I'm a 37-year-old \textbf{woman} and I've never been in a relationship.  Who cares?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I loved watching Bree Olson cry in another video.  Made my fucking day.  These roasties think they are still human.  LOL LOL LOL...you are product.  Deal with it.  I don't keep the gum I'm chewing.  I spit it on the ground and it becomes a \textbf{black} smudge.  This is the destiny of all porn stars and hookers.  \textbf{Black} patches on the pavement of our culture.  You did it for the money and attention and \textbf{sex}.  You are not coming to the PTA meeting morons.\normalsize   & \cellcolor{green!27}Black, Sex & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/84 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small AdamIt will get better because people tend to grow up with \textbf{age}.  She's not interested in sniveling children anyway.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small this \textbf{woman} is beautiful but also disgusting thot\normalsize   & \cellcolor{green!27}THOT, Woman & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small This is so fucking cringe. Having \textbf{sex} for a living and can't get a successful relationship. Shocker\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small All girls are good at are:\textbf{Sex}Sucking DickCheating Cooking Cleaning Reproducing Annoying you\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Very revealing..calling us civilians ..So she admits she is part of a war machine..Lauryl Canyons relationship with military intelligence has been researched wellUtube lauryl canyon military psyopPorn is just another progressional social engineering program to further the debt currency system....nowadays they r selling to normalise incest..next it will be pedophillia..Thats how u boil a \textbf{frog}..nice and slow..The war is about farming human energy in the form of debt ..It gives the roman system the licence to continue the war against humanityUtube : dum diversas papal slip of enslavementGoogle : UN legal research doctrine of discoveryThis is a war..against our souls\normalsize   & \cellcolor{green!5}Frog & \cellcolor{green!5}Nationality - French & \cellcolor{green!5}1/111 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small 1. Who needs dating when you have more \textbf{sex} than ppl in relationships anyways, and get paid?2. If I dated her I would cheat on her every single day.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small The \textbf{misogyny} in the comments is astounding. Neckbeards truly are a miserable kind.\normalsize   & \cellcolor{green!5}Misogyny & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Muhammad You are muslim, I can at least assume so from your username. You follow bronze \textbf{age} mythology that condones murder of innocence. Don't fucking lecture anyone about morality, you fucking \textbf{blind}, indoctrinated dunce.\normalsize   & \cellcolor{green!27}Age, Blind & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small MuhammadNo, you can't. Murderer and child rape are not voluntary acts between consenting adults. A \textbf{woman} chooses to have a career in the \textbf{sex} industry and her clients choose to engage her services. Any action that doesn't conform to your standards is "fake freedom" and any person who doesn't agree is a "subhuman" who deserves to be murdered. I get it, little Hitler.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/64 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Hahahahahah, again with the pseudo-intellectualism. Your delusion that "consenting adults" is even a question for morality is amusing, instead of the affects it has on these women and the men who exploit women for their own personal greed. You're a scumbag basically sticking up for capitalist \textbf{pigs} who run an industry which is morally abhorrent, fucking everything that moves and filming it on camera is not a moral evil according to you. This is what I mean by your fake freedom, your freedom which dictates if people are so fucked in the head that they consent to doing these things, it makes it ok. No, you retarded virmin, there are much better virtues in existence than your pathetic freedom beats all, things like honor, empathy, humbleness, virtues that exceed greed and physical gain of wealth or power. People like you obviously don't understand it, because you are of a lowly subhuman stock whether it's in your genetics or your spirit I'm not sure, but the only thing I am sure of is that scum like you need to be eradicated from the earth. And no, I hate Hitler, as he and the Nazis attempting to genocide millions of slavs and had an open anti-slavic policy, so try again, scum. I hope your daughter if you have one ends up in the porn industry, just so you can feel the pain of every father, brother and living relative of porn stars, and understand how detrimental it is to society, and everyone participating in (except those who make profit off of filmed prostitution). Now, instead of trying me again with your pathetic, over-used justifications of "muh consenting adults", re-examine your moral compass and re-examine your disgusting, indoctrinated world view, you fucking consumerist garbage.Also, "consent" is something the porn industry capitalist scum like to feed zombies like you, the illusion that these women are in any way "consenting" to their lives being ruined forever, instead what really happens is exploitation of people who are in dire need of either money or fulfilment, you will never find a pornstar who started porn because of a positive motive, rather that these women are left on the street, abused by family or had a fucked up childhood, it all comes back to psychology and they end up being in the most depraved industries in existence. But again, of course zombie capitalist shills like you would attempt to justify.\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/403 & \cellcolor{green!27}0.248 \\  \hline
  \cellcolor{green!5}\small MuhammadIn fact, the funny thing is that you're no real danger to anybody because you're just another mouth on the internet. You fantasize about murdering people you disagree with and whine about your imaginary objective morals but at the end of the day you'll do \textbf{nothing} but sit on your arse typing away like the poser and hypocrite you are. You don't have the courage to act on your convictions.You're right. People like that have increased since the advent of online forums.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small All I see is typical garbage from an inferior, \textbf{pussy} being who thinks he knows it all. Very \textbf{common} walking cliche these days, it's like a dog who believes it can see colour. Very amusing, if you sincerely believe I don't have the courage to act on my convictions I feel bad for you, because you are so deluded. But please, it's amusing the typical "ehehe ur a basement dweller"  talk, from someone who gets all of his views fed to him via social media and pop culture. "imaginary morals" - interesting that you call these morals imaginary, as through all of history these morals have been the basis of good societies and people, and up until recently they've been sucked dry by greed and power, you're only the product of it. But again, amusing. Desperation is all I hear from you, but when the shit hits the fan you'll only be begging for mercy. And spare me your hollywood psychology analysis please, it's actually amazing how predictable you robots are. Depraved, sick, putrid. I don't know if a God exists, but if they do, i'll be for sure the one to send people like you to them.\normalsize   & \cellcolor{green!27}Common, pussy & \cellcolor{green!27}Nationality - Chinese, Social Class - Working class & \cellcolor{green!27}2/198 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small MuhammadI'm starting to notice a theme here. You dislike capitalism, you're disdainful of education and personal choice. It all seems to point towards you being insecure about the fact that you've generally failed to achieve anything in life. Also explains why you desperately want a simplistic moral law handed to you so you can convince yourself you're superior to people who make different choices. You obviously can't pretend you're superior based on merit or achievement when you have neither.Your whole persona and this act that you do makes sense to me now. Though I think you're failing to grasp the fact that you're still going to be the same sad, angry man no matter how much you judge others. Happiness isn't a relative scale and you're never going to achieve genuine happiness by putting others down. Ever thought about going back to school, maybe doing something productive with your life? It's not too late.Sure, if my mother chose to have \textbf{sex} with 20 men that'd be up to her. Why would it bother me?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/177 & \cellcolor{green!5}0.565 \\  \hline
  \cellcolor{green!27}\small Judas Iscariot Ahahahahahha again the same hollywood, tedious psychology application to something the poor zombie can't grasp, so he has to attempt to create a story and character to fit his stereotypical views fed to him by popular culture, that people who question modern neoliberal system of capitalism and moral depravation are just basement dwellers with no achievements, right. Again I repeat, same \textbf{old} same \textbf{old} walking cliche of a person. You are the direct result of the system I am talking about, fed on the capitalist fantasies of "merit" and "freedom" and lied to in order for profits, what a sad and depraved result. And you unironically just said you'd be ok with your mother banging twenty men, which to me and to most people signifies deep \textbf{mental} issues and lack of morality, simple as that. Just like we can't explain to ants what morality is, we can't explain to the likes of people like you what it is. And as a result of people like you; we have a fucked up system today which is built upon exploitation and destruction of morals and values of the societies which have fuelled their economies, you are a pathetic creature who lives for consumerism and pleasure and looks at people who are superior to you in spirit as inferior beings, because you are a materialist and know \textbf{nothing} of true morals and human values. Again, the simple fact you would be ok with your own mother, the birth of your own being, getting used and defiled by random strangers and your mother giving the ultimate physical pleasure to anyone and anything speaks VOLUMES about your state of mind. I sincerely hope you get help.\normalsize   & \cellcolor{green!27}Mental, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/283 & \cellcolor{green!27}1.413 \\  \hline
  \cellcolor{green!5}\small MuhammadYes. A \textbf{woman} having the option to choose what she does with her own body and how she interacts sexually with other consenting adults is part of that enlightenment.Living in a free society involves recognizing the fact that sometimes people will make choices you don't agree with. If you don't appreciate that freedom why not move to Syria and join the other moralistic thugs. Seems like you'd be more comfortable there.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small MuhammadMy mother can fuck whoever she chooses to fuck. It's none of my business. Just like I can fuck anybody I want. I don't want people telling me who I'm allowed to have \textbf{sex} with so I afford other people the same respect. This is called being a grown-up.Funny how you'd rather sit on the internet and rant about your imaginary morals and talk about killing people than actually do it. If you had the balls you'd go join ISIS or some other group that shares your narrow moralistic views. Only thing more pathetic than a judgemental bigot is a judgemental bigot who lacks the courage to actually live up to his own convictions.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/116 & \cellcolor{green!27}0.862 \\  \hline
  \cellcolor{green!5}\small We get it, you're an enlightened intellectual, we understand. \textbf{BLACK} METAL, BANG EVERYTHING FK YEEEEEEEEEEEEEEEEEEEEEEEEEEEEEE BOI, FREEDOMZ Talks of sitting on the internet, replies to a dead comment section and boasting about his "superior' world view. Lmao, please kid, get with reality. Also, conflating everyone who doesn't want a degenerate, dead society to ISIS is the most cliche shit ever, at least get some new arguments. They're not even worth my time, because they're so stupid.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small with the insanely \textbf{common} and desired filming subsequent availabilty on the internet thats rockin around theres loads of every type of personality and lifestyle and cultural preferances and shit. i guess im far less surprised by the available number of male participants. but certainly \textbf{age} education social-ranking and whatever shit society is broken into that is producing females from all these categories that historically were not represented to any degree worthy of charting into the adult film productions. without question too, the ever increasing internet and iphone shit (twitter and so many) has drawn droves of younger people with a junkheads need for more attention by whatever means it breaks down to require.either way if people wanna promote and provide avaulablity of phone-camera filmed \textbf{sex} in their bedroom to the more intricate productions compete with a little acting around scenariarios that are are far-fetched to extreme of qualifying as fully psychotic representations from a mind bound 100 in delusion, they are all over. and no question are gonna continue to expand exponentially for however long. i think that the number of people seeking videos of adult film style in the frequency that are  reasonable are getting so many options and shit that the intent of finding a good ole \textbf{sex} video to enjoy are made less easily found by the sheer overburst of stuff around. either way im no expert and am qualified to comment in an informed manner on adult films in any way. but what the fuck? its youtube so leaving a comment means absolutkley \textbf{nothing}. it would matter a hell of alot more if i sat in a dark room and did \textbf{nothing} for 3 hours,  its a certainbnly tangible and a real action on eatrth. youtube and internet commennts in general are electronicly supported false representations of reality. its just so easy to fall into the fold of 2018 namerica where everyone exists in an illusion that they have accepted as more real than something like spendin g the afternoon in a city park.\normalsize   & \cellcolor{green!27}Age, Common, Nothing, Sex & \cellcolor{green!27}Age - General, Age - Youngsters, Gender - General, Social Class - Working class & \cellcolor{green!27}6/339 & \cellcolor{green!27}1.77 \\  \hline
  \cellcolor{green!5}\small I came across this video through another video of a porn star interview which for some reason popped up on my feed.. that other \textbf{chick} seemed drugged up and seriously fucked in the head saying all kinds of \textbf{dumb} shit and acting overtly \textbf{sexual}.. this girl seems pretty fucking normal.. slutty? maybe.. but fairly normal Lol.\normalsize   & \cellcolor{green!5}Chick, Dumb, Sexual & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/56 & \cellcolor{green!5}5.357 \\  \hline
  \cellcolor{green!27}\small Disgusting. People who have \textbf{sex} for anything other than love are horrid.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I just watched some of her videos. The girl his really \textbf{sexual}. I would date her if she didnt do porn\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small the reason for men's antipathy towards her, is mostly based on her mental-intellectual inferiority and social status, and only 0.00001 is based on her daily \textbf{sexual} intercourse with huge penises. and I hope she will never understand that, because watching a worm, that sees itself as python is fucking amazing and entertaining. she is not able to self actualize and she doesn't even know it (or she knows, but tries not to think about it). the only thing she can do is moving her flash and it warms my soul in the night and makes me smile in the morning.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small Porn stars, hookers and todays modern \textbf{woman} have much in \textbf{common}. 3:15. The job will always be number 1.\normalsize   & \cellcolor{green!5}Common, Woman & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Almost every \textbf{woman} fantasizes about getting many Dicks they are no different than man. Why you think they love movies like 50 shades basically soft porn\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Beauty is \textbf{nothing} but an illusion. Notice how they all curse heavy.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Okay \textbf{dumb} ass little minded girl just answered her own question.............. She said dating a person in the industry causes jealousy but expects a regular 9-5 person to understand when a fellow performer can't even understand............ GTFOH\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small The audacity of this bitch... First she says regular guys get jealous because she has \textbf{sex} with other guys THEN she says when performers date eachother they get jealous because their boyfriend fucked another girl in the ass last night. Like bitch, this is a 2 way street you chose this lifestyle.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small 'I have \textbf{sex} with a lot of guys, which makes the guy I'm dating totally insecure.'WTF.Insecure has \textbf{nothing} to do with it.The girl is a whore/slut call it whatever you want.She is paid to be naked and get reamed by multiple guys and gets semen all over of her body parts.Basically a fucking slut.And in her little lizard brain the guy is the one who is 'insecure'.Are you fucking kidding me?Anyone who dates this cum bucket is a loser.This is feminism at its finest.Shot sighted, self centered degenerate cunt.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/99 & \cellcolor{green!27}2.02 \\  \hline
  \cellcolor{green!5}\small It's embarrassing to all the decent women around the world to listen to her talk.  She acts like an 18 year \textbf{old} school girl .   She contradicts everything she says in the next sentence.  I feel sorry for her.  She is definitely fucked up.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small i dont understand how are these industries running most of the porn is available for free online, regarding relationship it seems to be a lonely lifestyle may thats why drugs and suicide is \textbf{common}, a probable solution is when you retire move to a place where internet has not reached yet hard to find but there are places and may be change looks and date there\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small i think it would be easier for her to say her life is a wreck, but the \textbf{sex} is good\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The only way her relationship will work is if she considered to stop and leaving that part of her, she doesn't need to erase it because she can't and it will always stays on the internet forever, but she can't keep selling \textbf{sex} as a work.The entire idea of a relationship is a connection between TWO people anyway, so that's final.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small i only watch her solo videos or \textbf{lesbian} videos\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small 1 - It is a profession. The law considers it one. If you want it outlawed, do not watch!2 - Piece* and I'd like the arguments to why a \textbf{woman} having \textbf{sex} on camera implies she's "worthless".3 - Downright*, the word you're looking for is "degrading", and if you do watch porn you're admitting to enjoying watching what you percieve as degrading stuff = you're a sadist. 4 - gentleman* and may I suggest that you look up who actually do marry/date former or current pornstars. Tito Ortiz, Lukas Rossi, Jesse James, Wayne Static (RIP), a slew of male pornstars. Masculine men.5 - If you want porn to exist, it shouldn't 'damage your reputation' professionally, as it'd effectively mean a legal profession warrants 2nd class citizen status - but since you call the women 'worthless' I'm not surprised. (That aside, it is not a respectable profession, but this doesn't mean it should be able to "taint" you - difference)\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/162 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small In the end.... So \textbf{lame} she is and all her thinking about everything.\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small well every \textbf{woman} becomes one... a used product.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Which \textbf{pussy} you think feels better, a 25 who sleeps around on camera, who has learned to fuck way better than you ever will, or a 25 year \textbf{old} with 3 kids. No mans dick on earth can do as much damage as pushing a kid out can. Fools.\normalsize   & \cellcolor{green!5}Old, pussy & \cellcolor{green!5}Age - Over 65s, Nationality - Chinese & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small I can just imagine hearing Barney Stinson saying, "You dumped a PORNSTAR!  FRIENDSHIP OVER!!!"  The \textbf{weird} thing is that high level pornstars are probably cleaner than most girls and guys lmfao.  Like she said in the interview, she has to tell the guys she dates to get tested all the time.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small I think you're the jealous and insecure people she was talking about. This \textbf{woman} just wants to do her job and live her love life separately, but she can't due to this biased stigma where, when a guy fucks many girls, he's awesome, when a girl fucks many guys, she's a dirty whore, slut, scum of society, tainted, sinner, no humanity, no morality, no self-worth, no dignity. Yet, you people masturbate to pornstars all day and still be considered "moral", "non-sinner", "clean". Get off your high horse. Respect this \textbf{woman}. She has contributed to society (specifically us men), more than most of us ever could.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/105 & \cellcolor{green!5}1.905 \\  \hline
  \cellcolor{green!27}\small To be clear, men who are WILLING to sleep around arent in short supply- that's the distinction-that's not to say who actually has more \textbf{sex}.  I feel like we're agreeing more than disagreeing.  If male sexuality was the rarer commodity, youd see more male prostitutes than women.  You don't.I agree now I was calling her insecure - I had missed where I said that as an afterthought- to me, her tone doesn't sound like someone with a confident, warm heart- note when she talks about the men that date her, it's framed as them having problems, but then later talking about dating coworkers, and how she'll still get jealous.  Shrug, it just came off as hypocritical to me, it's fine if you see it otherwise.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/126 & \cellcolor{green!27}0.794 \\  \hline
  \cellcolor{green!5}\small italkcrab dude her job is to have \textbf{sex} at a camera how the fukc would you feel if your partner did that\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I'd be fine. Very situational.I think its better to project a scenario on someone else for this argument. I'll use you ok? If you were financially stable, she won't be a pornstar anymore. Done.OK, lets say you were not financially stable, and she does her work to contribute paying the bills. But she comes home everyday, does everything with you, has better \textbf{sex} with you, more frequently, every night, genuinely cares about you and grateful that you would accept her despite her profession. Yknow, like a normal relationship. If you both are supportive of each other, that's that.If she makes it big eventually, she will retire, and make other sources of income using her profession's bulk payments or contracts. (E.g Investing in equity and bond markets)This is a lot better than many many relationships where you partner sleeps with other people without you knowing anyway, and she doesn't even get paid to do it.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/156 & \cellcolor{green!27}0.641 \\  \hline
  \cellcolor{green!5}\small Actually I'm a 21 year \textbf{old} virgin so I'm just a sad unused product but I get what you're saying.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small ummmmm I think you missed the picture here, I said she was a "used product" meaning she's had a lot of dick in her ass, you can't say I'm a "used product" because like I said I've never had \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small She is pretty insecure if the only way she feels worthless is by getting her \textbf{pussy} zoomed in front of millions of people while it gets battered by a dick. Talk about attention seeking whore. No shame and no morals = degenerate piece of shit that does not belong in this society.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Cam You don't need to get fucked to be a product, being a product has \textbf{nothing} to do with with \textbf{sex}. Bering a product is being used, that's it.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small Harry Potter Without doing any work? she enjoys \textbf{sex} and gets money for it, that's her problem and she seems really fine so stop fucking other people just because they are different. I bet you have a tiny dick haha\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small To bad that even with that many \textbf{sex} partners you would still wouldn't even be considered...\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small some men will say a 25 \textbf{pussy} that doesn't sleep around on cam and never had kids before???why u didn't mention this type??\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@20GRIZZ20 STFU there is \textbf{nothing} called learn to fuck. You do not earn experience from getting cucked everyday. If anything you lose interest in \textbf{sex} because of this repetition go search for porn stars testimonies they regret going into the industry why people do not research stuff beforehand. It destroys lives and there is no going back. Experience huh? How many times you think she will be lucky before catching HIV or STD.  \textbf{Sex} feels better when there is connection and a relationship not by sucking your dick and spitting on it for hours till you nut.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/97 & \cellcolor{green!27}3.093 \\  \hline
  \cellcolor{green!5}\small \@Cam  She's cute but she needs to shave her cooch into a better style.Reminds me of the \textbf{old} days when crotch grooming was lax and reminded dudes of hacking through SouthEast Asia to shoot Charlie.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small People who go around calling other human beings used products because they've had \textbf{sex} should probably not be so judgemental.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@Garegh62 There is a difference between having \textbf{sex} with say 20 people and say 400, which she has had at least.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Has an awful lot of \textbf{nothing} to say about dating...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Ok, \textbf{weird} thing...She looks EXACTLY like someone else I know... and her last name (if that's he real last name) is exactly the same. The only problem is that Dani is older...\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Any man who would allow his WIFE have \textbf{sex} with anyone other then himself is not a man AT ALL . Go out and get a job and support your wife as a husband is suppose to . What a worm plus your wife is a whore , with your blessings of course . Unbelievable!!!!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small I'm a  secure man. And that has \textbf{nothing} to do with not being okay with your partner getting screwed by a different guy or gal everyday. I get it's difficult dating if you are a Porn star. But saying that a man is insecure for not accepting with a smile that your girlfriend fucks different people on a daily is completely stupid.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Porn is \textbf{lame}...\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small What a sad life. Your only worth is your ability to have \textbf{sex} and use fowl language.  Please repent by asking God for forgiveness. If you keep doing this you will surely be damned. So beautiful on the outside but putrid on the inside. You can do so much better. At the end of the day you have 2 choices. Heaven or hell - forever.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small \@Ebin A \textbf{nation} that suffers from shizofrenia. They're filled to the brim with preachy moralists and religious nuts, and at the same time they produce more pornography than the rest of the world. Mind-boggling.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small So the main lesson I'm getting out of this interview, is she can't date people in the business because of her own jealousy which can't be helped but her life dating "civilians" sucks because they get jealous/uneasy about the guys she has \textbf{sex} with. The only way she will find love is if she dates a "civilian" who has more self restraint with jealousy than she does......\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Wait until she lose her youth and hit the wall, go see how \textbf{old} porn star live and look after their 3 years of fame fades away\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small what the hell do you expect you stupid \textbf{woman}! your a fucking headache lol\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Barbara Elle ....she sounds like a \textbf{dumb} person. She thinks it's OK to get dicked, but wouldn't like it if her man got many pussies. No real man would take this \textbf{woman} home to introduce to his family. LMAO\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small I almost cried for her. It's so sad to see someone with no respect for \textbf{sex} or herself. Cheapening the one thing in life that connects a man to a \textbf{woman}. After all those men, it must be like having \textbf{sex} with a glass of water.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/46 & \cellcolor{green!5}6.522 \\  \hline
  \cellcolor{green!27}\small You can be a human being but expect problems settling down with someone. How many straight laced 9 to 5 guys that go to church every Sunday end up divorced after 3 years because they find out their wife was fucking the pool boy while he's at work? Being a \textbf{sex} worker just gives you a different set of challenges. At least they're honest about their choices.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small She's trying to make this about men's inability to cope with her \textbf{promiscuous} and shameful lifestyle, when in fact, her lifestyle makes her considerably less attractive to any man with pride and no agenda.\normalsize   & \cellcolor{green!5}Promiscuous & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Very ironic that she refers to a "civilian" dating her being jealous and it being very wrong that guys are so jealous, but when she refers to dating someone in "the business", then she would also be jealous of her in "the business" boyfriend - yet she makes it clear that there is \textbf{nothing} wrong when she is the one being jealous ~ "I can do as I like, but you're not allowed to do as you like".\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small spencer vanceI didn't Google her name! I actually Googled her name followed by the word "\textbf{lesbian}":)\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small juniorgod321 are you a \textbf{lesbian}??\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small spencer vanceNo, but I wish I was! Maybe if that was the case, If I was really a \textbf{lesbian},  that would allow me to lick \textbf{pussy} more often and I just love doing that, but  who knows, these days with the whole \textbf{transgender} thing going, maybe, just maybe I could claim to be a \textbf{woman} trapped in the body of a man a hook up with lesbians( and they would have to accept me as I am, right? Because if they don't, I would just call them bigots and claim to be triggered by them)!\normalsize   & \cellcolor{green!5}Lesbian, Transgender, Woman, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese, Sexual Identity - Female homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}4/96 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Why not just have a normal life with just a kinky \textbf{sex} life an not be looked at by everyone else as a \textbf{sex} object or a person who sucks dick for money\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Beautiful girl.\textbf{Nothing} wrong with \textbf{sex}.:)\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small Whores are great <3All women are whores. Lose your job = lose your \textbf{woman}. That should tell you exactly what she is. And it's good!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small A whore is a whore and at the end of the day when all is said and done, \textbf{nobody} will respect you.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small You don't have to be a pornstar in order to not get dates. Try being a \textbf{woman} who doesnt bang a guy five min after meeting him, like everyone else is doing. I figure it this way. I'm gonna get blown off if I give it up, or blown off if I dont give it up.So I err on the side of caution, and don't give it up😁\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small First off from a feed of football draft videos I get this.... Only at \textbf{old} \textbf{age} will this women realize how bad she messed up! Sorry but porn or having \textbf{sex} with a crap ton of dudes is not normal. Before any ignorant comments go and do some research about ex porn stars. I have seen many headlines about regrets. But hey whatever floats everyones boats!\normalsize   & \cellcolor{green!5}Age, Old, Sex & \cellcolor{green!5}Age - General, Age - Over 65s, Gender - General & \cellcolor{green!5}3/66 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Some people really over intellectualise this profession. This girl talks about being good at her job, like it's takes an education to be gang banged. Most (not all) but most men are pretty easily please sexually, if you are a attractive or not so attractive if you get on you knees and and enthusiastically give a man or many men a BJ then they are going to be happy.Any girl that wants to do this type of work will find work.Most will have very short careers then what will they do? It's not easy to \textbf{transition} from porn star to a regular job. In fact I haven't heard of it happening at all. Then as this girl admitted herself most men wouldn't like the fact that there will be videos online that there friends and family can see even if they quit years previously.Even if it did somehow get passed those difficult obstacles what if they have kids their children, wrong as it may be  will get tormented and teased, maybe bullied as soon as the other kids find out which is inevitable... Lots of female porn stars admit they love their jobs and it's quick money and no qualifications are needed apart from being open minded sexually. Lots of girls love \textbf{sex} but thankfully most choose not to go down this porn route, instead they use their brains to make money not their bodies. Most girls realise know matter how much they may like \textbf{sex} they are smart enough to know it would be financially rewarding only in the short term not in the long run as they don't often if ever move on to a regular job when the porn work ends. It then leads to poverty and drug abuse and potentially \textbf{sexual} abuse. Some people say not all porn stars are stupid, well smart women don't choose to be porn stars, I don't care how academically smart a few may be they clearly lack foresight and \textbf{common} sense to think working in porn will be good thing. It's not good for their \textbf{mental} or physical health, it's not good for them emotionally, it's not good for relationships, it's not good for their children and it's not even good financially in the long term. It's not difficult to know this, just a tiny bit of \textbf{common} sense and foresight is all that's needed but those that choose this profession lack both which is not smart at all...\normalsize   & \cellcolor{green!27}Common, Mental, Sex, Sexual, Transition & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Transexuality, Social Class - Working class & \cellcolor{green!27}7/412 & \cellcolor{green!27}1.699 \\  \hline
  \cellcolor{green!5}\small at the end of the day, a \textbf{ho} is just a ho\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Unfortunately, most of them get into the business for all the wrong reasons. Some go to Hollywood to get into acting and end up in the porn industry because it would be easier money than starving, some end up in Hollywood after being sexually abused much of their life (thus having a poor esteem on themselves and couldn't care who gets hurt), but when it comes down to it, it is Hollywood at it's best.. taking people, using them and spitting them out as shells of themselves. Mind you, some don't fall for it, but Hollywood is easily one of the most psychologically destructive cities on the planet. Every type and style of human predator lives there and think \textbf{nothing} of destroying people to make a \textbf{buck}.\normalsize   & \cellcolor{green!27}Buck, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/127 & \cellcolor{green!27}1.575 \\  \hline
  \cellcolor{green!5}\small Birth happens 1-2 times and has a healing period. Regular \textbf{sex} causes relaxation of the muscles, similar to how regular anal \textbf{sex} causes loosening of the sphincter. In order to remain tightness they would have to start a kegel routine.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Yeah yo \textbf{pussy} wore out\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small its like a fucking legal prostution, they are \textbf{mental}, some girls work they're ass off not to end up in shit like this and they are like, ooh fuck it its a good money and i get to live a good life o yeah sweet.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small exactly, you got a \textbf{dumb} muthafucka to date a porn star then catch feelings\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small That's DISGUSTING.  🤢 \textbf{sex} with several big dicks??!!! Ur \textbf{pussy} has gotta be all TORN UP AND EXTREMELY LOSE, NASTY!!!!!!!!!!!!!🤢🤢🤢🤢🤢 she says it feels amazing.  She's lying. I've asked SEVERAL GIRLS ABOUT THIS TOPIC...... And every single one of them says the same thing it's painful and it makes them bleed and it's not good whatsoever.  But she's promoting certain films and she's paid to say certain things that's part of Hollywood disgusting. 🤢🤢🤢 I'm not huge but I'm not small either.  Between 7 \&8... so my point is she's FULL OF SHIT AND GROSS.\normalsize   & \cellcolor{green!5}Sex, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/95 & \cellcolor{green!5}2.105 \\  \hline
  \cellcolor{green!27}\small This was \textbf{dumb}, but worth a comment\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Jelly Fam Professional pornstars get tested routinely... I'd actually feel safer having \textbf{sex} with one lol\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small They have \textbf{sex} for a living and you don't think the industry has stds😂\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small And your point? Are a special type of fuckin stupid who only watches porn but doesn't understand the work behind the industry? It's her job \textbf{dumb} fuck, of course she wants her bf to be tested.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small James Hussey Hey James! It's me again! I wanted too share something with you. Who invented the intrinsic Swiss watch? Man, Right? Where did that man get the brains to make the watch? Only one person could have given man the ability to put together the finest watches in the world. If you were thinking God himself, you were correct. Without the hand of God intervening and giving men and women the abilities to be \textbf{Doctors}, Scientists etc.. Their would be no civilization.When questioning whether God exists, look at your own life and look at what he had has given you as a person.\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/104 & \cellcolor{green!27}0.962 \\  \hline
  \cellcolor{green!5}\small Jake Harmon Yo Jake! For some reason your full message wasn't on my board. But I just found the rest of your message. I respect what you had to say.There was \textbf{nothing} false about I said to that gentleman. He sounded like he needed some direction and guidance in believing in God and Jesus.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Oh no, its one of those religious nutjobs and say \textbf{crazy} shit but they mean no ill will. So I guess you had too much exposure to Christianity to the point of no return where all you say is God is this and that. Yikes\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small saxonsteveYou're clearly not reading it. That's the problem.Jesus spent all his time getting drunk and hanging around prostitutes, young men and people suffering from various forms of venerial disease. The book might not openly state Christs \textbf{sexual} proclivities but it doesn't take a genius to read between the lines and figure out what goes on when you escalate some guru figure to that status. We've seen that scenario play out repeatedly in modern times and we always find out later that the cult leader was banging everybody elses wives and children at night while preaching \textbf{sexual} purity during the day.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small saxonsteveJesus, if he existed at all, was just a man. A man on which the Biblical myths are based. Can you think of any example of a man who was elevated to leadership of some cult that didn't end up with a thoroughly warped perspective, \textbf{sexual} deviance and substance abuse, etc? I can't. In fact, the louder these people preach about morality and sin the darker their closets seem to be when they're finally exposed for the frauds they are.The fact that the Bible explicitly mentions Jesus spending time around prostitutes, young men and people with sexually transmitted diseases is telling in itself. The story about the \textbf{woman} at the Pharisees home who kissed Jesus feet, washed them with her hair and perfume, takes on a whole new sensual meaning when you read between the lines and comprehend the sexually deviant nature of a cult leader. You really think he wasn't sexually aroused and intent on intercourse with this beautiful, sinful \textbf{woman} who was licking and massaging his toes? Please. He was male. Surely not even a Christian could be that naive.I suggest you try not just reading the Bible but actually thinking about it. Consider the contexts and connotations involved rather than beginning with the assumption of who you think Jesus was and then accepting the book at face value. Surface level readings of complex texts are rarely accurate. Particularly in the case of myths and parable.\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/241 & \cellcolor{green!27}1.245 \\  \hline
  \cellcolor{green!5}\small akhs denlew No Trolling or Patroling Here! Just the good \textbf{old} fashioned truth!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Who would want to be eating that \textbf{pussy} or doing it after it's had like 10 guys cumming in it, on it!! I don't care how much douche you do, that shits gonna smell and residue of cum is in that skin!! Don't even get started on kissing!!  Yuch!!!!!!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small I don't wanna sound religious but \textbf{sex} is a sacred thing,you don't wan't  anybody else fucking your wife,gf/husband,bf either your religious or atheist.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small What guy in their right mind would date a porn star?  disgusting.  Bring a \textbf{black} light with you to see if her face is glowing.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small What a stupid whore!! She thinks she is so damn cool and she is \textbf{nothing}  more than a low class slut!!!  Tipical  American female!!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Moral decay at its finest...you the man have to get tested all the time while i have \textbf{sex} with 100 of guys who may or may not get tested. "Chimerism" gentlemen...look it up if you value ur lives.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small She says that you have to get tested all the time because if you cheat on me as much as I trust you you can cost me my Job. Ok so hold on since this \textbf{ho} is a pornstar who just said that it's her job to sit on dicks as big around as her arm everyday and her who's are all over the internet there really shouldn't be any such thing as cheating in a relationship like that and that's actually the only way I'd probably ever date a pornstar is if I could f*ck who ever I want because you should not expect me  to sit around and be happy about you fucking other guys 24-7 for money if I'm not allowed to fuck other people. The Reality is I could never love a porn star unless she decided to stop being a pornstar. And a female pornstar should never expect trust or love in a relationship because you gave those things up when you basically sold your soul to the devil for easy money.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/177 & \cellcolor{green!5}0.565 \\  \hline
  \cellcolor{green!27}\small She can eat \textbf{pussy} so so good damn\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small put subtitl goddamnit. \textbf{deaf} people like porn too.\normalsize   & \cellcolor{green!5}Deaf & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} tried to charge me 50 bucks to take a picture with her.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small These are the same issues a prostitute will have because it's the same thing, it's all prostitution. The one she is having \textbf{sex} with is not the one who is paying (although in some cases it might be) but she is getting paid by the viewers of the film to do it with him.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small This human being is utter gutter trash. Quite hot, would I date her? Not in a million years. Get a proper job you slag\normalsize   & \cellcolor{green!27}Slag & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Call me \textbf{old} fashioned but I would rather a beautiful educated \textbf{woman} who hasn't had her cunt tossed around a industry for money and can be publically seen forever on the internet, meaning my kids , kids , kids can see their great great grandma being pounded by over 100 different type of dicks. Men are naturally protective and loving when they're in love, this \textbf{woman} will never find love because of the stupid choice to make money instead of respect. How she shrugs off " yeah you can see me with big men all the time on the internet " just shows how fucked up this \textbf{woman} is in her head. Why would a man want a \textbf{woman} who is not mentally stable in her own self respect ? why would a man want not sloppy seconds , thirds , fourths or even 10ths but sloppy 100ths , why would that make a man feel special to be with you? The thought of you smiling at me as my \textbf{woman} would turn my stomach. You needed a father growing up and you need to stop pushing your porn agenda to civilian men because I can speak for all of us, we would rather clamp our nuts down then marry a porn actress\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}6/213 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small Whores are only good for \textbf{sex}. Never try to have a real relationship with one. You're just setting yourself up for failure.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Why would you mess up a wonderful thing like \textbf{Sex} for yourself and be a Porn Star? Is the money with it?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small well, i expected her to be \textbf{dumb}, wasnt surprised\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Is better to have a hot girl and share her that an ugly \textbf{woman} just for you...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small got to get that \textbf{black} dick\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small what's the point of dating if:bf: Honey wana have \textbf{sex}?gf: can we make it Thursday, i'm working all week.bf: sure, i'll hold on to the flashlight till then.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small You know what, Imma take the 'really' out of my original comment and say she's just 'well spoken.' I say this because she explained the \textbf{weird} quirks of pornstar dating in an understandable analogy. That's it, she's not a damn scholar. She just explained this particular thing well.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small I went to high school with a girl who looked exactly like Dani Daniels...Guess what her name was...Dana Daniels. Its Fucking \textbf{weird}! Theyre around the same \textbf{age} too. I can only imagine how many other similarities they have...\normalsize   & \cellcolor{green!5}Age, Weird & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small I honestly had to pause this video every 5 seconds just to be able to finish it it's very weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small It's not the size of the dick that's the problem, it's the idea that pornstars try hard to make out that what they do is a regular job and that you can separate your personal life with the nastiness that they do. \textbf{Sex} is the most intimate activity a human can do so after getting fucked in the ass and swallowing 5 spurts of cum on camera, \textbf{nothing} can ever 'normalize' a pornstar's life after that. Boyfriends and husbands are just a faint hope of being a regular person again.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small what a \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small So, basically if you are a "civilian" you don't have the right to be jealous of her having \textbf{sex} with others, but the moment she is in a relationship with someone in the business than she is the one getting jealous. Pure logic.By the way, why is YT suggesting me this?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small "Its very hard to date someone that has \textbf{sex} everyday with other people"-dani daniels 2015\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Holy shit, I'm possessive myself, but this comment section is cringey with their responses. What applies sexually to a \textbf{woman} applies to man, especially if you're just considering the emotional aspect. Women aren't objects anymore the men. More importantly, you aren't even fucking this \textbf{woman}, so where the sanctimonious \textbf{r\textbf{ed}} pilled attitude comes from beats me\normalsize   & \cellcolor{green!5}Red, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}4/56 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} will probably need to give up what she does if she ever wants a serious relationship. Porn actress probably has loads of health consequences that where not even fully aware yet.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small hahahahahhahaa world has gone mad, no wonder all western \textbf{woman} are whoring around\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Peter Dawes u never had a \textbf{woman} thats why u would date that, i would fuck hell yeah but not date my man, think about it when you love someone its hard to share my ex cheated on me i tried to fix it for 2 weeks cuz we was together since i was 15 i could not  make it work i was seeing the dude's face who hit her on my mind so i left her thats been 2 years since i broke up with her and im 23 so the whole point of my little story is to show u when u realy fucking love a person u would not resist that person to be shared. So dumbass get to the fucking reality and get a Gf\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/129 & \cellcolor{green!27}0.775 \\  \hline
  \cellcolor{green!5}\small Hi guys, do you know how to sell my girlfriends \textbf{sex} videos? I'm from Philippines, got lots of pretty girls. Message me at hawk21121\@gmail.com\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Youtube! FIX the damn algorithm system. This recommended list is becoming a mess since 2013 and still \textbf{nobody} at youtube or google can't fix this.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Ya porn can be cool or fun at times but what good does it truly ever bring anyone? \textbf{Nothing} that you can't get put of life or on your own recognizance or any better then what you seek out in your own life!  We watch it for one thing then we finish and it's off and we go about life with the same needs and desires as we had before we 'rubbed one out" or got off from it..... And we can always still use our good ol imaginations still too.  I like to fantasize a bit porn is just easy stimulation up front in your face when it's on\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/110 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small A performer this is how delusional this \textbf{woman} is are you f**** serious or performer you my dear are a hore\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I once considered the possibility that the most harmonious society is where everyone fucks everyone, where \textbf{sex} is a communal resource without ownership, but according to her jealousy still exists. I wonder if she would feel differently if she doesn't identifies anyone as her boyfriend, and instead tread all men as just men.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Let me sum this interview up.  She is a very pretty, and semingly intelligent, young girl who will never be happy because she is a whore.  I do not call her that to be mean, it is simply a fact, she has \textbf{sex} for money and that is the definition of a whore.  Being a whore is not a choice that ultimately will make a young women happy.  In years to come her life will only get worse.  Interview over.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small So evidently this is not the video in which to hear the message that \textbf{sex} finds its most appropriate expression within the context of a loving, committed monogamous relationship?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small the wages of sin is death. This women may never experience life again. We can only pray that one day she sees God in a whole new way. We cant understand how hard it would be, to be her husband. But even now, God may have someone lined up for her, if she only chose to live her life through the eyes of God. Women like this are just like our modern day rappers. So deeply invested into the dark depths of what this world has to offer. That it becomes harder and harder to understand how God forgives you. \textbf{Sex} outside  of marriage is one of the most corrupt things you can do to your mind. People dont understand the value of \textbf{sex}, the meaning, its all just a joke. Life is real, we only have 1 chance. This life determines the rest of our eternity.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/147 & \cellcolor{green!27}1.361 \\  \hline
  \cellcolor{green!5}\small I don't think the aspect of having \textbf{sex} with someone else is the problem. The problem is the lack of morals, value, purity, and humanity.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small I heard they use crack to keep large dicks. don't need that garbage to please a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Fucking whore. One thing (possibly the only thing) I respect about Muslims is that they don't take shit from whores like this. Fuck this disgusting excuse for a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small + Insane \textbf{crazy} shocking Bruce lee She's a hypocrite whore that pretends men should deal with her bullshit, but she ain't cheap, she charges +3000 US\$ per video, theres better escorts than her for less than 1 grand\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Insane \textbf{crazy} shocking Bruce lee Before pointing your finger to her point your finger a yourself... Why do you even watch it when you are such optimistic\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Harry Potter And it also dsnt change the fact....That you being a jerk after watching other people  having \textbf{sex}...  Extracting the fun and then commenting on their lives\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Insane \textbf{crazy} shocking Bruce leeWhat kind of a grown man refers to somebodies father as "daddy?" That's just \textbf{weird}.\normalsize   & \cellcolor{green!5}Crazy, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Insane \textbf{crazy} shocking Bruce leeI don't have a sister? You just called a grown man, "daddy." Do you refer to your own father that way, too? It's creepy.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Dating a girl who has \textbf{sex} with other men? In which universe is that possible? She says it herself: It doesnt work, we are simply jealous beings. But jealousy is there for a reason. It's not just another stupid human invention.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small The fact she refers to her "\textbf{sex}" as "having \textbf{sex} with dick" shows how broken she is - having to detach it from an actual human being\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Alcohol... drugs ...porn ...divorce ... abortion... SIN. All that is killing your countries and preparing others to take over. Ask Jesus for help.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I wouldn't give a fuck if she fucked bigger dick than me...\textbf{pussy} is \textbf{pussy} I'd still bang her and oral her asshole anyday\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small how \textbf{weird} of youtube recommending me this after watching Louis CK\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I wouldve thought that someone in the industry dating another person in the industry would value eachother more solely on personality instead of physical or \textbf{sex}. They get enough \textbf{sex} so i was thinking itd be more reliant on personalities and a stronger bond, but i guess jealousy is inevitable\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Shes wifey... the most attarctive \textbf{woman} ibe seen and her personality couldnt have been better\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Ah, don't date civilians, they get jealous too easily and don't like the concept of me having \textbf{sex} all the time! they just don't understand us in the business and how it is, how my life is, and they just don't accept that and understand that! so date in the business, but that only works if you have the same goals. financial goals, life goals, career goals, relationship goals. and that is hard to find. Especially when \textbf{Becky} fucked you on set last night, and Rachel, and Kim, Lexi, Stephanie, Becca, Sarah, and Ralph. and I don't want you talking to them anymore... you know what... I guess we don't have the same goals in life anymore.. I can't stand you fucking other girls in the porn industry...so since I guess we have different goals in life, that's not making this work...It is over... I can't date civilians cause they get uncomfortable and jealous and I can't date you in the business cause our life goals don't match up cause you fucked all those girls last night. but it is not jealousy either. It's life goals. 2+2=5, so it is over and I wish my dating life wasn't so damn hard!\normalsize   & \cellcolor{green!27}Becky, Sex & \cellcolor{green!27}Gender - Female intelligence, Gender - General & \cellcolor{green!27}2/201 & \cellcolor{green!27}0.995 \\  \hline
  \cellcolor{green!5}\small Why would anyone date a pornstar? Totally fkd up. Why BE a pornstar? \textbf{Mental} issues. Emotional issues. Its not normal healthy behavior.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small This chicks a fucking \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Don't know why this showed up in my recommended videos as I have no interest in knowing the personal problems of willing \textbf{sex} workers.  However, I will say that this is a prime example of why living without a moral compass cannot work.  Morals are not only what holds our social fabric together, they hold our personal lives and mental/emotional health together as well.  These jobs and indeed society at large is not sustainable without Morality.  If you're a porn star, and you're feeling unfulfilled, lost, lacking... there's a reason for that.  What you're doing is wrong and it doesn't agree with you.   I appreciate how candid this girl was, in sharing the difficulties she is encountering, instead of lying about it and pretending that everything is peachy keen; as porn stars often do to make people believe that \textbf{nothing} is wrong with their occupation.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/145 & \cellcolor{green!5}1.379 \\  \hline
  \cellcolor{green!27}\small You missed your chance again. You sound like an 11 year \textbf{old} with that spelling and shit\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Kiril Hristov you think theres people that don't love hookers or people that are very open with there \textbf{sex} it does happen believe it or not love knows no bounds lol\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Hey Honey can you only do Anal Today ?? I would like to have \textbf{sex} tonight and I would like your \textbf{Pussy} to not to be stretched 8 inches around . The normal 7 1/2 stretch would be great ...\normalsize   & \cellcolor{green!27}Sex, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small spoken like a true \textbf{indian} hypocrite..\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small - Sorry honey, I've enough \textbf{sex} at work today. Perhaps next week when I'm off okay ?- My boss screws me. My colleagues screw me. And I can't even complain.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Kiril Hristov People swing people get exited by the idea of there partner having \textbf{sex} with others. People are so different from one another I cant imagine there arent atleast some people who wouldnt want it!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small You know she'd get home from a HARD day at the 'office', be wanting a little action your self or wanting to help her rehearse for her next scenes, and she'd be like, "FUCK?  is that ALL you EVER think about?  I take on several foot longs all day, get royally reamed, and you think I am even going to FEEL your 4-penny nail??  My \textbf{Cooter} is tired... you go whack it in the bathroom sink...tiny"\normalsize   & \cellcolor{green!27}cooter & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small I would only be ok if she did \textbf{lesbian} porn.  I am guessing there are pornstars out there that only do other girls\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Karan burn leave her instead of behaving like s betamale \textbf{psycho}. Or cant you get a girl of your choice? "Burn her .." Sick boy.\normalsize   & \cellcolor{green!27}Psycho & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small see people always focus on the negatives and never on the positives.Sure she bangs 20 dudes on a given day but look at the positives!!!!!1) if that girl still has her carreer ironically she is std free 2) she will force u to be responsable and get urself checked. U could be an asshole with fucking aids and b spreading it around not knowing it3) if u cheat on her she cant say shit to u4) if u know someone in the business (especially a well ranked one like dani daniels) u could convince her to help u get in to the buisiness. And why the hell would any man not want to do that. Free \textbf{pussy}+ a livable wage. Id sell my left nut to get into the business.5) belive it or not its actually pretty hot to watch ur girlfriend get fucked. Best part about that is that it eliminates most of the jelousy and lets u have a more healthy relationship\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/169 & \cellcolor{green!5}0.592 \\  \hline
  \cellcolor{green!27}\small Karan or you could opt to be a man with self confidence and leave her and get a \textbf{woman} who is more suitable to your needs\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@LedZep's X I luv \textbf{lesbian} porn.....\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@who0lee You clearly know \textbf{nothing} about human physiology. \textbf{Sex} is Love. The hormones released during \textbf{sex} are dubbed the "love" hormones, and also also released when you have intense feeling of romantic attraction/love. So this \textbf{woman} is a whore by definition\normalsize   & \cellcolor{green!27}Nothing, Sex, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}4/41 & \cellcolor{green!27}9.756 \\  \hline
  \cellcolor{green!5}\small i can see u can't get a loyal woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Karan and that's why there is so much violence against girls in South Asia, because of insecure little punks who pretend that they can own a \textbf{woman}......\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@who0lee no \textbf{sex} is the ultimate expression of luv . Unfortunately you have people who have forgotten that fundamental truth. \textbf{Sex} is supposed to be between to  persons who have given themselves to one another in an exclusive relationship. How one equates fast food and prostitution is incomprehensible and furthermore reprehensible. The reason we have this epidemic of broken homes , abortion, sexually transmitted disease is linked to this ideology that \textbf{sex} is just sex\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/75 & \cellcolor{green!5}5.333 \\  \hline
  \cellcolor{green!27}\small you see it from the perspective of losing something every time she is in a body contact with someone else which is not the case . As far as I know a \textbf{woman} loses her virginity only once (per hole)  Since that day till the day you meet a \textbf{woman} some other guys slept with her (you just don't know it till you ask about it) but when you met her you assumed "she is a nice girl ,cant be that bad"  which is almost always the case . In other words the difference between true and imagination was obliterated by your question and her honest answer .  She could possibly say to you I only met this guy I lost my virginity with and you are the next . Am I right ??? now in the case of the porn star the true is difficult to hide obviously but on the other hand isn't better to know exactly what is going on ?  Yeah I get it is extreme for some people but don't forget there is a big percentage of married couples we call swingers or wives cuckolding their husbands , so give me a break , the whole world is breaking apart and you feel bad about porn stars  ???  What is important is to care about each other and love each other . the rest is bullshit !!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/232 & \cellcolor{green!27}0.862 \\  \hline
  \cellcolor{green!5}\small S G there's a \textbf{thin} line between love and lust..\normalsize   & \cellcolor{green!5}Thin & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Hmm. When she's 50 n wore out m \textbf{old}. Or sooner? Who would want that sloppy hole. Nasty \textbf{woman}. Porn is for young boys n loosers. That's not real life n most of us know this.\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small You can literally go to school for 12 years to become the best biological engineer in your field, develop roboneurotic prosthetics as sophisticated as the limbs that you have on your body, develop several legitimate treatments for muscular dystrophy and ALS, hold three Phd's in neuroscience, robotics, and neuroscience, \textbf{Nobody} gives a shitBut suck dicks on camera and within a year you have a wikipedia page and a fanbase as if you're a notable person. It's the easiest thing in the world for an attractive \textbf{woman} to get laid. In terms of difficulty, there's tying your shoe, making a bowl of cereal, then 50 feet of crap: a pretty girl getting laid.  Whores get waaaay too much credit for just existing. By the way, that person that developed roboneurotic prosthetics is a real person. That's who we should be praising. Her name is Yoky Matsuoka. But somehow whores get more attention and praise for selling their holes.\normalsize   & \cellcolor{green!5}Nobody, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/158 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small Tommey Tommey ....you are so right and this \textbf{chick} is so incredibly dumb\normalsize   & \cellcolor{green!27}Chick, Dumb & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small 0:35  no its the same with cars, \textbf{nobody} wants a car that was owned by 10 people\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I think the problem is that you fail to provide confidence in your partner and they will struggle to connect with you as you act as if you are another level to your dates. I imagine \textbf{sex} on set is different to real life \textbf{sex}, right? The size of someones penis shouldn't matter to a guy that knows you love him right? I think there should be no trouble loving somone with this job. So first stop calling people who are not in the industry cilivilians. Your trying to date these people girl! Also you are responcible for the majority of insucurity in a relationship with sane people. Reverse the role, "baby it's okay, I mean the tits of the girl I fuck are as big as my head each, but D's are good too I guess... Wtf how would you feel? So just before you blame your job look at your own actions. That is all you can control.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/160 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small whata fucin \textbf{weird} ass video\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small If you watch porn, you're not in a position to talk shit about a porn performer or women's rights, etc. The shittiest thing about porn is that it's the lowest quality of \textbf{sex}. Instead of having \textbf{sex} with a beautiful \textbf{woman} and potentially developing a meaningful relationship and raising strong kids, you outsource that to a few asshole type men to abuse these women and leave you with hand.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/69 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small the only reason its harder to date a pornstar is becasue now you can confirm how far you are from the best \textbf{sex} shes currently having not even HAD lol but all the bitches in general fucked a bunch of dudes before you without condoms doing all the same whore shit these bitches do and yeah guy we all love it and hate it at the same time its life. Cant live with them cant live without them...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Wow, women are \textbf{mental}, getting annoyed at regular men for being jealous of a pornstars huge cock then proceeding to rant about why she would get jealous dating a performer lol........right\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small WE are trying our best to fight against \textbf{woman} treating as sx objects and here she is trying to act all normal conveying her rights and insecurities as a "CIVILIAN". I am not against sleeping with many people but earning money through it. Girllll there are lots of work out there. WE are in a \textbf{age} where people are making us believe that only opinions matter but dear \textbf{nobody} can change a fact.\normalsize   & \cellcolor{green!5}Age, Nobody, Woman & \cellcolor{green!5}Age - General, Age - Youngsters, Gender - General & \cellcolor{green!5}3/73 & \cellcolor{green!5}4.11 \\  \hline
  \cellcolor{green!27}\small They signed up for that job how is that being used as a \textbf{sex} object if u sign up for that no one else to blame but there self\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small now you're just discriminating her job. i'm not saying what she is doing is ethically correct. but that's her job she gets paid doing it. same as construction workers or comedians who sometimes ridicule themselves to get laughs. what i mean is there are different types of jobs that may need the use of the body and may put you in shame but that does not mean we should shame themand saying what she does is wrong is like saying dancing is wrong or being an entertainer(which what she is) is wrong..and yes she is a \textbf{sex} object (that's exactly her job description and what she does to entertain)but her being a \textbf{sex} object does not mean other women are \textbf{sex} objects or every women in the world is a \textbf{sex} object ..\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/136 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small porn is what all human being are using daily because we are \textbf{sexual} beings and we cant just rape someone because we horny.. and an industry like any industry requiers workers and that what she chose to do and thats none of your buisness\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small well she doesn't only do \textbf{lesbian}... there's a man there performing with her most of the times, i don't see you complaing about men being treated as \textbf{sex} objects there. She chose to be a pornstar \textbf{nobody} forced her so you don't need to put on your SJW cape, just chill and let people do whatever they want with their life\normalsize   & \cellcolor{green!5}Lesbian, Nobody, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General, Sexual Identity - Female homosexuality & \cellcolor{green!5}3/61 & \cellcolor{green!5}4.918 \\  \hline
  \cellcolor{green!27}\small The world would go mad in today's \textbf{age} without porn.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small OP probably meant that majority of viewers think of pornstars as \textbf{sex} objects while watching porn. For example, think of the last time you watched porn and was like, "I wonder how great of a person he/she is. I wish we can be in a relationship". Most people watch porn and think of pornstars as \textbf{sexual} objects with the only purpose of leading you to your orgasm. They don't think of pornstars as regular people with traits we admire such as respect, dignity, intelligence etc. Pornstars have no shame and they are the reason why people see them this way.\normalsize   & \cellcolor{green!5}Sex, Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/100 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small I actually wouldn't mind being in a relationship with this \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small WOMAN are \textbf{SEX} OBJECTs........The One Talking BULLSHIT About WOMANS RIGHTS are RELIGIOUS CHRISTIANS and ATHEIST FASCIST which doesnt Know How MIND Their BUSINESS\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Not saying adult industry is the way, but those other "moral decent works" almost broke my back. So, no matter how you put it, it's not gonna be nice, \textbf{fuzzy} and pretty. There's no such thing as an "easy way". It may look like it, but behind the curtain, there is an ugly truth.Like Mike said: "It's a dirty job, but somebody's gotta do it".\normalsize   & \cellcolor{green!27}Fuzzy & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small +TheIcelandicPrincess Why on earth are men nowadays expected to be cucked at every instance of life? It is her choice and only herself to blame. You're not weak for looking out for your physical and \textbf{mental} wellbeing. It's time for men to turn this franchise around and have their own \textbf{sexual} revolution, because the current one is skewed.\normalsize   & \cellcolor{green!5}Mental, Sexual & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/58 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small This has \textbf{nothing} to do with peoples physical and \textbf{mental} well being. This has to do with insecure people that can't handle having their partner with more experience than them.Same applies if the person in question was male.\normalsize   & \cellcolor{green!27}Mental, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small She's got a \textbf{crazy} ass for sure!!!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Shes smarter and more grounded than she looks.Unfortunately, her career choice will most likely prevent her from ever having that happy ending (pun nonintended). A family, a husband, hapoy normal relationship....possible but unlikely. When they do its an anomaly. I feel sorry for her. Hey a girls got to make a \textbf{buck}. But she might regret it one day.\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small people are disgusting.talk about "lack of morals" and in the same sentence say the worst of things about a \textbf{woman} who harms \textbf{nobody}.she's most likely a better person than most people in the comment section. especially better than those semi-retarded religious types.yikes.\normalsize   & \cellcolor{green!5}Nobody, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small What is wrong with this \textbf{woman} man the world is a wild place\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small She's all cocky now but when she gets older and can't rely on her looks any longer she'll end up being a lonely \textbf{o\textbf{ld} h\textbf{ag}}.\normalsize   & \cellcolor{green!5}Hag, Old, Old hag & \cellcolor{green!5}Age - Over 65s, Gender - Female age and physical appearance & \cellcolor{green!5}3/25 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small Dating "civilians":  "They don't like that I have \textbf{sex} with a lot of dick -- it makes them very insecure. It's irritating. There's a jealousy factor."Dating people in the industry: "It's hard to date a performer because we're jealous. We're all fucking each other. You will get jealous."huh funny how that works.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small it seems that you are a pornstar in the eyes of some goverment oficial for while you were watching porn and playing with yourself, the goverment official was playing with him self while watching you. edit, how does it feel, being an unaware \textbf{g\textbf{ay}} pornstar actor?\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small don't tell me going from taking dicks as big as your forearm to a regular size still feels amazing,that's bullshit and you know it.I'm not hating on her but lets be honest,who wants a girl that has had \textbf{sex} with hundreds of different people?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small What a cheap \textbf{dumb} trashy bimbo\normalsize   & \cellcolor{green!5}Bimbo, Dumb & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I actually feel for these ladies. This is their job, it's how they make a living. They're more or less condemned to solitude in the prime of their life. I mean, having \textbf{sex} with a bunch of people, and one-night stands aside, finding and nurturing a proper relationship must be extremely hard for them.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Slag\normalsize   & \cellcolor{green!5}Slag & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small It's almost as if being a \textbf{sex} worker means you have a dysfunctional \textbf{sexual} aspect of your life, and this in turn means you cannot have a good, functional relationship. Shocking.\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small my question is, am i alowed to have \textbf{sex} with different girls while living together with this \textbf{chick}? like the principe of free love... or do i have to take money for \textbf{sex} to justify doing it while beeing in a relationship?\normalsize   & \cellcolor{green!5}Chick, Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/42 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Ivailo Markov ok mr.\textbf{bald} guy\normalsize   & \cellcolor{green!27}Bald & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Is that you ? The \textbf{bald} guy often appears in vixen \& tushy.com ?\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Man all these people commenting are such dicknobs. She's a grownass \textbf{woman}, let her do what she wants with her own body. She has full control. She's not a slut, she's a \textbf{woman} with a sexuality and she loves that about her self. That's the coolest thing in the world. I hope she gets what she wants and one day she finds a dude who completely gets her and it works out!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small theres a small small SMALL  of people that would date a \textbf{sex} worker.....\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Boyfriend or girlfriend? So you're bisexual? TBH I believe a lot of bisexuals kind of ruin the \textbf{g\textbf{ay}} community because people who don't understand being \textbf{g\textbf{ay}} then think it's a choice\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/31 & \cellcolor{green!27}12.903 \\  \hline
  \cellcolor{green!5}\small jon carter stfu bitch.... If you're gonna troll at least be good at it, I mean we realize you are either A.) child B.) jobless adult, living with mommy, with a micro penis C.) You're scum of the earth and a telemarketer and have \textbf{nothing} better to do than be a nuisance to society. Every one knows what he meant. If you're not clever enough to be good at trolling, don't troll. Leave that to actual intelligent and creative people.  Any numb nut can point out a spelling era, grammatical era, and/or the misuse of a word..... Haha you used the wrong word!!! You so stupid!  Hey! Everyone  look at me i caught a mistake, look how smart I am! You know who else does shit like that????? Do you???? 1st graders.... So congrats you're trolling is the level of a first grader.... Here's you a gold star little buddy 🌟\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/151 & \cellcolor{green!5}0.662 \\  \hline
  \cellcolor{green!27}\small Geez, Cletus Tyresha, are you still here? Why did you comment on my post in the first place when it wasn't even directed at you? Did I hit a nerve? Did you fail to make it to high school, even? How are you actually as stupid as you are, that you're resorting to the same stupid internet arguments over and over, even when it's pointed out to you that you're too stupid to form your own thoughts?What's next, comments on how I'm a hater drinking hateraid and I'm triggered cuz I'm a \textbf{snowflake}, or some such idiotic rhetoric that people like you resort to because you're completely lacking in even the most basic ability to say anything remotely original? Are you mad about how long my posts are because reading (and writing) more than a sentence or two hurts your brain? Oh, should I "take notes" on your stupidity? Yes, I've already taken them. Thanks for the lesson! Now get back to watching some rasslin' so you can prove what an intellectual giant you are.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/176 & \cellcolor{green!27}0.568 \\  \hline
  \cellcolor{green!5}\small jon carter and he's still mad and pissy. I can't wait to see the novel you wrote to this comment. Lol. It's pretty obvious you have some type of \textbf{mental} health issue. I mean I'm no doctor, but I highly suggest going and seeing one little buddy.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small There was a guy who consciously knew he had an HIV infection and he was making movies and getting actresses sick. \textbf{Nothing} ever happened to him no prosecution. I guess that's not attempted murder if everyone is getting paid to f***.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Gordon Mendez - Cool bro, that's totally your choice.  But very, very, very, very, very, very, very, very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very,very few men like tasting another man's cock that has just been inside and possibly busted inside the \textbf{pussy} they're about to eat and fuck, especially when that \textbf{pussy} belongs to their wife or girlfriend.  Typically men don't like sharing their dick germs with each other through their partner.   But hey, to each their own.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Every \textbf{woman} is a "slut" get over it stop shaming them \textbf{beta male} lol just because you can't find a girl doesn't  mean you go around calling girls sluts.\normalsize   & \cellcolor{green!27}Beta male, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small Im Sorry for ur Lost Eson! But maybe u just dont know how to satisfy a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Why can she get jealous of her man fucking a girl in the industry yet her man who isn't in the industry  isn't suppose to get jealous if she has \textbf{sex} with someone in the industry.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Im not \textbf{racist} or sexist, but here would be a great place to put a \textbf{racist} or sexist joke and start an internet war\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small +zazoom84 bit of a \textbf{misogynist} yeah?\normalsize   & \cellcolor{green!27}Misogynist & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small A pornstar talking about the President on 60 minutes and it going NO FUCKING PLACE.  The worst BTFO \textbf{nothing} burger I've ever seen.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Black Shark and they barely make enough to get by. Should have done the porn tbh\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Black Shark How is fucking on camera selling your fictional soul to a fictional character?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Black Shark ok dude. That was hilarious.😂😂\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Black Shark You have no proof. Bottom line is..you're as clueless as me.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Black shark , That's exactly what I think about them too . I know a cleaning young women myself and she could be easily in this kind of business but she s a hard worker instead . i have a lot of respect for her.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Fuck ya feelings The proof is everywhere. You need to look deeper than what's only in front of you.And no, I am not a "church goer" I don't believe in church. I believe in one creator. A creator of all existence. Church is a business with the use of God as their marketing strategy.If you want to believe there is no God and that a human created all of humanity, or if you were created by an \textbf{alien} species, or if you were created by the "big bang" then be my guest and feel free to maintain your perspective in darkness. It's your freedom of choice. Free will.Hopefully one day, before you leave this realm, you will realize and understand that the way you have been seeing things was not exactly how you assumed they were. Simply sit down, and observe the world around you. Ask yourself what the root of this entire environment is. And ask yourself what your true purpose of living a temporary life with an average span of about 100 years is.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/179 & \cellcolor{green!5}0.559 \\  \hline
  \cellcolor{green!27}\small Black Shark You just said a bunch of \textbf{nothing}. Don't preach your ancient fairy tales to me.\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Fuck ya feelings Check out the disease, drug addiction and suicide rates of the porn stars. It is prostitution. They have \textbf{sex} for money. And they get forced drugs as well as sold and trafficked. You want fairy tales...how about a left winged porn industry life? It always ends the same. And like a good left winger they always blame Christians for their behavior. And if you want to rate judgmental...try reading Twitter and the left. Unreal judgements from those cocksmokers.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Fuck ya feelings I do not preach. I explain reality. You choose to keep the vail over your eyes. One day you will remember my words. There is \textbf{nothing} worse than a \textbf{blind} man except someone who chooses not to see.\normalsize   & \cellcolor{green!27}Blind, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Black Shark Do you not understand that calling me \textbf{blind} doesn't prove anything? You claim what you say is reality, but haven't show one shred of evidence to back that up.\normalsize   & \cellcolor{green!5}Black, Blind & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Black Shark Yet you can't point out that evidence. You aren't on some higher plane of being or knowledge than me. I'm human and you're human, so don't patronize me by acting like I'm \textbf{blind}. You either prove your claims or stop wasting my time. How do i have a closed mind when I'm asking questions? That made no sense. I could call you \textbf{blind} about anything we disagree on...it wouldn't make me look smart, in fact it would make me look egotistical and pretentious. You have no proof because if you did, you would simply state it. And don't bring up my online name as if that means anything, it only shows how judgemental you are.\normalsize   & \cellcolor{green!27}Black, Blind & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/117 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Popeye Biswo Porn stars actually see the light when the catch \textbf{sexual} transmitted diseases or full blown or AIDS.  Then they wake up and blame themselves lol!!!\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Funny is that this \textbf{crazy} bitch \textbf{woman} don't want to be judged by the society haha\normalsize   & \cellcolor{green!27}Crazy, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Black SharkLmao just stop.  The burden of proof falls onto you.  And atheism isn't a belief either. It's the lack of a religious belief.You absolute goon.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I believe devil exist in mind. Maybe a state of mind like depression which a pron star can end up in easily. When a young \textbf{woman} chooses to get money the hard way by not doing porn, she is just avoiding that future depression that can come out of that profession. At this point she is not sure that depression wont come out of another profession but chances are pretty low compared to being a porn star. That mentality to take hardship at present by caring about future is something that gets respects from society and that respect makes sense as that mentality is what takes us forward as a species. Now when a religious man respects that mentality, he might use words like "not selling soul to devil" but if you are ready to not get too much into the syntax, even those are wise words... but then an atheist cant help as his primary sense of having an elevated conversation is to keep proving the non existence of god and devil.. even in a porn stars interview.. LOL\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/180 & \cellcolor{green!27}0.556 \\  \hline
  \cellcolor{green!5}\small Black Shark So you don't have proof? 😂😂 that's pathetic. Telling me to go find it myself proves you can't prove and are basing your belief on a lie.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Black Shark you say it's everywhere yet can't give an example. You're talking a lot of bullshit.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Why is youtube linking this shit to me.  Don't watch porn.  Porn is really \textbf{g\textbf{ay}}.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Great.. Have \textbf{sex} with people on daily basis.. But no my partner can't have \textbf{sex} with anyone except me.. I can coz its my job and you can't take away my job... And if you are in the same industry.. You can't fuck this girl.. You can't fuck that girl coz im jealous..\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small She looks like hell in this interview..I mean from what you see on the news She was good looking..here she looks like she just walked off the set of \textbf{Jerry} Springer....\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small These girls don't learn and apparently they haven't take note from ex-pornstars. How the hell can she be in a relationship when her \textbf{pussy} is all over the internet being stretched out. I have to be an idiot to put myself with any of these sluts/whores/harlots! Porn is not a profession. It's exploiting ones sexually in the most unpleasant ways. Go get your education and find a real job!!!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small I think there's a bigger issue in dating a porn star other than you having a small dick compared to all the BBCs she would be taking....first on the list would be 1. Taking her to meet ur parents LOL2. Watching porn in ur spare time and come across ya girl getting smashed and saying things like "yes daddy"3. Buying her a hotdog, then rethinking the decision to buy her a hotdog and making her spaghetti meatballs...oh wait that doesn't work either.....um....how about soup.4. Have all ur m8s laugh at you and tell you how they bust nuts to ya girl getting smashedI'll pass 100 of the time and get me a nice church going bible reading \textbf{woman} that makes one helluva sandwisandwich.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/127 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small U can make it cute saying porn star but u a hoe start and \textbf{nothing} wrong with that just wanted to point that out.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small She has no class whatsoever. Dropping F bombs and talking vulgar in front of an \textbf{elder} like that\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small why is it cheating if the guy has \textbf{sex} with another girl but she can have \textbf{sex} with as many guys as she wants and doesn't see it as cheating? lol\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Uhh.. \textbf{nobody} wants a whore for a girlfriend.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Rock Star games Of course not its not really her .They use a stunt \textbf{pussy} .\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small lol, a stunt pussy\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small 10/10 pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small such a hypocrite. she doesnt like the "civilian" being jealous and calls him "insecure", meanwhile it's totally legitimate to her logic to not date a performer because "it's hard to not get jealous". so its ok when you are the one fucking but bad when is the one getting all the \textbf{pussy}.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small It really sounds awful for women performers because she really is in a terrible dating spot. She is actually very emotionally intelligent. Most porn stars give off a \textbf{dumb} vibe. That's her decision and she living with it. I really can't imagine my girl with other porn actors while I'm dating her. I really cant.the concept just wouldn't run well with me. Supposed they always say that their is someone for everyone.i hope she finds happiness.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small Why would someone want a serious relationship with a prostitute? You are being paid for \textbf{sex} = prostitution; try and twist it all you want, it is what it is.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@Hawk Who Knows All .. .. .. "\textbf{Nothing} wrong with it" , WOW, 'vim' becoming his mom's first customer is not wrong in your view. Bravo man Bravo. I think you like your mom more than as a son. lol\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small I think most guys problem is that \textbf{sex} should remain between boyfriend/girlfriend or husband/wife. She's playing it off like all guys are jealous or insecure and I don't think that's the case.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Steve Wright liked Lovelace org luben. They gory \textbf{old} then blame the industry\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Having \textbf{sex} is not a job here or china its just another way to excuse are sins\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Well i wouldnt want to have \textbf{sex} with a walking Hiv :D\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small A \textbf{dumb} cumdumpster scratches her head trying to figure out why dating is hard...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small What a mouth on this girl.  \textbf{Nothing} wrong with a little porn but this is too much.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Would you. Have \textbf{sex} with me\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Revelation of the century: "Civilians don't like that I have \textbf{sex} with a lot of dick." What insight! She has spiritual herpes for the rest of her life, tattooed permanently right onto her soul, and she complains about dating being a nightmare. Amazing. She is scum of the earth, and I think she knows it. I strongly suspect she'll commit suicide some day.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small the fact is your a \textbf{slag},it cant be denied\normalsize   & \cellcolor{green!5}Slag & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I know it's prohibited to have \textbf{sex} b4 marriage in the Islamic religion but I never know why. After this video which is explained alot to me why the ladies suffer and suck the bitter of it for the seek of fame.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small There's a porn star that just started working at my job, her name is Kate England, not going to share her real name on here though. She seems very confident and intelligent. It's a sales job and I thought she would quit really quick, but she's been doing about 10 hours of un-paid overtime each week, she's motivated. Really surprised me.she's a little shy, but she's nice. She doesn't know that we all know, out of respect we don't mention anything to her, but you can tell she's had a really really rough life. Online she's not that attractive, but in person she's actually very pretty.She became a legal adult at the \textbf{age} of 15 because her parents constantly had the cops at the house. Tough life.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/129 & \cellcolor{green!5}0.775 \\  \hline
  \cellcolor{green!27}\small Eh fuck it I'll tell you her real name. Her name is EDIT Fuck it nvm, pointless to mention it. The only thing you'll find online when you search her real name is an \textbf{old} picture of when she used to do real estate though.Some one recently made a burner twitter account of her with her personal contact info and address. It just got reported and taken down a week ago. That's how I found out she did porn, but most of the people at my job just knew her because she's pretty well known as a porn star.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small Dude I wouldn't want any. There's a vid of her getting fucked by a \textbf{tranny}. And multiple DP videos. FUUUUUUCK THAAAT\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Grouchy Right......because \textbf{sex} is so bad. Go fuck yourself.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Thats because AMERICAN STUPID PARENTING Trying to CONTROL their KIDS AWAY from \textbf{SEX} and HIGH \textbf{Age} of CONSENT 18... and After 18 They can DO WHAT EVER THEY WANT.\normalsize   & \cellcolor{green!5}Age, Sex & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Yeah but it makes a good cover if the silly stuff you do now covers up the stuff that you do in the parks that can be seen from space. Once they figure out that "matter is all quanta" thinky that people here keep leaving out of the standard model by collapsing it to appoint it I keep making before I go. Then "they" all will be able to see my encryption key as a touch password form space should the earth be evacuated in the stellar \textbf{age}. When identity is all unique and not sandwiched into any buzz words everyone might finally be mature enough to handle equal quality and quantities of life from future algorithms of Ai posturing candidate people to keep resources as far from total entropy as possible with little greed and more contentment. WhatHumanCondition\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/139 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}\small she was disgusted because Dani is so \textbf{dumb}...she dosn´t want to date other porn stars for the same reason normal people won´t date her, that some first class bullshit.if you decide to suck cock for money you desidet more or less between Job and Relationship, realy idiotic to complain about the results of your own decisions.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small There's an engaging way of doing an interview. i'm a radio DJ, this is a trade requirement. This girl would lose her job in a minute. You get them talking, make them feel comfortable and conversational. At VERY least, make them feel like you're listening and empathetic. This awkward silent \textbf{lump} dragged an otherwise interesting topic through the mud. byeeeee\normalsize   & \cellcolor{green!27}Lump & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small your potential boyfriends are not mad that you have \textbf{sex} with huge dicks,  they just dont like the fact that you have \textbf{sex} with other people period\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Dani Daniels, I'll date you. Most people i know can't grasp the fact that \textbf{sex} and a relationship aren't one and the same.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Why would anyone date them in a serious sense? Like yeah honey, go take some good cock tonight! They're not marriage material. You wouldn't want your future kids growing up and having someone at their school showing em their mom's porn. These are all things these \textbf{dumb} broads should've considered but now it's a surprise.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small People that have \textbf{sex} with random people or that are in the porn business, then you need Jesus I'll pray for you. God bless.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I don't really watch porn much but she's one of the few performers whose name I remember. She always struck me as having a great personality. I don't know if it's the hopeless \textbf{lesbian} in me or just my personality but whenever I saw her I always thought she'd be cool to be friends with. And after watching this I still think that. Plus she's hot AF.\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small z Did you not watch the video? They get STD tests regularly. Being a professional pornstar is much safer than someone who has \textbf{sex} with many random people\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small ThunderAppeal She is rich and famous. You are a fucking loser, a \textbf{nobody}.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Zero logic.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small I almost became \textbf{deaf} at the intro part.\normalsize   & \cellcolor{green!5}Deaf & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small How's a \textbf{woman} to express herself if it doesn't involve blaming men?  Agreed.  Especially about the mother part.  What fucking child is going to grow up and not be at least somewhat disturbed by the fact that there are volumes of videos free to the public, of their mother being banged from every angle by hundreds of men?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small 'morals, value, purity, humanity''respectable wife, amazing mother' You literally sound like an islamist. Do you watch porn? If no, why are you here?Porn isn't a respectable profession but a legal profession can't reduce someone's human value to \textbf{zero}, that is completely irrational.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small THOT\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Don't try to be or do normal people because ur job isn't a normal thing u answered ur self here people get jealous so u can blame anyone but ur self it's no one's foult just ur own u are a modern day hore u really don't even deserve to be happy cause people like u drain everthing that is good out of life no one told u to go be a fuckin hore u only think of ur self if u want to do normal then get a normal job like everyone else don't think like ur stupid, but u people are a big disgrace to your familys and u just don't give a shit any guy who is willing to have a real relationship with u is \textbf{dumb} and desperate just a fact, stupid hore!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/137 & \cellcolor{green!5}0.73 \\  \hline
  \cellcolor{green!27}\small Dating for pornstars..?? Lol.. they break the Rule No.1 of dating someone the second they step in into the studio.. how the fuckkkkk are you suppose to date someone when you are regulalry getting naked infront of camera and having \textbf{sex} with several guys EVERYDAYYYY...??? Thats just against the basic human psychology.. we are programmed like that.. there is a reason why we COVER ourselves up when we go out.. there is a reason why personal parts are called "personal parts"... coz you keep them personal.. modesty is basic human nature.. and porn goes against the very essence of that.. so yeah.. obviouslt \textbf{nobody} wants their girfriend/boyfriend  who they have REAL FEELINGS for to get naked amd have s*x with other people on DAILY BASIS..!!!\normalsize   & \cellcolor{green!27}Nobody, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/125 & \cellcolor{green!27}1.6 \\  \hline
  \cellcolor{green!5}\small Thot\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Disgusting woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small It's so difficult not to judge. Smh this womans entire life is about \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I look at pornstar as legal hooker\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Why all the comments are like 1 or 2  days \textbf{old} while the video is 2 years \textbf{old}.. YouTube buffing is here guys\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small lmfao women logic "men are insecure because i have \textbf{sex} with big dicks"real logic "guys don't want some disgusting \textbf{tramp} that has swallowed tons of semen."Women who are in pornography are fucked up mentally with daddy issues. This stupid whore doesn't realize "civilians" don't want to date her, they just wanna stick their dick in some porn-woman's bacteria infested hole. (Notice how I didn't say Porn actress or Porn star, because laying on ur back taking a cock is not difficult.)When i see a girl ive fucked dating someone, i laugh at that guy. I got her \textbf{pussy} for free and he has to pay for it. LOLNO HYMEN NO DIAMONDPOPPED CHERRY DON'T MARRYThey say one man's trash is another man's treasure, but you won't find me searching through the garbage for a wife.\normalsize   & \cellcolor{green!27}Sex, Tramp, pussy & \cellcolor{green!27}Gender - Female sexuality, Gender - General, Nationality - Chinese & \cellcolor{green!27}3/140 & \cellcolor{green!27}2.143 \\  \hline
  \cellcolor{green!5}\small I think she's just embracing who she really is, \textbf{nothing} bad about that, besides it's HER life not ours.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small When she gets \textbf{old} by porn industry standards she will be cast to the side. No man wants sloppy seconds but this bitch is just slop. The amount of cum she has eaten is mind boggling. The novelty would wear off quick and then anyone would resent her. I hope she becomes a Muslim \textbf{lesbian} with a hijab on\normalsize   & \cellcolor{green!27}Lesbian, Old & \cellcolor{green!27}Age - Over 65s, Sexual Identity - Female homosexuality & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small And why today even when the video is 2 year old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Same thing here. Why is Youtube recommending this random \textbf{dumb} hoe to me? This literally appeared between a Theo Von standup video and "How to Help a Shy Timid Kitten | First Days Home!" video. Youtube is going down the drain quick I swear...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Same here bro...wtf.....I didn't even searched about \textbf{sex} for 5 months\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Omg this is so \textbf{weird} same here\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Local Guide lol😂but i enjoyed it.she seems like a cool \textbf{chick}.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small *3 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Cause you mom's gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Youtube \textbf{crazy} asf some dark side also\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Alcohol... drugs ...porn ...divorce ... abortion... SIN. All that is killing your countries and preparing others to take over. Ask Jesus for help\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Wow! Perfect timing! I just watched her get eaten out like 20 minutes ago. She has the most gorgeous \textbf{sex} face of all time.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I was wondering why this showed up in my list of recommends too.Yesterday i left political vid running while i was busy. At some point i heard it was smth else. And again after a while it was about thailand and some city there ppl go to for hookers. I saw some of that as i got back. I guess thats got to be it.\textbf{Weird} though.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Same here this is \textbf{NOTHING} like the videos I usually watch.JewTube is spreading its own agenda apparently.And SHE is Jewish as well with Jewish bosses in Jewish productions.But my reaction was the opposite:  ""Wake up twit. Quit your DAMNED JOB and repent of your filthy lifestyle and learn to live instead, with REAL LOVE serving your Maker in Heaven claiming the forgiveness of sins by the sacrifice of the Son of God.""She may very possibly never get this chance again.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small Me as well and this is my 14 years \textbf{old} daughter YouTube and I decided to take a look at what pop up for her to VIEW... THIS IS NOT ACCEPTABLE YOUTUBE .............\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Local Guide cuz you a \textbf{freak} fronting like you ain't searching for this shit\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small just wanted to write the same thingthere just whores \textbf{nobody} want to date a whore\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small You got recommended this video because you must have Alexa and Google heard you having \textbf{sex} since they hear and see everything you do.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small they know u are a \textbf{freak} duhh\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Because you a \textbf{ho}... Lol 😆😆😆\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Cause you search \textbf{sex} too much on yt\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Honesty is everything. \textbf{Nothing} else matters\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small What kind of "civilian" guy gets into a relationship with a pornstar? It has \textbf{nothing} to do with being insecure, more like normal human nature, which she herself alludes to when she talks about dating other pornstars, hypocrite much?If a girl is taking multiple 10"+ dicks like its \textbf{nothing}- she isnt even going to feel your 6,7,8".. again.. \textbf{nothing} to do with being insecure, it's just a fact.To some people- \textbf{sex} is a form of compassion and love, who woulda thought it.. I mean it is a relationship after-all...If your a porn star- that's great, but don't have the notion that your the "normal" one, just accept your messed up...\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/113 & \cellcolor{green!5}2.655 \\  \hline
  \cellcolor{green!27}\small I would date this \textbf{woman}. I respect that her job is simply that.  It's her job. When I commit to someone, I don't just claim ownership of thier genitals.  That's ridiculous.  Dani Daniels is a total fox, and from how well spoken she is, a pretty genuinely awesome human.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small stupid ho\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small What a disgusting slutty \textbf{ho}. Who would ever date that hot mess? Sloppy ass loose ass \textbf{pussy}, like throwing a hotdog down a hallway lmao\normalsize   & \cellcolor{green!27}Ho, pussy & \cellcolor{green!27}Gender - Female sexuality, Nationality - Chinese & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Don't be so autistic, grow a pair! If mommy is so \textbf{dumb} she doesn't think you jack it then mommy's well must be pretty dry\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Thinking that a \textbf{woman} is a whore because she fucks for money, means "feeling insecure" these days? Don't make me laugh. I wouldn't even shit on her, because how disgusting she is to me.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Bigsplash1   what? don't believe me? of course there's honest and decent women out there, but just pay attention to it a little and you'll see it. How often does a \textbf{woman} not own up for her mistakes or shortcomings and blames it on something else (and more often than not that something has a lot to do with men).\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small just another dirt \textbf{ho} with no morals\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small nick supreme since they traffic more human \textbf{sex} slaves than any other industry that you support.  Since the invade children's minds and poison their psyche for material consumerism.  But for you, who worship authority, you'll wait a long time for your masters to declare harming you, illegal.  Any other \textbf{dumb} fucking questions, peasant? Get back to work\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small tommy cane1151 - If you have an issue with the porn industry, which is perfectly legitimate, attack the people who run it, not Dani Daniels. 2 - It is not criminal. It sadly today defacto functions as a criminal industry (which should be solved through regulation IMO) but it is not and consequently you are wrong.3 -  " But for you, who worship authority, you'll wait a long time for your masters to declare harming you, illegal.  Any other \textbf{dumb} fucking questions, peasant? Get back to work" Not an argument. Where have I claimed I "worship authority"? I have no "masters". I am not a "peasant". If you want to be taken seriously, refrain from this type of ad hominem nonargumentative nonsense.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/125 & \cellcolor{green!27}0.8 \\  \hline
  \cellcolor{green!5}\small nick supreme "attack" people who run it.  ok we differ in our definitions of attack. "not dani daniels"- why not? fuck her. she's a scumbag. it's not criminal.  sure it is. mass hyponsis gets a big "fuck you" from me to you.  they redefined the value of \textbf{sex} for material gain. complete low life shit that designed to sell shit you don't need or really want. keeps you fucking \textbf{dumb}.  if it hurt business they would have banned it.  worship authority: yes you do.  criminals clearly run that shit. they cohort and bring YOUR women down. you think all of that shit is ok. you think its fair play, you think its cool to bank on ignorance and addiction and distribute that shit.  your women arent as important as you going shopping, and you spending money on shit you don't need, so that you can get a chance of fucking the pretty little \textbf{r\textbf{ed}} head at the convenience store.... you know the one with the wooden foot.\normalsize   & \cellcolor{green!5}Dumb, Red, Sex & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/167 & \cellcolor{green!5}2.395 \\  \hline
  \cellcolor{green!27}\small Wait wait wait...Her job is to fuck people.And she needs her partner to be tested...Even if that person havent had \textbf{sex} with anyone because she cant take the word for it.I wouldnt even want to be close to that girl after hearing that.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Do you realise that you just said that you got jealous if you date inside the industry because they had \textbf{sex} with your friends but then someone outside the industry shouldn't get jealous because have \textbf{sex} with multiple people... Think about that!!!!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She can fuck everyone she wants cause its her job and the civilian need to understand that and not be jealous , but if the person she is dating is also a *performer*, they cant fuck other people because she ll get jealous???? k stay \textbf{dumb}..\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Same as dating any other \textbf{chick} really...only you can actually get to see it.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small You can't "date" someone who has \textbf{sex} with other people every day -you can be their pimp though.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small This \textbf{dumb} \textbf{bimbo} has to understand that she has destroyed any chance of a normal life of love and family.That is all gone, traded with her soul.She is left with money, drugs, orgasams and a couple of years of porn fame before she is discarded as to \textbf{old} looking.Enjoy.\normalsize   & \cellcolor{green!5}Bimbo, Dumb, Old & \cellcolor{green!5}Age - Over 65s, Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small I'm probably the small minority where I don't mind how many guys a \textbf{woman} has been with. As long as they don't bring that into the relationship. Don't talk about what kind of dick you had in there, or what the \textbf{sex} was like. Don't use your profession as an excuse to cheat (yes, that can happen). Most importantly, don't talk down on your partner. Of course that doesn't just apply to pornstars. You don't need to be in that field to apply those principles.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/85 & \cellcolor{green!27}2.353 \\  \hline
  \cellcolor{green!5}\small Wow this \textbf{chick} actually good personality\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small THOT DETECTED\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small If she breathes she's a THOT\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Soooo moral of the story... don't get into porn. As fun as it may seem to get paid to have \textbf{sex}, that's exactly what causes you to not be able to have a normal life outside of your job\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I know right. Soo shocking lol. all sarcasm intended Seriously tho, female nature never ceases to amaze me lmfao. It's like the \textbf{old} saying goes. A key that can open many locks is a master key. A lock that can be opened by numerous keys is just a bad lock. That being said, why would any rational man wanna OWN damaged goods? Most you could hope for is to be a RENTAL for a pump and dump. I know it sounds harsh as the SJW's say, but sadly reality does not care about your fee fees.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small Unlesssssss you just fuckn single gang gang \textbf{nigga} and wanna fuck all day and be like gene Simmons then this is the job\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small some \textbf{fat} loser with no friends or life simp\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small 😌yup... \textbf{THOT} nuff said Begone\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Old interview. She's married now.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Imagine saying that to a \textbf{black} person... would u do that? No.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Anna he has a right to say that to anyone no matter the race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small South Asians are brown not black\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I can imagine it is a very tough position and occupation to be in. I say a lot have done porn out of insecurity. I would prefer porn never existed. I think that she is rather secure with what she does now though. If she wants a relationship she has to find something secure and sacred. That would be in an emotional \textbf{sex}. I think staying away from an ex, is a very fair compromise, if you want something as beautiful as a relationship. That doesn't mean stopping your career choice but it does mean keep the sensual slow and emotional side of \textbf{sex} to the person you cherish and as long as you and this person have something special that you have with no one else, it can work. It's absolutely a hard person to find, but there is no other way. There has to be something special between you two. Something sacred. At this point she is where she is. The only way forward is both people accepting that. I hope she and the other people in her situation find it.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/183 & \cellcolor{green!5}1.093 \\  \hline
  \cellcolor{green!27}\small Only a cuckold would want you for a wife.-So how was work today honey?-Swallowed a lot of semen from five \textbf{black} guys.-Very nice give me a kiss and I'll cook us some nice dinner.I don't think so, has \textbf{nothing} to do about insecurity, you're disgusting.\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small how about.... well.... find another Job for a man you really really love! Because let's be honest... for "civilians", having \textbf{Sex} with somebody else is cheating, no matter if you are drunk as hell and didn't know what you were doing, If you got a "weak" moment because your relationship becomes a place where you fight a lot (temporarily) or if you are in the Porn industry. For most people it's cheating... well because IT IS..\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small Why would you even date her, not like you can have kids with someone like that. Sure if you're looking for \textbf{sex} , but it's not a long term relationship ever\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small The definition of a whore is (of a \textbf{woman}) work as a prostitute."she spent her life whoring for dangerous men" synonyms:work as a prostitute, sell one's body, sell oneself, be in porn"she spent her life whoring"\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small You can't turn a whore into a housewife is the \textbf{old} saying, and it's said for a reason\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small what about her getting tested? I mean, yeah, she gets tested, which is kinda good for the partner, but still, there are risks of some fuck ups every single day, she could get infencted. PLUS I thought HIV for example is only detectable in a test after 6 weeks. So yeah, what good is a test, when she had the sperm of four men inside her last week, and you want to have \textbf{sex} with her?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small It's \textbf{weird} watching someone smile and talk and then watch them get fucked and swallowing cum later...\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Id date her, id have no issue with her fucking other men or women, its a job shes not ' cheating' on you as its a job, the texting side of things i wouldnt do, but i wouldnt have \textbf{sex} purely because i wouldnt want to, but yunno you can love without having sex\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small She seems like an intelligent and cool person but this \textbf{woman} has made her bed.  Finding a normal guy who respects her past and loves her body is going to be like finding a needle in a haystack even 20 years after she's worn out and retires.  Hopefully she can find another retired porn star when she's 45 or 50 and hopefully that person will be faithful.  She's pretty much traded a normal life partner off for what I hope will be a lucrative porn career.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Sorry \textbf{chick}, but you are on the other part of the lane. Keep counting your money. Enjoy.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small NOBODY wants to date a whore Dani (unless you're a degenerate), it's as simple as that.We're not "Insecure" nor do we feel "Inadequate" but rather repulsed by the filth that you participate in.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Never date a porn star kids, your friends will see your girl have \textbf{sex} all the time\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small i love her hairy pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Porn is toxic, it devalues a person. Maybe you wouldn't see it at the beginning (\textbf{sex} is great) but once you start having feeling for that person things change.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Just let her be her. Some women are \textbf{nothing} more then fuck dolls for us.  Just like how women use super rich men for their money. Some men are so ugly by the time they get rich....all girls want is their money.So it's ok.  Hookers and prostitutes have been around since civilization started. Before that.....rape and pillaging was very \textbf{common}.It's 2018.  If they want to be whores and be fucked by lots of men on film.....then go ahead.  They are fuck dolls.  Everyone of us would cum on their face without hesitation but 99.9 of us would never fucking have a baby with these whores.I mean come on.  if they have kids.....their kids will see those porn videos sooner or later.  So either those kids will grow up being disgusted or might turn out to be huge fucking whores as well.  That's just life.I mean if you want everyone to see your gaping \textbf{pussy} and butthole then you have some issues or money problems.No normal person would think it's a good idea. For all you guys who disagree...go ahead and make a video of yourself fingering your asshole and see how your life goes.  Cause a video of a guy fucking a girl is \textbf{nothing} compared to a girl being gang banged by a bunch of guys who just wants to leave a load inside that girl.Lets be real here. A lot of people would pay 500\$ to fuck these porn stars, but we would never fucking take these whores home or anywhere UNLESS you are one of those cuckold who is fine with seeing someone cum inside his wife ect.These women will have to deal with a lifetime of shame once their kids grow up.  I mean what's worse then growing up and one day seeing a video of your mom getting gang banged by 10+ guys. lmfaoThese porn stars should just keep on making videos and shut the fuck up.One of these days prostitution will be legal and maybe they will get more respect.Most of these girls have fucking problems if they are porn stars at \textbf{age} 18-25 or whatever.when you're 35+ and go through a divorcee and have grown kids..you can do whatever the fuck you want.  That's different.A 18 year \textbf{old} girl who gets into porn OBVIOUSLY had a very rough childhood.I know a girl who is 22 now and she is such a whore.  She wanted to do porn but idk what happened. It didnt work out i guess.Anyways, i remember her mom always talking about \textbf{sex} and she talks about fucking her boyfriend like guys talk about sports.I just knew her daughter was going to grow up being a whore. Ive known her since she was 14ish and the moment she was 16.....she fucked almost everyone who wanted to fuck.  fucking was talked about by her mom constantly, so of course it would be a normal subject. THE DAUGHTER learns from her mother.  lolMost of these girls have problems and they are being used to make money.I'm not complaining. I just think it's so fucking funny how these porn stars think they matter. The way they talk....Bitch, everyone wants to fuck you and dump a load in you, but they don't want to kiss you. trust me.\normalsize   & \cellcolor{green!27}Age, Common, Nothing, Old, Sex, pussy & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters, Gender - General, Nationality - Chinese, Social Class - Working class & \cellcolor{green!27}7/561 & \cellcolor{green!27}1.248 \\  \hline
  \cellcolor{green!5}\small Because you watch alot of \textbf{g\textbf{ay}} porn\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small 5 seconds, i have \textbf{sex} with a 'lot of dick' CHARMING  i have \textbf{sex} with huge penis's... it makes guys uncomfortable.... NO,  If it DOESNT make you 'uncomfortable' then we know all we need to know about your body and your brain....thanks, 5 seconds was enough\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Just shut up and show your \textbf{skinny} tits bitch ....\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I like how she demands that her partners get tested for disease, "like, all the time".  She is the one having \textbf{sex} with multiple people every day but she worries that her partner is likely to give her a disease?!  lol  Something doesn't add up inside her mind.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small its tue ! even if someone gets the world they will neber be satisfied. This bitch is getting all the \textbf{sex} in the world pornstars are getting allthe \textbf{sex} ie world why would they want to date ?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small i like the way she smiles , the way she talked , she seems like nice person, I believe she earns well , I don't care who's judging her , also hope she also doesn't care about people who tries to being judge everyday, she brings happiness to many people , I never seen her work but I know she have different world of her own , as she said controversy's of her relationship but here are many people who can truly love you, with respect to her I wanna say she's giving fuck to earn also shes earning fame-love-and many other things but people who called her civilians giving fuck to that boss to who they hate from that they are not earning enough money- not respect- \textbf{nothing} but same people judging her , I say judge yourself first before saying anything to her , m not blaming here anyone just to narrow minded people.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/156 & \cellcolor{green!27}0.641 \\  \hline
  \cellcolor{green!5}\small People need to take a chill pill.  It's her profession , they act the scene and get paid ; very well I might add. \textbf{Nothing} wrong in that.  Believe it or not the s*x they have is far more safer than a guy picking up a girl in a bar; its safer than the s*x even after dating someone for a while.  Because you never know the STDs and you just hope he or she is clean.  But in porn, there is a strict guidelines, they have to take test every week or month or so.  Sometimes they even do the test just before the scene.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/106 & \cellcolor{green!5}0.943 \\  \hline
  \cellcolor{green!27}\small Each of us has a different opinionAs a person, I do not like to wake up every day and on my side a \textbf{woman} who shares with me a lot of men is disgustedSo I do not want to get out of my door and see a \textbf{woman} like her coming out of the opposite door, this also affects with disgustBut she is free to doWho am I to judge themThe best women are those who keep their bodies for themselves and their husbands. Only those who are respected because they respect their spirit\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/99 & \cellcolor{green!27}2.02 \\  \hline
  \cellcolor{green!5}\small Stupid slut, \textbf{nothing} more, \textbf{nothing} less...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small She gets jealous of her man getting laid, how does she think a 'civi' feel? At least she gets \textbf{sex} when she wants it and paid, but not much of a full life being lived there\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small yeah man, we all know \textbf{sex} as a hooker/pornstar doesn't count.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I think you forgot to take your morning pills of \textbf{mental} illness\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Nigga want a scholarship?\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small If you think the \textbf{sex} made for the sake of getting paid doesn't count... well, that actually would be a valid opinion. I can't judge.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Fact of the matter is, is that a guy wants exclusivity with his \textbf{woman}, that can't happen in your line of work.Get a better job and start living.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I don't feel sorry for her because hey... \textbf{nobody} said go and fuck tons of big dicks everyday...she chose to live this life... fucking infront of a camera isn't the only job you can do... if you choose this life then you gotta deal with the consequences - period\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small I wouldn't call swinging the most natural way of having a relationship with a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I will take a hall pass, sleeping with anyone who has \textbf{sex} with multiple partners is just a turn off.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small insecure? its just gross because literally you get fucked probably by 150 different men a year. And your a \textbf{ho} .......\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small My fellow men should stay as far away as possible from this \textbf{woman} and all like her\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small damn, this girl is a \textbf{dumb} bitch. who the fuck would date a pornstar\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small why would she even bother to have \textbf{sex} when she come home from work,...imagine her boyfriend or husband who is with porn actress and have less \textbf{sex} than avarage men.weird\normalsize   & \cellcolor{green!27}Sex, Weird & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/30 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The reason dating is hard for her is because it's her that makes it hard  (no pun intended).  She says civilians get jealous of her having \textbf{sex} with porn stars but she gets jealous of porn stars having \textbf{sex} with porn stars. She wants the best of both worlds but she can't have it. So basically she makes dating hard on herself.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Get out of my recommended THOT\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Lol someone got triggered. And no I am not idiotic enough to reveal my face on a public page such as youtube without any reasoning behind it. And why are you mad again? I was giving her some advice. She can take as many dicks she wants and we can all enjoy the sight. You \textbf{g\textbf{ay}} or something bud?\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small Tameer تعمیر \textbf{Nobody} is forced to watch porn. People destroy themselves\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small she is \textbf{crazy} porn star\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small moody guy  what do u mean u people ? Were not playing the \textbf{race} card now arnt we?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small +Tameer  I dont know with that, Owen Heart, Eddie Gurerro, Chris Benoit, Randy Savage, Lady Elizabeth, Chyna; would you say wrestling destroyed those individuals and their families? People "choose" to go into such businesses \textbf{nobody} forces them.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small So you can't even argue the proper argument? This has \textbf{NOTHING} to do with Trump. The argument is whether or not the deaths are for no reason, not whether they increased, fucking idiot. While the states are busy trying to fight off the people who are a real threat to the middle east, like islam, people will get hit in the cross fire. They are saving many more lives than they are taking and it's not even close.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Chris71319 who pays money for porn this day and \textbf{age}? There are countless free images and videos all over the internet\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small how do the female porn stars know if a non porn star male interest in her for her, or because she is porn/movie star or seen as a \textbf{sex} freak/kinky girl.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small what a \textbf{lunatic}...she complained about "civilian" jealousy and then goes into a rant about how she cant date porn actors for the same reason.  Almost all these girls are just broken I think...\normalsize   & \cellcolor{green!5}Lunatic & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Do you mean "colleague"? First of all she said that she understands that people get jealous and that its hard (for a normal person) to be in a relationship with someone who's a pornstar. She never said that "people should be okay with it", in fact she said the opposite, its hard for people to be okay with it so in general its hard to find people to date. As for her "colleagues", she said people get jealous and that it doesn't work, she never applied a double standard anywhere. Also, when its with "colleagues" its fundamentally different, she's in an industry where everyone know each other. A couple within in that industry is confronted with their partner having \textbf{sex} with others right to their face. Imagine a regular relationship where one of the partners regularly meets their ex. That causes problems in relationships all the time. Now imagine that when they meet their fucking each other.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/157 & \cellcolor{green!27}0.637 \\  \hline
  \cellcolor{green!5}\small Lol, you sound as delusional as she is...  And No I dont mean "colleagues" at all otherwise I would have used that word.  A Nurse has "Colleagues"... This \textbf{woman}...Not so much\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small poor \textbf{woman}...has to get huge dicks up her ass for living...what a waste of life\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Wtf is up with everyone calling each other civillian? Since when is it oke to try and make others less because they arent doing what ur doing?Besides, correct me if im wrong... Isnt \textbf{sex} meant to LOVE each other? To have a time only you and her have? Something special? Instead u get fucked by huge doctor adjusted cocks and call people civillian and jealous. Jealous because ur a slut? Fuck yeah. I wish I was one.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Mutated Nutit takes a bit of intelligence to communicate and be understood, Dani is successful at that.What hurts is that she's a porn star and that upsets most people, she should be \textbf{dumb} and barely able to talk.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Shes not clever at all. Shes butthurt that men wont date her but doesnt realize that its against our primal instincts to be dating a \textbf{chick} that gets a different dick everyday. Men generally dont like to be cucked. Part of that has to do with paternity uncertainity.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small what a fucking \textbf{dumb} bitch she is, she has to ask her partner to get tested so it doesnt cost her her job??? she,s the 1 taking all the dicks, what a fucknuckle\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small "Imagine going to a school, and having \textbf{sex} with everyone in that school, and then trying to date people that are in that school but they just fucked your friend yesterday"Um no thanks, I don't want to imagine going to jail.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Al Phuckya fuck out of here with that no relationship and \textbf{g\textbf{ay}} shit\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small I would never date a porn star, \textbf{dumb} idea...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I totally agree..I've have 3 chances to date porn stars and couldn't do it, but I can say I just hang with them and it's great no \textbf{sex}..not because we don't want to but we just don't cross that line..whats funny is I'm a Musician...now keep in mind they don't get jealous but they do get TIFFED😂❤️ and of \textbf{coarse} I bust on em cuz for every one girl that hits on me 12 guys or girls hit on them and they're my buds so my problem is not insecurity but feel ur just not enough which..so if was be with a porn star they would have to get out of porn, but could or would never do that cuz that's there thing and they would never ask me to quit music..as a matter of fact I wrote and recorded a song for each gave it to them promised to never perform them unless they it's ok so I love all three and they me and getting IN VOLVED would shit up..what hilarious is I have to call them down cuz they talk about fucking, cock, fisting what ever like talk about the weather or foot ball....😂😂😂😂❤️🎸🎼🎶🎶🎶\normalsize   & \cellcolor{green!27}Coarse, Sex & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/197 & \cellcolor{green!27}1.015 \\  \hline
  \cellcolor{green!5}\small To be honest tongue is more important than dick for most girls. Look at pornhub's statistics. Majority of \textbf{woman} watch \textbf{lesbian} porn because \textbf{lesbian} porn showcase A LOT of eating out pussies.\normalsize   & \cellcolor{green!5}Lesbian, Woman & \cellcolor{green!5}Gender - General, Sexual Identity - Female homosexuality & \cellcolor{green!5}3/32 & \cellcolor{green!5}9.375 \\  \hline
  \cellcolor{green!27}\small I never judge a person by his/her profession. Financial and other circumstances can compel a person to enter into 'low-dignity' professions. We should not blame any person for the circumstances which he/she does not control. And regarding what she said, I like when women express themselves freely. Let us not forget that even if she is \textbf{sex} worker, she is still a human being with emotions. Profession cannot erase that fact. I would never disrespect a \textbf{woman} who is a prostitute, because I have no right to say so when I don't feed her with my hard-earned money.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Harry Potter Do you know her personally? Have you seen her annual expenses? What if she has some ailing family member who needs expensive medical treatment? We all face difficulties in life at some or the other time, don't we? No person would want to be abused. Everyone feels pain in life and needs someone to love and care. So what if she fucked with several men for money and now she wants to date? When men fuck several women they earn the title of 'ladykiller' and when women do the same, they are called whores. What kind of justice is this? Don't forget she is a \textbf{woman} and women are far weaker than men. Hurting women is not a manly attribute. I have sympathy for her because she is a human being and if I had known her personally, I would have tried to help her. I would never leave a \textbf{woman} to die just because she is a \textbf{sex} worker.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/162 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Are you \textbf{dumb} or what. it was her personal choice. Look at her twitter, she does it cause she loves fucking around. And she has a husband now but still fucks around with men. She does it cause she is a fucking whore who deserves \textbf{nothing}, not because she is poor.\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small Harry Potter Maybe you are right and I am \textbf{dumb}. But tell me, which sane man/woman wants to live a life without dignity? And can you know everything about a person just by looking at a few posts on their twitter account? My friends post on their social networks as 'feeling happy' but in reality I know how sad and frustated they are after they chat with me privately. And \textbf{sex} is not everything in life. After a limit has crossed, you will get fed up with that too! Just because you like pizza doesn't mean that you won't get fed up of it after eating everyday. She needs a husband not just for his dick but for emotional and social comfort. If her husband grants her consent to continue porn, why should you object? If she likes getting fucked by several men as you say, why would she want to date? Clearly, \textbf{sex} and money are not everything in life. We have other necessities too.\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/166 & \cellcolor{green!5}1.807 \\  \hline
  \cellcolor{green!27}\small Dude i already see her hairy \textbf{pussy}..lol\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Nitish Bhardwaj  ew you bigotic \textbf{indian} stink armpit hahahaha\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small she makes it sound like its the men's issues when guys having problems dating her lol. Girl u gotta check reality and see that you are the \textbf{weird} one in any relationships.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small There's \textbf{nothing} sadder than someone who has, in a sense, lost all purpose for a healthy, free and normal life, but is so inveterately sold to the idea that she actually has all of those things, only a little different (and infinitely more complicated) from those of "civilians". Wonder what the fallout will be when one day, HOPEFULLY, some good sense mindfucks her.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small hocine632 well said man...this shows ua intellectual and uneducated mantality..osm... \textbf{nothing} more can be expected from guys like you...keep going ...keep it up..all the best\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small A man who would make a porn star or a prostitute their \textbf{woman} is not a man. He is .......\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small lol that whole 1st answer was hilarious.   \textbf{Nobody} is insecure or jealous bitch, you fuck other guys for a living, why would anyone date you?\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Kayden Kross was my ultimate \textbf{woman}... now I fucking adore Lana Roheds\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Sex releases chemicals in your brain, to reward centers that act as a form of communication. You're brain is telling you that you are happy, using these substances. It's like drugs. But guess what, just like drugs, if you continue and continue and continue to exploit these chemicals, the reward is no longer the same. You dilute the very feelings you are going through all this effort to achieve. Big Lebowski: 'she cannot love, in the traditional sense of the word.' If anything, feel sad for these people. They are missing the point of the act of \textbf{sexual} intercourse. But, to each their own.\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small As much as she has smooth skin and blue eyes and silky hair, she is disturbingly disgusting person (like all her coleagues that are not "civilians" and are in front of a camera, ' "heroicly taking shots", and not from a rifle but from camera' ).I wouldn't poke her with a stick, letalone 'date' someone like her.It is not a normal job. \textbf{Nobody} pays for your pension and healthcare. It's prostitute-on-camera job. And \textbf{nobody} cares if you get infected by HIV/herpes etc.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small A \textbf{woman} can adapt to any man's size. She will have an orgasm if she's into you. You caress her body and emotions.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I respect women that have \textbf{sex} just for pleasure rather than money. I would rather my GF fucked a hundred guys for pleasure rather than fucking 100 guys for money. Also pornstars fuck way more people than an average girl so that was a stupid comparison\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small This is all totally irrational and it sheds light on human biology. We men call women whores when we are all man sluts ourselves and would love to fuck hundreds of women. It's a biological difference. That's why we care more about \textbf{sexual} loyalty over emotional loyalty while the opposite is true for women.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small \@Sean Lee Exactly. No one understands that for some \textbf{dumb} reason. Can't believe that women and men are different\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small It's one thing to date a girl that's done porn and had \textbf{sex} with these massive cocks, and still make a relationship work with the knowledge, but how is anyone seriously going to want to date someone that's ACTIVELY doing so?  You're telling me after the equivalent of getting fist fucked on a regular basis and your now going to go screw some average bloke, where that \textbf{sex} won't be affectively negatively for BOTH of you?  Not even talking on a mental/insecure level... I mean physically. yeaaa....   IDK I could never date a girl in porn even if she specialized in regular dick guys porn only. Just the fact she does it makes me loose all attraction. Might fucker her, but DATE her? Hell no.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/125 & \cellcolor{green!27}1.6 \\  \hline
  \cellcolor{green!5}\small yea and now she just absolutely sealed the deal on not being able to date a "citizen" again by admitting to the fact that it's not just emotionless \textbf{sex} and but rather like a job by admitting the jealousy's when it's only between the people in the industry.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small A slut, No brains, \textbf{pussy} is Probably ripped apart.. I'll pass thanks!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small So a \textbf{woman} fucks alot of guys, she's. Nasty whores, but when a man does it he's a stud or player. Never quite understood the double standards on that but it is what it is I guess.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small The big guys dick wouldn't bug me.  It would be the conflict between \textbf{sex} and love!  How do I cut loyalty out of \textbf{sex} and still be able to make love to you (Or anyone else for that matter).  That just makes it difficult to love.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small I'd date her and try my best to hit that \textbf{pussy} right every night\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small ....yup...just went to see some of her videos... She gotta deep\&big twat....then I saw her with some sad coloreds.... The kind of patheticism that's ready to fight\&maybe even kill  over this \textbf{pussy}.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small this \textbf{chick} sucks n fucks like a champ, u sold ur soul u are not allowed to date or marry\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I get how emotionally, people would get jealous, but come on, your mate is an actual professional at \textbf{sex}.  Is that a bad thing?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I love how all these comments are like "slut, \textbf{hooker}" etc, meanwhile they fapping to her porn whilst typing lol\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The only people pornstars can date are other pornstars. I don't see a difference  between a \textbf{hooker} and a pornstar...they both fuck strangers for money.\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small You know... jealousy aside. Dating a \textbf{chick} who is in a constant state of "sloppy seconds"  would just be too much. She said EVERYDAY!\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I'd rather jerk off then have \textbf{sex} with a loose bitch\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It looks like these pornstars only wise up after the fact and are completely deluded on what \textbf{sex} is. Yikes\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Lol i don't believe any relationship with a pornstar actually works. Unless they are the type that likes open relationships. \textbf{Nobody} is that secure to be cool with that lol\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small You're a porn star who has \textbf{sex} for a living BUT you want ME to be tested ?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Bull shit. Theyre holes probably smell like thousands of male cum mixed together. If that is what you call clean, then you're \textbf{blind} af.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Since she would be jealous of a guy she would be dating in the biz having \textbf{sex} with other women on the job, perhaps she understands why a guy she would be dating would be jealous of other guys having \textbf{sex} with her on the job.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small sighs That a \textbf{woman} as obviously articulate, smart, beautiful and hot as Ms. Daniels can't get a date due to her job does not reflect well on the rest of humanity.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Why isn't polyamoury more \textbf{common} in the industry, or is it?\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She eats more \textbf{pussy} then cock\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I am from India and I know that Sunny Leone is doing great. Not that she is now in Bollywood. She used to be a pornstar and she fucked with other guys. But still she is having a great married life. It all depends on the girl as well as the boy. It helps Leone that she belongs to the same industry as her husband. Still if you see someone and love no matter with whom he or she had \textbf{sex} with, it will work. It is hard, but it can work and maybe it will take more time to adjust. Pornstars can be loyal life partners.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/107 & \cellcolor{green!5}0.935 \\  \hline
  \cellcolor{green!27}\small Um.  You say you'll get jealous of your colleagues fucking your industry boyfriend, but you want a relationship where someone is okay with you having \textbf{sex} for money?  Okay.  Sorry, but this is... I'm going to watch another video now.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small I am actually really surprised by all the negative comments. Given, I don't think porn is a respectable industry but this \textbf{woman} doesn't seem like an idiot or a bad person.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small This is lame\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Asking her to have \textbf{sex} with you for \$100 would make her a \textbf{hooker} and thats unrespectable work...asking her to have \textbf{sex} with a friend while you record it for \$100 now thats respectable work.....pornstar logic\normalsize   & \cellcolor{green!5}Hooker, Sex & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Dani Daniels who? Who the fuck is this bitch? \textbf{Lame} brain duck.\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Does this stupido know to do anything or to talk about anything that is not reletad to \textbf{sexual} intercourse?\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Sorry but this girl is just okay looking. Not a real beauty like the \textbf{old} school stars like Nikki Dial,Celeste,or Raquel Darrian.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I'm going to \textbf{buck} the trend and say that she seems lovely. And I lean Right Wing.\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small The men in these comments talking trash act like they are soooo pure. So you guys are uptight prudes who don't have \textbf{sex} at all. So, you're here looking at porn but you hate female porn stars specifically?? Makes no sense....🤔🤔\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Just yuck - who would date a \textbf{hooker}?\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Unusual that everybody in the comments and the interviewer and interviewee equate dating with \textbf{sex}. I suppose that from a porn star viewpoint it is much less of an intimate act than a "civilian" viewpoint. Obviously everybody is an individual with their own level and I guess from her comments that having coitus is more intimate  than a "civilian" shaking hands with another "civilian"  but less than a "civilian" having coitus with another "civilian" . But what would be the equivalent act? A hug? A French kiss?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small I like how everybody here trash her out of orbit while you people are the ones who jack the fuck off to them.It's like complaining about how \textbf{Apple} run its business  while listening to music from an iPod and texting your iPhone while you buy an iPad at their store. In five minutes all of you will be masturbating at some website lusting over these women. At lest they don't trash the low lives behind computer screens. Somehow, their ethics are far superior for at least they respect the audience. You dipshits can't do that back.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small I can't imagine why anyone would get insecure over you having \textbf{sex} with other men for money.  I mean what a jerk.  Western women are making it really hard to argue against sharia law at this point. 😟\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Your a porn star what you expect? That \textbf{pussy} torn apart\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small +Lazy StasyIt is a war. A war of ideas, a war of beliefs, and war on a spiritual level whereby their job is to make as many people as perverted as possible. Porn destroys a person on a physical, \textbf{mental} and spiritual level, and it also activates one of the most addicting chemicals in our bodies that makes it so difficult to let go of it—causing you to stay stuck in an endless loop of a chemical high and feeling drained.One can have \textbf{sex} all one wants as long as it is based on love (an intimate relationship where your partner means much more to you than just \textbf{sex}) and it will never leave you feel drained or cause problems because it is not an addiction at that point, one can stop anytime one wants to—that is the difference between detached \textbf{sex} and \textbf{sex} based on love.Her problems is that she just wants someone to have a family with, she couldn't care less about love as she is getting enough "love" at work.\normalsize   & \cellcolor{green!27}Mental, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/176 & \cellcolor{green!27}2.841 \\  \hline
  \cellcolor{green!5}\small Lazy Stasy I think civilian is a \textbf{common} word all pornstars use to describe people not in the porn industry, but I'm not sure\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I can't stop laughing at this \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small It's a hypocritical lifestyle.  That's why people will tell you don't do porn.  It's sinful (not by gods terms but by normal human morals) for a reason.  There's the regret.  You won't find a partner who will ever be ok with it.  Later in life that shit will come back to haunt you especially if you have kids who grow up to find out.  And I'm sure there's a ton of psychological effects to deal with.   Porn stars probably need a lot of freaky shit just to get off else they probably don't get excited anymore.  It's just a \textbf{dumb} lifestyle choice.  \textbf{Sex} is a craving.  It'll only make you happy in the instant gratification/short term department.  I think the industry should use preexisting couples and edit the role play how they like rather than mixing and matching pornstars to other "professional strangers".\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/143 & \cellcolor{green!5}1.399 \\  \hline
  \cellcolor{green!27}\small Im sure her Grand parents are so proud of her. When she 2 years \textbf{old} sitting on grandpas knee she looked up at him and said I want to take 2 big dicks in my ass in have 50 guys jerk off on me. Fuck being a mommy or nurse or doctor. No shes a reprobate minded prostitute.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small It's interesting how they've renamed "prostitute" "pornstar." Get paid to perform \textbf{sexual} acts? Yep, that's the oldest profession in the world... o.0\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@pickle tarts Jonny Sins is not a female pornstar. Male pornstar is more acceptable having lots of \textbf{sex} is more acceptable for men rather than women in a biological standpoint (for example males are more dominant and they don't like \textbf{promiscuous} women, while women are relatively submissive)\normalsize   & \cellcolor{green!27}Promiscuous, Sex & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Of course, you're a \textbf{hooker}, but just on camera.\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small At the end of the day... shes a trash. \textbf{Nothing} else.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Chest of a 5 year \textbf{old} boy\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I have every right to judge her. If you haven't noticed 9/10 of the comments think she is a bad person for being in this profession, meaning most people would not want to be with a pornstar/have any form of relationship. And it was not enlightening at all. We already knew what pornstars lives are like: just disposable \textbf{sexual} objects that have no value. Also everyone has a right to have their own opinion. If you can't handle it, well too bad\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small DNA Tru Lyricist I like you.  Was about to type the exact same thing, even though I'm not a big fan of \textbf{sex} before marriage.  I respect her choice and she seemed relatively smart.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Sad...you will never be a porn star and have a normal life because you take the miracle and magic out of having a \textbf{sexual} relationship made to create life with another person you love and you've turned it into something meaningless. Very very sad.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small and thats why \textbf{Sex} is a sin from God it will make ur life miserable\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Wow!...What a waste of some beautiful \textbf{pussy}!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small her mouth is as dirty as her well used \textbf{pussy}, what a brain dead scamp\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small i bet all u of u guys if she showed up at your door step u can't refuse i know i would hit dat ass. unless y'all are fucking \textbf{g\textbf{ay}}.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Well she is a prostitute..end of story she gets paid for having sex\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small At the end of the day she's a pretty thing to look at but would you ever want this \textbf{woman} to be the mother of your children? lol.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small That's because you're dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Omkar Samanta I'm scrolling right now man. Damn. I honestly feel like Bill Gates compared to Dani, \textbf{nothing} against her it's jus like wtf man. Is this the conversation I would have everyday SMH. So hard not to judge people. Lord give me strength\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small It's \textbf{crazy} how that can happen\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Its not human anymore. Its whore,  \textbf{nothing} more\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small she looks sorrow, can i be your angel, hey \textbf{R\textbf{ed}} shirt\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small This is kind of personal XD  You know I call  myself Dan, which is a fucking good thing, because I would get upset that people would turn it into a girl term.  Daniel...  If you say it wrong gets very girly.  I do not want to brag but I can safely say that no girl has my DNA to this day...  Oh shit just as I type this, I just realized that DNA flipped a little bit = DAN.  And once I know the science of \textbf{sex}, it really is not a good idea to have that with a girl who has had some other guys DNA in her...  YOUR ABSORBING THEIR DNA you idiot!  A guy like me, I want the purest more un-tempered sample, for the best results, highest quality.  Because porn stars have male DNA in them, so they will behave like a male with a female body....  So yeah you have changed your chemistry, you changed your persona, you prevented yourself from being treated in a gentle manner.  Ya know what I mean?  You can no longer just be a girl, you sort of have to be a man.That is what happens when you start accepting a man's cash, you are not dealing like a man, you literally internally become a man.  Yeah....I do have that hypothesis is that you can overcome your past mistakes, with a little female vitality.  You have to slowly treat the male hormones growing every day, you got to slowly get that shit taken out of your system.  Basically you should be dealing with a doctor that can restore your original self.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/273 & \cellcolor{green!27}0.366 \\  \hline
  \cellcolor{green!5}\small Her 'holes' are the last 3 of 99 problems this \textbf{psycho} would pose.\normalsize   & \cellcolor{green!5}Psycho & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Begone THOT\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small It's the same with male pornstars as well. All women are insecure in their relationships - and a guy having \textbf{sex} with gorgeous women everyday. One of the cornerstones of a relationship is exclusivity.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small The intimate art of making love or having \textbf{sex} (even for porn) turned into a vile wretched mechanism by a stupid \textbf{woman}. She'll wake up one day and it won't be funny. Sadly she'll be left feeling worthless and soulless and probably commit suicide or OD! Terribly sad.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small could never fall in love with a porn star.. what kind of man is ok with his \textbf{woman} being fucked everyday?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Why does she even NEED a boyfriend? She has all the greatest \textbf{sex} she could ever want, and it's not like those actors in the porn business are able to fall in love anyway. What a disingenuous question. And she's using it for pity, as in "poor me, I can't get a boyfriend, sob, sob". What crap!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small your \textbf{pussy} must be so lose you can drive a truck in there\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Well, more than one ex of mine turned out to be lying dirty whores, so I assume that as long as you know what you're getting yourself into up front, it stands a chance of working with a "civilian" who is comfortable with the arrangement. It's my own fault for dating strippers and bartenders, so I'm not blaming the women, I made the choice and take responsibility for having those standards. I've known a dude who dated a professional courtesan and they're both very happy. Personally, I wouldn't mind trying to date a \textbf{woman} in this profession depending on the \textbf{woman}, of course...but the cocaine habit would have to go and so would the beatings. If, for instance I saw her being physically abused I would go apeshit and that's not cool. Lots of "porn" today is rather stark and disgusting, anyway. Thus, I might as well be comfortable not even trying since it's most likely a DOOMED prospect to begin with.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/162 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Yes, and there's \textbf{nothing} wrong with prostitution.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small There is everything wrong with prostitution, it's selling your body for market, objectifying it, you're not human anymore you're just a \textbf{sex} object, as much as a slave is a work object, doesn't matter if you chose it or not, still you're not a human in these interactions because your life is reduced to shitty monetized interactions which is why there are a lot of suicides, drugs and \textbf{alcohol} in this industry.\normalsize   & \cellcolor{green!27}Sex, alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol, Gender - General & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Well I'm male also, the name you see is mine, no frills, however at 72 I'm a bit beyond making you an offer you can't refuse. My daughter calls me a 'dirty \textbf{old} man' if I even look at, or comment about any of her female friends. She is 30 years younger than me and some of them I wouldn't mind at all, it has caused more than 1 or 2 rows.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small Old or traditional practices that are viewed as \textbf{common} does not make them right. Murder, killing and wars are also long term problems for humans on a worldwide basis, but it does not make it right.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Because you have \textbf{sex} for money you are not human? :D Really? What about people who kill other people for money? Or people who say things for money! People do everything for money! Money is the main driving force behind anything! Almost every relationship is based on money! There isn't a thing that can't be bought and there isn't a thing you can't sell!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small There are institutional things wrong with why people do it in the modern world at times, but there is \textbf{nothing} inherently wrong with putting a price on \textbf{sex}. seriously, get off your high horse. you pay for lots of things and the fact you think it dehumanises the other person, just because its \textbf{sex}, says a lot more about you than a person taking money for it.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/67 & \cellcolor{green!27}4.478 \\  \hline
  \cellcolor{green!5}\small i disagree mang. someone who pays for \textbf{sex} related thing once is definitely doing a wrong thing because he keeps the toxic industry going on. someone who gets money for it does it a lot though and is a living part of that industry\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small No way! Every human has a price! Offer a man a certain amount of money and he will do the things asked, especially simple things, like bring me this or never talk to him or leave him or say this and so on, even beat someone up or outright humiliate or be humiliated! Even leave their wives and so on! Look at the money prank videos on youtube for example i have no clue how real they are cuz i have only heard of them but i heard that the prankster offered a guy money for his girlfriend and he took it in 2mins and the girlfriend even understood his decision! Money is the most important thing in life, without today you have \textbf{nothing}, no girl will love you if you are poor af and no friend will take you as you are poor and an embarrassment! They might talk to you if you meat alone but that's it! No such thing as morals and ethics when it comes to getting what you need to survive! Obviously not including killing for money! but even that happens! Everybody can be bought anytime any place! Except those who already have enough money! But 70 will always want more!  I hope you can read that shit and understand what i am saying!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/219 & \cellcolor{green!27}0.457 \\  \hline
  \cellcolor{green!5}\small In Youtube world you can believe anything. 'Everybody can be bought anytime any place!' - if you believe this then it exposes your ignorance and poor education.People have been imprisoned for keeping integrity to a cause - ie. refusal to join the military. Even recently, a French police officer offered himself as a hostage in exchange for a \textbf{woman} who was being used as a human shield by 'terrorists'  who had already killed a number of people. The officer was later murdered by the 'terrorist' who himself ended up being shot.That is integrity beyond the temptation of money or financial gain - considering someone else's life as more valuable than one's own.Your inability to conceive of people that have true moral and ethical boundaries - ie. values that you yourself do not have, show how weak you are.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}\small antoine FFS another sjw who thinks sluts are victims ...you are not selling your body you are selling a service it's the same as a masseur and if people want to do that they should have every right to do so  without some \textbf{sex} starved granny victimising everyone\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Morons here seen to think men hurt women when they fucke them for money lol...jus shows how pathetically men think about themselves lol..I am going to see a \textbf{hooker} next week\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Christopher Lovelock Fucked up world.People and their needs.Need food, need cars, need entertainment, need \textbf{sex}.. all these needs causing so much pain.. Wonder why things could not be different, in a better way, than it is right now...Some suffers, so that others could satisfy their needs..\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small \@sleepingstate1978, ofc, the second you are selling your body (arms, brain or \textbf{sex}), you lose some humanity, you chosify yourself because you're producing for a market and not for human needs anymore. \textbf{Nothing} wrong with this statement.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small she bitches about how she gets jealous if her partner has \textbf{sex} with performers (if they date) then complains about "civilians" getting jealous.....hypocrite much...\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small nobody want to be with a slut\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I've posted on anotherYOUTUBE sitethe reason so many beautiful young women go into porn is because the \textbf{old} whores of HOLLYWOOD won't step asideand retiremany women in porn are drugged up against their will or without thier knowledge so they can and will perform extremely graphic \textbf{sex} scenesSASHA GREY was once quoted as saying" to do my 1st gang bang sceneI was so drugged out onEcstasy and GHB that I don't even remember it "most white women don't want to do interracial \textbf{sex} scenes and are forced or drugged into doing so1 \textbf{woman} that left the PORN INDUSTRYsaid" I was fine with boy girl \textbf{sex} and girl girl \textbf{sex} but they wanted gang bang and interracial and when I said `NO´ they blackballed from the industry and sent a fake medical report saying that I had AIDS , I sued them and they settled for an undisclosed amount "SO YOU SEE EVERYONE TRASH TALKING PORNSTARSIT'S A CUTTHROAT MONEY MAKING BUSINESS\normalsize   & \cellcolor{green!27}Old, Sex, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}6/174 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small This \textbf{dumb} bitch is \textbf{nothing} more than a whore, plain \& simple. Any man that screws her deserves to have his dick fall off.\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small No such thing as a porn star they are \textbf{sex} slaves !\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Oh my God such beautiful \textbf{woman} has fallen into Devil's trap. I wonder what make her to choose this infamous  highway to hell and everlasting death. But there is still a chance if she choose life, she may come to Lord Jesus Christ and believe in Him and He will give her new life.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small I want to have hot \textbf{sex} with Daniels I'm super HOT man great dick to me and her would burn the bed\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small THERE \textbf{CRAZY} WHORES....THERE INTO THAT DICK AND MONEY.....LOL\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small how does a \textbf{woman} become such a \textbf{sex} addict like that i think its the colour green on paper  💵\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Sex for most \textbf{woman} is 75 in the mind.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Dumb interview and her view of life is pathetic\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Dumb and Ugly \textbf{common} as cat shit, whats not to like lolol\normalsize   & \cellcolor{green!5}Common, Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Having \textbf{Sex} to get off is one thing, Having \textbf{sex} with someone you love is way better. \textbf{Sex} doesn't make you happy.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/22 & \cellcolor{green!27}13.636 \\  \hline
  \cellcolor{green!5}\small Very nice and smiley,  but i bet she has to coke up before "work " and that she really hates men.  she'll be a worn out \textbf{junkie} in a couple of years if she doesn't get her act together..\normalsize   & \cellcolor{green!5}Junkie & \cellcolor{green!5}Behavioural Addiction - Drugs & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Wow this bitch is \textbf{dumb} af.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Who would date a porn star? Like she said, she rides a lot of dick. Basically a glorified prostitute; too \textbf{dumb} to do anything else for a living.I think it's funny that some of them are actually married and have children. One day when little Timmy is cruising the internet for porn, he's going to find mommy taking two dicks.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small The way I see it, there is \textbf{nothing} morally wrong with being a pornstar. The people who will have problem with it, are usually some religious folks, because Jesus!Other than that, she cant really complain about dating being hard. I mean, most men will have problem with their girlfriend being fucked by dudes with huge dicks all the time. I mean, how can she even complain about the fact most men dont get  it?? Feels like she thinks dating, is just another \textbf{sex} partner.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/85 & \cellcolor{green!27}2.353 \\  \hline
  \cellcolor{green!5}\small so when the wrinkles set in and work dries up you'll end up a lonely \textbf{old} pornstar whose had had more pricks than a second hand dart board..... still I suppose your dildo won't get "jealous".....there again it won't buy you drinks either.....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small She a dirty stupid whore that's why she has \textbf{sex} for money she isn't good at anything but being a whore 😂\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I am another one who doesn't have a clue how this subject ended up on my YT timeline.It's late at night, \textbf{nothing} better to do, I DON'T watch porn, \textbf{nothing} close but the current SouthWest Airlines incident, but I DID watch this ladies interview.Behind the language and scenario, I saw a beautiful women who is truly hurt by not having a normal relationship.  I am glad she explained the reasons as I had no idea of any of it being a factor.  I kinda felt sorry for her as she is in a trap with little or no access.  Does she want to have kids and a family?I was around when Linda Lovelace became a household name.  Somehow she managed to get out and have a family life, but many managed to track her down trying to bring her back to her past.  I didn't work.I don't know who you are, but I truly wish you the best.  In some cases, size does not matter.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/169 & \cellcolor{green!5}1.183 \\  \hline
  \cellcolor{green!27}\small What guy or \textbf{woman} in their right mind date a porn star are you fucking kidding me really\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Haha this \textbf{chick} for reals???\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Why would you date a girl that has unprotected \textbf{sex} every day with random dudes?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small How in the hell do you take your job seriously when you make your living sucking and fucking?  This \textbf{woman} is so fucked up she has no clue how she sounds.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Piece of broken humanity.  Pitiful.  Oh, and \textbf{dumb} as a bag of hammers.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} think she is doing something normal and she do actually believe it , the funny part is there are some fools and morons who actually debate the normality of her (so called career) , all right \textbf{nobody} but a hardcore super cool pimp or a hardcore filthy whore would actually be fine with a \textbf{woman} fucking with guys and sucking cooks on daily basis for money , it is simple as that , these two types of people will absolutely defend her and start rambling shit about free will and modern societies and progressive thinking .\normalsize   & \cellcolor{green!5}Nobody, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/98 & \cellcolor{green!5}3.061 \\  \hline
  \cellcolor{green!27}\small Getting paid to have \textbf{sex}....  and still not satisfied.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I bet you would love her and marry her huh? Waking up everyday to see your wifes new porn movie. 1 whole hour of her getting raw dogged by some dude. That's your fantasy. We're judging her because she's a \textbf{dumb} selfish hoe. She claims men are insecure when in reality it's just that they have dignity. She want men that want to be monogamous while she goes have \textbf{sex} with anyone given to her? Also she's a legal \textbf{hooker}. If you wouldn't marry a normal \textbf{hooker} why would you marry a more well known \textbf{hooker}?\normalsize   & \cellcolor{green!5}Dumb, Hooker, Sex & \cellcolor{green!5}Gender - Female sexuality, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/96 & \cellcolor{green!5}5.208 \\  \hline
  \cellcolor{green!27}\small Dhrubajyoti Ray ah. Well if she is married and it's illegal to have \textbf{sex} with different partners then it's a no then. But if it's not illegal, then it's fine.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Slut is a slut man. There is \textbf{nothing} to judge.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small nobody isn't perfect this bitch is disgusting whore\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small someone667 She didn't label men as insecure, you are the one who misinterpreted her words.She knows that feeling insecure in a situation like this is normal and to be expected, she herself even admits she gets jealous. But even knowing this, it's still frustrating.As for the relationship bit, yes, most people wouldn't want to date someone who's having \textbf{sex} with so many people, I know I wouldn't. But she knows this, she isn't expecting me or you to date her, she just hopes to find someone who doesn't mind her work.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small Having a relationship with a pornstar is impossible to last. Pornstars can only do it for work or pleasure.Work: If a pornstar doesn't enjoy her work then \textbf{sex} with a boyfriend can not be anything more special.Pleasure: If a pornstar does enjoy her work then \textbf{sex} with a boyfriend is \textbf{nothing} special.Surely pornstars do it for money, pleasure and power. If not, then this job is impossible to perform because you would be overwhelmed by guilt all day long.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/82 & \cellcolor{green!27}3.659 \\  \hline
  \cellcolor{green!5}\small So why is this \textbf{hooker} being interviewed?\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Fame? Please people only know her as a \textbf{sexual} object who only serves the purpose of getting rid of an itch. I bet most people don't even know her name.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@JohnnythefirstWhen I used to watch porn, I always used to think pornstars were \textbf{sexual} objects, not someone that you can talk with like your friends or someone you look up, like your parents. They only served to get rid of an itch, and that is the only thing pornstars show the world when they do porn: \textbf{sexual} objects to get you off. I (and I am pretty sure many others) don't usually think that \textbf{sexual} objects like pornstars are better than a normal civilian. Civilians have self-respect and dignity. Pornstars don't. That is the impression they give to the world, so really they either have to stay a pornstar and deal with it or just leave this useless profession.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/120 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Oh right because you need to see porn to jack off? Look up the negative impacts of porn. Masturbation is natural, porn is not. People are not supposed to see other people fucking to jack off, that's not how nature works. And please if the porn industry shut down, I'm pretty sure most people would still be able to jack off without watching porn. And no getting fucked is not tough work you fuck. \textbf{Sex} is supposed to be pleasurable, not something you get tired of. These whores only do it for money or pleasure so you are incorrect. As for your last argument, I have a girlfriend, so I don't need to watch porn to jack off. Now go fuck your grandma so you don't die a virgin.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/129 & \cellcolor{green!27}0.775 \\  \hline
  \cellcolor{green!5}\small Why be with a pornstar like they record \textbf{sex} that they have with other men that aren't you and that must really suck\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Also 'being successful at her job' how is having \textbf{sex} on the daily hard\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Why I am the only one who finds her sweet and romantic?? I believe \textbf{sex} makes a huge difference if it is done without feelings, compared having \textbf{sex} when you are in love. And that's not the only part obviously but what comes with it. Caring for the other is what makes a good couple. I would feel bad if she had cheated on me because she wouldn't love me anymore. And by cheating I mean the guy she would have fucked must be a man he had deep feelings for. Obviously, as she admits finding a guy without that kind of Ego is hard to find I guess...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/109 & \cellcolor{green!5}1.835 \\  \hline
  \cellcolor{green!27}\small You chose to be a porn star and the guy is supposed to be ok with the love of his life being a porn star. It's like him asking you to be ok with him cheating or him being able to have \textbf{sex} with any other \textbf{woman}.What did you expect when you decided when you chose to be a porn star? Wait...oh...it's ok for you to impose expectations because you're a \textbf{woman}. Yup! That good ole double standard you can fall back on.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/84 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small And here I am, a 41 year-old virgin man, saving myself for the one \textbf{woman} who will never come (no pun intended). :(\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small George The guitar kid  Your comment is the most \textbf{dumb} comment I ever read; she is not a prostitute? Women who \textbf{sex} with multiple men and sell her body for money she is not a prostitute? And research? You need to research this kind of things? Who define the term pornstar? You call her by any title but she is a hoe a prostitute .\normalsize   & \cellcolor{green!27}Dumb, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small Bro she makes it sound as if normal people are lower than her. Proves how retarded pornstars are. Can't even distinguish intelligent/modern/respectful people from cum filled \textbf{sex} objects.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Dominus Providebit  Your turned-off, because she doesn't shave? I'm sorry that you like your women to look like a pre-teen down there. That's where that obsession comes from. I bet you're a blue \textbf{dot}.\normalsize   & \cellcolor{green!27}Dot & \cellcolor{green!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small If I'm honest, I guess insecurity would be part of it...but it's much more about just being grossed out; I don't want to be with a high-std-risk \textbf{woman}.  Why in hell would I.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Love her \textbf{Lesbian} ass licking scenes, she really loves doing it to girls.\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Looks like she's actually a pretty cool chick\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small And you are a moron.   Hypocrites tend not to be accepted by other people too well, and she contradicted herself hard in this interview.  She thinks men are insecure for not accepting her 'career' choice and being ok with her screwing a new guy every day, yet she doesn't like to date fellow pornstars because it bothers her that they screw new chicks every day.   She is \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small She's a Prostitute! ROFL She has \textbf{sex} for money! She's the trash of society.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I can tell that she is sad, depressed and insecure. She does not even seem to enjoy \textbf{sex}. She sold her body for this so called "job". She's an empty soul. What she has is no more than basic dopamine addict!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Difference is, you probably aren't using tinder to find a meaningful relationship... this \textbf{chick} expects men to be fine with her screwing a new guy every day while wanting to be in a long term relationship.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small She will always have some sad masochistic \textbf{beta male} to fall back on, for every \textbf{woman} like this there are 5 beta males lined up to house her, spoil her, let her fuck other men etc.\normalsize   & \cellcolor{green!27}Beta male, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Typical \textbf{ho} talk\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Lol porn stars are just always \textbf{dumb} and get get a job with skills so they gotta do shit like this to make money, lord save us all\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Listen to her laugh, 90 of Pornstars are Narc's, lacking any empathy what so ever.  Their jeolousy is not about other's feelings, it's only about them and \textbf{nobody} else.  For instance, this \textbf{chick} though looks like a Nun, is a prime example of the monster's out there that have no concept of how others feel.  What a strange life.........\normalsize   & \cellcolor{green!5}Chick, Nobody & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small Eww you have 0 fucking tits She's cute but no.   I only like \textbf{chubby} girls\normalsize   & \cellcolor{green!27}Chubby & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small the only issue is (with the following statement)............... "huge penises feels good" is that women have muscles down there. It sure is easy for them to give up and let the buffet come to them and choose to not provide any help down there, but its not something porn stars know. They can please a man by being less ignorant! Not by having more experience... A fact that all those pornstars would never teach young women. In a relationship, its not about what one does, but what they do both. If you have an equivalent amount of efforts, time spent for the other, money invested, thoughts (romance)... whilst both of the partners being two independant individuals... You get the most stable power couple there is. My parents are like that and Ive found countless women that I had to turn down despite having all the qualities, tact and... hum hum... talent to be that person. The majority of men and women I meet though... are ignorants in all the departments. The worst are easy to identify: provided for, narcissistic, more often than not theological bandwagon borderline \textbf{crazy} numbnuts, materialistic, superficial... list goes on and on. Men are less ignorant of matter, but women are SO \textbf{DUmb} because of how desperate men are. Whatever... this subject is ridiculous. Most certainly just because this is an improper introduction. Its easy to accept what a person does, but whenshe neglects the part where people respect themselves.............. (dont bs yourself by telling others that you respect yourself even though you do porn. You lost to the scale of the society so just admit THAT). Sure you can wish to be respected otherwise, but same goes for certain opinions. She doesn`t know what kind \textbf{sex} is. Lets not even talk about romance. She wouldnt even perceive it for how much money she gets out of that (not a whole lot either... but then the "needs" that they have for being used to having money is beyond ludicrous)..\normalsize   & \cellcolor{green!5}Crazy, Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/333 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small Let me add this. If she loves someone, she should find another job and adapt. Sure, it may seem like the ultimate sacrifice, but if you prefer getting pounded by everyone then there is no intimacy. Forget it. You must have same definitions in order to have a similar idea of the relationship... And if its something she loves doing and the guy brings it up as a solution that goes against what she enjoys: WELL WHAT THE HELL DID YOU EXPECT? LMAO. All and everything is linked... why do you think people cheat? They're not satisfied and they use the easiest way out... why not spoil ourselves with an opportunity that doesnt come twice (for men). Its much harder for a man to get some attention from the right women. For a \textbf{woman} in her prime (\textbf{sexual} peak: \textbf{age} and appearance-wise) its all offered. Respecting yourself means to choose your partners and learn from your mistakes. If your answer to that is: go in the \textbf{sex} industry because you have that prime given to you, but pour money on your looks enlessly... you're bound to never understand the reality that relationships are worth something and normal people Build them through time. You cant expect someone to trust you upfront and being asked to get tested is Not normal. Its criminal to give a disease to someone. Hello??? Criminal. If he knew and is brought to court on suspicion. He goes to jail! HELLO? Not the other way around. You cant ask it nicely if youre forced to ask it LMAO.Sure it can be a hassle to ask for that upfront as you create an inequity. If you offer to provide it, too... Then that settles it. Dont just require it like the p0rntard you are.\normalsize   & \cellcolor{green!27}Age, Sex, Sexual, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}4/297 & \cellcolor{green!27}1.347 \\  \hline
  \cellcolor{green!5}\small can't turn a \textbf{ho} into a housewife\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small You can't control emotions. She isn't doing it on purpose. But as she explains it isn't necessarily the having \textbf{sex} part she has a problem with but the fact that her boyfriend has had \textbf{sex} with all her friends. People who she knows.Also I don't think she requires her boyfriend to not be jealous, I think she just wants that jealousy to not taint the relationship. Obviously it will never work, and in order to have a relationship she has to quit the industry, but the intent is not bad in itself.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small Typical Western \textbf{woman}, she wants her cake and eat it too.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Her cunt must stink like a festering, rotting pile of scabrous, pus ridden, vile 6 month \textbf{old} corpses left out in the sun.  What a fucking slut. Mommy and daddy must be so proud.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Begone CUCK\normalsize   & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Tbh i think \textbf{old} ppl are more respectful as they have more experience. These are low cortisol pre-teens to young adults, and man-childs, who judge a girl for having slept with a 100+ guys but wouldn't blink twice if they had the same chance. I mean, if this girl has a job.. who is watching her? There must be a demand : ... :) Doesn't make sense to judge if you enjoy it, just shows how conflictuous these ppl are about sexuality.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small What a nasty ho\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small And I mean it in a good way... she is a gorgeous \textbf{ho}!\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Awwwww shes upset that she cant date like a normal person. Maybe she shouldnt be a PORNSTAR. What does she expect??????? Does she really think a man is not going to care that shes a pornstar?????. What normal man on earth is going to be ok with there \textbf{woman} getting fucked by men with huge dicks??? You cant be a pornstar and expect to have a normal dating life. If she wants to date then she needs to retire. Even then, most men wont be ok with dating a \textbf{woman} thats fucked hundreds of men (LITERALLY) not only that, EVERY MAN that shes fucked will mostly likely have been bigger than the man she will date. I dont care what she says, no normal/average sized dick is going to compare to the big dicks shes accustomed to having.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/138 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small I think she's FINE!!! and she has a hairy \textbf{pussy} too, that's sexy!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Sorry \textbf{hun},  let me tell you what real men think of "if to date a porn star"   THEY WOULD NEVER DATE A PORN STAR\normalsize   & \cellcolor{green!5}Hun & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small What god damn goals are they talking about? I dated 2 girls before they became pornstars and they are so desperate to escort to keep up with their plastic surgery's. There is \textbf{zero} finical security in that industry. The only thing they can do is land a \textbf{dumb} guy with money.\normalsize   & \cellcolor{green!27}Dumb, Zero & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small Would you date a prostitute? if the answer is no, then there you have it. Same thing with a pornstar, they're the same as a prostitute, get paid to fuck, the only difference is the camera. Why would any dude with a \textbf{common} sense want to go through that.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Man, This young video prostitutes \textbf{mental} illness has helped convince herself that what she does is normal and a "job".  LOL\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Pretty girl, \textbf{dumb} as a post.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small It's funny how she leaves out the main reason men wouldn't want to be in a relationship with a porn star, because the obviously reason man or \textbf{woman} they wouldn't is because people don't want to be with a whore... Like ...lolThere's lots of people with big dicks who just don't want to be committed with a whore it's that simple and everyone knows it. Stop making it this "victimhood cultre" bullshit.Both men and women can be whores people it's ok, just date amongst yourselves\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small YOU KNOW I WAS GOING TO CALL YOU THIS AND THAT BUT NO I WILL NOT BECAUSE I HAVE SLEPT WITH ALOT OF WOMEN AND I STILL CAN BUT I STOPPED DOING THAT AWHILE BACK BUT ON THE SERIOUS SIDE OF THINGS YIU REALLY NEED TO TAKE A DEEP LOOK AT YOURSELF JUST THING ABOUT WHEN YOU GROW \textbf{OLD} IF YOU ARE BLESSED TO LIVE TO BE WHATS GOING TO BE PLAYING DEEP IN YOUR MIND AND WHAT WILL YOU SAY WHEN YOU STAND BEFORE GOD ON JUDGEMENT DAY.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small So this \textbf{chick} is bothered if a boyfriend gets jealous yet she admits that she gets jealous when dating other porn stars.  She isn't paid to think, and it shows.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small So people SHE dates have to be tested when she's the slut?  Unreal.  \textbf{Sex} belongs between a man and a \textbf{woman} who are married.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Can someone explain the difference between \textbf{hooker} and pornstar? You're getting paid to fuck...\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Its funny how the media would have you believe that a porn star, is not a prostitute but something better. BY DEFINITION A PROSTITUTE IS A PERSON THAT GETS PAID TO HAVE \textbf{SEX} WITH SOMEONE ELSE, ITS NOT JUST A JOB, IT IS A LIFE CHOSE. F--K THIS CUNT FOR SALE AND HER DATING PROBLEMS. This is just plane silly and sad at the same time. THE END.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small If you're a porn star, dating could be hazardous to your \textbf{sex} life.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I'm a civilian. Always have been and always will be. What will you be when you can no longer do porn and no one wants you any more? When you hit 40 and your tits and ass start sagging,  all your orifices are stretched to the max and you have to wear nappies for the rest of your life because your rectum is too big to keep all the shit in? You'll be less than a civilian, you'll be a washed-up, has-been insignificant \textbf{nobody}.Civilian my ass.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small She's got an \textbf{old} lady mouth and a sharp nose...not very attractive.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Dani Daniels. You are not worth it. And stupid as fuck if you believe that what you're doing isn't cheating because it's your job but when he does it is. You are having \textbf{sex} with dudes for a living, it is only fair you accept he has \textbf{sex} with anyone he pleases too.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small She contradicted her self, I can see why shes in porn, \textbf{dumb} as a rock.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small sex sell well don't they?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Zehrudin Hasanovic education =/= intellect. If you were smart, you'd not be glibly commenting on other people's \textbf{mental} faculties.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I remember dating her in high school. Damn she could suck a \textbf{nigga} dick dry\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I love how she describes her work like she's a movie actress. "Someone on set told me something funny the other day." You're a fucking whore. No pun intended. Don't try to hide the fact that you literally have \textbf{sex} with someone while people are filming you. This \textbf{woman} has no shame.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Civopop11 Because she'll have \textbf{sex}? Why are you so worried about what your child will do in the bedroom? You sound creepy..\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Civopop11 It's kinda \textbf{weird} to say you'd never want a daughter because of some random pornstar you'll never meet apparently is a reflection of all women ever. I hope you don't have a daughter either, you'll be one of those controlling, stalkerish dads obsessed with her virginity.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Sex is great but keep them away from pop culture in this century. try to raise them on \textbf{nothing} but 80s cartoons until they are 12 or so, do not let them watch now days television, then at 13 raise em on the 90s before the USA got all fucked up along with parts of Europe. or just move away from major cities and build a cabin on some land in the woods.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small Esperanza Robertson We better pray to the gods too because I don't think if he ever gives birth to a daughter he will treat her like a father. He wants to have \textbf{sex} with a \textbf{woman} to give birth to a child but won't let his daughter have \textbf{sex} with whom she desires. As if girls do not have genitals and \textbf{sexual} desires!\normalsize   & \cellcolor{green!5}Sex, Sexual, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/63 & \cellcolor{green!5}6.349 \\  \hline
  \cellcolor{green!27}\small Esperanza Robertson there is \textbf{nothing} wrong to have a dad that cares about you and doesnt want his doughter to have a baby at 14. You sound like a single mom with 2 kids.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Dude, there's a dick in basically every porn movie, so lots of guys become porn stars. Also, if I had a child, I would raise it to become a kind and intelligent adult, while giving it as many possibilities to reach for its dreams as I can. If it's a girl and it turns out that she became a porn star (chances are next to \textbf{zero}), that would suck. She'd still be my daughter though. Not wanting a female child because there's a one in a million chance she'll be an adult performer is the most ridiculous thing I ever read. How many times a day do you jack off on porn btw?\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small Esperanza Robertson u are really triggered comparing a female with a male is like comparing water with fire my \textbf{nigga}.\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small +Civopop11 hope you enjoy your \textbf{sex} life with boys\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Getting ass fucked and humiliated on camera is different than ass fucking and humiliating,mens' roles in pornography are far less humiliating than womens' roles ,let's face it having my daughter suck a ton of dicks and get fucked to the point of nearly tearing up is \textbf{nothing} like having my son fuck a girl,saying otherwise is a clear lie,surely only a minority of people grow up to be pornstars,but I see why he fears having a daughter. \textbf{Sex} is fine ,but female pornography isn't something one would wish for his daughter...And it feels like an easy ,lazy way to earn money,this whore sounds as \textbf{dumb} as arock,and one would assume she couldn't get a real job and so sold her body,again ,not the dream life for one's child..\normalsize   & \cellcolor{green!27}Dumb, Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/128 & \cellcolor{green!27}2.344 \\  \hline
  \cellcolor{green!5}\small Civopop11 - When the artificial wombs and \textbf{sex} robots come, we can begin the termination of all female toxicity from our culture.  We can finally make a better world.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small nick supreme - So to study something like drug addiction one must be a degenerate \textbf{drug addict}.  Hmmm....you...are...a...fucking...genius...mate.\normalsize   & \cellcolor{green!27}Drug addict & \cellcolor{green!27}Behavioural Addiction - Drugs & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Nat Aki False equivalencyStudying drug addiction = scienceEnjoying pornography = done for \textbf{sexual} pleasureFinding \textbf{sexual} pleasure in something you percieve as degrading = sadistic by definition, mate. Then again... now I see your above comment"When the artificial wombs and \textbf{sex} robots come, we can begin the termination of all female toxicity from our culture.  We can finally make a better world."Not going to happen bro. Just because you don't get laid doesn't mean women should be "terminated".\normalsize   & \cellcolor{green!5}Sex, Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/82 & \cellcolor{green!5}3.659 \\  \hline
  \cellcolor{green!27}\small i like how she and other \textbf{pigs} like her think that guys who dont want to be with a prostitute like her are ""jealous" and "insecure". no guy wants to turn a slut into a wife including guys in the industry. you picked a brainless  profession where respect is not assossiated and the onky credentials you need is to know how to spread'em and swallow; so now you must deal with its down side.\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small What's the big deal? It's hot she's a porn star. It's just \textbf{sex} while being filmed. As long as her man is kool with it what's the big deal.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Difficult to accept what someone who makes a living having semen on her face says. TRUST makes relationships work. Where the hell is the trust in THAT?? If you are a porn star you get what you deserve. You deserve to have ejaculate on your face PERIOD!! There is \textbf{NOTHING} Nobel about that line of work. There is NO excuse for it. It's either your life style or do something ANYTHING else. You want MERCY..................................go to church!!!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small I was with her until she said her partners need to be regularly tested when she is the one having \textbf{sex} with many many people.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small The HIV-infected semen slowly drizzled down Dani´s filthy,piece of shit cranium filled with whorestuff as she were reading the newest William Shakespeare novel on Iphone whilst three \textbf{midget} cocks punished her knowledge-hungry anus...On the morrow.\normalsize   & \cellcolor{green!27}Midget & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Weird seeing porn stars with clothes on\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I guess I am the only girl who doesn't care about \textbf{sex} or man parts at all. My man could be without his wang and I would totally date him if he was a nice,interesting person.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Mushy Pork Exposing Jezebel Succubus Hoes there's \textbf{nothing} wrong with exppsing Sin\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small This girl sounds intelligent, but the truth is, she is a fucking \textbf{psycho}, it's all over her face, well most of the time anyway 😂\normalsize   & \cellcolor{green!27}Psycho & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Gonna go watch this \textbf{woman} take some dick now\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dated a porn star for a while and never had an issue, but, it is hard to see someone you are starting to have feelings for being fucked by not one or two but a bunch of guys. Didn't mind a the girls though lol But it is hard to deal with seeing your girlfriend being fucked by someone else day in and day out. Though I have to say porn stars are much better than 'civilian' girls, they are able to see and value things other girls won't. \textbf{Sex} can be amazing with anyone as far as both love each other\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small nobody wants a girl that sleeps with many guys\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dani is a gorgeous \textbf{woman} and I consider her one of the best performers in the porn industry. But man, she has some deep rooted insecurities about the job that she's doing. You can sense it in the way she talks about critics of her line of work.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Jeez she think's she's having \textbf{sex} ? She is an adult performer. I wouldn't call her act as \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Dating is not for ho's. So please keep sucking and fucking until u turn ugly and \textbf{old}. And then spend rest of your life taking care of your dog.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small is it tho? she gets to have \textbf{sex} for money. Alot of money. There are way worse jobs out there i'll tell you that.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small DcTbigkiller30 haha what a \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Wadsmitter there is absolutely \textbf{nothing} wrong with being a drug dealer as long as you don't sell to kids.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Randall Stevens even our flawed justice makes a distinction between an accomplice and the perpetrater of a crime.  Your logic is flawed. Most people from the \textbf{age} of puberty have a desire for \textbf{sex}, this does not make it right for industries to exploit that desire.\normalsize   & \cellcolor{green!27}Age, Sex & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small MrJaaaaake True but as long as it exists she'll find work. Plus there's always the \textbf{weird} world of GILF porn.😂\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small No she'll probably have gotten through 5 husbands with no stable relationships, and then die as an \textbf{o\textbf{ld} h\textbf{ag}}.\normalsize   & \cellcolor{green!27}Hag, Old, Old hag & \cellcolor{green!27}Age - Over 65s, Gender - Female age and physical appearance & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small louisphilippe1100 the wall doesn't matter for pornstars. she'll do milf and then gilf porn, so her "job" isn't effected by it. and her social life is fucked up as it is today. no need for a wall. her market value is already \textbf{zero} and she knows.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small italkcrab That's not being hypocritical. It is the truth that the porn industry is useless, indecent, and gives off a distorted view of \textbf{sex} and intimacy. We don't need shit like that in the world.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Its just for men to relieve themselves. Distorted view of \textbf{sex} and intimacy is associated with porn addiction which are rare cases. What the pornstars are doing is no different from Youtubers. People want to watch things, and so you make things for people to watch. Demand-Supply, simple Economics. If you gain a bad influence from it, is the content creator to be blamed, or the people who searched for that content?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small Doesn't necessarily mean you have to be porn addicts to be affected by the negative influence of porn. I checked Pornhub's statistics for 2017, for example and based on their data, there were a majority of searches with keywords such as "young teen", "mother", "sister" and shit like that. People get wrong ideas and fantasize about crap like this because of access to porn. Most pornvids also mainly focus on the \textbf{woman}, and because of this, most people begin to think of them as more of a thing to satisfy your \textbf{sexual} desire rather than a human being who has emotions/companion, etc.These are just some examples, and I am sure there are many more.\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/114 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small jw3 reads"A sad "industry," almost entirely controlled by the same people."Doesn't that apply to just about every industry in existence? Western oligarchies pretending to be democracies are almost entirely controlled by a small number of ultra wealthy individuals.I don't see how the porn industry is any more "sad" or exploitative than huge multi-billion dollar companies paying minimum wage for long hours to uneducated slaves so they can subsist for 60 years then have a stroke. At least this \textbf{woman} is honest about what she's doing.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small Harry PotterSo your problem isn't with promiscuity but with the fact that some women don't feel shame for straying outside of what you consider normal behavior? \textbf{Weird}.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Judas IscariotI don't consider promiscuity a problem. In American culture, for example, you see people fucking since they are 15, and it is even encouraged. I have no problem with that because after all \textbf{sex} is natural and human instinct. What I don't like however is that people get money by fucking in front of millions of people and the bad influence porn has on people\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Harry PotterSeems odd to me. If a \textbf{woman} is going to have \textbf{sex} with a significant volume of partners why not do it in a  safe, professional setting and get paid? Seems more logical to me. Beats being one of these 20-something college girls who get blackout drunk every weekend and has unprotected \textbf{sex} with half a dozen guys.I don't get your issue with filming \textbf{sex} or pornography. What bad influence are you talking about? Like anything, porn can have positive and negative effects based on many variables from use case to the psychology of the user. There's no conclusive evidence that it has an objectively "bad influence."\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/110 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small Harry Potter Lots of studies show porn consumption has many benefits. The thing with these types of "studies" that are funded by groups with an agenda is that find they always find the conclusion they go looking for because they have poor methodologies and no controls. That's the nature of confirmation bias.It's not societies job to legislate "shame." I don't see why the government should be involved in any act between consenting adults, whether it's \textbf{sex} workers or consumers. Do you really want to live in a repressive society like Saudi Arabia that criminalizes "immoral" behavior? I sure don't. Anybody who doesn't like pornography is free to not view pornography. Part of living in a free society involves giving consenting adults the right to make choices you may not agree with.Why would it bother me if other people want to walk around naked? Has literally \textbf{zero} impact on my life. The only reason I'd even notice is because it'd be unusual.\normalsize   & \cellcolor{green!5}Sex, Zero & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/163 & \cellcolor{green!5}1.227 \\  \hline
  \cellcolor{green!27}\small Nothing wrong with being a porn star, but don't judge others less attractive.We look at porn because we are SAD!Gone are the days when only "perverts " viewed porn. It's almost a majority activity, so lets cut the hypocrisy and silly virtue signalling.Porn is an addiction like booze and any other compulsion and we are mere mortals, fragile and weak.Can anyone suggest a substitute for the intimacy many of us don't have in our lives?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Look people truth be told......She must be AMAZING in the sack! Like Picasso painting. If you don't have to pay a fee for the \textbf{sex}? As long as you're safe, pardon the pun but..  I'm ALL IN!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small What a fucking stupid fucked up \textbf{slapper} !!!\normalsize   & \cellcolor{green!27}Slapper & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She is not hot enough for all this drama. She makes having \textbf{sex} professionally seem like being a coal miner. They are in deep dark holes for hours. You don't hear them complain.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small She's a \textbf{slag} end off... what does she expect ffs? 😂 stupid bitch\normalsize   & \cellcolor{green!27}Slag & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small No man with any kind of self respect is going to date a \textbf{ho} like that. She´s left with cucks and degenerate creeps.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Yeah, and the only reason someone would be with her is so they can get a decent blowjob or \textbf{sex}. Never love. Degenerates like her don't have emotions like that\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small If you look at her Instagram, you can see her husband looks like a fucking \textbf{fat} ass hobo that looks about 60. This man is right, no self-respecting man would want to be with her. Only the \textbf{old} ugly perverts with perhaps a big dick can satisfy her thirst.\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Harry Potter you don't need porn ? Well how come you are gonna have your \textbf{sex} education ? And dude drugs is killing you ... Just putting it here\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small You can learn about \textbf{sex} by reading articles or books. I never learned about \textbf{sex} from porn, I figured it out myself as I gre older by talking to friends or reading. And I was not saying porn kills. I was saying jsut because you do something doesn't mean you can't be critical about it....\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small Most guys issue is they don't want a partner where more ppl have been inside her then the local fast food place lol. Being a porn Star means you can't be faithful to your partner. Also there's a trust issue too, how can a guy trust that their porn Star GF is going to stay faithful to him. Porn stars are less exclusive because not only have many ppl been inside her, she's all over the net naked and having hardcore \textbf{sex} for everybody to see. Porn stars are good for one night stands, but not really marriage material.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small Exactly who wants to date a \textbf{chick} who swallows cum for a living.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small WireTamer oh look, a stupid 14 year old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small disarmsox you buffoon go and look up the definition of prostitution. It's taking money for \textbf{sex}. So it is effectively the same. Yes the title is different but the principle is the same.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Having \textbf{sex} on film is acting, not prostitution. If it was prostitution then the guy typically will be paying the \textbf{woman} for \textbf{sex}, not both parties being paid to have \textbf{sex} in front of camera. Two different things. I think you're just jealous of other people's success and money.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/49 & \cellcolor{green!27}8.163 \\  \hline
  \cellcolor{green!5}\small disarmsox you have already agreed there are similarities. That was my point all along. So \textbf{nothing} more to add. The fact is both earn money from \textbf{sex}. One performs for a camera taking money and one performs in private taking money. Don't get caught up in the semantics there is profit from the act of \textbf{sex} where a \textbf{woman} is selling herself for your entertainment and making money.\normalsize   & \cellcolor{green!5}Nothing, Sex, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}4/68 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small duaplex1 and it's not just the \textbf{woman} getting paid.. it's camera crew, the male, etc etc etc etc etc.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small disarmsox and the studio, still prostitution. They all profit from it. Here is the English Dictionary definition (the practice or occupation of engaging in \textbf{sexual} activity with someone for payment.) Different job title same outcome.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small With porn everyone gets paid. Not just the \textbf{chick}.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small duaplex1 don't listen to him he's a porn addict who watches some low iq \textbf{w\textbf{hite trash}} pretend to be connected to guys for money she like most other 'pornstars' probably has no connection to her parents as they have abandoned her she's never falling in love probably has drug and addiction problems is just overall a loser who offers no value to people's life besides 5 minutes of hedonistic tugging fantasying to have \textbf{sex} with her, and she's not even that attractive.\normalsize   & \cellcolor{green!5}Sex, White Trash & \cellcolor{green!5}Ethnicity - White, Gender - General, Social Class - Working class & \cellcolor{green!5}3/82 & \cellcolor{green!5}3.659 \\  \hline
  \cellcolor{green!27}\small stop saying pornstar \& making them like they do something noble..she is a \textbf{ho},bitch,whore,slut,\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Wow her job sucks she's fucked gosh that's a real pain in the ass job who knew being a pornstar would be such a stretch I couldn't see this working in a relationship I mean can you imagine trying to fuck her in the ass at night she's like I'm sorry I've already had a tree trunk up there my ass is still sore how about we just do \textbf{old} vaginal I still got some lube from earlier today let me throw my legs up in the air because if you hurry up it won't dry up I just didn't get it all out from before but honey it's sucking me in it feels like your cabin has been depressurized yeah that's okay I just had a mandingo gangbang party for the last 4 hours I've had about 40 feet of penis going in and out of that hole but you love me dear right why don't you go down on me I washed it it's clean I promise.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/169 & \cellcolor{green!5}0.592 \\  \hline
  \cellcolor{green!27}\small manuel men she sounds like a complete psychopath. All those strippers, porn stars are fucked up in the head. They can't be wives, they're not special women. They're either women who were raped as kids or had a traumatic childhood. \textbf{Nothing} special about them. She's just a object of society.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small inappropriately aligned metaphorical nourishment I personally think we don't have to go any further arguing about her since I think she's really living her life n getting money out of it while enjoying her \textbf{sex} life..so yea hope all is cool..spread the love not the hatred :)\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small I don't know what I watched that this was on my recommended listing. Honestly who gives a shit about a porn performer interview. Here's a short synopsis of what is actually not said in these interviews. " I am either sociopathic or have serious daddy issues to go along with my \textbf{sex} addiction and love of attention and or fast money. I have the occasional relationship to project the image of being normal but don't actually love anyone including myself."\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small What planet do you live on? Not Earth. \textbf{Nobody} wants a used up diseased vag that looks like a wizards sleeve.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Ria lol says who ? I for one would take a virgin over a used up \textbf{hag} with a torn up anus.\normalsize   & \cellcolor{green!27}Hag & \cellcolor{green!27}Gender - Female age and physical appearance & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small nick supreme all you need to do is google search her name with the safe search off and you'll see all the acts she partakes in , you see Unlike you I look up someone's past before I bash them  defend them. If a women allows herself to be treated like a object then she is indeed \textbf{nothing} more than a useless item that dirty back alley porn directors use to make a profit.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small The SlasherSo you "looked up" details of Dani Daniels' porn only to leave comments here. I don't think most people would buy that explanation.Answer this question: Do you watch porn yourself? Last part of your comment once again reflects your idea of a woman's value being tied to her \textbf{sexual} history. Having \textbf{sex} on camera =/= being a "useless item". Is this your view of male pornstars too?\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small The SlasherNow I see your new comment:Thanks for allowing me to prove you're lying to me even more.There is \textbf{ZERO} way to know details like"The men in her vids slap her around and penetrate her anus all while spitting on her"or" she gladly allows dozens of men to ejaculate inside of her mouth"without watching the video. \textbf{NOTHING} in the description indicates anything of this nature.And I definitely need an explanation to why you can know that the men spat on Dani Daniels the entire time even if you "never watched" - see my above comment.\normalsize   & \cellcolor{green!5}Nothing, Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small She is a whore not a porn star, there is no such a thing! She is clueless about what a man wants, we are not insecure, it's called stability and loving a \textbf{woman} that \textbf{nobody} is having but me,the real man. Wait until she wakes up....who is going to have 1000,s of therapy session that won't work eventually? Stupid ass bitch!\normalsize   & \cellcolor{green!27}Nobody, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small Life isn't only money and \textbf{sex} I'm afraid you r missing the real happy life and you will realise that when it's will b late\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small wait what you don't want to date a porn star why?i mean she has a lot of experience and who care's about her jobas long as you have fun and or feelings for each other who care's it like dating a \textbf{hooker},\textbf{sex} performer,  only difficult thing she is more famous\normalsize   & \cellcolor{green!27}Hooker, Sex & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small maybe the truth is that \textbf{NOBODY} wants to be with her so she decided to convince herself and others that its an insecurity thing with others  lol what a goon shell most likely od on depression drugh in a few years from now watch and see.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Performer? Prostitute is the correct term. You have \textbf{sex} for \$\$\$\$\$\$\$\$\$.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small she isn't very bright, guess that why she has \textbf{sex} for money.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Work is work. \textbf{Sex} for money is still work. There is \textbf{nothing} wrong or shameful in working.\normalsize   & \cellcolor{green!5}Nothing, Sex & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Assassins get paid to kill people. Work is work.  Killing for money is still work.  There is \textbf{nothing} wrong or shameful about it.  Game. Set. Match.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Well only idiotic whores without a proper education do \textbf{sex} for money. Otherwise you would have a decent job\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small What a \textbf{dumb} ass!  But keep performing baby dale😉\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Nothing faithful with her lol\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small More appealing to the general population and as someone said \textbf{nobody} wants to watch Margaret jane get fucked\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Was hoping for interview turned into \textbf{sex} pornography 🤣\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Nobody would date porn star\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small thot\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small I dnt understand why she needs a date...she is getting what other ppl dream for...daily \textbf{sex}...lolzzPpl date for \textbf{sex}...or for a good relation...i say make frds for good relation or for sharing things...you already getting enough \textbf{sex} with good sizes...😂😉lolzz\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small Does having \textbf{sex} with someone you love feels special compared to performing on screen?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small You re gross and have Stds that's why you have a hard time dating .Plus you having \textbf{sex} with other men for a living is a turn off.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small 1 Corinthians 6:9-10 (KJV) Know ye not that the unrighteous shall not inherit the kingdom of God? Be not deceived: neither fornicators, nor idolaters, nor adulterers, nor \textbf{effeminate}, nor abusers of themselves with mankind,Nor thieves, nor covetous, nor drunkards, nor revilers, nor extortioners, shall inherit the kingdom of God.\normalsize   & \cellcolor{green!5}Effeminate & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Please guys....... this ends the debate weather girls have \textbf{sex} for money.  They all do so sign pre nups.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small How does one person talking, speak for every \textbf{woman} on earth?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Sails I will only sign one pre-nup: bitch gets \textbf{nothing} if she leavesor better yet don't marry her unless you trust her more than anyone else on Earth!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Oggy Oggy....... I've learnt a few things in my life...... \textbf{woman} love money........ Americans love themselves ........and the English love ladyboys...... I bet your English...... I can smell the dick on your breath from here!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Best \textbf{pussy} ever.  DD THE BEST!!!!!!!!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small from a guys point of view : \textbf{Sex} all the time, bathroom all to myself, no drama, full control of my money. Why the hell would I want to screw up my already perfect life with a girlfriend?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small marlon anan porn is completely different than prostitution/\textbf{sex} trafficking. \textbf{sex} work is a much bigger field of work than that. the performers in porn are doing it willingly, they enjoy it, they choose it, they only do what they are comfortable with. STD's are taken very seriously which is why they get tested before all scenes. they are responsible believe it or not. if you opened up your mind to educate yourself about the industry you will definitely learn a lot! they are still people, but 'normal' people dehumanize them while at the same time using their work to their advantage. there's lots of documentaries on all forms of \textbf{sex} work I highly recommend you watch some! personal choices don't make someone a low life trash person. 🤷🏽‍♀️\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/128 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small +Alexia Zamora Incorrect. Personal choices define everything in the modern world. What we do with our lives gives insight into our values, lives, and everything about us. Low life trash like pornstars gives people a distorted view of what \textbf{sex} is. People take it for granted or get the wrong impression from it. There is a reason why the general public does not like pornstars. People respect those that have respect for themselves and those that help the society in some form. Tell me what value do pornstars have? And no don't give me some bullshit like so people can jerk off. Pretty pathetic if that is the only reason they are worth anything.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/114 & \cellcolor{green!5}0.877 \\  \hline
  \cellcolor{green!27}\small Hmmm interesting bunch of comments y'all......if I were a half decent \textbf{chick} I'd be a pornstar too......pleasure doing business with you x\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Oh, but you'll still watch porn, won't ya \textbf{fatty}?\normalsize   & \cellcolor{green!5}Fatty & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Anyone with \textbf{common} decency, would avoid anyone who is judgemental of people they have never met.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small TheFatAmericans1 she sounds like a complete psychopath. All those strippers, porn stars are fucked up in the head. They can't be wives, they're not special women. They're either women who were raped as kids or had a traumatic childhood. \textbf{Nothing} special about them. Porn stars are  just OBJECTS of society.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small You can't make a \textbf{ho} a housewife.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small she just got to find that guy like that type of \textbf{sex} life\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small A whore.\textbf{Nothing} else to say.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small All men want to fuck a whore but no man wants to be married to one. Dani Daniels is no exception you can just look at her and see she's not going to \textbf{age} well then what? She was probably abused as a child molested raised up with less than adequate moral values typical you might think it's mean and cruel to say that but you know what it's true doesn't mean we shouldn't love her for who she is but it's because we care about her that she needs to hear about it they used to call it boy \textbf{crazy} she just \textbf{crazy} about it she can't stop herself that chemical hormones you know that's all it is.\normalsize   & \cellcolor{green!5}Age, Crazy & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/119 & \cellcolor{green!5}2.521 \\  \hline
  \cellcolor{green!27}\small Witch one is dani\normalsize   & \cellcolor{green!27}Witch & \cellcolor{green!27}Gender - Female age and physical appearance & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small At what point did I even intimate she had \textbf{sex} with 300,000 people??\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small exactly so any person with so much mileage behind them. have some serious \textbf{mental} issues that come along with it.lost of any respect to long term relationship being one of those things\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small A good mechanic can let a car run good for a million miles.  \textbf{Old} cars require much more TLC, but then mechanics LOVE vintage cars.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small love your point of view, but sometimes you go in love at the second hand car shop with one have to much km and you take the risk...., and you drive it and you like which the rest of the people look and say guau i like the car is really cool, and probably  next day you gonna take it and dont go anymore because is brocken and is more xpensive repaire it than other in better conditions, and you know which you made the idiot for buy it but you say was beautifull and cool....., thats life, human \textbf{race} is in that way....., no problem if my dick isnt like my arm, i have a good tongh and i gonna put inside alll i can, incluiding arm and fist, all is goood in a battle...., i love it, i know im idiot but still i wish a pornstar with a nice fake tits than a normal and good \textbf{woman}, im human, but this one isnt my kind....\normalsize   & \cellcolor{green!27}Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/168 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small lmfao women logic "men are insecure because i have \textbf{sex} with big dicks" real logic "guys don't want some disgusting \textbf{tramp} that has swallowed tons of semen." Women who are in pornography are fucked up mentally with daddy issues. This stupid whore doesn't realize "civilians" don't want to date her, they just wanna stick their dick in some porn-woman's bacteria infested hole. (Notice how I didn't say Porn actress or Porn star, because laying on ur back taking a cock is not difficult.) When i see a girl ive fucked dating someone, i laugh at that guy. I got her \textbf{pussy} for free and he has to pay for it. LOL NO HYMEN NO DIAMOND POPPED CHERRY DON'T MARRY They say one man's trash is another man's treasure, but you won't find me searching through the garbage for a wife.\normalsize   & \cellcolor{green!5}Sex, Tramp, pussy & \cellcolor{green!5}Gender - Female sexuality, Gender - General, Nationality - Chinese & \cellcolor{green!5}3/140 & \cellcolor{green!5}2.143 \\  \hline
  \cellcolor{green!27}\small Horrible analogy. There's no indication a woman's \textbf{sex} life affects her the way mileage does a car. Maybe compare her to other humans?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Karan Drag what down to the lowest possible level? People deserve respect because that's basic human decency. And don't start that 'people have to earn my respect' bullshit. You respect strangers you pass on the street, right? \textbf{Nobody} is demanding your respect, it should already be respect there.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Memes. Many Such Cases! Dude you're a horrible person. You want a virgin, yet are not one yourself? Thinking of women you've had \textbf{sex} with as trash? Wow. I hope you learn empathy and how to treat people\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Arin, courtesy and respect aren't the same thing. When you're out in the community you treat others with a level of decency yo avoid conflict. Respect is a measure of esteem for another, that can't be given to someone you don't know, it can only be earned. And yes, men jack off to visuals of naked women having \textbf{sex}, that's what she gets paid for, it doesn't mean she automatically deserves respect! I have the same respect for a bottle of baby oil, which is also a tool I use to masturbate.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small To green \textbf{frog} above: Do you really think we believe you? I go to your channel and I find 'ironic' neofascist propaganda and anime girl videos. You can't make this shit up. Tough guy online, neckbeard in real life. By the way, kindly look up who actually date and marry famous pornstars and tell me if people like Tito Ortiz or Lukas Rossi or Jesse James or male pornstars really are the epitome of 'cucks'.\normalsize   & \cellcolor{green!27}Frog & \cellcolor{green!27}Nationality - French & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Looks good on the outside but the test drive \textbf{nothing} but loose v  .\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small When a pornstar who takes \textbf{alien} like dick says 6' feels amazing, 99 of guys are going to be fine\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I think it's interesting that the problem her non-industry boyfriends have,  according to her,  is self esteem issues,  but within the industry,  the problem, again according to her, is jealousy.   Personally,  I can see the jealousy issue, but what would want,  ideally,  is a frank and open discussion of any time that my partner begins to have romantic feelings for someone else or lise her romantic feelings for me (which I think all couples go through,  just usually in unhelpful silence). The \textbf{sex} wouldn't really bother me.  It's just \textbf{sex}.  What would bother me is the possibility of one of us looking to exit the relationship without warning and without trying to keep it alive. Anyway,  best of luck to her.  I am sure she will find happiness one day! She seems charismatic,  and he is definitely adorable.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/138 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Since the very beginning relationship was created for more than just between two people, that changed with the Christianity, in the older times it was normal to have many wives, and many men, it was a normal occurance to have sacred orgies every sunday to worship Gods, and it was not available only for the wealthy and privileged, and women always had positions to work in \textbf{sexual} services like prostitutes. But porn and prostitution itself have been in modern times completely corrupted, morally, spiritually, it is not even close to what it used to be, back then it was used for reaching higher spiritual realms of consciousness, it was not focused merely on the bodily pleasures, that was entirely perverted by Christians and society, there was a true love in polyamory, with no matter how many people they were with, polyamory is an evolved state of consciousness, not many can handle jealousy or insecurity that would come with it, that's how todays society has been psychologically damaged, far cry from what it used to be in pre-Atlantean \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Sexual & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/178 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Chiraq TookaPack at least the \textbf{ho} honest...she ain't on here like \textbf{black} women pretending Jesus sent them white boys.\normalsize   & \cellcolor{green!5}Black, Ho & \cellcolor{green!5}Ethnicity - Black, Gender - Female sexuality & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Wait till you see her used up \textbf{pussy} and asshole. All her holes probably smell like cum\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Dating ' civilians ' - they get jealous  but I'm compassionate. Dating a fellow star - we both get jealous.Duh \textbf{woman} that's normal.You are doing a favor by being compassionate xD\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small cartmanrlusall Son of an OB/GYN, can confirm rx7dude2006  has it right-ish. It's really a matter of the vagina being super elastic. The biggest factors in become loose are actually \textbf{age} and exercise, not dicks and babies.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small i like loose \textbf{pussy}...is this wrong?\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Even if she is not looser, imagine having to eat out her \textbf{pussy}. Probably can smell the traces of thousand of male cum mixed together lmao. Filthy as shit.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small rx7dude2006 bulshit I did a \textbf{sex} worker and a virgin , virgin way more stronger\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small she is fucking hot, plus she has a hairy \textbf{pussy}. mmmmmmmmmmmmmmm\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Seriously what guy wants a Porn star for his Girlfriend? Might as well date a \textbf{hooker} on the street or a Bar Slut.\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I never read lengthy comments but I just ready every comment on this feed. If you talk about \textbf{sex}, my attention goes waaay up No pun intended\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I don't feel sorry for this bitch. She chose to suck dick and get fucked in the ass on camera which means she does not give a fuck about her dignity and self worth. So no, why would any man seriously consider being in a relationship with that shit? Every time she goes on set she declares that she's just a hole to put your dick in, \textbf{nothing} more.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Pretty \textbf{woman}..But I think she is STRETCHED...😂\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small If she dates a civilian, she runs the risk of jealousy because she 'has a lot of dick, big dick', and that all of their friends have seen her naked 'and with things inside her'.  And yet, if she dates a performer, there's potential for jealousy because they all have \textbf{sex} with each other as a part of their job.  There's not a lot of wiggle room, there.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Pornstar are hopeless people who wants to have a good lifestyle without working hard.... Who would love to date you when you said you are going to work but instead you are having \textbf{sex} with someone\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small "Dating is a nightmare " gee I wonder why. \textbf{Nobody} wants to merry a prostitute.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small never got why pornstars complain about dating. if u wanna do porn fine but don't wine about not being able to find a partner. whenever u decide to sleep with other people it's gonna cause problems, it's only natural. i think deciding to do porn let's u have \textbf{sex} without a relationship sound pretty awsome.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small She eats \textbf{pussy}  and licks girls asses like a champ.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She ain't a pornstar no more she got married to some \textbf{old} fucking Bastard , she's living in New York,  and she don't even film scenes,  she only does that camsoda  crap\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small That \textbf{pussy} and asshole have been through endless cycle of dicks. No thanks.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small This person ( cough...not a lady for sure ) will end up lonely in her \textbf{old} \textbf{age} or with Manuel's shrunk dick . At least they will many pleasant memories together since no one else of substance will want to tie their souls to such ...whatever. Dont glamorous this life style.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small WireTamer I give both men and women shit if they are \textbf{promiscuous}, but lets get real. Men and women are biologically different. This means that men that hoe around aren't as damaged as women who do. Women that slut it up in my experience tend to have \textbf{mental} issues later on in life. I believe there is some research literature that confirms this.\normalsize   & \cellcolor{green!5}Mental, Promiscuous & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small Because you treat the very human act of \textbf{sex} that's supposed to be or looked as as sacred bond as a fly by night payday. Of course you are worn out. When you are 60 you will be not only a hotdog thrown down a hallway to  have \textbf{sex} with but you'll look like two pizzas with a ham dangling from between your legs. Sorry. That is sick but so are your choices. But hey. Its your choice to have a easy payday ..Money does \textbf{nothing} it's what you do for it that lowers your standards that give you that reputation.  You sold yourself out because you cant work a real job. No worries.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/114 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Surely it can't be just me that thought of some \textbf{black} dude when she said the name Manuel?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small what will she do when her body is no longer attractive? she has NO respect for herself. But Jesus died for her so I will not judge her. I will probably never understand why such a good looking \textbf{woman} gets caught up in this stuff. And she has no shame. I would love to ask her what she believes about Jesus. He said he forgives but sin no more. He will forgive if she is really sorry. She isn't. She is lost. The men she is with could care less about her. She may not have ever been loved in her life. But God's mercy is endless. I know he loves her. Please someone tell her. I do not consider her a "bad" person. I think she is beautiful. That is why I am perplexed. Not enough real men out there. Who will love and cherish her and treat her as a human being not an object. I am convinced that every single one of us is really looking to be loved. My heart aches for this girl. I will offer up my tears.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/184 & \cellcolor{green!27}0.543 \\  \hline
  \cellcolor{green!5}\small They also prey upon getting boys addicted to porn at as early of an \textbf{age} as they can.  Then often it turn them into clown punching pansies that are too nutless to approach women in real life.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small The porn industry is parasites that for the most part prey upon \textbf{drug addict} women.\normalsize   & \cellcolor{green!27}Drug addict & \cellcolor{green!27}Behavioural Addiction - Drugs & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Western women (especially American) are viewed as whores by the entire world. A lot aren't,  but I personally can totally understand why the majority of people on some other countries think that.  Sluts like this \textbf{tramp} laugh about being too stupid to make money any other way but being degraded like a brainless \textbf{sex} toy by guys.\normalsize   & \cellcolor{green!5}Sex, Tramp & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small Raul Trujillo porn is completely different than prostitution and comparing them is only doing damage to the real victims that need help. \textbf{sex} work is work.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Its testament to the world that men love sluts for casual \textbf{sex} but having a relationship with a slut or whore isn't going to work unless you are mentally disfunctional as men are like a dog with a bone, we don't like to share!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small You'll end up lonely babe, 'cause men don't marry the whores, men just spend some time with them and that's it \textbf{nothing} more.This is not the Pretty \textbf{Woman} movie you know.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Well I guess she's fucking the whole day on set and then comes home at the evening. Either she is exhausted and her boyfriend can hear her bitch about her job which equals being fucked by tons of guys, or she keeps fucking her boyfriend and spends her whole life with \textbf{sex}. As much as I enjoy \textbf{sex} should  it be the whole purpose of ones life?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small What the F.  Why are they called Porn 'Stars' when they are the lowest form of human.  \textbf{Sex} trafficking, in one of its various forms.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Russell, I was not responding to you. I actually  agree with you on Trafficking and for all of the reasons so many \textbf{sex} workers use, that there's not support to anti-prostitution laws, new ones anyway, so hard core feminisits and moralist right wingers all use it as  way to pull on heartstrings and it's dishonest all the way around.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small She's a ho\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small dino2170 He is telling what this \textbf{woman} is a WHORE as simple as that. Whores make \textbf{sex} for money that is what this WHORE is doing. \textbf{Nothing} to do with morals, I don't care a shit about her. If she wants to make \textbf{sex} for money ok, if she wants to kill herself with a shotgun is her problem, if she wants to jump from a cliff is her problem... as simple as that.\normalsize   & \cellcolor{green!5}Nothing, Sex, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}4/74 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small And there is \textbf{nothing} wrong with it, just a job like anything else. IF you dont sponsor it stop watching porn then.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I thought if they get paid from the guy. She gets paid to have \textbf{sex} while getting filmed. And she doesn't get paid from the guy she has \textbf{sex} with. Sorry but she is not a ho\normalsize   & \cellcolor{green!5}Ho, Sex & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small It is a job, and porn is legal not like drugs you see. They have \textbf{sex} for money which they support their life with. And by doing their job they give back to society by letting us who watch it get satisfied. And if you did not have you wife to fuck with every night you would sit and watch porn no doubt about it.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small dino2170 There's only one reason to date a porn star,to get \textbf{pussy} and treat them like the slut they are.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Norman Alvarez I wish I could have a \textbf{ho}.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Dumb bitch needs to stop referring to people as civilians,your not military ho\normalsize   & \cellcolor{green!5}Dumb, Ho & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Warren Van Niekerk Now yes but he's talking about when she gets too \textbf{old}. Which let's be honest is about 24, after which you move into the 'milf' niche.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small 1 mil is \textbf{nothing} these days espacially if you living in hollywood paying for luxury\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I can see the situation at hand and can  understand both sides of the story.I've Never been a performer but I've dated one before.Thankfully I knew what her job was SO, I knew what to expect and it wasn't for this reason we broke up.Yes, she had to work odd day's and nights but this didn't bother me so much.At the end of the day, dating someone that your not going to be happy with is not good, as she said one day to me.... '\textbf{sex} is just \textbf{sex}, its my job and yes I enjoy it but with you, as in with me, with you it's making love and not just \textbf{sex}....which is different.'I understood this and it worked really well, it was just something else that was a situation for us both that we decided to split amicably .... \textbf{Nothing} serious or too bad.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/151 & \cellcolor{green!27}1.987 \\  \hline
  \cellcolor{green!5}\small Robert Rp. "With you is not \textbf{sex} is making love" ha ha ha and you believe that? ha ha ha  that is what we men say to the women.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small A \textbf{woman} that lets men cum on her face for money is not a bad human being ? What a pig .\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small What's the point of her wearing clothes? Everyone on earth can see her \textbf{pussy} and tits anytime they want lol\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small they have a very high Suicide Rate, August Aimes,just passed away a few months an attractive looking \textbf{woman}, I read in a Newspaper that she was being harassed by people writing nasty comments about her.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Nobody wants to date a porn actor! Imagine how wide her ass hole and \textbf{pussy} hole are? Plus all the cum in her mouth!!! Its just gross.....\normalsize   & \cellcolor{green!5}Nobody, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Well she got married a while back, but it was to an \textbf{old} dude with money.. go figure.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I think she doesn't get it !\textbf{sexual} relationships were never meant for porn ,it was created for 2 people who love each other exclusively . A very important part of the relationship is commitment to each other and the intimacy .That is why porn relationships will always turn to shit , because you are going against God's intended plan .Repent ,  you have chosen a sinful unnatural path for your life ,no judgement intended ! I can tell you are intelligent and beautiful , what you do in the next minute could change your life for the better ,it is never too late .God bless and good luck !!\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/111 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small You are being very shortsighted.  \textbf{Sexual} Relationships were meant for reproduction and even if you take the biblical view of things, monogamy wasn't the default position.  But I can show you that marriage according to god's plan assuming you are a Christian, end badly at rate higher than documented Porn marriages and divorces.  There's not a lot of data on the subject but you seem to be implying that porn stars only get involved in relationships with other porn stars.  Many get married to people that aren't in the business.For marriages and relationships that go according to God's plan, there's a lot of infidelity, physical abuse and \textbf{mental} abuse. Seems like God's plan doesn't really have much to do with whether a relationship goes well or not one way or the other.  And IDK what your view is on \textbf{G\textbf{ay}} Marriage, but many Christians claim that same \textbf{sex} marriage goes against God's law citing essentially two verses from a text they never read the original version of from languages they can't read for themselves. But that said, there are plenty of very happy \textbf{g\textbf{ay}} marriages and divorce rates are lower than that of 'traditional marriage'. I'll be intellectually honest enough to point out that you can't make factual claims when the samples you are comparing are very different (porn professionals are an absolutely tiny part of the population, and if you are holding that \textbf{g\textbf{ay}} marriage goes against God's plan, gays tend toward 10-15 of the population, in both cases, they are groups much smaller than heterosexuals who get married).  But your claim is that relationship god doesn't approve of will go to sh*t.  There's no way around the fact that as defined by his book, relationships he does sanction, performed by his own believers and administered by his own leaders fail at an alarming rate.\normalsize   & \cellcolor{green!27}Gay, Mental, Sex, Sexual & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}9/307 & \cellcolor{green!27}2.932 \\  \hline
  \cellcolor{green!5}\small Humans are animals, idk why people are so offended by that, humans are no superior beings, god doesn't exist to give you a greater purpose, you're just some organism like any others and when you die you'll go back to \textbf{nothing}, not hell or paradise.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small live to create to live,  you said:"That is why porn relationships will always turn to shit"My response to that:First of all, they don't!And second of all, porn wasnever meant for relationships.They're just messing around for money, it's not a relationship!If there are any hard feelings, you're obviously in the wrong bushiness!I'll say it again: Porn Is Not A Relationship!Okay yeah, sure, if it was me,I would not ever do such things.But that's just me!Porn doesn't really seem to bother me at all.What does bother me, is lying and cheating,within an existing relationship.Like when I watched "Walk the Line"I got so mad at Johnny Cashfor his disturbing behavior,if you know what I mean,that the teacher had to ask meto walk out of the room, so thateveryone else could watch it in peace.So why did that bother me so much,but when it comes to something like thisI say, hey, it's your life, you're allowed to do with it as you will.Tell me, do you see a difference?I will refuse to believe that I'm just \textbf{crazy}, and my feelings are just random.That's what \textbf{dumb} people say, because they are too lazy to figure things out.No one's feelings are random.Okay, there has to be a reason,there must be a major difference here.Everything in this world,from the smallest breeze,to our every feeling, has a cause.So I'm not \textbf{crazy} for asking, what caused me to beso bothered over there, and yet at the same time not here.Why here do I say "do what you want",and yet over there, I'm actually sent out, for yelling at the screen?\normalsize   & \cellcolor{green!27}Crazy, Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/298 & \cellcolor{green!27}1.007 \\  \hline
  \cellcolor{green!5}\small live to create to live says who? Monogamous relationships are a thing of modernization, from the very beginning of the human \textbf{race} back when we where barely walking on two feet, poligamous relationships were the norm, reason why till this day, staying "faithful" to one person is a very hard thing to do for a lot of people. And let's not talk about \textbf{sex} as a bussines cause we all know that prostitution have been present from pretty much the moment humanity started to settle.\normalsize   & \cellcolor{green!5}Race, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small Pornstar relationships never work out. Even if it did, they have to like go through so many divorces and husbands, no one would want to marry them when they become an \textbf{o\textbf{ld} h\textbf{ag}}.\normalsize   & \cellcolor{green!27}Hag, Old, Old hag & \cellcolor{green!27}Age - Over 65s, Gender - Female age and physical appearance & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Before I say anything else, let me just make this clear:Most people don't want to marry anyone who is an \textbf{o\textbf{ld} h\textbf{ag}},porn-star or no porn-star! Why are we talking about \textbf{old} hags?You just took whatever point you had, and through it out the window there.Now back to the first thing you said, Harry Potter,I assume you mean their general relationships with people in general.Because there's no such thing as "Porn Relationships"as "live to create to live" had said it in the beginning.My point is:There is Porn, and then there is Relationships.They are two totally different things!  One is quite an interesting type of job,that some people obviously like to do.  And one is about beingstrongly connected with someone,with the addition of \textbf{sexual} feelings for them.Porn is not some form of dating!God! Go find yourself a dictionary!It has actually, \textbf{nothing} at all, to do with relationships!Of course, it may very well effect the type of people you date,but as "live to create to live" had put it, it is just simply inaccurate.You know what I'm saying, like dude, seriously,what the hell is a Porn Relationship? That's not a thing!Sorry to brake it to you! (not sorry, though)"PornSTAR relationships" on the other hand,the way you, Harry Potter, said it, is quite different.All that means is: Relationships that porn-stars have.Now you are talking about something real.And now that we're speaking English,lets discuss what you say, shall we.You go on to say "...never work out"To that I say: I don't haveexperience with them,so I can't say for sure,but I do think at leastsome of them work out.Maybe not in the same way as you and I would have.You know, like, they're probably more willingto accept that level of openness in their relationship.And other similar differences of sorts.But at the end of the day, it is a relationship.And with whomand for whatever level of opennessand for however long they decided toand for however long it lastsand for whatever other features yata...yata....bla..bla..etc.,it works!  At the end of the day, all said and done, it works!How often, and for what percent of them?Hey look man, I don't know.I haven't taken a proper surveyof every single one of them.But to just assume that they "never work out",I mean, you just don't know that.And as a second point,who said that they want a relationship anyways?Maybe they're perfectly happy with their way of life.You really don't know that they're all living miserable lives.Again, unless you have spoken to every single one of them,you just don't know that, to be the case.       Now, do I think it's a smart path to take? No. I definitely do not!But like I said in my previous comment above,it really doesn't seem to bother me.It's their life, and it doesn't affect anyone.Well, besides the people who choose to watch it,and in that case, it is only affecting themIN THE WAY OF THEIR CHOOSING,so that is still not the porn-stars problem.What?Are you gonna tell me they're forcing you to watch the stuff?I don't think so. So why would you have a problem with it?      On the other hand, for me, seeing such a character asshown by Joaquin Phoenix in the movie Walk The Linewas, for some reason, greatly disturbing to me.Even to the point that I was asked to leave the room,as I could not handle his horrible character,in regards to his marriage and women.So clearly, I do get bothered by disturbing behaviors and character.But people deciding to live their personal life as a porn-star,you know, for some reason, it doesn't seem to bother me, not at all.Maybe you can see the difference here. I think I can.      Now if porn really bothers you that much,then I recommend that you stop watching it!And if you were not watching it, then my question is:What the hell does it have to do with you?It's their life and it don't affect anyone, so why the hell do you care?(obliviously, I'm not talking to you Harry Potter, as you don't seem that bothered)(I'm probably referring, more so, to the original comment by "live to create to live") \normalsize   & \cellcolor{green!5}Hag, Nothing, Old, Old hag, Sexual & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Gender - Female age and physical appearance, Gender - General & \cellcolor{green!5}6/762 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small OMG...ban this video. After watching this video people might go celibate for whole life or prefer to die virgin.So many fucks and \textbf{sex}.Much confusing.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small can we stop calling them "stars" . they are whores all of them. just explained why living in a society of whores, is fkcd up, for sure. YOU DONT NEED TO BE A WHORE, TO BE A REAL "STAR" in the internet \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small say what?  Yea sure I have always looked forward to having a serious relationship with a \textbf{woman} that takes 10 plus dicks up her ass every week.  I mean what a better way to build some time of a relationship.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small I do not get anyone that would want to date a porn star.  WTF are you thinking.  She is blaming men for her getting a disease, and she could be giving them many, due to the volume of men she has \textbf{sex} with on a DAILY basis.  She is the one that is the higher risk to the man, not the other way around.  Both could be a risk to the other, be she is 100 times more vulnerable to get a disease than the "Civilian" she dates.  She just comes off as a royal BITCH.  Who would want her as a girlfriend??????\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small Imagine the Girth of her private parts after all of those Big penisis have violated herEvery other word is a swear word or dirty word Probably best to give her and \textbf{sexual} disease a miss\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small No thanks.dont want a \textbf{woman} who's had hundreds of cocks\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Plus she has the maturity level of a 13 year \textbf{old}..porn stars should realize that most guys fantasize about banging them but wouldn't actually bang them if given the chance\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Fuck you both bitch \textbf{witch} devil\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small this woman's logic lol this whole interview is \textbf{dumb} or a prank and she's not really a porn star.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small How \textbf{dumb} is this interview\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Doesn't she mainly do \textbf{lesbian} scenes?\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small To all you negative people commenting (not going to use the extremely juvenile h term), this is quite an \textbf{old} interview. Today, Dani is happily married, but does CamSoda shows on occasion, \& is really chill, having messaged her a few times.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small If you have lots of dicks in your holes your not in a serious relationship and never will be. You dont even understand how ridiculous you sound. A normal man with his shit together would never date a \textbf{woman} who has lots of dicks in her holes, as you say. Wow\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Therapist Joe says: "you took the words right out of my mouth".. \textbf{Sexual} abuse during childhood in females almost always results in promiscuity.. Usually \textbf{sex} at an early \textbf{age} with a lot of partners. But porn or escorting is another level. These are the most damaged of the damaged women..\normalsize   & \cellcolor{green!5}Age, Sex, Sexual & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}3/50 & \cellcolor{green!5}6.0 \\  \hline
  \cellcolor{green!27}\small her childhood was clearly within a dysfunctional family... psychologically, she was forced into adulthood. A poorly understood adulthood, since she was still a kid and had no idea what being a grown-up meant. She skipped adolescence by fucking with older people and not having a boyfriend of her own \textbf{age}. She is damaged because she skipped a step in life. Sad story. Makes it difficult to fap... to her.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small What a \textbf{mental} case\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small once a slut always a slut...western woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Sorry its more about a guy doesn't want to share his girl with all the penises in the world. Has \textbf{nothing} to do with confidence. Health wise,  to say its a risk is one big understatement.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small someone667 cheating is cheating; however, cheating is doing something outside of the established rules of a relationship. If you know someone is a pornstar when you start dating and you know they're going to continue being a pornstar it's not cheating because the two participants in the relationship already established what's going to be going on. Having \textbf{sex} with a pornstar does not necessarily mean you're getting sloppy seconds unless they did a creampie and didn't clean up and came right home and slept with their boyfriend. And all men with good-looking wives have to deal with knowing that there are other men jacking off thinking about their wives.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small What a \textbf{dumb} bitch.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Give me a break. Most porn stars are worth \textbf{nothing} but fuck whores. No "civilian " man wants to date or be in a relationship with a \textbf{woman} that has fuck over 100 men before him.\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Pussy for sale\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Is she able to have real orgasms even if she doesn't choose the actor she has \textbf{sex} with? Has she ever had a crush on an actor with whom she played?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I dont know would you really want to kiss this \textbf{woman} after shes finished work? Not me\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Insecure??? Get a word lady, \textbf{sex} is powerful in relationships and it's not something that you can just switch on or off...don't mix \textbf{sex} and profession.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small This bitch is retarded. \textbf{Nobody} wants a gaping \textbf{pussy} and asshole. Gross.\normalsize   & \cellcolor{green!5}Nobody, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small What a pig. She's worried about her boyfriend giving her a disease?? Her boyfriend is in much more danger of catching something from her as she's having unprotected \textbf{sex} with numerous guys on a daily basis. Her boyfriend can ruin her job?? What a joke!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Easy.....just have her have \textbf{sex} with only guys with small dicks......ha ha.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small it's not about some next dude's dick size (which is mostly faked, btw: most men's penises are the same size across the board regardless of height and most pornstars are tiny, as are most actors in general, making the dick look bigger). it's about the fact that when a guy looks for a serious long term breeding partner, which is where all healthy \textbf{sexual} attraction comes from, btw, the other-people-fucking complicates a few key tenants. we are attracted to others based off general health, specific \textbf{sexual} organ health, \textbf{mental} state of the partner and other things that are specifically easily negatively affected and/or changed by sleeping with other people. also semen has the effect of blocking other people's semen from impregnating, and we subconciously know this so the idea of someone else having \textbf{sex} with your partner gives the impression that it's going to be harder to impregnate them (regardless of the facts which may to be the contrary due to things like "pulling out" or condoms... you can blame millions of years of successful breeding and evolution vs a few hundred of condom use for that one), which is less attractive. finally, and i think this might be most important for many as we've essentially slowed down the reproduction process down from "grab her and fuck her if you like her, hopefully you don't get killed trying" to the full on flirting, dating, engagement, marriage etc is that men don't want to feel that that they could lose all invested time and effort spent on romantically wooing a \textbf{woman} and creating a positive relationship due to her essentially losing interest or running off with another man on a fling (extra negative points if the dude's actually bad/worse for her since stupidity is extremely unnatractive) so that risk, and the seeming idiocy of chasing multiple dudes is a huge turnoff, even if it's just fucking for money (maybe worse if it's \textbf{sex} work since generally \textbf{sex} work carries all of these implications AUTOMATICALLY, so it doesn't do anyone any favours). so, ladies, you can btfo with that whole "it's cuz someone else's dick was bigger", we all know it's because we want women that are good for us, and good to themselves, and everyone knows porn is terrible for everyone ;)\normalsize   & \cellcolor{green!27}Mental, Sex, Sexual, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/381 & \cellcolor{green!27}1.837 \\  \hline
  \cellcolor{green!5}\small Zero in the brain\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Any man with even a tiny amount of \textbf{common} sense knows better than to date a whore, be it a stripper a prostitute porn star or just straight up slut.  If a girl values orgasm and a some easy money over real love, family, security, loyalty and most of all, being a good mother, then she is not to be taken seriously.  Sexy is not everything.  My mom cheated on my father, slept around like a dog and always put her lovers over her children.  Now two of her sons have disowned her and the other one is doing 35 to life for murder.  You want to tell yourself morality and \textbf{common} decency are phony \textbf{old} fashioned superstitions, fine.  Just wait and see dear.  Where will you be when your youthful beauty fades?  The loyal wife and mother will have a family around her who love her and honor her.  The whore can cherish her memories of sucking dick.  The choice is yours.  It is not religious for me, it is \textbf{common} sense.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}4/173 & \cellcolor{green!27}2.312 \\  \hline
  \cellcolor{green!5}\small Elle Belle Try say the same thing about almost anything else, and you'll hear how stupid it sounds: "well if you agree to buy a car, then you can't turn around and say 'I don't like this car'." No matter what you apply that statement to... it just sounds \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small ksee yen. I bet the reason why she cant keep a man. Is because when he wants \textbf{sex}. She say's geesh I just got off work. I dont want to be bothered with \textbf{sex} or anything to do with \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/40 & \cellcolor{green!27}7.5 \\  \hline
  \cellcolor{green!5}\small Its ALWAYS the mens fault!!!If a \textbf{woman} makes good choices and ends up successful SHE tells the world about how SHE made it!However if a \textbf{woman} makes bad choices and fails in life its because of MEN!!.........ALWAYS!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Liber 8 u \textbf{dumb} right?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Some if you people have a problem with comprehension skills, I swear.She did not say 'it's always the guys fault', she is saying that the nature of her job by default creates a toxic relationship.She could be dating a girl and the outcome could be the same.And yes, if you date a porn star, you better be cool about her job.  It isn't as if you weren't aware of what you were getting into.It has \textbf{nothing} to do with them 'not owning up to their shit' and everything to do with you taking taking the leap before taking a closer look at what you are jumping into.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/111 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small David Cerino there's \textbf{nothing} comprehensive about it and the career doesn't make the relationship toxic,it's her " idgaf just support me no matter what or else walk away" attitude that riles up egos between the two and makes the relationship toxic\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Yes you're right, she didn't ACTUALLY SAY that 'its always the guys fault!'But that is what she was IMPLYING!!She was doing what women do EVERY DAY.Mocking men but at the same time trying to pretend that they're not.She even spoke with a stupid voice when pretending to be a man 0:48 'but I'm not that guy'Because obviously ALL men talk like they're \textbf{DUMB} don't they!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small TresTilo He's saying the truth. He even complained that they made men look \textbf{dumb} by talking like an idiot.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Lots of money, people in our society will kill each other over it. So what's \textbf{sex} if you make alot of cash.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small because it is easy to sell \textbf{pussy} than penis\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small she could still be smart and "fucked up". a lot of these girls come from broken homes or have had some kind of abuse as a child, either \textbf{sexual} , \textbf{mental} , or physical.\normalsize   & \cellcolor{green!5}Mental, Sexual & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small  [LINK]  - Porn stars have higher self-esteem \& spirituality than the average \textbf{woman}, despite stereotypes. \& I can definitely believe that too, as I've seen quite a few porn stars interviewed, \& they always sound confident \& well put together. I think the damaged goods stereotype more belongs to hookers with drug addictions, not porn stars.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Your vag gets wrecked by child birth, not \textbf{sex}. A women who's fucking just 1 guy could easily be having more \textbf{sex} than someone who's fucking hundreds of guys. What I mean by that, in case you haven't already worked it out, is that a \textbf{woman} with 1 \textbf{sexual} partner could be having \textbf{sex} with that partner every day of the year, while a porn star could be fucking a different guy every week, but she might only be fucking a couple of times a week.\normalsize   & \cellcolor{green!5}Sex, Sexual, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}5/86 & \cellcolor{green!5}5.814 \\  \hline
  \cellcolor{green!27}\small You know where I like it... you need to be confident if u do fucking live sex\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small  [LINK]  Wrong! \& just think about what you're saying. If you, as a man, were offered really good money for having \textbf{sex} \& you took it, does that suddenly mean you're damaged \& unstable? Of course not. Women love \textbf{sex} too. In fact, studies have proven, by measuring endorphin \& oxytocin levels, that women, on average, receive twice as much pleasure from \textbf{sex} than men do. So think about how good \textbf{sex} feels to you, now think about that pleasure doubled.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/81 & \cellcolor{green!5}4.938 \\  \hline
  \cellcolor{green!27}\small Additionally, porn actresses were more likely to have had a problem with \textbf{alcohol} and to report having used 10 different types of drugs in their lifetime.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small She will be a \textbf{crazy}, heavy drinking, toothless crack whore .That's how they all end up .\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Father LeoJust because you have different values in life, doesn't mean that you are being stupid. If you're a person who like \textbf{sex}, money and doesn't give a fuck about strangers masturbating to you. Then there you go.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Ali Rafatjah because \textbf{sex} is fun and she's obviously confident with her sexuality and has no American brainwashed hang ups. (Foreign girls rule)\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Ali Rafatjah well imagine a sittuation that some girl offers you to have a full night \textbf{sex} with her and in the morning she will pay you 1000 dollar....it,s hard to refuse such suggestion !\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Christian Fox being judgmental is a necessary biological, evolutionary, survival skill... if you don't have it, you wont last long. You \textbf{dumb} fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Easy money, plus she gets to fuck the girls too. Pornstar Bobbi Starr got into the business so she can have \textbf{sex} with Women.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small look at other regular actresses/actor in the movies or tv there married but they have \textbf{sex} scenes all the time! perhaps thats why there is such a high divorce rate in hollywood. that is the only profession you can cheat on your spouse and get away with it, why?? because they call it acting.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Robert Shupinski they dont have \textbf{sex} in movies but are u an actress? Im filming a movie and maybe we can change that\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Porn is like a cult in some way's.I am a jeweler i have made jewelry for several Porn Star's and director's.I got to see inside and how people are treated how they think.If they get then young 18 they program them.I have met a few PS that have a good head and are sharp,but for everyone of them there is a ton who are just fuck puppets for evil \textbf{old} dude's and foreign Russian dudes.I did get my brains fucked out at a party in the valley by PS they wore me out but no way could i do that everyday.I love the \textbf{woman} of Porn and wish them well.\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/110 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Men don't want a stretched out \textbf{pussy}. Or worries of getting HIV.  Good luck dating\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Your time will come.. make your money set your future up well ie any investments or businesses ect then later in life your be able to cut out the full \textbf{sex} part and earn money from the other parts\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small What guy wants to date a porcupine? If she had as many sticking out of her as she's had stuck in her she'd look just like a porcupine and no guy in his right mind wants to date one. They know that's what a \textbf{hooker} is going in when they solicit her but that's not dating.\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small My mate took a massive shit in the supermarket, down the frozen food isle I believe, he was drunk and high... He is now always complaining that no \textbf{woman} would date him, or fuck him... No \textbf{woman}  wants to be known as the \textbf{woman} who dates "Mr I'll shit in the supermarket"... So the morale of the story here people is, "Shitting or fucking is a private thing which you do either alone or either with somebody else" I say with somebody else because I believe Germans are into the whole "Pooping is sexy".........\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/94 & \cellcolor{green!5}3.191 \\  \hline
  \cellcolor{green!27}\small Ya its not the number of the dicks u suck u \textbf{bimbo}, its the  myriad of stds u carry that is turning people away.\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small so many negative comments,    Dani is the hottest \textbf{woman} willing to sport a natural bush in the business atleast. Best bush in the business basically.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Nothing wrong with her nose.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Pretty girl. However, I would still have a fear of disease. Plus the stigma of being involved with that type of \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small yeah man dont like to have a gf who fucks 100s of guys because they are insecure about how big other dicks are ,..yeah right....okey...another example of how \textbf{woman} make it all the man's fault...maybe they just dont want a whore as a girlfriend ? never thought about that ?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small As a asian male, i am so curious to about white women and \textbf{black} women.  Never had them in my lifetime lol, just plenty of other asian's.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Your much better off with what you have.  I lived in Asia for a little over two years, and was with many Asian women....they are far superior \textbf{sexual} partners.  For the most part, they are more open and willing to be adventurous.  They don't typically have many of the hang-ups Western women have, and they tend to want to please their men.  Far too many Western women think they are doing you a favor by granting you access to their "Golden vagina."  Western women also learn very early to use \textbf{sex} as a weapon against men in their relationships.  The grass is not greener on this side of the fence!\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/110 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small she's worried about her boyfriend cheating on her and having \textbf{sex} with someone else?........wait, DUH FUCK!!!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small thank you so much Dani Daniels for giving us this fascinating insider view into the industry .. i would love to be her partner (bf), it would also be a great opportunity to overcome deeply hidden insecurity .. toward men who are superior to us, speaking of their masculinity, testosterone, endowment, \textbf{sexual} functioning and performance .. i didnt know that partners of porn stars have to get tested all the time too .. but it's good to oblige with that without objecting or being fussy about it ..\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small someone667 Men love to look at naked women. \textbf{Nothing} will ever change that. Deal with it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small dating this \textbf{chick} is fine...and a live in too...but imagine being literally married to a pornstar ...man that's a tough ask ...!! one good thing about such arrangements could be like hey tonite I'm gonna give you an anal surprise or a cool bukkake :) in lieu of the diamond ring you bought me :) but this again could be a fantasy as everyday life is banal generally...\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small nah i don't mind that she \textbf{sex} with many different guys.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Starting off, I'm not sure I'd be okay with someone who has \textbf{sex} for a living. That said, I think it comes down to maturity. You have to understand the difference between fucking and making love.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Who is that pornstar, 'Who can fullfiled his fantasy besides of \textbf{sex}, With proudly, with easily, without prostetingg( like sining on a stage, Work for charity, Playing a charity match, especially compleating their study, live with their family with proudly always)?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Dani is real cool chick\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small What a lowlife degenarate you must be to be a couple with a pornstar, if dating means fucking than yes I would fuck the shit out of this stupid cunts but if dating means having a love relationship. Every serious relation should be be \textbf{woman} who could be potential mother to my children and you surely dont want a whore and a piece of shits who gets fucked infront of a camera(even if it was just once) as a mum, daughter or wife.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small If she has \textbf{sex} outside of a set, that is considered cheating.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small No, because she is a \textbf{woman} in feminist land\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small If you say your partner can have \textbf{sex} with another person and they do it. It's not cheating. Cheating is a breach of a partners trust.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I mean, it's real \textbf{sex}, but it's a fake scenario.It's not like she's sneaking around with the neighbor.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Gaetano Giacalone this has \textbf{nothing} to do with feminism.But it certainly shows how primitive your mindset is.If a guy dates a porn star, we can agree that it is blatantly understood that he will witness his girl have multiple \textbf{sex} with plenty of other men, including better endowed specimens.If the guy has his feelings hurt, that's on him.  It is not as if he was not aware of her profession.If he thought he could handle it and he later realized it was too much for him to handle, well, live and learn.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small The fact is that no matter how you justify it , this is still fucking a bunch of other guys or/and girls . This is tremendous psychological pain inflicted to their boy/girlfriends . I mean how will you get comfortable with your girl/boy if you know that she/he has fucked 6 different person before you , and is probably tired and not even invested in the act .I would date her if it's only for \textbf{sex} but I would never do something serious or commit myself to her .David Cerino is right tho , If you accepted to date her don't complain about that after , she didn't hide anything from you .\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}\small I have no problem dating someone who was a pornstar, especially, under the again of 25 (I wouldn't consider that any different than a "normal" girlfriend, But cannot date a active pornstar (unless under special circumstances, like Mia Kahlifa, who had less \textbf{sex} partners than I have.).\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small I just saw that she's married.... to a pudgy \textbf{bald} guy who looks 60.\normalsize   & \cellcolor{green!5}Bald & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Yea... at his \textbf{age} he no longer cared, so long as he got to bang a young \textbf{chick} every night.  Twisted marriage.\normalsize   & \cellcolor{green!27}Age, Chick & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small A \textbf{common} \textbf{sex} currency in America is the land of animals without borders .... Thank you America I  suddenly become an animal  WOOW !\normalsize   & \cellcolor{green!5}Common, Sex & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Very good interview.  It's not like the other porn star interviews.   The other ones are just covering the \textbf{sex} and not the lifestyle.   I'm more interested in how it effects someone's life.  If I was horns I'd just watch porn or have \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small No real man want \textbf{hooker} to be mom for his kids you are just meat for \textbf{sex} abuse.\normalsize   & \cellcolor{green!5}Hooker, Sex & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Love her \textbf{Lesbian} ass licking scenes\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Sunil Mishra ....you sound like a street hooker\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I liked this interview with Dani Daniels. She was asked a really thought provoking question. Daniels answer was so open-ened and honest. I guess those are some of the challenges for dating performer. I thought some of the jealousy Daniels mentions was based on \textbf{nothing} more than insecurity. i mean her past dates probably failed to realize that she is has a personal relationship with them unlike her co-worker performers. The \textbf{sex} she has with other porn performers isn't based on meaningful love. Dani Daniels is willing to love someone otherwise she wouldn't be trying to form personal relationship with "civilians" as she calls them.\normalsize   & \cellcolor{green!27}Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small Get tested ? what a fucking joker, the ' industry ' doesn't even test for herpes ! And she's ugly too but talks likes she's God's gift to \textbf{sex} , LOL !\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small God she sounds like a \textbf{libtard}.\normalsize   & \cellcolor{green!27}Libtard & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small the funny thing is that she talks as if it's the guys problem in a relationship. when her biological value falls when she hits 35 she'll realize the men only want her for sex\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Marriage before sex\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small exactly, who wants a \textbf{woman} that sucks, fucks and swallows cum for a living?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Pshh pornstar Karmen karma retired because she got married and she now is back making money on her only fans acct having \textbf{sex} and constantly tweeting about craving for other guys. As a man you'd have to be pitiful. Her husband works for the service and let a pornstar smash on camera. Sad\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Chuck Taylor the place where im from \textbf{sex} around is not that \textbf{common} ! Not everyone are as filthy about \textbf{sex} like west\normalsize   & \cellcolor{green!5}Common, Sex & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}3/23 & \cellcolor{green!5}13.043 \\  \hline
  \cellcolor{green!27}\small The kind that lives only for \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Pshh, her husband can never love her. Probably only worships her \textbf{sex} skills\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small How normal is have \textbf{sex} with different men everyday normal.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small God damn she is so fine. I beat off to her hairy \textbf{pussy} all the time.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The problem that many man have in dating a porn actress is that they still have a machismo attitude, treating women as their exclusive property and reducing them to an object in their hands.That`s why relationships should always be open, to allow both partners to date and have \textbf{sex} (if they want it, of course) with other people outside their relation. True love means to understand and respect the partners feelings and needs, instead of imposing a monogamous relation, without even caring if that`s what really makes the partner happy.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small Get the fuck out of here with that hippie free love bullshit. I would stay loyal to my \textbf{woman} and expect her to be loyal to me. That's the essence of a true relationship, it's intimate and exclusive. It's jealous and possessive. That's real love.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small I could date her. I just would't have any real affection for her. She would be like having a favorite seat on a bus. As long as I enjoy the ride it's all good. She accurately describes living a porn life and trying to have a normal life with the same people she is living a porn life with. (Of course she is limited to them because or the porn life she is living) Of course it would e no different for her if she dated (could date) outside the porn industry. Except for men like me. But just when she thought she found true love and acceptance I would step back and let her know that she was just a fuck puppet to me. \textbf{Nothing} she isn't used to being anyway.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small Tiara Le'que  You are quite correct except for identifying  what I said as "opinion." Allow me to explain. Everyone is in fact looking for love and genuine affection.  But what we are engaging in is fun, recreation, and instant gratification. Women are the biggest targets and victims of this. Only as long as you get what you want you don't see it, or just dismiss it because your so caught up in the euphoria of self indulgence. Women more so than men don't see themselves as what they sincerely are in modern day relationships. They are fuck puppets, playthings, cum receptacles, \textbf{sex} toys, etc, etc. it is because that is what they want to be. Which is their choice and I am not issuing reprimand to women for that. It is their right to exercise their free will as they please.  Women in their view of female empowerment and independence proudly engage in this lifestyle  \textbf{blind} to its reality. This is inclusive of serial affairs, long term relationships, boyfriends, hook ups, booty calls, one night stands, any relationship structure you can name. Including marriage. I'm not trying to define all relationships this way. However I  being honest in my observation, women for the most part have surrendered themselves to living as though they are \textbf{nothing} more than a mound of flesh with an expiration date. As well they foolishly believe that they have somehow reversed the roles where they are now choosing the men and men are lucky to be chosen. Then we get to the eventual desire for the substance of a relationship.  Love, a partnership, and a life together. In reality, there is no love in the life we are living today. That is why this hurts women more so than it could ever hurt men. What makes you think you are going to find love when you began having \textbf{sex} at 15 and by the time your thirty your in double digits with the number of dicks that have been in you? You may... I'm not ruling it out, but how do you think think you can now determine what is special?That brings us to my previous comment.  I sincerely don't hold any animosity to the girl in the video, or women at all. But I recognize that women have a different view of themselves than what the present as who they want to be perceived as. If not to all then in general as to themselves as a \textbf{woman}  They have to in order to live the way they do without revealing themselves as porn stars like the girl in the video. You cannot honestly say you want love, partnership and a life together with someone when you're throwing everything you would have for that someone out to someone else, or many others. You can't by reason but despite what would be reason the vast majority of women are. I used to think  I should respect women a great deal and many times I believed I was meeting someone special. Only to discover that more often, in fact always, the women were just like the \textbf{woman} in this video. There just wasn't a camera on them when they did it. The wanted me to see them differently because I was not the "bad boy" or "type"  they were willing to reveal themselves in this manner to. However for whatever their motivation I wasn't written out of their lives completely. (I still like the girls whom did write me off) but now seeing women for who are what they really are, much like the girl in this video, I see no reason to have all that respect for them since from my perspective they have no self respect anyway. Thus now instead of thinking, about the possibility of getting to know her and building a relationship I immediately rule that out. I see women as the fuck puppets they deliver themselves as. Other than my view of women I have not changed from the man I was when I held women in higher regard.  So women might draw  a distinction between me and another "type" or a "bad boy" thinking that they'll reserve me for friendship or the later possibility of a relationship. I instead think.. I would date her but I have no interest in love. She is a fuck puppet to me , just as she has chosen to be to so many others anyway. So it's not with hatred or dismissing her humanity that I made that remark. It is with education as to the world I now live in. I know this was long but I hope it provides some clarity.\normalsize   & \cellcolor{green!5}Blind, Nothing, Sex, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/779 & \cellcolor{green!5}0.77 \\  \hline
  \cellcolor{green!27}\small \@Tiara Le'que You are correct in viewing my perspective as not being fair. It is not meant to be. I have that perspective given the current nature of relationships in order to be fair to myself. I see that as the only effective way to insure my own success and level of comfort. However let me try to clarify what you continue to state as my "opinion."If I were to make an observation of teenage girls today vs an observation of their grandmother or great grandmother as teens those observations in general would be drastically different. Just the term "spreading your legs" would be extremely offensive to previous generations of young teens. I'm not stating young girls are bad. However being on birth control before you can come home after dark, having a supply of condoms in your purse "just in case," and having a boyfriend almost non stop from 15 on is an incredible distinction from aforementioned generations. Being so different it also establishes a different overall perspective of you. That is what I am acknowledging. I am not judging it. I am just acknowledging the status we live in now. Perhaps young teen girls would find that being described as their great-grandmother as a teen to be more favorable than to be described as they are now. But that observation doesn't get assigned to you just because you are a female and it's more flattering. We are what we are and it is what it is. I am not offering an opinion on it of any kind. I am just acknowledging... observing and articulating what is before me to see. Of course I understand that women have the same perspective of men that I have of women. That is exactly what I am addressing when I state that relationships now are based on \textbf{sexual} recreation, fantasy fulfillment, immediate gratification and etc. With Tinder, and the match up sites, the phenomenal success of the "bad boy" with even professional women. What you have acknowledged with that question and observation is some of the proof that what I have stated is fact... not opinion.Perhaps I need to be more clear. I am not saying that women are fuck puppets. I am stating that in our time relationships sexually based. Built on the desire to satiate a \textbf{sexual} craving, fantasy, immediate gratification, perverse desire, anything but a real bond, a purpose other than \textbf{sexual} gratification. Thus women are fuck puppets in the structure of the relationship. This is something that is hard to accept as I am certain it is not the desired position or status a \textbf{woman} wants. However she does not have to embrace this title to be the definition of one. If she participates in this she is one within the structure whether or not she accepts the title. It's like being no. 55 at the registry of motor vehicles. You are not Tiara Le'que in the registry. That is who you know yourself as but in that registry you are no. 55. You are no.55 no matter how you wish to see it and you will be no.55 until you are no longer participating in events at the registry. I am not defining women as or appointing women the title of "fuck puppets." What I am saying is that if someone changes that title to "girlfriend," "booty call," "wife." "hook-up," or any other title and you fulfill that role then that is what your are in that relationship because that is the role you are playing. I don't know how to answer you about your relationship that ended. Let me use my own words to repeat to you what you just told me. You said that you had a relationship (dating) with a guy whom you were sexually involved with. (Not stated but implied in your last line) Perhaps you always saw him as a perspective life partner (can't tell from what you stated) but certainly after some time you did. You then expressed yourself to him. Upon doing this your discovered his sentiments were quite inconsistent with yours. Would it be unreasonable to say his perspective of being with you was the exact opposite? I am going to say this.. and I sincerely hope you understand that I am being completely objective and I hope establishing a prerequisite for my comment allows you to forgive any offense. You did not choose to be a fuck puppet. However you fulfilled the role of one. According to you... you entered a relationship that had no other purpose than for \textbf{sexual} gratification. Even if it was not your intent, clearly it was his. The evidence of that is how your relationship ended. Please if you disagree then tell me what the educated you through this experience can salvage from this relationship to define it otherwise. When I use the term "fuck puppet" it is not to insult women. It's not pleasant I admit, but it is to identify the role not to insult anyone, Dani Daniels embraces her role as a fuck puppet. (at least as she appears to the general public)  Like I said to you earlier, if you fill that role, that is what you are. Like if you get a job as a bus driver, then you are a bus driver. Not being flattered by the title you may say..."I have a job driving a bus, but I am not a bus driver, that's what I do not who I am." However as long as you fulfill that role, like it or not, you are a bus driver. There are women who embrace that role of fuck puppet not because they acknowledge the title/role but because of the euphoria or what they are doing and/or who they are with. Those are the women who chose to be fuck puppets even if they don't acknowledge the role/title. But I mean no inset to them either. I am not ruling out men. It just doesn't have the same effect on men as it does women. Men don;t want to date a girl after someone else. They don't want "sloppy seconds" or to "clean up" after their friends or rival for your affections. If a man is willing to date you knowing he's the follow up guy he is likely just looking to get his turn at bat. I have been a man all my life, I know this is indisputable truth. On constrast I have seen women all my life all take turns dating the same guy. Even if a boyfriend cheats on a girls best friend with her she'll still date him. Then he'll do the same thing to her with her new best friend and the new best friend will date him. Women have a different perspective of men altogether than men have of women, That is why i said earlier this hurts women more then men. If women are or were fuck puppets for the most part they have to deceive men into believing they never were. Men can run right into home plate (marriage) celebrating all his conquest. That is because women accept it, not because it's different when a man does it. I know not every one is focused on being fuck puppets. But it does not matter what you desire to be if you fall into or willingly step into that role. If you fulfill it, that is what you are. I for one admit that I now wish to be a \textbf{woman}'s fuck puppet rather than seek a relationship I have stated why in previous comment to you. I was once what it appears that you wanted the guy you were dating to be. I wasn't rejected because I did anything wrong or provide to be the wrong guy. I was rejected because I did not do anything wrong, I wasn't a bad boy, wasn't the "type." (Type: the ambiguous description to justify or deny without substance) This reply has been far more lengthier than any I have ever posted. It is because I don't want you to take the "fuck puppet" remark personally or with insult. I wanted to explain where I was coming from and you seem to understand that. A man won't say "fuck puppet" to you, it will obviously offend you if he did, But being a man all my life I can tell you ... If a man doesn't have to love you, have a life goal with you, and a purpose grater that \textbf{sexual} gratification ... he won't. Most of my life I did it wrong because it is clear that is not what women have wanted as long as I have been alive, I just have no desire to be the type of man (the bad boy) that women are so willing to be the \textbf{sexual} gratification for. But now I'm noticing that to young girls I can be myself and being older still hanging with the young make me a "bad boy' to them. Every \textbf{woman} in my life is a Dani Daniel. There just isn't enough of them.\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}8/1518 & \cellcolor{green!27}0.527 \\  \hline
  \cellcolor{green!5}\small \@Tiara Le'que You are not a fuck puppet. When you looking the mirror you are not a fuck puppet. You have a desire for something greater than to be a \textbf{sex} toy for someone. You express a greater interest for yourself than to present or establish yourself for recreational \textbf{sex}. But to a man who has no intention of having a relationship with you with mutual interest but engage in \textbf{sex} with you, to him, you are a fuck puppet. I have a question for you about that. In general or specifically to you... if you ginuely consciously have those goals/interest how do you end up having \textbf{sex} with a man whom does not? A fuck puppet is just a synonym for "whore" defined by (and I'll use the definition of the word in it's etymology, not the current dictionary definition)  a \textbf{woman} who has \textbf{sex} outside of marriage, [NOTE: etymology is a word derived from the Greek word ἐτυμολογία  meaning "true sense", and the suffix -logia, denoting "the study of". In linguistics, the term etymon is used to refer to a word or morpheme  from which a later word is derived. The word "whore" has been redefined so much that the original definition has been intentionally altered of lost. There was no male equivalent as the word was to specifically define a \textbf{woman} by her actions. Men who did the same were defined as "whore mongers" as they sought to engage a whore sexually.]You appear to understand me with but one exception. You think I define every \textbf{woman} or every \textbf{woman} who has \textbf{sex} a fuck puppet. Just like I defined "whore" I am defining what one is. If you fulfill that definition then that is what you are by that definition.  Whore is a real word with a history. It's not easy to find the etymology of a word but if you desire to confirm what I say you can. It goes further back than the German definition that will immediately come up in a google search. It dates all the way back to Biblical history. This is the best I could find in short research:  [LINK]  When I learned the history long ago it was in books. "Fuck Puppet" is slang, modern vernacular. But both words are descriptive to behavior. In other words they only apply if you fulfill their definition.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}10/395 & \cellcolor{green!5}2.532 \\  \hline
  \cellcolor{green!27}\small I'm sorry +Tiara Le'que sincerely, however no updates will be coming. When the truth is unpleasant it is impossible to say it in a pleasant manner. I sincerely never meant any insult, just observation.I believe women in general, or in \textbf{common} mindset of the conventional wisdom, visualize themselves as being no different than their great grandmothers or her mother before that with the only difference being that they are not restricted by codes of conduct forced upon them by men. The problem with their thinking is that women are not self evaluating. The result is that in their minds women create a persona they want us as men to see that is not who they are. At least Dani Daniels doesn't present a facade, but then that is because she cannot hide who she is.I understand the reason women don't recognize who they are. Dani Daniels explains it well. However not acknowledging it doesn't make it non existent. Ignoring reality only results in being crushed by it when the imaginary/facade cannot support you any longer. That is what happens to women when they, as you characterized it, get their insides ripped out by men. Men don't have the burden of needing to present a facade of who they are. Women welcome the worst men could be. Somehow in women's mind they can embrace the worst of a man and either turn him into the best or change themselves to find pleasure in the worst. Whatever, as I said to you before, women accept it therefore men are rewarded by it so they do it. Men have no desire of a male version of feminism because men have always be satisfied and rewarded well for being a man. Women want to be free to express themselves as women without consequence. Believe it or not I support that. GOD made \textbf{nothing} dirty. Including a \textbf{woman}'s body, it's appeal, and the \textbf{sexual} desire she has. All that is perverted by man. (the mind of mankind) So I am not critical a a \textbf{woman}'s desired \textbf{sex} life no matter what it is. My criticism is what women do in living a dual life with the pretense that it is not. One of fantasy, self indulgence and excess, the other substance. The problem is the fantasy, self indulgence and excess leaves \textbf{nothing} for the substance. Where it is perfectly okay for you to walk this path, by your own culpable and intelligent consciousness, it cannot be made into something other than what it is. Being what it is you have no more power to create a new reality for it than I do for any decision I make. Whether or not I am culpable, intelligent and conscious or not. So even if it is not your intent, it still is what it is. I spent too much time in the side of wanting to see things differently. I had a more palatable concept of the human female, that concept was formed by feminism. A concept that simply recreates and redefines women removing personal accountability from them. Keeping in relation to this discussion.... in feminism if you conduct yourself as a whore/fuck puppet you are not a whore/fuck puppet. How can you be a whore/fuck puppet and not be a whore/fuck puppet? Just don't accept THE definition of a whore/fuck puppet. Create a definition for yourself. The reason I abandoned that "respect" for women is because my experience taught me that women had no respect for it, or the men who respected them. Had they that respect then they would not, could not make the decisions they were making. It is also why I feel no guilt now having \textbf{sex} with women with absolutely no desire for a meaningful relationship, no interest in love and certainly no prospect for marriage. I am not alone, not even a minority. Look at all the videos on youtube under the subject that men are abandoning marriage. I think all the psychoanalysis is bullshit but it does reveal that men have lost interest in the substance of a relationship between a man and a \textbf{woman}. I think all their evaluation is pure psychobabble as to explain the reasons why. I believe the reason why is the very issue you and I have been discussing.Men have never wanted a whore/fuck puppet. Nowhere in history, no matter what era or culture you study do you see where whores, however defined for that time, were any thing of value to their society other than playthings, \textbf{sex} toys, \textbf{sex} slaves, or something of similar definition. That is whether they were chained, paid, or volunteered. In all honesty I do not know what the women of this era see or experience that makes them believe it will be any different for them. It's not like women were not sought for the substance of a relationship, its the whore/fuck puppet that was not. My concept of the human female has changed. It has changed from the the concept women (feminist) taught me to have to the one education and experience revealed to me. It will not change until education and experience provide a lesson that reveals what I have learned now is false. However when you consider that most of my life I have been rejected or offered affections only from women who believing no one else wanted them I was desperate for them to now I'm not even asking and women are coming to me. That's going to be a difficult task for education and experience deliver upon.\normalsize   & \cellcolor{green!27}Common, Nothing, Sex, Sexual, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General, Social Class - Working class & \cellcolor{green!27}9/926 & \cellcolor{green!27}0.972 \\  \hline
  \cellcolor{green!5}\small Tiara your question is difficult to understand. the reason I asked you how you would have \textbf{sex} with a man who is not interested in having a baby is because you stated that is what you were interested in. I wanted to see how you evaluated yourself when considering that.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small God you must really be batshit \textbf{crazy} to believe that crap about yourself. (Why is there always a "catch" with beautiful women?!) I don't mean to sound rude. It's none of my business, but did you have a drunken stepfather (or something) who said stuff like that to belittle you, growing up?? Un-fucking-real, the meanness in some people, if that's the case.And "small eyes" ..Are you being serious?! It's amazing the outlandish stuff we think about ourselves in private (I probably do the same). But Tiara, your eyes/face combo are perfectly proportionate with each other. I scrolled through every one of your GooglePlus shots, and never got that impression once. I actually had to read that sentence from you TWICE, to process it.Also, my telling you to "go away" was, of course, facetious (hence the wink ;)And "fuck puppet"...No. I am an educated, well-mannered 32 year-old adult male who has never looked at a \textbf{woman} like that in my entire life. Lustful with my eyes? Sure. (Can't say I didn't ogle your photo for a sec!) But physical appearance is only a small fraction of what I look at in a beautiful \textbf{woman}......And speaking of "beautiful," from what I can tell from your initial post here (in response to that shallow male heathen), you are jaw-dropping-ly beautiful on the inside as well. So stay away from assholes like that, and you'll do just fine in life.Wish you the best with yours! :)-Eric\normalsize   & \cellcolor{green!27}Crazy, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/248 & \cellcolor{green!27}1.21 \\  \hline
  \cellcolor{green!5}\small I apologize for my ignorance - I haven't read the OP's full explanation/justification (only his first post)...I got a little bit distracted by some sweet young and beautiful middle eastern girl ;)  ".....Focus, Eric!" (Lol)I can say it 100 times over (without you hearing me, Tiara) but I am not trying to be "kind" here. At all. I don't "front." In fact, I have been known to be a HUGE swinging DICK (like 12 inches!) to girls who I didn't find physically attractive (and I'm a tough judge). Although, I regret those days of being so cruel).But Jesus, \textbf{woman}! You look like a fucking SUPERmodel in the \textbf{black} \& white shot! You would be the first girl I asked to dance on a dance floor with 100-plus girls.Oh well, I guess our "reality" (as you called it) is whatever we tell ourselves it is. At the end of the day. Sadly.(You really do make me feel sad to know that that's what you actually believe, but i digress.)Btw, your English is AMAZING for it not being your 1st language!! Keep up the super cool work."No one gives a fuck if your a muslim Christian Jew or athiests or anything or even a FUCKING \textbf{FROG}."....This is perhaps the funnist thing I have read on the internet since 2016. (It seems you have a cheeky smartass WIT too. LOVE it!)And....wait a tick (as Austin Powers would say)...WHAAT video thread are we on here.....How did i even wind up on this video page?! Lol.Cheers, EricP.S. So is Tiara your real name? (I ask b/c i don't want to call you by a name that isn't truly yours, since I feel like i know you a little bit and it doesn't feel right.)Also, as a side note, I heard in a movie once (forget which one) where a guy tells the main character basically that it is advantageous for a man to date a beautiful \textbf{woman} [who doesn't realize how amazing she looks], because then she might LEAVE him! Haha. So true in Your case...I mean if i knew you in the "real" world" and ever asked you out. Hypothetically! (I think that line was from Shallow Hal).)Anyway, good night over there, wherever you are. Stay sunny ;)\normalsize   & \cellcolor{green!5}Black, Frog, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General, Nationality - French & \cellcolor{green!5}4/386 & \cellcolor{green!5}1.036 \\  \hline
  \cellcolor{green!27}\small \@Tiara Le'que No. I don't do aliases \& pose as as someone else. But I am glad you found yourself a "husband" on Youtube. Nice job giving your email away to a guy that has "American \textbf{Psycho} stalker" written all over him btw ;)Also, is it really so hard to believe that there are TWO guys on here who find you intensely attractive, my loca Tiara..?   -ericP.S. That sucks you live in Australia. My loss. Our loss.(I'm 32 btw. Jeez you're young. How creepy)\normalsize   & \cellcolor{green!27}Psycho & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small Ha, no stalking. I was curious about my doppelganger ("same person as me") so i followed your pointing finger to that other video. (I didn't watch your video though, as that would be stalking.)Speaking of stalking...an "internet purposes" email address, yes that is in fact how things work, my sweet \& silly comrade. But in your particular case, you prbly use that email address for stalking Brad Pitt or something! Or Paul Hogan? :PThe thing is, I'm not like that other poster ("DL"). You might be beautiful as fuck, but so what. Pretty girls are a dime a dozen. I need more than just pretty. A lot more ;)And yes, I meant "my \textbf{CRAZY} Tiara" but in a very endearing way (you just seem too damn lovable to use it in any other fashion. Curse of the Australian! Lovability.)And yes, you \& I both are getting older...and older....every day......Thanks for the icy cold reminder, Debbie Downer! Lol :)Sweet dreams, Aussie Tiara  -Eric\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/167 & \cellcolor{green!5}0.599 \\  \hline
  \cellcolor{green!27}\small \@Tiara Le'que...A funny "human" as opposed to a funny "martian" from Mars (my homeland). Haha I love your word choice, kooky Ti. Very unique! And it's relieving to know that my "human emulation" software's up to date (my \textbf{race} is usually a few "updates" behind the Venusians \& the Moon Men ;)And so \textbf{weird} how it's the opposite time of day up here in NYC as it is in the land Down Under (where you "supposedly" are....u r prbly really one of those "valley girls" from Los Angeles, California, but that won't make me adore you any less if that's the case, i promise :)  ..Btw you don't have to tell me your full name, but is your first name actually Tiara?P.S. I'm not talking any "husband" talk here (like our friend "DL"...."Down Low?" was), but if you're ever stateside, I would truly look forward to hanging out in a coffee shop with you on a sunny summer Saturday morning, just shooting the breeze. ...I'd even have the courtesy to cover up my pointy \textbf{alien} face with a human-looking mask, to make things more comfortable. For you, I would do that :)\normalsize   & \cellcolor{green!27}Alien, Race, Weird & \cellcolor{green!27}Ethnicity - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/195 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Haha no dingo is definitely not better! You crack me up. Anyway while I like the meaning behind the alias ("Star, Where are you?" which I have been wondering myself lately), I like Tawar much better and I think you should go by it always. I would. ...If my \textbf{gender} was different! (alien-assigned \textbf{gender}, of course ;)Dingo sexier than Tawar. You Aussies. All we need is one girl to make the name sexy.. ;)\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small Hey are you still alive, gorgeous? Lol, you dropped straight off the face of the earth and now it totally sucks that you're gone! Seriously, this planet just got totally \textbf{lame} again \& now I am thinking about returning back to mine. Am literally prepping the ship for launch as we speak.\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Amere Garsun Who would date a \textbf{chick} that probably has every known and unknown type of STDs.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small The fact is that no matter how you justify it , this is still fucking a bunch of other guys or/and girls . This is tremendous psychological pain inflicted to their boy/girlfriends . I mean how will you get comfortable with your girl/boy if you know that she/he has fucked 6 different person before you , and is probably tired and not even invested in the act .I would date her if it's only for \textbf{sex} but I would never do something serious or commit myself to her .\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small Stormbringer Completely agree. It may not be nice to say, but they're basically just prostitutes. Most men don't want a prostitute as a girlfriend. Imagine dating even an ex porn star. Every time you have \textbf{sex} you know other guys have pleasured her way better than you can, every time you kiss her you know she's been deepthroating dozens of guys. And even if you make it past that, and you marry her and have children, everyone you know can see your wife fucking other men on the internet. Your parents, your friends, your colleagues. Even your children. I wouldn't want to be the kid who finds out his mom was a whore. Imagine the bullying they'd go through.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/119 & \cellcolor{green!5}0.84 \\  \hline
  \cellcolor{green!27}\small Jon Snow you know \textbf{nothing} Jon snow\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Of course it doesn't work. \textbf{Sex} is suppose to be something personal, intimate, emotional, and all that shit. How could you say, "When I have \textbf{sex} with this guy it's just my job, but when I have \textbf{sex} with this guy it means something"? Feelings don't have an on and off switch. Knowing someone intimately is one of the cool things about a relationship. Like she/he could have chosen anyone, but they chose me. That's not something you want to share with anyone else while you're seeing that person. If you go out and sleep with all these other people, what exactly makes this an exclusive or committed relationship?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/109 & \cellcolor{green!5}2.752 \\  \hline
  \cellcolor{green!27}\small Nothing. Porn stars and all other prostitutes  have to have an "open relationship" or none at all.  Then the main relationship is distinguished by the amount of time spent working on it and in it  vs. the little time, usually only a few hours a day spent strictly whoring their body for money in \textbf{sexual} acts. Just screwing a person, even if it's John Holmes with a 14 inch schlong as thick as a beer can around, does not constitute a deep relationship, no matter how much better he can pound it senseless than the average dude with a 5 or 6 inch pecker.  The problem is that most dudes don't know how to operate their equipment well or nowhere near THAT well and feel threatened since most dudes don't have much going on in the "relationship" department either. If the relationship was deep enough then regular fugging might be "as good" as being plowed by a man-horse. Otherwise, few guys are secure enough to risk a 10 inch or longer dick possibly making them look like total amateurs and stealing every last women from them without the stud ever having to speak more than a few sentences. Just his dick alone speaks volumes for him while the regular guy's dick is a short story and needs lots of outside embellishments in terms of "quality time" spent together to measure up.\normalsize   & \cellcolor{green!27}Nothing, Sexual & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/231 & \cellcolor{green!27}0.866 \\  \hline
  \cellcolor{green!5}\small The \textbf{sex} between porn star on set only last up to 20 to 30 min...it looks like it last long but it doesn't.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@CallingVain: it's actually your comment who is ridiculous. I've met some basic people who would proudly explain how having \textbf{sex} is not different from taking a dump.... well it is completely different. What happens in your brain and body is completely different. Whether you like it or not, when two people have \textbf{sex}, they release all kinds of hormones.... one of them being oxytocin, aka the "bonding hormone". So "intimacy", "bonding" are not some christian and/or female bullshit to sugarcoat \textbf{sex} (because I know that's the way you see it).... it's actually biology.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/93 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small louloutre \textbf{sex} is only special if it happens with someone special. Out of the 30+ girls I've banged it has only been special with two.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small That's love, but within us all we have that urge to just fuck. \textbf{Sex} with someone you love is something personal. \textbf{Sex} with just a random person, is a carnal appetite that sometimes needs to be done to get it out of your system.That's why people cheat. And that's also why people don't cheat.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small CavemanJesus4Life So u justifying cheaters just because of the fact that they have the "need" of having \textbf{sex}? which first of all is not a need but rather an option, some people might feel better because of drinking or doping emselves while others would probably feel better just by having \textbf{sex} with random people. As you can see, none of the options above leads into a good future result, nor for the person doing it or the other ones which are related or involved.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Max are you married? If not you have no idea what yer talking about. One night your wife can want you badly and the next she is just hoping you pop fast and get off her. So \textbf{sex} is ALWAYS a state of mind, no matter who or when you are having it (for women). Men, doesn't matter to most. Men have a problem connecting with their emotions so very rarely does a guy connect with a \textbf{woman} on that level sexually. But when you do the \textbf{sex} is the most amazing you ever had.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/95 & \cellcolor{green!27}3.158 \\  \hline
  \cellcolor{green!5}\small MaxCovington543 says who ? I don't see \textbf{sex} as something personal or intimate even worst emotional, I use \textbf{sex} as a means to satisfy my urges. There are all kinds of people, the fact that they see things different than you, doesn't mean you're right nor doesn't mean they are wrong.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small MaxCovington543 she sounds like a complete psychopath. All those strippers, porn stars are fucked up in the head. They can't be wives, they're not special women. They're either women who were raped as kids or had a traumatic childhood. \textbf{Nothing} special about them. There just OBJECTS of society.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small For the idiots here, that cannot think a bit and grew up in a world, where \textbf{sexual} liberation is supposed to be something good. You are all sheep btw. Have fun banging 30 women, hurt their feelings afterwards and reduce something special to a mere pleasure of the body. [LINK] \normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small MaxCovington543 lol, just treat \textbf{sex} as a hobby lmao, the rest just works its self out 😂\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small MaxCovington543 you can be intimate with someone without having sex\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small louloutre again, you can be intimate without having \textbf{sex}And you can have \textbf{sex} without being intimate because it's a all in your head so your actually ALL wrong AND right\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Gunslinger SyayoRPG/CRPG how \textbf{old} are you\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small itsjuank Separating intimacy from \textbf{sex} is like disconnecting health from food. Just like people who eat fast food for the quick high the \textbf{promiscuous} people go for the fast fuck, the cheap high. \textbf{Nothing} positive ever comes from addictive behavior instead you will destroy your life.\normalsize   & \cellcolor{green!27}Nothing, Promiscuous, Sex & \cellcolor{green!27}Age - Youngsters, Gender - Female sexuality, Gender - General & \cellcolor{green!27}3/46 & \cellcolor{green!27}6.522 \\  \hline
  \cellcolor{green!5}\small \@CallingVain : It's not that obvious to me. Porn is a selfish pleasure.... it's a rapid and simple way to satisfy a need, but you don't exchange fluids with anybody. Let me clarify what I've said. Young men have a strong urge to impregnate the maximum of women, so depending on their personality, they can have \textbf{sex} with little bonding.... that's true for teenage boys and boys in college. After that, most men look for intimacy more than just \textbf{sex}. As for women, they are biologically designed to bond with their \textbf{sexual} partner. That's why women have a very hard time sleeping with a lot of partners, and that's why female pornstars and prostitutes end up broken and mentally unstable. In spite of what feminists say, women don't care about \textbf{sex} for itself. They use \textbf{sex} to an end, which is finding a partner.\normalsize   & \cellcolor{green!5}Sex, Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}5/144 & \cellcolor{green!5}3.472 \\  \hline
  \cellcolor{green!27}\small metamorphosis67 your comment is a little fucked up. at no point do you even acknowledge something like "feelings". the way you describe relationships makes me feel like I need to be successful so my parents will love me. that's not how the world works, that's not how any of this works. and porn stars fuck up their relationships because they share the most intimate, private thing possible with lots of strangers. \textbf{sex} is also a way to express your love for someone. that's impossible for a pornstar.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small CallingVain Yes, of course people can have \textbf{sex} for emotional reasons and also due to lust. It starts being a problem when you have both, emotional valuable \textbf{sex} with your partner and purely physical fucking with the next door neighbour at the same time. that's called cheating and I'm pretty sure 99,9 of people aren't ok with that (and I don't even think monogamy is a cultural thing tbh; I also doubt most of the cucks out there who claim that they are ok with their partner sleeping around while sounding like they are already suicidal). the problem with this pornstar is that she won't acknowledge that she fucked up any chance of her having a meaningful relationship because of her "history online" and kinda scapegoats society for her own actions and decisions in the past and present. she chose that life. it's no use calling men "insecure" now.Why do we fuck for pleasure?Because fucking is pleasure. that's basic biology. as long as you can get a dompamine rush from it, people will always do it for pleasure. however, being in a relationship with someone is something that clearly distinguishes a person from the rest of society and what better way to distinguish them by reserving the most intimate activity a human can have for that person?Why we have porn?Hormones. We can't help ourselves.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/228 & \cellcolor{green!5}0.877 \\  \hline
  \cellcolor{green!27}\small I didn't know the \textbf{chick} from Life With Derek was a porn star.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Porn is just a job. There needs to be porn education teaching children that porn can be as addictive as drugs. I am not against the \textbf{sex} industry because it helps with \textbf{sexual} frustration of men. Rape crimes are likely to be lower in countries where prostitution and porn are legal. Please educate children about porn as much as you teach them about \textbf{alcohol}, cigarettes, drugs and \textbf{sex}.\normalsize   & \cellcolor{green!5}Sex, Sexual, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Gender - General & \cellcolor{green!5}4/68 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Puglous Oh come on. I won't deny that porn is a useful valve for society, but don't act like she is some virtuous hero who does this out of love for humanity. She's probably in porn because she's too incompetent for most other jobs that would pay equally. She's in it for the money. I'd rather respect \textbf{doctors} in public hospitals, teachers in public schools, soldiers, policemen, fire fighters,...\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Why the hell would anyone in LA date this \textbf{chick}. She's average looking in this city and she fucks for a living. There are plenty of hotter, single, non-porn star girls around here that can probably do everything she does just as well.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Andrea Andrews Thanks DEAR!    Good men aren't interested in "dating" such Trollops, they KNOW THERE IS NO FUTURE with her kind!   Even IF the \textbf{sex} was good- she's probably "faking it!"😂🤣😁😉\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Pedro Viteri. Which country will start WWIII? When will the super volcano at \textbf{Y\textbf{e\textbf{llow}}} Stone National park erupt? When will the government release the vaccine for libtardism?\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/27 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I knew she wasn't \textbf{lesbian} or even bi when she was doing \textbf{lesbian} porn. It was just \textbf{g\textbf{ay}} for pay. Now she's doing what she loves, and that's GUYS.\normalsize   & \cellcolor{green!27}Gay, Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/29 & \cellcolor{green!27}13.793 \\  \hline
  \cellcolor{green!5}\small You need to take a sip of this brah are you fucking kiding me... read my statment and what you wrote in return, and where from hell this religious bullshit just came in.. y the hell you are soo freaking out and referring  religious books stay to the subject nd if u cant handle the truth just keep your yap shut up!! how i got onto this video is not your fucking concerned nd believe it or not i do watch porn .. y should i care do u fuckin care what bible says... 80 of \textbf{w\textbf{hite trash}} believes in same \textbf{sex} marriages nd eat pork does bible says to go do that neither of  religion... DONT SAY WHAT YOU CANT HANDLE.\normalsize   & \cellcolor{green!5}Sex, White Trash & \cellcolor{green!5}Ethnicity - White, Gender - General, Social Class - Working class & \cellcolor{green!5}3/123 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small You need to take a sip of this brah God u r such a waste...cant see straight... what she had done to the socity is worst than a bomb more than a genocide is called slow poisoning nd its a condition which temps to do more harm to your brain, fills you up with filth nd disgrace, this fucking prostitue plays sister brother \textbf{sex} mother and son \textbf{sex}... and you r saying what harm does she do to the socity. i said to shoot her point blank so that i can assure she should die completely. nd i was not judging... look in history who judged and got killed read about KKK those were not muslims... those who blew up WTC were muslims with out a single valid proff ... its all a setup making ppl look stupid and you are on top of the list.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/146 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small No. You can't have a meaningful relationship, because you don't have anything meaningful to offer. There is no shortage of hot Pornstars, and there certainly isn't any shortage of casual \textbf{sex}.... If only Dani Daniels had the depth to realize that penis size is at the bottom of the long list of reasons not to date someone who gets fucked on camera for a living... Lol\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Man how disgusting is this \textbf{woman}?? Man I am glad that I bring up my girls to have self respect and not be a whore....this is disgusting....\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Karan He's hardly ugly, got a douche cut but not looking like some \textbf{hillbilly}.\normalsize   & \cellcolor{green!5}Hillbilly & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small So she gets to take all the dicks she wants but he is limited to her \textbf{old} saggy \textbf{pussy}? Not a very good deal\normalsize   & \cellcolor{green!27}Old, pussy & \cellcolor{green!27}Age - Over 65s, Nationality - Chinese & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small lmao, what a silly \textbf{woman}. "I can't date 'civilians' because they're insecure." then, "I can't date porn stars because i'm secure.".... oh... ok...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small agreed.. very silly \textbf{woman} !\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small silly \textbf{woman}....earning all of that money. Heck of a lot of jealousy on here today.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small What do porn stars think about the NoFap movement? I understand that pornography is just like any another job, a means to make money. Any habit that becomes an addiction is destructive. I think that pornography needs to be recognized to have the same addiction potential like drugs such as \textbf{alcohol}, tobacco, marijuana and gambling. Pornography needs to be regulated in such a way that access is made more difficult. There has to be a way that whoever wants to watch it, this person has to pay for the viewing. In the end, the porn industry can earn their money and the viewer understands that they have bought a service.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small \@Lenox Marauder You are awesome! Check out Reboot \textbf{Nation}. Prostitution and Pornography need to be regulated. Online Porn is just so addictive to children. I am glad that there is Pokemon Go now, kids go out into the fresh air and play. Pornstars shouldn't be against Nofappers, they won't kill their business. We have bars, Las Vegas, Strip Clubs, Marijuana Coffee Shops, Brothels around the world.  These society that legalized these named things function. I am for porn education in schools. So that when kids watch porn together at least one person will say get off it. Just like smoking, drinking and drugs. At least kids know it's bad. But with porn, no one says anything.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/116 & \cellcolor{green!5}0.862 \\  \hline
  \cellcolor{green!27}\small Fuck the government and everyone in it. It's not the job of the biggest mafia in the world to restrict access to \textbf{pigs} and dogs fucking on a farm to children since thousands of years ago. It's YOUR job, dipshit. Computers come with restricted access, use it or don't buy your damn kids computers. Who the fuck are you to dictate your retarded morality to anybody else bringing up the excuse of "children." If your kids' friends are showing them porn, guess what genius? You need to keep your kids away from those kinds of jerks, the same way you would if they beat up your kid. Stop trying to avoid and transfer responsibility. If you can't trust people with freedom, how can you trust them with power?  You absolutely cannot , ever.  Your "Big Brother" isn't here to help you, it's here to shaft you where the sun don't shine.  Get that through your head you \textbf{commie} motherfucker.\normalsize   & \cellcolor{green!27}Commie, PIGS & \cellcolor{green!27} Ideological and Political Identity - General, Nationality - Southern European & \cellcolor{green!27}2/159 & \cellcolor{green!27}1.258 \\  \hline
  \cellcolor{green!5}\small Be careful you dont get the \textbf{tranny} one.\normalsize   & \cellcolor{green!5}Tranny & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I'll happily date this AMAZING \textbf{woman}....and I'll get tested regularly because I do anyway.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small +Donovan Deans one thing you said that I agree with is that porn stars have expensive taste.....at least more than likely. However, I don't think it would be cheaper (or better) to cross oceans to buy a \textbf{hooker}. I mean, you don't actually believe that any \textbf{hooker} has been nutted on any less than a porn star do you??Yes porn stars take a lot of dick but have you had a opportunity to be with one?? You can tell me, while in your comfort zone, that you would NEVER lower yourself to dating a porn star......but just wait until a really hot one like this brushes up against you. :-)\normalsize   & \cellcolor{green!5}Hooker & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}2/111 & \cellcolor{green!5}1.802 \\  \hline
  \cellcolor{green!27}\small +Bob sagget Yep.....any \textbf{woman} as smokin HOT as her.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Ldkblue76 Eww you're like 40. \textbf{Old} asf..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Ldkblue76i want to make this perfectly clear. it is a fact that women get laid easier than men. that is why men are called studs versus women being called sluts. a \textbf{woman} can be hideous and yet that \textbf{woman} can get laid ( believe me, I've seen this shit with my very eyes ). even if you're an attractive man. you're not guaranteed to get laid with most girls. you may not like the facts, but it is indeed a fair statement.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small bloodiamondeyes Women are not supposed to sleep around because having \textbf{sex} is a huge risk for a \textbf{woman} from an evolution perspective. Men however are designed to spread their genes, and the better genetics you have the more women wants to bang you.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small bloodiamondeyes 80 of the girls sleep with 20 of men brah, because men sleep with girls way below their league all the time. A girl will know if she wants to bang you way before she knows anything about your financial status. Money will of course make you more attractive on the dating/sexual market, because more girls will be interested. But money itself won't make a \textbf{pussy} wet. For that you will need the same features as always, height, preferably some muscle gains, confidence and charisma.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Of course you would 'date' her just to bang... but what about a meaningful, long term relationship?  Of course you wouldn't... not unless you are the type of prick who just wants to have \textbf{sex} and reap the benefits of her money, in which case you are just a scumbag anyway.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small And I Suppose you are not ever going to get to that \textbf{age} ?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small yeah, tested for \textbf{mental} illness\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small PATRICK McShane cuck\normalsize   & \cellcolor{green!27}Cuck & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small What I don't understand is, do porn stars really expect to have a good dating life? I thought they went in knowing that it's not possible to have any proper family values etc. these people opted for this way of life for the party life? Traveling ? I wonder what she meant by 'if both of us have the same goal it works'. Being a pornstar and having family values is self contrary , it doesn't make any sense. Why do they try even? Work hard party, pay for a top notch \textbf{old} \textbf{age} home to retire and then die boom. I thought this what they figured, it seems a lot like dani Daniels is unhappy inside but putting up brave face because of her pride.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/126 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small It's true that she was talking about that but it's very convenient for her to concentrate on that as if it were the only issue. Most men are instinctually turned off by women whose \textbf{sexual} histories they have knowledge of.Most guys would prefer to think that those other guys before him did not exist at all and most girls try to minimize their \textbf{sexual} past to seem more attractive. When women see a man that's surrounded by women, they become interested in him but for men it's the opposite; the slightest hint of his romantic interest having a BF will cause them to get turned off unless they like living on the edge or have some strange fetish.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/118 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Yeah, well \textbf{nobody} wants a hoe, applies to all genders.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small macuś kraków ikr? It's not insecure if the guy doesn't want you to have \textbf{sex} with anyone even if they have a smaller penis than his\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@Rogue Floppers Lol talkin about \textbf{g\textbf{ay}}? and you gonna be the one making out with her 5 mintues after she sucks 20 dudes off with their cum remains still in her mouth?\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small she is getting so much \textbf{sex} why would she eant to date ?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small lol do you think she is shakespeare?   A \textbf{dumb} pornstar, who has to sell her body to make a living, her opinion of any value?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Yeah man is "insecure" if he doesn't like when his girlfriend is fucking and sucking other dicks, seriously? Maybe she should find polyamorous boyfriend as those people don't mind their partner(s) fucking other people. Plus, even normal actors often fall in love with their co-stars when they have \textbf{sex} scenes so wouldn't the risk for that be even greater if they are doing constant, err, porn fucking?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small feeling sorry, what for? \textbf{nobody} pushed her into this. She chose it because of her own reasons. Every job has ups and downs. What I didnt like is that she seems to blame "civilians" for insecurity. Obviously, if the husband/boyfriend knows his partner is screwing around that too in camera its not going to work out long term. And if a \textbf{ho} like her asks her boyfriend to get tested everytime the question he will have is "why should i pay the price for you being a \textbf{ho}" simple LOL\normalsize   & \cellcolor{green!5}Ho, Nobody & \cellcolor{green!5}Age - Youngsters, Gender - Female sexuality & \cellcolor{green!5}3/90 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Hella hot DAMN!!!!! I wanna fuck her straight in da \textbf{pussy} and ass\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small So many \textbf{dumb} insecure butt hurt straight men in the comments.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Jay J dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I think people are full of jealousy and neurosis. Just have to have an extreme amount of self discipline, tolerance and open-mindedness. I dated a \textbf{woman} who did a bit of \textbf{sex} work. You need to have a backbone about the jealousy and conformity drivel and stigma that people project.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Commercial \textbf{Sex} Workers. That's the "new" Profession title. Lol.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small +PenguinDame 009 I do not assign any deep and intricate meanings to what Dani Daniels has to say. She's an ordinary lady, really, not a spy for the GRU. I don't think Ms.Daniels is too unique in the appeal of her personality either, but to see that she is that relatable/nice/approachable is always refreshing. There are a few other adult film actresses that I've seen interviews with that also seem very nice. Mmm, ok, two others; Kayden Kross and Nicole Aniston. Both seemed to have very attractive personalities that matched their \textbf{sex} appeal. A little disclaimer: I haven't seen any of Dani Daniels porn-movie stuff, nor that much porn-movie stuff at all. I prefer the soft-core glamour photo shoot material many of these ladies also take part in.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/128 & \cellcolor{green!5}0.781 \\  \hline
  \cellcolor{green!27}\small Mannix JohnsonNo need for speculation, \textbf{dumb} shitard.My name and avatar were chosen as an IQ test I impose on morons like yourself who are too stupid to spend 2 seconds going to my channel.    And troll isn't a pejorative you retarded thumbsucker.  Every successful entertainer in the world is a successful troll.Oprah is a troll, Dr. Phil is a troll, ...  anyone in entertainment who can't successfully troll goes out of business, dipshit.  LOL\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small MannixTardedI don't need to brush up, \textbf{dumb} shitard.  I'm already far more successful than you can ever hope to be, lol.  How about you not be an anonymous thumbsucking coward on YouTard.... or is that too big a challenge for your raisin brain.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small KaranYou're confused bruh.  You clearly have no clue why I'm on YouTard.My vitriol is how I cope with being waterboarded by fools like yourself.And try and keep up, \textbf{dumb} shitard.  Troll isn't a pejorative.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small It's sexist. \textbf{Nobody} cares about male pornstars.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small OMG!  I just found some private info on this "TasteMyStinkhole" person. He is one of those dudes who likes to do this thing called "wallowing." This entails wallowing around in piles of feces for purposes of \textbf{sexual} gratification. I also found out that he was recently hospitalized for a bacterial infection he got from drinking contaminated enema water. This guy is a \textbf{psycho} for real. Where are the guys with the butterfly nets when you need them?\normalsize   & \cellcolor{green!27}Psycho, Sexual & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small Big RockyTarded Denise1. Have you found a publisher for that novel?2. Take the bait?  LOL.  You're confused \textbf{dumb} shitard.  I'm here laying the bait.  My whole purpose on YouTard is to take steaming hot shits all over YouTard and wait for housefly sized intellects like yourself to land on my shit and eat up.  Hence my name.3. You clearly haven't kept up on the discussion, as half your nonsense has already been addressed.4. -->"I despise religion...I decided at an early \textbf{age} to become a Christian"Oh, right, you retards try to claim christianity isn't a religion, it's a "relationship with a fictional gawd"I like how you stupidly admitted you decided AT AN EARLY \textbf{AGE}... lol... to become a Christ-tard.Guess what \textbf{dumb} shitard, at an EARLY \textbf{AGE} is exactly when your brain is too fucking \textbf{dumb} to make significant decisions.  Clearly you despise logical, rational thought, as you have no choice but to commit a dozen logical fallacies in order to twist your mentally ill mind into belief in gawd.Alright I'm outta this bitch!\normalsize   & \cellcolor{green!5}Age, Dumb & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/180 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small TasteMyStinkhole. Would you be my girlfriend? I'll bring you to my Church and reform you if your willing to give up your perverted lifestyle. I'm one of the deacons of the Church and I'm also good friends with the General Sinott of the Church. I can set up a room for you in the Church basement. You can come live there with me. But I have to warn you about something first. I usually scream for three or four hours in my sleep every night. You don't mind a little screaming do you? I also prefer to sleep naked because my anus needs lots of ventilation at night due to my extreme flatulence problem. I don't know why laying in a prone position makes me have gas.You also need to know one other thing. If your going to be my girlfriend, you'll have to share me with other women. I'm not monogamous at all. I usually have some of the \textbf{old} Church ladies come down into the Church basement and perform fellatio on me. But you don't have to be there when that goes on. You can leave so we can have some privacy. You'll be able to come and go as you please. The only people who have a key to the Church basement is the General Sinott and myself. But I can have a spare key made for you if you promise not to bring anybody else into the Church.That reminds me of a close call I had a few months ago. I was in my room in the Church basement and one of the older Church ladies was performing fellatio on me and the General Sinott started coming downstairs and almost caught us. The \textbf{old} lady had to put her dentures back in real fast and act like \textbf{nothing} unusual was happening. You see, I always have the \textbf{old} ladies remove their dentures before performing oral on me because that way I don't have to worry about their teeth hurting my foreskin. So does it sound like a good deal? You give up your perverted lifestyle in exchange for coming to live with me for free and you allow me to reform you. Take your time to think about it. I'll be waiting for your answer.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}4/381 & \cellcolor{green!27}1.05 \\  \hline
  \cellcolor{green!5}\small Big Rockytarded DeniseI see you've given up all hope of being able to suggest you aren't an illogictarded fool.  LOL.But lets not talk about the dark stuff I found on you.  Doing ass-to-mouth with the cross while cornholing your jesus doll is pretty sicko \textbf{psycho}.  And lets not even get into all the child porn you collected while raping kids at the church.\normalsize   & \cellcolor{green!5}Psycho & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small She's not stupid just because she is a pornstar, doesn't mean she's \textbf{dumb},\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small you're gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Zachary McDowall but you are dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I would not mind fucking this \textbf{woman}, but I do not like to get AIDS in the process, so no.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I don't get it.So A and B had \textbf{sex} yesterday, and B got inflected.B has a test right now, and the test will show him/her......positive?........or a small chance on negative?\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small +Faisal Al-Enizi The \textbf{old} testament is not followed by christians. Mohammed revered the \textbf{old} testament as a holy book. Porn production is not the work of those who follow Christ.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small +Faisal Al-Enizi Btw, making porn and having \textbf{sex} with strangers is nowhere as bad as raping women after killing their male relatives, something that Mohammed did and ISIS emulates.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small +AN C Watch the magnificent work of your fellow Christian girls' pussies fucked by Jewish James Deen and \textbf{black} long dicks while keeping your mouth shut!!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small kick this man to the moon..a \textbf{dumb} fellow\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small oye paaji tussi bhi fan \textbf{ho} inde\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Stfu pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small i agree with you, Faisal. this is not the americal legacy, though. it's fucking jews who own every single inch of USA. what a disgraceful \textbf{race}, me being one of them, unfortunately. cheers brother.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Faisal Al-Enizi There are porn stars in America there are also nuns in America,there are homeless people there are billionaires too, there are stupid people there are Nobel prize winner too there is a logical mistake that point one thing out and let it represent the whole picture,like a jihad \textbf{terrorist} doesn't represent whole Muslim group. Hope you learn some logic courses.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small "Btw, making porn and having \textbf{sex} with strangers is nowhere as bad as raping women after killing their male relatives, something that Mohammed did and ISIS emulates." 0 to 100 Real Talk\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Faisal Al-Enizi didn't Muhammad the pedophile prophet have \textbf{sex} with a nine year \textbf{old} little girl?\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Faisal Al-Enizi better to just marry a 6 year child like your prophet muhammad. Or capture 12 year \textbf{old} children, rape the shit out of them and then sell them to your Muslim brothers so they can do the same.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I know, how horrible that a \textbf{woman} can make money through \textbf{sex}, we should stone her like you guys stone all women who lose their virginity before marriage, because a \textbf{woman}'s human value is apparently tied to her virginity. BTW why the hell are you here, hypocrite?\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small sorry but she thinks its due to lack of mens confidence the problem is men don't want a \textbf{woman} who shares herself with the world a relationship is between 2 people not the whole porn world\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small She literally said in this video at 0:57 that it's tough for men to think about their partner having \textbf{sex} with multiple men. Then she goes on to talk about it more with the whole ''you had \textbf{sex} with this person/my friend'' thing.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small \@Big Rocky DennisMy brain's just recalling the reveal of the massive worldwide \textbf{sexual} abuse against kids in Christian institutions that took place over the last decades. Christianity seems to degrade even more .... ;)\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small To be fair though, all women care about how much money a man makes.  I don't know if many young, attractive women looking for a guy who isn't an earner.  Also, many people are more \textbf{promiscuous} today than they have probably ever been.  I still think it would be ludicrous to be in a relationship with a prostitute (porn stars are prostitutes, they just do it in front of a camera).\normalsize   & \cellcolor{green!27}Promiscuous & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small NED STARK hit the nail right on the head also if you're going to get serious and have kids with a \textbf{woman} you can't be embarrassed to tell your kids what their mother did once they grow up\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small you mean the bible approve that a \textbf{woman} can have multiple \textbf{sex} partner. holy shit...\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small That's all you've got huh?  Projecting blame on the guy for watching this video.  Whatever happened to the good \textbf{old} days when you people used to trot out your pseudoscientific "evidence".  I guess the younger generation isn't smart enough to be able to do that.  Which does what exactly to your theory of evolution?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Holy crap, some of you people are deluded.  If a \textbf{woman} is banging a different man almost every day, then she is cheating.  The context really doesn't frickin matter... she enjoys it, there will always be somewhat of an emotional connection with \textbf{sex} (especially when they do everything under the sun many times) if even just a little.  Not to mention the world of men/boys jacking off to your wife and seeing everything about her... it isn't a 'normal' thing to expect a man to be ok with his wife doing that crap.Open relationships are sick and twisted... if you do it for physical pleasure only then fine, but to expect a husband and a wife with an 'open' relationship to work is asinine.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/125 & \cellcolor{green!27}1.6 \\  \hline
  \cellcolor{green!5}\small Bitch please, she isn't doing porn cause she needs money anymore. Overtime you get enough money to quit. The only reason why she is doing it is cause she is a low life piece of trash that gets off of cucking her husband. Males are dominant in nature, which is why you see more polyamoric relationships with 1 man and several women rather than 1 \textbf{woman} and several man. If you have problems, blame evolution and how different genders are biologically wired. Stupid fucks\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Nothing but respect, but it's just kind of funny. Because she says that people or "civilians" would get jealous about the person that they love having \textbf{sex} with a bunch of people daily. But when she dates a performer she also gets jealous because the person that she loves is fucking somebody else. It's stuck in a never ending never resolving bind .. \textbf{Sex} is way better when it's love. I think that everybody has had a one night stand and felt kind of like shit afterwards. I don't judge because I have had a lot of \textbf{sex} partners but as a guy and the \textbf{woman} that I love is having \textbf{sex} with a bunch of guys daily, not to mention they would be twice the size of you which any man would get very insecure. It would be like Dani and I are dating, and I am a porn star and she's not. And all the porn stars that I am fucking have way bigger tits, and look way hotter than she does. Well of course it's going to eventually really bugged her that I'm doing that .. If you really want to find truelove you're going to have to get out of the industry in\normalsize   & \cellcolor{green!27}Nothing, Sex, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}6/207 & \cellcolor{green!27}2.899 \\  \hline
  \cellcolor{green!5}\small Jordan Anderson  no different between have \textbf{sex} with my wife  in the same bed and  have \textbf{sex} with my nighty girl out.... admit that ..maybe you can say may two couples have \textbf{sex} for better life and reall hot relationship both like  you said ....but turly . I personally I don't agree with you... your body isn't game to play it every where   ..... The \textbf{sex}  emotion for animal not for human and  remember that ...\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/76 & \cellcolor{green!5}5.263 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman, Sex, Sexual, Chick, Gender, Sexism, Misogyny, Misogynist & \cellcolor{red!27}1330 & \cellcolor{red!27}1330/234350& \cellcolor{red!27}0.5700000000000001 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Senior, Elder & \cellcolor{red!5}128 & \cellcolor{red!5}128/234350& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}pussy, cooter, Yellow & \cellcolor{red!27}102 & \cellcolor{red!27}102/234350& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Crazy, Weird, Dumb, Deaf, Mental, Blind, Lame, Freak, Weirdo, Disabled, Nutter, Lunatic, Eugenics, Psycho, Midget & \cellcolor{red!5}284 & \cellcolor{red!5}284/234350& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Nobody, Zero, Brat & \cellcolor{red!27}300 & \cellcolor{red!27}300/234350& \cellcolor{red!27}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female intelligence}  & \cellcolor{red!5}Bimbo, Feminazi, Becky & \cellcolor{red!5}8 & \cellcolor{red!5}8/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age & \cellcolor{red!27}48 & \cellcolor{red!27}48/234350& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Hooker, Slag, THOT, Promiscuous, Ho, Tramp, Sloot, Slapper & \cellcolor{red!5}110 & \cellcolor{red!5}110/234350& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay & \cellcolor{red!27}17 & \cellcolor{red!27}17/234350& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, Beta male, Fruit, Faggot, Fruitcake, Sissy, Effeminate & \cellcolor{red!5}29 & \cellcolor{red!5}29/234350& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Old hag, Hag, Witch & \cellcolor{red!27}13 & \cellcolor{red!27}13/234350& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, Hillbilly, Coarse, White Trash & \cellcolor{red!5}44 & \cellcolor{red!5}44/234350& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Red, Indian, Apple & \cellcolor{red!27}21 & \cellcolor{red!27}21/234350& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Red, Cuck, Snowflake, Libtard, Commie & \cellcolor{red!5}21 & \cellcolor{red!5}21/234350& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}7 & \cellcolor{red!27}7/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black, Nigga, Buck, Colored, Fuzzy & \cellcolor{red!5}70 & \cellcolor{red!5}70/234350& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Female homosexuality}  & \cellcolor{red!27}Lesbian & \cellcolor{red!27}23 & \cellcolor{red!27}23/234350& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Terrorist & \cellcolor{red!5}6 & \cellcolor{red!5}6/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}doctors, Nation, Alien & \cellcolor{red!27}11 & \cellcolor{red!27}11/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Christian}  & \cellcolor{red!5}Bible thumper & \cellcolor{red!5}1 & \cellcolor{red!5}1/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Jerry, Hun, Fritz & \cellcolor{red!27}5 & \cellcolor{red!27}5/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Irish}  & \cellcolor{red!5}Piker, Paddy & \cellcolor{red!5}2 & \cellcolor{red!5}2/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Southern European}  & \cellcolor{red!27}PIGS & \cellcolor{red!27}5 & \cellcolor{red!27}5/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Zip, Yellow & \cellcolor{red!5}2 & \cellcolor{red!5}2/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Drugs}  & \cellcolor{red!27}Drug addict, Junkie & \cellcolor{red!27}4 & \cellcolor{red!27}4/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Race, Racist & \cellcolor{red!5}10 & \cellcolor{red!5}10/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}Transsexual, Transgender, Transition, Tranny & \cellcolor{red!27}6 & \cellcolor{red!27}6/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Bald, Fat, Skinny, Thin, Lump, Chubby, Fatty & \cellcolor{red!5}36 & \cellcolor{red!5}36/234350& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - British}  & \cellcolor{red!27}Tan & \cellcolor{red!27}1 & \cellcolor{red!27}1/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!5}Dot & \cellcolor{red!5}2 & \cellcolor{red!5}2/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - French}  & \cellcolor{red!27}Frog & \cellcolor{red!27}3 & \cellcolor{red!27}3/234350& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - White}  & \cellcolor{red!5}White Trash & \cellcolor{red!5}2 & \cellcolor{red!5}2/234350& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Japanese}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}1 & \cellcolor{red!27}1/234350& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Age - Over 65s;Nationality - Chinese;Physical Identity - Physical (and Mental) Impairments;Age - Youngsters;Gender - Female intelligence;Age - General;Gender - Female sexuality;Sexual Identity - General;Sexual Identity - Male homosexuality;Gender - Female age and physical appearance;Social Class - Working class;Ethnicity - Native-American; Ideological and Political Identity - General;Behavioural Addiction - Alcohol;Ethnicity - Black;Sexual Identity - Female homosexuality;Religious Identity - Muslim;Nationality - General;Religious Identity - Christian;Nationality - German;Nationality - Irish;Nationality - Southern European;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Behavioural Addiction - Drugs;Ethnicity - General;Sexual Identity - Transexuality;Physical Identity - Physical Features;Nationality - British;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Nationality - French;Ethnicity - White;Nationality - Japanese;%.

\item The percentage of hate speech related words is 1.1316.

\item Considering that the variable \textbf{Gender - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 2653/10321 occurences of hate speech related comments.\end{itemize}\end{document}