\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_102.json :}\newline \par\Large\textbf {Title: \large  The new old people are going to suck | Lachlan Patterson }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small ((Thank God i lived in the 90s)) Im 33, all my \textbf{old} pics, like maybe 50 in 16 years are with oversized clothing and did not match in any way. My son is 1 year \textbf{old}, i think we have like 4 million photos of him...ralph lauren shirts, adidas pants, nikey shoes and so on....\textbf{crazy} times my friends\normalsize   & \cellcolor{green!27}Crazy, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/58 & \cellcolor{green!27}5.172 \\  \hline
  \cellcolor{green!5}\small Ha, true about the new \textbf{old} people!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Is this the caveman from the \textbf{old} Geico commercials?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Norm Macdonald i think had a bit sinilar to this talking about how \textbf{lame} and uninteresting older people of today will be because even taking a dump gets posted on social media. Anyway, this guys fuckin hot, who cares?\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small He future \textbf{old} people whose life stories will be about hours spent playing; Call of Duty, Battlefield, Fortnite, PUGB, Minecraft, Grand Theft etc.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small New young people already suck, so yeah, I'd imagine they're going to make \textbf{dumb} ass, obnoxious adults.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small i come from a mixed \textbf{race} family. my mother is white and my father is dark white. hahahhahahahaa\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small We'll have stories too. They'll just be digital. "Here's a picture of a severe thunderstorm I took because I like chasing storms like a \textbf{crazy} person".\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small "Here is a pic of your grandma and I being white people before it was considered "\textbf{racist}."\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small If a picture is really important in this day and \textbf{age}, you hang it on the wall or frame it. It could be a wooden frame, a plastic frame, you could keep it on your desk or your meditation space if it makes you happy. Decades from now this will be seen as stubborn and \textbf{old} fashioned, much like letter writing is today(I actually write as a 20 year \textbf{old} to my older relatives), we will be the ones who haven't adapted yet to whatever new thing they do in the future. I just like to think about things like this, I find it charming\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/105 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Old men listening to Nirvana and breaking their hips trying to drop into the empty swimming pool at the retirement home to do a sick heel flip 180 brah.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Bold of you to assume this generation will get to be \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small You will be \textbf{old} yourself shortly knob head, when this happens look back at this!,,,,\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small This cat noticed this young \textbf{whippersnapper} wannabe comedian has a 60's style haircut but yet his "comedic" skit pokes fun at Baby Boomers. We have a term for this, he's kinda fucked up.\normalsize   & \cellcolor{green!5}Whippersnapper & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Don't forget those pictures of you dumping an ice bucket on your head, eating a Tide Pod, and licking the ice cream container in the store.If you really want to learn patience, be married to a \textbf{woman} for 30 years, raise 2 daughters, and make sure your dog is female too.  That will make you as patient as a glacier.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small Interesting how all the positive   Stories of \textbf{old} people were grandfathers and all the horrible \textbf{old} people pictures of the future were grandmothers. I'm sure this guys instagram is a hipster nightmare.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Yes my image of \textbf{old} ladies in their blue jeans came true.  But the appocolapse is over.  Time for granny to dress pretty if she wants.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small When he said he loves \textbf{old} people, it was VERY similar to how Bill Burr said it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Hey \textbf{old} \textbf{old} people helped create the new \textbf{old} people. Only got yourselves to blame.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small My father is dark white What a way to not \textbf{racism} but still calling people black\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small i think he meant dark white as in darker \textbf{colored} whites like mediterranean/italian/spanish/greek...and \textbf{black} isn't a \textbf{racist} term bro\normalsize   & \cellcolor{green!27}Black, Colored, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Jokes on you there will be no new \textbf{old} people because everybody will be dead soon...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small selfies were \textbf{lame} 10 years ago. Some people refuse to give it up or they lack the intellect to understand how corny the selfie truly is, especially with duck lips or giving a peace sign\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small That was surprisingly bad. He built a great start and then said a 2015 Instagram girl joke. You sound \textbf{old} already bro.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small They might not live long enough to get \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Is this the caveman from the \textbf{old} Geico commercials ????\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small New \textbf{old} people aren't sucking as bad as new young millennial people who don't think anything is funny😆😆😆\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small "hey grandpa is this a picture of grandma?""did you just assume my \textbf{gender}?!?! that's me you \textbf{nazi} bigot"so brave\normalsize   & \cellcolor{green!5}Gender, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Gender - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Old People Now: 'This tattoo? Got it in the army. My \textbf{old} buddies and I all got the same design the night before we were shipped to Vietnam. I was the only one in the group who made it out alive. Last time I saw all the tattoos together again was when I had to say goodbye to each of my friends. My brothers. No badge or medal I ever earned came close to this.'\textbf{Old} people in 70 years: 'It's Pickle Riiiick!'\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small It's not for us to judge the new \textbf{old} people....it's for the future young generation to judge the new \textbf{old} people....we might think they suck but the future generation may think as per their time...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Old, bitchy, overly sensitive \textbf{old} people... We're in for a treat...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small This guy's \textbf{weird} haha\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Now that we have real technology there won't be this stereotype anymore about '\textbf{old} people'. You'll just be \textbf{old} lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small 'And here is me campaigning for \textbf{old} people to be executed after the fucking boomers voted to Leave and ruined my future. That was fifty years ago. Isn't my hair a lovely shade of green in this picture.'\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Yh I been saying for ages now, anyone you get than 40 today with kids will be the shortest generation of grandparents \textbf{old} whateva\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I should show him the pic of this \textbf{old} man.s175 young Mexican students  that I teach as a volunteer!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I use to imagine this .This generation is \textbf{dumb} AF.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small 50 years from now, kids born in 2000 will be the \textbf{old} people.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Old people now: made fun of\textbf{Old} people in the future: make fun of younger people Young ppl in the future: FUCK\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Tech has created a generation on metaphorical technology literate \textbf{common} sense illiterate socialist cavemen and women..just the right thing to get votes on catastrophe and helplessness\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Old \textbf{old} people suck\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small The mixed \textbf{race} joke was funny, but I heard it before (but told "slightly" different).  That was a great set though, I wanna see more of his stuff.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Being \textbf{old} now doesn't seem so bad anymore.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small When I ask my grandkid if he seen deez , he's not going to know what to do when I say deez nu nu nu nutz ! I still have to think of something fun to do if I have a granddaughter instead . I need to be able to fully embarrass her in public .Gen X will be the greatest \textbf{old} people ever . Hell , the way I figure it , I've only got 30 years left until I can walk down the street wearing \textbf{nothing} but a sock  and some ear muffs and get away with it .\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Stupid things \textbf{old} people will say in the future (and even some now).We thought the world was ending in the year 2000, but it didn't. Prince even made a song about it.We thought all computers were going to implode in the year 2000, because of Y2K, but \textbf{nothing} happened. Chris Jericho even made a wrestling nick name about it.We once had cell phones AND ipods at the same time. What do you mean 'what is an ipod'?I once let 20 \textbf{black} dudes gang bang me so we could post something on pornhub. (Grandma please stop telling me these stories).\normalsize   & \cellcolor{green!27}Black, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/103 & \cellcolor{green!27}2.913 \\  \hline
  \cellcolor{green!5}\small And here are trees.We used to have those \textbf{weird} and green oxygen-making machines back in the day\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small "Now they have to zap carbon dioxide to create oxygen and we have to buy it, sigh the good \textbf{old} days."\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I work in an \textbf{old} folks home, trust me on this.. \textbf{Old} \textbf{old} people suck.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Future is gonna be \textbf{crazy} as F**k!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Grandpa: "Billy, Heres a video of a cop shooting an unarmed \textbf{black} man".Billy: "That happened today Grandpa".\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Why do people use a New England accent when they try to talk like \textbf{old} people?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I'm just glad I will never see my grandparents \textbf{sex} video. That's a relief.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I like this dude solely because he reminds me of the caveman from the \textbf{old} Geico car insurance ads.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Never been so grateful of \textbf{old} people\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Yeah.. With names like "Lachlan" and awful stand up like this.. Yeah \textbf{old} people in the future are going to suck..\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small us Gen Z \textbf{old} people are gonna be the worst tho can u imagine.'Back in the gOOD \textbf{OLD} DAYS, we still had p a p e r and could go outside without an o x y g e n  t a n k!!'(12yo born in 2086 rolls their eyes)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small Why do literally 75 of you \textbf{old} people have the SAME star tattoos, grandma? Oh and grandma, that \textbf{tramp} stamp is half wiped away in the middle. Why?\normalsize   & \cellcolor{green!27}Old, Tramp & \cellcolor{green!27}Age - Over 65s, Gender - Female sexuality & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Here's a picture of a \textbf{black} hole, something humanity had never managed to capture before :)\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Bold of you to assume that we will all live to be \textbf{old} people\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Billy: Grandpa, what's this?GP: That's a photo of me outside my \textbf{old} house!Billy: Why is your hand in a \textbf{weird} circle?GP: cracks knuckles let me tell you about that Billy\normalsize   & \cellcolor{green!5}Old, Weird & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small It's ironic that every comments here was written by somebody \textbf{old} and/or \textbf{lame}.\normalsize   & \cellcolor{green!27}Lame, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Brilliant lol and truthful :( \textbf{common} people get a life so you can share stories with your grandkids. \textbf{Common} before it's too late, we can do it. No more selfies and self indulging, make your own memorable history\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Old people of any generation will never suck as the young people of any generation are going to suck more.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Doubt if \textbf{old} people will be allowed with these  upcoming "children of the corn" generations. They have \textbf{zero} social conscious \textbf{zero} value for life and disdain for anyone with wisdom.\normalsize   & \cellcolor{green!5}Old, Zero & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/30 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small B4 u know it, we'll have 60 yr \textbf{old} men bumping "Gucci Gang" \& "\textbf{Old} Town Road" in their cars 🤣🤣🤣\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small he only needs a white robe and a \textbf{r\textbf{ed}} band to be a perfect cosplay of jesus\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small I'll never forget my 89 year \textbf{old} Grandpa's last words:"Stop shaking the ladder you little shit!"\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Cant believe theres gonna be a day where a 80 year \textbf{old} is gonna be listening to 6ix 9ine talking about this was real music to there grand kids lol.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I'm 54 yrs \textbf{old}.  My  great-Uncle Homer (born in late 1895!) used to tell me stories of driving by the Santa Monica pier in his first car, a Model T, at the frightening speed of 35mph.... oh hearing War of the Worlds on the radio with his family and everyone freaking out because they thought it was real... of getting their first television, a \textbf{black} and white one.... of being in World War I ... and being in World War II. A few years before he passed, he bought a 'Scooby Doo' van, with an 8 track player in it and mag wheels, and taught me how to drive in it. He was a man that lived thru the first radios, TV's, The Great Depression, two World Wars, Viet Nam, commercial flying and the moon shot, 8 track tapes and MTV..... No generation before or since has seen the things that HIS generation did. I held his hand as we unplugged the life support system. . . and wished him happy journies as he went on to the next great adventure. ♥\normalsize   & \cellcolor{green!27}Black, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/182 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small So fucking true, if I see an \textbf{elderly} person at a stall when I go to boot sales I always enjoy chatting to them.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small No fuck you. \textbf{Old} people today literally ruined the world. I know its comedy but fuck you for making our generation look bad again. Come up with something original, you fuck\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small If anything social media has shown us how selfish and narcissistic people really are. You must work at being a good person. Everyone is born selfish and narcissistic and must be taught as children to be otherwise. \textbf{NOBODY} is born good!!! \textbf{NOBODY}!\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small It might not be more interesting, but it'll be more entertaining. Who doesn't wanna see young pics of their grandmother posing with ripped jeans and her tongue out, I'd love if that was a thing. Plus, people will actually be able to see what we looked like, how we were, and our personalities, which I always wish I could see in \textbf{old} photos, but all you get is random events they were part of. It tells you \textbf{nothing} about them other than that they did a lot of things. Which makes sense because of all the years that have gone by, so really you learn \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/106 & \cellcolor{green!27}2.83 \\  \hline
  \cellcolor{green!5}\small Melinials will mostly never reach retirement \textbf{age} anyway. \textbf{Fat} is beautiful  -10 years, smoking is cool especially marijuana-20 years, drinking 4 alcoholic beverages more that 4 times a week is fine -10 years, taking recreational drugs monthly+ -10 years average to more.. ya, the average mortality \textbf{age} already dropped 5 years due to lack of personal health even with the best medical care in the world.\normalsize   & \cellcolor{green!5}Age, Fat & \cellcolor{green!5}Age - General, Physical Identity - Physical Features & \cellcolor{green!5}3/66 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small You're fooling \textbf{nobody} here, Benedict cucumber\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small No man, we have Baby Boomers as \textbf{old} people now, and they're just the absolute worst whether they're young or \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small I mean he's absolutely right, The \textbf{old} people that are around now many of them are the most interesting people you will ever meet in your life, I shutter to imagine what the \textbf{old} people in 50 years will be like\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Grannys with nose and tongue studs. Tatoos all over and \textbf{tramp} stamp.  That is what we are facing.\normalsize   & \cellcolor{green!5}Tramp & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Not only this but theres a decent chance your grand mother will have a 30-50 year \textbf{old} sextape.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Hilarious. His \textbf{ethnicity} is like mine. LMAO Amazing comedy!! Love him\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Geico called, they're bringing your \textbf{old} character back.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small The \textbf{old}, \textbf{old} pipo kinda suck now !!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small New \textbf{old} people driving around in loud ass Subaru's, cranking lil pump, vaping\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I didn't watch this video yet but based on the title alone.. I've BEEN saying exactly that since the late 90s Gone are the days of the sweet, blue-haired, \textbf{old} ladies who baked cookies, sat and their rocking chairs and knit sweaters.. "Grandmom's" these days are getting tattooed, arguing on Facebook and showing off on Instagram 🤦 Help us ALL\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small The 👎is from the new \textbf{old} people that are gonna suck.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It's True, and Hilarious. The millennials are going to be the Worst"\textbf{old}"people Ever 😱if they make it to \textbf{old} \textbf{age} 🤣\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I feel like \textbf{nobody} ever mentions the huge gap between teens and kids now. Like, I'm a teen. And a few of my kid cousins are already more phone absorbed than I could ever be. Kids in general never stop talking about the latest memes, and I'm still here with my friends talking about that \textbf{weird} episode of spongebob I saw on TV when I was 5.\normalsize   & \cellcolor{green!27}Nobody, Weird & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small He looks like the caveman from \textbf{old} geico commercials\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small 'Grandma Skylar?''Yes, Pewdytwo?''Why are all my lab mates named after \textbf{old} people that were never famous?''Go and ask your father.'...'Hey, Google—''It was the algorithm, son.'\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small So worse than the \textbf{old} people that were hella \textbf{racist} and destroyed our economy and our government... okay\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small O come on! \textbf{Old} people suck now and they will continue to suck in the future. I will be considered an \textbf{old} person one day and I too will suck.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small We aint even living past 50 fucking cancer, heart disease and \textbf{mental} illness gonna wipe us out\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small yeah im mixed \textbf{race} to m gandad was a republican and grandmaw a democrat.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{black} and a republican my bf is a democrat from Texas\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small At least the new \textbf{old} people wont be nearly as \textbf{racist} or xenophobic.\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Current \textbf{old} people suck. Baby boomers are \textbf{nothing} like the WWII generation.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I like how his version of \textbf{old} people have a  transantlantic accent. Just all millennials,  when they get \textbf{old}, all of a sudden have this accent, lol.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Hey. Hey guys....Octogenarians with gauges and \textbf{skinny} jeens.\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small He's forgetting the biggest reason why \textbf{old} people are going to suck. We're going to still be bitching about no one agreeing with our point of view while we play video games and discuss our anime waifus and argue whether infinity war really is better than Justice league. We'll elect people who only meme and dab on their haters.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Glad Chris Cornell came back from the dead to shit talk the elderly\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Jesus, I never thought about it but he's right,the new-\textbf{old} people will suck ass because imagine a 70-80 year \textbf{old} cantankerous \textbf{old} person that used to troll onlinesmmfh\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Can't wait for wrinkled tattoo sleeves, \textbf{Tramp} Stamps, and nose ring fake boogers.\normalsize   & \cellcolor{green!5}Tramp & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That mermaid tattoo will have gone from Ariel to Ursula, the \textbf{tramp} stamp will have fallen into the crack, and no one will notice a ring in that veiny bulbus nose.\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Tattoo sleeves actually  still look sick. look up \textbf{old} people with tattoos\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Seriously! Tattoos are \textbf{t\textbf{railer trash}}.\normalsize   & \cellcolor{green!27}Trailer trash & \cellcolor{green!27}Ethnicity - White, Social Class - Working class & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small He is really \textbf{old} to a teenager, or his children.😭\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Yes, that is exactly how it is going to be! I am glad to be dead by then. 😳I just discovered that I also am of mixed race: one white with a bit of \textbf{r\textbf{ed}} in the cheeks and one a bit yellowish, beige. 😂😂😂😂😂\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small When he said "my dads getting \textbf{old}...yeah hes starting to hang plates on the walls" so accurate its scary lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Bro he looks like the caveman from the \textbf{old} Geico commercials!!!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Woah I was just thinking about this today that's \textbf{crazy} 😂\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Joke taken from an \textbf{old} meme without adding value beyond the meme it came from. Feels like some new type of plagiarism. As Einstein supposedly said 'the secret to creativity is knowing how to hide your sources' and this comedian just ran with it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I can type 50 Wpm with a \textbf{Apple} TV remote👍   1,086,865,086  👎   1   💬\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The area 51 survivor stories are gonna be \textbf{crazy} tho\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Ah, yes, a updated template of Nick Swardson's \textbf{old} people jokes.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small All these pictures will be lost on their 32 year \textbf{old} iphone. Future \textbf{old} people wont have shit, kinda sad honestly\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Wow...it makes you think indeed. I am almost 40, and I can see that difference, although..One thing that always bothered me was the fact that \textbf{old} photos are very mysterious. I have a few of my passed relatives' photos, but not much information to go on from them. \textbf{Nobody} wants to tell me about them in depth, so perhaps having pictures of their detailed life (breakfast they enjoyed, shoe style favorite, endless selfies of different angles, traveling photos) creates an archive of their lives, in a way I always craved to know my relatives in a deeper way. I am looking at this from a glass half full perspective, I believe lol.\normalsize   & \cellcolor{green!5}Nobody, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/113 & \cellcolor{green!5}1.77 \\  \hline
  \cellcolor{green!27}\small I don't know who is the joke thief here, but I've heard this before. New \textbf{old} people's pictures.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Thot this was hozier\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Fortunately life expectancy is going down. Enough selfie stick cliff tumbles ought to \textbf{thin} the herd.\normalsize   & \cellcolor{green!27}Thin & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I used to hang out with all \textbf{old} people then they all died and i became one\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Him holding the microphone like that in the first half was bugging me, I felt like a truck was gonna smack me down into a \textbf{pancake} 🥞 if he didn't stop٩( ᐛ )و\normalsize   & \cellcolor{green!27}Pancake & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small He's right \textbf{old} ppl will suck they won't be "real" grandparents. They're still going to be acting like it's a Hot Girl vs. City Boyz summer.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I can only imagine Gen Z when we are \textbf{elderly}. A couple young kids walk by, and here two \textbf{old} men saying 'You mum gay''You sister a mister''You bro a hoe' Etc\normalsize   & \cellcolor{green!27}Elderly, Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Criminals make the best \textbf{old} people\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Lol! Are u sure not Jewish? From Jesus bloodline? 😂 I think u right about the new \textbf{old} people.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Except \textbf{nobody} is having grandkids!\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small hahahaha an \textbf{ethnic} jew saying he's ethnically "white"oh how many lies are said in that one sentence lmfao\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small what does 'ethnic jew' and 'ethnically white' even mean?  Both misnomers and just a sign of how \textbf{dumb} and myopic humans are.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Yep, it's gonna be pretty bad......not to mention all the terrible trendy tattoos they'll have in \textbf{old} \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{old}...ish.Went to Australia for 2 weeks couple years ago. Solo.Only took 2 selfies.My reflection in a the diveboat/catamaran window while fully geared up.My reflection in a night club window that had upcoming punk/metal band posters.Only in a couple other of the thousand or so shots from the trip.Two were me on a knee proposing to some random half my \textbf{age} Filipina...Also got solar eclipse photos...And yes... I did get shots a meal or two, and of the wings while mid Pacific ocean.BtwI thought the joke was going to be about screen caps of Fortnite.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/105 & \cellcolor{green!5}1.905 \\  \hline
  \cellcolor{green!27}\small The current \textbf{old} people suck fucking dick!!!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small You really think these idiots are going to survive into \textbf{old} \textbf{age}??? Not likely.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small It's because the \textbf{old} people of today had to actually use their brains, had to work, had to figure things out, had to work through their lives. The kids nowadays they don't even have to think everything's taken care of for them! And look at the things that they do for entertainment. That alone should show you how far we have sunk.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Black Metal grandparents are gonna be epic! I can't wait to become one 🤘🏻\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small As an almost-old dude, I tell younger people I don't give a shit about their PC culture and the 96 genders they made up out of \textbf{thin} air. And if they dare tell me how to talk or what words to use, I stick a hard \textbf{bony} finger into their chest and tell them to STFU and die.  I do what I want, when I want.\normalsize   & \cellcolor{green!27}Bony, Thin & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small The skit was complete bulshit cuz his generation is going to be the next \textbf{old} people not not the kids she's complaining about. Kids aren't really allowed to be outside to do s*** anymore I have two places I go have no bikes or skate signs posted all over the place and have two gas stations I stopped at have those annoying buzzers to keep kids from hanging out there you try to go into any Forest areas you'll get arrested for trespassing onto Government property and and if I tried half the s*** that my parents pulled I would be in jail for half a century for various "crimes". So people constantly going oh this Young Generation oh the Next Generation they can go f*** themselves\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/127 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small don't post food pics people...it's so f'in \textbf{tacky}.  i was in a really bad 'social media training' and the instructor (from Pincher Creek don't hire him) said to post food pics on a business account, with my 300 lbs manager that sounded like the WORST idea ever, but she underlined that shit like it was going out of style.\normalsize   & \cellcolor{green!27}Tacky & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small I post food pics but it's in an actual \textbf{old} fashioned cooking group. Where we get recipes and share recipes. So I feel like that's different. And no I'm not going to show anybody in the future those pictures if it's all were they can look it up in the group then so be it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small It's going to be so awkward for the new grandchildren... Unless they manage to come up with something so wild it makes twerking comparable with a rebellious \textbf{woman} with short hair and shapeless dress in the 1920s 😄\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Bro did you just assume your future Grandma's \textbf{gender}?\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The new \textbf{old} people already suck. The WW2 vets that grew up in the depression were awesome. They're just about all gone. The \textbf{old} people now were too young for any of that but too \textbf{old} for Vietnam and retired way before the economy tanked. They graduated high school, went straight to work in a booming economy, and have known \textbf{nothing} but the highest standard of living the world has ever saw.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}4/72 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Wow that's \textbf{crazy}! Especially since the actor who played on the show's name is David.. not "Keith".\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Jason PH right?? I mean, why would the grandma tell him as if he didn't know who Keith was... however, he was asking about Keith 10 year prior.... wtf? And also, when he asked about the moms "boyfriend" and she blew up, wouldn't that mean they were already married twice (according to grandma) by then? Just about the biggest load of BS iv ever read.. and look how many people liked the comment.. jeez people are \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Roland Snyder and what a \textbf{lame} story the fake too, lifemust be pretty boring if this sounds interesting to them. like \textbf{nothing} cool even happened, \textbf{nobody} died, or got punched , \textbf{nobody} even stood up and clapped. Worst fake story ever.\normalsize   & \cellcolor{green!5}Lame, Nobody, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/41 & \cellcolor{green!5}9.756 \\  \hline
  \cellcolor{green!27}\small Gotta go on adventures to have cool stories when yer old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small The baby boomers getting \textbf{old} is a nightmare. All those \textbf{old} hippy wh*res and leftist 60's degenerates getting \textbf{old}? YUK\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/20 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small What's wrong with you the Baby Boomers are already \textbf{old}! Quit doing that!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Ooh look Nickelback jokes. Haven't heard those before.... \textbf{Lame} asses\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Old minimalist "I'd show you a picture but I threw everything out"\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I love this guys \textbf{old} voice with the accent lol ots perfect\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Omg he's so right \textbf{old} people are awesome\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small He said, '\textbf{Old} people will teach you patience. Just watch an \textbf{old} person enter their email address on an AppleTV' 😂😂😂\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small At least they wont be \textbf{homophobic}, sexist, religious, \textbf{racist} bigots like the boomers we have now\normalsize   & \cellcolor{green!27}Homophobic, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small "I'm mixed \textbf{race} my mom is white, my dad's an asshole." there you go kid, now finish it, try atleast. ;)\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Bold of you to believe we'll live long enough to be \textbf{elderly}.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Im not mentally prepared for a 70 yr \textbf{old} to say "lit AF".....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small My 96 year \textbf{old} grandfather says that lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small U realize that's gonna happen when he almost at that \textbf{age} as well right\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small lol I would be a wild ass \textbf{old} man\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Old person saying Lit, Finna, Yeet, And much more. Smh\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small You will be that 70 year old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Nobody should be saying that\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small grandpa 'Plays Fortnite, you don't know \textbf{nothing} about  this kids 🥴'\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Hopefully no one will say that \textbf{dumb} shit from this day forward. Shit in one hand wish in the other I guess. The "yoo brooo" and "fam" are also atrocious.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small At least they'll get \textbf{old}.  You'll probably be incinerated in a nuclear fireball, succumb to a pandemic or just keel over from heat exhaustion from that climate change.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Norm is an \textbf{old} person now.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Old people suck TODAY !    Im 56, \textbf{old} compared to the hipster twat who will inevitably respond to my comment with a clever retort.....but I was at a concert watching a row of oldER guys trying to get their cell phones to take videos of the band.....then, each one had to get up, leave, come back, etc. \textbf{Age} limit for driving?  Drinking?  Voting? I say the cut off for concerts is 65, no walkers, canes, or oxygen tanks.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/78 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small No no no, once all the boomers are dead and gone, I'll be glad to accept \textbf{old} people who have less interesting things to say. Better than \textbf{old} people now complaining about not getting what they want and how the new generation is lazy and cheap now that every job pays less and everything costs more.Just the political shift alone from the boomers being gone.... god I can't wait.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/70 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small ..........and half the comments section is those same crap new \textbf{old} people whining and moaning. It's too bad he isn't funny because that was a great premise.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small But the young people 50 years from now will be so bad they will make the \textbf{old} people 50 years from now seem decent enough in comparison.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Isnt that the Geico stone \textbf{age} man?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The new \textbf{old} people will still be baby boomers so they'll have plenty of film based photos from the 70s through 90s.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small It's definitely sour people who all have every photo this guy is talking about and \textbf{nothing} else. 99 of their photos are selfies....food plates before you eat it....Nd other unnecessary crap.When millions of Americans are all competing in sharing the same duck face look and half bent over postures or selfies......its no longer cool or desired.I'm looking forward to the next fad because the current ones suck. I take no part in it.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small This is white privilege!! Rich white guy trying to funny. He must be a \textbf{racist}, a sexist, a rapist, a homophob, a child molester, a white supremacists, and more importantly a expoiter of \textbf{old} people!! He should be doxed!! Blacklisted. Lock him up, lock him up!!!!!! Sounds stupid right? Well the so called "woke" made it like this!! So I say as a 50 yr \textbf{old} man "Go Fuck Yourselves!"\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}3/70 & \cellcolor{green!5}4.286 \\  \hline
  \cellcolor{green!27}\small I'm 45 does that mean I'm gonna suck when I get \textbf{old}? cause that just sucks bro. now I'm going to have to sit here and reflect....depressing.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I think he's talking more about Millennials and younger. Even though I'm almost 44 and we did have some good times but then it started getting \textbf{weird} past 20 years.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I can imagine \textbf{old} people 50 years from now scrolling through 8 billion IG photos with ugly filters that make them look like \textbf{alien} cat people, trying to show them to grandchildren who are too absorbed in their own holograms.\normalsize   & \cellcolor{green!27}Alien, Old & \cellcolor{green!27}Age - Over 65s, Nationality - General & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Imagine gen z becoming \textbf{old} 🤣\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Luckily, AI will save us from this cursed future by turning everything into bad dragon werewolf \textbf{sex} toys first.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I must be getting \textbf{old}, this guy sounds just like Bruce Dern, anyone remember the Movie "Silent Running"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Imagine all the nursing homes someday full of people covered in tattoos.  That's gonna look \textbf{weird}.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I work in a nursing home. When we put videos on for them it's always Lawrence Welk or some shit. \textbf{Old} folks in the future gonna be listening to Kanye and Beyonce. And the employees are gonna be like, "Damn, I hate this \textbf{old} fashioned shit!" Lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small There are already tons of \textbf{old} people in nursing homes with tattoos though they are mostly men. It isnt very \textbf{weird} and wont be that much different. I have worked with \textbf{elderly} people with tattoos and the main thing is small writing isnt legible but if you ask them they usually remember what it said and its a good conversation starter. I talked to a guy about his tattoos while killing ants he was covered in that he had gotten into walking outside. He didn't ever notice he had ants on him. Where we live its impossible to keep all the ants killed.\normalsize   & \cellcolor{green!27}Elderly, Old, Weird & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/103 & \cellcolor{green!27}2.913 \\  \hline
  \cellcolor{green!5}\small Tattoos are pure \textbf{t\textbf{railer trash}}. Our generation is screwed.\normalsize   & \cellcolor{green!5}Trailer trash & \cellcolor{green!5}Ethnicity - White, Social Class - Working class & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small When I'm \textbf{old}, I'm still gonna be smoking hooka lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Implying \textbf{old} people don't suck now.Edit: also implying the last generation didn't think the same way too.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Johnny Blaze right, since when have \textbf{old} people been great?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small You will be that new \textbf{old} person faster then you can blink.  That's how fast life goes\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Wait until the new, new people get \textbf{old}. God help us all lol.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Couldn't agree more a few year's ago I was at a Billy Idol concert and saw two females put their feet up on the back of the seat in front of them and take pic"s of their flipping shoes  F👺👺KING. \textbf{DUMB} AS HELL .\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small 'Here is the president of the country , yes they elected  a \textbf{woman} but the \textbf{old} white male govt made another person king, ain't happened since Bush. And it'll never happen again since we executed all the \textbf{old} white men in the revolution.'\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}3/43 & \cellcolor{green!27}6.977 \\  \hline
  \cellcolor{green!5}\small So funny , but true! My grandparents and great grandma had some amazing stories and photos to show me., I'm gonna be one of those horrible \textbf{old} ppl. 50 years from now when I'm 75, I'm not so sure I'll have anything amazing to show my grandkids 😬\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Some of the \textbf{old} people suck now. A lot of them are \textbf{crazy} acting like they're 50 at 75. Not like the REAL older generations in the past.\normalsize   & \cellcolor{green!27}Crazy, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small All the 80 year \textbf{old} grandmas will be coverd in tattoos from head to toe but they will be so saggy they will just be coverd in blotches and they will all be lesbians 😂\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small im imagining an \textbf{old} man with a slow cadence in voice saying this and it's funny\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small The dude is absolutely right. When your personal photographic record is \textbf{nothing} but selfies and what you ate at a restaurant it will suddenly hit you how useless and boring your youth was when you should have been out and about actually doing things. And don't blame your parents for buying you PS3s and iPhones. You made the decision to cry until you got them.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small My son says he likes \textbf{old} people is 13\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Funny how we make fun of \textbf{old} people when we are all going to be \textbf{old} if we live long enough lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Yeah. New \textbf{old} people are going to suck. They're going to have names like Lachlan.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Oh gee golly wiz \textbf{nothing} better than politically correct comedian... booooooooooring\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@You don't get to be offended by science! It's not that hard to live within your means. A lot of young people don't save money these days and instead of cooking at home, they opt for going to restaurants every night and fast food joints every day for lunch. I know people who make more money than I do per hour and yet I still have more savings and the way I know is because those people always complain about having little or no money. Young people want for too many things in this day and \textbf{age}. Less is truly more and the more you have, the less you're worth.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small You don't get to be offended by science! Most With tech jobs the number of young people who have high paying jobs is much higher than the generation before you, the \textbf{buck} stops here.\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small I feel bad for the millennials.  At least when I was under 35 we weren't tied to our phones/computers all day. I've got tons of stories and experiences of things I actually did out in the world in my teens/20s. going places, doing \textbf{crazy} stuff, being with other people. So many people this \textbf{age} are going to have \textbf{nothing} but stories about how they did \textbf{nothing} but look at memes or play video games for their entire teens and twenties. It's like watching a whole generation just throw their youth away on sitting around playing games....I could get behind people in their 50s and 60s doing that, because at that point you've lived a full live, and moving on to a virtual one as your body starts to slow down and whatnot makes sense. But seeing a 15 year \textbf{old} sit in their room all day every day for months playing minecraft is like watching someone die.\normalsize   & \cellcolor{green!27}Age, Crazy, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/157 & \cellcolor{green!27}3.185 \\  \hline
  \cellcolor{green!5}\small Wow, good point, and thank you for understanding, I'm 52 and a YouTube \textbf{junkie}. (Only when I'm waking up) other than that, I'm working, being outside, doing stuff. These younger kids are really missing out. I WISH I could be young again. Best times of my life.\normalsize   & \cellcolor{green!5}Junkie & \cellcolor{green!5}Behavioural Addiction - Drugs & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small thaaaaaaaaaat's a \textbf{fat} lie.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Jack Mars I work with 2 20 year olds n when I tell them stories about (simpler) times, (like when there was one phone attached to a cord hanging on the wall)they can't believe it.. oh n did I mention, they have the attention span of an infant..\textbf{nothing} is more annoying than tryin to talk to someone n they keep lookin down at their Phone!! THWAP!!' 🤦🏻‍♀️\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small Jack Mars pipe down \textbf{old} man before i unplug your life support\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@john wick watching some youtube videos for an hour or two here and there is \textbf{nothing} compared to the 19/20 years olds I know that sit and play online games for 12 hours at a clip almost everyday.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small I don't feel bad for them myself. \textbf{Nobody} ever made my mistakes or troubles, I did it myself. And \textbf{nobody} ever "felt bad" about my mistakes or troubles either. "Where's Bluto?" "oh he's in the hospital" "I guess surfing on that car was a bad idea" "Yep. Pass the ketchup"\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Lol obviously we go to stuff there arent enough \textbf{old} people to sell out full stadiums for games, concerts etc. Someones going to see Beyonce/Rihanna/All the Toy Stories and I gotta tell ya it's not people over 35. And the wing of a plane in a picture means you're going somewhere. We're addicted to electronics it's true but taking 15 minutes every 2 hours to smoke a cigarette back in the \textbf{old} days had to be just as distracting. We'll learn how to wean off of it just like you learned that cigarettes killed. I wouldnt worry too much about us we still value places and experiences we're just not sure how to document it in the best sense yet. Your photos had to mean something because film and photography was rare and expensive. Just because our way of life hasn't been fully formed or fleshed out doesnt mean you should feel bad for us. I think itll be interesting to see how we turn out. Sorry you wont be here to see it. But I'll be sure to tell you after\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/182 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small You can show them you were an \textbf{old} soundcloud rapper back in your day.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Grandad was a wild one back in the day. Just look at this tattoo of a...of a...melted \textbf{black} blob.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small "This is one a \textbf{hooker} drew on me for \$3 bucks at a strip club"\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Grandma...why do ALL \textbf{old} women have a butterfly tattoo there?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Stay in shape. Don't be a \textbf{fat} fuck\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@RONALD DAVID LEINDECKER \textbf{Tramp} stamp?\normalsize   & \cellcolor{green!5}Tramp & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Vito Scaletta I have. I just got off parole 2 and a half months ago. Lol. All my ink is \textbf{old} political prison gang ink. I'm "grown" up now and don't glorify that immature foolish life anymore.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Back when people were with themselves they were doing things too.People used to have newspapers (Which i have on my phone) Magazines (Which I have on my phone), they used to make their uninterested wife play chess on a physical chessboard. Now I can do it with someone who likes chess online on my Phone. Books? I read books on my phone every single day.What about listening to a record? I have music on my phone, I don't have to disturb others who don't like that music.Taking some notes? Browsing the Tv Guide? Solving crossword puzzles? I do indeed space out and think, feel or meditate but I'm telling you, people in the 'fake good \textbf{old} days' didn't have such a different life from now. The only difference is the people watching them sitting on their phone can't see what they are doing\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/146 & \cellcolor{green!5}0.685 \\  \hline
  \cellcolor{green!27}\small Funny, except that it's the people who are \textbf{old} now that are the worst \textbf{old} people that ever lived.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Oh,  you mean the people that are responsible for keeping this country afloat? Millennials are the worst generation to ever End up on this planet. They do \textbf{nothing}, just complain about how bad they have it living in their parents basement playing on their I phones and acting as if the world owes them something for existing. The ones that go to college are indoctrinated into thinking this country does not produce more charity for the entire planet than any other country on it. Safe spaces, cry closets, and endless lies with 0 evidence to backup any of their utopian delusions. Get over yourself, you must be one of them.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/110 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small Just fyi. They already suck in their young age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I think it's just a \textbf{weird} time... Y'all are pretty terrible rn too yno. As a matter of fact this joke pretty well describes my grandmother lol. There's always a counter culture that climbs out of these \textbf{weird} era's. People still won't be able work worth a damn, but I've come around to accept that this only benefits me by making me look good... \textbf{Nobody} has ever lived this way before. Like, all of history before the 1900s people were the same haha.\normalsize   & \cellcolor{green!5}Nobody, Weird & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/83 & \cellcolor{green!5}3.614 \\  \hline
  \cellcolor{green!27}\small Snook On the fly Everyone sucks. Young people are going around taking pictures with their stuff out, and the \textbf{old} people today just kinda post shitty slightly \textbf{racist} boomer memes on Facebook and dying of lung cancer\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Tbh people who are \textbf{old} now suck, too. \textbf{Racism}, \textbf{sexism}, \textbf{homophobia}... all quite \textbf{common} with older folks. Every generation sucks or at least has people who suck. They suck in different ways but they still suck. My grandpa thought that beating my brother and I over minor things was a completely normal means of discipline. I don't know a single person my \textbf{age} who would agree with that thank god.\normalsize   & \cellcolor{green!5}Age, Common, Homophobia, Old, Racism, Sexism & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - General, Gender - General, Sexual Identity - General, Social Class - Working class & \cellcolor{green!5}6/70 & \cellcolor{green!5}8.571 \\  \hline
  \cellcolor{green!27}\small If I've learned anything from the service industry....it's that everyone sucks: \textbf{old} people, children, and everything in between. Myself included.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small This is \textbf{racist} against Neanderthals.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small LOL!! Never thought of this! Its so right! What will the new \textbf{old} people have to tell .....\textbf{nothing} at all!! Only show a thousand selfies!!!\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Had me at 'new \textbf{old} people'\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small They teach you how to feel pain! Everything is 𝐩𝐚𝐢𝐧 when you're \textbf{old}!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small We are about to blow ourselves up, I don't see any of us twenty somethings getting very old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small You know how the millennials are always on tv saying their generations opinion counts more than the others and whatever cause they are the young people. I bet when my gen gets a little older and they are the \textbf{old} people they'll be yelling that their opinion counts most cause they are the \textbf{old} people. I've never seen a more self centered group. (Note I'm just generalizing I have friends and teachers that are millennials and they are great people just the ones that are always on the news for something bug me so much)\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/95 & \cellcolor{green!27}2.105 \\  \hline
  \cellcolor{green!5}\small And I'm \textbf{old} enough to know that this is inspired by (I won't say ripped off) of a Nick Swordson act from the mid 2000s.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small The caveman from those \textbf{old} Geico commercials has really done great things in his career.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small He looks so different from his \textbf{old} videos... he looks so hot now.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small IntrepidFraidyCat yeah, definitely need to do that at the end of every year... if it isn't interesting enough to keep at the end of the year, than \textbf{nobody} will give a shit in the year 2075!\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Ha but what about "Here's your grandma and grandma's \textbf{sex} tape when I got conceived"\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small I was just talkin about this very thing at my \textbf{old} work recently. That our kids as children are going to have a whole different experience with their elders. I'm already mourning the loss of the generation long before me. My dad's side of the family have amazing minds and they can tell you every little thing about growing up. This guy is funny and he Nails it. This is how things will be.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small the new \textbf{old} ppl are gonna suck bc liberalism\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Apple TV remote 😂\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small As \textbf{THOT} GRANNY GOES ON .... 'And here's a photo of people raving the streets like chickens with their heads cut off.... like a real Y2K except 20 years after originally warned about... the day the world went \textbf{crazy} because our phones and computer devices were rendered useless and that's why granny has no videos just photos and memories... of an era that almost ruined the entire human civilization.... with one video game.... '' FORTNITE.... oh wait that's not it... the name was FORKDITE.... no no that doesn't sound right either.... oh yes now I remember DORKFITE! That's the game ' 'it made children mad and teenagers madder. The parents had no care in mind... it was a terrible era... ''And don't get me started on this thing called a youtuber...'\normalsize   & \cellcolor{green!27}Crazy, THOT & \cellcolor{green!27}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/133 & \cellcolor{green!27}1.504 \\  \hline
  \cellcolor{green!5}\small Except, of course, for "Let me tell you about the time a third-rate businessman and reality TV host made a laughing stock of the entire \textbf{nation} by convincing people to elect him president."It's so unfathomable, future children are going to think it's a myth.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Millenials are an embarassment to the human \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Can't be \textbf{old} people if you execute their entire species\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I am mixed tooAm dark \textbf{black} and oil crude\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small We will have to explain all the \textbf{old} memes."What kind of meme is this, grandpa?" - "This is Jackie Chan looking perplexed. We used this when we saw some really stupid shit." - "Who is Jackie Chan?" - "Oh, this is a good occasion.*shows meme*"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small But seriously, we'll be the first generation of \textbf{elderly} people that will be able to show every bit of our lives to our grandchildren and through political change and acceptance we'll be able to tell stories of repression, \textbf{racism} and inequality in great detail. We'll be able to display through videos and photos how the world has become a better place.\normalsize   & \cellcolor{green!27}Elderly, Racism & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small He hasn't mentioned the \textbf{old} folks who will be former meme lords.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Universal sign of an \textbf{old} person's house = The garden globe.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small 50 years from now we're going to have \textbf{old} people partying late at night, driving drunk, riding skateboards.We do have some terrible \textbf{old} people coming.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small He compares two different types of people. Like there's not gonna be intelligent \textbf{elderly} people in the future.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Personally, I think those \textbf{old} people will be the best. I'd make my grandkids laugh their asses off with the stories behind those pictures\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Ill be rocking away to Billy Idol Gun's n Roses Nirvana    just a-knittin' and and a-reminiscin' about the good \textbf{old} when I dressed in \textbf{black} leather and had wild hair\normalsize   & \cellcolor{green!27}Black, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small This \textbf{nigga} is funny\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I think we all have pictures that mean a bit more to us, that we would keep 50 yrs from now. I also rarely post. Only when something interesting happens in my life but I might be a 22 year \textbf{old} exception to the rule, so I think my grandkids would have fun seeing me traveling and going through phases and stuff.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Think about what kind of "\textbf{old} music" we are gonna have our grandkids listen to"Now, listen here Jhonny, this one is a classic" plays the milkshake meme " Aah yes...""Katy! Do you remember this \textbf{old} song?" Post To Be starts playing Blasting Single Ladies in the kitchen while dancing the dance in front of grandkids\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small I hope I'm still around to watch them try to explain their \textbf{old} home movies (i.e., \textbf{sex} tapes) to their grandkids.\normalsize   & \cellcolor{green!27}Old, Sex & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small There is only one human \textbf{race}. Many tribes.Some \textbf{old} people are the ones who developed your laptop today.  Without them there would be no internet/s.m.\normalsize   & \cellcolor{green!5}Old, Race & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Ah yes, so much worst. Better not be too into uncessary photography and just work on being more like our \textbf{old} folks. Y'know a bit abusive, a lil bit of \textbf{racist} and a hella lot \textbf{homophobic}. 💁\normalsize   & \cellcolor{green!27}Homophobic, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}3/37 & \cellcolor{green!27}8.108 \\  \hline
  \cellcolor{green!5}\small Imagine showing your great grandchildren your \textbf{old} meme collection.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small yeah but maybe 50 years from now photographs would be so rare, its like the \textbf{black} and white photos now.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small old Doug Stanhope bit\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small The positive is that we have a more clear record of what we were doing with our lives...for better or worse.  It's a funny bit but \textbf{nobody} is going to look through all of anyone's photo collection nor would we want a story about each one.  I can't imagine my generation being worse than the Unaccountable Generation that attempted to raise me and others my \textbf{age}.  Also, it's fun to see pictures of people when they were young and having fun.\normalsize   & \cellcolor{green!27}Age, Nobody & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small Hey, young aspiring comedian, listen up. You are not funny. Not many \textbf{old} persons that I have ever met are like the way you are characterizing them in your boorish attempt to get some cheap laughs. The problem is not just you; it's also your audience and your peers. I was raised to respect my elders and that's because they were older and wiser. Values have seemingly fallen by the wayside these days. In the past 20 years I've witnessed outright mean and rude behavior in public by young people towards the \textbf{elderly}. It's sad and pathetic. You and your ilk should be spanked and sent to bed.\normalsize   & \cellcolor{green!5}Elderly, Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/108 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small My mother was white, my father was dark \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small With the fact that your ears and nose continue to grow and skin becomes stretched and less elastic as you \textbf{age}, it will be hilarious to see some members of my generation and younger walking around with 6' discs in their ear lobes!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Nothing new. Young people have always said this.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small No they haven't. Young people have always think that they're never going to grow \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I can't wait to meet a 90 year \textbf{old} "Britney" or "Dakota" or "Justin" in the nursing homes of the future....  :P\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I come from mixed marriage. Mom is \textbf{woman} and dad is man.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small The CURRENT \textbf{old} people are the worst we've ever had. Baby boomers. The undeserving, greedy, over privileged, over indulged wretches born from a generation of heroes. Heroes who died in their millions to stop what their disgraceful children would then vote into the heart of government.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Lachlan Patterson's \textbf{old} bit about Cat Personal ads is one of the best bits ever! Glad he's still rocking it!!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Thanks for posting this! I'm in my 40s and I just realized that my family photo albums abruptly ended in 2004. Blackberrys took over and all our images are in the clouds! How \textbf{crazy} does that sound?\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small 'in the clouds' 😂 ... \textbf{Crazy}, it sounds real \textbf{crazy}. Lol\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small This is funny. It's the reasons I hate people my \textbf{age} now\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Not like \textbf{old} \textbf{old} didn't suck... it's just different kind of sucking... /o/\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I don't think they'll be any pictures, lol, they will all be on \textbf{old} phones that won't exist anymore.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small You sound like an \textbf{old} person of today. Google photos, iTunes photos are a thing\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Chuggin Gigibytes what happens when they make a new input and you can't use the \textbf{old} one anymore? Like, your new computer doesn't have USB ports or they change them to force you to buy new stuff.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small 80 year \textbf{old} ladies showing their duck lips selfies.... 🦆 👄\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I have a feeling there will be some \textbf{weird} stuff in 50 years. Im sure it will be entertaning though.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small No the \textbf{old} people pave the way so u younger generation will have an easier life so learn to respect your elders motherfuckers or get bitch slapped 💪✊👊👊👊💥💥💥💫🤯😴\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I love comedy and this just felt like such low hanging \textbf{fruit}. The way he delivers jokes is pretty great-- he has a lot of potential-- but hopefully his writing improves. I haven't seen anything else from him, though, so maybe this was just an off day for him or something lol\normalsize   & \cellcolor{green!27}Fruit & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Old people now are racist\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Well hang on there folks. This generation of \textbf{old} folks has been given permission to forgo the shawl and rocking chair. I have photos of me riding horses. I'm 69 years \textbf{old} and I have friends in their 70s who  ride also and have photos.😉🐴\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Film cost us \$\$ \& time way back: go to the store, \$\$ to buy the film, go back home, load the film, take photos, unload film from camera, go back to the store to pay \$\$ to wait a week to get photos developed. Remember the \textbf{old} saying, "Don't waste the film!"....yeah, well that's an extinct expression. Digital photos now are free.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small The new \textbf{old} and we all don't suck\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Little snowflakes aren't even \textbf{old} yet and they already want to ban and outlaw and forbid everything: "That's offensive, that's misooooogynist, that's raaayciss!'"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Fitrian Hidayat not on all phones. Some have gestures- for example on my \textbf{old} phone you could swipe down with two fingers from top to bottom of the screen and with this phone, if you swipe your palm across the screen it captures the screen. I  tend clean the screen with the edge of my Palm so I always capture the screen!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Hmm seems odd. That has never happened to me! It must be an \textbf{apple} thing. I've only used an Android phone after i ditched my BB over a decade ago, and I've never had a accidental screenshot taken in my pocket. I have had some happen while I've been holding my phone in my hand, but that's different because I was actually touching the phone.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small No...no she wouldn't have. People weren't \textbf{tacky} and vacuous back then, like you are now.\normalsize   & \cellcolor{green!27}Tacky & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I know older people who had access to cameras and lots of  film and yes, they do have pictures of their  meals,   their pets, of the pictures already on their walls. Not kidding. They paid for professional photos, framed them, put them on the wall, and then got out a camera and took a picture of the pictures. Then, there are the thousands of slides, half of them taken from inside a car, so they are all through a windshield or window and have some car part in the picture. And they are like, "here is a \textbf{fuzzy} field of grass outside Wyoming, and this \textbf{fuzzy} pic of ducks is from Portland, and this blurry bridge is from  Portland, but the other one and here is my half-empty pool and here is a three leaf clover that I thought was 4 leaf until I got the picture back and here is my  rabbit's foot," and on and on.\normalsize   & \cellcolor{green!5}Fuzzy & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/158 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small The \textbf{old} folks busted their ass so we can be complaicent and comfortable and have something like a picture, which they cherished, at super easy access....its our generations job to make all of it global so its not just the US or 1st world.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I knew as soon as he started in on his \textbf{race} it was gonna be good...\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I have to say that may be pretty much what we get.  We have \textbf{old} people now who can tell you all about what went on at Woodstock, what it was like when President Kennedy was assassinated, how they eluded capture with the aid of Montagnard tribesmen after their plane was shot down in the central highlands of Vietnam, how they listened to Martin Luther King speak at the Lincoln memorial or how they stood with AIM at Wounded Knee.  Pretty hard to compete with people who were living the kind of life that most people today seem to be well insulated against.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small Race is everywhere\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Is this not the guy who played the Caveman in the \textbf{old} geico commercials? Lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small "And here's a photo of me at \textbf{age} 14 doing the ride the stick challenge" "ooh.. Me and ya grandma \@datsabutt was oh so good at that challenge.." "Them were the good ol days" 😂😂😂\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Andrew Eric But should anyone but a single \textbf{woman} care.?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small When i get \textbf{old} i expect 40 person lan games in the nursing home\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Just wait until all the \textbf{old} folks are barely able to drive and know how to work smart phones\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Funny yeah it's gonna be \textbf{lame} I'll talk about my favorite memes from 50 years ago that died a month after the fact.\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small F\@£ He is right ! I'm gunna be a terrible \textbf{old} person. OK, here's the plan..... Let's all do something amazing! Go, go do it now. Create a wonderful story that you can proudly share when you're an \textbf{old} fart! Do it ! Are you still here? 😂🤣😂🤣😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small The major difference between \textbf{old} people then and \textbf{old} people as they will be in 50 years is that the latter have way too much freedom in what they can document. Of course theres gonna be boring pictures when you live a boring life. Most exciting things already happened OR won't happen in our lifetime. I know it doesn't matter because this is a comedy skit and it ain't that deep, but it just makes sense that our pictures will be completely mundane when we look back on them in the future lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/93 & \cellcolor{green!5}2.151 \\  \hline
  \cellcolor{green!27}\small I think \textbf{old} people in 2070 are going to be less stuck in their ways and more intelligent\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small His reality is not mine! Life is an adventure or it is \textbf{nothing}!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That's what we're looking at if the demographic shifts continue and we have \textbf{nothing} but liberals in charge.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small My dad is one of these new \textbf{old} people. He has NO patience, refuses to learn computer basics.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Somewhere at some point, there will a \textbf{sex} video of your grandma dp and it's not you grandfather. Maybe you'll be scared, maybe you could learn something.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small He sounds exactly like \textbf{Jerry} Seinfeld!\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I turn into an \textbf{old} \textbf{black} guy when I get to that \textbf{age}.They got stories man.\normalsize   & \cellcolor{green!27}Age, Black, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}3/16 & \cellcolor{green!27}18.75 \\  \hline
  \cellcolor{green!5}\small Same here, I've thought this quite a bit over the past few years. The one point I really focus on is how absolutely ridiculous the \textbf{elderly} population is going to be in 50-60 years time when a quarter of their generation is covered in facial or neck tattoos. How are the children supposed to respect grandpa when he has "Hustler" tattooed in large letters across his neck?  Like the video says as well, what in the world is the conversation going to be like with the future grandparents of today? It's going to be a sad state of affairs I think.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small Well let's see, older generations had slavery, \textbf{Jim C\textbf{row}} laws, didn't allow women to vote, had terrible crime rates in the 80s and 90s (Gen Xers fault).  Millennials have many problems, but in many ways have more morals and empathy than previous generations.\normalsize   & \cellcolor{green!27}Crow, Jim Crow & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small Ehhhh most new \textbf{old} people are gonnas suck happend on the past gonna happen now\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small His \textbf{old} guy voice sounds like Abraham H Parnassus\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I was listening to "Bittersweet Symphony" by the Verve day before yesterday and my 12 yr \textbf{old} step son says "why are you listening to \textbf{old} lady music?"😬\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I know I'm getting \textbf{old}, it now makes perfect sense to pull my trousers up above my belly button. Comfortable.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Christ doing standup. Don't worry about any new \textbf{old} people, we have reached the end of times.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small When I clicked on the video I was like, those new \textbf{old} people will be so \textbf{old} they'll never see \textbf{old} \textbf{age}...cause they'll be dead before then....I can't look past 10 years. Can't even look past another year at this time before some DRAMATIC global shifts start happening.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}4/48 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small As was the statement between 1950's thru 1999.... here we are... It's almost 2020!! \textbf{Nothing} new, or said under the sun....the end of days happens EVERY DAY, at midnight... And EVERY time YOU decide to make a change in your own life, or a New product comes out that allows us to do things faster, etc. Jesus, or the translation thereof, said "these things that I do, you will do also, and even greater things you shall do"... Sooooooo, we're doing it... Jesus never said the world will End... All statements in the Bible state, "the world, as we Know it, will end..."\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small Yea they pulled the same shit global catastrophe on me in the 70's.  Then it was the new ice \textbf{age} and in the year 2000 we were all going to be ice cubes.  I wondered why waste time going to school if we're all going to be dead in 25 years.  Now they have much more media to make young people feel hopeless for their future.  This global warming/climate change crap always comes down to the same solution, emptying your pockets.  Notice the single use plastic garbage that is doing serious harm to the planet is never up for debate.  You're being played by our lying, rotten, corrupt ruling class if you buy into what they're selling.  Bring up banning 90 percent of plastics or making it from corn or hemp and see how far you get.  Those people couldn't give a shit less about the environment.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/147 & \cellcolor{green!27}0.68 \\  \hline
  \cellcolor{green!5}\small Just kinda? These are the same idiots that are supposed to pick up the slack when I'm too \textbf{old} to do it anymore\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Not really. It's just a joke. No one's actually gonna save every \textbf{lame} photo they ever took.And, there are still people doing exciting/notable things. Inventors still exist. There are still wars, and young people fighting in them.We take tons of photos of mundane things because cellphone camera photos are quick and free, and the tech is still kinda exciting and new to people.\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small He forgot that physical photos won't be a thing, and it be on some online storage, but there will be \textbf{nothing}, cause grandpa don't know how to use the new technology and accidently deleted the photos when he deleted his internet history.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Why does everything scare you people? You do realize that the children of today are going to be far more intelligent than what we were in the past, right?  A 9 yr \textbf{old} today can operate an ipad no problem. That is definitely something a child could not do way back when. I get it, getting \textbf{old} sucks and what sucks even more is feeling like we become less important over time, but that is no reason to be afraid or be bitter. Just enjoy the times, do good things and make memories. Not everything has to have some negative connotation to it. Times change. \textbf{Nothing} to worry about. I know it's the cool thing to say the world is fucked with this younger generation, but it really isnt. This younger generation is going to fix our fuck-ups. Just enjoy the ride.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/142 & \cellcolor{green!27}2.113 \\  \hline
  \cellcolor{green!5}\small Imagine an 80 year \textbf{old} wearing thrasher lmao\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small My dad is 94 years \textbf{old}. When he feels he's losing the argument, he calls 911. The police have been here at least 22 times. You'd think the police would arrest him for that...but they don't want to bring an \textbf{old} man into the station with a urine bag dragging on the floor. Ha!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/54 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Paul Weatherby  Haha. \textbf{Elderly} people can be so funny at times. My grandpa would have been 94 this year. He died 2 years ago. He had good humor and was great to be around\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small 🤜Stop torturing the \textbf{old} guy! Listen to his wisdom Ann's stop arguing LOL...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small At his \textbf{age}, I'd let him win every single argument. Give him the satisfaction of getting one over LolI'd give anything to be able to argue with my dad again.  💔\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small They should and you should commit the \textbf{old} resource draining dipshit\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small They should be arresting you. Arguing with a 94 year \textbf{old} must be a crime.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small If you guys were \textbf{African} in origin you wouldn't be alive neither you nor your grandpa SON ! Shot on the second 9 11 call\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Barry last and help him with his \textbf{Apple} TV\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The one great thing about getting \textbf{old} is you get away with things that would get you arrested if you were young.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@KamaraNoir hell, no. that's a horrible idea. he'll never hear the end of it. \textbf{old} people like to remind others how they were right that one time.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Good times...My 84 year \textbf{old} Father-in-law told me I was the only flower in his life...because I was a blooming idiot\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Your dad sounds like he should be in a home under constant supervision and care. Just don't argue with him and agree with everything he says(humor him) give him that at his \textbf{age} cuz the Police have more important things to do that settle arguments. That's such a sad story.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small \@taher tufenkeji lmao that's what the media portrays but its so far from the truth. I recently read a study that says that cops are much less likely to shoot an unarmed \textbf{black} man than they are an unarmed white man, this is probably due to the fact that whenever a \textbf{black} man gets shot by cops, people riot and there's a ton of backlash, no one gives a fuck whenever the same happens to \textbf{whitey}.\normalsize   & \cellcolor{green!27}Black, Whitey & \cellcolor{green!27}Ethnicity - Black, Ethnicity - White & \cellcolor{green!27}3/76 & \cellcolor{green!27}3.947 \\  \hline
  \cellcolor{green!5}\small Reverse \textbf{sex} skeletal structure entity\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small "Boy, this is a photo of a \textbf{woman} before they all were forced to become like men."\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small What does dark white mean🤦🏾‍♀️ hes \textbf{black} but acts like a white man? Uh... ....\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The new \textbf{age} grandma should be speaking in memes\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I love the \textbf{old} fashioned Grandparents lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small But the question is why are \textbf{old} people so fucking rude?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small You can see how some of the audience members stopped laughing and had a moment like, um...I have \textbf{nothing} but those exact photos in my phone lmao. This was brilliant\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Definitely jonah hill at 0:40. \textbf{Nobody} has pointed this out yet?\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Lame\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/1 & \cellcolor{green!5}200.0 \\  \hline
  \cellcolor{green!27}\small What's this guy \textbf{race} , i c some white mixed with something.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Y'all, I have no social media, still develop my photos at CVS and organize them into chronological albums, and to top it all off, I knit and collect hand fans. I WILL BE THE ALPHA ELDER\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small the worst part of the future \textbf{old} people.... is going to be how horrific \& disgusting they LOOK, with all their wrinkled \& saggy tattoos all over their entire bodies.... family reunions will be much like a terrifying horror show.   😆\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Never really understood why people make that comment lol. They won't look horrifying or disgusting, they'll just be saggy and wrinkled, just like literally every other part of your body. Unless you're disgusted by wrinkles and saggy bodyparts in general, in which case I suggest you stay away from all \textbf{elderly} people.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Idk what you're talking about, \textbf{old} people are gonna be awesome.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small the line up in the 2080 \textbf{old} folks storage facility,  Tiffany, Amber and Tyler, all with the same cat tattoo on their left tit looking like a giraffe sitting in their laps.  whining for their organic, gluten free, free range Olde People Chow.   I'm so glad I'll be gone WAY Before Then.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Funny video but we will actually be the best \textbf{old} people.'Grandpa I don't feel like school''Tell your father you feel sick and ill get you and we can play some dark souls'\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small the build up was super funny, the concluding joke wasnt too funny. it made sense and it was logical but too relevant to the point it was a bit dull. he shouldve been like, "and here are some of many memes made from video games clips, movie clips, tv show clips, and porn clips from when your grandparents were young adults. here are some tweets your grandma retweeted, oh, trump? we try to forget those years. but heres your grandads snapchat history, he loved posting videos of himself and the friends at frat partys. that hes holding? oh, thats a wizard staff. theyre beer cans. and heres your great grandma ripping a \textbf{bong} back when she went through the hippe new \textbf{age} movement, here are videos of her hula hoopin using nearly all her body parts.  yes, she had dreads and no she is not jamaican, shes from california"\normalsize   & \cellcolor{green!5}Age, Bong & \cellcolor{green!5}Age - General, Ethnicity - Aboriginal & \cellcolor{green!5}2/149 & \cellcolor{green!5}1.342 \\  \hline
  \cellcolor{green!27}\small Mixed \textbf{race} here too, my father is white and my mother viridian who-ite.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Oh \textbf{age} will come for you and you will remember what a fool you are....hahahaha.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Said literally every generation about the next one in line . I understand that you're coming to an \textbf{age} where you're starting to feel irrelevant, but no one's interested in your midlife-crisis rants. Thank you, next.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Pure gold !!! And im gonna be one of those \textbf{old} people !!!!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small the future \textbf{old} people are gonna be ruling the internet.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Scarily accurate, but hopefully today's millennial snowflakes will have melted due to \textbf{mental} overheating because they got offended by everything\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I laughed so hard! I needed a good knee \textbf{slapper}! Thank you!\normalsize   & \cellcolor{green!27}Slapper & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I like this guys humor.👌😂 He ain't lying, \textbf{old} people in 50yrs are just gonna be constantly Outraged \& Grumpy.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The young people who are in college now most likely won't get \textbf{old} because everything in the world offends them. They can't handle life.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small old people in 50 years will be awesome because their needs will be automated so their lack of efficiency will allow them to chase their hobbies more without suffering things like bad hygiene or the inability to go to the grocery store.  had a hard time following the logic.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Michael Stevens , I'm already the new \textbf{old}. I use my camera to take pictures of what I can't focus on anymore. Like med directions, stuff I've dropped under the couch or car seat... take a picture and blow it up!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small I see that \textbf{Weird} Al's newer looser, loopy curls are becoming a thing.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Go fuck your mother's hipsters. Pure boring garbage. Soft weak shit and you try to pass it off as intellectual humor. What did the applause sign tell you to clap and laugh? Die in a fire! \textbf{Pussy} shit!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small That was good.... and I'm old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Listen to joke about the new \textbf{old} people, talks about it being 50 years from now, realize that I will be 80 in 50 years, here we go existential crisis...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small The jokes are great but why does it sound like he's doing a Jack \textbf{Black} impersonation?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Being Me I think Ali Wong had some lines about having \textbf{sex} with a homeless guy in Baby Cobra.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Being Me I've been homeless on and off for the last six years. And while I lack the esteem (and narcissism) to consider myself hot, I don't think I'm unattractive. I'm in decent shape, I take care of myself to the best of my ability, and my hygiene, while not exactly top notch, isn't so abysmal as to make me look like I crawled from a burning dumpster. Hell, in all honesty, I know more fairly attractive homeless people than ones that look like your stereotypical \textbf{bum} (not to say I don't also know a fair amount that look like the cumulative crust under Zoidberg's ass flaps). It's not outside the realm of possibility, not even necessarily uncommon, for a \textbf{bum} to be good looking. It's easier for people to think of all houseless folk as unkempt, haggard, ugly, drug abusing drunkards, I guess, although those are only a part of a much larger demographic consisting of all races, ages, and genders. No skin off my back, though. It always amuses me when such narrow minded, bigoted, or simply uninformed views are proven to be false.\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}2/186 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small The best thing about having \textbf{sex} with a homeless person is that after you're done you can drop them off anywhere.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@RecoveringChristian you made me do a little shriek right out loud (got a couple of \textbf{weird} looks) well-done hilarious stranger, well-done 😁\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small The emperor is nude and that \textbf{chick} is a dude....all at the same time.\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small He reminds me of those \textbf{old} caveman comercials, like the ones where they became "modern"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@everywhere at the same time Im sorry have to go here what they took a kodak picture wtf are you talking about were you there oh if he is real 90 percent of you are going TO shit your pants when you see him what he looks like he is not white god is not white god is not jesus god is a being fyi he wont look like dude doing comedy nor kenny g no offense to ken g nor like the \textbf{black} felt picture asains sell to \textbf{black} folk You know the cool buff athletic built long braids jesus no one knows til that day if i wasnt human i would have went into religion for money cause you all are ez but im not put together like that\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/131 & \cellcolor{green!27}1.527 \\  \hline
  \cellcolor{green!5}\small I thought he was like a \textbf{skinny} caveman\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Iron \textbf{Snowflake} bitch you look nasty. White males hate white bitches like you.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Tsk 😒 thats \textbf{nothing} . I was homeless and hot. Arizona heat is no joke.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Old Snowflakes and Millennials will still be living in Nana's basement.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It's  good thing that most will die within the next 10 years. There is a threshold of \textbf{weird} we dare not cross before war, famine or disease roll in to cull the idiots straight off. You will be fine. If you have have the stomach for a  brief stint with Hell on earth.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small My Grandparents never had any stories....'What's this Grandmother....?' 'Oh this is my cousin whose my Aunt, whose related to my Mother's fathers side...twice removed Grandchild of your Grandfather. She was killed by escaped \textbf{pigs}...'\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small 2019: In the nursing homes today, the folks listen to classical music, big band, 50's and 60's music. 2059: \textbf{Old} people listen to Justin Beiber, Lady Gaga and Tupac\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Your going to get \textbf{old} one day also lol.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small The next generation of \textbf{old} people will be highly depressed,  without any relation to past,  cause all changes so quickly and innovate constantly that there is \textbf{nothing} to be attached to anymoreTrue love and sincere relations,  appreciation for simple things in life,  the pleasure of admiring and care for nature,  \textbf{nothing}... Once they loose their likes on Instagram it's all gone!  Life is overBillions of zombies waiting death without any meaningful experience in life!\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/76 & \cellcolor{green!5}3.947 \\  \hline
  \cellcolor{green!27}\small Sure that was funny and true, but there's \textbf{nothing} else funny about a culture trapped in the hellish and cheapened nightmare of social media. It's actually sad and empty, going nowhere in this digital hellscape.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Me and him We're the same race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small There won't be many new \textbf{old} people around. The younger generations will die of diabetes, CVD, depression and suicide.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I take pictures of my food but that's because it's an actual group \textbf{old} fashioned cooking. It's not like I'm going to keep those pictures to show my grandkids.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small What he is trying to say is millenials suck, and have \textbf{nothing} to show for themselves\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small The funny part is he thinks this SJW generation is smart enough to make it to \textbf{old} \textbf{age}. They literally play in traffic. (and dont understand why genitals exist)\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small The new \textbf{old} people seem to be starting early.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I have never thought of that concept, new \textbf{old} people yikes!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small 50 years from now, SJWs will become the new \textbf{old} people.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Grandson: Grandma, who's that in the picture?Grandma: Oh, that's me a convention in Baltimore. I can't think of what that man's name is, the man to my left.Grandson: A convention? What kind of convention.Grandma: It was a convention-, it was kind of like comic-con, but it was about this kids TV show called "My Little Pony". It was a huge fad back then, but after the show ended, the fad sort of died-. . .I think the convention was a called "brownie-con" or something like that.Grandson: . . .you grew at a \textbf{weird} time.Grandma: Yes, I know. We did all sorts of \textbf{weird} things back then. There were conventions held just for people who wanted to stand around dressed in animal costumes. I think they still hold those conventions, but I have never been to one.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/141 & \cellcolor{green!5}1.418 \\  \hline
  \cellcolor{green!27}\small He looks like the \textbf{common} depiction of Jesus!\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Can‘t wait to see \textbf{old} people playing Bingo with a „Viva la Vida loca' Tattoo\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Why is everyone fat\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Sadly this isn't so funny.... WORST \textbf{old} person right now: POTUS.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Smart to attack young people when the average \textbf{age} of your audience is 60\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I am mixed \textbf{race}.  My mother was white and my father was more white\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small That \textbf{Apple} TV joke hit home😂\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small MIllennials made it cool to be \textbf{old}. You morons know the 90's are over right? Every other generation hated the previous generation, not millennials with the way they ride the jock of gen x.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small milennials are YOUNG.. the \textbf{old} folks attacking them are ones that evidently havent done enough around the young people in their lives!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/22 & \cellcolor{green!27}13.636 \\  \hline
  \cellcolor{green!5}\small Ah the good \textbf{old} days. O my dear sweet grandchild those times were liiiiiiiiiiiiiiiiiiiiiiiiiittt.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small God, he'll have to explain the context for each one too cause no one is gonna understand 99 of the \textbf{dumb} memes out now in 50 years.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small we are living in the golden \textbf{age} of memes\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The only thing I've done with my lifeHonestly speaking to \textbf{elderly} patients is interesting when they've seen the world change so much and they had good musical taste good bands they got to see live and the places they went to i get that we still have good stories from people who did the same sort of athletic races and travelling the world and there are many many soldiers but ooft we have gotten cringy day to day\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Wisdom is becoming extinct. These "new \textbf{old} people" will be stupid. Government school stupid.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small better then looking at all the \textbf{old} photos of \textbf{homophobic} and \textbf{racist} people\normalsize   & \cellcolor{green!27}Homophobic, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}3/13 & \cellcolor{green!27}23.077 \\  \hline
  \cellcolor{green!5}\small Old people already suck, they're just gonna suck even worse\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Fond memories of teaching the \textbf{old} man to use the vcr and DVD player 😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small what happened to this comedian?  He used to be a hunk!  Now he looks like some new \textbf{age} guru :)  Total transformation, barely recognized him.  Still funny, that is what really counts.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small My father is Czech and my mother is Danish, that was considered mixed \textbf{race} when they married 60 years ago.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Reminds me of another stand up about \textbf{old} peoples war stories, compared to what will be our "remember that episode of Seinfeld?"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Jokes on him, I'm 26 and I've already been an \textbf{old} curmudgeon for years.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small We got some terrible \textbf{old} people coming!😄😄😄😄\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Perfect.  The Millennials think they are so important, yet they have achieved \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Will you do better? Just wondering. Before I was a teenager I had a great life living my family, uncles, aunts, grand parents, although my parents got divorced when I was still 6. After that in my teens things got more complicated. Lived with my mother (and three siblings) who had to make it alone as a single parent. I never got into being a rebel teen. I studied hard at school. Literally sitting in the front row in every single class. I focused on studies to get my mind off the constant lack of money in our family. After high school I worked for a year and then went to uni. I studied hard there as well. Same thing sitting in the front row and always taking notes and revising, doing assignments. I never went to parties, didn't drink, didn't do any drugs. After uni I thought I was ready to change the world, lol. Started working in Finance and work quickly puts your delusions away. You find out that \textbf{nothing} is about you. You are not special. You start from scratch doing really simple and boring tasks. Even later on as you progress, \textbf{nothing} at work is challenging intellectually. It's more about how much of the same you can get done, and about resolving differences between people and fixing processes in the team. So more psychology involved really, which they never teach you at school unless you pick it as a subject but even then I wonder how much of it you could put into practise at work. Also in the wider context like the job market you realize how competitive you have to be. Anyway, my point is when you're young it's easy to overestimate yourself and think you're better than the older generation because you are learning a lot of stuff at school and uni, and are up-to-date with all the cool new tech around, and therefore are well on your way to achieving amazing things. But believe me, once you start working and finally have to take on responsibilities on your own in your life, you're opinion of yourself will readjust itself and you will see that achieving great things is not for the majority of people, and your dreams will become more realistic, such as getting a pay increase at the end of the financial year. And trust me just that on its own is no easy thing. Employers will not give you that little increase for \textbf{nothing} or for little. You would have to pull over time during weekends and during the week. Taking on responsibility for tasks and issues at work that have \textbf{nothing} to do with your job role. You will have to demonstrate all that and document it and show how it results in the company permanently saving money each year. Not to mention the company politics with different people in high positions such as managers, team leads, and them hindering your progress because of something you said the wrong way once, or because they want to promote their friends instead of you. Also thinking about starting a business in the current economic conditions? That's going to be harder. I know because I am attempting that too and have family runnig a business. That doesn't mean you can't achieve great things, it just means it is really hard to do and would require your entire focus, time and effort, and even beyond what you can give. Achieving great things in life is not as easy as you think. Same in relationships. You would date someone. They would most likely reject you at some point for various reasons. You will find out you are not as awesome as you think and not a \textbf{chick} magnet. Each break up would result in you either having a lower self-esteem or ending up becoming more and more detached from the people you date, if you do get a date. If you are lucky to find a person serious enough to have a long-term relationship with, you would have to struggle through compromises to please them and try and balance their needs and preferences with yours. And if one day the person decides to leave you, you would have to pick up your life again and try and build something or maybe just live in dispair and be alone. It would be harder if you have children that have to put up with their parents' divorce. Life is not a straight forward path to success. Life is about struggling and it will demand the absolute best from you and will push you to your limits (physical and intellectual) and beyond. You will ask for help but most people can't help and those who can, can only do so to a point. Life is about doing the best you can and hoping for the best. And working with and being friendly with others makes it a lot easier. So yeah, don't be so quick to judge millenials if you are still young and have not yet lived through what life can throw at you.\normalsize   & \cellcolor{green!5}Chick, Nothing & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}5/848 & \cellcolor{green!5}0.59 \\  \hline
  \cellcolor{green!27}\small The reason why there is \textbf{ageism} in IT is because boomers are lazy and entitled, and don't feel the need to learn anything new to keep a 6 figure salary while adding no value to the organization.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small You're \textbf{nothing} more than an il-informed ignorant \textbf{old} person. You come from a time when the economy was booming. Your housing, education and healthcare was affordable, and you could easily work, buy a house, and support a family by your mid twenties. These days young people work MULTIPLE jobs, if they want to be able to afford their own shitty place. And if; god forbid you want to study and live on your own, you'll need to rent a shared house with 5 other people just to be able to afford rent. Young people of today work very hard, 10 times harder than you ever did, just to be able to afford to live, and they are rightly so; very unhappy with the world your generation left for them. You're know \textbf{nothing} about world history, if you truly believe that today's generation are entitled, and lazy.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/146 & \cellcolor{green!5}2.055 \\  \hline
  \cellcolor{green!27}\small \@Andrew Taylor I wouldn't call this guy \textbf{old}. He's just highlighting what is happening in the real world. And it IS bloody childish and inane to photograph a meal then tweet it to the world. Who gives a flying fuck?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small ..and what are yall doing in the present? Millenials aren't the ones leading y'all are and sadly society has slowed since you've been leading. Just take a break \textbf{old} man it's our turn.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small the new \textbf{old} people are going to become the lost generation of the west. and look at how chinese view their lost generation\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Very funny young man , from a new \textbf{old} person :)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I love the \textbf{old} people who are so \textbf{old} and just don't give a damn about anything of anyone anymore. I love listening to their rants. My grandmother was great at that.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small For many people it starts at middle \textbf{age}, you start giving a shit less and less about things that bothered you to death when you were young\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small +cellgrrl   When you get \textbf{old} enough, you hate the leftists and want to piss them off. That's the point.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small His first joke is a rip-off from Michael Blackson. I am mixed. My mutha is \textbf{black} my fathuh is dawrk \textbf{black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small I always like \textbf{old} people. know them from being born in 1870s. harder there life was the sweeter funnier more interresting they are. we are the dorks and it just going to keep getting worse. if there a here after its the \textbf{old} timers fires I want to set around and hear the wisdom and wit.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small The only flaw with this otherwise really funny and eye opening skit is that it assumes that \textbf{nothing} about the world will change in 50 years, and that the mundane and rather uninteresting things we document everyday are going to stay that way in the future, maybe in 50 years humans will be traveling in tubes that go across the globe in an hour and planes are a thing of the past, who knows?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small When I'm \textbf{old}, falls will increase because all these \textbf{old} ladies will be trying to twerk while their walkers are across the room.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Old people are already awful\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small same \textbf{old} jokes \textbf{nothing} particularly new or funny here\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small I'm 22 and glad to know that I won't suck as an \textbf{old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Old people are already fragile, but now we're gonna have a new type of fragile \textbf{old} people.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small \@Psychedelic Lizard A lot of them aren't going to get \textbf{old}. No exercise, awful diet, social isolation, clueless about what to do in an emergency, can't form relationships, no home skills etc, etc,\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Dont want to see the currant snowflakes as \textbf{old} people.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Psychedelic Lizard you're confusing baby boomers with generation \textbf{snowflake}, sadly the children of baby boomers. Or the grand children. One or the other. Baby boomers still got stories to tell\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small We are gonna be the fragile \textbf{old} people who don't wanna admit that they're fragile\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small exactly...people today suck...i may be \textbf{old} but i got to see all the cool bands...people today got to see kuntye west yelling "fuck" in the oval office with dirtbag donnie trump.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small I can't wait to see an 80 year \textbf{old} man in \textbf{skinny} jeans.\normalsize   & \cellcolor{green!27}Old, Skinny & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small How about an 80 yr \textbf{old} \textbf{woman} with a \textbf{tramp} stamp\normalsize   & \cellcolor{green!5}Old, Tramp, Woman & \cellcolor{green!5}Age - Over 65s, Gender - Female sexuality, Gender - General & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small crazyoldbroad No one with a \textbf{tramp} stamp will live to see 80\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Mick Jagger...\normalsize   & \cellcolor{green!5}Mick & \cellcolor{green!5}Nationality - Irish, Religious Identity - Roman Catholic & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Give it a few years, The Rolling Stones can't be too far away from that \textbf{age}. 😋\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small "I can't wait to see an 80 year \textbf{old} man in \textbf{skinny} jeans." And a "man bun"!!!!!!! OMFG!!!!! LOL\normalsize   & \cellcolor{green!5}Old, Skinny & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small \@crazyoldbroad Umm,thats \textbf{dumb} shit. A tattoo is forever clothes are not,not even in the same ball park. I have tattoos covering my arms,some on my face \& hands.  Got them in my 20s, im 50,guess what. They didnt wash off,so im pretty certain ill have them when im 60,70,80,\& if I make it to 100. Theyll be faded unless I have them touched up,but still there. So a \textbf{chick} with a lower back tattoo at 18,will most definitely have it at 80. You must not understand tattoos,science,\& biology idgit.\normalsize   & \cellcolor{green!27}Chick, Dumb & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small Better than \textbf{old} ppl in pants that don't reach the top of their ankles\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small A lot of guys look fucking \textbf{dumb} now\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small damn i'll be an 80 year \textbf{old} man in \textbf{skinny} jeans and vans... sad to think that will be the suspenders of the future😂\normalsize   & \cellcolor{green!5}Old, Skinny & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I think most \textbf{skinny} jean wearers are so narcissistic and self aware of how they look they would never wear them in \textbf{old} \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Old, Skinny & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}3/24 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@crazyoldbroad That wouldn't be long.   Some baby boomers have \textbf{tramp} stamps.   Yuck!\normalsize   & \cellcolor{green!5}Tramp & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small 30 yr olds already look ridiculous in \textbf{skinny} jeans.\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Skinny Jeans and Jordan's\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small How about an \textbf{old} \textbf{woman} with super tight tights\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small Adults have been dressing like teenagers for decades. Dickheads in shorts and trainers (sneakers). Put on some trousers and shoes, you undignified \textbf{old} bastards!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Theres no guy that looks good in \textbf{skinny} jeans no matter what \textbf{age}. Yuck! And man buns 🤢. I think the social \textbf{engineers} of this generation were laughing their asses off when they thought up these.\normalsize   & \cellcolor{green!27}Age, Engineers, Skinny & \cellcolor{green!27}Age - General, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small My mother bought my dad, he was 73 at the time, some pants. He put them on and I couldn't stop laughing because they were \textbf{skinny} pants lmao 😂 I wish I would have taken a picture\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small 80 year \textbf{old} hipsters are gonna be the equivalent of the \textbf{old} hippies we still see around today\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Go to California, they're all over the place. In fact, tell me if you don't see a pair a \textbf{skinny} jeans, that's survival mode.\normalsize   & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I think my teacher is but idk his \textbf{age}... he just old\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Isn't the great thing about \textbf{age} that you stop worrying about frivolous things like wearing the right fashion? Parents aren't supposed to look hip, they're supposed to look functional and reasonably stylish in a middle of the road way. You know you're getting \textbf{old} when elasticated waistbands become a sensible idea. If an 80-year \textbf{old} man was wearing \textbf{skinny} jeans, it'd be because they'd been in his drawer for decades and he's still getting the wear from them. Maybe by then, rampant consumerism will have been dismantled to save the planet and everybody will own unfashionable jeans they've had for decades.\normalsize   & \cellcolor{green!5}Age, Old, Skinny & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}4/101 & \cellcolor{green!5}3.96 \\  \hline
  \cellcolor{green!27}\small What 80 year \textbf{old} still dresses the same as they did 50 years ago? \textbf{Old} people dress for comfort, so by then we'll probably switch to PJs\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small When have \textbf{old} ppl not sucked? \textbf{Old} \textbf{age} itself sucks, and inevitably we follow suit.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Hey \textbf{snowflake}, what about stolen comedy... Norm Macdonald had almost the same bit on the last David Letterman\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small That's great, and next year is \textbf{sex} ed, they'll teach you what a hymen is. :)\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small You would like \textbf{Chubby} Brown\normalsize   & \cellcolor{green!27}Chubby & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Ruddy Relent I was just thinking about this topic in the morning, how the next \textbf{old} people are going to be failed twitch streamers  youtubers and instagram influencers, this are \textbf{common} topics this days that many comedians will inevitably end up talking about, it's more about how you structure them as jokes what really matters which I think this guy did very well.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small I agree. I can do some \textbf{old} blue comedy, but clean is refreshing. Brian Regan is another clean comic.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Something \textbf{old} people say\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small "... we got some terrible \textbf{old} people coming..." 😂😂😂 Dying and crying with laughter\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Boomers already suck as \textbf{old} people. \textbf{Nothing} worse than \textbf{old} narcissists.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small ...and the \textbf{old} people after the new \textbf{old} people are going to really really suck!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small I can't wait to see an 80 year \textbf{old} juggalo drinking Faygo.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small The new \textbf{old} people are going to be beating down by a system created by the \textbf{old} \textbf{old} people. Low wages high rent horrible economy. None of the new \textbf{old} people will be able to retire cause they are supporting the baby boom era.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/44 & \cellcolor{green!27}6.818 \\  \hline
  \cellcolor{green!5}\small \@Luke Warmwater Still remember that from my childhood. Brr. Forced to watch half an hour of palmtrees and buildings that mean \textbf{nothing} to me.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Luke Warmwater I remember when people used to have photos of their kids in their wallet. I had \textbf{old} girlfriend's photos in my wallet.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small All these mobile phone obsessed jerk offs, they make me sick. Stop following the crowd people: just get a small group of decent people, turn off the tv, the talent shows, the gossip, turn off your phone, un dye your hair from the silly color you've done it in, turn off cardi h or whoever you listen to and grow up. I'm 27, i like some people in my generation, but only some, there are only a few cool and intelligent people in the world, but most people have the \textbf{mental} agility of bird shit-- they're not worth it. I love \textbf{old} people, why?, because they talk to you like a human being, they tell you \textbf{old} stories about their life, they're warm and don't have to put you down with some stupid fucking comment with no regard for you or your life, and they communicate with you properly instead of grunting and texting and wearing \textbf{skinny} jeans and some goofy fuckin shoes. \textbf{Old} people are way cooler than my generation, my uncle is a Buddhist and was a hippy in the 60s, he tried to follow the Beatles to India but him and his pals only got as far as Greece!, he's cooler than any guy i know, you sit beside him and he doesn't even have to speak and you feel good around him, unlike all these girly little try hards.\normalsize   & \cellcolor{green!5}Mental, Old, Skinny & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}5/233 & \cellcolor{green!5}2.146 \\  \hline
  \cellcolor{green!27}\small * damn, you've got us there... our Instagram pics are wayyy too vane, we should go outside and follow in the footsteps of our great wise predecessors... oh, great \textbf{old} one, which \textbf{ethnic} minority shall we cleanse first? Which culture shall we insult? Which \textbf{gender} or \textbf{race} should we oppress next? You guys really did it all in your prime before everything got fucked over by the guys in charge when you were older\normalsize   & \cellcolor{green!27}Ethnic, Gender, Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Gender - General & \cellcolor{green!27}4/74 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small \@Madeleine Grayson nah I'm a 25 year \textbf{old} millennial and my mom is a baby boomer. And I'm like the youngest of the millenials. Cutoff is 94 I believe, I'm 93\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Oh look, \textbf{old} people blaming the younger generations cause they dont wanna admit they f*d up...how not stereotypical 😒\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Goinggoinggone123 aye I'm really curious about who was the sexually predatory tv host? Not asking you to confirm but I would like to look his \textbf{dumb} ass up, I've actually never heard of him\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small No. Gen Z is the worst. They  be doing all that \textbf{dumb} shit like eating tide pods, disappearing for 48 hours and the Kylie Jenner lip challenge. As a millenial, I cannot be bothered with any of that.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I'm pretty sure \textbf{old} people in 50 years will be talking about 911\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Ha! I cant watch my \textbf{old} man do something like that I just take it from him. I got it pop please let me lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small old people suck already!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Oh man, that is going to suck. Hell - when I'm \textbf{old}, I'll be surprised if any of my harddrives or ... memory sticks even work without having corrupted files in em... and even if they did, out of the 25000 photos probably handful have actual meaning.Man, I should take time to print out my actually meaningful photographs.... but hell, so I've planned for the past 10 years now.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small I have started printing pictures every year. At least 30-40 pictures each year because I'm afraid the hard drives will be corrupted by the time I get \textbf{old} and will have no pictures left.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Going through ur nannies insta \textbf{thot} pics in 2079\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Hit or miss Ha I guess u never miss ha , that was funny when I was young , grand son looks at u like how \textbf{dumb} were u guys lol\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Alinity = ultimate Thot\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Bonechip il be 78 years \textbf{old} in 2079😭😭\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small We need a good mixed \textbf{race} comic these days 😆\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Why mixed \textbf{race}?  When I want a good laugh, I really don't care WHO makes it happen.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small RACIST IDIOT !!! LET IT GO !!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Yeah we need a good mixed \textbf{race} trans, paraplegic,epileptic  vegan just so u feel like a good person\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Mark Brown Who the heck cares about what \textbf{race} the person is? If they're funny, they're funny. Does it really matter?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Old people from every generation suck.  Because they get bitter about not being cool anymore and make sure you know it.  And we're always glad when they are gone.  And our kids will be glad when we are gone.  It's the natural order of things for the new to replace the \textbf{old}.  Fuck 'em.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small People pull this kids-these-days crap all the time. Google "\textbf{weird} vintage photos" and tell me no one did pointless pictures for fun in those days too.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I'm mixed too. I'm \textbf{black} and dark black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small spike witwicky oh, like the difference between night and later that night.\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Green that's a color. Dark green means making green look more intense by making it look less lighter and more heavy by adding a dark color perhaps lets take \textbf{black} to mix with green which will make it more darker than it is i.e. less lighter than what it is now. So white. Let's make dark white. So we want to make it less white or less lighter white than what it is. So mix it with \textbf{black}. Voila we get a faint grey. But it still looks white. But its less bright white. So its dark white than what it previously was. Dark literally means go dark/unlit/night/no light just darkness. So dark white is basically white becoming less white. Similarly dark \textbf{black} means making  \textbf{black} more \textbf{black} or more intense \textbf{black}. So the whitest of white is the brightest of white and the blackest of \textbf{black} is the darkest of black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}8/152 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small You know \textbf{black} and dark \textbf{black} aren't colours right, you colourless p.o.s?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Im \textbf{black} with a mix of blacker\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@jairdabrini if you think there is only one \textbf{black} then you are very wrong. Some paints include matte, satin, flat, automatic, midnight (purple hue), and twilight (gray undertones) just to name a few. Some have to do with straight up color or the type of finish.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@jairdabrini how is \textbf{black} not a color?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small spike witwicky got a buddy who's half light skinned and half \textbf{r\textbf{ed}} boned.  He gets mistaken for Latino!\normalsize   & \cellcolor{green!27}Red, Spike & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Religious Identity - Protestant & \cellcolor{green!27}3/18 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Like redbone mixed with yellowbone? Or just \textbf{black} American mixed with \textbf{African}? 😉\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small \@Warclubz then theres \textbf{african} \textbf{black} which has purple highlights\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small I immediately can judge whether or not you are a stable cool person by if you have selfie's plastered everywhere on your social media accounts.   Any girl who takes a shit ton of selfies you know has \textbf{mental} issues and you should stay away from.  Anyone who is in love with themselves that much are creepy.  Dont date them.   Also it tells you a lot about women the fact that far more women do it than men and yet we are told how superior women are to men in our culture, I call bullshit.  The selfie thing proves that.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small Mixed \textbf{race} too. My father was white, my mother was off-white.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Yep, he had to open up with the pc self hating white jokes... make sure they keep that evil \textbf{whitey} narrative alive. I hate pc comedy.\normalsize   & \cellcolor{green!5}Whitey & \cellcolor{green!5}Ethnicity - White & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@0121 same. Chick's want my babies because I have a \textbf{weird} hazel eye color and they think it'll transfer\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small B Cage He is mocking PC culture if anything. Alexis Pruitt \textbf{race} baiting makes for an exhaustingly shitful read 🙄\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Lee Churchill Iberian people are \textbf{black} whites! I don't even know how u can call some Portuguese white people. They are darker than some of our \textbf{black} people.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Alexis Pruitt May I enquire as to what criteria you used as a measure of \@b.cage to be a \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Alexis Pruitt that goes for \textbf{black} folks too bro. I'll be extremely nice to some of them and they keep hating on me\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small My kids have are a mixed \textbf{race}.  I'm white an my wife is transparent.  Unless the sun is out, then she is as \textbf{r\textbf{ed}} as a fire truck.\normalsize   & \cellcolor{green!5}Race, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small \@lee chuchill blessed be the \textbf{fruit}.\normalsize   & \cellcolor{green!27}Fruit & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small It's becuz we can take so many pictures now for \textbf{nothing}. When a pic cost lots of money, you waited for something special 😂\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Is this really considered funny? Honestly, the only part I find interesting or funny is that we'll one day be sharing about the past with our grandchildren. We'll be the very best \textbf{old} people i think because we had the best example come before us.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small THINGS YOU CAN'T MAKE FUN OF-Anything but \textbf{old} white people.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small He's mixed race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small reminds me of jesus for some \textbf{weird} reason\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Old people are terrible now.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small That was just funny as fucking hell !!! and true ...... btw dont make fun of multi ethnicities . I the product of a white angry Puerto Rican \textbf{woman} and deep south Georgia boy  who never shut their bedroom door when they were fucking ..... I'm totally fucked but I have stories and that's what matters ; )\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small old people 50 years from now will be covered in tattoos with body piercings.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Make some changes or else what? Young people will make fun of \textbf{old} people? That's been happening for millennia, and there's \textbf{nothing} you can do to stop it. Relax.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small don't be so hard on us. we're not becoming as \textbf{lame} as you might think. technology only allowed people to take a very limited amount of photos at a time. nowadays, people can take unlimited photos and that's exactly what they're doing. So all the exciting photos with good stories are just covered with all the other dick pics and screenshots.\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small There's \textbf{nothing} wrong. Its just always been that way. Older people think they're better than the younger generation.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Sen Chi, you're right. Our lives has no story there is \textbf{nothing} entertaining about it or significant. We just bunch of hipsters hopelessly trying to bring in some meaning to our miserable lives. We certainly gotta do something about it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@Thaddeus Cheeley theatre is a mirror reflecting back at society,held by an honest fool to \textbf{dumb} to tell a lie\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@x0xTHLover4Lifex0x I'll answer your first question.And ignore the rest. I.e. not even read it.It's more selfish to not have children because, people who have children generally have an investment in the future, people who don't, by choice, are generally the type who live a child like existence only thinking of themselves and the now, generally when they act concerned with the world, it's to feel superior, not because of any real investment.The \textbf{old} story is about a person who gives to the needy only when others can see and another person who gives every chance they get. Who gives more you think.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small Old people were smelly miserableists in the past.They are smelly miserableists now.It's doubtful the future will be any different.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small You can write as many YouTube comments as you want but \textbf{nothing} will change. They're all gonna suck lol.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Byebye Bye Best not to take notice of a book written by bronze \textbf{age} goat herders with a limited knowledge of reality!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I didn't find this funny. I don't understand how taking photos of everyday things means that you don't have a rich and good life story? I rarely take photos, I rarely save them and I think it's bad. Photos help us remember things and what's wrong with remembering tasty breakfasts or how good you happened to look one day. I'm pretty sure \textbf{old} people would've taken photos the same way if the technology existed then. But I guess even then people would complain: "in my days everything was painted, it took so many hours!"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small Obviously you'd only show your grandkids the best selfie not the 12 you took before you got that shot, so what's  the problem? They'll be amazed at this \textbf{old} rinky dinky technology also, give them an education on the good \textbf{old} days when you had to take your own selfies\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Byebye Bye Technology like any other tool brings good and evil depends how you use it. It makes life easier for everyone and well as a whole people look better and live longer healthier lives. Although it can take away jobs and people after have to remind themselves. The \textbf{age} \textbf{old} question is is it better to make our bread and our lotions..... or buy them? Are we going back or moving forward?\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small \@PyroNinja713 it's interesting because years ago people had huge families as opposed today they may have one possibly two. I guess we're overpopulated because the human or mankind is living longer. More people living in a country requires bigger government it's a logical growth. So are we populating the Earth or are we closing the borders what are we doing now we're encouraging abortions are we stopping them are we getting people to use Electric so we can sell more appliances or are we having people conserve because we're running out of fossil fuel and supposedly polluting the Earth the sea and the animals.... killing the natural habitation or wildlife???? People always say a simpler life is a cleaner life yet \textbf{nobody} wants to go back to simple..... what is the answer?\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small Just don't breed, let the \textbf{race} die out.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Lol, like I haven't seen my parents' photo albums. They also took \textbf{dumb} pictures and made us pose with Mickey Mouse at Disney, and took pictures of people just standing and staring at the camera. My dad has some interesting pictures because he is military, but come on, don't act like everything was perfect and better before. 90 of family albums are people standing and staring at the camera in random places. How transcendent!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small You're dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small thats what literally every generationa says. humans progress, \textbf{nothing} you can do about it\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Not really, those \textbf{old} pictures have more stories because around that time you could only take pictures in very special occasions. Nowadays is just a \textbf{common} thing, people will always have stories what changes is the media.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Sen Chi Not really.  This is an exaggeration.  If you can't see that you are \textbf{blind}.  It's funny though\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Amenomihashiraold people make fun if young people too! The joke is on the \textbf{dumb} ass youth, always was, always will be! They laugh at them cuz they know they'll eventually \textbf{age}...if they're lucky hahaha\normalsize   & \cellcolor{green!5}Age, Dumb & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Sen Chi its in a joke format \textbf{dumb} ass by a stand up comedian. Smart person lmfao\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Make some changes to what?  Not take as many photos?  Have more interesting lives?  I mean it's not like all people over 60 years \textbf{old} today have lead exciting lives.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small You're a \textbf{dumb} ass. It's a funny joke and not a legitimate reflection of an actual problem. You know the reason we have all these worthless photos? Because we can. Digital cameras make taking and keeping useless images very easy. If they could, our grandparents would have too.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small \@Fona10 I wouldn't say easier. The \textbf{old} way was a simple button press . It is certainly cheaper to take meaningless photos now. I think the point was that there are people who are so self absorbed, that they think other people care what said person had for breakfast or considered buying. To \textbf{old} people the idea of it sounds \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/61 & \cellcolor{green!5}4.918 \\  \hline
  \cellcolor{green!27}\small An atheistic-minded \textbf{age} can only be full of narcissistic, selfish, soulless, cavernous zombies with \textbf{nothing} of worth to look back or forward to.\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small I agree Pathetic when it seems all girls thrive to be the best looking \textbf{thot} that'll do anything for money and the guy can't keep a relationship because he likes chasing those thots physically and virtually\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small 50 years from now \textbf{old} people will have no photos left because, unlike paper, all ssds become corrupted after 10-15 years- unless  you rewrite the data periodically, which very few do. But that's OK, since like it has been said, today's pictures are just \textbf{lame}.\normalsize   & \cellcolor{green!27}Lame, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Millennials are going to be boring \textbf{old} people. "Ah, yes. I remember the Twitter wars."\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Every generation suffers their own trials and tribulations, ours are still on the horizon. Sea-levels will rise, causing mass displacement and destruction of most major cities. Other countries will become increasingly uninhabitable, causing mass migration and cultural clashes. Extreme weather events will make resources more scarce, causing war. Call me \textbf{crazy}, but I think that the younger generations will have some worthwhile stories to tell before the end of their lifetime; and at the risk of seeming even crazier, I think they'll rise to the occasion.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small The new \textbf{old} people won't look at \textbf{old} photos, due to their deep depression over realizing how wrinkled and \textbf{fat} they'd become.  Karmas a bitch, then you die.   hahaha hahaha! 👴👵👴👵👴👵👴👵👴\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}3/31 & \cellcolor{green!5}9.677 \\  \hline
  \cellcolor{green!27}\small This guy looks Aussie and has an Aussie name. \textbf{Weird} hes not\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Holy shit that was funny! I'm getting \textbf{old}! Lol\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small looks like those cavemen from the \textbf{old} geico commercials\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Old people now is insane. True\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small He's not wrong. Our future \textbf{old} people won't know how to be \textbf{old} people. And especially in Canada. We used to go to grandma's house. Now grandma's and grandpa's don't own houses. We used to go for home cooked meals the ingredients were fresh from the supermarket. Future ld people will be feeding their grandkids canned presidents choice from the food stamp Food bank. No more Friday loonies or toonies. They won't be worth enough to buy even candies with.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/80 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Imagine an 80 year \textbf{old} sjw....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small He looks like the caveman from the \textbf{old} Geico Commercials 😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small What does him mentioning he is of a mixed \textbf{race} background have to do with ANYthing?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small TRIGGERED!!! This is not comedy. Its hate speech. This person is an \textbf{ageist} technophobe and must be sacrificed on the alter of political correctness. Pass me the popcorn.\normalsize   & \cellcolor{green!27}Ageist & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Bro you kidding? My photo album is gonna be: Here is a picture of your grandmother and I running from the twin towers on 9/11. Here is a picture of me and your godfather Noah at the largest protest in human history against the Iraq war.  Here is a picture of me at the inauguration of the first \textbf{black} president. Here is a pic of me capturing Saddam Hussein...And they will all have been photoshopped.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small Time changes without even knowing it. It all happend so fast. From \textbf{Black} to Dark \textbf{Black}😂😉\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Watch it \textbf{old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Didn't know  people become British when they get old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Good premise but, not the best delivery.  I felt like his 'millennial' \textbf{old} person could have been funnier.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small So far, 72 thumbs down by the 72 future \textbf{old} people smart enough to realize he was describing them; they're already butthurt.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small New \textbf{old} people will have ashtonishing pictures as well.. like a photo of the Antarctic when it was covered by ice. Huge areas covered by trees (it was called forest).. also darkwhite people :))\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small good bit... but of course in 50 years he himself will be the \textbf{old} person.  I'm 20 years from being that \textbf{old} person myself --- fortunately I never take selfies.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I thought he was gonna crap on Gen X but I guess there's not much to criticize.We're pretty much the most badass, in-tune, coolest \textbf{old} people that ever existed.Thank you Kurt Cobain.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Stupid people never realize they're going to be \textbf{old} soon or that older people know much more than they do.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small This is a stolen routine and just a reworking of Nick Swardson's bit about his grandmother and hip-hop and she was a \textbf{ho} in her day. White jesus is a joke thief...remember when you only saw one set of footprints? yeah that was when Nick's bit carried you.\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Nobody cares.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small 'scuse me ma'am, I'm with the \textbf{Age} Police. I'm afraid at the \textbf{age} of 61 you're not allowed to use "omfg" or emojis. Give the phone back to your son and have a nice cup of cocoa. Thank you, ma'am. (joking, I'm 56)\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small pfdrtom shut up \textbf{old} man no one cares\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small So your cat is 25 years \textbf{old} uh?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small bit \textbf{weird} you think men your sons \textbf{age} are attractive\normalsize   & \cellcolor{green!27}Age, Weird & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Well, your 25 year \textbf{old} son is probably going to be far better than all the teenagers and kids that are growing up now. He (like me) at least knew of a time when there wasn't any social media and unlimited digital photos, and what it's like playing outside (even with all the videogames). Kids growing up these days will be depressing to be around when they grow \textbf{old} 50 years later.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@K.E. Anderson yeah because when you're her \textbf{age} you'll only find people your \textbf{age} attractive.  What is the acceptable amount?  Like 4 years either way?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small \@Nostalgia For Infinity uh.... No. You're exactly the problem \textbf{age} mate. You don't even realize you're fucked, that's the best part. You think the shit that you do and think is perfectly normal.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small 61 is \textbf{old} tf?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Why are people saying 61 is \textbf{old}? My great grandfather is in his 90's and he's still more of a functioning human being than most people in their 20's\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small What 61 year \textbf{old} uses 'omfg'? I call bullshit.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Seems like it's more about zoomers than millennials. Considering 20+50 would equal \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small The close up shot at the beginning reminded me of the caveman from the \textbf{old} Insurance commercials, so easy, a caveman can do it 😂😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small thot confirmed\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/1 & \cellcolor{green!27}200.0 \\  \hline
  \cellcolor{green!5}\small Salmo Ali Replace 'men' with 'women' and there would be a meltdown in the streets. Most people like being appreciated for their physical traits, sure, but only by the people who they want to appreciate them. You're painting with too broad of a brush anyways - how would you even define 'men' in your statement? Straight men? \textbf{G\textbf{ay}} men? Every single person who has ever been born male? Most males? Even the \textbf{old} ones? I think YOU or someone you KNOW must enjoy being objectified, but that doesn't mean your same standards for objectification should be applied to the entire world. Not only because that just wouldn't work socially with all of the differences and complexities from country to country, but also because you're a dumbass.\normalsize   & \cellcolor{green!5}Gay, Old & \cellcolor{green!5}Age - Over 65s, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/126 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Deese Nuts uhhh women objectify men constantly. Have you never worked with women?They talk more openly \textbf{sexual} about men than vice versa.Cuz you know no mans going to HR about it\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small slydtsatmosman Jesus is \textbf{Black} Man Right\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small It's spelled "humor" you \textbf{limey} bastard.We invented the internet, so like aviation air traffic control worldwide, use American English, you fucking peasant.*Before you take personal insult, I'm just fucking with you, dude.  Chill.  It's a joke.\normalsize   & \cellcolor{green!27}Limey & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Jerry} VanNuys what a clever joke. Almost a little too far and mean\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Yeah - I think it was King Solomon who basically said - There is no New News - It's just \textbf{Old} News thats Presented to New People\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@CJ Live Actually its a recent Progressive agenda to talk \textbf{race} - For most of man's history people were identified by \textbf{NATION} - Progressive obsession with \textbf{Race} goes hand in hand with their agenda to do away with borders - The \textbf{Nation} State - When Jesus said that one of the signs of the time that we are living in would be \textbf{Nation} aganst \textbf{Nation} - The Greek Word the writers used was - \textbf{Ethnic} against \textbf{Ethnic} - Jesus probably looked like His ancestor David - Ruddy in completion (YES the Hebrew Word means \textbf{R\textbf{ed}}) Like His Ancestor Issac - Rebecca - Issac's wife - Came from Haran which is in Syria - Her brother Laban's name means White in Hebrew - This was before Ishmael when Syrians descended from Aram who was a Son of Shem - Syrians were originally light.\normalsize   & \cellcolor{green!5}Ethnic, Nation, Race, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}10/142 & \cellcolor{green!5}7.042 \\  \hline
  \cellcolor{green!27}\small P Master The Bible says Jesus Christ is \textbf{Black} Man.its Written in the Bible Jesus is \textbf{Black}!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Jesus had a \textbf{tan}, that's about it.\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@the Native Tahoma Navajo There's like a million bible versions, nearly all are worded different ways to please different groups of people. There's even a queen James Version which has all \textbf{homosexual} verses removed.\normalsize   & \cellcolor{green!27}Homosexual & \cellcolor{green!27}Sexual Identity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small If Jesus was reading these comments he would be laughing hard. There are more arguments about his skin color than his lessons. That seems like the point this comedian was making. Future \textbf{old} people with \textbf{nothing} valuable to say.\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Most current \textbf{elderly} people are right wing. Statistically millennials are mostly liberal. So if you're liberal, the future \textbf{old} people are going to be awesome.\normalsize   & \cellcolor{green!27}Elderly, Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small I wish I could agree with you but what about all those \textbf{elderly} who were hippies or progressive for their time? People tend to go more conservative the older they get...especially if they've had the privilege of accumulating wealth.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Most people get more conservative as they \textbf{age}. Look at all the former hippy baby boomers that are now the richest most selfish people of all time.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Statistically most young people in the late 60's were liberal too. They're now \textbf{old} people. So ... yeah. Reality.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small People tend to be more liberal when they're younger and become more conservative as they \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Except that studies show by \textbf{age} 30 people start getting more conservative.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small As people \textbf{age} liberals turn into conservative because they get frightened of change\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small You are future \textbf{old} people...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@MsZephyra / People don't become more conservative because of "the privilege of accumulating wealth". I'd even say that poor \textbf{old} people tend to be more conservative than rich \textbf{old} people.The reason \textbf{old} people become conservative is because they realize a lot of their dreams and the things they fought for when they were young, believing it would make the world a better place, ended up with bad results. So as we get older, we tend to be more careful about changing society.\textbf{Old} people become more conservative because life teaches them that the saying, "a bird in hand is worth two in the bush", is quite true.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}4/108 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@MsZephyra Also most poorer people support progressives policies but dont live long enough to be \textbf{old} liberals. Its the useless rich heirs who never worked a day in their lives who could afford yo be 90 and full of privileged biases who are \textbf{old} conservatives.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small Actually that trend seems to correlate with aging. So the older people are the more confused and conservative they become. The "liberals" of today are actually much closer to the Republicans of 25 years ago than they are to the actual left. \textbf{Old} people will likely always be more conservative and liberals will call themselves left while being closer to center-right. The left will continue to be silenced until they take up arms.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small don't kid yourself, today's \textbf{old} people were yesterday's hippies.........but they are just not bothering anyone.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The new generation isnt liberal, its completely reactionary. They think they are left but they have \textbf{nothing} to do with what this word stands for.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small most conservative \textbf{old} people were once young liberals.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small There's an \textbf{old} saying: "If you're not a liberal at \textbf{age} 20, you have no heart, If you're not a conservative at \textbf{age} 40, you have no brains."\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small Those \textbf{elderly} people were liberals when they were our \textbf{age}.\normalsize   & \cellcolor{green!5}Age, Elderly & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Bunch of triggered \textbf{old} people lol.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Gen z are conservative so we'll hate \textbf{old} liberals.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small If you are not liberal when young you have no heart. If you are not conservative when \textbf{old} you have no brain. - Winston Churchill\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Yayyyyyy let's turn something political that shouldn't be!!! (Right guys, can't you wait for all those LIBERAL \textbf{old} people? Me neither, if they weren't liberal, it wouldn't be any fun)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Statistically, the only future \textbf{old} Liberals are the ones that are going to be taxing the life out of you.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I don't know about that. Boomers were hippies in the 60s and 70s and yuppies in the 80s. Millennials may also change in their middle \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small To be young and right wing is to have no heart, To be \textbf{old} and liberal is to have no brain. Maybe it's the contrast between  the optimism of youth and the reality of experience that changes you as you get older. Happened to me and I'm not even 30. I was a super liberal actor, (which if you look young like I did there are a lot of \textbf{old} creepy perverts trying to fuck you in that industry) and it slowly pushed me central. Although these days anything center seems to get you treated like a rabid right winger. \textbf{Weird} times.\normalsize   & \cellcolor{green!27}Old, Weird & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/102 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small These \textbf{old} conservatives right  wing, whore once pot smoking hippies, fucking everything around in Woodstock, making riots, occupying parks and streets for months, walking naked and stoned  to everywhere in VW vans... Yes... These youngs now are liberals, and they are going to be awesome in 50 years...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small No they're not. Have you ever seen \textbf{old} hippies? I used to live in a very liberal area in New England, and let me tell you, those people are obnoxious. They're liberal so they make a real effort to try to understand the youth, and fail miserably because they're \textbf{old}. And unlike \textbf{old} conservatives, who deal with the fact that they're going to die by telling themselves lies about god and heaven, or drowning their sorrows in \textbf{alcohol}, \textbf{old} liberals tend to get all spiritual, like some kind of pagan mystics, and go completely batshit insane.\normalsize   & \cellcolor{green!27}Old, alcohol & \cellcolor{green!27}Age - Over 65s, Behavioural Addiction - Alcohol & \cellcolor{green!27}5/96 & \cellcolor{green!27}5.208 \\  \hline
  \cellcolor{green!5}\small There's an \textbf{old} quote that goes, "If you're not on the left when you're young you don't have a heart, and if you're not on the right when you're \textbf{old} you don't have a brain."Young people are liberal because they're inexperienced, naive and \textbf{dumb}. They've not yet understood just how little they actually understand about the world. At the same time, they've got a lot of energy, passion and a belief that they've got all the answers, and therefore also the duty, to lecture everyone else about how the world should be run and how they should go about creating paradise on earth. This always ends up in a disaster.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/111 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small maylightbewithyou  it's not your \textbf{age} but your educational level that determines how conservative you are. The most conservative are statistically the lowest educated.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small People become more afraid as they \textbf{age} which turns them conservative\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Thanks for the pointless politicising of being old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small If you're not liberal when you're young, you don't have a heart, and if you're not conservative when you're \textbf{old}, you don't have a brain.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small What a \textbf{dumb} thing to say.  All politics are toxic and so are you for not realizing it.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@MsZephyra That is true, because with \textbf{age} comes wisdom.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Steve Sherman "Most people get more conservative as they \textbf{age}. Look at all the former hippy baby boomers that are now the richest most selfish people of all time."Uh okay... but such as who that doesn't represent an absolute exception to the rule? Millennials frighten you! 🤣\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small There's an \textbf{old} saying 'if you're not a Liberal when your young you have no heart, if your still a Liberal when your \textbf{old} you have no brain'. With \textbf{age} comes wisdom I guess.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small The current \textbf{elderly} are Baby Boomers, seriously the worst generation. They came after the Silent Generation who were defined by integrity and they fell down in most regards.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{old}....WAS liberal.....but I'm tired of paying for everybody else's BS. Everybody just wants to be given more. They don't seem to realize someone has to pay for it!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I was a raving liberal when I was 18. As I got older I became more conservative. Now I am moderate but still not as left as I was in my youth. I think most people do get less liberal as they \textbf{age} at least fiscally.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Old hippies are the worst \textbf{old} people.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small maylightbewithyou I'll explain it for you guys from my perspective since I think I'm at an in between point in my life. When you are young you tend to be pretty liberal. What you see today a lot of times is so far left it can't even be considered liberal but it doesn't mean your heart isn't in the right place. Anyways when you're young you tend to be more naive to the realities of life, and think that anyone who disagrees with liberal policies is just a heartless piece of shit. You should be more liberal when you're young. You should have more compassion for people and more caring for others especially the ones you don't know. You have more time to look out for others and do more for the environment etc because you tend to not worry as much about your own future. When you're a kid into your early 20's you tend to think yourself invincible. Life is precious and should be protected at all costs. You think your group of friends will be friends forever and \textbf{nothing} will change as you get older. You think the older ones who disagree with you lack empathy and that they are just bitter \textbf{old} people. And why don't most \textbf{old} people agree with your teachers, professors, liberal politicians etc. Everyone likes being right, and hates to admit when they are wrong. So when an older person agrees with you you think they are the smartest people on the planet "hey, this guy gets it". The reality is as you get older you have been through more. You have learned from mistakes and from the experiences of life and the people who brought you up. You learned on your own that that \textbf{old} heartless bastard across the street or from grandfather weren't so wrong when they said that a lot of people do suck and you can't be so trusting of strangers. You also learn it's not worth helping people who won't even lift a finger to help themselves. You start to question things when people make shitty choices and fuck up yet expect others to help them out of their problems. Especially when they keep making the same shitty choices. If you keep trying to help people and they keep fucking up then they are never going to learn how to fix their own problems. You aren't doing them, and you especially aren't doing future generations any favors by bailing them out all the time. You start to focus more about the people closest to you and less on the rest. It doesn't mean you don't care. It just means you are going to focus on the ones you can help the most. When you're older you have attended the funerals of several friends and family members and you know life is precious and it can end at any moment. That 14-24 year \textbf{old} you that thought he/she was invincible has come to the realization that you aren't. You see the naive younger generation and think "God if they only knew" but you were that \textbf{age} once and you know telling them whats up will probably go in one ear and out the other. Now that you are the same \textbf{age} as the teachers, professors, and politicians you can more easily point out the ones who are full of shit. One of the most wise and decent men I know is a very conservative, but I have argued with him about certain left wing policies and if I make a good enough point he tends to say things like "looking at it from that perspective I see your point" or "I never really thought of it that way". He also hates the republican party. He doesn't like the democrats either but the younger generation needs to understand that conservative doesn't always mean republican, just like liberal doesn't always mean democrat.  If you are young and you aren't liberal you don't have a heart. When you're older if you still feel the same way as you did when you were young you don't have a brain.\normalsize   & \cellcolor{green!27}Age, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}7/687 & \cellcolor{green!27}1.019 \\  \hline
  \cellcolor{green!5}\small You seem to confuse leftist with liberal and right wing with self responsibility. Future \textbf{old} people saying you can say \textbf{nothing} or they will break out you windows and attack you?\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small If you're a "liberal" and \textbf{old} then chances are you're probably not the brightest.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Most people turn more conservative because as we \textbf{age} we become wiser.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Omg \textbf{old} liberals? That's gonna make me sick\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Well, \textbf{old} people probably saved you from Hillary Clinton.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Sara Check well as true as that may be, I gather that the term 'conservative' will mean something entirely different by then. I'm sure they'll be a lot more like yesterday's liberals than you might think, so I certainly won't mind. People won't start out as liberals whilst young today who are generally less religious, less \textbf{racist}, less sexist, etc than your average conservative.....and then \textbf{age} magically makes them more of those things. If I had to guess, the liberals who do turn into some of the conservative voter of tomorrow will have many liberal values when it comes to things like social issues, even if they become conservative in their views related to finance. When it comes to your stance on social issues, those generally don't change much as you \textbf{age}....considering they are a product more of your upbringing education, rather than your status. Your views on things like taxes, wages, budgets, immigration etc might very well change in accordance to where you are status/financial wise by then though. The older conservatives of today are the way they are simply due to the era of which they were born, the era of which most women knew their place, nonwhites  belong in the back of the bus, and gays are mentally ill dirty sinners. Younger people today, especially liberals, hold those opinions less often obviously, so they're far more likely not to have them when they're older whether they start leaning more towards conservative votes/support or not, because at the end of the day, money is what really talks, the rest isn't as flexible.\normalsize   & \cellcolor{green!27}Age, Racist & \cellcolor{green!27}Age - General, Ethnicity - General & \cellcolor{green!27}3/264 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}\small "show me a 20 year \textbf{old} who isn't Liberal, \& I'll show you a man w no heart. show me a 30 year \textbf{old} who isn't Conservative, \& I'll show you a man w/o a brain". -Some Dude\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} are you? Didnt you learn in school that the hippies of the late 1960s were liberal and are now ages 70+?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small You women are \textbf{weird}, he is kinda ugly/mediocre in my opinion\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I love mockig my older self and i think we will make funny ass \textbf{old} people. But thing is im in my twentys and i dont really take photos anymore. And when i do its something i want to have to rember. I print them off and hang them in my living room :) im actually such an \textbf{old} person.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Me: \textbf{Eggplant}? Grandmother: Yes. Your grandfather took top prize at the great \textbf{eggplant} growing competition of '25.Me: Cool!\normalsize   & \cellcolor{green!5}Eggplant & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Marc Bryant yeah the GIRL is the slut if the GUY sends a picture of his crinkled \textbf{r\textbf{ed}} penis. No.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small So you reckon he took it or the tumblr post took it from him? Tumblr is basically \textbf{nothing} but reposts\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small its a pretty \textbf{common} joke, not necessarily stolen, but funny nevertheless\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@kirwi kirwinson That the new \textbf{old} people are going to suck. Really hard to figure that out....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small he sounds \textbf{nothing} like burr and isn't even close to as funny lol.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Future \textbf{old} people will be able to look at at all of the children of the immigrants that come in and have babies. Because Americans and Europeans don't have babies anymore. So future \textbf{old} people will get to be the grandparents of first-generation immigrants\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small This is the best time in history of mankind. The most peaceful humans have ever been. People are fighting \textbf{racism}. And yet you think the younger generation does not care? That would be anti evolution, as time progresses humans have become more kind. Stop with this stupid outlook on life and enjoy the time you have.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Andy Hahahaa fighting \textbf{racism}. That's a good one. Just like we're fighting the war on terror in Afghanistan almost 20 years later. Stop it already. Humans always evolve huh. People went from electing a \textbf{black} president —> to one of the most \textbf{racist} men possible. Evolution I guess.In the grand scheme of things, say 500 years from now, yeah it seems humans will evolve. In between, you can have 100 years of backwardness no problem. Look at the dark ages. There called that for a reason.\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/87 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Iraq Lobsta!! 45 lol that was always true and will always be true Read and learn history Socrates aooroebtly claimed writing would destroy people's brains and that the young ones won't memorize anything \textbf{Old} people are \textbf{dumb} it's just that now \textbf{dumb} \textbf{old} people can complain to us 24/7 and now young people think we are \textbf{dumb} even though we are the most educated the world has ever been\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/69 & \cellcolor{green!27}7.246 \\  \hline
  \cellcolor{green!5}\small I thought that was a term for white people with a \textbf{black} grandparent or great grandparent\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Add Bow If Girl she is mixed \textbf{race} not white.simp\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Johnny Quest Republicans and Democrats are basically the same shit to anyone outside the US but you guys just don't see it. Both are imperialists; both profit from arms sales, prisons and the military industrial complex at taxpayers' expense; both create, fund and train \textbf{terrorist} groups just so they can invade foreign countries under the pretence of taking them down; and most importantly both are ultimately under the control of Israel, and have been since JFK was killed. Don't believe me? Look at how many members of the Senate and Congress hold dual Israeli and American citizenship. Look at how much influence Israeli lobby groups like AIPAC have on US foreign policy. Look at how much money the US gives to Israel every year for free (\$3 billion) at taxpayers' expense whilst homeless veterans die hungry on the street. Finally, look at the names of the heads of every major news network in America. It's a sad state of affairs...\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/160 & \cellcolor{green!5}0.625 \\  \hline
  \cellcolor{green!27}\small Obama was a C+ president who divided the country and gave them a reason to vote for someone as \textbf{crazy} as Donald Trump. And his only big achievement was being \textbf{black}.\normalsize   & \cellcolor{green!27}Black, Crazy & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Sage the fact that you posted this \textbf{dumb} comment about Obama's inauguration proves that the new \textbf{old} people are going to suck.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small A video of the worst president in the history of any \textbf{nation} on earth. That'll brighten up the kid's day.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small "Here we are watching a man take a job that we gave him because he was \textbf{black}, and we thought it would be cool if a \textbf{black} guy had that job.  We were okay with the socialist policies, \textbf{race} baiting, illegal spying, arming cartels, funding \textbf{terrorist} regimes, doubling our debt which you kids will have to pay off, and just all around being a smug piece of shit.  It was worth it because first \textbf{black}.  We wanted to first \textbf{black} all the things."\normalsize   & \cellcolor{green!5}Black, Race, Terrorist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!5}6/83 & \cellcolor{green!5}7.229 \\  \hline
  \cellcolor{green!27}\small Not for long.  One time, he looked at a \textbf{woman} wrong so feminists are going to erase him from their neo-puritan books.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Seriously? Trying to rationalize anything to do with Obama as "good"?This comedian is right: The next batch of \textbf{old} people WILL be awful!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small mike sanchez  No, their reason for voting for Trump was \textbf{racism}. And it was Hillary who lost to Trump, not Obama.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I've got a \textbf{crazy} collection of video games.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Yeah the base of the joke is the same: new \textbf{old} people will have shitloads of photos. Norm did it a lot better IMO, of course.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old, Elderly, Elder & \cellcolor{red!27}470 & \cellcolor{red!27}470/65542& \cellcolor{red!27}0.72 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Crazy, Lame, Dumb, Weird, Mental, Blind & \cellcolor{red!5}79 & \cellcolor{red!5}79/65542& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Race, Racist, Racism, Ethnicity, Ethnic & \cellcolor{red!27}55 & \cellcolor{red!27}55/65542& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age, Ageism, Ageist & \cellcolor{red!5}69 & \cellcolor{red!5}69/65542& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Whippersnapper, Nothing, Zero, Nobody & \cellcolor{red!27}73 & \cellcolor{red!27}73/65542& \cellcolor{red!27}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Woman, Gender, Sex, Sexism, Chick, Sexual & \cellcolor{red!5}27 & \cellcolor{red!5}27/65542& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, Colored, Buck, Nigga, Fuzzy, Crow, Jim Crow, African, Eggplant & \cellcolor{red!27}66 & \cellcolor{red!27}66/65542& \cellcolor{red!27}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Nazi, Red, Snowflake & \cellcolor{red!5}10 & \cellcolor{red!5}10/65542& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common, Trailer trash, Tacky & \cellcolor{red!27}12 & \cellcolor{red!27}12/65542& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Tramp, THOT, Hooker, Slapper, Ho & \cellcolor{red!5}17 & \cellcolor{red!5}17/65542& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Red, Apple & \cellcolor{red!27}11 & \cellcolor{red!27}11/65542& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Fat, Skinny, Thin, Bony, Chubby & \cellcolor{red!5}22 & \cellcolor{red!5}22/65542& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - White}  & \cellcolor{red!27}Trailer trash, Whitey & \cellcolor{red!27}4 & \cellcolor{red!27}4/65542& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Pancake & \cellcolor{red!5}1 & \cellcolor{red!5}1/65542& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Homophobic, Homophobia, Gay, Homosexual & \cellcolor{red!27}7 & \cellcolor{red!27}7/65542& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Alien, Nation, Engineers & \cellcolor{red!5}8 & \cellcolor{red!5}8/65542& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Drugs}  & \cellcolor{red!27}Junkie & \cellcolor{red!27}1 & \cellcolor{red!27}1/65542& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Fruit, Gay & \cellcolor{red!5}4 & \cellcolor{red!5}4/65542& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Jerry & \cellcolor{red!27}2 & \cellcolor{red!27}2/65542& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Aboriginal}  & \cellcolor{red!5}Bong & \cellcolor{red!5}1 & \cellcolor{red!5}1/65542& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}pussy & \cellcolor{red!27}1 & \cellcolor{red!27}1/65542& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Destitute}  & \cellcolor{red!5}Bum & \cellcolor{red!5}1 & \cellcolor{red!5}1/65542& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Southern European}  & \cellcolor{red!27}PIGS & \cellcolor{red!27}1 & \cellcolor{red!27}1/65542& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Irish}  & \cellcolor{red!5}Mick & \cellcolor{red!5}1 & \cellcolor{red!5}1/65542& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Roman Catholic}  & \cellcolor{red!27}Mick & \cellcolor{red!27}1 & \cellcolor{red!27}1/65542& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Protestant}  & \cellcolor{red!5}Spike & \cellcolor{red!5}2 & \cellcolor{red!5}2/65542& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - British}  & \cellcolor{red!27}Limey, Tan & \cellcolor{red!27}2 & \cellcolor{red!27}2/65542& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Behavioural Addiction - Alcohol}  & \cellcolor{red!5}alcohol & \cellcolor{red!5}1 & \cellcolor{red!5}1/65542& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}2 & \cellcolor{red!27}2/65542& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - Over 65s;Physical Identity - Physical (and Mental) Impairments;Ethnicity - General;Age - General;Age - Youngsters;Gender - General;Ethnicity - Black; Ideological and Political Identity - General;Social Class - Working class;Gender - Female sexuality;Ethnicity - Native-American;Physical Identity - Physical Features;Ethnicity - White;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Sexual Identity - General;Nationality - General;Behavioural Addiction - Drugs;Sexual Identity - Male homosexuality;Nationality - German;Ethnicity - Aboriginal;Nationality - Chinese;Social Class - Destitute;Nationality - Southern European;Nationality - Irish;Religious Identity - Roman Catholic;Religious Identity - Protestant;Nationality - British;Behavioural Addiction - Alcohol;Religious Identity - Muslim;%.

\item The percentage of hate speech related words is 1.451.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 953/4230 occurences of hate speech related comments.\end{itemize}\end{document}