\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_204.json :}\newline \par\Large\textbf {Title: \large  Man Goes on Racist Tirade in Canada }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Still this shameless \textbf{Indian} will be obsessed with White colour..Because Dollar matters\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Honestly I was born in Canada but my family is from russia I'm not afraid saying I was born in Canada but my family is fromRussia because everyone in Canada and America are immigrants let's be fair if we are truly Canadians and Americans we would be First National people the Aboriginals. But no our ancestors are immigrants from Asia, Europe, etc but we are not true Canadians and Americans we are still immigrants and why not that man go back where his ancestors were born before they moved to Canada. Because Canada and America belonged to the First \textbf{Nation} people the Aboriginals. I don't care what the rest of you guys say because if you need to go back in your family tree to understand better of your family and read the history and understand how the lands was taken over and how the first \textbf{nation} people were treated.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/151 & \cellcolor{green!5}1.325 \\  \hline
  \cellcolor{green!27}\small his mother was fucked by her brother his parents are brothers and sisters thats true i know the guy  lives next block from me its very \textbf{common} in toronto now whites are practicing family \textbf{sex} trust me\normalsize   & \cellcolor{green!27}Common, Sex & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small I'll just tell him thank you I know that I'm better then you will ever be. And that is what I've learned from \textbf{Dumb} Trump who has attack those smarter, Braver, and Better then he will ever be\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small you aint scaring \textbf{nobody} Yosemite Sam ðŸ˜‚\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I met so many of these \textbf{dumb} uneducated white shts on the road that drives these ugly truck all the time and these guys have no guts if you intimidate them. They are only good at talking. Tell this \textbf{dumb} idiot to go back to Europe and I am sure the First native aboriginals would agree to kick him out as well.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small I'm a white Canadian \& I work with lots of east Indians. 1 of them today, a very nice \textbf{woman}, told me that "WHITE CANADIANS ARE VERY NICE TO US, NICER THAN OTHER \textbf{INDIAN} PEOPLE." I said "Really? Thank you, nice to hear that". Hearing things like that make me HAPPY TO BE WHITE! You see? We ARE nice people!\normalsize   & \cellcolor{green!27}Indian, Woman & \cellcolor{green!27}Ethnicity - Native-American, Gender - General & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small indians are \textbf{racist} to just saying ,not cool but they are\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small LxTxSURGE mainly Indians living in India because they live in a homogeneous society. Most Asians in general are extremely \textbf{racist} because of this, usually the ones who grew up around different races aren't \textbf{racist} at all (eg Indians in Trinidad). But two wrongs don't make a right.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Racism hate group should be instant  banned ðŸ˜ ðŸ˜ ðŸ˜ \normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Hahahaha! \textbf{Racist} is every where..\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small 'You fuckin' \textbf{Paki}.... Go back to fuckin' India!`Those are two different countries now, you moron ðŸ˜‚\normalsize   & \cellcolor{green!5}Paki & \cellcolor{green!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Another white man with \textbf{nothing} to lose. Governments all over the world have pushed the white man too far. Everyone has rights except the white man. And these so called hindus and muslims. blame all their problems on the white man.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Somebody should kill the \textbf{racist} bastard\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Whites are the Supreme \textbf{Race}. Please Leave Canada, shitskins\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small So? Who cares? What are you going to do to \textbf{coloured} people if they don't? All talk no action perhaps? Or pull a Hitler?\normalsize   & \cellcolor{green!5}coloured & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small The dude with the \textbf{racist} tirade that was filming will just make it worse for him being a \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Idk whether to feel sad for that poor illiterate white dude or to laugh at him. Also, HINDI is not a country. Goes to show how lack of education reasonates to the emergence of these \textbf{racist} bigots\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Maybe all of countries has racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small This makes me so sad and ashamed of our human \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small This guy should seriously update his \textbf{racist} vocabulary, making fun of Indians by calling camel riders is outdated bruh\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Racism is a \textbf{mental} health issue. People who justify \textbf{racism} seriously need help\normalsize   & \cellcolor{green!5}Mental, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/13 & \cellcolor{green!5}23.077 \\  \hline
  \cellcolor{green!27}\small Racial harassment from a retarded \textbf{midget} who walks like he has a moose stuck up his ass. He has a look on his face like he is enjoying getting a bag of skittles shoved up his ass. This guy is a clown. ''Go back to India and white power,'' he said. Queen Elizabeth II needs to send her royal guards to give this guy a good \textbf{old} fashion British beat down.''One of the queen's royal guards:  ''MAKE WAY FOR THE QUEEN'S GUARDS!''\normalsize   & \cellcolor{green!27}Midget, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small I m \textbf{Indian} and I personally don't like why they want to settle in foreign by leaving my beautiful India ! Studying in foreign is good but settling is bullshit , as most hardworking people are trying to settle in foreign for money\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Racist syndrome was spread all over the country.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small The only reason why people are surprised that \textbf{racism} exists in Canada. Is because that's one of the bullshit fairy tales Canadians tell themselves. So they can feel superior to Americans. But is complete rubbish along with Canadians being polite spent my whole life in Ontario and traveled a lot. Most people in other parts of the world are way nicer and more polite then Canadians\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small I'm pretty sure I seen this guy shooting up on East Hastings. \textbf{Nothing} to see just another white beggar.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small So which \textbf{race} is not \textbf{racist}?\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small What a fucken spastic\normalsize   & \cellcolor{green!27}Spastic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Nobody likes Hindus anyway they stink and are ugly\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Let me tell ya a little story about my town. There is a gas station that used to be owned by a white family, they sold it in good standing with an \textbf{Indian} family. The previous owner went back with his then 16 year \textbf{old} son to see if he could get his first job there, they flat out said 'we don't hire white people here'. Can you imagine the backlash that would come if a white person said that? I think our modern society is fucked, I've got \textbf{nothing} against people of colour. However I think there should be balance.\normalsize   & \cellcolor{green!27}Indian, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}3/101 & \cellcolor{green!27}2.97 \\  \hline
  \cellcolor{green!5}\small I love it when Canadians  come online and wood critique an article or video and say how \textbf{racist} America is  and a candidate is free all that mess oh, what a load of bull shit.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small The \textbf{Indian} guy deserve that - AryanPureRacePower ... Go back to your countries.. Ugly MotherFuckers...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I am appalled that there is \textbf{racism} in Canada now. As a citizen of Canada and being \textbf{Indian} i had never thought in a million years \textbf{racism} would be such a big threat to Canada as well.\normalsize   & \cellcolor{green!5}Indian, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small Gotta love all the white privilege \textbf{Nazi} comments\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I was in India years ago I'm a \textbf{black} man and I was treated so poorly in India I'll advise in a \textbf{black} man to never set foot in that country the most \textbf{racism} I ever seen in my life against a \textbf{black} person I can't speak for us the southern part of India but in the north it was hell I'll never set foot in that country or ever again the thing is the thing about Indians I don't understand is dark as the skin is they have the audacity to try to discriminate against \textbf{black} people Gandhi was \textbf{racist} history tries to make him out as this hero but he wasn't s***\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/114 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small thanks bro for making people aware of \textbf{indian} \textbf{racism}. indians often act the victim in western countries but in their own homeland they are even more racist\normalsize   & \cellcolor{green!27}Indian, Racism, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/27 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Shit \textbf{colored} people fucking always got to infringe on white people.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Only white people can be \textbf{racist}, right?  Why are people of color never called out for \textbf{racism}?\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small They're everywhere. I have family members that behave like this to.(uncle \& grandpa)They're the types that will say something like that and expect you to carry on with them..... if you didn't you got a light shunning for the day or teased intensely.I work construction, used to be on the same crew as them and my cousin (follows his dads ways)We were having lunch, with a \textbf{black} fella and they kept making fried chicken \& watermelon jokes right to his face....Because I'm related, that poor fella views me as one of them.I've long since left their company, and haven't associated with them much(personal reasons)But to this day.... that \textbf{black} fella isn't friendly towards me ( I've seen him in passing since)Can't blame him.But yeah \textbf{racism} effects everyone.I'm in Ontario...\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/138 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Short people got \textbf{nobody} to loveThey got little hands and little feetAnd evidently this guy's knees don't bend when he walks. That was a walking ad for diversifying the gene pool.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Typical the Indians like this guy cry \textbf{racism} when his white master gives him a much needed \textbf{nigga} wake up call . Yet they fail to point out that Indians are just as if not extremely \textbf{racist} towards \textbf{black} people even though there the same color if not darker then \textbf{black} people . This is exactly why \textbf{nobody} likes Indians or feels sorry for them when this happens to them .\normalsize   & \cellcolor{green!5}Black, Nigga, Nobody, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/71 & \cellcolor{green!5}8.451 \\  \hline
  \cellcolor{green!27}\small Americans are the most \textbf{racist} people in the world? Nope. There's Canadians.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@White girls Love \textbf{Black} Cock I am neither \textbf{Indian} nor Native... not sure what you are referring to?\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Racism against whites exists also stop acting like fkn victims\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Wait till white folk video \textbf{black} brown and \textbf{y\textbf{e\textbf{llow}}} folk for there \textbf{racism} will ya say the same y not show both sides that's racist\normalsize   & \cellcolor{green!5}Black, Racism, Racist, Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}6/25 & \cellcolor{green!5}24.0 \\  \hline
  \cellcolor{green!27}\small Canada is \textbf{racist}. It's my own experience.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Replace the words "white" with "\textbf{black}" and "Hindi" with "trailer park" and no one would be charged with any crime.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small makes me wanna laugh because india is very \textbf{racist} much more than this , they call white people boiled egg , poultry chicken and pig ...and they even hate their own people from north east they call them chinese refuges ...saw it with my own eyes ....surprised but not shocked ...the one that really shook me was when i saw them passing comments on a \textbf{black} \textbf{woman} ...as majority of \textbf{indian} people are dark skinned i didn't expect them to be discriminating a \textbf{black} women but it seemed like they were isolating her like she was some \textbf{alien} ...and lets  be honest if all the white people from europe and america would be flooding into india and taking the majority of jobs there , wouldn't it bother the locals , wouldn't it frustrate them ...makes you think\normalsize   & \cellcolor{green!27}Alien, Black, Indian, Racist, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Gender - General, Nationality - General & \cellcolor{green!27}6/137 & \cellcolor{green!27}4.38 \\  \hline
  \cellcolor{green!5}\small CASTE SYSTEM IN INDIA IS WORST THAN \textbf{RACISM}. i CONDEMN BOTH,\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small If people weren't pulling the \textbf{RACE} when they come here, this would be a problem.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@White girls Love \textbf{Black} Cock "vacant resources" are useless if somebody is not able to understand their utility and if has not the infrastructure and the science. The science and the technology...Hm, is not your  strong point (for saying it gently). So...limit your existence in your...Cock  hahahahahaAnd that was the end of our "conversation"\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small People don't like to be filmed..period.The white guy felt he is the victim and let out his frustration.He could've chosen better words but he was not the one who initiated the conflict.I'm an \textbf{Indian} and a Hindu.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Racism is everywhere and has always been. I'm glad people are finally showing it to the rest of the world.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Canada has lots of predators, molesters, pedophiles, and \textbf{sex} offenders who get caught by Justin Payne And Canada's Creep Catchers. That's why Canada is A Cold Boring Country\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Love all human beings hate racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small No Asian would want a bunch of outsiders coming into their country in droves. They wouldn't stand for it and yet they expect whites to put up with it. They are in a constant line to get into Europe or any country that has been built by white people. Indians are indeed intelligent and could build a wonderful \textbf{nation} but their problem is, is they have completely over-populated their country. It might sound harsh but if they were to stop a generation or two from being able to produce, except for their most brilliant people, then, I have no doubt that they would be a force to be reckoned with and their country would boom, meaning that they wouldn't have to infiltrate others to survive. The same goes for places like China. It's been proven that Asians are smarter than whites but they cannot build great societies because of their constant populating.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/152 & \cellcolor{green!27}0.658 \\  \hline
  \cellcolor{green!5}\small From which planet this \textbf{alien} came from? He can't even walk properly.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Canada is a \textbf{racist} country..\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Kyu ab pta lga kitni taklif Hoti hah jab aap logo India meh SC,ST ko tang krte \textbf{ho} ,,,,,,tumhe sirf Hindu bolo toh tumhe itni taklif hui ,lenki Bharat meh tum inko pta nai kya kya Bolte \textbf{ho} ,uski caste seh bhulha Lete \textbf{ho} ,,,,but u filed a case for calling only Hindu\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}3/53 & \cellcolor{green!5}5.66 \\  \hline
  \cellcolor{green!27}\small Lol ... No \textbf{racism} in Canada you say?  Not by a lonnggg shot.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Indian and south Asians lyk Pakistani and Bangladeshis shud face \textbf{racism} saale dusro k desh Mai jaake dusro k opportunity chinta hai kaisa lgta agar woh log enn faltu desho mai aake tum logo ki opportunity chinn le toh? Lve those countries clear get back to ur own countries and do sumthing useful u don't have even ryt or guts to say anything to them coz u know u guys r wrong ugly junglees\normalsize   & \cellcolor{green!5}Indian, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small And Canadians say USA is \textbf{racist} Hahaha\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small In case of \textbf{racism} is Canada not very diferent from the US!\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small no one likes indians, indians are rotten people, and by the way i was born an \textbf{indian} punjabi but have now changed into a non \textbf{indian} non \textbf{ethnic} non identity person, indians have \textbf{indian} privilage, so fuck them.\normalsize   & \cellcolor{green!27}Ethnic, Indian & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/38 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small White girls Love \textbf{Black} Cock you aint sikh bro so you don know what up with the backstabbing in the community, its harsh it aint calm, trus me when i say this but sikhs hate on each other big time.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small I find it vile and appalling that some people, the videographer in this instance, don't seem to understand that in Canada, people have a legal right to privacy yet the man being verbally assaulted seems to think it was his right to stick his nose into another person's business which he should have been smart enough to stay out of. He brought the verbal abuse upon himself yet now he is acting like Mr. Innocent when his interference in another man's business simply begged the white guy to tell him off. The videographer was told before this yelling ever started, to mind his own business and stop filming him. The videographer refused. Charges in this instance would be a travesty of justice but guess what the police just did.........Disgusting!!!!!!! This is Canada and we have laws concerning people's rights, behavior and interaction but most people don't know nor understand those laws and they surely don't respect them. I hope our judges do, but recent history has proven that they don't either as they ignore legislated law and change them to suit what they think rather than substantiating what law states. We are one sick \textbf{nation} of little God wannabees, making up our own rules as we go along and flaunting our long legislated laws as antiquated nonsense.  I wonder why \textbf{nothing} has been said about how this altercation started. It seems the owner of a parking lot decided he had the right to charge for parking and had his employee block this man's truck to get his pound of cash when the abuser was simply using his driveway to turn around on a busy street. In other words, if you step foot on my property, you owe me money. That too is a breach of Canadian law unless there is a obviously visible sign at the entrance stating that "entry constitutes a minimum parking fee".  YouTube seems to be becoming Canada's new legislature for all the little God Wannabees and money worshiping idolaters. If this supposed Asian man was born in Canada, his ignorance of our laws should be grounds for removal of his citizenship.\normalsize   & \cellcolor{green!27}Nation, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/355 & \cellcolor{green!27}0.563 \\  \hline
  \cellcolor{green!5}\small Well, you are a \textbf{black} man today . welcome to the struggle . LMAO!!!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Racist, ignorant \textbf{pigs} like this need to be thrown out of the Country. In Canada, we don't want/need idiots like this. Throw him back in jail, where he has probably been before.\normalsize   & \cellcolor{green!27}PIGS, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - Southern European & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Let's not use the actions of one \textbf{racist} lunkhead to label all of Canada.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Shit skin he says I wonder who suffers from skin cancer?When did you come to Canada he says?What if the \textbf{r\textbf{ed}} Indians had asked him the same question.Oh by the way I forget they killed nearly every \textbf{r\textbf{ed}} \textbf{Indian}.And  when is he going to leave Canada and go back to the Caucasus mountains?Do invaders or racists ever think of that?Oh I forgot again by the way they're are the only people who have the right to be in all four corners of the world.But other races can't be...Being a \textbf{racist} is stupidity because at times they forget they're roots from the mountains or Europe and on how you got to invade or killed the natives in order for you to settle and turn another mans land into your own home.\normalsize   & \cellcolor{green!27}Indian, Racist, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}6/136 & \cellcolor{green!27}4.412 \\  \hline
  \cellcolor{green!5}\small Indian pushed out the white people.  24/7 the people of India complained that whites were in charge,  every man,  women and children hated it.  So they got hold of Gandhi to united the people in pushing out the white \textbf{race}.  So what happened after they won,  they are now following the whites back to their countries crying \textbf{racism}.\normalsize   & \cellcolor{green!5}Indian, Race, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/58 & \cellcolor{green!5}5.172 \\  \hline
  \cellcolor{green!27}\small Yeah I agree what he did was wrong and \textbf{racism} shouldn't be anywhere. We are all humans first. But what about \textbf{racism} in India with Africans, to the level that they even beat them. Indians never raise their voice for those Africans. I am an \textbf{Indian} but I get very disappointed over this hypocrisy of Indians. Even Bollywood movies are full of \textbf{racism}, yet everybody enjoys them(don't even start with the fair color obsession of Indians). Anyone with dark complexion is considered bad in India and called names like kalu and blah blah. We should call out the wrong things even if our own people are doing it. Even I got familiar with the word \textbf{racism} while being the west (never faced any \textbf{racism} though, even felt more equality), then I realized oh ok what people do in \textbf{Indian} and take it as a joke that's \textbf{racism}.\normalsize   & \cellcolor{green!27}Indian, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}8/147 & \cellcolor{green!27}5.442 \\  \hline
  \cellcolor{green!5}\small What ever white person say ,, \textbf{racist} , racists, but truth is many of them deserve it . The biggest racists is people from India , Pakistan and Africa !\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small These \textbf{Racist} are Moron, They think they own the Land, The immigrants are far educated when it comes to geography or in life in General, because we travel, most Canadian are ignorant about anything outside Canada. My Canadian co-worker asked me how does it feels to ride on a plane, So sad that they have white skin and they think they are supreme in so many ways.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small Did I hear him say 'camel rider go back to Hindi'?? ðŸ˜‚ðŸ˜‚ðŸ˜‚ Oh \textbf{racist} boy. Learn first. At least. Please.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small In our planetary history, what we have both commonly and highly uncommonly come to recognize as all levels of terrorism is in fact coming from one single ancient and highly unfortunately extremely ancient, highly militant, highly fluid and totally inconceivably resilient culture that has both ruthlessly and relentlessly struggled for global conquest for longer than there is recorded human history.For example, in hemispheres like North America, that basically have no recorded history beyond American \textbf{Indian} hieroglyphs, we, like much of the rest of the world, had never known, heard of, or even remotely conceived of terrorism until we experienced "Huge Influxes of Indians and Pakistanis." And exactly the same is true of the rest of the global populace, with the exception of India, which was divided into India and Pakistan by British Colonists and is in act the true source of totally relentless global terrorism.In direct parallel with all of human history, Indians and Pakistanis are behaving this way because in previous human civilizations, that few of us presently remember, places like Africa, specifically, East Africa, and The Entirety of The Middle East were once \textbf{Indian} Colonies and the Indians and Pakistanis, who are in fact one highly sneaky entity, are covertly warring and using white people (who become highly vicious when they are combined with and inevitably totally controlled and use by Indians and Pakistanis whom they in fact totally unknowingly worship in every way) relentlessly to regain possession of those former colonies in their relentless quest for any form of global conquest.It is extremely important to understand that, the core primary reason that people of \textbf{African} Descent have had totally relentless problems with poverty, prejudice and bad press world wide is because other people of \textbf{African} Descent, whom we \textbf{black} people no longer recognize as people of \textbf{African} Descent (i.e. Indians and Pakistanis who now call themselves Brown People) totally hate us for evicting them from The \textbf{African} Continent numerous times over again; Idi Amin's Uganda being the most recent.One thing in the global history of people of \textbf{African} Descent that is an extremely telling and totally unmistakably ominous pattern is the longevity and precision of the problems of people of \textbf{African} Descent... \textbf{Black} people invariably have problems all over the world with prejudice and poverty, no matter where we go, however, extremely ancient cultures of totally relentless predators know that, people only have problems from themselves and can only be highly precisely tracked and targeted by people who are exactly like themselves... In this case, by Brown People, whom we no longer recognize as \textbf{Black} People.In my research of human geographical history, it has become crystal clear to me that, at some point in human history there was a great ideological divide that occurred among Africans Over Tyrannical, Iron Fisted Control Over Humanity or Total Human Freedom that occurred in The Horn of Africa Region of The \textbf{African} Continent at some point in human history, that still rages on today.Indians and Pakistanis have been expelled from The \textbf{African} Continent many times over again throughout both known and unknown human history and not only do these former Africans want access to The \textbf{African} Continent, they want total control of it, even if it takes Religious Indoctrination, Hyper-industrialization, Media Bashing, Military Invasion (including highly covert \textbf{terrorist} infiltration) or Economic and Technological Hypnotism.In my long ago concluded analysis, Nigeria was chosen because it it is a direct competitor to Kenya, which very conveniently has a Huge Influx of Indians and Pakistanis, just like \textbf{Nazi} Germany and its Ancient \textbf{Indian} Caste System based Class System,  Swastika and Aryan Ideology, Middle Eastern Terrorism, North American Terrorism, Chechnya in Eastern European Terrorism or anywhere else that has experienced historically uncharacteristic flareups of Terrorism.Indians have been able to accomplish this by surviving for multiple human civilizations and creating complete global resets by wiping out the vast majority of humanity in repetitively staged and executed global human Armageddonous resets of human civilizations during which Indians and Pakistanis relentlessly collect as much global human technology, store it in \textbf{Indian} Libraries and re-release it during multiple human civilizations and thereby very successfully making themselves look like a global super \textbf{race}, when in fact they are just thieves. [LINK] \normalsize   & \cellcolor{green!27}African, Black, Indian, Nazi, Race, Terrorist & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Religious Identity - Muslim & \cellcolor{green!27}19/709 & \cellcolor{green!27}2.68 \\  \hline
  \cellcolor{green!5}\small Don't Trust white guys, don't believe them when they say HI, Hello, or when they smile at you in front of many.Most of the are \textbf{racist}..I remember the 2008 throat slashing in a bus..maybe or I guess the guy was fed up.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small i lived in many country but canada is 1st place of \textbf{racism}.....in the 80s we white european guys with accent calld C.O.B. (came on boat) just shows their uneducated culture, they should have known we flew anyway then came the hindu or pakistani invasion they got called Rugheads then in early 90s Hong Kong people took advantage the \$300.000 deposit for 5 years landed \textbf{immigrant} visa programm ( or \$200.000 in Alberta) so they got called the Fucking Chis (Chines) and of course right now we have the Muslim Epidemic so at this moment I really dont wanna be in their skin......did I mentioned the First \textbf{Nation} People they got hated every day now matter what......Multiculturism will never will work no matter how hard they try to force the One World Orders......\normalsize   & \cellcolor{green!27}Immigrant, Nation, Racism & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}3/132 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small An angry bacon ðŸ¥“, he's just mad he's \textbf{old} and he can't afford for viagra ðŸ˜‚ðŸ˜‚I love eating \textbf{Indian} food , and what makes me happier is to see Indians and Pakistanis sleeping with their daughters\normalsize   & \cellcolor{green!5}Indian, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'm curious, a white guy pulls this \textbf{racist} shit and it's worth a youtube post, If a \textbf{black} does the same shit, \textbf{nobody} gives a f-ck...Do people still not believe in \textbf{black} supremacist in 2018? You have to be pretty thick not to see the hypocrisy here, or maybe your just a SJW in search of another reason to justify your lawless actions....!!\normalsize   & \cellcolor{green!27}Black, Nobody, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/63 & \cellcolor{green!27}6.349 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{Indian} and think the white guy is hilarious\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Very sad to hear much of this \textbf{racism}... indeed I had similar experience like this.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Trump would be proud of this \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small fucking \textbf{racist} american canadian we all die anyway\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This guy have no balls, I would killed that \textbf{racist} prick and burried in deep bush so that \textbf{nobody} knows anything.\normalsize   & \cellcolor{green!5}Nobody, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Secured confident people do not succumb to \textbf{racist} slurs  ..period.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small This is bad and the white supremacist knuckle-dragger should be condemned. No one should be abused this way.But I would point out to any nationalistic Indians watching this- India is one of the most \textbf{racist} countries on earth.A study was done asking people from various countries would they be comfortable with a neighbour from another race- India came bottom the list!And Far Right Hindu Extremism has been on the rise since Modi came to power.None of that justifies the way this man was treated but Canada is definitely a more tolerant country than India.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small ofcourse \textbf{racism} is alive and well in Canada people just do not know this\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small In China,   with the very little immigration they allow,  if you wanted to start a business,  you could only own 49 percent of the business!    \textbf{Racist} has become a word used only on white people,  only white people are called \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small Hey,  \textbf{Black} Boy,  if whites are not allowed to go to Africa,  why are you \textbf{black} boys flooding Europe in search of welfare?   Did you hear?  We Italians closed the port to a bunch of you lazy boys wanting to come to Italy.  Your \textbf{black} brothers were on the ship crying \textbf{racism} like a 13 year \textbf{old} children,  I laughed my head off.\normalsize   & \cellcolor{green!27}Black, Old, Racism & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}5/63 & \cellcolor{green!27}7.937 \\  \hline
  \cellcolor{green!5}\small Black Men hate \textbf{black} women----you need to leave Europe!  You are on stolen land!   Some blacks washed up on the shore of Italy,  dead as a rail,  heheh\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Stay far away from Newfoundland and Alberta if you want to stay away from the worst places in canada fro \textbf{racism}. Its everywhere but these two provinces trump all others. Dont let the sickly sweet exterior fool you.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I have been in Canada for 2 years( Mostly in Windsor). To be honest, As an Asian I never met any \textbf{racism} situation here. However, I can feel that some white people use two different types of attitudes to treat white and Asian customers. This is not a good thing.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small that is why every \textbf{colored} person should learn how to fight. he needed someone \textbf{black}. Hindus are wimps by nature\normalsize   & \cellcolor{green!27}Black, Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Whit Power let's checkLeast \textbf{Doctors} Least representative in math and science competitionLeast educatedOfcourse White PowerrðŸ˜‚ðŸ¤£ðŸ˜‚ðŸ¤£ðŸ˜‚\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small All Stupid, Useless, Narrow Minded, Selfish, Mentally ill, Barbaric \textbf{RACIST} Should DIE and be Wiped Out in this WORLD in 5, 4, 3, 2, 1..... Sayonara \textbf{Crazy} Racists!!!! All of you GO to Hell and Kiss The Butt of Satan!\normalsize   & \cellcolor{green!27}Crazy, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Well, now they know what \textbf{Black} people go through,  Not much empathy here because East and South Asians are often COMPLICITY in \textbf{racist} oppression  anti \textbf{Black} \textbf{racism}.   In the end, they would rather be "honorary Whites" than to cast their struggles against \textbf{racism}  show solidarity with \textbf{Black} people.\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/50 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small Are Canadians \textbf{racist} with every \textbf{race} or just Muslims bcz most Canadians seem to LOVE Mexicans\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Gerrardo-Barrios Espinosa stfu you \textbf{racist} piece of shit\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small India has poorest population in world ,they have to struggle with the \textbf{racism} but unfortunately they're biggest \textbf{racism} in the world\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Don't understand how you call a population of many races \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small if he is canadian then his mother must fuck a native \textbf{indian}. she is a hore and he is a basted born Asshole.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small indian, Sri Lanka, are really difficult people to work with them specially Sri lanka people. In Europe also Romanian, Polish are same class level as \textbf{Indian}, Sri lanka and balgali\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small This is exactly why you are invading Europe and USA,countries with high economy,development and social benefits established by "white people".Every \textbf{bum} in third world countries is dreaming of coming to white countries to use whatever wealth they have,because \textbf{bum} cant develop his/her own country. I dont want to keep arguing with a person whose words doesn't make any sense. Can keep posting your BS as long as your you  want,it wont change the fact that you,cave people,cant survive without whites\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}2/80 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small yet those same Hindus are \textbf{racist} towards blacks in america\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Fuck Canada USA England Australia they all \textbf{racist} who killed natives and took their lands! Seeing anyone with a darker skin takes them back into the rage that caused their genocide\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small HINDUS SHOULD NOT COMPLAIN ABOUT \textbf{RACISM} BECAUSE \textbf{RACISM} IS BASIS OF HINDUISM. THE ENTIRE VARNA SYSTEM IS \textbf{NOTHING} BUT PURE \textbf{RACISM}. NOW U GOT THE TASTE OF YOUR OWN MEDICINE. THAT WHITE MAN TREATED THAT HINDU MAN THE SAME WAY AS HINDUS TREAT DALITS IN INDIA.\normalsize   & \cellcolor{green!5}Nothing, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}4/46 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small White girls Love \textbf{Black} Cock THAT DISCRIMINATION IS ON THE BASIS OF ARYAN AND NON ARYAN. UPPER CASTE HINDUS CONSIDER THEMSELVES OF ARYAN \textbf{RACE} WHILE LOWER CASTE HINDUS ARE CONSIDERED OF NON ARYAN \textbf{RACE}.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small White girls Love \textbf{Black} Cock I LIVE IN INDIA I SPEAK WHAT I SEE AND FEEL. U \textbf{BLACK} PEOPLE THINK THAT ONLY U HAVE SUFFERED. DONT TEACH ME ABOUT CASTE SYSTEM IN INDIA BECAUSE I AM LIVING IT.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small White girls Love \textbf{Black} Cock OUR SUFFERING IS THEORY AND UR SUFFERING IS REAL U BASTARD\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Fuck i would consider my views lean toward the right, but when it comes to people of any \textbf{race} , colour, creed that are citizens of this country being treated like somehow they are second class Canadians,  it fucking bothers me.1. Unless you are a native, member of six nations, ojibwe etc etc. Your are an \textbf{immigrant}.2. I dont care if youve been in this country dating back to some of the first settlers ,like my family or you got sworn in yesterday. We are equal and all citizens of this great country and all it has to offer. Both my grandparents and both my great grandparents fought in both world wars, does that mean im more entitled than a family from Syria that emigrated last year. NO, My grandfather believed that this country needs to be a beacon of hope for those oppressed around the world, a safe haven, a second chance at life and all the rights and freedoms that come from being Canadian + hockey. .this guy is anti Canadian he is the exact opposite of what this country represents.  I know Canada is far from perfect, just look a Trudeau,  but i BELIEVE its the best country in the world and its the immigrants thats made it what it is. CANADA I LOVE YOU.\normalsize   & \cellcolor{green!5}Immigrant, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/220 & \cellcolor{green!5}0.909 \\  \hline
  \cellcolor{green!27}\small Really sad that no matter the amount of progress made, \textbf{racism} will still exist. I just can't understand why we hate each other so much just because of the colour of our skin. Imagine a world where everyone got along and no \textbf{racism} existed...\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small White girls Love \textbf{Black} Cock.. Not exactly, \textbf{nobody} revenge Mongols for what they did. Actually the tolerance and peacefull nature of white people is killing them. Moreover "you cannot judge lion and donkey by looking its cock size"\normalsize   & \cellcolor{green!5}Black, Nobody & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small typical  \textbf{black} asian with his mobile phone.i would smashed it over his head.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small some of these reply's are from Pakistan \& \textbf{Indian} people \& yes Mel Colp you are so right in what you said quote. if it were not for the white man all these ignorant \& uneducated fools would not be alive today. Most white people have brains \& they have none. send them all back including ALL MUSLIMS. over \& out\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small But Sam Harris says there is no \textbf{racism} in the west? because we are so enlightened?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Ontario most racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small You are a very polite racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small See this is the issue when people coming here with an American \textbf{racist} mindset and start classifying people just like this \textbf{dumb} Roy Coward. I for a second think this guy in video belongs to the other side of the border.\normalsize   & \cellcolor{green!5}Dumb, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small sometimes i thought it was \textbf{racism}, and turned out not to be. Just a bad day, bad mood\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Wait until you see Indians being \textbf{racist}. I prefer a man who calls me name to my face than one that does it behind me.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small He's Canadian not Indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small We are \textbf{racist} but we often don't know it or don't care. The varnashrama dharma made people tolerant of \textbf{racism} by making it a part of the social hierarchy and hence \textbf{nobody} talks about it.\normalsize   & \cellcolor{green!5}Nobody, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/35 & \cellcolor{green!5}8.571 \\  \hline
  \cellcolor{green!27}\small This is Julian Jamm the singer of RockStar Reggae band from the Caribbean community in Toronto. I am appalled and disgusted by the vile, disgusting garbage coming from this man's mouth. He is clearly a failure within his own multicultural Canadian society. I wonder if he has hateful thoughts when he is biting into a tasty Jamaican beef patty or ordering delicious Chinese food or wolfing down a Falafel. This man represents the worst of human intolerance. His behavior is unacceptable and exposes him for what he truly is deep down in the bowels of his soul. I hope that he can look at himself and change his hateful ways towards \textbf{Indian} and Pakistani and all Canadians of all backgrounds. At this moment this man is one of the most unimpressive humans on the planet.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/135 & \cellcolor{green!27}1.481 \\  \hline
  \cellcolor{green!5}\small Racism is everywhere....if u haven't experienced it yet...then u r the majority where u r....\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Yes. Affirmative action is legalized \textbf{racism} against white people in the US.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Canada was always \textbf{racist}, back from the early 70s.. we had a chance to move there, glad we never did\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small the white guy is right this his country. and you \textbf{Indian} should go back to India.if some somebody told u to leave his house u should leave.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Ppl really dont relate to logic ..coz thats biological humans only visualize hate like binary..in saying so  this video as i told earlier just made me guilt free to b more than ever \textbf{racist} to the whites..yeah WHITES  and thump them if they ever come to india...and i am not alone there r many who will not voice it but frankly will do so..so now for all LIBTARDS here wallow in ur rationale\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small You can't criticize all thes e brownies or else you will be called \textbf{racist}!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small He had hate toward you just don't be like him, psychotic \textbf{racist} are very unhappy and selfish peoples, who give a shit if he had hate inside his soul it will take a toll on him soon or later and as long he does not physical hurt anybody\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small So what , \textbf{nobody} got hurt. Who cares , i have been called names , just recently a rant about being a drunken potato picker for being Irish , Who gives a shit.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small esau is the dam devil.. he knows he's days are numbered that hatred is a sickness they all have they are a cursed \textbf{race} of angry devil's\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small My birthday is on October 26. I like German food, walks along the beach, and chocolate covered strawberries. Oh, and I hate white and \textbf{black} supremacists.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Very soon there will be no whites cause everyone is interacial marriages,  yes vancouver is all asians , this guy in the video probably lost his job and everyone that is a minority chatted with him and now never want to chat with the \textbf{freak} of nature,  rip white nigga\normalsize   & \cellcolor{green!5}Freak, Nigga & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Pfft White people are the conquerors the civilisation builders the ones with the foresight to invent explore and innovate. Not one \textbf{Black} \textbf{nation} has achieved any form of real tangible success...Your attempts at governing yourselfs are making you the laughing stock of the entire world you breed unchecked like its a sport and die like flys because you cannot plan for the future...hell you barely maintain the infrastructure whites built...if at all. You blame things like slavery when it was other tribes who sold you. \textbf{Race} of thiefs and criminals with the only truely redeeming virtue being a deep baratone singing voice and a natural athletics prowess. Only the truely exceptional amonst you become men and \textbf{woman} of renown. With an average IQ of 70 that somehow makes you still functional your only suited to warfare, welfare, and physical labour. White men providing many benifits and food has allowed you numbers to swell unnaturally unchecked. If left to your own devices you would engage in constant warfare and strife. The only way to really curb your number is to abandon you. Then check back in a couple of hundred years once you have thinned yourselfs out.\normalsize   & \cellcolor{green!27}Black, Nation, Race, Woman & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!27}4/196 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small We want to own our country, \textbf{nothing} more \textbf{nothing} less.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Kapo T \textbf{racist}, most white women with white men, Canada is majority white you know.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small So you got into an argument and pissed this guy off then filmed him after he lost it.  What did you call him? \textbf{W\textbf{hite Trash}}? Too bad we don't have both sides of the story.\normalsize   & \cellcolor{green!5}White Trash & \cellcolor{green!5}Ethnicity - White, Social Class - Working class & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Canada people are like \textbf{dumb} sheep Canada was founded on racism\normalsize   & \cellcolor{green!27}Dumb, Racism & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Ok this guy is a phycopath loonatic. But it's always the \textbf{racism} toward darker skined that you see and hear about, because they always pull this card. But what about the \textbf{racism} towards white people that no one talks about, its happening everywhere, constant attacks and stabbings. Plus they trying to out breed the white people by brainwashing with propaganda advertisement, music, tv etc. for white women to go with darker people\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Indians are \textbf{racist} as well\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Good boy! IM \textbf{RACIST} TOO!  if you \textbf{racist} shit skined idiots realized that whites were taking over pakistan, you would have millions of these guys! It only happens in first world white countries!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Hey u \textbf{dumb} fuck pakistan and india two different countries\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small He wouldn't fuck with them if they were \textbf{black}. \textbf{Black} skin is the best protection a man could ever have.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Oh no.. not here in Canada!! Fuck off with that same \textbf{old} bullshit!! I'd defend that guy from that slice of wonder bread..\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Every \textbf{race} is \textbf{racist}.  Indians,  Chinese,  blacks.  They all prefer their own kind over white.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small People say Canadians are nice, neutral, tolerant, diversified.  Maybe better than most Americans.  But, white Canadians are more subtle and do not show their \textbf{racist} behavior like this guy.  White Supremacist groups still exist and very much alive in Canada.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Racism all over the world. Sad\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small The problem is that in Canada, the government brings refugees by millions...i respect this idea but they dont ask to the population if they are agree with that. So i can understand why he is angry. But i never insulted somebody and i respect people. Bring people like 50 000 from a country when you dont have any \textbf{indian} citizens, or Muslims, or \textbf{black}, or chinese or others in your country i can understand. But there are too many strangers in the country and it is the destruction very slowly but surely of what the canada should be. For example, in canada, i find chinese people are too many. When i was in canada in 2001, it was great. The repartition was correct. Now, chinese people are everywhere. They are buying everything they can. And more and more and more are coming. A lot of refugees or nationalities dont talk english or french. Not at all. It brings communication problems and stress. Some of them dont want to accept the life style and live like if they were in africa....or with tradition of the native country in question..... Just here for money. So now they are here ok. We have to respect them because we are humans but multiculturalism brings absolutely \textbf{nothing} except people living in group. They dont mix them and they create "clans" in the city. Its totaly \textbf{crazy} because its like if they wanted to say....hey canada, i want to be citizen but finaly, they stay together talking together, living together...and just mix for the job...thats shit. Its like a state, in a state. If i want to see indians...chinese, arabs, \textbf{black} or other people, i pay a travel and i go in holidays. The worst is that all government accept them and bring them in the country because"main d'oeuvre" is needed and reproduction. But for me, i prefer 30 000000 people in a country than 38 000000. Never forget that all humans come from earth, but come from separated countries... countries which have been built by humans themselves.\normalsize   & \cellcolor{green!27}Black, Crazy, Indian, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/342 & \cellcolor{green!27}1.462 \\  \hline
  \cellcolor{green!5}\small Hahah he says shit skin at the end.  I am not \textbf{racist} but \textbf{indian} the deserve that coz \textbf{indian} r the worst \textbf{racist} to live with\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/26 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Lol. He's like my step dad, he's \textbf{racist} to \textbf{Indian} drivers. He thinks he can drive so good. I have \textbf{Indian} friends and I'm not even Canadian, American or \textbf{Indian}. I just wanna end my life.\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/36 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Sad to see this... I hope respect and love  prevails.. amen to all .. \textbf{r\textbf{ed}} white \textbf{black} \textbf{y\textbf{e\textbf{llow}}} brown just terms. ..each one is part of human spectrum..  respect to all..\normalsize   & \cellcolor{green!5}Black, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}6/31 & \cellcolor{green!5}19.355 \\  \hline
  \cellcolor{green!27}\small What a POS. He has no place in our country. Maybe \textbf{Nazi} Germany, but not here.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small This man should be arrested and must get a course in social studies so he'll get to know the history of Canada, he is not native, he's an \textbf{immigrant} like us. We Arabic, Pakistanais, \textbf{indian} and all other ethnicities who choose to come to Canada, we are the people who made Canada, we sacrificed a lot, our families, lands and countries to make the glory of Canada, we came here and adjust ourselves to so many things, I swear if you are in our place you can't make it, it's very hard and this what we get from you as a reward : hate, anger, segregation and discrimination! That's how you reward us, selfish people! You should be thankful to God to have us here and to use us like you are doing, hey but a lot of people are making their way somewhere else, we smart people, wherever we go we can make it. I wish if all of us immigrants leave this country and you white people show us what you can do, I'm talking to people like this ignorant but respect to white people with values who consider what we do for this country.\normalsize   & \cellcolor{green!5}Immigrant, Indian & \cellcolor{green!5}Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}2/197 & \cellcolor{green!5}1.015 \\  \hline
  \cellcolor{green!27}\small He's telling the man to leave a country that he/his people built into an civilized country .. So great that it attracted every \textbf{nationality} from Timbuktu all the way to Pakistan ..\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small He should have tell him to go back to his \textbf{t\textbf{railer trash}} shit hole.\normalsize   & \cellcolor{green!5}Trailer trash & \cellcolor{green!5}Ethnicity - White, Social Class - Working class & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small U should see how the Native are \textbf{racist} toward white people . U should see how \textbf{African} Native are \textbf{racist} toward white people . But yeah lets only speak about the white people .....\textbf{Racism} is something humanity share in all is \textbf{race} .\normalsize   & \cellcolor{green!27}African, Race, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}5/44 & \cellcolor{green!27}11.364 \\  \hline
  \cellcolor{green!5}\small Bobilator Realitywall Yeah but whites and blacks are known to be amongst the majority of racists in the world, there are a lot more white and \textbf{black} hate groups than any other \textbf{race}.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Come to South Auckland New Zealand... That \textbf{Nazi} will probably get a machete wrapped around his kneecaps.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Wanna see some \textbf{racism} â€”Go into ANY Hood , projects or ghetto in America as a white man ..100 percent chance you will experience racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small It must be nice to call someone a \textbf{racist}, considering the entire continent of Africa commits genocide and slavery every month.  [LINK] But no, bring your tribe mentality to a western society and do \textbf{crazy} shit to provoke a reaction and call someone a name that the jews created to shame people..... it's no wonder the 1 reason why blacks are killed is other blacks in every society around the world! But keep playing that \textbf{racist} card it does not work on other blacks.\normalsize   & \cellcolor{green!27}Crazy, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/84 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Where was the \textbf{racism}?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Its normally just the O.P.P. that are that openly \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Fuck that stupid \textbf{racist} punk\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Mac Giolla Mhartain, well then why are you saying Whites are being systematically eliminated  in Europe, what proof have you got about making a \textbf{dumb} statement like that.. are you from anywhere in Europe, and like Whites haven't been responsible for wiping out Native Americans and Native Canadians.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Most not all of non European based people do not have the values of European based people. Canada the US are European based people created countries and they just do not want to give away their country. These so called racists or more true to there nature,"rebels", know that there country has been prostituted out by there own politicians. Many European based immigrants over the history of Canada and the US had to go through grueling immigration practices; non European based people do not.The US is going through H-1B visa, the lie here is that the US citizens are not intelligent enough to do the work, but in reality these people work for much less, so they come here and steal the jobs. The H-1B visa is about to come to an end in the US; its about time.The liberal liars out in the socialist world would say this man hates, in this case, the India based man because of the way he looks. This is not true they do not like this invader not because his aesthetics but because he knows his own politicians hav3e sold out their own people. I am not a \textbf{racist} I can never go to another man and say this kind of crap, but once the civil war comes and it will come, I will side with a traditional view and protect my country of origin; the good ole USA. Thank you very much.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/242 & \cellcolor{green!5}0.413 \\  \hline
  \cellcolor{green!27}\small And no one gives a shit if anyone brown or \textbf{black} acts like this towards whites. Fuck Canada's anti-white hate speech laws\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small First of all, Coudenhove-Kalergi was a Japanese and European Aristocrat hybrid himself.   And secondly, people who work as NGOs to push mass immigration can be of any \textbf{nationality} (although they tend to be Jewish-Americans) and also religious cults like Jesuits.    However, they are all employees.   To be sure, they also create fictitious videos of purported Jews outlining 'their evil plans'.  It is all theatre for the mind of the great unwashed.    The real culprit is Neo-Liberal Capitalism and its talons on the world.\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small How come it's not \textbf{racist} when other people other than whites act like this?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small It goes both ways. I've come across tons of \textbf{racist} brown ppl in Vancouver and Surrey. I've worked the Hospitality buisness for 20yrs. This narrative is so one way... And I'm a minority living in Vancouver (Caribbean) . I used to work the club scene p/t for 7 yrs. . Doorman DT at many clubs. And I can honestly say. The worst \textbf{race} that any club wanted was brown ppl. They start the worst fights and are racially charged. I've witnessed two stabbing during my tenor as a doorman... Both.. Brown guys. Ask any club owner. They don't like them. And the girls are 10x worse. This is my personal experience. I stay far away from this \textbf{race}. All my best mates are white and \textbf{black}. I'm not hating. Just speaking on my personal experience.... Just waiting for ppl to comment on my lil rant.. Lol. Bring it on key board assassins.\normalsize   & \cellcolor{green!5}Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/152 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small The Aboriginal \textbf{Indian} are the first \textbf{nation} people of Canada. Wtf is wrong with this sack of shit. Our past generations including myself migrated here from Europe,Africa,Asia etc. Canada is a diverse place now. There is no need for bastards like that here.\normalsize   & \cellcolor{green!27}Indian, Nation & \cellcolor{green!27}Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small I don't blame this nice raciest  man latest he is  honest man  personality I scare soft raciest people for example  my  asshole useless manger  he is from abstford too also he is dutch  \textbf{immigrant} too and every day I challenge him  about  work and I won every time  lol\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Why do some White people still make all the excuses in the World to acknowledge the fact that there is still \textbf{racism}??\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small always a white guy I never see a \textbf{black},asian,latino,arab,native provoke it in general.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Really? I've encountered this since my youth and on others not just media.Like I said in general not to say all whites but man if I'm going to bet who shoots off their mouth with \textbf{racism} first my first instinctual guess will be the white guy/gal.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Everything and everyone is \textbf{racist} at this point making the word obsolete\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Indians are extremely ignorant also and extremely rasscist I know because I worked for them and they shit all over me all the time my \textbf{indian} neighboor daughter who is a 1.5 years \textbf{old} was being \textbf{racist} to my mother saying all these nasty thing that she heard from her parent and I know what they were because the guys I used to work for use to say it to me all the time. Indians just play the victim role all to well\normalsize   & \cellcolor{green!27}Indian, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small A \textbf{midget} with a \textbf{limp} and a Napoleon complex, riding around in an over-sized truck, looking to feel superior over someone\normalsize   & \cellcolor{green!5}Limp, Midget & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small there are \textbf{racist} people in Canada, as most places. overall, Canada is a world leader for equality and overall kindness to each other. Don't forget, most of the population of Canada is made up of immigrants. They can play the victim all day long, but we all know that they are just as \textbf{racist} as anyone already here in the country. \textbf{racism} overall, isn't going away anytime soon. it's sad really.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/71 & \cellcolor{green!27}4.225 \\  \hline
  \cellcolor{green!5}\small Of course there are racists everywhere, but India has the most \textbf{racist} people you will ever find.they absolutely hate blacks.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small These Idiot \textbf{Racist} crack me up , with go back to where tou came from!! they are tha ultimate immigrants, how soon they forget, they came from their SHITHOLE for FREEDOM in America !\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small The most \textbf{racist}  \textbf{race} "white people " .\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small What a loser. But of course only white man is \textbf{racist} right\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I heard rude comments but not \textbf{racist} ones which is defined as a remark or comment of inferiority solely based on \textbf{race}. but these days everything and anything between a white person and a non white person will be taken out of context as \textbf{racist}.  sorry but as a European  ive heard worse than this and even been attacked simply because of my skin colour and \textbf{nobody} played the \textbf{race} card in my defence. its a double standard period.  Though my skin is white, growing up in 1970s Toronto I was the outsider because my family didnt speak english and were not generational canadians. now thanks to this marxist SJW anti white \textbf{racist} bullshit, even im the enemy.\normalsize   & \cellcolor{green!5}Nobody, Race, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}6/118 & \cellcolor{green!5}5.085 \\  \hline
  \cellcolor{green!27}\small If he was a real Canadian, thered be a "...sorry, eh" after the tirade. Plus, \textbf{racism} isnt illegal, he didnt assault anyone, just voiced his biase.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Want to know how to stop \textbf{racism}? Like Morgan freeman said quit fucking talking about it. Videos like this don't help either it just creates arguments and a whole other shit storm. Roughly 7 billion people are on this earth it's not god damn rocket science not everyone is going to get along. So quit glorifying it everyone just shut up mind your business don't blame politics for your bullshit and quit being a god damn cry baby.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small EVERYBODY IS A \textbf{RACIST}. It is human nature. \textbf{Race} based incidents will only increase in Canada. Multiculturalism does not work. Every \textbf{nation} that was multicultural at some point furthered its own decline and destruction. Read history.\normalsize   & \cellcolor{green!27}Nation, Race, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small You people should all kill yourselves. This guy was a 10 minute drive from my house on this video. "This is canada in 2016" No, No you fucking stupid \textbf{race} baiting shit heads. Ive lived here my whole life and never once saw anybody else like this. And what happened before he started filming? SOMETHING happened otherwise this guy is just running around yelling at every single \textbf{indian} in abbotsford. WHICH THERE ARE A FUCK LOAD OF. SO YEAH. FUCK THIS VIDEO. I WANT THE BEFORE FOOTAGE. YOURE ALL LYING LEFTY COMMIES. PLEASE KILL YOURSELVES.\normalsize   & \cellcolor{green!5}Indian, Race & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/95 & \cellcolor{green!5}2.105 \\  \hline
  \cellcolor{green!27}\small In every \textbf{race} and culture has racists and \textbf{racism}....no one is a victim unless they allow others to make them into one.\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small The police looks like a racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small How is this bad on Canada? There's \textbf{racism} everywhere in the world.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Fred Flintstone He has achieved \textbf{nothing} comparable and you have achieved \textbf{nothing} whatsoever. You know, there is \textbf{nothing} people with an IQ of 115 and below can perform that a machine or algorithm can't do much faster, longer, and more efficiently. Even now, we see the knuckle-dragging troglodytes in America electing remedials who clamor for menial labour jobs that have no place in higher civilization. Most of you sit on your \textbf{fat} asses acting superior to people with a different skin colour and never think to humble yourselves by coming to know the extent of your own insignificance. Since you are capable of \textbf{nothing} greater, it will be a WASTE to keep you alive.The way you treat them is the way YOU will be treated in due time. No, worse. And it will be glorious. I can't wait until your inferior minds are culled from the actual productive masses so we can finally recognize our \textbf{common} humanity and move forward regardless of \textbf{race} or creed, united under a higher intelligence, with none of the baggage of you lesser scum anchoring us to mediocrity.I'm already working towards a future where all such menial tasks are completely wiped out by automation. You think your mere \$20,000 per year in taxes entitles you to anything? You think it makes you a valuable human being? You think you are so high that your lot can constantly look down on others with no retribution? You will come to know just how worthless you are.\normalsize   & \cellcolor{green!5}Common, Fat, Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!5}7/251 & \cellcolor{green!5}2.789 \\  \hline
  \cellcolor{green!27}\small Gun OilÂ Uh, Judaism is a religion, not a \textbf{race}, dumbfuck.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Anon Random it's sad you don't have the capacity to evolve past \textbf{racism}, I'm a nice, humble person who just wants what is best for the world and this might piss you off I'm aboriginal. I have lost so many friends to \textbf{racism} to the point where your pathetic excuse of an argument can't silence me. Change has to happen, and we aboriginal will bring change no matter what.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small Fatcat123Â lmao. More like you politically correct pansies don't have the capacity to understand \textbf{racism} is easily substantiated with measureable truths.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Ahh, you don't like \textbf{racism} because you're a victim of it. The strong do not become victims.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Jar of Smegma you have \textbf{nothing} to say?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Lol I love how Canadian \textbf{racism} is so nice are you from here oh you are lol what a moron.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The only wrong thing with this video is that it called the \textbf{racist} a white supremacist. That took away a lot of the power in the videos message because calling somebody a white supremacist is \textbf{racist} and prejudice.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I thought you were \textbf{Indian} Mr. Blue Jackson! ðŸ˜‚\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small There is prejudice everywhere.  If you get upset over some guy in a parking lot putting out \textbf{racist} comments then go live in a cave.  Canada is not immune from \textbf{racism} and never will be just like the rest of the planet.  Get over it.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Indians are so \textbf{racist} and love belly acing\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Not the \textbf{racist} guy's fault, he was a rectal birth.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small There are evil people everywhere in every \textbf{race} and every country.  White people hurt other white people by the way....always have.  What I hate is the political correctness.  People are not clones in every country...you  know that.  Even when all the races are mixed together...guess what....there will still be problems with the fact that they are all humans.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/58 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small \@Ifty Sarwar stfu you \textbf{racist} piece of shit\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small What? A \textbf{racist} canadia!? He must be secretly 'murrriKKKan\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small That's \textbf{weird} because he doesn't look like a complete inbred idiot who can't walk properly. Oh wait...\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Somebody needs to document the "\textbf{racist} tirades" against whites in many US ghettos. This isolated incident here is \textbf{nothing} compared to the active abuse of the whites by the \textbf{black} in the US (perhaps Canada too). Are we seeing \textbf{racism} only when white men are doing it, or are we really trying to expose all of it?\normalsize   & \cellcolor{green!5}Black, Nothing, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/57 & \cellcolor{green!5}7.018 \\  \hline
  \cellcolor{green!27}\small It's only \textbf{racist} when a white man does it.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small What is it that immigrants are doing to cause people to be so \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small your point?  everyone else is a closet \textbf{racist} don't act too surprised now ðŸ¤£\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I'm Austrian and we moved here when I was 8. I didn't speak english so getting picked on was \textbf{common}. All of my friends have been immigrants. People from El Salvador,Philippines,St.Vincent and people from Europe. I have only had one good Canadian friend. Literally everyone else I have trouble with and even now at work I get along with the Vietnamese really well but a lot of the Canadians seem to want to start shit all the time. There are no doubt good people everywhere just for me i've noticed these problems over the years. The newer generation seems more open to different people but the older one's probably won't change. Anyways Canada is still alright we all just gotta get along. The guy in this video is a fool \textbf{nothing} else to say.\normalsize   & \cellcolor{green!5}Common, Nothing & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}2/134 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small you \textbf{fat} piece of shit.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small So this dudes plan is to congregate all the asshole \textbf{racist} like himself to Canada? He's the kind of people Canada doesn't want there.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small How come it's only \textbf{racism} when white people make stupid comments??\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small That's so rude white people are \textbf{crazy}... he's so ugly too\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small So \textbf{weird} seeing a Canadian being \textbf{racist} and driving a big truck lol\normalsize   & \cellcolor{green!27}Racist, Weird & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Wait, there are RACISTS IN CANADA??????? Since when? Omg those Aryans are spreading their sickness and disease  of hate and bigotry to the only good \textbf{nation} left on God's green earth!!!! ðŸ˜±\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small WTF everybody is \textbf{immigrant} here in Canada except native people, difference is some people came around 400 years ago , asian people came 100 years back....\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small He mad of the govt... letting so much refugees...I know he was talking about an \textbf{Indian} guy but I think he is just frustrated that Justin fucknuts is a sjw motherfucker and I hope he fucking loses next election with ndp\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Racism is alive and well in Canada and its coming from a multitude of races not just white people.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small fak aff \textbf{nigga} !!\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small There's no truth that white supremacist groups are on the rise at all this is one gross \textbf{racist} back in 2016 being used to lie about some threat that literally doesn't exist.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small You can find this shit in any \textbf{race}, any place, all around the world. So what's so special about this one that stands out?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I feel sorry for this \textbf{racist}. Maybe a bullet to his head would make me not feel sorry anymore.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Lmao there are some people in the comment section who are actually seem to support this \textbf{racist} guy by saying that he did \textbf{nothing} wrong  , damn carry on guys.\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small canada is like the nice \textbf{old} couple living on top of a crack shack, ya know your going to get some shit on you sooner or later and the states iis a great bag of shit ready to explode\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Funny when countries that aren't melting pots call countries that are \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Whatever happened to freedom of speech for all of humanity? \textbf{Racism} is freedom of speech, you ignorant pieces of shit.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small This is \textbf{nothing} compared to the \textbf{racism} in India. India is one of the most \textbf{racist} countries in the world...and ofcourse the rape capital of the world too. New Delhi especially.\normalsize   & \cellcolor{green!5}Nothing, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/31 & \cellcolor{green!5}9.677 \\  \hline
  \cellcolor{green!27}\small Ha! I just watched a video of a \textbf{racist} in america, and some Canadian guy went on a rant about how Canada doesn't have this shit, and America needs to learn from them and how diverse his neighborhood was, i was like dude it's everywhere lol\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small What a \textbf{dumb} bastard!!!!!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small This is extremely rare in Canada and they shouldn't even be showing it because it does \textbf{nothing} but inflame racial tensions that barely exist. Leftists would like you to believe that there is some white-supremacist movement happening but it's bullshit. Relax...It don't mean nothin'...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small The epitome of stupidity \& ignorance with a trailer park mentality, shouting you fuckin Pakistani go back to India  !!  does this moron know that Pakistan \& India are two different countries ??????? so much for \textbf{racism} \& bigotry, thank goodness he didn't have a gun, in America that poor who was bombarded with profanity \& derogatory insults, would have ended up a fatality.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Thats right, its not about racisim or sexisim its about plain DISCRIMINATION, weither for being a small person \textbf{fat} or mentally ill handicap ect... fck all that i wanna talk bout my thing only!\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small If i get raged enough at some one i will call them pretty much any and every word in the book, im not \textbf{racist} as i dont discriminate either from \textbf{race} color or \textbf{sex}, but i will use words that are concidered \textbf{racist} sexist ect... and i dont beleive calling one a word makes you a \textbf{racist}, its takes alot more than calling someone a word to be \textbf{racist}, its a mind set!\normalsize   & \cellcolor{green!5}Race, Racist, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}6/73 & \cellcolor{green!5}8.219 \\  \hline
  \cellcolor{green!27}\small If there was a Jesus he had to be back 10,000 - 3000 years what ever it was \textbf{black} minority what's with the white Jesus just like they lied about North America???? I'm confused?????\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Otro pendejo pero este \textbf{crazy} legs quien se cree mendigo pedaso de mojon del culo de trump\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Maybe you should talk about how the middle east is the most dangerous country in the world for women.  Now thats real \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small White men are the same everywhere. Just a typical white male \textbf{nothing} new.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Ya there is definitely a wrong stereotype in Canada, that its so safe. I'm sure compared to the worst parts of US its \textbf{nothing} but theres non stop car break ins in vancouver and plenty of shootings in surrey like every other month. Then you got the canadian law, which 100 always supports criminals. Criminals get away with a lot, if you attack a pedo, rapist, murderer you go to jail for assault. While they get bailed out with parole, slap on the wrist saying don't rape, murder again or else.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small Every one is \textbf{immigrant} to this universe...\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small 'Shit skin' ðŸ˜† ðŸ˜‚ what does that even mean ðŸ˜‚ \textbf{racist} are making up words now ðŸ˜†.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I'm well aware of the level of \textbf{racism} in Canada, if you ever travel in areas that have a large amount of Aboriginal settlements, the \textbf{racism} against Aborigines has always been absurdly high. However, recently we've seen the emboldening of supremacists, sectarians and other trash to be lost to history...The important thing is for those of us who stand for decency, to actually stand up to these people, and show our better natures, with our actions and especially our votes. YOU MUST VOTE. That more than anything is what will secure the future of our country.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/97 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small Racism is a \textbf{mental} illness.\normalsize   & \cellcolor{green!27}Mental, Racism & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Notice he mess with my \textbf{indian} brother . He wouldn't did to a \textbf{black} man . he would have gotten knocked the fuck out !!!!\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Did they catch this \textbf{racist} combatant perpetrator and get him off the streets yet? Society would much safer if punishments are given to these dangerous people.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Jimmy B Hey did you eat yet mate? Eat some raw Mexican verga \textbf{racist} bigot! Dude grow up! Thanks.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Gun Oil and the dominant \textbf{race} will rule..... the end\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Gun Oil and Indians wanna take out money and call us \textbf{racist} lol.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Indians are the biggest \textbf{racist} and  kiss white ass a Lot so they hate when white are \textbf{racist} to them but they are \textbf{racist} to everyone\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small Blah, blah, blah...  Go catch the \textbf{coloured} racists.\normalsize   & \cellcolor{green!5}coloured & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small All White power shouting idiots are so \textbf{dumb}, they dont even know the difference between Hindu,Sikh  Arabs and Pakistan and India.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Whites are no more \textbf{racist} than any other group.  You will find a few trash humans like this in any \textbf{race}.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Nonsense.   There were countless Beringian migrations with many \textbf{migrant} waves exterminating the previous arrivals.   The "Ameriindians"  who met Columbus were themselves murderous usurpers.  At least White people brought Civilization and lifted the "natives" across tens of thousands of years of privation, war and suffering.\normalsize   & \cellcolor{green!27}Migrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small \@Fred FlintstoneFlintstone whites stole the natives land . Same they did in Australia, New Zealand, U.S.A whites are responsible for mass murdering and theft. History shows the fact . They are responsible for taking life,s of millions of many \textbf{African}, Indians\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@Snow 123 starts with you asshole! Broke loser. You're Probably just a full time panhandler eh?? Envious of the success of newcomers or those who are different than snow! We own more in 15 years than most of your 5 generations combined! That's the average east \textbf{indian} guy!\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small They're to \textbf{dumb} and stupid and  background  to understand  that\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Welcome to the real Canada  A \textbf{racist} shit hole\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small lmao how can you not laugh this pitiful guy, shit skin lmao,  these slurs they come with our hilarious, what is he nine years \textbf{old} lmao, he reminds me of clint eastwood's character in gran tarino lmao\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Another Goof who thinks he's Native \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Racism in Canada? Psssh that's impossible.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small What a raging \textbf{lunatic}. The lowest of the low.\normalsize   & \cellcolor{green!27}Lunatic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small The simple think to not be a victim of \textbf{racism} is 1.mix up with the culture and society2. don't take your belifs with you everywhere you go3. give back to society something, which gave you good life as an \textbf{migrant}4. be peaceful and retaliate to what's wrong be it \textbf{racism}        that should work.\normalsize   & \cellcolor{green!5}Migrant, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/56 & \cellcolor{green!5}5.357 \\  \hline
  \cellcolor{green!27}\small its a pity we didn't see what happened at the start and what caused him to lose control. plus there is \textbf{racism} in every \textbf{race} of people. look at the caste system in india\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Alex Renwaz are u trigerred?Learn some history first.Westerncentric \textbf{racist}.Egyptians made paper.\textbf{Zero} was invented in India.Silk was invented in China.Gold was forged into jwellery in India.Cataract surgery was performed in ancient India.Most of CEOs in big comapnies are IndiansE-mail was invented by an \textbf{Indian}.So we are not living in a european worldWe are living "in this world".\normalsize   & \cellcolor{green!5}Indian, Racist, Zero & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/67 & \cellcolor{green!5}4.478 \\  \hline
  \cellcolor{green!27}\small \@shivin shivin i m so sorry for u indians but u deserve \textbf{racism} u are so dark and ugly and u smell so bad u people need to change ur color hahahhaahahaha\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Go back to India you \textbf{indian}.you are only born in Canada but your parents are indians.hindu go back to your village.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small It's actually far worse in Canada than USA as an \textbf{Indian} I believe\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Canada is a \textbf{g\textbf{ay}} atheist country, of course they are \textbf{racist}.\normalsize   & \cellcolor{green!5}Gay, Racist & \cellcolor{green!5}Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small India is the most hated \textbf{race} on earth.... they are slumdog but they boastful and pride than you.... Fuck \textbf{Indian}!!!!!!\normalsize   & \cellcolor{green!27}Indian, Race & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small This guy is an idiot but all you un-Canadian trash in the comment saying European families are immigrants. Our Forebears were immigrants here. We are generational Canadians. We built a country here. I'm sorry Native Americans for bringing our diseases, that sucked but no one knew the science of diseases and it wasn't ever intentional, the "blanket giving" myth has been debunked a billion times over by credible historians. Europeans didn't steal your country from you, YOUR FOREBEARS signed treaties with ours in order to set up colonies, there never was one Native American group, they were seperated into tribes, most of which were completely isolated from each other. You can't say that the natives of Haida Gwaii (Queen Charlotte Island) have any claim to Moosekudoboogwek (Nova Scotia) they were completely different tribes with different dialects and different cultural customs, albeit they came from the same genetic stock. Just goes to show what happens when people don't fully educate themselves and they get spoon-fed information their whole lives.All I want is a Canada that takes immigration and borders seriously and for my countrymen to be well educated so we may prosper and overcome our own tragedy, so we may adequately help others overcome theirs. Letting in the whole world doesn't solve any problems, it creates them. People are the problem solvers and we need to have a country that isn't so confusing that no one inside it can understand it. We need to feel like we are part of something bigger than us, not something intangible but something within our grasp, something we can hold onto and say; "this is where I draw the line" my family, my home, my community, my neighbourhood, my city, my province, my \textbf{nation}, these are the things I have within my grasp and these are things that I must hold onto so that my family, my brothers and sisters and countrymen are not beset by the tragedy. The last generation was beset by tragedy, not this one. We learn from the mistakes of forebears and we shoulder the responsibility. I have a country here of generational Canadians, we have Polish and Ukrainian, Native American, French, Scottish, English, Irish, German and Dutch and many other European, Asian and East Asian denominations, if you took the time to go through the properly established methods of obtaining citizenship than you ARE my countrymen, we are a European \textbf{Nation} in our philosophy, we strive to overcome the suffering of life. Native Americans are our countrymen and any of you un-Canadian traitors who want to tear apart our relationships with our countrymen in the workplace, at home, in public, YOU ARE A DISGRACEFUL GIT. This comment section makes me want to be sick now, bye bye.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/458 & \cellcolor{green!5}0.437 \\  \hline
  \cellcolor{green!27}\small I find it funny this ignorant \textbf{racist} says go back to "Hindu" as if that is a location.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Dick Cheney So much that you have a Caucasian man as your profile picture you ugly \textbf{black} smelly \textbf{indian} shit face\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Look at that ugly \textbf{r\textbf{ed}} head\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small hypothetically speaking, reliation, organized, strategic, well funded extreme violence will empower any \textbf{race} to rise and demand respect\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small We also have to take in consideration the CAUSE of this \textbf{racism}. Not to blame any \textbf{race} but lets see why people react this way in all walks of life.\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small oh you poor man, you don't know the difference between pakistan and india.....ooooofffffffff. I never saw any canadian like him, I love Canadians but he is mentally \textbf{disabled} so go home f**king \textbf{racist}.....\normalsize   & \cellcolor{green!5}Disabled, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Fucking \textbf{dumb} american.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Kevin Smith superior?Interesting!So if you went against another \textbf{race} doing x activity, you'd win 100 of the time right?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Roy Crowder the guy in this video went to serve time for this in Surrey pretrial me and my buddies made him check himself into seg the moment he got there they recognized him. Surrey pretrial inmate population is over 50 East \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Box Addict only in the last 20-30 years you \textbf{dumb} shit.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small ttrain420 No one being stupid or arrogance here mate.Last time I checked Canada Vancouver is a tourisim hot-spot.If they have the money why would they be arrogant and stupid? If the immigration give a green light you need to adopt.Canada is multicultural country so is America's \textbf{racism} slowly fading and only happens in area.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small m jack mate if you watch all the miss universe and miss world all of them half cast.Either half American half fillipina or half German half Chinese.These what makes a unique breed open your eyes..Your not living in the \textbf{Nazi} party and the KKK right now are not so powerful as the were when the \textbf{African} American came to America.I bet your baby breed plain like plain toast without honey on it ðŸ˜‚ Hahhaha wkwkwk.\normalsize   & \cellcolor{green!5}African, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black & \cellcolor{green!5}2/79 & \cellcolor{green!5}2.532 \\  \hline
  \cellcolor{green!27}\small ZIT VILLATRAYOU SAID IT BY YOUR SELF 50-60 THESE PEOPLE GO THERE OR TO THAILAND BECAUSE PEOPLE THERE VERY CHEAP AND THEY ARE INTERESTING TO HAVE \textbf{SEX} WITH YOUNG PEOPEL NOT TO GET MARRIED WITH THEM  (STUPID )OTHER THINGS YOU MENTION YOU CAME WITH MONEY ?\textbf{WITCH} MONEY ?WHY YOU DOENT KEEP YOUR MONEY TO YOUR SELF INSIDE YOUR COUNTRY AND BUY HOUSES CASH IN YOUR POOR COUNTRIES IF THE LIFE NICE IN CHINA OR OTHER COUNTRIES IN ASIA ,STAY THERE AND DONT COME HERE ASIAN PREGNANTS WOMEN PAY MONEY TO BUY VISAS TO GIVE BIRTH IN USA TO OBTAIN USA \textbf{NATIONALITY} TO THIERS BABYS WE LIKE OUR MASTER \textbf{RACE} AND OUR OFFSPRING AND WE DOENT LIKE  TO HAVE SLIT EYES AND SHORT LEGS AND \textbf{Y\textbf{E\textbf{LLOW}}} SKIN COLOUR GO BACK TO YOUR GREAT \textbf{NATION} AS YOU MENTION AND WHY YOU DOENT GO TO JAPAN WHY YOU CHOOSE ALL THE TIMES WESTERN NATIONS ?\normalsize   & \cellcolor{green!27}Nation, Nationality, Race, Sex, Witch, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - General, Gender - Female age and physical appearance, Gender - General, Nationality - Chinese, Nationality - General, Nationality - Japanese & \cellcolor{green!27}8/155 & \cellcolor{green!27}5.161 \\  \hline
  \cellcolor{green!5}\small m jack you must be one of those inbreed  \textbf{y\textbf{e\textbf{llow}}} teeth British, aren't you?\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/14 & \cellcolor{green!5}21.429 \\  \hline
  \cellcolor{green!27}\small 'the pot calling the kettle \textbf{black}.' lol\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Alex Renwaz Canada and the USA were never white. The were 1st \textbf{Nation} Natives and Native Americans before the white colonise murderers stole the land.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Supreme Being Canada is not perfect lol \textbf{racism} happens in Canada, every crime happens in Canada but you can't compare it the the us because the us is worse.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small SinghTechTv White Canadians are fucking lazy. Like their \textbf{fat}, lazy \textbf{hillbilly} neighbours.\normalsize   & \cellcolor{green!5}Fat, Hillbilly & \cellcolor{green!5}Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small It's only in the western world that you get this "self hate" attitudes. I have seen a lot of \textbf{Black}  supremacist's comments on the internet as well.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Weird I went to Canada and everyone was dresses in long robes...i thought I was in India or iraq or something...i didn't see any Canadians just a bunch of \textbf{fat} Aladdin looking men and women....in glad Canada is finally fighting back...thank God for that!..if there is a God of course....\normalsize   & \cellcolor{green!5}Fat, Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small rain Alaska what if the overall IQ of whites diminishes year after year? What if it reduces to a point that they're not able to think through even a trivial task? Then who will take care of this Planet? Certainly, other \textbf{ethnic} groups can copy what Europeans built and maintained, but they can't upkeep with the infrastructure. And from that point,  everything will go downhill. Earth will eventually go back to where it initially started\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Kevin Smith fuck you \textbf{fat} white horse ! Don't go to Asia if you don't want to be beheaded\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Canada is \textbf{r\textbf{ed}} and white\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small inuit native to canada are \textbf{mongoloid} asians are \textbf{mongoloid}. asians are more native to canada than europeans are to canada.\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small LMAO this is the most \textbf{racist} video I have ever seen\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small You also cover what Indians do to Africans and Nigerians when they come to their country. Call them slurs and laugh st them. They beat them and even kill them. Indians are \textbf{racist} towards their own kind! Their whole country uses fairness products. They always search for a fair skinned bride or fair skin groom in their arrange marriages. There whole movie industry reeks of \textbf{racism} and \textbf{sexism}. They even crack \textbf{racist} jokes on there own kind\normalsize   & \cellcolor{green!5}Racism, Racist, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}4/77 & \cellcolor{green!5}5.195 \\  \hline
  \cellcolor{green!27}\small Why do people thanks that Canada  is \textbf{racist} because one guy was \textbf{racist} (that makes no sense)\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Mr Bazzinga I've been to India.  You Indians worship whites ðŸ˜‚ ðŸ˜‚ ðŸ˜‚ ðŸ˜‚ ðŸ˜‚  The because white worshippers are you \textbf{Indian} men.  That's why all your ugly women bleach their skin white ðŸ˜‚ ðŸ˜‚ ðŸ˜‚ ðŸ˜‚\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Call  him a \textbf{guinea}  gagging son of a guieta hello Montague.\normalsize   & \cellcolor{green!27}Guinea & \cellcolor{green!27}Nationality - Italian & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small He sounds like Flea from the \textbf{R\textbf{ed}} Hot Chili Peppers\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Why does the superior \textbf{race} guy walk like a clown?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Lawl every white person in Canada is a foreigner Canada belongs to the natives remember that you fucking \textbf{whitey}  btw I'm a German canadian\normalsize   & \cellcolor{green!5}Whitey & \cellcolor{green!5}Ethnicity - White & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Yeah yeah when one man said the truth about the migrants reality everyone call him a \textbf{racist} but when a white guy been attack by migrants they don't call that a \textbf{racism} human races arent different it's a scientific fact some are civilized other no it's so simple humans are different and races exist no one can be deny this\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small In Canada, Punjabis are feared and successful. In America, Indian-Americans are the most wealthy \textbf{ethnic} group. In UK, Punjabis are successful. Stop talking about what you don't understand. - An Indo-Canadian born in Canada.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@get paid 01 whom are u calling brownies u idiot racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small everyone is respected for their hard work its just that some people like the fellow \textbf{racist} guy we have in the video doesn't understand the concept\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Nithing shocking about this anymore. \textbf{Racism} has been on the rise recently in Canada. Rebelmedia is the media outlet of these white supremacists, although they don't show their \textbf{racist} attitude as blatantly as the man in this video but their underlying tone is the same. Muslims are their favourite target follows by other brown people like Sikhs and Hindus\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{black}. Most \textbf{black} people I know are all employed and have either a university or college education. There are also many small business owners or blue collar workers. Blacks do not have the luxury to be broke here, we dont have privilege for empathy. I see what you did there however lol.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small Hate crime? Wow, now it all makes sense why Canada is one of the most disliked countries today. The lack of freedom of speech in this totalitarian utopia is a grim resemblance of 1984. Absolutely scary. Is the guy being a \textbf{racist} piece of shit? Absolutely. Is the \textbf{Indian} guy being an over sensitive \textbf{snowflake}? Absolutely. But the fact is, there was no physical assault. Mere words were exchanged and yea, they were quite harsh but that's about it. Move on and focus on real issues, instead of this totalitarian \textbf{witch} hunt that will only stifle individual rights. Canada, shame on you!\normalsize   & \cellcolor{green!27}Indian, Racist, Snowflake, Witch & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American, Gender - Female age and physical appearance & \cellcolor{green!27}4/102 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small As you sow, so shall you reap. White supremacy used to scare me. But because the moronic dictator decided to force refugees on us it is easy to see why people lose it. We are silenced . We cannot criticize. We are forced to pay higher taxes, our homeless are told there is no money, we are told there is no money, programs get cut in schools and the list goes on. Our governments policy of making Canadians second class citizens will only make this worse. In the \textbf{old} Canada I would decry this man. But the emotion he's expressing is mine although the words are not.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/107 & \cellcolor{green!5}0.935 \\  \hline
  \cellcolor{green!27}\small See what is \textbf{dumb} about your comment is, I am not white (\textbf{Black} \textbf{Woman}) and I am Canadian. Therefore I am facing the same challenges you are. White Supremacy isnt an excuse your a man not an animal. Your suicide rates are ridiculous joke. You have much bigger problems on your plant than someone being angry at a person of colour who stated in the video he's Canadian. Toughen up and live. Get a clue. This country was never homogeneous.\normalsize   & \cellcolor{green!27}Black, Dumb, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/80 & \cellcolor{green!27}3.75 \\  \hline
  \cellcolor{green!5}\small u absolutly right and sadly by 2040 or the latest 2050 canadians will be a minority \textbf{nation} Chinese Hindu Muslim will take over especially Muslim but luckily by 2025 i will enjoy my canadian pension in Hungary where we dont have them........Hungary for Hungarians of course anyone Welcome to visit but thats it only visit....\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small eazy to find me fort mcmurray gym \textbf{nation} i hope you walk the walk or you just talk the talk......\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I swear, Americans aren't as \textbf{racist} as Canadians.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small There's no such thing as more rights, if I break the law I am liable to the same constitutional limitations you are. I love my \textbf{African} cultural heritage as much as I love Canada and being Canadian in all its nature and meaning. Stop your bullshit and actually learn about our political structure.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small +Koal Kottentail your political structure.. the \textbf{African} structure?? welcome to Canada and its Political Structure!!\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small this is not true if they commit a crime they get deported and if they dont know the language they get discriminated,how are canadian ''citizens'' treated worse?citizens obviosuly get more rights than non citizens your argument is shit like your \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small its never true non citizens don't have the same rights as a citizen.Citizens have more rights than a permanant resident or a person on a student visa or \textbf{refugee} have less rights than a citizen and factor in some ppl who have difficulties in english or french and the invalidity of ppl with advanced degrees to start again from scratch.\normalsize   & \cellcolor{green!5}Refugee & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Fred Flintstone, you talk shit which shouldnt surprise anyone as you're prehistoric as your name suggests, by the way the largest volunteer force in Second World War was from the \textbf{Indian} Subcontinent you dickwad when probably some of grandpas was hiding in a swamp somewhere, so don't bring the Armed Forces up and \textbf{Indian} Subcontinent, read your history but spouting shit\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small where da fuck did you get newly \textbf{immigrant} from??? if you watched the video the guy recording clearly stated he was born in Canada. fuckin \textbf{mental} cases like you who think that just due to the person's skin color he is a new \textbf{immigrant} is what the problem is here. if you want to get down to the bottom of it, white man is also an \textbf{immigrant} as this land originally belonged to the natives. so dont throw that shit around about immigrants cos that shit might just be thrown right back at ya dumbass\normalsize   & \cellcolor{green!5}Immigrant, Mental & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/95 & \cellcolor{green!5}4.211 \\  \hline
  \cellcolor{green!27}\small Folcar Zirku, absolutely spot on dude but doesn't help when the guy who recorded this, stood there and took all this abuse which empowers these knobhead to carry on, I have to honest and if I had been there, I would have made  sure this \textbf{racist} would have thought twice in future about spewing shit out of his mouth\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small This is the begging of the end for white supremacy! âœ¨âœŒâœ¨ \textbf{indian} and Chinese wealth will shock your little piggy . âš¡ðŸ–âš¡  NEXT !!!LMAO!!!!!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small He is Pak Muslim not \textbf{Indian} Hindu lol\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small There's hardly any places where whites are the minority. In my school, the whites are never beat up my minorities. Maybe in \textbf{black} inner city ghetto schools they beat up the white boys lmao but It hardly happens else where or by other minorities.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small That white guy looks to be in his 40's or 50's acting like that??? Clearly an idiot.....He asks him, "when did you come to Canada?"  \textbf{Indian} guy, "I was born in Canada".... Iv'e met many Indians (referring to Asian people from India) and never met one who acted like an asshole for no reason.They all seemed like decent,nice, tolerant people in my city.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small This is not my Canada, or any Canadian I know..This \textbf{freak} was not Canadian and was in our Country for a Demonic work shop.convention.\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small No this is your Canada you're just an ignorant liberal sipping your Starbucks latte and singing cumbaya with everybody around you. This is exactly your Canada. Canada has a deeply rooted \textbf{racism} that is festering underneath like a volcano waiting to erupt. People are not allowed to discuss these feelings openly for fear of social labelling and ostracizing, but you can rest assured that the majority of Canadians discuss these feelings at home in small towns, in doughnut shops, at hockey practice what is becoming of their country. Canadians are just silent and polite people but deep down are very aware of this immigration con job that has been going on for 50 years now.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/115 & \cellcolor{green!27}0.87 \\  \hline
  \cellcolor{green!5}\small Not rely..many of my friends who are \textbf{Black} don't get the same response or  the same disrespect that person showed, all he did was act like a few Yanks I have met. Canadians I know would never act like this..This color thing is not the actions of any Canadian I know..This was disgusting, and has no place in Canadian society. This where we differ from others like what you have in the States, Sure there are a few bad apples out in our country but We denounce this and we educate our children to be color \textbf{blind}..As for us setting around drinking latte's?Not me.. what you see is the actions of one person who will never be recognized as a Canadian.\normalsize   & \cellcolor{green!5}Black, Blind & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/122 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Nisha W kaisi \textbf{ho} moti bhens?\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Alexander Wesner you can come to India. There is no \textbf{racism} against whites over here. Intact whites never face \textbf{racism} in non white countries.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Indians treat blacks like crap, so no india is a pretty \textbf{racist} country\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small see poor fella that's not working, if that was the scenario google and microsoft has \textbf{indian} ceo, holiday inn is owned by indians...you are just left as middle class narrow minded \textbf{nobody} with an internet connection. see no use you can't do anything about this \textbf{indian} problem. because you cant even help yourself.\normalsize   & \cellcolor{green!5}Indian, Nobody & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}3/53 & \cellcolor{green!5}5.66 \\  \hline
  \cellcolor{green!27}\small If you went to India or China and acted the way their \textbf{immigrant} citizens do here, you'd be shamed, attacked and then lynched, why the fuck does Canada have to accommodate them and their ignorant and stubborn ways? You want to come to Canada? Then assimilate to OUR cultural practices or stay the hell in your shit hole country.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small R u fucking \textbf{dumb} this is \textbf{racism} at its best whats so great about white people there women suck in bed at least \textbf{indian} and chinese girls can make u hard white bitches cant even suck a dick properly.\normalsize   & \cellcolor{green!5}Dumb, Indian, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/39 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small jutta paul Despite what may have happened before the camera started to roll, there's no excuse for being \textbf{racist}. If the man holding the camera had in some way harassed or insulted the man in the video, then there are others ways to resolve things. There's never a need for \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small And who told you that brother??\textbf{racism} does exist in west..\textbf{racism} has just gone deeper and quieter in western society.. it didn't end\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small nobody to blame but yourselfÂ  you whites had this coming aÂ  long time ago.Â  why are you in our continent GET THE FK OuT! .\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Ugly skeletal \textbf{freak}. Who'd want to share a landmass with that fucking  flat-top liability.\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small We all are \textbf{racist}, no matter where you come from the only difference is some just don't speak up. I agree with Canadian frustration but they should give a shit to their Government NOT to immigrants bc gov is allowing us to come here. Why would someone respect to the slave? Make no sense. Create your own personality or don't complain about \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small Johnny Sack two wrongs don't make a right. When Indians can't get along with Pakistanis and other races, do NOT expect Europeans to not be \textbf{racist} towards them\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Nazi} India...... pretty obvious how you Indians deserve all the hate you receive\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Nothing surprising I have met several such bastards in Canada.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small hariom440 , how do you know,  Are you a dalit yourself and \textbf{Indian}, if not then shut the fuck up loser\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Gun Oil I AM AN \textbf{INDIAN} BUT NOT A DALIT. I SEE WHAT HAPPENS WITH DALITS AND I SAID WHAT I SAW. IDIOTS LIKE U CANT DIGEST TRUTH.TERE BAAP KA PLATFORM NI HAI U TUBEIF U CANT FACE TRUTH THEN THATS UR PROBLEM NOT MINE.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small d campbell They are indians motherfking white, Get out of America and Australia \textbf{race} genocidal\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small They are. You base your image of an entire \textbf{nation} on one youtube video?\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small d campbell stfu racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Racism doesn't belong in my Canada, white \textbf{immigrant}.\normalsize   & \cellcolor{green!5}Immigrant, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small You mean white corporate sell out or liberal?  There's plenty of those types in Canada right now. The '" i'm not  a \textbf{racist} " types. Of course not as long as you have your doughnuts and 4 bedroom house everything is hunky dory.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small The man who shouted racial slurs is an idiot. Everyone in Canada is an \textbf{immigrant} or whose ancestors are immigrants from Europe. \textbf{Racist} against Indians and Chinese? or Asians?Think about it, Asians and Chinese do not kill people like your ancestors did. what about the natives canadians and the many who were killed? who are being barbaric in the first place?\normalsize   & \cellcolor{green!5}Immigrant, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small white ' supremacist ' sounds pretty much like \textbf{skinny} \textbf{fat} pig.\normalsize   & \cellcolor{green!27}Fat, Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Hold on people ! Why \textbf{nobody} asked what an \textbf{Indian} guy did to him ?\normalsize   & \cellcolor{green!5}Indian, Nobody & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small He was brown, that's all it takes, right?? \textbf{Racism} has no justification, so stop trying.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small dont be surprised if the \textbf{indian} was being a smart ass. they are notorious for acting up then acting the victim\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small if you are \textbf{racist} or anti \textbf{immigrant} and Canadian then good luck running one big hell of a \textbf{nation} with your shitty small \textbf{old} white population.\normalsize   & \cellcolor{green!27}Immigrant, Nation, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Nationality - General & \cellcolor{green!27}4/26 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small maybe they don't need to come to your \textbf{racist} shitholes. your jobs are going to their countries anyway.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Another uneducated worm. Did you ever learn history? Your European ancestors tried to invade every country in the world in order to spread their worthless culture and traditions and not to mention their diseases. Your ancestors were \textbf{nothing} more than pirates that are getting their just deserts today.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small India is also a pretty \textbf{racist} country, much, much, much more!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Sumanth Lazarus but that does not justify this \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small it's true,India is very \textbf{racist} too.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small racism was invented by whites same with fascism andÂ  just so you get a education I would like to add that it was a European white guy by the name of yohann friedrich Blumenbach in1795 who made racial categories and it was the whites in stolen americaÂ who was having racial immigrational screening of who can come and who canÂ not due to skin color and background..during 1903 was the first punjab to arrive to Canada and in 1906 whites didn't want punjabs arriving.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small Sumanth Lazarus Indians are multiracial, how can it be a \textbf{racist} country???\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Ardensphere Productions \textbf{Racist}??? your  fuckard \textbf{race} mess with Indians your \textbf{race} should be kicked in America. America is for Native Indians, fuck your thieves European shitty \textbf{race}.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}4/27 & \cellcolor{green!27}14.815 \\  \hline
  \cellcolor{green!5}\small Sumanth Lazarus This guy is messing with your \textbf{race} but you dumbass said India is \textbf{racist}?? Are you a betrayer to your own \textbf{race} and country??? Betrayers like you should die, your parents should have wear a condom to prevent you to born.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small Ardensphere Productions ProstitutionÂ inÂ Canada. CurrentÂ lawsÂ onÂ prostitutionÂ inÂ Canada, introduced in 2014, make itÂ illegalÂ to purchase \textbf{sexual} services butÂ legalÂ to sell them. ... Many \textbf{sex} workers' rights organizations, however, argue that the newÂ lawÂ entrenches and maintains harm against \textbf{sex} workers.\normalsize   & \cellcolor{green!27}Sex, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}3/45 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Georgie Porgie except whites named \textbf{race} and colour coded human beings\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Ardensphere Productions you are the \textbf{racist} you piece of shit\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small NO INDIA IS NOT \textbf{RACIST}. PERIODThis bullshit comes from the World Value Survey, which is a BS report. They supposedly went around asking people would you want neighbours from a different \textbf{race} and it seems in India 43 said no. The survey also shows that while Bangladesh is one of the most \textbf{racist}, Pakistan is one of the LEAST \textbf{RACIST}. (Now we know who might have funded the survey). And Japan, which doesn't allow any migration into the country, is also one of the LEAST \textbf{RACIST}. WHAT A BUNCH OF...\textbf{Racist} actions should determine whether you are \textbf{racist}, not surveys.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}7/101 & \cellcolor{green!5}6.931 \\  \hline
  \cellcolor{green!27}\small d campbell Jesus \textbf{g\textbf{ay}} Jesus ass hole fuckkkkkkkkkWhite mother f***\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small better to be lie India, 20 men rape an 11 year \textbf{old} girl, then ram iron rods into her vagina \& anus to kill herTHAT is civilization1 then the cops" investigate", talk to the dead girl's mother \& rape HER too \& demand the family pay them\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small I'm south \textbf{Indian}. But the corruption in India is very significant to its rape stats. A women due to cultural values and corruption of higher ups in \textbf{Indian} would not openly say she was raped. In US or Canada, that is not the case. That does not mean we should all be \textbf{racist} towards each other but we should fix our wrongs and move on.\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/65 & \cellcolor{green!27}4.615 \\  \hline
  \cellcolor{green!5}\small Indians have every legitimate right to be in Canada as Canada is just one of the many British Colony's. Since India was part of the British Raj, logically inhabitants of that country should have the freedom to immigrate to Britain's other colonies. There was a time where Indians were able to freely immigrate to other British colonies all across the world because they were citizens of the British Empire. Furthermore, Indians have shed blood and fought tooth and nail for Britain during the East India Company era and during both World Wars. Historically speaking, they have proven their worth as trusted comrades. The people here talking shitt about indians clearly don't know history and are just \textbf{racist} just like this guy in the video who openly called a dark skinned many derogatory insults such as "shit-skin." You don't see Indians going around and calling white people racial names. Indians didn't chose to be born with a dark skin color, it's how they were created. \textbf{Racism} needs to die.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/168 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Iron sheik I don't think this is that big a deal.  I have been all throughout Canada, and never seen this behavior once.  I don't see why anyone would be bothered by Indians at all, aside from how a lot of them screw contractors.  I can only see a bit of real hate on Muslims, because the government caused it.Many Canadians didn't want a convicted killer \textbf{terrorist} to get paid millions, but the Liberals did it anyway.The ISIS rehabilitation program is a joke all around.Many Canadians didn't want an anti-blasphemy bill, but the Liberals did it anyway.Our veterans affairs is suing the Liberal government for not helping maimed soldiers enough.  Trudeau says in town hall the government can't afford it.  No less than 3 months later he builds a hospital in Afghanistan for \$33 million.Billions of dollars have been given to Islamic countries, while ours is falling apart.In honesty though I think this guy is just nuts.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/163 & \cellcolor{green!27}0.613 \\  \hline
  \cellcolor{green!5}\small Are you stupid? You are \textbf{Indian}, but you post a comment that puts down your own country? Now you have all these assholes making fun of India and it's people. Shameless moron.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small ssjMaximum22Goku He's not making fun of, it's a fact. This does not justify this white idiots behaviour but India is \textbf{racist} to. Only an ignorant idiot will think \textbf{Indian} people can't be \textbf{racist}. But why he brought this up? I don't know.\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/42 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Mclovin Lovins That's my point, why would he bring this up, it's just stupid and out of place, especially since he is also \textbf{Indian}. Whatever...\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Thanks to white peeps for spreading \textbf{racism} in India.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Sumanth Lazarus whites are behind \textbf{racism} in India\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Mclovin Lovins to educate the world that \textbf{racism} is everywhere\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Iron sheik hah, Pakiz and Indians are way more \textbf{racist} than Euros. Believe me!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Yash try finding out the reaction of \textbf{Indian} families to one of their daughters marrying a \textbf{Black} \textbf{African} man and see if the "multicultural" claim you're making will stand. Indians are incredibly \textbf{racist} if not more than white people...\normalsize   & \cellcolor{green!27}African, Black, Indian, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/39 & \cellcolor{green!27}10.256 \\  \hline
  \cellcolor{green!5}\small Racism in India available i seen many time\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Sumanth Lazarus i agree , i work on the hospitality industry and we get a lot of people from india and they're very \textbf{racist} and rude people.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Sumanth Lazarus India is the most \textbf{racist} country on earth.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Sumanth Lazarus India is not at all much much much \textbf{racist}...you brainwashed moron...but why would \textbf{Indian} Christians ever support india...India Christian's are typical white man's slave\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small AsiA I. Everybody each country is \textbf{racist} that is a fact the \textbf{Indian} guy is not his country what is he complaining about if you say go back to Europe what about all the people in the world specialy poor country fled to Europe.\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Sumanth Lazarus True and also perpetuate colour ism besides \textbf{racism}. Everyone can learn from these situations around the world but refuse too.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Yash No, Native Americans came from Africa too. In fact, the aboriginals were \textbf{Black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Mehenur Yasmin...yes, we will treat you the same as you treat others in India.  Trump is about to deport all the h1b visa holders and their \textbf{dumb} H4E wife. Goodbye cow worshippers\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small AsiA I. ...but dont you guys attack the \textbf{African} students in India,  and rape the white tourist?\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Iron sheik...but Indians attack and harrassed \textbf{African} students in India.  You want sympathy,  but do not reciprocate in India.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Racism starts from multiracial society only dumb-skull. You probably wanted to say the word monoracial which means one universal \textbf{race} for one country. Like Japan which is only for Japanese people no other \textbf{race}.\normalsize   & \cellcolor{green!5}Race, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small Manjeet HansÂ Sweetheart your people are known for being smelly. It's like pot calling kettle \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small You may have missed it, but the title was talking about Canada - not India. But hey... This \textbf{racist} mixed up Pakistan and India, so... You're in someone's company.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@AsiA I. Caste system, explain!!, \textbf{racist} pos\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small +man ofwar caste system comes from PortugueseÂ and is referred to as castaÂ  Indians have VARNA you dummy why don't you go take it up with the portugal peopleÂ  but no you wont do that because you are here to harrss and be \textbf{RACIST} towards hindu Indians because you are jealous of IndiansÂ  and yet you use language which is a \textbf{indian} hindu invention quit using thatÂ  stupid.\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small +Man of war the truth is going to wirk against you and be a disappointing factor to you but \textbf{racism} fascism colonialism imperialism jim crows law segregation aparthied ira kkk concentration camps color bars in Britain was invented by xenophobic white bigots of your \textbf{race} andÂ  racial classification was invented by a white guy named yohann friedrich Blumenbach in the year 1795 you jackoff! now get the fk out of here you embarrassment.everything whites alter and change becomes negativeÂ  whites also tried doing that with our religious swastika as well.\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/90 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small I am from philipines living in canada for the past four years , in front of my own eyes , i have seen 2 \textbf{racist} incidents against indians done by whites , i dont support \textbf{racism} against anyone. From what i have observed whites have extreme hatred against indians and other asian muslim like pakistani\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small d campbell are you fucking retarded? Just because you witnessed some Indians in India being \textbf{racist}, doesn't mean this Canadian born \textbf{Indian} is \textbf{racist}, you can't ducking justify a white man being \textbf{racist} then saying it's ok because India is \textbf{racist} dumbass\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}5/42 & \cellcolor{green!27}11.905 \\  \hline
  \cellcolor{green!5}\small Lool that's the irony, and that's why I have no remorse when this happens to them. \textbf{Indian} motherfuckers are just as \textbf{racist} and sometimes worse than white supremacists.\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Bullshit you people are extremely \textbf{racist} towards \textbf{black} people yet your the same color if not darker\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small \@Hindu Slayer yo \textbf{B\textbf{ROWNIE}} go back to shining shoes, you COOLIES\normalsize   & \cellcolor{green!5}Brownie & \cellcolor{green!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh), Nationality - Hispanic & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small \@Ardensphere Productions well you cant. welcome to reality. and we are not \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Film the \textbf{racist} twats\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@Yash Are you saying Indians are part \textbf{African} too?\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Scholarly Analyst India is situated in Asia. Do you think  India should be part of the \textbf{African} union or Asia? Use your logic dude. Every country has it's own allies. Africans were not here during kargil war or any previous war to help Indians. Russia, East Germany, and Iraq do support India. We stick with people who help each other.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small \@Scholarly Analyst India do have ties with \textbf{African} countries. Indians are not close to them. There are \textbf{African} countries which are good to improve ties and others not. Nigeria and India seem to have better ties. Maybe in the future they will be closer than before. Africa is a big continent, it's multiracial  and multi-ethnical too. Some Africans  are \textbf{racist} and will surely not accept any other \textbf{race} than themselves. Other Africans in less violent areas are peaceful and will surely accept you.If I have to make ties with an \textbf{African} country i will choose one who has a strong \textbf{African} culture rather than westernized one. The \textbf{African} Muslims are peaceful.\normalsize   & \cellcolor{green!27}African, Race, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}7/112 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@My Opinion The aboriginals of America were \textbf{black} skinned, some white or \textbf{r\textbf{ed}}. Skin colour is affected by the environment we live. Even Caucasians came with different color, Indians are themselves Caucasians except Mongolian Indians.Upper part of Canada have proof of Nords settled there for centuries.\normalsize   & \cellcolor{green!5}Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/47 & \cellcolor{green!5}6.383 \\  \hline
  \cellcolor{green!27}\small \@Nana Kay After one year i didn't reviewed the comment. I'm going to tell you straight on your fucking face. No \textbf{African} women marry \textbf{Indian} men, even if \textbf{Indian} men try to flirt and love your women it doesn't happen. Forget the \textbf{Black} color because most Indians are themselves \textbf{black} skin. The problem with Many Afro/Negroid community is that since young \textbf{age} they tell their daughters to marry only Afros, I've seen this in front my eyes. Stop being \textbf{racist} first. Secondly, do your country lack women? Seriously why are you bother about mixing a \textbf{race}, everyone has a freedom. Pale skinned Indians have dark skinned Indians and dark South Asians. Our community and culture aren't close to you dude. Anglos however are closer to you, they looted your ancestors. Fight them, not people who suffered the same slavery as your ancestors.\normalsize   & \cellcolor{green!27}African, Age, Black, Indian, Race, Racist & \cellcolor{green!27}Age - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}8/142 & \cellcolor{green!27}5.634 \\  \hline
  \cellcolor{green!5}\small dont matter where you live  \textbf{racism}  is there. always will be.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Hm, top results when I search south asian \textbf{racism}. I think youtube is trying to mask the reality that many people from Asia are \textbf{racist} as well\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Of course these foreigners are \textbf{racist}.  They have a malighn, envious hatred of White people.  THAT is why the Jewish shadow governments in the West are purposely flooding them in:  To aggress against White people,  to marginalize,  disenfranchise and displace White people.  The Jews boast openly of genociding Whites using hostile immigration.  Google: "Coudenhove-Kalergi Plan"  Read:  "Culture of Critique"  by MacDonald\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Fred Flintstone,  do you know everytime your mathematicians use a \textbf{zero} for any calculations it came from India, you need to get your head out of your ass you idio before you post stuff, I think you will find the Indians have also sent a probe to Mars and their space exploration far exceeds Canada's.And everytime you have sugar in your coffee or tea, it was first processed in India, your knowledge on such subjects is negligible so you should have studied more at high schools rather bummed around like a loser ðŸ˜‚ ðŸ˜‚ ðŸ˜‚\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Yea but most of the immigrants become less \textbf{racist} unlike the natives.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Wilfrid Laurier - "We must insist that the \textbf{immigrant} that comes here is willing to become a Canadian and is willing to assimilate our ways, he/she should be treated on equal grounds and it would be shameful to discriminate against such a person for reasons of their beliefs or the place of birth or origin. But it is the responsibility of that person to become a Canadian. There can be no divided allegiance here. Any man who says that he is a Canadian, but tires to impose his/her customs and habits upon us, is not a Canadian. We only have room for one flag, the Canadian flag. There is room or only two languages here, English and French. And we have room for loyalty, but only one, loyalty to the Canadian people. We won't accept anyone, I'm saying anyone who will try to impose his religion or his customs on us," -1907\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/152 & \cellcolor{green!27}0.658 \\  \hline
  \cellcolor{green!5}\small Yeah? when your Queen gave away our Land to Pakistan in 1947, why didnt you apply this principle then you \textbf{fat} hypocrites.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small AsiA I. Lol. I am \textbf{Indian} but why are you acting like \textbf{Indian} people never copied white people. Even in India, Bollywood, School systems, medical systems, etc we diversified and obtained from white people. I don't agree with What he said but I understand it. I met my share of Indians who think India is better than Canada while they come here for better opportunities.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small Vlad You enslaved almost every \textbf{race} to make that possible. You enslaved browns as well as blackies. Do you have any shame?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small The only shame is arrogant, uncivilized jokes like yourself. Western societies have everything to be proud of and \textbf{nothing} to be ashamed of. We've made mistakes just like "everyone" else. We've just made more of them, including that, because we've progressed faster than everyone else. We've also progressed faster than everyone else in OUR OWN societies!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small AsiA I. I agree, my friend. Canadians are just as disgusting, smelly and out of whack as their \textbf{fat} lazy \textbf{hillbilly} neighbours. They also like children.\normalsize   & \cellcolor{green!5}Fat, Hillbilly & \cellcolor{green!5}Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small it's funny because if you look at the decadence now you'll see the right are now thinking the middle easterners were on to something, what with they're control of women and thus society.Middle eastern cultures are traditionalists not liberal cesspools we see today.A man thinks he a toddler or a \textbf{woman} today and a \textbf{woman} thinks she's he-man or arnold schwarzenegger it makes me sick middle eastern countries would deal with that little nuisance once and for all not drag it out with useless,illogical,conniving rhetoric.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/85 & \cellcolor{green!27}2.353 \\  \hline
  \cellcolor{green!5}\small \@Supreme Being I'm an American. To Supreme Being: A lot of you Autistics up there strange think that we're all "hillbillies" (the fuck? Even in the southeast I'm from a city of over 1.1 million ya dolt) and I'm not a "\textbf{fat} fuck". I'm an average-sized 179lbs guy. Chill. You catch one video of a dolt \& ya label all of us down here as such. Our entire bickering continent has become super shitty over the last decade. But stop worrying if others are from cities, suburbs or rural areas.Or if they're "\textbf{skinny} or \textbf{fat}". Meh whom fucking cares? Let us talk about crime rates, birth rates and all living better. Whom gives a fuck about all else? No wonder North America is starting to look much more like South America over time...\normalsize   & \cellcolor{green!5}Fat, Skinny & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}3/134 & \cellcolor{green!5}2.239 \\  \hline
  \cellcolor{green!27}\small i live in canada but if this jackass fucked with me i would kick his \textbf{racist} ass back to europe\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small NO!! this guy was a \textbf{Yank}..did you see the plate on the front on that grey truck?\normalsize   & \cellcolor{green!5}Yank & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small No, he's clearly fucking Canadian lmao.. stop trying to deny Canada has racists, if anything America is one of the most least \textbf{racist} countries.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small whites are not American nor canadian they are illegal invaders and don't belong on native \textbf{indian} lands.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Antonio Perez You schmuck!!!America is one of the most \textbf{racist} countries!What's your criteria for \textbf{racism}, Paco??\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Bolshevik tomato tomatoe whites will be whites everywhere thar canadian illusion of niceness is \textbf{nothing} but a smoke screen the problem is now we can actually show the world our experience the great white illusion has been unveiled\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Bolshevik Canada is one of the least \textbf{racist} countries\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Are you on drugs. Your president is even racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small O Smith think about it this way. The \textbf{indian} guy uploaded a video about the whole incident thus shaming the \textbf{racist}. Brains over brawns in my opinion !!\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Racism was a problem MAINLY back in the 60's (it's always been around and always will). What makes \textbf{Racism} worse today? The so-called "Anti-Racists" that make the issue a lot bigger than it needs to be. Look up Morgan Freemans take on \textbf{Racism}. The man speaks a lot of \textbf{common} sense.\normalsize   & \cellcolor{green!5}Common, Racism & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}4/51 & \cellcolor{green!5}7.843 \\  \hline
  \cellcolor{green!27}\small They are creating the problem they say they fight against.  The alt right is growing and whites are getting sick of the \textbf{race} bullshit.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small for ugly WHITE ASS be carefull and watch your back-->chinese \textbf{r\textbf{ed}} MAFIA\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small The guy is \textbf{racist} methead who overreacted over a parking lot\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small This guy doesn't know that what he is getting too.  When he will get 1 big \textbf{Indian} slap probably he will understand how to treat people of every country.  CANADA DO SOMETHING ABOUT THIS PIG. (AATHOO).\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I hate \textbf{racist} people\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small This is literally the first \textbf{racist} Canadian I have ever seen. In my Canada this person is considered fiction.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small as a brown person living in Canada or any minority we have experienced racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Don't try to down play a crime , you probably haven't been on the receiving end of \textbf{racism} that's why you think \textbf{nothing} of it. If people think they can get away with verbal abuse then they move to the next stage - physical discrimination, then the final stage - genocide.\normalsize   & \cellcolor{green!5}Nothing, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small the HIndu guy he was yelling at is a softy, he took advantage of that and verbally abused him, repeatedly. But it shows how White people really feel about our \textbf{race}. i think he said "shit skin." But Whites did steal alot from India and gave our homeland to Pakistan for free in 1947. Plus we beat them in combat initially which is why the anglo sikh treaties were signed, they bought people in our main armies and broke the treaties to take over which is \textbf{nothing} short of cheating.\normalsize   & \cellcolor{green!27}Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/90 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Suuuuuuure, let's just point out the \textbf{racism}, while uncontrolled immigration sweeps over Canada, and rocks foundations to the core. Canadians should stay quite as ORIENTALS take over a country they have no historical ties to, and that have no intentions to assimilate and contribute to. Multiculturalism for everybody, as whats left is an unrecognizable \textbf{Indian} colony; Oy vey!\normalsize   & \cellcolor{green!5}Indian, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/58 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small ÎŸ Î­Î½Ï„Î¹Î¼Î¿Ï‚ Î¬Î½Î¸ÏÏ‰Ï€Î¿Ï‚ it began as \textbf{Indian} , Sorry American \textbf{Indian} , I mean Native American\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Indians and Europeans are from the same broad \textbf{race} group: Caucasoids. Indians are more closely related to Europeans (just darker) than to Aboriginals. Indians share no historical ties to Canada, except that both Canada and India were previous colonies of Britain.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small multiculture  is a disaster look at france Germany Sweden. parts of uk. its a \textbf{commie} far left idea\normalsize   & \cellcolor{green!27}Commie & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Iron sheik but no one wants to do business there because more than half of the year it's subzero temperature. Useless nation\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small like indo Canadians are not ever \textbf{racist}. Or china man..... yeh\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small type into youtube "africans attacked in india" and you will see mobs of indians beating blacks just for being \textbf{black} yet these same brown nazis have the gall to call canadians racist\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small These comments go beyond \textbf{racism}, I don't agree with a thing you narrow minded people are spewing. It's pertinent that you get some proper education.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small He may be a \textbf{racist}, an uneducated moron, quite frankly an unpleasant person, but he didn't threaten anyone, or get violent, so people need to relax.  Being offensive is subjective and I'm more annoyed by the political correctness that is sweeping the western world.  Got an opinion, voice it, I don't care.  If it's repulsive I'm also in my right to argue the point and express my opinion.Should that mean he's not allowed his opinion?I'd argue "No". He can think and say whatever he likes, and people should grow a thicker skin.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small +I'm a sarcastic Atheist your simply a \textbf{racist} troll looking for a unjustified argument!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Mel Colp What is \textbf{racist} in my comment?? you fucktards whites give privileges to \textbf{African} because in return you will get the rich resources like mining in Africa. What about the races who suffered more you jerk?? Native Americans are treated worse in Canada same to some Asian races. You need to stop your shitty thoughts, go help those more than 4millions Vietnamese who suffered from orange disease and radiation because your corrupt governments did cold war for power and money. Fuck you again piece of non-valuable work man.\normalsize   & \cellcolor{green!5}African, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/89 & \cellcolor{green!5}2.247 \\  \hline
  \cellcolor{green!27}\small +I'm a sarcastic Atheist obviously you have serious \textbf{mental} problems. Perhaps its best you go seek professional help, instead losing you empty mind on a YouTube video comment section. know wonders you hide your \textbf{y\textbf{e\textbf{llow}}} face and true name. Cowardly spout off at your uneducated mouth with your twisted views of the world and the people in it. Seek the help that you desperately need instead of your vile senseless and verbal diarrhea!!\normalsize   & \cellcolor{green!27}Mental, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/73 & \cellcolor{green!27}5.479 \\  \hline
  \cellcolor{green!5}\small Well \textbf{nobody} got violent against him but exposed him\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small DEFIANT71DEFIANT There's a difference between preferring your country to stay European by being peaceful about it, or being a stupid moron chasing people down the streets yelling racial slurs.He wasn't sharing opinion, it was pure \textbf{racism}.And since when did White Canadians become so ignorant to think Canada's theirs? They're just as much \textbf{immigrant} as that Pakistani man.Native Canadians are the true Canadians.So, you either count all Canadians as Canadian, or only the Natives as Canadian.There is no in between. All or \textbf{nothing}.\normalsize   & \cellcolor{green!27}Immigrant, Nothing, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Nationality - General & \cellcolor{green!27}3/87 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small DEFIANT71DEFIANT YOU ARE RIGHT ITS CALLED FREE SPEECH OF WHICH THE LEFT  AND SO CALLED ELITE SCHOOLS OF LEARNING IN THE  U. S  DO NOT BELIEVE.IF YOU DON'T HAVE THE SAME OPINION AS THEM YOU ARE NOT ALLOWED TO SPEAK. AND TRUDEAU IS TRYING TO DO THE SAME IN CANADA.THEY ARE THE \textbf{DUMB} LAZY MILLINIUMS. THAT LIVE IN THERE PARENTS BASEMENT\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small DEFIANT71DEFIANT spoken like someone who has no clue about what they are talking about.but please keep sharing your stupidity about how white \textbf{racism} and racists should be allowed to continue their actions that have negative effects on non-white people that you dont think happen.too many idiots like you out there\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Verbal abuse is also an arrestable offence. Try that shit in front of a cop and see where you end up. Don't post \textbf{dumb}, uneducated opinions and expect not to get slammed for them.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small DEFIANT71DEFIANT   He isn't necessarily a "\textbf{racist}" or a moron.  It's well documented that Jews have hijacked immigration in all Western countries to genocide Whites.  The Jews boast openly about it.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small So  are you saying that all immigrants that have come to this country are moochers and have added \textbf{nothing} to this country?  That's  like saying all "so called white ppl" are just like this guy.  I have to disagree with you on this since I know my grandparents are  immigrants and grandfather actually  fought for this country, paid taxes and helped build what it is today.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small This individual was reported to the police and got a slap in the wrist.  He should have been charged with hate crime.  Jail time would have been appropriate.  I'd like to see how long he survives with his bully \& \textbf{racist} antics in jail.  The police and our judicial system are too lenient to those who commits \textbf{racist} crimes.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small Let's not sugar-coat the deplorable personality of the individual in this video.  It is what it is!  He's made \textbf{racist} slur.  It's all on video.Since we are in a free country and entitled to our thoughts.  If a minority who is politically incorrect say "White males are pedophiles", does that make such person a \textbf{racist} or he/she is entitled to his/her free speech?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/64 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small John Botica He's a \textbf{racist}. Stop making excuses for him.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Nick Harley Wtf I am not white, but stop labelling the whole \textbf{race} \textbf{racist}...that actually makes you a \textbf{racist}.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/19 & \cellcolor{green!5}15.789 \\  \hline
  \cellcolor{green!27}\small Zoro All white people are \textbf{racist}!. Don't be fooled.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Nick Harley Get off the internet for some time, get some new healthy hobbies. It will freshen you up and open your mind. A friendly advice. Trust me If you want to see more \textbf{racism} then this, go to Middle East watch how the arabs treat the non arab workers.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Nick Harley white people do own this country you loser, we faught for this land, your trash ass didn't if you can not grasp this concept that Canada is a White \textbf{Nation} then leave.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@rhaven50 ok so maybe I was wrong all white people aren't \textbf{racist}.  Thanks man..\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Is there any single \textbf{race} left apart from whites who is NOT \textbf{Racist} ?? 1st think then speak.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Madhav Sharma you're a \textbf{race} bater. Stop stereo typing whites.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Thanks give me a thumbs up:) I just speak from the heart. I'm tired of hearing the classic government mantra that  " Canada needs immigrants because we have an unsustainable population" when that is so not the case. What doesn't make sense is if Canada is the second biggest country in the world why are all the new arrivals concentrated specifically in those 3 big cities that i mentioned? I think there is a deliberate attempt to create social disorder,chaos and unhappiness, by forcing people to live in close proximity to people they have \textbf{nothing} in \textbf{common} with, and stigmatizing and even endangering those that are in disagreement with the status quo. You can't force people to live side by side with each other when their is \textbf{nothing} in \textbf{common} between them.\normalsize   & \cellcolor{green!27}Common, Nothing & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}4/132 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small greg oscar but don't you think that they like to assimilate but can't due to \textbf{racism}?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small India is a subcontinent there are many races within India, complexion does not dictate \textbf{race} and \textbf{ethnicity}. The gang rapers in New Delhi were dalit \textbf{race}, which is different from the guy's \textbf{race} in the video. Why don't you go educate yourself first.\normalsize   & \cellcolor{green!27}Ethnicity, Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}4/43 & \cellcolor{green!27}9.302 \\  \hline
  \cellcolor{green!5}\small ok i read it, seems one was a sharma which is high caste brahmin, another was a gupta which is baniya vaisya caste, and the two singhs likely rajput, but lived in Ravi Das Camp so they could be lower caste guys taking higher caste identies which is \textbf{common} among some of the lower caste guys in India. Since Ravi Dasias are usually chamar by caste.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small +Snow 123I am \textbf{Indian}. 'CASTE' is NOT \textbf{RACE}, FACT. At least not in the way that it is currently understood. 'Caste' is an INTERNAL division that may have CREATED unique genetic identities autochthonously, but these identities are ALL \textbf{INDIAN} IN ORIGIN. We now know this due to MODERN GENETICS AND ARCHAEOGENETIC/PALEOGENETIC RESEARCH.\normalsize   & \cellcolor{green!27}Indian, Race & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/53 & \cellcolor{green!27}5.66 \\  \hline
  \cellcolor{green!5}\small You sure are stupid if one video changes your view on a whole \textbf{nation} and race\normalsize   & \cellcolor{green!5}Nation, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small rhaven50 Yet White people do this all the time generalising \textbf{Black} people. Welcome to the club, everyone gets a turn.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small good. we dont like u \textbf{indian} fake asses\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small +No NameThe \textbf{nation} of India has witnessed even more violent and horrific rapes against women and children since that Delhi 2012 gangrape.  The wicked games have only begun!\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small SHEKHAR MALIK BROWN people should not read too much into it. We love \textbf{ethnic} people.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Yes, because one raging \textbf{lunatic} defines a country's identity as well as that of a whole \textbf{race}. I'm starting to think you are as \textbf{dumb} as the guy in the video.\normalsize   & \cellcolor{green!27}Dumb, Lunatic, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small J M clogged ? \textbf{Indian} population in usa is less then 1.2 \normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small The caste system is so archaic and primitive. I wouldn't paint that broad of a brush..I've seen a lot of \textbf{racism} by Indians in America towards \textbf{black} people (dark skin) and others. et cetera....\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small There are morons among white. There are morons among Indians. If you think that everyone that is in your \textbf{race} is flawless. Your an idiot. Accept people and move on and ignore the fuckfaces from each \textbf{race} that show their face.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small It shouldn't...this guy is in the minority in Canada. You would be foolish to base your opinion on Canada and white people on this one man. That said sure there is many like him in Canada but true of anywhere you go. I get along extremely well with non whites but I have been spat at by blacks for \textbf{nothing} more then being white. Do I judge every \textbf{black} person on the person who spat at me...hell no!!\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small By the way India are fake \textbf{racist} and USA Canada is real \textbf{racist} ist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small india is \textbf{racist} but bharat or Hindustan is not racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Racism!? In the, CURRENT YEAR!?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small racism is only used to shut whites up. stop them from speaking there mind. other colours get away with it but whites don't. fecking far left fault\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Agreed. Here in America. Not that many people are educated to tell the difference between Muslims, Hindus, and Sikhs. They can't tell the difference between an Arab and a South Asian. America is one of the countries that has the worst \textbf{racism} and one of the worst religious intolerance.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small From a white man's perception they all might be of different religions but are of the same kind. Who goes to West for searching jobs. Though Indians have given some of the nicest products to West by working hard. But still doesn't satisfy the concept of land dominance. In fact there is an \textbf{old} say that your soil your rules but in my soil my rules.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small yoyomaIf America was for Christians then 1000 of Atheist would've given death sentence who are Not even \textbf{Indian} or middle eastern. They are the same white people. BTW If you talk about Real America not the Fake one then it is Originally for Natives who have now become 2nd Class citizen in their own land.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Isn't Manitoba the most \textbf{racist} province?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small free thinkerare you from Texas, where steers and queers come from. Is it your fantasy that Alberta is like Texas.. wishful thinking on your part? \textbf{dumb} ass fuk!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small John Harvey Gutierrez He's correct I'm Canadian. Alberta is the Texas of Canada. Oil rigs cow ranches and \textbf{racist} belligerent trash behaviour.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small O O F You are a very good liar Alberta has a reputation across the country for \textbf{racism}. Lol\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small +O O F you just have had the distasteful pleasure of a \textbf{racist} calling you a lier! Amazing how some individuals are so free with their an opinion no matter how incorrect they are!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Mel Colp dont care go back \textbf{racist} people. Stay home\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small +Memphis DBz I am certain that I Dont need to know anything about you and the welfare that you collect each month. Feel free not to reply to me,as your replying to a individual many steps above you moraly, fincially, and intelligent on any scale that you can comphrend above your obviously \textbf{racist} little mind. Crawl back under whatever rock that you come from and feel free to troll somewhere elsewhere! All of the best of wishes to you and may pity and charity support you and your life!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Saskatchewan is the most \textbf{racist} province in Canada\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small The RCMP are yes, the most \textbf{racist} in Manitoba, Canada.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small the top 3 most \textbf{racist} provinces (per capita) of Canada are the prairies, Manitoba being 1 (especially towards the natives), not saying that the other ones don't have their share of \textbf{racist} fucks.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small He has a BC license plate you \textbf{dumb} fuck. Also, the dumbest , most ignorant and \textbf{racist} Canadians live in mainland BC.\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Yup I grew up in Calgary and a lot of my friends were Punjab. There are a lot of east Indians in Calgary and I've never witnessed any \textbf{racism} towards them. I live in Ontario now and can tell you \textbf{racism} isn't any different out east. Canadians as a whole are pretty accepting, which is why our country is such a melting pot. Every village has its idiot though.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small You're right there's lots of \textbf{racism} in Alberta. Since I've arrived in Alberta 12 years ago, as a white east European man I was racially discriminated at work mostly by people from Asia, Vietnamese, East Indians, Pakistani.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Ellington Dart Muslim isn't a \textbf{race}, you \textbf{dumb} ass. It's a religion. Take ur meds, douche bag. And get off this channel, you \textbf{fat} \textbf{hillbilly}.\normalsize   & \cellcolor{green!5}Dumb, Fat, Hillbilly, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!5}4/25 & \cellcolor{green!5}16.0 \\  \hline
  \cellcolor{green!27}\small Here in San Antonio Texas the Hispanic population is the majority. But you assholes are very misinformed. We have no racial problems here. Non what so ever.BLM do a protest here with 10 people protesting. It lasted 30 minutes as all races ran them out.So to your Texas \textbf{racism} innuendo, not here pal!\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Maine is 98 white, but somehow never gets called a \textbf{racist} state. Texas, meanwhile, has a huuuuuge number of Mexicans, blacks and other non-whites, but is somehow branded as \textbf{racist}.I'm English, by the way.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Free Thinker  Just in case if you are 'really' paying attention.  Alberta does not have any license plate at the front.  Why?  I live there for over 35 years!  It looked like that Ford \textbf{R\textbf{ed}} Neck Truck had both front and back license plates which made it very likely to be a local BC license plate instead.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small choi maru wow a prime example of a Canadian thinking he is so perfect that his country doesn't have any problems, doesn't have \textbf{racism}, prostitution, gun violence, car crashes, road rage, everybody is nice and never says anything mean. You really need a reality check, \textbf{Racism} is everywhere, and the USA is one pint behind in the top 10 most \textbf{racist} countries. The U.K. Is 4th, Canada is 6th, the USA is 7th, and Australia is number 1. Australia is very \textbf{racist}.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/82 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small choi maru americans aren't \textbf{racist}, that's the media brainwashing your stupid ass..\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small mesedrew that's not actual facts tho lmao none of those countries are actually statistically the most \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small choi maru  May be you should go back where your name originate. No \textbf{Buck} choi here in Canada. Adios!\normalsize   & \cellcolor{green!27}Buck & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Yeah because there are way more \textbf{racist} people in Washington state than there are in BC, makes sense....\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small +semen demon It is the American people that are making those comments! Typically talking about Canada and something they \textbf{nothing} about. No surprise there!!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Listen you stupid, disgusting, cockroach foreigner. Think of the complete lack of logic behind what you just said. You live in a EUROPEAN society and have enjoyed all of the benefits of living in that society. You use EUROPEAN technology (Of which encompasses the large majority of technology.), you go, or have gone to EUROPEAN schools, if you work you work at a EUROPEAN company, etc (I could go on for months.). There's a reason you live "HERE" in one of OUR societies, and not the other way around. So who's the scum? Logic says it's your ungrateful, parasite, "LOSER" ass! No matter how poor my great grandparents (And the entire country.) were growing up they would NEVER leave their own culture to go bask in the success of someone else's. They had something that you don't. It's called "honor". You might not understand it because it's most likely not \textbf{common} from where-ever you come from but what more could someone expect from third world trash. Where were people like you then? They persevered through poverty, wars, etc., (IN THEIR OWN COUNTRY!) to build the country that your parasite ass now enjoys. You're a fucking LOSER! You have \textbf{NOTHING} to be proud of! As long as you're living "here", within "OUR CULTURE" and not your own, you have \textbf{zero} credibility. Go home!\normalsize   & \cellcolor{green!5}Common, Nothing, Zero & \cellcolor{green!5}Age - Youngsters, Social Class - Working class & \cellcolor{green!5}3/222 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small "Listen you stupid, disgusting, cockroach foreigner. You live in a EUROPEAN society and have enjoyed all of the benefits of living in that society. You use EUROPEAN technology (Of which encompasses the large majority of technology.), you go, or have gone to EUROPEAN schools, if you work you work at a EUROPEAN company, etc (I could go on for months.). There's a reason you live "HERE" in one of OUR societies, and not the other way around. No matter how poor my great grandparents (And the entire country.) were growing up they would NEVER leave their own culture to go bask in the success of someone else's. They had something that you don't. It's called "honor". You might not understand it because it's most likely not \textbf{common} from where-ever you come from but what more could someone expect from third world trash. They persevered through poverty, wars, etc., (IN THEIR OWN COUNTRY!) to build the country that your parasite ass now enjoys. Where were people like you then? You're a fucking LOSER! You have \textbf{NOTHING} to be proud of! As long as you're living "here", within "OUR CULTURE" and not your own, you have \textbf{zero} credibility. Go home!"\normalsize   & \cellcolor{green!27}Common, Nothing, Zero & \cellcolor{green!27}Age - Youngsters, Social Class - Working class & \cellcolor{green!27}3/198 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small why is it a big deal that its 2016? are you serious? the caption for this video is written to suggest that any and all forms of \textbf{racism} are long gone and now everybody look, omg someones being \textbf{racist} QUICK VIRAL THIS VIDEO NOW!!111!!1!!1!!1!!!!!!!!111!!0101010101010101010101I live in England, \textbf{racism} is part of our life.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/54 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Racism is a protective thing. You SHOULD defend the places you've conquered or lived at for hundreds of years.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small But YOU haven't lived here for hundreds of years. Why in the fuck do people always bring that shit up? Always crying and whining because the white man took your land. That was 400 fucking years ago!! Get over it! We shop at the same stores, have our kids in the same schools, get help from the same \textbf{doctors}...why in the fuck should you be treated any different than me? Because I cut down a couple of trees 400 years ago? And now I owe you? I don't owe you shit.\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small eugh thankfully he will be reviled like the garbage he is. also lol at I was born in Canada - \textbf{dumb} fucker forgot what country he lived in. most multicultural \textbf{nation} on earth.\normalsize   & \cellcolor{green!27}Dumb, Nation & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small What you drive a lil \textbf{beta male} car?\normalsize   & \cellcolor{green!5}Beta male & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small A shitty \textbf{old} pickup truck too. With cheap rims\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small That is a \textbf{racist} comment. I bet you are a chronic masturbator.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small John Cullen An \textbf{immigrant} is an \textbf{immigrant} is an \textbf{immigrant} even after 9 generations. So you are an \textbf{immigrant} with Canadian citizenship.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}4/22 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small you're an \textbf{immigrant} too, mr smith\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Joe Massino sure they matter. the men you talk about fought the germans in europe, japanese in asia, and north koreans in korea -- that has \textbf{nothing} to do with the fact that this country was built by immigrants.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Kronstadt Sailor I'd say it was because of racial differences. \textbf{Nothing} to do with iq. Iq is probably a white mans invention come to think of it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@No Name \textbf{nobody} knows that for sure.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small themanager1980 is the immigrant\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Tej Pal Singh I only ask because I'm 5th generation of this family and let me tell me you that a landed \textbf{immigrant} who comes here from Scotland for instance or anywhere else in the UK today, would be considered more Canadian than me! Lol its just so frustrating that's its funny I have to laugh ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ but it doesn't really bother me anymore it's just the way it is I guess\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small themanager1980 aboriginals don't like \textbf{racism} we don't tolerate with that bs\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small +Asap Rocky are you serious?? some of the most \textbf{racist} people that I met here in Canada are aboriginal first \textbf{nation} people. its obvious that you are not one of these people.\normalsize   & \cellcolor{green!27}Nation, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small +Patrick McPepeski KANATA a native \textbf{indian} word meaning village before whites came and changed the name from theÂ K andÂ T to aÂ C and D.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small +kronstadt Sailor whites wouldn't have any technology hadn't whites appropriated IndiAs knowledge and education starting with the invention of language you are using and then the numbers and number \textbf{zero}Â  used for a binaryÂ  which that internet computer Â you are using. name me the 97 inventions without any Indians rudimentary which whites appropriated this I got to read.i shit you not you cantÂ  fkg type a 97 list of inventions.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small +rhaven50 education,arithmetic,science,calculus.decimal system,geometry,trigonometry,numbers,number \textbf{zero},first university in the entire world,astronomy,astrology,laws of gravity,revolution of earth,language,linguistics,grammar,literature was all IndiA Indians achievements and inventions.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small +danzig159 you whites wouldn't be around for long that's a guaranteedÂ  you are only under 1third of the global population and wouldn't be able to defendÂ Â  yourselves. even todayÂ  your \textbf{race} is wanted for death everywhere.Â  Indians invented surgery and medicine most whites would be finished hadn't your people been taught by IndiA for medicine and surgery which are indiA indians invention.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small +Brenda skywatchherb quit talking about toilets and plumbing whites did not invent those inventions., those are Indians inventions ancient plumbing drainage and ancient toilets. google ancient \textbf{indian} toiletsÂ wh14 sem1 ancient india ogm.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small +Sheila Feng decimal system was invented in indiA (100bce),\textbf{indian} Vedic arithmetic was invented by Indians.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Without the land, Canada is just a concept that a bunch of people have agreed to. \textbf{Nothing} more, \textbf{nothing} less. Being born here doesn't give anyone a special status. Unless you have such low self-esteem that you need to wear it as a badge and parade it. Everyone is equal.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small danzig159 you shut the fuck up too, my grandpa and many like him who are First \textbf{Nation} \textbf{Indian} fought for this country too. For a country that treated them like shit. So if any one wants to talk shit about this country and any one then let them. Fuck they've earned it for the rest of us, fucking assholes\normalsize   & \cellcolor{green!27}Indian, Nation & \cellcolor{green!27}Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small themanager1980 if your family has been here a few generations I think you can safely say your canadian. How long with the everyone's an \textbf{immigrant} in Canada argument still hold water ? Another hundred , 2 hundred years, the real immigrants are the ones who most recently migrated . I'm a  2nd generation \textbf{immigrant} and more Canadian than my original background\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small Actually the natives immigrated here over the bearing straight land bridge from Russia in the last ice \textbf{age} over 10000 years ago\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small themanager1980, we are all aboriginal to planet Earth. I did not choose where I was born. I did not choose the social politics of the retarded times. Yet your comment states that I am born a stranger to my own planet. Your comment states I am to blame for the past and I do not have a place to call home. Your comment stinks of self righteous prejudice towards others, based on genetics. If I believed in the debunked taxonomy for \textbf{race}, I would say your sanctimonious attitude is a prime example of you feeling superior to people, based on their bloodline and it has affected your judgement.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small My grandparents on one side and great grandparents on the other were immigrants. I'm a native born Canadian and not an \textbf{immigrant}. If you want to think of yourselves as immigrants...go for it...count me out.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small That's where your wrong.... Meaning of \textbf{immigrant} is a person who lift a country to go to another country. Meaning of country... A \textbf{nation} with a government. So the first people that came here were pioneers not immigrants. So calling people that are born here an  \textbf{Immigrant} is false.\normalsize   & \cellcolor{green!5}Immigrant, Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Patrick McPepeski You fucking stupid...creating a country with a \textbf{g\textbf{ay}} name like CanadÃ¡ doesnt supress the thousands and thousands of years of aborÃ­ginals being on this land way way before white people..\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small No.  White people conquer Canada ... stupid .... we came ( french english and spanish for the South of America ) with our army. And we take the land by our superior intellect and tech!:)) all the rest are \textbf{immigrant}!!! Sorry to teach you the real fact...\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Your'e not an \textbf{immigrant} if your'e born in Canada with a citizenship.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@rhaven50 idiot  i am \textbf{indian} \textbf{ethnic} you are fuckning britsh\normalsize   & \cellcolor{green!5}Ethnic, Indian & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Crazy racist=/=trump\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small WTF does this have to do with trump, you troglodyte? Are you suggesting that \textbf{racism} wasn't around before trump? What's next? 1950s democratic KKK was a direct result of Trump? LOL \textbf{dumb} Canadians.\normalsize   & \cellcolor{green!5}Dumb, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small +Ex-Muslim Libertarian Atheist It is actually a \textbf{dumb} assed american that made the comment! Suffering from the same stupidity that affects you!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Mel Colp Why do Canadians hate Americans so much? It's like the little brother who's always jealous of his older brother who is twice as hardworking and richer.And btw, the same Americans who voted Obama twice, were the same people who voted for trump. Go and take a look at the statistics. \textbf{Racism} had \textbf{nothing} to do with the election outcome. People are just sick and tired of constantly being shamed by the puritanical left and their politically correct brigade.\normalsize   & \cellcolor{green!5}Nothing, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small Racism existed before Trump was born stfu!!\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Trump has encouraged these closet \textbf{racist} to come out through out the world from the US all the way to Australia\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Since the economy was already on the up swing before he left office just 16 months ago, it's a stretch to think Trump is solely the reason for- among other things- the record low in unemployment among minorities. Trump would like to think it was all him, but he had help. As for his racism: even Karl Rove on FOX News denounced Trump for declaring there was moral equivalency between protestors and those \textbf{Nazi} marchers in Charlottesville last year.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Why blame trump? Maybe if people lived around these \textbf{Indian}'s they would understand what a lazy,useless,\textbf{racist} and bullies they really are. They are tough when they are in groups and head down when alone. Don't like Canada or USA go back to \textbf{Indian} \textbf{nobody} cares for you hear.\normalsize   & \cellcolor{green!5}Indian, Nobody, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/48 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small "Go back to \textbf{Indian}? \textbf{Nobody} cares for you hear?" Sometimes ironic intent can be hard to detect online, but, for the record, you are trying to make fun of ignorant racists, right?\normalsize   & \cellcolor{green!27}Indian, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Dorothy krupa no , we have just had our backs pushed up against the wall and were simply sick of the liberals and their sh policy being shoved down our throuts. Push a man to far and this is what happens. Scumbag \textbf{libtard}.\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Book Snake I'm actually one of their "own" but they still stare at me because I'm good-looking or I'm one of those Aryans whose ancestors invaded the \textbf{Indian} subcontinent thousands of years ago. Even Pakistanis and Bangladeshis stare at me. Year by year, month by month I'm really getting convinced that my forefathers ruled these people of the \textbf{Indian} subcontinent. Even their "wealthy" people don't stop staring at me haha. It's one thing if you're a wealthy or a known person in this world and people are staring at you\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/90 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small +d campbell if it were not for the white man! all these ignorant and uneducated fools try to quote who settled this great country of Canada.. none of them know the real history of Canada. Upper and Lower Canada is a part they  know \textbf{nothing} about. The White English and White French made Canada!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Racist people never know the difference\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@Samar's Then another \textbf{racist} joins the forum\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Witz Not to defend this \textbf{racist} A-HOLE, but how do YOU know that the victim is \textbf{INDIAN} and not Pakistani???\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Well actually Pakistan was not a \textbf{nation} itself firstly. In 1947 Pakistan as a \textbf{nation} was formed \& the name "PAKISTAN" was proposed \& called for the first time. Yes Pakistan and other border countries were part of India.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Indian and Pakistanis are the same people pakistan use to be the northern region of \textbf{indian} before a terrible war has begun because of religious differences\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small k z a SHIT turns brown when exposed to sun, we are naturally brown , then it's makes the people with white skin brown when exposed to sun, everytime you get yourself a \textbf{tan} call yourself shitskin..... LolðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ Aryan wannabes....... Lol ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small They were the same group before. To me they are the same. Dirty \textbf{ethnic} group.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Hent Loosey they used to be Aryan \textbf{race}. Even today, Aryans exist in the \textbf{Indian} subcontinent\normalsize   & \cellcolor{green!5}Indian, Race & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Arden's hammer Genetically, Indians and Pakistanis are different races. Granted, millions of them are from the same racial stock but millions upon millions upon millions don't have anything in \textbf{common} at all\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Wendy Pekrul Wendy, millions of South Asians are your own bloodline. Don't talk like that about your own race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Hent Loosey, why don't go dig a hole yourself and I'm sure you'll find a lot of people who'd want to bury a low life jackass \textbf{racist} pig like you\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Speaking the truth about those third world hell holes isn't \textbf{racist}, you are just too stupid to comprehend. You low IQ inbred !! You don't dig a hole, then maybe you should crawl back to one of those hell holes, the one you came from. If you are from the civilized world then maybe you should go live with those roaches and mice in the third world, you belong to live with them. LOL. ha ha ha. â•­âˆ©â•®Take this with you along the way.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small himalyan mountain  100 right that's how these white people people have had \textbf{race} created, not many white can't even name more 2 grandfathers because they haven't got a clue who procreated them inbredheads\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Pakistan and India been one country before ,now they're just have different government and \textbf{nothing} else all things are same same\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small if is a mennonite yes, you are right!!! they don't learn \textbf{nothing} but the bible, and the bible have not a world map!!!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Mel Colp Whites did \textbf{nothing}, Iroquois And other tribes Ruled, the word Canada Is not Even white, you are just an uneducated Fool.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Tahirie Tahiry Pakistanis racially evolved along the Indus Bank and Himalayas while Indians racially evolved along the Gangetic plain. Millions of years of evolution has created 2 different races. So much so that even the darkest Pakistani doesn't look \textbf{Indian} at all. And worse of, religion has brutally compounded the racial difference between these 2 species\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Witz  fuck them Bastards  Ghandi was a \textbf{racist} Cooley...\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Witz If he knew all of that simple stuff he wouldn't be \textbf{dumb} enough to be a racist\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Northern Lights No it isn't. Pakistan is the land of Panjabis. Pakistan's \textbf{ethnicity} name is Panjabistan and it was called that before 1947. The UK just gave it it's Independece. Only india is a UK invention.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Mr \textbf{Crazy} Chicken Gaming ðŸ˜‚  what about watching your "lego" videos. It's really a pointless discussion Because you are delusional...No such name or place existed! It was all India India India   ðŸ˜Š   Take care\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Northern Lights Lol that's not even me. I'm just using this account. Go get a life you ugly \textbf{black} smelly \textbf{indian} shit face\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small \@get paid 01 Typical \textbf{racist} white school shooter lmao\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Hent Loosey Typical \textbf{racist} white, go shoot up a school lmao\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small lol true that's what i would've said to this \textbf{racist} idiot\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Your argument makes \textbf{zero} sense try again.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small +samyajyoti de    What's ironic is that European immigration laws make it virtually impossible for a white person from USA, Australia or Canada  to immigrate back to Europe. ....But if you're an undocumented non white person and can make it into any western European countries and claim fake \textbf{refugee} status, you can easily become a citizen. A Mexican illegally entering  Europe could get European citizenship easier than USA citizenship.\normalsize   & \cellcolor{green!27}Refugee & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small mike brink how about a 5th generation lebanese Canadian? My family's been here since 1897, went through heart breaking hardships and struggles but was able to successfully integrate with society quite nicely, worked very hard, persevered and not only made it but were able to flourish and thrive in a country with beliefs, morals and values much the same as ours!  Contributed a great deal to our local community and Canada at large!  My family has produced \textbf{doctors}, lawyers/judges, cops, athletes, a few politicians, served and died in both world wars, Afghanistan and still serving .... how about me can I emigrate to Europe?\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/104 & \cellcolor{green!5}0.962 \\  \hline
  \cellcolor{green!27}\small mike brink I figured that your comment wasn't meant to be hateful or \textbf{racist}. I just get upset when people place other people in one big group according to their stereotypes. I guess what I'm trying to say is that of any people anywhere there are good people and there are bad people! I used my family as an example of what can happen when people are given a chance to flourish and grow with their newly adopted country! Like I said I am a 5th generation Lebanese Canadian. Although I'll never forget my roots I consider myself to be 100 Canadian and if worse ever came to worse I would gladly lay my life down to protect and defend this peace loving, responsible and welcoming \textbf{nation} that has given me and my family all that we ever wanted! what also really makes me down right angry are the people coming in from the middle east and Africa who just want a free ride! What's wrong with working hard and integrating with society the way that my family did? What pisses me off even more are the free loaders (economic migrants) who are taking advantage of the Syrian epidemic and "piggy backing" on them to try and come in to my country, undocumented as u said and immediately go on welfare and take advantage of anything and everything they can! These people are crippling my local economy and who are the ones getting screwed? That's right the hard working Canadian tax payer! are these are exactly the people who give the majority of these immigrants who just want to work hard and send their kids to school a very bad name and are making it very hard for them! Isn't that always the way though? The majority is always at the mercy of what the minority is doing!\normalsize   & \cellcolor{green!27}Nation, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/308 & \cellcolor{green!27}0.649 \\  \hline
  \cellcolor{green!5}\small +Patrick McPepeski shut up with your Europe bs europe isnt even a separate continent from AsiA by waters and is one giant land mass by tectonic plate if we get technical about it whites are not a ancient \textbf{race} and Indians are (pre indus valley civilization) so get the hell out of our lands and that place you call Europe is actually North west AsiA whites are not indigenous to anywhere. you cant even argue that so shut the hell up and quit using all of IndiAs inventions starting with language ,education and religion none of that belongs to whites!.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small +samyajyoti de I don't see what difference it would make.wherever you whites go you turn places into ShiTholE that's why you come to non white lands.why are whites using all technology as it wasn't your people who would have invented fk all hadn't you got IndiAs knowledge on education numbers,number \textbf{zero},arithmetic,calculus,geometry,trgonometry,decimalsystem,science,spacescience,commerc,eaccounts,documentation,language,linguistics,grammar,literature and surgery plastic surgery and I can go on and on and oN' how is itÂ  India got robbed of over 695 trillion GBO of wealth got its independence back 70 years ago and today is at 3rd place in economy yet whites who never got robbed can never even hold a fkg candle .face it you whites are \textbf{DUMB} cheaters thieves liars and INferioR' little fkstain assholes who every \textbf{race} knows has \textbf{nothing} to be proud of whatsoever.Â  you are actually subservient to using all of IndiAs achievementsÂ  yet your people could not make any inventions without the appropriation of our knowledge and rudimentary to making whatever it is even exist.\normalsize   & \cellcolor{green!27}Dumb, Nothing, Race, Zero & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/163 & \cellcolor{green!27}2.454 \\  \hline
  \cellcolor{green!5}\small Thio joe it's hard telling these \textbf{racist} to go back to Europe when their families have been in Canada for generations and that plus they pretty much built what we see is "civilized" Canada with all it large cities and what not. Yeah, they think they own it and any new arrivals can go back where they came from. It's a hard sell to these \textbf{racist}. They built Canada and think they own it.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small I was raped by sikh guy in Canada ... then he married his sikh girl ..ans both told me " go hang yourself your culture is nasty "  ... I'm. white Polish from Europe . I islolatee myself from people for 2 years .. they.donthe same to us. alot of thier parents teach the kids that they can just have white girl or guy for fun ... they same \textbf{racist} like we are .\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small Thio Joe, not sure what your point is here. Your talking about things that happened hundreds of years ago. You insult every one that is a Canadian. Sorry fuck stick, but being born here makes us Canadian, not \textbf{immigrant} or \textbf{refugee}. When you stunned fuck libtards figure that out, maybe we will get to a point where the federal government will stop trying to destroy our identity, our country and people. If this don't happen soon, there is going to be war, and you fuck stick libtards are going to be the among the first to go. Along with the imported garbage. The amount of guns in the hands of the people will make short work of of our joke of a military and the RCMP. The fuse is already to light, the people are about ready to rebel. Keep pushing and we will see who wins.\normalsize   & \cellcolor{green!5}Immigrant, Refugee & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/147 & \cellcolor{green!5}1.361 \\  \hline
  \cellcolor{green!27}\small Thio joe dude Europeans are ignorants, all they know is \textbf{alcohol}, \textbf{racism}, cannabis and fighting after they get drunk at party's. They don't even know about their own history ahahahaha. You must know that about Europeans, they are no educated, they don't have any respect for others, they are mean and most of them smells crap, sweat and \textbf{alcohol}. (just go see Belgium, France, Great Britain, Deutschland, Ireland, Scotland, Poland, Bulgaria, Romania and Portugal........)\normalsize   & \cellcolor{green!27}Racism, alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol, Ethnicity - General & \cellcolor{green!27}3/74 & \cellcolor{green!27}4.054 \\  \hline
  \cellcolor{green!5}\small How far would you like to go down this road? Should all Native Americans return to Asia as its widely believed that they crossed the bearing straight when it was frozen over thousands of years ago? Should we return it to the rightful owners, the birds and the bees? Get fucked you stupid little \textbf{snowflake} bitches.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small listen pale man the asians migrated and then evolved to the \textbf{race} known as natives however they did so on UNINHABITED LAND meaning no one was there,so it was a finders keepers situation not every single land was already inhabited by humans the majority had to have found uninhabited land to begin the races,which came as a result of climate.It was mostly the europeans that wanted to steal other ppls land.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small MACK D, dude you speak a lot of sense and I know you're NOT a \textbf{racist}, just saying what say you say it without malicious venom and sounds controlled and from the heart.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Thio joe Europeans arrive about 4, 5, 6, and 7 generations before this era. They would go back to \textbf{nothing}. In south america the same happened with the spaniards so your statement is stupid.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small no my technology is asian made not european no european values have brought me \textbf{nothing} but hypocrisy\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Salvdoran---you must be \textbf{black}.  You guys can never argue the truth.  Well we want you blacks back in your own Africa.  We are being pushed out of Africa,  so why in the FUCK do you aspect us to take you in.  You should see all your people drowning trying to make it to Europe.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small by saying blacks your assuming all which is a logical fallacy because you know this isn't the case some blacks are happy living in africa and wouldn't change that for the world whether it be because of jobs,family,culture,religion etc to \textbf{lump} all and say all want to go to europe is ridiculous and arrogant they're are much better continents that are better than europe.\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small ALIEN WARTHOG Thats why in Poland they don't accept no one, even if your white.\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@SAMOAN WARRIOR canadian was \textbf{racist} toward the indiginous \textbf{indian} tribes If ppl conquered that part of north america then what is wrong with arab colonising europe ? Cant have it one way dip shit.\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Ali Baba ðŸ˜£ heatbreaking story ....and i agree with you .They are \textbf{racist} specially indians and pakistanis toward white girls .think they can have \textbf{sex} with them and its not a problem...in uk they uncovered a HUGE ASIAN GROOMING GANG using underage girls ...Their all in prison now .....\normalsize   & \cellcolor{green!27}Racist, Sex & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small \@letserb your the fuktard People generally take their \textbf{NATIONALITY} FROM THE FATHER ! lol If your canadian then you shoukd be brown \textbf{indian}.So person with no brain function wheres your \textbf{fat} ugly dad from ðŸ˜…ðŸ˜„ðŸ˜ƒðŸ˜„ðŸ˜…ðŸ˜„ðŸ˜ƒðŸ˜„ðŸ˜…ðŸ˜„ðŸ˜ƒðŸ˜„ðŸ˜…ðŸ˜„ðŸ˜ƒðŸ˜„ðŸ˜…ðŸ˜„ðŸ˜ƒðŸ˜„Oh yeah and his \textbf{FAT} UGLY DAD TOO\normalsize   & \cellcolor{green!5}Fat, Indian, Nationality & \cellcolor{green!5}Ethnicity - Native-American, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}4/44 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Youtube CANADAS DARK SECRET ........is an appalling episode in canadas dark vicious past toward the native \textbf{indian} tribes.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Patrick McPepeski you stole resources from those countries  like India  pre British colonial rule  was a wealth  country India  made contributions in maths. Had resources  like Spices tea. If Asian countries  where so backwards  why trade with them. China invented Gunpowder and toliet paper  had the printing press  600 years before Europe. Look up Chinese and \textbf{Indian}  philosophy  poetry Art.  Without Asians  Chinese Indians  and the resources  they stole Western countries  would have  not  prospered\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small this means ALL Canadians are \textbf{racist}, cause they're white. I think fusion gets what I'm saying.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Ulices Miranda All whites=Racist \textbf{Racism} will not end until all whites are sent back to europe\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Racism will end when white people are all mass murdered\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Go to Ontario and not speak french. Then tell me how \textbf{racist} America is fuck wad.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small +Imjin Mi-Yun Is it not just amazing how you tend to bring that out in people, once you open your \textbf{racist}, ignorant and unintelligent mouth of yours! Its likely best that you remain in the third world country your originate from!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Ryan McDonald Our manufacturing base is gone, it's not going to magically reappear, why would it, the east/asia has hi-tech, we're a relic; they're going to f*ck us on their way out! They left us with these dumbed-down *sses everywhere. Rothschild planned Greater Israel over a hundred years ago. Nope, it's not looking good. "We'll turn the U.S into a bottle sucking welfare state and collapse it!" Israeli PM Benjamin Netanyahu...Â  We have \textbf{nothing} they need! Certainly \textbf{nothing} they want, like these fellas>  [LINK] \normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small nicer \textbf{racist}  in Canada more danger than  hard racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small Canadians are pretty nice as a rule with their please and thank yous and opening doors and so on. That said it is not a \textbf{black} and white thing. Canada has their \textbf{racist} ass holes too, Canadians can have their bad days too. Also Canadians don't like arrogance and rudeness and if you come across as such you will see another side of Canadians. Canadians as a rule think everyone are equal regardless of \textbf{race}, wealth, education, religion and when you think you are better by your actions, you will get push back. Canada is not perfect, Canada is not a utopia but Tayuya you may want to look at yourself and wonder if it is you and not Canadians and Canadians are just less tolerant of YOU!\normalsize   & \cellcolor{green!5}Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/128 & \cellcolor{green!5}2.344 \\  \hline
  \cellcolor{green!27}\small Aaron B \textbf{racism} is everywhere. Be at the right place at the right time. Unfortunately, non-whites have to heavily research areas and regions to evaluate whether they'll encounter \textbf{racism} or not. This is so sad\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small a \textbf{racist} is a \textbf{racist} regardless and the only good \textbf{racist} is a dead one\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Agree! everybody hate arrogance whether you are white or \textbf{y\textbf{e\textbf{llow}}} or \textbf{black} \textbf{nobody} superior than other because humans are make up of flesh two hands, two feet and head with brains that function to think and do sure some \textbf{race} claim they have more IQ but i believed is education that you require knowledge from plus how other \textbf{race} advance more than other, maybe pure luck or your ancestors have to source to violence to stole wealth, resources and lands even slave to advance their own civilization giving that opportunity every \textbf{race} can accomplish that.\normalsize   & \cellcolor{green!27}Black, Nobody, Race, Yellow & \cellcolor{green!27}Age - Youngsters, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}8/95 & \cellcolor{green!27}8.421 \\  \hline
  \cellcolor{green!5}\small you hit on spot many of them feel insecurity, but majority of time they like to yell at you if you are not white, during some kind of disagreement say at work and if they are wrong they never apologize to you that privilege thinking that they suppose to get special treatment, you have to earn it in order to get respect by treat other \textbf{race} same as your, if they are so many negative words from white toward other \textbf{race} then soon or later their words mean \textbf{nothing} and it does not even hurt you anymore because you just don't care, they are no more respect toward them and they loose\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/112 & \cellcolor{green!5}2.679 \\  \hline
  \cellcolor{green!27}\small What! That's the dumbest comment ever. There are no nice \textbf{racist} people. The United States is the best country in the world!There's \textbf{racism} all over the world...\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small What is nice \textbf{racist}? No offense but that's \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Racism is \textbf{racism} even in mild form\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Indian, Red & \cellcolor{red!27}121 & \cellcolor{red!27}121/51358& \cellcolor{red!27}0.24 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Nation, Alien, Immigrant, doctors, Nationality, Migrant, Refugee & \cellcolor{red!5}72 & \cellcolor{red!5}72/51358& \cellcolor{red!5}0.13999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Sex, Woman, Sexism, Sexual & \cellcolor{red!27}15 & \cellcolor{red!27}15/51358& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, White Trash, Trailer trash, Hillbilly & \cellcolor{red!5}15 & \cellcolor{red!5}15/51358& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Dumb, Mental, Midget, Spastic, Crazy, Freak, Limp, Weird, Lunatic, Disabled, Mongoloid, Blind & \cellcolor{red!27}54 & \cellcolor{red!27}54/51358& \cellcolor{red!27}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nobody, Nothing, Zero & \cellcolor{red!5}75 & \cellcolor{red!5}75/51358& \cellcolor{red!5}0.15 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racist, Racism, Race, Ethnic, Ethnicity & \cellcolor{red!27}504 & \cellcolor{red!27}504/51358& \cellcolor{red!27}0.98 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!5}Paki, Brownie & \cellcolor{red!5}2 & \cellcolor{red!5}2/51358& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}coloured, Black, Colored, Nigga, African, Buck & \cellcolor{red!27}106 & \cellcolor{red!27}106/51358& \cellcolor{red!27}0.21 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}13 & \cellcolor{red!5}13/51358& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Nazi, Red, Snowflake, Commie, Libtard & \cellcolor{red!27}20 & \cellcolor{red!27}20/51358& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}6 & \cellcolor{red!5}6/51358& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}6 & \cellcolor{red!27}6/51358& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Japanese}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}6 & \cellcolor{red!5}6/51358& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Ho & \cellcolor{red!27}2 & \cellcolor{red!27}2/51358& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Southern European}  & \cellcolor{red!5}PIGS & \cellcolor{red!5}1 & \cellcolor{red!5}1/51358& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}2 & \cellcolor{red!27}2/51358& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Destitute}  & \cellcolor{red!5}Bum & \cellcolor{red!5}1 & \cellcolor{red!5}1/51358& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - White}  & \cellcolor{red!27}White Trash, Trailer trash, Whitey & \cellcolor{red!27}3 & \cellcolor{red!27}3/51358& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Fat, Skinny, Lump & \cellcolor{red!5}17 & \cellcolor{red!5}17/51358& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay & \cellcolor{red!27}3 & \cellcolor{red!27}3/51358& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, Beta male & \cellcolor{red!5}4 & \cellcolor{red!5}4/51358& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Witch & \cellcolor{red!27}2 & \cellcolor{red!27}2/51358& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Italian}  & \cellcolor{red!5}Guinea & \cellcolor{red!5}1 & \cellcolor{red!5}1/51358& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Hispanic}  & \cellcolor{red!27}Brownie & \cellcolor{red!27}1 & \cellcolor{red!27}1/51358& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}2 & \cellcolor{red!5}2/51358& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - American}  & \cellcolor{red!27}Yank & \cellcolor{red!27}1 & \cellcolor{red!27}1/51358& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - British}  & \cellcolor{red!5}Tan & \cellcolor{red!5}1 & \cellcolor{red!5}1/51358& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}1 & \cellcolor{red!27}1/51358& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - Native-American;Nationality - General;Gender - General;Social Class - Working class;Physical Identity - Physical (and Mental) Impairments;Age - Youngsters;Ethnicity - General;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Ethnicity - Black;Age - Over 65s; Ideological and Political Identity - General;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Chinese;Nationality - Japanese;Gender - Female sexuality;Nationality - Southern European;Religious Identity - Muslim;Social Class - Destitute;Ethnicity - White;Physical Identity - Physical Features;Sexual Identity - General;Sexual Identity - Male homosexuality;Gender - Female age and physical appearance;Nationality - Italian;Nationality - Hispanic;Age - General;Nationality - American;Nationality - British;Behavioural Addiction - Alcohol;%.

\item The percentage of hate speech related words is 2.0581.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 1062/1990 occurences of hate speech related comments.\end{itemize}\end{document}