\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_92.json :}\newline \par\Large\textbf {Title: \large  Dumbest Blonde Ever }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Jeff: Lets talk about your options, Focus!!!Kelly: I'm listening too what your saying but I'm only hearing what I want to!!!Jeff:  That's just called being a \textbf{woman}!!ZING!!!!!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small She's so \textbf{dumb} it's not even funny its embarrassing and a shame that someone can be this \textbf{dumb} in America.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small If she was \textbf{dumb} she would have given wrong answer. She was smart enough to get help when she needed it and she won this question.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small She \textbf{dumb} as hell\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Is Land Rover a \textbf{Nation}?\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small She really is \textbf{dumb} asf, I tought title was misleading.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} seems like the perfect wife. Don't expect you kids to go to Harvard ofc but yeah it would be an easy life ;)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small " I'm listening but I hear what I want to"........" That's just called being a \textbf{woman}"Lol\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small That's called being a \textbf{woman},  oh  ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small what the hell?How \textbf{dumb} americans can be.... EuRoPe iS A cOuNtRy\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She's cute, \textbf{dumb}, and she can make kids giggle. Perfect wife right there if youre gonna aks me\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small My mom until she met my dad though Alaska was in the pacific ocean just because it was like that on the map. This \textbf{woman} makes her look like Einstein now\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Dumb is one thing, uneducated is something else. This young lady seems not to have had much of an education. This does not prove she's \textbf{dumb}. Geography is something she just doesn't know much about. Let's be fair. And what does this film show about education in the USA?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small Really fulfilling that stereotype of the \textbf{d\textbf{umb} blonde} American\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Not every blonde is \textbf{dumb}. I am the smartest one in class and I am blondeðŸ˜‚\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small And I'll bet if she was a brunette this wouldn't be on YouTube. By the way, this girl is not \textbf{dumb}, just unknowlegable when it comes to geography. The whole \textbf{d\textbf{umb} blonde} stereotype is very prejudiced and offensive, not to mention totally untrue according to scientific research ( google it!).\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/50 & \cellcolor{green!5}6.0 \\  \hline
  \cellcolor{green!27}\small What an idiot honestly who or what has the IQ of being this dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Literally even I don't know the answer to this. Am i fucking \textbf{dumb}? THE FUCK NOT! I'M A LITERAL GENIUS WITH AN IQ OF140!How fucking mature, America. Forcing ppl to answer fucking stupid, completely random and arbitrary geography questions that are literally useless to a person unless they were literally a geography teacher themself, then labeling them as "dumber than a fifth grader". HOW THE MOTHERFUCK IS LITERALLY KNOWING THE CAPITAL OF SOME RANDOM EUROPEAN COUNTRY, GOING TO FUCKING SAVE YOUR LIFE FROM DYING, OR LITERALLY MAKE YOU ANY MORE SUCCESSFUL IN LIFE?!?IT LITERALLY WILL NOT! NOT IN THE VERY LEAST BIT AT ALL! AGAIN, NOT UNLESS YOU LITERALLY ARE PLANNING TO BE AN ACTUAL GEOGRAPHY TEACHER YOURSELF! America doesn't seem to fucking understand the difference between being INTELLIGENT, and being WELL EDUCATED. While being well educated is very important TO SOME CERTAIN ASPECTS, we can all agree that geography of any county or continent is fucking quite literally completely useless aside from that profession i just mentioned. That subject should be completely abolished from standardized primary and secondary school. Leave in the actual useful fucking shit, like math, reading, and writing, where you use these skills LITERALLY EVERY SINGLE DAY OF YOUR BREATHING MOTHERFUCKING ADULT LIFE!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/210 & \cellcolor{green!5}0.476 \\  \hline
  \cellcolor{green!27}\small I remember watching this when I was like 7 and thinking I was \textbf{dumb} lol I mean I was right but it's justifiable\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small She maybe \textbf{dumb}, but she get the Dee\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small "that's just called being a \textbf{woman}"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Her Parents be likeDAD:Man What The F***Girl:Ohhh You just said a bad wor-Mom:YOU DONT F*** KNOW WHAT THE COUNTRIES ARE!!!NARRATOR:Now At This Moment She F******Knew That She Was \textbf{Dumb}...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Back when TV wasn't super PC pussified and you would still make a lighthearted sexist joke and everything is cool. Now you say, "That's just called being a \textbf{woman}" very funny joke at a perfect moment will trigger all the bitches in suits working in offices thinking they run the world.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small I read the title wrong I though it saidBlondest \textbf{dumb} everðŸ˜‚\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small correction \textbf{dumb} texan\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small This bitch only good for fucking and  \textbf{nothing} else\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Fake and gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/3 & \cellcolor{green!27}133.333 \\  \hline
  \cellcolor{green!5}\small I love how the kid just stands there thinking like "this bitch \textbf{dumb} af lmaoo"\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small She's so \textbf{dumb}, we all know that europe is a street in the town canada\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small He's an asshole for the \textbf{woman} remark. So, I guess being a jerk is a man thing!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small As a person with parents from European countries,im laughing at this.like bruh,she is so \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small â€˜hungary like hungry' NO tf that doesnt helphes stupid and ignoranti like the \textbf{woman} better- i dont even listen, i only listen to what i want to hear-thats called being a \textbf{woman}WHY DO AMERICANS ALLOW THIS ON NATIONAL TV\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small HungAry! Even the \textbf{old} man are can't speak\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I was feeling \textbf{dumb} and then i saw this...I lost more than half of my brain cells.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Not one can be that \textbf{dumb} this isn't real\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Well she's cute and hot but still she's dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dumb girls are good in bed\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small She sounds so \textbf{dumb} it goes around and sounds cute and endearing.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Thiz \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small (the lights are on but... there's \textbf{NOBODY} home.) DUH\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Doesn't matter had \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She is more \textbf{dumb} than a jar of picklers\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small ho lee sh*. you \textbf{dumb} bast**\normalsize   & \cellcolor{green!27}Dumb, Ho & \cellcolor{green!27}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Omg this is even dumber than the south caroline miss america 2007 woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" little sexist piece of shit\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small you could already see she was \textbf{dumb} do to that accent.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small What else could you expect from a \textbf{hillbilly}?\normalsize   & \cellcolor{green!27}Hillbilly & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Dumb, still cute ;)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small And she is \textbf{racist}. Well the reason is because she is rude to my country. She is like Hungary? That's a COUNTRY?  How should we respond to that like no it's France of course it's Hungary we just said the answer.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Connecting turkey to hungry; what's \textbf{dumb} about that? Perhaps those that call lack of exposure dumbness, may just need to admit themselves up for checking. Just saying; I mean I know that politics are dumbing down people.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small It is not a question, and yes, if you think that Europe is a country you are \textbf{dumb} as fuck.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Yeah no fucking way this is real, it's obviously staged. No one is that fucking \textbf{dumb} and would be constantly saying more and more \textbf{dumb} shit to prove that point.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The sad thing is that only, like, 5 people in the audience laughed when she said "I thought Europe was a country".The others are as \textbf{dumb} as her.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I'd still finger her tight \textbf{pussy} though.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Perfect \textbf{woman} :))\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small She's not \textbf{dumb} she is American\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Dumb \& Dumber , mock , yeah Ing , yeah , bird , yeah , yeah , yeah !\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small All know women are always dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Blonde have the highest average IQ. Higher than any other hair colour. But yeah, she's dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small It's Hungary so I guess everyone is \textbf{dumb} here even the presenter as well. it's \textbf{HUN} GA RY. NOT HUNGRY\normalsize   & \cellcolor{green!5}Dumb, Hun & \cellcolor{green!5}Nationality - German, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She probably believes the earth is flat as well. I honestly wouldn't be surprised if that were the case. She is \textbf{dumb} as a rock. Even Jake Paul is smarter than her. Lmao.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Pretty sure the \textbf{dumb} behaviour is an act on her end. She's a smart business \textbf{woman} and knows that this act will  give herself more exposure and therefore grant her more opportunities which it has.\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small I like \textbf{dumb} girl, because i can make funny everytime they speak.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Hungary has more than 1000 years \textbf{old} culture and  history. Usa  has less than 600 houndred years.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Average American Dumbass.The only people this video would surprise is other American's.    The rest of us outside your little bubble already know you're this \textbf{dumb}.    To us, none of this is shocking.   Please try to keep your \textbf{dumb} shit foreign policies out of other people's countries until you can learn to be a bit smarter, thanks.......poking Arab \textbf{terrorist} hornets nests and propping up neo nazi's in Ukraine is the level of \textbf{dumb} you should keep out of until you understand what you are doing.   You are responsible for a lot of innocent people dead.   Please keep your \textbf{dumb} asses locked away in your little bubble until you can learn to play nice with others. -  Lots of love, the rest of the world.\normalsize   & \cellcolor{green!27}Dumb, Terrorist & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!27}5/124 & \cellcolor{green!27}4.032 \\  \hline
  \cellcolor{green!5}\small ....or this \textbf{woman}  [LINK]  ....cast your vote in the search for the dumbest \textbf{woman} alive! The selected dumbest \textbf{woman} footage will receive a financial recompense generated out of the buzz of our world wide search, for THE WORLD'S DUMBEST \textbf{WOMAN}!P.s. I'd include men, but who's gonna buy that we men would not get wasted if we try any of this moves in the street, in the world?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/68 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Chalce Japanese,Korean,Mongolian,Persian,Chinese,Thai,Burmese,Filipino,Indonesian,Malaysian,Cambodian,Lao,Vietnamese,\textbf{Indian},Pakistani,Afghan,Turkish,Kazakh,Uzbek,Turkmen,Tajik and Russian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Girl ' GET some HELP' damn she really is dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small you can tell she's \textbf{dumb} by her voice at the start\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small 'I'm listening to what you're saying, but I only hear what I want to' - truer words never spoken by any \textbf{woman}...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small this is America's  brother  they don't even know what Europe is  she's thinking that Europe is country Turkey was a food hungary as hungry i feel sorry for Americans they are so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small I thought I was \textbf{dumb} for not knowing which country it was\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small How did someone that \textbf{dumb} get up to 10 thousand dollars\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Now i want see dumbest \textbf{nigga} ever hahah\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small U MAY BE \textbf{DUMB} GAL , BUT I WILL TAKE U FOR UR BEAUTY . AFTER ALL , WHO CARES FOR THE COMBINATION OF BRAINS AND BEAUTY IN A BLONDE \textbf{WOMAN} ? BOTH AT THE SAME TIME . NEVER HEARD OF IT .\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small If this \textbf{woman} is acting then she is actually very smart for making us believe that she is \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Nobody cares about shity country like hungary etc...gipsy country\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small SHE'S not \textbf{Dumb} cause \textbf{nobody} Knows Everything. IVE lived i. CALIFORNIA many Years and there are still cities ive never heard of\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small dumb bitch! Europe is a plant.USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA! USA!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2000 & \cellcolor{green!27}0.05 \\  \hline
  \cellcolor{green!5}\small That \textbf{woman} doesn't have brain cells.She has a plastic brain.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small You're picking some pretty \textbf{dumb} adults and smart 5th graders\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Huh i thought it was austria...I'm dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small This bitch \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small All blondes are \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Not sure she is \textbf{dumb}. There is not much here that shows how intelligent she might be.She is just extremely poorly educated in the field of geography.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I am Hungarian and please love this blond \textbf{woman} and dont mock her!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Oh my God I feel my brain cells dying off just listening to this chick\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small My brain is hurting for this \textbf{woman} like BiTCh WhAt ThE FuCk\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small find a single \textbf{woman}. she's a married \textbf{woman} who would probably kick your ass with those high heels she wears\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The comment section here sums up the milenial generation really, which I happen to be a part of, laughing at someone less educate then them behind their keyboards in a witty manner, never even applying to a TV quiz show.Fuck you all \textbf{snowflake} cocksuckers.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small she is a smart \textbf{woman}. just didn't remember which country it was. she's a singer/songwriter\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small She's a smart \textbf{woman} who simply didn't know what country it was. She's not so much a bitch as you are a fool for calling her one\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small wow this \textbf{woman} just hurt my feelings because i'm Hungarian xD\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small STOP WITH THE \textbf{D\textbf{UMB} BLONDE} STERYOTYPE IT ISNT TRUE\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Is her mouth a country which \textbf{black} cocks live in\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small American Dad had an extreme \textbf{dumb} girl in one of the episodes wich is looking just like her and have almost the same voice lmaoI think its may be an easter egg :)If you want to see it by your own,  just watch the Episode with "Sydney Hoffmann" great Episode btw\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small I still dont think she's the dumbest considering how clueless i was when the \textbf{old} man said "Hungry"..I was actually asking myself the same question until i went to the comments sectionðŸ˜‚\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small "That's just called bein' a \textbf{woman}." Lol. That was the best answer. Nice Jeff.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small That dudes moustash is bigger than his entire brain lmao he has so much more things in \textbf{common} with the blonde girl\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@\textbf{black} style and nightmares His brain is still bigger than your genitals\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She is drugged to the gills. \textbf{Nobody} can be so illiterate/stupid on purpose. That is not bonafide dumbness. As for that zoned out comment ' I am listening to you but I only hear what I want.' D-uhhhh! Is this \textbf{woman} firing on all cylinders or is she born missing some revs in her hearing and brain department?Not funny,but sad if this was scripted on purpose.However if due to some circumstances she couldn't get an education, what is to stop her from picking up a book and learning something instead of being proud of the fact that she is bone ignorant , illiterate, clueless and a third grader knows more than her?\normalsize   & \cellcolor{green!27}Nobody, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/113 & \cellcolor{green!27}1.77 \\  \hline
  \cellcolor{green!5}\small Herman Justice.......Yes, the very stupid one.\normalsize   & \cellcolor{green!5}Herman & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I can't believe how \textbf{dumb} us natural-born(guessing she is,anyways) Americans sometimes are..WHAT THE F...?!?! AND THIS IS A CELEB,Kellie Pickler? More like Kellie Pickled..this \textbf{chick} is brined,alright.I have NO HOPE LEFT for America! Lmfao\normalsize   & \cellcolor{green!27}Chick, Dumb & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I feel \textbf{dumb} cause I didn't even know the answerðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Dumb American LoL\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I wouldn't call her \textbf{dumb} for not knowing the question given, but the France and Europe thing she said was so stupid. Her being blonde has \textbf{nothing} to do with it though.\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Hungary you ignorant \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}." ðŸ˜„ Awesome host\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Shadows 11 gosh.. You need to stop... You're way too sensitive. Even that girl is taking it in a good sport but you on the other hand who doesn't even knows her is being offended. What are you some sort of sjw or something ? If you keep on taking YouTube comments so  seriously you're gonna soon turn \textbf{crazy}. Seriously now I've started to respect her more than you ðŸ˜‚.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Shadows 11 ikr.... \textbf{Dumb} people often have to go through that. Too sad.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Shadows 11 yeah right. So I need to give respect to someone who is both \textbf{dumb} and ignorant and proud of it. It seems to be your hobby not mine.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Shubham You don't have to be rude about it tho..And what is wrong with respecting each other, just because she might not appear be as smart as you it doesn't mean she deserve to be spoken down to! That's a disgusting mentality to have, \textbf{nobody} deserves that. What you consider to be "proud" could actually be nerves or a multitude of other things. I'm sure people laughing at her and calling her \textbf{dumb} won't do much for herself esteem either.\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/80 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Shubham \textbf{Nobody} should be spoken down to like that, that too on national television..he has no right to embarrass her like that..its bullying!\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small It's Jeff Foxworthy you're opinion means nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Shadows 11 i was surfing on  YouTube and your comment happens to pop up so I replied fast. You're taking literal meaning of my words. What I meant by " she's born to be condescended" is that she's just a \textbf{dumb} girl and gonna make herleslf look bad and make people laugh at her wherever she goes and \textbf{nothing} can change it , some people are just born that way. I don't wish anything evil for her or I don't even hate her. I just don't respect her. May she do all the good what she can with her life. My point is that she's \textbf{dumb} and ignorant. The way she says " I'm listening to you but I only hear what I want" , how can you respect someone like that. OK now let's just end this conversation. Why to waste each other's time when we don't even know each other ?\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/153 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small I think she was just playing \textbf{dumb} to help make the kids look smart. She is very hot, a great singer and one hell of a dancer. i love her.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Hey \textbf{woman} what's 9 + 10 =21\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small "I only hear what I want to""That's just called being a \textbf{woman}" I died\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The good \textbf{old} days\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She may not be smart but god damn she's beautiful . its a rare combination in my country to have that type. Are all southerners and westerners from usa look like that.I'd love me a \textbf{dumb} beautiful \textbf{woman} like her. The reason  I like women who are \textbf{dumb} and dense like her is because they are similar to me. \textbf{Dumb} as a rock like me and dense asf\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/69 & \cellcolor{green!5}5.797 \\  \hline
  \cellcolor{green!27}\small I thought blonde was a pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Lieutenant Adams because blondes are \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I love how that kids just have that "who is this \textbf{woman}, why is she here?" Look on their faces.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small But \textbf{dumb} blonds are great lays! Mindless \textbf{sex} can be fun!\normalsize   & \cellcolor{green!5}Dumb, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Andrew Needs been doing some \textbf{eugenics} research have we?\normalsize   & \cellcolor{green!27}Eugenics & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small White people are crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small LEMME TELL YA GUYS...SHE'S NOT \textbf{DUMB}...SHE'S JUST UNEDUCATED \& UNAWARE...GO FIND A MAP, GIRL...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Pretty much every American represented in that one blonde \textbf{woman}, lol.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Kellie Pickler is a very smart \textbf{woman} !!  She is playing the part.    She is an amazing singer and her country albums are extremely good. She has her own couple of ðŸ“º t.v. shows.   She is very smart and beautiful and a great performer if you ever get to see her live !!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Kelly Pickler...... easy to talk into anal \textbf{sex}......trust me....everyone does it...lol\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Yeah, let's send the pretentious \textbf{d\textbf{umb} blonde} home with 25k while making sure the poor starve to death and the \textbf{immigrant} children regret they were ever born . Good job, America.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde, Immigrant & \cellcolor{green!27}Gender - Female intelligence, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/31 & \cellcolor{green!27}9.677 \\  \hline
  \cellcolor{green!5}\small He's pretty \textbf{dumb} too. Hungry? Lmao\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" I'm dead XD\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Typical bleach blond southern \textbf{bimbo}!\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I hope her career in porn panned out, because she's seriously too \textbf{dumb} to hold a real job...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small COUNTRY SINGER KELLIE PICKLER EVERYBODY,... WHO CHANGED HER ENTIRE FACE WITH PLASTIC SURGERY AFTER THIS SHOW AIRED!! BUT YA GOTTA LIKE HER BECAUSE... SHE'S HILARIOUSLY HONEST ABOUT JUST HOW \textbf{DUMB} SHE REALLY IS...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Well you cant blame her for being a \textbf{d\textbf{umb} blonde} because shes country\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Dumb or not But who are you to judge someone? Your stupid videos can ruin lives Bear in mind before making videos\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small My 6 year \textbf{old} cousin would get this right in a matter of seconds\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small This is a \textbf{woman} most of the men wants: beautiful+silly at the same time\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small How the fuck do you know what most  men want LMAO. These types of girls are only good for a one night stand other than that I don't think any guy would want a \textbf{dumb} ass for life.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small I want a silly \textbf{woman} not a dumbass woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small muhammad amin sarabi don't forget \textbf{dumb} and look a little like a man. Men would love that. PS you may like that but all men aren't the same. Some men love intelligence and not stupidity.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small She may be \textbf{dumb} but she is haaaaaaaaaaaaaat\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Host: Focus...Blonde: I am, im listening to what i only want toHost: Thats just called being a \textbf{woman}DEAD\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small "I'm \textbf{lesbian}.""I thought you were American."\normalsize   & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Sexual Identity - Female homosexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Nigga I haven't heard of Budapest ever in my life\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I am asian, i know \textbf{nothing} of that .Btw,hey european?can u guys guess where Komodo dragon live,without search on googleðŸ˜‰answer at comment\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small "I'm listening to what you're saying but only hearing what I want to"- "it's ok that's called being a \textbf{woman}" LOL\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Ashleything Question now is did the 5th grader get it right? How did this \textbf{woman} go on that episode? Where I am \{Australia} we had our version of this show hosted by Rove McManus.  ðŸ¤”ðŸ‘¨â€ðŸŽ“ðŸ‘¨â€ðŸ«ðŸŒðŸ“ºâ™€ï¸â‰ï¸\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small This doesn't make her \textbf{dumb}. Everyone is not cut up for everything and I'm sure there's something that she's good at. Not necessary for anyone to comment back what that may be particularly if it's something offensive or abusive.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small She is literally \textbf{dumb}. She didn't know that Europe was a continent, and she didn't think France was a country. Stop white knighting for her you sad, strange little man\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Asad Zee maybe not \textbf{dumb}, but extremely ignorant\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She may not be so \textbf{dumb} in other areas but let ace it Geography is normally Americans worst subject...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Omg me and her should be friends, I'm \textbf{dumb} and blonde! Btw I'm \textbf{dumb} because I'm blonde, that's what people say\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small She is not \textbf{dumb}, grow up kiddos ..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I thought she was pretty and then I heard her \textbf{dumb} voice\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small It's a cute Southern accent. Not all Southerners are \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Paul Bink Most people would do her, thats why stupid people exist :) Intelligence has \textbf{nothing} over beauty, when chosing \textbf{sexual} partner.\normalsize   & \cellcolor{green!27}Nothing, Sexual & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small not \textbf{dumb} but super ignorant.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Just because she's blonde doesnt mean she's \textbf{dumb}...thats technically what your saying, dont judge people just on how they look. Like you can do any better...think before you say\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small The host is \textbf{dumb} as well, it's Hungary not Hungry! Lol.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small "That's just called bein a \textbf{woman}"mega oof\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small "thats called being a \textbf{woman}" eww fucking sexist\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small The presenter is a fucking prick anyway. "That's called being a \textbf{woman}", boy bye\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small If in America people get 25 k dollars just for being that \textbf{dumb}, I'm coming there! Oh wait is America a hamburger or a planet? Cause I'm Hungary!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small I almost threw my phone out the window cuz of how \textbf{dumb} she was\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small It's not only blondes that are \textbf{dumb}...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Just proves......blondes are dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She just a  globalist that supports the EUROPEAN union which believes that \textbf{nation} states must be abolished. She ahead of her time that's all.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Can't call her \textbf{dumb} for not knowing the capital of a foreign country, most people from Europe and even from America don't know where the city of Sucre is neither...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small even she is \textbf{dumb} there is a lot a man will take her as their wife\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Dumb americans\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small She's so \textbf{dumb} it hurts.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small This girl is so \textbf{dumb} that she probably thinks that New York is in India.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small She was looking kind a \textbf{dumb} with her finger in the bum-all star S H R E KKKK\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Dumb as hell but I would still fuck the shit out of her.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small If you'd have said you'd have \textbf{sex} with jeff then you'd have gone home with \$10,000.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small We need to \textbf{thin} out the herd\normalsize   & \cellcolor{green!27}Thin & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small That's just called being a \textbf{woman}...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Ok I didn't know the answer either but how the hell she think they speaking french there like wtf how \textbf{dumb} can u get?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small dumb girl\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" ðŸ˜‚, Respekt wahmen plz !!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small since nearly \textbf{nobody} laughed when she said "I thought europe was a country " I assume that most of these people thought the same...\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Y'all know who this is, right? And she is absolutely pretty enough to be 'that stupid' lol her life is way better than any \textbf{dumb} troll commenting on here. She has her own tv show and albums\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small 0:47 Blonde \textbf{woman} is France a country?       Me Nah it's a planet\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Hey how could you use such a difficult  word continent to explain what France is. She will Need to ask somebody to explain that word to her. And that person is going to say" Duhhhh, you know, continent means "lots of apartments for sale, in one Building property, spelling c-o-n-d-o-m-i-n-i-u-m- I guess, whatever."And both of them are going to be even more confused and will go squinting at the screen, trying to read what you have written.ignorance is definitely not a thing of which to be proud, unless you want to be \textbf{dumb} on purpose.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small Hungry? It's pronounced Hungary \textbf{old} man\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Different countries have different  enunciations \textbf{old} \textbf{woman}. Also different accents.\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Rikard no you \textbf{dumb} subhuman trashmurican, HUNGRY IS ONE WORD HUNGARY IS ANOTHER HAHA ARE YOU FUCKING BLOND?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Oh \textbf{hun}.. You ain't that pretty to be that stupid...\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Hungry for her pussy\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I am hungry for your mother's \textbf{pussy} ( I am from Hungary, and this shit is triggering the fuck out of me)\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small glen judge I'm for her pussy\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small "I thought Europe was a country". Jesus fricking wept.Not helping the stereotype of some Americans being \textbf{dumb} as fuck.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I'm a blonde and I'm so not as \textbf{dumb} as her. Lmao\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small So her hair color makes her \textbf{dumb}?  Looks bleached to me.  Ignorance.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small If you think she's \textbf{dumb}, explain "England is my city"\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small This \textbf{dumb} probably heard once in her lifetime that her ancestors are from Europe, that's why she thought Europe could be a country.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small and of course it's a \textbf{woman} ...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small actually she is smartest its the idiots who think I don't know one thing so im \textbf{dumb} ya right r\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Aiden Campbell So what if she's \textbf{dumb}? Why do you care about her intelligence?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Me Me you are so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Cheeto Bag There are countless morons who even became leaders of nations. How can you dismiss personality just like that? So what if she's not the brightest bulb? Don't you have slightly dumber friends who you have a blast with?  So what if they are \textbf{dumb}? Are you going to just unreasonably hate a \textbf{dumb} person even if he or she has a good heart? Smh.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@Me Me Um, no. Both are of equal importance in this world. If you're this woman's \textbf{age} and you don't know what France is you may need to go back to fifth grade.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small I'm hungary for her pussy\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small No freaking way she's that \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small And i thought i was \textbf{dumb}...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small What the heck did that \textbf{woman} her entire life, dafuq?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Chris Vesy of course an \textbf{old} man would make a political reference out of no where...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I think she's acting even more \textbf{dumb} than she actually is tbh. How does she not know that France is a country and Europe isn't ffs\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Pretty and \textbf{dumb} perfect\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I bet you she's still focusing on her \textbf{sexual} life...But is too \textbf{dumb} to know the number of balls her mans got\normalsize   & \cellcolor{green!27}Dumb, Sexual & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small Who cares she \textbf{dumb} hot as hell\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small She's just a typical \textbf{dumb} \textbf{yank} who'd vote for Trump.\normalsize   & \cellcolor{green!27}Dumb, Yank & \cellcolor{green!27}Nationality - American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Lev K Turkey IS a country. It is a land mass that is surrounded by the \textbf{Black} and Mediterranean seas, and is part of both Europe and Asia.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small a fucking \textbf{bum} in poland can recognize PMU logo as Iranian while americans dont even know what is Iran or PMU\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small It's one of the better places to be in, what with Europe having acid attacks and other countries receiving multiple \textbf{terrorist} attacks from neighboring countries, the only thing we have to worry about are shootings. And no, America is not perfect and all amazing, it does have flaws, and honestly I do find a lot of the people here to be less intelligent and more gullible then most people.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small I am glad to be British and know my geography.  How can she be so \textbf{old} but so stupid?  Jesus wept.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small The rest of the world is full of \textbf{dumb} people too. Mostly \textbf{dumb} people hate America anyways.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small "Europeans are fucking stupid ROFL".I agree.   And the very dumbest of them ended up in North America and helped give birth to one of the dumbest nations on the face of this earth......people,  I give you the average American, \textbf{fat} , \textbf{dumb} and ugly.....comes complete with \textbf{dumb} phrases like "europeans are fucking stupid rofl"  whilst ignoring their own European bloodline.You're like the crumb that falls off a piece of shit and looks around calling everyone else a piece of shit.   You're that kind of flavour of \textbf{dumb}.    You have to be an American to be that kind of \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb, Fat & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}5/101 & \cellcolor{green!27}4.95 \\  \hline
  \cellcolor{green!5}\small Jj I'm actually ashamed to be an American now, so I'm declaring myself an \textbf{immigrant} now lol\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Well, you need to stop generalizing 330 million people in that case, that just makes you look like an asshole. Yeah we got some \textbf{dumb} people here but we have very intelligent ones too, just like every country. And compareed to the other ~200 countries it IS better to live here than most. And, having the strongest military in the world, i don't know where the fuck you live but if we get into a war with you, you're probably dead\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small 0:58 "that's just called being a \textbf{woman}"   WTF is that sexist nonsense?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small ojideagu right!! Like I kept pausing the video because i was literally amazed that somebody let alone an adult was this ignorant. Like if anything this should show that our schooling system should be better because \textbf{nobody} should be this embarrassing.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Haha well I'm British and here and Europe we are always making fun of Americans geography education. This video is literally the stereotype people imagine! Of course this is extreme. How does someone go through life being this \textbf{dumb}? How do you have a conversation with them?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small ojideagu Man, I don't even know lol like I'm very open to knowledge but this may be one of those people that bullshitted their way through school...I live in Northern United States and its literally a stereotype that southern education is worse than ours. So I have no clue. But ive never seen somebody so \textbf{dumb} in my life...like its one thing to not know the capital of a country but this is a catastrophe.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small What is truly \textbf{dumb} is the guy who uploaded this doesn't even know who she is. Now that's \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small the host would be skinned alive by feminists  if he make the same comment today about being a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small robert ingram 10/10 I would bang a \textbf{dumb} and dense and beautiful \textbf{chick} like her. I ain't lying because I like girls who are \textbf{dumb} and dense like me\normalsize   & \cellcolor{green!5}Chick, Dumb & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/29 & \cellcolor{green!5}10.345 \\  \hline
  \cellcolor{green!27}\small Hair colour has \textbf{nothing} to do with it, a PC education system that prioritises indoctrinating kids with PC vaules must shoulder the blame for such stupidity.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Hannah Cat nah jake paul doesn't have the skills of writing his own songs dude he pays someone to do that and he writes \textbf{dumb} things for \textbf{dumb} people\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small nvr mnd its a fucking city in america yall \textbf{dumb} fucks\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I bet she is married! \textbf{Dumb} guys love \textbf{dumb} Ladies\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small This remind me of Hey I'm \textbf{lesbian}I thought you were american\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Even if she wins she is still going home with nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small That was \textbf{dumb}, but she's so good natured you feel bad for saying it.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Only another \textbf{dumb} ass would write what you wrote.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Woman from video: what is IQ?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Blondie-I'm listening to what you're saying but I'm only hearing what I want toHost   - That's just called being a \textbf{woman} Me  -ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small That doesn't make you \textbf{dumb}, it just means you chose to watch a video from a channel your likely didn't subscribe to.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small metoo Also can can't believe this \textbf{dumb} shit is a concept for a game show\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small TÃ˜P BÃ˜P I cant talk to a \textbf{freak} that actually likes Logan Paul he was cool before he did all that \textbf{dumb} bullshit and now I cant wait to see his ass get beat by the boi ksi\normalsize   & \cellcolor{green!27}Dumb, Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I'm wondering if they hired this lady to act this \textbf{dumb}?  As a blond, I'm insulted that they are deliberately are laughing at her because she's a blond.  Want to bet they did this to up their ratings?  I'm a teacher and no one's this ignorant at her \textbf{age}.  :(   I'm done and never going to watch this program again.  By the way, I have an I.Q. of 139 on the Mensa scale.  This show is perpetuating the, "\textbf{d\textbf{umb} blonde}," myth and I hate that you did this.  Shame on your people.  Just for ratings and you're also teaching this boy to disrespect an adult.  Aren't you proud of yourselves?  :(   Songs\normalsize   & \cellcolor{green!5}Age, Dumb, Dumb blonde & \cellcolor{green!5}Age - General, Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/112 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Banana Earth Community well, theres absolutely no proof at all that I'm \textbf{dumb} and actually I won an award in my school for geography and maths\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small jennifer g bitch shut the fuck up. You are just as \textbf{dumb} as her and her show.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Ohhh your from Budapest, \textbf{nobody} cares xD\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small this lady can be making fun of you but not the other way around if you look at the times before the migration of tribes it is logical to think that HUNgary is a country which its folks ancestors were asimiliated \textbf{hun} turks who became christian so when she said turkey she was the one who making fun of those who make fun of her.\normalsize   & \cellcolor{green!5}Hun & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small And they wonder why we call muricans dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small She's not "that" \textbf{dumb}... I mean, she was smart enough to choose "copy" for that question! ;-)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Kelly Pickler may fit into the category "\textbf{d\textbf{umb} blonde}", but she's hot and she's made a lot of money since being on American Idol. I took geography in elementary school but didn't know hardly anything about it until I started watching world events and the wars in the Middle East\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small c1ue scroll 07 Nooo... MERCURY is a country. Earth is just called being a \textbf{woman} !\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Not all Americans are this dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Even I'm not that \textbf{dumb}! ðŸ˜‚\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small lmao\@ that called being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I disagree with you. She's hot as hell. If she weren't so \textbf{dumb} I'd probably bang her and I know I'm not the only one. Lol.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@Jozi X I really don't get it. Why should it be cute being \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I need this gullible \textbf{woman}. ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I'm not offended by all the \textbf{d\textbf{umb} blonde} jokes because I know I'm not \textbf{dumb}... and I also know that I'm not blonde.  -- Dolly Parton\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small Ek 01 the question is waay too simple and clearly her parents didnt raise her good because every 6yrs \textbf{old} knows the answer...if the question is about math or geography history and like biology then it's probably her fault\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small CybermanFordStrikesBack since 2012 but i still find the internet a \textbf{weird} ass place XD\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Now that she's an adult and obviously has traveled to Europe for her shows, then she's \textbf{old} enough to have learned some of this on the way. You can't hide in childhood and blame parents forever. Somewhere along the road of life you can rise above the stupidity and educate yourself.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Nah, she's just another ignorant American who knows \textbf{nothing} about the world.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small shes \textbf{dumb} as fuck but its got \textbf{nothing} to do with her being blonde\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small thats racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small She might be unsophisticated, but she's not \textbf{dumb}. She plays it up as part of her act.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Jesus, get this poor \textbf{woman} a helmet.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small No. No no no. This can't be real. I've worked in retail and in food service, and until you work in one of those areas, u will not understand the level of stupid that exists in this world. I've done both. The people we call customers seem like Einstein and Hawking combined, compared to this \textbf{woman}.  She can't be that stupid. This can't be real. Someone tell me this isn't real.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small The host is literally \textbf{dumb}. He said "hungry" instead of "Hungary".\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small No thats taylor swift you \textbf{dumb} ass.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small You know all Pornstars are \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Galaxy Diamond u weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}"Lol ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small How thick is she,typical Fkin \textbf{yank}.\normalsize   & \cellcolor{green!5}Yank & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small That's just called being a \textbf{woman} ðŸ¤£\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small they cut part of this out where he says "a \textbf{woman} doesn't want to hear a man's opinion, she just wants to here her HER opinion in a deeper voice".  who cut that out i wonder?  hmmm.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small The only \textbf{dumb} thing she said is her admit that she don't know is France is a country. The rest was ok and funny.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}" ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Nothing to say\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small She's \textbf{dumb}, but she's \$25,000 worth of \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small video : 7 years \textbf{old}comments: super new????\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small At first I thought she was funny and joking around a little.Then I realized she is that \textbf{Dumb}. Poor girl. Her family watching this at home must have been dying of embarrassment..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb} but she sure can be good in bed\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small She's \textbf{dumb} in a cute way tho\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Just an average \textbf{yankee} degenerate. \textbf{Nothing} new or of importance here.\normalsize   & \cellcolor{green!27}Nothing, Yankee & \cellcolor{green!27}Age - Youngsters, Nationality - American & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small He's \textbf{g\textbf{ay}} but if he wasn't this is funny\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small He's actually a homosexual\normalsize   & \cellcolor{green!27}Homosexual & \cellcolor{green!27}Sexual Identity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Not all Americans are stupid. This \textbf{woman} is representative of a lot of poorly educated Americans. Thank f*** I was educated in England.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Turkey not in Europea Dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small This is so racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Dang, its 2011, I'm not sure how he got away with the \textbf{woman} comment when that was the verge of sjws\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small 'I'm listening but I'm only hearing what I want to.' 'That's called being a \textbf{woman}.' lollllllllllll\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small this is why \textbf{eugenics} is a necessity...\normalsize   & \cellcolor{green!27}Eugenics & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small She's dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Jonni Darko hmm you are judging the entire USA over one \textbf{bimbo} who really is the ignorant one.\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Jordan Staal knowing how a hockey player is isn't being \textbf{dumb}, not even ignorant because sports aren't important...if you like it, good for you, but that isn't important; not a bit...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Pedro Ortiz, you are wrong. I know most South American countries, many \textbf{African} and Asian ones and all European countries.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small pyroth309 I'm American and I LOVE learning about other countries and geography. Especially france because I plan on moving there soon. Don't just assume that just because some \textbf{dumb} ass blonde doesn't know anything about europe other americans don't. I might know about other places because im not a blonde and im glad.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small "Not being aware of the outside world will not have a negative impact on her life"YES IT WILL. Because 9/11 is the consequence of the foreign policy of USA during the heighties, a foreign policy against wich you would protest If the american people clearly understood it's consequences.And next consequence is the rise of ISIS because most of american people couldn't identify the real purpose of the war in Irak. If they new this stupid war would destabilized it, they would avoided it. France understood it, France warned USA about this, and USA came back with "freedom fries". All the prediction of France diplomacy happened. France predicted the destablization of middle east and the rise of organisations like ISIS.Many US soldiers were killed because the \textbf{dumb} voters voted for the \textbf{dumb} president Bush.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/136 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small ew editss im trash honestly That's not me. That's NHL hockey player Jordan Staal. I have brown hair. You're pretty \textbf{dumb} for thinking I must be that \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small ÎžÎµÎ½Î¿Ï†ÏŽÎ½Ï„Î±Ï‚ Î£Î¿ÏÎ»Î·Ï‚ cool no one cares and that contributed \textbf{nothing} to the thread you dunce\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small That's just called being a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}5/6 & \cellcolor{green!5}83.333 \\  \hline
  \cellcolor{green!27}\small Hey, you know what? I'm Hungary and I would kill for some Turkey right now. Especially if it has that special \textbf{apple} Greece on top it would be great. You don't have Turkey? No(r)way! At least tell me you have some deserts with Sweden milk please. Den Mark will come pick me up and take me to play some chess. I think today I'll beat him with a Czech mate.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small karaka73 Nah i think he was just messing with that \textbf{woman} ;)\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Herta Schneider I'm southern...and it's hun-gary...no excuses for \textbf{dumb} and dumber.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small and for being a mysoginistic douchebag. "that's just called being a \textbf{woman}" fuck that\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Don't ever get \textbf{fat} young lady .you may not survive if you do\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small She's just ignorant, not necessarily \textbf{dumb}.. A great possibility tho!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The lonely Guy I think he was mostly just trying to \textbf{dumb} it down for her.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small It's hard to fathom how \textbf{dumb} Kelly Pickler is....\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Has this \textbf{bimbo} ever gone to school? And the host is no better. The country is pronounced 'hung-ga-ry', not 'hungry' ('hungary like I am hungry' Is he kidding!)What a stupid show...\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small All she probably knows about is dick, \textbf{alcohol} and the local football team I doubt she even left the state she lives in but it's ok we can get past that baby ðŸ˜Ž\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Blonde's are hot but tend to be \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Stupid... \textbf{dumb}.... bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small this girl is \textbf{dumb}, but it's not just because she is blond. I get that the reason behind blond jokes is that supposedly, adult women with blond hair only care about beauty and know \textbf{nothing} else. This is ridiculous,  because it makes people with naturally blond hair seem stupid if they don't meet the other criteria. please don't assume that a blond person is \textbf{dumb} before you actually have evidence, or that someone who is stupid because of their hair color. blond jokes are ridiculous and offensive. I get that some humor is offensive and that is why its funny, but please don't take it too far or make assumptions about blond women and blond people in general. Anyone, regardless of hair color can be intelligent or unintelligent. this stereotype is like \textbf{racism} for hair color, and it needs to stop. I've met so many smart people with blond hair, and plenty of less-gifted people with other hair colors. I don't understand how people still believe this horrible stereotype, and that it is still socially acceptable. please, change your view on blonds. not all of us are stupid, not all brunettes and redheads are smart.Thank you and have a great day\normalsize   & \cellcolor{green!27}Dumb, Nothing, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/202 & \cellcolor{green!27}1.98 \\  \hline
  \cellcolor{green!5}\small BLONDE( Check),THICK(Check)American.....( CHECK)...sigh..\textbf{BIMBO}...( DEFFO)?\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small the title is bigotry on your part and plz don't try associate people hair color with dumbness cause that is just as \textbf{racist} as people that downgrade people because of color of their skin and \textbf{race}.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small That is called being a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Are you blond?  Maybe you are trying to protect blonds.  Maybe you can identify with her!  Maybe you should get an education and learn how to open cans without using your teeth.  What the hell does \textbf{age} have to do with this?  Apparently a lot because you defend you ability to have a non-functioning brain and fall into the classification of a millennial.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Kids must be thinking, dayum this blonde bitch is \textbf{dumb} as fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small France is in Africa and South AmericaHa you think I'm being \textbf{dumb} didn't you\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small That's just called being a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Calling Blonde people \textbf{dumb} is \textbf{dumb}, duh.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small me too blondie i thought Europe was a country too when I was 8 yrs \textbf{old}.u r nit alone\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Of course, but that would ruin the gag. And the whole thing was an obvious setup, which most people who've watched this thing seem to have fallen for, the misogynists most of all. Ironically enough, the joke's on them \& their own cognitive shortcomings - not "The \textbf{Dumb} Blonde's."\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small You betcha. Most ppl are too \textbf{dumb} to figure out why - and I must admit, I wasn't sure myself until the final punchline.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small you guys know they are told to be dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She might be \textbf{dumb}, but I bet she could suck a boiled egg through a straw.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small She is literally the most perfect \textbf{woman} iv ever seen lol but seriously i love her hahahaha\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small So you assume all blondes are \textbf{dumb}? ..........woooow\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Me as soon as he asks the question "I swear if she says France... nah. She cannot be THAT \textbf{dumb}" then... "I thought Europe was a country!" Oh dear..\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Dumb as a stick...bless her heart\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small She's so \textbf{dumb} I would fill her with cum\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small did  she go to school at all? Because i sorta feel bad for the uneducated woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small These are the times when literally any party "rules" the US. Stop spewing that pseudointellectual \textbf{communist} bullshit. Parties are just deep state puppets in the US.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small That's just called being a \textbf{woman} lmao\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small I wish she would just shut up while she is ahead.  She's \textbf{dumb} as a box of rocks.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Its funny how everyone is making fun of that \textbf{chick} but \textbf{nobody} pays attention to the fact that the game show host said that women are stupid\normalsize   & \cellcolor{green!5}Chick, Nobody & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small RISHEBAN SUTHAKARAN Right Iï¸ honestly thought Budapest was like a South Asian or \textbf{Indian} location...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small She is playing \textbf{dumb} for the show.  Which means she might be smarter than you think.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small damn \textbf{hick}!\normalsize   & \cellcolor{green!27}Hick & \cellcolor{green!27}Ethnicity - White & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small You are so right!The kid was like: She is so \textbf{dumb}!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small OMG!! I am from Alabama, USA, and I knew right away, the correct answer was Hungary!! She is a \textbf{d\textbf{umb} blonde}!! LOL!! ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜ŽâœŒ\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small I like \textbf{dumb} pretty blondes, I just say I'll show you a magic trick ,and ask her to sit on my face and she will do it\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Oh my freaking God. This blonde \textbf{bimbo} gives us Americans a bad name. Well let's face it...at least she's pretty, so she won't suffer as much in life.\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small She is fucking dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small That's not \textbf{dumb}, that is pig-ignorant. She lives in a little world of her own...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Them blond roots have penetrated her skull and allowed all that peroxide to slide down into her brain and destroy it. She's only good as a \textbf{sex} toy now........maybe.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I found out the reason why Einstein died. He met this woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small i wonder how the fuck is she alive being so \textbf{dumb}? i mean she is so \textbf{dumb} that she would cut her neck to see if it hurts or if she dies\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Greg W - I hope so, because she has \textbf{nothing} else going for her.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Denny Passas a \textbf{woman} doesn't  need to be good looking to be good in bed.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Dan Spille that's why she's so \textbf{dumb}. She's gotten by on looks her whole life\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small +Jordan Martinka Jealous harpies, no doubt. Can't stand a \textbf{woman} whose attractive, so they have to tear them down.She may not be very bright, but she's beautiful and she seems plenty friendly. The first two are superficial. It's the last one that matters.Although I'd be lying if I claimed beauty didn't help.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small LOL!Dumbest idiots are the ones writing comments!That's Kellie Pickler [LINK] Singer, comedian, actress who made her career in Hollywood  playing "\textbf{dumb} southern belle".She's just playing her part and laughing at you, morons, all the way to the bank...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} is the type of person to put "Chicago is the universe" on the multiple choice section of an AP Test lol\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb}, she's just an average American with no grasp of the world outside.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Oh Americans are really \textbf{dumb} and stupid\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small No I can assure you, most Americans have a very 'relaxed' attitude to knowledge of other countries. Not sure if it is due to education or encouraged \textbf{nationalism}. Either way it's pretty \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb, Nationalism & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Americans on average are one of the most stupid people in the world I've met. Not all of them, but about 90 of them. They're too stupid to even realize they are not smart. Most think they are smart. When I lived in Chicago for 5 years one man was arguing that my country the Czech republic is the same thing as Czechoslovakia. And even me - a man from that country did not change the "special man's mind". We are living in dangerously ignorant times, where stupidity is adored and funny and intellligence is confusing and \textbf{crazy}.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small Interesting suggestion. Do you think she might just have \textbf{zero} geographic knowledge? It would've been interesting to see the rest of the program to confirm\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Gaper Maker actually it is discouraged  \textbf{nationalism} and public school indoctrination.  Kids come out complete idiots even after college. An ignorant population is easy to control\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Nah, she's way worse than average. People may be \textbf{dumb}, but the average American isn't THIS \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Oh please continue to speak of over generalizations like a \textbf{dumb} bitch. Now stfu!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Gaper Maker Nice \textbf{racism} there buddy\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Incorrect use of the word \textbf{racism}. Come back in a couple of years and try again.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Gaper Maker Jewish and Muslim people are not a specific \textbf{race}, yet a culture and it is called \textbf{racism} when discriminating against them. Therefore if you're discriminating an entire \textbf{nation} by stereotyping them as stupid, you are in fact being \textbf{racist}. Come back in a few years when you realize a few morons don't define a country - look at Stephen Hawking. American.\normalsize   & \cellcolor{green!27}Nation, Race, Racism, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}4/63 & \cellcolor{green!27}6.349 \\  \hline
  \cellcolor{green!5}\small Actually, referring negatively  toward a \textbf{nation} as a whole isn't \textbf{racist}. It's called having prejudices or being prejudicial.\@Gaper Maker if you have ever lived in multiple countries around the world then one will similarly deduce that the average person of whatever country are just as \textbf{dumb} about the world too. Now once again, STFU!\normalsize   & \cellcolor{green!5}Dumb, Nation, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/55 & \cellcolor{green!5}5.455 \\  \hline
  \cellcolor{green!27}\small Gaper Maker oh, she's \textbf{dumb} alright, quite representative of many women these days\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small 0:57 Man: "Focus."\textbf{Woman}: "I am. Like, I'm listening to what you're saying but I only hear what I want to."Man: "That's just called being a \textbf{woman}."Holy shit, this moment alone already makes this video worth watching! ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small The answer is hungry lol!! That guy is probably as \textbf{dumb} as that blonde \textbf{chick}!\normalsize   & \cellcolor{green!27}Chick, Dumb & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small She may be \textbf{dumb} in GK, but let that fool you.......She's a genius in SEXOLOGY\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small No no no...she pretends to be the dumbest blonde on earth ðŸ˜ these questions are hard I think but she is just one of those girls who thinks being \textbf{dumb} is cute. It gives her an identity\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small 2 seconds into this, I'm starting to feel like this was filmed in the \textbf{old} \textbf{old} times, where no one knew anything.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Is Kellie Pickler really this \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small The contestant and host are both \textbf{dumb} actually. It's HUNGARY not HUNGRY you damn idiot!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small It's not nice to call a person dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Did she pass school? Like wtf she's so \textbf{dumb} lol. She doesn't frickin know that France is a country and Europe isn't. Like OMG, what has become of this world.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small this \textbf{woman} for next british prime minister\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small While the \textbf{d\textbf{umb} blonde} is pretty stupid, Jeff Foxworthy isn't quite the smartest person in the room either. It's not pronounced like "hungry" there's an "a" in there. It's Hun-ga-ry. Great food and some of the prettiest women in Eastern Europe.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small This can't be real, she must be playing dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Shese a spunky lady tho as \textbf{dumb} as she is\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small marcuspliable69 Oh yeah, well maybe the \textbf{tart} in the video does.  Besides, what do you know about stuff an' all that? That's right - nuthin'!\normalsize   & \cellcolor{green!27}Tart & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Dumb is \textbf{dumb}. Unfortunately American population Falls in that category\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small americans are \textbf{dumb} just like their president\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}"ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Mate I'm a \textbf{woman} and I found it funny, people need to lighten up ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small he'd be lynched by \textbf{communist} leftists if that was said these days\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small another beautiful young girl destined for the porn or \textbf{hooker} industry ...\normalsize   & \cellcolor{green!27}Hooker & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small What a dumbass bimbo\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I never have believed in the "\textbf{d\textbf{umb} blonde}" stereotype until now\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small 0:37 how does this \textbf{woman} have \$10,000\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Joshua Goh Ikr?Maybe she did well at first then they took a break and she smoked crack and got \textbf{dumb}. ðŸ˜‚\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small It's because she's a \textbf{sex} slave that gets paid.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small It's because her name is Kelly Pickler and she's just a \textbf{d\textbf{umb} blonde} country ass \textbf{bimbo} from Ablemarle, NC\normalsize   & \cellcolor{green!27}Bimbo, Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Beauty but dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Why do people think that blonde makes you \textbf{dumb}. It's really annoying. I'm \textbf{blind} and I have a 3.8 GPA\normalsize   & \cellcolor{green!27}Blind, Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small How can you read these comments if you are \textbf{blind}?\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Interesting how my country has a history of thousands of years and yours has a few hundreds of years. Interesting how Hungarian people can answer questions about any country in the world, and  idiotic Americans have no idea about countries in Europe. Interesting how \textbf{fat} and stupid Americans are, and how smart Hungarians are. You know, I am much more intelligent than to give a whit about your comments because you are just idiots with lower IQ's than a snail's.Thank you for apologizing, it seems that there are a few normal people out there too\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small What a \textbf{dumb} bitch.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small A Trump tramp\normalsize   & \cellcolor{green!27}Tramp & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I \textbf{thot} europe was a country!\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small is france a country? xD she's so freaking dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She's so sweet but so dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small LightningVolt what no she doesn't she's a \textbf{d\textbf{umb} blonde} that \textbf{woman} is a porn star\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde, Woman & \cellcolor{green!27}Gender - Female intelligence, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/15 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Bruuu noooðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ Blonde: im listening to what youre saying but im only hearing what i want to.Host: thats juat called being a \textbf{woman}. ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small 'I'm listening to what you're saying but I only hear what I want to.' 'That's just called being a \textbf{woman}.' Lmao\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Again... \textbf{old} \textbf{old} videos on my recommendation.  Btw at least I'm happy she didn't say â€˜England is my city'\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I know she's \textbf{dumb} but just because she's blonde, doesn't mean it's the reason for her stupidness. I'm blonde and I have the top grade in my class\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Stop lying. I know for a fact you're \textbf{dumb} soley because you're blonde.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small The very, very \textbf{old} children's joke was: Austria got Hungary and fried Turkey in Greece.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small GTA guides for gamers Eh heh heh. First, that's a stereotype. You are an idiot if you think that blondes are \textbf{dumb}. As if there are not people with different hair colors that are \textbf{dumb}. Second, I just checked my hair color, NOPE, not blonde.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small GTA guides for gamers Researchers at Ohio State University examined 10,878 men and women to determine if hair color had anything to do with intelligence. Participants in the study were given the Armed Forces Qualification Test, an exam used by the Pentagon to determine intelligence of all recruits.The study showed blonde haired women have a higher mean IQ (103.2 points) than women with brown (102.7), \textbf{r\textbf{ed}} (101.2) or \textbf{black} hair (100.5). Blondes were also more likely to be classified as geniuses and less likely to have an extremely low IQ than women with other hair colors, the researchers found."This study provides compelling evidence that there shouldn't be any discrimination against blondes based on their intelligence," said author Jay Zagorsky, a scientist at Ohio State University.Among blonde haired men, the average mean IQ was 103.9, a fraction lower than the average of brown haired men (104.4) but above those with \textbf{r\textbf{ed}} locks (100.5) or \textbf{black} hair (100.1)\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}6/159 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small GTA guides for gamers not all blondes are this \textbf{dumb} okie .w.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small The \textbf{d\textbf{umb} blonde} sterotype is \textbf{racist} nonsense. Blonde Europeans are among the most intelligent, advanced people on earth. I made a video explaining why on my channel.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde, Racist & \cellcolor{green!27}Ethnicity - General, Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}9/27 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small GTA guides for gamers ok so all Americans are \textbf{obese} arrogant ignorant shits like you ok...\normalsize   & \cellcolor{green!5}Obese & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small GTA guides for gamers Actually. Back then men favoured blondes more than the other hair colors, but since they got rejected they started calling blondes \textbf{dumb} and stupid all because they couldn't get a date. And I remember reading that a test was done on all women of different hair colors(brown, blonde, \textbf{black} etc.) And blonde scored higher. So...\normalsize   & \cellcolor{green!27}Black, Dumb & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small The hair, \textbf{gender}, \textbf{nationality}, accent.....\normalsize   & \cellcolor{green!5}Gender, Nationality & \cellcolor{green!5}Gender - General, Nationality - General & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Jojo Chima lmao then all people with \textbf{black} hair are emo\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Jojo Chima Mmmmm...yes really. Where do you think the phrase "\textbf{d\textbf{umb} blonde}" came from? Blondes being \textbf{dumb}. And if youre telling me not a lot of blondes are \textbf{dumb}, then youre obviously one of them.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/35 & \cellcolor{green!5}11.429 \\  \hline
  \cellcolor{green!27}\small Jojo Chima and where do you think stereotypes come from? Facts. Like the only reason you would call an american \textbf{fat}, becuase most of them are, based on facts. Why would you call a redhead souless? Becuase people used to think redheads didnt have souls. Why would you call a blonde \textbf{dumb}? Becuase a lot of them are.\normalsize   & \cellcolor{green!27}Dumb, Fat & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Wow, you call me \textbf{dumb}, but you cant even use the right type of "your" thanks for proving my point dumbass!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small If you don't know something doesn't make you \textbf{dumb}. Honestly I think she is not\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small No, they knew women were emotional and extra religious and would only vote for things that make their husband a better man (it never works). Outlawing \textbf{alcohol} for exmple.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Yes, she was pretty \textbf{dumb}, but I don't think she tops this :  [LINK] \normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small It should be illegal to be this dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Lol americans are \textbf{dumb} in general\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small That \textbf{d\textbf{umb} blonde} has her own tv show. I think she is sexy as hell . Sexy lady !\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Rylee Kincaid  It is offensive, and the phrase "\textbf{d\textbf{umb} blonde}" wouldn't normally be acceptable in today's society, but this is YouTube where toilet-humour is perfectly in order.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Maybe only \textbf{bimbo} got accepted to this show.\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small ITS EARTH OMGI HAVE ONE QUESTION! r u round and thiccOr r u just flat and \textbf{thin}??\normalsize   & \cellcolor{green!27}Thin & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Are you \textbf{crazy}? Earth is a village in Space and Space is a country...god damn..educate yourself\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Tf you \textbf{dumb} idiot its a city\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small c1ue scroll 07 Yes, Gosh, you're so \textbf{dumb}! Look how this generation is, they don't even know that EARTH IS A COUNTRY.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small c1ue scroll 07 is the sun a \textbf{black} hole?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small c1ue scroll 07 oh my g are you that \textbf{dumb} to think Earth is a country (someone who can't take a joke)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small its an \textbf{ALIEN} , SHOOT IT!!!\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Tf dude, are you a kid or something? of course not Earth isn't a country it's a fucking planet. Not even British empire came close to earth with it's 24. how \textbf{dumb} can this generation be because of gaming, oh god.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Please stop with the America bashing. You really have no idea. Funny thing is, America isn't the United States, so who is the idiot now? I can't tell you how many Brits think Mexico is in South America (the majority)...even Jamie Oliver said it one of his 15 min. meal eps! I've also been asked (though just once), where the United States was (the young \textbf{woman} clearly didn't know). And last week when I answered, "I'm from Texas", the delivery man said, "Oh my boss is from Texas too...she's from Alabama". On the whole, the Brits I've met actually know a LOT less about world geography, history, religion, food, customs, etc, than the Americans I know back home.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small Artful \textbf{Dodger} well that's been ny experience the last 6 years.\normalsize   & \cellcolor{green!5}dodger & \cellcolor{green!5}Religious Identity - Jewish & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Tyrone Catkiller Kang Oh please, you ain't fucked \textbf{nothing} hotter.But go ahead, make up some shit like it's real.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small She's pretty alright.... Pretty \textbf{dumb}!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Their is no such thing as a \textbf{d\textbf{umb} blonde} you ignorant cunts\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Dumb bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Putting 'Blonde' in the title doesn't make a difference... but yeah she's dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Perfect \textbf{woman} to have \textbf{sex} with!!!!!! \textbf{Dumb} as shit, Hot as Hell and best in bed!!!\normalsize   & \cellcolor{green!5}Dumb, Sex, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/16 & \cellcolor{green!5}18.75 \\  \hline
  \cellcolor{green!27}\small BIMBO\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Thats just being \textbf{woman} lmao\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" best part\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small That's called being a \textbf{woman} XD XD\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I think she works hard at looking \textbf{dumb}!!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small The kid was just like, 'This \textbf{woman} got an IQ of an orange, I'm gonna come home rich!'\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'm blonde ðŸ˜‚But this is dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I thought I was dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Dumb, but with a fine ass. Just the way it should be.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Ho,y crap,\normalsize   & \cellcolor{green!5}Ho & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Does anyone in Hungary knows what's the capitol of North Carolina? Nope. How about Alabama? Nope. Maybe Texas? Maybe. Why would she know a shitty country saussage eaters Hungarian \textbf{fat} niggas? They are like 5 million people or so. Important for \textbf{nothing}.\normalsize   & \cellcolor{green!27}Fat, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small It doesn't matter if she's \textbf{dumb} !! If she cooks . cleans and swallows that's good enough!!! Oh and shaves her box ðŸ‘…ðŸ‘…ðŸ‘…ðŸ‘„ðŸ’‹ðŸ‘„ðŸ’‹\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small She is the perfect woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}"O H  S H I Tshe was roasted just like TURKEY\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small She \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Dumb AF\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small As a fellow hungarian I can tell you one thing. The phrase "HUNGARY" makes no sense in my language. Instead of saying HUNGARY we say: MagyarorszÃ¡g (Not to mention, we are not even HUNs, but magyar(s). One of the ancient scythian tribes. Magyar is our \textbf{nationality}, "orszÃ¡g" means: country. Hard to pronuce for non - natives. If you were hungarian you would say: Why do the World keep calling my country Hungary? This is MagyarorszÃ¡g, cos we are magyar(s).\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small I AM HUNGARIAN YOU STUPID BLONDE \textbf{THOT}!\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small She's so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small all blonds are dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Some pretty useful stuff actually. This bitch just \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I love \textbf{dumb} women. They're cute..Perfect combination is  d+b. DumbandBeautiful. I would marry if I found that combination.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small You sure ? \textbf{Dumb} people can say stuff like you knew him so it wasn't cheating or I only killed not murdered. B careful what you wish for\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small She's certainly not the dumbest \textbf{woman} out there.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small "I'm listening to what you're saying but I only hear what I want to""That's just called being a \textbf{woman}"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Bimbo\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Aren't all blondes \textbf{dumb}?Sorry sorry sorryI'll leave now\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small How sharp she looks and how \textbf{dumb} she is\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small indeed very dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Blondes are always stupid and \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small she is just playing \textbf{dumb}, she's an actress.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Josh Milik it may be stereo typing but it's certainly not \textbf{racist}, you'd have to be pretty silly to think blonde is a \textbf{race}.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Luke Curtis did I say blonde people were a \textbf{race}? No. However blonde hair is a European phenotype so when you talk shit about blondes you are targeting Europeans, especially Nords. It's like talking shit about people with afro's.. sure anyone can have curly hair, but when I think of an Afro, I think of someone of \textbf{African} decent..When you hear a blonde joke, who do you conjur up in your mind? I'm almost certain most people are envisioning a white person.It's ironic considering Northern Europeans are one of the highest IQ'd people on earth with countries at the top of the HDI.\normalsize   & \cellcolor{green!27}African, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small Josh Milik Developed countries have higher IQs, it's \textbf{nothing} to do with \textbf{race}. This occurs due to a superior education system and better healthcare in developed countries which allows people to increase their IQ through study and logical thinking practice.  You'll notice that the smartest countries always put the most emphasis on critical thinking in their curriculum...\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small Trash....bruh this is a game show men .. this \textbf{woman} is a famouse singer KELLIE PICKLER .. this game she is pretending to be dumb\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Josh Milo usually when people make a \textbf{d\textbf{umb} blonde} joke they don't mean any harm by it.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Josh Milo  Yup, \textbf{racist}. Also can't spell descent. You must be a brunette?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small He's probably hoping he finds a blonde that \textbf{dumb} when he's \textbf{old} enough to go on serious dates.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb}. Just uneducated.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small "I've heard of Turkey" total \textbf{dumb} ass till that. Then she got kinda cute with it\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small But wouldnt it so much better the title was "\textbf{Woman} who has spent her time on singing, struggling on her education."?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Kral Not the focus of the point. This video isnt discussimg her life, but just her intellect. She might be the sweetest kindest cinnamon roll on earth, but she's still \textbf{dumb} as a rock. Doesnt change her other traits, but also the others dont deny this defect.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Its not her fault that shes \textbf{dumb}, its the education system of the USA. We had to learn American history better than ours, we had to learn how much states does America have, but they dont give a shit about the rest of the world. They are just learning their history and they dont care about Europe or Asia or some other continent.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small she's just a girl who hasn't studied her geography well, not \textbf{dumb} ..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small All these \textbf{dumb} americans ðŸ˜‚ðŸ¤¦\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I understand that she is \textbf{dumb} but why does it matter that she is blonde\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small No your all wrong French is the country France is the \textbf{nation}. Has anyone ever taught you thisPlease notice my sarcasm\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Lol Sorry not born in the UK/US/CA/AU. Yes, I have problems with this language because I'm still learning it. Do you speak any other languages apart from English "dear friend"? I don't think so. Move to a different country, and let me see how bad you will speak their language after 3 years.I've been in the UK. A young lady at the reception asked me when did I born. I said november, and she started to count the months on her fingers ðŸ˜‚ðŸ˜‚ðŸ˜‚ Then she asked, "it's the 10th month, right?" I have no other questions smarties.Do you learn history? \textbf{Nothing}, apart from native Americans.Do you learn maths? No. You do a simple dead easy GCSE and live your life. Do you learn English? Yes you do GCSE, which is equal to B2. (That's what everyone does in Europe, which is a medium level...) Do you learn anything useful apart from these in High School? \textbf{Nothing}. And you wondering if someone calls you stupid because  you know \textbf{nothing} about life.In Central Europe we always make jokes about the English people's intelegency, and it's not groundless indeed :)Btw, your country is the ugliest European country, and has no culture. Don't understand why people wants to go there...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}3/211 & \cellcolor{green!5}1.422 \\  \hline
  \cellcolor{green!27}\small Milan the capital of an Eastern European country isn't really that important or \textbf{common} knowledge.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small muzgnasicianie is \textbf{racism} the only way you could reply to me after showing you how your country is not important and no one cares about it?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Abd Mzn What is \textbf{racist}? You are just ignorant. I could say the same that only Emirates and Egypt are important because only there is something worthy to see.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Milan I don't know why you make such crass judgements about English people. Sure, there are some \textbf{dumb} people in the world (especially this \textbf{woman}). However, your one bad interaction with the \textbf{woman} in the UK doesn't represent everybody.I don't know where you got the idea that we only learn about native americans. We learn about a variety of subjects such as medicine through time, the cold war, \textbf{nazi} germany etc etc.And sure, some maths is easy but for others it's harder. You can't say they're \textbf{dumb} because of that.Quite frankly, GCSE English is shit over here. It's all about memorizing a bunch of books without much application.In the end, it's alright if you don't know some stuff because everybody knows different things. What's not alright is trashing other people because they aren't as intelligent as you.\normalsize   & \cellcolor{green!5}Dumb, Nazi, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}5/141 & \cellcolor{green!5}3.546 \\  \hline
  \cellcolor{green!27}\small "The capital of Budapest" was a good  one for \textbf{Brexit} voters. No more Budapesteans in the UK.\normalsize   & \cellcolor{green!27}Brexit & \cellcolor{green!27}Nationality - European or anti-Europeans & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small People from uk are \textbf{dumb} (that's what the statistics say no offence)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Milan not all British people are \textbf{dumb}, sweetheart. Maybe use your brain and realise we have world renown universities in Oxfordshire and Cambridgeshire ?? Appalling attitude on your behalf but nonetheless I hope you realise your mistake and have a good day â˜ºï¸\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small My grandfather was in United States quite a few decades ago.He told the \textbf{woman} in post office he wanted to send a letter to Poland.Got asked which state it is in -.-\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Thank god ðŸ˜‡ It's still better to be unknown than having a brain like this \textbf{woman} has in the video :)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Why was this is in my recommendation?.............DOES YOUTUBE THINK I'M \textbf{DUMB}???Oh well...you're right YouTube. Well done\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Every american is like that, \textbf{nothing} special\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small qudlik that is false. I for one know many, many Americans who are very smart. Just look at Bill Gates. How did he create a empire if he was \textbf{dumb}. I take offense to that. You probably don't even know where Somalia is.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Master Chief, Sierra 117  1. I know where Somalia is.2. He is one of the smartest with 60 ( sr i dont know how many people live in USA) milions \textbf{dumb} peoples\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small qudlik every country has \textbf{dumb} people who thinks education is to earn not to gain knowledge...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small qudlik Haha nah I'm just pointing out how stupid you have to be to not only believe that a nation's entire population can be comprised of idiots, but to publicly confess to having such a ridiculous notion. You, sir, are as \textbf{dumb} as she is, but in a different, and much more cynical way.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small Every country has smart people and \textbf{dumb} people. You shouldn't assume that a whole country is \textbf{dumb} based on a few people you've met. It's pretty much \textbf{racism}.\normalsize   & \cellcolor{green!5}Dumb, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/28 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small You shouldn't be talking about another person's intelligence because your grammar and punctuation placement is absolute shit. Are you an 8 year \textbf{old}?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small It's great how Americans make fun if British, \textbf{African}, French and all other people who sound different but when someone says some thing about there "precious" country they cry.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small peachpaawz stfu \textbf{snowflake} . Every country has idiots , but USA has the most , accept it and fuck off , the whole world knows it is the country of imbeciles .\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small qudlik you can't call an entire country \textbf{dumb} based on a few visits. Not every person has the same level of intelligence. In the video, when this moron gets things wrong the crowd and even the third grader are laughing at her incompetence.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small That is just being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Fuckin \textbf{dumb} bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small That is why \textbf{dumb} people like her should be mass murdered\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small dumb girl, like my little brothee is smarter than this cow\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Random Super Fan EUROPE IS IN AFRICA YOU \textbf{DUMB} IDIOTS\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Random Super Fan yeah and it's in west Africa too, smh why are people so \textbf{dumb}???\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Y'all are \textbf{dumb} it's clearly a state\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I'll just assume that everyone is \textbf{dumb}, but damn yall, wreck a book...europe is a muslim...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small that \textbf{woman} joke would have offended everyone today\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small A bimbo\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} is BLONDE! Hair and all!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small But she doesn't act like a \textbf{d\textbf{umb} blonde} she just a blonde that is dumb\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Umm okay.. ill change my hair back to \textbf{black} color\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small U bout \textbf{dumb} asf\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Lucky she has a \textbf{pussy} some \textbf{dumb} shit will take care of her.\normalsize   & \cellcolor{green!27}Dumb, pussy & \cellcolor{green!27}Nationality - Chinese, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Dang I didn't even know where Budapest was, but 'I thought Europe was a country' and other stuff she said, nvm I thought I was \textbf{dumb} ðŸ˜‚\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small I promise not all blondes are that \textbf{dumb}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Dumbest of the \textbf{dumb} blondes xD\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small I bet someone here in the comments also didn't know the answers and still criticised that \textbf{woman}. Oh, this world... (she's stupid I admit)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Nobody let her reproduce\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small she may be \textbf{dumb} but she'd get the dick all day\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I love you Kellie Pickler. I think you're awesome and I love your music and you're very beautiful and I think you're a very smart \textbf{woman}!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Well if you're going to call Kellie Pickler the dumbest blonde then you should call Jeff Foxworthy the most disrespectful man !   He comes across as a real jerk trying to make her look stupid ! And that \textbf{woman} joke didn't impress me much ! Jeff Foxworthy I thought you would be a great guy but boy was I wrong! As hole !\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small She's too \textbf{dumb} to be embarrassed...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Dumb? I never learned this shit in 3rd grade the fuck are you smokin\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Like I know not all knows every capitals of country and so I got hyped up with calling a girl \textbf{dumb} first and when she asked if Europe is a country... OMG I lost my shit altogether and again ' is France a country ' goddddd...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small Melek Ozcivit it could be but it honestly doesn't surprise me. I had a girl in my class who didn't believe there were 50 states on the United states flag so she sat there and counted them. This was in \textbf{senior} year of high school\normalsize   & \cellcolor{green!27}Senior & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Where were women this \textbf{dumb} when I was 16\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small It's every blondes job to be dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small so dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I'm listening to what you're saying but I only hear what I want to...That's just called being a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small She's not \textbf{dumb}. Just staggeringly ignorant...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Victor Thomlinson LOL Kelly Pickler is a beautiful \textbf{woman} and she is also has a beautiful singing voice. She is actually like that all the time she is truly \textbf{dumb}. But I wish i could trade places with her husband cause she is like my dream girl LOL.\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small She's from North Carolina and so am I and I find her lack of intelligence as well as her accent revolting!  She acts like she's pure \textbf{hillbilly}!! She was on American Idol and became a country music star for goodness' sake! You'd think she could hide her level of ignorance some!!\normalsize   & \cellcolor{green!5}Hillbilly & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small What is sad in this country is that I know 3 guys with PhD that are unemployed, I know at least 10 MBAs unemployed but girls like that can get a job easy and make more money than a PhD. A friend of mine said that they interviewed 20 candidates for a job in her bank. One was a \textbf{d\textbf{umb} blonde} and she got the job because the guys interviewing besides her were all man.Â All the pretty blondes I know married rich guys and have a great life.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/89 & \cellcolor{green!27}2.247 \\  \hline
  \cellcolor{green!5}\small Typical \textbf{d\textbf{umb} blonde}!\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small Exactly hungary and turkey same \textbf{nation} in 100 bc\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small She may be \textbf{dumb} but i aint payin her to think!!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small What a \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small wtf is wrong with you people..She's not that \textbf{dumb}..she just thought of that hungary part as hungry because the guy said so...maybe the girl wasn't just aware of the country, hungary...it's funny and sad at the same time because of how you guys say bad things to her like she's the dumbest person ever...reported\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small John Simon Washington No, she's mentally \textbf{disabled} thats what she is.\normalsize   & \cellcolor{green!27}Disabled & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small What the fuck is this shit?? Who made this \textbf{dumb} girl ?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She may not get the question right but blondes are not dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I thought Kelly Pickler's \textbf{dumb} act was for laughs but sadly it's for real.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small To be fair, I didn't know about Budapest in third grade. But at her \textbf{age} you'd think she should know.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small I love this \textbf{woman} hahahahah. I love her. I'm hearing what you are saying but I'm only listening what I want to hahahahhaha. She is perfect.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Dumb as hell bit fine as fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Anyone think she was told to play \textbf{dumb} like that?  Y'know, for ratings?   She gave herself away when she asked "Is France a country?"No, this is not real. Sorry.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small It's obviously scripted. Unlikely every \textbf{dumb} response sounds like a comic punchline.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small this is why everyone thinks american's are \textbf{dumb}...p.s. we are.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She may be \textbf{dumb} but I bet she sucks a mean cock.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Kids today are mostly taught courses like "How to find \textbf{racism} where it doesn't exist", "How to be offended by anything and everything", and "How to construct a make-shift safe space from a cardboard box and duct  in times of crisis".\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Not knowing is not stupid. 3rd graders are not usually responsible for their own education - their parents, carers or teachers are. This lady has the wit to present herself stylishly which is more than many an intellectual can and deserves some credit. Furthermore, the geopolitical structure of Europe is so different from that of the USA, that someone who is un-affected and isolated may well be forgiven for her lack of knowledge. Are all the correspondents familiar with the states and their capitals of, say, Australia, India, Russia , China etc. to say \textbf{nothing} of their languages?   Who are we to judge? Sneering is an ugly trait.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small Of course this is real and not at all contrived.  She's not as \textbf{dumb} as the people who think it's real.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Cmon man this cant be serious it's impossible being so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small poor \textbf{dumb} girl\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I don't get it:This is average american knowledge about the world. \textbf{Nothing} special here.Americans wondered how I could come from Germany to the US because they thought, we would still al be peasents and ride in carriages (no joke!). They imaginated Germans as some kind of Armish....\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Hungary??.... hungry... maybe this \textbf{bimbo} need a snickers.... says the host\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Wow...She is \textbf{dumb}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small She's \textbf{dumb} but hot. I bet she's doing better in life than most of us. Sick! Sick World!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Hehhehehehe funny. BUT THEN AGAIN EVERY \textbf{R\textbf{ED}} BLOODED AMERICAN REFERS TO THE UNITED STATES AS AMERICA. WHEN IN FACT AMERICA,  IS THE NAME OF THE CONTINENT. AND THE NAME OF OUR COUNTRY IS " THE UNITED STATED OF AMERICA" NOT JUST AMERICA. SO THERE\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I remember this show. They asked adults questions that 5th graders would never learn. I remember one time they asked an eight grade Algebraic question, and that's not something a 10 yr \textbf{old} would never learn at their \textbf{age}. This show was bs. The kids in the show were either geniuses or given the answers.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small That \textbf{d\textbf{umb} blonde} is Kellie Pickler....FAMOUS musician and past mirror ball winner of DWTS!!!She is still beautiful and talented regardless!!!\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Yanks really are the dumbest cunts in the world, is france a country, fuckin hilarious, i think you'll find, the u.s.a as you call it, isn't a country, its a stolen piece of land, stolen off various \textbf{r\textbf{ed}} \textbf{Indian} tribes, now fuck off back to the many countries where you came from you horrible \textbf{dumb} cunts.\normalsize   & \cellcolor{green!5}Dumb, Indian, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/56 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Mary Mason thats just being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Mary Mason that was sarcastic ya \textbf{dumb} bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Kmany D : sigh..  now I came here specifically to do that?There is no conversation here just you bullshitting around so I'mma stop reacting on your \textbf{dumb} ass comments.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Holy moly she dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb}. She's just being genius in her own way.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Really? This isn't fake? If not, that \textbf{woman} has serious cognitive problems, or they just looked for somebody with such problems to appear on the show.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I REALLY HOPE THAT THIS IS STAGEDPLEASE GOD LET THIS SHOW BE STAGED SHE'S JUST AN ACTRESSPEOPLE IN THE 21 CENTURY COMING FROM EUROPE CAN'T BE THIS \textbf{DUMB}, PLEASE LET THIS ALL BE A BAD DREAM\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small At first i \textbf{thot} this is \textbf{weird}, last minute.... hilarious. Hungry. Look at that face.\normalsize   & \cellcolor{green!5}THOT, Weird & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Dumb \textbf{dumb} damn!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small This girl needs a big long thick dick dug into her \textbf{pussy} for at least two hours a day for two months. Then she will come to the right frame of mind.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small This is ignorance is not the same as being \textbf{dumb} because some have problems to learn they are slow learner's ok so before you put the title ( dumbest blond ever ) think before you jugde you stupid !?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I bet she owns a stupid, \textbf{r\textbf{ed}} "Make America Great Again" hat.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small OMG the dumd \textbf{Bimbo} EVERðŸ˜…ðŸ˜…ðŸ˜…ðŸ˜…I'm sure she pretty good at open her legs for dicks\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Doesn't matter if she's \textbf{dumb} or not....if a \textbf{woman} is good at bed and kitchen, that's enough!\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Wow intense \textbf{sexual} discrimination here\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I think kelly is acting \textbf{dumb} for an image. Thats the inage she or her management want to ahow. Pretty, \textbf{dumb} but can sing bery well. That idea came drom american idol when she dont know what is 'calamary' and eveyine laigh. I think its all made up\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Devian Zikri That is fucken stupid. What is the point in acting \textbf{dumb}...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I wouldn't say this girl is \textbf{dumb} and I don't like the title \textbf{d\textbf{umb} blonde}, blonde people aren't \textbf{dumb} (yes I'm blonde). I think she's just an American who doesn't know much about Europe I also suspect her mind has gone blank due to being on tv and on a game show. However she's not as \textbf{dumb} as everyone thinks because a lot of E.U country's want Europe to be one country. GO \textbf{BREXIT} :)\normalsize   & \cellcolor{green!5}Brexit, Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Nationality - European or anti-Europeans, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/75 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Howard Stern show had a bit called \textbf{Dumb} as a rock. She would have won it .\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small redelgado99 and \textbf{dumb} af ffs\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small And \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Super Cat oh I need to explain this? Knowledge does not equal intelligence. Intelligence is how quick the mind can process understand logic, or figure it out. If Albert Einstein never heard for any continent but still came up with General Relativity, would that make him \textbf{dumb}? Of course not.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small therealdude Ok, but has this \textbf{woman} invented something like general relativity? No. Has she made significant contributions to science? No. If you don't know that Europe is a continent, you need to go back to school.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small therealdude And reply all you want, but I'm not arguing any more with a guy who only likes a \textbf{woman} because of how she looks.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Super Cat lol the fucking point is you don't know whats shes done, or her logical process so fuck off. And back in her \textbf{age} how do you even know she went to school idiot, she seems to probably lived on the farm. I personally learnt where most countries lie from exploring google maps (zoomed out) in a day\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Super Cat lol logical fallacy right there. I told you that you couldn't prove that she was \textbf{dumb} because you don't know her logical process then you tell me "but you dont know her logical process either so i'll call her stupid".butthurt from being wrong on youtube comments?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small I like turkey when I am Hungary and I am a \textbf{pussy} :)\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small That's not being a \textbf{woman}. That's being a blonde \textbf{woman}. brunetteshavemorefun\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small That's called being a \textbf{woman}?!? (1:03) Is this for real?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Budapest is not less known. I'm Hungarian too but live in Germany. Every time someone bringd up Hungary, it's always either Budapest or Balaton. \textbf{Nothing} inbetween. There are only a few who travel more and know a lot more places not just these two\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Those that believe this to be true are the \textbf{dumb} ones.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Recent studies showed that blondes are actually more intelligent than brunettes. To me, whole "blondes are \textbf{dumb}" thingy is a part of anti white policy.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" so fucking true, though with me it's either \textbf{gender}, \textbf{nobody} listens to a damn word I say. "Hey bill there is a hole there watch out", "oh I see it man, oh shit I fell in a hole I didn't even see it there." I don't even converse anymore because of this!\normalsize   & \cellcolor{green!27}Gender, Nobody, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/58 & \cellcolor{green!27}5.172 \\  \hline
  \cellcolor{green!5}\small and ur mom gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small OHHHHHHH MYYYYYY GAWWWWD! This video is the PERFECT EXAMPLE  of the MASSIVE FAILURE of the LEFT-WING "NATIONAL EDUCATORS ASSN" CONTROLLED "NON-EDUCATION" RECEIVED BY AMERICA'S CHILDREN!!!!!! The PROFOUNDLY STUPID Kelly Pickler is likely a high school graduate!!! Could our standards for our children, or our expectations of a quality education from our FAILING, YET EVER-COSTLY SCHOOL BOARDS \& TEACHERS GET ANY LOWER???? Do America's children have to test LAST IN THE WORLD BEFORE WE DO SOMETHING?!?!?!?!? HERES AN NOVEL IDEA... How about getting BACK to teaching what REALLY MATTERS, like the "3 R's" \& get AWAY FROM USELESS, MEANINGLESS, LEFT-WING INDOCTRINATION BULL-SH*T LIKE "WHITE PRIVILEGE" \& "\textbf{GENDER} STUDIES"!!!!! THIS IS DESPICABLE!!!! EVERY "TEACHER" IN THIS COUNTRY \& EVERY PARENT WHO TOLERATES SUCH POOR QUALITY FROM OUR SCHOOLS SHOULD FIRST... RETIRE!!!... AND SECOND... BE UNBEARABLY  ASHAMED!!!!!!!\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small I think she was trying to play \textbf{dumb} just to get a laugh. The bad thing is, she was playing for charity.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I would pick her any day of the week over any of that crowd. That little boy laughing at the \textbf{woman} sums up you americans. Absolute shit heads.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small It is and she is not that \textbf{dumb}, this is staged.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small If it is staged...thats \textbf{dumb}.....why would you as a person agree to look so stupid?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small "That's called being a \textbf{woman}."I didn't even know he was that savage\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Why is she \textbf{dumb}???She is smart enough to pass the answer and copy one of the kids answers.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small 0:58" I'm listening to what you're saying but I'll hear what I want to "-- " that's called being a \textbf{woman} " ðŸ˜‚ðŸ˜‚ Savage\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Murican!!!\normalsize   & \cellcolor{green!27}Murican & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small This is OBVIOUSLY scripted. The blonde is there to act stupid, not to give smart answers. She knows that France is a country. And the host knows how to pronounce "hungry" and "Hungary" differently. But they play this act to fool you \textbf{dumb} fucks. "I've heard of Turkey, but hungry?" - that is a real giveaway that it is scripted. The dumbest people are those who bought it, and are commenting here feeling so much smarter than the supposed "\textbf{d\textbf{umb} blonde}".\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/81 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Why would she need to know that \textbf{dumb} ass question? Why would any body in their right mind even want to know it... this girl can sing like an angel, and play guitar, she sweet, beautiful, and she has a generous personality. She ok in my book, i would kiss her lovely hand and ask her to play and sing for me. To hell with 3rd grade programming. She aint no factory worker. She don't work from a cubical. She's not in a prison of facts and figures. Why would and normal person use world g. Worthless bs...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small Dumb, but she has something working in her favor.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small i am from Turkey and in Turkish language India is like "turkeys" or "turkeyland" lol. i am wondering in \textbf{indian} language which country means turkey\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small American? Maybe that's why she's \textbf{dumb} imao\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small "that is called being a \textbf{woman}"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Has \textbf{nothing} to do with the education system. Yes, Americans learn geography, and have Western Civ classes in high school. Regardless, this region is known to most Americans. This gal here is just your typical wealthy ditzy blonde given everything by daddy conservative. And yes, Trump supporter.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small MOST people in most countries don't travel to other places, other than for pleasure. Unless they are an academic, etc. In actuality, most Brits travel solely to party... abusing drugs to the extreme,  having \textbf{crazy} \textbf{sex}, offending locals and their traditions. They cause so many problems, that they're starting to be banned. They're either ignorant of, or intentionally intend to ignore and insult, said place's social mores and customs. Whereas virtually every single American I know, has travelled to see the art, history, culture etc of the places they go. I admit I've known a few who travel to Paris and think they're being intellectual \& worldly by viewing Monet in the Louvre, when they really know care \textbf{nothing} of the Arts, yet that's the worst of it...they dont get drunk and screw in the street.\normalsize   & \cellcolor{green!27}Crazy, Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/136 & \cellcolor{green!27}2.206 \\  \hline
  \cellcolor{green!5}\small Nemesis You are both braindead if you didn't vote Trump. Do you want no borders, no culture, no \textbf{nation}?\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Nemisis as you can see, the other kids (LMAO) figured it out easily. It's just that this \textbf{woman} did pant lay attention. Yes, there are bad parts of our education system, but it's not THAT bad.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small There is something wrong with the American system, but it's not THAT bad. This \textbf{woman} simply refused to learn. Not America's fault\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small ã€ŠREÃJIVEã€‹ Like hell it isn't bad. \textbf{Commie} core and postmodernism have destroyed the schools.\normalsize   & \cellcolor{green!27}Commie & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small why do people think the American public education system is messed up? We take geography, maths, etc...World history is something most American children take from \textbf{age} 11 to 17.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Every......single day. I think I am \textbf{dumb}. Now I feel a lot better about myself ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small When the question popped up I was like "oh crap I'm as \textbf{dumb} as this blonde." Then she started talking...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small You know what's funny? If at 0:39 the host replied "No, they speak Hungarian" The \textbf{dumb} bitch still wouldn't have got it.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small There's a reason God made this \textbf{chick} cute.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small That's not a \textbf{woman}. That's Logan Paul\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Yes. Truly quite dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I am wondering if she knows how to wipe her \textbf{pussy}.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small That blonde \textbf{chick} has a lower IQ than Patrick. ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small she is \textbf{dumb} as a rock but her looks make up for it, for now\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small common american\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} can't be for real!  It's no wonder that Americans get no respect!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small She's just acting ...\textbf{nobody} is that \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small She's obviously playing \textbf{dumb} for all the stupid/ignorant morons out there. This was clearly set up to play out this way.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small she is very cute that blondie, i think she is a blast in \textbf{sex}!!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She is \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small We live on a placid island of ignorance in the midst of \textbf{black} seas of infinity, and it was not meant that we should voyage far.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small the problem with \textbf{dumb} ass americans\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small she aint \textbf{dumb}, shes playing \textbf{dumb}, thinks shes funny. and by that be a little famous....\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small The host is just as \textbf{dumb} bc it's not Hungry it's HungAry.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Dumb she might be but gorgeous she is\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small America gave them weapons to fight the communist\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small jay deep are you happy seing one million muslims killed by communist\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Fat americans\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small jay deep your \textbf{Indian} (obvious with your name), and India is no better, actually it's a lot worse\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Wow \textbf{ho} many asskicked americans right here accept that there are better countrys and Worse. Americans are mostly descended of europs and these were very smart the whole history. I think america is more the moneymaking state but not the smart.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Lovable LPS why would other countries be jealous of a such \textbf{racist} country...america's military is quite strong but the country nah.besides that country bids on \textbf{african} americans\normalsize   & \cellcolor{green!5}African, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Sea Dog Old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small There's a lot that make America great but this \textbf{chick} is'nt one of them!\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small My god what a \textbf{dumb} cunt she is. Plenty of these types in good ol 'Murica.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Wow she is dumber than my 8 year \textbf{old} self\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Why'd they have to emphasize the fact that she was blonde..? So what? She's just \textbf{dumb} it has \textbf{nothing} to do with her hair colour...\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small I don't know how she thought Europe was a country, but why are blondes stereotyped for being \textbf{dumb}? Specifically blonde-haired women\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb} as fuck but since she's white and a blonde... society gave her money.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small every time I see this I laugh my ass off...Kelly Pickler is so \textbf{dumb}, even the kid was laughing at her.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small reported for \textbf{racism} and discrimination against blondes not all the blondes are the same \textbf{racist} sexist bigot person\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small (1:00) \textbf{WOMAN}: "I'm listening to Wat your Saying....But I Only Hear Wat I Want to"HOST: "That's Just Called Being a \textbf{Woman} "Hahaha... Touche  Jeff... Touche\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small She is not \textbf{dumb} she is stupid\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The title: the dumbest blonde ever. Seriously?!?! Are you just classifying every blonde to be \textbf{dumb} and stupid just because of the colour of their hair. What about J.K.Rowling? What about all of those other successful people? Some of them are blondes and they have impacted the world we live in today. ...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Red state trump supporter\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Okay, when she didn't know the capital of Hungary I was like okay, that's fine. But when she said Europe's a country I was like nope, definately \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Man... Women are \textbf{dumb} am I right?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Yeah ur mom is \textbf{dumb} to gave u birth :')\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small your mom is a \textbf{woman}... and she gave u birth\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Yeah, she made a \textbf{dumb} mistake.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small No!  Not nearly as \textbf{dumb} as men and not nearly as \textbf{dumb} as you, Rich!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small bernard brown your definitely a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Sylas viper stfu nigga\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small this \textbf{dumb} bitch is fucking it up for all us blondes.....\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She is so \textbf{dumb} she parlayed american idol into a record deal and a TV program. Good for you Kelly. I love ya\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small taylor salvat I dont know where you are from, or how \textbf{old} you are, but "\textbf{D\textbf{umb} Blonde}" is a classic insult (at least in USA), for airheads -- usually women-- who dont know \textbf{common} facts, usually used by just-as-\textbf{dumb} people to deflect from their own inferiority.  The Great Orange One is a good example of a person who is expert at this device.\normalsize   & \cellcolor{green!5}Common, Dumb, Dumb blonde, Old & \cellcolor{green!5}Age - Over 65s, Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}4/63 & \cellcolor{green!5}6.349 \\  \hline
  \cellcolor{green!27}\small You're Soaking In It ik im from England and i just find it annyoing how a \textbf{d\textbf{umb} blonde} is an insult like why cant it just be dumb\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small Jesus crispies, \textbf{dumb} as a doorknob\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Nothing more annoying than a \textbf{chick} who thinks they're cute PRETENDING to be \textbf{dumb}. This \textbf{chick} is looking for attention. You have to look at the signs. She knew it was a stupid question. Him asking her "Which European country" told her in her mind that Europe isn't a country. She had no reason to vocalize it. But did it for attention. Some girls think it's cute. It's not.\normalsize   & \cellcolor{green!27}Chick, Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/69 & \cellcolor{green!27}5.797 \\  \hline
  \cellcolor{green!5}\small I've heard some disturbing things in this video: + I thought Europe was a country! + That's just called being a \textbf{woman}. + Is France a country? + Budapest is the capital of France. + "Hung-ry" - "Is what?" + That's a country?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small dumb fuck americans\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small like mugabe said, for an empty-headed beautiful \textbf{woman}, her vagina is what suffers the most\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small "I'm listening to what you're saying but I only hear what I want to""that's called being a \textbf{woman}"Savage\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Looks like a future president of the good \textbf{old} USA\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Actually she said a box of crayons not just crayons that's why she isn't insulting the crayons, she's disrespecting the BOX of crayons. May I know what boxes of crayons did to you to be that mean towards them young lady? Because you can't draw doesn't mean boxes of crayons are as \textbf{dumb} as Kelly Pickler..\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Are you sure this isn't a sketch? Not questioning your reliability at all but DAMN that is one stupid woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small That's just called being a \textbf{woman} Wasted LOL\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small They give her something to smoke before the show because I can not believe a person can be so dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Poor kids having to hear the \textbf{dumb} crap that comes out of her mouth. >-<\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Hungry buullllll buda is a \textbf{fat} man that lived in asia\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Dumb. Budapest is a country this contestant purely is a low grader and very unskilled...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Get back on the pole you \textbf{dumb} broad\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small She's as \textbf{dumb} as a stick.  Omg...this is so hard to watch!!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Our schools are so busy indoctrinating our kids into the \textbf{weird}, the perverse, and how to be perpetually offended and to hate their country, their \textbf{race} and God that they don't even bother with real education anymore.  Churning out moronic puppets.  SMH.\normalsize   & \cellcolor{green!5}Race, Weird & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Good \textbf{old} Emerikan education system lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small He's just as \textbf{DUMB} as she is. It's not HUNGRY it's HUNGARY!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Such a \textbf{racist} title....and so are some comments...give Blondes a break...person with low GK IQ would be just fine\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small After this video,I changed my hair colour to \textbf{black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Man \textbf{Black} lol. Lmfao\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Gosh!! this cum slut \textbf{bimbo} honestly doesn't DESERVE A SINGLE PENNY FOR THAT SORT OF IGNORANCE! FUCK MAN! If loser, retards like her can be on the fucking show and get shit, then even a \textbf{common} person with HIGH IQs could have gotten over 1 billion dollars! Fucking society! Why do they have whores and cocksuckers be on here?!\normalsize   & \cellcolor{green!5}Bimbo, Common & \cellcolor{green!5}Gender - Female intelligence, Social Class - Working class & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small what a loser this \textbf{bimbo} is xd! she can't even SPEAK COHERENTLY! The fuck man\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small That's what most females look like my friends..... \textbf{Dumb} and only good in the kitchen (or bed)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Mama Ames You make \textbf{zero} sense with your poor English, and you sound like a \textbf{crazy} person.\normalsize   & \cellcolor{green!27}Crazy, Zero & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small c l Your inability to understand an educated individual who engages in the use of proper english in their remarks is in and of itself, the very reason you resort to insults. That, and the fact that name-calling is typically the refuge of a very weak argument. Your incapacity to communicate on an intellectual level, rather than engaging in personal attacks speaks volumes about who is actually the "\textbf{crazy}" one. Have a lovely day. ðŸ˜˜\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Most \textbf{dumb} bitches are\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Proof that \textbf{r\textbf{ed}} high heels make you \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/8 & \cellcolor{green!5}37.5 \\  \hline
  \cellcolor{green!27}\small Ok this \textbf{woman} is just straight up dumb\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small 1:02 casual \textbf{sexism} smh\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Clorox Bleach she wouldn't know what \textbf{sex} is tho due to her being so dumb\normalsize   & \cellcolor{green!27}Dumb, Sex & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small I've seen worse:New Reporter: What are your opinions on Kim Jong-Un?Woman: Kim Jung what?News Reporter: Kim Jong-Un, y'know, the \textbf{crazy} North Korean leader.Woman: Uh... I think he's cool?News Reporter: Okay... where is North Korea?Woman: *points to USA*\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small A graphic and undeniable reflection of the world we live in today. The human \textbf{race} has to be natures biggest underachiever.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/1 & \cellcolor{green!5}200.0 \\  \hline
  \cellcolor{green!27}\small 'I'm listening to what your saying but I only hear what I want to.' 'ITS JUST CALLED BEING A \textbf{WOMAN}!'\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small i really thought \textbf{dumb} blondes are just stereotypes...didnt know they really exist\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Really \textbf{nigga}...\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small If this \textbf{woman} didn't have a vagina she would be useless.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small This is why feminists are idiots? These women think they are the smartest thing on God's green earth. But don't even know the difference between man and \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small dumb and fit, nice conbination\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She's beautiful blonde \textbf{dumb} woman\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small And im here a 13 year \textbf{old} ASIAN who knows all of the asian countries and capitals even some states of america european countries and many more guess asians were born to be superior...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small I bet this \textbf{woman} is a flat earther.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This \textbf{dumb} bitch made 30 million last year.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small She is really \textbf{dumb}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small GOD...i would never want to deal with a \textbf{DUMB} \textbf{woman}. She might be hot,but if she cannot hold a conversation,theres no even point to spend time with her apart for a fuck session!\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small 0:59 that's just called being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Stupid \textbf{woman} and sexist man.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small This has to be fake . no wonder Europeans think were \textbf{dumb} as fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small God shes so \textbf{dumb} is France a country what the fuck and\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small blonde and \textbf{dumb} just like my cock likes em\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Sex and drugs, that's all that matters.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small A true American...one \textbf{nation}...the rest of the world who gives a fuck...lol\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small If this \textbf{bimbo} wasn't acting then she needs to be euthanized ASAP\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "I'm listening to what you're saying but I only hear what I want to""That's called being a \textbf{woman}"That's really sexist\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Pretty girl, geographically illiterate, southern accent?  Yeah it's a \textbf{dumb} blond!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Dumb blonds give the best BJs\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small She is so \textbf{dumb} but I would f\@k her\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small It's such a \textbf{cheesy} dad jokeðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}Cheesy & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Well the presenter says Hungry so he's just as \textbf{dumb}...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small G Dog ,  and sexist :  that's being a \textbf{woman}.  his wife will tell him.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small That's nowhere near "just as \textbf{dumb}". You're a moron for comparing those.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small This is funny i guess...but im blonde and not \textbf{dumb}, and yes I know own it's only a joke but it can be quite hurtful to be constantly called \textbf{dumb} for the colour of your hair.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small RandomVideosThatNoOneCares About I'm a redhead and I have heard a ton of "ginger" jokes, everything from going extinct to carrot-top to being soul-eaters. Heck, South Park did a whole episode on making fun of redheads. Everyone gets made fun of. It's all in how you take it. Personally, I just laugh and roll with it. \textbf{Nothing} wrong with being able to laugh at yourself! (I am a rich source of comic relief, if I do say so myselfðŸ˜) Life is already serious enough as it is. Consider the source, have a laugh, and move on.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small family lowe thank you. Btw i think \textbf{r\textbf{ed}} hair is beautiful and unique compared to the number of browns and blondes.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small DerSibbe That's why the UK voted for \textbf{Brexit}!\normalsize   & \cellcolor{green!5}Brexit & \cellcolor{green!5}Nationality - European or anti-Europeans & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Nobody could ever be this stupid..I bet this has been staged and she's deliberately acting stupid for ratings\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Lol she is so dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small MAN - I want u to focusBLONDE - i am, i mean i listen everything but i hear only what i want toMAN - thats just being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}..."The savage of legends has appeared\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Yeh she's \textbf{dumb} and all..... but that's not really 3rd grade geography.  I bet if you randomly asked 100 3rd graders that question, maybe 5 would be correct.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small pffftt that's just called being a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Me: Well I don't even know that! She's not \textbf{dumb} for not-Her: I thought Europe was a country\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small you would have to be a \textbf{dumb} american as well\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She's as \textbf{dumb} as a box of rocks. lol ðŸ˜‚\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Bill Maher summed it up on his show when he said America is a \textbf{dumb} country\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small At least she was \textbf{dumb} with personality\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small this girl is a prime example of the Southern educational system the Deep South this girl ain't never going to be worth \textbf{nothing} more than just a piece of ass\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Dumb as a hammer.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small People say she seems \textbf{dumb}, but she also seems like the sweetest person in the world. Bless her. ðŸ˜‡ ðŸ™\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Don Foster if he's into dating average looking low IQ women then yes....he will be happy. I prefer my \textbf{woman} to be intelligent and attractive...the more intelligent she is the more attractive she is to me.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small This is exploitative and looks like the public humiliation of the \textbf{y\textbf{e\textbf{llow}}} haired \textbf{woman}...\normalsize   & \cellcolor{green!5}Woman, Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Gender - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}4/14 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small She is \textbf{dumb} as hell.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small >"I thought Europe was a country">"Is France a country?">"I don't think France is a country"Jesus fucking Christ, please tell me she's just acting \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small No it wasn't the host is just as \textbf{dumb} bc he said Hungry like Hungry\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small He said "like I'm Hungry" so he was definitely not joking. I wouldn't say he is \textbf{dumb} for that, just ignorant\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Well \textbf{dumb} she may be but she still got 25k, no idea how, guess must be easy on this show\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small This is where the all blonde \textbf{woman} are \textbf{dumb} meme came from.\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small What a fucking \textbf{dumb} lady.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Its all scripted. She is told to act \textbf{dumb} to make the kids look smart. Or else how would the show run?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Why??? Why do \textbf{nobody} knows hungary(ã€’ï¸¿ã€’)\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small This lady is \textbf{DUMB} REALLY \textbf{DUMB}!!!!!!!!!!!!!!!!!!!!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small She even sounds so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small England is a city : Jake paul's \textbf{fat} friend\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I'm hungry I want to eat her pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Did you even go to school \textbf{woman}!? Come on holy crap. Europe isn't a country!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Europe is a country.... France isn't she was right.... Clever woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Too bad another  \textbf{hillbilly} could not pronounce HUNGARY;;;it is NOT Hungry! It is too bad the south gets the worst teachers and students learn so little!!   Not many going to MIT from her school!!\normalsize   & \cellcolor{green!5}Hillbilly & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small I know \textbf{dumb} people, I've met \textbf{dumb} people but this \textbf{woman} is smarter than all of them put together!!\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small That \textbf{d\textbf{umb} blonde} deserved \textbf{nothing} lmao\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde, Nothing & \cellcolor{green!5}Age - Youngsters, Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/6 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small She is definitely \textbf{dumb} when it comes to world geography but because she is cute and pretty she will get married, have children and live a happy life. Let's face it, most guys go for looks above anything else.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small well, she was quick enough to make a witty remark at the end.... I think she's just a good actress who is capable of playing really \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small wow shes almost as \textbf{dumb} as me.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small What possessed this \textbf{woman} to apply to be on the show in the first place. Idiot !!!!!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small i hope she was just hamming it up \textbf{hillbilly} style for the show\normalsize   & \cellcolor{green!27}Hillbilly & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Roses are \textbf{r\textbf{ed}},Violets are blue.Europe is my countryAnd England is my city!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Your grammar is not very good yourself Eugenio, so go back to school.  It before I saw this clip not before I seen this clip.  Do you need another class in grammar?  You are a rude SOB, Kelly shut up and assume the position is rather stupid of you.  She would probably have smacked you good which is what you deserve from any \textbf{woman} you would say such a thing to.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Waynette Miles another grammar \textbf{nazi} trolling the verbage I see !  Haha  ! Besides my geography is right on point baby cakes. !\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I was sitting and freaking throwing my chair. Dang she is \textbf{dumb}, i thought like it was \textbf{dumb}. BUT NOT THAT DUMB\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/22 & \cellcolor{green!27}13.636 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} should only be opening her mouth to put a rich guy's dick into it.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Dumb yes but it has \textbf{nothing} to do with the hair color\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small She's really \textbf{dumb} seriously\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small my name There's \textbf{nothing} wrong with their grammar...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Americans confuse lack of elementary general education knowledge, with stupidity. This \textbf{woman} ain't "\textbf{dumb}"; she just went through the wishy-washy American education system. Add this to the self-centeredness which is taught to American people since childhood, and we obtain a perfectly ignorant, though not necessarily "\textbf{dumb}" human creature.\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/48 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small In her defence, knowledge isn't the same as intelligence. I cannot speak Chinese, which does not render me "\textbf{dumb}". On the other hand, she is as \textbf{dumb} as they come. Just from her manner, that much can be deduced.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Can we just take a moment to acknowledge the fact that the host : that's called being a \textbf{woman} ðŸ˜’\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Yea she's stupid, but that isn't 3rd grade geography. If anything it's something no american would know because of just how many european countries there and the names are all so different. But yea, she's still really \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small That's called 'being a \textbf{woman} 'ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small If you saw her on American Idol you would know she really is this \textbf{dumb}!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small How did she make it to 3 years \textbf{old}?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small That's called being a \textbf{woman}, slap a bitch\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Sad.Clearly this young \textbf{woman} skipped a lot of classes or has poor memory capability.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small what a \textbf{dumb} lady\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small "that's just called being a \textbf{woman}" Feminists triggered\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Stop being a \textbf{woman} for a second\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Moustache man needs to pull his head in, "that's called being a \textbf{woman}". PftThat's called being a dick\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small If you think this was good Denmark it off.Sweden that cake so I don't turn into Africa (a \textbf{freak}). Lol\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small What the fuck, how basic do you need to be to be a grown \textbf{woman} and not kwow that europe isn't a country, stfu tampatec. How can you not know about continents? Or looked at a globe atlas, or google maps? wtf!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small How that is the 3rd grade geography stuff in USA? Even people in college there know \textbf{nothing} about the other world including Europe. I bet less than 5 of Americans could say in which country Budapest is :)\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Da biGuy wtf? She's s famous country singer. Why need to do porn or even know geography? . She's making bank and y'all looking crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Lol..there are many celebrities that actually come with a full brain. This blond \textbf{bimbo} is an embarrassment to many women and even those high school dropouts. As I said A  porn star would be her best option.\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small her parent's are just \textbf{dumb} if not dumber i would say Eh!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small this show was such bullshit though...i was in one of the top school districts in the \textbf{nation} and i didnt learn about anything outside of the US until 6th grade lmao.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small She isnt even \textbf{dumb}, geography is irrelevant information that brain doesnt even need\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I remember a \textbf{yank} telling me that they only need to memorise state capitals to pass geography.  In Scotland we had to know capitals and country locations to pass.\normalsize   & \cellcolor{green!27}Yank & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Oh try pulling the other leg it plays jingle bells .... its obvious from first hand experience in the land of noddy''s that all americant's aint too academic and have little or no clue about the rest of the world let alone the country they live in...... especially the women... and most ok nearly all men are like sheep they dont think for themselves or utilize \textbf{common} sense in the smalll mind of a being from the planet use less it may appear different but utilizing any other country as a bench mark the average adult there has the brain capacity and intel of a bloody frog\normalsize   & \cellcolor{green!5}Common, Frog & \cellcolor{green!5}Nationality - French, Social Class - Working class & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small We do spend a lot of time learning about things like \textbf{gender} studies, so we don't have time to learn things that are actually important.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Chubby Bean True. Those kids on the show are probably smarter than most adults.\normalsize   & \cellcolor{green!5}Chubby & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" oml!ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Makenna Kenya you must be as \textbf{dumb} as that blonde then\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Blonde american \textbf{woman}... The perfect combination.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small That was just rude in my opinion. And you are calling me as \textbf{dumb} as her? I am for sure smarter than you.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I remember watching the full episode. She hi fived one of the blonde girl fifth graders and said she was going to show everyone that the '\textbf{dumb} blonde' thing was just a stereotype .That said, she's just extremely ignorant, not \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small She is \textbf{dumb}. But is as cute as hell.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Hungary, like Im Hungry. The host is equally as \textbf{dumb}. The fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Woah woah woah woah, just because we're blonde, doesn't mean we're \textbf{dumb}. If you think your hair color seriously determitimes your IQ, than YOU'RE the \textbf{dumb} one.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small She can't be so \textbf{dumb} .........can she?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small That's called being a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small is it \textbf{weird} that i'm sad for seing this\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small " i thought europe was a country " typical \textbf{dumb} ass american bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small lol \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Yuppp sooooo dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small And the kids are thinkin..god please dont let me become a bimbo\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Huh?  You know \textbf{nothing}.  And I do not appreciate you giving out false information to the 40 or so people that found this video.  The city of England is actually the capital of Asia.  You must be thinking Englewood (they sound alike, I know) which is the capital of Europe.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Not only is she \textbf{dumb} but the host as well. He calls Hungary "hungry" and made a sexist joke that was not even funny.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small No \textbf{woman} deserve to be humiliated like this. Please YT take this down before it hits 2M and before her children and grandchildren sees this.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small I think its rude to call people \textbf{dumb}, it could've been a brunette just like its a blonde. I'm a brunette, but i dont talk to people like that. Its really rude!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small That kid looks so fucking done ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ he's like pls kill  me already I don't want people to think I'm related to this \textbf{woman} in any way\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small She is SOOOOO \textbf{dumb} nut SOOOOOOOOOOOOOO HOT\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Okay, let's get one thing straight here... not knowing something doesn't mean you're dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Dumb and ugly\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Why is some \textbf{dumb} blond bitch in my recommended videos?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small That's just called being a \textbf{woman}?! Wtf\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Title shoulda been Blondest \textbf{dumb} ever\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small FUCKING HELL THIS \textbf{THOT} \textbf{DUMB} AS FUCK\normalsize   & \cellcolor{green!27}Dumb, THOT & \cellcolor{green!27}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small Common core stuff.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small She's soooooo dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small " I'm listening to what you're saying but I only hear what I want to "....Host: " That's just called being a \textbf{woman} "...LOL\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small JoseJose Jose honey, just because you got yourself a degree doesn't mean you're smart enough to realize \textbf{sexism} isn't funny. My comment still stands. You can have all the degrees possible and still not know shit about the world.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small B*tch I'm not "imposing my beliefs" I'm being a decent f*cking human being. But being one of the b*stards who voted for an orange-faced clown, I'm not surprised you're an assh*le.\normalsize   & \cellcolor{green!5}B*tch & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Meghna R. Iyer you sure have a potty mouth for an " educated " \textbf{woman}. Obviously, you're the one who needs an education. Go ahead, scream louder...look up the sky! You are a total loser...so is Crooked Hillary!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Meghna R. Iyer so you hate white men? Are you \textbf{black}?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small JoseJose Jose not all of them of course, because I do know some decent human beings that are white and male. In fact I met a very nice white man who came to my house selling internet for AT\&T and he was very respectful to my grandmother who was sitting outside. I do hate the white men like you, though. And no, lmao, I'm not \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Meghna R. Iyer Calls someone sexists. Acts \textbf{racist}. Typical \textbf{woman} lmao. Are you all this stupid?\normalsize   & \cellcolor{green!5}Racist, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Meghna R. Iyer wow u are as \textbf{dumb} as the \textbf{woman} shown over here. Literally proving the point the anchor saidðŸ˜‚. The irony. Btw being sexist is "discrimination" on the basis of \textbf{sex}, which I don't think he did. If a simple tv show joke offends u, I'm sorry but your right-wing self-claimed righteous feminist world has a very weak stand. And yeah, hating and degrading others on the basis of \textbf{race}("I hate white men") is being \textbf{racist}. So basically he just stated a joke never degraded a \textbf{woman}, but u were \textbf{racist}. Very smart of you.\normalsize   & \cellcolor{green!27}Dumb, Race, Racist, Sex, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/97 & \cellcolor{green!27}7.216 \\  \hline
  \cellcolor{green!5}\small JoseJose Jose she's \textbf{Indian} I'm assuming. Cause i am and she's got a south \textbf{Indian} name. She's being annoying af though ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small There's no need to be sexist or \textbf{racist}. Let me just get this straight. The man in the vid said 'that's called being a woman'. It's plain stupid to assume all women think like that, since, like men, they're all different individuals with different minds and that's a fact. So obviously, because of that, it's also extremely rude to say such a thing since (by the man's logic) he assumes all women think alike. He probably wouldn't say this about men (I'm pretty damn sure about this). Thus he feels superior, while his statement was actually quite stupid.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small It is funny, shut your mouth and go \textbf{make me a sandwich}.\normalsize   & \cellcolor{green!5}Make me a sandwich & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Hahaha i find this funny even tho i'm a girl and i dislike \textbf{crazy} feminists they need to chill geezðŸ˜‚\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Meghna R. Iyer \textbf{gender} studies doesn't count as a degree \textbf{dumb} \textbf{dumb} get a real job\normalsize   & \cellcolor{green!5}Dumb, Gender & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Meghna R. Iyerpull up your just a feminist bitch ... I can guarantee your stereotypical of all other \textbf{dumb} women that bight over something so little hence you must cake on the make up to hide the real you...... and yep your \textbf{bum} is big real big in fact  your just a pathetic drama queen who dosnt get enough satisfaction from your vibrator   Ouch damn it jury is out for lunch  Jose  she is in pms mode 28 days of the month and she's a female trying to make out that she has some sort of intelligence or wit....... fail fail fail Meglamaniac you need to back up and probably try some new giant size d l o   and stop being a feminist bitch  you must be a white american if not wtf is your excuse\normalsize   & \cellcolor{green!27}Bum, Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Social Class - Destitute & \cellcolor{green!27}2/135 & \cellcolor{green!27}1.481 \\  \hline
  \cellcolor{green!5}\small Oath ken oath youve just hit the nail smack fucken bang on the head   shit and i wrote a bio to try and make a similar point ... lol so true though eh... they dont get laid probably got some stinky pinky thing going on aside from the big \textbf{bum} hell who knows ya just cant figure the stupid womenno man ahah i said figure not finger shhh she s probably lurking around the corner\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Wendelin The \textbf{Weird} that's the part you're concerned about?\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Pink Pikachu not \textbf{crazy} feminists, but don't you agree with the more calm feminists?\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Meghna R. Iyer BEGONE SOUTH \textbf{INDIAN} THOT\normalsize   & \cellcolor{green!27}Indian, THOT & \cellcolor{green!27}Ethnicity - Native-American, Gender - Female sexuality & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small ya know when your born the doctor smacks the baby on thee \textbf{bum}   well the reason for this is so that the cock falls off the stupid ones\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Danny D That's an \textbf{Indian} name. Translated to "girl of the clouds/rain/thunder". Her last name Iyer indicates she is from Southern India (states like Tamilnadu). She probably got/gets a lot of \textbf{racism} due to her \textbf{Indian} heritage and dark complexion (even amongst Indians south \textbf{indian} are specially dark), hence her hate for white people amd her hate for men probably comes out of the fact that her father had/has absolute control over her actions \& future (marriage, career etc).\normalsize   & \cellcolor{green!27}Indian, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/79 & \cellcolor{green!27}5.063 \\  \hline
  \cellcolor{green!5}\small Just me Who the hell are YOU getting involved?! ðŸ˜‚ Fuck off you \textbf{freak} lol\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small The British Patriot Obviously. The media is the responsible for driving things to this extent. Like it or not, they influence what people find acceptable to a large degree. By equating political correctness with moral correctness, they have managed to make innocuous things tabboo. Back then this would have been a joke some people laughed at and a few uptight people might have been offended over. But now those few would be given hours of coverage on some news channel and hailed as heroes for "standing up" to the evil \textbf{sexism} of the host. This blond \textbf{woman} would have likely been made into some sort of intellectual who was unfairly insulted by the host, who they would mention over and over is a white male. Its really sickening how low our society has sunk in such a short time (and I am referring to modern western society as a whole, not any specific country). But I have no doubt that this is \textbf{nothing} but a passing phase as people grow fed up with the censorship.\normalsize   & \cellcolor{green!27}Nothing, Sexism, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/175 & \cellcolor{green!27}1.714 \\  \hline
  \cellcolor{green!5}\small Fam, pull out your college degrees on us like that. But fucking understand \textbf{sexism} isn't shit to joke about. If you want to be sexist, go back to the 1800's. You might just get yourself fucked these days..\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb} but this being a 3rd grade question has \textbf{nothing} to do with it. The question is just trivia. Hungary is as about as known as Morocco, actually Morocco is probably more known, but if I asked people what the capital of Morocco is they probably would say Casablanca. They wouldnt know because they don't need to, and if they learned about it then they naturally forgot because who cares tbh\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Hungary, never heard of it like is she dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small "thats just called being a \textbf{woman}" and the little "oh" at the end\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Hungry? That's a country? \textbf{Dumb} blond\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small You all dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}." bitch -\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small i mean she is \textbf{dumb} but to be fair, i didn't know what country Budapest is the capital of if I didn't get multiple choice.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small ElEternoPoetaLuis I think she may be to \textbf{dumb} to follow a porn shooting schedule.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small my family members would never be this dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Angellapie I'm guessing your retarded like her... \textbf{dumb} bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Wow y'all sure are sexist. It's nice to see how many \textbf{pigs} there are in the world....much more than people know.\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small This must be staged, i cant beleive that any one can be that \textbf{dumb}.....Seriously!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Jerry the Trap Mouse \textbf{Jerry} the Trap Mouse first of all, why do you think he would be able to? Second of all, he can *try*. Third of all, if the country is really turning into people like you, I would actually appreciate it. But to be deported, you need to be from a different country, and I was fucking born here bitch.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small Meghna R. Iyer I bet you're a \textbf{freak} in the sack, too.\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Bigga Winna Crapsa damn that irish girl is \textbf{dumb} but cute af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Jerry the Trap Mouse how tho\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Meghna R. Iyer you are \textbf{nothing} a but sad weak ass \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Meghna R. Iyer - Is the \textbf{woman} in the video someone close to your heart?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Jerry the Trap Mouse - Great In bed, knows how to keep a house, cooks the finest southern dishes and knows how to build American muscle cars.\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Jerry the Trap Mouse lol\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Meghna R. lyer, welcome to the internet, where you can find an abundance rapey, horney, sexist men. You can't wish it away \textbf{hun}, just hope you never meet one in real life and if you do, THEN CHOP OFF HIS DICK\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small lolaminer5 I'm not a worthless fucking \textbf{faggot} so dick isn't something I'm remotely attracted to. Feed me with you ass and tits.\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small lolaminer5 \textbf{Make me a sandwich} bitch.\normalsize   & \cellcolor{green!27}Make me a sandwich & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Jonathan Lehmann. she is so \textbf{dumb} that she wouldn't be morr use tham a latex doll.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Jerry the Trap Mouse I'm having an ooze drop as I type damn I need to find this \textbf{chick} fine as hell!\normalsize   & \cellcolor{green!27}Chick, Jerry & \cellcolor{green!27}Gender - General, Nationality - German & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I'd be happy to let you know, \textbf{Jerry} the Trap Mouse!\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small That isn't sexist. pervert maybe not sexist. Not one thing in his sentence had \textbf{nothing} to do with \textbf{gender}, I mean couldn't a \textbf{woman} have said the same if it was a \textbf{dumb} but handsome man.\normalsize   & \cellcolor{green!27}Dumb, Gender, Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/36 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Please don't just us blondes based upon this idiot. People always assume I am \textbf{dumb} just because of stereotypes and fools like this one.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small "that's called being a \textbf{woman}"?? UH THIS MAN IS DUMBER THAN THE \textbf{WOMAN}!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Omg.......she's really dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small But she hasÂ a sexy, gorgeous body. I just wannaÂ  have \textbf{sex} with her, not marry her.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Cuz shes a hillbilly\normalsize   & \cellcolor{green!5}Hillbilly & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small So fucking \textbf{dumb}, all she will ever do is suck dick for the rest of her life\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small 'Kel... focus.' I was just like wow mate, you have high hopes for this \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small oh hun\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small She thought Europe was a country. Well it's not too \textbf{crazy}. some people still believe America is a country, too. lol\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small At first I thought this was calling her \textbf{dumb} for not knowing Budapest is the capital of Hungary, which I didn't know, then I kept watching\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Who cares! No matter what her IQ is, it doesn't change how her \textbf{pussy} feels around your cock!\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small She's totally an actress lmao she's way too \textbf{dumb} to be real\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small how much money did she get? And who is here \textbf{dumb}, excuse me?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Poor Nathan. He lost a couple IQ points just by listening to the \textbf{woman} speak.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small imagine someone made that "being a \textbf{woman}" joke in 2018\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Dumb blonde? Ha! Why don't you appear in front of camera and make you nervous? Fu\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small RACIST!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small "that's just called being a \textbf{woman}" ðŸ˜‚ðŸ˜‚ðŸ˜‚ I'M DYING!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small im \textbf{dumb} to....\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Fucking stupid bimbo\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small When the Turks occupied Budapest and the Holy League sieged them in 1686, cannon fire caused a wall of the Church of Mary to collapse. It turned out that an \textbf{old} votive Madonna statue was hidden behind the wall. As the sculpture of the Virgin Mary appeared before the praying Muslims, the morale of the garrison collapsed and the city fell on the same day. That night, HUNGARY had themselves some ROAST TURKEY.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small MY GOD THIS GIRL IS DUMB\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small "that's just called being a \textbf{woman}".\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Where's Laura Ingraham? The contestant is ill-educated, fer sure. She's so ill-educated I can't cease sneezing. That boy is headed to Princeton. And I bet he'll solely date brunets and \textbf{r\textbf{ed}} heads.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Not even a natural blonde. It's always the bleache blondes that are \textbf{dumb} ðŸ™ƒ\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small God this \textbf{woman} is a idiot.. really a idiot\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small One of the most cringy parts for me was that not even the host, representing the authority of this knowledge-based program, could get it completely right.Hungary, not "hungry".I mean it's easy enough to make fun of such a person as this \textbf{woman}, because she sets the bar that low (even the lowest \textbf{common} denominator can join in and point fingers, not much intelligence required). Another thing is to mess up when trying to pose as the "rational" and "intelligent" counterpart to such ignorance.\normalsize   & \cellcolor{green!5}Common, Woman & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small omg hungarian people hate to be called the hungrys so please stop it. (im hungarian by the way) \textbf{dumb} stupid \textbf{woman}!!\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}."That will be still savage when the sun has gotten cold.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Dumbest? Really I think ur the \textbf{dumb} one here\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}" savage af\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Eagle \textbf{Nation} T H O T S L A Y E R I N T E N S I F I E S\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small cats OMG lmao I'm American and I can't say anything about that. I mean I didn't even know the answer, because all we learn about is the US HisToRy, \textbf{nothing} else really..\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small This blonde is equally ignorant who those who assume that all women are \textbf{dumb}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small   xNobody \textbf{Nobody} cares about grammar in YouTube comments you fuckaty fucket\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Jeez, to all the people saying Americans are stupid for not knowing this, calm down. Yeah, she's a lot older than those kids and it's super embarrassing that she didn't know France was a country. But really?Most American school kids are learning other things during Geography/History/Civics. Most of it is about US history, but we also learn about other countries pasts' too. The thing is, the kids who learn the other capitals from around the world and other facts and stuff CHOOSE TO. Its not a required curriculum, so many choose not to. You'll meet a lot of people who's interested in different cultures and therefore, choose to learn things like that.Please don't get me wrong; this \textbf{woman} seems to have not gone to school in any way. Seriously, she thought Europe was a country -.-But don't group all Americans into a 'stupid' category because some Americans are. Every country has \textbf{dumb} people; that's just life. For some reason, it seems idiotic Americans are just publicized more.\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/170 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small I'm Canadian and knew these answers. We were taught geography/history of the USA and the world.I saw this show when it aired. I'm also an \textbf{old} fart. \textbf{Age} has \textbf{nothing} to do with it.\normalsize   & \cellcolor{green!5}Age, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!5}3/35 & \cellcolor{green!5}8.571 \\  \hline
  \cellcolor{green!27}\small +Random Name capital of Suriname is Paramaribo and no I didn't Google that either there's an app called memrise that helps you remember capital cities and also all the US presidents. Perhaps this \textbf{woman} should check it out\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small "Thats just called being a \textbf{woman}" lmao golden\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small She is not \textbf{Dumb}.  She made the right choice to "Copy" instead of answer.  Plus she is an adult, most kids will be superior with questions like this that are irrelevant to adults.  When you are currently a sponge soaking up all information and are actively studying these things you will be more knowledgeable.  However, none of this stuff is important to the working person so we let some knowledge get lost and replace it with practical knowledge.  The Blonde was smart enough to make the right choice.  I bet most people commenting on here didn't know the answer.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small U have a valid point. Knowing geography may define intelligence but Not knowing it doesn't make her \textbf{dumb}. If her career was based on international relations, she could definitely master it in  matter of days, but if it's not why would she? We make fun Americans for lacking bookish knowledge, but they own the smartest companies - Microsoft,\textbf{Apple}, Google, Oracle, Amazon.\normalsize   & \cellcolor{green!5}Apple, Dumb & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small Well I knew it was Hungary and okay yeah we so lose some info that's not relevant to us sometimes but to question whether France is a country or not is pretty \textbf{dumb}. I can just about  forgive her for never hearing of Hungary before but apart from that she's pretty dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Michael, not knowing geography doesn't make a person \textbf{dumb}.  Again, she actually made the correct choice for this show so how can that be considered \textbf{dumb}?  It would have been \textbf{dumb} for her to guess knowing that she didn't know the answer.  She clearly can retain information, but chose not to retain that one specific piece.  You can get through High School and College without knowing that information.  A friend of mine just recently took the US citizenship test and had to study 100 questions about US history.  Basic questions that all Americans learn in school yet when I quizzed my coworkers (all who have bachelor and/or masters degrees and were 100 born and raised in the US) on the basic history questions they got maybe 4 out of the 100 correct.  Why is that?  Is it bc they don't retain information or bc they chose to exclude irrelevant information that doesn't pertain to them directly.  I mean, you can always research that info so why fill your brain up with it?  Funny thing is I quizzed some of their younger kids with the same test and the young kids got all 100 questions correct.  Probably bc they are actively learning this information in school, while the adults learned it at one point and discarded it.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/216 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small KHALIL01, I think you missed the point...completely.  There are plenty of questions I can ask you that you would not know the answer to...plenty.  They would be basic and \textbf{common} to me, but not basic and very uncommon to you.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small ç«™åœ¨åå¯¹é‚ªæ¶é†’æ¥å¸®åŠ© - Europe being a continent and not a country is very basic knowledge for anyone with access to world news, a television,..What would you think if a \textbf{woman} of \textbf{o\textbf{r\textbf{iental}}} ancestry believed that Asia is a country?\normalsize   & \cellcolor{green!5}Oriental, Woman & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Gender - General, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}4/39 & \cellcolor{green!5}10.256 \\  \hline
  \cellcolor{green!27}\small Luca, are u serious?  Simply copying is the smart choice when you don't know the answer, but think the other person does.  How is that not the smart choice?  Also, not knowing a few specific things doesn't define intelligence.  Like I already stated, I quizzed my American born coworkers on the 100 questions for US citizenship and they only got 4 out of the 100 correct.  So they don't know 96 specific things, which means they are \textbf{dumb} right?  They all have Bachelors and Master Degrees BTW, but you would say they are \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/94 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small michael seagal Oh comeon, At third grade noone really knows the significance of geography. Do you think third grader would understand what differentiate capital city from other cities? But we learn it anyways just to get a candy or avoid punishment. When I personally learned to look the map, all I wanted to see was which country is  bigger and smaller than mine. Memorizing capitals wasn't fun and did it like mind controlled bots without ever questioning any significance. I was a champ A grade pupil. But there were few who just rebelled, didn't find any motivation to learn it. Yet they excelled somewhere else, some in sports, and some in other academia. If you call being able to be mind controlled bots intelligent, than I have no comment. Here she clearly haven't encountered the importance of Civic Science and she is \textbf{dumb} on it.  But she is able to read, express herself, probably drive and probably has raised her kids.Seriously if my Kid tells me he doesn't want to put the geographical lists on his head to make room for something he values, I will say he doesn't need to and I dare anyone who judges him based on his knowledge of it.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/205 & \cellcolor{green!5}0.488 \\  \hline
  \cellcolor{green!27}\small KHALIL01, to answer your question I propose another question.  What would you think if people who were born and raised in the US and had their Master's Degree were only able to successfully answer 4 out of 100 questions pertaining to their country's history that is taught in elementary school?  Then a person who is not from their country studies their history in order to take the citizenship test and is able to answer 100 of those same questions accurately?  Are the Americans in this scenario stupid and the foreigners smarter? This is a true scenario BTW.  Should we judge the Americans intelligence based on their severe lack of knowledge of elementary school history or on the fact they have their Masters Degrees from an accredited University?  Are they \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/130 & \cellcolor{green!27}0.769 \\  \hline
  \cellcolor{green!5}\small robert smith beauty is \textbf{nothing} without brains\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Abe Laban  She didn't know a few questions... Can't determine someone's intelligence from that. That's just stupid\normalsize   & \cellcolor{green!27}Abe & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small All blondes are not \textbf{dumb}, but all of dumbs are blonde\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small That's JUST CALLED BEING A \textbf{WOMAN}????!!-??Screw you from all of us vaginaly \textbf{disabled} people.\normalsize   & \cellcolor{green!27}Disabled, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Omg there just so happens to be a blonde in my geography and she's EXACTLY like this. The teacher asked this question: 'What do countries such as Brazil, Russia, India and China have in \textbf{common}?' Her answer: 'They're all \textbf{black} people!' tHEy'rE aLL \textbf{blACk} PEoplE! And he's like: 'â€¦Yes, I'm sure there are no white guys - like Putin for example - in Russia.'\normalsize   & \cellcolor{green!5}Black, Common & \cellcolor{green!5}Ethnicity - Black, Social Class - Working class & \cellcolor{green!5}3/64 & \cellcolor{green!5}4.688 \\  \hline
  \cellcolor{green!27}\small Cody King that's what make her \textbf{dumb},  she doesnt even know france is a country, you should have heard about that country once or twice in your life even if you dont live in town\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small reminds me of an \textbf{African}-American \textbf{woman} on the radio one day who got into an argument with a talk show host claiming Africa was a country. the more he tried to explain it was a group of countries, she more she disagreed. then he offered her money if she could name 10 \textbf{African} nations, and she could not. She called him a \textbf{racist} even after he confessed to having adopted two \textbf{African} children from Somalia. Then she insisted Somalia was not Africa and vice versa. You can't argue with ignorance.\normalsize   & \cellcolor{green!5}African, Racist, Woman & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Gender - General & \cellcolor{green!5}4/90 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small top text bottom text Cry, \textbf{fat} boiii\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Not because you dont know something doesnt mean u are dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small If it does then look at a new born baby and call the baby \textbf{dumb} and look at the mirror, get it? Ur \textbf{dumb} for calling ... nvm\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Johb D.Forg A baby isn't \textbf{dumb} because it barely had time to learn. Also your English is trash.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small top text bottom text, North Americans think America is a country(when it is not. It is two continents: North America and South America). This \textbf{woman} is no different. In fact, she is the the example of the stereotype that North Americans do not know what a map is. But yes, that is the level of stupidity that North Americans have.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small and that was when I knew she was really that \textbf{dumb} and above all the \textbf{dumb} things in my life that I've seen.. THIS VIDEO takes the cake!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I have felt that i was THE DUMBEST person in the world....But when I put myself to this \textbf{woman},I feel like I'm GOD ðŸ˜†\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small american people are so \textbf{dumb} wtf, its general knowledge. you can know geography and science\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small America's education system always seems like \textbf{nothing} else than one big idoctrination party about how they are the best. What I always makes me Laugh is when they say they are better than every other country or \textbf{nation} not realising they are just one big mix of the worlds populationFucking dumbasses, some smart People in there but it seems like mostly just dumbasses\normalsize   & \cellcolor{green!27}Nation, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small +DxrkQueen TV Same. I knew Europe was a continent, France was a country and Paris is a state. That's \textbf{common} sense.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Look they have a moron clown as president .... this is nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Why would a person who is that \textbf{dumb} get on National TV and make a fool of herself, unless she was being paid good money to appear on the program.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Jeff is just like you \textbf{dumb} bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Stupid american trailer trash\normalsize   & \cellcolor{green!5}Trailer trash & \cellcolor{green!5}Ethnicity - White, Social Class - Working class & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small 'I'm listening to what you're saying but I'll only hear what I want to hear.' 'That's just called being a \textbf{woman}...' SAVAGE ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small So fucking dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small aren't all blonde \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Shes a hill billy and a thot\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small what the fuck this \textbf{chick} is dumber then a jar of dirt and she almost won \$25,000??\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Begone thot\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Dumb like a fox.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Just because she is blond does not make her dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb} as a post and the first thought half of the people in here express attraction. And people wonder why stupidity is rampant. Answer:  poor breeding selection.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small "sooo ehm \textbf{woman}? what do you do for a living?""Soo ehmm... there is this really nice guys i think he is an youtuber.. he is paying me to make fake gmails and subscribing his channel"\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small OMG SHE'S SO \textbf{DUMB} IM ONLY 11 AND I KNOW 10190478384753452345 TIMES SMARTER THAN HER\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Maybe she has disleksia (idk how to spell it, sorry). But she's porbably dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small She made me dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small ClichÃ© of a blonde American woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small 'that's just called being a \textbf{woman} ' are you serious? What a sexist jerk.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small HUNGARY \textbf{WOMAN}!!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small That's a new slapper\normalsize   & \cellcolor{green!27}Slapper & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman} " ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Oh my gosh! How does this \textbf{woman} find her way home at night?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small dumb fucks americans\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I feel \textbf{racist} now\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Sara Keng Don't go roasting people when you sentence has errors in it. For example, it should be want not wants. Also don't start your sentence off wth and. Another thing it's blonde not blond. Finally people can do whatever they want, not every blonde is \textbf{dumb}, it's just a stereotype.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small If you think your hair color seriously would determine your IQ, than YOU'RE the \textbf{dumb} one.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small No Asian wants to dye their hair blond! None! Except \textbf{dumb} ones who don't know that they looke good with \textbf{black} hair.\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Meghna R. Iyer Fact is asians look good with \textbf{black} hair\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Meghna R. Iyer They look better with \textbf{black} hair and dumber with blond. I just said it and now I say it again. And again one more time.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small You realize that Europeans and Americans dye their hair blonde too? Hell, even natural blondes dye their hair to different shades of blonde.I've met many blondes (both dyed and natural) who aren't \textbf{dumb} at all, so I don't think anyone should feel like a fool for having a hair of certain colour.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Okay but can we talk about how sexist his comment about "this is just being a \textbf{woman}" was? She's stupid okay, but he's not far.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small And this is why people think all blondes are \textbf{dumb}...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small This is fucking a stupid \textbf{dumb} blond\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Kelly Pickler playing the \textbf{d\textbf{umb} blonde} again, it gets \textbf{old}.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde, Old & \cellcolor{green!27}Age - Over 65s, Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/10 & \cellcolor{green!27}30.0 \\  \hline
  \cellcolor{green!5}\small She ain't \textbf{dumb}. She's high.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small "That's just being called a \textbf{woman}." Lmaoooo\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Weird Person I hope you agree that's a good thing. \textbf{Sexism} isn't funny. It just makes men look \textbf{dumb} as f*ck. :)\normalsize   & \cellcolor{green!5}Dumb, Sexism, Weird & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/22 & \cellcolor{green!5}13.636 \\  \hline
  \cellcolor{green!27}\small Duke Sonic please get an education. It's the law in America, so I don't know why you don't have one but \textbf{dumb} is not a pretty color on you.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Is no one gonna talk about the 'that's because you're a \textbf{woman} '????\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small This lady is so \textbf{dumb}!ðŸ˜‘ðŸ˜‘\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Why is \textbf{nobody} talking about 1:05 "that's just called being a \textbf{woman}"? It's sickening to see that the audience laughed.\normalsize   & \cellcolor{green!5}Nobody, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small sorry but how can you be so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Thats just called being a \textbf{woman}, about 2 read the feminists in the comments rage\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small How did she even make it to that \textbf{age} without doing something stupid\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small gito and mito doesn't look cute on a \textbf{black} girl.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Jesus Christ.....Even A Fucking 12 year \textbf{old} is smarter\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Technically, this tests knowledge and not intellect, meaning we don't know for sure if she's actually \textbf{dumb}. But I mean, I knew the answer instantly and I forgot just about everything that I'd been taught in geography in school. I still don't blame her for not knowing the answer, but she should have known Europe was a continent. And also that France is a country.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small If u r so f \textbf{dumb} do show on TV\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small waaaait \textbf{hun} bun. did he just fucking say ''thats called being a woman'' when she told him ''i only hear what i want to''\normalsize   & \cellcolor{green!5}Hun & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Wow she is so \textbf{dumb} France is a place united States is a country Russia is a country Philippines is a country Hong Kong is an important city\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Gigg Jsjeb Accents have \textbf{nothing} to do with intelligence.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Wtf did I just watch That's not what they said. It's like a Geordie saying these things would make it just as \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Steel Xcaliber No, that was what they said, accents have \textbf{nothing} to do with intelligence, like the commenter was implying.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Michael Von Patrick IV He is right though. English sound more proper. All I hear people say (even in the west north east etc.) Are stupid shit. Of course I know accents has \textbf{nothing} to do with it but society has lead us to believe that the way people sound associates with intelligence. Many know this though...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Yea we all know it's okay to stereotype the south because of jewish Hollywood movies. But only if they are white southerners. Go hug a transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small ThAtS JuSt CaLleD BeInG a \textbf{WoMaN} HAHAHAHAHAHAHAHAHAHAHAHHA\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Dumb people always come onto game shows because they are too \textbf{dumb} to get a job and get money, but then they don't realise they actually need half a brain to answer the question.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Woman:"Like Im listening to what you are saying but I only hear what I want to"Show host:"Thats just called being a \textbf{woman}".......well then.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small And i thought I was dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Girl:"I'm listening to what you're saying but I only hear what I want to ."Host:"That's just called being a \textbf{woman}"ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ I'm dying... ðŸ¤£ðŸ¤£\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small 100 \textbf{dumb} to live in the western country,even asian people know hungary..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She \textbf{dumb} but fuck she's hot\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small she's not stupid , she's being racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Man blinds are not \textbf{dumb} Steven Hawkins was blond and you probably blond to so that's saying your dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small It's not a fake bro, unfortunately. Yes, it is a show, but there are \textbf{dumb} people like that. There are even people who think that the earth is 2018 years \textbf{old}.\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small ahmar shad no it isn't you \textbf{dumb} fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Come on no one can be that dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Kacl - ugh I'm Hungarian as well and those types of jokes are so \textbf{old}.Like I'm not offended by it,it's just annoying really...\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Damn , thats is the reason why people are stupid enough to believe in media. Cause they dont study , like this girl . Who doesnt know the european history . Europe is full of cultures , language , \textbf{ethnic} and religious .\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small these type of girls suck dicks for 1 buck\normalsize   & \cellcolor{green!5}Buck & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The official dumbest of the \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small A \textbf{dumb} brown haired \textbf{woman} >> "dumbest \textbf{woman} ever"BUT A \textbf{d\textbf{umb} blonde} \textbf{woman} >> "dumbest blonde ever"\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde, Woman & \cellcolor{green!5}Gender - Female intelligence, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/18 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I assure you we Americans aren't all this \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small " Hungary that's a country?? ... I heard of turkey but Hungary never heard of it " she sounds like she southern part of America .How the hell she got into the show I have no idea she so \textbf{dumb} even the kids could not hold in the laughs.lol\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Dumb as a jockstrap.I'd still plow her till Christmas day though.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Cancer is my gender\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Evelin NOT HUNGARY NOT HUNGRY! IT IS THE SONS OF ATILLA THE HUN\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Nobody has ever heard of this country\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Hi didly ho\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Aren't all blondes \textbf{dumb}?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small = us \textbf{hillbilly} education system (:\normalsize   & \cellcolor{green!27}Hillbilly & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Blonde has \textbf{nothing} to do with it. She's from the south, they don't have schools.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Have you seen Pupina Stewart? I think that's her name. Anyway, she is really \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small You name that \textbf{dumb}? In my country a girl answered with Rrrrrusia for Uk's capital at a miss party. Say no more.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small If she looks like an anti social introvert who only talk to someone once in a month then i wouldn't call her \textbf{dumb} but she's obviously someone who's outgoing and highly social human being. It's probably a paid actress.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Darth Fryed what's the difference between nice and stupid. This guy is trying to say his mum is stupid and ur comment says she is nice which does not make any sense. This is because your comment is not related at all to what he is saying. This dum, I mean \textbf{dumb} \textbf{chick} in the background might also be nice but it does not mean that she is smart HINT HINT\normalsize   & \cellcolor{green!5}Chick, Dumb & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small She is not \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Sexist. Just because she's \textbf{dumb}, doesn't mean all girls are\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small well both are \textbf{dumb} cuz he doesn't even know how to pronouce Hungary\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Is \textbf{nobody} gonna point out that sexist comment? ðŸ™ƒ\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dumb or just American?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I hope this \textbf{woman} finds herself a man before her looks check out\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small big ol \textbf{fat} trump fan fo' show.....\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Isn't this what every blonde American \textbf{woman} is like?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I have actually met more \textbf{dumb} brown haired people than blonde haired people.Studies show that blondes are averagely smarter than other caucasian haircolours.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small COMMON CORE LADIES AND GENTLEMEN!!!!!!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Jeez how rude, she's not \textbf{dumb} she's uneducated there is a difference\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small That's one \textbf{dumb} bitch right there\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small She is \textbf{dumb}, but very cuteâ¤ðŸ˜\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small She might not have a clue about geography but I bet she has a Degree in \textbf{sex} positions!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Sisi TheOne people have \textbf{sex} with toys. What's wrong with it.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small mermaid 7 how?? He didn't refer to her \textbf{gender} being the main cause of her knowing \textbf{sex} positions but rather the fact that because she lacks skills in smarts that she would be more skilled in other areas plus it's a reference to the stereotype of hot \textbf{dumb} blondes.\normalsize   & \cellcolor{green!5}Dumb, Gender, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Sisi TheOne Cause she's gorgeous. I won't have debates with her. But I certainly will have \textbf{sex} with her.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Don't  say that she is \textbf{dumb} person. She has never learned it. Different education.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small yingkou Xiong \textbf{Dumb} - Adjective - Having or showing a lack of intelligenceShe's pretty much the definition of dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Nobody deserves to be called that no matter what. I'm sure if someone recorded u having a brain fart or being \textbf{dumb} for a minute and then posted it on youtube, u wouldn't like it either.\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small yingkou Xiong I know you're trying to be nice but how does a person her \textbf{age} think Europe is a country\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small we get ur trying to be nice but she is kinda the definition of \textbf{dumb}. she lacks intelligence. yeah maybe she never learned what budapest is the capital of but she didn't even know that europe is a continent. that's just \textbf{common} knowledge.\normalsize   & \cellcolor{green!5}Common, Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small you stupid ass you know she can have her own opinion so stop trying to call her out \textbf{dumb} ass and she can think what ever SHE WANTS LEAVE HER THE FUCK ALONE\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small yingkou Xiong That is one strange school she went to if she thinks Europe is a country, like seriously all her answers made her sound like she dropped out of school at the \textbf{age} of 5. You can have your own opinion, but if your like 20 or whatever and can not tell what Europe is then you should definitely head back to school.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small   xNobody in Texas, \textbf{nothing} is possible in education\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small yingkou Xiong im not going to sit here and pretend she isnt fucking \textbf{dumb} because its not nice, because shes fucking \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small yingkou Xiong this more than a brain fart, most people even if they haven't done geography at school would know Europe is not a country. She is the definition of \textbf{dumb} and you need to get your head out the clouds\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small stop trying to point out things Retro or should I say retarded because you the fucken \textbf{dumb} bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small gabrieldarkr apparently from what you are trying to say is that you must be related to this certain \textbf{woman}... At least I can give a better answer than this \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Kacl - No. Beeing \textbf{dumb} and uneducated are two different things.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small yingkou Xiong I've suffered two minor strokes, and when I have brain slips (nowhere near as bad as this idiot) I call myself a fucking dumbass. Calling her (and you, apparently) \textbf{dumb} has \textbf{nothing} to do with making myself feel better.\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Dumb, blonde, and pretty, is she married? Lol\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Kenneth Drewary Yeah LOL it's almost as if beauty and no brains is all a \textbf{woman} needs to be 'okay' and 'suitable for marriage'! Haha. Lol. \textbf{Sexism} is just so funny.\normalsize   & \cellcolor{green!27}Sexism, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Do you think you can do better ( person who posted this ). We all learn and become smart No has the right to judge nor call someone \textbf{dumb} .Instead of making a  difference you are  busy  degrading  and undermining  people i beg find your true purpose take it or live it same applies to everyone\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small I think they call blondes "\textbf{dumb}" because they often dye their hair to achieve the color, so that they are more attractive.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small She's \textbf{dumb} AF\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb}, what about people hundreds years back?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Blonde's hair darkens with \textbf{age}. 95 of blondes over 20 have dark roots and keep dying their hair blonde again\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Dumb shit\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Dumb fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I'm SÃ¸ Dun u look \textbf{Indian}. Are u?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Unfortunately it's the latter...how do people become this \textbf{dumb}? Honest question here.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb}, many people don't learn about European geography until older ages. Wait, maybe I should watch the video more.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small how \textbf{old} is she?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Typical white chick\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small This is either world class trolling or she's just plain dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small If she breathes, she is a \textbf{thot}!\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Adrienn Dobsa that's \textbf{old} foolðŸ˜‚\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Actually, many aliens are living on this planet. They all have human or animal form. I know it because I'm an \textbf{alien} myself.\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Glorious UdSSR Nope, I'm an \textbf{alien} in human form.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small GD JuryJohn if that's true then where did you land on Earth?How did you get here?Did you come alone?Are there any other \textbf{alien} species that look like humans?How would you sum up humanity in short?It's unlikely that you're actually an \textbf{alien} but only you know for sure so might as well ask\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small WhatAJoker, thank you for your questions. 1. We started landing in Africa, but spreaded around the Earth very quickly. 2. We got here by the big meteorite, who killed the dinosaurs. 3. No.4. I don't know. I know only one, and that's us.5. About 5-10 of humanity are aliens. We are separated from humans by our \textbf{weird} opinions, smartness, and interesting hobbies. Humans, don't worry, our \textbf{alien} species are peaceful (mostly).\normalsize   & \cellcolor{green!5}Alien, Weird & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small Guess what .. she's a blonde and \textbf{DUMB}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I ate 10000000 tide pods and drank a lot of bleach after watching this. She is so \textbf{dumb}! WTF\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Blond ppl aren't \textbf{dumb}. It's just this girl and some others, everyone gotta stop judging ppl bc of there hair especially if it's a dye jobðŸ˜‚\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I understand that the "blondes are \textbf{dumb}" is a stereotype, but this \textbf{woman} is just stupidBaka southerner\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Everyone is \textbf{dumb}... even I don't even know some of the questions ðŸ˜‚ðŸ¤£\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Its always the \textbf{dumb} ones that get the chance because of there looks\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That was so stupid I'd say it was a scrip but she really did seem that \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Ffs on a scale of 1 to 10 of \textbf{dumb}, she takes the scale past ten.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Thats just called being a \textbf{woman}oh\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I was like, how is it \textbf{dumb}? But Europe is not a country.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small "I THINK THIS IS A \textbf{DUMB} QUESTION"I think your dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small And people wonder why there's a stereotype of people down south being \textbf{dumb}...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Boy:this bitch is \textbf{dumb} af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Blondes on average have higher IQs than people with any other hair color. This whole "\textbf{d\textbf{umb} blonde}" thing does not even make since. Ya, she might be \textbf{dumb}, but she is only one person, not all blondes. Who even knows if she's a natural blonde.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Something 109 you learn some grammar dumbass! You're telling this \textbf{dumb} bitch in the video that she's \textbf{dumb}!? When you're own the way of speaking is poor! Therefore, you're clearly one to talk!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small I did not notice anything improper about my comment. I may have left out a comma or two, but that does not make me \textbf{dumb}. I am not even blonde, though a higher IQ might be nice!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Dumb af\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small The kid was even laughing at the \textbf{woman}.PATHETIC\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small that is.....that's just unbelievably \textbf{dumb}, like WOOOOOW she thinks europe is a country she isn't sure if france was a countryand i swear when i was 14 years \textbf{old} i was able to name every single country in the world and point at it's location on the mapanyway, she represents the blonde stereotype in an unbelievably perfect way\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small She is so fucking dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I was like that's not \textbf{dumb} I'm in middle school and I don't know where that is but then she said she thought Europe was a country and I was like ohhhhhhh\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small I hate the title: Dumbest Blonde Ever Why does it matter if she's blonde? Why not 'Dumbest \textbf{Woman} Ever'?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She is so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small She is an actor guys no one is that \textbf{dumb} she was paid to do this\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Tom Spotted THOT\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small jake paul is not \textbf{dumb}, he's the best person ever <3jakepauler4ever jakepaul\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Soffe Cruz you're obviously a 10 yr \textbf{old} idiot\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Soffe Cruz I love puppies, but hate \textbf{dumb} kids who are naiv and like the shit Jake and Logan post\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I don't know the capital!Who learns this stuff?But this \textbf{woman} is fricken dumb\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small She is \textbf{dumb}! But please don't categorize all blonde to this.I have \textbf{black} hair.\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Wow. What a brilliant show of wits. Briefly saying out that Europe was a country and seeing how she didn't think of Paris when she said France, and knowing that Europe and France existed but never heard of the country Hungary. What a great show of intellect. A big round of applause for this (presumably) Australian \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small That's called being a \textbf{woman} lol\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small lol ur so \textbf{dumb} Europe is a state in Texas\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small this is just \textbf{common} sense dude\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small And I thought I was dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Ummm...Europe is a CONTINENT you \textbf{dumb} bitch!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small its pronounced \textbf{hun} gary not hungry\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I facepalmed my face so hard the whole time like how \textbf{dumb} can you geeeeeetttt\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small This women \textbf{dumb} as fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small What an idiot like seriously hungary thats a country?! Wow i heard turkey you know dumbass a two year \textbf{old} kid is smarter then herðŸ¤£ðŸ¤£\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small -"I'm listening to what you're saying but I'm only hearing what i want to hear- that's called being a \textbf{woman}- oh ok"WTFFFF\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small That's just called being a \textbf{woman} ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I'm from Europe. I thought it was bad she didn't know that stuff, but honestly not as bad as what the fucker said; "that's called just being a \textbf{woman}". I mean..what the fuck\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small I bet the \textbf{woman} would just ask at this point; what are brain cells? Are they mini cell phones in your head?!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Okay for you and the \textbf{dumb} audiences to know.... Europe, South and North America, Asia, Australia, Antarctica and Africa are the seven CONTINENTS. Seriously? That's some of a 3rd Grader lessons. Go to school or something....\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small That's just called being a \textbf{woman} LMFAO\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small omg she is so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small She is \textbf{dumb} as fuck Jesus Christ\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small She is the reason blondes are labeled as dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Dumb woman:i thought europe is a country.Me:(â•¯Â°Ð”Â°)â•¯ â”»â”â”».\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Dumb sack of stupid\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Wow. She is so \textbf{dumb} like omg. She needs to go back to school\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Omg she's so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She is \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small But she's too skinny\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Super \textbf{dumb}, even dumber than the meaning of \textbf{dumb}, even dumber than that too, and it goes on\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small She's so cute I don't care how \textbf{dumb} she may seems .\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She may be \textbf{dumb}, but she's super duper sweet. Gosh, what a cutie! ðŸ˜Šâ¤ï¸\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Definitely not the kind of \textbf{woman} people should flirt with\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The pure definition of a bimbo\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small "Thats just called being a \textbf{woman}" OOOOOOHHHGGGG\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small is it bad if I didn't know where Budapest was either? the only way I knew it was from the 1st Avengers movie in that conversation between Hawkeye and \textbf{black} widow..\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small wtf why r ppl so retarded I swear this is the reason why the aliens haven't come to earth to give us new technology, because they know that \textbf{dumb} bitches would misuse this for nail polish or something\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small OMFG!! \textbf{Dumb} Texan blonde.... Tsk tsk tsk.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Me as Slovenian I don't think I am smart for usa. I know where is Miami, New York, California, Chicago, then I know there there are states Texas, Atlanta but I don't really know where they take place.. I am \textbf{dumb} for them, too, I guess. But hello, my neighbour! :D\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Dumb Blonde: 'Hello, can you help me find my mind? I think I lost it.'\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small She's putting that on, \textbf{nobody} is that dumb\normalsize   & \cellcolor{green!27}Dumb, Nobody & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Damn!! She's dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small King Ang she just died her hair to look \textbf{dumb} :D Or to match the stereotype whatever\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Ever think that maybe it's not that blonde people are naturally \textbf{dumb}, but that \textbf{dumb} people generally dye their hair blonde, trying to get by on looks since they don't have brains?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Jakk Frost Yes, thank you! That's where the stereotype comes from anyway because in world war 2 tons of women dyed their hair blonde so they were called dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I think that's mean to call her \textbf{dumb}... Who else thinks that?\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Thats just being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small It's a fu**in setup she can't be so \textbf{dumb} like seriously FRANCE, TURKEY..IT'S FUCKIN HUNGARY!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small She is a \textbf{woman} of European descent and doesn't know if Europe is a country or a continent.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} has blessed/cursed my Hetalian mind with the image of all of the european countries as one person.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I didn't know where was boodapest located so I thought I'm \textbf{dumb} as well but when she said "Is Europe a country?" I realized that she's Nick Comptons long lost \textbf{skinny} sister\normalsize   & \cellcolor{green!27}Dumb, Skinny & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small The bitch is crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Dumb muricans\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small just watching this \textbf{woman} makes me angry\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small after all the \textbf{dumb} shit ive seen for years after watching this, then come back to this vid and she still the dumbest person in this world. slightly dumber than the feminists\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Dumb enough to have her own show.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Did she seriously thought Europe is a countryMan she is dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small So dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small She's really dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small god she is so \textbf{dumb} like most Americans\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Ty Marshall and you are \textbf{dumb} as well. The children participating in this show are Americans and they knew what Budapest was, so are you calling them stupid, too? I've met British people who don't know geography, either.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Ty Marshall  what!! you're sorry for what happened in Texas we're just \textbf{dumb} Americans. Well thanks for your condolences\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small This is fake at this point. Seriously. You people are dumber than she is being for not realizing that. Do you seriously think a full grown \textbf{woman} who doesnt know that Europe is a continent?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Wow, she is \textbf{dumb}..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small IT'S NOT HUNGRY! IT'S. NOT. HUNGRY! "Hungry like I'm hungry." NO! \textbf{HUN} GA RY! goddamn I'm sorry I'm so worked up over that, but I AM from there, and it sucks so much when people as me if I'm hungry. - -\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Wonder how many people are triggered by that \textbf{woman} joke\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small PizzaIsLif3 YT Right??Im pretty sure alot of us dont know the majority of the map and there are people calling her \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Well then I suppose that she had him when she was ten years \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small All Americans are \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Comment section is just as \textbf{dumb} as she appears to be. That is a fucking actress, this is entertainment, not reality. Wake up.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Why this 7 year \textbf{old} vid on my recommendations now? Is it cos of jake paul?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small That's just being called a \textbf{woman}! OMG\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Is this for real or this \textbf{woman} pretented to be \textbf{dumb} ? I mean, ok, maybe she didn't know Budapest is the capital of Hungary, but to mistake Europe for a country is unacceptable.\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small When a \textbf{bimbo} cant do the limbo\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small its not the blond whos \textbf{dumb} its the entire population of the US\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small focus.i am but i only hear what i want to.thats called being a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small what a \textbf{d\textbf{umb} blonde}And i never thought EUROPE is a country\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Whose calling people \textbf{dumb} blonds ? Ha ha ha\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small She may be \textbf{dumb}, but I'd still do her.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Ummm I didn't know the anwser to that question either so I guess I'm \textbf{dumb}Lol â¤video\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Dumb as f\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I thought white people are smarter than Asians. This \textbf{woman} showed me that Asians are smart (maybe, some of them aren't but, most of them are).\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I found my self here after watching an \textbf{apple} ad\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Lila Willow There's different types of anxiety. To say 'I haven't experienced it on the same level,' is just based on assumptions.I have trouble sleeping at night because of things I did, years ago, that are stupid. I shake when I speak in front of my class, and sometimes I stutter. People always ask me things like 'why don't you talk?' Or similar questions. I don't know how bad your anxiety is, but the point is, that this \textbf{woman} wasn't anxious, but just blatantly ignorant.In fact, I'm pretty sure she's a country singer. If you have social anxiety, that's a really poor career choice.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small Lila Willow Oh My FuCkInG sWeEt PoSeIdOn. Are you serious? Yes sure anxiety makes you freze but this \textbf{woman} doesn't have anxiety attack. She is just extremely uneducated. Don't justify her with \textbf{mental} illness. That's pathetic.\normalsize   & \cellcolor{green!5}Mental, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small She's so \textbf{dumb}, it's cute!!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small back in the days when \textbf{dumb} ppl were funny before antifa and sjws\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Funny it seems like all \textbf{dumb} blondes are in reality natural brunettes who dye their hair to get the blonde looks. Lol\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Anybody Hungary for that \textbf{pussy} tho\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} is why Americans are considered ignorant and stupid.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Why is it called dumbest BLOND ever like all blondes are dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "That's called just being a \textbf{woman}" ðŸ¤£ðŸ¤£ðŸ¤£ðŸ¤£ feminists triggered!!!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small satorange That's radical third-wave feminism or mysandry. \textbf{Nothing} to do with the feminism that actually matters.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Jonah Safern lol there's only 2 guys at my school who are in the top 10, the rest are girls, it really depends on the person and whether or not they are willing to learn, not on gender\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Jonah Safern Women are smarter I would say but it is not about \textbf{gender} but about \textbf{race} and all that.\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Noob Slayer What you just said makes \textbf{zero} sense.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Instead of having a civilized discussion with factual arguments people are triggered because a person said something politically incorrect. Even I - as a \textbf{woman} myself - don't have any issues regarding that comment. What a shame.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small and thus, the phrase "\textbf{d\textbf{umb} blonde}" was born...\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Typical \textbf{dumb} Americans\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small - Like im listening to what youre saying but i only hear what i want- Thats just called being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small I only listen to what I want to, That's just called being a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Thats just bein a \textbf{woman} oh my god ðŸ˜­ðŸ˜­\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Wensley Eveillard Don't you mean the education of the United States? Ironic how you're insulting our education system on a video of Are you smarter than a fifth grader a show with children from the United States who are in college but are ten years \textbf{old}. Lastly if you are going to be a quasi- intellectual I implore you to not type like you don't know the rules of grammer in the english language.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small But America is very \textbf{dumb} compared to other countries. I comr from Belgium and from Germany so shut up stupid Americans.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small asmith121 Oh sry i'm just 14 years \textbf{old} but still better than Americans. Oh yes and compared to Germany is America a \textbf{dumb} shithole, you fatass.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Wensley Eveillard What do you know about it? American English isn't English, it's just a bunch of shit.    Can you talk German or French, or something else? No, you're American, you can't even talk english. You know \textbf{nothing} about me, or about Europe. That's just America= selfish, arrogant and they think they are the greatest! Go back to your "school"\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small American English originated from Britain but like another language the way we read and write alters throughout the years even German  the U.S.'s english is different because of the influences in the different regions such as Spain Frence and the Dutch which I'm sure I already since you have an amazing education just like creole is a mix four \textbf{African} languages english and mainly french and in Haiti their a two was of speaking just like in American their are different was to speak depending on your state and the spanish is an even larger example of languages having variety based on region but I'm sure you already know that with your AMAZING EDUCATION ðŸ˜ƒðŸ˜ƒðŸ˜ƒðŸ˜ƒðŸ˜ƒðŸ˜ƒðŸŽ“ðŸŽ“ðŸŽ“ðŸŽ“ðŸŽ“\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}\small Geral dro Your grammar is terrible... There is a grammatical error in every comment you have made. Take your \textbf{Nazi} self out of here and go commit grammar genocide somewhere else.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Geral dro how do Germans speak better English when its not even the countries main language? That make \textbf{zero} sense...\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Geral dro you are one of the biggest trolls I've ever seen. You probably arent even German, just some random 12 year \textbf{old} trying to start stuff so he can tell his little friends about it.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small That \textbf{woman} is the perfect representation of the US educational system prove me wrong ðŸ…±ï¸\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Geral dro lmao.1.boi who let you make a youtube account.2.ðŸ’€ðŸ’€ðŸ’€Yes like we gunna spend 24/7 insulting a place we don gAF about. We to busy "being \textbf{dumb}."\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small evokki0075 Yes because everyone was so happy donald became president.I'll give you one thing.Trump IS president b/c ppl like that \textbf{woman}.Yet there are others you do not need to drag into this mess.Learn about those who've protested his nonsense before you SPEAK. Get ur facts straight.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small David Hopscotch or as a \textbf{woman} lol\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Jake Paulers are going to be \textbf{doctors}, teachers, and other jobs essential to our society. we are fucked\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small And a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Briana Daya No. Women are bitches. Don't you here men say "I love me some bitches" but women don't say "I love me some bitches" (referring to men). Lol, bitch, just suck our \textbf{fat} dicks.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Wtf did I just watch hahah gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small Transgender\normalsize   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Americans are so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small BOB PLAYZ We're called United Statesmen,\textbf{dumb} is the inability to speak and end your sentence with punctuation.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb} because she's blonde she's \textbf{dumb} cause she's American!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Christopher Mclaren She's from the United States and \textbf{dumb} means the inability to speak.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Nick T omg stfu you can't roast you fucking 9-year old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Dylan Coppin also they just ended the \textbf{weird} as crap conversation\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} seems like a classic Trump supporter.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Some Gaming Because language is developed at very young \textbf{age}, around the 2nd year of a human life, the mistake FF THECRAFTER made was probably a mistake of translation from his language to english; After all, not changing singular noun to plural one or singular verb "to be" to plural verb "to be" is, to be honest, a slightly big and for someone from US/UK it would be an unimanigibly huge mistake. So, please, think before wrting critisism   \normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small Sir KaÄer you should probably check out some of his videos and see if he is above the \textbf{age} of 12\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small At least she wasn't \textbf{dumb} enough to lock in her answer!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small We just haven't learned about this but........ I'm not as \textbf{dumb} as this.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small If he made that \textbf{woman} joke in 2018 that man would be hung by nightfall.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Seriously. For anyone to say that a person is \textbf{dumb} for anything is \textbf{dumb} , come now how much longer can people really  believe that game shows really show anyone's intelligence.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small The way i see it people can be \textbf{dumb} yes, its when they're \textbf{dumb} and angry that makes it wrong\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small -Like, I'm listening to what you're saying but I only hear what I want to+That's... Just called being a \textbf{woman}GeniousðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Republican woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small This is a comedy skit, right? This is a joke. Please tell me this a joke. There is no way she can be that \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Samira Rose lol I know the personality of the girl she's an ex american idol contestant and she was that funny even at AI so I think she was just joking. I dont think she is that stupid plus she has \textbf{nothing} to lose after all in this game and she has talent fee for guesting in this show.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small I only hear what i want to."That's just being a \textbf{woman}"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She is really stupid.  If she doesn't know , she can just say she don't know rather saying lots of words and cheap acts that made her more stupid and \textbf{dumb}!!   Yes , she is absolutely the dumbest primitive person ever!Trying to be funny not realizing becoming stupid and dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small She is not \textbf{dumb}! She is just being a woman\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small She is the dumbest \textbf{chick} ever....how do you not know europe is MADE UP of countrys. Europe isnt a country itself what an idiot!\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Such a mong\normalsize   & \cellcolor{green!27}Mong & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Nigga wtf?????????\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small I actually thought Budapest is the Czech Republic capital and I'm from romania (basically next to hungary) so you can say I'm \textbf{dumb} too xd (:\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Kiss Dori omg you \textbf{g\textbf{ay}} shit I'm only 12 and you don't even know what romania is you fucking shit\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small If u think this is \textbf{dumb}, go see beetlejuice,  its even dumber than this Lmao\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I have seen \textbf{dumb} things but this is really dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small How is she \textbf{dumb} when she got the right answer by copying and walked off with at least \$25k\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small She's pretty and \textbf{dumb}. It's what you want .\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small This \textbf{chick} is really cute though...\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small All blondes are \textbf{dumb}!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small I don't care how \textbf{dumb} she is as long as  she is that hot\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Lol I'm blonde but I'm not \textbf{dumb}. That's only slightly funny because I didn't know for the longest time Hungry was a country either.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Dont be too offemsive shes not \textbf{dumb},  more like intertaining :)\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small There's \textbf{nothing} wrong with her. She's cute. She just needs a good teacher.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small This is Kellie Pickler who has gone on to become a huge singing star. She is worth MILLIONS. She fulfills the \textbf{old} joke about a girl friend. "I want a girl that is a nymphomaniac drug connect that owns a Ferrari dealership". ( This joke was from the late 70's. At least that is when I first heard it)\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small I fear about human \textbf{race}. Aliens will invade earth easily. Luckily there are few smart people left to save the day!\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small That's just called being a \textbf{woman} Ouch\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small That's called being a \textbf{woman} hahahahahaha\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small focus i am listening to what you're saying but i listen to what i want a hear that's being a \textbf{woman} ðŸ˜‚\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small She's not really \textbf{dumb}, I'm almost in 8th grade and I'm horrible in geography\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Is this \textbf{woman} retarded?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small stupidity is a clear lack of \textbf{common} sense.  there's a \textbf{thin} \textbf{r\textbf{ed}} line between stupidity and ignorance.  she's clearly ignorant but may not be entirely stupid.\normalsize   & \cellcolor{green!5}Common, Red, Thin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!5}4/26 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Not knowing the country is fine but thinking Europe is a country? Lmao \textbf{dumb} American bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small "that's just called being a \textbf{woman}" hahah\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small This is why I'm moving away from Tennessee. Originally being from Connecticut, this is all too real. The average intelligence here in this state is lower than that of a soap dish. Whenever I talk to someone outside of my family, I need to slow down my speech and \textbf{dumb} down the English language so people can understand me. I really hope Vegas (where I'm moving) is better because living around people exactly like this \textbf{woman} is extremely aggravating.\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small Dumb people make me feel smart\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small andrew marchitto get new, smart friends. I have the same problem. If you're smarter than average, you have to \textbf{dumb} down and conducen to other people, and it's freaking annoying.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small That1TechDude humble bragging is gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Not really, it has \textbf{nothing} to do with your knowledge, it's about your personality, you hate \textbf{dumb} people, that's okay, but someone finds this video funny, if you don't then you can just close it and move on. I am also good at geography, but I can't say it's painful to watch because it's just a show, show of clowns, based on humiliating them.\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small What i dont understand is, sometimes \textbf{dumb} people like this earn more money than some intelligent and hard working people who live in third world countries.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small wtfock he so stupid even my 6 year \textbf{old} brother know hungary is a country\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Ok now c'mon, not all of us Southerners are proud of \textbf{dumb} just like not all Mormons like being sister wives so they flee! I love my positive southern attributes and proudly take them with me BUT, I have done quite abit to prove to myself and others that I'm \textbf{dumb} as hell. However, if I don't know something I will blame it on being an original Mississippian and ask for forgiveness as I know stupid can often overrule knowledge so I just need a little help blowing the inherent ignorance out of my ears, away from my brain so I can function like a normie. ;)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small There really is a lot of \textbf{dumb} Americans!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Americans are \textbf{dumb} as fuck!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small It's sad to think blondes are \textbf{dumb}, this is the most fucking pathetic thing in the world.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Those kids will be stupid also when they get to her \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small If you think that's real, you're just as \textbf{dumb} as you think she is. The point of the show is to make the kids look smart.  The boy can't roll his eyes if she doesn't say something stupid.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small 80 of americans like this blonde. \textbf{nothing} special\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Did she graduate high school?Did she win \textbf{nothing} on this show?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small She's just playing \textbf{dumb} for the camera, it's obvious. The host pronounced Hungary "Hungry" and the second time around, she said she'd never heard of HungAry. Anything for the camera...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Kellie is so pure and innocent but she might be one of the strangest women on earth that we can't be mad at.   She might not be the sharpest person in the room but she is definitely a good \textbf{woman} to live the rest of your life with.  Think about it.   She is always happy , would never cheat , and always caring\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small Just get on your knees and start sucking \textbf{dumb} ass\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Awww, ... she is just Tooo pretty to be smart , ... so, she stays Pretty and \textbf{Dumb} .\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Pear Ross ðŸ˜ƒwell not really but I do sympatize with her because we European do the same.. We think to America as a \textbf{Nation} and not as a ContinentðŸ˜ƒ\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Pear Ross ðŸ˜ƒU caught m \textbf{R\textbf{ed}} handedðŸ‘\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small K22 channel bruh.... I'm pretty sure you're the only one who sees America as a nation\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Space Queers The United States of America is a \textbf{nation}, and many people who live in the US as well as outside call it America the same way some people call England Britian. America is a \textbf{nation}. America is not a continent. North and South America are both continents, but America is not\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small K22 channel not funny at all and and beautiness is not below intelligence .i am 9 yrs \textbf{old} and even i know that europe is a continent and Hungary does exist. ðŸ˜’ðŸ˜’ðŸ˜’ðŸ˜’ðŸ˜’\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Sneha Singh You are required to be 13 years \textbf{old} to be able to have an account on YouTube\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Sneha Singh I don't.... I don't care what your name is. You shouldn't be commenting on YouTube if you're under 13, nor should you just randomly tell people your \textbf{age} and name\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small She is uneducated. This does not prove she is \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small you can't be this \textbf{dumb}, it must be staged\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Black} Tim: Mexicans\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Black Tim Howard, Well, you have Americans from the Coasts, who are ever so slightly smarter.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Horny \textbf{Fruit} Flies and a woman\normalsize   & \cellcolor{green!27}Fruit, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Horny \textbf{Fruit} Flies I'm blonde, born in Mississippi, but raised in Tucson AZ, now living in SoCal.....I have the hospitality and humor of a Southern Belle plus book and street smarts of a Westerner. I lucked out! She is \textbf{dumb} though and most likely cause her damn parents had her in beauty pagents like so many southern parents do with their girls.\normalsize   & \cellcolor{green!5}Dumb, Fruit & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Horny \textbf{Fruit} Flies When she told Jeff she heard him but was only listening to what she wanted to my thought was "that's being a \textbf{woman}" then Jeff says the same! I love it!\normalsize   & \cellcolor{green!27}Fruit, Woman & \cellcolor{green!27}Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I hope that's a joke.. or you're the \textbf{dumb} one. But yes, there are some Americans, ESPECIALLY Southerners, who are making everyone else look really bad.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Horny \textbf{Fruit} Flies chill, here in California people are not as stupid, mainly because there are some immagrants including me...\normalsize   & \cellcolor{green!27}Fruit & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Omar De la Fuente - The reason people in California are smart has little to do with immigrants. It's because liberal blue states which are mainly up north and on the coasts have historically put an emphasis on reading and literacy. Liberals spend shit loads on education while education funding is always the first thing on the budget chopping block in conservative \textbf{r\textbf{ed}} states i.e. the entire South. Look at what's happening right now in W.Virginia with the entire state's teachers going on strike because many work two jobs and are still on public assistance. Education is viewed very differently up north. Stamford, Pomona, UC Berkeley amongst others are among the best schools, not only in the \textbf{nation} but in the world. That's just the west coast. The east coast has all of the Ivy League schools. Research and Development, technological innovations happen up north on the coasts. Manufacturing and snapping shit together happens down South.\normalsize   & \cellcolor{green!5}Nation, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}3/156 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Jayson Davis ignorant post from a leftist \textbf{libturd}. I live in NJ and there are many \textbf{dumb} ass Liberals that would give you and the blonde in the video a run for your money when it comes to being stupid.\normalsize   & \cellcolor{green!27}Dumb, Libturd & \cellcolor{green!27} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small JJ G - I live in Manhattan...in one of the most expensive \textbf{zip} codes in fact. Saying you live in NJ impresses no one. Hell, New Jerseyans are the inbred cousins of mid-Long Islanders...LOL!!Bitch please...\normalsize   & \cellcolor{green!5}Zip & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small You didn't mention that she's a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Horny \textbf{Fruit} Flies I don't think Southerners are dumber than Northerners\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Horny \textbf{Fruit} Flies ..... she's CBS...... cute but stupid.\normalsize   & \cellcolor{green!27}Fruit & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Southerners are not only \textbf{dumb}, they are \textbf{dumb} and stubborn like a donkey.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Horny \textbf{Fruit} Flies that \textbf{dumb} southern blonde was raised by her grandfather because her mother left her and now has her own tv show and is worth millions so enjoy you useless life hater\normalsize   & \cellcolor{green!27}Dumb, Fruit & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Horny \textbf{Fruit} Flies You meant "better". Be bless America.\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small â€¦â€¦â€¦Americans aren't all dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Nononono!Indians get more \textbf{dumb}.The more south, the more \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small JonnyNice America is a continent, south and north right? So why would you NOT call mexicans and americans? They are located on American continent..why not to call them american? Like in Russian Federation there are few countries and besides \textbf{nationality} they call themselves russians\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small JonnyNice and a woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Sad news is when \textbf{dumb} people act \textbf{dumb} !\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small ALL OF YOU WHO ARE BUTTHURT OVER THIS QUESTION ARE JUST LIKE MY BEST FRIEND WHO'S CZECH.IF YOU M E N T I O N THE CZECH REPUBLIC, HE GETS MAD.THERE'S \textbf{NOTHING} BAD ABOUT YOUR COUNTRIES IN THE JOKE. IT'S JUST FRIGGEN WORD PLAY.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small IDK how people can laugh at 184882 year \textbf{old} jokes lmao y'all as \textbf{dumb} as this bitch fr\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Abdul S. But maaaaaan that joke is really \textbf{old}... I cannot believe that some people are still finding it so fucking funny (no offense to you personally)\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small OMG!! SHE IS F*CKING DUMB\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Man, take it easy on Ms. Pickler.....she is a lovely \textbf{woman} inside and out.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Why call her a \textbf{d\textbf{umb} blonde}? Why not just \textbf{dumb}. IM OFFENDED\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/12 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I don't care she is \textbf{dumb} or not. She is hot.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Typical thick \textbf{yank} so fookin scary.....\normalsize   & \cellcolor{green!27}Yank & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small At first I was like: "I know Budapest is in Hungary, but I don't blame Americans for not knowing that"... Then she says: "I thought Europe WAS a country", and I was like: "Okay, this \textbf{woman} is \textbf{dumb} as hell!"\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small I didn't know it was Hungary but she thought Europe was a country? And she didn't know France was? K, I'm done hoping for the human race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Darrell Wilson woah woah a lot of americans arent stupid. The only reason you guys hear about americans being stupid is because thats the only things that are exposed. You never see a youtube video stating how smart Amerians are. Explain the founder of \textbf{apple}, Steve hawking, and the fiunder of facebook even get recognized really as well as bill gates.\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small I went to school and anyone who passed the fifth grade took geography and knew it was Hungary duh, where did they get this \textbf{bimbo} from?\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small TheMountainDewGamer that is what I learned in fifth grade geography class. That \textbf{bimbo} is proof of the dumbing down of America. That was just embarrassing.\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Alucard maybe i wasnt nice calling her a \textbf{bimbo} but it was frustrating to see an adult not able to answer basic elementary school question  as you see that little kid knew it.\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Budapest is a city of almost 2 mio and has been pretty important throughout Europe's history. And Europe is "\textbf{Old} Continent", most Americans came from here. So, it's kind of logical, Americans should have known important european cities.On the other hand, we, Europeans, know definitely all american cities over 1 mio. Even over 500.000. But we do not know all state capitals, as those are very often some small towns. In Europe, capitals are always biggest country cities.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small Jeez, to all the people saying Americans are stupid for not knowing this, calm down. Yeah, she's a lot older than those kids and it's super embarrassing that she didn't know France was a country. But really?Most American school kids are learning other things during Geography/History/Civics. Most of it is about US history, but we also learn about other countries pasts' too. The thing is, the kids who learn the other capitals from around the world and other facts and stuff CHOOSE TO. Its not a required curriculum, so many choose not to. You'll meet a lot of people who's interested in different cultures and therefore, choose to learn things like that.Please don't get me wrong; this \textbf{woman} seems to have not gone to school in any way. Seriously, she thought Europe was a country -.-But don't group all Americans into a 'stupid' category because some Americans are. Every country has \textbf{dumb} people; that's just life. For some reason, it seems idiotic Americans are just publicized more.(sorry for the rant)\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/174 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small There is \textbf{nothing} wrong with the American education system. Why don't you say that about Somalia?! She's just a farmgirl with a third grade education so stfu\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small +RyuN Then they haveÂ a lot in \textbf{common} with you.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I knew Kellie Pickler was stupid but God damn she's dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Sexy and \textbf{d\textbf{umb} blonde}.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small She is not \textbf{dumb}, it just she does not know that  there are countries out side the USA . I bet the  only other country she knows is China cos China is the  hostile and bad country towards USA and there is what she has been taught by the media .\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Kelli Pickler I don't care how \textbf{dumb} she is she has a beautiful singing voice, plus she's so fine I'd drink her bath water. hahaha not really but she's fine.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Matt Thomas you are as \textbf{dumb} As Her\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Kelly is ignorant due to lack of a good education but she definitely is not stupid. Indeed, she is a very intelligent, kind \textbf{woman} with a neat personality, has a great voice and by the way, is a millionaire.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small dumb yank\normalsize   & \cellcolor{green!5}Dumb, Yank & \cellcolor{green!5}Nationality - American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Holy shit is this \textbf{woman} real or was this just a staged thing? Surely no one is that \textbf{dumb} that1. She doesn't know what country Budapest is the capital of.2. She think Europe is a country.3. She doesn't know if France is a country \&4. She's never heard of Hungary but associates this country with Turkey because it's a good and she is hungry??? What in holy craps name planet is she from?\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small Kelly pickler...\textbf{dumb} as a box of rocks\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small She had to be acting , theres no way somebody can be that \textbf{dumb} and get on tv , wait i take that back ...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small That's fine. i. like. them. \textbf{dumb} and. hot\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I would have \textbf{sex} with her slutty mouth\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This girl was probably paid to act that \textbf{dumb}. The show likes to show case how smart kids can be.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Stupid can be hot. I know it may sound weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Am I wrong in thinking thats kelly pickler ?...and real \textbf{dumb} or fake \textbf{dumb} , I could watch and listen to her all day\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small At least she's CUTE, that's better than \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hot and \textbf{dumb}.  Shes perfect!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She probably got it confused with the European Union.  Which is a group of countries that are united as one.  Like the states make up the country of the USA!  They all have the same currency, except for Britian.  The Euro. All the responses on here are liberals critisizing someone who has more \textbf{common} sense than an average Hillary supporter.  If she did vote for him, so what, she's smart.  I am sick of liberals saying Trump is not smart.  He's accomplished more in one year, than any Dem presidents combined in the last 40 years.  He also has more wealth, by which most he created, which in turn translates in him being intelligent, and an extremely hard worker!!!  Getting back to her, the liberals act like that they  never have been in that situation where they did not know an easy answer.  I knew it, I didn't bash her, but wow is she HOT, was my first thought of the video!\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/162 & \cellcolor{green!27}0.617 \\  \hline
  \cellcolor{green!5}\small She is not so \textbf{dumb} if she walked away withi 10k or more.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Lack of knowledge is not \textbf{dumb}. \textbf{Dumb} is making fun of someone to make yourself feel better about yourself.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Kellie Piklor...\textbf{dumb} as three buckets of hair\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small This HAS to be fake; \textbf{nobody}...not even a BLONDE...can be THIS \textbf{dumb}!!!\normalsize   & \cellcolor{green!27}Dumb, Nobody & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Although I'm certain to be met with your stereotypical and false Liberal rhetoric...I'll answer that: I AM a Trump supporter.  I am a white male who KNOWS I'm a white male...and neither apologizes or hides the fact.  I take pride in being a white male, and neither apologize for it nor feel I have anything to apologize for.  I take pride in my \textbf{sex}, my \textbf{race}, my \textbf{nation}, and my family and for that I owe no one an explanation or an apology.  I'm heterosexual, educated, and like women and enjoy their company.  I believe in Honor and maintaining it as a Man; Women are the Heart of Honor.  I'm traditional in upbringing and with my value system, and hold strong beliefs in a nuclear family where one parent remains at home to raise children who believe in hard work, responsibility, and duty to family; children should NOT be left in daycare, with strangers, or raised outside of the familial unit that conceived and bore them.  I don't mince words with Fools nor do I entertain their delusions of grandeur or self-entitlement.  I believe there are TWO genders, and that people are born one of them and can't arbitrarily decide on a daily basis what they are going to "present" as that particular day.  I further believe that men should open doors, pull out chairs, and rise when a lady either enters or leaves the room.  I don't think women can necessarily do everything as well as men but I don't think that makes them inferior...it just makes them women.  I also don't mind being labeled \textbf{racist}, homophobe, misogynistic, ignorant, or any other "ist" or "phobe" word by Liberals or like minded people who are so close minded with their ways of thinking that they make complete hypocrites of themselves; hypocritical by screeching that everyone's life, choices, and decisions matter SO LONG as they coincide with the "La-La-Land" philosophy that they themselves entertain.  I believe that "Justice" is not often synonymous with "Legal" or "The Law," and sometimes one has to seek Justice for oneself and one's loved ones when the Rule of Law or the dismissive ideology of "Civilization" get in the way of what is TRULY Just.  Lastly, while I don't necessarily believe in god or gods, I do believe that there is a Higher Purpose that each of us is born to, and part of the journey of Life is to discover what that purpose is and to further make the decision to either strive for it...or not.  That is who I am and what I believe.  Likely, you'll respond with a snarky comment on my political beliefs, attempt to besmirch either my beliefs or your perception of my intellect or education, and lastly lambast me with a soap-box stance of your own beliefs juxtaposed with ideologies you either don't comprehend correctly or misconstrue the true meaning of.  Ya know what?  I'll sleep fine tonight regardless.  With THAT, I bid you a good day, sir!\normalsize   & \cellcolor{green!5}Nation, Race, Racist, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}4/498 & \cellcolor{green!5}0.803 \\  \hline
  \cellcolor{green!27}\small vMrMysteriousv I've met a lot of half retarded \textbf{gender} confused liberals too\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Dumb Americans.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small "that's just called being a \textbf{woman}" Best response. Love this guy\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It's obvi that Blonds are \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small She is so \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Not \textbf{dumb}, not educated.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small She would make a nice date though :) Good \textbf{sex}.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small she is not \textbf{dumb} becouse shes blonde or live somewhere idk where lol shes just dummbb (sr 4 my bad english)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Ngl people talk about how the master \textbf{race} is bad and etc, and sure it is a terrible frame of mind but everyone apart from these types of people are the master \textbf{race} so there you go...\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small Amartya Sau The idea of banging someone that \textbf{dumb} seems taboo, but of course I'd do it. I'm a pretty grim dude. I need a easy layup like this.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small why are all hotties \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small you are a blonde \textbf{bimbo} girlðŸ˜²\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small That's a \textbf{dumb} blonde\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Just the way I like them... gorgeous and \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small SO \textbf{DUMB}!!!!!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Dumb but gorgeous . She is a great country singer who has always entertained our military over seas .\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Cocksucking expert though so no she's not \textbf{dumb} in my books\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small She must be a southern \textbf{chick}... they are normally brainless zombies\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb}, but at least she's nice\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small It's actually how most Americans are. They will never admit it but they are just pure \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small American education is number one in the world. God bless the good \textbf{old} Jew S of A\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small "I'm jsut hearing what I want go hear." "that's jsut called being a \textbf{woman}"\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small "thats just called being a \textbf{woman}" okay regardless of how \textbf{dumb} she is, it's still fucking disrespectful to say misogynistic bullshit like that. smh.\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small When she said "Europe is a country" my little brother who is 5 years \textbf{old} started laughing his ass off ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small All blondes are dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small It's people like this \textbf{woman} in this video that make up the US population of racists and intolerance...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small ... This \textbf{Woman} vs Miss South Carolina ...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small How can you filter \textbf{dumb} girls if you are looking for smart one?Ask her next question:Bee is, wasp isn't. What is it then?  If she doesn't answer in a two second, and if she say hornet or bumble bee... Well, her IQ is around freezing point of the water (in Celsius ofc)...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small Eugenics might not be that bad of a plan, after all...\normalsize   & \cellcolor{green!27}Eugenics & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small all blonde girls are dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small To you \textbf{mental} midgets that say Americans are Stupid show your stupidity.  Americans have invented more stuff for the good of mankind and medical discoveries that has saved billions from disease than any Country in the world. Let me help you.  American's invented almost everything you use and touch.  The automobile, Interchangeable parts,. Telephone's,  TV, Computers.  Electrical grid,  Lightbulb, Submerines,  Telegraph,  and on and on.  For those reading this comment that are not American tell us three things invented in your country that has made things better for mankind in your country.  So now how \textbf{dumb} are Americans compared to your country.\normalsize   & \cellcolor{green!27}Dumb, Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/102 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small She would be fun at a party.  She was born \textbf{dumb} but God gave her beauty and it's ok.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small She's fucking \textbf{dumb} as fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I didn't laugh when he said "That's called being a \textbf{woman}" but at her response."Oh."ðŸ˜‚\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small You gotta give it to her, but "I heard of Turkey, but "Hungry" ?! Never heard of it" was actually quite witty. She is cute. I also think it gets \textbf{old} to claim Americans are stupid. It's obvious that by a complete failure in their education system they have no geography lessons whatsoever. But there is no reason to claim that they are stupid just because of that, because geography is mostly just useless general knowledge. And it's not just american. Some years ago in Indonesia I bought someone a T-Shirt with Albert Einstein on it, and he asked me "who is this?". Many countries in Asia only give lessons about their own history, for example in Thailand people are practically clueless who Fidel Castro was or any such things.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/130 & \cellcolor{green!27}0.769 \\  \hline
  \cellcolor{green!5}\small "I thought Europe was a country." As I sit with my palm planted firmly on my face, I wonder: is our education system that flawed? I question this while already knowing the answer as I continue to watch this \textbf{dumb} bitch.Edit: it's not even a fucking question!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Dominik Toth because a \textbf{dumb} lady never heard of Hungary? Get over yourself, no one cares if you're offended\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Dominik Toth Well not a lot of people know anything about Hungary!!! It's a \textbf{nation} with no history or culture so you shouldn't be offended\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Alex AndreasAnd your comment is just another reason for people thinking that most americans are \textbf{dumb} :/\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Am a \textbf{black} Jamaican guy and i know all the countries of Europe and their capital and financial hubs and this \textbf{dumb} with doesnt know.\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Steve \textbf{Elder} well do many people in the US heard of Lake Balaton?False comparison.\normalsize   & \cellcolor{green!27}Elder & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Alex Andreas no history and culture? Oh wow... that's offensive! Dude, you know \textbf{nothing} just like the \textbf{chick} in the video... Just because our ancestors immigrated for centuries doesn't mean we have \textbf{nothing}. I'm personally proud, that we are different than the rest of Europe and speak one of the most difficult languages. Try to respect others...\normalsize   & \cellcolor{green!5}Chick, Nothing & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}3/57 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Alex Andreas no history or culture? Damn you must be as \textbf{dumb} as this blonde. Our country is more than 1000 years \textbf{old} and our culture is 100 richer than yours, whatever shithole you come from.\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Steve \textbf{Elder} we heard about alabama thanks to lynyrd skynyrd. But you cannot really compare an actual country to a state inside another country.\normalsize   & \cellcolor{green!5}Elder & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Alex Andreas bet you're the blonde \textbf{woman} haha, Hungary has a culture from like 3000 years back.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small There is \textbf{nothing} to be offended about about\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Minion Slayer o god not a 12 year \textbf{old} retarded jake pauler\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I get it Jeff!Â  You want me to attract a large amount of \textbf{porker} moms.Â They probablyÂ go to Weight Watchers to gain weight.Â  JustÂ send them to Golden Corral and make sure the title onÂ the car is ironclad.Â  Whatever you do do not invite them to a baby shower.Â Â  We lost 12 unborn children because of porkers.Â  I thought it was bad enough when they told me not to have children but they drugged me and killed the baby at an abortion clinic and sterilized me.Â  Let life and death be determined by God, but I got a poisoned wafer at the last Mass.Â  It is time for them to pay for their deeds.Â Â Â  Isabel Sloane\normalsize   & \cellcolor{green!5}Porker & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/118 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}\small My only question to this is how did she make to \$10,000 i'm serious the \textbf{woman} that didn't know that Europe is a country somehow made it to \$10,000\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I'm not going to scroll down. Probably millions of \textbf{crazy} feminist comments after what the presenter said ðŸ˜‚\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small what's smarter, a 1 week \textbf{old} asian or this blonde\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small People \textbf{dumb} like this should be killed. Not even kidding.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small damn I guess if you're hot your dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You should've seen her \textbf{dumb} ass on family feud\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Really \textbf{dumb}, but also really cute, so I would definitely do her. What I wouldn't do is smart but ugly and/or \textbf{fat}.\normalsize   & \cellcolor{green!27}Dumb, Fat & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small "Is France a country?"No it's a fucking rare bag of Doritos you \textbf{dumb} shit.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small It's Hungary not Hungry! The host is almost as \textbf{dumb} as the blond \textbf{woman}!I want to end my life. nuke America and end their stupid lives wtf is this shit!?\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small It's videos like these that make foreigners think all Americans are extremely stupid. It's unfortunate only our \textbf{dumb} citizens get all the spotlight.  :/\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Shut up I'm blonde and I can't help it and if people bully me in the comments I might cry who ever made that there stupid and \textbf{dumb} and I get billed at school I get called a girl allllllllll the time and I want to punch them in the face so hard but I hate it whene I hurt people so please don't bully me in the comments\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Jerry Adams She's actually intelligent for fooling the people in this comment section and is a moderately successful singer and actor.\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Seems a bit too \textbf{dumb} like made up and fake\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small that's the kind of \textbf{woman} I can put up with.Â  brains make an annoying \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small She's \textbf{dumb}, but hot.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Kelly Pickler. It's Celebrity \textbf{Dumb} Fuck.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small The \textbf{old} saying "too stupid to live" comes to mind. Poor girl. I hope she marries well.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small She would have gone home with \textbf{nothing},even that little \textbf{black} dressðŸ˜ŽðŸ˜ŽðŸ˜†\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Hahaha yeah of course Europe is a country. Geez even that kid was thinking how \textbf{dumb} she is. Damn hope she doesn't ever have kids.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Wow , somebody send this \textbf{woman} some books. Oh wait ! she probably doesn't know how to read.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small When the Americans believe the world series only belongs in their own \textbf{nation} you can see where this intelligence comes from.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Seriously?  Holy crap!  That has \textbf{nothing} to do with being blonde, just totally ignorant!  Did she even go to school?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small it doesn't matter \textbf{hun} ... just take your top off\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Typical \textbf{dumb} person response, "never heard of it".So, the problem is the country not her.She's so \textbf{dumb} it's really hard to believe.The bad news is that many Americans are oblivious to the world outside of the US, unless perhaps their kidis in the military and being sent there.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Unbelievable.  Is this some kind of joke?  " Europe a country? !!! Is France a country?  "?!!Being Blonde has absolutely \textbf{nothing} to do with STUPIDY.I hope that they don't allow her to breed! Is she a Trump supporter by any chance?  How is he going to make America GREAT  when you have "this" in the gene pool?Please take away her right to vote.  ; )No wonder The World thinks that Americans are stupid.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small These are the type of celebrities that try to lecture us on politics. \textbf{Dumb} as f:;k\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small cupid stunt ,go back to school \textbf{dumb} bitch.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Ladies and gentlemen. That right there is a typical Trump supporter. Except prettier. Still \textbf{dumb} as shit though.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small i dated a \textbf{bimbo} like that once ....... once!!!!!!!!!!!!!!!\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Is France a country ðŸ˜¨ðŸ˜¨ðŸ˜¨ Her stupidity and lack of \textbf{common} knowledge must be fake. Some things you just know like the matter of fact that US is a constitutional republic, NY is not the capital of US and Europe isn't a country.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Dumb as a rock but hot as a fox\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small What do you call a blonde who dyes her hair brunette?Artificial intelligenceSanta Claus, a smart blonde and a \textbf{d\textbf{umb} blonde} are walking down the street... They see twenty dollars, who picks it up first????The \textbf{d\textbf{umb} blonde} coz the other 2 dont exist\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/45 & \cellcolor{green!5}8.889 \\  \hline
  \cellcolor{green!27}\small this \textbf{d\textbf{umb} blonde} is doing quite well for her self......\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small don not judge people bcuz of their lack of knowledge.and call them \textbf{dumb} blond.......that is just \textbf{dumb} its self if you are a grown up.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Don't get offended or that's just called being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small She's NOT \textbf{DUMB} at all, because has been using her BEAUTY card all her life.  You know they picked her for the show not because of her brain but her looks.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small I think this was a set-up, she can't be that \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Ignorance isn't a luxury at all in this century and internet \textbf{age}!!!!Europe a Country??? What a shame really!!!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small It's more sad than funny. I don't think she's \textbf{dumb}, she's just uneducated. Can't blame her for not knowing something she was likely never taught. She's super adorable though. It's more of a commentary video on the disparaging gap between the quality of American education across the \textbf{nation}. I do sure hope that whatever high school she attended got shut down after this.\normalsize   & \cellcolor{green!27}Dumb, Nation & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small I've seen thick but holy shit that's \textbf{DUMB} AS FUCK. !!!ðŸ¤¤ðŸ¤¤ðŸ¤¤\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Thats called a perfect \textbf{woman} !!! Pretty and \textbf{Dumb} as Fuck !!\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small This is so pathetic. A village is missing their special \textbf{snowflake}. That poor kid could barely contain his laughter. OMG this \textbf{bimbo} is Kelly Pickler.\normalsize   & \cellcolor{green!5}Bimbo, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Gender - Female intelligence & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small that was the most dumbest thing i've ever heard............how can a grownup \textbf{woman} think europe was a country.................:D\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small everyone is \textbf{dumb} if you ask them about shit they don't know.......\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small I feel bad living in America. We are insulted that we are \textbf{dumb} by foreign countries. SOME OF US ARE SMART XD\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small oh god this is the stupidest girl ever. my god, my 6 year \textbf{old} brother knows this and he isn't in school yet. its sad\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small To be honest, Hungary is not a popular country in the world.   I think pretty many ignorant people in the world react like this    Of course I know Hungary pretty well.Ural-Altaic language, Eastern Europe, Budapest, Hungary-Austro kingdom and \textbf{Hun} people from Asia in history etc.  But There are pretty many ignorant people in the world\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small The worst part is that when she said she thought Europe was a country \textbf{nobody} laughed. Who knows how many more thought the same in the audience.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small It's like saying America is a country what in reality it's a continent but \textbf{nobody} cares.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small AndrÃ©s Paz actually it's not. It's \textbf{nothing}. North America is a continent though.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small +A Box of Rocks You left out the cliche about \textbf{dumb} blondes.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Ksi Orze \textbf{nigga} since when?\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I'm a blonde so I must be \textbf{dumb}. ðŸ˜ž\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small It seems to me that this \textbf{woman} never went to school and never read an encyclopedia or used Wikipedia or the internet or anything and didn't meet and converse much with other people in her life. How oblivious to society would you have to be in order to be about 24 years \textbf{old} and not even know that Europe was a continent? I would have been about 8 years \textbf{old} when I first heard of Hungary, thanks to Encarta '95.\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small As all the non Americans comment how \textbf{dumb} Americans are, they fail to realize all the 5th graders are American. And were the idiots? This girl is most likely rich, like Paris Hilton, not much in the brain but a whole lot in the bank.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small She isn't really all that \textbf{dumb}. And for her, the word Naive suits better.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I can only hope this \textbf{bimbo} is a good lay, otherwise she would have NO useful value....\normalsize   & \cellcolor{green!27}Bimbo & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I do not believe this is for real. She is just playing \textbf{dumb} to amuse people.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small When a 12 year \textbf{old} is laughing at how stupid you are you know you failed in life.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small She CANT be this dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Lord Snickerdoodle Is France a country?Kevin Spacey: Actually i'm gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Dumb blonde:"I only hear what I want to."Host:"That's just called being a \textbf{woman}."Me: "Did you just say that on national television?"\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small I dont know how someone can be this dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small 01:04 "thats just called being a \textbf{woman}" OHHHHHHHH XD\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small i'm blonde too!!Am I stupid or \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small well maybe it is stupid, but it's also \textbf{dumb} - Patrick\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small +Gracie WoodmanseeÂ  Is English your third language or are you just one of those really \textbf{dumb} people who call others \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small she is real dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Fake they wouldn't have left someone with a \textbf{mental} disease on the showLol\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I hate how people being blonde automatically makes them \textbf{dumb}. I'm blonde, but I have an IQ as high as 143.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Oh my god, talk about \textbf{dumb} and thick, American schools seems to teach only about their own State, not even their own country, and the only people who know about the World are those who travel!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small blonde on the phone "please come quickly, my house is on fire".    fire man " Okay we're on our way, just tell us how to get there".   blonde " Well dah, the big \textbf{r\textbf{ed}} truck" ðŸ˜‚\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small All the people on comments are so stupid thinking she was \textbf{dumb} , she was trolling and fooled everybody , "what is france? " lol\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small This isn't fake she's that dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Ho Le Fuk let's hope so.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Europe they speak European it's \textbf{common} sense...\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small 0:59 hahaha that's just called being a woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Canadian Hart But the low IQ quality are from the south like this \textbf{woman}. Name one blue state from the south.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Jesus Christ she is dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small It's all act. Kelly Pickler has  a master's in Bio Engineering.  She took her grad courses in Yugoslavia.  Her accent is totally fake. Not as \textbf{dumb} as one might think.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Everyone even a 5 year \textbf{old} knows Europe is a continent not a country\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small omg she super dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Wow, not only is the blond \textbf{dumb} but Jeff can't even pronounce the country's name right.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small When I was in the USA in 2010,I was speaking hungarian to my sister,and some 15-16 year \textbf{old} \textbf{black} guys came up and asked what language are we speaking?we said hungarian,They asked are there nudist beaches in hungary?Are there toilets in Hungary?andstuff like that.After that we walked away and said something bad in hungarian.They asked what did we say.We said:You dont wanna know...\normalsize   & \cellcolor{green!5}Black, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/63 & \cellcolor{green!5}3.175 \\  \hline
  \cellcolor{green!27}\small This \textbf{woman} was failed by her education system. This level of ignorance is sad and dangerous. I mean,  some people are weak learners but unless you have a profound learning disability you should be expected to reach adulthood knowing that France is a country.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small The \textbf{r\textbf{ed}} high heels took all of her brain power\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Sex will overlook all of this  just because of her looks...\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Listen,listen,listen I swear not all blondes are like this I hate being called \textbf{dumb} because I'm a blonde just don't think all blondes are this fcking dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small They screen contestants, this must be deliberate comic relief. She's not all that hot, but she is all that \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small +Rubiks GamingÂ  Take it from a retired teacher - It's not only POSSIBLE to be that stupid, it's much more \textbf{COMMON} than you'd believe.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small This is embarrassing for the human race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Multi-Millionaire recording artist, Kelly Pickler... good thing for her she can sing. Well, maybe she could be a movie star..... playing a \textbf{d\textbf{umb} blonde}.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small na brooo... the smart states voted for a snake so we can atleast keep eyes on her on the other hand U GUYS VOTED FOR A CORRUPT \textbf{fat} \textbf{RACIST} who is power hungry.....gezz\normalsize   & \cellcolor{green!27}Fat, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small probably for the halfbreed queer\normalsize   & \cellcolor{green!5}Queer & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Everyone has a right to vote, \textbf{dumb} or smart so dont say that\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Horny \textbf{Fruit} Flies, I'm pretty sure she voted for Hillary because Trump has a penis, so they have absolutely \textbf{nothing} in \textbf{common}. At least that's what her brain tells her.\normalsize   & \cellcolor{green!5}Common, Fruit, Nothing & \cellcolor{green!5}Age - Youngsters, Sexual Identity - Male homosexuality, Social Class - Working class & \cellcolor{green!5}3/30 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}". You can't say that on TV or anywhere now with today's PC culture.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Well it is real \textbf{sexism} it's not PC bs.\normalsize   & \cellcolor{green!5}Sexism & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small No it's not sexism\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I find very offensive cuz I'm \textbf{fat} sweaty and I don't shave I want to be nice like the other girls and no boys like me cuz I'm a hairy sweaty mess but I found my peace with feminism\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Cherry Rockstar, Kellie Pickler is the name of the \textbf{woman}, she's a pretty good country singer, a former American Idol contestant and now co-host a talk show.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Horny \textbf{Fruit} Flies lol, dumbasses are breedrrs cause you thought she was for real lol\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Emeritus Gaming American blood makes you stupid or \textbf{fat} xD\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small bruh im stupid and \textbf{fat}, whatchu tryna say??\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Lord SulKing the Destroyer I'm 50 American and I'm not \textbf{fat} or stupid.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small im this \textbf{dumb} so..... xD\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She is quite \textbf{dumb}, but I disagree with the title "Dumbest blonde ever." It isn't fair to judge her on her hair colour. That's just a stupid stereotype\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small "That's just called being a \textbf{woman}" ROFL!!!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small apparently \textbf{dumb} people are cute now and intelligent people aren't attractive. istg i hate my own generation.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small so the saying is true blondes are dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Friz No \textbf{d\textbf{umb} blonde} americans\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small This isnt fake...Shes air-headed \& obviously dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small To all of Europe, I sincerely apologize on behalf of this borderline retarded American \textbf{woman}.  Please don't think we're all like this.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Joshua Jones Wtf are u apologize for lmao ðŸ˜‚ It was only the \textbf{d\textbf{umb} blonde} obviously\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small TheOrange Hexagon No y'all all are  bad !!!!! Let's see y'all use your brains to fuck, money hunger and oh yeah fuck toys and the brain u have left is basically who knows !! Blondes are the dumbest girls because all they do is fuck there sugar daddy's and \textbf{black} mans and than go shopping with daddy's credit card are there husband and than fuck agian and go to sleep lmao no Brains what so ever !!!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small what the fuck fuck you \textbf{woman} I'm French and I want to kil that woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Wikipedia: "Her mother left when Kellie was two years \textbf{old}, then returned and took custody of her for two years. After this, the court returned Kellie to her grandparents when she was 12 and they raised her to adulthood because her father was in and out of jail."\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Kelly might not be very smart but shes a hell of a singer and amazingly beautiful.  Shes got enough money now to see all those places she knows \textbf{nothing} about.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I just love how the kids are laughing like \textbf{crazy} since an older \textbf{woman} cant answer that question XD\normalsize   & \cellcolor{green!27}Crazy, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small my lord...i can't belive this \textbf{woman} is even on her\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small God, i'm done with these nasty rat \@ss sterotypes, just stop if anything your \textbf{dumb} and sexist (\& \textbf{racist} ;-;).\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small IT SHOULD BE A CRIME TO BE THIS \textbf{DUMB}....\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small yes, the punishment should be sterilization.  don't need \textbf{dumb} people producing \textbf{dumb} kids.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small I don't want to be so mean to her but we only have 2 options... Either she was put there on purpose and act that stupid or she is that \textbf{DUMB}. Cute but \textbf{Dumb} as \textbf{Dumb} can be.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/38 & \cellcolor{green!5}7.895 \\  \hline
  \cellcolor{green!27}\small Salvador PelÃ¡ez .Cute like a 2 yr \textbf{old}?  I think that she's a by product of the education system in her region.  She's very \textbf{dumb}."I thought Europe was a country Is France a country? !...They speak French in Budapest"She had me at Turkey and Hungary. ....; )Her stupidity is off the scale\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small Allan Googe Well she a \textbf{dumb} blonde\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small The fact that this person is rich makes me wanna blow my brains out. I don't care if you're a good singer, if you're this \textbf{dumb}, you belong in an asylum.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small "I only hear what I want to hear"......, "Well!.. That's just called being a \textbf{woman}!". Lmao bawahahaha\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small why do we glorify these \textbf{dumb} bitches\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small She's probably never been out of the states in all her life....She really is \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small That's fake and salute to her acting to be like \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small This blonde is so \textbf{dumb}! \textbf{D\textbf{UMB} BLONDE} STEREOTYPE!\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Oh my god as a \textbf{race} we are doomed . What are kids learning in school these days. All kids at about four should have a globe best way to learn geography.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Jackie Davies nope. Not the whole \textbf{race}. Just americans\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small My type. Blonde, pretty, and \textbf{dumb}. Js.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small crap, I feel a bit \textbf{dumb} too, I said Romania..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small when u are wrong , u r incorrect not \textbf{dumb}. dumbness is created by a great void of knowledge. She doesn't even knew Europe was a country or what , that's why she is \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small she is \textbf{dumb} but beautiful\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Lol im a \textbf{d\textbf{umb} blonde} ? hehe the first thing. its not my joke . its my grandpa joke. second thing its just a joke . im a french man but when i hear english jokes about french mens i laugh . u should have a sense of humor .umm and im sorry that was stupid from me heh\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/59 & \cellcolor{green!27}3.39 \\  \hline
  \cellcolor{green!5}\small \@alpha .L I'm not butthurt lol XD (It was quite funny) but it made me laugh because there was a spelling mistake in a \textbf{d\textbf{umb} blonde} joke\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small Tread Lightly my Friend, Real Blondes are not \textbf{Dumb} some of them are but most your \textbf{dumb} blonds were redheads or brunettes that bleached there hair blonde. My Wife is a Blonde she pretty smart, and pretty, But as for world affairs not so up on what country is what and she does some silly shit.It all depends on what you call smart.Deffinision of smart could be sevral things [LINK] In this girl's case she could be considered Smart! Dapper.Intelligence might not be her strong point.By the Way Blonde is spelt with an E on the end in english and I'm dyslexic.So english and spelling isn't my strong point either.Even the Real blonde didn't catch that.So where do the 3 fingers go? I'm lost? I'll ask my 34 year \textbf{old}!\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/137 & \cellcolor{green!27}2.19 \\  \hline
  \cellcolor{green!5}\small "thats just called being a \textbf{woman}" LMFAO i never laughed that hard in my entire life\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small as a guy i don't find that funny at all that's just being sexist and generalizing \textbf{woman} fk that.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small haha you sissy\normalsize   & \cellcolor{green!5}Sissy & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small " SHUT UP! OMG juzt l00k 4t our prezident guys "Okay, let's look at him :  Stock market went up 5 billion in six weeks, lowered the astronomical tax we had, 200 billion off national debt out, didn't get rid of the labor unions that progressives created and shielded it instead, fortified the political relation with Russia and China, 2 million new jobs, and is doing the best he can't to avoid US from becoming like current Sweden for all that \textbf{zero} regulation of illegal immigrants that have fucked up that poor country......\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small What are we supposed to look again ??  ....OH, YEAH. Him just saying he would grab some \textbf{pussy} and that he wants to build a wall with staff to protect our national border.No, seriously, what are we supposed to "look at our president" for?  ðŸ‘ŒðŸ˜‚\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small NIGGA XD\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small everyone's entitled to their opinion.  it's pretty \textbf{common} to not find \textbf{sexism} humorous, and people are allowed to voice that if they want.  people in these comments are just getting offended by people being offended.  people get offended or at least bothered- that's normal.  also, everyone has a different sense of humor.  even if something is intended to be a joke, it doesn't mean everyone will or should take it as  a joke.\normalsize   & \cellcolor{green!5}Common, Sexism & \cellcolor{green!5}Gender - General, Social Class - Working class & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small Except... it WAS a joke. There's no room for interpretation, he's a comedian. You can either get your panties in a bunch like a hysterical \textbf{woman}, or you can recognize it for what it factually was, a witty comment delivered at precisely the right moment for maximum laughability. We're all getting tired of the politically correct bullshit, and being a SJW actually harms your cause, so stop it... or be ruthlessly ridiculed.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small Carter Blunt do you genuinely think jokes have "no room for interpretation?"  I believe jokes greatly depend on it's interpretations.  there are people who will find it downright funny, maybe a little "funny ouchy,"  or just not funny at all.  that's okay.  imagine if everyone had the exact same sense of humor.  it sounds like a pretty boring world, doesn't it?  it seems like a world that lacks individuality.  imagine if someone said something extremely insulting towards you or a family member- something so hurtful that there's no way you would genuinely find it funny.  say the person who said it then stated that it was a joke.  does that then make you laugh?  i mean, it must considering that your logic is that anything meant as a joke must be taken as such and everyone must find it funny.  you are way more acting way more offended than anyone who was offended by the joke in the video.  i mean, i do believe it is okay to be offended by things but it is very hypocritical in your case.  why is it so hard for you to cope with the fact that some people just don't find the joke funny?  i think you are lying to me.  i think your saw that it was sexist and were ready to have a field day with anyone who didn't like it by calling them an "SJW."  i also think you added to the \textbf{sexism} ("hysterical \textbf{woman}") in order to get a heated response from me.  I've dealt with people like you before.  there are people all over the internet who are exactly like you.  this isn't new to anybody.  go ahead.  ridicule me.  you'll see that i won't back down because of childish behavior.\normalsize   & \cellcolor{green!5}Sexism, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/293 & \cellcolor{green!5}0.683 \\  \hline
  \cellcolor{green!27}\small it's interesting that you assert that jokes can't be offended.  maybe you've never been offended by a joke, but you are in no position to control what others think and say.  also, you stated "it WAS a joke. There's no room for interpretation, he's a comedian."  the fact that you claimed that there is no room for interpretation means that you believe your interpretation of the joke is the interpretation that should be shared by everybody.  it sounds ridiculous but hey, you're words, not mine.  I'm not completely sure why you're calling me a hypocrite.  i genuinely found your response a little confusing.   what i think you mean is that me calling your actions childish behavior is me sneakily insulting you.  I mentioned this because you claimed you would ridicule me for taking a position different from your own, which many would probably agree is childish.  i was letting you know that if this was continued, it is not something that will cause me to give up.  i believe people come to their senses at some point.  i at least like to try to make that happen.  sure, maybe it was an insult.  however, let's not forget that you insulted me first by calling me a "hysterical \textbf{woman}."  i assume at this point of your reading of this comment you are thinking it would be a good idea to ridicule me for being "offended" at that insult, but i'd like to remind you before that that you were initially offended by me calling you childish.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/255 & \cellcolor{green!27}0.392 \\  \hline
  \cellcolor{green!5}\small "it's interesting that you assert that jokes can't be offended." Can you read? For the second time, I never said "jokes can't be offensive", jokes are SUPPOSED to be offensive, that's what makes them come out of nowhere and ninja your funny bone. Though they can't be offendED, since a joke isn't a sentient being that cares about its feelings. Check what you wrote. Christ, it's painful addressing your retarded assumptions.The interpretation of a joke is your own fucking business, what's NOT open to interpretation is the FACT he was FUCKING JOKING!! Are you saying certain jokes shouldn't be allowed? Then fuck you!!And the hypocrisy in your case, is being against name-calling when you called me childish and sexist, just in a cowardly indirect way. This is us still going around and around in circles! You're a waste of time. You're not an intellectual, you're an intellectual \textbf{lightweight} who lacks basic reading comprehension. You're not even addressing my points, you're attacking strawmen.Now is the point where you get to prove you understood the joke, cause I just think you're stupid at this point. So, what was he implying when he said "that's just called being a \textbf{woman}"? Go ahead, interpret.\normalsize   & \cellcolor{green!5}Lightweight, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/203 & \cellcolor{green!5}0.985 \\  \hline
  \cellcolor{green!27}\small obviously that first sentence was a mistake on my part.  no one would write that and mean to say that.  what i meant to say was, "it's interesting that you assert that people shouldn't be offended by jokes."  i was typing fast and then got mixed up, oops.  however, you can easily figure out what i meant by reading what came after that.  kind of embarrassing that you thought i meant something else considering the context... yikes!  you have a problem with people being offended by jokes.  we know this.  i never implied that certain jokes shouldn't be allowed, so you're in fact using a logical fallacy, actively throwing your argument down the drain.  good job.  i never called you sexist, but it doesn't take a genius to figure out that the joke is sexist.  whether or not it is offensive to someone or not is up to that person.  \textbf{sexism} is defined as, "prejudice, stereotyping, or discrimination, typically against women, on the basis of \textbf{sex}."  the joke in question matches this definition because it stereotypes women as not being able to listen and only hearing what they want to hear, if i remember the video correctly.  whether you find it funny or not, it is in fact inarguably true that the joke is sexist.  it is up to you whether you find sexist jokes or at least some of them funny or not.  I already explained calling you childish, so it would be tiring to have to go over that again.  strange that you think i lack reading comprehension while you couldn't actually be bothered to read my comment regarding exactly what you are telling me now.  if you read it, you wouldn't have to be explaining to me what you are calling me a hypocrite for.  it's hard to explain to you when you haven't actually read what i said in my previous comment, so go ahead and read it.  i don't know what your point is at this point.  I guess it would make more sense to say that people's overall opinion toward the joke is what we are talking about.  i really hope this isn't the way you talk to people in real life, by the way.  you will soon find out how much that just won't work for you.  ask yourself this:  why is it bad for someone to be offended at a joke?  should everyone have the same opinions as me?  should \textbf{nobody} ever be offended?  will using bullying as an argument tactic actually further my point and enhance my argument?  maybe answering these will help you actually think critically for once.\normalsize   & \cellcolor{green!27}Nobody, Sex, Sexism & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/438 & \cellcolor{green!27}0.685 \\  \hline
  \cellcolor{green!5}\small "non binary feminized cucks" wtf? you need to brush up on your insult skills.  that sucked!  also, i am clearly facing "scrutiny against my views,"  that is why i'm here talking to you right now.  i explained both the \textbf{sexism} and the childish behavior, and i know it's not a good argumentative strategy to outright name call people which is why i tried to find a more polite way to criticize you.  i never once even thought of calling you personally sexist, because that isn't what the argument's main focus is.  as for childish behavior, i can admit now with certainty that that is what you are demonstrating.  if you think your acting like an adult, you need to take a better look at yourself.  why would i pose a physical threat anyway?  clearly you don't know anything about civil debate, because physical violence will most likely not do you any good.  i also know it will not help my case either, which is also a good reason to not engage in it.  your argument is, in the kindest possible way, completely moronic.  "if it is a joke, you shouldn't be offended."  who the fuck cares?  anyone is free to feel however they want.  i promise you you will be okay if someone is offended by a joke.  you will be perfectly fine... unless something is very wrong with you.  i know your probably just skimming through this right now counting out how many times you're going to call me a \textbf{pussy} in attempt to hurt someone else to make up for your lack of self esteem, but just continue reading for a moment to consider this example:  who's saying it?  say a jewish person makes an anti-Semitic joke.  next, say a neo \textbf{nazi} says the same joke.  context matters.  your argument is one of the most unintelligent i've ever heard.  however, the thing is, you probably think you're edgy for laughing at \textbf{sexism}, \textbf{racism}, etc and maybe the only option here is to wait a few years until you violently cringe at your past self.  it might take a while considering how you are covering your eyes and ears and screaming your head off to avoid any argument that contradicts your own.\normalsize   & \cellcolor{green!5}Nazi, Racism, Sexism, pussy & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Gender - General, Nationality - Chinese & \cellcolor{green!5}5/373 & \cellcolor{green!5}1.34 \\  \hline
  \cellcolor{green!27}\small If a Jew makes an anti-Semitic joke, that's self-deprecating humor. It can be funny. If a neo-Nazi makes an anti-Semitic joke, that's meant as an insult, but can also be funny. If a German makes an insensitive joke about his friend, like "shut this Jew up or he's going in the \textbf{oven}", that's definitely funny. Anyway, I'm ready to rest my case. All we're doing is arguing in circles. You'll never admit insinuations are the same as name-calling, and I'll never agree name-calling is childish.\normalsize   & \cellcolor{green!27}Oven & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small just so \textbf{dumb} i cant take it ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Bitch is so \textbf{dumb} she probably knows america and a 1 in a million chance she knows china\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small +WassupHD Tell me how it's racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@WassupHD Aaaaaand? Do you know the definirion of \textbf{racism}?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@WassupHD You really are stupid, aren't you? Here, let me help: 1 look up the difference between \textbf{racism} and \textbf{nationality}.2 look up the meaning of the word "joke."3 re-watch the vid and take note of it's tone. 4 re-read my post5 get your mammy to explain it all to you6 enrol in pre-school\normalsize   & \cellcolor{green!5}Nationality, Racism & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small +WassupHD Neither Buddhism nor being Chinese have anything to do with \textbf{race} or \textbf{racism}, you numbnut. Hard to belive that you are honestly this stupid, but I just watched a video where a \textbf{woman} thought that Europe is a country so I guess anything is possible.\normalsize   & \cellcolor{green!27}Race, Racism, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}3/46 & \cellcolor{green!27}6.522 \\  \hline
  \cellcolor{green!5}\small \@WassupHD Yes, it's used by dumbass SJW and PC folk that can't tell their asses from their faces. Not a vaild source of information, if you ask me.I actually recommend that you look up the DEFINITION of \textbf{RACISM}. Here's a hint; the meaning is hidden in the word.Harrassing someone because of their \textbf{nationality} is not "fine". But it's not fucking \textbf{racism}. On the same premise I could say that harrassing buddhists is \textbf{sexism}. That's the type of error you're doing here. You should actually learn the meaning of words before using them. There are different types of discrimination and \textbf{racism} is just one of them. You can't use \textbf{racism} to describe EVERY kind of discrimination, less you want to make an ass of yourself publicly.\normalsize   & \cellcolor{green!5}Nationality, Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}6/127 & \cellcolor{green!5}4.724 \\  \hline
  \cellcolor{green!27}\small \@WassupHD \textbf{Xenophobia} works, thought it is broad and also inculdes \textbf{racism} under it.Ethnocentrism is another example, thought I consider it more gentle.\textbf{Nationalism} is rarely used, and mostly is reffered to political ideologies, but the definition is "feeling of superiority of one's \textbf{nation} over another" so that goes as well. Althought I consider it the best one, many people actually think that's something to be proud of, confusing \textbf{nationalism} with patriotism.\normalsize   & \cellcolor{green!27}Nation, Nationalism, Racism, Xenophobia & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}5/72 & \cellcolor{green!27}6.944 \\  \hline
  \cellcolor{green!5}\small +Wayne Elliott boy i did my research is isn't in Turkey. you are so fucken \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small She's not \textbf{dumb}.Alot of people don't know that\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small directioner styels no child left behind.  Welcome to US public education.   I once worked with a geriatric nurse who knew \textbf{nothing} about foreskin.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small this bitch is dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She come in 6th on American Idol. Has a net worth of 1.5 million. She must not be to \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small SimplebutAwesome   "...2 continents together." My 7 yr \textbf{old} daughter knows the difference between a continent and a country. How can YOU possibly make fun of this \textbf{woman}...who is undoubtedly a blood relative?\normalsize   & \cellcolor{green!27}Old, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small being rich doesn't mean you're not \textbf{dumb}, just look at your president :p\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Chris Wheatley Yeah, but they're so \textbf{dumb}, they probably wouldn't survive\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small I understand the humour in this but Its more fun making feminists look stupid than making a sweet cute \textbf{woman} look stupid.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Did you hear that thick southern accent? Obviously a Republican. Notice the fact that she knows \textbf{nothing} about geography outside of North America. Typical shit-for-brains Republicans trying to make everything about politics.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small John Jones Your so \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small ... \textbf{Ho}... LY..... Crap\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small She is so \textbf{dumb} i Want to strangle her\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Wtf how \textbf{dumb} is this bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Omg she is sooooooooooooo dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Hungary = hungry.. what a \textbf{dumb} host\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small She isnt \textbf{dumb}, she is retarded. Sometimes I wonder how a person made it so far without getting eaten by wild animals. She is an insult to evolution!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small how can any \textbf{woman} be that pretty and so uneducated at the same time.???lol\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small "Like, I'm listening to what you're saying, but I only hear what I want to.""That's just called being a \textbf{woman}."LMFAO0:58\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small She ain't that \textbf{dumb} after all otherwise she would've said France!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small TheMoonlight2887 Your \textbf{dumb} as fuck keep your \textbf{dumb} ass blondes\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small If she was a Democrat, she'd of got greedy and lost it all. It's always easy for them to toss money away, since they don't work for it. Also, at least this girl is easy on the eyes. Democrat women are all disgusting \textbf{fat} \textbf{pigs}.\normalsize   & \cellcolor{green!27}Fat, PIGS & \cellcolor{green!27}Nationality - Southern European, Physical Identity - Physical Features & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small Also, I wish people in the comments wouldn't put the kind of shame I see on Americans. I mean, I took an IQ test recently and got a score of 126. Hopefully this doesn't sound like bragging (which isn't my intention) but I've received 2 academic awards, 1 award for Fine Arts/Athletics for keeping at least a 3.25 GPA and 95 attendance, 1 gold president education award and 1 silver award signed by Barack Obama including letters from the White House, 1 award for 2nd place in an essay contest, 1 award for reading and understanding, a certificate of achievement for a project at school, and awards for science, social studies, and mathematics for keeping a high grade all year. So, we're not all like this \textbf{woman}. (Please don't think of this as a way of showing off and being snobbish. I hope it doesn't seem like that. And maybe we could let some stereotypes aside before another flame war ensues.) Okie dokey?    \normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/164 & \cellcolor{green!5}0.61 \\  \hline
  \cellcolor{green!27}\small Jazzy Wood I know !!!!! \textbf{SEX} and shopping lmao\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small dumb ass hillary lover, go hang out with your feminist friends in your safe spaces\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Damen Rowland Ahh yes the simplistic thinking of Trump supporter assuming anyone pointing out the fact that Trump supporters are \textbf{dumb} that i must be a Hilary supporter...Well i can't stand Hilary, and you really need to stop assuming because \textbf{dumb} baseless assumptions is the fuel of the typical Trump supporter.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small +Michael Parker I support trump. I'm against illegal immigration and Syrian migrants. I'm not \textbf{racist}. I care about safety first.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@A55KIKO Trump has so little support from the people, politicians from both sides, and the contributors that own the politicians that Trump would be the most impotent president in history just making a lot of noise and looking like a fool as \textbf{nothing} he says gets done, and in the end that will lead to the establishment having even more control than if a non clown president who actually has any policies was there.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small \@Michael Parker The BAD things hillary has done has overshadowed trumps bad things by miles, yet all people talk about is what trump sed 20 years ago to a women lol she killed 5 men she flip flops on \textbf{g\textbf{ay}} marriage she takes money from arabs n wall street for her campaign, being investigated by fbi, shes corrupt and a lair, hillary is the establishment hes taking them on, your so brainwashed from liberal media and even obama has endorsed her, we all know shes going to be a crap president, people are scared of change, 3rd term obama, there not for him cause hes not a democrat duhh. just watch in 4 years everybody will be moaning shes a crappresident cause we all know she will be\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/129 & \cellcolor{green!5}1.55 \\  \hline
  \cellcolor{green!27}\small \@Damen Rowland Don't make \textbf{dumb} assumptions that because i recognise Trump as a joke that i support Hilary.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small She's smart enough to to have a career doing what she loves, and have people pay her millions to do it. The \textbf{dumb} blond act is schtick,  Marilyn Monroe and Goldie Hawn also used it, it's \textbf{nothing} new. Most people are intelligent enough to recognize schtick. Unless,  you are one of those people who think that Larry the cable guy, is actually a cable guy.\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small \@RT S She was a cheerleader, a beauty queen, and worked in a restaurant before ending up on reality TV.\textbf{Nothing} there speaks this intelligence you speak of, and no one is good enough an actor to fake that vacant look on her face.So exactly why do you think she's clever when everything says she's \textbf{nothing} more than a ditzy blonde who got some success because people find her entertaining.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small \@laura m I get it Laura, you pity people you don't believe are as intelligent as yourself. It's kind of like how I feel about \textbf{fat} people. They're gross, always sweating and breathing hard. Their fatness only shows that they're too lazy and weak minded to not control what they eat.   It doesn't matter if they're talented, successful, kind and generous, they're still \textbf{fat}. Sorry if I sound shallow, it's going around. The point is, people who live in glass houses shouldn't throw stones.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Kevin McGovern \textbf{Nothing} about anything she's ever done makes her seem that intelligent, so why do you think you're right while everything else says you're wrong?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@Michael Parker Strange, everyone else calling me wrong seems to be just you.Have you seen this \textbf{woman} off camera? Its an act, she is a comedian/actress and made a nice living from just acting \textbf{dumb}, pretty sure theres no easier way of making money legally. So she found the easiest way to make heap of money, I sure would like to find an easy way of becoming rich, wouldn't you? Do you do less for your wages?\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/78 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@Michael Parker Oh but I do agree the fact Trump is even a candidate and still in the \textbf{race}, shows the lack of intelligence in his supporters. He is a proven liar and not even a good businessman, he failed more companies than succeeded.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small vote bernie for \textbf{g\textbf{ay}} \textbf{communist} america\normalsize   & \cellcolor{green!5}Communist, Gay & \cellcolor{green!5} Ideological and Political Identity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}3/6 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Spot on. Typical audiences are easily suckered by media manipulating them to feel "smarter" than they really are and thereby feel a superiority they rarely can rationally feel in their real underwhelming lives. Ya know - morons - like many "average" uninformed, average IQ people that wants to be sold on something that makes them feel good rather than do the hard thinking and face their problems. AND do that rather than INTELLIGENTLY demanding their leaders do the same for the country they've actually taken pains to adequately inform themselves about, policy and history wise. Anyway - her act was too timed with the perfect lines like a performer trying to convince us she's THAT stupid and IGNORANT. An obvious act to get exposure on a show with producers wanting to \textbf{spike} ratings. One of the many "secrets" in the "reality" and game show TV industry. Of course - if she said, "Hungary" - would the producer's have hurt her career and held back her prize money? It's a secret......\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/170 & \cellcolor{green!27}0.588 \\  \hline
  \cellcolor{green!5}\small At least that's better than the typical narcissistic \textbf{libtard} crooked Hillary supporter......\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small ha sorry, \textbf{common} mistake\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Jacob West I was thinking the serial rapist named Bill Clinton, but the illegal \textbf{alien} invaders works too.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Roses are \textbf{r\textbf{ed}}Harambe's in heavenEveryone knows Bush did 9/11\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small \@Damen Rowlandya i agreen and im just a random 12 year \textbf{old} with gun lol idk my dad says trumps better gotta listen to dad bye gotta feed cows\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@travisbaskerfield Trump is very much an exception to the standard two party system, so in no way can you \textbf{lump} him in with the standard lack of choice explanation.\normalsize   & \cellcolor{green!27}Lump & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Michael Parker trump supporters are mostly guys and Hillary have supporters who are mostly women and transsexual\normalsize   & \cellcolor{green!5}Transsexual & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small LMFAO please don't say that to blonde \textbf{woman}, it will take them to long to get it causing major problems in the space time continuum resulting in less chores being done and more questions being asked!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Is Canada a country? I thought it was just a bunch of bears and guys riding horses with big \textbf{r\textbf{ed}} hats! Looking after Bullwinkle and is sidekick.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small \@Rob Kramer well you're not very intelligent then are you, just remember that stupid people are to \textbf{dumb} to realise that they are stupid.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small faimzan21 I'm not \textbf{dumb} cuz I know Africa is a continent\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small When she said she thought Europe was a country that's like as \textbf{dumb} as saying Canada's a state\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Honestly... I am hurt. Just because I am blonde doesn't mean I am \textbf{dumb}. Many adults don't know what us kids know today. I believe that she is smart in her own way. I didn't even know the answer and I am in 7th grade. I am disliking the video and I will NEVER watch another one of your videos. Who ever thinks all blondes are \textbf{dumb}, you are greatly mistaken. ðŸ‘¿\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small It's a general Stereotype that's mainly used by comedians that aren't funny enough to make jokes.Although if you think she is smart in her own way, i'd believe you are greatly mistaken. This \textbf{woman} is a \textbf{dumb} as bricks\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@Kayla MommsenÂ No, she is not, no one \textbf{dumb} enough to think Europe is a country is in any way shape or form capable of being smart at all. Even in their own way.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small +alex ojideagu FINE!!! I guess I don't like how they said \textbf{d\textbf{umb} BLONDE}... I am a blonde and I am really smart. I hate it when people say blondes are \textbf{dumb}. It is MEAN and CRUEL. I am DONE.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/39 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small thats just called being a \textbf{woman}. jeff is hilarious\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small That's Kellie Pickler, she made the top 10 (6) the year she was on American Idol.  She is a country music artist with a net worth of 5 million. Her shtick is to play the \textbf{dumb} blond, in this case Jeff Foxworthy is playing her straight man. It's a classic comedy routine, I'm surprised all you smart people didn't know this. There are lots of videos here on YouTube of her doing the same shtick on talk shows, award shows and her own show. You can also find her music videos on here as well.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small this \textbf{woman} is so cute\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small There is a big difference between the average USA person and the average European person. Stand in the middle of Europe and go in any direction for about 2,000km and you will cover most of Europe, which includes over 40 countries. Do the same in the USA and you will encounter at the most 4. In a country so vast as the USA I can see why geography of countries not making up the Americas may be \textbf{alien} to them.\normalsize   & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small not \textbf{dumb}, simply uneducated...she can learn.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Two words: \textbf{DUMB} LUCK. The little girl said Hungary.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small it is pronounced \textbf{hun} gary hungary so yeah im 12 how \textbf{old} is she\normalsize   & \cellcolor{green!5}Hun, Old & \cellcolor{green!5}Age - Over 65s, Nationality - German & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Even the host is \textbf{dumb}. It's called HungAry !!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small even my 10 year \textbf{old} brother knows the answer. i think she  never heard if going to  school .ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small haha she's \textbf{dumb} in a cute kinda way, i d still take her!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Nope, not scripted, Kellie Pickler is actually that \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Sexy AF but \textbf{dumb}?More like ugly and \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small +fernando juarez Yep, \textbf{Dumb}, uneducated white fucktards, well ugly and \textbf{dumb} asf, this one is just \textbf{dumb} but sexy asf\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/20 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small 100,000 Subs With No Vids Challange no, everything you said is a lie. Trump voters are the most uneducated demographic in America. Trump supporters are generally older and over weight so being a baby boomer and \textbf{obese} isn't fucking attractive. it's the opposite. and most of you are \textbf{racist}, look at trump supporters at rallys and the neo \textbf{Nazi} Kkk shit you Fuckers love. fuck trump and all his cult followers.\normalsize   & \cellcolor{green!27}Nazi, Obese, Racist & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}3/71 & \cellcolor{green!27}4.225 \\  \hline
  \cellcolor{green!5}\small dumb as a rock\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small that actually wasn't a stupid question, who knows the answer to that! certainly not me lolol am I a blonde bc I'm a \textbf{r\textbf{ed}} head\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Hungary. ...oh my God. .this blonde \textbf{chick} is \textbf{dumb} ?\normalsize   & \cellcolor{green!5}Chick, Dumb & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Anyone who believes that this \textbf{woman} is real, you are even dumber than the persona she's pretending to be.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Dumb fucking Americans\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I hate how everyone is like "Stupid Americans" instead of "Stupid American Government that these kids are forced to grow up and live by their \textbf{dumb} standards" or "Wow. The American Gov really f*cked up. Children are being raised to learn this and they don't know its wrong, but yet everyone bullies them about it." Also, not all Americans are \textbf{dumb}, just the big-shots kids. they don't give a sh*t. Teenagers like me in HS work three jobs and maintain straight A's but get no scholarship, just no one notices unless your daddy got money in the bank.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Americans are stupid though. Whether you like it or not. I'm American, but I don't hold the brainwashed belief in patriotism and \textbf{nationalism} that so many in this people hold. I call it like I see it; Americans are fucking morons compared to the rest of the world. This is a first-world developed \textbf{nation} with 6 of the most academically inclined universities in the world. Yet, more than half of the population can't even name world capitals. Americans are by far the most uneducated people in the developed world! That's just a fact! Americans always have this delusional false sense of superiority over the rest of the world; that somehow Americans are better than everyone at everything. When in reality; America doesn't lead the world in anything that has to do with academics. We're 7 in math, 22nd in science, 8th in literacy. America leads the world in only 3 things: military spending, number of incarcerated citizens per capita, and number of adults who believe angels are real... truth\normalsize   & \cellcolor{green!5}Nation, Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/169 & \cellcolor{green!5}1.183 \\  \hline
  \cellcolor{green!27}\small Shes not \textbf{dumb} everyone is smarter in their own way and if you really think shes that \textbf{dumb} you will regret it and blondes arent \textbf{dumb} and you are what you say so ya\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small +Madelyn Clemens she is \textbf{dumb}..\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small is she \textbf{crazy} or drunk?\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small +Lucky Rocket yeah 99 of reality tv is scripted, they wanted a hot girl, so a blonde girl, blondes have \textbf{dumb} stereotype hence they scripted it like that. she's really pretty.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small You're smarter than most of the people who are calling her \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Dumb as shit, but somewhat hot. This \textbf{woman} is perfect for PORN!\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small +Tyler F  well i'm a north \textbf{african}... i can educate you. but i will never make u understand mannersyou know what they say: "All generalizations are false, including this one.'\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Didn't say all \textbf{African} children, just making a point.....wondering why most Americans know \textbf{nothing} about geography of the world.\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small My 6 year \textbf{old} cousin is smarter than her\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Did she skip school or was she too \textbf{dumb} to find it\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Girl: I only hear what I want to.Host: Well that's just called being a \textbf{woman}.Applause to the Host That is too freaking true.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small I honestly think this was scripted, from the Hungary with hungry pronounciation and Turkey, to "that's just called being a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Louise Ricketts he was messing with her. To test if she is really that \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I swear, not all Americans are stupid. I knew the answer and I'm in 8th grade. People like her make other people think that everyone in the U.S is \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Oh she wasn't really \textbf{dumb} why did the title lie to me!?! ðŸ˜¬ðŸ˜¡ðŸ˜­\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small She's richer than you'll ever be. She's not as \textbf{dumb} as she looks or seems.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small But she's so friggin cute. Who cares if she's \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I love \textbf{dumb} bitches!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small +Peter she so \textbf{dumb} that she thought that Europe was a country and she thought the country of Budapest speak French omg!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Both the \textbf{woman} and the host are pretty \textbf{dumb}. It is not "Hungry", it is "Hungary". They forgot the "A"...\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small If your gona be \textbf{dumb} you gotta be tuff!!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small some whites are \textbf{dumb} as fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small 2:02 The kids thinking, holy crap this \textbf{woman} is stupid!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Shes not \textbf{Dumb}...she's just an American ;)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Everyone realizes this is Kelly Pickler, American Idol Kelly Pickler, Country Music Artist Kelly Pickler right?  Who's made millions marketing herself as the \textbf{dumb} country \textbf{hillbilly}.  She's no dummy...\normalsize   & \cellcolor{green!27}Dumb, Hillbilly & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small that \textbf{dumb} fuck doesn't deserve any money\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Why do people always put videos up about \textbf{dumb} blonds and if they see \textbf{dumb} brunnets they just push them of and get suprised when the blnd is smart ahhhhhhhhhhhhh i get so mad at \textbf{racist} people\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/37 & \cellcolor{green!27}8.108 \\  \hline
  \cellcolor{green!5}\small WHY ARE BLONDE GIRLS \textbf{DUMB}?! ITS NOT FAIR!!!! I AM BLONDE!!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}." Classic.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small good thing she's blond cuz of she wasn't then she would be just \textbf{dumb} (blond joke) (disclaimer I don't have anything against blonds, I promise. disclaimer over)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small She is like the new 12 year \textbf{old} kid. You give them there test and come back with 4 lions and a floating dildo\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "America, the most powerful \textbf{nation} on the planet" Q: How?\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Why is everyone hating on America? I'm from the UK, but I still think it's wrong! Not all Americans are \textbf{dumb}. I think that was \textbf{dumb} yourself for taking a few Americans and assuming that all Americans were like that! Rude?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Lilian Americans have invented more useful items and discovered more medical advances than the rest of the world combined.  You use car's, phones and have vaccinations.that keep you from getting terrible diseases.  You must be pompess.  If your European you aren't under \textbf{Nazi} Rule because our brave men have stopped communism, Hitler.  Most everything you touch was started in America.  Interchangeable parts.   Submerines,  TV, phones.  The electricity grid,. and on and on.  Now tell us three things from your country that has made the world a better place and things Americans use everyday.   Now are you smart enough to know you have been beat by a dumbass American.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small +Blank L Trust me \textbf{nobody} wants to American\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This \textbf{chick} is just for banging. Not debating the economic and political concerns of the world, and stupid chicks are the best!\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Dumb blonde: I'm listening to what you're saying but I'm only hearing what I what to...! hostdude: ..that's just called being a \textbf{woman}. DAYUM SAVAGE!\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small A person like her is judged as being \textbf{dumb} because she lacks knowledge of world geography as if its a given.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She's not the smartest but I think it's kind of rude that everyone keeps calling her \textbf{dumb} I mean she kind of is but still...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small thats just called being a \textbf{woman} holy shit lol\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small "That's just called being a \textbf{woman}" HAHAHAHHAHAHAH OWNEDDDDDDDD\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small this entertainment TV show probably paid her extra to deliberately act \textbf{dumb}....might just be one of the smartest Blondes ever!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Man I would like to...her silly. Bet that wouldn't take too long! Bet she's tight as a drum and makes "oh, daddy" noises when you flip her over and make her suffer. Dress her up like the little \textbf{b*tch} she is and finish in her mouth...\normalsize   & \cellcolor{green!27}B*tch & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Really pretty girl, really charming. \textbf{Dumb} as fuck, but pretty.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Accents mean \textbf{nothing} if her parents were born outside of Texas just like mine. Fortunately, I moved away from Texas before things got worse under Governor Greg Abbott!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small +Gingerboy987 Gam3r 13 she is \textbf{dumb} but pritty\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small +antoine tremblay I disagree. I'm really surprised how ugly she is. So made up, \textbf{skinny} lips, not great cheekbones. Really sub standard. Definitely not a beauty queen at all!\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Saying that Kellie Pickler was as \textbf{dumb} as a box of rocks would be an insult to the box of rocks.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small She's not pretty. Just \textbf{dumb} TrashGo to Sweden or any Scandinavian country and you'll see what pretty is. ..and the women are elegant and very Smart and friendly.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small antoine tremblay Pretty? Do you mean Pretty \textbf{DUMB}?  ;)\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small antoine tremblay Well Its much easier to handle a \textbf{Dumb} girl when you Compare with smart girls.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small DONT GO ON THE GAME SHOW IF YOUR SOOOO \textbf{DUMB}!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small LOL. they have a \textbf{hillbilly} as the host.\normalsize   & \cellcolor{green!27}Hillbilly & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small she's really \textbf{dumb} everywhere but America.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small +Pedro Lundergard actually not only did we invent this website weÂ invented the damn internet \textbf{dumb} bitch that account you made to respond to this video yea the one your using right now was made by Americans\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Well I am from Hungary and 50 percent of hungarians do not know what is the capital of Slovenia ( we have a \textbf{common} border  ) so it is not a big deal......\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small +Gzoli Gzoli dude. hungary is a bit diffrent. this \textbf{chick} thought that europe was a country. not only that, i don't know the capital of slovenia either and i was there 2 months ago\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@WK MacÂ Space exploration is done by Immigrants mostly, engineering students Â and profs Â in US universities are mostly foreigners and immigrants, and space researchers are mostly foreigners in Caltech and Nasa, oh and Spacex is founded by a South \textbf{African} Elon Musk... so yeah americans are 1 in everything when they get citizenship haha\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small +Spacefied And \textbf{zero} non-Americans that are smart, then again you dont have to be intelligent to work in a call center in some shit hole country.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small +SpacefiedÂ  Start with Alexander Graham Bell, Benjamin Franklin, Thomas Edison, Samuel Morse, Steve Jobs, Henry Ford, George Washington CarverÂ ... and the list of \textbf{dumb} Americans continues ...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small yes SpaceX, what's wrong with that ? as for the moon, \textbf{nobody} walked on it. there smart americans, the general public is stuupid that's all\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Need to more research about Bell because he was Scottish-born and died in Canada. Yes he lived in the States for many years and married a \textbf{woman} from Boston,but don't say he was American. In fact he did a lot of research in Brantford, Ontario, Canada. There's even a museum there showing his accomplishments. America shouldn't take credit for everything that is invented or discovered i.e Basketball was invented by a Canadian.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small That's Kellie Pickler, she made the top 10 (6) the year she was on American Idol.  She is a country music artist with a net worth of 5 million. Her shtick is to play the \textbf{dumb} blond, in this case Jeff Foxworthy is playing her straight man. It's a classic comedy routine, I'm surprised all you smart people didn't know this.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small \@RT S It's because NON Americans are \textbf{dumb} as shit.Â  They don't understand comedy.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Spacefied In the great U.S.A., the only requirement to run for president is that you be a natural born citizen and at least 35 years \textbf{old}. No class, caste or royalty are factored, no military dictators. But, our best and brightest, typically, choose not to enter politics. Which sometimes leaves you with a Trump or Hillary.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Well, that's a pretty \textbf{racist} thing to say!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small You're so \textbf{dumb} that you didn't realize that this is staged for entertainment.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Shaggy Rogers You sound much more educated than any American.  Your statement was almost grammatically correct.  LOL \textbf{dumb} ass.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Because she can sing dose not make her \textbf{dumb}?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small +Mr MC she can sing but she is \textbf{dumb} as shit\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Andrew messÂ <--scat \textbf{freak}..again..that illiterate rant means \textbf{nothing} as you are a mouth breathing idiot..seriously what the fuck did you just write?? Try punctuation and go back to 4th grade\normalsize   & \cellcolor{green!27}Freak, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small +Mr MC lmao u \textbf{dumb} af bruh do u fucking come to YouTube just to tell people their illiterate?? R u serious?? If you understand wat I'm saying y tf are u getting mad about it?? It's not a fucking English essay!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Mr MC lol you know \textbf{nothing} about my finances but Claim I'm poor lol and you call me \textbf{dumb} tut tut.....You judging people by there wealth and ranting on about "Mouth breathing" is hilarious lol\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small This argument has no meaning anymore. Just pointing out things the other has said and calling them \textbf{dumb} -.-\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small +Mr MC  lol, i re-read your comments as you suggested. i still fail to see where you actually recognize and admit her blatant stupidity. You just keep talking about money and charity work, ignoring the fact that she has the eduaction of a child in elementary school.... Anyway no, i will not take the time to explain all of the charitable ive done in my life to satisfy some moron loving troll who cant get over a conversation on the internt that started over a month ago. grow up dude, and get a life, Ive got \textbf{nothing} to prove.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small \@Kelli MillerÂ what do you mean you rest your case? You didn't even have an argument or present facts. OMG, you are a freaking idiot. You are just one of those idiot morons with \textbf{nothing} going on. You diss others just to pump up your \textbf{zero} self esteem or to appear cool or whatever. All you have done is call this girl names, yet you don't know her (as you have demonstrated). Most of all, you are not WORTHY of judging her, let alone ANYONE else. Here's a fact. this girl has DONATED more then you will earn your entire life!!! how small does that make you feel. This poorly educated girl is more worthy than you!It is amazing that people as stupid as you actually exist and try to have conversations!! It is truly hilarious. Enjoy your life in happy acres trailer parkLOL\normalsize   & \cellcolor{green!5}Nothing, Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/146 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small Holy fuck, this \textbf{chick} is so ducking stupid, if I saw her irl, I'd tell her my shit was some exotic chocolate and she's probably eat it... She should be shit in the fucking head...\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small +Katieboil Anegg you are the fucking dumbest person in the world, I know that there are 3 syllables in Hungary, and there are extremely smart Americans, I think you mean White people because Blondes are like the purpose of being dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@XxYumYumCookiexX FTW You are quite right. It was a bad comment, butÂ when you watch that \textbf{dumb} \textbf{woman} and then see hear the presenter, it's hard to hold you emotions! There areÂ millions of super smart Americans, and I am sure you are one of them. Those two - not so much (Although, I loved his comment about women)! Don't make it into a \textbf{race} thing. That really shows your stupidity too ;)\normalsize   & \cellcolor{green!27}Dumb, Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/73 & \cellcolor{green!27}4.11 \\  \hline
  \cellcolor{green!5}\small +Katieboil Anegg lel me too, also the most restarted are White people . . My Proof? Exhibit A, Donald Trump, Exhibit B, this \textbf{woman}, Exhibit C Scooter Kids and their Mom's\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@XxYumYumCookiexX FTW Take it all in jest. There wereÂ many other American comments. JustÂ laugh at it.Â I read you message again - \textbf{race}. Now if there is one thing \textbf{black}Â Americans fail at every point, angle and grey area; it's \textbf{race}. It's always a \textbf{race} issue. Fundamentally,Â Â you lose your seating by bringing it up in a non \textbf{race} issue. Now that is \textbf{dumb}. I can answer in 3 languages - and you?! American-\textbf{race}-English-language you have down to a tee. Ciao!\normalsize   & \cellcolor{green!27}Black, Dumb, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/82 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small \@XxYumYumCookiexX FTW Dude, I appreciate you comment. I replied in an honest way. It's youtube, but you are making it into a \textbf{race} issue, so - you lose on all fronts. Now, I don't want to be mean, but your spelling is not great - so are you really that smart? Chill out, laugh at the video and don't take it to heart!?!\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small \@XxYumYumCookiexX FTW Anyhow, it's been interesting chatting to you. I thought the video was real funny and I know that not all American are this \textbf{dumb}. It must be morning where you are - it's very late whereÂ I am, so nightyÂ night and seriously - in the nicest way ever from behind a computer - chill! It's no personal attack on you.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}\small \@TheFerociousLimeIt actually stands for ' Movie Star Planet' Now fuck off before you get out smarted by a 12 year old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Link\$ Official it's only Texas and all the shitty states \textbf{nobody} talks about\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small this appallingly ignorant \textbf{woman} won Dancing with the Stars with Derek Hough. He has to be a genius, to convey instructions to her! She is an excellent dancer, but is pretty pitiful in the realm of knowledge.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Exactly, \textbf{nothing} exists outside of Texas\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Lizzie Lou hahaha somebody is triggered.  Did I ever comment on her wealth or value?  And you're using "foreign" as an insult?  Oh please, don't tell me you're one of those trumpeters are you?  Hickies don't realize that Americas got more than one \textbf{race}.  Bye Felicia.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@ RT S ...I was engaged to a "\textbf{d\textbf{umb} blonde}" She was actually quite intelligent, which is how she knew when and how to  play \textbf{dumb}. In real life she was an R.N. for over 20 years so it should be obvious she had the smarts to keep her job!. She realy came out with some real whoppers, though, too, which requires a sharp mind. Kellie did the same with the "I heard of Turkey".. Priceless. Not saying there aren't some really \textbf{dumb} blondes (and brunettes) but they tend to all be in California. Comes from selective breeding. In California  appearance generally takes priority over intelligence, so eventually the gene pool becomes corrupted ;-(\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/115 & \cellcolor{green!27}3.478 \\  \hline
  \cellcolor{green!5}\small I'm blonde and country and I am embarrassed by this \textbf{woman}. I also feel bad for her.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Cr1zby Soo you mean that blondes are \textbf{dumb} thats rude\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@rasbadosÂ Either she is really acting, or she is really \textbf{dumb}...\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small So \textbf{dumb}, yet so hot xD\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Announcer says; '' America ! ''\textbf{Chick} says; '' Duuuhh.  I'm Erica ? You are not Erica ! You are a guy. ''I wouldn't be suprised m9.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small +Lord Cr1zby It's called making contractions.. Good FUCK'S SAKE CAN YOU FUCKING STOP ACTING LIKE A PARANOID GRAMMAR \textbf{NAZI} LIKE YOU'RE FUCKING PERFECT WITH GRAMMAR YOURSELF?? I WOULD UNDERSTAND IF YOUR GRAMMAR IS PERFECT BUT YOU LIKE BARELY CAN'T EVEN MAKE A SENTENCE WITHOUT MAKING AT LEAST MORE THAN THREE GRAMMATICAL ERRORS. ALSO IT'S "IT'S" YOU ARROGANT SELF ABSORBED PIECE OF WORTHLESS SELF RIGHTEOUS HYPOCRITICAL FUCK!!\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small there are periods dumbass look closer, stupid bitchGRAMMATICAL ARROGANT CONCEITED FUCK THAT'S SUPPOSED TO BE."There are periods \textbf{dumb} ass look closer, stupid bitch. "You're acting like you're so perfect with grammar yet you yourself are too comically lazy to clean your grammar you stupid fucking hypocrite!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small dude your the \textbf{dumb} ass that's commenting on something weeks old\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small I would rather be a beautiful, blonde, WITH a compassionate heart than unattractive BUT intelligent, ANY day ! And so would E - V - E - R - Y \textbf{woman} ! Any \textbf{woman} who contradicts this is unattractive AND a LIAR ! So lay off the beautiful blondes already and quit advertising your ENVY ! Have you no idea just HOW mean, petty and pathetic you appear ? A beautiful ( OR plain unattractive ) \textbf{woman} WITH a loving, kind and generous heart can do just as much, if not MORE, to alleviate the suffering in this world as a BRAIN SURGEON and, in the end, that really is ALL that TRULY matters !\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/115 & \cellcolor{green!5}2.609 \\  \hline
  \cellcolor{green!27}\small seriously ????Stupid \textbf{woman} ..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small + Vance Stone I'd expect one to say "FYI this \textbf{woman} does by no means represent all Americans."You might be being facetious, but I've talked to people that actually believe all Americans are like this.And FYI this \textbf{woman} does by no means represent all Americans.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small +Vance Stone this one \textbf{dumb} \textbf{woman} represents millions of americans? WOW\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small face palming right now im Hungarian \textbf{dumb} blondes these days\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small beauty is \textbf{nothing} without brain\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small +Ambrielle \textbf{Fritz} how?\normalsize   & \cellcolor{green!5}Fritz & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Ambrielle \textbf{Fritz}Every person in that room is laughing and for a good reason.\normalsize   & \cellcolor{green!27}Fritz & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small +Ambrielle \textbf{Fritz} You hate him cause you didn't know the answer either.\normalsize   & \cellcolor{green!5}Fritz & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small +Ambrielle \textbf{Fritz} I LOVE THE BOY FOR THAT!!  He would get my candy any day, no trick, just treats!\normalsize   & \cellcolor{green!27}Fritz & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small +saad alkuwari Â Err, no I am not a paedophile by any stretch of the imagination. Â I was literally meaning "candy" (as in hard fructose, sucrose, and any other sugars) as a reward for a good deed, i.e. showing a \textbf{d\textbf{umb} blonde} how simple some of the questions were by smirking real smug.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small +Yulong ZHAO she's is faking it \textbf{dumb} ass\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Yulong ZHAO That's like asking why helpless people can't get any help. \textbf{Dumb} question.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small +Yulong ZHAO Because \textbf{dumb} people rule the world.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Caleb Block Yeah! Like that \textbf{hick} William Faulkner. I bet you couldn't even read his stuff (because of his poor grammar, of course)\normalsize   & \cellcolor{green!5}Hick & \cellcolor{green!5}Ethnicity - White & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small +Yulong ZHAO She is not a bad person.  Her mind is a mind of a five years \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Because instinctively she knows her value in lifeÂ is physical, not \textbf{mental}.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Because she is beautiful, talented, rich, funny and has a heart of gold. Being called \textbf{dumb} because she didn't know something that has never had any meaning or importance to her probably doesn't matter.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Yulong ZHAO Hell she's too \textbf{dumb} to know what ignorance is!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small +Michelle Griffin The smartest kid in my Midwest school was a White boy from Alabama, who regularly scored in the top .0001 in the \textbf{nation} on tests. My dad was born in Virginia. He had a genius level IQ, and he was a powerlifter. I know that some of the schools and teachers in some school districts down there suck, but I'm not down with your self-hate.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small John Gold Self-hate? Please! Don't comment on things you no \textbf{nothing} about....Me for example.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small THIS STUPID COW. IS HE FORGETTING THAT A \textbf{WOMAN} GAVE BIRTH TO HIS UGLY ASS?. WHY, DISRESPECT \textbf{WOMAN} LIKE THAT?.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small she seems so cool and like a nice person :)1 question wont make her \textbf{dumb} if she didnt answer it the \textbf{dumb} people here are the one judging her by that\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small When Southern blondes think that Eirope is a country, you might be a \textbf{d\textbf{umb} blonde}.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small How did you come to that conclusion? Is it just because he's smarter than a \textbf{woman}?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small +Quinton Hall have you no respect for a \textbf{woman}!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Lord Cr1zbyÂ Just don't be \textbf{racist} and say stuff like your last comment against Muslims and 3rd world people. Â It isnt being tough...you are just being a bigot.You are the perfect example why no-one likes americans around the world. Â I wouldn't piss on you if you were on fire 14yr \textbf{old} pussyboy.\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small +Quinton Hall \textbf{Dumb} \textbf{chick} and a cup?\normalsize   & \cellcolor{green!27}Chick, Dumb & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small \@vann dilzen do you even scat \textbf{sex} bro?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small And before you turn on me let's get it straight I'm all for trashing this 14 yr \textbf{old} poisoned  bigot  that's giving us a worse name I'm just saying try a little harder maybe proofread\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small THAT \textbf{CHICK} WAS \textbf{DUMB} ðŸ˜‚ðŸ˜‚ðŸ˜‚\normalsize   & \cellcolor{green!5}Chick, Dumb & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Every time I heard this \textbf{woman} speak I felt my brain cells committing suicide 1 by 1... I lost 4 IQ points by watching this.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small I bet you that \textbf{dumb} ass never went to school\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Look at Australia,It's a Country and a Continent,But she still is Dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I absolutely love \textbf{dumb} chicks. They are the easiest to lay\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small thats so mean saying "thats just called being a \textbf{woman}"\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Bassam Yaghmour She was \textbf{crazy} cute anyway   \normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small this is why aliens wont visit us its coz theres fucking \textbf{dumb} people in the world\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small That guy is \textbf{dumb} not the girl\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Mia RomeroÂ The girl is \textbf{dumb}. She thought Europe was a country.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small +Jenni \& Sammy That's a \textbf{weird} thing to get annoyed by. The Southern US dialects tend to monophthongize some diphthongs. Oil for example becomes ohl, and all other words with the same sound tend to follow the trend (soil, boil, foil, toil, coil, etc). Are you perhaps FROM Hungary? Then it might make more sense. Otherwise, who gives a fuck?\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Hungary: Southern Belle Kell, like Attila The \textbf{Hun}, Magyars, Khazars, Kentucky Fried Chicken and Wendy's.\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small She's as \textbf{dumb} as a box of rocks, but damn she'd be fun. Give me 48 hours in a hotel room with her.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Even though a \textbf{woman} who looks like this is the object of the non-white man's desire, I still wouldn't waste my time on this air-head bimbo\normalsize   & \cellcolor{green!27}Bimbo, Woman & \cellcolor{green!27}Gender - Female intelligence, Gender - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@ventor11225Â But smart people remain smart, there is no excuse for her to be this stupid when smart people still exist lol. She is just \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I don't think that she is stupid but ratherâ€¦ not very bright when it comes to geography. I was never taught geography until last year, so I would probably be saying remotely the same things as her. However, I do not think that I am stupid, becauseâ€¦ well I can spell. I guessâ€¦ I don't know I don't have proof that I am not utterly stupid, but I do think that calling her \textbf{dumb} isn't completely true. She just needs to get better at geography.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small Huhâ€¦. I wouldn't call her a \textbf{D\textbf{UMB} BLONDE} 'cuz that sounds like an insult to smart blondes, i'd just call her a PERSON WITH NOT TO MANY SMARTS.\normalsize   & \cellcolor{green!5}Dumb, Dumb blonde & \cellcolor{green!5}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I only started learning it last year, and I still know absolutely \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small What a \textbf{dumb} shit\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Im blonde and not \textbf{dumb}.Wow she is. NAJA AMERICA LEUTE SIND EBEN SO.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small wat a \textbf{dumb} bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small She's so \textbf{dumb}! Â Does she write her own songs? Â If so, I wonder how with that pea brain of hers.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Country. Â There is no E in Country. Â  Sincerely --- Â A \textbf{dumb} American. And im southern. Have a nice day.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small *Country, please dont mock others when you cant even spell. As \textbf{dumb} as she is, you made yourself look just as stupid...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small NO IM NOT \textbf{DUMB} DONT U DARE CALL ME \textbf{DUMB} I WAS TIRED AT THAT TIME AND WHEN IM TIRED I CANT SPELL PROPLY\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small You are dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small she is an illiterate southern \textbf{dumb} fuck\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small another \textbf{d\textbf{umb} blonde}Â but well she looks good, so I guess brain is not necessary :l\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Whoa there. Just because one person who lives somewhere is \textbf{dumb} doesn't mean everyone is.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Yeah shes probably really \textbf{dumb}. But ignorance is not correlated with intelligence.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small woman stop just stop !!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Can people really be that \textbf{dumb}? I knew that France was a country when I was 3 YEARS \textbf{OLD}!!!\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small those kids were just laughing at the level of stupidity. The little boy was just laughing to himself. Sanders was so patient with this \textbf{woman}!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Dumb and Dumber\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Americans...they're funny, they're so undereducated and retarded, they only know about their own country and \textbf{nothing} else - but what do you expect from people who still believe in God? :DÂ  The Land of the \textbf{Dumb} and the Home of Retardation...\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small \@KIDDDÂ lol not all Americans are like that. I happen to be one. but God? yes, we do believe in God (again not all of us) I do and so what isn't everyone entitled to their own beliefs?? You can't judge a whole \textbf{nation} based off of one person. Me personally, there is a lot going on now that does make us look bad but again, you shouldn't judge a whole \textbf{nation} based off of one or two people.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small to believe in a god you need to have a religion, to have a religion you need to be able to read. and to be religious you need to be able to understand the holy book you read. i doubt the girl in the video above is religious and the kids of this generation 8/10 don't believe in god especially in america. you sir are one \textbf{dumb} bastard for that comment lmao stupid\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small No!!!!! I'm from America and I'm not stupid like that. For one thing she's from Alabama or one of the southern states and just doesn't know shit, but were not all \textbf{dumb}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small not all Americans are stupid...the ones who aren't are mentally \textbf{disabled} which this poorÂ waste of matter is.:(\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Frank Kojafreedom?I'm not \textbf{racist} and I'm an American citizen but some English people navigating to USA in search for a better place dosen't sound like freedom.Of course,we had a civil war but....not actually freedom\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I get it this women is really stupid, but don't compare the rest of America to that \textbf{bimbo}.\normalsize   & \cellcolor{green!5}Bimbo & \cellcolor{green!5}Gender - Female intelligence & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Frank KojaÂ Americans where the first people to land on the moon? Funny one. I challenge you to tell us who landed onthe moon next :P No one else- you should know that isn't it? You are from the US after all.The united states (America is a continent, not a country) is the only 1st world country to still mix religion with everything else including politics. You can't imagine how \textbf{dumb} it sounds to hear politicians say "God bless America" from any other civilized country who evolved past that point a while ago.The US should also let go of the obsolete \textbf{old} British Imperial system and convert to metric before it's too late :P\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/115 & \cellcolor{green!27}1.739 \\  \hline
  \cellcolor{green!5}\small \@campingkillenÂ That's just basically saying we're as \textbf{dumb} as her, which isn't true. We know about the US and that it's not just one big slab of land as you call it. Wherever you got that idea is beyond me.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small So \textbf{dumb}... but DAMN shes so fucking cute!!! Thats the kind of \textbf{woman} I need!!!\normalsize   & \cellcolor{green!27}Dumb, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Well, this girl is not very Bright...But most EuropeanÂ´s donÂ´t know much about the different states of the US either, itÂ´s just looked upon as a big slab of land basicly...(I know it isnÂ´t)But one big difference is that most of the countries in europÃ© has their own language,  and some really \textbf{old} history..USA is a not a very \textbf{old} country, that really must be better to learn out more important things than the great baseball stars.....Spent like a year in the US, so IÂ´ve heard some stories.....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/92 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small And blondes wonder why they are stereotyped as \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small You guys know the show when they take some \textbf{African} tribes to the civilization (eg NYC) so they can observe their shock and reactions? I would do the same with Americans and take them out of the US. 'Would be hilarious to watch, even more funny. I really hope someone is going to figure out that soon.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Seems like you Americans need to learn Geography. Here in Greece we started learning about countries in 1st grade. This is the show "Are you smarter than a 5th grader?". And this is a 3rd grade question. Even in 1st grade, i'd knew that answer. Dude, did you ever go to school, or listened in class? I'm sure you have done it in Geography... Unless you Americans are really \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Umm why are all the adults more stupid thent he kids then when the kids get older they are more stupid then there kids do people get stupid with age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small There is no way. She must of been just pretending to be that \textbf{dumb}. Right? Right? Please tell me that I'm right? Please!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small its really obvious she's playing being dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small she's only having a blonde moment , but to say she's totally \textbf{dumb} ....  i doubt very much...  she will have skills that aren't shown off in this game show... which is a waste of time... just saying turn off the television \& go do something more interesting instead\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small "Thats just called being a \textbf{woman}" DAMN FOXWORTHYxD\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The ironic thing is she's on a reality show now too. I think she's obessed with them. I mean first, there's American Idol. Then this show, Are You Smarter Than A Fifth Grader. Now, she's on Dancing With The Stars. It's \textbf{crazy}!\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small she though Europe was a country....I mean really.....how can anyone be sooooo \textbf{dumb}.....\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small dumber than \textbf{dumb}.....this is a perfect reason, why Americans consistently rank low on the education scale........shocking...pick up a book and stop watching NASCAR....\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small if she were of another persuasion you probably wouldn't love her; she'd be \textbf{dumb}, stupid or otherwise...smh - tell me who doesn't know France is a country!!!!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small I don't if anyone realizes this. I mean, there's gotta be some people that know.  But I'm just gonna say it anyway. This girl is not just some average "\textbf{d\textbf{umb} blonde}", she's famous. She was on American Idol. She's a country star.  I'm not trying to offend anyone by saying this but I just thought I should get that out there.\normalsize   & \cellcolor{green!27}Dumb, Dumb blonde & \cellcolor{green!27}Gender - Female intelligence, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small Amazing what people can get away with just offering \textbf{sex}...............\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small shes smart compared to some of the shit i've heard from people take the fact that some girl didnt even know how to spell april which just so happened to be her name an the month she was born in so for an american to know something not many europeans know themselves is nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman, Sex, Chick, Sexual, Gender, Sexism & \cellcolor{red!27}459 & \cellcolor{red!27}459/159832& \cellcolor{red!27}0.29 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Dumb, Crazy, Eugenics, Freak, Weird, Blind, Disabled, Mental, Mong & \cellcolor{red!5}1141 & \cellcolor{red!5}1141/159832& \cellcolor{red!5}0.7100000000000001 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nation, Immigrant, Nationalism, Nationality, Alien, doctors, Xenophobia & \cellcolor{red!27}48 & \cellcolor{red!27}48/159832& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female intelligence}  & \cellcolor{red!5}Dumb blonde, Bimbo, Make me a sandwich & \cellcolor{red!5}89 & \cellcolor{red!5}89/159832& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Nobody, Zero, Lightweight & \cellcolor{red!27}125 & \cellcolor{red!27}125/159832& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}Gay, Homosexual, Queer & \cellcolor{red!5}12 & \cellcolor{red!5}12/159832& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Gay, Faggot, Fruit, Queer, Sissy & \cellcolor{red!27}23 & \cellcolor{red!27}23/159832& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Senior, Elder & \cellcolor{red!5}85 & \cellcolor{red!5}85/159832& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Ho, Tart, Hooker, Tramp, THOT, B*tch, Slapper & \cellcolor{red!27}21 & \cellcolor{red!27}21/159832& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Hillbilly, Common, Cheesy, Trailer trash & \cellcolor{red!5}34 & \cellcolor{red!5}34/159832& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racist, Racism, Race, Ethnic & \cellcolor{red!27}78 & \cellcolor{red!27}78/159832& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}pussy, Yellow, Oriental & \cellcolor{red!5}17 & \cellcolor{red!5}17/159832& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Hun, Herman, Jerry, Fritz & \cellcolor{red!27}27 & \cellcolor{red!27}27/159832& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Terrorist & \cellcolor{red!5}2 & \cellcolor{red!5}2/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Indian, Apple, Red & \cellcolor{red!27}34 & \cellcolor{red!27}34/159832& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Nigga, Black, African, Buck & \cellcolor{red!5}48 & \cellcolor{red!5}48/159832& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Snowflake, Communist, Red, Nazi, Commie, Libturd, Libtard & \cellcolor{red!27}36 & \cellcolor{red!27}36/159832& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Female homosexuality}  & \cellcolor{red!5}Lesbian & \cellcolor{red!5}2 & \cellcolor{red!5}2/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Thin, Fat, Obese, Chubby, Skinny, Porker, Lump & \cellcolor{red!27}31 & \cellcolor{red!27}31/159832& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}19 & \cellcolor{red!5}19/159832& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - American}  & \cellcolor{red!27}Yank, Yankee, Murican & \cellcolor{red!27}7 & \cellcolor{red!27}7/159832& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Destitute}  & \cellcolor{red!5}Bum & \cellcolor{red!5}4 & \cellcolor{red!5}4/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}2 & \cellcolor{red!27}2/159832& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - White}  & \cellcolor{red!5}Hick, Trailer trash & \cellcolor{red!5}3 & \cellcolor{red!5}3/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Jewish}  & \cellcolor{red!27}dodger, Abe, Oven & \cellcolor{red!27}3 & \cellcolor{red!27}3/159832& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - European or anti-Europeans}  & \cellcolor{red!5}Brexit & \cellcolor{red!5}3 & \cellcolor{red!5}3/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!27}Yellow, Oriental, Zip & \cellcolor{red!27}3 & \cellcolor{red!27}3/159832& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Japanese}  & \cellcolor{red!5}Yellow, Oriental & \cellcolor{red!5}2 & \cellcolor{red!5}2/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - French}  & \cellcolor{red!27}Frog & \cellcolor{red!27}1 & \cellcolor{red!27}1/159832& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Southern European}  & \cellcolor{red!5}PIGS & \cellcolor{red!5}2 & \cellcolor{red!5}2/159832& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}Transgender, Transsexual & \cellcolor{red!27}3 & \cellcolor{red!27}3/159832& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Protestant}  & \cellcolor{red!5}Spike & \cellcolor{red!5}1 & \cellcolor{red!5}1/159832& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Physical Identity - Physical (and Mental) Impairments;Nationality - General;Gender - Female intelligence;Age - Youngsters;Sexual Identity - General;Sexual Identity - Male homosexuality;Age - Over 65s;Gender - Female sexuality;Social Class - Working class;Ethnicity - General;Nationality - Chinese;Nationality - German;Religious Identity - Muslim;Ethnicity - Native-American;Ethnicity - Black; Ideological and Political Identity - General;Sexual Identity - Female homosexuality;Physical Identity - Physical Features;Age - General;Nationality - American;Social Class - Destitute;Behavioural Addiction - Alcohol;Ethnicity - White;Religious Identity - Jewish;Nationality - European or anti-Europeans;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Japanese;Nationality - French;Nationality - Southern European;Sexual Identity - Transexuality;Religious Identity - Protestant;%.

\item The percentage of hate speech related words is 1.4797.

\item Considering that the variable \textbf{Physical Identity - Physical (and Mental) Impairments} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 2366/12141 occurences of hate speech related comments.\end{itemize}\end{document}