\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_141.json :}\newline \par\Large\textbf {Title: \large  Ageism in Hip-Hop | DEHH Convo Live \@A3C Festival \& Conference }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small kendrick, gibbs, ab-soul, badass, jay rock, chance, \textbf{m\textbf{ick}}, action bronson, sweatshirt, etc. More dope artists now than ever, but because the radio plays garbage hip-hop is in a bad place? The audience is way larger now and they are not all hip hop purists, the radio isn't designed for hip hop purists - its designed for people who dont care enough to choose their own music. They dont care enough to analyze and break down wordplay, they want to be entertained with uptempo beats and popular phrases that are easy to access. Let them have it. The main core of hip hop fans can still find, appreciate, and support dope artists so I don't really see an issue.\normalsize   & \cellcolor{green!27}Mick & \cellcolor{green!27}Nationality - Irish, Religious Identity - Roman Catholic & \cellcolor{green!27}2/118 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small People defending Lil YAchty. Just say something in your rap. Just flow. I swear literally anyone over the \textbf{age} of 10 could write a Lil Yachty rap.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small the guy with the afro sounds like a dumbass. he's like the Hipster that sits in the back of Starbucks bumping some new \textbf{age} shit on his phone thinking it's hot when everyone around to telling them the turn that shit off cuz it's garbage\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small the guy in the \textbf{r\textbf{ed}} cap nailed it with the Master P  analogy.  a lot of this  coming out now makes Master P look like big L  lol\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The \textbf{Old} Heads won this debate by flawlessly.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small That's right, 11 year \textbf{old} jackson 5 is so not playing at everyone's house party... 21 year \textbf{old} prince isn't being remade by today's youth.. Stop playing yourself.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@MykeCTown \textbf{M\textbf{ick}} Jenkins sold out a show in Atlanta brah. I was  there . \textbf{M\textbf{ick}} Jenkins came outside and bought those who couldn't get in, Pizza. Soooo you're wrong pimp. Machine Gun Kelly!!! Just sold out a show at Center Stage Abra just sold out a show at Masquerade.  Chance... joey badass. Big Krit.\normalsize   & \cellcolor{green!27}Mick & \cellcolor{green!27}Nationality - Irish, Religious Identity - Roman Catholic & \cellcolor{green!27}4/54 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small It seems that the actual complaint from Ken, Beezy, Myke \& others in that \textbf{age} range (I'm 31 like Feefo) is that its not easy enough to find quality music through mainstream channels.  Sad to say that hip-hop doesn't live in the mainstream, which it never really did ... when you say that Public Enemy was mainstream, that's not necessarily that accurate.  They were one of the more popular groups of the small emerging culture, but Def Jam was an independent label run out of a dorm room, it just seemed major.  And the EPMD's \& such came out on independent labels like Sleeping Bag Records \& played on college radio.  \textbf{Black} radio even hated rap music.  You couldn't see \textbf{Black} music on MTV at all until Michael Jackson's 2nd (Epic records) solo album if I remember correctly.  It was always a culture of digging.  But those of us who experienced music in the 90s got spoiled with Death Row, Bad Boy, No Limit, etc. breaking through as hip-hop took over MTV \& mainstream culture.  You have to except that hip-hop is counter culture and belongs to the underground and don't put weight in the complex's and other platforms that don't represent the voice of the culture, and not look to them to elevate our artists and to have the same standards that we do.  The big problem is that after a certain \textbf{age}, people stop digging for music due to responsibilities and a sort of \textbf{age} barrier to technology.  Mid 30s \& up aren't on boxden everyday looking for all the leaks, unless you're Kinge \& you have to listen to every release lol or you're more of a DJ type.  So when people say its a youth driven culture, and the commercial (commerce) aspect focuses on that under 30 ... that's why, because older than that aren't making an effort to find music, and are less likely to look to buy new releases every week, unless you're a digger. ... In that respect, as a music maker, I've realized how many people do rely on traditional mainstream outlets to filter music for you, and have more of a desire to make the Regulates that everybody will experience, instead of having to spam people on social media and get ignored.  So I can see both arguments\normalsize   & \cellcolor{green!5}Age, Black & \cellcolor{green!5}Age - General, Ethnicity - Black & \cellcolor{green!5}5/387 & \cellcolor{green!5}1.292 \\  \hline
  \cellcolor{green!27}\small You know what i find interesting... they say these guys don't be selling out shows... I go see young thug or migos at a venue and its barely half full. Then I go see a group like flatbush zombies at the same venue and the place is packed from wall to wall to the point where you can't move. Get the fuck outta here with that shit saying these other guys arn't poppin. Yoh is right, the machine gives you the illusion these guys are poppin and thats cus they have cheap viral fame... the artists that are actually selling out their merch, putting up numbers in sales, and selling out there shows are guys like joey, action bronson, mac miller, freddie gibbs, earl, danny brown, tde, flatbush, underachievers, and the list goes on and on. I go to these shows...the seemingly in the spotlight "trash" you guys say represents hip hop doesnt have nearly as much support when its time to show and prove. Not to knock migos or young thug cus I believe that music is great and its real hip hop as well. the fact of the matter is the artists that arn't around for a quick minute are the ones really representing hip hop and if you look at the amount of good content that comes out by the numbers, hip hops in the best place its ever been in. Yahty and uzi vert are \textbf{nothing} but a couple viral distractions, just like many before them.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/250 & \cellcolor{green!27}0.4 \\  \hline
  \cellcolor{green!5}\small "There is no \textbf{age} limit on creativity" Real talk Feefo ❤\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I must be \textbf{old} . But the guys defending today's music sound like they can't keep up .Their points aren't  sticking .\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small the artist I think Yoh is talking about at 26:14 is either Young M.A,  A \textbf{Boogie} (who has already admitted he's signed) or Chance The Rapper\normalsize   & \cellcolor{green!5}Boogie & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small COSMIC WARRIOR I think part of the problem was alluded to in his discussion. Radio is currently playing catchy music regardless of it has any substance behind it. You have to go out of your way to find music with substance. You want music with those aforementioned lyrical features? Check out the new \textbf{Common} album, or the Saba album, or the Tribe album. All great records, but I don't hear them being played on the radio.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small The twenties is a time of your life where you have dreams, you are naive, unaware, and kinda go around shooting in the dark. The thirties is when you make those dreams happen. But the \textbf{transition} time is hard and a big reality check. Dreams have to be modified as they were ungrounded. This switch is definitely observable say between a 28 yr \textbf{old} and a 31 yr \textbf{old}. The latter will be sadder in most cases, you can actually see this easily in ppl. This short but intense \textbf{transition} point usually involves pain, but is the key that explains why ppl in their 30s feel wiser and when they hear ppl in their 20s rambling, they are disconnected. These are, in a few words, the real source of all these debates between young and \textbf{old} generations. You not an adult until 30. Which means you think you not a pawn but you are, you just dont know you are...\normalsize   & \cellcolor{green!5}Old, Transition & \cellcolor{green!5}Age - Over 65s, Sexual Identity - Transexuality & \cellcolor{green!5}5/160 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I'm Young (23) and I'm more into \textbf{Old} School Rap, but I still love to enjoy what's popping today, Idgaf who get mad, Listen to 2pac, Biggie, NWA, Snoop, Method Man, Redman,  But I still party to Lil Uzi, Lil boat, Etc Etc, Us young artist get bashed on. but aye Big Daddy Kane got bashed on. so yeah.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Keyser Soeze Yeahhhhh \textbf{nigga} he's real name is Daren Jackson look up his \textbf{age} on Google,You just gotta type Rap critic's \textbf{age} and Daren Jackson will appear.\normalsize   & \cellcolor{green!5}Age, Nigga & \cellcolor{green!5}Age - General, Ethnicity - Black & \cellcolor{green!5}3/27 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@Dominicans Fuckwith \textbf{Black} Hippy rap critic is younger than asap rocky...bruhhh I'm mind blown\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Crazy right? It must be the beard\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small That \textbf{OLD} ASS right side of the table looking stupid lmfaoo...myke c-towns passive aggressive ass, beezy's quiet ass and kens \textbf{dumb} ass lmaooo\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small TommyFlacko512 \textbf{dumb} ass kids like you are why rap is the problem\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@thedondon911911 the problem to what? LMAO you probably \textbf{old} as shit.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@TommyFlacko512 kid shut your \textbf{dumb} ass up, you're a \textbf{dumb} ass child that cant even write a proper sentence, the young kids got fucking bodied becase this generation is completely dumbed down and retarded to the point where even the thought of backing up your argumnets fucks your head up. i dont get why you \textbf{dumb} ass kids are always calling people "\textbf{old}" LMFAO if being \textbf{old} means having brain cells and not being fucking retarded than i guess im \textbf{old}, kid dont ever comment on rap again , go blast your trap music you illiterate fuck\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/97 & \cellcolor{green!5}6.186 \\  \hline
  \cellcolor{green!27}\small LMAO dawg you mad at life i can tell.....Calling me illiterate based on what?? I Have a bachelors and a masters and graduated from stand ford boy...you said "rap is the problem" the fuck you mean..the problem as to why your life sucks...YOU \textbf{OLD} ENOUGH TO BE MY DADDY PROBABLY< COMMENTING ON YOUTUBE....GO TO YOUR CHILDS SOCCER GAME IF YOUR \textbf{LAME} ASS EVEN HAVE CHILDREN\normalsize   & \cellcolor{green!27}Lame, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small and you spelled half the shit in comment wrong lmfaooooo.....boy you done....get the fuck outta here, \textbf{lame} ass don't even know what an iPhone is....lmfaooo I'm dead\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@mrpostman730 dont even bother, this video is even living proof, kids these days will never accept defeat, the younger generation just got exposed and debunked with every argument they made yet i bet they walked out of there and started the same argument all over again, and whats also hilarious is these kids AGREEING with such debunked points, the kids would say"you cant compare these new artists to legends"than myke would say"why cant we compare them to legends"and they'll say"i didnt say we couldnt"LMFAO kids today have reached a whole new level of \textbf{mental} retardation\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/101 & \cellcolor{green!27}0.99 \\  \hline
  \cellcolor{green!5}\small The Rap Critic is how \textbf{old}???\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Dude in the \textbf{r\textbf{ed}} hat is a dumbfuck\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Good topic about the \textbf{ageism}. As a 25 year \textbf{old}, I find a lot of modern rap or trap music not appealing but I think it's because of my \textbf{age} because when I was in 10th grade, I actually really liked Soulja Boy, crime mob, D4L, dem franchize boys etc. Of course I still liked good quality hip hop and the \textbf{old} school and gems from the 90's too but I liked the more "ignorant" current stuff a lot as well when I was in middle school, 9th and 10th grade. \textbf{Age} has a lot to do with what you like I think. If I was like 5 years younger, I would probably be into the shitty trap shit lol. If you're 23 or older, you're from an older generation and chances are you don't like today's mainstream rap that much.\normalsize   & \cellcolor{green!5}Age, Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}5/141 & \cellcolor{green!5}3.546 \\  \hline
  \cellcolor{green!27}\small This argument needs to stop. If you don't think rap changed in terms of standards odds are you're a misinformed child. I don't remember whack rappers being in the forefront of hip hop while jay z , nas , and eminem sat in the back. I don't understand how anyone with rap knowledge can disagree. The very fact that people are arguing that "bad music" doesn't exist alone shows how terrible rap has gotten. Lil Yatchy , lil uzi vert, 21 savage , designer , future , young thug, etc. are at the forefront of hip hop, where else even back in 2013, you had kdot push a t (good) drake and more. People KNEW young thug and future were garbage but agreed there's a time and place for it. Now these \textbf{dumb} ass kids will argue that future and thug are actually great and pac reincarnated. These new rappers can't rap , admit they can't rap , say they don't take rap serious , disrespect hip hops history and culture , release the worst music to come out of the genre , don't even consider themselves rappers , yet y'all kids still vouch for them ? The fuck ? If someone can't ball , admits they can't ball, says they don't take balling serious , disrespects basketball , and says they don't consider themselves basketball players , are they still on the team ? Rap is dead , point blank period. A few clean spots doesn't make the pool not contaminated\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/252 & \cellcolor{green!27}0.397 \\  \hline
  \cellcolor{green!5}\small gios4ma (continued) so again bitch, this isn't argumentative anymore. "The game didn't change" yes it fucking did. The only music being played is trash, most of the rappers I see videos of on a daily basis are trash. Just fucking stop. You \textbf{dumb} ass kids who are indenial are what's killing the genre\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Dope ass panel \& discussion. Whole squad dropping gems like usual. BUT.Saba project at midnight. Yall gtta review it 4r da \textbf{squaw}.\normalsize   & \cellcolor{green!27}Squaw & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Here's what I've always been saying for a good while: disrespect to the pioneers and lack of originality are both big and inexcusable problems when it comes to these Yachtys, Uzis and Kodaks out right now along with most of the fans that listen to them. These guys are so quick to verbally assault the veterans that paved the way for the art form to come into existence and make this garbage that ALL sound EXACTLY the fucking same just to make money. I hear this excuse every time: "They're just doing them, being unique." HOW THE GODDAMN FUCK ARE THEY BEING THEMSELVES OR UNIQUE WHEN THEY MAKE THE SAME TYPE OF MUSIC? What's different about these niggas that we haven't heard before? \textbf{NOTHING}! Yes, they can do them; I'm not saying they can't. But they're not even TRYING to and that's the problem. And can someone PLEASE explain to me a logical reason on how and why it's even remotely okay for them to get away with dissing the \textbf{old} school artists that basically built this shit for them?! They don't HAVE to like their music, but saying the shit they're saying about them is hella unnecessary and half of those motherfuckers never even heard a bar from the legends let alone a full song! Think about it people, do we really need \textbf{old} school-disrespecting mumble rappers that like to copy a certain sound just to earn a quick \textbf{buck} from now on? Do we REALLY?\normalsize   & \cellcolor{green!5}Buck, Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}4/247 & \cellcolor{green!5}1.619 \\  \hline
  \cellcolor{green!27}\small Myke's argument, that when he was young, he still enjoyed music that wasn't necessarily made for him, has a major flaw. It is flawed because even the Hip-Hop back then had its haters. Hip-Hop in the 80's and 90's had it's own \textbf{old} heads hating on the younger generation's music. Hip-Hop has never been liked universally. For the record, I think Trap and Mumble rap are complete garbage.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small \@thedondon911911 The only one sounding like a child is you. The amount of cussing and hate in your comment leads me to think you probably fall asleep listening to trap and mumble rap. I think you used one period in that whole comment, so how can I take you seriously when it looks like you never graduated high school? And yes, Outkast, Nas, Jay Z got bashed by \textbf{old} people who didn't have taste for that type of music. People who listen to Trap and Mumble rap have every right to do so. More kids know about Future than Nas, or Lil Yatchy than Talib Kweli. You can't deny that fact. Like I said, take a trip into your local high school and ask them who their favorite artists are. You may not like Trap or mumble rap, but that's your opinion. Wether you like it or not, many people enjoy listening to it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/154 & \cellcolor{green!5}0.649 \\  \hline
  \cellcolor{green!27}\small Ok you're talking about how Trap has dumbed our generation down, yet your comments are filled with hate and terrible fucking grammar. And yes I will stand by my statement that Hip-Hop has always had its haters. Have you ever tried playing Hip-Hop for an \textbf{old} white man who likes country? Or someone who likes classical orchestra music? They don't like HipHop, and that is perfectly fine. And what do you mean Andre 3000 has been called the goat by \textbf{old} heads? Andre IS a fucking \textbf{old} head! (No disrespect intended) Andre is 41 years \textbf{old}, DJ cool Herc is only 61. There weren't really \textbf{old} heads in the 90s, Hip-Hop was still a very young genre. My point is, Hip-Hop is changing, you either ride the wave or you drown. And bro stop trying to diss me cause of my youth. LMAO if your so \textbf{old} then wtf are you doing on youtube? Shouldn't you be taking care of your kids? Chilling with the wifey? Or perhaps you're just a \textbf{old} head with no fucking life. Peace. Bitch.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}7/179 & \cellcolor{green!27}3.911 \\  \hline
  \cellcolor{green!5}\small There's plenty of young artists that the \textbf{old} heads could bump their heads to. Anderson Paak, Joey Badass and the whole Pro-Era Squad, the entire TDE Squad, \textbf{M\textbf{ick}} Jenkins, Chance... and of course, yours truly ;)\normalsize   & \cellcolor{green!5}Mick, Old & \cellcolor{green!5}Age - Over 65s, Nationality - Irish, Religious Identity - Roman Catholic & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small +VINCE BRETHEM how many are officially recognised? k.\textbf{dot} and young thug shouldn't be competing for the same airways. future and katy perry aren't competing in sales or popularity because they are not in the same lane. the same thing should apply to rap and trap\normalsize   & \cellcolor{green!27}Dot & \cellcolor{green!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small good point. same with house music. much of the "house" that people call don't identify with \textbf{ethnic} culture people, but rather middle america and dominant culture. So, it's still electronic dance music but it is NOT house. But yet, people still want to call it house and everyone competes while true house suffers.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Rap critic is 25!!!! Dude looks AT LEAST 35yrs \textbf{old}. I can't believe it!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@Sooftah theres no \textbf{age} gaps, none of the shit dropping now is different from past eras, the argument is over hip hop sonically, but quality wise, hip hop is not in a good place, any era that allows young thug, future, and desiigner to "run hip hop" while comparing them to iconic legends and arguing that they're just as much hip hop as them and how they dont make bad music or that there isnt bad music in general automatically makes this era fucking terrible, we are currently in the third dark ages\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small The quality hasn't changed, the access to music has increased and therefore has lead to perceived increase in so-called "low quality" music, but there is also an increase in "high quality" music. There will always be a Future or a Young Thug in Hip Hop. Rappers have been complaining about the state of hip hop since the 90s: Ice Cube - Turn Off The Radio, \textbf{Common} - I Used to love H.E.R, Wu-Tang Clan - Intro of the 2nd disc of Forever. There has always been a dissonance between what is perceived as aesthetically hip hop and what is portrayed in the mainstream media. This has not gotten worse, just we are starting to romanticise the 90s era, which is implicit of an \textbf{age} gap in Hip Hop and exaggerate the lack of talent in present day hip hop. To Pimp A Butterfly, arguably the most political and lyrical album in the past decade was a massive commercial success, proof that artistry is still celebrated in this era and the "industry machine" can get behind a "true emcee". There will be people ignorant of the culture and the history of the music and this is a shame, but not exclusive to hip hop. Artists that fail to acknowledge the past, will ultimately have a short lived career, there are plenty of young artists that do acknowledge and also include the legends on their albums (Schoolboy Q, Danny Brown, ASAP Rocky., Earl Sweatshirt for example) If 90s era rappers want to remain relevant and educate the youth who are more harder to reach due to their need for instant gratification, they need to show love to artists they genuinely like.\normalsize   & \cellcolor{green!27}Age, Common & \cellcolor{green!27}Age - General, Social Class - Working class & \cellcolor{green!27}2/279 & \cellcolor{green!27}0.717 \\  \hline
  \cellcolor{green!5}\small Sooftah Generally speaking I do believe hip hop is in a good place right now. There are outstanding young artists out there putting out new sounds with substance but also respect the history of the culture. Kendrick, Nick Grant, Schoolboy Q, J Cole, Joey Badass quickly come to mind. This year you also had \textbf{Common}, Tribe and De La Soul release outstanding albums. You can't ask for much more as a hip hop fan. For a few years I thought the substance in the music was fading but 2016 was an especially strong year and gives me hope for the direction of the genre. One thing I do think that's severely lacking is hip hop groups. There's no more Outkast's, Wu's, Tribe's, there's a lot of crews which individual artists put out projects but not a total group effort. Kanye is an interesting artist because he  bridges the \textbf{old} skool with the new skool. I think Drake is just ok, for the last two years a lot of his music sounds the same. With Nas, Prhyme and Freddie Gibbs w/Madlib hopefully dropping albums in the near future I do think hip hop is in a good space. There's something there for everyone.\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/202 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small Young people are \textbf{dumb}....itz da natural order ov thingz 4 dem ta learn frum and respect their elderz. Any young person who knowz anything ov significantz learnt it frum an \textbf{elder}. If u keep da knowledge frum a child for da first 18 yearz ov hiz life then you'll have a \textbf{dumb} ass 18 year \textbf{old}. Now dayz u got young dummies teachin young dummies and young dummies become \textbf{elder} dummies and therefore we got a few generationz ov dummies. Watch da movie 'idiocracy' - dat movie explainz it all.\normalsize   & \cellcolor{green!27}Dumb, Elder, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/90 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@RK Tech hell Busta Rhymes was even signed to Young Money! lol E-40 has collabed with Big Sean, \textbf{Common} has collabed with some of the drill rappers from Chicago, The Game has collabed with Lil Wayne, Juicy J was signed to Taylor Gang and has collabed with Whiz Khalifa, i could go on, please dont go there, cuz we can if you want to and you're acting like all the artists of the prior eras were ok with 90s hip hop, it's the same as today, some older artists are cool with what the new gen is doing and some arent\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small \@TruMusic89Whoa dude, you made a lot of assumptions there. The only reason I replied was to show you numerous examples where older era musicians were not hating on the 90s era. Then you decided to take it in some \textbf{weird} ass direction and assumed that I was the stereotypical "\textbf{old} head" that hates on everything from this era, when I'm not. I'm not part of this 90s vs now internet war bro. I was just a casual rap fan until the mid 2000s.\normalsize   & \cellcolor{green!27}Old, Weird & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/84 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Go listen to Joey Badass he's a prime example \textbf{age} shouldn't be an issue. There is many more young rappers that rep the \textbf{old} school other than Joey as well. Each individual artist should be referred to if u have a problem with them or the music they make. By saying the young kids suck or \textbf{old} rappers suck is being ignorant and disrespectful to artists who do make real music who may be young or \textbf{old}.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/77 & \cellcolor{green!5}5.195 \\  \hline
  \cellcolor{green!27}\small agreed, along with folks like Earl and \textbf{M\textbf{ick}} Jenkins\normalsize   & \cellcolor{green!27}Mick & \cellcolor{green!27}Nationality - Irish, Religious Identity - Roman Catholic & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small yea i wish the people repping for the new gen of Hip Hop researched this stuff so they could've called it out more, like how everybody complains about lyricism being bad because the rappers dont care about it, when in the 90s the producers were stealing parts of songs because they were horrible musicians, but \textbf{nobody} cared about that, i mean i love the 90s era, but that's the most obvious hypocrisy when it comes to the hip hop purists\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small +TruMusic89 +Mattwashere3014 All this conjecture would only hold water if I was wrong. Which I'm not. Bam. \textbf{Ho}.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small +Myke C-Town Yeah I wasn't trolling lol. I've been watching this channel for the past 5 years and actually found the channel through the \textbf{old} school vs new school video series. I just think y'all (minus Feefo) haven't updated your definition of what's hot in hip hop vs what's not. The truth is, the \textbf{weird} creative artists have been getting a lot of shine over the past three or four years, but y'all are still looking at the radio as the official home of hip hop's representation, instead of equally considering the many movements in Hip Hop that have sprouted from the Internet and made noise to millions of rap fans that don't listen to the radio anyways. To you Kinge and Beezy, it seems like mainstream/big time hip hop artist = a popular artist that makes party/trap/mumble music that you don't like. I can't take yall's argument seriously when you don't mention Kendrick or any of the guy's I listed earlier as a big time artist in Hip Hop, but you can mention Trinidad James, and Bobby Shmurda, (I get that it went with your point of making 2 songs and blowing up, but that pertains to lyrical/creative artists too). You guys even tried to make a case for Soulja Boy being relevant and he hasn't been hot in half a decade. I'm still a big fan of you guys! Y'all just be tripping on this subject lol.\normalsize   & \cellcolor{green!5}Old, Weird & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/239 & \cellcolor{green!5}0.837 \\  \hline
  \cellcolor{green!27}\small +Mattwashere3014 Wow. Did you even watch the whole video or do you have selective hearing? We stated numerous times that we are not only talking about radio. The discussion is about commercially successful hip hop artists as a whole. (Radio, internet, concert sales, etc.) Not sure how you missed that. Next, we didn't say the \textbf{weird} creative artists don't get shine. That wasn't even the point of this discussion. We do mention Kendrick but the point is when it comes to commercially successful artists (which is what we were talking about) the Kendricks are few and far between. You mentioned us brining up Trinidad and Shmurda as a detriment but then immediately admit that we were bringing them up for a specific purpose that has \textbf{nothing} at all to do with what you're talking about. And we did NOT make a case for Soulja Boy still being relevant! One of our guests brought him up and asked if he was relevant and I CLEARLY said I have no idea! See, this is why y'all never win arguments with me. You're saying you can't take our argument seriously, but the problem is you don't even know what the argument is! I appreciate you watching...but, real talk, you need to watch and listen a little bit harder, bro.\normalsize   & \cellcolor{green!27}Nothing, Weird & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/216 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small \@Mattwashere3014 you make \textbf{zero} sense, last time i checked kdot isnt even on the radio or talked about mainstream wise anymore, the problem isnt the bad, the problem is the bad being put on a pedistal higher than it should be, just because YOU pick and choose what you listen to doesnt make you the spokesman for the current hip hop generation, its clear you dont really know alot of rap, just take ya L\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Mattwashere3014 where the fuck are youGetting your facts ? Are you fucking retarded ? Kdot barely went platinum and it took Cole 2 years to reach 2x platinum , yet they somehow run rap ? LMFAO TLOP was the first rap album to go platinum on streams alone and drake went platinum in like a week , kid please shut up and stop commenting on shit you know \textbf{nothing} about. Like I said , kdot is getting praise from OTHER genres fanbases because hip hops is too busy with these mumble rappers. Type in TPAB on a hip hop forum kiddo , and maybe next time you'll learn your facts. You're a fucking idiot and indenial. Kdot and Cole aren't more popular , their videos lack in sales , they lack in popularity and lack in radio spins when compared to these trash rappers. Bitch you already got debunked in this video and again by myke\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/157 & \cellcolor{green!27}0.637 \\  \hline
  \cellcolor{green!5}\small Mattwashere3014 and bitch "please provide numbers" I just did you \textbf{dumb} ass child , even myke thinks you lack \textbf{common} sense\normalsize   & \cellcolor{green!5}Common, Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small TheShutYoMouth well I am laughing 😂 corny nigga\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small TheShutYoMouth what's funny is I'm some how retarded because I like a certain artist. You're the one acting like a bitch on MY comment. For sticking around so long on my comment YOU'RE award will be here soon 😂 have a nice day corny ass nigga\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small TheShutYoMouth it's \textbf{crazy} because you came to my comment and now I'm the one who needs to shut the fuck up? Because that's logical,right? Cause that'll make me shit up, right? Bitch get the fuck outta here\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small No, music is not worse than it used to be. What's changed is that the radio isn't playing diverse music anymore. All of it has the same topics and sound. To get music that sounds different, you have to go searching online to get it, which a lot of people won't do or don't know how to do.  The problem with hip hop radio is that party/braggadocios music does not \textbf{age} well. Listeners get older, they have other priorities and eventually they just can't relate. Love songs, breakup songs, living life to the fullest songs, etc. relates to a wider range of people.Hip hop is not the only genre dealing with this problem when it comes to the radio, but it's probably the only genre that doesn't have as much diversity as other genres on the radio(as small as that diversity is).\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/143 & \cellcolor{green!5}0.699 \\  \hline
  \cellcolor{green!27}\small JustDavid0823 I listen to literally everything , your comment is completely false. We went from college dropouts , \textbf{black} albums , speakerbox's, marshal Mather lp's, get rich or die trying's, etc. to what ? Hip hop is terrible now a days and that's a fact. Even kdot is slacking. If there isn't a jump soon you can bet that rap will take a huge dive and lose even more credibility. "Oh this basketball team isn't trash , you just have to look for the good players" "Oh this popcorn isn't burnt , you just have to look for the good kernels"If something was in good condition you wouldn't have to go out of your way to see the good condition. There's no reason why I need to go on YouTube in order to here some quality. I don't remember the blueprint or gods son having to be looked for. Every single song in a category sounds exactly the same , from trap to that new generic boom bap style conscious rappers keep using. We used to get songs like Stan on the radio , and had rappers from nas to \textbf{nelly} share radio spins. Now a days you could blow up because your hair braids are yellow\normalsize   & \cellcolor{green!27}Black, Nelly, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Nationality - Chinese, Nationality - Japanese, Sexual Identity - Male homosexuality & \cellcolor{green!27}5/208 & \cellcolor{green!27}2.404 \\  \hline
  \cellcolor{green!5}\small \@thedondon911911 My comment is an opinion. It can't be false lol...like your feelings of today's music is your opinion.  I wouldn't say kdot is slacking. His albums are still solid. I'd say his features are much to be desired.Your examples are "College Dropout", "\textbf{Black} Albums", "Speaker box" and "Marshall Mathers lp". I'd respond with "To Pimp A Butterfly", "12 for 12", "Tetsuo and Youth", "King Push", "I Don't Like Shit, I Don't Go Outside" and "Shyne Coldchain 2". Music goes through ebbs and flows. There are too many artist right now in every genre for anything to take a "huge dive". Rap has struggled with credibility since its inception. There's no point in wasting time worrying about that. Who cares if it doesn't receive credit. That doesn't connect to it's uprise or downfall.Using a basketball team as an example is a stretch because the music pool is so large. It's more like "Sports everywhere doesn't suck. Look at these teams and players over here."In response to your comments about not having to search for music on Youtube or the internet in general because they used to be played on the radio - you kind of pointed out the problem right there: The Radio. Radio controls what the mass audience is hearing. The radio works in trends and that's all. The trend right now is mumble rap and people that want to get famous see how easy it is to do it.The plus side is that the radio is basically Blockbuster and companies like Spotify are Netflix. It's slowly dying and being taken over by another medium. My personal opinion is that there is still great music being made in all genres. It sucks that you have to look for it, but it's out there.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/298 & \cellcolor{green!5}0.336 \\  \hline
  \cellcolor{green!27}\small JustDavid0823 I'm sorry but you're a perfect example of why this hip hop era is terrible. Just because something comes out of your mouth , doesn't make it opinionated. That's just a poor ass excuse kids make because they have trouble articulating an argument. The only album you named that can even be mentioned in the same sentence is TPAB, and no , that CANT be argued. The problem is non rap fans who know \textbf{nothing}About rap pre 05 using the lowered standards of today as their bases , what you call great , is only great by today's standards , yet if all you know is today's standards , it'll result in weak material being overrated. Did you just try and compare IDLSIDGO to speakerboxx ? LMFAO what ? No, this shit isn't even funny anymore. You kids are taking away the weight of the classics and quality music by turning into a second grade basketball "everyone's a winner" atmosphere which is single handily ruining rap. And LMFAO again , that's like getting shot in your arm , and the doctor saying "are you in pain" and you responding "even though my left arm is shot, the rest of my body isn't , so I'm fine" no. The fact that you can't see why speakeboxx and most of the albums you named shouldn't even be said in the same sentence makes It clear that you don't know rap or its history. We used to have songs like Stan all the way to "ride with me" getting huge praise and attention , not one hip hop album that dropped today would be considered good in 03, and I love a lot of albums this year. Yes , rap is getting bad. I don't remember crunk musicBeing in the forefront of rap with crunk artists disrespecting hip hop and calling themselves legends or saying they're better than past icons whileEminem, nas , and jay z drop music online with almost \textbf{zero} mainstream attention. No, no, and no. We weren't having this argument back in 2012-13, so anyone who tries to convince themselves their isn't a problem , is apart of the problem. Kdots features have been getting more and more lazy and I'm not expecting any new songsFrom him soon as his record label manager TOP is a dickhead and loves toHold back artists and let them work in cycles . You know how a certain type ofCOD series has their games drop every other year ? (\textbf{Black} ops , mw) that's similar to top dawg.We have to goThrough 2-3 more artists before we can get back to kdot, and in a generation that constantly needs to be reminded that you exist , that's not an effective system\normalsize   & \cellcolor{green!27}Black, Nothing, Zero & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/465 & \cellcolor{green!27}0.645 \\  \hline
  \cellcolor{green!5}\small \@JustDavid0823 it CAN be factual proving you fucking idiot, its called \textbf{COMMON} FUCKING SENSE, LMFAO i dont understand why kids in this era are so fucking retarded? actually its not kids as i was JUST talking to some today and they clearly had more brain cells just by their opinion on this topic, lmfao kid please shut the fuck up and stop talking, "you believing TPAB is the only viable example is an opinion" no, its a pretty known FACT and the other albums are \textbf{old} school artists so it doesnt count, kid shut up, you're \textbf{nothing} but a child that doesnt know shit about rap so you cant comment on albums and their quality from the past as you're too stupid to understand quality above what 2016 had to offer , you just said, "you say college dropout, i said IDLSIDGO" LMFAO as if those two albums are equal in terms of quality, no you child, that album was great, HOWEVER, is hot garbage by past standards and thats a FACT whether you accept it or not, instrumentation was more basic, more simpler, more straight foward, less original, not as much effort, only someone who doesnt know rap would ever disagree. no one said it sucks because it doesnt stack up you fucking idiot, again you children love to simplify shit, its the fact that standards have gotten lower, if you cant see that delete your youtube account, we used to get blueprints and college dropouts like its \textbf{nothing}, now what are we getting? forest hills drives? "speakerbox could be considered horrible" LMFAO i dont give a fuck what someone else thinks you idiot, not ONE person can offer an ACTUAL , UNBIASED explanation as to why it sucks, just because i said the blue sky is \textbf{r\textbf{ed}} doesnt mean im right, again you keep proving my point, you \textbf{dumb} ass kids love to pretend facts dont exist, "theres no such thing as bad music" , and other bullshit ass arguments that are killing hip hop, and yes i have heard every hip hop album that dropped this year you \textbf{dumb} ass child and not one was better than the big albums that dropped in 2003, FACTS\normalsize   & \cellcolor{green!5}Common, Dumb, Nothing, Old, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Age - Youngsters, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}8/368 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small David A. Bitch shut up, your \textbf{dumb} ass got bodied and you couldn't respond. "Music isn't getting worse" LMAO anyone who believes this is fucking retarded\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@theshutyomouth again applying a standard of hip hop from the \textbf{old} generation standard. heres my point and I'll leave this conversation alone because I know how endless this can get.This is my point of view.It's 2016 the mainstream has entered hip hop.The money The flash The success The materialism.There's a demographic of artist that make music for people who are interested in those things.Lil Yachty, future, Drake, meek mill, ect.Those songs hit people who like the night life turning up ect. It has its fan base, people like vibing out. People don't want to sit there through a poetry slam. They just don't.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small But there's a way to make not-so-lyrical party music without sounding like every thing else that's popular right now. Yachty, Uzi and of course Desiigner ALL stole Future's unique sound. Desiigner even proudly admitted it and claimed he does that sound better than Future. He also said that we can't get mad at him for that! WTF?! First of all, copying someone's sound is \textbf{NOTHING} to be proud of. Second of all, it is 100 impossible to do a sound better than the originator of said sound; the originator will ALWAYS be the best of a certain sound. These fools are just making themselves look hella stupid trying to copy Future, and don't make the excuse that they were influenced by that shit because that's different. Big K.R.I.T. for example is heavily influenced by both UGK and Outkast, but NONE of his songs copy their classics like "Diamonds \& Wood", "Chonkyfire" or the big hit that both of the legendary duos were on: "International Players Anthem (I Choose You)". You just hear an INFLUENCE and not an exact replica. And lastly, Desiigner said for us NOT to get mad at him for copying Future; why SHOULDN'T we?!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/197 & \cellcolor{green!27}0.508 \\  \hline
  \cellcolor{green!5}\small The argument isn't guys copying others styles, its part of it but no the main topic.What I'm arguing against the older dudes is that they hold hip hop to the same standards that they grew up in.The \textbf{old} heads don't get that it's not there era anymore.You guys don't get to tell my generation what is good music and what is bad music.Music is subjective and it's even more subjective when you grew up listening to hip hop 10-30 years ago and it's 2016 and your trying to implement those same \textbf{old} standards now:No fuck no.It's called evolution. You don't here car enthusiast get mad that cars don't look like they did 30 years ago, they understand that as time goes forward,technology and development does.Consumer consumption and option does.Lil Yachty and Uzi vert make good music " Again Subjective." For those who like them it's good music.Who am I or you to say that it's not?They may not be as lyrical as wu tang Nas tupac Rakim.But they make music that people like.End of story\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/188 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small Like I said, they don't HAVE to be lyrical like Nas or someone of that caliber. And you're 100 right that hip-hop has to evolve and there are certain \textbf{old} heads that want shit to be how it was. But there are other \textbf{old} heads that can clearly see that the genre is NOT evolving because these all of these motherfuckers sound the same and are dissing the \textbf{old} heads that paved the way for them. There are different ways to compose art without throwing shade to your predecessors and sounding like everyone else just to create buzz and earn stacks, which many of these guys admitted to being their purpose (i.e. Desiigner); that's all I'm saying.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/117 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@Sol King It's not creative if you're copying somebody. And you can like what you like; there's \textbf{nothing} wrong with that. Just understand why other people don't like the artist's music or their actions outside of their music.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@TruMusic89 We want originality and uniqueness in hip-hop and we don't have even a slight chance in getting that if these copycats keep stealing Future's style (which Desiigner admitted (proudly) to doing and claiming he does it better than Future). And we don't want EVERYTHING to sound like the 90s;quit making that accusation. Why the fuck would we want hip-hop to have only 1 certain sound when that's the main problem right now? That logic makes absolutely no sense. If that was the case, these "\textbf{old} heads" you're referring to wouldn't like Kendrick, Cole, Joey, Tyler, Chance, Hopsin, or Macklemore. Only one of these guys that I just named has that 90s boom-bap influence in his music-Joey Bada\$\$. Some of those "\textbf{old} heads" even like Wiz fucking Khalifa; his sound ain't like that! And at least Joey takes a certain sound that he's influenced by instead of trying to copy certain artists.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/152 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small \@TruMusic89 Once again, no one wants ALL rappers to be lyrical geniuses...just original and unique which all of these mumble rappers (except for Future of course since he's obviously the originator) are NOT. And "To Pimp A Butterfly" was not JUST for the "\textbf{old} head" audience. Where the fuck did you get that from? I know plenty of people from other demographics that enjoy both K. \textbf{Dot} and Cole, so don't give me that bullshit homie.\normalsize   & \cellcolor{green!5}Dot, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Asian (South- India, Pakistan, Bangladesh) & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small I got a problem with the way theyre taking this discussion; the topic shouldn't be \textbf{ageism} because \textbf{age} has \textbf{nothing} to do with the issue, the topic should be the shift in culture or "Culturalism". It's the cultural difference between 90s artists like jayo felony or gang start and current artists like Lil Yachty or 21 Savage that set them apart. Society is different compared to how it was in the 80s and 90s, if Tupac came out in 2013,  he wouldnt be popular in the mainstream line of things, but of course if Tupac dropped All Eyez on Me in 2013 it'd sound a whole lot different then it does now.\normalsize   & \cellcolor{green!27}Age, Ageism, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}3/112 & \cellcolor{green!27}2.679 \\  \hline
  \cellcolor{green!5}\small Waseem Jaas Definitely. Thats another problem. But that goes with everything. I dont think people have the \textbf{mental} ability to process the art of lyricism anymore. The reason this music is hot is because people are straight up getting stupid. I've had the opportunity to explain the art to many of my friends and they either don't care, or they will just tell me that they don't want to think that much when they listen to music. Its unfortunate. But yeah i see your point and theres definitely more than a few factors that go into what makes this music popular in today's time. Its a tough argument to have as we could just see because what hip hop is now is so developed that to just go back to how it was would be longer than pushing forward to something new. We don't need the \textbf{old} ideas to replace the new. We need new ideas to replace the new. That goes with anything in life. Whether it's technology, science, music, government.\normalsize   & \cellcolor{green!5}Mental, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/172 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small \@Tyler Mariano easier said than done. And especially today if a brand has a household name it's hard for a new brand to come out and succeed whether it was radio, TV, tech. Just look at \textbf{apple} and samsung in the smartphones industry. Even though they both make great phones, sometime other companies make phones just as good as \textbf{Apple}'s and Samsung's but don't get the same recognition because they are not a household name. Same in hiphop even if we had new station or website people still go to hiphopdx and mtv or some shit\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Tyler Mariano Don't get me wrong I love 90s music I just turn 20 by the way I'm very open minded with rap music. Some days I wanna listen to some lyrical shit then other days I don't, music should be based on how you feel at that certent moment or time and place it shouldn't be all serious, when it comes to music I just wanna sit there and enjoy music without criticizing it because of the lack lyrics I listen to Kanye West, Drake, Kendrick, J Cole, Earl Sweatshirt, Tyler The Creator, ASAP Rocky, Vince Staples, Logic, Asap Ferg, Mac Miller, fabulous, Bones, Xavier Wulf, (lil uzi vert,lil yatchy, young lean, playboi carti, when I listen to their music I really don't expect any lyrical content because I know how there  music is like even though the lrycs are ass I just like to vibe to there music. You gotta understand that most of these rappers get famous from SoundCloud or YouTube only reason why rappers like lil uzi vert and lil yachty are popular it's because of there fan base another reason why people like them is because they have a different sound from everybody else and there original I wish guys like Bones, Xavier Wulf would as popular them even though they have a really big fan base there music is way different from lil uzi vert and lil yachty at least they can rap better then them lil uzi vert can be more lyrical if he goes back to his \textbf{old} style.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/257 & \cellcolor{green!5}0.389 \\  \hline
  \cellcolor{green!27}\small +Tyler Mariano or they could just be able to like both types of music, for some reason that doesnt register with a lot of people who want everybody to shun the turn up rap, yes some of us have the ability to like both types, and there is \textbf{nothing} wrong with that\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small No, it doesn't have relevance to what you are talking about...you are correct on that. I was merely pointing it out, as a point of reference to something I disagreed on. You made it sound somewhere that you have to turn your brain off to enjoy something. Why? If you need to turn your brain off to enjoy it, then you aren't enjoying it. Yes a song may have a great beat (bumps in the whip) Is this song edifying to you in any other way? If it doesn't make you feel good when listening, or have you making faces at how stupid it is...why do that to yourself? We do have this generations Big Daddy Kane, Rakim, Kool G Rap, LL Cool J, Big Pun, Pac...if somebody just looks. Why put the good ones in with the bad, to make a point? It sounded strange to me is all. \textbf{Nothing} to do with your original statements, just something I saw that I wanted to challenge.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/166 & \cellcolor{green!5}0.602 \\  \hline
  \cellcolor{green!27}\small feefo you just said \textbf{ageism} gas no expiration date as in Jay Z and Nas bcuz they came up I'm the golden era of Hip hop, right? Ok what about the artist like yachty, desiigner, Kodak \textbf{black} etc -do you think they will still be relevant in years to come? will they still pyt out quality music like Nas or jayz?? Hell fucking No. does anyone see my point???\normalsize   & \cellcolor{green!27}Ageism, Black & \cellcolor{green!27}Age - General, Ethnicity - Black & \cellcolor{green!27}2/69 & \cellcolor{green!27}2.899 \\  \hline
  \cellcolor{green!5}\small the industry wants to down play hip hop and the artist that come out today looked up to soulja boy or other artist like that who would continue to make bullshit music. it's like a virus. while we was coming up hip hop taught u "write from wrong". hip hop was a culture. hip hop should have artist who can spit bars. these artist today don't do none of that. burrito does not understand the youth is listening to \textbf{nothing} but bullshit and that will down play not only hip hop but society in general.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small that "sell out" \textbf{dumb} stupid ignorant shit is corrupting hip hop. for god sakes the XXL freshman freestyle were trash!! hip hop used to actually mean something but now it's damn near how \textbf{racist} white people see \textbf{black} people. think about it. alot of artist are dope but they don't get a solid come up bcuz artist like desiigner who makes one track and blows up then that ignorant prick is giving hip hop a bad name. I domt even want to say hip hop anymore, now it's damn near just rap. hip hop is a culture and if you think yatchy or whoever is true to hip hop culture you are \textbf{crazy}. the industry wants the hip hop culture to be degraded.\normalsize   & \cellcolor{green!27}Black, Crazy, Dumb, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/123 & \cellcolor{green!27}3.252 \\  \hline
  \cellcolor{green!5}\small Shit I'm \textbf{deaf} on my right ear\normalsize   & \cellcolor{green!5}Deaf & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Bruh just listen to what you want to listen to. Don't let anybody pressure you into listening a certain type of music (\textbf{old} or new).Discover the soundtrack to YOUR life not just  everyone else's.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I think when an artist gets their initial shine its because theyre doing something trendy, but what most of DEHH isn't really getting is that to CONTINUE to stay hot they have to bring something of their own to the table.Lil Yachty, 21 Savage, Lil Uzi, Playboi Carti (edit) AND Kodak \textbf{Black}, all have their own style and bring their own unique characteristics to the table. If they arent poppin in 2 years, thats still on them. It's not that hard to understand\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small If you dont want to listen to \textbf{old} rap....who cares.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small there needs to be a balance on the radio \textbf{nobody} doesn't wanna hear 21 savage and yatchy all the time and we need more people like chance and anderson paak\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Feefo is the second best guy in DEHH behind Myke imo. Ken just sounds like a bitter \textbf{old} man, most of the time. And Beezy doesn't say much to begin with.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small How many videos have you seen on this channel, ShowTime? A bitter \textbf{old} man wouldn't like 2 Chainz or Lil B (which Ken does) and Beezy talks more than you think. Hell, he talked a whole lot on this one.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Oh hey, dickdick911911; it's been a short while. LOL Are you still having trouble admitting that Eminem being the best is NOT a fact? Haha Anyway, he dumbed himself down to like Lil B back in the day and in those \textbf{old} videos where DEHH talked about Lil B, he couldn't even make the least bit of sense to back up his points. Besides, I'm pretty sure that's not what ShowTime meant by "bitter". He was going more of the "being close-minded to that bullshit music" route, which Ken has shown many times the exact opposite of that, whether he hates fools like Yachty or not.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small \@Robert Kirby thats just what kids do now a days, anyone who doesnt like mumble rap is an "\textbf{old} head"\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@Robert Kirby try telling these kids that, they called a 16 year \textbf{old} an \textbf{old} head for bashing lil uzi vert LMFAO\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Robert Kirby apperently these kids think hip hop is just music and \textbf{nothing} else. whatever goes into hip hop is what the kids of each era soak up, its actually fucking \textbf{crazy} how much control these artists have on this generation or any in general, which makes any bullshit seeping through very dangerous\normalsize   & \cellcolor{green!5}Crazy, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small Lines from Lil Yachty - Im sorry ft Thegoodperry I can relate "Always arguing cause you a critic""Yeah, I said the wrong lineWish I could rewindWant to take you out, fine dineWant to make you my dime""Tell me where you goingProbably somewhere out there hoeingI'm always quick to judge, yeah, I know itBut this time, this timeI sure caught you slipping this timeWish I didn't have these thoughts on my mindBut I did some time, oh, what do I doOh, that's your brother not your \textbf{nigga} baby, I didn't know"\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small I wasn't hearing the other dude with the \textbf{r\textbf{ed}} cap either, but it's all good. Greetings from Brazil! a lot of people watch you guys over here, keep the great work!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small He definitely acts like an \textbf{old} man\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small rock heads don't disrespect \textbf{old} rock heads\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Rap Critic got that \textbf{old} man swagger.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small There's no excuse for not knowing \textbf{Old} Hip Hop, there's the internet. I'm 19, I never had OutKast or Biggie or Pun or Run DMC at my disposal. I YouTube'd the albums, sat down and listened to. No excuse for "That's before my time".\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small There is no need for an excuse if a person doesn't want to listen to \textbf{old} music\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Nobody should be forced to listen to what they don't want to listen to, whether folks consider it mandatory or not.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Yea but it is before there time. Not everyone wants to listen to \textbf{old} stuff lol you cant make someone who listens to beats now and go back and enjoy something like RUN DMC not everyone is like that. It was from a different time I cant relate to what most of them rapped about not everyone likes that \textbf{old} sound now I enjoy older albums but I like my newer albums more because it is closer to me and MY time.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/82 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small +VinWizzy No. But if you consider yourself a source of the genre, then it'd be best to learn the history of Hip Hop. Likewise, Hip Hop's history is more than just music, it's \textbf{black} history. What you're saying is like "Why should I have to study about MLK, he's before my time"... that's fucking stupid. History is extremely important.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small +Darrick Franklin History is important. They don't have to like it, but if you want to critically analyze the genre, and if you want to call yourself a fan, then you should transverse into all aspects and the history. Likewise, that excuse is a cop out. How do you know that people won't like the \textbf{old} shit just because it's \textbf{old}? That's like saying "Dr. Martin Luther King Jr is \textbf{old}, we should be studying Kanye because that's our time". Come on kid.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small so you listened to the funky 4+1, grandmaster flash, furious five, melly Mel, Kool Moe Dee? honestly it's \textbf{weird} we require everything in the late 80's and throughout the 90's to be listened too but \textbf{nothing} before or after that. You cant make a certain artist, song, album or even project a must thing to listen too or else you aren't a "fan" because honestly who are you to say that because what if they simply don't like it? Well according to you their isn't any way around it you either listen or don't that's jacked up\normalsize   & \cellcolor{green!5}Nothing, Weird & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/97 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small \@TheShutYoMouth there is no real significance in being recognized as a fan of something .. there is no real measure to what excactly a fan is and being called a fan certainly doesn't add to the listening experience. So biscally, ur reasoning behind making it an obligation for people to go listen to \textbf{old} music is not really that important.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small You don't have to listen to everything but if you like hip hop you should listen to great albums regardless when they came out, I can't take somebody seriously as a hip hop fan if you haven't heard certain artist or albums. The 90s wasn't that long ago, it isn't "\textbf{old}".\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small +Darrick Franklin I disagree with the notion that taste is subjective. Quality is subjective. But not taste. You can't taste an \textbf{apple} pie and tell me there's no \textbf{apple} in it and that's your opinion. You can't hear Hip Hop and say that a repetition in sound is innovative or that a complex layered track is lack luster.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small +MaskedAvenger13 Exactly. What's going to happen is that this generation will do the exact same thing they hate "\textbf{Old} heads" for doing. So when their kids don't know who Kendrick Lamar is, the cycle will continue and they'll feel like retards.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@TruMusic89 ahahah you know \textbf{nothing} about production if you think they went back and "Stole" parts of music\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@TheShutYoMouth there's very few producers from the 90s who could create a beat from scratch, almost all of the ones today can though, what you know about making instrumentals from scratch and musical composition? the same as most 90s producers, \textbf{nothing}, which is why they stuck to sampling\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small +Mylo Then why are you in this conversation? The topic is \textbf{Ageism}. No, you don't have to go back and listen to everything. But if you'd like to deem something quality and contribute to the genre, then you should, because how do you know quality? If none of that matters to you as a listener, then exclude yourself from the conversation. However to those who are here to discuss hip hop and share ideologies of a Top 10, and what the deem as quality, they'd better do their homework.\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small +TruMusic89 Oh man. You are on some other shit. Sampling is what made Hip Hop. DJ's started by Scratching and Sampling over tracks, then they evolved into producing their own shit. Hip Hop has never been whack lyrics. Never ever ever has anyone made a universally acclaimed Hip Hop track, with shitty lyrics. You say you know hip hop, but you don't because you don't understand that Sampling is different from Lyricism. That's the dumbest shit I've ever heard. Likewise, plenty of Hip Hop producers from the 90s could produce a track from Scratch. Those you listed do also sample. Boi-1da samples like \textbf{crazy}, he interpolates shit into his tracks as well. Your argument is a God awful one, and I pray that you wake up one day and realize how fucking stupid what you are saying is. Good luck lol\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}\small \@Mylo i agree Mylo, there's no obligation to go back and listen to \textbf{old} music if you dont want to, there's no rule book to music, people can do what the hell they want\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small \@TruMusic89 You guys really know \textbf{nothing}, playing instruments in hop hop production is irrelevant, you think new producers are playing a drum set? no they are using programmed drums on a drum machine, at least back in the 90s you had to find drums, chop them up individually, add compression or whatever sound you wanted and then resequence them how you wanted. Today they just have programmed drums.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small \@MaskedAvenger13 it didn't take more creativity back then, the music was already there, where was the creativity? you just took more time looking for somebody's nice sounding drum to take, it takes more creativity to create from scratch because you start from \textbf{nothing}, a completely blank slate, it takes absolutely no creativity to take a musical phrase from an already created song because the work is already done for you\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small \@theshutyomouth what if I did go back and didn't like the \textbf{old} shit and just like the newer shit?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Sol King​ exactly, nobody's obligated to learn \textbf{old} music just to please oldheads and young elitists, if you enjoy it, then that's cool, but it's not a requirement to be a rapper\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@TruMusic89 You don't have to listen to anything, but calling it 'old' or 'irrelevant' just because you know \textbf{nothing} about it is just a cop out. Would you take somebody seriously as a NBA fan if they don't know who Michael Jordan or Shaq is because their 'old'?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@TruMusic89 Right but eventually they would come across footage of them players or be interested in seeing footage of them, they wouldn't just be like 'fuck them \textbf{old} dudes' just because they are clueless about them, Their fav rappers are gonna be '\textbf{old}' too in five minutes.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small I know I'm definitely getting \textbf{old} because I could only hear this in one ear.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Joshua H Only happened when the moderator is speaking, so not an issue. I just wanted to make a joke about being \textbf{old} 😥\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Nationality - Irish}  & \cellcolor{red!27}Mick & \cellcolor{red!27}5 & \cellcolor{red!27}5/22800& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Roman Catholic}  & \cellcolor{red!5}Mick & \cellcolor{red!5}5 & \cellcolor{red!5}5/22800& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age, Ageism & \cellcolor{red!27}19 & \cellcolor{red!27}19/22800& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Red, Squaw, Apple & \cellcolor{red!5}8 & \cellcolor{red!5}8/22800& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Red & \cellcolor{red!27}4 & \cellcolor{red!27}4/22800& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old, Elder & \cellcolor{red!5}78 & \cellcolor{red!5}78/22800& \cellcolor{red!5}0.33999999999999997 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, Boogie, Nigga, Buck & \cellcolor{red!27}15 & \cellcolor{red!27}15/22800& \cellcolor{red!27}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Zero & \cellcolor{red!5}25 & \cellcolor{red!5}25/22800& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}6 & \cellcolor{red!27}6/22800& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Transexuality}  & \cellcolor{red!5}Transition & \cellcolor{red!5}1 & \cellcolor{red!5}1/22800& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Crazy, Dumb, Lame, Mental, Weird, Deaf & \cellcolor{red!27}28 & \cellcolor{red!27}28/22800& \cellcolor{red!27}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!5}Dot & \cellcolor{red!5}2 & \cellcolor{red!5}2/22800& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Ethnic, Racist & \cellcolor{red!27}2 & \cellcolor{red!27}2/22800& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho & \cellcolor{red!5}1 & \cellcolor{red!5}1/22800& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}1 & \cellcolor{red!27}1/22800& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}1 & \cellcolor{red!5}1/22800& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Japanese}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}1 & \cellcolor{red!27}1/22800& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Nelly & \cellcolor{red!5}1 & \cellcolor{red!5}1/22800& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Nationality - Irish;Religious Identity - Roman Catholic;Age - General;Ethnicity - Native-American; Ideological and Political Identity - General;Age - Over 65s;Ethnicity - Black;Age - Youngsters;Social Class - Working class;Sexual Identity - Transexuality;Physical Identity - Physical (and Mental) Impairments;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Ethnicity - General;Gender - Female sexuality;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Chinese;Nationality - Japanese;Sexual Identity - Male homosexuality;%.

\item The percentage of hate speech related words is 0.8904.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 205/531 occurences of hate speech related comments.\end{itemize}\end{document}