\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_159.json :}\newline \par\Large\textbf {Title: \large  Fighting Ageism On YouTube \& In The Beauty Industry | Beauty Blogger Over 40 }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Thanks so much for fighting \textbf{ageism} we r mature not dead. I am just now finding the time to take more interest in more makeup and more fashion. It's time we fight \textbf{ageism} in life as a whole ❤️\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small So very, very true and I am with you on this 100!! Whoever made rules for the beauty community must not be of a certain \textbf{age} group in the mature community, or if they are maybe they came from a generation or never felt the need to wear or do certain things. I always tell people to wear what makes them happy, and what they enjoy. In my book there are no rules at all, I go with it, and smile :) Have a good weekend, you now got me intrigued to do a video also about this very thing. XOXO <3\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small I am a total believer in spreading the message that we as mature women need more cosmetic company representatives. I too hate when skin care and cosmetics demonstrate products on younger women who have no visible need for it like u see with eye creams, etcThank you for doing this awareness campaign. I will be joining the YouTube community soon to talk and show \textbf{woman} with physical limitations using beauty products. As we \textbf{age} sometimes we develop arthritis and other functional limitations that make us adapt or repurpose tools and products to meet our needs. But make no mistake we are also extremely passionate about beauty products and have been gravely overlooked for yrs\normalsize   & \cellcolor{green!27}Age, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/115 & \cellcolor{green!27}1.739 \\  \hline
  \cellcolor{green!5}\small Ha I just turned 51. Always loved makeup but never wore eyeshadow till last year. Now I am obsessed with it! False lashes as well. Shimmers, colors, and mattes. I agree with you 100. We are as \textbf{old} as we feel and still get excited about makeup and beautiful things. Love your video and the message ❤️\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Absolutely agree, I'm 50 next year, I've only just really got into skin care \& makeup, I've looked after my kids being a stay at home mum for 20 years, , now 2 of 3 have left home, I have a job, we own our own home, but such a lot of skin care is aimed anti \textbf{ageing} , I'm not 'anti \textbf{ageing} '  I want to embrace my \textbf{age}, I want to look the best I can! I want to be confident, and companies really need to hear our voices!!\normalsize   & \cellcolor{green!27}Age, Ageing & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/91 & \cellcolor{green!27}3.297 \\  \hline
  \cellcolor{green!5}\small Well said! I absolutely agree, I am 53 years \textbf{old} and love make up, I try to buy as much as possible, just like you said, at this point in my life I have more money than when I was in my 20's, my children are grown and now it's time for me to do more for myself, this goes for cosmetics, clothing, etc. it drives me \textbf{crazy} when I go shopping for cosmetics and clothing, I can walk inside any clothing store and find all kinds of cute clothing in the junior section but as I go into the women's section I can't believe my eyes, us mature ladies want to look as good as we possibly can as well, I go into my local cosmetic store at the mall and it seems like the sales people are so focused on the ladies that are 20's - 30's, if your over 40 then you don't get the assistance you should have. Thank you for speaking up for all of us mature ladies.\normalsize   & \cellcolor{green!5}Crazy, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/173 & \cellcolor{green!5}1.156 \\  \hline
  \cellcolor{green!27}\small Old \textbf{age} and treachery will always overcome youth and skill.  snicker\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Im sorry but I'm going to have to disagree with you 35 mature skin really?? I don't think so even 40 is NOT mature skin at all! even 50 isn't mature skin things don't really start changing I'm talking about actual wrinkles not lines! Tell about \textbf{age} 56 around there. although I will say for me I'm a natural blond and we do \textbf{age} quicker it's the pigment of our skin so about the \textbf{age} of 49 i guess I had to start totally wearing different eyeshadow colors that I never would have worn when I was younger! and had to start reapplying makeup totally different otherwise I looked like a clown literally!!I'd always been able to wear a lot of \textbf{crazy} colors but dark Browns and \textbf{BLACK} EYELINER was my number one look!!\textbf{black} eyeliner does NOT work for me at all anymore I look like a streetwalker nor do the brown eyeshadows and lipstick colors I could wear any and every color which I can't do anymore especially dark colors that's very aging especially when they're Matt I never really wore Foundation just blush and bronzer I still can't stand the foundation I don't really have \textbf{age} spots I'm 61 but yeah I won't buy a lot of products because it's promoting an anti-aging product especially moisturizers or eye creams they're promoting and have a 13 to 20 year \textbf{old} up there as the model I simply WON'T BUY their product!! Because that SCREAMS to me it is NOT an ANTI-AGING PRODUCT at all ! Thanks so much for sharing\normalsize   & \cellcolor{green!5}Age, Black, Crazy, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}8/261 & \cellcolor{green!5}3.065 \\  \hline
  \cellcolor{green!27}\small Hi Sue, I understand what you're saying about aging not starting until after 50, but I started getting wrinkles at 40 \& noticed changes in my skin at 30, I wish I had started on Retin A at 30.  That just shows us that everyone is different. And you're right we don't have mature skin at 35, but using anti-aging products at that \textbf{age} would really help stave off wrinkles as we get older. thank you so much for watching xx\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small I'm a more mature \textbf{woman} who loves make up. I will sparkle forever! 😉\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Wonderful video Melissa !! I will be 50 in a few mths-long story short-I haven't worn any type of makeup since I was pregnant with my 1st of 5 children at 24. Fast forward to March 2018 \& I started dabbling in makeup again. BOY is it so different than it was back then. BUT the only thing that hasn't changed is the ‘young perfect looking models' that companies use to sell their product. I understand they do what they have to, to attract the public BUT it's giving younger generations the wrong impression. 'Wear this and you'll look perfect' or 'wear this and you'll have radiant skin(for life)' but it doesn't work that way. These companies definitely need more mature models, say 45 \& up that actually have some wrinkles to show that hey, even though we \textbf{age} we still want to look beautiful as well !! We'll \textbf{age} gracefully !!! Hugs girl xoxox\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/155 & \cellcolor{green!27}1.29 \\  \hline
  \cellcolor{green!5}\small Girl you nailed that quote again!! Great video...I love your channel, and you're video is great. You are a wonderful representative of our \textbf{age} group. I love it\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small MrsMelissaM Beauty yvw. I appreciate you doing the videos for \textbf{woman} of our \textbf{age}. I will keep watching and keep recommending your channel to everyone I know!!\normalsize   & \cellcolor{green!27}Age, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Very well said Melissa.  I agree with everything you are saying (I also love that commercial).  I've been wearing makeup since I was 17 years \textbf{old}.  I am now 53 and still continue to use it, although now I do use much more products under my makeup (such as primer, moisturizers etc) to make sure my make up still looks good on me. I love to wear false eyelashes and look at all the makeup trends and I also love to buy much of the new products that come out.....so not sure why makeup companies would think that you are no longer significant once you reach a certain \textbf{age}. Plus, as you pointed out, I am at that \textbf{age} where my kids are grown and I can afford to pamper myself more (although I must admit I always have).\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/139 & \cellcolor{green!5}2.158 \\  \hline
  \cellcolor{green!27}\small its funny, I am 63 years \textbf{old}, and I feel like im 40, and I don't think I look 63 either, people always say "oh my God", you are WHAT ?????  It makes me feel great !!!! And I don't wear makeup everyday either, I work in the medical field, so its not necessary for me to...…….but I love it on the weekends !!!! love you, Simone\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small Yesssss I'm turning 60 in October cannot believe it!!!still feel 25 in my mind.  But I loooove makeup and found YouTube about 6 mos ago and I'm soooo enjoying u all!! I work the front desk at a \textbf{doctors} office and sooo love doing different makeup looks every day.\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small My mother and her \textbf{age} group (she's 90) wore super minimal makeup.  Their daughters and granddaughters grew up playing with makeup.  I'm 64 and have a huge collection and still play and play with it.  I think cosmetics companies are stuck thinking of my mother and not catering to their descendants.  I love when Bobbi Brown features older, everyday women.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small Im hoping people like tati as they \textbf{age} will still do videos as a more mature \textbf{woman} as she is one of the people I watch and know she is going to give a good review of a product also emily noel she will be doing this at 60 im sure.  Thats one of the reasons I started watching you as you have some of the things I do.\normalsize   & \cellcolor{green!5}Age, Woman & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small Spot on Melissa.  What makes the most impact with cosmetic companies? Stop buying! Letters and calls are great and may get you some lip service but money is the bottom line- always. There are so many cosmetic/skin care  companies now that we can be selective. If you see an add with a 20 something \textbf{woman} advertising anti-aging products stop patronizing that company.  Personally, I feel the same about skin care companies that blatantly make claims about a product that are patently false. Companies arrogantly assume that people will not read the ingredients or research the validity.  As mature women, we are smarter than that! And with YouTube there are some great, easily accessed  resources  that enable us to take responsibility for what we put on our faces and bodies. I find it abominable that L'Oreal and Lancome have two new foundation products they have labeled as "broad spectrum SPF" when the only filter is octinoxate. Octinoxate does not filter UVA rays, the rays that go deeper, cause skin damage, destroy collagen and contribute to cancer. Because they are categorized as make up and not as sunscreens they do not have to meet FDA testing. Thanks for expanding this discussion. Hugs to you.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/202 & \cellcolor{green!27}0.495 \\  \hline
  \cellcolor{green!5}\small Right on!  I will forever use makeup!  We are a strong group of women!  Confident in our appearance.  I am \textbf{old} enough to do what I want and I don't follow the so called rules of \textbf{age} related makeup!  I have a grand daughter who is amazed that her grandmother will wear a blue diamond lip gloss!  😂 I told her everyone should wear makeup that they like as long as it is tastefully done!  I'm with you a 110  that the beauty industry needs to use more mature looking women!  ❤️❤️❤️❤️❤️❤️\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/92 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small I really hope that as some of these get older, that they will understand. Ironic that they will be able to see their young beautiful faces \textbf{age} as the years go by.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small A-1 video thank you! I'm 57 years \textbf{old} and feel you hit the nail on so many heads. Hope the cosmetic companies you contact really take a good listen because I do feel they are missing out on a huge demographic. Big hugs, 💕.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small I can picture you recommending things you like to people in the store 😄I love how you follow your own rules. You have a great point that the companies might think our generation wants to play it 'safe' and not experiment - actually I experiment MORE now because I can't just slap on any ol' concealer, powder, or lipstick like before (liquid lipstick? Not happening. Ever) I used to buy the same things over and over 20 or 30 years ago. I'm also way more picky than I used to be because of experience with makeup in general, like everyone else who's over 25. One thing I will say that bothers me that isn't talked about for sensitivity reasons -  big channels with millions of subscribers (who take in every word they say) are very vocal about discrimination when it comes to shade range, saying companies don't acknowledge all demographics and only cater to certain skin tones, and that's a valid point. They will literally boycott and encourage others to follow suit to send the companies a 'message'. Ok, great, but I never hear any of them complaining that certain \textbf{age} demographics are being excluded. I'm sure the companies are making what sells and don't need to consider \textbf{age} (in their minds) because they are making money regardless. I hope this makes sense.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/223 & \cellcolor{green!27}0.897 \\  \hline
  \cellcolor{green!5}\small It completely made sense Wendy.  \textbf{Ageism} is a real thing.  I remember my mom 10 years ago saying that it's awful to get \textbf{old}.  And it made me so sad.  Now I'm aging, I feel that way many times.   One thing I really don't like is the lack of respect that young people have for older ones.  It makes me furious when I see some of them making fun of older people.\normalsize   & \cellcolor{green!5}Ageism, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Love your message.   I am 51 and since I was 13 years \textbf{old} I have warn makeup and will never stop.  Wrinkles and all.  I am behind you I'd you need any help!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Definitely agree with you Lisa.  I've only ever seen 1 \textbf{woman} over 30 working in there. xx\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small In my opinion \textbf{woman} our \textbf{age} I'm 40 spend more on cosmetics and skincare and we share what's great too !\normalsize   & \cellcolor{green!27}Age, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small I agree with everything you've said Melissa. I'm still vital and want to look my best, even if the world only sees my crinkles and wrinkles. I'm still looking at the world through the eyes of a 25 year \textbf{old}, however the world looking back only sees the almost 48 year \textbf{old} shell those eyes are in! Its about time the beauty companies got with it and started to value and represent the mature consumer.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small Great video! I couldn't agree more. I'm in my 50's and I still care about my looks. And I agree with being more vocal, with \textbf{age} comes wisdom and I want to share what I've learned! ❤️❤️\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Great video. I've been in the beauty industry since I was 21 years of \textbf{age} I'm now 57 I like teach women 40 plus how to use makeup I agree with everything you say in this video it's just knowing how to apply makeup it doesn't matter what \textbf{age} you are! keep flying the flag for the older \textbf{woman} Melissa you're doing a great job 😊\normalsize   & \cellcolor{green!5}Age, Woman & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}3/66 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small hi Kimberly, ok here's where I step back on my soap box.  As a WOC I bet it's doubly frustrating to find shades and colors that work.  That makes me \textbf{crazy} when I see brands with like 5 foundation shades and the darkest one is medium at best.  That's one of the reasons I adore Juvia's Place! They stepped in and saw that need and took matters into their own hands.  I see them doing huge things.  I love it.  I hope you've found them too.  I hope my content helps, albeit a little. hugs lady\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}\small Sing it sister :) because we got a very large soap box !!! About a year ago while watching Sephora videos, me and some others were complaining where was the older models?? Do more with videos about aging ...and Sephora did start putting put those kind of videos...I think if us ladies start to bring this up that we matter too, we could be heard ...we just can't give up...my mom has always wore a \textbf{r\textbf{ed}} lip, and did her eyebrows all the time (and still to this day she paints her toe nails \textbf{r\textbf{ed}})...\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/95 & \cellcolor{green!5}4.211 \\  \hline
  \cellcolor{green!27}\small christine ronewicz Your Mom sounds like my kind of \textbf{woman}!!! 👍🏽👍🏽\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Apple of my Eyeliner thanks so much :) ...she near her 90 , she don't wear a lot of makeup,  but that's her basic, she has to fill in her brows, but never have I seen her with her \textbf{r\textbf{ed}} lip and toe nails lol ...I asked her once why do paint your toe nails \textbf{r\textbf{ed}} all the time, she said, you never know when you will kick your shoes off and dance lol ...I always paint my toe nails maybe not \textbf{r\textbf{ed}}, but they are paint, you never know when I may want to dance lol...sorry for the long comment ...have a great day :)\normalsize   & \cellcolor{green!5}Apple, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}7/106 & \cellcolor{green!5}6.604 \\  \hline
  \cellcolor{green!27}\small Apple of my Eyeliner sorry for your lost, your mom would be very proud of you,  yea she shaking her head with a great big smile on her face saying yup that's my daughter :)\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Melissa you took the words right out of my mouth!  These are my EXACT feelings about the beauty community!  The only companies I have seen who use more mature women in their campaigns are Lancombe and Covergirl.  I wonder what all the other brands would think it all of a sudden we stopped supporting them the way they stopped supporting us at a certain \textbf{age}?  I feel sure that we are spending more money on products whether it be for ourselves or for our daughters and granddaughters.  A 15 does not have the money for Two Faced, but Mom may!  I also think the beauty community within platforms like YouTube and Instagram are sending the wrong message to our youth.  I think more and more young people feel like looks are all you need in life, that everyone focuses their time on perfect makeup and then capturing each second of their lives with selfies.  What do I have has become more important than who am I.  It's sad and it's going to affect the future.  Beauty gurus don't have perfect lives.  They work hard, have ups and downs, heartbreak, frustrations.....just like everyone else.  However the younger ones portray perfect lives, perfect homes, perfect makeup, unlimited money all the time.  The younger generation is striving to be like their favorite YouTuber but the problem is that YouTuber is only showing their viewers as much of them as they want us to see.  We are seeing editing and pieced together parts of their lives.The message across the board needs to change.  Hugs Melissa!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/262 & \cellcolor{green!5}0.382 \\  \hline
  \cellcolor{green!27}\small Apple of my Eyeliner yes!  I think we in the mature demographic need to become more outspoken about it!  If we all picked a certain month or time period and bought NO beauty products maybe they'd understand how much of a difference we make on the bottom dollar!\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Good on you Melissa!! I switch off when I see an advert on TV or in magazines when a 20 year \textbf{old} is telling me that " gosh my wrinkles have disappeared since using whatever " even my husband shakes his head.I have bought so much more since I found influencers like you, I was able to make an educated decision.😘😘\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small SING IT SISTER! Thanks for representing us with such passion! I love it! I watch YouTube gals from 20-75. I myself just turned 62 \& after watching some younger girls with absolutely gorgeous skin cover it with full coverage foundations \& concealers I just have to end with our \textbf{age} group who are truly struggling with aging issues. I can't even wear most of the eye looks because my eyelids are literally laying on my eyelashes!! Hmm maybe \textbf{crazy} glue.. Oh the pain of it all lol!\normalsize   & \cellcolor{green!27}Age, Crazy & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/87 & \cellcolor{green!27}2.299 \\  \hline
  \cellcolor{green!5}\small I'm giggling as I'm reading the last comment about \textbf{crazy} glue Kathie, believe me, I've thought about it too!!  My dad had that problem with his eyelids and he ended up having surgery, I was like "dang dad, little vain these days" lol.  hugs to you sweetie\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small I'm 50, but I look younger now than I did a few years ago when I'd "given up" after developing a chronic illness. When I found the Mature Beauty Community on YouTube and started watching videos not even a year ago, I knew \textbf{nothing} about skin care or makeup. It's the same with some (definitely not ALL) of the Mature Fashion Community! I'm so glad I've found Melissa and a select few other Mature ladies that are all about breaking through the myths! I'm not a grandma (yet), but I don't EVER plan on looking (or dressing) like one! 💅🏼💄🤳🏼\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small Oh man Marti, I totally agree with you.  When Kayla got married and they were saying do you want to be called Nana...I'm like noooooo! Sounds like a \textbf{banana} to me. lol.  I think I've got a few years left too, but you know what I mean.  I think I'll be the grandma out pushing the envelope to help them find their way and Trying to teach them to love their inner selves first...\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small Hi Mrs M Fabulous video ....\textbf{Hun} xI feel like the cosmetic and fashion industry are stuck in a time shift and that it's still the 1940's 50's 60's 70's and even 80's where once you reached a 'certain \textbf{age}' out came the muted colours minimal makeup, sensible shoes ... conservative clothes ... like my granny used to wear ... Oh and you have to have a sensible type of hair cut 😳 my granny used to get it curled and set every week ... I say hell NO.I also wish beyond wish they'd drop the term 'Anti \textbf{ageing}' it drives me \textbf{bonkers} why do women \textbf{age} but older men just look Fatigued!!! Like Really !!! I don't think so!I'm 46 and I've already told my kids I'll be \textbf{ageing} disgracefully 😂 when they asked at my 45th birthday when would I be toning down what wear getting my hair cut oh and stop colouring my hair 😳 I said NEVER 😂😝\normalsize   & \cellcolor{green!27}Age, Ageing, Bonkers, Hun & \cellcolor{green!27}Age - General, Nationality - German, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/164 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small I totally agree with you, Melissa! You should be able to wear whatever you like \@ any \textbf{age}. We are all beautiful in our own way. Just do what makes you happy. I also think there should be more of a presence of mature Women in ad campaigns. Especially for products that are designed for us in the 1st place. Lol! Love ya! TFS! ~ Nona\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small I was just saying that to someone Nona, I mean use a 16 year \textbf{old} for an anti-aging campaign and what do you think they are going to anti-age to? 3 or 4 years \textbf{old}? lolo  love you too\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small When I'm 95 I'm still going to be rocking my makeup and that includes shimmers. Purple and pink are my neutrals and that won't ever change. Neither of my daughters, one 23 one 20, even wear makeup and that's the generation Beauty Companies are after. Many of their friends don't wear makeup either! I watched Risa's video and it was so well done but I get so frustrated because we aren't listened to. The \textbf{woman} in that Cover Girl commercial is also an IT Girl but it's time other companies pay attention. You did a fantastic job with this video.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/100 & \cellcolor{green!5}1.0 \\  \hline
  \cellcolor{green!27}\small Amen sister! As a consumer I'd like to see more people that are our \textbf{age} represented. I think I might contact some of these cosmetic companies myself and tell them how I feel. Just because I'm not a YouTuber or anything shouldn't matter. Thanks for the idea. Love you sis ❤️💎🌻\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small How did I know that you would be one of my cheerleaders doll? Love you so much, go get them \textbf{sissy}!\normalsize   & \cellcolor{green!5}Sissy & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small That is so true. Just because women are older doesn't mean that they don't care about makeup. It is the exact opposite because we are getting wrinkles, \textbf{age} spots and things like that so we want to make ourselves look the best we can. I quit wearing makeup for almost 20 years and I started back up this past year because I had some health problems in 2016 that changed how I looked for a while and it made me feel bad about myself. I am healing and starting to look more like I use too but I realized that even without the health problems, I don't look like I did 20 years ago which is a duh because I will be 48 this year and therefore my 20's was long ago.  So, you go girl!!!!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/136 & \cellcolor{green!27}0.735 \\  \hline
  \cellcolor{green!5}\small Julie Bryant - Good for you for starting to take pride in your appearance again! I had a \textbf{freak} accident in 2009 that left me in a wheelchair or on crutches between the 3 surgeries I've had since then (surgery 4 coming up), so I gained over 50 pounds and with all the steroids I didn't look like ME at all. Then a few years ago I developed a chronic illness and when I had to give up my career, severe depression kicked in. I stopped wearing makeup and stopped caring how I looked. My husband divorced me (was final earlier this year). But I lost 70+ pounds a year ago and that gave me motivation! About 6-8 months ago, I started watching Beauty videos and getting into makeup. I'd used the same drugstore stuff for 35 years (I'm 50), and I'd never heard of any other brands except maybe Clinique. Haha! So, everyone comes to this point in their lives differently and at different ages. Just keep it up this time! I'm never giving up on myself again... I'm single and now is the time I REALLY need to look good. 😁 HUGS for more healing!!! 🤗🤗🤗\normalsize   & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/198 & \cellcolor{green!5}0.505 \\  \hline
  \cellcolor{green!27}\small Marti, I've heard your story before, but it never ceases to amaze me what a strong \textbf{woman} you are through these unimaginable problems.  You're star shines so bright my friend and I'm so glad I get to know you and call you my friend.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small At 58 yrs \textbf{old} I love makeup more than ever and I'm so glad we have strong women in the YT community like you that stand up to these companies.  But more than that I'm glad I can watch a YT video and feel like I'm part of this group of mature beautiful women that help me to be the best I can be.  You have shown me that all the silly rules about \textbf{age} and makeup are ridiculous and I'm having so much fun trying new things!!!\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/88 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small great video 💜💕💛💕💙💕 exactly what \textbf{age} is that because I always like to feel good about myself... exactly what \textbf{age} is that because I always like to feel good about myself\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small I watch Risa, she is a classy , beautiful \textbf{woman} ....💜\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Lori Abercrombie Congrats, Fifty is a Tricky \textbf{age}, and when people would ask my \textbf{age}, I snapped a little saying I was \textbf{old} enough to have manners and  know how insanely rude it is to go around asking people you just met their \textbf{age} 👹(I guessI was uncomfortable with my \textbf{age}) BUT...  when I turned 60,  I realized I was saying my \textbf{age} loudly \& proudly,👸 of course to the same ill mannered crowd, yet they were nice enough to say your not 60..I can't believe your even in your fifties, no way, you must be in you early fifties..or mid fifties...I assured them if I was going to fib about my \textbf{age} I would not increase the number 5 to 10 years. But I thanked them... I like the sixties so far. Better then adjusting to my \textbf{age} in my fifties. So embrace your \textbf{age}, look into anti inflammatory diets, love your skin care, and I thank my lucky stars I started skin care early on, and if you haven't, embrace it now, its your most productive quiet time to spend with your self, and use your Sunscreen all seasons, on sunny or cloudy days. (Notice I didn't mention exercise, hmm...That's a thought to add to your bucket list). Oh and if you want a chuckle, do look on the Estee Lauder web site and look at the GIRLS, promoting EL products, if one of them is over 16 years \textbf{old}, I will be shocked. But I love love Estee Lauder, used it since I was 30, adore the Advanced Night products.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}10/263 & \cellcolor{green!27}3.802 \\  \hline
  \cellcolor{green!5}\small Hi Gee, you cracked me up with the \textbf{old} enough to know better...lol.  And my biggest beef about companies like Estee Lauder is they are marketing stuff as "anti-aging"...what do you want those 16 year olds to look like...3 years \textbf{old}?  it's ridiculous truly xxx\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Ageism, Age, Ageing & \cellcolor{red!27}47 & \cellcolor{red!27}47/8231& \cellcolor{red!27}0.5700000000000001 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Woman & \cellcolor{red!5}12 & \cellcolor{red!5}12/8231& \cellcolor{red!5}0.15 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}20 & \cellcolor{red!27}20/8231& \cellcolor{red!27}0.24 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Crazy, Bonkers, Freak & \cellcolor{red!5}7 & \cellcolor{red!5}7/8231& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black & \cellcolor{red!27}1 & \cellcolor{red!27}1/8231& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}doctors & \cellcolor{red!5}1 & \cellcolor{red!5}1/8231& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Red, Apple & \cellcolor{red!27}7 & \cellcolor{red!27}7/8231& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Red & \cellcolor{red!5}4 & \cellcolor{red!5}4/8231& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing & \cellcolor{red!27}1 & \cellcolor{red!27}1/8231& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Banana & \cellcolor{red!5}1 & \cellcolor{red!5}1/8231& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - German}  & \cellcolor{red!27}Hun & \cellcolor{red!27}1 & \cellcolor{red!27}1/8231& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Sissy & \cellcolor{red!5}1 & \cellcolor{red!5}1/8231& \cellcolor{red!5}0.01 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - General;Gender - General;Age - Over 65s;Physical Identity - Physical (and Mental) Impairments;Ethnicity - Black;Nationality - General;Ethnicity - Native-American; Ideological and Political Identity - General;Age - Youngsters;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - German;Sexual Identity - Male homosexuality;%.

\item The percentage of hate speech related words is 1.2514.

\item Considering that the variable \textbf{Age - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 107/180 occurences of hate speech related comments.\end{itemize}\end{document}