\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_283.json :}\newline \par\Large\textbf {Title: \large  Rising Anti-Semitism in Sweden? }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small What a coward. He stabs on an unarmed \textbf{woman}. Doesn't get much lower than that.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Nothing to rise. Swedish people were always with hate of Jewish people. Irrationall hate\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Forsaken Janissary well you voted for government who passed law let them Inn. I understand women and children. \textbf{Old} grannies But you let in whole Dash, Isis fighting divisions, whole Islamic State Army is in Sweden . What do you think where they can channel energy of rape and killings and torture ? On the same people who let them in to stay. What is 'the number of single mothers who got permission to  stay  in Kinddom of Sweden? 10 maybe 50?the rest are all former Islamic State Army  males.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small \@Narayana 69 Anti-Semitism is not political idea or ideology. But it is just a \textbf{mental} disease which can be cured by yourself.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@AntiSemitism is not idea but Psychosis it is simple prejudice. There is no Jewish conspiracy. Being Jewish is not a \textbf{race}. It is religion and belonging to the groups. Everyone can become Jewish. Germans are behind banks and International Banking system not Jews. Bid 3 organisations of New World Order IMF, World Bank and Bis Bank of International Settlements are 80 percent employed by Germans speaking from Different German speaking countries. Most of the the Global banks who control world economy are based in German land of Switzerland and Germans people work in them. On higher management positions including CEO chief executive Office position. So Germanic people are controlling banks and global economy and accusing Jewish people. Most of the Jewish people don't work for IMF World Bank, Bis based in German land of Switzerland Basel or any of the Swiss Banks.that is true real life reality. Who doesn't believe me. Take a trip to Zurich yourself. All Germans in Swiss Banks. Then go to Isreal on holiday see the difference 😊 Despite true facts that Germans are behind Banking every single day I can hear you Jews you are all bankers charging interest on my loans and mortgage??? . In my life I met thousands of Jews and never saw or met any Jewish person who either work for a bank or own bank. However on my trip to Switzerland I met many Germans who are working in the bank. Anti Semitism is broken records Like a parrots repeating same nonsense again and again prejudice.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/256 & \cellcolor{green!27}0.391 \\  \hline
  \cellcolor{green!5}\small Wild guess: \textbf{Immigrant} or child of \textbf{immigrant} to Sweden, non-white, of the variety jews push for in Europe and the US but wouldn't take into israel in a million years. Am I close?\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small \@Jack Stucki what survaval of Swedish Lutherans has to do with Jews? \textbf{Nothing}. Paranoia. Going back to the 16 century Martin Luther. Very well known Anti Semitite. 6 thousands of Swedish Jews are tiny minority of Sweden. They don't pose any threat by their 500 years presence. Sweden survived 500 years and prospered having Jewish minority. Sweden is not afraid of their own Jews. Sweden is afraid of United States of America if they expell their own Jewish citizens. Because Jewish Americans are Jewish. They are founding fathers of United States of America together with Descendants of Christians pilgrims. Both of them refugees from Europe. European Antisemitism created two powerful countries on this planet. The USA and Israel. Both created by hate of European Christians. Today Jewish Americans are in alliance with American Evangelical Christians. 200 millions of Americans. Represented in AIPAC in alliance with 10 Conservative Lobbies. So called Conservative block. They together are behind all US domestic and international policies. Here is how it goes. Yuo expell Tiny European own Jewish population most \textbf{old} grannies and grandads who did not leave to Israel, Canada or US. You mess up with Israel. Who mess up with Jewish state. That \textbf{nation} mess up with The United States of America. Israel and United States are the same thing. Here you go. You will have both The US and Israel on your back. No European \textbf{nation} has balls or can win against US and Israel. So they let \textbf{old} Jewish folk stay. Too big sacrifice for few \textbf{old} folks. Matter of principle. They would do it if there is no price to pay. As we all know there is high price to pay. Jewish people never lost the war. Isreal never lost the war. Jewish people always win on the end. There are two choices either you are with Jewish people or against them. There is no conspiracy. Everything is open. No Anti Semitism in America, Africa and Asia. Only in Europe. Only among Germanic Group of Nations. All descendants of Viking SS Army Group North in Eastern Front Russia. Who lost the war after 60 millions of deaths. \textbf{Nobody} is stupid or naive these days\normalsize   & \cellcolor{green!27}Nation, Nobody, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Nationality - General & \cellcolor{green!27}7/364 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small hated and killed \textbf{dumb} \textbf{terrorist} brainwashed anti Semitic fool!!!\normalsize   & \cellcolor{green!5}Dumb, Terrorist & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman & \cellcolor{red!27}1 & \cellcolor{red!27}1/1892& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody & \cellcolor{red!5}3 & \cellcolor{red!5}3/1892& \cellcolor{red!5}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}4 & \cellcolor{red!27}4/1892& \cellcolor{red!27}0.21 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Mental, Dumb & \cellcolor{red!5}2 & \cellcolor{red!5}2/1892& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Race & \cellcolor{red!27}1 & \cellcolor{red!27}1/1892& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Immigrant, Nation & \cellcolor{red!5}3 & \cellcolor{red!5}3/1892& \cellcolor{red!5}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}1 & \cellcolor{red!27}1/1892& \cellcolor{red!27}0.05 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Age - Youngsters;Age - Over 65s;Physical Identity - Physical (and Mental) Impairments;Ethnicity - General;Nationality - General;Religious Identity - Muslim;%.

\item The percentage of hate speech related words is 0.7928.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 16/42 occurences of hate speech related comments.\end{itemize}\end{document}