\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_86.json :}\newline \par\Large\textbf {Title: \large  Polyandry Is Running Wild }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small A married \textbf{woman} looking for something else Is a \textbf{woman} that isnt getting the proper dicking.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I wasnt getting much \textbf{pussy} in my town, im short, guess that was getting in my way, moved to a tourist area in my country got a job at the beach and i fucked women from 22 countries in a very short time, one day i remember fucked 3 girls innthe time lapse of a day (first one canadian then scottish then english girl) but after some time i felt so empty , i felt i was losing my soul my kindess and i was a fucking pervert fucking all these women some married with kids some with bf (i once fucked a polish \textbf{woman} at the damn toilet room while his husbandnwas looking for her calling her name) and all this girls i had only a good conecction wih one, i fell in love with her moved together but thenni cheat on her and she left, i never been this sad in my life , i try to improve as a person so i moved back home got myself a job shitty but isnsomething, gonnq study a masters degree as well, but hope this fucking sadness just go away , i dont know how much damage i made to women and how much also they damaged me\normalsize   & \cellcolor{green!5}Woman, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/208 & \cellcolor{green!5}0.962 \\  \hline
  \cellcolor{green!27}\small Dude, you're actually thinking about taking the quick and easy way to get \textbf{pussy} by way of a married \textbf{woman}?? To lower yourself, your name, your reputation, your standards all for some vagina?? Cmon on bro! That's a poor choice! So basically you're talking and giving advice to us guys but you're willing to sleep with one of our wives??? Word? That's what you're really about? I mean, you're saying it to the online world so what are we to think? To all of you guys out there listen: Messing with married women is not an option! Like no, not never!!! Dont disgrace yourself over \textbf{pussy}. Cmon now guys,  if we are each other's keeper and if we are all we have then why would we disgrace, disrespect and devalue each other by dealing with another man's wife? We have to stop being slaves to our dicks!!!\normalsize   & \cellcolor{green!27}Woman, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}3/147 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small you are a nice guy with values and an empath that's why you aren't slaying. You feel ridicolous in acting alpha and spreading sexuality without shame. You don't want to cause pain that's why the only lays you get are from women who do all the work, because you still subconisciously act like a gentleman. You can't change your nature, lfaTHe ones who are slaying in this day and \textbf{age} are dark triad machiavellians narcissists\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small \@LFA you give off a sad broken vibe, not a vibe of one who's having regular \textbf{sex} with hot girls and is happy\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Clicked on this because I was curious about what the fuss was about Polyandry. This video isn't about polyandry but the objection of females with multiple \textbf{sexual} partners outside of marriage, not multiple marriage partners.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small I hate this \textbf{skinny} wrist , I hate the fact you have to facecam to get a job nowadays , I hate how superficial people are , I hate how much power money got on our lives , I hate this Game of Political Correctness and mastering it is the only way to progress thrhough our system. But you know what I LOVE LIFE AND WE HAVE TO BE STRONG , WHEN NO ONE ELSE WILL WE HAVE TO STRUGGLE WE HAVE TO KEEP GOING , IMPROVE OURSELVES , take up martial arts , workout hard , get gains , get knowledge be the OPPOSITE OF WHAT YOU HATE\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small "She'll be crawling on over to your place to give you some \textbf{pussy}"-LFA\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Is this guy finally getting it that there is no  "pick up" game.   There is only Looks and money.  The whole  "elevating yourself" never appliesto average  \textbf{dumb} asses.  If you become rich or famous it MIGHT help you.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Dropping \textbf{r\textbf{ed}} pills as useul brother, Focus on yourself borthers. Soon the west will collapse and with it The SMV of women.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Bet this guy sleeps with a different women every weekend but he thinks a \textbf{woman} shouldn't do the same. (She shouldn't but he shouldn't either) He's mad he can't find a good \textbf{woman} maybe its you! Seem like the type of person who is too into himself and thinks he's too good for everyone. ¯\ (ツ) /¯ Attractive face but a shit personality won't get you very far!!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/66 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small That married \textbf{pussy} can get you all fucked up, or killed. Single women are a pain in the ass. Go Monk for a year, Clear your head. Both of them.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Find an activity you like--for me it was outdoors activity--soon you will see a \textbf{woman} with interests and energy--seek her company after such an event.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small LFA you are right things are looking very bad for average men when it comes to any type of a relationship with a \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I'm 54 and i have four wives. They all pretend i'm faithfull . At 53 i had a baby girl to an 18 year old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small But there's single men and husbands that had/have \textbf{sex} with many women. I mean there's whole religions/culture that allows polygamy for centuries. Now that women have a choice as how many partners they want there's a problem?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small red pill is hard to swallow especially if you wash it down with butt sweat.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small I think some women get tired of meeting \textbf{nothing} but losers who just want to have \textbf{sex}. Which leads women to start thinking well what the hell is in it for me?  This guy wants the \textbf{pussy} but he isn't willing to pay any of my bills. When a \textbf{woman} brings up this fact she is quickly labeled a gold digger, because men want what they want at no cost to them. If our monthly bills together come out to \$5000+ and the man cannot afford to contribute \$2500 to those bills then he does not make enough money to be in that relationship. Now, you can split the cost with another man but would obviously have to share your girl. Also, many men cannot comfortably support their females on one income. Meaning if she loses her job you guys are screwed. more people equals more safety net. Maybe a man doesn't want children, but she does, this is a solution to this problem. she can have the children she wants and you dont have to have any. Maybe one guy is not handy around the house and another man is, maybe one is better in bed than the other, maybe the other is more emotionally supportive. Most men feel as if it is okay to exploit women for free \textbf{sex} but cry foul when women start imposing demands on men. I am all for monogamy if the man can satisfy me and makes enough money to support me and my son. When I say makes enough, he needs to make more than me so that if one of us for what ever reason becomes unemployed or can no longer work we dont lose everything. Dont be hypocrites guys! if you do a polyandry relationship and all the men are committed to just that \textbf{woman} and she just those men, it can work without having such a financial hardship to bare. I have not done a polyandry relationship but i am thinking about it and the potential benefits because i am tired of struggling and lousy \textbf{sex} and companionship  from men.\normalsize   & \cellcolor{green!5}Nothing, Sex, Woman, pussy & \cellcolor{green!5}Age - Youngsters, Gender - General, Nationality - Chinese & \cellcolor{green!5}7/351 & \cellcolor{green!5}1.994 \\  \hline
  \cellcolor{green!27}\small If this fucking guy has \textbf{woman} issues it's game over man. Civilisation is fucked.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small They just fucking dirty. Last night pulled a 28 year \textbf{old}. Sweet timid looking thing I thought. How wrong was I.  She tries insisting no condom, begging me to smash her ass bareback.  I smashed every hole but sheathed. Had drunk a few beers so took me three hours to blow my load (over her face).  At the end she mentions she's married.  The husband had a minor bike crash and was in the local hospital over night for observation.  Marriage ? Not a fucking chance !\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small Love drinking milk of wife not mother. Have wives not wife.polygamy no monogamy.monotheist not polytheist .love money don't worship.Allah,Muhammad, \textbf{sex},jihad,money,friends,sons,fashion,infrastructure, bass music,bike,American house,American shop.dog bless all sorry god bless all Md Sam salafist 6302931104 s.India guntur\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small This is if you want attractive women,if your down for \textbf{fat} ugly beat chicks you MIGHT have a chance for loyalty!👎🏼\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small It is one a idea from me. 80 20 rule = an alpha male can have 4 wives like in Islam. All the others have bad luck. I don't like the idea but i think it can have a connection. Today's society is similar to the islamic world and pre middle \textbf{age} or even pre roman europe.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Who's not depressed this days! LFA is a human and \textbf{nothing} wrong to be disappointed about these realities and fact!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small My girlfriend threw my heart on the ground, jumped up and down on it and kicked it around,.. I soon found out what she did it for because she's a lying cheating fucked up  whore. She told me she didn't love me anymore I just cried and fell to the floor, she walked right past me and headed to the door , then I realised I was living in a war. I knew there were problems that I didn't fuckin tackle but I didn't realise it would turn into a battle the normal kind of stuff that  every couple has. ..like don't touch her titties or her sexy \textbf{fat} ass. All of her girl friends are just as fuckin bad they think their so caring I think their fuckin mad, it doesn't make me angry only really fuckin sad..  they will never know all the love that we had. But now that she gone and I've got to carry on,  I'm trying to write me a real rap song ...so I will start with the words I heard a long time ago "every fuckin \textbf{woman} is a bitch and a \textbf{ho}" !\normalsize   & \cellcolor{green!27}Fat, Ho, Woman & \cellcolor{green!27}Gender - Female sexuality, Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}3/192 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small And just what is wrong with being Polly Amorous?If people want to love Polly Parrot: There is \textbf{nothing} wrong with that.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Modern \textbf{woman} today are conditioned to cheat/disrespect and are engrained into the hookup culture. Fucking scary... look at this guys SMV and even hes having trouble..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small things are getting real bad, my friend got cheated on when he was deployed. when he asked his girl why she cheated on him. she and her friends(who call themselves feminists) were like "\textbf{nothing} wrong in what she did, its not even cheating, a \textbf{woman} is a \textbf{sexual} being and she has the right to get her \textbf{sexual} needs satisfied by other men when her man is not around, did she ever cheat on you when you were around?" he said "that logic is retarded" they started calling him a \textbf{misogynist} and that he likes oppressing women.  he was baffled.\normalsize   & \cellcolor{green!5}Misogynist, Nothing, Sexual, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}5/100 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The last \textbf{woman} I dated tried to tell me white men were responsible for all the world's problems.  When I didn't agree, she went \textbf{bonkers}.  It was downhill from there.\normalsize   & \cellcolor{green!27}Bonkers, Woman & \cellcolor{green!27}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small LFA great video bro, tip for you do NOT DRINK BEER they pump it full of Estrogen \& Progesterone, so drink \textbf{r\textbf{ed}} or white wine bro, ALSO, Tinder is a horror show do not participate in the dehumanisation process. with best wishes, M\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small My mother opened my eyes even more than my horrific experiences .  While my father declines at 75 she at 65 is taking frequent holidays to Turkey with my married aunt and her widowed friend. That's his reward for sacrificing his potential and being a loyal husband from the \textbf{age} of 28.  The funny thing is being \textbf{r\textbf{ed}} pilled I'm not surprised nor do I fucking care. Even at 65+ they will run for a ride on the carousel when circumstance permits.\normalsize   & \cellcolor{green!27}Age, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - General, Ethnicity - Native-American & \cellcolor{green!27}3/82 & \cellcolor{green!27}3.659 \\  \hline
  \cellcolor{green!5}\small Go with the married women.  I've got three of them.  All their husbands know about me.  The thing is.....these women are never pains in the arse.  They never try to "move the relationship forward"  They want \textbf{nothing} but to come over here and fuck and hang out for a night now and then.  And that is all I want.  Every time I start something up with a single women they end up thinking they have a licence to take over my life.   I got one I've seen for nearly six years....another is coming up to eight years.......and one I've known for  a massive 18 years.  Never argue with them about anything........it's perfect.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small You need to consider leaving the \textbf{pussy} behind, despite your rational weighing of the options and your correct conclusion that a married \textbf{woman} is more available, you are still a slave and number to the vagina. To hell with all of them. Men built civilization, we never needed women.\normalsize   & \cellcolor{green!27}Woman, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small Any man that sleeps with a married \textbf{woman} is just a piece of shit it's about your own morals not about her or her husband it makes you a tool in another mans downfall\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small polyandry is the cover up to coquettes, hoe culture, \textbf{sexual} liberation, and this casual hookup culture, all these titles are guises for what has been around for centuries.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small I don't like online dating because i think its gross. The men have so many options. You are easily replaceable to them. They either want \textbf{sex} within first few dates or settle down. Its all too quick and if you don't then they forget you and replace you quickly. It is not organic. I prefer meeting people in real life and also communication to be real, ether a real voice over a call and hanging out in real life instead of texting only. Digital should be extra tool not main tool.Also many women want monogamy and are taught hard way that if they act like they want that men run for the hills. So then they read books and watch videos to learn how to get mogonomy and are taught to not focus on one man so that men will care about them because believe it or not men like \& reward women that don't think about only them. It is sad. What rock have you been hiding under?\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/170 & \cellcolor{green!5}0.588 \\  \hline
  \cellcolor{green!27}\small Misty Holley your argument is predicated on the idea that men are more likely to cheat than women, which is also statistically not the case, especially in later years.And the reason why women 'compromise' on looks is because women find most men unattractive  and I can also back that up with peer reviewed research. The fact is that we have twice as many female ancestors as male, most men never got laid and the few that did impregnated multiple women.It's happening on Tinder right now, the reason you're having bad luck on there is because you, as well as 78 of other women, are only trying to match with the top 20 of males in looks, wealth, or general bad boyness..I'm sure you're a good person, but you're a slave to your instincts and your \textbf{gender} is slowly but surely destroying the fabric of civilization. We created marriage to give every man an equal shot of getting laid, but feminism and divorce courts as well as the hookup culture and \textbf{sexual} promiscuity has destroyed socially enforced monogamy. And if you really wanted monogamy; you know what guys you actually need to be going after. But you and I both know that's not what you really want.\normalsize   & \cellcolor{green!27}Gender, Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/209 & \cellcolor{green!27}0.957 \\  \hline
  \cellcolor{green!5}\small fucked a 45 yo milf a couple years ago from pof without a condom, in between \textbf{sex} she told me she's fucking 2 other guys on the side. Sad!\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small This video and many articles seem to affirm that the 8+ males like LFA are fucking ALL of the attractive women (6+.) I'm a 6.5/10 guy and I can't get my looksmatch to save my life.  All these western broads think they're 1 or 2 points hotter than they actually are. It stinks that I work hard in the gym and count every damn calorie that goes in to my body only to end up with a \textbf{woman} that's at least 20 pounds overweight.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small Your video is keeping it 100 brother. A married \textbf{woman} is the better  choice because she don't want to ruin her marriage, or risk her husband finding out. Your right on the money when you say single women have 100 men on the side. Yeah, its a shitty deal BUT the best \textbf{sex} is with a female that is cheating on her husband. A female that wont cheat is a UNICORN. Mine did it,  I can talk about it to. Yep, been with my wife over 20 years and it happened to me to while I was out to sea in the military. Military wives are SHIT to by the way, they can not be trusted. Your right the Polyandry is not going away with all these feminist all over the place. Your another MGTOW and I'm glad to see it. Ill tell you what, my son will know the dangers of women, marriage. It will stop with him. The MGTOW movement keeps getting bigger  and bigger by the minute. I keep seeing guys like you making all these videos about MGTOW or \textbf{R\textbf{ED}} PILL man its everywhere now days. Wish knew this when  I was a young man, wouldn't be in this mess called marriage. Anyways, good video man, keep pumping them out and helping out men all over the world....\normalsize   & \cellcolor{green!5}Red, Sex, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}4/222 & \cellcolor{green!5}1.802 \\  \hline
  \cellcolor{green!27}\small Bangin' a married \textbf{chick} was some of the hottest \textbf{sex} I've ever had. However, I don't care to be one of those guys who gets killed by a pissed off husband. That said, BUTT SWEAT!!!\normalsize   & \cellcolor{green!27}Chick, Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small LFA is right about married women. In Collage, like it's \textbf{crazy} how these 30+ women wanna bang. It's obvious they are showing signs. Like i been getting better grades, one professors even came to me and whispered to my ear just come on the next exam, i'l let you pass. I've been able to do lots of shit and get away with it. I am guessing most of these women just wanna fuck someone younger who is up for it.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small ITS ICE COLD!!! But LFA is speaking \textbf{nothing} but the PURE TRUTH Brothers...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Maybe LFA realized like many of us that this dating, this tinder even this mgtow thing is depressing. Yesterday I watched for the maybe 30th time in my lifetime Rocky. I realized I want a \textbf{woman} like Adrian next to me. But nowadays there are no more goodhearted and loyal women out there. Like LFA always says, we all have to take a deep breath and accept the hard truth and do the best we can do for us.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small LFA you are absolutely correct! Becoming \textbf{r\textbf{ed}} pill aware and making yourself the main point of origin is a must! I learned at a young \textbf{age} the true nature of women in a gym setting, totally raw and primal if you pay attention. Men need to realize their strengths and advantages in your-self and use that and the knowledge of how women tic- tock. Working out and keeping your health and body in shape is a must! Women love it, they will instantly notice this and your confidence that you will project. Unfortunately for married men, you are point on about single women vs married in present day. Check out a long time \textbf{r\textbf{ed}} piller named Ronin Man, he has some incredible background and experience on the sociology of married women and the differences of relationship they will give to a boyfriend vs husband.\normalsize   & \cellcolor{green!27}Age, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - General, Ethnicity - Native-American & \cellcolor{green!27}5/144 & \cellcolor{green!27}3.472 \\  \hline
  \cellcolor{green!5}\small Things are not looking good for 80 of men minimum. If you make it as the top 20 it's only any good if you are comfortable with PUMP AND DUMP. Casual \textbf{sex} is meaningless once you get beyond the novelty (which happens very quickly) unfortunately this is as good as it gets, completely depressing because women haven't the loyalty to stick at things. I'm going monkmode because women are not worth the sacrifice, and having food and shelter is more important.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small It isn't insecure, but the opposite, to demand \textbf{sexual} fidelity the moment you meet a \textbf{woman}. Last night I had a knockout argument with my 21 year \textbf{old} girlfriend where I said it was suspicious she was seeing others and I have no interest in catching something. I added a paragraph or two about the wall happening at \textbf{age} 25.She was crying and begging me to believe she'd never cheat.All men should lay down the law like that, even if they call your bluff anyway.\normalsize   & \cellcolor{green!27}Age, Old, Sexual, Woman & \cellcolor{green!27}Age - General, Age - Over 65s, Gender - General & \cellcolor{green!27}4/87 & \cellcolor{green!27}4.598 \\  \hline
  \cellcolor{green!5}\small Even the ugliest thots at work have upwards of 800 to 1000 matches on tinder. They look like the back end of a bus \& have the personalities to match. They get good looking guys that's for sure, they sleep around like \textbf{crazy}. Meanwhile I know many guys who haven't had \textbf{sex} in years\normalsize   & \cellcolor{green!5}Crazy, Sex & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small If that's the case, then I choose to be out of the gene pool. I'm Monogamous; Sure, I'm pretty damn confident that every heterosexual Dude wants to have a threesome. Believe me; I've been there, want to now don't. I believe in Monogamy. However, He's right in this day and \textbf{age}. I can't call it out anymore. It is finally putting me at risk. I honestly believe I destroyed my Music career because of it. Brothers and Sisters, Polyamory is a disease. For us to truly evolve, this needs to be extinguished from our gene pool. Do you honestly believe Polyamory will benefit our survival? Imagine having no room in a confined space. Now, let's add flavor; you eat a full meal every two days. You get to hydrate every three days. You have to blend your water diet with your food. Death is necessary. If a Husband sees his Wife fucking another Man, Kill them Both. Their sacrifice will guarantee our survival. Our future children do not need this influential curruption.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/172 & \cellcolor{green!27}0.581 \\  \hline
  \cellcolor{green!5}\small Man why you doing that stupid faces and push jaw to the front making underbite? It makes you looks \textbf{disabled} in some way.\normalsize   & \cellcolor{green!5}Disabled & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Don't take this the wrong way, but you might need to get off the drinking man, it seems to be really getting to you. \textbf{Alcohol} damages you insidiously.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@LFA Ah, I see. The last couple of videos of you I saw, you were cracking some cans open too.\textbf{Alcohol} is just something that insidiously caught up to me at one point without realizing. No disrespect, love your content!\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@Tech CP Haha, I probably shouldn't have commented that, it was all with good intentions. I had trouble with \textbf{alcohol} myself and I perhaps projected that onto him, good on him if he can have that "one drink" and not need more. I'm not that person :)\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Man....jusst stay away from the all those diseased pussies out there bro...NOT worth the time, \$\$, \& effort for some beat up coochy!  These females have \textbf{nothing} else to offer.  SAD but TRUE.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Watch this online dating video by darius m, it's as funny as sh\@t.  [LINK]  Womens days are already numbered with the new \textbf{sex} robots coming out. The average man is further ahead investing in himself then chasing some stupid desire without results. If adultfriendfinder can't land you a lay, your better off dropping out of every dating site online. Even if you were to get successful with hookup, theirs always an chance of getting her pregnant, or an std. The average man can replace one of a woman's functions using bad dragon \textbf{sex} toy+ oculus rift+ vr porn from porntube, redtube, ect.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/102 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Beta Buxxing is not \textbf{sexual} attraction.Please no more tinder experiments. 90 of tinder are incels running 'experiments' at this point\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Actually I think polyandry and 80/20 rule go hand in hand.  When 80 of women are having \textbf{sex} with 20 of men, that's four women to one man.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small It polyandry means each \textbf{woman} has multiple men.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Things aren't lookin good for every "class" of female cause ever since the 90's and especially since the The Matrix came out everything's been exposed and i love how it's mostly females that are lookin for "the best deal" and "who to exploit", they're gettin desperate fellas, be safe out there.What does that quote go like? A society that prioritizes \textbf{sex} above everything else will not survive.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Men need to stop basing their value, validation and success on women. It's not your \textbf{woman} it's just your turn. Remember that. MGTOW is freedom.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Guys, regarding to all women, Learn from Islam. [LINK] You don't have to become a Muslim or anything. Simply embrace those methods, After that, western \textbf{woman} will not dream or dare to do mess you guys because they know what awaits them. [LINK] Simply watch the videos and share them all over.Peace.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small LFA I get you. Just pointing out how dire and immoral the \textbf{gender} situation is. It is a shame.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small This is such a sad view on life. Firstly that there's only two types of girls and that both of those types cheat. Not true at all, not all girls want to have a million bfs, most just want one that will care for and love them. You choose to fuck a married \textbf{woman} because you're insecure about how you compare to the guys who are going for the single one. You go for the easy and disrespectful option, wow how alpha for you to fuck a married \textbf{woman}. If you honestly believe in your current view on women, I have to tell you it's not the women that are the problem it's your taste in women. You attract poly girls because you're poly yourself. You fuck a lot of girls and they see you as just that.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/138 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Thanks for the input. But all you did was deflected the subject with assumptions and name calling. Saying I'm not alpha isn't going to change the fact that one in every four women that show interest me me happen to be married and looking for something new. And calling me insecure isn't going to make me more interested in a \textbf{chick} that's sleeping with multiple guys.\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Thy only puts me on the alphafux side of things. Meaning women want me for \textbf{sex} but not relationship.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small LFA I never looked at it that way, I thought dudes like you just had an easy life and \textbf{nothing} to worry about. For me I'm giving up, packed a bag with all my stuff and about to fly to Eastern Europe permanantly. American women have \textbf{mental} problems :  My whole family is dead, and I guess I'm hoping a women can fill the empty voids in my life : (((\normalsize   & \cellcolor{green!5}Mental, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Social media, feminism and dating apps has made it absolutely impossible for the average Joe to be "enough". Sure he might find that special \textbf{woman}, but in her mind, he'll never match up to the Chads and Tyrones in her DM's\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small What is your deal?Why are you not having a dozen \textbf{woman} begging for your attention? Stop the search for her and look for your legacy. Unless your legacy is to find "the right \textbf{woman}".\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small my ex girlfriend wanted a break so i gave \textbf{thot} a break next thing i know we where broken up for 2 weeks and she cheated on me on the break i found out later cause i jailbreak her phone so she instigated the breakup to sleep with these dude who pissed her off afterwoods and she came crawling back this has become the norm because of tinder and the 100 guy's that mesage this so called average girls mind you i slept with her best friend afterwoods while she is less attractive than her i wanted to get some payback lol...\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/102 & \cellcolor{green!27}0.98 \\  \hline
  \cellcolor{green!5}\small A \textbf{nigga}...what ever gets the job done. It aint the best bear but its better than no beer. 🤷\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Stay away from \textbf{Pussy}.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Welcome to the internet \textbf{age}...women have reduced themselves to a commodity in all the wrong ways. A \textbf{sex} object of the highest sort. Ohh well...Here we are..record low marriage rate, birth rate and record low numbers even having \textbf{sex} anymore..all facts. We've burnt ourselves out I suppose. Thanks ladies!\normalsize   & \cellcolor{green!5}Age, Sex & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Truth, things aren't good for average men. My question is, have they ever been? The first image that comes to mind is the Baby Boomer generation: WWII vets coming home and banging their girls like a screen door in a hurricane. After their .mil service, you see (the idealized version) of men in slacks, button down shirts, shined shoes, just to go get a burger; Women in dresses, sons and daughters dressed like miniature copies of their parents. Those guys (and gals) would be above average by today's standards, say, 6.5-7+ based on physique and dress. LFA, I'd say you're above average from most American men in your \textbf{age} range (25-35). If things aren't going good for you on a hookup app like Tinder, then yeah, things are fucking really bad for average dudes. But again, have average men ever had a decent chance of acquiring a female mate? Or has it always been that women only accept the top 20 of men, leaving the bottom 80 to wither off and die, taking their "inferior" genes with them. Looks, Money, Status. LFA, you got the looks, idk your financials, or social status, but you've got confidence and attitude, along with the masculine physical characteristics that women recognize and are attracted to subconsciously. So again, if YOU are struggling with online dating/hooking up, the rest of us pleebs are doomed.Thanks for the straight talk and no apologies. Great content.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/239 & \cellcolor{green!27}0.418 \\  \hline
  \cellcolor{green!5}\small im in europe looking like van damme, have a plain picture on dating apps...\textbf{ZERO} matches. i tried writing \textbf{old} sluts. none interested. LOL\normalsize   & \cellcolor{green!5}Old, Zero & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small LFA let me tell you, you are a strong 7 out of 10. Maybe even an 8 out of 10. Women care about looks the most. After that I would say that status is extremely important. Money is just currency. Plenty of rich thirsty simps out there, begging for \textbf{pussy}. But you won't see a goodlooking asshole begging for \textbf{pussy}.You are 6'1" - so your height is almost perfect.You are built well and do look good. You are slightly \textbf{old} but that's definitely not that much of a big deal as a man. You have \textbf{R\textbf{ed}} Pill \textbf{Black} Pill knowledge, Charisma and kind of an asshole vibe.\normalsize   & \cellcolor{green!27}Black, Old, Red, pussy & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese & \cellcolor{green!27}6/109 & \cellcolor{green!27}5.505 \\  \hline
  \cellcolor{green!5}\small You forgot to mention..prostitution..but it the same as a \textbf{woman} who demands you take her out and spend money...same shit different day\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Although I appreciate the logic of your argument about going for the married \textbf{woman} being the better option, by doing so you are only contributing to part of the break down in the system. Do what you want to do, but be careful of the hypocrisy of preaching against the failing of modern western marriage while doing your part to destroy it, or at least not honor it. I like your videos and you seem like a good enough guy that I'd hang out with and share a 6 pack with. I just want to drop that note for consideration. Somehow I also think you are better than all that.. you don't seem like someone who seek out that. Not really.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small Pursue a foreign \textbf{chick} American bitches dirty\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Just be a wolf in sheep's clothing. Go \textbf{beta male} provider then pump and dump\normalsize   & \cellcolor{green!27}Beta male & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Just curious man, down deep at the bottom of your heart, would you like to be loved by a loyal \textbf{woman} If you Just happen to found a girl that isnt interested in money nor status and would be 100percent loyal? Im courious\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Is ANY \textbf{woman} worth your home, belongings, money, pension, and sanity?  I think not.  My advice to my fellow men out there--don't get married! Don't shack up with a \textbf{woman}.  They're in it to take your shit.  The vast majority of them are riding the carousel anyway.  We're just not aware of it.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small The second i find out a \textbf{woman} is married, I cross her off the list..I will not help these sluts cheat.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Most guys don't know what they're doing in bed (that's what their wives tell me), and most guys won't know their wife \textbf{woman} is sleeping with another dude.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Most incels want love and appreciation more that \textbf{sex}. Incels exist because they have no social confidence, they have no social confidence because they can not confide in their ability to meet their long term pre-socio-\textbf{sexual} survival needs(safety, food, water, shelter), and they are not able to meet those survival needs because they are paying the taxes for all of the poor \textbf{sexual} choices of average degenerate \textbf{woman} and bad boys. By removing this unfair burden from incels and placing it rightfully back on the shoulders of those legitinately privileged individuals who create such societal liabilities, it would allow incels to quickly become confident and attractive men that can find love, which is a good thing because as more and more men identify as incels and are unable to find love, they will certainly find hate. Then they become suicidal, homicidal, and eventually macro-political genocidal.Show me a man who takes by force what he wants from women and I'll show you 10 women who vote to take by force what they want from men. Show me a grave created by \textbf{patriarchy} and Ill show you an entire graveyard created by feminism/communism."Any society that negates the role of the father in the voluntarily marriage contract from decent civilization buliding men and replaces it with a involuntary centralized welfare state will not remain civilized for long."I didn't go looking for war, war came looking for me. I didn't go looking for \textbf{nationalism}, \textbf{nationalism} came looking for me. I didn't go looking for \textbf{racism}, \textbf{racism} came looking for me. The solution to \textbf{racism} is \textbf{patriarchy}. Moat of people killing each, both inter and intra \textbf{race}, is men competing for resources status to gain access to women. Jordan Peterson has a 10 minute or so video out their called "Does poverty chase crime? no. the gini coefficient explained" where he describes the most duplicateable law in the social sciences (the gini coefficient):  as economic inequality increases in a given geographic area, the male on male homicide rate will increase exponentially. The reason why is because as economic inequality increases women mostly flock to the top men. The solution to the gini coefficient dilemma? Jordan Peterson says its forced monogamy. That's how you balance unity with diversity so that society doesn't rip itself apart....Whites shooting up mosks in new Zealand? Would he have done it if he was married and loved and appreciated? Blacks killing each other in Chicago? Would they be doing that if they would have been married with loving wives in their lives?\textbf{SEX} SHOULD ONLY BE WITHIN MARRIAGE. IF YOU BELIEVE THAT HUMAN LIFE HAS NEGLECT-TRANSENDING VALUE THAT YOUR COMMUNITY IS OBLIGATED TO PROTECT AND SUPPORT, THEN BEFORE COUPLES HAVE \textbf{SEX} THEY NEED THE CONSENT \& COSIGNERS OF THE CHURCH \& VILLAGE(PARENTS, EXTENDED FAMILY, BEST MEN AND BRIDESMAIDS) TO ENSURE THE MAN AND \textbf{WOMAN} POTENTIALLY PROCREATING HUMAN LIFE POSES THE QUALITIES AND QUANTITIES NECESSARY TO GIVE THE CHILD(REN) THE ECONOMIC OPPORTUNITES NEEDED TO HAVE A FAIR CHANCE AT A GOOD LIFE AND THE ETHOS NEEDED TO ACHIEVE IT WHILE BEING FAIR TO OTHERS IN THE COMMUNITY.("IF THERE IS ANYONE HERE TODAY WHO FEELS THIS MAN AND \textbf{WOMAN} SHOULD NOT COME TOGETHER(( HAVE \textbf{SEX} AND POTENTIALLY MAKE BABIES)) TODAY, LET THEM SPEAK NOW OR FOREVER HOLD THEIR PEACE.") THIS WAY, IF THERE IS A NEED FOR A WELFARE NET TO HELP THE COUPLE AND/OR CHILD, COERCED  TAXATION IS NOT NECESSARY-THE SOCIAL NETWORK NEEDED TO FUFILL THIS ROLE HAS ALREADY BEEN PUT IN  PLACE THROUGH INTERPERSONAL CONSENT.AND THATS HOW YOU BALANCE-LOVE WITH FREEDOMMICRO WITH MACROUNITY WITH DIVERSITY-Marriage\normalsize   & \cellcolor{green!5}Nationalism, Patriarchy, Race, Racism, Sex, Sexual, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General, Nationality - General & \cellcolor{green!5}14/603 & \cellcolor{green!5}2.322 \\  \hline
  \cellcolor{green!27}\small LFA: Is it only "\textbf{pussy}" you want or do you want genuine connection with a faithful \textbf{woman}?\normalsize   & \cellcolor{green!27}Woman, pussy & \cellcolor{green!27}Gender - General, Nationality - Chinese & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small The 3rd type of women on tinder are \textbf{fat} lonely slobs\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small My cousin brought his wife from the Philippines. She had \textbf{nothing} when she came over. Not a resident, no job, no career, no hope. She soon began to see what other women around here are doing and I didn't take long before she got pregnant by some other dude. She took half of my cousins finances, kid has child support and she lives with the other dude. The Western culture got to her and now she feels like a queen and like her coochie is a gold vagina. I tried telling him that once these chicks see the culture, they want in. That's why I stay single. I'm not rolling dices on these hoes.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/114 & \cellcolor{green!27}0.877 \\  \hline
  \cellcolor{green!5}\small You're extremely stupid if you think you're not gonna compete for a married women. A.) unless she explicitly states that she has a husband she is going have orbiters. or B.) she's a hot \textbf{woman} and she still has the pick of the litter. The amount of hamstering in the video is ridiculous\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Your opinion of me is hilarious. But that's your imagination and it really has \textbf{nothing} to do with me. Thanks for the input though. Stay creative.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Or option 3 is a very poor \textbf{woman} who lives in a 3 world country like the Philippines but your going to have to move there if you get married.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I agree with some of what you say, but it's not like this everywhere. I'm married to a Chinese \textbf{woman} and is awesome. She doesn't go out without me often. She treats me as an important and valued member of the family. This is \textbf{common} with Asian women. She values me as an important component of our family. This makes a huge difference. Women and men want different things from family. Western women don't understand what family real is. They don't understand the purpose of living. They're living a lie. There are cultures that are not like this. That being said, Western men need to remember how to be men. The big issue is with the law society and the courts. They are using the family courts to bring back open slavery. Kill the judges and lawyers when they use the public trust to stall your property. This will then end right quick!\normalsize   & \cellcolor{green!27}Common, Woman & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/153 & \cellcolor{green!27}1.307 \\  \hline
  \cellcolor{green!5}\small the beer looked liked it didn't taste good...I've also been hunting for a good \textbf{woman}, I think it's how you carry yourself and your values morals etc... I know but know who I am with the help of lfa and the bitches out here... I'm content.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small LFA I have two questions I would love to hear your response on: Firstly, do you have a philosophy as to why is it that women are so obsessed/in love at the beginning of a relationship?Secondly in my experience it is a necessity for a \textbf{woman} to engage/marry/get-pregnant for power, so at what point do they know they have you by the nuts? I've not heard you cover this before so I'd be interested to know. I am 20y/o so I need all the experienced knowledge I can absorb!Also - Awesome videos!\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small I wouldn't risk my life messing with a married \textbf{woman}. As far as you know, her husband is following her and waiting. Then boom! Bullet to your head. No thanks.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small We have to look after ourselves because \textbf{nobody} else will.And I will NEVER touch a married \textbf{woman}. That shit is WRONG! Have some standards guys. It's a horrible thing to do to another man..... even if he doesn't know.DO THE RIGHT THING IN LIFE AND DO NOT BE SO OBSESSED WITH GETTING LAID\normalsize   & \cellcolor{green!27}Nobody, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}2/55 & \cellcolor{green!27}3.636 \\  \hline
  \cellcolor{green!5}\small If you're simply trying to sleep with a \textbf{woman}, what difference does it make if you're competing with 1 man or 100 men. Sounds like you're looking for a relationship.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small The best option is going foreign for a \textbf{woman} outside the Western Hemisphere,these women in the west are all just about done over here the average \textbf{woman} is \textbf{nothing} more than a man with a vagina!!!!\normalsize   & \cellcolor{green!27}Nothing, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small How can you be sure if you want to hook up with a wife you're only competing with her husband? Where does the confidence for that come from? In my opinion it is already breach of trust anyway - do not be the other guy, and she is just a \textbf{ho} in case she's looking for it, too, so not worth it. Seems like being married today (at least it seems for her) means \textbf{nothing} in terms of restraints, but I don't know about the guys and perceived male behavior. Theoretically speaking you just might be her Nth hookup that day.\normalsize   & \cellcolor{green!5}Ho, Nothing & \cellcolor{green!5}Age - Youngsters, Gender - Female sexuality & \cellcolor{green!5}2/101 & \cellcolor{green!5}1.98 \\  \hline
  \cellcolor{green!27}\small Men shouldnt think about \textbf{pussy} at all, its a primitive thought and not logical and to be honest fucking bitches aint worth shit if you can just bust a nut in 2 minutes on your own and save time, money, and headache from some hoe (which 95 of them are FACTS), its better to stack money because we live on a economic planet. fucking bitches and reproducing is mad work!!! only some guys can have a good life and get it all\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small Polyaundry is alright as long as everyone agrees, and when women are scarce in society... But in reality, it's not polyaundry when the \textbf{woman} is doing it on the DL... The unfortunate part is that it always back fire on women when they the wall. \textbf{Pussy} is power, but only for a limited Time... And don't want to understand this, but they need to...\normalsize   & \cellcolor{green!5}Woman, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/64 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Everything is subjective. And opinions. Theres plenty of factors to put in.  And id have to post a vid to break everything down. But life is not \textbf{black} and white. Sometimes Ppl can switch, depending on the person. In against cucking and all that.  But i have been in circumstances where i had a 10, and her \textbf{sex}  drive was too much.  So i was considering the cucking.  At the end of the day what men desire most is companionship. It takes time to get there,  different men at different ages figure that out.\normalsize   & \cellcolor{green!27}Black, Sex & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/94 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small As a man who was cheated on by my wife and she had his baby, I can't in good conscience chase married women. I have \textbf{zero} luck on dating apps and day game is over as I have gotten a bit older. As a guy approaching 40, I have basically submitted to travelling to Thailand for vacation and getting it all out of my system. I have grown to hate the western world, western women too so I will just remain a monk and work towards financial liberation.\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small I don't like to be tapping a \textbf{pussy} full of another man's sperm.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Come on now, stop being a drama queen. Straight men and women necessarily have the same amount of \textbf{sex} partners ON AVERAGE (assuming that the population is comprised of 50 men and 50 women). Some people just have more \textbf{sex} partners than others - and because of the 80/20 rule, alpha males are still the ones with the most \textbf{sex} partners.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/61 & \cellcolor{green!5}4.918 \\  \hline
  \cellcolor{green!27}\small I know what you mean, 2 out 3 women are \textbf{obese} these days and the ones that aren't have 100 boyfriend's.\normalsize   & \cellcolor{green!27}Obese & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small brent s DON'T DO IT ! As long as she breathes she's a \textbf{THOT}. ALWAYS REMEMBER NEVER FORGET ! 😠\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Weak guy who cannot get a \textbf{woman}! Still you can always find company on YT with the guys who took their sister to the prom.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Marriage is good for men that have NO income. Its like applying for gov't assistance. A \textbf{race} to the bottom. Dude you don't have to spend squat. If they like you, they got money, don't be a simp.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small you're doing something you know is morally wrong just because you can't live without \textbf{pussy}? you should sit and think about that\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small God dose not make lonley \textbf{woman} .Brother just ride roll that power on\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small You can't stop it,it's a self perpetuating mechanism,it creates more and more weak men that chase women even more. There is \textbf{nothing} you can do.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small It is rough out there in the \textbf{sexual} marketplace for men. I experimented with tinder too about 2 years ago. Stopped it after a year. The problem is the quality of women when it comes to family values and relationships is very low in the western world. Women put themselves and career first over a monogamous relationship with a man. They are very solipsistic creatures. The issue is women have had so much dick they literally lose their ability to pair bond with one man. Women 18-35 have so many options, it makes it difficult being a guy.  Jumping through various hoops and obstacles often makes the juice not worth the squeeze. I could never knowingly have \textbf{sex} with a married \textbf{woman} as I find it immoral. However I am also disgusted with the ethical behavior of most single women. It's a conundrum. I understand where you're coming from. I think the best bet if you're a man in the west looking for \textbf{sexual} intimacy  (not just pump and dump) is to seek a younger girl in her late teens to early 20s who has had little to no \textbf{sexual} experience yet since they have not been damaged by promiscuity. The problem is even women that young who haven't had more than 2-3 \textbf{sexual} partners is rare. Often girls in high school have already had plenty of \textbf{sex} so by the time she is a legal adult she is already damaged.  For a man who has ethics looking for a young \textbf{woman} who hasn't slept around is the best bet. They tend to have a much better value system. The problem is they are rare. They do exist however. The other issue is even these women can get corrupted by feminist dogma as they get older. There really isn't an answer on how to handle this terrible situation. My only advice as a man is to stay true to yourself and have self respect. If you do something you know you'll regret the next day don't do it.\normalsize   & \cellcolor{green!5}Sex, Sexual, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}8/338 & \cellcolor{green!5}2.367 \\  \hline
  \cellcolor{green!27}\small Did things ever looked good for the average men?It's sad.\textbf{Nobody} should dislike LFA videos, even with buttsweat.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Women Hit The Wall At 30....( \textbf{R\textbf{ED}} PILL )  [LINK] \normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small butt sweat...... \textbf{alcohol} is death.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Discovered \textbf{r\textbf{ed}} pill when my ex bpd gf cheated on me and fucked me mentally. Always have been going my own way, but I was fooled by that \textbf{woman}. Still recovering from that shit show, tho I'm getting back on track and embracing masculinity. Just wanna say thanks for these videos. Bless\normalsize   & \cellcolor{green!5}Red, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small Dislike here LFA. what is wrong with you man ?  You afraid because a single chic has many beta cucks who are competing for her ?  it´s not the way of HONOR to have \textbf{sex} with a \textbf{woman} who is married. and this shows  how fucked up many married women are. No HONOR, No LOYALTY.LESS REAL MEN = LESS REAL WOMEN = BAD AND BROKEN SOCIETY.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small Amen on the single \textbf{woman} thing\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Rather be one of the guys on the side - nailed it man. I was thinking that as you said it. Same again with the married \textbf{woman}. That's her husbands problem if he can't deliver. You don't have to live up to the standards expected of a husband. You can lie and make all the claims you like about your income and status. You never have to deliver on that. You just have to get hard on demand. All the fun and none of the pain. You deliver a fantasy. It's all fake.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small Forget Tinder dude, be a real man, go out by yourself and slay lots of \textbf{pussy}. There are two types of men in the world. Men of Action, and all others.. Drive fast, eat ass.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Thank you brothers for being here.I have dated many women. One thing I have learned as a older man is many many women are now on antidepressants they have no guilt no shame... these women are very strong and emotionally numbed. Many are  beautiful, successful and hot looking. \textbf{Sex} with many men is no problem and empowering to them.  Men be aware,  check those medicine cabinets nightstands maybe a purse  if you can. Yes it is sneaky but so are they, we have to be our own private investigator. These medicated women will mess you up and destroy you.Meanwhile they act like innocent angels.  Google: relationships destroyed by SSRI antidepressants.  Be aware this is a sign of the times.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/121 & \cellcolor{green!27}0.826 \\  \hline
  \cellcolor{green!5}\small If you're going to spend money to get laid then just buy a \textbf{hooker}. They are no worse than the average \textbf{woman} on tinder.\normalsize   & \cellcolor{green!5}Hooker, Woman & \cellcolor{green!5}Gender - Female sexuality, Gender - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small your a high 7 but for your \textbf{age} higher than that . s o pretty good for slaying\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Yesterday I stepped into the home of my buddy in Prison as we got possession back from his stripper baby momma who had not paid any rent on it in two years and she was the one who got him into this mess. Sadly the house was basically destroyed, kitchen cabinets all torn off, trash, holes in the walls, ceilings down. I walked into this mess with the mother of my buddy who is in her 70's....this is a christian lady but yesterday she looked me in the eye and said "I hate this girl with all my heart"!  A man who lays down with a Devil of a \textbf{Woman} will get his head chewed off one way or the other. Thank you for warning Men of the dangers of the Feminist Mindset................men are givers and women are takers:Reality!!   I hope men read this post and take warning. Timmy C. the forever bachelor.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/153 & \cellcolor{green!5}0.654 \\  \hline
  \cellcolor{green!27}\small My dream is a society with \textbf{sex} work decriminalized , indioendent women, end of \textbf{patriarchy} and poliandry.\normalsize   & \cellcolor{green!27}Patriarchy, Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small LFA: One idea: Convert to Islam and marry a muslim \textbf{woman}. No nonsense. Muslims really know how to keep their women at bay.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small 10 boyfriend competing for one women, what will happen? She will get self estime, she will say she deserve everything, she will try to take the best of each one of you, take momey fro each of you sellinf here \textbf{pussy} she doesnt cure she already a hoe. After she will date all of you, she will still looking outside to find the richest man she can get. That facts.Real man should protect his man strength. They best way is to go hard on here\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small Fuck that. I'm no Chad but I have access to 7 figures of cash. I have resources. Say I'm average looking. I had a \textbf{woman} reject me because I'm 5'10", same height as her in heels. No problem though going on expensive dates with me though. Took her out in a 90K newer lexus. I have 4 cars. I went in for a kiss and she told me she wants a guy taller. Not even such a hot \textbf{chick}. Who would want to have \textbf{sex} with those women, You are pretty much assured an STD. Eating her out is like licking off a mens toilet in a highway reststop.\normalsize   & \cellcolor{green!5}Chick, Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/109 & \cellcolor{green!5}2.752 \\  \hline
  \cellcolor{green!27}\small Great use of logic and \textbf{common} sense...\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Interesting video LFA, well at least you're doing better than ugly incels like me, but then again I wouldn't waste my time on Tinder or any on line dating site, as they are only good for women, and the top 20 of men, in terms of looks.The current hook up culture that dominates our society means that the dating game is totally rigged in favour of women. Even fat/or ugly women have more dating/hook up options than a Chad. In a recent Catfish experiment, two people (both from Toronto, Canada) ie. an ugly 2/10 looking \textbf{woman}, and a 8/10 good looking Chad, had their profiles put on Tinder to see how many messages they received in a week. In one week, the ugly 2/10 looking \textbf{woman} received 392 messages from interested men, whereas the Chad only got 44 messages from interested women.And when you factor in rampant female hypergamy, the 20/80 rule, the dating game  for average, and God forbid below average looking men is look very bleak indeed.LFA, given the draconian anti-male divorce courts you have there in the USA, I would advise you NOT to get married if I were you, just pump and dump women, it will work out cheaper than being married.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/209 & \cellcolor{green!5}0.957 \\  \hline
  \cellcolor{green!27}\small How about a video on forced celibacy and people/family thinking the guy is \textbf{g\textbf{ay}}. Meanwhile the guy just doesn't have any luck with women...LOL\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Married?!I can't believe you said that out loud.  No more \textbf{alcohol} for you.  That shit is killing your brain cells. Please refrain from getting drunk on camera  (at least with your clothes on ). You don't look like your normally handsome self.  2 thumbs down. Public drunkenness is unflattering to your image.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Hey I just want to let you know that your perspective seems to come from an American Reality. I live in Canada and I surround myself with women who have values and I don't date because I focus on my hobbies. But if I go to another town where my family lives I notice people have different lifestyles and values. And the \textbf{woman} that you want is not online. She's probably done university and works somewhere that she loves and doesnt have much time to date.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small who is to say that you re not competing with the ''100 other guys''  to become the mistress of a married \textbf{woman} as well?\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small John Hawkes That could be true. But I would think it is unlikely. If a \textbf{woman} is married, children, works outside the home, inside the home and such, she may not have time to hold auditions. She just wants her side penis that she can rely on.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@LeTHALxHeaDBanG  I can understand I was just like you. But after many experiences I realized its safest thing you can do. As far as HIV is concerned it's mostly disease of \textbf{g\textbf{ay}} ppl. Some hookers have even shown me their medical reports and were absolutely clean\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@LeTHALxHeaDBanG obviously you wear a condom, and there hasn't ever really been a case of a man catching HIV from a \textbf{woman}.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small LeTHALxHeaDBanG lol at being a cop, here in the u.k it's legal for women to sell \textbf{sex} online.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small If reality is tough for LFA, what are the chances for an average chump for having an healthy dating life in 2019?Spoiler: \textbf{Zero}.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Stop looking to fill the emptiness of your existence with a \textbf{woman}. Seek out Jesus Christ. He is all you will ever need. You can't ever trust a \textbf{woman}, you can trust Him. He created you, he knew you before you were born. Make Him the center of your life and stop worshipping women.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small LFA your stupid! The only reason you come up with these BULLSHIT philosophies is because your looking in the wrong places for the right \textbf{woman}. smh...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small It dont matter if they are married, if they looking for a side peice, they have many side peices on the back burner waiting. Soy boys these days, comment beautiful, sexy, n other compliments to a photo of a \textbf{woman} on fake book all the time waiting to break off a peice of that pie. I'm not being eskimo brothers with no one. F that!\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Of course. This is the reality we live in today. Meeting a new \textbf{woman} won't change reality.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I was just talking about this yesterday in regards to another Mgtow content creator. He seems like he could still be pulled in  to a relationship if he found a \textbf{woman} who isn't skanky and was good to him and I don't think that would change his channel's content because one decent \textbf{woman} won't change his past of all the horrible women he's had and the reality that there's millions of bad ones for every good one. Most men are not going to find a decent \textbf{woman} IMO.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/88 & \cellcolor{green!5}3.409 \\  \hline
  \cellcolor{green!27}\small Being \textbf{R\textbf{ed}} Pill has its good points and bad points.Good point: You look at things for what they are. You come to understand that not all things end well in life. Because of this, you are more aware, realistic, and cautious. You have a sense of freedom because you don't have to deal with these women trying to take undo advantage of you. Your eyes are opened, and you focus on self-improvement instead of trying to please a \textbf{woman}.Bad point: It can cause you to be become chronically depressed- if left unchecked.\normalsize   & \cellcolor{green!27}Red, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!27}3/94 & \cellcolor{green!27}3.191 \\  \hline
  \cellcolor{green!5}\small I prefer a sativa \textbf{b\textbf{rownie}} during the day.  Can go to the gym on cannabis not \textbf{alcohol}.\normalsize   & \cellcolor{green!5}Brownie, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - Asian (South- India, Pakistan, Bangladesh), Nationality - Hispanic & \cellcolor{green!5}3/17 & \cellcolor{green!5}17.647 \\  \hline
  \cellcolor{green!27}\small That pill is hard to swallow my brother. Let us look to new horizons and \textbf{sex} bots.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Nobody chooses what era he is born in its all destiny and luck , for us , its a pretty damn shitty era , i mean for human relationships , it went down the drain since 1960 , hope that in the future it will be rectified but at this rate i'm not sure, people who can abandon relationships can live well because only themseleves matter.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Does women want to be monogamous?? They want men to be monogamous and they want them to believe women are monogamous. So men focus their attention in one women while women explore their options!!!They want to be the primal \textbf{sexual} selectors and expand their options while reducing men's options!!They simply want full control over their hypergamy\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small DJYC21215 men only cheat after finding out female behavior??  Men cheat when they find another \textbf{woman} physically attractive as well dude\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Y'know, you keep saying you don't want to compete with 100 other men, and ask "what makes you stand out?" when liking a girl on Tinder. You also say that no one wants to talk to people in the real world anymore. The solution here is obviously cold approaching. Not in some PUA way, just saying "Hi" and introducing yourself to women you find attractive and getting their number/snapchat/whatever.Who gives a fuck if you're giving away free validation? You're not telling her she's beautiful, you're simply going up to a \textbf{woman} as a man, showing interest and putting yourself out there, like a man. Seriously, cold approaching is a damn cheat code. I've approached maybe 30 women the past 3 weeks and gotten 10-15 numbers/snapchats. It's more than the average fellow is going to get, I know that, but it shows that it's possible.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/145 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}\small I fuck em all and never take em anywhere... If tou just want \textbf{pussy}, who gives a fuck... I have the 'i dont give a fuck' street personality and these bitches cant get enough..\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small If it wasn't for the protection of the walls of civilization then the modern liberal man would die off. The strong and violent alpha males would be the only choice for women Both on the left and the right side of politics today. Women are in no need of the fit and able, well built males of present. Although they will gladly slake such lust with those goodlooking men while she is in her prime, jumping from one to the next... But more often than not the goodlooking male is usually living pretty basic in comparison to the smarter successful and often, less physically appealing guys. If the "chad" is not living Well into his 20s or early 30s with his family or a shared accommodation, then he is most likely sofa surfing between friends or bed hopping between his latest gf and side piece. \textbf{Sex} is a mans drive for everything he chases... Its the reason men want nice cars, big houses, over priced clothes and extravagant holidays ect. Men who get the avarage to slightly above or below females on a regular basis dont have the drive that the "nerds" or "geeks" have because the more "chad" like men are simply not as thirsty as the less attractive males are. But everything that we use and what has made our lives easy as they are today was because some smart geeky guy invented it just so he get some arsse on the back end.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/246 & \cellcolor{green!27}0.407 \\  \hline
  \cellcolor{green!5}\small Polyandry = polygamy in which a \textbf{woman} has more than one husband.Actually, women have the GOVERNMENT as their main husband and don't want or need men for anything more than a quick f~ck. I look at those used-up Thots with miles of cock run through them and I won't touch their \textbf{pussy} with a 10-foot pole. I want \textbf{nothing} to do with them.\normalsize   & \cellcolor{green!5}Nothing, Woman, pussy & \cellcolor{green!5}Age - Youngsters, Gender - General, Nationality - Chinese & \cellcolor{green!5}3/64 & \cellcolor{green!5}4.688 \\  \hline
  \cellcolor{green!27}\small Lolz I just like it when he says pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Definitely living in a time of uncharted territory for men. We need \textbf{sex} but we desire roots, stability, and family connections. When these seem out of reach we can get discouraged. Takes a lot of courage to push ahead.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Patriarchy = Polygamy/polygynyDegeneracy = fornication and adultery\normalsize   & \cellcolor{green!27}Patriarchy & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Patriarchy has siblings polyamory has half siblings\normalsize   & \cellcolor{green!5}Patriarchy & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Patriarchy = is polyamory\normalsize   & \cellcolor{green!27}Patriarchy & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@T I Women want to be the other \textbf{woman} or secretly wants another \textbf{woman} involved,  she just want you to do it the correct way without her telling you...it turns them on as long as she doesn't feel disrespected or left out\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I'm right there with you, bruh.  I'm 35, 6'0 and 220lbs (former beta) and what you'd consider a "Tyrone" and females today have no shame. They've been brainwashed by 3rd wave feminism and it's slowly decaying society.I'm on bumble and tinder, to kinda fuck around but semi serious and there are \textbf{nothing} but \textbf{fat} chicks, single moms and swingers, all of which are entitled AF.  I booted the last two since they all start ghosting and are obviously fucking around with other dudes and but im no orbiter.  But that pattern and behavior is almost \textbf{common} place for them, not realizing the damage they're doing.To answer your question, I think the better odds are to just pump and dump the milfs, since they're over the bullshit games.  We need to never be the guys waiting in the wings, hoping she'll come around.  Fuck validation and kissing their asses, they all take it for granted.  We all need to stop being simps because that's the only reason how they got so much power over us.LFA, if you're ever in southern california, hit me up, we'll grab some real beer😂👍\normalsize   & \cellcolor{green!27}Common, Fat, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!27}3/191 & \cellcolor{green!27}1.571 \\  \hline
  \cellcolor{green!5}\small Well I think your just the bees knees for being there for these women and facilitate their need to cheat on their husbands... I've never been married cause I'm smart enough not to.. but I'm sure you wouldn't hesitate to fuck a guys girlfriend.. your a scum bag if you think that identifies as masculine or male. I've been a sub for almost 5 months, women are whores but if you could care less about your fellow man and what happens to him, then I hope you end up feeling a bit of the pain you helped cause... scum bag no integrity half man here. Unsubscribed. No honor or integrity from some presumed 'alpha male' sipping coors light faggot\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/119 & \cellcolor{green!5}0.84 \\  \hline
  \cellcolor{green!27}\small Regular \textbf{alcohol} makes u pessimistic af avoid it bruh it will only make your views on life worse\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Well, how many guys are complicit  in the chuckledry. They claim to care about men but then go out knowingly screwing a \textbf{woman} who he knows has a man. The reality is yes, people don't want to go out but that's why you going out makes you stand out. Men today have as ridiculously high expectations as the women because a lot want want champagne p/women on cheap beer money. ...... i want submission..... a dime...... cooks....... clean...... suck..... f**. ..... be logical..... be loyal..... go 50:50.........but i don't pay for dates or an willing to pay the cost for a halfway decent \textbf{woman}.  You can't negotiate desire, a \textbf{woman} likes what she likes and it's emotional just as much as it's logical. A husband who can't give his wife a good \textbf{mental} and physical f** is in part why she's looking for some good d elsewhere (it's not justified but it's sadly part of it).\normalsize   & \cellcolor{green!5}Mental, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/156 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small You sound disappointed man. It is what it is. \textbf{Sexual} relationships are just a trade - you give me some of what I want, I'll give you some of what you want. And if we're lucky we'll care about each other as well... so long as the conditions of the contract remain satisfied.Our culture idealizes fairy tale love which builds in us a hunger for that type of thing... for that special someone to be close to... and the disappointment when it's not satisfied... but it's not realistic. It's quite funny - I actually realised about a year ago that the ideas of love I had in my 20s... were mostly picked up as a little kid from watching the soap operas my mother watched. Didn't even know it, until the connection hit me. You'd be surprised how much of it's just cultural programming.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/145 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}\small I had \textbf{sex} with a girl just to find out about a tattoo on her arm...searched on her Facebook, found him and saw he had healthy issues. Something in me died after that, or once I had \textbf{sex} with a girl and I found out she had cancer or the other time I found out a girl's father died just a week ago. I feel like a piece of shit and want to kill myself.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small I once saw my \textbf{old} chemistry teacher.it was savage.to bad she didnt swipe right though.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I recently got into banging \textbf{fat} chicks!They dont give a fuck!It's great!They just want it and totally happy to get it and high five see ya in a couple weeks it's great!!\textbf{Fat} chicks 2020!!\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Odds are in the favor for hot girls though.  Except that they suffer from pathological hypergamy and the 100's of guys simping on them 24/7 makes it too difficult to for them to decide, which inevitably results in the release of oxytocin for numerous \textbf{sexual} partners that permanently inhibits pair bonding.  A \textbf{fat} person at an all you can eat buffet will also sample everything because they cannot help themselves.\normalsize   & \cellcolor{green!27}Fat, Sexual & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/70 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small dont magnetise to the label i to have always been \textbf{r\textbf{ed}} pill and mgtow minded its not a new movement its just a label given to a thing where boys and simp men are educated by other men there is a way out be a bachelor i beat the uk government and never paid child support i do not will not have debt i will never get married ..i always beat the tax man the child support agency's the local councils never paid UK TV licence fee and have been found not guilty every single time in court I WAS ONCER ACCUSED OF CHILD BATTERY AND ABUSE imagine that.. i was found not guilty obviously...iv seen it all  from \textbf{woman} my last one went insane and wrote letters tyo death row in mates I AINT KIDDING  MY FIRDT ONE SPANISH 3 KIDS WITH HER gambling pathalogical addict 1/2 a miliuon uk pounds in slot machines   THERE ALL LIKE THAT FEMALE NATURE\normalsize   & \cellcolor{green!5}Red, Woman & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!5}3/161 & \cellcolor{green!5}1.863 \\  \hline
  \cellcolor{green!27}\small I've literally had EVERY \textbf{WOMAN} i've been romantically involved long term with all do the same shit as soon as they got comfortable. Turn into lazy bums. No matter how ambitious she may have been. These women want a "good man" for one reason only fellas. So they can kick their feet up.  Unfortunately for them, i dip as SOON as i notice that fuckery, and my drive for any typ of commitment has vanished. They do it to themselves.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small If you wanna be married today you have 2 otpions - 1.let your \textbf{woman} fuck multiple guys2. lock her into a cage\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Yeah... im 6'1" 250 pounds and somewhat lean. I have a score of an 8 on my face (100 women scored me)... i make decent money where i live (\$65,000) and am very confident, outgoing and been told my sense of humor is my greatest quality.... all that said i feel im an 8.5/10 overall and i still have been fucked over by \textbf{woman} that are 6-7 range. All women think they are 1-2 points higher though..\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small That just makes the \textbf{r\textbf{ed}} pill even more easy to swallow\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small \@zerximus I'm past the rage and sad phase of the \textbf{r\textbf{ed}} pill luckily, with occasional anxiety regarding relationships or lack thereof.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small \@Bill Hicks I concur. I don't think there is a perfect mgtow and a lot of guys who've taken the \textbf{r\textbf{ed}} pill , including myself put up a front as if it's a happy occasion to take the \textbf{r\textbf{ed}} pill, as if we're actually happy we're in this situation.  I've said this to myself and I'll say it here, mgtow is not a good thing whatsoever, it is only merely a consequence of feminism, social media, and the actions of modern day women. Let's face it, for all the men who put on a front , even the ones who say they're monk, if a girl you really , truly believed was for you, they'd jump at the opportunity in a heartbeat and throw all this mgtow stuff away BUT the sad reality is, this is the route men need to take to preserve what we have left, our money, dignity and our sanity. It's sad that it's really come to this and I don't see it getting much better any time soon. Good luck to you all and godspeed.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/180 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small I have an idea,when \textbf{patriarchy} is secured,when a man marries a \textbf{woman},the man must block a womans eye to other men,thus disabling her hypergamy and become a loyal housewife.Might not work probably\normalsize   & \cellcolor{green!27}Patriarchy, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small \@ReckMods I don't agree with him.  Fidelity and mate guarding go both ways.  Of course a married \textbf{woman} should ignore and not entertain other men, but men need to hold themselves accountable too.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small There are still monogamous classy women out there but they are really hard to come by. First thing you notice is that she doesnt "sexualize" her pictures. No cake make up and \textbf{hooker} clothing. Shes also independent. And does not seek attention. You land a \textbf{woman} like that she will fuck cook and clean for you..but i doubt you will find those traits in american women. They are usually found in small towns and cities not that developt. The real bonus is that she doesnt even realize how hot she looks lols. Ive met women like this that i still regret for fucking it up, i was a massive douche back then. If i even find one again i will still keep my guard. But i will try to keep her this time.\normalsize   & \cellcolor{green!27}Hooker, Woman & \cellcolor{green!27}Gender - Female sexuality, Gender - General & \cellcolor{green!27}2/133 & \cellcolor{green!27}1.504 \\  \hline
  \cellcolor{green!5}\small You think she's going to the gym and trying to look good for you ??  BAHAHAHA.  And yes she DOES like anal , she just doesn't have to, you married her \textbf{dumb} ass\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Her \textbf{mental} problems will be your 1 competitor bro ....\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Don't go for married \textbf{woman}. Don't be one of those sorry ass motherfuckers. Have some honor and dignity. Not because of her, but because of YOU. Don't teach those thots that they can cheat on their husbands. I will tell you what is the best deal for an 'average man'. The best deal is to focus on yourself, improve, change in any aspect of life that you feel you should improve. And WAIT. The best option will find you. Don't chase it! Because \textbf{sex} with a 'chased girl' is no way near as good as it is with the \textbf{woman} that chases you. Have you ever seen girls chasing hispanic summer lover Alejandro or another football player Brad? Well, you will never be like that, because you would already expirence that. The only option for you in this case is to spare your own honor and fuck those games. Keep mindset that you don't need any \textbf{woman}. That's the only way you can keep dignity in this puppet show.\normalsize   & \cellcolor{green!5}Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}4/169 & \cellcolor{green!5}2.367 \\  \hline
  \cellcolor{green!27}\small A \textbf{woman} marries the highest-income man she can get. That decision is completely unrelated to what man she actually wants to fuck. Women don't "do" loyalty. It's just not in their nature.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Maybe stop fucking women? Men don't need \textbf{sex}. It's all bs and you all are brainwashed by marketing. \textbf{Sex} is a drug and you have taken the bait. If you treat your girl like a drug dealer, guess what, just like a drug dealer she'll sell her stuff to the highest bidder. All this hypergamy shit is nonsense. Men are acting like \textbf{pussy} junkies and they're getting exactly they are asking for. If you want a good life stop fucking your girl and start getting to know her. I'm sure I'll get a lot hate for speaking this. But the truth is the truthKeep going down this path and pain and misery will follow.Even animals only mate at certain times. They don't hump 7 days a week like people are doing. It's a sickness and drug addiction and it's extremely BETA because it's weak\normalsize   & \cellcolor{green!5}Sex, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}3/146 & \cellcolor{green!5}2.055 \\  \hline
  \cellcolor{green!27}\small AmenJust to come clean the gal I commented about a few videos ago, that I met when giving blood in the \textbf{R\textbf{ed}} Cross blood drive bus, is married. Husband is older and believes losing the desire and not being able to perform \textbf{sex} as nature taking taking its course. She disagrees. She is an avid tennis player that frequents her sons gym to play n practice. Happens to be my gym and I just happen to live less than five minutes away.Wine Bars are really popular these days and are loaded with married women. Married women are like shooting fish in a barrel. Everything LFA says in this video is spot on.\normalsize   & \cellcolor{green!27}Red, Sex & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Gender - General & \cellcolor{green!27}3/113 & \cellcolor{green!27}2.655 \\  \hline
  \cellcolor{green!5}\small Stay \textbf{R\textbf{ed}} Pill\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/3 & \cellcolor{green!5}66.667 \\  \hline
  \cellcolor{green!27}\small It's for men who want some pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Fuck that. I'm no Chad but I have access to 7 figures of cash. I have resources. Say I'm average looking. I had a \textbf{woman} reject me because I'm 5'10", same height as her in heels. No problem though going on expensive dates with me though. Took her out in a 90K newer lexus. I have 4 cars. I went in for a kiss and she told me she wants a guy taller. Not even such a hot \textbf{chick}. Who would want to have \textbf{sex} with those women, You are pretty much assured an STD. Eating her out or even kissing is like licking off a mens toilet in a highway reststop. I am desperate at this point, I'm older, but I have to keep some standards.\normalsize   & \cellcolor{green!5}Chick, Sex, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/127 & \cellcolor{green!5}2.362 \\  \hline
  \cellcolor{green!27}\small \@Pradeep Thanks, I agree. Like I said, I can't say I'm a male model but probably a bit above average. Beyond that I can offer much, aside from the money I can cook, fix things, spend money wisely etc. This \textbf{woman} had 4 layer paint job on her face. Only thing is she was much younger than me, but people thought in the restaurant she was my wife :lol:. Why does she have to go with me when there are endless guys on Tinder she can pick from. At her \textbf{age} (29)her looks are starting to sunset and unlike men older women have very little to offer because they can't have kids.  Women really waste all their best years on shit today. I don't even blame them.The media pollutes them with fiction. \textbf{Sex} and the City, Feminism, other shit that just doesn't work in the real world. Women could never be men. In the end their SMV is tied to fertility and the ability to reproduce. That is why the average \textbf{age} of marriage used to be 21-22 for a \textbf{woman}. No technology was able to extend that.\normalsize   & \cellcolor{green!27}Age, Sex, Woman & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}5/188 & \cellcolor{green!27}2.66 \\  \hline
  \cellcolor{green!5}\small \@Brian Ross They have millions of choices a swipe away. How would you feel if you had unlimited women contacting you?  Couple that with no shame that existed even 20 years ago. It is a dumpster fire. She is still kinda young so I guess she feels she has smash value for another few years. Meanwhile at 29 people thought she is my wife, she don't even look that great. I'm 47.  With makeup though she looks ok. Looks like she had a car paintjob on her face. Primer base and clear :lol:. Wonder what she is hiding.With every \textbf{sexual} partner, a womans value drops. It is like a carfax, every owner is a downgrade. If men stopped accepting it though the problem would quickly end. What I see now is elite top 85 of men who smash women until they are used out, then they look for some beta with average looks and money. That aftermarket has to stop. It never existed in past times. My mom told me that after 25 (MAYBE 30) a \textbf{woman} became completely unmarriagable. Well, maybe for some 60yo widow. There was no cock carousel. It couldn't happen because women had reputations (if they fucked around in HS no guy would ever date them, maybe just fuck them) and they married young. Free \textbf{sex} reverts us back to the animal kingdom.\normalsize   & \cellcolor{green!5}Sex, Sexual, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}3/228 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small \@alb12345672 I couldn't agree more. Its really men who can force the change. We have to stop accepting bad behavior from women. If a \textbf{woman} fucks around too much...don't date her. At most bang her and move on. If she has a kid from another man..especially outside of a marriage...fucking next her ass. If men were to up their standards...a lot of this bullshit would go away. But it requires us to stop being slaves to our dick.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small \@alb12345672 Brother, I would recommend emigrating to another country (check out Southeast Asia) if you really want a good \textbf{woman}. You won't be able to find them in the West.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@joshspiker Unfortunately, I believe you are correct. Hate to uproot my lifestyle, but American women are trainwrecks anyway. I kinda saw it in the 90s but I denied it to myself. It is MUCH MUCH worse now.  The liberal climate, no shame for women, etc, etc,It started as a bad \textbf{common} cold, now it is Rabies, which is pretty much hopeless.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Taking a \textbf{woman} you don't even know yet to  'an expensive dinner'?    Why? lol    Listen to yourself - broadcasting \$\$\$,  newer lexus (how \textbf{old} are you that you're driving a 'lexus' and not a luxury sportscar), 4 cars, etc., etc.   My guess is that's all you were talking about.\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Never make a family with a western \textbf{woman} ...\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Western culture used to have family values. What has changed is women entering the work force in droves, universal suffrage, abortion and contraception (which gives women full control without any responsibility), and affirmative action and welfare programs that support women at the expense of men. This has led to an amoral society in the west where women can have \textbf{sex} with multiple men without consequence, and government programs and \textbf{gender} quotas which put women in a protected class where they no longer need men. The issue is since it's men who are the net taxpayers of society this imbalance can't continue forever as debts accrue and there is only so much of a man's money government can take. Western culture is a cesspool but it didn't always used to be that way. Once upon a time the west did have family values.\normalsize   & \cellcolor{green!5}Gender, Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/142 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small \@Gaza Gxrl /x Yes women working enmasse and taking contraceptives has changed the ballgame. From a logical perspective really think about it. What happens when the workforce doubles? It decreases wages by half and increases competition. This is simple economics. Men and women now compete against one another and women are taking on more masculine traits. Now due to this both men and women must work as wages compared to inflation have dropped dramatically. This means children become latchkey kids raised by state daycare and public institutions as both parents are working. Before the great society a person could support a whole family on one income.What happens when women are taking contraception? It means she can have \textbf{sex} with as many partners as she wants without worrying about the consequences. This increases promiscuity in women. You only have to look at the data to know this. This is just reality.As for being possessive, it's part of the male dominance instinct which society has been trying to stamp out (so called "toxic masculinity" and anti male sentiment like metoo). If men were taught to embrace their masculinity instead of being taught as boys that we are damaged girls who need to be \textbf{effeminate}, the Western world would be much better off and the family unit would still be at the forefront. There is \textbf{nothing} wrong with a man feeling possessive about the \textbf{woman} he wants to spend the rest of his life with. It's part of the protect and provide instinct that our socialist government tells boys and men that these natural inclinations are bad and evil.\normalsize   & \cellcolor{green!27}Effeminate, Nothing, Sex, Woman & \cellcolor{green!27}Age - Youngsters, Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/268 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small \@Gaza Gxrl /x Entirely true? Do you know the difference between Macro, Micro and anecdotal? It's not about extinction of the human \textbf{race}. It's about being replaced by immigrants outside the culture like what's happening in Europe with the Muslims. To have a sustainable population you need approximately 2.1 children per household and all of the West are under this. What this means is the native culture is being replaced. Both Quantity and quality are maintained through strong family units which is lacking in the west. You're like speaking to a child. Women of the west are far dumber than ever, solipsistic, and hedonistic. Indoctrination does not equal intelligence. Having 40 percent of women being single moms is not wise. Women having children when they are past the \textbf{age} of 30, many past the \textbf{age} of 35 with increased health risks for the child including down syndrome and other diseases isn't wise. Women initiating 70-80 percent of divorce without regard to their children isn't wise. Women putting career over husband and children isn't wise nor is it good for society. Anyone who thinks that way is a moron. Unfortunately people like yourself are \textbf{common} and representative of the mob. You're far from wise.\normalsize   & \cellcolor{green!5}Age, Common, Race & \cellcolor{green!5}Age - General, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}4/203 & \cellcolor{green!5}1.97 \\  \hline
  \cellcolor{green!27}\small \@Ben Sisko Thanks Ben. I've listened to TFM before but I don't follow him. I actually don't want to take women's rights away as you put it but there are harsh realities and part of being \textbf{r\textbf{ed}} pilled is seeking the truth regardless of how ugly it is. When you see women acting so irresponsibly when left to their own devices in regards to what's happening in the West a man must face observable reality. I mean now a \textbf{woman} can murder her baby outside the womb after it's born in New York and its now legal. Regardless of what you believe about abortion that is flat out murder. The supposedly more nurturing \textbf{sex} condones this as a group without batting an eyelash. Things like this will spread to other states as they always do. As degeneracy continues, women will become the figure heads and main supporters of these unethical behaviors. Women are unaccountable for their actions and the Western world promotes it. Females  unilaterally have shown their irresponsibility as they are continually given more authority and power by the state.I would say taking away women's unearned privileges is what is required if the west is to thrive.  Quite frankly though many men have become \textbf{effeminate} themselves and are also a big part of the problem. They support their own destruction and are the gatekeepers. While the solutions are simple, It's  the complexity of it's implementation and sheer numbers of the opposition that will inevitably be our downfall if \textbf{nothing} is done.\normalsize   & \cellcolor{green!27}Effeminate, Nothing, Red, Sex, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American, Gender - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}6/253 & \cellcolor{green!27}2.372 \\  \hline
  \cellcolor{green!5}\small \@M Rod Yes, indeed. And especially now that populations are so fractured it would be even more difficult to bring people together and unite under a \textbf{common} banner. We have been successfully atomized, it's a true shame. We all deserve better.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@brent s so heres my thinking: theres less \textbf{fat} in it so you can make it colder because \textbf{fat} insulates things from the cold. Is this sound logic? Nope. I'm brain damaged from half a life of heavy drinking. And on that note goodnight. I woke up to it being bedtime though so... kind of disorienting I think I'm still tired but I'm not.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@material pattern psilocibyns should totally be legalised..here's a thought..how is it, a magic mushroom that wont kill or harm you is illegal to pick and consume, yet a deadly mushroom, like gallerina for example, is perfectly legal to pick...go figure, eh? Smdh...im cutting down my beer and \textbf{alcohol} drinking, which will be hard as fuck, due to a potential health issue for fucksakes... Atleast here in Canada, pot is legal..👍\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Red pill is hard to swallow because you need to let your conditioned idea of love die forever if you would like to refrain from being destroyed.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small It used to be a curse as a young man banging hundreds of women and Not once having a heart for any of them. After nutting I'd immediately get grossed out about them. As I got into my 40s however it's been a blessing. I kept all my money and as my \textbf{sex} drive slows down a bit I get to enjoy swimming and bbq and no shitty women. And believe me, as a man ages - if you stay in shape and don't put out ,keep clean you will still get \textbf{pussy} at Least every three days.\normalsize   & \cellcolor{green!5}Sex, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/98 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small \@Jake Glad to see a man in his 40s doing great and living a happy life! I see all these slobs in their 40s lazy and complaining. It was great hearing this from you! Hope the rest of your life is twice as awesome! Enjoy from a 20 year \textbf{old} \textbf{r\textbf{ed}} pill man!\normalsize   & \cellcolor{green!27}Old, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}3/53 & \cellcolor{green!27}5.66 \\  \hline
  \cellcolor{green!5}\small Love exists but it's conditional and u only taste it if u have looks, money and status. That's female's nature they will never love u for who u are but for what u can do for them and they will deny it every time but it is absolutely true. So there are two choices either go mgtow or maximize  ur \textbf{sexual}  market value and slay  \textbf{pussy} and if u come across a unicorn marry her\normalsize   & \cellcolor{green!5}Sexual, pussy & \cellcolor{green!5}Gender - General, Nationality - Chinese & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small \@karim dhamer that's not love. That is infatuation. In 4 years she will leave. No matter how perfect you are. You not only fight hypergamy, you are also fighting her boredom. You will never ever satisfy a \textbf{woman} That's why the Bible says, *'\textbf{Woman} was made for man, and not the man for the \textbf{woman}.'*. Find value in your manhood, masculinity and your authenticity, build character, and purpose. These three you should desire more than the female curve.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small \@the LOGICian - theBeofox the truth is there is a shallow side to every person so love is based on ur \textbf{sexual} market value. It's all statistics 😂\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@karim dhamer yes, this is all true if you're a rational, but the same applies to how us rational men 'love' women. The worst thing is that I also know that the aesthetics of a \textbf{woman} will be smashed by the wall as its evolutions way of directing my reproductive efforts to other fertile women.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small \@karim dhamer If love is just based on looks, status and money then it's really not love at all. Sometimes I think the trailer park guy with his big \textbf{fat} toothless wife is better off. Atleast he found true love. There is something to be said for those who are not superficial.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small There's a difference between \textbf{r\textbf{ed}} pill and nihilism.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Bernardo Aaron Pina he's 51 years \textbf{old} bro... he's passed boasting. And he's right. There's enough girls out there looking for something fast because she's bored and wants so drama in her life. Girls high 5 each other and brag about their slutiness, trust me.... I know for a fact. I've seen them laugh and smile at each other while talking about their slutiness.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small YES they do!! Most of these girls can be down right aggressive! Im 5'6 125lb but in very good shape. I still do my Aikido/Kali morning workout I did in JR high. Girls BS detectors are pretty good, they can smell Fear or Confidence in a guy. I can take care of my self and don't give a sh!t about much and girls "feel" that.    Im at an \textbf{age} where my parents passed away within the past year and now friends are going. I went to see an \textbf{old} friend now that im back living in Illinois that is a math professor at 1 of the 3 top collages here to talk about a friend/workmate that passed. He had to stay for late classes and I had offers for lunch "dates" before I could get down the hall !!     DONT GIVE UP ON YOURSELF !!!!    Give it a try, the worst is the say no !!\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/156 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small The two kinds of 'women' I match with on tinder (I swipe right on everyone for a few min here and there - I got shit to do) are 1. \textbf{fat} and or ugly women...and 2. dudes pretending to be women.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Allergic to beer and \textbf{alcohol}, but this Bud" is 4 u.. Oh, Amen to not being the extra peeder in her pants!!! Or the spare tires for my Balls... damn gold digging bimbos..  \textbf{nobody} does it for love, they do it for money, first..\normalsize   & \cellcolor{green!27}Nobody, alcohol & \cellcolor{green!27}Age - Youngsters, Behavioural Addiction - Alcohol & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Definitely married women are the better lay. On a side note: I dated a \textbf{blind} girl once, but got dumped for a guy with a better voice! You have to have a tough skin nowadays. Men need a sense of humor about it because women are a joke!\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small upstart1234ify I've never been married but what the fuck is wrong with you people?! Why do you wanna fuck someone's wife? I'd put a bullet in your fucking head and live happily ever after In jail for doing so... scumbags in our day and \textbf{age}.. I slaughter \textbf{pussy} but never where another man has his heart. And if you call me a \textbf{pussy} your lying to yourself\normalsize   & \cellcolor{green!27}Age, pussy & \cellcolor{green!27}Age - General, Nationality - Chinese & \cellcolor{green!27}3/67 & \cellcolor{green!27}4.478 \\  \hline
  \cellcolor{green!5}\small maddtoker420 I wouldn't do it either. The risk of you getting killed are way too high, and it's just not worth it for the \textbf{pussy}.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Between a single \textbf{woman} with lots of guys after her and a married \textbf{woman} that only has one man, I'll stay with the \textbf{sex} doll: She's one-time cost, she will stay with me for the rest of my life, she will give me \textbf{sex} anytime I want, SHE WILL NEVER FUCKING COMPLAIN ABOUT ANYTHING, she won't play shit test games, she will never try to manipulate me, she'll never lie to me, she will never make me her emotional slave, she'll never make me her slave at all, she will never demand anything from me, and, again, she's one-time cost.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}4/100 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Thot Slayer couldn't have put it better myself\normalsize   & \cellcolor{green!5}THOT & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small If you're dating around then it's best you don't show them your actual social media anyway. Keep your actual ones for family and close friends. And make fake profiles for memes/stupid videos/random BS. But dont show each \textbf{chick} the same profile. Sure, women date around and have no problem with it. But they expect the man to only date them..\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small Alcohol makes you ugly and washed up. I'll stick to my water.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Side Kick you can, it's just makes you ugly. \textbf{Alcohol} has that effect.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Esharido i don't do drugs but Drink \textbf{alcohol}, find the error my friend. You are going to defend your habit and that's fine, i also enjoy the drug \textbf{alcohol}. If you want to be smart use Google "list of most dangerous drugs".\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The point is that it makes averages women bump up at least 2 points when you have some \textbf{alcohol} in your system.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small At this point you tell them straight up, I only want to be fwb \textbf{nothing} more \textbf{nothing} less. No dates till fucking a couple times.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Just dont take your \textbf{r\textbf{ed}} pills with a cold beer ;). In a literal way of course.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small He spends his days trying to get over that \textbf{r\textbf{ed}} brick wall !! Sometimes he gets half way sometimes he just sits next to it and talks to his phone\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Selling \textbf{r\textbf{ed}} pills and \textbf{r\textbf{ed}} pill accessories\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/7 & \cellcolor{green!27}57.143 \\  \hline
  \cellcolor{green!5}\small The last girl I had \textbf{sex} with gave me genital warts and herpes. Now my warts have blisters\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Just because the single girl is going out with 100 guys doesn't mean she is fucking all of em.  My personal experience and observation, women enjoy attention above all.  So 80/20 still applies.  Only 20 of the 100 will actually get the \textbf{pussy}.  The rest of the 80 will just be hopeful they can get something but never will.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Depression probably is derivitive of unflipped switches in the brain. If your \textbf{black} pilled and researching the causal forces behind weemin overrunning society with feminism and cheap entertainment at the cost of sanity, men's general health mentally, and children's future, you have weemin, not women, and only doing the real heavy research into ancient elites will lift your cognitive dissonance and neurosis.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small LFA , I'd like to know your opinion on men who have \textbf{sex} only with hookers cuz they aren't successful with women  and never been in any relationship\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Indian law system approved this last year.Marriage, Relationship even making little communication with women seems USELESS now.\textbf{Indian} men are getting to know about MGTOW \& Redpill more \& more everyday.Coz we know THIS IS THE END.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Satyajit Halder it's gonna get worse for \textbf{indian} men than western men. \textbf{Indian} women will use the past/present of the rapes etc and how they were late to the feminism thing to get 'revenge justice' and come for \textbf{indian} men harder than western women went for their men. Protect yourself, learn \textbf{r\textbf{ed}} pill, you guys didn't need it until now but at least the experimentation stages of \textbf{r\textbf{ed}} pill is over- devote yourself to it\normalsize   & \cellcolor{green!27}Indian, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}7/75 & \cellcolor{green!27}9.333 \\  \hline
  \cellcolor{green!5}\small \@Based Poseidon Rape is a false aligation by western media to brand Indians in a wrong way. Statistical data proves that there are more rapes in Western \textbf{nation} compared to population.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small \@Pradeep but \textbf{nobody} cares about statistics dude the reality is the media already brainwashed everybody with all those rape articles in india from \textbf{indian} men, the media rules not statistics.\normalsize   & \cellcolor{green!27}Indian, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Pradeep yeah considering there's shit everywhere, \textbf{racism} is rampant, and people are being murdered over their diet in India, I highly disagree with you that white people rape more!\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Do men really even want a wife and kids in the first place? I always thought having access to unlimited \textbf{pussy} was a good thing. Just bust and move on, don't fall into the relationship trap. The only people who will suffer in the end are women once they become \textbf{old} and infertile with no one to take care of them.\normalsize   & \cellcolor{green!27}Old, pussy & \cellcolor{green!27}Age - Over 65s, Nationality - Chinese & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{Indian}. I'm happy that Indians are becoming aware of \textbf{r\textbf{ed}} pill. We should not lose this silent war with society.\normalsize   & \cellcolor{green!5}Indian, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I saw some videos of white rich guys going to poor India. Hahaha if you say hello to a girl you can get into troubles.  the \textbf{Indian} guys  will beat the shit out of you. There must be \textbf{crazy} to attack a white guy (taller , more muscular, heavier bones) but they will attack as pyrania.. in groups... 20-30 on you!\normalsize   & \cellcolor{green!27}Crazy, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small \@John Volken Simple.  Be a man.  Tell them that you are not their bitch.  If they disown you, you are better off.   YOU OWE THEM \textbf{NOTHING}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small indian men r ugly and dark, they are forced into mtgow\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It makes no sense for a \textbf{woman} to have multiple husbands and partners.  Is she building a family with these men?  Can't be, that would take too long.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Pleasure, endless stimulus /entertainment and various sources to extract an abundance of resources from. You think it's more ideal for an egocentric \textbf{woman} to exclusively date one man? The only thing that stopped them in the past was shame and social stigmas (which are now fading into obscurity). Monogamy was created to stifle urges that would create imbalances towards the nuclear family. No one cares about the nuclear family structure in the west anymore so monogamy is dying........\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small Over four years on Tinder and I got 1 blowjob from one \textbf{woman} who turned out to be batshit \textbf{crazy} and very mean. Tinder seems mostly a complete waste of time, I have matched with several women and when it got down to it it turned out that they never even actually go on dates they just like to chat with men because they are lonely. They have kids at home and parents to look after and can't really get away. And I'm tall fit and wealthy SMH\normalsize   & \cellcolor{green!5}Crazy, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/88 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Yeah you bet. If even a super rich guy like him cannot get and keep a \textbf{woman},then the rest of us normal dudes don't have a chance in hell of doing so. Also,if these Thots keep pulling a metoo and/or falsely accusing men of \textbf{sexual} misconduct or just outright rape they will soon find the vast majority of men won't even want to DATE them anymore. Let alone speak to or even look at them because they don't want to catch a false accusation or be metoo'ed. We will have looked at,weighed our options and situation and found it all to just be too big a hassle;dealing with women and totally not worth the trouble,effort or risks versus benefits to deal with it all. And thats when the majority of men will have decided to walk away. Its totally retarded guys,just go MGTOW and go your own way from these female "CREATURES" and all their problems,bullcrap and drama.\normalsize   & \cellcolor{green!27}Sexual, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/158 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small \@D I would personally say quite a few men would rather \textbf{yank} their hotdog honestly. Rather than have to deal with the hateful,spiteful,gold digging, and vindictive creature that is called the human female.\normalsize   & \cellcolor{green!5}Yank & \cellcolor{green!5}Nationality - American & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@suspicionofdeceit  My other male cousin did something similar. I thought when he did it: Dude really?! Your last \textbf{old} lady was banging like 5 other dudes when she was married to you bro! You just recently divorced her and then you actually went and downgraded to a single mom with two kids?! Then you ACTUALLY MARRIED HER CUZ?! You are a TOTAL F\&\@*\$ MORON dude! He divorced her as well and is about flat broke and is living in a camper right now. I honestly really don't feel sorry for him,especially if he didn't learn his lesson after his first RELATIONSHIT (Terrence Pop) and ugly divorce. Go MGTOW gentlemen and avoid crap like this,I am speaking from personal experience of seeing my male friends and family get destroyed...\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small \@Odell Mateo I personally have had at least THREE male family members or friends who were very close to me get wrecked,because that a-hole named Mr. Boner lead them straight to the slaughterhouse for men: Relationships and Marriage. One of them who actually is my cousin is stillcurrently with the controlling,lazy,ungrateful and hateful CUNT he calls a wife. She has already cheated on and left him once and she also threatened to leave and divorce him and take their two boys with her. He actually ended up taking that cunt back. Mostly because he loved his kids and didn't want them taken away from him,partially because he still loved her a little bit. Its all so screwed,\textbf{mental} and sickening to me. Seeing all this happen to guys who were so close to me is a large part of why I went MGTOW in the first place. I saw how really screwed and toxic things actually were,I saw it all happen right before my eyes. You CANNOT unsee that kinda crap and I would have to be TOTALLY \textbf{blind} or just a COMPLETE blithering idiot to miss or ignore it all. And people who are close to me wonder why I don't have a girlfriend or anything like that,they also ask me when am I going to get one? I always end up telling them I NEVER will get or have one.  Is it any friggin' wonder why I don't want one after seeing what I have? NO THANKS.\normalsize   & \cellcolor{green!5}Blind, Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/249 & \cellcolor{green!5}0.803 \\  \hline
  \cellcolor{green!27}\small Is a \textbf{woman} (p*ssy) worth 35 billion dollars?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@HunterRhett114 No \textbf{pussy} or amount of \textbf{pussy} will ever be worth that.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@HunterRhett114 That \textbf{pussy} better be permanently waxed, not a stubble to be found! And even then it still aint worth 35 billion dollars.\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Please fact check what Bezos's wife did for Amazon before you go full comando and who was in a relationship before the divorce. MacKenzie is a novelist and a writer. She was the main reason Amazon started with books which paved the way for the huge success. She worked there and supported the family. Plus they have 4 children. Jeff is the one who wanted to opt out and has a new gf. This story has \textbf{nothing} to do with the typical gold digging women who just wants to exploit the system and rich man.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Lazar Mitev - He did all the hard work!!! Writing a novel is \textbf{nothing} like being CEO of one of worlds biggest companies. You give her too much credit!!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@Lazar Mitev Yeah tell yourself that she was the main inspiration. Men always credit their wives as being their source of inspiration. The saying "behind every great man is a \textbf{woman}" is often used with successful men and successful men themselves say that until they get divorced. Women will even use those words against a man in divorce court especially if she had any kind of involvement whatsoever with the company. Its okay to have hope  bro but don't fool yourself.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small because he's \textbf{old} \textbf{bald} and ugly\normalsize   & \cellcolor{green!27}Bald, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small 90 of males are betas or just plain balding angry \textbf{old} farts. young fertile women are attracted to masculine hunks and chads with no jobs and not to some mgtow losers who got bullied in highschool for being ugly fucks and were sent their own way by women when they became millionaires.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small \@Odell Mateo Oh I absolutely love myself for sure;I know for a FACT that no one else will EVER love me like I love myself,especially a \textbf{woman}.🙂 There is no way I couldn't love myself. You have a leg up on me though brother. I didn't ever have a father to teach me stuff like you did. My asshole mother personally saw to that,she divorced the man she claimed was my father before I was even born. He was a piece of crap though honestly,and he didn't want anything to do with me because of having to pay child support and because I was so sickly as a child. He only called and wanted to have something to do with me AFTER I had turned 21. Him doing that pissed me off so badly I ended up asking him where the hell he had been all this time. That he didn't have any excuses really,because he knew where I have lived almost since the day I was born and we didn't tell him he was forbidden from visiting me at all. He couldn't even come up with an answer or an excuse,I was so pissed off at him that I told him to go F\&\@ himself and I hoped I NEVER had to see or hear from him ever again. He has NEVER called back or sent a letter after that either. Most of what I know I have either had to learn myself,especially about women. Or I have even had to learn some of it from my grandfather. He was the closest thing I EVER had to an actual father and I really miss him actually being here. He unfortunately got Alzheimer's disease and I had to just watch him suffer and waste away both body and mind ever so slowly,everyday for several years before he actually passed away recently. It TOTALLY sucked ass watching that happen to him man... I REALLY,REALLY hope your dad is still alive and well,If he isn't I hope at the very least that he didn't suffer the same torment my grandfather did.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/349 & \cellcolor{green!27}0.287 \\  \hline
  \cellcolor{green!5}\small \@Movefasta 93 you can take all your money and resources to your grave, \textbf{nobody} cares.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Zachary Laid Finding Freedom that's sounds \textbf{crazy} losing billions over a women getting mad\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Well confirmed, he richest man on Earth can't please a \textbf{woman}....that speaks for itself....\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Gatorade \textbf{Zero} bish\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Woman, Sex, Sexual, Misogynist, Gender, Chick, Patriarchy & \cellcolor{red!27}209 & \cellcolor{red!27}209/34122& \cellcolor{red!27}0.61 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}pussy & \cellcolor{red!5}32 & \cellcolor{red!5}32/34122& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age & \cellcolor{red!27}15 & \cellcolor{red!27}15/34122& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Skinny, Fat, Obese, Bald & \cellcolor{red!5}14 & \cellcolor{red!5}14/34122& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Dumb, Bonkers, Crazy, Disabled, Mental, Blind & \cellcolor{red!27}15 & \cellcolor{red!27}15/34122& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Red, Indian & \cellcolor{red!5}38 & \cellcolor{red!5}38/34122& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Red & \cellcolor{red!27}29 & \cellcolor{red!27}29/34122& \cellcolor{red!27}0.08 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}14 & \cellcolor{red!5}14/34122& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Zero, Nobody & \cellcolor{red!27}32 & \cellcolor{red!27}32/34122& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho, THOT, Hooker & \cellcolor{red!5}7 & \cellcolor{red!5}7/34122& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}14 & \cellcolor{red!27}14/34122& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Nigga, Black & \cellcolor{red!5}4 & \cellcolor{red!5}4/34122& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Male homosexuality}  & \cellcolor{red!27}Beta male, Gay, Faggot, Effeminate & \cellcolor{red!27}6 & \cellcolor{red!27}6/34122& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Race, Racism & \cellcolor{red!5}6 & \cellcolor{red!5}6/34122& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationalism, Nation & \cellcolor{red!27}2 & \cellcolor{red!27}2/34122& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common & \cellcolor{red!5}6 & \cellcolor{red!5}6/34122& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay & \cellcolor{red!27}2 & \cellcolor{red!27}2/34122& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!5}Brownie & \cellcolor{red!5}1 & \cellcolor{red!5}1/34122& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Hispanic}  & \cellcolor{red!27}Brownie & \cellcolor{red!27}1 & \cellcolor{red!27}1/34122& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - American}  & \cellcolor{red!5}Yank & \cellcolor{red!5}1 & \cellcolor{red!5}1/34122& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Gender - General;Nationality - Chinese;Age - General;Physical Identity - Physical Features;Physical Identity - Physical (and Mental) Impairments;Ethnicity - Native-American; Ideological and Political Identity - General;Age - Over 65s;Age - Youngsters;Gender - Female sexuality;Behavioural Addiction - Alcohol;Ethnicity - Black;Sexual Identity - Male homosexuality;Ethnicity - General;Nationality - General;Social Class - Working class;Sexual Identity - General;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Nationality - Hispanic;Nationality - American;%.

\item The percentage of hate speech related words is 1.3129.

\item Considering that the variable \textbf{Gender - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 449/1144 occurences of hate speech related comments.\end{itemize}\end{document}