\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_176.json :}\newline \par\Large\textbf {Title: \large  Generation Z - Who are we? }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small crap, you all really want to make us victims just like all millenials want to look? gen z is more than that, we dont act like victims even though we have been victims of the negative generation perspective since we were born, we grew up listening everyone saying that we are internet addicts with no convictions, having a total broke global economy, what the wars have left, polution at its greatest, we are the generation with most probabilities of \textbf{mental} health issues such as depression or suicidal thoughts and we still look like a big ass strong new era, we dont go crying over all but actually laughing of it and trying to see the reallity, and guess what, gen z seniors since the last 2 years became adults and its the turn to this world starts seeing the new change, hope we all can set an actual different control over the global things and shut up everyone who said we were the mediocre gen, oof to them\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/168 & \cellcolor{green!27}0.595 \\  \hline
  \cellcolor{green!5}\small I'm trying to do a bit of research because I'm writting a paper on what it was like to grow up on the post 9/11 world and this seems like a complete millennial video. It is true that Instagram and Snapchat stories make us depressed but I find that it glosses over how we can be an independently thinking generation because we came of \textbf{age} during the time where there was very little keeping us from any information we wanted to know showing us that our planet is dying and we have until we're 25-35 to stop it yet the generations older than us just completely ignore the problem and think technology is making us \textbf{crazy}, I knew this video was bullshit when she said she was excited about the future\normalsize   & \cellcolor{green!5}Age, Crazy & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/131 & \cellcolor{green!5}1.527 \\  \hline
  \cellcolor{green!27}\small I was laughing the whollleeeee way through😂😂 as a gen z \textbf{nobody} takes me this serous 😂 no-one takes any gen z this serious lol most of us are like suicidal but pop off I guess. Also, if she b getting distinctions, she doing BTECs so I would not worry abt that b raising grade boundaries\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Not girls \textbf{Woman} are \textbf{nothing} Generation z all reale mens\normalsize   & \cellcolor{green!5}Nothing, Woman & \cellcolor{green!5}Age - Youngsters, Gender - General & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small if you're an 18/19 year \textbf{old} - you like I, am leading the charge. Everyday is tough but, WE are the ones who will come to right the wrongs that those who belittle us everyday, have done... they live in the NOW, we are the FUTURE! STAND UP \& LET'S GET IT!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small I'm a witch\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Well to all those saying this is a millennial that produced this video well check the persons channel it was a 17 year \textbf{old} kid. But who is financing this that's another matter i can't believe it's a millennial parent the kid is too \textbf{old} either generation x or baby boomers more likely.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/53 & \cellcolor{green!27}3.774 \\  \hline
  \cellcolor{green!5}\small I just want to ask one question how \textbf{old} are the people in this video\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small this video is the big \textbf{g\textbf{ay}}.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small The internet , social media was one of the generation defining things that happened this ya gen z have been able to absorb so much information that we know how messed up the world is at a young \textbf{age}. That's why we're probably more worried and serious. Millennials used the internet for fun but gen z used it for information. We see how much the past generations have messed up the world.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small We don't give a shit bout social media and we are the most diverse people out here. Most of us don't care about what people say on social media and if they say we look \textbf{dumb} in our out fit we will say some shit like 'ye' and continue on wearing whatever we want and being whoever we want\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small Why is it that every video about Gen Z sound like it was written and directed by some \textbf{old} fart or millennial and not by someone born in Gen Z. It makes it so inaccurate and annoying. -me (15 years \textbf{old})\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small Why does anyone have to be described as 'right' or 'left' I mean I'm right handed, does that count? Why separate things into neat little boxes when everyone has a slightly different view. I'm a gen z (2006), and honestly, I get why people say we are more conservative, but today, what does that even mean? What does it mean to be conservative, or liberal? I'm \textbf{l\textbf{g\textbf{bt}}}, so are many if my friends, and one on my friends from my \textbf{old} school was very much a traditional Christian kid, we still got along and respected each other perfectly well and talked about our reasonings for our beliefs. Even when we were polar opposites, he was a white Christian teen male, who thought that unless you are a teen who is totally unprepared, or the baby has a terminal genetic disease, everyone should at least do their best to make having a baby the most viable option, whereas I am a Bisexual Trans Boy who was very much raised in a liberal agnostic household. But despite our religious and political differences we agreed to disagree and still were able to mostly get along and respect each other. Not what would you label each of us as? How about instead of candidates for president being separated into parties, and then people whose beliefs align with that party choose that candidate, how about instead all candidates are equal, third party candidates aren't erased, and everyone just plain tells the people what their beliefs are and what they think is the best course of action, and then you choose based in that. Say if Bob Shmoe is a Buddhist \textbf{g\textbf{ay}} man who believes that people should all start planning for their future from a young \textbf{age}, and Jill Hill is a straight Christian \textbf{woman} who believes that children should have less time in school and explore more topics outside of the school environment to allow for individual growth in fields of interest. Not what party would you say those candidates are? Does it matter? They both have varied beliefs, same with everyone, so why isn't this how the system works? I'm open to criticism, but please no hate language I'm only thirteen with a very limited knowledge of these topics, I have only studied politics formally for one year, and google is hardly a reputable source, but this just makes more sense to me personally.\normalsize   & \cellcolor{green!27}Age, Gay, LGBT, Old, Woman & \cellcolor{green!27}Age - General, Age - Over 65s, Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}8/401 & \cellcolor{green!27}1.995 \\  \hline
  \cellcolor{green!5}\small Durr hdurr technology is bad fire is scary and Thomas Edison was a witch\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Generation Z is fucked because as a teen, Iv realized that other teens my \textbf{age} are too fucking obsessed with tech. I asked someone, "When was the last time you read a book outside of class?" Exactly. No one really is motivated for school because information is squashed in your brain for no fucking reason and you forget it over break anyways.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small So if I were to make a movie in which gen z is described (I was born in late 1998) I would be prone to do it differently. We grew up with a or two caring but worried parents. Our parents taught us to be careful with money and to be kind to people. We were taught that we have to work in order to make a living but we were also raised in the regret of our parents not having their dream job and encouraging us to do the job we feel will not bore us even after 40 years or more at work. Or maybe our parents had their dream job and encouraged us to do the same. We grew up with an incredible love for family, even though the love we give sometimes doesn't pay of. We also know that in order to support our parents and maybe, maybe not the family we want to have, needs financial support because they deserve it.We had our first job probably around \textbf{age} 16 because we just couldn't stand the feeling of using our parents money all the time. We grew up with the awareness that saving is mandatory because economy won't grow forever. And we grew up with more diversity then many generations before us, that's why we are so liberal, because at heart we know, people are just people and there will always be a small percentage of people who do wrong things, who are immoral, misguided and manipulated, sick and Ill. But we are aware that this is always a minority and we know that if we were in their situation we wouldn't act differently. We might have grown up with electronics, but we remember walkmans and cassette players and DVD players and \textbf{old} indestructable Nokia's. But we aren't experts on the internet. We face problems that we couldn't even influence. The war in the near East, presidents and dictators with  no sense for diplomatic discussions. We have to live with \textbf{Brexit} because the elders were against the EU. We partially weren't even allowed to vote yet. We have to face conspiracy theorists, fake news and alternative facts, we have to deal with people who won't vaccinate their children. We love progress but we're afraid it's to late for all of us. And we realise that we have to live for ourselves and what fullfils us. We are supportive of the LGBTQ+ community because we understand that two consenting humans are just humans and that they should have the same rights. Yet we find comfort in religion because it give us a sense of peace.\normalsize   & \cellcolor{green!5}Age, Brexit, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Nationality - European or anti-Europeans & \cellcolor{green!5}3/439 & \cellcolor{green!5}0.683 \\  \hline
  \cellcolor{green!27}\small I BET THIS WAS MADE BY A FLAT EARTHER, CUZ THE VIDEO IT SELF DESCRIBES THIS GENERATION FROM A FLAT PRESPERCTIVE!!I am from GenZ and yes we where born and the internet existed but God dammit I can tell u that just judging an entire group of people for "USING" technology cuz it exists and based them on their \textbf{age} is just FLAT MINDED, jeez the oldest of us is only 23 and everyone starts claiming that they know all shit about us, plus; no gen z uses face book so I bet this was made by millenials.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small This is just a small group of post millennials and gen z. Infact gen z is more open and welcoming, anyone can be anything and \textbf{nobody} can be influenced so easily by media. This I've learned as a genZ. Apparently we gonna grow up wearing what we want to and more conscious about real issues like climate change, president Trump etc etc.And there is no such thing as post millennials. We know we identify with genZ stop calling us post millennials. Idiots😏\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small Sometimes I think a better name for us would be the fixers, those that fix the mistakes of the current culture. These are just stuff I can imagine us saying about these topics:Us on racism- what is that? Never heard of such a stupid thing.Us on sexuality- Why isn't \textbf{g\textbf{ay}} marriage legal everywhere? Like four of my best friends are sexually fluid and I'm not even sure who I like. And what does homo/heterosexual mean. We are not to be put in boxes, I'm whatever I want to be.Us on the environment- Well, my parents screwed up with that. Let me get my recycling bags and electric cars and fix the mess that they created.Us on the economy- I'm going to create my own business. Watching other people wait too long or be lazy taught me to take initiative.Side note, people call us lazy, but I believe we are more hardworking than most generations, and we will be further along in life than any other generation when we reach adulthood because we start preparing for our futures young.Us on politics- Teenagers actually CARE. This is a new concept. Teen: "Mom, when I grow up I'll vote for x because of their y policies and their z ideologies." Mom: faints because her child knows more than her about politics.My point is, we are realistic, independent, fixers, and we are accepting. I think my favorite part about my generation is our acceptance, and that is something this video, obviously completely false, failed to highlight. And while we are fixers, we don't whine about having to fix the screwy culture left behind for us. We WANT to change it because it's in our DNA to help.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/290 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}\small That's 🅱️ucking \textbf{g\textbf{ay}} dude\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small \@Unfragle Gaming nah it's true though. In high school it seemed like depression/anxiety/self harm was more \textbf{common} than \textbf{sex} or drinking or anything else we probably would've rather been doing.\normalsize   & \cellcolor{green!27}Common, Sex & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Who are we? .. \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small These comments are pathetic, wait until you stupid fucks really grow up and realise your peers have opposing opinions. This is the same b.s. everybody said about my generation and NONE of it is true. FUCK THE \textbf{L\textbf{G\textbf{BT}}} AND LIBERAL PROGRESSIVE MOVEMENTS! Get ready for a global civil war.\normalsize   & \cellcolor{green!27}LGBT & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}3/49 & \cellcolor{green!27}6.122 \\  \hline
  \cellcolor{green!5}\small I'm Russian member of Gen z( I'm sixteen y.o). Wtf I'm doing here??? I looked at the comments. So, I, and my friends, always thougt that american pindostan is \textbf{pussy} country, where women are ugly and men not actually male. I don't know now, why we are hating countries of each other? Why our ancestors starting new cold war??? That's stupid! I think our generation will forget about past enmity between our countries. I really hope in that. Sorry for my English language, i haven't use goggle translate, because хуй его знает. But, let you all be well in your country. And let the friendship be. When these idiots in power will retire.\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small I still feel like there should be a generation between gen y and gen z that goes from 1995-2007 (when IPhones came out and got popular) because if you grew up before then you didnt have smartphones or \textbf{apple}, you probably went outside, watched Saturday cartoons, and yeah your family might have had a computer but siblings share and it wasnt fast or small. Gen z are supposed to be the people who only know tech but if you grew up before it was around or your family didnt have any of it then you remember a time before and after it. It's one of those things that I think should be smaller or more like a decade or so since if you grab 20 years worth of people and say they share similarities you're going to be wrong cause it's too broad of a group, you can't contain that many people in a box.\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/155 & \cellcolor{green!27}0.645 \\  \hline
  \cellcolor{green!5}\small This video doesn't feel like Gen Z. Generation Z aren't \textbf{weird} edgy indie hipster weirdos, that was millenials.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small 1997Social media pressure isn't much different then pressure from non-media sources, if anything 24 media as it is today makes is difficult to keep a tradition/cliche going. Many people with different styles coming in at all directions, its \textbf{common} to hear one use social media as what is holding them back but on the contrary it has propelled the whole world forward and continues to evolve. If you don't like the way you feel, thats not on anyone els, you got to resolve your insecurities on your own, you are the one who holds yourself to it. Why dont you put down the social media accounts if it only brings sadness? Because you dont want to be alone, so you walk with a crook in your neck perhaps for the rest of your life on account of "i want friends". To not be afraid to be alone is to be honest with yourself and others.Shit + Video = Shideo\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/161 & \cellcolor{green!27}0.621 \\  \hline
  \cellcolor{green!5}\small what is this? a series of still-like digitally created pictures (which is \textbf{nothing} but light) changing frames at an unimaginable rate which creates an illusion into our brain that we call movement. The light which is produced by a miniscule metal device is "absorbed" and detected by our pupils which are stimulated by them causing a series of "action-potential" chemical system of communication which ultimately ends up sending these "messages" to the back of our brains. The Brain then interprets each image and "flips it" around to one that we can comprehend fully. And thanks to this wonderful system which is innate in each one of us (sorry \textbf{blind} people), it has gave me the wisdom and ability to see through this video's utter bullsh*t. This generation has lived with the internet almost all their lives. We get bored of being there all the time. For example, I, now that I am in college, I actually LOVE going out on walks by myself and simply enjoy nature. And I am currently very motivated in doing something great with my life. I am not going to sit around and whine around like millennials, I am actually going to work hard for it.have a good day\normalsize   & \cellcolor{green!5}Blind, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/205 & \cellcolor{green!5}0.976 \\  \hline
  \cellcolor{green!27}\small thus video was so  \textbf{dumb}. it said \textbf{nothing}. clearly made by a millenial\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Yall aint z, yall millennials, you are too old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Lol these people are too \textbf{old} to be gen z\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Ok yeah maybe for these people but not all of us are tech obsessed,  I would say at least 25 of my school, doesn't use their phone for much besides nessacary things  and doesn't go on social media too much. We do have shorter attention spans, but we can multitask like \textbf{crazy}. Don't say that we don't worry about judgement cause that's bullshit. We don't live in this all accepting judgement free world, not yet.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small this is all bullshit. kids are self- conscience and look to technology for the future and to change the world. sounds like every other generation from the modern era... \textbf{nothing} deep or unique is even mentioned. whats with all the generational hate? how do you \textbf{lump} such a large group together with \textbf{nothing} in \textbf{common} but \textbf{age}, but then preach about stereotyping every other group (except white males)? this is just more polarizing bullshit to drive us apart so we are easier to manipulate and control.\normalsize   & \cellcolor{green!27}Age, Common, Lump, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters, Physical Identity - Physical Features, Social Class - Working class & \cellcolor{green!27}5/86 & \cellcolor{green!27}5.814 \\  \hline
  \cellcolor{green!5}\small This sounds like millennials not gen z we haven't shined yet that much since most of us are under the \textbf{age} of 18 I'm not being cocky but we are going to be way better than millennials and more open minded because we frankly don't give a f what people think and we just wanna be successful\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small So let's hope that, due to our generation's freedom of thought, we have more flexibility in government and such. Being a right winger or left winger is just kinda on the racks for me. Situations can all be dealt with differently and I'd rather have a middle ground. Maybe a neutral third party will win an election during our voting years :)(Honestly I just wish that we had a sole party of logic which takes every situation they are given and deduces a logical response to it. Stop bringing emotional stuff into it. Everything's situational so give us wiggle room. \textbf{Nothing} is \textbf{black} and white, really.)\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/107 & \cellcolor{green!27}1.869 \\  \hline
  \cellcolor{green!5}\small Nigga the last generation never told you to eat  tide pods\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small We might also be slightly more conservative than Millennials but not in every case.-I don't oppose \textbf{g\textbf{ay}} marriage or \textbf{L\textbf{G\textbf{BT}}} rights, heck i'm \textbf{g\textbf{ay}} myself. But i do not support going over L-G-B-T and double genders. -I don't oppose women's, minorities' or black's rights, many of my best friends and favourite people are not white but i do not support the whitewashing in the media industry that either erases us or makes us look bad. It's hard to even make a joke or a pun and not get bashed for being insensitive against those groups.-I support medicare for all-I support free college tuitions-I support a more isolationist and neutralist policy with the rest of the world -I support the raise of minimum wage-I strongly support the banning of assault weapons off the country.And of course i support a more integrated use of technology into our lives, even after the Cambridge Analytica fiasco, technology is our future and those who do not support it are just scared of it and will stay behind.I am a realist but that doesn't mean i don't hope for good stuff to happen. I just don't aim for the stars.I was born in 2000 and I am balls deep into the technologic era. Am I a Progressive? Am I a Conservative? Am I a Liberal? I don't know and frankly I don't care.\normalsize   & \cellcolor{green!27}Gay, LGBT & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}7/235 & \cellcolor{green!27}2.979 \\  \hline
  \cellcolor{green!5}\small I was born in late '98 and I've seen both the worst of millennials and the best of gen Z in me. Growing up, I always leaned towards those older than me so I could learn from them, but I realized their world isn't mine at all: I'm a self-imposed vegetarian since 14 for feeling \textbf{dumb} about eating dead animals, but not a vegan since it feels too extreme and I honestly enjoy dairy. Digging avocado toast before it was even a thing, even though it's just like any another meal and I don't feel the urge to take pictures of it and post 'em everywhere. I'm all about equality and justice really, but the whole SJW thing and antifa lunatics are \textbf{nothing} but pathetic. Politically, I'm center-right and almost all millennials think we're \textbf{crazy} nazis when they hear the word "right". When it comes to our differences my hope is to be able to build a \textbf{common} future where everyone has their space to feel comfortable in. No special treatments but no discrimination whatsoever either - why they, the Y gen, won't see things this way beats me.\normalsize   & \cellcolor{green!5}Common, Crazy, Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}4/189 & \cellcolor{green!5}2.116 \\  \hline
  \cellcolor{green!27}\small British people pronounce the letter z so weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Ok why is generation Z from 1995 to 2010? It should be 1995 to 2005. I was born in 2000 and grew up without a cell phone. Sure we had internet but let's be honest there wasn't much to do on it in the early years. I don't have much in \textbf{common} with the 2010 generation Z kids. Our early child hoods are so vastly different.  I watched VHS tapes, went outside, went to blockbuster. I had a dvd walkman taped to my hip before ipods came out! 2010 kids don't know what a VHS tape is....\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small This comment section just shows that you can't put a people of the same range of \textbf{age} in one box. In the end it doesn't matter which Gen you are because we live in the same time anyway, so if the situation is shitty right now, everyone should fix it not just one generation. And stop saying the older generations had it better, yeah maybe in the US, but the US is not the whole fucking world, it's the internet, where everyone can watch this video! I think it's easier to categorize people from the same country.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/97 & \cellcolor{green!27}1.031 \\  \hline
  \cellcolor{green!5}\small Once (WE THE PEOPLE) see and treat each generation (YOU AND I) as one...wholly and unconditionally and are able admit that we're ALL equally at fault for not yet having come together as one  with the \textbf{common} goals of peace and unity on all lands across the world...WE ALL will indefinitely remain divided which is exactly what a select few have always wanted for their own personal gain since the inception of mankind as we know it. The only way to win this 'game of life on earth' is to ALL come together and riding the world of the ignorance that consumes ALL of us in some respect or another. Ignorance is bliss that benefits others instead of ourselves. That being said...I'm a GenerationRevolution, what are you???✌️😉\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/127 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small millennials changed the world and this \textbf{dumb} generation Z is just enjoying the benefits. This weirdos that try so hard to look smart (wearing reading glasses) are the sons of older generation x conservative ignorant people. The true sons of the millennials (generation alpha) will easily beat the butt of this pathetic generation. Just wait and see.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Gurlll u not \textbf{fat}. u thicccc. Own it ;)\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I'm from gen z and I have social media but I rarely even use it and when I do I don't post my face on my Instagram because I believe people should follow me for my creativeness not for me \textbf{race}, face , body or \textbf{gender}. This video is very wrong\normalsize   & \cellcolor{green!27}Gender, Race & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small 1977-1984 = X/Y Cusps1985-1992 = Core Generation Y1993-2000 = Y/Z Cusps2001-2008 = Core Generation Z"Cusp" refers to a \textbf{transition} between one generation and another.1993 \& 1994 = Gen Y with some Gen Z influences1995 \& 1996 = Lean Gen Y, but some may relate more to Gen Z1997 \& 1998 = Lean Gen Z, but some may relate more to Gen Y1999 \& 2000 = Gen Z with some Gen Y influencesThis is mostly my opinion, but I believe it holds some truth since Pew Research at the beginning of March cut off the Millennials at 1996, and they seem to be going by a 16-year theory with 1965-1980 being X and 1981-1996 being Y, so we can assume 1997-2012 will be Z. Obviously though, 1993-1996 is Late Gen Y and 1997-2000 is Early Gen Z, meaning they'll have more in \textbf{common} with each other (especially those born 1995-1998) than they would with those in Early Gen Y (1981-1984) or Late Gen Z (2009-2012), so using a cusp range for those born in 1993-2000 seems fair to me.\normalsize   & \cellcolor{green!5}Common, Transition & \cellcolor{green!5}Sexual Identity - Transexuality, Social Class - Working class & \cellcolor{green!5}2/187 & \cellcolor{green!5}1.07 \\  \hline
  \cellcolor{green!27}\small Emily and Emma are 2 of the most \textbf{common} names Gen Zers have. The boy should have been Jayden.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Ummmm they do realise the \textbf{age} where you class as Gen Z is 2000, these people look older then 18\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Boomers gave us Led Zeppelin, \textbf{Black} Sabbath, Aerosmith, Lynyrd Skynyrd, Queen, Judas Priest, Iron Maiden, and Michael Jackson. Wouldn't call them the Worst Generation.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small kael suma the greatest generation A time of \textbf{racism},  \textbf{sexism} and outright genocide include kkk and the beginning of nazis and world war 1, which plunged Europe into Poverty and paranoia\normalsize   & \cellcolor{green!5}Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small This has to be made by a group of \textbf{old} men\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Generation Z in my opinion is a healthy mix of earth and natural ways and technology. we dont really care about materialistic things and want to be more understanding of different opinions and we want to be able to take criticism so we can then grow as an individual. we dont take life too seriously but we take it seriously enough to understand that our futures depend on us and not anyone else. we are realistic and while we were born into technology, we arent as needy about it. We are hard workers and dont expect things to be given to us for free because \textbf{nothing} in this world is for free. We are a combination of \textbf{old} fashioned morals and values and modern ways of expression and again morals. I dont think we care about how we are perceived by other people, we really are more focused on our futures. if we have personal success, why do other peoples opinions matter\normalsize   & \cellcolor{green!5}Nothing, Old & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/162 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small gen z is \textbf{NOTHING} like this what in the world is this\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Exactly. Our generation is the one with the most \textbf{mental} illnesses, we don't care about validation from people on the Internet\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Our generation is gonna fuck things up, everyones an anxious \textbf{lunatic}, or a nutty alt-right stormtrooper.\normalsize   & \cellcolor{green!27}Lunatic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@I3fyr the Otaku most people under the \textbf{age} of 60 have some \textbf{mental} disorder now (the destruction of the family corporations like it that  way easier to control us)\normalsize   & \cellcolor{green!5}Age, Mental & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small \@ SagetheWise idiot do some basic research before you crap out of your  arse this video was produced by a 17 year \textbf{old},who influenced him is another matter.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small As of today February 13 2018,  I am 16 years \textbf{old}. Would that make me a millennial or gen z.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Gen z is awake at 2:30 AM on a Sunday because it just turned 18 years \textbf{old} and looked up on line what it can legally do know. Tú dingout that it had done illegal things since the \textbf{age} of 15, then looking up what now but the search bar sent it to what generation am I then tonight out that it's z and not millennials and feels good because they are always shit talking the millennials, then it finds out that it includes generation z then opens up YouTube and end up in some video posting a useless comment, thinking it it's self shit I have school and I have to turn that 10 page paper on Tuesday for college, and then it thinks to itself, I just wasted 5 minutes of my life writing something that no one will read. Fuck grammar.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/144 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small Fuck me, I was born in 2001 I am gen Z. 😂😂 these fruitloops are \textbf{crazy}, we should all just play a large game of cricket and sip on \textbf{r\textbf{ed}} wine. La'cheim everyone\normalsize   & \cellcolor{green!5}Crazy, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/33 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Millennial gave birth to Insecurity, self loathing and a ridiculous vision of what and how an individual should act or behave. My Generation is a disgrace and this next one won't be any better. Proud and arrogant just like us, they will change \textbf{Nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Crazy ChickenGuy Same. I don't give a damn another's opinion about my looks for example.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Black Dynamite no it isnt actually, unless you are vloggin\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I am a millennial and i hate social media. \textbf{Weird} thing is that a bunch of my mom's boomer college classmates are addicted to facebook. So really all our generations are ruined.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Generation Z is just going to be another failure. Not one generation has been as hardworking as the baby boomers and their elders. You all think that you can "change the world". It's not going to, so stop acting like you can miraculously change it. Yes millennials did not have that much drive but you are in a worse situation. One that your whole life is  driven by technology, millennials and now generation z have felt the wrath of \textbf{mental} disorders including depression and bipolar, more than any past generations. Did you think that just sprung up by itself. Well it didn't. Next time don't be so foolish to think that the world will change to your liking just becuase you said so.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small I don't know why but most of the Gen Zs in my school often wear gray or \textbf{black} shirts and they are either on social media or reading novels 🤔\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Gen Z is the next greatest generation. We're gonna fix the mistakes of those \textbf{pansy} millennials.\normalsize   & \cellcolor{green!27}Pansy & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small +Jacob AndersonAre you okay? First you believe in God, and now you're acting as if you have some form of \textbf{mental} retardation. Maybe you should see a doctor.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small +Jacob AndersonExactly. You need \textbf{mental} help.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Jacob Anderson You claim that you use facebook, believe in God, the laws of attraction that will not bring you to success and then proceed to invalidate all of your claims.You really need \textbf{mental} helpAlso success will not come to you for no reason, if you live with that mentality, it wouldn't get you anywhere in life.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Dzé Francis success is developed through hard work. I'm not claiming anything just pulling your legs. Obviously you don't take the hint. So get the stick out of your ass and stop assuming and smother your pompous opinion. Losers are the only ones that complain. You gotta be pretty unhappy with yourself to be so negative in general. I work my ass off. I put the energy out there with my work and positive out look, I, in return receive the fruits of my labor, thus is called the law of attraction. God is real to Christians, god isn't real to atheist. You are neither stupid for believing either. Anyone who thinks that are themselves stupid. So pushing your views on people and calling them stupid or need \textbf{mental} help is ignorant. People who do that are the type of people that love to hear themselves talk instead of hearing other talk. The 'I'm right because I read an article. Because my friends say so. Because it's never happend to me' people. Bruh I know sitting down watching tv for the rest of my life thinking Ima get something isn't going to get me shit. That's not how the law of attraction works. If you actually had the will power to understand the different meanings of the law of attraction then you may understand. Side note law of attraction is just like law of gravity. It's a physical law. You can say gravity isn't real that the earths flat what ever, but that comes down to perspective. You may have so called facts, but I'm sure there are facts for the opposite opinion as well. For instance god isn't real. Some have facts or evidence they've talked to him, some say they never seen or ever talked to him. Either way it's a fact to you and your self truth. I do not need \textbf{mental} health. You can believe what you want. And if I'm saying the opposite of my original post it's because I don't take negative people in a serious light. For instance the comments above. I'm trolling him. Idc what he thinks of me. The guys a chump. Just because I say I believe in god I'm apparently an idiot. Thats just an opinion. But he wanted to force his opinion on me because if I don't believ what he believes then I must be lower then he is. If you disagree with someone doesn't mean they are idiots. We will see what happens in the after life. If your an atheist then good don't waste your time on religion. Lol don't be push your ideals on others like a chump. And also just because you are motivated and are doing something in life doesn't mean you are more successful then a poor \textbf{fat} man who loves what he does and if that's watching tv then so be it. There is no where in life. The only success in the world is happiness. If making money is your happiness then so be it. If relaxing all day is your happiness then so be it. The successful person is the person who lives a life without regret. A happy life. You can have millions and be unhappy. You can have \textbf{nothing} and be happy. That is what you rate success off of my friend.\normalsize   & \cellcolor{green!27}Fat, Mental, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}4/556 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}\small And then I read another comment on this video that says Gen Z is more rughtwinged than Millenials. I guess you can't just put people of the same \textbf{age} in one box\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Jeniacess RPR You are an idiot. Gen X was too busy raising Gen Z. Gen X has \textbf{nothing} to do with Millenials. blame your Boomer parents.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Lell Mi Your generation fucked up too were all doomed you fucking jerk not caring for our planet you \textbf{dumb} human hater if you hate humans why dont you kill one\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small jac of harts Our parents had one job taking care of the planet and what did they do \textbf{NOTHING} we need them to make our life fun and amazing!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Srbija News yah cuz their parents are stupid and too busy with their phones instead of taking care of their children's \textbf{mental} health.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Lell Mi: As a member of Gen Z, I really appreciate people who call us all stupid. I don't care what generation you are, by calling us techno zombies (keep in mind you're using technology right now), you are in a way admitting that Gen Z is more educated than yourself. Also, if you're referring to true war, Gen Z probably wouldn't participate voluntarily. Nuclear tensions in North Korea have deescalated considerably since you posted this hate comment against a whole generation. And while there are many extremely stupid members of my generation (of that I am well aware) the same goes for any generation. And the fact that you're judging a whole generation based off of their TEENAGE years is worrying. Surely you could understand the importance of analyzing things in a fair light. It's like if I judged Gen X based off of their teenage years. I could then call all of them smokers and rebels, which now is far from the truth. Quit being a douche. Plus, I get the sneaking suspicion you yourself are a millennial, which would create an extreme bias. Edit: Also, Generation Z is considered the most open and welcoming religion, free of extreme forms of \textbf{racism} present in past generations. This same discriminatory pattern that we do not have is clearly present in you.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/222 & \cellcolor{green!27}0.45 \\  \hline
  \cellcolor{green!5}\small I3fyr the Otaku"Also, Generation Z is considered the most open and welcoming religion, free of extreme forms of \textbf{racism} present in past generations"what a noob you are. Ever heard of 4chinz kiddo?I'm gen z and a lot of millenials would consider me a \textbf{racist} because i want to keep european countries european and asian countries asian and \textbf{african} countries \textbf{african}.\normalsize   & \cellcolor{green!5}African, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/63 & \cellcolor{green!5}6.349 \\  \hline
  \cellcolor{green!27}\small gen Z is \textbf{dumb} af it is the worst so fucked up\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small One thing for sure, Gen Z don't give a shit about sexuality, religion, and race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Rekt \textbf{communist} most of us are\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Rekt \textbf{communist}   нет\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small that one right winger Exactly. I was actually surprised by how many people my \textbf{age} are.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Gen z checking in, recently of voting \textbf{age}. Am I generation zyklon? No, I do not hate the jews. But in all other areas I fit the picture closely.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Yep. Think those who are self-conscious are self-conscious but we aren't idiotic enough to believe that we have to look like a model. It's what we'd want but we're comfortable enough in our own skin. Some people even are \textbf{crazy} over confident which is great 😁\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Norman Goldstein Shekelberg  you're a Marxist subverter. I don't advocate for or approve of mass migration or liberalism for any country. If I had my way every country would be founded on the basis of a \textbf{common} history, language, culture, religion, and \textbf{ethnicity}. Ethno-religious states like Israel are what works for the world, putting all of the world's people, some of which have historically slaughtered or enslaved each other, into one \textbf{nation} is a terrible idea and will surely result in the destruction of the host population. All humans are not created equal and neither are the genders without those peoples. Different races and ethnicities have variations in their genetic IQ, the forms of government and cultures that form due to the smarter races are not compatible with the less educated races. Multiculturalism is suicide.\normalsize   & \cellcolor{green!5}Common, Ethnicity, Nation & \cellcolor{green!5}Ethnicity - General, Nationality - General, Social Class - Working class & \cellcolor{green!5}3/135 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Norman Goldstein Shekelberg  You may be right, Bibi and Soros May be on the same team seeing as we are one tribe and that's our evolutionary survival strategy. However I'm not speaking of them, I'm speaking for myself. I'm an American, I put America First. I'm a Paleoconservative right-wing Nationalist. I want a border wall, I want mass deportations, I want an end to dual citizenship, I want an end to legal immigration, etc. I can only speak for myself, and my point is that you becoming angry at me because I'm Ashkenazi Jewish is asinine because I had \textbf{nothing} to do with the subversion of the west. I want to end the subversion and see the west survive this invasion and repel it back to Africa and Arabia. I love my Goy brothers, I have their best interests in mind because they are like family to me. I wouldn't want to see their \textbf{race} and cultures destroyed.\normalsize   & \cellcolor{green!27}Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/158 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small this generation is the worst of the worst... the majority have no gratitude for life, especially that of others,,, no real Honor or integrity whatsoever,,, everything is \textbf{nothing} to them,,, so you tell me when you look at the majority of the world,,, where are human beings headed, what do they contribute to the universe or the Earth for that matter... what purpose do human beings have in existence... when you stand above the Earth and look down on it ,,, what do you see in human beings,,, do you see any gratitude or appreciation for anything but themselves.... yeah,, this generation is the worst of the worst....\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small Boomers are the ones in Power, Gen X is like their Silent grandparents just accepting things how it is. Gen Z should accept too, there is \textbf{nothing} we can do. We have to accept.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small they look millennial \textbf{age}...what's yrs for Z?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Ace Of Moms Yea bellow 18 years of \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small then why are you commenting like you're from gen Y you fucking larping millenial?You're not gen z, gen z is \textbf{r\textbf{ed}} pilled\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small I don't understand how this makes a millennial or a gen z different from generations before? Everyone has always been influenced by advertising whether it was presented to them in magazines, newspapers, billboards, tv ads, fliers, what other people are saying. How does the fact that it is now electronic make it different? I also don't understand why a lot of people who identify as a gen zeder are saying advertising has been shoved down their throat by millennials. Millennials are aged between 1981 and 1997, making the oldest millennial 36 and the youngest 20. How does a Personally I am 23 and had \textbf{nothing} to do with the advertising being shoved into your (and my own) faces. I think you'll find that the older millennials and the generation before them is responsible for developing the technology we have today. Millennials and gen z are the ones who are experiencing growing up with it first hand. Whether it is good, bad, or a bit of both, I don't know, but I am sick and fucking tired of of people blaming millennials for everything.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/183 & \cellcolor{green!27}0.546 \\  \hline
  \cellcolor{green!5}\small \@Eadlyn June it's an epidemic across all \textbf{age} groups it very sad to see (though grouping people in generations is bullshit another way of dividing  people),generation z is in a lot of trouble much more then millennial‘s and generation X because family bonds are breaking down faster especially in English speaking nations. You can be as tech savvy as you want without a good foundation in life you will not succeeded.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Teeny African you know what conservative mean right? That has \textbf{nothing} to do with race\normalsize   & \cellcolor{green!27}Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small We (especially me) really enjoy this generation and everyone just feel bad for us, I love this lifestyle and every past generation just talk shit about us, if we were older you guys will be \textbf{nothing} and we gonna make this world more modern than before, that you couldn't even know how to use electronic devices anymore cuz its too new for you and then just talking more shit that we make it really hard and complicated. Just admitted you guys are great but the new generation is going to take over and you can do \textbf{nothing} to afford it. Just deal with it.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/104 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small They sound like typical millennials, all the Gen z kids I know are right-wing individualists. It's only the GIRLS that abuse social media and act like \textbf{communist} \textbf{gender} study majors.\normalsize   & \cellcolor{green!27}Communist, Gender & \cellcolor{green!27} Ideological and Political Identity - General, Gender - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small I'm a gen zed but I'm not straight in my phone screen all day I'm out side with friends and girls that are friends  my dad was afraid that I whould never have kids or live life I guss I'm different than the zed gen but I'm still apart of it I'm probably different because I have adhd or my dad is a drug dealer I grew up watching my dad get a rested I grew up on a pot farm and I lived in hamilton ontario for most of my life I know how to fight shoot guns I fell like I'm not the same I look to my future and I wanna be a mechanic but I'm afraid I'm not smart enough to do it I missed alot of school because of girls my dad my mom so it depends were u grew up if you grew up like me your probably gonna join a gang or go the easy way gen zed may not be a tuff gen but all people or different if your a parent reading this know that I'm more social than you were when your were my \textbf{age} same with your kids we make more friends than a day than u made in a month know that your kid is okay as long as he's not a Internet troll.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/226 & \cellcolor{green!5}0.442 \\  \hline
  \cellcolor{green!27}\small Gen Z should not even be in the 1990s.. It should be 2001-2011. They are people That right now are 14 Years \textbf{old} and 12 Years \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small I3fyr the Otaku  "Conservation of matter" The Erath is always changing and the currently in a Ice \textbf{Age}. Most actions of Humans barley even change the Earth. Environmental is a different issue. We cut down trees only to plant them back in the ground which is great. Humans can barely scratch the earth's temperature. We are in a constant cycle of flow.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Yep, I'm def. not from gen z. I was too \textbf{old} to care about this stuff when I started using social media.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small GEN ZYKLON checking inI am American, but America is a cesspool of multiculturalism. Sometimes I feel we have no culture except Europe's. Defend Europe from the invaders. I am proud to be white. One girl in my class (you know the type lol, \textbf{r\textbf{ed}} hair, five piercings, I guess they still exist) told all of us we have white privilege, no one engaged her. But I have noticed that we hide our power levels. Legit everyone in my class watches pewdiepie and jontron, i know for sure most of the guys browse that special website (taiwanese imageboard?). However I would never tell people I'm proud of being white or European because I am afraid of the backlash/doxxing as a rayciss. They talked about the school walkouts on the news, you know how many people walked out of my grade of 100 people? only 10 people. And they were all girls, and one vegan (everyone makes fun of her behind her back). Also does anyone else realllllly hate hippie baby boomers? OMG I was at my teacher's 70th birthday party and her crusty ass \textbf{old} degenerate friends from college came up to me and my friends and started talking about how my generation was going to be the most progressive yet and how we were going to change the world. I wanted to fucking throw up. Imagine their faces.... one day. One day.Also I had a millenial teacher and she was whining after the election and I was so fucking annoyed. Millenials whine about anything.\normalsize   & \cellcolor{green!5}Old, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!5}3/256 & \cellcolor{green!5}1.172 \\  \hline
  \cellcolor{green!27}\small Fuck you guys I'm in my 20s and I'm a generation y. How the fuck did I live long enough to have had a part in the social structures or political games in this country. Not so long ago I was able to vote for the first time. At least wait till we're 40 to say we fucked you guys! Because we're still trying to clean up the mess our parents and their bitch ass parents made. What I was counting on is that two very young generations could come together and change the world but what I'm seeing is a bunch of criticism and finger pointing with two generations that aren't \textbf{old} enough to do shit with the world let alone know how. And for the record generation y didn't have generation z kids unless we had kids at 10 years \textbf{old}. I'm to young to have a generation z kid who's \textbf{old} enough to think about changing the world. I think the generation timeline is cut to short. Generation z should be considered my six year \textbf{old} nephew or my ten year \textbf{old} niece. If you're fifteen claiming to be generation z then that's like saying my aunt who's in her 40s is in the same generation as I am. Whatever I'm so over this generation bullshit. I'm under 30, don't know shit but I'm trying to learn, so fuck anyone who's critical of me.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}5/237 & \cellcolor{green!27}2.11 \\  \hline
  \cellcolor{green!5}\small Darth Yoste God I fucking hate this millennial self-deprecating attitude like :"Sorry don't be like us gen z we ruined the world" -millenial in the comment sectionLike Wtf are you THAT hopeless to just give up? Millenials are NOT making everything worse, it's probably some bullshit the older people spew out because they're insecure that they're not young anymore. It's been happening in the past generations too. Former peak generations would criticize new younger generations as being lazy and the cycle repeats.If you're a millennial and you're admitting that your generation "ruined everything" WHY not do something about it instead of blaming your whole fucking generation about it and passing it on to the generation z?Sincerely, a generic generation z member who is probably gonna be called a special snowflake\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/134 & \cellcolor{green!5}0.746 \\  \hline
  \cellcolor{green!27}\small "If you're a young conservative, you have no heart. If you're an \textbf{old} liberal, you have no brain."I don't think Gen Z will care as much about identify politics, it seems like they're already tired of it. By some standards that's liberal because they'll treat people more equally. They're taught that no one will care about them, and to be self-reliant, by people who are tired of employing millennials who take days off for headaches. Some things that used to be radical will just be normal, like sustainability and recycling.But hey, some of Gen Z is just graduating kindergarten, and the first are just starting college, so who can tell?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/112 & \cellcolor{green!27}0.893 \\  \hline
  \cellcolor{green!5}\small ExistenceIsFutile | People can completely flip from the politics with which they were raised if their parents only say dogma and don't explain the views. More conservatives means more liberal rebels and vice versa. On another point, I'd expect more \textbf{g\textbf{ay}} (economically) conservative families in the next few years.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Walter Pico Most of the kids who want immigration and multicultural trash aren't even \textbf{old} enough to form a coherent political opinion that isn't full of their teacher's or their parent's biases.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Fuck that shit thats a millennial video. \textbf{Nothing} like Generation Zyklon !\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small You are kids! Give me a break. How can you know what you are at so young an \textbf{age}? People change so dramatically over a lifetime just through the nature of growth and \textbf{age} and changing roles throughout life and a changing body and a changing world and changing experience. The insistence on being defined and special and something to be wept over or exulted based on your "generation" is a failing and is \textbf{crazy}. It's self absorbed to be that into defining self. The relentless need to "identify" as a group of some sort is stifling the world. Let the mystery be. Live your like and stop grasping at a label\normalsize   & \cellcolor{green!27}Age, Crazy & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/112 & \cellcolor{green!27}2.679 \\  \hline
  \cellcolor{green!5}\small But I'm Indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small lol this is such bullshit, this is more of what millennials went through, generation z really just doesn't give a fuck and we quickly learned at a young \textbf{age} that the world is not a nice place and it's all fucked up because we weren't coddled like the millennials were we don't need safe spaces and trigger warnings we came out understanding the reality of the world already.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small All of you gen z members shut the fuck up about economics. You guys are so retarded that you form opinions about things you know \textbf{nothing} about; half of you are fucking 12! Don't fall into the tribe mentality, saying shit like "lol we are gen z we're smart an millenials r dum lol." It doesn't matter which generation you are a part of; 95 of you are sheep.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small Armok God of Blood we will kick out the Islamic invaders and keep our nations our own nationality\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Fuck muslims, fuck SJW, fuck Hillary supporting libtards, fuck Islam, fuck idiotic clueless people who take feelings over facts, fuck third-wave and modern feminism, fuck this video that clearly dont know shit about the internet and technology, fuck \textbf{fat} ugly shitstains that ruin our countries by letting muslim invadors attack us, fuck the left media. Gen Z wont be as fucked as we are now.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small This is Gen Z?... just a bunch of spoiled, lazy brats raised by even worse parents..If Millennials are psychopathic, autistic (sadly not in the real sense and no offense to actual autists) cowards, then this generation is really no better.Children grow up smarter and thus, more arrogant than each generation before them.This generation is not motivated. They are lazy, sluggish and dependent upon their parents for every single god damn thing. Believe me, as one of the previous generation (as much as I hate to name myself a millennial considering my centrist views on society), I know what I'm talking about.I did raise one of these \textbf{mental} throwbacks. These children will just promise and promise and exclaim bullshit from their collective mouths about doing something in their life, but so long as you continue to support them they wont do jack shit and spend their lives living in your damn basement.Only when you actually kick them the fuck out of your house do they manage to DO SOMETHING with their lives and only because they're forced to.The person I have in mind right now was kicked out, eventually got a job and a place to stay and during this period we all thought that she'd changed her behavior. Bullshit, all it did was force her to use her damn brain for a year and now shes right back where she started, without a single bit of inspiration to move, no self-initiative to change things, always begging her boss to let her keep her job even as she is the last to finish her work. If there is a date, then expect her to deliver on the last possible SECOND. Not day, second .\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/290 & \cellcolor{green!27}0.345 \\  \hline
  \cellcolor{green!5}\small Joyde Clearly this kid was raised wrong. Check the parenting. As a Gen Z kid myself, I do see kids like this. Some kids are lazy and waste their lives away, but that doesn't mean you should \textbf{lump} a whole generation with them. Most of the gen Z people I know are very motivated and want to do something with their lives.\normalsize   & \cellcolor{green!5}Lump & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Yeah, because all the gen "Z" kids in my City aren't proof enough.I only used my own as a means to express myself, but that's not to say that they are the only one.Sluggish?Lazy?You know what, you are right. Such words do not fit your generation.Useless degenerate. There that's a proper way to name you and the rest of your entitled generation who would be such great people if only all they had to do was come and pick the \textbf{fruit} which represents someone elses years of hard work and dedication.Actually, your generation makes me remember a song. You should listen to it sometime - Chaotica, I Despise.\normalsize   & \cellcolor{green!27}Fruit & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/114 & \cellcolor{green!27}0.877 \\  \hline
  \cellcolor{green!5}\small Well I'm in my 20s and I'm considered generation y, so why when the \textbf{age} difference is so short do we argue about generational values when I grew up with social media the internet, phones, and I'm anti religion at least for myself because I don't need a God, I'm all about finding myself or evolving consciously and becoming more self aware, and I feel like I'm responsible for cleaning up the mess my parent's left us. I just don't get why with such a small gap in \textbf{age}, we're arguing over this. I'm with generation z. I want us to become more innovative, have free energy, new technologies and hell maybe begin populating new planet's. I'm all about science and technology and I love rick and morty. Stop dividing us.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/131 & \cellcolor{green!5}1.527 \\  \hline
  \cellcolor{green!27}\small Aidan Wolf I should mention I was born late January of 1997. If that nakes any sort of difference. I feel like anybody born between 1996 - 1999 are lost. No one knows how to define them exactly in terms of generational labels. It's all too muddled. Honestly, I feel like these labels are just used by the government and older folk to just put the blame and target young people to either shame or make change. It's a \textbf{weird} tool that idk I want to buy into. You are whoever you want to be. Do something and be proactive for WHATEVER you believe in.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/105 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small Actually, it'd be more 1994-1999, because that \textbf{age} group would've grown up in both the Web 1.0 (90s-2004) and Web 2.0 (2005+) eras. The Web 1.0 era ended in Late 2004 when Motorola released the Razr and when broadband outsold dial up. www.websiteoptimization.com/bw/1008/Childhood is described as being from ages 3-12, albeit 3 \& 4 are more nursery rhyme \& Sesame Street aged, while 11 \& 12 are preteens starting puberty and getting into teen culture, so 5-10 are the core kid years.Those born in 1994-1999 all turned 5 in 1999-2004 (Web 1.0), but didn't turn 11 and become a preteen until 2005-2010 (Web 2.0).Someone born in 1993 became a preteen in the Web 1.0 era (2004), while someone born in 2000 started their core childhood in the Web 2.0 era (2005).\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/134 & \cellcolor{green!5}0.746 \\  \hline
  \cellcolor{green!27}\small Varun Chandra Let's be honest 1995 kids are \textbf{nothing} like 2000s kids. one group is in their twenties and the other is in middle school/high school. These kids grew up with phones on their pockets ffs\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@Avery MalcolmBy that logic, Gen Y would end in around 1991. There's no way in hell those born in 1992-1995 were \textbf{old} enough to comprehend the political impact of 9/11, and to them the event would've been no more impactful than a tornado or a flood. To be honest though, I actually wouldn't mind Gen Z starting in 1992, as those born in 1992 would've been the oldest to be born after the USSR Collapse and oldest in 4-year college when the Crimean Annexation occured.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27}\small Sounds like a millennial \textbf{snowflake} who doesn't want gen z to succeed. Stop projecting.\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I wouldn't be worried about vanity I would be concerned about how you want to make the internet 3 and the next \textbf{age} of human existence. I would be concerned about the empires that will try and fool you to behave against your dreams. I would seek to light a torch that glistens in the darkest of shadows and be ready to light the way for z2 your children to be.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small How \textbf{old} are you, since if u are 20  then you are generation z. So the difference between me, 14, and some people in this video who could be as \textbf{old} as 22/23 at the moment, is going to be quite large.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Eric Mezenberg no its not going to be large at all whether you are 14 or 22 the only difference is that you are in school and they are in university/working they grew up in the same tech \textbf{age} we grew up (im 17 btw) our parents are probably from the same generation too\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small why are they styled like my generation   fucking weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Im part of generation Z tho and i think SJW'S and hard core liberals are \textbf{dumb} as shit.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small you won't repel muslim invasion, you ignorant \textbf{nazi} fuck, the fascist whites will die out accept it or suffer.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small So in other words you're racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Quinten Obvious so does everyone else like all the \textbf{old} people who invented your cell phones and computers you now have.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Isabella Sevilla I think millenials and gen z have so much in \textbf{common}, I know conservative pundits try to make a big deal out of gen z. However, Gen Z knows the reality of how broken our society is in the same way millenials do, both generations have the ability to be colorful individuals, be into economic and social equality, play the game (aka get a job) and participate in the same system we know is unethical, and be optimistic and realistic at the same time. We are spiritual in different ways than previous generations, while both of our generations know that science is the future. People try to act like Gen Z is very regressive, but based on my observations of both Millenials and Gen Z growing up there are the same amount of progressives and regressives in each, I used to resent my peers and compare them to to older genrrations, but as I've grown up I've realized that both are the same really. I'm not sure if I'm gen z or a millenial, but I am who I am regardless.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/183 & \cellcolor{green!5}0.546 \\  \hline
  \cellcolor{green!27}\small Is it sounds so \textbf{cheesy} and stupid xd\normalsize   & \cellcolor{green!27}Cheesy & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Blah BlahBlah It does sound \textbf{cheesy}, but you're not wrong.\normalsize   & \cellcolor{green!5}Cheesy & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small J E ss E Y For my school, most people wear t-shirts and hoodies, and people that wear the brands are actually using them (track, sports, etc). And before you say I come from a poor school, I actually live in a rich school district. We dress up sometimes, normally Friday's, but God forbid we are not allowed to wear nice clothes every once in a while like any other generation. Plus, \textbf{nobody} really cares what you wear anymore. Look up the biggest boy band in the world, BTS and check out their clothes and hair colors. They show how fashion really doesn't have a distinct look anymore because we don't just look to our own country, we look to others as well. We are unique, casual, fancy, trashy, classy. Yes, we are on our phones all the time but so what. We get things done on it and learn more about the real world at an early \textbf{age}. I know more about politics than my parents do sometimes because of my phone. And we suffer from an extreme amount of pressure simply because we are the next gen and are supposed to be BETTER. This happened to the gen before us and while happen to the one after us. It's just normal, but we don't crack under it. We work, care about our educations, start networking online at early ages, learn new things everyday via the Internet. And if \textbf{nothing} changes your mind about my generation, just remember we are 25 of the worlds population. No matter how much you hate us, or think us to be self entitled brats, we are still here. We will be a primary part of the work force, we dominate social efforts (sexuality and race's don't matter anymore; we are open and care more about personalities than skin color or who you like. I'm genuinely disgusted by \textbf{homophobic} and \textbf{racist} people), we dominate social media, we are starting to be able to vote. We are becoming part of you. Disagree with us, hate us, but one day we will be the norm, and everyone else will be stuck in the past. And the cycle will repeat with my generation being stuck in the past in comparison to the newer generations. It's how the world works.\normalsize   & \cellcolor{green!27}Age, Homophobic, Nobody, Nothing, Racist & \cellcolor{green!27}Age - General, Age - Youngsters, Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}5/382 & \cellcolor{green!27}1.309 \\  \hline
  \cellcolor{green!5}\small Idk I'm worried about the future etc. But... Idk which gen I belong  I'm not so millennial.  From 93 I'm but I don't just fit with fucking \textbf{nothing}. N I'm a conscious one\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@ Revile Paragon 2 I wish that was true but every day people under the \textbf{age} of 40 are becoming like the kids on the video\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Generation Z have not had any influence on the world yet. Millennials and Gen Y are responsible for the world around you.What you said was complete bullshit though all i see of gen z is pretty much a whole generation of mindless braindead zombies who are afraid to be different from one another and are \textbf{nothing} without their social media and phones. As a millennial I dont want to live on this planet anymore when its gen z's turn to step up to the plate. Also what is up with the fucking remakes!?!? My whole childhood seems to have been rehashed and im a 90s kid for fuck sake. No originality.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small PSwizzle 93 | Teenage conformity is \textbf{nothing} new. Because they can connect so easily now, people that used to just be independent now have their own small cliques.As to the remakes, that's probably Boomers and Gen X getting into the movie industry and saying "now how can we farm the nostalgia of younger Gen X millennials?"\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Srbija News Thats fucking pedophilia u idiot! And who fuck have \textbf{sex} when they are 13? Yes they might have \textbf{sex} when they are 15-18 but to the people with the same \textbf{age} as them! U sicko\normalsize   & \cellcolor{green!5}Age, Sex & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small Childish Bambino How can u be so negative to say that we are generation that will destroy the world. We dont have any influence in the  world yet. We can learn from the mistakes that the older generation had made and try to fix a broken world :P Im not gonna follow a label given to me and my generation, that we are lazy and techno zombies. The thing that drive me to make the world better is the fear that the newer generation can't experience the things we experienced when we were the same \textbf{age} as them. U might think our generation is gonna destroy the world but i think we can still change. I mean we have our lives ahead of us..\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small Srbija News And since when was a \textbf{nationality} an insult 😂😂 but i might be wrong, u might have a future career as a prostitute with your "big dick". Goodluck on your future career! 😂😂\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Childish Bambino, I live in a very white, rich area right now and I think that the \textbf{thot} epidemic is what you are reffering to. If they don't smarten up and stop wearing ripped \textbf{skinny} jeans and crop tops I think our generation may truely be doomed\normalsize   & \cellcolor{green!27}Skinny, THOT & \cellcolor{green!27}Gender - Female sexuality, Physical Identity - Physical Features & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Bring out the Dragons wtf are you saying? Millennials grew up with 9/11 we were born after the \textbf{age} we would need to remember 9/11\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{Commie} Scum seems more like a social disorder more than anything. What you do online literally is not what real life interactions are like\normalsize   & \cellcolor{green!27}Commie & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small We (Generation Z) were born around 9/11 and we all grew up knowing \textbf{nothing} but a terror-stricken world. Yet we're constantly drilled into our heads that tolerance can solve it, and that we should solve other people's problems?I'm sorry, but I've noticed a trend among much of my other generation Z friends (male ones to be exact) — we couldn't give a shit about some craphole countries. Our economy is slowly crumbling. Our prospects for getting jobs are shrinking day by day amidst globalisation and automation. We have no chance of ever being able to buy a house and no chance of ever being able to retire. Yet the Millennials want to tell us that the billion fucking non-existent genders are more important than the future.Do you know why we won't be able to retire? Well, it's because of a simple thing you can't solve via immigration — Aging population. Do you think immigrants come here to pay for your retirement? Of course not. The entire pension system was able to function on the fact that there'd be more people in the next generation than the previous. Where the fuck does that leave us who live in times where people in the West would rather bask in their own selfishness than ever have kids.Our Generation is fucked in so many ways and I don't even care which way you politically lean, because you're probably just as fucked as anyone else. The millennials constant cry about their problems instead of working to solve them, and as a knock-on effect they're just passing the \textbf{buck} down to our generation of already over-burdened system-slaves.Does it even matter that we're better educated? We work all our childhood up to the end of University (or just secondary Education) and then, unlike our parents told us, we'll be working from then on for the rest of our lives. We have no choice. The system has decided for us. The last two generations have decided for us.I won't be surprised if there's another major war within my lifetime, probably while I am of fighting \textbf{age} as the cherry to top off all our problems.\normalsize   & \cellcolor{green!5}Age, Buck, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/362 & \cellcolor{green!5}0.829 \\  \hline
  \cellcolor{green!27}\small The last 2 generations or what I say last 4 generations are full of shit. Some 30/40 year \textbf{old} act like childs. And it's not really about generation. It's about personalities we need more strong men. Because men became a lot of them just childish and more feminine maybe due more women became more manly. I place myself totally out of this. Because it is about progress and never giving up on your goals. But these days everyone gives up and have a really poor mentality. And about solving this world. There is only one way to do this which was not available 10 years ago. Corruption, poverty and wars is about a financial system which drives all the money to the top 0.001 the people who manage this world. Create wars to earn more money. The only weapon we have is blockchain. But there is so much work to do to create a system based on blockchain where these 0.001 has no power. wars, terrorists, global news and social media are tools to fool the people to manage how they act to scare them. Tell me how you felt when there was a \textbf{terrorist} attack? You get scared for sure.\normalsize   & \cellcolor{green!27}Old, Terrorist & \cellcolor{green!27}Age - Over 65s, Religious Identity - Muslim & \cellcolor{green!27}2/201 & \cellcolor{green!27}0.995 \\  \hline
  \cellcolor{green!5}\small The new generation isn't more educated or intelligence driven. Maybe in other countries but the kids in my country glorify video games and all weigh a ton of weight playing the role of a \textbf{spike} strip on the road. The vocabulary consists of "woke" "fleek" I'm "offended" "you \textbf{racist}". Not to say it's all downhill from here I'm just seeing kids become robots more now then before. Obesity is mass problem pun unintended. Lol\normalsize   & \cellcolor{green!5}Racist, Spike & \cellcolor{green!5}Ethnicity - General, Religious Identity - Protestant & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Rosie Eggleston \textbf{nothing} wrong with it. comics ruined the 90s so what\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small jefferson diuguid Fuck snowflaky! whist I agree there are some casualties that are still brainwashed and pandered into millennial, \textbf{libtard} scum; the majority of us are sane. I'm 15 and have had multiple physically labour jobs and work hard for my pay. This is the altitude I hope and think my generation have.\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Mary  1462 yeah really though, good point. Also if all of these parents are so damn concerned about us always using our phones all of the time, they could, I don't know, quit handing phones, tablets, and computers out to their 8 year \textbf{old} children\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Mary  1462 this video is very inaccurate to most gen z. We don't use Facebook, this video seems to promote that we are 'being fake' on social media. We all know that's how social media works and this \textbf{weird} search for authenticity that was prevalent in the 90's seems inauthentic in itself. This video seems to apply to melenials more than us. Gen z just tend to be more on the side of not giving a shit about a lot of things and just living life in a way that will hopefully get you a job.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small \@Neonmaster Nelson I believe in many things that would be considered traditional left and don't like many traditional right values; but due to what the modern left has become and what the modern conservatives represent (they made \textbf{g\textbf{ay}} marriage legal for fuck sake) I find myself aligning with the conservatives. Different areas are very different; and the conservatives (I live in the UK) are very different from your republicans.Also calling people who don't agree with you Neo Nazis (when they're not or you don't know if they are) is close minded and one of the reason I'm so opposed to the modern left.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/104 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Neomaster Nelson It is you who started speaking about the left-right, conservatives and Neo-Nazis(what the hell Nazis got to do with this discussion). While its true that the left narrative was the leading one, and most of the social and economic disasters you inherited are due to their ideas. But the right have played along many times, and added damage of his own. For instance, It was the Republican Nixon, who debased the US currency from gold to \textbf{nothing}, thus enabling super-deficient spending. I encourage you to watch the movie GENERATION \textbf{ZERO}, it explains the subject greatly. You see, one of the major Philosophies that ruled and ruined the western world, is statiesm, the \textbf{transition} from relying on the individual, the family and the community, to letting the state(specially what is called - the establishment) solving all the problems, and be the ultimate moral arbitror - and this was mainly done by the left who was main dictating force in culture and society.\normalsize   & \cellcolor{green!5}Nothing, Transition, Zero & \cellcolor{green!5}Age - Youngsters, Sexual Identity - Transexuality & \cellcolor{green!5}3/163 & \cellcolor{green!5}1.84 \\  \hline
  \cellcolor{green!27}\small Alrighty, multiple replies, lets do this."modern left has become and what the modern conservatives represent (they made \textbf{g\textbf{ay}} marriage legal for fuck sake)" Now I dont exactly agree with marriage, but there should be \textbf{nothing} holding anyone back from same \textbf{sex} marriage, they contribute to society like everyone else." Different areas are very different; and the conservatives (I live in the UK) are very different from your republicans."  So you would know better than to generalize all left in the same coupe right? In Western Europe, the Left could be militants, in America, SJWs. Don't generalize sides like you just did atop.v" but due to what the modern left has become"v" Different areas are very different; and the conservatives (I live in the UK) are very different from your republicans."\normalsize   & \cellcolor{green!27}Gay, Nothing, Sex & \cellcolor{green!27}Age - Youngsters, Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}4/136 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Nah It was to clap back at this statement ", fuck libtards, sjws, PC culture" So i'd call you a Neo-Nazi, \textbf{Cuckservative}. Dont dish it out if you can't take it.\normalsize   & \cellcolor{green!5}Cuckservative & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small \@Neonmaster Nelson​ 1. You misunderstood me, I'm all for \textbf{g\textbf{ay}} marriage and the conservatives made it legal. [LINK]  true and I will attempt to single out the libtards from the actual traditional left in the future, but I did mention a difference between modern and traditional liberals.3. First of, I can take it. Secondly If your not a one of these things then it does not apply to you. Simple. I will however try to generalise less in the future.Edit/side note: please name who you are responding to in the future. Thanks!\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/94 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Jerry B No, bring down their \textbf{communist} manifesto, and replacing it with a Monarchy. Also tell them there are two genders. DEAL WITH IT. The end\normalsize   & \cellcolor{green!5}Communist, Jerry & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - German & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Your generation invented that multiple genders nonsense. When I was in school trans didn't even exist and \textbf{g\textbf{ay}} was an insult.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Jerry B No last time i checked it was those 20 to 30 yr olds bragging about that, i have no shit in that, im still in school, and we have more time worrying about terrorism than genders\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small What is gen z's opinion on \textbf{g\textbf{ay}} rights?\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Finally someone with some \textbf{common} sense, most of our generation do not align with right wing ideology\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Dumbass, we left England to get away from Monarchy to form a republic BY the people. - 28 yr \textbf{old} Millenial\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small It seems to me, you're all just the typical internet ADDICTS who always want to find something to whine instead of actually whining about the corruption inside a system (no matter what gen you identify with or belong, which I might agree with some of here who say that conforming to these kinds of label is utter bullshit). What makes the internet dangerous is 1.) Solelu based on how the perceiver and the receiver of the information takes everything on the net and 2.) On how misinformations and horrendous and (misinterpreted) ideologies (by the opposition) frolick freely and par with the actual good and benefitial information. Do you know how to combat these horrible cultures you say that had been shoved on you by the people you accused of who which were had been probably been shoved by their \textbf{elder} generations? Educate yourself. You've got the whole enchilada in your hands as you say. You grew up with the internet. It's time to use it well for progress not regress. Pointing out of what you perceived as mistakes of the ones ahead of you may they be from a subjective pov or objective is one thing and it should be brought upon. But don't act as if you know everything. These horrible cultures you're tagging had always been existent and it will surely exist in your own generation for all people have their own individuality, whether they were shaped by circumstances, nurture or nature. And I'm telling you as a twenty-one year \textbf{old} who still has to learn about everything around me, exclusion is a very wrong move and propagating for something, especially that will lead humanity to progress, SHOULD not only be effective on a certain group of people but for all. This should not actually be a certain generation vs generation but instead we should find a \textbf{common} ground and till on that. Connect and reconnect----that has been the purpose and somehow the good effect of the internet you grew up with, right? Now rants over. Y'all dismiss!😂\normalsize   & \cellcolor{green!5}Common, Elder, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}3/340 & \cellcolor{green!5}0.882 \\  \hline
  \cellcolor{green!27}\small scruffyEALOL speak for yourself you fucking LARPing millenial, im gen z and i'm hardcore rightwing and against ALL FORMS of non euro immigration to european countries (however I am also against ALL FORMS of non afro immigration to \textbf{african} countries and non asian immigration to asian countries). My little brother is only 11 and he's watching jontron and pewdiepie and arguing with my sister who is sort of left-leaning\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small swell guy how \textbf{old} are you\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Jerry You know we won't stay kids forever, right? 😂\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small im anti feminist rightist trump supporter hispanic at the \textbf{age} of 11, just go to my channel and see my face\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Ginsuma Don't \textbf{lump} all Gen Z kids in same category. 90 of my friends and kids my \textbf{age} I generally know are against SJW nonsense. Most of them are leaning to right, but calling them alt-right is wrong. We are more alt-light\normalsize   & \cellcolor{green!27}Age, Lump & \cellcolor{green!27}Age - General, Physical Identity - Physical Features & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Gintoki Sakata You're still an anime loving \textbf{pansy}. Stop trying so hard to justify yourself online.\normalsize   & \cellcolor{green!5}Pansy & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Zach Edwards apparently liking anime has to do with being a \textbf{pansy} which has to do with his argument\normalsize   & \cellcolor{green!27}Pansy & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small albaraa atif cookie cutter anime \textbf{pansy} please.\normalsize   & \cellcolor{green!5}Pansy & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Zadof Hensley I'm a 15 year \textbf{old}, anti sjw, left leaner who hate all the presidential canidents, and loves, gorillaz, lion king, and animaniacs. sjws are obsessed with \textbf{race} and \textbf{sex}, they say they are fighting against \textbf{racism} and \textbf{sexism},and are the \textbf{underdog} heros, but most are \textbf{racist} and sexist by definition and the high class mainstream villain\normalsize   & \cellcolor{green!27}Old, Race, Racism, Racist, Sex, Sexism, Underdog & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Gender - General, Social Class - Destitute & \cellcolor{green!27}7/58 & \cellcolor{green!27}12.069 \\  \hline
  \cellcolor{green!5}\small i'd rather be a millennial than pussies like generation z..oh do i look \textbf{fat} with this man bag\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small irish rover 4Chan is pure cancer. You can roll around in the dirt with the \textbf{pigs} all you want. You do you.\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Wtf? Okay this clearly was made by a millennial. Those whiny little cry babies always trying to create some perception of evil Corporations, while simultaneously giving all their money and power over to a bunch of corrupt losers in the government. We're one of the most entrepreneurial minded generations, and not going to put ourselves in debt to get a meaningless degree. This video was Incredibly vague, trying to hard to be deep when it's not. \textbf{Nobody} uses Facebook or twitter anymore, no one is that insecure we are all pretty confident and while technology is a big part of our lives we don't see that as a. Bad thing. This video was clearly made by a millennial expecting us to be the same Whitney pussies they are. News flash, we aren't. We are the pendulum swing. The revolt against your regressive politics and ideologies.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/145 & \cellcolor{green!5}0.69 \\  \hline
  \cellcolor{green!27}\small I'm generation Z (mixed \textbf{race} guy) and I have a job and am planning to save up for a house, I feel good, I'm American and so far in our history every president has been fucking stupid so Trump doesn't affect me, and got hella friends, I love to go to parties and meet cool people and talk, and social media is chill cause I can share pics and clothes I buy, and I make music for fun so...\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small sebastian jasso we're to young to have screwed up in life! Are you serious, and not all of us are in debt to our asses in student loans. Most of us are 20 something trying to figure it all out before we fuck up our lives. Damn generation z sounds like those \textbf{old} ass baby boomers being hypocritical. You won't find us trash talking the generation after us, but it's funny how you guys trash talk the generation before you. Fuck off we don't care about what your generation plan's are for the future. We're still trying to figure out own shit out.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/103 & \cellcolor{green!5}0.971 \\  \hline
  \cellcolor{green!27}\small Katiyildora Killer look I agree with you. And technically you're to young to have fucked your life up you haven't even lived yet. Tell me you fucked your life up when you're 45 and still doing the same shit. Our 20s are filled with fuck ups. It's trial and error. Two I feel like generation z is blaming generation y a generation that hasn't been around long enough to do anything with ourselves let alone fuck up society. If they want to blame anyone, they can blame the generation responsible for the recession. I'm not blaming anyone personally, but I was gonna do it I wouldn't blame a group of people within a five to ten year gap in \textbf{age}.  That's even more retarded.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small Sabrina t you haven't seen what we have. We were told to go to college and when we got out we were screwed over and there were \textbf{zero} jobs. You don't know what we've been through. We saw the world get dark as teenagers and 9/11 is something gen y saw and lived. Imagine as a kid having peace and and war start. We aren't hippies and don't judge us. Maybe look at the events we went through and the promises we grew up being told that were untrue. Gen y isn't to blame. Gen y actually wants to understand \& hear gen z and each generation has its skills. Honestly be careful of your claims because gen y actually knows technology just as much as gen z and the last of gen y is actually 23 to early 30's and we are young enough to learn technology so don't judge. We don't want to judge you\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/157 & \cellcolor{green!5}0.637 \\  \hline
  \cellcolor{green!27}\small Sophia Nichols I definitely remember growing up and being told if I went to college in would be in debt rest of my life. I remember when 9/11 everything changed around me. Attitudes got darker, as I got older  around 12 to about 13, I Remember hearing about how there is no jobs then I fucked up and got sent to a maximum security program called TIGER SHOP. shop stood for serious habitual offenders program. I was brainwashed into thinking that when I got out if I did good and followed the rules I would get a job and have a life. When I got out at \textbf{age} of 17, I realized it was straight up lies and no one wants to hire a thug. I could go on and on. But my point is the world we live in is a construct of the previous generation. All the road blocks we face, majority are because of the expectations of us by the previous generation. I'm 24 now and my generation has not had enough time to change anything yet we are still in our early to midish 20s\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/189 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small Katiyildora Killer you are gen y. Gen y's remember 9/11 and lived it. 1994 is the last gen y and my sis is 1994 and just turned 23. People don't realize that it used to be a 30 year gap between generations but now it's 15 Year's. There isn't much of an \textbf{age} gap and honestly gen y is just trying to figure things out as 20 something year olds. I'm only 3 years older than you and I'm gen y\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Quinten Obvious Thanks for realizing that. Not to mention we're not exactly \textbf{old} enough or in power yet to ruin or fix the world yet the oldest millennials are in their 30's and middle management in jobs at best mostly.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Noah Wilsey Donald trump a traditionalist ... Im Sorry i think you have the wrong guy. Bernie sanders a revolutionary? Kinda high praise for an \textbf{old} man who want to take my money and power and give it to corrupt people in the government.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Nobody. Slaves to smartphones who will be slaughtered and replaced by hordes from africa and middle-east.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Genderless \textbf{Alien} me to\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Us Canadians have to say it like that or people go grammer nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Ulfric Stormcloak gladly your wrong, gen z that has reached voting \textbf{age} so far has voted 69 conservative in the states\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Indypotter1 There are still a decent amount of the brain washed people who take what they're told as being the sole truth but, I think our generation is one that, due to our young \textbf{age}, is only like that due to how young we are. As you said, people find out their own information. I think that's more of something that will happen as the children of the generation mature. Personally I'm centralized on logic and looking at all possibilities, all standpoints, and the truth of the matter. I invest myself in topics to the point where I have spent 50+ hours researching a singular topic, reading every word from hundreds of websites and books. We have many people who are on opposite sides of the spectrum, though. My hope is that the few social media obsessed preppy people open themselves up a bit more. Someone of those people lack true aspirations, but I think many of us understand the world and can see it in many different lights. Realists sounds pretty good. Everyone I interact with in my grade has a realistic understanding on topics. Guess we're a generation of individuality, distinction and (generally educated) opinions. Though maybe I'm just being hopeful, lol 😂\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/205 & \cellcolor{green!27}0.488 \\  \hline
  \cellcolor{green!5}\small nah we not \textbf{libtard}. we libertarian/conservative.\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Revolutionary Guy there is \textbf{nothing} like cultural marxism in existence. You haven't read marxism either\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Ice Wallow Come Only the oldest members of Gen Z were \textbf{old} enough to vote in 2016. Most Gen Zers are under \textbf{age} of 18.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small I3fyr the Otaku a "free" world is not idea, unless you wanna go back to the stone \textbf{age} or to the \textbf{age} of trading and bartering, which I very much do not. I enjoy making money and buying stuff and I enjoy getting paid. Money is not the problem, it's people, but what are you gonna do? The government should keep it's nose where it belongs. At the same time things like health care should not be privatised.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Ginsuma no gen z is conservative we are the ones making memes of feminist and \textbf{crazy} liberals 😂\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Chunk Yogurt  lad no generation Z is like this In England l should know. I am from the UK and l am \textbf{nothing} like what they show in the video\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I'm going to be honest, I was born in 1997 and I can't relate to gen z. I relate more to gen y only because I never grew up with social media or a smart phone. I didn't even have a smart phone until I was in 10th grade and facebook was 9th grade. I'm seeing kids at \textbf{age} 5 with a smart phone and when I was 5 I was out playing outside or watching cartoons. I'm going with gen y on my part only because it doesn't make since to cut half of a decade out that had a big influence in the 2016 election when gen Z had no say in it yet everyone was talking about how all the millennials get a say in politics now ranging from 18-early 30s and I was 19 when I voted.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}\small The most \textbf{common} start date for Gen Z is 1995.1994 is the best year to cut off Gen Y, because they were born in the first half of the 1990s, were 5 years \textbf{old} and out of the child mortality \textbf{age} bracket (0-4) by Y2K, were in double digits in 2004 when Web 2.0 took over, started high school during the Bush Administration, and were \textbf{old} enough to vote for Barack Obama.\normalsize   & \cellcolor{green!27}Age, Common, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Social Class - Working class & \cellcolor{green!27}4/73 & \cellcolor{green!27}5.479 \\  \hline
  \cellcolor{green!5}\small There are some 1996-1998 borns who remember 9/11, as well as some 1993-1995 borns who don't. Memory is a subjective criteria. Plus, just because you remember it, doesn't mean you were impacted by it the same way as someone who was a teen or twenty-something at the time. Those born after 1990/1991 will only remember 9/11 the same way they would remember a tornado or a flood, no way in hell were they \textbf{old} enough to comprehend the political change after 9/11.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small its \textbf{age} 4 when memory startsNot true. It's been scientifically proven that some people can remember things from as early as 1, while others can't remember anything until they are 6. Memory depends on the person. If you're talking average, about 3 years 6 months would be about the average for when people start remembering stuff.Plus, those born in 1993-1995, although \textbf{old} enough to remember Y2K, were too young to comprehend the significance of it being a new millennium or to understand the Y2K bug thing.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/88 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small \@The \textbf{Commie} Scum, 19 and under? Bullshit.There's \textbf{nothing} cut off worthy about 1997.Those born in 1994 were the last to be out of the child mortality \textbf{age} bracket (0-4) by Y2K and the last to be able to vote for Obama.Those born in 1995 were the last to be out of the child mortality \textbf{age} bracket (0-4) when the 21st Century began on Jan 1, 2001.Those born in 1996 were the last to be out of the child mortality \textbf{age} bracket (0-4) by 9/11 and the last to be adults when the Ukraine and ISIS crisis started.Those born in 1998 were the last to be able to vote in the Trump/Hillary election.(keep in mind the child mortality \textbf{age} bracket is a figure used by the UN and therefore used globally)What does 1997 have that's cut off worthy? \textbf{Nothing}.\normalsize   & \cellcolor{green!5}Age, Commie, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - General, Age - Youngsters & \cellcolor{green!5}7/145 & \cellcolor{green!5}4.828 \\  \hline
  \cellcolor{green!27}\small gen z highest is like \textbf{age} 19 or 20\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Gen Z is still practically babies right now, you can't even rent a fucking car.....and for damn sure don't have student loans, of which, I hope for the sake of humanities future, you all learn that college is a scam and never invest into the bullshit unless your job requires licensing. Doctor, PHD's, Medical Field, Certification type fields etc. Going to college for any other reason is COMPLETE BULLSHIT! A message to Gen Z, College is a scam, the music industry is dead so do whatever the fuck you want with music because its fun (if you saturate anything it dies) TV is dead so remind your older friends to get rid of that dead ass device in the house or give it a use besides being there for white noise. As far as war goes, our generation will be generals and chiefs etc, DON'T LET OUR GENERATION/GEN Y CHANGE OUR MILITARY STANDARDS! I don't give a shit what they say they feel. Try to keep your families together, our parents were too hopped up on cocain and \textbf{dumb} shit in the 80s and 90s to keep their heads straight so do us all a favor and be better parents for your kids so no one needs to write another angsty bullshit song about how mommy or daddy didn't love them. Go with your gut and be creative, don't let some feggit tell you how to run your own shit. You only live once.....even though I hate that that saying became a meme. Oh and one more thing, Gen Y will soon be in charge of any deep state affairs, hidden projects or global agendas, DO NOT LET THEM GENETICALLY MODIFY, MANIPULATE, PANDER, OR SPEW ANY PROPAGANDA PROMOTING DEGENERACY TO YOU! I mean shit, when we babysat you guys you saw enough disney channel to know whats up, and I assure you, your favorite disney stars from back then aren't going wacko by random chance, we know why dirty \textbf{old} men like harvey weinstein and dirty \textbf{old} disney execs "enjoy" working with little kids so much, try to see past the manipulation that Gen Y had to deal with with our mainstream media etc. Food for thought, the mainstream media fucked up our generation so bad half the mother fuckers left don't have a single thought of their own nor can they function without whining when challenged. Don't censor yourself, and be yourself. Now here's to hoping that you guys can make it through the time space continuum all in once piece in the next few years. You have to....cause your youngest brother/sister/cousin who's like 6 right now is counting on your ass. Oh and 9/11 happened back in 2001 btw, never forget. No matter how tall you build your ego, it can always be torn down.Oh and one more thing, stop dying your hair purple blue green and whatever the fuck, its been a shitty looking fad since the 90s and will continue to make you looke like a low self esteem cock mongler. I would have said autist but..... autistst are usually pretty smart.....\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/517 & \cellcolor{green!5}0.58 \\  \hline
  \cellcolor{green!27}\small Captain Blackeye I was born in 1997 and remember seeing a document on it like in 2002-2003. I don't remember it happening but i saw it a bit later on from tv and all that \textbf{terrorist} talk..\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Caleb Evans Weell you're saying that you see 5 years \textbf{old} kids with phones in their hands,but as I know the youngest from gen z are 12-13 not 5.Second,I was born in 2003 and I didn't have a phone until u turned 13-14 or smth.Honestly,the early 00's kids had a similar childhood as 90's kids\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small scruffyEA \textbf{nigga} what\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Well I am I'm 13 but then z can be up to 7 years to 23 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Leah Tompson inability or unwillingness to learn? Fuck you! What have you learned that we didn't. We're not even 30 yet and still learning life and you guys talking like you're wiser than us and haven't even lived life. Sure most of us still live with our parents in our 20s but at least we know why and have some form of a plan for the future of this country.  Your generation has \textbf{nothing}, does \textbf{nothing} and in no way shape or form has a plan for the future of this country yet you belittle us, a generation of young people who are still trying to figure out life like you Are, how are two young generation really arguing over who's better. Your generation will continue the \textbf{age} \textbf{old} cycle of divide divide divide. All you can see is our differences instead of what makes us the same. Our generation faces the same problems yours does. We're both young insecure and unsure of where our future will lead us.\normalsize   & \cellcolor{green!27}Age, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}4/169 & \cellcolor{green!27}2.367 \\  \hline
  \cellcolor{green!5}\small Well then, they've already failed. Now, I am generation Z, but I like to think I'm not. (I Do things your grandparents would find \textbf{old} fashioned). But yeah, Gen-z has already failed.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Lord Benjen Stark Dude let me break it down. Gen z knows the world is fucked so we kinda live with it while You melenials makes a big deal out of everything and \textbf{freak} out every time  someone does one thing.\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small LazyTownIn2D  If you insist on calling Americans \textbf{fat}, I'll have to recommend you to see a dentist you snobbish brit fuck.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Well.. I mean, America is kinda... Lazy... \textbf{Obese}... Trigglypuff If you know what I'm saying.\normalsize   & \cellcolor{green!27}Obese & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Tony Hardison Why are you so mad? Cant accept that a lot of \textbf{obese} people live in America and that SJW and feminists are pro obesity?\normalsize   & \cellcolor{green!5}Obese & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Sabrina t I'll have to take your word for it, haven't seen evidence of it in my own little corner of the world, and I live in a solid \textbf{r\textbf{ed}} state of the midwest USA but I'm encouraged by the comments.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small swell guy oh shut up. 99' here do I agree that everyone gets offended by everything? Yes , however I still think there needs to be a lot of social reform but crying over social media does \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Saruulbuyan Munkhtur don't say woke you dumbass just say aware or alert. It's not \textbf{weird} to use high quality vocab words. Go for it buddy\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Mental, Crazy, Dumb, Weird, Blind, Lunatic, Freak & \cellcolor{red!27}37 & \cellcolor{red!27}37/42620& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}53 & \cellcolor{red!5}53/42620& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nobody, Nothing, Zero & \cellcolor{red!27}46 & \cellcolor{red!27}46/42620& \cellcolor{red!27}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Woman, Sex, Gender, Sexism & \cellcolor{red!5}11 & \cellcolor{red!5}11/42620& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old, Elder & \cellcolor{red!27}51 & \cellcolor{red!27}51/42620& \cellcolor{red!27}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female age and physical appearance}  & \cellcolor{red!5}Witch & \cellcolor{red!5}2 & \cellcolor{red!5}2/42620& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay, LGBT, Homophobic & \cellcolor{red!27}16 & \cellcolor{red!27}16/42620& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, LGBT, Pansy, Fruit & \cellcolor{red!5}20 & \cellcolor{red!5}20/42620& \cellcolor{red!5}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Transexuality}  & \cellcolor{red!27}LGBT, Transition & \cellcolor{red!27}5 & \cellcolor{red!27}5/42620& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - European or anti-Europeans}  & \cellcolor{red!5}Brexit & \cellcolor{red!5}1 & \cellcolor{red!5}1/42620& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common, Cheesy & \cellcolor{red!27}15 & \cellcolor{red!27}15/42620& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}pussy & \cellcolor{red!5}1 & \cellcolor{red!5}1/42620& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Apple, Red, Indian & \cellcolor{red!27}6 & \cellcolor{red!27}6/42620& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Lump, Fat, Skinny, Obese & \cellcolor{red!5}11 & \cellcolor{red!5}11/42620& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, Nigga, African, Buck & \cellcolor{red!27}10 & \cellcolor{red!27}10/42620& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Race, Racism, Racist, Ethnicity & \cellcolor{red!5}16 & \cellcolor{red!5}16/42620& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Red, Communist, Snowflake, Nazi, Commie, Libtard, Cuckservative & \cellcolor{red!27}17 & \cellcolor{red!27}17/42620& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - General}  & \cellcolor{red!5}Nation, Nationality, Alien & \cellcolor{red!5}4 & \cellcolor{red!5}4/42620& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}THOT & \cellcolor{red!27}1 & \cellcolor{red!27}1/42620& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Terrorist & \cellcolor{red!5}2 & \cellcolor{red!5}2/42620& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Protestant}  & \cellcolor{red!27}Spike & \cellcolor{red!27}1 & \cellcolor{red!27}1/42620& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry & \cellcolor{red!5}3 & \cellcolor{red!5}3/42620& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Destitute}  & \cellcolor{red!27}Underdog & \cellcolor{red!27}1 & \cellcolor{red!27}1/42620& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Southern European}  & \cellcolor{red!5}PIGS & \cellcolor{red!5}1 & \cellcolor{red!5}1/42620& \cellcolor{red!5}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Physical Identity - Physical (and Mental) Impairments;Age - General;Age - Youngsters;Gender - General;Age - Over 65s;Gender - Female age and physical appearance;Sexual Identity - General;Sexual Identity - Male homosexuality;Sexual Identity - Transexuality;Nationality - European or anti-Europeans;Social Class - Working class;Nationality - Chinese;Ethnicity - Native-American;Physical Identity - Physical Features;Ethnicity - Black;Ethnicity - General; Ideological and Political Identity - General;Nationality - General;Gender - Female sexuality;Religious Identity - Muslim;Religious Identity - Protestant;Nationality - German;Social Class - Destitute;Nationality - Southern European;%.

\item The percentage of hate speech related words is 0.7766.

\item Considering that the variable \textbf{Age - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 331/1405 occurences of hate speech related comments.\end{itemize}\end{document}