\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_177.json :}\newline \par\Large\textbf {Title: \large  Generation Z: the second worst generation in history }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Gen z Will be know as the generation of giving the finger to all the \textbf{old} bags\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small surprisingly, Gen Z females worry about \textbf{gender} discrimination hindering their career advancementsurprisingly my ass what the fuck\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small So? Millennials and gen x and baby boomers were just as \textbf{dumb} as us when they were teens. Baby boomers probably called gen x the worst generation. Gen x probably called millennials the worst generation. Now millennials call us the worst generation. We are probably going to call gen alpha the worst generation.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Dude uh we're not even that \textbf{old} yet?? What did we do\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small ummm... arts and humanities aren't pointless my dude... bashing these vocations has \textbf{nothing} to do with bashing gen z anyway\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Baby boomers ruined everything for us probably because of the bad health standards when they grew up damaged their \textbf{mental} capacity\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Bitch what the fuck, first of all what did we even do? we are not even adults yet, lmao. And second of all, this is entirely incorrect, there is a reason why \textbf{old} people lecture younger people. It is because our grandparents grew up in a time where everyone was polluting the entire planet, and not giving a crap about it. The mistakes that they did teaches them wisdom and when they get kids or grandkids, they will teach their mistakes to the younger generation to not make the same mistake and fuck up the whole newer generation that way we wont get a nickname for ourselves. Yet, you a 'Gen Z' is completely trashing our own generation that was meant to be better than our last generations, and you entirely ruin that by giving out reasons why Gen Z is bad, when it was not really the Gen Z's problem, but the generation before them. And to be completely honest, you yourself is ruining our own generation by making people think that this generation sucks. In which I can tell that ‘That' was not your point.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/187 & \cellcolor{green!27}0.535 \\  \hline
  \cellcolor{green!5}\small Yes, us pre-teens who are barely \textbf{old} enough to get a job, are one of the worst generations.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small 1. fuck millennials 2. not all of us are the same that just the mainstream. i hate rap and all that other shit. 3. fuck \textbf{feminazi} im conservative. 4. i barely use my phone\normalsize   & \cellcolor{green!27}Feminazi & \cellcolor{green!27}Gender - Female intelligence & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I agree, Teens today are addicted to \textbf{sex}, video games, drugs, and social media.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Me: Has lots of points to refute the points made in this videoMe, An intellectual gen z: lmao \textbf{old} people amirite\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Extreme debt?? What debt? Most of us aren't even \textbf{old} enough to get jobs???\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The highest \textbf{age} for Gen Z is 23 or 24. You're basically roasting teenagers lol. FYI us gen z-ers hate both boomers and millennials.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Okay listen here you uncultured dumba*s swine. If you had a little bit of a brain, you would realize that most of Gen-Z people are CHILDREN. Literal CHILDREN AND TEENS. How can we be the 2nd worst generation on earth while we're just going through puberty?? Like... I know there are some \textbf{dumb}, uneducated, \textbf{crazy} and whatnot people out there, but you, my dear, DEAR rude shait of a person are one of the worse cases.We are all humans. Gen-Z is the first generation that was most fully born in the modern technological \textbf{age}. We were born when phones were already invented. Who were phones invented by? Baby Boomers! So don't you dare tell me something so rude, SO INSULTING like this! Don't you dare tell me we're bad people, while YOUR generation made us like this! If anything, YOUR generation is more at fault than ours! We didn't CHOOSE to come to life at this \textbf{age}! On the other hand, You guys were the generation that MADE us like this! You're the generation who constantly criticize US for something YOU have caused! Generations BEFORE Millenials and Gen-Z's has caused us to act like we do. If not, then tell me why are most of us younger people unmotivated?? Because people like YOU make us feel like SHAITS!! That's why! I don't want to insult any older generations or any younger generations, unlike this guy. I don't care about what generation you're from, but when you go out and PURPOSELY insult any other human being, that's when you've crossed the line of being a dumbass, to being a literal scum of the earth. So please, for the love of god, go back to playing games in your mom's basement, and shut your dirty ass of a mouth.\normalsize   & \cellcolor{green!5}Age, Crazy, Dumb & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/298 & \cellcolor{green!5}1.342 \\  \hline
  \cellcolor{green!27}\small but who did it to us sir? We are not the worst because we didn't ruin this world. Boomers nowadays are arrogant, annoying parents, truthfully. And millennials are just sad bums now that they're \textbf{old}. Gen Z is paving the way.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small \@Daedric Shinu v2.0 god. Late 30s is \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Not \textbf{old} enough to hold any substantial political power. Most politicians are Baby Boomers and Gen X. Millennials have far less wealth to lobby for their own interests too.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small This is a \textbf{Nazi} propaganda machine made by the Baby Boomers\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Nothing can be worse than Millennials.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Yes, I'm so worried of \textbf{gender} discrimination, naw that's millennials.\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Brayden Nash i wont graduate until 2023 and I'm still considered part of your generation. Sadly, I'm closer to the cringier ones in \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Dont listen to the adults guys! We can pull their life support when they get \textbf{old} and get all that  inheritance and we can pay off our crippling debt\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Oh no. My generation would rather protest for \textbf{gender} equality than live a life of oppression in the work force. HOW WILL THE WORLD COPE.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small oh my gosh im sooo sorry that we all worry about our life and about \textbf{woman} rights, lgbtq and \textbf{racism}, we want to change the world and make it better for next generations ..\normalsize   & \cellcolor{green!5}Racism, Woman & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Chicken Nuggets Are Pretty Good Well, do something better. I have a life, I don't spend all my free time on the internet you \textbf{fat} fuck.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small ratchetandclank2016 Tony Stark haha chill out. I have \textbf{nothing} better to do with my time, and I'm only 120 so how about you fuck yourself instead of calling me a \textbf{fat} bastard\normalsize   & \cellcolor{green!5}Fat, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small At least in this generation there is less \textbf{racism} so let's be thankful for that one. We aren't ashamed of having different skin colors like most were in the early 1900s.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small 1st of all gen z is the youngest that means we haven't really changed the world so u guys pretty much trashed the earth before we came and people will say "kids these days"2nd most of the gen z have even graduated and u already expect the to like run a company and be successful3rd gen z is so new that they blame them for too much gadgets...uhm hello who raised gen z definitely not fellow gen z4th how on earth did u expect teens to have a job thats successful at our young \textbf{age} we actually bring peace\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small This tea is burning hot on one side and lukewarm on the other, \textbf{weird}.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Don't take your news from Big Media.  As far as I know the nerds of this generation are some of the \textbf{r\textbf{ed}} pill to mute.  we HATE pc speech.  and we love the SALT.  Can't be honest or handle honesty, you'll never have true friends who can be honest with you, just as much as you want to be with them, if you can't love the salt or understand a constant underlying caring and affection present for you at all moments even when something may have come off as insulting rather than constructive.  Go F yurself sensitive peoples. Thomas Paine: "He who dares not offend cannot be honest." Now go sulk about how your all alone and I may see you as you cry, but IDCare.  You deserve this for promoting the garbage of "safe speech," you deserve wierdo friends that aren't sincere and won't stick with you, based on your own efforts towards attracting them.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/156 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Gen Z will be worse then Gen Y, X, or boomers. They will be broken, apathetic, and riddled with \textbf{mental} illness. Sorry the hype was a lie.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small 'Gen z worry about \textbf{gender} discrimination' bull shit We are the most anti sensitive generation\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I'm gen Z and none of the females (including me) think that our \textbf{gender} is a factor that will make our future bleak. I am conscious that feminist take it to the extreme and there is no one stopping me at all, my \textbf{gender} is no obstacle whatsoever and other girls my \textbf{age} agree. So it impresses me how you think that gen Z's are all like that.\normalsize   & \cellcolor{green!27}Age, Gender & \cellcolor{green!27}Age - General, Gender - General & \cellcolor{green!27}3/68 & \cellcolor{green!27}4.412 \\  \hline
  \cellcolor{green!5}\small True also the baby boomers which are probably adults now ruined our college and we have to learn Korean i mean not like I hate it but like the baby boomers have no nationality\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@iDon'tCare LOL OK how \textbf{old} are you?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small theresn0limit Typical. You like to prove a point with \textbf{age}. Anyone can be a moron. Cheers.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@iDon'tCare uh? What? Lol all I asked was what your \textbf{age} was why are you all defensive. You gen z kids are all weirdos lmao\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Jeremy Maynard Nah, it's not that. You Gen Z people are all \textbf{weird} as fuck. You are all obsessed with materialistic shit, listen to shitty music, fight all the time over stupid little things (and scream worldstar), and haven't accomplished jack shit. Yall really are failing as a generation lmao\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small theresn0limit If your parents gave you a supercomputer at a young \textbf{age} would you use it? Hell fucking yeah. If you have access to such amazing stuff why not use it?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small theresn0limit whats your \textbf{age} then?\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small 7:24 'Some take it to the extreme with autism' tf is that supposed to mean? Let me just say, if you're like those people who use autism as an insult... honestly just stop. It's not funny and it never will be. Autism is an actual thing and I have a brother with it, and it's difficult for the person who has it, and it takes a large toll on their family and is not something to make fun of. Personally, I love my brother, but living with very strict parents and being given harsh expectations, along with dealing with constant stress and anxiety has taken a large toll on my health both mentally, and emotionally. Before even saying that to try and insult people, do some actual research. Also, as you can obviously see, pretty much \textbf{nobody} likes this video, unless they're another jerk just like you.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/147 & \cellcolor{green!27}0.68 \\  \hline
  \cellcolor{green!5}\small ArcticFoxyFox i absolutely get your arguement, but he wasnt giving autism a bad name on purpose. Its like calling people 'faggots'. Its a stupid and offensive thing to say, but some people say it. Youve gotta just realize that peoples speech on the internet means \textbf{nothing}, and just because he speaks of autism like that doesnt mean that autism is something that should be talked down on. You have every right to defend your brother, but just expect people to give you crap for having sensitivity on it i guess\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small Theres one good thing I can think of with everyone under the \textbf{age} of 40 being fucked.. more community awareness, I can only hope. When everyone older dies or doesn't support us anymore, we'll have to turn to eachother and the best of us better come out then. We're not the guaranteed success stories anymore that older generations were. Of course with some of X not doing well either on the younger end. It will be up to older X either to corral everyone else, or if not, we'll all have to turn to eachother, everyone from 38 to 15 yrs \textbf{old} and then generational lines will be erased and it will just have to end up being the everyone under 40 generation. We'll be like some big merger.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/129 & \cellcolor{green!27}1.55 \\  \hline
  \cellcolor{green!5}\small that feeling when you are Romanian and gen z, when the rest of the youth is drinking themselfs and listening to \textbf{gypsy} musicfeels bad man\normalsize   & \cellcolor{green!5}Gypsy & \cellcolor{green!5}Ethnicity - Roma & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Frog Patriotic way better than what the Americans listen to\normalsize   & \cellcolor{green!27}Frog & \cellcolor{green!27}Nationality - French & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small All generations talk smack about new generations. \textbf{Nothing} new here.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I hate \textbf{skinny} jeans, but I love baggy jeans!\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small I more see the problem with young kids receiving cell phones, my parents entrusted my with mine when I was eleven, because they trusted my responsibility, and I didn't let them down. mfw my six year \textbf{old} cousin had an iPhone X which he only uses to play Minecraft\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small An iPhone what? That's bullshit. Come on, unless he stays home alone everyday why does he need an X at six years \textbf{old}? Parents should set some kind of boundaries..\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small I got a flip phone when i was five and didnt tell anyone because i didnt want to seem like a spoiled \textbf{brat}. I actually used it when i got lost in a park once that year which was pretty noice\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Gen z is super conservative at this point. Only a few (\textbf{mental} ill-ey bois) drink Clorox and eat tide pods.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Soda in a Plastic Bottle true, but there isnt much else to do. 'Ride bikes' with who? Everyone wants to stay indoors and sit still. It sucks dude. Whenever i want to do stuff, its either with my best friend occasionally, or just by myself because \textbf{nobody} ever fucking leaves fortnite.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Not sure because art takes talent, but if you were taking a \textbf{gender} studies course just so that someone doesn't get offended then I would not hesitate to shit on you.\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small You're an IDIOT the onion is a satirical news site. Fake news dummy. Goes to show how \textbf{dumb} your generation is. Thanks.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@im a snacc I mean I'm not blaming it on him, but Millennials have left us Inna dark place constantly hating us for doing \textbf{nothing} wrong w\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Bruh were like this because we realized that no matter what happens \textbf{nothing} will actually change and anytime we want to really change so (like the school system) no one cares because we're just 'kids'\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small We're like this because a wrinkly \textbf{bum} wouldn't fuck off. and let us do our thing in cleaning up his broken glass.\normalsize   & \cellcolor{green!27}Bum & \cellcolor{green!27}Social Class - Destitute & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Huh see that is the WRONG attitude! This is why i hate My generation, most people say that they are "depressed" (lazy and dont want to do anything) and then say that \textbf{nothing} Will change like really?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small We are not all that bad ok. You are telling me you never did anything embarrassing is high school? We have gotten "worse" because the \textbf{old} generation has every "worse" so we invent a new "worse". But don't take it the wrong way the new generation is the most accepting liberal generation, that takes action. We are also the most peaceful generation, yes might Twitter battles but it is not like we are having a whole civil war. The new generation has been known for the young protestors who take action and stand up for things they value okay\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small Fr33 Worker bruh you sound like a briandead \textbf{retard} that plays fortnite for 8 hours straight\normalsize   & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Generations get worse as time goes on. To say the generation before is worse is just not true. Gen Z is a narcissistic collectivist sadistic sociopathic evil generation. They're all having kinky \textbf{sex} at 13 and they're shooting up their schools.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small T R U T H well, about the kinky \textbf{sex} at 13, about a hundred years ago, children could work in harsh factory jobs at thirteen, and the narcissist part I simply don't seem. Sure, they exist. To deny that is foolhardy, but hey, you weren't much better at your \textbf{age}, truth is, all teens suck, no matter what, we just have a bigger platform to show how much we suck\normalsize   & \cellcolor{green!5}Age, Sex & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small Maybe we're this way because people like you constantly put us down. You realize we are the future right? And yes, I understand that in your golden time your elders also put you down and told you that your generation is ruining everything but that is not reason to make a generalization that seems to be doing well seem like shit. \textbf{Nobody} justifies a thirteen year \textbf{old} having kinky \textbf{sex}, but you know your grandma was probably pregnant at fourteen and it was considered a bit late, right? And \textbf{nobody} justifies school shooters, do me a quick favor and reach into your ass so you can pull your head out of it. Don't make some absurd accusation without looking at the slightest chances of being hypocritical.\normalsize   & \cellcolor{green!27}Nobody, Old, Sex & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Gender - General & \cellcolor{green!27}4/126 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small we're not as bad as millenials but we're becomming mindless zombies. I'm a girl and I know for a fact \textbf{gender} discrimination isnt a thing anymore 😑 Everyones a total \textbf{snowflake} who thinks theyre special and r lazy and dont want to work hard for shit. I wish I was a part of gen x like my parents because their generation actually has social skills, they're hardworking and like real Human beings not zombies.\normalsize   & \cellcolor{green!5}Gender, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Gender - General & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small syz·y·gy \textbf{nothing} rly, u can't help it, just try to be better than the sjw's\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Your Probably a triggered 30 year \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Yo mom Is \textbf{g\textbf{ay}} oh a your mom joke, I'm so broken inside and also don't use the word triggered, it makes you sound like a dweeb!\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Yo mom Is \textbf{g\textbf{ay}} aw dang, hella roasts\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@Yo mom Is \textbf{g\textbf{ay}} i bet you think things from 1 second ago are outdated!\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small ​\@Void Master, Man Fuck that. He came at me. Screw that 40 year \textbf{old} \textbf{fat}, League of legends playin' butthole\normalsize   & \cellcolor{green!5}Fat, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical Features & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Yo mom Is \textbf{g\textbf{ay}} 🚫🧢\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Yo mom Is \textbf{g\textbf{ay}} what me ?\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small MyEyesAre OverHereProductions WOW you're really a 30 year \textbf{old} arguing with a child. 'Dweeb'\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Yo mom Is \textbf{g\textbf{ay}} Did you not see the name?\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Thats not how that works. As soon as they are too \textbf{old} to fix it, its our problem. We need to fix it ourselves to take care of gen bravo and gen charlie\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small As one of the oldest gen zers('99) I can be certain we aren't as bad as millennials. While there is a huge dependence on technology, this is technically not a bad thing as we find continuously use the internet to fuel our curiosities. It has been easier than ever to learn a new skill. Also, how can you be certain our jobs opportunities are scarce when the economical state of this country is better than it has been in a \textbf{crazy} long time and our unemployment rate hitting all time lows. How did you make not going to college, but going straight into the workforce to receive and education and job training to avoid debt sound like a bad thing. I am in college right now, however I know plenty of others who opted out and are upward projecting in the workforce."Millennials on steroids" ok, first off we're typically more conservative than millennials. Second off, you're still wrong about this entirely.I expect some shit like "attention span is horrible because if YouTube" and "if technology crashed they wouldn't know what to do". Not some of this ranting bullshit\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/190 & \cellcolor{green!5}0.526 \\  \hline
  \cellcolor{green!27}\small Rhiannon O'Connell wait you feel like wuss is mean? Wow that's amazing I can say you're overly sensitive or crybaby honestly you can't let the 12 year \textbf{old} idiots on the internet bully you it's just sad\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Best because they stare at their phones all day? Best because they'd rather look at social media than hold a conversation with someone else? Best because they'll all be hooking up through tinder with no feelings? Best for being \textbf{promiscuous}?\normalsize   & \cellcolor{green!5}Promiscuous & \cellcolor{green!5}Gender - Female sexuality & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@Soda in a Plastic Bottle Now I don't think gen z is the best but the idea of conversations is kinda \textbf{dumb}. What do you think these people are doing on their phones? It's communicating with friends.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@Soda in a Plastic Bottle Yes actually. Maybe they moved away and you want to keep in touch? Maybe your parents want you to go outside but god forbid you hang out with a friend? Don't be so conservative. And also- someone's \textbf{sex} life is not your business in any way shape or form, regardless of how religious or conservative you are. (edit: I'm still not going to deny some parents justifying it... that's just \textbf{weird})\normalsize   & \cellcolor{green!5}Sex, Weird & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@iDon'tCare I was just trolling and pretending to be one of those conservative hurr de durrs who think the new generations are messed up. But I did see some guy comment on a trailer of a new teenage Netflix show ranting on about how it glorifies immoral behaviour. When I asked him to elaborate on it he said that teenagers having a \textbf{sex} life from 13 is a warped reality and that we are a sick species for us to make it normal and having a show glorify it. If you want to read the thread the link is here. [LINK] \normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/101 & \cellcolor{green!27}0.99 \\  \hline
  \cellcolor{green!5}\small Soda in a Plastic Bottle Thanks will do. (Also I'm not going to deny it's always \textbf{weird} to hear a mom passing her thirteen year \textbf{old} son a condom sometimes..) Edit: I watched 36 seconds... Wtf... I already see where and why you're coming from even from a trolling point of view.\normalsize   & \cellcolor{green!5}Old, Weird & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I think people forgot or get the youngest of gen z is 6 YEARS OLD\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@EvanMindblow That's only the half of gen z who jokes about stuff like that and listens to that but the other half is just like you "I don't do the stuff that they do, It sucks."   And music has always been changing, everyone likes different genres im a \textbf{black} girl who listens to metal, alternative rock, \textbf{old} school rap, hell probably everything. Music is always guna change. Not everyone is exactly the same, cause there's the kids who like fandoms and stuff like fnaf and undertale and they listen to other types of songs. You say that as if everyone is the exact same and you're just this special \textbf{snowflake} out of gen z, we're all special, i don't understand why we're put into different generations anyways. We may not all be the same but we sure as hell are very similar. I could list the "differnt groups" and stuff.  The other generations had their slang too so yeah  - typed by a 13 yo girl wit no life\normalsize   & \cellcolor{green!5}Black, Old, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}3/169 & \cellcolor{green!5}1.775 \\  \hline
  \cellcolor{green!27}\small Sharon Bingham - Fortnite, liberal propaganda in movies and video games, lack of empathy in social dynamics, no social skills, always on their phone putting others in danger around them, their existence contributes to overpopulation, degeneracy, more bullying, sadism both online and in person, \textbf{sexual} deviancy, moral subjectivity and nihilism, being "too smart for your own good", drugs and \textbf{alcohol} death before the \textbf{age} of 18, top consumers in the Xanax and Opioid epidemic further elongating it's lifespan and war on drugs, mischievous anonymous mischief online that's literally causing an entire \textbf{nation} to have a civil war, bullying to a whole new degree of depravity and sadism, mass narcissism and depression and other \textbf{mental} illnesses, liberal anti-white brainwashing candidates (all that propaganda is targeted towards you, the children), terrible computer noise non-music, mumble rap and other simplistic dull minded music, rise in ghetto \textbf{black} culture and influence (every kid talks like they're \textbf{black} saying words like "savage" and "ight" because of all the toxic \textbf{black} culture in their music and social media). There are a million things that are wrong with you little Gen Z tumors and this isn't even 1 of it. If you were born after the year 2000 you shouldn't even be alive. You are the overpopulation we try to avoid.\normalsize   & \cellcolor{green!27}Age, Black, Mental, Nation, Sexual, alcohol & \cellcolor{green!27}Age - General, Behavioural Addiction - Alcohol, Ethnicity - Black, Gender - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}8/214 & \cellcolor{green!27}3.738 \\  \hline
  \cellcolor{green!5}\small \@Ann V. Considering I believe we have may potentially have higher IQ's as said person Ann VYou act like the other generations have never been \textbf{dumb} in their teen years. I hear stories from my parents all the time about the \textbf{dumb} things they do.I'd like evidence on how we're \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/53 & \cellcolor{green!5}5.66 \\  \hline
  \cellcolor{green!27}\small \@T R U T H Overpopulation isn't a thing neither is your IQ.You could easily live off of insects but you're just too damn narcissistic for it, yes?I've seen patterns at this point.Generations that are older are comnonly more narcissistic and care only for themselves. Fortnite is a video game that the generations before MY generation created along with smartphones and among other things. Even tidepods. Now, let's go more into depth.Here is Gen Z/iGen. We were born into a post 9/11 world handed to us by the previous gens.We were born into economic failure and terrorism along with school shootings, in which has influenced us into having \textbf{mental} illnesses. You're not commonly born with \textbf{mental} illnesses you idiot. Your childhood shapes them, and no, we're not narcisstic, you are.I don't believe the more outdated gens had to have a lockdown for school shootings, yes?Among last year there were mass shootings aka almost one shooting per week.Now, you can't blame us as we're still children.I don't believe your generation left a huge mark on America between the ages of 20 and 13.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/191 & \cellcolor{green!27}1.047 \\  \hline
  \cellcolor{green!5}\small \@T R U T H I also don't see how music makes up anything.Music is music.Just because we don't like your country music doesn't mean we have tumours =)At the same time, \textbf{black} culture isn't all that bad, now is it?I see it, you're a mere narcisstic disgusting \textbf{racist}, no?\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small RG Ghoulx - You act like you know me. "Your generation" "Your country music" I hate country music stfu and stop assuming you \textbf{dumb} kid.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@LordDanko Lol you just admitted you were a kid \textbf{nothing} you say is valid\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@T R U T H Evil cancer?Oh lord you need morality checks.Negroid music?So, basically you're a \textbf{racist} \textbf{fat} cunt?Also, not all the music I listen to is made on a computer dumbass nor is it all violent.Also, I don't see what's wrong with our music.Give me something other than "Vioolent intentions" because from what I've seen thus far is not all of Gen Z listens to \textbf{african} cultured music.As a matter of fact, you listen to pop, yes?High tier narcisstic music for the privileged.Makes no sense.Quite franklyI have justified my Generation being "Evil Cancer"Your generation and the generation before are the ones who made the United States like this, in which, you're also the ones who have started recent wars and are the rooted problem of this world?See how \textbf{dumb} you've been sounding. You're literally acting like \textbf{black} culture is impure, whilst you never said how it's impure."Negroid music" are you fucking joking? You ignorant ass people don't deserve anything people have put down for your narcisstic ass.\normalsize   & \cellcolor{green!27}African, Black, Dumb, Fat, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!27}5/182 & \cellcolor{green!27}2.747 \\  \hline
  \cellcolor{green!5}\small \@Inno Noctis just ignore it, its basically just another triggered \textbf{snowflake} who lost a battle in fortnite, since fortnite is the only game this guy said as an argument for us gen z's, like seriously, we are just growing up and many hate us, people like gen x and baby boomers are so hippies, i  guess this guy must be a liberal gen x or millenial\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small im a snacc you're probably eight years \textbf{old} with that profile picture and username.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Cult Leader Greg this \textbf{nigga}.\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@T R U T H  stfu dont talk trash my generation we ARE NOT PIECE OF GARBAGE. WRE YOUNG AND \textbf{DUMB}. WE WILL EVENTUALLY GROW \textbf{OLD} AND MATURE. YALL OLDHEAD SEEM TO FORGET YALL WERE AT THIS STAGE AT ONE POINT.🤡🤡🤡🤡🤡🤡\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small We don't worry about how \textbf{gender} discrimination will affect us, we worry about how SJWs and flipping feminists will ruin America and the world. Like, mah dude, wat you thinkin we worried about?\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small The big gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small janedoe well, thats pretty much \textbf{common} sense. Almost all specs are better than smartphones on any decent pc\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I LOVE THE FUCKING ONION\textbf{black} guy asks \textbf{nation} for change headlines 2012tired \textbf{nation} declares its trying ok headlines 2014memorial built for eminent disaster headlines 2015\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small Well, you're not a special \textbf{snowflake}.\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small You kids give me hope.  Please end the reign of these bullshit virus signaling millennials with your \textbf{common} sense, savings and more traditional values.  They were the worst thing since baby boomers.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@Madi Mucha yeah. Millenials try to make the world better by trying to make everyone a pussy\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@[Humanations Falling] Do you really think you develop major life qualities at 5 years of \textbf{age}?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Slu p4life we'll be legally adults very soon. Most of us already have jobs by the \textbf{age} of 14. We're building ourself up to adult level. And you'd be surprised what teens can do.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small IKR Being a gen z sucks your live in a world that is dying because \textbf{nobody} cared for it, natzis are back, we have a \textbf{racist} and sexist president (if you live in America) , minimum wage is to low, the cost for college, a simple home or even groceries are to high, everyone has depression or suicidal thoughts even as low as 9 years \textbf{old}, and everyone thinks you eat Tidepods and love Jake/Logan Paul, and \textbf{nobody} thinks you have an option or can think for themselves.\normalsize   & \cellcolor{green!27}Nobody, Old, Racist & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - General & \cellcolor{green!27}4/88 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Felisha Wagaga Gawww damn you are \textbf{dumb}. Gen z overwhelmingly supports Trump cause he is for us! No one is sexist the only \textbf{racist} fucks are you stupid ass liberals.\normalsize   & \cellcolor{green!5}Dumb, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Jesse martes Our Earth is quite literally dying because of fossil fuel use, our oceans are polluted with plastic, moronic leaders are taking charge, U.S economy is getting f*****, college debt is increasing, taxes, minimum wage is decreasing, a majority of all malls and stores are closing, and SO much more. Our Earth isn't even making progress, and we've gotten so far into pollution that there's \textbf{nothing} we can even do anymore. We're all screwed.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Slu p4life calm yo titties \textbf{fat} fuck\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Utopia Ethiopia why the fuck are you in the internet if you're 10 years old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small For people trashing this kid- Maturity does not depend on \textbf{age}, but experience. If someone is 10 but goes through a lot, they can be as mature as someone twice their \textbf{age}, and vice versa. -A member of gen z\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The Controller what 10 years \textbf{old}?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Slu p4life dude. Not everyone is a \textbf{fat} ass. Ive spent a decent chunk of my life in front of screens and I'm underweight(sort of)\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Being conservative is what killed this country, you will find out what happens when playing with fire. Second, learn grammar for 'the most educated gen' you idiots clearly fail to understand grammar and shit. Listen, in the end you will make the rich, richer and take away and viability anyone who isn't white or rich to have any opertunity at life. You have killed everything that I liked and in short I am waiting for the Reich to take me away and put me in a camp while you idiots type away about how 'your teh smurts on your shitty iPhones made by poor people in a third world country.' Yeah I am an SJW guess what fuckwad? If my gen wasn't out fighting the fascists right now you'd be dead. Oh but tell me how smart and unique you're. Gen X made you stupid, my gen is fucking doing something. No how's about you go make fun of some \textbf{black} guy who is into anime cause ' he ain't white enough and traitor to America'  just to fill that empty void you call a life.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/186 & \cellcolor{green!27}0.538 \\  \hline
  \cellcolor{green!5}\small Silent Anon Liberals are a disease bud. From gen z generation! No such things as facist in America. Only the \textbf{communist} fucks like you. So go fuck yourself little sjw\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small The Controller 'Being conservative is what killed this country,' says the \textbf{communist} SJW. Thanks for the advice lmao. Gen Z is gonna wipe out whatever hope you had of a socialist America. Go read a history book and learn something about this country\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small The Controller i like how you put up the most fucking ANNOYING ASS comment, and then are too much of a \textbf{pussy} to reply to anyone disagreeing with you. I would actually like to slap some sense into you\normalsize   & \cellcolor{green!5}pussy & \cellcolor{green!5}Nationality - Chinese & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Luigis Kids these days are stupid, all of our women are sluts, all of our boys will never be men, and everyone is turning \textbf{black}, I swear.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old & \cellcolor{red!27}29 & \cellcolor{red!27}29/16024& \cellcolor{red!27}0.18 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Gender, Sex, Woman, Sexual & \cellcolor{red!5}17 & \cellcolor{red!5}17/16024& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Dumb, Mental, Crazy, Weird, Retard & \cellcolor{red!27}24 & \cellcolor{red!27}24/16024& \cellcolor{red!27}0.15 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Brat & \cellcolor{red!5}18 & \cellcolor{red!5}18/16024& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female intelligence}  & \cellcolor{red!27}Feminazi & \cellcolor{red!27}1 & \cellcolor{red!27}1/16024& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}17 & \cellcolor{red!5}17/16024& \cellcolor{red!5}0.11 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity - General}  & \cellcolor{red!27}Nazi, Red, Snowflake, Communist & \cellcolor{red!27}8 & \cellcolor{red!27}8/16024& \cellcolor{red!27}0.05 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - General}  & \cellcolor{red!5}Racism, Racist & \cellcolor{red!5}6 & \cellcolor{red!5}6/16024& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Fat, Skinny & \cellcolor{red!27}7 & \cellcolor{red!27}7/16024& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Red & \cellcolor{red!5}1 & \cellcolor{red!5}1/16024& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationality, Nation & \cellcolor{red!27}4 & \cellcolor{red!27}4/16024& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Roma}  & \cellcolor{red!5}Gypsy & \cellcolor{red!5}1 & \cellcolor{red!5}1/16024& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - French}  & \cellcolor{red!27}Frog & \cellcolor{red!27}1 & \cellcolor{red!27}1/16024& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Destitute}  & \cellcolor{red!5}Bum & \cellcolor{red!5}1 & \cellcolor{red!5}1/16024& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay & \cellcolor{red!27}7 & \cellcolor{red!27}7/16024& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay & \cellcolor{red!5}7 & \cellcolor{red!5}7/16024& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Promiscuous & \cellcolor{red!27}1 & \cellcolor{red!27}1/16024& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Black}  & \cellcolor{red!5}Black, African, Nigga & \cellcolor{red!5}11 & \cellcolor{red!5}11/16024& \cellcolor{red!5}0.06999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}1 & \cellcolor{red!27}1/16024& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common & \cellcolor{red!5}2 & \cellcolor{red!5}2/16024& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}pussy & \cellcolor{red!27}2 & \cellcolor{red!27}2/16024& \cellcolor{red!27}0.01 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - Over 65s;Gender - General;Physical Identity - Physical (and Mental) Impairments;Age - Youngsters;Gender - Female intelligence;Age - General; Ideological and Political Identity - General;Ethnicity - General;Physical Identity - Physical Features;Ethnicity - Native-American;Nationality - General;Ethnicity - Roma;Nationality - French;Social Class - Destitute;Sexual Identity - General;Sexual Identity - Male homosexuality;Gender - Female sexuality;Ethnicity - Black;Behavioural Addiction - Alcohol;Social Class - Working class;Nationality - Chinese;%.

\item The percentage of hate speech related words is 1.0359.

\item Considering that the variable \textbf{Age - Over 65s} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 166/680 occurences of hate speech related comments.\end{itemize}\end{document}