\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_189.json :}\newline \par\Large\textbf {Title: \large  Young Women Discriminated Against? }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small I do see their point, but being young doesn't mean your wrong in what you are saying. In addition, I don't think being \textbf{old} means you know much. I know a lot of people 20 years + older than me who don't know a god damn thing.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small To the female spokeswomen:(Yes, you're still a moron.)     I was sincerely perturbed that no evidence was given to support this strong claim of yours that young women "Don't know shit". I was also disappointed to hear you say that in regards to stylistically expressing ourselves as a professional "You can't win". Lastly, what point do you make when you attempt to advise Maddy, and the rest of us, to take \textbf{age} discrimination as constructive criticism and move on? Where is there to move.    Let's put this in another light: Would you give similar advice to a \textbf{black} man who has been rejected for this position?\normalsize   & \cellcolor{green!5}Age, Black & \cellcolor{green!5}Age - General, Ethnicity - Black & \cellcolor{green!5}2/106 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small People are individuals and making generalizations is just ignorant. I didn't have to work as hard in school because I could cheat on my homework using the internet? I never did that. And I was never allowed to use a calculator during a test. You're just assuming that older people work harder with no facts to back that claim up. People should be judged based on who they are not how \textbf{old} they are. The original video isn't even about work ethic, its about the general value of a person's opinions.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small If you always demand people with the same worldly experience and \textbf{age} you will never get a fresh perspective on things. You can learn something totally new from a small child, wisdom usually comes from the most unexpected places.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small I wouldn't say "more likely". I'd probably say less likely if forced to make a sweeping generalization. My point was that it (the quality of a person's thoughts) is simply not something you can know ahead of time based merely on \textbf{age}.I suspect that, for pure \textbf{mental} powers, people probably peak in their early twenties and then gradually decline through adulthood. But that is gradual, and experience counts for a lot. I suspect heuristics increasing replace "thought" with \textbf{age} - with mixed results.\normalsize   & \cellcolor{green!27}Age, Mental & \cellcolor{green!27}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/84 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Think of it like this, if I was to write an article about space and the beginning of the universe and I was saying that the big bang theory is wrong or that God didn't create the earth in seven days. Would you criticize me because I'm only eighteen and am too young to know anything because I am immature or because I am simply wrong about my idea. \textbf{Age} discrimination shouldn't exist, \textbf{age} has \textbf{nothing} to do with knowledge nor does it have to do with credibility, if they are correct en there \textbf{age} won\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}4/96 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small If I say something that is invalid I want to be told why it is invalid. Not just be shrugged of and told I'm too young. My experience with people who say, "You're too young to understand what your talking about," is that they just aren't intelligent or articulate enough to tell me what it is I am "misunderstanding."Don't tell someone, "You're too young." It's condescending, and to assume that \textbf{age} is really the route of their problem is to not bother to understand the person.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}\small I absolutely disagree with Ana, not all teenagers think they know it all, apparently she did though.  I agree that with \textbf{age} you become more mature, although \textbf{age} doesn't define knowledge or maturity, I have met adults that are about as mature as a 12 year \textbf{old}.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/47 & \cellcolor{green!5}6.383 \\  \hline
  \cellcolor{green!27}\small I am pretty sure a 26 year \textbf{old} Einstein was smarter than the 40 year olds at the time by a whole lot more\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Kindergarten kids are not as knowledgeable as junior high students. That is the same idea and yet I don't think many people would flip out about it.You do gain knowledge as the years go by. There is \textbf{nothing} wrong with you and \textbf{nobody} said there is. Someday you will look back and realize how much more you know than you do right now.Just ask your older family members and I'm sure they can relate.\normalsize   & \cellcolor{green!5}Nobody, Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/76 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small There is an active and obvious disparity between the discrimination that men face versus the discrimination that women face. It's not rocket science unless you live under a rock or perhaps grew up heavily indoctrinated in a religion that teaches \textbf{sexism} as a good thing.\normalsize   & \cellcolor{green!27}Sexism & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Well it's pretty simple if you have active brain cells1. The video is from a \textbf{woman}. Shocking that they would talk about the person who made the video's personal experience.2. The male on the show says he notices it more for women than for men, and in his experience he has seen more \textbf{age} discrimination in women than he has for himself or other men.\normalsize   & \cellcolor{green!5}Age, Woman & \cellcolor{green!5}Age - General, Gender - General & \cellcolor{green!5}2/67 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small A huge majority of young people are like that. I can't think of even one of my friends that hasn't completely changed in the past 10 years of growing up, even though we thought we knew everything about everything. If you're currently young you have no idea how much knowledge and just \textbf{common} sense you will gain in the next few years so it's impossible to realize that you don't know half as much as you think you do.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Who said you live under a rock? People who create/moderate websites probably don't want to deal with backlash from parents or "family groups" if thirteen year olds are viewing content that isn't exactly appropriate for their \textbf{age}. Just like a porn shop isn't going to let you in just because you are mature, neither will every website.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small I am thirteen years \textbf{old}, and let me tell you, just stating that has gotten me kicked off a few sites. I hate that being older apparently makes you all-knowing and understanding, but while obviously it does mean you're more mature and more likely to understand some issues, it doesn't mean that a certain person is a complete idiot who has lived their whole life under a rock for being thirteen. Just sayin'.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small I'm totally feeling this topic. I am subject to \textbf{age} discrimination on a daily basis. Im a 20-something female in the medical field and i get ''abuse'' and comments from my patients all the time, telling me i know \textbf{nothing} and i dont know what i'm talking about, and that i should get a ''more experienced'' person come in for a second opinion. It gets on my nerves like no other.\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small I guess I'm one of the few people that don't associate \textbf{age} discrimination with \textbf{senior} citizens when I first hear the phrase. When I hear the word \textbf{age} discrimination, I associate it with how older people treat me, along with many people I know, have some type of \textbf{mental} illness because we are young. They only go off of \textbf{age} and assume we can't do anything because they know some kids who have participated in various illegal activities and act like they were raised in a barn. It gets really annoying.\normalsize   & \cellcolor{green!27}Age, Mental, Senior & \cellcolor{green!27}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/91 & \cellcolor{green!27}5.495 \\  \hline
  \cellcolor{green!5}\small Dude, when was the last time you heard that? That distinction of "women and children killed" is almost exclusively used in wartime situations because we assume that they weren't combatants or soldiers. Enemy casualties don't matter.That's an \textbf{old} convention, what does it have to do with this video or feminism?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small age is \textbf{nothing}! some of us like myself have life experiences because we had to grew up fast and moved around the world\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small both men and women get \textbf{age} discriminated. why is it a female issue?? smh\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small way to prove the point that \textbf{age} discrimination is a very real thing.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Stuff the assignment desk gives me. Relationship stuff, internet safety- \textbf{common} sense stuff.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small "Men and women make 25 work-life choices that actually create a wage gap. Men make decisions that result in their making more money. On the other hand, women make decisions that earn them better lives (e.g., more family and friend time).""Women actually earn more... Among workers who have never been married and never had children, women earn 117 of what men do. (This factors in education, hours worked and \textbf{age}.)" - Dr. Warren Farrell, *Why Men Earn More*\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small Hmmm. Looking at this again, I don't think that you were very fair. I was never claiming that I knew 'everything', or that at 20 I even knew 'a lot' (compared to many decades older). I was merely stating that for the one article they picked up on, \textbf{age} was not a negative issue, yet someone picked up on it. If anything in the article, I was still claiming ignorance on more 'adult' issues, like having affairs. You snipped parts of the video out.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small Is not about how fast you processing the data is about how much data you have to process to get to a conclusion. The more data you have to process and analyze the closer you will get to the truth. And in general younger people have less data sets than older people that is why older people tend to disrespect their input. But if you just want to talk about pure \textbf{mental} abilities, why not, you are probably smarter when you were 16-17.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small But Anna you just proved that \textbf{Age} doesn't matter because no matter how \textbf{old} you are you have a high probability to being a moron. Secondly Most people learn by doing.So giving a young person the opportunity early means they will be less of a "moron"later. The internship idea is based on this principle.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small I've had difficulty with \textbf{age} discrimination in the workplace. I'm nearly 27 and I look 16. I've tried changing my wardrobe, name, haircut, makeup and even changes to my demeanor. So, I somewhat understand the girls frustration. It's hard to get people to take you seriously as a professional when they still think your green behind the ears.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small I never heard about \textbf{age} discrimination before now.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Professional discrimination still exists when particularly sexist people end up at the top of workplace hierarchies, but like you said, this doesn't seem to be very \textbf{common}. To my knowledge, most of the "superficial statistics" (pay gap) is due to societal \textbf{gender} profiling as opposed to workplace discrimination - once women have kids they tend to work/earn less. In a lot of ways, this is still an example of discrimination, but not of the professional sort.\normalsize   & \cellcolor{green!27}Common, Gender & \cellcolor{green!27}Gender - General, Social Class - Working class & \cellcolor{green!27}2/76 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Gender discrimination goes both ways, particularly among the youth, in this case the \textbf{woman} is being discriminated against but in many local business' near my universities only women are hired for customer service, front of house, receptionist jobs etc as the managers want a pretty  face for all those pervy men they serve... which really hinders many male college students financial situations.\normalsize   & \cellcolor{green!5}Gender, Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small It is, in fact, hard to tell. Too hard for you, clearly. That's why there are peer reviewed papers, (as in, research by people, of both genders, who have done a proper and thorough analysis), and they prove the difference is societal and that there are no differences in \textbf{mental} ability. Show me real evidence and I'll believe you, but right now it looks exactly like you're making shit up.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Even if that were true, and of every 101 "good things" done, only one was achieved by a female - does that make her dumber than all the males, because there's one of her and 100 of them? No, it doesn't.More importantly, that claim is statistically incorrect anyway, and the imbalance that does exist is correcting itself over time, which suggests that the difference is mostly the product of societal discrimination. Discrimination from people who are actually \textbf{dumb}, like you.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Personally, I think the only time it's okay to make this kind of '\textbf{age} discrimination' such an overwhelming factor in determining who gets employed or not is when the person is, perhaps, maybe 19 or 18 and below. Otherwise, \textbf{age} really is just a number, making it a lesser factor than experience, education, references, etc, etc. It's a little more complicated than just 'they're right', Ana. I mean, do you know just by Maddy's \textbf{age} what her experience, education, references, etc, are like?\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small the third nobel prize went to a \textbf{woman}..awarded by a board of men....kinda disproves your theory that women have been discriminated against.Men recognise talent when it is apparent.And with an increase in female college places..etc..and all that shit..its still males leading the field in computer science, business,math, physics..etc\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small One thing that's soo annoying about trying to get a job based on experience, either work experience or general life experience... is that how is a young person expected to get any if \textbf{nobody} gives them a chance to gain experience..... I know lucky ones have family connections but I don't and I know many others don't either.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small You may be able to argue that females have not had documented cases of great accomplishments, but that in no way mirrors their actual ability. Women are equally intelligent as men in every way imaginable. I would not say the \textbf{sex} as a whole is more intelligent than the male \textbf{sex} as a whole, but there have certainly be individuals of each that have risen high above average.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Age is a poor test of ability, they dont inculded people who have been on their own at a young \textbf{age}, they learned how to adapt to world more quicklly than some 30 year olds and thats cause they had no support. they did that on their own. while i respect Ann she forgot to consider those who had to endure those kind of harships.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small How do you get experience if you get shut off at every corner? \textbf{Age} is just a number, experiences are just a variable.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Yeah, because Marie Curie's discoveries totally didn't deserve two nobel prizes in science, and Jane Austen's literature is just that widely read because she had \textbf{zero} intelligent things to say. To cut a long story short, you don't have intelligent opinions. You're \textbf{dumb} compared to everyone (including girls). Go back to school.\normalsize   & \cellcolor{green!27}Dumb, Zero & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/52 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Ana's getting \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small im in my mid twenties but I would say I was smarter when I was about 16-17...thats when I was at my smartest.you actually get dumber/slower as you \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small females dont have intelligent opinions..ever..girls are \textbf{dumb} compared to boys.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small The older you get the more likely for you to realize your "\textbf{dumb}"...most 20 year \textbf{old} have no idea that they are \textbf{dumb}/moron which is a bigger problem than actually being a \textbf{dumb} ass moron\normalsize   & \cellcolor{green!27}Dumb, Old & \cellcolor{green!27}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small When Sarah Palin becomes President, she will make it a federal crime for men to discriminate against women, especially young women. Women are the SUPERIOR \textbf{gender} and are the \textbf{GENDER} of GOD!\normalsize   & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Ana is really \textbf{dumb}..women get in the news for being pretty/showing skin/tits and sometiems get the job above more qualified men.I mean..Ana was actually picked for her looks on young turks..not her knowledge.Same with all the other girls on TYT....But if I wanna hear an intelligent input/discussion I listen to what Cenk or the other guys has to say.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small So just because Ana is dumb/moron...does that mean every 20 year \textbf{old} is dumb/moron.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Baaaad freeze.And I know that, Anna, but I was giving an account of something. I thought it was unfair that they only commented on \textbf{age}.Thanks for the feedback :DXx\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Why do you think you have to be a certain \textbf{age} to run for political office or for presidency...\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small People get very defensive when you are perceived to be attacking their group. Hence the comments below which criticise Ana for her views.However, she is 100 right. Ana didn't deny that \textbf{age} discrimination exists, just that it was right in some instances. Discrimination against \textbf{old} people is more discrimination against the attributes they tend to have (e.g. less willing to change, more likely to challenge their boss). I honestly don't see that as a problem.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/76 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small "Don't argue with stupid people. They bring you down to their level and slap you with their experience."  Stupid people tend to force the connection between intelligence/knowledge with experience.  They feel that because they are older and had more experiences, that they are smarter. It's called research. I haven't had kids and I know how to raise one, based on the examples that I have seen.  I hadn't had \textbf{sex} when I was younger and I knew how to protect myself.Didn't need to get an STD to learn.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}\small Yet its usually younger people who come up with the most innovative ideas because they haven't become steeped in "experience" and jaded by \textbf{age}, because they don't automatically assume that's "how things work"\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Younger people do have valuable things to contribute to the discussion, but there are times when they don't have the experience to realize it when their ideas aren't practical or have the knowledge to know that their "new idea" is actually \textbf{old} and has been tried and doesn't work.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Age counts for \textbf{nothing} if you waste the time you've lived through. The worst argument against an idea is targeted at the person presenting it, and there's no more blatant example of such an argument than criticizing the \textbf{age} of the presenter. If you disagree with a statement or believe its wrong you make your own case for WHY it is wrong.\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}3/62 & \cellcolor{green!27}4.839 \\  \hline
  \cellcolor{green!5}\small I know a 13 year \textbf{old} who knows more about how the world works than almost anyone I've ever met. Just because you were \textbf{dumb}, doesn't mean you should say all young people are.\normalsize   & \cellcolor{green!5}Dumb, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small I do a Youth Legislature thing where we take over the capitol building for a week. Someone proposed a splendid bill that would require driving tests every 2 years for people over 75. This 55 year \textbf{old} was loudly complaining how it was "\textbf{age} discrimination". Pissed me off. 15 year olds can't drive, but if a 75 year \textbf{old} man develops a neurological condition we have to wait 5 years to find out? BULLSHIT!\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/74 & \cellcolor{green!27}4.054 \\  \hline
  \cellcolor{green!5}\small I was discriminated against. I went to \textbf{Apple} and told them I could run their company but they were like "you don't have enough experience" and I said "Thats experience discrimination you ass!". Corporate bastards...\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Ana I'm disappointed.\textbf{age} is irreverent,you should only judge by there action.if I'm debating a 13 year \textbf{old} and they make a point I'm not going to brush it off thinking oh your only 13.that's disrespectful.you should always treat people equally and give every1 the same chance,\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Most USA politicians aren't able to differentiate an \textbf{apple} from an orange.. so maybe your brother is slightly above retardation?\normalsize   & \cellcolor{green!5}Apple & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small It is not a question of what you know. It is having an opinion on issue of the day, and an \textbf{old} opinion is no more valid than a young opinion. Frequently \textbf{old} opinions are jaded \& corrupt. They are self-serving. Young people can be more idealistic. They want the world the way it SHOULD be, \& that is how we make progress in the world. How about we send all these mature war creators to fight the next war, \& leave young people at home to run things. How do you imagine that war would go?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/97 & \cellcolor{green!27}2.062 \\  \hline
  \cellcolor{green!5}\small wow anna. the fact that you said that just shows your lack of maturity. Being well-seasoned and mature doesn't come with \textbf{age}. However, it's true that most young people are ignorant. But just because you've never tunneled out of North Korea, doesn't mean you can't empathize. Just because you've never begged for a meal, doesn't mean you can't understand. Clearly, you don't get what the girl in the video said. Instead of making an outright judgement, actually try to understand her problem.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small In vegas everyone is discriminated against.... unless your a young \textbf{woman}....\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small To be honest at 20, I've learned to humble myself, and learned over the past few years that it's true, at this \textbf{age} you really don't know much. No matter how intelligent you want to convince yourself you are; most people try to tell themselves they're a "special case" or they're different, but no, just no. I've learned that while I may know a bit for my \textbf{age} (I would like to think so, probably not), I have a lot to still learn, so I actually listen to what older people have to say to me.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}2/96 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small The "Young people don't know anything" attitude is BS. Some people are just naturally gifted on certain fields. They can form a deeper understanding of a topic much faster than others. \textbf{Age} doesn't make up stupidity.Ana, that feeling that things that you said in the past where moronic never leaves you. "Hind sight is always 20/20." It doesn't mean that you get smarter with \textbf{age}. It just means that you make mistakes just like everyone else. You will realize that when you look back at this video.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}2/88 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small I'm 19 years \textbf{old} and i don't think i know everything lol... who actually thinks that?\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I wouldn't specifically call lack of experience to be \textbf{age} discrimination!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small There is another interesting issue about this girl's statement. When people commented on her lack of experience, first thing that came to her mind was discrimination based on her \textbf{age} and \textbf{gender}, though it was obvious from the beginning that they're right - \textbf{nobody} cares about your opinion when you're 20. So maybe TYT should cover this issue: that some people are too eager to cry "discrimination" when someone dares to disagree with them. Cause in this case - this issue is very apparent.\normalsize   & \cellcolor{green!5}Age, Gender, Nobody & \cellcolor{green!5}Age - General, Age - Youngsters, Gender - General & \cellcolor{green!5}3/84 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Try having an intelligent conversation with a 17yr \textbf{old} girl \& then we'll talk about \textbf{age} discrimination. The new hostess at my 2nd job (waiter) has only been working for a whole 2 days, but apparently, the bitch already knows everything.........\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Age discrimination is perfectly legal unless the target is 40+.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I thought Anas advice was not very helpful at all. It sounded like she validated criticising someone based on their \textbf{age} and not on what they bring to the table in terms of a product, idea, etc. Taking criticism based on your \textbf{age} is never constructive, if someone says something stupid, it's because they dont understand what they're talking about. It's got \textbf{nothing} to do with \textbf{age}, someone who is 18 can be just as ignorant as someone who is 80. Or they could be less ignorant, \textbf{nothing} to do with \textbf{age}.\normalsize   & \cellcolor{green!27}Age, Nothing & \cellcolor{green!27}Age - General, Age - Youngsters & \cellcolor{green!27}6/92 & \cellcolor{green!27}6.522 \\  \hline
  \cellcolor{green!5}\small Ana you assume everyone was as stupid as you at a young age\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I agree to be honest alot of time older people just think that younger people dont know anything (sometimes its true) and younger people find older people annoying.. that cna easily be mistaken for ageism\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small It's true. I only target young women when I am looking for a \textbf{sex} picnic. I discriminate againt young women all the time, I only hit on them and only flirt with them. It's disgusting.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Old, Senior & \cellcolor{red!27}21 & \cellcolor{red!27}21/6751& \cellcolor{red!27}0.31 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age, Ageism & \cellcolor{red!5}53 & \cellcolor{red!5}53/6751& \cellcolor{red!5}0.79 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black & \cellcolor{red!27}1 & \cellcolor{red!27}1/6751& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Mental, Dumb & \cellcolor{red!5}11 & \cellcolor{red!5}11/6751& \cellcolor{red!5}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Nobody, Zero & \cellcolor{red!27}11 & \cellcolor{red!27}11/6751& \cellcolor{red!27}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Sexism, Woman, Gender, Sex & \cellcolor{red!5}14 & \cellcolor{red!5}14/6751& \cellcolor{red!5}0.21 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}3 & \cellcolor{red!27}3/6751& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Apple & \cellcolor{red!5}2 & \cellcolor{red!5}2/6751& \cellcolor{red!5}0.03 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - Over 65s;Age - General;Ethnicity - Black;Physical Identity - Physical (and Mental) Impairments;Age - Youngsters;Gender - General;Social Class - Working class;Ethnicity - Native-American;%.

\item The percentage of hate speech related words is 1.7183.

\item Considering that the variable \textbf{Age - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 116/178 occurences of hate speech related comments.\end{itemize}\end{document}