\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_158.json :}\newline \par\Large\textbf {Title: \large  Frugal's Take 096: Ageism and YouTube }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Are you familiar with the sci-fi novel (or 70s-era movie) "Logan's Run?" I have no idea who the hell made this rule, but in IT, after \textbf{age} 22 your life-clock crystal starts blinking for Last Day. It's sad, but I've seen many comments by aspiring coders (and other IT disciplines) who say, "I'm 22 but feel bad because Linus Torvalds started programming at \textbf{age} 10, do you think it's too late for me to become a programmer?" LOL?I enjoy seeing diversity in the IT sector of YouTube, regardless of \textbf{age}.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/91 & \cellcolor{green!27}3.297 \\  \hline
  \cellcolor{green!5}\small I just discover your videos today and been watching them all day long. I'll be 57yo in December and was always thinking about how 'different' I'm from other people my \textbf{age}. Playing and modding Fallout4 or Skyrim, listening to and watching Rammstein or Judas Priest, trying to produce some music on my DAW etc etc..... and I'm PC guy too - since DOS and Win3.1. So happy to finally get in 'touch' with a guy like you. Currently on disability due  to cancer, COPD and other 'crap', but feel the same way as you - inside I'm still in my 20's - ha ha. Thank you soooo much for what you doing !!!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small I'm not quite \textbf{old} enough to experience blatant \textbf{ageism} yet, but it is a real thing, and it's unnecessary. I won't tolerate \textbf{ageism}, and neither should you.\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}3/27 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small We see the same kind of discrimination over here in South Africa too. Discovered your channel while searching for Xenyx desk setups. To be honest, I initially thought "What is this \textbf{old} guy going to teach me?"Turns out you know more than I do, so now I'm subscribing to your channel.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small "to those who are Genuinely Interested" < I wish there were more people that were actually like that on YouTube. Also, you "admire and respect young people and how they embrace technology in their lives?" I don't know about being admired and respected for, say, going to an online school for some of my schoolwork.It's interesting how you are right, because I don't think I've heard much about any amount (even 0.1) of \textbf{age} discrimination for a while, and I think it's something I could improve on at least a bit. Thank you for making this video.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small Hey Bruce. I am 65 years young. OK Sometimes I feel it in my body. I, however,  possess an analytical ability which I witnessed recently when helping my 13 year \textbf{old} solve a problem with a video program. I do observe that he normally catches on very quickly on how to use the program but my ability to solve and analyze is by no means diminished. In fact my analytical ability is strong. Apart from some body pain I don't think I am \textbf{old}, even using the word "\textbf{old}" strikes me as odd. So keep up the good work and keep spreading the good words and information.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}3/107 & \cellcolor{green!5}2.804 \\  \hline
  \cellcolor{green!27}\small Great Video Bruce. I am 70 . . . you are just a young pup. I think keeping up with tech has kept my mind younger and sharper than it would be otherwise. When you are young you think you know everything and as you \textbf{age} you realize that you didn't know anything afterall. It's always been that way...\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}\small awesome  video   \textbf{age} is  just   number   thank you\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small When I was in my twenties fifty seven was \textbf{old}. Now that I'm forty four? Not so much. When I was seven or eight, I thought people in their teens and twenties were \textbf{old}. It's all relative.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/37 & \cellcolor{green!27}5.405 \\  \hline
  \cellcolor{green!5}\small The youngsters today have no idea what awaits them Bruce... Just like we did not have a clue! At 53 \textbf{age}, but 16 year mentality... I love how youngsters now look at me as though I have not got a clue... (ok that may be accurate...) yet.. have no idea what my background is, nor what amount of gear I have used and currently use now....  When the kids do see what I have it's like a major wake up call.... Have to agree with you on tech for ages though... there is certain tech that is aimed at a younger market... be it wearables... fashion etc.. yet... people in our \textbf{age} bracket... we seem to be getting left behind somewhat on the tech front... Tech Jackets... I want a pocket for wallet, glasses, keys, and THEN tech LOL!!! Anything on my wrist... if there is a way of looking at it without glasses... THEN its of interest! Ands thats the thing... until you get to a specific \textbf{age} and have to deal with the changes that come with it.. you really cannot appreciate... what is going to eventually come to us all!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/193 & \cellcolor{green!5}1.554 \\  \hline
  \cellcolor{green!27}\small Hey, great video. I wholeheartedly agree; learning should never stop, regardless of age\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small The reason I started following you is your unique way of showcasing stuff, there's more patience that sometimes can't be seen with younger people. TBH you're not that \textbf{old}, I know people 20 years older than you that are coding with no problems. It's never about the \textbf{age} but it's about the spirit. As long as you got the spirit to show off interesting tech in a chilled and cool format like you do you'll always have my view.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/79 & \cellcolor{green!5}2.532 \\  \hline
  \cellcolor{green!27}\small You are telling so much truth. I am grateful  for your videos.  I call \textbf{ageism} bullying\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Hey man, you make awesome videos. That's all I care about. I hope I'm cool like that when I'm your \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I love your videos and I agree with you anyone any \textbf{age} can be on YouTube as long as they're not too young\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Hey Bruce, I'm in the same ballpark related to \textbf{age}.  I agree that having and pursuing curiosity helps keep the mind young.  I still work as a database administrator and software developer and still love the technology.  I'm working on a Microsoft database certification to help with whatever \textbf{age} discrimination I run across in the job market.  Do technical certifications guarantee or prove anything?  No they don't, but it can't hurt.  I think part of \textbf{age} discrimination comes down to money.  Companies say they want fresh ideas from young people.  While that may be true in some cases, I believe that in most cases they can hire young people for less money and that's why they want to get rid of the older, better paid employees.  Thanks for the video.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}3/130 & \cellcolor{green!5}2.308 \\  \hline
  \cellcolor{green!27}\small Again \textbf{age} doesn't matter at all . If you have interesting things to say, than I'll be interested.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small In Canada you can carry on working after 65, they can't make you retire just because if your \textbf{age}.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small no one makes you retire, businesses would rather have younger, middle \textbf{age} people work for them than \textbf{old} people.\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small \@Satyam Patel But if they fire you because you are \textbf{old} you can take them to an employment tribunal. It just like any other discrimination in Canada it is against the Law.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small I subscribed after watching a few videos and seeing how you presented tech topics.  I did notice that I had never seen a tech channel w a host over 30-40, but that didn't mean the content was inferior.  It's the same stuff we're all interested in hearing about. I also think your engagement in the comment discussion is nice.btw I'm 24 and think wearables are \textbf{dumb} too.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small I am 28 in May and I always find that it doesn't matter how \textbf{old} you are, just how \textbf{old} you feel, and being older can have an advantage when it comes to having more experience and knowledge, which helps and one reason why I like your videos,  because of your knowledge and your passion to make tech videos like you do.I subscribe to a lot of YouTube channels from people that range from ages younger than I am or around my \textbf{age} in their late 20s to early 30s or even people in their 40s to your \textbf{age} like Michael Buckley or Tony Lee Glenn etc... and its not their \textbf{age} that I am concerned about and never will be, it is the content they produce and how good it is.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}5/132 & \cellcolor{green!5}3.788 \\  \hline
  \cellcolor{green!27}\small Very interesting topic Bruce.  I'll offer my opinion regarding this, becausesurely one opinion video welcomes the opinion of a viewer.  More and more 'older' folk (by which I think officially classed anybody over 50 is classed as '\textbf{old}') are getting on theInternet – probably due to their jobs, and just because that's the way the world is going.  Now people over the \textbf{age} of 70, things are very different – older people around that \textbf{age} have probably used a computer, but it's been very limited, and the chances of them owning one in their house is probably as lot lower than somebody twenty yearsyounger.  I wouldn't say the Internet is just for younger people because when it was initially created, many of us didn't even exist (myself included), but certain sites; such as Facebook, Twitter, YouTube, Twitch, and even a lot of gaming services such as Steam, I would imagine have a lot more younger users, probably a large majority of people underthe \textbf{age} of 40.  It reminds of another English guy over here on Twitch, I can't remember his exact name now, but at the time he was 67 and was streaming and playing Battlefield, and wasn't half bad either.  A lot of YouTuber's tend to be younger, and by that I suppose at the very most are under 40 – I'm not saying all, but just most.  Does it bother me?  No, it's great to see more people online and enjoying themselves and expressing their creativity.  Does \textbf{ageism} itself exist?  Well, I would imagine so as YouTube itself is deemed something for the younger people. I myself also use YouTube instead of watching TV, whereas my parents watch TV in the evenings – this also makes me wonder about the future of cable TV itself when online services such as Netflix are coming out, and you can watch what you want, when you want (without commercials?  I don't use Netflix).  I do think the Internet in regards to the future is going to be a lot more of a service and in our lives a lot more than cable TV ever was, and with services such as Skype will telephone services also cease to exist as  everything goes online? Certainly very interesting indeed.Was the hat just ‘because you had it sitting around'?  ;)  As you said in your video, it's nice to see older people using technology, which I can see as being \textbf{ageist}, but at the same time I also think it's bad to see younger people using technology, and I'm talking about those tablet devices made for small children.  They should be outside having fun, scuffing their knees, eating mud and just doing what children do!Talking about different ages and employment I'm going to talk about my father.  He works (or did, he's a manager now) in the haulage industry – his company are having problems,as is most of the haulage industry getting people my \textbf{age} into it...Older people are retiring, and not enough people are going into the industry to take up the slack.  I think the average \textbf{age} of drivers is 51.  As for my dad's company before they started offering an apprenticeship scheme I think the youngest person, at least in the UK side of the company was 34.  Most were aged between 45-55.As for that ‘too \textbf{old} to learn anything new', well to an extent, rather worryingly I've reached that point myself.  Don't get me wrong, I love technology, but certain aspects...VR, smart watches, Google Glass and other devices like that, I really don't want it forced down my throat. Maybe I'm just stubborn, but I'd rather have a computer for computing tasks, and then when I'm out to get away from it.  I own an iPhone, but it's only ever connected to WiFi when I'm at home...As soon as I go out all my social networking sites stop – if people want me, they can call me. I've often thought of going the same way Dave Cullen at computingforever has and getting a non-smartphone, but at the same time I'd still like to use Snapchat and Instagram – which is probably the primary use of my phone as it is.  A lot of people my \textbf{age} don't really do telephone calls anymore, or text...They might ask to FaceTime (similar to Skype – you can see each other's faces), but that's about all.I think that as long as you use technology to assist, and don't allow it to take over, then yes – you can have a better life by incorporating it and using it to it's potential.  Great video Bruce, and you're not 'too \textbf{old}' –keep at it, and keep having fun with it!  Happy Easter, and I hope that you and your family have a fantastic weekend.\normalsize   & \cellcolor{green!27}Age, Ageism, Ageist, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}9/806 & \cellcolor{green!27}1.117 \\  \hline
  \cellcolor{green!5}\small Hey Bruce, that camera footage does look very very nice.  There should be a setting to lock exposure and white balance for when shooting indoors. I got my PJ440 and just set the exposure and white balance. Then just make a preset in FCP to key those in each time. Now young man lets talk about \textbf{age}.. LOL.. Your not \textbf{old}, yea your 18 years older then I but heck, I got grey hair popping out each day as well, plus this horrid \textbf{bald} spot on top. But dont let \textbf{age} ever get you down. Once you stop living life is when you will stop living life. Ya know I think my \textbf{mental} \textbf{age} stopped at 25, but I spent over 6 years in the military since \textbf{age} 21. So I guess I got a lot of good life lessons in a short amount of time to help me make better decisions now. But my love for things and how I see the world, life and people around me never moved past that. I am a little more out of shape these days. But if I was still in the same shape I was then, life at least in my eyes would keep moving on the same around me. I am often shocked when I see photos on Facebook of kids of my friends that are not kids anymore. Their in high school or even college. I am normally left wondering, damn, did I just sleep ten years away. Where did the time go.What is sad though is the time it takes to foster a carrier these days. Heck lets look at this YouTube thing we both go going on or any real business for that matter. Takes 5 years to get it up to full speed. Then about another 5 more to set it in stone. Thats 10 years gone, 1/10th of our life expectancy. At least for 1/10th for those of us who don't smoke or drink like a fish. IDK, but then again if we wasn't doing something, that would be equally as bad. Anyway, I dont see you as \textbf{old}(er). I see you as Bruce. A wonderful person who has videos I enjoy and a person I hope to meet one day. So ignore the trolls, lord knows they been around since the days you and I were logging into BBS's on our \textbf{old} Hayes or Wang 1200bps modems. Often they are just the asshurt kids of democrats that just need a well placed mule kick in the face. So dont let their BS get to you. Make sure you drink your ensure and take care ;-)  Joe\normalsize   & \cellcolor{green!5}Age, Bald, Mental, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Physical Identity - Physical (and Mental) Impairments, Physical Identity - Physical Features & \cellcolor{green!5}9/443 & \cellcolor{green!5}2.032 \\  \hline
  \cellcolor{green!27}\small I love watching your videos really because your honesty not your \textbf{age} !!! Most YouTubers do it for the money and  forget the real purpose, keep the great work up. Your follower from CANCUN !!!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I ate \textbf{ageism}. Both against people who are older and younger. It makes getting a job harder and it makes keeping a job harder. There is always going to be a benefit to young dress blood and older blood that is more experienced.\normalsize   & \cellcolor{green!5}Ageism & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small +JKN Productions I have seen \textbf{ageism} on both sides. Early in my career I was too young.. Now too old\normalsize   & \cellcolor{green!27}Ageism, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small +FrugalTech am 50 perhaps i have some grey hair and get olderdad is 83i don t see you as \textbf{old},as older,.many \textbf{old} as we move to the internetlike report your tax evry year or online account internet don t know how to do it they can t follow today technology ,yesterday went to comic con,also with lot of technology ,take your pictuer with camara laptop to a printer,and the gamestoday am slow and still tired,.take day longer to recover,\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small It's because there where less \textbf{engineers} in "digital" subjects like computers when you where in your 30's.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I'm 67 and watch your channel to learn new tech and what I can do with it. I have a friend who it my \textbf{age}. In fact we went to school together. He isn't interested in computers and has a hard time working his cell phone. For him it's easier to ask me to update his computer and phone. I'm still working and running a company and he's been retired since 60. Were both happy. I wonder sometimes who's doing the right thing. I just find it hard to stop, or as think of it give up.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small Bruce, you're doing just great.  Love the channel and awesome Honda motorcycle jacket!  57?  That's not \textbf{old}.  You are right, discrimination of all forms, needs to stop!  Please keep up the great work!\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Hey Bruce - this 57 yr \textbf{old} just watched this video and went from a subscriber to fan!  Passion and enthusiasm will dictate your \textbf{age} with regards to virtually any aspect of life.  The improvements to technology have always been an enhancement to our lives and to not embrace them "at any \textbf{age}" would be naive at best.  Just for the record - my 94-year-\textbf{old} father and veteran of WWII - gets quite a kick out of his iPad which we gave to him last year!  He emails and can't quite get over the salaries of professional athletes that he has googled - you have got to love that!!\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/109 & \cellcolor{green!5}2.752 \\  \hline
  \cellcolor{green!27}\small If people make negative comments about your \textbf{age}, it means they've \textbf{nothing} better to exploit. I wouldn't even consider 50's that \textbf{old}, just older a lot of techies on YouTube. I think you're \textbf{age} is a massive advantage, because you've experience in both business and technology, and you've seen technology grow from its infancy, while our generation only gets to experience it in its current state. I'd say that on top of your personality makes you videos worthwhile for a lot of people.\normalsize   & \cellcolor{green!27}Age, Nothing, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!27}4/83 & \cellcolor{green!27}4.819 \\  \hline
  \cellcolor{green!5}\small I'm too \textbf{Old} for YouTube...;--(\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small good videos keep up the good work I know a lot of people who are in your \textbf{age} bracket that are in to tech\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small you've been playing with computers for years they act like when you get a certain \textbf{age} you're supposed to just be like you know what I don't like computers anymore I'm too \textbf{old} to play with computers that's the most ridiculous thing I've ever heard the older I get the more I lean towards technology and Technology only gets better over the years like you're supposed to just not be interested in it anymore that's like someone saying why do you like women you're too \textbf{old} to like women like when you hit 50 you all the sudden just stop liking women come on people really like you're supposed to just stop your hobbies because you're over 50\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}3/118 & \cellcolor{green!5}2.542 \\  \hline
  \cellcolor{green!27}\small +casper. do it all There are definitely  some people who believe that after a certain \textbf{age}, you are not relevant. You must be out dated and too \textbf{old} to know anything of value. Pity really..\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/35 & \cellcolor{green!27}5.714 \\  \hline
  \cellcolor{green!5}\small +FrugalTech I know it's ridiculous people think like you're going to lose interest in the things just because you're older it's like people saying why would he want a new car he's \textbf{old} he should be driving something \textbf{old} it doesn't matter what \textbf{age} you are you still like to have fun like we're supposed to just crawl up in a ball and sit in the corner and do \textbf{nothing} until you die\normalsize   & \cellcolor{green!5}Age, Nothing, Old & \cellcolor{green!5}Age - General, Age - Over 65s, Age - Youngsters & \cellcolor{green!5}4/73 & \cellcolor{green!5}5.479 \\  \hline
  \cellcolor{green!27}\small love the video uncle frugal and I don't think your \textbf{old} and never will be too old\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Great discussion.  BTW you're not \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Well Bruce, you sir are a year younger than Michael Jackson (R.I.P.), and you're probably the average \textbf{age} of the kids from The Brady Bunch. I certainly don't consider you an "\textbf{old} man who should be put out to pasture". If anything, I hope to God you continue to offer more \textbf{common} sense and sanity to YouTube techdom. Hell no, I don't want you to be my Grandpa...both of mine were already Grandaddies before you were even born!😎\normalsize   & \cellcolor{green!27}Age, Common, Old & \cellcolor{green!27}Age - General, Age - Over 65s, Social Class - Working class & \cellcolor{green!27}3/78 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Great video Bruce. I'm 19 years \textbf{old} and it doesn't matter how \textbf{old} you are! It is very interesting to see someone your \textbf{age} doing tech though! It honestly seems like someone your \textbf{age} has more knowledge or experience than some of the younger generation.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}4/45 & \cellcolor{green!5}8.889 \\  \hline
  \cellcolor{green!27}\small +Devin DeHart You know I appreciate  that. I have met some twenty somethings that I would describe as having an "\textbf{old} soul". It's like they have lived a prior life, and have a wisdom  beyond their years.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small I think I prefer your tech videos. I like how you come across. You and Techmoan as part of YT's Mature Content Creators, I don't care that you're whatever \textbf{age} you are. I enjoy Mickeleh as much as I enjoy Charlieissocoollike, and likewise, I like Frugaltech as much as any MKBHD\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small We oldies do have an advantage in the  jobmarket. In this day and \textbf{age} of part time work and lots of competition, employers favour older workers. It helps to stay curious and interested.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small You are doing a great job Bruce, so keep it up. Don't give a rat's ass whether someone thinks you are \textbf{old} or not.  We all get \textbf{old} and die eventually.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Great video Bruce.  I really liked what you said that you mentally lock into a certain \textbf{age}.  When I think about it I feel 27.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small +Joel Longie That's a great \textbf{age} to be locked into!\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small ageism is the worst for comparison you do the same thing as mkbhd and austin Evans but you have a charm that they don't have\normalsize   & \cellcolor{green!27}Ageism & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Age - General}  & \cellcolor{red!27}Age, Ageism, Ageist & \cellcolor{red!27}56 & \cellcolor{red!27}56/5132& \cellcolor{red!27}1.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}37 & \cellcolor{red!5}37/5132& \cellcolor{red!5}0.72 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Dumb, Mental & \cellcolor{red!27}2 & \cellcolor{red!27}2/5132& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Bald & \cellcolor{red!5}1 & \cellcolor{red!5}1/5132& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Engineers & \cellcolor{red!27}1 & \cellcolor{red!27}1/5132& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing & \cellcolor{red!5}2 & \cellcolor{red!5}2/5132& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Working class}  & \cellcolor{red!27}Common & \cellcolor{red!27}1 & \cellcolor{red!27}1/5132& \cellcolor{red!27}0.02 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Age - General;Age - Over 65s;Physical Identity - Physical (and Mental) Impairments;Physical Identity - Physical Features;Nationality - General;Age - Youngsters;Social Class - Working class;%.

\item The percentage of hate speech related words is 1.9486.

\item Considering that the variable \textbf{Age - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 102/128 occurences of hate speech related comments.\end{itemize}\end{document}