\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_291.json :}\newline \par\Large\textbf {Title: \large  6 Misconceptions About Native American People | Teen Vogue }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small In Minnesota we have a alot of reservations for native Americans and they own alot of casinos around my house. And if your not native American you can't step foot on the reservations or they will shoot you. They have therer own laws on the reservation to. And I know this video says they don't get paid for being \textbf{Indian} but I've talked to probably 100 \textbf{Indian} guys and most of them told me they were getting paid for being \textbf{Indian} , 90 of them are alcoholics and do wayyyy to many drugs at the one by my house. They are the most segregated people in america.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/107 & \cellcolor{green!27}2.804 \\  \hline
  \cellcolor{green!5}\small Notre \textbf{Dame} The Fighting Irish\normalsize   & \cellcolor{green!5}Dame & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Redskin means \textbf{black} Indians\normalsize   & \cellcolor{green!27}Black, Redskin & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small SITÚPI SKÁ and if you want to say that I can't tell you what \textbf{african} language we spoke so your point is invalid\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small 9 Mind News 101 So these '\textbf{black} Indians' don't have a name they're just called \textbf{black} Indians? Language and culture go together so that means they have no culture either. I'm not watching no Kurimeo video I know what he's about. He likes to delete his comments soon as you call him out on his bs.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small But they don't seem \textbf{r\textbf{ed}} enough :3\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small Man those two are funny. I LOVE Native humor \& I'm pretty \textbf{dumb} about humor.  (I've got to add one - "My grandmother was a Cherokee princess.")  My husband and I would always get that one said to us. Ugg\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@Bhav S It's not a victory. It's a reality. Unjust? Society is way too sensitive these days. Surveys have shown that a majority of Native Americans say they are unaffected by these team names. America is a great country but as with any and every country in existence there is a dark history. Let's not pretend a baseball or football team name represents that history. These symbols are symbols of strength and toughness. You have the Notre \textbf{Dame} fighting Irish, Boston Celtics, and there's even a small college team name of the "Saxons". These all represent caucasians. It's not a big deal. Have a good day!\normalsize   & \cellcolor{green!5}Dame & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/106 & \cellcolor{green!5}0.943 \\  \hline
  \cellcolor{green!27}\small The biggest mistake the ve \textbf{ho} did was make N A to learn their way. Native Americans should be allowed to keep culture their language and traditions.\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I'm half Native American and \textbf{Black} And my ggg grandmother was Also Native American and \textbf{Black} and my ggg grandfather was Native American so my whole family has some of that blood. I'm not familiar with my culture but I really do get the idea of it! I hope to learn more about it!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Yeah, \textbf{redskin} is \textbf{racist}, but I still don't care if someone calls me that.\normalsize   & \cellcolor{green!27}Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small ibesweetp2 nah that's being disrespectful having 17 is really nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I look white but im \textbf{crow} i have a really good \textbf{tan} but you couldn't tell my hair is blackish but whatever\normalsize   & \cellcolor{green!27}Crow, Tan & \cellcolor{green!27}Ethnicity - Black, Nationality - British & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small poppa dee Explain how you negroid/caucasoids aka \textbf{African} Americans are indigenous to the 'America's'? Where's your culture and linguistics? Where's the archeological, genetic, and anthropological evidence? What makes you indigenous?\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small because we DO pay taxes unless its on an \textbf{INDIAN} RESERVATION WHERE ITS A SHITHOLE.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small My family is half native and half black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small A lot of the so-called people coming out of Mexico right now came out of South America and passed over so this is why Trump is such an or uproar \textbf{black} people floating in as well as Mexicans Mexicans are Native Americans the majority of Mexicans are Native Americans as well as the blacks that came out of there their Native Americans also they were already here for thousands of years but then the angles when they came in they took original people in mix this with \textbf{African} people so they can have a new breed of people\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/98 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small There are a lot of Native Americans that have a mixture of Asian \textbf{black} and Morris blood\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Ah shadd up you rez ladies and go make my \textbf{Indian} tacos your gonna look like fiona shrek anyways after you hit 25 ah hah rez women so live it up"Eh whadda marron"  bugs bunny\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Mexican isn't a \textbf{race} and the majority  of Mexicans are native Americans so that's probably why.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Some natives get hush money to keep quit about the copper \textbf{colored} "real" aboriginals\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small You guys were all forced to change your way of life and not speak your language otherwise you would never say that you dont live in a tipi, that's how people came to be in tipi's so you might not live in a tipi but the blood of you and your ancestors did and that says a lot more than what all these young girls are saying , they truly have lost their history and \textbf{common} sense now\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Native Americans have ancestral cemeteries which most White or \textbf{Black}  can't afford.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Hummmmm! There wasn't a part mentioned that how some or majority of Native American population are actually Asian. And don't forget the reason why they are called Native American in the first place is because Columbus and other European settlers didn't know who they are so they guess that since these people are in America then they have to be 'Native American'. Plus they were also called \textbf{Indian} too because at that time Columbus thought he was in India.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small \@Joshua Aguilar u know there light skin natives right just like there's light skinned \textbf{black} people . And phenotype doesn't mean \textbf{nothing}. And not every indigenous person is dark, there's different shades of brown.\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Joshua Aguilar my friend is full \textbf{black} and he's light skinned doesn't mean he's half \textbf{black} or anything or someone is more \textbf{black} then him.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/25 & \cellcolor{green!5}12.0 \\  \hline
  \cellcolor{green!27}\small India is a different country on a different continent with a different \textbf{race} of people...\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Native Americans: We are neither \textbf{r\textbf{ed}} nor \textbf{Indian}.Indians: We are not Aryans, we are the children of the soil.Israel: God promised us the holy land.\normalsize   & \cellcolor{green!5}Indian, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/27 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Idk about the rest, but it's true about Indians... Not all of us are Aryan. Most south Indians are Dravidian and the North Eastern states are Mongloid.... But that's only if you have to divide it, \textbf{nobody} even falls under any category specifically, this racial stuff is only taught as school history.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small I cant lie a lot of native Americans do have \textbf{tan} \textbf{r\textbf{ed}} skin though like my grandpa and my grandma. im more on the tanner less \textbf{r\textbf{ed}} side but yes we are not all \textbf{r\textbf{ed}} .\normalsize   & \cellcolor{green!5}Red, Tan & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - British & \cellcolor{green!5}7/36 & \cellcolor{green!5}19.444 \\  \hline
  \cellcolor{green!27}\small I am a Native Brit, and proud of it, been born in England, the most important part of life is your \textbf{nationality}, your language and your way of life is your history, lose it, then you lose everything, many years ago I read about the American War of Independence against the British, Native Americans sided with British against the White Americans, White Americans never won that war nor did the White Americans win the war in 1812 again against the British, both wars were settled on Treaties and Agreements, indeed, if you read the Treaty of Paris you find-out America is still very closely connected to the British and not really independent as Americans believe or learned in their schools, America is owned by the Banks but who owns the Banks in the USA, the British, The True Legal Owners of America however are without doubt the Native Americans without them there is No America, after the second world war in 1948 Churchill handed down the Human Rights in Congress, these rights apply to every human being on earth, the Rights to Free Healthcare, Freedom of Movement, Freedom of Private Life, and another 100 plus Rights, the problem is the White Americans over the years have been the Biggest Violator of the Human Rights on Earth, even worse than China and Russia, The Native Americans will never die, as they are America, without the Native Americans there is No America.  thank you.Warmest Regards. Ray Cornes, Staffordshire England. UK.\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/249 & \cellcolor{green!27}0.402 \\  \hline
  \cellcolor{green!5}\small I get the importance of getting rid of misconceptions but I feel bad for theses kids cause those were some horribly \textbf{racist} questions and some were unnecessarily \textbf{racist}. (The only time some of those are brought up is by a \textbf{racist} with \textbf{zero} intent of having an open dialogue. Their only aim is to be hurtful). I understand these kids have probably heard worse before but it's cruel to put them into a position of being victimized for a video. They shouldn't have to deal with it especially one right after the other like that. There is a better way to get this information across without being harmful to these kids. Teen Vogue needs to do a better job protecting them.\normalsize   & \cellcolor{green!5}Racist, Zero & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}4/121 & \cellcolor{green!5}3.306 \\  \hline
  \cellcolor{green!27}\small Mexican isn't a \textbf{race} it's a \textbf{nationality}  and the majority of Mexicans are native Americans.\normalsize   & \cellcolor{green!27}Nationality, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small They are not Aboriginal American Indians, they are Native Americans. American Indians are \textbf{Colored} People or "\textbf{Black} People"\normalsize   & \cellcolor{green!5}Black, Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Lots of \textbf{racist} europeans in the comment section\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Redskin🤮 Girl if you look at my skin I can tel you right now I ain't no fire engine red\normalsize   & \cellcolor{green!5}Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small People told me that native Mexican isn't a culture or \textbf{ethnicity} but I'm pretty sure i know what \textbf{ethnicity}'s make me up\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small My grandpa is cherokee \textbf{indian}. No I'm not claiming to be something I'm not, If I knew you irl I'd show you the picture\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small LuminanceSnow calling native Americans Indians is disrespectful. If he is Native American call him that, hot Indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I'm white but it don't matter who you are or what color you are or what \textbf{race} you  are it's what in your heart and who you respect  as a person\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Your too wet behind the ears to understand. The fact is your descendents didn't leave you \textbf{nothing}, but a pile of lies. Enjoy them because your paying the bill.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small There \textbf{nothing} to watch at POW WOW but FOOLs.lol\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Calling a native person \textbf{Indian} just shows how unintelligent you are.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small How about the truth that the Indigenous ppls of the "Americas" were a majority copper \textbf{colored} peoples. Which is why they were called "redskins"\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I'm Mexican and we have the same blood color as any superior so called race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Littlehawk777 Avia my great great aunt was a complete Native American and she had a pretty \textbf{r\textbf{ed}} complexion. Not all native Americans have \textbf{r\textbf{ed}} skin, but some do\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/28 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Theres a great pretty  big difference between embracing a culture and being \textbf{racist} about it. And its funny cause, you can't tell what someones \textbf{ethnicity} or culture is by the color of their skin anymore. We're just that diverse.\normalsize   & \cellcolor{green!27}Ethnicity, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small So if \textbf{African} Americans are the REAL Native Americans, who are these so called Indians?\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Some tribes(mostly small ones) do give out monthly paychecks for each tribal member and good health insurance. Some tribes offer to pay for college because they can, and of course you have to meet requirements. Plus, they are a bit \textbf{r\textbf{ed}} due to classifications back in the day; however, today that's changing because of the differences between the south western and northern tribes color differences in majority. They don't live in teepees, usually they are used for prayer sessions or to have them up for special occasions. The  Navajo have hoogans instead of a teepee. Head dresses are used or may not be used in different ways in each tribe, or be very similar to one another. Another fun fact they should mention is the assumption of being Mexican or Hawaiian in public because of the similarities they share. Overall, this video is alright in pointing out the obvious, but it was a bit forced.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/155 & \cellcolor{green!27}1.29 \\  \hline
  \cellcolor{green!5}\small At least you guys have rights we native \textbf{indian} in India so called datits  live a  miserable life, they names us untouchables and taken all of our rights. 😔\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small T S \textbf{nobody} gives a stuff about natives here tbh\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small 3 out of 6 of those misconceptions are total false\textbf{Nobody} believes that natives live in tipis. \textbf{Nobody} believes that they live tax free. \textbf{Nobody} believes that they wear headresses. Pushing forth ignorance only begets more ignorance. Respect these cultures for what they are: Human.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small My history teacher told me we have no more native Americans, school teaches u nothing\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small You are either an American or an \textbf{Indian} you can not be both.When you make up your mind then we can talk.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Zeek M they are not Indians, they are native Americans... maybe go study a bit of history and find out why \textbf{dumb} Americans had the misconception of calling them Indians\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small ah ha! Native americans are not \textbf{black}! Take a look africans people! Now stop stealing other people historY!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'm white but \textbf{ethnic} a little (sorta middle eastern and Eastern European but I'm actually Russian) and everyone thinks I'm either Hispanic or Native American. Preach sisters ;)\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Y'ALL AREN'T THE REAL INDIGENOUS PEOPLE THE SO CALLED \textbf{AFRICAN} AMERICANS ARE!!! Y'all are look white or Asians smh\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Sorry. The real Americans (indigenous) were of copper color as described in books.  Before they brought these \textbf{mongoloid} and white folks to participate in paying to be an \textbf{Indian} and given land. Do your research please!!!!!!!!!!!!!!!!!!!\normalsize   & \cellcolor{green!27}Indian, Mongoloid & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/36 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small moval moval Looks like you're the one that needs to do your research. Do you even know the history behind the term \$5 \textbf{Indian}?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small I wish the term "Native American" was used universally for the native peoples of North and South America. The Inuit people of Canada, the Mixtec of Mexico, the Quecha of the South American Andes, The Yaghan of the Southern tip of the Americas, The Amazonians of Brazil and the Taino/Arowak people of the Caribbean all should have the right to be called Native Americans. Most "Latinos" deny or don't know their native heritage, its what gives us color in our skin! Its sad and shouldn't be this way, with a \textbf{common} event of colonialism in our roots we should all be proud of who we are now and who we where as a people before now in the Americas and in the world.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small how are these even misconceptions, as a south \textbf{african} i find it hard to think that people believe any of this.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Banathi Nkehli There really are people in America that really do believe some of these misconceptions...I've lived in America my whole life so you would be surprised how many have have also lived here for a long time yet know little to \textbf{nothing} about Native Americans except for what they teach us in history books. I personally even had some misconceptions about them myself, but I've learned more about them now...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small Just imagine if they all lived to this time in \textbf{age} with no genocide what would their architecture their technology look like\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small There are only two kinds of Humans(Racially). 1) Whites 2) Non-Whites also called \textbf{Colored}. eg: Blacks, reds, browns. This is just my opinion.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small These are not native american, the first people were actually white \& not mix with \textbf{Mongoloid} \& came to north american before the ice \textbf{age} \& before the Egyptians build the pyramids\normalsize   & \cellcolor{green!5}Age, Mongoloid & \cellcolor{green!5}Age - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Greek Mathematician That sounds a lot like Racial hygiene.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I'm fullblood native american, you want to go half on a baby ? 😁💙 i'm not \textbf{racist} at all.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small What kind of \textbf{racist} think of these questions 'misconceptions'?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small At my school (in the uk) we've been learning about the native Americans and I just wanted to say, that I feel so sorry for everything that their ancestors have gone through. Recently we just finished learning about the Wounded Knee Massacre and it actually sickens me to think what happend that day. How disgustingly the US army and settlers treated them. How they destroyed their buffalo, stole  their sacred land and slaughtered their women children and \textbf{elderly}. I'm so sorry for what has happened,And the irreversible damage that was caused.\normalsize   & \cellcolor{green!5}Elderly & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small There homelands?! Lol they didn't own this land the real Redskins did they white. The \textbf{Redskin} Indians was much darker then them and was practically forced to give up there land. And if it's there homelands then how my grandpa owns land and it was passed down by his indigenous ancestors who hue was dark or copper color.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck what is? Lol I'm going to drop a gem that is pretty true just have to look it up. They found artifacts and ancient Hebrew hieroglyphics writings here on turtle island they found it in South America and Ohio. The original language of this land was Hebrew. The Cherokees spoke the language. Look this up.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Crazy Canuck I know that, I am Polynesian myself, precisely Tahitian.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Proud Cherokee here, and I must say thank god for the white people taking our land! Who knows what our land would be like without progress. I know, I know I'm offensive. I'm Cherokee and my ancestors were slave owners... did you know whites weren't the only slave owners? So \textbf{black} people should be mad at natives too, for that one percentage of slave owners, right?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small The term ‘redskins' is inappropriate and \textbf{racist}. As others say, you don't see any \textbf{ethnic} people running around the streets wearing a shirt with a white man head on it that says ‘crackers' . If you disagree that's not it sis\normalsize   & \cellcolor{green!27}Ethnic, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Y'all weren't the first americans. Because the first americans would be \textbf{Black}  \textbf{r\textbf{ed}}  The color of the penny.\normalsize   & \cellcolor{green!5}Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/20 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck its funny because its ignorant. Ever hear of the Fighting Irish? Vikings? Trojans? Piates? Celtics? Ever hear those cultures whine about it? Didnt think so\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I went to California one time for a couple of months and a lot of people actually think stuff like this, it's so \textbf{weird}.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@Clyde Brown Tbf, doesnt that mean we're overcoming \textbf{racism}?Also is it really fair to punish people for something their ancestors did?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Celtics, fighting Irish. \textbf{Racism} is everywhere.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Leticia Tejada-Espino they don't even look like the \textbf{redskin} mascot but \textbf{black} people do , now let that sink it , negros are The true Native Americans\normalsize   & \cellcolor{green!27}Black, Redskin & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small \@Kevin is Nice So basically \textbf{nobody} is an American if that's your point.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Not All native Americans are offended by being called \textbf{RedSkin}...  [LINK] \normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Living Lifeform But having a native american as a sports mascot has \textbf{nothing} to do with that.Yes, its understandably \textbf{racist} if they name the team the "redskins" or make the mascot look as stereotypically offensive as possible, but simply having a historic warrior (gladiator, knight, samurai, aztec eagle warrior, māori toa, etc) as a mascot is not wrong...\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small Kevin is Nice you're native to Europe, immigrant\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Gaby del cristo \textbf{Gringo} isn't a slur or an insult. It's just another way to do white. You could also say blanco, but that's more for color than \textbf{race}.\normalsize   & \cellcolor{green!5}Gringo, Race & \cellcolor{green!5}Ethnicity - General, Nationality - American & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small \@Youre On Stolen Land go back to europe whitey\normalsize   & \cellcolor{green!27}Whitey & \cellcolor{green!27}Ethnicity - White & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Amberly Quakegesic Yes, like I said the prblem isnt that they have a native american mascot. Its the name "Redskins".For something to be \textbf{racist}, there needs to be direct correlation to \textbf{racism} and discrimination.The term "\textbf{redskin}" was an actual slur used for native americans.Having a NA mascot, or a white person wearing a NA headdress does not have direct correlation to NA discrimination.Another example is Blackface vs white people with dreadlocks. The latter of which was not used to discriminate against \textbf{black} people while the former was.\normalsize   & \cellcolor{green!5}Black, Racism, Racist, Redskin & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/91 & \cellcolor{green!5}4.396 \\  \hline
  \cellcolor{green!27}\small Sure we do.  Notre \textbf{Dame} the fighting Irish.\normalsize   & \cellcolor{green!27}Dame & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Jo Doney Yes; I look like warao \textbf{Indian} tribe.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small CALLING SOMEONE A "\textbf{GRINGO}" MEANS FOREIGNER NOT WHITE!!!!!!! BLANCO MEANS WHITE.\normalsize   & \cellcolor{green!27}Gringo & \cellcolor{green!27}Nationality - American & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@pinkoya If they want to rename the team to the "Salish Warriors", "Nimìipuu Warriors", or some other kind of NA warriors, thats fine.I agree that the term "\textbf{Redskin}" is offensive. But not being able to have any Native maskot is going too far.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small \@The Real J P Morgan  It is true we migrated here around 15000 years ago. You are correct in that statement. Have you forgotten about the ice \textbf{age}? Prior to 15000 years ago North America continent was locked in ice \textbf{age} that started in the late pleistocene era. That means this continent was underneath a mile of ice. That is why there is no forensic remains prior to the remains of my people. North America was uninhabitable during the ice \textbf{age}. Just another little fun fact for you.....\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}3/88 & \cellcolor{green!27}3.409 \\  \hline
  \cellcolor{green!5}\small \@The Real J P Morgan  Now look at \textbf{black} people as a \textbf{race}. And yes they are a \textbf{race}. Kinky hair, wide noses, and dark skin all to help with the heat. Your people evolved in an extremely hot climate. So you guys are trying to say that a people evolved for a very hot climate survived in subzero temperatures for hundreds of thousands of years?...... Doesn't make a whole lot of sense if you think about it does it....\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small Miranda Olmos Mexicans are the same \textbf{race} as these ppl\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@オルモスサラエリザベス mexicans are the descendents of mixing between the spanish and native americans of mesoamerica. why do you think mexicans are brown?theyre native,they have indigenous blood. not all native americans were colonized by the british or french. obviously the cultures evpvled differently because of the histories of mexico vs america but all the same \textbf{race} lol. amerindians\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Crazy Canuck why is that?\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Brian Sheehan found the racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Kyle HORIzON Yeah, but instead they needed the white man's help to destroy other tribes, and the white man used them against each other because they couldn't stop slaughtering each other. This is why our Army recruited \textbf{Indian} scouts and skirmishers, making the Indians destroy each other.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@Brian Le WHAT IF IT HAPPENS OR HAPPENED TO YOU, LIKE THAT TRULY HURTFUL AND DISRESPECTFUL, LIKE I SAID WE DIDN'T DO \textbf{NOTHING} TO YOU SO WHY...WHY DO IT TO US!!!😔😳😒\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Crazy Canuck idk where 'we' comes in but Kayla Rudd and I are talking about what if my people were conquered.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Samhita Mehta the Africans, East Asians, and Mesoamericans conquered and killed each other too so don't say it's only middle eastern and European. You sound \textbf{racist} and stupid. Learn history. Everyone on this planet has an ancestor somewhere down the line who killed another people for their territory. It's human nature.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck yo wassup buddy it's the \textbf{Crazy} Canuck! Lol! You're that guy with the trash talk! Dude I wish you were an ancient native tribesmen and I was a European conqueror and I could just massacre your whole village it would be awesome. Just get it through your head that might makes right. Obviously you're on a couple different videos with your victim mentality about ancient dead tribes. Well I'll be here to tell you that nature is as nature does. And it's human nature to take territory. Every single \textbf{race} of people have done it so it's not about \textbf{race}. It's just the way it is. One day our great American culture will be conquered too. The difference is that if it happens in our lifetime, I will join the new culture or die with a gun in my hand if they want to slaughter us. But you will die with your hands tied like a coward, sobbing as you're beheaded.\normalsize   & \cellcolor{green!27}Crazy, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/163 & \cellcolor{green!27}2.454 \\  \hline
  \cellcolor{green!5}\small \@Brian Le yeah see making up \textbf{dumb} excuses for genocide is a cop out.  Beewww they killed each other sometimes so they all deseeved to be wiped out permanently thats a cop out\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@katya z So do you agree that the Lakota stole the lands of the Arikara, Mandan, Hidatsa, Kiowa, Oto, Ponca, Omaha, \textbf{Crow} and Pawnee?\normalsize   & \cellcolor{green!27}Crow & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small The Indians were conquered. \textbf{Nothing} was "stolen".\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck lve got 37 years to prove you wrong.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Tho two \textbf{fat} fucks dont\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Anthony Mongan two \textbf{fat} angels r beautiful than ur mama n wife that's why u r badly obsess.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck  Why are you so unhinged?\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Tahnee Ferris nope there not. Usually \textbf{fat}, Napi hair, gross teeth, and there asses are always so flat.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small That long \textbf{black} hair is so pretty 😍\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck thank you\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small The people saying we don't look good are talking about the native people living off the streets but still every \textbf{race} has ugly people and beautiful people\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small The 2 \textbf{fat} bitches don't u must b smoking wen u typed that\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Cushite no they don't these r Asiatic natives cuz \textbf{colored} natives look \textbf{nothing} like these ppl\normalsize   & \cellcolor{green!5}Colored, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Zacobie Dyer  1st off there's no such thing as a \textbf{colored} native. Embrace your own culture and stop trying to steal others.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@siksika plus dumbass there was darker \textbf{colored} natives u dumbfuck\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small No they dont. These are \textbf{fat} and/ugly girls and they are a good representation of how ugly indians are\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Lisa Dixon stfu you stupid woman\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Zacobie Dyer  I believe the only \textbf{dumb} a** here is you. You and your freakin fantasies about \textbf{black} natives. The only place blacks were native to is Africa.\normalsize   & \cellcolor{green!27}Black, Dumb & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Lee Francis and apparently ‘low life' doesn't associate with stirring up \textbf{racism} towards Native American. Smh\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Lee Francis Oml🤭How sick are you? I get these vibes that you're a trolling 10 year \textbf{old} looking for trouble on YouTube.... am I right? I hope so, because any DECENT well-minded individual would not have said the things you did. So we're all gonna assume your a kid (and if you're not, you have the aptitude of one) and leave you alone k? God bless your ignorant, \textbf{racist} and young soul. Stay in school kid😁\normalsize   & \cellcolor{green!27}Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small Furbbles stuff No argument the real orginal Americans are White, Indians aren't American's. The first \textbf{Indian} who became a American didn't happen until 1924.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Americans don't know \textbf{Indian} culture.lol\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small I'm happy white man took \textbf{redskin} land. Those feather headed fools murdered there own tribes and raped women:) sorry if I hurt any libtards feelings.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Lonely Spirit lts not \textbf{racist} not like BUMS\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Tanaysia White They're \textbf{nothing} sacred about a pow wow.indians selling Mexican goods and telling people it was made by Indians. More lies.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@Tanaysia White pow wow \textbf{nothing} but a laugh of Primitive jerks.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Lee Francis Whites knew \textbf{nothing} about the Americas until only less than 300 years ago. Youre not the superior \textbf{race}. Go back to your plague-infested medieval Europe. Go get some help and while you're at it, some real history classes too.\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small I'm Seminole Creek and after turning a certain \textbf{age} I really dived deep into my culture and in learning more about my people. Even if I wasnt native I'd like to believe that I'd be really into reading and meeting people who are native because it really is so interesting to see all the cultures/tribes and to hear the language and listen to the stories that have been passed down.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small \@Lee Francis You pulled the , look at me I like Indians crowds selfrightous  trigger. They dont like truth and to be honest I've read of the land bridge too. I'm sure other than the Israelites using it ,others did too.. except the \textbf{black} man . They mingled when the native americans raided the plantations in the late 1700s and took women and children to increase their numbers durring the \textbf{indian} wars with America.  Alot of white European looking native Americans.  Alot.\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/82 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small \@Sinx Native Americans are White not \textbf{R\textbf{ed}}.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck Indians the retards of America, have \textbf{nothing} but bordom.\normalsize   & \cellcolor{green!5}Crazy, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck It's our Culture that is adored around the world.lol\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck My condolences to Indians your poorer than dirt.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck l feel sorry for such losers.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck The originals Americans are white. Indians don't have a country, never did either.lol\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck My Condones for such stupid losers.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@SAVE THE AMAZON RAINFOREST Simple task the Europeans made America a Country, developed it into the fine \textbf{Nation} it is today. If a build a house, the house is yours. America belongs to all Americans.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Lee Francis Your more ignorant than I thought a dna tests shows the specific locations of a persons genome to tract their ancestory to show what traits they may have your blood group has \textbf{nothing} to do with it .\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck insane Canuck try me l speak German, Spanish, and English.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small cause white, \textbf{black}, and Asian people can't be "real" Americans I guess?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Felim Ryan typical coward hiding behind a fake account to spread hate . You would never say all you have said to a group of Native American men. If you wanna be a real \textbf{racist} do it in person you little  poosy and see what happens\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@Rose A bunch of Balonie, their \textbf{nothing} but Drifters.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck America has had many Anti-Americans but none like the Indians. Why haven't they moved on somewhere else? It would make all Americans happy, and probably the Indians too m\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small they should have interviewed older native americans. that would have been interesting to hear their \textbf{old} ways of life and how much has changed. These younger generations are just living the american teenage way of life\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small I'm a native american, a Navajo to be specific and 'rich off of casinos' uh no sis we ain't. 'Redskin' is \textbf{racist} asf\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small So I'm a northen native american Im in a cooking class with a friend and I'm sautening some \textbf{r\textbf{ed}} bell peppers. Then she says.Banana: Hey it looks like your face.(Pointing at the \textbf{r\textbf{ed}} peppers)Me:What? How does that even resembles my fa- oh you asshat.(Realizes what she ment mid sentence)\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/52 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Red skin is Exactly like calling a sports team hanging(N) word See what would happen\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small I respect every culture but the fact that most supporters of Donald's Trump don't.... it's sad and y'all wanna call yourself Americans???? Americans don't disrespect other Americans. I don't care if they English Americans... \textbf{African} Americans...Native Americans,etc. they are still American because they earned their right of citizenship.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Wrong, these people are 100 Native Americans. DNA tests dismantle your \textbf{racist} afrocentric views\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Are you copper toned or \textbf{black}?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Yo u can tell all the dislike are \textbf{racist} or \textbf{Redskin} fans\normalsize   & \cellcolor{green!5}Racist, Redskin & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Noun of these people are cooperd colored\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I thought Indians are cooperd colored\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Latte Knowsbest all aboriginal  of America  are cooperd colors  these  people  here are siberian \textbf{witch} came threw Alaska  Eskimo\normalsize   & \cellcolor{green!27}Witch & \cellcolor{green!27}Gender - Female age and physical appearance & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small They re the real Americans... Not the others who killed them... I always here everyone crying about \textbf{black} rights but not really about native Americans rights and situation, I just don't understand why they would be less important, actually they should be more important\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small The most oppressed \textbf{race}?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I'm watching this bc my ignorant friends want to make a ‘red \textbf{Indian} ‘ themed party while I kept on telling them how \textbf{racist} that was they continue d to make ignorant remarks ‘why doesIt matter they're all dead any ways' well a mistreated minority's culture isn't a party theme and they kept on talking about the headdresses and not knowing anything abt them I just got so pissed off\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small All of the reservations I've seen are all filled with trash and rusted \textbf{old} car parts on the lawns with over grown weeds, alcoholics with tempers.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small I'm mixed with both \textbf{black} and native American.. Tribe choctaw 😊\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I am a Native American and people will be like " U don't look like it ". (I am mixed with \textbf{black}). I get so mad when people say this or "like prove it". I be like WHAT U MEAN\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Whatever \textbf{Black} people make similar claims and get called a cry baby so much hypocrisy.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small In the Chippewa tribe only the Tribe leader wore head dresses i know its \textbf{dumb} but  i take my culture VERY seriously and i see all these straight up WHITE GIRLS wearing them as a Halloween costume and i get offended because when i was 6-10 i was bullied for my \textbf{race} and i would hear all these questions like "did YOUR people scalp white people?" .."do you wear moccasins all the time?" It has still been a constant battle being half native and im 18.. and proud of what i am\normalsize   & \cellcolor{green!27}Dumb, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/92 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small I'm native America I'm \textbf{crow} and Souix\normalsize   & \cellcolor{green!5}Crow & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I don't get how people think we have "\textbf{r\textbf{ed}}" skin...Why?\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small The \textbf{chubby} one?Not my type tbf.\normalsize   & \cellcolor{green!5}Chubby & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small I have Native American (Shasta) in me, and I feel as if I know exactly what they go through and what they're feeling. Of course I'm \textbf{Black}, and being a \textbf{Black} American, we go through a lot of things, similar to what Native Americans go through. But I feel as though I am a part of their culture, in a sense. There are a lot of misconceptions for all people of color!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/72 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Native Americans enslaved \textbf{black} people and it's all documented. God luck to those who mistreat others based on color like whites and Native Americans.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Everyone enslaved everyone, don't make it a \textbf{race} thing. Natives were captured and made slaves, Africans inslaved and sold most of the "\textbf{black}" slaves. Plus why is everyone responsible for what their ancestors did?\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small People saying "I'm offended of being called \textbf{redskin}" how are you not offended of being called native american? That's a false name\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small My grandma is creole , \textbf{black} and \textbf{Indian} even though I'm brown skin you can see the \textbf{Indian} features in me like the high cheek bones\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small \@Mal Rose Your right. I never said different. Your just missing part of the story. Ever here of a 5 dollar \textbf{indian}? More then enough proof to show natives were Hebrews. So why don't any native American speak or claim any Hebrew heritage? Like I said look it up.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small The natives did the scalping not the europeans, so what they are saying about the \textbf{redskin} term is bs.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Do you know that there are a group of \textbf{black} people who are claiming that they are indigenous Native Americans?  They call themselves Moors and that they a Moroccans LMFAO!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small I think if native Americans still had all their lands global warming wouldn't be a thing, or if native Americans were introduced to guns before white man arrived, we would still have all our lands, we were strong fighters, we had \textbf{nothing} but our basically nature maid tools, and whites had guns bullets,  life would of been way different.all these cities wouldn't even be here.just something to think   About🤔\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Wow, some of the comments here are so \textbf{racist} and disrespectful. Very disgusting!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Free speech libtard\normalsize   & \cellcolor{green!27}Libtard & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Felim Ryan OP has free speech too. And they have the right to call these \textbf{racist} comments deplorable.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Felim Ryan literally what every \textbf{homophobic} and \textbf{racist} person says lmao\normalsize   & \cellcolor{green!27}Homophobic, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small almost every native american video on youtube is full of \textbf{racist} comments. Someone should make a video about it and put these racists on blast. I am sure social media would love that .\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Felim Ryan Shut up hick\normalsize   & \cellcolor{green!27}Hick & \cellcolor{green!27}Ethnicity - White & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small oh, if it wasn't for the white man.    Native  would not have what you have today    education technology cars  computers  condos.  House.   And you guy don't pay taxes. you guys used to live in tent.    Your welcome.  You ungrateful people   you  racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Ivan Drago Learn to spell before you go commenting \textbf{racist} crap.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small JC Denton Why? You have \textbf{nothing} to be sorry about. You personally did \textbf{nothing} wrong..\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Isn't the \textbf{r\textbf{ed}} skin nickname a historical term? Native Americans aka \textbf{r\textbf{ed}} Indians, \textbf{r\textbf{ed}} skin because of the \textbf{r\textbf{ed}} pigment on their face or the blood on there face when the \textbf{old} immigrants wiped them out. Isn't it not a racial term but just a historical name they were also known as?\normalsize   & \cellcolor{green!27}Old, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}9/52 & \cellcolor{green!27}17.308 \\  \hline
  \cellcolor{green!5}\small Amy Warnock We were known as that before because most of us kind of looked \textbf{r\textbf{ed}} when we were out in the sun.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Allways thought \textbf{r\textbf{ed}} was native in the medicine wheel as asians were \textbf{y\textbf{e\textbf{llow}}} and \textbf{black} n white were \textbf{black} n white?\normalsize   & \cellcolor{green!27}Black, Red, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}7/21 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small ' it's not like we have a mascot of a white man'You had to use white people as an example? Couldn't used a \textbf{black} or Mexican as an example? Kind of funny\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small I'm Cherokee and Choctaw \textbf{Indian} and I will always have a lot of pride\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small whoever thumbed down this video is either a \textbf{racist} or a very triggered native american\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small You look \textbf{african} descendant though, and it was the whites who brought the Africans.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small These are the real americans ,not that \textbf{racist} white people ,they are not american ,CAN'T RELATE\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The reservations are ghetto and they're all \textbf{fat}.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Brian Le not really though, since archeology really doesn't support the idea that war is \textbf{common} in human history\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Sal Ochoa Doesn't matter fam, we have little archaeological evidence to suggest war was \textbf{common} in human history. Some cannibalism in one group over thousands of years doesn't overturn that.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@LordSear1982 Did you just assume kuls \textbf{ethnicity}, and where they live.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Native Americans are Siberian's, roughly 250 Siberian's that traveled to America became the first native Americans, Native American is not a \textbf{race} they are just Siberian's who earned the title native Americans by the Europeans when they came here, but their is no such thing as \textbf{race} just saying.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small LordSear1982 I learned it in AP world History, it's a class you take in college but I'm taking it early. In college you learn that \textbf{race} is just a social construction made by man, their is no such thing as \textbf{race} and saying their is races is what divides even more, we are the same.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small Having an \textbf{African} Dad but growing up in Germany, I was confronted with questions like: do they still live in huts and wear fur on their genitals? I can relate\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small sorry but all this is still happening in many \textbf{african} countries its legit questions\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Americans \textbf{Indian}. Is the best culture on the United States   Not white  peoples. You  understand.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small the girl's \textbf{y\textbf{e\textbf{llow}}} outfit is so good\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/7 & \cellcolor{green!5}42.857 \\  \hline
  \cellcolor{green!27}\small Lee Francis Yeah they're not. Indians are \textbf{Indian} (India). Native Americans are Americans.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{African} American and Native American\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Bharatveer Singh Judge - Every \textbf{nation} is built upon people killing each other for land.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Bharatveer Singh Judge Both of the world wars where not a "white man's war". There where attempts of painting it as a white war at the time, for example the French government requesting only white man to match onto Paris after German occupation despite \textbf{African} volenteer forces doing alot of fighting. And obviously there is imperial Japan.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small It got some \textbf{dumb} blk folks claiming they the true native americans lol I debunked them easily in a video i made on my page\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small at 1:59 , "\textbf{Redskin} is \textbf{racist}"???  Google this sentence in Google, and Google images: "At a Navajo high school, the \textbf{R\textbf{ed}} Mesa Redskins have become a potent symbol in the national debate over a NFL team name".  Back in the day, women did not speak with authority, and younglings would never have a stage, to spew their misconceptions. This would be very forbidden.\normalsize   & \cellcolor{green!5}Racist, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/63 & \cellcolor{green!5}6.349 \\  \hline
  \cellcolor{green!27}\small Some \textbf{Indian} tribes give out 30,000 a year put in a trust until 18, then they get it every year... So I think some of them are pretty well off\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Umm that's money that our tribe has earned sorry white people are greedy and don't share and consider that just Cherokee alone controlled five states northand south Carolina Georgia Tenn and Virginia what do we control now about 100 sqaure miles on a mountain \textbf{nobody} wants to live on so thank you colonizers for leaving us \textbf{nothing} so yeah yuns be butthurt over out little bit of money that our casino makes we earned that through the blood sweat and tears of our people\normalsize   & \cellcolor{green!5}Nobody, Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Noah Murphy lmao I'm \textbf{Indian} too and I get the money and I'm not offended so what's your problem? Some people ....\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small To the government hand outs, it is true BUT TO A CERTAIN EXTENT. We have to work just as hard as everyone else, but in Oklahoma, and I believe in just Oklahoma? We do get some things. As children in schools we get \$10 each semester for book fairs. In the part of where I live in Oklahoma, we have a \textbf{Indian} hospital where they do look primarily for people of \textbf{Indian} heritage BUT they do hire people of other ethnicities too!! My dad (\textbf{indian}) works there, and so does my mom (not \textbf{indian}) so it is \textbf{common} for others to work there! In schools, growing up, we also got a free dentist care. I believe it was just a check up and enamel sealant, it wasn't much and only happened once a year in the school. A majority of the people I've grown up with in Oklahoma have \textbf{Indian} heritage and as long as they have their \textbf{Indian} card they are available to receive these benefits.\normalsize   & \cellcolor{green!5}Common, Indian & \cellcolor{green!5}Ethnicity - Native-American, Social Class - Working class & \cellcolor{green!5}7/167 & \cellcolor{green!5}4.192 \\  \hline
  \cellcolor{green!27}\small The highschool that I went to still calls its football team the "\textbf{R\textbf{ed}} Raiders" and it makes me so angry, people have been trying to get the school to change for 40 years now.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Actually no one knows why they used the term \textbf{Redskin}.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small My teachers last name is \textbf{Redskin} 😭\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small The girl in the \textbf{y\textbf{e\textbf{llow}}} has \textbf{African} in her..\normalsize   & \cellcolor{green!5}African, Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}4/9 & \cellcolor{green!5}44.444 \\  \hline
  \cellcolor{green!27}\small The girl in the \textbf{y\textbf{e\textbf{llow}}} shirt and glasses is the best being honest...\normalsize   & \cellcolor{green!27}Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}3/13 & \cellcolor{green!27}23.077 \\  \hline
  \cellcolor{green!5}\small No one cares!!!!!!everyone cares about \textbf{black} AMD white!!!! The US GOVERNMENT DOES NOT CARE......AT ALL..WAKE UP AND REALIZE THIS!!!!!!!!!in some tribes,  we DOOO EARN head cheif!!!stfu you ignorant fucks???????????\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small All you people in the comments acting like natives owned the land and it was all ruined by whites. First off genetically natives are very similar to ancient europeans and share approx 1/3 european blood before the europeans you speak of even made contact. Second off whites thought blacks were ugly and natives were sexy. When the spanish came to mexico half of them were about the same colour anyway. Acting like the natives werent just as brutal as whites. Mexicans may be a spanish native mixture but are even more rasict to blacks then whites. Natives think they are \textbf{black} when they are an ancient european  asian mixture hence large noses. Negroids or mongoloids cannont genetically have large noses. Natives are scientifically a Caucasioid/mongoloid admixture\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small If you look at me im not black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small They look \textbf{nothing} like Indians\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Anyone else proud to be Indigenous??I'm a proud full Indigneous \textbf{woman},I speak Cree fluently and understand it very well 💕\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Tom Jones dude are you being \textbf{racist} to natives sounds like a rude Joke then again maybe not\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small I'm fluent in cree, Ojibwe and Oji-Cree and my English isn't really that good when I speak.And I love being First \textbf{Nation} in Canada..\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck  Don't be butthurt.  Just accept the truth.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small If you native Americans don't mind me asking, what kind of faith do you follow. I heard a lot of ancient faiths were forced to be made Christian and \textbf{old} faiths were abandoned. I really want to know more about ancient cultures tho\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small Why would you be proud to be part of such a culture of losers? You lost everything because we were better than you and still are. Have fun drinking yourself to death redskin\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Wait but you like K-pop why is there asian or whatever on your YouTube page?. Not tryna be mean but I find that weird\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Yes of course was stereotypes about all cultures of the world. Even my own culture I go to other countries and they think all white Americans are rich and that all Americans all they eat is McDonald's.  they think none of them can speak the language of that country. People think that all Mexicans eat \textbf{nothing} but rice and beans... but just because they are stereotypes doesn't mean that we should stop traditions. Just because people of Georgia or Alabama have a southern twang does that mean that they all should go to Accent elimination. It's okay to have stereotypes I say. Because that's what makes us different from one another as long as we accept each other's differences and not be over sensitive and mean to each other. I like people who show off their culture and traditions and I'll proud of themselves but not mean towards people who are not of their own \textbf{race}.\normalsize   & \cellcolor{green!27}Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/156 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}\small I wish they had asked about the word "American \textbf{Indian}," rather than \textbf{redskin}. That one seems more of a gray area.\normalsize   & \cellcolor{green!5}Indian, Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Legit question... Do you guys prefer Native American or American \textbf{Indian}? My history teachers say American \textbf{Indian}.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small I'm half Native American and I feel like these saying are super crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Well i see yall mtfk felt guilty for invaded others land. There's no White supremacy no \textbf{Black} powers and shit, we're all equal here as a human. Even the native can accept it. Why weren't you?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Yes they do look white mix with Chinese there mongoloid\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small They need to make misconceptions of white peopleQuestion: why are you \textbf{racist} you white piece of shit?Answer: umm I'm not y is everyone being rude to white people now\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small What that the not the real indains \textbf{crazy}..your a white women\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Sauce Lord yes mongoloid\normalsize   & \cellcolor{green!27}Mongoloid & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small No I'm not an \textbf{Indian} im a Aboriginal\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small ( American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK]  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK] ( somebody lied whos copper \textbf{colored}?\textbf{African} american ant \textbf{african} ) [LINK] ( City of David in,Perusaksaywaman Ancient jerusalem in Cusco/Navel /Hierosolym ) [LINK] ??? [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK] ( somebody lied whos copper \textbf{colored}?\textbf{African} american ant \textbf{african} ) [LINK] ( City of David in,Perusaksaywaman Ancient jerusalem in Cusco/Navel /Hierosolym ) [LINK] ??? [LINK] \normalsize   & \cellcolor{green!27}African, Black, Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}18/382 & \cellcolor{green!27}4.712 \\  \hline
  \cellcolor{green!5}\small Does every \textbf{race} deserve their land back. [LINK]  [LINK] \normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Wtf is wrong with all these comments? Can't y'all watch the video without making it a \textbf{race} war, country war, or political war????\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Fish buddy I mean, the video is responding to stereotypes.They mentioned Trump which will automatically cause a political war, and during the end when she said 'whiteman,' sealed the deal for the \textbf{race} war.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@Delta 38 they are not starting a \textbf{race} war. they are just politely pointing out that if the tables were turned people would give fucks instaed of turning a \textbf{blind} eye.\normalsize   & \cellcolor{green!27}Blind, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Ugh white people started the \textbf{race} war. Now you dont want it?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Being an American \textbf{Indian} does not make you an expert on the culture.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small So \textbf{African} Americans included? Okaaaay seems fair enough.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Nah they can be extremely \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Not true. European Americans are coolest ones. Natives are \textbf{weird} looking freaks, sorry.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Marko Milojevic What about \textbf{African} Americans?\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small there was a \textbf{race} in Mexico called the aztecs who did a ritual that involved human sacrifice of people of all ages, children also. that these people were raised to be sacrificed (they were raised thinking it was the best death one could achieve) so that the aztecs could read the future of their country to see if their gods were happy with them and would allow them to have a good crop year if not, the sacrifices would last for months.  I'm sure that many of the native Americans would offer up tributes of people who were raised to be sacrificed by the aztecs.  there are rumors that the aztecs had huts made of skeleton and human tissue to live in, they had shaped heads and sharp teeth. the whole area of the aztec \textbf{nation} smelled of rotting corpses, all the way up to Oregon.\normalsize   & \cellcolor{green!5}Nation, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/146 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small The thing about skin color is so real . I literally fought a girl who were saying that native americans can only have "\textbf{r\textbf{ed}} skin" and I was explaining to her that that's not always the case and even mentioned my mom as example because she is a full blood native american but no she insisted and said that brazilians native americans don't count. I wish I knew this video existed so I could link this shit to her.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small Anastaciacl18 right it's the same for Africans. DNA is showing up that some of the "light skinned" ones as they call it are more \textbf{African} then some \textbf{African} Americans. Skin color means \textbf{nothing}. People get lighter from less sun exposer and some get darker from the sun. It's natural\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small "If you look at me I'm not \textbf{r\textbf{ed}}". No shit, you're not fully native either.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small Wesley W skin color means \textbf{nothing}. Who are you to say they are not "fully native" when your American asses are over here getting DNA tests to find out what you are! There are \textbf{African} American with light skin and come up more \textbf{African} then the darker ones sometimes.\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Wesley W sorry I'm not American. I just don't like how much Americans disrespect them. I had a playlist of DNA testing but it got disorganized but I'll have it up soon again. Africans themselves will say that they come in a range of skin colors not just stereotypical \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small I am \textbf{G\textbf{ay}} who are you to say they are not full when it's your asses getting DNA testing. Your disgusting to be using language to determine if they are native when your ignorant ass should do some research and get schooled on how they went through the boarding school system and basically beaten till they couldn't speak their language. That's the horrors they went threw. So if you use language to determine they are not native then your looking for a ass beating.\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@IridescentSoul I never said they not native chill u \textbf{g\textbf{ay}} fucker\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Gotta go to Canada for that just in northern Ontario alone you have tons of real crees and ojibwe with there language intact. Just the younger gen prefer to speak English with native/French slang into it. Like them theirs also a large French metis first \textbf{nation} population in the north.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Albino Natividad I think it's becuase we are around Americans so we speak like then😂🤦‍♀️ \textbf{DUMB} comment\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Natalie Rose this isnt a \textbf{dumb} comment this is an observation and comparison to other \textbf{indian} tribes in america. Native americans in the unitwd states have adopted american accent and speak english no one speaks native language while native americans in central and south america still speak their native langauage. So dont get mad.\normalsize   & \cellcolor{green!5}Dumb, Indian & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Also should every other \textbf{race} that also caused a genocide against other people have the same happen to them. [LINK]  [LINK]  [LINK]  [LINK]  [LINK]  [LINK]  [LINK] \normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small They were Black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Wasn't the whole 'red skin' thing because the natives in the area where the Europeans went had like a slightly reddish tint. It was something \textbf{dumb} like that. Hell the whole concept of \textbf{race} and skin color is \textbf{dumb}. Since like it's not just this person is \textbf{black} and this person is Asian. It's more like a scale. Like we consider Italians white but they weren't always. We consider Hispanic a \textbf{race} but it's just mixed indigenous and Spanish. And the indigenous people once came from Asia. Are they considered Asian? And what about the Chinese and the Japanese. They are both different in appearance yet they are still Asian\normalsize   & \cellcolor{green!27}Black, Dumb, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}5/110 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small health care has \textbf{nothing} to do with how you drink and eat Indians stop \textbf{alcohol} pop eating chips fast food\normalsize   & \cellcolor{green!5}Nothing, alcohol & \cellcolor{green!5}Age - Youngsters, Behavioural Addiction - Alcohol & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small 1. No one thinks this.2. This is not a myth. Depending on which tribe you're from, you may get lots of government handouts. "Where is my check?" Really? How about getting a job and working for a check instead of expecting others to hand one to you?3. This is also not a myth. And you didn't even address it! Really? Just a cheap, stupid dig at Donald Trump (who, OF COURSE, pays taxes, you idiots!)? Great way to politicize and brainwash these young girls, TV. Bravo.4. No one thinks this, either. Everyone knows that there are some Native American-run casinos. Try again.5. ...*facepalms* No one thinks this, either... 6. So, the southwestern Native American tribes who name their own sports teams "Redskins" are being \textbf{racist}? Against themselves? So much fail in this video.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/137 & \cellcolor{green!27}0.73 \\  \hline
  \cellcolor{green!5}\small I'm half \textbf{black} and Native American 🙏🏽💕\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Native Americans hates blacks please don't mix with us we don't want your \textbf{negro} gene\normalsize   & \cellcolor{green!27}Negro & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Scary God Not all natives hate blacks. They did \textbf{nothing} wrong towards us. Any negative or hurtful words you say after this to me I won't see because they don't deserve my attention. Bye....\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Scary God us natives and \textbf{black} went though a lot so we are actually friends don't know about you tho\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Dude u are a idiot native americans are not \textbf{black} stop saying such false accusations. Those anyone in this video even look half \textbf{black} or full \textbf{black} I don't think so so ur wrong\@anime lord\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/35 & \cellcolor{green!5}8.571 \\  \hline
  \cellcolor{green!27}\small Jalen HC no. And native Americans owned \textbf{African} slaves plantations.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Scary God are you \textbf{dumb}, just because someone says you look Native American and your not doesn't mean you can just claim to be that race\normalsize   & \cellcolor{green!5}Dumb, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Scary God I look like I'm a New Zealand native but that doesn't mean I can speak on their behalf or say that I'm one of them, because I'm not. It's almost 2019 and if you don't like mixed races then gtfo here. Your \textbf{racism} isn't appropriate or needed.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small theres \textbf{nothing} wrong with believing in God. if you dont agree you can respectfully disagree\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Cuz my great great grandmother is native was my color, i'am \textbf{black} and brown and she didn't have \textbf{african} decent....so.\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small And \textbf{african} americans aren't \textbf{african}. Either.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@cathy2000 No. \textbf{African} americans aren't \textbf{african} they are indigenous to the America's\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Black genes can ruin everytging. Were sorry for you\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small My grandpa is half \textbf{black} and half \textbf{Indian}. His mom was \textbf{Indian} and his dad was \textbf{black}. His mom had beautiful long hair.\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}4/23 & \cellcolor{green!27}17.391 \\  \hline
  \cellcolor{green!5}\small Scary God they love each other they don't have to be the same \textbf{race}. My mom is white and my dad is native\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I'm latino meaning having native, white, \textbf{black}, and that's all\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Paris Paris I apologize for all the hateful replies you're getting to your comment. I'm tri-racial (European, Afro Cuban and Native American) and it sucks when people talk to you as if you're less of a person for something you had no choice of in the first place! I get hated on by some white people because they think I'm Mexican, get hated on by some \textbf{black} people because I'm too white, it's ridiculous. F ‘em all. They're freaking stupid. I'm willing to bet you look 500times more attractive than some of these morons. lol.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Ok look. Just because your \textbf{black}. Doesn't make you a native American. Unless you actually are.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Scary God don't do that bc my grandfather was 100 Native American  and I'm half \textbf{black} and I go and play with my cousins they look at me as I'm one of them still\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Native Americans and \textbf{black} Americans are part European.  Maybe, you didn't know that...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Scary God dude there's evidence that the Indians were \textbf{black}. Christopher Columbus documented it himself when he thought he made it to India but wounded up in Haiti.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@Cali God wrong! Asians don't even have \textbf{Redskin}. I have \textbf{r\textbf{ed}} skin. Y'all are fuckin white! \textbf{Redskin} people hue was dark, but \textbf{r\textbf{ed}} in the sunlight. Get outta here with y'all lies. I know the fuckin truth.\normalsize   & \cellcolor{green!27}Red, Redskin & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}6/37 & \cellcolor{green!27}16.216 \\  \hline
  \cellcolor{green!5}\small \@Scary God That's not true I freaking love \textbf{black} people!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Scary God , the Spanish raped and plundered and sodomized their own children I don't blame you for not wanting to mix with the \textbf{black} people because we are superior to your neanderthal thinking. Short little Dwarfs!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Scary God you're fuckin \textbf{dumb} bruh Made 2 generalizations off top\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I am mixed \textbf{race} of White and First Nations as far as I know\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Scary God I have a white mom and a native dad. Racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Jayboirocks HCMostly true most \textbf{black} Americans are the real natives of America but lots of them do have some minor mix backgrounds too.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Same im \textbf{black} and Diné\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{black} and native American too girl! 😊💓\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small {BLITZ NATION} NORTHERN FRONTIER you can be mixed with both like one parent can be fully Native American and the other can be black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@Rochelle Isnana \textbf{nothing}!!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Keshonda-L'gayle Jackson No stop with that in ur pic u just look black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Scary God listen i know your trolling but natives ACTUALLY get along with \textbf{black} people really well and if you actually are a person of color why are you attacking other people of color?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small goobert goo dude you are \textbf{blind} ain't none of them look white there skin was brown I think you need to fix your eyes\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Felim Ryan I'm literally not even a liberal. Are you \textbf{dumb}? What about my statement was liberal? Lmfao\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small FUCKEN \$5 \textbf{INDIAN} COCKSUCKERS\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small they don't look \textbf{black} to me\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small The serious question though:Are \textbf{r\textbf{ed}} indians.... INDIANS?🇮🇳\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small serious answer though:Are ye fucking \textbf{dumb} mate?\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I met a few native Americans in the army they are head strong people but at the same time willing to listen and very understanding never met one in my life who didn't stand strong on their beliefs and ideals, they are like wolves you gotta be ready to to fight or get put in a cowards place \textbf{nothing} is given everything is respectfully earned\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Wow because this happend in your school it means it happens throughout all the nation\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small No \textbf{r\textbf{ed}} skin did not come from scalping it come from the fact that native Americans all had a \textbf{r\textbf{ed}} pigment in their skin but you can't see it in most natives because almost no one has pure native American blood\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/41 & \cellcolor{green!5}9.756 \\  \hline
  \cellcolor{green!27}\small I think the term "\textbf{R\textbf{ed}} Skin" came from , 1-the blood  that's on their faces (during  the \textbf{old} times) and 2- some of them have sun-kissed or brown skin that turns a bit \textbf{r\textbf{ed}}, mostly coz of the rush blood in their veins when it's cold just like what eskimos have. The second is just my theory , haha.  But, you got colors like \textbf{black}, white, brown, \textbf{y\textbf{e\textbf{llow}}}, why not \textbf{r\textbf{ed}} right?😆 And I don't think it's \textbf{racist}, \textbf{racism} is how you negatively perceive a certain \textbf{ethnicity} or make fun of how they look. I, for example  could be considered a \textbf{y\textbf{e\textbf{llow}}}-brown skin😊\normalsize   & \cellcolor{green!27}Black, Ethnicity, Old, Racism, Racist, Red, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}14/103 & \cellcolor{green!27}13.592 \\  \hline
  \cellcolor{green!5}\small \@anime lord yes but not on purpose since \textbf{nobody} knew how germs worked\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{Black} and I learn a lot of things about native Americans in my school and I'm in 8th grade so I'm 13 years \textbf{old} and today we're were talking about native Americans\normalsize   & \cellcolor{green!27}Black, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Ive got a PhD in Latin and \textbf{R\textbf{ed}} skin meant rudden, not \textbf{r\textbf{ed}} but a brown earth like. For example. \textbf{R\textbf{ed}} dog or \textbf{r\textbf{ed}} bird these are not \textbf{r\textbf{ed}} they are earth like.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}10/33 & \cellcolor{green!5}30.303 \\  \hline
  \cellcolor{green!27}\small most non native americans werent taught the truth in american history because text books were controlled by companies that are conservative and biased. also most non american indians do not understand tribal histories, laws, treaties. treaties are the one thing that are continually ignored by the us congress, especially with the current presidential adminstration and the department of the interior and the bureau of \textbf{indian} affairs. we need more american indians in top positions in government to oversee the laws governing tribes and prevent mismanagement, return treaty laws to current review and legislation, reopen the treaties and allow due process to the eventual returns of lands stolen by the us government from the treaty violations. paha sapa is a region in western south dakota that has been taken illegally and needs to be returned. the cash valuecis over one million dollars and is held in a trust fund. land is more important than the million dollars. the money is basically a cash settlement for the forfeiture of the paha sapa. after the 1876 battle of the little bighorn did the government truly took the paha sapa as a punishment and violation of the 1868 treaty. the us lost in 1876 and to show its punishment the us government allowed settlement and gold mining and passage by totally violating the fort laramie treaty. the united nations have sent messages to us congress that treaty violation is a violation of the native american indians right to sovereignty and their rightful ownership of that land which is sacred and spiritual territory.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/258 & \cellcolor{green!27}0.388 \\  \hline
  \cellcolor{green!5}\small my great  grandma was a \textbf{black} and native american and my my great grandfather was from barbados I dont know much about my grandfather but he was mixed    an had a good grade of hair people might not believe me and personal I dont care im learning about my family as I get older and I have a right to be who I am even though I have a little native and thats okay I dont like what natives are going though It pisses me off and its wrong period\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}\small Yes I'm \textbf{black}, native American, Brazillan and Japanese\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{crow} and Cheyenne\normalsize   & \cellcolor{green!5}Crow & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@Straight Lids stfu and this is how all obsessed kboo people act online \textbf{nobody} like you peopke smh\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small So I know y'all might say "oh we don't claim you"butnim \textbf{black} and native American from the Sacagawe and shoshoni tribe I have very curly hair\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small you cant believe everything your told it was quite peaceful here before occupation and we were advanced in our own way had cures for our own illnesses a long time ago before pre history there was a cataclysm that destroyed most of our civilization and there is many archaeological discoveries to prove we had an advanced civilization but unfortunately they are kept hidden from public knowledge to keep up the main  stream belief of what we native Americans were and are before Europeans came we were still recovering and healing from the damage our continent suffered  greed sickness war control of mens lives and freedoms did not exist in our different races of native Americans  and our open hearts love and  acceptance of all life under the creator  was taken advantage of we trusted loved  and accepted the European ancestors as our own and most lived in harmony but the European monarchs of that time saw more wealth and power in our sacred pure land and wanted to control it all bringing war to this land Spanish British and french fought for control destroyed the land and poisoned the native Americans killed are food sources and clean water in an attempt to bring us into extinction and the few of us that survived the genocide were rallied into segregated stripped naked of resource pockets of land where later on brought upon us there perverted twisted version of  the catholic religion saying our suffering would be taken if we submit to Christ and the lies and control structure of the church of that time i will add that though i am not religious that all the churches of the world into any Christ faith is blasphemy and Christ would be ashamed that his teachings were hijacked and twisted into a tool of control his words were simple love each other take care of each other no man is above another  and understand that our creator is always watching  with that said our children were forcefully taken into these residential schools beaten raped murdered and stripped of our moral beings and identities until they were closed not so long ago leaving us without our self respect culture and identities of who we are and where we came from constantly in a battle against \textbf{racism} stereotypes and being oppressed until this day so next time you see a native american poor drunk on drugs understand that this is not from being savagely or unintelligent people but people who are lost confused and have broken hearts and believe there is no hope for them in this civilization and society\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/435 & \cellcolor{green!27}0.23 \\  \hline
  \cellcolor{green!5}\small These pocaHauntUs women look \textbf{weird}. Heads up, Cortez and his men have come back to finish what they've started.Just joking people.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small You 100 do get government handouts and special treatment  if you are Federally recognized1. Indians only pay Federal tax they do not pay state tax, state sales taxes etc2. If your tribe has a treaty with the government you do get money via the BIA3. You get to extract resources or lease our mineral/resource rights on "\textbf{Indian} land" which you pay no tax on4. Youre allowed to build and run gambling operations on \textbf{indian} land5. You can sell tobacco tax free6. The BIA gives you free housing grants and funding\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Got it easier than i did growing up lower class, i didnt get any handouts,free housing etc and i didnt get any special education grants because of my \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Yup systematic \textbf{racism} than is as bad as now, no one should be denied rights or employment because of their skin colour, no one should be given any special treatment because of it either, why should someone get housing, education grants because they are indians and i get \textbf{nothing}?\normalsize   & \cellcolor{green!27}Nothing, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/49 & \cellcolor{green!27}4.082 \\  \hline
  \cellcolor{green!5}\small "I thought only Trump didn't pay taxes" 😂😂 I don't know how \textbf{old} they are but they're too much.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small I have a LOT of ancestors that are native american but i dont tell people that i have alot of genetics/dna blood etc from them because im white af and i would look \textbf{racist} 😂😂\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small I consider myself a \textbf{r\textbf{ed}} skin but I'm native Americans not making fun of them\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Im native american, Irish, french, and somewhat \textbf{African} american\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Who said I was talk about your ethnicity\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small We're not"\textbf{R\textbf{ED}}" THAT'S THE COLOR OF OUR BLOOD THAT WAS SPILT BECAUSE OUR FOREFATHERS AND MOTHER'S DIED FIGHTING FOR OUR LAND'S WHICH WAS STOLEN FROM US AND SOLD TO EUROPEAN PRICKS WERE STILL PERSICUTED AND ARRESTED FOR NON JUSTICE REASONS BECAUSE OF WHOM WE ARE TAKE FOR INSTANCE THE PIECE OF SHIT THING THEY CALL THE PRESIDENT OF THE UNITED STATES DONALD JACKASS TRUMP AND OTHERS OUT THERE THAT DON'T GIVE A FUCK ABOUT OUR CULTURE AND WE AS PEOPLE HELL YES WE ARE DIFFERENT THAN YOU! LET US ALONE AND LET US HAVE OUR LAND YOU'VE TAKEN WAY TOO MUCH AS IT IS! WE ARE STILL PRISONERS AGAINST OUR WILL'S WE WERE HERE FIRST DONALD TRUMP TALKS ABOUT IMAGRANTS WHAT ABOUT HIS GRANDPARENTS THEY WERE DEFINITELY IMAGRANTS!! We were 17,000 years before you were we are the originals here in this land\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/143 & \cellcolor{green!27}1.399 \\  \hline
  \cellcolor{green!5}\small All of us don't have light skin btw I'm Cherokee and people mistake me as \textbf{African} American just because my skin color.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Ever hear of the Minnesota Vikings?How about the Notre \textbf{Dame} Fighting Irish?Boston Celtics?Alfred University Saxons?\normalsize   & \cellcolor{green!5}Dame & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small What were you expecting? \textbf{Black}? You're an idiot\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I'm native American and once I was standing in line and this white lady pointed to an Asian family towards the head of line and said "you can go stand with your family you don't have to wait here" and then I started laughing and she got confused. (I LOOKED \textbf{NOTHING} LIKE THEM)\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small You are the ones making these misconceptions, \textbf{nobody} thinks think that ALL native americans STILL live in tipis, and the whole thing about taxes and 'free' healthcare and the whole \textbf{redskin} team name being 'racist' yet only now you care, what do I say.  You are using these people and their situation caused by a neglectful bureau as political tools to push an agenda and it is honestly disgusting, you all think in 'black' and 'white'.  You are the racists, just as you were 150 years ago when we took away your slaves\normalsize   & \cellcolor{green!27}Nobody, Redskin & \cellcolor{green!27}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small PAUL WISE 411. HOW MIS INFORMED ARE YOU MIXED BREEDS OF EUROPEAN ENGLANDERS AND EUROPEAN SPAINSH BLOOD!! YOU TWO WERE CALLED \$5 INDIANS!! THE ORIGINAL NATIVE INDIANS WERE PURE \textbf{BLACK} IN COLOR- BRONZE- COPPER PENNY IN COLOR- DARK BROWN!! ALL SOCALLED \textbf{BLACK} PEOPLE DIDNT COME HERE FROM AFRICA! THE SOCALLED BLACKMAN AND BLACKWOMEN WERE AND STILL BEEN HERE FOR 1000S OF YEARS!! THESE MIXED PEOPLE IN THESE VIDEO ARE OF WHITE- SPANISH EUROPEAN BLOOD! THEY ARE A NEW BREED OF PEOPLE CREATED BY THE MIXING IN WITH THE ORIGINAL \textbf{BLACK}- BRONZE- COPPER AND DARKBROWN ORIGINAL NATIVES DURING AND AFTER SLAVERY! THROUGH RAPE AND INNERRACIAL MARRIAGES!! ALL SOCALLED BLACKS ARE FROM AFRICA EVEN THOUGH YOU CAN FIND OUR BEGININGS FROM EVERY PART OF MOTHER EARTH!! LOOKUP \$5 INDIANS!! THEY ARE MIXED NOT DIRECT DESCENDANTS OF THE ORIGINAL NATIVE INDIANS!!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/138 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small People are so \textbf{dumb} I swear\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Sophia Peradze, whites stole \textbf{nothing} from the natives, it was simply a conquering of land, happens all the time\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Ain't gonna happen the whites took it over killed a bunch a people innocent people but that's no biggie to them. It's ok the \textbf{race} is gonna die out soon.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@\textbf{old} white dude Damn you are retarded\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@\textbf{old} white dude Good to know, we won't have to deal with \textbf{coloured} people all the time when we're dead!\normalsize   & \cellcolor{green!27}Old, coloured & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Moon Pilot good \textbf{colored} people won't have to deal with u pale skins\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@anime lord Besides, what do you define "\textbf{coloured}"?\normalsize   & \cellcolor{green!27}coloured & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I don't mean to be disrespectful but i bought a headdress because I love Native Americans. I love the history and I love learning about them. I wore it because I was interested in what it would feel like, it's sat on a shelf along with my pan flute. Well, I aim to put the pan flute there. Anyways, i noticed the headdress was made in Indonesia anyways which kinda annoyed me.. It then made me realise 😂 But I really have always wished I was Native American! The history is awesome and I'd be proud. Rather then being some pale, blonde, British... literally so boring! I was hoping so much to be even 1 Native American in my DNA test  because I believe it doesn't matter if you're 95 whatever and only 5 something else it still makes you equally that \textbf{nationality} because it's still in our blood, it's still the sa,e history and traditions our ancestors lived. Equally our ancestors from our 95 blood that's just more recent. But no.... Just Italy, England and Ireland and stuff. I'M SO JEALOUS!\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/182 & \cellcolor{green!5}0.549 \\  \hline
  \cellcolor{green!27}\small An even more \textbf{common} misconception is that they're NATIVE to these shores. They are genetically linked to Asians (certain physical attributes making that clear) therefore they are NOT any rightful heirs to anything. They were here before white Europeans, true. But the mere fact that their roots are prehistorically Asiatic suggests to me that they themselves were merauders who traversed the world , came upon this continent and more than likely uprooted the former inhabitants of this land...The same way we did much later. This "Noble Savage" myth is laughably untrue. They were just as capable of violence and cruelty as anyone else. White men are simply more evolved, culturally and biologically so our cruelty is more efficient.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/118 & \cellcolor{green!27}0.847 \\  \hline
  \cellcolor{green!5}\small People informed big time being native \textbf{Indian} means everything to me  because I am native \textbf{Indian} I didn't say I was American \textbf{Indian} I said I was native \textbf{Indian} Christopher Columbus was lost in our land he didn't know where the fuck he was after years went by they murdered our people raped our women stole our land and lied to us white man fucked us over again and again and again and again and again and again and again and again and again and again and again and again to no end in sight!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}4/95 & \cellcolor{green!5}4.211 \\  \hline
  \cellcolor{green!27}\small Most members of my tribe aren't liberals.  Teen Vogue you should be ashamed of your selves for exploiting these girls for your political agenda.  This video is very \textbf{racist} and stereotypical\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Ya'll are from Siberia. The oldest Americans the Paleoindian population looked like Africans Melanesians South Indians Negritos and Australians.  [LINK] Comparative morphological studies of the earliest human skeletons of the New World have shown that, whereas late prehistoric, recent, and present Native Americans tend to exhibit a cranial morphology similar to late and modern Northern Asians (short and wide neurocrania; high, orthognatic and broad faces; and relatively high and narrow orbits and noses), the earliest South Americans tend to be more similar to present Australians, Melanesians, and Sub-Saharan Africans (narrow and long neurocrania; prognatic, low faces; and relatively low and broad orbits and noses). However, most of the previous studies of early American human remains were based on small cranial samples. Herein we compare the largest sample of early American skulls ever studied (81 skulls of the Lagoa Santa region) with worldwide data sets representing global morphological variation in humans, through three different multivariate analyses. The results obtained from all multivariate analyses confirm a close morphological affinity between SouthAmerican Paleoindians and extant Australo-Melanesians groups, supporting the hypothesis that two distinct biological populations could have colonized the New World in the Pleistocene/Holocene \textbf{transition}.\normalsize   & \cellcolor{green!5}Transition & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/192 & \cellcolor{green!5}0.521 \\  \hline
  \cellcolor{green!27}\small Eat Tomato . They were shamans and priests merchants and sea navigators.  If the Siberians were ruling they invaded and went to war against the Paleoindians like their European, Middle Eastern North \textbf{African} , North \textbf{Indian} and East Asian cousins who later came and abused them. ( Gistory repeats itself) Anywhere you find Africans Melanesians South Indians Negrito and Australians you find a group of pale skinned straight haired people insisting  literally religiously and hypothetically that they are or were superior--placing themselves at the head of the dominance hierarchy . When Europeans arrived they said the natives were well built. I've seen how many Siberian descendants are shaped and they are a bit angular and not very well proportioned.\normalsize   & \cellcolor{green!27}African, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}2/119 & \cellcolor{green!27}1.681 \\  \hline
  \cellcolor{green!5}\small h h Sinodonty modern Asians don't exist in the fossil record until after 11 thousand years ago. Japan has evidence of inhabitants going back 50 thousand years ago. The Andamanese Jawara males carry the basal haplogroup which that of the Ainu and many Tibetan \textbf{ethnic} groups are down stream mutations of. Meaning most of these haplogroup mutations arose long before the Bering straight could  not be crossed yet they wanna claim Siberians were in the Americas before their phenotype was detected in Asia?Australia has been occupied for nearly 70 years by homo sapiens sapiens. This is no different than half of European males having the R1b1a1a2 which is the down stream mutation of R1b1a2 which non-admixed \textbf{African} males from Chad Niger Sudan Cameroon and Congo have. Europeans like East and Central Asians Middle Eastern North Africans and Ancestral North Indians largely can be described as a population that has inherited their characterizing cutaneous albinoid condition from an \textbf{African} Melanesian Negrito,South \textbf{Indian} or Australian ancestor.It's basic logic.\normalsize   & \cellcolor{green!5}African, Ethnic, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/167 & \cellcolor{green!5}2.395 \\  \hline
  \cellcolor{green!27}\small Eat Tomato You do realize they cannot pinpoint where geographically in the continent most \textbf{African} DNA comes from. Artificial borders and imposition by Indo Europeans invading who became the North \textbf{African} pale skinned populations followed by the Greco-Roman and later Arab/Turk/Middle Eastern religious wars and slavery as far South as Mali in the West and as far south as Zanzibar in the East. The sequestered clusters of \textbf{ethnic} groups and their unique genetic characteristics are in no way representative of their geographic place of origin. I'm West East Central and East \textbf{African} DNA I also have Melanesian ,East Asian and so called" Native American " DNA as well as West and East European DNA. My great grandmother who is 100 has Central American DNA which doesn't show up in any of her descendants.  They enslaved the natives who looked like Africans and Australo-Melanesians and sold them into the Caribbean and later the Americas. We have been here much longer than the pale skinned Siberians.\normalsize   & \cellcolor{green!27}African, Ethnic & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/164 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small this is \textbf{racist} stuff I may look white but I'm 4th generation native american and when I watched this i was so heart broke that those exist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Bryan Betancourt still butthurt over patriots loss? Don't have to be \textbf{racist} to take your anger out 😂 what did natives ever do to you?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Haha it's not l \textbf{ike} we have a mascot named whiteman..\normalsize   & \cellcolor{green!5}Ike & \cellcolor{green!5}Religious Identity - Jewish & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@TiffanyKirby86 A \textbf{yankee} is a person from the US. Since not all Americans are white that can be any \textbf{race}.\normalsize   & \cellcolor{green!27}Race, Yankee & \cellcolor{green!27}Ethnicity - General, Nationality - American & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Red Skin is another word for \textbf{R\textbf{ed}} Neck.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/8 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Black people were been indigenous in america. Not whites!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Jayboirocks HC \textbf{Black} people are about as indigenous as to america as whites are.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@B.E. Kid Adventures native american aith a \textbf{race} either...\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Liam Jayme \textbf{Nothing} has changed in nearly 300 years. I'll stick with history.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Liam Jayme You know \textbf{nothing} of America. You can't even spell America you sick Twitt.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Liam Jayme Stay on the Reservation where you belong. America has enough \textbf{lunatic} walking around with no health insurance.\normalsize   & \cellcolor{green!5}Lunatic & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@UCix0bA4Yx1J5HTWoMZDQ3IA You know \textbf{nothing} of culture either brain dead. How many years have you been married to your brother?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Liam Jayme HaHaHa go take your meds \textbf{lunatic}.\normalsize   & \cellcolor{green!5}Lunatic & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Liam Jayme More \textbf{Indian} non-sense.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small at the end of the day.. people are gonna talk shit about every \textbf{race} idk why... I guess evil, \textbf{dumb}, hypocritical people never change\normalsize   & \cellcolor{green!5}Dumb, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small red skin is not because of the blood!also,is super sad to see how they trained kids with lies about their past.All of that just to fill an agenda. wtf is wrong with murica,it used to be so cool now they are all pansies just like the uk\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Actually I think the reason Native Americans were called redskins way back then was because some tribes painted their whole bodies \textbf{r\textbf{ed}}. Hence '\textbf{r\textbf{ed}} skin'.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small I love how teen vogue shows so many cultures from people deep from that culture and \textbf{nationality}. Its beautiful to see people embracing their own cultures and not steeling others people's.\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small There is an \textbf{African} American man named Dane Calloway that claims that \textbf{black} people are the true Native Americans and he don't seem to know where the indigenous Natives came from. Is there some true Native that will debate him on this. Some one who have documents to back up their argument. He has several videos on Youtube claiming that, it is said he has 14 million views from all the videos and \textbf{black} people believe him and there appears to be a movement supporting his claim.\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/87 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small everything is racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I a AMERICAN INDIAN\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Technically your body holds so much sugar cause your \textbf{race} was not built to take in pure sugar like whites did for hundreds of years to your body its say wtf were did all this sugar come frome im gonna hold on to this\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Red skins was so call \textbf{black} people the real native americans\normalsize   & \cellcolor{green!5}Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small indians these days lol  , no wonder they are alcoholics and uber \textbf{fat} , all that roleplaying\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Dude it's just genetics. I'm Native American. I'm simply not built to be small. I'm at a healthy BMI and weight, I eat my fruits and veggies everyday, I work out. It's just not possible. Most of us are built that way. People call me \textbf{fat} but it's not like I can help it unless I starve myself which isn't remotely healthy.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small rocktokiohotel94 Some. Just as so. E White, \textbf{black}, brown, blue, ect are.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I don't like how people call native Americans \textbf{r\textbf{ed}} Indians like what!!!!  First of all they ain't \textbf{r\textbf{ed}} nor are they \textbf{Indian}.\normalsize   & \cellcolor{green!5}Indian, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}5/22 & \cellcolor{green!5}22.727 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{black}, native american, hispanic, and white. That makes me multiracial. They should change the name of that football team its just disrespectful and the fans need to stop wearing headdresses and painting their faces \textbf{r\textbf{ed}} because that is called whitewashing.This is apart of my heritage. My culture is not a costume\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small Fuck 90 of native Americans all you people are ignorant lazy rude fuckin people I lived around a Hochunk \textbf{nation} all a bunch of meth heads drunks\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Beautiful \textbf{race} ❤️\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small i like native amwrican than white americans whose ancestors were from Europe and they stole a land that is for \textbf{indian} people and these white people have a strong voice against them just like \textbf{racism} words.\normalsize   & \cellcolor{green!5}Indian, Racism & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I heard the term \textbf{redskin} came from the Spanish, when they met the Taino in the Caribbean. The Taino used to smear achiote on themselves to stop mosquitoes from biting them.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Why the term ‘redskin' is \textbf{racist}? I'm from Poland and I remember as a child reading book - there are different races: white, \textbf{y\textbf{e\textbf{llow}}}, \textbf{black} and \textbf{r\textbf{ed}}. I wouldn't get offended if I was called ‘whiteskin', and the term ‘redskin' is not \textbf{racist} in PL so please explain! :)\normalsize   & \cellcolor{green!5}Black, Racist, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}8/49 & \cellcolor{green!5}16.327 \\  \hline
  \cellcolor{green!27}\small olga bojar A \textbf{redskin} was known as the scalped head from a native american, They scalped them because it was a bounty you could turn them in for money\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Well it is True, if your are a indigenous native American \& can prove, u absolutely can get school grants \& monthly financial govt assistance. The term \textbf{Redskin}, (my own personal hypothesis) during the time when British first landed \& tried to claim the land as their own, the natives spent most their time outside. White ppl get sunburn. But we have melanin so we get \textbf{r\textbf{ed}}, but \textbf{tan}. And that's what I think. Upon UK 1st arrival, \& seeing natives for the 1st time, they never saw anyone with soon different from theirs. So they called it \textbf{Redskin}. I could be totally 100 wrong, I probably am, about skin color, Not wrong about school grants \& govt asst. But itsounds about right to me where the term \textbf{Redskin} came from.\normalsize   & \cellcolor{green!5}Red, Redskin, Tan & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - British & \cellcolor{green!5}6/131 & \cellcolor{green!5}4.58 \\  \hline
  \cellcolor{green!27}\small I've read all of these comments on here about how whites  are all these things. You guys are hypocrites. \textbf{Nobody} supports \textbf{racism}. We have racists, who are punished by society and the law. But to discriminate against whites just because of a thing that has been practiced for millenia. Everyone around the world has practice slavery. It's still practiced. You know where? Africa and the Middle East. You know how long whites have practice slavery compared to other races? The other races are represented my whole body, while whites are a single hand. Guess who sold off the first slaves to the Europeans. Blacks. Everyone here is ignorant. Hey TeenVogue wanna be unbiased and stop brainwashing us teens? Do you know what else we haven't been taught. Blacks sold off their people to the Europeans. The whites didn't swoop in and snatch them up. Their own people have forsaken them. You're a disgrace TeenVogue. You corrupt us the children, and you should be ashamed of yourselves. Instead of telling the whole truth, you only write about what supports your political agenda. Shame on you.\normalsize   & \cellcolor{green!27}Nobody, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/184 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}\small I totally respect them and admire, but I don't think the \textbf{r\textbf{ed}} skin thing is something \textbf{racist}, I mean of course, if they portrayed that all native Americans looks like the same stereotypical image of it, it is. But there are a lot of people around the world that are actually \textbf{r\textbf{ed}} skinned, so... yeah All my props for these people!\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}5/61 & \cellcolor{green!5}8.197 \\  \hline
  \cellcolor{green!27}\small Dave Dee its because the majority of Mexicans are Native American or have Native Blood so like I am Mexican and I identity as Native American as my \textbf{race} because Native American is beinge Native to the Americas\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small YourHotel IsDead yes they are lmao \textbf{dumb} bitch obviously you wouldn't know\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Liberals love there \textbf{ethnic} minority pets. Its disgusting how they politicise minorities to advance an agenda.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Im sure this video has been very informative for ignorant, stupid or \textbf{racist} people.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Nothing funny man, the native Americans should be paid good money every month by the US government for all the crime they did in the past against them. And as a matter of fact, they should have a leader they chose which is above the president\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small I think all native populations have misconceptions in \textbf{common}, we have them here in Sweden with the Sàmi-people too\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Fact: European-looking Native Americans are the same as the White people from Europe. The true Native Americans are \textbf{Black} and live among the \textbf{Black} people. Remember that saying, "They all look alike." It means the \textbf{Black} who came over on the slave ship looked the same as the Indians Christopher Columbus met. Study the \$5 \textbf{Indian} Law. You people are not the real Indians. [LINK] \normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}4/65 & \cellcolor{green!27}6.154 \\  \hline
  \cellcolor{green!5}\small 50 \textbf{nigga} ( well just clarify that n get it out the way).From Oklahoma 25 Creek n 25 Seminole  :)Where my Hvktes at (Native Girls)!!!:)\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Carmen Jones white? They're clearly brown! What you think natives look \textbf{black}?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Carmen Jones racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Do native \textbf{woman} like Mexican men?\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small No. Mines oji-cree first \textbf{nation} and is pretty \textbf{racist} to other tribes and doesnt think Mexicans are ndn lol\normalsize   & \cellcolor{green!5}Nation, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small \@Constantine Byzantine we didn't want your technology or your religion. We had our own forms but the US government didn't tolerate other people's ways and stripped us of our heritage through \textbf{Indian} Boarding schools. Gtfo out of here, loser.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Jerry FromUSA navajo \textbf{nation}. The biggest tribe in America dude. Some water even is radioactive...\normalsize   & \cellcolor{green!5}Jerry, Nation & \cellcolor{green!5}Nationality - General, Nationality - German & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Jerry FromUSA navajo \textbf{nation} is in the middle of nowhere in the desert. Also no casinos. The Hopi reservation and tribe is against casinos too and they are on the same land\normalsize   & \cellcolor{green!27}Jerry, Nation & \cellcolor{green!27}Nationality - General, Nationality - German & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Dåñk męmęš IDK but about \textbf{race} I would say Native American \textbf{Ethnicity} I would say Latino/a and \textbf{Nationality} Mexican/American\normalsize   & \cellcolor{green!5}Ethnicity, Nationality, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/19 & \cellcolor{green!5}15.789 \\  \hline
  \cellcolor{green!27}\small This kind of \textbf{racism} against american indians is ridiculous, here in brazil one in each three brazilians has some kind of indigenous decendence,n im so proud of my mixblooded decendence n my american \textbf{indian} fisionomy,no matter if my skin is clean.the ladies of this vids could be my sisters n cousins,i use my \textbf{black} n smooth hair long,n i just dont use baidings in public because in brazil the people will no undertand the mean of this.\normalsize   & \cellcolor{green!27}Black, Indian, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/77 & \cellcolor{green!27}3.896 \\  \hline
  \cellcolor{green!5}\small WoodsMan I am 48 percent other is 3 percent Sub Saharan \textbf{African} and 0.9 East Asian the rest good \textbf{old} Spanish\normalsize   & \cellcolor{green!5}African, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Gelber Lopez what's your \textbf{ethnicity}?\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small So a quick \textbf{racist} guide :White = Caucassian\textbf{Y\textbf{e\textbf{llow}}} = Asian in General (Chinese, Korean, Japanese)\textbf{R\textbf{ed}} = Native American\textbf{Black} = \textbf{African}, NigerianBrown = \textbf{Indian}, Southern Asia (Arabic, Persian, Emirates)So anything that I missed?\normalsize   & \cellcolor{green!5}African, Black, Indian, Racist, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}9/38 & \cellcolor{green!5}23.684 \\  \hline
  \cellcolor{green!27}\small The showed the \textbf{black} girl one time?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small It's a good thing we have 12 year \textbf{old} girls teaching us about stuff they don't rly know about\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Jose martino!\textbf{nobody} likes YOU!go die,noone cares🖕\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small You guys are so beautiful, more beautiful than the White (\textbf{Immigrant}) Americans...Our \textbf{ethnicity} resembles a lot.\normalsize   & \cellcolor{green!5}Ethnicity, Immigrant & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I'm so confused by this, my husband is native, my son is native, both status, \& both absolutely get free health care through the band, in fact my husband just got his entire mouth done and fixed including two root canals....free. He also does absolutely have the option of going to post secondary paid by his band....yes, he has to have the same academic requirements as everyone else in order to go to post secondary but so long as you have the grades, his band will pay for post secondary. His band also offers band housing (often just \$400 a month on average) for a brand new home built by the band for your family, all you have to do is put your name on the list and wait for your turn to come around and boom...the band will build you and your family a brand new home here on the reservation where we currently rent, sometimes you can be on that list for a couple of years so if we wanted a house faster, we just have to come up with 10 grand and the band will build us a home of our own brand new. There are LOTS of financial benefits, perhaps every band is just different. And I actually had a conversation about headdresses with one of my husbands uncles, I asked him is it true that only natives can put on a headdress, because it needs to be earned' and he just laughed and said 'point to a single native in this day in \textbf{age}, that has earned the right to put on a headdress  according to \textbf{old} values and traditions, you won't find many' just thought that was an interesting response, Anyways, clearly every band is very different, but to say these benefits are just wildly fabricated rumors across the board just simply isn't true. Oh and we also DO get tax free, we get tax free on anything on ANY band land, even if it's not YOUR band land, so long as your status, \& where I live that includes high end shops like Sephora even, the source, marks, name brand stores, tax free gas, tax free tobacco, tax free groceries, tax free makeup, tax free clothes. The tax never seems like much but it adds up. His band also sends out bonus \$250 every Christmas to each band member, plus a voucher for a turkey lol. he also gets all of his work gear paid for, shoes, tools, anything he needs for work, I literally could go on forever......\normalsize   & \cellcolor{green!27}Age, Old & \cellcolor{green!27}Age - General, Age - Over 65s & \cellcolor{green!27}2/426 & \cellcolor{green!27}0.469 \\  \hline
  \cellcolor{green!5}\small Red skin comes from blood.. we use to paint our faces and body  in human blood ..\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small 'We get \textbf{nothing} free' How are those government given reservations? Firstly I know for sure that Americans/Europeans shouldn't of been cruel and maybe tried to co exist but that is kind of false what she said\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small If Rex skin is disrespectful then why the hell did the leaders of aim use the slogan \textbf{R\textbf{ED}} PRIDE ??\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Bullshit native Americans get schooling for free i live in south dakota and its all over the radio tell native to go to native college and get it for free.  So go bull shit some where else.  Plus native Americans do get money for the casino.  And u need to stop calling your self \textbf{Indian} or even native Americans.  Because ur people every aka native tribe came from east Asia and cam here fallowing the buffalo and alot of the animals.  And u stole the land from the Viking and wiped oit their history\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}\small I do see lots of Indians wearing \textbf{black} why for hmm ?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Nobody thinks any of those things...\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small EC3 1: they're 2: Muslim isn't a \textbf{race}3: I don't know where you got the idea that I don't think Indians are humans. 4: The res is a mess because if the people living in it.5: This is anti white propaganda, and makes it look like the average person legitimately thinks any of the questions they were asked.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small this is what fetal \textbf{alcohol} syndrome looks like\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small 6 Misconceptions About Native American People That You've Never Heard Of? Are they actually \textbf{common}? Cause... I've never heard anyone even mention 5 of them, and the "\textbf{r\textbf{ed}} skin" thing only in a history lesson of "They used to be referred to as redskins, but their skin isn't actually \textbf{r\textbf{ed}} at all." And I'm nearly 27, living in the rural Deep South. You'd think misconceptions like those would run rampant down here. But no, I've never heard any of them. Actually, I haven't hear of most every "\textbf{common} misconception" of ANY minority group as being anything other than a misconception. It just makes me question where are all these people who actually have those misconceptions to make them \textbf{common}? Not saying any of these or any other minority are making it up. That'd be a \textbf{weird} thing to make up. It just doesn't make sense. \textbf{Common} like... Of the misconceptions that very few have, these are the most \textbf{common} among those? Or are they actually supposed to be \textbf{common} like the majority of U.S citizens have heard of them?\normalsize   & \cellcolor{green!5}Common, Red, Weird & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}11/179 & \cellcolor{green!5}6.145 \\  \hline
  \cellcolor{green!27}\small But how is \textbf{redskin} \textbf{racist} if native american isnt a \textbf{race} a girl here even called it an \textbf{ethnicity}? Im genuinely just trying to understand?\normalsize   & \cellcolor{green!27}Ethnicity, Race, Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/25 & \cellcolor{green!27}16.0 \\  \hline
  \cellcolor{green!5}\small Y'all are \textbf{Mongoloid} came. Across the bearing sea and mixed with the Olmec\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Bruh I'm white and I don't get offended when people call me white trash\normalsize   & \cellcolor{green!27}White Trash & \cellcolor{green!27}Ethnicity - White, Social Class - Working class & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small dragon hating Whites is \textbf{Racist}.yep after Years of people hating me for being European and my ancestorsI hate the Non-Europeans now\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small theres \textbf{nothing} wrong with living in a tipi full time\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small At my school, Indians get to go on a special trip just for them. The white kids are left at school. It's \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small This video is so stupid. \textbf{Nobody} would ask or wonder half of these questions. Everyone took 8th grade history. I'm Native American BTW\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small mran anime uh huh you are some \textbf{dumb} Bitch lol. fuck off\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small mran anime you are some \textbf{dumb} Bitch who don't know nothing\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small mran anime This is absolutely ridiculous. Name-calling doesn't win you arguments. You have \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small mran anime finno-uralic are Siberians a \textbf{Race} Germanic is a \textbf{Race} and \textbf{Ethnicity} and DNA and wordSlavic is a \textbf{Race} and \textbf{ethnicity} and DNA and Name.\normalsize   & \cellcolor{green!27}Ethnicity, Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}5/27 & \cellcolor{green!27}18.519 \\  \hline
  \cellcolor{green!5}\small Elizabeth Jerrett Thank you. 'mran anime' literally doesn't know anything about \textbf{race} or genetics. He's not even close to being the stupidest person I've debates though, which is a feat.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small mran anime You literally said in a previous comment 'There is \textbf{nothing} call germanic it's German'. You're shooting yourself in the foot here dude. You don't realize that what you're saying is stupid nonsense.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small La Original shut up you damn \textbf{racist} Bitch I seen you before you Afrocentric Cunt\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Phantom1op she is Afrocentric and \textbf{Racist}..\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small I am sure that many other cultures  from around the world knew this information. Thank you though. I believe the misconceptions of all American \textbf{indian} tribes were bought on and pushed even to this day by white americans..\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small i'm native and literally every time i mention it people are like 'but you're not \textbf{r\textbf{ed}}!' like no honey sit down\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small This stupid girl at my school says Full native Americans are \textbf{black}.  Bitch where.  can someone please proof me wrong or right?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Why is it ok to call a caucasian person 'white' but it's \textbf{racist} to call a native 'red'\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small In my country, the natives are named \textbf{redskin} by their skin's collor\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Go cry to the \textbf{Indian} casinos that make Billions of dollars every year while the ones on the reservations live in tin shacks...🤓\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Goddesses, Heroes, Shamans: Young People's Guide to Mythology - Japanese Kidneys Areas in Maryland図表(I am not native american)--  [LINK] Why people have japanese kidneys!(The gods voted and decided people are getting more Asian in all the good ways)Why the people live in townhomes not apartments!16 YO Nihonjin Judge working for the Supreme Court!!! HARUKO!!!We are under 18. Japanese Kid NEEDS!--- Apparently there was a huge problem with security guards (which japan always warns against) at stores and various places in Maryland. It just looked to foolish, we respect police not security guards who behave like gangs supposedly protected the ultrarich beyond the extent of the law.When you have lots of security guards it's always unfair and in this situation they were annoying and encouraging racial strife and they were charged for having pedophilia.Modern kids usually have no racial trauma in their early childhood unlike kids from the 60s, the attempt of guards to make everything about \textbf{racism} and transcending it wasn't good because we had more creative ideas that are not based on black/white models, but the zen that is beyond that. Now that they are gone kids of all heritages feel more able to be ourselves whether it's our traditional heritage image a mixmatch or something nonconformist. We are not being guilted to chose one story or perspective or convinced everyone who looks like that does these "insert behavior here" things. As a result we have better stories art music and more relevant things happening in the world. ----IN REALITY the stories that were most compatible with the modern world right now we're Japan's, Greece and Ireland. The truth is a lot of us are very interested. Our sincere heart is not with the mythos of these other people's however we respect it as equal!In the world where mass media exists, this is what you will see most often by far. It seems mean but in reality the Gods are just asking us what we like, we tell them in a vote and then they know what the majority is, no blame. (Mainly because these myths offer us access from the comfort of home with all our culture comforts we are used to, the other ones are literally trying to get us out in strange environments and it makes it more difficult, few do those but the reward is great if sincere, in contrast SO MANY do the japanese Greek and Irish ones)....清潔 love you, tripping ハートチャクラ ... 清潔 cleansing the aura... charging the folktales w love... goddesses heroes and shamans young peoples guide to world mythology.. my favorite book :) you have TIAMAT HILARY - Walter Johnson, everyone from your school that you know, none of them died what I mean is, they didn't grow up, TABEMASU.. there was some kind of bizarre eclipse and idunno,    somehow, they are all still 16, !    this is some kind of angelic code the universe recently started following... its not guided by the acts of man, but by the Heavens, i talked to a greek philosopher in the road who may have been a real person that fed suzanne ... mr feeny. SPIRITOFSHAWNHUNTERANDCORYMATTHEWS, it looks like teepees and suburban houses, these native americans have ancestral peace SOSEN NO HEIWA with us, because we've respected mother nature DAKARA SUNCHOU HAHANARUDAICHI.... our parents are honored THEYGOCRAZYFORNIHON.... I saw to the root of time which is that no matter what season they try to say it is, its actually only ever been now and now never really goes away, therefore time is not real and that means that weed is not physical, its an angel from a dream, which means that the world is like angelic.the roof opened up and the sky god mizochigabi accepted our thanks for this, smiling through heavenly clouds, mizochigabi just lunches, lunching Buddha. mizochigabi is the comedian when it is ther you eat well, whether serious or funny, you laugh, its healthy, it doesn't make fun of races. lol... its just thankful forest life technology from the HAWAIIAN BABYWOODROSE spirit that we have to be thankful for..its like, aloha... Microsoft.. there was a quest ...iching determines America votes for the spirit of good and obviously that is Clinton but its also other things///just thought about so much stuff... like meaningful stuff.. saw prince, we studied torah together lol, you guys were there! ... Japanese medicine... miraculously being there for you when you actually need me, and never in bad ways there wasso much heart chakra, the sunlight, there weredifficultparts but it never really was horrible, just so much life .. like this place is aliveClaire, please, karma's law, we are the immortals, but still, we are begging for wisdom here, hehe...  カリスマ,  .. I guess it wants to encourage us to kind of just say our style of communication is celestial and we don't feel shame for that which is most comfortable to us,  its also not what many people seem to believe it is. It's like Claire is a good person, one of the ancients who protects the planet,LOVENICKJOHNS\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/856 & \cellcolor{green!5}0.117 \\  \hline
  \cellcolor{green!27}\small Yeah but you guys are ugly except for the 2 \textbf{fat} ones you 2 look normal\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small We came through the storm, nooses on our neck and  a smallpox blanket to keep our numbers checked.On a 747 on the pentagon lawnWake up, the alarm clock is connected to a bomb.Anthrax lab on a west Virginia farm.Shorty ain't learned how to walk but already heavily armed.Civilians and little children is especially harmed.Camouflaged Torahs, bibles and glorious Qu'rans.The books that take you to heaven and let you meet the Lord there.Have become misinterpreted, reasons for warfare.We read em with \textbf{blind} eyes I guarantee you there's a lot more there.The rich must be \textbf{blind} because they didn't see the poor there.'The world is but a stage.'\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/117 & \cellcolor{green!5}1.709 \\  \hline
  \cellcolor{green!27}\small Their eyes look weird\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Why don't you take a DNA test and see that you are \textbf{nothing} but a so called white person from Europe.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I thought the Native Americans helped in the war of independence by scalping some of the British, or was it for the French? I'm not big up on American history, but I got a tattoo of an \textbf{Indian} American when I left school at 16, and I read about it after.  It's not going to go down well, with absolutely anyone.  Accept maybe the Irish, apparently, I read on Wikipedia, liked Buffalo Bill, but that things always full of..., or that they gave money to the Irish, or something. Maybe there's still a chance I could play this thing off?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}\small My god , I'm chippawean and no one in North Dakota thinks that native Americans live in tipis, I where weaves for my ancestors, and I beat the living shit out of someone for calling me a redskin\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Your teachings have been altered by the 'white man' during the reeducation and assimilation of your people. You are made to believe that you can claim entitlement over this great land. However, it is fact that the 'Pale' skinned mongoloids weren't enslaved do to there lack of technological advancements and their lower levels of thinking. It is not at all hard to see an example of this for it is true that your people believed you get reparations for stolen land. Who in the right mind would give there land to lying foreign invader and later fight back after they have the upper hand. As for the real \textbf{r\textbf{ed}} skins 'African-Americans' my people were killed, traded, and or enslaved do to our willingness to fight and our higher state of consciousness. It is clearly apparent that the white established governance over this glorifying land still to this day oppresses my people because they dont want the truth to be revealed.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/160 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small Marcell Holmes well asians and natives share many traits and are under the racial catergory of \textbf{mongoloid}.\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Yeah you arent \textbf{r\textbf{ed}} lol and thats a lie the name \textbf{r\textbf{ed}} skin is derived from the cooper and or rust colour of so called 'african americans'\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/27 & \cellcolor{green!27}14.815 \\  \hline
  \cellcolor{green!5}\small \@THE SERPENT KING  Serpent Lordz  The polar bear has \textbf{black} skin to keep itself warm, the fur has lack of melanin. Besides I wasn't talking about their skin was I? Their skins never see the daylight.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Marcell Holmes Native Americans are considered paleo mongoloids, which means we are older than the Asian looking neo mongoloids, such as Chinese, Japanese, Koreans. We been in the America's THOUSANDS of years before the neo \textbf{mongoloid} existed. Which explains why paleo Indians such as luzia, naia, and kennewick man had australoid skulls, because the \textbf{mongoloid} \textbf{race} only goes back 9,000 years, before that they had australoid skulls.\normalsize   & \cellcolor{green!27}Mongoloid, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/67 & \cellcolor{green!27}4.478 \\  \hline
  \cellcolor{green!5}\small \@Lakȟóta Ikče Wičašá You're a Native American on paper, not on stone! \textbf{Black} People RULED Mesoamerica.Again, the colossal heads are 100 proof that my ancestors have been here for ages. If your face has not been carved into stone then you should stfu because I don't see your \textbf{tan} face anywhere other than in text books. White man lies, you play the victim..sorry ass.\normalsize   & \cellcolor{green!5}Black, Tan & \cellcolor{green!5}Ethnicity - Black, Nationality - British & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small Serpent Lordz We're talking about the America's not Africa. I've seen white people with slanted eyes as well as high cheek bones, they're not just \textbf{mongoloid} features. Melanin isn't just present in negroid populations either, the ONLY people that don't have melanin are called albinos. Also anyone closer to the equator will be darker then those further away. You really need to do more research.\normalsize   & \cellcolor{green!27}Mongoloid & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Serpent Lordz Lmao your ancestors have no history here prior to the 1600's. You were brought up from Spanish America to the English colonies because they couldn't get us to be their slaves. After your ancestors were sold into slavery by their own people of course. I'm pretty sure more of my ancestors died on this land then yours. The genocide of millions of my people from the 1400's to the 1800's, they massacred whole villages of us. Foh! The land my tribe controlled and still live today has been ours for hundreds of years. We fought and defeated other tribes for it. Sorry no mixed mutt here, no European or \textbf{African} ancestry here, just straight up paleo \textbf{mongoloid}. No European last name either lol. But yet your women love sewing our hair into theirs?\normalsize   & \cellcolor{green!5}African, Mongoloid & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/135 & \cellcolor{green!5}1.481 \\  \hline
  \cellcolor{green!27}\small \@Terribly Good I'm Irish. I'm white what the fuck are you talking about you \textbf{dumb} shit\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@THE SERPENT KING bud you know the descendents of the Olmec are still around right? And that they look incredibly similar to the olmec heads? And that they aren't \textbf{black}? Africa has an incredibly rich and deep history, deeper than anywhere else on earth! There's no need to try to claim other cultures. Time and time again through history white people in the Americas have tried to claim that white cultures actually built native american monuments instead of recognizing the truth of native accomplishments. Do you understand why your claim would be incredibly upsetting in that context?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small Marcell Holmes racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Marcell Holmes how would you know someone's \textbf{race} just by looking at them? Lol stfu dumbass\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Another one is that you don't have to be \textbf{tan} or "Brown" to be Native American. I'm Choctaw and Cherokee and I'm white as a mf ghost and I have a CDIB. Just like you don't have to be Brown to be Hispanic.\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Native Americans don't really exist anymore u can be partly Native American but that's it. There just sensitive young teenagers, them two \textbf{fat} sisters look Asian probably because they have \textbf{fat} faces or they are half Chinese and like 15 native or something, your not a Native American if your mostly another \textbf{ethnicity} it means your partly native and clearly most of these people are probably more European or something.\normalsize   & \cellcolor{green!5}Ethnicity, Fat & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!5}3/70 & \cellcolor{green!5}4.286 \\  \hline
  \cellcolor{green!27}\small It sucks to know white people fucked up both sides of heritage \textbf{black} and native\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small 2:13, probably the name \textbf{r\textbf{ed}} skin was given because of some tribes in the sun belt had some what \textbf{r\textbf{ed}} skin,\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/21 & \cellcolor{green!5}19.048 \\  \hline
  \cellcolor{green!27}\small Let me slap the shit out of a white man and see who's more \textbf{R\textbf{ed}}!\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small I'm part native American. My skin was \textbf{r\textbf{ed}} when I was a baby but that was it. But I personally don't find the sports team \textbf{racist} at all. I could care less actually. I hate sports...with a passion.\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/38 & \cellcolor{green!5}7.895 \\  \hline
  \cellcolor{green!27}\small "That's \textbf{racist}" i'm dead😂😂😂😂😂 she is sooo pretty though\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small In 2:05 she said "but if you look at me i'm not \textbf{r\textbf{ed}}"  exactly and yet \textbf{African} and darker skinned people are called \textbf{black}. We are just 50 shades of brown. Anyways, regardless if native Americans are \textbf{r\textbf{ed}} or not they are still beautiful people with beautiful cultures :)\normalsize   & \cellcolor{green!5}African, Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}6/49 & \cellcolor{green!5}12.245 \\  \hline
  \cellcolor{green!27}\small i'm pretty sure  \textbf{nobody} thinks any of these things?these guys are just triggered\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I use to be a Washington fan because I was born in DC , but I had to examine my priorities and my moral stance against covert \textbf{racism} overshadowed my desire to connect with a football team. So I ride with my indigenous brothers and sisters on this.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small We are not \textbf{r\textbf{ed}},   it was the European White who called us that.   Why are ppl still so damn uneducated?   I graduated medical school... And didn't go for free\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small And Europeans are "white"?  While some of us, like myself, are pretty pasty, there are lots of olive, brown, and beige toned "white" people.  Even my super "white" brother has a \textbf{r\textbf{ed}}, rudy  undertone.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/34 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Newsflash, White and \textbf{Black} people are not actually white or \textbf{black} skinned. Yet obviously you don't consider it \textbf{racist} to use the term "White"... I'm not offended by it, because who gives a shit. I am, though, annoyed by ignorance.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/40 & \cellcolor{green!27}7.5 \\  \hline
  \cellcolor{green!5}\small Non-"MISS"-conception: American \textbf{Indian} women NEVER win a Miss Universe contest. P.S. The majority of winners are from South America and South American women = Latinas.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small BELIZEAN RENEGADE RIDAH and your \textbf{Race} will be forgotten\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small David Linares I know a \textbf{Woman} who is Yakut \textbf{Woman} mixed with Irish Yakut is East Asiatic but she has Blue eyes and Blonde hair and East Asiatic\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small 0:43 'if we had free healthcare, then our diabetes and heart disease rate would be low.'....this type of \textbf{blind} thinking could lead to extinction? The only reason I say that because I work in a non-reservation area, that's close to the Navajo reservation. As an outsider coming into the community I was very happy to learn about the native ways. The only things I've learned, (and I work with many retail outlets across the area) is that at least in the Navajo culture, education is 'advertised' that it's highly prioritized, but the way people act and treat each other really says a different story. I'm sorry but the constant assortment of Navajo people I deal with on a daily basis, I can safely say MOST are biased and rude, MOST DON'T like to use please and thank you, and If you need to sell a whole pallet of coke or blue bird flour at Walmart, it only takes 30 mins, and 10 mins on the first of the month. This video is redundant to me, and only shows me others ignorance.\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/181 & \cellcolor{green!27}0.552 \\  \hline
  \cellcolor{green!5}\small I'm Native American but \textbf{nobody} treats me like it because I don't look Native American\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Gabe Stagg I think I would know if I wasn't I mean my grandpa was dark asf and he wasn't \textbf{black} or hispanic\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small This is a random comnent, and I don't want to start a comment section \textbf{race} war but do Native Americans hate \textbf{black} people?\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Native Americans created racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Im Cherokee and \textbf{black} foot but im only half percent.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Navajos still live in Hogan's 👍💪. Check come from the casinos but Navajo tribes too big so I don't get any. We do get free healthcare through IHA lots of school have free tuition for natives. Redskins and all that other shit might've been \textbf{racist} but c'mon it's 2018 no one does that shit no more. It's not a big deal, just a word.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}\small lol... if u look at me im not \textbf{r\textbf{ed}} .. ofcourse u have some white in u XD\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small THERE ARE NATIVE AMERICANS FROM CANADA TO ARGENTINA..DIFF TRIBES DIFF CULTURES..NATIVE CPULD BE SAME \textbf{RACE}(TRIBE) BUT DIFF NATIONALUTIES..PPL NEED TO UNDERSTAND MATIONALITY IS NOT THE SAME AS RACE\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Of course you don't live in TP's and since when do people think you are all rich. It's also very obvious you don't have \textbf{r\textbf{ed}} skin XD All races get wrongly stereotyped and the largest misconception nowadays is that some people think that it is just white skinned people who are \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/52 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small Serenity Moon Let me say this. White supremacy and White privilege. How often do you here \textbf{Black} supremacy or \textbf{Black} privilege? Exactly though I do get what you mean and I agree not all Whites are \textbf{racist} but just understand that there is a reason why white people are always be called out for rasicim. Just think about it. As an Indigenous person or \textbf{Indian} boy as you would call me I never been sterotyped as rich or that I live in a TP. Only sterotyped for being poor, rude and that I get free handouts from the Government. \textbf{Racism} towards indigenous people in Canada is more worse than in America. You choose to believe me or not but I just explained some facts.\normalsize   & \cellcolor{green!27}Black, Indian, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}5/124 & \cellcolor{green!27}4.032 \\  \hline
  \cellcolor{green!5}\small Serenity Moon uhhhhhhhh cause it's mostly just white ppl. im guessing you're white and not a POC so you don't get to speak about \textbf{racism} as if you've experienced it. xD\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Flechxdimple Oh my God. Okay you must be so closed minded. Yes I am white and I understand that I don't get as much \textbf{racism} as others. But I have had \textbf{black} people asking my \textbf{black} friends why they hang out with white people like me. I have had \textbf{black} people calling my friends \textbf{dumb} because we're white. If that's not \textbf{racism} then what is?! I don't understand how you can't see that. It's awful how badly \textbf{black} people have been treated over the years. But that is no excuse to turn it around on white people because that makes them as bad as white people who are \textbf{racist}. I would never be \textbf{racist}, I never was, I grew up knowing that people's skin colour varies the same as hair and eye colours, and that is beautiful.\normalsize   & \cellcolor{green!27}Black, Dumb, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}9/137 & \cellcolor{green!27}6.569 \\  \hline
  \cellcolor{green!5}\small Serenity Moon i'm not closed minded. that's how i knew you were white. you can't be \textbf{racist} towards white ppl. even if some ppl tell you smth doesn't mean you understand the struggle of having \textbf{colored} skin. doesn't matter if you're not \textbf{racist}, you never understood people hating you or calling you names for being not white. people try to kill us cause we aren't white. people think my people r rapist and criminals cause were mexican. just because you get someone stereotyping you, don't act like you understand how \textbf{racism} works. i'm not closed minded, i just understand because that's exactly what a white person would say and i'm just stating the facts.\normalsize   & \cellcolor{green!5}Colored, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/114 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small Flechxdimple White people can get raped too. Maybe not because of their skin colour and I'm not stupid, people without white skin get it by far worse, point is though, \textbf{black} people can be \textbf{racist} too. Don't act like I talk different to you, of course people without white skin have been through shit because of whites. I can't compare with those experiences in the case of \textbf{racism}. I'm  sorry about that, but my second point being that my comment meant that not everyone who is white, is \textbf{racist}.\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/89 & \cellcolor{green!27}4.494 \\  \hline
  \cellcolor{green!5}\small Flechxdimple You CAN be \textbf{racist} towards a white person. Nowadays  all I see is fighting \textbf{racism} with \textbf{racism}. I hope you know some of your people also sold their OWN people as slaves and were racists to their own for probably having darker skin than themselves. Don't come at me with that bs that what I'm saying isn't true. Hell, some white people were slaves themselves for speaking up for POC. You're clearly living in the past tho. I'm not sure if you've noticed, but they've been giving us POC a lot of praise, attention, and calling our skin beautiful. Any \textbf{race} can be \textbf{racist}.\normalsize   & \cellcolor{green!5}Race, Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}5/105 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small g l oh i know. i'm not living in the past, you did not read my comments from earlier correctly. how can you be \textbf{racist} towards a white person? tell me. they're privileged, no one follows them around in a store, and they don't even get called names. they don't get made fun of for having different color skin. because i've never seen it. on the news they've never said anything about it. oh lucky you, some ppl aren't \textbf{racist} towards you. but yet the world is taking so many steps back from \textbf{racism} and it's become so much worse since donald trump going into office. i'm not saying trump is \textbf{racist} (he probably is) but ppl have always been \textbf{racist} but now they're not trying to hide it.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}5/129 & \cellcolor{green!27}3.876 \\  \hline
  \cellcolor{green!5}\small Flechxdimple "because I've never seen it" are you slow? In my city, a \textbf{black} man broke into a white man's house, killed him and raped his wife, all because they were white.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Flechxdimple You can be \textbf{racist} towards ANY person of ANY skin color. Maybe you haven't seen \textbf{racism} towards a white person, but I have, I'm saying this as a person of color. Just because you haven't seen it doesn't mean it doesn't exist.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small You are so wrong about almost everything you've said it hurts. You can be \textbf{racist} towards any skin color. And you said people of color get followed around in a store because the owner suspects them to steal shit? Yeah, that's because black/mexican people are waayy mor criminal than whites and asians.Also, no one is going around just killing POCs, that's just a retarded thing to say\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Actually there's no such thing as reverse \textbf{racism} - lookit up of you don't know what that is. \textbf{Racism} is based on color of skin so no a white person doesn't experience \textbf{racism}. Stereotyping/discrimination/nationalism etc is different, when people say why do you hang out with whites... that's not \textbf{racism}. White or white passing privilige is a real thing. One way it shows is not knowing what \textbf{racism} is.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}5/69 & \cellcolor{green!27}7.246 \\  \hline
  \cellcolor{green!5}\small Anna Leon yes \textbf{racism} is discrimination based on color of your skin. So white (or rather beige) isn't a color? What are you on about?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Farn0 Ok. So what's your point?  That's because its a "color" they automatically experience \textbf{racism} ?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Anna Leon of course they do! If someone hates a white man because he's white it's \textbf{racism}. If someone hates a \textbf{black} man because of his skin color it's also \textbf{racism}.\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/31 & \cellcolor{green!5}9.677 \\  \hline
  \cellcolor{green!27}\small Serenity Moon, you fit the word \textbf{racist} perfect.  I grew up in \textbf{racism} from the british side of my family (fathers). Only love my Cherokee Mothers. This will become Reality (shall lay before them their evil thoughts, and the torments where with they shall begin to be tormented)\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/48 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I get what you're saying but majority of the population in North American countries are white and the rest are minorities so overall when I see \textbf{racism} or experience it it's because of white people so that's what created the misconception that you're all racist\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small Flechxdimple You're both \textbf{racist} and ethnocentric. \textbf{Racism} is prejudice based on skin color. White is as much a color as is \textbf{black}. Just because you live in a white-majority country (so statistically you're more likely to experience \textbf{racism} against blacks by whites) doesn't mean \textbf{racism} against whites by blacks doesn't happen in \textbf{black}-majority countries, or even \textbf{black} majority areas within the US, simultaneously. How do you think Zimbabwe's hyperinflation happened?\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}6/70 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small yourallsinners 1 What have I said that is \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Donald Trump Oh yeah no I agree. People who are not white get far more \textbf{racism}, but that doesn't mean that whites don't get \textbf{racism}, so I agree.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Serenity Moon redskins is a term for a native scalp not the colour of their skin.....when will Americans gonna see how \textbf{racist} "redskins" really is?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Flechxdimple asian is a \textbf{race} and i think they meant latino not mexican\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I get commented how I don't fit in with the physical sterotypes. Like the white and \textbf{black} classmates of mine think that native american teens are either bulky or stick \textbf{skinny}. But im neither of those. I am also not dark brown/red skinned and i don't have that native accent.\normalsize   & \cellcolor{green!5}Black, Skinny & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Serenity Moon wow they called you \textbf{dumb} you've been through soooo much\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small And I absolutely agree that other races get far more \textbf{racism}. I mean there is a very very small percentage of Native Americans left. And people are STILL \textbf{racist} towards \textbf{African} Americans. And you barely ever meet a Jew. But, with that being said, you still can be \textbf{racist} towards any \textbf{race}. But that doesn't mean I want you to feel bad for white people, I'm just trying to prove a point.\normalsize   & \cellcolor{green!5}African, Race, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}5/72 & \cellcolor{green!5}6.944 \\  \hline
  \cellcolor{green!27}\small Anna Leon \textbf{racism} is based on colour of skin, yeah so you can be \textbf{racist} to a white person because their skin is white\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Blacks and AFFIRMATIVE ACTION . Blacks have WAAAAAAY more priviledge than any other \textbf{race} and they are still playing the victim and whining . the worst people in the world are \textbf{black} women . the men not so much.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small Let's just ignore the systemic eradication of their history, religion and culture as well as the abhorrent methods of treatment our US government did unto them even through the 70s and early 80s. Forcing their women not to have children and giving them ridiculous sentences in court all the while allowing corporations to overtake their privately owned land for no reason other than to make a bunch of \textbf{fat} suits more money.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small \@Flechxdimple actually again from a person of color myself it's \textbf{racist} to say that a person can't be something.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Flechxdimple first how are you going to tell me what \textbf{race} i am! second white privilege doesn't exited in America. and if it does where your proof? third how would you like it if told you what \textbf{race} you were?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Serenity Moon actually called \textbf{ethnicity} there is only one \textbf{race} the human race\normalsize   & \cellcolor{green!5}Ethnicity, Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/13 & \cellcolor{green!5}23.077 \\  \hline
  \cellcolor{green!27}\small A lot of people think only Germans are \textbf{racist} because of Germany's past\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Anna Gabriela definition;"\textbf{racism}ˈreɪsɪz(ə)m/nounprejudice, discrimination, or antagonism directed against someone of a different \textbf{race} based on the belief that one's own \textbf{race} is superior."a programme to combat \textbf{racism}"synonyms:racial discrimination, racialism, racial prejudice/bigotry, \textbf{xenophobia}, chauvinism, bigotry, bias, intolerance; Morethe belief that all members of each \textbf{race} possess characteristics, abilities, or qualities specific to that \textbf{race}, especially so as to distinguish it as inferior or superior to another \textbf{race} or races"So yes, white people can experience \textbf{racism} as well.\normalsize   & \cellcolor{green!5}Race, Racism, Xenophobia & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}9/84 & \cellcolor{green!5}10.714 \\  \hline
  \cellcolor{green!27}\small \@Flechxdimple Are you \textbf{dumb}? Have you not seen the video where \textbf{black} students blocked the entrance of a school and only let \textbf{coloured} people through?\normalsize   & \cellcolor{green!27}Black, Dumb, coloured & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/25 & \cellcolor{green!27}12.0 \\  \hline
  \cellcolor{green!5}\small \@Anna Gabriela If I said "why do you hang out with blacks?" Wouldn't that offend you?Also reverse \textbf{racism} isn't a thing, \textbf{racism} is always \textbf{racism}!!! You're telling me white isn't a skin colour? Neither is \textbf{black}, because they're tints. And actually I have experienced stereotyping, and \textbf{racism}. Don't come at me saying "stereotyping isn't a bad thing" people get triggered when you say "\textbf{black} people love chicken".\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}6/68 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small \@Flechxdimple Asian is a \textbf{race} actually. Do you think they're just white people?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Beden Huncho Back to Africa you \textbf{racist} hoe!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Anna Gabriela It's not an opinion, \textbf{hun}. It's a fact, as you seem to claim alot of them.I \@ you because I wanted to explain it to you, that's what the comment section for is. This video just appeared in my recommended, that's why I replied months later."I'm not interested in this conversation, yet you replied to me, if you really weren't interested in it you wouldn't have replied. Bye bye!\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Moon Pilot you're \textbf{racist}. i'm not dealing with a \textbf{racist}. you'll never get it through your head.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small \@Flechxdimple Lmao, \textbf{nothing} left to say, and how am I \textbf{racist} again? Nice try.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Zimmer i heard more time white supremacy because \textbf{nobody} would argue that blacks are superior besides your arguments suggests that you think stereotypes are also true.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Many of you people don't know the difference between \textbf{racism} and prejudice...smh\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Wolfae Fox So someone from a different \textbf{race} calls you \textbf{dumb} there \textbf{racist}? Lmfao funniest shit I've heard all day\normalsize   & \cellcolor{green!5}Dumb, Race, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/20 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small Stop being a baby ...you people that get offended for the stupidest words. Just shut up and suck it up. Also, if you get "triggered" for getting ask why you hang with \textbf{black} people or white  just tell am cuz u want too and move on .....why don't you deal with real \textbf{racism} ? I'm Mexican and I get followed at stores.....but I don't care cuz I'm not stealing and ima keep on shopping the same way if they're following me or not. during that moment I didn't feel less privileged then any white people .\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Zimmer There's lot of \textbf{racist} First Nations people There's a lot of \textbf{racist} blacks, Whites, Pacific Islanders, Hispanics, Etc\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Wolfae Fox You know what's really hilarious? Over 800,000 Jews left Europe during the so-called "Holocaust" to Mexico. Look at any Mexican today they look little to \textbf{nothing} like the Native Americans you seen before they were "colonized by white people". They were literally orientals with dark skin. Almost all of Mexicans today look Middle Eastern. There was a Mexican educator who tested his genealogy and found he was Jewish. He did this for some 60 other people and found they were all Jewish even though they claimed "pure" Native American heritage. So yes, if Mexico was "conquered by the evil whites" as our "History texts" so claim wouldn't all Mexicans today be blonde haired with blue eyes like the Norwegians are? I just love how today's generation of "Mexicans with Native heritage" attack white people for the Native massacre yet have \textbf{zero} connection to these people. Because they're ALL Jewish and stole their identity!\normalsize   & \cellcolor{green!27}Nothing, Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/155 & \cellcolor{green!27}1.29 \\  \hline
  \cellcolor{green!5}\small \@Anna Gabriela Merriam-Webster Definition- a belief that \textbf{race} is the primary determinant of human traits and capacities and that racial differences produce an inherent superiority of a particular \textbf{race}Last time I checked, there's no such thing as reverse \textbf{racism}, just racism\normalsize   & \cellcolor{green!5}Race, Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/42 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small I think they are called \textbf{r\textbf{ed}} skin cause they can become \textbf{r\textbf{ed}} when they are hot just like white people unlike indians who won't blush under any circumstances\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/28 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Josta Heers i agree with you but i have to hit you with the jews are a \textbf{race} no they are a religion\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Lee Francis How \textbf{old} are you?who just says too bad, that doesn't even make any sense lol\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small People call us INDIANS because of Columbus. He thought he discovered India and yet India is clear across he world. It's not correct to call us that. Most other languages call us in some way \textbf{Indian} because of Columbus. I have to be honest. When anyone calls NATIVE AMERICANS Indians I get so pissed off.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Lee Francis not being rude. But NO it doesn't mean the same thing. We are NATIVE not \textbf{Indian} because that means we come from India which we don't. Please use the correct word.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small SavetheWorld Girl lt \textbf{indian} you never were Americans.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@Lee Francis And we were here before any "americans" were. I'm surprised a 70 year \textbf{old} wouldn't know that.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Lee Francis We were the FIRST Americans. Everyone else was an \textbf{immigrant}.\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Lee Francis if you're 70 how come you can't fucking spell and act like a 10 year \textbf{old} 😂😂\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small SavetheWorld Girl If you want to be that picky, you're not Native AMERICAN either. America is the European founding name of the lands Europeans took control of. So to be honest, insisting on being called Native American is worse. At least with "\textbf{Indian}", you're just rolling with a mistaken use of proper nouns. But with native "American", you choose to ide tify with the white man's name for the land he took.Just refer to yourself as your tribe name. And as to skmething you said to someone else, yes there were nations. Northeastern Peoples of the Land had nations and confederacies with permanent settlements. They did not roam. The People of the Plains roamed, but by the time Europeans arrived, there was no connection between the two. It would be like assuming Irish and Estonians are the same because "Europe" and "white people".\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/144 & \cellcolor{green!5}0.694 \\  \hline
  \cellcolor{green!27}\small Ok but Native Americans were the first people to live in America and therefore it is their native land,Columbus didn't 'discover' shit,people were already there,and he wasn't even the first European to find America.The Natives were her first and everyone else is an \textbf{immigrant},plain and simple\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small SavetheWorld Girl So if you're a native, are u \textbf{black}? Well Native means Indeginous people of the planet which are blacks, hello.... You're just Mongoloids grafted by Yaku\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small \@PubliusAfricanus whats the point? go study about racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@dxelson i cant speak for other natives but up here in canada we still refere ourselves as native americans because we talk about the continent itself. but we ONLY say that when speaking in english,french ect. we do have a name for the north american continent and our tribe name. im not a fan of people using the term ''\textbf{indian}''  as its incorrect but i usually ask them to just refer us by tribe and use native american ( or anishinaabekaa in my case(ojibwe for ''there are (a lot of) people'')) when talking about the whole popuation of pre-columbian humans in the americas.now when it comes to the portugese language with Índios and Indianos im cool with that since they deliberate changed the name for both parties to differentiate the two. but when you just say \textbf{indian} with no context then it makes no sense.also there was at least one confederation of natives befor the europeans came who actually hade a set of rules that were used bu the us to make the constitution! i present the Iroquois Confederacy  [LINK]  this video explanes that better.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/185 & \cellcolor{green!5}0.541 \\  \hline
  \cellcolor{green!27}\small But that isn't same in every language. In Finnish \textbf{Indian} (India living person) is "intialainen" and native americans "intiaani"\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I still call myself indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I have heard them refer to themselves as the \textbf{Indian} \textbf{nation} by their secretary of state. \textbf{Indian} it is.\normalsize   & \cellcolor{green!27}Indian, Nation & \cellcolor{green!27}Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small racist. a disrespectful word to my culture.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small SavetheWorld Girl As a real \textbf{indian}, I can agree. I get so confused when someone's says \textbf{Indian}. Idk if they mean us or native Americans.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Omg they call then \textbf{r\textbf{ed}} Indians it's so messed up\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \@Lee Francis honeslty I give 2 shits. \textbf{Indian} native american whats the difference 😭😭😂😂\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@we 3rd The indians isolate themselfs on reservations, and have limitied contact with everday Americans. Their children attend \textbf{indian} ran schools they live in the past, and behind the times.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@TFO Cyborg indians are \textbf{nothing} but an embrassements.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Lee Francis I can't tell if you're 10 or just \textbf{dumb} and ignorant\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Lee Francis, you said you were 70? Ha that's funny because I didn't think 70 year olds were as stupid to tell someone '''your life is a joke''' and saying that the other person is ''a laugh of the entire world'' Because that just YOU, you are the one that's making a fool of yourself! Do you wonder why \textbf{nobody} here sided with you? It's because you have trashy reasons for a trashy point. Might as well say that the world has pollution and it's all Hawaii's fault, it's just as stupid as saying that ''NaTiVe AmErIcAnS aRe iNdIaNs''\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small Lee Francis, now \textbf{nobody} knows which Indians you are talking about, Native Americans (not Indians) or actual Indians!\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Colours its so disrespectful when i tell idiots that im native american they say oh your that kind of \textbf{indian}? Or that \textbf{indian} pointing there fingers on there forehead. It upsets me that its \textbf{racist}.\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small \@PubliusAfricanus yeah because they are dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Renenutet666 Renenutet666 yeah we are \textbf{black} and we have every right to say we are cause we are\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Lee Francis what facts for looking at us because of our skin color and just to say we're \textbf{Indian} yeah totally facts\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small \@pygronze.2 Your \textbf{nothing} but trash.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Glerii But your color is what tells it all, so Mongoloids and Caucasoids aren't trying to be \textbf{black} because most of them have not prevented the system that has oppressed the indigenous \textbf{black} people of the planet, but have added on to the problem... Aquarius \textbf{Age} will really tell\normalsize   & \cellcolor{green!5}Age, Black & \cellcolor{green!5}Age - General, Ethnicity - Black & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small \@Lee Francis ummmmm ew I'm sorry but ur a bit \textbf{old} to be spamming me\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@i am not here anymore Never too \textbf{old} to she'd the light.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@i am not here anymore What happened to the \textbf{Indian} and Buffalo on the Nickel?\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@FFOO FFUU l know l've been around to long \textbf{Indian}.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Lonely Spirit If anyone is a \textbf{racist} it's you. I don't have time for evil like you.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Columbus was searching for Indians and that's why they called Indians and it's seriously annoying that \textbf{Indian},USA and Uk history is all started Together\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Satan The devil no Columbus was searching for the lost tribes of Israel as he stated in his book , he didn't get LOST , because he only heard about the new world after Cortez and desoto took over and were already here!! Columbus never came to the main land he only landed in Puerto Rico!!! And he called them Indians because \textbf{old} English the word indio means DARK HUE , the first natives were copper \textbf{colored} , now thy are all asian and white , that's why the \textbf{redskin} mascot is so dark because that's what the REAL Indians look like , and the real Indians are the so called negroes and blacks\normalsize   & \cellcolor{green!27}Colored, Old, Redskin & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/114 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Lee Francis you also lived in a time of \textbf{racism} and oppression. Just cause you're \textbf{old} doesn't make it right. Sit down girl\normalsize   & \cellcolor{green!5}Old, Racism & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Calling natives indians is like saying the n word or calling a white man snowflake\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Matthew Dorry excuse me, but as someone who has Cherokee Native American heritage, it's very rude and disrespectful to call native Americans Indians. If you put a Native American next to a \textbf{Indian} they look \textbf{nothing} alike. You people just don't get it. 1) we're not Indians, 2) we are the only true American people, and 3) if you're going to be on the land at least be respectful. Thank you repent and have a great day\normalsize   & \cellcolor{green!5}Indian, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small \@Edgy 9 year \textbf{old} No one's fault it's just something that happened. Indians want to blame the White Man for everything, because they weren't smart enough to start a Country.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck Check out the Lincoln Memorial, and read the words, it's telling who brought forth a new \textbf{Nation}.\normalsize   & \cellcolor{green!5}Crazy, Nation & \cellcolor{green!5}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck Lol you stay ignorant.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck That's what l thought a dummy would say.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck You've always been a do \textbf{nothing} \textbf{Bum}.\normalsize   & \cellcolor{green!27}Bum, Crazy, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments, Social Class - Destitute & \cellcolor{green!27}3/9 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck No wonder the Indians are premitive you teaching them.lol\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck is \textbf{crazy} for \textbf{black} guys.lol\normalsize   & \cellcolor{green!27}Black, Crazy & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/7 & \cellcolor{green!27}42.857 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck likes \textbf{black} guys.lol\normalsize   & \cellcolor{green!5}Black, Crazy & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck your \textbf{crazy} for \textbf{black} guys.lol\normalsize   & \cellcolor{green!27}Black, Crazy & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/7 & \cellcolor{green!27}42.857 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck No habla Espanol Stupido.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Lee Francis and you are \textbf{nothing} but a disappoinment.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@PubliusAfricanus I'm Native American \textbf{Indian} and my skin is \textbf{r\textbf{ed}} \& I do not mind being called \textbf{Indian}.  I just wish my own \textbf{Indian} Govrnment leaders would make up their minds what we are to be called Indigenous or Aboriginal or First Nations.  Here in Canada anyways.\normalsize   & \cellcolor{green!5}Indian, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}5/47 & \cellcolor{green!5}10.638 \\  \hline
  \cellcolor{green!27}\small \@Renenutet666 Renenutet666 Native Americans are of the Tribe of Gad of The Israelites of the Bible and are \textbf{R\textbf{ed}} Skinned, like Asians are \textbf{Y\textbf{e\textbf{llow}}}, Blacks are \textbf{Black}, Latinos are Brown, and Indians hmmm. Brown \textbf{Black}.? Best to ask them cuz I do not really know.  And what about Middle East?  Same as India?  All are people and should be treated the same. If someone of say Middle East would correct me or say, they are considered this skin color.   Well, I would believe them.  No non-color of that \textbf{race} can call someone else a different color.  Like Asians won't say they are \textbf{R\textbf{ed}}.\normalsize   & \cellcolor{green!27}Black, Race, Red, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}10/103 & \cellcolor{green!27}9.709 \\  \hline
  \cellcolor{green!5}\small PubliusAfricanus no they're saying that's it's disrespectful to call another \textbf{race} Indians when the Indians in Asia have \textbf{nothing} to do with them.\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small \@yeet What's all this "you" nonsense? Are you under the impression that white people are immortal? Are you responsible for whatever crime someone of your \textbf{ethnicity} committed centuries ago?\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@Faithful Nerd well that would be offensive even to an actual \textbf{Indian} like myself\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small why native americans are still refered as indians.It was that columbus who discovered america but he felt that it was india and refered natives as \textbf{indian}.But they should be refered as aemerican.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Please school me I know \textbf{nothing} about the current Native American culture\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Hey um native to probs \textbf{nobody} believe me but ya\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I'm red\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small Crossed the bering strait and invaded the copper \textbf{colored} so called blacks.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small YOU PEOPLE ARE IMPOSTERS AND ARE SIBERIANS AND EURASIANS CLAIMING TO BE MY PEOPLE , THE TRUE INDIANS ARE THE SO CALLED \textbf{AFRICAN} AMERICAN AKA BLACKS , YOU PPL WILL PAY FOR LYING\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Gabe Stagg stfu you \textbf{FAT} ass bitch I know my blood line , you whites ARE \textbf{NOTHING} BUT LIARS , you whites want to everyone but you , you claim to be Native you claim to be Jews you claim to be Egyptians , THE WHITE \textbf{RACE} HAS NO CREDIBILITY AND IS A COMPLETE JOKE😂😂😂\normalsize   & \cellcolor{green!27}Fat, Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}3/55 & \cellcolor{green!27}5.455 \\  \hline
  \cellcolor{green!5}\small I never knew that I had some Native American/\textbf{Indian} blood until I moved in with my grandmother when I was \textbf{age} 22.  Once in high school someone told me that I looked Chinese because I had high cheekbones.  My grandmother, though mostly of Anglo-Celtic ancestry, had extremely large high cheekbones,  hidden upper eyelids, and other \textbf{Indian} features.  Her NA features were very beautiful.  She wouldn't admit that she had some \textbf{Indian} blood, but sometime between the "Mayflower" and her birth, her ancestors obviously mixed with Native Americans.  Anyone who has any NA ancestry should be PROUD of it!\normalsize   & \cellcolor{green!5}Age, Indian & \cellcolor{green!5}Age - General, Ethnicity - Native-American & \cellcolor{green!5}3/98 & \cellcolor{green!5}3.061 \\  \hline
  \cellcolor{green!27}\small Sofia Some Mexicans are white, some are \textbf{black},  and some are Arab or Asian.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Dont be so obtuse . Everybody knows that Texas and southern California ,New Mexico ,parts of Nevada and Arizona were Mexican . They were lost in the wars . Thats the way of the world . Parts of Europe  were lost . Everybody lost something way back . stop whining . you sound like the whiny BLM . What \textbf{racist} POS they are.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small actually there are mexicans that aren't native. i'd say majority are native descendant but some mexicans alike every other hispanic country are mixed with white (spaniard) and black\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small man, you're a native because you're Mexican. All the south of US was stolen from México, the north from the natives. So, if you have an hispanic name, girl, you're welcome. You're lucky to be Mexican. With all my respect to the native americans, that are in \textbf{racist} and pressed reservation, forgotten by the government that have always killed them. Saludos.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small Most Mexicans are half white half native with like 3-5 \textbf{African}. There are lots of Mexicans who are full indigenous. Especially in the south of Mexico. Peru has the largest Percentage of native Americans in Latin America.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small People saying that all Latinx people are Native American... you're terribly wrong. Latin America is a land of racial mixing. Argentina and Uruguay for example are almost entirely white. Brazil es pretty white too (they just elected a white supremacist as president). Other countries are more Native American and others more \textbf{Black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Daniel Embree stfu only 1 of Mexico is \textbf{black}.  Mexico is a proud country of Natives, mestizos, and Spaniards.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Mexicans are native central american maybe.....anyways most mexicans are mixed nowday with a lot of european blood and some have subsaharan \textbf{african} blood in em\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small 666 666 Most of the \textbf{African} blood is too little to consider ourselves triracial.  Even if you have curly hair or big lips I consider you indigenous as long as your nose and eyes look native, if you're Mexican.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small 666 666 By culture, but everyone can take one look at a mestizo and see his flatter jawline, \textbf{black} hair, \textbf{black} eyes, etc.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small btw most mexicans are part native and european, some \textbf{black} not as much as for example puerto ricans...but yeah we are mestizo mostly\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small ehm yes i live in a country with many many native mixed ppl bolivians peruvians and paraguayans often have 50-80 native dnathese folks in this videos mos def all of them except one have less in the same time none of the  bolivian peruvian folks who are very very native mixed would claim to be native this ppl right here are not native majorly green eye white skin u think this is a native then white men can be called \textbf{black} \textbf{african} if thats your parameter great no native ppl exist every white or \textbf{black} person can call themselves native\@Dar Candelaria\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/102 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@Dar Candelaria also i made this comment months ago amongst other comments in here so if you wanna be specific be it and dont complain if the first answer was wrongly addressed \textbf{dumb} hoe\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small No, \@Sofia ! Most Mexicans are mestizos(Mix of native american and spanish), followed by indeginous, european, then \textbf{African}!\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Daniel Embree Most Mexicans are mestizo (indigenous and Spanish). Then you have predominantly Whiter, indigenous, and \textbf{Black} Mexicans (smallest percentage). So technically most Mexicans have indigenous blood.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small ​\@Sammy's adventure There is no obligation to follow such a culture or any for that reason. They're not disrespecting anything, they have a choice on how they want to individually lead their own lives, and if theirs is a conscious choice unclouded by outside pressure, so be it. You don't have to pay homage to anybody. Regardless, here people have a very poor understanding of history it seems anyway. There is a reason why things are different, one of which is the policies that the Anglos and the Latins tended to follow in their colonisation efforts. The British often employed segregation, a thing the Anglo-americans have carried on doing with the US. While the Spanish and Portuguese often used a policy of assimilation/integration, out of necessity usually. This is why \textbf{race} is such a huge issue in the US compared to the other Latin American nations.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/146 & \cellcolor{green!5}0.685 \\  \hline
  \cellcolor{green!27}\small I'm glad that these ladies said what they did about EARNING every feather on their headresses. People ignorantly buying them, just to do drugs, and other stupid shit in them, are so \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small The Deflector white boii u know nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Emily Hamm You know what's really hilarious? Over 800,000 Jews left Europe during the so-called "Holocaust" to Mexico. Look at any Mexican today they look little to \textbf{nothing} like the Native Americans you seen before they were "colonized by white people". They were literally orientals with dark skin. Almost all of Mexicans today look Middle Eastern. There was a Mexican educator who tested his genealogy and found he was Jewish. He did this for some 60 other people and found they were all Jewish even though they claimed "pure" Native American heritage. So yes, if Mexico was "conquered by the evil whites" as our "History texts" so claim wouldn't all Mexicans today be blonde haired with blue eyes like the Norwegians are? I just love how today's generation of "Mexicans with Native heritage" attack white people for the Native massacre yet have \textbf{zero} connection to these people. Because they're ALL Jewish and stole their identity!\normalsize   & \cellcolor{green!27}Nothing, Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/155 & \cellcolor{green!27}1.29 \\  \hline
  \cellcolor{green!5}\small Nativefall you sound \textbf{dumb}. There's lots of European culture in Europe\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Natives battled over land with other tribes long before white man came. Do some research \textbf{libtard}.\normalsize   & \cellcolor{green!27}Libtard & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck It wasn't.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small America is the most corrupt and \textbf{racist} country\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hirzy Lameo statistically, India is the most \textbf{racist} country. And America is a bit of corrupt and successful wealth of a country.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Hirzy Lameo You're dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small the whole world is corrupt,i dunno about the \textbf{racist} part\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small People talkin bout Americans being \textbf{racist} when I mostly see \textbf{racist} comments causally calling all Americans \textbf{fat} and stupid\normalsize   & \cellcolor{green!27}Fat, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical Features & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Less blacks - less \textbf{racism}.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Maybe \textbf{racist} but corrupt North Korea\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Some arguments are invalid. Free healthcare does not mean lack of diabetes because diabetes is either genetic (type 1) or lifestyle related (type 2). \textbf{R\textbf{ed}} skin is a stupid name but how is it \textbf{racist}? Whites are light brown, not white, is that \textbf{racist}? Universities have diversity policies. One girl says we don't get subsidies then says if we were rich why do we get subsidies. This video failed to reach its full potential\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/74 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small Redskin didn't come from the scalping of the Native people.. Its because the early Native people have a \textbf{r\textbf{ed}} undertone before colonisation. Because we were colonised by Spanish, British, \textbf{African} American slaves ect we have all sorts of colours.\normalsize   & \cellcolor{green!27}African, Red, Redskin & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}4/39 & \cellcolor{green!27}10.256 \\  \hline
  \cellcolor{green!5}\small I remember playing cowboys and Indians as a child and couldn't wait to go to America to visit them... I remember meeting \textbf{r\textbf{ed}} Indians in the USA at a museum shop they even show me  traditions like how they use make a tomahawk and wigwam scalping etc and how they use the Buffalo and the peace pipe and smoke signals they said jokingly that the only good thing the white man bring was fire water which apparently is a name they use for whiskey but they not trust the white man because White man speak with forked tongue which means lies in \textbf{r\textbf{ed}} \textbf{Indian} to grab land ... the \textbf{r\textbf{ed}} India's in the USA seem smart joyous friendly \textbf{race} with lots of \textbf{old} wisdom and as a plus they have no bitterness over the past and no chip on their shoulder unlike some people do .. it's a too bad most \textbf{r\textbf{ed}} \textbf{Indian} tribes  got wiped out  just over a bit of land ...\normalsize   & \cellcolor{green!5}Indian, Old, Race, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}12/164 & \cellcolor{green!5}7.317 \\  \hline
  \cellcolor{green!27}\small I look at those \textbf{old} photos from the 1880s and say to myself "These women were the most beautiful women to have ever walked the face of the earth" Their descendants are the same.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Are u \textbf{blind} or it were just kidding?\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Rayed A. Last Name sigh you must be one of those people who say ' EvErYoNe Is BeAutIfuL' during \textbf{black} history month when people say that \textbf{black} people are beautiful\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Noa Williams, you kinda implied it. I think that you think I believe that I oppose the \textbf{Black} Lives Matter Movement by saying, All Lives Matter. Maybe you think I am \textbf{racist}????? Now I am afraid to post a Youtube comment.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/41 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small you're black\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small You're black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/2 & \cellcolor{green!5}150.0 \\  \hline
  \cellcolor{green!27}\small You're African\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Blacks always say they m8c with \textbf{indian} lol but cant proove it lol\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Buboy Olea \textbf{Black} not African\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Your \textbf{black} as shit ok dont try to fit in with us ok be proud to be black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Bricardi St Savardi apparently you haven't heard of the \textbf{black} Cherokee people. For all you know she could be at least second or third generation Native American\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@Kwaengi how would you know what ive heard n not heard are you \textbf{dumb} trying to educate a Native about his own culture wow buddy just fuck off eh\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@Kwaengi shes \textbf{black} \textbf{african} american and dont defend her she can do that herself she is not \textbf{black} cherokee l\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}3/20 & \cellcolor{green!27}15.0 \\  \hline
  \cellcolor{green!5}\small \@Yeg Mtb native pro ppl are \textbf{black} too so she basically saying she \textbf{black}!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Jichooi, your question is truly simple to answer. There are light-skin \textbf{Black} people in this world who have no Caucasoid genes in them. There are \textbf{Black} Albinos with no Caucasoid genes. These girls and her people are proclaiming to be Native Indians are not light skin. They are Caucasoids. We know the difference. We know our own people. The government made your Caucasoid ancestors Indians by paying \$5.00. Your ancestors did just that. They paid \$5.00 to be in a tribe they were never a part of in the beginning. These girls cannot teach on something they know \textbf{nothing} about. There are still \textbf{Black} Indians in America. They were told by their ancestors who they were.Unfortunately, these girls' ancestors fought to have the real Indians pushed out of their own tribes to live among the other \textbf{Black} people. The Native Americans will pay for their wickedness against God's people. I hope the \$5.00 they paid was worth stealing the identity of other people. Being tricked by your own people does not excuse the theft. [LINK] \normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}5/176 & \cellcolor{green!27}2.841 \\  \hline
  \cellcolor{green!5}\small You can tell someone's \textbf{ethnicity} just by looking at them? You are the one to determine this? Lol.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small They are native. Lol I can tell. they do not look \textbf{black} or European to me at the slightest..\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small End Of Dayz you look pretty white to me anyway why you trying to claim to be \textbf{black} and then disrespect actual \textbf{black} and native peoples like this.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The \$5 \textbf{indian} thing is actually true. Whites payed \$5 to say they are native american to get free land... Its kinda messed up that some of these whites just dont know where they are coming from. Smh...😐😕\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Native Americans have naturally straight \textbf{black} hair... the fuck are you talking about "woolly hair" you're delusional lmao\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small According-To-My-Black-Experience Sharron that's not you're call to make. They don't need to be pure. I'm 70 Native. I was born on a reservation. I am Native American. Band of Chippewa. I claim my ancestors. I'm Native at heart. No we do not learn our \textbf{old} traditions anymore. But we try our best. And it's rare to find people who are 100 Native American. Who are pure.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small According-To-My-Black-Experience Sharron native americans bear no \textbf{negro} blood in them\normalsize   & \cellcolor{green!5}Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Aboriginal people often is used to describe the natives of Australia, and yes they did look how you described. I'm \textbf{black} and native American, but \textbf{nobody} would guess it from how I look. It kinda depends on how much native you are, and how strong of genes your parents have. But yeah, I see a lot of white people trying to claim that they are 25 or 35 native american, but there's not a sure way to prove they are wrong.\normalsize   & \cellcolor{green!27}Black, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small God Dess holy shit what are you a Native American nationalist? \textbf{Indian} American Hitler?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small The two girls together look Mexican maybe 2 but one for sure looks white and another look mixed with  black\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small You think all white people are blonde with blue eyes? How ignorant. That's not even the case in Scandinavia (if you even know where that is) it's all stereotyping. Any proof of white people claiming to be \textbf{Indian}? Didn't think som\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small We come in all shades,  as do \textbf{black} ppl, Latinos,  middle eastern ppl, asian, and white even.  Im light, but my features let everyone know my heritage,  I was born and raised with my elders,  remembering powwows and ceremonies before going to kindergarten,  I speak my language, i wear regalia,  I know my history so don't say these girls aren't native,  you have no clue.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Saying that they are not Native because they are not \textbf{black} enough for you is really \textbf{racist}. Also what is your problem with light skin?\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small You're just stereotyping the look of a \textbf{race}. There is a lot of variety in all races - and not necessarily because their mixed\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small They have many native features. We aren't 'Indians.' Not all natives are dark even if they are full blooded. Some can be very VERY pale. And who are you to judge if someone's a certain \textbf{ethnicity} enough to talk about their own culture? There is a very small amount of full blooded natives.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small \@Moonpai 3 You have no clue about the higher forces that are prepared to rock this evil white empowered world. Scriptures clearly states that the great tribulation of the \textbf{Black} Man will end with our rise and, your demise.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Guys, apparently we have to be roasting \textbf{black} to be native\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small All of you girls are so beautiful. It is such a pity that people have these misconceptions. Besides, that derogatory term makes absolutely no sense at all. My face is actually \textbf{r\textbf{ed}}, you should see my childhood pictures.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small You should totally have a white man mascot! How awesome would that be? Btw native Americans have the best sense of humor out of any other \textbf{race} in this world . Great video! Please make more.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small I live in a great place that has a very large Native American population, and I even have a Native American friend... who's a \textbf{Nazi}...\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small As a young kid I was friends with a girl who was Native, but I didn't know she was Native at the time. Maybe that's \textbf{weird}, but it was never brought up. I never cared or thought about such things back then. I just thought she was nice and a lot of fun to be around.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small Spoke to a Navajo \textbf{woman} visiting Dundee (Scotland) years ago, (I think I'm still in love)\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small I'm \textbf{African} American and Native American. I don't know the type sadly.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Look at some of the \textbf{old} color pictures of Native Americans who weren't mixed with negroid races and you'll see the real reason we're called redskins. The real truth of the matter is, if you go back far enough we're ASIANS.Today most of us have more white and \textbf{black} than Native American in us. I know a guy whos a Viet-Span and everybody SWEARS he's an "\textbf{Indian}"\normalsize   & \cellcolor{green!27}Black, Indian, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/68 & \cellcolor{green!27}4.412 \\  \hline
  \cellcolor{green!5}\small \@Иосиф Сталин Yes, racial purity matters, a lot of native languages through the continent are dead now, the average latin american doesn't identify as native american despite being about half native, the mixed native americans normally have different interests and world views than the full-blooded ones, etc, all of this thanks to \textbf{race} mixing, so if you really care about native americans then let go of the taboo behind racial purity and admit that there's a correlation with it and the preservation of a culture.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small I'm not saying Indians are white or \textbf{black} or some look \textbf{black} and others look white, but to say all natives share the same skin tone and hair texture is wrong... I am Chiricahua, Kiowa, and \textbf{black} (my mom is native \& \textbf{black} \& my dad is native) I have brownish/\textbf{tan} skin with wavy dark hair) and there are other natives like me \& we still identify as mixed native; kainoa blackeagle has an entire video with someone who identifies the same. There is no one image of an entire collection of people and that's what everyone fails to understand. Plenty of my family lives on the rez and there are natives with curly hair, light skin, \textbf{tan} skin, etc.\normalsize   & \cellcolor{green!27}Black, Tan & \cellcolor{green!27}Ethnicity - Black, Nationality - British & \cellcolor{green!27}5/120 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I assume you may be referring in part to blood quantum, or the system that was introduced by the American government to mathematically decrease and "wipe out" indigenous Americans, and i also assume that you are referring to the myth that there is one singular native look.  To address blood quantum, well, let's just say that as long as you are an active member of your \textbf{nation} or tribe, its a bunch of bs and doesn't mean a thing.  If you're a member of your \textbf{nation} or tribe and you're active in the tribe, then you're native, full stop. It doesn't matter if you have blonde hair and blue eyes, if you're a member of your tribe, then you're native. To address the myth of the one singular native look, let's just put it this way: you're lumping indigenous Americans into one group, when in reality, there are many many different nations and tribes in many many different locations around the US.  Not only that, but you're also basing the "native look" on a stereotype. One's skin color is determined, yes, by genetics, but also in part by the environment the people live in.  For example, a member of the Apache \textbf{nation} (SW United States) might have darker skin than a member of the Miami \textbf{nation} (Midwestern United States).  Not only that, but basing \textbf{race} on phenotypes alone is wholly unreliable. My grandmother is 3/4 Native (not revealing tribe name) and she has the lightest blue eyes you've ever seen.  But her mother and father both had dark brown hair and dark brown eyes. The group y'all label as "Native American" is such a diverse group that I feel as though it is a crime to just \textbf{lump} us all together as one group, because it creates this idea that all tribes are essentially the same and believe the same thing which is entirely false, but that's a different argument for a different day.This is a long post and a long read, but I just had to address this comment to talk about these issues.\normalsize   & \cellcolor{green!5}Lump, Nation, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!5}6/346 & \cellcolor{green!5}1.734 \\  \hline
  \cellcolor{green!27}\small teresaguerrasalazar yeahh no, mexicans arent the purest form of anything, since the natives werent killed as much and the Spanish brought \textbf{black} slaves, everyone had kids with everyone (at one point the Spanish tried to categorize everyone into races, they ended up making like 40 of them) so we all turned out to be some shade brown, then there was  a bit of Asian migration, making out 23andMe profiles a true mess\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}\small teresaguerrasalazar Amerindians?.. are you fkn kidding me? Is that a thing on some tribe? Never heard that shit from any  natives around here. How embarrassing of a word. WTF.. proud to be a \textbf{REDSKIN}! Ain't no shame what the sun does to my complexion. LMAO. Wtf did Vogue do to these kids? Well clearly offered them money and/or whiskey. This video is horseshit!\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small Victoria Faith They're mixed \textbf{race} accept it\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small We come in all shades,  every \textbf{race} does,  look around.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Jay Y I'm sorry but look a pictures of native Americans now vs then. A big difference. They're obviously mixed \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small I sell air That's racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Native Americans are not \textbf{black}. Lol\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small most native American people in this day and \textbf{age} look like that because they are not true native Americans. they probably have some sort of other mixing of white in their blood line\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Natives never stood a chance. The west had mathematics, built and sailed ocean worthy vessels, created the telescope, the steam engine - list goes on and on. Natives never even learned to forge steel. They were happy to do their thing in the Americas living off the land. I'm not putting them down. If everyone did their thing the earth may be a cleaner place. Just pointing out the difference in cultures. Combine the two cultures and it's a recipe for disaster especially 600 years ago. Read "Guns, Germs and Steel" or "This \textbf{Indian} Country". Both informative books.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small martin martinez, I always cringe when people try to \textbf{lump} these huge disparate cultures together. The history and achievements of say the Tarascan and Mayans are different than say...the Iroquois, Cherokee and Sioux. \textbf{Nothing} against them, but these are different people. It's a modern American construct: when whites are just white, forget about the difference between a Swede and a Portuguese, or Asians are just Asians.\normalsize   & \cellcolor{green!5}Lump, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!5}2/66 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Different \textbf{elder} different teachings. Keep an open mind and respect others beliefs, that's what they were taught.\normalsize   & \cellcolor{green!27}Elder & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I did not know that's where the term \textbf{r\textbf{ed}} skin came from... Jesus Christ that's awful. I am guilty, I thought it had something to do with having a \textbf{r\textbf{ed}} complexion, the way Asian people aren't actually \textbf{y\textbf{e\textbf{llow}}}, white people aren't literally white, etc. So yeah... the term ‘redskin' just became 100x more \textbf{racist} than I already thought it was\normalsize   & \cellcolor{green!5}Racist, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - General, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}8/60 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small redskin? i suppose when the natives called the euros palefaces the euros had to think hard for a comeback,, brown skin was already taken as was \textbf{black} skin , so was \textbf{y\textbf{e\textbf{llow}}} skin, so the only color left was \textbf{r\textbf{ed}}. the mistake the natives had made was not calling these pink and \textbf{r\textbf{ed}} euros,  redskins first.\normalsize   & \cellcolor{green!27}Black, Red, Redskin, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}9/56 & \cellcolor{green!27}16.071 \\  \hline
  \cellcolor{green!5}\small Chris Opium Ohhh 😂 ....all of that just because i love the native Americans ? Why you are so mad?  I LOVE THEM NOT YOU PLEASE: If you aren't the \textbf{race} you're speaking about DONT speak on behalf of them and before you say anything about us Please read some  history to know who  murdered over 100 million native Americans\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Chris Opium Haha OMG look who is talking about terrorism !! a white piece of shit whose ancestors killed over 100 million native Americans ! and whose people  killed countless people in iraq Syria Lybia  Japan  Palestine Africa they would kill anyone for oil . who caused these people to perish after they ve been welcomed with flowers and peace ?? you cannot label anyone as \textbf{terrorist} when your filthy hands have so much blood on them you fucking little \textbf{terrorist} . We love Native American people we support them and make sure you dont poke your nose in things that do not concern you next time\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}2/107 & \cellcolor{green!27}1.869 \\  \hline
  \cellcolor{green!5}\small Chris Opium  you say they would kill them ? HoHo but they didn't ! Guess who killed this peaceful innocent \textbf{nation} ??  white people did ! You did !\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I am a white person and I am literally obsessed with indigenous history.I basically research and educate myself most of the week!I was ignorant and \textbf{racist} before until one day I had a Oji-Cree Indigenous couples as roommates than I decided to learn about their history.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small FYI, everyone... The population estimates are more like 50-112 million. No one knows for sure. (We're talking about the total Native population of all of the Americas here.) About 90-95 of Natives died from disease in the first years of contact (Smallpox, Hepatitis A, \textbf{y\textbf{e\textbf{llow}}} fever, plague, influenza, etc.) but in the aftermath there was of course genocide of remaining tribes in both North and South America. European colonization wouldn't have been possible, however, if the Natives had had any immunity to all of these diseases. The rest of the world had already paid the price for these diseases centuries before with continuous waves of outbreaks and repeatedly massive death tolls throughout Europe, Asia and Africa that had earned all these people immunity, so in a sense the Native Americans were simply playing catch up and this high death toll was inevitable.\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/142 & \cellcolor{green!5}2.113 \\  \hline
  \cellcolor{green!27}\small I'm native American and I am DARK not \textbf{black} but dark\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Shawna Williams they killed my people we were called valorians we were like animals we did \textbf{weird} sounds i can do them\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Shawna Williams oh stfu you've done \textbf{nothing}.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Bitch you are as white as snow.Indigenous people are very dark.Get ya \$5 \textbf{Indian} ass outta here.America is \textbf{Black} Land.\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small You're \textbf{crazy}. Your ancestors and mine were murdered and conquered. They'll never be proud because the mistakes they made got us into this mess. Follow logic.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck Worthless bums.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Crazy} Canuck Never their land, just bums like you.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Crazy} Canuck Never their land, a bunch of \textbf{Indian} BS.\normalsize   & \cellcolor{green!5}Crazy, Indian & \cellcolor{green!5}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I am \textbf{black} and native American I get \textbf{r\textbf{ed}} skin and \textbf{y\textbf{e\textbf{llow}}} skin, but I don't take offense to it. Love the video!!\normalsize   & \cellcolor{green!27}Black, Red, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}6/23 & \cellcolor{green!27}26.087 \\  \hline
  \cellcolor{green!5}\small You're just \textbf{black} to me\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small A white person has \textbf{sex} with one of those you got yourself a Mexican\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Me No 25 of the dna in the first know American \textbf{Indian} tribes are European. They were there at the same time (obviously because they reproduced together) as the first Indians, probably before them.  [LINK] \normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small One in the \textbf{y\textbf{e\textbf{llow}}} remind me of Danielle brigoli\normalsize   & \cellcolor{green!27}Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}3/9 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Jesus why do liberals always use kids as soldiers for their political war1.There are some tribes who do get money from the government 2. \textbf{Nobody} thinks you live in tpeeeees3. Some native americans don't pay taxes especially on reservations4. Some native americans ARE rich off casinos 5. \textbf{Nobody} thinks all native americans wear headdresses6.They were called "\textbf{redskin}" because there skin WAS \textbf{r\textbf{ed}} maybe your skin isn't \textbf{r\textbf{ed}} because different temperature, climate, condition, cultural practice, and location just like how \textbf{African} americans are \textbf{black} \textbf{black} The problem is just because you are native american does not mean your an expert I would probably believe adults and not brainwashed kids\normalsize   & \cellcolor{green!5}African, Black, Nobody, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}9/112 & \cellcolor{green!5}8.036 \\  \hline
  \cellcolor{green!27}\small Brown Boy for the most part you're right! On 2 and 5,A lot of people don't know much about Native Americans (usually people not from America) so it would be understandable since they wouldn't know a lot about Natives. On 6 though,Natives were called redskins because of scalping. The conjunction '\textbf{R\textbf{ed}}-skin' was used during the 19th century when scalp hunting was on going. The main reason why this happened was to "Annihilate" the rest of the Native Americans from existance. When a native was scalped,blood ran down their face,thus calling them a \textbf{r\textbf{ed}} skin.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/93 & \cellcolor{green!27}2.151 \\  \hline
  \cellcolor{green!5}\small Only Americans claim "white" as a \textbf{race} because color matters to them.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small You clearly don't know shit about about native Americans and their tribes! My family is Native American and we have been discriminated and called \textbf{r\textbf{ed}} skin!! Clearly you know \textbf{nothing} about us or our culture therefore you should really keep your mouth. We don't get money from the government and we don't get rich off of casinos so please have a seat. You'll never what it's like to be discriminated for being a '\textbf{r\textbf{ed}} skin'\normalsize   & \cellcolor{green!27}Nothing, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}3/75 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small PyroTheCat 'get over it' if you were Native American and had your land taken away maybe you would understand it's hard to just 'get over it' when your land was your everything and it was just taken by the white man like it means \textbf{nothing} 🤷🏽‍♀️ not trying to be rude but its true\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small I am native American \textbf{Indian} you Yuki\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small .....🦊.....lol,.....these kids know \textbf{nothing},....and neither do there parents,...or council ‘,...not one medicine person has said anything ‘,...and when u do ,....I'll be waiting for you 🐾🐾🐾🐾🐾\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I am a full blooded Native American... Navajo \textbf{Indian}... and I would be offended being called a \textbf{Redskin} if the whole state of Texas was offended that the Cowboys was their mascot. If that wasn't clear, I'm not offended. Native peoples do the same. Shiprock High has the Chieftans, Hopi has the Bruins, Window Rock has the Scouts... its a double standard, \& I honestly don't care.\normalsize   & \cellcolor{green!27}Indian, Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small black people say \textbf{nigga} all the time but that doesnt make it ok or any less offensive\normalsize   & \cellcolor{green!5}Black, Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Terry Teller would you be okay with a sports team called 'the Texas KKK'? I assume your answer will be no.... why are you okay with the Texas rangers? They were a \textbf{racist} group known to lynch mexican texans (born in texas). We should start a team called  'al-qaeda' and the logo can be some burning towers. I'm sure white people would not have an issue with that huh?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Episode Interactive you've gotten confused. \textbf{Redskin} is more akin to calling a \textbf{black} person \textbf{black} than it is to calling them a nigga\normalsize   & \cellcolor{green!5}Black, Nigga, Redskin & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}4/23 & \cellcolor{green!5}17.391 \\  \hline
  \cellcolor{green!27}\small Kp you're fucken ignorant. why do you think natives fight to get it removed? because it's \textbf{racist}. \textbf{redskin} was the bounty placed on native heads. it is equally \textbf{racist}. you reak of privilege timmy\normalsize   & \cellcolor{green!27}Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/34 & \cellcolor{green!27}8.824 \\  \hline
  \cellcolor{green!5}\small Kp who said all? quit strawmanning buddy. a great majority of Germans didn't oppose the Jewish holocaust, so according to you that makes it okay and not wrong at all.... hahahaha come on man, your logic is embarrassing. there was a bounty placed on native heads. it was called \textbf{redskin}. bring a native' s head and be given money. that's not \textbf{racist}? yup I can call you \textbf{racist} too, but I chose to give you the benefit of the doubt and call you ignorant.\normalsize   & \cellcolor{green!5}Racist, Redskin & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/84 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Ramon Romo and awww thats so thoughtful of you to not call me \textbf{racist} but instead just ignorant. you're such a virtuous angel of a human being hahaha\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Kp well what natives call each other has \textbf{nothing} to do with you. please go call a \textbf{black} person a \textbf{nigga}, please. see what happens. you can use your stupid logic with them and see how far it takes you. and for your statistic of 90 don't care, I just wish you knew that poll was taken using 500 SELF-IDENTIFIED natives, not real natives. so those white people claiming their great grand mama was a Cherokee princess is on that poll.\normalsize   & \cellcolor{green!5}Black, Nigga, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/81 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Ramon Romo look the fact is, if a massive percentage of the native population was against the name it would be removed. But they aren't so it isn't. You're devoting all this energy to a non problem. People think natives are badass hence why the redskins makes such a good pro football name,  but you're all tied up in this stupid semantic crusade that it's \textbf{racist} when really its just an appreciation of a culture.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small hddd Saying that term is wrong, but it is what it is to communicate with \textbf{black} people.But when a different \textbf{colored} person, especially a white person, says it, it has a double meaning given the history.\normalsize   & \cellcolor{green!5}Black, Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small i eat salads \textbf{redskin} was a bounty. this bounty systematically KILLED Millions of indigenous just like the KKK and Texan Rangers. your technicality doesn't hold weight. hope you left with more knowledge than with the one you came with. there's no excuse for this level of ignorance\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Another native just setting the record straight from this neck of the woods.. I pride myself of my \textbf{R\textbf{ED}} skin as any member of my family and any other \textbf{r\textbf{ed}} family I know. So the jackass saying "it's still \textbf{racist}" go fk yourself it's not your decision. I'm native, I'm a \textbf{REDSKIN}, I'm anishinnabe, I'm American,  put this \textbf{racist} BS to bed and move on and teenvogue, as well as other democratic nutjob magazines/media outlets should stop using little native girls to play some political agenda. guarantee you find those little savages on the rez and they be \textbf{racist} as fk (can't blame them this whole country was supposed to be theirs and is more flooded with every other \textbf{race} from around the whole globe than our own people) but it's life. Not like all non natives are going to move out any time soon. Anyways this is chief dirty butt of the neverwipe tribe.. ☮️\normalsize   & \cellcolor{green!5}Race, Racist, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}9/156 & \cellcolor{green!5}5.769 \\  \hline
  \cellcolor{green!27}\small jaime there were even jews helping Nazis. internalized \textbf{racism} is a bitch isn't it? oh you wouldn't know. no one said natives cant say \textbf{redskin} you \textbf{dumb} ignorant shit. \textbf{black} people say \textbf{nigga}, i dont tell them they shouldnt. i tell whites not to say it, just like i tell whites not to say \textbf{redskin}. youre either not the brightest crayon in the box, or youre not really native. which one is it?\normalsize   & \cellcolor{green!27}Black, Dumb, Nigga, Racism, Redskin & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/73 & \cellcolor{green!27}8.219 \\  \hline
  \cellcolor{green!5}\small there are people that say all tribes were Matirarcal societiesthe all "worshiped wolves"all tribes had 8 genders and their \textbf{transgender} members were always sacredall tribes were mostly vegetarianthey all got along and only white people taught them how to hate that \textbf{Black} Afircans were here thousands of years before themmore misconceptions\normalsize   & \cellcolor{green!5}Black, Transgender & \cellcolor{green!5}Ethnicity - Black, Sexual Identity - Transexuality & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small 0:09 ok, turning that \textbf{dumb}, pseudo education video off. That's ridiculously obvious.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Redskin is due to the blood dripping on the skin? When you look at actual photos of 100 native North Americans (not 95 white like these girls) they had dark reddish skin. So I would have thought it was a description of skin tone just like \textbf{black}, brown, white, \textbf{y\textbf{e\textbf{llow}}}.\normalsize   & \cellcolor{green!5}Black, Redskin, Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}5/50 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small More than 2000 year of human history... I wish to see nations act as the people of the world and let go of their origin as we are connected now - we are living in an \textbf{age} where every person can have internet  in second world countries up to first world countries. We should start to act like the Human \textbf{Race} and not like a bunch of nations arguing with each other. There is no \textbf{racism} when you are human because humanity is one fuking \textbf{race} - human \textbf{race} ... for fuks sake.\normalsize   & \cellcolor{green!27}Age, Race, Racism & \cellcolor{green!27}Age - General, Ethnicity - General & \cellcolor{green!27}5/93 & \cellcolor{green!27}5.376 \\  \hline
  \cellcolor{green!5}\small No such thing as native American.  This wasn't America when the Indians were the only ones who lived here.  And yes some Indians do get checks because they are \textbf{Indian}.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Haha this is such bullshit, my goddaughters father, is from \textbf{r\textbf{ed}} lake \textbf{nation} which is a branch of the Ojibwa, and he is of the chief bloodline and he does \textbf{nothing} but he gets a \textbf{fat} check once a month\normalsize   & \cellcolor{green!27}Fat, Nation, Nothing, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American, Nationality - General, Physical Identity - Physical Features & \cellcolor{green!27}5/40 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You saying they don't chant "hey how are ya" "hey how are ya" that's mind blowing lol. They lieing they don't get money? Lmfao the guy down the road is almost full \textbf{Indian} and he calls the money he gets from the government  his "blood money"\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small I learned that the expression \textbf{R\textbf{ed}} Skins was from the Newfoundland natives that were observed to have \textbf{r\textbf{ed}} soil on their skin, presumably to fend off mosquitoes.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/27 & \cellcolor{green!27}14.815 \\  \hline
  \cellcolor{green!5}\small Wow I'm half \textbf{black} half native American and these are all stereotypes people picked on me for\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small These are \textbf{Mongoloid} descendants from the Bering Straits into Canada then into America not native. Ppl who are native to America are not from the north but the south. The ones who met Columbus we not these people! Stop the lies!\normalsize   & \cellcolor{green!27}Mongoloid & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small I'm mostly nativ3 I'm 52 percent and 32 percent white and 18 percent black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small my cousin married the most stunning first \textbf{nation} lady . they are so happy .\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Uh what? I'm half Native American we get to go to \textbf{doctors} for free because of it?? And my mom get checks from the government because she's Native American cuz she inherited some of her dads land which he got cuz he was Native seriously this  vid is false lol\normalsize   & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Is the diabetes rate high because they are \textbf{fat}. I am 25 Lakotan  btwwwwww\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small True Native Americans are copper \textbf{colored} ... the 'African Americans' who think they decend from Africa are the true natives of this land\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small both my parents are half \textbf{black} and half native amercian ( except my half sister and brother. theyre dad is \textbf{black}) but my mom and dad and my full brothers and sisters all tannish \textbf{r\textbf{ed}}. we turn \textbf{r\textbf{ed}} outta nowhere. soo that redskins part applied to us....\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}6/47 & \cellcolor{green!27}12.766 \\  \hline
  \cellcolor{green!5}\small Who wrote these \textbf{dumb} ass questions to ask them\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Im \textbf{black} but my grandma says her pops was straight Chickisaw or sum shit from Mississippi\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Isaiah loc13 we actually are you \textbf{dumb} hillbilly\normalsize   & \cellcolor{green!5}Dumb, Hillbilly & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Isaiah loc13 well i cant speak for every \textbf{black} personI am an Individual\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Damon Figures back then, the tribes use to take in darker skinned. They knew how the white people were damaging everyone around them. So i know what your grandmother is talking about. Its actually very \textbf{common} in history.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small My ancestors are \textbf{African} and Native American\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Lmao I'm Chinese Filipina Spanish But only grew up learning the Chinese and American culture even though I lived in the Philippines. I was shun out because I was '\textbf{weird}' in some way. I only spoke Chavacano and English, I was not fluent in Tagalog. But when I heard people talking about my \textbf{race} and culture, saying being Chinese is \textbf{weird}, being a Filipino is dirty and being Spanish makes you sadistic. I hated it so much, I understand the girls in the video. They went through the same things as me, and I'm happy I found somebody that went through what I went through too.\normalsize   & \cellcolor{green!5}Race, Weird & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/106 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Here in Washington natives get checks and houses from the government. They deserve it but what they don't deserve is the addiction of opiates and \textbf{alcohol} that spread through their communities because of the natural inability to process such poison. Alluding that money to them didn't make them addicts, our society did....\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Love, respect and appreciate for native americans, i feel so bad for the most disaster crime happened in the world through history for the native ppl by killing tens of millions of ur ppl through 4 centuries by the criminals white ppl, what ever u get now its \textbf{nothing} for the disaster that happened for ur ppl.Sameer from Palestine\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Being from Cleveland , we have our baseball team, the Indians. I can get why people think it's \textbf{racist} but here's the thing . Ohio is made up of dozens of \textbf{Indian} tribes and a lot of the area has been 'built up' on that history. The Cleveland Indians actually had drafted the first Native American player sometime I think near the 1920s or so. We have museums dedicated to the NA history , cities and there are still burial mounds you can visit here\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/85 & \cellcolor{green!27}2.353 \\  \hline
  \cellcolor{green!5}\small I'm European and I just wanna say-sorry for everything we've done to not only Natives but to \textbf{African} Americans, Asians, Jews, Muslims, literally everyone. I am so sorry for the deeply-rooted oppression that runs in my blood. I try so hard to not say anything offensive and I am honestly not \textbf{racist}.\normalsize   & \cellcolor{green!5}African, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small I think that another misconception is that we are all one monolith group. Aside from cultural differences, such as the fact that our languages and dialects differ between tribes, not every Native agrees on every political issue. For example, it was great to see tribes in solidarity against DAPL, and even though my mother's family is from Standing Rock, some of my father's family in OK didn't understand why there were protests. It's ridiculous to me how a Native female can blindly support Trump and attack BLM and hate immigrants and be \textbf{crazy} over guns and not be affected by any mass shootings. One Native girl I got into an argument with didn't believe that she could be \textbf{racist} for spouting bullshit about \textbf{black} people or Muslims or Mexicans. I had friends from all three groups growing up.  I didn't grow up on a reservation and that was my parents' choice. My father had to deal with outright \textbf{racism} from segregation back in the 60's, 70's, and 80's, and my mother was adopted out before ICWA by a white family.  I'm glad to live in a generation where advocacy is much more accessible and normal than it was for my parents. That is why I speak out and share my history. It's also why I show solidarity with people of color who welcome support.\normalsize   & \cellcolor{green!27}Black, Crazy, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/224 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small My dad says that his great grandad was cherkoee \textbf{indian} but my hair is brown and my eyes are hazel???\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The real Americans don't hate South Asian immigrants. The haters are the \textbf{dumb} people who don't know where are they actually from!No offence.. not talking about everyone...\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small there is \textbf{nothing} wrong with a tee pee i wish i lived in a tee pee\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Thick skulls, with knowledge so dull. You're wrong our song, play louder with our words. The skin, within and out feather heads. The pipe, \textbf{fruit} ripe, stop saying we're all \textbf{r\textbf{ed}}. A spectrum of colors what we are and what we'll be. Stay woke or get choked by the cloak of society.\normalsize   & \cellcolor{green!27}Fruit, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/52 & \cellcolor{green!27}5.769 \\  \hline
  \cellcolor{green!5}\small stupid bitches pitch a fit over nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small The Injuns are actually not native to North America, they are invaders from Siberia that genocide the real native Americans. They are \textbf{nothing} more than genocidal maniacs who were brought to heel by a superior people.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small how can you be a native american and be half white? If you see \textbf{old} photos of native americans in general, they dont look like these people in the video. Half doesnt mean full. That's disrepectful to people who have TWO Full Blood Native American Parents. Fuck the one drop rule bullshit\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Oh young ladies..... I think you know better than that. Having a team called the Redskins has \textbf{nothing} to do with scalping and it has \textbf{nothing} to do with disrespect towards Native Americans. Most of your adults think that it is an honor. It was a Native American that designed the mascot for the Redskins. So stop it! And don't tell me I'm a \textbf{racist} because I too am part Native American. My great grandma was full-blooded Cherokee, my grandpa was half Cherokee and my mom I'm 1/4 Cherokee. I love the Native American people and I to believe that they have been mistreated greatly by our government.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/108 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small my question is who was the one to say "ok let's call our selfs Native Americans" and how that \textbf{race} of people got into the world, were they the first people on earth or did they just one day just came out of nowhere? actually how did any \textbf{race} of people just came into this world.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Sounds like \textbf{African} American,Native Americans,Muslims,Mexicans, Asians,get the hardest treatment in this country\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Native in Canada actually had to pay taxes by \textbf{DUMB} EVIL SHIT, Steve Harper. All those taxes went to the rich.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Red Skins are NFL team, not MLB!!!\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small All native tribes deal with different issues. Some native tribes are still fighting to get their land back and its sad to see the natives suffer and are suffering to protect their land seems like \textbf{nobody} give a dam about them NATIVE LIVES MATTER  atleast some tribes get reservations some dont and cant and my tribe has tired rising money to buy our homeland back but we cant\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small i'm white and the shit my \textbf{race} does is so fucked all the \textbf{old} generations of whites are \textbf{racist} it's embarrassing and i don't even want to know my history or culture\normalsize   & \cellcolor{green!27}Old, Race, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}3/32 & \cellcolor{green!27}9.375 \\  \hline
  \cellcolor{green!5}\small Don't take it up the \textbf{bum} 😂😂 lmao us natives love to joke around but clearly you wouldn't understand with your glum attitude\normalsize   & \cellcolor{green!5}Bum & \cellcolor{green!5}Social Class - Destitute & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I could say the same with you. Given with your last name, you're maybe hispanic or mexican or some sort of latino related \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small I would imagine that they would have preferred continuing their lives according to their culture. But being robbed of it, what choice do they have? Also, if you look at some reservations ( not all), you won't find many achievements the white man gave them, unless you are cynical enough to call water-leaking trailers and \textbf{alcohol} an achievement they should be thankful for.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small The white man didn't invent houses. The type of houses that people live in today were invented by white people, but having a shelter over your head dates way back. Everything else about this comment is pretty true, heck these people are speaking the white mans language, so am I.  I'm a fellow muslim born in Iran and I don't have European blood, but this is \textbf{common} sense.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Who said you didYour people drink alot of \textbf{Alcohol} But you get collage free unless you dont make good grades.I know \textbf{Indian} You are stupid\normalsize   & \cellcolor{green!5}Indian, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - Native-American & \cellcolor{green!5}2/27 & \cellcolor{green!5}7.407 \\  \hline
  \cellcolor{green!27}\small 7 not all native Americans are skinny\normalsize   & \cellcolor{green!27}Skinny & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I saw this documentary, scientist say that native americans  do not actually have \textbf{r\textbf{ed}} skin but is because in that time natives lived in higher altitudes like in mountains and sun light hit them directly, so that's why they are \textbf{r\textbf{ed}}.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/41 & \cellcolor{green!5}9.756 \\  \hline
  \cellcolor{green!27}\small Yay. Okay I like this. As an Ojibwe/Potawatomi person I have a few things to say. I like when people reach out to learn about other cultures although I wouldn't say I'm the best person to come to for information. I'm still young and learning. Obviously I don't speak for every Indigenous/Native/Aboriginal/\textbf{Indian} (whatever you prefer). I speak for me and what I understand.Tiipiis - I haven't met anyone who geninuinely thought I lived in a tiipii. My teacher, actually, in elementary school went to visit another school off reserve and the kids there thought we lived in longhouses and tiipiis and that we don't have candy which I found hilarious. But making a tiipii or wiigwam is something that I have done with my family and elementary school. Fire pit, scone and everything.Government funding - Not so familiar with this topic, I admit. I do get funding. On my reserve, members get a significant amount of zhoonyaa for various things like schooling. As for healthcare, same as any Canadian.Taxes - I have a status card that I can use on purchases that takes taxes off. Completely? I don't think so?Casinos. A reserve near me does have a popular Casino. And gambling is also an issue.Headresses - Completely agree with the girls. It is sacred and something earned, not bought.Redskins - I don't know if it's just me but this doesn't bug me so much, only when it turns into something used in a negative way. The term "\textbf{Indian}" I've also used. I don't mind. I know many people that don't mind either. I also know many people DO mind. I mean, just stay frosty. I think the name "person of colour" annoys me more than anything because, well, everyone has colour in their skin.This is just what I know. It's unfortunate that a large amount of hostility comes with the interactions of natives and non-natives. Admittedly on both sides. Yes, there has been a LONG history of \textbf{racism}, cultural genocide and other things with the last residential school closing in just 1996. We won't forget it and we shouldn't but we should also not let it make us bitter moving forward. Correcting someone if they're incorrect is good and being open to learning about us is good too. "Reconciliation" is the goal.\normalsize   & \cellcolor{green!27}Indian, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/389 & \cellcolor{green!27}0.514 \\  \hline
  \cellcolor{green!5}\small wrong. we do get benefits we get free healthcare and free money from the casinos your tribe owns, you get that money when you turn 18. we do have \textbf{r\textbf{ed}} skin you kids are just half white. and tbh dont be such hypocrite we are \textbf{racist} to white ppl.\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small um when I look at my sister who is native American she looks like the actual color \textbf{r\textbf{ed}}. I call her \textbf{redskin} because she's my sister.  you kids are really white and dont look \textbf{nothing} like natives expected for the 2 \textbf{fat} 1s\normalsize   & \cellcolor{green!27}Fat, Nothing, Red, Redskin & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!27}5/43 & \cellcolor{green!27}11.628 \\  \hline
  \cellcolor{green!5}\small I'm Native American and I don't understand how you can get offended by \textbf{redskin}, sure people say things as an insult, but it's depends wether you take it offensive or not. Same goes for the headdresses, if it's Halloween, it's not cultural appropriation, it's just celebrating my culture, again you either take it offensive or not.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small f ten ... What are you? (\textbf{Race})\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Joey Duran same I am too I have the facal features jaw line nose eyebrows head size I just don't have the skin color I got it from my mom and it's kinda \textbf{common} for mixed kids to come out the color of their white parent but has everything else just the skin color I've been called a five dollar \textbf{Indian} everything\normalsize   & \cellcolor{green!5}Common, Indian & \cellcolor{green!5}Ethnicity - Native-American, Social Class - Working class & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small You either are or ya ain't!!! lol.We get that alot in OK,Well blah blah is this n that im half this n that soooo....I'm this n that lol xDOklahoma Eastside (Creek \textbf{Nation})!!!\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Ghada Alshammari says the \textbf{woman} hiding behind her husband's mask.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small wow. using fake stereotypes and \textbf{racism} as your only comeback and/or argument just goes to show that you're wrong. period.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Ghada Alshammari ( American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK]  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK] ( somebody lied whos copper \textbf{colored}?\textbf{African} american ant \textbf{african} ) [LINK] ( City of David in,Perusaksaywaman Ancient jerusalem in Cusco/Navel /Hierosolym ) [LINK] ??? [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK]  American indians negros sold as slaves )  [LINK] (Painting of St Mary of the Good Winds show American Indians as ...) [LINK] ( \textbf{Black} natives in the museums ) : [LINK] ( free land for white adverse possession for blacks) :  [LINK] (cdc exterminates blacks) [LINK] ( alabama senator calls \textbf{black} americans aboriginals) [LINK] ( somebody lied whos copper \textbf{colored}?\textbf{African} american ant \textbf{african} ) [LINK] ( City of David in,Perusaksaywaman Ancient jerusalem in Cusco/Navel /Hierosolym ) [LINK] ??? [LINK] \normalsize   & \cellcolor{green!5}African, Black, Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}18/384 & \cellcolor{green!5}4.688 \\  \hline
  \cellcolor{green!27}\small +Kickative truth I highly doubt your full blooded native. you would babe to be at least around 100 years \textbf{old} which your not.  so your native bit not full,  don't fool yourself\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Weird how this comment is female    based\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small This video is bs. The guy I work with is 75 \textbf{indian}..... He don't get taxes taking out and gets a 5000 a year check.  Native American check. And a check every 6 months for 1,000. Casenio check....... free dental and health.... don't lie I seen it with my own eyes (white 27 Nebraska) eyes.....work 60 hours a week where's my check.. most fucked up thing is he pays no taxes but gets over 10000  a year back from taxes fuck the indians\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small Wow these questions are fucking stupid and I doubt anyone with \textbf{common} sense wouldn't actually ask these questions. Stop trying to make people feel guilty, stop trying to make everyone feel bad for something that happened a long time ago. Those are just stereotypes and some stereotypes become stereotypes because they most likely to be \textbf{COMMON} .. most of these stereotypes are out dated lol\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small Lame\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Red or and bear Grease.Red\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/5 & \cellcolor{green!5}80.0 \\  \hline
  \cellcolor{green!27}\small lol they don't even know the term redskins came from \textbf{r\textbf{ed}} facepainting..a look at a historical portrait of eastern tribes  from the iroquois \textbf{nation} will show you that\normalsize   & \cellcolor{green!27}Nation, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}3/28 & \cellcolor{green!27}10.714 \\  \hline
  \cellcolor{green!5}\small white people get \textbf{r\textbf{ed}}. Natives just get tanner\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Im canadian and im native and \textbf{redskin} is not racist\normalsize   & \cellcolor{green!27}Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/10 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small they aren't dark and with \textbf{r\textbf{ed}} tones like their ancestors but yes that's not a good word. natives have been raped over the years (by whites) there's no test that can really accurately say what their genes are. president Obama made rapes in reservations illegal which is good. no one can convince me though these girls are full blooded natives though they are very light compared to their ancestors. its the same with \textbf{black} people, their ancestors were much darker until intermixing\normalsize   & \cellcolor{green!5}Black, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/82 & \cellcolor{green!5}3.659 \\  \hline
  \cellcolor{green!27}\small All of these non natives saying no one thought these things in the video to be true, lol... I'm Native American and have had lots of people believe these things about me and that my entire family were 'alcoholics' when I attended a predominantly white school. Some people were cool and didn't care about my \textbf{ethnicity} or skin color, but a whole lot of others did and therefore treated me like shit. If you aren't native you don't get to decide if these things are 'true' or not because you have never experienced it and you never will.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small They are not beautiful really at all, that is quite subjective and it seems that many Native Americans who appear to mostly all have more Caucasian blood than native. It seems to be many "Native Americans" are at the whims of white worshiping and 'preference' of lighter skin, like other communities in America such as many \textbf{African} Americans.....It seems many Natives who look more Native have far more self-hatred, and it is only the \$5 Indians and whites who suffer no \textbf{racism} that strive so hard to show and prove how "Native" they are......\normalsize   & \cellcolor{green!5}African, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/94 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Nobody believe this... NOBODY\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Red skins are gingers. We all know that!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small So stupid \textbf{Indian} hoes are being trained by Vogue to play SJW games\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small The sad thing about our society is most people know very little about Native Americans I am a \textbf{Black} man,  a minority but I chose at a very young \textbf{age} to meet and learn about the first Americans. I met a Navajo Native in the Marine Corp, visited the Navajo \textbf{Nation} Fair.and went to a family a Native American Choctaw store front church in the late sixties early seventies. Many people only see the negative such as alcoholism and living in the Rez.\normalsize   & \cellcolor{green!5}Age, Black, Nation & \cellcolor{green!5}Age - General, Ethnicity - Black, Nationality - General & \cellcolor{green!5}3/83 & \cellcolor{green!5}3.614 \\  \hline
  \cellcolor{green!27}\small Thank you for purposely educating yourself at a young \textbf{age}.  We as native ppl appreciate ppl like you!\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Jay Y Stfu!You're everywhere in this comment section claiming to be Native American.Get a life \textbf{Mongoloid}!\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small American Indians are Asian.  DNA analysis proves it.  Walk back to Mongolia or get out of the way --Make room for \textbf{whitey}.  And written language, and metallurgy and electricity.\normalsize   & \cellcolor{green!27}Whitey & \cellcolor{green!27}Ethnicity - White & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Um, who still thinks any of this? \textbf{Nobody} over the \textbf{age} of five thinks any of this stuff is true. And also, if you're getting upset over a sports team, then you really need to get out more.\normalsize   & \cellcolor{green!5}Age, Nobody & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small "That's \textbf{racist}!""\textbf{Redskin} means the blood of enemies poured onto the body"Contradiction much?\normalsize   & \cellcolor{green!27}Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Cheese Curl 190 your so fucking dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Most of natives living in english \textbf{old} colonies are influenced too much by colonies culture.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small When she said that buying a headdress is disrespectful I immediately thought 'oh no!' Because last year my mom bought me one because my room is American \textbf{Indian} 'themed' because I love any thing Native American because I have quite a bit of Native American in me. I'm so sorry!! I didn't know it's disrespectful!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Black people would claim that they are not \textbf{African} descent but were the first \textbf{nation} Ameridian in America....what a joke !!!!\normalsize   & \cellcolor{green!27}African, Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}3/21 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Liberal bias first of all, sit down \textbf{hun} and let me school you. I am of mixed \textbf{race}, I'm cherokee \textbf{Indian}, Sawk American \textbf{Indian}, \textbf{black}, white, Puerto Rican, and Trinidadian. There are some \textbf{black} people that steal cultures, but most of us don't, and second of all,  our culture does not suck. If our culture sucks so much, why do the Kardashians feed off it?Oh ard, sit down.\normalsize   & \cellcolor{green!5}Black, Hun, Indian, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - German & \cellcolor{green!5}6/68 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small There is absolutely \textbf{nothing} wrong with \textbf{black} kinky hair.   This boy must really hate himself!\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small JaeThaaGoat You're \textbf{black} to me, your name is \textbf{black} and your way of talking integrates ebonics, ergo you are \textbf{black} to me.  You don't have enough white in you to look white.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/32 & \cellcolor{green!5}9.375 \\  \hline
  \cellcolor{green!27}\small Why is it a joke Chris Opium? Believe me, I use to think the same that Indians were rich and are jokes! Until I decided to education myself and research. Native Americans are the most poorest \textbf{race} in our countries, and they are mistreated by our governments with broken promises. If they were rich and everything, I'm pretty sure they would have there own hospitals, high schools, college, and clean water in their communities :)\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Actually, I'm \textbf{black} and native American. I embrace both sides of my heritage. Anyone who doesn't claim their ancestors is a dishonor to everyone who tries so hard to get people to understand our cultures. Don't throw all \textbf{black} people into one general group, because that is ridiculous.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Liberal bias you need to educate yourself \textbf{hun}. If it sucks so bad why do people like to steal it???huh???before making a statement you should at least have some type of evidence behind it.but you don't.because it's not true.\normalsize   & \cellcolor{green!27}Hun & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Isaiah loc13 you know you're racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small hahaha,,racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small  [LINK] that's not where the phrase Redskins comes from.yeah she's like twelve and this is obviously some \textbf{weird} political message, but the dummy doesn't even know her own history.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small We are very very wealthy, not in materialism or awesome credit with cash. You've been misinformed just like with our other \textbf{colored} brothers and sisters.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Malik ItBe DREAM ON \textbf{INDIAN}.HAHAHA\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Actually the term \textbf{r\textbf{ed}} skin was coined from the french term "peau rouge", a term used by the early french explorers to describe the the Beothuk who used \textbf{r\textbf{ed}} ochre  to protect their skin.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/34 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small My father was adopted when he was a baby so unfortunately we do not know his father but we've found out who his mother is. He is native american. My father married my mother who is white so I am a mixed \textbf{race} child. We've never been connected to any tribe or taken part in any cultural things. I wanted peoples opinions on this: is it insensitive to classify myself as native american because I've always felt more in touch with that side of me?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small InTeR SkAtEr: Stfu, bitch. You know \textbf{nothing} at all.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Daniel Bennett, that is because InTeR SkAtEr is \textbf{nothing} but a two-bit, ignorant, bitch troll who makes stupid comments regarding something about which they know \textbf{nothing}.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I live in sw mn and have had many native american friends.. great great friends indeed.. our history about the native \textbf{indian} makes me angry angry.. so sad the way our forefathers enslaved and made them live on a reservation.. but yet we as sons and daughters of our forefathers we still turn a \textbf{blind} eye to the fact that.. this is their land.. their land..you are GODS chosen people..free yourself.. .your people have suffered long enough.. in the morning when you look to the east.. you will witness a white man dressed in feathers.. but he will not be who you think he is.. wash away your eyes and then you will see another spirit that comes as a  leopard only he will be the anti-christ.. the beast will try to place a mark on your arm or forehead..tell him to be gone for you are a child of GOD.. only when you see your people rise out of poverty and disparity will you be free to be what you once were.. a proud people indeed.. GO WITH GOD..\normalsize   & \cellcolor{green!27}Blind, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/180 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small Those two girls in the \textbf{r\textbf{ed}} and orange sweater duo are fabulous and basically me as a kid. Tho I gotta admit I'd laugh at NA folks havin a white mascot dude.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I'm full blooded Native and it's ok to call me \textbf{R\textbf{ed}} or Skin. I'm \textbf{r\textbf{ed}} I'm skin. It's a state of mind. I'm a \textbf{r\textbf{ed}} skin, it doesn't hurt my feelings but I know who my ancestors are and I'm here because they thought about me\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}6/46 & \cellcolor{green!27}13.043 \\  \hline
  \cellcolor{green!5}\small I'm 1/4 native. My grandpa was born and raised Blackfoot native. Unfortunately, the fair skinned European is more prominent in me. I spent months every year on the reservation where my grandfather grew up and my cousins live. I'm part of the culture, but because of my skin and hair, I'm told I know \textbf{nothing}. That I'm faking it. That is terrible.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Why do you care so much about your cousins' acceptance. You say you spend a few months every year on the reservation. If you are not fulltime committed to living a traditional, native lifestyle why do you care if people don't fully accept you as a native. Although, I'm sure you know a great deal more than "\textbf{nothing}".\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small I'm 1/2 indigenous with a mix between mayan and dixaá (popularly known as mexican zapotecos) the other half is spanish and arabic... but I'm white and very tall for the average mexican women so \textbf{nobody} takes me seriously in life 😂😭\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small I'm 40 percent I just don't have the skin color I have everything else tho I don't sunburn easily and I \textbf{tan} really good\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Oh dang...*Unfortunately*, the fair skinned European is more prominent in you... is it trendy to wish to be another \textbf{race} now?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Sometimes I wanna marry a girl from other \textbf{race} in the future but like you say they can lose or may not be welcome in both of his/her mixed \textbf{race} community\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small Archaeological evidence shows the Africans in North America first landed on her Eastern shores 51,700 years ago in Allendale County in South Carolina. They then slowly drifted to the West. For example. "The vanguard of Algonquin speaking people's *(THE BLACKFEET)emerged from the Eastern Mountain Woodlands to the grasslands they came to rest early in the 18th century on the Northern Great Plains at the Eastern base of the Rocky Mount. *SOURCE Toner, M.(2004). "Earliest Americans may predate Ice \textbf{Age}." The Atlanta Journal Counstitution.  Retrieved from March 20, 2010 from www.allendale-expedition.net/pressrelease/AJC18earlyman.pdf.  *Dr. Albert Goodyear, a South Carolina University professor says "humans lived along the east Bank of the Savannah River 50,000 years ago."\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}\small Ryan Elliott David imhotep is a biased Afrocentrist. And yes, humans may have been here earlier, they weren't from Africa. They were native Americans and they were not \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Damien McGonnell Dr. Albert Goodyear, A South Carolina University Professor says qoute "humans lived along the east Bank of the Savannah River 50, 000 years ago." The 51,700 year \textbf{old} North American Site found in Allendale County South Carolina by the Savannah River is less than 30 miles from the Atlantic Ocean. Yes They are Melenated Dark skin pigmentated people from Continental Africa. It was not that hard Damienfor them to get over here\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}\small Jessica Ferry I feel you I'm half Mexican but don't look \textbf{nothing} like it and my great grandmother was native\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@A lone Cockroach why the hell does it suck I have to deal with \textbf{racism} everyday of my life because of my skin\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small The natives tell you that you know \textbf{nothing} . Nice people.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Paul the 2 marek Sørensen your not a Blackfoot \textbf{Indian} if your 3\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Ryan Elliott Garafuna ppl are natives in Honduras and yes have \textbf{black} skin.  Beautiful ppl\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Almost all of these are true. My best friend is a full stunning native American and sitting right beside me right now. We are laughing bc we live in northern ontario and ATLEAST 4 out of 7 of these are hard facts.... no shame. WTF? This is the shit that creates \textbf{racism}.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small yeah i am osage i don't get money from the osage casino yeah my dad works at the osage \textbf{nation} fitness center but we dont go walking around in our mocasins and were our feathers like its 1895 we are alive we are modern people get the fact we are not \textbf{r\textbf{ed}} we are not a basic white chicks or white people we are natives\normalsize   & \cellcolor{green!27}Nation, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}3/65 & \cellcolor{green!27}4.615 \\  \hline
  \cellcolor{green!5}\small What about \textbf{Black} Americans we are in slavery and lynched and killed every day by cops\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small USA =NOT WHITE LAND.USA=STOLEN LAND AND COUNTRY FROM THE NATIVE \textbf{INDIAN} AMERICANS.USA=NATIVE \textbf{INDIAN} AMERICAN LAND.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small I hope Native \textbf{Indian} American get THEIR land back.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Redskin isn't a \textbf{racist} its just like braves, Indians, Chiefs just words. I think it's better than \textbf{Indian} or Native American because Indians are from India. Native American is every person born in America. It would be more cool to just say your tribe you belong than be group as one because we weren't.\normalsize   & \cellcolor{green!27}Indian, Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/54 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small American \textbf{Indian} girls are the right mix of beauty and allure... now wonder why my great-great granddday fucked one of them\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small New England patriots are \textbf{racist} my family were loyalist \textbf{crazy} to thing they would name a professional team after traitors wow...\normalsize   & \cellcolor{green!27}Crazy, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small 6. I think people know that. Its stupid to think people actually think that...5. Yes you do... some tribes get over a million dollars4. They don't pay most taxes in stores and other purchases. They do if they open a chain and stuff like that.(Its funny how liberals are trying to screw up these girls minds and have them say oh Trump blah blah) shut up liberals love to use minorities to push their agendas.3. I mean casinos are a living profit 2. I mean I think everybody knows that. 1. I don't think people use \textbf{redskin} to offend and the term has changed in meaning over the years so don't act like it affects you because it doesn't  so sorry pussies\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/125 & \cellcolor{green!5}0.8 \\  \hline
  \cellcolor{green!27}\small look mexican? Mexican isnt a \textbf{race}. Do you mean mestizo?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small this is bullshit! does are mixed \textbf{race} people, real native americans  did have reddish skin this girls are probably  25 percent  native  american at most, stop the white guilt  is just ignorant  the french treat them quite well and the spaniards regarless of popular believe  didn't  massacre  them they mostly die because of European  diseases\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small and BTW my grandfather had \textbf{r\textbf{ed}} skin bc he worked a farm in Tennessee so I would say that back in the day we had \textbf{r\textbf{ed}} skin\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/27 & \cellcolor{green!27}14.815 \\  \hline
  \cellcolor{green!5}\small why are they so white and \textbf{fat} ,just asking\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small namethatrevealsnothingaboutme Everybody have some \textbf{black} \textbf{african} DNA because the first human was \textbf{black}. That doesn't mean we are all \textbf{black} you shit for brains\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}4/24 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small namethatrevealsnothingaboutme your delusional full of fairy tales keep dreaming.YOU HAVE NO EVIDENCE of what your saying you hate the truth because your \textbf{racist} and hate the fact that INDIGENOUS NATIVE AMERICANS ALWAYS HAVE BEEN LIVING IN THE AMERICAS FOR THOUSANDS OF YEARS\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small namethatrevealsnothing MONTE VERDE archaeological evidence of one of the oldest  tribe in south america and theirs no giants objects or remains look it up MONTE VERDE. THIS CHINCHORRO MUMMIES IS TRUE EVIDENCE. Also i check your source of giants and are all lies keep dreaming I DO NOT BELIEVE EUROPEANS \textbf{RACIST}  FAIRY TALES LIES  LOL\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small namethatrevealsnothingaboutme you have funny tales that \textbf{nobody} believes   keeps saying lies congradulations your a special kind of IGNORANT LOL.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@God Dess You have no understanding of anthropology. Whites came from the Caucasus Mountains near Russia. Hence the name Caucasian. White people created almost every modern amenity you use daily, including the computer and internet you're using right now. So for you to talk about white people like they're some sub species while your \textbf{race} hardly ever contributed anything to the world is laughable.  I suggest you stop being a \textbf{racist} moron, your jealousy is showing.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/76 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small God Dess wow, whites must really have you fucked up if you believe that, you that whites came from blacks, scientists even proved that.  White can't fade \textbf{black} \textbf{black} can only fade white, put bleach on a \textbf{black} shirt anf it will turn white, now put bleach on a white shirt, it stays white, y'all came from us you Neanderthal\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Android Miller WHO SAYS WHITES WERE SMARTER, because if you are talking about the intelligence quotient aka I.Q, then you are more mentally retarded than Jake Paul and Whoa Vicky put together, because I.Q isn't even real \textbf{hun}, talk about being smart huh?  It is just a game and you really believe that because of a man going to France and taking an I.Q test by the name of Henry H. Goddard, and coming back over to America and setting his score for ALL whites across the country makes y'all smart? Boo boo, you are more stupid then I imagined, the smartest man right now is a \textbf{black} man, but y'all all have the same score in I.Q though? Does that make any sense?  No the hell it doesn't.  That  was just a thing to do because they didn't like the fact that blacks were smarter and they wanted to do something about it because they were jealous (you can tell this is true because all of y'all make up lies and claim it as the truth because y'all try so hard to be as smart as us) so they did that and set it FOR ALL WHITES, you read?  ALL WHITES, meaning no other white person but him tested.\normalsize   & \cellcolor{green!27}Black, Hun & \cellcolor{green!27}Ethnicity - Black, Nationality - German & \cellcolor{green!27}2/210 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small Melanin Magic retarded? White iq is about 15 points higher than \textbf{black}.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Melanin Magic "blacks are better at it" okay, then why do I go to a mixed \textbf{race} school and most \textbf{black} kids won't even graduate at this rate.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/28 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small because we are close in blood or DNA I think,,,or the \textbf{indian} come from asia a thousand years ago\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Dragon Kim damn thank you so much because I knew the islanders Asian and native America had something in \textbf{common} 👌👏👏👏\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small No disrespect but that's why I'm here. I'm just trying to figure out do y'all have Asian decent bc the native portrayed in Hollywood was usually a native with some melanin or a white actor with a \textbf{tan}. But alot of y'all look Asian. I'm intrigued by \textbf{race} in general with all do respect. I'm a lil native aswell. Multiracial and I just think where we all come from is important to know and intriguing.\normalsize   & \cellcolor{green!5}Race, Tan & \cellcolor{green!5}Ethnicity - General, Nationality - British & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small Here is the truth aborigines were first in America and "native Americans " came through Mongolian DNA and mixed with the original people here 85 to 95 percent of slaves were aborigines not \textbf{African} decent. White man is the smartest in innovation and development then hebrews and egyptions and Samaritans then Asians, then Africans then the rest of the middle East and aborigines from other countries, just look at history.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Jaden Nicholson I'm Native American and people always think I'm \textbf{African} American\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Your \textbf{black} dude\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@Vanessa G and Asia is where the \textbf{black} man originated\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small With that logic \textbf{nobody} is really European or Asian, right? Dude, shut the fuck up, the indigenous populations of America lived here for tens of thousands of years prior to any self-righteous white boy who feels the need to change history to suit their narrative which tries to justify genocide and slavery.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Your one redeeming quality was understanding the ancestry of caucasions. Whites didn't invent everything, again, another fucking invention you folks need to make up. Computers and the internet were a shared invention and most everything else we use today is an amalgamation from cultures and religions the world over. Not just fucking white people you \textbf{racist}, ignorant piece of shit.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small \@Karl V Redweld The intelligence quota doesn't exist you \textbf{dumb} fuck.The Human mind is transcendental and, cannot be scaled by scholastic examinations.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small holy fuck this is \textbf{dumb} lolol straight propaganda!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Every single Native American I've met have been \textbf{nothing} but \textbf{racist} towards me just because I'm white\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Redskin skin \textbf{r\textbf{ed}} thats why its called that most native americans are mixed with European that's why those girls aren't \textbf{r\textbf{ed}}.\normalsize   & \cellcolor{green!5}Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}5/21 & \cellcolor{green!5}23.81 \\  \hline
  \cellcolor{green!27}\small 😊 Are Native Americans Mongoloid/East-Asian? (like the Mongolian, Chinese, Korean, Japanese, etc.)? I'm Mexican born and raised in southern-California, but I'm very curious about what \textbf{race} my Native-American ancestors really are. Just, how many races are there in the world? 😄\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small 1. Who the fuck still thinks Indians live in tipis. 2. Yes, it's a fact that they get government \$.3. Type 2 diabetes is a genetic issue, sugar is new to them. 4. Plenty of universities offer free school if you can genetically prove you are an American \textbf{Indian}. 5. It's a fact, if you live on a reservation you don't have to pay taxes. In Canada, they don't even pay sales tax. 6. Casinos do send checks to \textbf{Indian} tribes. 7. No one thinks that all Indians wear headdresses. 8. \textbf{Redskin} is not \textbf{racist}. You have \textbf{Indian} high schools naming their teams "redskins". In fact before this drama even began, 9/10 Indians were found to believe that the name is not \textbf{racist}. Now the left has politicized and brainwashed these people into believing it is \textbf{racist}. Sports teams like the Braves and Redskins obviously revere native Americans, why the fuck would they name their team after an insult. 9. That scalping story is complete, utter bullshit. Natives were the ones to start scalping. 10. Liberals treat these minorities as pets to further their anti trump agenda. It's sick and \textbf{racist} and in this videos case it comes across as child abuse.\normalsize   & \cellcolor{green!5}Indian, Racist, Redskin & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}8/203 & \cellcolor{green!5}3.941 \\  \hline
  \cellcolor{green!27}\small Dark Shadow Storm don't really know where to start on this one. First of all you cited Wikipedia.. That's literally rule 1 of what not to do in any situation similar to this. Second you cited an opinionated article. This article even mentions the poll I mentioned previously. It says "forget the poll the term \textbf{redskin} offends". By that logic we need to take a poll on who is offended by each team mascot in America and if the results are 100 'not offended' then it must go. Is that what you're trying to tell me right now? That just because a very small percentage of natives find it offensive that it should go, and by doing this you completely shit on the overwhelming majority that aren't offended and/or like the name.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small Dark Shadow Storm the amount of people that were surveyed, 504 to be exact, is a high enough number to get an accurate representation of what it would be like if they did literally ask every native. The poll had a margin of error of 5.5, meaning that 95/100 more times they could do this poll the results wouldn't change more than 5.5. Now please stop trying to play the victim here and move on. \textbf{Redskin} is not \textbf{racist} nor should it offend. No one is using it to be offensive so you shouldn't take it that way.\normalsize   & \cellcolor{green!5}Racist, Redskin & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/98 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}\small Jeremy Woolard Only 504? how many Natives do you think there are ? As of 2010 it has been around 5.2 million Natives 504 is a pretty small percentage of that number that is nowhere near majority and also people seem to hold some ridiculous belief that they "honor" our culture by doing things like that but treating our culture as a mascot is not honoring us in the slightest and says \textbf{nothing} about us as a people except stereotypes 😐\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Dark Shadow Storm Lol, obviously there are more than 504 natives. You don't know how these surveys and polling questions work I guess. 504 people were surveyed across each state and they came to the result that 9/10 aren't offended. As I said before, 504 is a big enough number to get an educated answer on how many natives are offended by \textbf{redskin}. And why not have native mascots? That's how you keep your culture alive! But you've not once responded to me when I suggest you stop playing the victim and move on. Do you try to be the victim in other situations as well? That's no way to go through life.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small Jeremy Woolard Again in the scheme of things 504 is not a big enough sample size which as you know the bigger the sample size the more accurate the results and no the team's are not how we keep our culture alive I will tell you how we really honor our culture we have a celebration of sorts where our people dance traditionally and our elders teach the youth stories and some of our language which is regretfully very hard because of how residential schools nearly destroyed it and so we don't need people pretending to be Native and acting like our culture is \textbf{nothing} but a mascot and again take a look through history we are not "playing" the victim there is plenty of historical trauma\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/127 & \cellcolor{green!27}0.787 \\  \hline
  \cellcolor{green!5}\small nukymama umm...you assumed that this dude is white. That makes you \textbf{racist}. Btw I'm not white I'm a Latina from Colombia not Columbia GET IT RIGHT CHICAS!🇨🇴\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Lol this has \textbf{nothing} to do with trump. Even if they don't pay taxes on those reservations, a lot of them are in poverty on those reservations, and still have a lot of issues going on\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small stop refering yourself as \textbf{indian} refer yourself as native american.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Jeremy Woolard By the way, the poll is very flawed because they called self identifying native Americans over the phone. There was no way to tell if they were real or not. Besides, polling about an issue that is very \textbf{racist} doesn't make sense. Almost every Native American I know does think the name is offensive. Stop trying to speak for us when you know \textbf{nothing} but what you see on the internet.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small 1 lots of people have the misconception indians lived in tipis its part of the hollywood myth2 not every \textbf{indian} gets money its true the tribe may get government funds but usually its not that much and most individuals never see a cent3 thats pretty correct 4 its not as many schools as youd think 5 thats false6 casions only send checks if the casino is on \textbf{indian} land or its \textbf{indian} owned but again most individuals never see a cent7 again many people think all tribes wore headdresses its part of the hollywood effect 8 redskins is a \textbf{racist} term that came from the scalps of government bounties 9 indians didnt scalp until germanic peoples brought the practice to the americas 10 you just sound like a \textbf{racist} idiot\normalsize   & \cellcolor{green!5}Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}5/134 & \cellcolor{green!5}3.731 \\  \hline
  \cellcolor{green!27}\small namethatrevealsnothingaboutme theres no \textbf{redskin} tribe dumbass\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small namethatrevealsnothingaboutme DAMN YOU MUST LOOK AS STUPID AS YOU SOUND. There is no Tribe in Alaska, Canada, North Amerikkka, Central America, or even South America with the Tribal affiliation or identity calling themselves "Redskins", it really is a misconception portrayed on Native Peoples. And I am a real Native American, Apache from the central mountains of Arizona. T.A.T.-A.ZAnd for you to call underage girls bitches is sick and disgusting, it shows how much I would never want any female from my family around you, you would probably end up a real \textbf{redskin} yourself, the way that girl said,... so idk where your getting your info, planet \textbf{dumb} idiot... But here on earth, there is no Tribe called \textbf{redskin}, you yourself said it, there are Apaches, Navajos, Hopis, Zunis, Papagoes, Pimas, Tohono'O'Dams, Yavapais, and I'm just naming whats  around my geographic area, to label us all as \textbf{Redskin} is only testifying to the truth that we still deal with negative stereotypes in 2018,... I can only guess your an internet, sit behind a phone or computer warrior, \textbf{nobody} hating motherfucka,... There is no Tribe known as \textbf{Redskin} dummy....\normalsize   & \cellcolor{green!5}Dumb, Nobody, Redskin & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/188 & \cellcolor{green!5}3.191 \\  \hline
  \cellcolor{green!27}\small Ronald MacMFDonaldTrumpLoverThere is NO Native American owned team called white man is what she's saying dummy,... you taking someone else's words out of context just to make sense of your truth, which only makes sense if we listen to what you say and discredit everything she said. THERE IS NO NFL TEAM OWNED BY ANY NATIVE AMERICAN, and white people take pride in their white mascot teams, WE DON'T TAKE LIGHTLY TO YOU WHITE PEOPLE OWNING YOUR OWN TEAM CALLING YOURSELVES Redskins AND MAKING US LOOK AS STUPID AS YOU, but I wear the Redskins logo to show you Motherfukkkers I am proud to be \textbf{Indian}, and that a logo can't define me, I define that fuckkking logo....\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/119 & \cellcolor{green!27}0.84 \\  \hline
  \cellcolor{green!5}\small namethatrevealsnothingaboutme yes, because you speak for the entire \textbf{redskin} tribe.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Andrew Kwasek you do realize that the target audience of teen vogue is...young girls, right? Not everything is some \textbf{weird} ploy.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Depending on the tribe, yes American Indians do get government handouts. Free healthcare does not magically cure diseases. You would still have diabetes and heart disease.  Yes, you do get schooling for free. There are a ton of American \textbf{Indian} scholarships. "We all gamble." , isn't that a \textbf{racist} stereotype ? If you buy a headdress you are earning those feathers because you earned that money. \textbf{R\textbf{ed}} skin is no more \textbf{racist} than saying white or \textbf{black}. There are a ton of white mascots, the fighting Irish, patriots, cowboys, and so on.\normalsize   & \cellcolor{green!5}Black, Indian, Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}6/92 & \cellcolor{green!5}6.522 \\  \hline
  \cellcolor{green!27}\small Shut up \textbf{whitey}, stop trying to be oppressed. It'd only be handouts if Native people weren't continuously being treated like shit and having their land taken by white people.\normalsize   & \cellcolor{green!27}Whitey & \cellcolor{green!27}Ethnicity - White & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small whitey ? Well, clearly you are \textbf{racist}. You don't even know my \textbf{race}. I'm not oppressed at all. It's the American Indians who are trying to look oppressed. They don't own the land. They never did. American Indians are nomads. So yes they are looking for handouts.\normalsize   & \cellcolor{green!5}Race, Racist, Whitey & \cellcolor{green!5}Ethnicity - General, Ethnicity - White & \cellcolor{green!5}3/47 & \cellcolor{green!5}6.383 \\  \hline
  \cellcolor{green!27}\small What \textbf{racism} have they experienced ? Can you give some examples please ? Actually according to statistics whites experience police brutality the most. What violence have the experienced ? Again, can you give examples ? Whites  buy the land legally.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Toxic-Pop I just gave examples of \textbf{racism} (police brutality, environmental \textbf{racism}, mascots, history classes rewriting history, etc), and in this video they speak about the \textbf{racism} and stereotypes and microaggressions they encounter. Another example are how Native American schools get low funding which leads to higher drop out rates. Not to mention how their schools are understaffed and some of them are infested with rodents (more things that can cause sickness). Natives already have a lower life expectancy than the average. Housing discrimination is another example of the \textbf{racism} they face. If you're just looking at percentages obviously it's gonna say white ppl experience police brutality the most (white ppl make up about 60-70 of the population, clearly) but if you break it down like many studies have Natives and blacks experience it the most. You really need a definition of violent crimes....? Are you being serious? How about rape, murder, assault, hate crimes, etc. Don't be dense. Oh and btw you can look up all of these things if you don't believe them, finding this information is easily accessible if you have internet or a library card.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}4/188 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small No, those are not examples at all. I mean real cases. Give me the names of American Indians who've suffered from  police brutality. Low funding does not leads to higher drop out rates. If someone drops out it's because they choose to do so. \textbf{Nobody} forces them and it's not because of their \textbf{race}. Give me an example of housing discrimination. Give me a name of an American \textbf{Indian} who was discriminated against and give me evidence it was because of their \textbf{race}. How is a lower life expectancy cause by \textbf{racism} ? Oh, and there are way more white sports mascots than American \textbf{Indian} mascots. Like the fighting Irish, Dallas cowboys, Patriots, and so on.\normalsize   & \cellcolor{green!27}Indian, Nobody, Race, Racism & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}6/116 & \cellcolor{green!27}5.172 \\  \hline
  \cellcolor{green!5}\small Toxic-Pop ... are you being serious right now? Why do you need the names of specific Natives Americans who experience police brutality, do you think the statistics are just making up lies? How will a list of names prove that they experience it more when the stats will prove that? You aren't making sense. Do you know how this type of research even works? Have you even done research on police brutality? Cases about Native Americans experiencing police brutality are rarely reported about, so all there is the statistics. Which is what you should be looking for because it'll prove my point even more. Low funding is directly relate to the drop out rate going up, which is why it happens more in schools that don't get any funding. If schools aren't being funded and students don't even have books to learn from why would they keep going to school? You're obviously very privileged and haven't experienced going to a school in a low income neighborhood that doesn't get any government funding, that's good for you. But that's not the experience for a lot of other people. There's been articles about Natives experiencing housing discrimination, a study was done by the Department of Housing and Urban Development and it showed that 1 in 4 Natives experienced housing discrimination. Since you want names for some reason one of the articles was about a man named Ken Hebah. I mentioned the lower life expectancy because of environmental \textbf{racism} that contaminates poor neighborhoods including reservations where Natives live, a lot of them don't have health insurance because they're in poverty so if they get sick they won't be able to go to the hospital for care or medication. Read and comprehend what I'm saying before you reply or I'll just end up repeating myself. None of those team names you listed are slurs or offensive toward white people. So idk why you even tried with that lol, white ppl are hilarious\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/328 & \cellcolor{green!5}0.305 \\  \hline
  \cellcolor{green!27}\small Because if you can't give names you don't have evidence. Without names you have \textbf{nothing}. There is no statistic that proves that there is any injustice because of \textbf{race}. For example, You claim that American Indians have a higher dropout rate. But, you can't prove that this is a result of \textbf{racism}. All you have proven is American Indians choose (that's the key word there, choose \textbf{nobody} forced them ) to drop out more than others. There is no link to \textbf{racism} that you have provided. Articles is not scientific evidence. There are articles claiming that the earth if flat, it doesn't make it true. What is the evidence of this so called "housing discrimination" ? Did the landlord say that they denied them specifically because of their \textbf{race} ? Did they say, we don't rent to Indians ?  What is environmental \textbf{racism} ? The environment is not \textbf{racist}. Rain clouds do not target specific races to rain on. They are poor because of \textbf{racism} ?  So white people are stopping American Indians from getting a job, becoming rich, and moving away ? Sorry, no, that is not how life works in America. \textbf{Nobody} is preventing them from getting a job. \textbf{Nobody} is forcing them to live there. They can move off the reservation. They can live wherever they want. \textbf{Nobody} is stopping them from getting health insurance. Again, what makes you think I'm white ? Assuming my \textbf{race} is \textbf{racist}.\normalsize   & \cellcolor{green!27}Nobody, Nothing, Race, Racism, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}14/241 & \cellcolor{green!27}5.809 \\  \hline
  \cellcolor{green!5}\small Toxic-Pop White people are so privileged they really can't even imagine that someone could get discriminated against based on their \textbf{race} because y'all have never experienced anything like that. Natives Americans make up such a small percentage in North America and you really think that them being killed and experiencing police brutality and housing discrimination at a higher rate than white people is just a coincidence and it has \textbf{nothing} to do with \textbf{race}? If you don't even know what environmental \textbf{racism} is then you really shouldn't even responding to me because you clearly are educated enough in \textbf{racism} and the different forms of it to even be talking about it. Please educate yourself before you speak on things. You just look like every other ignorant white person who thinks America is post racial. Y'all are trash\normalsize   & \cellcolor{green!5}Nothing, Race, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}5/137 & \cellcolor{green!5}3.65 \\  \hline
  \cellcolor{green!27}\small I can imagine a lot. But, I need proof to believe something. Them being killed ? Who is specifically targeting and killing American Indians ? Again, were is your proof that anything is happening to American Indians because of their \textbf{race} ? Clearly you don't know what environmental \textbf{racism} is or else you would explain it. Just like so called American \textbf{Indian} \textbf{racism} you can't prove it exists. Clearly America is not post racial since you hate white people because of their \textbf{race}.\normalsize   & \cellcolor{green!27}Indian, Race, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}5/83 & \cellcolor{green!27}6.024 \\  \hline
  \cellcolor{green!5}\small Toxic-Pop You don't know anything about \textbf{racism} so why are you still trying to talk about this? Why would I bring up environmental \textbf{racism} if I didn't know what it was? I already gave examples of it anyway. So not only are you trying to discuss something you know \textbf{nothing} about and embarrassing yourself, you are awful at reading comprehension. Sad. Even if I did hate white people it'd be completely justified lol\normalsize   & \cellcolor{green!5}Nothing, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/73 & \cellcolor{green!5}4.11 \\  \hline
  \cellcolor{green!27}\small I know a lot about \textbf{racism}. For example you've called me, "\textbf{Whitey}" which is a \textbf{racist} slur. And you don't even my \textbf{race}. So you are \textbf{racist}. Hatred of any \textbf{race} is never justified.\normalsize   & \cellcolor{green!27}Race, Racism, Racist, Whitey & \cellcolor{green!27}Ethnicity - General, Ethnicity - White & \cellcolor{green!27}6/34 & \cellcolor{green!27}17.647 \\  \hline
  \cellcolor{green!5}\small Toxic-Pop Yah, no you don't lol. You've already proven that, you thought environmental \textbf{racism} had to do with it raining lol. And wrong again mayo, whites don't experience \textbf{racism}. Try again\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small "mayo" Another racial slur. You've just proved that whites do experience \textbf{racism} as you have used to racial slurs on me without even knowing my \textbf{race}.\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I have to say this was good. Its not a condescending video. They don't seem to want sympathy from anyone they just seem to be setting the record straight. I like how they explained how the head dress is disrespectful rather than just saying its \textbf{racist} to wear one. Good job girls. Native American history and culture is always interesting to learn. I must brush up on mine :)\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small next time can u get girls who can explain themselves better? they didnt seem they new what they were talking about. native american have a high risk of diabetes because of their genetics. they haven't been been digesting  sugar for as long as other cultures, they arent used to it. its not because they dont have free healthcare. most native american tribes dont pay taxes, and some dont pay sales tax. there are over 500 native american tribes. a lot of them do get checks because of the land they are living on. but you are right that native americans can't get into school just because they are native american. you get free college, but you still have to meet the requirements. plus \textbf{nobody} thinks native Americans live in tepees anymore. wtf\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/132 & \cellcolor{green!27}0.758 \\  \hline
  \cellcolor{green!5}\small I live in Australia and would like to know are Native Americans well respected in America?? Here Aboriginal people and the culture are important and we have weeks dedicated to Aboriginal culture. I know it's a \textbf{dumb} question, but I'm asking this since I know  \textbf{black} history more than Native American history.\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Marie fuck off \textbf{redskin} is not a \textbf{racist} term do some research many native American schools mascots are the redskins because it's not offensive\normalsize   & \cellcolor{green!27}Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm no expert on Native American history, but I do know that the term "\textbf{redskin}" does NOT come from scalping.  That's absurd.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Hold Up, no... just... wow... no.  Google "origin of \textbf{redskin}" and read the Wikipedia summary and the article from the Washington Post. There is no mention that the term originated from scalping.  Feel free to correct me.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small nobody does.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Juliet Fischer We? Whose we? I sure as fuck didn't. I'm white, my Polish ancestors didn't. Even if I was British or French or Spanish or Portuguese... I wouldn't have done it. Put the blame on the dead people that had a hand in it, not their descendants generations down the line who find it appalling.The government has been dumping money into impoverished people of all backgrounds in all places for decades, and it hasn't really fixed much. There's \textbf{nothing} wrong with helping people in poor conditions, but they also have to help themselves. Throwing money at the issue isn't always going to be the solution, especially the way Canadian and American governments have done it.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/117 & \cellcolor{green!27}0.855 \\  \hline
  \cellcolor{green!5}\small We still benefit disproportionately from the system our ancestors created. Every time governments talk about 'cutting waste', social programs are the first on the list regardless of effectiveness. People bleat and blather about individual initiative while refusing to approve and fund programs that will work. Native Americans had an \textbf{alien} culture foisted upon them. Their own religions, cultures, customs, and languages were derided as primitive. When they shed those ways, they were still abused because of their ancestry. They are trying to cope and adapt while too many whites refuse to listen to what they want and need -- or get angry because they're still around or not conforming to the 'noble \textbf{r\textbf{ed}} man' stereotype.\normalsize   & \cellcolor{green!5}Alien, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}3/115 & \cellcolor{green!5}2.609 \\  \hline
  \cellcolor{green!27}\small We could try listening to them about what they need and want so that we can help them properly. Stop treating them as either magical beings or sordid beasts. Stop cooing over the people pretending to be Indians or to be inheritors of \textbf{Indian} lore for the money. Stop treating them as if they are in the way or don't matter.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small If you look at me you'll realize I'm not white either, YouTube's background is white. \textbf{Redskin} is a relative term just like "\textbf{Black} Man" and "White Man", neither of them are \textbf{racist}.\normalsize   & \cellcolor{green!5}Black, Racist, Redskin & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/32 & \cellcolor{green!5}9.375 \\  \hline
  \cellcolor{green!27}\small these girls have been trained by liberals to label everything \textbf{racist}!! McInnes brought me here\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Joe Mora they said \textbf{racist} at like one point in the video.....\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Yeah, like being called a \textbf{redskin} aint racist\normalsize   & \cellcolor{green!27}Racist, Redskin & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/8 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small hey uneducated midgets; you need to learn some history.1. natives still live in tipisthis point is actually valid. no one thinks that native American live in tipis. would you want to live in a tent in the winter?2. natives get a lot of government hand outsa tribe in Minnesota has every member earning at least \$1 million each year from government assistanceGirl says to that, "where is my check". I say, "ask your parents"3. natives don't pay taxes"I thought only trump didn't pay taxes" way to dodge that question because you don't actually pay taxes!4. natives get rich off casinos"if we get rich off casinos, then why do we need government handouts?"just because a person has one way of obtaining money doesn't mean they wont pursue another way to make money.5. all natives where headdressesno one thinks thatalthough saying you didn't earn something by paying for it sounds vaguely anti capitalist.6. \textbf{redskin} is another word for native American1st congrats on going full in by saying, "THATS \textbf{RACIST}"I would probably only use the names Native American or \textbf{Indian}. but not \textbf{redskin} (that's a sports team) and diffidently not \textbf{Injun}."the name \textbf{r\textbf{ed}} skin comes from our skin color, but I'm not \textbf{r\textbf{ed}}."there is a thing called interracial marriage. over time natives have..."mingled" with other races and created less..."pure" skin tones.\normalsize   & \cellcolor{green!5}Indian, Injun, Racist, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}9/236 & \cellcolor{green!5}3.814 \\  \hline
  \cellcolor{green!27}\small Using children to spread inaccuracies is wrong. Yes, native Americans are eligible for free college tuition, many do get checks from the govt because of \textbf{old} land deals between their tribe and the US govt. Who coached these kids before their interview?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small So tell me, what makes a white man native, or any culter born in America..? What is a "Native"? Seems to me, it's just a label. So why bitch about who earns that title more, when it means absolutely \textbf{nothing}. We're all human, with images some people can't accept. That's life, past or future.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small this is some stupid backward ass \textbf{racist} shit\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Literally NO ONE in this day and \textbf{age} thinks native Americans live in teepees! And the term "\textbf{redskin}" DID NOT come about because of bleeding ANYTHING, never mind bleeding skalps! That claim she made is ACTUALLY a real MYTH!\normalsize   & \cellcolor{green!5}Age, Redskin & \cellcolor{green!5}Age - General, Ethnicity - Native-American & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small I personally think that they are not grouping. They are talking about their personal life as an example that not all natives are the same. They are not saying that \textbf{nobody} fits into the stereotype, they are just saying that THEY don't fit, which is a great way of breaking the assumptions.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small Treestump \& Thunderarch But the cowboys aren't portrayed in a \textbf{racist} way\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Treestump \& Thunderarch Natives were called \textbf{r\textbf{ed}} skins cause they were skinned alive, it's \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/15 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Negro12 Agosto But that's not Afrocentric cuz they want \textbf{nothing} to do with Africa.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small truthisgood 777 read and learn about residential schools before talking about religion or the bible....plus if Natives were \textbf{Black} how there are no \textbf{Black} Native tribes in Canada? Please do tell......plus I am Denesuline from Canada part of Athabaskan language family similar to Navajo and Apache plus among other tribes who come from Athabaskan language family....Blacks should stop lying about Natives being \textbf{Black}.....\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}3/63 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small the girls with the \textbf{r\textbf{ed}} and brown or orange sweter look so mexican.they really look mexicans\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small You're no better than the \textbf{racist} whites tbh. You judge people by the color of they skin.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small You're probably a "\$5 \textbf{Indian}" AKA a fake ass Native.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Boo Bat that's not what he is saying when he is saying "5 dollar \textbf{Indian}"\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small hueykhalidX I'm 45 percent my dad looks just like a native american cause he is and my mom is white lemme guess I'm a 5 dollar \textbf{Indian} cause I'm not full lol you're a joke\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@2:20,A lot of people are citing a bounty advertisement referencing blood as the origin of the term 'Redskin', but that ad was written in 1863, long after the term was established. Most likely, the term either comes from \textbf{r\textbf{ed}} paint or from someone who thought Native Tribes had skin that looked \textbf{r\textbf{ed}}(possibly from Sun burn).\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/56 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Disciple of SceneableThat is because you do not know what it is like to be the first peoples of this \textbf{nation} and the deep seeded roots that we as a people have shared for generations. Natives  will continue to share our customs and traditions with all people who respect our ways and our culture. Native Pride till the day I die and when I walk on I will still continue to be with my people in spirit.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small Latina isn't a \textbf{race}..Hispanic DNA is majority Iberian Peninsula, Native, UK based, , \textbf{African} and even Ashkenazi Jew being the least in, as you all say "white" Latinos. While it's the other way around for afro Latinos \textbf{African}, Native, UK, Iberian Peninsula and Ashkenazi Jew. (Asian is also present in the pool)So saying you're Latina but 30 Native is like saying I'm \textbf{African} (\textbf{nationality}) but 30 Native.. It's an \textbf{ethnicity}, not a \textbf{race}.\normalsize   & \cellcolor{green!27}African, Ethnicity, Nationality, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!27}7/75 & \cellcolor{green!27}9.333 \\  \hline
  \cellcolor{green!5}\small teemakesitbetter Latina isn't a race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{African} American and I am 0.22 native lol wtf\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Latina is not a "\textbf{race}". What do you think is the genetic difference from Native Mexicans and Native "Americans"...evidently not much. Given Mexico's racial history, I'm not sure what there is to be proud of? Why are people proud of things they had no say or involvement in?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small That \textbf{R\textbf{ed}} skin part is some bs\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/7 & \cellcolor{green!27}28.571 \\  \hline
  \cellcolor{green!5}\small My mom's part native American, and I think the reason why we were called redskins is because  our skin turns a kind of \textbf{r\textbf{ed}} if we are in the sun.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small don't drink but they live in apartments? once the Post-Apocalyptic Anarchy comes, everyone will go back their \textbf{old} tribal folkish ways\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small A \textbf{racist} would never rape a Non-White because of tainted blood\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small These are not Native Americans coming from a 100 native 2 of them are Inuit which are Viking natives who almost destroyed the northern tribes 1 is whit and the other half black\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Olivia - lol that's classic liberal expediency! Every culture is '\textbf{racist}' to a degree. \textbf{Indian} (ie. in India...before some of you misunderstand the reference \& take offence at the term '\textbf{Indian}') society is even based on \textbf{ethnic} prejudice. It's just that as white people, we are not allowed to 'punch down' (in a 'traditional power' sense...before some of you take offence at that too :D) due to PC culture; it's okay to be \textbf{racist} upwardly though! God! Expressing one's opinion is a veritable left-wing minefield :P\normalsize   & \cellcolor{green!5}Ethnic, Indian, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/86 & \cellcolor{green!5}3.488 \\  \hline
  \cellcolor{green!27}\small Did you just agree with a \textbf{racist} douchebag who called Native Americans substance abusers? Native Americans try to cope with being shit on by our society. Some make the unfortunate choice of \textbf{alcohol}, drugs, or whatever the hell the point of huffing is. Most of them navigate and struggle with systems and issues that a just and fair society would never have imposed on them.\normalsize   & \cellcolor{green!27}Racist, alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol, Ethnicity - General & \cellcolor{green!27}2/65 & \cellcolor{green!27}3.077 \\  \hline
  \cellcolor{green!5}\small Juliet Fischer, no it's not really a deal breaker, it's more I'm just curious if anyone who actually shares the same \textbf{ethnicity} as I, have taken the time to comment on any of these, especially due to the agressiveness of these comments. Why are you becoming so defensive?\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Caucasians call themselves white, so don't think you're clever. And for whites, theirs is the color of morality, intelligence, civilization, and divine favor. 'White' refers exclusively to people of European ancestry (preferably Germanic and Celtic populations). Jews, Arabs, Turks, Afghanis, and so forth are not 'white enough' for the people who think the KKK is a heroic organization.The names that white people imposed on those they conquered carry weight. Those names deny the differences among the non-EuroWhite population of the planet. They carry meanings of cowardice, stupidity, laziness, passivity, latent violence, immorality, barbarism, and inferiority.You haven't seen many Asians if you think they all have light skin. We whites stole people from Africa to work our mines and fields. They lost their \textbf{ethnic} and religious identities along with their names. 'Black' is the least-freighted imposed identity. By contrast, the various Asian peoples brought to Europe and the Americas kept their \textbf{ethnic} identities fairly well, along with their languages and religions. They identify as of Chinese, Japanese, Vietnamese, etc. in ancestry while also primarily as citizens of their countries of birth.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/182 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small Not all. Just the ones who've gone overboard, such as the Nuwaubian \textbf{Nation} of Moors.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Джейсон Хичкок why do you people keep calling us negros all the fucking time in comments.I don't go out of my way to use a \textbf{racist} term about white people and I never will.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Those 2 \textbf{fat} chicks are so funny. Talking jokes all the time lol\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small both have a weakness, \textbf{alcohol} and hard work\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Джейсон Хичкок i hope you choke, you \textbf{racist} piece of shit\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Theyve had a horrible story, but they arent in the past, theyre here today so why suffer for shit that didnt happen to you? Ive tried to become friends with native but they are the MOST \textbf{racist} people ive met to this day in the 8 months that ive been here i  the states\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small A major \textbf{ethnic} groups among the ancient Egyptians/Nubians where are the manding people. An original niger-congo Homeland in the general vicinity of the upper Nile Valley is probably as good a hypothesis as any. The Manding/Xi People according Leo Weiner  presented evidence that the high civilizations of Mexico (Maya and Aztecs) had acquired many of the cultural and religious traditions of the malinke- Bambara (Manding people).  of West Africa... Weiner discussed the analogy between the glyphs on the Tuxtula (Mexican) statuette and the Manding glyphs engraved on the rocks in Mandeland Africa.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small Politically Incorrect that's really \textbf{racist} honestly\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small My dad's in the Navy and he used to live in Australia and he said the way they treated Aborigines there was basically like being Native American and \textbf{black} at the same time in America\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Politically Incorrect Do you have any evidence or proof? indigenous Australians did have wooden shelters sure it wasn't as technologically advanced as europian architecture at the time, but it provided shelter and warmth. Another misconception you have is that indigenous Australians drink out of puddles? what? they build underground water reserves. I mean I share a conservative ideology and view on policies but there is no room for \textbf{racism} what so ever and I'm sure many well-spoken conservative leaders would agree.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small supahotfan You know what's really hilarious? Over 800,000 Jews left Europe during the so-called "Holocaust" to Mexico. Look at any Mexican today they look little to \textbf{nothing} like the Native Americans you seen before they were "colonized by white people". They were literally orientals with dark skin. Almost all of Mexicans today look Middle Eastern. There was a Mexican educator who tested his genealogy and found he was Jewish. He did this for some 60 other people and found they were all Jewish even though they claimed "pure" Native American heritage. So yes, if Mexico was "conquered by the evil whites" as our "History texts" so claim wouldn't all Mexicans today be blonde haired with blue eyes like the Norwegians are? I just love how today's generation of "Mexicans with Native heritage" attack white people for the Native massacre yet have \textbf{zero} connection to these people. Because they're ALL Jewish and stole their identity!\normalsize   & \cellcolor{green!5}Nothing, Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/154 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small \@Juliet Fischer I still speak Navajo and Apache  I spend alot of time trying to explain to people that all my years living on and ofd the rez I NEVER ONCE heard a reel \textbf{injun} say the white man stole our land or demand they give land back.Thats so weak and embarrassing to my own spiritual beliefs Smh They seem to be speaking against all that I know my people to be.No one owns the wind or the sky How can you own the Earth or the Sea We do not believe anyone OWNS the Earth beneath our feet.We are to share and respect in harmony all that has been loaned to us while we journey here for a season. I cant speak for other tribes but the Navajo is the most numerous in the southwestern U.S  the  Navajo \textbf{Nation} Reservation is on the same land our ancestors walked upon we never got exiled off of it .We still make the same arts rugs basket weavings,sandpaintings, hogans,drawings of certain charachters as those that archeologists found in the ancienr ruins at Chaco Canyon,Mesa Verde Cliff dwellings,Shiprock,Windowrock,Pueblo Pintado,Four Corners Monument Navajo \textbf{Nation} Southern Utah,Colorado,northern New Mexico,Arizona the Navajo \textbf{Nation} all the way through Apache Country Pine Top Arizona the beautiful White Mountain Apache Reservation We are still on all the very same lands that our ancestors walked upon .I dont know why people use us for thier political bullcrap liberal leftist \textbf{race} baiting lies.The Navajo Code talkers were honored when presidenr Trumo went out to honor them with awards and he told the Elizabeth Warren pocahontus joke which we thought was funny I got a funnier one  I say she is from the Wannabeewee tribe of wannabees .They told Trump they did not get offended when people yelled Geronimo while jumping out of planes. I never even heard the term Native American until the 90s sometime. We older school natives do  not start tripping or get all butthurt at the word \textbf{indian} . Please fact check me on all that I have said  Go look on youtube for a song by Keith Secola its one of my favorites  its called " Riding in my \textbf{Indian} Car.They try to teach us to hate Christopher Colombus well I cant hate the spaniards because I have a little bit of spanish in my blood that is what Nakai Yaz means in Navajo.Please donr think all natives go around pkaying the victim \textbf{race} card .We are a very quiet people who do not practice a lifestyle of complaining or living in the past To rehash \textbf{old} wounds is not our way.To live in misery and unforgiveness is not something honorable The idea that anyone who claims to be native would go  around crying about stolen land to me would be dishonoring the warriors or \textbf{old} and to dishonor the decisions that were made.We dont think on coulda shoulda woulda so to speak We are to be grateful for each new day of life and what is now To live in and enjoy the present moment so to speak.To live in such a way that youre rehashing \textbf{old} wounds has got to bring extrem misery and sadness Talk about oppressing your very own spirit  Thats so tragic  I find it very hard to believe these people who complain the loudest crying out in anger and misery of the past and demanding others do something in order that they can have a better life i dont see how they can be real native people I dont believe they are real natives   if they are they have been greatly indoctrinated by the racebaiting crooked left globalist school of thought and have really really wandered far far away from the true native spirit .We dont need someone else ro make us happy peaceful or succesful  We know how to make that happen for ourselves We are free in America  unless you are in chains you are not oppressed in America.Im so tired of having to defend my white friends from all the undeserved \textbf{race} hate they get attacked with by liars claiming the land belongs to them  What nerve.I have never once seen or heard a reel \textbf{injun} from my tribe say such idiotic nonsense.There is so much more I would like to say but I will close for now. Blessings to You and Yours Im sorry about grammatical errors  i cant find my reading glasses.\normalsize   & \cellcolor{green!27}Indian, Injun, Nation, Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}13/737 & \cellcolor{green!27}1.764 \\  \hline
  \cellcolor{green!5}\small \@Juliet Fischer You are right I have seen it all the \textbf{racism} toward whites  Its \textbf{racism} I dont care what they try to call it   please do not believe they are real native people  i honestly cant see how thats even possible   Its not the native way to hate or rehash the past  The earth belongs to no one  so why would we be demanding it back   i dont believe they can all be natives    its highly susoect   They are prob paid by soros\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small \@Alfredo Graulau What Natives are you speaking of   the Navajos and Apaches are never \textbf{racist}  we dont believe in such ways. We dont get offended by p.c words  Go look at Keith Secola riding in my \textbf{Indian} Car  on youtube   Its one of my favorite songs  The word \textbf{Indian} does not offend me   We have our own name for ourselves in our own language so it makes no difference to me  The mere words of others do not have the power to effect  me\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/84 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@Jose Menii - East \textbf{Indian}, by your username. Just as messed over by us Europeans.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Cena \textbf{Black} - At the time, Columbus thought he was on the ass-end of the Indies. By the time Europeans knew better, the name was too familiar to change.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@Nakai Yaz - Whites think of many things in terms of ownership and money. Even when we aren't intending to be cruel, we measure things that way. Which is why our attempts at aid go awry: we don't know how to work with the people.Our ancestors looked at the land that indigenous people lived on and saw property going to waste because it wasn't bounded by fences, threaded by roads, dotted with factory-towns, mines, farms, and estates. They felt no guilt because they saw it as God's gift to them, and every 'How can you own the land and the sky' question or protest was evidence that they were right.They took the land by drawing lines on maps and building walls and fences along those lines. Anybody who 'didn't belong' was murdered or driven off. You have all been fighting, in various ways, to keep what remains to you. Elizabeth Warren never traded on her ancestry. It was a family story, \textbf{nothing} more. It was her political opponents who belittled her with their lies. Seems to me that the real wannabe Indians are the white people who decide that a Native ancestor from 1700 means they can cosplay their fantasy, or write those New \textbf{Age} books misrepresenting Native beliefs (or plain making stuff up).\normalsize   & \cellcolor{green!5}Age, Nothing & \cellcolor{green!5}Age - General, Age - Youngsters & \cellcolor{green!5}2/216 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}\small \@Nakai Yaz - Oh, you had to mention Soros. Why? Why do you believe the lies of the greedy bastards who would strip the land, foul the water, and poison the air for money? The greedy bastards who tried to prevent Natives from voting in the mid-terms? The ones who want everybody to sit down, be quiet, and do as they're told without argument. The ones led by a man who has joked about dating his daughter -- what father does that? You can't understand why people still being screwed by whites would be angry at them? The Standing Rock protests were to keep an oil pipeline away from an aquifer that provided drinking water to thousands of people, in addition to protecting local grave sites. Native women are murdered at rates far higher than women of other ethnicities in the same area. What I've read about the various First Nations has never included silence and inaction in the face of evil or injustice. 'Sit down and shut up' has never ended well for those who did so, regardless of \textbf{ethnicity}.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/181 & \cellcolor{green!27}0.552 \\  \hline
  \cellcolor{green!5}\small \@Juliet Fischer Did you think I was defending Soros?  Do you realize that   Natives are a hell of alot stronger then the liberal left democraps keeo making us out to be. We fought with Mexico in 1870 and on Geronimo and his band of warriors were very small in number compared to the huge amount of mexicans that were mercenaries working hard to out all the Apaches on the extinction list.Mexico was heavily involved in the exact same thing they accusw whites of. I dont think you understand my position. I will NEVER surrender my right to defend myself. I know in the big picture of reality the Left wing and tge right wing are all part of the same muddypuppin bird !!! Im not fooled into believed any political propaganda for either side. If you think Trump is \textbf{racist} and hurts peoples feelings like so many brainwashed fools thats fine. I could care less about feelings Im not the little weakling with emotions so delicate that I need the democraps to be word nazis and police people not to offend my wittle feewings  .Thats how the democraps try to make people think all minorities are. I go by facts and Trump did alot of tangible real life things that I can see and feel in the lives of many minorities like opening up factories obama closed down ,the amount of jobs have blown up for minorities that were so relieved  to finally have jobs again. I know some \textbf{black} ,hispanic,apache and navajo people who believe the way I do but most importantly  Its a matter of life or death and being able to defend myself and my family if the mexicans or anyone else tries to come for us again and I chose Trump because that evil murdering hypicrite KILLARY actually thought everyone forgot how evil she treated women who were rape victims a child they recorded her laughing about getting a child molestor out of trouble I heard it with my own ears these are facts that Hilkary never denied I remember when her and bill called blacks super predators and she stole and exploited from the entire country just fact check haiti. My main concern is thatTRUMP DEFENDS OUR RIGHT TO BEAR ARMS AND KILLARY THOUGHT SHE WAS GOING TO IMPOSE GUN CONTROL AND ILL BE DAMED IF I WILL GIVE UP MY RIGHT TO PROTECT MYSELF !!! TRUMP must not be that \textbf{racist} he wants us to live and hillary wanted us disarmed look how she laughed about the dead soldiers at Bengazi and look how she never cared abiut women at all.whatever Trump did or said is not enough for me to bow to surrender my right to bear arms. Im not against mexico either Im just tired of alo the ones that talk trash and blame whites and have the nerve to say mexico fukn belongs to them then they try to hide their attempts at genocide  How convenient that they never mention all the Apaches they massacred   You shouldnt buy into all the left and right crap based on feelings  you should decde on what will help your life personally .If they try to take our guns away I would rather die fighting and remember the Warriors who said   It is a good day to die .Hillary was the most evil and people who examine facts didnt fall for her bullshit anymore. Trump treated all of us natives so nice when he presented the code talkers in person with honorary its on Youtube  Thats not why I am for Trump though its more important to me that hes not trying to take our guns  like Killary anyway i cant find my reading glasses sorry for grammaticak errors  I hope you dont supoort soros\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/630 & \cellcolor{green!5}0.476 \\  \hline
  \cellcolor{green!27}\small \@Juliet Fischer NATIVE AMERICANS DONT ALL TRY TO COPE BLAH BLAH BLAH   WE ARE NOT VICTIMS   STOP WITH YOUR PATRONIZING TRYING TO MAKE US OUT TO BE WEAK LITTLE EMOS THAT NEED YOU TO PROTECT US FROM THE BIG BAD \textbf{RACIST} STOP IT WE ARE NOT OPRESSED VICTIMS AND DONT NEED YOU TO PROTECT US\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small \@Juliet Fischer BECAUSE YOU ARE PUSHING REAL NATIVES TO THE SIDE AND TRYING TO TELL US WE ARE POWERLESS VICTIMS WHO NEED YOU TO EXPLAIM SHIT FOR US   DID IT EVER OCCUR TO YOU THAT THEM \textbf{DUMB} INJUNS CAN SPEAK FOR THEMSELVES!!!! GO SPEAK FOR YOUR OWN PEOPLE !!! DO NOT GENERALIZE ABOUT US ALL AND CLAIM TO KNOW WHY WE DO OR DONT DO THIS OR THAT AND DONT EVER CALL US VICTIMS OR POWERLESS AGAIN\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small \@Juliet Fischer What the hell does that have to freaking do with today.You make the mistake of trying  to speak for us. We are not all the same. I have never once in my entire 52 years of life hear any native yell at or blame white man for anything.There are way too many people speaking for us and explaining shit that I have never even seen or experienced. The Navajo and Apache tribes still live on the exact same land as our ancestors .We never claim to own the land or demand land back because that is not the way we believe We dont believe anyone owns the earth we walk upon. The Navajo \textbf{Nation} all the way to pine top arizona is very beautiful land .I hate to bust your bubble but white man has never oppressed me or caused me grief They have no power over my personal life to make me or mine miserable. I spend alot of time defending whites who get picked on when I lived in Los Angeles .I have lived on the reservation and in the city.I think you give yourself to much credit you are not responsible for what the powers that be or the government did way back when. We had more problems from Mexico than any white man 1870s Mexican government tried to wipe us all out  Fact check me on all I say  Apache Vs Mexico wars .Mexico is always railing accusations at white man demanding land back when they fought us here in the southwest and were worse then any whites thats for sure. Despite that all we dont go around rehashing \textbf{old} wounds .I see more happy peaceful natives about there business.The past was handled the way it was and people who go around demanding land back are a dishonor to thier ancestors who were warriors. People who dont enjoy the good that they do have in the here and now are the most miserable of all. To speak or natives in a way that groups us all together is a huge error ,we are all different  .Those who have been brainwashed to believe all that politicak propaganda have sadly strayed away from the true native spirit. I must say that you did not strip us of our language or our customs ,culture \textbf{nothing} .We still make the exact same rugs ,sandpaintings,pottery,hogans,weavings of baskets and all forms of art that were found by archeoligists at chaco canyon,mesa verde cliff dwellings four corner,shiprock,windowrock,lfrom Navajo \textbf{Nation} all the way through Apache country to pinetop arizona \textbf{Indian} country is beautiful and we didnt go away anywhere or get exiled from the land .I dont have ny reading glasses I can barely see the keyboard on my phone.I had to respond and I do it quickly regardkess of how manu errors I dont care to impress anyone with grammatical perfe tion.  I got things to do in this happy life of my .There are no sad indians sitting around dwelling on the past or feeling oppressed where i come from.Im sure there are some sad people some where but thats not the norm becuz even the natives who are not well off financislly love to laugh and live and enjoy life  We are not a weak unhappy brooding  people and we dont cinsider ourseoves these oppressed victims  I thiughtthe pocahontis joke was.funny  but we have our own joke about warren  she is from the wannabeewee tribe of wanna bees    .Im gonna go listen to riding in my \textbf{indian}  car by keith secols and enjoy my conquistador ancestry husband and clean up from thanksgiving while enjoying some politically incorrect music while I enjoy the technology the invaders brought lmao Dont believe all you hear on tv or at \textbf{libtard} universities    we are not weak  victims in misery wasting away our lives nursing \textbf{old} wounds\normalsize   & \cellcolor{green!27}Indian, Libtard, Nation, Nothing, Old & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Age - Youngsters, Ethnicity - Native-American, Nationality - General & \cellcolor{green!27}8/643 & \cellcolor{green!27}1.244 \\  \hline
  \cellcolor{green!5}\small \@Dave Bak47 - Work on your reading comprehension. I have, in other fora, been bitched at for not having the appropriate \textbf{ethnicity}, religion, or other qualities. Or were you playing to your audience with your silly comment?\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small supahotfan I think Australian Aboriginals treated are much worse. They are treated as \textbf{black} people basically.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Margarita M. we are black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Black Hebrew Israelite Egyptian Chinese Native American : THEY DONT GET FREE REPARATIONS?? WE WUZNT NATIVE AMERICANS ANYMORE N SHIIEEEET!!!"\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small supahotfan , get over it, the white and \textbf{black} Americans are there to stay.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Cena \textbf{Black} Africans are not of ANAHUAC, they never have been and never will be!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Lee Francis You aren't Native, you're Anchor Baby invaders, who have no place here. No wars, no deaths, no accomplishments, no laws, \textbf{nothing} will make you true blood kin to this land!\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@RPG FLAMEZ What \textbf{race} are you? White? Sounds like it.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Sheridan Burns Irish is not an insult. \textbf{Indian} is an insult. It sos different. You are talking about oranges and apples\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small these girls come from some other native Americans I wanna see the real native native people like the amazonian people them are the real native Americans of the land they survive in the wild and everything people call them \textbf{r\textbf{ed}} skin because their tone is darker brown and has a mellow or \textbf{r\textbf{ed}} under tone like a bronze color\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/59 & \cellcolor{green!27}6.78 \\  \hline
  \cellcolor{green!5}\small hey i come form the American \textbf{Indian} the are the way in my life and this life to great spirit is the way in life\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Actually, If you do some REAL research you will find that the original Natives of North America were dark skinned and many Europeans like Christopher Columbus and numerous other's referred to them as dark skinned people with copper to reddish skin which is where the "\textbf{redskin}" definition actually came from. Because of the \$5 \textbf{Indian} period where Europeans could "buy" into the native culture, they dropped the "\textbf{r\textbf{ed}} skin" description and called it negative or derogatory because they weren't \textbf{r\textbf{ed}} skinned people that fit the true definition of an authentic native. These are not real natives historically. Why didn't they have any of them say what tribe they're from? If they go by the Europeanized 5 so called civilized tribes names they are decedents of \$5 Indians who have mixed in and are descendants of traitors that don't know the tribes original name. ask yourself, who built all of the hundreds of pyramids across North America that predates any tribe? Natives never built pyramids, they built mounds which was a different structure all together. The Africans that came over on land bridges etc built those pyramids thus the reason why original natives were dark \textbf{colored} ranging from copper tone to reddish. White supremacy is always busy lying! even got these people on here confused about who they are like everyone else! PLUS!!! No, all tribes don't get govt assistance, but the 5 so called civilized ones do have access to funds' schooling, casino money etc. They have documentary's out about that! do some research..sheeesh...smh\normalsize   & \cellcolor{green!27}Colored, Indian, Red, Redskin & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}7/254 & \cellcolor{green!27}2.756 \\  \hline
  \cellcolor{green!5}\small why sensitive? I just thought it was a bit \textbf{weird} for her to say that, as a teacher XD\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small My mom is full \textbf{Indian} and my dad is \textbf{black} so what would I be\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small African is Native to this continent as the first settlers here. You would be Native technically, but white supremacy likes to divide and conquer native peoples.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small The stars That shine up and down half \textbf{black} half Native? 😂\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small You would be half Amerindian, the \textbf{black} side would be many things, as \textbf{black} Americans tend to have many types of gentic out of Africa, some even have up to 20 British isle genetics. I'm half basque and Native American. My sister Married a \textbf{black} man and her daughter has 23 Native American 10 British, and about 40 \textbf{black}, the rest is from other parts of Europe like French Basque.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}4/70 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small You are half \textbf{black} and  have native so on your records it should have you as other. That's what my mother put on my birth certificate. My father is native American too\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small As Native American, I come from a tribe that haves a casino. One the government didn't give us money to build, my people before me started bingo games in a building and we work our way up to get a bigger casino after the years. The government didn't provide \textbf{nothing} for us.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small My dad calls us "\textbf{r\textbf{ed}} skins" ? 🤔It ain't \textbf{racist} to us. And we do get free schooling and money. (I'm Native American from Canada!) 😃😕 I'm Native but I have like tiny tiny percentages of white and other stuff in me but I don't pay attention to those cultures I go as FULL Native American\normalsize   & \cellcolor{green!27}Racist, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/56 & \cellcolor{green!27}5.357 \\  \hline
  \cellcolor{green!5}\small white people look 10x.more \textbf{r\textbf{ed}} in the summer than natives\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small It's referring to the dark orange/red native Americans due to prolonged sun exposure. It's not \textbf{racist} to call them \textbf{redskin}... it was first used to describe them in general. Like how you would call a white man white or \textbf{black} \textbf{black}.\normalsize   & \cellcolor{green!27}Black, Racist, Redskin & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}3/41 & \cellcolor{green!27}7.317 \\  \hline
  \cellcolor{green!5}\small don't forget when their mad then their \textbf{r\textbf{ed}} and when their cold their blue\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small abrinasayy Depends what roots they have.   I'm ethnically Slavic and I \textbf{tan}....\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Im Native American and can't \textbf{tan} lol so yea very \textbf{r\textbf{ed}} during the summer\normalsize   & \cellcolor{green!5}Red, Tan & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - British & \cellcolor{green!5}3/14 & \cellcolor{green!5}21.429 \\  \hline
  \cellcolor{green!27}\small Natives dont get \textbf{r\textbf{ed}} they get brown, iam a native just really lightskin\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Lol. Im part native with lighter skin (\textbf{tan} in color) and never burn. My family (side not native) burn like fried chicken. I laugh then feel bad lol\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Redskin comes from the scalp laws. There was no bounty paid for scalps taken off a corpse.  They had to be bloody to prove that you had killed the person ie \textbf{r\textbf{ed}} skins.\normalsize   & \cellcolor{green!27}Red, Redskin & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}3/33 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small LITERALLY!!! I seriously don't want a \textbf{tan} this summer because I'm too brown 😭😂\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Heraldo Medrano oh, I mean if whites have to go back, coz it is natives' land, that means that you'll be also sending out blacks and muslims to Africa and Middle East. YOU \textbf{RACIST}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small Matt X While I do respect that answer, I do think that if historically your family runs with a certain culture more than any other "\textbf{race}", that they should try to get back to that and retain that as much as they can rather than letting people who have had an almost totally different background running from their family retaining another culture. But I'll definitely keep your perspective in mind\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Matt X I've seen avatar, are you suggesting that the main character joining in on those avatar' culture? If so I'm not sure about that example because originally he did that because he wanted legs and could only get that from being an avatar. So ultimately that sounds like going in on something for benefit. Ultimately that reminds me of that \$5 \textbf{Indian} scheme that had occurred against American Indians. i'm not sure if you've heard or read into that..\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small I'm white/Native and if I'm in the sun for 0.2 seconds I'm dark. Not \textbf{r\textbf{ed}}, dark. I'm just so cunfuzeld.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small mia Cook If I'm in the sun for 3 seconds I'm \textbf{tan}!\normalsize   & \cellcolor{green!27}Tan & \cellcolor{green!27}Nationality - British & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Kevin Renner 🤣🤣🤣🤣🤣 I know bro! I'm \textbf{y\textbf{e\textbf{llow}}} and when I \textbf{tan}  it's my face and arms.brown and \textbf{y\textbf{e\textbf{llow}}}😂😂😂\normalsize   & \cellcolor{green!5}Tan, Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - British, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}4/19 & \cellcolor{green!5}21.053 \\  \hline
  \cellcolor{green!27}\small I'm Waldo right \textbf{black} skins, \textbf{y\textbf{e\textbf{llow}}} skins, white skins let's just call them that instead of what they'd rather be called\normalsize   & \cellcolor{green!27}Black, Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}4/21 & \cellcolor{green!27}19.048 \\  \hline
  \cellcolor{green!5}\small Gamerglazer423 \textbf{Racist} ahead\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Heraldo Medrano But you're not denying you're \textbf{racist}?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Uncle Tom Also they weren't as mixed \textbf{race} as they are nowadays.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Not when you cover your skin in \textbf{r\textbf{ed}} paint symbolic or during war time.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Lol that's true cinnamon colored\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Native Americans are mixed anyways if you live in the U.S., Canada, and Latin America. I dont want to be mean or it is mean to say the people in the video may have some other \textbf{ethnicity} as well because Native tribes intermarried with Europeans a long time ago, you know.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small correct me if I'm wrong but you said the word \textbf{Redskin} used to be given to a certain tribe not exactly North American Native \textbf{Indian} Giants who had \textbf{r\textbf{ed}} skin and used to cannibalize Native Americans correct me if I'm wrong\normalsize   & \cellcolor{green!5}Indian, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/41 & \cellcolor{green!5}9.756 \\  \hline
  \cellcolor{green!27}\small i am native american \textbf{African} American Mexican and Spanish i represent all my cultures the best i can\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small lol, this Ladies were funny! especially the team called "white man" in reference to Chicago's \textbf{r\textbf{ed}} skins! so funny!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small As a Native American--this is so \textbf{dumb}.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small 1:59Wtf, white  people are \textbf{r\textbf{ed}} and they get even more redder when they laugh , so freakin annoying. White people make up stuff and say, Asians are \textbf{y\textbf{e\textbf{llow}}},Native Americans are \textbf{r\textbf{ed}}, \textbf{Black} people are \textbf{black}  when blacks are actually not even \textbf{black} , they come in different shades😂 .-. And they don't think about themselves, their not white! Their pink mixed with \textbf{r\textbf{ed}} 😴 sorry for being rude but I'm actually being serious , and this is serious 😤\normalsize   & \cellcolor{green!5}Black, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}12/80 & \cellcolor{green!5}15.0 \\  \hline
  \cellcolor{green!27}\small Scarlet Buruka you are under the impression that White people make up these terms.  you realize that the Japanese people have a word to describe themselves and other asians and it literally translates too  "\textbf{y\textbf{e\textbf{llow}}} people"   I know you get an erection at the idea of trashtalking white people but you should probably take a step back and reevaluate things.\normalsize   & \cellcolor{green!27}Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}3/60 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Ignorant asshole- Trump pays no taxes."Or maybe [the reason Trump doesn't release his tax returns is that] he doesn't want the American people, all of you watching tonight, to know that he's paid \textbf{nothing} in federal taxes, because the only years that anybody's ever seen were a couple of years when he had to turn them over to state authorities when he was trying to get a casino license, and they showed he didn't pay any federal income tax."No denial whatsoever; on the contrary, he gloated- That makes me smart\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small I don't want to hear about your \textbf{g\textbf{ay}} fantasies.\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small There is \textbf{nothing} wrong with being gay; however, there is something VERY wrong with sucking-off Donald Trump like you do. I'll pray for you.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Alethea P wow. Really? You can literally get to pay thousands of euros as a penalty if you will ask such question a person in Norway. Same goes to many other countries. Coz depending on how much you get, the bigger gets your tax. And asking that question you directly demanding personal information of the person, which salary/wage/all the other legal means of recieving money are. Would you mind telling us some of your confidential information? Probably not. Such private information can be easily used in slandering ways. Despite that, \textbf{nobody} has to explain why one does not revial personal information. Do not respect Trump, but respect individual privacy. You people are sick. Ge 🤦🏻‍♀️\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/115 & \cellcolor{green!27}0.87 \\  \hline
  \cellcolor{green!5}\small Ira Kraeva, what you apparently don't realize is that things here are not like in Norway. U.S. presidents and presidential candidates going clear back to Harry S. Truman have made their tax returns public as a matter of courtesy, not obligation. It's like showing us they have \textbf{nothing} up their sleeves.Trump has not made his tax returns public even after promising he would, and this not only makes him cagey but also a goddamned liar.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small If I want your inane level of shit commentary, I shall inquire at a \textbf{mental} infirmary Android Miller you stupid fuck.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Omg the two girls in the orange and \textbf{r\textbf{ed}} are so funny!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Another misconception is all natives have black/brown hair and brown eyes. I'm half native due to my mom and I have brownish/blonde hair and blue eyes. \textbf{Nobody} believes me until they look at my grandmother and then look back at me. Lol\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small REDSKINS comes from the paint that some Eastern and Caribbean tribes used. a lot of things taught to whites about native america is false but so is what's taught to native kids. but they are just kids so I won't hold it over them. however the natives I know are NOT offended by \textbf{REDSKIN}. btw aniyunwiya and proud NDN\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small Brandon Reeder I'm a piikani \textbf{Indian} 😂💀\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small clickity clack  You are a realist brother. These people are just trying to cause more division by pointing out the misconceptions and blame white people for all of it. Those bad times are gone, the white man is not fighting the \textbf{Indian} man anymore. Most American Indians are treated like 1st class citizens. Also I believe the term Native American is a false term because native means you are from, and every American that was born in the US is a Native American, I believe the term indigenous american would be better.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/92 & \cellcolor{green!5}1.087 \\  \hline
  \cellcolor{green!27}\small thats like saying \textbf{nigga} is ok to say just cause people dont mean it doesnt make it not offensive\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Futile attempt at humor falls flat. \textbf{R\textbf{ed}} Skin came from the \textbf{r\textbf{ed}} paint that a lot of eastern tribes wore.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/20 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Blackfeet \textbf{Nation} ❤️❤️❤️❤️❤️❤️❤️\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Native American here lol soo glad to hear these ladies speak out about everything people misconcept. I am not \textbf{r\textbf{ed}} either, we don't live in teepees only used for ceremonies around here.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small I'm native American and German. My great grandpa is german and great grandma is native American, when she died he was the only one who knew what tribe we came from. Because he was \textbf{racist} and wanted to get back at my mom (because my little brother is also \textbf{black}) he never told anyone what tribe it was. So it makes me sad to not know what tribe I come from.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/71 & \cellcolor{green!27}2.817 \\  \hline
  \cellcolor{green!5}\small The term \textbf{redskin} also came about, because of a tribe that painted their bodies and faces \textbf{r\textbf{ed}} in Newfoundland, and when the British came over, those were the first natives they encountered, so the settlers called every native that. And yes it's very racist\normalsize   & \cellcolor{green!5}Racist, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/44 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small My Great grandfather is half native American and half \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I'm not sure if I understood my U.S History book, but from what I learned it's true about what Christopher Columbus did to them but thay doesn't compare to anything that the Americans have done throughout the years. Americans have greatly taken advantage of Native Americans, African-American,  and any other \textbf{race}. Always discriminated since a long time ago. So far that's what I have been reading. Their victories were mostly because they took advantage of people.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small I teach on a Native Reserve in Alberta Canada. The amount of ignorant and \textbf{racist} questions I get asked about my students and school is thoroughly upsetting. My favourite, "Wow...Must be very scary teaching on a Reserve?" Scary? Where do these people think I am going? To war? My students treat me with love and respect. I have never felt happier teaching at a school like I am at my current school. I love my First \textbf{Nation} students.\normalsize   & \cellcolor{green!27}Nation, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/78 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Never call a Native American a "\textbf{redskin}." It's so fucking disrespectful and that's showing so much disregard for our cultures and the suffering we've been put through. But I'd like to petition for us to have a mascot called Whiteman. It sounds good, has a very nice ring to it.\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small These bitches don't know shit just young an dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small red skins is just as \textbf{racist} as calling someone the N-word.  it's horrible to this that there is a football club named after that\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/24 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Some girl in my class wants to not be white soo bad she pretends to be other races one day she's \textbf{Indian} another day she's Native American and the next day she's Mexican\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small SocalledNegro be AbOriginal to AmaRica and Earth and \textbf{aLIEn} Murderous Vipers be squattin\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Great video! I'm Yaqui myself. The biggest misconception I hear is that the border changes our \textbf{ethnicity}, because it doesn't. Native American \textbf{ethnicity} travels all the way down to Chile from Canada. We occupied this entire land, not just the modern states. Mexico has the most Native Americans by an insanely large margin and yet we still call them "immigrants". We always have to be educating people.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/67 & \cellcolor{green!27}2.985 \\  \hline
  \cellcolor{green!5}\small its not even close to being true and the fact you said that is \textbf{racist} as fuck\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small is her definition of \textbf{redskin} correct? I feel like it's very similar to a definition of chi*k I heard once. anyway great vid I just wish that girl didn't say "we are evolving," yikes. (also what they said was right for them everyone don't take their word as law. they're young native girls but still can't speak for all native ppl. this was just to dispel stereotypes which is good.) teen vogue is on a roll. almost makes me sad I ended my subscription.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}\small Vato bitch ass nigga\normalsize   & \cellcolor{green!5}Nigga & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small No one on earth is pure anything. (Except the Un contacted tribes on islands) If we were we would all be dead of disease. We all get immunities to diseases from different races of people in our ancestry Sorry to break it to you, but there shouldn't be shame attached to the pigment of your skin either \textbf{black}, white, brown. People shouldn't be persecuted for the acts of their ancestors. Very backwards thinking if you ask me.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}\small probably the most \textbf{racist} comment I've ever read. so nonchalant, full of hubris. Hilarious. I will add it to my collection. A+\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Joseph Quīnque ur \textbf{dumb} dont you know there are still full blood natives today right???dumbass\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Flashy Gold funny how you say we got raped. Im 4/4 navajo and my ancestors did not get raped. The complexity of the native americans varies by location of the tribe. Tribes that deal with heavy winters you will notice are more light toned and tribes down south have deeper complexity. There are some tribes that were anglo adopted and they look \textbf{nothing} like these young women\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small You are very \textbf{racist} and a idiot I can't help that my dad fell in love with a white women and it really shouldn't matter\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Sad part is you're a \textbf{racist} moron. Sorry that you feel that way, hopefully you can stop with that ignorant attitude and grow up.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Its just \textbf{lame} when someone is 10 this or that and they abandon their main heritage to pretend to be 100 something else. Its like that BS one drop rule. I don't doubt these girls are what most people consider "Native American". However their ancestors came here from Asia though the Bering Strait so that makes them immigrants...Native to Serbia.\normalsize   & \cellcolor{green!27}Lame & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small Hostile Pebble  There's still pure \textbf{race} folks.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small What kind of name is Fred Muggs for a \textbf{redskin} anyways? You should be named Tonto or something. Living in your little Teepee.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Biracial and proud! Their is \textbf{nothing} sad about being mixed, growing up and being pale i was treated horribly because of my skin color. Now i love how unique i am being mohawk and french canadian\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Charm venus Not all native. I don't know if you don't remember or \textbf{nobody} teach about theIMPERIO AZTECAIMPERIO MAYAIMPERIO INCAand the OLMECAS\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small It's rare for U.S. natives to be 100 Native American but it's \textbf{common} in several Latin American countries.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Dude I'm Native. I know a Native when I see one. These girls are pure Native, telling by their voice and sense of style. And I have a right to say this, because it's my \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small KIJIJI ALLIN do you even know what \textbf{racist} even means? Stop using that word as a defense omg, whites invented the word \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small umno.\textbf{r\textbf{ed}} skin comes from the ruddy copper complection of the native americans who were not of mixed \textbf{race} when europeand first encountered them here.it has \textbf{nothing} to do with blood...\normalsize   & \cellcolor{green!27}Nothing, Race, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/33 & \cellcolor{green!27}12.121 \\  \hline
  \cellcolor{green!5}\small Louisa Capell I was thinking do white people not bleed \textbf{r\textbf{ed}} blood when they are scalped or something lmao it makes no Sense\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Craig Fox ur so \textbf{dumb} learn ur history it has \textbf{nothing} to do with that\normalsize   & \cellcolor{green!27}Dumb, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/15 & \cellcolor{green!27}13.333 \\  \hline
  \cellcolor{green!5}\small "Redskins" was also a term used to refer to their scalps. I saw it on \textbf{old} posters, offering bounty for them.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small red skins was literally the term used for scalps of indians you killed for government bounties\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Um no. You're wrong.  It's because scalps had to be taken from a person just killed to collect the bounty.  \textbf{R\textbf{ed}} skins or dead skins.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small I didn't get schooled. I already knew all this. Mostly because I live in an area where there are many natives. Growing up in an area where there was a lower population of natives, I was incredibly shocked and disappointed after I moved here. The majority of natives here are dirty and rude. They frequently steal and commit petty crimes. Many of them have this uneducated-sounding, mumbling accent they pick up on the reservation. Fucking ENUNCIATE. I work near a casino and the only people we ever see going in and out all day and night are Natives. Do they not work? Do they not have jobs? Many of them do get free money, and they will get a job for a short period and abruptly quit to work the system. They are given free money every year towards their reservations, yet the reservations still look like shit because they have no pride or cleanliness. My friend works in health care and she's told me countless stories about neglected and sexually/physically abused kids on the res. It's a SERIOUS problem. \textbf{Alcohol} is also a serious problem. Pine Ridge is about an hour from where I live, and it is literally the poorest shit stain in the US. Look it up. It sickens me when I see bumper stickers that say "Native Pride." What are you proud of? Your ancestors would be just as disgusted with you. These people don't need their land back. They will only trash it. They feel entitled because this is their "land." Yet, they don't do anything to better their situation or living conditions. Meanwhile they pop out multiple kids they can't afford. Their kids are running around with lice. They allow their children to be raped, sodomized and abused by their own uncles and cousins. I have NO respect for Natives. Not the ones like that, which is what I have to put up with day in and day out. Obviously not ALL Natives are like this, but in my experience (and where I live) MOST of them are. Cry if you want but these are FACTS. Just by doing a quick google search you can see that I'm not lying about the amount of abuse and criminal activities many Natives indulge themselves in. \textbf{Alcohol} abuse and sexual/physical abuse are rampant. Countless studies have proven it.Also, not all Native land was stolen. There were many treaties and agreements in reference to land. Even for the land that was stolen... they aren't the only fucking people. Every single country has been invaded or had land stolen. Every single country has invaded or stolen land. Native Americans just happen to be one of the more recent examples, so people whine about it. In most other countries, these people weren't given land back. They weren't given free money from the government either. I hope you guys just realize that some of your tax money going towards Natives are really going to Playstations and hot cheetos at Walmart at the first of the month instead of the cause you THINK you're paying for.\normalsize   & \cellcolor{green!27}alcohol & \cellcolor{green!27}Behavioural Addiction - Alcohol & \cellcolor{green!27}2/515 & \cellcolor{green!27}0.388 \\  \hline
  \cellcolor{green!5}\small My ancestory started from \textbf{R\textbf{ed}} Clouds sister and Wild Bill Hickok's cousin, John Nelson.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small In Australia the term \textbf{redskin} is a childhood memory of a sticky artificially flavoured deliciously chewy lolly\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I'm Canadian, and no, no they don't. All public schools are free, regardless of \textbf{race}. University isn't.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Angel Lee, if you live on a reserve and are status, you can qualify for exemptions that lower taxes.  You can be exempt from paying personal taxes if you earn your income on the reserve.  If you earn your income off the reserve, you are subject to pay taxes, just like ALL Canadians.  Same applies to schooling, if you're not status you pay for your schooling regardless of what your \textbf{ethnicity}.  Even with status, it's hard to obtain funding for post-secondary schooling.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}\small Nobody actually thinks any of these things\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small aren't they supposed to have a \textbf{tan} like Pocahontas?  Or in the \textbf{old} western movies? idk...inside too much I guess🤔🤔 but they supposed to be a bit darker right🤔😕😞\normalsize   & \cellcolor{green!27}Old, Tan & \cellcolor{green!27}Age - Over 65s, Nationality - British & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small \$5 Indian\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Probably because you're mostly white. Its okay to be white, you don't need to side with the \textbf{race} you're genetically like 5.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Julia Rose If I was 1/8 \textbf{Black} I wouldn't claim to be \textbf{African} American\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Yeah hate to break it to you, but those aren't the real natives, these are the European ones.  The true ones are the ones that they call \textbf{African} American.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small William Moreno stop what, telling the truth? And apparently AFRICANS are from AFRICA \textbf{dumb} one, and natives are from America, but one question, who and what do the natives come from, because blacks being the first people on the planet and originated in Africa they had to come from someone, and the ancient Indians were dark skinned not these so called Indians that are here today, and of course Indians will be in America, and Africans and \textbf{African} Americans are two different things, in fact they're smarter then us Americans.\normalsize   & \cellcolor{green!5}African, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Melanin Magic so that doesn't mean \textbf{nothing} ow I no more then u because of ur grammar bitch plz just stop kill your self\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Because you're not. Native Americans are \textbf{black} people in America. Aboriginal people\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Melanin Magic stop. \textbf{Nobody}, not even natives buy into your Afrocentric bullshit\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Melanin Magic    That is \textbf{nothing} but an Afrocentric lie.  Many of the Native American tribes keep strict oral histories much like the ancient Hebrews did, passed down generation to generation without a single word of defiance allowed.  We know our ancestors saw the white man before they ever saw the \textbf{black} man.  Also, ALL ancient forensic remains are of our people, the true Native Americans, and not negroids.  Our genome contains the 9 repeat allele, which no \textbf{black} or white people group carries.\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/83 & \cellcolor{green!5}3.614 \\  \hline
  \cellcolor{green!27}\small Native Americans should marry from their community to reserve the pure race\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small they look European \textbf{Indian}?? or did trump blow a whistle....mixed maybe because over the decades everything is turning from dark skins to pale skins\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small It still doesn't stop you from being European descent. Original Native American were very very dark like chocolate and some lighter. Today the media promote the mixed ones or white native Americans. They don't put someone of my complexion in the media. The \textbf{black} people in America are the original native Americans. History even says that and they said now it's applied to euro descent people.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small As being a Native American the one thing I hate is when people say that im \textbf{Indian} like no TF I'm not\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small why is the term 'redskins' \textbf{racist} or bad or offensive in any way? \textbf{nothing} offensive about being described by a physical features.\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small This seems to only interview girls from one specific tribe out west. I guess it's a \textbf{common} misconception that there is only one type of native american.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small "If we had free healthcare the heart disease and diabetes rate would be very low." Last time I checked, free services are usually the lowest quality because, you know, they're free. And "free" in this world usually means "paid for by taxes" so they have no incentive to help people, and therefore no incentive to become skilled at their jobs.Where I live, I'm supporting the community in recovery from the opioid epidemic. I'd say 80 or more of the people in recovery I've met became addicted to a prescription drug that was directly pushed on them by willfully corrupt medical staff. Most of these people were on "free" healthcare. Their \textbf{doctors} were so bad they were making them sick for more money.\normalsize   & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small isn't the \textbf{r\textbf{ed}} = native thing just black= \textbf{African}  and white= Caucasian  and yellow= asian?\normalsize   & \cellcolor{green!5}African, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}3/15 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small no \textbf{r\textbf{ed}} skin had \textbf{nothing} to do with blood. it was because the English were dicks and thought their skin was of a \textbf{r\textbf{ed}} hue.\normalsize   & \cellcolor{green!27}Nothing, Red & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!27}5/25 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small you are racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Love from an Amazigh... North \textbf{african} native 💝\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small its direspectful and maybe \textbf{racist} to buy anything native when ur not native\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small yeah for taking our land something that's still done to this day we don't try to drive you guys out now since we have law and we only have a small amount of land that was took wouldn't you be mad if your family had everything took and you had no say over it? or how about your whole \textbf{race} sent to space cause I wanted your planet\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small may you not forget the bill of lives and you have been destoring this world you say we should be greatful but your hands have blood you have been killing all races including yourself you leave we will to but your kind will soon start killing the others in the galaxy so in any way you kill and play like you HAD to do it and the money deal was different we didn't cut trees for money we traded for what we wanted i wanted a axe i'll give 3 horse but now it's you give me paper you'll get this much stuff and not to mention you gave us drinks and smokes we never had it so we got addicted then the hybrid children seen their fathers raping and touching so that must of started with native americans the schooling was took many of it a few elders many adults learning but they were drunk then children couldn't learn cause elders were dying or they just couldn't I still think without whites the world wouldn't be as bad as it is and what does africans have to do with this? seems you are inculding others than don't need to be bring others so you can find ground against me a 13 year \textbf{old} but yet i'll still say something you are showing your colors first hiding it while i showed mine now your revealing yourself and it's not pretty seems like you guys never change unless you are stuggling then your peaceful and helping I've dealt with one now i'm dealing with you and if you haven't seen i'm not say you should be this i'm saying why this i wrong you people truly don't change i've seen it in you and the other i wonder if all are like that but you can't say that unless they say\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/310 & \cellcolor{green!5}0.323 \\  \hline
  \cellcolor{green!27}\small oh now your talking about IQ's that was there way of life now cause YOUR \textbf{race} was SMARTER in their way means yours is the best and you weren't the only ones who kept history mine did just not in paper then say oh forget it, it's in a book now i can read it no my people were taught this and never wrote history e remembered it passed down then it was partly corrupted cause of the killings and drinking and have I never mentioned that Siberians are every tribe they must only thought since they kept theres' why can't we? and must of never got the messege\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small i forgot to mention yes we have blood but not in a way about every \textbf{race} was earned you've killed at least one of every \textbf{race} my kind only got the early ones before every \textbf{race} was here and there\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/40 & \cellcolor{green!5}7.5 \\  \hline
  \cellcolor{green!27}\small also funny how you can say we did this and we came from here but i think you don't know \textbf{nothing} of me or my tribe but yet you push me around and now that i'm fighting back you do the same push and push until you get your way funny reminds me of my mother and i stated i'm not a Siberian i'm lakota only killed them cause they started first in a way my people didn't approve of you wouldn't like your man/woman taken and you have no say\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small dude ur a european inbred \textbf{faggot} stfu go have some more inbred kids u cancer euroofag\normalsize   & \cellcolor{green!5}Faggot & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small namethatrevealsnothingaboutme non whites.... HahaYour history is full of torture devices and public decapitation. Throughout the UK and the America. Disgusting pools of blood on roads and shit thrown out windows.Stealing food from Irish white people during the famine allowing them to suffer and starve and die.Art work depicting most \textbf{race} in an ugly way\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small The truth is Native Americans were slaughtering each other in wars long before the white man came. Not to mention it was \textbf{common} for them to sacrifice small children to their sun gods. Everything happens for a reason, so i guess they got what was coming to them.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Scalping was implimented first by non-natives for bounty hunters who roamed America in search of \textbf{Indian} scalps, it eventually even became part of the US Army's policy back in the day. Collecting \textbf{Indian} scalps was practiced first as a means to not only eradicate Native people, but destroy their image in the world. In Arizona, an Apache mans scalp was worth \$100, a woman's  \$50, and a child's  \$25, so  any \textbf{Indian} with long hair usually fell victim.. Allot of people saying we scalped first, we only did it in response because it was happening to us, but we did it back in such a way that you know we meant we weren't playing about letting you kill us all, we just tried scalping more than they did to us...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/130 & \cellcolor{green!27}2.308 \\  \hline
  \cellcolor{green!5}\small Android Miller,.. We never slaughtered each other to the point of extinction, like how the first European settlers tried to ethnically cleanse "America" of Native peoples. And sacrificing to the sun god was primarily accustomed to a handful of powerful tribes of the day, like Aztecs, Incas, so on so forth.. a lot to discuss culturally and why they did what they did, but it won't matter explaining shit to you since movies and the internet can "teach" you all you need to know... And child sacrifice was practiced all over the world, Abraham almost sacrificed his own son because it was testimony to the times and what was going on around him, child sacrifice... And on your American loved 300 movie, the early Spartans killed newborns they deemed unworthy based on a disability.. again, the world is to big to judge and point the finger. I'm simply saying, we didn't get what was coming to us, our wars or conflicts we had with each other before the white man came never included genocide or \textbf{ethnic} cleansing. We had our differences but existed in relative peace, or we wouldn't  have had as many Native Nations as we had before we were killed off...\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/203 & \cellcolor{green!5}0.493 \\  \hline
  \cellcolor{green!27}\small Android Miller,.. Everyone was killing each other before the white man came, including us Natives, all men are capable of murder and for ages have always practiced it. BUT WE NEVER PRACTICED GENOCIDE,.. war or conflicts existed but not because of our differnces in skin color which there was none, but someone had to do something in order for us to react to kill... And we haven't met our last adversary, still have some to this day on our own reservations, where we have our sovereignty and fight for our exisistence in a country full of haters like you.. just shut up?? I actually haven't made a sound to shut up, you can say stop writing, which you should do because clearly you got something against me cuz I'm Native and I'm standing up to you and your false opinions, too many privileged white people today who let their mouths run, after their track record proves the whole non-white world hates them for their \textbf{crazy} way of thinking and actions, no matter what you just prove a point that millions like me are awakening to in these days, there are still \textbf{racist} ignorant people in 2018...\normalsize   & \cellcolor{green!27}Crazy, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/196 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}\small Android Miller,... Natives fought with one another over different reasons,.. theft from one another which could be seen as raiding, conflicts over hunting territory, or things were personal, where someone was wronged in some way, that's why we had strong warrior men.. when the white man came over, our fighting was different, it became a long standing war, white people wanted the land, minerals, and timber, whatever they wanted to create America... so the war was more complex and intense, at first we were somewhat peaceful with whites, until more and more kept coming.. in time shit was bound to happen, we weren't going to go down without a fight.. a lot of craziness was remembered on all sides back then, White and Native, but we still had a voice and our own reasons for what we did, if it don't make sense to you, I don't know how else to put it, I already told you a lot to try and get you to understand, that even though we did some things, we were human, acting only as humans would in those times.. We didn't have the technologies that the other side of the world had, and we didn't unify enough to repel the invasion... Native American history is a topic that keeps getting mutilated and cofused, all angles need to be understood to get a good picture of what it is you are looking at... And genocide, submission, trickery, and forced removal ended the \textbf{Indian} Wars... And to say that innocents die for the greater good like in Hiroshima is sickening, that's a more modern example of how evil has escalated even since the \textbf{Indian} wars.. And your so called "civilized" country today is godless, you all worship the doller, you all spend more time in front of the tv or phones that makes you stupid, your country is \textbf{g\textbf{ay}}, you have Satan churches in capitals and major towns, science rules the country, and \textbf{racism} still exists... America is corrupt, it lies to it's own people, it's unjust, and is backwards.. education is declining, crime is rising, there's a drug and \textbf{alcohol} abuse epidemic, so what is so perfect about this country that was built on Native blood and stolen land??\normalsize   & \cellcolor{green!5}Gay, Indian, Racism, alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol, Ethnicity - General, Ethnicity - Native-American, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}6/373 & \cellcolor{green!5}1.609 \\  \hline
  \cellcolor{green!27}\small Android Miller,.. 90 killed off by disease?  Naw more like 50 killed by disease, 40 by war, genocide, or conflict, whatever you want to call it, and 10 of us survived till this day... No matter what we did experience genocide, removal, and renewal. And it was genocide because the US government made it a key to attack and kill Indians specifically, or \textbf{ethnic} cleansing of some sort, we were the only targets.. rounded up and massacred like at Wounded Knee... idk, I'm done arguing with you, I said all I had to say, and it keeps going here and there,.. fuck that, I got better things to do, read back and all my opinions are stated. Yeah partly mixed with pride, but I can tell it's the same with you, proud educated professor.... teach on........ or preach on.....\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/139 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}\small Android Miller,.. It went from slaughtering and scalping, to disease and death numbers.. But reguardless of being seen as savages, we helped build that modern era, after the reservations were established, we helped the Army as scouts, we built roads, trails, and dams, we helped build the modern era. That goes unheard of, only we remember such things, or no one knows anything or thinks we sit on the rez and do \textbf{nothing} but drink.. a lot of Natives after the reservations were made, were busy people with a rich culture still dealing with opression.. \textbf{Indian} agents, and government control. Boarding schools and culture eradication. But in the 1970s we've been on a rebound, trying to regain all we've lost..\normalsize   & \cellcolor{green!5}Indian, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}2/120 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Yeah we didn't have to give you \textbf{Indian} reservations but you got them.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Why is everyone drinking themselves to death on \textbf{Indian} Reservations?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Android Miller,. You use "we" like you did somthing, you did \textbf{nothing}. And the "we" that did make reservations, made them as an attempt to try and control and segregate Native people. It wasn't like we enjoyed getting the reservation package when the whole continent was our stomping grounds. No one gave us what was already ours, the reservation is just an idea that really didn't work, we go back and forth as we please, we formed new communities beyond the concentration camp reservations, and we have our sovereignty because we did it on our own, they gave us our reservations because they knew they had too...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}\small So you can say "we showed you guys how to survive in the new continent", as if you personally showed them how to survive. But when I say "we" its a problem? I'm going to have to call you out on that. Sorry but we didn't have to give you people anything.  There's no rule in war that states you have to give the loser anything.  WE also didn't have to give 238 tribes \textbf{Indian} casinos that earn tax free money.  The government spends \$20 Billion a year in benefits, programs, etc. for Native Americans.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Android Miller,.. ok, me using "we" was a contradiction on myself,.. you can say "we", just as much as I've been using it... But I'm going to call you out on thinking that your white people "did things" for us, none of you did shit for us, our self-determination kept us alive, we fought to exist,.. your people woke up to consciousness and thought it was better and easier to make reservations for control and assimilation. And casinos were ideas thought of by each Tribal Council that decided to use \textbf{Indian} Gaming as a means to economically sustain the Tribes... our own will is why we have all we have, from reservations to everything we have. Yeah, poor people live on welfare, but it's a fact that not all Indians get free money from the govenment, like everyone else, you have to meet certain standards to get "free" shit... And if we make money on the rez, or any rez, it's through our own enterprises, not the government, anything the rez has ever offered me was through the rez, not the government, we take care of ourselves, at least we do on my rez... the government spends money on fake white \textbf{Indian} rezes that actually do exist, where a small Tribe of like 200 white people claim \textbf{Indian} blood, have white skin and get sovereignty somehow,... those Tribes you need to be looking into when it comes to "free" shit, and real Natives know Native, I can tell by facial features and skin color that stick out like the mountains in the ground,.... But those so called Natives are frauds and phonies... so go talk to them...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/277 & \cellcolor{green!27}1.083 \\  \hline
  \cellcolor{green!5}\small yeah you're not \textbf{r\textbf{ed}} skin because you're bloodline was obviously mixed with white. Real native Americans were a beautiful dark brown. like cinnamon.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Dark brown and cinnamon are not the same color ..... color \textbf{blind} are you?\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I'm Native American and I was part of the \textbf{R\textbf{ed}} Skins as a small child. Given how that particular logo is now a relic of the past, I wish I still had it as a souvenir. \textbf{Racist} carricitures are a part of this country's collective history. My mom worked in antiques and she collected a lot of it.\normalsize   & \cellcolor{green!5}Racist, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}3/58 & \cellcolor{green!5}5.172 \\  \hline
  \cellcolor{green!27}\small Joel Kotto ....there are "facial features" that are shared in all peoples.....so you see white in a \textbf{r\textbf{ed}} face ? small world is it not ?   Natives have people who are light skinned and dark skinned and all in between....you seem very limited in your views of people. The NDN's have a large variety of looks and shades ...though they tend to be closer to  Asian....but like any people ...they allso have euro or \textbf{african} features to....they don't all look the same and all wear \textbf{r\textbf{ed}} head bands with one feather\normalsize   & \cellcolor{green!27}African, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}5/91 & \cellcolor{green!27}5.495 \\  \hline
  \cellcolor{green!5}\small I thought we were called \textbf{r\textbf{ed}} skins because of a thing called asian glow (face turning \textbf{r\textbf{ed}} when drunk(, and we were stereotyped to be drunks (I'm in denying it tbh).\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/31 & \cellcolor{green!5}12.903 \\  \hline
  \cellcolor{green!27}\small My family always gets mad when I talk about how fucking stupid it is that there are sports teams with Native American mascots. Like...um who the hell thought it was ok to have a \textbf{race} of people be your Mascot??? like I think the fuck not. It pisses me off and no one takes it seriously at all.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small Umm.. where are the actual Native Americans ? That \textbf{r\textbf{ed}} skin story was pure b.s....\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small I'm mixed with \textbf{black} and native american my skin tone \textbf{tan}.\normalsize   & \cellcolor{green!27}Black, Tan & \cellcolor{green!27}Ethnicity - Black, Nationality - British & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small im native, and i \textbf{dot} think that having a football team named after us is \textbf{racist}, i think people are over reacting. I mean, if anything we should take it as a compliment that we have a team named after us. (lol that sounded super arrogent like everyone in this vid XD)\normalsize   & \cellcolor{green!5}Dot, Racist & \cellcolor{green!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh), Ethnicity - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Honestly the indigenous Natives were \textbf{black} \& coppered \textbf{colored}. Not saying these girls don't have any Native in them at all. But I can guarantee they are more European descent than indigenous Native American because of white washing. Indigenous (original) Native Americans still exist.\normalsize   & \cellcolor{green!27}Black, Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Who the fuck thinks this? \textbf{Nobody} thinks this lol\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Native Americans don't owe ANY non Native American an explanation. All these stereotypes are from white Americans ignorance and \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small here in Canada, native americans get lots of government hand-outs BUT I don't find anything wrong with that. After all they've been throught, it's \textbf{nothing} much...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Actually, they are no more native Americans than any white people are.  They are in fact "\textbf{mongoloid}", which is an Asian \textbf{race}, and thus they are "immigrants" just as we all in America are.\normalsize   & \cellcolor{green!27}Mongoloid, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Ones I Know Already Amerindians are not actually1. Always \textbf{R\textbf{ed}}2. Indians3. The Same As Alaska Natives4. Hunter Gatherers5. Warriors6. Casino Workers And Owners7. Hotel Owners And Workers8. Motel Owners And Workers9. Owners And Workers Of Lodges10. Owners And Residents Of Reservations\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/51 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small j escoti We \textbf{african} americans help create this USA country too the whites came and got us!!\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small No we own these lands now and you mongloids are \textbf{nothing} to us\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Too bad they're too dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/1 & \cellcolor{green!5}200.0 \\  \hline
  \cellcolor{green!27}\small j esco why only european?\textbf{Racist} much??!!If you do that,also kick out the blacks,the asian\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small j esco the average \textbf{racist} white man won't let anyone live on peace. No matter where you come from,or where they came from.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Y'all got me all types of fucked up..... I'm-........I dont what the fuck I am....I identify as \textbf{black} but I know there is more like people tellin' me I'm \textbf{Indian}, White,from one of the native peoples of Jamaica and America  all kinds of ethnicities from my family and all I know definitely is that I'm \textbf{black}.... but there's somethibg else going on.....I have an identity crisis and I don't wanna go back to Jamaica I came here for a better life....\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/81 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Racist Asshat, this type of stuff needs to stop.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small i think mike tyson more look like a native american than \textbf{african} amercan\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Crazy Horse!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small America belongs to Asian \textbf{Race} \textbf{Mongoloid} , Asians have the right to deport White gypsies to Europe and Caucasian mountain , Asia and America is for \textbf{Mongoloid} \textbf{Race} .\normalsize   & \cellcolor{green!27}Mongoloid, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/29 & \cellcolor{green!27}13.793 \\  \hline
  \cellcolor{green!5}\small Minnesota Vikings Notre \textbf{Dame} Irish\normalsize   & \cellcolor{green!5}Dame & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small literally \textbf{nobody} thinks native Americans still live in tipis\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Actually us Natives get the Nickname \textbf{R\textbf{ed}} Skin because of Our Skin Complexion We have or (Had) A \textbf{R\textbf{ed}} Undertone In my Family it still goes Strong I turn \textbf{R\textbf{ed}} easy. people call me Rudolph the \textbf{r\textbf{ed}} nose reindeer Whenever I'm cold because my Nose Turns \textbf{R\textbf{ed}} lol. The reason She doesn't have the \textbf{R\textbf{ed}} Undertone is because She Obviously is mixed with a Decent Amount of European blood.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}12/69 & \cellcolor{green!5}17.391 \\  \hline
  \cellcolor{green!27}\small Skin color has \textbf{nothing} to do with \textbf{race}, its a gene that can be turn off and off, which usually does in most of the population. Blond hair didn't even appear in Europe until 3,000-5,000  years ago. That trait was brought by the Steppe people. Southern Europeans were the first with color eyes but they were dark like Native Americans. Even today, Southern Europeans tend to have darker tones. I actually live in Spain now and I tend to be paler than most Europeans, the only things that differ are my features. Even features change through history due to diets and genetics changing. We will never be our ancestors and our future humans will not look like us.  Even before the Europeans came to the Americas. There were light skin Native Americans. In the Aztec world, these children would be taken care as well as their families for the rest of their lives. The child would be sacrificed to the Gods after a certain \textbf{age}. Having a light skin baby was a huge deal in Native culture. In some USA tribes, these children were usually seen as gifted and could often tell you the future.\normalsize   & \cellcolor{green!27}Age, Nothing, Race & \cellcolor{green!27}Age - General, Age - Youngsters, Ethnicity - General & \cellcolor{green!27}3/195 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small Studies have also shown that most of Latin America has a higher percentage of Native American genetics than previously thought. The census doesn't mean much, but genetics do. People can check a box that they are white, but even those people have a huge percentage of Native genetics. I'm proud to have Native. I never say I'm Hispanic or Latino. I say, I'm an American citizen! I'm Native American and French Basque which is what I am. \textbf{nothing} less \textbf{nothing} more.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small No, I'm Mexican my skin is brown. I use to live south of Mexico. I'm native to my land. I'm an \textbf{Indian} in Mexico Aztec. We do look like Native Americans but we don't share the same culture. They are the original in America and we are the original of Mexico. We were welcome by the Native Americans. Unless your mom is Mexican and your dad is Native Americans then yes you are Native Mexican-American.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Also, don't forget Mexican is a \textbf{nationality} Just like the United States of America. That says \textbf{nothing} about who you are beside your \textbf{nationality}. My \textbf{nationality} is American. If you live in Mexico and have Mexican citizenship then you are Mexican. Even though I am American I am French-Basque and Native. As a basque, I lack certain genetics that the Spanish brought.Like Middle Eastern (Moor) or even \textbf{African} Genetics or Asian. I'm basically pure European since the basque are the oldest known Europeans in Europe (who never mixed with other tribes,) and I'm Mix with Northen region Naitve (Miwok tribes of California). Those things are important to me because it helps me understand why my family came to the Americas and how did they live in the past. I'm a product of all this. If we know our past, we know our future, and we become stronger people of ​The America's. Yes most of us are Mix, but we hold a rich history in North America and we must help our brothers and sisters that are Native and tell them we are part of you and we stand with you.\normalsize   & \cellcolor{green!5}African, Nationality, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Nationality - General & \cellcolor{green!5}5/190 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small I'm Hispanic and in my country only like 10-15 is Native American the rest of us are mixed between European , \textbf{Black} and Native American , some people have more of European others have more of \textbf{Black} and others have more of Native American\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small APACHE RENEGADE Every time someone call me \textbf{Indian} I correct them and tell them what I am an AMERICAN. because I didn't born in India an the they realize about their mistake. It is something important to me to recognize myself as an American and no as and \textbf{Indian}. I use the term Americans and sometimes native American.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/58 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small JAZZ Jam,.. yeah that's where language, culture, and identity kick in.. all the names I just listed are what the other, non \textbf{Indian} world label Native names, like how I'm not really Apache, I'm Dilzhé'éh, a northern band of ŃŃ'ÉÉ in Arizona, that's what helps us recognize who we really are, and every Tribe is the same.. I don't know what Pimas called themselves in their language but that was their true identity, as for all nations, languages, and peoples, the names they had in their languages recognized who they were..\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small JAZZ Jam,. Yeah the invaders used religion as a tool of war, to them that book deemed them superior and god sent. They saw Indians as pagans or Satan worshippers. They killed in the name of the Lord. They believed they could create a Christian country, when today their descendants don't believe in their god, or they blatantly worship Lucifer with their new churches, they take god out of their government buildings and schools, and they killed Natives just to create a country that does not epitomize a model follower of Christ. I do believe in God or the Creator, and I believe God has many forms and manifestations. And to us Apaches we have a supreme being or Creator in our langugae, and there are spirits/angels, the gááns or mountain spirits, and there's Changing \textbf{Woman} and her son Monster Slayer who is like our Jesus. And there's all the other powers and spirits we recognize, animal spirits, celestial spirits, and earthly, like the mountains, trees, and water. We had a strong sense of life and we were intelligent people..But it's good your learning, hopefully Natives continue educating themselves in their culture and heritage... We need more smart Injuns to combat today's failing society, a society that tries to rid itself of the Indians, or the \textbf{Indian} problem, today the battle is against assimilation, those who oppose our sovereignty, and against those who act as if the Natives never existed...\normalsize   & \cellcolor{green!5}Indian, Woman & \cellcolor{green!5}Ethnicity - Native-American, Gender - General & \cellcolor{green!5}2/241 & \cellcolor{green!5}0.83 \\  \hline
  \cellcolor{green!27}\small ONE STEREOTYPE IS THAT NATIVE AMERICANS LIKE TO STEAL LEFT SHOES!!!......THE WANNALAYA PRACTICED LEFT SHOE STEALING BUT ONLY FOR A SHORT WHILE!! ANOTHER ONE IS THAT THEY ALL CAN TURN INTO WOLVES......NOT TRUE....ONLY A FEW CAN DO IT!!....AND FINALLY THAT \textbf{INDIAN} MALES HAVE NO NIPPLES.....OF COURSE THEY DO....THEY HAVE ONE NIPPLE.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small Squaw, get em firewood!\normalsize   & \cellcolor{green!5}Squaw & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small one thing is true tho . native Americans are \textbf{racist} towards \textbf{indian} , arab and jew guys\normalsize   & \cellcolor{green!27}Indian, Racist & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Oversimplification of history and generally how the word "advanced" works. You \textbf{dumb} uneducated piece of shit open a book not just your snapchat\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small I couldn't agree with anything else for a week, because that's how much I agree with you. People are so \textbf{dumb} and heartless, like Trump\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small You sound so stupid. Who do you think?! You really don't make any sense, you're just mad because it's true. Obviously, sense you need an obvious answer to your \textbf{dumb} nonsense question, it's whites. If they took over the land, who else. Stop being so petty, you just can't face the truth.... or think properly, "No Offense". I hate writing comments that could hurt mini trump's feelings, but really, don't try being a jerk to other people, when you know they have so much more knowledge than you. So calm down, stop feeling so eager to try to prove someone wrong. I mean really, you know it's true, I see so many comments like yours, and it's annoying. So there is your answer, jerk\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/124 & \cellcolor{green!5}0.806 \\  \hline
  \cellcolor{green!27}\small Zer0Gravity X I'm assuming you're replying to me? First of all, "since" not "sense", a question mark is needed after "else", and your punctuation is all over the place. Now, I'm guessing you're either trolling or a 10 year \textbf{old} because A) No one mentioned Trump here, and B) I'm far from a Trump fan (not even American so I don't even care).Second of all, like the original commenter and the other repliers, you aren't making any good arguments. Western culture (which is predominantly "white") is arguably one of the most influential if not the most influential cultures in history. So like it or not, "white" people contributed a lot of good things to humanity. Also, before you assume I'm white, I'm not :) so don't drag me down that bullshit argument either.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small +Jim Gallagher Yes, the dark skin Europeans (who were not even of Caucasian blood at the time) were the first to come into this land, but many native tribes evolved from both \textbf{mongoloid} and Africans.  This was long before white people came to be.  The natives we know of today are an evolved species that evolved in the Americas...therefore their breed of human is technically indigenous to America or originated in America.  Therefore they are the first species to evolve in what is now America.\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}\small +Jackisana Its hard to tell what white people invented because they take credit for everything another \textbf{race} invented...and then write it in their own history books.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small +sonafanchick- "Well, from personal experience-"Personal anecdotes do not count as fact.  Otherwise anything anybody says can be counted as the truth.- "Madonna still takes credit for "voguing"So?  Who takes Madonna seriously?  I will tell you.  The same people that take Justin Bieber seriously.  Morons.  You can like their music, just dont take them seriously on an intellectual level.- "People still credit Elvis for Rock n Roll."Elvis merely popularized it.  The origins of rock and roll are ambiguous at best, seeing as its a blend of several types of music from the early to mid 20th century America.  Or do you have a more precise definition?  And what makes it true?- "I wouldn't be surprised considering that white people used to oppress people"Every \textbf{race} has oppressed people at some point for a prolonged period of time.  NO \textbf{race} or people are innocent in terms of history.  Why is it that ONLY white people are demonized for something everyone else has done?  Looking down on white people for things that used to happen only shows your own bigotry.- "and they hardly ever put the name of inventors that were not white."Well, until someone comes forth with a more accurate depiction of what happened, whos to say that the status quo is wrong?  You?  Show me the proof.- "They would put "unknown" or no inventor at all.  Just look at the artifacts.There is physical proof that they would not give credit where its do and modern proof at that. Not just something written in a book."Do you have proof of that?  Besides, has it ever occurred to you that maybe the reason things are labeled as "unknown" is because \textbf{nobody} actually knows?  Since you seem to know everything, maybe you should go work at that office, that way everything will get labeled correctly.Seriously though.  Proof.  Bring it.  Please.  Im not one of those "listen of believe" types.\normalsize   & \cellcolor{green!5}Nobody, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/327 & \cellcolor{green!5}0.917 \\  \hline
  \cellcolor{green!27}\small sorafanchick You're seriously retarded if you think no other \textbf{race} occupied and stole other territories/lands. Even the natives killed other tribes and took over their villages.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small +Sarah theGeek American's didn't invent guns. Nor did the Europeans. The invention of guns was triggered by Subutai Khan, one of Temujin Ghengis Khan's generals, when he was trying to get around the difficulty of transporting siege weapons across the hellhole of Turkey. So he pulled together his pet \textbf{engineers} and they mixed Persian Steel, Chinese Gunpowder and \textbf{Indian} blowguns together and came out with the first cannon.\normalsize   & \cellcolor{green!5}Engineers, Indian & \cellcolor{green!5}Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}2/68 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small +Kladstone1.) Weaboo a.k.a weeb...a word made up  by a person that actually made a typo and it became an internet meme afterwards.  You're a apart of a stupid generation that resorts to internet slang to get our point across. I can't even take you seriously.2.) Natives were not CONSTANTLY engaged in war because their tribes were spread further apart.  It would take months to travel sometimes to an enemy's territory through brutal weather and climate.  It was easier to be allies with tribes.  Most would have trade agreements or marriages to keep peace. This is why Natives began dividing territory among each other to make sure everyone had their own territories.   It wasn't until the introduction of the horse that more raids too place.  The horse was introduced by Europeans.  And again, they never tricked any one that was their ally.  They never fought allies.  White people turned on even their native allies.  Its funny again that you tell me to read a book yet you say the world was young when the Native's land was taken.  Actually, those years are fairly recent.  More recent than American slavery and more recent than \textbf{Jim C\textbf{row}} Laws were established.  Maybe...you should stop embarrassing yourself and do for yourself what you tell others to do...read a mfing book.\normalsize   & \cellcolor{green!27}Crow, Jim Crow & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/217 & \cellcolor{green!27}0.922 \\  \hline
  \cellcolor{green!5}\small sorafanchick I never said the natives deserved it moron....but they became a victim of social evolution.  And yes, Europeans are being incredibly stupid with their current foreign affairs, and immigration policies.  They could very easily become the next dismantled \textbf{race}, unless they wise up, and quit with the same political correct bullshit that brought an end to the Romans.  Those who do not know History are doomed to repeat it.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small +Michael Kearns " until they proved too stupid, and allowed themselves to be conquered"  This sounds like you think the Natives deserved to be conquered because they were "stupid" in your opinion.  Apparently you think "stupid" people deserve to go down. Otherwise you wouldn't be making excuses for it. "Those who do not remember their history are condemned to repeat it" Yes, this is true for all people.  And this is why Native people put so much emphasis on their past...to never make the same mistakes they did when their land was conquered by trusting white people. You're right.  Europe should wise up...but if they don't, hey, its apart of good 'ol social evolution.  It is inevitable, right?  No \textbf{nation} lasts forever.  At least that is one thing the Natives learned.  I wasn't being sarcastic when I said they were stupid for trusting white people.  This is the truth because white people ended up turning on the allied tribes as well because they wanted the land for themselves.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/168 & \cellcolor{green!27}0.595 \\  \hline
  \cellcolor{green!5}\small +sorafanchick A week or too away on foot, often as not. There were of course those who ran for months to aid those on the other side of the Iroquois and south American nations, but that wasn't particularly \textbf{common}. My point mostly was that it was a lot like medieval Europe in terms of travel distances. Less so in many cases because they didn't travel in massive armies requiring slower speeds and massive supply chains. On them trusting Europeans, yeah they could have handled that better. For the first 50 years, they had the upper hand on regular occasion, but kept not following through by the anthropology books I've read. They always would have lost by resisting, Europe just had too high a birthrate at the time and too large a military base, they would never have stopped. But the indians could have tried to work from a position of strength and absorb the incomers and take on their strengths instead. Honestly though, they did alot better than their more developed south American cousins against the Spanish. Reading studies on the Conquistador I can easily see why people would still hold a grudge after the great great grand children of all the morons involved on both sides was already dead.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/210 & \cellcolor{green!5}0.476 \\  \hline
  \cellcolor{green!27}\small +Michael Kearns Actually I agree with you here.  The Europeans also had more experience with massive warfare.  While the natives did go to battle, it was usually not as often that they had to defend themselves because most other natives around them were just as defended or defenseless as they were.  Whereas in European countries that are so close to \textbf{African} and Asian nations, Europeans had to defend themselves on all sides and so it pushed them to develop more efficient weaponry.  To add, they did have more advanced medicine because they had more experience with stronger diseases.  The natives were weak in comparison to these advantages.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}\small Boy, a lot of shitstained comments here.  The technology for cellphones came from a \textbf{black} man.  60 of the world food supply is Native American in origin, the Chinese invented gun powder AND guns, and Japanese people created the miniaturized computers/components we use today.  There is a LOT of garbage comments here, and it's apparently by white people.  Natives weren't here first?  Where is your proof?  Scientific, and archaeological?  You have none.  And before you start, Land Bridge Theory was debunked long ago.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}\small +Aniyunwiya Ageya, I'm assuming you're referring to Jesse Eugene Russel? Lots of sites credit him with the cell phone, but the patent office does not. Instead it credits him with 112 patents involving mostly broadband communication infrastructure. This would suggest he was instrumental in the proliferation and possibly development of cell phones, but not the phone itself. The thing you seem to fail to understand is that statistics are easily researched and while there are indeed exceptional \textbf{black} people, more exceptional people of native American descent and many exceptional inventors among the ranks of the Asian ethnicities, American whites are still solely responsible for a significant chunk of inventions over the last 200 years and a larger chunk of so called key inventions.If this were simply recognized by people at large there would be no problem. All races have their genius inventors, and their not so genius innovators. But current propaganda (and +Sarah theGeek's comment is a good reflection of this) is that whites had \textbf{nothing} to do with anything except slavery and conquest. This is patently untrue.\normalsize   & \cellcolor{green!27}Black, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}2/179 & \cellcolor{green!27}1.117 \\  \hline
  \cellcolor{green!5}\small Yeah...look at this FUCKED UP MESS!  When you fuckers got here, we could drink water from the source.  Our food wasn't full of sugar or pesticides.  We didn't have fucked-up diseases we couldn't cure.  The air wasn't toxic.  Do you think "progress" would never have made it here, had it not been for vile colonists?  Do you think white people invented everything?  If you do, then you've just proven how incredibly fucking stupid you truly are.  \textbf{Dumb} ass.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small +Aniyunwiya Ageya I know you're a brainwashed leftist pleeb, but do try to be reasonable. Everything we break, we clean up. With the exception for Marxism, that mistake we keep pushing.(250Million genocide and counting...)On the slave issue, keep in mind that the Native North Americans were never slaves and the \textbf{African} slave trade was 7000 years \textbf{old} by record, longer suspected. Europe had a hand in it for 200 years and put up major capital to STOP it. If you really want someone to whine at, look to Islam who participated in the \textbf{African} slave trade for 1300 years and are still trying to keep it alive in present day. On what wealth and infrastructure was built by slavery, post civil war reconstruction erased every penny of it, we owe you \textbf{nothing}. The Rich Democrats who Actually kept and bred you like cattle still keep and breed you like cattle, the difference now being they want your votes, not your labor.\normalsize   & \cellcolor{green!27}African, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}4/163 & \cellcolor{green!27}2.454 \\  \hline
  \cellcolor{green!5}\small Hugo Jones, are you mentally incompetent, hilariously uneducated, or so generalized you're \textbf{racist}?In the case of america, north was a 400 year back and forth slug-fest; south with the Spanish and Portuguese you have things more or less correct, but it was still largely mutual. The Spaniards were simply the more effective monsters. Read an anthropology text some time. Something with actual research and references. On the rest of it, genocide and pogroms were rampant across africa for the 7000 years of recorded history; sporadic across the 5000 years of white history and systematic across the 6000 years of Asian history.What we now call warcrimes? That was standard military doctrine until more or less the Napoleonic wars, the world over. Making them crimes didn't really stop them, but its still a white moral system trying to limit them. We more or less have to force it on other cultures. Even today. Especially africa and the middle east where they're still culturally acceptable. Mass rape? Every single culture across their entire history. Where war went, rape was left in it's wake. It's STILL rampant all over africa. Very sporadic and individual in white countries. And child rape? Legal in the middle east. Illegal in every white country, even though it still happens.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/213 & \cellcolor{green!5}0.469 \\  \hline
  \cellcolor{green!27}\small White people made all the good shit...LOL...bullshit.  Someone else invented it, white people stole it and changed it, and you have \textbf{zero} idea who 'improved' it, dumbass.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Sorry, not my day for miracles...you've already assumed I live 'in the 'hood', which I do not.  I do not live on the rez, either.  I live in a suburban neighbourhood in a 121 year \textbf{old} house that I own and maintain.  Stupid such as yours I see daily online, and as I stated, while yours is incredibly stupid, it's not the most stupid I've seen today.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small My response to each statement: "Native Americans still live in tipis." First of all, not all tribes even used tipi's but a majority of plains tribes did like the ones I come from and no, that era of living has ended around the late 1800's, early 1900's I believe."Native Americans get lots of handouts." This is a widespread belief amongst a lot of non-natives. Even if they did, it might've been because the government made treaties where they promised direct help in exchange for land in the past but as we all know, most treaties are not even practiced or respected."Native Americans don't pay taxes. lol I'm Native and only 21 and I pay taxes. If you're Native and live and work on the reservation you are exempt from state tax I believe but you are still subject to federal tax but if you are native and work off the reservation then you are still subject to state and federal. It might have to be due to the fact that reservations are considered "sovereign." I'm not completely sure."Native Americans are rich off of casinos." Some native tribes have gained a lot of financial prosperity from casinos but that is a small number of tribes who have and those tribes usually have strict enrollment qualifications and sometimes low enrollment so even that is a low percentage of natives. I know damn well my tribes are not rich off of our casinos. lol"All native Americans wore headdresses." Not all tribes do wear headdresses and not every tribes headdress were alike. Also there were different kinds of headdresses as well. My tribe wore headdresses but like they stated, only certain people are allowed to wear them."Another word for Native Americans is \textbf{redskin}." There's no word like that in our language. I never have once heard someone within our own people call ourselves \textbf{redskin}. I personally don't like the term either. I personally would rather be called by my tribe.I have been asked these types of questions before and thankfully, the non-natives who ask are always willing to listen and try to understand. I have been asked so many \textbf{crazy} questions on "being native" as well, it is \textbf{crazy}. lol\normalsize   & \cellcolor{green!27}Crazy, Redskin & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/372 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small Jaris Goes Ahead PrettyI know why you do not mention the maya and the Aztec, its because they where advanced and organized while the American indians where stuck in the stone \textbf{age} fighting the white man for no fucking reason. People like you blame American white people for everything when if you truly look at it every \textbf{nation} was founded on the conquering or another people, look at the Russian mongols and turkic speaking peoples, they are just like the American \textbf{indian} in genetics and like the plains \textbf{indian} in lifestyle, they enjoy being under russian rule, oh and just so you know, I am Native too, Cherokee.\normalsize   & \cellcolor{green!5}Age, Indian, Nation & \cellcolor{green!5}Age - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}4/109 & \cellcolor{green!5}3.67 \\  \hline
  \cellcolor{green!27}\small White people, please quit lumping us into one group and only interviewing a few from that demographic.If you're German and every video, article, or bit of media that ever covered europeans or european perspective featured French people would you get tired of being represented by the French? I'd say the biggest misconception about my people is who we are relative to. The media loves to group all of north america together and all of south america together and not even address the fact that quite a lot of those tribes have more to do with people from the other continent than people east or west of them.White man seems to think his influence on us is greater than the thousands of years of culture, but it's not true. Y'all also seem to think the American colonies, France, Spain, the Dutch, and Portuguese all explored and conquered in the same manner.  I've more in \textbf{common} with an Arawak than a Cheyenne. Not just because of our shared pre-european history, but because our european-american history is more similar as well. I'm not \textbf{Crow}. I wasn't \textbf{Crow} thousands of years ago, I wasn't \textbf{Crow} hundreds of years ago, I'm not \textbf{Crow} now, but you damn sure can't tell by this video.\normalsize   & \cellcolor{green!27}Common, Crow & \cellcolor{green!27}Ethnicity - Black, Social Class - Working class & \cellcolor{green!27}5/209 & \cellcolor{green!27}2.392 \\  \hline
  \cellcolor{green!5}\small What tribes do you represent?  How much contact do you have with other tribes throughout the country?  I loved your video but in somethings it is not good to speak for all Native Americans.  I live in Oklahoma.  I am not a Native American but I'm learning about some of the tribes.  I have had a Choctaw tell me about benefits they receive.  He was encouraging us to see if we where Choctaw so we could get the benefits too.  In Oklahoma, there are special Clinics and hospitals for Native Americans.  I don't know if they are free or reduced priced.  There is some benefit to going to them or people would not drive over an hour to go to them.  We have \textbf{Indian} WIC which I was told is better than normal WIC.  Much of these benefits come from the revenue of the casinos owned by the various tribes.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/150 & \cellcolor{green!5}0.667 \\  \hline
  \cellcolor{green!27}\small I love that Teen Vogue is woke af while Vogue recently dressed Karlie Kloss in \textbf{y\textbf{e\textbf{llow}}} face instead of getting an actual Japanese model. Keep it up Teen Vogue. 👏🏼\normalsize   & \cellcolor{green!27}Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}3/30 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The most respectable \textbf{nation} to which imbued with deep respect, to its great past and traditions, may God bless every \textbf{Indian}!If there is a desire to communicate, to want to learn more about the culture of Indians\normalsize   & \cellcolor{green!5}Indian, Nation & \cellcolor{green!5}Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small I am not attacking them, I am attacking this \textbf{racist} video.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Eddy Viscosity I'm sorry that things like that happened where you are. But it's not everywhere, and it's does \textbf{nothing} to help to say that it is! My best friend is white (German but English speaking)  and I love her and I love German people and I think they are really sweet and comforting, and not the stoic and strict (over generlized and seemingly untrue) stereotype they have to deal with. 😊💙\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small +Spooky Babe That's actually a pretty good comeback and I laffed. But I do have friends. Just not \textbf{racist} ones. And I measure my friends by quality not quantity.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I'm First \textbf{Nation} it's basically the first people in Canada but we don't have to pay taxes oh the Rez and The government pays for our university/College  and medical school but we have to work hard for that it's fair only 1 million First Nations in Canada there was originally around 100 million before so and I'm mi'kmaq there's only about 40 thousand also my family is also Native American because I'm also Coast Salish :3\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small I'm half \textbf{black} and half Native American\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Mikayla Bonner, Same thing. "\textbf{African} Americans" are Native Americans. \textbf{Black} people are indigenous to this planet. American history is full of lies. :)\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Big \textbf{Black} Cock true\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small i think the native american lifestyle is being used to keep people homeless forever. think about it all. the tent. the seperation from the "white men".forming groups but not coming together to build.bad relationship with \textbf{alcohol}. eating corn. it seems more like a tool than a culture.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Maukie Paukie I hate being White, I was under the assumption that I'd be a rich CEO for a multi-billion dollar company, with no criminal record, the ability to have \textbf{sex} with any \textbf{woman} I wanted, and to get into any school I wanted....all lies.\normalsize   & \cellcolor{green!27}Sex, Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}2/45 & \cellcolor{green!27}4.444 \\  \hline
  \cellcolor{green!5}\small A large group of \textbf{black} people. They assume that no crime will ever show up on your criminal record, you will get top jobs without qualifications, you will get free money from the government etc. because you're white\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small Well tell those fucks that you don't speak 'Welfare'. Statistically speaking a white person is less likely to commit a crime than a \textbf{black} person, that's a fact.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Maukie Paukie It's not a generalization when the statistics come from a government welfare statistics website. Nice try though! And it is true, as I said, look it up. I live in a predominately white and Native state, and a majority of whites don't fucking work. I also live in a Republican state, which are known to recieve most benefits, and those who recieve benefits are broken up by their \textbf{race} and percentage of how many of each \textbf{race} accepts welfare. But you're retarded and can't understand statistics, so...And obviously, your "mom's friend" is living beyond her means and that isn't anyone's issue. You only have two jobs if you're living beyond your means, have more kids than what you can afford, or make poor financial choices. Not anyone's fault but her own.Blacks and Whites are the two races that eat up the majority of welfare. That's facts whether you like it or not, Trigglypuff.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/157 & \cellcolor{green!5}1.274 \\  \hline
  \cellcolor{green!27}\small A lot of \textbf{race} baiters in the comment section.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small These are real natives ..not some \textbf{dumb} ass people sayin they are gods people and chosen and always been here....who would believe that shit? more \textbf{mental} patients ?\normalsize   & \cellcolor{green!5}Dumb, Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I'm 25 \textbf{Indian} my dad is 35 \textbf{indian} my grandma is 50 \textbf{Indian} my great great grand father is 100 \textbf{Indian} so yes I get offended all the time about Donald Trump about the way us Indians are miss treated everything I'm Cherokee Blackfoot English and mixed \textbf{black} and white I live on American soil\normalsize   & \cellcolor{green!27}Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}5/55 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small A tribe isn't a lifestyle. It's like your ethnicity/community/family. You can't change it. Although here in Canada, the terms "band" or "\textbf{nation}" are used instead. Then you also have different clans in each \textbf{nation} or "tribe" as well. So for example, you can be Mohawk or Oneida (\textbf{nation}/tribe) and turtle clan, bear clan, wolf clan, etc.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small kalikalla43 yeah no. My family has lived in Arizona before the US claimed it. It was once apart of Mexico. Go read a book you ignorant fuck. You're probably a \textbf{whitey} who claims to be native. I'm Mexican and my ancestors were Navajo. Fuck out\normalsize   & \cellcolor{green!27}Whitey & \cellcolor{green!27}Ethnicity - White & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small car Av.....Pay them no mind. kalikalla43 is CLEARLY a white person that's pretending to be Native because they love to do that but they dont want to be thought of as Mexican cause they're \textbf{racist}. Mexicans ARE ALL part Native. I'm Native and any TRUE NATIVE knows this. We are both Brothers and Sisters. Are you stupid? You realize there was no "AMERICANS", "MEXICANS" "CANADIANS" right? If Mexicans are Native then that would be like saying Natives in Canada are Natives. That's fucking stupid. Go read a fucking book. Mexicans are just Natives that have more Spanish, Incan or Mayan blood. Do you really fucking think Native tribes didn't extend thru what is now known as "Mexico".? You have to be stupid to think \textbf{nobody} ever crossed over the imaginary borders that didn't even exist back then.\normalsize   & \cellcolor{green!5}Nobody, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/137 & \cellcolor{green!5}1.46 \\  \hline
  \cellcolor{green!27}\small I see them do this often. \textbf{racist} Whites will go onto comment sections and pretend to be one \textbf{race} and say all kind of \textbf{racist} stuff to another \textbf{race} to cause hate between us. Or they will say all kinds of nasty stuff about White people pretending to be \textbf{Black} or Mexican or Arab to give the illusion that White people are victims too. Kinda how the rich White people would treat the poor Irish immigrants a bit better than the poor Italian immigrants and treat them a bit better than they did the poor Jew immigrants and treat them a bit better than the poor Asian immigrants and so on and  so on. Together they could EASILY over take the rich and bring about change but the poor are to busy hating other poor so \textbf{nobody} goes after the rich because divided we fall...Actually they still do it. That's why you'll find poor people hating on other poor people for getting welfare even though we spend WAAAAAAAAY more on taxes to give billion dollar corporations tax breaks. It's \textbf{crazy} how stupid the general population is and how easy they are to manipulate.\normalsize   & \cellcolor{green!27}Black, Crazy, Nobody, Race, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/193 & \cellcolor{green!27}3.627 \\  \hline
  \cellcolor{green!5}\small Gatorson The 54th True it is so annoying when people pretend to be Native but can't even name their tribe or its a \textbf{common} tribe that everyone knows the name of. Some can't even show their roll number.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small You mean the white people that mexicans try SO hard to be like? mexicans are so ashamed of their mexican \textbf{indian} roots that they try to breed with white looking people so their kids will look less mexican \textbf{indian}. LMAO.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/40 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small kalikalla43 I don't know what types of so call Mexicans you been hanging around with cause know one is trying to be or act white.Also l hope you're not referring to latino/Hispanic as just Mexicans and really breed? More like you can date and marry anyone regardless of where they're from and \textbf{race}.I swear are all Americans full of themselves like you?I'm losing brain cells just by talking to you.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small kalikalla43 Actually it depends on where you come from. Some Spaniards have light skin and blonde hair. I think the term you are looking for is native. They would not be \textbf{Indian}. I don't think any Mexican Americans including myself are ashamed of their heritage at all. In fact we proud of it.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small fuck all these mestizos who claim to be native american, you idiots are white european in the eyes of real natives. everything good you have comes from the beautiful European superiority. if you didnt had the superior european blood you would still be living in the mud doing human sacrifice for your satanic fake gods and die of \textbf{old} \textbf{age} at 30.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small 니로다 가미니 파띠바다 아리야사까 드까 That's pretty terrible to say. There is no such thing as superior when it comes to people. I happen to be Native Paiute, Mexican, A bit of German on my Grandmothers side, and much more. Lots of people are mixed \textbf{race}. Also the Aztec lived in adobe houses. Which is made of clay. It comes from the earth but it is not mud. Also Spaniards are not the same. They are the ones with light skin and blonde hair. I don't like people pretending to be Native myself but the only way to prove it is to name your tribe and roll number.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}\small Dark Shadow Storm you are not a native you are a mutt. are you claiming that full pure blooded latino \textbf{african} are not real \textbf{african} if they dont know their tribe? that is your standard and thats pretty insensitive considering all of them lost their \textbf{ethnic} history in the slave trade, ever thought about that? and of course european blood is superior in many ways, for example if i am 1 90 and you are 1 60 then i am superior in height, and it just happen to be that european whites are the tallest people in the world. now among thay superiority they have the brillance to build great superior civilization like the one you are living in with freedom of speech and comerce which is not something \textbf{common} amongs the mud peoples.\normalsize   & \cellcolor{green!5}African, Common, Ethnic & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}4/134 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small 니로다 가미니 파띠바다 아리야사까 드까 Stop saying the word mutt \textbf{race}. Like we are some type of dog breed.Just use the word mestizo it's the proper term.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I'm native American and look \textbf{nothing} like them..the original native Americans were dark with very shaped noses until Europeans  came and raped native women that's why they are lighter..I'm more a \textbf{r\textbf{ed}} skin basically what she denied..\normalsize   & \cellcolor{green!5}Nothing, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small red and white descendant 👏🏽👏🏽👏🏽🙌🏽🙌🏽🙌🏽\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Latin is not a \textbf{race}, and SOME Latin people are of native decent.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Rakan N as soon as I finished reading your comment it made me start thinking about 21 savege like you don't see me going around naming my self 21 \textbf{nigga} making shit music\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small I thought "\textbf{R\textbf{ed}} Skin" came from French and referred to Algonquin people wearing Ochre pigment- like the paintings by George Catlin\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small I'm half \textbf{black} half Native American 😊\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I am from the Shoshone tribe, but I also have Cherokee on my mother's side.  My father was \textbf{black} though.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small RooFooChoo this comment is sort of \textbf{old} but I'm Yaqui too!!! ✊🏻❤️\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Native Pride I'm Native American, Ojibwe 🖐 and Mexican and \textbf{African} American\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Native to America or native to mexico? Lot of scumbag people making up fairy tales in order to falsely claim American \textbf{Indian} lands.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small 100 cree. i cant believe these fucking kids are lying to all the white people... we do still have Tipi's but obviously \textbf{nobody} lives in them, that fact has been accomplished over 30 years ago... we do receive free money its called land claims... and we do get free education as a first nations person as well... the list goes on. these kids are aboriginal but have no idea about their own culture... when will our fukin rezes start building schools fuck\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{black},Korean, and Odwa\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Then its not \textbf{Indian} country. You cant have it both ways.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small First \textbf{Nation} wasupp\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small yeah.... both of my parents are half \textbf{black} and native..... but i'm like like literally tanish/\textbf{r\textbf{ed}}.... i turn \textbf{r\textbf{ed}} outta nowhere... the \textbf{redskin} would contribute to me... my dad is Iroquois and my mom is Cherokee ( my grandma is full)... but i hate when they think all natives had teepees.... like no... iroquois didnt even have teepees.... they had long houses....( not sure about other tribes but iknow Iroquois wasnt one of them.) i wanna meet other natives but i wouldn't know where to go.  especially in the state of maryland.. I only know one native and thats my best friend. but shes half like me... and i see her everyday, i want to meet others... we never been to the celebrations or get togethers or etc ( them celebrations they have every spring/summer in maryland) but i want to go to one. but the nearest one is near ocean city maryland and thats HOURS away from us... so i just stick with youtube....\normalsize   & \cellcolor{green!5}Black, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}4/165 & \cellcolor{green!5}2.424 \\  \hline
  \cellcolor{green!27}\small Chris W \textbf{nigga} you ain't natives you \textbf{black} asf\normalsize   & \cellcolor{green!27}Black, Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small Black Elk decendant, cousin to ckazy horse, great Lakota \textbf{nation}!\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Honestly these questions are self explanatory I am Native and I hate being call \textbf{r\textbf{ed}} skin also Latino\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Yep, reading all the comments and now i defiantly know that you all aren't native, you cant be half native and half another \textbf{race}, and just because you have some native ancestors doesn't make you native either. Look into this shit people! YOU AREN'T NATIVES, YOU'RE ALL JUST \textbf{DUMB}!\normalsize   & \cellcolor{green!5}Dumb, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/49 & \cellcolor{green!5}4.082 \\  \hline
  \cellcolor{green!27}\small Yes Creek \textbf{Indian}. Wind Clan\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Native Pride half cherokee native and \textbf{black} 👍\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Where are all the \textbf{black} Natives?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small No, they are not. Just like white, \textbf{black} etc. people aren't beautiful. Individuals can be perceived as ''beautiful'' but saying a whole group of people is is plain retarded.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small I live in Oklahoma and most of my friends are native. They don't give a shit about all of the \textbf{race} shit. They all get checks. If you aren't getting enough money it's because the tribes are governments, through the bureaucracy keeps the dollars at the top... duh. It's \textbf{racist} to keep minority pets.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}6/54 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Nana \textbf{Banana} lol\normalsize   & \cellcolor{green!5}Banana & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam) & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Grace yes that's an opinion, but the reason I went in against that is because that's called a generalisation. It's \textbf{dumb} and nonsensical to say all millions of Native Americans are beautiful, just like you don't say all \textbf{african} americans are athletic, or all white americans are. run-off the mill\normalsize   & \cellcolor{green!27}African, Dumb & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small **Love** "natives to America" is what you're actually saying first \textbf{Nation} is the right term\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small In the Cherokee Indians"  there was Ten/10 different Tribes... And other \textbf{Indian} Tri es also.  It was found at least 1000 Native \textbf{Indian} Tribes in this Countryland before it was stole by evil and wicked people. Some Indians are told different truths by their Tribes.  Now all Caucasian People Weren't like that.  Many Caucasian People were decent People.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small I was an \textbf{Indian} for Halloween when I was a kid. Thank you for sharing your beautiful culture.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I was a \textbf{squaw} in my school's Thanksgiving play. My mom made a beautiful  costume with beaded fringe. It was so beautiful :)\normalsize   & \cellcolor{green!27}Squaw & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small So my elders was right about the definition of the word "Redskins." And as a French-Creole \textbf{African} American \textbf{woman} with Native American lineages from the Deep South, I feel native Americans should get free health care, government hand-outs, or rich off of something. Considering the horrible stuff they had to or is still going through. In the \textbf{Black} community we always say we're owe everything considering what our ancestors been through, but I think Native Americans deserves stuff too.\normalsize   & \cellcolor{green!5}African, Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}3/79 & \cellcolor{green!5}3.797 \\  \hline
  \cellcolor{green!27}\small Chassity Oubre A. Tribes as a whole have already been given land and repayments back andB. Thats an awful idea. Making people dependent on something is setting them up for failure. One example is welfare for primarily \textbf{black} citizens. So many people screw with the system. C. America is trying to \textbf{transition} into equality. How is giving people handouts, effected or not, bringing equality to our country? D. Special programs and loan payment services dedicated to native minorities already exist.\normalsize   & \cellcolor{green!27}Black, Transition & \cellcolor{green!27}Ethnicity - Black, Sexual Identity - Transexuality & \cellcolor{green!27}2/81 & \cellcolor{green!27}2.469 \\  \hline
  \cellcolor{green!5}\small ABCDE FGHIJK I'm assuming you're not a person of color. And no it isn't setting anyone up for failure, it's just something people for deserves for having to endure/still much. And there is \textbf{nothing} equality moving about America, especially not right now.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small ABCDE FGHIJK That's the most \textbf{racist}, stereotypical excuse I've ever heard. I won't argue with a narrow-minded person like you. Because you definitely speak for people as whole and everyone with a hand-out isn't failure.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Chassity Oubre What do you mean? I never said anything \textbf{racist} or stereotypical. Welfare has become an epidemic issue in the U.S, not because its a bad idea, but because its an easy system to cheat and has been used to do so, especially in places like Detroit and Milwaukee. Imagine that the government gives you X-amount of money each month for simply applying to a job or having Y-amount of children, but not working a job or taking care of said children. The same applies to charities in foreign countries. The economy collapses because they aren't making money or learning the trade, they are simply piggy backing. Point being that waving a magical wand and giving people free stuff because they have certain DNA (which is how a monarchy works, which was the downfall of some major European nations) doesn't solve anything and only angers other groups, because it isn't fair. It isn't a bad thing to be on welfare, especially when you are trying to get out of it. Its another thing to sit their and expect things out of it without an applicable skills to a certain trade. Now, only 22 of Natives actually live in poverty where all assistance is needed. What about all the Natives that are financially stable and educated? They should get free benefits for being born that way? This is exactly the issue I was warning you about; A simple system like that is so easy to cheat. And its not a simple "I cheated, my bad" type of thing. Its something that effects other people, so why can't these Natives use simple goverment assistance like everyone else? Aren't we all trying to be equal? America has had many equality breakthroughs in the last two century's, has it not? No ones enslaved, no ones being killed, everyone can get an equal opportunity to education. So, why would you suddenly screw things up like that? And that doesn't include other things, such as tribal scholarships, which a white guy such as myself couldn't recieve anyway. Lets not forget that alot of land and money has been returned to Tribes, although some have refused to take it.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/363 & \cellcolor{green!5}0.275 \\  \hline
  \cellcolor{green!27}\small So... they should be given free health care, and lands and goverment hands off just encause they are native american?  I think no one should be given anything based on there \textbf{ethnicity}, because thats just stupid and kind of xenophobic.  Also, of you think only \textbf{black} people have gone through shit, or native americans, or jews. You should know some more history, Irish have been highly discriminated, and some scottish people like the mcgregors were hounted like animals by the english, and yet you think that what happened to natives and africans is worth considering when you take care of people. Tell me, if you could help a hounded native kid or a white kid. Would you just take care of the native one?\normalsize   & \cellcolor{green!27}Black, Ethnicity & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/124 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small I sincerely hope for the future of our country, that we STOP living by labels, creating victimhood, and categorizing people based on a social construct (\textbf{RACE}).  ALL americans deserve free healthcare, not just a group of them.  All Americans deserve the ability to get help when they sincerely need it, not just a select group.  At the end of the day, we're all human.  There are bad white people, there are bad \textbf{black} people, there are bad native americans, there are bad whatever, whatever, whatever.  Human, ONE BLOOD, just human.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small fernando aldazabal Well I don't think it should be decided on \textbf{race} either but as history also tells, direct help was supposed to be provided by the government because a lot of tribes were basically forced to give up land. They promised so many things to a lot of tribes and protection to which even to this day is still not utilized. So many treaties are overlooked nowadays.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small I'm Greek and we have been through nearly four HUNDRED years of ottoman rule. Should turkey now give is money just like that? THESE COMMENTS ARE DUMB\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Chassity Oubre the word doesn't owe anybody anything every \textbf{ethnicity} has been victimized in some way\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small +Alex Renteria Actually, as someone of British \textbf{ethnicity}, should I be compensated by people of Scandinavian heritage for the raids their people inflicted upon mine (Anglo Saxons)? Why don't you educate yourself on Europe a bit mate\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Alex Renteria Do you understand how many people in the world classify as White? You could think about your statement for literally 5 seconds with a fifth grader education to know what you just said is 100 false... not only that but it only agitates the situation and makes you seem \textbf{dumb} and reverse \textbf{racist} to those that know better. What you just said only inflames racial tensions. None of us know everything 100, but this is the type of statement where you need to be told to educate yourself a bit better before you go blabbering. We don't need any more of that level of intelligence in the conversation.\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/110 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Nobody ever used the term "Redskins" to describe blood pouring down faces. This video is a deception.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Everyone's head bleeds \textbf{r\textbf{ed}} when its scalped, i call bullshit on it.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/12 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Chassity Oubre so are you telling me the \textbf{black} communities are doing fantastic???? LOL you can't be serious\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Paying for things that were once agreed to be paid for isn't a "handout"  People love to overlook the fact that MANY treaties were made and by the American government and then broken. There are hundreds of signed documents between certain tribes and the American government that were later broken by the American government. I guess that's ok tho because YOU get to benefit from those things but when it affects your family THEN it's an issue. Do you know how many fucking men, women, children and \textbf{elderly} Natives died on the Trail of Tears? All because the government "gave" them a piece of land and then they Natives found gold on that land so the government then broke that treaty and made them walk across States and States to a more barren wasteland that had no natural resources.\normalsize   & \cellcolor{green!27}Elderly & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/139 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}\small This has \textbf{nothing} to fucking do with the original White settlers, this has to do with the American government TO THIS FUCKING DAY taking and taking what little we have left. And with Trump as President it'll get even worse, he hates Natives more than he hates Mexicans because they compete with him in the casino business. He once called us "All drug dealers" that we were akin to the Italian Mafia. Probably why some of his first orders as President was to fuck over Native people trying to prevent an oil pipeline from going directly through their only water source where they get all their drinking, showering, fishing etc from  on the small chunk of land they were forced onto. Because oil means more to Trump then Native children having clean water to drink. Also he VOWED to changed a Mountains name that was OWNED AND THEN TAKEN FROM THROUGH BROKEN TREATIES BY THE AMERICAN GOVERNMENT back to "Mount McKinley" because Obama in a sign of respect and wanting to work with the Tribe couldn't give them back ownership of the Mountain that is very sacred to that tribe so as a peace offering he changed the name BACK to the Mountains ORIGINAL name that it had for THOUSANDS of years before it was stolen and renamed Mount McKinley by the American Government. YUP THAT'S the most important thing to Trump a fucking Mountain that doesn't mean shit to anyone but that tribe but he's so spiteful and hates Natives so much (again because of casino competition) that's some REAL important shit Trump, you better get right on that. Got N Korea practicing how to blow us up, got ISIS signing up to be Uber drivers everywhere, got Putin and Trump measuring each others dick, Americans are \textbf{racist} as ever but sure let's make sure we change a stolen mountain BACK to the name the thieves gave the Mountain that's a TOP PRIORITY.  So sad to see all that my people had be destroyed and probably soon to be discarded after you raped it of it's resources just like you all discarded your original Countries. My tribe had 100 equality of the sexes, we respected the earth and it's animals (Go ask all the wild Bison.....oh that's right.... you can't because you fuckers killed 99.9 of them too) we didn't look down on \textbf{g\textbf{ay}} or trans people in fact they were respected and called them "two spirits", women had an equal vote in the tribe and could hold council right alongside a man, own property (meanwhile white women didn't even have rights to their own children and a dead father could will his children away to strangers and the mother could do \textbf{nothing}) but suuuuuuure keep telling yourself that we were "behind the time savages" YOU DON"T EVEN HAVE THE MORALS NOW THAT WE HAD THOUSANDS OF YEARS AGO!!!! So what you brought technology and growth in different ways? You realize that could have been done along side the Natives right? White people like to pretend that we'd still be in the dark ages if they didn't come over and commit genocide, I don't think you have to rape 4 year olds and start a child \textbf{sex} ring like the whites immediately did (like immediately idk why child rape is their favorite and first priority) to invent fucking light  bulbs. Fact is everything you have was built off the death of the Natives and the sweat and back of the Blacks. I love how you push off the blame of genocide, slavery and \textbf{racism} but then take credit for all the things Americans have accomplished since coming here. Can't have both bitch. "Dead skin, dead hair and the eyes of a dead pig. We brought them food and shelter they brought us an evil we have never known. I don't believe they are humans as we are humans, they can't be. They say WE aren't like them, that we aren't civilized, that they are humans too but if they are humans then I don't want to be a human. I thought they were my biggest fear, I thought the death, evil and sickness they bring was my biggest fear but more than that more than the devil himself, I fear we will become them.....demons in human form" ---My great great Uncle \textbf{Nelly}But I'm sure you don't give a fuck because fuck the people who took care of this land for thousands of years. So that it was nice and full of resources. What's your address btw? Apparently I'm American which means I can just take your home and stuff if I feel like it. Oh wait but then you'll suddenly care.... Maybe give me an address to one of your non white, non Christians neighbors? I wouldn't wanna upset YOU as you clearly don't give a shit about other peoples suffering, only your own.\normalsize   & \cellcolor{green!5}Gay, Nelly, Nothing, Racism, Racist, Sex & \cellcolor{green!5}Age - Youngsters, Ethnicity - General, Gender - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}8/816 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small Chassity Oubre ... Then join \textbf{black} lives matter and create \textbf{r\textbf{ed}} lives matter. Just fucking destroy the planet by creating more \textbf{racism}. Keep tearing us apart by playing your ancestors \textbf{race} card. What happened to several races hundreds of years ago is terrible but 100s of years is a long time.  But current \textbf{racism} is still going on all over the world to other races that needs the world's attention and help. They need help now and here u r begging for attention and handouts. It's only handouts if ppl receiving the stuff are abusing that gift and begging for more. A small percentage do this and it gives everyone in the same "group" a bad name.... people like u. Visit Nobullshit on YouTube.. . \textbf{Black} lives matter videos....\normalsize   & \cellcolor{green!27}Black, Race, Racism, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}7/129 & \cellcolor{green!27}5.426 \\  \hline
  \cellcolor{green!5}\small Chassity OubreOf course they do. We only ask for reparations not land or anything else. And if you're the person in your profile picture you're not \textbf{black}. You have \textbf{black} 'lineages' just like you have native american ''lineages''. Don't see what's \textbf{black} about you\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/45 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small ABCDE FGHIJK"So many people screw with the system." So are you bothered that they screw with the system or sad that they're dependent on it? Which is it? You guys are so full of shit when you pretend to care about \textbf{black} people. And welfare isn't only or mostly for \textbf{black} people you stereotyping idiot. Welfare has a majority of white people on it. All native americans didn't get repayments either. You white people just talk straight out of your ass when talking about \textbf{race} Giving reparations for mistreated and marginalized people isn't inequality. How about while you take your time transitioning while still being \textbf{racist}, you give us that reparations and let us help ourselves instead waiting for you to decide when you feel like not being \textbf{racist} shits.\normalsize   & \cellcolor{green!27}Black, Race, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}5/131 & \cellcolor{green!27}3.817 \\  \hline
  \cellcolor{green!5}\small Firth aldazabal FarquharTypical irish bullshit. If the irish care about how they were treated they can pursue their own resolutions to their grievances. Problem is they were accepted and many became racists and mistreated other people as well. There's no impeding negative associations with them today as there are with \textbf{black} americans\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Leah MotleyWhat relevance do those raids have on you today you absolute \textbf{dumb} bitch? I'm pretty that was resolved in the past. Most people fucking each other over doesn't mean you shouldn't make up for it when you fuck over someone in the present and mistreat them. You use other people's wrong doing as an excuse not to do the right thing. And that's what makes you shit people\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small Gianna FontanezThe irish were persecuted by other white people. A real comparison would be white people suffering simply because they're white and \textbf{nothing} else. When has that happen idiot?And If they're really bothered by that history they can complain to other white people about it. But we all know they don't give a fuck because it wasn't anything like what \textbf{black} people dealt with and still deal with which makes it all very relevant. It's been an unbroken chain of \textbf{racism} for blacks from whites. Cunts like you only bring up other groups to justify the mistreatment of blacks and not making it right. It essentially makes you a racist\normalsize   & \cellcolor{green!5}Black, Nothing, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/112 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small KladstoneList me a right that is denied or enforced on rich people or middle class everyday people you \textbf{dumb} white moron. You can't because they don't exist either but disparities in how the law is applied to rich people, celebrities, politicians and women is still different isn't it? Only takes a moron or a desperate \textbf{racist} to just you need laws for injustice or mistreatment of any group. Most of you are \textbf{racist}, that's enough to marginalize \textbf{black} people. There's no law stopping \textbf{racism} and the ones that are supposed to work aren't enforced and also typically end up being a he said she said. Unless you're recorded being a \textbf{racist} cunt\normalsize   & \cellcolor{green!27}Black, Dumb, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/113 & \cellcolor{green!27}5.31 \\  \hline
  \cellcolor{green!5}\small Julianna ChristoBut the \textbf{racism} we have now doesn't bother you. Only the people who try to address that \textbf{racism}. Typical white \textbf{racist} bitch. You're a disingenuous pretending like you actually give a fuck about \textbf{racism}. If you did you'd want to do something about it instead of bitching at people who want to and giving excuses to racists for why they're \textbf{racist}. Stupid bitch\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}5/65 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Everyone has ancestors who have been through something terrible...so should everyone get handouts? How about people who have directly suffered in some way or are disadvantaged should receive help eg. \textbf{Disabled}, mentally ill, \textbf{old}, sick,  \textbf{sexual} abuse/assault/DV victims. You are a greedy awful \textbf{woman} for wanting to exploit the misfortunes of your ancestors.\normalsize   & \cellcolor{green!27}Disabled, Old, Sexual, Woman & \cellcolor{green!27}Age - Over 65s, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/53 & \cellcolor{green!27}7.547 \\  \hline
  \cellcolor{green!5}\small +Chassity Oubre "Wahh you're \textbf{racist} im not talking to you anymore!!"Lmao, you're just mad you got BTFO'd. No Native American alive today had to go through being kicked off their land, or go through the war their ancestors went through. Why should they get free shit just because their ancestors sucked at warfare? Do you see the Irish complaining? No.And what does ABCDE FGHIJK being \textbf{coloured} or not have to do with this argument? Oh, let me guess, his opinion is worth less because he's white, right? You're the \textbf{racist} here.\normalsize   & \cellcolor{green!5}Racist, coloured & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/93 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small +Carlos ETC96 "culture vultures" Dude, stfu. You people say you want to live in a multicultural society, then you hate when people try to appreciate your culture. Make up your fucking minds. And you complain about "cultural appropriation" from whites? Okay, if we can't use anything from your culture, don't use anything from European cultures. No electricity, plumbing, TVs, phones, automobiles, modern house design, hell anything invented by a European. Get rid of all of that stuff, you culture vulture.+Scoring57 No \textbf{black} alive in America today has ever been a slave. Anybody can be anything they want as long as they work hard for it. Problem is the Democrats made you people dependent on welfare and handouts, yet you dumbasses still keep voting for them. Take some advice from Thomas Sowell or Ben Carson. Oh but they're "'uncle toms" right? Lol, it's funny that you'd rather stay poor and dependent than become Republicans because "evil \textbf{whitey}". Yeah, and that \textbf{racism} you speak of, goes both ways, moron.\normalsize   & \cellcolor{green!27}Black, Racism, Whitey & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Ethnicity - White & \cellcolor{green!27}3/168 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small +namethatrevealsnothingaboutme They are coming out about their anti white hate now, because they think since we're going to be a minority soon they can attack us with ease. It won't end well for them when they spark a \textbf{race} war. The military is overwhelmingly white, whites own most of the guns, farmland, etc.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small im native and im suprised they dont allow most mexicans native americans they are there from north america btw no lie my skin gets \textbf{r\textbf{ed}} af latinos are natives mixed with spanish or \textbf{black} its true\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/36 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Most "natives "are less native than Mexicans. I know Mexicans whose first language was mayan.  Mayans Aztecs these are native people  too. Latinos  look just like these girls a lot of times and to say they don't count just because they are from South America instead of North America is just ridiculous. They're are people who look 100 percent white and live on reservations . It's just \textbf{crazy} to me\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small Desi Pfander a white mexican \textbf{chick} who i swear i thought was euro took a dna test and was only 3 european! Her \textbf{black} boyfriend who was 95 \textbf{african} was more white than her, she was pure native.. I just cant get over that, i mean she looked mixed but she was pale asf so natives are not all dark\normalsize   & \cellcolor{green!27}African, Black, Chick & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}3/60 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small \@j escoto  bro your like full spanish or european something  u have blue eyes brown hair white skin look just cause your mexican doesnt mean your latino its \textbf{nationality}  feel me\normalsize   & \cellcolor{green!5}Nationality & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Also one  ore thing to everyone mexican is \textbf{nationality} not \textbf{race} u could be mexican european mexican \textbf{african} mexican american the list goes on\normalsize   & \cellcolor{green!27}African, Nationality, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!27}3/24 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Most natives \textbf{Racist} towards Mexicans. They don't see them as Native. It's the same way Mexicans see Salvadorians like shit.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Hipster \textbf{Black} Metal which is hilarious because most Salvadorans are Pipil descendants which is a tribe that has roots in Central Mexico then they migrated south into El Salvador\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@j escoto: While not every Mexican is Mestizo(racial mixture of White Spaniard or European in general and Indigenous) and very predominantly Amerindian/Indigenous, you can't deny that you "pure white" Mexicans still make up a small population of Mexico's demographics(even slightly smaller than the indigenous population), hence why the majority of people have these misconceptions that all Mexicans are either Mestizo or Amerindian or that all Mexicans or Latinos are predominantly an original homogeneous \textbf{race} like East Asians and Europeans. Also, the definition "white" in Mexico(like the vast majority of Latin America) has different meaning from the United States' version of their "white \textbf{race}" definition, with the US socially using the "One-Drop Rule" to determine someone's racial background or purity, while in Mexico or most of Latin America, Castizos(and Arabs too, I think) are sometimes lumped into the same group as "White" Mexicans/Latinos.I disagree with the way the US or Western Media portrays all Latinos as "brown" but telenovelas also do absolutely no justice for Latinos in their portrayals of them either(with nearly all the main characters always being white/criollo Latinos).\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/181 & \cellcolor{green!5}1.105 \\  \hline
  \cellcolor{green!27}\small TheLatinoAssassin480 I agree. But I don't see a problem with Latin American countries lumping in Arabs or predominately European Latinos in their "white" category. If you look white, even if you're not 100 pure I'm pretty sure I myself am not, you should be put on the white category. Not even Spaniards or Italians, or Portuguese people are pure "white" they have Arab and North \textbf{African} blood in them because of the Moor Conquest. That "one drop rule" is lonnnggg gone now. People who aren't 100 pure white but look white can put down "white" in the US census\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small j escoto Yeah, speaking of putting down "white" on the US census, you're not gonna believe how many "white-passing" people I've encountered in the US who you would never thought or believe that are half or a quarter Black/African-American or Native American. This is basically why I laugh at Neo Nazi/White Supremacists and their outrageous concept of \textbf{race}("white purity", which is much likely less \textbf{common} here all over the Americas).\normalsize   & \cellcolor{green!5}Common, Race & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/70 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Desi Pfander  I'm \textbf{nigga} so replace that with king please\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small You do know that California was STOLEN by spain/mexico from American \textbf{Indian} tribes that were the original inhabitants.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{racist} af and I am part Native American.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Another \textbf{common} misconception is that we all look like these girls in the video.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Steve Morales Aye, dude. Let me fill you in on this. I'm 50 native american, 27 Italian. Let's stop there because literally there is no percentage higher than that. Your facts are incorrect, because I'm pale as fuck, but am 50 NATIVE AMERICAN. So... Fact check buddy \textbf{old} pal\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small exactly! bc I look \textbf{nothing} like the girls in this video and I'm native!!😬\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Steve Morales the girls are mixed with white lmfao..they probably don't know it but their ancestors were definitely raped by Europeans ..the original native American are \textbf{redskin} "dark" with pointy big noises they didn't become light-skinned until they started to get raped. so your wrong.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small This video is SOO not true. Only some tribes have a \textbf{r\textbf{ed}} tint to their skin like my tribe. The Cherokee tribe. My skin is white tho because I'm only like 1/8. And anyway these girls can't be more than 1/2 Native because I have friends that are full native and they are WAY darker and one is a little \textbf{r\textbf{ed}}-skinned Also most tribes give Native Americans \$500 a year on their birthday. And also Native Americans don't have to pay taxes if they live on Native American reserves, which is 20 of them.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/94 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small AidanT Fletcher haha your \textbf{dumb} asf im native and i never once got \$500 on my birthday\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small AidanT Fletcher are you \textbf{dumb} or are you just stupid\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I actually used to call myself \textbf{redskin} cause I thought it was okay, then at school people called me "\textbf{R\textbf{ed}} Boy," but that eventually stopped when I got into grade 7, I'm now in grade 9 and I hear "\textbf{Indian}" so much and I find that offensive, because I know that's not what I am, but still to this day I go by the name "\textbf{R\textbf{eD}}" as a nickname and no one has yet to say that is an offensive nickname to call myself.\normalsize   & \cellcolor{green!27}Indian, Red, Redskin & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}6/84 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I have a feeling you have no education. The 13 colonies had that constitution. Let's not forget the rest was part of Spain and Mexico and even some parts were Fench. The USA that we know today is not white. \textbf{Black} people are as American as anyone else. Obviously your not even American enough to know that. Irish, and Italians at one point were nonwhite. Stop spreading hate! I think you have issues. If you're this angry many of us are willing to listen to your problems. Women at that time didn't have voting rights either and they were white. Stop being a fool, please!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/105 & \cellcolor{green!5}0.952 \\  \hline
  \cellcolor{green!27}\small So your Italian? Maybe you should go get a DNA test since they have tons of Afro and Middle Eastern DNA. Italians didn't discover America. The Kingdom of Spain did. Have you been to Rome? Probably not, you are not educated enough. They have these little things called the Spanish Steps. Keep sticking to your story. Ignorance is bliss! Later \textbf{black} man!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small A study was recently done by Sir Hillary Beckles on blacks in Anglophone Caribbean countries, for example he found that in Jamaica 60 of the people over 50 either had diabetes, CVD or hypertension. Interestingly these aren't diseases which are indicative of  native born Africans. These diseases are due to the high level of stress and limited food sources slaves had to endure for hundreds of years so much so it changed their genetic make up.Furthermore the medication used to treat these disease only have a 70 efficacy rate on blacks who are descendants of slaves; whereas whites and native born Africans the meds are 90 effective.I think it's a safe bet that these diseases which are prevalent among Native and \textbf{black} Americans, are most likely attributed to the same historical set of events.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/136 & \cellcolor{green!5}0.735 \\  \hline
  \cellcolor{green!27}\small Desaline Redux There is also a prevalence of prostate cancer in Caribbean men. What is interesting is the comparison between Caribbean people and Caribbean people who live abroad and funnily enough the results for people from the \textbf{Indian} sub -continent  and those those living abroad is practically the same. You might get some answers here.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small +Desaline Redux That is a load of rubbish you stupid \textbf{black} \textbf{race} hustler. Diabetes and hypertension are not genetic. Lots of whites have the same issues. Is that due to slavery or some other crap whites faced in the past? And finally, how the fekk is any of that related to Halloween costumes?\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small The two sisters in the orange and \textbf{r\textbf{ed}} sweaters are hilarious😂😂\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small TAMAR LEMMA pls bitch, they are beautiful cos all humans are. You say it like some other people are ugly! \textbf{Racist}!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Lmao these ones are either \textbf{fat} landwhales, look like Genghis Khan's offspring, or have receding hairlines. Neither are beautiful.\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small define beautiful people always say your beautiful or in some other expresion such as eatable ass seem you only aim for men who has a ass and don't call anyone a bitch your the only one here (grammar \textbf{Nazi} same as you and don't fix my grammar)\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small Gamerglazer423 they are not beautiful. They are ugly as hell. I would flee if I saw one. \textbf{Fat} heads nd all. Nope! Bye!\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Gamerglazer423 first and foremost, am a man. Second am a \textbf{black} man (\textbf{African} decent). Thirdly, I dont think \textbf{black} is beautiful. I think there are some blacks who are beautiful and others who are really really ugly. Also with every other \textbf{race}. In my eyes, most \textbf{indian} americans and australian aboriginals are fiercly ugly. I am yet to see one single fine one (both male or female). Not all whites or hispanics are beauitiful either. Some are, but most are not.No \textbf{race} is "beautiful". There are simply beautiful amongst each \textbf{race} and ugly amongst them.I am an ugly looking man by my standards. But I know a good looking man when I see one. I don't decieve maself and would rather no one decieve me. I dont need anyones beauty approval. It is who I am, I didnt create maself that way. So I let those who are enjoy it nd move on to other more important things (attitude). But to just see some ugly bitches and be like "they are beautiful" is the most leftist/brainwashed/patronizing statement ive heard all 2017.\normalsize   & \cellcolor{green!5}African, Black, Indian, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}7/183 & \cellcolor{green!5}3.825 \\  \hline
  \cellcolor{green!27}\small I'm mixed native American and \textbf{black} so it gives me a reddish skin tone but I take it offensive when someone mentions redskins\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Joshua Bolton Why? Native americans long ago used the term redskins to describe their own people. Its not \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small increto axb It is \textbf{racist}. She explained why in the video.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small So you are a \textbf{black} \textbf{redskin}?\normalsize   & \cellcolor{green!5}Black, Redskin & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/6 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Both my parents are Native and I don't give a shit if someone were to call me a \textbf{redskin}. Words have as much power as you give them.\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Joshua Bolton be proud savage pride ! This is my country my world! I embrace anything that resemble my people. Dont got shit they took all away. So now im \textbf{crazy}!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Carlos ETC96, I'm 65 sub-Saharan \textbf{African} and 35 Native American, so that doesn't count?\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Penelope Wood you're not 35 percent of \textbf{black}  you too dark\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Isaiah loc13 she didn't say that she was 35 \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Joshua Bolton I am \textbf{black} and I native American too!!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small I'm Australian, I've always wanted to learn about Native American history. It's sad that in America there's still stereotypical labels and connotations linked to this \textbf{race} but, then I look at Australia with Aboriginals and it's like seeing reflections. I'm just glad Australia has gotten to a better point. We still have a long way to go though.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}\small they don't exist, they live in a \textbf{mental} illusion.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small never seen a \textbf{fat} Indian\normalsize   & \cellcolor{green!27}Fat, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical Features & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Tyler Cook thank you. being native American is such a benefit it's retarded. I get the benefits because I am 1/32 but it's so \textbf{dumb} how much free shit I get\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small With all that's happened it's really not \textbf{dumb}, especially if you look at the history and the effects it's still causing today\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Tyler Cook Honestly what does it matter? Everybody gets something for free like white americans don't have to deal with predjudices. In Germany you get money, so that you won't be homeless(money for people not having a job). In so many cases they do not want to work and it is their fault. But for them to live happier it is better.In Germany everybody be like all those immigrants get so much money, but that is not true.My mother and father emmigrate from syria 20 years ago and we don't get shit it is even harder to live because you have to deal with those \textbf{racist} people thinking you get everything in life although we can't even find a flat because people knowing that we are not german don't sell their flat. If native americans get money, it is a small amount which doesn't even count!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/148 & \cellcolor{green!5}0.676 \\  \hline
  \cellcolor{green!27}\small Native Americans entitled privileged attitude is getting extremely \textbf{old}. I don't owe you anything just like you don't owe me anything. If you want something go earn it I don't pay taxes for handouts. And you say white Americans don't experience prejudice? We seem to be the only \textbf{race} that can openly be discriminated against without punishment. So I obviously disagree with your assertion.\normalsize   & \cellcolor{green!27}Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - General & \cellcolor{green!27}2/64 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@Helin Bisho It sounds like you live in a white neighborhood, I'm white and most of the people where I live are brown, \textbf{black}, and native american. When the tables are turned it's very different, I hear \textbf{racist} remarks about white people all the time.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small Pepe Is Love, Pepe Is Life But I do stood up for myself and others of my \textbf{ethnicity} a lot however it won't really work.Have you ever stood up for your self maybe it will help.\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small MY SCHOOL MASCOT IS FREAKING \textbf{REDSKIN}! I'M NOT KIDDING!!!!!!\normalsize   & \cellcolor{green!5}Redskin & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small WOW!! I got schooled yall!! What the fuck do you mean yall don't live in teepee's? Are you saying you live in houses? Whoaaaa dude...total mind \textbf{freak}! I'm taking this new knowledge and I'm going to tell everyone who doesn't know...which would be no one...everyone knows this shit.\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small J. José Rivera Torres calling a team whiteskins or yellowskins or blackskins would be inappropriate, this is no different. It's rude and \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small In all fairness, speaking from an Irish point of view, if the "\textbf{redskin}" term comes from real Native American history and then there is a mascot then I can see where their argument is coming from, since a leprechaun is a fictional creature and generally i have no clue why it is associated with Celts then I don't think this point has an argument against theirs\normalsize   & \cellcolor{green!27}Redskin & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Irish Deco  Yes and no. Like they act like they are the only \textbf{race} that has mascots and shit made about them. How about Polynesian people when Summer time decor comes out?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small There are some posting that what these girls are saying is \textbf{common} sense or I know all of these things. But racial stereotypes about Native Americans are pervasive just like they are for other \textbf{ethnic} groups. You heard it from these Native American girls first! It IS offensive to wear a headdress for Halloween or any occasion. This past Halloween Spirit Halloween sold costumes marked "Reservation Royalty." If people would stop buying these costumes, Spirit Halloween would stop selling them. And the team renaming itself so that they're not called the Washington Redskins would be nice. But football worship is at an all time high in this country. I mean it's the millenium. Come out of the dark ages!\normalsize   & \cellcolor{green!27}Common, Ethnic & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}2/119 & \cellcolor{green!27}1.681 \\  \hline
  \cellcolor{green!5}\small what about wearing a clan hood and having a guy in \textbf{black} face as my slave for a Halloween costume, is that offensive\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Jaris Goes Ahead Pretty Oh, I see.I mean, I think that's kind of nice their curious about you, but, I can imagine it being annoying from time to time in that way.I have to admit though,it'd be nice if people were like that with me, but, I like talking, so it's just me really, lol. When most people see me they think \textbf{Black}, but, I'm a lot more than that, lol.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Yes you poor poor "Ginger's" When will you guys stop getting persecuted...give me a break. I highly doubt your dad is 100...seriously? That is not very \textbf{common}.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Timmy Hoskinson yeah. no way her dads 100. my grandpa's dad was mostly native and his mom was white and he came out with that typical silky \textbf{black} native hair and brown skin and brown eyes. really unlikely that someone with blue eyes and ginger hair has a 100 native parent\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small ashleighmarie14 they \textbf{dumb} as Fuck and they seam boring\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small sorafanchick I wasn't trolling and I'm 14 (around the same \textbf{age} as them) I also am \textbf{Indian} myself\normalsize   & \cellcolor{green!27}Age, Indian & \cellcolor{green!27}Age - General, Ethnicity - Native-American & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Edgar Castaneda I was kidding I'm \textbf{indian} and fuck you you backwoods \textbf{hillbilly} bitch fucking your second cousins getting beat up by pa and your parents must be real retards for giving you a name like Edgar\normalsize   & \cellcolor{green!5}Hillbilly, Indian & \cellcolor{green!5}Ethnicity - Native-American, Social Class - Working class & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small John Barb is that racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small John Barb I am 14 years old\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small John Barb fys \textbf{faggot}. I wasn't replying to your bitch ass and yeah I'm native. Got a problem?\normalsize   & \cellcolor{green!27}Faggot & \cellcolor{green!27}Sexual Identity - Male homosexuality & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small John Barb ITS NOT CALLED \textbf{INDIAN} STUPID ASS\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small +Cassidy StarkeNo, it means stop trying to make out that white people are the only \textbf{race} to do fucked up shit, lol.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Roger Wenell please do your research because that's not true. there is no evidence that anyone in Europe used to scalp before they found America. It was some \textbf{Indian} tribes ( not all) who would use the scalps of their enemies at their victory rituals. This info was from an native American website.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small How \textbf{common} is it for Americans to be part Native American? I'm 10 (ish) but idk if that's a super \textbf{common} thing that most people have\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Mystical Bacon which \textbf{nation} and which  reserve? Can you tell me?\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Mystical what are you talking about? We literally have \textbf{ZERO} tax here on Fort William First \textbf{Nation} reserve... no HST, no water bill, no hydro... stop lying... we dont get taxed...\normalsize   & \cellcolor{green!27}Nation, Zero & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small OK. But this video has \textbf{nothing} to do with immigration. Trump doesn't give three fucks about immigrants who come here legally. His beef is with those that enter the country illegally. Apparently YOU cant see the difference and he will get absolutely \textbf{nothing} from watching this video. Your original comment just made you look like a jack ass...\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/58 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small This has \textbf{nothing} to do with immigrants. Native Americans lived in North America even before Europeans "discovered" it, so the truth is that white people are the immigrants on this land.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small I am Oglala Lakota Native American, and I voted for Trump. Obama did \textbf{nothing} to help our tribe. Trump is not the boogy man people claim him to be. Trump cares deeply for us all, and I wish people would see that.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small African Americans are Native Americans not \textbf{African} Immigrants... They Kicked Us off the Reservations in the South So We came North... I'm Cherokee and Creek\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Americas is the Whole Continent though... Some of Our People if not Most came From the Islands or the Mexico and South America Territory. Remember Texas , New Mexico, Arizona and California was Mexico... Mexico had a \textbf{Black} President\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Florida, New Orleans, Alabama, Georgia, Mississippi, Missouri, Tennessee was \textbf{Indian} Territory... Mexico Helped Us Fight Wars against The U.S. 13 Colonies\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Trump has \textbf{nothing} against American Indians, just the indians from mexico. LOL\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Dumb Ass, Your Not from Americas, Spanish Hispanics of Spainard Descent ... If You Meant North American Indians, Then Your Talking About My People. Soooo\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small Lomp15 No clue as to why you felt the need to disrespect another group of human-beings. That is pure arrogance, mate. You seem like the casual European descendant. Let's trace back your history, shall we?European history;Indo-European sub-species (White-man) found it's way out of the Caucus Mountains (Hence the name "Caucasian,") and was taught by the indigenous tribes of Eurasia (Europe/Asia). After being taught and accepted by other humans, the Caucasian man betrayed and conquered with tactics and tools given to them. \textbf{Nothing} but disease and havoc came from this sub-species. All your ancestors have done, is wonder around the world in numbers (Because we all know these regressive fucks reproduced quickly, yet they call other sub-species by the term "Roach,") and spread sexually transmitted diseases that arose only from your blood-type and regressed DNA. Your ancestors were so filthy, \textbf{African} tribes had to teach them how to bathe because they were covered in fecal matter. Laughable, isn't it? Your ancestors tried colonizing the Americas, which were already colonized by indigenous people who welcomed your ancestors. Your ancestors did \textbf{nothing} but steal food, hunting tactics which they failed at, and spread diseases that killed off large chunks of the indigenous population. Your ancestors had diseases that caused the skin of a man to fall off, head to toe, yet you ridicule the indigenous people for "Scalping." Guess who they scalped? Your ancestors.\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/233 & \cellcolor{green!5}1.288 \\  \hline
  \cellcolor{green!27}\small +ElxiTheObserverI don't judge people based off of their ancestors. But hey, if you want to bash people who are thousands and hundreds of years dead go ahead. It's not like I'm related to every white person.But hey, if you're going to think of people as a collective then fine, white people are the best at war, adapting, and learning in general. You already said they didn't know how to do shit in the beginning but, they were taught and they perfected it. Tech in general would not be nearly this advanced without white people/civilizations. Look at Africa now, look at the Middle East now. These places are the most backwards and savage places on the planet.Also, I'm only 4th generation in this country so no, my "ancestors" did not spread any diseases. Also, \textbf{nobody} knew anything about diseases and how they actually spread back in that time. How were they supposed to know they were carrying diseases the natives weren't resistant to? It's not like they just threw diseased people at them.Also, I was making a joke. How the fuck can you find a joke that offensive? That shit happened hundreds of years ago. It's not like I look at an \textbf{Indian} person and say, "Yeah that \textbf{Indian} man scalped my ancestors let's get him!"  (as if I'm related to every white person) Also, the white people that came to America didn't "steal" food. They hunted for it. (I bet there was one time that it happened and you're going to point it out. But guess what? Indians stole too.)Also, "regressed DNA" wow.... sounds like someone thinks their superior, which is actually \textbf{racist}. If you're talking about neanderthal DNA that's a tiny chunk of the white population but it actually helps with cold resistance and resistance to diseases.But I'll restate what I said in the beginning, who gives a shit about ancestors? Why would you judge someone for something that happened in their ancestry? That's backwards logic. Judge people based on merit today, it's not that hard.\normalsize   & \cellcolor{green!27}Indian, Nobody, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}4/343 & \cellcolor{green!27}1.166 \\  \hline
  \cellcolor{green!5}\small ElxiTheObserver  We WON. We beat them, We destroyed them. We took what we wanted. They were weaker and we were stronger. That's all that matters. Your shit talk means \textbf{nothing}. Have a nice fucking day!  ;)\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small chedderz66 you're \textbf{racist} as fuck go die\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small I'm reporting your comment you \textbf{racist} devil JERK!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Not \textbf{racist} at all. just speaking the truth. The indians were conquered and that's that. It's history. For any country to get where they are now someone had to lose. Survival of the fittest. It's been that way for centuries. The Indians did the same thing well before any European arrived. The \textbf{race} card is so overplayed and watered down it's pathetic. Someone disagrees with you and boom, play the \textbf{race} card. So many of these so called oppressed people talk about being strong and brave they are but continue to whine and cry and expect free stuff.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/98 & \cellcolor{green!27}3.061 \\  \hline
  \cellcolor{green!5}\small Indians harmed \textbf{nobody} in their history. IKR\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Jacquelinedncr17 No not everyone a lot of my friends don't know the difference, \textbf{dumb} fuck\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small +Tatiana Sierra I agree but it's more or so thought of as offensive to mainly non Natives who only use the pc term which many Natives don't even like being called and I'm sure ALL Native elders have no problem with \textbf{Indian} as I've never come across one who doesn't self identify as so, the younger youth are the ones who prefer to be called Native aside from their tribal name or \textbf{nation}. I don't mean those fake Natives with a great granny who was "Cherokee", I mean actual tribal Natives. Side note, according to census, more Natives preferred the term American \textbf{Indian} over Native American and those were mainly the full blood's who preferred the term but yes some don't like \textbf{Indian}. I guess it depends on where you are and who you're talking to.\normalsize   & \cellcolor{green!5}Indian, Nation & \cellcolor{green!5}Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}4/136 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Tatiana Sierra I've never been to America but they're original name is Indians I think that doesn't mean that they are from India I think it's just what they are called, in my language they are called "\textbf{indian}" and people from India are called "indianie"\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small Selena Gomez Acapella Just going to say this, not out of arrogance or anything. Forgive me if I come off as rude. Any 'Native American' DNA, whether distant or close in your bloodline, makes you 'Native American' regardless. It could be a "Great Granny who is Cherokee," that doesn't make a difference. If the DNA tests and ancestral back tracking show that you are indigenous to the continent, you're indigenous. \textbf{Nothing} to it. You don't have to be a part of a tribe to claim your ancestry, to think that is complete asinine bullshit.Just shedding some light, much love and wisdom, may the ancestors guide you.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/107 & \cellcolor{green!5}0.935 \\  \hline
  \cellcolor{green!27}\small Indian was for Indigenous... You have Too Find 16 - 18 Century Dictionaries to find the True meanings... If theres a \textbf{Old} English, and We Speak English Today. It has to be a Difference!\normalsize   & \cellcolor{green!27}Indian, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Native-American & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small BLACK AMERICANS ARE THE "INDIANS"\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small cee sco no they're not. the only reason anyone with \textbf{African} ancestry exists on this continent is because white people brought them here as slaves. blacks are not native Americans/American Indians. you're sub Saharan \textbf{African} European mixed people. you're not native to this land.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small cee sco LMFAO!!! you're funny!! is that why voodoo, an \textbf{African} religion, exists in Brazil, all over the Carribean and in the south of USA? you know. places where a hell of a lot of \textbf{African} slaves were brought. you can't deny all the \textbf{African} culture those slaves brought here. you'd have to be completely delusional to actually believe your ancestors weren't slaves from Africa.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/65 & \cellcolor{green!5}4.615 \\  \hline
  \cellcolor{green!27}\small cee sco \textbf{black} people with nappy hair only come from one part of the world, sub Saharan Africa. no other \textbf{race} on the planet looks anything like \textbf{black} Africans. and native american basically polar opposites of blacks just with their hair alone.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/42 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small cee sco I'm still waiting for you to explain to me why an \textbf{African} religion(voodoo) is practiced on parts of the continent where so many slaves were brought? :)\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Sapa Inti We are Humans You Guys Aren't. So Yea Indians conjured Spirits , Everyone knows That Lol What are You Saying. We are the Copper \textbf{Colored} People thats were Already Here.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small cee sco sorry man voodoo is an \textbf{AFRICAN} religion that originated in benin/togo Africa, native Americans didn't practice voodooism that's entirely \textbf{African}.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small cee sco yeah that's all you idiots ever say "we copper \textbf{colored} we the real Indians" idiot. my grandfather actually speaks an indigenous language and he's brown with straight \textbf{black} hair he looks absolutely \textbf{nothing} like a \textbf{black} person. you idiots claim you're indigenous with absolutely \textbf{nothing} to back up your argument.\normalsize   & \cellcolor{green!27}Black, Colored, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}5/52 & \cellcolor{green!27}9.615 \\  \hline
  \cellcolor{green!5}\small Sapa Inti A \textbf{Mongoloid} Probably Ya Caveman\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small cee sco you're all the same I swear. read a few posts on instagram/facebook saying "blacks are indigenous we are copper \textbf{colored} we are the real indians" and you instantly feel so woke and enlightened like you've just discovered the truth the white man's been hiding from you. the reality is your ancestors are slaves from Africa, and Europeans. the vast majority of \textbf{African} Americans have absolutely no indigenous blood. there were no blacks on this continent before slavery and there's \textbf{nothing} to back up what you're saying.\normalsize   & \cellcolor{green!27}African, Colored, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black & \cellcolor{green!27}3/88 & \cellcolor{green!27}3.409 \\  \hline
  \cellcolor{green!5}\small cee sco Nah my grandpa's not a \textbf{mongoloid} or a caveman LMFAO! my grandfather's ancestors had some of the first civilizations and cities on the planet idiot\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Sapa Inti I'm not sure whether to call you \textbf{racist}, prejudice, or just plain rude.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Sapa Inti You Clearly Do Not Know History. If Your a So called Native, Then You would know what I'm saying is True. The Indigenous Americans are "\textbf{Black}" always has been and Always Will. Just Because Whites and Mongoloids Play the Roles on Tv You Believe there The Indians Lol. Shows Your Stupidity! You probably think the Egyptians were White Also Lol. Your in the Matrix\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small cee sco LMFAO! I'm from Ecuador idiot.my country is majority mixed people and native people. native people have brown skin and silky smooth straight \textbf{black} hair. my grandfathers dad was mostly indigenous, spoke his indigenous language fluently and didn't look anything like a \textbf{black} person. I am a Latino American with two half sisters with fathers that are a mix of indigenous and \textbf{African}, and one has European blood too. they look a lot different than my family that is just indigenous and Spanish, and the fully indigenous latinos I know. you don't know my history. the indigenous people of this continent are not \textbf{black} at all. I don't make this conclusion by watching TV, I make this conclusion by having an understanding of history, my family's dna (which is all my channel feel free to check it out) and actually living around fully indigenous people. you've been brainwashed. you're not indigenous. blacks are not the original people of this continent.\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}8/161 & \cellcolor{green!27}4.969 \\  \hline
  \cellcolor{green!5}\small Queen Valencia none of those I assure you :) I do have some \textbf{African} ancestry and quiet a few of my relatives have pretty significant amounts of \textbf{African} ancestry I'd never want them to feel ashamed for that. there's \textbf{nothing} wrong with that.  however I absolutely hate when afrocentrics or eurocentrics claim to be the indigenous people of this continent.\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/60 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Sapa Inti Yea You just Proved My Point. Lol, Since your "Latino" You should Your Ancestors our From Across Seas. If Your Grand Father isn't a Man of Color then He is not Indigenous, Thats a fact Sir. Idgaf what Language He speaks. If he isnt Copper Tone or Dark Skin He isn't Indigenous. Oh and Hair Textures don't matter Ya \textbf{Dumb} Ass. Thats contolled by The Environment not Genetics!  The True Indians are my Ancestors. If You are not A \textbf{Colored} Person Your Just Mimic of the Real Deal. Ohhh Just So You know I happen to Be a "\textbf{Black}" who wasn't Disconnected from His Ancestors Past So I know exactly where I'm from and How I ended Up where I Am... Ya Dick\normalsize   & \cellcolor{green!27}Black, Colored, Dumb & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/125 & \cellcolor{green!27}2.4 \\  \hline
  \cellcolor{green!5}\small Tatiana Sierra but you see in my language indians and native americans have similar names nut not the same native americans = \textbf{Indian}Actual Indians = Indianie\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small cee sco my grandfather is brown af as the majority of my family idiot 😂 the majority of latinos are mixed \textbf{race} either a mix of native and Spanish or native Spanish and \textbf{African} or just \textbf{African} and native as the Dna of My family proves which is all on my channel :) take yourself a dna test and see 0 native American come up tho it would be a nice wake up call for you. my family has strong indigenous culture still in us. I know who my ancestors were. my indigenous ancestors had some of the first cultures on this continent and the depictions they made of themselves look exactly like the indigenous people of my country today, they look like all native Americans. blacks hair texture is only native to Africa and no where else on the world. native Americans have the complete polar opposite. blacks have nappy coiled hair that you can't even run your fingers through, native Americans have the softest smoothest straightest hair on the planet. complete opposites. you're a moron. you'll never be indigenous regardless of how many instagram posts convince you that you're native for having "copper \textbf{colored} skin" your ancestors came here on slave ships from Africa, and on the Mayflower from Europe. \textbf{African} Americans are a mix of \textbf{African} and European, it's extremely rare to find an \textbf{African} American even with 2 native American ancestry. but people from Latin America have anywhere from 12-100 native American ancestry. delusional\normalsize   & \cellcolor{green!27}African, Colored, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}7/248 & \cellcolor{green!27}2.823 \\  \hline
  \cellcolor{green!5}\small \@Sapa Inti Native Americans are Native American. Egyptians are Egyptian. \textbf{African} Americans are \textbf{African} American. But a great percentage of Blacks, including me, come from Native American decent.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Queen Valencia I know. I have two half sisters who have dads that are both of native and \textbf{African} descent too. but we're all from Latin America, \textbf{black}/native mixes are much much much more \textbf{common} in Latin America. most American, \textbf{black} or white are rarely ever over 3 native.\normalsize   & \cellcolor{green!27}African, Black, Common & \cellcolor{green!27}Ethnicity - Black, Social Class - Working class & \cellcolor{green!27}3/49 & \cellcolor{green!27}6.122 \\  \hline
  \cellcolor{green!5}\small \@ElxiTheObserver Except it doesn't. 99 of those Cherokee/Blackfoot grandma claims are false, less than 5 of all white and \textbf{black} Americans actually have any Native ancestry (in regards to queen valencia). Native American is a legal term, if you aren't enrolled in one of the 500+ USA federally recognized tribes then you aren't Native American. Being 5 Native makes you a DESCENDANT of a distant Native, it doesn't make you Native.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small LAYLA SIERRA    >>> -->-> What your language ?? What is your \textbf{race}?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small ElxiTheObserver False, statistically only less than 5 of all "white" \& "\textbf{black}" Americans (more or so people of European \& \textbf{African} descent) have any American \textbf{Indian} ancestry. The only possible way for the numbers to be over 30 is if you're including Latinos. There's no such thing as "\textbf{race}" so you can't be "part native" you are a descendant point blank. Having native ancestry doesn't make you native. Unless you are apart of a tribal community and or know the traditions, culture, language etc from real natives not stuff you google online or look up on YouTube and in libraries, you are NOT native. Sorry to burst your bubble.\normalsize   & \cellcolor{green!5}African, Black, Indian, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/109 & \cellcolor{green!5}3.67 \\  \hline
  \cellcolor{green!27}\small + Tatiana Sierra  THANK YOUU I'm not Native American but it really aggravates me when people constantly call them \textbf{Indian}. Native Americans don't even look \textbf{Indian} first of all and secondly Christopher Columbus was trying to find routes to India, but where he ended up (which is today known as America) was not India but he assumed it was, that's why he called Native Americans \textbf{Indian} which they aren't.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/69 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Gabriella Mcpherson \textbf{Indian} is easier to say than Native American.... that's why it's used\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Denise NODAP montes Oglesby Its Written All My Face... \textbf{INDIAN} is A term to Describe Brown or Dark skin People ... India was Not called India back then... "INDI" \textbf{Indian}, Indigo, Indigenous... Even The Definition American - Is the Copper-\textbf{Colored} Races, If You look at a "\textbf{African} American" Your looking at the Copper-\textbf{Colored} Races, Remember they "\textbf{Colored}" In the 60's, Whites Only and \textbf{Colored} Only...\normalsize   & \cellcolor{green!27}African, Colored, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}5/65 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small cee cso........... wow....hummmmmm........i am looking at three, they are my children, there dad was \textbf{black}, sorry no cooper here.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small KarEve vH.P INDI - \textbf{Indian}, Indigenous, Indigo... Indians are Brown Skin Copper Tone Tropical People\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Tatiana Sierra  same everyone is like ur \textbf{Indian} I am like no I am native\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Bella \&Laila American Indians are The \textbf{Black} Americans\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Bella \&Laila your aunties and elders don't call themselves \textbf{Indian}? That's a first, it's said all the time on most Rez's.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small mixedandnot - correct but we still call ourselves \textbf{Indian} (well the ones here in the states). Most of us anyways, we have IHS (\textbf{Indian} Health Services), CDIBs (Certificate of Degree of \textbf{Indian} Blood), tribal newspapers are called \textbf{Indian} Country Today, we have the BIA (Bureau of \textbf{Indian} Affairs) and so much more. You should check out \textbf{Indian} Country Media Network, it's like our newspaper but for all nations. Russell Means identified strictly as American \textbf{Indian}  \textbf{Indian}, he hated the term Native American (as do many Natives). It's offensive in some Latin American countries though but in Brazil they call themselves Indians from what I've seen. I guess it's because the Spanish made them ashamed to be "Indians" idk. Just don't say the r word, that's offensive and will get you smacked. It's the equivalent to the N word.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}8/139 & \cellcolor{green!27}5.755 \\  \hline
  \cellcolor{green!5}\small Denise NODAP montes Oglesby No,  I'm Aboriginal American \textbf{Indian}... They think \textbf{Indian} is a Derogatory Term but its not It means Indigenous peoples Like Indigo of Color... Copper-Colored Races Negroes... We come in All Shades from A Copper Hue, Light Brown to Dark Brown...\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Selena Gomez Acapella Your not \textbf{Indian} Silly Ass...Your Asian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small cee sco - and you're delusional... Natives come in all shades, learn about how melanin actually works, adaption and the climates of North/South America. No one gives af about that ancient outdated superficial definition. There's dark Indians all over the US, there's light skin ones and there's pale ones. There's even Indians in Mexico that are darker than the average \textbf{African} American. Or should I point out the numerous human remains that have been found here that are over 12,000 \& 13,000 years \textbf{old} and that their DNA  genetics match ours. Y'all need to stop stalking Native videos and harassing the comments with your ethnocentric nonsense.\normalsize   & \cellcolor{green!5}African, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small Selena Gomez Acapella You a Pale Skin... I'm a \textbf{R\textbf{ed}} Skin... Wake Up... There is a American \textbf{Indian} Museum in Manhattan New York... Its Us Not You... Your from Asia , Your Ancestors Migrated here...\normalsize   & \cellcolor{green!27}Indian, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}3/35 & \cellcolor{green!27}8.571 \\  \hline
  \cellcolor{green!5}\small cee sco You are a \textbf{lunatic}, you're not \textbf{Indian}, never will be. The term "\textbf{redskin}" which will get you knocked TF out, had \textbf{nothing} to do with our skin color. It was Indians who covered themselves in \textbf{r\textbf{ed}} clay to protect them from the sun.\normalsize   & \cellcolor{green!5}Indian, Lunatic, Nothing, Red, Redskin & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}6/45 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small Selena Gomez Acapella + cee sco im 3/4 native American and am pale as fuck. i can assure you only one person in my entire family is \textbf{black} (ie came from africa) all of my family is from American and only america on my moms sidd my great 7 grandpa is sitting bull and on my fathers side my great 8 grandpa is \textbf{crazy} horse. and i dont care if you call me native American , American \textbf{indian}, \textbf{indian},  (if you call me \textbf{redskin} i wont slap you ill just laugh, cause im to damn pale to be a 'red skin')\normalsize   & \cellcolor{green!27}Black, Crazy, Indian, Redskin & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/99 & \cellcolor{green!27}4.04 \\  \hline
  \cellcolor{green!5}\small You Still don't Understand... Your not American, Your a \textbf{Immigrant} , Your Ancestors came from Asia. \textbf{Black} is not a \textbf{Race}, You can Be \textbf{Black} Too Silly. \textbf{Black} is a Status in the U.S.... My \textbf{Race} is Human, My \textbf{Nationality} is Aboriginal American \textbf{Indian}.   One Day You will Understand...\normalsize   & \cellcolor{green!5}Black, Immigrant, Indian, Nationality, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - General & \cellcolor{green!5}8/49 & \cellcolor{green!5}16.327 \\  \hline
  \cellcolor{green!27}\small other CHANNEL awsomegirl Aboriginal American \textbf{Indian}...\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Is Nikki Minaj 1/4 Native American or Asian \textbf{Indian}?\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Kanishka Parashar she is "\textbf{Black}" just Like the Rest of the West Indians\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small this is false. my family is is from Louisiana have been here before slavery and we are \textbf{black} and native american. our tribe is choctaw... no one in my family has ever been a slave. please look up choctaw tribe and please stop speaking on what u think u know.. when people say there are no \textbf{black} native americans this bothers me so much because i am one and so is my mother and her mother and father and so on and so forth. also, not every \textbf{black} person was a slave.. this is also false.. maybe an african** but not a \textbf{black} person. we are two different people with two different languages two different religions and two different ways of life. please do ur research before making me a non existent person :S\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}4/134 & \cellcolor{green!5}2.985 \\  \hline
  \cellcolor{green!27}\small I agree. I am a quarter Native American, and I think it's absolutely stupid to tell someone to deny their blood heritage. If there were no such thing as a \textbf{Black} Native American, then I would not be here.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small cee sco ok I'm just super curious, so you look \textbf{black}? but you're from a certain tribe native to the US? but people mistaken that by just calling you \textbf{black}? or something, I'm just curious\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/35 & \cellcolor{green!5}5.714 \\  \hline
  \cellcolor{green!27}\small Samera Meade You can't Look \textbf{Black}, \textbf{Black} is a Status not a \textbf{Race}... The Irish and Italians were \textbf{Black} before they served servitude, Now they are White. Its Just a Status... The \textbf{Black} and White People DON'T Actually exist these are Just Titles... The People they Call \textbf{African} Americans are not from Africa, And There Were "\textbf{African} Americans" in America before Anyone Else migrated Here... There were No Europeans(White People) Here. The People You See in The Video are White.... The Copper-Coloreds are still Here, We are the Soul Rich People\normalsize   & \cellcolor{green!27}African, Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}6/91 & \cellcolor{green!27}6.593 \\  \hline
  \cellcolor{green!5}\small cee sco Native Americans are not \textbf{African}, kid. Their traits are so much more distinct than Africans.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small i have a questions do u guys know that \textbf{black} and \textbf{african} are two different things? You can tell the difference between us and them very quickly. also there were "\textbf{black}" people or people with dark skin here before slavery.. its like if u see a person with dark skin u assume there a \textbf{black} person. which is kinda how the \textbf{black} native american was formed. they were much darker than other natives, but u people don't picture a native american being dark so u associate being dark with being \textbf{black} but i am a native and i am Caramel skin. but when other people see me they see me as \textbf{black} so i associate with being \textbf{black} native in this day and \textbf{age}. and also \textbf{black} is not really a group. its more of a mixture of people. we are or they are not really our own person. but in reality no one is.\normalsize   & \cellcolor{green!27}African, Age, Black & \cellcolor{green!27}Age - General, Ethnicity - Black & \cellcolor{green!27}9/155 & \cellcolor{green!27}5.806 \\  \hline
  \cellcolor{green!5}\small Erika Garza You Dont Know World History... All You know is U.S. History, There were \textbf{Black} People in America before Anyone Else. The Definition of American - Copper \textbf{Colored} Races ... These are White and Asian People "Caucasians", You have Eyes Open em Up... If the East Indians are Brown Skinned, The West Indians from the West Indies and the Mainland are Brown Skinned (Copper-\textbf{Colored}) ... We Still Here\normalsize   & \cellcolor{green!5}Black, Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/69 & \cellcolor{green!5}2.899 \\  \hline
  \cellcolor{green!27}\small cee sco Native Americans range from colors. They aren't a specific color. \textbf{African} also aren't native to the Americas. I know what a Native American looks like. I'm what you'd call a "Mestizo", a mixture of European and Native American which is most of Latin America. You seem very ignorant.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Tatiana Sierra We Didn't Come To America, We didn't Migrate, We were always Here. We Built this Country, My Family were Never Slaves I have Proof... Americas is a Continent , The U.S.A. is a Country In Americas... Before the White Europeans came Here , You All were Living in Peace and Harmony Among Some Our Tribes. But Not All of Our People were Friendly, Blacks from the Caribbean and Blacks from the Mainland were at War. The French Had The Eskimos in Enslaved in Canada as Well, and Some Blacks Too because there are \textbf{Black} Eskimos as Well... Negroes or \textbf{Black} People are Still Today In Canada, USA, Mexico, South America Because We are not Africans, We are the Aborigines Indigenous Peoples of Americas...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/125 & \cellcolor{green!5}1.6 \\  \hline
  \cellcolor{green!27}\small cee sco dude what are you talking about seriously. Native Americans can be dark people but I don't consider them \textbf{black}, I'm a mestizo so I'm part Native American and I have some very dark relatives!! And yes native Americans migrated from Asia, you do realize there are some really dark Asians out there.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small J Frito  America , Cherokee , Choctaw, Blue \textbf{Black} and Seminole\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small J Frito You Mongol or \textbf{Negro} ?\normalsize   & \cellcolor{green!27}Negro & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small you never know there might be that one person who is \textbf{Indian} and native american\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small John Barb no they're not! \textbf{Indian} and native.... there's a difference! \textbf{Dumb} fuck\normalsize   & \cellcolor{green!27}Dumb, Indian & \cellcolor{green!27}Ethnicity - Native-American, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small i love this, because in class or whenever i am having a social conversation about Natives and my heritage, they all use the "American Indians" or simply "\textbf{Indian}" terminology and i just get so overwhelmed. However, if they refer to us as " Indigenous" or "Native American i am at ease. It really shows who was taught correctly and who wasn't taught at all. There is a major difference between Indians and Indigenous :)\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small Why they look so white?like those \textbf{y\textbf{e\textbf{llow}}} Asians mixed with white people.Those people are like robots or clones they can't even tell they are watered down government plants.I gaurantee the original indigenous Americans was a brown deep mahogany people.Not \textbf{y\textbf{e\textbf{llow}}} white Asians.This world is freaking retarded.\normalsize   & \cellcolor{green!27}Yellow & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}6/51 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small Not all native americans have \textbf{Black} or brown straight here. Maybe full blooded but we're all different. Native American don't always have straight hair. I'm Native American, from the Apache's Tribe of Oklahoma. And I don't have Straight \textbf{black} hair, i have blackish brown \& it's curly and wavy. Not all of our skin color are brown, we can be white, we can be \textbf{tan}. Depending on our family. Native Americans did come here first, not mexican people, not \textbf{black} people \& for damn sure not white people. We are thought in school that Columbus discovered the world first which he didn't. We ARE ALL HUMAN. not just \textbf{black} people. ALL OF US EVERY ONE OF US. We don't wear our regalia everyday, we wear it when we dance at the powwows.\normalsize   & \cellcolor{green!5}Black, Tan & \cellcolor{green!5}Ethnicity - Black, Nationality - British & \cellcolor{green!5}5/132 & \cellcolor{green!5}3.788 \\  \hline
  \cellcolor{green!27}\small \@Sapa IntiThere is an argument though. Where are the slave ships now?However, there is definitely evidence of the oldest fossil remains in America, that of a melanoid \textbf{woman} from Brazil and of \textbf{African} descent, who they named, "Lucia".I indeed believe a nice deal of us were already set up here long before a white man stepped foot on this soil.\normalsize   & \cellcolor{green!27}African, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/63 & \cellcolor{green!27}3.175 \\  \hline
  \cellcolor{green!5}\small cee sco Caucasians are a sub \textbf{race} of asians lol and caucasian doesnt mean white or pale only in america lol you proved not 1 fact\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small cee sco your so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Selena Gomez Acapella, Yes, we do have a problem being called \textbf{Indian}, especially here in Canada.  We're First Nations, indigenous works as well.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Katy Simmer than you just have \textbf{dumb} friends\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small +Layla jhkybki WHAT???? StopIt🚦 THEY'RE SIBERIANS THAT MIGRATED HERE, AFTER THE LAST ICE \textbf{AGE}, IF I'M CORRECT ON THE TIMELINE. GTFOH\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small +ElxiTheObserver YEAH..INDIGENOUS TO SIBERIA. NOT THIS CONTINENT. SO-CALLED \textbf{BLACK} PEOPLE THE VERY FIRST \textbf{RACE} OF HUMANITY, and INDIGENOUS TO EVERY CONTINENT, AROUND THE ENTIRE GLOBE🌍 ScientificFacts🔬📚\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small +cee sco WE'RE INDIGENOUS AROUND THE GLOBE. WE ROAMED THE EARTH 1000's OF YEARS BEFORE ANY \textbf{RACE}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small +Sapa Inti RESPOND TO WHY NONE OF YOU MFs ARE REDDISH, BROWN, COPPER \textbf{COLORED} PEOPLE ANYMORE💡 THESE YELLOWISH, PALE SKINNED ONES OF TODAY, ARE EUROPEAN BRED TO THE CORE. MANY OF OUR ANCESTORS WERE SLAVES. NOT ALL OF THEM. YOU DISTORTED HISTORY PUSHING MF.\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small +Sapa Inti WERE THE VERY FIRST \textbf{RACE} OF HUMANITY. ThatsAScientificFact🔬📚 THAT'S ALL THE PROOF WE'LL EVER NEED MF\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small +Sapa Inti BITCH PLEASE..STOP IT🚦 \textbf{BLACK} ARE FAR MORE ANCIENT THAN ANY \textbf{RACE} OF PEOPLE. THE PEOPLE YOU SPEAK OF ARE SIBERIANS.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@cee sco I have friends born in Africa and you look just like them! A little lighter skin but that's probably because your ancestors were raped on plantations but you are undoubtedly a child of the \textbf{African} diaspora, you can cry all you want but the fact is your ancestors are still buried under that wonderful fertile \textbf{African} soil!\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/59 & \cellcolor{green!5}3.39 \\  \hline
  \cellcolor{green!27}\small \@Joel Polk lmfao I live in Ecuador and we all have a lot of American \textbf{Indian} blood most people are Brown/copper \textbf{colored} over 20 of my countries population is fully American \textbf{Indian} they are brown/copper \textbf{colored} I have plenty of videos on my channel, blacks aren't indigneous to this continent Thanks\normalsize   & \cellcolor{green!27}Colored, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}4/51 & \cellcolor{green!27}7.843 \\  \hline
  \cellcolor{green!5}\small Mal Maleficent \textbf{nobody} thinks like that. these people just want to be a victim for something\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@i s a i a h 愚者 Yeah - the whole world IS native \textbf{African}.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Papaloi lio The oldest language is hebrew, everyone came from africa, and native americans aren't \textbf{black}. You're not special.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Papaloi lio no they really don't, do you know any natives? They only look "\textbf{black}" when they're mixed, having dark skin doesn't mean they're \textbf{black} you tard.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small i s a i a h 愚者 yeah there are other \textbf{African} traits other than dark skin, lots of tribes range or depend where you're located. If anything going back in history they'd be Eurasian but that's thousands of years ago.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Too bad for Jews that their stereotypes are true - nepotistic, greedy, control the banks, media, governments, \textbf{racist}, xenophobic, manipulative, hypocritical, back stabbers with droopy bottom lips, big noses and high pitched whiney voices is all true.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small +Ben Cowsass: Too  bad for you Nazis every that stereotype about your ilk is true: hateful, paranoid,, \textbf{racist}, delusional, greedy, violent, self obsessed. if ur the master \textbf{race}, then we are all doomed\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small Papaloi lio I thought the original  natives were described as being a \textbf{r\textbf{ed}}-tanned color by the Spaniards who first visited here, hence the \textbf{r\textbf{ed}} skin insult. Don't get me wrong, but I have never seen a \textbf{r\textbf{ed}} shaded \textbf{black} person.\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}5/40 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small ABCDE FGHIJK Probably because \textbf{nobody} in the world is \textbf{r\textbf{ed}} shaded. I'm \textbf{black}, have a huge Native background, have hints of \textbf{r\textbf{ed}} and light brown on me, but a person of the colour \textbf{r\textbf{ed}} does not exist.\normalsize   & \cellcolor{green!5}Black, Nobody, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}8/37 & \cellcolor{green!5}21.622 \\  \hline
  \cellcolor{green!27}\small Everyone has an undertone, native americans have a \textbf{r\textbf{ed}} tint in their skin, no one is pure \textbf{black}, or pure white but we still call them \textbf{black} or white.\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}4/29 & \cellcolor{green!27}13.793 \\  \hline
  \cellcolor{green!5}\small \@greenelephant1231 Ok 1) "Uncivilised"? Bitch much?2) Let's get one thing straight. We. Were. Here. First. Meaning we founded this land. Whether white people stole, conquered (whatever tf you want to call it) this land, we were still here first. 3) \textbf{Nobody} said white men don't have a right to be here, we're just saying y'all don't have a right to day you founded it.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small Actually... before world government, before immigration, there was no one in this land. DNA traces the Native American roots back to Siberia. Immigration is how we ALL got here into the states. \textbf{Black}, White, Native American. However, that does not mean I excuse my white ancestors for what they did. Not all white skinned folk are monsters.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small TEAMJACOB495 That's a bit over the top, don't you think? America is LAND. Not white, not \textbf{black}, not any kind of land. NORTH America, since that's the one I assume you are talking about, was intended to be a melting pot of cultures in the early 20th century.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Brae Boujee \textbf{Racist} much?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Brae Boujee No, you're just plain \textbf{racist}. The "governments of the world" own all the land. Sorry, I don't like it either, but your statement was plain \textbf{racist}. Want a definition of \textbf{racism}?"rac·ismˈrāˌsizəm/nounprejudice, discrimination, or antagonism directed against someone of a different \textbf{race} based on the belief that one's own \textbf{race} is superior."If you believe that your \textbf{race} is superior to others, that makes you a \textbf{racist}. That's a fact. Your statement was blatantly \textbf{racist}. Do you like being part of the problem? Blaming white people for all the issues in your life? Well, that's the narrative that the Government wants you to feed into. It'd be nice if you could remove the blinders you have over your eyes and see who is really creating the division between \textbf{race} and color today, because it isn't white people like me.FYI, Christopher Columbus came from Spain. I have Irish and Italian in my heritage... guess which one of those in my heritage endured slavery, too... the Irish! Remember that next time you blame a white person for your issues. Every single \textbf{race} has endured slavery... if you're only denouncing the Mid-Atlantic Slave Trade, and not every incidence of slavery in this world, then maybe you should reconsider your views a little bit and denounce it all, like I do. It might make you a better person in the long run.\normalsize   & \cellcolor{green!5}Race, Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}10/234 & \cellcolor{green!5}4.274 \\  \hline
  \cellcolor{green!27}\small Billy Blunder is that the way you want to view it? We didn't conquer anything. Our ancestors did. Now because of weak minded people like you, our government owns every bit of land. You think your house and the land it's on is yours? Think again. You pay property tax even if your house is paid off... that makes you a "renter". Think you own your car? You don't own that either. You pay property tax on that too. Anyways, you, like Brae, feed into the \textbf{racist} narrative that the government wants you to... you know... divide and conquer. It seems to be working brilliantly for them. Hop down from your high horse and see the real problem for once.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}\small +Zoo Wee Mama oh yes "plenty" i'm sure. hahahahaha.Well i'd like you to know something, when you say you don't care about Native American history, what you're really saying is that you don't care about American history.But i tire of tutoring you. i hope this little conversation has been an educating experience for you!please do take my invitation to better your learning(as it may help you sound less like a hyper nine year \textbf{old} who somehow got hold of computor(if but a little))and with that i bid you adieu!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small No, what you see is someone disagreeing with you and you go all juvenile.  \textbf{Nothing} here is worth sadness.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Zoo Wee Mama From 1999 to 2014, the number of white births fell 8.4 to 2.1 million overall in the U.S., declines accelerated by the 2008-09 recession that caused many women to delay having children due to economic concerns. The number of deaths in that same period rose 5.8 to more than 2 million. Previous studies have shown that more white Americans, particularly middle-aged men, are dying from opioid abuse, suicide and problems associated with obesity in recent years. The study mirrors projections by the U.S. Census Bureau that the country's white population will start to decline in absolute numbers by 2025. Minority populations, particularly Latinos, continue to grow thanks to higher fertility rates, and the Census projects that the U.S. will be majority-minority around the mid-2040s.'The future of the growth in this country has to do with racial minorities,' says William Frey, a demographer with the Brookings Institution. 'If we didn't have minorities in this country, we would be like Japan, which is very \textbf{old} and has a declining labor force and declining population.'The move toward a majority-minority \textbf{nation} isn't likely to reverse itself, Johnson says, adding that several more states, including Vermont, South Carolina, Oregon and Tennessee, could soon see natural decreases in white population in the next few years.\normalsize   & \cellcolor{green!5}Nation, Old & \cellcolor{green!5}Age - Over 65s, Nationality - General & \cellcolor{green!5}2/214 & \cellcolor{green!5}0.935 \\  \hline
  \cellcolor{green!27}\small Quentie Prent I am proud that my ancesters helped conquer this land. The United States has become the most powerful and prosperous \textbf{nation}, capable of providing the highest quality of life and greatest opportunity to people in pretty much all of history. You should be ashamed if your people are able to be conquered, you would be equal to a slave. There is no reason to be ashamed of being on the winning side of history. The natives had the opportunity to unite under Tecumseh and make a stand, but they were too under developed, constantly fighting themselves, and ultimately lost to a superior people. Oh, and I guess I can say that because I have Native American ancestry, not that it matters.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/123 & \cellcolor{green!27}0.813 \\  \hline
  \cellcolor{green!5}\small \@James Russell my dear friend, respect for human life is trait to be comended not sneared at. the native american people welcomed the whites to share the land, and what did they get for it? shot in the back and thrown on reservations, the inability to vote until the thirties(after women and \textbf{black} people) and continued prejudice to this day.yes america is a great and a free land, but that terrible sacrifice should not be forgoten or made a mockery of.you make me sick, and as a soldier that's saying something.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27}\small James Russell  you must be  privileged. To think so highly of America  lmao... you see I don't expect people like you to understand. Maybe if you weren't the \textbf{race} that anybody could guess and say correctly. You have never struggled in the way others have.  Your definition of winning is different than mine because what other \textbf{race} than yours acknowledge your 'accomplishment' as winning.. more like cheating or just being greedy?  I don't know you decide... I'm  sure I can't change your opinion that you generated from others against mine which is from experience ... I will always respect natives who stood up and fight for the unjust treatment and 'exchange' they would have received... because what would they be called if they agreed? rolled over?  for such stupidity.... WEAK... so James Russell since you think genocide is some trophy.... congrats... if any \textbf{race} deserves it.... I can honestly say you're all winners. congratulations..... I believe and hope that there are people of your \textbf{race} that do understand  and aren't of the same mentality as you..  I really do.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}4/179 & \cellcolor{green!27}2.235 \\  \hline
  \cellcolor{green!5}\small Zoo Wee Mama  lol  I honestly wishhh I had the time to list them but hey we have YouTube use it.. just type in struggles of a \textbf{black} person in this society not 50 years or so back.... let's talk about now where being \textbf{black} and not only \textbf{black} but a \textbf{black} \textbf{woman} isn't a walk in the park.... I truly hope you are interested to hear my struggle because if you are just type it in the search bar and you'll have enough to write a book... lol or just buy a book about our struggle...\normalsize   & \cellcolor{green!5}Black, Woman & \cellcolor{green!5}Ethnicity - Black, Gender - General & \cellcolor{green!5}5/97 & \cellcolor{green!5}5.155 \\  \hline
  \cellcolor{green!27}\small Zoo Wee Mama if anybody's an idiot you are my profile pic is a \textbf{black} girl ...yours is some white kid I don't think I'd assume your native American either... anyways I honestly don't have the time for history when I have exams about enthalpy tomorrow  but I'm sure if you scroll up you'll find someone to argue or discuss this with\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small Quentie Prent You hinted that you were native but whatever. Just say some struggles and stop dodging questions. I'll name some struggles white people have. I am a target in most ghettos. No matter how hard I work people like you will say my "privilege" got me there. I am least likely to get a state and government jobs due to reverse discrimination: If I score higher on an application test a minority will most likely get the job to balance out the races (affirmative action). It is social acceptable to rash and be \textbf{racist} towards white people. Here are a few and I didn't ask you to look it up. If you don't list anything next comment you lost this debate and just making up bullshit.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/127 & \cellcolor{green!5}0.787 \\  \hline
  \cellcolor{green!27}\small Zoo Wee Mama  lol how \textbf{old} are you to think that me not replying makes me lose this debate?  so we are debating?  lol okay I'll  list a few but after please do not prolong this pointless convo  I really do have a test tomorrow..1. As a \textbf{black} person my big lips and broad hips and many other features are desired by other races just not on me.. constantly being teased that their not beautiful and my body is 'too much'2.my hair is to curly and 'big' and people constantly tells me to texurize or straighten to be accepted ( I did... but I'm going back natural if you know what that means)  yet other races flat hair is beautiful and if they curl their hair it is seen as just another hairstyle or cornrowing it to look exotic... but I'm judged for straightening my hair on a daily basis3.the lighter you are the more beautiful you are the more 'white' you look or talk the betterit's sad that this isn't just other races telling us but even our \textbf{race} educational  do you know how hard I have to work in school? and being told constantly that art and fashion is a white thing... doing sciences wasn't a choice... being told you have to be a doctor or lawyer to prove society wrong that \textbf{black} people can be great and must be great to prove that we are more than just slaves to the white man.... recently I was so afraid for blacks when all you could see on the news were videos of bad cops killing young men on such a regular basis even hanging... blacks are also being targeted in the work place and many of your struggles are on our list... being the least desirable \textbf{race} in the world.. congrats on being the most desirable.. you can look that up toobeing called so many degrading names not only by other races but our own labelled as bitches and ratchet and if your educated your trying to be white or think your too special or some \textbf{dumb} assumption is madetheir is a long list but it basically sums up to being \textbf{black} in this society is a constant fight to prove you can be seen as equal,  you have to show you mean no harm, you are not what people say and you are beautiful in your own skin.  it's a total different struggle being just \textbf{black} and being a \textbf{black} male or female.... I really hope you look it up on YouTube and see other individuals who have it way worse than I do and I understand that ever \textbf{race} has it's struggle but I also know these struggles aren't the same....\normalsize   & \cellcolor{green!27}Black, Dumb, Old, Race & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}10/461 & \cellcolor{green!27}2.169 \\  \hline
  \cellcolor{green!5}\small Zoo Wee Mama Ok so youre saying "you act as because im white i have \textbf{nothing} bad happen to me you are ignorant and spineless" youre literally trying to prove that person has little problems. "get over yourself" unless youre an \textbf{african} american female with these same problems you have no credibility in saying that her problems dont matter. you then turn around and try to play the victim... uh i call bullsh*t\normalsize   & \cellcolor{green!5}African, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/73 & \cellcolor{green!5}2.74 \\  \hline
  \cellcolor{green!27}\small Juvia Fullbuster I don't have to be on the sun to know how hot it is. I don't have to be \textbf{black} or a female to know what goes down. You say I can't tell her that her problems are small, but then you she says because I'm white I will never have problems as bad as her. I'm trying to teach people to get over themselves. Every time people fail a lot blame white people and \textbf{racism}, which causes more tension. Michael Jordan, Oprah, or Morgan Freeman didn't whine their way to the top. Neither should this girl with "problems that hold her back" (which they don't) and neither should I with my "problems". I listed my problems because even though they exist, I'm still successful, same thing with Obama, Shaq, and Denzil Washington. America is turning into a big cry and therapy session full of weak, spineless people.\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/150 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small Quentie Prent Get over yourself. \textbf{Black} people are way more \textbf{racist} then white people, as you demonstrated in your last three comments. I'm not the one crying, I'm speaking the truth\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Zoo Wee Mama  lol get over myself?  and focus on who?  you!?  never.  I won't argue and state false information about which is more \textbf{racist} but I'd advise you to look at who voted in a president even after hearing how \textbf{racist} he was and how he plans to deal with Muslims, blacks and Mexican who voted the most??... definitely not blacks.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Zoo Wee Mama and I'm not \textbf{racist} I believe in equality and people being treat justly.. that's what my first comment was about...  unlike yours that and many others who seem to want to justify genocide\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Quentie Prent My parents voted for Hillary. \textbf{Black} people don't need help. And Islam is what is wrong with the world\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Papaloi lio I'm \textbf{black} and I know that's a lie. The first to step on North America were Asians. They crossed the land bridge.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@Liara Tootoosis ~ you sure enjoy the 'white privilege ' technology. You suffered \textbf{nothing}, you sacrificed \textbf{nothing}. You're  just another entitled leftist. 'Native Americans' crossed the Bering Strait and are classified as Asian/Mongloid. The entire world lived by conquest and everyone engaged in it when this land was settled. I get that you romantasize the \textbf{old} ways, but you were never a part of it.\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}3/65 & \cellcolor{green!27}4.615 \\  \hline
  \cellcolor{green!5}\small Liara Tootoosis I treat people with the victim mentality differently, they clearly want to be treated different.  And the world would be far better if everyone adopted Western culture.  The natives that abandoned their \textbf{old} culture for the new, Western one certainly faired better.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small ~ read The Great Influenza by John Barry. That killed over 100 million and it all started by a little pig flu and a demand for men in the Great War. And that figure is a conservative one. It wiped out the young, not too much the \textbf{old}. Immunity is a powerful defense.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Layla Stone Sounds like you are the one in need of a safe space. And I am proud that my ancestors were winners and helped build one of the strongest nations in history. I am proud that, for the most part, they were not stone-age savages who were too stupid fighting themselves to notice a real threat. The natives in my bloodline could see the writing on the wall (or so I'd like to think). And if your \textbf{nation} is unable to protect the land it makes a claim to, then they do not own it and the \textbf{nation} doesn't exist, no matter how long your ancestors hunted on those lands. But such was/is the fate of all indigenous peoples who were stuck in the past and were unable to compete. So, does your safespace have a door, or a teepee flap?\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/142 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small Aesthetic Memer "Too stupid to invent bullets". But they were talented with arrows, which they poisoned by either mixing a tincture or rubbing poison dart frogs on the tip, and could also cure \textbf{common} illnesses such as colds and flus, whereas your people died from colds, flus, and the \textbf{black} plaque because you people were filthy, throwing your shit and piss right ouside your door, and too \textbf{dumb} to create medication. 😂😂😂 Hahaha, good one, inbred \textbf{whitey}.\normalsize   & \cellcolor{green!27}Black, Common, Dumb, Whitey & \cellcolor{green!27}Ethnicity - Black, Ethnicity - White, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}4/77 & \cellcolor{green!27}5.195 \\  \hline
  \cellcolor{green!5}\small ali renfro you don't know half of the story. Want to know why there is so much \textbf{alcohol} and drug abuse. Residential Schools, they brought tremendous amounts of Abuse, Torture, And Rape. It effected my great-kokum, she drank a lot to try ease the pain. It never worked. She neglected her children bc of \textbf{alcohol} and such. Then my kokum didn't have a good childhood and drank. Do your research. You guys are honestly so pathetic. Bragging about your ancestors being perverts, murderers and abusive people. Killing our own culture.\normalsize   & \cellcolor{green!5}alcohol & \cellcolor{green!5}Behavioural Addiction - Alcohol & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Layla Stone My ancestors were Mohawk, but my ancestors were also European. I have no animosity at all because I know the destruction of the native culture was inevitable, and the Western Anglo-American culture and society that has replaced the near Neolithic one of the natives has been able to provide myself with a better quality of life and allowed for the creation of the strongest \textbf{nation} in history. And you seem to have some untainted view of the natives either out of pride or stupidity, but the Natives did engage in rape, they did murder, they attacked neighboring tribes reclaimed their land, some even took slaves, mainly because those are traits found in all societies throughout history. I suggest you do your research and avoid ignoring information just to give yourself the illusion that the natives were peaceful, selfless, and all caring. It is a load of rubbish.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/149 & \cellcolor{green!27}0.671 \\  \hline
  \cellcolor{green!5}\small Natives come from Asia, whites come from Europe. \textbf{Black} people were here first. Full \textbf{black} aborginies do exist and they are probably the pure breeds. There's this \textbf{black} native lady who's dark skinned not \textbf{r\textbf{ed}} skinned who looks just like my great grandma. She talks just like a \textbf{old} \textbf{black} lady and has all of our characteristics. Also look up the song "Taxi" by j Blackfoot. He is a soul singer and he is a blackfoot native. My mom does not believe we are from Africa alot of our ancestors sold their children's identities. If u think history is as simple as "we came from Africa on slave ships" then u are retarded. There are many pieces missing of the story. The white Mason's have twisted shit so much u will never know unless u start being opened minded and unlearn everything from ur history books. Malcom x even said how we hated calling ourselves aborginies.\normalsize   & \cellcolor{green!5}Black, Old, Red & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}7/156 & \cellcolor{green!5}4.487 \\  \hline
  \cellcolor{green!27}\small Yelly Yellez 😆😆😆 thats because the Indians also kept blacks as slaves and eventually bred with them. Aborigines exist in Australia and are quite distinct. \textbf{Nothing} to be ashaned of being from Africa. It is unfortunate rival tribes sold off their enemies ino the slave trade. But that is the history of man. There are slao balck Americans who claim to be the lost tribes of the Hebrews.Shalom! 😆😆😆\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small ali renfro Um no honey, it's \textbf{common} knowledge that u should learn in a college setting that not all blacks came from Africa. Alot blacks were already here in America and there are pictures of them who are dark as Africans not mixed with \textbf{Indian}. Like how retarded are u. My great grandmother is definitely not mixed and is really dark skinned.\normalsize   & \cellcolor{green!5}Common, Indian & \cellcolor{green!5}Ethnicity - Native-American, Social Class - Working class & \cellcolor{green!5}2/62 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Yelly, your \textbf{common} knowledge isn't knowledge and you're wrong.----------------- [LINK] "The time range of 40,000–16,500 years ago is debatable and probably will remain so for years to come.[37][38] The few agreements achieved to date include:[53][54]  origin from Central Asia (DNA studies reported in 2012 indicate the area of Altai Republic, with a separation of populations 20,000-25,000 years ago)[55] widespread habitation of the Americas during the end of the last glacial period, or more specifically what is known as the Late Glacial Maximum, around 16,000–13,000 years before present""In 2014, the autosomal DNA was sequenced of a 12,500+-year-\textbf{old} infant from Montana, whose remains were found in close association with several Clovis artifacts.[58] These are the Anzick-1 remains from the Anzick Clovis burial in Montana. The data indicate that the individual was closely related to present North American Native American populations. But, the DNA was ancestral to present-day South American and Central American Native American populations. The implication is that there was an early divergence between North American indigenous peoples and those of Central and South America. Hypotheses which posit that invasions subsequent to the Clovis culture overwhelmed or assimilated previous migrants into the Americas were ruled out.[58] After study, the remains were returned to Montana for burial by Native Americans.  Similarly, the skeleton of a teenage girl (named 'Naia' after a water nymph from Greek mythology) was found in 2007 in the underwater caves called sistema Sac Actun in Mexico's eastern Yucatán Peninsula. DNA was extracted and dated. The skeleton was found to be 13,000 years \textbf{old}, and it is considered the oldest genetically intact human skeleton ever found in the Americas. The DNA indicates she was from a lineage derived from Asian origins and also represented in the DNA of the modern native population.[59]"--------------- [LINK] "DNA from an ancient baby's skeleton shows that all Native Americans descend from a single gene pool. And their ancestral roots are in Asia, a new study finds."----------------------------And the haploid groups make them outside of Australian aborigines and more in line with the proto asians (proto southeast asians) and They are of Eurasian heritage. You grandmother just get her a dna test. Its possible for her to me mostly native but appear differently with just a bit of admixture.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/378 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small Alexander, they can be as \textbf{racist} as they like against white people because they changed the definition of \textbf{racist} so that they could exclude themselves of being accused of what they accuse white people of. They have no concept of the world hypocrite either. Anti \textbf{racist} means anti white.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/49 & \cellcolor{green!5}6.122 \\  \hline
  \cellcolor{green!27}\small Marisol Boop That is true this land belonged to the Natives before Europeans arrived. Technically Europeans are immigrants by definition since their ancestors land was Europe. The only reason they even survived the winter was because of the Native people who were kind enough to help. But how were they repaid? They were murdered and their lands stolen. Even today did you know that DAPL desecrated a Native American burial ground. Due to this fact I find it \textbf{weird} that people are so against immigrants when they technically are themselves.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small Dark,Say i want to make sprockets. Well sprockets have to be a thing first, someone had to invent them, but some things are invented long before they are utilized (steam engine is as \textbf{old} a ancient Greece) or utilized for long times without much innovation (the wheel). But more importantly someone has to build a way to make them if they ever will see wide usage or improve them if they want to claim some special rights. Maybe first it starts off cutting a single one out from a piece of metal, so you have dozens of people in different towns. Then a few of these people, somewhere down the line, figures hey i can press these out, later stamp these out, and so on. After much physical and \textbf{mental} effort you a get a modern sprocket factory from this. If i spent the capital, time, resources, and so on to build this factory that makes sprockets so improved and distinct from the originals, what claim does one of those first people or dozen towns have on my factory? Why do they, or their children, get to say i was one of the first peoples who ever made sprockets so your factory is mine (in part)? Why do they get to claim because they used the wheel, they own part of the profit for ultra light weight carbon wheels.TLDR- Europeans built America and the West. Sure they didn't make a new earth to build it on, nor did they reinvent the wheel for all the concepts that made the West. The improved \textbf{old} government and economic systems, in places others used to be (that they replaced). But the immigrants the come into the West didn't build the West. And they aren't helping continue it (You can look up the numbers most, as in over 50, are a net drain on the system).Sounds awful and its not their fault its the governments fault, but none of that changes reality.\normalsize   & \cellcolor{green!5}Mental, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/331 & \cellcolor{green!5}0.906 \\  \hline
  \cellcolor{green!27}\small "Your factory would not exist without them having built the sprocket in the first place." Okay, so who invented the sprocket? "You have a Thomas Edison situation on your hands. He didn't exactly invent the light bulb and he didn't even own the first patent for it yet he is known for inventing it how does that work."No, absolutely not. Because we aren't concerned with who built the sprocket, just who built and runs the factory. Whoever invented the sprocket is long dead. Now if were were talking about a new specific design for a sprocket (chain saw or bike chain) then that is different, because you could show that you invested the time and effort into producing and developing such a product. Its also different if i was talking about a factory that had been making a certain wheel for 200 years, at this point anyone can make that same sprocket, because no one can show THEY made it anymore (they are all dead) and its uniqueness is no longer a thing as its design is \textbf{common} practice. In this case, anyone can make a similar sprocket, however, they cannot demand to do so with your factory as that is something that is still owned, unique, and a current product of your effort.  "Similar to how Columbus is credited with "discovering" America when no one could have since Natives were already there. " Say he hadn't, say that the Americans existed in another dimension. The West and America wouldn't be there now. It was Europeans that made the West (they built and continue to run the factory). " America existed long before the Europeans came they didn't make it because Natives already had a society and a way of doing things." The land, not the Technology, country, or structure. I didn't say the factory owners made their own land they built the factory on. " Immigrants go to school yes? " Its a bit more than that "A well educated society leads to progress. " Perhaps, so would sterilizing all low IQ individuals and forcing progeny of higher IQ individuals. So might banning frivolous entertainment and service industries?  Sad reality here is 10 more collective IQ points is worth far more than tons of money in schools systems. And as progress is your virtue i have to ask, at what cost?"They also have to work for a living as well. This makes the labor force bigger and gets more done." In an increasingly automated society... we need more people who aren't worth minimum wage.. how do you figure? " So again, why are people against immigrants." Because they are harmful to them. Its right in front of your face. Humans are greedy. They act on what each feels is beneficial. You do also, you told us yourself.  You want progress and getting more done is good. It is the people the West's fault in that they did not keep control of their governments, but don't twist that with the reality that the answer to your questions is that its the government that put people against immigrants.If \textbf{racist} \textbf{r\textbf{edneck}} bob could ban everyone, but Germans, from his store, then he doesn't have to care (at least no where to the same degree) if there are a bunch of Irish running around.If the government didn't steal tons of money from Europeans (Asians too) for the benefit of other groups. Then increasing the numbers of people they have to forcibly provide for immigration is going to be taken hostilely. Saying i want more immigration in the West currently is no different than saying i want to take more money from you to give to people that will continually make the State and its people poorer. This is the cold hard reality of current majority of immigration to the West. Its a losing proposition. But not because of the immigrants.I could continue this, but again ill end with my personal feelings that immigration isn't bad, its that the State is doing bad things and immigration makes those bad things worse. So the question is 'Why don't we stop those bad things' and my reply is, 'You don't see officers on the take, reporting their fellow officers on the take, but if you are a good officer you don't expect them too. You might still be able to have all officers bank accounts audited regularly. Even if its not ideal, you have to work with what you have."But why be emotionally hostile to immigrants, because by they're natrue they have shown they are perfectly find by coming into a \textbf{nation} against your desire at your harm. The immigrants disregard the citizens feelings, so why should the citizens care about them? Furthermore, why don't you hold immigrants to the same standards?\normalsize   & \cellcolor{green!27}Common, Nation, Racist, Redneck & \cellcolor{green!27}Ethnicity - General, Ethnicity - White, Nationality - General, Social Class - Working class & \cellcolor{green!27}5/802 & \cellcolor{green!27}0.623 \\  \hline
  \cellcolor{green!5}\small Loco Moco hey man chill.. it's ok to hate on another \textbf{race}..\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Cieara Hoseok You're \textbf{black} not native. The Injuns kept blacks as slaves. Lol\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Sonrisa Fields Shut up, you probably get your ass beat by your drunk \textbf{injun} dad. Lol\normalsize   & \cellcolor{green!5}Injun & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Sonrisa Fields They had a \textbf{weird} way of showing that they wanted to "share" the land with scalpings, rapes and murders of settlers. The good natured savage bit about Injuns has to go, it's an out right lie.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@TEAMJACOB495 250 years is \textbf{nothing} for a country. The USA is basically a baby\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small NOBODY OWNS LAND . LAND IS JUST THERE.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small It is true the Natives were here before the Europeans came. But we originated from Asia. The spanish were here before us. But still most natives died from dieases from the Europeans. I still think that this is a pointless argument. But I do feel offended by most of these comments. The white people do not own this country neither do the natives. We are just here for home. If you actually research more about American and the Europeans. But America is filled with tons of different cultures. Please don't be biased to one \textbf{race}.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/95 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Billy Blunder You really know \textbf{nothing} at all. I can go on and on about this topic but your small minded brain wouldn't be able to comprehend\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small James Russell honestly, the reason you probably have native ancestry is because your white 5x great grandfather raped a native \textbf{woman}.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Zoo Wee Mama please tell me you are not saying some sacrifices had to be made as in the murdering of a \textbf{race} that tried to offer life saving help to poor sickly white strangers on ships to then be repayed by attempted genocide. You can't condone that,  right?  Then our children were taken to boarding schools forcibly hair cut names taken and given "Christian " names and the actual beating of our heritage,  culture,  language and all that makes us human beat out of the children so jesus could be literally beat into them. Jesus never struck a person or child in order to make them believe in him being the son of God. But in his name 5 to 17 yr \textbf{old} kids were beat until they could be possibly saved from thier \textbf{Indian}-ness. Many family and friends in many tribes I know harbour a hate for Jesus because of this. The son of the living God! Was that ok?  When im called slurs or held down by white American college men and told im lucky they chose to fuck an \textbf{Indian} instead of killing one tonight,  was that sacrifice I gave to this country? Did I give my tears and ripping of my genitalia from the rape making this place great,  greatest in the world?  Cuz my dad's a cop, u should try to report this, that was what was said and truly go back to your reservation the cops tell me as a hate crime \textbf{sexual} crime is not reported but addressed as a compliant by a \textbf{woman} with said rapist having 2 friends watch not witnessing but insuring it was consensual. Not accessory to rape,  but proof no crime occurred,  is my very \textbf{common} rape and dismissal not a product of your said sacrifice that had to be made?  I am 1 of every 3 of 5 native women to be and who will be raped by a non native,  higher than the \textbf{nation}'s average for any other \textbf{race}.  We must be the sacrifice? My family and their murders and their surviving through more than I will type,  this is ok with you?  I would fight for you and yours if I saw the same atrocities happen to you.  I would do anything to help. I would never call a country who ordered all of it great,  much less the greatest in the world. I would call it an abomination. Please,  don't say things you don't mean and if you truly mean what you said,  please next time you pray,  tell God you feel this way,  for it is written Acts 10-34 God is not partial but in every \textbf{nation} the man who fears him and does what is right is acceptable to Him.\normalsize   & \cellcolor{green!27}Common, Indian, Nation, Old, Race, Sexual, Woman & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Ethnicity - Native-American, Gender - General, Nationality - General, Social Class - Working class & \cellcolor{green!27}8/459 & \cellcolor{green!27}1.743 \\  \hline
  \cellcolor{green!5}\small \@Zoo Wee Mama you have not met every \textbf{black} person you cannot say that \textbf{black} people are more \textbf{racist} than whites.\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/21 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Jay Y Native Americans are classified as part of the \textbf{MONGOLOID} \textbf{race}. Most indigenous Americans also LOOK Asian. They are NOT native to the U.S., they clearly crossed over. Even DNA tests prove this...You guys are originally from Siberia.You can claim you're "Native" all you want, but the rest of the world sees you as Asian.\normalsize   & \cellcolor{green!27}Mongoloid, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/57 & \cellcolor{green!27}3.509 \\  \hline
  \cellcolor{green!5}\small +Jay Y Either way, indigenous peoples of the Americas, from Alaska, TO the tip of South America, LOOK very \textbf{Mongoloid}. Their physical characteristics INDICATE that they came from Eastern Asia. FULL-BLOODED Amerindians can easily pass as Filipino or Vietnamese. The reason why some reservation Indians look a bit different from Asians is due to their White ancestry. The vast majority of so-called "Native Americans" have White ancestry due to colonization. And they don't OWN America since they came here from Asia...We all came from SOMEWHERE. And it doesn't make me upset lol. Those sources which you mentioned are all biased and left-wing. Their information is nonsensical as it has been proven time and time again that "Native Americans" are genetically Asian.\normalsize   & \cellcolor{green!5}Mongoloid & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/121 & \cellcolor{green!5}0.826 \\  \hline
  \cellcolor{green!27}\small \@Jay Y I see you haven't replied yet lol. Which means that you agree that Native Americans came from Asia. There's no denying their \textbf{Mongoloid} characteristics and genetics.\normalsize   & \cellcolor{green!27}Mongoloid & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@greenelephant1231 ha! You don't agree with my sources so they are biased!  Good one, we do all come from somewhere,  native tribes of north America come from the land of north America. Life started in Africa if you want to get technical so yes every one began there and from africa moved outward all over centuries inhabiting certain lands first.  North America is where my and many other people's tribes first inhabited, there for we were the native ppl or 1st ppl to be here and establish a way of life. Why must we be certain asain ppl? You are stuck on something that is not true, for some reason it's super important for you that my ppl be from Siberia and parts of Asia. Why?  Why you insist  on these untrue "facts"  much about a disproven theory that affects no one really in anyway,  it just seems like the more and more  \textbf{common} cry of non native ppl who don't want to be told to stop complaining about immigration when your English ancestors immigrated here illegally and then did bad things(to say the least) to the original ppl who already were here- type of cop out, resorting to saying but no... Native ppl are immigrated ppl from asia so that makes it of course not native ppls homeland that was stolen as well as the lessening of any guilt of what white ppls Engish ancestors did to us cuz 'we weren't from this country neither'. I've been hearing this allot latley when ever white ppl not being here first comes up latley in interviews and the news and the like when a white person is asked certain questions this whole "well natives aren't native they are Asian" thing comes up as a defence. I told you before reading your reply above I was done wasting time with replying to you since I have a life I need to live, but had to respond to this one of yours as it's ridiculous stuff you keep replying to me about.  But seriously,  you can't spend life on you tube waiting for reply after reply man,  I don't have enough time in the day to be on the internet for anything other than work,  replying back and forth to you is not on list of priorities so I say to you again,  i must go and you should spend a lil less time trolling around and go out side,  do something worth doing instead of trying to go round with me,  less screen time man,  go live your life and stop with this,  stick a fork in me man. Im done,  got school to study up for.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/445 & \cellcolor{green!5}0.225 \\  \hline
  \cellcolor{green!27}\small \@Jay Y Your left-wing sources ARE biased. Native Americans, full-blooded ones, are CLEARLY \textbf{Mongoloid}. They have \textbf{Mongoloid} features as well! There's no denying that they are originally Asian.And ha! I knew you were in middle school. It's sad how liberals brainwash you\normalsize   & \cellcolor{green!27}Mongoloid & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small +DrPhilFurry Just like how most \textbf{Black} Americans are 50 percent White, on average. There's no such thing as "light-skinned \textbf{Black}" unless they are mixed. Many \textbf{Black} Americans, just like Whites, also have Native American ancestry, which makes them look Asian and/or Hispanic\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/42 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small simple words = they are the real americans not the whites or other \textbf{ethnicity} who came after that lol\normalsize   & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small there are natives with \textbf{tan} skin but i see what she meant\normalsize   & \cellcolor{green!5}Tan & \cellcolor{green!5}Nationality - British & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small even if its \textbf{tan} it's still not red\normalsize   & \cellcolor{green!27}Red, Tan & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - British & \cellcolor{green!27}3/8 & \cellcolor{green!27}37.5 \\  \hline
  \cellcolor{green!5}\small THERE ARE ALSO DARK SKINNED NATIVE AMERICANS... BUT!!!! We still do not refer to our selves as \textbf{r\textbf{ed}}. Because its disrespectful.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Indigo Inspired I don't really get this, they can think it's disrespectful and I respect that but white people do not have white skin, but pink skin, and \textbf{black} people have brown skin, \textbf{r\textbf{ed}} I think it's referring to their undertone, and it's just a colour associated with them, and me personally I never thought of it in a negative way.\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/61 & \cellcolor{green!27}4.918 \\  \hline
  \cellcolor{green!5}\small ..... The point is people come in all different colors yes.... But alot of times \textbf{redskin} is used either derogatory or it is appropriated very much like what happens with \textbf{black} culture and everything else. because of that it makes it offensive\normalsize   & \cellcolor{green!5}Black, Redskin & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}2/42 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Indigo Inspired \textbf{Black} Americans are the Dark Natives, They Enslaved Our Ancestors as \textbf{Black} Indians, These People are Americans too, Not the European looking One though, Just the Ones who look "Asian" But are not...These Are Northern American \textbf{Indian}, \textbf{BLACK} PEOPLE are Tropical American Indians. We did not See each other Different People, We were just People Living Off the Land , the Europeans started that We Descendants of \textbf{African} and they Descendants of Asians, To further Divide Us... We are both From Here\normalsize   & \cellcolor{green!27}African, Black, Indian & \cellcolor{green!27}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}5/84 & \cellcolor{green!27}5.952 \\  \hline
  \cellcolor{green!5}\small Mexicans and South Americans as well. They just have more Inca, Mayan, Spanish and \textbf{African} ancestors. It kills me when people pretend to love Natives but then hate Mexicans. lol like same thing. We all lived near and together, there was no Mexican border.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Beatrice Quaglieri I saw a Native American \textbf{woman} in a store recognized her immediately because of her undertone and when she asked how I knew I didn't want to say why.\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small African Americans who are mix, should be label as mix, they should not claim one side of the blood... You have Pure Native Americans that despise Mix Native Americans. Ok? That exist. Listen stop mixing if you want to keep your phenotype, or keep mixing until all Natives look European.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small +Carlos ETC96 Ok, boy I hope you keep mixing until your people look European so that we can claim that all Native American look European in the modern times. Our phenotype will dominate the world. Then in the future when your people keep mixing, \textbf{nobody} will ever know how a pure on looked like except that they now look European. You will see the white man phenotype in every single Native American one day, in about 6000 years from now they will look like a German man wearing a head dress.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small +Carlos ETC96 Listen you \textbf{dumb} shrimp boy, tell your people to stop mixing, do you know what happens when people mix? That is a lost of culture at risk and the lost of identity. Elizabeth Warren claiming she has Native American blood, but you will see comments that people wrote for Example, "I bet she has only 1/32 Native American Blood" that is because she don't look like one.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small I'm \textbf{African} American  with nappy/striaght hair my grandpa was a darksinned native American lol I wish I met him\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small and also white people are not actually white and most \textbf{black} people are not actually \textbf{black} and \textbf{y\textbf{e\textbf{llow}}} people are quite far from being \textbf{y\textbf{e\textbf{llow}}}. so why the hell would be wrong to call the most \textbf{r\textbf{ed}} skinned people \textbf{r\textbf{ed}} skin?\normalsize   & \cellcolor{green!5}Black, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}12/41 & \cellcolor{green!5}29.268 \\  \hline
  \cellcolor{green!27}\small 니로다 가미니 파띠바다 아리야사까 드까 because they are not \textbf{r\textbf{ed}} skined its like calling us Meztizos \textbf{R\textbf{ed}} skined has well most native americans are ligth brown or darker brown you cant just call a group of people something they are not\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}4/41 & \cellcolor{green!27}9.756 \\  \hline
  \cellcolor{green!5}\small Leah \textbf{tan} is not red\normalsize   & \cellcolor{green!5}Red, Tan & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American, Nationality - British & \cellcolor{green!5}3/5 & \cellcolor{green!5}60.0 \\  \hline
  \cellcolor{green!27}\small These natives are more white. My tribe is more dark or \textbf{r\textbf{ed}} as u say guess they're lighter more east\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Beatrice Quaglieri some \textbf{black} people do have \textbf{black} skin.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small Maya Goodwin white people aren't really white, \textbf{black} people aren't really back. You're point?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I am actually light tanned, but i turn \textbf{black} with i get a sun tan😅\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@Lomp15 I know, that has \textbf{nothing} to do with my point\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Papaloi lio shut the fuck up cuz they aren't now. They were still Native American whether their skin was dark or fair. That's like saying light skinned \textbf{African} Americans aren't \textbf{African} American because they have fair skin. Color doesn't define \textbf{race} or \textbf{ethnicity}. There's culture/traditions to these type of things.\normalsize   & \cellcolor{green!5}African, Ethnicity, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/50 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Papaloi lio \textbf{lunatic}. no blacks aren't the real natives. Latin America actually has countries that are majority indigenous where most people speak their indigenous languages and carry on their indigenous customs and traditions. and actual indigenous look absolutely \textbf{nothing} like blacks. they're brown and have straight \textbf{black} hair. \textbf{nothing} like Africans.\normalsize   & \cellcolor{green!27}Black, Lunatic, Nothing & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/51 & \cellcolor{green!27}7.843 \\  \hline
  \cellcolor{green!5}\small Papaloi lio you aren't even \textbf{African} or from the America's at all are you? you're from India? none of this concerns you. you don't know what you're talking about. my grandfather is from Ecuador and is brown and actually speaks an indigenous language. the \textbf{black} people in our country don't speak indigenous language.\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/53 & \cellcolor{green!5}3.774 \\  \hline
  \cellcolor{green!27}\small Papaloi lio yes dravadians are \textbf{black} af, some of the darkest humans on earth, but they're not negroid.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Mariaah \textbf{redskin} isnt \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist, Redskin & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}2/4 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Mariaah fuck you \textbf{racist} son of a Bitch I'm native and I'm proud and I don't have anything against white people only \textbf{racist} people no matter there skin colour\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small +Jayden Coonishish Do you realize you're the one being \textbf{racist} right now?... I haven't insulted anyone or said anything bad about anyone and you just did that... For what reason, I don't know...\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small She say "I'm not \textbf{r\textbf{ed}} skin"I say " I'm not \textbf{black} skin"She say "tribes"I say "what tribe, I know not what tribe I belong and DNA ancestry is Bull Dogs"I guess only certain People, don't have tribes. Blacks have some connection to a tribe (whether it is known or not), Native Americans have tribes.The dominant group lacks tribe. Yup, that's cause they create it.\normalsize   & \cellcolor{green!27}Black, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!27}3/69 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Cizza O'sully I know a lot of real native Americans as a native American \textbf{woman}.  we are not extinct\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small kavana tsosie im not trying to be \textbf{racist} or anything i really hate americans for destroying native american culture\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Webster's dictionary defintion of strawman-a position, as in debate, set forth as one's opponent's view but typically misrepresenting it so that it may be convincingly refutedOkay, so what in this video is "misrepresented" to make a person wrong? These girls are simply saying that a lot of people make the same \textbf{dumb} stereotypes, some of which are ironic. (You own casinos but get gov't handouts?) And a shitty political agenda? Yeah, treat Native Americans with respect. Oh wow, so shitty (Sarcasm).\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Mariaah hey i come form tham  great spirit it the way on life \textbf{Indian} are my life  my be you need to see more about this be for you put that on here reply to this\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small 7.  You forgot they are the most brain wash and condition by the white man, and white people love to be Native \textbf{Indian} impostors.8. Native Indians were a larger population than \textbf{Black} people. Now there are over 46 million blacks against 1 million Native Americans.\normalsize   & \cellcolor{green!5}Black, Indian & \cellcolor{green!5}Ethnicity - Black, Ethnicity - Native-American & \cellcolor{green!5}4/46 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small They think the same about \textbf{black} people. They are retarded. \textbf{Black} people get food stamps. Yes some of them but so do alot of white people. Just cuz u get food stamps or welfare does not mean u are better off. Food stamps and welfare are not handouts for soley \textbf{black} people. Anyone has a good chance at getting it but they are just too good for it and like to talk shit about other people even though white females lead in welfare and food stamps. And \textbf{black} people that do have it most likely still have to work their asses off and still live in the ghetto so what difference does it make. We have \textbf{black} scholarships made for us but white people think every \textbf{black} person gets a free scholarship. No, that's not how it works. First of all \textbf{black} scholarships are rare. And when u find one u still have to compete with other \textbf{black} people to get it. So 100 \textbf{black} people can apply for it but only 1 or 2 blacks will get it and the other 98 are stuck trying to find a scholarship. Even though minority scholarships exist white people are stastically way more likely to get more scholarships than minorties. Then affirmative action. That is barely exists. If it was a big part then most \textbf{black} people would not be poor. I got a 3.6-7 GPA and graduated with honors but affirmative action did not help me get in. Alot of whites are in charge of the schools and jobs. The only reason affirmative action exists in some places because whites in charge depending who they are can be biased. And if whites are biased then that holds people back from getting jobs because of their color which is why affirmative action exists. But like I said barely anyone gets affirmative action. I never seen anyone get affirmative action. And whites still lead in numbers at universitys so affirmative action is not stopping them from getting their education. This shit whites talk about literally barely any one effectively. Everyone for the most part food stamps or no food stamps has to work to be at the place they wanna be at. I hate when whites come at me like "I am white and I had to work for everything I had" im just like so \textbf{nigga} why are u telling me that. That shit is my pet peeve. I had to work too special \textbf{snowflake} so go sit down.\normalsize   & \cellcolor{green!27}Black, Nigga, Snowflake & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black & \cellcolor{green!27}12/417 & \cellcolor{green!27}2.878 \\  \hline
  \cellcolor{green!5}\small wait so if a person has \textbf{black} skin it doesnt actually mean they are \textbf{black}? so the people with white skin arnt always white? were talking skin color not \textbf{ethnicity} or some shit. not all \textbf{black} people are africans lol.\normalsize   & \cellcolor{green!5}Black, Ethnicity & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/40 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small definitely. some make thousands a month... some make hundreds... depends on the tribe and how they manage it all.. there are millionaire native americans that never worked a day in their life... than there are native bums that have \textbf{nothing} and have not worked a day in their life lol than there are obviously people who accept the capitalist free market society, joins and works their way up the ladder.  many people are truly living in the past, we must work to fix what we have.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}\small JOHN BARB I see none of my posts had the reply tag with it so it definitely makes my replies hard to track but overall my problem with this video is the fact they had kids talking about what goes on with the native community when they dont hold that knowledge. its kindve rude to do that to some clueless teens but many will probably know no better. one of the big problems with native communities these days is the handling of finances... some tribes dole out the money to the citizens.. some invest it into healthcare and infrastructure.. the natives north of me get about 5grand ever few months but they have to worry more about their healthcare themselves... while the tribe to the east of me actually distribute it more into housing and healthcare while the citizens get whats left... 500-1000? every few months... my ex friend gets free healthcare,land and a built home, and 600\$ every few months. but than he also gets food stamps from the government(US gov not tribal) at about 200 a month... he tells them he still takes care of his kids(he walked out on them at 2years \textbf{old}) so he actually gets more stamps for himself. he hasnt worked in years. not because he cant but he doesnt want to. welfare is hurting people. all around. no matter the \textbf{ethnicity}. but if you want a rebuttal to this video in which disproves some of these myths in this "teen vogue" video... heres a link...\normalsize   & \cellcolor{green!5}Ethnicity, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/252 & \cellcolor{green!5}0.794 \\  \hline
  \cellcolor{green!27}\small Mariaah. No one believes this shit genius. The video is a way of creating an argument around a non-existent argument in order to push the oppressed \textbf{Indian} narrative.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small There was \textbf{nothing} to learn. These girls are unknowingly perpetuating SJW lies.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Shane Simmons No, lefties have \textbf{nothing} better to do except perpetuate lies that benefit their narrative and it's harmful and regressive especially when they're telling kids.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Michellle Marshall this is just such a stupid video! No one thinks they still live in tipis like \textbf{common}. And yes there school is paid for!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small thank you Shane. all it takes is going to Canada for a few hours to see First Nations people live in modern city life and still respect the reservation but DEFINITELY choose not to live there. Fuck im First Nation's (Cree) and would never fuck around on a reserve a day in my life, white people gave us opportunity and gave us privilege, more privilege than any white person in Canada. we are very fortunate for that. unlike Michelle, who is a \textbf{racist} (probably American-made) First Nation's women. Shameful.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Chazzie ! Its seriously really big of you to say that and im very happy to see that all natives arent complete \textbf{racist} scumbags. All the reserves around home all have brand new homes on them and dont think for a second that the people who live in them pay for them. Its ignorannce like michelle that give them a bad name\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small Shane Morton hell no I don't live in Canada! And hell no you don't own my home. Spew hate but I'm the \textbf{racist} huh? That's funny\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small Michellle Marshall spew hate? Your the one freaking out i just commented on the fact that the video is innacurate and you lost it. Grow up and have an adult conversation on the matter instead of accusing me of being \textbf{racist} and slandering me\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - Native-American}  & \cellcolor{red!27}Indian, Redskin, Red, Injun, Squaw & \cellcolor{red!27}564 & \cellcolor{red!27}564/173507& \cellcolor{red!27}0.33 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Dame, Woman, Sex, Sexual, Chick & \cellcolor{red!5}28 & \cellcolor{red!5}28/173507& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, African, Crow, Colored, Negro, coloured, Nigga, Jim Crow & \cellcolor{red!27}656 & \cellcolor{red!27}656/173507& \cellcolor{red!27}0.38 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Red, Libtard, Snowflake, Nazi & \cellcolor{red!5}217 & \cellcolor{red!5}217/173507& \cellcolor{red!5}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!27}Dumb, Mongoloid, Crazy, Weird, Blind, Lunatic, Lame, Mental, Disabled, Freak & \cellcolor{red!27}182 & \cellcolor{red!27}182/173507& \cellcolor{red!27}0.1 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female sexuality}  & \cellcolor{red!5}Ho & \cellcolor{red!5}1 & \cellcolor{red!5}1/173507& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racist, Race, Ethnicity, Ethnic, Racism & \cellcolor{red!27}630 & \cellcolor{red!27}630/173507& \cellcolor{red!27}0.36 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Zero & \cellcolor{red!5}213 & \cellcolor{red!5}213/173507& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - British}  & \cellcolor{red!27}Tan & \cellcolor{red!27}20 & \cellcolor{red!27}20/173507& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, White Trash, Hillbilly, Redneck & \cellcolor{red!5}44 & \cellcolor{red!5}44/173507& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationality, Immigrant, Nation, Xenophobia, doctors, Alien, Engineers & \cellcolor{red!27}75 & \cellcolor{red!27}75/173507& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}23 & \cellcolor{red!5}23/173507& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Over 65s}  & \cellcolor{red!27}Elderly, Old, Elder & \cellcolor{red!27}66 & \cellcolor{red!27}66/173507& \cellcolor{red!27}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - American}  & \cellcolor{red!5}Gringo, Yankee & \cellcolor{red!5}3 & \cellcolor{red!5}3/173507& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - White}  & \cellcolor{red!27}Whitey, Hick, White Trash, Redneck & \cellcolor{red!27}11 & \cellcolor{red!27}11/173507& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Fat, Chubby, Skinny, Lump & \cellcolor{red!5}27 & \cellcolor{red!5}27/173507& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female age and physical appearance}  & \cellcolor{red!27}Witch & \cellcolor{red!27}1 & \cellcolor{red!27}1/173507& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - General}  & \cellcolor{red!5}Homophobic, Gay & \cellcolor{red!5}6 & \cellcolor{red!5}6/173507& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!27}Yellow, Banana & \cellcolor{red!27}24 & \cellcolor{red!27}24/173507& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Chinese}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}23 & \cellcolor{red!5}23/173507& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Japanese}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}23 & \cellcolor{red!27}23/173507& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, Fruit, Faggot, Nelly & \cellcolor{red!5}9 & \cellcolor{red!5}9/173507& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Behavioural Addiction - Alcohol}  & \cellcolor{red!27}alcohol & \cellcolor{red!27}13 & \cellcolor{red!27}13/173507& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Transexuality}  & \cellcolor{red!5}Transition, Transgender & \cellcolor{red!5}3 & \cellcolor{red!5}3/173507& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Jewish}  & \cellcolor{red!27}Ike & \cellcolor{red!27}1 & \cellcolor{red!27}1/173507& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry, Hun & \cellcolor{red!5}6 & \cellcolor{red!5}6/173507& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Social Class - Destitute}  & \cellcolor{red!27}Bum & \cellcolor{red!27}2 & \cellcolor{red!27}2/173507& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Muslim}  & \cellcolor{red!5}Terrorist & \cellcolor{red!5}1 & \cellcolor{red!5}1/173507& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!27}Dot & \cellcolor{red!27}1 & \cellcolor{red!27}1/173507& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - Native-American;Gender - General;Ethnicity - Black; Ideological and Political Identity - General;Physical Identity - Physical (and Mental) Impairments;Gender - Female sexuality;Ethnicity - General;Age - Youngsters;Nationality - British;Social Class - Working class;Nationality - General;Age - General;Age - Over 65s;Nationality - American;Ethnicity - White;Physical Identity - Physical Features;Gender - Female age and physical appearance;Sexual Identity - General;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Chinese;Nationality - Japanese;Sexual Identity - Male homosexuality;Behavioural Addiction - Alcohol;Sexual Identity - Transexuality;Religious Identity - Jewish;Nationality - German;Social Class - Destitute;Religious Identity - Muslim;Ethnicity - Asian (South- India, Pakistan, Bangladesh);%.

\item The percentage of hate speech related words is 1.6558.

\item Considering that the variable \textbf{Ethnicity - Black} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 2876/6727 occurences of hate speech related comments.\end{itemize}\end{document}