\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_269.json :}\newline \par\Large\textbf {Title: \large  Dramatic spike in anti-Semitic incidents in US }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small America Woke up. Our thirst for knowledge is unstable. When the blue check mark Atheistic Jews started appearing on Twitter in 2015-2016 pretending to be Whites telling White people to denounce their whiteness to minorities and Jews. We stated looking deeper into them and we found very dark well hidden things about them. Things we would have not noticed had we not awoken. We have the logs. We have screen capped and archived everything. Lets talk about Russia \& Jewish History since I can easily back everything up with names and documents. 1931 the US state department published a three volume report on the origins of Communism in Russia, reveals how Jewish controlled German banks; under the leadership of Max Warberg conspired as early as 1914 to send large Payments to Lenin, Trotsky \& others in their attempts to take down the Czar. As part of this conspiracy, Jacob Schiff (Head of of the New York banking house Kuhn, Loeb \& Co.) invested at least \$20,000,000, which would be around \$1,000,000,000 today t-words the establishment of Bolshevism in Russia. In its article about Socialism, The Jewish Encyclopedia published in 1905 freely admits: "Jews in Russia were a Right For Revolution." In Russia, It; Socialism had become a movement of the Jewish masses. The later Encyclopedia, Judaica (1971) Tells us: "The \textbf{communist} movement and ideology played an Important part in Jewish life, particularly in the 1920's, 1930's and during and after World War 2." The Judaica (1971) in fact presents an Extensive List of the most powerful Jewish leaders of Bolshevism, Which included: Trotsky, Sverdlov, Serebryakov, Kamenev, Litvinov, Kaganovich \& many others. The Judaica also tells us, how many Jews filled the \textbf{Communist} ranks. It says: "Antisemitism drove the bulk to Russian/Jewish youth into the ranks of the Bolshevik Regime." When the white Russian patriots heroically attempted to regain their freedom from The Jews, The Judaica says: "Compact Jewish Masses were utilized by the Bolsheviks' to suppress such counter revolution." Clearly Jews and Native Russians were engaged in a death struggle over the destiny of Russia. Unfortunately The Jewish masses won. In 1918, Intelligence services of the Western Powers were buzzing with reports that Communism was an international conspiracy fomented by Atheistic Jews. British, Dutch, American \& other intelligence reports confirm that Jews filled the Bolshevik ranks, that as much as 75 of all Soviet Commissars were Jewish. In the Illustrated Sunday Herald of February, 8th 1920, Sir Winston Churchill commented on that had almost become public knowledge. " There is no need to exaggerate the part played in the creation of Bolshevism by these international and for the most part Atheistical Jews. It is certainly a very great one." In the decades following the revolution the question became, How much influence did The Jews still exert on the Soviet Experiment? Although many of the Jewish Kingpins in Bolshevism perished in Stalinist Purges in the late 30's. None other than Nikita Khrushchev gives us an eye opening view of how many Jews were still in the Soviet Government. Speaking to a delegation of French Socialists, Khrushchev admitted in 1956: "The government has found in some of its departments a heavy concentration of Jewish people, upwards of 50 of the staff." Because Communism has historically been top heavy with Jews the soviet policy of so-called Antisemitism much protested by Jews in the west may in reality be a ploy to distract the world from communism's Jewish past. Although most Jews had indeed been removed from high profile positions in the Soviet Hierarchy in the following 30 years. Jews remained highly favored when it came to immigration to the prosperous west. After World War 2, more than a million Jews had been allowed to leave the Iron Curtain sometimes in waves as much as 52,000 a year. This contrast to the grim reality that if only one gentile were to try to escape, they would be lucky to receive only 15 years in prison. The war ended in 1923 in the sense that Bolshevik \textbf{communist} control of the newly formed Soviet Union was now assured, although armed national resistance in Central Asia was not completely crushed until 1934. There were an estimated 7,000,000–12,000,000 casualties during the war, mostly civilians. Everything and preach bullshit. They still can't officially conclude how many people actually died in the Holocaust, or even how they were killed. The story keeps changing. As a matter of fact over the past 50 years the official story has changed 17 times. The Jews have even been on record to say that Hitler tricked the \textbf{r\textbf{ed}} cross in asserting how many Jews fictionally died in certain camps. Nevermind the fact that after World War 1 there was a thing called the November Revolution in Germany where the Jews tried to overthrow the German Government in favor of Jewish controlled Socialism. Nevermind the fact that the ADL is run by the Jews themselves and can make up whatever they want on a whim to what is and isn't antisemitic its not like like a cartoon \textbf{frog} is a hate symbol or saying 'Its okay to be white' is \textbf{racist}, is it? The Narrative that they never did anything wrong is bullshit by a Longshot. Who the fuck do you think you're peddling snake oil to?\normalsize   & \cellcolor{green!27}Communist, Frog, Racist, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Ethnicity - Native-American, Nationality - French & \cellcolor{green!27}7/882 & \cellcolor{green!27}0.794 \\  \hline
  \cellcolor{green!5}\small It's an insult when you use my people for your ratings...you are \textbf{racist}!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small I want to drink a lot of \textbf{apple} jews\normalsize   & \cellcolor{green!27}Apple & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Username checks out What you said sounded so gay\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/9 & \cellcolor{green!5}22.222 \\  \hline
  \cellcolor{green!27}\small The term chosen ones is not referred to \textbf{race} in the bibleOy vey goodness me ❎😑🙅‍♂️🤦‍♀️🤦‍♂️❎🚫The term chosen means as holy beloved compassionate hearts kindness humility meekness and patience bearing with one another.These things are mentioned in the bibleSo don't go hating the jews ugh 🤦‍♂️❎❌🚫🤦‍♀️🙅‍♂️🌍Understand the meaning of the scripture\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small I hate Nazis but I hate that Jews are \textbf{racist} people too cuz their religion makes them think that God chose their \textbf{race} only... That means they think they are superior than you and treat you badly... I thought they were victims from Nazis but looks like they are the new Nazis of earth... I don't hate them but I don't like that they destroys other's people freedom cuz their religion force them to that...\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/75 & \cellcolor{green!5}2.667 \\  \hline
  \cellcolor{green!27}\small As a Chinese,,,,,,,,,,,,,I don't know what side I should stand:1. Jews help Chinese \textbf{communist} government officers wash the money stolen from Chinese public,but they get attacked by this guy;Or,2.The Jews get attacked by this guy,but Jews help Chinese \textbf{communist} government officers wash the money stolen from Chinese public.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small On behalf representatives of socialism \textbf{nationalism} in iraq I'd like to say "God bless anti-semitism\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small "A \textbf{nazi} shakes your hand while holding a knife in the other"\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small "A jew will tell you everything that's been done TO him but never WHY." - \textbf{Old} Russian proverb\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Stranger Nazism is the opposite of globalism.  In fact, Nazism was created to oppose globalization.  So why shouldn't Nazism be appealing to people?  In what way has globalization been better for the West than \textbf{nationalism}?  All the evidence of the world shows us that globalization has been a disaster for Western countries.  Virtually every Western country you can think of is in economic, demographic, social, and political decline thanks to globalization, so why would people not be drawn towards Nazism?\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}\small \@Literally Hitler fuck off nazi\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Everyone who likes is a nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small "Dramatic \textbf{spike}"   and yet CNN shows no provable data. It's just their gut feelings LOL!ADL is a bullshit scam run by a jew. Where did he get those numbers? His ass? OY VEY!\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@Not Sure What we really need is what happened in Germany a right wing rise to power, sadly it would be very hard to do so. The only real way to do it would be start a Reveloution. And such things could only happen in America. It would be very hard. And most right wing groups are \textbf{racist} idiots with guns. Instead of this stuff we should be putting up posters and Trying to get headlines in papers telling the truth and trying to explain our goals. Putting a Swastika on a wall or shooting Jews proves \textbf{nothing}. But putting posters up explaining National Socalism and why it's good, or something Similar could actually have a semi impact. The only way things will get better is when things get worse. Either A: Jews gain their grip and people start revoltingB: Iran attacks Israel with Nuclear weapons.The only people with actual culture are the Islamic state. They are fighting a Holy war from medivial times in the modern \textbf{age}. Even if some things they do get pointed out by media they make big deals of everything. If only groups like ANTIFA would stop making us look \textbf{dumb} and making a bad name as well. Heil Viktoria!\normalsize   & \cellcolor{green!27}Age, Dumb, Nothing, Racist & \cellcolor{green!27}Age - General, Age - Youngsters, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/207 & \cellcolor{green!27}1.932 \\  \hline
  \cellcolor{green!5}\small Things are not going to get better. There is not a \textbf{nation} on Earth where Jews are welcome, except Israel. There are two sides to every coin and at least two angles to every story. Conflicts and violence are not created in a vacuum.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small If you talk any bad thoughts about a Jewish person your a \textbf{nazi} I'm from Poland maybe my grandfather should tell you about the Jews and what was going on.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small "Dramatic \textbf{Spike}" my ass. Fake news with "Sensationalized Wording" to catch the eye. Anything to sell commercials and politically slander Trump. Misleading people may not be a crime (not yet) but it is a sin. You'll all be wearing millstones soon enough.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Zero tolerance of intolerance is infinite intolerance. 🇮🇱  🇺🇸 - Theodore Alexander Vegh, B.S.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@david chappel The Swastika is an ancient Religious symbol, the Version that he is talking about is am anti \textbf{communist} symbol made by AH\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small They did \textbf{nothing} wrong!\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Anghel Dorin who did \textbf{nothing} wrong\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Just think about it people.  In order to boost your self esteem and globalist, "non \textbf{racist}" cred, you are willing to enslave all of us to the Jews...forever.That's correct.  Every single human generation from here until we go extinct, enslaved to the Jewish money system because you want to...fit in and feel good about yourself.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small Jews are \textbf{negro} lovers.  They use blacks against the rest of us.\normalsize   & \cellcolor{green!5}Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@Eli Kaplan Oh and Jews were behind the Holodomor. And under the 95 Jewish \textbf{communist} Hungarian government under the Jew Bela Kun, Jews terrorized the Hungarian people.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small I doubt it lmao You're an idiot, why don't you learn and research real history before going \textbf{crazy}?\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Minna Alegra \textbf{Nobody} was gassed\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small superdominacion 08 this has \textbf{nothing} to do with some made up religions but with what a few people are doing on mass scale to others, and it must stop\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small At least 10 times in the last few years Jews have done this there selves and been arrested and charged. Blatantly there own dirty work to keep alive the biggest lie in history. OF \textbf{coarse} CNN will never tell you that they consistently get caught doing these \textbf{nazi} logos them selves, then reporting it and playing scared. Just cut the BS, its been over 70 years, the majority know it never happened. We know who the true sick ones are still running this world today and screing us and many other countries over daily right in front of our faces then claiming anti antisemitism if we talk of there CRIMES..  Enough is enough, we will never forget dont worry.. Never forget the lies and corruption, How could we anyway\normalsize   & \cellcolor{green!27}Coarse, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Social Class - Working class & \cellcolor{green!27}2/129 & \cellcolor{green!27}1.55 \\  \hline
  \cellcolor{green!5}\small Should read : Dramatic \textbf{spike} in FAKE anti-Semitic incidents in US\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small seti111 jeez ur very dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small It's funny how everyone in the comments calls this a hoax but any other form of \textbf{racism} is so horrible.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small ikr people who hate jewish people are dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Ah CNN attacking the president, \textbf{nothing} about immigration messing up the world\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small You probably love a cold toilet seat on a February morning as well. \textbf{Weirdo}.\normalsize   & \cellcolor{green!27}Weirdo & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Can someone answer this question if the world has finally admitted that Jesus wasn't White, how is it his chosen people the Jews that you see today are still White? I never heard of a cover-up or lie throughout history where only one part of the story is a lie but everything there after is the truth. Another thing what makes the Jews that you see today God's chosen people they don't have \textbf{nothing} from birth other than their own privileged that makes them stand out from anyone else I like \textbf{black} people where is obvious who got Isley. Of when he created the Sun lol Unless God invented sunblock the same time he invent in the Sun. And all the other things that \textbf{black} people have straight from birth no matter their income that was given to them by God whether it's the ability to learn to walk sooner at Birth, the ability to hold their head up by themselves, the ability of strength fast reflexes the ability to turn the sun into energy oh, the ability to have a functional pineal gland in the center of the brain. I just want to know what makes these people with recessive genes God's chosen people? No one can answer that with that being said I don't think people should treat these fake Jews the way they are treating them just because they were brainwashed as well\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}3/236 & \cellcolor{green!5}1.271 \\  \hline
  \cellcolor{green!27}\small The \textbf{Nazi} cries out that you're crying out while you strike him as he strikes you.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small ADL also keeps a chart on their wall marking the purposeful declining population by the \textbf{ethnic} cleansing of White peoples through replacement migration. 'They' are the primary force behind doing the exact same thing in Europe, Canada and Australia. All I have to say is, hell or high water, OPEN BORDERS FOR ISRAEL!!!\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small Maybe if Jews started to respect other people then \textbf{nobody} would have a problem with them, but no...\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Eli Kaplan From Jesus, to bolsheviks, to CNN, Soros and Israel... Nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Adrian we didn't kill jesus the romans did, that's a conspiracy theory, CNN is not biased ur just mad, and Israel has \textbf{nothing} wrong with it\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small yikes ur pretty dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Don't give any sympathy to the Jews, don't forget how Jesus Christ was crucified, these psychopathic  \textbf{race} of people are exactly the same kind of people that murdered their own messiah!\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small AshkeNAZI is intolerant hate ideology in itself It's \textbf{communist} through Bolshevism through Frankish belief of SupremacyFacts\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Whatcha doing, \textbf{Nazi}?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Why other \textbf{ethnic} group cannot receive so much money like the Jew in ?It is unfair to pay money to them so much and the other? \textbf{Black}, Latinos, indigenous people they are receiving nothing\normalsize   & \cellcolor{green!5}Black, Ethnic, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/34 & \cellcolor{green!5}8.824 \\  \hline
  \cellcolor{green!27}\small CNN is not being truthful again  yes \textbf{crazy} white person who killed people in the temple  but please tell us who is commtiing the overwhelming amount against Jew  the same ones that prey on Asian   please be truthful CNN tell us\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Oi vey!!! Maybe if Jews weren't such a supremacist \textbf{racist} group of people there wouldn't be so much resistance to them.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small hahahah that's not true how are we racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Nuclear Redfield it's not fake u \textbf{dumb} ho\normalsize   & \cellcolor{green!5}Dumb, Ho & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Institutional \textbf{racism} only matters when it comes to the chosen people. You think blacks and Arabs don't get attacked?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small CNN top and middle management are all Jews (or at least 99). Isn't that \textbf{weird}. On top of that, they aren't ordinary Jews. They are Zionists.So CNN should be renamed to ZNN  =  Zionist-News-Network\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Wonderful news. Antisemitism will only continue to grow until the \textbf{nation} wrecking parasites are thrown out\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Fuck off nazi\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Jews are not Semites Jews are mixed \textbf{race} because in Judaism in order to be a Jew your mother has to be Jewish that's why if a Chinese guy has a kid with a Jewish women his Asian kid would be Jewish. That's the opposite of ancient Hebrew tribal tradition that pass down from father to son\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Huh... PewDiePie's Attacks On Indians Also Started Around This Videos Uploading Time. Felix, You Are A Nazi\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small AKA \textbf{racism} or even bigotry. Take your pick\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hey Johnny boy. What are you waiting for? If you feel \textbf{froggy}, why don't you leap?\normalsize   & \cellcolor{green!5}Froggy & \cellcolor{green!5}Nationality - French & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Fake and gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small Biggest reason Jews are so universally disliked is because they are the PHONIEST people on earth. E.g.> PHONY, Left-Wing Jews are always lecturing the rest of us about [sic] diversity \& \textbf{racism} while they DOMINATE the two MOST \textbf{RACIST} industries in the USA - Movies \& TV.  Most Jews are TOTAL PHONIES!\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Jonathan Hock is your typical PHONY, Left-Wing Jew who lectures the rest of us re diversity \& \textbf{racism} and he does so as a member of the most \textbf{racist} industry in the USA - Movie \& TV Industry - which is totally dominated by PHONY, Left-Wing Jews!\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/47 & \cellcolor{green!27}4.255 \\  \hline
  \cellcolor{green!5}\small Who do you think you are?? So what they are in the america they are living there if you have a problem so go far away from them and shut the hell up!! What did they do to you??\textbf{NOTHING} SO GO FUCK YOURSELF!!!😡😡\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small I hate the Jews. All they do is destroy civilizations. Tell whites tp racemix, tell whites to not marry or have children, tell good white ppl to accept third world immigration and have \textbf{sex} with them.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small The amount of brainwashed Nazis in the comment section is astonishing Hitler got in power the same way it's so funny people are still brainwashed by \textbf{Nazi} propaganda from the 30s\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Noah Balboul Say that shit to my face and i'll lay you out on the fucking street. \textbf{Nazi} scum like you don't deserve to live.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small There's a dramatic \textbf{spike} in human rights violations by Israel.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small This comment section is proof the people on the left are anti-Semitic and have a lot in \textbf{common} with the \textbf{Nazi} party\normalsize   & \cellcolor{green!27}Common, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Social Class - Working class & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Micdhael Masink you're an obvious racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Because you people on the left now sympathize with the \textbf{Nazi} party\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small You are more proof that people on the left have a lot in \textbf{common} with the socialists of Germany in the late 1920s\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Fake and Gay\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/3 & \cellcolor{green!27}66.667 \\  \hline
  \cellcolor{green!5}\small Everyone bashes Muslims and call them \textbf{terrorist},if you say one bad thing about Israel automatically you're being antisemetic. Ignore the anti semetic remarks and it will go away. If Muslims react to all the hate crimes and murdering that goes in the east it would make an impact.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small Go away Nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Nothing wrong with Jews.  It's zionism that people hate. I been to a Jewish area and trust me when I say they did not like me being around. I am a Catholic  From the uk\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small U \textbf{racist} u should die they did \textbf{nothing} wrong, they're people only different, have respect for others and people will respect u\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Yeah well maybe if you didn't commit a genocide against our people in the abortion clinics while flooding our land with third world savages, this wouldn't be happening you \textbf{racist} abomination!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small \@PaPa \textbf{JeRRy} yy thanks\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small CNN. My dude. Trump went to the Wailing Wall and wore a FREAKING kippah. You're gonna peg this on Trump supporters? You can't put hate on the entirety of a party, not Democrat or Republican. (save for the literal \textbf{Nazi} Party, and other political groups, but in the mainstream, generalizing political parties is dangerous to free speech.)\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Ya at least he respects them and if yr gonna be \textbf{racist}, no one will like u for being so mean\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@PaPa \textbf{JeRRy} yy Of course. the whole point of a reputation is that one seeks to maintain it; if Trump went about and stated explicitly close minded and hateful things, then what supporters would he have in legitimate government or in the electorate?\normalsize   & \cellcolor{green!5}Jerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}\small \@Logan S alright but at least respect others and u will get respect just like Jews. They did \textbf{nothing} wrong and that's true, white people aren't the best neither, they think they are but no, we are all equal and different and being different doesn't make you better than others, it means that u have different capabilities but if they are really good then it leads to violence and aggressive behaviour on other people who are different than them. OK but I understand yr point but please remember what I said\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}\small Bull shit, jews always want \textbf{zero} tolerance... but they treat and talk shit about everyone\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I know it has \textbf{nothing} to do with the mainstream media pitting people against each other\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small When your narrative constantly hates on white people, you give these people legitimacy.. stop sanctioning white hate and white people who feel hated on will stop joining these groups. Every time you point the fingers three are pointing back at you. Why does antifa get to beat people in terrorizing they don't get in trouble? They are a \textbf{terrorist} group.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small \@Chris Duane ...try using your real name, pussy\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Eli Kaplan ...makes sense. It should be expanded to all \textbf{race} hating bigots. They're all as bad as  each other.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Jack Wertz it was, the Zionist \textbf{pigs} brainwashed the world and wanted the United States to invade the Middle East and disrupt order so Israel can expand. Free Palestine 🇵🇸 death to Israel\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small KatynMermaid 187 hahaha how \textbf{dumb} are you\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@KatynMermaid 187 ...are you an inbred \textbf{Nazi}?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@KatynMermaid 187 ...that's bullshit anti Jew propaganda. You have \textbf{nothing} but lies and propaganda.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small If I find a \textbf{NAZi} can die by themselves\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small That is so sad 😭 to the Jewish community and it scary for society to be like I don't understand why people hate Jewish people like no one deserves it I hope the US AND THE WORLD 🌍 🌎 change like the world is full of diversity and it 21st century come on man like stop being a hater and \textbf{racist} we need love ❤️ in the world not hate\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}\small \@sUcc my peepee plz im realy Horny \textbf{Nothing} intelligent to say I guess?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Dillon Moreno ......but didn't Nazis  create the first \textbf{sex} doll?(just a statment)\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small 2,000 Subscribers Without Any Videos? They were top of slave trading living in Holland you stupid \textbf{twerp} AshkeNAZI who they are Moron\normalsize   & \cellcolor{green!27}Twerp & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Yes. I just don't see why these people target a certain group. Everyone acts differently, everyone is their own individual person. Religion and \textbf{race} does not define who we are.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@Barry Guyer They'll hire some \textbf{black} people to beat your ass while they laugh in the shadows eating/deepthroating kosher bread and butter pickles.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@infinite cognizance ...where did you get that bullshit \textbf{racist} propaganda? Do you hide behind your moniker because you're an idiot or because you're a coward?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@- jocelyn. Religion and \textbf{race} absolutely do define who we are.  There are definite traits and traditions we share as a result of those things.I'm not saying those are the only things that define us or that we can't have our own opinions but \textbf{race} and religion  have deep roots.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small I mean, \textbf{race} and/or religion doesn't define our personality or the way we act towards others. Of course, in some cases, religion can influence our actions. I'm just trying to state that everyone is their own individual person.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@get roasted Nazis practiced group \textbf{sex} and orgies.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Paul Rogers the \textbf{Nazi} will always act like he's superior but got his ass kicked twice.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small kaminoshiyo yes and in this case the rilgion says \textbf{nothing} as horrible as what they describe\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small cinegraphics to answer your question I will ask another, why do people hate \textbf{black} people? The answers is that they were immigrants (outsiders/different), us Jews were one of the first to become immigrants, that is why people hate us. Also if you are able to think for your self than do are we, all Jews act differently, so does everyone else,\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small TX Johnson why would we be \textbf{nazi} they killed us (the logic) and if you say we kill Palestinians or Muslim than you are wrong, and don't answer this.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest precisely, with precise precision.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Hey, I'm working on being a better person. Sorry! Jeez.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@infinite cognizance  That sounds about exactly right as to the thinking of the \textbf{common} jew!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Engineers Quest Keep drinking that jew-aid,Goyboy.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small infinite cognizance wow ur a \textbf{dumb} \textbf{ho} i'm jewish and i would totally kill you by stuffing a torah down ur throat\normalsize   & \cellcolor{green!5}Dumb, Ho & \cellcolor{green!5}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Jake Wood jews don't run everything \textbf{dumb} \textbf{ho} do u think i'm boss of anything— no\normalsize   & \cellcolor{green!27}Dumb, Ho & \cellcolor{green!27}Gender - Female sexuality, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Schlomo rabbi Goldberg Multiculturalstein \textbf{dumb} ass\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Schlomo rabbi Goldberg Multiculturalstein that's one company u \textbf{dumb} bitch have some compassion you white bitch\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Godzilla hahahah this bitch \textbf{dumb} you think that will ever happen we did so much that we could to help the british in the war. Many jewish people were paratroopers and helping plan attacks on germany and the austrian empire\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small The \textbf{racist} kills why saying they're the victim.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Isn't jewish people asking for land the same as christian people or witches or amish people asking to be a recognized \textbf{race} and then asking for their own country and keep taking more and more land?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small \@fieldy409 love Nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small haha anti semitism a political tool such as highly likely m.s.m u.k love this crock of shit also whos shouting anti semitism JEWS? lets be fair these people keep the indigenous populas poorer and poorer u.k seems like usary and street begging are legit enterprises . u.k aint \textbf{nothing} going on but the rent forced labour and usary . NO MAY NO DEAL NO MAY DEAL EVER. JOHN MAJOR SHITBAG TONY BLAIR SHITBAG TESSY MAY SHITBAG CORBYN SEEMS THE MOST HONEST AND COHERRANT HERE U.K M.S.M SIMPLY A JOKE AS IS THIS REGIME IN U.K . M.S.M U.K RINSING OUT THE POPULAS WITH SHITBAG HACKS . AND T.V PRESENTERS U.K GOING BACKWARDS AGAIN . RENT USARY POVERTY CRISES DESPERATION \textbf{BREXIT} I NOW UNDERSTAND GUY FAWKES . USELESS BRAINLESS SHILLS . ANTIQUATED AND POINTLESS .\normalsize   & \cellcolor{green!5}Brexit, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - European or anti-Europeans & \cellcolor{green!5}2/134 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small RACIST FUCKS\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Over 2400 US servicemen died when the Japanese bombed Pearl Harbor. Do you hate Japanese people too? Get the fuck over yourself and grow up, \textbf{Nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest ...I hear you brother. It was a tragic mistake but a mistake nonetheless. Israel had no reason to attack their number one ally in the world. It would have made \textbf{zero} sense to do so.Anti semites and Nazis alike use the USS Liberty as some sort of battle cry even despite the fact that they hate the military and those of us who are veterans.We care for our own. We don't need feigned sympathy or demagoguery to suit their means to an end.\normalsize   & \cellcolor{green!27}Engineers, Zero & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/87 & \cellcolor{green!27}2.299 \\  \hline
  \cellcolor{green!5}\small This is all zionist propaganda.  The ONLY anti-semites around today are israelis.  They are mostly white eastern europeans who hate palestine.  Palestinians ARE semetic.JEWS ARE ANTI-SEMITESJUDAISM IS ONLY A RELIGEON, NOT AN \textbf{ETHNICITY}.\normalsize   & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@nick worster Jews aren't Semetic, stop it! That's getting \textbf{old}... Arabs are the real Semetic\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest Not me I do not hush for anyone!  If you mean that in fun I get it!\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@Chloe wilson  That's true, but I want a simple (good-enough) explanation for people who have never heard of Zionists. Which is majority. Also, since Zionists have invested so much money in propagating the word "\textbf{Nazi}" in a negative way, by equalizing Nazis and Zionists I'm actually using their long-term investment and effort against them.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest I am aware of what I said.  Don't they do the same?  Of course they do!\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Chloe wilson Not all. But every \textbf{race} and religion have some that are guilty of doing it.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest Not like Israel though.  They are trying to commit complete genocide on the Palestinians and no-one has committed false flags like they have.  Have you ever read up on ISRAELI FALSE FLAGS.  When those oh so poor, persecuted people came off those ships into Palestine.  The first thing they did was steal their homes and contents, raped and murdered.  PM A. Sharon, aka The Butcher was the leader of the pack.  He loved to disembowel these people.  Now that tells me these were \textbf{nothing} more than Bolsheviks and Communists.  Oh well enough.\normalsize   & \cellcolor{green!5}Engineers, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/94 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Well, why not?\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Chloe wilson They are not trying to do any such thing. Sounds like you've gotten some misleading information either from misinformed sources suggesting study material or from sought out sources supporting preconceived beliefs. I could be mistaken though. I can't judge someone I know \textbf{nothing} about. That would be wrong. Correct? I also couldn't judge an entire group of people for the actions of a few in the past. EVERY group of people has had and still has their fair share of bad apples. As far as stealing land, I'm from the United States. If I condemned such an action I'd be a hypocrite.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/104 & \cellcolor{green!5}0.962 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest I just turned the \textbf{oven} on, let me known when your stopping by I'll keep it nice and warm for you.\normalsize   & \cellcolor{green!27}Engineers, Oven & \cellcolor{green!27}Nationality - General, Religious Identity - Jewish & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest I appreciate the thought but I'll pass on the gift\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Why's that?\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest Yes they are!  Have you looked back at their wicked history?  The Bolshevik/Jews slaughtered 66 mill white Christians in Russia.  Then there was the Ukrainian Holodomor, 12 mill by forced starvation.  All wars are started by them.  Who funded WW1, WW2, the Rothschilds, Shiffs, Morgans, Warhburgs.  I know all about them.  Had the misfortune of living amongst them and plus I do read their history.  They had Jesus murdered did they not?  Have you forgotten about him?\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small \@Chloe wilson Again you're speaking of the past. We ALL have one. Did every single Jew do this? As far as Jesus, the Romans had a choice. \textbf{Nobody} made them do anything they didn't want to. How many were asking for His death? Any idea? Do you know who they were? Should we hate their descendants who had \textbf{nothing} to do with it?  How many followers and supporters did He have that obviously didn't want Him dead? Did you know they were Jewish like Him?  Do you know every single Jew personally? I don't think anyone can condemn someone without knowing them.\normalsize   & \cellcolor{green!27}Nobody, Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/102 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest In answer to your question, the answer is NO!  Well maybe one or two of them were good!\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Yes.  Many!\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest What are you doing taking a survey?  I have \textbf{nothing} further to say to you!\normalsize   & \cellcolor{green!5}Engineers, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small \@Jack Wertz You cannot say where my hatred comes from.  Obviously you have never looked up the Bolshevik Rev.,whereby the murdered untold millions of Christians and the Holodomor, 12 mill by forced starvation. Israel if the \textbf{terrorist} country of this world.  The min they stepped foot into Palestine they started murdering the Palestinians.  I love it where Israel stated that one of the Palestinian bombs backfired and killed that \textbf{woman} and her child.  ISRAELI FALSE FLAGS!  FRANKFURT SCHOOL ON LINE - THE ARCHITECTS OF WESTERN DECLINE AND CULTURAL MARXISM. Try and deny those.  Always playing the victim never the perpetrator!\normalsize   & \cellcolor{green!27}Terrorist, Woman & \cellcolor{green!27}Gender - General, Religious Identity - Muslim & \cellcolor{green!27}2/100 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small \@Chloe wilson ...provide one shred of proof of your \textbf{racist} propaganda. Your hatred obviously comes from YOU. As with all low IQ \textbf{nazi} miscreants you're trying to insinuate others are to blame for your stone cold \textbf{racism}. You are the epitome of a \textbf{racist} \textbf{nazi}. You blame an entire group of people based on lies and \textbf{racist} propaganda. None of the feces spewing from your mouth has any basis in reality.Stand with Israel 🇮🇱🇮🇱🇮🇱\normalsize   & \cellcolor{green!5}Nazi, Racism, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}6/75 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@Chloe wilson I just want you to know that I understand you not wanting to talk anymore. Sometimes someone asks us questions or make a comment that make us question our beliefs that we cling to so strongly and it can be quite uncomfortable. This is why we can't or won't answer those questions. Sometimes our pride plays a part in this. We don't want to seem weak by admitting to ourselves that the person asking the questions may be right or at least have a point. Denial is quite \textbf{common} as well. I know from experience. I'm no better than you. I have \textbf{nothing} against you. You're not weak. You just need to understand that no entire group of people should be looked down on because of the actions of some whether in the past, present, or future. You are part of some group as well. We all have areas we need to grow in and we always will no matter how \textbf{old} we get. You will. So will I.\normalsize   & \cellcolor{green!27}Common, Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Social Class - Working class & \cellcolor{green!27}3/171 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest I have no idea what this is about!\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Bolshevism, Communism ring a bell?\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest So true.  I am reading yr emails for the first time now.  I never received any of this the first time around!\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Yes.  Look at the havoc they are creating in the US.  Have u ever watched FRANKFURT SCHOOL ON LINE - THE ARCHITECTS OF WESTERN DECLINE AND CULTURAL MARXISM.  It will be thought provoking!\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest True.  Lol!\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest  I will\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest  I live very near Pittsburgh\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest WHAT DO YOU WANT TO DO?\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest I'm not too tough for your mouth\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest  That just what I thought about you when you invited trouble with me!  You don't know me or any of the other people on here you mouthed off to, that's how I knew you were stupid and could easily be trolled\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small cinegraphics THEIR NOT FUCKING EQUAL YOU PIECE OF SHIT THE NAZIS KILLED SIX MILLION OF MY RELIGION AND KILLED MANY OTHER MINORITIES WHILE ZIONISTS HAVE DONE \textbf{NOTHING} LEARN SOMETHING YOU FUCKING PIECE OF SHIT\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Chloe wilson hahahah this bitch is so \textbf{dumb} thinks that it wasn't germany's fault for the war\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Chloe wilson just so you know it never happened it's a conspiracy theory there's \textbf{nothing} on it\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@Eli Kaplan ...and you're spewing the same \textbf{ethnic} based propaganda your \textbf{Nazi} friend Chloe is spewing when you generalize about the US\normalsize   & \cellcolor{green!27}Ethnic, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Jack Wertz to think ur telling me i'm the same as a \textbf{nazi} when 11 of my people died\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Jack Wertz \textbf{race} and religion are two different things don't even try to comeback u fucked up bro\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@Logical Extreme why is everyone on the left anti-Semitic you people seem like you're sympathetic with the \textbf{Nazi} party because you do seem to have a lot in common\normalsize   & \cellcolor{green!5}Common, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Social Class - Working class & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small Trump said: "I'm going to make America great gain."Hitler said: "I'm going to make Germany great again."Why did they claim to be making something "great again" when they actually wanted to make it "\textbf{racist} again?"\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Why is this happening? America is not helping people rebuild their homes after an disaster if they boycott Israel, essentially they are putting the Jewish people in danger more than helping them Note: I am not a neo \textbf{nazi} and I love the Jewish people I just hate Israel and their regime\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small PUNISHER of PINKO PEDOS hahahah \textbf{dumb} ass we don't believe in hell remember how can we go to a place that doesn't exist\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Jacob Forrest ohh little Jew boy mad cause he's not very bright 😢go cry to your little Jewish mommy you \textbf{brat} go burn in hell XD I'm the best\normalsize   & \cellcolor{green!5}Brat & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@Jew Hunter = angry \textbf{Nazi} coward\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@Jew Hunter ..."you Jew". Hahahaha. Is that supposed to be an insult? You're even too stupid to be a \textbf{Nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Anti-semitism is a word invented by jews to gain power over anyone who criticizes them for their parasitic behavior. I hear a lot of Anti-White propaganda and \textbf{nobody} seems to give a shit about it.. And the media doesn't call out hoaxers neither does the media correct itself after false news comes out that is polarizing the country and creating tensions between groups and hatred. Wanna get rid of antisemitism, stop giving people a reason to criticize you and become loyal to the people in the country you live in, instead of being a 🦠\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small At the conclusion of WW1, Germany was in the grips of a civil war between German Freikorps volunteer militias primarily made up of returning soldiers as well as patriotic citizens of Germany, and the Spartacus League, a group of radical \textbf{Communist} revolutionaries led primarily by Jews such as Rosa Luxemburg, Karl Radek and Kurt Eisner. Thousands of Jews would attempt to install the same Soviet-style Bolshevik government that had put into place in Russia. The overwhelming preponderance of Jews among the \textbf{Communist} movements was well noted by soldiers and citizens alike, in Germany and abroad, until the Spartacus League was finally put down.\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/103 & \cellcolor{green!5}1.942 \\  \hline
  \cellcolor{green!27}\small Anti-Semitism is the downfall of every Empire/Kingdom in the history of mankind. This is the end of the American \textbf{Age} as we know it. No wonder why the East is rising and the West is falling. Europe, North America and Africa this is your end and you are just gonna be  second and third nations. Attacking Jews people for what, bunch of imbeciles, cowards,spoilt bratts with no sense in the head.\normalsize   & \cellcolor{green!27}Age & \cellcolor{green!27}Age - General & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}\small You have it backwards. First the Jews destroy your \textbf{nation} and then you become antisemitic. You put the cart before the horse, dummy.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small blame this on TRUMP I don't think so. Obama brought record numbers of Muslims into our country and they do three things 1collect welfare 2 reproduce 3 hate Jews . so you ain't seen \textbf{nothing} yet\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Dramatic \textbf{spike} in anti-Semitic incidents in US.....And the bad news is???????....LOL...The bad news is that there are not nearly enough anti-Semitic incidents in the US.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Those who hate Jews and claim to be Christians are \textbf{dumb} asf. Christ is Israeli/Jewish. That's according to your Bible\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small someone who is \textbf{racist} against jewish people\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small ur so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small Of course CNN would try to spin this to blame Trump. The election has \textbf{nothing} to do with it. As Trump is one of the biggest Israel supporting Presidents of all time. He totally supported Jerusalem becoming the Jewish capital of Israel. Fuck you CNN!  Israel loves Trump for what he is doing. I just heard yesterday Jews on the radio praising Trump for what he is doing. CNN always trying to \textbf{race} bait.\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/74 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small Oven lol\normalsize   & \cellcolor{green!27}Oven & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small Has to be demonrats cause no self respecting Republican could do those things only Roosevelt, Truman can all demonrats and Bush and Obama demonrats would engage in false flags to further erode the constitution. Don't believe \textbf{lame} stream media and if comes from CNN JUST KNOW ITS THE OPPOSITE OF WHAT THEY SAY\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small I'm more concerned about how Jews seem to have an increasing sense of superiority over all non-Jews.  Please read this very disturbing quote from the former Prime Minister of Israel, Menachem Begin, as he describes the place of Jews above all others and then question why the 3 biggest Jews in government, Schumer, Pelosi and Feinsteinn have worked SO hard to weaken, destabilize, and endanger our entire country:'Our \textbf{race} is the Master \textbf{Race}. We are divine gods on this planet. We are as different from the inferior races as they are from insects. In fact, compared to our \textbf{race}, other races are beasts and animals, cattle at best. Other races are considered as human excrement. Our destiny is to rule over the inferior races. Our earthly kingdom will be ruled by our leader with a rod of iron. The masses will lick our feet and serve us as our slaves.' — Menachem Begin – Israeli Prime Minister 1977-1983.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/159 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Long story short - Chuck Schumer (JEW), Nancy Pelosi (JEW), Dianne Feinstein (JEW) were the principle people responsible for the total breakdown in our democratic institutions because of their sick obsession and lust for power.  They showed us that anyone can be guilty at any time, with no presumption of innocence, whenever some kook levels \textbf{sexual} assault charges against a good and decent family man.  Why?  POWER!!!  They obsess over the POWER!! It's an addiction I can't relate.  I simply can't and I'm happy to say that as a popular and well-adjusted member of society, I have never wanted to desired the ability to lord over others.  However, additional research proved to me that this obsession with power was not just limited to these 3 Jews.  In fact, it's been an important goal for Jews since the early 1900's to create a globalist society in which they are the only Caucasians (note Jewish George Soros paying for the boats that just keep on flooding Europe with idiots from Africa and other shithole sandboxes). The ultimate end goal is for them to rule over all others, because their "administrative" brains naturally predispose them to best rule everyone else. That's almost as arrogant as the whole "chosen" thing they always try to convince everyone is really referring to positives and not the more realistic proposal I came up with in which "chosen" is actually another way of explaining they were singled out and punished for their Jewish behaviors.  The punishment includes being limited to the relatively small area in the sandbox known as Israel, while all others are free to roam the earth anywhere they please. Further, I now think it's very possible that an additional way they were "chosen" to be punished was with their physical appearance and that in an effort to provide gentiles with some warning sign, God CHOSE for the Jews to look strikingly similar to dirty rodents, like the mouse/rat. (See Steven Spielberg's cartoon movie "An American Tale" and note the main mouse, Feivel, looks like almost every Jew I went to high school with!!!  Thanks for the warning, God!Even more curious with the direction this was going, I continued my search for answers and I was led to one of the 2 most damning pieces of evidence as to why I am now proud to be an anti-Semite until Schumer, Sanders, Pelosi et al. start to actually put our country before their bank account!  The "Protocols of the Elders of Zion" is a very controversial book that in and of itself is a brilliant piece of writing that really demonstrates a brilliant covert battle to slowly give the Jews all that they need to enslave all others and rule over us.  This book was written in the early 1900's, shortly before the Jews in Russia suddenly and violently fired off the Bolshevik Revolution in which they killed the ruling aristocracy and turned Russia into the USSR, where they enacted communism. That didn't turn out very well almost immediately and upon seeing that it was a really stupid idea, they decided to save face by forcefully making people labor for free in the gulags.  It was a combination of the terrible conditions in the gulags and Jewish paranoia to losing their new power that led to the deaths of 10 to 40 million people.As one might now expect, Jews simply assert the "Protocols" are simply fiction, despite the fact they have correctly predicted events that only recently occurred!!!  The Protocols instructed Jews to takeover all media sources so they could control and limit how their actions are portrayed = DONE!  It also instructed them to have the countries they are trying to destabilize and force to collapse to begin by GOING OFF THE GOLD STANDARD (yes, that was successfully completed in the1970's) and there are dozens of other that have been accomplished, such as Israels' false flag attacks on the USS Liberty (100 proven to be a deliberate attack and murder of US sailors because \textbf{pussy} Jews can't fight and wanted us to be pulled into the Six Day War and of course, 9/11 being pulled off by Mossad agents and forcing us to become an active presence in the middle east.  BTW, did you notice every single Jew in the media was furious when trump announced our pullout from Syria?  Why? Because Israel is TRULY very \textbf{pussy} and prefers US to fight for them, so they wanted us to stay indefinitely to protect them against Iran.  The way history unfolded exactly like the "Protocls" instructed the Jews to make it unfold is alarming, but they swear it's just fiction, but offer no evidence of any kind of this claim, whereas their is actually compelling evidence the doc was legitimate.  I prefer to use logic and reason and because of that, I strongly agree that at this point, just a denial doesn't cut it and this is one of those things they really should be discussing if they want to help slow down their eventual removal from this country.Speaking of which! Back to he "woo is me" tales Jews always cite about the persecution they 've always faced.  I'm sorry, but I don't believe someone woke up one morning and said, "Ding dang, it sure is nice out and I think I'll kill out the Jews today!!!"  NOPE!  What's more likely?  That throughout history, people like Feinstein, Schumer, Pelosi, etc. have tried actively to weaken and destroy countries until the people finally woke up enough to see and try to stop it by first kicking them the fuck out of the country.  Yeah, pretty sure that's the more likely scenario!So, I hope soon Schumer and Pelosi and the others can explain why suddenly now that we have constant invasions of thousands of criminals who are totally uneducated/unskilled men of rape \textbf{age}, that it's suddenly the great idea of theirs to prevent the MOST effective measure to protect us actual American legal citizens.  If you watched the funeral for slain officer Singh, you know that only the most heartless and corrupt assholes could possibly still fight this hard to ensure the future murder of more innocent American lives.because undermining and ruining a country was probably the reason  prematurely killed. And they should probably address the "Jewish questions" pretty damn quick, because the pure hatred I'm spring up across the country is alarming and wont turn out well for a lot of Jews if they choose to continue to place their Zionist interests aboive the society they are currently lording over (which reminds me, Pelosi also very deliberately created a method to cheat during the midterm elections and that's the only reason she's back. The REAL poll numbers had her losing badly, but she had her employees fill out the thousands of mail-in ballots necessary to get her elected.  It's actually a very disgusting example of how the left is now a tyrannical aristocracy ruling without any fear of backlash in future elections, because with ballot harvesting, they can't lose!!  It should also be noted that Pelosi essentially admitted she was cheating when she appeared shorty before the elections on the late night show hosted by that Colbert guy with the jacked up ear.  This isn't even a full listing of all the reasons I turned into a total Jew hater/loather/despiser from the totally indifferent person I was only a couple years ago!  I will remain a staunch anti-Semite until they start to explain why the double-standards when it comes to who I prefer to marry over who a Jew does and why lie cheat and steal all the time and why let good men get murdered by very evil men and then laugh and joke you will give Trump a \$1 for his wall.  If it's so ineffective, why not be all for him doing it and then getting to sweep the next elections when you point out what a waste it was and what an idiot he was?!?!  BECAUSE YOU KNOW YOU ARE LYING LIKE USUAL AND THE WALL IS JUST AS EFFECTIVE AT KEEPING US SAFE AS ISRAEL's WALL (which is where they will go after they have sufficiently ruined America in case you were thinking I must be wrong because they have to live here too - NOPE!  But non-Jews can't get into Israel to live, so it's just more evidence the Protocols are right on track!).   Damn that revved me up with fierce anger and I really want to go slap Pelosi around with her soggy Depends diapers!!!  Feel free to contact me if you want to join our members list that currently has over 11,000 people also fed up with  a very specific group of Jews intent on ruining our government.  You will receive a monthly email newsletter, as well as regular bonus materials all deter special instructions explaining how you can easily spot a Jew based on their physical appearance, actions and/or inactions, or even just by the distinct accent frequently found among certain tribes.  Also, you will receive regularly hilarious stories of the way I try to keep my brutal rage at bay and attempt constructive, but still really evil ways to blow off steam every now and then, such as when I went on a first date with a very Semite looking Jewish American Princess, complete with a budget titjob (don't skimp on things that cheapo!) and I used ancient Goy techniques to convince her my cock would somehow fit in her shithole and that the ritual draining of my balls onto her  Torah was just a way for me to show my appreciation to all Jews for all they had engaged in so that they could fuck over everyone throughout history that she had sitting on a stand in her room (and she was so horny for my nut to erupt and spray the room that she even agreed to it when I pushed the envelope by asking for permission first!) P.S. Feel free to let any of the named politicians currently suffering from delusions of Jewish supremacy know that their continued attacks on our country will ultimately end with their dismissal from this great country permanently.\normalsize   & \cellcolor{green!5}Age, Sexual, pussy & \cellcolor{green!5}Age - General, Gender - General, Nationality - Chinese & \cellcolor{green!5}4/1702 & \cellcolor{green!5}0.235 \\  \hline
  \cellcolor{green!27}\small \@skumfuck yes and your not judah by blood line your \textbf{nothing} butt lie about everything you your are gomer gentiles Genesis 10:2-4 King James Version (KJV)2 The sons of Japheth; Gomer, and Magog, and Madai, and Javan, and Tubal, and Meshech, and Tiras.3 And the sons of Gomer; Ashkenaz, and Riphath, and Togarmah.4 And the sons of Javan; Elishah, and Tarshish, Kittim, and Dodanim. what Ashkenaz from gomer ok meaning time אַשְׁכְּנַז ʼAshkᵉnaz, ash-ken-az'; of foreign origin; Ashkenaz, a Japhethite, also his descendants:—Ashkenaz. ok by jewish own mouth not mine Ashkenaz (Heb. אַשְׁכְּנָז) refers to a people and a country bordering on Armenia and the upper Euphrates; listed in Genesis 10:3 and I Chronicles 1:6 among the descendants of Gomer. The name Ashkenaz also occurs once in Jeremiah 51:27 in a passage calling upon the kingdoms of Ararat, Minni, and Ashkenaz to rise and destroy Babylon this from  [LINK]  ok now the home land Khazars KHAZARS, a national group of general Turkic type, independent and sovereign in Eastern Europe between the seventh and tenth centuries C.E. During part of this time the leading Khazars professed Judaism. The name is frequently pronounced with an a-vowel, as in the Greek Χάξαροι and Arabic Khazar (Ḥazar), but there are traces of a different pronunciation in Hebrew (Kuzari, pl. Kuzarim), Greek (Χότξιροι), and Chines  [LINK]  hebrew law 2 and 3 witness is true we are pass this it can be proven hands down you own more  of the slaves and own all the slave ships this also come out your own mouth ok now lets see about Japheth he will go in the tents of shem thatts right isreal is not your land you theft lands that not yours Gen 9:27God shall enlarge Japheth, and he shall dwell in the tents of Shem; and Canaan shall be his servant. ok get enlarge and your in the tents of shem right now פָּתָה pâthâh, paw-thaw'; a primitive root; to open, i.e. be (causatively, make) roomy; usually figuratively (in a \textbf{mental} or moral sense) to be (causatively, make) simple or (in a sinister way) delude:—allure, deceive, enlarge, entice, flatter, persuade, silly (one). lol you been deceive\normalsize   & \cellcolor{green!27}Mental, Nothing & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/365 & \cellcolor{green!27}0.548 \\  \hline
  \cellcolor{green!5}\small The official number citing the source "\textbf{Black} Book of Communism" is 8-61 million, 20 million approx under Jewish Lenin terror gangs funded by Max Warburg and other banking criminals since 1917\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small I'm Jewish and I'm DISGUSTED by this behavior. People only target Jews because they cry in the corner. Jew do \textbf{nothing}. If anything, the Israeli soldiers HELP the rest of the world. What about he Arabs who swear on the streets? What about everyone who has no respect WHATSOEVER for others? What about the criminals? The robbers? The kidnappers? There are so many more terrible people in the world to focus on more. People, it's 21th century. Finally, we have earned women's rights, like in Arab countries, woo men were recently let to drive. Why can't we achieve the same respect as everyone else gets?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/105 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small You're very smart for your \textbf{age}, if you want to learn more why don't you watch documentaries about the balfour declaration.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small So you think hate crimes and anti semetism is bogus? What if I said that islamophobia is bogus and that all Muslims are highly accepted and rose to high power? You'd probably say something different. While your not entirely wrong on the fact that Jews are accepted more, just remember all the various crimes committed. The Pittsburgh synagogue shooting, defaced Jewish cemetery's, violence in Europe towards Jews. You'd have to be \textbf{blind} to believe that anti semetism doesn't exist\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small \@David Nissim Trump is the latest In a long line of US presidents controlled by Israel. He is ready to spill more US blood for the \textbf{terrorist} state, but not his own family's\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@peter evans you are a \textbf{racist} piece of shit\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Logical Extreme you're the type of person that acts tough in a comment section but face-to-face you are \textbf{nothing} more than a coward\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@peter evans go away \textbf{Nazi} sympathizer\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@Eli Kaplan go back To the gas chamber fuck shit, \textbf{nobody} wants you, not the 108 countries atleast.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Luke M HAHAHAH omg ur so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Luke M ...you're a typical ignorant \textbf{nazi} dolt. Your \textbf{racism} and stupidity literally define you.\normalsize   & \cellcolor{green!5}Nazi, Racism & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest jews are incapable of love\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest read your talmud. That book is pure evil.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest I am not anti-Semitic nor do I hold any beliefs against Jews or 'hate them'.  However, I am against Zionism and the state of Israel and what they stand for.  Sorry I couldn't get back to you when you replied.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small \@Taha Hagar So you're going to judge all Jews by either the words of a few or your interpretation of centuries \textbf{old} texts? Maybe from something you googled? Everything on the internet is true you know. Lol. Maybe you figure that the words of a few represent the whole? Is it possible that you're only focusing on the bits and pieces that SEEM to support your preconceived beliefs? Maybe you need to study the true meanings of the scriptures before you spew hatred. I spent years trying to make sense of English text translated from centuries \textbf{old} Japanese text while learning the martial art I study. It just not that simple. Everything can't be taken literally. It's a different language from a different time. You need someone to teach you it's true meanings. You can't learn from Rabbi Google, just like I can't learn from Sensei Book. I wonder if there may be any similar negativity related to YOUR \textbf{race}, religion, country, beliefs, etc. Can I stereotype your entire group before I know the truth as well? Sure I could. But I wouldn't.\normalsize   & \cellcolor{green!5}Old, Race & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}3/183 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Lol more \textbf{mental} gymnastics, why dont you give up on your cognitive dissonance and realize that IsraHell is a jewish ultra-racial supremacist apartheid state where all non jews especially paledtinians are second class citizens.  [LINK] killing, ethnically cleansing, land grabbing, massacring, spying, assassinating, plotting coups and false flags, arming, funding and treating rebels and terrorists, bombing, occupying, discrimnating, brainwashing, besieging, invading, maming, burning, violating human rights, acumilating hundreds of UN resolution and condemnations by the International community, stockpiling hundreds of illegal weapons of mass destruction. Unless you condone these things, you have to stop defending this \textbf{terrorist} satanic state.\normalsize   & \cellcolor{green!27}Engineers, Mental, Terrorist & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!27}3/101 & \cellcolor{green!27}2.97 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest Question- Do you support the apertheid fascist policies of Israel? Do you hate Arabs and Muslims ?\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest Judaism is a \textbf{racist} religion. In Israel Jews are not allowed to marry gentiles. Death to Judaism and your Synagogue of Satan\normalsize   & \cellcolor{green!27}Engineers, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small .... and u cry out as u get bitchslapped by 3 year \textbf{old} girls ....\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest No you don't stop lying. They're all jews aka Semites. Your religion discourages people to convert to Judaism, not to mention to be a real Jew you have to born a Jew. \textbf{Racist} piece of shit, just look at Israel.\normalsize   & \cellcolor{green!27}Engineers, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@zyzz You are VERY wrong. Who or what told you this? Anyone at all can be a convert. As far as me being a \textbf{racist}, I have friends of several different races. You know \textbf{nothing} about me. Don't assume.\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@A British National Socialist Far from a snowflake\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@A British National Socialist I'm a veteran US Army Combat Engineer amongst other things. FAR from being a \textbf{snowflake}. But who am I to stop you from believing what makes you feel better?\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@A British National Socialist Yeah. Because \textbf{nobody} on the internet can be a Combat Engineer, right? Lol! Believe what you want to. I don't expect you to believe anything. It doesn't change the truth. Somebody has to be out there doing that job. We can't all be keyboard warfare specialists with the Comment \textbf{Engineers} like you.\normalsize   & \cellcolor{green!27}Engineers, Nobody & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}2/56 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@A British National Socialist ... those of on the right created the term "\textbf{snowflake}" to describe leftwing pansies like you who melt under the slightest amount of heat. Being a \textbf{communist} I'm sure you love your taxpayer funded council flat and 3rd world rated NHS.\normalsize   & \cellcolor{green!5}Communist, Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest ...nevermind the British \textbf{communist}. He's still upset the government wont give him more money for doing \textbf{nothing}.BTW...thanks for your service!\normalsize   & \cellcolor{green!27}Communist, Engineers, Nothing & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Nationality - General & \cellcolor{green!27}3/23 & \cellcolor{green!27}13.043 \\  \hline
  \cellcolor{green!5}\small \@A British National Socialist Yes. It is hate. I'm not \textbf{blind} at all. My eyes are open enough to see more than one side and more than what I choose to believe. But you're eyes are clearly clouded. You believe that the "white" \textbf{race} will become a minority? Even if it were true, what does it matter who is the minority or majority? Were all one \textbf{race}. Human. Our pride is our downfall. While you're fighting who you think is your enemy, our real enemies are walking right in on you. You're useless in our fight against our true enemies. Get behind us and we'll protect you. You'll still be alive and unaffected by your white genocide, lol. The world needs warriors to fight the real threats not worriers like you fighting perceived threats. Tje Jews aren't coming to get you and take over the world. Get off the YouTube videos and learn about true Judaism from someone qualified to teach you. Open your eyes wider.Liberal? I've never been a liberal.\normalsize   & \cellcolor{green!5}Blind, Race & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/172 & \cellcolor{green!5}1.744 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest  are Ethiopians semites?\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest  but there are Ethiopian jews and it says Ethiopian are semites  when i try to look it up .\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@zyzz Judaism has \textbf{nothing} to do with \textbf{race} you ignorant anti semitic shitwit.\normalsize   & \cellcolor{green!27}Nothing, Race & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Engineers} Quest the Romans "killed"  JC, not the Jews...Anyway, if you worship JC, then you're worshiping a Jew.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@Joel Weiner Obviously He's Jewish and the Romans killed him. But he isn't the false Messiah. \textbf{Nothing} wrong with Him being Jewish either.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Joel Weiner Jesus was a jew whom had a mother that cheated on a jewish man for a roman soldier. The couple lied about immaculate conception, because jews were suppose to only breed with themselves and the couple was afraid that she would be persecuted for her sins. And even though jesus's mother had cheated, the guy she was with loved her so much that he did not question or leave her rather supported her and stuck with her .  Jesus grew to be a respected scholar, but had turned his back on the jewish tribal ways and reached out to his enslaved brethren. He was out shining the king  ( Herod the Great) and because jesus was part roman and a sympathizer to people outside of his tribe, he was murdered for the kings insecurities and hatred towards people outside of his \textbf{race}. Jesus loved the kings enemies, because jesus had grew up a bit of an outsider because jesus was multiracial and thought differently . Jesus called himself "king of the jews" to the king himself and because jesus was half roman, the king took it as the highest insult. Because jesus was raised by the jews and then became to outshine the very people that raised him. In todays terms, Herod the Great was butthurt,insecure, insulted, and intimidated. The moment he called himself the king of the jews and was treating the people being oppressed as one of his own, the king viewed him as a threat and infiltrator. And if it does not go that way, it goes the opposite way and pontius pilate killed him for the same reasoning . He was murdered for not having the ability to be loyal to one side or the other, rather created his own path and rule and the other leaders did not know how to handle it.Or if you are a harry potter fan, he was an outsider and hated for being a "mudblood", just like harry.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/331 & \cellcolor{green!5}0.302 \\  \hline
  \cellcolor{green!27}\small Not sure but would this maybe  cover 80  of th so called \textbf{spike}? [LINK] \normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small The Talmud did this this. Absolutely disgusting.Yebamoth 63a. States that Adam had \textbf{sexual} intercourse with all the animals in the Garden of Eden.Yebamoth 63a. Declares that agriculture is the lowest of occupations.Sanhedrin 55b. A Jew may marry a three year \textbf{old} girl (specifically, three years "and a day" \textbf{old}).Sanhedrin 54b. A Jew may have \textbf{sex} with a child as long as the child is less than nine years \textbf{old}.Kethuboth 11b. "When a grown-up man has intercourse with a little girl it is \textbf{nothing}."Yebamoth 59b. A \textbf{woman} who had intercourse with a beast is eligible to marry a Jewish priest. A \textbf{woman} who has \textbf{sex} with a demon is also eligible to marry a Jewish priest.Abodah Zarah 17a. States that there is not a whore in the world that the Talmudic sage Rabbi Eleazar has not had \textbf{sex} with. On one of his whorehouse romps, Rabbi Eleazar leanred that there was one particular prostitute residing in a whorehouse near the sea, who would receive a bag of money for her services. He took a bag of money and went to her, crossing seven rivers to do so. During their intercourse the prostitute farted. After this the whore told Rabbi Eleazar: "Just as this gas will never return to my anus, Rabbi Eleazar will never get to heaven."Hagigah 27a. States that no rabbi can ever go to hell.Baba Mezia 59b. A rabbi debates God and defeats Him. God admits the rabbi won the debate.Gittin 70a. The Rabbis taught: "On coming from a privy (outdoor toilet) a man should not have \textbf{sexual} intercourse till he has waited long enough to walk half a mile, because the demon of the privy is with him for that time; if he does, his children will be epileptic."Gittin 69b. To heal the disease of pleurisy ("catarrh") a Jew should "take the excrement of a white dog and knead it with balsam, but if he can possibly avoid it he should not eat the dog's excrement as it loosens the limbs."Pesahim 111a. It is forbidden for dogs, women or palm trees to pass between two men, nor may others walk between dogs, women or palm trees. Special dangers are involved if the women are menstruating or sitting at a crossroads.Menahoth 43b-44a. A Jewish man is obligated to say the following prayer every day: Thank you God for not making me a gentile, a \textbf{woman} or a slave\normalsize   & \cellcolor{green!5}Nothing, Old, Sex, Sexual, Woman & \cellcolor{green!5}Age - Over 65s, Age - Youngsters, Gender - General & \cellcolor{green!5}12/412 & \cellcolor{green!5}2.913 \\  \hline
  \cellcolor{green!27}\small Just read a passage from their Talmud. They are deviant, disgusting perverted, \textbf{racist} narcissists. Yebamoth 63a. States that Adam had \textbf{sexual} intercourse with all the animals in the Garden of Eden.Yebamoth 63a. Declares that agriculture is the lowest of occupations.Sanhedrin 55b. A Jew may marry a three year \textbf{old} girl (specifically, three years "and a day" \textbf{old}).Sanhedrin 54b. A Jew may have \textbf{sex} with a child as long as the child is less than nine years \textbf{old}.Kethuboth 11b. "When a grown-up man has intercourse with a little girl it is \textbf{nothing}."Yebamoth 59b. A \textbf{woman} who had intercourse with a beast is eligible to marry a Jewish priest. A \textbf{woman} who has \textbf{sex} with a demon is also eligible to marry a Jewish priest.Abodah Zarah 17a. States that there is not a whore in the world that the Talmudic sage Rabbi Eleazar has not had \textbf{sex} with. On one of his whorehouse romps, Rabbi Eleazar leanred that there was one particular prostitute residing in a whorehouse near the sea, who would receive a bag of money for her services. He took a bag of money and went to her, crossing seven rivers to do so. During their intercourse the prostitute farted. After this the whore told Rabbi Eleazar: "Just as this gas will never return to my anus, Rabbi Eleazar will never get to heaven."Hagigah 27a. States that no rabbi can ever go to hell.Baba Mezia 59b. A rabbi debates God and defeats Him. God admits the rabbi won the debate.Gittin 70a. The Rabbis taught: "On coming from a privy (outdoor toilet) a man should not have \textbf{sexual} intercourse till he has waited long enough to walk half a mile, because the demon of the privy is with him for that time; if he does, his children will be epileptic."Gittin 69b. To heal the disease of pleurisy ("catarrh") a Jew should "take the excrement of a white dog and knead it with balsam, but if he can possibly avoid it he should not eat the dog's excrement as it loosens the limbs."Pesahim 111a. It is forbidden for dogs, women or palm trees to pass between two men, nor may others walk between dogs, women or palm trees. Special dangers are involved if the women are menstruating or sitting at a crossroads.Menahoth 43b-44a. A Jewish man is obligated to say the following prayer every day: Thank you God for not making me a gentile, a \textbf{woman} or a slave\normalsize   & \cellcolor{green!27}Nothing, Old, Racist, Sex, Sexual, Woman & \cellcolor{green!27}Age - Over 65s, Age - Youngsters, Ethnicity - General, Gender - General & \cellcolor{green!27}13/419 & \cellcolor{green!27}3.103 \\  \hline
  \cellcolor{green!5}\small \@kimex gamer tell that to the hundreds of millions killed by jews.....In the \textbf{Communist} holodomores, the Armenian Genocides, and the Atlantic Slave Trade...........Just the facts bro......Facts are it is what it is......The \textbf{Communist} Government was 85 Jewish and they were financed by the Bolsheviks in New York City.....People that speak truth are called AntiSemitic.....The reason they were kicked out of 109 countries is for doing to other countries, what they have done to the US....UK,...and....Europe,.......The Globalist Jews push vaccines, GMOs, Mass Immigration, Open Borders, and Communism etc, etc ,etc..........Facts\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/89 & \cellcolor{green!5}2.247 \\  \hline
  \cellcolor{green!27}\small Who cares? All I ever hear is boohoo the white man did this and boohoo the white man did that. Ok to all blacks who read this. ->White people don't owe y'all shit, for one I ain't never owned a slave in my lifetime. Two; Welfare, EBT-SNAP, etc. No matter how much free money and shit y'all mooch off the white man y'all will never be satisfied. Real talk, if anything y'all should be thanking us not crying and bitching about slavery and all that nonsense. Think about it. If it wasn't for white people y'all would still be in Africa dying of aids. Bunch of ungrateful bastards. Hispanics, stop coming to America to mooch off the white man. We don't need not want y'all here. If y'all keep flooding our cities and states with your pathetic existence then eventually there will be a cut in Government Assistance and that would ultimately lead to the blacks declaring war on y'all for cutting into their crybaby money. Muslims, y'all suck too and Allah loves Ham, Bacon, Sausage, Pork Chops, Pickled \textbf{Pigs} Feet etc. And for the Jews, y'all are outright evil. Y'all invade any Country that white people civilize and y'all open up abortion clinics everywhere y'all don't get ran off from because y'all are baby killers, the rabbi circumcises Jewish babies by biting the foreskin off and then for several minutes sucks blood from the baby's genitalia in most cases giving the little Jew some STD's and y'all do multiple other satanic rituals in the synagogue of Satan.\normalsize   & \cellcolor{green!27}PIGS & \cellcolor{green!27}Nationality - Southern European & \cellcolor{green!27}1/258 & \cellcolor{green!27}0.388 \\  \hline
  \cellcolor{green!5}\small It seems to me   that a lot of these ANTI SEMITES  are coming from the \textbf{NEGRO} population  ?? I thought Negroes  were perfect  and didn't   get  involved  in HATE  \textbf{RACISM} /Bigotry ??It seems that this Anti semitism HATE   is being taught  in schools  of higher education  and allowed by the mains street media ??  We all know that  Muslims HATE  Jews   and that  NEGROES  matriculate   towards ISLAM  ?We will have to be more watch full  in the future  ???\normalsize   & \cellcolor{green!5}Negro, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/81 & \cellcolor{green!5}2.469 \\  \hline
  \cellcolor{green!27}\small its a crime punishable by death to deny \textbf{fritz} habers final solution for non jews:)-wtf is a semite a turd?\normalsize   & \cellcolor{green!27}Fritz & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small What a joke... CNN pushing their \textbf{racism} loving leftist agenda. This is the left doing this shit. ALL set up by democrats. \textbf{Racism} is almost non existent in this country. But the left needs you to think otherwise. ANYTHING from the ADL or SPLC is BULLSHIT. Its portably other jews spraying swazis everywhere.  They LOVE being "victims".  ANY of this that IS real is because of the left acting the way they do. Without \textbf{racism} the left has \textbf{nothing}. Its their baby.\normalsize   & \cellcolor{green!5}Nothing, Racism & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}4/82 & \cellcolor{green!5}4.878 \\  \hline
  \cellcolor{green!27}\small I think we can all agree that CNN and other FAKE NEWS is 100 percent responsible for antisemitism. Start sharing the entire story CNN. Why don't you share the leftist college who has invited an Islamic speaker who says: "Jews \& Christians are filthy, their lives \& property can be taken in jihad by the Muslims." (including women as \textbf{sex} slaves)Anti-Semitic Speaker Invited to Orlando's Valencia College Wake up people. This is what Fake News has you supporting! They don't tell the whole story. This is what CNN won't tell you, while you vote for our nation's demise. Wake up, Walk away!\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small Those \textbf{Nazi} bastards deserved to be hung burned and torn to shreds EVERY. SINGLE. ONE. There is no such thing as a good nazi\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Anti \textbf{Nazi}Anti PalestineAnti IranPro Israel Jews\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Jews are the originators of \textbf{racism} \& discrimination and yet cry aloud about anti-semitism. For example, in the Babylonian Talmud take note of what is written about negroes: Ham is told by his outraged father that, because you have abused me in the darkness of the night, your children shall be born \textbf{black} and ugly; because you have twisted your head to cause me embarrassment, they shall have kinky hair and \textbf{r\textbf{ed}} eyes; because your lips jested at my expense, theirs shall swell; and because you neglected my nakedness, they shall go naked" (page 81).\normalsize   & \cellcolor{green!5}Black, Racism, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/95 & \cellcolor{green!5}4.211 \\  \hline
  \cellcolor{green!27}\small I conceal carry my 9mm in case I run into one of these Inbred \textbf{racist} maggots, have no problem exterminating a maggot, its as easy as stepping on a Cockroach\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small They caught the \textbf{NAZI} Graffiti Criminal. Hes \textbf{Black} and a Democrat. >Graffiti Culprit Caught! It's Not Who'd You Expect   [LINK] You wouldnt know this when CNN reported since FAKE NEWS CNN never mentioned in their story\normalsize   & \cellcolor{green!5}Black, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small I am just in disbelief that the media portray the right as hating Jews, it's the anti capitalist Democrats that constantly beat the drum against the rich Jews.  It has always been the party of hate, it was the Democrats that hated blacks.  Just too many sheep in the US, 10 of millions imported for their vote instead of their intelligence.  More sheep to feed the propaganda.  So sad the state of the Democratic Party.  The Democrats are the party of 1. Violence, 2. Limiting freespeech, 3. The party of fascism, 4. The party of propaganda, 5. The party of ifyou're a Republican, or a white male you are guilty until proven innocent, 6.The party with the lower average IQ. 7. The party of hate (including \textbf{racism}).  This is beyond cavil.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/134 & \cellcolor{green!27}0.746 \\  \hline
  \cellcolor{green!5}\small \@cinegraphics ...you're as bad as any \textbf{Nazi} is\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@cinegraphics ...not even a logical arguement. Most Jews and Christians ARE Zionists and despise all forms of anti Semitism like the veiled shit you're peddling.You seem more like a \textbf{Nazi} than anyone on this thread\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Am I anti-Semitic; no, I like the Palestinians. "Pimp-Daddy Trump" pledged 100 support for Israel, leaving 0 for Trump supporters, leaving them betrayed and not being able to handle the rejection; oh yes, they still rally around him, out of ignorance I suppose? Now-days, most \textbf{common} are women who stay with an abusive spouse or a pimp, and Trump supporters who struggle with reality…and CNN who doesn't like the truth any more than government likes the truth.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}\small The funny thing is, this study doesn't show an increase in anti-semitic incidents at all. It actually shows a 46 decrease. CNN is counting on the likelihood that none of their viewers will actually read the study. The INCREASE has \textbf{nothing} to do with actual or reported incidents, it's about "perceived" anti-semitism. They are counting thinks like a Jewish person being given what they percieve as bad service at a restaurant as anti-semitism. And they failed to remove the falsely reported incidents where Jews were caught perpetuating hoaxes. In other words, this is fake news.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/95 & \cellcolor{green!27}1.053 \\  \hline
  \cellcolor{green!5}\small haha this. bitch dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small fuck all these people . \textbf{nobody} gives a flyin fuck about them. that's the reason Jentiles never be apart of God. all they know is hate and destruction. \textbf{nothing} more\normalsize   & \cellcolor{green!27}Nobody, Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small more important than the imaginary \textbf{nazi} epidemic is the real criminal cowardly stench of lying leftist trash and their 'protected' exploitation of the us constitution law and americas freedoms and responsibilities. they rely on their disgusting anti american dishonesty to excuse their illegal interference and they will regret such warped cowardly corrupt dishonest ways. lying and denying is their work, when not stealing stinking stalking hacking cheating suckerpunching sabotaging and worse.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small spike reported by the Jewish media\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small In the future they should put each \textbf{race} on their own planet\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Maybe it's the hate and lies being vomited out by the leftist media and leftist \textbf{communist} groups around the country. That's it for sure.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small CNN has lost their minds. Don Lemon said the most disgusting \textbf{racist} garbage I've ever heard in my life. CNN all you do is fill people with hate. I've come to realize CNN that's your Job, fill everyone with hate. I don't know how anyone supports a network that employes someone like Don Lemon that spews disgusting \textbf{racist} crap. CNN MUST FIRE DON LEMON. MUST!!!BTW I've never met a \textbf{nazi} in my life but according to CNN they're everywhere.\normalsize   & \cellcolor{green!5}Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}3/80 & \cellcolor{green!5}3.75 \\  \hline
  \cellcolor{green!27}\small Kevin Caleb dumbass overkill. 'i've never met a \textbf{Nazi} so they aren't around anymore'. Meanwhile the FBI and Department of Homeland Security repeatedly report that white supremacist terrorism is the 1 threat of domestic terrorism in this country.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@Rat Bat Nuff Time ...still haven't seen an intelligent reply from you. Unlike Don Lemon Hannity always speaks the truth. And unlike Lemon he'd be fired if he lied like CNN and MSNBC anchors regularly do.BTW...wasn't it Don Lemon who theorized on HIS own show that Malaysia Air flight 370 might have disappeared in some sort of \textbf{black} hole like on the show "Lost"? LMFAO... [LINK] \normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}\small \@Jack Wertz Hannity's a \textbf{racist} pig.........just like you. You really want to re-hash history again to see if you can moralise and normalise the entitled, genocidal psychosis of you and your ancestors??? Not with me. Find a lesser mortal within your echo chamber or with a Hebrew Israelite and have fun. Good day.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small \@Rat Bat Nuff Time ...dude, seriously. Link to ANYTHING \textbf{racist} that Hannity either said or did. I'll be waiting for your shitwitted response.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small \@Rat Bat Nuff Time ...BTW, Hannity is a 20+ year member of the NAACP. Yeah, sounds like a real \textbf{racist} to me.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Rat Bat Nuff Time ...tell me how I'm \textbf{racist}?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Anti-semitism is the only logical response to the Supremacist and \textbf{Racist} religion of judaism.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Yes CNN, blame it on Trump. Like it's Trump who said that all \textbf{black} people look the same... so pathetic...\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Breaking news a dramatic \textbf{spike} in Jews controling the media to destroy America from within.(Jeff Zucker) these people are very dangerous\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small If you're not white or Jewish. Your death doesn't matter. Which is worst anti semitism or \textbf{racism} yet anti semitism is spoken about cause most Jews are white lol. Go ahead.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small Would it be fair to drag forward the bits of the church who instigated the atrocities of the Inquisition, which included torture and maiming of people based on \textbf{nothing} other than not being Christian, and claim that they represent Christian Values? How about the Catholic priests who touch little boys - is it fair to say these are the truest representatives of Christendom?Do any of your sources on it include actual rabbis who write for popular sites like Aish, or only Stormfront preachers who pick out the nastiest bits of the worst rabbis in history and wave them around like flags so they can point YOU like a weapon?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}\small 99.99 white people on the Right think \textbf{Nazi} are fucking idiots ,00.01 of whites who think Nazis are good are the \textbf{dumb} people , because you are on Right it don't make you \textbf{racist} , anti Semitic is evil , I hope this \textbf{Nazi} dick get the death pen ,,,,,,\normalsize   & \cellcolor{green!5}Dumb, Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/50 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@cinegraphics Shut your \textbf{racist} mouth up. You ignorant grott.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@3ds max ...you being an anti semitic \textbf{nazi} are just as bad at CNN\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Jack Wertz I'm a \textbf{Nazi}?  Yep.....go right for the standard insults: \textbf{Racist}, \textbf{nazi}, white supremacist etc. Don't debate with facts....juts insult me! Typical liberal response every time! Is that you Fredo? LOL!\normalsize   & \cellcolor{green!27}Nazi, Racist & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!27}3/32 & \cellcolor{green!27}9.375 \\  \hline
  \cellcolor{green!5}\small \@3ds max ...you use an anti Jewish caricature as your profile picture. Yes, you're a \textbf{nazi}!\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@3ds max ...and for the record I hate liberals as much as I hate Nazi's like you. \textbf{Dumb} fucking anti semitic moron\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@The Law You know \textbf{nothing} about Jews other than what you choose to learn.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I wonder what this whole thing is all about.As someone who believes in nihilism as seen in the attached link, I have always wondered about the monolithic nature of Christianity in the US, why were are given so little information about Naziism as a belief, and why so many societies have persecuted Jews for 'Trying to  dominate the planet.'In my 40 years of natural observation on this Earth, I have a theory that would, in the best case, make a great movie.The Christian religion as it is practiced by some factions in the US is a front, like a mafiaman would own a laundry mat or a coffee shop.I understand that this has been the idea behind why peoples of various nations around the world have persecuted the Jews over time. They felt that Jews are 'up to no good,' because of the money they control that could be a product of living a moral life, but probably has more to do with organizational connection.The biggest difference between pre-WW2 Jews and US Christians is that the US Christians of today don't only own coffee shops but have a more heavy influence on International markets because of globalism and the virality of US brands.It freaks me out that the monolithic Christian establishment in the US has so much influence in our government.The US Government has the largest nuclear arsenal on the planet.Years back, around the First Gulf War, there was a news report that I remember seeing that said the CIA thwarted an INTERNATIONAL CHRISTIAN \textbf{TERRORIST} GROUP from committing several simultaneous \textbf{terrorist} attacks internationally, as a means of bringing on 'The Second Coming of Jesus Christ.'In the same way, I sometimes wonder if Nazis are the missing resistance army in my theory. That which is demonized by the government that said, 'Good idea,' to the whole world domination, purist ideologies of all 3, Jew, Christian, and \textbf{Nazi}, is a little package called MANIFEST DESTINY...Let me be clear, I am not a \textbf{Nazi} or affiliated to ANY religious or political party.See, as we enter this era of global warming, we as people and those among us who are addicted to the idea of having more money than anybody else, are panicking for a new renewable source of energy.Ever seen the movie the Matrix?Humans are renewable energy personified, when we live in step with nature, we ourselves are 'renewable.'And slavery is a valid renewable economy construct.Are you seeing the dots connecting? I hope so.The only question I have in my mind anymore is:Is it the religious ones that are bad, or are they also just a front for their boss, their respective governments around the world?Regardless of who's to blame or why they are doing it, it is most interesting to see how all of this plays out.Will positivity, bravery, and human ingenuity birth a sustainable economy, devoid of slavery?Or will negativity, cowardice, and anachronism take us back to slavery?Maybe that IS 'THE GREAT EXPERIMENT.'Maybe this has happened many times already, maybe it hasn't, but regardless of what you believe, it's a cool story, the best theory I know as to WHY all this crap is happening, and what we can do to make the world a better place regardless...Yep, yep ☺︎Nihilism, its not a religion its philosophy. [LINK] \normalsize   & \cellcolor{green!27}Nazi, Terrorist & \cellcolor{green!27} Ideological and Political Identity - General, Religious Identity - Muslim & \cellcolor{green!27}4/570 & \cellcolor{green!27}0.702 \\  \hline
  \cellcolor{green!5}\small Must say this the Minister never spewed hatred to \textbf{black} people that made us go kill whites he EDUCATED us to hold ourselves up to a higher standard as a broken people. So he does not deserve to be included in the same category as white supremacists.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}\small White \textbf{racist} are coming out and up because they been planning this while the rest of us have been playing games and holding hands while gossiping about our neighbor's and spewing our own hatred.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}\small I'm proud to be an American...cause at least I know I'm free....to be a \textbf{dumb} cunt\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The full spectrum bigot Trump is who he says he is:a Nationalist, and he is NOT, through purpose or ignorance, the arbiter of it's universally understood actual political meaning; Self Proclaimed Nationalist Herr Trump; a1930, noun and adjective, from German \textbf{Nazi}, abbreviation of German pronunciation of Nationalsozialist (based on earlier German sozi, popular abbreviation of "socialist"), from Nationalsozialistische Deutsche Arbeiterpartei "National Socialist German Workers' Party," led by Hitler from 1920.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}\small They really started paying attention to the issue again and now calling it a \textbf{spike}? I'm betting Trumps getting blame for others bs again? These media giants associated with the world bank other branches are seriously worried, clearly.With him trying to remove the hook out of the peoples mouth with this mandated citizenship, they're really steamed.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small don't like the way they dragged Farrakhan in there to act like this issue isn't caused by white people when actually it is! Farrakhan has been around since way before 2016 so this \textbf{spike} in anti-semitic incidents is clearly because of one thing and that isn't Louis Farrakhan - SMH - guess they looked in the mirror and didn't quite like what was looking back\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small If so, we're apparently doing a shit job of it, because people still hate us and wants to kill us. I tried so fucking long to understand what we were doing wrong, What I could do different, now I know there's \textbf{nothing} we can do - you hate us if we're rich or poor, integrated or separate, white or \textbf{black}, whatever. You just hate us.\normalsize   & \cellcolor{green!5}Black, Nothing & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/65 & \cellcolor{green!5}3.077 \\  \hline
  \cellcolor{green!27}\small Why is there no coverage of Hillary Clinton Booker Holder comment "they look the same"... cover this \textbf{racist} cnn\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Perfectly Imperfect They've been caught doing that many times over the years.  Every single time, when they're caught, the media says they need help for their \textbf{mental} illness.What they're doing is trying to cause racial and \textbf{ethnic} violence.\normalsize   & \cellcolor{green!5}Ethnic, Mental & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@Sam Vimes Not only that, many if not all \textbf{black} symbols of hate are done by.....wait for it........blacks! White supremacy is so prevalent jews and blacks have to fake hate crimes against themselves LOL!!!  Smollett anyone?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Sam Vimes the \textbf{black} people are just an example and Israelis aren't necessarily Jewish\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@3ds max The demand for \textbf{racism} far exceeds the supply it seems.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small CNN won't report on the daily \textbf{black} on white murders, assaults and rapes -- go to new \textbf{nation} \textbf{dot} org for proof\normalsize   & \cellcolor{green!5}Black, Dot, Nation & \cellcolor{green!5}Ethnicity - Asian (South- India, Pakistan, Bangladesh), Ethnicity - Black, Nationality - General & \cellcolor{green!5}3/22 & \cellcolor{green!5}13.636 \\  \hline
  \cellcolor{green!27}\small Maybe cnn should pay the \textbf{Nation} of Islam a visit. Just 2 weeks ago Farrakhan called Jews Termites. SMH....selective outrage for Politics. Lets not forget Linda Sarsour whom is no fan of Jews either with her constant support of Hamas.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small This very irresponsible Trump reaps what he sows with his glorification of weapons, his \textbf{racism} and his sneaky antisemitism.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small How is it that the GOP can both support Israel and hate Jews?Are they really that \textbf{blind} to that large of a hypocrisy?\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "Leadership:  Whatever happens, you're responsible.  If it doesn't happen, you're responsible."DJT - 11/18/13. 1:01PMThat tweet didn't \textbf{age} well, did it you hypocrite piece of shit.\normalsize   & \cellcolor{green!5}Age & \cellcolor{green!5}Age - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small COMMUNIST LIES \& \textbf{COMMUNIST} BS! 95 of the self-proclaimed Chosen People in the USA are non-Semite Khazars fraudulently posing as Semites. God's Chosen People are the SEED of Abraham through Isaac (Genesis 12:7).  Less than 2 or modern Israel has Semite DNA!   [LINK] \normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small Ok I'm a republican but these guys are not republican there the \textbf{nazi} party boys so let's all get ready see y'all in cod ww2 and bf5\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@Seleteles Yep. I think additional ways of asking the question is: Why would American Jews support a Jewish supremacist state? Why would American Jews support a state that attacks its neighbors, steals and then occupies their land for sixty years, and then acts like it's the victim? Why would American Jewish organizations except for Jewish Voice for Peace and HIAS decide to collaborate with anti-semitic Evangelical groups here in the US, and oppose \textbf{Black} Lives Matter, instead of the other way around? Why would groups like the Anti-Defamation League sponsor trips for American police to train in Tel Aviv and then, like the Ferguson police, return to the US and gun down \textbf{black} people? Don't these policies show a consistent pattern of making the US more dangerous, Israel more dangerous and the middle east more dangerous?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/136 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small He Needs Be Put In Electric Chair Burn His \textbf{nazi} Ass 💀♨♨  You Have Been Replaced By Humanity!!!   Nazis will never win over Right  ♨ burn in Hell .\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Rion sure \textbf{ho} ✡️✡️i stan with jews\normalsize   & \cellcolor{green!27}Ho & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small What happens to Jared Kutchner and Steven who are both Jews when they are spewing white supremacy, where are the terms for Jews who incite \textbf{racist} propaganda on everyone else?Jews who are in the White House.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small \@Micdhael Masink bring it on trailer park.  Please, be the first \textbf{Nazi} at my front door.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Trumps daughter in law is jewish. he has done more to strengthen ties with israel than any other president in a long time, he is not anti semitic, and also CNN fake news. the "\textbf{nazi}" symbol you have in your thumbnail is backwards no self respecting \textbf{nazi} would paint it that way. fake news all the way. Trump didnt create this, trump brought up an illegal immigration issue that YOU CNN turned into an argument for \textbf{racism} by omitting the fact that he said mexico was sending drugs and MS-13 gang members - you intentionally headlined with "trump said immigrants are criminals"  YOU CNN are responsible for the rise in hatred in this country not trump.\normalsize   & \cellcolor{green!5}Nazi, Racism & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}3/116 & \cellcolor{green!5}2.586 \\  \hline
  \cellcolor{green!27}\small CNN is \textbf{racist} you don't hear \textbf{nothing} about \textbf{black} family's on the news they just report on other races they are the divider of fake news\normalsize   & \cellcolor{green!27}Black, Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/26 & \cellcolor{green!27}11.538 \\  \hline
  \cellcolor{green!5}\small I like how 11 is supposed to be a high number and it's 2018 and we are talking about Americas history of mistreating Jews...So it took 525 years for a white guy to kill 11 of these much hated ...'jews'... at the same time...am I missing something?These people are acting like this is the most people that have died at one time by a white supremacist...this is silly...Don't ever make a fucking graphic and then have some \textbf{old} \textbf{woman} talk about how Jews have been treated in this country...fucking pathetic...YOU PEOPLE HAVE NOT EXPERIENCED SHIT HERE...lick my balls.\normalsize   & \cellcolor{green!5}Old, Woman & \cellcolor{green!5}Age - Over 65s, Gender - General & \cellcolor{green!5}2/102 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small 11? And we are bringing up the History of the treatment of jews  IN AMERICA...wow. That's a lot for one time... and this was the first 11 at once in America, huh? They used to fucking hang \textbf{black} people at picnics...when a white person Dylan roof kills \textbf{black} people in hopes of starting a \textbf{race} war, do they bring up the history of how they have treated blacks?Yeah, fuck y'all.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/71 & \cellcolor{green!27}4.225 \\  \hline
  \cellcolor{green!5}\small Not true at all...most of middle America is made of conservative Christians who support Israel and Jewish people alike.The anti-Semitic \textbf{racist} cowards make up a fraction of a fraction of the US population.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@FREEDOMFIGHTER47 ...you're a \textbf{racist} fucking coward.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Swastikas has been band in Germany. So \textbf{Nazi} groups in Germany is now using the Confederate flag as their symbol. We're now exporting our hate and \textbf{racism} around the world.\normalsize   & \cellcolor{green!5}Nazi, Racism & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small * RUSSIA HAS ALWAYS WANTED TO  COME AND MOVE IN CONTROL ON U.S GOVERNMENT AND TRUMP IS DELIVERING HIS PROMISE , THIS PEOPLE ARE NOT FUCKN PLAYING !!!!* Russia can't move there operations in if the country unit's in numbers . that's why trump is hard on that dam boarder , because also Mexico will come an add to the complications of the \textbf{transition} there chances are better with the boarder completely locked down an the inside of the country is completely in division , and soon as a inside war begins within the country the countries that have been watching an waiting is definitely going to began there waves of attacks , these countries are coming soon as they see that the inside of the country is in a full-blown massive war . TRUMP IS SPARKING SOMETHING THAT HAS NEVER BEEN DONE BEFORE , A \textbf{RACE} WAR SPARKED FOR political power . this is an will be the last war of all civilization here in U.S soil  . this will be what sparked WW3 . Trust an believe U.S will not over come this move if y'all let trump set this war off an they slide that bitch muthufucku out an away . y'all better stop an get fuckn smart . ain't that much fuckn protection once y'all know what the fuck trump is doing to the country .\normalsize   & \cellcolor{green!27}Race, Transition & \cellcolor{green!27}Ethnicity - General, Sexual Identity - Transexuality & \cellcolor{green!27}2/230 & \cellcolor{green!27}0.87 \\  \hline
  \cellcolor{green!5}\small Jewish supremacy, be it traditional Judaism or \textbf{racist} Zionism, contributes to anti-Jewish sentiment and breeds White supremacy.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Identification with any religion, philosophy, ideology, \textbf{race}, \textbf{nation}, etc., invents the illusion of division and separation, which breeds conflict, violence, and suffering. As long as this illusion persists, there is no Love, no Peace, no Joy, no Kindness, no Goodness, no Compassion (Passion for All), no Beauty, no Creativity, no Feeling, no ExperiencING, no Lucidity, no Truth, no Wisdom, no Freedom, no Communication, no Communion, no Relationship with anyone or anything in daily life...none whatsoever. Only their limitations and imitations.\normalsize   & \cellcolor{green!27}Nation, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/80 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Well it is left who places \textbf{Race} in front of everything else.It is never John and Terry but a white man and a \textbf{black} man.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Tee Jay there's \textbf{nothing} about A few random Jews dying that are in any prophecy. Why are blacks always so stupid?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Seriously people, we're not in the 20th century no more. World War 2 is over, the Nazis are dead, so should be the KKK, and the Confederate Flag should be burned. The Confederates lost during the Civil War, get over it people! Quit living in the past, we are all human beings, no one is the same, we all are different in our own special ways. But y'all need to understand the difference between right and wrong. Get some \textbf{common} sense.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small Ever wonder why the mainstream media is so against this Administration?  Although CNN was probably too new to be rated they probably fall in this group now. In their 1986 book, The Media Elite, political scientists S. Robert Lichter, Stanley Rothman and Linda S. Lichter reported the results of their survey of 240 journalists at the nation's top media outlets: \textbf{ABC}, CBS, NBC, PBS, the New York Times, Washington Post, Wall Street Journal, Time, Newsweek and U.S. News \& World Report. When asked about their voting patterns, journalists admitted their preference for Democrats. Lichter's team focused on journalists at the very top news organizations. Other surveys of journalists have discovered that the whole profession shares the same liberal view, although the media elite's liberalism is the most extreme. While accepting an award from the World Federalist Movement, Walter Cronkite called for a Democratic World Government. Walter Cronkite was a pioneer for the new mainstream media, Don't you think?\normalsize   & \cellcolor{green!27}ABC & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/158 & \cellcolor{green!27}0.633 \\  \hline
  \cellcolor{green!5}\small Why is this happening we have a president spewing hate His supporters are \textbf{racist} just go to one of his \textbf{Nazi} rallies\normalsize   & \cellcolor{green!5}Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small The shooter was a democrat \textbf{nothing} new here\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Btw Trump loves Jews that's why this guy hated Trump.. So maybe get your \textbf{libtard} head out of your ass?\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Just to have a word on what the \textbf{bald} guy says... When the jews are targeted,  \textbf{zero} tolerance... But when muslims are... "Meh, just another day in the land of freedom"?Belligerent and dangerous rhetoric should be called out ALL the time.\normalsize   & \cellcolor{green!27}Bald, Zero & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical Features & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Fake news Jews are \textbf{black} not white!! JESUS WAS A \textbf{BLACK} MAN\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small so sad  Democrats have \textbf{nothing} to run on   gun grabbing open border illegals voting felons voting more taxes more regulations job killing Democrat policies. that's all\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small White \textbf{nationalism} is being sponsored by the president of the United States. And the Republican Party doesn't care because he's helping their agenda.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Can't you just say Nazis are bad... Think of the Normandy beach and D-Day and those soldiers who are hard as fuck compared to Americans nowadays because who the hell would want to do that...Thousands of Americans died to fight \textbf{Nazi} ideals and motions...  But these groups have always been in America since the war then and now... well here America is divided as ever so who cares about the fake news whichever network you listen to is your choice. It's the battle between PC culture vs. rich/poor white guys who love Jesus and the color of their skin.  So the middle moderate person are the ones who need to rise and relinquish these \textbf{crazy} motions of the extreme left college white people who \textbf{nobody} likes vs. the extreme right rich white  people who don't care about anybody. And yes they are all white people. Scary rhetoric or not, "Actions speak louder than words"-Abraham Lincoln. Trump has the words, but he really is one giant \textbf{pussy}. You all know it\normalsize   & \cellcolor{green!27}Crazy, Nazi, Nobody, pussy & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters, Nationality - Chinese, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/170 & \cellcolor{green!27}2.353 \\  \hline
  \cellcolor{green!5}\small What, \textbf{racism} in America? what else is new better yet what has really changed in 200+yrs\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small SOROS was a \textbf{Nazi}(probably still is)...KKK formed by Democrats and still remains so...Leftist MSM are lying bastards for the hope of destroying America tor a NWO of Socialism...American Patriots will destroy all of them for the Republic for which WE stand...Pack your shit, the \textbf{R\textbf{ed}} Wave is coming...\normalsize   & \cellcolor{green!27}Nazi, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}3/48 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Racism sadly will never go away, but liberals and Dems sorta sponsor it with BLM and  the illegals.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small My mother and father fought against \textbf{Nazi} Germany in WW II.  Those symbols mean only one thing and that's hate. Lots of people gave their lives as allies to defeat that \textbf{Nazi} regime. Post WW ll  Germany has recognised this and taught the lessons learned by a horrific war to their people. They took responsibility for it and I admire them for that. And I bear no ill will  towards them and latter generations are not at all responsible. Pure hate and \textbf{racism} are taught not learned.  Don't know what's wrong with  all these haters except hate. And they've been riled up no matter what anyone says. Crowd mentality takes over and it's easy to push buttons with the right rhetoric and this is what happens and has happened. I wouldn't desecrate anyone's grave regardless of who they are, that's beyond sanity and it's just pure unadulterated hate. Think your religious, think again because your not regardless of your supposed religious screwed belief.\normalsize   & \cellcolor{green!27}Nazi, Racism & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!27}3/163 & \cellcolor{green!27}1.84 \\  \hline
  \cellcolor{green!5}\small I'm from Pittsburgh . The president has absolutely \textbf{nothing} to do with some psychopath killing a bunch of innocent people . And I think CNN it's fucking disgusting for trying to imply that\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small a \textbf{migrant} was shot at the mexico guatemala border, why are you not covering this?\normalsize   & \cellcolor{green!27}Migrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Jews voted for Trump because he supported Jerusalem as the capital of Israel. They knew what they were getting into. Antisemitism is higher than Anti Muslim in America. Hate groups hate Jews more than Blacks, Mexicans, Muslims \& the \textbf{L\textbf{G\textbf{BT}}} community. If you voted for somebody who doesn't disown hate groups or prosecutes hate crimes, you get what you deserve.\normalsize   & \cellcolor{green!5}LGBT & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}3/60 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Trump is Making the white Supremacist do \textbf{crazy} things!! We should have a \textbf{zero} tolerance policy for blacks being killed.\normalsize   & \cellcolor{green!27}Crazy, Zero & \cellcolor{green!27}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small *Soloyea, sure.  Trump has a hot line to \textbf{Nazi} headquarters and sends them orders.  too much Kool-Aid for you.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Lies lies lies from this Babylonian  whore anchor media  \textbf{woman} scare of lies you should be CNN it's pure lies\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Micdhael Masink wow ur so dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Why would you drag minister Farrakhan into this?!? He has \textbf{nothing} to do with what you people do to each other! All he ever spoke was the true of the so called Jews. He never said go out and kill them.. He also never said to hate them\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small How can people expect Jews to be safe when the \textbf{dumb} politicians keep letting the acursed anti-semtic Muslims bring their dirty hateful"-\& -,,?*!  Into the U.S.ADD THEM TO ALREADY EVIL \textbf{RACIST} AND IT'S A RECIPE FOR DISASTER FOR MINORITIES AND JEWS.THE U.S. MUST STOP GIVING ASYLUM TO JEW HATING FOREIGNERS .\normalsize   & \cellcolor{green!5}Dumb, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/52 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small \@BaronVonTacocat Many countries like Russia imprison or even kill you for being \textbf{g\textbf{ay}}.Israel respects gays,they are more secular and \textbf{black} people face less dicrimination according to some Etopian Jews I have spoken to while in Israel.Is Israel free of critisicm?No ofcourse not,some people in Israel are idiots who do not realise that arabs are the same \textbf{race} yet have \textbf{racist} views towards them and the current president is to right wing.My father imagrated from Iran and found safety in Israel after being abused in Iran.Where will jews go if Israel is destroyed.Back to Iran,Iraq and Egypt?Remember from the perspective of Jews they are hated and feared another genocide so took tge former land of the ottamans and it is not their fualt that England gave them terrible borders and from an arabs perspective it is stealing land.I personally believe in a two state separation but it sadly seems unlikely.\normalsize   & \cellcolor{green!27}Black, Gay, Race, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}5/149 & \cellcolor{green!27}3.356 \\  \hline
  \cellcolor{green!5}\small \@CynicalCloud Israel is a \textbf{racist} apartheid state which steals land from their neighbors. I think they should return to the 1967 borders and be happy with the land they stole without feeling the ever constant need to steal more. Fuck the IDF, bunch o' ZioNazi child shooters and open racists who cry "OY VEY ANTISEMITISM ANTISEMITISM" any time anyone points out their Jewish supremacist ideology or war crimes against their neighbors.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small \@CynicalCloud Why Israel make \textbf{African} female migrants take birth control that cuase  them weren'td to have babies just they come and live in the country?. Why isn't israel Drown themselves with diversity and multiculturalism of people we recently attack ? This war wasn't we fighting is not for our freedom. It's isreal interest.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small \@BaronVonTacocat Becuase the in has countries like China,Saudi Arabia and Iraq on its human council which is a complete fucking joke.Most of the the time it is those countries who say so .As I said earlier there are Arabs Christians on the supreme court.How the fuck is it apartheid?It is simply amazing how you guys believe you are morally superior over a \textbf{nation} you have never been to.This video isn't even about Israel but Jews in America.How does your small mind compare the two?How?I am a half Mizrahi Jew for crying out loud.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}\small \@CynicalCloud here some \textbf{Racist} shit from Israel  [LINK] \normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Disenfranchised young males  with no jobs that pay good salary fucked over by system creates white  \textbf{nationalism}  /blacks we become \textbf{black}  nationalist why disenfranchised that leads to crime  \textbf{nationalism} and a lot of angry males\normalsize   & \cellcolor{green!5}Black, Nationalism & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Other people die everyday and the Zio media says \textbf{nothing}. A few Jews die and they act like the world ended. And they wonder why people are getting ANNOYED by them? Folks, the extremist Jews/Zios believe that YOU are BELOW them. Do you understand?\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small \@Jibran Khan Who knows. If that's the case he didn't need to because a lot of people are awake now. I feel sorry for the innocent Jews because they literally have no idea what's going on. And i DONT feel sorry for the \textbf{blind} followers of Rabbis that brainwash their followers.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small Anti Semitism has risen in the last two years because Donald Trump has given his blessing to White Supremacists. Trump supports \textbf{racism} \& hate speech.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Obama \textbf{Nigger} Whatever comrade. Fake profile, No content \& textbook  diversionary rhetoric = Russian Backed Troll. Nice try Vlad but no one's buying your Bullshitski here comrade.\normalsize   & \cellcolor{green!5}Nigger & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Liar, and we have all the proof who the Racists are ANTIFA \textbf{Black} Lies Mater, American Democratic Socialists, Communists, Obama Loyalists.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Maam, people tend to strike only that tree which bears \textbf{fruit}...\normalsize   & \cellcolor{green!5}Fruit & \cellcolor{green!5}Sexual Identity - Male homosexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small Y'all miss a \textbf{nigga} Huh ?\normalsize   & \cellcolor{green!27}Nigga & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small It doesnt help to calling people carrying \textbf{Nazi} and Confederate flags good people and athletes who take a knee during the national anthem to protest the shooting of unarmed Americans sons of bitches... hmmm .. what's the difference? Hmmm.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small Not one of these fuck heads served in the U.S. military, how tough are they ???? They are cowards just like Donald Trump president of the United States of America a \textbf{pussy} bitch \textbf{y\textbf{e\textbf{llow}}} belly draft \textbf{dodger} coward\normalsize   & \cellcolor{green!27}Yellow, dodger, pussy & \cellcolor{green!27}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese, Religious Identity - Jewish & \cellcolor{green!27}5/38 & \cellcolor{green!27}13.158 \\  \hline
  \cellcolor{green!5}\small Trump is making \textbf{racism} great again. I am literally shaking Trump is worse than Hitler\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small People like you with profile names such as yours cannot call another person such as trump as hitler. Your knowledge is below zero\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@MidnightSlasher 22 You should relax, the Nazis were defeated 70 years ago, the people claiming that mantle have \textbf{mental} problems.\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small 'Scary time for Americans right now' - Smh, bunch of victims! Ppl who grew up back when \textbf{racism} was real \textbf{racism} would slap you overly sensitive coots in a heartbeat... Propaganda in the modern day makes you afraid when back in the day there was public lynchings, fire bombs and segregation.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small so um what about \textbf{black} live matter who went around beating and killing innocent people during obama time in office no one talks about that anymore\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small CNN is a clown show.  Alisyn Camerota is a bigot and bullied an \textbf{Indian} Girl on the air....and CNN keeps her around?!?!\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small \@Stephanie Tihanyi but Democrats are. They are leaning socialist now and the \textbf{nazi} party was the national socialist party. They are even adopting \textbf{nazi} tactics by attacking Republicans and anyone else that disagrees with them. Wake up and smell the coffee you bird brain\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/44 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small 3 Emotions are required to keep Anger at bay. 2 are holding the Anger back. 1 is waiting for an opportunity, potentially to intervene. Reason, love, hate, and truth are (regarding the situation are) nowhere to be found...There are many emotions in this situation each connected to an individual person... Each person is representative of these emotions, and will be referred to as the emotions they represent...The emotions fighting are respectively Peace, Mischief, Patience, and Anger. Reason is nowhere to be found... neither is Honesty...There are some bystanders; Laughter, Sadness, Shock, Fear, Confidence, and Happiness whom are spectating the conflict...Laughter is enjoying the fight, not knowing the reason why everyone is fighting. Sadness leaves with Confidence. Fear is panicking. Shock is of coursed paralyzed with Fear. Happiness is minding its own business.Peace to tries to make Anger relax.Mischief is insulting Anger.Patience stays silent, says \textbf{nothing}, merely listens to what Anger, Peace, and Mischief are saying as it is he who holds Anger back.Anger's fists keep swinging at Peace and Mischief as Anger's friends Reason and Honesty are nowhere to be found...The Bystanders suddenly change their mood... Happiness has turned to Fear, Laughter has turned to Shock, the reason? Sadness and Confidence have found the body of Reason...Peace offers amnesty to try and make peace, but what Peace says makes Anger confused... it doesnt make sense why Anger should not be angry, because Anger's friends, the ones whom keep Anger under control; Reason and Honesty (often associated with Truth), are no longer around.Mischief demands submission, Anger breaks out of the hold of Patience. Anger and Mischief fall to the ground taking Peace with it.A knife covered in blood falls out of the back pockets of Peace... Everyone turns to Fear and Shock as Confidence, Happiness, and Sadness call upon Peace and Patience.Suddenly 4 new individuals are seen... Apathy is carrying the dead body of Honesty. Hatred is holding a wounded Love. Anger stops fighting and turns to Sadness... Peace turns to Hate and speaks of Love but Love says \textbf{nothing}... Mischief turns to Shock... Patience sees the bodies of Reason and Honesty, as Apathy points to Peace, in turn Patience turns to Anger...Suddenly, Fear turns to Laughter and Confidence... Hate, Apathy, Love, Sadness, and Patience, turn to Shock but then Anger.Anger, upon seeing the dead bodies of Honesty and Reason turns to Fear... Fear however points to Confidence, as Confidence points to Peace, Peace points to Hate and Anger, Hate and Anger points to the dead bodies of Honesty and Reason... Love and Sadness mourn Honesty and Reason. Apathy pulls out a gun and points it at Peace...Laughter is on the sidelines with Mischief, as Happiness walks away... and Patience is nowhere to be seen...Patience disappears as Honesty and Reason are no longer present...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/480 & \cellcolor{green!27}0.417 \\  \hline
  \cellcolor{green!5}\small what about \textbf{racism} against Whites\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small The anti-European league AEL there was a dramatic increase in anti-European sentiment in 2016 for years instance of anti-European hate was on the decline in America then came the 2016 Presidential election  since then a "meteoric rise" a 34 increase in blah blah blah. These are all European ideas from 2000.Meteoric rise: Used to describe something that develops very fast and attracts a lot of attention ( anti-Muslim  ). ( 2015  hate speech ).  ( 2016 hate crime ).The undemocratic Democrats are attempting to do what the socialists and the unelected EU have done in Europe, takeaway your First Amendment. And replace it with the European Union's "unlawful  speech." Then they will want to take away your guns and if you speak out against that, that will be "unlawful  speech." Be careful of this \textbf{old} socialist propaganda you will all end up being treated like Tommy Robinson. Protect your ( Human Rights ) I really mean it... vote GOP... It really does matter..Read up on modern European politics ( EU ) CNN is attempting to do for the Democrats what has already been done in Europe..... Word for word...?\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/192 & \cellcolor{green!27}0.521 \\  \hline
  \cellcolor{green!5}\small So much for the mythical stereotype of the big \textbf{black} scary man.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small "DRAMATIC \textbf{SPIKE} IN RACIALIZED RADICAL TERRORISM \& HATE CRIMES IN THE U.S."\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Am a \textbf{black} conservative but I hate how Trump handled the situation. He didn't even have remorse for those who died\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small What's wrong with the \textbf{nazi} flag? Americans always wear the rising sun Japanese flag which is equivalent to the \textbf{nazi} flag. I've seen it on t-shirts, stickers, internet and on daily items. The Japanese navy still uses the flag on military parades and in the navy. You can't pick and choose what's anti-Semitic or not. The Japanese were just as bad if not worse than the \textbf{nazi}.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}3/67 & \cellcolor{green!27}4.478 \\  \hline
  \cellcolor{green!5}\small This fuckin stupid narrative that theres more rascism n anti semitism cuz of Trumps rhetoric is fuckin RETARDED.. If anything cnn enables this stupidity and highlights n reports this behavior when it happens to give the illusion that there's a increase of these incidents but the truth is all this stuff was happening under EVERY   ADMINISTRATION IN RECENT HISTORY....A perfect example of that would be blaming Obama for all the blk people killed by law enforcement on his watch ...one could easily turnaround n say because of obama being office more \textbf{black} people died because of his administration's lack of action... But would they be a fair conclusion to come to  ??? Nooo ... But its ok to pin shit on trump cuz hes always been the problem. The truth is u cant blame one person for the actions of others ...plain n simple.. People jus follow others without knowing all the facts n this why this country is so divided.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/161 & \cellcolor{green!5}0.621 \\  \hline
  \cellcolor{green!27}\small omg ur so dumb\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small \@Tchannel Frim That is it. NO Fear of words, be it hate or words of  oppression or prejudice , ill spoken words , their violent verbal dealings will be returned to them double fold. We won't fear their words that spew hate and \textbf{racism} or superiority.  That s exactly what I mean whether they are from the President or Farrakan.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small \@Whiterun Guard Agreed.  Words  they are powerful containers ,but I still won't fear them.  The only good if any that can come out of this is when these hateful words are spoken out, we can come against their violent verbal dealings. We can rebuke those words we can  counter their words. we can say things like may those words never come to fruition, and may those words never fall to the ground.  We bind those I'll spoken  words. We loose words of  peace , wisdom, life and liberty  and prosperity and justice into our lives. I stand with my Jewish brothers and sisters and all those who are are the side of peace  and righteousness.  Not this lawlessness and cowardice that has infected this \textbf{nation}.Still we will not fear their words. They want us to respond to them with fear The only word I'll respond with is Peace. Peace is the opposite of Fear and much more powerful. Shalom\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/159 & \cellcolor{green!27}0.629 \\  \hline
  \cellcolor{green!5}\small What a reach i honestly hope CNN stretched beforehand. First Trump supports all Jewish movements both his son and daughter converted to Judaism and his son in law actively controls a lot of the aspects of the Whitehouse, in fact they are one of the very few groups that Trump has not attacked. The biggest of all he is the only US president to recognise Jerusalem as the Jewish capital despite worldwide condemnation. So nice try CNN trump has \textbf{nothing} to do with this.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}\small CNN is owned by Jeff Zucker (a Jew). Its staff is filled with Jews. The ADL is a Jewish organization established to protect a Jewish man that raped and murdered a 13 year \textbf{old} girl and tried to blame a \textbf{black} man for it.\normalsize   & \cellcolor{green!27}Black, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}2/44 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Bullshit, FAKE NEWS yet again.I believe these antisemitic incidents have always been there, they're just being reported on more.These fools are going to try to lead you to believe this is the fault of the Republicans, or Trump.These are the actions of very stupid, ignorant, hateful, scared people. \textbf{Nothing} more, \textbf{nothing} less.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small Free speech, as long as they are not acting on their bigotry there is \textbf{nothing} the law can do.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Um.. the \textbf{Nation} of Islam doesn't condone violence, only self defense. And has never physically assaulted or condoned attacking Jews.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Nazi bullshit propaganda\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small omfg stop making a big deal about something who cares?!!! why do we care if a few idiots kill a few jews? what about real problems facing our \textbf{nation}?what about how 1 percent own 99 percent of our wealth? what about how mega corporations control us? how about how our government spies on us? huh? what affects us more? a few idiots or real problems that affect ever man women and child\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small Civil war would be great ! I'd love too see an \textbf{obese} country fight . Soys vs the Alex Jones retards in a battle royal !\normalsize   & \cellcolor{green!27}Obese & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}\small \@Hanz and we beat the natives in war,if \textbf{nothing} changes after war then Hitler would still be alive. If Mexico wins in war they have the right to take our country.  It's always been that way but lately you retards have been denying history.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small \@kfox gaming yeap thats called envy and hate , a \textbf{common} thing on the left .That's all political things are there mostly forms of hate. A guy could bust his ass days with no sleep selling on eBay while working two jobs and a left wanker could work part time and still feel that he should pay for it.  And of course wish death on that same person.   Wanting what others have is one of the worst things you can dwell on.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small Nothing wrong with nationalists.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small \@BaronVonTacocat except \textbf{racism}, \textbf{xenophobia}, violence and division, in one word - fascism... . It isn't tolerant of those who are not. It doesn't tolerate diverse populations. Trump isn't a Nationalist,  he serves Putin, he is a traitor... about a dead opposite of a Nationalist... his party and worshippers aren't Nationalist either , they are fascists and xenophobes serving their Supreme Leader and acting on his rhetoric.... Neither care about the \textbf{nation}, Constitution,  Bill of Rights, etc... They blame and when they run out of enemies they attack each other....\normalsize   & \cellcolor{green!27}Nation, Racism, Xenophobia & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}3/89 & \cellcolor{green!27}3.371 \\  \hline
  \cellcolor{green!5}\small Nationalism : Devotion to the interests or culture of one's \textbf{nation}.The belief that nations will benefit from acting independently rather than collectively, emphasizing national rather than international goals.Aspirations for national independence in a country under foreign domination.\normalsize   & \cellcolor{green!5}Nation, Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@BaronVonTacocat yea, it all sounds good until you ask which culture is the national culture and who is a loyal follower and who isnt.... crowds of white guys hating on Jews, blacks, Hispanics and declaring their \textbf{race} and their culture as the National culture is how it works out in reality. People murdering those that they think are a threat to the national identity they espouse... The NAZIs are proud nationalists,  all about cultural purity and a singular identity.so did the Japanese .. we already decided that wasn't an American value and members of my family fought and died stopping it. I served in that tradition. You can't be a Nationalist and do your duty to serve your country and fellow citizens... a patriot does not serve blindly....\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}\small \@Everblue Freediving ...you're idiocy amazes me. Funny how you over exaggerate the spectre of "white nationalists" even though they are far smaller in size than their equally vile bretheran anti white racists on the left. There exists no greater \textbf{race} hating group than the progressive left. You see no one for their merits alone, but only for their skin color, \textbf{gender}, \textbf{age}, \textbf{sexual} preference, and \textbf{race}.\normalsize   & \cellcolor{green!5}Age, Gender, Race, Sexual & \cellcolor{green!5}Age - General, Ethnicity - General, Gender - General & \cellcolor{green!5}5/66 & \cellcolor{green!5}7.576 \\  \hline
  \cellcolor{green!27}\small \@BaronVonTacocat ...you and your leftwing buddy everblue are on the same team. You're both arguing over different shades of the same color (\textbf{r\textbf{ed}}).\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/23 & \cellcolor{green!27}8.696 \\  \hline
  \cellcolor{green!5}\small I think \textbf{nationalism} is good for a \textbf{nation} and he doesn't so I don't think we're on the same side. \@Jack Wertz\normalsize   & \cellcolor{green!5}Nation, Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small White supremacists and \textbf{black} supremacists must be stopped ! Down with the \textbf{black} panthers and KKK!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small I wouldn't doubt one bit if this is the work of the Jews. now they want laws passed against saying anything bad about Jews. When it is a \textbf{black} guy ir a white, \textbf{y\textbf{e\textbf{llow}}}, \textbf{r\textbf{ed}} man they look the other way. But when it happens to them they act like it is the end of the world and everyone should care. Double standard.\normalsize   & \cellcolor{green!5}Black, Red, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}6/63 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small Sorry but no news outlet said that, but a few do say he was republican. Please fact check this to prevent us from looking as confused as a \textbf{transgender} choosing a restroom\normalsize   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Sexual Identity - Transexuality & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Education is the key to avoid having history repeat itself. Hate is always stamped out when God steps in. Please pray for our country, founded on freedom of religion, one \textbf{nation} under God, domestic tranquillity. We are all part of ONE HUMAN \textbf{RACE}. Get over divisiveness and greed. No one \textbf{race} or group is superior to another. The only ONE SUPERIOR is God, Almighty. ' Pride goeth before a fall.'\normalsize   & \cellcolor{green!5}Nation, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}3/70 & \cellcolor{green!5}4.286 \\  \hline
  \cellcolor{green!27}\small What is happening to America? Did I miss out on some giant mass text conversation 3 or 4 years ago, where we all decided to reenact a documentary of early 1930s Germany and the rise of Hitler and the \textbf{Nazi} party? Or did someone put LSD in the drinking water again? How has one orange imbecile managed to single-handedly dismantle our country over the course of a few years? I've never felt such a combination of rage and pity towards so many of my fellow Americans. Pity for their ignorance, and rage as I watch them in their ignorance destroy everything that makes this country great, while claiming they want to "Make it great again".\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/115 & \cellcolor{green!27}0.87 \\  \hline
  \cellcolor{green!5}\small Jesus America and others went to war to fight the \textbf{Nazi} but yet they are allowing them to rise why are they not classed as a \textbf{terrorist} group blows my mind\normalsize   & \cellcolor{green!5}Nazi, Terrorist & \cellcolor{green!5} Ideological and Political Identity - General, Religious Identity - Muslim & \cellcolor{green!5}2/31 & \cellcolor{green!5}6.452 \\  \hline
  \cellcolor{green!27}\small Wow!!! \textbf{Black} boys getting shot by law enforcement but no attention on this. But Jews get a threat and CNN takes note. You talk about \textbf{Racism} but you act when Jews get shot. Now GAB gets bad press . When Jews get attacked \textbf{Zero} tolerance but blacks get killed we look the other way. CNN always has a Agenda!\normalsize   & \cellcolor{green!27}Black, Racism, Zero & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/59 & \cellcolor{green!27}5.085 \\  \hline
  \cellcolor{green!5}\small From 2016 and on alot of these \textbf{racism} attacks been getting worst hmmm, i wonder who is the cause of this, im sure you guys can figure it out 2016 and on smh.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Rion are u \textbf{dumb} there's a difference between a crime and a hate crime\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small All done by \textbf{racist} pig trump supporters. Remember trumpd says there good people.this is just trump and his \textbf{racist} trump supporters making America white again\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small Fake news cnn, this bitch is so anti trump it's crazy\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small It is far time we start to hear somebody has blasted a few \textbf{racist} in retaliation..🇬🇧..\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The \textbf{R\textbf{ed}} wave is coming\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/5 & \cellcolor{green!27}40.0 \\  \hline
  \cellcolor{green!5}\small Engineers Quest See a urologist for that\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small We as a people have to re-embrace America's motto, E pluribus unum, "Out of many one". Our strength has always been our diversity. Diversity of thought, culture, \textbf{race} and religious belief. How else can one explain our rise and depth of talent. We can only be Great if we are united. Anyone that fosters hate and division are un-American and contribute to the demise of our republic. They are doing the work for Putin and Xe.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small How sad 😞politics, aside, personal views, ie,political relgious  ect, but as human beings, why is this acceptable to dregrade, to even have the same battle ,for who know the begin of time? To degrade to persecute, to demean,to dehumanize,ie all the bad \textbf{racist}, in history, like all the hateful redirect an reset events,its against Human Beings with different ie,raises, relgious, political, ect views then those human beings doing the attacking....killing,threating, .Then other human being us, are debating whether whos,to blame ,an who right an who's righter than right ,then others, takin all that hate adding there own,so on an on, instead of coming together as humans, and STAND up for what's right for basic  humanity,.so yea it's so sad you can feel the pain, the hate, it's so ugly, how much uglier is goin to get?! Just a personal rambling, I guess ,vote ,prayer ,thought,for the good to provel, an triumph over evil,throughout these uglyness\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/155 & \cellcolor{green!5}0.645 \\  \hline
  \cellcolor{green!27}\small You're calling Ben Shapiro a \textbf{Nazi}? Hahahahaha. He's \textbf{nothing} like you at all. He's an American Patriot...more so than you'll ever be.\normalsize   & \cellcolor{green!27}Nazi, Nothing & \cellcolor{green!27} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!27}2/22 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small That \textbf{dumb} ass who did this hated trump so stop blaming the president for this u stupid morans\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Fuck Bibi n his Zionist \textbf{terrorist}! FreeJulianAssange Wikileaks\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small We know what you're doing CNN. This is false flag bait. We the people know better and will not be provoked/tricked into these games. VOTE \textbf{R\textbf{ED}} and ignore the false flag attacks!!!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small What is fake? The shooting? The \textbf{racism}? Come on, explain you ignorant scum.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Alex Q what \textbf{racism} u scum\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Using the \textbf{black} man to cover the \textbf{racism} of the republicans and trump lol faracan is not to blame for the raise in hatred as no one take any notice of him as his a scumbag \textbf{racist}. Trump is to blame and the republican promotion of \textbf{racist} nonsense on TV.\normalsize   & \cellcolor{green!27}Black, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/50 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small Why not America is "\textbf{Nazi} Germany West," these pale white Neo/Alt-Reich-Right \textbf{Nazi} wannabes know that their genes are too weak to live among people of color and strong Cultures they can't survive. Also "Jew be should called out how they treat their neighbors to West of IS- Ra-EL."\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Black kkklansman is a piss poor \textbf{race} hustling movie. If you want more reasons to hate white people more just rewatch Roots over and over again.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small I really hope \textbf{nobody} takes these swaztikas seriously.. Anti Trump people on the left have been caught spray painting swaztikas and blaming it on trump supporters to push a false narrative saying they're "nazis".. Fake hate crimes\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}4/37 & \cellcolor{green!5}10.811 \\  \hline
  \cellcolor{green!27}\small Here's the deal: MOST criminals AREN'T insane. I know that word gets tossed around a lot, but MOST criminals are fairly sane people, legally speaking. Most aren't willing to get caught painting something like a swastika unless they mean what the swastika says. So-called "fake hate crimes" are much less likely than the real deal. You're using that same, \textbf{old} "logic" of thinking a person will spend all their money, go into debt, be humiliated and get death threats just to fake-accuse someone of rape. Sure, possible, but highly unlikely.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}\small Anti-semitism is wrong, but why are we only starting to put real airplay and analysis on hate just now? White people have been running into \textbf{black} churches and killing, and it has only gotten 10 second blurbs on TV.\textbf{Racism} will ALWAYS exist when people only care when it happens to them, or their particular group.\normalsize   & \cellcolor{green!5}Black, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Flying \textbf{nazi} symbols and spewing anti-semitic phrases,  I can only guess that these idiots who do had forefathers that fought against the \textbf{nazi} regime during WW2.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Trump IS to blame for the blatant outpouring of hatred and \textbf{racism} in this country.  While those horrible thoughts and feelings were present under Obama, Bush and Clinton at least our leadership kept them at bay.  Now in just 2 years he has led America to a country that is divided not united.  We are no longer the UNITED States of America thanks to the Republican party and the man they so love to defend and refuse to bring to justice for his continued division of the country and incessant lying.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/91 & \cellcolor{green!5}1.099 \\  \hline
  \cellcolor{green!27}\small Why would it be unacceptable when \textbf{black} people get killed by police poverty self hate y'all minority think  shit sweet until the true majority reminds you that your a minority then y'all what sympathy they hate all of us let's stand with love and unity one America for all\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small Judaism it is adopted religion story from South Africa, Installed in Middle East by Roman empire. Moses and \textbf{Negro} folk(Israelis) didn't go to Canaan but heading to Africa to promised land (Negroland). In the new testament bible, that is why Jesus (Yeshua) use Aramaic language speak against those FakeJ3w people, Because he knew the Hebrew language that FakeJ3w people used in that time are not real Hebrew language. The Chinese (Mongol) empire hold the secret ancient Africa continent map tell the true location of real Jerusalem in Africa. The so called J3w in Israel today they are not RealJ3w people, but folk from the \textbf{Black} Sea called khazarian from Khazar empire. The Khazarian they hate and do war against Slavic people (the Russia) and today they still do war against them. Today those FakeJ3w they use Jew name, eat Jew food, dress like a Jew. speak like Jew, but truly they had no a single of Jew blood from they ancestor. They are the bad copy of chosen people. They are Robbery in Police uniform, always use police card to rob poor people who not learn so much about history.\normalsize   & \cellcolor{green!5}Black, Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/190 & \cellcolor{green!5}1.053 \\  \hline
  \cellcolor{green!27}\small Nazis in America are a small group of stupid \textbf{dumb} fucks , the leftist like call everybody Nazis today who do not agree with them ,  real \textbf{Nazi} are small but dangerous , you need to stop call every body a \textbf{Nazi} and point out the real Nazis\normalsize   & \cellcolor{green!27}Dumb, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/48 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Trump is a disgusting cancer he told \textbf{nazi} they were Ok  good men\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small That is bullshit \textbf{black} been telling you this country fucked up please don't be surprised\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Anti-Semitics is wannabe trump base As trump is Traitorous bastard to this country so is he baae plane and simple Understand trumpeters this is America and not \textbf{Nazi} Germany you sinh lullabies for the \textbf{old} days.... hitler lost so will daffy duck trump.\normalsize   & \cellcolor{green!5}Nazi, Old & \cellcolor{green!5} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small \@Tchannel Frim stupid \textbf{thin} skin whore are you wishing death upon others...vile cannibal \textbf{gender} benders (u)\normalsize   & \cellcolor{green!27}Gender, Thin & \cellcolor{green!27}Gender - General, Physical Identity - Physical Features & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Greeky Gaming Probably a lot of KKK members in the comment section - they're called feds and Jewish plants.Edit: And this one will spin your little brain sideways - why are Jewish people able to maintain a closed borders ethno-state in Israel while advocating for open borders for us Europeans? Why is us protesting our \textbf{ethnic} replacement an indication of being a "KKK member"?\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small I don't think America was so star spangled great before Trump took office either. All these \textbf{racist} assholes existed before as well. The only difference now is that they have enough support from the current administration to be assholes in public.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Communist states like Maoist China killed 50,000,000 people. or perhaps Stalinist Russia and their 20,000,000 executed. yep Communism is good. what a crock!\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Before they came for the Mexican, after they came for the Muslim , than they came for the \textbf{black}... now the comes for the Jews... They will find a way to come to you ! If you keep still silence:  you don't have to complain Later ...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Blacks have been going through this area since this country was established. It is a shame but true. This country is supposed to be the land of the free but free for who? It's a shame but people follow \textbf{crazy} people. Tell me why some white people in the United States think they are better than everybody in the whole world. It just make them look like fools which they are for believing they are better than anyone else. But will you have a leader in office seeing the things that he says then that is a problem. I am so happy I moved out of the United States 5 years ago.  It's only going to get worse.  There going to be more mass shooting before this year is out. And what I want they going to say he's insane.  Thetell me how do you say when people get guns\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/150 & \cellcolor{green!5}0.667 \\  \hline
  \cellcolor{green!27}\small CNN VIEWERS ARE IDIOTS...THIS IS YOU LAST ATTEMPT TO WIN AN ELECTION AND THIS ALL YOU HAVE? ...\textbf{RACIST} HILLARY WILL BE SO PROUD.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Trump is as pro Israel as it gets, his daughter is jewish, grandchildren are jewish, his son married a jew and some his top advisors are jewish and his cabinet is disproportionately jewish. Two of the biggest reasons for the spikes in the ADL data are because of the jewish teen in Israel who hated Trump and made bomb threats to synagogues in the US to try and blame Trump supporters. Then there was the \textbf{black} muslim who wrote for the Atlantic who also sent in a few bomb threats to synagogues, actual violence in the ADL data shows a sharp drop.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}\small \@jon smith It was MAGA \textbf{terrorist} that shot and killed innocent people and sent bombs.  We know who's who.  You probably got your tiki torch in hand.  Fucken loser!\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small \@[̲̅K̲̅]An actual \textbf{terrorist} sent 'bombs' with literal clocks on them like the ones you'd see on TV shows? None of which detonated. Are you really that dense, or is it just conformation bias?\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small There is a difference between Zionist Jews who follow the Talmud and non Zionist jews who follow the Torah yet the Zionist Jews who own the media label everyone who criticizes Zionism as antisemitic when they are not even authentic jews in the first place.  They are satanists who  follow the Talmud which promotes \textbf{sex} with 3 year olds as well as the killing and enslavement of all non jews.  The Zionists control both parties btw creating the illusion of choice since divide and conquer is a tactic they use to remain in power though you people are too inconceivably stupid and brainwashed to comprehend these things\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}\small News choices:☑ Trump☑ Jews☑ Racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small "Nature \textbf{Freak}" is an interesting username for someone who seems to have difficulty discerning a single tree from the entire forest. When you say, "This is how progressive Democrats roll," what you suggest sounds like a single personality, like a superorganism, like colony of ants? Is that what you are: part of a colony of a single personality? I'm curious to know... Is this how you view human beings?\normalsize   & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small These ADL numbers aren't just crime, it includes harassment, it doesn't differentiate between right wing and left wing hate, lots of anti-Israel ppl on the left. ONe of the biggest reasons for the \textbf{spike} was the multiple bomb threats made to synagogues....by an ISRAELI teen.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small As I said it doesn't include just crimes, violent hate crimes were down according to ADL data. That one Israeli teen had MULTIPLE incidents of threatening synagogues, he was not a Trump supporter. The \textbf{black} muslim who wrote for leftists websites also made multiple bomb threats to synagogues, according to their own data, these 2 ppl accounted for most of the \textbf{spike} in overall incidents. So anti-Trumpers by the ADL's own data were more likely to contribute to the \textbf{spike} than Trump supporters.\normalsize   & \cellcolor{green!27}Black, Spike & \cellcolor{green!27}Ethnicity - Black, Religious Identity - Protestant & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small You have a \textbf{weird} sense of humor.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Max Covfefe dont be a whiny little bitchpeople have freedom of speech in OUR nation\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small CNN = cock nipple nibblerBBC = big \textbf{black} cock\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Jews have been hated everywhere for all time. Thats just a fact. I dont support ant \textbf{weird} \textbf{NAZI} crap, but jews are hated everywhere.\normalsize   & \cellcolor{green!27}Nazi, Weird & \cellcolor{green!27} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Amirhosein Herandy The people have spoken, out of the 130 people that voted 62 voted for trump, which shows you that people wanted him in office,the people were sick of these political clowns promising and not delivering and he's always been the same since 1987...and everyone loved him before he became president. so no I don't think you're correct in what you're trying to say, people are fucked up cuz the media deff influences a lot more when you see a celebrity news outlet like access Hollywood and you're favorite stars start throwing out subliminal messages. Trump is basically a adult looking at the media (who are the babies) and saying 'goo goo Gaga!' And then the babies on the left go' he said goo goo Gaga!? And they try to bring all these experts to explain why everyone is butt hurt, he's playing y'all and y'all too \textbf{dumb} to see it\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/152 & \cellcolor{green!5}0.658 \\  \hline
  \cellcolor{green!27}\small \@Allothersweretaken \textbf{Nothing} insightful will contain the phrase "goo goo gaga". Only little children say that. Which is why you're juvenile.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Great post. Too bad the average \textbf{mong} at CNN is incapable of understanding the world through an objective lens.\normalsize   & \cellcolor{green!5}Mong & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Trump is the leader of the KKK! He even said said it! He heard from CNN that he was calling for a \textbf{race} war too and that he hates puppies! Impeachment !\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small If anyone hates Ben Shapiro it has \textbf{nothing} to do with \textbf{race} or religion and everything to do with character he's a complete douche lol\normalsize   & \cellcolor{green!5}Nothing, Race & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/25 & \cellcolor{green!5}8.0 \\  \hline
  \cellcolor{green!27}\small \@John Caulfield If only you could make money like a Jew. But you will always be a \textbf{nothing} loser.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small It's clear as day, trump encouraged this Republican \textbf{terrorist}. Maybe he will try to ban all Republicans from the US like he tried to ban all Muslims.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small That is what they called "Make America Great Again " We didn't see \textbf{nothing} yet wait his second term or impeach him all hell gonna break lose .\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small CNN in the did \textbf{nothing} but insight hatred against  Isreal. But you want to blame Trump. CNN is complete BS.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small You mean a massive \textbf{spike} in SELF INFLICTED ATTACKS? These people always end up being Jews attacking their own stupid synagogues.\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small WOW \textbf{ZERO} TOLERANCE POLICY ON SAYING MEAN THINGS ABOUT A GROUP OF PPL. ...but what \textbf{black} america goes through "ehhhhh"\normalsize   & \cellcolor{green!5}Black, Zero & \cellcolor{green!5}Age - Youngsters, Ethnicity - Black & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Cnn and their followers are \textbf{nothing} but fuckin hypocrites\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small ohi bacon ok so he was anti Trump. How many people who are committing these crimes support Trump or spew the same hats fulled \textbf{racist} remarks that Trump does? A leader leads by example. His behavior has opened Pandora's Box filled with all kinds of divisive rhetoric, fear mongering, violence approval, \& hate. That's not how a supposed Christian or leader should behave...period!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}\small \@Lambert Lum 'invasion', 'globalists a.k.a. George Soros' - you just need to remove the blindfold and watch one of his rallies. I guess you did already you are just in denial if you still need an explanation.Btw. being pro-Israel doesn't mean anything. They also have a radical right wing government and they are occupying, oppressing, displacing, killing non-white people so there is a \textbf{common} denominator there...\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small \@Tamas Varga So what exactly did you hear at MAGA rallies that inspired the synagogue shooting? If you can't produce a quote, then I would assume you are making things up.Donald Trump on Charlottesville, "\textbf{Racism} is evil, and those who cause violence in its name are criminals and thugs, including the KKK, neo-Nazis and white supremacists and other hate groups that are repugnant to everything we hold dear as Americans," [LINK] \normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}\small \@Lambert Lum You are playing \textbf{dumb} or you are \textbf{dumb}. I won't produce and quotes it's just wasted time because you can watch countless videos on youtube and you can hear it from Trump himself, even his "very fine people" comment.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/41 & \cellcolor{green!27}4.878 \\  \hline
  \cellcolor{green!5}\small Lambert Lum when you sew the seeds of distrust \& hatred it leads to dehumanizing them. Trumps \textbf{racist} rhetoric has allowed extremism to be accepted as socially normal \& acceptable. Just because he might care for his Jewish daughter doesn't mean these extremist groups will. I see posts daily from my family in West Virginia about how the Jews control everything \& are corrupting society through media manipulation. It's a \textbf{common} theme among Trump supporters. They won't listen to him when it comes to supporting the Jews when he's teaching them to distrust everyone else. I've seen it backfire on him before over the summer. That's part of the Pandora's box...sew chaos \& it will come back to haunt you.\normalsize   & \cellcolor{green!5}Common, Racist & \cellcolor{green!5}Ethnicity - General, Social Class - Working class & \cellcolor{green!5}2/120 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}\small Hulein Pylo I will be the first to admit \textbf{nobody} is perfect. Your comment lacks any substance. My family comes from all racial, political, religious, \& economic status. I am an American through \& through since my Native ancestors set foot on this land till today. I set all differences aside to unite as a country so we aren't divided by those who seek to overpower us. What happened in the past is the past. We are here right now \& our problems are mounting with a power struggle over greed \& corruption.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small \@Tamas Varga I am not playing \textbf{dumb}. I am just catching you off guard for your failure to produce any backing for your statement. If you want to make a claim, back up your claim. If you can't back up your claim, then you have \textbf{nothing} to say.As for the fine people comment, Trump is hypothesizing of a small minority of people  who have legitimate concerns. I'm a Civil War buff,  and I am deeply bothered about toppling statues. I side with the Union, but I have respect for the Southern generals. Even Lincoln forgave the Southern generals.I have established that Trump is anti-racist. You either present a counter-argument or you don't\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/114 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small \@Rebecca Mæd I am going to agree with you that I see a lot of anti-semite statements from people who are otherwise Trump supporters. I tell them to either submit to Trump, or get off the Trump train. Trump is a friend of the Jews, and any Trump supporter must submit or leave.I also browbeat anti-semites by pointing to Jesus. Jesus ministered to the Jews before he ministered to the Gentiles. Jesus gave Jews priority over Gentiles in timing. Then when the Jews killed Jesus, Jesus said, "Forgive them for they know not what they are doing."  Finally, I will stick my finger at them, and tell them that the reason why Jews reject Jesus is because of their anti-semitism. Those who impede Jesus ministry to the Jews, should either submit to Jesus, or leave.Besides, all these Jewish conspiracy theories are getting \textbf{old} after a while. This has been happening for a thousand years. it's always the same thing. And these conspiracy theories never pan out. Never. You can even go to the book of Esther and see an early conspiracy theory against Mordecai by Haman. A conspiracy theory dating back to the Persian empire. Will people stop conjuring these ridiculous conspiracy theories?I wish good luck to you Rebecca in your stance against anti-semitism. We must all stand united against this.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/224 & \cellcolor{green!27}0.446 \\  \hline
  \cellcolor{green!5}\small Lambert Lum You have established that Trump is 'anti racist' - you are really not pretending that you are \textbf{dumb}... 😂😂😂😂😂\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small How do you no that the shooter hate Trump. What a \textbf{dumb} fucker you are.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small hmmmmmm.... yes....Very suspicious indeed. mail bomb's that cant explode and now a anti trump mass shooter whom hated jew's so much he targetted very \textbf{old} people. Just before the mid term elections.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small It's funny how the Jews Talk about \textbf{racism} when they practice \textbf{racism} in Israel right now when they are expelling all africans in Israel and had the nerve to go to South Africa to help white farmers  who stole land from \textbf{black} South Africans keep the land that they stole and don't forget the Jews supported Trump and praised him it's funny how history repeat itself don't forget it was Jews  who financed Hitler\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/74 & \cellcolor{green!27}4.054 \\  \hline
  \cellcolor{green!5}\small americans fought the nazis , now trump from german family turns america into \textbf{nazi} land 2.0.    mindboggeling\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Trump and his uneducated, ignorant supporters will blame liberals for everything negative in this \textbf{nation}. Trump will never take responsibility for his actions. He's a disgrace to this country. Vote blue\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small tell me why there isn't crackdowns on these people considered \textbf{terrorist} come on you raid crack houses gotta get rid of all these people\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small Nationalism can be a powerful means of achieving goals as a country. \textbf{Nationalism} can also be a tool of manipulation by the leadership or a divided \textbf{nation} and can lead to grave violence when said goals are previously undefined. Trump is using a propaganda tool with proven success from history.\normalsize   & \cellcolor{green!27}Nation, Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}6/50 & \cellcolor{green!27}12.0 \\  \hline
  \cellcolor{green!5}\small Dramatic \textbf{spike} in fake news\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small \& literally \textbf{zero} bullet holes. just like vegas. And who shows up? that Jew Bari Weiss demanding gun control.\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small You wanna see hate, YouTube Saudi man beats Ethiopian \textbf{woman} upside down.\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small So what if they're all in one area let them live amongst themselves if they want to be stupid and be by themselves and so big why we making a big deal out of it and leave them alone and they'll leave you alone as long as you don't cross that boundary they don't give a crap when making too big of a deal out of \textbf{nothing}! Is white supremacist really had so much power they would be in power which is why they're living in Charlottesville doing \textbf{nothing} with three teeth smoking meth drinking Schlitz\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small Kurochan See how easily you forget. That's because msm only covers them for about a day. There was one just a little over a year ago done by a muslim \textbf{refugee} from Africa, and another by a white guy. Both in the south. Reports other than cnn believed the white guy was an antifa \textbf{communist}.  He shot everyone in the congregation. Dozens died. There were many Mexican Christians in there too.\normalsize   & \cellcolor{green!5}Communist, Refugee & \cellcolor{green!5} Ideological and Political Identity - General, Nationality - General & \cellcolor{green!5}2/71 & \cellcolor{green!5}2.817 \\  \hline
  \cellcolor{green!27}\small "There was one just a little over a year ago done by a muslim \textbf{refugee} from Africa, and another by a white guy." - Can you narrow the scope here?\normalsize   & \cellcolor{green!27}Refugee & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small If this continues, America will be destroyed by \textbf{y\textbf{e\textbf{llow}}} stone volcanoe.\normalsize   & \cellcolor{green!5}Yellow & \cellcolor{green!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Nationality - Chinese, Nationality - Japanese & \cellcolor{green!5}3/11 & \cellcolor{green!5}27.273 \\  \hline
  \cellcolor{green!27}\small Anti Semitic is on the uprising and it not only the far right whites and blacks but with   the radical far left and radical Islam too ,  it ok to be a radical Muslims and  left with \textbf{black} nationalist  and be a ant Semitic in world too , all anti Semitic is evil\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Perhaps the media should expose ALL anti-Semitic speech and activity.  I see the moronic comments below, claiming Trump is responsible.......  Does anyone remember a man named Barack Obama?  He was a man who went to a church with a \textbf{racist}, anti-Semitic pastor named Jeremiah Wright.  Apparently this man named Barack Obama went to the church for 20 years, but he never heard the \textbf{racist} and rants against Jews.  When Mr. Obama made it to the White House, his pastor then said the Jews wouldn't let him near him.  Personally, I wouldn't associate with someone like that, and I certainly wouldn't have that man officiate my marriage.  Did CNN report on this?  NO.  To steal one of CNN's BS headlines:  CNN NEVER REPORTED ON PRESIDENT OBAMA'S ANTI-SEMITIC PASTOR, AND WHY IT MATTERS.  That goes unreported because the anti-Semites involved are Democrats, or \textbf{African} American.  That is NOT OK.  I've seen countless anti-Semitic comments online from people who are not Trump supporters.  Whether it's about 9-11, or banking, or the 1, you'll see comments aimed at the Jewish people by the left all day long.  This matters.  Let's not forget the anti-Israel activists on the left, who are really just anti-Jewish activists.  CNN had an opportunity to shine a light on Reverend Wright's hate filled, anti-Semitic sermons, but they failed.  How many members of the church leave those sermons hating Jews?  What a shame.  It matters when you ignore hate because it's being spewed by someone with a (D) after his/her name.\normalsize   & \cellcolor{green!5}African, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/250 & \cellcolor{green!5}1.2 \\  \hline
  \cellcolor{green!27}\small Once the Russian infiltrated the German frontline, these \textbf{Nazi} bitches were fucked deep in the ass, so yeah those pussies still have animosity for the people that defeated them, and had them bend over and grab their ankles Early 1945.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Thats a fake \textbf{nazi} flag !\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small What we are currently living thru is America's modern day version of Hitlers \textbf{Nazi} Germany. If the dems lose the midterms, we will have surpassed the point of know return.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@Lambert Lum AND YOUR MF'ng point?? DIDN'T SHE MARRY INTO IT? HE'S OBVIOUSLY ACTING LIKE HE DOESN'T CARE ABOUT ANYTHING... I DON'T FEEL SORRY FOR PRISONERS WHO'LL END UP IN JAIL FOR CRIMES...  REGARDLESS OF \textbf{RACE} CREED OR RELIGION.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small If we were, you'd be the first in the \textbf{oven}.\normalsize   & \cellcolor{green!27}Oven & \cellcolor{green!27}Religious Identity - Jewish & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Don't they own Hollywood? Didn't Hollywood just get accused of decades of \textbf{sexual} abuse? Not all Jews are victims. Fuck the labels, not all people are victims. The actual people of this violent act were victims. Not the whole culture.\normalsize   & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small A growing beat by you \textbf{racist} air heads. I bet if people stopped listening to this news shit and looked within there wouldn't be as much hate to go around.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small Because of our \textbf{racist} president he make excuses  up for chaos and negative  behavior  this is what they  want divide and conquer\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small I feel bad for them.   I mean \textbf{racist} white people hate Jews almost as much as they hate \textbf{black} people but minorities think Jews are white so get the white guilt hate and blame that white folks have but technically they aren't white.    Like when Ben Shapiro explains stuff to folks he cannot even rest on his Jewish background cause no one considers them a marganalized people.  They see him as a white boy but then the Neo Nazis hate them the most but Jews are still called Neo-Nazis.  It is almost like a no win for them.  They were slaves and they were targeted for Genocide.  They have suffered throughout history under the yoke of \textbf{black} folks (Egypt) to white folks (Rome, German) to brown folks (Arabic).  No one cares about their marganilized and persecuted status in the US.  Most folks see another white guy\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/146 & \cellcolor{green!27}2.055 \\  \hline
  \cellcolor{green!5}\small \@sean roche Yeah....mine wear a ridiculous \textbf{r\textbf{ed}} cap that's made in China.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/12 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small \@Gig 'Em stop watching Rachel Maddie and your lefty news channel \textbf{witch} was proved to be lying to spread there agenda. Shot up a country western concert. Just \textbf{common} sense. They never released his political alliances. Wonder why?\normalsize   & \cellcolor{green!27}Common, Witch & \cellcolor{green!27}Gender - Female age and physical appearance, Social Class - Working class & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small VOTE \textbf{R\textbf{ED}}!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/2 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}\small White on white crime. \textbf{Nothing} new\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Everyone has to agree that no matter what this is horrible. HORRIBLE! \textbf{Nobody} can support this type of filth... Right?\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small louis farrakhan trash should be ashamed. Being a \textbf{black} man in America, wasn't it the Jewish community that stood by the \textbf{black} community during the civil right movement?... don't worry I'll wait.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small He wants a \textbf{zero} tolerance act for hate on Jews. What about other races?\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I hope to God that America will be cured from all this hate and violence. Because all you oblivious haters who support Trump, that stands by a \textbf{Nazi}, or KKK symbol, will be brought to justice, and so will Trump.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Its sad to see that you can be killed and persecuted in this country just for the color of your skin or the why you choose to worship. Meanwhile the people who commit this crimes are held up by own President and many of his supporters( i say many because some still have the heart to stand against him and what he stands for) as so called "real American". Im sorry but this is not making America great again, but it is instead returning this great country to a time when many of it's citizens have to fear for their lives everytime they leave their homes. We have to stop this! If not for ourselves, then for those that come after us. For is this really the legacy that we want to leave our children? One of hate and division? I for one say no! So i call on all of you and ask you to rise up the only way that we can and vote people who push hate and seed evil( like our president) out of office. So that we may right the ship and steer our country into the future the right way! Or stand back and do \textbf{nothing}, and watch as it sinks into the darkness of a past that so many fought and died to free us from! The choice is ours\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/227 & \cellcolor{green!5}0.441 \\  \hline
  \cellcolor{green!27}\small When all american politicians kiss Nethaniahu's ass or some bankers asses , people are fed up with that , but unfortunatly ordinary jews have to suffer for the horrors comited by their 1 . People should not blame ordinary jews for what others do.People should blame the 1 jewish and non-jewish alike . \textbf{Nobody} should suffer becouse he or she is part of a certain \textbf{ethnic} group or a certain religion. Everybody should be responsible for its own actions. Why deranged people are allowed to carry weapons beats me . Next mass shooting will happen on a school or in a Sinagogue , Church or a Mosque becouse an idiot is allowed to own a gun or he bought a weapon in some carparking.\normalsize   & \cellcolor{green!27}Ethnic, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/124 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small I like how CNN says "dramatic \textbf{spike}" yet this is the first week they ever reported it.\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Trump has \textbf{nothing} to do with it. It was here long before him will be here long after him.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Trump is the new \textbf{Nazi} party. Maga\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Thank you Mr Trump for all your efforts to make these freaking nut cases come out of there hell holes! Still think there was good people on both sides! For your own benefits you have awoke these \textbf{Racist} SOBs\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Why would anyone ask its because of the orange buffoon and the people that turn and \textbf{blind} eye and support him.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small I wish some \textbf{dumb} trumptard tries to come at me with this \textbf{racist} crap.\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Is this an example for America great again?Mmmm 🤔 ? Lets see if taking every races that they thought they wanted to get rid off out of USA I'm wondering if these \textbf{crazy} ppl will be happy?!?!Trump brainwashed them real good!  What a evil!\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small It's almost like there's a \textbf{Nazi} in the Whitehouse...\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Our \textbf{nation} is divided thanks to Jewish revolutionaries.  You have Jews, Jesuits, \textbf{L\textbf{G\textbf{BT}}}, and people of color, all of them ANTI-CHRIST on the one side, and on the other White \textbf{race} Christians, white \textbf{race} people in general.  People of color who are Christians and or patriots.  All for Christ.  This time in our \textbf{nation} will make us either for Christ, or for all the Judaized left, anti Christ.  Who will win?  Those for Christ because the USA is the home set aside for those who serve Jesus Christ.\normalsize   & \cellcolor{green!5}LGBT, Nation, Race & \cellcolor{green!5}Ethnicity - General, Nationality - General, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}7/88 & \cellcolor{green!5}7.955 \\  \hline
  \cellcolor{green!27}\small Trump has transformed the Republican Party from an honorable American institution into the most dangerous domestic \textbf{terrorist} organization America has ever witnessed.\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small Not to sound divisive, but why is it an issue now that Jewish people have been attacked. Really I just want to say welcome to the fold. \textbf{Black}, Brown, Asian the numbers have been going up. This is not a now issue it's been an issue. We should just ban together and push out all the hate groups. No more riots in the streets, just tactical assaults on EVERY hate group until they are scared to show themselves again.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small To much division \textbf{racism} and corruption . No wonder America is a extremely violent. No one seems to get along even on social media is a political war. Canada is cold but peaceful.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small Sadly, Jim Jones managed to get his following by offering people an alternative to the \textbf{racism} in America... that's how, and according to him "why," Jonestown was founded. Only then did he go \textbf{crazy} with power and kill everyone. The worst among us often masquerade as the best among us. :( (Not saying anything about Trump, just commenting on Jones.)\normalsize   & \cellcolor{green!5}Crazy, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/60 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Jack Darcy Im not talking about his position on jews specifically.I said that there is a whole set of \textbf{crazy} people (alt right, white supremacists) who believe in jewish conspiracy theories regarding the new world order and orchestrated events like the \textbf{migrant} caravan, etcAgain, Trump is the symptom of a larger problem, one that has been incubating for decades.\normalsize   & \cellcolor{green!27}Crazy, Migrant & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small The only people talking about Jewish conspiracies are you and the desperate delusional left. It seems the left loves Nazi's, slavery, \textbf{racism}, \textbf{sexism}, communism, Marxism, pedophilia, rape, and many other twisted subjects. It's a coalition of \textbf{mental} midgets.\normalsize   & \cellcolor{green!5}Mental, Racism, Sexism & \cellcolor{green!5}Ethnicity - General, Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/38 & \cellcolor{green!5}7.895 \\  \hline
  \cellcolor{green!27}\small Avelier Plays I don't agree with trump on many things.  But his statement towards these fucktards was a strong one.   Not a republican and sure the fuck not a douche bag liberal. But I will stand with trump if these white supremacy fucks that they can start hunting Jewish people then we will hunt them!   And as far as you liberal fuck goes.  Just stop spreading your fucking hate!!! You are no better than these skin head fucks don't need them nor the white liberal so fuck off nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small But CNN lit a fire under it's ass. But \textbf{nobody} mind's because they made the white man the boogey man. Boo\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small they already caught the spray painter... it was a \textbf{black} man\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/11 & \cellcolor{green!27}18.182 \\  \hline
  \cellcolor{green!5}\small Yeah you're right. I mean just a while ago i saw this propaganda video with these slimy \textbf{old} people looking like hateful jewish caricatures making fun of young people and smugly declaring their support of trump.Oh, wait. The democrats made that one. I take that back, it's not antisemitic when the left does it.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small \@Patti Diggs When trump said there were good people on both sides, he meant not everyone on the right wihpng side was affiliated with the KKK. But apparently saying not all Republicans are hateful baby eating biblethumpers, is hateful and \textbf{racist}. Do you people even use brains?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@Avelier Plays you apparently hate yourself and all those that came before you. As for a good portion of us, who are not mixed, we would like it to stay that way. Muhammad Ali once said blue birds for blue birds, \textbf{r\textbf{ed}} birds for \textbf{r\textbf{ed}} birds. Was he wrong? Is he a horrible person who should have never existed? Maybe even \textbf{racist}? Oh no because only whites are \textbf{racist} for calling a \textbf{spade} a \textbf{spade}. You should fook off and leave the rest of us alone.\normalsize   & \cellcolor{green!5}Racist, Red, Spade & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}8/86 & \cellcolor{green!5}9.302 \\  \hline
  \cellcolor{green!27}\small \@paper airplane LMFAO the \textbf{racist} thinks conspiracy theories are "truth". How adorable. So tell me, is the earth flat?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Proud Zionist How's the view from ethnocentric Israel? I wish I could come and bring my morals, values and merit but unfortunately you're all racists there and don't accept other ethnicities. Fuck off \textbf{racist}!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small Where will he go next, this phantom from another time, this resurrected ghost of a previous nightmare – Chicago? Los Angeles? Miami, Florida? Vincennes, Indiana? Syracuse, New York? Anyplace, everyplace, where there's hate, where there's prejudice, where there's bigotry. He's alive. He's alive so long as these evils exist. Remember that when he comes to your town. Remember it when you hear his voice speaking out through others. Remember it when you hear a name called, a minority attacked, any \textbf{blind}, unreasoning assault on a people or any human being. He's alive because through these things we keep him alive.- Rod Serling Twilight Zone Closing Narration- January 24, 1963\normalsize   & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/109 & \cellcolor{green!27}0.917 \\  \hline
  \cellcolor{green!5}\small Trump and his \textbf{racist} followers are disgusting.  Lower than human shit.  All of them.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small When \textbf{Black}, Hispanic, Asian \textbf{racism} occurred, All Media \& Trump were very quiet.  Whenever Jews got attacked, All Media \& Trump act like whole \textbf{nation} is falling down.  It self is a \textbf{RACIST} ACT, CNN!\normalsize   & \cellcolor{green!27}Black, Nation, Racism, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Nationality - General & \cellcolor{green!27}4/35 & \cellcolor{green!27}11.429 \\  \hline
  \cellcolor{green!5}\small But you'll say Jews have 80 of highest paying jobs , most of them are "well off" and white privileged or maybe because they're actually smart and loyal to their religion? , but obviously you don't care that since Trump was elected 35 increase in Anti Semetic incidents occurred back in 2016? You're the only \textbf{Nazi} here hating Jews , again hypocrite. And I'm full blown Mexican so fuck you calling me biased or Uncle Tom 😂 I care for where I'm living , America ! Red\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}\small they already caught the sparay painters... \textbf{black} kids\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Just what happened a \textbf{crazy} white guy killed \textbf{Black} people in the Mall in Kentucky. First thing the news does blame guns or \textbf{Racism}. But doesn't blame that we need \textbf{mental} health and healthcare for people. This happened 'OMG not the Jew it's anti-Semitic. Fuck the guns it's a anti-Semitic a attack guys. We need to worry about this shit.'\normalsize   & \cellcolor{green!5}Black, Crazy, Mental, Racism & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/60 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Found the anti-semite!Anti-black and latino \textbf{racism} have DOMINATED the news for years now.  Ever heard of BLM?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Jew controlling the Media attack on Latino and \textbf{black}, white.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small There is a jew actor pretending he, not jew but he Youtuber agent, That expose jews basically a being a shill. What he doing attacking free speech on youtube. So if you say anything about jews you are banned.  Meanwhile there \textbf{racist} \textbf{black} /white/Hispanic video untouched. Please go look for a channel called handsometruth15 aka real name Ron minadeo. he is jew actor from California pretending to fight jew supremacy. so youtube oppressed your speech on youtube.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small \@A!V3n . . maybe they are \textbf{Communist} and steal everything they get through Nepotism......\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I never got it. There still white, it's just a different religion. I mean, I still don't understand why the hate us \textbf{black} ppl. But I can't get into the WST mind. It's too dark of a place! 😤🖕🏽🤬🤔\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small I think we should all continue to hate and kill each other until there is \textbf{nothing} left to spite anymore.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Smh these guys big mad fr...who even got time or want to be a \textbf{nazi} in 2018.  We got internet porn video games food for delivery on speed dial...these dudes got entirely way too much time on their hands. I literally wake up woke from 330 am till 2pm and wanna go home and pass out for nap wake up and play some games or fuck.   Who has energy for \textbf{nazi} shit frfr\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/73 & \cellcolor{green!27}2.74 \\  \hline
  \cellcolor{green!5}\small And here i am I'm still waiting for the white supremacist who killed those two \textbf{black} people to be charged with a hate crime. The justice system is quick to charge this man with a hate crime but when it's a white supremacist killing \textbf{black} folks..."stop \textbf{race} baiting", "He was mentally ill", "let's not jump to conclusions here. That's America for you born out of white supremacist and will die by it.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/72 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small If u see a \textbf{nazi}, kill it..kill it dead and laugh your balls off while doing it...\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Ever since  the kkk and \textbf{Nazi} movements began there was a fringe group of antisemitism. When Trump began his presidential campaign he encouraged and enflamed with his rhetoric these fringe groups. He admired Hitler, and other modern dictators who used hate speech as strong leaders to pattern himself by. Even when he declaims antisemitic behavior he still calls these neo \textbf{Nazi}, and white supremicist groups "good people", encouraging them with his rhetoric to more violence. And too many Americans are buying in to all that venom  and treating it as acceptable and normal to do such evil.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/97 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small The Democratic leaders are the Nazis. Lying to the \textbf{black} communities for their vote. Look at your cities. What have the left some for the\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small To anyone genuinely interested in the source of the horrific events of recent times, I implore you to wrestle with the writings of the greatest philosopher and political thinker of modern times - Alain Badiou. One of Badiou's central propositions is the followiing: the State is not the expression of the will of the people; the State, rather, is an injunction against civil war. American capitalism has been in a heightened state of tension since the 2008 economic crash. This is because the gap between the free market and the State was closed when the Federal Reserve bailed out the Financial sector in order to prevent the entire American economy going under. The primary condition for civil war in American is not racial or religious. It is the violent hatred and fear of the ultra-rich for the middle-classes and, most of all, for the working-class poor. All the micro-hatreds that we now see: of liberals, of Trump supporters, of \textbf{ethnic} minorities and of migrants: all of these boil down to that fundamental hatred of the ultra-rich for the rest of America's population, whom they basically despise.\normalsize   & \cellcolor{green!5}Ethnic & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/186 & \cellcolor{green!5}0.538 \\  \hline
  \cellcolor{green!27}\small Do a story on blacks beating Rabbis in New York City. Yes, your precious \textbf{black} minority stomping the faces of Jews mercilessly in your beloved liberal capital. Quite a leftist conundrum.  Better keep sweeping this one under the rug and concentrate on those whites.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small It's ironic how all of a sudden just after this attack The Anti-Defamation League and CNN report on this. \textbf{Nothing} in the past year or two. In fact I can't remember this being a main topic in the media for a long time. When Trump moved the American Embassy to Jerusalem it's just possible some were not happy. Yet, the media again is trying to use this attack as a political hit on Trump, Fake news.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small Why is this happening? Because law enforcement sux! When a group of protected citizens gets attacked in our country by terrorists why doesnt law enforcement become proactive? Like literally putting eyes on every place of worship. Oh and feds should cover the overtime. give them \textbf{black} \textbf{nazi} uniforms also. Try some meds or something cnn. Focus on solving the problem and discuss that not the players them selves. maybe you will get your ratings back. That was the intent of a free press being a hallmark on that \textbf{old} piece of paper i got as a kid in Washington dc. In like a video i saw, or whatever, on the internet about a piece of paper some \textbf{old} guy wrote under our flag before pictures, when like when the world started or whatever, Cnn is like crack- you know its bad but you keep trying lol we should have cnn conundrum crack parties with lgbqjvdfvhk.All races, sexes, orientation, but no damn muslims, or aliens, cause aliens will kill you. i saw it in a movie with Sigourney weaver... Ha ha ha\normalsize   & \cellcolor{green!27}Black, Nazi, Old & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}4/181 & \cellcolor{green!27}2.21 \\  \hline
  \cellcolor{green!5}\small \@Manbun Reactionary Lol you know \textbf{nothing} about me. You assume too much. I'm hardly your stereotypical Jew. In fact you'd never know unless I told you. Be careful. You and your kind could get yourselves hurt.Define whites?\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@Manbun Reactionary You're priceless. So you're sure you could identify me as a Jew based upon my supposed ancestors? Who are my ancestors? Do you know my \textbf{nationality}? What country am I from? Describe my daily appearance. What do I wear? You already have my beliefs wrong. Not Hasidic either. Let's see if you can get something right. Assumptions are very dangerous. You really should be cautious. By the way, I loved the anti-white part. Lol! You never defined "white" by the way.\normalsize   & \cellcolor{green!27}Nationality & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/83 & \cellcolor{green!27}1.205 \\  \hline
  \cellcolor{green!5}\small \@namo234 You have the wrong person for many reasons. You know \textbf{nothing} about me. 😉\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small \@namo234 Like I said, you know \textbf{nothing} about me. And you CLEARLY don't know the majority of Jews. You can't learn Judaism from YouTube. Keep in mind that ALL people can convert to Judaism. So there is no exclusion of anyone.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small Engineers Quest I know the majority of Jews you are like that.And people would be considerd inferior before converting to Judaism it's written in your own frigging holy book.\normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small \@namo234 You've only read lines I'm sure. Studying the books is something totally different. Learning from a Rabbi teaches you the true meanings of what the books show you. Judaism is \textbf{nothing} like you believe.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small Engineers Quest  [LINK] \normalsize   & \cellcolor{green!5}Engineers & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small Always interesting there's never more \textbf{racism} and white supremacy, than near elections and always dug up by the Left....then like magic, it all goes away. \textbf{African} Americans know it better than anyone, the Dems show up for the vote and disappear like a thief in the night, see you again in 4 years.....\textbf{African} Americans....What the Hell do you have to lose???? Vote \textbf{R\textbf{ed}}.\normalsize   & \cellcolor{green!27}African, Racism, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}5/63 & \cellcolor{green!27}7.937 \\  \hline
  \cellcolor{green!5}\small Farrakhan is not anti-Semitic! What pissed me off is that if CNN can talk, and have interviews with a \textbf{nazi} who assaulted you, why can't they talk to a man( Farrakhan) who has changed the lives of people for the better?!\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}\small Hitler didn't die he lives in Republicans!   Republicans are the real \textbf{terrorist} threat!   And Trump is a clear and present danger to democracy!\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small The Nazis are a fucked up \textbf{race},same as the Germans fucking horrible cunts another fucked up \textbf{race}.fucking horrible people still to this day they are a odd lot.\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small FUCK \textbf{RACIST} FUCK \textbf{RACIST} TRUMP SUPPORTERS\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small We all bleed \textbf{r\textbf{ed}} blood. We're all all human beings.\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small I'm waiting for the \textbf{black} people to jump on the bandwagon on which \textbf{race} was handled differently during these tragedies\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/20 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small I live in indiana and the \textbf{racism} is in 98white small towns\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small You moron. The USA used to be 90 percent white until Jews changed the immigration laws to intentionally replace whites. Replacing any \textbf{ethnic} demographic on purpose comes with resistance. America is not a melting pot and \textbf{nobody} that says they love multiculturalism actually wants it in their own country. Muslims were brought in by Jews and Jews have been their voice since arriving. Time Jews showed us how to be tolerant in their own country for once. openbordersforIsrael .\normalsize   & \cellcolor{green!27}Ethnic, Nobody & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/79 & \cellcolor{green!27}2.532 \\  \hline
  \cellcolor{green!5}\small I wonder why? Oh wait, we have a blatant \textbf{racist} pretending to be our president , and telling everyone following him that it's okay to be a \textbf{racist}!! \textbf{Nothing} but evil in the White House now! Everyone who isn't \textbf{racist} can see it! Very very sad 😔\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}4/47 & \cellcolor{green!5}8.511 \\  \hline
  \cellcolor{green!27}\small Are you fucking kidding cnn?? 'Trump is too close to Jews and shouldn't move embassy to Israel' and now he is motivating anti-semites?? No you liars. It's your leftist pro-Palestinian communist/anarchist who attack American Jews. \textbf{Nazi} are socialists too btw. The pro-palestinians have been calling in attacks on Jewish centers all year and the leftist Muslim community, who can do no wrong to you, is directly involved. Your womens March organizer is a Hezbollah and Hamas supporter. Fuck you. Get your heads out of your ass and report the news. You look like a bigger baby then Trump rn. You cant help but steep to such a low level against him. That's why views are down and that's why internet news will destroy you talking heads\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/126 & \cellcolor{green!27}0.794 \\  \hline
  \cellcolor{green!5}\small Trump and the Neo Republicans empower White \textbf{Nationalism} and Fascism! America became absolute SHIT!\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small FAKE NEWS ONCE AGAIN FROM THE LEADER IN FAKE NEWS , FUNNY THING IS HE HATES TRUMP AND IS A LEFT WING  SUPPORTER, Trumps  Daughter , grandkids and son in-law are Jewish , shame on you CNN. THE BIGGEST THREAT TO AMERICA IS THE \textbf{LIBTARD} LEFT AND THE FAKE NEWS MEDIA .\normalsize   & \cellcolor{green!27}Libtard & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small I'm white and I want every remaining \textbf{Nazi} and every \textbf{nazi} sympathizer dead. There goes your stupid fucking argument.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Janice Van Horn He's done \textbf{nothing} to condemn white nationalists. You know...the guys who chant ‘Jews will not replace us'?  Trump's has a long history of bigotry. And his inflammatory rhetoric inspired these latest attacks. He's failing epically at being a leader to his people.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small The left hated Bush with a everything they had. Bush had 2 wars going on and a horrible economy.  Trump has \textbf{zero} wars and has created the best economy in 50 years. The left hates Trump with everything they have.   Maybe it ISN'T Trump,   Maybe YOU are the ones full of hate !\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}\small That synagogue that had the \textbf{Nazi} flag spray painted on their sign is in Carmel, IN, north of Indianapolis. That one was all over the local news.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small What about Islam.  Israel is surrounded by Muslims who hate her.  They call for the complete annihilation of Jews.  There numbers far surpass white nationalists.  It's good someone is shining a light on this.  Jews have suffered more then any other \textbf{race}.  Iran calls us big satan and Israel little satan.  There's much more unity between Christian and Jews then muslims and Jews.  With a growing Muslim population, I think this problem could get worse.  How do we fix this?  Scary!\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}\small It's just kids spraypainting swastikas. They think it's funny, but they dont understand. Trying to scare \textbf{old} ladies? It works. Orange Man bad\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small So \textbf{weird} how ppl, for millenniums, have disliked jews. It's almost like there's a reason.\normalsize   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Oh bullshit, stop blaming trump, he supported Israel, while the left demonizes Israel. When a \textbf{terrorist} attack happens an it was a Muslim, the left goes notallmuslims there "peaceful", but if someone is a \textbf{racist} the left blames all trump supporters for one shitty persons mindset. Hmmm? Doesn't sound hypocritical. Good job CNN way to keep up the division of American for views an a political agenda. Clap... Clap... Clap... An you spergs just eat this shit up without doing your own research.\normalsize   & \cellcolor{green!27}Racist, Terrorist & \cellcolor{green!27}Ethnicity - General, Religious Identity - Muslim & \cellcolor{green!27}2/83 & \cellcolor{green!27}2.41 \\  \hline
  \cellcolor{green!5}\small That looks like it was done by some kids.When I was 13 me and my friends would graffiti swastikas for shits and giggles because it rebeled against the establishments norm, I was never a \textbf{Nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small The Mocking Bird Fake News Media creates \textbf{racism} and wants us divided to keep us distracted from what they are doing behind the scenes....its soo good to see \@kanyewest not buying their lies and destroying the Liberal Agenda with peace and love!\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Hillary Clinton believes that all \textbf{black} people look alike. Fake news CNN agrees.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Great going CNN for creating all this hatred and fake news.  thanks a million.  If you're looking for someone to blame, look in the mirror.    \textbf{R\textbf{ED}} WAVE COMING  HOPE YOU GUYS DON'T CRY ON TV AGAIN  DON'T WORRY, I'LL BRING SOME TISSUE\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small You can thank the \textbf{spike} in jews running the world themed videos on youtube thats where all of this is coming from lol\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Wake up Jews.  I say this lovingly as a \textbf{black} person... wake up.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Nazis were chased down and tried for war crimes. And some of them were executed. Now, there are \textbf{Nazi} sympathizers lives in your neighborhood and y'all didn't do anything? From Nazis to Moslem extremists, I don't get why they just don't build a country for themselves, live with their own rules, and stay the fuck out other people's business?! I mean, if they hate a certain \textbf{race} or a certain religion that much, why don't they go find an unoccupied island somewhere, start their own country, and don't deal with the rest of the world?? If they're really that superior, I'm sure they can do that on their own and be superior in their own "country". So when they feel like wanna be superior in another country, that means fucking war! Get your own fucking "home"!\normalsize   & \cellcolor{green!5}Nazi, Race & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/136 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small If Civil War is brought to our doorstep by Nazis and White Surpremists simpathizers, than its clear that such a War will be needed just to remove the  degenerate influences of Old-World \textbf{Racist} thinking.  This can't go on any longer!   The world needs to change, and while I do not agree with the willingness to act on war.  The Very Lives of the many Good people in various racial communities and LGBTQ, are being endangered by a very Cowardly lot of individuals who desire \textbf{nothing} but to bring death and chaos to many Innocent People without remorse, just fulfill some belief having an All-White American Christian Catholic Non-Gay Society!   And it's sad!\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/112 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}\small If Trump was \textbf{black} all these clowns would be following him\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small I'm sorry everyone if the democrats take the house which I think they will and their is someone to slow trump's  \textbf{Racist} politics down it's only going to get much worse all of this is going to get much worse we all might as well prepare  It is almost all I can think of every day how badd things have gotten and how much worse they're going to get I never thought someone the likes of him  Could tear us apart\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Cnn is why.. antifa and \textbf{black} lives matter\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small "\textbf{Zero} tolerance policy on intolerance"  Yeah fuck \textbf{racism} against Jewish, wish the same could be said for \textbf{black} people\normalsize   & \cellcolor{green!27}Black, Racism, Zero & \cellcolor{green!27}Age - Youngsters, Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/19 & \cellcolor{green!27}15.789 \\  \hline
  \cellcolor{green!5}\small Hey CNN, are you going to report on Hillary saying all \textbf{black} men look alike?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small If I may try to explain this 'spike', in my perspective at least Long Island, NY - I saw a Perry Gershon ad saying he was gonna protect Soc Sec, and Medicare, and spoke of Trump's massive tax cuts to the wealthy, hurting the middle classLee Zeldin - a Trumptard, talks about MS13 \& sanctuary city taking over, oh my! My folks live on LI, and at 70 they know that's all over-hyped bullshit. However, Other then that, Zeldin has no policy Anti-semitism, \textbf{racism}, \textbf{xenophobia}, ALL of it is on the rise, and its not just Trump's fault. Its the GOP tactic. That is what they run on since their economic policies are the worst! (Especially for the middle class) They're feeding the American public fear in order to say in power because they have \textbf{nothing} else to offer\normalsize   & \cellcolor{green!27}Nothing, Racism, Xenophobia & \cellcolor{green!27}Age - Youngsters, Ethnicity - General, Nationality - General & \cellcolor{green!27}3/140 & \cellcolor{green!27}2.143 \\  \hline
  \cellcolor{green!5}\small Isn't Trump's son-in-law, daughter, and grandchildren Jewish? What the hell is wrong with this damn country? America is a country for all people whether of their religion, \textbf{race}, etc.?\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small Maybe CNN should stop calling everyone and their grandma "\textbf{racist}". This showed what a real \textbf{racist} is and how serious of an accusation it is. No one outside the furthest left takes them seriously when they constantly cry wolf.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small To admit there are different races of mankind that have different cultures makes you a \textbf{Racist} by default !!!   To admit there is a male and a female makes you a sexist by default !!!   The only way out is to say Reality is Fake and make your own !!! 'Those who are able to see beyond the shadows and lies of their culture will never be understood, let alone believed, by the masses.'  ― Plato\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/76 & \cellcolor{green!5}1.316 \\  \hline
  \cellcolor{green!27}\small Fuck Trump  is a troll/bot anyway.Couldnt tell you anything \textbf{racist} that Trump has done nor anything anti-semitic....  Liberals are famous for not letting facts get in the way of good propaganda\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small Virtue signaling at its best "im not \textbf{racist} I love all \textbf{black} people and whamen" ( I hope someone sees all the things I write here so I can get some street cred at the next Antifa mixer)\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Nothing} O Its attitudes like this that makes me lose faith in humanity...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Lol Trump is in your head that much you had to change your name to "Fuck Trump"? lololol. Is this your life goal now? Admit it you would have \textbf{nothing} to do without Trump. You need something to hate. I mean look at you your life is revolving around hating 1 single human on this planet. Guess what Trump will come and go, your life won't and you're wasting your time being so upset.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}\small Once Obama got into office, I heard news reporters and the media swear that this was the..Post Racial Era. \textbf{Racism} is over really?\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small NEWSFLASH📣📣📣 The "REAL JEWS" are God's chosen people... they are the \textbf{black} "HEBREW ISRAELITES" aka "12 Tribes of Israel"🇮🇱✊🏾 ...not AFRICANS🚫...not EGYPTIANS🚫...not ARABS🚫...not EUROPEAN ASHKENAZI ROMAN JEWS🚫! ➖➖➖➖➖➖➖➖➖➖➖➖➖➖➖ ...What group of TROUBLED people did Jesus call POOR? (\textbf{Black} Israelites) ...Why did Jesus call the "ASHKENAZI/EUROPEAN/ILLUMINATE JEWS" ...fake Jews? ➖➖➖➖➖➖➖➖➖➖➖➖➖➖➖ ➡️Revelation 2:9⬅️ 'I know your troubles, and I know that you are poor, but really you are rich! I know the insults you have suffered from people who say they are Jews. But they are not true Jews. They are a group that belongs to Satan. ➖➖➖➖➖➖➖➖➖➖➖➖➖➖➖➡️Revelation 3:9⬅️ Listen! There is a group that belongs to Satan. They say they are Jews, but they are liars. They are not true Jews. I will make them come before you and bow at your feet. They will know that you are the people I have loved.400YearsOfSlavery 1619-2019HebrewIsraelitesInAmerica\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/147 & \cellcolor{green!5}1.361 \\  \hline
  \cellcolor{green!27}\small Sumumma Bish ummm, the rise in white nationalists is in response to the rise in left wing identitarians. Jared Taylor and even the more extreme white nationalists have been quoted as recently as 3 or 4 years ago that they love identity politics as it's resulted in a \textbf{spike} in their numbers.\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small You would do anything for votes lol... Newsflash 🚨 \textbf{Dumb} ppl react off of feelings and ppl with sense act off of facts... The President had \textbf{nothing} to do with the act of an individual that doesn't share his outlook on life. But continue with your fear mongering tho, hopefully you relocate to Canada or Venezuela.\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/56 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Wow... he used a stereotype that Jews are good money handlers....... yup. Thats it right there. Thats like one step away from the Final Solution....So, everyone who says something like, "white people cant dance" is a total \textbf{racist}. "Blacks are pretty good at basketball" I guess thats a dog whistle for bringing back the \textbf{Jim C\textbf{row}} era?Really, thats a long way from being anti-semitic... and even farther away from inciting violence and murder against an entire group of people.Try again.\normalsize   & \cellcolor{green!27}Crow, Jim Crow, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/83 & \cellcolor{green!27}3.614 \\  \hline
  \cellcolor{green!5}\small And regarding the "not replace us" thing... is that a reference to Charlottesville? I seem to recall Trump, more than once, disavowing white \textbf{nationalism}.... as well as denouncing the violence... though he said "violence on both sides" I guess that meant that he hates blacks.......    What is he supposed to do to 'defend' people against that? Round up white nationalists and execute them? I think Trumps actions over and over, including his policy decisions show that he is in no way anti-semitic.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}\small Typical leftist garbage.  "If you are <insert group of people> and you vote for Trump, you are a race/gender/creed traitor, and you are complicit in everything".  That attitude is completely divisive.  THAT is the language that divides people; the language of "all Blacks/Jews/Women/etc. MUST vote Trump out" is how tribalism starts.  THAT is literally dividing people by group.  THAT is \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}\small your mom how about you stand up for Jewish people in the United States not just the ones on Israel? Oldest stereotype in the world are Jews are good woth money that's why it's \textbf{racist}. It builds hatred from those who think by being good with money they have it all and take it from  every day white people. Everything is dependent on how your followers take it\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/68 & \cellcolor{green!5}1.471 \\  \hline
  \cellcolor{green!27}\small Douchebag brigade, funny thing is there were only two viable candidates last general election. One that acknowledged FACTS that there were good people and bad people in BOTH crowds, and the other who just recently joked, "that they all look the same" when an interviewer was confusing booker and holder, she has also gone on the record as stating that "young \textbf{black} males are SUPER PREDATORS". So which one is the \textbf{racist}?Edited to ad link [LINK] \normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/77 & \cellcolor{green!27}2.597 \\  \hline
  \cellcolor{green!5}\small That's y'all problem that man had \textbf{nothing} to do with those people getting killed i guess he had something to do with 9-11 y'all mad Trump is president he was put there to clean up Washington an he doing a good job how can you so call work for the people an in a few years you rich something is not right an just look around you this is going to hell with those so call leaders of theses states all they do is LIE look at these neighborhood around the U.S. an they worry about letting illegals in the country hay i think we need to fix our citizens an country so when President Trump say we are not going to let them in i am 💯 behind him an all Americans should be too🇺🇸🇺🇸🇺🇸🇺🇸\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/136 & \cellcolor{green!5}0.735 \\  \hline
  \cellcolor{green!27}\small Larry Grogan she was sarcastically knocking the lady who messed up his name. Let's be honest she was chastising the other \textbf{woman}. We all know that trump is the most anti minority president of all time. His rhetoric got two \textbf{African} Americans killed outside a Kroger\normalsize   & \cellcolor{green!27}African, Woman & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/46 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Douchebag brigade, let's imagine trump said EXACTLY what she said. You would claim it as another example that he is \textbf{racist} yet when she says it she gets a pass. Remember her talking about super predators ? She was talking about inner city gang members primarily young \textbf{BLACK} MEN. Face it she supports racists, even holds them up on a pedestal can you say ROBERT BYRD ? Look him up, watch his services, the Clintons speak glowingly about that \textbf{RACIST}. The democrat party's  history can not be refuted, the Clintons history can not be refuted. Go find a mirror and accept it, you support the party of \textbf{racism}. And yes there were violent idiots in both crowds in Charlottesville to deny this fact is ridiculous. The counter protesters had people that were there looking for trouble as did the initial protestors.\normalsize   & \cellcolor{green!5}Black, Racism, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}4/141 & \cellcolor{green!5}2.837 \\  \hline
  \cellcolor{green!27}\small Douchebag brigade, and as for trump being the most anti minority president in history ? He must be a really \textbf{dumb} \textbf{racist} as his policies continue to elevate minorities of EVERY DEMOGRAPHIC. When you look at unemployment and income numbers for every minority group their unemployment numbers are at historic lows and their incomes are at historic highs. Accept it trump is doing great things for minority communities his policy effects speak louder than your rhetoric.\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/76 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small Larry Grogan one I wouldn't say he's \textbf{racist} for making a comment throwing someone else's questionable comment out there as a sarcastic joke but more importantly they're no place for kkk fighting against them shouldn't be looked down at. Now trump bans multiple minorities from coming wants to get rid of birthright which in the past effects all of our ancestors and now I'm suppose to say he isn't \textbf{racist} when at every rally his rhetoric causes white supremacist and those secretly \textbf{racist} to come out and commit heinous crimes? Listen economic changes take years Obama's moved us in a good direction and you are acting like trump is the one helping put minorities on the map. Fiscal conservative techniques don't work tax cuts for corporations do not mean a better wage for the employees meaning there is no trickle down. I'm sorry but this president is a monster and a bigot any way you dice it, you can give me examples of other people making statements but you can't defend him. He is literally a hate spewing fear mongerer. No care for the people just for his own interest like most politicians but times a thousand\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/197 & \cellcolor{green!5}1.523 \\  \hline
  \cellcolor{green!27}\small \@your mom as you know it is not the strategy to be openly \textbf{racist} anymore. You have people in the KKK swearing \textbf{black} and blue that they are not \textbf{racist}. When you have a group of nationalists chanting JEWS WILL NOT REP,ACE US and then your leader claiming there are fine people within that group ....it's not rocket science. These people are part of his base and he is happy to endorse them.\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/73 & \cellcolor{green!27}4.11 \\  \hline
  \cellcolor{green!5}\small Mana Coromandel thank you because for some reason Larry thinks that's the status quo. If it is than trump made America great again for Larry but that's the America I want to live in. No matter what you say Larry nor regime dem or rep has had openly \textbf{racist} backing.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}\small Larry Grogan Larry all I have to say is we have a \textbf{dumb} president who thinks he's above he constitution and he is getting rid off the ability for people born here to be citizens. In that world none of us are citizens unless you are Native American\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small If anyone dies of anything even \textbf{old} \textbf{age} blame TRUMP vote against him or your just as guilty as father time.\normalsize   & \cellcolor{green!5}Age, Old & \cellcolor{green!5}Age - General, Age - Over 65s & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small If you are Jewish and have vote for Democrats then YOU are responsible for the replacement of the white European majority that build the USA (which makes you genocidal) and as well as having blood on YOUR HANDS for every person murdered by an \textbf{immigrant}, which is a lot more than the 11 grannies in the synagogue. Since Jews love immigration so much then why is Israel a closed borders Jewish supremacist state? openbordersforIsrael\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/74 & \cellcolor{green!27}1.351 \\  \hline
  \cellcolor{green!5}\small the caught the spray painter... a \textbf{black} man\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small It's not on the rise they're taking a few extremely rare cases of some \textbf{crazy} people and trying to scare people into believing it's everywhere. The fake news strikes again. Give me an anti Semite quote from Trump I bet you cant find one.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small Trump ran on a platform based on closing the borders, getting the US out of wars and stopping SJW. The Jews were one of the loudest, vicious and nasty voices to stop all these three points: they want open borders, they want to involve the US in wars (against Russia, for instance) and they are one of the loudest supporters of SJWism. People are just tired of fake news, anti-white \textbf{racism}, open borders to import low-wage workers and make white people a minority and starting WW III against Russia. They are also tired of the hypocrisy: the Jews want an ethnostate for themselves, but open borders for others. And when someone harms Jews, it's 24/7 news. But all the hate crimes against white people who are literally getting REPLACED right now by mass-immigration and no one bats an eye...\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/139 & \cellcolor{green!5}0.719 \\  \hline
  \cellcolor{green!27}\small Social media, mainstream media, etc. They add \textbf{nothing} but fuel to the flame.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small hitler and the \textbf{Nazi} party were funded by Zionist wall street bankers leading up to world war 2\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Things many times get worse before they get better. This \textbf{nation} has always had this cancer inside of it but now it's time to deal with it, so like any other healing process it gets painful and seems to be getting worse when really the root of the problem now is being dealt with and healing and restoration will soon happen if we ALL humble ourselves.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small \@Sonsarae ronnow Our fight is not against flesh and blood.. If you don't know who your true enemy is you won't stand a chance and this \textbf{nation} will come to self destruction.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small Oscar Dominquez. The more you force people of different backgrounds to live together the more conflict there is. Immigration should not be forced onto an existing group and it should only be done with people that genuinely like the country they are moving to. White Americans are feeling pissed but any other group would feel pissed if they were being replaced as well. The worst thing about all this is that Jews are driving open borders for USA while they make sure immigration is limited ONLY to \textbf{ethnic} Jews.\normalsize   & \cellcolor{green!27}Ethnic & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}\small Into white nationalists get kill in large number that when Trump will do something because a dead \textbf{nazi} can't vote.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Showing \textbf{nazi} imagery on theyre channel isn't smart, they blame trump for this yet they show this, do they no realize it will only cause more problems to rise by showing? It will encourage more because they are giving the negative more coverage. Has anyone realized this yet? Because do they know alot of different people watch their channel because, and one could be an antisemitic person watching this just think about that\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small Nazi Bastards! Rot in hell motherfuckers.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Proud Zionist they pour mass immigration into every white country they control all the media and academia. This is a proven fact look up who's pouring billions into \textbf{migrant} caravan since 2015 \textbf{refugee} crisis. Look up Eric Kaufmann new book end of white majorities 'white shift' these Eric Kaufmann Barbara spectre George Soros genocidal maniacs Frankfurt schooler Bolsheviks need to be eradicated\normalsize   & \cellcolor{green!27}Migrant, Refugee & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small what's all the fuss?  there is good people in the \textbf{Nazi} camp according to the "President ".\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Not every Republican is a \textbf{racist}. But nearly every \textbf{racist} is a Republican. The racists think that having a \textbf{racist} president gives them license to be openly \textbf{racist}.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}4/28 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small YOUR FROM EUROPE YOU \textbf{DUMB} FUCK!!GUESS WHAT?AT THE END!THE LAND BELONGSFOR THOSE WHO WORKED THE LAND!WICH YOU FUCKS TO LAZY TO PICK YOUR \textbf{FRUIT}!! WHEN THERE IS MO INTERNET!! YOU WONT SURVIVE, CAUSE YOU CANT EVEN KNOW HOW GO BACK TO BASIC LIVING!!\normalsize   & \cellcolor{green!5}Dumb, Fruit & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/48 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}\small N Trump will free that \textbf{Nazi} pig to pardon with hem cuz he loves his Nazis\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Come 2 da \textbf{black} community stop going 2 churches bitches weak get dat ass served\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small White people gotta go!!!!!.. \textbf{Racist} ones but.....\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small yes orange is new black\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Large number of anti-Semitic threats are later found to be done by Jews. Those are included in the fake statistics. Soros is not hated for being a Jew. He is an atheist and \textbf{Nazi}. CNN still fake news 💩\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small People who think Donald Trump is the reason are completely ignorant. Trump has never EVER said a single anti Semitic thing in his life. These attacks on Judaism have \textbf{nothing} to do with politics, but with crazed psychopaths. This is not a liberal thing. This is not a conservative thing. This is something we need to unite together against.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small have never understood why white people hate Jews...i know arabs or muslims hate jews cause of their religion...have never heard \textbf{black} or asians hating on jews....but white people, why hate jews?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small ...jesus fucking christ. Thanks trump! Vote GREEN, vote BLUE! fuck the \textbf{R\textbf{ED}} hate cult, remove these fuckers from power!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Racists and anti-semites feeling newly emboldened to act on their hate. I'm sure it's \textbf{nothing} to do with the hateful messages president Twitter sends from his toilet at 3am\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Trumpies be like "I'm not the \textbf{Nazi}! YOU'RE the \textbf{Nazi}!!" Haha, stupid Nazis.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small How can liberals be so damm \textbf{dumb}!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small What abt the 64 Palestinians and 14 kids killed by Jews, maybe he was tired of them murdering innocent I don't know \textbf{mental} health Americans\normalsize   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small But they're the same \textbf{nation}of people of japheth, thereal jews are \textbf{black}, nosich thing as jewish( ish means pertaning to, thats like saying I'm blackish, youeither are or not).\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Why Hate Crime? TrumpWhy Economic problems? TrumpWhy \textbf{Racism}? TrumpWhy terrorism? TrumpWhy problems in diplomacy? TrumpWhy are we behind in education? TrumpWhy are we not getting laid? TrumpWhy this? TrumpWhy that? TrumpWhy trump? TrumpIs there anything besides trump CNN\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small He's stumbling through the white house like a drunk leprechaun, so yeah, a lot of things are his fault. But this is \textbf{nothing} less than what America deserved for being so arrogant to elect that fuck. I am so glad that I don't live there. Cheers\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small Luis Farrakhan never killed any Jews or provoked his followers too! He never provoked violence towards anyone. He doesn't have a hateful movement why blame him!! \textbf{Crazy} always find a way to blame \textbf{black} people! I do condemn any name calling of all forms it's disgusting but blaming Luis .f who has no real platform or power in the country to someone holding the keys to this \textbf{nation} and global affairs is blame shifting\normalsize   & \cellcolor{green!5}Black, Crazy, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/74 & \cellcolor{green!5}4.054 \\  \hline
  \cellcolor{green!27}\small Like when CNN calls all Trump supporters \textbf{racist} yea not so subtle but yea CNN is full of hate\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small If you support Trump, you are a \textbf{racist}. Plain and simple. If what he says and does doesn't appal you; there must be something wrong with you. Cheers from Europe\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@Guinness  I thought not liking a person because of their \textbf{race} made you a \textbf{racist}, things must work different in Europe. Over here we don't call people \textbf{racist} with out proof cause that's rude and kind of mean. But we do hate the Irish just kidding everyone loves the Irish :)\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/51 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small TRUMP DILEMMA \textbf{NAZI} LOVETRUMP BECAUSE IMMIGRATION.\textbf{NAZI} HATE TRUMP BECAUSE HE IS PRO ISRAEL.THATS HAPPEN WHEN YOU DEAL WITH THE DEMON.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small When Blacks \& \textbf{colored} people get killed everyday, get over it they say, y'all can get over this aswell. There's no 1 side to winning this, it's together or we all loose\normalsize   & \cellcolor{green!27}Colored & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small get lost it's only ignorant people like you that will counter what I said with \textbf{Black} kill more of their own bcoz apparently you are that shallow to realise \textbf{nazi} \& Jews are both white 😅\& oh if you are going to call someone a moron online, try not to hide behind a fake account coward!\normalsize   & \cellcolor{green!5}Black, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small A white man killed eleven \textbf{old} white people. Waaaah the poor Negroes. Waaaah how the Negroes suffer. And they wonder why people hate them.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small Black dies because they are ignorant and shameful to the community.  These ppl that just died are great for the community. Big difference\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small True Confession Louis Farrakhan, Tamika Mallory, Cynthia McKinney, Trayon White, Stokely Carmichael, Tony Martin...\textbf{black} public figures, all raving Jew haters. Waiting for somebody \textbf{black} to say that there's something wrong with it.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/32 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@True Confession He does that because you're \textbf{black} \& because he hates all \textbf{black} people\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small \@Jon Lenihan Who "Jewish" have any of them murdered lil nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Jon Lenihan, eleven \textbf{old} white people? Where? All I heard of were Semitic Jews being killed.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Jon Lenihan 🔫Charlottesville "\textbf{Race} war, blood \& soil"??? So u gonna tell me that didn't happen?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@get lost with the exception of Chicago which you fucks use a "talking point" murder among blacks has gone down. They are starting to get hip to the fact ,so thank you \textbf{Nazi} fucks for showing us the light on who to turn the guns to.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/46 & \cellcolor{green!5}2.174 \\  \hline
  \cellcolor{green!27}\small \@Lyseight1 L of course it happens, but don't you think it's shocking that a \textbf{black} person is more likely to be killed by a \textbf{black} person than a white person, despite blacks only being about 13 of the population?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Elizabeth Gibson so when a \textbf{black} person dies it's because we're all ignorant and shameful? Damn that's foul. Those two poor souls in Kentucky and the \textbf{black} parishioners killed by Dylan Roof just deserved it huh?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@jbless757 Look up the facts....Blacks kill more of their own kind than any \textbf{race}...That is pretty shameful if you ask me..\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small When you're not from the USA and can't even tell who is on which side from the comments because they are all spewing hate left and right.Yes, pun intended! You people are awful, seriously. When you protect and privilege people for all eternity for something that happened generations ago they will not be liked. Affirmative action, another example. You can't force people to like people, but you don't have to hate them and want to kill them either. Guns are your problem but most are too \textbf{blind} or set in their ways to realize that. It's sad to see these reactions on a comment that tries to show some perspective and reason.\normalsize   & \cellcolor{green!5}Blind & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small \@KeiraR Our media especially CNN  has created and pushed this hate since trump won in 2016.  This country was already divided before trump even became president, but the media these days just make it worse!  Guns are not the problem....\textbf{Crazy} people with guns is though!!  I've owned guns all my life and never shot or killed anyone, but do know how to use it if needed.  Trump didn't create this division.  Division created Trump and put him into office\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small the difference is \textbf{race} is not a religion and when theres a \textbf{black} man killed every comment on that video says rip im jewish and i read these comments and all of them say f*** jews .all these ppl were just trying 2 pray and they get killed plus a person getting shot is not a massacre this is (btw im not \textbf{racist} i love all ppl cuz thats what Judaism is about)\normalsize   & \cellcolor{green!5}Black, Race, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/73 & \cellcolor{green!5}4.11 \\  \hline
  \cellcolor{green!27}\small \@get lost "guns are not the problem" We have no guns, they are illegal. If there is ever a shooting it's idiot criminal kids playing American. Our prisons are closing because we don't have anyone to put in them. No guns, none, \textbf{zero}, \textbf{zilch}, zippedydooda and hardly any real crime.Guns are for insecure people who get made scared a lot with invisible enemies. Gotta keep those arms factories running folks, as you president would say. Edit: It's not totally true, if you really wanted to you could join a club and shoot guns there. You'd have to have a psych evaluation and your guns stay at the club.\normalsize   & \cellcolor{green!27}Zero, Zilch & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}2/109 & \cellcolor{green!27}1.835 \\  \hline
  \cellcolor{green!5}\small \@your mom You can't be serious. Neither the Democrats or the Republicans care what happens to "the blacks."  They are two sides of the same coin, affluent white males on both sides. 62 of the population has 90 of the wealth in the U.S., blacks possess just 1. They are not a self sustainable, people, they control absolutely no resources. This thanks to laws on the books by Democrats and Republicans alike intended to render them a permanent underclass in this country.   It is they that have created conditions of crime and generational poverty. It is to their benefit that blacks remain powerless consumers. The Jews, like many other whites harbour a \textbf{racist} disdain for blacks. In fact, they are largely responsible for the \textbf{racist}, evil propaganda that is disseminated around the world about them. I find it ironic that the face of evil that visited them yesterday wasn't \textbf{black} at all. He looked like the white newscasters they employ, he didn't look like a "gang banger," but he came into their "house of worship" and left more people dead there than any place in Chicago yesterday. Interesting. Very interesting in deed, but keep worrying about "the blacks."\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/198 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small \@KeiraR Let me guess you are canadian or Austrailian or just some random moron????  \textbf{Nobody} gives a shit what some practically 3rd world shit hole tries to sell us!!!!  If someone wants to kill somebody they can still do it even if guns are illegal....And if your from canada knows one gives a shit , canada has sold out with its muslim loving Trudeau shitter.. I have the right to defend myself and bear arms..\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small \@Elizabeth Gibson SO for you there are categories of people. You must be the biggest \textbf{racist} and snob of all!! Every life matters whether you are a person from the gutter or the richest person Ms. Elizabeth...And yes whether you like ti or not Blacks have been brought to this country as second class citizens and are still treated this way! Lets not talk about the native Indians who don't exist anymore. So before you open your mouth think twice\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/80 & \cellcolor{green!5}1.25 \\  \hline
  \cellcolor{green!27}\small \@Nicholas Price \textbf{nigga} I am as \textbf{racist} as anyone here in america. It's america everyone is \textbf{racist} someway some how. Don't fucking lie either. If \textbf{black} are always late, asian can't drive white ppl can't dance, mexican have a lot of kids. All of that is facts and stereotypes  because it is true. Stfu don't tell me your \textbf{dumb} ass ain't \textbf{racist} before. Exactly stfu\normalsize   & \cellcolor{green!27}Black, Dumb, Nigga, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}6/65 & \cellcolor{green!27}9.231 \\  \hline
  \cellcolor{green!5}\small Thats because the KKK is the Democrats!  Do ur research! They fool u with these stories so u vote for them thinking they care about you! Democrats are the real \textbf{racist} Nazis WALKAWAY\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small See here is the thing... Us white folks... When we try to stop degeneracy we are condemned by our own people for trying to do the right thing and basically written off... So really there is no point in trying to reason with people whom dont see reason... I dont need to go through the same \textbf{old} song and dance do I?\textbf{Black} folks seem to have trouble condemning the criminals among them...Jerome Sydney BarretCurtis TuckerCharles JohnsonScott D OliverThomas YoungRonald lee KylesStanley Carter LogginsRobert Simon and Anthony CarrCurrie, Smith, Schiro, Harrison, White...Alton Coleman and Debra brownAlfred GaynorCleophus Prince JrCarl Eurgene WattsWayne WilliamsMicah JohnsonChester Dewayne TurnerNikko JenkinsLonnie FranklinMaury TravisTimothy Wilson SpencerMoses SitholeIll add more (maybe later if I dont forget...)\textbf{Black} folks... Condemn them... Or proclaim these murderers as victims of white supremacy... I dont care which 😆 I'll say in public that I condemn KKK, Nazis, Biker Gangs, Right and Left wingers,and White supremacy... In turn you have to collect the names of every \textbf{black} murderer, thug, thief, and degenerate, and make me a list of them. I'll let my people handle the rest 😈Maybe I'll even post the names of every white murderer with a kill count of over 50. Or every Rabbi with a baby fetish. Or every Muslim Rapist. Or ever Latino drug dealer. Or every Catholic Pedophile. Etc etc etc\normalsize   & \cellcolor{green!27}Black, Old & \cellcolor{green!27}Age - Over 65s, Ethnicity - Black & \cellcolor{green!27}4/247 & \cellcolor{green!27}1.619 \\  \hline
  \cellcolor{green!5}\small When Blacks \& \textbf{colored} people get killed everyday mostly by other Blacks \& \textbf{colored} people this needs to be addressed too. Get over it is not good enough.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/28 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Jon LenihanLMAO....what dumbass. Louis Farrakhan been teaching blacks the opposite. I've been to many speeches by him and never incites blacks to do what whites do everyday that is to kill kill kill. Look at your mass killings. Look at all your wars with other white nations including the dark ones. Farrakhan us right. You Are The Devil of your bible. It's whites killing whites in mass shootings. But like Farrakhan says y'all dying out anyway. You'll be gone soon and the world will soon be at peace. It's your gov't that goes around destabilising other gov't now it's finally coming home to you Esau. The cursing is now upon all white people for what you did to the real children of Israel. Not those white people who stole land from the Palestinians. They are white people who converted to Judaism. Look at everything you did to devastate the \textbf{black} community. Now it's happening to yours. Everything! I'm just sitting back watching God and Christ whip America for her evils and her sins. The only way out is to repent but if course the bible said Satan would be cast down to the bottom less pit of hell. Apparently, it's not in you to do so. Jesus said the same. He said " my words has no place in you" if they didn't hear the master Jesus. I would be a fool to think white people will get out from what's coming to them. Thank God for making trump president because trump will end America reign in the world. Thanks Father who art in heaven.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/265 & \cellcolor{green!27}0.377 \\  \hline
  \cellcolor{green!5}\small \@randomsheep11 apparently whites kill whites too. Something like 89. Statically people, regardless of colour, are more likely to kill people where they live. So it's not a problem that is unique to just \textbf{black} people.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small Here's an Idea. All \textbf{black} people should turn their guns to white people.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Biggest dumbass right here. I'm sure you're not out there preaching to the \textbf{black} community how they need to stop killing each other right? That thought wouldnt even pop into your head. Go cry about it you little baby if you cant handle life just go end it but stop blaming everyone for your problems\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Kapteeni Finland In the Americas, \textbf{race}= skin color. Different system from that of Europe. Hatred of Jews is seen here as religious hatred, not \textbf{race} based hatred.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small They already caught who di it... A \textbf{black} person, its just a cry for attention don't buy into fake news!\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The One Urban America neighborhoods change \textbf{ethnic} majorities with the changing of generations. Your Irish neighborhood may change to an Italian neighborhood. Your Italian neighborhood may change to a Chinese neighborhood. During these transitions, everyone adjusts, happily or unhappily. In changing neighborhoods, some things remain the same. Italian grandmothers in going-Chinese neighborhoods can go shopping, sit in the park, dig in the garden without fear. Children can go to school unmolested. There is only one \textbf{ethnic} group, the arrival of which signals the end of normal human society: blacks. Grandmothers will be beaten on the streets or in their yards. The new \textbf{black} neighbors will say, "Dat ole wah bitch she be deserve it." Ten year olds will be mugged by packs of \textbf{black} fifteen year olds, on the way to school. The \textbf{black} families will say, "Dey jess chillins. Chillins be do dat." Humans have something called "empathy." White, \textbf{y\textbf{e\textbf{llow}}}, \textbf{r\textbf{ed}}, brown, but not \textbf{black}.\normalsize   & \cellcolor{green!27}Black, Ethnic, Red, Yellow & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - General, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese & \cellcolor{green!27}11/156 & \cellcolor{green!27}7.051 \\  \hline
  \cellcolor{green!5}\small Deborah Devine oop ur dumb\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Thank you, Mike. I'm sad too, but I haven't given up on "US" yet. It's very humbling to see this happen. I didn't think it was possible here. I mean, i knew it was possible in the sense of "anything is possible," but I didn't think it could/would happen in my lifetime, and that if it did it woulda happened a lot more gradually. It's like suddenly a bunch of citizens were like "the USA sucks, I hate this country, let's trash it and make something outdated like 150 years ago, but with nukes and rockets!" It's so... \textbf{weird}.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small \@Mariam not sure how \textbf{old} you are but there was a time, google robert kennedy speeches, or the first moon walk, i could go on but there was a time\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Jason Sanderson I'll be glad to call anyone by whatever \textbf{gender} they wish, because iam an adult that was raised with real morals and principles, not fake christianity and hate. I'd take that any day over a population of uneducated over armed, under regulated NPCs and corrupt oppressive police states\normalsize   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}\small Trump us evil in makeing way 4 the antichrist. \textbf{Witch} us Kushner.\normalsize   & \cellcolor{green!5}Witch & \cellcolor{green!5}Gender - Female age and physical appearance & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small All of it should be called out when EVERY \textbf{race} is massacred \& racially targeted, NOT only Jewish people\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small All of its unacceptable but when it comes to \textbf{BLACK} people there's a thousand excuses!?\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small I do not condone any of this from either side, but I cant help but wonder why no one has pointed out that since thug rap and gangster rap have been spewing out lies about how they live the hate on both sides has grown. the county had been heading in the right direction for quite some time. but the more whites heard the youth of the \textbf{black} community filled with rage and out for blood  tolerance has diminished .  when lines get drawn more will follow . we watched as a special needs child was held captive and tortured on video tape,  but the media said it wasn't a hate crime even though it was plain to see it was.  \textbf{racism} is \textbf{racism} regardless of who it is against. address the whole issue or your just spinning your wheel's\normalsize   & \cellcolor{green!27}Black, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/140 & \cellcolor{green!27}2.143 \\  \hline
  \cellcolor{green!5}\small i agree, all of the anti jews bs should be punished severely,the same way anti muslims, anti \textbf{black} ,anti chinese, anti hispanic, anti white ect...punished on the same level tho... not one community better than the other.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small The left preaches about how Trump causes hate yet they do \textbf{nothing} but spout hate an do violent shit themselves...why is that? How can you preach all that bullshit and turn around an do the same thing...and were the retards? Fucking trolls\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small alright nazi\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}\small Stephen Shelley \textbf{Nazi} party was on the left , sorry bud try again .. And the shooter was anti trump.. He was one of you. The blood is on your hands ..\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@Deplorable Patriot    The shooter did dislike Trump, but that's because he's to the right of Trump, not the left. I don't think Trump is quite as far right as popularly believed. He'll pander to the far right, he'll use them, he'll spout rhetoric and support policies that make the far right happy, but at the end of the day his interests lie with the wealthy and powerful who acknowledge him, whoever they might be. Those who can prop him up. Trump doesn't actually care what happens to the average \textbf{racist} or white nationalist, but he does put on a good show for them.I don't blame Trump for the synagogue shooting. but I also don't think he gives a shit about what happened.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/123 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}\small D S might want to go back to history class fuck tard. The \textbf{Nazi} party was a socialist nationalist government , left wing.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Hey all you \textbf{Nazi} bigots, find your way back to Germany. You have caused so much destruction throughout our history here in America. Watch your back.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small The Alt-Right, White Nationalists, Neo-Nazis and Trump fans rejoice.What they all have in \textbf{common} is the fact that they stood together to vote for their orange god.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small CNN is \textbf{racist}.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small You are clearly just \textbf{dumb} as dirt Ms. Johnson\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small SuperUbermensch Beep Beep Trump is a \textbf{Nazi} Beep Beep\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small I voted \textbf{R\textbf{ed}}. So does that mean I am a \textbf{Nazi} because I vote \textbf{r\textbf{ed}}?\normalsize   & \cellcolor{green!27}Nazi, Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}5/15 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@Hulein Pylo, the answer to your very baited question is simply, no. Now, on the other hand if you vote \textbf{r\textbf{ed}} because Trump looks the other way while you talk shit about Jewish people and think George Soros runs the whole world", then yes, you are a \textbf{Nazi}. Or at minimum a enthusiastic KKK fan. Get it? It's really very simple. But why are you asking me Mr. Pylo? I wouldn't know one way or the other about your affiliations with Nazis.\normalsize   & \cellcolor{green!5}Nazi, Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}3/82 & \cellcolor{green!5}3.659 \\  \hline
  \cellcolor{green!27}\small \@Stephen Shelley Just glade to hear that you don't consider all \textbf{r\textbf{ed}} votes are from Nazis.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/16 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@jon smith , thanks for the heads up nut job! Ooh, the dark agenda is coming for your ass. \textbf{Lame}. What are you ten years \textbf{old}? I love reading conspiracy \textbf{freak} posts, because the incredibly deep ignorance of reality is delivered with a \textbf{crazy} arrogance. Don't let Mr. Soros grab your ass in the "dark times", you idiot. Really?\normalsize   & \cellcolor{green!5}Crazy, Freak, Lame, Old & \cellcolor{green!5}Age - Over 65s, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/59 & \cellcolor{green!5}6.78 \\  \hline
  \cellcolor{green!27}\small \@Hulein Pylo no Mr. Pylo, and i am especially heartened to hear that you are not a \textbf{Nazi} white nationalist. Good news for both of us! See, as Americans we are both on the same page. Now, please help us impeach fascist bozo. thank you.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small \@Hulein Pylo At the least your a \textbf{Nazi} sympathizer.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@Hulein Pylo thats just the lefts cruse words , if they didn't like a cheese burger they would call it a \textbf{Nazi}.  Yet they are pussys and just name call and don't actually do anything.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@Stephen Shelley if they impeched trump the Alex Jones nuts would be kicking down your door , and even though they are mostly just \textbf{fat} ass's they would probably win in a civil war.\normalsize   & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@SuperUbermensch I'ma make sure when Trump wins again to comment reply to this  and remind you,  Trigglypuff  ! (Insert rageing \textbf{fat} sjw gif)\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Funny that America was becoming more anti semetic after Obama didn't back Israel at the UN . Funny how the actual \textbf{Nazi} that was just deported by Trump was allowed to stay in America under Obama ....They knew about it , took the guys citizenship but never kicked him out .\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}\small Nothing is funny when you a trying to spin lies. Stop working for Satan.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small I really thank you for the bottom of my heart, president 45 for all the hate and \textbf{racist} white supremacists supporters that you have cost, thank you so much with all the lies, I hope karma kick you in the ass and throw your ass in Jail 🖕🖕🖕🖕🖕🖕🖕🖕🖕\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small You can always vote for people who enable \textbf{racism} to happen in the WH\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small When will the mainstream media talk about shitholes like 4chan and reddit? These places basically convert people into racists and anti-Semite through trend hoping and peer pressure. All the childish behavior from the alt-right have roots in these places. The manchildren started off trolling and attacking each other over different taste in video games and other stuff, now they extend all these childish behaviour to politics and serious social issues.The internet continue to be the biggest source of influence on children and \textbf{nobody} seems to give a fuck about what kind of sick shit kids are exposed to.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}\small Obama, some elements of DNC and \textbf{black} congressional caucus are antisemitic and friends of Louis Farakahn and the Muslim brotherhood\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Trump is a white neo.\textbf{Nazi} lover o yeah don't forget KKK he said they have some good people really\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Damn these \textbf{Nazi} Socialist Brownshirts/Antifa.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small already voted all \textbf{r\textbf{ed}} shitter\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Alabama Freethinker I guess u don't know the real meaning of \textbf{communist}.\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@ebie j Steve Bannon employs a lot of jewish people at breibart you \textbf{dumb} liberal shit... stop reading fake news\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small CNN always pushing \textbf{racism} SMH\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small So white supremacy is bad but \textbf{black} lives matter marching down the street saying we want dead cops, and Antifa are ok..... Cnn picking on whites again.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Does any of these libtards in this comments thread know what \textbf{nazi} stand for.  They were socialists you \textbf{dumb} fucks just like the like loonies in the democrat party.\normalsize   & \cellcolor{green!27}Dumb, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small "\textbf{zero} tolerance policy on intolerance" is a really \textbf{weird} thing to say. Not sure that's actually the answer. There's a loophole there. Lol\normalsize   & \cellcolor{green!5}Weird, Zero & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small Donald Trump has part of his family jewish. How is he a \textbf{nazi}? You people are fools!\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small I would say while I think there is likely a strong link to the Trump presidential campaign and a rise in anti-Semitic attacks I would like to see some more statistics for a more comprehensive breakdown. For instance do the attacks rise when Israeli-Palestine incidents are in the news? Do right wing or neo \textbf{nazi} groups increase their activities in response to things like the removal of monuments? That kind of thing. And while I'm certain sites like Gab really are cesspools for hate we should be careful with introducing ideas about policing them so as to not restrict justified criticism of religious groups. Such as say \textbf{homophobia} in the Christian and Muslim communities, or criticism of the accuracy of the texts.\normalsize   & \cellcolor{green!5}Homophobia, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Sexual Identity - General & \cellcolor{green!5}2/122 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}\small America has the worst hardest probably I should say impossible to get migration immigration system,  because to migrate to America there r no choices America \textbf{racist} immigration system just cater to rich people who invest some \textbf{crazy} amount and gets green card and the other choice  Is some \textbf{crazy} employer visa system which is impossible to get and takes \textbf{crazy} amount of time and no company or office  or store will sponsor u  like that and wait for like 5 to 10 years that's \textbf{crazy} mad immigration system and first of all no employer will sponsor u and the other one is family which only caters to family. So people the real problem is America immigration law need to change and get easy system,  that's why there r so many illegals in America, America needs a immigration system like if u stay in America for 3 or 5 years u I'll get green card or many other easy immigration system. Australia immigration is also \textbf{racist} towards \textbf{old} people like only people under 45 can get work immigration to Australia,  that's also needs to change and get an easy and not raceist immigration system.for all ages.\normalsize   & \cellcolor{green!27}Crazy, Old, Racist & \cellcolor{green!27}Age - Over 65s, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}7/195 & \cellcolor{green!27}3.59 \\  \hline
  \cellcolor{green!5}\small So when Jews say negative things about blacks, about muslims,  that's okay? Jews are okay with hate speech on others but we must all protect them. Look, where was all of this reporting when that \textbf{racist} shot up the \textbf{black} church. Where were all the candleholders then?\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small Why are some American-born Whites supporting this 'Master Race' nonsense? It only took one Donald tRump to bring out the worst in this \textbf{nation}.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small "dramatic \textbf{spike}" everything is a drama for CNN, always lies to keep people in fear and stress, let start telling the truth\normalsize   & \cellcolor{green!5}Spike & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small Welcome to \textbf{Nazi} America. I hope we can get Trumpkin and the rest of his cronies out.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@JOE BLOE yeah, there's just too many idiots in this world. The harsh truth is that some sort of monarchy but will multiple people in charge would be best, no elections no nothing\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small \@J S Cool, \textbf{nobody} wants to go to China. Not anybody who believes in freedom, at least.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@J S 😂🤣, name just 1 single time it has ever worked. Then I will debunk your \textbf{dumb} ass.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small wrong. china is declining, japan is rising again (despite 90 less population it's still the largest creditor \textbf{nation} in the world). you won't stop english, though mandarin is a nice language. learn hebrew (jews), and make aliyah. that's the key, not a fundamental failure of america as an entity or \textbf{nation}.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/51 & \cellcolor{green!27}3.922 \\  \hline
  \cellcolor{green!5}\small Mark Hirstwood China is declining lol how wrong you are. In fact, if current trends continue, China will overtake the USA both economically and militarily within the next 50 years. America has been on a steady decline since the 80's, has this had accelerated rapidly in the last two years. Your politicians are too corrupt, your economy based on too much debt, and your population is too \textbf{dumb}. All empires decline, you're next.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small I wonder if it was like the \textbf{black} church that was burned and donald trump was written on it... then come to find out it was a member of the church who was \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/34 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Prob Democrats pretending to be \textbf{racist} doing it to play to their narrative. Democrats are the most \textbf{racist} mother fuckers I've seen or heard..its white devil white devil all day everyday maybe take your own advise and um well dont be a \textbf{racist}..\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/43 & \cellcolor{green!5}6.977 \\  \hline
  \cellcolor{green!27}\small I find it so \textbf{weird} how the very thing Americans fought against is now consuming itself.\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small You know why it's on the Rise because we got a hateful ass president that is a \textbf{racist} and sexist!!!!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small The \textbf{Nazi} cancer is spreading little by little and we need to stop it as soon as possible. VOTE BLUE\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}\small Yep that's what happens when you have a \textbf{racist} president and I am afraid more Trumpy the Clown's supporter nut cases will be cause more havic !!!!!!!!!!!!!!!!!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small All perpetrated by democrats. We have played this game before and its always democrats making up fake hate crimes.......its getting \textbf{old}.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small Yeah, you are getting \textbf{old} Neo-Nazi conspriacy theorist. I'd much rather stab you in your neck and watch you bleed to death than listen to you spout anymore of your crap!\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}\small We have a hoard of about 20,00 people with at least 80 men attempting to invade our Country and yet the fake news is ignoring it. They want these illegals here so maybe they can vote democrat. This invasion is full of rapist,criminals, and \textbf{terrorist}. Every American better be concerned about the safety of their daughters, sisters, wives,mothers. These people are being sent here by radical leftist. Vote Republican because the democrats want to let all of them in our Country\normalsize   & \cellcolor{green!27}Terrorist & \cellcolor{green!27}Religious Identity - Muslim & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Nazis are formed from Christianity thats why they have  Cross in the sign. According to their believe jews killed jesus. CNN should address them as \textbf{terrorist} and their religion's ideology  that create  hate.\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Die. \textbf{Nazi}. Scum.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small I am empathetic to the loss of life, specifically that which hatred is at the origin of it, like this tragedy in Pittsburgh. As a \textbf{black} man in America, I do disagree with the message CNN \& Anti Defamation League are attempting to send by looping Minister Louis Farrakhan in this "\textbf{spike} in antisemitic crimes". Minister Farrakhan and the \textbf{Nation} of Islam are completely unrelated, and what CNN did here is an age-old tactic to discredit \textbf{black} leadership and committ character assassination for ratings. \textbf{Black} people do not commit anti-Semitic crimes, and to suggest that someone like this deranged murderer in Pittsburgh was inspired or influenced by the speeches and words of Louis Farrakhan is illogical and shows poor thought on behalf of CNN \& Anti Defamation League. Louis Farrakhan \& The \textbf{Nation} of Islam are not anti-semetic. Speaking out against societal ills and injustices does not make one anti-semetic. Grow up CNN!\normalsize   & \cellcolor{green!5}Black, Nation, Spike & \cellcolor{green!5}Ethnicity - Black, Nationality - General, Religious Identity - Protestant & \cellcolor{green!5}6/153 & \cellcolor{green!5}3.922 \\  \hline
  \cellcolor{green!27}\small Its funny No One listens to Louis Farrahkhan's hate but Jewish people and white people comment only when looking for excuses of other people doing the same bad things. Wrong is Wrong as an \textbf{African} American and many that I know we are NOT listening to Min. Farrahkhan's messages for Jew hate speech. We're listening for the lack of America holding up the end of her promise to ALL citizens. Let's discuss that!\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small I'm not one to be a grammar \textbf{nazi} but that's not how you spell America you silly Nancy.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small As if he has ever said anything outstanding to the point of \textbf{racism} and discrimination to religion on a large scale. Stop being a fuck.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small I rather it be kkk than \textbf{black} lives matter anytime\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@MrChadwke what a stupid ass person. Ahha the bible is \textbf{common} sense of good and bad. Only idiots thinks that's bad. Stfu u lost\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}\small \@Dio brando.n \textbf{Black} man good\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Black lives matter as a group are MORE \textbf{racist} then white supremicists. FACT\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small Luke Wojcik um \textbf{black} lives matter doesn't have a history murdering people and hanging people from trees. There would never be any \textbf{black} lives matter if \textbf{black} people were always treated right in the first place.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}3/36 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Trump doesn't like white supremacists either, "\textbf{Racism} is evil, and those who cause violence in its name are criminals and thugs, including the KKK, neo-Nazis and white supremacists and other hate groups that are repugnant to everything we hold dear as Americans," [LINK] \normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small Sure, Trump's a white supremacist.  That's why he moved our Israeli embassy from Tel Aviv to Jerusalem.  He moved it because he is a white supremacist.  That's why he is married to a non-white.  Because he is a white supremacist.  That is why, when he attended a meeting of the Young \textbf{Black} Leadership Alliance, he was greeted with a standing ovation.  Because he is a white supremacist.  I swear, 90 of your insults that you throw at Trump are baseless innuendo.  You hear someone say "Hey, Trump is   !", and you just jump on the bandwagon.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27}\small Luke Wojcik no you grow up and stop trolling and stay out of our affairs. You must support him enough to say anything. Don't tell me to educate myself when white supremacist have killed hung \textbf{black} people for years. They hate Latinos and Jews too. And they feel Trump is on they're side.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Rational Conservative Trump is "COMPLIANT" of people being \textbf{racist} at his rallys wavying confederate flags. Those people don't likes blacks, Latinos or Jews. He makes them feel like they have a place in his world.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small What was people thinking when they let NASCAR teams have all those anti American confederation loser rags fly on pit stop flag poles ?Start with the real problem the NASCAR fan base  and teams .In 2015 NASCAR was offering FREE US flag to everyone that turns their confederation loser rag in , less than 10  did it .If you remember in Charlottesville , confederation loser rags was in harmony with \textbf{nazi} flags ... after that it is useless to try to explain why a person or a major sports have confederating loser rags ...they are \textbf{nazi} supporters just like NASCAR teams .\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/106 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Lambert Lum I'm telling you Trump is a rich man that is using the white supremacist of the country to get votes ok he doesn't give a shit about any of us he is a entertainer. A Trump rally looks \textbf{nothing} like America in 2018 You and I both know America is way more diverse then that.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Makes me so anger, and am not even Jewish. These ugly \textbf{Nazi} people are so gross. How can people be so cruel?  It's all this \textbf{racism}, \textbf{misogyny}, too. Not in this day and \textbf{age}, it just can't be. We must face it head on and not tolerate it for one second, starting with Trump. NO MORE.\normalsize   & \cellcolor{green!27}Age, Misogyny, Nazi, Racism & \cellcolor{green!27} Ideological and Political Identity - General, Age - General, Ethnicity - General, Gender - General & \cellcolor{green!27}4/56 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small sure, it has \textbf{nothing} to do with the anti jew, anti zionist narrative of those tinfoil hat channels on the web who were popping up like shrooms since way even before the presidential elections.trump condemned the attack but he's to blame.blame, blame, blame.people are not radio commanded by trump like you lefties are by cnn. your hate reached a new level of blindness.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/66 & \cellcolor{green!5}1.515 \\  \hline
  \cellcolor{green!27}\small Remember, when you see a \textbf{Nazi} stab him in the throat.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small thats quite sick, are you deranged or just a \textbf{loony}??\normalsize   & \cellcolor{green!5}Loony & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small But Israel Loves Trump because they both hate Hate Brown Folk!  \textbf{Nothing} brings \textbf{Racist} together like Hate!🤗\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small \@20,000 Subscribers Without Any Subscribers no, it's a white supremacist \textbf{nation}.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small No alot of people hate the US but not because the people but the presidents and politics.. the US trys to be that guy that thinks he's better than everyone else but only annoys everyone else.. why do you think Mexico never gets hit with terrorism. When mexico used to be in peace Americans would go all the time to real freedom, everything from drugs, pharmacys,\textbf{sex},food, candy, coffee,etc everything was so beautiful so great... after that and US suffering from all the drugs Americans was buying from the plugs..just like the flood of crack in \textbf{black} neighbor Hoods they went and flood the the US w heroin too which almost all Mexicans got hooked on and in Mexico everything went South very dangerous "the evil people" demanded the attacks of innocent people in a way to scare and controll people something some people showed Mexico to do\normalsize   & \cellcolor{green!27}Black, Sex & \cellcolor{green!27}Ethnicity - Black, Gender - General & \cellcolor{green!27}2/147 & \cellcolor{green!27}1.361 \\  \hline
  \cellcolor{green!5}\small The US, Israel, and Saudis are best allies, because they are eternal morons along with their radical \textbf{terrorist} and \textbf{nazi} henchmen. .\normalsize   & \cellcolor{green!5}Nazi, Terrorist & \cellcolor{green!5} Ideological and Political Identity - General, Religious Identity - Muslim & \cellcolor{green!5}2/22 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@StormyWeather Oh yes cause that means they aren't oppressed. You know damn well you wouldn't want to be an Arab in \textbf{Nazi} Israel.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small Trump really hates brown folk by getting them jobs. Dont believe the hype \textbf{African} American unemployment is lowest it has ever been. If he hated somone dont you think that would be the opposite?\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small *Omegaand yet Trump has lowered \textbf{Black} and Brown unemployment to historic lows.  you throwing shade on that?\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@StormyWeather so I do recall seeing a video of a \textbf{refugee} camp in Israel with forced labor. I cannot find the video anymore. Just like I can no longer find videos of Donald Trump talking about his progress abortion Democrat views but that doesn't mean they never existed. ;) I did find this though and basically they're doing what Donald is doing which most followers of this channel disagree with.  [LINK] \normalsize   & \cellcolor{green!5}Refugee & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/71 & \cellcolor{green!5}1.408 \\  \hline
  \cellcolor{green!27}\small No single group (especially one of a cosmology or ideology, really has any say over how other groups perceive them. This is a social contract based on behavior we all use as a cultural operating system upstream from religion and \textbf{race}.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}\small "\textbf{Nothing} is sacred, not human lives, or places of worship, or even where the dead are buried..." at 1:17\textbf{Nothing} is sacred. That perfectly described Trump's value system and his entire life. Also described Melania's apathy toward cold lonely babies in cages, as well as the soul quality of those who proved Trump right, after he screamed "I could shoot somebody in the middle of Fifth Avenue and I wouldn't lose any voters okay? It's like incredible!"\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small Funny how you didnt care when Obama had similar "apathy towards lonely babies in cages"... odd huh?Funny how none of you cared when HILLARY voted for a border wall... and no one said shit when that vote she made was signed into LAW... thats okay. I understand you guys are a little ignorant of history.How little outcry was there when Hillary made \textbf{racist} comments? Or even recently comparing two \textbf{black} men saying "they all look the same"  Didnt see you commenting on that one.Yet here we are, you guys trying to paint Trump as an anti-semite...... but cant actually back it up with facts. Nevermind his daughter is Jewish and his attitude towards Israel... I have no doubt that Trump is a jerk... a Grade A asshole. But what difference does that really make?  Where are his policies that are \textbf{racist}? Sexist? Anti-Semitic?\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/146 & \cellcolor{green!27}2.055 \\  \hline
  \cellcolor{green!5}\small I'm sure the guy who killed those people is a VERY good person. And let's not forget the people who write hateful anti sematic and \textbf{racist} comments... ALL Good People.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small Vee King I didn't vote for Trump and I don't watch fox news. Maybe you should step outside your echo chamber for 5 minutes and try to understand propaganda for what it actually is. You have lost the ability to think for yourself. A lot of bad things happened in the world before January, 2017. The president isn't responsible for the actions of some random idiot with a delusional world view and an inferiority complex. Sanders wasn't responsible for the nutcase that shot up a congressional baseball game and Obama wasn't responsible for the record number of school shootings during his 8 years in office. There are over 300 million people in America. Some of them are \textbf{crazy}. Trump isn't ruining your life or making you a hate-filled hypocrite, you're doing that yourself because you're an irrational, partisan apologist and you can't accept reality. You view your political opposition as one dimensional villains without making any effort to examine your own flawed philosophy. You're basically the very thing that you claim to oppose.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/173 & \cellcolor{green!27}0.578 \\  \hline
  \cellcolor{green!5}\small \@whatsthebigfndeal You Know... My beloved mother ALWAYS said... When you Assume, you make dumbass out of yourself. I'd def say mother was right. Lol. You just assumed Alot about someone you don't know lil guy. You're talking to someone who has very conservative parents, an equal amount of right and left wing friends, and someone who has never voted in his life. I don't care about any these politicians... What I care about is my country NOT being the laughing stock of the world as we are now. I care about people living in peace without you \textbf{Racist} Alt Right Animals killing them. Things have gotten worse since your master Trump got into office. He has embolden his hateful \textbf{Lunatic} following and hate crimes have indeed risen. So all that bullshit you're talking... Save it. You clearly don't know what your talking about.What I said regarding the guy who killed these innocent people is FACTS. I know you Trump Trash Cultist are used to Alternative Facts. But what you said about him was a lie. Am I shocked? No. You Animals tend to lie all the time without having the intelligence to do your research from multiple places to find the truth. The truth isn't propaganda, the truth is just that. Truth.\normalsize   & \cellcolor{green!5}Lunatic, Racist & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/213 & \cellcolor{green!5}0.939 \\  \hline
  \cellcolor{green!27}\small Vee King "What I said about the shooter" was not, in fact, a lie. He's a never Trumper that claims Trump is an Israeli puppet. Which part of that statement is inaccurate? You're talking about making assumptions while you're making assumptions. You're lumping everyone into one group because your hive-like brain can't comprehend that it's ok to disagree with the narrative that you've accepted as the gospel. As I said, I didn't vote for Trump, nor am I a fan of his rhetoric. You seem to have some issues with reading comprehension, as well as an unhealthy amount of anger and hostility towards anyone with the ability to see past partisan propoganda. Your obsession with Trump is unhealthy and will only lead you to even more \textbf{mental} instability and delusion than you already seem to have. The murderer, like you, also had an obssesive hatred for Trump. Does that mean that you're going to go shoot up a church? I mean, after all, y'all have that one thing in \textbf{common} so surely you're just like him, right? Can you even comprehend how stupid that sounds?\normalsize   & \cellcolor{green!27}Common, Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!27}2/185 & \cellcolor{green!27}1.081 \\  \hline
  \cellcolor{green!5}\small \@whatsthebigfndeal I'm the immature one yet you're the one who keeps coming under my comment talking and bitching and crying about absolutely \textbf{nothing}. Lol. Assuming like a dummy as if we've met and gotten to know each other over beers. Talking about shit you have no idea about. Huh Lol, Your So exhausting and pretty boring which i find to be very disappointing. You can assume all you want about my politics and who I hate and don't hate... It honestly doesn't bother me at all. I only value Civilised opinions, not Trump Trash. Keep believing those alternative facts and I'll keep laughing at how \textbf{dumb} you are. Deal? Cool. Now have yourself a great night and do the world a favor and not wake up. 1 less Trump Cultist in the world would makes things so much more peaceful... Don't you think? Goodnight little guy.\normalsize   & \cellcolor{green!5}Dumb, Nothing & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/146 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}\small Lol...I consider myself as a \textbf{Black} Man in my America\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small The alt right consists of \textbf{Nazi} sympathizers and KKK. They just don't tell you they are. The reason being that they know people will stop supporting them. They keep a tight lid on the \textbf{racism} and hate in their hearts. You rarely see them speaking publicly, because from the overflow of their heart does their mouth speak.\normalsize   & \cellcolor{green!5}Nazi, Racism & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/57 & \cellcolor{green!5}3.509 \\  \hline
  \cellcolor{green!27}\small \@Dragon Eater Donald Trump rejects neo-nazis and KKK, "\textbf{Racism} is evil, and those who cause violence in its name are criminals and thugs, including the KKK, neo-Nazis and white supremacists and other hate groups that are repugnant to everything we hold dear as Americans," [LINK] \normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}\small WHITE NATIONALISTS \textbf{PUSSY} AKA KKK ARE COWARDS THEY WILL NEVER TAKE THERE WHITE ASSES AND FIGHT MS13 OR 18ST GANGS OR ANY \textbf{AFRICAN} AMERICAN GANGS!!BUT THEY WILL BEATUP \textbf{OLD} \textbf{WOMAN}  AND KILL CHILDREN AND WOMEN AND \textbf{OLD} MEN!!!AND MINORITY'S THAT CAN'T FIGHT AND NON VIOLENT PEOPLE!!WHAT A BUNCH OF WHITE MALE \textbf{PUSSY}!!\normalsize   & \cellcolor{green!5}African, Old, Woman, pussy & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black, Gender - General, Nationality - Chinese & \cellcolor{green!5}6/52 & \cellcolor{green!5}11.538 \\  \hline
  \cellcolor{green!27}\small Dramatic \textbf{spike} in fake news being reported on CNN.\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Meanwhile CNN reports positively on "\textbf{black} political groups" working to create a "\textbf{black} wave" in the upcoming elections. But, don't think you're part of a group with \textbf{common} interests that would be racist\normalsize   & \cellcolor{green!5}Black, Common, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}4/33 & \cellcolor{green!5}12.121 \\  \hline
  \cellcolor{green!27}\small Black people have bigger dicks, is that what bothers you?? be honest\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small The immigrants don't have to try and take over this \textbf{nation}, we will open the borders for them unimpeded after we have a civil war and kill ourselves.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}\small Both sides are to blame but its not equal 95-5 where right wing groups are more likely to follow through on violence. The \textbf{Nation} of Islam doesn't have much support in the Left and the \textbf{African} American community which is majority Christian. Whataboutism is how the GOP respond to this issues but the GOP control three branches of government, majority of governorships, and gerrymandered house districts in favor of Republicans and the Right are act like a minority. Wait. On the numbers the GOP runs the country but represent a fraction of the American people. That's not right. Necesitamos a votar! We need to vote.\normalsize   & \cellcolor{green!27}African, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}2/105 & \cellcolor{green!27}1.905 \\  \hline
  \cellcolor{green!5}\small It's ironic that these \textbf{racist} losers come from the states(Pa , Wis, Mich) they voted for this \textbf{racist} president they put this \textbf{racist} president in power.  I have as much hatred towards Trump voters as these \textbf{racist} has towards Jews and others.  PLEASE if your NOT a \textbf{racist} don't buy anything that are from these 3 states and don't visit the \textbf{RACIST} states of Wisconsin - Pennsylvania - Michigan.  To all the \textbf{Racist} people from these states FUCK YOU!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}7/79 & \cellcolor{green!5}8.861 \\  \hline
  \cellcolor{green!27}\small Have you not been told everything is political now-a-days? Anything in which either the right or left can use as a tool to gain a political edge is turned political. Gay-rights, \textbf{migrant} caravans, shootings, birth-rights, GOD, basically anything you can think of. Both sides do it, just a while ago the death of a beautiful white American citizen female due to a illegal \textbf{immigrant} was quickly politicized by the right as justification to get rid of those "dirty illegals". haha welcome to reality xD\normalsize   & \cellcolor{green!27}Immigrant, Migrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/84 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}\small Big Loud Mandingos - BLM - they were going \textbf{ape}!and shops were looted, one guy stole some shoes and wore them and then ran out to loot some more with those shoes on. and the women???Women be shopping!!\normalsize   & \cellcolor{green!5}Ape & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small So funny blacksTalk about this we areTalking about it to much...but once it hits another culture than there's something we need to do about it..\textbf{Nobody} is better than anybody and when things like this happen people should get involved but they don't until it affects their family or people who look like them and it's sad....now you want to have a discussion about how bad people have been treated for years and years and years come on you guys stop being fake it is what it is when everybody's being hurt hate don't make things better hate is a brewing disease and it only gets worse...it's sad when things have to hit your home personally before you want to get involved because other than that it didn't pertain to you remember it was just those people you know the ones that help fight for rights in this country...that everybody  takes part of with no second thought but my people died for Acceptance in this country...And fought and marched for the rights....but you down play our history and involvement...American hypocrisy....stand for everybody it affects everybody...\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/189 & \cellcolor{green!27}0.529 \\  \hline
  \cellcolor{green!5}\small They have fooled the entire world into believing that they are they of the book. And the descendants if Abraham Isaac and JACOB when in truth they are not now nor have they ever been a \textbf{NEGRO} who are the true PEOPLE of the bible and the true descendants of Abraham Isaac and JACOB. REVELATION 3: 8-10 tells you who these liars are. Now dispute the word of TMH ELOHIM the ELOHIM of my FOREFATHERS ABRAHAM ISAAC and JACOB.\normalsize   & \cellcolor{green!5}Negro & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/79 & \cellcolor{green!5}1.266 \\  \hline
  \cellcolor{green!27}\small what about \textbf{black} babies??\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Racism it's a \textbf{mental} disorder😷\normalsize   & \cellcolor{green!5}Mental, Racism & \cellcolor{green!5}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/5 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small Trump and his \textbf{Nazi} vermin.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Jews will not replace y'all.  Ain't \textbf{nothing} as evil as y'all. So Nazi's enjoy your status\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small The republicans have been embracing \textbf{racism} for decades now, and trump is the outcome of it. If you noticed the raise in right-wing terrorism has grown for decades, and trump was the amplifier for the right-wing terrorism to do more.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small Justin Norton oh really? Is that why all of the most \textbf{racist}, violent hate groups arrised  from under the democratic party name? kkk, blm, antifa, etc. All under the democratic party. Why? It's because you guys are obsessed with \textbf{race}.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/40 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@DishingOut Ls wow, not only are you a \textbf{dumb} ass, but you're a stupid fucking \textbf{dumb} ass. Fucking clowns, all of you trump supporters.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@Lambert Lum , and that's why I said trump isn't the cause of this. He is just a selfish moron that sells anyone out to make a \textbf{buck}. The only people he can appeal to are uninformed, uneducated, and \textbf{racist} people. That's why he is now saying he is a nationalist, aka white supremacist.\normalsize   & \cellcolor{green!5}Buck, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small ​\@Justin Norton You're the biggest dumbass here. You can't even see how brainwashed your fucking dumbass is. And don't do that whole bullshit argument that the parties changed over time you fucking imbecile. That's bullshit. I know thats why you tried to call me a dumbass you fucking idiot. You can't pick and choose what aligns with your party and what doesn't fucking idiot bitch. It's true you guys are obsessed with \textbf{race} you fucking idiot. Go read the comments under this video. You'll with ease find many comments saying "white people are the problem" or just blaming white men in general. Im not white, but seriously get so annoyed at hypocrites and \textbf{racism}. Racists are the most hateful group of people, and the left is full of hypocrisy and \textbf{racism}. How about you set up a time date and location so we can further this conversation in person.\normalsize   & \cellcolor{green!27}Race, Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/149 & \cellcolor{green!27}2.013 \\  \hline
  \cellcolor{green!5}\small \@Justin Norton Go look up the definition of a Nationalist Justin. You're brainwashed by CNN into thinking that just because someone loves their country that means they are a \textbf{racist} white \textbf{nazi}. You guys are fucking \textbf{racist}. You guys hate the US. thats why you guys never support the US and always go against the US. You guys are the biggest embarrassment to a country. Who the fuck lives in the most priviledged country in the world and complains. Exactly you.\normalsize   & \cellcolor{green!5}Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}3/81 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@Justin Norton Nationalist just means looking after your \textbf{nation}. It doesn't mean white supremacist. People who are nationalists are opposed to globalism. Globalists seek to erase US leadership and make US submissive to a global body.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small \@get lost another \textbf{dumb} \textbf{blind} stupid moron.\normalsize   & \cellcolor{green!5}Blind, Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/7 & \cellcolor{green!5}28.571 \\  \hline
  \cellcolor{green!27}\small Ignores the level of \textbf{black} unemployment going down and the number of growing \textbf{black} neighborhoods. Also, if you pull the border wall shit, remember that the people coming in bring drugs and crime that could affect you, your family, your loved ones, or friends. Trump wants the best for us.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/50 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small The word \textbf{racism} has been used so many times out of context it is now meaningless.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Oh shut the fuck up. \textbf{Racism} has been happening wayyy before trump became president.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Justin Norton it the dem who embrace racism\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small More evidence as to why CNN is now less popular than Home and Garden television.Not even a year ago CNN flipped out about Trump moving the Embassy to Jerusalem because Israel (the Jews) are our Ally and Trump supports them. If there's a rise in anti-Semitism, then obviously it is not coming from Trump and his supporters. There's only one other place that can come from and I'm addressing the biggest instigators of it right now.Your lack of \textbf{Common} Sense knows no bounds.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/85 & \cellcolor{green!27}1.176 \\  \hline
  \cellcolor{green!5}\small \@Lambert Lum please tell me that you teach children. We need people like you stopping the creation of people like the ones in this comment section. Either completely devoid of all \textbf{common} sense and blinded by political hatred, or pushed to the point of insanity, rudeness, and profanity, intentionally by the same blinded group.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small \@Nathan C no I'm not the problem man.  I get told fuck you, \textbf{racist}, dumbass all the time on here and reply civily. But not today.  Why should I show respect to people who show \textbf{nothing} but disrespect back?\normalsize   & \cellcolor{green!27}Nothing, Racist & \cellcolor{green!27}Age - Youngsters, Ethnicity - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small \@Nathan C war has always been a good solution. Both sides just want control from guns to drugs to now even right of speech, I'm sick of it. I'm ready to see you both in a all out battle royal, it won't be too \textbf{crazy} because of Americas obeseity crisis lmao.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}\small \@Nathan C Actually, I do children's ministry at Church, but we don't usually talk politics at Church.  What I am doing is something you can do quite easily.  Just do a \textbf{mental} exercise of argument, counter-argument. I practice that a lot. I only engage when I know the other guy has no counter-argument. I hate losing, so I never bother to engage unless I know I can win. The other person will eventually give up for lack of a counter argument. Sometimes the other guy gets angry and resorts to insults. I just point out that such insults are a front, an illusion that hides one's weakness. Occasionally, I offer to pray for the person. It's quite disarming to show good to someone's evil.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/124 & \cellcolor{green!27}0.806 \\  \hline
  \cellcolor{green!5}\small DUMB ASS PRESIDENT TRUMP TO BLAME!\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small MEANWHILE in ACTUAL news: 15,000 illegals are marching on our country from the south. Trump is deploying 5,000 troops to meet them. It's either vote \textbf{R\textbf{ed}} for borders and sanity or Blue for open borders, anarchy, and the end of this country entirely.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small Meanwhile 3000 poor souls are marching to this country and draft dodging bitch Trump and his \textbf{racist} supporters like your bitch ass are spreading lies tour family is not from this country you and your sorry as family are immigrants also but your stupid ass is \textbf{dumb} that you don't know history, America is a \textbf{nation} if immigrants and always Will be I suggest you pack up your family and get your \textbf{racist} ass out of America. Vietnam Veteran retired\normalsize   & \cellcolor{green!5}Dumb, Nation, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}4/80 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Only good \textbf{Nazi} is a dead \textbf{Nazi}. My grandfather killed many. I'm ready to do my part. Idiots might want to learn some history. It won't end well for you.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small We should be condemning all hate speech, not just anti-Semitic. Two \textbf{black} people were gunned down and a young \textbf{black} man was hung in his backyard this past week also.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/30 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small STOP calling CNN Fake News... They are not! These are the Champions of Freedom and Justice who want to stop Trumpf and his Nuclear Attack against the Caravan! Make sure to vote on Nov8 and have the blue wave defeat the \textbf{Nazi} White CONservatives.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}\small \@Max Covfefe You are? Sorry to hear that...  A \textbf{sex} change may fix that.\normalsize   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Nazi 45 likes this\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small CNN- Covering ANYTHING but the multiple \textbf{migrant} caravans materializing to invade our country and Trump's response of mobilizing over 5,000 troops. That's not even an important story. Don't pay attention to that or we might lose the midterms, pleaseeeeeeeeeeeee.\normalsize   & \cellcolor{green!5}Migrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small He didn't like Trump bc he thought he was Zionist controlled so... so think about it retards, Trump has treated Jews w a level of respect that pissed the \textbf{nazi} off. Many of the radicalized right feel the same\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small GOD BLESS ALL THE JEWS AND THE ISRAELIS AND ISRAEL AND ALL THE PEOPLE WHO SUPPORT THEM! F..K ANTI SEMITISM AND F..K THIS \textbf{NAZI} SHIT, IT DIED WITH HITLER, KEEP IT BURIED.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small These punks only attack defenseless people,  i challege any \textbf{nazi} out there, for a boxing match since you that brave come get me in the ring, win or loose, you go home with a hundred thousand dollars,  i swear i will whoop the evilness out of you.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small \@Alex Mack CNN give proof with evidence while your fox news peddle hate with lies. This case being a clear indication. Lord i pray every day to be attack by a \textbf{nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@Saul Dean just open your mind to the idea that there is a great conspiracy to divide us by \textbf{race}. Do it for 3 days and watch CNN. You owe it to yourself.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small \@Saul Dean yes it's fake news. That was at the unite the right protest. Look into who started that protest. It had \textbf{nothing} to do with uniting the right. It was a protest started by an operative and was designed to  associate 'right' with \textbf{racism}. That was the biggest \textbf{racist} event in the country, and you saw maybe 20 people there with torches. Multiple KKK heads have been cia agents, and Robert Byrd (former KKK head) was very, very close friends with Hillary Clinton. There is so much more about this topic to learn. Once you learn it, you can't go back. Cnn is just one arm of a huge evil conspiracy.\normalsize   & \cellcolor{green!5}Nothing, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/112 & \cellcolor{green!5}2.679 \\  \hline
  \cellcolor{green!27}\small Maybe if people stop praising \textbf{racist} people in history\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Isn't it ironical Republicans use \textbf{R\textbf{ED}} as their color?:D No matter if it's anti-communism or anti-immigrants, anti-minority, the ugly face of white Supremacy would take an excuse and repeat itself if we allow them!  The eerie similarity of the Jewish martyrs are alarming! The only differences is the senate is now full of McCarthys!  But it's also the military that brought down McCarthy!! Don't let the victims blood flew in vain! censure and vote all the McCarthys out 11/6/18 just like we did 12/1954!!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/84 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}\small Ha Ha \textbf{spike} in Anti-Semitism! Hilarious Nazis didn't just start running around America! A decline my add typical cognitive dissonance! Guess as long as it's h8 against blacks why should they care. \$ talk\$ louder than pain! Hint Hint\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}\small Like my Father before me who fought them in WWII, I Hate Nazis!\textbf{Nothing} is more Un American than White Supremacists.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small The western world got rich off of \textbf{racism} and hate it's just as american as \textbf{apple} pie\normalsize   & \cellcolor{green!27}Apple, Racism & \cellcolor{green!27}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!27}2/17 & \cellcolor{green!27}11.765 \\  \hline
  \cellcolor{green!5}\small \@lineflyer1 Christian/Right Wing logic: Hate Jews for "killing Jesus", but at the same time, believe that God's Plan of Salvation REQUIRED Christ to become the pure Lamb of God and be Crucified for your sins. By your reasoning, you also hate Italians for being descended from the Romans who invented crucifixion. \textbf{Nazi} Punks Fuck Off.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small \@Robert Leonard He was \textbf{black}. And the biblical Hebrews/Israelites/Ju were, too. He wasn't a Khazarian.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Make Racists Afraid Again there is \textbf{nothing} more Un American then \textbf{black}, \textbf{r\textbf{ed}}, pink, purple, \textbf{y\textbf{e\textbf{llow}}}, brown, leftest, democrat, \textbf{skinny}, \textbf{fat}, \textbf{bald}, hairy, whatever freaking label you want to use. Any supremacist are not the only ones who can be anti semitic  I remember a certain President who suggested Israel to give up the land they won  in the 6 day war just to make the palestinians happy  lol   He got his hat fed to him :D\normalsize   & \cellcolor{green!5}Bald, Black, Fat, Nothing, Red, Skinny, Yellow & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam), Ethnicity - Black, Ethnicity - Native-American, Nationality - Chinese, Nationality - Japanese, Physical Identity - Physical Features & \cellcolor{green!5}10/77 & \cellcolor{green!5}12.987 \\  \hline
  \cellcolor{green!27}\small To the left being white \textbf{race} makes you a \textbf{Nazi}.  You have fallen for the lefts propaganda.  The amount of whites who are Nazis in America couldn't fill a small high school gym.\normalsize   & \cellcolor{green!27}Nazi, Race & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!27}2/33 & \cellcolor{green!27}6.061 \\  \hline
  \cellcolor{green!5}\small Or \textbf{Black} panthers.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@hijacked symbols While I Agree that Jesus was Not WHITE in todays term, He Was Middle Eastern and not from AFRICA which is commonly known as \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small This \textbf{black} man is with you because it's going beyond the point where we cannot be passive no more.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small robert leonard Right, but the Jews still ordered for his killing. It didn't happen because Jesus was also Jewish? Are you \textbf{g\textbf{ay}} and retarded? LOL\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/25 & \cellcolor{green!27}8.0 \\  \hline
  \cellcolor{green!5}\small \@First Last Why do you ask whether someone is \textbf{G\textbf{ay}}????Are you looking for a Date???\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/16 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small If you talking about the Big Lie CNN pushes about We Patriotic Trump Supporters, all I can say is BRING IT ON \textbf{PUSSY}!I love with a Passion making scum sucking Fascist dog's disappear ... and all ANTIFA and most of todays democrats Wahck-a-doodles are Facist dogs, who really NEED to go away.So if you feel like a real bad ass ...Look me up Punk ..we can Dance!\normalsize   & \cellcolor{green!27}pussy & \cellcolor{green!27}Nationality - Chinese & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}\small Make Racists Afraid Again - I agree 100! And I'm a right winger. (Libertarian) - How long before people start targeting these \textbf{racist} fuks? Count me in!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small \@\textbf{jerry} henrie what would be an example of the rights propaganda? (Actually asking, not trying to be a dick)\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small I don't see all a couple of messages over the internet is gonna make racists ppl like this guy "afraid" I don't think any of the lefts soys are gonna scare these people, Not even when you blokes where masks lmao. You should stop being scared yourself and fight back. Im honestly surprised the \textbf{black} panthers haven't did something like this yet, those guys are the only group that can actually be taken seriously on the left if there was a civil war. But in all honesty you \textbf{fat} sjws don't scare anything.\normalsize   & \cellcolor{green!5}Black, Fat & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical Features & \cellcolor{green!5}2/93 & \cellcolor{green!5}2.151 \\  \hline
  \cellcolor{green!27}\small \@Renee Elliott it's funny how the left doesn't talk about the \textbf{black} panthers , because they are no better than this sick fookers!! But \textbf{black} panthers are some how justified by sjw propaganda. Evil is evil even if i has a different coat of paint. Why can't we just agree that being \textbf{racist} is bad no matter what color ! And mybe this just was just \textbf{crazy}.\normalsize   & \cellcolor{green!27}Black, Crazy, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}4/67 & \cellcolor{green!27}5.97 \\  \hline
  \cellcolor{green!5}\small Make \textbf{Racist} Afraid Again Same Here! My grandfather fought in WWII as well, and fought against them.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Small government, low taxes, fair trade, borders, small immigration that matches countries needs. A constitution with bill of rights. Liberty, freedom, strong military, the protection of Christian values in all areas including regulating porn.  abortion only after real consideration and needs.  Not allowing companies to buy half of all aborted babies to make food additives and young blood for the elite to stay young.  Not allowing the white \textbf{race} to become a minority in the \textbf{nation} they created, keeping the white population level at say 70. Focusing on American citizens, and not sending money we borrow all over the world.  realizing that God says all people who are mentally and physically able must work to survive, that the only people we are responsible for are those citizens in our \textbf{nation} who are mentally or physically unable to not work, to be taken care of.  In other words we don't owe any people or \textbf{nation} anything, as God  or the universe demands all people to be responsible for their own care and needs.  No one owes anyone anything in the world.  the fact we are alive today is based on the fact that our forefathers worked and did the things it took to survive.\normalsize   & \cellcolor{green!27}Nation, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}4/203 & \cellcolor{green!27}1.97 \\  \hline
  \cellcolor{green!5}\small \@gamer nature  maybe because the Panthers are more intelligent than the \textbf{racist} spreading propaganda on pages belonging to news sort, or social media. A fool running around with guns, will eventually be self destructive.  wise warriors watch and stay calm, while the fool takes each bait.  Now, Panthers are not terriorist and their agendas is not to dominated anyone, this makes them exceptional to society.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}\small This \textbf{nation}, and in fact every \textbf{nation} is ran by Jewish Bankers who control ALL the worlds central banks.  Both parties in America have been taken over by these elite globalist whose final goal is the one world government that will be communism.  They control both sides of everything.  They were the Nazis and commys at the same time, they were the Bolsheviks and in democracies at the same time. No matter who wins they win one way or other, and they get to control the narrative in TV movies and newspapers and TV news shows.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/96 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}\small \@Andrea LOvingLife yeah I'll agree especially retards like him see the media hypeing every mass murder like there some celebrity  just like in this video. Now they add \textbf{racism} too the mix the whole tone too this video is fucking sick. They need too stop covering mass murders , kids see this and think it's a game to see how many they can kill.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}\small Make Racists Afraid Again   "\textbf{Nothing} is more Un American than White Supremacists."  Awesome...name one:)WTCRtmTaRtATM     Ibyttopt-----(ntmuabosai) TaCntrtrastaeattsf--ICwftowg"ts",yonacolmgnbiolnaacfiolmgrorbswhwyattbtntgambLinux Free Font TestLIberation Sans\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small Make Racists Afraid Again \textbf{nothing} is more american then bombing germans and nuking parts of Japan yeah the "good guys"....\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small Make Racists Afraid AgainYou're stupid and \textbf{nothing} more who doesn't even know that you've been fighting with the wrong side all along! Even after so much had happened, you're still asleep and trying to misguide others, still eating CNN shit. Look around what is happening and who is behind it.Germans were the right guys and try to read about holodomor too!There is a reason why they were expelled from 109 times throughout history. Plus you can't be antisemite if the person is not of semite root! Keep that in mind.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/93 & \cellcolor{green!27}1.075 \\  \hline
  \cellcolor{green!5}\small \@cgoh 500 There is a lot of misinformation and misconceptions spread around about Nazis.If you want to learn real history, always study economics behind events because that's where true history lies. \textbf{Nothing} happens in politics by chance remember that.Read about Rockefeller and Jewish organizations involvement in public schooling. That will tell you a lot.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small \@\textbf{jerry} henrie Well you're partly right!\normalsize   & \cellcolor{green!27}Jerry & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Someone get this \textbf{racist} asshole out of office\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I've never understood antisemitism. What has Judaism ever done to people to warrant such hate? America is in a tough spot. Trump seems to be having a bad effect, although I don't blame Trump directly. More so the political climate and the divide in the \textbf{nation}.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small \@Ernest Brown Take off the tinfoil hat \textbf{libtard}.\normalsize   & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@JT SMITH you aren't really mad at CNN...you are mad at Twitter and other social media outlets for kicking you and you friends off of their platform.   do you feel replaced?  LOL did you \textbf{Nazi} that coming?? LOLOL\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@dn30001 So everyone who disagrees with you is a \textbf{Nazi}? Typical \textbf{libtard} tactics. This is why you will lose the next election and future ones as well. I'll enjoy those salty tears\normalsize   & \cellcolor{green!5}Libtard, Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/32 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Steve King is a \textbf{Nazi}. I hope he loses his election in Iowa.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small yess  hitler \textbf{nazi} \textbf{racist}   hitler \textbf{nazi} \textbf{racist}   hitler \textbf{nazi} \textbf{racist}   hitler \textbf{nazi} \textbf{racist} ...then u wonder \textbf{nobody} believes jews\normalsize   & \cellcolor{green!5}Nazi, Nobody, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters, Ethnicity - General & \cellcolor{green!5}9/20 & \cellcolor{green!5}45.0 \\  \hline
  \cellcolor{green!27}\small Everybody who doesn't agree with you is a "\textbf{Nazi}"... It's getting \textbf{old} man...\normalsize   & \cellcolor{green!27}Nazi, Old & \cellcolor{green!27} Ideological and Political Identity - General, Age - Over 65s & \cellcolor{green!27}2/13 & \cellcolor{green!27}15.385 \\  \hline
  \cellcolor{green!5}\small HRS Darwish he isn't a \textbf{Nazi} ... he's a bastard but he's no \textbf{Nazi}. He's a neoconservative. That doesn't make him a \textbf{Nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}3/23 & \cellcolor{green!5}13.043 \\  \hline
  \cellcolor{green!27}\small Vote \textbf{R\textbf{ED}} in November!!\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/4 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}\small \@lineflyer1 That was 2500 years ago....! You \textbf{racist} dummies need to grow up and get the fuck over it, no one cares about your irrelevant theism.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small While I don't condone violence or profiling of any kind, I do wish people would stop using the term "Anti - Semite". Most of these people are not true Semites. It's a deliberately misleading phrase. To those who are targeting all those identifying as "Jews", your issue is with the elites not the \textbf{common} people. The elite are the puppet masters. You are playing into their hands.\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}\small nobody cares what some foreign 3rd world inbred thinks kiddo\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small \@Joey G " If anyone is a fascist it is the liberal party. " "Banning people of opposing sides from speaking in universities" Who bombs people who go against their ideals? right wingers. Who calls for any media not pushing alt right conspiracies to be shut down? right wingers. Who purges voters from the ballot, manly \textbf{African} Americans who vote democrat? republicans. When has a democrat banned someone from speaking in a university?  You can say liberals are fascists all you want, but no evidence exist to suggest we are fascists, we openly encourage other view points, even if we disagree with them.\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}\small Mad Luigi Too many pussies in this country and if you arent a \textbf{pussy}, youre an asshole who does and says \textbf{nothing} because theyre comfortable. America is basically this "If it doesn't affect me? I dont give a fuck." Sad state were in\normalsize   & \cellcolor{green!5}Nothing, pussy & \cellcolor{green!5}Age - Youngsters, Nationality - Chinese & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small Trump 2020, the hate is coming from the left. They say Trump is \textbf{racist} when he isn't, which causes actual \textbf{racist}'s to think they have power when they really don't. Hence the reason all of them are arrested or killed by our government if they do anything.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small stop making trump in to a \textbf{nazi} dude\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small You \& your ilk WILL reap what you've sown. For YOU are the ones that have breathed life into \& created what you rail \& fight against. New era, just the beginning, for you Neo Bolshevik \textbf{commie} Marxist infected shitstains. Already happening. Brazil, Germany, Italy, Poland,  Eastern Europe, America \& more. \textbf{Nationalism} rising. Across the planet. Bourdain yourselves\normalsize   & \cellcolor{green!27}Commie, Nationalism & \cellcolor{green!27} Ideological and Political Identity - General, Nationality - General & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Good thing our President denounced all hate groups and \textbf{racism} multiple times. Thankfully Trump is pro Israel.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@lineflyer1 It was the Romans you \textbf{dumb} mother fucker!\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small The confederate flag is not a \textbf{nazi} flag moron........Try going to any southern state and telling a southerner that their confederate flag is nazism..  I bet you would get your face smashed pretty quickly spewing that bullshit kiddo\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}\small \@ThirdEyeOpen your another fucking moron.....lol, the confederate flag is not a \textbf{nazi} flag\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small How would he feel about college kids and ANTIFA waving the soviets \textbf{communist} flag?He only spent a huge chunk of his life after WWII and up to 1989 hating Americas greatest enemy I bet\normalsize   & \cellcolor{green!5}Communist & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}\small \@Brian Bianco ... Throughout its four-year existence, the Confederacy was at war.  The battle flag is more prominent.How many of today's Germans have relatives who served in Hitler's military?  Does that justify waving the \textbf{Nazi} standard?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small \@get lost Yet, every time you see a swastika \& any of it's derivatives, you see the Stars n Bars right next to it. People only fly it for one reason: To shout their white \textbf{nationalism} at everyone. [LINK] \normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@Alex Thompson someone said that the Confederate Flag is not the \textbf{Nazi} Flag........very true.....they both represent two totally different things.  Someone asked "what is it then"........I replied.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small \@Dauntless07  Putting the Rebel Flag next to \textbf{Old} Glory is like preferring dicks on your anime chicks. Which you probably do.And ol' Adolph thought this kind of dude was destined to be the Master \textbf{Race}?? Y'all alt-righters are a buncha freaks and mutants. Real Hills Have Eyes type shit.\normalsize   & \cellcolor{green!5}Old, Race & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Cool story bro. Stop deflecting, \textbf{Nazi}.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small \@lineflyer1 for Christsake leave The Jesus out of this.   \textbf{Dumb} argument from someone who doesn9know the New Testement all that Well.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small \@Alex Thompson ask a \textbf{Bible thumper} this..  if you hate Jews so much than why are you still quoting from their book?   I dont get it.  TRUE Christian then should only be quoting the New Testement.  Otherwise leave Jesus out of this debate.\normalsize   & \cellcolor{green!27}Bible thumper & \cellcolor{green!27}Religious Identity - Christian & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small \@Alex Thompson as \textbf{crazy} as hating on all white people over slavery 200 years ago.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small Your grandfather fought for himself and his friends, \textbf{nothing} else.  The ones sent to war have no idea what they're fighting for. He probably just wanted to sweet talk some girls and get some poon, not shoot a rifle across the planet at people he never met.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}\small Do they call things out when \textbf{African} Americans are attacked?  This is awful but have this same energy when it's done to \textbf{African} Americans.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/24 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small Hilary being \textbf{racist} against blacks, calling for incivility, Maxine waters calling for mob violence against political opponents, funding foreign invasions to come to America, fake bomb false flags, authoritarian.. corrupt news outlets the levels of depravity the Globalists, CNN, democrats and antifa are going too is sickening the american people have had enough!VoteRed\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/54 & \cellcolor{green!27}1.852 \\  \hline
  \cellcolor{green!5}\small BULLSHIT. It's not on the rise. Talk to 3 or 4 people, show a little graffiti and some \textbf{old} clips and they say it's on the rise. Brainwashing bullshit.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}\small It had another \textbf{spike} right after our moron in chief declared himself a nationalist.\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Do we have NOSTRADAMUS documents writing/portraying re-establishment of \textbf{NAZI} ANTI-SEMITISM 70 YEARS LATER???\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small AND HATE FOR \textbf{BLACK} PEOPLE TOO! BUT THAT IS NOT IN THE NEWS!\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Education is the only way to rid the population of \textbf{racism} and hatred\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Fake news!Fake outrage!Fake \textbf{nazi}!Fake reporters!Fake compassion!\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Just a reminder for the \textbf{nazi} lovers:  [LINK] \normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small I'm pretty sure it's all fake .. Just like the jewish \textbf{chick} at the college who was drawing the swastikas ... and yet you call the the shooting of the top office in Florida vandalism ... CNN is trash news\normalsize   & \cellcolor{green!27}Chick & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small lineflyer1...pretty \textbf{lame}, Millhouse.\normalsize   & \cellcolor{green!5}Lame & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small I'm pretty sure your a \textbf{racist} and a piece of shit who would have been better off if your mama had aborted your ignorant stupid ass. Vietnam Veteran retired\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Ernest Brown just because I don't believe the official story dissent make me a \textbf{racist} ... I am part Jewish btw I just don't beleive the story at all ... I'm pretty sure the Vietnam war is the stupidest war ever faught and an obvious banker war but thanks for your service regardless ...\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small \@Glucoperon basic Hegelian dialectic tactic so both sides are fcked. This is why those who GOVERN the \textbf{MENTal} always win over the sheeple\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@Zack Asante   Love how you bring \textbf{race} into it right off the bat. \textbf{Racist}.\normalsize   & \cellcolor{green!5}Race, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/14 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Glucoperon those who GOVERN your \textbf{MENTal} are never on our side, time to grow up buddy\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small \@Glucoperon \@Zack Asante schooled you, you racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small America needs counseling. \textbf{Black} people have p.t.s. on the same levels as our American troops. White men are getting more and more violent....its like as a \textbf{nation} we take one step forward and three steps back. How long can a \textbf{nation} thrive with the way things are going. And people won't even own up to their wrong doings. Can't heal what we won't admit exists. Real shizit\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}3/67 & \cellcolor{green!27}4.478 \\  \hline
  \cellcolor{green!5}\small when Jews are attacked it should be unacceptable but when \textbf{black} people are attacked apologize and \textbf{black} people should forgive them\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/21 & \cellcolor{green!5}9.524 \\  \hline
  \cellcolor{green!27}\small rich coming from a \textbf{nazi} like you and its cult.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Who cares? Israel and every \textbf{nation} that surronds it are shitholes that would serve the world better by simply not existing.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Israel is a criminal \textbf{nation}. Trump is a puppet.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small So his solution to stop the Jews who "run the world" was to murder a bunch of \textbf{old} people who have \textbf{zero} control over anything. And a doctor...Like i don't get right wing logic.If you really wanted to "stop the Jews" why not kill someone who actually has power.Oh thats right because the powerful have guards that would fuck their asses up.These Nazis aren't just stupid they are fucking cowards.I hope they rape his ass everynight in prison.\normalsize   & \cellcolor{green!5}Old, Zero & \cellcolor{green!5}Age - Over 65s, Age - Youngsters & \cellcolor{green!5}2/83 & \cellcolor{green!5}2.41 \\  \hline
  \cellcolor{green!27}\small Weird flex but ok\normalsize   & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Here goes CNN again, desperately trying to upset the \textbf{R\textbf{ED}} WAVE that is coming!!  GO ORANGE MAN!!!\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Fun fact - \textbf{R\textbf{ed}} Tides are toxic to humans.\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/9 & \cellcolor{green!27}22.222 \\  \hline
  \cellcolor{green!5}\small you aren't really mad at CNN...you are mad at Twitter and other social media outlets for kicking you and you friends off of their platform.   do you feel replaced?  LOL did you \textbf{Nazi} that coming?? LOLOL\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Honor Victims AND Vets: punch a \textbf{nazi}.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small White ppl been getting reeeaaalll bold with the displays of hate speech lately. Smh, racists, anti semitics, anti \textbf{l\textbf{g\textbf{bt}}}, anti immigrants, etc etc etc. need to be eradicated. How the fuck are nazis and racists gonna tell other ppl to leave America? Y'all are the embodiment of what America isn't and is tryna to get away from. America destroyed a lot of Native American, Mexican and \textbf{Black} ppls lives regarding education and just the qualities of life in general for centuries. Yet we can seem to have that same aggressive energy to eradicated racists and nazis? Why is that?\normalsize   & \cellcolor{green!5}Black, LGBT & \cellcolor{green!5}Ethnicity - Black, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!5}4/99 & \cellcolor{green!5}4.04 \\  \hline
  \cellcolor{green!27}\small Covfefe IV Alt right and \textbf{Nazi} are different things, I think you just figured that out for yourself though.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@JOE BLOE of course they're different. I'm not saying Trump supporters are Nazis. I'm saying Nazis... who are clearly \textbf{Nazi}, considering they hold up \textbf{Nazi} flags and \textbf{Nazi} talking points, are more involved in the Alt-Right than any other political affiliation. It's not absurd to suggest it. Just because something bad might be in the same political affiliation as you, it doesn't automatically make YOU as bad as them. I'm not saying Right-Wingers and Trump supporters are evil. I'm just saying THESE Nazis need to be challenged on a philosophical, political, and intellectual level, because their ideology is just fuckin' asinine.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}3/101 & \cellcolor{green!5}2.97 \\  \hline
  \cellcolor{green!27}\small \@Dewitt McDidditt Nazis are more philosophical and intellectual than most people, They listen to classical music like Wagner, and make plans to conquer the galaxy with advanced technology. Alt righters are a bunch of Trump ass kissing \textbf{hillbilly} retards, who like meth, country music, etc.. The alt right was born in America earlier this decade, National Socialism was invented by Adolf Hitler in the 1920's. Understand the difference?\normalsize   & \cellcolor{green!27}Hillbilly & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}\small Covfefe IV - Because they are \textbf{dumb} ignorant morons. We used to just ignore those idiots and not give them the time of day or a platform in the media. Now, not so much. We're fixated on these racists because they identify with Trump. So the media uses them as a way to bash the President. And it's only serving to legitimize them and allow their voices to be heard which, in turn creates more of them. The media is a perfect recruitment tool for them. Which is why we used to ignore them in the first place.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27}\small Covfefe IV - No, we don't need to challenge their philosophy! That's \textbf{dumb}. We just need to start ignoring them again! If you challenge their philosophy, it legitimizes their beliefs as an actual philosophy. Its not. Its completely fukin stupid.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}\small \@Dewitt McDidditt I don't know you, but I know one thing about you. I know that you have never met a \textbf{nazi}. Because \textbf{nobody} has. Because they're not real. CNN is trying to scare you. How do you not see through this yet?\normalsize   & \cellcolor{green!5}Nazi, Nobody & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!5}2/43 & \cellcolor{green!5}4.651 \\  \hline
  \cellcolor{green!27}\small \@Dewitt McDidditt You've heard from many? Where are you running into nazis? Don't lie. Some 12 year \textbf{old} kid larping on the internet doesn't count. What are you even trying to say when you say "they exist alongside KKK White supremacists"? You haven't met one of those either.  And no, a white nationalist is not the same as a white supremacist. I'm neither, but I'm not an idiot, so I don't pretend they're the same.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small \@Alex Mack and yes, I'm specifically addressing the "Nationalist" side of the spectrum. Not so much the "Supremacist" side. I'm just saying it's a little asinine to claim to be a pro-America nationalist yet support a 1930s GERMAN ideology that WE fought in the 1940s. Why is that so difficult to understand? If you're going to be a nationalist, then be a nationalist. Support American ideals. It's just pathetic and lazy to simply copy German \textbf{nationalism} and pretend like it's new and hip again. It's just cringe. Very cringe.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27}\small Covfefe IV - It's not 'ignore them and they'll go away'.  It's 'let's not give them airtime and publicity.' They're never go gonna go away completely. And trust me, they love the new media policy. When they did marches and protests before, no one listened to them. Now they get plastered all over the national news. Its the best thing that ever happened to them. And it's what EVERY intelligent person does when confronted with absurd nonsense. You don't dignify it with a response! It \textbf{common} sense.  I don't know who raised you or how \textbf{old} you are but you sound very young and niave. You've seriously never heard of this very commonly used tactic? Ask around.\normalsize   & \cellcolor{green!27}Common, Old & \cellcolor{green!27}Age - Over 65s, Social Class - Working class & \cellcolor{green!27}2/117 & \cellcolor{green!27}1.709 \\  \hline
  \cellcolor{green!5}\small Covfefe IV - What would have happened in Charlottesville if \textbf{nobody} showed up to that stupid rally and those idiots ended up marching in an empty ghost town?  \textbf{Nothing}. We wouldn't even be having this discussion right now.\normalsize   & \cellcolor{green!5}Nobody, Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/38 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Covfefe IV - Hello!?!? I'm not saying ingnore the problem! We should still teach our children and students that \textbf{racism} is wrong and should have no place in our society! I'm saying ignore the RACISTS when they're out to get attention and stir the pot. Don't give them a platform. Don't give them the megaphone.  Don't give them airtime. Don't dignify them with a response. And certainly don't provide free publicity and advertising for their ignorant philosophy. Again,  this is \textbf{common} sense! Not elitism, not ignoring problems.....\textbf{common} sense.\normalsize   & \cellcolor{green!27}Common, Racism & \cellcolor{green!27}Ethnicity - General, Social Class - Working class & \cellcolor{green!27}3/88 & \cellcolor{green!27}3.409 \\  \hline
  \cellcolor{green!5}\small Covfefe IV - It's NOT faulty logic. We started that policy in the 70's and \textbf{racist} incidents had been declining for decades. Now we give \textbf{racism} a platform and free publicity again and lo and behold,  \textbf{racist} incidents are on the rise! Obviously it's YOUR LOGIC that is faulty. The proof is in the pudding darling.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}3/56 & \cellcolor{green!5}5.357 \\  \hline
  \cellcolor{green!27}\small \@Bovine One my logic isn't the logic that's reflected in the MSM, bud. I'm not saying to give them a platform. I'm saying any reasonable person would have the ability to win arguments against people who have terrible beliefs. It shouldn't be ignored nor given a platform. It should be dismantled on it's own terms, like the flat-Earth society, but obviously not in that EXACT way. Of course here in Elkton, Maryland, where I live, I don't confront Nazis on the daily. It doesn't mean they don't exist ironically down in the Bible belt, lol. Every major society tries to ignore ideological trends and outside ideas. They never go away. If we have the ability to dismantle their ideas, we have \textbf{nothing} to worry about. We just need to hammer in what we know and convince people who might be tempted by such extremist beliefs.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/145 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}\small Covfefe IV -And I'm saying we shouldn't be arguing with them in the first place. We combat the problem by teaching our young people about the dangers and stupidity of \textbf{racism} and by not dignifying actual racists by engaging them in debate or giving them free publicity.  I've made my point and you've made yours. Agree to disagree?\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small this is laughable, Trump is as pro Israel as it gets, his daughter is jewish, grandchildren are jewish, his son married a jew and some his top advisors are jewish and his cabinet is disproportionately jewish. Two of the biggest reasons for the spikes in the ADL data are because of the jewish teen in Israel who hated Trump and made bomb threats to synagogues in the US to try and blame Trump supporters. Then there was the \textbf{black} muslim who wrote for the Atlantic who also sent in a few bomb threats to synagogues, actual violence in the ADL data shows a sharp drop.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/105 & \cellcolor{green!27}0.952 \\  \hline
  \cellcolor{green!5}\small \@kathy kelly all of that means \textbf{nothing} Trump also married a \textbf{woman}( at least I think it's a \textbf{woman}) he has daughters and a sister he had a mom all of whom are women yet he treats women like shit remember grab them by the \textbf{pussy} or the fact that he's cheated on all three of his wives he speaks of his own daughter in a most inappropriate way like he really wants to date her and that's cleaning it up so all of that mess that you said about how he feels about Jews is bullshit\normalsize   & \cellcolor{green!5}Nothing, Woman, pussy & \cellcolor{green!5}Age - Youngsters, Gender - General, Nationality - Chinese & \cellcolor{green!5}4/97 & \cellcolor{green!5}4.124 \\  \hline
  \cellcolor{green!27}\small The EU is having a dramatic \textbf{spike} in Anti-semetic attacks because they let millions of Muslims in.\normalsize   & \cellcolor{green!27}Spike & \cellcolor{green!27}Religious Identity - Protestant & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small Spike in anti-semitism? Correct. College \textbf{age} leftist agitators supporting and enabling Palestinian and Arabic \textbf{terrorist} groups and individuals.\normalsize   & \cellcolor{green!5}Age, Spike, Terrorist & \cellcolor{green!5}Age - General, Religious Identity - Muslim, Religious Identity - Protestant & \cellcolor{green!5}3/18 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small What's the matter they hurt your \textbf{Nazi} feelings?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small You're \textbf{dumb}, perfect fit to be a democrat.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Zero Tolerance for Jews but not everyone else?\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small Hate TV is at it again! Stoking fear and conjuring up vile comments from the \textbf{Nazi} News Makers (NNM) at CNN...\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Tom Manley...amazing powers of \textbf{nothing} notable.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Fake news fake news I will say this though since Trump is became president all the white people been acting crazy\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Hunt down these anti Semitic freaks and let's hope they rot in hell for this and get the fbi or Armed forces track and hunt down Neo \textbf{Nazi} terrorists and White supremacist groups and put them in jail where they will suffer the consequences. Never again with Nationalist or Socialist \textbf{nationalism} And never again mess with America ever.\normalsize   & \cellcolor{green!27}Nationalism, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Nationality - General & \cellcolor{green!27}2/58 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small it was your \textbf{nazi} in chief you kin piece of \textbf{nazi} treasonous shit.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/13 & \cellcolor{green!5}15.385 \\  \hline
  \cellcolor{green!27}\small Your mama caused this because she had your stupid ass she should have aborted your bitch ass and then we wouldn't have to here from \textbf{crazy} ignorant ass. Vietnam Veteran retired\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small \@randomsheep11 the shooter was an inbred who still has \textbf{sex} with his daughter to preserve the white \textbf{race}.\normalsize   & \cellcolor{green!5}Race, Sex & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small look at those repuglicants cards and see the swastika stamped on it\textbf{nazi} POS.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@El Taco H. SARCASTIC AND TASTY oh? That sounds awesome, because at the very least I am not a rasist \textbf{hick} who believes lies from a man with a dead hamster on his hair, and a dick to match, now of you excuse me I have to work for a job that pays, have fun with your right hand\normalsize   & \cellcolor{green!5}Hick & \cellcolor{green!5}Ethnicity - White & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}\small DEMOCRATS AND THE \textbf{NAZI} PARTY AT IT AGAIN.Democrats started the KKK and are the slavery PARTY. Cnn is a klan meeting place.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}\small you are the \textbf{nazi} you kin bastard \textbf{terrorist}.\normalsize   & \cellcolor{green!5}Nazi, Terrorist & \cellcolor{green!5} Ideological and Political Identity - General, Religious Identity - Muslim & \cellcolor{green!5}2/8 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small The KKK was created by Albert Pike a Republican.Its membership came from all politicals parties. When the Democrats passed the Civil Rights Act 1965 the KKK became a arm of the Republican party.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within.\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}2/114 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}\small Harley Trujillo...the \textbf{Nazi} party purged assholes like you. They labelled someone like you as 'feeble minded'. Grab a history book and while you're at it read about Adolf, Trump's hero.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small \@Hawkzblade  facts are facts Democrats are the \textbf{Nazi} party\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Harley Trujillo explain why rumps voters are the only ones wearing \textbf{Nazi} insignia.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Mr407Mike Democrats support Antifa and \textbf{Black} lives matter  these groups are the kkk\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Harley Trujillo explain why rumps voters are the only ones wearing \textbf{Nazi} insignia\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@Darrin Rentruc I think I would rather be deported than live in a country that thinks blatant \textbf{racist} and white supremacy is okay. Oh wait, my people were here first! Maybe YOU PEOPLE should get the hell out!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@Dhark Rix \textbf{Nobody} knows who was here first \textbf{dumb} \textbf{dumb}.\normalsize   & \cellcolor{green!5}Dumb, Nobody & \cellcolor{green!5}Age - Youngsters, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/10 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Lee Cortez go to Mexico's ass and wade in your \textbf{racist} bullshit\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I wonder why fox news doesn't cover the farmers receiving welfare are the \textbf{racist} states that TRUMP visits Mississippi Texas south and North Dakota where most of the white people who are republicans are own government assistance. Vietnam Veteran retired\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small Because they don't have to do with white \textbf{nationalism}? Stay on topic moron.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small J Russ technically the left plans to divide and conquer. Divide us by \textbf{gender}, \textbf{race} religion, etc.\normalsize   & \cellcolor{green!5}Gender, Race & \cellcolor{green!5}Ethnicity - General, Gender - General & \cellcolor{green!5}2/17 & \cellcolor{green!5}11.765 \\  \hline
  \cellcolor{green!27}\small Shadow Might but creating categories implies that there is a more structural hierarchy. That's a dangerous road to go down. A lot of republicans (especially in the south) tend not to divide each other and really don't care what you identify as or come from so long as you're respectful. Source: I'm \textbf{black}.\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}\small Another \textbf{black} reporter insinuating that Trump is a \textbf{Nazi}. I'm not surprised that the Alt-Left media is using accusations of \textbf{racism}, and bigotry to defame their political enemies. This is the Kavanaugh Confirmation hearings all over again.\normalsize   & \cellcolor{green!5}Black, Nazi, Racism & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/37 & \cellcolor{green!5}8.108 \\  \hline
  \cellcolor{green!27}\small Who said she was \textbf{black}? Y'all see darker skin and automatical think \textbf{black}. Gtfoh. Damn IGNORANT, JOBLESS trolls 😂\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/19 & \cellcolor{green!27}10.526 \\  \hline
  \cellcolor{green!5}\small Reporters don't have to insinuate anything. Trump surprise us with his \textbf{racism}, bigotry and ignorance everyday and in every way. All countries divided among themselves will surely fall. You idiots are only helping to destroy this country from within. I can here the words of other world leaders through their laughter, foe and friends alike. "Let them fight and destroy themselves...  Hell will sort them out. We don't have to loose any men or sleep over this country.\normalsize   & \cellcolor{green!5}Racism & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}\small \@TheDent InRm'sChin You fucking \textbf{racist}!!!!!!!!!!!!!! HOW DARE YOU ASSUME SHE' MAY NOT BE \textbf{BLACK}!!!!!!!!!!!!!!!!!\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@DishingOut Ls don't you just love it when trumpazees accuse everyone else of that which you are most guilty? Rape enthusiasts, homophobes \& bigoted trash are facing backlash so I'm sure you view it as bullying - but really you're just being asked to keep your unwanted microdicks \& \textbf{racist} hate to yourselves. Grow the fuck up \& deal with it, bitch.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}\small \@Theatre Junkee who the duck is a rape enthusiast you fucking imbecile. Ohhhhhh it's actually you fucking idiots on the left.  90 percent of the women in Hollywood have been raped to get into the entertainment industry. That's why the me-too movement started. Because of all the wacko \textbf{sex} addict leftist rapists. Whatta buncha whackos.\normalsize   & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}\small Jester I asked my mom if you were an incel. She just shook her head, saying "There isn't enough cash \& tequila in this world to get a \textbf{woman} with that poor lil fellow."I'm thinking that means "yes."\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}\small \@Theatre Junkee alright let me start off by saying it may have been a bit unnecessary the way I last commented to you lol so my apologies there,  but anyway...........I don't want to find sources to post. But it's the truth. You can look up basically how the metoo movement started. It all started with those casting directors groping women if they wanted to get a role in a movie. Even Terry Crews said he was groped. They do it because they know that if they speak out then no other groping producer will ever hire them. Their name will basically be tarnished in the Hollywood industry. For example, Bill Cosby. Everyone thought he was so innocent, but was appearently found guilty of \textbf{sexual} assault. So i mean it should be all on the internet.\normalsize   & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/135 & \cellcolor{green!27}0.741 \\  \hline
  \cellcolor{green!5}\small \@DishingOut Ls so everyone else should do research to support your opinion? Awesome. Can you at least reference your statistics?While you're at it, can you prove such inappropriate behavior occurs solely within the entertainment industry? Cuz there's a couple few alter boys claiming kids aren't safe within the church.But nevermind cuz f*ckin lazy, right?Also, you seem to think harassment is transactional - like an offer was made \& the targeted person somehow agreed to it. Coercion is not consent. And more often than not, it's really a matter of "I'm powerful enough to destroy any chance of you having a career so STFU \& take it." I've spent some time in HR, more than one industry. The majority of those harassed expressed the desire to be left tf alone \& allowed to earn their own way. Generally it was the lechers who made the most threats against the company (and are often protected to avoid PR issues for the organization.) The very best any harassed person can hope for is hush money. They're likely \textbf{black} balled from their industry of choice either way.So in addition to being lazy, you're also ignorant af.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/196 & \cellcolor{green!5}0.51 \\  \hline
  \cellcolor{green!27}\small \@Theatre Junkee lol I like how the list keeps growing. Dude you said you worked in HR. That means you had somebody watching you. These guys don't have anybody above them watching. They have \textbf{nobody} else to report to but themselves. Its a different situation.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}\small I say we get back to kicking and maiming nazis. The only good \textbf{Nazi} is a dead \textbf{Nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/18 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small CROOKED HILLARY SHOWS HER DIXIE DEMOCRAT ROOTS.  [LINK]  \textbf{RACIST} BITCH.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small HOW CAN ANY PERSON BE A WHITE NATIONALIST WHEN 750,000 AMERICAN SOLDIERS DIED DEFEATING HITLER; THEY'RE ANTI-AMERICANS \& NOT TRUE PATRIOTS \& SCREW FARRAKHAN TOO HE'S A \textbf{BLACK} \textbf{RACIST} \& JUST AS BAD AS THEY ARE!!💯😈😈🆗🇺🇸✌😎\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/36 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small \@lineflyer1 Well.. jesus was just a \textbf{crazy} guy who walked around in robes talking about how he was the son of god.. what would you do if you saw someone like that today?  You would send him to the \textbf{loony} bin.  Back then, they were a tad bit less civilized than trump supporters of today, and they killed without remorse.\normalsize   & \cellcolor{green!27}Crazy, Loony & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/60 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}\small \@Tomee Gunz Stop defending him.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small \@max smart and here you are again you are a sociopath \textbf{lunatic} you are on every CNN post expressing your discontent your hate and your propaganda I'm guessing you're some 400lb loser living in your \textbf{transgender} Daddy's basement that you call a safe space with your Obama blow up doll next to you.. you need to get a life or a hobby and masturbating to \textbf{g\textbf{ay}} porn is not a hobby.. it eats you up inside that Trump is president, it drives a \textbf{mental} doesn't it LOL ...pathetic loser\normalsize   & \cellcolor{green!27}Gay, Lunatic, Mental, Transgender & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}5/89 & \cellcolor{green!27}5.618 \\  \hline
  \cellcolor{green!5}\small Things were much better when we had \textbf{race} riots burning down cities going on under Obama\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small \@Tomee Gunz Stop defending him.Facts: Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}2/86 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}\small \@WhiteWalkers i was bit by a \textbf{transsexual}.\normalsize   & \cellcolor{green!5}Transsexual & \cellcolor{green!5}Sexual Identity - Transexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small WOW! Lots of butt hurt traitors of America on this thread. Now get your fucking broke dick and \textbf{fat} asses back to work. Trump created 7.1 million jobs in August. Instead of sitting at Starbucks all day sponging free internet and spreading hate, you can contribute to society. Then you can go home and suck off your \textbf{faggot} and \textbf{lesbian} lovers and eat mustard sandwiches and watch the View.\normalsize   & \cellcolor{green!27}Faggot, Fat, Lesbian & \cellcolor{green!27}Physical Identity - Physical Features, Sexual Identity - Female homosexuality, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/69 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small RC how did he do that? By letting his son give him jewish grandchildren or by making Jerusalem the capital of Israel.You are a \textbf{dumb} bastard aren't you.  All of the hate comes from the left side \textbf{black} lies matter Code pinkAntifaLinda Sarsour I could keep going!\normalsize   & \cellcolor{green!5}Black, Dumb & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/50 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small max smart Who is the biggest supporter of the socialist liberal democratic party.George Soros who during ww2 collaborated with the \textbf{nazi} and sent his own jewish people to the death camps men women and children THOUSANDS of them!Then soros and the nazis stole their property now where fo you think your hate filled party gets its money from!F'ing idiot.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}\small No thick fuck that would be soros and antifa who shout \textbf{nazi}  check the photos of him in his ss uniform\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}\small Nobody is making you hate.  Take a look around.  The left is full of hate\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@max smart "Stop defending him."  Why, its SOOooo easy:)   1. Trump stole all his policies from David Duke and the KKKProof?1. Trump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Of course, you would have to prove that PRESIDENT Trump's MAGA.....is for "whites only".   Good luck:)3. Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally. [LINK]    "was IN the KKK"....LMAO.4. Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.LMAO....."charged", 1973     "destroying the \textbf{nation}."   Oh really?  How exactly????    WTCRtmTaRtATM     Ibyttopt-----(ntmuabosai) TaCntrtrastaeattsf--ICwftowg"ts",yonacolmgnbiolnaacfiolmgrorbswhwyattbtntgambLinux Free Font TestLIberation Sans\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/129 & \cellcolor{green!5}1.55 \\  \hline
  \cellcolor{green!27}\small RC ,,, it wasn't trump it was Obama start hate , before Obama , blacks and whites go on better , it true ,  everybody went out and vote.for the first \textbf{black} leader and we all hope Obama was going to make everybody closer \textbf{black} and white , women and men but he make things worst , he really did ,  and then we got Trump out of it ,  it \textbf{crazy} but true ,\normalsize   & \cellcolor{green!27}Black, Crazy & \cellcolor{green!27}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}3/75 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small \@Sigkim Civil rights violations Trump company:In 1973, the U.S. Department of Justice's (DOJ) Civil Rights Division filed a civil rights suit against The Trump Organization charging that it refused to rent to \textbf{black} people. The National Urban League had sent \textbf{black} and white testers to apply for apartments in Trump-owned complexes; the whites got the apartments, the blacks did not. According to court records, four superintendents or rental agents reported that applications sent to the central office for acceptance or rejection were coded by \textbf{race}.\normalsize   & \cellcolor{green!5}Black, Race & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}3/86 & \cellcolor{green!5}3.488 \\  \hline
  \cellcolor{green!27}\small \@max smart "America First and Make America Great Again come from the 1920s KKK the second part of it is make it white."  OH...but of course you "ignore", the following:)   " Of course, you would have to prove that PRESIDENT Trump's MAGA.....is for "whites only"Fail:("See: The Trump Duke ticket." [LINK] See blatant propaganda piece, with the INSERTED voice of Lindsat Graham.Oh lookie...."COMMENTS \textbf{DISABLED}"....HA HA HA.OH GEE< I wonder why????  Maybe for the FACT that it takes Trumps words out of context??  [LINK]      [LINK]    YOUR....."version".  "We must immediately suspend immigration..."   THE REAL VERSION with CONTEXT..."We must immediately suspend immigration, from any \textbf{nation}, that has been compromised by terrorism, until such time as proven vetting mechanisms have been put in place, WE DONT WANT THEM in our country.  OH GEE< lets see what Trump's E.O says:)  [LINK]  8 U.S.C. 1182(f),   <<The hell is that?  OH:) [8 U.S. Code § 1182(f) - Inadmissible aliens Suspension of entry or imposition of restrictions by President  Whenever the President finds that the entry of any aliens or of any class of aliens into the United States would be detrimental to the interests of the United States, he may by proclamation, and for such period as he shall deem necessary, suspend the entry of all aliens or any class of aliens as immigrants or nonimmigrants, or impose on the entry of aliens any restrictions he may deem to be appropriate.]   The above is CURRENT, CONSTITUTIONAL LAW, as was proclaimed in PRESIDENT Trump's E.O. PROTECTING THE \textbf{NATION} FROM FOREIGN \textbf{TERRORIST} ENTRY INTO THE UNITED STATES    Thats just on part of your little shit show debunked....shall we go ON??????I await your response:)    WTCRtmTaRtATM     Ibyttopt-----(ntmuabosai) TaCntrtrastaeattsf--ICwftowg"ts",yonacolmgnbiolnaacfiolmgrorbswhwyattbtntgambLinux Free Font TestLIberation Sans\normalsize   & \cellcolor{green!27}Disabled, Nation, Terrorist & \cellcolor{green!27}Nationality - General, Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!27}4/292 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}\small \@max smart Well...wheres your "rebuttals?   Or is that your thing?  Just accuse, throw out crap, and then scurry away after being challenged?    BTW....you FAIL to answer this question:    [1. Trump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Of course, you would have to prove that PRESIDENT Trump's MAGA.....is for "whites only".   Good luck:) ]      Still working on that?   OH< lets not forget:\@t   Watch for a few seconds\@t   Warch for 20 seconds to see the full context.It seems you offer BLATANT propaganda as "proof" of \textbf{racist} \textbf{racist} \textbf{racist}.....As for PRESIDENT Trumps FACTHER< you have YET to offer proof of HIM being in the KKK.....which of course would have \textbf{nothing} to do with PRESIDENT Trump himself even if he WAS.Shall we go on about PRESIDENT Trump's settled case with the government from 1975?????How about the montage of candidate AND president AND civillian Trump,  denouncing david dumbass duke,  AND the KKK, despite all the fake ass news media claims he never did, or refusesd to do so?    Anything else?????\@t   Watch for a few seconds\@t   Warch for 20 seconds to see the full context.Of course, the above is the most rediculous you have to offer, and was taken COMPLETELY out of context.....no apology for submitting such blatant CRAP as actual "evidence" of \textbf{racist} \textbf{racist} \textbf{racist}?Personally, I would be embarrased as hell if I was trying to "prove", something, and offered this CRAP as actual "proof".   Care to make a retraction of your "proof?"  Or are you actaullly going to "let it stand?"WTCRtmTaRtATM     Ibyttopt-----(ntmuabosai) TaCntrtrastaeattsf--ICwftowg"ts",yonacolmgnbiolnaacfiolmgrorbswhwyattbtntgambLinux Free Font TestLIberation Sans\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}5/279 & \cellcolor{green!5}1.792 \\  \hline
  \cellcolor{green!27}\small White supremacy is a myth. it only exists in the mind of the left. This country is less \textbf{racist} now than its ever been. Most of there \textbf{racism} is from the left. Conservatives are WAY more tolerant and accepting of other people..\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/42 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small HATE was already  with us HUMANS  and \textbf{ZERO} brought it out  with BLM  and then growing and harvesting  ISIS  /ISIL   and then  investing in IRAN  ?? Did you forget that  or are are you covering up  the World wide Migration  that has destroyed  Germany  and is attacking  FRANCE ?? The World has caught on   and is  responding ???  \textbf{ZERO} was a svengali  for Socialism  and the destruction  of the USA ?? sorry\normalsize   & \cellcolor{green!5}Zero & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}2/72 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small Thanks MSM for turning the entire \textbf{nation} against itself.i mean ORANGE MAN BAD, FREEZE PEACH, DERP\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small vague1 a vague shape: indistinct, indefinite, indeterminate, unclear, ill-defined; hazy, \textbf{fuzzy}, misty, blurred, blurry, out of focus, faint, shadowy, \textbf{dim}, obscure, nebulous, amorphous, diaphanous. ANTONYMS clear, precise.2 a vague description: imprecise, rough, approximate, inexact, incomplete, nonspecific, generalized, ambiguous, equivocal, hazy, woolly. ANTONYMS clear, precise.3 they had only vague plans: hazy, uncertain, undecided, unsure, unclear, unsettled, indefinite, indeterminate, unconfirmed, up in the air, speculative, sketchy. ANTONYMS firm.4 she was so vague in everyday life: absentminded, forgetful, dreamy, abstracted, with one's head in the clouds, scatty, scattered, not with it. ANTONYMS organized, together.\normalsize   & \cellcolor{green!5}Dim, Fuzzy & \cellcolor{green!5}Ethnicity - Black, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/95 & \cellcolor{green!5}2.105 \\  \hline
  \cellcolor{green!27}\small I'm an \textbf{immigrant} in US. As a lots of immigrants, I probably should hate Trump too. But, I don't and let's talk real. He can change some rules, but not the people. If you hate somebody, please don't blame anybody else. How did Trump make you hate others? I just don't get it. I guess it's just easy not to take any responsibility and blame others...\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small I hate you for your inability to keep your mouth shut when all you added was something so ridiculous, you made everyone totally clear that you are an idiot with no logic, reasoning, or \textbf{common} sense.  I'm not a proud anti-Semite because of Donald!  I think he's WAAAAY to easy on them considering the top problems wit politics today are the Jews in the liberal party that don't care about murdered police officers  that won't get to see their 5 month \textbf{old} son's next Christmas and who want to give more rights and freedoms to everyone not even living here, but then they wan to tax us up to 70 to make ANOTHER attempt at the same fucking thing that has NEVER EVER EVER FUCKING WORKED!!!  P.S.  I hate you as much as a Jew.  You Juden?  GAS!!!\normalsize   & \cellcolor{green!5}Common, Old & \cellcolor{green!5}Age - Over 65s, Social Class - Working class & \cellcolor{green!5}2/138 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small You're going to confuse alot of uneducated noe \textbf{nazi} \textbf{t\textbf{railer trash}} rump supporters.Good job! 😀👍\normalsize   & \cellcolor{green!27}Nazi, Trailer trash & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - White, Social Class - Working class & \cellcolor{green!27}3/16 & \cellcolor{green!27}18.75 \\  \hline
  \cellcolor{green!5}\small yes barry is mixed race\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Spurred on by SDN, the \textbf{Nazi} network.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Terrorist KKK Trumptards Very \textbf{Lunatic} Folks who Need Medical Help 🤔\normalsize   & \cellcolor{green!5}Lunatic, Terrorist & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}2/11 & \cellcolor{green!5}18.182 \\  \hline
  \cellcolor{green!27}\small Terrorist KKK Trumptards Very \textbf{Lunatic} Folks who Need a noose, electric chair, lethal injection or firing squad. Fixerated.\normalsize   & \cellcolor{green!27}Lunatic, Terrorist & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!27}2/18 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small \@Stop Political Cencorship pls Bannon created the Alt right and White nationalist to get Trump elected.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/96 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}\small \@Kolin Mademe It's not nice to call people retarded because they dont have the same political views as you. Autism is \textbf{nothing} too joke about. Grow up.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Agree with every word mate. These \textbf{Racist} Animals needs to be put out the country asap. These Trump Trash Cultist are Lunatics all of them.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small Wait a minute I thought we were communists? How can we be \textbf{communist} and fascist at the same time?\normalsize   & \cellcolor{green!27}Communist & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small Obama is a Christian and Louis Farrakhan doesn't speak for \textbf{black} people like Obama and myself in fact Louis Farrakhan has white blood in his body he s more like stupid ass th an Obama and me we \textbf{black} don't follow because your \textbf{black} the jews have been their for \textbf{black} people way before Farrakhan and I am a ex \textbf{black} panther. Vietnam Veteran retired\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}5/65 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small Lunatic Lindsey Graham 😁\normalsize   & \cellcolor{green!27}Lunatic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small And here you go again every day you're here expressing hate you need to get a life get a hobby masturbation is not a hobby but then again you're probably some 400 pound loser stuck in your mommy and daddy's basement watching \textbf{g\textbf{ay}} porn all day\normalsize   & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!5}2/46 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Well well here you are again you're on every post every day you are a sociopath \textbf{lunatic} obviously\normalsize   & \cellcolor{green!27}Lunatic & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small But it was Hilary who was \textbf{racist}? Saying blacks lookalike, explain that?\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}\small stop \textbf{racism} QUEENKIM4EVER.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@Your Friendly Neighborhood Lawbringer Stop defending him.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..Trumps daughter married a jewish guy to piss off daddy.\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/97 & \cellcolor{green!5}2.062 \\  \hline
  \cellcolor{green!27}\small \@Stop Political Cencorship pls But we all know Trump is a \textbf{racist}, bigoted Archie Bunker wannabe,  that's the difference between he \& Ali...\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}\small \@The Crusader Do you REALLY wanna lay out who's \textbf{racist} \& what they have said and/or done? Do you REALLY wanna go there ? Lmao\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@The Remixstress Hillary called \textbf{black} people super predators...\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@The Remixstress but trump is BFF with Kanye West last i checked he was an \textbf{African} American.\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small \@John Balnis Mom First off, He and Kanye are NOT bff's.....The same \textbf{African} American that Trump has said he "wouldn't let count his money" ......\textbf{Racist}, bigots love to say, "I'm not a \textbf{racist}, I have a \textbf{Black} friend!" LMFAOOOO\normalsize   & \cellcolor{green!27}African, Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}4/39 & \cellcolor{green!27}10.256 \\  \hline
  \cellcolor{green!5}\small \@Your Friendly Neighborhood Lawbringer Its fact:Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans. Make it white is the next line. Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/93 & \cellcolor{green!5}2.151 \\  \hline
  \cellcolor{green!27}\small Liberals be like "White devils white devils" then try to pretend not to be \textbf{racist} lol\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Cry me an ocean, white \textbf{nationalism} is the best thing ever.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@The Remixstress it's people like you that think white people and \textbf{African} Americans can't be bff. Your \textbf{racism} makes me sick.\normalsize   & \cellcolor{green!27}African, Racism & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/21 & \cellcolor{green!27}9.524 \\  \hline
  \cellcolor{green!5}\small Good job being a insensitive jackass. People get murdered and you have to inject your politics. You're a real quality piece of shit. Oh by the way a Nationalist is a good thing. Mahatma Ghandi was a nationalist. Is he a \textbf{racist}, hate filled \textbf{nazi} bigot too?\normalsize   & \cellcolor{green!5}Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General & \cellcolor{green!5}2/47 & \cellcolor{green!5}4.255 \\  \hline
  \cellcolor{green!27}\small \@Slick Smoke I can give you a PLETHORA of examples of how the Republicans are DEFINITELY the most \textbf{racist}! You have the UNMITIGATED GALL to say that Dems are the "most \textbf{racist} people ever seen or heard", really, where have you been living all these years, in a box stored \& tucked away in someone's attic???I'd give you some examples of "most \textbf{racist} people ever" since you/the  Republicans love to get Amnesia, but I don't mind "refreshing your drink"!!! Dylann Roof(whom you/the Republicans all LOVE) is a perfect example of the Rightbeing "the most \textbf{racist} people ever" .....Ask the Right wing nutjobs that have went to abortion clinics and shot up \& murdered people if they were too far gone ..... The Right wing Neo-\textbf{Nazi} nutjobs that stood up there chanting "Hail Trump" while doing the \textbf{Nazi} salute is another perfect example of the Right "being the most \textbf{racist} people ever!!"The Right wing White Supremacist nutjobs in Charlottesville that killed a \textbf{Woman} is the Right "being the most \textbf{racist} people ever"!!Shall I continue?\normalsize   & \cellcolor{green!27}Nazi, Racist, Woman & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Gender - General & \cellcolor{green!27}8/177 & \cellcolor{green!27}4.52 \\  \hline
  \cellcolor{green!5}\small \@CynicalJester David Duke is a "Nationalist" too, the same kind as Trump, a \textbf{racist}, bigoted WHITE NATIONALIST!!!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small QUEENKIM4EVER ,, the \textbf{Nazi} hate trump , the \textbf{Nazi} dick who kill the Jews in Pittsburgh , say on is wed sit he trump because he said trump was Jews lover ,  trump said he was a American nationalist not white nationalist ,\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/43 & \cellcolor{green!27}4.651 \\  \hline
  \cellcolor{green!5}\small \@Antonio blonde Sicilian When did I say the media said anything about him being a White Nationalist? That's the problem with you dumbed down, imbecile, Zealot of a Trump cult member, you try to put words into people's mouth all while LYING!With all his \textbf{racist} rhetoric, I think it's pretty safe to say he's a White Nationalist....And besides, Nationalist or White Nationalist, he knows it's a no no to say. hence the reason he said himself, "They say I'm not suppose to say this"!!! Maybe it's YOU whom needs to look up the history behind the word. He should've said he was a Patriotist or has Patriotism , not Nationalist!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/111 & \cellcolor{green!5}0.901 \\  \hline
  \cellcolor{green!27}\small \@CynicalJester Either way, you research the \textbf{racist} tone \& \textbf{racism} that word has behind it and get back with me!!! How about that, since you seem to be uninformed on that!\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small \@CynicalJester GTFOH.....Are you kidding me with that statement of , "I feel sorry for you that your mind is so narrow that one bad person is enough for you to justify generalizing a whole group of people."When the \textbf{racist}, bigoted Dictator you're defending \{Trump} is the MASTER of "generalizing a whole group of people"!!You've got to be joking with that statement or just looking for attention via the Youtube comment section, because that statement towards me, when Trump does EXACTLY what you're pointing the finger at me saying I'm doing, is an oxy moron!! LMAOOOOOO\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/97 & \cellcolor{green!5}1.031 \\  \hline
  \cellcolor{green!27}\small Can you believe the \textbf{racist} remarks president Trump made!? He said that all \textbf{black} people look alike?!Well he didn't... Hillary said it.bluewavegoodbye\normalsize   & \cellcolor{green!27}Black, Racist & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Trumps grandchildren are Jews. You would have to be a spectacular moron to think that Trump is a \textbf{Nazi}.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Notice how trump has no solution when it's the right wing committing these attacks.If it's a Muslim or \textbf{immigrant}, trump blames foreigners all the time and demands to close off all immigration\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}\small VOTE YES ON NPC VOTING RIGHTS REMOVAL ACT 2020 quit deflecting bitch, the orange cunt Defends \textbf{nazi} fags cuz he is one himself or is using them to get voters.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}\small People be calling him a \textbf{nazi} with no proof what so ever\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small I'm not racist\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@Rydoboy94 I never called him a nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@John Tuya Is that all you can come up with? You're \textbf{racist} leftist and you know it.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small +Jim Morgan \textbf{Nobody} is afraid of them. We're sick of paying for them. These use welfare at higher rates than all other groups at 73.\normalsize   & \cellcolor{green!27}Nobody & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}\small There are no \textbf{immigrant} or Muslim attacks.  Only white right winged according to cnn\normalsize   & \cellcolor{green!5}Immigrant & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small I saw a trump supporter even say "You can blame all of us for something one \textbf{crazy} guy did"Ummm thats what us Muslims have been saying for years. they are hypocrites.\normalsize   & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Black} Ascension fbi stats, look it up.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small MINUSCULE? People are dying do I need to spell it out for you D Y I N G also being \textbf{racist} isn't gonna help anything I also guess you think that \textbf{g\textbf{ay}} marriage is a sin 🙄\normalsize   & \cellcolor{green!27}Gay, Racist & \cellcolor{green!27}Ethnicity - General, Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}3/37 & \cellcolor{green!27}8.108 \\  \hline
  \cellcolor{green!5}\small VOTE YES ON NPC VOTING RIGHTS REMOVAL ACT 2020 Dude, are you \textbf{blind}? The FBI actually warned of 'growing right-wing terrorism'. Robert Bowers, the man who shot up the synagogue, was motivated by right-wing media who said that the Central American caravan was organized by \textbf{communist} Jews trying to take down the US. And let's not forget the murderous white supremacy cults such as the KKK, Neo-Nazis, Aryan Brotherhood, Neo-Confederates, American \textbf{Nazi} Party, etc, who are all registered Republicans. You must be out of your mind to blame murders on people of color when there are more \textbf{terrorist} attacks and murders being committed by white people. Your username gives me all the info I need about you. You are an alt-right extremist Trump supporter and we will not tolerate your \textbf{racism} and hatred.\normalsize   & \cellcolor{green!5}Blind, Communist, Nazi, Racism, Terrorist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Physical Identity - Physical (and Mental) Impairments, Religious Identity - Muslim & \cellcolor{green!5}5/133 & \cellcolor{green!5}3.759 \\  \hline
  \cellcolor{green!27}\small hijacked symbols Hitler was a fascist. You know... an alt-right ideology. Do you know what the Night Of The Long Knives was? Every socialist \textbf{Nazi} officer was rounded up and publicly executed. Read your history before you spout bullshit. If Hitler was a socialist, then he wouldn't be rounding people up and killing them based on their \textbf{race}, religion, \textbf{ethnicity}, \textbf{sexual} orientation, etc. That is the definition of fascism.\normalsize   & \cellcolor{green!27}Ethnicity, Nazi, Race, Sexual & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - General, Gender - General & \cellcolor{green!27}4/69 & \cellcolor{green!27}5.797 \\  \hline
  \cellcolor{green!5}\small \@David Nissim antifa is a \textbf{terrorist} group.. they have been listed as such in most States.. so. Why are they being allowed to get away with harming people? Why are they being allowed to bash Jewish people over the head with a bike lock or conservatives? That does more to inflame violence than Donald Trump\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}\small Trump will denounce \textbf{nationalism} when Jewish community condemns the murder of Jesus Christ\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Lord Jesus Christ. God almighty ikr I'm pretty sure he's a 12 year \textbf{old}.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Because anyone who disagree with you is a \textbf{Nazi} obviously.When will you understand that constantly calling people \textbf{Nazi} made the insult worthless and ineffective ?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@The Crusader gotcha....👀. Oh, \& I'm NOT a lefty. I don't have ties to any party. I don't believe in it. My father is Jamaican. I'm a citizen \& grew up there also. Yes I'm born in the states before you start tripping. But in Jamaica they have 2 parties also....the JLP \& PLP. \& guess what? They fight each other just as they do here. Lol, I learned as a kid that politics are useless no matter what place or people.....\textbf{nothing} more than a gang is all. I affiliate myself w my son \& daughter. Only party I belong too.\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/101 & \cellcolor{green!5}0.99 \\  \hline
  \cellcolor{green!27}\small \@Peyton Bell these trolls are trying to demonize \textbf{Nationalism} they call people who are nationalists Nazi's ... Chinese are Nationalist, Scottish are Nationalist and Jamaicans are Nationalist the left seem to think we're all Nazis, they are ridiculous.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small \@The Crusader trolls?? YOU ARE A \textbf{NAZI}!\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small \@Rick Sanchez are popstars fascist, \textbf{Nazi} white supremacists too?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small Impeach \textbf{Nazi} Monster 45 😠\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small You are a sociopath \textbf{lunatic} you are here everyday commenting on every comment and it's all hate and negativity what are you some kind of dedicated emo loser living in your \textbf{transgender} Daddy's basement that you call a safe space with your blow up Obama doll you probably sit around all day and watch \textbf{g\textbf{ay}} porn. You are 1 dedicate a loser you really are\normalsize   & \cellcolor{green!27}Gay, Lunatic, Transgender & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments, Sexual Identity - General, Sexual Identity - Male homosexuality, Sexual Identity - Transexuality & \cellcolor{green!27}4/65 & \cellcolor{green!27}6.154 \\  \hline
  \cellcolor{green!5}\small And how is Donald Trump a \textbf{nazi} now?\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small JESUS CHRIST THE MOST HIGH GOD Impeaching Trump will change \textbf{nothing}.  Trump is just a symptom of the problem.  The source of the problem is the corporate state our \textbf{nation} has become.  We've allowed our political system to be hijacked by the ruling financial elite.  Only a handful of democrats in Congress that don't take corporate money remain who truly represent us.  The rest of the democrats in Congress like Pelosi, Schumer, Feinstein, Booker, Harris, etc, are just as bought off as republicans.  Until this changes \textbf{nothing} else will change.  Only when Congress and the White House are controlled by FDR democrats and Eisenhower republicans can things change.\normalsize   & \cellcolor{green!27}Nation, Nothing & \cellcolor{green!27}Age - Youngsters, Nationality - General & \cellcolor{green!27}3/108 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}\small Terrorist like a tourist it is not funny -i dont no what is right tell somebody ?\normalsize   & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Religious Identity - Muslim & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Trump is as likely to Be called a Jew lover by the radical left as a Nazi\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small This has \textbf{nothing} to do with trump or \textbf{Nationalism}.... \textbf{Nationalism} is a great thing it's the identity of the people.. Chinese are Nationalist, Jamaicans are Nationalist, Scottish are Nationalist.. you, are an idiot.\normalsize   & \cellcolor{green!5}Nationalism, Nothing & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}2/33 & \cellcolor{green!5}6.061 \\  \hline
  \cellcolor{green!27}\small \@Iridescent ink What makes me laugh is that Russia built the tanks and planes the German military used to invade Russia. Joseph Stalin was so much of a fool he believed Hitler when he said, we have no plans to invade Russia, while at the same time Hitler was calling Russians a subhuman \textbf{mongoloid} \textbf{race}. So again little man do your research.\normalsize   & \cellcolor{green!27}Mongoloid, Race & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/62 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Nationalism means strength.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}\small \@theylied1776: Here you go what we teach children. It will help your \textbf{mental} disability:  [LINK]  operation Barbarossa idiot.\normalsize   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@ThirdEyeOpen How is this a weakness ?The success of western civilization would never have come to be without \textbf{nationalism}.I could even argue making a country abandon \textbf{nationalism} is the best recipe to slowly destroying it.\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}2/37 & \cellcolor{green!5}5.405 \\  \hline
  \cellcolor{green!27}\small \@The CrusaderBut you have to remember that leftists hate the US, so that means they are against \textbf{nationalism}.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small \@ThirdEyeOpen How is that weakness? lol If anything that means strength. Imagine a \textbf{nation} that sticks together for their country vs. a \textbf{nation} where \textbf{nobody} sticks up for each other. Who do you think is the stronger one? Exactly. Whitchyo im tryna sound smart headed azz\normalsize   & \cellcolor{green!5}Nation, Nobody & \cellcolor{green!5}Age - Youngsters, Nationality - General & \cellcolor{green!5}3/46 & \cellcolor{green!5}6.522 \\  \hline
  \cellcolor{green!27}\small Bernie Sanders owns the Socialist label.  That's the second half of National Socialist.  Does that make him a \textbf{NAZI}?  Can't have it both ways moron.  If the victims were in the 1, does that make Bernie and the rest of the Democratic Party responsible for their rhetoric?  Have you heard the anti Jewish rhetoric from the upcoming Democrats?  You're not listening, or you're just watching CNN.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}\small Wahhh crys the \textbf{snowflake} Trump2020\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small Racist\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Democrats are socialists you f**** snowflake\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}\small Why are you so afraid of \textbf{nationalism} ?\textbf{Nationalism} is not Nazism.\textbf{Nationalism} is putting the interest of your country before any other, (sometimes at the depend of them) which is the most natural and logic thing to do.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/39 & \cellcolor{green!27}5.128 \\  \hline
  \cellcolor{green!5}\small Gigatony... there's a difference between \textbf{nationalism} and white nationalist\normalsize   & \cellcolor{green!5}Nationalism & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small \@WhiteWalkers I just looked the definition and i don't see how is that a wrong thing as along that white \textbf{nationalism} doesn't become supremacy...I mean every other nations that doesn't have a white majority has [ethnicity] \textbf{nationalism}.\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/38 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@WhiteWalkers but if you believe in \textbf{nationalism}......which I was taught that it means you have pride in your country and wouldn't want to be anywhere else because it is the best........that makes you a nationalist.  White nationalist comes across as being derogatory against white people and shaming them for having pride in their country.  It also makes it look like they want their country to be white-only when that should be labeled as "white supremacy".I feel like people hear Trump say he is a nationalist and right away people are quick to say......derrrrrrrr.......he a \textbf{nazi}........\textbf{racist}.....something-something.\normalsize   & \cellcolor{green!5}Nationalism, Nazi, Racist & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - General, Nationality - General & \cellcolor{green!5}3/96 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small White and \textbf{Black} and Hispanic Nationalists....Gandi and Mandela were too..\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Curtis Brown stop being \textbf{blind} and \textbf{deaf} to facts trailer trash\normalsize   & \cellcolor{green!5}Blind, Deaf, Trailer trash & \cellcolor{green!5}Ethnicity - White, Physical Identity - Physical (and Mental) Impairments, Social Class - Working class & \cellcolor{green!5}4/11 & \cellcolor{green!5}36.364 \\  \hline
  \cellcolor{green!27}\small SNOOP Coleman ,, fuck dick , the \textbf{Nazi} dick who done the shooting in Pittsburgh hater trump , he call trump a Jew lover , on is  \textbf{Nazi} We'd Sit\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}2/30 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@Bobbo Morgan he did exist the only thing to debate on is whether you think he was the son of god or a regular guy. Im not religious just in case you call me a \textbf{bible basher} or sum shit\normalsize   & \cellcolor{green!5}Bible basher & \cellcolor{green!5}Religious Identity - Protestant & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}\small \@John Noneya HE STILL WAS A \textbf{RACIST} LIKE TRUMP \textbf{DUMB} A\$\$ \& NOW *MUTE*!!🆗😈👋👋✌😂😂😂\normalsize   & \cellcolor{green!27}Dumb, Racist & \cellcolor{green!27}Ethnicity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@Evangelist Baptist John Worley YOU'RE AN EVANGELIST BAPTIST HUH=*GOOGLE:ARE THE WHITE EVANGELICALS \textbf{RACIST},*KKK😈😈😈🆗🇺🇸✌\& *MUTE*!!🆗😈👋👋✌😂😂😂\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small \@Rolls Royce Network I'M THAT \textbf{NIGGAH} FROM NEW YORK CITY A'IGHT BUT ITZ ALL GOOD YO'!!🐶🐶✊😎💯💯💪💪🗽🗽🗽✌\normalsize   & \cellcolor{green!27}Niggah & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Deport all Terrorists Trumptards Back 2 \textbf{Nazi} Germany 😠💣💥\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small Racism\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}\small Its called Trump.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/83 & \cellcolor{green!5}2.41 \\  \hline
  \cellcolor{green!27}\small max smart people change, \textbf{racist} people aren't broken they're just damaged, it's called America, we love and forgive, we are one \textbf{nation}, indivisible, under god. There are bad apples in every \textbf{race}, but we won't let that divide us. United we stand, divided we fall.\normalsize   & \cellcolor{green!27}Nation, Race, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}3/45 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small this \textbf{dumb} ass mother fucker voted for a \textbf{woman} who eulogized a KKK member though.\normalsize   & \cellcolor{green!5}Dumb, Woman & \cellcolor{green!5}Gender - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/15 & \cellcolor{green!5}13.333 \\  \hline
  \cellcolor{green!27}\small It is up to us youth to eradicate the baby boomer generation and take back America on its progress that it was intended to do that was stalled for the last 40 years by the baby boomers. Join the \textbf{Nazi} and do your part in bringing forth national socialism for all.. not just for one greedy hypocrical  selfish generation who has robbed 3 generation after them of their time... end the maddnes. End the boomers.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}\small It's simply amazing that we're having service providers take down Gab and banning alt-right extremists from Twitter and Facebook as if that's going to solve the problem or be helpful in any way.  Haven't we learned our lessons about freedom of speech yet?  When you ban people from \textbf{common} platforms and confine them to corners, you encourage them to find smaller and smaller niches where they can self-affirm themselves and never find an opposing viewpoint within their own tight little circles, even turning to encouraged violence and agreement that violence is the answer.  What do you think happened with this guy going to Gab here?  Sweeping shit under the carpet never works, and makes the problem much worse over time.  The only solution to bad free speech is MORE free speech!  Wake up!\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/133 & \cellcolor{green!5}0.752 \\  \hline
  \cellcolor{green!27}\small \@Kingdoms Sounds like someone is jealous or just a lazy \textbf{fat} fuck\normalsize   & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small It real \textbf{mental} gymnastics to equate National Socialism with Trump! Yet ppl are still calling him a \textbf{NAZI} as if he's a secret Socialist or something... Can anyone explain this nonsense to me? He hates the left and Socialism!\normalsize   & \cellcolor{green!5}Mental, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/39 & \cellcolor{green!5}5.128 \\  \hline
  \cellcolor{green!27}\small \@Saor Alba Stop being a disappointment to the Scots ya \textbf{racist} wee gimp.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small \@Big Lurch...   I a not \textbf{racist}...  i am pointing out what the Jewish Talmud teaches... and that is supremacist  beliefs,  \textbf{racist} doctrine,  and disregard for all non Jews on the planet.....  use your own due diligence and investigate my claims if you think i'm lying......\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/45 & \cellcolor{green!5}4.444 \\  \hline
  \cellcolor{green!27}\small Catfish Jenkem   The left loves phony hate crimes.  Like the \textbf{lesbian} couple who spray painted their own home with anti - \textbf{lesbian} hate.    There have been 100s the last few years.\normalsize   & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Sexual Identity - Female homosexuality & \cellcolor{green!27}2/31 & \cellcolor{green!27}6.452 \\  \hline
  \cellcolor{green!5}\small \@BoomeR DoomeR CNN doesn't ever endorse nazism. I don't know what the hell alternate reality you've created but you're \textbf{crazy} and no one claims you.\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@END it's not about white power. It's about truth. I don't know how \textbf{old} you are, but I remember when CNN used to report news. Journalism is dead.\normalsize   & \cellcolor{green!27}Old & \cellcolor{green!27}Age - Over 65s & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small For real, look at the \textbf{race} and culture diversity comparison between the allied powers and axis powers, and then tell me why you believe the nazis were more compared to the kkk.. doesn't make sense with history..\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small The reason is that cnn pushes hate and trys \textbf{race} baiting on a daily basis\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@END ok \textbf{hillbilly} degenerate toothless clyde from alabama go crawl back under your rock.\normalsize   & \cellcolor{green!5}Hillbilly & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Scholoryteller has a playlist of videos tackling \textbf{racism}.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small If you're the President, and David Duke tweets that you support \textbf{nationalism} and support his cause, there is only one thing to do. You pick up your iPhone with your tiny, little hands, and you tweet, "I fully reject the support of David Duke, as well as the Klan, The Proud Boys, Neo-Nazis, Skinheads, and all \textbf{racist} hate groups. Do not vote for me. You have no place in our country." Then, you immediately stop using the term, "Nationalist", no matter what new connotation you want to attach to it, because it's a loaded term. It's totally unnecessary to use, especially in this political climate, so just fucking drop it.\normalsize   & \cellcolor{green!5}Nationalism, Racist & \cellcolor{green!5}Ethnicity - General, Nationality - General & \cellcolor{green!5}4/110 & \cellcolor{green!5}3.636 \\  \hline
  \cellcolor{green!27}\small \@MetalDetroit   I do not hate anyone based on their religion...  i merely presented some facts regarding what is stated in the Jewish Talmud...    again....instead of assuming i am a Jew hater you can use your own due diligence and investigate my claims,  "which happen to be \textbf{common} knowledge to most people that know what the fuck they are talking about regarding the subject" ......     leave your self concocted assumptions for your imagination and fact find,  it would serve you a whole lot better than to just paint me as a Jew hater....    the truth is there are many Jews i respect... Dr Norman Finkelstein among others....\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}\small ​\@Laraine B...   Perhaps it doesn't affect you....  but it sure affects your \textbf{nation}.   you soldiers have been fighting for a Zionist cause masquerading as "war on terror"   or some other nefarious deception...    your politics have been hi-jacked by special interests .. Israeli infiltration groups such as AIPAC.   The ZOA "Zionist  Organisation of America"  your politicians are Neo Con Zionists,  and while those Jews that have influxed into the Holy Land get lovely "at the expense of the US taxpayer"  funded condos in Tel Aviv  and ILLEGAL settlements in the West bank...and billions of US taxpayers hard earned dollars...   meanwhile   the residents at home in Flint Michigan drink lead instead,   Detroit decays  with desolation where the crack whores sell their body for another hit of that pipe and Skid row  looks like  the village of damned\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/135 & \cellcolor{green!5}0.741 \\  \hline
  \cellcolor{green!27}\small \@Noneshere Smack a Christian and they commiy genocide on your \textbf{race}. The Aztecs and Mayans know.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Catfish Jenkem TRUMPS FUCKING DAUGHTER IS JEWISH AND HIS GRANDSONS like why would he spew anti Semitic rhetoric just shut up u liberal cucks. This is obviously just to make trump look terrible before midterms. Oh ya all this really bad stuff is Happening 2 weeks before elections!? I'm sure.... but ya u guys will call me \textbf{crazy} because I don't believe everything msm puts out there lol cucks\normalsize   & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}\small \@BoomeR DoomeR Lol OK \textbf{Fritz}. Have fun getting your ass handed to you by America a second time.\normalsize   & \cellcolor{green!27}Fritz & \cellcolor{green!27}Nationality - German & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small Yeah its an \textbf{old} trick that anglo saxon capitalists use to fool the lower class ones. Blame the hated minority for the excesses of the capitalist system which they created in the first place. Its that simple really, blame those fuckers over there that way the low class scum wont come for our asses.\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}\small \@Jon Lenihan .  Why would Jewish people force people to become Jewish???  Unless you wish to marry a Jew of course..   "Ivanka Trump"  as just one example.....we all know the feeling among Jewish communities about marrying a Christian...lol... and in that example,  what happens to the Gods "chosen people"  mantra....  Ivanka chose herself to become a Jew....   \textbf{nothing} to do with being Gods chosen people whatsoever...   the whole thing is an absolute "conjob"   just like the state of Israel...\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small \@Heavy Pupper Plus a good part of the area which is now incorporated into the newly founded Zionist  state of Israel  established in"1948"   was NEVER part of the area of the Israelites in biblical times...  it seems like it's \textbf{nothing} more than an EXPANSIONIST project..   \textbf{imperialist} ,militaristic, where the Christian area of Bethlehem and Nazareth has Israeli Merkava tanks and checkpoints  "papers please"  resembling some warsaw ghetto nearby..  while the new condos with the swimming pools for the Israeli settlers keep popping up  courtosy of the US taxpayer regardless if they agree with it or not..........................fuckin robbery if you ask me...more like rape of the US taxpayer\normalsize   & \cellcolor{green!5}Imperialist, Nothing & \cellcolor{green!5} Ideological and Political Identity - General, Age - Youngsters & \cellcolor{green!5}2/107 & \cellcolor{green!5}1.869 \\  \hline
  \cellcolor{green!27}\small FetterzVonFett how can we have Unity when these haters all other \textbf{race} of people?\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small tRump has encouraged hatred and anti semetism since Charlottesville Virginia murders during those despicable riots.The bad side is the white supremacist side. tRump handpicked these \textbf{racist} nazis for his base; primed them with infowars, and other internet shills crap.Dictator tRump will not unite or fix anything.He must be stopped along with other haters.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}\small \@Jon Lenihan \@Jon Lenihan...Plus most Jews today are converts ,descended from converts to the religion and have ABSOLUTELY FUCKAL to do with the Hebrew tribes....  so AGAIN..  how does that fit in with the    "Gods chosen people" mantra ...     kinda fucks up the Israel is our homeland fallacy too   doesn't it???.....    it's all an absolute deception and anyone who thinks otherwise must think Ivanka Trump and all  the other millions of self chosen Jews are Gods chosen master \textbf{race} or something ...superior to the rest of us and deserve  a wee lovely condo with a swimming pool in Israel\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/99 & \cellcolor{green!27}1.01 \\  \hline
  \cellcolor{green!5}\small \@Maria Dowler You have an incorect definiton of Zionism.Zi·on·ist/ˈzīənəst/noun1.a supporter of Zionism; a person who believes in the development and protection of a Jewish \textbf{nation} in what is now Israel."the artist's parents were committed Zionists"Neither believe in the Talmund. Zionists just think that Jews should have land that they always owned.\normalsize   & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}\small \@Heavy Pupper Pilate was not going to order the crucifixion of Jesus and never wanted to...this is \textbf{common} knowledge for anyone who took the slightest interest in Bible class at school......   the reality is the crowds of JEWS that were baying for blood threatened uprising,    Pilate only ordered the crucifixion fearing the wrath of  Caesar if he lost control in the Holy Land......  you are trying to play your little Jewdi mind tricks and distort reality here..... "no surprises there though"\normalsize   & \cellcolor{green!27}Common & \cellcolor{green!27}Social Class - Working class & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}\small Zionist Jew Supremacist Maurice Samuel from his book titled "You Gentiles": "We Jews, we are the destroyers and will remain the destroyers. \textbf{Nothing} you can do will meet our demands and needs. We will forever destroy because we want a world of our own" Ya mean like that? Maybe?Or 100s of other quotes made by hyper \textbf{racist} Zio-Jew supremacist extremists?\normalsize   & \cellcolor{green!5}Nothing, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}2/61 & \cellcolor{green!5}3.279 \\  \hline
  \cellcolor{green!27}\small They already caught who did it... a \textbf{black} man. don't buy inot fake news, racisms is = to bigfoot\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}\small \@Peyton Bell I guess it's all about you, huh? \textbf{Nobody} else's beliefs matter?\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest if your "beliefs" are too hate then NO! Fuck no it doesn't matter.\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small Why should I shush when I'm right... Roseanne Barr.. a jew.. most of trump's family are jews. I'm convinced that trump is even a jew.most of trump's team are jews. Most of trump's sponsors are jews. the liberal youth hates that trump is giving Jews more power over isreal. When the youth liberal realize that they are \textbf{old} school Nazis and stop playing this deflecting game from a false dogma of it... and start accepting that they are indeed the nazis like the far left has told them that they are, then great things will happen. They just need to realize that the anti progress culture of today's America are the baby boomers..\normalsize   & \cellcolor{green!5}Old & \cellcolor{green!5}Age - Over 65s & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Engineers} Quest are you replying to a comment I made? I leave judgement to CNN. I just report the news ☺\normalsize   & \cellcolor{green!27}Engineers & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}\small \@Tracy Weber How?Romans did so if you want to be \textbf{racist} blame white Italians\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}\small Yes, the reason is its all being pushed by the left. \textbf{Racism} is the lefts baby. ALL of this is bullshit. Lies. \textbf{Racism} is almost non existent in this country. Its such a TINY party of the population. But CNN would want you to believe half the country is \textbf{racist}.\normalsize   & \cellcolor{green!27}Racism, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}3/50 & \cellcolor{green!27}6.0 \\  \hline
  \cellcolor{green!5}\small \@axelg5 And if your whole base of Argument is the rightwing Farrakhan argument. The left are neither Anti White nor Anti \textbf{Homosexual} nor Anti Jew. All things Farrakhan has been accused of being.\normalsize   & \cellcolor{green!5}Homosexual & \cellcolor{green!5}Sexual Identity - General & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}\small Youtube also lets people spew \textbf{Nazi} hate speech all the time too. BUT they attack and shut down channels that don't kiss Obama or the msm's ass.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}\small Yes because they are  profiteers That don't come out of their tight little circles but yet they want to call everyone else \textbf{racist} and prejudice\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}\small \@Marq LOECSTA you're not a Scot! You're a subsaharan \textbf{African}. Don't forget your place, boy!\normalsize   & \cellcolor{green!27}African & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}\small \@\textbf{Gerry} Adams TV Actually it was Pontius Pilate that ordered his arrest due to the fact the baying mob of bloodthirsty Jews threatened an uprising , Pilate in his fear of losing control and Caesars wrath capitulated to their demands..   it could be said that the baying bloodthirsty mob despised Jesus not so much for his claims about God and his teachings but in fact that Jesus was indeed vehemently outspoken against and opposed to the Jewish practice of USURY , which in reality is the Jewish ran banking system of today that creates the debt slave...  it is mentioned in the Bible of how Jesus flew of the handle at the temple at the money changers and lenders.. the Jews had him marked for death because of it...    the Romans had no intention of killing Jesus and never seen his as a criminal or threat it was th fact Pilate shat himself at the thought of his master in Romes wrath of losing control of the area in Jewish uprising....\normalsize   & \cellcolor{green!5}Gerry & \cellcolor{green!5}Nationality - German & \cellcolor{green!5}1/171 & \cellcolor{green!5}0.585 \\  \hline
  \cellcolor{green!27}\small ​ Sorry i can't agree with you're supremacist views..   same shit the Talmud teaches those that follow that piece of \textbf{racist} literature you seem chose a "Herrenvolk" ideology for yourself also....\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small \@Trust me, I'm not a fed! I'm promise! who the fuck says I'm not Scottish! I was born here ya fucking cockwomble. Fyi I'm not \textbf{African} you utter pleb. My dad is Jamaican. Are you wanting knocked out then sexually assaulted you piece of shit\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small Gregory Lang piss off snowflake\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small \@Saor Alba don't forget Bolsheviks,  look at the utopian state they created in Soviet Russia.. It only took 10s of millions to die..they just pretended they had \textbf{nothing} to do with it and moved onto Zionism,  but they are sure about this one's success\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}\small Our forefathers believed in a \textbf{nation} of free white men with good character.\normalsize   & \cellcolor{green!27}Nation & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Arent the Demoncrats Socialists? Ask Bernie Slanders what he has in \textbf{common} with National Socialist German Workers party (\textbf{NAZI})\normalsize   & \cellcolor{green!5}Common, Nazi & \cellcolor{green!5} Ideological and Political Identity - General, Social Class - Working class & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small \@\textbf{Zero} Sum: Look up capitalism: social market economy . Fair compromise?\normalsize   & \cellcolor{green!27}Zero & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Iridescent ink funny I forgot that \textbf{black} people were slaves and natives were enslaved and European white men thought and believed they were superior to \textbf{black} people and natives.\normalsize   & \cellcolor{green!5}Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/29 & \cellcolor{green!5}6.897 \\  \hline
  \cellcolor{green!27}\small You can be a nationalist and not a \textbf{Nazi} moron.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small Americans only started fighting nationalists because Japan sided with Germany and had attacked America. We have to remember that there big \textbf{Nazi} rallies in Washington DC. So their forefathers might have been goosestepping around in DC.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}\small If you're the President, and David Duke tweets that you support \textbf{nationalism} and support his cause, there is only one thing to do. You pick up your iPhone with your tiny, little hands, and you tweet, "I fully reject the support of David Duke, as well as the Klan, The Proud Boys, Neo-Nazis, Skinheads, and all \textbf{racist} hate groups. Do not vote for me. You have no place in our country." Then, you immediately stop using the term, "Nationalist", no matter what new connotation you want to attach to it, because it's a loaded term. It's totally unnecessary to use, especially in this political climate, so just fucking drop it.  You don't argue semantics. You don't double down. You don't blame the press for painting you in a negative light, (especially when you coordinate with the biggest right-wing network news outlet there is. Sean Hannity practically has a fucking desk in the White House.) By the way, if he's going to say, "fake news" 20 times a day, he needs to add two pieces of information   to these accusations - 1) WHO in the media said something "false"? 2) WHAT, SPECIFICALLY, is "false"?\normalsize   & \cellcolor{green!27}Nationalism, Racist & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}4/193 & \cellcolor{green!27}2.073 \\  \hline
  \cellcolor{green!5}\small I remember the good \textbf{old} days when they would hang \textbf{colored} people. I pray that those days come back.\normalsize   & \cellcolor{green!5}Colored, Old & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Ryan Smith you are using the term "nationalist" wrong in the sense Trump spoke. Our forefathers didn't have nazis. They had the British. People often refer to the US as the most superior \textbf{nation} in the world. No different to what Trump said. He believes in putting the US first over other countries. You can be a National Socialist without being a \textbf{Nazi}. Look at the left. Bernie Sanders, a large percentage of Democrats.\normalsize   & \cellcolor{green!27}Nation, Nazi & \cellcolor{green!27} Ideological and Political Identity - General, Nationality - General & \cellcolor{green!27}2/74 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}\small Alex Hamilton  [LINK] forefather nounfore·​fa·​ther | \ˈfȯr-ˌfä-t͟hər  /Definition of forefather 1 : ANCESTOR sense 1a2 : a person of an earlier period and \textbf{common} heritageYou're thinking of the founding fathers.\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@Kingdoms The \textbf{nazi} party was created by the Zionist jews and Hitler was a controlled opposition Zionist himself who killed non Zionist Jews who were opposed to the creation of Israel.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}\small Iridescent ink The Statue of Liberty isn't the constitution you \textbf{dumb} Fuck 😂 we don't go by what the Statue of Liberty says.\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}\small Iridescent ink \textbf{nationalism} never once destroyed the world. All of history is \textbf{nationalism}. There's never been a country that wasn't nationalist and also survived\normalsize   & \cellcolor{green!27}Nationalism & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small \@J Groovy ...the Proud Boys are not \textbf{racist}, dumbshit. Ever heard of 'Tiny Toese'? He among many others are not white at all. The proud boys fight the radical leftwing fascist hate group known known antifa. That is the sole reason for their existence in the first place.While you're listing all the hate groups you forgot to list the much larger number of leftwing anti white hate groups. But of course those of you on the left are ok with \textbf{racism} as long as it's directed at white people.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/90 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}\small \@Curtis Brown The KKK was created by Albert Pike a Republican. Its membership came from all political backgrounds. Stop defending Trump.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!27}Black, Nation & \cellcolor{green!27}Ethnicity - Black, Nationality - General & \cellcolor{green!27}2/101 & \cellcolor{green!27}1.98 \\  \hline
  \cellcolor{green!5}\small \@max smart trumptards will deny the facts you mentioned. Gaining knowledge is an \textbf{alien} concept to them, unless it's hammered into their puny brains  by fox news, Breitbart, the blaze and infowars.\normalsize   & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality - General & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}\small \@Opal Beifong Civil rights violations Trump company:In 1973, the U.S. Department of Justice's (DOJ) Civil Rights Division filed a civil rights suit against The Trump Organization charging that it refused to rent to \textbf{black} people. The National Urban League had sent \textbf{black} and white testers to apply for apartments in Trump-owned complexes; the whites got the apartments, the blacks did not. According to court records, four superintendents or rental agents reported that applications sent to the central office for acceptance or rejection were coded by \textbf{race}.\normalsize   & \cellcolor{green!27}Black, Race & \cellcolor{green!27}Ethnicity - Black, Ethnicity - General & \cellcolor{green!27}3/87 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small wonder if you realize you voted for a \textbf{woman} who eulogized a KKK member?I'm waiting soy boi\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small Andi amo Wrote in Bernie, Trumpflake. I'm not a liberal, I'm a conservative that's tired of idiots like you making 'Hurr Durr Triggered Cuckflake' the modern debate, and turning MY party into a bigoted, \textbf{racist} joke. We've lost any moral high ground on the Dems, something we used to have in spades. Your not a conservative, your a neckbeard who showed up from 4chan to vote for a troll candidate because you thought it was funny.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5}\small \@SamoaVsEverybody 814 ™ 2.0 Just like a stupid \textbf{libturd}. The exact opposite of facts. Read a book dumbass. The losing confederate army created the KKK you imbecile. And if you're from Samoa, lots of those people are \textbf{dumb} as shit. I served with them and lots were as \textbf{dumb} as dirt.\normalsize   & \cellcolor{green!5}Dumb, Libturd & \cellcolor{green!5} Ideological and Political Identity - General, Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}3/50 & \cellcolor{green!5}6.0 \\  \hline
  \cellcolor{green!27}\small sorry the American public isn't buying your nonsense but you are entertaining.  Keep it up, \textbf{snowflake} :)\normalsize   & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small You mean Zionist AshkeNAZI candidate you \textbf{dumb} knuckle dragging buffoon\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small Ah, you mean the father of a Jewish daughter and son in law? You mean a good friend of Benjamin Netanyahu for over 25 years? You mean the most pro Israel and pro Jewish president im US history? How on earth would \textbf{Nazi} scum support the most prolific Zionist in US history?\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}\small \@Melinda Virosteck ...that's how you absolve yourself and the Democrat party of decades of abject \textbf{racism} and the creation of the KKK? Oh yeah, back in the 60s all the "\textbf{racist}" democrats just magically left the democrat party became Republicans....hahaha. How many are you talking about, 5, 10, 50? That is \textbf{nothing} more than an urban legend that literally never happened.Remember Grand Wizard Sen Robert Bird (D), West Virginia? He was a Democrat Senator up until he died while still holding office in 2010.\normalsize   & \cellcolor{green!5}Nothing, Racism, Racist & \cellcolor{green!5}Age - Youngsters, Ethnicity - General & \cellcolor{green!5}3/85 & \cellcolor{green!5}3.529 \\  \hline
  \cellcolor{green!27}\small \@max smart ...the Poway shooter John Earnest is 19 years \textbf{old}, not registered to vote, not a member of the Republican party, not a member of the NRA, and hated Trump because he considers him a "pro Zionist traitor".\textbf{Nothing} you posted in this thread has any basis in fact. Typical leftist propaganda. You're  what Saul Alinski called a "useful idiot".\normalsize   & \cellcolor{green!27}Nothing, Old & \cellcolor{green!27}Age - Over 65s, Age - Youngsters & \cellcolor{green!27}2/61 & \cellcolor{green!27}3.279 \\  \hline
  \cellcolor{green!5}\small Thanks trump for giving the thumbs up to the Nazis  Edit : the \textbf{snowflake} magatards can't read 😂😂😂 stage 4 brain cancer is all over my replies\normalsize   & \cellcolor{green!5}Snowflake & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small Trump is the one that called these Nazis "fine people" when they killed that \textbf{woman} at CharlottesvilleWhy can't he say it as it is? RIGHT WING TERRORISM\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}\small \@Curtis Brown Stop defending him.Trump stole all his policies from David Duke and the KKKTrump stole his slogans from the 1920s KKK America First and MAGA both KKK slogans.Trumps dad Fred was in the KKK and arrested in 1927 for beating a \textbf{black} man and police in his KKK robes at a klan rally.Trump was charged with Civil rights violations for Refusing to allow blacks to rent or buy in his buildings.The man is toxic destroying the \textbf{nation} from within..\normalsize   & \cellcolor{green!5}Black, Nation & \cellcolor{green!5}Ethnicity - Black, Nationality - General & \cellcolor{green!5}2/85 & \cellcolor{green!5}2.353 \\  \hline
  \cellcolor{green!27}\small That \textbf{Nazi} Graffiti looks like the CNN logo.\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small \@Darrin Rentruc but he did vote for trump. Didn't you see \textbf{Nazi} Richard Spencer's rally saying "hail trump" while doing the \textbf{Nazi} salute?\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small You are so \textbf{g\textbf{ay}} haha. MAGA\normalsize   & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity - General, Sexual Identity - Male homosexuality & \cellcolor{green!27}2/6 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}\small \@colonel 100 The \textbf{Dim} witted Libtards still think that Trump called Nazis fine people? Oh man, America is in trouble.\normalsize   & \cellcolor{green!5}Dim & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}\small \@colonel 100 I hope you are not that easily convinced by the lying fake news media. President Trumps Son in law is a Jew, President Trump fights on the side of Israel and there president Netanyahu loves Trump. Do you really believe the president of Israel would support a \textbf{Nazi}?  You can not possibly be that ignorant of the facts\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}\small \@B. Stone haha ok \textbf{leftard}. You guys are losing.\normalsize   & \cellcolor{green!5}Leftard & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}\small The only living \textbf{Nazi} I know of, is George Soros. 🇮🇱\normalsize   & \cellcolor{green!27}Nazi & \cellcolor{green!27} Ideological and Political Identity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small \@Blob Fatterson I don't think trump is hitler, at least hitler had the balls to serve his country.Other than that they're both \textbf{racist} \textbf{old} cunts.\normalsize   & \cellcolor{green!5}Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - General & \cellcolor{green!5}2/26 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}\small You're means "you are " and your means "belonging to you" first learn to spell \textbf{dumb} magatard\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}\small \@Big Papa Parker he deported a \textbf{Nazi} hiding in new york. o bama wasn't bothered.\normalsize   & \cellcolor{green!5}Nazi & \cellcolor{green!5} Ideological and Political Identity - General & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}\small What a cheap way to try and win an election. Enjoy the \textbf{r\textbf{ed}} wave\normalsize   & \cellcolor{green!27}Red & \cellcolor{green!27} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!27}2/14 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@J Bell \textbf{r\textbf{ed}} wave? What state is turning \textbf{r\textbf{ed}} 😂😂\normalsize   & \cellcolor{green!5}Red & \cellcolor{green!5} Ideological and Political Identity - General, Ethnicity - Native-American & \cellcolor{green!5}4/10 & \cellcolor{green!5}40.0 \\  \hline
  \cellcolor{green!27}\small they just caught the spray painter a \textbf{black} man..\normalsize   & \cellcolor{green!27}Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}\small colonel 100 Trump keeps winning and Republicans keep winning! All you have  is a salty mentality hidden away in YouTube comments. You gonna take a poo poo  In your pants when he's re elected?\textbf{Nothing} you say or do will change the fact he will be serving two terms...Enjoy😁\normalsize   & \cellcolor{green!5}Nothing & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racist, Race, Racism, Ethnic, Ethnicity & \cellcolor{red!27}405 & \cellcolor{red!27}405/127499& \cellcolor{red!27}0.32 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Red, Apple, Indian & \cellcolor{red!5}33 & \cellcolor{red!5}33/127499& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - French}  & \cellcolor{red!27}Frog, Froggy & \cellcolor{red!27}2 & \cellcolor{red!27}2/127499& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5} Ideological and Political Identity - General}  & \cellcolor{red!5}Communist, Red, Nazi, Snowflake, Libtard, Commie, Imperialist, Libturd, Leftard & \cellcolor{red!5}308 & \cellcolor{red!5}308/127499& \cellcolor{red!5}0.24 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - General}  & \cellcolor{red!27}Gay, LGBT, Homophobia, Homosexual & \cellcolor{red!27}16 & \cellcolor{red!27}16/127499& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Male homosexuality}  & \cellcolor{red!5}Gay, LGBT, Fruit, Faggot & \cellcolor{red!5}17 & \cellcolor{red!5}17/127499& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationalism, Nation, Engineers, Migrant, Xenophobia, Refugee, Nationality, Immigrant, Alien & \cellcolor{red!27}163 & \cellcolor{red!27}163/127499& \cellcolor{red!27}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}48 & \cellcolor{red!5}48/127499& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Protestant}  & \cellcolor{red!27}Spike, Bible basher & \cellcolor{red!27}27 & \cellcolor{red!27}27/127499& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - General}  & \cellcolor{red!5}Age & \cellcolor{red!5}9 & \cellcolor{red!5}9/127499& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Age - Youngsters}  & \cellcolor{red!27}Nothing, Zero, Nobody, Twerp, Brat, Zilch & \cellcolor{red!27}178 & \cellcolor{red!27}178/127499& \cellcolor{red!27}0.13999999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Dumb, Crazy, Weirdo, Weird, Lame, Mental, Blind, Freak, Mong, Loony, Lunatic, Disabled, Dim, Mongoloid, Deaf & \cellcolor{red!5}148 & \cellcolor{red!5}148/127499& \cellcolor{red!5}0.12 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Negro, Black, African, Nigger, Nigga, Spade, Crow, Jim Crow, Colored, Ape, Buck, Fuzzy, Niggah & \cellcolor{red!27}230 & \cellcolor{red!27}230/127499& \cellcolor{red!27}0.18 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Coarse, Common, Hillbilly, Trailer trash & \cellcolor{red!5}32 & \cellcolor{red!5}32/127499& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Ho & \cellcolor{red!27}4 & \cellcolor{red!27}4/127499& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - General}  & \cellcolor{red!5}Sex, Woman, Sexual, Gender, Sexism, Misogyny, Chick & \cellcolor{red!5}50 & \cellcolor{red!5}50/127499& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}27 & \cellcolor{red!27}27/127499& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - German}  & \cellcolor{red!5}Jerry, Fritz, Gerry & \cellcolor{red!5}7 & \cellcolor{red!5}7/127499& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Chinese}  & \cellcolor{red!27}pussy, ABC, Yellow & \cellcolor{red!27}16 & \cellcolor{red!27}16/127499& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Nationality - Southern European}  & \cellcolor{red!5}PIGS & \cellcolor{red!5}2 & \cellcolor{red!5}2/127499& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - European or anti-Europeans}  & \cellcolor{red!27}Brexit & \cellcolor{red!27}1 & \cellcolor{red!27}1/127499& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Religious Identity - Jewish}  & \cellcolor{red!5}Oven, dodger & \cellcolor{red!5}4 & \cellcolor{red!5}4/127499& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Asian (South- India, Pakistan, Bangladesh)}  & \cellcolor{red!27}Dot & \cellcolor{red!27}1 & \cellcolor{red!27}1/127499& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Sexual Identity - Transexuality}  & \cellcolor{red!5}Transition, LGBT, Transgender, Transsexual & \cellcolor{red!5}8 & \cellcolor{red!5}8/127499& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Bald, Obese, Thin, Fat, Skinny & \cellcolor{red!27}11 & \cellcolor{red!27}11/127499& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam)}  & \cellcolor{red!5}Yellow & \cellcolor{red!5}5 & \cellcolor{red!5}5/127499& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - Japanese}  & \cellcolor{red!27}Yellow & \cellcolor{red!27}5 & \cellcolor{red!27}5/127499& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female age and physical appearance}  & \cellcolor{red!5}Witch & \cellcolor{red!5}2 & \cellcolor{red!5}2/127499& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Religious Identity - Christian}  & \cellcolor{red!27}Bible thumper & \cellcolor{red!27}1 & \cellcolor{red!27}1/127499& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - White}  & \cellcolor{red!5}Hick, Trailer trash & \cellcolor{red!5}3 & \cellcolor{red!5}3/127499& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity - Female homosexuality}  & \cellcolor{red!27}Lesbian & \cellcolor{red!27}3 & \cellcolor{red!27}3/127499& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - General;Ethnicity - Native-American;Nationality - French; Ideological and Political Identity - General;Sexual Identity - General;Sexual Identity - Male homosexuality;Nationality - General;Age - Over 65s;Religious Identity - Protestant;Age - General;Age - Youngsters;Physical Identity - Physical (and Mental) Impairments;Ethnicity - Black;Social Class - Working class;Gender - Female sexuality;Gender - General;Religious Identity - Muslim;Nationality - German;Nationality - Chinese;Nationality - Southern European;Nationality - European or anti-Europeans;Religious Identity - Jewish;Ethnicity - Asian (South- India, Pakistan, Bangladesh);Sexual Identity - Transexuality;Physical Identity - Physical Features;Ethnicity - Asian (East- China, Japan, Korea, Philippines, Vietnam);Nationality - Japanese;Gender - Female age and physical appearance;Religious Identity - Christian;Ethnicity - White;Sexual Identity - Female homosexuality;%.

\item The percentage of hate speech related words is 1.3851.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 1768/4933 occurences of hate speech related comments.\end{itemize}\end{document}