\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In youtube\_extraction\_english\_292.json :}\newline \par\Large\textbf {Title: \large  Congresswoman Makes Racist Native American 'War Cry' }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small This isn't \textbf{racism}, this is stereotypes. Big difference.\normalsize   & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small ðŸ‘‹ Indians in America should be holding seats in every state and federal governments. Not Mexicans . Sanchez is not \textbf{Indian} . And what makes me mad is Mexicans are getting buy pretending to be \textbf{Indian} musicians . Try to find \textbf{Indian} musicians. All you get are people below the border . Only a few are recognized as \textbf{Indian} . They too are stealing what is not theirs from the Indians in America And Peruvians not America \textbf{Indian} .And neither is a Mexican\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}5/83 & \cellcolor{green!5}6.024 \\  \hline
  \cellcolor{green!27}\small Native American not Indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small I'm shocked... how sensitive some native Americans are and unable to laugh about themselves sometimes, too. People that are triggered by every little action are so annoying just stay relaxed for once. And everyone who wants to accuse me of \textbf{racism} now, just do so because i don't care no more since \textbf{racist} is used to describe literally any joke that may be slightly, slightly offensive to one sad person living out there. Cry me a river.\normalsize   & \cellcolor{green!5}Racism, Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/77 & \cellcolor{green!5}2.597 \\  \hline
  \cellcolor{green!27}\small Why are people so \textbf{racist} to native Americans we came and stole parts of their land and we are jerks to them and we have them live in reservations\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}\small Native American not \textbf{Indian} they find it offensive\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Everyone in America is a half \textbf{Indian} these days, everyone wants those virtue points\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small Doesn't matter. They see us as a dead \textbf{race}. We are ghosts living in the present...\normalsize   & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small Kamala Harris is \textbf{racist} af too. So her opinion is worthless.\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Respect for native \textbf{Indian} people and culture â¤â¤â¤â¤â¤â¤â¤â¤â¤â¤â¤â¤â¤ðŸ’ªðŸ’ªðŸ’ªðŸ’ªðŸ’ªðŸ¤ðŸ¤ðŸ¤ðŸ’ªðŸ’ªðŸ’ªðŸ’ªðŸ’ªðŸ’ªðŸ’ªðŸ’ª\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Native american* india is a country and \textbf{indian} is a person who lives in india. Oh come on..\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}\small You know what white \textbf{chick} I feel affened by you cause I'm native and your a washto\normalsize   & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}\small Why am i not suprised to hear a politician say the speak these words, well beside a very small percentage of politicians that would not say stuff like idiot the rest of them do not care about the american pepole they just care about getting their big pay check and the power that goes with it and the control, but i also feel sorry for them cause to keep their jobs they must and i repeat they must kiss the highest asses that run not just the U.S but the whole world and these pepole are known as the elite, secret societies and by many more names these politicians are bound to do what ever these elite tell them to do and if they do not do what they are told to do on their hand and knees then there is a chance they might not be found no where (R.I.P.) me personally i would rather die standing up then on my knees all these criminals are \textbf{nothing} less than world destroyers.  The initials NWO stands for Never  Will  Occur.\normalsize   & \cellcolor{green!27}Nothing & \cellcolor{green!27}Age - Youngsters & \cellcolor{green!27}1/180 & \cellcolor{green!27}0.556 \\  \hline
  \cellcolor{green!5}\small This \textbf{woman} is the epitome of ignorant...\normalsize   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender - General & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}\small Isaiah loc13 but not Native American Indian\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small \@laprinciac924 I don't know how you meant it but its usually Indians who are offended at the mixup, not the other way around. But it's because the proper name is for them and not because they have any \textbf{racist} thoughts on Natives. Anyways, you are \textbf{black}, so how would you know any of this?\normalsize   & \cellcolor{green!5}Black, Racist & \cellcolor{green!5}Ethnicity - Black, Ethnicity - General & \cellcolor{green!5}2/54 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}\small HISTORICALLY, YOU DO NOT KNOW ANCIENT \textbf{AFRICAN} HISTORY. THE PALEOAMERICANS ( KHOISANS) MIXED THEIR BLOOD WITH THE MONGOLIAN ASIANS AND PRODUCED THE \textbf{BLACK} NATIVE AMERICANS ( AFRO - AMERICANS).\normalsize   & \cellcolor{green!27}African, Black & \cellcolor{green!27}Ethnicity - Black & \cellcolor{green!27}2/29 & \cellcolor{green!27}6.897 \\  \hline
  \cellcolor{green!5}\small About 50-65 of Mexico's population is half native and 2/3 white and the rest \textbf{black} or northern \textbf{African} lol\normalsize   & \cellcolor{green!5}African, Black & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  \cellcolor{green!27}\small Robert Lance so she's being disrespectful and \textbf{racist}!!\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small This is stupid she is east \textbf{Indian} not native actually Loretta is native she is mestizo lol dumbasses\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}\small dumb and dumberIdiocracy was right.\normalsize   & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small Very cool, now how this became a propaganda video for her adversary, "half \textbf{Indian}" Kamala Harris is another question though. Now, I will add, looking at both women's faces and last names, the one who is more native American is not exactly the victim here and all these political garbage has way too many layers of irony\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27}\small Heather Billy it's not \textbf{racist} lol\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}\small KAMALA HARRIS IS HALF-EAST \textbf{INDIAN}.  How ignorant you jerks are. Get it straight. How embarrassing.  Native American and \textbf{Indian} are NOT THE SAME!!!\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}2/23 & \cellcolor{green!5}8.696 \\  \hline
  \cellcolor{green!27}\small What do you mean by \textbf{thin} skinned trha I'm a Native American\normalsize   & \cellcolor{green!27}Thin & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Native Americans are this \textbf{thin} skinned? Grow up.\normalsize   & \cellcolor{green!5}Thin & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small trha2222 what is \textbf{thin} skinned\normalsize   & \cellcolor{green!27}Thin & \cellcolor{green!27}Physical Identity - Physical Features & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small A native American is ANY American BORN IN America!! The term native American used to describe only American Indians is a relatively recent phenomenon in the history of America and is a result of the ignorance, madness, and lies of political correctness. Those who practice the ignorance, madness and lies of political correctness do not get to redefine the word native, and in the process insult every other native American that is not American \textbf{Indian}!!Approximately 90 of ALL AMERICANS are native American!! American Indians it is great for you all to be proud to be a part of such an amazing country and whatever tribe you associate with, but please don't resort to ignorance and \textbf{racism} in using the term native American while excluding other fellow native Americans who are not American \textbf{Indian}. It is at best being ignorant and at worst being \textbf{racist}.The ignorance, madness, and lies of political correctness will destroy America if Americans do not take a stand for what is true.\normalsize   & \cellcolor{green!5}Indian, Racism, Racist & \cellcolor{green!5}Ethnicity - General, Ethnicity - Native-American & \cellcolor{green!5}4/167 & \cellcolor{green!5}2.395 \\  \hline
  \cellcolor{green!27}\small What about indigenous, or aboriginal? I understand that every single one of us in native to this land, but won't those terms be correct? It's describing to every other \textbf{race} as well. Not just them. Well whether you agree or not, I still hope you have a nice day.\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}\small American \textbf{Indian} isn't the correct term either. Indians are from India. Lets start calling white Americans "Russian Americans" regardless of their ancestry.\normalsize   & \cellcolor{green!5}Indian & \cellcolor{green!5}Ethnicity - Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}\small lol stupid Latino woman\normalsize   & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender - General & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}\small Sanchez might be Mexican, a \textbf{common} misconception, they are not Latino\normalsize   & \cellcolor{green!5}Common & \cellcolor{green!5}Social Class - Working class & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}\small \@Josh Guevara hunny I'm not meaning to offend anyone but she's a \textbf{racist}. I'm native American and I really don't care what \textbf{race} she is she's rude.\normalsize   & \cellcolor{green!27}Race, Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}2/27 & \cellcolor{green!27}7.407 \\  \hline
  \cellcolor{green!5}\small Racist??????? Certain tribes use to DO this!!!!! hahahahahahahahahahahaha\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small Lol your mom is a nasty thot\normalsize   & \cellcolor{green!27}THOT & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}\small Sure she will, \textbf{nobody} cares, a lot think it's funny..You think way to much of yourself.\normalsize   & \cellcolor{green!5}Nobody & \cellcolor{green!5}Age - Youngsters & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}\small When it comes to ANY remarks regarding \textbf{race}, every politician needs to be VERY self-aware. Anything less is just being stupid, like this woman\normalsize   & \cellcolor{green!27}Race, Woman & \cellcolor{green!27}Ethnicity - General, Gender - General & \cellcolor{green!27}2/24 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}\small Why does this \textbf{hag} think people are going to believe the mistake card? Yeah, no. You're just a \textbf{racist} cow.\normalsize   & \cellcolor{green!5}Hag, Racist & \cellcolor{green!5}Ethnicity - General, Gender - Female age and physical appearance & \cellcolor{green!5}2/20 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}\small How is that \textbf{racist} haha\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}\small Lol what a \textbf{dumb} bitch\normalsize   & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}\small She's Mexican herself so she's Mestizo, how is she \textbf{racist}?\normalsize   & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}\small \@Surq Madeeq Muhammed are you really so stupid that you actually think that because she has a spanish last name that she can't be \textbf{racist}?  That's foolish, Surq.  Plus she ain't no real mexican she's fucking white.\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}\small \@Bigga Numba Six Thats a true Mexican being white also. There are many Mexican people who are white and remember its a \textbf{nationality} not a \textbf{race}.\normalsize   & \cellcolor{green!27}Nationality, Race & \cellcolor{green!27}Ethnicity - General, Nationality - General & \cellcolor{green!27}2/26 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}\small Opps I was \textbf{racist}! Native guy come here!\normalsize   & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}\small \@rtswift  She's not white she's the daughter of Mexican \textbf{immigrant}, she's Mestizo in origin.\normalsize   & \cellcolor{green!27}Immigrant & \cellcolor{green!27}Nationality - General & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}\small \@Surq Madeeq Muhammed those are the most deceptive whites. they act like they are \textbf{colored} but in all reality they are just spanish blood. kinda like how all of the Telemundo stars are white.\normalsize   & \cellcolor{green!5}Colored & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}\small \@peterpiperdiedharper what I was alluding to was the unnecessary nitpicking and persecution between political ideologies, AJ+ is a very liberal outlet and this is just a little act of stupidity that this organization is trying to turn into a big deal. I did that very same act in kindergarten when we were learning about the Native Americans, my guess is in that moment she couldn't think of another way to differentiate the Asian \textbf{Indian} and American \textbf{Indian} cultures and just goofed, and it is very obvious that she immediately regretted it. Even the American \textbf{Indian} lady they were interviewing didn't seem very upset about it.\normalsize   & \cellcolor{green!27}Indian & \cellcolor{green!27}Ethnicity - Native-American & \cellcolor{green!27}3/105 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}\small \@MrSquiggliesÂ i would not compare the act of a kindergartner to that of someone running for government office. She was embarrassed but, only because she got caught doing it. It may not be intentionally \textbf{racist}, but it speaks of what she usually thinks of Native Indians because, it was the first thing she used as an example. That's where the problem is, not what her color is, but her disposition towards a group of people based on what little knowledge she gathered from \textbf{old} western movies(perhaps). It's like the idea that people from Texas are gun wielding \textbf{hillbilly}, or \textbf{black} people are thugs playing loud hip hop in their cars. She is running for a major position, she has to know and understand the diversity of the people and the value of their \textbf{ethnicity}. Frankly, she seemed like a go getter in the small clip provided. Those who seek power are often the least suited to use it it seems, or sth like that.\normalsize   & \cellcolor{green!5}Black, Ethnicity, Hillbilly, Old, Racist & \cellcolor{green!5}Age - Over 65s, Ethnicity - Black, Ethnicity - General, Social Class - Working class & \cellcolor{green!5}5/164 & \cellcolor{green!5}3.049 \\  \hline
  \cellcolor{green!27}\small \@Askjey Hell Yeah and those overly sensitive Native Americans too. You tell em' ! Just as a rule of thumb , you probably should be a member of the group that is or isn't being insulted to make that call. That would be like saying it doesn't offend you when people call dwarfs midgets. If you are not a \textbf{dwarf}, you look like an ass.\normalsize   & \cellcolor{green!27}Dwarf & \cellcolor{green!27}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}\small What is she said, "I thought I was going to meet with 'thugs' when they said \textbf{African} Americans." Would you still be calling these people sensitive?\normalsize   & \cellcolor{green!5}African & \cellcolor{green!5}Ethnicity - Black & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}\small Pulls out the \textbf{race} card - gg political campaign\normalsize   & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racism, Racist, Race, Ethnicity & \cellcolor{red!27}25 & \cellcolor{red!27}25/3196& \cellcolor{red!27}0.7799999999999999 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity - Native-American}  & \cellcolor{red!5}Indian & \cellcolor{red!5}17 & \cellcolor{red!5}17/3196& \cellcolor{red!5}0.53 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - General}  & \cellcolor{red!27}Chick, Woman & \cellcolor{red!27}4 & \cellcolor{red!27}4/3196& \cellcolor{red!27}0.13 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Youngsters}  & \cellcolor{red!5}Nothing, Nobody & \cellcolor{red!5}2 & \cellcolor{red!5}2/3196& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity - Black}  & \cellcolor{red!27}Black, African, Colored & \cellcolor{red!27}8 & \cellcolor{red!27}8/3196& \cellcolor{red!27}0.25 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Dumb, Dwarf & \cellcolor{red!5}3 & \cellcolor{red!5}3/3196& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Identity - Physical Features}  & \cellcolor{red!27}Thin & \cellcolor{red!27}3 & \cellcolor{red!27}3/3196& \cellcolor{red!27}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Social Class - Working class}  & \cellcolor{red!5}Common, Hillbilly & \cellcolor{red!5}2 & \cellcolor{red!5}2/3196& \cellcolor{red!5}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}THOT & \cellcolor{red!27}1 & \cellcolor{red!27}1/3196& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Gender - Female age and physical appearance}  & \cellcolor{red!5}Hag & \cellcolor{red!5}1 & \cellcolor{red!5}1/3196& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality - General}  & \cellcolor{red!27}Nationality, Immigrant & \cellcolor{red!27}2 & \cellcolor{red!27}2/3196& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age - Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}1 & \cellcolor{red!5}1/3196& \cellcolor{red!5}0.03 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - General;Ethnicity - Native-American;Gender - General;Age - Youngsters;Ethnicity - Black;Physical Identity - Physical (and Mental) Impairments;Physical Identity - Physical Features;Social Class - Working class;Gender - Female sexuality;Gender - Female age and physical appearance;Nationality - General;Age - Over 65s;%.

\item The percentage of hate speech related words is 2.1589.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 73/167 occurences of hate speech related comments.\end{itemize}\end{document}