\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In Sol\_extraction\_portuguese\_149.json :}\newline \par\Large\textbf {Title: \large  O dia mais negro do Brasil }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small NÃ FOI POR FALTA DE AVISO PÁ!  MAS AINDA segundo algumas perspectivas TÃO SÓ NO COMEÇO PÁ! E NÃ QUERIAM DESTRUIR A AMAZÓNIA E COMUNIDADES DE ÍNDIOS BRASILEIROS? QUEM É QUE LEVOU COM QUASE TODA A FUMADA VINDA DA AMAZÓNIA? O estado de São Paulo PRATICAMENTE PÁ! AFINAL COVID-19 ADORA POLUIÇÃO E PORCARIA PÁ! POR ISSO SE DEU TÃO BEM EM WUHAN! <br/>PÁ NENHUM/A \textbf{BRASUCA} PODE DIZER QUE EUZINHA MAGDAZINHA NÃ TENHA AVISADO PÁ! E QUEM AVISA AMIGA É!\normalsize   & \cellcolor{green!27}Brasuca & \cellcolor{green!27}Nationality - Brazilian & \cellcolor{green!27}1/79 & \cellcolor{green!27}1.266 \\  \hline
  \cellcolor{green!5}\small ...olha que novidade! ...Tóquio, Seul, Singapura e Taiwan não são densamente habitadas?<br/>...a América tem um rácio de 150 óbitos por um milhão de habitantes e o \textbf{idiota} do Trump ainda acha que são poucos e exige que os governadores dos estados mais afetados acabem com o confinamento ...isto é uma atitude de um assassino \textbf{psicopata}!\normalsize   & \cellcolor{green!5}Idiota, Psicopata & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}2/55 & \cellcolor{green!5}3.636 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Nationality - Brazilian}  & \cellcolor{red!27}Brasuca & \cellcolor{red!27}1 & \cellcolor{red!27}1/1723& \cellcolor{red!27}0.06 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Idiota, Psicopata & \cellcolor{red!5}2 & \cellcolor{red!5}2/1723& \cellcolor{red!5}0.12 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Nationality - Brazilian;Physical Identity - Physical (and Mental) Impairments;%.

\item The percentage of hate speech related words is 0.1741.

\item Considering that the variable \textbf{Physical Identity - Physical (and Mental) Impairments} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 3/48 occurences of hate speech related comments.\end{itemize}\end{document}