\documentclass[11pt]{article}
\ExplSyntaxOn
\let\tl_length:n\tl_count:n
\ExplSyntaxOff
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=0.8in]{geometry}
\newcommand{\MinNumber}{0}
\begin{document}

\textbf {\huge In Sol\_extraction\_portuguese\_61.json :}\newline \par\Large\textbf {Title: \large  Suzana Garcia volta a comentar polémica: 'A minha avó é negra e a minha mãe é mulata' }\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{\textcolor{blue}{\underline{Table 2}}}: Summary of the results per sociolinguistic variable;}\newline \normalsize\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.65\mylength}|C{.30\mylength}|C{.12\mylength}|C{.12\mylength}|C{.12\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic variables (Hiper - Hipo)}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}\small Ela não é \textbf{racista}. Ela só comenta casos em que pessoas de outras raças agridem alguem. Agora mesmo está a passar um caso na tv em que, por "mera coincidência", ela não está no painel. Isso diz muito.\normalsize   & \cellcolor{green!27}Racista & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}\small A \textbf{Gorda} tem Pinta...:)\normalsize   & \cellcolor{green!5}Gorda & \cellcolor{green!5}Physical Identity - Physical Features & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Se lhe tirarem as partes que fazem mal ao colesterol, é um \textbf{ganda} naco de carne!!\normalsize   & \cellcolor{green!27}Ganda & \cellcolor{green!27}Gender - Female sexuality & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}\small Esta "miss piggy" deve ter mais tomates que tu, o teu papá e o teu avozinho todos juntos, \textbf{imbecil}...\normalsize   & \cellcolor{green!5}Imbecil & \cellcolor{green!5}Physical Identity - Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}\small Mas novela de pretalhada \textbf{racista}. O cheiro a katinga é insuportável.\normalsize   & \cellcolor{green!27}Racista & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}\small Estás a ser \textbf{racista}...\normalsize   & \cellcolor{green!5}Racista & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}\small Sim su o teu rabo caucasiano é \textbf{racista}.\normalsize   & \cellcolor{green!27}Racista & \cellcolor{green!27}Ethnicity - General & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}\small De \textbf{racista} para \textbf{racista}, tu ela e os vossos rabinhos caucasianos ficariam muito bem juntos á janela do coucha.\normalsize   & \cellcolor{green!5}Racista & \cellcolor{green!5}Ethnicity - General & \cellcolor{green!5}2/19 & \cellcolor{green!5}10.526 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.50\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Sociolinguistic variables (Hiper - Hipo)} & \textbf{KeyWords} & \textbf{Number of occurrences} & \textbf{Frequency}  & \textbf{Frequency(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Ethnicity - General}  & \cellcolor{red!27}Racista & \cellcolor{red!27}6 & \cellcolor{red!27}6/262& \cellcolor{red!27}2.29 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical Features}  & \cellcolor{red!5}Gorda & \cellcolor{red!5}1 & \cellcolor{red!5}1/262& \cellcolor{red!5}0.38 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender - Female sexuality}  & \cellcolor{red!27}Ganda & \cellcolor{red!27}1 & \cellcolor{red!27}1/262& \cellcolor{red!27}0.38 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical Identity - Physical (and Mental) Impairments}  & \cellcolor{red!5}Imbecil & \cellcolor{red!5}1 & \cellcolor{red!5}1/262& \cellcolor{red!5}0.38 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Ethnicity - General;Physical Identity - Physical Features;Gender - Female sexuality;Physical Identity - Physical (and Mental) Impairments;%.

\item The percentage of hate speech related words is 3.4351.

\item Considering that the variable \textbf{Ethnicity - General} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 9/24 occurences of hate speech related comments.\end{itemize}\end{document}